### 2021-08-01 notes.tex
created tex file

% !TEX TS-program = xelatex
\documentclass[twoside]{report}

\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec,geometry}
\usepackage[T1]{fontenc}
\usepackage[hidelinks,pdfusetitle]{hyperref}
\usepackage[stable]{footmisc}
\renewcommand{\arraystretch}{2}
\setlength\delimitershortfall{-2pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\fancyfoot[C]{\thepage}
\fancyhead[OL]{\nouppercase\leftmark}    
\fancyhead[ER]{\rightmark}
\setlength{\headheight}{52pt}
\setcounter{tocdepth}{1}
\DeclareMathOperator{\sech}{sech}
\raggedbottom
\numberwithin{equation}{section}
\allowdisplaybreaks

\title{Generating Hubbard Model Solutions from Anderson Impurity Model Solutions}
\author{Abhirup Mukherjee\\Dr. Siddhartha Lal}
\begin{document}
\maketitle

hi

\end{document}

### 2021-08-01 notes.tex
added introduction

@@
 % !TEX TS-program = xelatex
-\documentclass[twoside]{report}
+\documentclass[twoside]{article}
 
@@
 \title{Generating Hubbard Model Solutions from Anderson Impurity Model Solutions}
-\author{Abhirup Mukherjee\\Dr. Siddhartha Lal}
+\author{Abhirup Mukherjee, Dr. Siddhartha Lal}
 \begin{document}
 \maketitle
-
-hi
+\section{Introduction}
+This is an attempt to obtain solutions of the Hubbard model (groundstate wavefunction and ground state energy) using the solutions of the simpler single-impurity Anderson model (SIAM) (the models will be defined later).
+Broadly speaking, the method involves first solving the SIAM using a unitary renormalisation group approach, to get the ground state wavefunction and energy eigenvalue, and then combining these wavefunctions in a symmetrized fashion to get the wavefunction for the Hubbard model lattice.
+It is quite similar to dynamical mean-field theory (DMFT) in essence, but differs in practice.
+The similar part is the involvement of an impurity-solver.
+The difference, however, lies in the following points:
+\begin{itemize}
+	\item While DMFT primarily works with Green's functions and self-energies, this method involves Hamiltonians and wavefunctions.
+	\item The impurity-solver in DMFT provides an impurity Green's function (which is then equated with the local Green's function of the bath), while the impurity-solver in this method actually provides a wavefunction.
+	\item The final step of DMFT is the self-consistency equation, where the impurity and bath-local quantities are set equal.
+This ensures all sites, along with the impurity site, have the same self-energy, something which is required on grounds of  translational invariance.
+The present method, however, brings about the translational invariance in a different way.
+It symmetrizes the wavefunctions and Hamiltonians itself, such that all quantites then derived from the Hamiltonian or wavefunction are then guaranteed to have the symmetry.
+\end{itemize}
+The meaning of each of these statements will become clearer when we describe the method in more detail.
 

### 2021-08-01 notes.tex
added philosophy of method

@@
 % !TEX TS-program = xelatex
-\documentclass[twoside]{article}
-
+\documentclass{article}
 \usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec,geometry}
@@
 \fancyfoot{}
-\fancyfoot[C]{\thepage}
-\fancyhead[OL]{\nouppercase\leftmark}    
-\fancyhead[ER]{\rightmark}
+\fancyhead[L]{\nouppercase\leftmark}    
+\fancyhead[R]{\thepage}    
 \setlength{\headheight}{52pt}
@@
 \section{Introduction}
-This is an attempt to obtain solutions of the Hubbard model (groundstate wavefunction and ground state energy) using the solutions of the simpler single-impurity Anderson model (SIAM) (the models will be defined later).
+This is an attempt to obtain solutions of the Hubbard model (groundstate wavefunction and ground state energy) using the solutions of the simpler single-impurity Anderson model (SIAM).
+The models are defined using the Hamiltonians
+\begin{equation}\begin{aligned}
+H_\text{hubb} &= -t^H\sum_{\sigma,\left<i,j \right>}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right) + U^H\sum_i \hat n_{i \uparrow} \hat n_{i \downarrow} - \mu^H \sum_{i\sigma}\hat n_{i\sigma}\\
+	H_\text{siam} &= -t^A\sum_{\sigma,\left<i,j \right>\atop{i \neq d \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right) + \epsilon_d^A \sum_\sigma\hat n_{d\sigma} + U^A \hat n_{d \uparrow} \hat n_{d \downarrow} - \mu^A \sum_{i\neq d,\sigma}\hat n_{i\sigma}
+\end{aligned}\end{equation}
 Broadly speaking, the method involves first solving the SIAM using a unitary renormalisation group approach, to get the ground state wavefunction and energy eigenvalue, and then combining these wavefunctions in a symmetrized fashion to get the wavefunction for the Hubbard model lattice.
@@
 
+\section{Philosophy of the method}
+The method is closely tied to the auxiliary system approach described in \cite{martin_2016}.
+We can view the full Hamiltonian as a sum of two component Hamiltonians \(H_1, H_2\) connected via the interaction term \(H_{12}\).
+\begin{equation}\begin{aligned}
+	H = \begin{pmatrix} H_1 && H_{12} \\ H_{12}^* && H_2 \end{pmatrix} = H_1 \ket{1}\bra{1} + H_2\ket{2}\bra{2} + H_{12}\ket{1}\bra{2} + H_{12}^*\ket{2}\bra{1}
+\end{aligned}\end{equation}
+where \(\ket{1(2)}\) actually represents a sum over all basis kets of the subsystem 1(2).
+As an example, we can split the the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows:
+\begin{equation}\begin{aligned}
+	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_1} \\
+		      &+ \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_2}\\
+		      & -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{12} + H_{12}^*}\\
+\end{aligned}\end{equation}
+The Green's function of the full Hamiltonian can also be split in a similar fashion:
+\begin{equation}\begin{aligned}
+	G(\omega) = \begin{pmatrix} G_1 && G_{12} \\ G_{12}^* && G_2 \end{pmatrix} 
+\end{aligned}\end{equation}
+The subsystem 1 is usually taken to be the "smaller system", and consequently, subsystem 2 represents the "bath".
+The smaller system is typically chosen such that its eigenstates are known exactly.
+Progress is then made by choosing a simpler version of the bath \(H_2\) and a simpler form also for its coupling \(H_{12}\) with the smaller system.
+This combination of the smaller system and the simpler bath is then called the \textit{auxiliary system}.
+A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{12}\).
+
+The algorithm of DMFT then involves starting with some local self-energy of the bath, \(\Sigma(\omega)\), and using an impurity solver to calculate the impurity Green's function in the presence of this self-energy.
+This impurity Green's function is then used to calculate the impurity self-energy \(\Sigma_d(\omega)\), and the self-energy of the bath is then set equal to this impurity self-energy: \(\Sigma(\omega) = \Sigma_d(\omega)\), because we expect, on grounds of the lattice symmetry, that the impurity is the same as any other site in the bath.
+This is said to be the self-consistency step, because the bath self-energy is completely determined only at the end.
+With this updated bath self-energy, one then repeats the entire process until there is no further change in the bath self-energy at the self-consistency step.
+
+The present method intends to calculate the quantities in a different fashion.
+We start with a SIAM (possibly with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian.
+At the fixed-point, assuming the couplings are much larger compared to the kinetic energy, we can approximate the Hamiltonian by a zero-mode of the kinetic energy part, which leads to a two-site Anderson molecule Hamiltonian.
+Such a model is exactly solvable.
+Armed with such a groundstate, we will then create the wavefunction of the entire Hubbard Hamiltonian by combining them according to a prescription which is guided by the symmetries of the problem.
+The impurity electron will be read off as an arbitrary site, \(p\), of the lattice, while the zero-mode site becomes the site that is nearest to it.
+There are also integrals of motion that come out of the URG, they make up the rest of the sites in the lattice.
+We will first demonstrate this explicitly for the Hubbard dimer.
+Then we will show how we can create a full Hubbard Hamiltonian by joining Anderson molecule Hamiltonians, and this should hopefully be a step towards getting a general prescription for generating wavefunctions for the full lattice (not just dimers).
+
+\bibliographystyle{unsrt}
+\bibliography{notes}
 \end{document}

### 2021-08-01 notes.tex
added dimer-molecule transformations

@@
 
+\section{Solution of the Hubbard dimer using the Anderson molecule}
+The Hubbard dimer and Anderson molecules (zero-mode) are defined by the following respective Hamiltonians:
+\begin{equation}\begin{aligned}
+	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat n_{i \uparrow}\hat n_{i \downarrow} - \mu^H \sum_{\sigma, i=1,2}\hat n_{i\sigma}\\
+	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \epsilon_d^A \sum_{\sigma}\hat n_{d\sigma} + U^A\hat n_{d \uparrow}\hat n_{d \downarrow}
+\end{aligned}\end{equation}
+In the first Hamiltonian, the indices \(i=1,2\) refer to the two lattice sites that constitute the dimer.
+In the second Hamiltonian, the subscript \(d\) indicates the impurity site, while the subscript \(z\) indicates the zero-mode site.
+First, we will assume that the Hubbard dimer is at half-filling (\(\frac{1}{2}U^H = \mu^H\)):
+\begin{equation}\begin{aligned}
+	\label{hubb_dimer}
+	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \left(\frac{1}{2}U^H- \mu^H\right) \sum_{\sigma, i=1,2}\hat n_{i\sigma} + \text{constant}\\
+	    &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
+\end{aligned}\end{equation}
+Since the Hubbard Hamiltonian is at half-filling, we will also place the impurity at half-filling by setting \(\epsilon_d^A = -\frac{1}{2}U^A\):
+\begin{equation}\begin{aligned}
+	\label{and_dimer}
+	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \left(\epsilon_d^A + \frac{1}{2}U^A\right) \sum_{\sigma}\hat \tau_{d\sigma} + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow} + \text{constant}\\
+	    &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow}
+\end{aligned}\end{equation}
+The first step is to recreate the Hubbard dimer Hamiltonian eq.~\ref{hubb_dimer} using the Anderson molecule Hamiltonian eq.~\ref{and_dimer}:
+\begin{equation}\begin{aligned}
+	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
+	    &= \frac{1}{2}\left[-t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + t^H\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\right] + \frac{1}{2} 2U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
+	    &= \frac{1}{2}\left[-t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right)\bigg\vert_{z \to 2, d \to 1\atop{t^A \to t^H}} + t^A\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\bigg\vert_{d \to 2,z \to 1\atop{t^A \to t^H}} \right] \\
+	    &+ \frac{1}{2} \left(U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 1\atop{U^A \to 2U^H}} + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 2\atop{U^A \to 2U^H}}\right)\\
+	    &=\frac{1}{2}\left[H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 1, z \to 2\right) + H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 2, z \to 1\right)\right]
+\end{aligned}\end{equation}
+The conclusion we can draw from this is that the Hubbard dimer Hamiltonian can be obtained from the Anderson dimer Hamiltonian in the following fashion:
+\begin{itemize}
+	\item The essential idea is that we have to create a local Hubbard Hamiltonian for each site of the Hubbard lattice by replacing the impurity label \(d\) in the Anderson dimer with the label of the particular site.
+So if there are two sites, we will get two local Hamiltonians obtained by replacing \(d\) with 1 and 2 respectively.
+For each local Hamiltonian, the zero-mode label \(z\) is replaced by the site that is nearest to the one that \(d\) is being replaced by.
+So, if \(d \to 1(2)\), then \(z \to 2(1)\).
+	\item This, however, is not the only change that we must make, in order to get the local Hamiltonian for a particular site.
+Along with \(d\) and \(z\), we must also make the transformations \(t^A \to t^H, U^A \to 2U^H\).
+	\item Finally, once we have the local Hamiltonians for sites 1 and 2, we average them to get the total Hubbard Hamiltonian.
+\end{itemize}
+Note that we expect most of these "rules" to be specific for the dimer, and there will be generalizations to most of them for a general \(N-\)site Hubbard Hamiltonian.
+
+The wavefunctions for the \(N=2\) sector can also be connected through these transformations. Since both the Hamiltonians are analytically solvable, we can write down their groundstate wavefunctions:
+\begin{equation}\begin{aligned}
+	\ket{\Psi^H_\text{GS}} &= 4t^H\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) + \left[\Delta\left( U^H, t^H \right) - U^H\right]{\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
+	\ket{\Psi^A_\text{GS}} &= 4t^A\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) + \left[\Delta\left( \frac{1}{2}U^A, t^A \right) - \frac{1}{2}U^A\right]{\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
+	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right),\quad E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right), \quad\Delta(x,y) \equiv \sqrt{x^2 + y^2}\\
+\end{aligned}\end{equation}
+From the forms of the wavefunctions and eigenenergies, we can immediately write down
+\begin{equation}\begin{aligned}
+	\ket{\Psi^H_\text{GS}} &= \frac{1}{2}\left[\ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 1, z \to 2\right) + \ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 2, z \to 1\right)\right]\\
+	E^H_\text{GS} &= E^A_\text{GS}\left(t^A, U^A \to t^H, 2U^H\right)
+\end{aligned}\end{equation}
+This shows that the rules laid out before work for the Hamiltonians, as well as the wavefunctions and energy eigenvalues of the \(N=2,0,4\) sector.
+These sectors specifically work because it is only in these sectors can we ensure that \(n_d = n_z\), which is required for the Hubbard Hamiltonian because \(n_1 = n_2\).
+In the other sectors (\(N=1,3\)), the impurity site and the zero-mode sites have to be singly-occupied in some part, and since the impurity site incurs a single-occupation cost of \(-\frac{U^H}{2}\) which is not borne by the zero-mode site, there is an intrinsic dissimilarity between the two sites of the Anderson molecule in this regime.
+This dissimilarity does not exist for the Hubbard model, so we cannot hope to connect the two models in this regime.
+
 \bibliographystyle{unsrt}

### 2021-08-01 notes.tex
added general Hamiltonian mapping

@@
 \title{Generating Hubbard Model Solutions from Anderson Impurity Model Solutions}
-\author{Abhirup Mukherjee, Dr. Siddhartha Lal}
+\author{}%Abhirup Mukherjee, Dr. Siddhartha Lal}
 \begin{document}
@@
 
-The wavefunctions for the \(N=2\) sector can also be connected through these transformations. Since both the Hamiltonians are analytically solvable, we can write down their groundstate wavefunctions:
+The wavefunctions for the \(N=2\) sector can also be connected through these transformations.
+Since both the Hamiltonians are analytically solvable, we can write down their groundstate wavefunctions \cite{pavarini}:
 \begin{equation}\begin{aligned}
@@
 
+\section{Creating General \(N-\)site Hubbard Hamiltonian from Anderson molecule}
+We will follow the strategy outlined in the previous section.
+For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site.
+Note that a uniform number of nearest neighbours means that there is perfect translational invariance on the lattice, which means there cannot be any edge sites.
+This is achieved by applying periodic boundary conditions on the edges of the lattice.
+A square 2d lattice is thus placed on a torus.
+
+For each site \(i\) out of the \(N\) sites (having nearest neighbours \(\{i_j, j\in\left[1,w\right]\}\)), we will create \(w\) local Hamiltonians \(\{H^H_{i,i_j}, i\in \left[1,N\right], j \in \left[1,w\right]  \}\) out of the Anderson molecule Hamiltonian, by setting the impurity index \(d\) to \(i\) and the zero-mode index \(z\) to \(i_j\).
+We will also need to suitably transform the Hamiltonian parameters \(U^A, t^A\), but we will figure those out as we go along.
+All \(N\) sites will then produce \(Nw\) local Hamiltonians in total, and the general Hubbard Hamiltonian should be the average of these local Hamiltonians.
+
+The local Hamiltonians look like
+\begin{equation}\begin{aligned}
+	H^H_{i,i_j} = -t^A\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i_j\sigma} + \text{h.c.}\right) + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
+\end{aligned}\end{equation}
+We havent transformed the Anderson parameters \(U^A, t^A\) to the Hubbard parameters yet. The sum of all local Hamiltonians for a particular site \(i\) then gives the total Hamiltonian for that site:
+\begin{equation}\begin{aligned}
+	H^H_{i} = \sum_{j\in\left[1,w\right]}H^H_{i,i_j} = \sum_{\sigma\atop{j \in \text{N.N.
+of }i}}-t^A\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
+\end{aligned}\end{equation}
+If we now sum over all the lattice sites and take the average of all the Hamiltonians (\(Nw\) in number), we get
+\begin{equation}\begin{aligned}
+	H^H = \frac{1}{Nw}\sum_{i=1}^N H^H_{i} = -\frac{2}{Nw}t^A\sum_{\sigma\atop{\left<ij \right>}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{N}U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
+\end{aligned}\end{equation}
+The factor of 2 in front of \(t^A\) appears because each nearest neighbour pair \(\left<i,j \right>\) is counted twice, once when \(d\to i\) and again when \(d \to j\).
+Comparing with the actual Hubbard model, we can guess the following transformations for the model paramters:
+\begin{equation}\begin{aligned}
+	\frac{2}{Nw}t^A \to t^H, && \frac{1}{N}U^A \to U^H
+\end{aligned}\end{equation}
+For the dimer versions, we had \(N=2, w=1\) and if we substitute these values into the transformations we recover the transformations we had discovered that worked for the dimer.
+
 \bibliographystyle{unsrt}

### 2021-08-02 notes.tex
forgot to add the final Hamiltonian transformation equation
added relation between Green's functions

@@
 For the dimer versions, we had \(N=2, w=1\) and if we substitute these values into the transformations we recover the transformations we had discovered that worked for the dimer.
+The Hubbard Hamiltonian can thus be obtained from the Anderson dimer using the following equation
+\begin{equation}\begin{aligned}
+	H^H = \frac{1}{Nw}\sum_{i=1}^N\sum_{j\in\text{N.N. of }i}H^A\left(t^A \to \frac{Nw}{2}t^H, U^A \to N U^H, d \to i, z \to j\right)
+\end{aligned}\end{equation}
+In terms of the Green's function, this equation becomes
+\begin{equation}\begin{aligned}
+	\label{green_eq}
+	\omega - {G_H}^{-1}(\omega) = \frac{1}{Nw}\sum_{i=1}^N\sum_{j\in\text{N.N. of }i}\left(\omega - {G_A}^{-1}(\omega)\right) \left(t^A \to \frac{Nw}{2}t^H, U^A \to N U^H, d \to i, z \to j\right)
+\end{aligned}\end{equation}
+where $G_H$ and $G_A$ are the Hubbard and SIAM Green's functions:
+\begin{equation}\begin{aligned}
+	G_H(\omega) = \frac{1}{\omega - H_H}, && G_A(\omega) = \frac{1}{\omega - H_A}
+\end{aligned}\end{equation}
+Since the $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, it can be pulled out along with a factor of $ \frac{1}{Nw}Nw = 1$, allowing it to cancel the $\omega$ on the LHS.
+The equation then simplifies to
+\begin{equation}\begin{aligned}
+	{G_H}^{-1}(\omega) = \frac{1}{Nw}\sum_{i=1}^N\sum_{j\in\text{N.N. of }i}{G_{i, j}}^{-1}(\omega) 
+\end{aligned}\end{equation}
+where $G_{i, j}^{-1} = \omega - H^A_{i, j}$, and $H^A_{i, j}$ is defined as
+\begin{equation}\begin{aligned}
+	H^A_{i, j} = -\frac{Nw}{2}t^H\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + N U^H\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
+\end{aligned}\end{equation}
 

### 2021-08-02 notes.tex
entered the relation between off-diagonal Green functions

--- 2021-08-01 notes.tex
@@
 For the dimer versions, we had \(N=2, w=1\) and if we substitute these values into the transformations we recover the transformations we had discovered that worked for the dimer.
+The Hubbard Hamiltonian can thus be obtained from the Anderson dimer using the following equation
+\begin{equation}\begin{aligned}
+	H^H = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
+\end{aligned}\end{equation}
+In terms of the Green's function, this equation becomes
+\begin{equation}\begin{aligned}
+	\label{green_eq}
+	\omega - {G_H}^{-1}(\omega) = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[\left(\omega - {G_A}^{-1}(\omega)\right)\left(d, z \to i,j\right) + \left(\omega - {G_A}^{-1}(\omega)\right)\left(d,z \to j,i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
+\end{aligned}\end{equation}
+where $G_H$ and $G_A$ are the Hubbard and SIAM Green's functions:
+\begin{equation}\begin{aligned}
+	G_H(\omega) = \frac{1}{\omega - H_H}, && G_A(\omega) = \frac{1}{\omega - H_A}
+\end{aligned}\end{equation}
+Since the $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, it can be pulled out along with a factor of $ \frac{1}{Nw}Nw = 1$, allowing it to cancel the $\omega$ on the LHS.
+The equation then simplifies to
+\begin{equation}\begin{aligned}
+	\label{green_eq_final}
+	{G_H}^{-1}(\omega) = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[\tilde G_A^{-1}(\omega, i, j) + \tilde G_A^{-1}(\omega, j, i)\right]
+\end{aligned}\end{equation}
+where $\tilde G_A^{-1}(\omega, i, j) = \omega - \tilde H^A(i, j)$, and $H^A(i, j)$ is defined as
+\begin{equation}\begin{aligned}
+	\tilde H^A(i, j) = -\frac{Nw}{2}t^H\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + N U^H\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
+\end{aligned}\end{equation}
+$\tilde H^A(i, j)$ is nothing but the Anderson molecule Hamiltonian, but with the impurity replaced by the $i^\text{th}$ site and the zero-mode replaced by the $j^\text{th}$ site.
+It is important to note that $\tilde G_A^{-1}(\omega, i, j)$ only scatters between the sites $i,j$.
+If we now take the matrix element of eq.~\ref{green_eq_final} between two \textit{distint} sites $i,j$, then only those terms will survive on the right hand side that involve both $i$ and $j$.
+In other words, the only nearest-neighbour pair that will survive is $\left( i,j \right) $.
+\begin{equation}\begin{aligned}
+	\left(G_{H}^{-1}(\omega)\right)_{i\sigma,j\sigma} &= \frac{1}{Nw}\bra{i\sigma}\left[\tilde G_A^{-1}(\omega, i, j) + \tilde G_A^{-1}(\omega, j, i)\right]\ket{j\sigma}\\
+							  &= \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]
+\end{aligned}\end{equation}
 

### 2021-08-02 notes.tex
added relation between diagonal Green's functions

--- 2021-08-01 notes.tex
@@
 \begin{equation}\begin{aligned}
-	H^H_{i,i_j} = -t^A\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i_j\sigma} + \text{h.c.}\right) + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
+	H^A_{i,i_j} = -t^A\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i_j\sigma} + \text{h.c.}\right) + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	H^H_{i} = \sum_{j\in\left[1,w\right]}H^H_{i,i_j} = \sum_{\sigma\atop{j \in \text{N.N.
+	H^A_{i} = \sum_{j\in\left[1,w\right]}H^H_{i,i_j} = \sum_{\sigma\atop{j \in \text{N.N.
 of }i}}-t^A\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
@@
 For the dimer versions, we had \(N=2, w=1\) and if we substitute these values into the transformations we recover the transformations we had discovered that worked for the dimer.
+The Hubbard Hamiltonian can thus be obtained from the Anderson dimer using the following equation
+\begin{equation}\begin{aligned}
+	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
+\end{aligned}\end{equation}
+In terms of the Green's function, this equation becomes
+\begin{equation}\begin{aligned}
+	\label{green_eq}
+	\omega - {G_H}^{-1}(\omega) = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[\left(\omega - {G_A}^{-1}(\omega)\right)\left(d, z \to i,j\right) + \left(\omega - {G_A}^{-1}(\omega)\right)\left(d,z \to j,i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
+\end{aligned}\end{equation}
+where $G_H$ and $G_A$ are the Hubbard and SIAM Green's functions:
+\begin{equation}\begin{aligned}
+	G_H(\omega) = \frac{1}{\omega - H_H}, && G_A(\omega) = \frac{1}{\omega - H_A}
+\end{aligned}\end{equation}
+Since the two $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, they can be pulled out along with a factor.
+Each will come with a factor which is just the total number of nearest neighbour pairs, which is $ \frac{Nw}{2}$.
+This allows them to cancel the $\omega$ on the LHS.
+The equation then simplifies to
+\begin{equation}\begin{aligned}
+	\label{green_eq_final}
+	{G_H}^{-1}(\omega) = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[\tilde G_A^{-1}(\omega, i, j) + \tilde G_A^{-1}(\omega, j, i)\right]
+\end{aligned}\end{equation}
+where $\tilde G_A^{-1}(\omega, i, j) = \omega - \tilde H^A(i, j)$, and $H^A(i, j)$ is defined as
+\begin{equation}\begin{aligned}
+	\tilde H^A(i, j) = -\frac{Nw}{2}t^H\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + N U^H\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
+\end{aligned}\end{equation}
+$\tilde H^A(i, j)$ is nothing but the Anderson molecule Hamiltonian, but with the impurity replaced by the $i^\text{th}$ site and the zero-mode replaced by the $j^\text{th}$ site.
+It is important to note that $\tilde G_A^{-1}(\omega, i, j)$ only scatters between the sites $i,j$.
+
+We will now calculate the single-particle site diagonal and site offdiagonal Green's functions.
+First lets consider the diagonal Green's function at $i^\text{th}$ site.
+The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have $i$ in one of the indices.
+There will be $w$ such terms, because $i$ has $w$ nearest neighbours.
+Each such pair will have two terms, one with $i$ as the impurity and another with $i$ as the zero-mode.
+For the term that has $i$ as the impurity, the Green's function would then represent the impurity-diagonal Green's function $(G_{dd}^\sigma)$ of the zero-mode SIAM, while for the other term, the Green's function would represent the bath-diagonal or the zero-mode diagonal Green's function $(G_{zz}^\sigma)$.
+\begin{equation}\begin{aligned}
+	\left(G_{H}^{-1}(\omega)\right)_{i\sigma,i\sigma} = \frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right]
+\end{aligned}\end{equation}
+Now we come to the off-diagonal Green's function for the nearest neighbour sites $i$ and $j$.
+This will receive contribution from only one nearest neighbour pair in the summation of the RHS of eq.~\ref{green_eq_final}, namely that of $\left(i,j\right)$.
+The two terms for this nearest neighbour pair will be one for impurity as $i$ and the other for impurity as $j$.
+The Grnee's function will thus be the impurity-zero mode and zero mode-impurity Green's functions:
+\begin{equation}\begin{aligned}
+	\left(G_{H}^{-1}(\omega)\right)_{i\sigma,j\sigma} &= \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]
+\end{aligned}\end{equation}
 

### 2021-08-03 notes.tex
obtained Hubbard dimer local Green's function, for future purposes like comparing with formal results

@@
 \begin{equation}\begin{aligned}
-	\ket{\Psi^H_\text{GS}} &= 4t^H\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) + \left[\Delta\left( U^H, t^H \right) - U^H\right]{\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
-	\ket{\Psi^A_\text{GS}} &= 4t^A\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) + \left[\Delta\left( \frac{1}{2}U^A, t^A \right) - \frac{1}{2}U^A\right]{\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
-	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right),\quad E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right), \quad\Delta(x,y) \equiv \sqrt{x^2 + y^2}\\
+	\ket{\Psi^H_\text{GS}} &= a_1(t^H, U^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) + a_2(t^H, U^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
+	\ket{\Psi^A_\text{GS}} &= a_1(t^A, \frac{1}{2}U^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) + a_2(t^A, \frac{1}{2}U^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
+	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right), E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right)
+\end{aligned}\end{equation}
+where 
+\begin{equation}\begin{aligned}
+	a_1(x,y) \equiv \frac{4x}{\sqrt{2\Delta(x,y)\left( \Delta(x,y) - y \right) }}, && a_2(x,y) \equiv \sqrt{\frac{\Delta(x,y) - y}{2\Delta(x,y)}}, &&\Delta(x,y) \equiv \sqrt{x^2 + y^2}\\
 \end{aligned}\end{equation}
@@
 
+\section*{Appendix}
+\subsection*{Particle-Hole symmetric Hubbard dimer spectrum}
+Here we document the entire spectrum of the Hamiltonian eq.~\ref{hubb_dimer}.
+\begin{table}[htpb]
+	\centering
+	\begin{tabular}{|c|c|c|}
+	\hline
+	Wavefunction & Symbol & Eigenvalue \\
+	\hline
+	$\ket{0,0}$ & $\ket{0}$ & \( \frac{U}{2}\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,0} \pm \ket{0,\sigma}\right)$ & $\ket{0\sigma_\pm}$ & \(\mp t\)\\
+	$\ket{\sigma,\sigma}$ & $\ket{\sigma\sigma}$ & \( -\frac{U}{2}\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow}\right)$ & $\ket{ST}$ & \( -\frac{U}{2}\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2}\right)$ & $\ket{CS}$ & \( \frac{U}{2}\)\\
+	$a_1(t,U) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) \pm a_2(t,U)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{\pm}$ & \(\pm \frac{1}{2}\Delta(t, U)\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,2} \pm \ket{2,\sigma}\right)$ & $\ket{2\sigma_\pm}$ & \(\pm t\)\\
+	$\ket{2,2}$ & $\ket{4}$ & \( \frac{U}{2}\)\\
+\hline
+	\end{tabular}
+	\caption{Spectrum of Hubbard dimer at half-filling}
+	\label{hubb_dim_spectrum}
+\end{table}
+\subsection*{Local Green's function for the Hubbard dimer}
+From the spectral representation, we have the following expression for the local Green's function at the $i^\text{th}$:
+\begin{equation}\begin{aligned}
+	G_{i i}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}c_{i\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
+\end{aligned}\end{equation}
+$m,n$ sum over the exact eigenstates.
+$E_m, E_n$ are the corresponding energies.
+We are interested in teh $T \to 0$ Green's function.
+In that limit, all exponentials except that for the ground state $E_{gs}$ will die out.
+The exponential inside the summation will then cancel the exponential in the partition function.
+\begin{equation}\begin{aligned}
+	G_{i i}^\sigma(\omega, T \to 0) &= \sum_{n}\left[||\bra{GS}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
+					&= \sum_{n}\left[||\bra{n}c^\dagger_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
+\end{aligned}\end{equation}
+
+The ground state $\ket{GS}$ is just the state $\ket{-}$ in the table \ref{hubb_dim_spectrum}. We will choose to look at $\sigma = \uparrow`$. Then,
+\begin{equation}\begin{aligned}
+	c_{1\uparrow}\ket{-} &= \frac{a_1}{\sqrt 2}\ket{0, \downarrow} + \frac{a_2}{\sqrt 2}\ket{\downarrow,0}\\
+	c^\dagger_{1\uparrow}\ket{-} &= -\frac{a_1}{\sqrt 2}\ket{2, \uparrow} + \frac{a_2}{\sqrt 2}\ket{\uparrow,2}\\
+\end{aligned}\end{equation}
+The set of states $\ket{n}$ that give non-zero inner product $\ket{GS}$ are therefore
+\begin{equation}\begin{aligned}
+	\left\{ \ket{n} \right\} &= \ket{0\downarrow_\pm}\\
+	||\bra{n}c_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left( a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \pm 2a_1a_2\right) 	\\
+	\left\{ E_n \right\} &= \mp t
+\end{aligned}\end{equation}
+for the first inner product, and
+\begin{equation}\begin{aligned}
+	\left\{\ket{n}\right\} &= \ket{2\uparrow_\pm}\\
+	||\bra{n}c^\dagger_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left( a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \pm 2a_1a_2\right)\\
+	\left\{ E_n \right\} &= \pm t
+\end{aligned}\end{equation}
+for the second. The Greens function is therefore
+\begin{equation}\begin{aligned}
+	G_{i i}^\sigma(\omega, T \to 0) &= \frac{1}{2}\left[\frac{1}{\omega + E_{GS} + t} + \frac{1}{\omega + E_{GS} - t}\right]
+\end{aligned}\end{equation}
+
 \bibliographystyle{unsrt}

### 2021-08-03 notes.tex
added p-h symmetric SIAM spectrum

--- 2021-08-02 notes.tex
@@
 	\ket{\Psi^A_\text{GS}} &= 4t^A\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) + \left[\Delta\left( \frac{1}{2}U^A, t^A \right) - \frac{1}{2}U^A\right]{\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
-	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right),\quad E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right), \quad\Delta(x,y) \equiv \sqrt{x^2 + y^2}\\
+	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right),\quad E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right), \quad\Delta(x,y) \equiv \sqrt{x^2 + 16y^2}\\
 \end{aligned}\end{equation}
@@
 The two terms for this nearest neighbour pair will be one for impurity as $i$ and the other for impurity as $j$.
-The Grnee's function will thus be the impurity-zero mode and zero mode-impurity Green's functions:
+The Greens function will thus be the impurity-zero mode and zero mode-impurity Green's functions:
 \begin{equation}\begin{aligned}
@@
 
+\section*{Appendix}
+\subsection{Spectrum of the Anderson molecule}
+Here we tabulate the eigenstates and eigenvalues of the Hamiltonian in eq.~\ref{and_dimer}.
+\begin{table}[htpb]
+	\centering
+	\begin{tabular}{|c|c|c|}
+	\hline
+	eigenstate & symbol & eigenvalue\\
+	\hline
+	\(\ket{0,0}\) & \(\ket{0}\) & \(\frac{U}{4}\)\\
+	\(-\frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) \pm U\right)}}\ket{\sigma,0} \pm \frac{1}{\sqrt{2\Delta}}\ket{0, \sigma}\) & \(\ket{0\sigma_\pm}\) & \(\pm\frac{1}{4}\Delta(U,t)\)\\
+	\(\ket{\sigma,\sigma}\) & \(\ket{\sigma\sigma}\) & \(-\frac{U}{4}\)\\
+	\(\frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} + \ket{\downarrow, \uparrow}\right)\) & \(\ket{ST}\) & \(-\frac{U}{4}\)\\
+	\(\frac{1}{\sqrt 2}\left(\ket{2, 0} - \ket{0, 2}\right)\) & \(\ket{CS}\) & \(\frac{U}{4}\)\\
+	\(-\frac{4t}{\sqrt{2\Delta(\frac{1}{2}U,t)\left( \Delta(\frac{1}{2}U,t) \pm \frac{1}{2}U\right)}}\frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow, \uparrow}\right) \pm \sqrt{\frac{1}{2} \pm \frac{1}{2}\frac{U/2}{\Delta(\frac{U}{2},t)}}\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0, 2}\right)\) & \(\ket{\pm}\) & \(\pm\frac{1}{2}\Delta(\frac{U}{2},t)\)\\
+	\(\frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) \pm U\right)}}\ket{\sigma,2} \pm \frac{1}{\sqrt{2\Delta}}\ket{2, \sigma}\) & \(\ket{0\sigma_\pm}\) & \(\pm\frac{1}{4}\Delta(U,t)\)\\
+	\(\ket{2,2}\) & \(\ket{4}\) & \(\frac{U}{4}\)\\
+	\hline
+	\end{tabular}
+\end{table}
+
 \bibliographystyle{unsrt}

### 2021-08-04 notes.tex

--- 2021-08-03 notes.tex
@@
 \begin{equation}\begin{aligned}
-	\ket{\Psi^H_\text{GS}} &= a_1(t^H, U^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) + a_2(t^H, U^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
-	\ket{\Psi^A_\text{GS}} &= a_1(t^A, \frac{1}{2}U^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) + a_2(t^A, \frac{1}{2}U^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
+	\ket{\Psi^H_\text{GS}} &= a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) + a_2(U^H,t^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
+	\ket{\Psi^A_\text{GS}} &= a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) + a_2(\frac{1}{2}U^A,t^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
 	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right), E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right)
@@
 \begin{equation}\begin{aligned}
-	a_1(x,y) \equiv \frac{4x}{\sqrt{2\Delta(x,y)\left( \Delta(x,y) - y \right) }}, && a_2(x,y) \equiv \sqrt{\frac{\Delta(x,y) - y}{2\Delta(x,y)}}, &&\Delta(x,y) \equiv \sqrt{x^2 + y^2}\\
+	a_1(U,t) \equiv \frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) - U \right) }}, && a_2(U,t) \equiv \sqrt{\frac{\Delta(U,t) - U}{2\Delta(U,t)}}, &&\Delta(U,t) \equiv \sqrt{U^2 + 16t^2}\\
 \end{aligned}\end{equation}
@@
 
+\newpage
 \section*{Appendix}
-\subsection*{Particle-Hole symmetric Hubbard dimer spectrum}
-Here we document the entire spectrum of the Hamiltonian eq.~\ref{hubb_dimer}.
-\begin{table}[htpb]
+\subsection*{Spectra of Hubbard dimer and Anderson molecule}
+Here we document the spectra of the Hamiltonians in eqs.~\ref{hubb_dimer} and \ref{and_dimer}.
+\begin{table}[htpb!]
 	\centering
@@
 	\hline
-	Wavefunction & Symbol & Eigenvalue \\
+	eigenstate & symbol & eigenvalue \\
 	\hline
@@
 	\label{hubb_dim_spectrum}
+
+	\begin{tabular}{|c|c|c|}
+	\hline
+	eigenstate & symbol & eigenvalue\\
+	\hline
+	\(\ket{0,0}\) & \(\ket{0}\) & \(\frac{U}{4}\)\\
+	\(-\frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) \pm U\right)}}\ket{\sigma,0} \pm \frac{1}{\sqrt{2\Delta}}\ket{0, \sigma}\) & \(\ket{0\sigma_\pm}\) & \(\pm\frac{1}{4}\Delta(U,t)\)\\
+	\(\ket{\sigma,\sigma}\) & \(\ket{\sigma\sigma}\) & \(-\frac{U}{4}\)\\
+	\(\frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} + \ket{\downarrow, \uparrow}\right)\) & \(\ket{ST}\) & \(-\frac{U}{4}\)\\
+	\(\frac{1}{\sqrt 2}\left(\ket{2, 0} - \ket{0, 2}\right)\) & \(\ket{CS}\) & \(\frac{U}{4}\)\\
+	\(-\frac{4t}{\sqrt{2\Delta(\frac{1}{2}U,t)\left( \Delta(\frac{1}{2}U,t) \pm \frac{1}{2}U\right)}}\frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow, \uparrow}\right) \pm \sqrt{\frac{1}{2} \pm \frac{1}{2}\frac{U/2}{\Delta(\frac{U}{2},t)}}\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0, 2}\right)\) & \(\ket{\pm}\) & \(\pm\frac{1}{2}\Delta(\frac{U}{2},t)\)\\
+	\(\frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) \pm U\right)}}\ket{\sigma,2} \pm \frac{1}{\sqrt{2\Delta}}\ket{2, \sigma}\) & \(\ket{0\sigma_\pm}\) & \(\pm\frac{1}{4}\Delta(U,t)\)\\
+	\(\ket{2,2}\) & \(\ket{4}\) & \(\frac{U}{4}\)\\
+	\hline
+	\end{tabular}
+	\caption{Spectrum of Anderson molecule at particle-hole symmetry}
 \end{table}	

### 2021-08-04 notes.tex
replaced some expressions with predefined symbols, made corrections
obtained local GF for hubbard dimer

--- 2021-08-03 notes.tex
@@
 \begin{equation}\begin{aligned}
-	\ket{\Psi^H_\text{GS}} &= a_1(t^H, U^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) + a_2(t^H, U^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
-	\ket{\Psi^A_\text{GS}} &= a_1(t^A, \frac{1}{2}U^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) + a_2(t^A, \frac{1}{2}U^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
+	\ket{\Psi^H_\text{GS}} &= a_1(-U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) - a_2(-U^H,t^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
+	\ket{\Psi^A_\text{GS}} &= a_1(-\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) - a_2(-\frac{1}{2}U^A,t^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
 	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right), E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right)
@@
 \begin{equation}\begin{aligned}
-	a_1(x,y) \equiv \frac{4x}{\sqrt{2\Delta(x,y)\left( \Delta(x,y) - y \right) }}, && a_2(x,y) \equiv \sqrt{\frac{\Delta(x,y) - y}{2\Delta(x,y)}}, &&\Delta(x,y) \equiv \sqrt{x^2 + y^2}\\
+	a_1(U,t) \equiv \frac{-4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) + U \right) }}, && a_2(U,t) \equiv \sqrt{\frac{\Delta(U,t) + U}{2\Delta(U,t)}}, &&\Delta(U,t) \equiv \sqrt{U^2 + 16t^2}\\
 \end{aligned}\end{equation}
+$a_1,a_2$ satisfy $a_1(-U,t) = -a_2(U,t)$.
 From the forms of the wavefunctions and eigenenergies, we can immediately write down
@@
 	\hline
-	Wavefunction & Symbol & Eigenvalue \\
+	eigenstate & symbol & eigenvalue \\
 	\hline
-	$\ket{0,0}$ & $\ket{0}$ & \( \frac{U}{2}\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,0} \pm \ket{0,\sigma}\right)$ & $\ket{0\sigma_\pm}$ & \(\mp t\)\\
-	$\ket{\sigma,\sigma}$ & $\ket{\sigma\sigma}$ & \( -\frac{U}{2}\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow}\right)$ & $\ket{ST}$ & \( -\frac{U}{2}\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2}\right)$ & $\ket{CS}$ & \( \frac{U}{2}\)\\
-	$a_1(t,U) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) \pm a_2(t,U)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{\pm}$ & \(\pm \frac{1}{2}\Delta(t, U)\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,2} \pm \ket{2,\sigma}\right)$ & $\ket{2\sigma_\pm}$ & \(\pm t\)\\
-	$\ket{2,2}$ & $\ket{4}$ & \( \frac{U}{2}\)\\
+	$\ket{0,0}$ & $\ket{0}$ & \( \frac{U^H}{2}\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,0} \pm \ket{0,\sigma}\right)$ & $\ket{0\sigma_\pm}$ & \(\mp t^H\)\\
+	$\ket{\sigma,\sigma}$ & $\ket{\sigma\sigma}$ & \( -\frac{U^H}{2}\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow}\right)$ & $\ket{ST}$ & \( -\frac{U^H}{2}\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2}\right)$ & $\ket{CS}$ & \( \frac{U^H}{2}\)\\
+	$a_1(\pm U^H, t^H) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) \pm a_2(\pm U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{\pm}$ & \(\pm \frac{1}{2}\Delta(U^H, t^H)\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,2} \pm \ket{2,\sigma}\right)$ & $\ket{2\sigma_\pm}$ & \(\pm t^H\)\\
+	$\ket{2,2}$ & $\ket{4}$ & \( \frac{U^H}{2}\)\\
 \hline
@@
 	\label{hubb_dim_spectrum}
+	\begin{tabular}{|c|c|c|}
+	\hline
+	eigenstate & symbol & eigenvalue\\
+	\hline
+	\(\ket{0,0}\) & \(\ket{0}\) & \(\frac{U^A}{4}\)\\
+	\(a_1\left(\pm U^A, t^A\right)\ket{\sigma,0} \pm a_2\left(\pm U^A, t^A\right)\ket{0, \sigma}\) & \(\ket{0\sigma_\pm}\) & \(\pm\frac{1}{4}\Delta(U^A, t^A)\)\\
+	\(\ket{\sigma,\sigma}\) & \(\ket{\sigma\sigma}\) & \(-\frac{U^A}{4}\)\\
+	\(\frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} + \ket{\downarrow, \uparrow}\right)\) & \(\ket{ST}\) & \(-\frac{U^A}{4}\)\\
+	\(\frac{1}{\sqrt 2}\left(\ket{2, 0} - \ket{0, 2}\right)\) & \(\ket{CS}\) & \(\frac{U^A}{4}\)\\
+	\(a_1\left(\pm \frac{U^A}{2}, t^A\right) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow, \uparrow}\right) \pm a_2\left(\pm \frac{U^A}{2}, t^A\right) \frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0, 2}\right)\) & \(\ket{\pm}\) & \(\pm\frac{1}{2}\Delta(\frac{U^A}{2}, t^A)\)\\
+	\(-a_1\left(\pm U^A, t^A\right)\ket{\sigma,2} \pm a_2\left(\pm U^A, t^A\right)\ket{2, \sigma}\) & \(\ket{2\sigma_\pm}\) & \(\pm\frac{1}{4}\Delta(U^A, t^A)\)\\
+	\(\ket{2,2}\) & \(\ket{4}\) & \(\frac{U^A}{4}\)\\
+	\hline
+	\end{tabular}
+	\caption{Spectrum of Anderson molecule at particle-hole symmetry}
 \end{table}	
@@
 \begin{equation}\begin{aligned}
-	c_{1\uparrow}\ket{-} &= \frac{a_1}{\sqrt 2}\ket{0, \downarrow} + \frac{a_2}{\sqrt 2}\ket{\downarrow,0}\\
-	c^\dagger_{1\uparrow}\ket{-} &= -\frac{a_1}{\sqrt 2}\ket{2, \uparrow} + \frac{a_2}{\sqrt 2}\ket{\uparrow,2}\\
+	c_{1\uparrow}\ket{-} &= \frac{a_1}{\sqrt 2}\ket{0, \downarrow} - \frac{a_2}{\sqrt 2}\ket{\downarrow,0}\\
+	c^\dagger_{1\uparrow}\ket{-} &= -\frac{a_1}{\sqrt 2}\ket{2, \uparrow} - \frac{a_2}{\sqrt 2}\ket{\uparrow,2}\\
 \end{aligned}\end{equation}
@@
 	\left\{ \ket{n} \right\} &= \ket{0\downarrow_\pm}\\
-	||\bra{n}c_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left( a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \pm 2a_1a_2\right) 	\\
+	||\bra{n}c_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left(-a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \mp 2a_1a_2\right)\\
 	\left\{ E_n \right\} &= \mp t
@@
 \begin{equation}\begin{aligned}
-	G_{i i}^\sigma(\omega, T \to 0) &= \frac{1}{2}\left[\frac{1}{\omega + E_{GS} + t} + \frac{1}{\omega + E_{GS} - t}\right]
+	G_{i i}^\uparrow(\omega, T \to 0) &= \frac{\omega}{2}\left[\frac{1 + 2a_1(-U^H, t^H)a_2(-U^H, t^H)}{\omega^2 - \left(E_{GS} + t\right)^2} + \frac{1 - 2a_1(-U^H, t^H)a_2(-U^H, t^H)}{\omega^2 - \left(E_{GS} - t\right)^2}\right]
 \end{aligned}\end{equation}

### 2021-08-04 notes.tex
obtained local Green's function in terms of parameters, matches with pavarini

--- 2021-08-03 notes.tex
@@
 % !TEX TS-program = xelatex
-\documentclass{article}
-\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec,geometry}
+\documentclass[12pt]{article}
+\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
+\usepackage[margin=0.5in,bottom=0.8in]{geometry}
 \usepackage[T1]{fontenc}
@@
 \begin{equation}\begin{aligned}
-	\ket{\Psi^H_\text{GS}} &= 4t^H\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) + \left[\Delta\left( U^H, t^H \right) - U^H\right]{\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
-	\ket{\Psi^A_\text{GS}} &= 4t^A\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) + \left[\Delta\left( \frac{1}{2}U^A, t^A \right) - \frac{1}{2}U^A\right]{\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
-	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right),\quad E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right), \quad\Delta(x,y) \equiv \sqrt{x^2 + 16y^2}\\
+	\ket{\Psi^H_\text{GS}} &= a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) - a_2(U^H,t^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
+	\ket{\Psi^A_\text{GS}} &= a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) - a_2(\frac{1}{2}U^A,t^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
+	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right), E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right)
 \end{aligned}\end{equation}
+where 
+\begin{equation}\begin{aligned}
+	a_1(U,t) \equiv \frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) - U \right) }}, && a_2(U,t) \equiv \sqrt{\frac{\Delta(U,t) - U}{2\Delta(U,t)}}, &&\Delta(U,t) \equiv \sqrt{U^2 + 16t^2}\\
+\end{aligned}\end{equation}
+$a_1,a_2$ satisfy $a_1(-U,t) = -a_2(U,t)$ and $a_1(U,t)a_2(U,t)= \frac{2t}{\Delta(U,t)}$.
 From the forms of the wavefunctions and eigenenergies, we can immediately write down
@@
 
+\newpage
 \section*{Appendix}
-\subsection{Spectrum of the Anderson molecule}
-Here we tabulate the eigenstates and eigenvalues of the Hamiltonian in eq.~\ref{and_dimer}.
-\begin{table}[htpb]
-	\centering
+\subsection*{Spectra of Hubbard dimer and Anderson molecule}
+%Here we document the spectra of the Hamiltonians in eqs.~\ref{hubb_dimer} and \ref{and_dimer}.
+\begin{center}
+	\begin{tabular}{|c|c|c|}
+	\hline
+	eigenstate & symbol & eigenvalue \\
+	\hline
+	$\ket{0,0}$ & $\ket{0}$ & \( \frac{U^H}{2}\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,0} \pm \ket{0,\sigma}\right)$ & $\ket{0\sigma_\pm}$ & \(\mp t^H\)\\
+	$\ket{\sigma,\sigma}$ & $\ket{\sigma\sigma}$ & \( -\frac{U^H}{2}\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow}\right)$ & $\ket{ST}$ & \( -\frac{U^H}{2}\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2}\right)$ & $\ket{CS}$ & \( \frac{U^H}{2}\)\\
+	$a_1(U^H, t^H) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_2(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{-}$ & \(-\frac{1}{2}\Delta(U^H, t^H)\)\\
+	$-a_2(U^H, t^H) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{+}$ & \(\frac{1}{2}\Delta(U^H, t^H)\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,2} \pm \ket{2,\sigma}\right)$ & $\ket{2\sigma_\pm}$ & \(\pm t^H\)\\
+	$\ket{2,2}$ & $\ket{4}$ & \( \frac{U^H}{2}\)\\
+\hline
+	\end{tabular}
+	\captionof{table}{Spectrum of Hubbard dimer at half-filling}
+	\label{hubb_dim_spectrum}
 	\begin{tabular}{|c|c|c|}
@@
 	\hline
-	\(\ket{0,0}\) & \(\ket{0}\) & \(\frac{U}{4}\)\\
-	\(-\frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) \pm U\right)}}\ket{\sigma,0} \pm \frac{1}{\sqrt{2\Delta}}\ket{0, \sigma}\) & \(\ket{0\sigma_\pm}\) & \(\pm\frac{1}{4}\Delta(U,t)\)\\
-	\(\ket{\sigma,\sigma}\) & \(\ket{\sigma\sigma}\) & \(-\frac{U}{4}\)\\
-	\(\frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} + \ket{\downarrow, \uparrow}\right)\) & \(\ket{ST}\) & \(-\frac{U}{4}\)\\
-	\(\frac{1}{\sqrt 2}\left(\ket{2, 0} - \ket{0, 2}\right)\) & \(\ket{CS}\) & \(\frac{U}{4}\)\\
-	\(-\frac{4t}{\sqrt{2\Delta(\frac{1}{2}U,t)\left( \Delta(\frac{1}{2}U,t) \pm \frac{1}{2}U\right)}}\frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow, \uparrow}\right) \pm \sqrt{\frac{1}{2} \pm \frac{1}{2}\frac{U/2}{\Delta(\frac{U}{2},t)}}\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0, 2}\right)\) & \(\ket{\pm}\) & \(\pm\frac{1}{2}\Delta(\frac{U}{2},t)\)\\
-	\(\frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) \pm U\right)}}\ket{\sigma,2} \pm \frac{1}{\sqrt{2\Delta}}\ket{2, \sigma}\) & \(\ket{0\sigma_\pm}\) & \(\pm\frac{1}{4}\Delta(U,t)\)\\
-	\(\ket{2,2}\) & \(\ket{4}\) & \(\frac{U}{4}\)\\
+	\(\ket{0,0}\) & \(\ket{0}\) & \(\frac{U^A}{4}\)\\
+	\(a_1\left(U^A, t^A\right)\ket{\sigma,0} + a_2\left(U^A, t^A\right)\ket{0, \sigma}\) & \(\ket{0\sigma_-}\) & \(-\frac{1}{4}\Delta(U^A, t^A)\)\\
+	\(-a_2\left(U^A, t^A\right)\ket{\sigma,0} + a_1\left(U^A, t^A\right)\ket{0, \sigma}\) & \(\ket{0\sigma_+}\) & \(\frac{1}{4}\Delta(U^A, t^A)\)\\
+	\(\ket{\sigma,\sigma}\) & \(\ket{\sigma\sigma}\) & \(-\frac{U^A}{4}\)\\
+	\(\frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} + \ket{\downarrow, \uparrow}\right)\) & \(\ket{ST}\) & \(-\frac{U^A}{4}\)\\
+	\(\frac{1}{\sqrt 2}\left(\ket{2, 0} - \ket{0, 2}\right)\) & \(\ket{CS}\) & \(\frac{U^A}{4}\)\\
+	$a_1( \frac{1}{2}U^A, t^A) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_2( \frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{-}$ & \(-\frac{1}{2}\Delta( \frac{1}{2}U^A, t^A)\)\\
+	$-a_2(\frac{1}{2}U^A, t^A) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{+}$ & \(\frac{1}{2}\Delta(\frac{1}{2}U^A, t^A)\)\\
+	\(-a_1\left(\pm U^A, t^A\right)\ket{\sigma,2} \pm a_2\left(\pm U^A, t^A\right)\ket{2, \sigma}\) & \(\ket{2\sigma_\pm}\) & \(\pm\frac{1}{4}\Delta(U^A, t^A)\)\\
+	\(\ket{2,2}\) & \(\ket{4}\) & \(\frac{U^A}{4}\)\\
 	\hline
 	\end{tabular}
-\end{table}
+	\captionof{table}{Spectrum of Anderson molecule at particle-hole symmetry}
+\end{center}
+\subsection*{Local Green's function for the Hubbard dimer}
+From the spectral representation, we have the following expression for the local Green's function at the $i^\text{th}$:
+\begin{equation}\begin{aligned}
+	G_{i i}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}c_{i\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
+\end{aligned}\end{equation}
+$m,n$ sum over the exact eigenstates.
+$E_m, E_n$ are the corresponding energies.
+We are interested in teh $T \to 0$ Green's function.
+In that limit, all exponentials except that for the ground state $E_{gs}$ will die out.
+The exponential inside the summation will then cancel the exponential in the partition function.
+\begin{equation}\begin{aligned}
+	G_{i i}^\sigma(\omega, T \to 0) &= \sum_{n}\left[||\bra{GS}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
+					&= \sum_{n}\left[||\bra{n}c^\dagger_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
+\end{aligned}\end{equation}
+
+The ground state $\ket{GS}$ is just the state $\ket{-}$ in the table \ref{hubb_dim_spectrum}. We will choose to look at $\sigma = \uparrow`$. Then,
+\begin{equation}\begin{aligned}
+	c_{1\uparrow}\ket{-} &= \frac{a_1}{\sqrt 2}\ket{0, \downarrow} + \frac{a_2}{\sqrt 2}\ket{\downarrow,0}\\
+	c^\dagger_{1\uparrow}\ket{-} &= -\frac{a_1}{\sqrt 2}\ket{2, \uparrow} + \frac{a_2}{\sqrt 2}\ket{\uparrow,2}\\
+\end{aligned}\end{equation}
+The set of states $\ket{n}$ that give non-zero inner product $\ket{GS}$ are therefore
+\begin{equation}\begin{aligned}
+	\left\{ \ket{n} \right\} &= \ket{0\downarrow_\pm}\\
+	||\bra{n}c_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left(a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \pm 2a_1a_2\right)\\
+	\left\{ E_n \right\} &= \mp t
+\end{aligned}\end{equation}
+for the first inner product, and
+\begin{equation}\begin{aligned}
+	\left\{\ket{n}\right\} &= \ket{2\uparrow_\pm}\\
+	||\bra{n}c^\dagger_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left( a_2 \mp a_1 \right)^2 = \frac{1}{4}\left(1 \mp 2a_1a_2\right)\\
+	\left\{ E_n \right\} &= \pm t
+\end{aligned}\end{equation}
+for the second. The Greens function is therefore
+\begin{equation}\begin{aligned}
+	G_{i i}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} - t\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} + t\right) ^2}
+\end{aligned}\end{equation}
 

### 2021-08-04 notes.tex
obtained spectral function, plotted it as well
expressed Gkw of general Hubbard in terms of inverse Gs of SIAM

@@
 \begin{equation}\begin{aligned}
+	\label{H_tiled}
 	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
 \end{aligned}\end{equation}
-In terms of the Green's function, this equation becomes
+\section{Computing Greens functions and related quantities}
+In terms of the Green's function, equation \ref{H_tiled} becomes
 \begin{equation}\begin{aligned}
@@
 \begin{equation}\begin{aligned}
-	\left(G_{H}^{-1}(\omega)\right)_{i\sigma,j\sigma} &= \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]
+	\left(G_{H}^{-1}(\omega)\right)_{\left<i,j \right>\sigma} &= \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]
+\end{aligned}\end{equation}
+Since the only real-space interaction is that between the nearest neighbours, there are no further real space Green's functions, and the matrix $G^{-1}$ is tridiagonal in real space.
+Because of translational invariance, we know that $\left(G_H^{-1}\right)_{ii}$ and $\left(G_H^{-1}\right)_{ij}$ are independent of $i,j$.
+For brevity, we therefore label them $g_0$ and $g_1$ respectively.
+\begin{equation}\begin{aligned}
+	g_0 &\equiv \frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right]\\
+	g_1 &\equiv \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]
+\end{aligned}\end{equation}
+
+\begin{equation}\begin{aligned}
+	G^{-1}_H(\omega) = \begin{pmatrix} \left(G^{-1}\right)_{00} & \left(G^{-1}\right)_{01} & ... & ... & \left(G^{-1}\right)_{0N}\\
+		\left(G^{-1}\right)_{10} & \left(G^{-1}\right)_{11} & \left(G^{-1}\right)_{12} & ... & ...\\
+		... & \left(G^{-1}\right)_{21} & \left(G^{-1}\right)_{22} & \left(G^{-1}\right)_{23} & ... \\
+		    &&.&&\\
+		    &&.&&\\
+		    &&.&&\\
+\end{pmatrix} = \begin{pmatrix} g_0 & g_1 & ... & ... & g_1\\
+		g_1 & g_0 & g_1 & ... & ...\\
+		... & g_1 & g_0 & g_1 & ... \\
+		    &&...&&\\
+		    &&...&&\\
+\end{pmatrix} 
+\end{aligned}\end{equation}
+It can be written in the operator form as
+\begin{equation}\begin{aligned}
+	G_H^{-1}(\omega) = g_0\sum_{i=1}^N\ket{i}\bra{i} + g_1\sum_{\left<i,j \right>}^N\left( \ket{i}\bra{j} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+We can Fourier transform the real space basis kets $\ket{i} \equiv \ket{\vec r_i}$ into momentum space:
+\begin{equation}\begin{aligned}
+	\ket{i} &= \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\vec k}\\
+	\sum_i \ket{i}\bra{i} &= \frac{1}{N}\sum_i \sum_{\vec k, \vec q} e^{i \left(\vec{k} - \vec q\right)\cdot\vec{r_i}}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{\vec k, \vec q} N \delta\left(\vec{k} - \vec q\right)\ket{\vec k}\bra{\vec q} = \sum_{\vec k=\vec k_1}^{\vec k_N} \ket{\vec k}\bra{\vec k}\\
+\sum_{\left<i,j \right>} \ket{i}\bra{j} &= \frac{1}{N}\sum_{\left<i,j \right>} \sum_{\vec k, \vec q} e^{i \left(\vec{k}\cdot \vec r_i - \vec q\cdot \vec r_j\right)}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{i=1}^N e^{i \left(\vec{k} - \vec q\right)\cdot \vec r_i}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec k, \vec q} e^{-i\vec q\cdot a_i\hat e_i}\ket{\vec k}\bra{\vec q}\\
+					&=\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec q} e^{-i\vec q\cdot \vec e_i}\ket{\vec q}\bra{\vec q} = \sum_{\vec q} \left(\sum_{i_1}^{D}e^{-ia_iq_i}\right)\ket{\vec q}\bra{\vec q}
+\end{aligned}\end{equation}
+$\hat e_i$ are the primitive lattice unit vectors for the general $d-$dimensional lattice.
+$q_i$ are the projections of $\vec q$ along those vectors.
+$a_i$ are the lattice spacings along each primitive vector.
+Adding the Hermitian conjugate simply extracts the real part:
+\begin{equation}\begin{aligned}
+	\sum_i \ket{i}\bra{i} =\sum_{\vec q} \underbrace{\sum_{i_1}^{D}2\cos\left(a_iq_i\right)}_{\equiv \xi_{\vec q}}\ket{\vec q}\bra{\vec q}
+\end{aligned}\end{equation}
+The inverse Greens function thus becomes diagonal in momentum space
+\begin{equation}\begin{aligned}
+G_H^{-1}(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)\ket{\vec k}\bra{\vec k} = \begin{pmatrix} g_0 + g_1\xi_{\vec k_1} &&& \\
+	& g_0 + g_1\xi_{\vec k_2} && \\
+	&& g_0 + g_1\xi_{\vec k_3} & \\
+	...&...&...&\\
+	\end{pmatrix} 
+\end{aligned}\end{equation}
+The matrix is of course written in momentum space. Since $G_H^{-1}(\omega)$ is diagonal in this basis, we can invert the matrix trivially by replacing the diagonal elements with their reciprocals.
+\begin{equation}\begin{aligned}
+	G_H(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\ket{\vec k}\bra{\vec k} = \begin{pmatrix} \left(g_0 + g_1\xi_{\vec k_1}\right)^{-1} &&& \\
+	& \left(g_0 + g_1\xi_{\vec k_2}\right)^{-1} && \\
+	&& \left(g_0 + g_1\xi_{\vec k_3}\right)^{-1} & \\
+	...&...&...&\\
+	\end{pmatrix} 
+\end{aligned}\end{equation}
+The diagonal elements of $G_H$ in momentum space are simply $G_H(\vec k, \omega)$.
+\begin{equation}\begin{aligned}
+	G_H(\vec k, \omega) &= g_0 + g_1 \xi_{\vec k}\\
+			    &= \frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right] + \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]\xi_{\vec k}
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
+The site local spectral can now be calculated:
+\begin{equation}\begin{aligned}
+	A(i\uparrow, \omega) &= - \frac{1}{\pi}\text{Im }G_{i i}^\uparrow(\omega)\\
+			     &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right)\left[\delta(\omega - \frac{1}{2}\Delta - t) + \delta(\omega + \frac{1}{2}\Delta + t)\right] + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \left[\delta(\omega - \frac{1}{2}\Delta + t) + \delta(\omega + \frac{1}{2}\Delta - t)\right]
+\end{aligned}\end{equation}
 

### 2021-08-04 notes.tex
wrote general formula for all four Greens functions of Anderson molecule, time for biriani

@@
 \usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
-\usepackage[margin=0.5in,bottom=0.8in]{geometry}
+\usepackage[margin=0.5in]{geometry}
 \usepackage[T1]{fontenc}
@@
 \usepackage[stable]{footmisc}
-\renewcommand{\arraystretch}{2}
+\renewcommand{\arraystretch}{1.9}
 \setlength\delimitershortfall{-2pt}
@@
 \begin{itemize}
-	\item While DMFT primarily works with Green's functions and self-energies, this method involves Hamiltonians and wavefunctions.
-	\item The impurity-solver in DMFT provides an impurity Green's function (which is then equated with the local Green's function of the bath), while the impurity-solver in this method actually provides a wavefunction.
+	\item While DMFT primarily works with Greens functions and self-energies, this method involves Hamiltonians and wavefunctions.
+	\item The impurity-solver in DMFT provides an impurity Greens function (which is then equated with the local Greens function of the bath), while the impurity-solver in this method actually provides a wavefunction.
 	\item The final step of DMFT is the self-consistency equation, where the impurity and bath-local quantities are set equal.
@@
 \end{aligned}\end{equation}
-The Green's function of the full Hamiltonian can also be split in a similar fashion:
+The Greens function of the full Hamiltonian can also be split in a similar fashion:
 \begin{equation}\begin{aligned}
@@
 
-The algorithm of DMFT then involves starting with some local self-energy of the bath, \(\Sigma(\omega)\), and using an impurity solver to calculate the impurity Green's function in the presence of this self-energy.
-This impurity Green's function is then used to calculate the impurity self-energy \(\Sigma_d(\omega)\), and the self-energy of the bath is then set equal to this impurity self-energy: \(\Sigma(\omega) = \Sigma_d(\omega)\), because we expect, on grounds of the lattice symmetry, that the impurity is the same as any other site in the bath.
+The algorithm of DMFT then involves starting with some local self-energy of the bath, \(\Sigma(\omega)\), and using an impurity solver to calculate the impurity Greens function in the presence of this self-energy.
+This impurity Greens function is then used to calculate the impurity self-energy \(\Sigma_d(\omega)\), and the self-energy of the bath is then set equal to this impurity self-energy: \(\Sigma(\omega) = \Sigma_d(\omega)\), because we expect, on grounds of the lattice symmetry, that the impurity is the same as any other site in the bath.
 This is said to be the self-consistency step, because the bath self-energy is completely determined only at the end.
@@
 \section{Computing Greens functions and related quantities}
-In terms of the Green's function, equation \ref{H_tiled} becomes
+In terms of the Greens function, equation \ref{H_tiled} becomes
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-where $G_H$ and $G_A$ are the Hubbard and SIAM Green's functions:
+where $G_H$ and $G_A$ are the Hubbard and SIAM Greens functions:
 \begin{equation}\begin{aligned}
@@
 
-We will now calculate the single-particle site diagonal and site offdiagonal Green's functions.
-First lets consider the diagonal Green's function at $i^\text{th}$ site.
+We will now calculate the single-particle site diagonal and site offdiagonal Greens functions.
+First lets consider the diagonal Greens function at $i^\text{th}$ site.
 The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have $i$ in one of the indices.
@@
 Each such pair will have two terms, one with $i$ as the impurity and another with $i$ as the zero-mode.
-For the term that has $i$ as the impurity, the Green's function would then represent the impurity-diagonal Green's function $(G_{dd}^\sigma)$ of the zero-mode SIAM, while for the other term, the Green's function would represent the bath-diagonal or the zero-mode diagonal Green's function $(G_{zz}^\sigma)$.
+For the term that has $i$ as the impurity, the Greens function would then represent the impurity-diagonal Greens function $(G_{dd}^\sigma)$ of the zero-mode SIAM, while for the other term, the Greens function would represent the bath-diagonal or the zero-mode diagonal Greens function $(G_{zz}^\sigma)$.
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-Now we come to the off-diagonal Green's function for the nearest neighbour sites $i$ and $j$.
+Now we come to the off-diagonal Greens function for the nearest neighbour sites $i$ and $j$.
 This will receive contribution from only one nearest neighbour pair in the summation of the RHS of eq.~\ref{green_eq_final}, namely that of $\left(i,j\right)$.
 The two terms for this nearest neighbour pair will be one for impurity as $i$ and the other for impurity as $j$.
-The Greens function will thus be the impurity-zero mode and zero mode-impurity Green's functions:
+The Greens function will thus be the impurity-zero mode and zero mode-impurity Greens functions:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-Since the only real-space interaction is that between the nearest neighbours, there are no further real space Green's functions, and the matrix $G^{-1}$ is tridiagonal in real space.
+Since the only real-space interaction is that between the nearest neighbours, there are no further real space Greens functions, and the matrix $G^{-1}$ is tridiagonal in real space.
 Because of translational invariance, we know that $\left(G_H^{-1}\right)_{ii}$ and $\left(G_H^{-1}\right)_{ij}$ are independent of $i,j$.
@@
 \end{center}
-\subsection*{Local Green's function for the Hubbard dimer}
-From the spectral representation, we have the following expression for the local Green's function at the $i^\text{th}$:
+\subsection*{Local Greens function for the Hubbard dimer}
+From the spectral representation, we have the following expression for the local Greens function at the $i^\text{th}$:
 \begin{equation}\begin{aligned}
@@
 $E_m, E_n$ are the corresponding energies.
-We are interested in teh $T \to 0$ Green's function.
+We are interested in teh $T \to 0$ Greens function.
 In that limit, all exponentials except that for the ground state $E_{gs}$ will die out.
@@
 
+\subsection*{Greens functions for Anderson molecule}
+\begin{equation}\begin{aligned}
+	G_{dd}^\uparrow(\omega) &= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{d\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{d\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
+	G_{zz}^\uparrow(\omega)&= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{z\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{z\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
+	G_{dz}^\uparrow(\omega)	&= \sum_{n}\left[\frac{\left<GS|c_{d\uparrow} | n \right>\left<n |c^\dagger_{z \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{d\uparrow} | GS\right>\left<GS |c^\dagger_{z \uparrow} |n\right>}{\omega + E_{GS} - E_n}\right]\\
+	G_{zd}^\uparrow(\omega) &= \sum_{n}\left[\frac{\left<GS|c_{z \uparrow} | n \right>\left<n |c^\dagger_{d \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{z \uparrow} | GS\right>\left<GS |c^\dagger_{d \uparrow} | n\right>}{\omega + E_{n} - E_{GS}}\right]\\
+\end{aligned}\end{equation}
+
 \bibliographystyle{unsrt}

### 2021-08-05 notes.tex
added Anderson molecule diagonal Green's functions
wrote all four Greens functions for Anderson molecule, in expanded as well as compact notations

@@
 \usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
-\usepackage[margin=0.5in]{geometry}
+\usepackage[margin=0.5in,bottom=0.6in]{geometry}
 \usepackage[T1]{fontenc}
@@
 \setlength\delimitershortfall{-2pt}
-\pagestyle{fancy}
-\fancyhf{}
-\fancyfoot{}
-\fancyhead[L]{\nouppercase\leftmark}    
-\fancyhead[R]{\thepage}    
-\setlength{\headheight}{52pt}
+%\pagestyle{fancy}
+%\fancyhf{}
+%\fancyfoot{}
+%\fancyhead[L]{\nouppercase\leftmark}    
+%\fancyhead[R]{\thepage}    
+%\setlength{\headheight}{52pt}
 \setcounter{tocdepth}{1}
@@
 \newpage
-\section*{Appendix}
-\subsection*{Spectra of Hubbard dimer and Anderson molecule}
+\section*{Appendix: Spectra of Hubbard dimer and Anderson molecule}
 %Here we document the spectra of the Hamiltonians in eqs.~\ref{hubb_dimer} and \ref{and_dimer}.
@@
 	$-a_2(\frac{1}{2}U^A, t^A) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{+}$ & \(\frac{1}{2}\Delta(\frac{1}{2}U^A, t^A)\)\\
-	\(-a_1\left(\pm U^A, t^A\right)\ket{\sigma,2} \pm a_2\left(\pm U^A, t^A\right)\ket{2, \sigma}\) & \(\ket{2\sigma_\pm}\) & \(\pm\frac{1}{4}\Delta(U^A, t^A)\)\\
+	\(a_1\left(U^A, t^A\right)\ket{\sigma,2} - a_2\left(U^A, t^A\right)\ket{2, \sigma}\) & \(\ket{2\sigma_-}\) & \(-\frac{1}{4}\Delta(U^A, t^A)\)\\
+	\(a_2\left(U^A, t^A\right)\ket{\sigma,2} + a_1\left(U^A, t^A\right)\ket{2, \sigma}\) & \(\ket{2\sigma_+}\) & \(\frac{1}{4}\Delta(U^A, t^A)\)\\
 	\(\ket{2,2}\) & \(\ket{4}\) & \(\frac{U^A}{4}\)\\
@@
 \end{center}
-\subsection*{Local Greens function for the Hubbard dimer}
+\section*{Appendix: Local Greens function for the Hubbard dimer}
 From the spectral representation, we have the following expression for the local Greens function at the $i^\text{th}$:
@@
 
-\subsection*{Greens functions for Anderson molecule}
+\section*{Appendix: Greens functions for Anderson molecule}
 \begin{equation}\begin{aligned}
@@
 	G_{zz}^\uparrow(\omega)&= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{z\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{z\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
-	G_{dz}^\uparrow(\omega)	&= \sum_{n}\left[\frac{\left<GS|c_{d\uparrow} | n \right>\left<n |c^\dagger_{z \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{d\uparrow} | GS\right>\left<GS |c^\dagger_{z \uparrow} |n\right>}{\omega + E_{GS} - E_n}\right]\\
-	G_{zd}^\uparrow(\omega) &= \sum_{n}\left[\frac{\left<GS|c_{z \uparrow} | n \right>\left<n |c^\dagger_{d \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{z \uparrow} | GS\right>\left<GS |c^\dagger_{d \uparrow} | n\right>}{\omega + E_{n} - E_{GS}}\right]\\
+	G_{dz}^\uparrow(\omega)	&= \sum_{n}\left[\frac{\left<GS|c_{d\uparrow} | n \right>\left<n |c^\dagger_{z \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{d\uparrow} | GS\right>\left<GS |c^\dagger_{z \uparrow} |n\right>}{\omega + E_{n} - E_{GS}}\right]\\
+	G_{zd}^\uparrow(\omega) &= \sum_{n}\left[\frac{\left<GS|c_{z \uparrow} | n \right>\left<n |c^\dagger_{d \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{z \uparrow} | GS\right>\left<GS |c^\dagger_{d \uparrow} | n\right>}{\omega + E_{n} - E_{GS}}\right] = \left\{G_{dz}^\uparrow(\omega)\right\}^\dagger\\
+\end{aligned}\end{equation}
+We proceed exactly as before. With the following shorthand notations,
+\begin{equation}\begin{aligned}
+	a_{1,2} &\equiv a_{1,2}\left(U^A, t^A\right), &&\tilde a_{1,2} \equiv a_{1,2}\left(\frac{1}{2}U^A, t^A\right) \\
+	\Delta &\equiv \Delta\left(U^A, t^A\right), &&\tilde \Delta \equiv \Delta\left(\frac{1}{2}U^A, t^A\right)\\
+	C_z^\pm &\equiv a_1 \tilde a_1 \pm a_2 \tilde a_2, &&C_x^\pm \equiv a_1 \tilde a_2 \pm a_2 \tilde a_1
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	E_{\pm} \equiv E(\ket{2\sigma_\pm}) - E(\ket{-}) = E(\ket{0\sigma_\pm}) - E(\ket{-}) = \frac{1}{2}\tilde\Delta \pm \frac{1}{4}\Delta\\
+\end{aligned}\end{equation}
+the diagonal Green's functions are
+\begin{equation}\begin{aligned}
+	G_{d d}^\uparrow(\omega) &= \left[a_1\tilde a_2 + a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_1 - a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
+				 &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	G_{z z}^\uparrow(\omega) &= \left[a_1\tilde a_1 + a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_2 - a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
+				 &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
+\end{aligned}\end{equation}
+and the off-diagonal Greens functions are
+\begin{equation}\begin{aligned}
+	G_{dz}^\uparrow(\omega) &= \left(a_1 \tilde a_1 + a_2 \tilde a_2\right) \left(a_1 \tilde a_2 + a_2 \tilde a_1\right) \frac{\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta}{\omega^2 - \left(\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta\right)^2} - \left(a_1 \tilde a_1 - a_2 \tilde a_2\right) \left(a_1 \tilde a_2 - a_2 \tilde a_1\right) \frac{\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta}{\omega^2  - \left(\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right)^2}\\
+				&= -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}\\
+G_{zd}^\uparrow(\omega) &= {G_{dz}^\uparrow(\omega)}^\dagger = G_{dz}^\uparrow(\omega)
+\end{aligned}\end{equation}
+To summarize, the four Green's real space Greens functions, in the compact notation, of the Anderson molecule are
+\begin{equation}\begin{aligned}
+	G_{dd}^\uparrow(\omega) &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
+	G_{zz}^\uparrow(\omega) &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
+	G_{dz}^\uparrow(\omega) &= G_{zd}^\uparrow(\omega) = -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}
 \end{aligned}\end{equation}

### 2021-08-05 notes.tex
the Greens functions dont seem to match up, most probably because of the dissimilar n=1(3) sectors. Scrape this approach.

--- 2021-08-04 notes.tex
@@
 \begin{equation}\begin{aligned}
-	G_H(\vec k, \omega) &= g_0 + g_1 \xi_{\vec k}\\
-			    &= \frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right] + \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]\xi_{\vec k}
+	G_H(\vec k, \omega) &= \left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\\
+			    &= \left\{\frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right] + \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]\xi_{\vec k}\right\}^{-1}
 \end{aligned}\end{equation}
 
+\section{Why this does not work}
+Armed with the expression for the momentum space Greens function, one can compute the real space local Green's function by summing over the momenta:
+\begin{equation}\begin{aligned}
+	G_H(\vec r = 0, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}
+\end{aligned}\end{equation}
+For the Hubbard dimer, the set of momenta are $0, \frac{\pi}{a}$, so
+\begin{equation}\begin{aligned}
+	\xi_{\vec k} = 2, -2
+\end{aligned}\end{equation}
+Therefore, the Greens function at $\vec r=0$ for the Hubbard dimer can be expressed as
+\begin{equation}\begin{aligned}
+	G_H(\vec r = 0, \omega) = \frac{1}{2}\left[\frac{1}{g_0 + 2g_1} + \frac{1}{g_0 - 2g_1}\right]  = \frac{g_0}{g_0^2 - 4g_1^2}
+\end{aligned}\end{equation}
+$g_{0,1}$ are expressed in terms of the elements of the inverse Greens function matrix of the Anderson molecule. The inverse of a $2\times 2$ matrix is
+\begin{equation}\begin{aligned}
+	G_A^{-1} = \frac{1}{\text{Det }G_A}\begin{pmatrix} \left(G_A\right)_{zz} &  -\left(G_A\right)_{zd} \\ -\left(G_A\right)_{zd} & \left(G_A\right)_{dd}\end{pmatrix} \implies \begin{cases}
+		g_0 = \frac{1}{2} \frac{1}{\text{Det }G_A}\left[\left(G_A\right)_{zz} + \left(G_A\right)_{dd}\right] \\
+		g_1 = -\frac{1}{\text{Det }G_A}\left(G_A\right)_{zd} \\
+	\end{cases}
+\end{aligned}\end{equation}
+The matrix elements of $G_A$ are calculated in the appendix.
+The actual real space local Greens function for the Hubbard dimer is also shown there.
+By comparing the Greens functions (for eg., eqs.~\ref{dimer_local_G} and \ref{mole_local_G}), one can see that the structures of the denominators are different.
+This is because of the fact that the eigenvalues for $n=1$ or $n=3$ of the Hubbard dimer are different from that for the Anderson molecule.
+This indicates that we need to change the auxiliary system (SIAM with non-interacting zero mode).
 \newpage
-\section*{Appendix}
-\subsection*{Spectra of Hubbard dimer and Anderson molecule}
+\section*{Appendix: Spectra of Hubbard dimer and Anderson molecule}
 %Here we document the spectra of the Hamiltonians in eqs.~\ref{hubb_dimer} and \ref{and_dimer}.
@@
 \begin{equation}\begin{aligned}
+	\label{dimer_local_G}
 	G_{i i}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} - t\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} + t\right) ^2}
@@
 	G_{zz}^\uparrow(\omega)&= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{z\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{z\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
-	G_{dz}^\uparrow(\omega)	&= \sum_{n}\left[\frac{\left<GS|c_{d\uparrow} | n \right>\left<n |c^\dagger_{z \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{d\uparrow} | GS\right>\left<GS |c^\dagger_{z \uparrow} |n\right>}{\omega + E_{GS} - E_n}\right]\\
-	G_{zd}^\uparrow(\omega) &= \sum_{n}\left[\frac{\left<GS|c_{z \uparrow} | n \right>\left<n |c^\dagger_{d \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{z \uparrow} | GS\right>\left<GS |c^\dagger_{d \uparrow} | n\right>}{\omega + E_{n} - E_{GS}}\right]\\
+	G_{dz}^\uparrow(\omega)	&= \sum_{n}\left[\frac{\left<GS|c_{d\uparrow} | n \right>\left<n |c^\dagger_{z \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{d\uparrow} | GS\right>\left<GS |c^\dagger_{z \uparrow} |n\right>}{\omega + E_{n} - E_{GS}}\right]\\
+	G_{zd}^\uparrow(\omega) &= \sum_{n}\left[\frac{\left<GS|c_{z \uparrow} | n \right>\left<n |c^\dagger_{d \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{z \uparrow} | GS\right>\left<GS |c^\dagger_{d \uparrow} | n\right>}{\omega + E_{n} - E_{GS}}\right] = \left\{G_{dz}^\uparrow(\omega)\right\}^\dagger\\
+\end{aligned}\end{equation}
+We proceed exactly as before. With the following shorthand notations,
+\begin{equation}\begin{aligned}
+	a_{1,2} &\equiv a_{1,2}\left(U^A, t^A\right), &&\tilde a_{1,2} \equiv a_{1,2}\left(\frac{1}{2}U^A, t^A\right) \\
+	\Delta &\equiv \Delta\left(U^A, t^A\right), &&\tilde \Delta \equiv \Delta\left(\frac{1}{2}U^A, t^A\right)\\
+	C_z^\pm &\equiv a_1 \tilde a_1 \pm a_2 \tilde a_2, &&C_x^\pm \equiv a_1 \tilde a_2 \pm a_2 \tilde a_1
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	E_{\pm} \equiv E(\ket{2\sigma_\pm}) - E(\ket{-}) = E(\ket{0\sigma_\pm}) - E(\ket{-}) = \frac{1}{2}\tilde\Delta \pm \frac{1}{4}\Delta\\
+\end{aligned}\end{equation}
+the diagonal Green's functions are
+\begin{equation}\begin{aligned}
+	\label{mole_local_G}
+	G_{d d}^\uparrow(\omega) &= \left[a_1\tilde a_2 + a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_1 - a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
+				 &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	G_{z z}^\uparrow(\omega) &= \left[a_1\tilde a_1 + a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_2 - a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
+				 &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
+\end{aligned}\end{equation}
+and the off-diagonal Greens functions are
+\begin{equation}\begin{aligned}
+	G_{dz}^\uparrow(\omega) &= \left(a_1 \tilde a_1 + a_2 \tilde a_2\right) \left(a_1 \tilde a_2 + a_2 \tilde a_1\right) \frac{\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta}{\omega^2 - \left(\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta\right)^2} - \left(a_1 \tilde a_1 - a_2 \tilde a_2\right) \left(a_1 \tilde a_2 - a_2 \tilde a_1\right) \frac{\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta}{\omega^2  - \left(\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right)^2}\\
+				&= -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}\\
+G_{zd}^\uparrow(\omega) &= {G_{dz}^\uparrow(\omega)}^\dagger = G_{dz}^\uparrow(\omega)
+\end{aligned}\end{equation}
+To summarize, the four Green's real space Greens functions, in the compact notation, of the Anderson molecule are
+\begin{equation}\begin{aligned}
+	G_{dd}^\uparrow(\omega) &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
+	G_{zz}^\uparrow(\omega) &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
+	G_{dz}^\uparrow(\omega) &= G_{zd}^\uparrow(\omega) = -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}
 \end{aligned}\end{equation}

### 2021-08-05 notes.tex
oh god, what a blunder. Incorrectly calculated the general expression for the Greens function. Rectified the general part. Next need to do that for the specific case of the dimer

@@
 For the dimer versions, we had \(N=2, w=1\) and if we substitute these values into the transformations we recover the transformations we had discovered that worked for the dimer.
-The Hubbard Hamiltonian can thus be obtained from the Anderson dimer using the following equation
+The Hubbard Hamiltonian can thus be obtained from the Anderson molecule using the following equation:
+\begin{equation}\begin{aligned}
+	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
+\end{aligned}\end{equation}
+The combination that is being summed over,
+\begin{equation}\begin{aligned}
+	H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)
+\end{aligned}\end{equation}
+is actually a Hubbard dimer Hamiltonian.
+\begin{equation}\begin{aligned}
+	&H^D(U^D, t^D) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)\\
+	&H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right) = -2t^A\sum_\sigma\left( c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.} \right) + U^A\left( \tau_{i \uparrow}\tau_{i \downarrow} + \tau_{i \uparrow}\tau_{i \downarrow}\right)\\
+	\implies &H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right) = H^D(0 \to i, 1 \to j, t^D \to 2t^A, U^D \to U^A)
+\end{aligned}\end{equation}
+The tiling can thus be actually done in terms of Hubbard dimers:
+\begin{equation}\begin{aligned}
+	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^D\left(1 \to i, 2 \to j\right)\right]_{t^D \to Nwt^H \atop{U^A \to N U^H}}
+\end{aligned}\end{equation}
+For reasons that will become apparent later, we will scale the internal Hubbard dimer by half, pulling out a two:
 \begin{equation}\begin{aligned}
 	\label{H_tiled}
-	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
+	H^H\left(t^H, U^H\right)  = \frac{2}{Nw}\sum_{\left<i,j\right>}\left[H^D\left(1 \to i, 2 \to j\right)\right]_{t^D \to \frac{1}{2}Nwt^H \atop{U^D \to \frac{1}{2}N U^H}}
 \end{aligned}\end{equation}
+
 \section{Computing Greens functions and related quantities}
@@
 	\label{green_eq}
-	\omega - {G_H}^{-1}(\omega) = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[\left(\omega - {G_A}^{-1}(\omega)\right)\left(d, z \to i,j\right) + \left(\omega - {G_A}^{-1}(\omega)\right)\left(d,z \to j,i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
+	\omega - {G_H}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}\left[\omega - G_D^{-1}\left(1 \to i, 2 \to j\right)\right]_{t^D \to \frac{1}{2}Nwt^H \atop{U^D \to \frac{1}{2}N U^H}}
 \end{aligned}\end{equation}
-where $G_H$ and $G_A$ are the Hubbard and SIAM Greens functions:
+where $G_H$ and $G_A$ are the Greens functions for the full Hubbard and the Hubbard dimer respectively:
 \begin{equation}\begin{aligned}
-	G_H(\omega) = \frac{1}{\omega - H_H}, && G_A(\omega) = \frac{1}{\omega - H_A}
+	G_H(\omega) = \frac{1}{\omega - H^H}, && G_D(\omega) = \frac{1}{\omega - H^D}
 \end{aligned}\end{equation}
-Since the two $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, they can be pulled out along with a factor.
-Each will come with a factor which is just the total number of nearest neighbour pairs, which is $ \frac{Nw}{2}$.
-This allows them to cancel the $\omega$ on the LHS.
+Since the $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, they can be pulled out along with a factor.
+The factor is just the total number of nearest neighbour pairs, which is $\frac{Nw}{2}$.
+This allows it to cancel the $\omega$ on the LHS.
 The equation then simplifies to
@@
 	\label{green_eq_final}
-	{G_H}^{-1}(\omega) = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[\tilde G_A^{-1}(\omega, i, j) + \tilde G_A^{-1}(\omega, j, i)\right]
+{G_H}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}\left[G_D^{-1}\left(\omega, 1 \to i, 2 \to j\right)\right]_{t^D \to \frac{1}{2}Nwt^H \atop{U^D \to \frac{1}{2}N U^H}} = \frac{2}{Nw}\sum_{\left<i,j\right>}G_D^{-1}\left(\omega, i, j, t^D = \frac{1}{2}Nwt^H, U^D = \frac{1}{2}N U^H\right)
 \end{aligned}\end{equation}
-where $\tilde G_A^{-1}(\omega, i, j) = \omega - \tilde H^A(i, j)$, and $H^A(i, j)$ is defined as
+where $G_D^{-1}(i,j,t^D,U^D)$ is the Greens function (matrix) of the Hubbard dimer Hamiltonian with $i, j$ as the two sites.
+Henceforth, we will supress the transformation rules in the arguments of the Greens function and assume they have been applied.
+For the record, the transformations are
 \begin{equation}\begin{aligned}
-	\tilde H^A(i, j) = -\frac{Nw}{2}t^H\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + N U^H\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
+	t^D &= \frac{1}{2}Nwt^H\\
+	U^D &= \frac{1}{2}N U^H
 \end{aligned}\end{equation}
-$\tilde H^A(i, j)$ is nothing but the Anderson molecule Hamiltonian, but with the impurity replaced by the $i^\text{th}$ site and the zero-mode replaced by the $j^\text{th}$ site.
-It is important to note that $\tilde G_A^{-1}(\omega, i, j)$ only scatters between the sites $i,j$.
-
+\\\\
 We will now calculate the single-particle site diagonal and site offdiagonal Greens functions.
@@
 There will be $w$ such terms, because $i$ has $w$ nearest neighbours.
-Each such pair will have two terms, one with $i$ as the impurity and another with $i$ as the zero-mode.
-For the term that has $i$ as the impurity, the Greens function would then represent the impurity-diagonal Greens function $(G_{dd}^\sigma)$ of the zero-mode SIAM, while for the other term, the Greens function would represent the bath-diagonal or the zero-mode diagonal Greens function $(G_{zz}^\sigma)$.
+Thus, the right hand side will be a sum of $w$ terms, each term being the inverse Greens function of a Hubbard dimer.
+Each term will be a real space local Greens function, and because of translational invariance, it will be the same on both sites.
+So we will represent the real space local inverse Greens function as $\left[G_D^{-1}(\omega)\right]_{00\sigma}$.
+The entire thing is thus $w$ times this local Greens function.
 \begin{equation}\begin{aligned}
-	\left(G_{H}^{-1}(\omega)\right)_{i\sigma,i\sigma} = \frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right]
+	\left(G_{H}^{-1}(\omega)\right)_{i\sigma,i\sigma} = \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{00\sigma}\times w = \frac{2}{N}\left[G_{D}^{-1}(\omega)\right]_{00\sigma} \equiv g_0
 \end{aligned}\end{equation}
@@
 This will receive contribution from only one nearest neighbour pair in the summation of the RHS of eq.~\ref{green_eq_final}, namely that of $\left(i,j\right)$.
-The two terms for this nearest neighbour pair will be one for impurity as $i$ and the other for impurity as $j$.
-The Greens function will thus be the impurity-zero mode and zero mode-impurity Greens functions:
+This will not be a diagonal Greens function.
+Instead, it involves two nearest neighbour sites.
+We call this Greens function $\left[G_D^{-1}(\omega)\right]_{01\sigma}$.
 \begin{equation}\begin{aligned}
-	\left(G_{H}^{-1}(\omega)\right)_{\left<i,j \right>\sigma} &= \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]
+	\left(G_{H}^{-1}(\omega)\right)_{\left<i,j \right>\sigma} &= \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01\sigma} \equiv g_1
 \end{aligned}\end{equation}
@@
 Because of translational invariance, we know that $\left(G_H^{-1}\right)_{ii}$ and $\left(G_H^{-1}\right)_{ij}$ are independent of $i,j$.
-For brevity, we therefore label them $g_0$ and $g_1$ respectively.
-\begin{equation}\begin{aligned}
-	g_0 &\equiv \frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right]\\
-	g_1 &\equiv \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]
-\end{aligned}\end{equation}
-
 \begin{equation}\begin{aligned}
@@
 	G_H(\vec k, \omega) &= \left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\\
-			    &= \left\{\frac{1}{N}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-d\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-z\sigma}\right] + \frac{1}{Nw}\left[\left(\tilde G_{A}^{-1}(\omega)\right)_{d\sigma-z\sigma} + \left(\tilde G_{A}^{-1}(\omega)\right)_{z\sigma-d\sigma}\right]\xi_{\vec k}\right\}^{-1}
+			    &= \left\{\frac{2}{N}\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}
 \end{aligned}\end{equation}
 
-\section{Why this does not work}
-Armed with the expression for the momentum space Greens function, one can compute the real space local Green's function by summing over the momenta:
-\begin{equation}\begin{aligned}
-	G_H(\vec r = 0, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}
-\end{aligned}\end{equation}
-For the Hubbard dimer, the set of momenta are $0, \frac{\pi}{a}$, so
-\begin{equation}\begin{aligned}
-	\xi_{\vec k} = 2, -2
-\end{aligned}\end{equation}
-Therefore, the Greens function at $\vec r=0$ for the Hubbard dimer can be expressed as
-\begin{equation}\begin{aligned}
-	G_H(\vec r = 0, \omega) = \frac{1}{2}\left[\frac{1}{g_0 + 2g_1} + \frac{1}{g_0 - 2g_1}\right]  = \frac{g_0}{g_0^2 - 4g_1^2}
-\end{aligned}\end{equation}
-$g_{0,1}$ are expressed in terms of the elements of the inverse Greens function matrix of the Anderson molecule. The inverse of a $2\times 2$ matrix is
-\begin{equation}\begin{aligned}
-	G_A^{-1} = \frac{1}{\text{Det }G_A}\begin{pmatrix} \left(G_A\right)_{zz} &  -\left(G_A\right)_{zd} \\ -\left(G_A\right)_{zd} & \left(G_A\right)_{dd}\end{pmatrix} \implies \begin{cases}
-		g_0 = \frac{1}{2} \frac{1}{\text{Det }G_A}\left[\left(G_A\right)_{zz} + \left(G_A\right)_{dd}\right] \\
-		g_1 = -\frac{1}{\text{Det }G_A}\left(G_A\right)_{zd} \\
-	\end{cases}
-\end{aligned}\end{equation}
-The matrix elements of $G_A$ are calculated in the appendix.
-The actual real space local Greens function for the Hubbard dimer is also shown there.
-By comparing the Greens functions (for eg., eqs.~\ref{dimer_local_G} and \ref{mole_local_G}), one can see that the structures of the denominators are different.
-This is because of the fact that the eigenvalues for $n=1$ or $n=3$ of the Hubbard dimer are different from that for the Anderson molecule.
-This indicates that we need to change the auxiliary system (SIAM with non-interacting zero mode).
 \newpage

### 2021-08-05 notes.tex
tried to calculate GF for dimer, ran into some problems, will check after dinner

@@
 \end{aligned}\end{equation}
+Armed with the expression for the momentum space Greens function, one can compute the real space local Green's function by summing over the momenta:
+\begin{equation}\begin{aligned}
+	G_H(\vec r = 0, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}
+\end{aligned}\end{equation}
+For the Hubbard dimer, the set of momenta are $0, \frac{\pi}{a}$, so
+\begin{equation}\begin{aligned}
+	\xi_{\vec k} = 2, -2
+\end{aligned}\end{equation}
+Therefore, the Greens function at $\vec r=0$ for the Hubbard dimer can be expressed as
+\begin{equation}\begin{aligned}
+	G_H(\vec r = 0, \omega) = \frac{1}{2}\left[\frac{1}{g_0 + 2g_1} + \frac{1}{g_0 - 2g_1}\right]  = \frac{g_0}{g_0^2 - 4g_1^2}
+\end{aligned}\end{equation}
+$g_{0,1}$ are expressed in terms of the elements of the inverse Greens function matrix of the Hubbard dimer. The inverse of a $2\times 2$ matrix is
+\begin{equation}\begin{aligned}
+	G_D^{-1} = \frac{1}{\text{Det }G_D}\begin{pmatrix} \left(G_D\right)_{00} &  -\left(G_D\right)_{01} \\ -\left(G_D\right)_{01} & \left(G_D\right)_{00}\end{pmatrix} \implies \begin{cases}
+		g_0 = \frac{2}{2} \frac{1}{\text{Det }G_D}\left(G_D\right)_{00} \\
+		\\
+		g_1 = -\frac{2}{2\times 1}\frac{1}{\text{Det }G_D}\left(G_D\right)_{01} \\
+	\end{cases}
+\end{aligned}\end{equation}
+Substituting these values into the expression gives
+\begin{equation}\begin{aligned}
+	G_H(\vec r = 0, \omega) = \text{Det }G_D\frac{g_0}{g_0^2 - 4g_1^2}
+\end{aligned}\end{equation}
 

### 2021-08-05 notes.tex
finally managed to match the Greens functions for the Hubbard dimer

@@
 \end{aligned}\end{equation}
-\\\\
 We will now calculate the single-particle site diagonal and site offdiagonal Greens functions.
@@
 	\sum_i \ket{i}\bra{i} &= \frac{1}{N}\sum_i \sum_{\vec k, \vec q} e^{i \left(\vec{k} - \vec q\right)\cdot\vec{r_i}}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{\vec k, \vec q} N \delta\left(\vec{k} - \vec q\right)\ket{\vec k}\bra{\vec q} = \sum_{\vec k=\vec k_1}^{\vec k_N} \ket{\vec k}\bra{\vec k}\\
-\sum_{\left<i,j \right>} \ket{i}\bra{j} &= \frac{1}{N}\sum_{\left<i,j \right>} \sum_{\vec k, \vec q} e^{i \left(\vec{k}\cdot \vec r_i - \vec q\cdot \vec r_j\right)}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{i=1}^N e^{i \left(\vec{k} - \vec q\right)\cdot \vec r_i}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec k, \vec q} e^{-i\vec q\cdot a_i\hat e_i}\ket{\vec k}\bra{\vec q}\\
-					&=\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec q} e^{-i\vec q\cdot \vec e_i}\ket{\vec q}\bra{\vec q} = \sum_{\vec q} \left(\sum_{i_1}^{D}e^{-ia_iq_i}\right)\ket{\vec q}\bra{\vec q}
+	\sum_{\left<i,j \right>} \ket{i}\bra{j} &= \frac{1}{N}\sum_{\left<i,j \right>} \sum_{\vec k, \vec q} e^{i \left(\vec{k}\cdot \vec r_i - \vec q\cdot \vec r_j\right)}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\frac{1}{2}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec k, \vec q} e^{-i\vec q\cdot a_i\hat e_i}\ket{\vec k}\bra{\vec q}\sum_{i=1}^N e^{i \left(\vec{k} - \vec q\right)\cdot \vec r_i} & \left[\sum_{\left<i,j \right>} = \frac{1}{2}\sum_i \sum_{j \in \text{NN of i}}\right] \\
+					&=\frac{1}{2}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec q} e^{-i\vec q\cdot \vec e_i}\ket{\vec q}\bra{\vec q} = \frac{1}{2}\sum_{\vec q} \left(\sum_{i_1}^{D}e^{-ia_iq_i}\right)\ket{\vec q}\bra{\vec q}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\sum_i \ket{i}\bra{i} =\sum_{\vec q} \underbrace{\sum_{i_1}^{D}2\cos\left(a_iq_i\right)}_{\equiv \xi_{\vec q}}\ket{\vec q}\bra{\vec q}
+	\sum_{\left<i,j \right>} \ket{i}\bra{j} + \text{h.c.} =\sum_{\vec q} \underbrace{\sum_{i_1}^{D}\cos\left(a_iq_i\right)}_{\equiv \xi_{\vec q}}\ket{\vec q}\bra{\vec q}
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
-For the Hubbard dimer, the set of momenta are $0, \frac{\pi}{a}$, so
+We now wish to calculate \(G_H(\vec r = 0, \omega)\) (hence test this expression) for the Hubbard dimer \(\left(N = 2, w = 1 \right)\). The discrete set of momenta are $0, \frac{\pi}{a}$, so
 \begin{equation}\begin{aligned}
-	\xi_{\vec k} = 2, -2
+	\xi_{\vec k} = 1, -1
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G_H(\vec r = 0, \omega) = \frac{1}{2}\left[\frac{1}{g_0 + 2g_1} + \frac{1}{g_0 - 2g_1}\right]  = \frac{g_0}{g_0^2 - 4g_1^2}
+	G_H(\vec r = 0, \omega) = \frac{1}{2}\left[\frac{1}{g_0 + g_1} + \frac{1}{g_0 - g_1}\right]  = \frac{g_0}{g_0^2 - g_1^2}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G_H(\vec r = 0, \omega) = \text{Det }G_D\frac{g_0}{g_0^2 - 4g_1^2}
+	G_H(\vec r = 0, \omega) = \text{Det }G_D\frac{\left(G_D\right)_{00}}{\left(G_D\right)_{00}^2 - \left(G_D\right)_{01}^2} = \text{Det }G_D\frac{\left(G_D\right)_{00}}{\text{Det }G_D} = \left(G_D\right)_{00}
 \end{aligned}\end{equation}
+This is the correct result, because the full Hubbard model in this case was simply the Hubbard dimer, so \(G_H(\vec r = 0, \omega)\) should just be \(\left(G_D\right)_{00}\).
+Although this is a trivial example (we matched the Hubbard dimer with another Hubbard dimer), this atleast tells us that this algorithm for calculating the real space local Greens function from the inverse Greens function matrix elements is sensible.
 

### 2021-08-06 notes.tex
added figures for Greens function

@@
 \usepackage[hidelinks,pdfusetitle]{hyperref}
-\usepackage[stable]{footmisc}
 \renewcommand{\arraystretch}{1.9}
 \setlength\delimitershortfall{-2pt}
-%\pagestyle{fancy}
-%\fancyhf{}
-%\fancyfoot{}
-%\fancyhead[L]{\nouppercase\leftmark}    
-%\fancyhead[R]{\thepage}    
-%\setlength{\headheight}{52pt}
 \setcounter{tocdepth}{1}
@@
 \end{aligned}\end{equation}
-For reasons that will become apparent later, we will scale the internal Hubbard dimer by half, pulling out a two:
+Since the total number of nearest neighbour pairs is $\frac{Nw}{2}$, we want the prefactor to be the same. We will scale the internal Hubbard dimer by half, pulling out a two:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
+From this representation of the full Hubbard model, it is clear that symmetrizing the Anderson molecules by translating them throughout the lattice has restored translational invariance, and generated correlations on all sites (as compared to just on the impurity site).
+This also takes care of the problem that the spectrum of the Anderson molecule and Hubbard dimer are different for the $N=1$ or $N=3$ sectors: By translating the Anderson molecule suitably, we have recovered the correct spectrum in all sectors.
 
@@
 \begin{equation}\begin{aligned}
+	\label{local_gf}
 	\left(G_{H}^{-1}(\omega)\right)_{i\sigma,i\sigma} = \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{00\sigma}\times w = \frac{2}{N}\left[G_{D}^{-1}(\omega)\right]_{00\sigma} \equiv g_0
@@
 \end{aligned}\end{equation}
+\begin{figure}[htpb!]
+	\centering
+	\hspace*{\fill}
+	\includegraphics[width=0.7\textwidth]{./lattice.png}
+	\hspace*{\fill}
+	\caption{\textit{Left:} Part of the lattice that is picked out by the Greens function on the LHS of eq.~\ref{local_gf}.
+\textit{Right:} Hamiltonian whose Greens functions appear on the right hand side of same equation.
+The two submodels are identical.}
+	\label{fig:}
+\end{figure}
+\\\\
 Since the only real-space interaction is that between the nearest neighbours, there are no further real space Greens functions, and the matrix $G^{-1}$ is tridiagonal in real space.

### 2021-08-06 notes.tex
polished the overall thing, added a part on the Bethe lattice, added figures for Anderson molecule and Hubbard dimer

@@
 \documentclass[12pt]{article}
-\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
+%\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
+\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
 \usepackage[margin=0.5in,bottom=0.6in]{geometry}
@@
 We start with a SIAM (possibly with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian.
-At the fixed-point, assuming the couplings are much larger compared to the kinetic energy, we can approximate the Hamiltonian by a zero-mode of the kinetic energy part, which leads to a two-site Anderson molecule Hamiltonian.
+At the fixed-point, assuming the couplings are much larger compared to the kinetic energy, we can approximate the Hamiltonian by a zero-mode of the kinetic energy part, which leads to a two-site Anderson molecule Hamiltonian (shown in fig.~\ref{and_mol}).
 Such a model is exactly solvable.
@@
 Then we will show how we can create a full Hubbard Hamiltonian by joining Anderson molecule Hamiltonians, and this should hopefully be a step towards getting a general prescription for generating wavefunctions for the full lattice (not just dimers).
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.6\textwidth]{./gen_siam.png}
+	\caption{Anderson molecule schematic version. It consists of two sites, impurity(blue) and zero mode(green). The impurity site has onsite repulsion, and their is inter-site hopping.}
+	\label{and_mol}
+\end{figure}
 
@@
 
-\section{Creating General \(N-\)site Hubbard Hamiltonian from Anderson molecule}
+\section{Creating General \(N-\)site Hubbard Hamiltonian from Hubbard dimers: tiling the lattice with Anderson molecules}
 We will follow the strategy outlined in the previous section.
@@
 \end{aligned}\end{equation}
-The tiling can thus be actually done in terms of Hubbard dimers:
+The tiling can thus be actually done in terms of Hubbard dimers (shown in fig.~\ref{hubb-dim}):
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
+\begin{figure}[htpb!]
+	\centering
+	\includegraphics[width=0.6\textwidth]{./hubb_dim.png}
+	\caption{Hubbard dimer schematic version. It again consists of two sites, like the Anderson molecule, but now both sites have onsite repulsion, and their is again inter-site hopping.}
+	\label{hubb-dim}
+\end{figure}
 Since the total number of nearest neighbour pairs is $\frac{Nw}{2}$, we want the prefactor to be the same. We will scale the internal Hubbard dimer by half, pulling out a two:
@@
 
-\section{Computing Greens functions and related quantities}
+\section{Computing single particle Greens functions and related quantities}
 In terms of the Greens function, equation \ref{H_tiled} becomes
@@
 \end{aligned}\end{equation}
-where $G_H$ and $G_A$ are the Greens functions for the full Hubbard and the Hubbard dimer respectively:
+where $G_H$ and $G_D$ are the Greens functions for the full Hubbard and the Hubbard dimer respectively:
 \begin{equation}\begin{aligned}
@@
 \begin{equation}\begin{aligned}
+\label{nn_gf}
 	\left(G_{H}^{-1}(\omega)\right)_{\left<i,j \right>\sigma} &= \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01\sigma} \equiv g_1
@@
 \end{figure}
-\\\\
 Since the only real-space interaction is that between the nearest neighbours, there are no further real space Greens functions, and the matrix $G^{-1}$ is tridiagonal in real space.
 Because of translational invariance, we know that $\left(G_H^{-1}\right)_{ii}$ and $\left(G_H^{-1}\right)_{ij}$ are independent of $i,j$.
+Furthermore, all expressions below are for a particular spin $\sigma$; from the spin rotational symmetry of the Hubbard Hamiltonian, the same expressions are obtained for the opposite spin.
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
+On a 2D square lattice, for instance, we obtain
+\begin{eqnarray}
+\xi_{\vec{q}} &=& 2(\cos q_{x}a_{x} + \cos q_{y}a_{y})\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
+\epsilon_{\vec{q}} &=& -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})~.\label{2dsquaretb}
+\end{eqnarray}
 The inverse Greens function thus becomes diagonal in momentum space
@@
 \end{aligned}\end{equation}
-The matrix is of course written in momentum space. Since $G_H^{-1}(\omega)$ is diagonal in this basis, we can invert the matrix trivially by replacing the diagonal elements with their reciprocals.
+The matrix is of course written in momentum space, and diagonal.
+Using Dyson's equation for the self-energy $\Sigma = G_{0}^{-1} - G^{-1}$ (where the matrix $G_{0,H}^{-1} (\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N} (\omega -\epsilon_{k})\ket{\vec k}\bra{\vec k}=\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega +t^{H}\xi_{k})\ket{\vec k}\bra{\vec k} $ is the inverse Greens function for the appropriate non-interacting tight-binding system), we obtain the self-energy matrix as
+\begin{eqnarray}
+\Sigma_{H} (\omega) &=& G_{0,H}^{-1} - G_{H}^{-1}~,\nonumber\\
+&=&\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}})\ket{\vec k}\bra{\vec k} = \sum_{\vec k=\vec k_1}^{\vec k_N} \Sigma_{H} (\vec{k},\omega) \ket{\vec k}\bra{\vec k}~,\nonumber\\
+\Sigma_{H} (\vec{k},\omega) &=& \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}~.
+\end{eqnarray}
+Thus, we can use eqs.\eqref{2dsquaretb},\eqref{local_gf} and \eqref{nn_gf} to obtain the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
+\par\noindent
+Since $G_H^{-1}(\omega)$ is diagonal in this basis, we can invert the matrix trivially by replacing the diagonal elements with their reciprocals.
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-The diagonal elements of $G_H$ in momentum space are simply $G_H(\vec k, \omega)$.
+The diagonal elements of $G_H$ in momentum space are simply $G_H(\vec k, \omega)$
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-Armed with the expression for the momentum space Greens function, one can compute the real space local Green's function by summing over the momenta:
+The real-space Greens function, $G_{H}(\vec{r},\omega)$, can now be obtained by Fourier transforming $G_H(\vec k, \omega)$ 
+\begin{equation}
+G_H(\vec r, \omega) = \frac{1}{N}\sum_{\vec k} e^{i\vec{k}.\vec{r}}G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}e^{i\vec{k}.\vec{r}}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}~.
+\end{equation}
+Thus, we can now compute the real space local Green's function $G_H(\vec r = 0, \omega)$ by summing over the momenta:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-We now wish to calculate \(G_H(\vec r = 0, \omega)\) (hence test this expression) for the Hubbard dimer \(\left(N = 2, w = 1 \right)\). The discrete set of momenta are $0, \frac{\pi}{a}$, so
+We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
+\begin{eqnarray}
+A_{H}(\vec{k},\omega) &=& -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{1}{\pi} \textrm{Im}\left[ (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right]~,\nonumber\\
+A_{H}(\vec{r}=0,\omega) &=& -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = -\frac{1}{N\pi} \textrm{Im}\left[\sum_{\vec{k}} (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right] = ~-\frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)~.
+\end{eqnarray}
+We can again use eqs.\eqref{2dsquaretb},\eqref{local_gf} and \eqref{nn_gf} to obtain the spectral functions  $A_{H} (\vec{k},\omega)$ and $A_{H} (\vec{r}=0,\omega)$ for the Hubbard model on the 2D square lattice.
+\par\noindent
+The simplest test involves calculating \(G_H(\vec r = 0, \omega)\) for the Hubbard dimer \(\left(N = 2, w = 1 \right)\). The discrete set of momenta are $0, \frac{\pi}{a}$, so
 \begin{equation}\begin{aligned}
@@
 	G_D^{-1} = \frac{1}{\text{Det }G_D}\begin{pmatrix} \left(G_D\right)_{00} &  -\left(G_D\right)_{01} \\ -\left(G_D\right)_{01} & \left(G_D\right)_{00}\end{pmatrix} \implies \begin{cases}
-		g_0 = \frac{2}{2} \frac{1}{\text{Det }G_D}\left(G_D\right)_{00} \\
+		g_0\equiv\frac{2}{N} (G^{-1}_{D})_{00} = \frac{2}{N} \frac{1}{\text{Det }G_D}\left(G_D\right)_{00} \\
 		\\
-		g_1 = -\frac{2}{2\times 1}\frac{1}{\text{Det }G_D}\left(G_D\right)_{01} \\
+		g_1\equiv\frac{2}{Nw} (G^{-1}_{D})_{00} = -\frac{2}{Nw}\frac{1}{\text{Det }G_D}\left(G_D\right)_{01} \\
 	\end{cases}
 \end{aligned}\end{equation}
-Substituting these values into the expression gives
+Using the expressions for $(G_{D})_{00}$ and $(G_{D})_{01}$ shown in the appendix, we can obtain $g_{0}$ and $g_{1}$ very generally.
+For the Hubbard dimer, we substitute $N=2, w=1$ into the expressions for $g_{0}$ and $g_{1}$ to obtain
 \begin{equation}\begin{aligned}
@@
 Although this is a trivial example (we matched the Hubbard dimer with another Hubbard dimer), this atleast tells us that this algorithm for calculating the real space local Greens function from the inverse Greens function matrix elements is sensible.
-
+\par\noindent
+Another test involves considering the case of infinite number of nearest neighbours $w\to\infty$ (the coordination number, and effectively the dimensionality).
+Here, as has been argued in the DMFT literature, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$ such that the kinetic energy of the associated tight-binding lattice model is finite.
+This allows for the competition between the kinetic and potential terms of the Hamiltonian to drive a metal-insulator transition in the limit of $w\to\infty$ as well.
+Further, it has been argued in the DMFT literature that the Greens function matrix of the Hubbard model on the Bethe lattice with $w\to\infty$ becomes purely local (i.e., it has vanishing inter-site matrix elements).
+We can also see this from eqs.\eqref{local_gf},\eqref{nn_gf} where $(G^{H})^{-1}$ matrix has no $k$ dependence as $(G^{H})^{-1}_{ij}\propto 1/w \to 0$ as $w\to\infty$.
+Thus, in the self-energy
+\begin{eqnarray}
+\Sigma_{H} (\vec{k},\omega) &=& \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}\nonumber\\
+&\to & \lim_{w\to\infty} \omega - {g}_{0} + t^{H}\xi_{\vec{k}}~,
+\end{eqnarray}
+We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.
+\par\noindent
+While we have provided expressions for the single particle Greens functions of the $N$-site Hubbard model from their equivalent single particle Greens functions of the Hubbard dimer, we expect that eq.\eqref{green_eq_final} holds quite generally for the two-particle Greens function sector as well.
+We will provide these expressions at a later point in time.
 \newpage
@@
 \section*{Appendix: Local Greens function for the Hubbard dimer}
-From the spectral representation, we have the following expression for the local Greens function at the $i^\text{th}$:
+From the spectral representation, we have the following expression for the local Greens function for the Hubbard dimer at site $0$:
 \begin{equation}\begin{aligned}
-	G_{i i}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}c_{i\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
+	G_{D,00}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}c_{i\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G_{i i}^\sigma(\omega, T \to 0) &= \sum_{n}\left[||\bra{GS}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
+	G_{D,00}^\sigma(\omega, T \to 0) &= \sum_{n}\left[||\bra{GS}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
 					&= \sum_{n}\left[||\bra{n}c^\dagger_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
@@
 	\label{dimer_local_G}
-	G_{i i}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} - t\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} + t\right) ^2}
+	G_{D,00}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} - t\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} + t\right) ^2} = G_{D,00}^\downarrow(\omega, T \to 0)~.
 \end{aligned}\end{equation}
-The site local spectral can now be calculated:
+In the atomic limit $(t=0)$, the Greens function simplifies to
 \begin{equation}\begin{aligned}
-	A(i\uparrow, \omega) &= - \frac{1}{\pi}\text{Im }G_{i i}^\uparrow(\omega)\\
-			     &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right)\left[\delta(\omega - \frac{1}{2}\Delta - t) + \delta(\omega + \frac{1}{2}\Delta + t)\right] + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \left[\delta(\omega - \frac{1}{2}\Delta + t) + \delta(\omega + \frac{1}{2}\Delta - t)\right]
+	G_{D,00}^\uparrow(\omega, T \to 0) \bigg\vert_\text{atomic} = \frac{\omega}{\omega^2 - \frac{1}{4}U^2}
 \end{aligned}\end{equation}
-
-\section*{Appendix: Greens functions for Anderson molecule}
-\begin{equation}\begin{aligned}
-	G_{dd}^\uparrow(\omega) &= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{d\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{d\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
-	G_{zz}^\uparrow(\omega)&= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{z\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{z\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
-	G_{dz}^\uparrow(\omega)	&= \sum_{n}\left[\frac{\left<GS|c_{d\uparrow} | n \right>\left<n |c^\dagger_{z \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{d\uparrow} | GS\right>\left<GS |c^\dagger_{z \uparrow} |n\right>}{\omega + E_{n} - E_{GS}}\right]\\
-	G_{zd}^\uparrow(\omega) &= \sum_{n}\left[\frac{\left<GS|c_{z \uparrow} | n \right>\left<n |c^\dagger_{d \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{z \uparrow} | GS\right>\left<GS |c^\dagger_{d \uparrow} | n\right>}{\omega + E_{n} - E_{GS}}\right] = \left\{G_{dz}^\uparrow(\omega)\right\}^\dagger\\
-\end{aligned}\end{equation}
-We proceed exactly as before. With the following shorthand notations,
-\begin{equation}\begin{aligned}
-	a_{1,2} &\equiv a_{1,2}\left(U^A, t^A\right), &&\tilde a_{1,2} \equiv a_{1,2}\left(\frac{1}{2}U^A, t^A\right) \\
-	\Delta &\equiv \Delta\left(U^A, t^A\right), &&\tilde \Delta \equiv \Delta\left(\frac{1}{2}U^A, t^A\right)\\
-	C_z^\pm &\equiv a_1 \tilde a_1 \pm a_2 \tilde a_2, &&C_x^\pm \equiv a_1 \tilde a_2 \pm a_2 \tilde a_1
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-	E_{\pm} \equiv E(\ket{2\sigma_\pm}) - E(\ket{-}) = E(\ket{0\sigma_\pm}) - E(\ket{-}) = \frac{1}{2}\tilde\Delta \pm \frac{1}{4}\Delta\\
-\end{aligned}\end{equation}
-the diagonal Green's functions are
-\begin{equation}\begin{aligned}
-	\label{mole_local_G}
-	G_{d d}^\uparrow(\omega) &= \left[a_1\tilde a_2 + a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_1 - a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
-				 &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-	G_{z z}^\uparrow(\omega) &= \left[a_1\tilde a_1 + a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_2 - a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
-				 &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
-\end{aligned}\end{equation}
-and the off-diagonal Greens functions are
-\begin{equation}\begin{aligned}
-	G_{dz}^\uparrow(\omega) &= \left(a_1 \tilde a_1 + a_2 \tilde a_2\right) \left(a_1 \tilde a_2 + a_2 \tilde a_1\right) \frac{\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta}{\omega^2 - \left(\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta\right)^2} - \left(a_1 \tilde a_1 - a_2 \tilde a_2\right) \left(a_1 \tilde a_2 - a_2 \tilde a_1\right) \frac{\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta}{\omega^2  - \left(\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right)^2}\\
-				&= -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}\\
-G_{zd}^\uparrow(\omega) &= {G_{dz}^\uparrow(\omega)}^\dagger = G_{dz}^\uparrow(\omega)
-\end{aligned}\end{equation}
-To summarize, the four Green's real space Greens functions, in the compact notation, of the Anderson molecule are
-\begin{equation}\begin{aligned}
-	G_{dd}^\uparrow(\omega) &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
-	G_{zz}^\uparrow(\omega) &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
-	G_{dz}^\uparrow(\omega) &= G_{zd}^\uparrow(\omega) = -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}
-\end{aligned}\end{equation}
+The site local spectral function can now be calculated:
+\begin{eqnarray}
+A(0\uparrow, \omega) &=& - \frac{1}{\pi}\text{Im }G_{D,00}^\uparrow(\omega)\nonumber\\
+			     &=& \left( \frac{1}{2} + \frac{2t}{\Delta} \right)\left[\delta(\omega - \frac{1}{2}\Delta - t) + \delta(\omega + \frac{1}{2}\Delta + t)\right]\nonumber\\ 
+			     &&+ \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \left[\delta(\omega - \frac{1}{2}\Delta + t) + \delta(\omega + \frac{1}{2}\Delta - t)\right]\\ 
+			     &=& A(0\downarrow, \omega)~.\nonumber
+\end{eqnarray}
+Finally, the inter-site Greens function for the Hubbard dimer is given by
+\begin{equation}
+\label{dimer_intersite_G}
+	G_{D,01}^\uparrow(\omega, T \to 0) = \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{t}{(\omega +\frac{\Delta}{2})^2 - t^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{t}{(\omega -\frac{\Delta}{2})^2 - t^2} = G_{D,01}^\downarrow(\omega, T \to 0)~.
+\end{equation}
+%\section*{Appendix: Greens functions for Anderson molecule}
+%\begin{equation}\begin{aligned}
+%	G_{dd}^\uparrow(\omega) &= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{d\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{d\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
+%	G_{zz}^\uparrow(\omega)&= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{z\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{z\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
+%	G_{dz}^\uparrow(\omega)	&= \sum_{n}\left[\frac{\left<GS|c_{d\uparrow} | n \right>\left<n |c^\dagger_{z \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{d\uparrow} | GS\right>\left<GS |c^\dagger_{z \uparrow} |n\right>}{\omega + E_{n} - E_{GS}}\right]\\
+%	G_{zd}^\uparrow(\omega) &= \sum_{n}\left[\frac{\left<GS|c_{z \uparrow} | n \right>\left<n |c^\dagger_{d \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{z \uparrow} | GS\right>\left<GS |c^\dagger_{d \uparrow} | n\right>}{\omega + E_{n} - E_{GS}}\right] = \left\{G_{dz}^\uparrow(\omega)\right\}^\dagger\\
+%\end{aligned}\end{equation}
+%We proceed exactly as before. With the following shorthand notations,
+%\begin{equation}\begin{aligned}
+%	a_{1,2} &\equiv a_{1,2}\left(U^A, t^A\right), &&\tilde a_{1,2} \equiv a_{1,2}\left(\frac{1}{2}U^A, t^A\right) \\
+%	\Delta &\equiv \Delta\left(U^A, t^A\right), &&\tilde \Delta \equiv \Delta\left(\frac{1}{2}U^A, t^A\right)\\
+%	C_z^\pm &\equiv a_1 \tilde a_1 \pm a_2 \tilde a_2, &&C_x^\pm \equiv a_1 \tilde a_2 \pm a_2 \tilde a_1
+%\end{aligned}\end{equation}
+%\begin{equation}\begin{aligned}
+%	E_{\pm} \equiv E(\ket{2\sigma_\pm}) - E(\ket{-}) = E(\ket{0\sigma_\pm}) - E(\ket{-}) = \frac{1}{2}\tilde\Delta \pm \frac{1}{4}\Delta\\
+%\end{aligned}\end{equation}
+%the diagonal Green's functions are
+%\begin{equation}\begin{aligned}
+%	\label{mole_local_G}
+%	G_{d d}^\uparrow(\omega) &= \left[a_1\tilde a_2 + a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_1 - a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
+%				 &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
+%\end{aligned}\end{equation}
+%\begin{equation}\begin{aligned}
+%	G_{z z}^\uparrow(\omega) &= \left[a_1\tilde a_1 + a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_2 - a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
+%				 &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
+%\end{aligned}\end{equation}
+%and the off-diagonal Greens functions are
+%\begin{equation}\begin{aligned}
+%	G_{dz}^\uparrow(\omega) &= \left(a_1 \tilde a_1 + a_2 \tilde a_2\right) \left(a_1 \tilde a_2 + a_2 \tilde a_1\right) \frac{\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta}{\omega^2 - \left(\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta\right)^2} - \left(a_1 \tilde a_1 - a_2 \tilde a_2\right) \left(a_1 \tilde a_2 - a_2 \tilde a_1\right) \frac{\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta}{\omega^2  - \left(\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right)^2}\\
+%				&= -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}\\
+%G_{zd}^\uparrow(\omega) &= {G_{dz}^\uparrow(\omega)}^\dagger = G_{dz}^\uparrow(\omega)
+%\end{aligned}\end{equation}
+%To summarize, the four Green's real space Greens functions, in the compact notation, of the Anderson molecule are
+%\begin{equation}\begin{aligned}
+%	G_{dd}^\uparrow(\omega) &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
+%	G_{zz}^\uparrow(\omega) &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
+%	G_{dz}^\uparrow(\omega) &= G_{zd}^\uparrow(\omega) = -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}
+%\end{aligned}\end{equation}
 

### 2021-08-07 notes.tex
made some obvious simplifications

@@
 	G_H(\vec k, \omega) &= \left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\\
-			    &= \left\{\frac{2}{N}\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}
+			    &= \left\{\frac{2}{N}\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}\\
+			    &= \frac{N}{2}\left\{\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{1}{w}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}\\
 \end{aligned}\end{equation}
 The real-space Greens function, $G_{H}(\vec{r},\omega)$, can now be obtained by Fourier transforming $G_H(\vec k, \omega)$ 
-\begin{equation}
-G_H(\vec r, \omega) = \frac{1}{N}\sum_{\vec k} e^{i\vec{k}.\vec{r}}G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}e^{i\vec{k}.\vec{r}}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}~.
-\end{equation}
+\begin{equation}\begin{aligned}
+	G_H(\vec r, \omega) = \frac{1}{\sqrt N}\sum_{\vec k} e^{i\vec{k}.\vec{r}}G_H(\vec k, \omega) &= \frac{1}{\sqrt N}\sum_{\vec k}e^{i\vec{k}.\vec{r}}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\\
+												     &= \frac{\sqrt N}{2}\sum_{\vec k}e^{i\vec{k}.\vec{r}}\left\{\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{1}{w}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}
+\end{aligned}\end{equation}
 Thus, we can now compute the real space local Green's function $G_H(\vec r = 0, \omega)$ by summing over the momenta:
 \begin{equation}\begin{aligned}
-	G_H(\vec r = 0, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}
+	G_H(\vec r = 0, \omega) = \frac{1}{\sqrt N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{\sqrt N}\sum_{\vec k}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}
 \end{aligned}\end{equation}
 We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
-\begin{eqnarray}
-A_{H}(\vec{k},\omega) &=& -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{1}{\pi} \textrm{Im}\left[ (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right]~,\nonumber\\
-A_{H}(\vec{r}=0,\omega) &=& -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = -\frac{1}{N\pi} \textrm{Im}\left[\sum_{\vec{k}} (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right] = ~-\frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)~.
-\end{eqnarray}
-We can again use eqs.\eqref{2dsquaretb},\eqref{local_gf} and \eqref{nn_gf} to obtain the spectral functions  $A_{H} (\vec{k},\omega)$ and $A_{H} (\vec{r}=0,\omega)$ for the Hubbard model on the 2D square lattice.
+\begin{equation}\begin{aligned}
+A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{1}{\pi} \textrm{Im}\left[ (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right]\\
+A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = -\frac{1}{\sqrt N\pi} \textrm{Im}\left[\sum_{\vec{k}} (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right] = -\frac{1}{\sqrt N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
+\end{aligned}\end{equation}
+We can again use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the spectral functions  $A_{H} (\vec{k},\omega)$ and $A_{H} (\vec{r}=0,\omega)$ for the Hubbard model on the 2D square lattice.
 \par\noindent

### 2021-08-07 notes.tex
cosmetic changes and elaborations

@@
 
-\section{Computing single particle Greens functions and related quantities}
+\section{Formal expressions for single particle Greens functions and other related many-body quantites}
+\subsection{Expressing matrix elements of the inverse single particle Greens function in terms of Hubbard dimer counterparts}
 In terms of the Greens function, equation \ref{H_tiled} becomes
@@
 The two submodels are identical.}
-	\label{fig:}
 \end{figure}
+\subsection{Constructing full Greens function matrix from the inverse matrix via Fourier transformation to \(k-\)space}
 Since the only real-space interaction is that between the nearest neighbours, there are no further real space Greens functions, and the matrix $G^{-1}$ is tridiagonal in real space.
@@
 We can Fourier transform the real space basis kets $\ket{i} \equiv \ket{\vec r_i}$ into momentum space:
-\begin{equation}\begin{aligned}
-	\ket{i} &= \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\vec k}\\
+\begin{flalign*}
+	\ket{i} &= \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\vec k} \Leftrightarrow \ket{k} = \frac{1}{\sqrt N}\sum_{\vec i} e^{-i \vec{k}\cdot\vec{r_i}}\ket{\vec r_i} \\
 	\sum_i \ket{i}\bra{i} &= \frac{1}{N}\sum_i \sum_{\vec k, \vec q} e^{i \left(\vec{k} - \vec q\right)\cdot\vec{r_i}}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{\vec k, \vec q} N \delta\left(\vec{k} - \vec q\right)\ket{\vec k}\bra{\vec q} = \sum_{\vec k=\vec k_1}^{\vec k_N} \ket{\vec k}\bra{\vec k}\\
@@
 					&=\frac{1}{2}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec q} e^{-i\vec q\cdot \vec e_i}\ket{\vec q}\bra{\vec q} = \frac{1}{2}\sum_{\vec q} \left(\sum_{i_1}^{D}e^{-ia_iq_i}\right)\ket{\vec q}\bra{\vec q}
-\end{aligned}\end{equation}
+\end{flalign*}
 $\hat e_i$ are the primitive lattice unit vectors for the general $d-$dimensional lattice.
@@
 \end{aligned}\end{equation}
-The matrix is of course written in momentum space, and diagonal.
+The matrix entries are written in momentum space, and the matrix is diagonal in this basis.
+\subsection{Calculation of self energy matrix from the Dyson equation}
 Using Dyson's equation for the self-energy $\Sigma = G_{0}^{-1} - G^{-1}$ (where the matrix $G_{0,H}^{-1} (\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N} (\omega -\epsilon_{k})\ket{\vec k}\bra{\vec k}=\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega +t^{H}\xi_{k})\ket{\vec k}\bra{\vec k} $ is the inverse Greens function for the appropriate non-interacting tight-binding system), we obtain the self-energy matrix as
@@
 \Sigma_{H} (\omega) &=& G_{0,H}^{-1} - G_{H}^{-1}~,\nonumber\\
-&=&\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}})\ket{\vec k}\bra{\vec k} = \sum_{\vec k=\vec k_1}^{\vec k_N} \Sigma_{H} (\vec{k},\omega) \ket{\vec k}\bra{\vec k}~,\nonumber\\
-\Sigma_{H} (\vec{k},\omega) &=& \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}~.
+&=&\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}})\ket{\vec k}\bra{\vec k}
 \end{eqnarray}
-Thus, we can use eqs.\eqref{2dsquaretb},\eqref{local_gf} and \eqref{nn_gf} to obtain the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
-\par\noindent
+This is the full self energy matrix. One can get both real space and momentum space self energies by taking appropriate matrix elements. For instance, the self-energy in momentum space is
+\begin{equation}\begin{aligned}
+	\label{selfenergy}
+	\Sigma_{H} (\vec{k},\omega) \equiv \bra{\vec k} \Sigma_H (\omega) \ket{\vec k} = \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}~.
+\end{aligned}\end{equation}
+Thus, we can use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
+\subsection{Obtaining real space Greens functions from the full matrix}
 Since $G_H^{-1}(\omega)$ is diagonal in this basis, we can invert the matrix trivially by replacing the diagonal elements with their reciprocals.
 \begin{equation}\begin{aligned}
-	G_H(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\ket{\vec k}\bra{\vec k} = \begin{pmatrix} \left(g_0 + g_1\xi_{\vec k_1}\right)^{-1} &&& \\
-	& \left(g_0 + g_1\xi_{\vec k_2}\right)^{-1} && \\
-	&& \left(g_0 + g_1\xi_{\vec k_3}\right)^{-1} & \\
-	...&...&...&\\
+	\label{k-space-gf}
+	G_H(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\ket{\vec k}\bra{\vec k} = \begin{pmatrix} \left(g_0 + g_1\xi_{\vec k_1}\right)^{-1} &&&&\\
+	& \left(g_0 + g_1\xi_{\vec k_2}\right)^{-1} &&&\\
+	&& \left(g_0 + g_1\xi_{\vec k_3}\right)^{-1} &&\\
+		...&&&...&\\
 	\end{pmatrix} 
@@
 \end{aligned}\end{equation}
-The real-space Greens function, $G_{H}(\vec{r},\omega)$, can now be obtained by Fourier transforming $G_H(\vec k, \omega)$ 
+The real-space Greens functions can now be obtained by taking matrix elements of the full Greens function matrix in eq.~\ref{k-space-gf}:
 \begin{equation}\begin{aligned}
-	G_H(\vec r, \omega) = \frac{1}{\sqrt N}\sum_{\vec k} e^{i\vec{k}.\vec{r}}G_H(\vec k, \omega) &= \frac{1}{\sqrt N}\sum_{\vec k}e^{i\vec{k}.\vec{r}}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\\
-												     &= \frac{\sqrt N}{2}\sum_{\vec k}e^{i\vec{k}.\vec{r}}\left\{\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{1}{w}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}
+	G_H(\vec r_i, \vec  r_j, \omega) \equiv \bra{\vec r_i} G_H(\omega) \ket{\vec r_j} = \sum_{\vec k} G_H(\vec k, \omega)  \left<\vec r_i | \vec k\right>\left<\vec k | \vec r_j\right>
 \end{aligned}\end{equation}
-Thus, we can now compute the real space local Green's function $G_H(\vec r = 0, \omega)$ by summing over the momenta:
+From the definition of the Fourier transforms mentioned previously, we can write
 \begin{equation}\begin{aligned}
-	G_H(\vec r = 0, \omega) = \frac{1}{\sqrt N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{\sqrt N}\sum_{\vec k}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}
+	\left<\vec r_i | \vec k\right> = \frac{1}{\sqrt N}\sum_{\vec r} e^{- \vec{k}\cdot\vec{r}} \left<\vec r_i | \vec r \right> = \frac{1}{\sqrt N}e^{- \vec{k}\cdot\vec{r_i}}
+\end{aligned}\end{equation}
+Substituting this gives
+\begin{equation}\begin{aligned}
+	G_H(\vec r_i, \vec  r_j, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega)  e^{\vec{k}\cdot\left(\vec r_j - \vec{r_i}\right)} \equiv G_H(\vec r_j - \vec  r_i, \omega)
+\end{aligned}\end{equation}
+The final expression brings out the fact that the Greens function for excitations between \(\vec r_i\) and \(\vec r_j\) depends only on the relative position \(\vec r_j - \vec r_i\), not on their absolute positions.
+This is expected on grounds of translational invariance.
+By choosing \(\vec r_i = \vec r_j\), we can obtain the real space \textit{local} Greens function:
+\begin{equation}\begin{aligned}
+	\left(G_H\right)_{ii}(\omega) \equiv G_H(\vec r_j - \vec  r_i = 0, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}
 \end{aligned}\end{equation}
@@
 We can again use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the spectral functions  $A_{H} (\vec{k},\omega)$ and $A_{H} (\vec{r}=0,\omega)$ for the Hubbard model on the 2D square lattice.
-\par\noindent
-The simplest test involves calculating \(G_H(\vec r = 0, \omega)\) for the Hubbard dimer \(\left(N = 2, w = 1 \right)\). The discrete set of momenta are $0, \frac{\pi}{a}$, so
+\subsection{Obtaining \(g_0\) and \(g_1\)}
+These two quantities are expressed in terms of matrix elements of the inverse Greens function \(G_D^{-1}\) of the Hubbard dimer. Since \(G_D\) is a \(2\times 2\) matrix, it is easy to invert:
 \begin{equation}\begin{aligned}
-	\xi_{\vec k} = 1, -1
+	G_D &= \begin{pmatrix} \left(G_D\right)_{00} &  \left(G_D\right)_{01} \\ \left(G_D\right)_{01} & \left(G_D\right)_{00}\end{pmatrix} \\
+	\implies G_D^{-1} &= \frac{1}{\text{Det }G_D}\begin{pmatrix} \left(G_D\right)_{00} &  -\left(G_D\right)_{01} \\ -\left(G_D\right)_{01} & \left(G_D\right)_{00}\end{pmatrix}\\
+		 \implies g_0 &\equiv\frac{2}{N} (G^{-1}_{D})_{00} = \frac{2}{N} \frac{1}{\text{Det }G_D}\left(G_D\right)_{00},\\
+		 g_1 &\equiv\frac{2}{Nw} (G^{-1}_{D})_{00} = -\frac{2}{Nw}\frac{1}{\text{Det }G_D}\left(G_D\right)_{01} 
+\end{aligned}\end{equation}
+Using the expressions for $(G_{D})_{00}$ and $(G_{D})_{01}$ shown in the appendix, we can obtain $g_{0}$ and $g_{1}$ very generally.
+
+\section{Analytic consistency checks}
+\subsection{Single-particle Greens function and self energy for the Hubbard dimer}
+The simplest test involves calculating \(G_H(\vec r = 0, \omega)\) for the Hubbard dimer \(\left(N = 2, w = 1 \right)\).
+The discrete set of momenta are \(\left\{ \vec k_n \right\} = 0, \frac{\pi}{a}\), so
+\begin{equation}\begin{aligned}
+	\left\{\xi_{\vec k}\right\} = 1, -1
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
-$g_{0,1}$ are expressed in terms of the elements of the inverse Greens function matrix of the Hubbard dimer. The inverse of a $2\times 2$ matrix is
+For the Hubbard dimer, we substitute $N=2, w=1$ into the expressions for $g_{0}$ and $g_{1}$ to obtain
 \begin{equation}\begin{aligned}
-	G_D^{-1} = \frac{1}{\text{Det }G_D}\begin{pmatrix} \left(G_D\right)_{00} &  -\left(G_D\right)_{01} \\ -\left(G_D\right)_{01} & \left(G_D\right)_{00}\end{pmatrix} \implies \begin{cases}
-		g_0\equiv\frac{2}{N} (G^{-1}_{D})_{00} = \frac{2}{N} \frac{1}{\text{Det }G_D}\left(G_D\right)_{00} \\
-		\\
-		g_1\equiv\frac{2}{Nw} (G^{-1}_{D})_{00} = -\frac{2}{Nw}\frac{1}{\text{Det }G_D}\left(G_D\right)_{01} \\
-	\end{cases}
+	&g_0 = \frac{1}{\text{Det }G_D}\left( G_D \right)_{00}, &g_1 = -\frac{1}{\text{Det }G_D}\left( G_D \right)_{01}
 \end{aligned}\end{equation}
-Using the expressions for $(G_{D})_{00}$ and $(G_{D})_{01}$ shown in the appendix, we can obtain $g_{0}$ and $g_{1}$ very generally.
-For the Hubbard dimer, we substitute $N=2, w=1$ into the expressions for $g_{0}$ and $g_{1}$ to obtain
+The Greens function at the zeroth site then becomes
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-This is the correct result, because the full Hubbard model in this case was simply the Hubbard dimer, so \(G_H(\vec r = 0, \omega)\) should just be \(\left(G_D\right)_{00}\).
+This is the expected result.
+Because the full Hubbard model in this case was simply the Hubbard dimer, \(G_H(\vec r = 0, \omega)\) should just be \(\left(G_D\right)_{00}\).
 Although this is a trivial example (we matched the Hubbard dimer with another Hubbard dimer), this atleast tells us that this algorithm for calculating the real space local Greens function from the inverse Greens function matrix elements is sensible.
-\par\noindent
+
+\subsection{On the Bethe lattice}
 Another test involves considering the case of infinite number of nearest neighbours $w\to\infty$ (the coordination number, and effectively the dimensionality).
@@
 \end{aligned}\end{equation}
-The site local spectral function can now be calculated:
+In the atomic limit, the singly-occupied state has zero energy:
+\begin{equation}\begin{aligned}
+	E_1(t=0) = \bra{1,0}\left(U \tau_{0 \uparrow}\tau_{0 \downarrow} + U \tau_{1 \uparrow}\tau_{1 \downarrow}\right) \ket{1,0} = 0
+\end{aligned}\end{equation}
+We can write the atomic limit Greens function in terms of this energy and the self energy:
+\begin{equation}\begin{aligned}
+	G_{D,00}^\uparrow(\omega, T \to 0) \bigg\vert_\text{atomic} = \frac{1}{\omega - E_1(t=0) - \Sigma(t=0)} = \frac{1}{\omega - 0 -\frac{U^2}{4\omega}}
+\end{aligned}\end{equation}
+The self energy in the atomic limit can be read off as 
+\begin{equation}\begin{aligned}
+	\label{dimer_selfenergy}
+\Sigma(t=0) = \frac{U^2}{4\omega}
+\end{aligned}\end{equation}
+The site local spectral function can also be calculated from the local Greens function:
 \begin{eqnarray}

### 2021-08-10 notes.tex
typos
removed hyperlinks for sir to compile
performed comparison with trimer, failed spectacularly
updated notes to reflect the full cluster + bath --> RG route, specified all approximations

@@
 %\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
-\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
+\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec,color}
 \usepackage[margin=0.5in,bottom=0.6in]{geometry}
@@
 \section{Introduction}
-This is an attempt to obtain solutions of the Hubbard model (groundstate wavefunction and ground state energy) using the solutions of the simpler single-impurity Anderson model (SIAM).
-The models are defined using the Hamiltonians
-\begin{equation}\begin{aligned}
+This is an attempt to obtain various quantities like Greens functions, self-energies, spectral functions and (if possible) energies and wavefunctions of the Hubbard model, using a cluster-bath approach.
+The cluster-bath system is taken to be a single-impurity Anderson model with a correlated bath.
+The correlation will be brought about in two ways: a self-energy $\Sigma(k,\omega)$ of the bath, and a double occupancy repulsion cost $U_b$.
+The Hubbard and the correlated single-impurity Anderson models are defined using the Hamiltonians
+\begin{align}
 H_\text{hubb} &= -t^H\sum_{\sigma,\left<i,j \right>}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right) + U^H\sum_i \hat n_{i \uparrow} \hat n_{i \downarrow} - \mu^H \sum_{i\sigma}\hat n_{i\sigma}\\
-	H_\text{siam} &= -t^A\sum_{\sigma,\left<i,j \right>\atop{i \neq d \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right) + \epsilon_d^A \sum_\sigma\hat n_{d\sigma} + U^A \hat n_{d \uparrow} \hat n_{d \downarrow} - \mu^A \sum_{i\neq d,\sigma}\hat n_{i\sigma}
-\end{aligned}\end{equation}
-Broadly speaking, the method involves first solving the SIAM using a unitary renormalisation group approach, to get the ground state wavefunction and energy eigenvalue, and then combining these wavefunctions in a symmetrized fashion to get the wavefunction for the Hubbard model lattice.
-It is quite similar to dynamical mean-field theory (DMFT) in essence, but differs in practice.
-The similar part is the involvement of an impurity-solver.
+H_\text{siam} &= \sum_{k\sigma}\left[\epsilon_k + \Sigma(k,\omega)\right]\hat n_{k\sigma} + \epsilon_d^A \sum_\sigma\hat n_{d\sigma} + U^A \hat n_{d \uparrow} \hat n_{d \downarrow} + U_b \sum_{kk^\prime}\hat n_k \hat n_{k^\prime} - \mu^A \sum_{i\neq d,\sigma}\hat n_{i\sigma}
+	\label{hams}
+\end{align}
+Broadly speaking, the method involves first solving the SIAM using a unitary renormalisation group approach, to get the low energy effective theory, and then combining the low energy Hamiltonians in a symmetrized fashion to get the Hamiltonian for the Hubbard model lattice.
+It is reminescent of dynamical mean-field theory (DMFT) - both involve an impurity-solver that solves an auxiliary system.
 The difference, however, lies in the following points:
 \begin{itemize}
-	\item While DMFT primarily works with Greens functions and self-energies, this method involves Hamiltonians and wavefunctions.
-	\item The impurity-solver in DMFT provides an impurity Greens function (which is then equated with the local Greens function of the bath), while the impurity-solver in this method actually provides a wavefunction.
+	\item While DMFT primarily works with Greens functions and self-energies, this method involves Hamiltonians.
+The impurity-solver in DMFT provides an impurity Greens function (which is then equated with the local Greens function of the bath), while the impurity-solver in this method actually provides a low energy Hamiltonian.
 	\item The final step of DMFT is the self-consistency equation, where the impurity and bath-local quantities are set equal.
@@
 The present method, however, brings about the translational invariance in a different way.
-It symmetrizes the wavefunctions and Hamiltonians itself, such that all quantites then derived from the Hamiltonian or wavefunction are then guaranteed to have the symmetry.
+It symmetrizes the Hamiltonians itself, such that all quantites then derived from the Hamiltonian are then guaranteed to have the symmetry.
 \end{itemize}
@@
 A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{12}\).
+Such a construction is shown in fig.~\ref{cluster-bath}.
+\begin{figure}[htpb!]
+	\centering
+	\includegraphics[width=0.8\textwidth]{./cluster-bath.png}
+	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$.
+\textit{Right}: Extraction of the auxiliary (cluster+bath) system from the full lattice.
+The central site on left becomes the impurity site (red) on the right (with an onsite repulsion $\epsilon_d$), while the rest of the $N-1$ sites on the left form a conduction bath (green circles) (with dispersion $\epsilon_k$ and correlation modelled by the self-energy $\Sigma_k(\omega)$) that hybridizes with the impurity through the coupling $V$.}
+	\label{cluster-bath}
+\end{figure}
 
@@
 The present method intends to calculate the quantities in a different fashion.
-We start with a SIAM (possibly with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian.
-At the fixed-point, assuming the couplings are much larger compared to the kinetic energy, we can approximate the Hamiltonian by a zero-mode of the kinetic energy part, which leads to a two-site Anderson molecule Hamiltonian (shown in fig.~\ref{and_mol}).
-Such a model is exactly solvable.
-Armed with such a groundstate, we will then create the wavefunction of the entire Hubbard Hamiltonian by combining them according to a prescription which is guided by the symmetries of the problem.
+We start with a SIAM (with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian.
+The fixed point Hamiltonian will in general involve the impurity site (with renormalised parameters $\epsilon_d^*, U^*$) interacting with a smaller number of momentum states.
+Assuming the impurity-bath couplings are much larger than the dispersion of the bath, we can approximate the conduction bath part by a zero-mode of the kinetic energy part.
+What this means is that all the momentum states will then collapse to a single site (which we call the zero mode site, and represents the origin of the lattice) with a single correlation coupling $U^A_z$.
+Such a model, shown in fig.~\ref{and_mol} is exactly solvable.
+Armed with such a Hamiltonian and its spectrum, we will then create the the entire Hubbard Hamiltonian by combining the zero-mode Hamiltonians according to a prescription which is guided by the symmetries of the problem.
 The impurity electron will be read off as an arbitrary site, \(p\), of the lattice, while the zero-mode site becomes the site that is nearest to it.
-There are also integrals of motion that come out of the URG, they make up the rest of the sites in the lattice.
-We will first demonstrate this explicitly for the Hubbard dimer.
-Then we will show how we can create a full Hubbard Hamiltonian by joining Anderson molecule Hamiltonians, and this should hopefully be a step towards getting a general prescription for generating wavefunctions for the full lattice (not just dimers).
-
+%TODO
+\textbf{We will first demonstrate this explicitly for the Hubbard dimer. Then we will show how we can create a full Hubbard Hamiltonian by joining Anderson molecule Hamiltonians.}
 \begin{figure}[htpb]
@@
 	\includegraphics[width=0.6\textwidth]{./gen_siam.png}
-	\caption{Anderson molecule schematic version. It consists of two sites, impurity(blue) and zero mode(green). The impurity site has onsite repulsion, and their is inter-site hopping.}
+	\caption{Correlated Anderson molecule schematic version. It consists of two sites, impurity(blue) and zero mode(green). The impurity site has onsite repulsion, and their is inter-site hopping.}
 	\label{and_mol}
 \end{figure}
-
-\section{Solution of the Hubbard dimer using the Anderson molecule}
-The Hubbard dimer and Anderson molecules (zero-mode) are defined by the following respective Hamiltonians:
+At this point, we will assume that we have a Hubbard model in mind that has motivated a correlated SIAM as the auxiliary system, and we have performed renormalisation group analysis on this auxiliary system to get down to an effective Hamiltonian.
+We will also assume that the parameters of the auxiliary system have been chosen such that in the effective Hamiltonian, the impurity and zero mode have the same onsite repulsion: $U^A = U^A_z$ (this is required for translational invariance).
+What this all means is that the RG analysis of the bare Hubbard Hamiltonian has led to a Hubbard dimer Hamiltonian.
 \begin{equation}\begin{aligned}
-	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat n_{i \uparrow}\hat n_{i \downarrow} - \mu^H \sum_{\sigma, i=1,2}\hat n_{i\sigma}\\
-	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \epsilon_d^A \sum_{\sigma}\hat n_{d\sigma} + U^A\hat n_{d \uparrow}\hat n_{d \downarrow}
+	H^D(U^D, t^D) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)
 \end{aligned}\end{equation}
-In the first Hamiltonian, the indices \(i=1,2\) refer to the two lattice sites that constitute the dimer.
-In the second Hamiltonian, the subscript \(d\) indicates the impurity site, while the subscript \(z\) indicates the zero-mode site.
-First, we will assume that the Hubbard dimer is at half-filling (\(\frac{1}{2}U^H = \mu^H\)):
-\begin{equation}\begin{aligned}
-	\label{hubb_dimer}
-	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \left(\frac{1}{2}U^H- \mu^H\right) \sum_{\sigma, i=1,2}\hat n_{i\sigma} + \text{constant}\\
-	    &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
-\end{aligned}\end{equation}
-Since the Hubbard Hamiltonian is at half-filling, we will also place the impurity at half-filling by setting \(\epsilon_d^A = -\frac{1}{2}U^A\):
-\begin{equation}\begin{aligned}
-	\label{and_dimer}
-	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \left(\epsilon_d^A + \frac{1}{2}U^A\right) \sum_{\sigma}\hat \tau_{d\sigma} + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow} + \text{constant}\\
-	    &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow}
-\end{aligned}\end{equation}
-The first step is to recreate the Hubbard dimer Hamiltonian eq.~\ref{hubb_dimer} using the Anderson molecule Hamiltonian eq.~\ref{and_dimer}:
-\begin{equation}\begin{aligned}
-	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
-	    &= \frac{1}{2}\left[-t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + t^H\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\right] + \frac{1}{2} 2U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
-	    &= \frac{1}{2}\left[-t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right)\bigg\vert_{z \to 2, d \to 1\atop{t^A \to t^H}} + t^A\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\bigg\vert_{d \to 2,z \to 1\atop{t^A \to t^H}} \right] \\
-	    &+ \frac{1}{2} \left(U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 1\atop{U^A \to 2U^H}} + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 2\atop{U^A \to 2U^H}}\right)\\
-	    &=\frac{1}{2}\left[H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 1, z \to 2\right) + H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 2, z \to 1\right)\right]
-\end{aligned}\end{equation}
-The conclusion we can draw from this is that the Hubbard dimer Hamiltonian can be obtained from the Anderson dimer Hamiltonian in the following fashion:
-\begin{itemize}
-	\item The essential idea is that we have to create a local Hubbard Hamiltonian for each site of the Hubbard lattice by replacing the impurity label \(d\) in the Anderson dimer with the label of the particular site.
-So if there are two sites, we will get two local Hamiltonians obtained by replacing \(d\) with 1 and 2 respectively.
-For each local Hamiltonian, the zero-mode label \(z\) is replaced by the site that is nearest to the one that \(d\) is being replaced by.
-So, if \(d \to 1(2)\), then \(z \to 2(1)\).
-	\item This, however, is not the only change that we must make, in order to get the local Hamiltonian for a particular site.
-Along with \(d\) and \(z\), we must also make the transformations \(t^A \to t^H, U^A \to 2U^H\).
-	\item Finally, once we have the local Hamiltonians for sites 1 and 2, we average them to get the total Hubbard Hamiltonian.
-\end{itemize}
-Note that we expect most of these "rules" to be specific for the dimer, and there will be generalizations to most of them for a general \(N-\)site Hubbard Hamiltonian.
-
-The wavefunctions for the \(N=2\) sector can also be connected through these transformations.
-Since both the Hamiltonians are analytically solvable, we can write down their groundstate wavefunctions \cite{pavarini}:
-\begin{equation}\begin{aligned}
-	\ket{\Psi^H_\text{GS}} &= a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) - a_2(U^H,t^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
-	\ket{\Psi^A_\text{GS}} &= a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) - a_2(\frac{1}{2}U^A,t^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
-	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right), E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right)
-\end{aligned}\end{equation}
-where 
-\begin{equation}\begin{aligned}
-	a_1(U,t) \equiv \frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) - U \right) }}, && a_2(U,t) \equiv \sqrt{\frac{\Delta(U,t) - U}{2\Delta(U,t)}}, &&\Delta(U,t) \equiv \sqrt{U^2 + 16t^2}\\
-\end{aligned}\end{equation}
-$a_1,a_2$ satisfy $a_1(-U,t) = -a_2(U,t)$ and $a_1(U,t)a_2(U,t)= \frac{2t}{\Delta(U,t)}$.
-From the forms of the wavefunctions and eigenenergies, we can immediately write down
-\begin{equation}\begin{aligned}
-	\ket{\Psi^H_\text{GS}} &= \frac{1}{2}\left[\ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 1, z \to 2\right) + \ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 2, z \to 1\right)\right]\\
-	E^H_\text{GS} &= E^A_\text{GS}\left(t^A, U^A \to t^H, 2U^H\right)
-\end{aligned}\end{equation}
-This shows that the rules laid out before work for the Hamiltonians, as well as the wavefunctions and energy eigenvalues of the \(N=2,0,4\) sector.
-These sectors specifically work because it is only in these sectors can we ensure that \(n_d = n_z\), which is required for the Hubbard Hamiltonian because \(n_1 = n_2\).
-In the other sectors (\(N=1,3\)), the impurity site and the zero-mode sites have to be singly-occupied in some part, and since the impurity site incurs a single-occupation cost of \(-\frac{U^H}{2}\) which is not borne by the zero-mode site, there is an intrinsic dissimilarity between the two sites of the Anderson molecule in this regime.
-This dissimilarity does not exist for the Hubbard model, so we cannot hope to connect the two models in this regime.
-
-\section{Creating General \(N-\)site Hubbard Hamiltonian from Hubbard dimers: tiling the lattice with Anderson molecules}
-We will follow the strategy outlined in the previous section.
-For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site.
-Note that a uniform number of nearest neighbours means that there is perfect translational invariance on the lattice, which means there cannot be any edge sites.
-This is achieved by applying periodic boundary conditions on the edges of the lattice.
-A square 2d lattice is thus placed on a torus.
-
-For each site \(i\) out of the \(N\) sites (having nearest neighbours \(\{i_j, j\in\left[1,w\right]\}\)), we will create \(w\) local Hamiltonians \(\{H^H_{i,i_j}, i\in \left[1,N\right], j \in \left[1,w\right]  \}\) out of the Anderson molecule Hamiltonian, by setting the impurity index \(d\) to \(i\) and the zero-mode index \(z\) to \(i_j\).
-We will also need to suitably transform the Hamiltonian parameters \(U^A, t^A\), but we will figure those out as we go along.
-All \(N\) sites will then produce \(Nw\) local Hamiltonians in total, and the general Hubbard Hamiltonian should be the average of these local Hamiltonians.
-
-The local Hamiltonians look like
-\begin{equation}\begin{aligned}
-	H^A_{i,i_j} = -t^A\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i_j\sigma} + \text{h.c.}\right) + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
-\end{aligned}\end{equation}
-We havent transformed the Anderson parameters \(U^A, t^A\) to the Hubbard parameters yet. The sum of all local Hamiltonians for a particular site \(i\) then gives the total Hamiltonian for that site:
-\begin{equation}\begin{aligned}
-	H^A_{i} = \sum_{j\in\left[1,w\right]}H^H_{i,i_j} = \sum_{\sigma\atop{j \in \text{N.N.
-of }i}}-t^A\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
-\end{aligned}\end{equation}
-If we now sum over all the lattice sites and take the average of all the Hamiltonians (\(Nw\) in number), we get
-\begin{equation}\begin{aligned}
-	H^H = \frac{1}{Nw}\sum_{i=1}^N H^H_{i} = -\frac{2}{Nw}t^A\sum_{\sigma\atop{\left<ij \right>}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{N}U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
-\end{aligned}\end{equation}
-The factor of 2 in front of \(t^A\) appears because each nearest neighbour pair \(\left<i,j \right>\) is counted twice, once when \(d\to i\) and again when \(d \to j\).
-Comparing with the actual Hubbard model, we can guess the following transformations for the model paramters:
-\begin{equation}\begin{aligned}
-	\frac{2}{Nw}t^A \to t^H, && \frac{1}{N}U^A \to U^H
-\end{aligned}\end{equation}
-For the dimer versions, we had \(N=2, w=1\) and if we substitute these values into the transformations we recover the transformations we had discovered that worked for the dimer.
-The Hubbard Hamiltonian can thus be obtained from the Anderson molecule using the following equation:
-\begin{equation}\begin{aligned}
-	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
-\end{aligned}\end{equation}
-The combination that is being summed over,
-\begin{equation}\begin{aligned}
-	H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)
-\end{aligned}\end{equation}
-is actually a Hubbard dimer Hamiltonian.
-\begin{equation}\begin{aligned}
-	&H^D(U^D, t^D) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)\\
-	&H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right) = -2t^A\sum_\sigma\left( c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.} \right) + U^A\left( \tau_{i \uparrow}\tau_{i \downarrow} + \tau_{i \uparrow}\tau_{i \downarrow}\right)\\
-	\implies &H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right) = H^D(0 \to i, 1 \to j, t^D \to 2t^A, U^D \to U^A)
-\end{aligned}\end{equation}
-The tiling can thus be actually done in terms of Hubbard dimers (shown in fig.~\ref{hubb-dim}):
-\begin{equation}\begin{aligned}
-	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^D\left(1 \to i, 2 \to j\right)\right]_{t^D \to Nwt^H \atop{U^A \to N U^H}}
-\end{aligned}\end{equation}
+This Hubbard dimer is shown in fig.~\ref{hubb-dim}.
 \begin{figure}[htpb!]
@@
 \end{figure}
-Since the total number of nearest neighbour pairs is $\frac{Nw}{2}$, we want the prefactor to be the same. We will scale the internal Hubbard dimer by half, pulling out a two:
+The next step is to combine these Hubbard dimers into a full Hubbard model, $H_\text{symm}$. Along the way, we have made two approximations:
+\begin{itemize}
+	\item We have replaced the full Hubbard model by an auxiliary system described by the SIAM Hamiltonian in eq.~\ref{hams}.
+The accuracy of this assumption is determined by the choice of the SIAM parameters, particular the self-energy and repulsion of the bath.
+If it is exact, then the equation
+\begin{equation}\begin{aligned}
+	\label{app1}
+	H^H = H^A
+\end{aligned}\end{equation}
+holds.
+	\item We then perform a unitary RG on $H^A$.
+This leads to a fixed-point Hamiltonian $U_A H^A U_A^\dagger$.
+At this point, we extract a zero mode of this Hamiltonian to obtain the Hubbard dimer Hamiltonian: $H^D = \left(U_A H^A U_A^\dagger\right)_z$, and this constitutes the second approximations we make.
+We tile this Hubbard dimer Hamiltonian to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $H_\text{symm}$.
+If we assume that the tiling perfectly rectifies the approximation made while taking the zero mode, then we can write
+\begin{equation}\begin{aligned}
+	\label{app2}
+	H_\text{symm} = U_A H^A U_A^\dagger
+\end{aligned}\end{equation}
+\end{itemize}
+Combining the two eqs.~\ref{app1},\ref{app2}, we can say that
+\begin{equation}\begin{aligned}
+	H_\text{symm} = U_A H^H U_A^\dagger
+\end{aligned}\end{equation}
+which would mean that the final Hamiltonian is unitarily connected to the bare Hubbard model, but is actually made of Hubbard dimers and is hence more amenable to calculations.
+This of course depends on how good the approximations are and strictly speaking need to be verified.
+
+%\section{Solution of the Hubbard dimer using the Anderson molecule}
+%The Hubbard dimer and Anderson molecules (zero-mode) are defined by the following respective Hamiltonians:
+%\begin{equation}\begin{aligned}
+%	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat n_{i \uparrow}\hat n_{i \downarrow} - \mu^H \sum_{\sigma, i=1,2}\hat n_{i\sigma}\\
+%	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \epsilon_d^A \sum_{\sigma}\hat n_{d\sigma} + U^A\hat n_{d \uparrow}\hat n_{d \downarrow}
+%\end{aligned}\end{equation}
+%In the first Hamiltonian, the indices \(i=1,2\) refer to the two lattice sites that constitute the dimer.
+In the second Hamiltonian, the subscript \(d\) indicates the impurity site, while the subscript \(z\) indicates the zero-mode site.
+First, we will assume that the Hubbard dimer is at half-filling (\(\frac{1}{2}U^H = \mu^H\)):
+%\begin{equation}\begin{aligned}
+%	\label{hubb_dimer}
+%	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \left(\frac{1}{2}U^H- \mu^H\right) \sum_{\sigma, i=1,2}\hat n_{i\sigma} + \text{constant}\\
+%	    &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
+%\end{aligned}\end{equation}
+%Since the Hubbard Hamiltonian is at half-filling, we will also place the impurity at half-filling by setting \(\epsilon_d^A = -\frac{1}{2}U^A\):
+%\begin{equation}\begin{aligned}
+%	\label{and_dimer}
+%	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \left(\epsilon_d^A + \frac{1}{2}U^A\right) \sum_{\sigma}\hat \tau_{d\sigma} + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow} + \text{constant}\\
+%	    &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow}
+%\end{aligned}\end{equation}
+%The first step is to recreate the Hubbard dimer Hamiltonian eq.~\ref{hubb_dimer} using the Anderson molecule Hamiltonian eq.~\ref{and_dimer}:
+%\begin{equation}\begin{aligned}
+%	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
+%	    &= \frac{1}{2}\left[-t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + t^H\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\right] + \frac{1}{2} 2U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
+%	    &= \frac{1}{2}\left[-t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right)\bigg\vert_{z \to 2, d \to 1\atop{t^A \to t^H}} + t^A\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\bigg\vert_{d \to 2,z \to 1\atop{t^A \to t^H}} \right] \\
+%	    &+ \frac{1}{2} \left(U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 1\atop{U^A \to 2U^H}} + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 2\atop{U^A \to 2U^H}}\right)\\
+%	    &=\frac{1}{2}\left[H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 1, z \to 2\right) + H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 2, z \to 1\right)\right]
+%\end{aligned}\end{equation}
+%The conclusion we can draw from this is that the Hubbard dimer Hamiltonian can be obtained from the Anderson dimer Hamiltonian in the following fashion:
+%\begin{itemize}
+%	\item The essential idea is that we have to create a local Hubbard Hamiltonian for each site of the Hubbard lattice by replacing the impurity label \(d\) in the Anderson dimer with the label of the particular site.
+So if there are two sites, we will get two local Hamiltonians obtained by replacing \(d\) with 1 and 2 respectively.
+For each local Hamiltonian, the zero-mode label \(z\) is replaced by the site that is nearest to the one that \(d\) is being replaced by.
+So, if \(d \to 1(2)\), then \(z \to 2(1)\).
+%	\item This, however, is not the only change that we must make, in order to get the local Hamiltonian for a particular site.
+Along with \(d\) and \(z\), we must also make the transformations \(t^A \to t^H, U^A \to 2U^H\).
+%	\item Finally, once we have the local Hamiltonians for sites 1 and 2, we average them to get the total Hubbard Hamiltonian.
+%\end{itemize}
+%Note that we expect most of these "rules" to be specific for the dimer, and there will be generalizations to most of them for a general \(N-\)site Hubbard Hamiltonian.
+%
+%
+%The wavefunctions for the \(N=2\) sector can also be connected through these transformations.
+Since both the Hamiltonians are analytically solvable, we can write down their groundstate wavefunctions \cite{pavarini}:
+%\begin{equation}\begin{aligned}
+%	\ket{\Psi^H_\text{GS}} &= a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) - a_2(U^H,t^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
+%	\ket{\Psi^A_\text{GS}} &= a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) - a_2(\frac{1}{2}U^A,t^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
+%	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right), E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right)
+%\end{aligned}\end{equation}
+%where 
+%\begin{equation}\begin{aligned}
+%	a_1(U,t) \equiv \frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) - U \right) }}, && a_2(U,t) \equiv \sqrt{\frac{\Delta(U,t) - U}{2\Delta(U,t)}}, &&\Delta(U,t) \equiv \sqrt{U^2 + 16t^2}\\
+%\end{aligned}\end{equation}
+%$a_1,a_2$ satisfy $a_1(-U,t) = -a_2(U,t)$ and $a_1(U,t)a_2(U,t)= \frac{2t}{\Delta(U,t)}$.
+%From the forms of the wavefunctions and eigenenergies, we can immediately write down
+%\begin{equation}\begin{aligned}
+%	\ket{\Psi^H_\text{GS}} &= \frac{1}{2}\left[\ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 1, z \to 2\right) + \ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 2, z \to 1\right)\right]\\
+%	E^H_\text{GS} &= E^A_\text{GS}\left(t^A, U^A \to t^H, 2U^H\right)
+%\end{aligned}\end{equation}
+%This shows that the rules laid out before work for the Hamiltonians, as well as the wavefunctions and energy eigenvalues of the \(N=2,0,4\) sector.
+These sectors specifically work because it is only in these sectors can we ensure that \(n_d = n_z\), which is required for the Hubbard Hamiltonian because \(n_1 = n_2\).
+In the other sectors (\(N=1,3\)), the impurity site and the zero-mode sites have to be singly-occupied in some part, and since the impurity site incurs a single-occupation cost of \(-\frac{U^H}{2}\) which is not borne by the zero-mode site, there is an intrinsic dissimilarity between the two sites of the Anderson molecule in this regime.
+This dissimilarity does not exist for the Hubbard model, so we cannot hope to connect the two models in this regime.
+
+%\section{Creating General \(N-\)site Hubbard Hamiltonian from Hubbard dimers: tiling the lattice with Anderson molecules}
+\section{Creating General \(N-\)site Hubbard Hamiltonian from Hubbard dimers}
+We will follow the strategy outlined in the previous section.
+For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site.
+Note that a uniform number of nearest neighbours means that there is perfect translational invariance on the lattice, which means there cannot be any edge sites.
+This is achieved by applying periodic boundary conditions on the edges of the lattice.
+A square 2d lattice is thus placed on a torus.
+\\\\
+For each site \(i\) out of the \(N\) sites (having nearest neighbours \(\{i_j, j\in\left[1,w\right]\}\)), we will create \(w\) local Hamiltonians \(\{H^H_{i,i_j}, i\in \left[1,N\right], j \in \left[1,w\right]  \}\) out of the Hubbard dimer Hamiltonians, by setting the impurity index \(d\) to \(i\) and the zero-mode index \(z\) to \(i_j\).
+We will also need to suitably transform the Hamiltonian parameters \(U^A, t^A\), but we will figure those out as we go along.
+All \(N\) sites will then produce \(Nw\) local Hamiltonians in total, and the general Hubbard Hamiltonian should be the average of these local Hamiltonians.
+\\\\
+The local Hamiltonians look like
+\begin{equation}\begin{aligned}
+	H^D_{i,i_j} = -t^D\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i_j\sigma} + \text{h.c.}\right) + U^D\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + U^D\hat \tau_{i_j \uparrow}\hat \tau_{i_j \downarrow}
+\end{aligned}\end{equation}
+We havent transformed the dimer parameters \(U^D, t^D\) to the Hubbard parameters yet. The sum of all local Hamiltonians for a particular site \(i\) then gives the total Hamiltonian for that site:
+\begin{equation}\begin{aligned}
+	H^D_{i} = \sum_{j\in\left[1,w\right]}H^D_{i,i_j} = \sum_{\sigma\atop{j \in \text{N.N.
+of }i}}-t^D\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^D\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + U^D\sum_{j \in \text{N.N.
+of }i}\hat \tau_{j \uparrow}\hat \tau_{j \downarrow}
+\end{aligned}\end{equation}
+If we now sum over all the lattice sites and take the average of all the Hamiltonians (\(Nw\) in number), we get
+\begin{equation}\begin{aligned}
+	H_\text{symm} &= \frac{1}{Nw}\sum_{i=1}^N H^D_{i} \\
+		      &= \frac{1}{Nw}\left[\sum_{\sigma i=1}^N\sum_{j \in \text{NN of }j}-t^D\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^D\sum_{i=1}^N \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + U^D\sum_{i=1}^N\sum_{j \in \text{N.N.
+of }i}\hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right] \\
+		      &= \frac{1}{Nw}\left[-t^D 2\sum_{\sigma \left<ij\right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + 2 U^D\sum_{\left<ij\right>} \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + 2 U^D\sum_{\left<ij\right>} \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right]\\
+		      &= \frac{2}{Nw}\sum_{\left<ij\right>}\left[-t^D \sum_\sigma \left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + U^D\left(\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right)\right]\\
+		      &= \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
+\end{aligned}\end{equation}
+There we used the identity
+\begin{equation}\begin{aligned}
+	\sum_{i=1}^N\sum_{j \in \text{NN of }j} = 2\sum_{\left<ij\right>}
+\end{aligned}\end{equation}
+The sum $\left<ij\right>$ is over all nearest-neighbour pairs. So $H_\text{symm}$ can thus be written as
 \begin{equation}\begin{aligned}
 	\label{H_tiled}
-	H^H\left(t^H, U^H\right)  = \frac{2}{Nw}\sum_{\left<i,j\right>}\left[H^D\left(1 \to i, 2 \to j\right)\right]_{t^D \to \frac{1}{2}Nwt^H \atop{U^D \to \frac{1}{2}N U^H}}
+	H_\text{symm} = - \frac{2t^D}{Nw}\sum_{\sigma \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
 \end{aligned}\end{equation}
-From this representation of the full Hubbard model, it is clear that symmetrizing the Anderson molecules by translating them throughout the lattice has restored translational invariance, and generated correlations on all sites (as compared to just on the impurity site).
-This also takes care of the problem that the spectrum of the Anderson molecule and Hubbard dimer are different for the $N=1$ or $N=3$ sectors: By translating the Anderson molecule suitably, we have recovered the correct spectrum in all sectors.
+The conclusion is that on tiling the Hubbard dimer Hamiltonians into all the nearest neighbour pairs, we end up with a new Hubbard model Hamiltonian with "renormalised parameters"
+\begin{equation}\begin{aligned}
+	\tilde t = \frac{2t^D}{Nw}, \tilde U = \frac{2U^D}{N}
+\end{aligned}\end{equation}
+The claim made in a previous section was that this Hamiltonian is very close to the unitarily transformed Hubbard Hamiltonian:
+\begin{equation}\begin{aligned}
+	\frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D) \color{red}{\simeq U_S H^H U_S^\dagger}
+\end{aligned}\end{equation}
+It is clear that symmetrizing the Anderson molecules by translating them throughout the lattice has restored translational invariance, and generated correlations on all sites (as compared to just on the impurity site).
+%This also takes care of the problem that the spectrum of the Anderson molecule and Hubbard dimer are different for the $N=1$ or $N=3$ sectors: By translating the Anderson molecule suitably, we have recovered the correct spectrum in all sectors.
 
@@
 \subsection{Expressing matrix elements of the inverse single particle Greens function in terms of Hubbard dimer counterparts}
+If the groundstate wavefunction of $H^H$ is $\ket{0}$, then the groundstate wavefunction of $H_\text{symm}$ is $\ket{\tilde 0} = U_S\ket{0}$.
+The advantage of $H_\text{symm}$ being unitarily connected to $H^H$ is that they will have the same single-particle Greens functions.
+\begin{equation}\begin{aligned}
+	\left(G_H\right)_{ij}(t) \equiv -i\theta(t)\bra{0}\left\{c_i,c^\dagger_j \right\}\ket{0} &= -i\theta(t)\bra{0}U_S^\dagger\left\{ U_S c_i U_S^\dagger U_S c^\dagger_j U_S^\dagger + U_S c^\dagger_j U_S^\dagger U_S c_i U_S^\dagger\right\}U_S\ket{0}\\
+												 &=-i\theta(t)\bra{\tilde 0}\left\{\tilde c_i \tilde c^\dagger_j + \tilde c^\dagger_j \tilde c_i \right\}\ket{\tilde 0}
+\end{aligned}\end{equation}
+This says that the Greens function of the bare Hubbard model $H^H$ for excitations $c_i,c^\dagger_j$ on top of its ground state $\ket{0}$ is exactly equal to the Greens function of the renormalised Hamiltonian $H_\text{symm}$ for renormalised excitations $\tilde c_i \equiv U_S c_i U_S^\dagger, \tilde c_j^\dagger \equiv U_S c^\dagger_j U_S^\dagger$ on top of its renormalised ground state $\ket{\tilde 0} = U_S \ket{0}$.
 In terms of the Greens function, equation \ref{H_tiled} becomes
@@
 A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{1}{\pi} \textrm{Im}\left[ (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right]\\
-A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = -\frac{1}{\sqrt N\pi} \textrm{Im}\left[\sum_{\vec{k}} (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right] = -\frac{1}{\sqrt N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
+A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = -\frac{1}{N\pi} \textrm{Im}\left[\sum_{\vec{k}} (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right] = -\frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
-for the first inner product, and
+for the second inner product, and
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-for the second. The Greens function is therefore
+for the first. The Greens function is therefore
 \begin{equation}\begin{aligned}
@@
 A(0\uparrow, \omega) &=& - \frac{1}{\pi}\text{Im }G_{D,00}^\uparrow(\omega)\nonumber\\
-			     &=& \left( \frac{1}{2} + \frac{2t}{\Delta} \right)\left[\delta(\omega - \frac{1}{2}\Delta - t) + \delta(\omega + \frac{1}{2}\Delta + t)\right]\nonumber\\ 
-			     &&+ \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \left[\delta(\omega - \frac{1}{2}\Delta + t) + \delta(\omega + \frac{1}{2}\Delta - t)\right]\\ 
+			     &=& \left( \frac{1}{4} - \frac{t}{\Delta} \right)\left[\delta(\omega - \frac{1}{2}\Delta - t) + \delta(\omega + \frac{1}{2}\Delta + t)\right]\nonumber\\ 
+			     &&+ \left( \frac{1}{4} + \frac{t}{\Delta} \right) \left[\delta(\omega - \frac{1}{2}\Delta + t) + \delta(\omega + \frac{1}{2}\Delta - t)\right]\\ 
 			     &=& A(0\downarrow, \omega)~.\nonumber

### 2021-08-11 notes.tex
reinserted molecule to dimer section, rewrote the Greens functions part in terms of unitaries, noted the remaining doubts

@@
 \end{align}
+\\\\
+{\textbf{\color{red}{[CHECK]That $U_b$ does not actually give a zero mode, rather it gives an $N^2$ type piece.}}
+\\\\
 Broadly speaking, the method involves first solving the SIAM using a unitary renormalisation group approach, to get the low energy effective theory, and then combining the low energy Hamiltonians in a symmetrized fashion to get the Hamiltonian for the Hubbard model lattice.
@@
 \end{figure}
-The next step is to combine these Hubbard dimers into a full Hubbard model, $H_\text{symm}$. Along the way, we have made two approximations:
+The next step is to combine these Hubbard dimers into a full Hubbard model, $\tilde H$. Along the way, we have made two approximations:
 \begin{itemize}
@@
 At this point, we extract a zero mode of this Hamiltonian to obtain the Hubbard dimer Hamiltonian: $H^D = \left(U_A H^A U_A^\dagger\right)_z$, and this constitutes the second approximations we make.
-We tile this Hubbard dimer Hamiltonian to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $H_\text{symm}$.
+We tile this Hubbard dimer Hamiltonian to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H$.
 If we assume that the tiling perfectly rectifies the approximation made while taking the zero mode, then we can write
@@
 	\label{app2}
-	H_\text{symm} = U_A H^A U_A^\dagger
+	\tilde H = U_A H^A U_A^\dagger
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	H_\text{symm} = U_A H^H U_A^\dagger
+	\tilde H = U_A H^H U_A^\dagger
 \end{aligned}\end{equation}
@@
 
-%\section{Solution of the Hubbard dimer using the Anderson molecule}
-%The Hubbard dimer and Anderson molecules (zero-mode) are defined by the following respective Hamiltonians:
-%\begin{equation}\begin{aligned}
-%	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat n_{i \uparrow}\hat n_{i \downarrow} - \mu^H \sum_{\sigma, i=1,2}\hat n_{i\sigma}\\
-%	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \epsilon_d^A \sum_{\sigma}\hat n_{d\sigma} + U^A\hat n_{d \uparrow}\hat n_{d \downarrow}
-%\end{aligned}\end{equation}
-%In the first Hamiltonian, the indices \(i=1,2\) refer to the two lattice sites that constitute the dimer.
+\section{Solution of the Hubbard dimer using the Anderson molecule}
+This section tries to see how far we can we can go if we just work with the Anderson molecule as the smallest unit of tiling.
+We will attempt to reproduce the entire spectrum of a Hubbard dimer by creating a new Hamiltonian made up purely of Anderson molecules.
+This will guide us in deciding how to generalize the "tiling method" for a general $N-$site Hubbard model, as well as give indications as to whether we need a different smallest unit for tiling.
+\\\\
+The Hubbard dimer and Anderson molecules (zero-mode) are defined by the following respective Hamiltonians:
+\begin{equation}\begin{aligned}
+	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat n_{i \uparrow}\hat n_{i \downarrow} - \mu^H \sum_{\sigma, i=1,2}\hat n_{i\sigma}\\
+	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \epsilon_d^A \sum_{\sigma}\hat n_{d\sigma} + U^A\hat n_{d \uparrow}\hat n_{d \downarrow}
+\end{aligned}\end{equation}
+In the first Hamiltonian, the indices \(i=1,2\) refer to the two lattice sites that constitute the dimer.
 In the second Hamiltonian, the subscript \(d\) indicates the impurity site, while the subscript \(z\) indicates the zero-mode site.
 First, we will assume that the Hubbard dimer is at half-filling (\(\frac{1}{2}U^H = \mu^H\)):
-%\begin{equation}\begin{aligned}
-%	\label{hubb_dimer}
-%	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \left(\frac{1}{2}U^H- \mu^H\right) \sum_{\sigma, i=1,2}\hat n_{i\sigma} + \text{constant}\\
-%	    &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
-%\end{aligned}\end{equation}
-%Since the Hubbard Hamiltonian is at half-filling, we will also place the impurity at half-filling by setting \(\epsilon_d^A = -\frac{1}{2}U^A\):
-%\begin{equation}\begin{aligned}
-%	\label{and_dimer}
-%	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \left(\epsilon_d^A + \frac{1}{2}U^A\right) \sum_{\sigma}\hat \tau_{d\sigma} + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow} + \text{constant}\\
-%	    &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow}
-%\end{aligned}\end{equation}
-%The first step is to recreate the Hubbard dimer Hamiltonian eq.~\ref{hubb_dimer} using the Anderson molecule Hamiltonian eq.~\ref{and_dimer}:
-%\begin{equation}\begin{aligned}
-%	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
-%	    &= \frac{1}{2}\left[-t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + t^H\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\right] + \frac{1}{2} 2U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
-%	    &= \frac{1}{2}\left[-t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right)\bigg\vert_{z \to 2, d \to 1\atop{t^A \to t^H}} + t^A\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\bigg\vert_{d \to 2,z \to 1\atop{t^A \to t^H}} \right] \\
-%	    &+ \frac{1}{2} \left(U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 1\atop{U^A \to 2U^H}} + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 2\atop{U^A \to 2U^H}}\right)\\
-%	    &=\frac{1}{2}\left[H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 1, z \to 2\right) + H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 2, z \to 1\right)\right]
-%\end{aligned}\end{equation}
-%The conclusion we can draw from this is that the Hubbard dimer Hamiltonian can be obtained from the Anderson dimer Hamiltonian in the following fashion:
-%\begin{itemize}
-%	\item The essential idea is that we have to create a local Hubbard Hamiltonian for each site of the Hubbard lattice by replacing the impurity label \(d\) in the Anderson dimer with the label of the particular site.
+\begin{equation}\begin{aligned}
+	\label{hubb_dimer}
+	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \left(\frac{1}{2}U^H- \mu^H\right) \sum_{\sigma, i=1,2}\hat n_{i\sigma} + \text{constant}\\
+	    &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
+\end{aligned}\end{equation}
+Since the Hubbard Hamiltonian is at half-filling, we will also place the impurity at half-filling by setting \(\epsilon_d^A = -\frac{1}{2}U^A\):
+\begin{equation}\begin{aligned}
+	\label{and_dimer}
+	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \left(\epsilon_d^A + \frac{1}{2}U^A\right) \sum_{\sigma}\hat \tau_{d\sigma} + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow} + \text{constant}\\
+	    &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow}
+\end{aligned}\end{equation}
+The first step is to recreate the Hubbard dimer Hamiltonian eq.~\ref{hubb_dimer} using the Anderson molecule Hamiltonian eq.~\ref{and_dimer}:
+\begin{equation}\begin{aligned}
+	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
+	    &= \frac{1}{2}\left[-t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + t^H\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\right] + \frac{1}{2} 2U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
+	    &= \frac{1}{2}\left[-t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right)\bigg\vert_{z \to 2, d \to 1\atop{t^A \to t^H}} + t^A\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\bigg\vert_{d \to 2,z \to 1\atop{t^A \to t^H}} \right] \\
+	    &+ \frac{1}{2} \left(U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 1\atop{U^A \to 2U^H}} + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 2\atop{U^A \to 2U^H}}\right)\\
+	    &=\frac{1}{2}\left[H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 1, z \to 2\right) + H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 2, z \to 1\right)\right]
+\end{aligned}\end{equation}
+The conclusion we can draw from this is that the Hubbard dimer Hamiltonian can be obtained from the Anderson dimer Hamiltonian in the following fashion:
+\begin{itemize}
+	\item The essential idea is that we have to create a local Hubbard Hamiltonian for each site of the Hubbard lattice by replacing the impurity label \(d\) in the Anderson dimer with the label of the particular site.
 So if there are two sites, we will get two local Hamiltonians obtained by replacing \(d\) with 1 and 2 respectively.
@@
 So, if \(d \to 1(2)\), then \(z \to 2(1)\).
-%	\item This, however, is not the only change that we must make, in order to get the local Hamiltonian for a particular site.
+	\item This, however, is not the only change that we must make, in order to get the local Hamiltonian for a particular site.
 Along with \(d\) and \(z\), we must also make the transformations \(t^A \to t^H, U^A \to 2U^H\).
-%	\item Finally, once we have the local Hamiltonians for sites 1 and 2, we average them to get the total Hubbard Hamiltonian.
-%\end{itemize}
-%Note that we expect most of these "rules" to be specific for the dimer, and there will be generalizations to most of them for a general \(N-\)site Hubbard Hamiltonian.
-%
-%
-%The wavefunctions for the \(N=2\) sector can also be connected through these transformations.
+	\item Finally, once we have the local Hamiltonians for sites 1 and 2, we average them to get the total Hubbard Hamiltonian.
+\end{itemize}
+Note that we expect most of these "rules" to be specific for the dimer, and there will be generalizations to most of them for a general \(N-\)site Hubbard Hamiltonian.
+
+The wavefunctions for the \(N=2\) sector can also be connected through these transformations.
 Since both the Hamiltonians are analytically solvable, we can write down their groundstate wavefunctions \cite{pavarini}:
-%\begin{equation}\begin{aligned}
-%	\ket{\Psi^H_\text{GS}} &= a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) - a_2(U^H,t^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
-%	\ket{\Psi^A_\text{GS}} &= a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) - a_2(\frac{1}{2}U^A,t^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
-%	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right), E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right)
-%\end{aligned}\end{equation}
-%where 
-%\begin{equation}\begin{aligned}
-%	a_1(U,t) \equiv \frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) - U \right) }}, && a_2(U,t) \equiv \sqrt{\frac{\Delta(U,t) - U}{2\Delta(U,t)}}, &&\Delta(U,t) \equiv \sqrt{U^2 + 16t^2}\\
-%\end{aligned}\end{equation}
-%$a_1,a_2$ satisfy $a_1(-U,t) = -a_2(U,t)$ and $a_1(U,t)a_2(U,t)= \frac{2t}{\Delta(U,t)}$.
-%From the forms of the wavefunctions and eigenenergies, we can immediately write down
-%\begin{equation}\begin{aligned}
-%	\ket{\Psi^H_\text{GS}} &= \frac{1}{2}\left[\ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 1, z \to 2\right) + \ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 2, z \to 1\right)\right]\\
-%	E^H_\text{GS} &= E^A_\text{GS}\left(t^A, U^A \to t^H, 2U^H\right)
-%\end{aligned}\end{equation}
-%This shows that the rules laid out before work for the Hamiltonians, as well as the wavefunctions and energy eigenvalues of the \(N=2,0,4\) sector.
+\begin{equation}\begin{aligned}
+	\ket{\Psi^H_\text{GS}} &= a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) - a_2(U^H,t^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
+	\ket{\Psi^A_\text{GS}} &= a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) - a_2(\frac{1}{2}U^A,t^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
+	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right), E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right)
+\end{aligned}\end{equation}
+where 
+\begin{equation}\begin{aligned}
+	a_1(U,t) \equiv \frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) - U \right) }}, && a_2(U,t) \equiv \sqrt{\frac{\Delta(U,t) - U}{2\Delta(U,t)}}, &&\Delta(U,t) \equiv \sqrt{U^2 + 16t^2}\\
+\end{aligned}\end{equation}
+$a_1,a_2$ satisfy $a_1(-U,t) = -a_2(U,t)$ and $a_1(U,t)a_2(U,t)= \frac{2t}{\Delta(U,t)}$.
+From the forms of the wavefunctions and eigenenergies, we can immediately write down
+\begin{equation}\begin{aligned}
+	\ket{\Psi^H_\text{GS}} &= \frac{1}{2}\left[\ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 1, z \to 2\right) + \ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 2, z \to 1\right)\right]\\
+	E^H_\text{GS} &= E^A_\text{GS}\left(t^A, U^A \to t^H, 2U^H\right)
+\end{aligned}\end{equation}
+This shows that the rules laid out before work for the Hamiltonians, as well as the wavefunctions and energy eigenvalues of the \(N=2,0,4\) sector.
 These sectors specifically work because it is only in these sectors can we ensure that \(n_d = n_z\), which is required for the Hubbard Hamiltonian because \(n_1 = n_2\).
@@
 This dissimilarity does not exist for the Hubbard model, so we cannot hope to connect the two models in this regime.
+Going forward, we will switch to using Hubbard dimers as the smallest tiling unit for a general Hubbard model.
 
@@
 \begin{equation}\begin{aligned}
-	H_\text{symm} &= \frac{1}{Nw}\sum_{i=1}^N H^D_{i} \\
+	\tilde H &= \frac{1}{Nw}\sum_{i=1}^N H^D_{i} \\
 		      &= \frac{1}{Nw}\left[\sum_{\sigma i=1}^N\sum_{j \in \text{NN of }j}-t^D\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^D\sum_{i=1}^N \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + U^D\sum_{i=1}^N\sum_{j \in \text{N.N.
@@
 \end{aligned}\end{equation}
-The sum $\left<ij\right>$ is over all nearest-neighbour pairs. So $H_\text{symm}$ can thus be written as
+The sum $\left<ij\right>$ is over all nearest-neighbour pairs. So $\tilde H$ can thus be written as
 \begin{equation}\begin{aligned}
 	\label{H_tiled}
-	H_\text{symm} = - \frac{2t^D}{Nw}\sum_{\sigma \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
+	\tilde H = - \frac{2t^D}{Nw}\sum_{\sigma \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
+It is clear that symmetrizing the Anderson molecules by translating them throughout the lattice has restored translational invariance, and generated correlations on all sites (as compared to just on the impurity site).
+%This also takes care of the problem that the spectrum of the Anderson molecule and Hubbard dimer are different for the $N=1$ or $N=3$ sectors: By translating the Anderson molecule suitably, we have recovered the correct spectrum in all sectors.
+\\\\
 The claim made in a previous section was that this Hamiltonian is very close to the unitarily transformed Hubbard Hamiltonian:
 \begin{equation}\begin{aligned}
-	\frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D) \color{red}{\simeq U_S H^H U_S^\dagger}
+	\frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D) \simeq  \mathcal{U}_A H^H  \mathcal{U}_A^\dagger
 \end{aligned}\end{equation}
-It is clear that symmetrizing the Anderson molecules by translating them throughout the lattice has restored translational invariance, and generated correlations on all sites (as compared to just on the impurity site).
-%This also takes care of the problem that the spectrum of the Anderson molecule and Hubbard dimer are different for the $N=1$ or $N=3$ sectors: By translating the Anderson molecule suitably, we have recovered the correct spectrum in all sectors.
+$\mathcal{U}_A$ is the total unitary transformation that completes the URG starting from the bare cluster+bath Anderson model up to the fixed-point Hamiltonian.
 
@@
 \subsection{Expressing matrix elements of the inverse single particle Greens function in terms of Hubbard dimer counterparts}
-If the groundstate wavefunction of $H^H$ is $\ket{0}$, then the groundstate wavefunction of $H_\text{symm}$ is $\ket{\tilde 0} = U_S\ket{0}$.
-The advantage of $H_\text{symm}$ being unitarily connected to $H^H$ is that they will have the same single-particle Greens functions.
+If the groundstate wavefunction of $H^H$ is $\ket{0}$, then the groundstate wavefunction of $\tilde H$ is $\ket{\tilde 0} =  \mathcal{U}_A\ket{0}$.
+The advantage of $\tilde H$ being unitarily connected to $H^H$ is that they will have the same single-particle Greens functions.
 \begin{equation}\begin{aligned}
-	\left(G_H\right)_{ij}(t) \equiv -i\theta(t)\bra{0}\left\{c_i,c^\dagger_j \right\}\ket{0} &= -i\theta(t)\bra{0}U_S^\dagger\left\{ U_S c_i U_S^\dagger U_S c^\dagger_j U_S^\dagger + U_S c^\dagger_j U_S^\dagger U_S c_i U_S^\dagger\right\}U_S\ket{0}\\
-												 &=-i\theta(t)\bra{\tilde 0}\left\{\tilde c_i \tilde c^\dagger_j + \tilde c^\dagger_j \tilde c_i \right\}\ket{\tilde 0}
+	\left(G_H\right)^\sigma_{ij}(t) \equiv -i\theta(t)\bra{0}\left\{c_{i\sigma},c^\dagger_{j\sigma} \right\}\ket{0} &= -i\theta(t)\bra{0} \mathcal{U}_A^\dagger\left\{  \mathcal{U}_A c_{i\sigma}  \mathcal{U}_A^\dagger  \mathcal{U}_A c^\dagger_{j\sigma}  \mathcal{U}_A^\dagger +  \mathcal{U}_A c^\dagger_{j\sigma}  \mathcal{U}_A^\dagger  \mathcal{U}_A c_{i\sigma}  \mathcal{U}_A^\dagger\right\} \mathcal{U}_A\ket{0}\\
+															&=-i\theta(t)\bra{\tilde 0}\left\{\tilde c_{i\sigma} \tilde c^\dagger_{j\sigma} + \tilde c^\dagger_{j\sigma} \tilde c_{i\sigma} \right\}\ket{\tilde 0}\\
+															&= \left(\tilde G\right)_{\tilde {i\sigma} \tilde {j\sigma}}(t)
 \end{aligned}\end{equation}
-This says that the Greens function of the bare Hubbard model $H^H$ for excitations $c_i,c^\dagger_j$ on top of its ground state $\ket{0}$ is exactly equal to the Greens function of the renormalised Hamiltonian $H_\text{symm}$ for renormalised excitations $\tilde c_i \equiv U_S c_i U_S^\dagger, \tilde c_j^\dagger \equiv U_S c^\dagger_j U_S^\dagger$ on top of its renormalised ground state $\ket{\tilde 0} = U_S \ket{0}$.
-In terms of the Greens function, equation \ref{H_tiled} becomes
+This says that the Greens function $G_H$ of the bare Hubbard model $H^H$ for excitations $\ket{{j\sigma}} \equiv c^\dagger_{j\sigma}\ket{0}$ on top of its ground state $\ket{0}$ is exactly equal to the Greens function $\tilde G$ of the renormalised Hamiltonian $\tilde H$ for renormalised excitations $\ket{\tilde {j\sigma}} \equiv \tilde c^\dagger_{j\sigma}\ket{\tilde 0} \equiv  \mathcal{U}_A c^\dagger_i  \mathcal{U}_A^\dagger  \mathcal{U}_A\ket{0} =  \mathcal{U}_A\ket{{j\sigma}}$ on top of its renormalised ground state $\ket{\tilde 0} =  \mathcal{U}_A \ket{0}$.
+This means,
+\begin{equation}\begin{aligned}
+	\bra{{i\sigma}}G_H\ket{{j\sigma}} = \bra{\tilde {i\sigma}}\tilde G\ket{\tilde {j\sigma}}
+\end{aligned}\end{equation}
+This same unitary connection also allows us to equate the inverse Greens functions:
+\begin{equation}\begin{aligned}
+	\left[\left(G_H\right)^{-1}\right]^\sigma_{ij} = \bra{i\sigma}\omega - H^H\ket{j\sigma} = \bra{i\sigma} \mathcal{U}_A^\dagger\left(\omega -  \mathcal{U}_A H^H  \mathcal{U}_A^\dagger\right)  \mathcal{U}_A\ket{j\sigma} = \bra{\tilde i\sigma}\left(\omega - \tilde H\right)\ket{\tilde j\sigma} = \left[\left(\tilde G\right)^{-1}\right]^\sigma_{\tilde i,\tilde j}
+\end{aligned}\end{equation}
+We will now see how we can use the Hubbard dimer expansion to get simple expressions for the inverse Greens functions of $\tilde H$, and hence $H^H$.
+\\\\
+In terms of the inverse Greens function, equation \ref{H_tiled} becomes
 \begin{equation}\begin{aligned}
 	\label{green_eq}
-	\omega - {G_H}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}\left[\omega - G_D^{-1}\left(1 \to i, 2 \to j\right)\right]_{t^D \to \frac{1}{2}Nwt^H \atop{U^D \to \frac{1}{2}N U^H}}
+	\omega - \left(\tilde G\right)^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}\left[\omega - G_D^{-1}\left(i, j\right)\right]
 \end{aligned}\end{equation}
-where $G_H$ and $G_D$ are the Greens functions for the full Hubbard and the Hubbard dimer respectively:
+where $\tilde G$ and $G_D$ are the Greens functions for the new (symmetrized) Hubbard model and the Hubbard dimer respectively:
 \begin{equation}\begin{aligned}
-	G_H(\omega) = \frac{1}{\omega - H^H}, && G_D(\omega) = \frac{1}{\omega - H^D}
+	\tilde G(\omega) = \frac{1}{\omega - \tilde H}, && G_D(\omega) = \frac{1}{\omega - H^D}
 \end{aligned}\end{equation}
@@
 	\label{green_eq_final}
-{G_H}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}\left[G_D^{-1}\left(\omega, 1 \to i, 2 \to j\right)\right]_{t^D \to \frac{1}{2}Nwt^H \atop{U^D \to \frac{1}{2}N U^H}} = \frac{2}{Nw}\sum_{\left<i,j\right>}G_D^{-1}\left(\omega, i, j, t^D = \frac{1}{2}Nwt^H, U^D = \frac{1}{2}N U^H\right)
+	\left(\tilde G\right)^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}G_D^{-1}\left(\omega, i, j\right)
 \end{aligned}\end{equation}
 where $G_D^{-1}(i,j,t^D,U^D)$ is the Greens function (matrix) of the Hubbard dimer Hamiltonian with $i, j$ as the two sites.
-Henceforth, we will supress the transformation rules in the arguments of the Greens function and assume they have been applied.
-For the record, the transformations are
+\\\\
+We will now calculate the single-particle site-diagonal and site-off-diagonal Greens functions.
+First lets consider the diagonal Greens function at $i^\text{th}$ site.
+We will extract this using the definition
 \begin{equation}\begin{aligned}
-	t^D &= \frac{1}{2}Nwt^H\\
-	U^D &= \frac{1}{2}N U^H
+	\left[\tilde G(\omega)^{-1}\right]^\sigma_{\tilde i \tilde i} = \bra{\tilde i\sigma}\tilde G(\omega)^{-1}\ket{\tilde i\sigma} = \bra{ i\sigma} G_H(\omega)^{-1}\ket{ i\sigma} = \left[G_H(\omega)^{-1}\right]^\sigma_{ii}
 \end{aligned}\end{equation}
-We will now calculate the single-particle site diagonal and site offdiagonal Greens functions.
-First lets consider the diagonal Greens function at $i^\text{th}$ site.
+\\\\
+{\textbf{\color{red}{[CHECK]How should we connect the Hubbard dimers wavefunctions with the renormalised ground state $\ket{\tilde 0}$?
+If we use just the latter, then the RHS will not be the dimer's greens functions.
+If we use just the former, then the LHS will not be the Greens functions of $\tilde H$, and hence not of $H^H$}.}}
+\\\\
 The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have $i$ in one of the indices.
@@
 	\label{local_gf}
-	\left(G_{H}^{-1}(\omega)\right)_{i\sigma,i\sigma} = \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{00\sigma}\times w = \frac{2}{N}\left[G_{D}^{-1}(\omega)\right]_{00\sigma} \equiv g_0
+	\left(G_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]^\sigma_{00}\times w = \frac{2}{N}\left[G_{D}^{-1}(\omega)\right]^\sigma_{00} \equiv g_0
 \end{aligned}\end{equation}
@@
 Instead, it involves two nearest neighbour sites.
-We call this Greens function $\left[G_D^{-1}(\omega)\right]_{01\sigma}$.
+We call this Greens function $\left[G_D^{-1}(\omega)\right]_{01}^\sigma$.
 \begin{equation}\begin{aligned}
 \label{nn_gf}
-	\left(G_{H}^{-1}(\omega)\right)_{\left<i,j \right>\sigma} &= \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01\sigma} \equiv g_1
+	\left(G_{H}^{-1}(\omega)\right)_{ij}^\sigma &= \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01}^\sigma \equiv g_1
 \end{aligned}\end{equation}
@@
 \end{equation}
-%\section*{Appendix: Greens functions for Anderson molecule}
-%\begin{equation}\begin{aligned}
-%	G_{dd}^\uparrow(\omega) &= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{d\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{d\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
-%	G_{zz}^\uparrow(\omega)&= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{z\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{z\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
-%	G_{dz}^\uparrow(\omega)	&= \sum_{n}\left[\frac{\left<GS|c_{d\uparrow} | n \right>\left<n |c^\dagger_{z \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{d\uparrow} | GS\right>\left<GS |c^\dagger_{z \uparrow} |n\right>}{\omega + E_{n} - E_{GS}}\right]\\
-%	G_{zd}^\uparrow(\omega) &= \sum_{n}\left[\frac{\left<GS|c_{z \uparrow} | n \right>\left<n |c^\dagger_{d \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{z \uparrow} | GS\right>\left<GS |c^\dagger_{d \uparrow} | n\right>}{\omega + E_{n} - E_{GS}}\right] = \left\{G_{dz}^\uparrow(\omega)\right\}^\dagger\\
-%\end{aligned}\end{equation}
-%We proceed exactly as before. With the following shorthand notations,
-%\begin{equation}\begin{aligned}
-%	a_{1,2} &\equiv a_{1,2}\left(U^A, t^A\right), &&\tilde a_{1,2} \equiv a_{1,2}\left(\frac{1}{2}U^A, t^A\right) \\
-%	\Delta &\equiv \Delta\left(U^A, t^A\right), &&\tilde \Delta \equiv \Delta\left(\frac{1}{2}U^A, t^A\right)\\
-%	C_z^\pm &\equiv a_1 \tilde a_1 \pm a_2 \tilde a_2, &&C_x^\pm \equiv a_1 \tilde a_2 \pm a_2 \tilde a_1
-%\end{aligned}\end{equation}
-%\begin{equation}\begin{aligned}
-%	E_{\pm} \equiv E(\ket{2\sigma_\pm}) - E(\ket{-}) = E(\ket{0\sigma_\pm}) - E(\ket{-}) = \frac{1}{2}\tilde\Delta \pm \frac{1}{4}\Delta\\
-%\end{aligned}\end{equation}
-%the diagonal Green's functions are
-%\begin{equation}\begin{aligned}
-%	\label{mole_local_G}
-%	G_{d d}^\uparrow(\omega) &= \left[a_1\tilde a_2 + a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_1 - a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
-%				 &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
-%\end{aligned}\end{equation}
-%\begin{equation}\begin{aligned}
-%	G_{z z}^\uparrow(\omega) &= \left[a_1\tilde a_1 + a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_2 - a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
-%				 &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
-%\end{aligned}\end{equation}
-%and the off-diagonal Greens functions are
-%\begin{equation}\begin{aligned}
-%	G_{dz}^\uparrow(\omega) &= \left(a_1 \tilde a_1 + a_2 \tilde a_2\right) \left(a_1 \tilde a_2 + a_2 \tilde a_1\right) \frac{\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta}{\omega^2 - \left(\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta\right)^2} - \left(a_1 \tilde a_1 - a_2 \tilde a_2\right) \left(a_1 \tilde a_2 - a_2 \tilde a_1\right) \frac{\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta}{\omega^2  - \left(\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right)^2}\\
-%				&= -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}\\
-%G_{zd}^\uparrow(\omega) &= {G_{dz}^\uparrow(\omega)}^\dagger = G_{dz}^\uparrow(\omega)
-%\end{aligned}\end{equation}
-%To summarize, the four Green's real space Greens functions, in the compact notation, of the Anderson molecule are
-%\begin{equation}\begin{aligned}
-%	G_{dd}^\uparrow(\omega) &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
-%	G_{zz}^\uparrow(\omega) &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
-%	G_{dz}^\uparrow(\omega) &= G_{zd}^\uparrow(\omega) = -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}
-%\end{aligned}\end{equation}
 

### 2021-08-11 notes.tex
discussed the approximations in more detail, put in ways of computing the wavefunctions

@@
 H_\text{hubb} &= -t^H\sum_{\sigma,\left<i,j \right>}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right) + U^H\sum_i \hat n_{i \uparrow} \hat n_{i \downarrow} - \mu^H \sum_{i\sigma}\hat n_{i\sigma}\\
-H_\text{siam} &= \sum_{k\sigma}\left[\epsilon_k + \Sigma(k,\omega)\right]\hat n_{k\sigma} + \epsilon_d^A \sum_\sigma\hat n_{d\sigma} + U^A \hat n_{d \uparrow} \hat n_{d \downarrow} + U_b \sum_{kk^\prime}\hat n_k \hat n_{k^\prime} - \mu^A \sum_{i\neq d,\sigma}\hat n_{i\sigma}
-	\label{hams}
+H_\text{siam} &= \sum_{k\sigma}\left[\epsilon_k + \Sigma(k,\omega)\right]\hat n_{k\sigma} + \epsilon_d^A \sum_\sigma\hat n_{d\sigma} + U^A \hat n_{d \uparrow} \hat n_{d \downarrow} + U_b \sum_{kk^\prime}\hat n_k \hat n_{k^\prime} - \mu^A \sum_{i\neq d,\sigma}\hat n_{i\sigma} \label{clus_bath_siam}
 \end{align}
-\\\\
-{\textbf{\color{red}{[CHECK]That $U_b$ does not actually give a zero mode, rather it gives an $N^2$ type piece.}}
-\\\\
 Broadly speaking, the method involves first solving the SIAM using a unitary renormalisation group approach, to get the low energy effective theory, and then combining the low energy Hamiltonians in a symmetrized fashion to get the Hamiltonian for the Hubbard model lattice.
@@
 \end{figure}
+\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model.
+To allow computing quantities, one would need to make the bath (which is a much larger system) simpler than the cluster (which is a single site).
+This distinction breaks the translational symmetry of the Hubbard model.
+For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath only has a global capacitative cost $(\sim U_b N^2)$ means we have broken the symmetry between the cluster and the bath.}
 
@@
 Assuming the impurity-bath couplings are much larger than the dispersion of the bath, we can approximate the conduction bath part by a zero-mode of the kinetic energy part.
-What this means is that all the momentum states will then collapse to a single site (which we call the zero mode site, and represents the origin of the lattice) with a single correlation coupling $U^A_z$.
+The zero mode is defined as $c_0 = \frac{1}{\sqrt N}\sum_k c_k$, so it is just the zeroth site.
+What this means is that all the momentum states will then collapse to a single site (which we call the zero mode site, and represents the origin of the lattice).
+We will also pick out the zeroth site part of the onsite correlation part, and replace that with a single correlation coupling $U^A_z$.
 Such a model, shown in fig.~\ref{and_mol} is exactly solvable.
-Armed with such a Hamiltonian and its spectrum, we will then create the the entire Hubbard Hamiltonian by combining the zero-mode Hamiltonians according to a prescription which is guided by the symmetries of the problem.
+\begin{equation}\begin{aligned}
+	H^A_\text{corr} = -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + U^A\tau_{d \uparrow}\tau_{d \downarrow} + U^A_z\tau_{z \uparrow}\tau_{z \downarrow}
+\end{aligned}\end{equation}
+The motivation for extracting the zero mode is that it leads to a very simple effective Hamiltonian without losing much of the low energy physics.
+\\\\
+We will then create the the entire Hubbard Hamiltonian by combining the zero-mode Hamiltonians according to a prescription which is guided by the symmetries of the problem.
 The impurity electron will be read off as an arbitrary site, \(p\), of the lattice, while the zero-mode site becomes the site that is nearest to it.
-%TODO
-\textbf{We will first demonstrate this explicitly for the Hubbard dimer. Then we will show how we can create a full Hubbard Hamiltonian by joining Anderson molecule Hamiltonians.}
+We will first demonstrate this explicitly for the Hubbard dimer.
+Then we will show how we can create a full Hubbard Hamiltonian by joining Anderson molecule Hamiltonians.
 \begin{figure}[htpb]
@@
 \begin{itemize}
-	\item We have replaced the full Hubbard model by an auxiliary system described by the SIAM Hamiltonian in eq.~\ref{hams}.
+	\item We have replaced the full Hubbard model by an auxiliary system described by the SIAM Hamiltonian in eq.~\ref{clus_bath_siam}.
 The accuracy of this assumption is determined by the choice of the SIAM parameters, particular the self-energy and repulsion of the bath.
-If it is exact, then the equation
-\begin{equation}\begin{aligned}
-	\label{app1}
-	H^H = H^A
-\end{aligned}\end{equation}
-holds.
+As discussed before, the very choice of th cluster and bath spoil the translational invariance of the parent model.
 	\item We then perform a unitary RG on $H^A$.
@@
 At this point, we extract a zero mode of this Hamiltonian to obtain the Hubbard dimer Hamiltonian: $H^D = \left(U_A H^A U_A^\dagger\right)_z$, and this constitutes the second approximations we make.
-We tile this Hubbard dimer Hamiltonian to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H$.
-If we assume that the tiling perfectly rectifies the approximation made while taking the zero mode, then we can write
+This approximation further reduces the symmetry, because we have dropped all other lattice sites and kept just the zeroth lattice site.
+\end{itemize}
+We now tile this Hubbard dimer Hamiltonian to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H$.
+We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.
+\begin{equation}\begin{aligned}
+	\tilde H = - \frac{2t^D}{Nw}\sum_{\sigma \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
+\end{aligned}\end{equation}
+What that means is that we have placed the Hubbard dimer at all nearest neighbour pairs to reconstruct a new Hubbard model.
+If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as taking the zero mode, we can write
 \begin{equation}\begin{aligned}
 	\label{app2}
-	\tilde H = U_A H^A U_A^\dagger
+	\tilde H = \mathcal{U} H^A \mathcal{U}^\dagger
 \end{aligned}\end{equation}
-\end{itemize}
-Combining the two eqs.~\ref{app1},\ref{app2}, we can say that
-\begin{equation}\begin{aligned}
-	\tilde H = U_A H^H U_A^\dagger
-\end{aligned}\end{equation}
-which would mean that the final Hamiltonian is unitarily connected to the bare Hubbard model, but is actually made of Hubbard dimers and is hence more amenable to calculations.
+The content of the above equation is that we expect the final tiled translationally invariant new (renormalised) Hubbard Hamiltonian to be connected to the bare parent Hubbard model through some unitary transformation $\mathcal{U}$.
 This of course depends on how good the approximations are and strictly speaking need to be verified.
@@
 \\\\
-The claim made in a previous section was that this Hamiltonian is very close to the unitarily transformed Hubbard Hamiltonian:
+The claim made in a previous section was that this Hamiltonian is very close to a unitarily transformed Hubbard Hamiltonian:
 \begin{equation}\begin{aligned}
-	\frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D) \simeq  \mathcal{U}_A H^H  \mathcal{U}_A^\dagger
+	\frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D) \simeq  \mathcal{U} H^H  \mathcal{U}^\dagger
 \end{aligned}\end{equation}
-$\mathcal{U}_A$ is the total unitary transformation that completes the URG starting from the bare cluster+bath Anderson model up to the fixed-point Hamiltonian.
+$\mathcal{U}$ is actually distinct from the unitary transformation that completes the URG starting from the bare cluster+bath Anderson model up to the fixed-point Hamiltonian.
+It is a larger transformation that involves three steps: the URG transformations $\mathcal{U}_A$, the extracting of the zero mode $Z$ and the tiling procedure outline in this section, $T$.
+\begin{equation}\begin{aligned}
+	\mathcal{U} = T Z \mathcal{U}_A
+\end{aligned}\end{equation}
 
@@
 \subsection{Expressing matrix elements of the inverse single particle Greens function in terms of Hubbard dimer counterparts}
-If the groundstate wavefunction of $H^H$ is $\ket{0}$, then the groundstate wavefunction of $\tilde H$ is $\ket{\tilde 0} =  \mathcal{U}_A\ket{0}$.
+If the groundstate wavefunction of $H^H$ is $\ket{0}$, then the groundstate wavefunction of $\tilde H$ is $\ket{\tilde 0} =  \mathcal{U}\ket{0}$.
 The advantage of $\tilde H$ being unitarily connected to $H^H$ is that they will have the same single-particle Greens functions.
 \begin{equation}\begin{aligned}
-	\left(G_H\right)^\sigma_{ij}(t) \equiv -i\theta(t)\bra{0}\left\{c_{i\sigma},c^\dagger_{j\sigma} \right\}\ket{0} &= -i\theta(t)\bra{0} \mathcal{U}_A^\dagger\left\{  \mathcal{U}_A c_{i\sigma}  \mathcal{U}_A^\dagger  \mathcal{U}_A c^\dagger_{j\sigma}  \mathcal{U}_A^\dagger +  \mathcal{U}_A c^\dagger_{j\sigma}  \mathcal{U}_A^\dagger  \mathcal{U}_A c_{i\sigma}  \mathcal{U}_A^\dagger\right\} \mathcal{U}_A\ket{0}\\
+	\left(G_H\right)^\sigma_{ij}(t) \equiv -i\theta(t)\bra{0}\left\{c_{i\sigma},c^\dagger_{j\sigma} \right\}\ket{0} &= -i\theta(t)\bra{0} \mathcal{U}^\dagger\left\{  \mathcal{U} c_{i\sigma}  \mathcal{U}^\dagger  \mathcal{U} c^\dagger_{j\sigma}  \mathcal{U}^\dagger +  \mathcal{U} c^\dagger_{j\sigma}  \mathcal{U}^\dagger  \mathcal{U} c_{i\sigma}  \mathcal{U}^\dagger\right\} \mathcal{U}\ket{0}\\
 															&=-i\theta(t)\bra{\tilde 0}\left\{\tilde c_{i\sigma} \tilde c^\dagger_{j\sigma} + \tilde c^\dagger_{j\sigma} \tilde c_{i\sigma} \right\}\ket{\tilde 0}\\
@@
 \end{aligned}\end{equation}
-This says that the Greens function $G_H$ of the bare Hubbard model $H^H$ for excitations $\ket{{j\sigma}} \equiv c^\dagger_{j\sigma}\ket{0}$ on top of its ground state $\ket{0}$ is exactly equal to the Greens function $\tilde G$ of the renormalised Hamiltonian $\tilde H$ for renormalised excitations $\ket{\tilde {j\sigma}} \equiv \tilde c^\dagger_{j\sigma}\ket{\tilde 0} \equiv  \mathcal{U}_A c^\dagger_i  \mathcal{U}_A^\dagger  \mathcal{U}_A\ket{0} =  \mathcal{U}_A\ket{{j\sigma}}$ on top of its renormalised ground state $\ket{\tilde 0} =  \mathcal{U}_A \ket{0}$.
+This says that the Greens function $G_H$ of the bare Hubbard model $H^H$ for excitations $\ket{{j\sigma}} \equiv c^\dagger_{j\sigma}\ket{0}$ on top of its ground state $\ket{0}$ is exactly equal to the Greens function $\tilde G$ of the renormalised Hamiltonian $\tilde H$ for renormalised excitations $\ket{\tilde {j\sigma}} \equiv \tilde c^\dagger_{j\sigma}\ket{\tilde 0} \equiv  \mathcal{U} c^\dagger_i  \mathcal{U}^\dagger  \mathcal{U}\ket{0} =  \mathcal{U}\ket{{j\sigma}}$ on top of its renormalised ground state $\ket{\tilde 0} =  \mathcal{U} \ket{0}$.
 This means,
@@
 \begin{equation}\begin{aligned}
-	\left[\left(G_H\right)^{-1}\right]^\sigma_{ij} = \bra{i\sigma}\omega - H^H\ket{j\sigma} = \bra{i\sigma} \mathcal{U}_A^\dagger\left(\omega -  \mathcal{U}_A H^H  \mathcal{U}_A^\dagger\right)  \mathcal{U}_A\ket{j\sigma} = \bra{\tilde i\sigma}\left(\omega - \tilde H\right)\ket{\tilde j\sigma} = \left[\left(\tilde G\right)^{-1}\right]^\sigma_{\tilde i,\tilde j}
+	\left[\left(G_H\right)^{-1}\right]^\sigma_{ij} = \bra{i\sigma}\omega - H^H\ket{j\sigma} = \bra{i\sigma} \mathcal{U}^\dagger\left(\omega -  \mathcal{U} H^H  \mathcal{U}^\dagger\right)  \mathcal{U}\ket{j\sigma} = \bra{\tilde i\sigma}\left(\omega - \tilde H\right)\ket{\tilde j\sigma} = \left[\left(\tilde G\right)^{-1}\right]^\sigma_{\tilde i,\tilde j}
 \end{aligned}\end{equation}
@@
 \\\\
-In terms of the inverse Greens function, equation \ref{H_tiled} becomes
+Equation \ref{H_tiled} can be rewritten in terms of inverse Greens functions.
+However, before proceeding, we should note that even though eq.~\ref{H_tiled} used the indices $i,$, the correct indices are actually $\tilde i, \tilde j$, in light of the fact that operators get renormalised as $c_i \to \tilde c_i\equiv Uc_i$.
+With this in mind, we can write
 \begin{equation}\begin{aligned}
 	\label{green_eq}
-	\omega - \left(\tilde G\right)^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}\left[\omega - G_D^{-1}\left(i, j\right)\right]
+	\omega - \left(\tilde G\right)^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<\tilde i, \tilde j\right>}\left[\omega - G_D^{-1}\left(\tilde i, \tilde j\right)\right]
 \end{aligned}\end{equation}
@@
 	\label{green_eq_final}
-	\left(\tilde G\right)^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}G_D^{-1}\left(\omega, i, j\right)
+	\left(\tilde G\right)^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}G_D^{-1}\left(\omega, \tilde i, \tilde j\right)
 \end{aligned}\end{equation}
-where $G_D^{-1}(i,j,t^D,U^D)$ is the Greens function (matrix) of the Hubbard dimer Hamiltonian with $i, j$ as the two sites.
+where $G_D^{-1}(\tilde i,\tilde j,t^D,U^D)$ is the Greens function (matrix) of the Hubbard dimer Hamiltonian with $\tilde i, \tilde j$ as the two sites.
 \\\\
 We will now calculate the single-particle site-diagonal and site-off-diagonal Greens functions.
-First lets consider the diagonal Greens function at $i^\text{th}$ site.
+First lets consider the diagonal Greens function at $\tilde i^\text{th}$ site.
 We will extract this using the definition
@@
 \end{aligned}\end{equation}
-\\\\
-{\textbf{\color{red}{[CHECK]How should we connect the Hubbard dimers wavefunctions with the renormalised ground state $\ket{\tilde 0}$?
-If we use just the latter, then the RHS will not be the dimer's greens functions.
-If we use just the former, then the LHS will not be the Greens functions of $\tilde H$, and hence not of $H^H$}.}}
-\\\\
-The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have $i$ in one of the indices.
-There will be $w$ such terms, because $i$ has $w$ nearest neighbours.
+This means that we will take the matrix element of eq.~\ref{green_eq_final} between the excitations above the exact ground state of $\tilde H$, which is $\ket{\tilde i}$.
+The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have $\tilde i$ in one of the indices.
+There will be $w$ such terms, because $\tilde i$ has $w$ nearest neighbours.
 Thus, the right hand side will be a sum of $w$ terms, each term being the inverse Greens function of a Hubbard dimer.
 Each term will be a real space local Greens function, and because of translational invariance, it will be the same on both sites.
-So we will represent the real space local inverse Greens function as $\left[G_D^{-1}(\omega)\right]_{00\sigma}$.
+So we will represent the real space local inverse Greens function as $\left[G_D^{-1}(\omega)\right]_{00}^{\sigma}$.
 The entire thing is thus $w$ times this local Greens function.
@@
 \end{aligned}\end{equation}
-Now we come to the off-diagonal Greens function for the nearest neighbour sites $i$ and $j$.
+Now we come to the off-diagonal Greens function for the nearest neighbour sites $i$ and $j$.We will extract this using the definition
+\begin{equation}\begin{aligned}
+	\left[\tilde G(\omega)^{-1}\right]^\sigma_{\tilde i \tilde j} = \bra{\tilde i\sigma}\tilde G(\omega)^{-1}\ket{\tilde j\sigma} = \bra{ i\sigma} G_H(\omega)^{-1}\ket{j\sigma} = \left[G_H(\omega)^{-1}\right]^\sigma_{ij}
+\end{aligned}\end{equation}
+We will again take the matrix element of eq.~\ref{green_eq_final} between the excitations above the exact ground state of $\tilde H$.
 This will receive contribution from only one nearest neighbour pair in the summation of the RHS of eq.~\ref{green_eq_final}, namely that of $\left(i,j\right)$.
@@
 We will provide these expressions at a later point in time.
+\section{Calculating $g_0$ and $g_1$ in practice}
+The expressions for $g_0$ and $g_1$, as mentioned above, involve taking matrix elements of the Hubbard dimer Hamiltonian against the exact wavefunctions of the full Hubbard model.
+\begin{itemize}
+	\item Since the full Hubbard model ground state wavefunctions are not readily available, one can, as the simplest approximation, assume the ground state has the form
+	\begin{equation}\begin{aligned}
+		\ket{\tilde 0} = \sum_{\left<ij \right>}\ket{\Phi^D_{ij}}\otimes\ket{\Psi_{\hat i, \hat j}}\label{guess}
+	\end{aligned}\end{equation}
+	$\ket{\Phi^D_{ij}}$ would be the ground state of the Hubbard dimer with $i,j$ creating the two sites of the dimer, while $\ket{\Psi_{\hat i, \hat j}}$ would be the wavefunction involving the rest of the sites.
+This ofcourse assumes that the two sets $(i,j)$ and $(a,b,...,h,k,...)$ are not entangled, and is not true in general.
+With this assumption, $g_0$ and $g_1$ become related to the inverse Greens functions of the Hubbard dimer.
+Such a choice of the wavefunction is motivated by the fact that in the auxiliary system we chose, the bath had only a diagonal interaction; there was no off-diagonal two particle scattering term.
+	\item Another way of approaching this is to obtain the ground state wavefunction numerically, and then computing the matrix elements of $H^D$ against this wavefunction to obtain $g_0$ and $g_1$ for each value of $U^H$ and $t^H$ of the bare Hubbard model.
+This however means we lose any analytical insight into $g_0$ and $g_1$.
+	\item The overall best way of calculating $g_0$ and $g_1$ is probably by systematically improving the ground state wavefunctions.
+This can done by obtaining the wavefunction not just for the dimer, but for a dimer with dispersion:
+\begin{equation}\begin{aligned}
+		H^D_\text{improved} = -t\sum_{{k\in\text{NN of }z}}\left(c^\dagger_{k\sigma}c_{z\sigma} + \text{h.c.}\right) -t \left(c^\dagger_{i\sigma}c_{z\sigma} + \text{h.c.}\right) + U\left(\tau_{d \uparrow}\tau_{d \downarrow} + \tau_{z \uparrow}\tau_{z \downarrow}\right)
+\end{aligned}\end{equation}
+
+\end{itemize}
+By systematically increasing the number of nearest neighbours, we can get better and better ground state wavefunctions, with which we can compute matrix elements, and hence $g_0$, $g_1$.
+What this means is that if we had just a Hubbard dimer wavefunction, then the impurity can at most hop onto its nearest neighbour, and then hop back, hence the wavefunction in eq.~\ref{guess}.
+However, with this additional hopping, the impurity can now now hop on to the nearest neighbour $z$, and then on to the next nearest neighbours.
+This leads to entanglement between the impurity site and the next nearest neighbour sites, which was missing in eq.~\ref{guess}.
+Another improvement can be made by introducing a self-energy into the dispersion.
+This introduces correlation on sites beyond the impurity and its nearest neighbour.
+The introduction of the dispersion and a self-energy gives the hope that we can capture a spectral function of the three peak form, because previously we have seen such a spectral function in the Anderson molecule with dispersion.
 \newpage
@@
 \end{equation}
+Once we have calculated the diagonal and off-diagonal matrix elements of the Greens function, we can compute the parameters $g_0$ and $g_1$:
+\begin{equation}\begin{aligned}
+		 g_0 \equiv\frac{2}{N} (G^{-1}_{D})_{00} = \frac{2}{N} \frac{1}{\text{Det }G_D}\left(G_D\right)_{00}, g_1 \equiv\frac{2}{Nw} (G^{-1}_{D})_{00} = -\frac{2}{Nw}\frac{1}{\text{Det }G_D}\left(G_D\right)_{01}
+ \end{aligned}\end{equation}
 

### 2021-08-12 notes.tex
changed unitary to similarity, added figure for the improved wavefunction

@@
 H_\text{hubb} &= -t^H\sum_{\sigma,\left<i,j \right>}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right) + U^H\sum_i \hat n_{i \uparrow} \hat n_{i \downarrow} - \mu^H \sum_{i\sigma}\hat n_{i\sigma}\\
-H_\text{siam} &= \sum_{k\sigma}\left[\epsilon_k + \Sigma(k,\omega)\right]\hat n_{k\sigma} + \epsilon_d^A \sum_\sigma\hat n_{d\sigma} + U^A \hat n_{d \uparrow} \hat n_{d \downarrow} + U_b \sum_{kk^\prime}\hat n_k \hat n_{k^\prime} - \mu^A \sum_{i\neq d,\sigma}\hat n_{i\sigma} \label{clus_bath_siam}
+H_\text{siam} &= \sum_{k\sigma}\left[\epsilon_k + \Sigma(k,\omega)\right]\hat n_{k\sigma} + \epsilon_d^A \sum_\sigma\hat n_{d\sigma} + U^A \hat n_{d \uparrow} \hat n_{d \downarrow} + U_b \sum_{kk^\prime}\hat n_k \hat n_{k^\prime} -t^A\sum_{k\sigma}\left(c^\dagger_{d\sigma}c_{k\sigma} + \text{h.c.}\right) \label{clus_bath_siam}
 \end{align}
@@
 	\label{app2}
-	\tilde H = \mathcal{U} H^A \mathcal{U}^\dagger
+	\tilde H = \mathcal{U} H^H \mathcal{U}^{-1}
 \end{aligned}\end{equation}
-The content of the above equation is that we expect the final tiled translationally invariant new (renormalised) Hubbard Hamiltonian to be connected to the bare parent Hubbard model through some unitary transformation $\mathcal{U}$.
+where $\mathcal{U}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation..
+The content of the above equation is that we expect the final tiled translationally invariant new (renormalised) Hubbard Hamiltonian to be connected to the bare parent Hubbard model through some unitary/similarity transformation $\mathcal{U}$.
 This of course depends on how good the approximations are and strictly speaking need to be verified.
@@
 \\\\
-The claim made in a previous section was that this Hamiltonian is very close to a unitarily transformed Hubbard Hamiltonian:
+The claim made in a previous section was that this Hamiltonian is very close to a similarity transformed Hubbard Hamiltonian:
 \begin{equation}\begin{aligned}
-	\frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D) \simeq  \mathcal{U} H^H  \mathcal{U}^\dagger
+	\frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D) \simeq  \mathcal{U} H^H  \mathcal{U}^{-1}
 \end{aligned}\end{equation}
-$\mathcal{U}$ is actually distinct from the unitary transformation that completes the URG starting from the bare cluster+bath Anderson model up to the fixed-point Hamiltonian.
+$\mathcal{U}$ is in general distinct from the unitary transformation that completes the URG starting from the bare cluster+bath Anderson model up to the fixed-point Hamiltonian.
 It is a larger transformation that involves three steps: the URG transformations $\mathcal{U}_A$, the extracting of the zero mode $Z$ and the tiling procedure outline in this section, $T$.
 \begin{equation}\begin{aligned}
-	\mathcal{U} = T Z \mathcal{U}_A
+	\mathcal{U} = T Z \mathcal{U}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(G_H\right)^\sigma_{ij}(t) \equiv -i\theta(t)\bra{0}\left\{c_{i\sigma},c^\dagger_{j\sigma} \right\}\ket{0} &= -i\theta(t)\bra{0} \mathcal{U}^\dagger\left\{  \mathcal{U} c_{i\sigma}  \mathcal{U}^\dagger  \mathcal{U} c^\dagger_{j\sigma}  \mathcal{U}^\dagger +  \mathcal{U} c^\dagger_{j\sigma}  \mathcal{U}^\dagger  \mathcal{U} c_{i\sigma}  \mathcal{U}^\dagger\right\} \mathcal{U}\ket{0}\\
+	\left(G_H\right)^\sigma_{ij}(t) \equiv -i\theta(t)\bra{0}\left\{c_{i\sigma},c^\dagger_{j\sigma} \right\}\ket{0} &= -i\theta(t)\bra{0} \mathcal{U}^{-1}\left\{  \mathcal{U} c_{i\sigma}  \mathcal{U}^{-1}  \mathcal{U} c^\dagger_{j\sigma}  \mathcal{U}^{-1} +  \mathcal{U} c^\dagger_{j\sigma}  \mathcal{U}^{-1}  \mathcal{U} c_{i\sigma}  \mathcal{U}^{-1}\right\} \mathcal{U}\ket{0}\\
 															&=-i\theta(t)\bra{\tilde 0}\left\{\tilde c_{i\sigma} \tilde c^\dagger_{j\sigma} + \tilde c^\dagger_{j\sigma} \tilde c_{i\sigma} \right\}\ket{\tilde 0}\\
@@
 \end{aligned}\end{equation}
-This says that the Greens function $G_H$ of the bare Hubbard model $H^H$ for excitations $\ket{{j\sigma}} \equiv c^\dagger_{j\sigma}\ket{0}$ on top of its ground state $\ket{0}$ is exactly equal to the Greens function $\tilde G$ of the renormalised Hamiltonian $\tilde H$ for renormalised excitations $\ket{\tilde {j\sigma}} \equiv \tilde c^\dagger_{j\sigma}\ket{\tilde 0} \equiv  \mathcal{U} c^\dagger_i  \mathcal{U}^\dagger  \mathcal{U}\ket{0} =  \mathcal{U}\ket{{j\sigma}}$ on top of its renormalised ground state $\ket{\tilde 0} =  \mathcal{U} \ket{0}$.
+This says that the Greens function $G_H$ of the bare Hubbard model $H^H$ for excitations $\ket{{j\sigma}} \equiv c^\dagger_{j\sigma}\ket{0}$ on top of its ground state $\ket{0}$ is exactly equal to the Greens function $\tilde G$ of the renormalised Hamiltonian $\tilde H$ for renormalised excitations $\ket{\tilde {j\sigma}} \equiv \tilde c^\dagger_{j\sigma}\ket{\tilde 0} \equiv  \left(\mathcal{U} c^\dagger_i  \mathcal{U}^{-1}\right)  \mathcal{U}\ket{0} =  \mathcal{U}\ket{{j\sigma}}$ on top of its renormalised ground state $\ket{\tilde 0} =  \mathcal{U} \ket{0}$.
 This means,
@@
 \begin{equation}\begin{aligned}
-	\left[\left(G_H\right)^{-1}\right]^\sigma_{ij} = \bra{i\sigma}\omega - H^H\ket{j\sigma} = \bra{i\sigma} \mathcal{U}^\dagger\left(\omega -  \mathcal{U} H^H  \mathcal{U}^\dagger\right)  \mathcal{U}\ket{j\sigma} = \bra{\tilde i\sigma}\left(\omega - \tilde H\right)\ket{\tilde j\sigma} = \left[\left(\tilde G\right)^{-1}\right]^\sigma_{\tilde i,\tilde j}
+	\left[\left(G_H\right)^{-1}\right]^\sigma_{ij} = \bra{i\sigma}\omega - H^H\ket{j\sigma} = \bra{i\sigma} \mathcal{U}^{-1}\left(\omega -  \mathcal{U} H^H  \mathcal{U}^{-1}\right)  \mathcal{U}\ket{j\sigma} = \bra{\tilde i\sigma}\left(\omega - \tilde H\right)\ket{\tilde j\sigma} = \left[\left(\tilde G\right)^{-1}\right]^\sigma_{\tilde i,\tilde j}
 \end{aligned}\end{equation}
@@
 	\begin{equation}\begin{aligned}
-		\ket{\tilde 0} = \sum_{\left<ij \right>}\ket{\Phi^D_{ij}}\otimes\ket{\Psi_{\hat i, \hat j}}\label{guess}
+		\ket{\tilde 0} = \sum_{\left<\tilde i \tilde j \right>}\ket{\Phi^D_{\tilde i\tilde j}}\otimes\ket{\Psi_{\hat{\tilde i}, \hat {\tilde j}}}\label{guess}
 	\end{aligned}\end{equation}
@@
 Such a choice of the wavefunction is motivated by the fact that in the auxiliary system we chose, the bath had only a diagonal interaction; there was no off-diagonal two particle scattering term.
+It further enforced when we extract the zero mode of the entire bath and keep just the zeroth site.
+The zeroth site, along with the impurity, then forms the $\ket{\Phi}$ part of the wavefunction.
 	\item Another way of approaching this is to obtain the ground state wavefunction numerically, and then computing the matrix elements of $H^D$ against this wavefunction to obtain $g_0$ and $g_1$ for each value of $U^H$ and $t^H$ of the bare Hubbard model.
 This however means we lose any analytical insight into $g_0$ and $g_1$.
-	\item The overall best way of calculating $g_0$ and $g_1$ is probably by systematically improving the ground state wavefunctions.
-This can done by obtaining the wavefunction not just for the dimer, but for a dimer with dispersion:
+	\item The overall best way of calculating $g_0$ and $g_1$ is by systematically improving the ground state wavefunctions.
+This can done by obtaining the wavefunction of a Hamiltonian that has not just for the dimer, but also a bath (with dispersion) that connects with both the sites of the dimer:
 \begin{equation}\begin{aligned}
-		H^D_\text{improved} = -t\sum_{{k\in\text{NN of }z}}\left(c^\dagger_{k\sigma}c_{z\sigma} + \text{h.c.}\right) -t \left(c^\dagger_{i\sigma}c_{z\sigma} + \text{h.c.}\right) + U\left(\tau_{d \uparrow}\tau_{d \downarrow} + \tau_{z \uparrow}\tau_{z \downarrow}\right)
+		\label{dimer_dispersion}
+	H^D_\text{bath}(\tilde i, \tilde j) = \underbrace{U\left(\tau_{\tilde i \uparrow}\tau_{\tilde i \downarrow} + \tau_{\tilde j \uparrow}\tau_{\tilde j \downarrow}\right) - t \sum_\sigma\left(c^\dagger_{\tilde i\sigma}c_{\tilde j\sigma} + \text{h.c.}\right)}_\text{Hubbard dimer} + \underbrace{\sum_{k\sigma}\epsilon_{k\sigma}\tau_{k\sigma}}_\text{bath} \underbrace{- t \sum_{k\sigma}\left(c^\dagger_{\tilde i\sigma}c_{k\sigma} + c^\dagger_{\tilde j\sigma}c_{k\sigma} + \text{h.c.}\right)}_\text{bath-dimer hybridisation}
 \end{aligned}\end{equation}
-
-\end{itemize}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{./dimer_dispersion.png}
+	\caption{Hubbard dimer with dispersion that connects to both sites}
+\end{figure}
+\\\\
 By systematically increasing the number of nearest neighbours, we can get better and better ground state wavefunctions, with which we can compute matrix elements, and hence $g_0$, $g_1$.
@@
 This leads to entanglement between the impurity site and the next nearest neighbour sites, which was missing in eq.~\ref{guess}.
-Another improvement can be made by introducing a self-energy into the dispersion.
+The introduction of the dispersion gives the hope that we can capture a spectral function of the three peak form, because we have previously seen such a spectral function in the fixed point of the URG analysis of the SIAM (the fixed point Hamiltonian was an Anderson molecule with dispersion).
+\item Another improvement can be made by introducing a self-energy into the dispersion.
 This introduces correlation on sites beyond the impurity and its nearest neighbour.
-The introduction of the dispersion and a self-energy gives the hope that we can capture a spectral function of the three peak form, because previously we have seen such a spectral function in the Anderson molecule with dispersion.
+The Hamiltonian would be the same as eq.~\ref{dimer_dispersion}, with $\epsilon_k$ replaced by $\tilde \epsilon_k \equiv \epsilon_k + \Sigma(k,\omega)$.
+The self-energy $\Sigma$ will have to be chosen depending on the phase we want to look at.
+With a $\Sigma$ that is singular near the Fermi surface at $\omega \to 0$, the dispersion will become gapped and the phase will be insulating.
+In such a situation, eq.~\ref{guess} will be a very good approximation to the actual ground state.
+On the other hand, if we use a self energy that vanishes near the Fermi surface ($\Sigma(\omega) \sim \omega^2$), then we will end up in a metallic phase.
+Introducing the self energy therefore gives us a larger variety of wavefunctions and features to work with.
+\end{itemize}
 \newpage

### 2021-08-12 notes.tex
touch ups by sir

@@
 \usepackage[T1]{fontenc}
-\usepackage[hidelinks,pdfusetitle]{hyperref}
+%\usepackage[hidelinks,pdfusetitle]{hyperref}
+\usepackage[pdfusetitle]{hyperref}
 \renewcommand{\arraystretch}{1.9}
@@
 \end{aligned}\end{equation}
-The motivation for extracting the zero mode is that it leads to a very simple effective Hamiltonian without losing much of the low energy physics.
+The motivation for extracting the zero mode is that it leads to a very simple effective Hamiltonian (the asymmetric Anderson molecule) without losing much of the low energy physics.
 \\\\
@@
 	\includegraphics[width=0.6\textwidth]{./gen_siam.png}
-	\caption{Correlated Anderson molecule schematic version. It consists of two sites, impurity(blue) and zero mode(green). The impurity site has onsite repulsion, and their is inter-site hopping.}
+	\caption{Correlated asymmetric Anderson molecule schematic version.
+It consists of two sites, impurity(blue) and zero mode(green).
+The impurity site has onsite repulsion, and their is inter-site hopping.}
 	\label{and_mol}
@@
 We will also assume that the parameters of the auxiliary system have been chosen such that in the effective Hamiltonian, the impurity and zero mode have the same onsite repulsion: $U^A = U^A_z$ (this is required for translational invariance).
-What this all means is that the RG analysis of the bare Hubbard Hamiltonian has led to a Hubbard dimer Hamiltonian.
+What this all means is that the RG analysis of the auxiliary model (appropriately chosen to model the bare Hubbard Hamiltonian) has led to a stable fixed point theory effective Hamiltonian described by a Hubbard dimer
 \begin{equation}\begin{aligned}
@@
 \end{figure}
-The next step is to combine these Hubbard dimers into a full Hubbard model, $\tilde H$. Along the way, we have made two approximations:
+\par\noindent
+The next step is to restore the lost translational invariance of the full system.
+We intend to do this by recreating a full Hubbard model, $\tilde H$, through the iterative real-space translation of the Hubbard dimer effective Hamiltonian obtained above.
+We will describe this process in detail below.
+However, we first specify the two approximations made along the entire journey from the original Hubbard model to the reconstructed one:
 \begin{itemize}
@@
 	\item We then perform a unitary RG on $H^A$.
-This leads to a fixed-point Hamiltonian $U_A H^A U_A^\dagger$.
-At this point, we extract a zero mode of this Hamiltonian to obtain the Hubbard dimer Hamiltonian: $H^D = \left(U_A H^A U_A^\dagger\right)_z$, and this constitutes the second approximations we make.
-This approximation further reduces the symmetry, because we have dropped all other lattice sites and kept just the zeroth lattice site.
+This leads to a fixed-point Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$.
+At this point, we extract a zero mode of this Hamiltonian to obtain the Hubbard dimer Hamiltonian: $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$, where $Z$ defines the projection operator that extracts the zero mode from the effective stable fixed Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$.
+This constitutes the second approximations we make.
+This approximation further reduces the symmetry, because we have dropped all other lattice sites and kept just the zeroth lattice site (i.e., the site to which the impurity is coupled through single electron hybridisation).
 \end{itemize}
-We now tile this Hubbard dimer Hamiltonian to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H$.
+We now tile the real-space lattice with this Hubbard dimer Hamiltonian to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H = T\left[ H^{D} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the dimer Hamiltonian to span the target real-space lattice.
 We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.
@@
 	\label{app2}
-	\tilde H = \mathcal{U} H^H \mathcal{U}^{-1}
+	\tilde H = \mathcal{U} H^H \mathcal{U}^{-1} = TZ\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right]Z^{-1} T^{-1}~,
 \end{aligned}\end{equation}
-where $\mathcal{U}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation..
-The content of the above equation is that we expect the final tiled translationally invariant new (renormalised) Hubbard Hamiltonian to be connected to the bare parent Hubbard model through some unitary/similarity transformation $\mathcal{U}$.
-This of course depends on how good the approximations are and strictly speaking need to be verified.
+where $\mathcal{U} = TZ\mathcal{U}_{A}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation that maps from the original to the reconstructed Hubbard Hamiltonian.
+%The content of the above equation is that we expect the final tiled translationally invariant new (renormalised) Hubbard Hamiltonian to be connected to the bare parent Hubbard model through some unitary/similarity transformation $\mathcal{U}$.
+The existence of $U$ is contingent on how good the approximations are, and strictly speaking needs to be verified.
 
@@
 This is achieved by applying periodic boundary conditions on the edges of the lattice.
-A square 2d lattice is thus placed on a torus.
+A square 2d lattice is thus placed on a 2-torus.
 \\\\
@@
 	\tilde H &= \frac{1}{Nw}\sum_{i=1}^N H^D_{i} \\
-		      &= \frac{1}{Nw}\left[\sum_{\sigma i=1}^N\sum_{j \in \text{NN of }j}-t^D\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^D\sum_{i=1}^N \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + U^D\sum_{i=1}^N\sum_{j \in \text{N.N.
+		      &= \frac{1}{Nw}\left[\sum_{\sigma, i=1}^N\sum_{j \in \text{NN of }j}-t^D\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^D\sum_{i=1}^N \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + U^D\sum_{i=1}^N\sum_{j \in \text{N.N.
 of }i}\hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right] \\
-		      &= \frac{1}{Nw}\left[-t^D 2\sum_{\sigma \left<ij\right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + 2 U^D\sum_{\left<ij\right>} \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + 2 U^D\sum_{\left<ij\right>} \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right]\\
+		      &= \frac{1}{Nw}\left[-t^D 2\sum_{\sigma, \left<ij\right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + 2 U^D\sum_{\left<ij\right>} \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + 2 U^D\sum_{\left<ij\right>} \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right]\\
 		      &= \frac{2}{Nw}\sum_{\left<ij\right>}\left[-t^D \sum_\sigma \left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + U^D\left(\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right)\right]\\
@@
 \end{aligned}\end{equation}
-The sum $\left<ij\right>$ is over all nearest-neighbour pairs. So $\tilde H$ can thus be written as
+The sum $\left<ij\right>$ is over all nearest-neighbour pairs. Thus, $\tilde H$ can be written as
 \begin{equation}\begin{aligned}
 	\label{H_tiled}
-	\tilde H = - \frac{2t^D}{Nw}\sum_{\sigma \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
+	\tilde H = - \frac{2t^D}{Nw}\sum_{\sigma, \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
 \end{aligned}\end{equation}
-The conclusion is that on tiling the Hubbard dimer Hamiltonians into all the nearest neighbour pairs, we end up with a new Hubbard model Hamiltonian with "renormalised parameters"
+The conclusion is that on tiling the Hubbard dimer Hamiltonians into all the nearest neighbour pairs, we end up with a new Hubbard model Hamiltonian with "renormalised parameters" given by
 \begin{equation}\begin{aligned}
-	\tilde t = \frac{2t^D}{Nw}, \tilde U = \frac{2U^D}{N}
+	\tilde t = \frac{2t^D}{Nw}~~,~~ \tilde U = \frac{2U^D}{N}~.
 \end{aligned}\end{equation}
-It is clear that symmetrizing the Anderson molecules by translating them throughout the lattice has restored translational invariance, and generated correlations on all sites (as compared to just on the impurity site).
+It is thus apparent that translating the Hubbard dimers throughout the lattice has restored translational invariance, and generated correlations on all sites. 
+%(as compared to just on the impurity site).
 %This also takes care of the problem that the spectrum of the Anderson molecule and Hubbard dimer are different for the $N=1$ or $N=3$ sectors: By translating the Anderson molecule suitably, we have recovered the correct spectrum in all sectors.
@@
 \begin{equation}\begin{aligned}
-	\frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D) \simeq  \mathcal{U} H^H  \mathcal{U}^{-1}
+	\tilde{H} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D) \equiv  \mathcal{U} H^H  \mathcal{U}^{-1}~,
 \end{aligned}\end{equation}
-$\mathcal{U}$ is in general distinct from the unitary transformation that completes the URG starting from the bare cluster+bath Anderson model up to the fixed-point Hamiltonian.
-It is a larger transformation that involves three steps: the URG transformations $\mathcal{U}_A$, the extracting of the zero mode $Z$ and the tiling procedure outline in this section, $T$.
+where $\mathcal{U}$ is in general distinct from the unitary transformation that completes the URG starting from the bare cluster+bath Anderson model up to the fixed-point Hamiltonian.
+As shown earlier, $U$ transformation that involves three steps: the URG transformations $\mathcal{U}_A$, the extracting of the zero mode $Z$ and the tiling procedure outline in this section, $T$
 \begin{equation}\begin{aligned}
-	\mathcal{U} = T Z \mathcal{U}
+	\mathcal{U} = T Z \mathcal{U}_{A}~.
 \end{aligned}\end{equation}
@@
 If the groundstate wavefunction of $H^H$ is $\ket{0}$, then the groundstate wavefunction of $\tilde H$ is $\ket{\tilde 0} =  \mathcal{U}\ket{0}$.
-The advantage of $\tilde H$ being unitarily connected to $H^H$ is that they will have the same single-particle Greens functions.
+The advantage of $\tilde H$ being connected to $H^H$ through unitary (or atleast similarity) transformations is that they will have the same single-particle Greens functions
 \begin{equation}\begin{aligned}
@@
 															&=-i\theta(t)\bra{\tilde 0}\left\{\tilde c_{i\sigma} \tilde c^\dagger_{j\sigma} + \tilde c^\dagger_{j\sigma} \tilde c_{i\sigma} \right\}\ket{\tilde 0}\\
-															&= \left(\tilde G\right)_{\tilde {i\sigma} \tilde {j\sigma}}(t)
+															&= \left(\tilde G\right)_{\tilde {i\sigma} \tilde {j\sigma}}(t)~.
 \end{aligned}\end{equation}
@@
 We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.
-\par\noindent
-While we have provided expressions for the single particle Greens functions of the $N$-site Hubbard model from their equivalent single particle Greens functions of the Hubbard dimer, we expect that eq.\eqref{green_eq_final} holds quite generally for the two-particle Greens function sector as well.
-We will provide these expressions at a later point in time.
 \section{Calculating $g_0$ and $g_1$ in practice}
@@
 \begin{itemize}
-	\item Since the full Hubbard model ground state wavefunctions are not readily available, one can, as the simplest approximation, assume the ground state has the form
+	\item[1.] Since the full Hubbard model ground state wavefunctions are not readily available, one can, as the simplest approximation, assume the ground state has the form
 	\begin{equation}\begin{aligned}
@@
 	$\ket{\Phi^D_{ij}}$ would be the ground state of the Hubbard dimer with $i,j$ creating the two sites of the dimer, while $\ket{\Psi_{\hat i, \hat j}}$ would be the wavefunction involving the rest of the sites.
-This ofcourse assumes that the two sets $(i,j)$ and $(a,b,...,h,k,...)$ are not entangled, and is not true in general.
+This of course assumes that the two sets $(i,j)$ and $(a,b,...,h,k,...)$ are not entangled, and is not true in general.
 With this assumption, $g_0$ and $g_1$ become related to the inverse Greens functions of the Hubbard dimer.
 Such a choice of the wavefunction is motivated by the fact that in the auxiliary system we chose, the bath had only a diagonal interaction; there was no off-diagonal two particle scattering term.
-It further enforced when we extract the zero mode of the entire bath and keep just the zeroth site.
+It is further enforced when we extract the zero mode of the entire bath (i.e., we keep just the zeroth site).
 The zeroth site, along with the impurity, then forms the $\ket{\Phi}$ part of the wavefunction.
-	\item Another way of approaching this is to obtain the ground state wavefunction numerically, and then computing the matrix elements of $H^D$ against this wavefunction to obtain $g_0$ and $g_1$ for each value of $U^H$ and $t^H$ of the bare Hubbard model.
-This however means we lose any analytical insight into $g_0$ and $g_1$.
-	\item The overall best way of calculating $g_0$ and $g_1$ is by systematically improving the ground state wavefunctions.
-This can done by obtaining the wavefunction of a Hamiltonian that has not just for the dimer, but also a bath (with dispersion) that connects with both the sites of the dimer:
+This will allow for analytic insight, but at the cost of accuracy as discussed above.
+	\item[2.] Another way of approaching the problem is to obtain the ground state wavefunction of a Hubbard model numerically for several values of $U^H$ and $t^H$, and then computing the matrix elements of $H^D$ against this wavefunction to obtain a family of $(g_0,  g_1)$.
+This brings the numerical accuracy for a given finite-sized lattice realisation of the Hubbard model.
+However, this also means we lose any analytical insight into the structure of $g_0$ and $g_1$.
+	\item[3.] The most promising approach of calculating $g_0$ and $g_1$ is by systematically improving the required ground state wavefunctions as follows.
+We obtain numerically the ground state wavefunction of a Hamiltonian that has not just the Hubbard dimer, but also a bath (with dispersion) that connects to both the sites of the dimer:
 \begin{equation}\begin{aligned}
@@
 \end{figure}
-\\\\
-By systematically increasing the number of nearest neighbours, we can get better and better ground state wavefunctions, with which we can compute matrix elements, and hence $g_0$, $g_1$.
-What this means is that if we had just a Hubbard dimer wavefunction, then the impurity can at most hop onto its nearest neighbour, and then hop back, hence the wavefunction in eq.~\ref{guess}.
-However, with this additional hopping, the impurity can now now hop on to the nearest neighbour $z$, and then on to the next nearest neighbours.
-This leads to entanglement between the impurity site and the next nearest neighbour sites, which was missing in eq.~\ref{guess}.
-The introduction of the dispersion gives the hope that we can capture a spectral function of the three peak form, because we have previously seen such a spectral function in the fixed point of the URG analysis of the SIAM (the fixed point Hamiltonian was an Anderson molecule with dispersion).
-\item Another improvement can be made by introducing a self-energy into the dispersion.
-This introduces correlation on sites beyond the impurity and its nearest neighbour.
-The Hamiltonian would be the same as eq.~\ref{dimer_dispersion}, with $\epsilon_k$ replaced by $\tilde \epsilon_k \equiv \epsilon_k + \Sigma(k,\omega)$.
-The self-energy $\Sigma$ will have to be chosen depending on the phase we want to look at.
+\par\noindent
+By systematically increasing the number of momentum states in the bath dispersion, we can systematically improve the numerical computation of the ground state wavefunction.
+From here, we can compute matrix elements of $H^{D}$, and hence the functions $g_0$ and $g_1$.
+The presence of the bath can be understood as follow.
+In the absence of a bath, i.e., we have just a Hubbard dimer, an electron can at most hop between the two sites and lead to the wavefunction in eq.~\ref{guess}.
+However, with a single particle hopping term connecting the dimer to a bath, an electron can also journey between the two sites of the bath via the bath.
+This leads to entanglement between the dimer's sites and those in the bath; this was clearly ignored in the ground state wavefunction eq.~\ref{guess}.
+The introduction of the bath dispersion offers the possibility that we can capture a site diagonal spectral function of the three peak form, because we have previously seen such a spectral function in the fixed point of the URG analysis of the SIAM (where the fixed point effective Hamiltonian was an Anderson molecule with dispersion).
+If this can be found, then a metal-insulator transition of the full Hubbard model can perhaps be captured by studying the spectral functions of the bath-coupled Hubbard dimer.
+\item[4.] Another improvement can be made by introducing a self-energy $\Sigma (k,\omega)$ into the bath dispersion.
+This introduces correlation within the bath.
+The Hamiltonian that we would need to solve would be the same as eq.~\ref{dimer_dispersion}, but with $\epsilon_k$ replaced by $\tilde \epsilon_k \equiv \epsilon_k + \Sigma(k,\omega)$.
+The self-energy $\Sigma (k,\omega)$ will have to be chosen depending on the phase we want to look at (e.g., metal, insulator etc.).
 With a $\Sigma$ that is singular near the Fermi surface at $\omega \to 0$, the dispersion will become gapped and the phase will be insulating.
-In such a situation, eq.~\ref{guess} will be a very good approximation to the actual ground state.
-On the other hand, if we use a self energy that vanishes near the Fermi surface ($\Sigma(\omega) \sim \omega^2$), then we will end up in a metallic phase.
+In such a situation, there are no low-energy bath excitations within a given energy window proximate to its putative Fermi energy.
+This will localise the bath electrons, as well as confine all journeys between the two sites of the dimer to only the direct path.
+This is an indication of the localisation of electrons in the Hubbard model to holon-doublon excitations on nearest neighbour sites.
+In such a circumstance, eq.~\ref{guess} will be a very good approximation to the actual insulating ground state of the Hubbard model.
+On the other hand, if we use a self energy that vanishes near the Fermi surface ($\Sigma(\omega) \sim \omega^2$, i.e., a Fermi liquid bath), then we expect to end up in a metallic phase of the Hubbard model.
+This is simply due to the possibility of holons and doublons now dispersing throughout the lattice, and be concomitant with the presence of a pole in the single-particle Greens function $G(k,\omega)$ of the Hubbard model.
 Introducing the self energy therefore gives us a larger variety of wavefunctions and features to work with.
+Further, this appears to be in line with the original proposals offered by Mott and Kohn for the Mott metal insulator transition as the localisation-delocalisation transition of holon-doublon pairs.
+With regards to the transition itself, the precise form of the bath $\Sigma (k,\omega)$ (or spectral function) remains to be determined.
 \end{itemize}
+\section{Future goals}
+\begin{itemize}
+\item[1.] Obtain the metal insulator transition of the 2D Hubbard model on the square lattice from our formalism.
+Compare with what is obtained from DMFT and its improvements.
+Also, determine the nature of the bath $\Sigma (k,\omega)$ for the transition point.
+\item[2.] While we have provided expressions for the single particle Greens functions of the $N$-site Hubbard model from their equivalent single particle Greens functions of the Hubbard dimer, we expect that eq.\eqref{green_eq_final} holds quite generally for the two-particle Greens function sector as well.
+We will provide these expressions at a later point in time.
+\item[3.] Study various other models of strong correlation with this approach:~(i) 
+\end{itemize}
+
 \newpage

### 2021-08-12 notes.tex
improved the dimer bath figure

@@
 The expressions for $g_0$ and $g_1$, as mentioned above, involve taking matrix elements of the Hubbard dimer Hamiltonian against the exact wavefunctions of the full Hubbard model.
-\begin{itemize}
-	\item[1.] Since the full Hubbard model ground state wavefunctions are not readily available, one can, as the simplest approximation, assume the ground state has the form
+\begin{enumerate}
+	\item Since the full Hubbard model ground state wavefunctions are not readily available, one can, as the simplest approximation, assume the ground state has the form
 	\begin{equation}\begin{aligned}
@@
 This will allow for analytic insight, but at the cost of accuracy as discussed above.
-	\item[2.] Another way of approaching the problem is to obtain the ground state wavefunction of a Hubbard model numerically for several values of $U^H$ and $t^H$, and then computing the matrix elements of $H^D$ against this wavefunction to obtain a family of $(g_0,  g_1)$.
+	\item Another way of approaching the problem is to obtain the ground state wavefunction of a Hubbard model numerically for several values of $U^H$ and $t^H$, and then computing the matrix elements of $H^D$ against this wavefunction to obtain a family of $(g_0,  g_1)$.
 This brings the numerical accuracy for a given finite-sized lattice realisation of the Hubbard model.
 However, this also means we lose any analytical insight into the structure of $g_0$ and $g_1$.
-	\item[3.] The most promising approach of calculating $g_0$ and $g_1$ is by systematically improving the required ground state wavefunctions as follows.
+	\item The most promising approach of calculating $g_0$ and $g_1$ is by systematically improving the required ground state wavefunctions as follows.
 We obtain numerically the ground state wavefunction of a Hamiltonian that has not just the Hubbard dimer, but also a bath (with dispersion) that connects to both the sites of the dimer:
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{./dimer_dispersion.png}
+	\includegraphics[width=0.4\textwidth]{./dimer_dispersion.png}
 	\caption{Hubbard dimer with dispersion that connects to both sites}
@@
 If this can be found, then a metal-insulator transition of the full Hubbard model can perhaps be captured by studying the spectral functions of the bath-coupled Hubbard dimer.
-\item[4.] Another improvement can be made by introducing a self-energy $\Sigma (k,\omega)$ into the bath dispersion.
+\item Another improvement can be made by introducing a self-energy $\Sigma (k,\omega)$ into the bath dispersion.
 This introduces correlation within the bath.
@@
 With regards to the transition itself, the precise form of the bath $\Sigma (k,\omega)$ (or spectral function) remains to be determined.
-\end{itemize}
+\end{enumerate}
 \section{Future goals}
-\begin{itemize}
+\begin{enumerate}
 \item[1.] Obtain the metal insulator transition of the 2D Hubbard model on the square lattice from our formalism.
@@
 \item[3.] Study various other models of strong correlation with this approach:~(i) 
-\end{itemize}
+\end{enumerate}
 

### 2021-08-13 notes.tex
obtained relations between dimer and parent Hubbard parameters; the scaling with N is such that both the parent and the renormalized hubbard parameters scale similarly with N$

@@
 \title{Generating Hubbard Model Solutions from Anderson Impurity Model Solutions}
-\author{}%Abhirup Mukherjee, Dr. Siddhartha Lal}
+\author{Abhirup Mukherjee, Dr. Siddhartha Lal}
 \begin{document}
@@
 \end{aligned}\end{equation}
-
+With some knowledge of the RG procedure, one can even write down the relation between the Hubbard dimer couplings $t^D, U^D$ and the parent Hubbard model parameters $t^H, U^H$.
+We have seen previously in another work that in the absence of any explicit spin or charge isospin exchange couplings, the impurity-bath hybridisation coupling $t^A$ does not flow under the RG.
+In going from the Hubbard model to the auxiliary model, we replace the non-local operator $c_i$ with the local operator $c_d$.
+If we define the normalization of the Fourier transform such that both spaces have $\frac{1}{\sqrt N}$, then the auxiliary model coupling can be written as $t^A = \sqrt N t^H$.
+When we write the fixed-point hopping purely in terms of zero mode, another such factor appears: $\sum_k c_k = \sqrt N c_0$, such that $t^D = \sqrt N (t^A)*$.
+Combining these, we get
+\[ t^D = \sqrt N \times (t^A)^* = \sqrt N \times t^A = N \times t^H \]
+As for the on-site repulsion $U^H$, we will constrain the RG flows such that the fixed-point value of the impurity ons-te repulsion $U^A$ is identical to that of the on-site repulsion of the bath, $U_b$.
+A sensible choice for the bath on-site repulsion is simply $U^H\times N$.
+The factor of $N$ maintains the extensivity of the bath correlation term.
+We can therefore write
+\[U^D \equiv (U^A)* = U_b = N \times U^H\]
 \section{Formal expressions for single particle Greens functions and other related many-body quantites}
@@
 \begin{enumerate}
-\item[1.] Obtain the metal insulator transition of the 2D Hubbard model on the square lattice from our formalism.
+\item Obtain the metal insulator transition of the 2D Hubbard model on the square lattice from our formalism.
 Compare with what is obtained from DMFT and its improvements.
 Also, determine the nature of the bath $\Sigma (k,\omega)$ for the transition point.
-\item[2.] While we have provided expressions for the single particle Greens functions of the $N$-site Hubbard model from their equivalent single particle Greens functions of the Hubbard dimer, we expect that eq.\eqref{green_eq_final} holds quite generally for the two-particle Greens function sector as well.
+\item While we have provided expressions for the single particle Greens functions of the $N$-site Hubbard model from their equivalent single particle Greens functions of the Hubbard dimer, we expect that eq.\eqref{green_eq_final} holds quite generally for the two-particle Greens function sector as well.
 We will provide these expressions at a later point in time.
-\item[3.] Study various other models of strong correlation with this approach:~(i) 
+\item Study various other models of strong correlation with this approach:
+	\begin{enumerate}
+		\item Heisenberg model, by starting from a Kondo model effective Hamiltonian
+		\item Periodic Anderson model, by starting from a SIAM with a dispersive bath
+		\item Periodic Kondo model, by starting from a Kondo model with a dispersive bath
+		\item Hubbard-Heisenberg model, by starting from a generalized Anderson molecule (Anderson molecule with two-particle spin and charge interactions between the two sites)
+	\end{enumerate}
 \end{enumerate}

### 2021-08-14 notes.tex
updated list of future goals after the discussion with Arghya sir

@@
 Also, determine the nature of the bath $\Sigma (k,\omega)$ for the transition point.
+
+\item Once the zero temperature Mott metal-insulator transition is observed, we will investigate its nature.
+
 \item While we have provided expressions for the single particle Greens functions of the $N$-site Hubbard model from their equivalent single particle Greens functions of the Hubbard dimer, we expect that eq.\eqref{green_eq_final} holds quite generally for the two-particle Greens function sector as well.
 We will provide these expressions at a later point in time.
-\item Study various other models of strong correlation with this approach:
+More specifically, we will calculate the Greens functions for holon-doublon and spinon-spinon excitations as they are likely to contain more information regarding the ground state.
+
+\item It is also important to benchmark the ground state energy and double occupancy obtained from this method against the ground state wavefunction obtained from exact diagonalisation of small lattices and finite size scaling.
+
+\item It should also prove instructive to investigate the nature of many-particle entanglement in the ground state wavefunction of various phases, and  look for signs of a quantum liquid.
+
+\item Once we have a handle on the zero temperature features, we intend to compute Greens functions at non zero temperatures.
+
+\item This method can also be extended to various other models of strong correlation:
 	\begin{enumerate}

### 2021-08-16 notes.tex
added connection between single particle Greens function, and Greens function matrix, its not as simple as just taking matrix elements. Updated rest of notes to match this

@@
 \documentclass[12pt]{article}
-%\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
 \usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec,color}
@@
 \usepackage[T1]{fontenc}
-%\usepackage[hidelinks,pdfusetitle]{hyperref}
 \usepackage[pdfusetitle]{hyperref}
-\renewcommand{\arraystretch}{1.9}
+\renewcommand{\arraystretch}{2}
 \setlength\delimitershortfall{-2pt}
@@
 \subsection{Expressing matrix elements of the inverse single particle Greens function in terms of Hubbard dimer counterparts}
-If the groundstate wavefunction of $H^H$ is $\ket{0}$, then the groundstate wavefunction of $\tilde H$ is $\ket{\tilde 0} =  \mathcal{U}\ket{0}$.
+%If the groundstate wavefunction of $H^H$ is $\ket{0}$, then the groundstate wavefunction of $\tilde H$ is $\ket{\tilde 0} =  \mathcal{U}\ket{0}$.
 The advantage of $\tilde H$ being connected to $H^H$ through unitary (or atleast similarity) transformations is that they will have the same single-particle Greens functions
+%\begin{equation}\begin{aligned}
+%	\left(G_H\right)^\sigma_{\nu \nu^\prime}(t) \equiv -i\theta(t)\bra{0}\left\{c_{\nu},c^\dagger_{\nu^\prime} \right\}\ket{0} &= -i\theta(t)\bra{0} \mathcal{U}^{-1}\left\{  \mathcal{U} c_{\nu}  \mathcal{U}^{-1}  \mathcal{U} c^\dagger_{\nu^\prime}  \mathcal{U}^{-1} +  \mathcal{U} c^\dagger_{\nu^\prime}  \mathcal{U}^{-1}  \mathcal{U} c_{\nu}  \mathcal{U}^{-1}\right\} \mathcal{U}\ket{0}\\
+%															&=-i\theta(t)\bra{\tilde 0}\left\{\tilde c_{\nu} \tilde c^\dagger_{\nu^\prime} + \tilde c^\dagger_{\nu^\prime} \tilde c_{\nu} \right\}\ket{\tilde 0}\\
+%															&= \left(\tilde G\right)_{\tilde {\nu} \tilde {\nu^\prime}}(t)~.
+%\end{aligned}\end{equation}
+%This says that the Greens function $G_H$ of the bare Hubbard model $H^H$ for propagation of excitations (on top of its ground state $\ket{0}$) starting from $\ket{\nu^\prime} \equiv c^\dagger_{\nu^\prime}\ket{0}$ and ending at $\ket{\nu} \equiv c^\dagger_{\nu}\ket{0}$ is exactly equal to the Greens function $\tilde G$ of the renormalised Hamiltonian $\tilde H$ for propagation of the renormalised excitations (on top of its renormalised ground state $\ket{\tilde 0} =  \mathcal{U} \ket{0}$) starting from $\ket{\tilde {\nu^\prime}} \equiv \tilde c^\dagger_{\nu^\prime}\ket{\tilde 0} \equiv  \left(\mathcal{U} c^\dagger_{\nu^\prime}  \mathcal{U}^{-1}\right)  \mathcal{U}\ket{0} =  \mathcal{U}\ket{{\nu^\prime}}$ and ending at $\ket{\tilde \nu} \equiv \tilde c^\dagger_{\nu}\ket{\tilde 0}$.
+This means,
+%\begin{equation}\begin{aligned}
+%	\bra{\nu}G_H\ket{{\nu^\prime}} = \bra{\tilde {\nu}}\tilde G\ket{\tilde {\nu^\prime}}
+%\end{aligned}\end{equation}
+Since the two Hamiltonians $H^H$ and $\tilde H$ are connected via a similarity transformation $\mathcal{U}$, their ground states are also connected by the same transformation: $\ket{\tilde 0} = \mathcal{U}\ket{0}$.
+This means that matrix elements of the type in eq.~\ref{G_mat_el} will also be connected.
+The matrix elements are of the inverse Greebs function operator defined in eq.~\ref{inv_G_func}:
  \begin{equation}\begin{aligned}
-	\left(G_H\right)^\sigma_{ij}(t) \equiv -i\theta(t)\bra{0}\left\{c_{i\sigma},c^\dagger_{j\sigma} \right\}\ket{0} &= -i\theta(t)\bra{0} \mathcal{U}^{-1}\left\{  \mathcal{U} c_{i\sigma}  \mathcal{U}^{-1}  \mathcal{U} c^\dagger_{j\sigma}  \mathcal{U}^{-1} +  \mathcal{U} c^\dagger_{j\sigma}  \mathcal{U}^{-1}  \mathcal{U} c_{i\sigma}  \mathcal{U}^{-1}\right\} \mathcal{U}\ket{0}\\
-															&=-i\theta(t)\bra{\tilde 0}\left\{\tilde c_{i\sigma} \tilde c^\dagger_{j\sigma} + \tilde c^\dagger_{j\sigma} \tilde c_{i\sigma} \right\}\ket{\tilde 0}\\
-															&= \left(\tilde G\right)_{\tilde {i\sigma} \tilde {j\sigma}}(t)~.
+	 \mathcal{G}(\omega, H) = \frac{1}{\omega - (H - E_\text{GS})}
  \end{aligned}\end{equation}
-This says that the Greens function $G_H$ of the bare Hubbard model $H^H$ for excitations $\ket{{j\sigma}} \equiv c^\dagger_{j\sigma}\ket{0}$ on top of its ground state $\ket{0}$ is exactly equal to the Greens function $\tilde G$ of the renormalised Hamiltonian $\tilde H$ for renormalised excitations $\ket{\tilde {j\sigma}} \equiv \tilde c^\dagger_{j\sigma}\ket{\tilde 0} \equiv  \left(\mathcal{U} c^\dagger_i  \mathcal{U}^{-1}\right)  \mathcal{U}\ket{0} =  \mathcal{U}\ket{{j\sigma}}$ on top of its renormalised ground state $\ket{\tilde 0} =  \mathcal{U} \ket{0}$.
-This means,
+Its easy to see that the matrix elements of the original and renormalised versions of this operator, between the original and renormalised states, are equal:
 \begin{equation}\begin{aligned}
-	\bra{{i\sigma}}G_H\ket{{j\sigma}} = \bra{\tilde {i\sigma}}\tilde G\ket{\tilde {j\sigma}}
+	\left[\mathcal{G}_H^{-1}\right]_{\nu \nu^\prime} = \bra{\nu}\omega - H^H + E_\text{GS}\ket{\nu^\prime} = \bra{\nu} \mathcal{U}^{-1}\left(\omega -  \mathcal{U} H^H  \mathcal{U}^{-1} + E_\text{GS}\right)  \mathcal{U}\ket{\nu^\prime} = \bra{\tilde \nu}\left(\omega - \tilde H + E_\text{GS}\right)\ket{\tilde \nu^\prime}\\
+	= \left[\mathcal{\tilde G}^{-1}\right]_{\tilde \nu,\tilde \nu^\prime}
 \end{aligned}\end{equation}
-This same unitary connection also allows us to equate the inverse Greens functions:
+where we have defined the renormalised excitation $\ket{\tilde {\nu^\prime}} \equiv \tilde c^\dagger_{\nu^\prime}\ket{\tilde 0} \equiv  \left(\mathcal{U} c^\dagger_{\nu^\prime}  \mathcal{U}^{-1}\right)  \mathcal{U}\ket{0} =  \mathcal{U}\ket{{\nu^\prime}}$.
+importance of these equalities is that we can calculate these matrix elements for $\tilde H$, which will be equal to those of $H^H$, and once we have the matrix elements of $\mathcal{G}$, we can use them to obtain the single-particle Greens functions using eq.~\ref{G_mat_el}.
+More specifically, to calculate the real space single-particle Greens function between the lattice sites $i$ and $j$, both with spin $\sigma$, we will use the relation:
 \begin{equation}\begin{aligned}
-	\left[\left(G_H\right)^{-1}\right]^\sigma_{ij} = \bra{i\sigma}\omega - H^H\ket{j\sigma} = \bra{i\sigma} \mathcal{U}^{-1}\left(\omega -  \mathcal{U} H^H  \mathcal{U}^{-1}\right)  \mathcal{U}\ket{j\sigma} = \bra{\tilde i\sigma}\left(\omega - \tilde H\right)\ket{\tilde j\sigma} = \left[\left(\tilde G\right)^{-1}\right]^\sigma_{\tilde i,\tilde j}
+	G( i\sigma,  j\sigma, \omega) = \bra{ i\sigma} \mathcal{G}(\omega, H) \ket{ j\sigma} - \bra{\overline{i\sigma}} \mathcal{G}(-\omega, H) \ket{\overline {j\sigma}} = \mathcal{G}(\omega, H)_{ i\sigma, j\sigma} - \mathcal{G}(-\omega, H)_{\overline{i\sigma}, \overline {j\sigma}}
 \end{aligned}\end{equation}
-We will now see how we can use the Hubbard dimer expansion to get simple expressions for the inverse Greens functions of $\tilde H$, and hence $H^H$.
+where $\ket{i\sigma}=c^\dagger_{i\sigma}\ket{0}$ and $\ket{\overline{i\sigma}}=c_{i\sigma}\ket{0}$.
+We can see from the relation that we will need two types of matrix elements, one that propagates a particle excitation $\left( \ket{i\sigma} \right) $ and the one that propagates a hole excitation $\ket{\overline{i\sigma}}$.
 \\\\
-Equation \ref{H_tiled} can be rewritten in terms of inverse Greens functions.
+To this end, we rewrite eq.~\ref{H_tiled} in terms of inverse Greens function operators for the new (symmetrized) Hubbard model and the Hubbard dimer respectively:
+\begin{equation}\begin{aligned}
+	\mathcal{\tilde G}(\omega) = \frac{1}{\omega - \tilde H}, && \mathcal{G}_D(\omega) = \frac{1}{\omega - H^D}
+\end{aligned}\end{equation}
+\textit{It has been assumed that the Hamiltonians have been normal ordered such that the ground state energy is 0.} Then, these are the same operators that appear in the appendix.
 However, before proceeding, we should note that even though eq.~\ref{H_tiled} used the indices $i,$, the correct indices are actually $\tilde i, \tilde j$, in light of the fact that operators get renormalised as $c_i \to \tilde c_i\equiv Uc_i$.
@@
 	\label{green_eq}
-	\omega - \left(\tilde G\right)^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<\tilde i, \tilde j\right>}\left[\omega - G_D^{-1}\left(\tilde i, \tilde j\right)\right]
+	\omega - \mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<\tilde i, \tilde j\right>}\left[\omega - \mathcal{G}_D^{-1}\left(\tilde i, \tilde j\right)\right]
 \end{aligned}\end{equation}
-where $\tilde G$ and $G_D$ are the Greens functions for the new (symmetrized) Hubbard model and the Hubbard dimer respectively:
-\begin{equation}\begin{aligned}
-	\tilde G(\omega) = \frac{1}{\omega - \tilde H}, && G_D(\omega) = \frac{1}{\omega - H^D}
-\end{aligned}\end{equation}
+where $\mathcal{G}_D^{-1}(\tilde i,\tilde j)$ is the Greens function inverse matrix of the Hubbard dimer Hamiltonian with $\tilde i, \tilde j$ as the two sites.
 Since the $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, they can be pulled out along with a factor.
@@
 	\label{green_eq_final}
-	\left(\tilde G\right)^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}G_D^{-1}\left(\omega, \tilde i, \tilde j\right)
+	\mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}\mathcal{G}_D^{-1}\left(\omega, \tilde i, \tilde j\right)
 \end{aligned}\end{equation}
-where $G_D^{-1}(\tilde i,\tilde j,t^D,U^D)$ is the Greens function (matrix) of the Hubbard dimer Hamiltonian with $\tilde i, \tilde j$ as the two sites.
+We will now calculate the site-diagonal and site-off-diagonal matrix elements for particle propagation.
+The site-diagonal matrix element is calculated between the state $\ket{\tilde i, \sigma} = \mathcal{U}c^\dagger_{i\sigma}\ket{0}$ and its bra, while the off-diagonal one is between $\ket{\tilde j\sigma}$ and $\bra{\tilde i\sigma}$.
+Since it has already been shown that the matrix elements of the renormalised Hamiltonian are the same as those of the original Hamiltonian, we will directly replace the former with the latter.
 \\\\
-We will now calculate the single-particle site-diagonal and site-off-diagonal Greens functions.
-First lets consider the diagonal Greens function at $\tilde i^\text{th}$ site.
-We will extract this using the definition
-\begin{equation}\begin{aligned}
-	\left[\tilde G(\omega)^{-1}\right]^\sigma_{\tilde i \tilde i} = \bra{\tilde i\sigma}\tilde G(\omega)^{-1}\ket{\tilde i\sigma} = \bra{ i\sigma} G_H(\omega)^{-1}\ket{ i\sigma} = \left[G_H(\omega)^{-1}\right]^\sigma_{ii}
-\end{aligned}\end{equation}
-This means that we will take the matrix element of eq.~\ref{green_eq_final} between the excitations above the exact ground state of $\tilde H$, which is $\ket{\tilde i}$.
+First lets consider the diagonal matrix element at $\tilde i^\text{th}$ site.
 The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have $\tilde i$ in one of the indices.
@@
 Each term will be a real space local Greens function, and because of translational invariance, it will be the same on both sites.
-So we will represent the real space local inverse Greens function as $\left[G_D^{-1}(\omega)\right]_{00}^{\sigma}$.
+So we will represent the real space local inverse Greens function as $\left[\mathcal{G}_D^{-1}(\omega)\right]_{00}^{\sigma}$.
 The entire thing is thus $w$ times this local Greens function.
-\begin{equation}\begin{aligned}
+\begin{gather}
 	\label{local_gf}
-	\left(G_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]^\sigma_{00}\times w = \frac{2}{N}\left[G_{D}^{-1}(\omega)\right]^\sigma_{00} \equiv g_0
-\end{aligned}\end{equation}
-Now we come to the off-diagonal Greens function for the nearest neighbour sites $i$ and $j$.We will extract this using the definition
-\begin{equation}\begin{aligned}
-	\left[\tilde G(\omega)^{-1}\right]^\sigma_{\tilde i \tilde j} = \bra{\tilde i\sigma}\tilde G(\omega)^{-1}\ket{\tilde j\sigma} = \bra{ i\sigma} G_H(\omega)^{-1}\ket{j\sigma} = \left[G_H(\omega)^{-1}\right]^\sigma_{ij}
-\end{aligned}\end{equation}
-We will again take the matrix element of eq.~\ref{green_eq_final} between the excitations above the exact ground state of $\tilde H$.
+	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00}\times w = \frac{2}{N}\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00} \equiv g_0\\
+	\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00} = \bra{0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{0}
+\end{gather}
+Now we come to the off-diagonal Greens function for the nearest neighbour sites $i$ and $j$.We will extract this using the definition.
 This will receive contribution from only one nearest neighbour pair in the summation of the RHS of eq.~\ref{green_eq_final}, namely that of $\left(i,j\right)$.
@@
 Instead, it involves two nearest neighbour sites.
-We call this Greens function $\left[G_D^{-1}(\omega)\right]_{01}^\sigma$.
-\begin{equation}\begin{aligned}
+We call this Greens function $\left[\mathcal{G}_D^{-1}(\omega)\right]_{01}^\sigma$.
+\begin{gather}
 \label{nn_gf}
-	\left(G_{H}^{-1}(\omega)\right)_{ij}^\sigma &= \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01}^\sigma \equiv g_1
-\end{aligned}\end{equation}
+\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\left[\mathcal{G}_{D}^{-1}(\omega)\right]_{01}^\sigma \equiv g_1\\
+	\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{01} = \bra{0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{1\sigma}\ket{0}
+\end{gather}
 \begin{figure}[htpb!]
@@
 \end{figure}
+The matrix elements for hole propagation are obtained similarly:
+\begin{equation}\begin{aligned}
+	&\left(\mathcal{G}_{H}^{-1}(-\omega)\right)_{\overline{ii}}^\sigma = \frac{2}{N}\left[\mathcal{G}_{D}^{-1}(-\omega)\right]^\sigma_{\overline{00}} \equiv \overline{g_0}, &&&\left[\mathcal{G}_{D}^{-1}(-\omega)\right]^\sigma_{\overline{00}} = \bra{0}c^\dagger_{0\sigma}\mathcal{G}_{D}^{-1}(-\omega)c_{0\sigma}\ket{0}\\
+	&\left(\mathcal{G}_{H}^{-1}(-\omega)\right)_{\overline{ij}}^\sigma = \frac{2}{Nw}\left[\mathcal{G}_{D}^{-1}(-\omega)\right]_{\overline{01}}^\sigma \equiv \overline{g_1}, &&&\left[\mathcal{G}_{D}^{-1}(-\omega)\right]^\sigma_{\overline{01}} = \bra{0}c^\dagger_{0\sigma}\mathcal{G}_{D}^{-1}(-\omega)c_{1\sigma}\ket{0}
+\end{aligned}\end{equation}
+
 \subsection{Constructing full Greens function matrix from the inverse matrix via Fourier transformation to \(k-\)space}
-Since the only real-space interaction is that between the nearest neighbours, there are no further real space Greens functions, and the matrix $G^{-1}$ is tridiagonal in real space.
-Because of translational invariance, we know that $\left(G_H^{-1}\right)_{ii}$ and $\left(G_H^{-1}\right)_{ij}$ are independent of $i,j$.
+Since the only real-space interaction is that between the nearest neighbours, there are no further real space Greens functions.
+Because of translational invariance, we know that $\left(\mathcal{G}_H^{-1}\right)_{ii}$ and $\left(\mathcal{G}_H^{-1}\right)_{ij}$ are independent of $i,j$.
 Furthermore, all expressions below are for a particular spin $\sigma$; from the spin rotational symmetry of the Hubbard Hamiltonian, the same expressions are obtained for the opposite spin.
+We will now recreate the entire matrix $\mathcal{G_H}^{-1}$ using the matrix elements we calculated previously.
+Since the two sets $\left\{ \ket{i\sigma} \right\}$ and $\left\{ \ket{\overline{i\sigma}}\right\}$ are orthogonal, we will create separate matrix for the two sets.
 \begin{equation}\begin{aligned}
-	G^{-1}_H(\omega) = \begin{pmatrix} \left(G^{-1}\right)_{00} & \left(G^{-1}\right)_{01} & ... & ... & \left(G^{-1}\right)_{0N}\\
-		\left(G^{-1}\right)_{10} & \left(G^{-1}\right)_{11} & \left(G^{-1}\right)_{12} & ... & ...\\
-		... & \left(G^{-1}\right)_{21} & \left(G^{-1}\right)_{22} & \left(G^{-1}\right)_{23} & ... \\
-		    &&.&&\\
-		    &&.&&\\
+	\mathcal{G}^{-1}_H(\omega) = \begin{pmatrix} \left(\mathcal{G}^{-1}\right)_{00} & \left(\mathcal{G}^{-1}\right)_{01} & ... & ... & \left(\mathcal{G}^{-1}\right)_{0N}\\
+		\left(\mathcal{G}^{-1}\right)_{10} & \left(\mathcal{G}^{-1}\right)_{11} & \left(\mathcal{G}^{-1}\right)_{12} & ... & ...\\
+		... & \left(\mathcal{G}^{-1}\right)_{21} & \left(\mathcal{G}^{-1}\right)_{22} & \left(\mathcal{G}^{-1}\right)_{23} & ... \\
 		    &&.&&\\
@@
 		    &&...&&\\
+\end{pmatrix}\\
+		\overline{\mathcal{G}^{-1}_H}(-\omega) = \begin{pmatrix} \left(\mathcal{G}^{-1}\right)_{\overline{00}} & \left(\mathcal{G}^{-1}\right)_{\overline{01}} & ...
+& ...
+& \left(\mathcal{G}^{-1}\right)_{\overline{0N}}\\
+			\left(\mathcal{G}^{-1}\right)_{\overline{10}} & \left(\mathcal{G}^{-1}\right)_{\overline{11}} & \left(\mathcal{G}^{-1}\right)_{\overline{12}} & ... & ...\\
+			... & \left(\mathcal{G}^{-1}\right)_{\overline{21}} & \left(\mathcal{G}^{-1}\right)_{\overline{22}} & \left(\mathcal{G}^{-1}\right)_{\overline{23}} & ... \\
+		    &&.&&\\
+			\end{pmatrix} = \begin{pmatrix} \overline{g_0} & \overline{g_1} & ... & ... & \overline{g_1}\\
+			\overline{g_1} & \overline{g_0} & \overline{g_1} & ... & ...\\
+			... & \overline{g_1} & \overline{g_0} & \overline{g_1} & ... \\
 		    &&...&&\\
@@
 \end{aligned}\end{equation}
-It can be written in the operator form as
+Both the matrices can be written in the operator form of a tight-binding Hamiltonian:
 \begin{equation}\begin{aligned}
-	G_H^{-1}(\omega) = g_0\sum_{i=1}^N\ket{i}\bra{i} + g_1\sum_{\left<i,j \right>}^N\left( \ket{i}\bra{j} + \text{h.c.}\right)
+	\mathcal{G}_H^{-1}(\omega) = g_0\sum_{i=1}^N\ket{i}\bra{i} + g_1\sum_{\left<i,j \right>}^N\left( \ket{i}\bra{j} + \text{h.c.}\right)\\
+	\overline{\mathcal{G}_H^{-1}}(-\omega) = \overline{g_0}\sum_{\overline i=1}^N\ket{\overline i}\bra{\overline i} + \overline{g_1}\sum_{\left<\overline i,\overline j \right>}^N\left( \ket{\overline i}\bra{\overline j} + \text{h.c.}\right)
 \end{aligned}\end{equation}
@@
 \begin{flalign*}
-	\ket{i} &= \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\vec k} \Leftrightarrow \ket{k} = \frac{1}{\sqrt N}\sum_{\vec i} e^{-i \vec{k}\cdot\vec{r_i}}\ket{\vec r_i} \\
+	\ket{\vec r_i} &\equiv c^\dagger_{\vec r_i\sigma}\ket{0} = \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}c^\dagger_{k\sigma}\ket{0} \equiv \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\vec k} \Leftrightarrow \ket{k} = \frac{1}{\sqrt N}\sum_{\vec i} e^{-i \vec{k}\cdot\vec{r_i}}\ket{\vec r_i} \\
+	\ket{\overline{\vec r_i}} &\equiv c_{\vec r_i\sigma}\ket{0} = \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}c_{k\sigma}\ket{0} \equiv \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\overline{\vec k}} \Leftrightarrow \ket{\overline{\vec k}} = \frac{1}{\sqrt N}\sum_{\vec i} e^{-i \vec{k}\cdot\vec{r_i}}\ket{\overline{\vec r_i}}
+\end{flalign*}
+We will now Fourier transform the matrix $\mathcal{G}_H^{-1}(\omega)$ to momentum space. In doing so, we will diagonalize the matrix.
+\begin{flalign*}
 	\sum_i \ket{i}\bra{i} &= \frac{1}{N}\sum_i \sum_{\vec k, \vec q} e^{i \left(\vec{k} - \vec q\right)\cdot\vec{r_i}}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{\vec k, \vec q} N \delta\left(\vec{k} - \vec q\right)\ket{\vec k}\bra{\vec q} = \sum_{\vec k=\vec k_1}^{\vec k_N} \ket{\vec k}\bra{\vec k}\\
@@
 \begin{equation}\begin{aligned}
-G_H^{-1}(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)\ket{\vec k}\bra{\vec k} = \begin{pmatrix} g_0 + g_1\xi_{\vec k_1} &&& \\
+	\mathcal{G}_H^{-1}(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)\ket{\vec k}\bra{\vec k} = \begin{pmatrix} g_0 + g_1\xi_{\vec k_1} &&& \\
 	& g_0 + g_1\xi_{\vec k_2} && \\
@@
 \end{aligned}\end{equation}
-The matrix entries are written in momentum space, and the matrix is diagonal in this basis.
+The matrix entries are written in momentum space, and the matrix is diagonal in this basis. The other matrix can also be diagonalized similarly:
+\begin{equation}\begin{aligned}
+	\overline{\mathcal{G}_H^{-1}}(-\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)\ket{\overline{\vec k}}\bra{\overline{\vec k}} = \begin{pmatrix} \overline{g_0} + \overline{g_1}\xi_{\vec k_1} &&& \\
+	& \overline{g_0} + \overline{g_1}\xi_{\vec k_2} && \\
+	&& \overline{g_0} + \overline{g_1}\xi_{\vec k_3} & \\
+	...&...&...&\\
+	\end{pmatrix} 
+\end{aligned}\end{equation}
+
 \subsection{Calculation of self energy matrix from the Dyson equation}
@@
 \subsection{Obtaining real space Greens functions from the full matrix}
-Since $G_H^{-1}(\omega)$ is diagonal in this basis, we can invert the matrix trivially by replacing the diagonal elements with their reciprocals.
+Since ${\mathcal{G}_H^{-1}}(\omega)$ and $\overline{\mathcal{G}_H^{-1}}(\omega)$ are diagonal in momentum space, we can invert these matrices trivially by replacing the diagonal elements with their reciprocals.
 \begin{equation}\begin{aligned}
 	\label{k-space-gf}
-	G_H(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\ket{\vec k}\bra{\vec k} = \begin{pmatrix} \left(g_0 + g_1\xi_{\vec k_1}\right)^{-1} &&&&\\
+	\mathcal{G}_H(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\ket{\vec k}\bra{\vec k} = \begin{pmatrix} \left(g_0 + g_1\xi_{\vec k_1}\right)^{-1} &&&&\\
 	& \left(g_0 + g_1\xi_{\vec k_2}\right)^{-1} &&&\\
@@
 		...&&&...&\\
+	\end{pmatrix} \\
+		\overline{\mathcal{G}_H}(-\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\ket{\overline{\vec k}}\bra{\overline{\vec k}} = \begin{pmatrix} \left(\overline{g_0} + \overline{g_1}\xi_{\vec k_1}\right)^{-1} &&&&\\
+	& \left(\overline{g_0} + \overline{g_1}\xi_{\vec k_2}\right)^{-1} &&&\\
+	&& \left(\overline{g_0} + \overline{g_1}\xi_{\vec k_3}\right)^{-1} &&\\
+		...&&&...&\\
 	\end{pmatrix} 
 \end{aligned}\end{equation}
-The diagonal elements of $G_H$ in momentum space are simply $G_H(\vec k, \omega)$
+The diagonal elements of $\mathcal{G}_H$ in momentum space are:
 \begin{equation}\begin{aligned}
-	G_H(\vec k, \omega) &= \left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\\
+	\mathcal{G}(\omega, H^H)_{\vec k, \vec k} &= \left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\\
 			    &= \left\{\frac{2}{N}\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}\\
-			    &= \frac{N}{2}\left\{\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{1}{w}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}\\
+			    &= \frac{N}{2}\left\{\left[\mathcal{G}_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{1}{w}\left[\mathcal{G}_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}\\
+	\mathcal{G}(-\omega, H^H)_{\overline{\vec k}, \overline{\vec k}} &= \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\\
+									&= \frac{N}{2}\left\{\left[\mathcal{G}_{D}^{-1}(-\omega)\right]_{\overline{00}\sigma} + \frac{1}{w}\left[\mathcal{G}_{D}^{-1}(-\omega)\right]_{\overline{01}\sigma}\xi_{\vec k}\right\}^{-1}\\
 \end{aligned}\end{equation}
-The real-space Greens functions can now be obtained by taking matrix elements of the full Greens function matrix in eq.~\ref{k-space-gf}:
+\textit{The single-particle momentum space Greens function can now be written down}, following eq.~\ref{G_mat_el}:
 \begin{equation}\begin{aligned}
-	G_H(\vec r_i, \vec  r_j, \omega) \equiv \bra{\vec r_i} G_H(\omega) \ket{\vec r_j} = \sum_{\vec k} G_H(\vec k, \omega)  \left<\vec r_i | \vec k\right>\left<\vec k | \vec r_j\right>
+	G_H(\vec k, \omega) = \mathcal{G}(\omega, H^H)_{\vec k, \vec k} - \mathcal{G}(-\omega, H^H)_{\overline{\vec k}, \overline{\vec k}} = \left(g_0 + g_1 \xi_{\vec k}\right)^{-1} - \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}
 \end{aligned}\end{equation}
-From the definition of the Fourier transforms mentioned previously, we can write
+The real-space Greens functions can now be obtained by Fourier transforming $G_H(\vec k, \omega)$:
 \begin{equation}\begin{aligned}
-	\left<\vec r_i | \vec k\right> = \frac{1}{\sqrt N}\sum_{\vec r} e^{- \vec{k}\cdot\vec{r}} \left<\vec r_i | \vec r \right> = \frac{1}{\sqrt N}e^{- \vec{k}\cdot\vec{r_i}}
+	G_H(\vec r_i - \vec  r_j, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega)  e^{\vec{k}\cdot\left(\vec r_j - \vec{r_i}\right)} \equiv G_H(\vec r_j - \vec  r_i, \omega)
 \end{aligned}\end{equation}
-Substituting this gives
-\begin{equation}\begin{aligned}
-	G_H(\vec r_i, \vec  r_j, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega)  e^{\vec{k}\cdot\left(\vec r_j - \vec{r_i}\right)} \equiv G_H(\vec r_j - \vec  r_i, \omega)
-\end{aligned}\end{equation}
-The final expression brings out the fact that the Greens function for excitations between \(\vec r_i\) and \(\vec r_j\) depends only on the relative position \(\vec r_j - \vec r_i\), not on their absolute positions.
+The Greens function for excitations between \(\vec r_i\) and \(\vec r_j\) depends only on the relative position \(\vec r_j - \vec r_i\), not on their absolute positions.
 This is expected on grounds of translational invariance.
@@
 \begin{equation}\begin{aligned}
-	\left(G_H\right)_{ii}(\omega) \equiv G_H(\vec r_j - \vec  r_i = 0, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}
+	\left(G_H\right)_{ii}(\omega) \equiv G_H(\vec r_j - \vec  r_i = 0, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}\left(\frac{1}{g_0 + g_1 \xi_{\vec k}} - \frac{1}{\overline{g_0} + \overline{g_1} \xi_{\vec k}}\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{1}{\pi} \textrm{Im}\left[ (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right]\\
-A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = -\frac{1}{N\pi} \textrm{Im}\left[\sum_{\vec{k}} (g_{0} + g_{1}\xi_{\vec{k}})^{-1}\right] = -\frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
+A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{1}{\pi} \textrm{Im}\left[\left(g_0 + g_1 \xi_{\vec k}\right)^{-1} - \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\right]\\
+A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = -\frac{1}{N\pi} \textrm{Im}\sum_{\vec{k}}\left[\left(g_0 + g_1 \xi_{\vec k}\right)^{-1} - \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\right] = \frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
 \end{aligned}\end{equation}
@@
 	\label{hubb_dim_spectrum}
-	\begin{tabular}{|c|c|c|}
-	\hline
-	eigenstate & symbol & eigenvalue\\
-	\hline
-	\(\ket{0,0}\) & \(\ket{0}\) & \(\frac{U^A}{4}\)\\
-	\(a_1\left(U^A, t^A\right)\ket{\sigma,0} + a_2\left(U^A, t^A\right)\ket{0, \sigma}\) & \(\ket{0\sigma_-}\) & \(-\frac{1}{4}\Delta(U^A, t^A)\)\\
-	\(-a_2\left(U^A, t^A\right)\ket{\sigma,0} + a_1\left(U^A, t^A\right)\ket{0, \sigma}\) & \(\ket{0\sigma_+}\) & \(\frac{1}{4}\Delta(U^A, t^A)\)\\
-	\(\ket{\sigma,\sigma}\) & \(\ket{\sigma\sigma}\) & \(-\frac{U^A}{4}\)\\
-	\(\frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} + \ket{\downarrow, \uparrow}\right)\) & \(\ket{ST}\) & \(-\frac{U^A}{4}\)\\
-	\(\frac{1}{\sqrt 2}\left(\ket{2, 0} - \ket{0, 2}\right)\) & \(\ket{CS}\) & \(\frac{U^A}{4}\)\\
-	$a_1( \frac{1}{2}U^A, t^A) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_2( \frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{-}$ & \(-\frac{1}{2}\Delta( \frac{1}{2}U^A, t^A)\)\\
-	$-a_2(\frac{1}{2}U^A, t^A) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{+}$ & \(\frac{1}{2}\Delta(\frac{1}{2}U^A, t^A)\)\\
-	\(a_1\left(U^A, t^A\right)\ket{\sigma,2} - a_2\left(U^A, t^A\right)\ket{2, \sigma}\) & \(\ket{2\sigma_-}\) & \(-\frac{1}{4}\Delta(U^A, t^A)\)\\
-	\(a_2\left(U^A, t^A\right)\ket{\sigma,2} + a_1\left(U^A, t^A\right)\ket{2, \sigma}\) & \(\ket{2\sigma_+}\) & \(\frac{1}{4}\Delta(U^A, t^A)\)\\
-	\(\ket{2,2}\) & \(\ket{4}\) & \(\frac{U^A}{4}\)\\
-	\hline
-	\end{tabular}
-	\captionof{table}{Spectrum of Anderson molecule at particle-hole symmetry}
+%	\begin{tabular}{|c|c|c|}
+%	\hline
+%	eigenstate & symbol & eigenvalue\\
+%	\hline
+%	\(\ket{0,0}\) & \(\ket{0}\) & \(\frac{U^A}{4}\)\\
+%	\(a_1\left(U^A, t^A\right)\ket{\sigma,0} + a_2\left(U^A, t^A\right)\ket{0, \sigma}\) & \(\ket{0\sigma_-}\) & \(-\frac{1}{4}\Delta(U^A, t^A)\)\\
+%	\(-a_2\left(U^A, t^A\right)\ket{\sigma,0} + a_1\left(U^A, t^A\right)\ket{0, \sigma}\) & \(\ket{0\sigma_+}\) & \(\frac{1}{4}\Delta(U^A, t^A)\)\\
+%	\(\ket{\sigma,\sigma}\) & \(\ket{\sigma\sigma}\) & \(-\frac{U^A}{4}\)\\
+%	\(\frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} + \ket{\downarrow, \uparrow}\right)\) & \(\ket{ST}\) & \(-\frac{U^A}{4}\)\\
+%	\(\frac{1}{\sqrt 2}\left(\ket{2, 0} - \ket{0, 2}\right)\) & \(\ket{CS}\) & \(\frac{U^A}{4}\)\\
+%	$a_1( \frac{1}{2}U^A, t^A) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_2( \frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{-}$ & \(-\frac{1}{2}\Delta( \frac{1}{2}U^A, t^A)\)\\
+%	$-a_2(\frac{1}{2}U^A, t^A) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{+}$ & \(\frac{1}{2}\Delta(\frac{1}{2}U^A, t^A)\)\\
+%	\(a_1\left(U^A, t^A\right)\ket{\sigma,2} - a_2\left(U^A, t^A\right)\ket{2, \sigma}\) & \(\ket{2\sigma_-}\) & \(-\frac{1}{4}\Delta(U^A, t^A)\)\\
+%	\(a_2\left(U^A, t^A\right)\ket{\sigma,2} + a_1\left(U^A, t^A\right)\ket{2, \sigma}\) & \(\ket{2\sigma_+}\) & \(\frac{1}{4}\Delta(U^A, t^A)\)\\
+%	\(\ket{2,2}\) & \(\ket{4}\) & \(\frac{U^A}{4}\)\\
+%	\hline
+%	\end{tabular}
+%	\captionof{table}{Spectrum of Anderson molecule at particle-hole symmetry}
 \end{center}
@@
 
+ \section{Appendix: Relation between single-particle Greens function and the Greens function operator}
+ The single-particle Greens function is defined as the solution of the equation:
+ \begin{equation}\begin{aligned}
+	 \left(i\partial_t - H(\vec r)\right)G(\vec r,\vec r^\prime, t) = \delta(\vec r - \vec r^\prime)
+ \end{aligned}\end{equation}
+ and is given by the expression
+ \begin{equation}\begin{aligned}
+	 G(\vec r,\vec r^\prime, t) = -i \theta(t) \left< \left\{ c(\vec r, t) c^\dagger(\vec r^\prime, 0)\right\} \right>
+ \end{aligned}\end{equation}
+ This solution can be written in the Lehmann representation  and at $T=0$ as
+ \begin{equation}\begin{aligned}
+	 G(\vec r \sigma, \vec r^\prime \sigma, \omega) = \sum_{n}\left[\frac{\bra{GS}c({\vec r,\sigma})\ket{n}\bra{n}c^\dagger(\vec r^\prime,\sigma)\ket{GS}}{\omega + E_{GS} - E_n} + \frac{\bra{GS}c^\dagger(\vec r^\prime,\sigma)\ket{n}\bra{n}c({\vec r,\sigma})\ket{GS}}{\omega + E_n - E_{GS}}\right]
+ \end{aligned}\end{equation}
+ The sum is over the exact eigenstates of the Hamiltonian. In what follows, we will represent $\vec r,\sigma \equiv \nu$ and $\vec r^\prime,\sigma \equiv \nu^\prime$.
+ \begin{equation}\begin{aligned}
+	 G(\nu, \nu^\prime, \omega) &= \sum_{n}\left[\frac{\bra{GS}c(\nu)\ket{n}\bra{n}c^\dagger(\nu^\prime)\ket{GS}}{\omega + E_{GS} - E_n} + \frac{\bra{GS}c^\dagger(\nu^\prime)\ket{n}\bra{n}c(\nu)\ket{GS}}{\omega + E_n - E_{GS}}\right]\\
+							&= \bra{GS}c(\nu)\frac{1}{\omega + E_{GS} - H}c^\dagger(\nu^\prime)\ket{GS} + \bra{GS}c^\dagger(\nu^\prime)\frac{1}{\omega + H - E_{GS}}c(\nu)\ket{GS}\\
+ \end{aligned}\end{equation}
+ If we now define a Greens function operator
+ \begin{equation}\begin{aligned}
+	 \label{inv_G_func}
+	 \mathcal{G}(\omega, H) = \frac{1}{\omega - (H - E_\text{GS})}
+ \end{aligned}\end{equation}
+ we can write the single-particle Greens function as a sum of the matrix elements of this operator:
+ \begin{equation}\begin{aligned}
+	 \label{G_mat_el}
+	 G(\nu, \nu^\prime, \omega) = \bra{\nu} \mathcal{G}(\omega, H) \ket{\nu^\prime} - \bra{\overline\nu} \mathcal{G}(-\omega, H) \ket{\overline\nu^\prime} = \mathcal{G}(\omega, H)_{\nu,\nu^\prime} - \mathcal{G}(-\omega, H)_{\overline\nu, \overline\nu^\prime}
+ \end{aligned}\end{equation}
+ where we have defined the states $\ket{\nu} \equiv c^\dagger(\nu)\ket{GS}$ and $\ket{\overline\nu} \equiv c(\nu)\ket{GS}$
+
 \bibliographystyle{unsrt}

### 2021-08-17 notes.tex
corrected some typos in appendix

@@
 \newpage
-\section*{Appendix: Spectra of Hubbard dimer and Anderson molecule}
-%Here we document the spectra of the Hamiltonians in eqs.~\ref{hubb_dimer} and \ref{and_dimer}.
+\section*{Appendix: Spectra of Hubbard dimer}
+Here we document the spectrum of the Hamiltonian in eqs.~\ref{hubb_dimer}.
 \begin{center}
@@
 
- \section{Appendix: Relation between single-particle Greens function and the Greens function operator}
+ \section*{Appendix: Relation between single-particle Greens function and the Greens function operator}
  The single-particle Greens function is defined as the solution of the equation:

### 2021-08-17 notes.tex
corrected the real space dimer Greens function in appendix and also added the momentum space greens function

@@
 	\label{dimer_local_G}
-	G_{D,00}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} - t\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(\frac{\Delta}{2} + t\right) ^2} = G_{D,00}^\downarrow(\omega, T \to 0)~.
+	G_{D,00}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(t - \frac{\Delta}{2}\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(t + \frac{\Delta}{2}\right) ^2} = G_{D,00}^\downarrow(\omega, T \to 0)~.
 \end{aligned}\end{equation}
@@
 \label{dimer_intersite_G}
-	G_{D,01}^\uparrow(\omega, T \to 0) = \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{t}{(\omega +\frac{\Delta}{2})^2 - t^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{t}{(\omega -\frac{\Delta}{2})^2 - t^2} = G_{D,01}^\downarrow(\omega, T \to 0)~.
+G_{D,01}^\uparrow(\omega, T \to 0) = \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{t - \frac{\Delta}{2}}{\omega^2 - \left(t - \frac{\Delta}{2}\right)^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{t + \frac{\Delta}{2}}{\omega^2 - \left(t + \frac{\Delta}{2}\right)^2} = G_{D,01}^\downarrow(\omega, T \to 0)~.
 \end{equation}
-Once we have calculated the diagonal and off-diagonal matrix elements of the Greens function, we can compute the parameters $g_0$ and $g_1$:
+% Once we have calculated the diagonal and off-diagonal matrix elements of the Greens function, we can compute the parameters $g_0$ and $g_1$:
+% \begin{equation}\begin{aligned}
+%		 g_0 \equiv\frac{2}{N} (G^{-1}_{D})_{00} = \frac{2}{N} \frac{1}{\text{Det }G_D}\left(G_D\right)_{00}, g_1 \equiv\frac{2}{Nw} (G^{-1}_{D})_{00} = -\frac{2}{Nw}\frac{1}{\text{Det }G_D}\left(G_D\right)_{01}
+% \end{aligned}\end{equation}
+Using the diagonal and off-diagonal real space Greens functions, we can now compute the momentum-space Greens functions.
+The two momentum states are $ka = 0, \pi$.
+By Fourier transforming, these two Greens functions can be written as
 \begin{equation}\begin{aligned}
-		 g_0 \equiv\frac{2}{N} (G^{-1}_{D})_{00} = \frac{2}{N} \frac{1}{\text{Det }G_D}\left(G_D\right)_{00}, g_1 \equiv\frac{2}{Nw} (G^{-1}_{D})_{00} = -\frac{2}{Nw}\frac{1}{\text{Det }G_D}\left(G_D\right)_{01}
+	G(k=0, \sigma) = \sum_r e^{ikr} G(r, \sigma) = G(r=0, \sigma) + G(r=a, \sigma) = \frac{1/2 + 2t/\Delta}{\omega -t + \Delta/2} + \frac{1/2 - 2t/\Delta}{\omega - t - \Delta/2}\\
+	G(k=\pi, \sigma) = \sum_r e^{ikr} G(r, \sigma) = G(r=0, \sigma) - G(r=a, \sigma) = \frac{1/2 + 2t/\Delta}{\omega + t - \Delta/2} + \frac{1/2 - 2t/\Delta}{\omega + t + \Delta/2}\\
 \end{aligned}\end{equation}

### 2021-08-17 notes.tex
removed unnecessary parts and updated the dimer consistency part by calculating g0 and g1 from the GReens function of the dimer itself, because calculating them from the Hamiltonian itself does not seem to work

@@
 \begin{equation}\begin{aligned}
-	G( i\sigma,  j\sigma, \omega) = \bra{ i\sigma} \mathcal{G}(\omega, H) \ket{ j\sigma} - \bra{\overline{i\sigma}} \mathcal{G}(-\omega, H) \ket{\overline {j\sigma}} = \mathcal{G}(\omega, H)_{ i\sigma, j\sigma} - \mathcal{G}(-\omega, H)_{\overline{i\sigma}, \overline {j\sigma}}
+	G(i\sigma, j\sigma, \omega) = \bra{ i\sigma} \mathcal{G}(\omega, H) \ket{ j\sigma} - \bra{\overline{i\sigma}} \mathcal{G}(-\omega, H) \ket{\overline {j\sigma}} = \mathcal{G}(\omega, H)_{ i\sigma, j\sigma} - \mathcal{G}(-\omega, H)_{\overline{i\sigma}, \overline {j\sigma}}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\mathcal{\tilde G}(\omega) = \frac{1}{\omega - \tilde H}, && \mathcal{G}_D(\omega) = \frac{1}{\omega - H^D}
+	\label{Gd_op}
+	\mathcal{\tilde G}(\omega) = \frac{1}{\omega - \left(\tilde H - E_\text{GS}\right)}, && \mathcal{G}_D(\omega) = \frac{1}{\omega - \left(H^D - E_\text{GS}\right)}
 \end{aligned}\end{equation}
-\textit{It has been assumed that the Hamiltonians have been normal ordered such that the ground state energy is 0.} Then, these are the same operators that appear in the appendix.
+%\textit{It has been assumed that the Hamiltonians have been normal ordered such that the ground state energy is 0.} Then, these are the same operators that appear in the appendix.
+These are the same operators that appear in the appendix.
 However, before proceeding, we should note that even though eq.~\ref{H_tiled} used the indices $i,$, the correct indices are actually $\tilde i, \tilde j$, in light of the fact that operators get renormalised as $c_i \to \tilde c_i\equiv Uc_i$.
@@
 \begin{equation}\begin{aligned}
+	\label{hole_gf}
 	&\left(\mathcal{G}_{H}^{-1}(-\omega)\right)_{\overline{ii}}^\sigma = \frac{2}{N}\left[\mathcal{G}_{D}^{-1}(-\omega)\right]^\sigma_{\overline{00}} \equiv \overline{g_0}, &&&\left[\mathcal{G}_{D}^{-1}(-\omega)\right]^\sigma_{\overline{00}} = \bra{0}c^\dagger_{0\sigma}\mathcal{G}_{D}^{-1}(-\omega)c_{0\sigma}\ket{0}\\
@@
 \begin{equation}\begin{aligned}
+	\label{k_Gf}
 	G_H(\vec k, \omega) = \mathcal{G}(\omega, H^H)_{\vec k, \vec k} - \mathcal{G}(-\omega, H^H)_{\overline{\vec k}, \overline{\vec k}} = \left(g_0 + g_1 \xi_{\vec k}\right)^{-1} - \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}
@@
 We can again use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the spectral functions  $A_{H} (\vec{k},\omega)$ and $A_{H} (\vec{r}=0,\omega)$ for the Hubbard model on the 2D square lattice.
-\subsection{Obtaining \(g_0\) and \(g_1\)}
-These two quantities are expressed in terms of matrix elements of the inverse Greens function \(G_D^{-1}\) of the Hubbard dimer. Since \(G_D\) is a \(2\times 2\) matrix, it is easy to invert:
-\begin{equation}\begin{aligned}
-	G_D &= \begin{pmatrix} \left(G_D\right)_{00} &  \left(G_D\right)_{01} \\ \left(G_D\right)_{01} & \left(G_D\right)_{00}\end{pmatrix} \\
-	\implies G_D^{-1} &= \frac{1}{\text{Det }G_D}\begin{pmatrix} \left(G_D\right)_{00} &  -\left(G_D\right)_{01} \\ -\left(G_D\right)_{01} & \left(G_D\right)_{00}\end{pmatrix}\\
-		 \implies g_0 &\equiv\frac{2}{N} (G^{-1}_{D})_{00} = \frac{2}{N} \frac{1}{\text{Det }G_D}\left(G_D\right)_{00},\\
-		 g_1 &\equiv\frac{2}{Nw} (G^{-1}_{D})_{00} = -\frac{2}{Nw}\frac{1}{\text{Det }G_D}\left(G_D\right)_{01} 
-\end{aligned}\end{equation}
-Using the expressions for $(G_{D})_{00}$ and $(G_{D})_{01}$ shown in the appendix, we can obtain $g_{0}$ and $g_{1}$ very generally.
 
@@
 \subsection{Single-particle Greens function and self energy for the Hubbard dimer}
-The simplest test involves calculating \(G_H(\vec r = 0, \omega)\) for the Hubbard dimer \(\left(N = 2, w = 1 \right)\).
-The discrete set of momenta are \(\left\{ \vec k_n \right\} = 0, \frac{\pi}{a}\), so
+The simplest test involves choosing $H^H = H^D$ and then calculating the momentum space Greens function at $k=0$, $G(k=0, \sigma)$, for the Hubbard dimer \(\left(N = 2, w = 1 \right)\).
+The discrete set of momenta are \(\left\{ \vec k_n \right\} = 0, \frac{\pi}{a}\).
+For $k=0$, we have
 \begin{equation}\begin{aligned}
-	\left\{\xi_{\vec k}\right\} = 1, -1
+	\xi_{\vec k = 0} = 1
 \end{aligned}\end{equation}
-Therefore, the Greens function at $\vec r=0$ for the Hubbard dimer can be expressed as
+Substituting this into eq.~\ref{k_Gf} gives
 \begin{equation}\begin{aligned}
-	G_H(\vec r = 0, \omega) = \frac{1}{2}\left[\frac{1}{g_0 + g_1} + \frac{1}{g_0 - g_1}\right]  = \frac{g_0}{g_0^2 - g_1^2}
+	\label{Gk_dim}
+	G(k=0,\sigma) = \left(g_0 + g_1 \right)^{-1} - \left(\overline{g_0} + \overline{g_1} \right)^{-1}
 \end{aligned}\end{equation}
-For the Hubbard dimer, we substitute $N=2, w=1$ into the expressions for $g_{0}$ and $g_{1}$ to obtain
+We will now calculate $g_0$ and $g_1$ from the Greens function matrices of the Hubbard dimer. From the spectral representation of the Greens function matrix elements in eq.~\ref{G_mat_spec}, we obtain
 \begin{equation}\begin{aligned}
-	&g_0 = \frac{1}{\text{Det }G_D}\left( G_D \right)_{00}, &g_1 = -\frac{1}{\text{Det }G_D}\left( G_D \right)_{01}
+	\left(\mathcal{G}_D\right)_{\nu \nu^\prime} = \begin{pmatrix} x_- + y_- && x_- - y_- \\ x_- - y_- && x_- + y_- \end{pmatrix}
 \end{aligned}\end{equation}
-The Greens function at the zeroth site then becomes
+where
 \begin{equation}\begin{aligned}
-	G_H(\vec r = 0, \omega) = \text{Det }G_D\frac{\left(G_D\right)_{00}}{\left(G_D\right)_{00}^2 - \left(G_D\right)_{01}^2} = \text{Det }G_D\frac{\left(G_D\right)_{00}}{\text{Det }G_D} = \left(G_D\right)_{00}
+	x_\pm \equiv \left( \frac{1}{4} \pm \frac{t}{\Delta} \right) \frac{1}{\mp\omega - \frac{\Delta}{2} \pm t}, && y_\pm \equiv \left( \frac{1}{4} \mp \frac{t}{\Delta} \right) \frac{1}{\mp\omega - \frac{\Delta}{2} \mp t}
 \end{aligned}\end{equation}
-This is the expected result.
+The matrix is easily inverted:
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}_D^{-1}\right)_{\nu \nu^\prime}(\omega) = \frac{1}{4}\begin{pmatrix}  \frac{1}{x_-} + \frac{1}{y_-} &&  \frac{1}{x_-} - \frac{1}{y_-} \\  \frac{1}{x_-} - \frac{1}{y_-} &&  \frac{1}{x_-} + \frac{1}{y_-} \end{pmatrix}
+\end{aligned}\end{equation}
+$g_0$ and $g_1$ can now be read off:
+\begin{equation}\begin{aligned}
+	g_0 = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{00} = \frac{1}{4}\left( \frac{1}{x_-} + \frac{1}{y_-}\right), && g_1 = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{01} = \frac{1}{4}\left( \frac{1}{x_-} - \frac{1}{y_-}\right)
+\end{aligned}\end{equation}
+Similarly, we obtain the other matrix:
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}_D\right)_{\overline{\nu \nu^\prime}}(-\omega) = \begin{pmatrix} x_+ + y_+ && x_+ - y_+ \\ x_+ - y_+ && x_+ + y_+ \end{pmatrix}
+\end{aligned}\end{equation}
+which gives
+\begin{equation}\begin{aligned}
+	\overline{g_0} = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{00} = \frac{1}{4}\left( \frac{1}{x_+} + \frac{1}{y_+}\right), && \overline{g_1} = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{01} = \frac{1}{4}\left( \frac{1}{x_+} - \frac{1}{y_+}\right)
+\end{aligned}\end{equation}
+Substituting these values of $g_0, g_1, \overline{g_0}$ and $\overline{g_1}$ in eq.~\ref{Gk_dim} gives the same expression as that obtained in eq.~\ref{Gk0}.
+
+%To verify this result, we just need to show the momentum space Greens function of the Hubbard dimer calculated from the exact eigenstates (as shown in the appendix) also takes the same form.
+Using the Fourier transform, we can write
+%\begin{equation}\begin{aligned}
+%	G(k=0, \sigma) = G(r=0, \sigma) + G(r=a, \sigma)
+%\end{aligned}\end{equation}
+%The terms on the RHS are the real space local and nearest-neighbour Greens functions of the Hubbard dimer.
+%Therefore, the Greens function at $\vec r=0$ for the Hubbard dimer can be expressed as
+%\begin{equation}\begin{aligned}
+%	G_H(\vec r = 0, \omega) = \frac{1}{2}\left[\frac{1}{g_0 + g_1} + \frac{1}{g_0 - g_1}\right]  = \frac{g_0}{g_0^2 - g_1^2}
+%\end{aligned}\end{equation}
+%For the Hubbard dimer, we substitute $N=2, w=1$ into the expressions for $g_{0}$ and $g_{1}$ to obtain
+%\begin{equation}\begin{aligned}
+%	&g_0 = \frac{1}{\text{Det }G_D}\left( G_D \right)_{00}, &g_1 = -\frac{1}{\text{Det }G_D}\left( G_D \right)_{01}
+%\end{aligned}\end{equation}
+%The Greens function at the zeroth site then becomes
+%\begin{equation}\begin{aligned}
+%	G_H(\vec r = 0, \omega) = \text{Det }G_D\frac{\left(G_D\right)_{00}}{\left(G_D\right)_{00}^2 - \left(G_D\right)_{01}^2} = \text{Det }G_D\frac{\left(G_D\right)_{00}}{\text{Det }G_D} = \left(G_D\right)_{00}
+%\end{aligned}\end{equation}
+%This is the expected result.
 Because the full Hubbard model in this case was simply the Hubbard dimer, \(G_H(\vec r = 0, \omega)\) should just be \(\left(G_D\right)_{00}\).
@@
 We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.
+
 \section{Calculating $g_0$ and $g_1$ in practice}
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{./dimer_dispersion.png}
+	\includegraphics[width=0.2\textwidth]{./dimer_dispersion.png}
 	\caption{Hubbard dimer with dispersion that connects to both sites}
@@
 \end{enumerate}
+Once we have chosen a test Hamiltonian whose wavefunction we can calculate, we can use that to obtain the ground state energy of this state.
+The wavefunction will act as our $\ket{0}$ and the ground state energy will be our $E_\text{GS}$.
+We can then substitute these into the Lehmann representation form of the Greens function, and calculate the matrix elements $\mathcal{G}_D(\omega)_{\nu \nu^\prime}$ and $\mathcal{G}_D(-\omega)_{\overline{\nu \nu^\prime}}$ for the Hubbard dimer Hamiltonian.
+Each set will form a $2\times2$ matrix, and we can invert them to obtain $\mathcal{G}_D(\omega)$, and then the matrix elements of this inverted matrix will give all the parameters $g_0$ through $\overline{g_1}$.
 \section{Future goals}
@@
 \begin{equation}\begin{aligned}
+	\label{Gk0}
 	G(k=0, \sigma) = \sum_r e^{ikr} G(r, \sigma) = G(r=0, \sigma) + G(r=a, \sigma) = \frac{1/2 + 2t/\Delta}{\omega -t + \Delta/2} + \frac{1/2 - 2t/\Delta}{\omega - t - \Delta/2}\\
@@
 
- \section*{Appendix: Relation between single-particle Greens function and the Greens function operator}
+\section*{Appendix: Relation between single-particle Greens function and the Greens function operator $(T=0)$}
  The single-particle Greens function is defined as the solution of the equation:
@@
 	 \label{G_mat_el}
-	 G(\nu, \nu^\prime, \omega) = \bra{\nu} \mathcal{G}(\omega, H) \ket{\nu^\prime} - \bra{\overline\nu} \mathcal{G}(-\omega, H) \ket{\overline\nu^\prime} = \mathcal{G}(\omega, H)_{\nu,\nu^\prime} - \mathcal{G}(-\omega, H)_{\overline\nu, \overline\nu^\prime}
+	 G(\nu, \nu^\prime, \omega) = \bra{\nu} \mathcal{G}(\omega, H) \ket{\nu^\prime} - \bra{\overline{\nu^\prime}} \mathcal{G}(-\omega, H) \ket{\overline\nu} = \mathcal{G}(\omega, H)_{\nu,\nu^\prime} - \mathcal{G}(-\omega, H)_{\overline{\nu^\prime}, \overline\nu}
  \end{aligned}\end{equation}
- where we have defined the states $\ket{\nu} \equiv c^\dagger(\nu)\ket{GS}$ and $\ket{\overline\nu} \equiv c(\nu)\ket{GS}$
+ where we have defined the states $\ket{\nu} \equiv c^\dagger(\nu)\ket{GS}$ and $\ket{\overline\nu} \equiv c(\nu)\ket{GS}$.
+The two matrix elements can also be represented in their individual spectral representations:
+ \begin{equation}\begin{aligned}
+	 \label{G_mat_spec}
+ 	\mathcal{G}(\omega, H)_{\nu,\nu^\prime} = \sum_{n}\frac{\bra{GS}c(\nu)\ket{n}\bra{n}c^\dagger(\nu^\prime)\ket{GS}}{\omega + E_{GS} - E_n}\\
+	\mathcal{G}(\omega, H)_{\overline{\nu^\prime}, \overline\nu} = \sum_{n}\frac{\bra{GS}c^\dagger(\nu^\prime)\ket{n}\bra{n}c(\nu)\ket{GS}}{\omega + E_\text{GS} - E_n}
+ \end{aligned}\end{equation}
 

### 2021-08-19 notes.tex
added the dimer check calculuation (albeit in the non-orthogonal basis), also added a parallel calculation of G^inv_k from the spectrum of the dimer

@@
 \end{aligned}\end{equation}
-We can Fourier transform the real space basis kets $\ket{i} \equiv \ket{\vec r_i}$ into momentum space:
+We can Fourier transform the real space kets $\ket{i} \equiv \ket{\vec r_i}$ into momentum space:
 \begin{flalign*}
@@
 \subsection{Single-particle Greens function and self energy for the Hubbard dimer}
-The simplest test involves choosing $H^H = H^D$ and then calculating the momentum space Greens function at $k=0$, $G(k=0, \sigma)$, for the Hubbard dimer \(\left(N = 2, w = 1 \right)\).
+The simplest test involves choosing $H^H = H^D$ and then calculating the momentum space Greens function at $k=0$, $G(k=0, \uparrow)$, for the Hubbard dimer \(\left(N = 2, w = 1 \right)\).
 The discrete set of momenta are \(\left\{ \vec k_n \right\} = 0, \frac{\pi}{a}\).
@@
 	\label{Gk_dim}
-	G(k=0,\sigma) = \left(g_0 + g_1 \right)^{-1} - \left(\overline{g_0} + \overline{g_1} \right)^{-1}
+	G(k=0,\uparrow) = \left(g_0 + g_1 \right)^{-1} - \left(\overline{g_0} + \overline{g_1} \right)^{-1}
 \end{aligned}\end{equation}
-We will now calculate $g_0$ and $g_1$ from the Greens function matrices of the Hubbard dimer. From the spectral representation of the Greens function matrix elements in eq.~\ref{G_mat_spec}, we obtain
+We will now calculate the matrix elements $g_0$ and $g_1$ from the Hubbard dimer Hamiltonian. Those two parameters are defined as
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}_D\right)_{\nu \nu^\prime} = \begin{pmatrix} x_- + y_- && x_- - y_- \\ x_- - y_- && x_- + y_- \end{pmatrix}
+	g_0 \equiv \frac{2}{N}\bra{\text{GS}}c_{0\uparrow}\left(\omega + E_\text{GS} - H^D\right)c^\dagger_{0\uparrow}\ket{\text{GS}}\\
+	g_1 \equiv \frac{2}{N}\bra{\text{GS}}c_{0\uparrow}\left(\omega + E_\text{GS} - H^D\right)c^\dagger_{1\uparrow}\ket{\text{GS}}\\
 \end{aligned}\end{equation}
-where
+As a shorthand notation, we will use $\ket{0 \sigma} \equiv c^\dagger_{0\uparrow}\ket{\text{GS}}$.
+The matrix whose elements we want to calculate, $\omega + E_\text{GS} - H^D$, can be written as a diagonal matrix in the basis formed by the eigenstates in $N=3, S^z= \frac{1}{2}$ as defined in table \ref{hubb_dim_spectrum}:
 \begin{equation}\begin{aligned}
-	x_\pm \equiv \left( \frac{1}{4} \pm \frac{t}{\Delta} \right) \frac{1}{\mp\omega - \frac{\Delta}{2} \pm t}, && y_\pm \equiv \left( \frac{1}{4} \mp \frac{t}{\Delta} \right) \frac{1}{\mp\omega - \frac{\Delta}{2} \mp t}
+	\ket{\pm} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{\pm} = E_\pm \ket{\pm}
 \end{aligned}\end{equation}
-The matrix is easily inverted:
+In the basis of $\ket{\pm}$, we can write
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}_D^{-1}\right)_{\nu \nu^\prime}(\omega) = \frac{1}{4}\begin{pmatrix}  \frac{1}{x_-} + \frac{1}{y_-} &&  \frac{1}{x_-} - \frac{1}{y_-} \\  \frac{1}{x_-} - \frac{1}{y_-} &&  \frac{1}{x_-} + \frac{1}{y_-} \end{pmatrix}
+	\omega + E_\text{GS} - H^D &= \begin{pmatrix} \omega + E_\text{GS} - E_+ & 0 \\ 0 & \omega + E_\text{GS} - E_- \end{pmatrix}\\
+				   &= \left(\omega + E_\text{GS} - E_+\right) \ket{+}\bra{+} + \left(\omega + E_\text{GS} - E_-\right) \ket{-}\bra{-}
 \end{aligned}\end{equation}
-$g_0$ and $g_1$ can now be read off:
+The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates. As shown in the appendix, we can write
 \begin{equation}\begin{aligned}
-	g_0 = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{00} = \frac{1}{4}\left( \frac{1}{x_-} + \frac{1}{y_-}\right), && g_1 = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{01} = \frac{1}{4}\left( \frac{1}{x_-} - \frac{1}{y_-}\right)
+	\ket{0 \uparrow} \equiv c^\dagger_{0\uparrow}\ket{\text{GS}} =x\ket{+} + y\ket{-}, && \ket{1 \uparrow} \equiv c^\dagger_{1\uparrow}\ket{\text{GS}} = x\ket{+} - y\ket{-}
 \end{aligned}\end{equation}
-Similarly, we obtain the other matrix:
+with $x = \frac{a_2 - a_1}{2}, y=\frac{a_2 + a_1}{2}$. We can therefore express $\ket{\pm}$ in terms $\ket{0,1\uparrow}$:
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}_D\right)_{\overline{\nu \nu^\prime}}(-\omega) = \begin{pmatrix} x_+ + y_+ && x_+ - y_+ \\ x_+ - y_+ && x_+ + y_+ \end{pmatrix}
+	\ket{+} = \frac{1}{2x}\left(\ket{0 \uparrow} + \ket{1 \uparrow}\right), && \ket{-} = \frac{1}{2y}\left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)
 \end{aligned}\end{equation}
-which gives
+Substituting these into the operator form of $\omega + E_\text{GS} - H^D$ gives
 \begin{equation}\begin{aligned}
-	\overline{g_0} = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{00} = \frac{1}{4}\left( \frac{1}{x_+} + \frac{1}{y_+}\right), && \overline{g_1} = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{01} = \frac{1}{4}\left( \frac{1}{x_+} - \frac{1}{y_+}\right)
+	\omega + E_\text{GS} - H^D =& \frac{1}{4x^2}\left(\omega + E_\text{GS} - E_+\right) \left(\ket{0 \uparrow} + \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} + \bra{1 \uparrow}\right) \\
+				   &+ \frac{1}{4y^2}\left(\omega + E_\text{GS} - E_-\right) \left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} - \bra{1 \uparrow}\right)\\
+=& \begin{pmatrix}\left(\frac{1}{4x^2} + \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ - \frac{1}{4y^2}E_- & \left(\frac{1}{4x^2} - \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ + \frac{1}{4y^2}E_- \\ \left(\frac{1}{4x^2} - \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ + \frac{1}{4y^2}E_- & \left(\frac{1}{4x^2} + \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ - \frac{1}{4y^2}E_-\end{pmatrix}
 \end{aligned}\end{equation}
-Substituting these values of $g_0, g_1, \overline{g_0}$ and $\overline{g_1}$ in eq.~\ref{Gk_dim} gives the same expression as that obtained in eq.~\ref{Gk0}.
+Now we will Fourier transform to the diagonal momentum space: $\ket{0 \sigma} = \frac{1}{\sqrt 2}\left(\ket{{k_0} \sigma} + \ket{k_\pi \sigma} \right), \ket{1 \sigma} = \frac{1}{\sqrt 2}\left(\ket{{k_0} \sigma} - \ket{k_\pi \sigma} \right)$.
+\begin{equation}\begin{aligned}
+	\left(\ket{0 \uparrow} + \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} + \bra{1 \uparrow}\right) = 2\ket{k_0 \uparrow}\bra{k_0 \uparrow}\\
+	\left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} - \bra{1 \uparrow}\right) = 2\ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
+\end{aligned}\end{equation}
+This transformation can be substituted in the operator expansion:
+\begin{equation}\begin{aligned}
+	\omega + E_\text{GS} - H^D =& \frac{1}{2x^2}\left(\omega + E_\text{GS} - E_+\right) \ket{k_0 \uparrow}\bra{k_0 \uparrow} + \frac{1}{2y^2}\left(\omega + E_\text{GS} - E_-\right) \ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
+\end{aligned}\end{equation}
+This can be easily inverted:
+\begin{equation}\begin{aligned}
+	\frac{1}{\omega + E_\text{GS} - H^D} =& \frac{2x^2}{\omega + E_\text{GS} - E_+}\ket{k_0 \uparrow}\bra{k_0 \uparrow} + \frac{2y^2}{\omega + E_\text{GS} - E_-} \ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
+\end{aligned}\end{equation}
+Since this is already in the momentum space basis, we can write
+\begin{equation}\begin{aligned}
+	\left(\frac{1}{\omega + E_\text{GS} - H^D}\right)_{k_0 k_0} = \frac{2x^2}{\omega + E_\text{GS} - E_+}\ket{k_0 \uparrow}
+\end{aligned}\end{equation}
+Performing a similar calculation for the hole excitations will give
+\begin{equation}\begin{aligned}
+	\frac{1}{-\omega + E_\text{GS} - H^D} =& \frac{2y^2}{-\omega + E_\text{GS} - \overline{E_+}}\ket{\overline{k_0 \uparrow}}\bra{\overline{k_0 \uparrow}} + \frac{2x^2}{-\omega + E_\text{GS} - \overline{E_-}} \ket{\overline{k_\pi \uparrow}}\bra{\overline{k_\pi \uparrow}}\\
+\end{aligned}\end{equation}
+where $\ket{\overline{\nu}} \equiv c_\nu \ket{\text{GS}}$ and $\overline{E_\pm}$ are the eigenenergies of the $N=1, S^z = \frac{1}{2}$ sector eigenstates.
+From the spectrum, we know that $E_\pm = -\overline{E_\pm}$.\\\\
+Combining these two, we can obtain the $k=0$ Greens function of the Hubbard dimer:
+\begin{equation}\begin{aligned}
+	G(k=0, \uparrow) &= \left(\frac{1}{\omega + E_\text{GS} - H^D}\right)_{k_0 k_0} - \left(\frac{1}{-\omega + E_\text{GS} - H^D}\right)_{\overline{k_0 k_0}}\\
+			 &= \frac{2x^2}{\omega + E_\text{GS} - E_+} - \frac{2y^2}{-\omega + E_\text{GS} - \overline{E_+}}\\
+			 &= \frac{2x^2}{\omega + E_\text{GS} - E_+} + \frac{2y^2}{\omega - E_\text{GS} - E_+}\\
+\end{aligned}\end{equation}
+From the definitions of $x$ and $y$, we get $2x^2 = \frac{a_1^2 + a_2^2 - 2a_1 a_2}{2} = \frac{1}{2} - \frac{2t}{\Delta}$ and $2y^2 = \frac{1}{2} + \frac{2t}{\Delta}$.
+Also, the ground state energy is $E_\text{GS} = -\frac{\Delta}{2}$ and the excited energy $E_+$ is $t$.
+Substituting these gives
+\begin{equation}\begin{aligned}
+	G(k=0, \uparrow) &= \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} + \frac{\frac{1}{2} + \frac{2t}{\Delta}}{\omega + \frac{\Delta}{2} - t}\\
+\end{aligned}\end{equation}
+
+% from the Greens function matrices of the Hubbard dimer. From the spectral representation of the Greens function matrix elements in eq.~\ref{G_mat_spec}, we obtain
+% \begin{equation}\begin{aligned}
+% 	\left(\mathcal{G}_D\right)_{\nu \nu^\prime} = \begin{pmatrix} x_- + y_- && x_- - y_- \\ x_- - y_- && x_- + y_- \end{pmatrix}
+% \end{aligned}\end{equation}
+% where
+% \begin{equation}\begin{aligned}
+% 	x_\pm \equiv \left( \frac{1}{4} \pm \frac{t}{\Delta} \right) \frac{1}{\mp\omega - \frac{\Delta}{2} \pm t}, && y_\pm \equiv \left( \frac{1}{4} \mp \frac{t}{\Delta} \right) \frac{1}{\mp\omega - \frac{\Delta}{2} \mp t}
+% \end{aligned}\end{equation}
+% The matrix is easily inverted:
+% \begin{equation}\begin{aligned}
+% 	\left(\mathcal{G}_D^{-1}\right)_{\nu \nu^\prime}(\omega) = \frac{1}{4}\begin{pmatrix}  \frac{1}{x_-} + \frac{1}{y_-} &&  \frac{1}{x_-} - \frac{1}{y_-} \\  \frac{1}{x_-} - \frac{1}{y_-} &&  \frac{1}{x_-} + \frac{1}{y_-} \end{pmatrix}
+% \end{aligned}\end{equation}
+% $g_0$ and $g_1$ can now be read off:
+% \begin{equation}\begin{aligned}
+% 	g_0 = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{00} = \frac{1}{4}\left( \frac{1}{x_-} + \frac{1}{y_-}\right), && g_1 = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{01} = \frac{1}{4}\left( \frac{1}{x_-} - \frac{1}{y_-}\right)
+% \end{aligned}\end{equation}
+% Similarly, we obtain the other matrix:
+% \begin{equation}\begin{aligned}
+% 	\left(\mathcal{G}_D\right)_{\overline{\nu \nu^\prime}}(-\omega) = \begin{pmatrix} x_+ + y_+ && x_+ - y_+ \\ x_+ - y_+ && x_+ + y_+ \end{pmatrix}
+% \end{aligned}\end{equation}
+% which gives
+% \begin{equation}\begin{aligned}
+% 	\overline{g_0} = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{00} = \frac{1}{4}\left( \frac{1}{x_+} + \frac{1}{y_+}\right), && \overline{g_1} = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{01} = \frac{1}{4}\left( \frac{1}{x_+} - \frac{1}{y_+}\right)
+% \end{aligned}\end{equation}
+% Substituting these values of $g_0, g_1, \overline{g_0}$ and $\overline{g_1}$ in eq.~\ref{Gk_dim} gives the same expression as that obtained in eq.~\ref{Gk0}.
 
@@
 
+\section{Appendix: Writing single-particle excitations of ground state in terms of $N=3, S^z = \frac{1}{2}$ eigenstates}
+The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates $\ket{3\pm\uparrow}$ defined in table \ref{hubb_dim_spectrum}.
+\begin{equation}\begin{aligned}
+	\ket{\pm} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{\pm} = \pm t\ket{\pm}
+\end{aligned}\end{equation}
+In terms of these eigenstates, we can write
+\begin{equation}\begin{aligned}
+	c^\dagger_{0\uparrow}\ket{\text{GS}} 
+	&= c^\dagger_{0\uparrow}\left[a_1 \ket{SS} + a_2 \ket{CT}\right] \\
+	&= a_2 \frac{1}{\sqrt 2}\ket{\uparrow,2} - a_1 \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
+	&= \left(x + y\right) \frac{1}{\sqrt 2}\ket{\uparrow,2} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
+	&=x\ket{+} + y\ket{-}
+\end{aligned}\end{equation}
+where $x + y \equiv a_2$ and $x-y \equiv -a_1$. Similarly, for the other excitation, we can write
+\begin{equation}\begin{aligned}
+	c^\dagger_{1\uparrow}\ket{\text{GS}} 
+	&= c^\dagger_{1\uparrow}\left[a_1 \ket{SS} + a_2 \ket{CT}\right] \\
+	&= a_2 \frac{1}{\sqrt 2}\ket{2, \uparrow} - a_1 \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
+	&=  \left(x + y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
+	&=x\ket{+} - y\ket{-}
+\end{aligned}\end{equation}
+Solving for $x$ and $y$ gives
+\begin{equation}\begin{aligned}
+	x = \frac{a_2 - a_1}{2}, && y = \frac{a_2 + a_1}{2}
+\end{aligned}\end{equation}
+
+\section{Appendix: Matrix elements of $G^{-1}$ between single-particle momentum excitations, for the Hubbard dimer}
+\begin{equation}\begin{aligned}
+	G^{-1} \equiv \omega + E_\text{GS} - H_D
+\end{aligned}\end{equation}
+The particle excitation momentum space kets are $\ket{k_0} = \frac{1}{\sqrt 2}\left(\ket{0} + \ket{1}\right) ,\ket{k_\pi} = \frac{1}{\sqrt 2}\left(\ket{0} - \ket{1}\right)$. Therefore,
+\begin{equation}\begin{aligned}
+	\left(G^{-1}\right)_{k_0 k_0} &= \frac{1}{2}\left(\bra{0} + \bra{1}\right)\left(\omega + E_\text{GS} - H_D\right)\left(\ket{0} + \ket{1}\right)\\
+				      &= \frac{1}{2}\left(2x\bra{+}\right)\left(\omega + E_\text{GS} - H_D\right)\left(2x\ket{+}\right)\\
+				      &= 2x^2\left(\omega + E_\text{GS} - t\right)\\
+\end{aligned}\end{equation}
+At the final step, we used $\braket{+,+} = 1$ and $\braket{+|H_D|+} = t$.
 \bibliographystyle{unsrt}

### 2021-08-19 notes.tex
reformulated in terms of orthogonal states, rewrote all the formal part and started rewriting the dimer check part, currently hungry

@@
 Each term will be a real space local Greens function, and because of translational invariance, it will be the same on both sites.
-So we will represent the real space local inverse Greens function as $\left[\mathcal{G}_D^{-1}(\omega)\right]_{00}^{\sigma}$.
+%So we will represent the real space local inverse Greens function as $\left[\mathcal{G}_D^{-1}(\omega)\right]_{00}^{\sigma}$.
 The entire thing is thus $w$ times this local Greens function.
+% \begin{gather}
+% 	\label{local_gf}
+% 	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00}\times w = \frac{2}{N}\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00} \equiv g_0\\
+% 	\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00} = \bra{0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{0}
+% \end{gather}
 \begin{gather}
 	\label{local_gf}
-	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00}\times w = \frac{2}{N}\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00} \equiv g_0\\
-	\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00} = \bra{0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{0}
+	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\bra{0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{0}\times w = \frac{2}{N}\bra{0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{0}
 \end{gather}
+We can expand the state $c^\dagger_{0\sigma}\ket{0}$ and $c^\dagger_{1\sigma}\ket{0}$ in terms of a complete set of orthogonal states:
+\begin{equation}\begin{aligned}
+	c^\dagger_{0\sigma}\ket{0} = \sum_n C^0_n \ket{n}, && c^\dagger_{1\sigma}\ket{0} = \sum_n C^1_n \ket{n}%\sum_{m,\alpha,\beta} C^i_{m,\alpha,\beta} \ket{m,\alpha,\beta}
+\end{aligned}\end{equation}
+The index $n$ actually defines a set of quantum numbers that characterize the state $\ket{n}$.
+For example it might be a combination of number of particles, parity and total spin angular momentum $(n \equiv n, P, S^z)$.
+One simple way of choosing the orthogonal basis $\left\{ \ket{n} \right\}$ is to take them from the eigenstates of a system comprising a Hubbard dimer and a conduction bath, decoupled from each other.
+The set of eigenstates that have the total number of particles equal to $N+1$ will then form the basis in question.
+Since the dimer is decoupled from the bath, the total wavefunction will be a direct product of a Hubbard dimer wavefunction and a bath wavefunction.
+\begin{equation}\begin{aligned}
+	\ket{m,\alpha,\beta} = \Phi^D_{m,\alpha} \otimes \Psi^B_{N-m+1, \beta}
+\end{aligned}\end{equation}
+$\alpha$ is an internal quantum number of the Hubbard dimer while $\beta$ is that for the bath.
+The subscripts $m$ and $N-m+1$ label the total number of particles in each part of the wavefunction.
+These two labels have to add to $N+1$.
+Using this expansion, the matrix element of $\mathcal{G}$ can be written as
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{N}\sum_{nn^\prime} \left(C^0_{n^\prime}\right)^*\bra{n^\prime}\mathcal{G}_{D}^{-1}(\omega)\ket{n} C^0_{n}
+\end{aligned}\end{equation}
+Since the Hubbard dimer of the ket $\ket{n}$ is an actual eigenstate, $\mathcal{G}_{D}^{-1}(\omega)$ will be diagonal in that basis:
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{N}\sum_{n} |C^0_{n}|^2 \left(\mathcal{G}_{D}^{-1}(\omega)\right)_{n n} 
+\end{aligned}\end{equation}
 Now we come to the off-diagonal Greens function for the nearest neighbour sites $i$ and $j$.We will extract this using the definition.
@@
 Instead, it involves two nearest neighbour sites.
-We call this Greens function $\left[\mathcal{G}_D^{-1}(\omega)\right]_{01}^\sigma$.
+%We call this Greens function $\left[\mathcal{G}_D^{-1}(\omega)\right]_{01}^\sigma$.
 \begin{gather}
 \label{nn_gf}
-\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\left[\mathcal{G}_{D}^{-1}(\omega)\right]_{01}^\sigma \equiv g_1\\
-	\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{01} = \bra{0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{1\sigma}\ket{0}
+\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\bra{0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{1\sigma}\ket{0} = \frac{2}{Nw}\sum_{n} \left(C^0_{n}\right)^* C^1_{n} \left(\mathcal{G}_{D}^{-1}(\omega)\right)_{nn}
+%\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\left[\mathcal{G}_{D}^{-1}(\omega)\right]_{01}^\sigma \equiv g_1\\
+	%\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{01} = \bra{0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{1\sigma}\ket{0}
 \end{gather}
+For convenience, we define $g_n = \left(\mathcal{G}_{D}^{-1}(\omega)\right)_{nn}$.
 \begin{figure}[htpb!]
@@
 \end{figure}
-The matrix elements for hole propagation are obtained similarly:
+\\\\
+The matrix elements for hole propagation are obtained similarly.
+Here the relavant excitations are $\ket{\overline{i\sigma}} \equiv c_{i\sigma}\ket{0}$, at frequency $-\omega$.
+To expand these states, we choose the $N-1$ eigenstates as the orthonormal basis:
 \begin{equation}\begin{aligned}
-	\label{hole_gf}
-	&\left(\mathcal{G}_{H}^{-1}(-\omega)\right)_{\overline{ii}}^\sigma = \frac{2}{N}\left[\mathcal{G}_{D}^{-1}(-\omega)\right]^\sigma_{\overline{00}} \equiv \overline{g_0}, &&&\left[\mathcal{G}_{D}^{-1}(-\omega)\right]^\sigma_{\overline{00}} = \bra{0}c^\dagger_{0\sigma}\mathcal{G}_{D}^{-1}(-\omega)c_{0\sigma}\ket{0}\\
-	&\left(\mathcal{G}_{H}^{-1}(-\omega)\right)_{\overline{ij}}^\sigma = \frac{2}{Nw}\left[\mathcal{G}_{D}^{-1}(-\omega)\right]_{\overline{01}}^\sigma \equiv \overline{g_1}, &&&\left[\mathcal{G}_{D}^{-1}(-\omega)\right]^\sigma_{\overline{01}} = \bra{0}c^\dagger_{0\sigma}\mathcal{G}_{D}^{-1}(-\omega)c_{1\sigma}\ket{0}
+	c_{0\sigma}\ket{0} = \sum_n \overline C^0_n \ket{\overline{n}}, && c_{1\sigma}\ket{0} = \sum_n \overline C^1_n \ket{\overline{n}}%\sum_{m,\alpha,\beta} C^i_{m,\alpha,\beta} \ket{m,\alpha,\beta}
+\end{aligned}\end{equation}
+and the counterpart for $g_n$, here, is
+\begin{equation}\begin{aligned}
+	\overline {g_n} = \bra{\overline n}\mathcal{G}_{D}^{-1}(-\omega)\ket{\overline n}
+\end{aligned}\end{equation}
+By suitably replacing the symbols, we can write down the matrix elements of $\mathcal{G}_H^{-1}(-\omega)$ for hole propagation:
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}_{H}^{-1}(-\omega)\right)_{\overline{ii}}^\sigma &= \frac{2}{N}\sum_{n} |\overline C^0_{n}|^2 \overline{g_n}\\
+	\left(\mathcal{G}_{H}^{-1}(-\omega)\right)_{ij}^\sigma &= \frac{2}{Nw}\sum_{n} \left(\overline C^0_{n}\right)^* \overline C^1_{n} \overline{g_n} 
 \end{aligned}\end{equation}
 
+% \begin{equation}\begin{aligned}
+% 	\label{hole_gf}
+% 	&\left(\mathcal{G}_{H}^{-1}(-\omega)\right)_{\overline{ii}}^\sigma = \frac{2}{N}\left[\mathcal{G}_{D}^{-1}(-\omega)\right]^\sigma_{\overline{00}} \equiv \overline{g_0}, &&&\left[\mathcal{G}_{D}^{-1}(-\omega)\right]^\sigma_{\overline{00}} = \bra{0}c^\dagger_{0\sigma}\mathcal{G}_{D}^{-1}(-\omega)c_{0\sigma}\ket{0}\\
+% 	&\left(\mathcal{G}_{H}^{-1}(-\omega)\right)_{\overline{ij}}^\sigma = \frac{2}{Nw}\left[\mathcal{G}_{D}^{-1}(-\omega)\right]_{\overline{01}}^\sigma \equiv \overline{g_1}, &&&\left[\mathcal{G}_{D}^{-1}(-\omega)\right]^\sigma_{\overline{01}} = \bra{0}c^\dagger_{0\sigma}\mathcal{G}_{D}^{-1}(-\omega)c_{1\sigma}\ket{0}
+% \end{aligned}\end{equation}
+
 \subsection{Constructing full Greens function matrix from the inverse matrix via Fourier transformation to \(k-\)space}
-Since the only real-space interaction is that between the nearest neighbours, there are no further real space Greens functions.
+The matrix elements $\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma$ and its nearest neighbour partner can be obtained simply by inverting the internal matrix $\mathcal{G}^{-1}_D$.
+This is because,
+\begin{equation}\begin{aligned}
+	A_{ij} = \sum_{mn}\braket{i | n} A_{nm} \braket{m|j} \implies A^{-1}_{ij} = \sum_{mn}\braket{i|n} A^{-1}_{nm} \braket{m|j}
+\end{aligned}\end{equation}
+The spectral weights remain unchanged; only the matrix element changes from $A_nm$ to $(A^{-1})_{nm}$.
+Inverting the matrix $\mathcal{G}_D$ is actually simple because it is diagonal in the chosen basis:
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_D\right)_{nn} = \begin{pmatrix} g_{0} & 0 & & \\ 0 & g_{1} & & \\ && ..
+&  \\ &&& g_{M} \end{pmatrix} \implies \left(\mathcal{G}_D\right)_{nn} = \begin{pmatrix} \frac{1}{g_0} & 0 & \\ 0 & \frac{1}{g_1} & \\ && ...
+& \\ &&& \frac{1}{g_M}\end{pmatrix}
+\end{aligned}\end{equation}
+This allows us to write
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}_{H}(\omega)\right)_{ii}^\sigma = \frac{2}{N}\sum_{n} |C^0_{n}|^2 \frac{1}{g_n}, && \left(\mathcal{G}_{H}(-\omega)\right)_{\overline{ii}}^\sigma = \frac{2}{N}\sum_{n} |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}}
+\end{aligned}\end{equation}
+and
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\sum_{n} {C^0_{n}}^* C^1_{n} \frac{1}{g_n}, && \left(\mathcal{G}_{H}(-\omega)\right)_{\overline{ij}}^\sigma = \frac{2}{Nw}\sum_{n} {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}
+\end{aligned}\end{equation}
+These two expressions can be used to obtain an expression for the real space local and nearest-neighbour Greens functions:
+\begin{equation}\begin{aligned}
+	G_H(\omega)_\text{loc} &= \left(\mathcal{G}_H(\omega)\right)_{ii} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ii}} = \frac{2}{N}\sum_n\left(|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}}\right)\\
+	G_H(\omega)_\text{nn} &= \left(\mathcal{G}_H(\omega)\right)_{ij} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ji}} = \frac{2}{Nw}\sum_n\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\\
+\end{aligned}\end{equation}
+The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
+\begin{equation}\begin{aligned}
+	G_H (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_H (|\vec{r_i} - \vec {r_j}|, \omega)
+\end{aligned}\end{equation}
+where $\vec{r_i}$ is the position vector of a particular lattice site.
+Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites.
+As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
+As we do not have real space Greens function that are more non-local than nearest neighbour, we will attempt to obtain momentum space Greens function from these two contributions:
+\begin{equation}\begin{aligned}
+	G_H (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}G_H (\omega)_\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_H (\omega)_\text{nn}
+\end{aligned}\end{equation}
+The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, w\right]\right\}$.
+\begin{equation}\begin{aligned}
+	\label{k_Gf}
+	G_H (\vec k, \omega) &\simeq G_H (\omega)_\text{loc} + G_H (\omega)_\text{nn}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\\
+			     &= G_H (\omega)_\text{loc} + G_H (\omega)_\text{nn} \xi_{\vec k}\\
+			     &= \frac{2}{N}\sum_n\left[|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}} + \frac{\xi_{\vec{k}}}{w}\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\right]
+\end{aligned}\end{equation}
+where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\). For example, on a d-dimensional hypercubic lattice, we obtain
+\begin{equation}\begin{aligned}
+	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i
+\end{aligned}\end{equation}
+On a 2D square lattice with lattice spacing $a$, this simplifies to
+\begin{eqnarray}
+	\label{2dsquaretb}
+\xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
+\epsilon_{\vec{q}} &=& -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})~
+\end{eqnarray}
+where \(\epsilon_{\vec{q}}\) is the tight-binding dispersion.
+\\\\
+We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
+\begin{equation}\begin{aligned}
+	A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{2}{N\pi} \textrm{Im}\sum_n\left[|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}} + \frac{\xi_{\vec{k}}}{w}\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\right]\\
+A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = \frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
+\end{aligned}\end{equation}
+We can again use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the spectral functions  $A_{H} (\vec{k},\omega)$ and $A_{H} (\vec{r}=0,\omega)$ for the Hubbard model on the 2D square lattice.
+
+% Since the only real-space interaction is that between the nearest neighbours, there are no further real space Greens functions.
 Because of translational invariance, we know that $\left(\mathcal{G}_H^{-1}\right)_{ii}$ and $\left(\mathcal{G}_H^{-1}\right)_{ij}$ are independent of $i,j$.
@@
 Since the two sets $\left\{ \ket{i\sigma} \right\}$ and $\left\{ \ket{\overline{i\sigma}}\right\}$ are orthogonal, we will create separate matrix for the two sets.
-\begin{equation}\begin{aligned}
-	\mathcal{G}^{-1}_H(\omega) = \begin{pmatrix} \left(\mathcal{G}^{-1}\right)_{00} & \left(\mathcal{G}^{-1}\right)_{01} & ... & ... & \left(\mathcal{G}^{-1}\right)_{0N}\\
-		\left(\mathcal{G}^{-1}\right)_{10} & \left(\mathcal{G}^{-1}\right)_{11} & \left(\mathcal{G}^{-1}\right)_{12} & ... & ...\\
-		... & \left(\mathcal{G}^{-1}\right)_{21} & \left(\mathcal{G}^{-1}\right)_{22} & \left(\mathcal{G}^{-1}\right)_{23} & ... \\
-		    &&.&&\\
-\end{pmatrix} = \begin{pmatrix} g_0 & g_1 & ... & ... & g_1\\
-		g_1 & g_0 & g_1 & ... & ...\\
-		... & g_1 & g_0 & g_1 & ... \\
-		    &&...&&\\
-\end{pmatrix}\\
-		\overline{\mathcal{G}^{-1}_H}(-\omega) = \begin{pmatrix} \left(\mathcal{G}^{-1}\right)_{\overline{00}} & \left(\mathcal{G}^{-1}\right)_{\overline{01}} & ...
+% \begin{equation}\begin{aligned}
+% 	\mathcal{G}^{-1}_H(\omega) = \begin{pmatrix} \left(\mathcal{G}^{-1}\right)_{00} & \left(\mathcal{G}^{-1}\right)_{01} & ... & ... & \left(\mathcal{G}^{-1}\right)_{0N}\\
+% 		\left(\mathcal{G}^{-1}\right)_{10} & \left(\mathcal{G}^{-1}\right)_{11} & \left(\mathcal{G}^{-1}\right)_{12} & ... & ...\\
+% 		... & \left(\mathcal{G}^{-1}\right)_{21} & \left(\mathcal{G}^{-1}\right)_{22} & \left(\mathcal{G}^{-1}\right)_{23} & ... \\
+% 		    &&.&&\\
+% \end{pmatrix} = \begin{pmatrix} g_0 & g_1 & ... & ... & g_1\\
+% 		g_1 & g_0 & g_1 & ... & ...\\
+% 		... & g_1 & g_0 & g_1 & ... \\
+% 		    &&...&&\\
+% \end{pmatrix}\\
+% 		\overline{\mathcal{G}^{-1}_H}(-\omega) = \begin{pmatrix} \left(\mathcal{G}^{-1}\right)_{\overline{00}} & \left(\mathcal{G}^{-1}\right)_{\overline{01}} & ...
 & ...
 & \left(\mathcal{G}^{-1}\right)_{\overline{0N}}\\
-			\left(\mathcal{G}^{-1}\right)_{\overline{10}} & \left(\mathcal{G}^{-1}\right)_{\overline{11}} & \left(\mathcal{G}^{-1}\right)_{\overline{12}} & ... & ...\\
-			... & \left(\mathcal{G}^{-1}\right)_{\overline{21}} & \left(\mathcal{G}^{-1}\right)_{\overline{22}} & \left(\mathcal{G}^{-1}\right)_{\overline{23}} & ... \\
-		    &&.&&\\
-			\end{pmatrix} = \begin{pmatrix} \overline{g_0} & \overline{g_1} & ... & ... & \overline{g_1}\\
-			\overline{g_1} & \overline{g_0} & \overline{g_1} & ... & ...\\
-			... & \overline{g_1} & \overline{g_0} & \overline{g_1} & ... \\
-		    &&...&&\\
-\end{pmatrix} 
-\end{aligned}\end{equation}
-Both the matrices can be written in the operator form of a tight-binding Hamiltonian:
-\begin{equation}\begin{aligned}
-	\mathcal{G}_H^{-1}(\omega) = g_0\sum_{i=1}^N\ket{i}\bra{i} + g_1\sum_{\left<i,j \right>}^N\left( \ket{i}\bra{j} + \text{h.c.}\right)\\
-	\overline{\mathcal{G}_H^{-1}}(-\omega) = \overline{g_0}\sum_{\overline i=1}^N\ket{\overline i}\bra{\overline i} + \overline{g_1}\sum_{\left<\overline i,\overline j \right>}^N\left( \ket{\overline i}\bra{\overline j} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-We can Fourier transform the real space kets $\ket{i} \equiv \ket{\vec r_i}$ into momentum space:
-\begin{flalign*}
-	\ket{\vec r_i} &\equiv c^\dagger_{\vec r_i\sigma}\ket{0} = \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}c^\dagger_{k\sigma}\ket{0} \equiv \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\vec k} \Leftrightarrow \ket{k} = \frac{1}{\sqrt N}\sum_{\vec i} e^{-i \vec{k}\cdot\vec{r_i}}\ket{\vec r_i} \\
-	\ket{\overline{\vec r_i}} &\equiv c_{\vec r_i\sigma}\ket{0} = \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}c_{k\sigma}\ket{0} \equiv \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\overline{\vec k}} \Leftrightarrow \ket{\overline{\vec k}} = \frac{1}{\sqrt N}\sum_{\vec i} e^{-i \vec{k}\cdot\vec{r_i}}\ket{\overline{\vec r_i}}
-\end{flalign*}
-We will now Fourier transform the matrix $\mathcal{G}_H^{-1}(\omega)$ to momentum space. In doing so, we will diagonalize the matrix.
-\begin{flalign*}
-	\sum_i \ket{i}\bra{i} &= \frac{1}{N}\sum_i \sum_{\vec k, \vec q} e^{i \left(\vec{k} - \vec q\right)\cdot\vec{r_i}}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{\vec k, \vec q} N \delta\left(\vec{k} - \vec q\right)\ket{\vec k}\bra{\vec q} = \sum_{\vec k=\vec k_1}^{\vec k_N} \ket{\vec k}\bra{\vec k}\\
-	\sum_{\left<i,j \right>} \ket{i}\bra{j} &= \frac{1}{N}\sum_{\left<i,j \right>} \sum_{\vec k, \vec q} e^{i \left(\vec{k}\cdot \vec r_i - \vec q\cdot \vec r_j\right)}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\frac{1}{2}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec k, \vec q} e^{-i\vec q\cdot a_i\hat e_i}\ket{\vec k}\bra{\vec q}\sum_{i=1}^N e^{i \left(\vec{k} - \vec q\right)\cdot \vec r_i} & \left[\sum_{\left<i,j \right>} = \frac{1}{2}\sum_i \sum_{j \in \text{NN of i}}\right] \\
-					&=\frac{1}{2}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec q} e^{-i\vec q\cdot \vec e_i}\ket{\vec q}\bra{\vec q} = \frac{1}{2}\sum_{\vec q} \left(\sum_{i_1}^{D}e^{-ia_iq_i}\right)\ket{\vec q}\bra{\vec q}
-\end{flalign*}
-$\hat e_i$ are the primitive lattice unit vectors for the general $d-$dimensional lattice.
+% 			\left(\mathcal{G}^{-1}\right)_{\overline{10}} & \left(\mathcal{G}^{-1}\right)_{\overline{11}} & \left(\mathcal{G}^{-1}\right)_{\overline{12}} & ... & ...\\
+% 			... & \left(\mathcal{G}^{-1}\right)_{\overline{21}} & \left(\mathcal{G}^{-1}\right)_{\overline{22}} & \left(\mathcal{G}^{-1}\right)_{\overline{23}} & ... \\
+% 		    &&.&&\\
+% 			\end{pmatrix} = \begin{pmatrix} \overline{g_0} & \overline{g_1} & ... & ... & \overline{g_1}\\
+% 			\overline{g_1} & \overline{g_0} & \overline{g_1} & ... & ...\\
+% 			... & \overline{g_1} & \overline{g_0} & \overline{g_1} & ... \\
+% 		    &&...&&\\
+% \end{pmatrix} 
+% \end{aligned}\end{equation}
+% Both the matrices can be written in the operator form of a tight-binding Hamiltonian:
+% \begin{equation}\begin{aligned}
+% 	\mathcal{G}_H^{-1}(\omega) = g_0\sum_{i=1}^N\ket{i}\bra{i} + g_1\sum_{\left<i,j \right>}^N\left( \ket{i}\bra{j} + \text{h.c.}\right)\\
+% 	\overline{\mathcal{G}_H^{-1}}(-\omega) = \overline{g_0}\sum_{\overline i=1}^N\ket{\overline i}\bra{\overline i} + \overline{g_1}\sum_{\left<\overline i,\overline j \right>}^N\left( \ket{\overline i}\bra{\overline j} + \text{h.c.}\right)
+% \end{aligned}\end{equation}
+% We can Fourier transform the real space kets $\ket{i} \equiv \ket{\vec r_i}$ into momentum space:
+% \begin{flalign*}
+% 	\ket{\vec r_i} &\equiv c^\dagger_{\vec r_i\sigma}\ket{0} = \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}c^\dagger_{k\sigma}\ket{0} \equiv \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\vec k} \Leftrightarrow \ket{k} = \frac{1}{\sqrt N}\sum_{\vec i} e^{-i \vec{k}\cdot\vec{r_i}}\ket{\vec r_i} \\
+% 	\ket{\overline{\vec r_i}} &\equiv c_{\vec r_i\sigma}\ket{0} = \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}c_{k\sigma}\ket{0} \equiv \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\overline{\vec k}} \Leftrightarrow \ket{\overline{\vec k}} = \frac{1}{\sqrt N}\sum_{\vec i} e^{-i \vec{k}\cdot\vec{r_i}}\ket{\overline{\vec r_i}}
+% \end{flalign*}
+% We will now Fourier transform the matrix $\mathcal{G}_H^{-1}(\omega)$ to momentum space. In doing so, we will diagonalize the matrix.
+% \begin{flalign*}
+% 	\sum_i \ket{i}\bra{i} &= \frac{1}{N}\sum_i \sum_{\vec k, \vec q} e^{i \left(\vec{k} - \vec q\right)\cdot\vec{r_i}}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{\vec k, \vec q} N \delta\left(\vec{k} - \vec q\right)\ket{\vec k}\bra{\vec q} = \sum_{\vec k=\vec k_1}^{\vec k_N} \ket{\vec k}\bra{\vec k}\\
+% 	\sum_{\left<i,j \right>} \ket{i}\bra{j} &= \frac{1}{N}\sum_{\left<i,j \right>} \sum_{\vec k, \vec q} e^{i \left(\vec{k}\cdot \vec r_i - \vec q\cdot \vec r_j\right)}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\frac{1}{2}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec k, \vec q} e^{-i\vec q\cdot a_i\hat e_i}\ket{\vec k}\bra{\vec q}\sum_{i=1}^N e^{i \left(\vec{k} - \vec q\right)\cdot \vec r_i} & \left[\sum_{\left<i,j \right>} = \frac{1}{2}\sum_i \sum_{j \in \text{NN of i}}\right] \\
+% 					&=\frac{1}{2}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec q} e^{-i\vec q\cdot \vec e_i}\ket{\vec q}\bra{\vec q} = \frac{1}{2}\sum_{\vec q} \left(\sum_{i_1}^{D}e^{-ia_iq_i}\right)\ket{\vec q}\bra{\vec q}
+% \end{flalign*}
+% $\hat e_i$ are the primitive lattice unit vectors for the general $d-$dimensional lattice.
 $q_i$ are the projections of $\vec q$ along those vectors.
@@
 Adding the Hermitian conjugate simply extracts the real part:
-\begin{equation}\begin{aligned}
-	\sum_{\left<i,j \right>} \ket{i}\bra{j} + \text{h.c.} =\sum_{\vec q} \underbrace{\sum_{i_1}^{D}\cos\left(a_iq_i\right)}_{\equiv \xi_{\vec q}}\ket{\vec q}\bra{\vec q}
-\end{aligned}\end{equation}
-On a 2D square lattice, for instance, we obtain
-\begin{eqnarray}
-\xi_{\vec{q}} &=& 2(\cos q_{x}a_{x} + \cos q_{y}a_{y})\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
-\epsilon_{\vec{q}} &=& -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})~.\label{2dsquaretb}
-\end{eqnarray}
-The inverse Greens function thus becomes diagonal in momentum space
-\begin{equation}\begin{aligned}
-	\mathcal{G}_H^{-1}(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)\ket{\vec k}\bra{\vec k} = \begin{pmatrix} g_0 + g_1\xi_{\vec k_1} &&& \\
-	& g_0 + g_1\xi_{\vec k_2} && \\
-	&& g_0 + g_1\xi_{\vec k_3} & \\
-	...&...&...&\\
-	\end{pmatrix} 
-\end{aligned}\end{equation}
-The matrix entries are written in momentum space, and the matrix is diagonal in this basis. The other matrix can also be diagonalized similarly:
-\begin{equation}\begin{aligned}
-	\overline{\mathcal{G}_H^{-1}}(-\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)\ket{\overline{\vec k}}\bra{\overline{\vec k}} = \begin{pmatrix} \overline{g_0} + \overline{g_1}\xi_{\vec k_1} &&& \\
-	& \overline{g_0} + \overline{g_1}\xi_{\vec k_2} && \\
-	&& \overline{g_0} + \overline{g_1}\xi_{\vec k_3} & \\
-	...&...&...&\\
-	\end{pmatrix} 
-\end{aligned}\end{equation}
+% \begin{equation}\begin{aligned}
+% 	\sum_{\left<i,j \right>} \ket{i}\bra{j} + \text{h.c.} =\sum_{\vec q} \underbrace{\sum_{i_1}^{D}\cos\left(a_iq_i\right)}_{\equiv \xi_{\vec q}}\ket{\vec q}\bra{\vec q}
+% \end{aligned}\end{equation}
+% On a 2D square lattice, for instance, we obtain
+% \begin{eqnarray}
+% \xi_{\vec{q}} &=& 2(\cos q_{x}a_{x} + \cos q_{y}a_{y})\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
+% \epsilon_{\vec{q}} &=& -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})~.\label{2dsquaretb}
+% \end{eqnarray}
+% The inverse Greens function thus becomes diagonal in momentum space
+% \begin{equation}\begin{aligned}
+% 	\mathcal{G}_H^{-1}(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)\ket{\vec k}\bra{\vec k} = \begin{pmatrix} g_0 + g_1\xi_{\vec k_1} &&& \\
+% 	& g_0 + g_1\xi_{\vec k_2} && \\
+% 	&& g_0 + g_1\xi_{\vec k_3} & \\
+% 	...&...&...&\\
+% 	\end{pmatrix} 
+% \end{aligned}\end{equation}
+% The matrix entries are written in momentum space, and the matrix is diagonal in this basis. The other matrix can also be diagonalized similarly:
+% \begin{equation}\begin{aligned}
+% 	\overline{\mathcal{G}_H^{-1}}(-\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)\ket{\overline{\vec k}}\bra{\overline{\vec k}} = \begin{pmatrix} \overline{g_0} + \overline{g_1}\xi_{\vec k_1} &&& \\
+% 	& \overline{g_0} + \overline{g_1}\xi_{\vec k_2} && \\
+% 	&& \overline{g_0} + \overline{g_1}\xi_{\vec k_3} & \\
+% 	...&...&...&\\
+% 	\end{pmatrix} 
+% \end{aligned}\end{equation}
 
@@
 Thus, we can use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
-\subsection{Obtaining real space Greens functions from the full matrix}
-Since ${\mathcal{G}_H^{-1}}(\omega)$ and $\overline{\mathcal{G}_H^{-1}}(\omega)$ are diagonal in momentum space, we can invert these matrices trivially by replacing the diagonal elements with their reciprocals.
-\begin{equation}\begin{aligned}
-	\label{k-space-gf}
-	\mathcal{G}_H(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\ket{\vec k}\bra{\vec k} = \begin{pmatrix} \left(g_0 + g_1\xi_{\vec k_1}\right)^{-1} &&&&\\
-	& \left(g_0 + g_1\xi_{\vec k_2}\right)^{-1} &&&\\
-	&& \left(g_0 + g_1\xi_{\vec k_3}\right)^{-1} &&\\
-		...&&&...&\\
-	\end{pmatrix} \\
-		\overline{\mathcal{G}_H}(-\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\ket{\overline{\vec k}}\bra{\overline{\vec k}} = \begin{pmatrix} \left(\overline{g_0} + \overline{g_1}\xi_{\vec k_1}\right)^{-1} &&&&\\
-	& \left(\overline{g_0} + \overline{g_1}\xi_{\vec k_2}\right)^{-1} &&&\\
-	&& \left(\overline{g_0} + \overline{g_1}\xi_{\vec k_3}\right)^{-1} &&\\
-		...&&&...&\\
-	\end{pmatrix} 
-\end{aligned}\end{equation}
-The diagonal elements of $\mathcal{G}_H$ in momentum space are:
-\begin{equation}\begin{aligned}
-	\mathcal{G}(\omega, H^H)_{\vec k, \vec k} &= \left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\\
-			    &= \left\{\frac{2}{N}\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}\\
-			    &= \frac{N}{2}\left\{\left[\mathcal{G}_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{1}{w}\left[\mathcal{G}_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}\\
-	\mathcal{G}(-\omega, H^H)_{\overline{\vec k}, \overline{\vec k}} &= \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\\
-									&= \frac{N}{2}\left\{\left[\mathcal{G}_{D}^{-1}(-\omega)\right]_{\overline{00}\sigma} + \frac{1}{w}\left[\mathcal{G}_{D}^{-1}(-\omega)\right]_{\overline{01}\sigma}\xi_{\vec k}\right\}^{-1}\\
-\end{aligned}\end{equation}
-\textit{The single-particle momentum space Greens function can now be written down}, following eq.~\ref{G_mat_el}:
-\begin{equation}\begin{aligned}
-	\label{k_Gf}
-	G_H(\vec k, \omega) = \mathcal{G}(\omega, H^H)_{\vec k, \vec k} - \mathcal{G}(-\omega, H^H)_{\overline{\vec k}, \overline{\vec k}} = \left(g_0 + g_1 \xi_{\vec k}\right)^{-1} - \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}
-\end{aligned}\end{equation}
-The real-space Greens functions can now be obtained by Fourier transforming $G_H(\vec k, \omega)$:
-\begin{equation}\begin{aligned}
-	G_H(\vec r_i - \vec  r_j, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega)  e^{\vec{k}\cdot\left(\vec r_j - \vec{r_i}\right)} \equiv G_H(\vec r_j - \vec  r_i, \omega)
-\end{aligned}\end{equation}
-The Greens function for excitations between \(\vec r_i\) and \(\vec r_j\) depends only on the relative position \(\vec r_j - \vec r_i\), not on their absolute positions.
+% \subsection{Obtaining real space Greens functions from the full matrix}
+% Since ${\mathcal{G}_H^{-1}}(\omega)$ and $\overline{\mathcal{G}_H^{-1}}(\omega)$ are diagonal in momentum space, we can invert these matrices trivially by replacing the diagonal elements with their reciprocals.
+% \begin{equation}\begin{aligned}
+% 	\label{k-space-gf}
+% 	\mathcal{G}_H(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\ket{\vec k}\bra{\vec k} = \begin{pmatrix} \left(g_0 + g_1\xi_{\vec k_1}\right)^{-1} &&&&\\
+% 	& \left(g_0 + g_1\xi_{\vec k_2}\right)^{-1} &&&\\
+% 	&& \left(g_0 + g_1\xi_{\vec k_3}\right)^{-1} &&\\
+% 		...&&&...&\\
+% 	\end{pmatrix} \\
+% 		\overline{\mathcal{G}_H}(-\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\ket{\overline{\vec k}}\bra{\overline{\vec k}} = \begin{pmatrix} \left(\overline{g_0} + \overline{g_1}\xi_{\vec k_1}\right)^{-1} &&&&\\
+% 	& \left(\overline{g_0} + \overline{g_1}\xi_{\vec k_2}\right)^{-1} &&&\\
+% 	&& \left(\overline{g_0} + \overline{g_1}\xi_{\vec k_3}\right)^{-1} &&\\
+% 		...&&&...&\\
+% 	\end{pmatrix} 
+% \end{aligned}\end{equation}
+% The diagonal elements of $\mathcal{G}_H$ in momentum space are:
+% \begin{equation}\begin{aligned}
+% 	\mathcal{G}(\omega, H^H)_{\vec k, \vec k} &= \left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\\
+% 			    &= \left\{\frac{2}{N}\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}\\
+% 			    &= \frac{N}{2}\left\{\left[\mathcal{G}_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{1}{w}\left[\mathcal{G}_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}\\
+% 	\mathcal{G}(-\omega, H^H)_{\overline{\vec k}, \overline{\vec k}} &= \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\\
+% 									&= \frac{N}{2}\left\{\left[\mathcal{G}_{D}^{-1}(-\omega)\right]_{\overline{00}\sigma} + \frac{1}{w}\left[\mathcal{G}_{D}^{-1}(-\omega)\right]_{\overline{01}\sigma}\xi_{\vec k}\right\}^{-1}\\
+% \end{aligned}\end{equation}
+% \textit{The single-particle momentum space Greens function can now be written down}, following eq.~\ref{G_mat_el}:
+% \begin{equation}\begin{aligned}
+% 	\label{k_Gf}
+% 	G_H(\vec k, \omega) = \mathcal{G}(\omega, H^H)_{\vec k, \vec k} - \mathcal{G}(-\omega, H^H)_{\overline{\vec k}, \overline{\vec k}} = \left(g_0 + g_1 \xi_{\vec k}\right)^{-1} - \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}
+% \end{aligned}\end{equation}
+% The real-space Greens functions can now be obtained by Fourier transforming $G_H(\vec k, \omega)$:
+% \begin{equation}\begin{aligned}
+% 	G_H(\vec r_i - \vec  r_j, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega)  e^{\vec{k}\cdot\left(\vec r_j - \vec{r_i}\right)} \equiv G_H(\vec r_j - \vec  r_i, \omega)
+% \end{aligned}\end{equation}
+% The Greens function for excitations between \(\vec r_i\) and \(\vec r_j\) depends only on the relative position \(\vec r_j - \vec r_i\), not on their absolute positions.
 This is expected on grounds of translational invariance.
 By choosing \(\vec r_i = \vec r_j\), we can obtain the real space \textit{local} Greens function:
-\begin{equation}\begin{aligned}
-	\left(G_H\right)_{ii}(\omega) \equiv G_H(\vec r_j - \vec  r_i = 0, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}\left(\frac{1}{g_0 + g_1 \xi_{\vec k}} - \frac{1}{\overline{g_0} + \overline{g_1} \xi_{\vec k}}\right)
-\end{aligned}\end{equation}
-We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
-\begin{equation}\begin{aligned}
-A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{1}{\pi} \textrm{Im}\left[\left(g_0 + g_1 \xi_{\vec k}\right)^{-1} - \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\right]\\
-A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = -\frac{1}{N\pi} \textrm{Im}\sum_{\vec{k}}\left[\left(g_0 + g_1 \xi_{\vec k}\right)^{-1} - \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\right] = \frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
-\end{aligned}\end{equation}
-We can again use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the spectral functions  $A_{H} (\vec{k},\omega)$ and $A_{H} (\vec{r}=0,\omega)$ for the Hubbard model on the 2D square lattice.
+% \begin{equation}\begin{aligned}
+% 	\left(G_H\right)_{ii}(\omega) \equiv G_H(\vec r_j - \vec  r_i = 0, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}\left(\frac{1}{g_0 + g_1 \xi_{\vec k}} - \frac{1}{\overline{g_0} + \overline{g_1} \xi_{\vec k}}\right)
+% \end{aligned}\end{equation}
+% We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
+% \begin{equation}\begin{aligned}
+% A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{1}{\pi} \textrm{Im}\left[\left(g_0 + g_1 \xi_{\vec k}\right)^{-1} - \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\right]\\
+% A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = -\frac{1}{N\pi} \textrm{Im}\sum_{\vec{k}}\left[\left(g_0 + g_1 \xi_{\vec k}\right)^{-1} - \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\right] = \frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
+% \end{aligned}\end{equation}
+% We can again use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the spectral functions  $A_{H} (\vec{k},\omega)$ and $A_{H} (\vec{r}=0,\omega)$ for the Hubbard model on the 2D square lattice.
 
@@
 \begin{equation}\begin{aligned}
-	\xi_{\vec k = 0} = 1
+	\xi_{\vec k = 0} = e^{ikr} = 1
 \end{aligned}\end{equation}
@@
 	\label{Gk_dim}
-	G(k=0,\uparrow) = \left(g_0 + g_1 \right)^{-1} - \left(\overline{g_0} + \overline{g_1} \right)^{-1}
+	G(k=0,\uparrow) = \frac{2}{N}\sum_n\left[|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}} + \frac{\xi_{\vec{k}}}{w}\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\right]
 \end{aligned}\end{equation}
-We will now calculate the matrix elements $g_0$ and $g_1$ from the Hubbard dimer Hamiltonian. Those two parameters are defined as
-\begin{equation}\begin{aligned}
-	g_0 \equiv \frac{2}{N}\bra{\text{GS}}c_{0\uparrow}\left(\omega + E_\text{GS} - H^D\right)c^\dagger_{0\uparrow}\ket{\text{GS}}\\
-	g_1 \equiv \frac{2}{N}\bra{\text{GS}}c_{0\uparrow}\left(\omega + E_\text{GS} - H^D\right)c^\dagger_{1\uparrow}\ket{\text{GS}}\\
-\end{aligned}\end{equation}
-As a shorthand notation, we will use $\ket{0 \sigma} \equiv c^\dagger_{0\uparrow}\ket{\text{GS}}$.
+% We will now calculate the matrix elements $g_0$ and $g_1$ from the Hubbard dimer Hamiltonian. Those two parameters are defined as
+% \begin{equation}\begin{aligned}
+% 	g_0 \equiv \frac{2}{N}\bra{\text{GS}}c_{0\uparrow}\left(\omega + E_\text{GS} - H^D\right)c^\dagger_{0\uparrow}\ket{\text{GS}}\\
+% 	g_1 \equiv \frac{2}{N}\bra{\text{GS}}c_{0\uparrow}\left(\omega + E_\text{GS} - H^D\right)c^\dagger_{1\uparrow}\ket{\text{GS}}\\
+% \end{aligned}\end{equation}
+% As a shorthand notation, we will use $\ket{0 \sigma} \equiv c^\dagger_{0\uparrow}\ket{\text{GS}}$.
 The matrix whose elements we want to calculate, $\omega + E_\text{GS} - H^D$, can be written as a diagonal matrix in the basis formed by the eigenstates in $N=3, S^z= \frac{1}{2}$ as defined in table \ref{hubb_dim_spectrum}:
-\begin{equation}\begin{aligned}
-	\ket{\pm} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{\pm} = E_\pm \ket{\pm}
-\end{aligned}\end{equation}
-In the basis of $\ket{\pm}$, we can write
-\begin{equation}\begin{aligned}
-	\omega + E_\text{GS} - H^D &= \begin{pmatrix} \omega + E_\text{GS} - E_+ & 0 \\ 0 & \omega + E_\text{GS} - E_- \end{pmatrix}\\
-				   &= \left(\omega + E_\text{GS} - E_+\right) \ket{+}\bra{+} + \left(\omega + E_\text{GS} - E_-\right) \ket{-}\bra{-}
-\end{aligned}\end{equation}
-The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates. As shown in the appendix, we can write
-\begin{equation}\begin{aligned}
-	\ket{0 \uparrow} \equiv c^\dagger_{0\uparrow}\ket{\text{GS}} =x\ket{+} + y\ket{-}, && \ket{1 \uparrow} \equiv c^\dagger_{1\uparrow}\ket{\text{GS}} = x\ket{+} - y\ket{-}
-\end{aligned}\end{equation}
-with $x = \frac{a_2 - a_1}{2}, y=\frac{a_2 + a_1}{2}$. We can therefore express $\ket{\pm}$ in terms $\ket{0,1\uparrow}$:
-\begin{equation}\begin{aligned}
-	\ket{+} = \frac{1}{2x}\left(\ket{0 \uparrow} + \ket{1 \uparrow}\right), && \ket{-} = \frac{1}{2y}\left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)
-\end{aligned}\end{equation}
-Substituting these into the operator form of $\omega + E_\text{GS} - H^D$ gives
-\begin{equation}\begin{aligned}
-	\omega + E_\text{GS} - H^D =& \frac{1}{4x^2}\left(\omega + E_\text{GS} - E_+\right) \left(\ket{0 \uparrow} + \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} + \bra{1 \uparrow}\right) \\
-				   &+ \frac{1}{4y^2}\left(\omega + E_\text{GS} - E_-\right) \left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} - \bra{1 \uparrow}\right)\\
-=& \begin{pmatrix}\left(\frac{1}{4x^2} + \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ - \frac{1}{4y^2}E_- & \left(\frac{1}{4x^2} - \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ + \frac{1}{4y^2}E_- \\ \left(\frac{1}{4x^2} - \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ + \frac{1}{4y^2}E_- & \left(\frac{1}{4x^2} + \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ - \frac{1}{4y^2}E_-\end{pmatrix}
-\end{aligned}\end{equation}
-Now we will Fourier transform to the diagonal momentum space: $\ket{0 \sigma} = \frac{1}{\sqrt 2}\left(\ket{{k_0} \sigma} + \ket{k_\pi \sigma} \right), \ket{1 \sigma} = \frac{1}{\sqrt 2}\left(\ket{{k_0} \sigma} - \ket{k_\pi \sigma} \right)$.
-\begin{equation}\begin{aligned}
-	\left(\ket{0 \uparrow} + \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} + \bra{1 \uparrow}\right) = 2\ket{k_0 \uparrow}\bra{k_0 \uparrow}\\
-	\left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} - \bra{1 \uparrow}\right) = 2\ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
-\end{aligned}\end{equation}
-This transformation can be substituted in the operator expansion:
-\begin{equation}\begin{aligned}
-	\omega + E_\text{GS} - H^D =& \frac{1}{2x^2}\left(\omega + E_\text{GS} - E_+\right) \ket{k_0 \uparrow}\bra{k_0 \uparrow} + \frac{1}{2y^2}\left(\omega + E_\text{GS} - E_-\right) \ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
-\end{aligned}\end{equation}
-This can be easily inverted:
-\begin{equation}\begin{aligned}
-	\frac{1}{\omega + E_\text{GS} - H^D} =& \frac{2x^2}{\omega + E_\text{GS} - E_+}\ket{k_0 \uparrow}\bra{k_0 \uparrow} + \frac{2y^2}{\omega + E_\text{GS} - E_-} \ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
-\end{aligned}\end{equation}
-Since this is already in the momentum space basis, we can write
-\begin{equation}\begin{aligned}
-	\left(\frac{1}{\omega + E_\text{GS} - H^D}\right)_{k_0 k_0} = \frac{2x^2}{\omega + E_\text{GS} - E_+}\ket{k_0 \uparrow}
-\end{aligned}\end{equation}
-Performing a similar calculation for the hole excitations will give
-\begin{equation}\begin{aligned}
-	\frac{1}{-\omega + E_\text{GS} - H^D} =& \frac{2y^2}{-\omega + E_\text{GS} - \overline{E_+}}\ket{\overline{k_0 \uparrow}}\bra{\overline{k_0 \uparrow}} + \frac{2x^2}{-\omega + E_\text{GS} - \overline{E_-}} \ket{\overline{k_\pi \uparrow}}\bra{\overline{k_\pi \uparrow}}\\
-\end{aligned}\end{equation}
-where $\ket{\overline{\nu}} \equiv c_\nu \ket{\text{GS}}$ and $\overline{E_\pm}$ are the eigenenergies of the $N=1, S^z = \frac{1}{2}$ sector eigenstates.
+% \begin{equation}\begin{aligned}
+% 	\ket{\pm} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{\pm} = E_\pm \ket{\pm}
+% \end{aligned}\end{equation}
+% In the basis of $\ket{\pm}$, we can write
+% \begin{equation}\begin{aligned}
+% 	\omega + E_\text{GS} - H^D &= \begin{pmatrix} \omega + E_\text{GS} - E_+ & 0 \\ 0 & \omega + E_\text{GS} - E_- \end{pmatrix}\\
+% 				   &= \left(\omega + E_\text{GS} - E_+\right) \ket{+}\bra{+} + \left(\omega + E_\text{GS} - E_-\right) \ket{-}\bra{-}
+% \end{aligned}\end{equation}
+% The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates. As shown in the appendix, we can write
+% \begin{equation}\begin{aligned}
+% 	\ket{0 \uparrow} \equiv c^\dagger_{0\uparrow}\ket{\text{GS}} =x\ket{+} + y\ket{-}, && \ket{1 \uparrow} \equiv c^\dagger_{1\uparrow}\ket{\text{GS}} = x\ket{+} - y\ket{-}
+% \end{aligned}\end{equation}
+% with $x = \frac{a_2 - a_1}{2}, y=\frac{a_2 + a_1}{2}$. We can therefore express $\ket{\pm}$ in terms $\ket{0,1\uparrow}$:
+% \begin{equation}\begin{aligned}
+% 	\ket{+} = \frac{1}{2x}\left(\ket{0 \uparrow} + \ket{1 \uparrow}\right), && \ket{-} = \frac{1}{2y}\left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)
+% \end{aligned}\end{equation}
+% Substituting these into the operator form of $\omega + E_\text{GS} - H^D$ gives
+% \begin{equation}\begin{aligned}
+% 	\omega + E_\text{GS} - H^D =& \frac{1}{4x^2}\left(\omega + E_\text{GS} - E_+\right) \left(\ket{0 \uparrow} + \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} + \bra{1 \uparrow}\right) \\
+% 				   &+ \frac{1}{4y^2}\left(\omega + E_\text{GS} - E_-\right) \left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} - \bra{1 \uparrow}\right)\\
+% =& \begin{pmatrix}\left(\frac{1}{4x^2} + \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ - \frac{1}{4y^2}E_- & \left(\frac{1}{4x^2} - \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ + \frac{1}{4y^2}E_- \\ \left(\frac{1}{4x^2} - \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ + \frac{1}{4y^2}E_- & \left(\frac{1}{4x^2} + \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ - \frac{1}{4y^2}E_-\end{pmatrix}
+% \end{aligned}\end{equation}
+% Now we will Fourier transform to the diagonal momentum space: $\ket{0 \sigma} = \frac{1}{\sqrt 2}\left(\ket{{k_0} \sigma} + \ket{k_\pi \sigma} \right), \ket{1 \sigma} = \frac{1}{\sqrt 2}\left(\ket{{k_0} \sigma} - \ket{k_\pi \sigma} \right)$.
+% \begin{equation}\begin{aligned}
+% 	\left(\ket{0 \uparrow} + \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} + \bra{1 \uparrow}\right) = 2\ket{k_0 \uparrow}\bra{k_0 \uparrow}\\
+% 	\left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} - \bra{1 \uparrow}\right) = 2\ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
+% \end{aligned}\end{equation}
+% This transformation can be substituted in the operator expansion:
+% \begin{equation}\begin{aligned}
+% 	\omega + E_\text{GS} - H^D =& \frac{1}{2x^2}\left(\omega + E_\text{GS} - E_+\right) \ket{k_0 \uparrow}\bra{k_0 \uparrow} + \frac{1}{2y^2}\left(\omega + E_\text{GS} - E_-\right) \ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
+% \end{aligned}\end{equation}
+% This can be easily inverted:
+% \begin{equation}\begin{aligned}
+% 	\frac{1}{\omega + E_\text{GS} - H^D} =& \frac{2x^2}{\omega + E_\text{GS} - E_+}\ket{k_0 \uparrow}\bra{k_0 \uparrow} + \frac{2y^2}{\omega + E_\text{GS} - E_-} \ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
+% \end{aligned}\end{equation}
+% Since this is already in the momentum space basis, we can write
+% \begin{equation}\begin{aligned}
+% 	\left(\frac{1}{\omega + E_\text{GS} - H^D}\right)_{k_0 k_0} = \frac{2x^2}{\omega + E_\text{GS} - E_+}\ket{k_0 \uparrow}
+% \end{aligned}\end{equation}
+% Performing a similar calculation for the hole excitations will give
+% \begin{equation}\begin{aligned}
+% 	\frac{1}{-\omega + E_\text{GS} - H^D} =& \frac{2y^2}{-\omega + E_\text{GS} - \overline{E_+}}\ket{\overline{k_0 \uparrow}}\bra{\overline{k_0 \uparrow}} + \frac{2x^2}{-\omega + E_\text{GS} - \overline{E_-}} \ket{\overline{k_\pi \uparrow}}\bra{\overline{k_\pi \uparrow}}\\
+% \end{aligned}\end{equation}
+% where $\ket{\overline{\nu}} \equiv c_\nu \ket{\text{GS}}$ and $\overline{E_\pm}$ are the eigenenergies of the $N=1, S^z = \frac{1}{2}$ sector eigenstates.
 From the spectrum, we know that $E_\pm = -\overline{E_\pm}$.\\\\
-Combining these two, we can obtain the $k=0$ Greens function of the Hubbard dimer:
-\begin{equation}\begin{aligned}
-	G(k=0, \uparrow) &= \left(\frac{1}{\omega + E_\text{GS} - H^D}\right)_{k_0 k_0} - \left(\frac{1}{-\omega + E_\text{GS} - H^D}\right)_{\overline{k_0 k_0}}\\
-			 &= \frac{2x^2}{\omega + E_\text{GS} - E_+} - \frac{2y^2}{-\omega + E_\text{GS} - \overline{E_+}}\\
-			 &= \frac{2x^2}{\omega + E_\text{GS} - E_+} + \frac{2y^2}{\omega - E_\text{GS} - E_+}\\
-\end{aligned}\end{equation}
-From the definitions of $x$ and $y$, we get $2x^2 = \frac{a_1^2 + a_2^2 - 2a_1 a_2}{2} = \frac{1}{2} - \frac{2t}{\Delta}$ and $2y^2 = \frac{1}{2} + \frac{2t}{\Delta}$.
+% Combining these two, we can obtain the $k=0$ Greens function of the Hubbard dimer:
+% \begin{equation}\begin{aligned}
+% 	G(k=0, \uparrow) &= \left(\frac{1}{\omega + E_\text{GS} - H^D}\right)_{k_0 k_0} - \left(\frac{1}{-\omega + E_\text{GS} - H^D}\right)_{\overline{k_0 k_0}}\\
+% 			 &= \frac{2x^2}{\omega + E_\text{GS} - E_+} - \frac{2y^2}{-\omega + E_\text{GS} - \overline{E_+}}\\
+% 			 &= \frac{2x^2}{\omega + E_\text{GS} - E_+} + \frac{2y^2}{\omega - E_\text{GS} - E_+}\\
+% \end{aligned}\end{equation}
+% From the definitions of $x$ and $y$, we get $2x^2 = \frac{a_1^2 + a_2^2 - 2a_1 a_2}{2} = \frac{1}{2} - \frac{2t}{\Delta}$ and $2y^2 = \frac{1}{2} + \frac{2t}{\Delta}$.
 Also, the ground state energy is $E_\text{GS} = -\frac{\Delta}{2}$ and the excited energy $E_+$ is $t$.
 Substituting these gives
-\begin{equation}\begin{aligned}
-	G(k=0, \uparrow) &= \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} + \frac{\frac{1}{2} + \frac{2t}{\Delta}}{\omega + \frac{\Delta}{2} - t}\\
-\end{aligned}\end{equation}
+% \begin{equation}\begin{aligned}
+% 	G(k=0, \uparrow) &= \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} + \frac{\frac{1}{2} + \frac{2t}{\Delta}}{\omega + \frac{\Delta}{2} - t}\\
+% \end{aligned}\end{equation}
 

### 2021-08-19 notes.tex
completed the dimer consistency check part, it works !

@@
 			     &= G_H (\omega)_\text{loc} + G_H (\omega)_\text{nn} \xi_{\vec k}\\
-			     &= \frac{2}{N}\sum_n\left[|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}} + \frac{\xi_{\vec{k}}}{w}\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\right]
+			     &= \frac{2}{N}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{2}{N\pi} \textrm{Im}\sum_n\left[|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}} + \frac{\xi_{\vec{k}}}{w}\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\right]\\
+	A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{2}{N\pi} \textrm{Im}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\\
 A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = \frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
@@
 	\label{Gk_dim}
-	G(k=0,\uparrow) = \frac{2}{N}\sum_n\left[|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}} + \frac{\xi_{\vec{k}}}{w}\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\right]
-\end{aligned}\end{equation}
+	G(k=0,\uparrow) = \sum_n\left[\left(|C^0_{n}|^2 + {C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + {C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
+\end{aligned}\end{equation}
+The expansion in terms of the exact eigenstates takes the form:
+\begin{equation}\begin{aligned}
+	c^\dagger_{0 \uparrow}\ket{\tilde 0} = x\ket{3+ \uparrow} + y\ket{3- \uparrow}, && c^\dagger_{1 \uparrow}\ket{\tilde 0} = x\ket{3+ \uparrow} - y\ket{3- \uparrow}\\
+	c_{0 \uparrow}\ket{\tilde 0} = y\ket{1+ \downarrow} + x\ket{1- \downarrow}, && c_{1 \uparrow}\ket{\tilde 0} = y\ket{1+ \downarrow} - x\ket{1- \downarrow}\\
+\end{aligned}\end{equation}
+where $\ket{(3,1)\pm (\uparrow, \downarrow)}$ are the $N=(3,1), S^z = (+\frac{1}{2}, -\frac{1}{2})$ eigenstates of even $(+)$ and odd \((-)\) parity:
+\begin{equation}\begin{aligned}
+	H^D\ket{3\pm \uparrow} = \pm t \ket{3\pm \uparrow}\\
+	H^D\ket{1\pm \downarrow} = \mp t \ket{1\pm \downarrow}\\
+\end{aligned}\end{equation}
+and \(x = \frac{a_2 - a_1}{2}, y = \frac{a_2 + a_1}{2}\). The orthogonal basis is therefore
+\begin{equation}\begin{aligned}
+	\left\{ \ket{n} \right\} = \ket{3+ \uparrow}, \ket{3- \uparrow}\\
+	\left\{ \ket{\overline n} \right\} = \ket{1+ \downarrow}, \ket{1- \downarrow}
+\end{aligned}\end{equation}
+The coefficients can thus be determined:
+\begin{gather*}
+	C^0_\pm = \braket{3\pm \uparrow|c^\dagger_{0 \uparrow} |\tilde 0} = x, y\\
+	C^1_\pm = \braket{3\pm \uparrow|c^\dagger_{1 \uparrow} |\tilde 0} = x, -y\\
+	\overline C^0_\pm = \braket{1 \pm \downarrow|c_{0 \uparrow} |\tilde 0} = y, x\\
+	\overline C^1_\pm = \braket{1 \pm \downarrow|c_{1 \uparrow} |\tilde 0} = y, -x\\
+	g_\pm = \bra{3 \pm \uparrow}\left( \omega + E_{GS} - H^D\right) \ket{3 \pm \uparrow} = \omega + E_{GS} \mp t\\
+	\overline{g_\pm} = \bra{1 \pm \downarrow}\left(-\omega + E_{GS} - H^D\right) \ket{1 \pm \downarrow} = -\omega + E_{GS} \pm t\\
+\end{gather*}
+We can see that $|C^0_-|^2 + {C^0_-}^* C^1_- = y^2 - y^2 = 0$ and $|\overline C^0_-|^2 + {\overline C^0_-}^* \overline C^1_- = x^2 - x^2 = 0$.
+So we do not need to consider those terms.
+With this preparation, we can now calculate the Greens function:
+\begin{equation}\begin{aligned}
+	G(k=0, \omega) = \left(|C^0_{+}|^2 + {C^0_{+}}^* C^1_{+} \right)\frac{1}{g_+} - \left(|\overline C^0_{+}|^2 + {C^0_{+}}^* \overline C^1_{+}\right)\frac{1}{\overline{g_+}} = \frac{2x^2}{\omega + E_{GS} - t} - \frac{2y^2}{-\omega + E_{GS} + t}
+\end{aligned}\end{equation}
+The final step is to recognize that $2x^2 = \frac{a_1^2 + a_2^2 -2a_1a_2}{2} = \frac{1}{2} - \frac{2t}{\Delta}$, $2y^2 = \frac{a_1^2 + a_2^2 + 2a_1a_2}{2} = \frac{1}{2} + \frac{2t}{\Delta}$ and $E_{GS} = -\frac{\Delta}{2}$.
+Then,
+\begin{equation}\begin{aligned}
+	G(k=0, \omega) = \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} - \frac{\frac{1}{2} + \frac{2t}{\Delta}}{-\omega - \frac{\Delta}{2} + t} = \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} + \frac{\frac{1}{2} + \frac{2t}{\Delta}}{\omega + \frac{\Delta}{2} - t}
+\end{aligned}\end{equation}
+
 % We will now calculate the matrix elements $g_0$ and $g_1$ from the Hubbard dimer Hamiltonian. Those two parameters are defined as
@@
 \begin{equation}\begin{aligned}
-	\ket{\pm} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{\pm} = \pm t\ket{\pm}
+	\ket{3\pm \uparrow} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{3\pm \uparrow} = \pm t\ket{3\pm \uparrow}
 \end{aligned}\end{equation}
@@
 	&= \left(x + y\right) \frac{1}{\sqrt 2}\ket{\uparrow,2} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
-	&=x\ket{+} + y\ket{-}
-\end{aligned}\end{equation}
-where $x + y \equiv a_2$ and $x-y \equiv -a_1$. Similarly, for the other excitation, we can write
+	&=x\ket{3+ \uparrow} + y\ket{3- \uparrow}
+\end{aligned}\end{equation}
+where $x + y \equiv a_2$ and $x-y \equiv -a_1$. Similarly, for the other site excitation, we can write
 \begin{equation}\begin{aligned}
@@
 	&=  \left(x + y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
-	&=x\ket{+} - y\ket{-}
+	&=x\ket{3+ \uparrow} - y\ket{3- \uparrow}
 \end{aligned}\end{equation}
@@
 	x = \frac{a_2 - a_1}{2}, && y = \frac{a_2 + a_1}{2}
+\end{aligned}\end{equation}
+Similarly, we can also write the single-hole excitation $c_{0 \uparrow}\ket{GS}$ in terms of the $N=1, S^z = -\frac{1}{2}$ eigenstates, $\ket{1\pm \downarrow}$:
+\begin{equation}\begin{aligned}
+	\ket{1\pm \downarrow} = \frac{1}{\sqrt 2}\left(\ket{\downarrow, 0} \pm \ket{0, \downarrow}\right), && H^D \ket{1\pm \downarrow} = \mp t\ket{1\pm \downarrow}
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	c_{0 \uparrow}\ket{GS} = a_1 \frac{1}{\sqrt 2}\ket{0, \downarrow} + a_2 \frac{1}{\sqrt 2}\ket{\downarrow, 0} = y\ket{1+ \downarrow} + x\ket{1- \downarrow}\\
+	c_{1 \uparrow}\ket{GS} = a_1 \frac{1}{\sqrt 2}\ket{\downarrow, 0} + a_2 \frac{1}{\sqrt 2}\ket{0, \downarrow} = y\ket{1+ \downarrow} - x\ket{1- \downarrow}\\
 \end{aligned}\end{equation}

### 2021-08-20 notes.tex
completed self energy part, and incorporated sir's edits as well

@@
 \end{aligned}\end{equation}
+where $C^{0}$ and $C^{1}$ are coefficients of the linear superposition defined by
+\begin{equation}
+C^{0}_{n} = \bra{n} c^\dagger_{0\sigma}\ket{0}~,~ C^{1}_{n} = \bra{n} c^\dagger_{1\sigma}\ket{0}~.
+\end{equation}
+Due to the translation invariance, the coefficients $C^{0}_{n}$ and $C^{1}_{n}$ are independent of the site indices.
 The index $n$ actually defines a set of quantum numbers that characterize the state $\ket{n}$.
@@
 These two labels have to add to $N+1$.
+Our choice of the $\ket{n}$ is motivated by noting that the effective auxiliary model we are invoking here is that of a Hubbard dimer connected to a bath via single-particle hybridisation; the eigenstates of the isolated dimer and bath subsystems then act as the natural choices of the orthogonal bases in which to expand the wavefunction for the single-particle excitation of the interacting system $c^\dagger_{0\sigma}\ket{0}$.
+Further, while the eigenstates ($\Phi^D_{m,\alpha}$) of the Hubbard dimer are known analytically, we can safely assume the eigenstates of the bath ($\Psi^B_{N-m+1, \beta}$) to be a simple direct product of various single-particle Fock states in $k$-space.
+We then compute the matrix element of eq.\eqref{local_gf} for site $i$ and its immediate neighbours (i.e., a given realisation of a auxiliary model).
+Then, using translation invariance, we demand that this matrix element is independent of the site index $i$.
+The correctness of this auxiliary model approach hinges on how close the state $\ket{\tilde{0}}$ is to the 2-site local nature of the exact ground state of the target model (here the Hubbard model on a given lattice).
+Further improvement can be made by improving (i) the state $\ket{\tilde{0}}$ for the present auxiliary model (involving a Hubbard dimer), or (ii) choosing a better auxiliary model with an ``impurity" system that has more sites than two (i.e., a Bethe-Peierls improvement of the dimer auxiliary model).
+\\\\
 Using this expansion, the matrix element of $\mathcal{G}$ can be written as
@@
 Here the relavant excitations are $\ket{\overline{i\sigma}} \equiv c_{i\sigma}\ket{0}$, at frequency $-\omega$.
-To expand these states, we choose the $N-1$ eigenstates as the orthonormal basis:
+To expand these states, we choose the eigenstates with $N-1$ total particles as the orthonormal basis:
 \begin{equation}\begin{aligned}
@@
 
-\subsection{Constructing full Greens function matrix from the inverse matrix via Fourier transformation to \(k-\)space}
+\subsection{Constructing full Greens function matrix from the inverse matrix}
 The matrix elements $\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma$ and its nearest neighbour partner can be obtained simply by inverting the internal matrix $\mathcal{G}^{-1}_D$.
@@
 \end{aligned}\end{equation}
-The spectral weights remain unchanged; only the matrix element changes from $A_nm$ to $(A^{-1})_{nm}$.
+The spectral weights remain unchanged; only the matrix element changes from $A_{nm}$ to $(A^{-1})_{nm}$.
 Inverting the matrix $\mathcal{G}_D$ is actually simple because it is diagonal in the chosen basis:
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_D\right)_{nn} = \begin{pmatrix} g_{0} & 0 & & \\ 0 & g_{1} & & \\ && ..
-&  \\ &&& g_{M} \end{pmatrix} \implies \left(\mathcal{G}_D\right)_{nn} = \begin{pmatrix} \frac{1}{g_0} & 0 & \\ 0 & \frac{1}{g_1} & \\ && ...
+	\left(\mathcal{G}^{-1}_D\right)_{nn} = \begin{pmatrix} g_{0} && 0 && &..& 0\\ 0 && g_{1} && && \\ &&..&& ..
+&&  \\ 0 &&&&&& g_{M} \end{pmatrix} \implies \left(\mathcal{G}_D\right)_{nn} = \begin{pmatrix} \frac{1}{g_0} & 0 & \\ 0 & \frac{1}{g_1} & \\ && ...
 & \\ &&& \frac{1}{g_M}\end{pmatrix}
@@
 \subsection{Calculation of self energy matrix from the Dyson equation}
-Using Dyson's equation for the self-energy $\Sigma = G_{0}^{-1} - G^{-1}$ (where the matrix $G_{0,H}^{-1} (\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N} (\omega -\epsilon_{k})\ket{\vec k}\bra{\vec k}=\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega +t^{H}\xi_{k})\ket{\vec k}\bra{\vec k} $ is the inverse Greens function for the appropriate non-interacting tight-binding system), we obtain the self-energy matrix as
-\begin{eqnarray}
-\Sigma_{H} (\omega) &=& G_{0,H}^{-1} - G_{H}^{-1}~,\nonumber\\
-&=&\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}})\ket{\vec k}\bra{\vec k}
-\end{eqnarray}
-This is the full self energy matrix. One can get both real space and momentum space self energies by taking appropriate matrix elements. For instance, the self-energy in momentum space is
-\begin{equation}\begin{aligned}
-	\label{selfenergy}
-	\Sigma_{H} (\vec{k},\omega) \equiv \bra{\vec k} \Sigma_H (\omega) \ket{\vec k} = \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}~.
-\end{aligned}\end{equation}
+% Using Dyson's equation for the self-energy $\Sigma = G_{0}^{-1} - G^{-1}$ (where the matrix $G_{0,H}^{-1} (\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N} (\omega -\epsilon_{k})\ket{\vec k}\bra{\vec k}=\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega +t^{H}\xi_{k})\ket{\vec k}\bra{\vec k} $ is the inverse Greens function for the appropriate non-interacting tight-binding system), we obtain the self-energy matrix as
+% \begin{eqnarray}
+% \Sigma_{H} (\omega) &=& G_{0,H}^{-1} - G_{H}^{-1}~,\nonumber\\
+% &=&\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}})\ket{\vec k}\bra{\vec k}
+% \end{eqnarray}
+% This is the full self energy matrix. One can get both real space and momentum space self energies by taking appropriate matrix elements. For instance, the self-energy in momentum space is
+% \begin{equation}\begin{aligned}
+% 	\label{selfenergy}
+% 	\Sigma_{H} (\vec{k},\omega) \equiv \bra{\vec k} \Sigma_H (\omega) \ket{\vec k} = \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}~.
+% \end{aligned}\end{equation}
+With the knowledge of the momentum-space Greens function $G_H(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
+\begin{equation}\begin{aligned}
+	\Sigma(\vec k,\omega) = G_0(\vec k,\omega)^{-1} - G(\vec k,\omega)^{-1}
+\end{aligned}\end{equation}
+where the $G_{0}(\vec k, \omega)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system.
+Substituting this as well as the full Greens function $G_H(\vec k, \omega)$ into Dyson's equation gives
+\begin{equation}\begin{aligned}
+	\Sigma_H(\vec k,\omega) = \omega +t^{H}\xi_{k} - \frac{N}{2}\left\{\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1}
+\end{aligned}\end{equation}
+
 Thus, we can use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.

### 2021-08-20 notes.tex
minor improvements like replacing \ket{0} with \ket{\Phi_0} and correcting the wavefunction section by replacing g0 and g1 with C0 and C1

@@
 %\end{aligned}\end{equation}
-Since the two Hamiltonians $H^H$ and $\tilde H$ are connected via a similarity transformation $\mathcal{U}$, their ground states are also connected by the same transformation: $\ket{\tilde 0} = \mathcal{U}\ket{0}$.
+Since the two Hamiltonians $H^H$ and $\tilde H$ are connected via a similarity transformation $\mathcal{U}$, their ground states are also connected by the same transformation.
+That is, if the ground states are $\ket{\Phi_0}$ and $\ket{\tilde{\Phi_0}}$ respectively, then $\ket{\tilde{\Phi_0}} = \mathcal{U}\ket{\Phi_0}$.
 This means that matrix elements of the type in eq.~\ref{G_mat_el} will also be connected.
@@
 \end{aligned}\end{equation}
-where we have defined the renormalised excitation $\ket{\tilde {\nu^\prime}} \equiv \tilde c^\dagger_{\nu^\prime}\ket{\tilde 0} \equiv  \left(\mathcal{U} c^\dagger_{\nu^\prime}  \mathcal{U}^{-1}\right)  \mathcal{U}\ket{0} =  \mathcal{U}\ket{{\nu^\prime}}$.
-importance of these equalities is that we can calculate these matrix elements for $\tilde H$, which will be equal to those of $H^H$, and once we have the matrix elements of $\mathcal{G}$, we can use them to obtain the single-particle Greens functions using eq.~\ref{G_mat_el}.
+where we have defined the renormalised excitation $\ket{\tilde {\nu^\prime}} \equiv \tilde c^\dagger_{\nu^\prime}\ket{\tilde \Phi_0} \equiv  \left(\mathcal{U} c^\dagger_{\nu^\prime}  \mathcal{U}^{-1}\right)  \mathcal{U}\ket{\Phi_0} =  \mathcal{U}\ket{{\nu^\prime}}$.
+These equalities are important because they allows us to calculate these matrix elements for $\tilde H$ and then equate them to those of $H^H$, and once we have the matrix elements of $\mathcal{G}$, we can use them to obtain the single-particle Greens functions using eq.~\ref{G_mat_el}.
 More specifically, to calculate the real space single-particle Greens function between the lattice sites $i$ and $j$, both with spin $\sigma$, we will use the relation:
@@
 \end{aligned}\end{equation}
-where $\ket{i\sigma}=c^\dagger_{i\sigma}\ket{0}$ and $\ket{\overline{i\sigma}}=c_{i\sigma}\ket{0}$.
+where $\ket{i\sigma}=c^\dagger_{i\sigma}\ket{\Phi_0}$ and $\ket{\overline{i\sigma}}=c_{i\sigma}\ket{\Phi_0}$.
 We can see from the relation that we will need two types of matrix elements, one that propagates a particle excitation $\left( \ket{i\sigma} \right) $ and the one that propagates a hole excitation $\ket{\overline{i\sigma}}$.
@@
 We will now calculate the site-diagonal and site-off-diagonal matrix elements for particle propagation.
-The site-diagonal matrix element is calculated between the state $\ket{\tilde i, \sigma} = \mathcal{U}c^\dagger_{i\sigma}\ket{0}$ and its bra, while the off-diagonal one is between $\ket{\tilde j\sigma}$ and $\bra{\tilde i\sigma}$.
+The site-diagonal matrix element is calculated between the state $\ket{\tilde i, \sigma} = \mathcal{U}c^\dagger_{i\sigma}\ket{\Phi_0}$ and its bra, while the off-diagonal one is between $\ket{\tilde j\sigma}$ and $\bra{\tilde i\sigma}$.
 Since it has already been shown that the matrix elements of the renormalised Hamiltonian are the same as those of the original Hamiltonian, we will directly replace the former with the latter.
@@
 % 	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00}\times w = \frac{2}{N}\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00} \equiv g_0\\
-% 	\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00} = \bra{0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{0}
+% 	\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00} = \bra{\Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{\Phi_0}
 % \end{gather}
@@
 	\label{local_gf}
-	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\bra{0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{0}\times w = \frac{2}{N}\bra{0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{0}
+	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\bra{\tilde \Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{\tilde \Phi_0}\times w = \frac{2}{N}\bra{\tilde \Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{\tilde \Phi_0}
 \end{gather}
-We can expand the state $c^\dagger_{0\sigma}\ket{0}$ and $c^\dagger_{1\sigma}\ket{0}$ in terms of a complete set of orthogonal states:
-\begin{equation}\begin{aligned}
-	c^\dagger_{0\sigma}\ket{0} = \sum_n C^0_n \ket{n}, && c^\dagger_{1\sigma}\ket{0} = \sum_n C^1_n \ket{n}%\sum_{m,\alpha,\beta} C^i_{m,\alpha,\beta} \ket{m,\alpha,\beta}
+We can expand the state $c^\dagger_{0\sigma}\ket{\tilde \Phi_0}$ and $c^\dagger_{1\sigma}\ket{\tilde \Phi_0}$ in terms of a complete set of orthogonal states:
+\begin{equation}\begin{aligned}
+	c^\dagger_{0\sigma}\ket{\tilde \Phi_0} = \sum_n C^0_n \ket{n}, && c^\dagger_{1\sigma}\ket{\tilde \Phi_0} = \sum_n C^1_n \ket{n}%\sum_{m,\alpha,\beta} C^i_{m,\alpha,\beta} \ket{m,\alpha,\beta}
 \end{aligned}\end{equation}
@@
 \begin{equation}
-C^{0}_{n} = \bra{n} c^\dagger_{0\sigma}\ket{0}~,~ C^{1}_{n} = \bra{n} c^\dagger_{1\sigma}\ket{0}~.
+C^{0}_{n} = \bra{n} c^\dagger_{0\sigma}\ket{\tilde \Phi_0}~,~ C^{1}_{n} = \bra{n} c^\dagger_{1\sigma}\ket{\tilde \Phi_0}~.
 \end{equation}
@@
 These two labels have to add to $N+1$.
-Our choice of the $\ket{n}$ is motivated by noting that the effective auxiliary model we are invoking here is that of a Hubbard dimer connected to a bath via single-particle hybridisation; the eigenstates of the isolated dimer and bath subsystems then act as the natural choices of the orthogonal bases in which to expand the wavefunction for the single-particle excitation of the interacting system $c^\dagger_{0\sigma}\ket{0}$.
+Our choice of the $\ket{n}$ is motivated by noting that the effective auxiliary model we are invoking here is that of a Hubbard dimer connected to a bath via single-particle hybridisation; the eigenstates of the isolated dimer and bath subsystems then act as the natural choices of the orthogonal bases in which to expand the wavefunction for the single-particle excitation of the interacting system $c^\dagger_{0\sigma}\ket{\tilde \Phi_0}$.
 Further, while the eigenstates ($\Phi^D_{m,\alpha}$) of the Hubbard dimer are known analytically, we can safely assume the eigenstates of the bath ($\Psi^B_{N-m+1, \beta}$) to be a simple direct product of various single-particle Fock states in $k$-space.
@@
 Then, using translation invariance, we demand that this matrix element is independent of the site index $i$.
-The correctness of this auxiliary model approach hinges on how close the state $\ket{\tilde{0}}$ is to the 2-site local nature of the exact ground state of the target model (here the Hubbard model on a given lattice).
-Further improvement can be made by improving (i) the state $\ket{\tilde{0}}$ for the present auxiliary model (involving a Hubbard dimer), or (ii) choosing a better auxiliary model with an ``impurity" system that has more sites than two (i.e., a Bethe-Peierls improvement of the dimer auxiliary model).
+The correctness of this auxiliary model approach hinges on how close the state $\ket{\tilde{\Phi_0}}$ is to the 2-site local nature of the exact ground state of the target model (here the Hubbard model on a given lattice).
+Further improvement can be made by improving (i) the state $\ket{\tilde{\Phi_0}}$ for the present auxiliary model (involving a Hubbard dimer), or (ii) choosing a better auxiliary model with an ``impurity" system that has more sites than two (i.e., a Bethe-Peierls improvement of the dimer auxiliary model).
 \\\\
@@
 \label{nn_gf}
-\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\bra{0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{1\sigma}\ket{0} = \frac{2}{Nw}\sum_{n} \left(C^0_{n}\right)^* C^1_{n} \left(\mathcal{G}_{D}^{-1}(\omega)\right)_{nn}
+\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\bra{\tilde \Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{1\sigma}\ket{\tilde \Phi_0} = \frac{2}{Nw}\sum_{n} \left(C^0_{n}\right)^* C^1_{n} \left(\mathcal{G}_{D}^{-1}(\omega)\right)_{nn}
 %\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\left[\mathcal{G}_{D}^{-1}(\omega)\right]_{01}^\sigma \equiv g_1\\
-	%\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{01} = \bra{0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{1\sigma}\ket{0}
+	%\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{01} = \bra{\Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{1\sigma}\ket{\Phi_0}
 \end{gather}
@@
 The matrix elements for hole propagation are obtained similarly.
-Here the relavant excitations are $\ket{\overline{i\sigma}} \equiv c_{i\sigma}\ket{0}$, at frequency $-\omega$.
+Here the relavant excitations are $\ket{\overline{i\sigma}} \equiv c_{i\sigma}\ket{\tilde \Phi_0}$, at frequency $-\omega$.
 To expand these states, we choose the eigenstates with $N-1$ total particles as the orthonormal basis:
 \begin{equation}\begin{aligned}
-	c_{0\sigma}\ket{0} = \sum_n \overline C^0_n \ket{\overline{n}}, && c_{1\sigma}\ket{0} = \sum_n \overline C^1_n \ket{\overline{n}}%\sum_{m,\alpha,\beta} C^i_{m,\alpha,\beta} \ket{m,\alpha,\beta}
+	c_{0\sigma}\ket{\tilde \Phi_0} = \sum_n \overline C^0_n \ket{\overline{n}}, && c_{1\sigma}\ket{\tilde \Phi_0} = \sum_n \overline C^1_n \ket{\overline{n}}%\sum_{m,\alpha,\beta} C^i_{m,\alpha,\beta} \ket{m,\alpha,\beta}
 \end{aligned}\end{equation}
@@
 	\left(\mathcal{G}^{-1}_D\right)_{nn} = \begin{pmatrix} g_{0} && 0 && &..& 0\\ 0 && g_{1} && && \\ &&..&& ..
-&&  \\ 0 &&&&&& g_{M} \end{pmatrix} \implies \left(\mathcal{G}_D\right)_{nn} = \begin{pmatrix} \frac{1}{g_0} & 0 & \\ 0 & \frac{1}{g_1} & \\ && ...
-& \\ &&& \frac{1}{g_M}\end{pmatrix}
+&&  \\ 0 &&&&&& g_{M} \end{pmatrix} \implies \left(\mathcal{G}_D\right)_{nn} = \begin{pmatrix} \frac{1}{g_{0}} && 0 && &..& 0\\ 0 && \frac{1}{g_{1}} && && \\ &&..&& ..
+&&  \\ 0 &&&&&& \frac{1}{g_{M}} \end{pmatrix}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Sigma_H(\vec k,\omega) = \omega +t^{H}\xi_{k} - \frac{N}{2}\left\{\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1}
+	\Sigma_H(\vec k,\omega) = \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	c^\dagger_{0 \uparrow}\ket{\tilde 0} = x\ket{3+ \uparrow} + y\ket{3- \uparrow}, && c^\dagger_{1 \uparrow}\ket{\tilde 0} = x\ket{3+ \uparrow} - y\ket{3- \uparrow}\\
-	c_{0 \uparrow}\ket{\tilde 0} = y\ket{1+ \downarrow} + x\ket{1- \downarrow}, && c_{1 \uparrow}\ket{\tilde 0} = y\ket{1+ \downarrow} - x\ket{1- \downarrow}\\
+	c^\dagger_{0 \uparrow}\ket{\tilde \Phi_0} = x\ket{3+ \uparrow} + y\ket{3- \uparrow}, && c^\dagger_{1 \uparrow}\ket{\tilde \Phi_0} = x\ket{3+ \uparrow} - y\ket{3- \uparrow}\\
+	c_{0 \uparrow}\ket{\tilde \Phi_0} = y\ket{1+ \downarrow} + x\ket{1- \downarrow}, && c_{1 \uparrow}\ket{\tilde \Phi_0} = y\ket{1+ \downarrow} - x\ket{1- \downarrow}\\
 \end{aligned}\end{equation}
@@
 \begin{gather*}
-	C^0_\pm = \braket{3\pm \uparrow|c^\dagger_{0 \uparrow} |\tilde 0} = x, y\\
-	C^1_\pm = \braket{3\pm \uparrow|c^\dagger_{1 \uparrow} |\tilde 0} = x, -y\\
-	\overline C^0_\pm = \braket{1 \pm \downarrow|c_{0 \uparrow} |\tilde 0} = y, x\\
-	\overline C^1_\pm = \braket{1 \pm \downarrow|c_{1 \uparrow} |\tilde 0} = y, -x\\
+	C^0_\pm = \braket{3\pm \uparrow|c^\dagger_{0 \uparrow} |\tilde \Phi_0} = x, y\\
+	C^1_\pm = \braket{3\pm \uparrow|c^\dagger_{1 \uparrow} |\tilde \Phi_0} = x, -y\\
+	\overline C^0_\pm = \braket{1 \pm \downarrow|c_{0 \uparrow} |\tilde \Phi_0} = y, x\\
+	\overline C^1_\pm = \braket{1 \pm \downarrow|c_{1 \uparrow} |\tilde \Phi_0} = y, -x\\
 	g_\pm = \bra{3 \pm \uparrow}\left( \omega + E_{GS} - H^D\right) \ket{3 \pm \uparrow} = \omega + E_{GS} \mp t\\
@@
 
-\section{Calculating $g_0$ and $g_1$ in practice}
-The expressions for $g_0$ and $g_1$, as mentioned above, involve taking matrix elements of the Hubbard dimer Hamiltonian against the exact wavefunctions of the full Hubbard model.
+\section{Calculating the coefficients $C^{0,1}_n$ and $\overline C^{0,1}_n$ in practice}
+The expressions for $C^{0,1}_n$ and $\overline C^{0,1}_n$, as mentioned above, involve taking the projection of the exact ground state of the full Hubbard model, $\ket{\tilde \Phi_0}$, against the chosen orthogonal basis $\ket{n}$.
 \begin{enumerate}
@@
 	\begin{equation}\begin{aligned}
-		\ket{\tilde 0} = \sum_{\left<\tilde i \tilde j \right>}\ket{\Phi^D_{\tilde i\tilde j}}\otimes\ket{\Psi_{\hat{\tilde i}, \hat {\tilde j}}}\label{guess}
+		\ket{\tilde \Phi_0} = \sum_{\left<\tilde i \tilde j \right>}\ket{\Phi^D_{\tilde i\tilde j}}\otimes\ket{\Psi_{\hat{\tilde i}, \hat {\tilde j}}}\label{guess}
 	\end{aligned}\end{equation}

### 2021-08-20 notes.tex
updated the self energy part

@@
 \begin{equation}\begin{aligned}
+	\label{G_mat_loc}
 	\left(\mathcal{G}_{H}(\omega)\right)_{ii}^\sigma = \frac{2}{N}\sum_{n} |C^0_{n}|^2 \frac{1}{g_n}, && \left(\mathcal{G}_{H}(-\omega)\right)_{\overline{ii}}^\sigma = \frac{2}{N}\sum_{n} |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}}
@@
 \begin{equation}\begin{aligned}
+	\label{G_mat_nn}
 	\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\sum_{n} {C^0_{n}}^* C^1_{n} \frac{1}{g_n}, && \left(\mathcal{G}_{H}(-\omega)\right)_{\overline{ij}}^\sigma = \frac{2}{Nw}\sum_{n} {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}
@@
 			     &= G_H (\omega)_\text{loc} + G_H (\omega)_\text{nn} \xi_{\vec k}\\
-			     &= \frac{2}{N}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
+			     &= \frac{2}{N}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{2}{N\pi} \textrm{Im}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\\
+	A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{2}{N\pi} \textrm{Im}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\\
 A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = \frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
@@
 \begin{equation}\begin{aligned}
-	\Sigma_H(\vec k,\omega) = \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1}
+	\Sigma_H(\vec k,\omega) = \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1}
 \end{aligned}\end{equation}
@@
 Further, it has been argued in the DMFT literature that the Greens function matrix of the Hubbard model on the Bethe lattice with $w\to\infty$ becomes purely local (i.e., it has vanishing inter-site matrix elements).
-We can also see this from eqs.\eqref{local_gf},\eqref{nn_gf} where $(G^{H})^{-1}$ matrix has no $k$ dependence as $(G^{H})^{-1}_{ij}\propto 1/w \to 0$ as $w\to\infty$.
-Thus, in the self-energy
-\begin{eqnarray}
-\Sigma_{H} (\vec{k},\omega) &=& \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}\nonumber\\
-&\to & \lim_{w\to\infty} \omega - {g}_{0} + t^{H}\xi_{\vec{k}}~,
-\end{eqnarray}
+We can also see this from eqs.\eqref{G_mat_nn}- the nearest-neighbour inverse Greens function vanishes in the limit of $w \to \infty$:
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\sum_{n} {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}} \implies \lim_{w \to \infty}\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma \to 0
+\end{aligned}\end{equation}
+There we used the fact since at half-filling on an $SU(2)$ symmetric mode, we expect $\left<\hat n_{i \uparrow} \right> = \frac{1}{2}$, the orthonormal expansion of $c^\dagger_{i \sigma}\ket{\tilde \Phi_0} = \sum_n C^i_n \ket{n}$ to be constrained to $\sum_n |C_n^i|^2 = \frac{1}{2}$, such that the only term that scales with $w$ is $w$ itself.
+This result then implies that $G^{H}$ matrix has no $k$ dependence.
+\\\\
+In this limit, the self-energy also simplifies:
+\begin{equation}\begin{aligned}
+	\lim_{w \to \infty}\Sigma_H(\vec k,\omega) &= \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n \lim_{w \to \infty}\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1} \\
+						   &=\omega +t^{H}\xi_{\vec k} - \frac{N}{2}\frac{1}{\sum_n \left[ \frac{|C^0_{n}|^2}{g_n} - \frac{|\overline C^0_{n}|^2}{\overline{g_n}}\right]}
+\end{aligned}\end{equation}
 We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.

### 2021-08-20 notes.tex
described in more detail how to write down the orthonormal set ket{n}

@@
 One simple way of choosing the orthogonal basis $\left\{ \ket{n} \right\}$ is to take them from the eigenstates of a system comprising a Hubbard dimer and a conduction bath, decoupled from each other.
-The set of eigenstates that have the total number of particles equal to $N+1$ will then form the basis in question.
+The dimer will of course have 2 sites, which means the conduction bath will have $N-2$ sites, or $N-2$ momentum states.
+The set of eigenstates that have the total number of particles (combining the dimer and the bath) equal to $N+1$ will then form the basis in question.
 Since the dimer is decoupled from the bath, the total wavefunction will be a direct product of a Hubbard dimer wavefunction and a bath wavefunction.
@@
 
-\section{Analytic consistency checks}
-\subsection{Single-particle Greens function and self energy for the Hubbard dimer}
-The simplest test involves choosing $H^H = H^D$ and then calculating the momentum space Greens function at $k=0$, $G(k=0, \uparrow)$, for the Hubbard dimer \(\left(N = 2, w = 1 \right)\).
-The discrete set of momenta are \(\left\{ \vec k_n \right\} = 0, \frac{\pi}{a}\).
-For $k=0$, we have
-\begin{equation}\begin{aligned}
-	\xi_{\vec k = 0} = e^{ikr} = 1
-\end{aligned}\end{equation}
-Substituting this into eq.~\ref{k_Gf} gives
-\begin{equation}\begin{aligned}
-	\label{Gk_dim}
-	G(k=0,\uparrow) = \sum_n\left[\left(|C^0_{n}|^2 + {C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + {C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
-\end{aligned}\end{equation}
-The expansion in terms of the exact eigenstates takes the form:
-\begin{equation}\begin{aligned}
-	c^\dagger_{0 \uparrow}\ket{\tilde \Phi_0} = x\ket{3+ \uparrow} + y\ket{3- \uparrow}, && c^\dagger_{1 \uparrow}\ket{\tilde \Phi_0} = x\ket{3+ \uparrow} - y\ket{3- \uparrow}\\
-	c_{0 \uparrow}\ket{\tilde \Phi_0} = y\ket{1+ \downarrow} + x\ket{1- \downarrow}, && c_{1 \uparrow}\ket{\tilde \Phi_0} = y\ket{1+ \downarrow} - x\ket{1- \downarrow}\\
-\end{aligned}\end{equation}
-where $\ket{(3,1)\pm (\uparrow, \downarrow)}$ are the $N=(3,1), S^z = (+\frac{1}{2}, -\frac{1}{2})$ eigenstates of even $(+)$ and odd \((-)\) parity:
-\begin{equation}\begin{aligned}
-	H^D\ket{3\pm \uparrow} = \pm t \ket{3\pm \uparrow}\\
-	H^D\ket{1\pm \downarrow} = \mp t \ket{1\pm \downarrow}\\
-\end{aligned}\end{equation}
-and \(x = \frac{a_2 - a_1}{2}, y = \frac{a_2 + a_1}{2}\). The orthogonal basis is therefore
-\begin{equation}\begin{aligned}
-	\left\{ \ket{n} \right\} = \ket{3+ \uparrow}, \ket{3- \uparrow}\\
-	\left\{ \ket{\overline n} \right\} = \ket{1+ \downarrow}, \ket{1- \downarrow}
-\end{aligned}\end{equation}
-The coefficients can thus be determined:
-\begin{gather*}
-	C^0_\pm = \braket{3\pm \uparrow|c^\dagger_{0 \uparrow} |\tilde \Phi_0} = x, y\\
-	C^1_\pm = \braket{3\pm \uparrow|c^\dagger_{1 \uparrow} |\tilde \Phi_0} = x, -y\\
-	\overline C^0_\pm = \braket{1 \pm \downarrow|c_{0 \uparrow} |\tilde \Phi_0} = y, x\\
-	\overline C^1_\pm = \braket{1 \pm \downarrow|c_{1 \uparrow} |\tilde \Phi_0} = y, -x\\
-	g_\pm = \bra{3 \pm \uparrow}\left( \omega + E_{GS} - H^D\right) \ket{3 \pm \uparrow} = \omega + E_{GS} \mp t\\
-	\overline{g_\pm} = \bra{1 \pm \downarrow}\left(-\omega + E_{GS} - H^D\right) \ket{1 \pm \downarrow} = -\omega + E_{GS} \pm t\\
-\end{gather*}
-We can see that $|C^0_-|^2 + {C^0_-}^* C^1_- = y^2 - y^2 = 0$ and $|\overline C^0_-|^2 + {\overline C^0_-}^* \overline C^1_- = x^2 - x^2 = 0$.
-So we do not need to consider those terms.
-With this preparation, we can now calculate the Greens function:
-\begin{equation}\begin{aligned}
-	G(k=0, \omega) = \left(|C^0_{+}|^2 + {C^0_{+}}^* C^1_{+} \right)\frac{1}{g_+} - \left(|\overline C^0_{+}|^2 + {C^0_{+}}^* \overline C^1_{+}\right)\frac{1}{\overline{g_+}} = \frac{2x^2}{\omega + E_{GS} - t} - \frac{2y^2}{-\omega + E_{GS} + t}
-\end{aligned}\end{equation}
-The final step is to recognize that $2x^2 = \frac{a_1^2 + a_2^2 -2a_1a_2}{2} = \frac{1}{2} - \frac{2t}{\Delta}$, $2y^2 = \frac{a_1^2 + a_2^2 + 2a_1a_2}{2} = \frac{1}{2} + \frac{2t}{\Delta}$ and $E_{GS} = -\frac{\Delta}{2}$.
-Then,
-\begin{equation}\begin{aligned}
-	G(k=0, \omega) = \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} - \frac{\frac{1}{2} + \frac{2t}{\Delta}}{-\omega - \frac{\Delta}{2} + t} = \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} + \frac{\frac{1}{2} + \frac{2t}{\Delta}}{\omega + \frac{\Delta}{2} - t}
-\end{aligned}\end{equation}
-
-% We will now calculate the matrix elements $g_0$ and $g_1$ from the Hubbard dimer Hamiltonian. Those two parameters are defined as
-% \begin{equation}\begin{aligned}
-% 	g_0 \equiv \frac{2}{N}\bra{\text{GS}}c_{0\uparrow}\left(\omega + E_\text{GS} - H^D\right)c^\dagger_{0\uparrow}\ket{\text{GS}}\\
-% 	g_1 \equiv \frac{2}{N}\bra{\text{GS}}c_{0\uparrow}\left(\omega + E_\text{GS} - H^D\right)c^\dagger_{1\uparrow}\ket{\text{GS}}\\
-% \end{aligned}\end{equation}
-% As a shorthand notation, we will use $\ket{0 \sigma} \equiv c^\dagger_{0\uparrow}\ket{\text{GS}}$.
-The matrix whose elements we want to calculate, $\omega + E_\text{GS} - H^D$, can be written as a diagonal matrix in the basis formed by the eigenstates in $N=3, S^z= \frac{1}{2}$ as defined in table \ref{hubb_dim_spectrum}:
-% \begin{equation}\begin{aligned}
-% 	\ket{\pm} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{\pm} = E_\pm \ket{\pm}
-% \end{aligned}\end{equation}
-% In the basis of $\ket{\pm}$, we can write
-% \begin{equation}\begin{aligned}
-% 	\omega + E_\text{GS} - H^D &= \begin{pmatrix} \omega + E_\text{GS} - E_+ & 0 \\ 0 & \omega + E_\text{GS} - E_- \end{pmatrix}\\
-% 				   &= \left(\omega + E_\text{GS} - E_+\right) \ket{+}\bra{+} + \left(\omega + E_\text{GS} - E_-\right) \ket{-}\bra{-}
-% \end{aligned}\end{equation}
-% The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates. As shown in the appendix, we can write
-% \begin{equation}\begin{aligned}
-% 	\ket{0 \uparrow} \equiv c^\dagger_{0\uparrow}\ket{\text{GS}} =x\ket{+} + y\ket{-}, && \ket{1 \uparrow} \equiv c^\dagger_{1\uparrow}\ket{\text{GS}} = x\ket{+} - y\ket{-}
-% \end{aligned}\end{equation}
-% with $x = \frac{a_2 - a_1}{2}, y=\frac{a_2 + a_1}{2}$. We can therefore express $\ket{\pm}$ in terms $\ket{0,1\uparrow}$:
-% \begin{equation}\begin{aligned}
-% 	\ket{+} = \frac{1}{2x}\left(\ket{0 \uparrow} + \ket{1 \uparrow}\right), && \ket{-} = \frac{1}{2y}\left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)
-% \end{aligned}\end{equation}
-% Substituting these into the operator form of $\omega + E_\text{GS} - H^D$ gives
-% \begin{equation}\begin{aligned}
-% 	\omega + E_\text{GS} - H^D =& \frac{1}{4x^2}\left(\omega + E_\text{GS} - E_+\right) \left(\ket{0 \uparrow} + \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} + \bra{1 \uparrow}\right) \\
-% 				   &+ \frac{1}{4y^2}\left(\omega + E_\text{GS} - E_-\right) \left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} - \bra{1 \uparrow}\right)\\
-% =& \begin{pmatrix}\left(\frac{1}{4x^2} + \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ - \frac{1}{4y^2}E_- & \left(\frac{1}{4x^2} - \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ + \frac{1}{4y^2}E_- \\ \left(\frac{1}{4x^2} - \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ + \frac{1}{4y^2}E_- & \left(\frac{1}{4x^2} + \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ - \frac{1}{4y^2}E_-\end{pmatrix}
-% \end{aligned}\end{equation}
-% Now we will Fourier transform to the diagonal momentum space: $\ket{0 \sigma} = \frac{1}{\sqrt 2}\left(\ket{{k_0} \sigma} + \ket{k_\pi \sigma} \right), \ket{1 \sigma} = \frac{1}{\sqrt 2}\left(\ket{{k_0} \sigma} - \ket{k_\pi \sigma} \right)$.
-% \begin{equation}\begin{aligned}
-% 	\left(\ket{0 \uparrow} + \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} + \bra{1 \uparrow}\right) = 2\ket{k_0 \uparrow}\bra{k_0 \uparrow}\\
-% 	\left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} - \bra{1 \uparrow}\right) = 2\ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
-% \end{aligned}\end{equation}
-% This transformation can be substituted in the operator expansion:
-% \begin{equation}\begin{aligned}
-% 	\omega + E_\text{GS} - H^D =& \frac{1}{2x^2}\left(\omega + E_\text{GS} - E_+\right) \ket{k_0 \uparrow}\bra{k_0 \uparrow} + \frac{1}{2y^2}\left(\omega + E_\text{GS} - E_-\right) \ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
-% \end{aligned}\end{equation}
-% This can be easily inverted:
-% \begin{equation}\begin{aligned}
-% 	\frac{1}{\omega + E_\text{GS} - H^D} =& \frac{2x^2}{\omega + E_\text{GS} - E_+}\ket{k_0 \uparrow}\bra{k_0 \uparrow} + \frac{2y^2}{\omega + E_\text{GS} - E_-} \ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
-% \end{aligned}\end{equation}
-% Since this is already in the momentum space basis, we can write
-% \begin{equation}\begin{aligned}
-% 	\left(\frac{1}{\omega + E_\text{GS} - H^D}\right)_{k_0 k_0} = \frac{2x^2}{\omega + E_\text{GS} - E_+}\ket{k_0 \uparrow}
-% \end{aligned}\end{equation}
-% Performing a similar calculation for the hole excitations will give
-% \begin{equation}\begin{aligned}
-% 	\frac{1}{-\omega + E_\text{GS} - H^D} =& \frac{2y^2}{-\omega + E_\text{GS} - \overline{E_+}}\ket{\overline{k_0 \uparrow}}\bra{\overline{k_0 \uparrow}} + \frac{2x^2}{-\omega + E_\text{GS} - \overline{E_-}} \ket{\overline{k_\pi \uparrow}}\bra{\overline{k_\pi \uparrow}}\\
-% \end{aligned}\end{equation}
-% where $\ket{\overline{\nu}} \equiv c_\nu \ket{\text{GS}}$ and $\overline{E_\pm}$ are the eigenenergies of the $N=1, S^z = \frac{1}{2}$ sector eigenstates.
-From the spectrum, we know that $E_\pm = -\overline{E_\pm}$.\\\\
-% Combining these two, we can obtain the $k=0$ Greens function of the Hubbard dimer:
-% \begin{equation}\begin{aligned}
-% 	G(k=0, \uparrow) &= \left(\frac{1}{\omega + E_\text{GS} - H^D}\right)_{k_0 k_0} - \left(\frac{1}{-\omega + E_\text{GS} - H^D}\right)_{\overline{k_0 k_0}}\\
-% 			 &= \frac{2x^2}{\omega + E_\text{GS} - E_+} - \frac{2y^2}{-\omega + E_\text{GS} - \overline{E_+}}\\
-% 			 &= \frac{2x^2}{\omega + E_\text{GS} - E_+} + \frac{2y^2}{\omega - E_\text{GS} - E_+}\\
-% \end{aligned}\end{equation}
-% From the definitions of $x$ and $y$, we get $2x^2 = \frac{a_1^2 + a_2^2 - 2a_1 a_2}{2} = \frac{1}{2} - \frac{2t}{\Delta}$ and $2y^2 = \frac{1}{2} + \frac{2t}{\Delta}$.
-Also, the ground state energy is $E_\text{GS} = -\frac{\Delta}{2}$ and the excited energy $E_+$ is $t$.
-Substituting these gives
-% \begin{equation}\begin{aligned}
-% 	G(k=0, \uparrow) &= \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} + \frac{\frac{1}{2} + \frac{2t}{\Delta}}{\omega + \frac{\Delta}{2} - t}\\
-% \end{aligned}\end{equation}
-
-% from the Greens function matrices of the Hubbard dimer. From the spectral representation of the Greens function matrix elements in eq.~\ref{G_mat_spec}, we obtain
-% \begin{equation}\begin{aligned}
-% 	\left(\mathcal{G}_D\right)_{\nu \nu^\prime} = \begin{pmatrix} x_- + y_- && x_- - y_- \\ x_- - y_- && x_- + y_- \end{pmatrix}
-% \end{aligned}\end{equation}
-% where
-% \begin{equation}\begin{aligned}
-% 	x_\pm \equiv \left( \frac{1}{4} \pm \frac{t}{\Delta} \right) \frac{1}{\mp\omega - \frac{\Delta}{2} \pm t}, && y_\pm \equiv \left( \frac{1}{4} \mp \frac{t}{\Delta} \right) \frac{1}{\mp\omega - \frac{\Delta}{2} \mp t}
-% \end{aligned}\end{equation}
-% The matrix is easily inverted:
-% \begin{equation}\begin{aligned}
-% 	\left(\mathcal{G}_D^{-1}\right)_{\nu \nu^\prime}(\omega) = \frac{1}{4}\begin{pmatrix}  \frac{1}{x_-} + \frac{1}{y_-} &&  \frac{1}{x_-} - \frac{1}{y_-} \\  \frac{1}{x_-} - \frac{1}{y_-} &&  \frac{1}{x_-} + \frac{1}{y_-} \end{pmatrix}
-% \end{aligned}\end{equation}
-% $g_0$ and $g_1$ can now be read off:
-% \begin{equation}\begin{aligned}
-% 	g_0 = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{00} = \frac{1}{4}\left( \frac{1}{x_-} + \frac{1}{y_-}\right), && g_1 = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{01} = \frac{1}{4}\left( \frac{1}{x_-} - \frac{1}{y_-}\right)
-% \end{aligned}\end{equation}
-% Similarly, we obtain the other matrix:
-% \begin{equation}\begin{aligned}
-% 	\left(\mathcal{G}_D\right)_{\overline{\nu \nu^\prime}}(-\omega) = \begin{pmatrix} x_+ + y_+ && x_+ - y_+ \\ x_+ - y_+ && x_+ + y_+ \end{pmatrix}
-% \end{aligned}\end{equation}
-% which gives
-% \begin{equation}\begin{aligned}
-% 	\overline{g_0} = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{00} = \frac{1}{4}\left( \frac{1}{x_+} + \frac{1}{y_+}\right), && \overline{g_1} = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{01} = \frac{1}{4}\left( \frac{1}{x_+} - \frac{1}{y_+}\right)
-% \end{aligned}\end{equation}
-% Substituting these values of $g_0, g_1, \overline{g_0}$ and $\overline{g_1}$ in eq.~\ref{Gk_dim} gives the same expression as that obtained in eq.~\ref{Gk0}.
-
-%To verify this result, we just need to show the momentum space Greens function of the Hubbard dimer calculated from the exact eigenstates (as shown in the appendix) also takes the same form.
-Using the Fourier transform, we can write
-%\begin{equation}\begin{aligned}
-%	G(k=0, \sigma) = G(r=0, \sigma) + G(r=a, \sigma)
-%\end{aligned}\end{equation}
-%The terms on the RHS are the real space local and nearest-neighbour Greens functions of the Hubbard dimer.
-%Therefore, the Greens function at $\vec r=0$ for the Hubbard dimer can be expressed as
-%\begin{equation}\begin{aligned}
-%	G_H(\vec r = 0, \omega) = \frac{1}{2}\left[\frac{1}{g_0 + g_1} + \frac{1}{g_0 - g_1}\right]  = \frac{g_0}{g_0^2 - g_1^2}
-%\end{aligned}\end{equation}
-%For the Hubbard dimer, we substitute $N=2, w=1$ into the expressions for $g_{0}$ and $g_{1}$ to obtain
-%\begin{equation}\begin{aligned}
-%	&g_0 = \frac{1}{\text{Det }G_D}\left( G_D \right)_{00}, &g_1 = -\frac{1}{\text{Det }G_D}\left( G_D \right)_{01}
-%\end{aligned}\end{equation}
-%The Greens function at the zeroth site then becomes
-%\begin{equation}\begin{aligned}
-%	G_H(\vec r = 0, \omega) = \text{Det }G_D\frac{\left(G_D\right)_{00}}{\left(G_D\right)_{00}^2 - \left(G_D\right)_{01}^2} = \text{Det }G_D\frac{\left(G_D\right)_{00}}{\text{Det }G_D} = \left(G_D\right)_{00}
-%\end{aligned}\end{equation}
-%This is the expected result.
-Because the full Hubbard model in this case was simply the Hubbard dimer, \(G_H(\vec r = 0, \omega)\) should just be \(\left(G_D\right)_{00}\).
-Although this is a trivial example (we matched the Hubbard dimer with another Hubbard dimer), this atleast tells us that this algorithm for calculating the real space local Greens function from the inverse Greens function matrix elements is sensible.
-
-\subsection{On the Bethe lattice}
-Another test involves considering the case of infinite number of nearest neighbours $w\to\infty$ (the coordination number, and effectively the dimensionality).
-Here, as has been argued in the DMFT literature, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$ such that the kinetic energy of the associated tight-binding lattice model is finite.
-This allows for the competition between the kinetic and potential terms of the Hamiltonian to drive a metal-insulator transition in the limit of $w\to\infty$ as well.
-Further, it has been argued in the DMFT literature that the Greens function matrix of the Hubbard model on the Bethe lattice with $w\to\infty$ becomes purely local (i.e., it has vanishing inter-site matrix elements).
-We can also see this from eqs.\eqref{G_mat_nn}- the nearest-neighbour inverse Greens function vanishes in the limit of $w \to \infty$:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\sum_{n} {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}} \implies \lim_{w \to \infty}\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma \to 0
-\end{aligned}\end{equation}
-There we used the fact since at half-filling on an $SU(2)$ symmetric mode, we expect $\left<\hat n_{i \uparrow} \right> = \frac{1}{2}$, the orthonormal expansion of $c^\dagger_{i \sigma}\ket{\tilde \Phi_0} = \sum_n C^i_n \ket{n}$ to be constrained to $\sum_n |C_n^i|^2 = \frac{1}{2}$, such that the only term that scales with $w$ is $w$ itself.
-This result then implies that $G^{H}$ matrix has no $k$ dependence.
-\\\\
-In this limit, the self-energy also simplifies:
-\begin{equation}\begin{aligned}
-	\lim_{w \to \infty}\Sigma_H(\vec k,\omega) &= \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n \lim_{w \to \infty}\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1} \\
-						   &=\omega +t^{H}\xi_{\vec k} - \frac{N}{2}\frac{1}{\sum_n \left[ \frac{|C^0_{n}|^2}{g_n} - \frac{|\overline C^0_{n}|^2}{\overline{g_n}}\right]}
-\end{aligned}\end{equation}
-We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.
+\section{Some comments on writing down the orthonormal basis $\left\{ \ket{n} \right\}$}
+As mentioned previously, for a parent model of $N$ sites, the orthonormal basis is constructed out of those eigenstates of a decoupled dimer+bath system that have total number of particles equal to $\mathcal{N}_\text{tot} = \mathcal{N}_\text{dim} + \mathcal{N}_\text{bath} = N+1$.
+The condition on the total number is necessary because that is also the total particile number of the state we are expanding $(c^\dagger_{i\sigma}\ket{\tilde \Phi_0}$.
+The dimer will have 2 sites, while the rest $N-2$ sites go into the bath.
+\\\\
+If we are solving the trivial example of $H^H = H^D$ (that is, if we take the Hubbard dimer itself as the full Hubbard model that we are trying to solve), the bath is non-existant.
+The entire set of $\ket{n}$ for expanding $c^\dagger_{i\sigma}\ket{\tilde \Phi_0}$ is then made up by the $\mathcal{N} = N + 1 = 3, S^z = \frac{1}{2}\sigma$ eigenstates of $H^D$.
+There are two of those; these two make up the entire orthonormal basis in which we can expand the single-particle excitaions:
+\begin{equation}\begin{aligned}
+	\left\{ \ket{n} \right\} = \ket{3 \pm \sigma}
+\end{aligned}\end{equation}
+Similarly, for expanding the hole excitaions $c_{i\sigma}\ket{\tilde \Phi_0}$, we will instead choose the $\mathcal{N} = N - 1 = 1, S^z = -\frac{1}{2}\sigma$ eigenstates of $H^D$.
+There are again two of those:
+\begin{equation}\begin{aligned}
+	\left\{ \ket{\overline n} \right\} = \ket{1 \pm -\sigma}
+\end{aligned}\end{equation}
+\\\\
+For a more general $N(>2)$-site model, there will be a bath of $N-2$ momentum states.
+These momentum states are labelled as $k_1, k_2, ..., k_{N-2}$.
+Let us designate the set of eigenstates of the Hubbard dimer as \(\left\{ \ket{\Phi^D_i} \right\} \) and those of the bath as \(\left\{ \ket{\Psi^B_{j, \nu^j}} \right\} \).
+Since the bath is non-interacting, those eigenstates can be written down easily:
+\begin{equation}\begin{aligned}
+	\left\{ \ket{\Psi^B_{j, \nu^j}} \right\} = \begin{cases} &  j \in [0, 2N-4]\\[-10pt]
+	\otimes_{i=1}^j\hat n_{\nu^j_i} = 1:\\[-10pt]
+& \nu^j \in \text{all subsets of length $j$ of the set $\left[k_1 \uparrow, k_1 \downarrow, k_2 \uparrow, ..., k_{N-2} \uparrow, k_{N-2} \downarrow\right]$} \end{cases}
+\end{aligned}\end{equation}
+$j$ defines the number of occupied states in a particular eigenstate of the conduction bath.
+The string $\nu^j$ runs over all possible set of quantum numbers of a particular length $j$.
+For example, if we have 3 momentum states in the bath $k_1, k_2, k_3$, then $\nu^2$ would take the values
+\begin{equation}\begin{aligned}
+	\left\{\nu^2\right\} = \left(k_1 \uparrow, k_1 \downarrow\right),\left(k_1 \uparrow, k_2 \uparrow\right),\left(k_1 \uparrow, k_2 \downarrow\right),\left(k_1 \uparrow, k_3 \uparrow\right),\left(k_1 \uparrow, k_3 \downarrow\right),\left(k_1 \downarrow, k_2 \uparrow\right),\left(k_1 \downarrow, k_2 \downarrow\right),\\
+	\left(k_1 \downarrow, k_3 \uparrow\right),\left(k_1 \downarrow, k_3 \downarrow\right),\left(k_2 \uparrow, k_2 \downarrow\right),\left(k_2 \uparrow, k_3 \uparrow\right),\left(k_2 \uparrow, k_3 \downarrow\right),\left(k_2 \downarrow, k_3 \uparrow\right),\left(k_2 \downarrow, k_3 \downarrow\right),\\
+\left(k_3 \uparrow, k_3 \downarrow\right)
+\end{aligned}\end{equation}
+The $j=0$ case means the bath is empty.
+The general complete set of orthonormal kets is given by
+\begin{equation}\begin{aligned}
+	\left\{ \ket{n} \right\} = \sum_{i=1}^{16}\sum_{j=0}^{N-2}\sum_{\nu^j}\ket{\Phi^D_i}\otimes \ket{\Psi^B_{j, \nu^j}}
+\end{aligned}\end{equation}
+The first twp sums are unconstrained.
+The index $i$ runs through all 16 eigenstates of the Hubbard dimer, the index $j$ runs through all the possible total number of particles the eigenstate of the bath can have.
+For each value of $j$, the string $\nu^j$ runs through all possible combinations of length $j$ from the complete set of quantum numbers $\left\{ k\sigma \right\} $.
 
@@
 Each set will form a $2\times2$ matrix, and we can invert them to obtain $\mathcal{G}_D(\omega)$, and then the matrix elements of this inverted matrix will give all the parameters $g_0$ through $\overline{g_1}$.
+
+\section{Analytic consistency checks}
+\subsection{Single-particle Greens function and self energy for the Hubbard dimer}
+The simplest test involves choosing $H^H = H^D$ and then calculating the momentum space Greens function at $k=0$, $G(k=0, \uparrow)$, for the Hubbard dimer \(\left(N = 2, w = 1 \right)\).
+The discrete set of momenta are \(\left\{ \vec k_n \right\} = 0, \frac{\pi}{a}\).
+For $k=0$, we have
+\begin{equation}\begin{aligned}
+	\xi_{\vec k = 0} = e^{ikr} = 1
+\end{aligned}\end{equation}
+Substituting this into eq.~\ref{k_Gf} gives
+\begin{equation}\begin{aligned}
+	\label{Gk_dim}
+	G(k=0,\uparrow) = \sum_n\left[\left(|C^0_{n}|^2 + {C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + {C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
+\end{aligned}\end{equation}
+The expansion in terms of the exact eigenstates takes the form:
+\begin{equation}\begin{aligned}
+	c^\dagger_{0 \uparrow}\ket{\tilde \Phi_0} = x\ket{3+ \uparrow} + y\ket{3- \uparrow}, && c^\dagger_{1 \uparrow}\ket{\tilde \Phi_0} = x\ket{3+ \uparrow} - y\ket{3- \uparrow}\\
+	c_{0 \uparrow}\ket{\tilde \Phi_0} = y\ket{1+ \downarrow} + x\ket{1- \downarrow}, && c_{1 \uparrow}\ket{\tilde \Phi_0} = y\ket{1+ \downarrow} - x\ket{1- \downarrow}\\
+\end{aligned}\end{equation}
+where $\ket{(3,1)\pm (\uparrow, \downarrow)}$ are the $N=(3,1), S^z = (+\frac{1}{2}, -\frac{1}{2})$ eigenstates of even $(+)$ and odd \((-)\) parity:
+\begin{equation}\begin{aligned}
+	H^D\ket{3\pm \uparrow} = \pm t \ket{3\pm \uparrow}\\
+	H^D\ket{1\pm \downarrow} = \mp t \ket{1\pm \downarrow}\\
+\end{aligned}\end{equation}
+and \(x = \frac{a_2 - a_1}{2}, y = \frac{a_2 + a_1}{2}\). The orthogonal basis is therefore
+\begin{equation}\begin{aligned}
+	\left\{ \ket{n} \right\} = \ket{3+ \uparrow}, \ket{3- \uparrow}\\
+	\left\{ \ket{\overline n} \right\} = \ket{1+ \downarrow}, \ket{1- \downarrow}
+\end{aligned}\end{equation}
+The coefficients can thus be determined:
+\begin{gather*}
+	C^0_\pm = \braket{3\pm \uparrow|c^\dagger_{0 \uparrow} |\tilde \Phi_0} = x, y\\
+	C^1_\pm = \braket{3\pm \uparrow|c^\dagger_{1 \uparrow} |\tilde \Phi_0} = x, -y\\
+	\overline C^0_\pm = \braket{1 \pm \downarrow|c_{0 \uparrow} |\tilde \Phi_0} = y, x\\
+	\overline C^1_\pm = \braket{1 \pm \downarrow|c_{1 \uparrow} |\tilde \Phi_0} = y, -x\\
+	g_\pm = \bra{3 \pm \uparrow}\left( \omega + E_{GS} - H^D\right) \ket{3 \pm \uparrow} = \omega + E_{GS} \mp t\\
+	\overline{g_\pm} = \bra{1 \pm \downarrow}\left(-\omega + E_{GS} - H^D\right) \ket{1 \pm \downarrow} = -\omega + E_{GS} \pm t\\
+\end{gather*}
+We can see that $|C^0_-|^2 + {C^0_-}^* C^1_- = y^2 - y^2 = 0$ and $|\overline C^0_-|^2 + {\overline C^0_-}^* \overline C^1_- = x^2 - x^2 = 0$.
+So we do not need to consider those terms.
+With this preparation, we can now calculate the Greens function:
+\begin{equation}\begin{aligned}
+	G(k=0, \omega) = \left(|C^0_{+}|^2 + {C^0_{+}}^* C^1_{+} \right)\frac{1}{g_+} - \left(|\overline C^0_{+}|^2 + {C^0_{+}}^* \overline C^1_{+}\right)\frac{1}{\overline{g_+}} = \frac{2x^2}{\omega + E_{GS} - t} - \frac{2y^2}{-\omega + E_{GS} + t}
+\end{aligned}\end{equation}
+The final step is to recognize that $2x^2 = \frac{a_1^2 + a_2^2 -2a_1a_2}{2} = \frac{1}{2} - \frac{2t}{\Delta}$, $2y^2 = \frac{a_1^2 + a_2^2 + 2a_1a_2}{2} = \frac{1}{2} + \frac{2t}{\Delta}$ and $E_{GS} = -\frac{\Delta}{2}$.
+Then,
+\begin{equation}\begin{aligned}
+	G(k=0, \omega) = \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} - \frac{\frac{1}{2} + \frac{2t}{\Delta}}{-\omega - \frac{\Delta}{2} + t} = \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} + \frac{\frac{1}{2} + \frac{2t}{\Delta}}{\omega + \frac{\Delta}{2} - t}
+\end{aligned}\end{equation}
+
+% We will now calculate the matrix elements $g_0$ and $g_1$ from the Hubbard dimer Hamiltonian. Those two parameters are defined as
+% \begin{equation}\begin{aligned}
+% 	g_0 \equiv \frac{2}{N}\bra{\text{GS}}c_{0\uparrow}\left(\omega + E_\text{GS} - H^D\right)c^\dagger_{0\uparrow}\ket{\text{GS}}\\
+% 	g_1 \equiv \frac{2}{N}\bra{\text{GS}}c_{0\uparrow}\left(\omega + E_\text{GS} - H^D\right)c^\dagger_{1\uparrow}\ket{\text{GS}}\\
+% \end{aligned}\end{equation}
+% As a shorthand notation, we will use $\ket{0 \sigma} \equiv c^\dagger_{0\uparrow}\ket{\text{GS}}$.
+The matrix whose elements we want to calculate, $\omega + E_\text{GS} - H^D$, can be written as a diagonal matrix in the basis formed by the eigenstates in $N=3, S^z= \frac{1}{2}$ as defined in table \ref{hubb_dim_spectrum}:
+% \begin{equation}\begin{aligned}
+% 	\ket{\pm} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{\pm} = E_\pm \ket{\pm}
+% \end{aligned}\end{equation}
+% In the basis of $\ket{\pm}$, we can write
+% \begin{equation}\begin{aligned}
+% 	\omega + E_\text{GS} - H^D &= \begin{pmatrix} \omega + E_\text{GS} - E_+ & 0 \\ 0 & \omega + E_\text{GS} - E_- \end{pmatrix}\\
+% 				   &= \left(\omega + E_\text{GS} - E_+\right) \ket{+}\bra{+} + \left(\omega + E_\text{GS} - E_-\right) \ket{-}\bra{-}
+% \end{aligned}\end{equation}
+% The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates. As shown in the appendix, we can write
+% \begin{equation}\begin{aligned}
+% 	\ket{0 \uparrow} \equiv c^\dagger_{0\uparrow}\ket{\text{GS}} =x\ket{+} + y\ket{-}, && \ket{1 \uparrow} \equiv c^\dagger_{1\uparrow}\ket{\text{GS}} = x\ket{+} - y\ket{-}
+% \end{aligned}\end{equation}
+% with $x = \frac{a_2 - a_1}{2}, y=\frac{a_2 + a_1}{2}$. We can therefore express $\ket{\pm}$ in terms $\ket{0,1\uparrow}$:
+% \begin{equation}\begin{aligned}
+% 	\ket{+} = \frac{1}{2x}\left(\ket{0 \uparrow} + \ket{1 \uparrow}\right), && \ket{-} = \frac{1}{2y}\left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)
+% \end{aligned}\end{equation}
+% Substituting these into the operator form of $\omega + E_\text{GS} - H^D$ gives
+% \begin{equation}\begin{aligned}
+% 	\omega + E_\text{GS} - H^D =& \frac{1}{4x^2}\left(\omega + E_\text{GS} - E_+\right) \left(\ket{0 \uparrow} + \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} + \bra{1 \uparrow}\right) \\
+% 				   &+ \frac{1}{4y^2}\left(\omega + E_\text{GS} - E_-\right) \left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} - \bra{1 \uparrow}\right)\\
+% =& \begin{pmatrix}\left(\frac{1}{4x^2} + \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ - \frac{1}{4y^2}E_- & \left(\frac{1}{4x^2} - \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ + \frac{1}{4y^2}E_- \\ \left(\frac{1}{4x^2} - \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ + \frac{1}{4y^2}E_- & \left(\frac{1}{4x^2} + \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ - \frac{1}{4y^2}E_-\end{pmatrix}
+% \end{aligned}\end{equation}
+% Now we will Fourier transform to the diagonal momentum space: $\ket{0 \sigma} = \frac{1}{\sqrt 2}\left(\ket{{k_0} \sigma} + \ket{k_\pi \sigma} \right), \ket{1 \sigma} = \frac{1}{\sqrt 2}\left(\ket{{k_0} \sigma} - \ket{k_\pi \sigma} \right)$.
+% \begin{equation}\begin{aligned}
+% 	\left(\ket{0 \uparrow} + \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} + \bra{1 \uparrow}\right) = 2\ket{k_0 \uparrow}\bra{k_0 \uparrow}\\
+% 	\left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} - \bra{1 \uparrow}\right) = 2\ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
+% \end{aligned}\end{equation}
+% This transformation can be substituted in the operator expansion:
+% \begin{equation}\begin{aligned}
+% 	\omega + E_\text{GS} - H^D =& \frac{1}{2x^2}\left(\omega + E_\text{GS} - E_+\right) \ket{k_0 \uparrow}\bra{k_0 \uparrow} + \frac{1}{2y^2}\left(\omega + E_\text{GS} - E_-\right) \ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
+% \end{aligned}\end{equation}
+% This can be easily inverted:
+% \begin{equation}\begin{aligned}
+% 	\frac{1}{\omega + E_\text{GS} - H^D} =& \frac{2x^2}{\omega + E_\text{GS} - E_+}\ket{k_0 \uparrow}\bra{k_0 \uparrow} + \frac{2y^2}{\omega + E_\text{GS} - E_-} \ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
+% \end{aligned}\end{equation}
+% Since this is already in the momentum space basis, we can write
+% \begin{equation}\begin{aligned}
+% 	\left(\frac{1}{\omega + E_\text{GS} - H^D}\right)_{k_0 k_0} = \frac{2x^2}{\omega + E_\text{GS} - E_+}\ket{k_0 \uparrow}
+% \end{aligned}\end{equation}
+% Performing a similar calculation for the hole excitations will give
+% \begin{equation}\begin{aligned}
+% 	\frac{1}{-\omega + E_\text{GS} - H^D} =& \frac{2y^2}{-\omega + E_\text{GS} - \overline{E_+}}\ket{\overline{k_0 \uparrow}}\bra{\overline{k_0 \uparrow}} + \frac{2x^2}{-\omega + E_\text{GS} - \overline{E_-}} \ket{\overline{k_\pi \uparrow}}\bra{\overline{k_\pi \uparrow}}\\
+% \end{aligned}\end{equation}
+% where $\ket{\overline{\nu}} \equiv c_\nu \ket{\text{GS}}$ and $\overline{E_\pm}$ are the eigenenergies of the $N=1, S^z = \frac{1}{2}$ sector eigenstates.
+From the spectrum, we know that $E_\pm = -\overline{E_\pm}$.\\\\
+% Combining these two, we can obtain the $k=0$ Greens function of the Hubbard dimer:
+% \begin{equation}\begin{aligned}
+% 	G(k=0, \uparrow) &= \left(\frac{1}{\omega + E_\text{GS} - H^D}\right)_{k_0 k_0} - \left(\frac{1}{-\omega + E_\text{GS} - H^D}\right)_{\overline{k_0 k_0}}\\
+% 			 &= \frac{2x^2}{\omega + E_\text{GS} - E_+} - \frac{2y^2}{-\omega + E_\text{GS} - \overline{E_+}}\\
+% 			 &= \frac{2x^2}{\omega + E_\text{GS} - E_+} + \frac{2y^2}{\omega - E_\text{GS} - E_+}\\
+% \end{aligned}\end{equation}
+% From the definitions of $x$ and $y$, we get $2x^2 = \frac{a_1^2 + a_2^2 - 2a_1 a_2}{2} = \frac{1}{2} - \frac{2t}{\Delta}$ and $2y^2 = \frac{1}{2} + \frac{2t}{\Delta}$.
+Also, the ground state energy is $E_\text{GS} = -\frac{\Delta}{2}$ and the excited energy $E_+$ is $t$.
+Substituting these gives
+% \begin{equation}\begin{aligned}
+% 	G(k=0, \uparrow) &= \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} + \frac{\frac{1}{2} + \frac{2t}{\Delta}}{\omega + \frac{\Delta}{2} - t}\\
+% \end{aligned}\end{equation}
+
+% from the Greens function matrices of the Hubbard dimer. From the spectral representation of the Greens function matrix elements in eq.~\ref{G_mat_spec}, we obtain
+% \begin{equation}\begin{aligned}
+% 	\left(\mathcal{G}_D\right)_{\nu \nu^\prime} = \begin{pmatrix} x_- + y_- && x_- - y_- \\ x_- - y_- && x_- + y_- \end{pmatrix}
+% \end{aligned}\end{equation}
+% where
+% \begin{equation}\begin{aligned}
+% 	x_\pm \equiv \left( \frac{1}{4} \pm \frac{t}{\Delta} \right) \frac{1}{\mp\omega - \frac{\Delta}{2} \pm t}, && y_\pm \equiv \left( \frac{1}{4} \mp \frac{t}{\Delta} \right) \frac{1}{\mp\omega - \frac{\Delta}{2} \mp t}
+% \end{aligned}\end{equation}
+% The matrix is easily inverted:
+% \begin{equation}\begin{aligned}
+% 	\left(\mathcal{G}_D^{-1}\right)_{\nu \nu^\prime}(\omega) = \frac{1}{4}\begin{pmatrix}  \frac{1}{x_-} + \frac{1}{y_-} &&  \frac{1}{x_-} - \frac{1}{y_-} \\  \frac{1}{x_-} - \frac{1}{y_-} &&  \frac{1}{x_-} + \frac{1}{y_-} \end{pmatrix}
+% \end{aligned}\end{equation}
+% $g_0$ and $g_1$ can now be read off:
+% \begin{equation}\begin{aligned}
+% 	g_0 = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{00} = \frac{1}{4}\left( \frac{1}{x_-} + \frac{1}{y_-}\right), && g_1 = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{01} = \frac{1}{4}\left( \frac{1}{x_-} - \frac{1}{y_-}\right)
+% \end{aligned}\end{equation}
+% Similarly, we obtain the other matrix:
+% \begin{equation}\begin{aligned}
+% 	\left(\mathcal{G}_D\right)_{\overline{\nu \nu^\prime}}(-\omega) = \begin{pmatrix} x_+ + y_+ && x_+ - y_+ \\ x_+ - y_+ && x_+ + y_+ \end{pmatrix}
+% \end{aligned}\end{equation}
+% which gives
+% \begin{equation}\begin{aligned}
+% 	\overline{g_0} = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{00} = \frac{1}{4}\left( \frac{1}{x_+} + \frac{1}{y_+}\right), && \overline{g_1} = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{01} = \frac{1}{4}\left( \frac{1}{x_+} - \frac{1}{y_+}\right)
+% \end{aligned}\end{equation}
+% Substituting these values of $g_0, g_1, \overline{g_0}$ and $\overline{g_1}$ in eq.~\ref{Gk_dim} gives the same expression as that obtained in eq.~\ref{Gk0}.
+
+%To verify this result, we just need to show the momentum space Greens function of the Hubbard dimer calculated from the exact eigenstates (as shown in the appendix) also takes the same form.
+Using the Fourier transform, we can write
+%\begin{equation}\begin{aligned}
+%	G(k=0, \sigma) = G(r=0, \sigma) + G(r=a, \sigma)
+%\end{aligned}\end{equation}
+%The terms on the RHS are the real space local and nearest-neighbour Greens functions of the Hubbard dimer.
+%Therefore, the Greens function at $\vec r=0$ for the Hubbard dimer can be expressed as
+%\begin{equation}\begin{aligned}
+%	G_H(\vec r = 0, \omega) = \frac{1}{2}\left[\frac{1}{g_0 + g_1} + \frac{1}{g_0 - g_1}\right]  = \frac{g_0}{g_0^2 - g_1^2}
+%\end{aligned}\end{equation}
+%For the Hubbard dimer, we substitute $N=2, w=1$ into the expressions for $g_{0}$ and $g_{1}$ to obtain
+%\begin{equation}\begin{aligned}
+%	&g_0 = \frac{1}{\text{Det }G_D}\left( G_D \right)_{00}, &g_1 = -\frac{1}{\text{Det }G_D}\left( G_D \right)_{01}
+%\end{aligned}\end{equation}
+%The Greens function at the zeroth site then becomes
+%\begin{equation}\begin{aligned}
+%	G_H(\vec r = 0, \omega) = \text{Det }G_D\frac{\left(G_D\right)_{00}}{\left(G_D\right)_{00}^2 - \left(G_D\right)_{01}^2} = \text{Det }G_D\frac{\left(G_D\right)_{00}}{\text{Det }G_D} = \left(G_D\right)_{00}
+%\end{aligned}\end{equation}
+%This is the expected result.
+Because the full Hubbard model in this case was simply the Hubbard dimer, \(G_H(\vec r = 0, \omega)\) should just be \(\left(G_D\right)_{00}\).
+Although this is a trivial example (we matched the Hubbard dimer with another Hubbard dimer), this atleast tells us that this algorithm for calculating the real space local Greens function from the inverse Greens function matrix elements is sensible.
+
+\subsection{On the Bethe lattice}
+Another test involves considering the case of infinite number of nearest neighbours $w\to\infty$ (the coordination number, and effectively the dimensionality).
+Here, as has been argued in the DMFT literature, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$ such that the kinetic energy of the associated tight-binding lattice model is finite.
+This allows for the competition between the kinetic and potential terms of the Hamiltonian to drive a metal-insulator transition in the limit of $w\to\infty$ as well.
+Further, it has been argued in the DMFT literature that the Greens function matrix of the Hubbard model on the Bethe lattice with $w\to\infty$ becomes purely local (i.e., it has vanishing inter-site matrix elements).
+We can also see this from eqs.\eqref{G_mat_nn}- the nearest-neighbour inverse Greens function vanishes in the limit of $w \to \infty$:
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\sum_{n} {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}} \implies \lim_{w \to \infty}\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma \to 0
+\end{aligned}\end{equation}
+There we used the fact since at half-filling on an $SU(2)$ symmetric mode, we expect $\left<\hat n_{i \uparrow} \right> = \frac{1}{2}$, the orthonormal expansion of $c^\dagger_{i \sigma}\ket{\tilde \Phi_0} = \sum_n C^i_n \ket{n}$ to be constrained to $\sum_n |C_n^i|^2 = \frac{1}{2}$, such that the only term that scales with $w$ is $w$ itself.
+This result then implies that $G^{H}$ matrix has no $k$ dependence.
+\\\\
+In this limit, the self-energy also simplifies:
+\begin{equation}\begin{aligned}
+	\lim_{w \to \infty}\Sigma_H(\vec k,\omega) &= \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n \lim_{w \to \infty}\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1} \\
+						   &=\omega +t^{H}\xi_{\vec k} - \frac{N}{2}\frac{1}{\sum_n \left[ \frac{|C^0_{n}|^2}{g_n} - \frac{|\overline C^0_{n}|^2}{\overline{g_n}}\right]}
+\end{aligned}\end{equation}
+We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.
+
 \section{Future goals}

### 2021-08-20 notes.tex
implemented the formulation numerically, manager part is left
completed numerical implementation, obtained some preliminary plots

@@
 	G_H(\omega)_\text{loc} &= \left(\mathcal{G}_H(\omega)\right)_{ii} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ii}} = \frac{2}{N}\sum_n\left(|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}}\right)\\
-	G_H(\omega)_\text{nn} &= \left(\mathcal{G}_H(\omega)\right)_{ij} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ji}} = \frac{2}{Nw}\sum_n\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\\
+	G_H(\omega)_\text{nn} &= \left(\mathcal{G}_H(\omega)\right)_{ij} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ji}} = \frac{2}{Nw}\sum_n\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\\
 \end{aligned}\end{equation}
@@
 			     &= G_H (\omega)_\text{loc} + G_H (\omega)_\text{nn} \xi_{\vec k}\\
-			     &= \frac{2}{N}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
+			     &= \frac{2}{N}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{2}{N\pi} \textrm{Im}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\\
+	A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{2}{N\pi} \textrm{Im}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\\
 A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = \frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
@@
 \begin{equation}\begin{aligned}
-	\Sigma_H(\vec k,\omega) = \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1}
+	\Sigma_H(\vec k,\omega) = \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1}
 \end{aligned}\end{equation}
@@
 	\label{Gk_dim}
-	G(k=0,\uparrow) = \sum_n\left[\left(|C^0_{n}|^2 + {C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + {C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
+	G(k=0,\uparrow) = \sum_n\left[\left(|C^0_{n}|^2 + {C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + {\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\lim_{w \to \infty}\Sigma_H(\vec k,\omega) &= \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n \lim_{w \to \infty}\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1} \\
+	\lim_{w \to \infty}\Sigma_H(\vec k,\omega) &= \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n \lim_{w \to \infty}\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1} \\
 						   &=\omega +t^{H}\xi_{\vec k} - \frac{N}{2}\frac{1}{\sum_n \left[ \frac{|C^0_{n}|^2}{g_n} - \frac{|\overline C^0_{n}|^2}{\overline{g_n}}\right]}
@@
 
+\section*{Appendix; Contributions of various excitations to the site local spectral function}
+The site local spectral function is
+\begin{equation}\begin{aligned}
+	A(0\uparrow, \omega) = \left( \frac{1}{4} - \frac{t}{\Delta} \right)\left[\delta(\omega - \frac{\Delta}{2} - t) + \delta(\omega + \frac{\Delta}{2} + t)\right]\nonumber + \left( \frac{1}{4} + \frac{t}{\Delta} \right) \left[\delta(\omega - \frac{\Delta}{2} + t) + \delta(\omega + \frac{\Delta}{2} - t)\right]
+\end{aligned}\end{equation}
+If the eigenstates of the $N=1, S^z = - \frac{1}{2}$ sector are $\ket{1 \pm \downarrow}$ and those of $N=3, S^z = \frac{1}{2}$ sector are $\ket{3 \pm \uparrow}$, this spectral function originates from the expression:
+\begin{equation}\begin{aligned}
+	A(0\uparrow, \omega) =& \braket{1 \downarrow_- | c_{0 \uparrow} | \text{GS}} \delta\left(\omega + \frac{\Delta}{2} + t\right) + \braket{2 \uparrow_+ | c^\dagger_{0 \uparrow} | \text{GS}}\delta\left(\omega - \frac{\Delta}{2} - t\right) \\
+			      &+ \braket{1 \downarrow_+ | c_{0 \uparrow} | \text{GS}}\delta\left(\omega + \frac{\Delta}{2} - t\right) + \braket{2 \uparrow_- | c^\dagger_{0 \uparrow} | \text{GS}}\delta(\omega - \frac{\Delta}{2} + t)
+\end{aligned}\end{equation}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.7\textwidth]{./dimer-peaks.png}
+	\caption{Position, weight and nature of each of the peaks in the Hubbard dimer site local spectral function}
+\end{figure}
+
 \section*{Appendix: Relation between single-particle Greens function and the Greens function operator $(T=0)$}

### 2021-08-23 notes.tex
obtained 1-3-2 peak journey from ED and spectral representation of dimer in bath, albeit through a strange choice of the broadening
started rewriting in terms of dimer+bath system

@@
 \usepackage[margin=0.5in,bottom=0.6in]{geometry}
+\graphicspath{{./figures/}}
 \usepackage[T1]{fontenc}
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{./cluster-bath.png}
+	\includegraphics[width=0.8\textwidth]{cluster-bath.png}
 	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$.
@@
 The fixed point Hamiltonian will in general involve the impurity site (with renormalised parameters $\epsilon_d^*, U^*$) interacting with a smaller number of momentum states.
-Assuming the impurity-bath couplings are much larger than the dispersion of the bath, we can approximate the conduction bath part by a zero-mode of the kinetic energy part.
+% Assuming the impurity-bath couplings are much larger than the dispersion of the bath, we can approximate the conduction bath part by a zero-mode of the kinetic energy part.
 The zero mode is defined as $c_0 = \frac{1}{\sqrt N}\sum_k c_k$, so it is just the zeroth site.
-What this means is that all the momentum states will then collapse to a single site (which we call the zero mode site, and represents the origin of the lattice).
+% What this means is that all the momentum states will then collapse to a single site (which we call the zero mode site, and represents the origin of the lattice).
 We will also pick out the zeroth site part of the onsite correlation part, and replace that with a single correlation coupling $U^A_z$.
-Such a model, shown in fig.~\ref{and_mol} is exactly solvable.
-\begin{equation}\begin{aligned}
-	H^A_\text{corr} = -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + U^A\tau_{d \uparrow}\tau_{d \downarrow} + U^A_z\tau_{z \uparrow}\tau_{z \downarrow}
-\end{aligned}\end{equation}
-The motivation for extracting the zero mode is that it leads to a very simple effective Hamiltonian (the asymmetric Anderson molecule) without losing much of the low energy physics.
-\\\\
-We will then create the the entire Hubbard Hamiltonian by combining the zero-mode Hamiltonians according to a prescription which is guided by the symmetries of the problem.
-The impurity electron will be read off as an arbitrary site, \(p\), of the lattice, while the zero-mode site becomes the site that is nearest to it.
-We will first demonstrate this explicitly for the Hubbard dimer.
-Then we will show how we can create a full Hubbard Hamiltonian by joining Anderson molecule Hamiltonians.
+% Such a model, shown in fig.~\ref{and_mol} is exactly solvable.
+At this point, we will assume that we have a Hubbard model in mind that has motivated a correlated SIAM as the auxiliary system, and we have performed renormalisation group analysis on this auxiliary system to get down to an effective Hamiltonian.
+We will also assume that the parameters of the auxiliary system have been chosen such that in the effective Hamiltonian, the impurity and zero mode have the same onsite repulsion: $U^A = U^A_z$ (this is required for translational invariance).
+\\\\
+To obtain a comparatively simple but physically well-motivated auxiliary model, we identify $\sum_k c_k = \sqrt N c_0$; \(c_0\) is the operator for the zeroth site (the site nearest to the impurity).
+We will call the set of all \(N-2\) sites apart from the impurity and this zeroth site as the "effective bath".
+The fixed point Hamiltonian can be separated into these parts: an isolated impurity part, an isolated zeroth site part, an isolated effective bath part, hopping between impurity and the zeroth site and hopping between the zeroth site and the effective bath.
+\textit{As a simplification, we will ignore the correlation term \((U)\) on the effective bath}.
+In preparation of a symmetrization procedure, we will relabel the impurity site as 0, and the zeroth site as 1.
+With all these steps, the Hamiltonian takes the form:
+\begin{equation}\begin{aligned}
+	% H^A_\text{corr} = -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + U^A\tau_{d \uparrow}\tau_{d \downarrow} + U^A_z\tau_{z \uparrow}\tau_{z \downarrow}
+	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow}}_\text{imp.
+\& zero-mode isolated} - \underbrace{t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{0-1 coupling} - \underbrace{t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{1 \& eff.
+bath coupling} - \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff.
+bath isolated}
+\end{aligned}\end{equation}
+This Hamiltonian is, however, explicitly asymmetric between the sites 0 and 1 (the effective bath couples only to 1).
+To rectify that, we will symmetrize the coupling between the effective bath and the sites 0 and 1, by exchanging the sites 0 and 1.
+The resultant Hamiltonian is
+\begin{equation}\begin{aligned}
+	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow} - t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{2-site Hubbard model} +\underbrace{- t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)- t^A\sum_{j \in \atop{\text{NN of 0}}}\left(c^\dagger_{0\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{dimer \& eff.
+bath coupling} \\
+	- \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff. bath isolated}
+\end{aligned}\end{equation}
+% The motivation for extracting the zero mode is that it leads to a very simple effective Hamiltonian (the asymmetric Anderson molecule) without losing much of the low energy physics.
+To further simplify this Hamiltonian, \textit{we will combine the nearest neighbour sites of \(1\) and \(0\) into a single site}.
+\begin{equation}\begin{aligned}
+	\sum_{\vec k}^\text{eff. bath} = c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}
+\end{aligned}\end{equation}
+This single site will act as the zeroth site of the effective bath, and it means that both sites of the Hubbard dimer hybridizes with the effective through just a single site.
+With this assumption, the Hamiltonian for "a Hubbard dimer hopping into an effective bath" takes the simple form
+\begin{equation}\begin{aligned}
+	\tilde H^D = H^D(0,1) - t^D \sum_{\vec k}^\text{eff.
+bath}\left(c^\dagger_{0\sigma}c_{\vec k,\sigma} + c^\dagger_{0\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff.
+bath}\epsilon_{\vec k}\hat n_{\vec k}
+\end{aligned}\end{equation}
+\(H^D(0,1)\) is the Hubbard dimer Hamiltonian:
+\begin{equation}\begin{aligned}
+	\label{dimer_ham}
+	H^D(0,1) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)
+\end{aligned}\end{equation}
+This Hubbard dimer is shown in fig.~\ref{hubb-dim}.
+\\\\
+We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice.
+We will then create the the entire Hubbard Hamiltonian by combining the members of this family of Hamiltonians according to a prescription which is guided by the symmetries of the problem.
 \begin{figure}[htpb]
 	\centering
-	\includegraphics[width=0.6\textwidth]{./gen_siam.png}
+	\includegraphics[width=0.6\textwidth]{gen_siam.png}
 	\caption{Correlated asymmetric Anderson molecule schematic version.
@@
 \end{figure}
-At this point, we will assume that we have a Hubbard model in mind that has motivated a correlated SIAM as the auxiliary system, and we have performed renormalisation group analysis on this auxiliary system to get down to an effective Hamiltonian.
-We will also assume that the parameters of the auxiliary system have been chosen such that in the effective Hamiltonian, the impurity and zero mode have the same onsite repulsion: $U^A = U^A_z$ (this is required for translational invariance).
-What this all means is that the RG analysis of the auxiliary model (appropriately chosen to model the bare Hubbard Hamiltonian) has led to a stable fixed point theory effective Hamiltonian described by a Hubbard dimer
-\begin{equation}\begin{aligned}
-	H^D(U^D, t^D) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)
-\end{aligned}\end{equation}
-This Hubbard dimer is shown in fig.~\ref{hubb-dim}.
 \begin{figure}[htpb!]
 	\centering
-	\includegraphics[width=0.6\textwidth]{./hubb_dim.png}
+	\includegraphics[width=0.6\textwidth]{hubb_dim.png}
 	\caption{Hubbard dimer schematic version. It again consists of two sites, like the Anderson molecule, but now both sites have onsite repulsion, and their is again inter-site hopping.}
@@
 \par\noindent
-The next step is to restore the lost translational invariance of the full system.
-We intend to do this by recreating a full Hubbard model, $\tilde H$, through the iterative real-space translation of the Hubbard dimer effective Hamiltonian obtained above.
-We will describe this process in detail below.
 However, we first specify the two approximations made along the entire journey from the original Hubbard model to the reconstructed one:
@@
 This leads to a fixed-point Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$.
-At this point, we extract a zero mode of this Hamiltonian to obtain the Hubbard dimer Hamiltonian: $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$, where $Z$ defines the projection operator that extracts the zero mode from the effective stable fixed Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$.
+At this point, we go from the fixed point Hamiltonian to the dimer+bath Hamiltonian: $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$.
 This constitutes the second approximations we make.
-This approximation further reduces the symmetry, because we have dropped all other lattice sites and kept just the zeroth lattice site (i.e., the site to which the impurity is coupled through single electron hybridisation).
+This constitutes the second approximations we make.
 \end{itemize}
@@
 \\\\
-For each site \(i\) out of the \(N\) sites (having nearest neighbours \(\{i_j, j\in\left[1,w\right]\}\)), we will create \(w\) local Hamiltonians \(\{H^H_{i,i_j}, i\in \left[1,N\right], j \in \left[1,w\right]  \}\) out of the Hubbard dimer Hamiltonians, by setting the impurity index \(d\) to \(i\) and the zero-mode index \(z\) to \(i_j\).
-We will also need to suitably transform the Hamiltonian parameters \(U^A, t^A\), but we will figure those out as we go along.
-All \(N\) sites will then produce \(Nw\) local Hamiltonians in total, and the general Hubbard Hamiltonian should be the average of these local Hamiltonians.
+For each nearest-neighbour pair \(i,j\), we will create a local Hamiltonian \(H^D_{i,j}\) from the Hamiltonian of the Hubbard dimer with bath (we will interpret the effective bath as the remaining \(N-2\) sites of the lattice, apart from \(i,j\)).
+We will need to suitably transform the Hamiltonian parameters \(U^D, t^D\), but we will figure those out as we go along.
+Since the number of nearest neighbour pairs is \(\frac{Nw}{2}\), the general Hubbard Hamiltonian should be the average of these local Hamiltonians.
 \\\\
@@
 \begin{equation}\begin{aligned}
-	H^D_{i,i_j} = -t^D\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i_j\sigma} + \text{h.c.}\right) + U^D\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + U^D\hat \tau_{i_j \uparrow}\hat \tau_{i_j \downarrow}
-\end{aligned}\end{equation}
-We havent transformed the dimer parameters \(U^D, t^D\) to the Hubbard parameters yet. The sum of all local Hamiltonians for a particular site \(i\) then gives the total Hamiltonian for that site:
-\begin{equation}\begin{aligned}
-	H^D_{i} = \sum_{j\in\left[1,w\right]}H^D_{i,i_j} = \sum_{\sigma\atop{j \in \text{N.N.
-of }i}}-t^D\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^D\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + U^D\sum_{j \in \text{N.N.
-of }i}\hat \tau_{j \uparrow}\hat \tau_{j \downarrow}
-\end{aligned}\end{equation}
-If we now sum over all the lattice sites and take the average of all the Hamiltonians (\(Nw\) in number), we get
-\begin{equation}\begin{aligned}
-	\tilde H &= \frac{1}{Nw}\sum_{i=1}^N H^D_{i} \\
+	H^D_{i,j} = H^D(i, j) -t^A\sum_{k \in \text{NN of i}}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.}\right)-t^A\sum_{k \in \text{NN of j}}\left(c^\dagger_{j\sigma}c_{k\sigma} + \text{h.c.}\right) - t^A\sum_{\left<k,q\right> \neq i,j}\left(c^\dagger_{j\sigma}c_{k\sigma} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+\(H^D(0 \to i, 1 \to j)\) is the Hubbard dimer Hamiltonian in eq.~\ref{dimer_ham} with the indices 0 and 1 replaced by \(i, j\) respectively.
+Note that this local Hamiltonian actually has all the hoppings of the full Hubbard model, but the correlation is present just on the sites \(i,j\).
+We havent transformed the dimer parameters \(U^D, t^D\) to the Hubbard parameters yet.
+\\\\
+If we now sum over all the nearest-neighbour pairs and take the average of all the Hamiltonians (\(\frac{1}{2}Nw\) in number), we get
+\begin{equation}\begin{aligned}
+	\tilde H &= \frac{2}{Nw}\sum_{\left<ij \right>}^N H^D_{i,j} \\
+		 &= -t^A\sum_{\left<ij\right>}\left( c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.} \right) + \frac{2}{N}\sum_i U \tau_{i \uparrow}\tau_{i \downarrow}\\
 		      &= \frac{1}{Nw}\left[\sum_{\sigma, i=1}^N\sum_{j \in \text{NN of }j}-t^D\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^D\sum_{i=1}^N \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + U^D\sum_{i=1}^N\sum_{j \in \text{N.N.
@@
 	\hspace*{\fill}
-	\includegraphics[width=0.7\textwidth]{./lattice.png}
+	\includegraphics[width=0.7\textwidth]{lattice.png}
 	\hspace*{\fill}
@@
 	\centering
-	\includegraphics[width=0.2\textwidth]{./dimer_dispersion.png}
+	\includegraphics[width=0.2\textwidth]{dimer_dispersion.png}
 	\caption{Hubbard dimer with dispersion that connects to both sites}
@@
 	\centering
-	\includegraphics[width=0.7\textwidth]{./dimer-peaks.png}
+	\includegraphics[width=0.9\textwidth]{dimer-peaks.png}
 	\caption{Position, weight and nature of each of the peaks in the Hubbard dimer site local spectral function}

### 2021-08-23 notes.tex
added some figures

@@
 \end{aligned}\end{equation}
-This Hamiltonian is, however, explicitly asymmetric between the sites 0 and 1 (the effective bath couples only to 1).
-To rectify that, we will symmetrize the coupling between the effective bath and the sites 0 and 1, by exchanging the sites 0 and 1.
-The resultant Hamiltonian is
-\begin{equation}\begin{aligned}
-	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow} - t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{2-site Hubbard model} +\underbrace{- t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)- t^A\sum_{j \in \atop{\text{NN of 0}}}\left(c^\dagger_{0\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{dimer \& eff.
-bath coupling} \\
-	- \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff. bath isolated}
-\end{aligned}\end{equation}
-% The motivation for extracting the zero mode is that it leads to a very simple effective Hamiltonian (the asymmetric Anderson molecule) without losing much of the low energy physics.
-To further simplify this Hamiltonian, \textit{we will combine the nearest neighbour sites of \(1\) and \(0\) into a single site}.
-\begin{equation}\begin{aligned}
-	\sum_{\vec k}^\text{eff. bath} = c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}
-\end{aligned}\end{equation}
-This single site will act as the zeroth site of the effective bath, and it means that both sites of the Hubbard dimer hybridizes with the effective through just a single site.
-With this assumption, the Hamiltonian for "a Hubbard dimer hopping into an effective bath" takes the simple form
-\begin{equation}\begin{aligned}
-	\tilde H^D = H^D(0,1) - t^D \sum_{\vec k}^\text{eff.
-bath}\left(c^\dagger_{0\sigma}c_{\vec k,\sigma} + c^\dagger_{0\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff.
-bath}\epsilon_{\vec k}\hat n_{\vec k}
-\end{aligned}\end{equation}
-\(H^D(0,1)\) is the Hubbard dimer Hamiltonian:
-\begin{equation}\begin{aligned}
-	\label{dimer_ham}
-	H^D(0,1) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)
-\end{aligned}\end{equation}
-This Hubbard dimer is shown in fig.~\ref{hubb-dim}.
-\\\\
-We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice.
-We will then create the the entire Hubbard Hamiltonian by combining the members of this family of Hamiltonians according to a prescription which is guided by the symmetries of the problem.
 \begin{figure}[htpb]
@@
 	\caption{Correlated asymmetric Anderson molecule schematic version.
-It consists of two sites, impurity(blue) and zero mode(green).
-The impurity site has onsite repulsion, and their is inter-site hopping.}
+It consists of an impurity site (blue) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink).
+The other sites (green) form the rest of the bath.
+Just the impurity site and the zeroth site have onsite repulsion.}
 	\label{and_mol}
 \end{figure}
+This Hamiltonian is depicted in fig.~\ref{and_mol}.
+Such a Hamiltonian is, however, explicitly asymmetric between the sites 0 and 1 (the effective bath couples only to 1).
+To rectify that, we will symmetrize the coupling between the effective bath and the sites 0 and 1, by exchanging the sites 0 and 1.
+The resultant Hamiltonian is
+\begin{equation}\begin{aligned}
+	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow} - t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{2-site Hubbard model} +\underbrace{- t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)- t^A\sum_{j \in \atop{\text{NN of 0}}}\left(c^\dagger_{0\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{dimer \& eff.
+bath coupling} \\
+	- \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff. bath isolated}
+\end{aligned}\end{equation}
+% The motivation for extracting the zero mode is that it leads to a very simple effective Hamiltonian (the asymmetric Anderson molecule) without losing much of the low energy physics.
+To further simplify this Hamiltonian, \textit{we will combine the nearest neighbour sites of \(1\) and \(0\) into a single site}.
+\begin{equation}\begin{aligned}
+	\sum_{\vec k}^\text{eff. bath} = c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}
+\end{aligned}\end{equation}
+This single site will act as the zeroth site of the effective bath, and it means that both sites of the Hubbard dimer hybridizes with the effective through just a single site.
+With this assumption, the Hamiltonian for "a Hubbard dimer hopping into an effective bath" takes the simple form
+\begin{equation}\begin{aligned}
+	\tilde H^D = H^D(0,1) - t^D \sum_{\vec k}^\text{eff.
+bath}\left(c^\dagger_{0\sigma}c_{\vec k,\sigma} + c^\dagger_{0\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff.
+bath}\epsilon_{\vec k}\hat n_{\vec k}
+\end{aligned}\end{equation}
+\(H^D(0,1)\) is the Hubbard dimer Hamiltonian (shown in fig.~\ref{hubb-dim}):
+\begin{equation}\begin{aligned}
+	\label{dimer_ham}
+	H^D(0,1) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)
+\end{aligned}\end{equation}
 \begin{figure}[htpb!]
 	\centering
-	\includegraphics[width=0.6\textwidth]{hubb_dim.png}
+	\includegraphics[width=0.4\textwidth]{hubb_dim.png}
 	\caption{Hubbard dimer schematic version. It again consists of two sites, like the Anderson molecule, but now both sites have onsite repulsion, and their is again inter-site hopping.}
@@
 \end{figure}
+This entire procedure is depicted in fig.~\ref{dimer-bath}.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.8\textwidth]{dimer_bath.png}
+	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.}
+	\label{dimer-bath}
+\end{figure}
+We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice.
+We will then create the the entire Hubbard Hamiltonian by combining the members of this family of Hamiltonians according to a prescription which is guided by the symmetries of the problem.
 \par\noindent

### 2021-08-24 notes.tex
minor edits

@@
 \begin{equation}\begin{aligned}
+	\label{dimer_p_bat}
 	\tilde H^D = H^D(0,1) - t^D \sum_{\vec k}^\text{eff.
-bath}\left(c^\dagger_{0\sigma}c_{\vec k,\sigma} + c^\dagger_{0\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff.
+bath}\left(c^\dagger_{0\sigma}c_{\vec k,\sigma} + c^\dagger_{1\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff.
 bath}\epsilon_{\vec k}\hat n_{\vec k}
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{dimer_bath.png}
-	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.}
+	\includegraphics[width=0.3\textwidth]{dimer_bath.png}
+	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.
+We first add the asymmetric Hamiltonians to get a symmetrized Hamiltonian.
+In the symmetrized Hamiltonian, the dimer has \(w\) entry points into the bath, \(w\) being the coordination number of the lattice.
+We then merge these \(w\) lattice sites (enclosed in the black box) into a single lattice site.}
 	\label{dimer-bath} 
@@
 We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice.
-We will then create the the entire Hubbard Hamiltonian by combining the members of this family of Hamiltonians according to a prescription which is guided by the symmetries of the problem.
-\par\noindent
-However, we first specify the two approximations made along the entire journey from the original Hubbard model to the reconstructed one:
+The next step in the programme is to tile the real-space lattice with this dimer+bath Hamiltonian \(\tilde H_D\) to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H = T\left[ \tilde H^{D} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the dimer Hamiltonian to span the target real-space lattice.
+We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.
+\begin{equation}\begin{aligned}
+	\color{red}{\tilde H = - \frac{2t^D}{Nw}\sum_{\sigma \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)}
+\end{aligned}\end{equation}
+What that means is that we have placed the Hubbard dimer at all nearest neighbour pairs to reconstruct a new Hubbard model.
+If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as dropping the correlation on the bath sites, we can write
+\begin{equation}\begin{aligned}
+	\label{app2}
+	\tilde H = \mathcal{U} H^H \mathcal{U}^{-1} = TZ\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right]Z^{-1} T^{-1}~,
+\end{aligned}\end{equation}
+where $\mathcal{U} = TZ\mathcal{U}_{A}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation that maps from the original to the reconstructed Hubbard Hamiltonian.
+The existence of $U$ is contingent on how good the approximations are.
+\\\\
+We mention the two approximations made along the entire journey from the original Hubbard model to the reconstructed one here.
 \begin{itemize}
@@
 This leads to a fixed-point Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$.
-At this point, we go from the fixed point Hamiltonian to the dimer+bath Hamiltonian: $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$.
-This constitutes the second approximations we make.
-This constitutes the second approximations we make.
+At this point, we go from the fixed point Hamiltonian to the dimer+bath Hamiltonian in eq.~\ref{dimer_p_bat}.
+If we represent this transformation from the fixed point Hamiltonian to the Hamiltonian in eq.~\ref{dimer_p_bat} by an operator \(Z\), we can write $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$.
+This constitutes the second approximation we make.
 \end{itemize}
-We now tile the real-space lattice with this Hubbard dimer Hamiltonian to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H = T\left[ H^{D} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the dimer Hamiltonian to span the target real-space lattice.
-We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.
-\begin{equation}\begin{aligned}
-	\tilde H = - \frac{2t^D}{Nw}\sum_{\sigma \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
-\end{aligned}\end{equation}
-What that means is that we have placed the Hubbard dimer at all nearest neighbour pairs to reconstruct a new Hubbard model.
-If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as taking the zero mode, we can write
-\begin{equation}\begin{aligned}
-	\label{app2}
-	\tilde H = \mathcal{U} H^H \mathcal{U}^{-1} = TZ\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right]Z^{-1} T^{-1}~,
-\end{aligned}\end{equation}
-where $\mathcal{U} = TZ\mathcal{U}_{A}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation that maps from the original to the reconstructed Hubbard Hamiltonian.
-%The content of the above equation is that we expect the final tiled translationally invariant new (renormalised) Hubbard Hamiltonian to be connected to the bare parent Hubbard model through some unitary/similarity transformation $\mathcal{U}$.
-The existence of $U$ is contingent on how good the approximations are, and strictly speaking needs to be verified.
 
@@
 \\\\
-The local Hamiltonians look like
-\begin{equation}\begin{aligned}
-	H^D_{i,j} = H^D(i, j) -t^A\sum_{k \in \text{NN of i}}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.}\right)-t^A\sum_{k \in \text{NN of j}}\left(c^\dagger_{j\sigma}c_{k\sigma} + \text{h.c.}\right) - t^A\sum_{\left<k,q\right> \neq i,j}\left(c^\dagger_{j\sigma}c_{k\sigma} + \text{h.c.}\right)
+We recall the dimer+bath Hamiltonian here, since we are going to create the full Hamiltonian by combining various realizations of that Hamiltonian:
+\begin{equation}\begin{aligned}
+	\tilde H^D = H^D(0,1) - t^D \sum_{\vec k}^\text{eff.
+bath}\left(c^\dagger_{0\sigma}c_{\vec k,\sigma} + c^\dagger_{0\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff.
+bath}\epsilon_{\vec k}\hat n_{\vec k}
+\end{aligned}\end{equation}
+We will first create a "local" Hamiltonian, where one particular nearest neighbour pair \((i,j)\) makes up the dimer sites of the Hamiltonian, while the rest \(N-2\) sites of the lattice make up the effective bath.
+The zero-mode site of the effective bath is mapped to one of the nearest-neighbours of \(i\) or \(j\)
+\begin{equation}\begin{aligned}
+	\tilde H^D_(i,j) = H^D(i, j) - t^D \sum_{\vec k}^\text{eff.
+bath (i,j)}\left(c^\dagger_{i\sigma}c_{\vec k,\sigma} + c^\dagger_{0\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff.
+bath (i,j)}\epsilon_{\vec k}\hat n_{\vec k}
 \end{aligned}\end{equation}

### 2021-08-24 notes.tex
rewrote the notes with dimer+bath auxiliary model in mind

@@
 \begin{equation}\begin{aligned}
-	\sum_{\vec k}^\text{eff. bath} = c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}
+	c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}
 \end{aligned}\end{equation}
@@
 	\label{dimer_p_bat}
-	\tilde H^D = H^D(0,1) - t^D \sum_{\vec k}^\text{eff.
-bath}\left(c^\dagger_{0\sigma}c_{\vec k,\sigma} + c^\dagger_{1\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff.
-bath}\epsilon_{\vec k}\hat n_{\vec k}
+	\tilde H^D = H^D(0,1) - t^D \sum_{\sigma}\left(c^\dagger_{0\sigma}c_{z\sigma} + c^\dagger_{1\sigma}c_{z\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
-We will first create a "local" Hamiltonian, where one particular nearest neighbour pair \((i,j)\) makes up the dimer sites of the Hamiltonian, while the rest \(N-2\) sites of the lattice make up the effective bath.
-The zero-mode site of the effective bath is mapped to one of the nearest-neighbours of \(i\) or \(j\)
-\begin{equation}\begin{aligned}
-	\tilde H^D_(i,j) = H^D(i, j) - t^D \sum_{\vec k}^\text{eff.
-bath (i,j)}\left(c^\dagger_{i\sigma}c_{\vec k,\sigma} + c^\dagger_{0\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff.
-bath (i,j)}\epsilon_{\vec k}\hat n_{\vec k}
-\end{aligned}\end{equation}
-\(H^D(0 \to i, 1 \to j)\) is the Hubbard dimer Hamiltonian in eq.~\ref{dimer_ham} with the indices 0 and 1 replaced by \(i, j\) respectively.
-Note that this local Hamiltonian actually has all the hoppings of the full Hubbard model, but the correlation is present just on the sites \(i,j\).
+We now choose a particular nearest neighbour pair from the full lattice, say \((i,j\), and one site that is nearest neighbour to this pair, call that \(l\).
+We will first create a "local" Hamiltonian, where one particular nearest neighbour pair \((i,j)\) makes up the dimer sites of the Hamiltonian, while the rest \(N-2\) sites of the lattice make up the effective bath and the site \(l\) forms the zeroth site of the bath.
+\begin{equation}\begin{aligned}
+	\label{Hdjl}
+	\tilde H^D(i, j, l) \equiv \tilde H^D(0\to i, 1\to j, z \to l) = H^D(i, j) - t^D \sum_{\sigma}\left(c^\dagger_{i\sigma}c_{l,\sigma} + c^\dagger_{j\sigma}c_{l,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^{\text{eff.
+bath (i,j)}\atop{z = l}}\epsilon_{\vec k}\hat n_{\vec k}\\
+\end{aligned}\end{equation}
+\(H^D(i, j)\) is the Hubbard dimer Hamiltonian in eq.~\ref{dimer_ham} with the indices 0 and 1 replaced by \(i, j\) respectively.
+This is not the total local Hamiltonian for the nearest neighbour pair \((i,j\), because it has just one nearest neighbour of the dimer, namely \(l\).
+To get the full thing, we need to \textit{average} over all the nearest neighbours of the pair \(i,j\), \(2(w-1)\) in number.
+What we mean by nearest neighbours of the dimer pair \((i,j)\) is made clear in \ref{dimer-nn}.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.3\textwidth]{dimer-nn.png}
+	\caption{Blue circles indicate the dimer sites (enclosed by dotted circle).
+Green circles are the sites that are nearest neighbour to the dimer and the ones that are being summed over under the index \(l\).
+Orange circles are sites that are \textit{not} nearest neighbour to the dimer.}
+	\label{dimer-nn}
+\end{figure}
+
+The total  Hamiltonian for a particular dimer pair \((i,j)\) then looks like:
+\begin{equation}\begin{aligned}
+	\tilde H^D(i, j) &= \frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}} \left[H^D(i, j) - t^D \sum_{\sigma}\left(c^\dagger_{i\sigma}c_{l,\sigma} + c^\dagger_{j\sigma}c_{l,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^{\text{eff.
+bath (i,j)}\atop{z = l}}\epsilon_{\vec k}\hat n_{\vec k}\right]\\
+			 &= H^D(i, j) + \frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\left[- t^D \sum_\sigma\left(c^\dagger_{i\sigma}c_{l,\sigma} + c^\dagger_{j\sigma}c_{l,\sigma} + \text{h.c.}\right) + \sum_{\vec k,\sigma}^{\text{eff.
+bath (i,j)}\atop{z = l}}\epsilon_{\vec k}\hat n_{\vec k}\right]
+\end{aligned}\end{equation}
+We now translate this Hamiltonian over all nearest neighbour pairs on the lattice, and take the average:
+\begin{equation}\begin{aligned}
+	\label{H_tiled}
+	\tilde H = \frac{2}{Nw}\sum_{\left<ij\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\tilde H^D(i, j, l) = \frac{2}{N}U^D\sum_{i} \tau_{i \uparrow}\tau_{i \downarrow} - \frac{2}{Nw}\left(1 + \frac{Nw}{2}\right)t^D\sum_{\left<ij\right>}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+% Note that this local Hamiltonian actually has all the hoppings of the full Hubbard model, but the correlation is present just on the sites \(i,j\).
 We havent transformed the dimer parameters \(U^D, t^D\) to the Hubbard parameters yet.
-\\\\
-If we now sum over all the nearest-neighbour pairs and take the average of all the Hamiltonians (\(\frac{1}{2}Nw\) in number), we get
-\begin{equation}\begin{aligned}
-	\tilde H &= \frac{2}{Nw}\sum_{\left<ij \right>}^N H^D_{i,j} \\
-		 &= -t^A\sum_{\left<ij\right>}\left( c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.} \right) + \frac{2}{N}\sum_i U \tau_{i \uparrow}\tau_{i \downarrow}\\
-		      &= \frac{1}{Nw}\left[\sum_{\sigma, i=1}^N\sum_{j \in \text{NN of }j}-t^D\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^D\sum_{i=1}^N \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + U^D\sum_{i=1}^N\sum_{j \in \text{N.N.
-of }i}\hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right] \\
-		      &= \frac{1}{Nw}\left[-t^D 2\sum_{\sigma, \left<ij\right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + 2 U^D\sum_{\left<ij\right>} \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + 2 U^D\sum_{\left<ij\right>} \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right]\\
-		      &= \frac{2}{Nw}\sum_{\left<ij\right>}\left[-t^D \sum_\sigma \left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + U^D\left(\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right)\right]\\
-		      &= \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
-\end{aligned}\end{equation}
-There we used the identity
-\begin{equation}\begin{aligned}
-	\sum_{i=1}^N\sum_{j \in \text{NN of }j} = 2\sum_{\left<ij\right>}
-\end{aligned}\end{equation}
-The sum $\left<ij\right>$ is over all nearest-neighbour pairs. Thus, $\tilde H$ can be written as
-\begin{equation}\begin{aligned}
-	\label{H_tiled}
-	\tilde H = - \frac{2t^D}{Nw}\sum_{\sigma, \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
-\end{aligned}\end{equation}
-The conclusion is that on tiling the Hubbard dimer Hamiltonians into all the nearest neighbour pairs, we end up with a new Hubbard model Hamiltonian with "renormalised parameters" given by
-\begin{equation}\begin{aligned}
-	\tilde t = \frac{2t^D}{Nw}~~,~~ \tilde U = \frac{2U^D}{N}~.
+% \\\\
+% If we now sum over all the nearest-neighbour pairs and take the average of all the Hamiltonians (\(\frac{1}{2}Nw\) in number), we get
+% \begin{equation}\begin{aligned}
+% 	\tilde H &= \frac{2}{Nw}\sum_{\left<ij \right>}^N H^D_{i,j} \\
+% 		 &= -t^A\sum_{\left<ij\right>}\left( c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.} \right) + \frac{2}{N}\sum_i U \tau_{i \uparrow}\tau_{i \downarrow}\\
+% 		 &= \frac{1}{Nw}\left[\sum_{\sigma, i=1}^N\sum_{j \in \text{NN of }j}-t^D\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^D\sum_{i=1}^N \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + U^D\sum_{i=1}^N\sum_{j \in \text{N.N.
+of }i}\hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right]\\
+% 		      &= \frac{1}{Nw}\left[-t^D 2\sum_{\sigma, \left<ij\right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + 2 U^D\sum_{\left<ij\right>} \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + 2 U^D\sum_{\left<ij\right>} \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right]\\
+% 		      &= \frac{2}{Nw}\sum_{\left<ij\right>}\left[-t^D \sum_\sigma \left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + U^D\left(\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right)\right]\\
+% 		      &= \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
+% \end{aligned}\end{equation}
+% There we used the identity
+% \begin{equation}\begin{aligned}
+% 	\sum_{i=1}^N\sum_{j \in \text{NN of }j} = 2\sum_{\left<ij\right>}
+% \end{aligned}\end{equation}
+The sum $\left<ij\right>$ is over all nearest-neighbour pairs. 
+% Thus, $\tilde H$ can be written as
+% \begin{equation}\begin{aligned}
+% 	\label{H_tiled}
+% 	\tilde H = - \frac{2t^D}{Nw}\sum_{\sigma, \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
+% \end{aligned}\end{equation}
+The conclusion is that on tiling the Hubbard dimer+bath Hamiltonians into all the nearest neighbour pairs, we end up with a new Hubbard model Hamiltonian with "renormalised parameters" given by
+\begin{equation}\begin{aligned}
+	\tilde t = \frac{2}{Nw}(1 + \frac{Nw}{2})t^D, &&\tilde U = \frac{2}{N}U^D
 \end{aligned}\end{equation}
@@
 %This also takes care of the problem that the spectrum of the Anderson molecule and Hubbard dimer are different for the $N=1$ or $N=3$ sectors: By translating the Anderson molecule suitably, we have recovered the correct spectrum in all sectors.
-\\\\
-The claim made in a previous section was that this Hamiltonian is very close to a similarity transformed Hubbard Hamiltonian:
-\begin{equation}\begin{aligned}
-	\tilde{H} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D) \equiv  \mathcal{U} H^H  \mathcal{U}^{-1}~,
-\end{aligned}\end{equation}
-where $\mathcal{U}$ is in general distinct from the unitary transformation that completes the URG starting from the bare cluster+bath Anderson model up to the fixed-point Hamiltonian.
+% \\\\
+% The claim made in a previous section was that this Hamiltonian is very close to a similarity transformed Hubbard Hamiltonian:
+% \begin{equation}\begin{aligned}
+% 	\tilde{H} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D) \equiv  \mathcal{U} H^H  \mathcal{U}^{-1}~,
+% \end{aligned}\end{equation}
+% where $\mathcal{U}$ is in general distinct from the unitary transformation that completes the URG starting from the bare cluster+bath Anderson model up to the fixed-point Hamiltonian.
 As shown earlier, $U$ transformation that involves three steps: the URG transformations $\mathcal{U}_A$, the extracting of the zero mode $Z$ and the tiling procedure outline in this section, $T$
-\begin{equation}\begin{aligned}
-	\mathcal{U} = T Z \mathcal{U}_{A}~.
-\end{aligned}\end{equation}
+% \begin{equation}\begin{aligned}
+% 	\mathcal{U} = T Z \mathcal{U}_{A}~.
+% \end{aligned}\end{equation}
+\textcolor{red}{
 With some knowledge of the RG procedure, one can even write down the relation between the Hubbard dimer couplings $t^D, U^D$ and the parent Hubbard model parameters $t^H, U^H$.
@@
 \[U^D \equiv (U^A)* = U_b = N \times U^H\]
+}
 \section{Formal expressions for single particle Greens functions and other related many-body quantites}
@@
 	\label{Gd_op}
-	\mathcal{\tilde G}(\omega) = \frac{1}{\omega - \left(\tilde H - E_\text{GS}\right)}, && \mathcal{G}_D(\omega) = \frac{1}{\omega - \left(H^D - E_\text{GS}\right)}
+	\mathcal{\tilde G}(\omega) = \frac{1}{\omega - \left(\tilde H - E_\text{GS}\right)}, && \mathcal{G}_D(\omega) = \frac{1}{\omega - \left(\tilde H^D(i,j,l) - E_\text{GS}\right)}
 \end{aligned}\end{equation}
@@
 	\label{green_eq}
-	\omega - \mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<\tilde i, \tilde j\right>}\left[\omega - \mathcal{G}_D^{-1}\left(\tilde i, \tilde j\right)\right]
-\end{aligned}\end{equation}
-where $\mathcal{G}_D^{-1}(\tilde i,\tilde j)$ is the Greens function inverse matrix of the Hubbard dimer Hamiltonian with $\tilde i, \tilde j$ as the two sites.
+	\omega - \mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<\tilde i, \tilde j\right>} \frac{1}{2(w-1)} \sum_{l \in \text{NN of j}}\left[\omega - \mathcal{G}_D^{-1}\left(\tilde i, \tilde j, \tilde l\right)\right]
+\end{aligned}\end{equation}
+where $\mathcal{G}_D^{-1}(\tilde i,\tilde j, \tilde l)$ is the Greens function inverse matrix of the Hubbard dimer+bath Hamiltonian with $\tilde i, \tilde j$ as the two sites and \(\tilde l\) as the zero mode of the bath, eq.~\ref{Hdjl}, or equivalently, eq.~\ref{dimer_p_bat}.
 Since the $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, they can be pulled out along with a factor.
@@
 \begin{equation}\begin{aligned}
+	\mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of j}}\mathcal{G}_D^{-1}\left(\omega, \tilde i, \tilde j, \tilde l\right)
+\end{aligned}\end{equation}
+Because of translational invariance, all values of \(l\) should give the same Greens function, and we can simplify this to
+\begin{equation}\begin{aligned}
 	\label{green_eq_final}
-	\mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}\mathcal{G}_D^{-1}\left(\omega, \tilde i, \tilde j\right)
-\end{aligned}\end{equation}
+	\mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\frac{1}{2(w-1)}\times 2(w-1)\sum_{\left<i,j\right>}\mathcal{G}_D^{-1}\left(\omega, \tilde i, \tilde j\right) = \frac{2}{Nw}\sum_{\left<i,j\right>}\mathcal{G}_D^{-1}\left(\omega, \tilde i, \tilde j\right)
+\end{aligned}\end{equation}
+We dropped the index \(\tilde l\) on \(\mathcal{G}_D^{-1}\) to mean that any particular choice of \(\tilde l\) will do.
 We will now calculate the site-diagonal and site-off-diagonal matrix elements for particle propagation.
-The site-diagonal matrix element is calculated between the state $\ket{\tilde i, \sigma} = \mathcal{U}c^\dagger_{i\sigma}\ket{\Phi_0}$ and its bra, while the off-diagonal one is between $\ket{\tilde j\sigma}$ and $\bra{\tilde i\sigma}$.
+The site-diagonal matrix element will be calculated between the state $\ket{\tilde i, \sigma} = \mathcal{U}c^\dagger_{i\sigma}\ket{\Phi_0}$ and its bra, while the off-diagonal one is between $\ket{\tilde j\sigma}$ and $\bra{\tilde i\sigma}$.
 Since it has already been shown that the matrix elements of the renormalised Hamiltonian are the same as those of the original Hamiltonian, we will directly replace the former with the latter.
@@
 First lets consider the diagonal matrix element at $\tilde i^\text{th}$ site.
-The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have $\tilde i$ in one of the indices.
-There will be $w$ such terms, because $\tilde i$ has $w$ nearest neighbours.
-Thus, the right hand side will be a sum of $w$ terms, each term being the inverse Greens function of a Hubbard dimer.
-Each term will be a real space local Greens function, and because of translational invariance, it will be the same on both sites.
+The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have the index $\tilde i$ on the dimer.
+There are $w$ terms that have the index \(\tilde i\) on the dimer corresponding to the $w$ nearest neighbours of \(\tilde i\).
+Thus, the right hand side will be a sum of $w$ terms, each term being the inverse Greens function of a Hubbard dimer+bath Hamiltonian.
+Each term will be a real space local Greens function, and because of translational invariance, it will be the same for all choices of the nearest neighbour of \(\tilde i\).
 %So we will represent the real space local inverse Greens function as $\left[\mathcal{G}_D^{-1}(\omega)\right]_{00}^{\sigma}$.
-The entire thing is thus $w$ times this local Greens function.
 % \begin{gather}
@@
 \begin{gather}
+	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\sum_{j \in \text{NN of i}}\bra{\tilde \Phi_0}c_{i\sigma}\mathcal{G}_{D}^{-1}(\omega, \tilde i, \tilde j)c^\dagger_{i\sigma}\ket{\tilde \Phi_0} = \frac{2}{N}\bra{\tilde \Phi_0}c_{i\sigma}\mathcal{G}_{D}^{-1}(\omega, \tilde i)c^\dagger_{i\sigma}\ket{\tilde \Phi_0}
+\end{gather}
+Once we have stripped away the \(j,l\) dependence, we can view the RHS as simply the matrix element of the dimer-bath Hamiltonian eq.~\ref{dimer_p_bat} between the local states of the site zero of the bath:
+\begin{gather}
 	\label{local_gf}
-	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\bra{\tilde \Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{\tilde \Phi_0}\times w = \frac{2}{N}\bra{\tilde \Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{\tilde \Phi_0}
+	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{N}\bra{\tilde \Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{\tilde \Phi_0}
 \end{gather}
-We can expand the state $c^\dagger_{0\sigma}\ket{\tilde \Phi_0}$ and $c^\dagger_{1\sigma}\ket{\tilde \Phi_0}$ in terms of a complete set of orthogonal states:
+Just to make it explicit, we repeat once more that \(\mathcal{G}_{D}^{-1}(\omega)\) is the inverse Greens function operator of the Hamiltonian in eq.~\ref{dimer_p_bat}.
+We can expand the state $c^\dagger_{i\sigma}\ket{\tilde \Phi_0}$ in terms of a complete set of orthogonal states:
 \begin{equation}\begin{aligned}
@@
 For example it might be a combination of number of particles, parity and total spin angular momentum $(n \equiv n, P, S^z)$.
-One simple way of choosing the orthogonal basis $\left\{ \ket{n} \right\}$ is to take them from the eigenstates of a system comprising a Hubbard dimer and a conduction bath, decoupled from each other.
+In light of the Greens function we have in between te states, we choose the orthogonal set to be formed by the eigenstates of the dim
+er+bath Hamiltonian.
+% One simple way of choosing the orthogonal basis $\left\{ \ket{n} \right\}$ is to take them from the eigenstates of a system comprising a Hubbard dimer and a conduction bath, decoupled from each other.
 The dimer will of course have 2 sites, which means the conduction bath will have $N-2$ sites, or $N-2$ momentum states.
@@
 Since the dimer is decoupled from the bath, the total wavefunction will be a direct product of a Hubbard dimer wavefunction and a bath wavefunction.
-\begin{equation}\begin{aligned}
-	\ket{m,\alpha,\beta} = \Phi^D_{m,\alpha} \otimes \Psi^B_{N-m+1, \beta}
-\end{aligned}\end{equation}
-$\alpha$ is an internal quantum number of the Hubbard dimer while $\beta$ is that for the bath.
+% \begin{equation}\begin{aligned}
+% 	\ket{m,\alpha,\beta} = \Phi^D_{m,\alpha} \otimes \Psi^B_{N-m+1, \beta}
+% \end{aligned}\end{equation}
+% $\alpha$ is an internal quantum number of the Hubbard dimer while $\beta$ is that for the bath.
 The subscripts $m$ and $N-m+1$ label the total number of particles in each part of the wavefunction.
@@
 Further improvement can be made by improving (i) the state $\ket{\tilde{\Phi_0}}$ for the present auxiliary model (involving a Hubbard dimer), or (ii) choosing a better auxiliary model with an ``impurity" system that has more sites than two (i.e., a Bethe-Peierls improvement of the dimer auxiliary model).
-\\\\
+% \\\\
 Using this expansion, the matrix element of $\mathcal{G}$ can be written as
@@
 \end{aligned}\end{equation}
-Since the Hubbard dimer of the ket $\ket{n}$ is an actual eigenstate, $\mathcal{G}_{D}^{-1}(\omega)$ will be diagonal in that basis:
+Since $\ket{n}$ is an actual eigenstate of the Hamiltonian that defines \(\mathcal{G}_{D}^{-1}(\omega)\), $\mathcal{G}_{D}^{-1}(\omega)$ will be diagonal in that basis:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-Now we come to the off-diagonal Greens function for the nearest neighbour sites $i$ and $j$.We will extract this using the definition.
-This will receive contribution from only one nearest neighbour pair in the summation of the RHS of eq.~\ref{green_eq_final}, namely that of $\left(i,j\right)$.
-This will not be a diagonal Greens function.
+Now we come to the off-diagonal Greens function for the nearest neighbour sites $i$ and $j$.
+This will receive contribution from only that dimer+bath Hamiltonian that has \(i,j\) as the dimer sites.
+This will not be a real space diagonal Greens function.
 Instead, it involves two nearest neighbour sites.
@@
 	\label{G_mat_loc}
-	\left(\mathcal{G}_{H}(\omega)\right)_{ii}^\sigma = \frac{2}{N}\sum_{n} |C^0_{n}|^2 \frac{1}{g_n}, && \left(\mathcal{G}_{H}(-\omega)\right)_{\overline{ii}}^\sigma = \frac{2}{N}\sum_{n} |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}}
+	\left(\mathcal{G}_{H}(\omega)\right)_{ii}^\sigma = \frac{4(w-1)}{N}\sum_{n} |C^0_{n}|^2 \frac{1}{g_n}, && \left(\mathcal{G}_{H}(-\omega)\right)_{\overline{ii}}^\sigma = \frac{4(w-1)}{N}\sum_{n} |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}}
 \end{aligned}\end{equation}
@@
 	\label{G_mat_nn}
-	\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\sum_{n} {C^0_{n}}^* C^1_{n} \frac{1}{g_n}, && \left(\mathcal{G}_{H}(-\omega)\right)_{\overline{ij}}^\sigma = \frac{2}{Nw}\sum_{n} {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}
+	\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma = \frac{4(w-1)}{Nw}\sum_{n} {C^0_{n}}^* C^1_{n} \frac{1}{g_n}, && \left(\mathcal{G}_{H}(-\omega)\right)_{\overline{ij}}^\sigma = \frac{4(w-1)}{Nw}\sum_{n} {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G_H(\omega)_\text{loc} &= \left(\mathcal{G}_H(\omega)\right)_{ii} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ii}} = \frac{2}{N}\sum_n\left(|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}}\right)\\
-	G_H(\omega)_\text{nn} &= \left(\mathcal{G}_H(\omega)\right)_{ij} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ji}} = \frac{2}{Nw}\sum_n\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\\
+	G_H(\omega)_\text{loc} &= \left(\mathcal{G}_H(\omega)\right)_{ii} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ii}} = \frac{4(w-1)}{N}\sum_n\left(|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}}\right)\\
+	G_H(\omega)_\text{nn} &= \left(\mathcal{G}_H(\omega)\right)_{ij} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ji}} = \frac{4(w-1)}{Nw}\sum_n\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\\
 \end{aligned}\end{equation}
@@
 			     &= G_H (\omega)_\text{loc} + G_H (\omega)_\text{nn} \xi_{\vec k}\\
-			     &= \frac{2}{N}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
+			     &= \frac{4(w-1)}{N}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{2}{N\pi} \textrm{Im}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\\
+	A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{4(w-1)}{N\pi} \textrm{Im}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\\
 A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = \frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
@@
 
-\section{Some comments on writing down the orthonormal basis $\left\{ \ket{n} \right\}$}
-As mentioned previously, for a parent model of $N$ sites, the orthonormal basis is constructed out of those eigenstates of a decoupled dimer+bath system that have total number of particles equal to $\mathcal{N}_\text{tot} = \mathcal{N}_\text{dim} + \mathcal{N}_\text{bath} = N+1$.
+% \section{Some comments on writing down the orthonormal basis $\left\{ \ket{n} \right\}$}
+% As mentioned previously, for a parent model of $N$ sites, the orthonormal basis is constructed out of those eigenstates of a decoupled dimer+bath system that have total number of particles equal to $\mathcal{N}_\text{tot} = \mathcal{N}_\text{dim} + \mathcal{N}_\text{bath} = N+1$.
 The condition on the total number is necessary because that is also the total particile number of the state we are expanding $(c^\dagger_{i\sigma}\ket{\tilde \Phi_0}$.
 The dimer will have 2 sites, while the rest $N-2$ sites go into the bath.
-\\\\
-If we are solving the trivial example of $H^H = H^D$ (that is, if we take the Hubbard dimer itself as the full Hubbard model that we are trying to solve), the bath is non-existant.
+% \\\\
+% If we are solving the trivial example of $H^H = H^D$ (that is, if we take the Hubbard dimer itself as the full Hubbard model that we are trying to solve), the bath is non-existant.
 The entire set of $\ket{n}$ for expanding $c^\dagger_{i\sigma}\ket{\tilde \Phi_0}$ is then made up by the $\mathcal{N} = N + 1 = 3, S^z = \frac{1}{2}\sigma$ eigenstates of $H^D$.
 There are two of those; these two make up the entire orthonormal basis in which we can expand the single-particle excitaions:
-\begin{equation}\begin{aligned}
-	\left\{ \ket{n} \right\} = \ket{3 \pm \sigma}
-\end{aligned}\end{equation}
-Similarly, for expanding the hole excitaions $c_{i\sigma}\ket{\tilde \Phi_0}$, we will instead choose the $\mathcal{N} = N - 1 = 1, S^z = -\frac{1}{2}\sigma$ eigenstates of $H^D$.
+% \begin{equation}\begin{aligned}
+% 	\left\{ \ket{n} \right\} = \ket{3 \pm \sigma}
+% \end{aligned}\end{equation}
+% Similarly, for expanding the hole excitaions $c_{i\sigma}\ket{\tilde \Phi_0}$, we will instead choose the $\mathcal{N} = N - 1 = 1, S^z = -\frac{1}{2}\sigma$ eigenstates of $H^D$.
 There are again two of those:
-\begin{equation}\begin{aligned}
-	\left\{ \ket{\overline n} \right\} = \ket{1 \pm -\sigma}
-\end{aligned}\end{equation}
-\\\\
-For a more general $N(>2)$-site model, there will be a bath of $N-2$ momentum states.
+% \begin{equation}\begin{aligned}
+% 	\left\{ \ket{\overline n} \right\} = \ket{1 \pm -\sigma}
+% \end{aligned}\end{equation}
+% \\\\
+% For a more general $N(>2)$-site model, there will be a bath of $N-2$ momentum states.
 These momentum states are labelled as $k_1, k_2, ..., k_{N-2}$.
@@
 Since the bath is non-interacting, those eigenstates can be written down easily:
-\begin{equation}\begin{aligned}
-	\left\{ \ket{\Psi^B_{j, \nu^j}} \right\} = \begin{cases} &  j \in [0, 2N-4]\\[-10pt]
-	\otimes_{i=1}^j\hat n_{\nu^j_i} = 1:\\[-10pt]
-& \nu^j \in \text{all subsets of length $j$ of the set $\left[k_1 \uparrow, k_1 \downarrow, k_2 \uparrow, ..., k_{N-2} \uparrow, k_{N-2} \downarrow\right]$} \end{cases}
-\end{aligned}\end{equation}
-$j$ defines the number of occupied states in a particular eigenstate of the conduction bath.
+% \begin{equation}\begin{aligned}
+% 	\left\{ \ket{\Psi^B_{j, \nu^j}} \right\} = \begin{cases} &  j \in [0, 2N-4]\\[-10pt]
+% 	\otimes_{i=1}^j\hat n_{\nu^j_i} = 1:\\[-10pt]
+% & \nu^j \in \text{all subsets of length $j$ of the set $\left[k_1 \uparrow, k_1 \downarrow, k_2 \uparrow, ..., k_{N-2} \uparrow, k_{N-2} \downarrow\right]$} \end{cases}
+% \end{aligned}\end{equation}
+% $j$ defines the number of occupied states in a particular eigenstate of the conduction bath.
 The string $\nu^j$ runs over all possible set of quantum numbers of a particular length $j$.
 For example, if we have 3 momentum states in the bath $k_1, k_2, k_3$, then $\nu^2$ would take the values
-\begin{equation}\begin{aligned}
-	\left\{\nu^2\right\} = \left(k_1 \uparrow, k_1 \downarrow\right),\left(k_1 \uparrow, k_2 \uparrow\right),\left(k_1 \uparrow, k_2 \downarrow\right),\left(k_1 \uparrow, k_3 \uparrow\right),\left(k_1 \uparrow, k_3 \downarrow\right),\left(k_1 \downarrow, k_2 \uparrow\right),\left(k_1 \downarrow, k_2 \downarrow\right),\\
-	\left(k_1 \downarrow, k_3 \uparrow\right),\left(k_1 \downarrow, k_3 \downarrow\right),\left(k_2 \uparrow, k_2 \downarrow\right),\left(k_2 \uparrow, k_3 \uparrow\right),\left(k_2 \uparrow, k_3 \downarrow\right),\left(k_2 \downarrow, k_3 \uparrow\right),\left(k_2 \downarrow, k_3 \downarrow\right),\\
-\left(k_3 \uparrow, k_3 \downarrow\right)
-\end{aligned}\end{equation}
-The $j=0$ case means the bath is empty.
-The general complete set of orthonormal kets is given by
-\begin{equation}\begin{aligned}
-	\left\{ \ket{n} \right\} = \sum_{i=1}^{16}\sum_{j=0}^{N-2}\sum_{\nu^j}\ket{\Phi^D_i}\otimes \ket{\Psi^B_{j, \nu^j}}
-\end{aligned}\end{equation}
-The first twp sums are unconstrained.
+% \begin{equation}\begin{aligned}
+% 	\left\{\nu^2\right\} = \left(k_1 \uparrow, k_1 \downarrow\right),\left(k_1 \uparrow, k_2 \uparrow\right),\left(k_1 \uparrow, k_2 \downarrow\right),\left(k_1 \uparrow, k_3 \uparrow\right),\left(k_1 \uparrow, k_3 \downarrow\right),\left(k_1 \downarrow, k_2 \uparrow\right),\left(k_1 \downarrow, k_2 \downarrow\right),\\
+% 	\left(k_1 \downarrow, k_3 \uparrow\right),\left(k_1 \downarrow, k_3 \downarrow\right),\left(k_2 \uparrow, k_2 \downarrow\right),\left(k_2 \uparrow, k_3 \uparrow\right),\left(k_2 \uparrow, k_3 \downarrow\right),\left(k_2 \downarrow, k_3 \uparrow\right),\left(k_2 \downarrow, k_3 \downarrow\right),\\
+% \left(k_3 \uparrow, k_3 \downarrow\right)
+% \end{aligned}\end{equation}
+% The $j=0$ case means the bath is empty.
+% The general complete set of orthonormal kets is given by
+% \begin{equation}\begin{aligned}
+% 	\left\{ \ket{n} \right\} = \sum_{i=1}^{16}\sum_{j=0}^{N-2}\sum_{\nu^j}\ket{\Phi^D_i}\otimes \ket{\Psi^B_{j, \nu^j}}
+% \end{aligned}\end{equation}
+% The first twp sums are unconstrained.
 The index $i$ runs through all 16 eigenstates of the Hubbard dimer, the index $j$ runs through all the possible total number of particles the eigenstate of the bath can have.

### 2021-08-24 notes.tex
typos

@@
 \begin{equation}\begin{aligned}
-	\color{red}{\tilde H = - \frac{2t^D}{Nw}\sum_{\sigma \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)}
-\end{aligned}\end{equation}
-What that means is that we have placed the Hubbard dimer at all nearest neighbour pairs to reconstruct a new Hubbard model.
+	\tilde H &= \frac{2}{Nw}\sum_{\left<ij\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\tilde H^D((0,1,z) \to (i, j, l))\\
+		 &= \frac{2}{N}U^D\sum_{i} \tau_{i \uparrow}\tau_{i \downarrow} - \frac{2}{Nw}\left(1 + \frac{Nw}{2}\right)t^D\sum_{\left<ij\right>}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+What that means is that we have placed the Hubbard dimer+bath system at all nearest neighbour pairs to reconstruct a new Hubbard model.
 If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as dropping the correlation on the bath sites, we can write
@@
 \begin{equation}\begin{aligned}
-	\tilde H^D = H^D(0,1) - t^D \sum_{\vec k}^\text{eff.
-bath}\left(c^\dagger_{0\sigma}c_{\vec k,\sigma} + c^\dagger_{0\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff.
-bath}\epsilon_{\vec k}\hat n_{\vec k}
+	\tilde H^D = H^D(0,1) - t^D \left(c^\dagger_{0\sigma}c_{z\sigma} + c^\dagger_{1\sigma}c_{z\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}
 \end{aligned}\end{equation}
@@
 % \end{aligned}\end{equation}
-\textcolor{red}{
 With some knowledge of the RG procedure, one can even write down the relation between the Hubbard dimer couplings $t^D, U^D$ and the parent Hubbard model parameters $t^H, U^H$.
@@
 \[U^D \equiv (U^A)* = U_b = N \times U^H\]
-}
 \section{Formal expressions for single particle Greens functions and other related many-body quantites}
@@
 For example it might be a combination of number of particles, parity and total spin angular momentum $(n \equiv n, P, S^z)$.
-In light of the Greens function we have in between te states, we choose the orthogonal set to be formed by the eigenstates of the dim
-er+bath Hamiltonian.
+In light of the Greens function we have in between te states, we choose the orthogonal set to be formed by the eigenstates of the dimer+bath Hamiltonian.
 % One simple way of choosing the orthogonal basis $\left\{ \ket{n} \right\}$ is to take them from the eigenstates of a system comprising a Hubbard dimer and a conduction bath, decoupled from each other.
@@
 We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.
+
+\section{Numerical Results for a bath with two momentum modes}
 

### 2021-09-05 notes.tex
reverted to simple fit with 3 params

@@
 \maketitle
+\tableofcontents
+\newpage
 \section{Introduction}
@@
 \end{itemize}
+
+\section{Spectral function of the single-impurity Anderson model}
+To get a better look at what we are getting into and what we should expect going forward, we first calculate the spectral function of the smaller single-impurity Anderson model that is obtained as the low-energy Hamiltonian of an URG analysis of the full SIAM.
+This ow energy effective Hamiltonian is
+\begin{equation}\begin{aligned}
+	\epsilon_d \hat n_d + U\hat n_{d \uparrow} \hat n_{d \downarrow} + v \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + \sum_{k \in \left[-\Lambda^*, \Lambda^*\right], \sigma}\epsilon_k \hat n_{k\sigma}
+\end{aligned}\end{equation}
+All the impurity couplings are fixed point values, and the momentum states of the bath now run over a reduced bandwidth.
+The subscript \(d\) indicates that the operator is that of the impurity, while the subscript \(0\) indicates it is of the zeroth site of the bath: \(c_0 = \frac{1}{\sqrt N}\sum_k c_k\).
+The spectral function of the SIAM is already known from other methods like the numerical renormalization group.
+For small values of \(U\), the spectral function consists of just the central quasiparticle excitation peak.
+At larger values of \(U\), we see the emergence of the two Hubbard side bands while the spectral weight at the centre decreases.
+We also calculated the spectral function of the low energy theory sing exact diagonalization.
+The plots are shown in fig.~\ref{siam_spec_func}.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.9\textwidth]{./siam_specfunc_all.pdf}
+	\caption{Spectral function of the effective SIAM Hamiltonian for various values of \(\frac{U}{\Delta}\).
+\(\Delta\) is defined by the height of the central peak in the non-interacting model \(U=0\).
+The inset shows a zoom-in of the final spectral function \(\left( \frac{U}{\Delta} = 19.71 \right)\) near \(\omega = 0\).}
+	\label{siam_spec_func}
+\end{figure}
+\\\\
+Because we kept only a discrete bath of 4 momentum states, \textit{we had to artificially enforce the constancy of the height of the central peak.} To convert the delta functions into a continuous spectrum, we  The central peak (or equivalently, the central pole in the impurity Greens function) does not vanish even for exhorbitantly large values of \(\frac{U}{\Delta}\), implying that there is no stable local moment phase in the SIAM (a local moment phase would involve a gap at zero frequency in the impurity spectral function).
+Formally, the local moment phase will be stable only at \(U \to \infty\) or \(v^* = 0\).
+\\\\
+We also checked how the width of the central peak varies with increasing \(U\). The behaviour is shown in fig.~\ref{fwhm}. The width was also fitted against a function, as shown in the plot.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.6\textwidth]{./fwhm_vs_U_hrk_fit.pdf}
+	\caption{The decay of the full width at half maximum (FWHM) of the central peak, with increasing \(\frac{U}{\Delta}\). The behaviour satisfies a function of the form shown in the legend.}
+	\label{fwhm}
+\end{figure}
+
+\section{Spectral function of a correlated SIAM}
+Since the SIAM cannot show a transition from a metallic (Fermi liquid) phase to a local moment phase, we next consider the slightly more correlated version where the zeroth site (which the impurity couples to) now has a Hubbard repulsion.
+\begin{equation}\begin{aligned}
+	\epsilon_d \hat n_d + U\hat n_{d \uparrow} \hat n_{d \downarrow} + U_b\hat n_{0 \uparrow} \hat n_{0 \downarrow} + v \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + \sum_{k \in \left[-\Lambda^*, \Lambda^*\right], \sigma}\epsilon_k \hat n_{k\sigma}
+\end{aligned}\end{equation}
+In such a model, if the impurity is to hybridize with the bath, it has to hop onto the zeroth site, but that site now has a double-occupancy cost.
+As a result, this new physics makes it harder for the impurity electron to delocalise, and suggests that there might be a metal-insulator transition at some critical value of the impurity \(U\), and this critical value should itself be a function of \(U_b\).
+This model therefore provides a tool for showing the changes in the phase diagram of the SIAM.
+Without any correlation in the bath, the SIAM has just one stable fixed point, the strong-coupling one.
+Starting up a correlation on the zero mode allows us to examine how this scenario might change if we have a correlated bath.
+One can also draw a comparison to DMFT and argue that such a model is similar to that stage of DMFT when the process has gone through a few steps of self-consistency enforcement and the bath itself has started to become correlated.
+\\\\
+Apart from its importance as a standalone problem, this correlated SIAM also sets the stage for a fully-symmetrized auxiliary model, the Hubbard dimer in a bath.
+In other words, by taking a symmetric combination of the correlated SIAM Hamiltonians (the symmetrization is done by exchanging the impurity and bath zero mode sites), one can obtain the Hamiltonian of a dimer hybridising with a bath, as shown in eq.~\ref{dimer_p_bat}.
+Such a symmetrised Hamiltonian should presumably correspond to a DMFT final-stage Hamiltonian, because the impurity and bath zero mode sites are now completely symmetric.
 

### 2021-09-15 notes/notes.tex
inserted new plot into the notes, corrected some errors in the latex file like xelatex shebang and location of figures
enhanced the discussion on the broadening

--- 2021-09-05 notes.tex
@@
-% !TEX TS-program = xelatex
-\documentclass[12pt]{article}
+\documentclass{article}
 \usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec,color}
 \usepackage[margin=0.5in,bottom=0.6in]{geometry}
-\graphicspath{{./figures/}}
+\graphicspath{{../figures/}}
 \usepackage[T1]{fontenc}
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{./siam_specfunc_all.pdf}
+	\includegraphics[width=\textwidth]{./siam_specfunc_all.pdf}
 	\caption{Spectral function of the effective SIAM Hamiltonian for various values of \(\frac{U}{\Delta}\).
@@
 \\\\
-Because we kept only a discrete bath of 4 momentum states, \textit{we had to artificially enforce the constancy of the height of the central peak.} To convert the delta functions into a continuous spectrum, we  The central peak (or equivalently, the central pole in the impurity Greens function) does not vanish even for exhorbitantly large values of \(\frac{U}{\Delta}\), implying that there is no stable local moment phase in the SIAM (a local moment phase would involve a gap at zero frequency in the impurity spectral function).
+Because we kept only a discrete bath of 4 momentum states, \textit{we had to artificially enforce the constancy of the height of the central peak, using \cite{Langreth}.} To convert the discrete sum of delta functions into a continuous spectrum, we broadened them using a Gaussian.
+Following \cite{bulla_costi_nrg}, we replace the delta-functions at \(\pm x_n \equiv \pm(E_n - E_0)\) by normalised Gaussian functions
+\begin{equation}\begin{aligned}
+	\delta(\omega \pm x_n) \to \frac{1}{\eta_n\sqrt \pi}e^{-\left(\frac{\omega \pm x_n}{\eta_n}\right)^2}
+\end{aligned}\end{equation}
+The parameter \(\eta_n\) determines the height and width of the Gaussian, and is chosen such that the higher energy poles are broader than the lower energy ones.
+\begin{equation}\begin{aligned}
+	\eta_n = 2\Delta + \frac{1}{2}|x_n| 
+\end{aligned}\end{equation}
+where \(\Delta = \frac{V^2}{t}\) is the relevant energy scale of the non-interacting problem and \(t\) is the tight-binding hopping parameter of the conduction bath.
+\\\\
+The central peak (or equivalently, the central pole in the impurity Greens function) does not vanish even for exhorbitantly large values of \(\frac{U}{\Delta}\), implying that there is no stable local moment phase in the SIAM (a local moment phase would involve a gap at zero frequency in the impurity spectral function).
 Formally, the local moment phase will be stable only at \(U \to \infty\) or \(v^* = 0\).
@@
 We also checked how the width of the central peak varies with increasing \(U\). The behaviour is shown in fig.~\ref{fwhm}. The width was also fitted against a function, as shown in the plot.
-\begin{figure}[htpb]
+\begin{figure}[htpb!]
 	\centering
-	\includegraphics[width=0.6\textwidth]{./fwhm_vs_U_hrk_fit.pdf}
+	\includegraphics[width=0.5\textwidth]{./width_vs_U_simple_fit.pdf}
 	\caption{The decay of the full width at half maximum (FWHM) of the central peak, with increasing \(\frac{U}{\Delta}\). The behaviour satisfies a function of the form shown in the legend.}
@@
 We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.
-
-\section{Numerical Results for a bath with two momentum modes}
 

### 2022-03-07 notes/notes.tex
--no-message
updated auxiliary model notes with the Ub business and the entire gen siam

--- 2021-08-24 notes.tex
@@
-% !TEX TS-program = xelatex
-\documentclass[12pt]{article}
-\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec,color}
-\usepackage[margin=0.5in,bottom=0.6in]{geometry}
-\graphicspath{{./figures/}}
+\documentclass{report}
+\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix}
+% \usepackage[draft]{graphicx}
+\usepackage{graphicx}
+\usepackage[hidelinks]{hyperref}
+\usepackage[margin=0.8in,top=0.3in,bottom=1.4in]{geometry}
+\usepackage[utf8]{inputenc}
 \usepackage[T1]{fontenc}
-\usepackage[pdfusetitle]{hyperref}
 \renewcommand{\arraystretch}{2}
@@
 \setcounter{tocdepth}{1}
-\DeclareMathOperator{\sech}{sech}
-\raggedbottom
+\pagestyle{headings}
+\setlength{\headheight}{52pt}
 \numberwithin{equation}{section}
 \allowdisplaybreaks
-
-\title{Generating Hubbard Model Solutions from Anderson Impurity Model Solutions}
-\author{Abhirup Mukherjee, Dr. Siddhartha Lal}
+\bibliographystyle{ieeetr}
+
+\title{\bf Auxiliary Model Approach to Strongly-Correlated Systems}
+\author{\Large Abhirup Mukherjee, Siddhartha Lal}
+\date{\Large \today}
+
 \begin{document}
 \maketitle
+\tableofcontents
+\newpage
+\chapter{Introduction}
+\section{What is the minimal impurity model for a Mott MIT?}
+A correlated single impurity site connected with a non-interacting bath with a uniform density of states leads to a well-defined Kondo resonance at low temperatures, as seen in the impurity spectral function.
+Increasing the impurity correlation \(U\) only serves to reduce the width of the central peak at the cost of the appearance of side bands at energy scales of the order of \(U\), but the resonance never dies.
+The situation is however different if the impurity is embedded in a correlated conduction bath with a non-trivial density of states.
+For the case of a conduction band with the DOS shown in the right of the figure below, the impurity hybridises into a reduced bandwidth because of the correlation on the lattice.
+This difference is what leads to a metal-insulator transition of a bulk Hubbard model under dynamical mean-field theory (DMFT).
+Under self-consistency, the non-interacting bath gets modified into one with a highly-correlated self-energy.
+At low \(U\), the impurity spectral function remains gapless, but at sufficiently large \(U\), the bath is able to kill the Kondo resonance and lead to an insulating state.
+\textit{This leaves open the following question: What is the minimal correlation one can insert into the non-interacting bath (of a single-impurity Anderson model) that can capture both the metallic and insulating phases of the bulk model?}
+\cite{held_2013}
+
+\begin{figure}[htpb]
+\centering
+\includegraphics[width=0.5\textwidth]{../figures/correlated_bath.png}
+\caption{"Comparison of the usual Anderson
+impurity model of a strongly interacting site coupled via $V$ to
+an uncorrelated featureless and wide conduction-electron band
+(left-hand side) and the Hubbard model situation (right-hand
+side). In the latter case, an electron leaving a correlated site
+moves within the strongly correlated and narrow band of the
+central peak. In this situation there is a kink at the effective
+Kondo energy scale which is smaller than the width of the
+narrow band." Image and caption source in footnote.}
+\end{figure}
 \section{Introduction}
@@
 \section{Philosophy of the method}
-The method is closely tied to the auxiliary system approach described in \cite{martin_2016}.
+The method is closely tied to the auxiliary system approach described in [CITE MARTIN].
 We can view the full Hamiltonian as a sum of two component Hamiltonians \(H_1, H_2\) connected via the interaction term \(H_{12}\).
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{cluster-bath.png}
+	\includegraphics[width=0.8\textwidth]{../figures/cluster-bath.png}
 	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$.
@@
 	\centering
-	\includegraphics[width=0.6\textwidth]{gen_siam.png}
+	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.png}
 	\caption{Correlated asymmetric Anderson molecule schematic version.
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{hubb_dim.png}
+	\includegraphics[width=0.4\textwidth]{../figures/hubb_dim.png}
 	\caption{Hubbard dimer schematic version. It again consists of two sites, like the Anderson molecule, but now both sites have onsite repulsion, and their is again inter-site hopping.}
@@
 	\centering
-	\includegraphics[width=0.3\textwidth]{dimer_bath.png}
+	\includegraphics[width=0.3\textwidth]{../figures/dimer_bath.png}
 	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.
@@
 
+\chapter{Physics of the generalised single-impurity Anderson model}
+\section{Introduction of spin-exchange and charge isospin-exchange interactions into the SIAM: the generalised SIAM}
+We will now study the generalised SIAM obtained by introducing spin-exchange and charge isospin-exchange interactions between the impurity and the conduction bath.
+Such terms are generated when one does a Schrieffer-Wolff transformation on the SIAM, but we will find it prudent to keep these terms in the bare model itself.
+
+The spin-exchange interaction has the form
+\begin{equation}\begin{aligned}
+	J \vec{S_d}\cdot\vec{s} = J \left[S_d^z s^z + \frac{1}{2}\left( S_d^+ s^- + S_d^- s^+ \right) \right] ~,
+\end{aligned}\end{equation}
+where \(\vec S_d = \left(S_d^x, S_d^y, S_d^z\right) = \sum_{\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{d\alpha}c_{d\beta}\) is the impurity spin operator, \(\vec s = \sum_{kk^\prime\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{k\alpha}c_{k^\prime\beta}\) is the spin operator for the conduction bath and \(J\) is the spin-exchange coupling.
+The bath spin operator actually acts locally, as can be seen by Fourier transforming to real space (using the definition \(f(k) = \frac{1}{\sqrt N}\sum_r g(r)\exp(ikr)\)):
+\begin{equation}\begin{aligned}
+	\vec s = \sum_{k k^\prime r r^\prime} \frac{1}{N} e^{ikr - ik^\prime r^\prime} \vec \sigma_{\alpha\beta} c^\dagger_{r\alpha} c_{r^\prime\beta} = \sum_{rr^\prime}\frac{1}{N}\vec \sigma_{\alpha\beta} c^\dagger_{r\alpha} c_{r^\prime\beta} N \delta(r)\delta(r^\prime) = \vec \sigma_{\alpha\beta} c^\dagger_{0\alpha} c_{0\beta}
+\end{aligned}\end{equation}
+
+In order to introduce the charge isospin coupling, we define the Nambu spinor \cite{anderson1958random,nambu_1960} \(\psi^k = \left( c_{k\uparrow} \quad c^\dagger_{k\downarrow} \right)\), and the charge isospin \cite{zitko_2006} for the mobile conduction electrons
+\begin{equation}\begin{aligned}
+\vec C = \sum_{kk^\prime} {\psi^k}^\dagger \vec S \psi^{k^\prime} = \frac{1}{2}\sum_{kk^\prime\alpha\beta} {\psi^k_\alpha}^\dagger \vec \sigma_{\alpha\beta} \psi^{k^\prime}_\beta
+\end{aligned}\end{equation}
+The various components of the isospin are
+\begin{equation}\begin{aligned}
+	C^z &= \sum_{kk^\prime\sigma}\frac{1}{2} {\psi^k_\sigma}^\dagger \sigma^z_{\sigma\sigma} \psi^{k^\prime}_\sigma = \frac{1}{2}\sum_{kk^\prime\sigma}\left(c^\dagger_{k\sigma}c_{k^\prime \sigma} - \frac{1}{2}\delta_{kk^\prime}\right)\label{diagonalCz}\\
+	C^x &= \sum_{kk^\prime\sigma}\frac{1}{2} {\psi^k_\sigma}^\dagger \sigma^x_{\sigma\overline\sigma} \psi^{k^\prime}_{\overline\sigma} = \sum_{kk^\prime\sigma} \frac{\sigma}{4}\left( c^\dagger_{k\sigma}c^\dagger_{k^\prime\overline\sigma} + \text{h.c.} \right) \\
+	C^y &= \sum_{kk^\prime\sigma}\frac{1}{2} {\psi^k_\sigma}^\dagger \sigma^y_{\sigma\overline\sigma} \psi^{k^\prime}_{\overline\sigma} = \sum_{kk^\prime\sigma} - \frac{i\sigma}{4}\left( c^\dagger_{k\sigma}c^\dagger_{k^\prime\overline\sigma} - \text{h.c.} \right)\\
+\end{aligned}\end{equation}
+It is easy to verify that these operators satisfy the SU(2) commutation algebra.
+For example, if we write \(C^x = A + A^\dagger\) and \(C^y = B + B^\dagger\), then \(\left[ C^x, C^y \right] = \left[ A, B^\dagger \right] - \text{h.c.}\), where
+\begin{equation}\begin{aligned}
+	\left[ A, B^\dagger \right] = \frac{1}{4}\sum_{kk^\prime,qq^\prime}\left[ c^\dagger_{k\uparrow}c^\dagger_{k^\prime \downarrow}, i c_{q^\prime \downarrow}c_{q \uparrow} \right] = \frac{i}{4}\sum_{kq}\left(c^\dagger_{k\uparrow}c_{q \uparrow} - c_{k \downarrow}c^\dagger_{q \downarrow}\right)
+\end{aligned}\end{equation}
+and therefore
+\begin{equation}\begin{aligned}
+	\implies \left[ C^x, C^y \right] = \frac{i}{2}\sum_{kq}\left(c^\dagger_{k\uparrow}c_{q \uparrow} - c_{k \downarrow}c^\dagger_{q \downarrow}\right) = i C^z
+\end{aligned}\end{equation}
+There are similar operators for the impurity electron:
+\begin{equation}\begin{aligned}
+	\psi_d = \left( c_{d\uparrow} \quad c^\dagger_{d\downarrow}\right), &&\vec C_d = \frac{1}{2}\sum_{\beta} {\psi_{d,\alpha}}^\dagger \vec \sigma_{\alpha\beta} \psi_{d,\beta}
+\end{aligned}\end{equation}
+The full charge-Kondo interaction can now be written down in terms of these isospins:
+\begin{equation}\begin{aligned}
+	K \vec{C_d}\cdot\vec{C} = K \left[C_d^z C^z + \frac{1}{2}\left(C_d^+ C^-+ C_d^- C^+\right)\right]
+\end{aligned}\end{equation}
+where \(C^\pm \equiv C^x \pm iC^y\).
+\begin{equation}\begin{aligned}
+	C^+ = \sum_{kk^\prime} c^\dagger_{k\uparrow}c^\dagger_{k^\prime\downarrow}, && C^- = \sum_{kk^\prime}c_{k^\prime\downarrow}c_{k\uparrow}
+\end{aligned}\end{equation}
+The full generalised Anderson model Hamiltonian, at particle-hole symmetry, is
+\begin{equation}\begin{aligned}
+	\mathcal{H} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} + \epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} + K \vec{C_d}\cdot\vec{C}
+\end{aligned}\end{equation}
+
+For the URG analysis, at each RG step, we decouple the electronic states \(q\beta\) on the \(k-\)space shell of radius\(\Lambda_j\).
+For simplicity, we will only consider those diagonal terms in the denominator that either have both \(q\beta\) and \(q\overline\beta\) or  both \(q\beta\) and \(d\) or both \(q\overline\beta\) and \(d\).
+Terms that have purely \(q\overline\beta\) will not be considered.
+Also, the scattering between just \(d\) and \(q\overline\beta\) can be ignored since it is diagonal in \(q\beta\).
+The diagonal (number-preserving) part is
+\begin{equation}\begin{aligned}
+	H_D = \sum_\beta\epsilon_q\tau_{q\beta} + \epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + J S^z_ds^z_{q} + K C^z_d C^z_q\\
+\end{aligned}\end{equation}
+where \(s_q^z = \frac{1}{2}\left(\hat n_{q\uparrow} - \hat n_{q\downarrow}\right)\) and \(C_q^z = \frac{1}{2}\left(\hat n_{q \uparrow} + \hat n_{q \downarrow} - 1\right)\). The off-diagonal part is:
+\begin{equation}\begin{aligned}
+	H_X = \sum_{\beta=\uparrow,\downarrow}\left[V c^\dagger_{d\beta}c_{q\beta} + \frac{1}{2}J \sum_{k<\Lambda_N}\left\{\left(\hat n_{d \beta} - \hat n_{d \overline\beta}\right) \frac{1}{2} c^\dagger_{k\beta}c_{q\beta} + c^\dagger_{d\beta}c_{d\overline\beta}c^\dagger_{k\overline\beta}c_{q \beta}\right\} + \frac{1}{2}K \sum_{k<\Lambda_N}\left\{\left(\hat n_d -1\right)\frac{1}{2}c^\dagger_{k\beta}c_{q\beta} + \right.\right.\\
+\left.\left.c^\dagger_{d\beta}c^\dagger_{d\overline\beta}c_{k\overline\beta}c_{q\beta}\right\}\right] + \text{h.c.}~.
+\end{aligned}\end{equation}
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../figures/zeromode.pdf}
+	\caption{While we have studied the full model under renormalisation group, often we will turn to a simplified zero-bandwidth version of the model that is obtained by ignoring the kinetic energy part of the Hamiltonian.
+This zero-bandwidth model is effectively a two site model.}
+\end{figure}
+
+\section{RG equations for generalised SIAM}
+\begin{equation}\begin{aligned}
+	\Delta \epsilon_d &= 2V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + \frac{n_j}{2}\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right),\\
+	\Delta V &= -\frac{3n_j V}{8}\left[J\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)\right],\\
+	\Delta J &= -\frac{n_j J^2}{\omega - \frac{D}{2} + \frac{J}{4}},\\ 
+	\Delta K &= -\frac{n_j K^2}{\omega - \frac{D}{2} + \frac{K}{4}}
+\end{aligned}\end{equation}
+In terms of \(U = -2\epsilon_d\), the equations become
+\begin{gather}
+	\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\left(\frac{J^2}{d_2} - \frac{K^2}{d_3}\right),\\
+	\Delta V = -\frac{3n_j V}{8}\left[J\left(\frac{1}{d_2} + \frac{1}{d_1}\right) + K \left(\frac{1}{d_3} + \frac{1}{d_0}\right)\right],\\
+	\Delta J = -\frac{n_j J^2}{d_2}, \quad\quad\Delta K = -\frac{n_j K^2}{d_3}
+\end{gather}
+\(d_i\) are the denominators:
+\begin{equation}\begin{aligned}
+	\label{denominators}
+	d_0 = \omega - \frac{D}{2} - \frac{U}{2} + \frac{K}{4}, \quad d_1 = \omega - \frac{D}{2} + \frac{U}{2} + \frac{J}{4}, \quad d_2 = \omega - \frac{D}{2} + \frac{J}{4}, \quad d_3 = \omega - \frac{D}{2} + \frac{K}{4}
+\end{aligned}\end{equation}
+
+\section{Nature of coupling RG flows}
+\subsection{Repulsive interaction on impurity: \(U>0\)}
+For the Hamiltonians with positive on-site correlation, we will assume that the spin-exchange coupling is positive and charge isospin-exchange coupling is negative: \(J>0, K<0\).
+This choice is motivated by the signs of the corresponding terms when they are generated via a Schrieffer-Wolff transformation~\cite{schrieffer1966}.
+The impurity-bath hybridisation \(V\) is always positive.
+The sign of the couplings lead to inequalities among the denominators which we will utilise at various points.
+First of all, since \(U>0\), we have \(d_1 - d_2 = \frac{U}{2} > 0\).
+Secondly, since \(K<0\), we have \(d_2 - d_3 = \frac{J-K}{4} > 0\).
+And finally, we have \(d_3 - d_0 = \frac{U}{2} > 0\).
+Combining these, we can write
+\begin{equation}\begin{aligned}
+	\label{ineq_den}
+	d_1 > d_2 > d_3 > d_0
+\end{aligned}\end{equation}
+
+The strong-coupling regime is defined as the range of values of \(\omega\) where the hybridisation is relevant.
+This is ensured by the assumption \(d_1<0\).
+From eq.~\ref{ineq_den}, we can then conclude that all denominators are negative: \(d_i = - |d_i|\).
+The simplest consequence of this is the RG flow of \(K\):
+\begin{equation}\begin{aligned}
+	\Delta K= -\frac{n_j K^2}{d_3} = \frac{n_j K^2}{|d_3|} > 0 \implies K_{j+1} > K_j \implies K_0 = -|K_0|, K^* \to 0
+\end{aligned}\end{equation}
+\(K_j\) is the value of \(K\) after the \(j^\text{th}\) RG step, \(K_0\) representing the bare value.
+In other words, since \(d_3 < 0\), the RG equation for \(K\) provides an algebraic increment, and the negative \(K\) increases and flows towards zero.
+The \(*\) indicates a fixed point value.
+The isospin coupling is irrelevant in this regime, and we will ignore it.
+
+The coupling \(J\), on the other hand, is relevant and flows from a small positive value towards a large value at strong-coupling.
+\begin{equation}\begin{aligned}
+	\Delta J= -\frac{n_j J^2}{d_2} = \frac{n_j J^2}{|d_2|} > 0 \implies J_{j+1} > J_j \implies J_0 \to \text{ large } J^* ~(\text{strong-coupling})
+\end{aligned}\end{equation}
+The value of \(J^*\) is obtained when the denominator \(d_2\) vanishes.
+
+Because of the RG irrelevance of \(K\), we can simplify the RG equation for \(V\):
+\begin{equation}\begin{aligned}
+	\Delta V = -\frac{3n_j VJ}{8}\left(\frac{1}{d_2} + \frac{1}{d_1}\right) = \frac{3n_j VJ}{8}\left(\frac{1}{|d_2|} + \frac{1}{|d_1|}\right) > 0
+\end{aligned}\end{equation}
+Since both the denominators are positive, \(V\) is relevant. The fixed point value \(V^*\) is attained when the denominator \(d_1\) vanishes (\(d_1\) will vanish earlier than \(d_2\)).
+
+We can compare the rate of flows of \(V\) and \(J\):
+\begin{equation}\begin{aligned}
+	\frac{\Delta V}{\Delta J} = \frac{3V}{8J}\left(1 + \frac{|d_2|}{|d_1|}\right) > \frac{3V}{4J}
+\end{aligned}\end{equation}
+There we used the fact that \(|d_2| > |d_1|\).
+We finally come to the RG equation for \(U\):
+\begin{equation}\begin{aligned}
+	\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\frac{J^2}{d_2} = -4V^2\left(U + \frac{J}{4}\right)\frac{n_j}{d_0 d_1} - \frac{n_j J^2}{d_2}
+\end{aligned}\end{equation}
+For \(V>J\), we can expect \(U\) to be irrelevant. On the other hand, \(V<J\) makes \(U\) relevant.
+
+In short, the \(U>0\) regime is characterised by an irrelevant isospin-exchange coupling \(K\) and a relevant spin-exchange coupling \(J\), and the following set of RG equations for the remaining couplings \(U\) and \(V\):
+\begin{equation}\begin{aligned}
+	\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\frac{J^2}{d_2}, \quad \Delta V = -\frac{3n_j VJ}{8}\left(\frac{1}{d_2} + \frac{1}{d_1}\right)
+\end{aligned}\end{equation}
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U>0,U.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U>0,V.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U>0,J.pdf}
+
+	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U>0,U.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U>0,V.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U>0,J.pdf}
+\end{figure}
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.48\textwidth]{../figures/VvsJ_relvsirr.pdf}
+	\hspace*{\fill}
+	\includegraphics[width=0.48\textwidth]{../figures/UvsJ_relvsirr.pdf}
+\end{figure}
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.48\textwidth]{../figures/VcvsJ.pdf}
+	\hspace*{\fill}
+	\includegraphics[width=0.48\textwidth]{../figures/UcvsJ.pdf}
+\end{figure}
+
+\subsection{Attractive interaction on impurity: \(U<0\)}
+Here, we have \(J<0\) and \(K>0\). The denominators satisfy the following inequality in this regime:
+\begin{equation}\begin{aligned}
+	d_0 > d_3 > d_2 > d_1
+\end{aligned}\end{equation}
+
+The strong-coupling regime here corresponds to \(d_0 < 0\).
+This again means that all the denominators are negative.
+The spin-exchange coupling \(J\) is now irrelevant, because its bare value is negative while its RG equation is positive: \(\Delta J>0\).
+Moreover, the isospin coupling \(K\) is now positive and so is its RG equation: \(\Delta K>0\), which means it flows to strong-coupling.
+\(V\) also flows to strong-coupling.
+The RG equation for \(U\) can be written as
+\begin{equation}\begin{aligned}
+	\Delta U = 4V^2\left(\frac{K}{4} - U\right)\frac{n_j}{d_0 d_1} + \frac{n_j K^2}{d_3}
+\end{aligned}\end{equation}
+The first term is necessarily positive, while the second term is negative.
+This means that for roughly \(V_0 > J_0\), we  will have \(\Delta U > 0\), and since \(U_0 < 0\), this amounts to an irrelevant flow of \(U\) towards zero.
+On the other hand, for \(J_0 > V_0\), we will have \(\Delta U < 0\), and this corresponds to a relevant flow of \(U\) towards large negative value.
+
+In other words, the RG flows in this regime can be exactly mapped to those in the positive \(U\) regime.
+The general statement is: in the strong-coupling regime of positive(negative) \(U\), \(V\) is always relevant, \(J\)(\(K\)) is relevant, \(K\)(\(J\)) is irrelevant, and \(U\) is relevant when \(J(K) > V\), otherwise \(U\) is irrelevant.
+
+\section{Effective Hamiltonian and ground state}
+The fixed point Hamiltonian can, in general, be written as
+\begin{equation}\begin{aligned}
+	\mathcal{H}^* = \sum_{\sigma, k}\epsilon_k \tau_{k\sigma} - \frac{U^*}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2  + \sum_{\sigma, k < \Lambda^*}\left( V^* c^\dagger_{k\sigma}c_{d\sigma} + \text{h.c.} \right) + J^* \vec{S_d}\cdot\vec{s} + K^* \vec{C_d}\cdot\vec{C}
+\end{aligned}\end{equation}
+The first term is the kinetic energy of all the electrons.
+The next two terms are the impurity-diagonal pieces, featuring the renormalised interaction \(U^*\).
+The next three terms are the residual interactions between the impurity and the metal, with the renormalised couplings \(V^*, J^*\) and \(K^*\).
+The summations in these terms extend from the fixed point momentum cutoff \(\Lambda^*\) to 0.
+This is the region of momentum space  which the URG was unable to decouple.
+The operators \(\vec s\) and \(\vec C\) represent the macroscopic magnetic and charge spins formed by the remaining electrons that are lying inside the window \(\left[ 0, \Lambda^* \right] \):
+\begin{equation}\begin{aligned}
+	\vec s = \sum_{kk^\prime<\Lambda^*\atop{\alpha\beta}} c^\dagger_{k\alpha}\vec \sigma_{\alpha\beta}c_{k^\prime\beta}
+\end{aligned}\end{equation}
+Our goal here is to write down the ground state wavefunction for this low-energy Hamiltonian.
+
+To make progress, we will simplify the effective Hamiltonian by taking the zero bandwidth limit.
+This reduces it to a two-site problem.
+One site is of course the impurity site, and this site will be labeled as site 1.
+The other site will be formed by the center of mass degree of freedom of the conduction electrons, and will be labeled as site 2.
+The Hamiltonian for this two-site problem is
+\begin{equation}\begin{aligned}
+	\mathcal{H}_{IR} = - \frac{U^*}{2}\left(\hat n_{1 \uparrow} - \hat n_{1 \downarrow}\right)^2 + V^*\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.} \right) + J^*\vec{S_1}\cdot\vec{S_2} + K^* \vec{C_1}\cdot\vec{C_2}
+\end{aligned}\end{equation}
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.4\textwidth]{../figures/two_site_problem.png}
+	\caption{Two-site effective problem of fixed point Hamiltonian}
+	\label{twosite}
+
+\end{figure}
+The subscripts on the operators designate the site on which they act; \(\hat n_1\) is the number operator for the first site.
+
+We will adopt the following notation to represent the states in this Hilbert space.
+A general state will be represented in the Fock space basis as \(\ket{n_{1 \uparrow}n_{1 \downarrow}n_{2 \uparrow}n_{2 \downarrow}}\).
+For example,
+\begin{equation}\begin{aligned}
+	\ket{1101} = c^\dagger_{1 \uparrow}c^\dagger_{1 \downarrow}c^\dagger_{2 \downarrow}\ket{-}
+\end{aligned}\end{equation}
+\(\ket{-}\) is the vacuum state.
+
+For \(U>0\), the ground state is given by
+\begin{gather}
+	\label{gstate}
+	\ket{\Psi}_\text{1} = c_s \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c_c \frac{1}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right), \quad E_1 =  -V^*\sqrt{\gamma^2 + 4} -\frac{1}{4}U^* - \frac{3}{8}{J^*}
+\end{gather}
+where $\gamma = \frac{1}{2{V^*}}\left[ \frac{1}{4}\left( 3J^* + K^* \right) + \frac{1}{2}U^* \right]$. The probabilities for the spin and charge sectors for the ground state are
+\begin{equation}\begin{aligned}
+	\label{coeff_def}
+	\left(c_s\right)^2 = \frac{1}{2\sqrt{\gamma^2 + 4}}\left(\sqrt{\gamma^2 + 4} + \gamma\right), \quad \left(c_c \right)^2 = \frac{1}{2\sqrt{\gamma^2 + 4}}\left(\sqrt{\gamma^2 + 4} - \gamma\right)~.
+\end{aligned}\end{equation}
+For (roughly) \(J_0 > V_0\), we get \(J^* \gg V^*\) and \(U^* \gg U_0\) so that \(\gamma \gg 1\).
+This gives \(\left( c_s \right) ^2 \sim 1\) and \(\left( c_c \right) ^2 \sim 0\).
+The entire contribution to the ground state then comes from the spin sectors of the two sites.
+This is calculated numerically in fig.~\ref{cs_cc}.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../figures/coeffs_vs_J.pdf}
+	\caption{Variation of relative weights \(c_s\) and \(c_c\) with \(J_0\)}
+	\label{cs_cc}
+\end{figure}
+
+In the other regime of \(U<0\), the two competing states are \(\ket{\Psi}_1\) defined above (with energy \(E_1\)), and \(\ket{\Psi_2}\), the charge singlet: \(\ket{\Psi}_2 = \frac{1}{\sqrt 2}\left( \ket{2,0} - \ket{0,2} \right)\) having energy \(E_2\).
+\begin{equation}\begin{aligned}
+	E_2 = -\frac{3}{4}K^*, \quad E_1 - E_2 = -\frac{1}{4}\sqrt{\left( \frac{1}{2}K^* + U^* \right)^2 + (4V^*)^2} - \frac{1}{4}U^* + \frac{3}{4}K^*
+\end{aligned}\end{equation}
+For \(V_0 \gg K_0\), the largest energy scale will be \(V^*\), and we can then approximate this difference as
+\begin{equation}\begin{aligned}
+	E_1 - E_2 \simeq -V^* < 0
+\end{aligned}\end{equation}
+In such a case, \(\ket{\Psi}_1\) will therefore be the ground state. In the other regime \(V_0 \ll K_0\), the largest energy scale will be \(K^*\), and we can then write
+\begin{equation}\begin{aligned}
+	E_1 - E_2 \simeq - \frac{1}{8}K^* + \frac{3}{4}K^* > 0
+\end{aligned}\end{equation}
+In this case, the ground state will be \(\ket{\Psi}_2\).
+There exists, therefore, a phase transition at a critical plane \((U_c, K_c, V_c)\), where the ground state changes between the charge singlet \(\ket{\Psi}_2\) and the spin singlet + charge triplet \(\ket{\Psi}_1\).
+
+\section{Approach towards the thermodynamic limit}
+The URG method works strictly on finite systems and leads to finite values of fixed point couplings.
+The behaviour of the Hamiltonian in the thermodynamic limit can then be determined using finite-size scaling where we increase the bandwidth and decrease the width of each RG step.
+When applied to the fixed point value of the impurity-bath hybridisation parameter \(V\) (fig.~\ref{V_vs_D}), it can be seen that the fixed point value increases as the system size is increased, implying that the continuum limit of \(V^*\) is \(\infty\).
+This holds for both \(V_0 > J_0\) and \(V_0 < J_0\), as shown in the two panels of fig.~\ref{V_vs_D}.
+\begin{figure}[htpb]
+	\centering
+	\hspace*{\fill}
+	\includegraphics[width=0.4\textwidth]{../figures/Vstar_vs_D_smallV.pdf}
+	\hspace*{\fill}
+	\includegraphics[width=0.4\textwidth]{../figures/Vstar_vs_D_largeV.pdf}
+	\hspace*{\fill}
+	\caption{Variation of fixed point value \(V^*\) with increasing bandwith \(D_0\), for both \(V_0 > J_0\) and \(V_0 < J_0\).}
+	\label{V_vs_D}
+\end{figure}
+
+In a similar manner, we checked the variation of the spin and charge probabilities, \(c_s\) and \(c_c\), in the ground state, with increasing bandwith. The result is shown in fig.~\ref{c_vs_D}.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.45\textwidth]{../figures/coeffs_vs_D_largeV.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/coeffs_vs_D_smallV.pdf}
+	\caption{Variation of spin and charge fractions, \(c_s\) and \(c_c\), of the ground state, as a function of bare bandwidth \(D_0\).
+Left and right panels show the cases of \(J_0 < V_0\) and \(J_0 > V_0\) respectively.}
+	\label{c_vs_D}
+\end{figure}
+For both \(V_0 < J_0\) and \(V_0 > J_0\), we see that the spin contribution increases towards unity while the charge contribution vanishes.
+This indicates that at large bandwidth, the ground state becomes purely a spin singlet, formed purely by singly-occupied impurity states.
+\begin{equation}\begin{aligned}
+	\label{gstate_kondo}
+	\lim_{D_0 \to \infty} \ket{\Psi}_1 = \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) 
+\end{aligned}\end{equation}
+\section{Spectral function of the single-impurity Anderson model}
+To get a better look at what we are getting into and what we should expect going forward, we first calculate the spectral function of the smaller single-impurity Anderson model that is obtained as the low-energy Hamiltonian of an URG analysis of the full SIAM.
+This ow energy effective Hamiltonian is
+\begin{equation}\begin{aligned}
+	\epsilon_d \hat n_d + U\hat n_{d \uparrow} \hat n_{d \downarrow} + v \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + \sum_{k \in \left[-\Lambda^*, \Lambda^*\right], \sigma}\epsilon_k \hat n_{k\sigma}
+\end{aligned}\end{equation}
+All the impurity couplings are fixed point values, and the momentum states of the bath now run over a reduced bandwidth.
+The subscript \(d\) indicates that the operator is that of the impurity, while the subscript \(0\) indicates it is of the zeroth site of the bath: \(c_0 = \frac{1}{\sqrt N}\sum_k c_k\).
+The spectral function of the SIAM is already known from other methods like the numerical renormalization group.
+For small values of \(U\), the spectral function consists of just the central quasiparticle excitation peak.
+At larger values of \(U\), we see the emergence of the two Hubbard side bands while the spectral weight at the centre decreases.
+We also calculated the spectral function of the low energy theory sing exact diagonalization.
+The plots are shown in fig.~\ref{siam_spec_func}.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=\textwidth]{../figures/siam_specfunc_all.pdf}
+	\caption{Spectral function of the effective SIAM Hamiltonian for various values of \(\frac{U}{\Delta}\).
+\(\Delta\) is defined by the height of the central peak in the non-interacting model \(U=0\).
+The inset shows a zoom-in of the final spectral function \(\left( \frac{U}{\Delta} = 19.71 \right)\) near \(\omega = 0\).}
+	\label{siam_spec_func}
+\end{figure}
+\\\\
+Because we kept only a discrete bath of 4 momentum states, \textit{we had to artificially enforce the constancy of the height of the central peak, using \cite{langreth1966}.} To convert the discrete sum of delta functions into a continuous spectrum, we broadened them using a Gaussian.
+Following \cite{bullaNRGreview}, we replace the delta-functions at \(\pm x_n \equiv \pm(E_n - E_0)\) by normalised Gaussian functions
+\begin{equation}\begin{aligned}
+	\delta(\omega \pm x_n) \to \frac{1}{\eta_n\sqrt \pi}e^{-\left(\frac{\omega \pm x_n}{\eta_n}\right)^2}
+\end{aligned}\end{equation}
+The parameter \(\eta_n\) determines the height and width of the Gaussian, and is chosen such that the higher energy poles are broader than the lower energy ones.
+\begin{equation}\begin{aligned}
+	\eta_n = 2\Delta + \frac{1}{2}|x_n| 
+\end{aligned}\end{equation}
+where \(\Delta = \frac{V^2}{t}\) is the relevant energy scale of the non-interacting problem and \(t\) is the tight-binding hopping parameter of the conduction bath.
+\\\\
+The central peak (or equivalently, the central pole in the impurity Greens function) does not vanish even for exhorbitantly large values of \(\frac{U}{\Delta}\), implying that there is no stable local moment phase in the SIAM (a local moment phase would involve a gap at zero frequency in the impurity spectral function).
+Formally, the local moment phase will be stable only at \(U \to \infty\) or \(v^* = 0\).
+\\\\
+We also checked how the width of the central peak varies with increasing \(U\). The behaviour is shown in fig.~\ref{fwhm}. The width was also fitted against a function, as shown in the plot.
+\begin{figure}[htpb!]
+	\centering
+	\includegraphics[width=0.55\textwidth]{../figures/width_vs_U_simple_fit.pdf}
+	% \includegraphics[width=0.49\textwidth]{./width_vs_U_simple_fit_log.pdf}
+	\caption{The decay of the full width at half maximum (FWHM) of the central peak, with increasing \(\frac{U}{\Delta}\). The behaviour satisfies a function of the form shown in the legend.}
+	\label{fwhm}
+\end{figure}
+
+\section{Effective temperature scale at the fixed point}
+We will first change the discrete RG equation to a continuum equation by interpreting \(\Delta J\) as \(\frac{\Delta J}{\Delta \ln D}\), where the denominator is unity: \(\Delta \ln D = 1\).
+Now, since the bandwidth is decreasing under the RG, we can write \(\Delta \ln D = -d \ln D\).
+The continuum equation (for \(K=0\)) becomes
+\begin{equation}\begin{aligned}
+	\frac{\:\mathrm{d}J}{\:\mathrm{d}\ln D} = n(0)J^2 \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}
+\end{aligned}\end{equation}
+where we have replaced by the number of states at each shell with that at the Fermi surface (uniform DOS).
+We can define a dimensionless quantity \(g \equiv \frac{J}{\frac{D}{2}} - \omega\).
+In terms of \(g\), the continuum RG equation becomes
+\begin{equation}\begin{aligned}
+	-\frac{\:\mathrm{d}g}{\:\mathrm{d}\ln D} + \frac{D g}{2\omega - D} = \frac{n(0) g^2}{1 - \frac{g}{4}}
+\end{aligned}\end{equation}
+Now, for the specific case where \(D\) is small (\(D \to 0\)), we can simplify and integrate this equation:
+\begin{equation}\begin{aligned}
+	\frac{\:\mathrm{d}g}{\:\mathrm{d}\ln D} &= \frac{n(0) g^2}{\frac{g}{4} - 1}\\
+	\implies \left[\frac{1}{g} + \frac{1}{4}\ln g\right]_{g_0}^{g^*} &= n(0)\ln D\big\vert_{D_0}^{D^*}
+\end{aligned}\end{equation}
+\(g^*(_0), D^*(_0)\) are the fixed point (bare) values of \(g, D\).
+From the denominator structure, the fixed-point value is \(g^* =  4\).
+This gives an estimate of the bandwidth of the emergent window:
+\begin{equation}\begin{aligned}
+	D^* = D_0 \left( \frac{4}{g_0} \right)^\frac{1}{4n(0)}\exp\left\{-\frac{1}{n(0)}\left(\frac{1}{g_0} - \frac{1}{4}\right)\right\}
+\end{aligned}\end{equation}
+We can now define a temperature scale for the fixed-point theory:
+\begin{equation}\begin{aligned}
+	T_K \equiv \frac{2N^*}{\pi}D^* = \frac{2N^*}{\pi}D_0 \left( \frac{4}{g_0} \right)^\frac{1}{4n(0)}\exp\left\{-\frac{1}{n(0)}\left(\frac{1}{g_0} - \frac{1}{4}\right)\right\}
+\end{aligned}\end{equation}
+The factor of \(2N^*\) is inserted to make the Kondo temperature intensive (we will see below that the \(N^*\) allows it to  be written in terms of parameters of the two-site Hamiltonian) - \(2N^*\) is the total number of momentum states in the fixed point theory.
+The factor of \(\frac{1}{\pi}\) is for aesthetic reasons.
+Since we have and will primarily work with \(\omega=0\), the fixed point condition can be used to write \(D^* = \frac{J^* + K^*}{2}\).
+\begin{equation}\begin{aligned}
+	T_K = \frac{2N^*}{\pi}\frac{1}{2}\left(J^* + K^*\right) = \frac{1}{\pi}\left(j + k\right)
+\end{aligned}\end{equation}
+\section{Impurity susceptibilities}
+\subsection{Spin susceptibility}
+The spin susceptibility is defined as
+\begin{equation}\begin{aligned}
+	\label{chi_def}
+	\chi(\beta) = \beta \left(\left<\left(S_d^z\right)^2\right> - \left<S_d^z\right>^2\right)
+\end{aligned}\end{equation}
+There is an alternate way of calculating this. We insert a fictitious magnetic field that couples only to the impurity site. The Hamiltonian in the presence of this field is
+\begin{equation}\begin{aligned}
+	\label{field_ham}
+	\mathcal{H}^\prime(B) = \mathcal{H} + B S_d^z
+\end{aligned}\end{equation}
+The susceptibility is then given by
+\begin{equation}\begin{aligned}
+	\label{chi_exp}
+	\chi(\beta) &= \lim_{B \to 0}\frac{1}{\beta}\left[\frac{1}{Z(B)} \frac{\partial^2{Z(B)}}{\partial{B^2}}-\frac{1}{Z(B)^2} \left(\frac{\partial{Z(B)}}{\partial{B}}\right)^2\right]
+\end{aligned}\end{equation}
+where \(Z(B)\) is the partition function of the Hamiltonian \(\mathcal{H}^\prime(B)\).
+The following is to prove that the RHS of eqs.~\ref{chi_def} and \ref{chi_exp} are the same.
+We start with \ref{chi_exp}.
+The first derivative can be written as
+\begin{equation}\begin{aligned}
+	\frac{\partial{Z(B)}}{\partial{B}} = \text{Trace}\left[\frac{\partial{}}{\partial{B}} \exp\left\{-\beta\left( \mathcal{H} + BS_d^z \right) \right\}\right] = \text{Trace}\left[-\beta S_d^z \exp\left\{-\beta\left( \mathcal{H} + BS_d^z \right) \right\}\right]
+\end{aligned}\end{equation}
+which means the first term becomes
+\begin{equation}\begin{aligned}
+	\lim_{B \to 0}-\frac{1}{Z(B)^2} \left(\frac{\partial{Z(B)}}{\partial{B}}\right)^2 = -\left(\beta \frac{1}{\text{Trace}\left[\exp\left\{-\beta\mathcal{H}\right\}\right]} \text{Trace}\left[S_d^z \exp\left\{-\beta\mathcal{H}\right\}\right]\right)^2 = -\beta^2 \left<S_d^z\right>^2
+\end{aligned}\end{equation}
+The second derivative is
+\begin{equation}\begin{aligned}
+	\frac{\partial^2{Z(B)}}{\partial{B^2}} = \text{Trace}\left[-\beta S_d^z  \frac{\partial{}}{\partial{B}}\exp\left\{-\beta \left( \mathcal{H} + BS_d^z \right) \right\}\right] = \text{Trace}\left[\beta^2 \left(S_d^z\right)^2 \exp\left\{-\beta \left( \mathcal{H} + BS_d^z \right) \right\}\right]
+\end{aligned}\end{equation}
+so the second term becomes
+\begin{equation}\begin{aligned}
+	\lim_{B \to 0}\frac{1}{Z(B)} \frac{\partial^2{Z(B)}}{\partial{B^2}} = \beta^2 \frac{1}{\text{Trace}\left[\exp\left\{-\beta \mathcal{H}\right\}\right]}\text{Trace}\left[\left(S_d^z\right)^2 \exp\left\{-\beta \mathcal{H}\right\}\right] = \beta^2 \left<\left(S_d^z\right)^2 \right>
+\end{aligned}\end{equation}
+The full thing becomes
+\begin{equation}\begin{aligned}
+	\lim_{B \to 0}\frac{1}{\beta}\left[\frac{1}{Z(B)} \frac{\partial^2{Z(B)}}{\partial{B^2}}-\frac{1}{Z(B)^2} \left(\frac{\partial{Z(B)}}{\partial{B}}\right)^2\right] = \frac{1}{\beta}\left(-\beta^2 \left<S_d^z\right>^2 + \beta^2 \left<\left(S_d^z\right)^2 \right>\right) \\
+	= \beta \left(\left<\left(S_d^z\right)^2\right> - \left<S_d^z\right>^2\right) 
+\end{aligned}\end{equation}
+This completes the proof.
+
+To calculate the impurity susceptibility, we take the zero bandwidth Hamiltonian \(\mathcal{H}_{IR}\) and insert a magnetic field to obtain the Hamiltonian in eq.~\eqref{field_ham}.
+For a particular regime of \(U\), only one of \(J\) or \(K\) will be non-zero.
+We then numerically diagonalise this Hamiltonian to obtain the partition function \(Z(B)\) and its derivatives.
+The spin susceptibility can then be calculated using eq.~\eqref{chi_exp}.
+The results for \(U>0\) are shown in fig.~\ref{chi}.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.49\textwidth]{../figures/chiT_J=0.020.pdf}
+	\includegraphics[width=0.49\textwidth]{../figures/chiT_J=0.100.pdf}
+	\caption{Spin susceptibility of the impurity times temperature, for two sets of bare parameters, in \(U>0\).
+At low temperatures, it becomes linear because \(\chi\) itself becomes constant (screening), while at high temperatures, \(\chi\times T\) becomes constant because of the paramagnetic \(\sim 1/T\) form of \(\chi\).
+For the right panel with a larger value of the spin-exchange coupling, the \(\chi\) tries to go towards the local moment value of \(1/4\) but eventually drops back to the free orbital value of \(1/8\).}
+	\label{chi}
+\end{figure}
+
+\subsection{Charge susceptibility}
+We can similarly define the charge susceptibility as
+\begin{equation}\begin{aligned}
+	\label{zero_chi_charge}
+	\chi(\beta) = \beta \left(\left<\left(C_d^z\right)^2\right> - \left<C_d^z\right>^2\right) = \lim_{B_c \to 0}\frac{1}{\beta}\left[\frac{1}{Z(B_c)} \frac{\partial^2{Z(B_c)}}{\partial{B_c^2}}-\frac{1}{Z(B_c)^2} \left(\frac{\partial{Z(B_c)}}{\partial{B_c}}\right)^2\right]
+\end{aligned}\end{equation}
+where \(B_c\) is now a field that couples to the impurity charge-isospin:
+\begin{equation}\begin{aligned}
+	\label{charge_field}
+	\mathcal{H}^\prime(B_c) = \mathcal{H} + B_c C_d^z
+\end{aligned}\end{equation}
+The charge susceptibility for \(U<0\) is shown in fig.~\ref{chi_charge}.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.49\textwidth]{../figures/chi_chargeT_K=0.010.pdf}
+	\includegraphics[width=0.49\textwidth]{../figures/chi_chargeT_K=0.100.pdf}
+	\caption{Charge susceptibility for the impurity at \(U<0\), for two sets of bare parameters. The physics is very similar to that of the spin susceptibility in \(U>0\).}
+	\label{chi_charge}
+\end{figure}
+
+It is interesting to look at the behaviour of the charge susceptibility in the positive \(U\) regime, fig.~\ref{chi_charge_posU}.
+It  is seen that for \(J_0<V_0\), the charge susceptibility is very similar to the spin susceptibility, with a reduced saturation value.
+This is because, for that range of bare values, the ground state consists of a comparable mixture of the spin and charge states (see fig.~\ref{cs_cc}).
+This means that the magnetic field term in eq.~\eqref{charge_field} can couple to the charge component of the ground state, and give a non-zero charge susceptibility at zero temperature.
+On the other hand, for \(J_0 > V_0\), we see that \(\chi_c\) vanishes at low temperatures.
+This can again be understood from the ground state.
+For that range of bare values, the ground state can be approximated by purely the singlet, because the charge fraction \(c_-^c\) becomes very small.
+This means that the field \(B_c \) has nothing to couple with.
+Alternatively, it can be said that since the ground state has only terms with \(\hat n_d=1\), no number fluctuation is possible, and the impurity isospin is not susceptible at all to charge polarisation.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.48\textwidth]{../figures/chiC_posU_J=small.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/chiC_posU_J=large.pdf}
+	\caption{Charge susceptibility of the impurity in the positive \(U\) regime, for two values of \(J_0\).
+The smaller bare value leads to a spin+charge mixed ground state, and hence a non-zero \(\chi_c\) at zero temperature.
+The larger \(J_0\), however, leads to a purely spin ground state without any number fluctuation, and this gives vanishing \(\chi_c\) at zero temperature.}
+	\label{chi_charge_posU}
+\end{figure}
+
+From eq.~\eqref{gstate_kondo}, we know that in the thermodynamic limit, the ground state of \(U>0\) regime reduces to a screened local moment.
+That then implies that the charge susceptibility vanishes at low temperatures, owing to lack of any charge content in the ground state in the large bandwidth limit.
+\begin{equation}\begin{aligned}
+	\lim_{D_0 \to \infty}\chi_c(U>0, T \to 0) = 0
+\end{aligned}\end{equation}
+
+\section{Specific heat}
+The specific heat is calculated by diagonalizing the fixed point Hamiltonian, numerically.
+The obtained spectrum is denoted by \(\left\{ \mathcal{E}_i \right\} \).
+The total average energy of the impurity+cloud at temperature \(T\) is then
+\begin{equation}\begin{aligned}
+	\left<\mathcal{E} \right> = \frac{1}{Z}\sum_{i} \mathcal{E}_i e^{-\beta \mathcal{E}_i}
+\end{aligned}\end{equation}
+where \(Z = \sum_{i} e^{-\beta E_i}\) is the partition function. The specific heat of this system is thus
+\begin{equation}\begin{aligned}
+	C_V &= \frac{\partial{\left<\mathcal{E} \right>}}{\partial{T}} \\
+	    &= -\frac{1}{k_B T^2} \frac{\partial{\left<\mathcal{E} \right>}}{\partial{\beta}} \\
+	    &= \frac{1}{k_B T^2}\left[\frac{1}{Z}\sum_i \mathcal{E}_i^2 e^{-\beta \mathcal{E}_i} - \left(\frac{1}{Z}\sum_i \mathcal{E}_i e^{-\beta \mathcal{E}_i}\right)^2 \right] 
+\end{aligned}\end{equation}
+In the absence of impurity, the eigenvalues of the Hamiltonian are \(\left\{\mathcal{E}_i^0\right\}\) with a partition function \(Z^0 = \sum_{i} e^{-\beta E_i^0}\), so the bath specific heat is
+\begin{equation}\begin{aligned}
+	C_V^0 &= \frac{1}{k_B T^2}\left[\frac{1}{Z_0}\sum_i \mathcal{E}_i^2 e^{-\beta \mathcal{E}_i^0} - \left(\frac{1}{Z_0}\sum_i \mathcal{E}_i^0 e^{-\beta \mathcal{E}_i^0}\right)^2 \right] 
+\end{aligned}\end{equation}
+The impurity specific heat is the difference.
+\begin{equation}\begin{aligned}
+	C_V^\text{imp} = C_V - C_V^0
+\end{aligned}\end{equation}
+These values were calculated numerically and plotted against temperature in fig.~\ref{cv}.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../figures/Cv.pdf}
+	\caption{Impurity specific heat}
+	\label{cv}
+\end{figure}
+
+\section{Renormalization of impurity spectral function}
+In this section we will obtain the impurity spectral function, which is defined in terms of the impurity Green's function as
+\begin{equation}\begin{aligned}
+	\mathcal{A(\omega)} = -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] 
+\end{aligned}\end{equation}
+The zero temperature retarded Green's function for the impurity, in the frequency domain, can be written as (see Appendix.~\ref{appx-spectral-func})
+\begin{equation}\begin{aligned}
+	\mathcal{A(\omega)} = \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]
+\end{aligned}\end{equation}
+where \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in.
+The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term
+Since this is in terms of the exact eigenstates, it is a discrete sum of delta-functions.
+In practice, we get a continuous distribution.
+To compare with experiment, we need to convert the discrete sum into a continuous function.
+Following \cite{bullaNRGreview}, we replace the delta-functions at \(\pm x_n \equiv \pm(E_n - E_0)\) by normalized Gaussian functions
+\begin{equation}\begin{aligned}
+	\delta(\omega \pm x_n) \to \frac{1}{\eta_n\sqrt \pi}e^{-\left(\frac{\omega \pm x_n}{\eta_n}\right)^2}
+\end{aligned}\end{equation}
+The parameter \(\eta_n\) determines the height and width of the Gaussian, and is chosen such that the higher energy poles are broader than the lower energy ones:
+\begin{equation}\begin{aligned}
+	\eta_n = 4\Delta + \frac{1}{2}|x_n| 
+\end{aligned}\end{equation}
+\(\Delta = \pi \rho(0)V^2\) is the relevant energy scale for the non-interacting \((U=0)\) problem, \(\rho(0)\) being the density of states of the conduction bath at the Fermi energy.
+As a result, the function that we will numerically compute and plot is
+\begin{equation}\begin{aligned}
+	\mathcal{A(\omega)} &= \sum_{n,0}\frac{1}{d_0 \sqrt \pi \eta_n}\left[||\bra{0}c_{d\sigma}\ket{n}||^2e^{-\left(\frac{\omega - x_n}{\eta_n}\right)^2} + ||\bra{n}c_{d\sigma}\ket{0}||^2e^{-\left(\frac{\omega + x_n}{\eta_n}\right)^2}\right]
+\end{aligned}\end{equation}
+From the results of Langreth \cite{langreth1966}, we know that the spectral function at zero frequency is fixed by the occupancy of the impurity.
+Since we are in the particle-hole symmetric regime, this occupancy is fixed at 1, and hence so is the spectral function height at \(\omega = 0\).
+This result has been used to fix the spectral function height at the center during the computations.
+The fixed-point Hamiltonian \(H^*\) is diagonalized numerically to obtain \(\left\{E_n, \ket{n}\right\}\), for various values of the couplings.
+The intention here is to get an idea of how the spectral function morphs under the RG.
+Doing an actual reverse RG (described in \ref{rev_rg}) would require us to diagonalize a huge Hamiltonian.
+We take the simpler route of tuning the \(U\) from zero to soem large value.
+This should mimic the journey from the IR theory \((U=0)\) to the UV theory \((U \gg 0)\).
+
+The spectral function is plotted for three sets of values in fig.~\ref{spec_func}.
+For low values of \(U\), the profile is that of a single peak at zero frequency.
+This is expected because at the low energy effective theory, the high energy Hubbard side bands have been integrated out.
+As \(U\) increases, shoulder-like structures appear on either side of the peak, which finally, at larger \(U\), develop into two side-peaks.
+This is the microscopic theory, where high energy features are also relevant.
+\begin{center}
+	\includegraphics[width=0.8\textwidth]{../figures/gen_siam_spec_func.pdf}
+	\captionof{figure}{Impurity spectral function for multiple values of \(U\). The increase in value of \(U\) is accompanied by the appearance of the side-peaks.}
+	\label{spec_func}
+\end{center}
+The physics of the three peaks can now be looked into.
+Since the central peak is at zero energy, it has to do with excitations that do not cost any energy.
+There are two such excitations: excitations within the spin sector and within the charge sector.
+\begin{equation}\begin{aligned}
+	\ket{\uparrow} \mathrel{\mathlarger{\mathlarger{\mathop{\rightleftarrows}}^{J S_d^-}_{JS_d^+}}}\ket{\downarrow}, &&&&\ket{\Uparrow} \mathrel{\mathlarger{\mathlarger{\mathop{\rightleftarrows}}^{K C_d^-}_{K C_d^+}}}\ket{\Downarrow}\\
+\end{aligned}\end{equation}
+The thick arrow \(\Uparrow\) represents the charge isospin.
+At particle-hole symmetry, both the spin configurations has energy of \(\epsilon_d\), while the charge configurations have energy of \(2\epsilon_d + U=0\) and 0.
+Hence, no energy is required for these excitations, which is why see a macroscopic number of cloud electrons resonating with the impurity at the Fermi surface.
+Also note that if \(\hat S_i\) and \(\hat C_j\) are two operators of the spin and charge sector (\(i,j \in \left\{ x,y,z \right\} \)), then
+\begin{equation}\begin{aligned}
+	\hat S_i \hat C_j = \hat C_j \hat S_i = 0
+\end{aligned}\end{equation}
+We can see this by applying that operator on a basis state. Since the set of four states 
+\begin{equation}\begin{aligned}
+	\ket{\hat S_i = \pm \frac{1}{2}, \hat C_j = 0}, \ket{\hat S_i = 0, \hat C_j = \pm\frac{1}{2}}
+\end{aligned}\end{equation}
+are all independent, they form a basis. If we apply the operator on these states:
+\begin{equation}\begin{aligned}
+	\hat S_i \hat C_j \ket{\hat S_i} &= 0, &&&&\hat C_j \hat S_i \ket{S_i} = S_i \hat C_j \ket{S_i} = 0\\
+	\hat C_j \hat S_i \ket{C_j} &= 0, &&&&\hat S_i \hat C_j \ket{\hat C_j} = C_j \hat S_i \ket{\hat C_j} = 0 \\
+\end{aligned}\end{equation}
+This shows that each operator acts only on its own subspace. \(S_i\) does not act on the charge sector, and vice-versa. There is no single-particle excitation here.
+
+The physics of the side-peaks is that of single number fluctuations on the impurity. These are brought about by the term \(Vc^\dagger_{0\sigma}c_{d\sigma} + \text{h.c.}\).
+\begin{equation}\begin{aligned}
+	\left( \epsilon_d  \right) \ket{\sigma} & \mathrel{\mathlarger{\mathlarger{\mathop{\rightleftarrows}}^{V c^\dagger_{d\overline\sigma}/V c_{d\sigma}}_{V c_{d\overline\sigma}/V c^\dagger_{d\sigma}}}} &\ket{n_d=2,0} \left( 0 \right) \\
+\end{aligned}\end{equation}
+These transitions involve energy transfer of the order of \(\epsilon_d\).
+This is why, at very small \(U\), they remain absorbed inside the central peak.
+These transitions do not involve any spin or charge-flip, rather they take the impurity between the spin and charge sectors.
+
+\section{Effective Hamiltonian for excitations of the Kondo cloud}
+To find an effective Hamiltonian for the excitations of the Kondo cloud, we will integrate out the impurity part of the wavefunction. The Schrodinger equation for the \(J > K\) ground state is
+\begin{equation}\begin{aligned}
+	E_g &\left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right] \\
+	    &= \mathcal{H} \left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]\\
+	    &= \mathcal{H}_0^* \left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]\\
+	    &+V\sum_{\beta}\left[c^\dagger_{2\beta}c_{1\beta} - c_{2\beta}c^\dagger_{1\beta}\right]\left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]\\
+	    &+ J \vec{S_d}\cdot\vec{s}\left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]\\
+	    &+ K \vec{C_d}\cdot\vec{c}\left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]
+\end{aligned}\end{equation}
+The last two lines gives
+\begin{equation}\begin{aligned}
+\frac{1}{2}Jc_-^s \left[s^z \left(\ket{\uparrow, \downarrow} + \ket{\downarrow, \uparrow}\right) +  s^+ \ket{\downarrow, \downarrow} - s^-\ket{\uparrow, \uparrow}\right] + \frac{1}{2}Kc^c_- \left[c^z\left(\ket{\uparrow\downarrow, 0} - \ket{0, \uparrow\downarrow}\right) + c^+\ket{0, 0} \right.\\
++ \left.c^-\ket{2, 2}\right]
+\end{aligned}\end{equation}
+The second line gives
+\begin{equation}\begin{aligned}
+	V c^\dagger_{2\uparrow}\left[c_-^s \left(\ket{0, \downarrow}\right) + c^c_- \left(\ket{\downarrow, 0}\right)\right] + V c^\dagger_{2 \downarrow}\left[c_-^s \left(- \ket{0, \uparrow}\right) + c^c_- \left(\ket{\uparrow, 0}\right)\right] \\
+	- Vc_{2 \uparrow}\left[c_-^s \left(- \ket{ \uparrow\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow, \uparrow\downarrow}\right)\right] - V c_{2 \downarrow}\left[c_-^s \left(-\ket{ \uparrow\downarrow, \downarrow}\right) + c^c_- \left(\ket{ \downarrow, \uparrow\downarrow}\right)\right]
+\end{aligned}\end{equation}
+We will now write down four equations by comparing the coefficients of \(\ket{ \uparrow}, \ket{ \downarrow}, \ket{0}\) and \(\ket{2}\) of the impurity sector:
+\begin{equation}\begin{aligned}
+	\left( E_g - H_0^* \right) c_-^s \ket{\downarrow} &= V c^c_- \left( c^\dagger_{2 \downarrow}\ket{0} - c_{2 \uparrow}\ket{2} \right) + \frac{1}{2}J c^s_-\left( s^z\ket{ \downarrow} - s^-\ket{\uparrow} \right) && \left[\text{eq.
+from }\ket{\uparrow}\right] \\
+	\left( -E_g + H_0^* \right) c_-^s \ket{\uparrow} &= V c^c_- \left( c^\dagger_{2 \uparrow}\ket{0} - c^\dagger_{2 \downarrow}\ket{2} \right) + \frac{1}{2}J c^s_-\left( s^z\ket{\uparrow} + s^+\ket{ \downarrow} \right)&& \left[\text{eq.
+from }\ket{\downarrow}\right] \\
+	\left( E_g - H_0^* \right) c_-^c \ket{2} &= V c^s_- \left( c^\dagger_{2 \uparrow}\ket{ \downarrow} - c^\dagger_{2 \downarrow}\ket{ \uparrow} \right) + \frac{1}{2}K c^c_-\left( -c^z\ket{2} + c^+\ket{0} \right) && \left[\text{eq.
+from }\ket{0}\right] \\
+	\left( E_g - H_0^* \right) c_-^c \ket{0} &= V c^s_- \left( c_{2 \uparrow}\ket{ \uparrow} + c_{2 \downarrow}\ket{ \downarrow} \right) + \frac{1}{2}K c^c_-\left( c^z\ket{0} + c^-\ket{2} \right) && \left[\text{eq.
+from }\ket{2}\right]
+\end{aligned}\end{equation}
+These can be rearranged into
+\begin{equation}\begin{aligned}
+	\left( E_g - H_0^* - \frac{1}{2}J s^z\right) \ket{\downarrow} &= V \lambda^{-1} \left( c^\dagger_{2 \downarrow}\ket{0} - c_{2 \uparrow}\ket{2} \right) - \frac{1}{2}J s^-\ket{\uparrow} \\
+	\left( E_g - H_0^*  + \frac{1}{2}J s^z\right) \ket{\uparrow} &= V \lambda^{-1} \left( c_{2 \downarrow}\ket{2} - c^\dagger_{2 \uparrow}\ket{0}\right) - \frac{1}{2}J s^+\ket{ \downarrow} \\
+	\left( E_g - H_0^*  + \frac{1}{2}K c^z\right)  \ket{2} &= V \lambda \left( c^\dagger_{2 \uparrow}\ket{ \downarrow} - c^\dagger_{2 \downarrow}\ket{ \uparrow} \right) + \frac{1}{2}K c^+\ket{0}  \\
+	\left( E_g - H_0^* - \frac{1}{2}K c^z\right)  \ket{0} &= V \lambda \left( c_{2 \uparrow}\ket{ \uparrow} + c_{2 \downarrow}\ket{ \downarrow} \right) + \frac{1}{2}K c^-\ket{2} 
+\end{aligned}\end{equation}
+where \(\lambda = \frac{c^s_-}{c^c_-}\). We want to find the effective Hamiltonian in the subspace of \(\ket{\downarrow}\). We first eliminate the charge sector from these equations:
+\begin{equation}\begin{aligned}
+	\ket{0} =& V\lambda\left[\frac{1}{A^K_-}c_{2 \uparrow} + \frac{K}{2}\frac{1}{A^K_-}c^- \frac{1}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left(\frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \uparrow}- c^\dagger_{2 \downarrow}\right)\right]\ket{ \uparrow} \\
+		 &+V\lambda\left[\frac{1}{A^K_-}c_{2 \downarrow} + \frac{K}{2}\frac{1}{A^K_-}c^- \frac{1}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left(c^\dagger_{2 \uparrow} + \frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \downarrow}\right)\right]\ket{ \downarrow}\\
+	\ket{2} &= \frac{V\lambda}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left[\left(c^\dagger_{2 \uparrow} + \frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \downarrow}\right)\ket{ \downarrow} + \left(\frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \uparrow}- c^\dagger_{2 \downarrow}\right)\ket{ \uparrow}\right]
+\end{aligned}\end{equation}
+where
+\begin{equation}\begin{aligned}
+	A^K_\pm = E_g - H_0^* \pm \frac{1}{2}Kc^z
+\end{aligned}\end{equation}
+For ease of labeling, we will think of these equations as
+\begin{equation}\begin{aligned}
+	\ket{0} = a_0^\uparrow \ket{ \uparrow} + a_0^\downarrow\ket{ \downarrow}, \ket{2} = a_2^\uparrow \ket{ \uparrow} + a_2^\downarrow\ket{ \downarrow}
+\end{aligned}\end{equation}
+The remaining two equations can then be written as
+\begin{equation}\begin{aligned}
+	A^J_-\ket{ \downarrow} &= \frac{V}{\lambda}\left[ c^\dagger_{2 \downarrow}\left(a_0^\uparrow \ket{ \uparrow} + a_0^\downarrow\ket{ \downarrow}\right) - c_{2 \uparrow}\left(a_2^\uparrow \ket{ \uparrow} + a_2^\downarrow\ket{ \downarrow}\right) \right] - \frac{J}{2}s^- \ket{ \uparrow}\\
+	A^J_+\ket{\uparrow} &= \frac{V}{\lambda}\left[ c_{2 \downarrow}\left(a_2^\uparrow \ket{ \uparrow} + a_2^\downarrow\ket{ \downarrow}\right) - c^\dagger_{2 \uparrow}\left(a_0^\uparrow \ket{ \uparrow} + a_0^\downarrow\ket{ \downarrow}\right) \right]  - \frac{J}{2}s^+ \ket{ \downarrow}\\
+\end{aligned}\end{equation}
+where 
+\begin{equation}\begin{aligned}
+	A^J_\pm = E_g - H_0^* \pm \frac{1}{2}Js^z
+\end{aligned}\end{equation}
+Eliminating \(\ket{\downarrow}\) and solving for \(\ket{\uparrow}\) gives
+\begin{equation}\begin{aligned}
+	A^J_+ \ket{\uparrow} =&  \frac{V}{\lambda}\left( c_{2 \downarrow}a_2^\uparrow - c^\dagger_{2 \uparrow}a_0^\uparrow \right) \ket{\uparrow} + \left( \frac{V}{\lambda}c_{2 \downarrow}a_2^\downarrow - \frac{V}{\lambda}c^\dagger_{2 \uparrow}a_0^\downarrow - \frac{J}{2}s^+ \right) \ket{\downarrow}\\
+			     =& \frac{V}{\lambda}\left( c_{2 \downarrow}a_2^\uparrow - c^\dagger_{2 \uparrow}a_0^\uparrow \right) \ket{\uparrow} \\
+			     +& \left[ \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow\right) - \frac{J}{2}s^+ \right] \frac{1}{A^J_- - \frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\downarrow - c_{2 \uparrow}a_2^\downarrow \right) }\left[\frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow\right) - \frac{J}{2}s^-\right] \ket{\uparrow}
+\end{aligned}\end{equation}
+The effective Hamiltonian for the \(\ket{\uparrow}\) state is
+\begin{equation}\begin{aligned}
+	\label{full_ham}
+	H_0^* - \frac{J}{2}s^z + \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\uparrow - c^\dagger_{2 \uparrow}a_0^\uparrow \right) + \left[ \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow\right) - \frac{J}{2}s^+ \right] \frac{1}{A^J_- - \frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\downarrow - c_{2 \uparrow}a_2^\downarrow \right) }\\
+	\times\left[\frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow\right) - \frac{J}{2}s^-\right]
+\end{aligned}\end{equation}
+To get a clearer picture of this effective Hamiltonian, we will keep up to two-particle interactions. We first write down the full forms of \(a_{0,2}^\sigma\):
+\begin{equation}\begin{aligned}
+	a_0^\sigma &= V\lambda\left[\frac{1}{A^K_-}c_{2 \sigma} + \frac{K}{2}\frac{1}{A^K_-}c^- \frac{1}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left(\frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \sigma}- \sigma c^\dagger_{2 \sigma}\right)\right]\\
+	a_2^\sigma &= \frac{V\lambda}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left(-\sigma c^\dagger_{2 -\sigma} + \frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \sigma}\right)
+\end{aligned}\end{equation}
+We will first look at the special case of \(K = 0\). There, the above expressions simplify to
+\begin{equation}\begin{aligned}
+	a_0^\sigma &= V\lambda\frac{1}{A^K_-}c_{2 \sigma} = \frac{V \lambda}{E_g}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c_{2\sigma} + \mathcal{O}({H_0^*}^3)\\
+	a_2^\sigma &= -\sigma V\lambda\frac{1}{A^K_+}c^\dagger_{2 -\sigma} = -\sigma\frac{V \lambda}{E_g}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c^\dagger_{2 -\sigma} + \mathcal{O}({H_0^*}^3)\\
+\end{aligned}\end{equation}
+We will make use of the following commutators:
+\begin{equation}\begin{aligned}
+	&\left[\left(H_0^*\right)^m, c_{2\sigma}\right] = - \sum_k \frac{\epsilon^m_k}{\sqrt{N^*}}c_{k\sigma}, && \left[\left(H_0^*\right)^m, c^\dagger_{2\sigma}\right] = \sum_k \frac{\epsilon_k^m}{\sqrt{N^*}}c^\dagger_{k\sigma}, && m = 1, 2\\
+	&\left[\left(H_0^*\right)^m, s^+\right] = \sum_{kk^\prime}\left(\epsilon_k^m - \epsilon_{k^\prime}^m\right)c^\dagger_{k\beta}c_{k^\prime \overline \beta} , &&&& m = 1, 2\\
+	&\left[\left(s^z\right)^m, c_{2\sigma}\right] = - \left(\frac{\sigma}{2}\right)^mc_{2\sigma}, && \left[\left(s^z\right)^m, c^\dagger_{2\sigma}\right] = \left(\frac{\sigma}{2}\right)^mc^\dagger_{2\sigma}, && m = 1, 2\\
+	&\left[\left(c^z\right)^m, c_{2\sigma}\right] = - \left(\frac{1}{2}\right)^mc_{2\sigma}, && \left[\left(c^z\right)^m, c^\dagger_{2\sigma}\right] = \left(\frac{1}{2}\right)^mc^\dagger_{2\sigma}, && m = 1, 2\\
+\end{aligned}\end{equation}
+Now we evaluate the various terms in the effective Hamiltonian.
+\begin{flalign*}
+	{{c_{2 \downarrow}a_2^\uparrow}} &= -\frac{V \lambda}{E_g}c_{2 \downarrow}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c^\dagger_{2\downarrow}\\
+				     &= -\frac{V \lambda}{E_g}\left[c_{2 \downarrow} + \frac{1}{E_g}\left(H_0^* \right)c_{2 \downarrow} + \sum_k \frac{\epsilon_k}{E_g\sqrt{N^*}}c_{k\downarrow} + \frac{1}{E_g^2}\left(H_0^* \right)^2c_{2 \downarrow} + \sum_k \frac{\epsilon^2_k}{E_g^2\sqrt{N^*}}c_{k\downarrow}\right]c^\dagger_{2\downarrow}\\
+				     &= -\frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]c_{2 \downarrow}c^\dagger_{2\downarrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\\
+{{c_{2 \uparrow}a_2^\downarrow }}&= -\frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]c_{2 \uparrow}c^\dagger_{2\uparrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right) c_{k\uparrow}c^\dagger_{k^\prime\uparrow}\\
+{{c^\dagger_{2 \uparrow}a_0^\uparrow}} &= c^\dagger_{2 \uparrow} \frac{V \lambda}{E_g}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c_{2 \uparrow}\\
+					   &= \frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]c^\dagger_{2 \uparrow}c_{2\uparrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c^\dagger_{k\uparrow}c_{k^\prime\uparrow}\\
+{{c^\dagger_{2 \downarrow}a_0^\downarrow}} &= \frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]c^\dagger_{2 \downarrow}c_{2\downarrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\\
+{{c_{2 \downarrow}a_2^\downarrow }}&= \frac{V \lambda}{E_g}c_{2 \downarrow}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c^\dagger_{2\uparrow}\\
+				       &=\frac{V \lambda}{E_g}\left[1 + \frac{1}{E_g}\left(H_0^* \right)\right]c_{2 \downarrow}c^\dagger_{2\uparrow} + \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c_{k\downarrow}c^\dagger_{k^\prime\uparrow}\\
+{{c_{2 \uparrow}a_2^\uparrow}} &=-\frac{V \lambda}{E_g}\left[1 + \frac{1}{E_g}\left(H_0^* \right)\right]c_{2 \uparrow}c^\dagger_{2\downarrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c_{k\uparrow}c^\dagger_{k^\prime\downarrow}\\
+{{c^\dagger_{2 \uparrow}a_0^\downarrow }}&= \frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g}\right]c^\dagger_{2 \uparrow}c_{2\downarrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c^\dagger_{k\uparrow}c_{k^\prime\downarrow}\\
+{{c^\dagger_{2 \downarrow}a_0^\uparrow}} &= \frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g}\right]c^\dagger_{2 \downarrow}c_{2\uparrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c^\dagger_{k\downarrow}c_{k^\prime\uparrow}\\
+{{c_{2 \downarrow}a_2^\uparrow - c^\dagger_{2 \uparrow}a_0^\uparrow}} &= -\frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]\times 2 + \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)\left(c^\dagger_{k\uparrow}c_{k^\prime\uparrow} - c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\right)\\
+{{c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow }}&= \frac{V \lambda}{E_g}\left[1 + \frac{1}{E_g}\left(H_0^* \right)\right]c_{2 \downarrow}c^\dagger_{2\uparrow} \times 2 + \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)\left(c_{k\downarrow}c^\dagger_{k^\prime\uparrow} + c^\dagger_{k\uparrow}c_{k^\prime\downarrow}\right)\\
+{{c^\dagger_{2 \downarrow}a_0^\downarrow - c_{2 \uparrow}a_2^\downarrow}} &= \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)\left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right)\\
+	{{c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow}} &= \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)\left(c_{k\uparrow}c^\dagger_{k^\prime\downarrow} - c^\dagger_{k\downarrow}c_{k^\prime\uparrow}\right)
+\end{flalign*}
+In all the expressions, we have dropped terms that have more than 4 operators in product.
+Also, in the last four equations, we have substituted \(\hat n_{2 \uparrow} - \hat n_{2 \downarrow} = 1\), because this is the effective Hamiltonian for the state with \(s^z = \frac{1}{2}\).
+We now substitute these expressions into the effective Hamiltonian:
+\begin{equation}\begin{aligned}
+	&H_0^* - \frac{J}{2}s^z -\frac{2V^2}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right] + \frac{V^2 }{E_g N^*}\sum_{kk^\prime} \xi_k \left(c^\dagger_{k\uparrow}c_{k^\prime\uparrow} - c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\right) \\
+	&+ \left[ \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow\right)\right] \frac{1}{A^J_- - \frac{V^2}{E_g N^*}\sum_{kk^\prime} \xi_k \left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right) }\left[\frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow\right)\right]\\
+	&+ \left[ \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow\right) \right] \frac{1}{A^J_- - \frac{V^2}{E_g N^*}\sum_{kk^\prime} \xi_k \left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right) }\left[ - \frac{J}{2}s^-\right]\\
+	&+ \left[- \frac{J}{2}s^+ \right] \frac{1}{A^J_- - \frac{V^2}{E_g N^*}\sum_{kk^\prime} \xi_k \left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right) }\left[\frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow\right)\right]\\
+	&+ \frac{J^2}{4}\left[s^+ \right] \frac{1}{A^J_- - \frac{V^2}{E_g N^*}\sum_{kk^\prime} \xi_k \left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right) }\left[s^-\right]\\
+\end{aligned}\end{equation}
+where \(\xi_k = \frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\). We first consider only zeroth order terms of the central propagator.
+\begin{equation}\begin{aligned}
+	&H_0^* - \frac{J}{2}\underbrace{s^z}_{\frac{1}{2}} -\frac{2V^2}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right] + \frac{V^2 }{E_g N^*}\sum_{kk^\prime} \left(\xi_k \right)\left(c^\dagger_{k\uparrow}c_{k^\prime\uparrow} - c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\right) \\
+	&+ \frac{V^4}{E^2_g {N^*}^2 \left( E_g + \frac{J}{4} \right) }\sum_{kk^\prime}\left(\xi_{k^\prime} + 2 - \xi_k \right)c^\dagger_{k\uparrow}c_{k^\prime\downarrow}\sum_{kk^\prime} \left(\xi_k + \xi_{k^\prime}\right)c^\dagger_{k\downarrow}c_{k^\prime\uparrow}\\
+	&+ \frac{V^2 J}{2E_g \left( E_g + \frac{J}{4} \right){N^*}}\sum_{kk^\prime}\left(\xi_{k^\prime} + 2 - \xi_k \right)c^\dagger_{k\uparrow}c_{k^\prime\downarrow}\sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow}\\
+	&+ \frac{JV^2}{2E_g \left( E_g + \frac{J}{4} \right)N^*} \sum_{kk^\prime}c^\dagger_{k \uparrow}c_{k^\prime \downarrow}\sum_{kk^\prime} \left(\xi_k + \xi_{k^\prime}\right)c^\dagger_{k\downarrow}c_{k^\prime\uparrow}\\
+	&+ \frac{J^2}{4\left( E_g + \frac{J}{4} \right)}\underbrace{s^+ s^-}_{s^z + \frac{1}{2}= 1}
+\end{aligned}\end{equation}
+We have set \(s^z = -\frac{1}{2}\) in the denominator, hence the \(E_g = \frac{J}{4}\).
+If we also consider the first and second order terms from the central propagator, note that they will produce terms of more than quartic interactions in the first three terms.
+For the last term, we get
+\begin{equation}\begin{aligned}
+	\frac{J^2}{4\left( E_g + \frac{J}{4} \right)}s^+\left[\frac{H_0^*}{E_g + \frac{J}{4}} + \left(\frac{H_0^*}{E_g + \frac{J}{4}}\right)^2\right]s^-
+\end{aligned}\end{equation}
+Using the commutator of \(H_0^*\) with \(s^+\) to bring \(H_0^*\) to the left, and using \(s^+ s^- = s^z + \frac{1}{2} = 1\), we get
+\begin{equation}\begin{aligned}
+	\frac{J^2}{4\left( E_g + \frac{J}{4} \right)}\left[\frac{H_0^*}{E_g + \frac{J}{4}} + \left(\frac{H_0^*}{E_g + \frac{J}{4}}\right)^2 - \sum_{kk^\prime qq^\prime} \left( \xi_k^J - \xi_{k^\prime}^J \right)  c^\dagger_{k \uparrow}c_{k^\prime \downarrow}c^\dagger_{q \downarrow}c_{q^\prime \uparrow}\right]
+\end{aligned}\end{equation}
+where \(\xi_k^J = \frac{\epsilon_k }{E_g + \frac{J}{4}}+ \frac{\epsilon_k^2}{\left(E_g + \frac{J}{4}\right)^2}\). The full effective Hamiltonian, for \(K=0\), up to quartic interactions, is
+\begin{equation}\begin{aligned}
+	H_0^* + \frac{J}{4}\left(\frac{J}{E_g + \frac{J}{4}} - 1\right) - \frac{2V^2}{E_g} + \frac{V^2 }{E_g N^*}\sum_{kk^\prime} \left(\xi_k \right)\left(c^\dagger_{k\uparrow}c_{k^\prime\uparrow} - c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\right) - \frac{2V^2}{E_g}\left[\frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right] \\
+	+ \frac{J^2}{4\left( E_g + \frac{J}{4} \right) }\left[\frac{H_0^*}{E_g + \frac{J}{4}} + \left(  \frac{H_0^*}{E_g + \frac{J}{4}}\right)^2 \right] + \sum_{kk^\prime q q^\prime} F_{kk^\prime qq^\prime}c^\dagger_{k \uparrow}c_{k^\prime \downarrow}c^\dagger_{q \downarrow}c_{q^\prime \uparrow}
+\end{aligned}\end{equation}
+The coefficient \(F_{kk^\prime qq^\prime}\) is
+\begin{equation}\begin{aligned}
+	\label{off_diag_coeff}
+	F_{kk^\prime qq^\prime} = \frac{V^2}{E_g N^* (E_g + \frac{J}{4})}\left[\frac{V^2}{E_g N^*}\left( \xi_{k^\prime} + 2 - \xi_k \right)\left( \xi_q + \xi_{q^\prime} \right) + \frac{J}{2}\left( \xi_{k^\prime} + 2 - \xi_k + \xi_q + \xi_{q^\prime} \right)  \right] \\
++ \frac{J^2}{4\left( E_g + \frac{J}{4} \right)} \left(\xi_{k^\prime}^J - \xi_{k}^J\right)
+\end{aligned}\end{equation}
+There are two main types of interactions that gets generated upon integrating out the impurity.
+One is the Fermi liquid type interactions arising from the \({H_0^*}^2\) terms.
+The Fermi liquid part of the Hamiltonian is
+\begin{equation}\begin{aligned}
+	\left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right)^2} - \frac{2V^2}{E_g^2}\right] H_0^* + \left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right)^2} - \frac{2V^2}{E_g^3}\right] {H_0^*}^2 \\
+	= \left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right)^2} - \frac{2V^2}{E_g^2}\right] \left[ H_0^* + \sum_{kk^\prime \sigma \sigma^\prime} f_{kk^\prime} \hat n_{k\sigma} \hat n_{k^\prime \sigma^\prime}\right]
+\end{aligned}\end{equation}
+where the Landau parameter is given by
+\begin{equation}\begin{aligned}
+	\label{fermiliq}
+	f_{kk^\prime} = \left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right)^2} - \frac{2V^2}{E_g^2}\right]^{-1}\left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right) ^3} - \frac{2V^2}{E_g^3}\right]\epsilon_k \epsilon_{k^\prime}
+\end{aligned}\end{equation}
+The more interesting interaction is the off-diagonal term
+\begin{equation}\begin{aligned}
+	 \sum_{kk^\prime q q^\prime} F_{kk^\prime qq^\prime}c^\dagger_{k \uparrow}c_{k^\prime \downarrow}c^\dagger_{q \downarrow}c_{q^\prime \uparrow}
+\end{aligned}\end{equation}
+This interaction arises from the enhanced entanglement between the impurity and the conduction electrons; removing the impurity from the singlet and the triplet generates these off-diagonal scatterings.
+As such, this is an indicator of the macroscopic entanglement of the singlet formed at the IR fixed point, and plotted in fig.~\ref{mutI}.
+
+We also wish to point out that this scattering is a signature of the change in Luttinger's count in going from the free orbital or local moment fixed point to the strong-coupling fixed point, as shown in eq.~\eqref{luttinger_change}.
+Both this off-diagonal scattering as well as the change in Luttinger's count are a direct consequence of the non-number conserving term \(V c^\dagger_{k} c_d\) in the full Hamiltonian.
+The topological change of Luttinger's count is concomitant with the presence of the off-diagonal scattering term in the effective Hamiltonian.
+\textit{Just the Fermi liquid piece in eq.~\eqref{fermiliq} will give neither the enhanced mutual information nor the change in Luttinger's count}.
+
+\section{Obtaining the real space low energy Hamiltonian: the local Fermi liquid}
+The next step is to obtain the lowest excitations of the fixed point Hamiltonian, in real space.
+We will work in the \(U>0\) regime.
+For \(V,J \gg 1\), the impurity couples very strongly with the zeroth site, and at zeroth order, it suffices to say that the zeroth site decouples from the rest of the lattice.
+This zeroth Hamiltonian then consists of two sites interacting with each other through \(V\) and \(J\) (the two site problem analysed before).
+\begin{gather}
+	H^*_0 = \sum_{\sigma}\left( V^* c^\dagger_{0\sigma}c_{d\sigma} + \text{h.c.} \right) + J^* \vec{S_d}\cdot\vec{s} - \frac{1}{2}U^*\left( \hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 \\
+	\ket{\Psi}_1 = {c_s} \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + {c_c} \frac{1}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right), \quad E_1 =  -V^*\sqrt{\gamma^2 + 4} -\frac{1}{4}U^* - \frac{3}{8}{J^*}
+\end{gather}
+These were obtained in eq.~\eqref{gstate}. The quantities \(\gamma\) and \(c_{s,c}\) were defined in and around eq.~\eqref{coeff_def}.
+
+We start with the ground state \(\ket{\Psi}_1\) and the star graph as the zeroth level ground state and Hamiltonian, and then add a nearest-neighbour hopping term as a perturbation of the zeroth Hamiltonian.
+We know that the ground state for the interacting part is predominantly the spin-singlet (it was shown while calculating the ground states of the effective zero-mode Hamiltonian that the ground state is a mixture of singlet and triplet, and the triplet part dies out at large system sizes, see eq.~\eqref{gstate_kondo}), so we will take that as our reference state and treat the hopping part that connects the origin to the first site,
+\begin{equation}\begin{aligned}
+	H_X = t\sum_{\vec r_1,\sigma} c^\dagger_{0\sigma}c_{\vec r_1,\sigma} +\text{h.c.} \equiv v^\dagger + v
+\end{aligned}\end{equation}
+as a weak perturbation.
+\(\vec r_1\) here sums over the sites that are nearest to the origin.
+Once this perturbation is taken care of up to a certain order, we will have a decoupled singlet formed by the impurity and the zeroth site, and the rest of the lattice formed by \(N-1\) sites along with the interaction induced by the perturbation.
+To be precise, the goal is to integrate out the perturbation and generate an effective Hamiltonian in the subspace of the minimal energy states of the two site Hamiltonian, and this effective Hamiltonian will therefore describe the lowest excitations on top of the ground state \(\ket{\Psi}_1\).
+The minimal energy subspace is given by the states:
+\begin{equation}\begin{aligned}
+	\ket{\Phi}_{i} = \ket{\Psi}_1 \otimes \ket{\hat n_{1 \uparrow}, \hat n_{1 \downarrow}}, ~\text{ where }i \in \begin{cases}
+		0: & \hat n_{1 \uparrow} = \hat n_{1 \downarrow} = 0\\
+		1: & 1 - \hat n_{1 \uparrow} =  \hat n_{1 \downarrow} = 0\\
+		2: & \hat n_{1 \uparrow} = 1 - \hat n_{1 \downarrow} = 0\\
+		3: & 1 - \hat n_{1 \uparrow} =  1 - \hat n_{1 \downarrow} = 0
+	\end{cases} 
+\end{aligned}\end{equation}
+
+The effective Hamiltonian will be calculated using perturbation theory in \(\frac{H_X^{n}}{{H_0^*}^{n-1}}\).
+Since an odd number of scattering processes cannot bring the initial state back to itself, such orders will be absent from the effective Hamiltonian.
+
+ \subsection{Second order effective Hamiltonian}
+ We first consider the case of \(n=2\). The renormalisation of the effective Hamiltonian in the ground state subspace, at this order, is given by
+\begin{equation}\begin{aligned}
+	\Delta H = \sum_{ij,n}\ket{\Phi}_i \bra{\Phi_i}H_X \ket{\Psi}_n \frac{1}{E_\text{gs} - E_n} \bra{\Psi}_n H_X \ket{\Phi}_j \bra{\Phi_j} = \sum_{ij}\ket{\Phi}_i \bra{\Phi_j} \bra{\Phi_i}v + v^\dagger \ket{\Psi}_n \frac{1}{E_\text{gs} - E_n} \bra{\Psi}_n v + v^\dagger \ket{\Phi}_j~.
+\end{aligned}\end{equation}
+Here, \(\ket{\Psi}_n\) are the eigenstates of the two site problem, with eigenvalue \(E_n\).
+The total scattering process can be described as \(H_X\) acting on \(\ket{\Phi}_j\) to excite to \(\ket{\Psi}_n\), and then a subsequent \(H_X\) acting on \(\ket{\Psi}_n\) to decay back to \(\ket{\Phi}_j\) and into the ground state manifold.
+Since \(\ket{\Phi}_{i,j}\) are eigenstates of the two site Hamiltonian, they are all eigenstates of the total number operator \(\hat n_{d0} = \sum_\sigma \left(\hat n_{d\sigma} + \hat n_{0\sigma}\right) \) for the two site model, with eigenvalue \(2\).
+Since we are to finally return to the ground state manifold, only those processes in \(H_X^2\) are allowed that conserve \(\hat n_{d0}\).
+These processes are \(v, v^\dagger\) and \(v^\dagger,v\).
+This also means that the total number of particles on site 1 will remain constant in the process, and we wil have \(\ket{\Phi}_i = \ket{\Phi}_j\).
+\begin{equation}\begin{aligned}
+	\Delta H = \sum_{i}\ket{\Phi}_i \bra{\Phi_i} \frac{1}{E_\text{gs} - E_n} \left(\bra{\Phi_i}v^\dagger \ket{\Psi}_n \bra{\Psi}_n v \ket{\Phi}_i + \bra{\Phi_i} v \ket{\Psi}_n \bra{\Psi}_n v^\dagger \ket{\Phi}_i\right) ~.
+\end{aligned}\end{equation}
+If we define the matrix element \(v_{ni} \equiv \bra{\Psi}_n v \ket{\Phi}_i\) of \(v\) and the excitation energy \(\delta E_{n} = E_n - E_\text{gs}\), we can write the renormalisation as
+\begin{equation}\begin{aligned}
+	\Delta H = \sum_{i,n}\frac{|v_{ni}|^2 + |v_{in}|^2}{-\delta E_{n}} \ket{\Phi}_i \bra{\Phi_i}~.
+\end{aligned}\end{equation}
+
+We now look at each \(\ket{\Phi_i}\) separately. For \(\ket{\Phi_i} = \ket{\Phi}_0 = \ket{\Psi}_1 \otimes \ket{0,0}\), we can write
+\begin{equation}\begin{aligned}
+	v^\dagger \ket{\Phi}_i = 0, ~ v \ket{\Phi}_i = \frac{t}{\sqrt 2}\sum_\sigma \overline\sigma\left({c_s^-} \ket{\sigma, 0} + {c_c^-} \ket{0, \sigma}\right) \ket{\overline\sigma}
+\end{aligned}\end{equation}
+The first relation gives \(v_{in} = \bra{\Phi}_i v \ket{\Psi}_n = \left(\bra{\Psi}_n v^\dagger \ket{\Phi}_i\right)^* = 0\).
+The set of states that give non-zero \(v^\dagger_{in}\) are specific elements of the set of eigenstates that have a total of either 1 or 3 electrons on the impurity and zeroth sites:
+\begin{equation}\begin{aligned}
+	\ket{\Psi}_n = \ket{\Psi}_{\pm,\sigma}^{s, p} = -\sqrt 2\left(a_{1,\pm}\ket{\sigma,p} + a_{2,\pm} \ket{p,\sigma}\right)\otimes\ket{s},~~ \sigma = \uparrow,\downarrow, ~~ E^{s,p}_{\pm, \sigma} = -\frac{U}{4} \pm \frac{1}{2}\Delta~;
+\end{aligned}\end{equation}
+here, \(s\) is a string from the set \(\left\{0, \uparrow, \downarrow, 2\right\} \) and represents the configuration of the first site \(\ket{s}\) in direct product with the impurity and zeroth site entangled composite state, and \(p\) is either \(2\) or 0 such that \(p+1 (= 1\text{ or }3)\) represents the total number of electrons on the impurity and zeroth sites.
+For \(\ket{\Phi}_0\), only \(s=\overline\sigma\) and \(p=0\) give non-zero inner product.
+The coefficients are defined as \(a_{1,\pm}=\frac{4V}{\sqrt 2 \mathcal{N}_\pm}, a_{2,\pm}=\frac{U \pm 2\Delta}{\sqrt 2 \mathcal{N}_\pm}\).
+The inner product is
+\begin{equation}\begin{aligned}
+	\label{vni}
+	v_{\pm\sigma,i} = \braket{\Psi_{\pm,\sigma}^{\overline\sigma,0} | v | \Phi_i} = \sigma t \left[a_{1,\pm}{c_s^-} + a_{2,\pm} {c_c^-}\right]
+\end{aligned}\end{equation}
+\(\mathcal{N}_\pm = \sqrt{16V^2 + \left(U \pm 2\Delta\right)^2}\) is the normalisation factor and \(\Delta = \frac{1}{2}\sqrt{U^2 + 16V^2}\). The renormalisation for this value of \(i\) then becomes
+\begin{equation}\begin{aligned}
+	\label{eff_ham_0}
+	\left(\Delta H\right)_{i=0} = \ket{\Phi}_0 \bra{\Phi}_0 \sum_{n}\frac{|v_{ni}|^2}{-\delta E_{n}} = \ket{\Phi}_0 \bra{\Phi}_0 \sum_{\sigma,\pm}\frac{|v_{\pm\sigma,i}|^2}{-\delta E_{\pm}^\sigma} = -\ket{\Phi}_0 \bra{\Phi}_0 2t^2\sum_{\pm}\frac{\left[a_{1,\pm}{c_s^-} + a_{2,\pm} {c_c^-}\right]^2}{\delta E_{\pm}^\sigma}
+\end{aligned}\end{equation}
+where \(\delta E_{\pm}^\sigma = E^\sigma_{\pm} - E_\text{gs}\).
+
+For \(i=1\), we have \(\ket{\Phi}_1 = \ket{\Psi}_1 \otimes \ket{\uparrow}\). Carrying out a similar calculation above, we get
+\begin{gather}
+	v\ket{\Phi}_1 = t \frac{1}{\sqrt 2}\left({c_s^-}\ket{\uparrow, 0, 2} + {c_c^-}\ket{0, \uparrow, 2}\right), ~ ~ ~\ket{\psi}_n = \ket{\Psi}^{2,0}_{\pm,\uparrow}, ~ ~ ~ v_{ni} = -t\left({c_s^-} a_{1,\pm} + {c_c^-} a_{2,\pm}\right) \label{vvdag_i1}\\
+	v^\dagger\ket{\Phi}_1 = t \frac{1}{\sqrt 2}\left({c_s^-}\ket{\uparrow, 2, 0} - {c_c^-}\ket{2, \uparrow, 0}\right), ~ ~ ~\ket{\psi}_n = \ket{\Psi}^{0,2}_{\pm,\uparrow}, ~ ~ ~ v_{in} = -t\left({c_s^-} a_{1,\pm} - {c_c^-} a_{2,\pm}\right)\label{vvdag_i1_2}\\
+	\left(\Delta H\right)_{i=1} = -\ket{\Phi}_1 \bra{\Phi}_1 2t^2\sum_{\pm}\frac{a_{1,\pm}^2 {c_s^-}^2 + a_{2,\pm}^2 {c_c^-}^2}{\delta E_{\pm}^\sigma}
+\end{gather}
+
+The total Hamiltonian \(H_0^* + H_X\) is invariant under the transformations \(c^\dagger_\sigma \to c_\sigma, t \to -t\).
+Since the renormalisation only involves even powers of \(t\), we can conclude that the renormalisation for \(i=2\)  and \(i=3\) will be the same as that of \(i=1\) and \(i=0\) respectively.
+The total renormalisation at second order is
+\begin{equation}\begin{aligned}
+	\Delta H &= -\sum_{i=0}^3\ket{\Phi}_i \bra{\Phi}_i 2t^2\sum_{\pm}\frac{a_{1,\pm}^2 {c_s^-}^2 + a_{2,\pm}^2 {c_c^-}^2}{\delta E_{\pm}^\sigma} - \left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right)4t^2\sum_{\pm}\frac{a_{1,\pm} a_{2,\pm} {c_s^-} {c_c^-}}{\delta E_{\pm}^\sigma}\\
+		 &= -\sum_{i=0}^3\ket{\Phi}_i \bra{\Phi}_i t^2\sum_{\pm}\frac{1}{\mathcal{N}_\pm^2}\frac{\left(4V{c_s^-}\right)^2 + \left(U \pm 2\Delta\right)^2 {c_c^-}^2}{\delta E_{\pm}^\sigma} - \left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right)\sum_{\pm}\frac{t^2}{\mathcal{N}_\pm^2}\frac{8V {c_s^-} \left(U \pm 2\Delta\right) {c_c^-}}{\delta E_{\pm}^\sigma}
+\end{aligned}\end{equation}
+Since the \(\ket{\hat n_{1\sigma}, \hat n_{1\overline\sigma}}\) form a complete set, we have \(\sum_{i=0}^3\ket{\Phi}_i \bra{\Phi}_i = \ket{\Psi}_1 \bra{\Psi}_1\), and the first term becomes a constant.
+The second term is a local Fermi liquid term on the first site:
+\begin{equation}\begin{aligned}
+	\Delta H &= \ket{\Psi}_1 \bra{\Psi}_1\left[\mathrm{constant} - \left\{\hat n_{1 \uparrow}\hat n_{1 \downarrow} + \left(1 - \hat n_{1 \uparrow}\right) \left(1 - \hat n_{1 \downarrow}\right)\right\}\sum_{\pm}\frac{t^2}{\mathcal{N}_\pm^2}\frac{8V {c_s^-} \left(U \pm 2\Delta\right) {c_c^-}}{\delta E_{\pm}^\sigma}\right]\\
+		 &= \ket{\Psi}_1 \bra{\Psi}_1\left[\mathrm{constant} + \left(\hat n_{1 \uparrow} - \hat n_{1 \downarrow}\right)^2 \sum_{\pm}\frac{t^2}{\mathcal{N}_\pm^2}\frac{8V {c_s^-} \left(U \pm 2\Delta\right) {c_c^-}}{\delta E_{\pm}^\sigma}\right]\\
+\end{aligned}\end{equation}
+
+In the strong-coupling regime, we have \(J,V \gg U\), and we can then approximate:
+\begin{equation}\begin{aligned}
+	\delta E_{\pm}^\sigma \simeq \frac{3J}{8} + \sqrt{4V^2 - \left(\frac{3J}{8}\right)^2} \mp V, ~~U \pm 2\Delta \simeq \pm 4V, \text{ and }~~ \mathcal{N}_\pm^2 \simeq 32V^2
+\end{aligned}\end{equation}
+Substituting this gives
+\begin{equation}\begin{aligned}
+	\Delta H = \ket{\Psi}_1 \bra{\Psi}_1\left[\mathrm{constant} - \left(\hat n_{1 \uparrow} - \hat n_{1 \downarrow}\right)^2 \frac{2t^2V {c_s^-} {c_c^-}}{2\left(\frac{3J}{8}\right)^2 + 3V^2 + \frac{3J}{4}\sqrt{4V^2 + \left(\frac{3J}{8}\right)^2}}\right]\\
+\end{aligned}\end{equation}
+
+\subsection{Fourth order effective Hamiltonian}
+Using fourth order perturbation theory, we can write the effective Hamiltonian renormalisation at that order in the form
+\begin{equation}\begin{aligned}
+	\label{eff_ham_4}
+	\Delta H &= -\sum_{i}\ket{\Phi}_i\bra{\Phi}_i\left[\sum_{lmn}\frac{\braket{\Phi_i | H_X | \Psi_l}\braket{\Psi_l | H_X | \Psi_m}\braket{\Psi_m | H_X | \Psi_n}\braket{\Psi_n | H_X | \Phi_i}}{\delta E_l ~ \delta E_m ~ \delta E_n} + \Delta^{(2)}H \sum_{n} \frac{|\braket{\Psi_n | H_X | \Phi_i}|^2}{\left(\delta E_n\right)^2}\right]~,\\
+		 &= -\sum_{i}\ket{\Phi}_i\bra{\Phi}_i\left[\sum_{m}\frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 + \Delta^{(2)}H \sum_{n} \frac{1}{\left(\delta E_n\right)^2}\big\Vert\left(H_X\right)_{ni}\big\Vert^2\right]~.
+\end{aligned}\end{equation}
+We can have at most two successive \(v^\dagger\) or two successive \(v\) act on a particular state.
+Any more would lead to \(c^\dagger_\sigma \ket{\hat n_\sigma =2} = 0\).
+This limits the possible scattering processes (in the first term) to the following channels:
+\begin{equation}\begin{aligned}
+	a.~v v^\dagger v v^\dagger,~~b.~v^\dagger v v^\dagger v,~~c.~v v v^\dagger v^\dagger,~~d.~v^\dagger v^\dagger v v~.
+\end{aligned}\end{equation}
+
+We start with \(i=0\).
+Out of the four channels \(a\) through \(d\), only \(b\) and \(d\) survive.
+For \(i=0\), we already know the relevant \(\ket{\Psi}_n\) and hence the \(\left(H_X\right)_{ni} = v_{ni}\), from eq.~\eqref{vni}.
+\begin{equation}\begin{aligned}
+	v_{\pm\sigma,i} = \braket{\Psi_{\pm,\sigma}^{\overline\sigma,0} | v | \Phi_i} = \sigma t \left[a_{1,\pm}{c_s^-} + a_{2,\pm} {c_c^-}\right] = \sigma t \mathcal{S}^-_\pm
+\end{aligned}\end{equation}
+where we have defined the sum and difference \(\mathcal{S}^\pm_\pm = a_{1,\pm}{c_s^\pm} + a_{2,\pm} {c_c^\pm}, ~ ~ \mathcal{D}^\pm_\pm = a_{1,\pm}{c_s^\pm} - a_{2,\pm} {c_c^\pm}\).
+For channel \(b\), we then proceed as follows:
+\begin{gather}
+	\ket{\Psi}_{\pm,\sigma}^{\overline\sigma, 0} = -\sqrt 2\left(a_{1,\pm}\ket{\sigma,0} + a_{2,\pm} \ket{0,\sigma}\right)\otimes\ket{\overline\sigma}\\
+	v^\dagger\ket{\Psi}_n = v^\dagger\ket{\Psi}^{\overline\sigma,0}_{\pm,\sigma} = \sqrt 2 t \left(a_{1,\pm}\ket{\sigma,\overline\sigma} + a_{2,\pm} \ket{0,\sigma\overline\sigma}\right)\otimes\ket{0}\\
+	\ket{\Psi}_m = \begin{cases}
+	\frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow})\right)\otimes\ket{0} \\
+	\frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2})\right)\otimes\ket{0}\\ 
+	\left[ \frac{c^+_s}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) +  \frac{c^+_c}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right] \otimes\ket{0}
+	\end{cases}
+	\implies \left(H_X\right)_{m,\pm\sigma} = \begin{cases}
+		t a_{1\pm}\\
+		\overline\sigma t a_{2\pm}\\
+		\sigma t \left(a_{1\pm} {c_s^+} + a_{2\pm}{c_c^+}\right) = \sigma t \mathcal{S}^+_\pm
+	\end{cases}\label{psi_m}\\
+	 \frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 = \begin{cases}
+	 \frac{1}{\delta E_\mathrm{ST}}\left(\sum_{\sigma,\pm}\frac{t^2}{\delta E_\pm}\sigma a_{1\pm}\mathcal{S}^-_\pm\right)^2 = 0\\
+	 \frac{1}{\delta E_\mathrm{CS}}\left(\sum_{\pm,\sigma} \frac{t^2}{\delta E_\pm}a_{2\pm}\mathcal{S}^-_\pm\right)^2 =  \frac{4t^4}{\delta E_\mathrm{CS}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{2\pm}\mathcal{S}^-_\pm\right)^2\\
+	 \frac{1}{\delta E_\mathrm{2}}\left(-\sum_{\pm,\sigma}\frac{t^2}{\delta E_\pm}\mathcal{S}^+_\pm\mathcal{S}^-_\pm\right)^2 = \frac{4t^4}{\delta E_\mathrm{2}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}\mathcal{S}^+_\pm\mathcal{S}^-_\pm\right)^2
+	\end{cases}
+\end{gather}
+\(E_\mathrm{ST}, E_\mathrm{CS}\) and \(E_2\) are the energies of the spin triplet zero, charge singlet and spin singlet+charge triplet excited states of the set \(\ket{\Psi}_m\) in eq.~\eqref{psi_m}.
+
+We now turn to channel \(d\):
+\begin{gather}
+	v\ket{\Psi}_n = v\ket{\Psi}^{\overline\sigma,0}_{\pm,\sigma} = \sqrt 2 t \sigma a_{2\pm} \ket{0,0}\otimes\ket{2},~ ~ ~\ket{\Psi}_m = \ket{0,0,2}, ~ ~ ~ \left(H_X\right)_{m,\pm\sigma} = \sqrt 2 t \sigma a_{2\pm}\\
+\frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 = \frac{8t^4}{\delta E_{00}} \left(\sum_\pm \frac{1}{\delta E_\pm}a_{2\pm}\mathcal{S}^-_\pm\right)^2
+\end{gather}
+\(E_{00}\) is the energy of the state \(\ket{0,0,2}\).
+
+Having accounted for both channels, we will calculate the second part of the effective Hamiltonian in eq.~\eqref{eff_ham_4}, the part involving \(\Delta^{(2)} H\).
+We already know, from eq.~\eqref{eff_ham_0}, that
+\begin{equation}\begin{aligned}
+	\Delta^{(2)} H_{i=0} = -2t^2\sum_\pm \frac{1}{\delta E_\pm}\left(\mathcal{S}^-_\pm\right)^2
+\end{aligned}\end{equation}
+Also, from the expression of \(v_{\pm\sigma,i}\), we get
+\begin{equation}\begin{aligned}
+	\sum_{n} \frac{1}{\left(\delta E_n\right)^2}\big\Vert\left(H_X\right)_{ni}\big\Vert^2 =	\sum_{\pm} \frac{2t^2}{\left(\delta E_\pm\right)^2}\left(\mathcal{S}^-_\pm\right)^2
+\end{aligned}\end{equation}
+Combining it all, the total renormalisation in \(i=0\) is
+\begin{equation}\begin{aligned}
+	- \ket{\Phi}_0 \bra{\Phi}_0 4t^4\left[ \left(\frac{1}{\delta E_\mathrm{CS}} + \frac{2}{\delta E_{00}}\right)  \left(\sum_{\pm}\frac{a_{2\pm}\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \frac{1}{\delta E_\mathrm{2}}\left(\sum_{\pm}\frac{\mathcal{S}^+_\pm\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 - \sum_\pm \frac{\left(\mathcal{S}^-_\pm\right)^2}{\delta E_\pm}\sum_{\pm} \left(\frac{\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2\right]\\
+\end{aligned}\end{equation}
+
+We now come to \(i=1\): \(\ket{\Phi}_1 = \ket{\Psi}_1 \otimes \ket{\uparrow}\).
+Channels \(a\) and \(b\) are non-zero here.
+We start with channel \(b: v^\dagger v v^\dagger v\).
+We already know, from eq.~\eqref{vvdag_i1}, that
+\begin{gather}
+v\ket{\Phi}_1 = t \frac{1}{\sqrt 2}\left({c_s^-}\ket{\uparrow, 0, 2} + {c_c^-}\ket{0, \uparrow, 2}\right), ~ ~ ~ \ket{\psi}_n = \ket{\Psi}^{2,0}_{\pm,\uparrow} = -\sqrt 2\left(a_{1,\pm}\ket{\uparrow,0} + a_{2,\pm} \ket{0,\uparrow}\right)\otimes\ket{2}, ~ ~ ~ \left(H_X\right)_{ni} = -t \mathcal{S}^-_\pm
+\end{gather}
+Moving forward:
+\begin{gather}
+v^\dagger \ket{\Psi}_n = \sqrt 2 t \left(a_{1,\pm}\ket{\uparrow,\uparrow}\otimes\ket{\downarrow} - a_{1,\pm}\ket{\uparrow,\downarrow}\otimes\ket{\uparrow} - a_{2,\pm} \ket{0,2}\otimes\ket{\uparrow}\right)\\
+	\ket{\Psi}_m = \begin{cases}
+	\frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow})\right)\otimes\ket{\uparrow} \\
+	\frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2})\right)\otimes\ket{\uparrow}\\ 
+	\left[ \frac{c^+_s}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) +  \frac{c^+_c}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right] \otimes\ket{\uparrow}\\
+	\ket{\uparrow,\uparrow}\otimes\ket{\downarrow}
+	\end{cases}
+	\implies \left(H_X\right)_{m,\pm}\left(H_X\right)_{\pm,i} = \begin{cases}
+		t^2 a_{1\pm} \mathcal{S}^-_\pm\\
+		-t^2 a_{2\pm}\mathcal{S}^-_\pm\\
+		t^2 \mathcal{S}^+_\pm\mathcal{S}^-_\pm\\
+		-\sqrt 2 t^2 a_{1\pm}\mathcal{S}^-_\pm
+	\end{cases}\\
+	\frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 = \begin{cases}
+	 \frac{t^4}{\delta E_\mathrm{ST}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{1\pm}\mathcal{S}^-_\pm\right)^2 \\
+	 \frac{t^4}{\delta E_\mathrm{CS}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{2\pm}\mathcal{S}^-_\pm\right)^2\\
+	 \frac{t^4}{\delta E_\mathrm{2}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}\mathcal{S}^+_\pm\mathcal{S}^-_\pm\right)^2\\
+	 \frac{2 t^4}{\delta E_\mathrm{\uparrow \uparrow}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{1\pm}\mathcal{S}^-_\pm\right)^2\\
+	\end{cases}
+\end{gather}
+\(E_{\uparrow \uparrow}\) is the energy of the upwards polarised state \(\ket{\uparrow,\uparrow}\otimes\ket{\downarrow}\).
+
+Next is channel \(a : v v^\dagger v v^\dagger\). Using eq.~\eqref{vvdag_i1_2} and following the same steps as above, we get:
+\begin{gather}
+	v^\dagger\ket{\Phi}_1 = t \frac{1}{\sqrt 2}\left({c_s^-}\ket{\uparrow, 2, 0} - {c_c^-}\ket{2, \uparrow, 0}\right), ~ ~ ~\ket{\Psi}_n = \ket{\Psi}^{0,2}_{\pm,\uparrow} = -\sqrt 2\left(a_{1,\pm}\ket{\uparrow,2} + a_{2,\pm} \ket{2,\uparrow}\right)\otimes\ket{0}, ~ ~ ~ \left(H_X\right)_{ni} = -t \mathcal{D}^-_\pm\\
+	v \ket{\Psi}_n = \sqrt 2 t\left(a_{1,\pm}\ket{\uparrow,\uparrow}\otimes\ket{\downarrow} - a_{1,\pm}\ket{\uparrow,\downarrow}\otimes\ket{\uparrow} + a_{2,\pm} \ket{2,0}\otimes\ket{\uparrow}\right)\\
+		\ket{\Psi}_m = \begin{cases}
+		\frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow})\right)\otimes\ket{\uparrow} \\
+		\frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2})\right)\otimes\ket{\uparrow}\\ 
+		\left[ \frac{c^+_s}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) +  \frac{c^+_c}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right] \otimes\ket{\uparrow}\\
+		\ket{\uparrow,\uparrow}\otimes\ket{\downarrow}
+		\end{cases}
+		\implies \left(H_X\right)_{m,\pm}\left(H_X\right)_{\pm,i} = \begin{cases}
+			t^2 a_{1\pm} \mathcal{D}^-_\pm\\
+			-t^2 a_{2\pm}\mathcal{D}^-_\pm\\
+			t^2 \mathcal{D}^+_\pm\mathcal{D}^-_\pm\\
+			-\sqrt 2 t^2 a_{1\pm}\mathcal{D}^-_\pm
+		\end{cases}\\
+		\frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 = \begin{cases}
+		\frac{1}{\delta E_\mathrm{ST}}\left(\sum_{\pm}\frac{t^2}{\delta E_\pm}a_{1\pm}\mathcal{D}^-_\pm\right)^2 \\
+		\frac{t^4}{\delta E_\mathrm{CS}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{2\pm}\mathcal{D}^-_\pm\right)^2\\
+		\frac{t^4}{\delta E_\mathrm{2}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}\mathcal{D}^+_\pm\mathcal{D}^-_\pm\right)^2\\
+		\frac{2 t^4}{\delta E_\mathrm{\uparrow \uparrow}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{1\pm}\mathcal{D}^-_\pm\right)^2\\
+		\end{cases}
+\end{gather}
+
+For the final part, we again use \(\Delta^{(2)} H_{i=1} = -t^2\sum_\pm \frac{1}{\delta E_\pm} \left[\left(\mathcal{S}^-_\pm\right)^2 + \left(\mathcal{D}^-_\pm\right)^2\right]\).
+Also, since \(\left(H_X\right)_{ni} = \left(v + v^\dagger\right)_{ni}\), we have
+\begin{equation}\begin{aligned}
+\sum_{n} \frac{1}{\left(\delta E_n\right)^2}\big\Vert\left(H_X\right)_{ni}\big\Vert^2 =	t^2\sum_{\pm} \left[\left(\frac{\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \left(\frac{\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right]
+\end{aligned}\end{equation}
+
+Combining all the terms, we get
+\begin{equation}\begin{aligned}
+	- \ket{\Phi}_1 \bra{\Phi}_1 4t^4\left[\left(\frac{1}{\delta E_\mathrm{ST}} + \frac{2}{\delta E_{\uparrow \uparrow}}\right) \left\{\left(\frac{1}{2}\sum_{\pm}\frac{a_{1\pm}\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \left(\frac{1}{2}\sum_{\pm}\frac{a_{1\pm}\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right\} + \frac{1}{\delta E_\mathrm{CS}} \left\{\left(\frac{1}{2}\sum_{\pm}\frac{a_{2\pm}\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2  \right.
+\right.\\
+	+ \left.
+\left.
+\left(\frac{1}{2}\sum_{\pm}\frac{a_{2\pm}\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right\} + \frac{1}{\delta E_\mathrm{2}}\left\{\left(\frac{1}{2}\sum_{\pm}\frac{\mathcal{S}^+_\pm\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \left(\frac{1}{2}\sum_{\pm}\frac{\mathcal{D}^+_\pm\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right\} \right.
+\\
+- \left.\sum_\pm \frac{1}{\delta E_\pm} \frac{1}{2}\left\{\left(\mathcal{S}^-_\pm\right)^2 + \left(\mathcal{D}^-_\pm\right)^2\right\}\sum_\pm \frac{1}{2}\left\{\left(\frac{\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \left(\frac{\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right\}\right]\\
+\end{aligned}\end{equation}
+If we define some quantities: \(F_{(1,2)} = \sum_{\pm}\frac{a_{(1,2)\pm}\mathcal{S}^-_\pm}{\delta E_\pm}, G_{(1,2)} = \sum_{\pm}\frac{a_{(1,2)\pm}\mathcal{D}^-_\pm}{\delta E_\pm}, P = \sum_{\pm}\frac{\mathcal{S}^+_\pm\mathcal{S}^-_\pm}{\delta E_\pm}, Q = \sum_{\pm}\frac{\mathcal{D}^+_\pm\mathcal{D}^-_\pm}{\delta E_\pm}, X_n = \sum_\pm \frac{\left(\mathcal{S}_\pm^-\right)^2}{\left(\delta E_\pm\right)^n}, Y_n = \sum_\pm \frac{\left(\mathcal{D}_\pm^-\right)^2}{\left(\delta E_\pm\right)^n}\), the total renormalisation from second and fourth order can be written as
+\begin{gather}
+	-\left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right) 4t^4 \left[\frac{1}{2t^2}X_1 + \left(\frac{1}{\delta E_\mathrm{CS}} + \frac{2}{\delta E_{00}}\right) F_{2}^2 + \frac{1}{\delta E_\mathrm{2}}P^2 - X_1 X_2\right]\nonumber\\
+	- \left(\ket{\Phi}_1 \bra{\Phi}_1 + \ket{\Phi}_2 \bra{\Phi}_2\right) t^4\left[\frac{1}{t^2}\left(X_1 + Y_1\right) + \left(\frac{1}{\delta E_\mathrm{ST}} + \frac{2}{\delta E_{\uparrow \uparrow}}\right) \left(F_1^2 + G_1^2\right) + \frac{1}{\delta E_\mathrm{CS}} \left(F_2^2 + G_2^2\right)\right.\nonumber\\
+\left. + \frac{1}{\delta E_\mathrm{2}} \left(P^2 + Q^2\right) - \left(X_1 + Y_1\right) \left(X_2 + Y_2\right)\right]
+\end{gather}
+The excitation energies are given by
+\begin{equation}
+	\delta E_\mathrm{CS} = \delta E_{00} = \frac{3J}{8} + \frac{U}{4} + \alpha, ~ ~ \delta E_{\uparrow \uparrow} = \delta E_\mathrm{ST}  = -\frac{U}{4} + \frac{5J}{8} + \alpha, ~ ~ \delta E_2 = 2\alpha, ~ ~ \delta E_\pm = \frac{3J}{8} + \alpha \pm \frac{1}{2}\Delta, ~ ~ \alpha \equiv \sqrt{V^2 \gamma^2 + 4V^2}
+\end{equation}
+where \(V\gamma = \frac{3J}{8} + \frac{U}{4}\) and \(\Delta = \sqrt{\frac{U^2}{4} + 4V^2}\). The effective Hamiltonian can be expressed in the general form
+\begin{equation}
+	H_\text{eff} = \ket{\Psi}_1\bra{\Psi}_1\otimes \left[\text{constant} + \alpha_\text{spin} \mathcal{\hat{P}}_\text{spin} + \alpha_\text{charge} \mathcal{\hat{P}}_\text{charge}\right] 
+\end{equation}
+\(\mathcal{\hat  P}_\text{charge}\) and \(\mathcal{\hat P}_\text{spin}\) are projection operators for, respectively, the charge \((\hat n_1 \neq 1)\) and spin \(\left(\hat n_1=1\right) \) sectors of the first site.
+Since \(\mathcal{\hat P}_\text{charge} + \mathcal{\hat P}_\text{spin} = 1\), we can eliminate one of the terms and rewrite the effective Hamiltonian in the simpler form
+\begin{equation}\begin{aligned}
+	H_\text{eff} = \ket{\Psi}_1\bra{\Psi}_1\otimes \left[\text{constant} + \mathcal{F} \mathcal{\hat P}_\text{charge}\right] 
+\end{aligned}\end{equation}
+where \(\mathcal{F} \equiv \alpha_\text{charge} - \alpha_\text{spin}\) is the net energy of the charge sector above the spin sector.
+
+We will now look at the extreme strong-coupling regime \(J \gg V \gg U,t\). There, all the expressions simplify:
+\begin{gather}
+	V\gamma \simeq \frac{3J}{8},~ ~ \Delta \simeq 2V,~ ~ \alpha \simeq \frac{3J}{8}, ~ ~ c_s^+ = -c_c^- \simeq 0, ~ ~ c_s^- = c_c^+ \simeq 1, ~ ~ \mathcal{N}_\pm \simeq 4\sqrt 2 V, ~ ~ a_{1,\pm} \simeq \frac{1}{2}, ~ ~ a_{2,\pm} \simeq \pm \frac{1}{2}~,\nonumber\\
+	\delta E_\pm = \delta E_\mathrm{CS} = \delta E_{00} = \delta E_2 \simeq \frac{3J}{4}, ~ ~ \delta E_\mathrm{ST} = \delta E_{\uparrow \uparrow} \simeq J, ~ ~ \mathcal{S}^-_\pm = \mathcal{D}^-_\pm \simeq \frac{1}{2}, ~ ~ \mathcal{S}^+_\pm = -\mathcal{D}^+_\pm \simeq \pm \frac{1}{2},~\nonumber\\
+	F_1 = G_1 \simeq \frac{2}{3J}, ~ ~ F_2 = G_2 \simeq 0, ~ ~ P = Q \simeq 0,~ ~ X_1 = Y_1 \simeq \frac{2}{3J}, ~ ~ X_2 = Y_2 \simeq \frac{8}{9J^2}
+\end{gather}
+The effective Hamiltonian becomes
+\begin{equation}\begin{aligned}
+	&-\left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right) \frac{4t^2}{3J}\left[1 - \frac{16 t^2}{9 J^3}\right] - \left(\ket{\Phi}_1 \bra{\Phi}_1 + \ket{\Phi}_2 \bra{\Phi}_2\right) \frac{4t^2}{3J}\left[1 + \frac{2t^2}{9 J^2} \right]\\
+	=&-\frac{4t^2}{3J}\sum_i \ket{\Phi}_i \bra{\Phi}_i +  \left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right) \frac{64 t^4}{27 J^3} - \left(\ket{\Phi}_1 \bra{\Phi}_1 + \ket{\Phi}_2 \bra{\Phi}_2\right) \frac{8t^4}{27 J^3}\\
+	=& \ket{\Psi}_1 \bra{\Psi}_1 \left[\text{constant} + \frac{64 t^4}{27 J^3} \mathcal{P}_\text{charge}  - \frac{8t^4}{27 J^3}\mathcal{P}_\text{spin}\right] 
+\end{aligned}\end{equation}
+\(\mathcal{P}_\text{spin}\) and \(\mathcal{P}_\text{charge}\) project, respectively,  onto the spin and charge sectors of the first site.
+The fact that the charge sector comes with a positive factor means that the holon-doublon states are repulsive, and this renormalisation of the states generates an effective particle-hole symmetric Fermi liquid interaction on the first site - also known as the local Fermi liquid (LFL)~\cite{nozieres1974fermi}.
+
+\section{Calculating the \(T=0\) Wilson ratio from low energy excitations}
+The total system now consists of two decoupled parts - the singlet composed of the impurity and the zeroth site, and the remaining lattice composed of N-1 sites with a tight-binding dispersion and a local interaction at the 1-th site.
+The effective Hamiltonian for the remaining lattice is
+\begin{equation}\begin{aligned}
+	\sum_{i=1\atop{\sigma}}^\infty t\left(c^\dagger_{i\sigma}c_{i+1 \sigma} + c^\dagger_{i+1 \sigma}c_{i\sigma}\right) + u \hat n_{1 \uparrow} \hat n_{1 \downarrow}
+\end{aligned}\end{equation}
+We have rewritten the holon term in terms of the spin and doublon operators.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.7\textwidth]{../figures/lattice_eff.png}
+	\caption{\textit{Left}: The nearest-neighbor hopping described by the effective Hamiltonian.
+The red circle is the impurity.
+The black cloud at the center demarcates the collection of electrons at the origin of the lattice (which couple to the impurity).
+The green circles represent lattice sites that are nearest to the origin.
+The blue circles represent next-nearest sites.
+\textit{Right}: After treating the hopping between origin and its nearest neighbors as perturbation, we get a system consisting of two decoupled parts: one part is the impurity+cloud singlet, the other part is the rest of the lattice sites.
+The effect of the hopping between the origin and the green sites is a repulsion term on the green sites.}
+\end{figure}
+We will now invoke the mean-field approximation in simplifying this term.
+We will be dealing with thermodynamic quantities soon, so the operators will be replaced by their thermodynamic values, that is, the values that minimize the free energy functional.
+\begin{equation}\begin{aligned}
+	\hat n_{1 \uparrow} \hat n_{1 \downarrow} \to \langle \hat n_{1 \uparrow} \hat n_{1 \downarrow}\rangle = \langle  \delta n_{1 \uparrow} \delta n_{1 \downarrow}\rangle + \langle  n_{1 \uparrow}\rangle\langle  n_{1 \downarrow}\rangle
+\end{aligned}\end{equation}
+where \(\delta n_{1\sigma} \equiv n_{1 \sigma} - \langle  n_{1\sigma} \rangle\) is the fluctuation of the particle number above the ground state.
+The mean-field approximation then involves dropping the first term which is a quadratic fluctuation - since we are interested in values of quantities at \( T \to 0\), this quadratic fluctuation is very small.
+The interaction we are left with is
+\begin{equation}\begin{aligned}
+	u\langle  n_{1 \uparrow}\rangle\langle  n_{1 \downarrow}\rangle = \sum_{kq\sigma}f_{kq}\langle  n_{k \sigma}\rangle\langle  n_{q \overline\sigma}\rangle
+\end{aligned}\end{equation}
+This interaction converts the problem to that of a Landau Fermi liquid, with the quasiparticle energy functional being given by
+\begin{equation}\begin{aligned}
+	\epsilon_{k\sigma} = \epsilon_k + \sum_{q}f_{kq}\left<\hat n_{q \overline\sigma}\right>
+\end{aligned}\end{equation}
+From the form of the quasiparticle energy functional, we can see that there is no spin-parallel term, so we can write
+\begin{equation}\begin{aligned}
+	\label{rel_landau}
+	f_{kk^\prime\sigma\sigma} = 0,  f_{kk^\prime\sigma\overline\sigma} = f_{kk^\prime}
+\end{aligned}\end{equation}
+We will now use this Fermi liquid form to extract the Wilson ratio. We will make use of the following definitions/results:
+\begin{gather}
+	dn_{k\sigma} = \frac{\partial{n}}{\partial{\epsilon_{k\sigma}}}\left( d\epsilon_{k\sigma} - d\mu \right) ~ ~ \left[\text{follows from differentiating FD distribution}\right] \\
+	C_V = \frac{\:\mathrm{d}\epsilon}{\:\mathrm{d}T}, ~ ~ \chi^{s,c} = \frac{\:\mathrm{d}}{\:\mathrm{d}(B, \mu)}\left(n_\uparrow \mp n_\downarrow\right), ~ ~ 2f_0^{s,a} = \sum_k\left(f_{kk^\prime \uparrow \uparrow} \pm f_{kk^\prime \uparrow \downarrow}\right), ~ ~ F_0^{s,a} = \rho(0) f_0^{s,a}
+\end{gather}
+\subsection{Low-\(T\) Specific heat}
+\begin{equation}\begin{aligned}
+	C &= \frac{\:\mathrm{d}}{\:\mathrm{d}T}\sum_{k\sigma}\epsilon_{k\sigma}n_{k\sigma} \\
+	    &\approx \sum_{k\sigma}\epsilon^0_{k\sigma} \frac{\:\mathrm{d}n_{k\sigma}}{\:\mathrm{d}T} && \left[\text{no quasiparticles at ground state}\right] \\
+	    &\approx \sum_{k\sigma}\epsilon^0_{k\sigma} \frac{\:\mathrm{d}n_{k\sigma}}{\:\mathrm{d}T} && \left[\text{same expression as Fermi gas but with modified distribution function}\right] \\
+	    &= \rho(0) T
+\end{aligned}\end{equation}
+where \(\rho\) is the total quasiparticle DOS with contributions from conduction bath and impurity.
+\begin{equation}\begin{aligned}
+	\rho \sim \text{Im }\text{Trace}\left[G\right] = \text{Im}\sum_{d\sigma}G_{dd}^\sigma + \text{Im}\sum_{k\sigma}G_{kk}^\sigma = \rho_0 + \rho_\text{imp}
+\end{aligned}\end{equation}
+which gives
+\begin{equation}\begin{aligned}
+	C_{imp} \equiv C - C_0 = \rho_{imp}(0)T
+\end{aligned}\end{equation}
+
+\subsection{Low-\(T\) Charge Susceptibility}
+\begin{equation}\begin{aligned}
+	\chi^c &= \frac{\:\mathrm{d}N}{\:\mathrm{d}\mu}\\
+\end{aligned}\end{equation}
+Due to change in chemical potential, \(\delta\epsilon_{k\sigma}\) is isotropic and SU(2)-symmetric. Hence
+\begin{equation}\begin{aligned}
+	d\epsilon_{k\sigma} &= \sum_{k^\prime\sigma^\prime}f_{kk^\prime\sigma\sigma^\prime}d n_{k^\prime\sigma^\prime}\\
+			    &= d n\sum_{k^\prime}\left(f_{kk^\prime\uparrow \uparrow} + f_{kk^\prime \uparrow \downarrow}\right) && \left[dn = dn_{k^\prime \uparrow} = dn_{k \downarrow}\right] \\
+			    &= 2dn f_0^s
+\end{aligned}\end{equation}
+Therefore,
+\begin{equation}\begin{aligned}
+	dN &= \sum_{k\sigma}dn_{k\sigma} = \sum_{k\sigma}\frac{\partial{n}}{\partial{\epsilon_{k\sigma}}}\left( d\epsilon_{k\sigma} - d\mu \right) = \sum_{k\sigma}-\frac{1}{2}\rho\left(2dn f_0^s - d\mu \right) = -\rho(0) d N f_0^s + d\mu \rho(0) \\
+	   &\approx d\mu \rho(0) - \rho(0) f_0^s d\mu \rho(0) \left[\text{substitute \(dN\) back into itself}\right] \\
+	\implies \frac{\:\mathrm{d}N}{\:\mathrm{d}\mu} &= \rho(0)\left( 1 - \rho(0)f_0^s \right) \implies \chi^c_{imp} = \rho(0)_{imp} - \rho(0)f_0^s \\
+\end{aligned}\end{equation}
+At an intermediate state, we substituted \(dN\) back into itself and kept only the leading order term.
+This is justified because \(f_{kk^\prime}\) goes as \(\frac{1}{N J}\).
+At the fixed point and for a thermodynamically large system, both \(J\) and \(N\) are very large, so keeping only the leading order suffices.
+
+From a previous calculation, we know that the charge susceptibility at \(T=0\) is zero (eq.~\eqref{zero_chi_charge}), so we can write down the following relation:
+\begin{equation}\begin{aligned}
+	\label{fp_constraint}
+	f_0^s = \frac{\rho(0)_{imp}}{\rho(0)}
+\end{aligned}\end{equation}
+
+\subsection{Low-\(T\) Spin Susceptibility}
+\begin{equation}\begin{aligned}
+	\chi^s &= \frac{\:\mathrm{d}m}{\:\mathrm{d}\mu}\\
+\end{aligned}\end{equation}
+Due to change in magnetic field, change in \(\epsilon_{k\sigma}\) should be isotropic and SU(2)-\text{anti}symmetric. Hence
+\begin{equation}\begin{aligned}
+	d\epsilon_{k\sigma} &= -\frac{1}{2}dB \sigma + \sum_{k^\prime\sigma^\prime}f_{kk^\prime\sigma\sigma^\prime}d n_{k^\prime\sigma^\prime}\\
+			    &= -\frac{1}{2}dB \sigma + d n_{\sigma}\sum_{k^\prime}\left(f_{kk^\prime\uparrow \uparrow} - f_{kk^\prime \uparrow \downarrow}\right) && \left[dn_{k^\prime \uparrow} = -dn_{k \downarrow}\right] \\
+			    &= -\frac{1}{2}dB \sigma + 2dn_\sigma f_0^a
+\end{aligned}\end{equation}
+Since the total number remains constant, \(\mu=0\). Therefore,
+\begin{equation}\begin{aligned}
+	dm &= \sum_{k}\left(dn_{k \uparrow} - dn_{k \downarrow}\right) = -\frac{1}{2}\sum_{k}\rho\left( d\epsilon_{k \uparrow} - d\epsilon_{k \downarrow} \right) = -\frac{1}{2}\sum_{k}\rho\left(-dB + 2f_0^a \left(dn_{k \uparrow} - dn_{k \downarrow}\right)\right) \\
+	   &= dB\rho(0) - dm \rho(0)f_0^a \approx dB\rho(0) - \rho(0)f_0^aB\rho(0) ~ \left[\text{substitute \(dm\) back into itself}\right] \\
+	\implies \frac{\:\mathrm{d}m}{\:\mathrm{d}B} &= \rho(0)\left( 1 - \rho(0)f_0^a \right) \implies \chi^s_{imp} = \rho(0)_{imp} - \rho(0)f_0^a \\
+\end{aligned}\end{equation}
+
+\subsection{Wilson ratio}
+The Wilson ratio for the impurity is defined as
+\begin{equation}\begin{aligned}
+	R = \frac{\chi^s_{imp}}{\frac{C_{imp}}{T}}
+\end{aligned}\end{equation}
+From eq.~\eqref{rel_landau}, we have \(f_0^s = -f_0^a\), which, when combined with eq.~\eqref{fp_constraint}, gives
+\begin{equation}\begin{aligned}
+	\chi^s_{imp} &= 2\rho(0)_{imp}
+\end{aligned}\end{equation}
+The Wilson ratio becomes
+\begin{equation}\begin{aligned}
+	R = \frac{2\rho(0)_{imp}}{\rho(0)_{imp}} = 2
+\end{aligned}\end{equation}
+
+\section{Luttinger's and Friedel's sum rules}
+The subsequent discussions are for the first quadrant where \(U^* = 0\) and \(J^* > K^*\). At high temperatures, we see that the impurity susceptibility attains the value of
+\begin{equation}\begin{aligned}
+	\frac{1}{8k_B T}
+\end{aligned}\end{equation}
+which implies that the impurity behaves as a free orbital in this limit, having no coupling with the bath. We can write down the following effective Hamiltonian for such a limit:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{high-T} = \tilde \epsilon_d \hat n_d + \sum_{k\sigma} \epsilon_k\hat n_{k\sigma}
+\end{aligned}\end{equation}
+Since the impurity is decoupled from the bath, we can immediately write down the Hamiltonian just for the impurity:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{high-T, imp} = \tilde \epsilon_d \hat n_d
+\end{aligned}\end{equation}
+
+We consider the resonant-level model:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{res} = \sum_{k\sigma}\epsilon_k \hat n_{k\sigma} + \epsilon_d n_d + \sum_{k\sigma}\left(V_k c^\dagger_{k\sigma} c_{d\sigma} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+The total Green's function is 
+\begin{equation}\begin{aligned}
+	G(z) = \frac{1}{z - \mathcal{H}_\text{res}}
+\end{aligned}\end{equation}
+The impurity diagonal Green's function is
+\begin{equation}\begin{aligned}
+	G_{dd}(z) &= \frac{1}{z - \epsilon_d - \Sigma_d(z)}, &&	G_d(z) = G_{dd}\ket{d}\bra{d}
+\end{aligned}\end{equation}
+where \(\Sigma_d(z)\) is in general complex and is zero at the free orbital fixed point. The conduction electron Green's function is 
+\begin{equation}\begin{aligned}
+	&G_{kk}(z) = G_k^0(z) + \left[G_k^0(z)V_k\right]^2 G_{dd}(z), & G_c(z) \equiv \sum_k \ket{k}\bra{k}G_{kk}(z), && G_{c0}(z) \equiv \sum_k G_{kk}^0(z)\ket{k}\bra{k}
+\end{aligned}\end{equation}
+The total Green's function can be written as
+\begin{equation}\begin{aligned}
+	G(z) &= \left(\sum_{k}\ket{k}\bra{k} + \ket{d}\bra{d}\right) G \left(\sum_{k}\ket{k}\bra{k} + \ket{d}\bra{d}\right)\\
+	     &= \sum_{k} \ket{k}\bra{k}G_{kk}(z) + G_{dd}(z)\ket{d}\bra{d} + \text{off-diagonal terms}\\
+	     &= G_c(z) + G_{d}(z) + \text{off-diagonal terms}
+\end{aligned}\end{equation}
+The total number of electrons is given by
+\begin{equation}\begin{aligned}
+	N &= \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G(z) \right]\\
+	  &= \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_{d}(z) + G_c(z)\right]
+\end{aligned}\end{equation}
+The contour \(\Gamma\) counts all the singularities of \(\text{Tr} G(z)\), and thus encloses only the real axis of the complex plane (since \(G(z)\) comes from a Hermitian matrix \(\mathcal{H}_\text{res}\), all its singularities are real).
+At this point, we can use an identity:
+\begin{equation}\begin{aligned}
+	\text{Tr}\left[G_{d}(z)\right] &= \text{Tr}\left[ \frac{\ket{d}\bra{d}}{z - \epsilon_d - \Sigma_d(z)}\right] = \text{Tr}\left[ \frac{\ket{d}\bra{d}}{z - \epsilon_d - \Sigma_d(z)}\frac{\partial{\left(z - \epsilon_d\right)}}{\partial{z}} \right] = \text{Tr}\left[ \ket{d}\bra{d}G_{dd}\frac{\partial{\left\{G_{dd}^{-1}(z) + \Sigma_d(z)\right\}}}{\partial{z}} \right]\\
+				       &= \text{Tr}\left[ G_{d}(z)\frac{\partial{G_{d}^{-1}(z)}}{\partial{z}} \right] + \text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right] = \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}G_{d}^{-1}(z)\right] + \text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right]\\
+\end{aligned}\end{equation}
+In the last step, we converted the trace to a determinant using
+\begin{equation}\begin{aligned}
+	\text{Tr}\left[A \frac{\partial{A^{-1}}}{\partial{z}}\right] = \frac{\partial{}}{\partial{z}}\text{Tr}\ln A^{-1} =\frac{\partial{}}{\partial{z}}\sum_i \ln \lambda_i = \frac{\partial{}}{\partial{z}}\ln \prod_i \lambda_i = \frac{\partial{}}{\partial{z}}\ln \text{Det}A^{-1}
+\end{aligned}\end{equation}
+where \(\lambda_i\) are the eigenvalues of \(A^{-1}\). Substituting \(\text{Tr}\left[G_d(z)\right] \) into the total number of particles gives
+\begin{equation}\begin{aligned}
+	N  &= \oint \frac{dz}{2\pi i}n_F(z) \left[\frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{G^{-1}_d(z)\right\} + \text{Tr} \left( G_d(z) \frac{\partial{}}{\partial{z}}\Sigma_d(z) \right) + \text{Tr}G_c(z)\right]
+\end{aligned}\end{equation}
+The conduction electron part can also be simplified:
+\begin{equation}\begin{aligned}
+	\text{Tr}G_c(z) &= \text{Tr}\left[G_{c0}(z) + \sum_k \left\{G_k^0(z)V_k\right\}^2 G_{dd}(z)\ket{k}\bra{k}\right] =\text{Tr}\left[G_{c0}(z)\right] + \sum_k\left[G_k^0(z)V_k\right]^2 G_{dd}(z)\\
+\end{aligned}\end{equation}
+Since \(G_{c0}^{-1}(z) = z - \sum_k \epsilon_k \hat n_k\), we can write \(\text{Tr}\left[G_{c0}(z)\right] = \text{Tr}\left[G_{c0}(z) \frac{\partial{}}{\partial{z}}G_{c0}^{-1}\right]\) and hence
+\begin{equation}\begin{aligned}
+	\text{Tr}G_c(z) &=\frac{\partial{}}{\partial{z}}\left[\ln \text{Det}G_{c0}^{-1}(z)\right] + \sum_k\left[G_k^0(z)V_k\right]^2 G_{dd}(z)
+\end{aligned}\end{equation}
+Updating the total particles with this leads to
+\begin{equation}\begin{aligned}
+	N  = \oint \frac{dz}{2\pi i}n_F(z) \left[\frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{G^{-1}_d(z)\right\} + \frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{G^{-1}_{c0}(z)\right\} + \text{Tr} \left( G_d(z) \frac{\partial{}}{\partial{z}}\Sigma_d(z) \right) + \sum_k\left( V_k G_k^0 \right)^2 G_{dd}(z)\right]
+\end{aligned}\end{equation}
+For the resonant-level model, we have
+\begin{equation}\begin{aligned}
+	\Sigma_d = \sum_k V^2_k G^0_k = \sum_k \frac{V_k^2}{z - \epsilon_k}
+\end{aligned}\end{equation}
+such that
+\begin{equation}\begin{aligned}
+	\text{Tr} \left( G_d(z) \frac{\partial{}}{\partial{z}}\Sigma_d(z) \right) = -G_{dd}(z) \sum_k \left( V_k G_k^0 \right)^2
+\end{aligned}\end{equation}
+which allows us to write
+\begin{equation}\begin{aligned}
+	N  = \oint \frac{dz}{2\pi i}n_F(z) \left[\frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{G^{-1}_d(z)\right\} + \frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{G^{-1}_{c0}(z)\right\} \right]
+\end{aligned}\end{equation}
+At \(T=0\), \(n_F\) is defined as 1 below the FS, \(\frac{1}{2}\) at the FS and 0 above it.
+\begin{equation}\begin{aligned}
+	N  = \left[\oint_{\Gamma_<} + \frac{1}{2}\oint_{\Gamma_0}\right]\frac{dz}{2\pi i}\left[\frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{G^{-1}_d(z)\right\} + \frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{G^{-1}_{c0}(z)\right\} \right]
+\end{aligned}\end{equation}
+Following Seki and Yunoki, we can define a winding number for a Green's function \(G(z)\):
+\begin{equation}\begin{aligned}
+	n_{\text{Det} G^{-1}}(C) = \oint_{C} \frac{dz}{2\pi i} \frac{\partial{\ln\text{Det }G^{-1}(z)}}{\partial{z}} = \oint_{\text{Det} G^{-1}(C)} \frac{\mathrm{d}\; \text{Det }G^{-1}}{\text{Det }G^{-1}}
+\end{aligned}\end{equation}
+Since \(n_{\text{Det } G^{-1}(C)}\) counts the number of times the curve \(\text{Det } G^{-1}(C)\) winds around the origin, it is integer-valued and topological.
+Seki and Yunoki also show that the this number is given by
+\begin{equation}\begin{aligned}
+n_{\text{Det }G^{-1}(C)} = P_{\text{Det }G}(C) - Z_{\text{Det }G}(C)
+\end{aligned}\end{equation}
+where \(P_{f(z)}(C)\) is the number of poles of \(f(z)\) enclosed by the contour \(C\), and \(Z\) is the corresponding number of zeros.
+The total number of particles in the resonant level model can thus be written as
+\begin{equation}\begin{aligned}
+	N = P_{\text{Det }G_d}(\Gamma_<) - Z_{\text{Det }G_d}(\Gamma_<) + \frac{1}{2}\left[P_{\text{Det }G_d}(\Gamma_0) - Z_{\text{Det }G_d}(\Gamma_0)\right] + P_{\text{Det }G_{c0}}(\Gamma_<) - Z_{\text{Det }G_{c0}}(\Gamma_<) \\
+	+ \frac{1}{2}\left[P_{\text{Det }G_{c0}}(\Gamma_0) - Z_{\text{Det }G_{c0}}(\Gamma_0)\right]
+\end{aligned}\end{equation}
+The average number of particles can thus be expressed purely in terms of the number of poles and zeros of the impurity and the conduction electron Green's functions.
+As shown by Seki and Yunoki, the second line gives the Luttinger volume \(V_L\):
+\begin{equation}\begin{aligned}
+	\label{total_lutt}
+	N = P_{\text{Det }G_d}(\Gamma_<) - Z_{\text{Det }G_d}(\Gamma_<) + \frac{1}{2}\left[P_{\text{Det }G_d}(\Gamma_0) - Z_{\text{Det }G_d}(\Gamma_0)\right] + V_L
+\end{aligned}\end{equation}
+If we start from a non-interacting model (\(V_k = 0\)), we can write
+\begin{equation}\begin{aligned}
+	N = \mathcal{N}^0_{imp} + V_L^0
+\end{aligned}\end{equation}
+where \(\mathcal{N}^0_{imp}\) is simply the number of singularities of \(G_d\) on the real axis, for the non-interacting case.
+We now turn up the interaction \(V_k\), keeping the total number of particles conserved at \(N\).
+With a non-zero \(V_k\), the impurity self-energy can be written (assuming a constant density of states) as
+\begin{equation}\begin{aligned}
+	\Sigma_d(z) = \Sigma_d^\text{real}(z) - i \Delta
+\end{aligned}\end{equation}
+so that the impurity Greens function becomes
+\begin{equation}\begin{aligned}
+	G_d(z) = \frac{1}{z - \epsilon_d - \Sigma_d^\text{real}(z) + i \Delta}
+\end{aligned}\end{equation}
+We can see that the presence of an imaginary part lifts the pole of \(G_d(z)\) off the real axis, and since the contour \(\Gamma_0\) encloses only the real axis, this will count as a loss in the number of poles of \(G_d(z)\).
+Also, if we specialize to the case where the renormalized impurity site energy \(\epsilon_d^* = \epsilon_d + \Sigma_d^\text{real} = 0\), this loss will happen at the Fermi surface, and will hence be multiplied by a factor of half.
+We can therefore write
+\begin{equation}\begin{aligned}
+	N &= \mathcal{N}_{imp} + V_L = \mathcal{N}^0_{imp} - \frac{1}{2} + V_L \implies V_L &= V_L^0 + \frac{1}{2}
+\end{aligned}\end{equation}
+If we take into account the spin-degeneracy and redefine \(V_L\) to mean the Luttinger volume for both momentum and spin degrees of freedom, we get
+\begin{equation}\begin{aligned}
+	\label{luttinger_change}
+	V_L = V_L^0 + 1
+\end{aligned}\end{equation}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[scale=0.2]{../figures/luttinger_top_change.png}
+\end{figure}
+This is a specific case of the more general result for Kondo lattices obtained by Oshikawa using flux-insertion arguments in \cite{oshikawa2000topological}.
+One can now ask what happens to this result once we also incorporate the spin-exchange interaction \(J \vec{S_d}\cdot\vec{s}\); we can expect that it will complicate the self-energy of the impurity.
+It cannot, however, preclude the loss of the real pole, nor can it create a new singularity - to do so would require the self-energy to diverge, and we are working with finite systems here.
+This suggests that the eq.~\eqref{luttinger_change} would still hold.
+
+We have also not accounted for the RG flow from the local moment fixed point to the strong-coupling fixed point. The local moment fixed point is characterized by a decoupled quantum top:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{LM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow}
+\end{aligned}\end{equation}
+It can be shown that the single-particle Green's function for this effective Hamiltonian is similar to the one at the free-orbital fixed point.
+We will use the equation of motion technique to solve for the Green's function.
+The time-domain retarded Green's function is defined as
+\begin{equation}\begin{aligned}
+	G_{d\sigma}(t, t^\prime) = -i\theta(t-t^\prime) \left<\left\{ c_{d\sigma}(t), c^\dagger_{d\sigma}(t^\prime) \right\} \right>
+\end{aligned}\end{equation}
+Since the Hamiltonian is time-translation invariant, we can drop one of the instants:
+\begin{equation}\begin{aligned}
+	G_{d\sigma}(t, 0) = -i\theta(t) \left<\left\{ c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right>
+\end{aligned}\end{equation}
+The time derivative is
+\begin{equation}\begin{aligned}
+	\partial_t G_{d\sigma} &= -i \left[\partial_t \theta(t) \left<\left\{ c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right> + \theta(t) \partial_t \left<\left\{ c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right>\right] \\
+			       &= -i \left[\delta(t) \left<\left\{ c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right> + \theta(t) \left<\left\{ \partial_t c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right>\right] = -i \delta(t) -i\theta(t) \left<\left\{ \partial_t c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right>
+\end{aligned}\end{equation}
+From the Heisenberg equations of motion, we get
+\begin{equation}\begin{aligned}
+	i \partial_t c_{d\sigma}(t) = \left[c_{d\sigma}(t), \mathcal{H}_{LM}(t)\right] = \left[\epsilon_d + U \hat n_{d\overline\sigma}(t)\right]c_{d\sigma}(t)
+\end{aligned}\end{equation}
+Substituting this into the time-derivative gives
+\begin{equation}\begin{aligned}
+	\partial_t G_{d\sigma} &= -i \delta(t) -i \theta(t) \left<\left\{ -i\left[\epsilon_d + U \hat n_{d\overline\sigma}(t)\right]c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right> = -i \delta(t) - i\epsilon_d G_{d\sigma} - U \theta(t) \left<\hat n_{d\overline\sigma}(t)\left\{c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right>\\
+\end{aligned}\end{equation}
+We define another Greens function
+\begin{equation}\begin{aligned}
+	G^\prime = -i \theta(t) \left<\hat n_{d\overline\sigma}(t)\left\{c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right>
+\end{aligned}\end{equation}
+which satisfies the equation of motion
+\begin{equation}\begin{aligned}
+	\partial_t G^\prime = -i \delta(t) -i\theta(t) \left<\left\{\partial_t \hat n_{d\overline\sigma}(t)c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right> -i\theta(t) \left<\left\{\hat n_{d\overline\sigma}(t)\partial_t c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right>
+\end{aligned}\end{equation}
+The second term vanishes because \(\left[\hat n_{d\overline\sigma}, \mathcal{H}_{LM}\right] = 0\) and hence \(\partial_t \hat n_{d\overline\sigma} = 0\). Also,
+\begin{equation}\begin{aligned}
+	\hat n_{d\overline\sigma}(t)\partial_t c_{d\sigma}(t) = -i\hat n_{d\overline\sigma}(t)\left[\epsilon_d + U \hat n_{d\overline\sigma}(t)\right]c_{d\sigma}(t) = -i\left[\epsilon_d + U\right]\hat n_{d\overline\sigma}(t)c_{d\sigma}(t)
+\end{aligned}\end{equation}
+Therefore,
+\begin{equation}\begin{aligned}
+	\partial_t G^\prime = -i \delta(t) \left< \hat n_{d\overline\sigma}(0)\right>- \left[\epsilon_d + U\right]\theta(t) \left<\left\{\hat n_{d\overline\sigma}(t)c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right> = -i \delta(t) -i \left( \epsilon_d + U \right) G^\prime
+\end{aligned}\end{equation}
+Changing all quantities to frequency-domain:
+\begin{equation}\begin{aligned}
+	G^\prime(t) &= \int_{-\infty}^\infty d\omega e^{-i\omega t} G^\prime(\omega)\\
+	\partial_t G^\prime(t) &= -\int_{-\infty}^\infty d\omega i \omega e^{-i\omega t} G^\prime(\omega)\\
+	\delta(t) &= \int_{-\infty}^\infty d\omega e^{-i\omega t}
+\end{aligned}\end{equation}
+Substituting these forms in the equation and comparing the coefficients of \(e^{i\omega t}\) gives
+\begin{equation}\begin{aligned}
+	 \omega G^\prime(\omega) =  \left< \hat n_{d\overline\sigma}(0)\right> + \left( \epsilon_d + U \right) G^\prime(\omega)\implies G^\prime(\omega) = \frac{\left< \hat n_{d\overline\sigma}(0)\right>}{\omega - \epsilon_d - U}
+\end{aligned}\end{equation}
+The equation of motion \(G_{d\sigma}\) can now be solved
+\begin{equation}\begin{aligned}
+	\partial_t G_{d\sigma}(t) &= -i \delta(t) - i\epsilon_d G_{d\sigma}(t) - iU G^\prime_{d\sigma}(t) \implies \omega G_{d\sigma}(\omega) = 1 + \epsilon_d G_{d\sigma}(\omega) + U\frac{\left< \hat n_{d\overline\sigma}(0)\right>}{\omega - \epsilon_d - U}\\
+	\implies G_{d\sigma}(\omega) &= \frac{1}{\omega - \epsilon_d} + \frac{U\left< \hat n_{d\overline\sigma}(0)\right>}{\left( \omega - \epsilon_d \right) \left(\omega - \epsilon_d - U\right)}
+\end{aligned}\end{equation}
+For a particle-hole symmetric system, we can substitute \(\epsilon_d = -|\epsilon_d|\) and \(\epsilon_d + U = |\epsilon_d|\).
+\begin{equation}\begin{aligned}
+	G_{d\sigma}(\omega) &= \frac{1}{\omega + |\epsilon_d|} + \frac{U\left< \hat n_{d\overline\sigma}(0)\right>}{\left( \omega + |\epsilon_d| \right) \left(\omega - |\epsilon_d|\right)}
+\end{aligned}\end{equation}
+which reveals two poles at \(\pm |\epsilon_d|\), one above and one below the Fermi surface.
+Since the RHS of eq.~\eqref{total_lutt} counts the number of poles on or below the FS, we will still count one pole for \(G_{d\sigma}\).
+Thus, this Green's function is topological similar to the free-orbital one at \(T=0\).
+
+The scattering phase shift suffered by the conduction electrons at the Fermi surface, off the impurity, can be calculated from the impurity occupancy, using the Friedel sum rule.
+From the ground state wavefunction, we can calculate the average number of particles on the impurity:
+\begin{equation}\begin{aligned}
+	\left<n_d \right> = \bra{\Psi}_1\sum_\sigma \hat n_{d\sigma} \ket{\Psi}_1
+\end{aligned}\end{equation}
+\(\ket{\Psi}_1\) is the lower energy state in eq.~\eqref{gstate}. Performing the inner product gives
+\begin{equation}\begin{aligned}
+	\left<n_d \right> = \left( c_s^- \right)^2 + \left( c_c^- \right)^2 = 1
+\end{aligned}\end{equation}
+The phase shift is thus
+\begin{equation}\begin{aligned}
+	\frac{1}{\pi}\sum_\sigma \delta_\sigma(0) = \left<n_d \right> \implies \delta_\sigma(0) = \frac{\pi}{2}
+\end{aligned}\end{equation}
+There we used \(\delta_\uparrow = \delta_\downarrow\) because the model is SU(2)-symmetric. This line of arguments was first presented for the Kondo model in \cite{martin1982fermi}.
+
+The change in Luttinger's number also allows us to calculate the Wilson ratio of the system, from eq.~\eqref{wilson_luttinger}.
+\begin{equation}\begin{aligned}
+	R = 1 + \sin^2 \left( \frac{\pi}{2}\Delta N_L \right) = 1 + \sin^2 \frac{\pi}{2} = 2
+\end{aligned}\end{equation}
+\section{Reverse RG analysis}\label{rev_rg}
+The goal here is to chart the journey starting from the IR fixed point towards the UV regime, by following one particular wavefunction.
+We will start with a very simple IR ground state wavefunction, and then go back towards the UV ground state by applying the inverse unitary operator \(U^\dagger\):
+\begin{equation*}\begin{aligned}
+	U : \underbrace{\ket{1,2,...,N}}_\text{UV ground state} \rightarrow \ket{1,2,...,N-1}\ket{N} \rightarrow ... \rightarrow \underbrace{\ket{1,2,...,N^*}\ket{N^*+1}...\ket{N}}_\text{IR ground state}
+\end{aligned}\end{equation*}
+\begin{equation*}\begin{aligned}
+	U^\dagger : \underbrace{\ket{1,2,...,N^*}\ket{N^*+1}...\ket{N}}_\text{IR ground state} \rightarrow \ket{1,2,...,N^*+1}\ket{N^*+2}...\ket{N} \rightarrow ...
+\rightarrow\underbrace{\ket{1,,2,...,N}}_\text{UV ground state}
+\end{aligned}\end{equation*}
+The first process is the forward RG which we used to obtain the scaling equations.
+The second process is the reverse RG which we will undertake now.
+In general, we start with an IR wavefunction that consists a certain number of momentum states \(n_1\) still entangled with the impurity, and the remaining momentum states \(n_2\) disentangled from the impurity.
+The former are said to be part of the emergent Kondo cloud, while the latter are said to be part of the integrals of motion (IOMs) and appear in direct product with the cloud+impurity system in the ground state wavefunction.
+Each momentum state is tagged with two conduction bath levels, one above the Fermi surface and one below.
+These will be represented as \(k,\pm\).
+If we represent the emergent cloud momentum states as \(\left\{k_i\right\} \) and the IOM states as \(\left\{q_i\right\}\), the ground state wavefunction can be written as
+\begin{equation}\begin{aligned}
+	\ket{\Psi}_0 = \left(\otimes_{i=1}^{n_2}\ket{q_i,-,\uparrow}\ket{q_i,-,\downarrow}\right)\ket{\Phi}_\text{cloud}\left(\otimes_{i=1}^{n_2}\ket{q_i,+,\uparrow}\ket{q_i,+,\downarrow}\right)
+\end{aligned}\end{equation}
+Throughout, we have assumed that the IOMs below the Fermi surface are occupied while those above are unoccupied. This means:
+\begin{equation}\begin{aligned}
+	\ket{\Psi}_0 = \left(\otimes_{i=1}^{n_2}\ket{\hat n_{q_i,-,\uparrow}=1}\ket{\hat n_{q_i,-,\downarrow}=1}\right)\ket{\Phi}_\text{cloud}\left(\otimes_{i=1}^{n_2}\ket{\hat n_{q_i,+,\uparrow}=0}\ket{\hat n_{q_i,+,\downarrow}=0}\right)
+\end{aligned}\end{equation}
+\(\ket{\Phi}_\text{cloud}\) will be obtained by diagonalising a small system of \(n_1\) conduction bath \(k\) states.
+This completes the construction of the IR ground state \(\ket{\Psi}_0\).
+The algorithm of reverse RG then involves applying unitary transformations on this IR wavefunction; the unitary transformations will be the inverse of those that were applied during the forward RG algorithm.
+Since the forwards RG transformations decoupled \(k\) states and transformed them into the IOMS, the inverse transformations will take the momentum states in the IOMs and re-entangle them with the impurity+cloud system, one at a time.
+This is shown in fig.~\ref{rev-rg}.
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=0.4\textwidth]{../figures/reverse-rg.png}
+	\caption{We start with a Hamiltonian with an impurity site (red) coupled with two conduction electrons (dark green), with four other decoupled electrons (bright green).
+The dotted rectangle represents the emergent window \(\left( -\Lambda_j, \Lambda_j \right) \) at each step; the electrons inside that rectangle are still entangled with the impurity, while the ones inside have been decoupled.
+The next step of reverse RG involves applying the inverse transformation on the Hamiltonian, which will couple two more electrons from the IOMS (hence four dark green circles in the second step), leading to an enlargement of the emergent window.
+The unitary varies for each step, hence the notation \(U_j\).}
+	\label{rev-rg}
+\end{figure}
+
+The next step is to write down the unitaries that will take us from the IR ground state to the UV ground state.
+In the forward RG, we used the following unitary for decoupling the shell \(\epsilon_q\) and spin \(\beta\) is
+\begin{equation}\begin{aligned}
+	U_{q\beta} = \frac{1}{\sqrt 2}\left[1 + \eta_{0 \beta} + \eta_{1\beta}^\dagger\right]~.
+\end{aligned}\end{equation}
+Here, the subscripts \(0\) and \(1\) indicate it decouples an electron above and below the Fermi surface respectively. The inverse transformation for re-entangling \(q\beta\) is
+\begin{equation}\begin{aligned}
+	U^\dagger_{q\beta} = \frac{1}{\sqrt 2}\left[1 + \eta_{0 \beta}^\dagger + \eta_{1\beta}\right]~.
+\end{aligned}\end{equation}
+In the \(U>0\) regime, the \(\eta\)s are given by
+\begin{equation}\begin{aligned}
+	\eta_{0\beta}^\dagger = V \left[\frac{1}{d_0}\left( 1 - \hat n_{d\overline\beta} \right) + \frac{1}{d_1}\hat n_{d\overline\beta}  \right]c^\dagger_{q\beta}c_{d\beta} + \frac{1}{d_2}\frac{J}{2}\sum_{k} \left( S_d^z \beta c^\dagger_{q\beta}c_{k\beta} + c^\dagger_{d\overline\beta}c_{d\beta}c^\dagger_{q\beta}c_{k\overline\beta}\right) ~,\\
+	\eta_{1\beta} = V \left[\frac{1}{d_1}\left( 1 - \hat n_{d\overline\beta} \right) + \frac{1}{d_0}\hat n_{d\overline\beta}  \right]c^\dagger_{d\beta}c_{q\beta} + \frac{1}{d_2}\frac{J}{2}\sum_{k} \left( S_d^z \beta c^\dagger_{k\beta}c_{q\beta} + c^\dagger_{d\beta}c_{d\overline\beta}c^\dagger_{k\overline\beta}c_{q\beta}\right)~;
+\end{aligned}\end{equation}
+since \(K\) is irrelevant, we have set \(K=0\) here. The denominators have already been defined in eq.~\eqref{denominators}.
+\begin{equation}\begin{aligned}
+	d_0 = \omega - \frac{D}{2} - \frac{U}{2} + \frac{K}{4}, \quad d_1 = \omega - \frac{D}{2} + \frac{U}{2} + \frac{J}{4}, \quad d_2 = \omega - \frac{D}{2} + \frac{J}{4}, \quad d_3 = \omega - \frac{D}{2} + \frac{K}{4}
+\end{aligned}\end{equation}
+
+The wavefunction after reversing one step of the RG will thus be
+\begin{equation}\begin{aligned}
+	\ket{\Psi}_1 = U^\dagger_{q \uparrow}U^\dagger_{q \downarrow}\ket{\Psi}_0
+\end{aligned}\end{equation}
+Here, \(q\) is the first momentum state immediately outside the emergent cloud.
+Re-entangling further momentum states using their respective unitaries lead to the sequence of wavefunctions \(\ket{\Psi}_2, \ket{\Psi}_3\) and so on.
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=0.45\textwidth]{../figures/mut_I_ee.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/mut_I_ie.pdf}
+	\caption{\textit{Left}: Mutual information between two conduction electrons inside the cloud.
+\textit{Right}: Mutual information between a conduction electron inside the cloud and an impurity electron.
+Both the measures increase towards the strong-coupling fixed point, because of the distillation of the Kondo cloud brought about by the RG flow.}
+	\label{mutI}
+\end{figure}
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=0.45\textwidth]{../figures/corr_same.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/corr_opp.pdf}
+	\caption{Increase in the diagonal correlation functions between cloud electrons under RG flow towards the strong-coupling fixed point.
+This is consistent with the Fermi liquid pieces generated in the \(k-\)space effective Hamiltonian of the Kondo cloud.}
+\end{figure}
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=0.45\textwidth]{../figures/corr_od.pdf}
+	\caption{Growth of the off-diagonal correlation function between Kondo cloud electrons towards the strong-coupling fixed point.
+This is the direct cause of the screening of the impurity spin, and is a reflection of the off-diagonal two-particle scattering terms in the \(k-\)space effective Hamiltonian of the Kondo cloud.}
+\end{figure}
+
+The results of the reverse RG study are depicted in the following plots.
+We have used two types of quantities in the process - mutual information and correlation functions.
+The mutual information between two subsystems \(A\) and \(B\) in a wavefunction with many subsystems is defined as
+\begin{equation}\begin{aligned}
+	I(A: B) = S_A + S_B - S_{AB}
+\end{aligned}\end{equation}
+where \(S_{ij..q}\) is the von-Neumann entropy of the reduced density matrix obtained after tracing out all degrees of freedom except those in the subscript of \(S\).
+
+The mutual information between two electrons inside the entangled cloud increases as we go towards the IR fixed point.
+This can be understood in the following manner; as the wavefunction flows towards a smaller sized emergent cloud, the entanglement between those electrons gets distilled out.
+
+We have also computed some correlation functions.
+All of them increase towards the IR fixed point.
+The increase in the correlation function \(\left<\hat n_{k_1 \uparrow} \hat n_{k_2 \downarrow} \right>\) arises from the crystallization of the spin singlet at the fixed point.
+The increase in the correlation function \(\left<\hat n_{k \uparrow} \hat n_{k \downarrow} \right>\) arises from the charge triplet content of the wavefunction, showing the increase of the charge contribution on the momenta.
+The increase in the off-diagonal correlation function \(\left< c^\dagger_{k \uparrow}c_{k^\prime \downarrow}c^\dagger_{q \downarrow}c_{q^\prime \uparrow}\right>\) shows that the there is a large and non-trivial interaction between the electrons of the cloud that is being mediated by the impurity electron.
+This interaction is not of the Fermi liquid type, but instead was obtained in the effective Hamiltonian for the Kondo cloud.
+
+\chapter{Effect of minimal attractive correlation in the bath}
+
+\section{The modified hamiltonian}
+We will include a local particle-hole symmetric correlation of strength \(U_b\) on the origin of the lattice:
+\begin{equation}\begin{aligned}
+	\mathcal{H} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} + \epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
+\end{aligned}\end{equation}
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../figures/zeromode.pdf}
+	\caption{While we have studied the full model under renormalisation group, often we will turn to a simplified zero-bandwidth version of the model that is obtained by ignoring the kinetic energy part of the Hamiltonian.
+This zero-bandwidth model is effectively a two site model.}
+\end{figure}
+
+\section{RG Equations}
+The derivation of the RG equations are shown at the end. \(n_j\) is the number of \(k-\)states at the \(j^\text{th}\) isoenergetic shell. 
+\begin{gather}
+	\Delta U_b = 0, ~ ~\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\left(\frac{J^2}{d_2} - \frac{K^2}{d_3}\right),\\
+	\Delta V = -\frac{3n_j V}{8}\left[\left(J + 4U_b/3\right) \left(\frac{1}{d_2} + \frac{1}{d_1}\right) + \left(K + 4U_b/3\right)\left(\frac{1}{d_3} + \frac{1}{d_0}\right)\right],\\
+	\Delta J = -\frac{n_j J\left(J + 4U_b\right)}{d_2},~ ~\Delta K = -\frac{n_j K\left(K + 4U_b\right)}{d_3}
+\end{gather}
+
+The denominators are
+\begin{equation}\begin{aligned}
+	d_0 = \omega - \frac{D}{2} + \frac{U_b}{2} - \frac{U}{2} + \frac{K}{4}, \quad d_1 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{U}{2} + \frac{J}{4}, \quad d_2 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}, \quad d_3 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}
+\end{aligned}\end{equation}
+
+\paragraph{Important points regarding notation}
+\begin{itemize}
+	\item The labels \(U_0,J_0,V_0\) that may occur in the axes of the plots or anywhere else represent the bare values of the couplings \(U,J\) and \(V\). 
+	\item Throughout the results, the bare value of \(U_b\) is set to the negative of the bare value of \(U_0\): \(U_b = -U_0\).
+This means that whenever we vary \(U_0\) along the axis of a plot, we are simultaneous varying \(U_b\).
+\end{itemize}
+
+\section{Phase diagram}
+
+\begin{center}
+	\includegraphics[width=0.9\textwidth]{../figures/phase-map_D=1000.pdf}
+\end{center}
+
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+phase & RG flow & fixed point & GS & 2-site GS \\ 
+\hline
+blue & \(\Delta U <0, \Delta J,\Delta V>0\) & \(U^* \ll V^* \ll J^*\) & SS & \(\ket{SS}=\ket{\uparrow,\downarrow} - \ket{\downarrow, \uparrow}\)  \\ 
+green &  \(\Delta U < 0, \Delta J < 0,\Delta V>0\) & \(V^* < U^* \ll V^*\) & SS + CT-0 & \(c\ket{SS} + \sqrt{1-c^2}\ket{CT-0}\)  \\  
+red &  \(\Delta U > 0, \Delta J,\Delta V<0\) & \(U^* \gg 1,  V^* = J^* = 0\) & decoupled LM & \(\left\{\ket{\uparrow}, \ket{\downarrow} \right\} \otimes \left\{\ket{0}, \ket{2}\right\} \) \\
+yellow &  \(\Delta U, \Delta J,\Delta V < 0\) & \(U^* = V^* = J^* = 0\) & lattice & \(\left\{\ket{\uparrow}, \ket{\downarrow}, \ket{0}, \ket{2} \right\} \otimes \left\{\ket{0}, \ket{2}\right\}\) \\
+\hline
+\end{tabular}
+\end{center}
+
+\section{Overlap of ground state against spin singlet and charge triplet zero states}
+\begin{center}
+	\includegraphics[width=0.8\textwidth]{../figures/overlaps_gs_D=500,J=0.500.pdf}\\
+	\includegraphics[width=0.8\textwidth]{../figures/overlaps_gs_D=500,J=5.000.pdf}\\
+	\includegraphics[width=0.8\textwidth]{../figures/overlaps_gs_D=500,J=50.000.pdf}
+\end{center}
+
+\section{Spin and charge correlations in ground state}
+\begin{center}
+	\includegraphics[width=0.8\textwidth]{../figures/corrs_gs_D=500,J=0.500.pdf}\\
+	\includegraphics[width=0.8\textwidth]{../figures/corrs_gs_D=500,J=5.000.pdf}\\
+	\includegraphics[width=0.8\textwidth]{../figures/corrs_gs_D=500,J=50.000.pdf}
+\end{center}
+
+\section{\large Behaviour of \(\mathcal{F}\), the gap and the small parameter}
+These quantities are related to the local Fermi liquid of the Kondo strong-coupling fixed point and the perturbation theory associated with it.
+\(min(\delta E)\) is the gap in the spectrum of the two-site Hamiltonian; this which acts as the denominator for the perturbation theoretic calculations.
+\(t^2/\delta E\) is the small parameter for the expansion, \(t\) being the tight-binding hopping.
+\(\mathcal{F}\) is the strength of the local Fermi liquid \((\mathcal{F} \hat n_{1 \uparrow} \hat n_{1 \downarrow})\).
+\begin{center}
+	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+\end{center}
+
+\section{\large Behaviour of correlation within the Kondo cloud}
+\begin{center}
+	\includegraphics[width=0.24\textwidth]{../figures/corr-k-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.24\textwidth]{../figures/mi-dk-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.24\textwidth]{../figures/corr-k-diag-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.24\textwidth]{../figures/corr-k-od-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+\end{center}
+
+\section{\large Behaviour of mutual information between various real space members}
+\begin{center}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+\end{center}
+
+\section{\large Behaviour of impurity entanglement entropy and spin-spin correlations}
+
+\begin{center}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+
+	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+\end{center}
+
+\section{Behaviour of real-space correlations}
+\begin{center}
+	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+
+	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+\end{center}
+
+\section{Impurity spectral function}
+\begin{center}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.00.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=1.50.pdf}\\
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=1.76.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=4.00.pdf}\\
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=6.00.pdf}
+\end{center}
+\chapter{From the auxiliary model to the bulk}
 \section{Solution of the Hubbard dimer using the Anderson molecule}
@@
 The wavefunctions for the \(N=2\) sector can also be connected through these transformations.
-Since both the Hamiltonians are analytically solvable, we can write down their groundstate wavefunctions \cite{pavarini}:
+Since both the Hamiltonians are analytically solvable, we can write down their groundstate wavefunctions [CITE PAVARINI]:
 \begin{equation}\begin{aligned}
@@
 	\centering
-	\includegraphics[width=0.3\textwidth]{dimer-nn.png}
+	\includegraphics[width=0.3\textwidth]{../figures/dimer-nn.png}
 	\caption{Blue circles indicate the dimer sites (enclosed by dotted circle).
@@
 	\hspace*{\fill}
-	\includegraphics[width=0.7\textwidth]{lattice.png}
+	\includegraphics[width=0.7\textwidth]{../figures/lattice.png}
 	\hspace*{\fill}
@@
 	\centering
-	\includegraphics[width=0.2\textwidth]{dimer_dispersion.png}
+	\includegraphics[width=0.2\textwidth]{../figures/dimer_dispersion.png}
 	\caption{Hubbard dimer with dispersion that connects to both sites}
@@
 
-\section{Numerical Results for a bath with two momentum modes}
-
-\section{Future goals}
+\chapter{Future goals}
 \begin{enumerate}
@@
 
-\newpage
-\section*{Appendix: Spectra of Hubbard dimer}
+\begin{appendices}
+\appendixtitleon
+\appendixtitletocon
+\chapter{Derivation of RG equations: \(U_b\)-free terms}
+\section{Renormalisation of the impurity energy \(\epsilon_d\)}
+The coupling \(\epsilon_d\) is renormalised by three kinds of vertices: \(V^2\), \(J^2\) and \(K^2\).
+We will consider these processes one after another.
+We define \(n_j\) as the number of states being decoupled on each side of the Fermi surface, at the \(j^\text{th}\) RG step.
+In order to treat both spin and isospin exchanges democratically, we take \(\ket{\Psi}_i = \frac{1}{2}\left(\ket{0} + \ket{q\uparrow} + \ket{q\downarrow} + \ket{q\uparrow, q\downarrow}\right) \) as the \textit{initial} state for the scattering processes.
+The intermediate states \(\ket{\Psi}_\text{int}\) in the particle sector \(\left(c_{q\beta}\ket{\Psi}_i\right)\) and hole sector \(\left(c^\dagger_{q\beta}\ket{\Psi}_i\right)\) will then have both spin and isospin excitations which can couple with the corresponding impurity degree of freedom.
+We will assume that states  \(q > k_F~\left(\epsilon_q > 0\right) \) above the Fermi surface can have only particle excitations and states below the Fermi surface can only have hole excitations.
+The kinetic energy part \(\epsilon_q \tau_{q\beta}\) of \(H_D\) for \(\ket{\Psi}_i\) is then zero, whereas it is always \(D/2\) for \(\ket{\Psi}_\text{int}\).
+To demonstrate this for a typical \(q < k_F\), the hole excitation is \(c_{q \uparrow}\ket{\Psi}_i = \frac{1}{\sqrt 2}\left(\ket{0} + \ket{q \downarrow}\right)\).
+This has an isospin term in the form of the \textit{holon} and a spin term in the form of the down state.
+Since \(\tau_{q \uparrow} = -\frac{1}{2}\) in the excited state, the kinetic energy for \(\ket{\Psi}_\text{int}\) is \(\epsilon_q \tau_{q \uparrow} = \left(-D\right)\times\left(-\frac{1}{2}\right) = D/2\).
+
+The renormalisation arising from the first kind of terms, in the particle sector, is
+\begin{equation}\begin{aligned}
+	\sum_{q\beta}c^\dagger_{q\beta}c_{d\beta}\frac{V^2}{\omega - H_D}c^\dagger_{d\beta}c_{q\beta} = \sum_{q\beta}V^2 \hat n_{q\beta} \left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega - E_0} + \frac{\hat n_{d \overline\beta}}{\omega^\prime - E_1}\right) = V^2 n_j\sum_{\beta}\left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega_0 - E_0} + \frac{\hat n_{d \overline\beta}}{\omega_1 - E_1}\right)
+\end{aligned}\end{equation}
+\(q\) runs over the momentum states that are being decoupled at this RG step: \(|q| = \Lambda_j\).
+\(E_{1,0}\) are the diagonal parts of the Hamiltonian at \(\hat n_{d\overline \beta}=0,1\) respectively.
+We have \(\hat n_{d\beta}=1\) in the intermediate state because of the \(c^\dagger_{d\beta}\) in front of the Greens function.
+Applying \(c_{q\beta}\) on the initial state \(\ket{\Psi}_i\) leaves us with \(C^z_q = - \frac{1}{2}\) and \(s^z_q = \frac{1}{2}\overline\beta\).
+We also know that
+\begin{equation}\begin{aligned}
+	\hat n_{d\beta}=1,
+	\begin{cases}
+		\hat n_{d\overline\beta}=0 &\implies S_d^z = \frac{1}{2}\beta, C_d^z = 0, \epsilon_d\left(\hat n_{d\uparrow} - \hat n_{d \downarrow}\right)^2 = \epsilon_d\\	
+		\hat n_{d\overline\beta}=1 &\implies S_d^z = 0, C_d^z = \frac{1}{2}, \epsilon_d\left(\hat n_{d\uparrow} - \hat n_{d \downarrow}\right)^2 = 0
+	\end{cases}
+\end{aligned}\end{equation}
+Combining all this, we can write \(E_1 = \frac{D}{2} - \frac{K}{4}\) and \(E_0 = \frac{D}{2} + \epsilon_d - \frac{J}{4}\).
+In order to relate \(\omega_0\) with \(\omega_1\) with the common fluctuation scale \(\omega\) for the conduction electrons, we will replace these quantum fluctuation scales by the current renormalised values of the single-particle self-energy for the initial state from which we started scattering.
+For \(\hat n_{d\overline\beta}=0\), there is no additional self-energy because the impurity does not have any spin: \(\omega_0 = \omega\).
+For \(\hat n_{d\overline\beta} = 1\), we have an additional self-energy of \(\epsilon_d\) arising from the correlation on the impurity: \(\omega_1 = \omega + \epsilon_d\).
+Substituting the values of \(E_{0,1}\) and \(\omega_{0,1}\), we get
+\begin{equation}\begin{aligned}
+	\label{ren_ed_Vp}
+	V^2 n_j\sum_{\beta}\left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)
+\end{aligned}\end{equation}
+Performing a similar calculation for the hole sector gives the contribution:
+\begin{equation}\begin{aligned}
+	\label{ren_ed_Vh}
+	V^2 n_j\sum_{\beta}\hat n_{d\beta}\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right)
+\end{aligned}\end{equation}
+We now come to the second type of terms: spin-spin. We first look at the particle sector:
+\begin{equation}\begin{aligned}
+	\label{ren_ed_Jpp}
+	\frac{J^2}{4}\sum_{q\beta}c^\dagger_{d\overline\beta}c_{d\beta}c^\dagger_{q\beta}c_{-q\overline\beta} \frac{1}{\omega - H_D}c^\dagger_{d\beta}c_{d\overline\beta}c^\dagger_{q\overline\beta}c_{q\beta} = \frac{J^2}{4} n_j\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{\beta}\hat n_{d\overline\beta}\left( 1 - \hat n_{d\beta} \right)
+\end{aligned}\end{equation}
+The diagonal part in the denominator was simple to deduce in this case, because the nature of the scattering requires the spins \(S_d^z\) and \(\frac{\beta}{2}\left(\hat n_{q\beta} - \hat n_{q \overline\beta}\right)\) to be anti-parallel.
+This ensures that the intermediate state has an energy of \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\), and the quantum fluctuation scale is \(\omega^\prime = \omega + \epsilon_d\), such that \(\omega^\prime - E = \omega - \frac{D}{2} + \frac{J}{4}\).
+In the hole sector, we have
+\begin{equation}\begin{aligned}
+	\label{ren_ed_Jph}
+	\frac{J^2}{4} n_j\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{\beta}\hat n_{d\beta}\left( 1 - \hat n_{d\overline\beta} \right)
+\end{aligned}\end{equation}
+The final kind of scattering is the \(K^2\) type. Similar to the \(J^2\) term, we get the following contribution:
+\begin{equation}\begin{aligned}
+	\label{ren_ed_Kpp}
+	\frac{K^2}{4}\sum_{q\beta}c^\dagger_{q\beta}c^\dagger_{q\overline\beta}c_{d\overline\beta}c_{d\beta} \frac{1}{\omega - H_D}c^\dagger_{d\beta}c^\dagger_{d\overline\beta}c_{q\overline\beta}c_{q\beta} = \frac{K^2}{2} n_j\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} \left(1 - \hat n_{d \uparrow}\right) \left( 1 - \hat n_{d \downarrow} \right)
+\end{aligned}\end{equation}
+in the particle sector. This is again because \(E = \frac{D}{2} - \frac{K}{4}\) in the intermediate state and \(\omega^\prime = \omega\). In the hole sector, we get
+\begin{equation}\begin{aligned}
+	\label{ren_ed_Kph}
+	\frac{K^2}{2} n_j\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} \hat n_{d\uparrow}\hat n_{d \downarrow}~.
+\end{aligned}\end{equation}
+
+We now have all possible renormalisation to the impurity energy \(\epsilon_d\).
+To actually compute the renormalisation, we will first calculate the renormalisation in the energies \(\epsilon_0, \epsilon_1\) and \(\epsilon_2\) of the impurity states \(\ket{\hat n_d = 0}, \ket{\hat n_d = 1}, \ket{\hat n_d = 2}\) respectively.
+The renormalisation of these states are given by the following terms:
+\begin{itemize}
+	\item \(\Delta \epsilon_0\) is given by the renormalisation of the term \(\left(1 - \hat n_{d\uparrow}\right)\left(1 - \hat n_{d \downarrow}\right)\)
+	\item \(\Delta \epsilon_1\) is given by the renormalisation of either \(\left(1 - \hat n_{d\uparrow}\right)\hat n_{d \downarrow}\) or \(\left(1 - \hat n_{d\downarrow}\right)\hat n_{d \uparrow}\)
+	\item \(\Delta \epsilon_2\) is given by the renormalisation of \(\hat n_{d\uparrow}\hat n_{d \downarrow}\)
+\end{itemize}
+From eqs.~\ref{ren_ed_Vp}, \ref{ren_ed_Vh}, \ref{ren_ed_Jpp}, \ref{ren_ed_Jph}, \ref{ren_ed_Kpp} and \ref{ren_ed_Kph}, we write
+\begin{equation}\begin{aligned}
+	\Delta \epsilon_0 = \Delta \epsilon_2 = \frac{2V^2 n_j}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}} + \frac{K^2 n_j/2}{\omega - \frac{D}{2} + \frac{K}{4}}, && \Delta \epsilon_1 = \frac{2V^2 n_j}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} + \frac{J^2 n_j/2}{\omega - \frac{D}{2} + \frac{J}{4}}
+\end{aligned}\end{equation}
+We had started with a particle-hole symmetric Hamiltonian \((2\epsilon_d + U = 0)\); the fact that \(\Delta \epsilon_0 = \Delta \epsilon_2\) means the RG transformation has preserved that symmetry.
+The renormalisation of \(\epsilon_d\) is simply the renormalisation in the energy difference between the singly-occupied and vacant impurity levels: \(\Delta \epsilon_d = \Delta \epsilon_1 - \Delta \epsilon_0\).
+This gives our first RG equation:
+\begin{equation}\begin{aligned}
+	\Delta \epsilon_d = 2V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + \frac{n_j}{2}\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right)
+\end{aligned}\end{equation}
+
+\section{Renormalisation of the hybridisation \(V\)}
+Renormalisation of \(V\) happens through two kinds of processes: \(VJ\) and \(VK\).
+In order words, the two vertices involve one single-particle scattering and one spin or isospin exchange respectively.
+We first look at the vertices that involve a spin-exchange scattering.
+
+Within spin-exchange, the scattering can be either via \(S_d^z\) or through \(S_d^\pm\). For the first kind, we have the following contribution in the particle sector:
+\begin{equation}\begin{aligned}
+	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{4}J \sum_{k} \left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) c^\dagger_{k\beta}c_{q\beta} = \frac{1}{4}V J n_j \frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right)\sum_{k\beta} \left(1 - \hat n_{d\overline\beta}\right) c_{d\beta}c^\dagger_{k\beta}
+\end{aligned}\end{equation}
+The transformation from \(\frac{1}{\omega - H_D}\) to \(\frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right)\) is made so that we can account for both the initial state and the final state energies through the two fluctuation scales \(\omega^\prime_1\) and \(\omega_2^\prime\) respectively; we calculate the denominators for both the initial and final states, and then take the mean of the two (hence the factor of half in front).
+This was not required previously because in the earlier scattering processes, the impurity returned to its initial state at the end, at least in terms of \(\epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right)^2 \), and so we had \(\omega_1^\prime = \omega_2^\prime = \omega^\prime\).
+
+Note that the \(c_{d\beta}\) in front of the Greens function resulted in \(\left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) \to \left(1 - \hat n_{d\overline\beta}\right)\).
+The intermediate state is characterised by \(\hat n_{d\beta} = 1 - \hat n_{d \overline \beta} = 1\), which means that \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\).
+Moreover, the initial state gives \(\omega_1^\prime = \omega + \epsilon_d\) while the final state gives \(\omega^\prime_2 = \omega\).
+Therefore, the renormalisation becomes
+\begin{equation}\begin{aligned}
+	-\frac{n_j}{4}V J \frac{1}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right)\sum_{k\beta}\left(1 - \hat n_{d\overline\beta}\right) c^\dagger_{k\beta} c_{d\beta}
+\end{aligned}\end{equation}
+One can generate another such process by exchanging the single-particle process and the spin-exchange process:
+\begin{equation}\begin{aligned}
+	\sum_{q\beta} \frac{1}{4}J \sum_{k} \left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) c^\dagger_{q\beta}c_{k\beta} \frac{1}{\omega - H_D} V c^\dagger_{d\beta} c_{q\beta}
+\end{aligned}\end{equation}
+This is simply the Hermitian conjugate of the previous contribution. Combining this with the previous then gives
+\begin{equation}\begin{aligned}
+	-\frac{n_j}{8}V J \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta}\left(1 - \hat n_{d\overline\beta}\right)\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+
+We now consider the spin-exchange processes involving \(S_d^\pm\):
+\begin{equation}\begin{aligned}
+	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{2}J \sum_{k} c^\dagger_{d\beta}c_{d\overline\beta} c^\dagger_{k\overline\beta}c_{q\beta} = \frac{1}{2}V J n_j \frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) c_{d\overline\beta}c^\dagger_{k\overline\beta}
+\end{aligned}\end{equation}
+We again have \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4},\omega_1^\prime = \omega + \epsilon_d\) and \(\omega_2^\prime = \omega\), which gives
+\begin{equation}\begin{aligned}
+	-\frac{1}{2}V J n_j \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)c^\dagger_{k\overline\beta} c_{d\overline\beta}
+\end{aligned}\end{equation}
+Combining this with the Hermitian conjugate obtained from exchanging the processes gives
+\begin{equation}\begin{aligned}
+	-\frac{1}{4}V J n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)\left(c^\dagger_{k\overline\beta} c_{d\overline\beta} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+
+The contributions from the hole sector are obtained making the transformation \(\hat n_{d\overline\beta} \to 1 - \hat n_{d\overline\beta}\) on the particle sector contributions.
+The total renormalisation to \(V\) from \(VJ\) processes are
+\begin{equation}\begin{aligned}
+	-\frac{3n_j}{8}V J \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+
+We now look at the \(VK\) processes. The first one is
+\begin{equation}\begin{aligned}
+	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{4}K \sum_{k} \left(\hat n_{d} - 1\right) c^\dagger_{k\beta}c_{q\beta} = -\frac{1}{8}V K n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \hat n_{d\overline \beta}c^\dagger_{k\beta}c_{d\beta}
+\end{aligned}\end{equation}
+The exchanged process again gives the Hermitian conjugate, so the combined contribution is
+\begin{equation}\begin{aligned}
+	-\frac{1}{8}V K n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \hat n_{d\overline \beta} \left(c^\dagger_{k\beta}c_{d\beta} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+
+The isospin-flip vertex gives
+\begin{equation}\begin{aligned}
+	\sum_{q\beta} V c^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{2}K \sum_{k} c^\dagger_{d\beta}c^\dagger_{d\overline\beta} c_{k\overline\beta} c_{q\beta} = \frac{1}{4}K V n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) c^\dagger_{d\overline\beta}c_{k\overline\beta}~.
+\end{aligned}\end{equation}
+Combining with Hermitian conjugate gives
+\begin{equation}\begin{aligned}
+	\frac{1}{4}K V n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) \left(c^\dagger_{d\overline\beta}c_{k\overline\beta} + \text{h.c.}\right)~.
+\end{aligned}\end{equation}
+
+After obtaining the hole sector contributions, the total renormalisation from \(VK\) processes is
+\begin{equation}\begin{aligned}
+	-\frac{3n_j}{4}V K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)~.
+\end{aligned}\end{equation}
+
+The RG equation for \(V\) is
+\begin{equation}\begin{aligned}
+	\Delta V = -\frac{3n_j V}{8}\left[J\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)\right]
+\end{aligned}\end{equation}
+
+\section{Renormalisation of the exchange couplings \(J\) and \(K\)}
+We will just note the renormalisation in \(J^z\), which will be equal to \(J^\pm\) due to spin-rotation symmetry.
+The terms that renormalise \(J^z\) are of the form \(S_d^\pm S_d^\mp\).
+In the particle sector, we have
+\begin{equation}\begin{aligned}
+	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^\pm c^\dagger_{q\mp}c_{k^\prime\pm} \frac{1}{\omega - H_D}S_d^\mp c^\dagger_{k\pm}c_{q\mp} = -n_j \frac{1}{4}J^2 \left(\frac{1}{2} \pm S_d^z\right) \sum_{kk^\prime}c^\dagger_{k \pm}c_{k\pm} \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
+\end{aligned}\end{equation}
+The denominator is determined using \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\) and \(\omega^\prime = \omega + \epsilon_d\).
+In the hole sector, we similarly have
+\begin{equation}\begin{aligned}
+	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^\mp c^\dagger_{k\pm}c_{q\mp} \frac{1}{\omega - H_D}S_d^\pm c^\dagger_{q\mp}c_{k^\prime\pm} = n_j \frac{1}{4}J^2 \left(\frac{1}{2} \mp S_d^z\right) \sum_{kk^\prime}c^\dagger_{k \pm}c_{k\pm} \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
+\end{aligned}\end{equation}
+Adding all four expressions and dropping the constant part, we get
+\begin{equation}\begin{aligned}
+	-n_j \frac{1}{2}J^2 S_d^z \sum_{kk^\prime}\left(c^\dagger_{k \uparrow}c_{k^\prime \uparrow} - c^\dagger_{k \downarrow}c_{k^\prime \downarrow}\right) \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
+\end{aligned}\end{equation}
+We can now directly read off the RG equation for \(J\):
+\begin{equation}\begin{aligned}
+	\Delta J = -\frac{n_j J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
+\end{aligned}\end{equation}
+
+Since the spin and charge degrees of freedom are treated on an equal footing in the model, we obtain the RG equation for \(K\) by simply changing \(J \to K\):
+\begin{equation}\begin{aligned}
+	\Delta K = -\frac{n_j K^2}{\omega - \frac{D}{2} + \frac{K}{4}}
+\end{aligned}\end{equation}
+
+\chapter{Derivation of RG equations: \(U_b\)-included terms}
+
+We first Fourier transform the \(U_b\)-term to \(k-\)space.
+In \(k-\)space, the diagonal contribution (to \(H_D\)) coming from this term is the single-particle self-energy \(-U_b\left(\hat n_{q \beta}\right)^2\) which can be made particle-hole symmetric in the form:
+\begin{equation}\begin{aligned}
+	-U_b\left(\tau_{q \beta}\right)^2
+\end{aligned}\end{equation}
+where \(q\) is the \(k-\)state being decoupled and \(\tau \equiv \hat n - 1/2\).
+In the initial state \(\ket{\Psi}_i\), we have \(\langle \hat n_{q\beta} \rangle = 1/2 \implies \tau_{q\beta} = 0\), so the contribution of \(U_b\) to that state is 0.
+For both hole excitations \(c_{q\beta}\ket{\Psi}_i\) as well as particle excitations \(c^\dagger_{q\beta}\ket{\Psi}_i\), the intermediate state energy lowers to \(-U_b/4\).
+
+The off-diagonal part is
+\begin{equation}\begin{aligned}
+	-\frac{U_b}{2}\sum_{kk^\prime\sigma}c^\dagger_{k\sigma}c_{k^\prime\sigma} + U_b \sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_1 \uparrow}c_{k_2 \uparrow} c^\dagger_{k^\prime_1 \downarrow}c_{k^\prime_2 \downarrow}
+\end{aligned}\end{equation}
+We ignore the potential scattering arising from the first term.
+
+\section{Renormalisation of \(U_b\)}
+\(U_b\) can renormalise only via itself. The relevant renormalisation term in the particle sector is
+\begin{equation}\begin{aligned}
+	U_b^2 \sum_{q\beta}\sum_{k_1,k_2,k_3,k_1^\prime,k_2^\prime,k_3^\prime} c^\dagger_{q\beta}c_{k_1\beta}c^\dagger_{k_3\overline\beta}c_{k_1^\prime\overline\beta}\frac{1}{\omega - H_D}c^\dagger_{k_2^\prime\overline\beta}c_{k_3^\prime\overline\beta}c^\dagger_{k_2\beta}c_{q\beta}
+\end{aligned}\end{equation}
+In order to renormalise \(U_b\), we need to contract one more pair of momenta.
+There are two choices.
+The first is by setting \(k_3 = k_3^\prime = q\).
+The two internal states, then, are \(q\beta\) and \(q\overline\beta\).
+As discussed above, the intermediate state energy is \(-U_b/4\).
+We therefore have
+\begin{equation}\begin{aligned}
+	\frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c_{k_1\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2^\prime\overline\beta}c^\dagger_{k_2\beta} = \frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_2^\prime\overline\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
+\end{aligned}\end{equation}
+Another way to contract the momenta is by setting \(k_1^\prime = k_2^\prime = q\), which gives a renormalisation of
+\begin{equation}\begin{aligned}
+	\frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c_{k_1\beta}c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta} = -\frac{U_b^2 n_j}{\omega - D/2}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
+\end{aligned}\end{equation}
+The two contributions cancel each other. The same cancellation happens in the hole sector as well.
+
+\section{Renormalisation of \(U\)}
+\(U_b\) does not have any new renormalisation term on account of \(U_b\). \(U_b\) does however modify the existing RG equation for \(U\), by shifting the denominator. The existing RG equation is
+\begin{equation}\begin{aligned}
+	\Delta U &= -4V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) - n_j\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right)~.
+\end{aligned}\end{equation}
+On accounting for the contribution of \(U_b\) to the denominator, we get
+\begin{equation}\begin{aligned}
+	\Delta U &= -4V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} - \epsilon_d + \frac{J}{4}}\right) - n_j\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right)~.
+\end{aligned}\end{equation}
+
+\section{Renormalisation of \(V\)}
+The single-particle  hybridisation \(V\) renormalises through terms of \(V U_b\) and \(U_b V\) kind. The first term gives
+\begin{equation}\begin{aligned}
+	&\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{k\beta} \hat n_{q\overline\beta} \frac{1}{\omega - H_D} c^\dagger_{d\beta}c_{q\beta} \\
+	&= n_jU_b V\sum_{k\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_1 - E_1} + \frac{1}{\omega^\prime_1 - E_1}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_0 - E_0} + \frac{1}{\omega_0^\prime - E_0}\right)\right] c^\dagger_{d\beta}
+\end{aligned}\end{equation}
+\(E_1\) and \(E_0\) are the intermediate state energies for \(\hat n_{d\overline\beta}=1\) and 0 respectively.
+\(\omega_{1,0}\) are the quantum fluctuation scales for the corresponding initial states.
+\(\omega^\prime_{1,0}\) are the fluctuation scales for the corresponding final states.
+The intermediate energies are \(E_1 = D/2 - U_b/4 - K/4,~ ~ ~ E_0 = D/2 - U_b/4 - U/2 - J/4\).
+The fluctuation scales are \(\omega_1 = \omega - U/2= \omega_0^\prime,~ ~ ~ \omega_1^\prime = \omega = \omega_0\).
+Substituting these gives
+\begin{equation}\begin{aligned}
+	-n_jU_b V\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
++\left.
+\frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+\end{aligned}\end{equation}
+
+The second term is of the form
+\begin{equation}\begin{aligned}
+	\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{d\beta} \frac{1}{\omega - H_D} \hat n_{q\overline\beta} c^\dagger_{k\beta}c_{q\beta}
+\end{aligned}\end{equation}
+and this is just the Hermitian conjugate of the previous term, so these two terms together lead to
+\begin{equation}\begin{aligned}
+	-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
+	+ \left.\frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+\end{aligned}\end{equation}
+
+In the hole sector, we have
+\begin{equation}\begin{aligned}
+	&\sum_{q\beta}\sum_{k}U_b V \hat n_{q\overline\beta} c^\dagger_{k\beta}c_{q\beta} \frac{1}{\omega - H_D} c^\dagger_{q\beta}c_{d\beta}\\
+	&-\sum_{q\beta}\sum_{k}U_b V \left(1 - \hat n_{q\overline\beta}\right) c^\dagger_{k\beta}c_{q\beta} \frac{1}{\omega - H_D} c^\dagger_{q\beta}c_{d\beta}\\
+	&= -n_jU_b V\sum_{k\beta} c^\dagger_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_1 - E_1} + \frac{1}{\omega^\prime_1 - E_1}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_0 - E_0} + \frac{1}{\omega_0^\prime - E_0}\right)\right] c_{d\beta}
+\end{aligned}\end{equation}
+\(E_1 = D/2 - U_b/4 - U/2 - J/4,~ ~ ~ E_0 = D/2 - U_b/4 - K/4\).
+The fluctuation scales are \(\omega_1 = \omega = \omega_0^\prime,~ ~ ~ \omega_1^\prime = \omega - U/2 = \omega_0\).
+Substituting these gives
+\begin{equation}\begin{aligned}
+	-n_jU_b V\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{1 - \hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
++\left. \frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+\end{aligned}\end{equation}
+The other term, obtained by exchanging \(V\) and \(U_b\), gives the Hermitian conjugate, so the overall contribution from the hole sector is the same as the total contribution from the particle sector, but with \(\hat n_{d\overline\beta} \to 1 - \hat n_{d\overline\beta}\).
+Combining both the sectors, we get
+\begin{equation}\begin{aligned}
+	-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \frac{1}{2}\left[\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
++\left. \left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+\end{aligned}\end{equation}
+
+Combining with the already existing RG equations, the complete RG equation for \(V\) becomes
+\begin{equation}\begin{aligned}
+	\Delta V =& -\frac{3n_j V}{8}\left[\left(\frac{J}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} + \frac{J}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}}\right) + K \left(\frac{K}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{K}{\omega - \frac{D}{2} + \frac{U_b}{4} - \frac{U}{2} + \frac{K}{4}}\right)\right]\\
+		 &-\frac{n_jU_b}{2}\left[\left(\frac{V}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) + \left(\frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]\\
+		 &=-\frac{n_j V}{8}\left[\left(\frac{3J + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} + \frac{3J + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}}\right) + \left(\frac{3K + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{3K + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} - \frac{U}{2} + \frac{K}{4}}\right)\right]
+\end{aligned}\end{equation}
+
+\section{Renormalisation of \(J\)}
+We will track the entire renormalisation purely from that of \(J^+\), by virtue of the SU(2) symmetry. \(J^+\) renormalises through the \(J U_b\) terms. One of the terms is
+\begin{equation}\begin{aligned}
+	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} S_d^+ c^\dagger_{q \downarrow} c_{k \uparrow} \frac{1}{\omega - H_D} \hat n_{q \uparrow} c^\dagger_{k^\prime \downarrow}c_{q \downarrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
+\end{aligned}\end{equation}
+The factor of half in front is the same half factor that appears in front of the \(S_1^+ S_2^-, S_1^-S_2^+\) terms when we rewrite \(\vec{S}_1\cdot\vec{S}_2\) in terms of \(S^z, S^\pm\).
+Another term is obtained by switching \(J\) and \(U_b\):
+\begin{equation}\begin{aligned}
+	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \downarrow} c^\dagger_{q \uparrow} c_{k \uparrow} \frac{1}{\omega - H_D}S_d^+ c^\dagger_{k^\prime \downarrow} c_{q \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
+\end{aligned}\end{equation}
+
+The corresponding terms in the hole sector are
+\begin{equation}\begin{aligned}
+	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{q \uparrow} \frac{1}{\omega - H_D} \hat n_{q \downarrow} c^\dagger_{q \uparrow}c_{k \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \uparrow} c^\dagger_{k^\prime \downarrow} c_{q \downarrow} \frac{1}{\omega - H_D}S_d^+ c^\dagger_{q \downarrow} c_{k \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
+\end{aligned}\end{equation}
+
+Adding all these terms and combining with the existing RG equation, we get the updated RG equation for \(J\):
+\begin{equation}\begin{aligned}
+	\Delta J = -J n_j\frac{4 U_b + J}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}}
+\end{aligned}\end{equation}
+
+\section{Renormalisation of \(K\)}
+We will follow the same strategy with \(K\) - we will calculate the renormalisation in \(K^+\). The first term is
+\begin{equation}\begin{aligned}
+	\frac{1}{2} K U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \downarrow} c^\dagger_{q \uparrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D} C_d^+ c_{k \downarrow} c_{q \uparrow} = -\frac{1}{2}\frac{K U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}} \sum_{k,k^\prime} C_d^+ c_{k \downarrow} c_{k^\prime \uparrow}
+\end{aligned}\end{equation}
+The second term in the same sector is obtained by flipping the spins of \(k\) and \(q\):
+\begin{equation}\begin{aligned}
+	\frac{1}{2} K U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \uparrow} c^\dagger_{q \downarrow}c_{k^\prime \downarrow} \frac{1}{\omega - H_D} C_d^+ c_{q \downarrow} c_{k \uparrow} = -\frac{1}{2}\frac{K U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}} \sum_{k,k^\prime} C_d^+ c_{k \downarrow} c_{k^\prime \uparrow}
+\end{aligned}\end{equation}
+
+The terms in the hole sector give identical contributions. The RG equation for \(K\) is
+\begin{equation}\begin{aligned}
+	\Delta K = -K n_j\frac{4 U_b + K}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}}
+\end{aligned}\end{equation}
+
+\chapter{Analytic results for the Hubbard dimer}
+\section*{Spectrum of the Hubbard dimer}
 Here we document the spectrum of the Hamiltonian in eqs.~\ref{hubb_dimer}.
@@
 	\label{hubb_dim_spectrum}
-%	\begin{tabular}{|c|c|c|}
-%	\hline
-%	eigenstate & symbol & eigenvalue\\
-%	\hline
-%	\(\ket{0,0}\) & \(\ket{0}\) & \(\frac{U^A}{4}\)\\
-%	\(a_1\left(U^A, t^A\right)\ket{\sigma,0} + a_2\left(U^A, t^A\right)\ket{0, \sigma}\) & \(\ket{0\sigma_-}\) & \(-\frac{1}{4}\Delta(U^A, t^A)\)\\
-%	\(-a_2\left(U^A, t^A\right)\ket{\sigma,0} + a_1\left(U^A, t^A\right)\ket{0, \sigma}\) & \(\ket{0\sigma_+}\) & \(\frac{1}{4}\Delta(U^A, t^A)\)\\
-%	\(\ket{\sigma,\sigma}\) & \(\ket{\sigma\sigma}\) & \(-\frac{U^A}{4}\)\\
-%	\(\frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} + \ket{\downarrow, \uparrow}\right)\) & \(\ket{ST}\) & \(-\frac{U^A}{4}\)\\
-%	\(\frac{1}{\sqrt 2}\left(\ket{2, 0} - \ket{0, 2}\right)\) & \(\ket{CS}\) & \(\frac{U^A}{4}\)\\
-%	$a_1( \frac{1}{2}U^A, t^A) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_2( \frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{-}$ & \(-\frac{1}{2}\Delta( \frac{1}{2}U^A, t^A)\)\\
-%	$-a_2(\frac{1}{2}U^A, t^A) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{+}$ & \(\frac{1}{2}\Delta(\frac{1}{2}U^A, t^A)\)\\
-%	\(a_1\left(U^A, t^A\right)\ket{\sigma,2} - a_2\left(U^A, t^A\right)\ket{2, \sigma}\) & \(\ket{2\sigma_-}\) & \(-\frac{1}{4}\Delta(U^A, t^A)\)\\
-%	\(a_2\left(U^A, t^A\right)\ket{\sigma,2} + a_1\left(U^A, t^A\right)\ket{2, \sigma}\) & \(\ket{2\sigma_+}\) & \(\frac{1}{4}\Delta(U^A, t^A)\)\\
-%	\(\ket{2,2}\) & \(\ket{4}\) & \(\frac{U^A}{4}\)\\
-%	\hline
-%	\end{tabular}
-%	\captionof{table}{Spectrum of Anderson molecule at particle-hole symmetry}
 \end{center}
@@
 
-\section*{Appendix; Contributions of various excitations to the site local spectral function}
+\section*{Contributions of various excitations to the site local spectral function}
 The site local spectral function is
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{dimer-peaks.png}
+	\includegraphics[width=0.9\textwidth]{../figures/dimer-peaks.png}
 	\caption{Position, weight and nature of each of the peaks in the Hubbard dimer site local spectral function}
@@
 
-\section*{Appendix: Relation between single-particle Greens function and the Greens function operator $(T=0)$}
+\chapter{Simple results for the Greens functions}
+\section*{Relation between single-particle Greens function and the Greens function operator $(T=0)$}
  The single-particle Greens function is defined as the solution of the equation:
@@
 
-\section{Appendix: Writing single-particle excitations of ground state in terms of $N=3, S^z = \frac{1}{2}$ eigenstates}
+\section*{Writing single-particle excitations of ground state in terms of $N=3, S^z = \frac{1}{2}$ eigenstates}
 The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates $\ket{3\pm\uparrow}$ defined in table \ref{hubb_dim_spectrum}.
@@
 
-\section{Appendix: Matrix elements of $G^{-1}$ between single-particle momentum excitations, for the Hubbard dimer}
+\section*{Matrix elements of $G^{-1}$ between single-particle momentum excitations, for the Hubbard dimer}
 \begin{equation}\begin{aligned}
@@
 At the final step, we used $\braket{+,+} = 1$ and $\braket{+|H_D|+} = t$.
-\bibliographystyle{unsrt}
+
+\chapter{Zero temperature Greens function in frequency domain}
+
+\label{appx-spectral-func}
+The impurity retarded Green's function (assuming the Hamiltonian to be time-independent, which it is) is defined as
+\begin{equation}\begin{aligned}
+	G_{dd}^\sigma(t) = -i\theta(t) \left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right>
+\end{aligned}\end{equation}
+where the average \(\left< \right>\) is over a canonical ensemble at temperature \(T\), and \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in.
+The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term.
+What follows is a standard calculation where we write the Green's function in the Lehmann representation.
+The ensemble average for an arbitrary operator \(\hat M\) can be written in terms of the exact eigenstates of the fixed point Hamiltonian:
+\begin{equation}\begin{aligned}
+	H^* \ket{n} &= E_n^* \ket{n}, ~ ~ ~\left<\hat M \right> &\equiv \frac{1}{Z}\sum_n \bra{n} \hat M \ket{n} e^{-\beta E_n^*}
+\end{aligned}\end{equation}
+where \(Z = \sum_n e^{-\beta E_n^*}\) is the fixed point partition function and \(\left\{ \ket{n} \right\} \) is the set of eigenfunctions of the fixed point Hamiltonian. We can therefore write
+\begin{equation}\begin{aligned}
+	&\left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right> \\
+	&= \frac{1}{Z}\sum_{m}e^{-\beta E_m}\bra{m}\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\} \ket{m}\\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( \mathcal{O}_{\sigma}(t)\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma}(t)\right) \ket{m} && \left[\sum_n \ket{n}\bra{n} = 1\right]  \\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\right) \ket{m}\\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\left( e^{i\left( E_m - E_n \right)  t}\bra{m}\mathcal{O}_{\sigma}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} \ket{m} + e^{i\left( E_n - E_m \right)  t}\bra{m}\mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma} \ket{m}\right)\\
+	&= \frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
+\end{aligned}\end{equation}
+The time-domain impurity Green's function can thus be written as (this is the so-called Lehmann representation)
+\begin{equation}\begin{aligned}
+	G_{dd}^\sigma = -i\theta(t)\frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
+\end{aligned}\end{equation}
+We are interested in the frequency domain form.
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega) &= \int_{-\infty}^\infty dt e^{i \omega t}G_{d d}^\sigma(t) \\
+			       &= \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t}
+\end{aligned}\end{equation}
+To evaluate the time-integral, we will use the integral representation of the Heaviside function:
+\begin{equation}\begin{aligned}
+	\theta(t) = \frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty \frac{1}{x- i\eta}e^{ixt}dx
+\end{aligned}\end{equation}
+With this definition, the integral in \(G_{dd}^\sigma(\omega)\) becomes
+\begin{equation}\begin{aligned}
+	\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t} &= \left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta}\int_{-\infty}^\infty dt e^{i\left( \omega + E_m - E_n + x\right)t} \\
+									     &=\left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta} 2\pi \delta\left( \omega + E_m - E_n + x\right) \\
+									     &=\left(-i\right)\frac{1}{i}\lim_{\eta \to 0^+} \frac{-1}{\omega + E_m - E_n- i\eta} \\
+									     &=\frac{1}{\omega + E_m - E_n} \\
+\end{aligned}\end{equation}
+The frequency-domain Green's function is thus
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
+\end{aligned}\end{equation}
+The zero temperature Green's function is obtained by taking the limit of \(\beta \to \infty\).
+In both the partition function as well as inside the summation, the only term that will survive is the exponential of the ground state energy \(E_0\).
+\begin{equation*}\begin{aligned}
+	Z \equiv \sum_m e^{-\beta E_m} \implies \lim_{\beta \to \infty}Z = d_0 e^{-\beta E_0}, && E_0 \equiv \text{min}\left\{ E_n \right\} 
+\end{aligned}\end{equation*}
+where \(d_0\) is the degeneracy of the ground state. The Greens function then simplifies to
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega, \beta \to \infty) &= \frac{1}{d_0e^{-\beta E_0}}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left[e^{-\beta E_m}\delta_{E_m, E_0} + e^{-\beta E_n}\delta_{E_n, E_0}\right]\frac{1}{\omega + E_m - E_n}\\
+						 &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n}\right]\\
+\end{aligned}\end{equation}
+The label 0 sums over all states \(\ket{0}\) with energy \(E_0\).
+The spectral function is the imaginary part of this Green's function.
+To extract the imaginary part, we insert an infinitesimal imaginary part in the denominator:
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega, \eta) = \frac{1}{d_0}\lim_{\eta \to 0^-}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n + i\eta} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n + i\eta}\right]\\
+\end{aligned}\end{equation}
+The spectral function at zero temperature can then be written as
+\begin{equation}\begin{aligned}
+	\mathcal{A(\omega)} &= -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] \\
+			    &= \frac{1}{d_0}\frac{1}{\pi}\text{ Im }\left[\lim_{\eta \to 0^-}\sum_{n,0}\left(\frac{-i\eta ||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2}{\left(\omega + E_0 - E_n\right)^2 + \eta^2} + \frac{-i\eta ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2}{\left(\omega - E_0 + E_n\right)^2 + \eta^2}\right)\right]\\
+			    &= \frac{1}{d_0}\frac{1}{\pi}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\pi\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\pi\delta\left(\omega - E_0 + E_n\right)\right]\\
+			    &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]\\
+\end{aligned}\end{equation}
+
+\chapter{Topological interpretation of the Wilson ratio}
+From the Friedel sum rule\cite{langer1961friedel}, we can relate the phase shift \(\delta(0)\) due to scattering (at the Fermi surface) off a local impurity to the number of electrons bound in the potential well produced by that impurity:
+\begin{equation}\begin{aligned}
+\widetilde N = \frac{1}{2\pi i}\text{Tr }\ln S(0) = \int_\Gamma dz\partial_z \frac{1}{2\pi i}\text{Tr }\ln S(0)
+\end{aligned}\end{equation}
+From the optical theorem, we can write
+\begin{equation}\begin{aligned}
+	S = 1 + TG_0 = \frac{G}{G_0} && \left[G = G_0 + G_0 T G_0\right]
+\end{aligned}\end{equation}
+This allows us to write \cite{anirbanurg1}
+\begin{equation}\begin{aligned}
+\widetilde N = \int_\Gamma dz\partial_z \frac{1}{2\pi i}\text{Tr }\ln \frac{G}{G_0}
+\end{aligned}\end{equation}
+Since \(\text{Tr }\ln \hat O = \sum_\lambda \ln O_\lambda = \ln \prod_\lambda O_\lambda = \ln \text{Det} \hat O\), we get
+\begin{equation}\begin{aligned}
+\widetilde N &= \int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln \text{Det } \frac{G}{G_0}\\
+      &= -\int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln \frac{\text{Det } G_0}{\text{Det } G}\\
+      &\equiv -\int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln D\\
+      &= -\int_{\Gamma(D)}\frac{dD}{D}
+\end{aligned}\end{equation}
+From the work of Seki and Yunoki \cite{seki2017topological}, we know that this quantity is essentially the winding number of the curve \(\Gamma(D)\) in the complex plane spanned by the real and imaginary parts of \(D\), and is equal to the change in Luttinger's volume \(V_L\) at \(T=0\).
+\begin{equation}\begin{aligned}
+\widetilde N &= -\int_{\Gamma(D)}\frac{dD}{D} = -\Delta V_L
+\end{aligned}\end{equation}
+The incoming electrons can have \(\sigma = \uparrow,\downarrow\).
+Since the impurity singlet ground state is rotationally invariant, we have \(\delta_\uparrow = \delta_\downarrow = \delta(0)\).
+\begin{equation}\begin{aligned}
+\widetilde N &= \frac{1}{\pi}\sum_\sigma\delta_\sigma(0)\\
+\implies \delta(0) &= \frac{\pi}{2}\widetilde N = -\frac{\pi}{2}\Delta V_L
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+\label{wilson_luttinger}
+R &= 1 + \sin^2 \left(\frac{\pi}{2}\widetilde N\right)\\
+  &= 1 + \sin^2 \left(\frac{\pi}{2}\Delta V_L\right)
+\end{aligned}\end{equation}
+We note that this connection between \(R\) and \(\Delta V_L\) has not been obtained in the existing literature thus far.
+In the unitary limit, \(\delta(0) = \frac{\pi}{2}\), giving \(\Delta V_L = -1 = -\tilde N\) \cite{martin1982fermi} (i.e., one electronic state from the impurity has been absorbed into the Luttinger volume of the conduction bath), such that \(R = 2\) in this limit.
+In this way, we see that a change in the topological quantum number \(\tilde N\) causes the well known renormalisation of the Wilson ratio R from its non-interacting value \((1)\) to the value \((2)\) obtained for the local Fermi liquid \cite{nozieres1974fermi}.
+
+\end{appendices}
+
 \bibliography{notes}

### 2022-03-07 notes/notes.tex
added gen SIAM correlations

@@
 \end{figure}
-\section{Introduction}
+
 This is an attempt to obtain various quantities like Greens functions, self-energies, spectral functions and (if possible) energies and wavefunctions of the Hubbard model, using a cluster-bath approach.
@@
 
-\section{Philosophy of the method}
+\section{Philosophy of the auxiliary model method}
 The method is closely tied to the auxiliary system approach described in [CITE MARTIN].
@@
 \end{aligned}\end{equation}
-\section{Spectral function of the single-impurity Anderson model}
-To get a better look at what we are getting into and what we should expect going forward, we first calculate the spectral function of the smaller single-impurity Anderson model that is obtained as the low-energy Hamiltonian of an URG analysis of the full SIAM.
-This ow energy effective Hamiltonian is
-\begin{equation}\begin{aligned}
-	\epsilon_d \hat n_d + U\hat n_{d \uparrow} \hat n_{d \downarrow} + v \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + \sum_{k \in \left[-\Lambda^*, \Lambda^*\right], \sigma}\epsilon_k \hat n_{k\sigma}
-\end{aligned}\end{equation}
-All the impurity couplings are fixed point values, and the momentum states of the bath now run over a reduced bandwidth.
-The subscript \(d\) indicates that the operator is that of the impurity, while the subscript \(0\) indicates it is of the zeroth site of the bath: \(c_0 = \frac{1}{\sqrt N}\sum_k c_k\).
-The spectral function of the SIAM is already known from other methods like the numerical renormalization group.
-For small values of \(U\), the spectral function consists of just the central quasiparticle excitation peak.
-At larger values of \(U\), we see the emergence of the two Hubbard side bands while the spectral weight at the centre decreases.
-We also calculated the spectral function of the low energy theory sing exact diagonalization.
-The plots are shown in fig.~\ref{siam_spec_func}.
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=\textwidth]{../figures/siam_specfunc_all.pdf}
-	\caption{Spectral function of the effective SIAM Hamiltonian for various values of \(\frac{U}{\Delta}\).
-\(\Delta\) is defined by the height of the central peak in the non-interacting model \(U=0\).
-The inset shows a zoom-in of the final spectral function \(\left( \frac{U}{\Delta} = 19.71 \right)\) near \(\omega = 0\).}
-	\label{siam_spec_func}
-\end{figure}
-\\\\
-Because we kept only a discrete bath of 4 momentum states, \textit{we had to artificially enforce the constancy of the height of the central peak, using \cite{langreth1966}.} To convert the discrete sum of delta functions into a continuous spectrum, we broadened them using a Gaussian.
-Following \cite{bullaNRGreview}, we replace the delta-functions at \(\pm x_n \equiv \pm(E_n - E_0)\) by normalised Gaussian functions
-\begin{equation}\begin{aligned}
-	\delta(\omega \pm x_n) \to \frac{1}{\eta_n\sqrt \pi}e^{-\left(\frac{\omega \pm x_n}{\eta_n}\right)^2}
-\end{aligned}\end{equation}
-The parameter \(\eta_n\) determines the height and width of the Gaussian, and is chosen such that the higher energy poles are broader than the lower energy ones.
-\begin{equation}\begin{aligned}
-	\eta_n = 2\Delta + \frac{1}{2}|x_n| 
-\end{aligned}\end{equation}
-where \(\Delta = \frac{V^2}{t}\) is the relevant energy scale of the non-interacting problem and \(t\) is the tight-binding hopping parameter of the conduction bath.
-\\\\
-The central peak (or equivalently, the central pole in the impurity Greens function) does not vanish even for exhorbitantly large values of \(\frac{U}{\Delta}\), implying that there is no stable local moment phase in the SIAM (a local moment phase would involve a gap at zero frequency in the impurity spectral function).
-Formally, the local moment phase will be stable only at \(U \to \infty\) or \(v^* = 0\).
-\\\\
-We also checked how the width of the central peak varies with increasing \(U\). The behaviour is shown in fig.~\ref{fwhm}. The width was also fitted against a function, as shown in the plot.
-\begin{figure}[htpb!]
-	\centering
-	\includegraphics[width=0.55\textwidth]{../figures/width_vs_U_simple_fit.pdf}
-	% \includegraphics[width=0.49\textwidth]{./width_vs_U_simple_fit_log.pdf}
-	\caption{The decay of the full width at half maximum (FWHM) of the central peak, with increasing \(\frac{U}{\Delta}\). The behaviour satisfies a function of the form shown in the legend.}
-	\label{fwhm}
-\end{figure}
 
@@
 The fact that the charge sector comes with a positive factor means that the holon-doublon states are repulsive, and this renormalisation of the states generates an effective particle-hole symmetric Fermi liquid interaction on the first site - also known as the local Fermi liquid (LFL)~\cite{nozieres1974fermi}.
+
+\section{Destruction of the Abrikosov-Suhl resonance: transition from strong-coupling to local moment}
+
+We will now tune the parameters of the fixed point Hamiltonian and study the variation of quantities related to the effective Hamiltonian like the local FL strength \(\mathcal{F}\), the gap in the spectrum of the zeroth Hamiltonian \(H_0^*\) and the value of the small parameter \(t^2/\delta E\), as well as various measures of entanglement like entanglement entropy, mutual information and spin-spin correlations between various sets of members of the real-space impurity+lattice construction.
+We will trace a specific path through the space of values of fixed point couplings: we will start from the strong-coupling regime \(U \ll J,V\) and go towards the local moment regime \(U \gg J,V\).
+The context of this study is that the technique of dynamical mean-field theory (DMFT) obtains a metal-insulator transition in the 2D Hubbard model by studying the Anderson impurity model as the auxiliary system for the Hubbard; there, the local moment regime of the impurity corresponds to the insulator in the bulk.
+Our goal here is to study what precisely happens in the effective Hamiltonian in the journey from the metal to the insulator, and draw a concrete connection between this modification of the effective Hamiltonian, and the simultaneous change of the impurity spectral function in fig.~\ref{spec_func}.
+This is done with the knowledge that the local moment phase of the generalised SIAM is never RG-stable.
+
+\subsection*{Perturbation theory parameters}
+\begin{center}
+	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+\end{center}
+The vanishing of the gap and the growth of the small parameter indicates the breakdown of perturbation theory around the singlet; this simply shows that there is a degeneracy in the local moment regime, and the effective Hamiltonian will have to be obtained using degenerate perturbation theory.
+The presence of degeneracy also suggests that the effective Hamiltonian will be of the non-Fermi liquid type.
+
+\subsection*{\(k-\)space correlations within the Kondo cloud}
+\begin{center}
+	\includegraphics[width=0.24\textwidth]{../figures/corr-k-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.24\textwidth]{../figures/mi-dk-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.24\textwidth]{../figures/corr-k-diag-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.24\textwidth]{../figures/corr-k-od-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+\end{center}
+The vanishing of the Kondo cloud at large \(U/J\) is clear indication of the destruction of the Kondo cloud and the breakdown of screening.
+Non-zero mutual information indicates an (impurity-mediated) interaction between the \(k-\)states of the conduction bath; seen differently, it is this interaction that is responsively for the screening of the impurity.
+The disappearance of the mutual information is indicative of the disappearance of this interaction.
+
+\subsection*{Mutual information between various real space members}
+\begin{center}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+\end{center}
+The impurity-zeroth site mutual information \(I(d:0)\) remains unchanged at the maximum for an appreciable range of values, and this shows the stability of the singlet.
+Meanwhile, the mutual information between the zeroth site and the site nearest to it (\(I(0:1)\)) grows, because when the singlet weakens, the zeroth site is able to entangle more with the other sites.
+It finally saturates to its maximum value, which is the value produced as result of the tight-binding hopping.
+The mutual information between the impurity and sites beyond the zeroth site (\(I(d:1)\)) show a non-monotonic behaviour; it first increases as the entanglement that was initially restricted to just the impurity and the zeroth sites begins "seeping" into the other sites as well.
+Beyond a critical value of \(U/J\), \(I(d:1)\) starts dropping, because the entanglement has now mostly shifted out of the zero mode and into the conduction bath.
+
+\subsection*{Impurity entanglement entropy and spin-spin correlations}
+
+\begin{center}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+
+	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+\end{center}
+
+The von-Neumann entanglement entropy \(S(d)\) of the impurity shows pretty straightforward behaviour.
+It is maximum for \(U \ll J\) because it is in a singlet configuration.
+For \(U \gg J\), the singlet weakens and the impurity begins to decouple from the bath, leading to a reduction in \(S(d)\).
+At sufficiently low values of \(J/U\), the impurity decouples from the zeroth site and the total system can be factorised into a local moment in product with a tight-binding chain, so that the impurity site will now have zero entanglement entropy.
+
+\subsection*{Behaviour of real-space correlations}
+\begin{center}
+	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+
+	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+\end{center}
+
+\subsection*{Behaviour of real-space correlations as function of distance}
+\begin{center}
+	\includegraphics[width=0.35\textwidth]{../figures/corr-di-min-t=1.000,J=1_over_U,V=J,N=6,U=0.010,100.000,100.pdf}
+	\includegraphics[width=0.35\textwidth]{../figures/corr-di-max-t=1.000,J=1_over_U,V=J,N=6,U=0.010,100.000,100.pdf}
+
+	\includegraphics[width=0.45\textwidth]{../figures/corr-all-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/I-all-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+\end{center}
+
+\subsection*{Behaviour of \(A(\omega)\)}
+\begin{center}
+	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=0.100.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=9.000.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=16.000.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=20.250.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=36.000.pdf}
+\end{center}
 

### 2022-03-08 notes/notes.tex
added spin-spin correlations between 0 and 1,2,3

@@
 \section{Philosophy of the auxiliary model method}
-The method is closely tied to the auxiliary system approach described in [CITE MARTIN].
+The method is closely tied to the auxiliary system approach described in \cite{martin_2016}.
 We can view the full Hamiltonian as a sum of two component Hamiltonians \(H_1, H_2\) connected via the interaction term \(H_{12}\).
@@
 	\centering
-	\includegraphics[width=0.3\textwidth]{../figures/dimer_bath.png}
+	\includegraphics[width=\textwidth]{../figures/dimer_bath.pdf}
 	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.
@@
 
-\section{Destruction of the Abrikosov-Suhl resonance: transition from strong-coupling to local moment}
+\section{Destruction of the Abrikosov-Suhl resonance: passage from strong-coupling to local moment}
 
@@
 \begin{center}
-	\includegraphics[width=0.24\textwidth]{../figures/corr-k-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.24\textwidth]{../figures/mi-dk-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.24\textwidth]{../figures/corr-k-diag-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.24\textwidth]{../figures/corr-k-od-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
 \end{center}
@@
 
-\subsection*{Behaviour of real-space correlations}
+\subsection*{Real-space correlations}
 \begin{center}
@@
 
-\subsection*{Behaviour of real-space correlations as function of distance}
+\subsection*{Real-space correlations as function of distance}
 \begin{center}
@@
 
-\subsection*{Behaviour of \(A(\omega)\)}
+\subsection*{Impurity spectral function}
 \begin{center}
@@
 blue & \(\Delta U <0, \Delta J,\Delta V>0\) & \(U^* \ll V^* \ll J^*\) & SS & \(\ket{SS}=\ket{\uparrow,\downarrow} - \ket{\downarrow, \uparrow}\)  \\ 
-green &  \(\Delta U < 0, \Delta J < 0,\Delta V>0\) & \(V^* < U^* \ll V^*\) & SS + CT-0 & \(c\ket{SS} + \sqrt{1-c^2}\ket{CT-0}\)  \\  
+green &  \(\Delta U < 0, \Delta J < 0,\Delta V>0\) & \(J^* < U^* \ll V^*\) & SS + CT-0 & \(c\ket{SS} + \sqrt{1-c^2}\ket{CT-0}\)  \\  
 red &  \(\Delta U > 0, \Delta J,\Delta V<0\) & \(U^* \gg 1,  V^* = J^* = 0\) & decoupled LM & \(\left\{\ket{\uparrow}, \ket{\downarrow} \right\} \otimes \left\{\ket{0}, \ket{2}\right\} \) \\
@@
 
-\section{Overlap of ground state against spin singlet and charge triplet zero states}
+\section{Evolution of the groundstate across the transition}
+
+\subsection*{Overlap of ground state against spin singlet and charge triplet zero states}
 \begin{center}
-	\includegraphics[width=0.8\textwidth]{../figures/overlaps_gs_D=500,J=0.500.pdf}\\
-	\includegraphics[width=0.8\textwidth]{../figures/overlaps_gs_D=500,J=5.000.pdf}\\
-	\includegraphics[width=0.8\textwidth]{../figures/overlaps_gs_D=500,J=50.000.pdf}
+	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs_D=400,J=0.400.pdf}\\
+	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs_D=400,J=4.000.pdf}\\
+	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs_D=400,J=40.000.pdf}
 \end{center}
 
-\section{Spin and charge correlations in ground state}
+\subsection*{Spin and charge correlations in ground state}
 \begin{center}
-	\includegraphics[width=0.8\textwidth]{../figures/corrs_gs_D=500,J=0.500.pdf}\\
-	\includegraphics[width=0.8\textwidth]{../figures/corrs_gs_D=500,J=5.000.pdf}\\
-	\includegraphics[width=0.8\textwidth]{../figures/corrs_gs_D=500,J=50.000.pdf}
+	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs_D=400,J=0.400.pdf}\\
+	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs_D=400,J=4.000.pdf}\\
+	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs_D=400,J=40.000.pdf}
 \end{center}
 
-\section{\large Behaviour of \(\mathcal{F}\), the gap and the small parameter}
+\section{Evolution of various correlation measures and other quantities}
+
+\subsection*{Perturbation theoretic terms}
 These quantities are related to the local Fermi liquid of the Kondo strong-coupling fixed point and the perturbation theory associated with it.
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
 \end{center}
 
-\section{\large Behaviour of correlation within the Kondo cloud}
+\subsection*{Correlation within the Kondo cloud}
 \begin{center}
-	\includegraphics[width=0.24\textwidth]{../figures/corr-k-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-	\includegraphics[width=0.24\textwidth]{../figures/mi-dk-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-	\includegraphics[width=0.24\textwidth]{../figures/corr-k-diag-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-	\includegraphics[width=0.24\textwidth]{../figures/corr-k-od-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
 \end{center}
 
-\section{\large Behaviour of mutual information between various real space members}
+\subsection*{Mutual information between various real space members}
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
 \end{center}
 
-\section{\large Behaviour of impurity entanglement entropy and spin-spin correlations}
+\subsection*{Impurity entanglement entropy and spin-spin correlations}
 
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-
-	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+
+	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
 \end{center}
 
-\section{Behaviour of real-space correlations}
+\subsection*{Real-space correlations}
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-
-	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=100,V=2J,Ubath=-U,N=4,U=0.100,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+
+	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
 \end{center}
 
-\section{Impurity spectral function}
+\subsection*{Impurity spectral function}
 \begin{center}
@@
 \end{center}
+
 \chapter{From the auxiliary model to the bulk}
@@
 	\centering
-	\includegraphics[width=0.3\textwidth]{../figures/dimer-nn.png}
-	\caption{Blue circles indicate the dimer sites (enclosed by dotted circle).
+	\includegraphics[width=0.3\textwidth]{../figures/dimer-nn.pdf}
+	\caption{Blue circles (enclosed by the oval) indicate the dimer sites.
 Green circles are the sites that are nearest neighbour to the dimer and the ones that are being summed over under the index \(l\).
-Orange circles are sites that are \textit{not} nearest neighbour to the dimer.}
+The red circles are sites that are \textit{not} nearest neighbour to the dimer.}
 	\label{dimer-nn}
@@
 \begin{appendices}
+
 \appendixtitleon
-\appendixtitletocon
+
 \chapter{Derivation of RG equations: \(U_b\)-free terms}
@@
 
-\section{Renormalisation of \(J\)}
+\section{Renormalisation of \(J\) and \(K\)}
 We will track the entire renormalisation purely from that of \(J^+\), by virtue of the SU(2) symmetry. \(J^+\) renormalises through the \(J U_b\) terms. One of the terms is
@@
 
-\section{Renormalisation of \(K\)}
 We will follow the same strategy with \(K\) - we will calculate the renormalisation in \(K^+\). The first term is

### 2022-03-09 notes/notes.tex
rewrote tiling for SIAM

@@
 \chapter{Introduction}
+
+\section{Philosophy of the auxiliary model method}
+The method is closely tied to the auxiliary system approach described in \cite{martin_2016}.
+We can view the full Hamiltonian as a sum of two component Hamiltonians \(H_1, H_2\) connected via the interaction term \(H_{12}\).
+\begin{equation}\begin{aligned}
+	H = \begin{pmatrix} H_1 && H_{12} \\ H_{12}^* && H_2 \end{pmatrix} = H_1 \ket{1}\bra{1} + H_2\ket{2}\bra{2} + H_{12}\ket{1}\bra{2} + H_{12}^*\ket{2}\bra{1}
+\end{aligned}\end{equation}
+where \(\ket{1}(\ket{2})\) actually represents a sum over all basis kets of subsystem 1(subsystem 2).
+As an example, we can split the the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows:
+\begin{equation}\begin{aligned}
+	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_1} \\
+		      &+ \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_2}\\
+		      & -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{12} + H_{12}^*}\\
+\end{aligned}\end{equation}
+The Greens function of the full Hamiltonian can also be split in a similar fashion:
+\begin{equation}\begin{aligned}
+	G(\omega) = \begin{pmatrix} G_1 && G_{12} \\ G_{12}^* && G_2 \end{pmatrix} 
+\end{aligned}\end{equation}
+The subsystem 1 is usually taken to be the "smaller system", and consequently, subsystem 2 represents the "bath".
+The smaller system is typically chosen such that its eigenstates are known exactly.
+Progress is then made by choosing a simpler version of the bath \(H_2\) and a simpler form also for its coupling \(H_{12}\) with the smaller system.
+This combination of the smaller system and the simpler bath is then called the \textit{auxiliary system}.
+A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{12}\).
+Such a construction is shown in fig.~\ref{cluster-bath}.
+\begin{figure}[htpb!]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../figures/cluster-bath.png}
+	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$.
+\textit{Right}: Extraction of the auxiliary (cluster+bath) system from the full lattice.
+The central site on left becomes the impurity site (red) on the right (with an onsite repulsion $\epsilon_d$), while the rest of the $N-1$ sites on the left form a conduction bath (green circles) (with dispersion $\epsilon_k$ and correlation modelled by the self-energy $\Sigma_k(\omega)$) that hybridizes with the impurity through the coupling $V$.}
+	\label{cluster-bath}
+\end{figure}
+\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model.
+To allow computing quantities, one would need to make the bath (which is a much larger system) simpler than the cluster (which is a single site).
+This distinction breaks the translational symmetry of the Hubbard model.
+For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath only has a global capacitative cost $(\sim U_b N^2)$ means we have broken the symmetry between the cluster and the bath.}
+
+The algorithm of DMFT then involves starting with some local self-energy of the bath, \(\Sigma(\omega)\), and using an impurity solver to calculate the impurity Greens function in the presence of this self-energy.
+This impurity Greens function is then used to calculate the impurity self-energy \(\Sigma_d(\omega)\), and the self-energy of the bath is then set equal to this impurity self-energy: \(\Sigma(\omega) = \Sigma_d(\omega)\), because we expect, on grounds of the lattice symmetry, that the impurity is the same as any other site in the bath.
+This is said to be the self-consistency step, because the bath self-energy is completely determined only at the end.
+With this updated bath self-energy, one then repeats the entire process until there is no further change in the bath self-energy at the self-consistency step.
+
+% The present method intends to calculate the quantities in a different fashion.
+% We start with a SIAM (with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian.
+% The fixed point Hamiltonian will in general involve the impurity site (with renormalised parameters $\epsilon_d^*, U^*$) interacting with a smaller number of momentum states.
+
+% At this point, we will assume that we have a Hubbard model in mind that has motivated a correlated SIAM as the auxiliary system, and we have performed renormalisation group analysis on this auxiliary system to get down to an effective Hamiltonian.
+We will also assume that the parameters of the auxiliary system have been chosen such that in the effective Hamiltonian, the impurity and zero mode have the same onsite repulsion: $U^A = U^A_z$ (this is required for translational invariance).
+% \\\\
+% To obtain a comparatively simple but physically well-motivated auxiliary model, we identify $\sum_k c_k = \sqrt N c_0$; \(c_0\) is the operator for the zeroth site (the site nearest to the impurity).
+We will call the set of all \(N-2\) sites apart from the impurity and this zeroth site as the "effective bath".
+The fixed point Hamiltonian can be separated into these parts: an isolated impurity part, an isolated zeroth site part, an isolated effective bath part, hopping between impurity and the zeroth site and hopping between the zeroth site and the effective bath.
+\textit{As a simplification, we will ignore the correlation term \((U)\) on the effective bath}.
+In preparation of a symmetrization procedure, we will relabel the impurity site as 0, and the zeroth site as 1.
+With all these steps, the Hamiltonian takes the form:
+% \begin{equation}\begin{aligned}
+% 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow}}_\text{imp.
+\& zero-mode isolated} - \underbrace{t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{0-1 coupling} - \underbrace{t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{1 \& eff.
+bath coupling} - \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff.
+bath isolated}
+% \end{aligned}\end{equation}
+% \begin{figure}[htpb]
+% 	\centering
+% 	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.png}
+% 	\caption{Correlated asymmetric Anderson molecule schematic version.
+It consists of an impurity site (blue) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink).
+The other sites (green) form the rest of the bath.
+Just the impurity site and the zeroth site have onsite repulsion.}
+% 	\label{and_mol}
+% \end{figure}
+% This Hamiltonian is depicted in fig.~\ref{and_mol}.
+Such a Hamiltonian is, however, explicitly asymmetric between the sites 0 and 1 (the effective bath couples only to 1).
+To rectify that, we will symmetrize the coupling between the effective bath and the sites 0 and 1, by exchanging the sites 0 and 1.
+The resultant Hamiltonian is
+% \begin{equation}\begin{aligned}
+% 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow} - t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{2-site Hubbard model} +\underbrace{- t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)- t^A\sum_{j \in \atop{\text{NN of 0}}}\left(c^\dagger_{0\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{dimer \& eff.
+bath coupling} \\
+% 	- \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff. bath isolated}
+% \end{aligned}\end{equation}
+% % The motivation for extracting the zero mode is that it leads to a very simple effective Hamiltonian (the asymmetric Anderson molecule) without losing much of the low energy physics.
+% To further simplify this Hamiltonian, \textit{we will combine the nearest neighbour sites of \(1\) and \(0\) into a single site}.
+% \begin{equation}\begin{aligned}
+% 	c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}
+% \end{aligned}\end{equation}
+% This single site will act as the zeroth site of the effective bath, and it means that both sites of the Hubbard dimer hybridizes with the effective through just a single site.
+With this assumption, the Hamiltonian for "a Hubbard dimer hopping into an effective bath" takes the simple form
+% \begin{equation}\begin{aligned}
+% 	\label{dimer_p_bat}
+% 	\tilde H^D = H^D(0,1) - t^D \sum_{\sigma}\left(c^\dagger_{0\sigma}c_{z\sigma} + c^\dagger_{1\sigma}c_{z\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}
+% \end{aligned}\end{equation}
+% \(H^D(0,1)\) is the Hubbard dimer Hamiltonian (shown in fig.~\ref{hubb-dim}):
+% \begin{equation}\begin{aligned}
+% 	\label{dimer_ham}
+% 	H^D(0,1) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)
+% \end{aligned}\end{equation}
+% \begin{figure}[htpb!]
+% 	\centering
+% 	\includegraphics[width=0.4\textwidth]{../figures/hubb_dim.png}
+% 	\caption{Hubbard dimer schematic version. It again consists of two sites, like the Anderson molecule, but now both sites have onsite repulsion, and their is again inter-site hopping.}
+% 	\label{hubb-dim}
+% \end{figure}
+% This entire procedure is depicted in fig.~\ref{dimer-bath}.
+% \begin{figure}[htpb]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{../figures/dimer_bath.pdf}
+% 	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.
+We first add the asymmetric Hamiltonians to get a symmetrized Hamiltonian.
+In the symmetrized Hamiltonian, the dimer has \(w\) entry points into the bath, \(w\) being the coordination number of the lattice.
+We then merge these \(w\) lattice sites (enclosed in the black box) into a single lattice site.}
+% 	\label{dimer-bath} 
+% \end{figure}
+% We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice.
+The next step in the programme is to tile the real-space lattice with this dimer+bath Hamiltonian \(\tilde H_D\) to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H = T\left[ \tilde H^{D} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the dimer Hamiltonian to span the target real-space lattice.
+We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.
+% \begin{equation}\begin{aligned}
+% 	\tilde H &= \frac{2}{Nw}\sum_{\left<ij\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\tilde H^D((0,1,z) \to (i, j, l))\\
+% 		 &= \frac{2}{N}U^D\sum_{i} \tau_{i \uparrow}\tau_{i \downarrow} - \frac{2}{Nw}\left(1 + \frac{Nw}{2}\right)t^D\sum_{\left<ij\right>}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)
+% \end{aligned}\end{equation}
+% What that means is that we have placed the Hubbard dimer+bath system at all nearest neighbour pairs to reconstruct a new Hubbard model.
+If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as dropping the correlation on the bath sites, we can write
+% \begin{equation}\begin{aligned}
+% 	\label{app2}
+% 	\tilde H = \mathcal{U} H^H \mathcal{U}^{-1} = TZ\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right]Z^{-1} T^{-1}~,
+% \end{aligned}\end{equation}
+% where $\mathcal{U} = TZ\mathcal{U}_{A}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation that maps from the original to the reconstructed Hubbard Hamiltonian.
+% The existence of $U$ is contingent on how good the approximations are.
+% \\\\
+% We mention the two approximations made along the entire journey from the original Hubbard model to the reconstructed one here.
+% \begin{itemize}
+% 	\item We have replaced the full Hubbard model by an auxiliary system described by the SIAM Hamiltonian in eq.~\ref{clus_bath_siam}.
+The accuracy of this assumption is determined by the choice of the SIAM parameters, particular the self-energy and repulsion of the bath.
+As discussed before, the very choice of th cluster and bath spoil the translational invariance of the parent model.
+% 	\item We then perform a unitary RG on $H^A$.
+This leads to a fixed-point Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$.
+At this point, we go from the fixed point Hamiltonian to the dimer+bath Hamiltonian in eq.~\ref{dimer_p_bat}.
+If we represent this transformation from the fixed point Hamiltonian to the Hamiltonian in eq.~\ref{dimer_p_bat} by an operator \(Z\), we can write $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$.
+This constitutes the second approximation we make.
+% \end{itemize}
+
 \section{What is the minimal impurity model for a Mott MIT?}
@@
 The meaning of each of these statements will become clearer when we describe the method in more detail.
-
-\section{Philosophy of the auxiliary model method}
-The method is closely tied to the auxiliary system approach described in \cite{martin_2016}.
-We can view the full Hamiltonian as a sum of two component Hamiltonians \(H_1, H_2\) connected via the interaction term \(H_{12}\).
-\begin{equation}\begin{aligned}
-	H = \begin{pmatrix} H_1 && H_{12} \\ H_{12}^* && H_2 \end{pmatrix} = H_1 \ket{1}\bra{1} + H_2\ket{2}\bra{2} + H_{12}\ket{1}\bra{2} + H_{12}^*\ket{2}\bra{1}
-\end{aligned}\end{equation}
-where \(\ket{1(2)}\) actually represents a sum over all basis kets of the subsystem 1(2).
-As an example, we can split the the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows:
-\begin{equation}\begin{aligned}
-	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_1} \\
-		      &+ \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_2}\\
-		      & -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{12} + H_{12}^*}\\
-\end{aligned}\end{equation}
-The Greens function of the full Hamiltonian can also be split in a similar fashion:
-\begin{equation}\begin{aligned}
-	G(\omega) = \begin{pmatrix} G_1 && G_{12} \\ G_{12}^* && G_2 \end{pmatrix} 
-\end{aligned}\end{equation}
-The subsystem 1 is usually taken to be the "smaller system", and consequently, subsystem 2 represents the "bath".
-The smaller system is typically chosen such that its eigenstates are known exactly.
-Progress is then made by choosing a simpler version of the bath \(H_2\) and a simpler form also for its coupling \(H_{12}\) with the smaller system.
-This combination of the smaller system and the simpler bath is then called the \textit{auxiliary system}.
-A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{12}\).
-Such a construction is shown in fig.~\ref{cluster-bath}.
-\begin{figure}[htpb!]
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/cluster-bath.png}
-	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$.
-\textit{Right}: Extraction of the auxiliary (cluster+bath) system from the full lattice.
-The central site on left becomes the impurity site (red) on the right (with an onsite repulsion $\epsilon_d$), while the rest of the $N-1$ sites on the left form a conduction bath (green circles) (with dispersion $\epsilon_k$ and correlation modelled by the self-energy $\Sigma_k(\omega)$) that hybridizes with the impurity through the coupling $V$.}
-	\label{cluster-bath}
-\end{figure}
-\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model.
-To allow computing quantities, one would need to make the bath (which is a much larger system) simpler than the cluster (which is a single site).
-This distinction breaks the translational symmetry of the Hubbard model.
-For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath only has a global capacitative cost $(\sim U_b N^2)$ means we have broken the symmetry between the cluster and the bath.}
-
-The algorithm of DMFT then involves starting with some local self-energy of the bath, \(\Sigma(\omega)\), and using an impurity solver to calculate the impurity Greens function in the presence of this self-energy.
-This impurity Greens function is then used to calculate the impurity self-energy \(\Sigma_d(\omega)\), and the self-energy of the bath is then set equal to this impurity self-energy: \(\Sigma(\omega) = \Sigma_d(\omega)\), because we expect, on grounds of the lattice symmetry, that the impurity is the same as any other site in the bath.
-This is said to be the self-consistency step, because the bath self-energy is completely determined only at the end.
-With this updated bath self-energy, one then repeats the entire process until there is no further change in the bath self-energy at the self-consistency step.
-
-The present method intends to calculate the quantities in a different fashion.
-We start with a SIAM (with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian.
-The fixed point Hamiltonian will in general involve the impurity site (with renormalised parameters $\epsilon_d^*, U^*$) interacting with a smaller number of momentum states.
-% Assuming the impurity-bath couplings are much larger than the dispersion of the bath, we can approximate the conduction bath part by a zero-mode of the kinetic energy part.
-The zero mode is defined as $c_0 = \frac{1}{\sqrt N}\sum_k c_k$, so it is just the zeroth site.
-% What this means is that all the momentum states will then collapse to a single site (which we call the zero mode site, and represents the origin of the lattice).
-We will also pick out the zeroth site part of the onsite correlation part, and replace that with a single correlation coupling $U^A_z$.
-% Such a model, shown in fig.~\ref{and_mol} is exactly solvable.
-At this point, we will assume that we have a Hubbard model in mind that has motivated a correlated SIAM as the auxiliary system, and we have performed renormalisation group analysis on this auxiliary system to get down to an effective Hamiltonian.
-We will also assume that the parameters of the auxiliary system have been chosen such that in the effective Hamiltonian, the impurity and zero mode have the same onsite repulsion: $U^A = U^A_z$ (this is required for translational invariance).
-\\\\
-To obtain a comparatively simple but physically well-motivated auxiliary model, we identify $\sum_k c_k = \sqrt N c_0$; \(c_0\) is the operator for the zeroth site (the site nearest to the impurity).
-We will call the set of all \(N-2\) sites apart from the impurity and this zeroth site as the "effective bath".
-The fixed point Hamiltonian can be separated into these parts: an isolated impurity part, an isolated zeroth site part, an isolated effective bath part, hopping between impurity and the zeroth site and hopping between the zeroth site and the effective bath.
-\textit{As a simplification, we will ignore the correlation term \((U)\) on the effective bath}.
-In preparation of a symmetrization procedure, we will relabel the impurity site as 0, and the zeroth site as 1.
-With all these steps, the Hamiltonian takes the form:
-\begin{equation}\begin{aligned}
-	% H^A_\text{corr} = -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + U^A\tau_{d \uparrow}\tau_{d \downarrow} + U^A_z\tau_{z \uparrow}\tau_{z \downarrow}
-	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow}}_\text{imp.
-\& zero-mode isolated} - \underbrace{t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{0-1 coupling} - \underbrace{t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{1 \& eff.
-bath coupling} - \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff.
-bath isolated}
-\end{aligned}\end{equation}
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.png}
-	\caption{Correlated asymmetric Anderson molecule schematic version.
-It consists of an impurity site (blue) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink).
-The other sites (green) form the rest of the bath.
-Just the impurity site and the zeroth site have onsite repulsion.}
-	\label{and_mol}
-\end{figure}
-This Hamiltonian is depicted in fig.~\ref{and_mol}.
-Such a Hamiltonian is, however, explicitly asymmetric between the sites 0 and 1 (the effective bath couples only to 1).
-To rectify that, we will symmetrize the coupling between the effective bath and the sites 0 and 1, by exchanging the sites 0 and 1.
-The resultant Hamiltonian is
-\begin{equation}\begin{aligned}
-	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow} - t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{2-site Hubbard model} +\underbrace{- t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)- t^A\sum_{j \in \atop{\text{NN of 0}}}\left(c^\dagger_{0\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{dimer \& eff.
-bath coupling} \\
-	- \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff. bath isolated}
-\end{aligned}\end{equation}
-% The motivation for extracting the zero mode is that it leads to a very simple effective Hamiltonian (the asymmetric Anderson molecule) without losing much of the low energy physics.
-To further simplify this Hamiltonian, \textit{we will combine the nearest neighbour sites of \(1\) and \(0\) into a single site}.
-\begin{equation}\begin{aligned}
-	c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}
-\end{aligned}\end{equation}
-This single site will act as the zeroth site of the effective bath, and it means that both sites of the Hubbard dimer hybridizes with the effective through just a single site.
-With this assumption, the Hamiltonian for "a Hubbard dimer hopping into an effective bath" takes the simple form
-\begin{equation}\begin{aligned}
-	\label{dimer_p_bat}
-	\tilde H^D = H^D(0,1) - t^D \sum_{\sigma}\left(c^\dagger_{0\sigma}c_{z\sigma} + c^\dagger_{1\sigma}c_{z\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}
-\end{aligned}\end{equation}
-\(H^D(0,1)\) is the Hubbard dimer Hamiltonian (shown in fig.~\ref{hubb-dim}):
-\begin{equation}\begin{aligned}
-	\label{dimer_ham}
-	H^D(0,1) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)
-\end{aligned}\end{equation}
-\begin{figure}[htpb!]
-	\centering
-	\includegraphics[width=0.4\textwidth]{../figures/hubb_dim.png}
-	\caption{Hubbard dimer schematic version. It again consists of two sites, like the Anderson molecule, but now both sites have onsite repulsion, and their is again inter-site hopping.}
-	\label{hubb-dim}
-\end{figure}
-This entire procedure is depicted in fig.~\ref{dimer-bath}.
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=\textwidth]{../figures/dimer_bath.pdf}
-	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.
-We first add the asymmetric Hamiltonians to get a symmetrized Hamiltonian.
-In the symmetrized Hamiltonian, the dimer has \(w\) entry points into the bath, \(w\) being the coordination number of the lattice.
-We then merge these \(w\) lattice sites (enclosed in the black box) into a single lattice site.}
-	\label{dimer-bath} 
-\end{figure}
-We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice.
-The next step in the programme is to tile the real-space lattice with this dimer+bath Hamiltonian \(\tilde H_D\) to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H = T\left[ \tilde H^{D} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the dimer Hamiltonian to span the target real-space lattice.
-We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.
-\begin{equation}\begin{aligned}
-	\tilde H &= \frac{2}{Nw}\sum_{\left<ij\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\tilde H^D((0,1,z) \to (i, j, l))\\
-		 &= \frac{2}{N}U^D\sum_{i} \tau_{i \uparrow}\tau_{i \downarrow} - \frac{2}{Nw}\left(1 + \frac{Nw}{2}\right)t^D\sum_{\left<ij\right>}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-What that means is that we have placed the Hubbard dimer+bath system at all nearest neighbour pairs to reconstruct a new Hubbard model.
-If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as dropping the correlation on the bath sites, we can write
-\begin{equation}\begin{aligned}
-	\label{app2}
-	\tilde H = \mathcal{U} H^H \mathcal{U}^{-1} = TZ\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right]Z^{-1} T^{-1}~,
-\end{aligned}\end{equation}
-where $\mathcal{U} = TZ\mathcal{U}_{A}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation that maps from the original to the reconstructed Hubbard Hamiltonian.
-The existence of $U$ is contingent on how good the approximations are.
-\\\\
-We mention the two approximations made along the entire journey from the original Hubbard model to the reconstructed one here.
-\begin{itemize}
-	\item We have replaced the full Hubbard model by an auxiliary system described by the SIAM Hamiltonian in eq.~\ref{clus_bath_siam}.
-The accuracy of this assumption is determined by the choice of the SIAM parameters, particular the self-energy and repulsion of the bath.
-As discussed before, the very choice of th cluster and bath spoil the translational invariance of the parent model.
-	\item We then perform a unitary RG on $H^A$.
-This leads to a fixed-point Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$.
-At this point, we go from the fixed point Hamiltonian to the dimer+bath Hamiltonian in eq.~\ref{dimer_p_bat}.
-If we represent this transformation from the fixed point Hamiltonian to the Hamiltonian in eq.~\ref{dimer_p_bat} by an operator \(Z\), we can write $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$.
-This constitutes the second approximation we make.
-\end{itemize}
 
@@
 \begin{center}
+	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
 	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
@@
 	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-
-	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+
 \end{center}
@@
 
-%\section{Creating General \(N-\)site Hubbard Hamiltonian from Hubbard dimers: tiling the lattice with Anderson molecules}
+\section{Creating General \(N-\)site Hubbard Hamiltonian from Anderson molecule embedded in an interacting bath}
+
+Previously, we have worked out the grounstate phases of a single-impurity model with an interacting bath:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
+\end{aligned}\end{equation}
+We will use this as the auxiliary model to study the Hubbard model.
+We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
+To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(i\) of the lattice, and the bath coupled to the impurity as the set of remaining \(N-1\) sites in the lattice.
+We will also identity the zeroth site of the SIAM lattice as one of the nearest neighbours \(j\) of \(i\):
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux}(i,j) = -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n} \left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2
+\end{aligned}\end{equation}
+The tight-binding term sums over all nearest pairs \((m,n)\) that do not involve the site \(i\).
+In general \(i\) will have \(w\) nearest neighbours for a lattice with coordination number \(w\).
+The total local Hamiltonian for the site \(i\) is obtained by averaging over the Hamiltonians \(\mathcal{H}_\text{aux}(i,j)\) for all nearest neighbours \(j\) of \(i\):
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux}(i) &= \frac{1}{w}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{w}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
+				  &\left.- U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\\
+				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
+				  &\left.- U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]
+\end{aligned}\end{equation}
+Once we have this local Hamiltonian for a particular site, we translate this over all sites \(i\), and take the average.
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{full} =& \frac{1}{N}\sum_i \mathcal{H}_\text{aux}(i) = \frac{1}{N}\sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
+				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\right]\\
+	=& -\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{N}\sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
+				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j\right]\right]
+\end{aligned}\end{equation}
+In the entire tight-binding term \(\sum_i\sum_{<m,n>,\sigma}^{m \neq i \neq n}\), each pair will appear \(N-2\) times, because that is the total number of sites that do not involve either \(m\) or \(n\).
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{full} =& -\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{2t (N-2)}{N}\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{Nw}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
+				  &+ \left. J \vec{S_i}\cdot\vec{S}_j\right]\\
+				  &=-\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(\frac{2t (N-2)}{N} - \frac{2V}{Nw}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{Nw} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
+\end{aligned}\end{equation}
+We end up with a Hubbard-Heisenberg model:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_{H-H} = -\sum_{i} U_H \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_H\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_H\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j
+\end{aligned}\end{equation}
+The mapping between the parameters is
+\begin{equation}\begin{aligned}
+	t^H = \frac{1}{N}\left(2t (N-2) - \frac{2V}{N}\right),~ ~ U^H = \frac{1}{N}\left(\frac{U}{2} + U_b\right), ~ ~ J_H = \frac{2J}{Nw}
+\end{aligned}\end{equation}
+The conclusion is that we can tile Anderson models with interacting baths into a Hubbard-Heisenberg model:
+\begin{equation}\begin{aligned}
+	\label{siam_to_hubb}
+	\frac{1}{Nw}\sum_i \sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = \mathcal{H}_{H-H}
+\end{aligned}\end{equation}
+
+\section{Single-particle Green's function}
+We now define the Greens function {\it operators}:
+\begin{equation}\begin{aligned}
+	\mathcal{G}_H = \frac{1}{\omega - H_{H-H}}, \mathcal{G}_\text{aux}(i,j) = \frac{1}{\omega - H_\text{aux}(i,j)}
+\end{aligned}\end{equation}
+Rewriting eq.~\ref{siam_to_hubb} in terms of these operators, we get
+\begin{equation}\begin{aligned}
+	\frac{1}{Nw}\sum_i \sum_{j \in \text{NN of i}} \left(\omega - \mathcal{G}^{-1}_\text{aux}(i,j)\right) = \omega - \mathcal{G}^{-1}_{H-H} \implies \frac{1}{Nw}\sum_i \sum_{j \in \text{NN of i}} \mathcal{G}^{-1}_\text{aux}(i,j) = \mathcal{G}^{-1}_{H-H}
+\end{aligned}\end{equation}
+There we used \(\frac{1}{Nw}\sum_i \sum_{j \in \text{NN of i}} \omega = \omega\).
+
 \section{Creating General \(N-\)site Hubbard Hamiltonian from Hubbard dimers}

### 2022-03-09 notes/notes.tex
obtained upto Greens functions

@@
 
-\chapter{From the auxiliary model to the bulk}
+\chapter{From the auxiliary model to the bulk - single site approach}
+
+\section{Creating General \(N-\)site Hubbard Hamiltonian from Anderson molecule embedded in an interacting bath}
+
+Previously, we have worked out the grounstate phases of a single-impurity model with an interacting bath:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
+\end{aligned}\end{equation}
+We will use this as the auxiliary model to study the Hubbard model.
+We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
+To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(i\) of the lattice, and the bath coupled to the impurity as the set of remaining \(N-1\) sites in the lattice.
+We will also identity the zeroth site of the SIAM lattice as one of the nearest neighbours \(j\) of \(i\):
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux}(i,j) = -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n} \left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2
+\end{aligned}\end{equation}
+The tight-binding term sums over all nearest pairs \((m,n)\) that do not involve the site \(i\).
+In general \(i\) will have \(w\) nearest neighbours for a lattice with coordination number \(w\).
+The total local Hamiltonian for the site \(i\) is obtained by averaging over the Hamiltonians \(\mathcal{H}_\text{aux}(i,j)\) for all nearest neighbours \(j\) of \(i\):
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux}(i) &= \frac{1}{w}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{w}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
+				  &\left.- U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\\
+				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
+				  &\left.- U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]
+\end{aligned}\end{equation}
+Once we have this local Hamiltonian for a particular site, we translate this over all sites \(i\), and take the average.
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{full} =& \frac{1}{N}\sum_i \mathcal{H}_\text{aux}(i) = \frac{1}{N}\sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
+				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\right]\\
+	=& -\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{N}\sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
+				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j\right]\right]
+\end{aligned}\end{equation}
+In the entire tight-binding term \(\sum_i\sum_{<m,n>,\sigma}^{m \neq i \neq n}\), each pair will appear \(N-2\) times, because that is the total number of sites that do not involve either \(m\) or \(n\).
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{full} =& -\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{2t (N-2)}{N}\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{Nw}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
+				  &+ \left. J \vec{S_i}\cdot\vec{S}_j\right]\\
+				  &=-\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(\frac{2t (N-2)}{N} - \frac{2V}{Nw}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{Nw} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
+\end{aligned}\end{equation}
+We end up with a Hubbard-Heisenberg model:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_{H-H} = -\sum_{i} U_H \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_H\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_H\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j
+\end{aligned}\end{equation}
+The mapping between the parameters is
+\begin{equation}\begin{aligned}
+	t^H = \frac{1}{N}\left(2t (N-2) - \frac{2V}{N}\right),~ ~ U^H = \frac{1}{N}\left(\frac{U}{2} + U_b\right), ~ ~ J_H = \frac{2J}{Nw}
+\end{aligned}\end{equation}
+The conclusion is that we can tile Anderson models with interacting baths into a Hubbard-Heisenberg model:
+\begin{equation}\begin{aligned}
+	\label{siam_to_hubb}
+	\frac{1}{N}\sum_i \mathcal{H}_\text{aux}(i) = \mathcal{H}_{H-H}
+\end{aligned}\end{equation}
+
+\section{Single-particle Green's function}
+We now define the Greens function {\it operators}:
+\begin{equation}\begin{aligned}
+	\mathcal{G}_{H-H} = \frac{1}{\omega - \left(H_{H-H} - E_\text{gs}\right) }, \mathcal{G}_\text{aux}(i) = \frac{1}{\omega - \left(H_\text{aux}(i) - E_\text{gs}\right)}
+\end{aligned}\end{equation}
+Rewriting eq.~\ref{siam_to_hubb} in terms of these operators, we get
+\begin{equation}\begin{aligned}
+	\frac{1}{N}\sum_i \left(\omega - \mathcal{G}^{-1}_\text{aux}(i)\right) = \omega - \mathcal{G}^{-1}_{H-H} \implies \frac{1}{N}\sum_i \mathcal{G}^{-1}_\text{aux}(i) = \mathcal{G}^{-1}_{H-H}~,
+\end{aligned}\end{equation}
+where we used \(\frac{1}{N}\sum_i \omega = \omega\).
+We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model.
+Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(H_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate.
+We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{Nw}\sum_j \sum_{k \in \text{NN of j}}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(j,k) c^\dagger_{i\sigma} | \Phi_0}
+\end{aligned}\end{equation}
+The superscript \(p\) indicates that this is the particle propagation matrix element.
+Under the single site approximation, we ignore the hopping between multiple impurity that reside in separate instances of the auxiliary model.
+Therefore, the only operator \(\mathcal{G}^{-1}_\text{aux}(j)\) that affects the matrix element is \(j=i, k \in \text{NN of i}\).
+Moreover, because of translation invariance, all \(k\) are equivalent.
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \frac{1}{Nw} w\times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i) c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{N}\braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{d\sigma} | \Phi_0}
+\end{aligned}\end{equation}
+where we have identitied site \(i\) in the auxiliary model as the impurity.
+By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}(d)\), we get
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \frac{1}{N}\sum_{m,n} \braket{\Phi_0 | c_{d\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux}(d) \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d\sigma} | \Phi_0} = \left(\mathcal{G}^{-1}_{H-H}\right)_{ii} = \frac{1}{N}\sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}
+\end{aligned}\end{equation}
+There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(H_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\).
+We also defined \(d^p_n = \bra{\Phi_n}c^\dagger_{d\sigma}\ket{\Phi_0}\).
+The hole propagation matrix element can be obtained similarly:
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \frac{1}{N}\sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn} 
+\end{aligned}\end{equation}
+where \(d^h_n = \bra{\Phi_n}c_{d\sigma}\ket{\Phi_0}\).
+The off-diagonal matrix elements can also be obtained similarly.
+The difference from the diagonal case is that only one out of the \(w\) nearest-neighbour pairs contributes to the matrix element:
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{i,i+1} \equiv \braket{\Phi_0 | c_{i,\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{Nw}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i,i+1) c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{Nw}\braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{z,\sigma} | \Phi_0}
+\end{aligned}\end{equation}
+Here, we identity \(i+1\) as the bath zero mode \(z\) and \(i\) as the impurity \(d\).
+We again define matrix elements \(z_n^p = \braket{\Phi_n | c^\dagger_{z\sigma} | \Phi_0}, z_n^h = \braket{\Phi_n | c_{z\sigma} | \Phi_0}\).
+The matrix element becomes
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}
+\end{aligned}\end{equation}
+The hole counterpart is
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}
+\end{aligned}\end{equation}
+In summary, the four Greens functions are
+\begin{gather}
+	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \frac{1}{N}\sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \frac{1}{N}\sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn}\\
+	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}
+\end{gather}
+
+In order to obtain the matrix elements of \(\mathcal{G}_{H-H}\) as compared to its inverse, we note that the matrix elements of the inverse are related to the matrix elements of another inverse operator, through some coefficients.
+We can therefore use the identity
+\begin{equation}\begin{aligned}
+\left(\hat O\right)_{ij} = \bra{i} \hat O \ket{j} = \sum_{m,n} \braket{i|m} \left(\hat O\right)_{mn} \braket{n|j} \implies \left(\hat O^{-1}\right)_{ij} = \sum_{m,n} \braket{i|m} \left(\hat O^{-1}\right)_{mn} \braket{n|j}
+\end{aligned}\end{equation}
+We can identity \(\left(\hat O^{-1}\right)_{mn}\) as the matrix elements of \(\mathcal{G}_\text{aux}^{-1}\) in our expressions. Using the relation, we can therefore write
+\begin{gather}
+	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \frac{1}{N}\sum_{n} |d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \frac{1}{N}\sum_{n} |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\\
+	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}_\text{aux}(d, -\omega) \right)_{nn}
+\end{gather}
+
+The single-particle Greens functions can now be written in terms of these matrix elements. Using eq.~\ref{G_mat_el}, we write
+\begin{equation}\begin{aligned}
+	\left(G_{H-H}(\omega)\right)_\text{loc} &= \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \frac{1}{N}\sum_n \left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right] \\
+	\left(G_{H-H}(\omega)\right)_\text{nn} &= \left(G_{H-H}(\omega)\right)_{i,i+1}^p - \left(G_{H-H}(-\omega)\right)_{i+1,i}^h = \frac{1}{Nw}\sum_n \left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
+\end{aligned}\end{equation}
+
+\chapter{From the auxiliary model to the bulk - two site approach}
+
 \section{Solution of the Hubbard dimer using the Anderson molecule}
@@
 Going forward, we will switch to using Hubbard dimers as the smallest tiling unit for a general Hubbard model.
-
-\section{Creating General \(N-\)site Hubbard Hamiltonian from Anderson molecule embedded in an interacting bath}
-
-Previously, we have worked out the grounstate phases of a single-impurity model with an interacting bath:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
-\end{aligned}\end{equation}
-We will use this as the auxiliary model to study the Hubbard model.
-We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
-To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(i\) of the lattice, and the bath coupled to the impurity as the set of remaining \(N-1\) sites in the lattice.
-We will also identity the zeroth site of the SIAM lattice as one of the nearest neighbours \(j\) of \(i\):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(i,j) = -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n} \left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2
-\end{aligned}\end{equation}
-The tight-binding term sums over all nearest pairs \((m,n)\) that do not involve the site \(i\).
-In general \(i\) will have \(w\) nearest neighbours for a lattice with coordination number \(w\).
-The total local Hamiltonian for the site \(i\) is obtained by averaging over the Hamiltonians \(\mathcal{H}_\text{aux}(i,j)\) for all nearest neighbours \(j\) of \(i\):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(i) &= \frac{1}{w}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{w}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
-				  &\left.- U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\\
-				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
-				  &\left.- U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]
-\end{aligned}\end{equation}
-Once we have this local Hamiltonian for a particular site, we translate this over all sites \(i\), and take the average.
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& \frac{1}{N}\sum_i \mathcal{H}_\text{aux}(i) = \frac{1}{N}\sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
-				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\right]\\
-	=& -\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{N}\sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
-				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j\right]\right]
-\end{aligned}\end{equation}
-In the entire tight-binding term \(\sum_i\sum_{<m,n>,\sigma}^{m \neq i \neq n}\), each pair will appear \(N-2\) times, because that is the total number of sites that do not involve either \(m\) or \(n\).
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& -\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{2t (N-2)}{N}\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{Nw}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
-				  &+ \left. J \vec{S_i}\cdot\vec{S}_j\right]\\
-				  &=-\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(\frac{2t (N-2)}{N} - \frac{2V}{Nw}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{Nw} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
-\end{aligned}\end{equation}
-We end up with a Hubbard-Heisenberg model:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{H-H} = -\sum_{i} U_H \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_H\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_H\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j
-\end{aligned}\end{equation}
-The mapping between the parameters is
-\begin{equation}\begin{aligned}
-	t^H = \frac{1}{N}\left(2t (N-2) - \frac{2V}{N}\right),~ ~ U^H = \frac{1}{N}\left(\frac{U}{2} + U_b\right), ~ ~ J_H = \frac{2J}{Nw}
-\end{aligned}\end{equation}
-The conclusion is that we can tile Anderson models with interacting baths into a Hubbard-Heisenberg model:
-\begin{equation}\begin{aligned}
-	\label{siam_to_hubb}
-	\frac{1}{Nw}\sum_i \sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = \mathcal{H}_{H-H}
-\end{aligned}\end{equation}
-
-\section{Single-particle Green's function}
-We now define the Greens function {\it operators}:
-\begin{equation}\begin{aligned}
-	\mathcal{G}_H = \frac{1}{\omega - H_{H-H}}, \mathcal{G}_\text{aux}(i,j) = \frac{1}{\omega - H_\text{aux}(i,j)}
-\end{aligned}\end{equation}
-Rewriting eq.~\ref{siam_to_hubb} in terms of these operators, we get
-\begin{equation}\begin{aligned}
-	\frac{1}{Nw}\sum_i \sum_{j \in \text{NN of i}} \left(\omega - \mathcal{G}^{-1}_\text{aux}(i,j)\right) = \omega - \mathcal{G}^{-1}_{H-H} \implies \frac{1}{Nw}\sum_i \sum_{j \in \text{NN of i}} \mathcal{G}^{-1}_\text{aux}(i,j) = \mathcal{G}^{-1}_{H-H}
-\end{aligned}\end{equation}
-There we used \(\frac{1}{Nw}\sum_i \sum_{j \in \text{NN of i}} \omega = \omega\).
 

### 2022-03-10 notes/notes.tex
Wrote down the argument for the MIT

@@
 \chapter{Effect of minimal attractive correlation in the bath}
+\label{siam-attr-chap}
 
@@
 \begin{equation}\begin{aligned}
+	\label{siam_attr}
 	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
@@
 \begin{equation}\begin{aligned}
-	t^H = \frac{1}{N}\left(2t (N-2) - \frac{2V}{N}\right),~ ~ U^H = \frac{1}{N}\left(\frac{U}{2} + U_b\right), ~ ~ J_H = \frac{2J}{Nw}
+	\label{map_aux_bulk}
+	t_{H-H} = \frac{1}{N}\left(2t (N-2) - \frac{2V}{N}\right),~ ~ U_{H-H} = \frac{1}{N}\left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{Nw}
 \end{aligned}\end{equation}
@@
 \begin{gather}
+\label{green_eq_final_siam}
 	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \frac{1}{N}\sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \frac{1}{N}\sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn}\\
@@
 \begin{equation}\begin{aligned}
+	\label{greens_func_siam}
 	\left(G_{H-H}(\omega)\right)_\text{loc} &= \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \frac{1}{N}\sum_n \left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right] \\
-	\left(G_{H-H}(\omega)\right)_\text{nn} &= \left(G_{H-H}(\omega)\right)_{i,i+1}^p - \left(G_{H-H}(-\omega)\right)_{i+1,i}^h = \frac{1}{Nw}\sum_n \left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
-\end{aligned}\end{equation}
+	\left(G_{H-H}(\omega)\right)_\text{n-n} &= \left(G_{H-H}(\omega)\right)_{i,i+1}^p - \left(G_{H-H}(-\omega)\right)_{i+1,i}^h = \frac{1}{Nw}\sum_n \left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
+\end{aligned}\end{equation}
+
+\section{Spectral functions and self-energies}
+
+The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
+\begin{equation}\begin{aligned}
+	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
+\end{aligned}\end{equation}
+where $\vec{r_i}$ is the position vector of a particular lattice site.
+Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites.
+As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
+As we do not have real space Greens function that are more non-local than nearest neighbour, we will attempt to obtain momentum space Greens function from these two contributions:
+\begin{equation}\begin{aligned}
+	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
+\end{aligned}\end{equation}
+The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, w\right]\right\}$.
+\begin{equation}\begin{aligned}
+	\label{k_Gf_siam}
+	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} = G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k}\\
+			     &= \frac{1}{N}\sum_n\left[\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
+\end{aligned}\end{equation}
+where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\). For example, on a d-dimensional hypercubic lattice, we obtain
+\begin{equation}\begin{aligned}
+	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i
+\end{aligned}\end{equation}
+On a 2D square lattice with lattice spacing $a$, this simplifies to
+\begin{eqnarray}
+	\label{2dsquaretb}
+\xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
+\epsilon_{\vec{q}} &=& -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})~
+\end{eqnarray}
+where \(\epsilon_{\vec{q}}\) is the tight-binding dispersion.
+\\\\
+We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
+\begin{equation}\begin{aligned}
+	A_\text{H-H}(\vec{k},\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega)) = -\frac{1}{N\pi} \textrm{Im}\sum_n\left[\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\right.\\
+	\left.\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\\
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+A_\text{H-H}(\vec{r}=0,\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{r}=0,\omega)) = \sum_{\vec{k}}A_{H-H}(\vec{k},\omega)
+\end{aligned}\end{equation}
+
+With the knowledge of the momentum-space Greens function $G_\text{H-H}(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
+\begin{equation}\begin{aligned}
+	\Sigma(\vec k,\omega) = G_0(\vec k,\omega)^{-1} - G(\vec k,\omega)^{-1}
+\end{aligned}\end{equation}
+where the $G_{0}(\vec k, \omega)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system.
+Substituting this as well as the full Greens function $G_{H-H}(\vec k, \omega)$ into Dyson's equation gives
+\begin{equation}\begin{aligned}
+	\Sigma_{H-H}(\vec k,\omega) = \omega +t^{H-H}\xi_{\vec k} - N\left\{\sum_n\left[\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}
+\end{aligned}\end{equation}
+This allows us to calculate the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
+
+\section{Evidence for the Mott MIT}
+Through the URG study of the generalised SIAM with correlation (eq.~\ref{siam_attr}) shown in chapter \ref{siam-attr-chap}, we can conclude the following about that model:
+\begin{itemize}
+	\item For \(U_b > J/4\), the couplings \(J\) and \(V\) become irrelevant while \(U\) is relevant, which means that \textbf{the impurity gets cut off from the bath at low energies}.
+\begin{center}
+	\includegraphics[width=0.7\textwidth]{../figures/phase-map_D=1000.pdf}
+\end{center}
+	\item Study of the impurity spectral function shows a gap at low \(\omega\) for \(U_b > J/4\).
+Other measures like mutual information and spin-spin correlations also show a sharp change on crossing that value, demonstrating \textbf{the destruction of the Kondo cloud and the stabilisation of the local moment on the impurity}.
+\begin{center}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.00.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=6.00.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/corr-k-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/corr-d0-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r1p-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+\end{center}
+	\item In the context of the auxiliary model, this represents an \textbf{impurity phase transition} from the completely-screened spin-singlet phase to the unscrened local moment phase.
+\begin{center}
+	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs_D=400,J=40.000.pdf}
+\end{center}
+
+Using the mappings between the auxiliary model parameters and the bulk paramets (eq.~\ref{map_aux_bulk}), one can define a critical value \(r_c\) of the ratio \(r = U_{H-H}/J_{H-H}\) at the critical points \(-U_b/J=1/4\) \textit{for a given and fixed value of \(U\)}.
+We will now argue that this critical point describes a metal-insulator transition.
+For \(r < r_c\), the well-defined low-\(\omega\) central peak in the impurity spectral function, as well as the large mutual and information correlations, in the ground state, among the members of the Kondo cloud or between the impurity and the zeroth site show that the impurity and the bath are very strongly entangled, and the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) are non-zero at low \(\omega\).
+This means that both the local and the nearest-neighbour Greens functions, that are related to these paramers via eq.~\ref{greens_func_siam}, have poles at low\(-\omega\) and support the propagation of electrons through gapless excitations.
+Since the spectral function is also very simply related to that of the auxiliary model, the former also shows the same zero-energy resonance.
+
+On the other side \(r > r_c\) of the critical point, we know that the impurity gets decoupled from the bath, such that the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) vanish.
+This is simply the loss of spectral weight at low-\(\omega\) because of the removal of the gapless excitations.
+This then implies that the bulk Greens functions will also gap out at low energies, and that describes an insulating phase where the electrons get "jammed" in the local states.
+By the same argument as above, the spectral functin also sees a gap in this phase.
+\end{itemize}
 
@@
 \end{aligned}\end{equation}
-% Note that this local Hamiltonian actually has all the hoppings of the full Hubbard model, but the correlation is present just on the sites \(i,j\).
-We havent transformed the dimer parameters \(U^D, t^D\) to the Hubbard parameters yet.
-% \\\\
-% If we now sum over all the nearest-neighbour pairs and take the average of all the Hamiltonians (\(\frac{1}{2}Nw\) in number), we get
-% \begin{equation}\begin{aligned}
-% 	\tilde H &= \frac{2}{Nw}\sum_{\left<ij \right>}^N H^D_{i,j} \\
-% 		 &= -t^A\sum_{\left<ij\right>}\left( c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.} \right) + \frac{2}{N}\sum_i U \tau_{i \uparrow}\tau_{i \downarrow}\\
-% 		 &= \frac{1}{Nw}\left[\sum_{\sigma, i=1}^N\sum_{j \in \text{NN of }j}-t^D\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^D\sum_{i=1}^N \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + U^D\sum_{i=1}^N\sum_{j \in \text{N.N.
-of }i}\hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right]\\
-% 		      &= \frac{1}{Nw}\left[-t^D 2\sum_{\sigma, \left<ij\right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + 2 U^D\sum_{\left<ij\right>} \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + 2 U^D\sum_{\left<ij\right>} \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right]\\
-% 		      &= \frac{2}{Nw}\sum_{\left<ij\right>}\left[-t^D \sum_\sigma \left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + U^D\left(\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \hat \tau_{j \uparrow}\hat \tau_{j \downarrow}\right)\right]\\
-% 		      &= \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
-% \end{aligned}\end{equation}
-% There we used the identity
-% \begin{equation}\begin{aligned}
-% 	\sum_{i=1}^N\sum_{j \in \text{NN of }j} = 2\sum_{\left<ij\right>}
-% \end{aligned}\end{equation}
 The sum $\left<ij\right>$ is over all nearest-neighbour pairs. 
-% Thus, $\tilde H$ can be written as
-% \begin{equation}\begin{aligned}
-% 	\label{H_tiled}
-% 	\tilde H = - \frac{2t^D}{Nw}\sum_{\sigma, \left<ij \right>}\left(c^\dagger_{\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{2U^D}{N}\sum_i \hat \tau_{i \uparrow}\hat \tau_{i \downarrow} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D)
-% \end{aligned}\end{equation}
 The conclusion is that on tiling the Hubbard dimer+bath Hamiltonians into all the nearest neighbour pairs, we end up with a new Hubbard model Hamiltonian with "renormalised parameters" given by
@@
 It is thus apparent that translating the Hubbard dimers throughout the lattice has restored translational invariance, and generated correlations on all sites. 
-%(as compared to just on the impurity site).
-%This also takes care of the problem that the spectrum of the Anderson molecule and Hubbard dimer are different for the $N=1$ or $N=3$ sectors: By translating the Anderson molecule suitably, we have recovered the correct spectrum in all sectors.
-% \\\\
-% The claim made in a previous section was that this Hamiltonian is very close to a similarity transformed Hubbard Hamiltonian:
-% \begin{equation}\begin{aligned}
-% 	\tilde{H} = \frac{2}{Nw}\sum_{\left<ij \right>} H^D(i,j,t^D, U^D) \equiv  \mathcal{U} H^H  \mathcal{U}^{-1}~,
-% \end{aligned}\end{equation}
-% where $\mathcal{U}$ is in general distinct from the unitary transformation that completes the URG starting from the bare cluster+bath Anderson model up to the fixed-point Hamiltonian.
-As shown earlier, $U$ transformation that involves three steps: the URG transformations $\mathcal{U}_A$, the extracting of the zero mode $Z$ and the tiling procedure outline in this section, $T$
-% \begin{equation}\begin{aligned}
-% 	\mathcal{U} = T Z \mathcal{U}_{A}~.
-% \end{aligned}\end{equation}
 With some knowledge of the RG procedure, one can even write down the relation between the Hubbard dimer couplings $t^D, U^D$ and the parent Hubbard model parameters $t^H, U^H$.
@@
 \subsection{Expressing matrix elements of the inverse single particle Greens function in terms of Hubbard dimer counterparts}
-%If the groundstate wavefunction of $H^H$ is $\ket{0}$, then the groundstate wavefunction of $\tilde H$ is $\ket{\tilde 0} =  \mathcal{U}\ket{0}$.
-The advantage of $\tilde H$ being connected to $H^H$ through unitary (or atleast similarity) transformations is that they will have the same single-particle Greens functions
-%\begin{equation}\begin{aligned}
-%	\left(G_H\right)^\sigma_{\nu \nu^\prime}(t) \equiv -i\theta(t)\bra{0}\left\{c_{\nu},c^\dagger_{\nu^\prime} \right\}\ket{0} &= -i\theta(t)\bra{0} \mathcal{U}^{-1}\left\{  \mathcal{U} c_{\nu}  \mathcal{U}^{-1}  \mathcal{U} c^\dagger_{\nu^\prime}  \mathcal{U}^{-1} +  \mathcal{U} c^\dagger_{\nu^\prime}  \mathcal{U}^{-1}  \mathcal{U} c_{\nu}  \mathcal{U}^{-1}\right\} \mathcal{U}\ket{0}\\
-%															&=-i\theta(t)\bra{\tilde 0}\left\{\tilde c_{\nu} \tilde c^\dagger_{\nu^\prime} + \tilde c^\dagger_{\nu^\prime} \tilde c_{\nu} \right\}\ket{\tilde 0}\\
-%															&= \left(\tilde G\right)_{\tilde {\nu} \tilde {\nu^\prime}}(t)~.
-%\end{aligned}\end{equation}
-%This says that the Greens function $G_H$ of the bare Hubbard model $H^H$ for propagation of excitations (on top of its ground state $\ket{0}$) starting from $\ket{\nu^\prime} \equiv c^\dagger_{\nu^\prime}\ket{0}$ and ending at $\ket{\nu} \equiv c^\dagger_{\nu}\ket{0}$ is exactly equal to the Greens function $\tilde G$ of the renormalised Hamiltonian $\tilde H$ for propagation of the renormalised excitations (on top of its renormalised ground state $\ket{\tilde 0} =  \mathcal{U} \ket{0}$) starting from $\ket{\tilde {\nu^\prime}} \equiv \tilde c^\dagger_{\nu^\prime}\ket{\tilde 0} \equiv  \left(\mathcal{U} c^\dagger_{\nu^\prime}  \mathcal{U}^{-1}\right)  \mathcal{U}\ket{0} =  \mathcal{U}\ket{{\nu^\prime}}$ and ending at $\ket{\tilde \nu} \equiv \tilde c^\dagger_{\nu}\ket{\tilde 0}$.
-This means,
-%\begin{equation}\begin{aligned}
-%	\bra{\nu}G_H\ket{{\nu^\prime}} = \bra{\tilde {\nu}}\tilde G\ket{\tilde {\nu^\prime}}
-%\end{aligned}\end{equation}
 Since the two Hamiltonians $H^H$ and $\tilde H$ are connected via a similarity transformation $\mathcal{U}$, their ground states are also connected by the same transformation.
@@
 \end{aligned}\end{equation}
-%\textit{It has been assumed that the Hamiltonians have been normal ordered such that the ground state energy is 0.} Then, these are the same operators that appear in the appendix.
 These are the same operators that appear in the appendix.
@@
 Each term will be a real space local Greens function, and because of translational invariance, it will be the same for all choices of the nearest neighbour of \(\tilde i\).
-%So we will represent the real space local inverse Greens function as $\left[\mathcal{G}_D^{-1}(\omega)\right]_{00}^{\sigma}$.
-% \begin{gather}
-% 	\label{local_gf}
-% 	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00}\times w = \frac{2}{N}\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00} \equiv g_0\\
-% 	\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{00} = \bra{\Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{\Phi_0}
-% \end{gather}
 \begin{gather}
@@
 \begin{equation}\begin{aligned}
-	c^\dagger_{0\sigma}\ket{\tilde \Phi_0} = \sum_n C^0_n \ket{n}, && c^\dagger_{1\sigma}\ket{\tilde \Phi_0} = \sum_n C^1_n \ket{n}%\sum_{m,\alpha,\beta} C^i_{m,\alpha,\beta} \ket{m,\alpha,\beta}
+	c^\dagger_{0\sigma}\ket{\tilde \Phi_0} = \sum_n C^0_n \ket{n}, && c^\dagger_{1\sigma}\ket{\tilde \Phi_0} = \sum_n C^1_n \ket{n}
 \end{aligned}\end{equation}
@@
 In light of the Greens function we have in between te states, we choose the orthogonal set to be formed by the eigenstates of the dimer+bath Hamiltonian.
-% One simple way of choosing the orthogonal basis $\left\{ \ket{n} \right\}$ is to take them from the eigenstates of a system comprising a Hubbard dimer and a conduction bath, decoupled from each other.
-The dimer will of course have 2 sites, which means the conduction bath will have $N-2$ sites, or $N-2$ momentum states.
-The set of eigenstates that have the total number of particles (combining the dimer and the bath) equal to $N+1$ will then form the basis in question.
-Since the dimer is decoupled from the bath, the total wavefunction will be a direct product of a Hubbard dimer wavefunction and a bath wavefunction.
-% \begin{equation}\begin{aligned}
-% 	\ket{m,\alpha,\beta} = \Phi^D_{m,\alpha} \otimes \Psi^B_{N-m+1, \beta}
-% \end{aligned}\end{equation}
-% $\alpha$ is an internal quantum number of the Hubbard dimer while $\beta$ is that for the bath.
-The subscripts $m$ and $N-m+1$ label the total number of particles in each part of the wavefunction.
-These two labels have to add to $N+1$.
-Our choice of the $\ket{n}$ is motivated by noting that the effective auxiliary model we are invoking here is that of a Hubbard dimer connected to a bath via single-particle hybridisation; the eigenstates of the isolated dimer and bath subsystems then act as the natural choices of the orthogonal bases in which to expand the wavefunction for the single-particle excitation of the interacting system $c^\dagger_{0\sigma}\ket{\tilde \Phi_0}$.
-Further, while the eigenstates ($\Phi^D_{m,\alpha}$) of the Hubbard dimer are known analytically, we can safely assume the eigenstates of the bath ($\Psi^B_{N-m+1, \beta}$) to be a simple direct product of various single-particle Fock states in $k$-space.
-We then compute the matrix element of eq.\eqref{local_gf} for site $i$ and its immediate neighbours (i.e., a given realisation of a auxiliary model).
-Then, using translation invariance, we demand that this matrix element is independent of the site index $i$.
-The correctness of this auxiliary model approach hinges on how close the state $\ket{\tilde{\Phi_0}}$ is to the 2-site local nature of the exact ground state of the target model (here the Hubbard model on a given lattice).
-Further improvement can be made by improving (i) the state $\ket{\tilde{\Phi_0}}$ for the present auxiliary model (involving a Hubbard dimer), or (ii) choosing a better auxiliary model with an ``impurity" system that has more sites than two (i.e., a Bethe-Peierls improvement of the dimer auxiliary model).
-% \\\\
+
 Using this expansion, the matrix element of $\mathcal{G}$ can be written as
@@
 \left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\bra{\tilde \Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{1\sigma}\ket{\tilde \Phi_0} = \frac{2}{Nw}\sum_{n} \left(C^0_{n}\right)^* C^1_{n} \left(\mathcal{G}_{D}^{-1}(\omega)\right)_{nn}
-%\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\left[\mathcal{G}_{D}^{-1}(\omega)\right]_{01}^\sigma \equiv g_1\\
-	%\left[\mathcal{G}_{D}^{-1}(\omega)\right]^\sigma_{01} = \bra{\Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{1\sigma}\ket{\Phi_0}
 \end{gather}
@@
 
-% \begin{equation}\begin{aligned}
-% 	\label{hole_gf}
-% 	&\left(\mathcal{G}_{H}^{-1}(-\omega)\right)_{\overline{ii}}^\sigma = \frac{2}{N}\left[\mathcal{G}_{D}^{-1}(-\omega)\right]^\sigma_{\overline{00}} \equiv \overline{g_0}, &&&\left[\mathcal{G}_{D}^{-1}(-\omega)\right]^\sigma_{\overline{00}} = \bra{0}c^\dagger_{0\sigma}\mathcal{G}_{D}^{-1}(-\omega)c_{0\sigma}\ket{0}\\
-% 	&\left(\mathcal{G}_{H}^{-1}(-\omega)\right)_{\overline{ij}}^\sigma = \frac{2}{Nw}\left[\mathcal{G}_{D}^{-1}(-\omega)\right]_{\overline{01}}^\sigma \equiv \overline{g_1}, &&&\left[\mathcal{G}_{D}^{-1}(-\omega)\right]^\sigma_{\overline{01}} = \bra{0}c^\dagger_{0\sigma}\mathcal{G}_{D}^{-1}(-\omega)c_{1\sigma}\ket{0}
-% \end{aligned}\end{equation}
-
 \subsection{Constructing full Greens function matrix from the inverse matrix}
@@
 
-% Since the only real-space interaction is that between the nearest neighbours, there are no further real space Greens functions.
-Because of translational invariance, we know that $\left(\mathcal{G}_H^{-1}\right)_{ii}$ and $\left(\mathcal{G}_H^{-1}\right)_{ij}$ are independent of $i,j$.
-Furthermore, all expressions below are for a particular spin $\sigma$; from the spin rotational symmetry of the Hubbard Hamiltonian, the same expressions are obtained for the opposite spin.
-We will now recreate the entire matrix $\mathcal{G_H}^{-1}$ using the matrix elements we calculated previously.
-Since the two sets $\left\{ \ket{i\sigma} \right\}$ and $\left\{ \ket{\overline{i\sigma}}\right\}$ are orthogonal, we will create separate matrix for the two sets.
-% \begin{equation}\begin{aligned}
-% 	\mathcal{G}^{-1}_H(\omega) = \begin{pmatrix} \left(\mathcal{G}^{-1}\right)_{00} & \left(\mathcal{G}^{-1}\right)_{01} & ... & ... & \left(\mathcal{G}^{-1}\right)_{0N}\\
-% 		\left(\mathcal{G}^{-1}\right)_{10} & \left(\mathcal{G}^{-1}\right)_{11} & \left(\mathcal{G}^{-1}\right)_{12} & ... & ...\\
-% 		... & \left(\mathcal{G}^{-1}\right)_{21} & \left(\mathcal{G}^{-1}\right)_{22} & \left(\mathcal{G}^{-1}\right)_{23} & ... \\
-% 		    &&.&&\\
-% \end{pmatrix} = \begin{pmatrix} g_0 & g_1 & ... & ... & g_1\\
-% 		g_1 & g_0 & g_1 & ... & ...\\
-% 		... & g_1 & g_0 & g_1 & ... \\
-% 		    &&...&&\\
-% \end{pmatrix}\\
-% 		\overline{\mathcal{G}^{-1}_H}(-\omega) = \begin{pmatrix} \left(\mathcal{G}^{-1}\right)_{\overline{00}} & \left(\mathcal{G}^{-1}\right)_{\overline{01}} & ...
-& ...
-& \left(\mathcal{G}^{-1}\right)_{\overline{0N}}\\
-% 			\left(\mathcal{G}^{-1}\right)_{\overline{10}} & \left(\mathcal{G}^{-1}\right)_{\overline{11}} & \left(\mathcal{G}^{-1}\right)_{\overline{12}} & ... & ...\\
-% 			... & \left(\mathcal{G}^{-1}\right)_{\overline{21}} & \left(\mathcal{G}^{-1}\right)_{\overline{22}} & \left(\mathcal{G}^{-1}\right)_{\overline{23}} & ... \\
-% 		    &&.&&\\
-% 			\end{pmatrix} = \begin{pmatrix} \overline{g_0} & \overline{g_1} & ... & ... & \overline{g_1}\\
-% 			\overline{g_1} & \overline{g_0} & \overline{g_1} & ... & ...\\
-% 			... & \overline{g_1} & \overline{g_0} & \overline{g_1} & ... \\
-% 		    &&...&&\\
-% \end{pmatrix} 
-% \end{aligned}\end{equation}
-% Both the matrices can be written in the operator form of a tight-binding Hamiltonian:
-% \begin{equation}\begin{aligned}
-% 	\mathcal{G}_H^{-1}(\omega) = g_0\sum_{i=1}^N\ket{i}\bra{i} + g_1\sum_{\left<i,j \right>}^N\left( \ket{i}\bra{j} + \text{h.c.}\right)\\
-% 	\overline{\mathcal{G}_H^{-1}}(-\omega) = \overline{g_0}\sum_{\overline i=1}^N\ket{\overline i}\bra{\overline i} + \overline{g_1}\sum_{\left<\overline i,\overline j \right>}^N\left( \ket{\overline i}\bra{\overline j} + \text{h.c.}\right)
-% \end{aligned}\end{equation}
-% We can Fourier transform the real space kets $\ket{i} \equiv \ket{\vec r_i}$ into momentum space:
-% \begin{flalign*}
-% 	\ket{\vec r_i} &\equiv c^\dagger_{\vec r_i\sigma}\ket{0} = \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}c^\dagger_{k\sigma}\ket{0} \equiv \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\vec k} \Leftrightarrow \ket{k} = \frac{1}{\sqrt N}\sum_{\vec i} e^{-i \vec{k}\cdot\vec{r_i}}\ket{\vec r_i} \\
-% 	\ket{\overline{\vec r_i}} &\equiv c_{\vec r_i\sigma}\ket{0} = \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}c_{k\sigma}\ket{0} \equiv \frac{1}{\sqrt N}\sum_{\vec k=\vec k_1}^{\vec k_N} e^{i \vec{k}\cdot\vec{r_i}}\ket{\overline{\vec k}} \Leftrightarrow \ket{\overline{\vec k}} = \frac{1}{\sqrt N}\sum_{\vec i} e^{-i \vec{k}\cdot\vec{r_i}}\ket{\overline{\vec r_i}}
-% \end{flalign*}
-% We will now Fourier transform the matrix $\mathcal{G}_H^{-1}(\omega)$ to momentum space. In doing so, we will diagonalize the matrix.
-% \begin{flalign*}
-% 	\sum_i \ket{i}\bra{i} &= \frac{1}{N}\sum_i \sum_{\vec k, \vec q} e^{i \left(\vec{k} - \vec q\right)\cdot\vec{r_i}}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\sum_{\vec k, \vec q} N \delta\left(\vec{k} - \vec q\right)\ket{\vec k}\bra{\vec q} = \sum_{\vec k=\vec k_1}^{\vec k_N} \ket{\vec k}\bra{\vec k}\\
-% 	\sum_{\left<i,j \right>} \ket{i}\bra{j} &= \frac{1}{N}\sum_{\left<i,j \right>} \sum_{\vec k, \vec q} e^{i \left(\vec{k}\cdot \vec r_i - \vec q\cdot \vec r_j\right)}\ket{\vec k}\bra{\vec q} = \frac{1}{N}\frac{1}{2}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec k, \vec q} e^{-i\vec q\cdot a_i\hat e_i}\ket{\vec k}\bra{\vec q}\sum_{i=1}^N e^{i \left(\vec{k} - \vec q\right)\cdot \vec r_i} & \left[\sum_{\left<i,j \right>} = \frac{1}{2}\sum_i \sum_{j \in \text{NN of i}}\right] \\
-% 					&=\frac{1}{2}\sum_{\hat e_i = \hat e_1}^{\hat e_D}\sum_{\vec q} e^{-i\vec q\cdot \vec e_i}\ket{\vec q}\bra{\vec q} = \frac{1}{2}\sum_{\vec q} \left(\sum_{i_1}^{D}e^{-ia_iq_i}\right)\ket{\vec q}\bra{\vec q}
-% \end{flalign*}
-% $\hat e_i$ are the primitive lattice unit vectors for the general $d-$dimensional lattice.
-$q_i$ are the projections of $\vec q$ along those vectors.
-$a_i$ are the lattice spacings along each primitive vector.
-Adding the Hermitian conjugate simply extracts the real part:
-% \begin{equation}\begin{aligned}
-% 	\sum_{\left<i,j \right>} \ket{i}\bra{j} + \text{h.c.} =\sum_{\vec q} \underbrace{\sum_{i_1}^{D}\cos\left(a_iq_i\right)}_{\equiv \xi_{\vec q}}\ket{\vec q}\bra{\vec q}
-% \end{aligned}\end{equation}
-% On a 2D square lattice, for instance, we obtain
-% \begin{eqnarray}
-% \xi_{\vec{q}} &=& 2(\cos q_{x}a_{x} + \cos q_{y}a_{y})\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
-% \epsilon_{\vec{q}} &=& -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})~.\label{2dsquaretb}
-% \end{eqnarray}
-% The inverse Greens function thus becomes diagonal in momentum space
-% \begin{equation}\begin{aligned}
-% 	\mathcal{G}_H^{-1}(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)\ket{\vec k}\bra{\vec k} = \begin{pmatrix} g_0 + g_1\xi_{\vec k_1} &&& \\
-% 	& g_0 + g_1\xi_{\vec k_2} && \\
-% 	&& g_0 + g_1\xi_{\vec k_3} & \\
-% 	...&...&...&\\
-% 	\end{pmatrix} 
-% \end{aligned}\end{equation}
-% The matrix entries are written in momentum space, and the matrix is diagonal in this basis. The other matrix can also be diagonalized similarly:
-% \begin{equation}\begin{aligned}
-% 	\overline{\mathcal{G}_H^{-1}}(-\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)\ket{\overline{\vec k}}\bra{\overline{\vec k}} = \begin{pmatrix} \overline{g_0} + \overline{g_1}\xi_{\vec k_1} &&& \\
-% 	& \overline{g_0} + \overline{g_1}\xi_{\vec k_2} && \\
-% 	&& \overline{g_0} + \overline{g_1}\xi_{\vec k_3} & \\
-% 	...&...&...&\\
-% 	\end{pmatrix} 
-% \end{aligned}\end{equation}
-
 \subsection{Calculation of self energy matrix from the Dyson equation}
-% Using Dyson's equation for the self-energy $\Sigma = G_{0}^{-1} - G^{-1}$ (where the matrix $G_{0,H}^{-1} (\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N} (\omega -\epsilon_{k})\ket{\vec k}\bra{\vec k}=\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega +t^{H}\xi_{k})\ket{\vec k}\bra{\vec k} $ is the inverse Greens function for the appropriate non-interacting tight-binding system), we obtain the self-energy matrix as
-% \begin{eqnarray}
-% \Sigma_{H} (\omega) &=& G_{0,H}^{-1} - G_{H}^{-1}~,\nonumber\\
-% &=&\sum_{\vec k=\vec k_1}^{\vec k_N} (\omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}})\ket{\vec k}\bra{\vec k}
-% \end{eqnarray}
-% This is the full self energy matrix. One can get both real space and momentum space self energies by taking appropriate matrix elements. For instance, the self-energy in momentum space is
-% \begin{equation}\begin{aligned}
-% 	\label{selfenergy}
-% 	\Sigma_{H} (\vec{k},\omega) \equiv \bra{\vec k} \Sigma_H (\omega) \ket{\vec k} = \omega - g_{0} + (t^{H} - g_{1})\xi_{\vec{k}}~.
-% \end{aligned}\end{equation}
 With the knowledge of the momentum-space Greens function $G_H(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
@@
 Thus, we can use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
-% \subsection{Obtaining real space Greens functions from the full matrix}
-% Since ${\mathcal{G}_H^{-1}}(\omega)$ and $\overline{\mathcal{G}_H^{-1}}(\omega)$ are diagonal in momentum space, we can invert these matrices trivially by replacing the diagonal elements with their reciprocals.
-% \begin{equation}\begin{aligned}
-% 	\label{k-space-gf}
-% 	\mathcal{G}_H(\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\ket{\vec k}\bra{\vec k} = \begin{pmatrix} \left(g_0 + g_1\xi_{\vec k_1}\right)^{-1} &&&&\\
-% 	& \left(g_0 + g_1\xi_{\vec k_2}\right)^{-1} &&&\\
-% 	&& \left(g_0 + g_1\xi_{\vec k_3}\right)^{-1} &&\\
-% 		...&&&...&\\
-% 	\end{pmatrix} \\
-% 		\overline{\mathcal{G}_H}(-\omega) = \sum_{\vec k=\vec k_1}^{\vec k_N}\left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\ket{\overline{\vec k}}\bra{\overline{\vec k}} = \begin{pmatrix} \left(\overline{g_0} + \overline{g_1}\xi_{\vec k_1}\right)^{-1} &&&&\\
-% 	& \left(\overline{g_0} + \overline{g_1}\xi_{\vec k_2}\right)^{-1} &&&\\
-% 	&& \left(\overline{g_0} + \overline{g_1}\xi_{\vec k_3}\right)^{-1} &&\\
-% 		...&&&...&\\
-% 	\end{pmatrix} 
-% \end{aligned}\end{equation}
-% The diagonal elements of $\mathcal{G}_H$ in momentum space are:
-% \begin{equation}\begin{aligned}
-% 	\mathcal{G}(\omega, H^H)_{\vec k, \vec k} &= \left(g_0 + g_1 \xi_{\vec k}\right)^{-1}\\
-% 			    &= \left\{\frac{2}{N}\left[G_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{2}{Nw}\left[G_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}\\
-% 			    &= \frac{N}{2}\left\{\left[\mathcal{G}_{D}^{-1}(\omega)\right]_{00\sigma} + \frac{1}{w}\left[\mathcal{G}_{D}^{-1}(\omega)\right]_{01\sigma}\xi_{\vec k}\right\}^{-1}\\
-% 	\mathcal{G}(-\omega, H^H)_{\overline{\vec k}, \overline{\vec k}} &= \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\\
-% 									&= \frac{N}{2}\left\{\left[\mathcal{G}_{D}^{-1}(-\omega)\right]_{\overline{00}\sigma} + \frac{1}{w}\left[\mathcal{G}_{D}^{-1}(-\omega)\right]_{\overline{01}\sigma}\xi_{\vec k}\right\}^{-1}\\
-% \end{aligned}\end{equation}
-% \textit{The single-particle momentum space Greens function can now be written down}, following eq.~\ref{G_mat_el}:
-% \begin{equation}\begin{aligned}
-% 	\label{k_Gf}
-% 	G_H(\vec k, \omega) = \mathcal{G}(\omega, H^H)_{\vec k, \vec k} - \mathcal{G}(-\omega, H^H)_{\overline{\vec k}, \overline{\vec k}} = \left(g_0 + g_1 \xi_{\vec k}\right)^{-1} - \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}
-% \end{aligned}\end{equation}
-% The real-space Greens functions can now be obtained by Fourier transforming $G_H(\vec k, \omega)$:
-% \begin{equation}\begin{aligned}
-% 	G_H(\vec r_i - \vec  r_j, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega)  e^{\vec{k}\cdot\left(\vec r_j - \vec{r_i}\right)} \equiv G_H(\vec r_j - \vec  r_i, \omega)
-% \end{aligned}\end{equation}
-% The Greens function for excitations between \(\vec r_i\) and \(\vec r_j\) depends only on the relative position \(\vec r_j - \vec r_i\), not on their absolute positions.
-This is expected on grounds of translational invariance.
-By choosing \(\vec r_i = \vec r_j\), we can obtain the real space \textit{local} Greens function:
-% \begin{equation}\begin{aligned}
-% 	\left(G_H\right)_{ii}(\omega) \equiv G_H(\vec r_j - \vec  r_i = 0, \omega) = \frac{1}{N}\sum_{\vec k} G_H(\vec k, \omega) = \frac{1}{N}\sum_{\vec k}\left(\frac{1}{g_0 + g_1 \xi_{\vec k}} - \frac{1}{\overline{g_0} + \overline{g_1} \xi_{\vec k}}\right)
-% \end{aligned}\end{equation}
-% We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
-% \begin{equation}\begin{aligned}
-% A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{1}{\pi} \textrm{Im}\left[\left(g_0 + g_1 \xi_{\vec k}\right)^{-1} - \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\right]\\
-% A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = -\frac{1}{N\pi} \textrm{Im}\sum_{\vec{k}}\left[\left(g_0 + g_1 \xi_{\vec k}\right)^{-1} - \left(\overline{g_0} + \overline{g_1} \xi_{\vec k}\right)^{-1}\right] = \frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
-% \end{aligned}\end{equation}
-% We can again use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the spectral functions  $A_{H} (\vec{k},\omega)$ and $A_{H} (\vec{r}=0,\omega)$ for the Hubbard model on the 2D square lattice.
-
-% \section{Some comments on writing down the orthonormal basis $\left\{ \ket{n} \right\}$}
-% As mentioned previously, for a parent model of $N$ sites, the orthonormal basis is constructed out of those eigenstates of a decoupled dimer+bath system that have total number of particles equal to $\mathcal{N}_\text{tot} = \mathcal{N}_\text{dim} + \mathcal{N}_\text{bath} = N+1$.
-The condition on the total number is necessary because that is also the total particile number of the state we are expanding $(c^\dagger_{i\sigma}\ket{\tilde \Phi_0}$.
-The dimer will have 2 sites, while the rest $N-2$ sites go into the bath.
-% \\\\
-% If we are solving the trivial example of $H^H = H^D$ (that is, if we take the Hubbard dimer itself as the full Hubbard model that we are trying to solve), the bath is non-existant.
-The entire set of $\ket{n}$ for expanding $c^\dagger_{i\sigma}\ket{\tilde \Phi_0}$ is then made up by the $\mathcal{N} = N + 1 = 3, S^z = \frac{1}{2}\sigma$ eigenstates of $H^D$.
-There are two of those; these two make up the entire orthonormal basis in which we can expand the single-particle excitaions:
-% \begin{equation}\begin{aligned}
-% 	\left\{ \ket{n} \right\} = \ket{3 \pm \sigma}
-% \end{aligned}\end{equation}
-% Similarly, for expanding the hole excitaions $c_{i\sigma}\ket{\tilde \Phi_0}$, we will instead choose the $\mathcal{N} = N - 1 = 1, S^z = -\frac{1}{2}\sigma$ eigenstates of $H^D$.
-There are again two of those:
-% \begin{equation}\begin{aligned}
-% 	\left\{ \ket{\overline n} \right\} = \ket{1 \pm -\sigma}
-% \end{aligned}\end{equation}
-% \\\\
-% For a more general $N(>2)$-site model, there will be a bath of $N-2$ momentum states.
-These momentum states are labelled as $k_1, k_2, ..., k_{N-2}$.
-Let us designate the set of eigenstates of the Hubbard dimer as \(\left\{ \ket{\Phi^D_i} \right\} \) and those of the bath as \(\left\{ \ket{\Psi^B_{j, \nu^j}} \right\} \).
-Since the bath is non-interacting, those eigenstates can be written down easily:
-% \begin{equation}\begin{aligned}
-% 	\left\{ \ket{\Psi^B_{j, \nu^j}} \right\} = \begin{cases} &  j \in [0, 2N-4]\\[-10pt]
-% 	\otimes_{i=1}^j\hat n_{\nu^j_i} = 1:\\[-10pt]
-% & \nu^j \in \text{all subsets of length $j$ of the set $\left[k_1 \uparrow, k_1 \downarrow, k_2 \uparrow, ..., k_{N-2} \uparrow, k_{N-2} \downarrow\right]$} \end{cases}
-% \end{aligned}\end{equation}
-% $j$ defines the number of occupied states in a particular eigenstate of the conduction bath.
-The string $\nu^j$ runs over all possible set of quantum numbers of a particular length $j$.
-For example, if we have 3 momentum states in the bath $k_1, k_2, k_3$, then $\nu^2$ would take the values
-% \begin{equation}\begin{aligned}
-% 	\left\{\nu^2\right\} = \left(k_1 \uparrow, k_1 \downarrow\right),\left(k_1 \uparrow, k_2 \uparrow\right),\left(k_1 \uparrow, k_2 \downarrow\right),\left(k_1 \uparrow, k_3 \uparrow\right),\left(k_1 \uparrow, k_3 \downarrow\right),\left(k_1 \downarrow, k_2 \uparrow\right),\left(k_1 \downarrow, k_2 \downarrow\right),\\
-% 	\left(k_1 \downarrow, k_3 \uparrow\right),\left(k_1 \downarrow, k_3 \downarrow\right),\left(k_2 \uparrow, k_2 \downarrow\right),\left(k_2 \uparrow, k_3 \uparrow\right),\left(k_2 \uparrow, k_3 \downarrow\right),\left(k_2 \downarrow, k_3 \uparrow\right),\left(k_2 \downarrow, k_3 \downarrow\right),\\
-% \left(k_3 \uparrow, k_3 \downarrow\right)
-% \end{aligned}\end{equation}
-% The $j=0$ case means the bath is empty.
-% The general complete set of orthonormal kets is given by
-% \begin{equation}\begin{aligned}
-% 	\left\{ \ket{n} \right\} = \sum_{i=1}^{16}\sum_{j=0}^{N-2}\sum_{\nu^j}\ket{\Phi^D_i}\otimes \ket{\Psi^B_{j, \nu^j}}
-% \end{aligned}\end{equation}
-% The first twp sums are unconstrained.
-The index $i$ runs through all 16 eigenstates of the Hubbard dimer, the index $j$ runs through all the possible total number of particles the eigenstate of the bath can have.
-For each value of $j$, the string $\nu^j$ runs through all possible combinations of length $j$ from the complete set of quantum numbers $\left\{ k\sigma \right\} $.
 
@@
 
-% We will now calculate the matrix elements $g_0$ and $g_1$ from the Hubbard dimer Hamiltonian. Those two parameters are defined as
-% \begin{equation}\begin{aligned}
-% 	g_0 \equiv \frac{2}{N}\bra{\text{GS}}c_{0\uparrow}\left(\omega + E_\text{GS} - H^D\right)c^\dagger_{0\uparrow}\ket{\text{GS}}\\
-% 	g_1 \equiv \frac{2}{N}\bra{\text{GS}}c_{0\uparrow}\left(\omega + E_\text{GS} - H^D\right)c^\dagger_{1\uparrow}\ket{\text{GS}}\\
-% \end{aligned}\end{equation}
-% As a shorthand notation, we will use $\ket{0 \sigma} \equiv c^\dagger_{0\uparrow}\ket{\text{GS}}$.
-The matrix whose elements we want to calculate, $\omega + E_\text{GS} - H^D$, can be written as a diagonal matrix in the basis formed by the eigenstates in $N=3, S^z= \frac{1}{2}$ as defined in table \ref{hubb_dim_spectrum}:
-% \begin{equation}\begin{aligned}
-% 	\ket{\pm} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{\pm} = E_\pm \ket{\pm}
-% \end{aligned}\end{equation}
-% In the basis of $\ket{\pm}$, we can write
-% \begin{equation}\begin{aligned}
-% 	\omega + E_\text{GS} - H^D &= \begin{pmatrix} \omega + E_\text{GS} - E_+ & 0 \\ 0 & \omega + E_\text{GS} - E_- \end{pmatrix}\\
-% 				   &= \left(\omega + E_\text{GS} - E_+\right) \ket{+}\bra{+} + \left(\omega + E_\text{GS} - E_-\right) \ket{-}\bra{-}
-% \end{aligned}\end{equation}
-% The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates. As shown in the appendix, we can write
-% \begin{equation}\begin{aligned}
-% 	\ket{0 \uparrow} \equiv c^\dagger_{0\uparrow}\ket{\text{GS}} =x\ket{+} + y\ket{-}, && \ket{1 \uparrow} \equiv c^\dagger_{1\uparrow}\ket{\text{GS}} = x\ket{+} - y\ket{-}
-% \end{aligned}\end{equation}
-% with $x = \frac{a_2 - a_1}{2}, y=\frac{a_2 + a_1}{2}$. We can therefore express $\ket{\pm}$ in terms $\ket{0,1\uparrow}$:
-% \begin{equation}\begin{aligned}
-% 	\ket{+} = \frac{1}{2x}\left(\ket{0 \uparrow} + \ket{1 \uparrow}\right), && \ket{-} = \frac{1}{2y}\left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)
-% \end{aligned}\end{equation}
-% Substituting these into the operator form of $\omega + E_\text{GS} - H^D$ gives
-% \begin{equation}\begin{aligned}
-% 	\omega + E_\text{GS} - H^D =& \frac{1}{4x^2}\left(\omega + E_\text{GS} - E_+\right) \left(\ket{0 \uparrow} + \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} + \bra{1 \uparrow}\right) \\
-% 				   &+ \frac{1}{4y^2}\left(\omega + E_\text{GS} - E_-\right) \left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} - \bra{1 \uparrow}\right)\\
-% =& \begin{pmatrix}\left(\frac{1}{4x^2} + \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ - \frac{1}{4y^2}E_- & \left(\frac{1}{4x^2} - \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ + \frac{1}{4y^2}E_- \\ \left(\frac{1}{4x^2} - \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ + \frac{1}{4y^2}E_- & \left(\frac{1}{4x^2} + \frac{1}{4y^2}\right) \left(\omega + E_\text{GS}\right) - \frac{1}{4x^2}E_+ - \frac{1}{4y^2}E_-\end{pmatrix}
-% \end{aligned}\end{equation}
-% Now we will Fourier transform to the diagonal momentum space: $\ket{0 \sigma} = \frac{1}{\sqrt 2}\left(\ket{{k_0} \sigma} + \ket{k_\pi \sigma} \right), \ket{1 \sigma} = \frac{1}{\sqrt 2}\left(\ket{{k_0} \sigma} - \ket{k_\pi \sigma} \right)$.
-% \begin{equation}\begin{aligned}
-% 	\left(\ket{0 \uparrow} + \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} + \bra{1 \uparrow}\right) = 2\ket{k_0 \uparrow}\bra{k_0 \uparrow}\\
-% 	\left(\ket{0 \uparrow} - \ket{1 \uparrow}\right)\left(\bra{0 \uparrow} - \bra{1 \uparrow}\right) = 2\ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
-% \end{aligned}\end{equation}
-% This transformation can be substituted in the operator expansion:
-% \begin{equation}\begin{aligned}
-% 	\omega + E_\text{GS} - H^D =& \frac{1}{2x^2}\left(\omega + E_\text{GS} - E_+\right) \ket{k_0 \uparrow}\bra{k_0 \uparrow} + \frac{1}{2y^2}\left(\omega + E_\text{GS} - E_-\right) \ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
-% \end{aligned}\end{equation}
-% This can be easily inverted:
-% \begin{equation}\begin{aligned}
-% 	\frac{1}{\omega + E_\text{GS} - H^D} =& \frac{2x^2}{\omega + E_\text{GS} - E_+}\ket{k_0 \uparrow}\bra{k_0 \uparrow} + \frac{2y^2}{\omega + E_\text{GS} - E_-} \ket{k_\pi \uparrow}\bra{k_\pi \uparrow}\\
-% \end{aligned}\end{equation}
-% Since this is already in the momentum space basis, we can write
-% \begin{equation}\begin{aligned}
-% 	\left(\frac{1}{\omega + E_\text{GS} - H^D}\right)_{k_0 k_0} = \frac{2x^2}{\omega + E_\text{GS} - E_+}\ket{k_0 \uparrow}
-% \end{aligned}\end{equation}
-% Performing a similar calculation for the hole excitations will give
-% \begin{equation}\begin{aligned}
-% 	\frac{1}{-\omega + E_\text{GS} - H^D} =& \frac{2y^2}{-\omega + E_\text{GS} - \overline{E_+}}\ket{\overline{k_0 \uparrow}}\bra{\overline{k_0 \uparrow}} + \frac{2x^2}{-\omega + E_\text{GS} - \overline{E_-}} \ket{\overline{k_\pi \uparrow}}\bra{\overline{k_\pi \uparrow}}\\
-% \end{aligned}\end{equation}
-% where $\ket{\overline{\nu}} \equiv c_\nu \ket{\text{GS}}$ and $\overline{E_\pm}$ are the eigenenergies of the $N=1, S^z = \frac{1}{2}$ sector eigenstates.
-From the spectrum, we know that $E_\pm = -\overline{E_\pm}$.\\\\
-% Combining these two, we can obtain the $k=0$ Greens function of the Hubbard dimer:
-% \begin{equation}\begin{aligned}
-% 	G(k=0, \uparrow) &= \left(\frac{1}{\omega + E_\text{GS} - H^D}\right)_{k_0 k_0} - \left(\frac{1}{-\omega + E_\text{GS} - H^D}\right)_{\overline{k_0 k_0}}\\
-% 			 &= \frac{2x^2}{\omega + E_\text{GS} - E_+} - \frac{2y^2}{-\omega + E_\text{GS} - \overline{E_+}}\\
-% 			 &= \frac{2x^2}{\omega + E_\text{GS} - E_+} + \frac{2y^2}{\omega - E_\text{GS} - E_+}\\
-% \end{aligned}\end{equation}
-% From the definitions of $x$ and $y$, we get $2x^2 = \frac{a_1^2 + a_2^2 - 2a_1 a_2}{2} = \frac{1}{2} - \frac{2t}{\Delta}$ and $2y^2 = \frac{1}{2} + \frac{2t}{\Delta}$.
-Also, the ground state energy is $E_\text{GS} = -\frac{\Delta}{2}$ and the excited energy $E_+$ is $t$.
-Substituting these gives
-% \begin{equation}\begin{aligned}
-% 	G(k=0, \uparrow) &= \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} + \frac{\frac{1}{2} + \frac{2t}{\Delta}}{\omega + \frac{\Delta}{2} - t}\\
-% \end{aligned}\end{equation}
-
-% from the Greens function matrices of the Hubbard dimer. From the spectral representation of the Greens function matrix elements in eq.~\ref{G_mat_spec}, we obtain
-% \begin{equation}\begin{aligned}
-% 	\left(\mathcal{G}_D\right)_{\nu \nu^\prime} = \begin{pmatrix} x_- + y_- && x_- - y_- \\ x_- - y_- && x_- + y_- \end{pmatrix}
-% \end{aligned}\end{equation}
-% where
-% \begin{equation}\begin{aligned}
-% 	x_\pm \equiv \left( \frac{1}{4} \pm \frac{t}{\Delta} \right) \frac{1}{\mp\omega - \frac{\Delta}{2} \pm t}, && y_\pm \equiv \left( \frac{1}{4} \mp \frac{t}{\Delta} \right) \frac{1}{\mp\omega - \frac{\Delta}{2} \mp t}
-% \end{aligned}\end{equation}
-% The matrix is easily inverted:
-% \begin{equation}\begin{aligned}
-% 	\left(\mathcal{G}_D^{-1}\right)_{\nu \nu^\prime}(\omega) = \frac{1}{4}\begin{pmatrix}  \frac{1}{x_-} + \frac{1}{y_-} &&  \frac{1}{x_-} - \frac{1}{y_-} \\  \frac{1}{x_-} - \frac{1}{y_-} &&  \frac{1}{x_-} + \frac{1}{y_-} \end{pmatrix}
-% \end{aligned}\end{equation}
-% $g_0$ and $g_1$ can now be read off:
-% \begin{equation}\begin{aligned}
-% 	g_0 = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{00} = \frac{1}{4}\left( \frac{1}{x_-} + \frac{1}{y_-}\right), && g_1 = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{01} = \frac{1}{4}\left( \frac{1}{x_-} - \frac{1}{y_-}\right)
-% \end{aligned}\end{equation}
-% Similarly, we obtain the other matrix:
-% \begin{equation}\begin{aligned}
-% 	\left(\mathcal{G}_D\right)_{\overline{\nu \nu^\prime}}(-\omega) = \begin{pmatrix} x_+ + y_+ && x_+ - y_+ \\ x_+ - y_+ && x_+ + y_+ \end{pmatrix}
-% \end{aligned}\end{equation}
-% which gives
-% \begin{equation}\begin{aligned}
-% 	\overline{g_0} = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{00} = \frac{1}{4}\left( \frac{1}{x_+} + \frac{1}{y_+}\right), && \overline{g_1} = \frac{2}{N}\left(\mathcal{G}_D^{-1}\right)_{01} = \frac{1}{4}\left( \frac{1}{x_+} - \frac{1}{y_+}\right)
-% \end{aligned}\end{equation}
-% Substituting these values of $g_0, g_1, \overline{g_0}$ and $\overline{g_1}$ in eq.~\ref{Gk_dim} gives the same expression as that obtained in eq.~\ref{Gk0}.
-
-%To verify this result, we just need to show the momentum space Greens function of the Hubbard dimer calculated from the exact eigenstates (as shown in the appendix) also takes the same form.
-Using the Fourier transform, we can write
-%\begin{equation}\begin{aligned}
-%	G(k=0, \sigma) = G(r=0, \sigma) + G(r=a, \sigma)
-%\end{aligned}\end{equation}
-%The terms on the RHS are the real space local and nearest-neighbour Greens functions of the Hubbard dimer.
-%Therefore, the Greens function at $\vec r=0$ for the Hubbard dimer can be expressed as
-%\begin{equation}\begin{aligned}
-%	G_H(\vec r = 0, \omega) = \frac{1}{2}\left[\frac{1}{g_0 + g_1} + \frac{1}{g_0 - g_1}\right]  = \frac{g_0}{g_0^2 - g_1^2}
-%\end{aligned}\end{equation}
-%For the Hubbard dimer, we substitute $N=2, w=1$ into the expressions for $g_{0}$ and $g_{1}$ to obtain
-%\begin{equation}\begin{aligned}
-%	&g_0 = \frac{1}{\text{Det }G_D}\left( G_D \right)_{00}, &g_1 = -\frac{1}{\text{Det }G_D}\left( G_D \right)_{01}
-%\end{aligned}\end{equation}
-%The Greens function at the zeroth site then becomes
-%\begin{equation}\begin{aligned}
-%	G_H(\vec r = 0, \omega) = \text{Det }G_D\frac{\left(G_D\right)_{00}}{\left(G_D\right)_{00}^2 - \left(G_D\right)_{01}^2} = \text{Det }G_D\frac{\left(G_D\right)_{00}}{\text{Det }G_D} = \left(G_D\right)_{00}
-%\end{aligned}\end{equation}
-%This is the expected result.
-Because the full Hubbard model in this case was simply the Hubbard dimer, \(G_H(\vec r = 0, \omega)\) should just be \(\left(G_D\right)_{00}\).
-Although this is a trivial example (we matched the Hubbard dimer with another Hubbard dimer), this atleast tells us that this algorithm for calculating the real space local Greens function from the inverse Greens function matrix elements is sensible.
-
 \subsection{On the Bethe lattice}
@@
 
-\item While we have provided expressions for the single particle Greens functions of the $N$-site Hubbard model from their equivalent single particle Greens functions of the Hubbard dimer, we expect that eq.\eqref{green_eq_final} holds quite generally for the two-particle Greens function sector as well.
+\item While we have provided expressions for the single particle Greens functions of the $N$-site Hubbard model from their equivalent single particle Greens functions of the Hubbard dimer, we expect that eq.\eqref{green_eq_final_siam} holds quite generally for the two-particle Greens function sector as well.
 We will provide these expressions at a later point in time.
@@
 \section*{Spectrum of the Hubbard dimer}
-Here we document the spectrum of the Hamiltonian in eqs.~\ref{hubb_dimer}.
+Here we document the spectrum of the Hubbard dimer Hamiltonian in eqs.~\ref{hubb_dimer}.
 \begin{center}

### 2022-03-10 notes/notes.tex
sir's changes

@@
 
-% The present method intends to calculate the quantities in a different fashion.
+ The present method intends to calculate the quantities in a different fashion.
+We first obtain an auxiliary model ($H_{Cl}$) by choosing a cluster of correlated sites that are hybridised with a bath through one-particle and two-particle exchange terms.
+The bath may additionally have local correlations.
+Then, we carry out a URG analysis of this auxiliary model to obtain a stable fixed point effective Hamiltonian:  $H^{*}_{CL} = \left[\mathcal{U}_{CL} H_{CL} \mathcal{U}_{CL}^\dagger \right]$.
 % We start with a SIAM (with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian.
-% The fixed point Hamiltonian will in general involve the impurity site (with renormalised parameters $\epsilon_d^*, U^*$) interacting with a smaller number of momentum states.
-
+The fixed point Hamiltonian will in general involve the impurity site (with renormalised parameters $\epsilon_d^*, U^*$) interacting with a smaller number of momentum states.
 % At this point, we will assume that we have a Hubbard model in mind that has motivated a correlated SIAM as the auxiliary system, and we have performed renormalisation group analysis on this auxiliary system to get down to an effective Hamiltonian.
@@
 % \end{aligned}\end{equation}
-% \begin{figure}[htpb]
-% 	\centering
-% 	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.png}
-% 	\caption{Correlated asymmetric Anderson molecule schematic version.
-It consists of an impurity site (blue) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink).
+ \begin{figure}[htpb]
+ 	\centering
+ 	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.pdf}
+ 	\caption{Cluster+bath construction of auxiliary model.
+It consists of a cluster (red square) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink).
 The other sites (green) form the rest of the bath.
-Just the impurity site and the zeroth site have onsite repulsion.}
-% 	\label{and_mol}
-% \end{figure}
+Just the cluster and the zeroth site have onsite correlations.}
+ \end{figure}
 % This Hamiltonian is depicted in fig.~\ref{and_mol}.
@@
 % We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice.
-The next step in the programme is to tile the real-space lattice with this dimer+bath Hamiltonian \(\tilde H_D\) to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H = T\left[ \tilde H^{D} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the dimer Hamiltonian to span the target real-space lattice.
-We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.
-% \begin{equation}\begin{aligned}
-% 	\tilde H &= \frac{2}{Nw}\sum_{\left<ij\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\tilde H^D((0,1,z) \to (i, j, l))\\
-% 		 &= \frac{2}{N}U^D\sum_{i} \tau_{i \uparrow}\tau_{i \downarrow} - \frac{2}{Nw}\left(1 + \frac{Nw}{2}\right)t^D\sum_{\left<ij\right>}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)
-% \end{aligned}\end{equation}
-% What that means is that we have placed the Hubbard dimer+bath system at all nearest neighbour pairs to reconstruct a new Hubbard model.
+The next step in the programme is to tile the real-space lattice with this cluster+bath Hamiltonian \(\tilde H\) to restore translational invariance (shown in a later section), and obtain a new bulk Hamiltonian for correlated electrons, $\tilde H = T\left[ \tilde H^{*}_{CL} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the cluster-bath (auxiliary model) Hamiltonian to span the target real-space lattice.
+Given a general auxiliary model Hamiltonian \(H_\text{CL}^*\), the result of tiling can be written very generally as
+ \begin{equation}\begin{aligned}
+	 \tilde H = \sum_{\left\{i_1,i_2,...\right\}} H^*_\text{CL}\left(\left\{i_1,i_2,...\right\}\right)
+ \end{aligned}\end{equation}
+where \(\left\{i_1,i_2,...\right\}\) represents the indices for the members of the cluster.
+To reiterate, what that means is that we have placed the cluster+bath system at all lattice point sets \(\left\{i_1,i_2,...\right\}\) to reconstruct a new model of correlated electsons.
 If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as dropping the correlation on the bath sites, we can write
-% \begin{equation}\begin{aligned}
-% 	\label{app2}
-% 	\tilde H = \mathcal{U} H^H \mathcal{U}^{-1} = TZ\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right]Z^{-1} T^{-1}~,
-% \end{aligned}\end{equation}
-% where $\mathcal{U} = TZ\mathcal{U}_{A}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation that maps from the original to the reconstructed Hubbard Hamiltonian.
-% The existence of $U$ is contingent on how good the approximations are.
-% \\\\
+ \begin{equation}\begin{aligned}
+ 	\label{app2}
+ 	\tilde H = \mathcal{U} H_{CL} \mathcal{U}^{-1} = T\left[\mathcal{U}_{CL} H_{CL} \mathcal{U}_{CL}^\dagger \right]T^{-1}~,
+ \end{aligned}\end{equation}
+ where $\mathcal{U} = T \mathcal{U}_{CL}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation that maps from the original auxiliary model Hamiltonian to the reconstructed bulk Hamiltonian.
+The answer to how closely $\tilde H$ approximates a target model of correlated electrons lies in (i) the choice of the cluster-bath construction of the auxiliary model, and (ii) the accuracy of the URG procedure on the auxiliary model.
+ %The existence of $U$ is contingent on how good the approximations are.\\\\
 % We mention the two approximations made along the entire journey from the original Hubbard model to the reconstructed one here.
@@
 
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U>0,U.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U>0,V.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U>0,J.pdf}
-
-	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U>0,U.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U>0,V.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U>0,J.pdf}
-\end{figure}
+%\begin{figure}[htpb]
+%	\centering
+%	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U>0,U.pdf}
+%	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U>0,V.pdf}
+%	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U>0,J.pdf}
+%
+%	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U>0,U.pdf}
+%	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U>0,V.pdf}
+%	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U>0,J.pdf}
+%\end{figure}
 
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-
-	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-
-	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=1_over_U,V=J,N=4,U=0.016,91.116,32.pdf}
+
+	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.35\textwidth]{../figures/corr-di-min-t=1.000,J=1_over_U,V=J,N=6,U=0.010,100.000,100.pdf}
-	\includegraphics[width=0.35\textwidth]{../figures/corr-di-max-t=1.000,J=1_over_U,V=J,N=6,U=0.010,100.000,100.pdf}
-
-	\includegraphics[width=0.45\textwidth]{../figures/corr-all-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/I-all-t=1.000,J=1_over_U,V=J,N=4,U=0.016,100.000,95.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/corr-di-min-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/corr-di-max-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+
+	\includegraphics[width=0.45\textwidth]{../figures/corr-all-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/I-all-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
 \end{center}
@@
 
-\section{Creating General \(N-\)site Hubbard Hamiltonian from Anderson molecule embedded in an interacting bath}
+\section{Creating \(N-\)site Hubbard Hamiltonian from Anderson impurity embedded in an interacting bath}
 
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(i) &= \frac{1}{w}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{w}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
-				  &\left.- U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\\
+	\mathcal{H}_\text{aux}(i) &= \frac{1}{w}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{w}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right)  \right.\\
+				  &\left. +J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\\
 				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
@@
 where we have identitied site \(i\) in the auxiliary model as the impurity.
-By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}(d)\), we get
+By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}(d)\), we get from the spectral representation
 \begin{equation}\begin{aligned}
@@
 We again define matrix elements \(z_n^p = \braket{\Phi_n | c^\dagger_{z\sigma} | \Phi_0}, z_n^h = \braket{\Phi_n | c_{z\sigma} | \Phi_0}\).
-The matrix element becomes
+Thus, the spectral representation of the matrix element is obtained as
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-In summary, the four Greens functions are
+In summary, the spectral representation of the matrix elements of the four inverse Greens operators are given by
 \begin{gather}
@@
 
-In order to obtain the matrix elements of \(\mathcal{G}_{H-H}\) as compared to its inverse, we note that the matrix elements of the inverse are related to the matrix elements of another inverse operator, through some coefficients.
-We can therefore use the identity
+In order to obtain the matrix elements of the Greens operators \(\mathcal{G}_{H-H}\) (as compared to its inverse), we note that we have just observed that the matrix elements of the inverse Greens operators are related to the matrix elements of another inverse operator through some coefficients.
+We can, therefore, use the identity
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-We can identity \(\left(\hat O^{-1}\right)_{mn}\) as the matrix elements of \(\mathcal{G}_\text{aux}^{-1}\) in our expressions. Using the relation, we can therefore write
+We can now identify \(\left(\hat O^{-1}\right)_{mn}\) as the matrix elements of \(\mathcal{G}_\text{aux}^{-1}\) in our expressions.
+Using the above relation, we can therefore write the spectral representation of the matrix elements of the Greens operators as
 \begin{gather}
@@
 
-The single-particle Greens functions can now be written in terms of these matrix elements. Using eq.~\ref{G_mat_el}, we write
+The Lehmann-Callen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements.
+Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
 \begin{equation}\begin{aligned}
@@
 	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} = G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k}\\
-			     &= \frac{1}{N}\sum_n\left[\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
+			     &= \frac{1}{N}\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	A_\text{H-H}(\vec{k},\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega)) = -\frac{1}{N\pi} \textrm{Im}\sum_n\left[\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\right.\\
-	\left.\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\\
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-A_\text{H-H}(\vec{r}=0,\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{r}=0,\omega)) = \sum_{\vec{k}}A_{H-H}(\vec{k},\omega)
+	A_\text{H-H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega))\\ 
+	&= -\frac{1}{N\pi} \textrm{Im}\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\\
+	&= \frac{1}{N}\left [A_\text{aux,dd} + \frac{\xi_{\vec k}}{w} A_\text{aux,dz}\right]
+\end{aligned}\end{equation}
+where 
+\begin{eqnarray}
+G_\text{aux,dd} &=& \sum_n\left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\nonumber\\
+G_\text{aux,dz} &=& \sum_n\left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
+\end{eqnarray}
+and the spectral function $A_\text{aux,dd}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dd}$~,~$A_\text{aux,dz}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dz}$.
+Further, \textbf{CHECK!}
+\begin{equation}\begin{aligned}
+A_\text{H-H}(\vec{r}=0,\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{r}=0,\omega)) 
+%= \sum_{\vec{k}}A_{H-H}(\vec{k},\omega) 
+= \frac{A_\text{aux,dd}}{N}
+\label{main}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Sigma_{H-H}(\vec k,\omega) = \omega +t^{H-H}\xi_{\vec k} - N\left\{\sum_n\left[\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}
+	\Sigma_{H-H}(\vec k,\omega) &= \omega +t^{H-H}\xi_{\vec k} - N\left\{\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}\\
+&= 	 \omega +t^{H-H}\xi_{\vec k} - N\left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}
 \end{aligned}\end{equation}
@@
 
+%\clearpage
 \section{Evidence for the Mott MIT}
@@
 \begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.00.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=6.00.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.00.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=4.00.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=6.00.pdf}
 	\includegraphics[width=0.3\textwidth]{../figures/corr-k-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
@@
 \begin{center}
-	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs_D=400,J=40.000.pdf}
+	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs_D=400,J=4.000.pdf}
 \end{center}
 
-Using the mappings between the auxiliary model parameters and the bulk paramets (eq.~\ref{map_aux_bulk}), one can define a critical value \(r_c\) of the ratio \(r = U_{H-H}/J_{H-H}\) at the critical points \(-U_b/J=1/4\) \textit{for a given and fixed value of \(U\)}.
+Using the mappings between the auxiliary model parameters and the bulk paramets (eq.~\ref{map_aux_bulk}), one can define a critical value \(r^{*}\) of the ratio \(r = U_{H-H}/J_{H-H}\) at the critical points \(-U_b/J=1/4\) \textit{for a given and fixed value of \(U\)}.
 We will now argue that this critical point describes a metal-insulator transition.
-For \(r < r_c\), the well-defined low-\(\omega\) central peak in the impurity spectral function, as well as the large mutual and information correlations, in the ground state, among the members of the Kondo cloud or between the impurity and the zeroth site show that the impurity and the bath are very strongly entangled, and the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) are non-zero at low \(\omega\).
-This means that both the local and the nearest-neighbour Greens functions, that are related to these paramers via eq.~\ref{greens_func_siam}, have poles at low\(-\omega\) and support the propagation of electrons through gapless excitations.
-Since the spectral function is also very simply related to that of the auxiliary model, the former also shows the same zero-energy resonance.
-
-On the other side \(r > r_c\) of the critical point, we know that the impurity gets decoupled from the bath, such that the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) vanish.
+For \(r < r^{*}\), the well-defined low-\(\omega\) central peak in the impurity spectral function, as well as the large mutual and information correlations, in the ground state, among the members of the Kondo cloud or between the impurity and the zeroth site show that the impurity and the bath are very strongly entangled, and the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) are non-zero at low \(\omega\).
+This means that both the local and the nearest-neighbour Greens functions, that are related to these parameters via eq.~\ref{greens_func_siam}, have poles at low\(-\omega\) and support the propagation of electrons through gapless excitations.
+Since the spectral function is also very simply related to that of the auxiliary model (eq.\eqref{main}), the former also shows the same zero-energy resonance.
+
+On the other side \(r > r^{*}\) of the critical point, we know that the impurity gets decoupled from the bath, such that the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) vanish.
 This is simply the loss of spectral weight at low-\(\omega\) because of the removal of the gapless excitations.
 This then implies that the bulk Greens functions will also gap out at low energies, and that describes an insulating phase where the electrons get "jammed" in the local states.
-By the same argument as above, the spectral functin also sees a gap in this phase.
+By the same argument as above, the bulk spectral function also sees a gap in this phase when the impurity spectral function is gapped (see eq.\eqref{main}).
+
+Finally, using eqs.\eqref{map_aux_bulk} and the criticality condition $U_{b}^{*}=-\frac{J^{*}}{4}$, we can offer a functional form for the critical value of the parameter $r^{*} = U_{H-H}^{*}/J_{H-H}^{*}\)
+\begin{eqnarray}
+r^{*} &=& \frac{U_{H-H}^{*}}{J_{H-H}^{*}} = \frac{w}{4}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)
+\end{eqnarray}
+where $U^{*}$ and $J^{*}$ are the values of the on-site and Kondo couplings of the auxiliary model at the auxiliary model (i.e., the generalised SIAM with a correlated bath) at the transition between the Kondo screened and the local moment phases.
+Parametrising the bath correlation coupling as $U_{b}=-\frac{U}{20}$, we obtain $U^{*}/J^{*}=5$, and $r^{*} = 4.5$ for the 2D square lattice Hubbard-Heisenberg model (with coordination number $w=4$).
+In general, $w=2d$ for the $d$-dimensional hypercubic lattice, and
+$r^{*}_\text{Hyperc.} = \frac{d}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)$.
+The growth of $r^{*}$ with $d$ indicates that the MIT is increasingly rendered difficult in a higher dimensional hypercubic lattice, as it is easier for electrons to delocalise and a very large on-site repulsion is needed to overcome this.
 \end{itemize}
@@
 
-\section{Creating General \(N-\)site Hubbard Hamiltonian from Hubbard dimers}
+\section{Strategy by starting from a zero bandwidth model}
+We start with a SIAM (with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian.
+The fixed point Hamiltonian will in general involve the impurity site (with renormalised parameters $\epsilon_d^*, U^*$) interacting with a smaller number of momentum states.
+% At this point, we will assume that we have a Hubbard model in mind that has motivated a correlated SIAM as the auxiliary system, and we have performed renormalisation group analysis on this auxiliary system to get down to an effective Hamiltonian.
+We will also assume that the parameters of the auxiliary system have been chosen such that in the effective Hamiltonian, the impurity and zero mode have the same onsite repulsion: $U^A = U^A_z$ (this is required for translational invariance).
+% \\\\
+ To obtain a comparatively simple but physically well-motivated auxiliary model, we identify $\sum_k c_k = \sqrt N c_0$; \(c_0\) is the operator for the zeroth site (the site nearest to the impurity).
+We will call the set of all \(N-2\) sites apart from the impurity and this zeroth site as the "effective bath".
+The fixed point Hamiltonian can be separated into these parts: an isolated impurity part, an isolated zeroth site part, an isolated effective bath part, hopping between impurity and the zeroth site and hopping between the zeroth site and the effective bath.
+\textit{As a simplification, we will ignore the correlation term \((U)\) on the effective bath}.
+In preparation of a symmetrization procedure, we will relabel the impurity site as 0, and the zeroth site as 1.
+With all these steps, the Hamiltonian takes the form:
+ \begin{equation}\begin{aligned}
+ 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow}}_\text{imp.
+\& zero-mode isolated} - \underbrace{t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{0-1 coupling} - \underbrace{t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{1 \& eff.
+bath coupling} - \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff.
+bath isolated}
+ \end{aligned}\end{equation}
+ \begin{figure}[htpb]
+ 	\centering
+ 	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.png}
+ 	\caption{Correlated asymmetric Anderson molecule schematic version.
+It consists of an impurity site (blue) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink).
+The other sites (green) form the rest of the bath.
+Just the impurity site and the zeroth site have onsite repulsion.}
+ 	\label{and_mol}
+ \end{figure}
+ This Hamiltonian is depicted in fig.~\ref{and_mol}.
+Such a Hamiltonian is, however, explicitly asymmetric between the sites 0 and 1 (the effective bath couples only to 1).
+To rectify that, we will symmetrize the coupling between the effective bath and the sites 0 and 1, by exchanging the sites 0 and 1.
+The resultant Hamiltonian is
+ \begin{equation}\begin{aligned}
+ 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow} - t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{2-site Hubbard model} +\underbrace{- t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)- t^A\sum_{j \in \atop{\text{NN of 0}}}\left(c^\dagger_{0\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{dimer \& eff.
+bath coupling} \\
+ 	- \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff. bath isolated}
+ \end{aligned}\end{equation}
+ % The motivation for extracting the zero mode is that it leads to a very simple effective Hamiltonian (the asymmetric Anderson molecule) without losing much of the low energy physics.
+ To further simplify this Hamiltonian, \textit{we will combine the nearest neighbour sites of \(1\) and \(0\) into a single site}.
+ \begin{equation}\begin{aligned}
+ 	c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}
+ \end{aligned}\end{equation}
+ This single site will act as the zeroth site of the effective bath, and it means that both sites of the Hubbard dimer hybridizes with the effective through just a single site.
+With this assumption, the Hamiltonian for "a Hubbard dimer hopping into an effective bath" takes the simple form
+ \begin{equation}\begin{aligned}
+ 	\label{dimer_p_bat}
+ 	\tilde H^D = H^D(0,1) - t^D \sum_{\sigma}\left(c^\dagger_{0\sigma}c_{z\sigma} + c^\dagger_{1\sigma}c_{z\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}
+ \end{aligned}\end{equation}
+ \(H^D(0,1)\) is the Hubbard dimer Hamiltonian (shown in fig.~\ref{hubb-dim}):
+ \begin{equation}\begin{aligned}
+ 	\label{dimer_ham}
+ 	H^D(0,1) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)
+ \end{aligned}\end{equation}
+ \begin{figure}[htpb!]
+ 	\centering
+ 	\includegraphics[width=0.4\textwidth]{../figures/hubb_dim.png}
+ 	\caption{Hubbard dimer schematic version. It again consists of two sites, like the Anderson molecule, but now both sites have onsite repulsion, and their is again inter-site hopping.}
+ 	\label{hubb-dim}
+ \end{figure}
+ This entire procedure is depicted in fig.~\ref{dimer-bath}.
+ \begin{figure}[htpb]
+ 	\centering
+ 	\includegraphics[width=\textwidth]{../figures/dimer_bath.pdf}
+ 	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.
+We first add the asymmetric Hamiltonians to get a symmetrized Hamiltonian.
+In the symmetrized Hamiltonian, the dimer has \(w\) entry points into the bath, \(w\) being the coordination number of the lattice.
+We then merge these \(w\) lattice sites (enclosed in the black box) into a single lattice site.}
+ 	\label{dimer-bath} 
+ \end{figure}
+ We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice.
+The next step in the programme is to tile the real-space lattice with this dimer+bath Hamiltonian \(\tilde H_D\) to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H = T\left[ \tilde H^{D} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the dimer Hamiltonian to span the target real-space lattice.
+We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.
+ \begin{equation}\begin{aligned}
+ 	\tilde H &= \frac{2}{Nw}\sum_{\left<ij\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\tilde H^D((0,1,z) \to (i, j, l))\\
+ 		 &= \frac{2}{N}U^D\sum_{i} \tau_{i \uparrow}\tau_{i \downarrow} - \frac{2}{Nw}\left(1 + \frac{Nw}{2}\right)t^D\sum_{\left<ij\right>}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)
+ \end{aligned}\end{equation}
+ What that means is that we have placed the Hubbard dimer+bath system at all nearest neighbour pairs to reconstruct a new Hubbard model.
+If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as dropping the correlation on the bath sites, we can write
+ \begin{equation}\begin{aligned}
+ 	\tilde H = \mathcal{U} H^H \mathcal{U}^{-1} = TZ\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right]Z^{-1} T^{-1}~,
+ \end{aligned}\end{equation}
+ where $\mathcal{U} = TZ\mathcal{U}_{A}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation that maps from the original to the reconstructed Hubbard Hamiltonian.
+ The existence of $U$ is contingent on how good the approximations are.
+ \\\\
+ We mention the two approximations made along the entire journey from the original Hubbard model to the reconstructed one here.
+ \begin{itemize}
+ 	\item We have replaced the full Hubbard model by an auxiliary system described by the SIAM Hamiltonian in eq.~\ref{clus_bath_siam}.
+The accuracy of this assumption is determined by the choice of the SIAM parameters, particular the self-energy and repulsion of the bath.
+As discussed before, the very choice of th cluster and bath spoil the translational invariance of the parent model.
+ 	\item We then perform a unitary RG on $H^A$.
+This leads to a fixed-point Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$.
+At this point, we go from the fixed point Hamiltonian to the dimer+bath Hamiltonian in eq.~\ref{dimer_p_bat}.
+If we represent this transformation from the fixed point Hamiltonian to the Hamiltonian in eq.~\ref{dimer_p_bat} by an operator \(Z\), we can write $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$.
+This constitutes the second approximation we make.
+ \end{itemize}
+
+\section{Creating \(N-\)site Hubbard Hamiltonian from Hubbard dimer embedded in a bath}
 We will follow the strategy outlined in the previous section.
@@
 \begin{eqnarray}
-	\label{2dsquaretb}
 \xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\

### 2022-03-10 notes/notes.tex
wrote width code, need to fit it

@@
 \end{aligned}\end{equation}
-Once we have this local Hamiltonian for a particular site, we translate this over all sites \(i\), and take the average.
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& \frac{1}{N}\sum_i \mathcal{H}_\text{aux}(i) = \frac{1}{N}\sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
+Once we have this local Hamiltonian for a particular site, we translate this over all sites \(i\):
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{full} =& \sum_i \mathcal{H}_\text{aux}(i) = \sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
 				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\right]\\
-	=& -\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{N}\sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
+	=& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
 				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j\right]\right]
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& -\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{2t (N-2)}{N}\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{Nw}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
+	\mathcal{H}_\text{full} =& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - 2t\left(N-2\right)\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{w}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
 				  &+ \left. J \vec{S_i}\cdot\vec{S}_j\right]\\
-				  &=-\frac{1}{N}\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(\frac{2t (N-2)}{N} - \frac{2V}{Nw}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{Nw} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
+				  &=-\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(2t (N-2) - \frac{2V}{w}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{w} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
 \end{aligned}\end{equation}
@@
 	\label{map_aux_bulk}
-	t_{H-H} = \frac{1}{N}\left(2t (N-2) - \frac{2V}{N}\right),~ ~ U_{H-H} = \frac{1}{N}\left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{Nw}
+	t_{H-H} = \left(2t (N-2) - \frac{2V}{N}\right),~ ~ U_{H-H} = \left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{w}
 \end{aligned}\end{equation}
@@
 	\label{siam_to_hubb}
-	\frac{1}{N}\sum_i \mathcal{H}_\text{aux}(i) = \mathcal{H}_{H-H}
+	\sum_i \mathcal{H}_\text{aux}(i) = \mathcal{H}_{H-H}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\mathcal{G}_{H-H} = \frac{1}{\omega - \left(H_{H-H} - E_\text{gs}\right) }, \mathcal{G}_\text{aux}(i) = \frac{1}{\omega - \left(H_\text{aux}(i) - E_\text{gs}\right)}
-\end{aligned}\end{equation}
-Rewriting eq.~\ref{siam_to_hubb} in terms of these operators, we get
-\begin{equation}\begin{aligned}
-	\frac{1}{N}\sum_i \left(\omega - \mathcal{G}^{-1}_\text{aux}(i)\right) = \omega - \mathcal{G}^{-1}_{H-H} \implies \frac{1}{N}\sum_i \mathcal{G}^{-1}_\text{aux}(i) = \mathcal{G}^{-1}_{H-H}~,
-\end{aligned}\end{equation}
-where we used \(\frac{1}{N}\sum_i \omega = \omega\).
+	\mathcal{G}_{H-H} = \frac{1}{\omega^\prime - \left(H_{H-H} - E_\text{gs}^\prime\right) }, \mathcal{G}_\text{aux}(i) = \frac{1}{\omega - \left(H_\text{aux}(i) - E_\text{gs}\right)}
+\end{aligned}\end{equation}
+Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian, while the primed quantities \(E_\text{gs}^\prime\) and \(\omega^\prime\) are the same quantities but for the full model \(\mathcal{H}_{H-H}\).
+From the relation eq.~\ref{siam_to_hubb} we know that while the auxiliary model is intensive, the full Hamiltonian is extensive (scales with system size).
+This means that we must have \(\omega^\prime = N\omega\) and \(E_\text{gs}^\prime = N E_\text{gs}\).
+Rewriting eq.~\ref{siam_to_hubb} in terms of the operators \(\mathcal{G}\), we get
+\begin{equation}\begin{aligned}
+\sum_i \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i)\right) = N\omega + N E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_i \mathcal{G}^{-1}_\text{aux}(i) = \mathcal{G}^{-1}_{H-H}~,
+\end{aligned}\end{equation}
 We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model.
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{Nw}\sum_j \sum_{k \in \text{NN of j}}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(j,k) c^\dagger_{i\sigma} | \Phi_0}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{w}\sum_j \sum_{k \in \text{NN of j}}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(j,k) c^\dagger_{i\sigma} | \Phi_0}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \frac{1}{Nw} w\times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i) c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{N}\braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{d\sigma} | \Phi_0}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \frac{1}{w} w\times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i) c^\dagger_{i\sigma} | \Phi_0} = \braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{d\sigma} | \Phi_0}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \frac{1}{N}\sum_{m,n} \braket{\Phi_0 | c_{d\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux}(d) \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d\sigma} | \Phi_0} = \left(\mathcal{G}^{-1}_{H-H}\right)_{ii} = \frac{1}{N}\sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}
+	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{m,n} \braket{\Phi_0 | c_{d\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux}(d) \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d\sigma} | \Phi_0} = \left(\mathcal{G}^{-1}_{H-H}\right)_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \frac{1}{N}\sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn} 
+	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn} 
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{i,i+1} \equiv \braket{\Phi_0 | c_{i,\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{Nw}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i,i+1) c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{Nw}\braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{z,\sigma} | \Phi_0}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{i,i+1} \equiv \braket{\Phi_0 | c_{i,\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{w}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i,i+1) c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{w}\braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{z,\sigma} | \Phi_0}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}
+	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}
+	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}
 \end{aligned}\end{equation}
@@
 \label{green_eq_final_siam}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \frac{1}{N}\sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \frac{1}{N}\sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn}\\
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}
+	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn}\\
+	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}
 \end{gather}
@@
 \begin{gather}
-	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \frac{1}{N}\sum_{n} |d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \frac{1}{N}\sum_{n} |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\\
-	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{Nw} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}_\text{aux}(d, -\omega) \right)_{nn}
+	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\\
+	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}_\text{aux}(d, -\omega) \right)_{nn}
 \end{gather}
@@
 	\label{greens_func_siam}
-	\left(G_{H-H}(\omega)\right)_\text{loc} &= \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \frac{1}{N}\sum_n \left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right] \\
-	\left(G_{H-H}(\omega)\right)_\text{n-n} &= \left(G_{H-H}(\omega)\right)_{i,i+1}^p - \left(G_{H-H}(-\omega)\right)_{i+1,i}^h = \frac{1}{Nw}\sum_n \left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
+	\left(G_{H-H}(\omega)\right)_\text{loc} &= \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right] \\
+	\left(G_{H-H}(\omega)\right)_\text{n-n} &= \left(G_{H-H}(\omega)\right)_{i,i+1}^p - \left(G_{H-H}(-\omega)\right)_{i+1,i}^h = \frac{1}{w}\sum_n \left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
 \end{aligned}\end{equation}
@@
 	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} = G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k}\\
-			     &= \frac{1}{N}\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
+			     &= \sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
 \end{aligned}\end{equation}
@@
 	A_\text{H-H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega))\\ 
-	&= -\frac{1}{N\pi} \textrm{Im}\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\\
-	&= \frac{1}{N}\left [A_\text{aux,dd} + \frac{\xi_{\vec k}}{w} A_\text{aux,dz}\right]
+	&= -\frac{1}{\pi} \textrm{Im}\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\\
+	&= A_\text{aux,dd} + \frac{\xi_{\vec k}}{w} A_\text{aux,dz}
 \end{aligned}\end{equation}
@@
 and the spectral function $A_\text{aux,dd}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dd}$~,~$A_\text{aux,dz}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dz}$.
-Further, \textbf{CHECK!}
+Further,
 \begin{equation}\begin{aligned}
 A_\text{H-H}(\vec{r}=0,\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{r}=0,\omega)) 
-%= \sum_{\vec{k}}A_{H-H}(\vec{k},\omega) 
-= \frac{A_\text{aux,dd}}{N}
+= A_\text{aux,dd}
 \label{main}
@@
 \begin{equation}\begin{aligned}
-	\Sigma_{H-H}(\vec k,\omega) &= \omega +t^{H-H}\xi_{\vec k} - N\left\{\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}\\
-&= 	 \omega +t^{H-H}\xi_{\vec k} - N\left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}
+	\Sigma_{H-H}(\vec k,\omega) &= \omega +t^{H-H}\xi_{\vec k} - \left\{\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}\\
+&= 	 \omega +t^{H-H}\xi_{\vec k} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}
 \end{aligned}\end{equation}

### 2022-03-11 notes/notes.tex
obtained fwhm scaling
corrected label on spec func figures and specified delta

@@
 
+\section{Evolution of the impurity spectral function}
+
 \subsection*{Impurity spectral function}
 \begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.00.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=1.50.pdf}\\
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=1.76.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=4.00.pdf}\\
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=6.00.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.000.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.115.pdf}\\
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.117.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.250.pdf}\\
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.40.pdf}
 \end{center}
+
+\subsection*{Width of central peak}
+
+\begin{figure}[!htpb]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../figures/spec_func_width_fit.pdf}
+\end{figure}
 
@@
 \begin{center}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.00.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=4.00.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=6.00.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.000.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.250.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.40.pdf}
 	\includegraphics[width=0.3\textwidth]{../figures/corr-k-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}

### 2022-03-12 notes/notes.tex
added mott's picture, mottness and two self-energies

@@
 
-The Lehmann-Callen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements.
+The Lehmann-Kallen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements.
 Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
@@
 
-Finally, using eqs.\eqref{map_aux_bulk} and the criticality condition $U_{b}^{*}=-\frac{J^{*}}{4}$, we can offer a functional form for the critical value of the parameter $r^{*} = U_{H-H}^{*}/J_{H-H}^{*}\)
+Finally, using eqs.\eqref{map_aux_bulk} and the criticality condition $U_{b}^{*}=-\frac{J^{*}}{4}$, we can offer a functional form for the critical value of the parameter $r^{*} = U_{H-H}^{*}/J_{H-H}^{*}$
 \begin{eqnarray}
@@
 \end{itemize}
+
+\section{Important Remarks}
+\subsection{Greens function in the insulating phase: the Hubbard bands and mottness}
+In the insulating state, the cluster becomes a local moment and the bulk system reduces to the atomic limit \(H = -\frac{U}{2}\sum_i\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\).
+The Greens function in this limit is given in Appendix~\ref{atomic limit}.
+From eq.~\ref{atomic_limit_gf}, we have
+\begin{equation}\begin{aligned}
+	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 + \left<\tau_{i }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i}\right>}{\omega + \frac{U}{2}}
+\end{aligned}\end{equation}
+where \(\tau_i = \sum_\sigma \hat n_{i,\sigma} - 1\).
+At half-filling \(\left<\tau_{i}\right>=0\), the low and high-energy poles have equal spectral weights.
+\textit{This is different from the situation in a band insulator, where the valence band has all the spectral weight in the ground state while the conduction band is empty.} On doping holes into the system such that \(\left<\tau_{i}\right> = -x < 0\), spectral weight is transferred from the upper Hubbard band at \(\omega = U/2\) to the lower one at \(\omega = -U/2\):
+
+\begin{equation}\begin{aligned}
+	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 - x}{\omega - \frac{U}{2}} + \frac{1 + x}{\omega + \frac{U}{2}}
+\end{aligned}\end{equation}
+\begin{figure}[!htpb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../figures/hubbard_bands.pdf}
+	\caption{Structure of the Greens function in the atomic limit.
+The two poles at \(\omega = \pm \frac{U}{2}\) form the two Hubbard bands.
+Doping the system leads to transfer of spectral weight between the bands.}
+\end{figure}
+
+\textit{This transfer of spectral weight across energy scales of the order of \(U\), as well as the lack of poles at zero energies, is referred to as mottness.}
+
+\subsection{Nature of propagation: metal vs insulator}
+In the metallic state, the impurity in the auxiliary model hybridises with the bath through both 1-particle and 2-particle interactions.
+For any two auxiliary models differing by the locations \(i_1, i_2\) of the impurity, the baths will always overlap.
+This means that an electron that starts out from the impurity site at \(i_1\) can hop into the bath, and eventually reach \(i_2\) by hopping out of the other bath and into the other impurity.
+Such processes connect all sites of the lattice and \textit{allow spectral flow}.
+
+In the insulating state, each auxiliary model separates into an impurity and a bath that decoupled from each other.
+This means that the impurity cannot hybridise into the bath, and hence cannot tunnel into any other impurity.
+This leads to the atomic limit of the system, where each site develops a local moment configuration because of the repulsive local correlation, but these local moments cannot communicate with each other, either through spin-exchange processes or by breaking into holons and doublons.
+Any attempt at spectral flow fails because the boundaries of the system become disconnected from each other.
+
+A more accurate picture of the insulating and metallic phases can be obtained by working with a more complicated choice of the cluster.
+For instance, instead of a single impurity, one can take two correlated impurities interacting with each other through a single-particle hopping, and this cluster then interacts with the bath through the usual interactions.
+The ground state of such a cluster is actually a quantum liquid, consisting of the entangled spin and charge degrees of freedom.
+In the metallic state, various members of this liquid such as the holons, doublons and the spinons are free to propagate across the system through the baths.
+In the insulating state, it is this cluster that then gets decoupled from the other clusters.
+The composite degrees of freedom are then unable to propagate outside the cluster, and \textit{the holons and the doublons are bound to each other} within the confines of the cluster.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../figures/metal_prop.pdf}
+	\caption{Propagation of electrons from one cluster to another through the bath, in the metallic state}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../figures/ins_prop.pdf}
+	\caption{The clusters get isolated from each other in the insulator, because they get decoupled from their baths.}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=0.9\textwidth]{../figures/ins_prop_cluster.pdf}
+	\caption{Each cluster is a quantum liquid composed of spin \(\left(\uparrow,\downarrow\right) \) and charge \(\left(0,2\right) \) degrees of freedom.
+In the insulating state, these degrees of freedom get bound within the cluster and are unable to propagate outside.}
+\end{figure}
+
+\subsection*{Presence of two self-energies under symmetry-breaking}
+The effective Hamiltonian that describes either the metallic or the insulating phase has $\mathrm{SU}(2)$ symmetry in both the spin and charge sectors.
+Since the repulsive correlation on the impurity picks out the spin sector, we focus on that for now.
+Applying a small magnetic field on the impurity breaks this spin-rotation symmetry and picks out either the up or the down state on the impurity.
+The Hamiltonian has the form \(H(h)_i = -\frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 = h\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)\).
+The unique groundstate is \(\ket{\hat n_{i,\sigma = \text{sgn}(h)}=1,\hat n_{i,\sigma = -\text{sgn}(h)}=0}\), with an energy of \(E_\text{gs} = -\frac{U}{2} - h\).
+The Greens function is easiest to obtain from the Lehmann-Kallen representation (eq.~\ref{Gf_lk}):
+\begin{equation}\begin{aligned}
+	G_{i,\sigma} = \sum_{n}\left[||\bra{\text{GS}}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_\text{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{\text{GS}}||^2\frac{1}{\omega - E_\text{GS} + E_n}\right]\\
+\end{aligned}\end{equation}
+We have \(c_{i,\sigma}\ket{\text{GS}} = \ket{\hat n_i = 0}\delta_{\sigma,\text{sgn}(h)}\) and \(c^\dagger_{i,\sigma}\ket{\text{GS}} = \ket{\hat n_i = 2}\delta_{\sigma,-\text{sgn}(h)}\), so that the only excited states that give non-zero inner product is \(\ket{n}=\ket{\hat n_i = 0}\) for the second term and \(\ket{n}=\ket{\hat n_i=2}\) for the first term, with energies \(E_n=0\).
+Substituting these, we get
+\begin{equation}\begin{aligned}
+	G_{i,\sigma}(h) = \frac{\delta_{\sigma,-\text{sgn}(h)}}{\omega - \frac{U}{2} - h} + \frac{\delta_{\sigma,\text{sgn}(h)}}{\omega + \frac{U}{2} + h} = \frac{1}{\omega + \left(\frac{U}{2}+h\right)\sigma \times \text{sgn}(h) }
+\end{aligned}\end{equation}
+Taking the limit of \(h \to 0^\pm\) then gives
+\begin{equation}\begin{aligned}
+	G_{i,\sigma}(h=0^\pm) = \frac{1}{\omega \pm \frac{U}{2}\sigma}
+\end{aligned}\end{equation}
+
+The self-energies arising from the correlation \(U\) can also be obtained using Dyson's equation \(\Sigma = G^{-1} - G_0^{-1}\), where \(G_0^{-1} = \omega\) is the Greens function at \(U=0\).
+Using Dyson's equation, we get
+\begin{equation}\begin{aligned}
+	\Sigma_{i,\sigma} = \pm\frac{U}{2}\sigma
+\end{aligned}\end{equation}
 
@@
 The wavefunction will act as our $\ket{0}$ and the ground state energy will be our $E_\text{GS}$.
-We can then substitute these into the Lehmann representation form of the Greens function, and calculate the matrix elements $\mathcal{G}_D(\omega)_{\nu \nu^\prime}$ and $\mathcal{G}_D(-\omega)_{\overline{\nu \nu^\prime}}$ for the Hubbard dimer Hamiltonian.
+We can then substitute these into the Lehmann-Kallen representation form of the Greens function, and calculate the matrix elements $\mathcal{G}_D(\omega)_{\nu \nu^\prime}$ and $\mathcal{G}_D(-\omega)_{\overline{\nu \nu^\prime}}$ for the Hubbard dimer Hamiltonian.
 Each set will form a $2\times2$ matrix, and we can invert them to obtain $\mathcal{G}_D(\omega)$, and then the matrix elements of this inverted matrix will give all the parameters $g_0$ through $\overline{g_1}$.
@@
 
-\chapter{Analytic results for the Hubbard dimer}
-\section*{Spectrum of the Hubbard dimer}
+\chapter{Some analytic results for the Hubbard dimer and the Hubbard model}
+\section{Spectrum of the Hubbard dimer}
 Here we document the spectrum of the Hubbard dimer Hamiltonian in eqs.~\ref{hubb_dimer}.
@@
 \end{center}
-\section*{Appendix: Local Greens function for the Hubbard dimer}
+
+\section{Greens function of Hubbard model in the atomic limit}
+\label{atomic limit}
+The atomic limit is described by the Hamiltonian \(H = -\frac{U}{2}\sum_i\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\).
+Since the Hamiltonian has decoupled into \(\sum_i \equiv N\) single-site Hamiltonians, we can easily write down the retarded Greens function for a single site by identifying the ground state configuration of a site.
+The ground states are of course \(\ket{\Psi}_i = \ket{\uparrow},\ket{\downarrow}\), in the absence of any symmetry-breaking.
+The finite temperature retarded Greens function in the time domain is given by
+\begin{equation}\begin{aligned}
+	G_{i,\sigma}(T,t) = -i\theta(t) \frac{1}{Z}\sum_n e^{-\beta E_n} \braket{n | \left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} | n}
+\end{aligned}\end{equation}
+where \(n\) labels the eigenstates of the \(H\). At \(T \to 0\), only the ground states will survive in the exponential and the partition function \(Z\), such that the formula then reduces to
+\begin{equation}\begin{aligned}
+G_{i,\sigma}(T \to 0,t) = -i\theta(t)\braket{GS | \left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} | GS}
+\end{aligned}\end{equation}
+Since the Hamiltonian is simple, we can compute the time-dependent operator \(c_{i\sigma}(t) = e^{iH t} c_{i\sigma} e^{-iHt}\). Using the BCH lemma, we have
+\begin{equation}\begin{aligned}
+	e^{iH t} c_{i\sigma} e^{-iHt} = \sum_{n=0}^\infty \left(it\right)^n \frac{1}{n!}\left[H,c_{i\sigma}\right]_n
+\end{aligned}\end{equation}
+where \(\left[H,c_{i\sigma}\right]_n = \left[H,\left[H,c_{i\sigma}\right]_{n-1}\right],\left[H,c_{i\sigma}\right]_0=c_{i\sigma}\). The first two non-trivial commutators are
+\begin{equation}\begin{aligned}
+	\left[H, c_{i\sigma}\right]_1 = -U \tau_{i\overline\sigma}c_{i\sigma},~ ~\text{and} ~~\left[H, c_{i\sigma}\right]_2 = \frac{1}{4}U^2 c_{i\sigma}~,
+\end{aligned}\end{equation}
+such that
+\begin{equation}\begin{aligned}
+	e^{iH t} c_{i\sigma} e^{-iHt} =& \left[c_{i\sigma} + \frac{i^2 t^2}{2!}\frac{U^2}{2^2} c_{i\sigma} + \frac{i^4 t^4}{4!}\frac{U^4}{2^4} c_{i\sigma} + \ldots\right] + \left[- \frac{it}{1!}U\tau_{i\overline\sigma}c_{i\sigma} - \frac{i^3 t^3}{3!}\frac{U^3}{4}\tau_{i\overline\sigma}c_{i\sigma} + \ldots \right]\\
+				       &= c_{i\sigma} \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] 
+\end{aligned}\end{equation}
+Using this, we can write
+\begin{equation}\begin{aligned}
+	\left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} = \left\{c_{i\sigma},c^\dagger_{i\sigma}\right\} \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] = \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right]
+\end{aligned}\end{equation}
+and the Greens function becomes
+\begin{equation}\begin{aligned}
+	G_{i,\sigma}(T \to 0,t) = -i\theta(t) \braket{GS | \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] | GS} = -i\theta(t)\left[\cos \frac{Ut}{2} - 2i\sin \frac{Ut}{2} \left<\tau_{i\overline\sigma} \right>\right]
+\end{aligned}\end{equation}
+We now Fourier transform to frequency domain:
+\begin{equation}\begin{aligned}
+	G_{i,\sigma}(\omega) = -i\int_{0}^\infty \mathrm{dt} e^{i\omega t}\left[\cos \frac{Ut}{2} - 2i\sin \frac{Ut}{2} \left<\tau_{i\overline\sigma} \right>\right] = \frac{1 + \left<\tau_{i\overline\sigma }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i\overline\sigma}\right>}{\omega + \frac{U}{2}}
+\end{aligned}\end{equation}
+The spin-total Greens function for the site \(i\) is
+\begin{equation}\begin{aligned}
+	\label{atomic_limit_gf}
+	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 + \left<\tau_{i }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i}\right>}{\omega + \frac{U}{2}}
+\end{aligned}\end{equation}
+At half-filling, we have \(\tau_i = 1\).
+\section{Local Greens function for the Hubbard dimer}
 From the spectral representation, we have the following expression for the local Greens function for the Hubbard dimer at site $0$:
@@
 
-\section*{Contributions of various excitations to the site local spectral function}
+\section{Contributions of various excitations to the site local spectral function}
 The site local spectral function is
@@
 \chapter{Simple results for the Greens functions}
-\section*{Relation between single-particle Greens function and the Greens function operator $(T=0)$}
+\section{Relation between single-particle Greens function and the Greens function operator $(T=0)$}
  The single-particle Greens function is defined as the solution of the equation:
@@
  \end{aligned}\end{equation}
- This solution can be written in the Lehmann representation  and at $T=0$ as
+ This solution can be written in the Lehmann-Kallen representation  and at $T=0$ as
  \begin{equation}\begin{aligned}
@@
 
-\section*{Writing single-particle excitations of ground state in terms of $N=3, S^z = \frac{1}{2}$ eigenstates}
+\section{Writing single-particle excitations of ground state in terms of $N=3, S^z = \frac{1}{2}$ eigenstates}
 The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates $\ket{3\pm\uparrow}$ defined in table \ref{hubb_dim_spectrum}.
@@
 
-\section*{Matrix elements of $G^{-1}$ between single-particle momentum excitations, for the Hubbard dimer}
+\section{Matrix elements of $G^{-1}$ between single-particle momentum excitations, for the Hubbard dimer}
 \begin{equation}\begin{aligned}
@@
 The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term.
-What follows is a standard calculation where we write the Green's function in the Lehmann representation.
+What follows is a standard calculation where we write the Green's function in the Lehmann-Kallen representation.
 The ensemble average for an arbitrary operator \(\hat M\) can be written in terms of the exact eigenstates of the fixed point Hamiltonian:
@@
 \end{aligned}\end{equation}
-The time-domain impurity Green's function can thus be written as (this is the so-called Lehmann representation)
+The time-domain impurity Green's function can thus be written as (this is the so-called Lehmann-Kallen representation)
 \begin{equation}\begin{aligned}
@@
 \begin{equation}\begin{aligned}
+	\label{Gf_lk}
 	G_{d d}^\sigma(\omega, \beta \to \infty) &= \frac{1}{d_0e^{-\beta E_0}}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left[e^{-\beta E_m}\delta_{E_m, E_0} + e^{-\beta E_n}\delta_{E_n, E_0}\right]\frac{1}{\omega + E_m - E_n}\\

### 2022-03-14 notes/notes.tex
computed spectral functions for same parameters

@@
 	\item The labels \(U_0,J_0,V_0\) that may occur in the axes of the plots or anywhere else represent the bare values of the couplings \(U,J\) and \(V\). 
-	\item Throughout the results, the bare value of \(U_b\) is set to the negative of the bare value of \(U_0\): \(U_b = -U_0\).
+	\item Throughout the upcoming results, the bare value of \(U_b\) is set to the negative of the bare value of \(U_0\): \(U_b = -U_0\).
 This means that whenever we vary \(U_0\) along the axis of a plot, we are simultaneous varying \(U_b\).
@@
 
-\section{Evolution of the impurity spectral function}
-
-\subsection*{Impurity spectral function}
+\section{Spectral functions}
+
+\subsection{Impurity spectral function \(A_{dd}(\omega)\)}
+These are the frequency-domain spectral functions for the retarded propagator \(-i\theta(t)\left<\left\{c_{d\sigma}(t),c^\dagger_{d\sigma}\right\}  \right>\):
 \begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.000.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.115.pdf}\\
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.117.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.040.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.141.pdf}\\
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.185.pdf}
 	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.250.pdf}\\
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.40.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.26.pdf}
 \end{center}
 
-\subsection*{Width of central peak}
+\subsection{Impurity-bath off-diagonal spectral function \(A_{dz}(\omega)\)}
+These are the frequency-domain spectral functions for the off-diagonal retarded propagator \(-i\theta(t)\left<\left\{c_{d\sigma}(t),c^\dagger_{0\sigma}\right\}  \right>\):
+\begin{center}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.040.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.141.pdf}\\
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.185.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.250.pdf}\\
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.26.pdf}
+\end{center}
+
+\subsection{Width of central peak of \(A_{dd}\)}
 
@@
 \end{aligned}\end{equation}
+\textit{This transfer of spectral weight across energy scales of the order of \(U\), as well as the lack of poles at zero energies, is referred to as mottness.}
 \begin{figure}[!htpb]
@@
 
-\textit{This transfer of spectral weight across energy scales of the order of \(U\), as well as the lack of poles at zero energies, is referred to as mottness.}
-
 \subsection{Nature of propagation: metal vs insulator}
@@
 	\centering
-	\includegraphics[width=0.6\textwidth]{../figures/metal_prop.pdf}
+	\includegraphics[width=0.55\textwidth]{../figures/metal_prop.pdf}
 	\caption{Propagation of electrons from one cluster to another through the bath, in the metallic state}
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/ins_prop.pdf}
+	\includegraphics[width=0.75\textwidth]{../figures/ins_prop.pdf}
 	\caption{The clusters get isolated from each other in the insulator, because they get decoupled from their baths.}
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{../figures/ins_prop_cluster.pdf}
+	\includegraphics[width=0.85\textwidth]{../figures/ins_prop_cluster.pdf}
 	\caption{Each cluster is a quantum liquid composed of spin \(\left(\uparrow,\downarrow\right) \) and charge \(\left(0,2\right) \) degrees of freedom.
@@
 Applying a small magnetic field on the impurity breaks this spin-rotation symmetry and picks out either the up or the down state on the impurity.
-The Hamiltonian has the form \(H(h)_i = -\frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 = h\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)\).
+The Hamiltonian has the form \(H(h)_i = -\frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - h\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)\).
 The unique groundstate is \(\ket{\hat n_{i,\sigma = \text{sgn}(h)}=1,\hat n_{i,\sigma = -\text{sgn}(h)}=0}\), with an energy of \(E_\text{gs} = -\frac{U}{2} - h\).

### 2022-03-14 notes/notes.tex
added references to mott,logan and mottness

@@
 \end{aligned}\end{equation}
-\textit{This transfer of spectral weight across energy scales of the order of \(U\), as well as the lack of poles at zero energies, is referred to as mottness.}
+\textit{This transfer of spectral weight across energy scales of the order of \(U\), as well as the lack of poles at zero energies, is referred to as mottness}~\cite{phillips2006mottness}.
 \begin{figure}[!htpb]
@@
 In the insulating state, it is this cluster that then gets decoupled from the other clusters.
-The composite degrees of freedom are then unable to propagate outside the cluster, and \textit{the holons and the doublons are bound to each other} within the confines of the cluster.
+The composite degrees of freedom are then unable to propagate outside the cluster, and \textit{the holons and the doublons are bound to each other}~\cite{Mott_1949} within the confines of the cluster.
 
@@
 Since the repulsive correlation on the impurity picks out the spin sector, we focus on that for now.
-Applying a small magnetic field on the impurity breaks this spin-rotation symmetry and picks out either the up or the down state on the impurity.
+Applying a small magnetic field on the impurity breaks this spin-rotation symmetry and picks out either the up or the down state on the impurity, leading to two kinds of self-energies, one for each spin state~\cite{logan_2014,Logan_2015}.
 The Hamiltonian has the form \(H(h)_i = -\frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - h\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)\).
@@
 \end{aligned}\end{equation}
-
 The self-energies arising from the correlation \(U\) can also be obtained using Dyson's equation \(\Sigma = G^{-1} - G_0^{-1}\), where \(G_0^{-1} = \omega\) is the Greens function at \(U=0\).

### 2022-03-14 notes/notes.tex
obtained Gzz and pole positions of Gzz in metal and lm

@@
 
+\subsection{Bath spectral function \(A_{00}(\omega)\)}
+\begin{center}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_U_by_J=0.040.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_U_by_J=0.141.pdf}\\
+	\includegraphics[width=0.48\textwidth]{../figures/spec_func_00_U_by_J=0.185.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/spec_func_00_U_by_J=0.250.pdf}\\
+\end{center}
+
+\subsection{Position of lowest-energy pole}
+\begin{center}
+	\includegraphics[width=0.48\textwidth]{../figures/poles_lm.pdf}
+\end{center}
+
 \subsection{Width of central peak of \(A_{dd}\)}
@@
 \begin{center}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.000.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.040.pdf}
 	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.250.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.40.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.26.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_U_by_J=0.040.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_U_by_J=0.250.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_U_by_J=0.26.pdf}
 	\includegraphics[width=0.3\textwidth]{../figures/corr-k-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}

### 2022-03-15 notes/notes.tex
cleaned the program

@@
 \usepackage[T1]{fontenc}
+\usepackage[sfdefault]{FiraSans} %% option 'sfdefault' activates Fira Sans as the default text font
+\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}
+
 \renewcommand{\arraystretch}{2}
@@
 
-%\begin{figure}[htpb]
-%	\centering
-%	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U>0,U.pdf}
-%	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U>0,V.pdf}
-%	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U>0,J.pdf}
-%
-%	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U>0,U.pdf}
-%	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U>0,V.pdf}
-%	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U>0,J.pdf}
-%\end{figure}
-
 \begin{figure}[htpb]
 	\centering
-	\includegraphics[width=0.48\textwidth]{../figures/VvsJ_relvsirr.pdf}
-	\hspace*{\fill}
-	\includegraphics[width=0.48\textwidth]{../figures/UvsJ_relvsirr.pdf}
-\end{figure}
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.48\textwidth]{../figures/VcvsJ.pdf}
-	\hspace*{\fill}
-	\includegraphics[width=0.48\textwidth]{../figures/UcvsJ.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U_gt_0,U.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U_gt_0,J.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U_gt_0,V.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U_gt_0,U.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U_gt_0,J.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U_gt_0,V.pdf}
 \end{figure}
@@
 There exists, therefore, a phase transition at a critical plane \((U_c, K_c, V_c)\), where the ground state changes between the charge singlet \(\ket{\Psi}_2\) and the spin singlet + charge triplet \(\ket{\Psi}_1\).
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../figures/E1_vs_E3.pdf}
+\end{figure}
 
 \section{Approach towards the thermodynamic limit}
+
+{\bf \Large [Update with V vs D plots]}
+
 The URG method works strictly on finite systems and leads to finite values of fixed point couplings.
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/coeffs_vs_D_largeV.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/coeffs_vs_D_smallV.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/coeffs_vs_D.pdf}
 	\caption{Variation of spin and charge fractions, \(c_s\) and \(c_c\), of the ground state, as a function of bare bandwidth \(D_0\).
@@
 	\centering
-	\includegraphics[width=0.49\textwidth]{../figures/chiT_J=0.020.pdf}
-	\includegraphics[width=0.49\textwidth]{../figures/chiT_J=0.100.pdf}
+	\includegraphics[width=0.49\textwidth]{../figures/chiT.pdf}
+	\includegraphics[width=0.49\textwidth]{../figures/chiT_large.pdf}
+	\includegraphics[width=0.49\textwidth]{../figures/chi.pdf}
 	\caption{Spin susceptibility of the impurity times temperature, for two sets of bare parameters, in \(U>0\).
@@
 	\centering
-	\includegraphics[width=0.49\textwidth]{../figures/chi_chargeT_K=0.010.pdf}
-	\includegraphics[width=0.49\textwidth]{../figures/chi_chargeT_K=0.100.pdf}
+	\includegraphics[width=0.49\textwidth]{../figures/chic.pdf}
+	\includegraphics[width=0.49\textwidth]{../figures/chic_T.pdf}
 	\caption{Charge susceptibility for the impurity at \(U<0\), for two sets of bare parameters. The physics is very similar to that of the spin susceptibility in \(U>0\).}
@@
 	\centering
-	\includegraphics[width=0.48\textwidth]{../figures/chiC_posU_J=small.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/chiC_posU_J=large.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/chiC_posU_J0=10.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/chiC_posU_J0=40.pdf}
 	\caption{Charge susceptibility of the impurity in the positive \(U\) regime, for two values of \(J_0\).
@@
 \begin{center}
-	\includegraphics[width=0.9\textwidth]{../figures/phase-map_D=1000.pdf}
+	\includegraphics[width=0.9\textwidth]{../figures/phase-map-MIT.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs_D=400,J=0.400.pdf}\\
-	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs_D=400,J=4.000.pdf}\\
-	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs_D=400,J=40.000.pdf}
+	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=0.050.pdf}\\
+	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=5.000.pdf}\\
+	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=50.000.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs_D=400,J=0.400.pdf}\\
-	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs_D=400,J=4.000.pdf}\\
-	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs_D=400,J=40.000.pdf}
+	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=0.050.pdf}\\
+	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=5.000.pdf}\\
+	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=50.000.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_U_by_J=0.040.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_U_by_J=0.020.pdf}
 	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_U_by_J=0.141.pdf}\\
@@
 	\includegraphics[width=0.48\textwidth]{../figures/spec_func_00_U_by_J=0.250.pdf}\\
+	\includegraphics[width=0.48\textwidth]{../figures/spec_func_00_U_by_J=0.26.pdf}\\
 \end{center}
@@
 	\centering
-	\includegraphics[width=0.6\textwidth]{../figures/spec_func_width_fit.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_width_fit.pdf}
 \end{figure}

### 2022-03-15 notes/notes.tex
obtained Azz without height constraint

@@
 
+\newcommand{\comment}[1]{{}}
 \renewcommand{\arraystretch}{2}
@@
 
+\section{Analytic consistency check - On the Bethe lattice}
+Another test involves considering the case of infinite number of nearest neighbours $w\to\infty$ (the coordination number, and effectively the dimensionality).
+Here, as has been argued in the DMFT literature, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$ such that the kinetic energy of the associated tight-binding lattice model is finite.
+This allows for the competition between the kinetic and potential terms of the Hamiltonian to drive a metal-insulator transition in the limit of $w\to\infty$ as well.
+Further, it has been argued in the DMFT literature that the Greens function matrix of the Hubbard model on the Bethe lattice with $w\to\infty$ becomes purely local (i.e., it has vanishing inter-site matrix elements).
+We can also see this from eqs.\eqref{green_eq_final_siam}- the nearest-neighbour inverse Greens function vanishes in the limit of $w \to \infty$:
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}_{H-H}(\omega)\right)_{ij}^\sigma = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn} \implies \lim_{w \to \infty}\left(\mathcal{G}_{H-H}(\omega)\right)_{ij}^\sigma \to 0
+\end{aligned}\end{equation}
+There we used the fact since at half-filling on an $SU(2)$ symmetric mode, we expect $\left<\hat n_{i \uparrow} \right> = \frac{1}{2}$, the orthonormal expansion of $c^\dagger_{i \sigma}\ket{\tilde \Phi_0} = \sum_n C^i_n \ket{n}$ to be constrained to $\sum_n |C_n^i|^2 = \frac{1}{2}$, such that the only term that scales with $w$ is $w$ itself.
+This result then implies that $G^{H}$ matrix has no $k$ dependence.
+\\\\
+In this limit, the self-energy also simplifies:
+\begin{equation}\begin{aligned}
+	\lim_{w \to \infty}\Sigma_H(\vec k,\omega) &= \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n \lim_{w \to \infty}\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1} \\
+						   &=\omega +t^{H}\xi_{\vec k} - \frac{N}{2}\frac{1}{\sum_n \left[ \frac{|C^0_{n}|^2}{g_n} - \frac{|\overline C^0_{n}|^2}{\overline{g_n}}\right]}
+\end{aligned}\end{equation}
+We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.
+
+\comment{
 \chapter{From the auxiliary model to the bulk - two site approach}
@@
 We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.
+}
 

### 2022-03-16 notes/notes.tex
talked about Adz in MIT

@@
 \begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.040.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.141.pdf}\\
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.185.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.100.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.133.pdf}\\
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.182.pdf}
 	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.250.pdf}\\
@@
 \begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.040.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.141.pdf}\\
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.185.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.100.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.133.pdf}\\
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.182.pdf}
 	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.250.pdf}\\
@@
 where \(\epsilon_{\vec{q}}\) is the tight-binding dispersion.
-\\\\
+
 We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
@@
 \begin{center}
-	\includegraphics[width=0.7\textwidth]{../figures/phase-map_D=1000.pdf}
+	\includegraphics[width=0.7\textwidth]{../figures/phase-map-MIT.pdf}
 \end{center}
-	\item Study of the impurity spectral function shows a gap at low \(\omega\) for \(U_b > J/4\).
+\item The impurity spectral function \(A_{dd}(\omega)\) and the impurity-bath real space off-diagonal Greens function \(A_{d0}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
+The gap in the diagonal spectral function shows that the impurity site cannot fluctuate through gapless excitations, while the vanishing of the off-diagonal spectral function shows that an electron on the impurity site cannot delocalise out of that site.
 Other measures like mutual information and spin-spin correlations also show a sharp change on crossing that value, demonstrating \textbf{the destruction of the Kondo cloud and the stabilisation of the local moment on the impurity}.
-\begin{center}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.040.pdf}
+
+\begin{figure}[!htpb]
+\centering
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.100.pdf}
 	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.250.pdf}
 	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.26.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_U_by_J=0.040.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_U_by_J=0.100.pdf}
 	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_U_by_J=0.250.pdf}
 	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_U_by_J=0.26.pdf}
+	\caption{Evolution of diagonal and off-diagonal spectral functions across the transition.}
+	\label{spec_func_mit}
+\end{figure}
+
+\begin{figure}[!htb]
+\centering
 	\includegraphics[width=0.3\textwidth]{../figures/corr-k-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
@@
 	\includegraphics[width=0.3\textwidth]{../figures/r1p-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-\end{center}
-	\item In the context of the auxiliary model, this represents an \textbf{impurity phase transition} from the completely-screened spin-singlet phase to the unscrened local moment phase.
-\begin{center}
+	\caption{Evolution of correlation functions and mutual information across the transition.}
+\end{figure}
+
+	\item In the context of the auxiliary model, this represents an \textbf{impurity phase transition} from the completely-screened spin-singlet phase to the unscreened local moment phase.
+
+\begin{figure}[!htb]
+\centering
 	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs_D=400,J=4.000.pdf}
-\end{center}
-
-Using the mappings between the auxiliary model parameters and the bulk paramets (eq.~\ref{map_aux_bulk}), one can define a critical value \(r^{*}\) of the ratio \(r = U_{H-H}/J_{H-H}\) at the critical points \(-U_b/J=1/4\) \textit{for a given and fixed value of \(U\)}.
+	\caption{Evolution of the zero-bandwidth ground state across the transition.}
+\end{figure}
+
+Using the mappings between the auxiliary model parameters and the bulk parameters (eq.~\ref{map_aux_bulk}), one can define a critical value \(r^{*}\) of the ratio \(r = U_{H-H}/J_{H-H}\) at the critical points \(-U_b/J=1/4\) \textit{for a given and fixed value of \(U\)}.
 We will now argue that this critical point describes a metal-insulator transition.
@@
 On the other side \(r > r^{*}\) of the critical point, we know that the impurity gets decoupled from the bath, such that the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) vanish.
-This is simply the loss of spectral weight at low-\(\omega\) because of the removal of the gapless excitations.
+This is simply the loss of spectral weight at low-\(\omega\) because of the removal of the gapless excitations, and is demonstrated through both the diagonal and off-diagonal spectral functions in fig.~\ref{spec_func_mit}.
 This then implies that the bulk Greens functions will also gap out at low energies, and that describes an insulating phase where the electrons get "jammed" in the local states.
@@
 \end{aligned}\end{equation}
-There we used the fact since at half-filling on an $SU(2)$ symmetric mode, we expect $\left<\hat n_{i \uparrow} \right> = \frac{1}{2}$, the orthonormal expansion of $c^\dagger_{i \sigma}\ket{\tilde \Phi_0} = \sum_n C^i_n \ket{n}$ to be constrained to $\sum_n |C_n^i|^2 = \frac{1}{2}$, such that the only term that scales with $w$ is $w$ itself.
-This result then implies that $G^{H}$ matrix has no $k$ dependence.
-\\\\
+There we used the fact since at half-filling on an $SU(2)$ symmetric model, we expect $\left<\hat n_{i \uparrow} \right> = \frac{1}{2}$, the orthonormal expansion of $c^\dagger_{i \sigma}\ket{\Phi_0} = \sum_n d^p_n \ket{\Phi_n}$ and \(c^\dagger_{i+1,\sigma}\ket{\Phi_0}=z^p_n\ket{\Phi_n}\) are constrained such that $\sum_n |d^p_n|^2 = \sum_n |z^p_n|^2 = \frac{1}{2}$, so that the only term that scales with $w$ is $w$ itself.
+This result then implies that $G^{H-H}$ matrix has no $k$ dependence.
+
 In this limit, the self-energy also simplifies:
 \begin{equation}\begin{aligned}
-	\lim_{w \to \infty}\Sigma_H(\vec k,\omega) &= \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n \lim_{w \to \infty}\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1} \\
-						   &=\omega +t^{H}\xi_{\vec k} - \frac{N}{2}\frac{1}{\sum_n \left[ \frac{|C^0_{n}|^2}{g_n} - \frac{|\overline C^0_{n}|^2}{\overline{g_n}}\right]}
+	\lim_{w \to \infty}\Sigma_H(\vec k,\omega) = = \omega +t^{H-H}\xi_{\vec k} - \left\{\sum_n \left[|d^p_n|^2  \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}- |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}
 \end{aligned}\end{equation}
@@
 This will guide us in deciding how to generalize the "tiling method" for a general $N-$site Hubbard model, as well as give indications as to whether we need a different smallest unit for tiling.
-\\\\
+
 The Hubbard dimer and Anderson molecules (zero-mode) are defined by the following respective Hamiltonians:
@@
  The existence of $U$ is contingent on how good the approximations are.
- \\\\
+
  We mention the two approximations made along the entire journey from the original Hubbard model to the reconstructed one here.
@@
 A square 2d lattice is thus placed on a 2-torus.
-\\\\
+
 For each nearest-neighbour pair \(i,j\), we will create a local Hamiltonian \(H^D_{i,j}\) from the Hamiltonian of the Hubbard dimer with bath (we will interpret the effective bath as the remaining \(N-2\) sites of the lattice, apart from \(i,j\)).
@@
 Since the number of nearest neighbour pairs is \(\frac{Nw}{2}\), the general Hubbard Hamiltonian should be the average of these local Hamiltonians.
-\\\\
+
 We recall the dimer+bath Hamiltonian here, since we are going to create the full Hamiltonian by combining various realizations of that Hamiltonian:
@@
 We can see from the relation that we will need two types of matrix elements, one that propagates a particle excitation $\left( \ket{i\sigma} \right) $ and the one that propagates a hole excitation $\ket{\overline{i\sigma}}$.
-\\\\
+
 To this end, we rewrite eq.~\ref{H_tiled} in terms of inverse Greens function operators for the new (symmetrized) Hubbard model and the Hubbard dimer respectively:
@@
 \end{figure}
-\\\\
+
 The matrix elements for hole propagation are obtained similarly.
@@
 This result then implies that $G^{H}$ matrix has no $k$ dependence.
-\\\\
+
 In this limit, the self-energy also simplifies:

### 2022-03-19 notes/notes.tex
obtained Add and Adz at Ub=-U/10

@@
 
+\clearpage
 \subsection{Impurity spectral function \(A_{dd}(\omega)\)}
@@
 \begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.100.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.133.pdf}\\
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.182.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.250.pdf}\\
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_U_by_J=0.26.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.100.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.145.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.188.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.250.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.26.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.100.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.133.pdf}\\
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.182.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.250.pdf}\\
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_U_by_J=0.26.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.100.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.145.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.188.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.250.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.26.pdf}
 \end{center}

### 2022-03-19 notes/notes.tex
generated all plots for N=5 and with positive probs

@@
 
-\clearpage
 \subsection{Impurity spectral function \(A_{dd}(\omega)\)}
@@
 \begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_U_by_J=0.020.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_U_by_J=0.141.pdf}\\
-	\includegraphics[width=0.48\textwidth]{../figures/spec_func_00_U_by_J=0.185.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/spec_func_00_U_by_J=0.250.pdf}\\
-	\includegraphics[width=0.48\textwidth]{../figures/spec_func_00_U_by_J=0.26.pdf}\\
-\end{center}
-
-\subsection{Position of lowest-energy pole}
-\begin{center}
-	\includegraphics[width=0.48\textwidth]{../figures/poles_lm.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_Ub_by_J=-0.000.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_Ub_by_J=-0.125.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_Ub_by_J=-0.250.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_Ub_by_J=-0.26.pdf}
 \end{center}
@@
 \centering
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.100.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.250.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_U_by_J=0.26.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_U_by_J=0.100.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_U_by_J=0.250.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_U_by_J=0.26.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_Ub_by_J=-0.100.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_Ub_by_J=-0.250.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_Ub_by_J=-0.26.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.100.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.250.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.26.pdf}
 	\caption{Evolution of diagonal and off-diagonal spectral functions across the transition.}
@@
 where $U^{*}$ and $J^{*}$ are the values of the on-site and Kondo couplings of the auxiliary model at the auxiliary model (i.e., the generalised SIAM with a correlated bath) at the transition between the Kondo screened and the local moment phases.
-Parametrising the bath correlation coupling as $U_{b}=-\frac{U}{20}$, we obtain $U^{*}/J^{*}=5$, and $r^{*} = 4.5$ for the 2D square lattice Hubbard-Heisenberg model (with coordination number $w=4$).
+Parametrising the bath correlation coupling as $U_{b}=-\frac{U}{10}$, we obtain $U^{*}/J^{*}=5/2$, and $r^{*} = 2$ for the 2D square lattice Hubbard-Heisenberg model (with coordination number $w=4$).
 In general, $w=2d$ for the $d$-dimensional hypercubic lattice, and
-$r^{*}_\text{Hyperc.} = \frac{d}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)$.
+$r^{*}_\text{hyperc.} = \frac{d}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)$.
 The growth of $r^{*}$ with $d$ indicates that the MIT is increasingly rendered difficult in a higher dimensional hypercubic lattice, as it is easier for electrons to delocalise and a very large on-site repulsion is needed to overcome this.

### 2022-03-19 notes/notes.tex
final version of 1 site

@@
 
-\comment{
 \chapter{From the auxiliary model to the bulk - two site approach}
+
+\section{Preface}
+The previous chapter dealt with treating the Hubbard-Heisenberg model using an auxiliary model that has a single-site cluster.
+In this chapter, we will improve the formalism by considering a larger cluster that has two impurities interacting with each other:
+\begin{equation}\begin{aligned}
+	\label{dimer_ham}
+	H_\text{CL} = \mathcal{H}_D = -t^A\sum_{\sigma, i=1,2}\left(c^\dagger_{d_i\sigma}c_{z\sigma} + \text{h.c.}\right) - \frac{U^A}{2}\sum_{i=1,2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 - t^A \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+The name \(\mathcal{H}_D\) is used to indicate that the impurity sites now form a dimer interacting with a bath.
+\(d_1\) and \(d_2\), or \(d_i\) in general, represent the two impurity sites in the dimer.
+Note that this chapter only sets out the relations between such an auxiliary model and the corresponding bulk model (in this case, a Hubbard), but does not describe the physics of this auxiliary model.
+That requires performing a renormalisation group calculation for \(H_\text{CL}\), and that will be provided at a later point in time.
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.2\textwidth]{../figures/dimer_dispersion.png}
+	\caption{Two-impurity SIAM hybridising with a bath}
+\end{figure}
 
@@
 
+\comment{
 \section{Strategy by starting from a zero bandwidth model}
@@
 \end{itemize}
+}
 
@@
 \end{aligned}\end{equation}
-where $\mathcal{G}_D^{-1}(\tilde i,\tilde j, \tilde l)$ is the Greens function inverse matrix of the Hubbard dimer+bath Hamiltonian with $\tilde i, \tilde j$ as the two sites and \(\tilde l\) as the zero mode of the bath, eq.~\ref{Hdjl}, or equivalently, eq.~\ref{dimer_p_bat}.
+where $\mathcal{G}_D^{-1}(\tilde i,\tilde j, \tilde l)$ is the Greens function inverse matrix of the Hubbard dimer+bath Hamiltonian with $\tilde i, \tilde j$ as the two sites and \(\tilde l\) as the zero mode of the bath, eq.~\ref{Hdjl}.
 Since the $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, they can be pulled out along with a factor.
@@
 \end{gather}
-Once we have stripped away the \(j,l\) dependence, we can view the RHS as simply the matrix element of the dimer-bath Hamiltonian eq.~\ref{dimer_p_bat} between the local states of the site zero of the bath:
+Once we have stripped away the \(j,l\) dependence, we can view the RHS as simply the matrix element of the dimer-bath Hamiltonian eq.~\ref{dimer_ham} between the local states of the site zero of the bath:
 \begin{gather}
@@
 \end{gather}
-Just to make it explicit, we repeat once more that \(\mathcal{G}_{D}^{-1}(\omega)\) is the inverse Greens function operator of the Hamiltonian in eq.~\ref{dimer_p_bat}.
+Just to make it explicit, we repeat once more that \(\mathcal{G}_{D}^{-1}(\omega)\) is the inverse Greens function operator of the Hamiltonian in eq.~\ref{dimer_ham}.
 We can expand the state $c^\dagger_{i\sigma}\ket{\tilde \Phi_0}$ in terms of a complete set of orthogonal states:
@@
 
-\section{Calculating the coefficients $C^{0,1}_n$ and $\overline C^{0,1}_n$ in practice}
-The expressions for $C^{0,1}_n$ and $\overline C^{0,1}_n$, as mentioned above, involve taking the projection of the exact ground state of the full Hubbard model, $\ket{\tilde \Phi_0}$, against the chosen orthogonal basis $\ket{n}$.
-\begin{enumerate}
-	\item Since the full Hubbard model ground state wavefunctions are not readily available, one can, as the simplest approximation, assume the ground state has the form
-	\begin{equation}\begin{aligned}
-		\ket{\tilde \Phi_0} = \sum_{\left<\tilde i \tilde j \right>}\ket{\Phi^D_{\tilde i\tilde j}}\otimes\ket{\Psi_{\hat{\tilde i}, \hat {\tilde j}}}\label{guess}
-	\end{aligned}\end{equation}
-	$\ket{\Phi^D_{ij}}$ would be the ground state of the Hubbard dimer with $i,j$ creating the two sites of the dimer, while $\ket{\Psi_{\hat i, \hat j}}$ would be the wavefunction involving the rest of the sites.
+% \section{Calculating the coefficients $C^{0,1}_n$ and $\overline C^{0,1}_n$ in practice}
+% The expressions for $C^{0,1}_n$ and $\overline C^{0,1}_n$, as mentioned above, involve taking the projection of the exact ground state of the full Hubbard model, $\ket{\tilde \Phi_0}$, against the chosen orthogonal basis $\ket{n}$.
+% \begin{enumerate}
+% 	\item Since the full Hubbard model ground state wavefunctions are not readily available, one can, as the simplest approximation, assume the ground state has the form
+% 	\begin{equation}\begin{aligned}
+% 		\ket{\tilde \Phi_0} = \sum_{\left<\tilde i \tilde j \right>}\ket{\Phi^D_{\tilde i\tilde j}}\otimes\ket{\Psi_{\hat{\tilde i}, \hat {\tilde j}}}\label{guess}
+% 	\end{aligned}\end{equation}
+% 	$\ket{\Phi^D_{ij}}$ would be the ground state of the Hubbard dimer with $i,j$ creating the two sites of the dimer, while $\ket{\Psi_{\hat i, \hat j}}$ would be the wavefunction involving the rest of the sites.
 This of course assumes that the two sets $(i,j)$ and $(a,b,...,h,k,...)$ are not entangled, and is not true in general.
@@
 This will allow for analytic insight, but at the cost of accuracy as discussed above.
-	\item Another way of approaching the problem is to obtain the ground state wavefunction of a Hubbard model numerically for several values of $U^H$ and $t^H$, and then computing the matrix elements of $H^D$ against this wavefunction to obtain a family of $(g_0,  g_1)$.
+% 	\item Another way of approaching the problem is to obtain the ground state wavefunction of a Hubbard model numerically for several values of $U^H$ and $t^H$, and then computing the matrix elements of $H^D$ against this wavefunction to obtain a family of $(g_0,  g_1)$.
 This brings the numerical accuracy for a given finite-sized lattice realisation of the Hubbard model.
 However, this also means we lose any analytical insight into the structure of $g_0$ and $g_1$.
-	\item The most promising approach of calculating $g_0$ and $g_1$ is by systematically improving the required ground state wavefunctions as follows.
+% 	\item The most promising approach of calculating $g_0$ and $g_1$ is by systematically improving the required ground state wavefunctions as follows.
 We obtain numerically the ground state wavefunction of a Hamiltonian that has not just the Hubbard dimer, but also a bath (with dispersion) that connects to both the sites of the dimer:
-\begin{equation}\begin{aligned}
-		\label{dimer_dispersion}
-	H^D_\text{bath}(\tilde i, \tilde j) = \underbrace{U\left(\tau_{\tilde i \uparrow}\tau_{\tilde i \downarrow} + \tau_{\tilde j \uparrow}\tau_{\tilde j \downarrow}\right) - t \sum_\sigma\left(c^\dagger_{\tilde i\sigma}c_{\tilde j\sigma} + \text{h.c.}\right)}_\text{Hubbard dimer} + \underbrace{\sum_{k\sigma}\epsilon_{k\sigma}\tau_{k\sigma}}_\text{bath} \underbrace{- t \sum_{k\sigma}\left(c^\dagger_{\tilde i\sigma}c_{k\sigma} + c^\dagger_{\tilde j\sigma}c_{k\sigma} + \text{h.c.}\right)}_\text{bath-dimer hybridisation}
-\end{aligned}\end{equation}
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.2\textwidth]{../figures/dimer_dispersion.png}
-	\caption{Hubbard dimer with dispersion that connects to both sites}
-\end{figure}
-\par\noindent
-By systematically increasing the number of momentum states in the bath dispersion, we can systematically improve the numerical computation of the ground state wavefunction.
+% \begin{equation}\begin{aligned}
+% 		\label{dimer_dispersion}
+% 	H^D_\text{bath}(\tilde i, \tilde j) = \underbrace{U\left(\tau_{\tilde i \uparrow}\tau_{\tilde i \downarrow} + \tau_{\tilde j \uparrow}\tau_{\tilde j \downarrow}\right) - t \sum_\sigma\left(c^\dagger_{\tilde i\sigma}c_{\tilde j\sigma} + \text{h.c.}\right)}_\text{Hubbard dimer} + \underbrace{\sum_{k\sigma}\epsilon_{k\sigma}\tau_{k\sigma}}_\text{bath} \underbrace{- t \sum_{k\sigma}\left(c^\dagger_{\tilde i\sigma}c_{k\sigma} + c^\dagger_{\tilde j\sigma}c_{k\sigma} + \text{h.c.}\right)}_\text{bath-dimer hybridisation}
+% \end{aligned}\end{equation}
+% \begin{figure}[htpb]
+% 	\centering
+% 	\includegraphics[width=0.2\textwidth]{../figures/dimer_dispersion.png}
+% 	\caption{Hubbard dimer with dispersion that connects to both sites}
+% \end{figure}
+% \par\noindent
+% By systematically increasing the number of momentum states in the bath dispersion, we can systematically improve the numerical computation of the ground state wavefunction.
 From here, we can compute matrix elements of $H^{D}$, and hence the functions $g_0$ and $g_1$.
@@
 If this can be found, then a metal-insulator transition of the full Hubbard model can perhaps be captured by studying the spectral functions of the bath-coupled Hubbard dimer.
-\item Another improvement can be made by introducing a self-energy $\Sigma (k,\omega)$ into the bath dispersion.
+% \item Another improvement can be made by introducing a self-energy $\Sigma (k,\omega)$ into the bath dispersion.
 This introduces correlation within the bath.
@@
 With regards to the transition itself, the precise form of the bath $\Sigma (k,\omega)$ (or spectral function) remains to be determined.
-\end{enumerate}
-Once we have chosen a test Hamiltonian whose wavefunction we can calculate, we can use that to obtain the ground state energy of this state.
+% \end{enumerate}
+% Once we have chosen a test Hamiltonian whose wavefunction we can calculate, we can use that to obtain the ground state energy of this state.
 The wavefunction will act as our $\ket{0}$ and the ground state energy will be our $E_\text{GS}$.
@@
 We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.
-}
 

### 2022-03-21 notes/notes.tex
replaced other figures with Ub=-U by 10

@@
 	\item The labels \(U_0,J_0,V_0\) that may occur in the axes of the plots or anywhere else represent the bare values of the couplings \(U,J\) and \(V\). 
-	\item Throughout the upcoming results, the bare value of \(U_b\) is set to the negative of the bare value of \(U_0\): \(U_b = -U_0\).
+	\item Throughout the upcoming results, the bare value of \(U_b\) is set to the negative of the bare value of \(U_0\): \(U_b = -U_0/10\).
 This means that whenever we vary \(U_0\) along the axis of a plot, we are simultaneous varying \(U_b\).
@@
 red &  \(\Delta U > 0, \Delta J,\Delta V<0\) & \(U^* \gg 1,  V^* = J^* = 0\) & decoupled LM & \(\left\{\ket{\uparrow}, \ket{\downarrow} \right\} \otimes \left\{\ket{0}, \ket{2}\right\} \) \\
-yellow &  \(\Delta U, \Delta J,\Delta V < 0\) & \(U^* = V^* = J^* = 0\) & lattice & \(\left\{\ket{\uparrow}, \ket{\downarrow}, \ket{0}, \ket{2} \right\} \otimes \left\{\ket{0}, \ket{2}\right\}\) \\
+gray &  \(\Delta U, \Delta J,\Delta V < 0\) & \(U^* = V^* = J^* = 0\) & lattice & \(\left\{\ket{\uparrow}, \ket{\downarrow}, \ket{0}, \ket{2} \right\} \otimes \left\{\ket{0}, \ket{2}\right\}\) \\
 \hline
@@
 \begin{center}
-	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=0.050.pdf}\\
-	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=5.000.pdf}\\
+	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=0.100.pdf}\\
+	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=10.000.pdf}\\
 	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=50.000.pdf}
@@
 \begin{center}
-	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=0.050.pdf}\\
-	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=5.000.pdf}\\
+	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=0.100.pdf}\\
+	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=10.000.pdf}\\
 	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=50.000.pdf}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
 
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-
-	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+
+	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
 \end{center}

### 2022-03-22 notes/notes.tex
typo

@@
 \end{aligned}\end{equation}
-where we have identitied site \(i\) in the auxiliary model as the impurity.
+where we have identified site \(i\) in the auxiliary model as the impurity.
 By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}(d)\), we get from the spectral representation
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{m,n} \braket{\Phi_0 | c_{d\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux}(d) \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d\sigma} | \Phi_0} = \left(\mathcal{G}^{-1}_{H-H}\right)_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}
+	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{m,n} \braket{\Phi_0 | c_{d\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux}(d) \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d\sigma} | \Phi_0} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}
 \end{aligned}\end{equation}
@@
 \section{Analytic consistency check - On the Bethe lattice}
-Another test involves considering the case of infinite number of nearest neighbours $w\to\infty$ (the coordination number, and effectively the dimensionality).
+One can apply a test to this method: it involves considering the case of infinite number of nearest-neighbours $w\to\infty$ (the coordination number, and effectively the dimension).
 Here, as has been argued in the DMFT literature, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$ such that the kinetic energy of the associated tight-binding lattice model is finite.

### 2022-03-23 notes/notes.tex
UNSTABLE STATE: COMPLETE REVERSE RG!

@@
 \documentclass{report}
-\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix}
+\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk}
 % \usepackage[draft]{graphicx}
@@
 \usepackage[T1]{fontenc}
-\usepackage[sfdefault]{FiraSans} %% option 'sfdefault' activates Fira Sans as the default text font
+\usepackage[sfdefault]{FiraSans}
 \renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}
@@
 
-\title{\bf Auxiliary Model Approach to Strongly-Correlated Systems}
-\author{\Large Abhirup Mukherjee, Siddhartha Lal}
-\date{\Large \today}
+\title{Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Systems}
+\author{Abhirup Mukherjee, Siddhartha Lal}
+\affil{Indian Institute of Science Education and Research Kolkata, Mohanpur}
+\date{\today}
 
@@
 This is the microscopic theory, where high energy features are also relevant.
-\begin{center}
-	\includegraphics[width=0.8\textwidth]{../figures/gen_siam_spec_func.pdf}
-	\captionof{figure}{Impurity spectral function for multiple values of \(U\). The increase in value of \(U\) is accompanied by the appearance of the side-peaks.}
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=0.00.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=3.00.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=5.00.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=10.00.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=25.00.pdf}
+	\caption{Impurity spectral function for multiple values of \(U\). The increase in value of \(U\) is accompanied by the appearance of the side-peaks.}
 	\label{spec_func}
-\end{center}
+\end{figure}
 The physics of the three peaks can now be looked into.
@@
 \centering
-	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs_D=400,J=4.000.pdf}
+	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=10.000.pdf}
 	\caption{Evolution of the zero-bandwidth ground state across the transition.}

### 2022-03-24 notes/notes.tex
took care of fonts and some numerics, still need to take care of rev RG and two site chapter
improved the first chapter

@@
 \usepackage[T1]{fontenc}
-\usepackage[sfdefault]{FiraSans}
+\usepackage[sfdefault]{roboto}
 \renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}
@@
 
-\title{Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Systems}
+\title{A New Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Systems}
 \author{Abhirup Mukherjee, Siddhartha Lal}
@@
 \begin{equation}\begin{aligned}
-	H = \begin{pmatrix} H_1 && H_{12} \\ H_{12}^* && H_2 \end{pmatrix} = H_1 \ket{1}\bra{1} + H_2\ket{2}\bra{2} + H_{12}\ket{1}\bra{2} + H_{12}^*\ket{2}\bra{1}
-\end{aligned}\end{equation}
-where \(\ket{1}(\ket{2})\) actually represents a sum over all basis kets of subsystem 1(subsystem 2).
-As an example, we can split the the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows:
-\begin{equation}\begin{aligned}
-	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_1} \\
-		      &+ \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_2}\\
+	H = \begin{bmatrix} & H_1 && H_{12} & \\ & H_{12}^* && H_2 & \end{bmatrix} = H_1 \ket{1}\bra{1} + H_2\ket{2}\bra{2} + H_{12}\ket{1}\bra{2} + H_{12}^*\ket{2}\bra{1}
+\end{aligned}\end{equation}
+where \(\ket{1}\) and \(\ket{2}\) actually represents sums over all basis kets of subsystems 1 and 2.
+As an example, we can split the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows:
+\begin{equation}\begin{aligned}
+	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_1} + \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_2}\\
 		      & -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{12} + H_{12}^*}\\
@@
 \end{aligned}\end{equation}
-The subsystem 1 is usually taken to be the "smaller system", and consequently, subsystem 2 represents the "bath".
+Each Greens function can be written in terms of the non-interacting counterpart and the self-energy through the Dyson equation: \(\Sigma_i = 1/G_{i,0} - 1/G_i\).
+
+The subsystem 1 is usually taken to be the "cluster", and consequently, subsystem 2 represents the "bath".
 The smaller system is typically chosen such that its eigenstates are known exactly.
 Progress is then made by choosing a simpler version of the bath \(H_2\) and a simpler form also for its coupling \(H_{12}\) with the smaller system.
-This combination of the smaller system and the simpler bath is then called the \textit{auxiliary system}.
+This combination of the cluster and the simpler bath is then called the \textit{auxiliary system}.
 A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{12}\).
@@
 \end{figure}
-\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model.
+\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model}.
 To allow computing quantities, one would need to make the bath (which is a much larger system) simpler than the cluster (which is a single site).
 This distinction breaks the translational symmetry of the Hubbard model.
-For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath only has a global capacitative cost $(\sim U_b N^2)$ means we have broken the symmetry between the cluster and the bath.}
-
-The algorithm of DMFT then involves starting with some local self-energy of the bath, \(\Sigma(\omega)\), and using an impurity solver to calculate the impurity Greens function in the presence of this self-energy.
-This impurity Greens function is then used to calculate the impurity self-energy \(\Sigma_d(\omega)\), and the self-energy of the bath is then set equal to this impurity self-energy: \(\Sigma(\omega) = \Sigma_d(\omega)\), because we expect, on grounds of the lattice symmetry, that the impurity is the same as any other site in the bath.
-This is said to be the self-consistency step, because the bath self-energy is completely determined only at the end.
-With this updated bath self-energy, one then repeats the entire process until there is no further change in the bath self-energy at the self-consistency step.
-
- The present method intends to calculate the quantities in a different fashion.
-We first obtain an auxiliary model ($H_{Cl}$) by choosing a cluster of correlated sites that are hybridised with a bath through one-particle and two-particle exchange terms.
-The bath may additionally have local correlations.
-Then, we carry out a URG analysis of this auxiliary model to obtain a stable fixed point effective Hamiltonian:  $H^{*}_{CL} = \left[\mathcal{U}_{CL} H_{CL} \mathcal{U}_{CL}^\dagger \right]$.
-% We start with a SIAM (with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian.
-The fixed point Hamiltonian will in general involve the impurity site (with renormalised parameters $\epsilon_d^*, U^*$) interacting with a smaller number of momentum states.
-% At this point, we will assume that we have a Hubbard model in mind that has motivated a correlated SIAM as the auxiliary system, and we have performed renormalisation group analysis on this auxiliary system to get down to an effective Hamiltonian.
-We will also assume that the parameters of the auxiliary system have been chosen such that in the effective Hamiltonian, the impurity and zero mode have the same onsite repulsion: $U^A = U^A_z$ (this is required for translational invariance).
-% \\\\
-% To obtain a comparatively simple but physically well-motivated auxiliary model, we identify $\sum_k c_k = \sqrt N c_0$; \(c_0\) is the operator for the zeroth site (the site nearest to the impurity).
-We will call the set of all \(N-2\) sites apart from the impurity and this zeroth site as the "effective bath".
-The fixed point Hamiltonian can be separated into these parts: an isolated impurity part, an isolated zeroth site part, an isolated effective bath part, hopping between impurity and the zeroth site and hopping between the zeroth site and the effective bath.
-\textit{As a simplification, we will ignore the correlation term \((U)\) on the effective bath}.
-In preparation of a symmetrization procedure, we will relabel the impurity site as 0, and the zeroth site as 1.
-With all these steps, the Hamiltonian takes the form:
-% \begin{equation}\begin{aligned}
-% 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow}}_\text{imp.
-\& zero-mode isolated} - \underbrace{t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{0-1 coupling} - \underbrace{t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{1 \& eff.
-bath coupling} - \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff.
-bath isolated}
-% \end{aligned}\end{equation}
+For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath only has a global capacitance cost $(\sim U_b N^2)$ means we have broken the symmetry between the cluster and the bath.
+
+\subsection*{Dynamical mean-field theory - an example of an auxiliary model approach}
+Dynamical mean-field theory is an approximation scheme that use impurity models to obtain Greens functions of bulk systems of strong-correlation~\cite{kotliar1996,kotliar1992}.
+The essential idea is to find the most suitable impurity model that replicates the full Hamiltonian.
+This is done through the following algorithm.
+Given a bulk Hamiltonian with on=site correlation \(U\) and a non-interacting \(k-\)space Greens function \(G_{k,0}\) for the bath:
+\begin{itemize}
+	\item[1.] We first create an impurity model with on-site correlation \(U\) and non-interacting impurity Greens function \(G_{i,0} = \sum_k G_{k,0}\).
+		\[H_\text{aux} = H_\text{imp}(U) -t \sum_\sigma \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + H_\text{bath}\left(t,G_{i,0}\right)\]
+
+	\item[2.] This impurity model is solved using some method like numerical renormalisation group, and the self-energy \(\Sigma_\text{aux}\) of the impurity is obtained.
+
+	\item[3.] The impurity self-energy is now {\it equated} with the bath momentum-space self-energy:
+		\[\Sigma_{k}(\omega) = \Sigma_\text{aux}(\omega)\]
+		Since the impurity is purely local, this is an approximation that involves replacing a non-local quantity by its purely local component: \(\Sigma_{k}(\omega) = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}}\Sigma_{\vec r}(\omega) \simeq \Sigma_{\vec r = 0}(\omega)\).
+This approximation is a result of the single-site nature of the cluster of the chosen auxiliary model - larger clusters with more impurities can generate non-local components.
+This local approximation becomes exact in the limit of large system dimension \(w\), because it can be shown that the non-local components of the self-energy scale as \(w^{-3/2}\).
+
+	\item[4.] With this updated bath self-energy, we now create a new \(k-\)space Greens function for the bath:
+		\[G_{i}(\omega) = \sum_k G_{k}(\omega) = \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_k(\omega)} = \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_\text{aux}(\omega)}\]
+	This interacting Greens function is then used to obtain the updated non-interacting Greens function, using Dyson's equation:
+	\[G_{i,0} = \frac{1}{1/G_{i} + \Sigma_\text{aux}}\]
+	\item[5.] Repeat the algorithm from step 1 with the updated \(G_{i,0}\), until \(\Sigma_\text{aux}\) stops changing.
+\end{itemize}
+The stopping condition is the consistency relation that makes the bath and impurity self-energies equal.
+
 \begin{figure}[htpb]
 	\centering
- 	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.pdf}
- 	\caption{Cluster+bath construction of auxiliary model.
-It consists of a cluster (red square) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink).
-The other sites (green) form the rest of the bath.
-Just the cluster and the zeroth site have onsite correlations.}
- \end{figure}
-% This Hamiltonian is depicted in fig.~\ref{and_mol}.
-Such a Hamiltonian is, however, explicitly asymmetric between the sites 0 and 1 (the effective bath couples only to 1).
-To rectify that, we will symmetrize the coupling between the effective bath and the sites 0 and 1, by exchanging the sites 0 and 1.
-The resultant Hamiltonian is
-% \begin{equation}\begin{aligned}
-% 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow} - t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{2-site Hubbard model} +\underbrace{- t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)- t^A\sum_{j \in \atop{\text{NN of 0}}}\left(c^\dagger_{0\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{dimer \& eff.
-bath coupling} \\
-% 	- \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff. bath isolated}
-% \end{aligned}\end{equation}
-% % The motivation for extracting the zero mode is that it leads to a very simple effective Hamiltonian (the asymmetric Anderson molecule) without losing much of the low energy physics.
-% To further simplify this Hamiltonian, \textit{we will combine the nearest neighbour sites of \(1\) and \(0\) into a single site}.
-% \begin{equation}\begin{aligned}
-% 	c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}
-% \end{aligned}\end{equation}
-% This single site will act as the zeroth site of the effective bath, and it means that both sites of the Hubbard dimer hybridizes with the effective through just a single site.
-With this assumption, the Hamiltonian for "a Hubbard dimer hopping into an effective bath" takes the simple form
-% \begin{equation}\begin{aligned}
-% 	\label{dimer_p_bat}
-% 	\tilde H^D = H^D(0,1) - t^D \sum_{\sigma}\left(c^\dagger_{0\sigma}c_{z\sigma} + c^\dagger_{1\sigma}c_{z\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}
-% \end{aligned}\end{equation}
-% \(H^D(0,1)\) is the Hubbard dimer Hamiltonian (shown in fig.~\ref{hubb-dim}):
-% \begin{equation}\begin{aligned}
-% 	\label{dimer_ham}
-% 	H^D(0,1) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)
-% \end{aligned}\end{equation}
-% \begin{figure}[htpb!]
-% 	\centering
-% 	\includegraphics[width=0.4\textwidth]{../figures/hubb_dim.png}
-% 	\caption{Hubbard dimer schematic version. It again consists of two sites, like the Anderson molecule, but now both sites have onsite repulsion, and their is again inter-site hopping.}
-% 	\label{hubb-dim}
-% \end{figure}
-% This entire procedure is depicted in fig.~\ref{dimer-bath}.
-% \begin{figure}[htpb]
-% 	\centering
-% 	\includegraphics[width=\textwidth]{../figures/dimer_bath.pdf}
-% 	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.
-We first add the asymmetric Hamiltonians to get a symmetrized Hamiltonian.
-In the symmetrized Hamiltonian, the dimer has \(w\) entry points into the bath, \(w\) being the coordination number of the lattice.
-We then merge these \(w\) lattice sites (enclosed in the black box) into a single lattice site.}
-% 	\label{dimer-bath} 
-% \end{figure}
-% We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice.
-The next step in the programme is to tile the real-space lattice with this cluster+bath Hamiltonian \(\tilde H\) to restore translational invariance (shown in a later section), and obtain a new bulk Hamiltonian for correlated electrons, $\tilde H = T\left[ \tilde H^{*}_{CL} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the cluster-bath (auxiliary model) Hamiltonian to span the target real-space lattice.
-Given a general auxiliary model Hamiltonian \(H_\text{CL}^*\), the result of tiling can be written very generally as
- \begin{equation}\begin{aligned}
-	 \tilde H = \sum_{\left\{i_1,i_2,...\right\}} H^*_\text{CL}\left(\left\{i_1,i_2,...\right\}\right)
- \end{aligned}\end{equation}
-where \(\left\{i_1,i_2,...\right\}\) represents the indices for the members of the cluster.
-To reiterate, what that means is that we have placed the cluster+bath system at all lattice point sets \(\left\{i_1,i_2,...\right\}\) to reconstruct a new model of correlated electsons.
-If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as dropping the correlation on the bath sites, we can write
- \begin{equation}\begin{aligned}
- 	\label{app2}
- 	\tilde H = \mathcal{U} H_{CL} \mathcal{U}^{-1} = T\left[\mathcal{U}_{CL} H_{CL} \mathcal{U}_{CL}^\dagger \right]T^{-1}~,
- \end{aligned}\end{equation}
- where $\mathcal{U} = T \mathcal{U}_{CL}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation that maps from the original auxiliary model Hamiltonian to the reconstructed bulk Hamiltonian.
-The answer to how closely $\tilde H$ approximates a target model of correlated electrons lies in (i) the choice of the cluster-bath construction of the auxiliary model, and (ii) the accuracy of the URG procedure on the auxiliary model.
- %The existence of $U$ is contingent on how good the approximations are.\\\\
-% We mention the two approximations made along the entire journey from the original Hubbard model to the reconstructed one here.
-% \begin{itemize}
-% 	\item We have replaced the full Hubbard model by an auxiliary system described by the SIAM Hamiltonian in eq.~\ref{clus_bath_siam}.
-The accuracy of this assumption is determined by the choice of the SIAM parameters, particular the self-energy and repulsion of the bath.
-As discussed before, the very choice of th cluster and bath spoil the translational invariance of the parent model.
-% 	\item We then perform a unitary RG on $H^A$.
-This leads to a fixed-point Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$.
-At this point, we go from the fixed point Hamiltonian to the dimer+bath Hamiltonian in eq.~\ref{dimer_p_bat}.
-If we represent this transformation from the fixed point Hamiltonian to the Hamiltonian in eq.~\ref{dimer_p_bat} by an operator \(Z\), we can write $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$.
-This constitutes the second approximation we make.
-% \end{itemize}
-
-\section{What is the minimal impurity model for a Mott MIT?}
+	\includegraphics[width=0.8\textwidth]{../figures/dmft.pdf}
+\end{figure}
+
+\section{What is the minimal impurity model for a Mott metal-insulator transition?}
+The Hubbard model is one of the fundamental models for strong electronic correlation; in its simplest form, it features a single band of conduction electrons hopping on a lattice and interacting via local correlations that provide a cost \(U\) if any site is doubly occupied:
+\[H_\text{hubb} = -t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}+\text{h.c.}\right) + U\sum_i \hat n_{i \uparrow} \hat n_{i \downarrow} - \mu \sum_{i,\sigma}\hat n_{i\sigma}\]
+The model can be made particle-hole symmetric by choosing \(\mu = U/2\):
+\[H_\text{hubb} = -t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}+\text{h.c.}\right) - \frac{U}{2}\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\]
+There are two trivial limits of the model.
+At \(U=0\), the bath consists of just a kinetic energy part, and the ground state is just a filled Fermi sea.
+At \(t=0\), each lattice site decouples from the rest and becomes a local moment, which under symmetry-breaking becomes a Neel antiferromagnet.
+This suggests that on increasing \(U/t\) beyond some critical value, the system might undergo a phase transition from a metallic state to an insulating state~\cite{Mott_1949}.
+This transition is reflected in the local spectral function - while it has a well-defined zero energy peak in the metallic phase, it is gapped in the insulating phase.
+
 A correlated single impurity site connected with a non-interacting bath with a uniform density of states leads to a well-defined Kondo resonance at low temperatures, as seen in the impurity spectral function.
@@
 
-This is an attempt to obtain various quantities like Greens functions, self-energies, spectral functions and (if possible) energies and wavefunctions of the Hubbard model, using a cluster-bath approach.
-The cluster-bath system is taken to be a single-impurity Anderson model with a correlated bath.
-The correlation will be brought about in two ways: a self-energy $\Sigma(k,\omega)$ of the bath, and a double occupancy repulsion cost $U_b$.
-The Hubbard and the correlated single-impurity Anderson models are defined using the Hamiltonians
-\begin{align}
-H_\text{hubb} &= -t^H\sum_{\sigma,\left<i,j \right>}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right) + U^H\sum_i \hat n_{i \uparrow} \hat n_{i \downarrow} - \mu^H \sum_{i\sigma}\hat n_{i\sigma}\\
-H_\text{siam} &= \sum_{k\sigma}\left[\epsilon_k + \Sigma(k,\omega)\right]\hat n_{k\sigma} + \epsilon_d^A \sum_\sigma\hat n_{d\sigma} + U^A \hat n_{d \uparrow} \hat n_{d \downarrow} + U_b \sum_{kk^\prime}\hat n_k \hat n_{k^\prime} -t^A\sum_{k\sigma}\left(c^\dagger_{d\sigma}c_{k\sigma} + \text{h.c.}\right) \label{clus_bath_siam}
-\end{align}
-Broadly speaking, the method involves first solving the SIAM using a unitary renormalisation group approach, to get the low energy effective theory, and then combining the low energy Hamiltonians in a symmetrized fashion to get the Hamiltonian for the Hubbard model lattice.
-It is reminescent of dynamical mean-field theory (DMFT) - both involve an impurity-solver that solves an auxiliary system.
-The difference, however, lies in the following points:
+\section{A "bottoms-up" approach to using auxiliary models}
+As mentioned in the previous section, the question we are posing is the following: what is the simplest auxiliary model of impurity in a bath that can capture the metal-insulator transition in a Hubbard-like model of correlated electrons.
+We approach this problem in a constructionist/bottoms-up way: we first identity an appropriate quantum impurity model (fig.~\ref{cluster-bath}) that shows an impurity phase transition, and then create a bulk model out of this auxiliary model.
+The bulk model hence created will then show a metal-insulator transition.
+The impurity models are studied using the recently-developed unitary renormalisation group method~\cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome}, and this analysis is shown in chapters~\ref{chap:urg1}~and~\ref{siam-attr-chap}.
+The leap to the bulk model is then made by applying lattice translation operators on the auxiliary model.
+This process is shown in chapter~\ref{chap:tile}.
+This process, referred to as tiling here, relates the auxiliary model Hamiltonian with that of the bulk, and hence allows connecting the Greens functions and other related quantities across dimensions.
+One nice outcome is that since the auxiliary model has multiple sites, there is a real-space off-diagonal component of the self-energy, and this leads to a \(k-\)dependence in the self-energy of the bulk, which is in contrast with the lack of \(k-\)dependence in single-site DMFT.
+
+In our approach, the auxiliary models can be chosen in various ways. The simplest choice is of course the single-impurity Anderson model:
+\begin{equation}
+\label{clus_bath_siam}
+H_\text{SIAM} = -\frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right) ^2 + V\sum_\sigma\left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.} \right) + \text{K.E.}
+\end{equation}
+This model, of course, does not show any impurity phase transition. Correlation can be introduced into the auxiliary model in two ways:
 \begin{itemize}
-	\item While DMFT primarily works with Greens functions and self-energies, this method involves Hamiltonians.
-The impurity-solver in DMFT provides an impurity Greens function (which is then equated with the local Greens function of the bath), while the impurity-solver in this method actually provides a low energy Hamiltonian.
-	\item The final step of DMFT is the self-consistency equation, where the impurity and bath-local quantities are set equal.
-This ensures all sites, along with the impurity site, have the same self-energy, something which is required on grounds of  translational invariance.
-The present method, however, brings about the translational invariance in a different way.
-It symmetrizes the Hamiltonians itself, such that all quantites then derived from the Hamiltonian are then guaranteed to have the symmetry.
+	\item[1.] The impurity or the bath can be made to have additional interaction: 
+\begin{gather}
+H_\text{aux} = H_\text{SIAM} + J \vec{S}_d\cdot\vec{s}_0\\
+H_\text{aux} = H_\text{SIAM} + J \vec{S}_d\cdot\vec{s}_0 - U_b \left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
+\end{gather}
+The first example has a spin-exchange interaction between the impurity site and the zeroth site, while the second example additionally has a correlation locally on the zeroth site.
+\item[2.] The second method is to make the cluster itself more complicated. That is, one can introduce multiple impurity sites that are connected via the hopping:
+\begin{equation}
+H_\text{aux} = -\frac{U}{2}\sum_{d_i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right) ^2 + V\sum_{d_i}\sum_\sigma\left( c^\dagger_{d_i\sigma}c_{0\sigma} + \text{h.c.} \right) + \text{K.E.} - t\sum_{\sigma}\left(c^\dagger_{d_1\sigma}c_{d_2\sigma} + \text{h.c.}\right)
+\end{equation}
+
 \end{itemize}
-The meaning of each of these statements will become clearer when we describe the method in more detail.
+
+\begin{figure}[htpb]
+ 	\centering
+ 	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.pdf}
+ 	\caption{Cluster+bath construction of auxiliary model.
+It consists of a cluster (red square) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink).
+The other sites (green) form the rest of the bath.
+Just the cluster and the zeroth site have onsite correlations.}
+ \end{figure}
+ The next step in the programme is to tile the real-space lattice with this cluster+bath Hamiltonian \(\tilde H\) to restore translational invariance (shown in a later section), and obtain a new bulk Hamiltonian for correlated electrons, $\tilde H = T\left[ H_\text{aux} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the cluster-bath (auxiliary model) Hamiltonian to span the target real-space lattice.
+Given a general auxiliary model Hamiltonian \(H_\text{aux}\), the result of tiling can be written very generally as
+ \begin{equation}\begin{aligned}
+	 \tilde H = \sum_{\left\{i_1,i_2,...\right\}} H_\text{aux}\left(\left\{i_1,i_2,...\right\}\right)
+ \end{aligned}\end{equation}
+where \(\left\{i_1,i_2,...\right\}\) represents the indices for the members of the cluster.
+To reiterate, what that means is that we have placed the cluster+bath system at all lattice point sets \(\left\{i_1,i_2,...\right\}\) to reconstruct a new model of correlated electrons.
+The answer to how closely $\tilde H$ approximates a target model of correlated electrons lies in (i) the choice of the cluster-bath construction of the auxiliary model, and (ii) the accuracy of the URG procedure on the auxiliary model.
 
 \chapter{Physics of the generalised single-impurity Anderson model}
+\label{chap:urg1}
 \section{Introduction of spin-exchange and charge isospin-exchange interactions into the SIAM: the generalised SIAM}
@@
 \chapter{From the auxiliary model to the bulk - single site approach}
+\label{chap:tile}
 
@@
 
-\chapter{From the auxiliary model to the bulk - two site approach}
-
-\section{Preface}
-The previous chapter dealt with treating the Hubbard-Heisenberg model using an auxiliary model that has a single-site cluster.
+\chapter{Going to larger clusters - the two site approach}
+
+\section{Why expand the cluster?}
+The previous chapter dealt with treating the Hubbard-Heisenberg model using an auxiliary model that has a single-site cluster:
+\begin{equation}\begin{aligned}
+	H_\text{aux} = 
+\end{aligned}\end{equation}
+
 In this chapter, we will improve the formalism by considering a larger cluster that has two impurities interacting with each other:
@@
 The fixed point Hamiltonian will in general involve the impurity site (with renormalised parameters $\epsilon_d^*, U^*$) interacting with a smaller number of momentum states.
-% At this point, we will assume that we have a Hubbard model in mind that has motivated a correlated SIAM as the auxiliary system, and we have performed renormalisation group analysis on this auxiliary system to get down to an effective Hamiltonian.
-We will also assume that the parameters of the auxiliary system have been chosen such that in the effective Hamiltonian, the impurity and zero mode have the same onsite repulsion: $U^A = U^A_z$ (this is required for translational invariance).
-% \\\\
+
  To obtain a comparatively simple but physically well-motivated auxiliary model, we identify $\sum_k c_k = \sqrt N c_0$; \(c_0\) is the operator for the zeroth site (the site nearest to the impurity).
@@
  \end{aligned}\end{equation}
- % The motivation for extracting the zero mode is that it leads to a very simple effective Hamiltonian (the asymmetric Anderson molecule) without losing much of the low energy physics.
+
  To further simplify this Hamiltonian, \textit{we will combine the nearest neighbour sites of \(1\) and \(0\) into a single site}.
@@
 Thus, we can use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
-
-% \section{Calculating the coefficients $C^{0,1}_n$ and $\overline C^{0,1}_n$ in practice}
-% The expressions for $C^{0,1}_n$ and $\overline C^{0,1}_n$, as mentioned above, involve taking the projection of the exact ground state of the full Hubbard model, $\ket{\tilde \Phi_0}$, against the chosen orthogonal basis $\ket{n}$.
-% \begin{enumerate}
-% 	\item Since the full Hubbard model ground state wavefunctions are not readily available, one can, as the simplest approximation, assume the ground state has the form
-% 	\begin{equation}\begin{aligned}
-% 		\ket{\tilde \Phi_0} = \sum_{\left<\tilde i \tilde j \right>}\ket{\Phi^D_{\tilde i\tilde j}}\otimes\ket{\Psi_{\hat{\tilde i}, \hat {\tilde j}}}\label{guess}
-% 	\end{aligned}\end{equation}
-% 	$\ket{\Phi^D_{ij}}$ would be the ground state of the Hubbard dimer with $i,j$ creating the two sites of the dimer, while $\ket{\Psi_{\hat i, \hat j}}$ would be the wavefunction involving the rest of the sites.
-This of course assumes that the two sets $(i,j)$ and $(a,b,...,h,k,...)$ are not entangled, and is not true in general.
-With this assumption, $g_0$ and $g_1$ become related to the inverse Greens functions of the Hubbard dimer.
-Such a choice of the wavefunction is motivated by the fact that in the auxiliary system we chose, the bath had only a diagonal interaction; there was no off-diagonal two particle scattering term.
-It is further enforced when we extract the zero mode of the entire bath (i.e., we keep just the zeroth site).
-The zeroth site, along with the impurity, then forms the $\ket{\Phi}$ part of the wavefunction.
-This will allow for analytic insight, but at the cost of accuracy as discussed above.
-% 	\item Another way of approaching the problem is to obtain the ground state wavefunction of a Hubbard model numerically for several values of $U^H$ and $t^H$, and then computing the matrix elements of $H^D$ against this wavefunction to obtain a family of $(g_0,  g_1)$.
-This brings the numerical accuracy for a given finite-sized lattice realisation of the Hubbard model.
-However, this also means we lose any analytical insight into the structure of $g_0$ and $g_1$.
-% 	\item The most promising approach of calculating $g_0$ and $g_1$ is by systematically improving the required ground state wavefunctions as follows.
-We obtain numerically the ground state wavefunction of a Hamiltonian that has not just the Hubbard dimer, but also a bath (with dispersion) that connects to both the sites of the dimer:
-% \begin{equation}\begin{aligned}
-% 		\label{dimer_dispersion}
-% 	H^D_\text{bath}(\tilde i, \tilde j) = \underbrace{U\left(\tau_{\tilde i \uparrow}\tau_{\tilde i \downarrow} + \tau_{\tilde j \uparrow}\tau_{\tilde j \downarrow}\right) - t \sum_\sigma\left(c^\dagger_{\tilde i\sigma}c_{\tilde j\sigma} + \text{h.c.}\right)}_\text{Hubbard dimer} + \underbrace{\sum_{k\sigma}\epsilon_{k\sigma}\tau_{k\sigma}}_\text{bath} \underbrace{- t \sum_{k\sigma}\left(c^\dagger_{\tilde i\sigma}c_{k\sigma} + c^\dagger_{\tilde j\sigma}c_{k\sigma} + \text{h.c.}\right)}_\text{bath-dimer hybridisation}
-% \end{aligned}\end{equation}
-% \begin{figure}[htpb]
-% 	\centering
-% 	\includegraphics[width=0.2\textwidth]{../figures/dimer_dispersion.png}
-% 	\caption{Hubbard dimer with dispersion that connects to both sites}
-% \end{figure}
-% \par\noindent
-% By systematically increasing the number of momentum states in the bath dispersion, we can systematically improve the numerical computation of the ground state wavefunction.
-From here, we can compute matrix elements of $H^{D}$, and hence the functions $g_0$ and $g_1$.
-The presence of the bath can be understood as follow.
-In the absence of a bath, i.e., we have just a Hubbard dimer, an electron can at most hop between the two sites and lead to the wavefunction in eq.~\ref{guess}.
-However, with a single particle hopping term connecting the dimer to a bath, an electron can also journey between the two sites of the bath via the bath.
-This leads to entanglement between the dimer's sites and those in the bath; this was clearly ignored in the ground state wavefunction eq.~\ref{guess}.
-The introduction of the bath dispersion offers the possibility that we can capture a site diagonal spectral function of the three peak form, because we have previously seen such a spectral function in the fixed point of the URG analysis of the SIAM (where the fixed point effective Hamiltonian was an Anderson molecule with dispersion).
-If this can be found, then a metal-insulator transition of the full Hubbard model can perhaps be captured by studying the spectral functions of the bath-coupled Hubbard dimer.
-% \item Another improvement can be made by introducing a self-energy $\Sigma (k,\omega)$ into the bath dispersion.
-This introduces correlation within the bath.
-The Hamiltonian that we would need to solve would be the same as eq.~\ref{dimer_dispersion}, but with $\epsilon_k$ replaced by $\tilde \epsilon_k \equiv \epsilon_k + \Sigma(k,\omega)$.
-The self-energy $\Sigma (k,\omega)$ will have to be chosen depending on the phase we want to look at (e.g., metal, insulator etc.).
-With a $\Sigma$ that is singular near the Fermi surface at $\omega \to 0$, the dispersion will become gapped and the phase will be insulating.
-In such a situation, there are no low-energy bath excitations within a given energy window proximate to its putative Fermi energy.
-This will localise the bath electrons, as well as confine all journeys between the two sites of the dimer to only the direct path.
-This is an indication of the localisation of electrons in the Hubbard model to holon-doublon excitations on nearest neighbour sites.
-In such a circumstance, eq.~\ref{guess} will be a very good approximation to the actual insulating ground state of the Hubbard model.
-On the other hand, if we use a self energy that vanishes near the Fermi surface ($\Sigma(\omega) \sim \omega^2$, i.e., a Fermi liquid bath), then we expect to end up in a metallic phase of the Hubbard model.
-This is simply due to the possibility of holons and doublons now dispersing throughout the lattice, and be concomitant with the presence of a pole in the single-particle Greens function $G(k,\omega)$ of the Hubbard model.
-Introducing the self energy therefore gives us a larger variety of wavefunctions and features to work with.
-Further, this appears to be in line with the original proposals offered by Mott and Kohn for the Mott metal insulator transition as the localisation-delocalisation transition of holon-doublon pairs.
-With regards to the transition itself, the precise form of the bath $\Sigma (k,\omega)$ (or spectral function) remains to be determined.
-% \end{enumerate}
-% Once we have chosen a test Hamiltonian whose wavefunction we can calculate, we can use that to obtain the ground state energy of this state.
-The wavefunction will act as our $\ket{0}$ and the ground state energy will be our $E_\text{GS}$.
-We can then substitute these into the Lehmann-Kallen representation form of the Greens function, and calculate the matrix elements $\mathcal{G}_D(\omega)_{\nu \nu^\prime}$ and $\mathcal{G}_D(-\omega)_{\overline{\nu \nu^\prime}}$ for the Hubbard dimer Hamiltonian.
-Each set will form a $2\times2$ matrix, and we can invert them to obtain $\mathcal{G}_D(\omega)$, and then the matrix elements of this inverted matrix will give all the parameters $g_0$ through $\overline{g_1}$.
 
@@
 \end{equation}
-% Once we have calculated the diagonal and off-diagonal matrix elements of the Greens function, we can compute the parameters $g_0$ and $g_1$:
-% \begin{equation}\begin{aligned}
-%		 g_0 \equiv\frac{2}{N} (G^{-1}_{D})_{00} = \frac{2}{N} \frac{1}{\text{Det }G_D}\left(G_D\right)_{00}, g_1 \equiv\frac{2}{Nw} (G^{-1}_{D})_{00} = -\frac{2}{Nw}\frac{1}{\text{Det }G_D}\left(G_D\right)_{01}
-% \end{aligned}\end{equation}
 Using the diagonal and off-diagonal real space Greens functions, we can now compute the momentum-space Greens functions.

### 2022-03-25 notes/notes.tex
started rewriting chap5

@@
 
-\section{Philosophy of the auxiliary model method}
-The method is closely tied to the auxiliary system approach described in \cite{martin_2016}.
-We can view the full Hamiltonian as a sum of two component Hamiltonians \(H_1, H_2\) connected via the interaction term \(H_{12}\).
-\begin{equation}\begin{aligned}
-	H = \begin{bmatrix} & H_1 && H_{12} & \\ & H_{12}^* && H_2 & \end{bmatrix} = H_1 \ket{1}\bra{1} + H_2\ket{2}\bra{2} + H_{12}\ket{1}\bra{2} + H_{12}^*\ket{2}\bra{1}
-\end{aligned}\end{equation}
-where \(\ket{1}\) and \(\ket{2}\) actually represents sums over all basis kets of subsystems 1 and 2.
-As an example, we can split the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows:
-\begin{equation}\begin{aligned}
-	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_1} + \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_2}\\
-		      & -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{12} + H_{12}^*}\\
-\end{aligned}\end{equation}
-The Greens function of the full Hamiltonian can also be split in a similar fashion:
-\begin{equation}\begin{aligned}
-	G(\omega) = \begin{pmatrix} G_1 && G_{12} \\ G_{12}^* && G_2 \end{pmatrix}
-\end{aligned}\end{equation}
-Each Greens function can be written in terms of the non-interacting counterpart and the self-energy through the Dyson equation: \(\Sigma_i = 1/G_{i,0} - 1/G_i\).
-
-The subsystem 1 is usually taken to be the "cluster", and consequently, subsystem 2 represents the "bath".
-The smaller system is typically chosen such that its eigenstates are known exactly.
-Progress is then made by choosing a simpler version of the bath \(H_2\) and a simpler form also for its coupling \(H_{12}\) with the smaller system.
-This combination of the cluster and the simpler bath is then called the \textit{auxiliary system}.
-A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{12}\).
-Such a construction is shown in fig.~\ref{cluster-bath}.
-\begin{figure}[htpb!]
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/cluster-bath.png}
-	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$.
-\textit{Right}: Extraction of the auxiliary (cluster+bath) system from the full lattice.
-The central site on left becomes the impurity site (red) on the right (with an onsite repulsion $\epsilon_d$), while the rest of the $N-1$ sites on the left form a conduction bath (green circles) (with dispersion $\epsilon_k$ and correlation modelled by the self-energy $\Sigma_k(\omega)$) that hybridizes with the impurity through the coupling $V$.}
-	\label{cluster-bath}
-\end{figure}
-\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model}.
-To allow computing quantities, one would need to make the bath (which is a much larger system) simpler than the cluster (which is a single site).
-This distinction breaks the translational symmetry of the Hubbard model.
-For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath only has a global capacitance cost $(\sim U_b N^2)$ means we have broken the symmetry between the cluster and the bath.
-
-\subsection*{Dynamical mean-field theory - an example of an auxiliary model approach}
-Dynamical mean-field theory is an approximation scheme that use impurity models to obtain Greens functions of bulk systems of strong-correlation~\cite{kotliar1996,kotliar1992}.
-The essential idea is to find the most suitable impurity model that replicates the full Hamiltonian.
-This is done through the following algorithm.
-Given a bulk Hamiltonian with on=site correlation \(U\) and a non-interacting \(k-\)space Greens function \(G_{k,0}\) for the bath:
-\begin{itemize}
-	\item[1.] We first create an impurity model with on-site correlation \(U\) and non-interacting impurity Greens function \(G_{i,0} = \sum_k G_{k,0}\).
-		\[H_\text{aux} = H_\text{imp}(U) -t \sum_\sigma \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + H_\text{bath}\left(t,G_{i,0}\right)\]
-
-	\item[2.] This impurity model is solved using some method like numerical renormalisation group, and the self-energy \(\Sigma_\text{aux}\) of the impurity is obtained.
-
-	\item[3.] The impurity self-energy is now {\it equated} with the bath momentum-space self-energy:
-		\[\Sigma_{k}(\omega) = \Sigma_\text{aux}(\omega)\]
-		Since the impurity is purely local, this is an approximation that involves replacing a non-local quantity by its purely local component: \(\Sigma_{k}(\omega) = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}}\Sigma_{\vec r}(\omega) \simeq \Sigma_{\vec r = 0}(\omega)\).
-This approximation is a result of the single-site nature of the cluster of the chosen auxiliary model - larger clusters with more impurities can generate non-local components.
-This local approximation becomes exact in the limit of large system dimension \(w\), because it can be shown that the non-local components of the self-energy scale as \(w^{-3/2}\).
-
-	\item[4.] With this updated bath self-energy, we now create a new \(k-\)space Greens function for the bath:
-		\[G_{i}(\omega) = \sum_k G_{k}(\omega) = \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_k(\omega)} = \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_\text{aux}(\omega)}\]
-	This interacting Greens function is then used to obtain the updated non-interacting Greens function, using Dyson's equation:
-	\[G_{i,0} = \frac{1}{1/G_{i} + \Sigma_\text{aux}}\]
-	\item[5.] Repeat the algorithm from step 1 with the updated \(G_{i,0}\), until \(\Sigma_\text{aux}\) stops changing.
-\end{itemize}
-The stopping condition is the consistency relation that makes the bath and impurity self-energies equal.
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/dmft.pdf}
-\end{figure}
-
 \section{What is the minimal impurity model for a Mott metal-insulator transition?}
@@
 
-A correlated single impurity site connected with a non-interacting bath with a uniform density of states leads to a well-defined Kondo resonance at low temperatures, as seen in the impurity spectral function.
+One method of studying Hubbard models is through auxiliary models, described in the next section.
+Auxiliary models are simpler versions of the full Hamiltonian that are able to capture the essential physics.
+For eg, a correlated impurity interacting with a conduction bath is a potential auxiliary model for the Hubbard Hamiltonian:
+\begin{equation}
+\label{clus_bath_siam}
+\mathcal{H}_\text{SIAM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow} - t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)
+\end{equation}
+The impurity has onsite energy \(\epsilon_d\) and an onsite correlation \(U\). It hybridises into the bath through \(V\).
+
+If the impurity site hybridises with a {\it non-interacting} bath defined by a uniform density of states, the impurity spectral function is found to have a well-defined Kondo resonance at low temperatures.
 Increasing the impurity correlation \(U\) only serves to reduce the width of the central peak at the cost of the appearance of side bands at energy scales of the order of \(U\), but the resonance never dies.
 The situation is however different if the impurity is embedded in a correlated conduction bath with a non-trivial density of states.
-For the case of a conduction band with the DOS shown in the right of the figure below, the impurity hybridises into a reduced bandwidth because of the correlation on the lattice.
-This difference is what leads to a metal-insulator transition of a bulk Hubbard model under dynamical mean-field theory (DMFT).
-Under self-consistency, the non-interacting bath gets modified into one with a highly-correlated self-energy.
-At low \(U\), the impurity spectral function remains gapless, but at sufficiently large \(U\), the bath is able to kill the Kondo resonance and lead to an insulating state.
+For the case of a conduction band with the DOS shown in the right of the figure below, the impurity hybridises into a reduced bandwidth because of the correlation on the lattice~\cite{held_2013}.
+
+This difference in the type of conduction baths is utilised in dynamical mean-field theory to describe various phases of the bulk system.
+This is done through the DMFT algorithm: one starts with a non-interacting bath, but depending on the value of \(U\), the conduction bath then gets modified and we ultimately end up with something that is different from what we started with.
+For small\(U\), the bath does not change much and we retain the central resonance of the impurity spectral function.
+This then describes a metal in the bulk.
+For larger values of \(U\), however, the bath changes significantly such that its density of states becomes non-constant.
+Above a critical \(U_c\), the impurity spectral function gets gapped out, and that then describes the insulating phase in the bulk.
 \textit{This leaves open the following question: What is the minimal correlation one can insert into the non-interacting bath (of a single-impurity Anderson model) that can capture both the metallic and insulating phases of the bulk model?}
-\cite{held_2013}
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{../figures/correlated_bath.png}
-\caption{"Comparison of the usual Anderson
-impurity model of a strongly interacting site coupled via $V$ to
-an uncorrelated featureless and wide conduction-electron band
-(left-hand side) and the Hubbard model situation (right-hand
-side). In the latter case, an electron leaving a correlated site
-moves within the strongly correlated and narrow band of the
-central peak. In this situation there is a kink at the effective
-Kondo energy scale which is smaller than the width of the
-narrow band." Image and caption source in footnote.}
+\includegraphics[width=0.5\textwidth]{../figures/dos_diff.pdf}
+\caption{Various kinds of bath that an impurity can hybridise into.
+The left panel shows a non-interacting conduction band with a flat density of states.
+The right panel shows an interacting bath with an energy-dependent density of states.
+In the latter case, the impurity "feels" a reduced effective bandwidth defined by the width of the central peak.}
+\end{figure}
+
+\section{Philosophy of auxiliary model methods}
+The present method is a realisation of the general method of using simpler systems called auxiliary models to study bulk systems~\cite{martin_2016}.
+In general, a full Hamiltonian can be separated into the Hamiltonians for a particular subsystem \(S\), the rest of the system \(R\), and the interactions between \(S\) and \(R\).
+\begin{equation}\begin{aligned}
+	\mathcal{H} = \mathcal{H}_S\ket{S}\bra{S} + \mathcal{H}_R \ket{R}\bra{R} + \mathcal{H}_{SR} \ket{S}\bra{R} + \mathcal{H}_{RS}\ket{S}\bra{R} = \begin{bmatrix} & \mathcal{H}_{R} && \mathcal{H}_{RS} & \\ & \mathcal{H}_{RS}^* && \mathcal{H}_{S} & \end{bmatrix}
+\end{aligned}\end{equation}
+where \(\ket{S}\) and \(\ket{R}\) actually represents sums over all basis kets of \(S\) and \(R\) respectively.
+As an example, we can split the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows (fig.~\ref{cluster-bath}):
+\begin{equation}\begin{aligned}
+	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_S} + \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_R}\\
+		      & -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{SR} + H_{RS}}\\
+\end{aligned}\end{equation}
+The Greens function of the full Hamiltonian can also be split in a similar fashion:
+\begin{equation}\begin{aligned}
+	G(\omega) = \begin{bmatrix} G_S && G_{SR} \\ G_{RS} && G_R \end{bmatrix}
+\end{aligned}\end{equation}
+Each Greens function can be written in terms of the non-interacting counterpart and the self-energy through the Dyson equation: \(\Sigma_i = 1/G_{i,0} - 1/G_i\).
+
+The subsystem \(S\) is usually taken to be the "cluster", and consequently, \(R\) represents the "bath".
+The smaller system is typically chosen such that its eigenstates are known exactly.
+Progress is then made by choosing a simpler version of \(H_R\) and a simpler form also for its coupling \(H_{RS}\) with the smaller system.
+This combination of the cluster and the simpler bath is then called the \textit{auxiliary system}.
+A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{RS}\).
+Such a construction is shown in fig.~\ref{cluster-bath}.
+\begin{figure}[htpb!]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../figures/cluster-bath.pdf}
+	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$.
+\textit{Right}: Extraction of the auxiliary (cluster+bath) system from the full lattice.
+The central site on left becomes the impurity site (red) on the right (with an onsite repulsion $\epsilon_d$), while the rest of the $N-1$ sites on the left form a conduction bath (green circles) (with dispersion $\epsilon_k$ and correlation modelled by the self-energy $\Sigma_k(\omega)$) that hybridizes with the impurity through the coupling $V$.}
+	\label{cluster-bath}
+\end{figure}
+\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model}.
+To allow computing quantities, one would need to make the bath (which is a much larger system) simpler than the cluster (which is a single site).
+This distinction breaks the translational symmetry of the Hubbard model.
+For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath does not means we have broken the symmetry between the cluster and the bath.
+
+\subsection*{Dynamical mean-field theory - an example of an auxiliary model approach}
+Dynamical mean-field theory is an approximation scheme that use impurity models to obtain Greens functions of bulk systems of strong correlation~\cite{kotliar1996,kotliar1992}.
+The essential idea is to find the most suitable impurity model that replicates the full Hamiltonian.
+This is done through the following algorithm.
+Given a bulk Hamiltonian with on=site correlation \(U\) and a non-interacting \(k-\)space Greens function \(G_{k,0}\) for the bath:
+\begin{itemize}
+	\item[1.] We first create an impurity model with on-site correlation \(U\) and non-interacting impurity Greens function \(G_{i,0} = \sum_k G_{k,0}\).
+		\[\mathcal{H}_\text{aux} = H_\text{imp}(U) -t \sum_\sigma \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + H_\text{bath}\left(t,G_{i,0}\right)\]
+
+	\item[2.] This impurity model is solved using some method like numerical renormalisation group, and the self-energy \(\Sigma_\text{aux}\) of the impurity is obtained.
+
+	\item[3.] The impurity self-energy is now {\it equated} with the bath momentum-space self-energy:
+		\[\Sigma_{k}(\omega) = \Sigma_\text{aux}(\omega)\]
+		Since the impurity is purely local, this is an approximation that involves replacing a non-local quantity by its purely local component: \(\Sigma_{k}(\omega) = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}}\Sigma_{\vec r}(\omega) \simeq \Sigma_{\vec r = 0}(\omega)\).
+This approximation is a result of the single-site nature of the cluster of the chosen auxiliary model - larger clusters with more impurities can generate non-local components.
+This local approximation becomes exact in the limit of large system dimension \(w\), because it can be shown that the non-local components of the self-energy scale as \(w^{-3/2}\).
+
+	\item[4.] With this updated bath self-energy, we now create a new \(k-\)space Greens function for the bath:
+		\[G_{i}(\omega) = \sum_k G_{k}(\omega) = \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_k(\omega)} = \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_\text{aux}(\omega)}\]
+	This interacting Greens function is then used to obtain the updated non-interacting Greens function, using Dyson's equation:
+	\[G_{i,0} = \frac{1}{1/G_{i} + \Sigma_\text{aux}}\]
+	\item[5.] Repeat the algorithm from step 1 with the updated \(G_{i,0}\), until \(\Sigma_\text{aux}\) stops changing.
+\end{itemize}
+The stopping condition is the consistency relation that makes the bath and impurity self-energies equal.
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../figures/dmft.pdf}
 \end{figure}
@@
 
-In our approach, the auxiliary models can be chosen in various ways. The simplest choice is of course the single-impurity Anderson model:
+In our approach, the auxiliary models can be chosen in various ways. The simplest choice is of course the single-impurity Anderson model of eq.~\ref{clus_bath_siam}:
 \begin{equation}
-\label{clus_bath_siam}
-H_\text{SIAM} = -\frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right) ^2 + V\sum_\sigma\left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.} \right) + \text{K.E.}
+\mathcal{H}_\text{SIAM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow} - t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)
 \end{equation}
-This model, of course, does not show any impurity phase transition. Correlation can be introduced into the auxiliary model in two ways:
+This model does not show any impurity phase transition - the impurity is always screened~\cite{hrk_wilson_1980,wilson1975,bullaNRGreview}.
+Correlation can be introduced into the auxiliary model in two ways:
 \begin{itemize}
@@
 \begin{gather}
-H_\text{aux} = H_\text{SIAM} + J \vec{S}_d\cdot\vec{s}_0\\
-H_\text{aux} = H_\text{SIAM} + J \vec{S}_d\cdot\vec{s}_0 - U_b \left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
+\mathcal{H}_\text{aux} = H_\text{SIAM} + J \vec{S}_d\cdot\vec{s}_0\\
+\mathcal{H}_\text{aux} = H_\text{SIAM} + J \vec{S}_d\cdot\vec{s}_0 - U_b \left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
 \end{gather}
@@
 \begin{equation}
-H_\text{aux} = -\frac{U}{2}\sum_{d_i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right) ^2 + V\sum_{d_i}\sum_\sigma\left( c^\dagger_{d_i\sigma}c_{0\sigma} + \text{h.c.} \right) + \text{K.E.} - t\sum_{\sigma}\left(c^\dagger_{d_1\sigma}c_{d_2\sigma} + \text{h.c.}\right)
+\mathcal{H}_\text{aux} = -\frac{U}{2}\sum_{d_i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right) ^2 + V\sum_{d_i}\sum_\sigma\left( c^\dagger_{d_i\sigma}c_{0\sigma} + \text{h.c.} \right) + \text{K.E.} - t\sum_{\sigma}\left(c^\dagger_{d_1\sigma}c_{d_2\sigma} + \text{h.c.}\right)
 \end{equation}
@@
  \end{figure}
- The next step in the programme is to tile the real-space lattice with this cluster+bath Hamiltonian \(\tilde H\) to restore translational invariance (shown in a later section), and obtain a new bulk Hamiltonian for correlated electrons, $\tilde H = T\left[ H_\text{aux} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the cluster-bath (auxiliary model) Hamiltonian to span the target real-space lattice.
-Given a general auxiliary model Hamiltonian \(H_\text{aux}\), the result of tiling can be written very generally as
- \begin{equation}\begin{aligned}
-	 \tilde H = \sum_{\left\{i_1,i_2,...\right\}} H_\text{aux}\left(\left\{i_1,i_2,...\right\}\right)
+ The next step in the programme is to tile the real-space lattice with this cluster+bath Hamiltonian \(\tilde H\) to restore translational invariance (shown in a later section), and obtain a new bulk Hamiltonian for correlated electrons, $\tilde H = T\left[ \mathcal{H}_\text{aux} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the cluster-bath (auxiliary model) Hamiltonian to span the target real-space lattice.
+Given a general auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}\), the result of tiling can be written very generally as
+ \begin{equation}\begin{aligned}
+	 \tilde H = \sum_{\left\{i_1,i_2,...\right\}} \mathcal{H}_\text{aux}\left(\left\{i_1,i_2,...\right\}\right)
  \end{aligned}\end{equation}
@@
 
-The strong-coupling regime is defined as the range of values of \(\omega\) where the hybridisation is relevant.
+The strong coupling regime is defined as the range of values of \(\omega\) where the hybridisation is relevant.
 This is ensured by the assumption \(d_1<0\).
@@
 
-The coupling \(J\), on the other hand, is relevant and flows from a small positive value towards a large value at strong-coupling.
-\begin{equation}\begin{aligned}
-	\Delta J= -\frac{n_j J^2}{d_2} = \frac{n_j J^2}{|d_2|} > 0 \implies J_{j+1} > J_j \implies J_0 \to \text{ large } J^* ~(\text{strong-coupling})
+The coupling \(J\), on the other hand, is relevant and flows from a small positive value towards a large value at strong coupling.
+\begin{equation}\begin{aligned}
+	\Delta J= -\frac{n_j J^2}{d_2} = \frac{n_j J^2}{|d_2|} > 0 \implies J_{j+1} > J_j \implies J_0 \to \text{ large } J^* ~(\text{strong coupling})
 \end{aligned}\end{equation}
@@
 
-The strong-coupling regime here corresponds to \(d_0 < 0\).
+The strong coupling regime here corresponds to \(d_0 < 0\).
 This again means that all the denominators are negative.
 The spin-exchange coupling \(J\) is now irrelevant, because its bare value is negative while its RG equation is positive: \(\Delta J>0\).
-Moreover, the isospin coupling \(K\) is now positive and so is its RG equation: \(\Delta K>0\), which means it flows to strong-coupling.
-\(V\) also flows to strong-coupling.
+Moreover, the isospin coupling \(K\) is now positive and so is its RG equation: \(\Delta K>0\), which means it flows to strong coupling.
+\(V\) also flows to strong coupling.
 The RG equation for \(U\) can be written as
@@
 In other words, the RG flows in this regime can be exactly mapped to those in the positive \(U\) regime.
-The general statement is: in the strong-coupling regime of positive(negative) \(U\), \(V\) is always relevant, \(J\)(\(K\)) is relevant, \(K\)(\(J\)) is irrelevant, and \(U\) is relevant when \(J(K) > V\), otherwise \(U\) is irrelevant.
+The general statement is: in the strong coupling regime of positive(negative) \(U\), \(V\) is always relevant, \(J\)(\(K\)) is relevant, \(K\)(\(J\)) is irrelevant, and \(U\) is relevant when \(J(K) > V\), otherwise \(U\) is irrelevant.
 
@@
 
-We also wish to point out that this scattering is a signature of the change in Luttinger's count in going from the free orbital or local moment fixed point to the strong-coupling fixed point, as shown in eq.~\eqref{luttinger_change}.
+We also wish to point out that this scattering is a signature of the change in Luttinger's count in going from the free orbital or local moment fixed point to the strong coupling fixed point, as shown in eq.~\eqref{luttinger_change}.
 Both this off-diagonal scattering as well as the change in Luttinger's count are a direct consequence of the non-number conserving term \(V c^\dagger_{k} c_d\) in the full Hamiltonian.
@@
 
-In the strong-coupling regime, we have \(J,V \gg U\), and we can then approximate:
+In the strong coupling regime, we have \(J,V \gg U\), and we can then approximate:
 \begin{equation}\begin{aligned}
@@
 
-We will now look at the extreme strong-coupling regime \(J \gg V \gg U,t\). There, all the expressions simplify:
+We will now look at the extreme strong coupling regime \(J \gg V \gg U,t\). There, all the expressions simplify:
 \begin{gather}
@@
 
-\section{Destruction of the Abrikosov-Suhl resonance: passage from strong-coupling to local moment}
+\section{Destruction of the Abrikosov-Suhl resonance: passage from strong coupling to local moment}
 
 We will now tune the parameters of the fixed point Hamiltonian and study the variation of quantities related to the effective Hamiltonian like the local FL strength \(\mathcal{F}\), the gap in the spectrum of the zeroth Hamiltonian \(H_0^*\) and the value of the small parameter \(t^2/\delta E\), as well as various measures of entanglement like entanglement entropy, mutual information and spin-spin correlations between various sets of members of the real-space impurity+lattice construction.
-We will trace a specific path through the space of values of fixed point couplings: we will start from the strong-coupling regime \(U \ll J,V\) and go towards the local moment regime \(U \gg J,V\).
+We will trace a specific path through the space of values of fixed point couplings: we will start from the strong coupling regime \(U \ll J,V\) and go towards the local moment regime \(U \gg J,V\).
 The context of this study is that the technique of dynamical mean-field theory (DMFT) obtains a metal-insulator transition in the 2D Hubbard model by studying the Anderson impurity model as the auxiliary system for the Hubbard; there, the local moment regime of the impurity corresponds to the insulator in the bulk.
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=1_over_U,V=3J,N=4,U=1.000,1.000,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=1_over_U,V=3J,N=4,U=1.000,1.000,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=1_over_U,V=3J,N=4,U=1.000,1.000,50.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
 \end{center}
-The vanishing of the Kondo cloud at large \(U/J\) is clear indication of the destruction of the Kondo cloud and the breakdown of screening.
-Non-zero mutual information indicates an (impurity-mediated) interaction between the \(k-\)states of the conduction bath; seen differently, it is this interaction that is responsively for the screening of the impurity.
-The disappearance of the mutual information is indicative of the disappearance of this interaction.
+
+The mutual information \(I(d:k)\) between the impurity and the cloud vanishes as \(U/J\) is increased.
+This is a signature of the loss of entanglement and the breakdown of the singlet.
+The reduction of the mutual information within the cloud, \(I(k_1:k_2)\), shows that the Kondo cloud is being killed as \(U/J\) is increased; it ultimately drops to zero, characteristic of a decoupled tight-binding chain.
+The four-Fermion off-diagonal term also vanishes as \(U/J\) increases and this is again a signature of the reduction in the spin-flip processes.
+The diagonal correlation \(\left<\hat n_{k \uparrow} \hat n_{q \downarrow} \right>\) increasing to 1 shows the formation of a filled Fermi sea.
 
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
 \end{center}
@@
 The mutual information between the impurity and sites beyond the zeroth site (\(I(d:1)\)) show a non-monotonic behaviour; it first increases as the entanglement that was initially restricted to just the impurity and the zeroth sites begins "seeping" into the other sites as well.
-Beyond a critical value of \(U/J\), \(I(d:1)\) starts dropping, because the entanglement has now mostly shifted out of the zero mode and into the conduction bath.
+Beyond a critical value of \(U/J\), \(I(d:1)\) starts dropping, because the entanglement has now mostly shifted out of the singlet and into the conduction bath.
 
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
 
@@
 At sufficiently low values of \(J/U\), the impurity decouples from the zeroth site and the total system can be factorised into a local moment in product with a tight-binding chain, so that the impurity site will now have zero entanglement entropy.
+The spin-spin correlation \(\vec{S}_d\cdot\vec{S}_0\) is most negative at large \(J\), showing maximum screening at strong-coupling.
+It decreases to 0 as the singlet breaks.
+This reduction in the spin-spin correlation between the impurity and the zeroth site is accompanied by the appearance of antiferromagnetic spin-spin correlation \(\vec{S}_0\cdot\vec{S}_1, \vec{S}_0\cdot\vec{S}_3\) between the zeroth site and odd-numbered sites like 1 and 3.
+This can be understood on the following grounds:since the tight-binding hopping only connects same spin states, an electron on the first site has to have spin opposite to that on the zeroth site in order to hop onto that site.
+This requirement of opposite spin is what induces an antiferromagnetic superexchange interaction \(J_1\) between the zeroth site and the first site.
+This interaction strength increases as \(J\) is decreased, because \(J_1 \sim t^2/J\).
+By the same argument, a ferromagnetic superexchange interaction is induced between the impurity site and the first site, as well as between the zeroth site and the other even-numbered sites.
+These are also seen in the plots.
 
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=1_over_U,V=J,N=4,U=0.016,91.116,32.pdf}
-
-	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=1_over_U,V=3J,N=4,U=1.000,1.000,50.pdf}
+
+	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
 \end{center}
+
+The increase of single-particle hopping correlation is another signature of the "handover" of entanglement from the singlet to the tight-binding chain.
+Exactly the same can be said for the four-Fermion interaction as well.
 
@@
 \begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/corr-di-min-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/corr-di-max-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-
-	\includegraphics[width=0.45\textwidth]{../figures/corr-all-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/I-all-t=1.000,J=1_over_U,V=J,N=6,U=0.016,91.116,32.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/corr-di-min-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/corr-di-max-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+
+	\includegraphics[width=0.45\textwidth]{../figures/corr-all-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/I-all-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
 \end{center}
+
+The first thing to note in the first two figures is the difference in the order of magnitudes; the correlations are very small in the first figure, because the impurity is being screened almost completely by the zeroth site at \(J \gg U\).
+This changes in the second figure where, because \(U \gg J\), the singlet has become entangled with the other sites, and the impurity is being screened by multiple sites.
+The mutual information all vary similarly with distance in the bottom right figure.
 
@@
 
-We have also not accounted for the RG flow from the local moment fixed point to the strong-coupling fixed point. The local moment fixed point is characterized by a decoupled quantum top:
+We have also not accounted for the RG flow from the local moment fixed point to the strong coupling fixed point. The local moment fixed point is characterized by a decoupled quantum top:
 \begin{equation}\begin{aligned}
@@
 \textit{Right}: Mutual information between a conduction electron inside the cloud and an impurity electron.
-Both the measures increase towards the strong-coupling fixed point, because of the distillation of the Kondo cloud brought about by the RG flow.}
+Both the measures increase towards the strong coupling fixed point, because of the distillation of the Kondo cloud brought about by the RG flow.}
 	\label{mutI}
@@
 	\includegraphics[width=0.45\textwidth]{../figures/corr_opp.pdf}
-	\caption{Increase in the diagonal correlation functions between cloud electrons under RG flow towards the strong-coupling fixed point.
+	\caption{Increase in the diagonal correlation functions between cloud electrons under RG flow towards the strong coupling fixed point.
 This is consistent with the Fermi liquid pieces generated in the \(k-\)space effective Hamiltonian of the Kondo cloud.}
@@
 	\includegraphics[width=0.45\textwidth]{../figures/corr_od.pdf}
-	\caption{Growth of the off-diagonal correlation function between Kondo cloud electrons towards the strong-coupling fixed point.
+	\caption{Growth of the off-diagonal correlation function between Kondo cloud electrons towards the strong coupling fixed point.
 This is the direct cause of the screening of the impurity spin, and is a reflection of the off-diagonal two-particle scattering terms in the \(k-\)space effective Hamiltonian of the Kondo cloud.}
@@
 \subsection*{Perturbation theoretic terms}
-These quantities are related to the local Fermi liquid of the Kondo strong-coupling fixed point and the perturbation theory associated with it.
+These quantities are related to the local Fermi liquid of the Kondo strong coupling fixed point and the perturbation theory associated with it.
 \(min(\delta E)\) is the gap in the spectrum of the two-site Hamiltonian; this which acts as the denominator for the perturbation theoretic calculations.
@@
 	\label{map_aux_bulk}
-	t_{H-H} = \left(2t (N-2) - \frac{2V}{N}\right),~ ~ U_{H-H} = \left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{w}
+	t_{H-H} = \left(2t (N-2) - \frac{2V}{w}\right),~ ~ U_{H-H} = \left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{w}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\mathcal{G}_{H-H} = \frac{1}{\omega^\prime - \left(H_{H-H} - E_\text{gs}^\prime\right) }, \mathcal{G}_\text{aux}(i) = \frac{1}{\omega - \left(H_\text{aux}(i) - E_\text{gs}\right)}
+	\mathcal{G}_{H-H} = \frac{1}{\omega^\prime - \left(H_{H-H} - E_\text{gs}^\prime\right) }, \mathcal{G}_\text{aux}(i) = \frac{1}{\omega - \left(\mathcal{H}_\text{aux}(i) - E_\text{gs}\right)}
 \end{aligned}\end{equation}
@@
 We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model.
-Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(H_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate.
+Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(\mathcal{H}_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate.
 We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
@@
 \end{aligned}\end{equation}
-There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(H_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\).
+There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(\mathcal{H}_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\).
 We also defined \(d^p_n = \bra{\Phi_n}c^\dagger_{d\sigma}\ket{\Phi_0}\).
@@
 \begin{equation}\begin{aligned}
-	H_\text{aux} = 
-\end{aligned}\end{equation}
-
-In this chapter, we will improve the formalism by considering a larger cluster that has two impurities interacting with each other:
+	\mathcal{H}_\text{aux} =  \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s}_0 - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
+\end{aligned}\end{equation}
+This was able to describe an impurity phase transition from screened strong-coupling phase to local moment weak coupling phase, upon tuning \(U_b/J\).
+This then leads to a metal-insulator transition in the bulk, owing to the relations between the Greens functions and spectral functions obtained earlier.
+The single-site nature of the cluster (there was only a single impurity) has the following consequences:
+\begin{itemize}
+	\item [1.] The \(k-\)space self-energy of the bath has only minimal \(k-\)dependence arising from nearest-neighbour non-locality between the impurity and the zeroth site of the bath.
+	\item [2.] The local moment phase (which reduces to a set of decoupled clusters) becomes just the atomic limit, because each cluster has just one impurity.
+\end{itemize}
+
+In this chapter, we will improve on these two points by considering a larger cluster that has two impurities interacting with each other:
 \begin{equation}\begin{aligned}
 	\label{dimer_ham}
-	H_\text{CL} = \mathcal{H}_D = -t^A\sum_{\sigma, i=1,2}\left(c^\dagger_{d_i\sigma}c_{z\sigma} + \text{h.c.}\right) - \frac{U^A}{2}\sum_{i=1,2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 - t^A \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-The name \(\mathcal{H}_D\) is used to indicate that the impurity sites now form a dimer interacting with a bath.
+	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right]\\
+	 -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right) + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
+\end{aligned}\end{equation}
 \(d_1\) and \(d_2\), or \(d_i\) in general, represent the two impurity sites in the dimer.
-Note that this chapter only sets out the relations between such an auxiliary model and the corresponding bulk model (in this case, a Hubbard), but does not describe the physics of this auxiliary model.
-That requires performing a renormalisation group calculation for \(H_\text{CL}\), and that will be provided at a later point in time.
+They interact with each other through the same hopping parameter \(t\) as the bath.
+Each of the impurities has its own correlation \(U\) and hybridisation with the bath through \(V\) and \(J\).
+Each impurity site \(d_i\) couples with a bath site \(0_i\).
+\(0_1\) and \(0_2\) are assumed to be adjacent to each other, connected by the hopping \(t\).
+The setup is shown in fig.~\ref{two-imp-cluster}.
+
+Note that this chapter only sets out the relations between such an auxiliary model and the corresponding bulk model (in this case, a Hubbard-Heisenberg), but does not describe the physics of this new auxiliary model.
+That requires performing a renormalisation group calculation for \(H_\text{aux}\), and that will be provided at a later point in time.
 
@@
 	\centering
-	\includegraphics[width=0.2\textwidth]{../figures/dimer_dispersion.png}
+	\includegraphics[width=0.6\textwidth]{../figures/two-site-cluster.pdf}
 	\caption{Two-impurity SIAM hybridising with a bath}
+	\label{two-imp-cluster}
 \end{figure}
@@
 \section{Creating \(N-\)site Hubbard Hamiltonian from Hubbard dimer embedded in a bath}
-We will follow the strategy outlined in the previous section.
+Similar to the previous chapterm, we will now tile the lattice with the two-site auxiliary model
+\begin{equation}\begin{aligned}
+	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right]\\
+	 -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right) + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
+\end{aligned}\end{equation}
 For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site.
@@
 This is achieved by applying periodic boundary conditions on the edges of the lattice.
-A square 2d lattice is thus placed on a 2-torus.
-
-For each nearest-neighbour pair \(i,j\), we will create a local Hamiltonian \(H^D_{i,j}\) from the Hamiltonian of the Hubbard dimer with bath (we will interpret the effective bath as the remaining \(N-2\) sites of the lattice, apart from \(i,j\)).
-We will need to suitably transform the Hamiltonian parameters \(U^D, t^D\), but we will figure those out as we go along.
-Since the number of nearest neighbour pairs is \(\frac{Nw}{2}\), the general Hubbard Hamiltonian should be the average of these local Hamiltonians.
-
-We recall the dimer+bath Hamiltonian here, since we are going to create the full Hamiltonian by combining various realizations of that Hamiltonian:
-\begin{equation}\begin{aligned}
-	\tilde H^D = H^D(0,1) - t^D \left(c^\dagger_{0\sigma}c_{z\sigma} + c^\dagger_{1\sigma}c_{z\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}
-\end{aligned}\end{equation}
-We now choose a particular nearest neighbour pair from the full lattice, say \((i,j\), and one site that is nearest neighbour to this pair, call that \(l\).
-We will first create a "local" Hamiltonian, where one particular nearest neighbour pair \((i,j)\) makes up the dimer sites of the Hamiltonian, while the rest \(N-2\) sites of the lattice make up the effective bath and the site \(l\) forms the zeroth site of the bath.
-\begin{equation}\begin{aligned}
-	\label{Hdjl}
-	\tilde H^D(i, j, l) \equiv \tilde H^D(0\to i, 1\to j, z \to l) = H^D(i, j) - t^D \sum_{\sigma}\left(c^\dagger_{i\sigma}c_{l,\sigma} + c^\dagger_{j\sigma}c_{l,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^{\text{eff.
-bath (i,j)}\atop{z = l}}\epsilon_{\vec k}\hat n_{\vec k}\\
-\end{aligned}\end{equation}
-\(H^D(i, j)\) is the Hubbard dimer Hamiltonian in eq.~\ref{dimer_ham} with the indices 0 and 1 replaced by \(i, j\) respectively.
-This is not the total local Hamiltonian for the nearest neighbour pair \((i,j\), because it has just one nearest neighbour of the dimer, namely \(l\).
-To get the full thing, we need to \textit{average} over all the nearest neighbours of the pair \(i,j\), \(2(w-1)\) in number.
-What we mean by nearest neighbours of the dimer pair \((i,j)\) is made clear in \ref{dimer-nn}.
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.3\textwidth]{../figures/dimer-nn.pdf}
-	\caption{Blue circles (enclosed by the oval) indicate the dimer sites.
-Green circles are the sites that are nearest neighbour to the dimer and the ones that are being summed over under the index \(l\).
-The red circles are sites that are \textit{not} nearest neighbour to the dimer.}
-	\label{dimer-nn}
-\end{figure}
-
-The total  Hamiltonian for a particular dimer pair \((i,j)\) then looks like:
-\begin{equation}\begin{aligned}
-	\tilde H^D(i, j) &= \frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}} \left[H^D(i, j) - t^D \sum_{\sigma}\left(c^\dagger_{i\sigma}c_{l,\sigma} + c^\dagger_{j\sigma}c_{l,\sigma} + \text{h.c.}\right) + \sum_{\vec k}^{\text{eff.
-bath (i,j)}\atop{z = l}}\epsilon_{\vec k}\hat n_{\vec k}\right]\\
-			 &= H^D(i, j) + \frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\left[- t^D \sum_\sigma\left(c^\dagger_{i\sigma}c_{l,\sigma} + c^\dagger_{j\sigma}c_{l,\sigma} + \text{h.c.}\right) + \sum_{\vec k,\sigma}^{\text{eff.
-bath (i,j)}\atop{z = l}}\epsilon_{\vec k}\hat n_{\vec k}\right]
-\end{aligned}\end{equation}
-We now translate this Hamiltonian over all nearest neighbour pairs on the lattice, and take the average:
-\begin{equation}\begin{aligned}
-	\label{H_tiled}
-	\tilde H = \frac{2}{Nw}\sum_{\left<ij\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\tilde H^D(i, j, l) = \frac{2}{N}U^D\sum_{i} \tau_{i \uparrow}\tau_{i \downarrow} - \frac{2}{Nw}\left(1 + \frac{Nw}{2}\right)t^D\sum_{\left<ij\right>}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-The sum $\left<ij\right>$ is over all nearest-neighbour pairs. 
-The conclusion is that on tiling the Hubbard dimer+bath Hamiltonians into all the nearest neighbour pairs, we end up with a new Hubbard model Hamiltonian with "renormalised parameters" given by
-\begin{equation}\begin{aligned}
-	\tilde t = \frac{2}{Nw}(1 + \frac{Nw}{2})t^D, &&\tilde U = \frac{2}{N}U^D
-\end{aligned}\end{equation}
-It is thus apparent that translating the Hubbard dimers throughout the lattice has restored translational invariance, and generated correlations on all sites. 
-With some knowledge of the RG procedure, one can even write down the relation between the Hubbard dimer couplings $t^D, U^D$ and the parent Hubbard model parameters $t^H, U^H$.
-We have seen previously in another work that in the absence of any explicit spin or charge isospin exchange couplings, the impurity-bath hybridisation coupling $t^A$ does not flow under the RG.
-In going from the Hubbard model to the auxiliary model, we replace the non-local operator $c_i$ with the local operator $c_d$.
-If we define the normalization of the Fourier transform such that both spaces have $\frac{1}{\sqrt N}$, then the auxiliary model coupling can be written as $t^A = \sqrt N t^H$.
-When we write the fixed-point hopping purely in terms of zero mode, another such factor appears: $\sum_k c_k = \sqrt N c_0$, such that $t^D = \sqrt N (t^A)*$.
-Combining these, we get
-\[ t^D = \sqrt N \times (t^A)^* = \sqrt N \times t^A = N \times t^H \]
-As for the on-site repulsion $U^H$, we will constrain the RG flows such that the fixed-point value of the impurity ons-te repulsion $U^A$ is identical to that of the on-site repulsion of the bath, $U_b$.
-A sensible choice for the bath on-site repulsion is simply $U^H\times N$.
-The factor of $N$ maintains the extensivity of the bath correlation term.
-We can therefore write
-\[U^D \equiv (U^A)* = U_b = N \times U^H\]
-\section{Formal expressions for single particle Greens functions and other related many-body quantites}
-\subsection{Expressing matrix elements of the inverse single particle Greens function in terms of Hubbard dimer counterparts}
-Since the two Hamiltonians $H^H$ and $\tilde H$ are connected via a similarity transformation $\mathcal{U}$, their ground states are also connected by the same transformation.
-That is, if the ground states are $\ket{\Phi_0}$ and $\ket{\tilde{\Phi_0}}$ respectively, then $\ket{\tilde{\Phi_0}} = \mathcal{U}\ket{\Phi_0}$.
-This means that matrix elements of the type in eq.~\ref{G_mat_el} will also be connected.
-The matrix elements are of the inverse Greebs function operator defined in eq.~\ref{inv_G_func}:
- \begin{equation}\begin{aligned}
-	 \mathcal{G}(\omega, H) = \frac{1}{\omega - (H - E_\text{GS})}
- \end{aligned}\end{equation}
-Its easy to see that the matrix elements of the original and renormalised versions of this operator, between the original and renormalised states, are equal:
-\begin{equation}\begin{aligned}
-	\left[\mathcal{G}_H^{-1}\right]_{\nu \nu^\prime} = \bra{\nu}\omega - H^H + E_\text{GS}\ket{\nu^\prime} = \bra{\nu} \mathcal{U}^{-1}\left(\omega -  \mathcal{U} H^H  \mathcal{U}^{-1} + E_\text{GS}\right)  \mathcal{U}\ket{\nu^\prime} = \bra{\tilde \nu}\left(\omega - \tilde H + E_\text{GS}\right)\ket{\tilde \nu^\prime}\\
-	= \left[\mathcal{\tilde G}^{-1}\right]_{\tilde \nu,\tilde \nu^\prime}
-\end{aligned}\end{equation}
-where we have defined the renormalised excitation $\ket{\tilde {\nu^\prime}} \equiv \tilde c^\dagger_{\nu^\prime}\ket{\tilde \Phi_0} \equiv  \left(\mathcal{U} c^\dagger_{\nu^\prime}  \mathcal{U}^{-1}\right)  \mathcal{U}\ket{\Phi_0} =  \mathcal{U}\ket{{\nu^\prime}}$.
-These equalities are important because they allows us to calculate these matrix elements for $\tilde H$ and then equate them to those of $H^H$, and once we have the matrix elements of $\mathcal{G}$, we can use them to obtain the single-particle Greens functions using eq.~\ref{G_mat_el}.
-More specifically, to calculate the real space single-particle Greens function between the lattice sites $i$ and $j$, both with spin $\sigma$, we will use the relation:
-\begin{equation}\begin{aligned}
-	G(i\sigma, j\sigma, \omega) = \bra{ i\sigma} \mathcal{G}(\omega, H) \ket{ j\sigma} - \bra{\overline{i\sigma}} \mathcal{G}(-\omega, H) \ket{\overline {j\sigma}} = \mathcal{G}(\omega, H)_{ i\sigma, j\sigma} - \mathcal{G}(-\omega, H)_{\overline{i\sigma}, \overline {j\sigma}}
-\end{aligned}\end{equation}
-where $\ket{i\sigma}=c^\dagger_{i\sigma}\ket{\Phi_0}$ and $\ket{\overline{i\sigma}}=c_{i\sigma}\ket{\Phi_0}$.
-We can see from the relation that we will need two types of matrix elements, one that propagates a particle excitation $\left( \ket{i\sigma} \right) $ and the one that propagates a hole excitation $\ket{\overline{i\sigma}}$.
-
-To this end, we rewrite eq.~\ref{H_tiled} in terms of inverse Greens function operators for the new (symmetrized) Hubbard model and the Hubbard dimer respectively:
-\begin{equation}\begin{aligned}
-	\label{Gd_op}
-	\mathcal{\tilde G}(\omega) = \frac{1}{\omega - \left(\tilde H - E_\text{GS}\right)}, && \mathcal{G}_D(\omega) = \frac{1}{\omega - \left(\tilde H^D(i,j,l) - E_\text{GS}\right)}
-\end{aligned}\end{equation}
-These are the same operators that appear in the appendix.
-However, before proceeding, we should note that even though eq.~\ref{H_tiled} used the indices $i,$, the correct indices are actually $\tilde i, \tilde j$, in light of the fact that operators get renormalised as $c_i \to \tilde c_i\equiv Uc_i$.
-With this in mind, we can write
-\begin{equation}\begin{aligned}
-	\label{green_eq}
-	\omega - \mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<\tilde i, \tilde j\right>} \frac{1}{2(w-1)} \sum_{l \in \text{NN of j}}\left[\omega - \mathcal{G}_D^{-1}\left(\tilde i, \tilde j, \tilde l\right)\right]
-\end{aligned}\end{equation}
-where $\mathcal{G}_D^{-1}(\tilde i,\tilde j, \tilde l)$ is the Greens function inverse matrix of the Hubbard dimer+bath Hamiltonian with $\tilde i, \tilde j$ as the two sites and \(\tilde l\) as the zero mode of the bath, eq.~\ref{Hdjl}.
-Since the $\omega$ on the RHS of eq.~\ref{green_eq} is independent of the summation indices, they can be pulled out along with a factor.
-The factor is just the total number of nearest neighbour pairs, which is $\frac{Nw}{2}$.
-This allows it to cancel the $\omega$ on the LHS.
-The equation then simplifies to
-\begin{equation}\begin{aligned}
-	\mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\sum_{\left<i,j\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of j}}\mathcal{G}_D^{-1}\left(\omega, \tilde i, \tilde j, \tilde l\right)
-\end{aligned}\end{equation}
-Because of translational invariance, all values of \(l\) should give the same Greens function, and we can simplify this to
-\begin{equation}\begin{aligned}
-	\label{green_eq_final}
-	\mathcal{\tilde G}^{-1}(\omega) = \frac{2}{Nw}\frac{1}{2(w-1)}\times 2(w-1)\sum_{\left<i,j\right>}\mathcal{G}_D^{-1}\left(\omega, \tilde i, \tilde j\right) = \frac{2}{Nw}\sum_{\left<i,j\right>}\mathcal{G}_D^{-1}\left(\omega, \tilde i, \tilde j\right)
-\end{aligned}\end{equation}
-We dropped the index \(\tilde l\) on \(\mathcal{G}_D^{-1}\) to mean that any particular choice of \(\tilde l\) will do.
-We will now calculate the site-diagonal and site-off-diagonal matrix elements for particle propagation.
-The site-diagonal matrix element will be calculated between the state $\ket{\tilde i, \sigma} = \mathcal{U}c^\dagger_{i\sigma}\ket{\Phi_0}$ and its bra, while the off-diagonal one is between $\ket{\tilde j\sigma}$ and $\bra{\tilde i\sigma}$.
-Since it has already been shown that the matrix elements of the renormalised Hamiltonian are the same as those of the original Hamiltonian, we will directly replace the former with the latter.
-\\\\
-First lets consider the diagonal matrix element at $\tilde i^\text{th}$ site.
-The only terms that will contribute on the RHS of eq.~\ref{green_eq_final} are those that have the index $\tilde i$ on the dimer.
-There are $w$ terms that have the index \(\tilde i\) on the dimer corresponding to the $w$ nearest neighbours of \(\tilde i\).
-Thus, the right hand side will be a sum of $w$ terms, each term being the inverse Greens function of a Hubbard dimer+bath Hamiltonian.
-Each term will be a real space local Greens function, and because of translational invariance, it will be the same for all choices of the nearest neighbour of \(\tilde i\).
+For example, a square 2d lattice will have to be placed on a 2-torus.
+
+The first step is to identity the two impurity sites \(d_1\) and \(d_2\) and the two bath sites \(0_1\) and \(0_2\) as sitting on a square arrangement of the lattice.
+\(d_i\) form one arm of the square, while \(0_i\) form the opposite arm.
+This square arrangement is shown in fig.~\ref{square-arms}, and is dictated by the auxiliary model chosen and shown in fig.~\ref{two-imp-cluster}.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.3\textwidth]{../figures/square_arms.pdf}
+	\caption{Placing the impurity and bath sites \(d_i,0_i\) on a chosen square of the lattice. The chosen square is marked in blue, the impurity sites in orange and the bath sites in green.}
+	\label{square-arms}
+\end{figure}
+The sites at the vertices of the square are labelled as \(i,j,k,l\). With this identification, the Hamiltonian becomes
+\begin{equation}\begin{aligned}
+	H_\text{aux}(i,j,k,l) = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \frac{U}{2}\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.} + c^\dagger_{j\sigma}c_{l\sigma} + \text{h.c.}\right) + J \vec{S}_{i}\cdot\vec{s}_{k} \right.\\
++ \left.
+J \vec{S}_{j}\cdot\vec{s}_{l} - U_b\left(\hat n_{k \uparrow} - \hat n_{k \downarrow}\right)^2 - U_b\left(\hat n_{l \uparrow} - \hat n_{l \downarrow}\right)^2\right] -t \sum_\sigma \left(c^\dagger_{i,\sigma}c_{j,\sigma} + \text{h.c.}\right) -t \sum_{\left<m,n \right>, \sigma}^{m,n \notin \left\{i,j\right\}}\left(c^\dagger_{m\sigma,n\sigma} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+As before, the kinetic energy part sums over all nearest neighbour pairs that involve neither \(i\) nor \(j\).
+For a given arm \(i-j\), the square can be rotated along the axis \(i-j\) to give one square arrangements for each dimension perpendicular to the axis along \(i-j\).
+Since there are \(w/2\) dimensions, the number of such squares is \(w/2 - 1\).
+For each such square, we can obtain another square by reflecting the square in the plane of \(i-j-l-k-i\) and across the line \(i-j\).
+The total number of squares is therefore \(w - 2\).
+The upshot is that given \(i-j\), there are multiple ways of choosing \(k\); if \(\left\{\vec a\right\}\) represents the set of \(w\) primitive vectors that connect a particular lattice site to its nearest neighbours, \(k\) can be situated at all \(\vec r_i + \vec a\) for which \(\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0\).
+Choosing \(k\) then automatically fixes \(l\) at \(\vec r_j + \vec a\).
+The condition \(\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0\) simply means we only take those \(\vec a\) that are perpendicular to \(\vec r_j - \vec r_i\).
+Since there are \(w\) number of \(\vec a\) in total and 2 of them are parallel, the total number of choices of \(k,l\) is \(w-2\).
+For a 2D lattice, we have \(w=4\), so there are only two possible choices of the square.
+They are shown in fig.~\ref{square-arms-all}.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../figures/square_arms_all.pdf}
+	\caption{Placing the impurity and bath sites \(d_i,0_i\) on a chosen square of the lattice. The chosen square is marked in blue, the impurity sites in orange and the bath sites in green.}
+	\label{square-arms-all}
+\end{figure}
+
+The Hamiltonian for an arm \(i-j\) is then obtained by averaging over these squares:
+\begin{equation}\begin{aligned}
+	H_\text{aux}(i,j) = \frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
+\end{aligned}\end{equation}
+The final step is to sum over all nearest neighbour arms \(i-j\):
+\begin{equation}\begin{aligned}
+	\label{22siam_to_hubb}
+	H_\text{full} = \sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
+\end{aligned}\end{equation}
+
+There are four kinds of terms: the first kind, \(A(i), A(j)\), depend only on either \(i\) or \(j\).
+They can be summed over easily by noting that the internal summation gives a constant factor of \(w-2\) which is cancelled by the factor of \(1/(w-2)\) in the front, and the external summation gives \(\sum_{i,j}A(i) = \frac{w}{2} \sum_i A(i)\), because \(i\) is a member of \(w/2\) distinct nearest-neighbour pairs.
+The second kind, \(B(i,j)\) depends on both \(i\) and \(j\).
+The internal summation is again cancelled by the prefactor.
+The external summation simply sums over all nearest-neighbour values of \(A(i,j)\).
+The third kind, \(C(i,k), C(j,l)\), depend on \(i\) and \(k\).
+Here, the total summation \(\sum_{i,j,k}C(i,k)\) gives \((w-2)\sum_{\left<i,k\right>}\left(C(i,k) + C(k,i)\right)\), because the pair \((i,k)\) occurs \(w-2\) times corresponding to the \(w-2\) vectors \(\vec r_j - \vec r_i\) that are perpendicular to \(\vec r_i - \vec r_k\).
+The factor is again cancelled by the existing prefactor.
+The fourth kind, \(D(k), D(l), E(k,l)\), depend on just \(k\), just \(l\) or both \(k\) and \(l\).
+For each pair \(i-j\) in the external summation, the particular pair \(k-l\) appears only once.
+When \(i-j\) is summed over, a factor of \(2(w/2-1)\) is generated because there are that many squares that involve \(k-l\).
+This factor cancels the inverse factor in front, giving \(\sum_{\left<k\right>} D(k), \sum_{\left<k,l \right>}E(k,l)\).
+The full Hamiltonian reads
+\begin{equation}\begin{aligned}
+	H_\text{full} =& w\sum_i\left[- \frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\right] - t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + 4V\sum_{\sigma, \left<i,k\right>}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.}\right)\\
+		      &+ 4J \sum_{\left<i,k\right>}\left(\vec{S}_{i}\cdot\vec{S}_{k}\right) - 2 U_b\sum_k\left(\hat n_{k \uparrow} - \hat n_{k \downarrow}\right)^2 - \frac{Nw/2}{w-2}t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)\\
+	=& -\frac{1}{2}\left(Uw - 2U_b\right)^2\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{Nw/2}{w-2}t + t - 4V\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 4J \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
+\end{aligned}\end{equation}
+The bulk model hence obtained is again a Hubbard-Heisenberg model.
+In eq.~\ref{2siam_to_hubb}, the total number of terms in the outer summation is \(Nw/2\).
+In order to make sure that this full Hamiltonian scales as \(N\), we divide this by \(w\):
+\begin{equation}\begin{aligned}
+	\label{2siam_to_hubb}
+	H_\text{full} &= \frac{1}{w}\sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
+		      &= -\left(U/2 - U_b/w\right)^2\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{N}{2w-4}t + t/w - 4V/w\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 4J/w \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
+\end{aligned}\end{equation}
+The mappings between the parameters of the auxiliary model and the bulk are
+\begin{equation}\begin{aligned}
+	t_\text{H-H} = \left(\frac{N}{2w-4}t + t/w - 4V/w\right),~ ~ ~ U_\text{H-H} = \left(U/2 - U_b/w\right),~ ~ ~ J_\text{H-H} = 4J/w
+\end{aligned}\end{equation}
+
+\section{Single-particle Green's function}
+We now define the Greens function {\it operators}:
+\begin{equation}\begin{aligned}
+	\mathcal{G}_{H-H} = \frac{1}{\omega^\prime - \left(H_{H-H} - E_\text{gs}^\prime\right) }, \mathcal{G}_\text{aux}(i,j) = \frac{1}{\omega - \left(\mathcal{H}_\text{aux}(i,j) - E_\text{gs}\right)}
+\end{aligned}\end{equation}
+Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian, while the primed quantities \(E_\text{gs}^\prime\) and \(\omega^\prime\) are the same quantities but for the full model \(\mathcal{H}_{H-H}\).
+While the auxiliary model is intensive, the full Hamiltonian is extensive and scales as \(N\).
+This means that we must have \(\omega^\prime = N\omega\) and \(E_\text{gs}^\prime = N E_\text{gs}\).
+Rewriting eq.~\ref{2siam_to_hubb} in terms of the operators \(\mathcal{G}\), we get
+\begin{equation}\begin{aligned}
+\sum_{\left<i,j \right>} \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i,j)\right) = N\omega + N E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_{\left<i,j \right>} \mathcal{G}^{-1}_\text{aux}(i,j) = \mathcal{G}^{-1}_{H-H}~,
+\end{aligned}\end{equation}
+We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model.
+Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(\mathcal{H}_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate.
+We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0}
+\end{aligned}\end{equation}
+The superscript \(p\) indicates that this is the particle propagation matrix element.
+Under the auxiliary model approximation, we ignore the virtual entanglement between separate clusters.
+Therefore, the only operators \(\mathcal{G}^{-1}_\text{aux}(k,l)\) that affect the matrix element are those that satisfy \(i \in \left(k,l\right)\).
+There are \(w\) such pairs: \(\left\{k,l\right\} = \left\{i,j\right\} \text{ such that } j \in \text{NN of i}\).
+Moreover, because of translation invariance, all \(j \in \text{NN of i}\) are equivalent.
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{w} \times w \times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i, i+1) c^\dagger_{i\sigma} | \Phi_0} = \braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}
+\end{aligned}\end{equation}
+where we have identified site \(i\) in the auxiliary model as one of the impurities \(d_1\).
+We could very well have chosen \(d_2\) since the model is symmetric in \(d_1,d_2\).
+\(\mathcal{G}^{-1}_\text{aux}(d_1,d_2)\) is the Greens operator corresponding to the Hamiltonian in eq.~\ref{dimer_ham}.
+
+By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}\), we get from the spectral representation
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{m,n} \braket{\Phi_0 | c_{d_1\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux} \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d_1\sigma} | \Phi_0} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+\end{aligned}\end{equation}
+There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(\mathcal{H}_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\).
+We also defined \(d^p_{1,n} = \bra{\Phi_n}c^\dagger_{d_1\sigma}\ket{\Phi_0}\).
+The hole propagation matrix element can be obtained similarly:
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn} 
+\end{aligned}\end{equation}
+where \(d^h_{1,n} = \bra{\Phi_n}c_{d_1\sigma}\ket{\Phi_0}\).
+The off-diagonal matrix elements between two sites \(i\) and \(j\) can also be obtained similarly.
+Only that auxiliary model contributes that has \(\left\{k,l\right\} = \left\{i,j\right\}\):
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{i,j} \equiv \braket{\Phi_0 | c_{i,\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{j,\sigma} | \Phi_0} = \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i,j) c^\dagger_{j,\sigma} | \Phi_0} = \frac{1}{w}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux} c^\dagger_{d_2,\sigma} | \Phi_0}
+\end{aligned}\end{equation}
+We again define matrix elements \(d_{2,n}^p = \braket{\Phi_n | c^\dagger_{d_2\sigma} | \Phi_0}, d_{2,n}^h = \braket{\Phi_n | c_{d_2\sigma} | \Phi_0}\).
+Thus, the spectral representation of the matrix element is obtained as
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,j} = \frac{1}{w}\sum_n \left(d^p_{1,n}\right)^* d^p_{2,n} \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}
+\end{aligned}\end{equation}
+The hole counterpart is
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,j} = \frac{1}{w}\sum_n \left(d^h_{1,n}\right)^* d^h_{2,n} \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}
+\end{aligned}\end{equation}
+In summary, the spectral representation of the matrix elements of the four inverse Greens operators are given by
 \begin{gather}
-	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{Nw}\sum_{j \in \text{NN of i}}\bra{\tilde \Phi_0}c_{i\sigma}\mathcal{G}_{D}^{-1}(\omega, \tilde i, \tilde j)c^\dagger_{i\sigma}\ket{\tilde \Phi_0} = \frac{2}{N}\bra{\tilde \Phi_0}c_{i\sigma}\mathcal{G}_{D}^{-1}(\omega, \tilde i)c^\dagger_{i\sigma}\ket{\tilde \Phi_0}
+\label{green_eq_final_siam}
+	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn}\\
+	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,j} = \frac{1}{w}\sum_n \left(d^p_{1,n}\right)^* d^p_{2,n} \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,j} = \frac{1}{w}\sum_n \left(d^h_{1,n}\right)^* d^h_{2,n} \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}
 \end{gather}
-Once we have stripped away the \(j,l\) dependence, we can view the RHS as simply the matrix element of the dimer-bath Hamiltonian eq.~\ref{dimer_ham} between the local states of the site zero of the bath:
+
+In order to obtain the matrix elements of the Greens operators \(\mathcal{G}_{H-H}\) (as compared to its inverse), we note that we have just observed that the matrix elements of the inverse Greens operators are related to the matrix elements of another inverse operator through some coefficients.
+We can, therefore, use the identity
+\begin{equation}\begin{aligned}
+\left(\hat O\right)_{ij} = \bra{i} \hat O \ket{j} = \sum_{m,n} \braket{i|m} \left(\hat O\right)_{mn} \braket{n|j} \implies \left(\hat O^{-1}\right)_{ij} = \sum_{m,n} \braket{i|m} \left(\hat O^{-1}\right)_{mn} \braket{n|j}
+\end{aligned}\end{equation}
+We can now identify \(\left(\hat O^{-1}\right)_{mn}\) as the matrix elements of \(\mathcal{G}_\text{aux}^{-1}\) in our expressions.
+Using the above relation, we can therefore write the spectral representation of the matrix elements of the Greens operators as
 \begin{gather}
-	\label{local_gf}
-	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{N}\bra{\tilde \Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{0\sigma}\ket{\tilde \Phi_0}
+	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\\
+	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,j} = \frac{1}{w}\sum_n \left(d^p_{1,n}\right)^* d^p_{2,n} \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,j} = \frac{1}{w}\sum_n \left(d^h_{1,n}\right)^* d^h_{2,n} \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}
 \end{gather}
-Just to make it explicit, we repeat once more that \(\mathcal{G}_{D}^{-1}(\omega)\) is the inverse Greens function operator of the Hamiltonian in eq.~\ref{dimer_ham}.
-We can expand the state $c^\dagger_{i\sigma}\ket{\tilde \Phi_0}$ in terms of a complete set of orthogonal states:
-\begin{equation}\begin{aligned}
-	c^\dagger_{0\sigma}\ket{\tilde \Phi_0} = \sum_n C^0_n \ket{n}, && c^\dagger_{1\sigma}\ket{\tilde \Phi_0} = \sum_n C^1_n \ket{n}
-\end{aligned}\end{equation}
-where $C^{0}$ and $C^{1}$ are coefficients of the linear superposition defined by
-\begin{equation}
-C^{0}_{n} = \bra{n} c^\dagger_{0\sigma}\ket{\tilde \Phi_0}~,~ C^{1}_{n} = \bra{n} c^\dagger_{1\sigma}\ket{\tilde \Phi_0}~.
-\end{equation}
-Due to the translation invariance, the coefficients $C^{0}_{n}$ and $C^{1}_{n}$ are independent of the site indices.
-The index $n$ actually defines a set of quantum numbers that characterize the state $\ket{n}$.
-For example it might be a combination of number of particles, parity and total spin angular momentum $(n \equiv n, P, S^z)$.
-In light of the Greens function we have in between te states, we choose the orthogonal set to be formed by the eigenstates of the dimer+bath Hamiltonian.
-
-Using this expansion, the matrix element of $\mathcal{G}$ can be written as
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{N}\sum_{nn^\prime} \left(C^0_{n^\prime}\right)^*\bra{n^\prime}\mathcal{G}_{D}^{-1}(\omega)\ket{n} C^0_{n}
-\end{aligned}\end{equation}
-Since $\ket{n}$ is an actual eigenstate of the Hamiltonian that defines \(\mathcal{G}_{D}^{-1}(\omega)\), $\mathcal{G}_{D}^{-1}(\omega)$ will be diagonal in that basis:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma = \frac{2}{N}\sum_{n} |C^0_{n}|^2 \left(\mathcal{G}_{D}^{-1}(\omega)\right)_{n n} 
-\end{aligned}\end{equation}
-Now we come to the off-diagonal Greens function for the nearest neighbour sites $i$ and $j$.
-This will receive contribution from only that dimer+bath Hamiltonian that has \(i,j\) as the dimer sites.
-This will not be a real space diagonal Greens function.
-Instead, it involves two nearest neighbour sites.
-%We call this Greens function $\left[\mathcal{G}_D^{-1}(\omega)\right]_{01}^\sigma$.
-\begin{gather}
-\label{nn_gf}
-\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\bra{\tilde \Phi_0}c_{0\sigma}\mathcal{G}_{D}^{-1}(\omega)c^\dagger_{1\sigma}\ket{\tilde \Phi_0} = \frac{2}{Nw}\sum_{n} \left(C^0_{n}\right)^* C^1_{n} \left(\mathcal{G}_{D}^{-1}(\omega)\right)_{nn}
-\end{gather}
-For convenience, we define $g_n = \left(\mathcal{G}_{D}^{-1}(\omega)\right)_{nn}$.
-\begin{figure}[htpb!]
-	\centering
-	\hspace*{\fill}
-	\includegraphics[width=0.7\textwidth]{../figures/lattice.png}
-	\hspace*{\fill}
-	\caption{\textit{Left:} Part of the lattice that is picked out by the Greens function on the LHS of eq.~\ref{local_gf}.
-\textit{Right:} Hamiltonian whose Greens functions appear on the right hand side of same equation.
-The two submodels are identical.}
-\end{figure}
-
-The matrix elements for hole propagation are obtained similarly.
-Here the relavant excitations are $\ket{\overline{i\sigma}} \equiv c_{i\sigma}\ket{\tilde \Phi_0}$, at frequency $-\omega$.
-To expand these states, we choose the eigenstates with $N-1$ total particles as the orthonormal basis:
-\begin{equation}\begin{aligned}
-	c_{0\sigma}\ket{\tilde \Phi_0} = \sum_n \overline C^0_n \ket{\overline{n}}, && c_{1\sigma}\ket{\tilde \Phi_0} = \sum_n \overline C^1_n \ket{\overline{n}}%\sum_{m,\alpha,\beta} C^i_{m,\alpha,\beta} \ket{m,\alpha,\beta}
-\end{aligned}\end{equation}
-and the counterpart for $g_n$, here, is
-\begin{equation}\begin{aligned}
-	\overline {g_n} = \bra{\overline n}\mathcal{G}_{D}^{-1}(-\omega)\ket{\overline n}
-\end{aligned}\end{equation}
-By suitably replacing the symbols, we can write down the matrix elements of $\mathcal{G}_H^{-1}(-\omega)$ for hole propagation:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}_{H}^{-1}(-\omega)\right)_{\overline{ii}}^\sigma &= \frac{2}{N}\sum_{n} |\overline C^0_{n}|^2 \overline{g_n}\\
-	\left(\mathcal{G}_{H}^{-1}(-\omega)\right)_{ij}^\sigma &= \frac{2}{Nw}\sum_{n} \left(\overline C^0_{n}\right)^* \overline C^1_{n} \overline{g_n} 
-\end{aligned}\end{equation}
-
-\subsection{Constructing full Greens function matrix from the inverse matrix}
-The matrix elements $\left(\mathcal{G}_{H}^{-1}(\omega)\right)_{ii}^\sigma$ and its nearest neighbour partner can be obtained simply by inverting the internal matrix $\mathcal{G}^{-1}_D$.
-This is because,
-\begin{equation}\begin{aligned}
-	A_{ij} = \sum_{mn}\braket{i | n} A_{nm} \braket{m|j} \implies A^{-1}_{ij} = \sum_{mn}\braket{i|n} A^{-1}_{nm} \braket{m|j}
-\end{aligned}\end{equation}
-The spectral weights remain unchanged; only the matrix element changes from $A_{nm}$ to $(A^{-1})_{nm}$.
-Inverting the matrix $\mathcal{G}_D$ is actually simple because it is diagonal in the chosen basis:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_D\right)_{nn} = \begin{pmatrix} g_{0} && 0 && &..& 0\\ 0 && g_{1} && && \\ &&..&& ..
-&&  \\ 0 &&&&&& g_{M} \end{pmatrix} \implies \left(\mathcal{G}_D\right)_{nn} = \begin{pmatrix} \frac{1}{g_{0}} && 0 && &..& 0\\ 0 && \frac{1}{g_{1}} && && \\ &&..&& ..
-&&  \\ 0 &&&&&& \frac{1}{g_{M}} \end{pmatrix}
-\end{aligned}\end{equation}
-This allows us to write
-\begin{equation}\begin{aligned}
-	\label{G_mat_loc}
-	\left(\mathcal{G}_{H}(\omega)\right)_{ii}^\sigma = \frac{4(w-1)}{N}\sum_{n} |C^0_{n}|^2 \frac{1}{g_n}, && \left(\mathcal{G}_{H}(-\omega)\right)_{\overline{ii}}^\sigma = \frac{4(w-1)}{N}\sum_{n} |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}}
-\end{aligned}\end{equation}
-and
-\begin{equation}\begin{aligned}
-	\label{G_mat_nn}
-	\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma = \frac{4(w-1)}{Nw}\sum_{n} {C^0_{n}}^* C^1_{n} \frac{1}{g_n}, && \left(\mathcal{G}_{H}(-\omega)\right)_{\overline{ij}}^\sigma = \frac{4(w-1)}{Nw}\sum_{n} {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}
-\end{aligned}\end{equation}
-These two expressions can be used to obtain an expression for the real space local and nearest-neighbour Greens functions:
-\begin{equation}\begin{aligned}
-	G_H(\omega)_\text{loc} &= \left(\mathcal{G}_H(\omega)\right)_{ii} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ii}} = \frac{4(w-1)}{N}\sum_n\left(|C^0_{n}|^2 \frac{1}{g_n} - |\overline C^0_{n}|^2 \frac{1}{\overline{g_n}}\right)\\
-	G_H(\omega)_\text{nn} &= \left(\mathcal{G}_H(\omega)\right)_{ij} - \left(\mathcal{G}_H(-\omega)\right)_{\overline{ji}} = \frac{4(w-1)}{Nw}\sum_n\left({C^0_{n}}^* C^1_{n} \frac{1}{g_n} - {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}}\right)\\
-\end{aligned}\end{equation}
+
+The Lehmann-Kallen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements.
+Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
+\begin{equation}\begin{aligned}
+	\label{greens_func_siam}
+	\left(G_{H-H}(\omega)\right)_\text{loc} &= \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn} - |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\right] \\
+	\left(G_{H-H}(\omega)\right)_\text{n-n} &= \left(G_{H-H}(\omega)\right)_{i,j}^p - \left(G_{H-H}(-\omega)\right)_{j,i}^h = \frac{1}{w}\sum_n \left[\left(d^p_{1,n}\right)^* d^p_{2,n} \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn} - \left(d^h_{2,n}\right)^* d^h_{1,n} \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\right]
+\end{aligned}\end{equation}
+
+\section{Spectral functions and self-energies}
+
 The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
 \begin{equation}\begin{aligned}
-	G_H (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_H (|\vec{r_i} - \vec {r_j}|, \omega)
+	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G_H (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}G_H (\omega)_\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_H (\omega)_\text{nn}
+	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\label{k_Gf}
-	G_H (\vec k, \omega) &\simeq G_H (\omega)_\text{loc} + G_H (\omega)_\text{nn}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\\
-			     &= G_H (\omega)_\text{loc} + G_H (\omega)_\text{nn} \xi_{\vec k}\\
-			     &= \frac{4(w-1)}{N}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
+	\label{k_Gf_siam}
+	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} = G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k}\\
+			     &= \sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
 \end{aligned}\end{equation}
@@
 \begin{eqnarray}
+	\label{2dsquaretb}
 \xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
@@
 \begin{equation}\begin{aligned}
-	A_{H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{k},\omega)) = -\frac{4(w-1)}{N\pi} \textrm{Im}\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\\
-A_{H}(\vec{r}=0,\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H}(\vec{r}=0,\omega)) = \frac{1}{N}\sum_{\vec{k}}A_{H}(\vec{k},\omega)
-\end{aligned}\end{equation}
-We can again use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the spectral functions  $A_{H} (\vec{k},\omega)$ and $A_{H} (\vec{r}=0,\omega)$ for the Hubbard model on the 2D square lattice.
-
-\subsection{Calculation of self energy matrix from the Dyson equation}
-With the knowledge of the momentum-space Greens function $G_H(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
+	A_\text{H-H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega))\\ 
+	&= -\frac{1}{\pi} \textrm{Im}\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\\
+	&= A_\text{aux,dd} + \frac{\xi_{\vec k}}{w} A_\text{aux,dz}
+\end{aligned}\end{equation}
+where 
+\begin{eqnarray}
+G_\text{aux,dd} &=& \sum_n\left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\nonumber\\
+G_\text{aux,dz} &=& \sum_n\left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
+\end{eqnarray}
+and the spectral function $A_\text{aux,dd}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dd}$~,~$A_\text{aux,dz}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dz}$.
+Further,
+\begin{equation}\begin{aligned}
+A_\text{H-H}(\vec{r}=0,\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{r}=0,\omega)) 
+= A_\text{aux,dd}
+\label{main}
+\end{aligned}\end{equation}
+
+With the knowledge of the momentum-space Greens function $G_\text{H-H}(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-where the $G_{0}(\vec k, \omega)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system.
-Substituting this as well as the full Greens function $G_H(\vec k, \omega)$ into Dyson's equation gives
-\begin{equation}\begin{aligned}
-	\Sigma_H(\vec k,\omega) = \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1}
-\end{aligned}\end{equation}
-
-Thus, we can use eqs.\eqref{2dsquaretb}, \eqref{local_gf} and \eqref{nn_gf} to obtain the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
-
+where the $G_{0}(\vec k, \omega)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system.
+Substituting this as well as the full Greens function $G_{H-H}(\vec k, \omega)$ into Dyson's equation gives
+\begin{equation}\begin{aligned}
+	\Sigma_{H-H}(\vec k,\omega) &= \omega +t^{H-H}\xi_{\vec k} - \left\{\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}\\
+&= 	 \omega +t^{H-H}\xi_{\vec k} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}
+\end{aligned}\end{equation}
+This allows us to calculate the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
 \section{Analytic consistency checks}

### 2022-03-26 notes/notes.tex
completed obtaining selfenergy and Greens functions for two site cluster

@@
 \usepackage[hidelinks]{hyperref}
-\usepackage[margin=0.8in,top=0.3in,bottom=1.4in]{geometry}
+\usepackage[margin=0.5in,top=0.3in,bottom=1.4in]{geometry}
 \usepackage[utf8]{inputenc}
@@
 
-There are four kinds of terms: the first kind, \(A(i), A(j)\), depend only on either \(i\) or \(j\).
-They can be summed over easily by noting that the internal summation gives a constant factor of \(w-2\) which is cancelled by the factor of \(1/(w-2)\) in the front, and the external summation gives \(\sum_{i,j}A(i) = \frac{w}{2} \sum_i A(i)\), because \(i\) is a member of \(w/2\) distinct nearest-neighbour pairs.
-The second kind, \(B(i,j)\) depends on both \(i\) and \(j\).
+There are four kinds of terms:
+\begin{itemize}
+	\item the first kind, \(A(i), A(j)\), depend only on either \(i\) or \(j\).
+They can be summed over easily by noting that the internal summation gives a constant factor of \(w-2\) which is canceled by the factor of \(1/(w-2)\) in the front, and the external summation gives \(\sum_{i,j}A(i) = \frac{w}{2} \sum_i A(i)\), because \(i\) is a member of \(w/2\) distinct nearest-neighbour pairs.
+	\item The second kind, \(B(i,j)\) depends on both \(i\) and \(j\).
 The internal summation is again cancelled by the prefactor.
 The external summation simply sums over all nearest-neighbour values of \(A(i,j)\).
-The third kind, \(C(i,k), C(j,l)\), depend on \(i\) and \(k\).
+	\item The third kind, \(C(i,k), C(j,l)\), depend on \(i\) and \(k\).
 Here, the total summation \(\sum_{i,j,k}C(i,k)\) gives \((w-2)\sum_{\left<i,k\right>}\left(C(i,k) + C(k,i)\right)\), because the pair \((i,k)\) occurs \(w-2\) times corresponding to the \(w-2\) vectors \(\vec r_j - \vec r_i\) that are perpendicular to \(\vec r_i - \vec r_k\).
 The factor is again cancelled by the existing prefactor.
-The fourth kind, \(D(k), D(l), E(k,l)\), depend on just \(k\), just \(l\) or both \(k\) and \(l\).
+	\item The fourth kind, \(D(k), D(l), E(k,l)\), depend on just \(k\), just \(l\) or both \(k\) and \(l\).
 For each pair \(i-j\) in the external summation, the particular pair \(k-l\) appears only once.
@@
 This factor cancels the inverse factor in front, giving \(\sum_{\left<k\right>} D(k), \sum_{\left<k,l \right>}E(k,l)\).
+\end{itemize}
+
  The full Hamiltonian reads
@@
 	\label{2siam_to_hubb}
-	H_\text{full} &= \frac{1}{w}\sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
+	H_\text{full} &= \frac{1}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) = \frac{1}{w}\sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
 		      &= -\left(U/2 - U_b/w\right)^2\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{N}{2w-4}t + t/w - 4V/w\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 4J/w \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
@@
 Therefore, the only operators \(\mathcal{G}^{-1}_\text{aux}(k,l)\) that affect the matrix element are those that satisfy \(i \in \left(k,l\right)\).
-There are \(w\) such pairs: \(\left\{k,l\right\} = \left\{i,j\right\} \text{ such that } j \in \text{NN of i}\).
+There are \(w\) such pairs: \(\left\{k,l\right\} = \left\{i,j\right\} \forall~ j \in \text{NN of i}\).
 Moreover, because of translation invariance, all \(j \in \text{NN of i}\) are equivalent.
+These configurations are shown in fig.~\ref{diag_conrib}.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../figures/diagonal_contributors.pdf}
+	\caption{The various configurations of auxiliary models that contribute to the diagonal matrix element at site \(i\). Orange colour represents impurities and green represents bath sites.}
+	\label{diag_conrib}
+\end{figure}
+
 \begin{equation}\begin{aligned}
@@
 There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(\mathcal{H}_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\).
-We also defined \(d^p_{1,n} = \bra{\Phi_n}c^\dagger_{d_1\sigma}\ket{\Phi_0}\).
+We also defined \(d^p_{i,n} = \bra{\Phi_n}c^\dagger_{d_i\sigma}\ket{\Phi_0}\).
 The hole propagation matrix element can be obtained similarly:
@@
 \end{aligned}\end{equation}
-where \(d^h_{1,n} = \bra{\Phi_n}c_{d_1\sigma}\ket{\Phi_0}\).
-The off-diagonal matrix elements between two sites \(i\) and \(j\) can also be obtained similarly.
-Only that auxiliary model contributes that has \(\left\{k,l\right\} = \left\{i,j\right\}\):
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{i,j} \equiv \braket{\Phi_0 | c_{i,\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{j,\sigma} | \Phi_0} = \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i,j) c^\dagger_{j,\sigma} | \Phi_0} = \frac{1}{w}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux} c^\dagger_{d_2,\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-We again define matrix elements \(d_{2,n}^p = \braket{\Phi_n | c^\dagger_{d_2\sigma} | \Phi_0}, d_{2,n}^h = \braket{\Phi_n | c_{d_2\sigma} | \Phi_0}\).
-Thus, the spectral representation of the matrix element is obtained as
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,j} = \frac{1}{w}\sum_n \left(d^p_{1,n}\right)^* d^p_{2,n} \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}
+where \(d^h_{i,n} = \bra{\Phi_n}c_{d_i\sigma}\ket{\Phi_0}\).
+
+The off-diagonal matrix elements between two nearest-neighbour sites \(i\) and \(i+1\) can also be obtained similarly. Several  auxiliary models can contribute to such a matrix element:
+\begin{itemize}
+	\item those auxiliary models that have \(i\) and \(i+1\) as the two impurities.
+These give the contribution \(\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0}\).
+We can symmetrise it by exchanging \(d_1\) and \(d_2\):
+	\begin{equation}\begin{aligned}
+		\frac{1}{2}\left[\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0} + \braket{\Phi_0 | c_{d_2\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}\right] = \frac{1}{2}\sum_{n} \left(\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{2,n}\right)^* d^p_{1,n}\right) \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+	\end{aligned}\end{equation}
+	\item those that have \(i\) as an impurity and \(i+1\) as the corresponding bath site. There will be \(w-2\) of these in number:
+	\begin{equation}
+		(w-2) \times \frac{1}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{0_1\sigma} | \Phi_0} = \frac{1}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+	\end{equation}
+		where \(z^p_{i,n} = \braket{\Phi_n | c^\dagger_{0_i,\sigma} | \Phi_0}\).
+	\item those that have \(i+1\) as an impurity site and \(i\) as the corresponding bath site. There are again \(w-2\) of these:
+	\begin{equation}
+		(w-2) \times \frac{1}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{0_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0} = \frac{1}{w}\left(z^p_{1,n}\right)^* d^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+	\end{equation}
+\end{itemize}
+These choices are shown in fig.~\ref{off-diag-contrib}.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../figures/offdiagonal_contributors.pdf}
+	\caption{Auxiliary models that contribute to the off-diagonal matrix element. \(j \equiv i+1\)}
+	\label{off-diag-contrib}
+\end{figure}
+
+Adding all contributions gives
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^p_{1,n}\right)^*d^p_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,j} = \frac{1}{w}\sum_n \left(d^h_{1,n}\right)^* d^h_{2,n} \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}
-\end{aligned}\end{equation}
-In summary, the spectral representation of the matrix elements of the four inverse Greens operators are given by
+	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^h_{1,n}\right)^*d^h_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}
+\end{aligned}\end{equation}
+where \(z^h_{i,n} = \bra{\Phi_n}c_{z_i\sigma}\ket{\Phi_0}\).
+
+\par\noindent
+\begin{minipage}{0.65\textwidth}
+	The off-diagonal matrix element between next-to-nearest-neighbour sites \(i,i+2\) can also be obtained, provided their positions are related as \(\vec r_{i+2} = \vec r_i + \vec a + \vec a^\prime\), where \(\vec a\) and \(\vec a^\prime\) are primitive vectors that connect any lattice site to its nearest-neighbours, and \(\vec{a}\cdot\vec{a}^\prime = 0\).
+This is shown in fig.~\ref{next-near}.
+In other words, the two sites have to form the two most separated vertices of a right-angled triangle.
+To find the auxiliary models that contribute to this matrix element, note that there is only one square that can be formed keeping both \(i\) and \(i+2\) on it - we call this square \(ABCD\), where \(A\) is the vertex \(i\) and \(C\) is the vertex \(i+2\).
+We can set \(A=d_1, C=0_2\).
+The other two vertices \(B\) and \(D\) can have two possible configurations:\(B=d_2,D=0_1\) and \(B=0_1,D=d_2\).
+This gives two configurations.
+Two more configurations can be obtained by taking each of these two configurations and keeping \(B,D\) unchanged but exchanging \(A\) and \(C\).
+These four configurations are shown in fig.~\ref{nn-configs}.
+\end{minipage}
+\hspace*{\fill}
+\begin{minipage}{0.29\textwidth}
+	\centering
+	\includegraphics[width=0.7\textwidth]{../figures/next-near.pdf}
+	\captionof{figure}{The kind of next-nearest neighbour sites that can be connected by the auxiliary model.}
+	\label{next-near}
+\end{minipage}
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../figures/nn-offdiagonal_contributors.pdf}
+	\caption{Auxiliary model configurations that contribute to the next-nearest neighbour matrix elements. \(j \equiv i+2\)}
+	\label{nn-configs}
+\end{figure}
+
+These four configurations give
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} &= \frac{2}{w(w-2)}\left[\braket{\Phi_0|c_{d_1\sigma}\mathcal{G}^{-1}_\text{aux}(d_1,d_2)c^\dagger_{0_2,\sigma}|\Phi_0} + \braket{\Phi_0|c_{0_2\sigma}\mathcal{G}^{-1}_\text{aux}(d_1,d_2)c^\dagger_{d_1,\sigma}|\Phi_0}\right] \\
+										 &= \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}
+\end{aligned}\end{equation}
+
+In summary, the spectral representation of the matrix elements of the inverse Greens operators are given by
 \begin{gather}
 \label{green_eq_final_siam}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn}\\
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,j} = \frac{1}{w}\sum_n \left(d^p_{1,n}\right)^* d^p_{2,n} \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,j} = \frac{1}{w}\sum_n \left(d^h_{1,n}\right)^* d^h_{2,n} \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}
+	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
+	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn}~,\\
+	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^p_{1,n}\right)^*d^p_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}~,\\
+	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^h_{1,n}\right)^*d^h_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}~,\\
+	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
+	\left(\mathcal{G}_\text{H-H}^{-1}\left( -\omega \right) \right)^h_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^h_{1,n}\right)^* z^h_{2,n} + \left(z^h_{2,n}\right)^* d^h_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~.
 \end{gather}
@@
 \begin{gather}
-	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\\
-	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,j} = \frac{1}{w}\sum_n \left(d^p_{1,n}\right)^* d^p_{2,n} \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,j} = \frac{1}{w}\sum_n \left(d^h_{1,n}\right)^* d^h_{2,n} \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}
+	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~,\\
+	\left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}~,\\
+	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^p_{1,n}\right)^*d^p_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn}~,\\
+	\left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^h_{1,n}\right)^*d^h_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}~,\\
+	\left(\mathcal{G}_\text{H-H}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~,\\
+	\left(\mathcal{G}_\text{H-H}\left( -\omega \right) \right)^h_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^h_{1,n}\right)^* z^h_{2,n} + \left(z^h_{2,n}\right)^* d^h_{1,n}\right] \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~.
 \end{gather}
@@
 	\label{greens_func_siam}
-	\left(G_{H-H}(\omega)\right)_\text{loc} &= \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn} - |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\right] \\
-	\left(G_{H-H}(\omega)\right)_\text{n-n} &= \left(G_{H-H}(\omega)\right)_{i,j}^p - \left(G_{H-H}(-\omega)\right)_{j,i}^h = \frac{1}{w}\sum_n \left[\left(d^p_{1,n}\right)^* d^p_{2,n} \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn} - \left(d^h_{2,n}\right)^* d^h_{1,n} \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\right]
+	&\left(G_{H-H}(\omega)\right)_\text{loc} = \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn} - |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\right] = G_\text{aux}(d_1,d_1;\omega)\\
+	&\left(G_{H-H}(\omega)\right)_\text{n-n} =\\
+						&\sum_n \left\{\left[\frac{1}{2} \left(d^p_{1,n}\right)^*d^p_{2,n} + \frac{1}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn} - \left[\frac{1}{2} \left(d^h_{1,n}\right)^*d^h_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}\right\}\\
+						&= \frac{1}{2}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_2,d_1;\omega)\right] + \frac{1}{w}\left[G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right]\\
+						&\left(G_\text{H-H}\right)_\text{n-n-n} = \frac{2}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right] 
 \end{aligned}\end{equation}
@@
 As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
-As we do not have real space Greens function that are more non-local than nearest neighbour, we will attempt to obtain momentum space Greens function from these two contributions:
+As we do not have real space Greens function that are more non-local than next-nearest neighbour, we will attempt to obtain momentum space Greens function from these contributions:
 \begin{equation}\begin{aligned}
@@
 \begin{equation}\begin{aligned}
-	\label{k_Gf_siam}
-	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} = G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k}\\
-			     &= \sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
-\end{aligned}\end{equation}
-where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\). For example, on a d-dimensional hypercubic lattice, we obtain
-\begin{equation}\begin{aligned}
-	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i
-\end{aligned}\end{equation}
+	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} + G_{H-H} (\omega)_\text{n-n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {b_i}}= G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k} + G_{H-H} (\omega)_\text{n-n-n} \xi^\prime_{\vec k}
+\end{aligned}\end{equation}
+where we defined \(\left\{b_i\right\} \) as the set of vectors that connect a particular lattice site with its next-nearest-neighbours,\(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\) and \(\xi^\prime_{\vec k} \equiv \sum_{j} e^{i \vec{k}\cdot\vec {b_j}}\).
+Note that \(b_j\) is simply \(a_i + a{i^\prime}\) where \(a_i\) and \(a_{i^\prime}\) are orthogonal.
+On a d-dimensional hypercubic lattice, we obtain
+\begin{gather}
+	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i\\
+\end{gather}
 On a 2D square lattice with lattice spacing $a$, this simplifies to
@@
 \xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
-\epsilon_{\vec{q}} &=& -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})~
 \end{eqnarray}
-where \(\epsilon_{\vec{q}}\) is the tight-binding dispersion.
+where \(\epsilon_{\vec{q}} = -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})\) is the tight-binding dispersion.
+\begin{equation}\begin{aligned}
+	\label{k_Gf_siam}
+	G_{H-H} (\vec k, \omega) = G_\text{aux}(d_1,d_1;\omega) + \xi_{\vec k}\left[G_\text{aux}(d_1,d_2;\omega) + \frac{1}{w}\left[G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right]\right] \\
+	+ \xi^\prime_{\vec k}\frac{2}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]
+\end{aligned}\end{equation}
 
@@
 	A_\text{H-H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega))\\ 
-	&= -\frac{1}{\pi} \textrm{Im}\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\\
-	&= A_\text{aux,dd} + \frac{\xi_{\vec k}}{w} A_\text{aux,dz}
-\end{aligned}\end{equation}
-where 
-\begin{eqnarray}
-G_\text{aux,dd} &=& \sum_n\left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\nonumber\\
-G_\text{aux,dz} &=& \sum_n\left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
-\end{eqnarray}
-and the spectral function $A_\text{aux,dd}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dd}$~,~$A_\text{aux,dz}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dz}$.
-Further,
-\begin{equation}\begin{aligned}
-A_\text{H-H}(\vec{r}=0,\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{r}=0,\omega)) 
-= A_\text{aux,dd}
-\label{main}
-\end{aligned}\end{equation}
+				     &=A_\text{aux}(d_1,d_1;\omega) + \xi_{\vec k}\left[A_\text{aux}(d_1,d_2;\omega) + \frac{1}{w}\left[A_\text{aux}(d_1,0_1;\omega) + A_\text{aux}(0_1,d_1;\omega)\right]\right] \\
+				     &+ \xi^\prime_{\vec k}\frac{2}{w(w-2)} \left[A_\text{aux}(d_1,0_2;\omega) + A_\text{aux}(0_2,d_1;\omega)\right]
+\end{aligned}\end{equation}
+where the spectral function $A_\text{aux}=-\frac{1}{\pi}\textrm{Im}G_\text{aux}$.
 
@@
 \begin{equation}\begin{aligned}
-	\Sigma_{H-H}(\vec k,\omega) &= \omega +t^{H-H}\xi_{\vec k} - \left\{\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}\\
-&= 	 \omega +t^{H-H}\xi_{\vec k} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}
+	&\Sigma_{H-H}(\vec k,\omega) = \omega +t^{H-H}\xi_{\vec k} -\\
+	&\left [G_\text{aux}(d_1,d_1;\omega) + \xi_{\vec k}\left[G_\text{aux}(d_1,d_2;\omega) + \frac{1}{w}\left[G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right]\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}
 \end{aligned}\end{equation}

### 2022-03-28 notes/notes.tex
completed the bethe lattice part

@@
-\documentclass{report}
+\documentclass[10pt]{report}
 \usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk}
@@
 		      &+ 4J \sum_{\left<i,k\right>}\left(\vec{S}_{i}\cdot\vec{S}_{k}\right) - 2 U_b\sum_k\left(\hat n_{k \uparrow} - \hat n_{k \downarrow}\right)^2 - \frac{Nw/2}{w-2}t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)\\
-	=& -\frac{1}{2}\left(Uw - 2U_b\right)^2\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{Nw/2}{w-2}t + t - 4V\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 4J \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
+	=& -\frac{1}{2}\left(Uw + 4U_b\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{Nw/2}{w-2}t + t - 4V\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 4J \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
 \end{aligned}\end{equation}
@@
 In eq.~\ref{2siam_to_hubb}, the total number of terms in the outer summation is \(Nw/2\).
-In order to make sure that this full Hamiltonian scales as \(N\), we divide this by \(w\):
+In order to make sure that this full Hamiltonian scales as \(N\), we divide this by \(w/2\):
 \begin{equation}\begin{aligned}
 	\label{2siam_to_hubb}
-	H_\text{full} &= \frac{1}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) = \frac{1}{w}\sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
-		      &= -\left(U/2 - U_b/w\right)^2\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{N}{2w-4}t + t/w - 4V/w\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 4J/w \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
+	H_\text{full} &= \frac{2}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) = \frac{2}{w}\sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
+		      &= -\frac{1}{2}\left(2U + 8U_b/w\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{N}{w-2}t + 2t/w - 8V/w\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 8J/w \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	t_\text{H-H} = \left(\frac{N}{2w-4}t + t/w - 4V/w\right),~ ~ ~ U_\text{H-H} = \left(U/2 - U_b/w\right),~ ~ ~ J_\text{H-H} = 4J/w
+	t_\text{H-H} = \left(\frac{N}{w-2}t + 2t/w - 8V/w\right),~ ~ ~ U_\text{H-H} = 2U + 8U_b/w,~ ~ ~ J_\text{H-H} = 8J/w
 \end{aligned}\end{equation}
@@
 Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian, while the primed quantities \(E_\text{gs}^\prime\) and \(\omega^\prime\) are the same quantities but for the full model \(\mathcal{H}_{H-H}\).
-While the auxiliary model is intensive, the full Hamiltonian is extensive and scales as \(N\).
+While the auxiliary model is intensive, the full Hamiltonian is extensive and scales as \(N\):
+\begin{equation}\begin{aligned}
+	H_\text{full} &= \frac{2}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) \sim N H_\text{aux}(d_1,d_2)~.
+\end{aligned}\end{equation}
 This means that we must have \(\omega^\prime = N\omega\) and \(E_\text{gs}^\prime = N E_\text{gs}\).
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{w} \times w \times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i, i+1) c^\dagger_{i\sigma} | \Phi_0} = \braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0} = \frac{2}{w} \times w \times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i, i+1) c^\dagger_{i\sigma} | \Phi_0} = 2\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{m,n} \braket{\Phi_0 | c_{d_1\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux} \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d_1\sigma} | \Phi_0} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = 2\sum_{m,n} \braket{\Phi_0 | c_{d_1\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux} \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d_1\sigma} | \Phi_0} = 2\sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn} 
+	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = 2\sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn} 
 \end{aligned}\end{equation}
@@
 \begin{itemize}
-	\item those auxiliary models that have \(i\) and \(i+1\) as the two impurities.
-These give the contribution \(\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0}\).
-We can symmetrise it by exchanging \(d_1\) and \(d_2\):
-	\begin{equation}\begin{aligned}
-		\frac{1}{2}\left[\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0} + \braket{\Phi_0 | c_{d_2\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}\right] = \frac{1}{2}\sum_{n} \left(\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{2,n}\right)^* d^p_{1,n}\right) \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+	\item those auxiliary models that have \(i\) and \(i+1\) as the two impurities. These give the contribution \\
+		\(\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0}\). 
+	\begin{equation}\begin{aligned}
+		\frac{2}{w}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0} = \frac{2}{w}\sum_{n} \left(d^p_{1,n}\right)^*d^p_{2,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
 	\end{aligned}\end{equation}
@@
 	\begin{equation}
-		(w-2) \times \frac{1}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{0_1\sigma} | \Phi_0} = \frac{1}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+		(w-2) \times \frac{2}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{0_1\sigma} | \Phi_0} = \frac{2}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
 	\end{equation}
@@
 	\begin{equation}
-		(w-2) \times \frac{1}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{0_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0} = \frac{1}{w}\left(z^p_{1,n}\right)^* d^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+		(w-2) \times \frac{2}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{0_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0} = \frac{2}{w}\left(z^p_{1,n}\right)^* d^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
 	\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^p_{1,n}\right)^*d^p_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}
+	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^h_{1,n}\right)^*d^h_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}
+	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}
 \end{aligned}\end{equation}
@@
 
-\par\noindent
-\begin{minipage}{0.65\textwidth}
 The off-diagonal matrix element between next-to-nearest-neighbour sites \(i,i+2\) can also be obtained, provided their positions are related as \(\vec r_{i+2} = \vec r_i + \vec a + \vec a^\prime\), where \(\vec a\) and \(\vec a^\prime\) are primitive vectors that connect any lattice site to its nearest-neighbours, and \(\vec{a}\cdot\vec{a}^\prime = 0\).
 This is shown in fig.~\ref{next-near}.
-In other words, the two sites have to form the two most separated vertices of a right-angled triangle.
+
+\par\noindent
+\begin{minipage}{0.6\textwidth}
+The essence is that the two sites have to form the two most separated vertices of a right-angled triangle.
 To find the auxiliary models that contribute to this matrix element, note that there is only one square that can be formed keeping both \(i\) and \(i+2\) on it - we call this square \(ABCD\), where \(A\) is the vertex \(i\) and \(C\) is the vertex \(i+2\).
@@
 The other two vertices \(B\) and \(D\) can have two possible configurations:\(B=d_2,D=0_1\) and \(B=0_1,D=d_2\).
-This gives two configurations.
 Two more configurations can be obtained by taking each of these two configurations and keeping \(B,D\) unchanged but exchanging \(A\) and \(C\).
@@
 \hspace*{\fill}
-\begin{minipage}{0.29\textwidth}
-	\centering
-	\includegraphics[width=0.7\textwidth]{../figures/next-near.pdf}
+\begin{minipage}{0.35\textwidth}
+	\centering
+	\includegraphics[width=0.9\textwidth]{../figures/next-near.pdf}
 	\captionof{figure}{The kind of next-nearest neighbour sites that can be connected by the auxiliary model.}
@@
 	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^p_{1,n}\right)^*d^p_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}~,\\
-	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^h_{1,n}\right)^*d^h_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}~,\\
+	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}~,\\
+	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}~,\\
 	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
@@
 	\left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^p_{1,n}\right)^*d^p_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn}~,\\
-	\left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \sum_n \left[\frac{1}{2} \left(d^h_{1,n}\right)^*d^h_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}~,\\
+	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w}\sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn}~,\\
+	\left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w}\sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}~,\\
 	\left(\mathcal{G}_\text{H-H}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~,\\
@@
 	\label{greens_func_siam}
-	&\left(G_{H-H}(\omega)\right)_\text{loc} = \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn} - |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\right] = G_\text{aux}(d_1,d_1;\omega)\\
-	&\left(G_{H-H}(\omega)\right)_\text{n-n} =\\
-						&\sum_n \left\{\left[\frac{1}{2} \left(d^p_{1,n}\right)^*d^p_{2,n} + \frac{1}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn} - \left[\frac{1}{2} \left(d^h_{1,n}\right)^*d^h_{2,n} + \text{h.c.} + \frac{1}{w}\left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}\right\}\\
-						&= \frac{1}{2}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_2,d_1;\omega)\right] + \frac{1}{w}\left[G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right]\\
+	&\left(G_{H-H}(\omega)\right)_\text{loc} = \left(\mathcal{G}_{H-H}(\omega)\right)_{ii}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn} - |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\right] = G_\text{aux}(d_1,d_1;\omega)\\
+	&\left(G_{H-H}(\omega)\right)_\text{n-n} = \left(\mathcal{G}_{H-H}(\omega)\right)_{i,i+1}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{i+1,i}^h\\
+						&\frac{2}{w}\sum_n \left\{\left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn} - \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}\right\}\\
+						&= \frac{2}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right]\\
 						&\left(G_\text{H-H}\right)_\text{n-n-n} = \frac{2}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right] 
@@
 	\label{k_Gf_siam}
-	G_{H-H} (\vec k, \omega) = G_\text{aux}(d_1,d_1;\omega) + \xi_{\vec k}\left[G_\text{aux}(d_1,d_2;\omega) + \frac{1}{w}\left[G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right]\right] \\
-	+ \xi^\prime_{\vec k}\frac{2}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]
+	G_{H-H} (\vec k, \omega) = G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) \right.\\
+	+ \left.G_\text{aux}(0_2,d_1;\omega)\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	A_\text{H-H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega))\\ 
-				     &=A_\text{aux}(d_1,d_1;\omega) + \xi_{\vec k}\left[A_\text{aux}(d_1,d_2;\omega) + \frac{1}{w}\left[A_\text{aux}(d_1,0_1;\omega) + A_\text{aux}(0_1,d_1;\omega)\right]\right] \\
-				     &+ \xi^\prime_{\vec k}\frac{2}{w(w-2)} \left[A_\text{aux}(d_1,0_2;\omega) + A_\text{aux}(0_2,d_1;\omega)\right]
+	A_\text{H-H}(\vec{k},\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega)) =A_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[A_\text{aux}(d_1,d_2;\omega) + A_\text{aux}(d_1,0_1;\omega) + A_\text{aux}(0_1,d_1;\omega)\right]\\
+	 + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[A_\text{aux}(d_1,0_2;\omega) + A_\text{aux}(0_2,d_1;\omega)\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
+	\label{self-energy}
 	&\Sigma_{H-H}(\vec k,\omega) = \omega +t^{H-H}\xi_{\vec k} -\\
-	&\left [G_\text{aux}(d_1,d_1;\omega) + \xi_{\vec k}\left[G_\text{aux}(d_1,d_2;\omega) + \frac{1}{w}\left[G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right]\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}
+	&\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	H^D\ket{3\pm \uparrow} = \pm t \ket{3\pm \uparrow}\\
-	H^D\ket{1\pm \downarrow} = \mp t \ket{1\pm \downarrow}\\
+	H^D\ket{3\pm \uparrow} = \pm t \ket{3\pm \uparrow}, ~ ~ ~H^D\ket{1\pm \downarrow} = \mp t \ket{1\pm \downarrow}\\
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left\{ \ket{n} \right\} = \ket{3+ \uparrow}, \ket{3- \uparrow}\\
-	\left\{ \ket{\overline n} \right\} = \ket{1+ \downarrow}, \ket{1- \downarrow}
+	\left\{ \ket{n} \right\} = \ket{3+ \uparrow}, \ket{3- \uparrow}, ~ ~ ~\left\{ \ket{\overline n} \right\} = \ket{1+ \downarrow}, \ket{1- \downarrow}
 \end{aligned}\end{equation}
@@
 \begin{gather*}
-	C^0_\pm = \braket{3\pm \uparrow|c^\dagger_{0 \uparrow} |\tilde \Phi_0} = x, y\\
-	C^1_\pm = \braket{3\pm \uparrow|c^\dagger_{1 \uparrow} |\tilde \Phi_0} = x, -y\\
-	\overline C^0_\pm = \braket{1 \pm \downarrow|c_{0 \uparrow} |\tilde \Phi_0} = y, x\\
-	\overline C^1_\pm = \braket{1 \pm \downarrow|c_{1 \uparrow} |\tilde \Phi_0} = y, -x\\
-	g_\pm = \bra{3 \pm \uparrow}\left( \omega + E_{GS} - H^D\right) \ket{3 \pm \uparrow} = \omega + E_{GS} \mp t\\
-	\overline{g_\pm} = \bra{1 \pm \downarrow}\left(-\omega + E_{GS} - H^D\right) \ket{1 \pm \downarrow} = -\omega + E_{GS} \pm t\\
+	C^0_\pm = \braket{3\pm \uparrow|c^\dagger_{0 \uparrow} |\tilde \Phi_0} = x, y, ~ ~ ~ C^1_\pm = \braket{3\pm \uparrow|c^\dagger_{1 \uparrow} |\tilde \Phi_0} = x, -y\\
+	\overline C^0_\pm = \braket{1 \pm \downarrow|c_{0 \uparrow} |\tilde \Phi_0} = y, x, ~ ~ ~\overline C^1_\pm = \braket{1 \pm \downarrow|c_{1 \uparrow} |\tilde \Phi_0} = y, -x\\
+	g_\pm = \bra{3 \pm \uparrow}\left( \omega + E_{GS} - H^D\right) \ket{3 \pm \uparrow} = \omega + E_{GS} \mp t, ~ ~ ~\overline{g_\pm} = \bra{1 \pm \downarrow}\left(-\omega + E_{GS} - H^D\right) \ket{1 \pm \downarrow} = -\omega + E_{GS} \pm t\\
 \end{gather*}
@@
 \subsection{On the Bethe lattice}
-Another test involves considering the case of infinite number of nearest neighbours $w\to\infty$ (the coordination number, and effectively the dimensionality).
-Here, as has been argued in the DMFT literature, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$ such that the kinetic energy of the associated tight-binding lattice model is finite.
-This allows for the competition between the kinetic and potential terms of the Hamiltonian to drive a metal-insulator transition in the limit of $w\to\infty$ as well.
-Further, it has been argued in the DMFT literature that the Greens function matrix of the Hubbard model on the Bethe lattice with $w\to\infty$ becomes purely local (i.e., it has vanishing inter-site matrix elements).
-We can also see this from eqs.\eqref{G_mat_nn}- the nearest-neighbour inverse Greens function vanishes in the limit of $w \to \infty$:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma = \frac{2}{Nw}\sum_{n} {\overline C^0_{n}}^* \overline C^1_{n} \frac{1}{\overline{g_n}} \implies \lim_{w \to \infty}\left(\mathcal{G}_{H}(\omega)\right)_{ij}^\sigma \to 0
-\end{aligned}\end{equation}
-There we used the fact since at half-filling on an $SU(2)$ symmetric mode, we expect $\left<\hat n_{i \uparrow} \right> = \frac{1}{2}$, the orthonormal expansion of $c^\dagger_{i \sigma}\ket{\tilde \Phi_0} = \sum_n C^i_n \ket{n}$ to be constrained to $\sum_n |C_n^i|^2 = \frac{1}{2}$, such that the only term that scales with $w$ is $w$ itself.
-This result then implies that $G^{H}$ matrix has no $k$ dependence.
-
-In this limit, the self-energy also simplifies:
-\begin{equation}\begin{aligned}
-	\lim_{w \to \infty}\Sigma_H(\vec k,\omega) &= \omega +t^{H}\xi_{\vec k} - \frac{N}{2}\left\{\sum_n \lim_{w \to \infty}\left[\left(|C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{C^0_{n}}^* C^1_{n} \frac{1}{g_n}\right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + \frac{\xi_{\vec{k}}}{w}{\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]\right\}^{-1} \\
-						   &=\omega +t^{H}\xi_{\vec k} - \frac{N}{2}\frac{1}{\sum_n \left[ \frac{|C^0_{n}|^2}{g_n} - \frac{|\overline C^0_{n}|^2}{\overline{g_n}}\right]}
-\end{aligned}\end{equation}
-We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.
+Another test involves considering the case of a Bethe lattice with infinite number of nearest neighbours $w\to\infty$ (the coordination number).
+In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
+This allows a metal-insulator transition in the limit of $w\to\infty$ as well.
+In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}.
+This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy}.
+Applying the limit of \(w\to \infty\) on that equation gives
+\begin{equation}\begin{aligned}
+	&\Sigma_{H-H}(\omega) = \lim_{k\to \infty} G_0 -\\
+	&\lim_{w \to \infty}\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}\\
+	& = \lim_{w\to \infty}\left[G_0(\omega) - G_\text{aux}(d_1,d_1;\omega)\right] 
+\end{aligned}\end{equation}
+It is clear from the final form that only the diagonal term \(G_\text{aux}(d_1,d_1;\omega)\) of the interacting Greens function affects the self-energy.
 

### 2022-03-28 notes/notes.tex
updated future goals

@@
 \documentclass[10pt]{report}
-\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk}
+\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk,pifont,enumitem}
 % \usepackage[draft]{graphicx}
@@
 \renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}
+\newlist{todolist}{itemize}{2}
+\setlist[todolist]{label=$\square$}
+\newcommand{\cmark}{\ding{51}}%
 
@@
 \begin{equation}\begin{aligned}
-	&\Sigma_{H-H}(\omega) = \lim_{k\to \infty} G_0 -\\
-	&\lim_{w \to \infty}\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}\\
-	& = \lim_{w\to \infty}\left[G_0(\omega) - G_\text{aux}(d_1,d_1;\omega)\right] 
-\end{aligned}\end{equation}
+	&\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left[G_\text{aux}^{(0)}(\vec k,\omega)\right]^{-1} -\right.\\
+	&\left.\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}\right\}\\
+	& = \lim_{w\to \infty}\left\{G_\text{aux}^{(0)}(\vec k,\omega) - G_\text{aux}(d_1,d_1;\omega)\right\}^{-1} 
+\end{aligned}\end{equation}
+where \(G_\text{aux}^{(0)}(\vec k,\omega)\) is the non-interacting Greens function.
 It is clear from the final form that only the diagonal term \(G_\text{aux}(d_1,d_1;\omega)\) of the interacting Greens function affects the self-energy.
@@
 \begin{enumerate}
-\item Obtain the metal insulator transition of the 2D Hubbard model on the square lattice from our formalism.
-Compare with what is obtained from DMFT and its improvements.
-Also, determine the nature of the bath $\Sigma (k,\omega)$ for the transition point.
-
-\item Once the zero temperature Mott metal-insulator transition is observed, we will investigate its nature.
-
-\item While we have provided expressions for the single particle Greens functions of the $N$-site Hubbard model from their equivalent single particle Greens functions of the Hubbard dimer, we expect that eq.\eqref{green_eq_final_siam} holds quite generally for the two-particle Greens function sector as well.
-We will provide these expressions at a later point in time.
-More specifically, we will calculate the Greens functions for holon-doublon and spinon-spinon excitations as they are likely to contain more information regarding the ground state.
-
-\item It is also important to benchmark the ground state energy and double occupancy obtained from this method against the ground state wavefunction obtained from exact diagonalisation of small lattices and finite size scaling.
-
-\item It should also prove instructive to investigate the nature of many-particle entanglement in the ground state wavefunction of various phases, and  look for signs of a quantum liquid.
+\item The Mott metal-insulator transition:
+	\begin{todolist}
+	\item[\cmark] Obtain the metal insulator transition of the 2D Hubbard-Heisenberg model on the square lattice from the present formalism. 
+	\item Determine the nature of the bath $\Sigma (k,\omega)$ in the metallic phase, insulating phase as well as at criticality.
+	\item Investigate nature of the zero-temperature transition (order of transition, order parameter, etc)
+	\end{todolist}
+
+\item Higher-order Greens functions:
+	\begin{todolist}
+	\item Provide expressions for two-particle Greens functions.
+	\item Calculate explicitly the Greens functions for holon-doublon and spinon-spinon excitations as they are likely to contain more information regarding the ground state.
+	\item Obtain spectral functions for such excitations
+	\end{todolist}
+
+\item Benchmarking against ED and/or finite size scaling:
+	\begin{todolist}
+	\item ground state energy
+	\item double occupancy
+	\end{todolist}
+
+\item Upgrade to two-site cluster:
+	\begin{todolist}
+	\item Study a two-impurity model under renormalisation group
+	\item[\cmark] Derive the tiling and Greens function relations for such a two-impurity model 
+	\item Demonstrate Mott MIT here.
+	\item Investigate the nature of many-particle entanglement in such a cluster
+	\item look for signs of a quantum liquid.
+	\end{todolist}
 
@@
 		\item Periodic Kondo model, by starting from a Kondo model with a dispersive bath
-		\item Hubbard-Heisenberg model, by starting from a generalized Anderson molecule (Anderson molecule with two-particle spin and charge interactions between the two sites)
 	\end{enumerate}
@@
 
-\chapter{Derivation of RG equations: \(U_b\)-free terms}
-\section{Renormalisation of the impurity energy \(\epsilon_d\)}
+\chapter{Derivation of RG equations}
+\section{\(U_b\)-free terms}
+\subsection{Renormalisation of the impurity energy \(\epsilon_d\)}
 The coupling \(\epsilon_d\) is renormalised by three kinds of vertices: \(V^2\), \(J^2\) and \(K^2\).
@@
 
-\section{Renormalisation of the hybridisation \(V\)}
+\subsection{Renormalisation of the hybridisation \(V\)}
 Renormalisation of \(V\) happens through two kinds of processes: \(VJ\) and \(VK\).
@@
 
-\section{Renormalisation of the exchange couplings \(J\) and \(K\)}
+\subsection{Renormalisation of the exchange couplings \(J\) and \(K\)}
 We will just note the renormalisation in \(J^z\), which will be equal to \(J^\pm\) due to spin-rotation symmetry.
@@
 
-\chapter{Derivation of RG equations: \(U_b\)-included terms}
+\section{\(U_b\)-included terms}
 
@@
 
-\section{Renormalisation of \(U_b\)}
+\subsection{Renormalisation of \(U_b\)}
 \(U_b\) can renormalise only via itself. The relevant renormalisation term in the particle sector is
@@
 
-\section{Renormalisation of \(U\)}
+\subsection{Renormalisation of \(U\)}
 \(U_b\) does not have any new renormalisation term on account of \(U_b\). \(U_b\) does however modify the existing RG equation for \(U\), by shifting the denominator. The existing RG equation is
@@
 
-\section{Renormalisation of \(V\)}
+\subsection{Renormalisation of \(V\)}
 The single-particle  hybridisation \(V\) renormalises through terms of \(V U_b\) and \(U_b V\) kind. The first term gives
@@
 
-\section{Renormalisation of \(J\) and \(K\)}
+\subsection{Renormalisation of \(J\) and \(K\)}
 We will track the entire renormalisation purely from that of \(J^+\), by virtue of the SU(2) symmetry. \(J^+\) renormalises through the \(J U_b\) terms. One of the terms is

### 2022-03-28 notes/notes.tex
introduced general filling and spin exchange between impurities

@@
 This is done through the DMFT algorithm: one starts with a non-interacting bath, but depending on the value of \(U\), the conduction bath then gets modified and we ultimately end up with something that is different from what we started with.
-For small\(U\), the bath does not change much and we retain the central resonance of the impurity spectral function.
+For small \(U\), the bath does not change much and we retain the central resonance of the impurity spectral function.
 This then describes a metal in the bulk.
@@
 \section{Introduction of spin-exchange and charge isospin-exchange interactions into the SIAM: the generalised SIAM}
-We will now study the generalised SIAM obtained by introducing spin-exchange and charge isospin-exchange interactions between the impurity and the conduction bath.
+We will now study the generalised SIAM obtained by introducing spin-exchange and charge isospin-exchange interactions between the impurity and the conduction bath~\cite{zitko_2006}.
 Such terms are generated when one does a Schrieffer-Wolff transformation on the SIAM, but we will find it prudent to keep these terms in the bare model itself.
@@
 \end{aligned}\end{equation}
-We can now define a temperature scale for the fixed-point theory:
+We can now define a temperature scale~\cite{wilson1975,hrk_wilson_1980} for the fixed-point theory:
 \begin{equation}\begin{aligned}
@@
 \section{Renormalization of impurity spectral function}
-In this section we will obtain the impurity spectral function, which is defined in terms of the impurity Green's function as
+In this section we will obtain the impurity spectral function~\cite{costi2000,rosch_costi2003,bullaNRGreview}, which is defined in terms of the impurity Green's function as
 \begin{equation}\begin{aligned}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=1_over_U,V=3J,N=4,U=1.000,1.000,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=1_over_U,V=3J,N=4,U=1.000,1.000,50.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=1_over_U,V=3J,N=4,U=1.000,1.000,50.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
 \end{center}
@@
 \subsection{Wilson ratio}
-The Wilson ratio for the impurity is defined as
+The Wilson ratio for the impurity~\cite{wilson1975,nozieres1974fermi,hewson1993} is defined as
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-Following Seki and Yunoki, we can define a winding number for a Green's function \(G(z)\):
+Following Seki and Yunoki~\cite{seki2017topological}, we can define a winding number for a Green's function \(G(z)\):
 \begin{equation}\begin{aligned}
@@
 The second process is the reverse RG which we will undertake now.
+The method has already been applied to study the renormalisation of entanglement in various models of strong correlation~\cite{siddharthacpi,anirban_kondo,anirban_mott_ent}.
 In general, we start with an IR wavefunction that consists a certain number of momentum states \(n_1\) still entangled with the impurity, and the remaining momentum states \(n_2\) disentangled from the impurity.
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
 
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-
-	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=10.000,0.000,40,V=3J,Ubath=-U_by_10,N=4,U=1.000,1000.000,40.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+
+	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
 \end{center}
@@
 	\label{siam_attr}
-	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
-\end{aligned}\end{equation}
+	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
+\end{aligned}\end{equation}
+
 We will use this as the auxiliary model to study the Hubbard model.
 We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
+Note that the impurity level is explicitly at half-filling, because the correlation term \(\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is symmetric under a particle-hole transformation \(\hat n_{d\sigma} \to 1 - \hat n_{d\sigma}\).
+Moreover, the conduction bath is also at half-filling, because we have set the chemical potential \(\mu\) to zero.
+These two ensure that the bulk model is also at half-filling.
+At the end of this section, we will also mention how the tiling works out in the presence of a non-zero filling.
+
 To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(i\) of the lattice, and the bath coupled to the impurity as the set of remaining \(N-1\) sites in the lattice.
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_{H-H} = -\sum_{i} U_H \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_H\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_H\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j
+	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
+
+As mentioned before, no chemical potential \(\mu\) is generated becuase the auxiliary model was at half-filling, both in the impurity as well as in the bath.
+We can change the chemical potential by introducing two terms:
+\begin{equation}\begin{aligned}
+	\eta \sum_\sigma\left(n_{d\sigma} - \frac{1}{2}\right), \mu \sum_{i,\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
+\end{aligned}\end{equation}
+The first term is the particle-hole asymmetry term, and tuning that term moves the impurity away from half-filling.
+The second term is the usual chemical potential in the bath.
+Introducing these terms in the auxiliary model changes the bulk model into:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j + \mu_\text{H-H}\sum_{i\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
+\end{aligned}\end{equation}
+The only change is the generation of the last term. The mappings between the existing parameters and their auxiliary model counterparts remain the same, while \(\mu_\text{H-H}\) is given by
+\begin{equation}\begin{aligned}
+	\mu_\text{H-H} = \eta + \left(N-1\right) \mu
+\end{aligned}\end{equation}
+In the discussion henceforth, we will assume all the models are at half-filling. We will come back to the doped case at a later point in time.
 
@@
 \centering
-	\includegraphics[width=0.3\textwidth]{../figures/corr-k-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/corr-d0-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r1p-t=1.000,J=31.623,0.000,50,V=2J,Ubath=-U,N=4,U=0.032,3.162,50.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/corr-k-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/corr-d0-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r1p-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
 	\caption{Evolution of correlation functions and mutual information across the transition.}
@@
 \section{Creating \(N-\)site Hubbard Hamiltonian from Hubbard dimer embedded in a bath}
-Similar to the previous chapterm, we will now tile the lattice with the two-site auxiliary model
+Similar to the previous chapter, we will now tile the lattice with the two-site auxiliary model
 \begin{equation}\begin{aligned}
@@
 	t_\text{H-H} = \left(\frac{N}{w-2}t + 2t/w - 8V/w\right),~ ~ ~ U_\text{H-H} = 2U + 8U_b/w,~ ~ ~ J_\text{H-H} = 8J/w
+\end{aligned}\end{equation}
+
+We could have also inserted a spin-exchange interaction between the two impurities in the auxiliary model:
+\begin{equation}\begin{aligned}
+	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right] -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right)\\
+	+ J_d \vec{S}_{d_1}\cdot\vec{S}_{d_2} + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
+\end{aligned}\end{equation}
+In the presence of this term, the bulk Hamiltonian remains the same, but the expression of \(J_\text{H-H}\) changes.
+Since this term is similar in form to the term preceding it, we can easily obtain the updated expression:
+\begin{equation}\begin{aligned}
+	J_\text{H-H} = \frac{2}{w}\left(4J + 2J_d\right)
 \end{aligned}\end{equation}

### 2022-03-29 notes/notes.tex
--no-message

@@
 \begin{equation}\begin{aligned}
-	\Sigma(\vec k,\omega) = G_0(\vec k,\omega)^{-1} - G(\vec k,\omega)^{-1}
-\end{aligned}\end{equation}
-where the $G_{0}(\vec k, \omega)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system.
+	\Sigma(\vec k,\omega) = \left(G^{(0)}(\vec k,\omega)\right)^{-1} - G(\vec k,\omega)^{-1}
+\end{aligned}\end{equation}
+where $\left(G^{(0)}(\vec k,\omega)\right)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system.
 Substituting this as well as the full Greens function $G_{H-H}(\vec k, \omega)$ into Dyson's equation gives
@@
 	\label{self-energy}
-	&\Sigma_{H-H}(\vec k,\omega) = \omega +t^{H-H}\xi_{\vec k} -\\
+	&\Sigma_{H-H}(\vec k,\omega) = \left(G^{(0)}(\vec k,\omega)\right)^{-1} -\\
 	&\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}
@@
 \begin{equation}\begin{aligned}
-	&\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left[G_\text{aux}^{(0)}(\vec k,\omega)\right]^{-1} -\right.\\
+	&\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left[G^{(0)}(\vec k,\omega)\right]^{-1} -\right.\\
 	&\left.\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}\right\}\\
-	& = \lim_{w\to \infty}\left\{G_\text{aux}^{(0)}(\vec k,\omega) - G_\text{aux}(d_1,d_1;\omega)\right\}^{-1} 
+	& = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux}(d_1,d_1;\omega)\right\}^{-1} 
 \end{aligned}\end{equation}
@@
 It is clear from the final form that only the diagonal term \(G_\text{aux}(d_1,d_1;\omega)\) of the interacting Greens function affects the self-energy.
+Even the non-interacting part Greens function can be shown to be diagonal in the limit of \(w\to\infty\)~\cite{kuramoto_manybody}.
+From its definition in time domain, we have
+\begin{equation}\begin{aligned}
+	G^{(0)}(\vec k, t) = -i\theta(t) \left<\left\{c_{\vec k}(t), c^\dagger_{\vec k}\right\} \right> = -i\theta(t) \left<\left\{e^{i H^{(0)}t} c_{\vec k} e^{-i H^{(0)}t}, c^\dagger_{\vec k}\right\} \right> = -i\theta(t) e^{-i \epsilon_{\vec k}t}\left[ \left<1 - \hat n_{\vec k}\right> + \left<\hat n_{\vec k}\right>\right] = -i \theta(t) e^{-i \epsilon_{\vec k}t}
+\end{aligned}\end{equation}
+A quick Fourier transform to \(\omega-\)domain shows that this is identical to the \(G^{(0)}(\vec k, \omega)\) defined just above eq.~\ref{self-energy}.
+We note that \(|G^{(0)}(\vec k, t)| \leq 1\).
+Using the Fourier transform  definition
+\begin{equation}\begin{aligned}
+	f(\vec k) = \frac{1}{d_N}\sum_{\vec r_i}h(\vec r_i) e^{i \vec{k}\cdot\vec{r}_i}
+\end{aligned}\end{equation}
+where \(d_N\) is a factor that only depends on the total number of sites and not on the coordination number, we can write
+\begin{equation}\begin{aligned}
+	|G^{(0)}(\vec k, t)|^2 = \frac{1}{d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}
+\end{aligned}\end{equation}
+From the inequality \(|G^{(0)}(\vec k, t)| \leq 1\), we get
+\begin{equation}\begin{aligned}
+	1 \geq \frac{1}{N}\sum_k |G^{(0)}(\vec k, t)|^2 = \frac{1}{N d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* \underbrace{\sum_k e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}}_{N \delta_{\vec r_i = \vec r_j}} = \frac{1}{d_N^2}\sum_{\vec r_i} |G^{(0)}(\vec r_i, t)|^2
+\end{aligned}\end{equation}
+For a coordination number of \(w\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
+Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{w}\).
+In contrast, there is only one local Greens function, that for \(\vec r_i=0\).
+The local Greens function therefore scales independent of \(w\).
+This implies that
+\begin{equation}\begin{aligned}
+	\lim_{w\to \infty}G^{(0)}(\vec k,\omega) = G^{(0)}(\vec r=0,\omega)
+\end{aligned}\end{equation}
+Since both the non-interacting and the interaction Greens functions lose their non-locality, the self-energy becomes completely local in the limit of \(w \to \infty\).
 

### 2022-03-30 notes/notes.tex
incorporated luttinger volume

@@
 \section{Luttinger's and Friedel's sum rules}
-The subsequent discussions are for the first quadrant where \(U^* = 0\) and \(J^* > K^*\). At high temperatures, we see that the impurity susceptibility attains the value of
-\begin{equation}\begin{aligned}
-	\frac{1}{8k_B T}
-\end{aligned}\end{equation}
-which implies that the impurity behaves as a free orbital in this limit, having no coupling with the bath. We can write down the following effective Hamiltonian for such a limit:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{high-T} = \tilde \epsilon_d \hat n_d + \sum_{k\sigma} \epsilon_k\hat n_{k\sigma}
-\end{aligned}\end{equation}
-Since the impurity is decoupled from the bath, we can immediately write down the Hamiltonian just for the impurity:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{high-T, imp} = \tilde \epsilon_d \hat n_d
-\end{aligned}\end{equation}
-
-We consider the resonant-level model:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{res} = \sum_{k\sigma}\epsilon_k \hat n_{k\sigma} + \epsilon_d n_d + \sum_{k\sigma}\left(V_k c^\dagger_{k\sigma} c_{d\sigma} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-The total Green's function is 
-\begin{equation}\begin{aligned}
-	G(z) = \frac{1}{z - \mathcal{H}_\text{res}}
-\end{aligned}\end{equation}
-The impurity diagonal Green's function is
-\begin{equation}\begin{aligned}
-	G_{dd}(z) &= \frac{1}{z - \epsilon_d - \Sigma_d(z)}, &&	G_d(z) = G_{dd}\ket{d}\bra{d}
-\end{aligned}\end{equation}
-where \(\Sigma_d(z)\) is in general complex and is zero at the free orbital fixed point. The conduction electron Green's function is 
-\begin{equation}\begin{aligned}
-	&G_{kk}(z) = G_k^0(z) + \left[G_k^0(z)V_k\right]^2 G_{dd}(z), & G_c(z) \equiv \sum_k \ket{k}\bra{k}G_{kk}(z), && G_{c0}(z) \equiv \sum_k G_{kk}^0(z)\ket{k}\bra{k}
-\end{aligned}\end{equation}
-The total Green's function can be written as
-\begin{equation}\begin{aligned}
-	G(z) &= \left(\sum_{k}\ket{k}\bra{k} + \ket{d}\bra{d}\right) G \left(\sum_{k}\ket{k}\bra{k} + \ket{d}\bra{d}\right)\\
-	     &= \sum_{k} \ket{k}\bra{k}G_{kk}(z) + G_{dd}(z)\ket{d}\bra{d} + \text{off-diagonal terms}\\
-	     &= G_c(z) + G_{d}(z) + \text{off-diagonal terms}
-\end{aligned}\end{equation}
-The total number of electrons is given by
-\begin{equation}\begin{aligned}
-	N &= \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G(z) \right]\\
-	  &= \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_{d}(z) + G_c(z)\right]
-\end{aligned}\end{equation}
-The contour \(\Gamma\) counts all the singularities of \(\text{Tr} G(z)\), and thus encloses only the real axis of the complex plane (since \(G(z)\) comes from a Hermitian matrix \(\mathcal{H}_\text{res}\), all its singularities are real).
-At this point, we can use an identity:
-\begin{equation}\begin{aligned}
-	\text{Tr}\left[G_{d}(z)\right] &= \text{Tr}\left[ \frac{\ket{d}\bra{d}}{z - \epsilon_d - \Sigma_d(z)}\right] = \text{Tr}\left[ \frac{\ket{d}\bra{d}}{z - \epsilon_d - \Sigma_d(z)}\frac{\partial{\left(z - \epsilon_d\right)}}{\partial{z}} \right] = \text{Tr}\left[ \ket{d}\bra{d}G_{dd}\frac{\partial{\left\{G_{dd}^{-1}(z) + \Sigma_d(z)\right\}}}{\partial{z}} \right]\\
-				       &= \text{Tr}\left[ G_{d}(z)\frac{\partial{G_{d}^{-1}(z)}}{\partial{z}} \right] + \text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right] = \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}G_{d}^{-1}(z)\right] + \text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right]\\
-\end{aligned}\end{equation}
-In the last step, we converted the trace to a determinant using
-\begin{equation}\begin{aligned}
-	\text{Tr}\left[A \frac{\partial{A^{-1}}}{\partial{z}}\right] = \frac{\partial{}}{\partial{z}}\text{Tr}\ln A^{-1} =\frac{\partial{}}{\partial{z}}\sum_i \ln \lambda_i = \frac{\partial{}}{\partial{z}}\ln \prod_i \lambda_i = \frac{\partial{}}{\partial{z}}\ln \text{Det}A^{-1}
-\end{aligned}\end{equation}
-where \(\lambda_i\) are the eigenvalues of \(A^{-1}\). Substituting \(\text{Tr}\left[G_d(z)\right] \) into the total number of particles gives
-\begin{equation}\begin{aligned}
-	N  &= \oint \frac{dz}{2\pi i}n_F(z) \left[\frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{G^{-1}_d(z)\right\} + \text{Tr} \left( G_d(z) \frac{\partial{}}{\partial{z}}\Sigma_d(z) \right) + \text{Tr}G_c(z)\right]
-\end{aligned}\end{equation}
-The conduction electron part can also be simplified:
-\begin{equation}\begin{aligned}
-	\text{Tr}G_c(z) &= \text{Tr}\left[G_{c0}(z) + \sum_k \left\{G_k^0(z)V_k\right\}^2 G_{dd}(z)\ket{k}\bra{k}\right] =\text{Tr}\left[G_{c0}(z)\right] + \sum_k\left[G_k^0(z)V_k\right]^2 G_{dd}(z)\\
-\end{aligned}\end{equation}
-Since \(G_{c0}^{-1}(z) = z - \sum_k \epsilon_k \hat n_k\), we can write \(\text{Tr}\left[G_{c0}(z)\right] = \text{Tr}\left[G_{c0}(z) \frac{\partial{}}{\partial{z}}G_{c0}^{-1}\right]\) and hence
-\begin{equation}\begin{aligned}
-	\text{Tr}G_c(z) &=\frac{\partial{}}{\partial{z}}\left[\ln \text{Det}G_{c0}^{-1}(z)\right] + \sum_k\left[G_k^0(z)V_k\right]^2 G_{dd}(z)
-\end{aligned}\end{equation}
-Updating the total particles with this leads to
-\begin{equation}\begin{aligned}
-	N  = \oint \frac{dz}{2\pi i}n_F(z) \left[\frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{G^{-1}_d(z)\right\} + \frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{G^{-1}_{c0}(z)\right\} + \text{Tr} \left( G_d(z) \frac{\partial{}}{\partial{z}}\Sigma_d(z) \right) + \sum_k\left( V_k G_k^0 \right)^2 G_{dd}(z)\right]
-\end{aligned}\end{equation}
-For the resonant-level model, we have
-\begin{equation}\begin{aligned}
-	\Sigma_d = \sum_k V^2_k G^0_k = \sum_k \frac{V_k^2}{z - \epsilon_k}
-\end{aligned}\end{equation}
-such that
-\begin{equation}\begin{aligned}
-	\text{Tr} \left( G_d(z) \frac{\partial{}}{\partial{z}}\Sigma_d(z) \right) = -G_{dd}(z) \sum_k \left( V_k G_k^0 \right)^2
-\end{aligned}\end{equation}
-which allows us to write
-\begin{equation}\begin{aligned}
-	N  = \oint \frac{dz}{2\pi i}n_F(z) \left[\frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{G^{-1}_d(z)\right\} + \frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{G^{-1}_{c0}(z)\right\} \right]
+\label{lutt_theorem}
+In this section, we will compute Luttinger's sum for the various fixed-point theories.
+Luttinger's sum is essentially the volume enclosed by the Fermi surface~\cite{luttinger1960fermi,oshikawa2000topological,seki2017topological}, and Luttinger's theorem states that this volume counts the number of conduction electrons in the system~\cite{luttinger1960fermi,oshikawa2000topological,seki2017topological}.
+
+We first consider the strong-coupling fixed point Hamiltonian, which is essentially just a resonant-level model:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{res} = \sum_{k\sigma}\epsilon_k \hat n_{k\sigma} + \sum_{k\sigma}\left(V_k c^\dagger_{k\sigma} c_{d\sigma} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+The impurity Green's function is given by~\cite{anderson_1961,hewson1993,coleman2015}
+\begin{equation}\begin{aligned}
+	G_{d}(z) &= \frac{1}{z - \Sigma_d}\ket{d\sigma}\bra{d\sigma}, ~ ~ \Sigma_d = \sum_k \frac{V^2}{z - \epsilon_k}
+\end{aligned}\end{equation}
+\(\Sigma_d(z)\) is zero at the free orbital fixed point. The conduction electron Green's function is 
+\begin{gather}
+	G_{k}(z) = G_k^0(z) + \left[G_k^0(z)V_k\right]^2 G_{d}(z), ~ ~ G_k^0 = \frac{1}{z - \epsilon_k}, ~ ~ G_c^0(z) = \sum_k G_k^0(z)\ket{k}\bra{k}~,\\
+	G_c(z) = \sum_k G_k(z)\ket{k}\bra{k} = G_c^0 + \left[G_k^0(z)V_k\right]^2 G_{d}(z)\ket{k}\bra{k} 
+\end{gather}
+The total number of electrons is given by the sum of the number of electrons in the conduction bath and at the impurity:
+\begin{equation}\begin{aligned}
+	\label{tot_num}
+	N &= \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_{d}(z) + G_c(z)\right] = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_{d}(z) + G_c^0(z) + \left[G_k^0(z)V_k\right]^2 G_{d}(z)\ket{k}\bra{k}\right]
+\end{aligned}\end{equation}
+Since the eigenstates of the system are situated at real poles, the contour \(\Gamma\) encloses only the real axes and hence picks out those real poles to count the total number of particles.
+
+Since \(1/G_{c}^0(z) = z - \sum_k \epsilon_k \hat n_k\), we can write \(\text{Tr}\left[G_{c}^{0}(z)\right] = \text{Tr}\left[G_{c}^{0} \frac{\partial{}}{\partial{z}}\left(1/G_{c}^{0}\right)\right]\) and hence
+\begin{equation}\begin{aligned}
+	\label{simple_bath}
+	\text{Tr}\left[G_c(z)\right] &=\frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{c}^{0}\right)\right] + \sum_k\left[G_k^0(z)V_k\right]^2 G_{d}(z)
+\end{aligned}\end{equation}
+
+The impurity part can, on the other hand, be written as
+\begin{equation}\begin{aligned}
+	\text{Tr}\left[G_{d}(z)\right] &= \text{Tr}\left[ \frac{\ket{d}\bra{d}}{z - \Sigma_d(z)}\right] = \text{Tr}\left[ \frac{\ket{d}\bra{d}}{z - \Sigma_d(z)}\frac{\partial{\left(z\right)}}{\partial{z}} \right] = \text{Tr}\left[ G_{d}(z)\frac{\partial{G_{d}^{-1}(z)}}{\partial{z}} \right] + \text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right]\\
+\end{aligned}\end{equation}
+The fist term can be written as \(\text{Tr}\left[ G_{d}(z)\frac{\partial{G_{d}^{-1}(z)}}{\partial{z}} \right] = \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}G_{d}^{-1}(z)\right]\).
+The second part can be written as \(\frac{\partial{\Sigma_d(z)}}{\partial{z}} = -\sum_k V^2 {G_k^0}^2\).
+Together, we get
+\begin{equation}\begin{aligned}
+	\label{simple_imp}
+	\text{Tr}\left[G_{d}(z)\right] = \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{d}\right)\right] - \text{Tr}\left[ G_{d}(z)\sum_k V^2 {G_k^0}^2\right]\\
+\end{aligned}\end{equation}
+Substituting eqs.~\ref{simple_bath} and \ref{simple_imp} into eq.~\ref{tot_num}, we get
+\begin{equation}\begin{aligned}
+	N = \oint \frac{dz}{2\pi i}n_F(z) \left[\frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{d}\right)\right] + \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{c}^{0}\right)\right]\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	N  = \left[\oint_{\Gamma_<} + \frac{1}{2}\oint_{\Gamma_0}\right]\frac{dz}{2\pi i}\left[\frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{G^{-1}_d(z)\right\} + \frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{G^{-1}_{c0}(z)\right\} \right]
+N  = \left[\oint_{\Gamma_<} + \frac{1}{2}\oint_{\Gamma_0}\right]\frac{dz}{2\pi i}\left[\frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{1/G_d(z)\right\} + \frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{1/G_{c}^{0}(z)\right\} \right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	N = P_{\text{Det }G_d}(\Gamma_<) - Z_{\text{Det }G_d}(\Gamma_<) + \frac{1}{2}\left[P_{\text{Det }G_d}(\Gamma_0) - Z_{\text{Det }G_d}(\Gamma_0)\right] + P_{\text{Det }G_{c0}}(\Gamma_<) - Z_{\text{Det }G_{c0}}(\Gamma_<) \\
-	+ \frac{1}{2}\left[P_{\text{Det }G_{c0}}(\Gamma_0) - Z_{\text{Det }G_{c0}}(\Gamma_0)\right]
+N = P_{\text{Det }G_d}(\Gamma_<) - Z_{\text{Det }G_d}(\Gamma_<) + \frac{1}{2}\left[P_{\text{Det }G_d}(\Gamma_0) - Z_{\text{Det }G_d}(\Gamma_0)\right] + P_{\text{Det }G_{c}^{0}}(\Gamma_<) - Z_{\text{Det }G_{c}^{0}}(\Gamma_<) + \frac{1}{2}\left[P_{\text{Det }G_{c}^{0}}(\Gamma_0) - Z_{\text{Det }G_{c}^{0}}(\Gamma_0)\right]
 \end{aligned}\end{equation}
 The average number of particles can thus be expressed purely in terms of the number of poles and zeros of the impurity and the conduction electron Green's functions.
-As shown by Seki and Yunoki, the second line gives the Luttinger volume \(V_L\):
+The number of poles in the conduction electron Greens function \(G_c^0\) minus the number of zeros gives the Luttinger volume \(V_L = V_L^< + \frac{1}{2}V_L^0\)~\cite{seki2017topological}, while those in the impurity Greens function \(G_d = V_\text{imp}^< + \frac{1}{2}V_\text{imp}^0\) give the number of localised excitations \(V_\text{imp}\) on the impurity:
 \begin{equation}\begin{aligned}
 	\label{total_lutt}
-	N = P_{\text{Det }G_d}(\Gamma_<) - Z_{\text{Det }G_d}(\Gamma_<) + \frac{1}{2}\left[P_{\text{Det }G_d}(\Gamma_0) - Z_{\text{Det }G_d}(\Gamma_0)\right] + V_L
-\end{aligned}\end{equation}
+	N = V_\text{imp}^< + \frac{1}{2}V_\text{imp}^0 + V_L^< + \frac{1}{2}V_L^0
+\end{aligned}\end{equation}
+Note that this also holds at the free orbital fixed point, because it is a special case of the strong-coupling fixed point with \(V=0\).
+
+If we are the local moment fixed point with particle-hole symmetry, we instead have the Hamiltonian
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{lm} = \sum_{k\sigma}\epsilon_k \hat n_{k\sigma} + H_\text{imp}
+\end{aligned}\end{equation}
+where \(H_\text{imp} = -(U/2)\hat n_d + U\hat n_{d \uparrow} \hat n_{d \downarrow}\) is the impurity Hamiltonian.
+In this atomic limit, the impurity Greens function is given by~\cite{phillips2012advanced}
+\begin{equation}\begin{aligned}
+	G_d = \sum_{a=\pm U/2} \frac{1}{z - a} 
+\end{aligned}\end{equation}
+where \(a=\pm U/2\) represent the two Hubbard side bands. Such a Greens function satisfies
+\begin{equation}\begin{aligned}
+	\frac{1}{2\pi i}\o\int dz n_F(z)\text{Tr}\left[G_d\right] = \sum_{a = \pm U/2}n_F(a) = V_\text{imp}^< + \frac{1}{2}V_\text{imp}^0
+\end{aligned}\end{equation}
+The conduction bath can be written in a similar form over the scattering states \(\epsilon_k\).
+
+This shows that the equation eq.~\ref{total_lutt} holds at all three fixed points - free orbital, local moment and strong-coupling.
+
 If we start from a non-interacting model (\(V_k = 0\)), we can write
@@
 This is a specific case of the more general result for Kondo lattices obtained by Oshikawa using flux-insertion arguments in \cite{oshikawa2000topological}.
-One can now ask what happens to this result once we also incorporate the spin-exchange interaction \(J \vec{S_d}\cdot\vec{s}\); we can expect that it will complicate the self-energy of the impurity.
-It cannot, however, preclude the loss of the real pole, nor can it create a new singularity - to do so would require the self-energy to diverge, and we are working with finite systems here.
-This suggests that the eq.~\eqref{luttinger_change} would still hold.
-
-We have also not accounted for the RG flow from the local moment fixed point to the strong coupling fixed point. The local moment fixed point is characterized by a decoupled quantum top:
+
+We have not accounted for the RG flow from the local moment fixed point to the strong coupling fixed point. The local moment fixed point is characterized by a decoupled quantum top:
 \begin{equation}\begin{aligned}
@@
 \section{Important Remarks}
+\subsection{Topological nature of the transition}
+The phase transition is characterised by a change in a topological quantity - the Fermi surface volume.
+As shown in section~\ref{lutt_theorem}, the total number of particles in the system can be expressed in terms of topological quantities:
+\begin{equation}\begin{aligned}
+	N = V_\text{imp}^< + \frac{1}{2}V_\text{imp}^0 + V_L^< + \frac{1}{2}V_L^0
+\end{aligned}\end{equation}
+\(V_L^<\) represents the winding number of the curve traced by the determinant of the conduction electron Greens function on the contour that encloses all real poles below the Fermi surface.
+\(V_L^0\) does the same but for the real poles {\it on} the Fermi surface.
+\(V_\text{imp}^{<,0}\) has the same meanings but for the impurity Greens function.
+This equation holds for the free orbital, local moment and strong coupling fixed points.
+At the local moment fixed point, the impurity Greens function has a single real pole below the Fermi surface, while that pole moves off the real axis at the strong-coupling fixed point.
+That means, \(V_\text{imp}^\text{loc} = V_\text{imp}^\text{sc} + 1\).
+Assuming the total number of particles remains conserved in the process, we get the equation
+\begin{equation}\begin{aligned}
+	V_L^\text{sc} = V_L^\text{loc} + 1
+\end{aligned}\end{equation}
+This shows that the localised \(d-\)electrons is hybridising with the bath and this shows up in the transfer of a real pole from the impurity Greens function into the bath Greens function.
+The addition of this pole "enlarges" the Fermi volume.
+The transition from the metal to the insulator is therefore characterised by the change in the winding number by 1.
+
 \subsection{Greens function in the insulating phase: the Hubbard bands and mottness}

### 2022-03-30 notes/notes.tex
corrected local moment part of lut theorem

@@
 \begin{equation}\begin{aligned}
+	\label{self_id}
 	\text{Tr}\left[G_{d}(z)\right] &= \text{Tr}\left[ \frac{\ket{d}\bra{d}}{z - \Sigma_d(z)}\right] = \text{Tr}\left[ \frac{\ket{d}\bra{d}}{z - \Sigma_d(z)}\frac{\partial{\left(z\right)}}{\partial{z}} \right] = \text{Tr}\left[ G_{d}(z)\frac{\partial{G_{d}^{-1}(z)}}{\partial{z}} \right] + \text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right]\\
@@
 The fist term can be written as \(\text{Tr}\left[ G_{d}(z)\frac{\partial{G_{d}^{-1}(z)}}{\partial{z}} \right] = \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}G_{d}^{-1}(z)\right]\).
-The second part can be written as \(\frac{\partial{\Sigma_d(z)}}{\partial{z}} = -\sum_k V^2 {G_k^0}^2\).
+The second part can be written as \(\frac{\partial{}}{\partial{z}}{\Sigma_d(z)} = -\sum_k V^2 {G_k^0}^2\).
 Together, we get
@@
 \begin{equation}\begin{aligned}
-N = P_{\text{Det }G_d}(\Gamma_<) - Z_{\text{Det }G_d}(\Gamma_<) + \frac{1}{2}\left[P_{\text{Det }G_d}(\Gamma_0) - Z_{\text{Det }G_d}(\Gamma_0)\right] + P_{\text{Det }G_{c}^{0}}(\Gamma_<) - Z_{\text{Det }G_{c}^{0}}(\Gamma_<) + \frac{1}{2}\left[P_{\text{Det }G_{c}^{0}}(\Gamma_0) - Z_{\text{Det }G_{c}^{0}}(\Gamma_0)\right]
+	N &= \underbrace{P_{\text{Det }G_d}(\Gamma_<) - Z_{\text{Det }G_d}(\Gamma_<)}_{V_\text{imp}^<} + \underbrace{\frac{1}{2}\left[P_{\text{Det }G_d}(\Gamma_0) - Z_{\text{Det }G_d}(\Gamma_0)\right]}_{V_\text{imp}^0} + \underbrace{P_{\text{Det }G_{c}^{0}}(\Gamma_<) - Z_{\text{Det }G_{c}^{0}}(\Gamma_<)}_{V_\text{L}^<} + \underbrace{\frac{1}{2}\left[P_{\text{Det }G_{c}^{0}}(\Gamma_0) - Z_{\text{Det }G_{c}^{0}}(\Gamma_0)\right]}_{V_\text{L}^0}\\
+	  &= V_\text{imp}^< + \frac{1}{2}V_\text{imp}^0 + V_L^< + \frac{1}{2}V_L^0
 \end{aligned}\end{equation}
 The average number of particles can thus be expressed purely in terms of the number of poles and zeros of the impurity and the conduction electron Green's functions.
-The number of poles in the conduction electron Greens function \(G_c^0\) minus the number of zeros gives the Luttinger volume \(V_L = V_L^< + \frac{1}{2}V_L^0\)~\cite{seki2017topological}, while those in the impurity Greens function \(G_d = V_\text{imp}^< + \frac{1}{2}V_\text{imp}^0\) give the number of localised excitations \(V_\text{imp}\) on the impurity:
+The number of poles in the conduction electron Greens function \(G_c^0\) minus the number of zeros gives the Luttinger volume \(V_L = V_L^< + \frac{1}{2}V_L^0\)~\cite{seki2017topological}, while those in the impurity Greens function \(V_\text{imp} = V_\text{imp}^< + \frac{1}{2}V_\text{imp}^0\) give the number of localised excitations on the impurity:
 \begin{equation}\begin{aligned}
 	\label{total_lutt}
-	N = V_\text{imp}^< + \frac{1}{2}V_\text{imp}^0 + V_L^< + \frac{1}{2}V_L^0
-\end{aligned}\end{equation}
+	N = V_\text{imp} + V_L
+\end{aligned}\end{equation}
+
 Note that this also holds at the free orbital fixed point, because it is a special case of the strong-coupling fixed point with \(V=0\).
@@
 \begin{equation}\begin{aligned}
-	G_d = \sum_{a=\pm U/2} \frac{1}{z - a} 
-\end{aligned}\end{equation}
-where \(a=\pm U/2\) represent the two Hubbard side bands. Such a Greens function satisfies
-\begin{equation}\begin{aligned}
-	\frac{1}{2\pi i}\o\int dz n_F(z)\text{Tr}\left[G_d\right] = \sum_{a = \pm U/2}n_F(a) = V_\text{imp}^< + \frac{1}{2}V_\text{imp}^0
-\end{aligned}\end{equation}
-The conduction bath can be written in a similar form over the scattering states \(\epsilon_k\).
-
-This shows that the equation eq.~\ref{total_lutt} holds at all three fixed points - free orbital, local moment and strong-coupling.
-
-If we start from a non-interacting model (\(V_k = 0\)), we can write
-\begin{equation}\begin{aligned}
-	N = \mathcal{N}^0_{imp} + V_L^0
-\end{aligned}\end{equation}
-where \(\mathcal{N}^0_{imp}\) is simply the number of singularities of \(G_d\) on the real axis, for the non-interacting case.
-We now turn up the interaction \(V_k\), keeping the total number of particles conserved at \(N\).
-With a non-zero \(V_k\), the impurity self-energy can be written (assuming a constant density of states) as
-\begin{equation}\begin{aligned}
-	\Sigma_d(z) = \Sigma_d^\text{real}(z) - i \Delta
-\end{aligned}\end{equation}
-so that the impurity Greens function becomes
-\begin{equation}\begin{aligned}
-	G_d(z) = \frac{1}{z - \epsilon_d - \Sigma_d^\text{real}(z) + i \Delta}
-\end{aligned}\end{equation}
-We can see that the presence of an imaginary part lifts the pole of \(G_d(z)\) off the real axis, and since the contour \(\Gamma_0\) encloses only the real axis, this will count as a loss in the number of poles of \(G_d(z)\).
-Also, if we specialize to the case where the renormalized impurity site energy \(\epsilon_d^* = \epsilon_d + \Sigma_d^\text{real} = 0\), this loss will happen at the Fermi surface, and will hence be multiplied by a factor of half.
-We can therefore write
-\begin{equation}\begin{aligned}
-	N &= \mathcal{N}_{imp} + V_L = \mathcal{N}^0_{imp} - \frac{1}{2} + V_L \implies V_L &= V_L^0 + \frac{1}{2}
-\end{aligned}\end{equation}
-If we take into account the spin-degeneracy and redefine \(V_L\) to mean the Luttinger volume for both momentum and spin degrees of freedom, we get
+	\label{lm_sigma}
+	G_d = \frac{1}{z - \Sigma_d(z)}, ~ ~ ~\Sigma_d = \frac{U^2}{4}\frac{1}{z}
+\end{aligned}\end{equation}
+Since \(V=0\) at this fixed point, the total number of particles is given by
+\begin{equation}\begin{aligned}
+	\label{total_num_lm}
+	N = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_{d}(z) + G_c^0(z)\right]
+\end{aligned}\end{equation}
+We again use eq.~\ref{self_id} to write
+\begin{equation}\begin{aligned}
+	\text{Tr}\left[G_{d}(z)\right] = \text{Tr}\left[ G_{d}(z)\frac{\partial{G_{d}^{-1}(z)}}{\partial{z}} \right] + \text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right] = \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{d}\right)\right] + \text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right]
+\end{aligned}\end{equation}
+Performing the integral for the second term gives
+\begin{equation}\begin{aligned}
+	\left(\int_{\Gamma_<} + \frac{1}{2}\int_{\Gamma_0}\right)\frac{dz}{2\pi i}\text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right] = 0
+\end{aligned}\end{equation}
+Here we used the form of \(\Sigma_d\) in eq.~\ref{lm_sigma}. Repeating the same steps as before, we recover eq.~\ref{total_lutt}.
+
+We now compare the Luttinger volume across the fixed points.
+At the local moment fixed point, the impurity Greens function has a single pole at \(z<0\) and a zero at \(z=0\), so \(V_\text{imp} = 1 - 1/2 = 1/2\), and eq.~\ref{total_lutt} becomes
+\begin{equation}\begin{aligned}
+	N = 1/2 + V_\text{L}^{LM}
+\end{aligned}\end{equation}
+The same thing happens at the free orbital fixed point; there, \(G_d\) has a single pole at \(z=0\), so \(V_\text{imp} = 1/2\) and we again get \(N = 1/2 + V_\text{L}^{FO}\).
+The change happens when we go to the strong-coupling fixed point.
+There, the impurity self-energy becomes imaginary, so the real pole that existed at the free orbital fixed point moves off the real axis.
+We therefore have \(V_\text{imp} = 0\).
+Assuming the number of particles \(N\) remained constant, we obtain \(N = V_\text{L}^{SC}\).
+The change in the Fermi volume in going from the local moment to the strong coupling fixed point is therefore by \(1/2\).
+If one defines new a Luttinger volume \(\mathcal{V} = 2V\) to also account for the spin degeneracy, we can write:
 \begin{equation}\begin{aligned}
 	\label{luttinger_change}
-	V_L = V_L^0 + 1
-\end{aligned}\end{equation}
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[scale=0.2]{../figures/luttinger_top_change.png}
-\end{figure}
-This is a specific case of the more general result for Kondo lattices obtained by Oshikawa using flux-insertion arguments in \cite{oshikawa2000topological}.
-
-We have not accounted for the RG flow from the local moment fixed point to the strong coupling fixed point. The local moment fixed point is characterized by a decoupled quantum top:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{LM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow}
-\end{aligned}\end{equation}
-It can be shown that the single-particle Green's function for this effective Hamiltonian is similar to the one at the free-orbital fixed point.
-We will use the equation of motion technique to solve for the Green's function.
-The time-domain retarded Green's function is defined as
-\begin{equation}\begin{aligned}
-	G_{d\sigma}(t, t^\prime) = -i\theta(t-t^\prime) \left<\left\{ c_{d\sigma}(t), c^\dagger_{d\sigma}(t^\prime) \right\} \right>
-\end{aligned}\end{equation}
-Since the Hamiltonian is time-translation invariant, we can drop one of the instants:
-\begin{equation}\begin{aligned}
-	G_{d\sigma}(t, 0) = -i\theta(t) \left<\left\{ c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right>
-\end{aligned}\end{equation}
-The time derivative is
-\begin{equation}\begin{aligned}
-	\partial_t G_{d\sigma} &= -i \left[\partial_t \theta(t) \left<\left\{ c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right> + \theta(t) \partial_t \left<\left\{ c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right>\right] \\
-			       &= -i \left[\delta(t) \left<\left\{ c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right> + \theta(t) \left<\left\{ \partial_t c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right>\right] = -i \delta(t) -i\theta(t) \left<\left\{ \partial_t c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right>
-\end{aligned}\end{equation}
-From the Heisenberg equations of motion, we get
-\begin{equation}\begin{aligned}
-	i \partial_t c_{d\sigma}(t) = \left[c_{d\sigma}(t), \mathcal{H}_{LM}(t)\right] = \left[\epsilon_d + U \hat n_{d\overline\sigma}(t)\right]c_{d\sigma}(t)
-\end{aligned}\end{equation}
-Substituting this into the time-derivative gives
-\begin{equation}\begin{aligned}
-	\partial_t G_{d\sigma} &= -i \delta(t) -i \theta(t) \left<\left\{ -i\left[\epsilon_d + U \hat n_{d\overline\sigma}(t)\right]c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right> = -i \delta(t) - i\epsilon_d G_{d\sigma} - U \theta(t) \left<\hat n_{d\overline\sigma}(t)\left\{c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right>\\
-\end{aligned}\end{equation}
-We define another Greens function
-\begin{equation}\begin{aligned}
-	G^\prime = -i \theta(t) \left<\hat n_{d\overline\sigma}(t)\left\{c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right>
-\end{aligned}\end{equation}
-which satisfies the equation of motion
-\begin{equation}\begin{aligned}
-	\partial_t G^\prime = -i \delta(t) -i\theta(t) \left<\left\{\partial_t \hat n_{d\overline\sigma}(t)c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right> -i\theta(t) \left<\left\{\hat n_{d\overline\sigma}(t)\partial_t c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right>
-\end{aligned}\end{equation}
-The second term vanishes because \(\left[\hat n_{d\overline\sigma}, \mathcal{H}_{LM}\right] = 0\) and hence \(\partial_t \hat n_{d\overline\sigma} = 0\). Also,
-\begin{equation}\begin{aligned}
-	\hat n_{d\overline\sigma}(t)\partial_t c_{d\sigma}(t) = -i\hat n_{d\overline\sigma}(t)\left[\epsilon_d + U \hat n_{d\overline\sigma}(t)\right]c_{d\sigma}(t) = -i\left[\epsilon_d + U\right]\hat n_{d\overline\sigma}(t)c_{d\sigma}(t)
-\end{aligned}\end{equation}
-Therefore,
-\begin{equation}\begin{aligned}
-	\partial_t G^\prime = -i \delta(t) \left< \hat n_{d\overline\sigma}(0)\right>- \left[\epsilon_d + U\right]\theta(t) \left<\left\{\hat n_{d\overline\sigma}(t)c_{d\sigma}(t), c^\dagger_{d\sigma}(0) \right\} \right> = -i \delta(t) -i \left( \epsilon_d + U \right) G^\prime
-\end{aligned}\end{equation}
-Changing all quantities to frequency-domain:
-\begin{equation}\begin{aligned}
-	G^\prime(t) &= \int_{-\infty}^\infty d\omega e^{-i\omega t} G^\prime(\omega)\\
-	\partial_t G^\prime(t) &= -\int_{-\infty}^\infty d\omega i \omega e^{-i\omega t} G^\prime(\omega)\\
-	\delta(t) &= \int_{-\infty}^\infty d\omega e^{-i\omega t}
-\end{aligned}\end{equation}
-Substituting these forms in the equation and comparing the coefficients of \(e^{i\omega t}\) gives
-\begin{equation}\begin{aligned}
-	 \omega G^\prime(\omega) =  \left< \hat n_{d\overline\sigma}(0)\right> + \left( \epsilon_d + U \right) G^\prime(\omega)\implies G^\prime(\omega) = \frac{\left< \hat n_{d\overline\sigma}(0)\right>}{\omega - \epsilon_d - U}
-\end{aligned}\end{equation}
-The equation of motion \(G_{d\sigma}\) can now be solved
-\begin{equation}\begin{aligned}
-	\partial_t G_{d\sigma}(t) &= -i \delta(t) - i\epsilon_d G_{d\sigma}(t) - iU G^\prime_{d\sigma}(t) \implies \omega G_{d\sigma}(\omega) = 1 + \epsilon_d G_{d\sigma}(\omega) + U\frac{\left< \hat n_{d\overline\sigma}(0)\right>}{\omega - \epsilon_d - U}\\
-	\implies G_{d\sigma}(\omega) &= \frac{1}{\omega - \epsilon_d} + \frac{U\left< \hat n_{d\overline\sigma}(0)\right>}{\left( \omega - \epsilon_d \right) \left(\omega - \epsilon_d - U\right)}
-\end{aligned}\end{equation}
-For a particle-hole symmetric system, we can substitute \(\epsilon_d = -|\epsilon_d|\) and \(\epsilon_d + U = |\epsilon_d|\).
-\begin{equation}\begin{aligned}
-	G_{d\sigma}(\omega) &= \frac{1}{\omega + |\epsilon_d|} + \frac{U\left< \hat n_{d\overline\sigma}(0)\right>}{\left( \omega + |\epsilon_d| \right) \left(\omega - |\epsilon_d|\right)}
-\end{aligned}\end{equation}
-which reveals two poles at \(\pm |\epsilon_d|\), one above and one below the Fermi surface.
-Since the RHS of eq.~\eqref{total_lutt} counts the number of poles on or below the FS, we will still count one pole for \(G_{d\sigma}\).
-Thus, this Green's function is topological similar to the free-orbital one at \(T=0\).
+	\Delta \mathcal{V}_L = 1
+\end{aligned}\end{equation}
 
@@
 The phase transition is characterised by a change in a topological quantity - the Fermi surface volume.
-As shown in section~\ref{lutt_theorem}, the total number of particles in the system can be expressed in terms of topological quantities:
-\begin{equation}\begin{aligned}
-	N = V_\text{imp}^< + \frac{1}{2}V_\text{imp}^0 + V_L^< + \frac{1}{2}V_L^0
-\end{aligned}\end{equation}
-\(V_L^<\) represents the winding number of the curve traced by the determinant of the conduction electron Greens function on the contour that encloses all real poles below the Fermi surface.
-\(V_L^0\) does the same but for the real poles {\it on} the Fermi surface.
-\(V_\text{imp}^{<,0}\) has the same meanings but for the impurity Greens function.
+As shown in section~\ref{lutt_theorem}, the total number of particles in the system can be expressed in terms of topological winding numbers that count the number of poles and zeros of the impurity and bath Greens functions:
+\begin{equation}\begin{aligned}
+	N = V_\text{imp} + V_L
+\end{aligned}\end{equation}
+\(V_L\) counts the number of poles minus the number of zeros of the bath Greens function at or below the Fermi surface, those at the Fermi surface being counted half.
+\(V_\text{imp}\) is defined in the same way but for the impurity Greens function.
 This equation holds for the free orbital, local moment and strong coupling fixed points.
@@
 
-\subsection*{Presence of two self-energies under symmetry-breaking}
+\subsection{Presence of two self-energies under symmetry-breaking}
 The effective Hamiltonian that describes either the metallic or the insulating phase has $\mathrm{SU}(2)$ symmetry in both the spin and charge sectors.

### 2022-03-31 notes/notes.tex
completed proof of topological transition

@@
-\documentclass[10pt]{report}
+\documentclass[12pt]{report}
 \usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk,pifont,enumitem}
@@
 \usepackage[margin=0.5in,top=0.3in,bottom=1.4in]{geometry}
+
 \usepackage[utf8]{inputenc}
@@
 \usepackage[sfdefault]{roboto}
+
 \renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}
@@
 
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 \centering
@@
 Such a construction is shown in fig.~\ref{cluster-bath}.
-\begin{figure}[htpb!]
+\begin{figure}[!htb]
 	\centering
@@
 
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
@@
 
-\begin{figure}[htpb]
+\begin{figure}[!htb]
  	\centering
@@
 This is calculated numerically in fig.~\ref{cs_cc}.
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
@@
 There exists, therefore, a phase transition at a critical plane \((U_c, K_c, V_c)\), where the ground state changes between the charge singlet \(\ket{\Psi}_2\) and the spin singlet + charge triplet \(\ket{\Psi}_1\).
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
@@
 This holds for both \(V_0 > J_0\) and \(V_0 < J_0\), as shown in the two panels of fig.~\ref{V_vs_D}.
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
@@
 In a similar manner, we checked the variation of the spin and charge probabilities, \(c_s\) and \(c_c\), in the ground state, with increasing bandwith. The result is shown in fig.~\ref{c_vs_D}.
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
@@
 The results for \(U>0\) are shown in fig.~\ref{chi}.
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
@@
 The charge susceptibility for \(U<0\) is shown in fig.~\ref{chi_charge}.
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
@@
 Alternatively, it can be said that since the ground state has only terms with \(\hat n_d=1\), no number fluctuation is possible, and the impurity isospin is not susceptible at all to charge polarisation.
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
@@
 These values were calculated numerically and plotted against temperature in fig.~\ref{cv}.
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
@@
 We have rewritten the holon term in terms of the spin and doublon operators.
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
@@
 In this section, we will compute Luttinger's sum for the various fixed-point theories.
-Luttinger's sum is essentially the volume enclosed by the Fermi surface~\cite{luttinger1960fermi,oshikawa2000topological,seki2017topological}, and Luttinger's theorem states that this volume counts the number of conduction electrons in the system~\cite{luttinger1960fermi,oshikawa2000topological,seki2017topological}.
+Luttinger's sum is essentially the volume enclosed by the Fermi surface~\cite{luttinger1960fermi,oshikawa2000topological,seki2017topological}, and Luttinger's theorem states that this volume counts the number of electrons in the system~\cite{luttinger1960fermi,oshikawa2000topological,seki2017topological}.
 
@@
 \end{gather}
-The total number of electrons is given by the sum of the number of electrons in the conduction bath and at the impurity:
+The total number of electrons is given by the sum of the number of electrons in the conduction bath and at the impurity~\cite{hewson1993,langreth1966}:
 \begin{equation}\begin{aligned}
@@
 \begin{equation}\begin{aligned}
-	N &= \underbrace{P_{\text{Det }G_d}(\Gamma_<) - Z_{\text{Det }G_d}(\Gamma_<)}_{V_\text{imp}^<} + \underbrace{\frac{1}{2}\left[P_{\text{Det }G_d}(\Gamma_0) - Z_{\text{Det }G_d}(\Gamma_0)\right]}_{V_\text{imp}^0} + \underbrace{P_{\text{Det }G_{c}^{0}}(\Gamma_<) - Z_{\text{Det }G_{c}^{0}}(\Gamma_<)}_{V_\text{L}^<} + \underbrace{\frac{1}{2}\left[P_{\text{Det }G_{c}^{0}}(\Gamma_0) - Z_{\text{Det }G_{c}^{0}}(\Gamma_0)\right]}_{V_\text{L}^0}\\
-	  &= V_\text{imp}^< + \frac{1}{2}V_\text{imp}^0 + V_L^< + \frac{1}{2}V_L^0
-\end{aligned}\end{equation}
-The average number of particles can thus be expressed purely in terms of the number of poles and zeros of the impurity and the conduction electron Green's functions.
-The number of poles in the conduction electron Greens function \(G_c^0\) minus the number of zeros gives the Luttinger volume \(V_L = V_L^< + \frac{1}{2}V_L^0\)~\cite{seki2017topological}, while those in the impurity Greens function \(V_\text{imp} = V_\text{imp}^< + \frac{1}{2}V_\text{imp}^0\) give the number of localised excitations on the impurity:
+	N =& \underbrace{P_{\text{Det }G_d}(\Gamma_<) - Z_{\text{Det }G_d}(\Gamma_<)}_{N_\text{imp}^<} + \underbrace{\frac{1}{2}\left[P_{\text{Det }G_d}(\Gamma_0) - Z_{\text{Det }G_d}(\Gamma_0)\right]}_{N_\text{imp}^0} + \underbrace{P_{\text{Det }G_{c}^{0}}(\Gamma_<) - Z_{\text{Det }G_{c}^{0}}(\Gamma_<)}_{N_\text{L}^<} \\
+	  &+ \underbrace{\frac{1}{2}\left[P_{\text{Det }G_{c}^{0}}(\Gamma_0) - Z_{\text{Det }G_{c}^{0}}(\Gamma_0)\right]}_{N_\text{L}^0}\\
+	  =& N_\text{imp}^< + \frac{1}{2}N_\text{imp}^0 + N_L^< + \frac{1}{2}N_L^0
+\end{aligned}\end{equation}
+The average number of particles can thus be expressed purely in terms of the number of real poles and real zeros of the impurity and the conduction electron Green's functions.
+\(N_\text{imp}^<\left(N_\text{imp}^<\right)\) is the number of poles minus the number of zeros of the impurity Greens function inside (on) the Fermi surface.
+\(N_\text{imp} = N_\text{imp}^0 + \frac{1}{2}N_\text{imp}^0\)  therefore gives the total number of localised eigenstates of the system.
+Similarly, \(N_L^<\left( N_L^0 \right) \) gives the number of real poles in the conduction electron Greens function minus the number of real zeros, and \(N_L = N_L^< + \frac{1}{2}N_L^0\) gives the total number of delocalised eigenstates of the system.
 \begin{equation}\begin{aligned}
 	\label{total_lutt}
-	N = V_\text{imp} + V_L
-\end{aligned}\end{equation}
-
+	N = N_\text{imp} + N_L
+\end{aligned}\end{equation}
 Note that this also holds at the free orbital fixed point, because it is a special case of the strong-coupling fixed point with \(V=0\).
@@
 We now compare the Luttinger volume across the fixed points.
-At the local moment fixed point, the impurity Greens function has a single pole at \(z<0\) and a zero at \(z=0\), so \(V_\text{imp} = 1 - 1/2 = 1/2\), and eq.~\ref{total_lutt} becomes
-\begin{equation}\begin{aligned}
-	N = 1/2 + V_\text{L}^{LM}
-\end{aligned}\end{equation}
-The same thing happens at the free orbital fixed point; there, \(G_d\) has a single pole at \(z=0\), so \(V_\text{imp} = 1/2\) and we again get \(N = 1/2 + V_\text{L}^{FO}\).
-The change happens when we go to the strong-coupling fixed point.
-There, the impurity self-energy becomes imaginary, so the real pole that existed at the free orbital fixed point moves off the real axis.
-We therefore have \(V_\text{imp} = 0\).
-Assuming the number of particles \(N\) remained constant, we obtain \(N = V_\text{L}^{SC}\).
+At the local moment fixed point, the impurity Greens function has a single pole at \(z<0\) and a zero at \(z=0\), so \(N_\text{imp} = 1 - 1/2 = 1/2\), and eq.~\ref{total_lutt} becomes
+\begin{equation}\begin{aligned}
+	N = 1/2 + N_\text{L}^{LM}
+\end{aligned}\end{equation}
+The same thing happens at the free orbital fixed point; there, \(G_d\) has a single pole at \(z=0\), so \(N_\text{imp} = 1/2\) and we again get \(N = 1/2 + N_\text{L}^{FO}\).
+The change happens when we go to the strong-coupling resonant-level fixed point.
+There, the impurity self-energy can be written as~\cite{anderson_1961,hewson1993,coleman2015}
+\begin{equation}\begin{aligned}
+	\Sigma_d^\text{sc} = \text{Re}\left[\Sigma_d^\text{sc}\right] - i\Delta
+\end{aligned}\end{equation}
+That is, the self-energy becomes imaginary, so the real pole that existed at the free orbital fixed point moves off the real axis.
+We therefore have \(N_\text{imp} = 0\).
+Assuming the number of particles \(N\) remained constant, we obtain \(N = N_\text{L}^{SC}\).
 The change in the Fermi volume in going from the local moment to the strong coupling fixed point is therefore by \(1/2\).
-If one defines new a Luttinger volume \(\mathcal{V} = 2V\) to also account for the spin degeneracy, we can write:
+If one defines new a Luttinger volume \(\mathcal{N}_L = 2N_L\) to also account for the spin degeneracy, we can write:
 \begin{equation}\begin{aligned}
 	\label{luttinger_change}
-	\Delta \mathcal{V}_L = 1
-\end{aligned}\end{equation}
+	\Delta \mathcal{N}_L = 1
+\end{aligned}\end{equation}
+This is a specific case of the more general result for Kondo lattices obtained by Oshikawa using flux-insertion arguments\cite{oshikawa2000topological}.
 
@@
 \begin{equation}\begin{aligned}
-	R = 1 + \sin^2 \left( \frac{\pi}{2}\Delta N_L \right) = 1 + \sin^2 \frac{\pi}{2} = 2
+	R = 1 + \sin^2 \left( \frac{\pi}{2}\Delta \mathcal{N}_L \right) = 1 + \sin^2 \frac{\pi}{2} = 2
 \end{aligned}\end{equation}
@@
 
-\begin{figure}[!htpb]
+\begin{figure}[!htb]
 	\centering
@@
 	\label{greens_func_siam}
-	\left(G_{H-H}(\omega)\right)_\text{loc} &= \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right] \\
-	\left(G_{H-H}(\omega)\right)_\text{n-n} &= \left(G_{H-H}(\omega)\right)_{i,i+1}^p - \left(G_{H-H}(-\omega)\right)_{i+1,i}^h = \frac{1}{w}\sum_n \left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
+	\left(G_{H-H}(\omega)\right)_\text{loc} = \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right] \\
+	= G(\omega)_\text{aux,dd}
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	\left(G_{H-H}(\omega)\right)_\text{n-n} = \left(G_{H-H}(\omega)\right)_{i,i+1}^p - \left(G_{H-H}(-\omega)\right)_{i+1,i}^h = \frac{1}{w}\sum_n \left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn} \right.\\
+ - \left.\left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]= G(\omega)_\text{aux,dz}
 \end{aligned}\end{equation}
@@
 
-\begin{figure}[!htpb]
+\begin{figure}[!htb]
 \centering
@@
 \subsection{Topological nature of the transition}
-The phase transition is characterised by a change in a topological quantity - the Fermi surface volume.
-As shown in section~\ref{lutt_theorem}, the total number of particles in the system can be expressed in terms of topological winding numbers that count the number of poles and zeros of the impurity and bath Greens functions:
-\begin{equation}\begin{aligned}
-	N = V_\text{imp} + V_L
-\end{aligned}\end{equation}
-\(V_L\) counts the number of poles minus the number of zeros of the bath Greens function at or below the Fermi surface, those at the Fermi surface being counted half.
-\(V_\text{imp}\) is defined in the same way but for the impurity Greens function.
-This equation holds for the free orbital, local moment and strong coupling fixed points.
-At the local moment fixed point, the impurity Greens function has a single real pole below the Fermi surface, while that pole moves off the real axis at the strong-coupling fixed point.
-That means, \(V_\text{imp}^\text{loc} = V_\text{imp}^\text{sc} + 1\).
-Assuming the total number of particles remains conserved in the process, we get the equation
-\begin{equation}\begin{aligned}
-	V_L^\text{sc} = V_L^\text{loc} + 1
-\end{aligned}\end{equation}
-This shows that the localised \(d-\)electrons is hybridising with the bath and this shows up in the transfer of a real pole from the impurity Greens function into the bath Greens function.
-The addition of this pole "enlarges" the Fermi volume.
-The transition from the metal to the insulator is therefore characterised by the change in the winding number by 1.
+As shown in section~\ref{lutt_theorem}, there is a difference in the value of the Luttinger volume between the local moment (LM) and the strong-coupling (SC) fixed points.
+If we define \(\mathcal{N}_L\) as the Luttinger volume with the spin-degeneracy accounted for, we can write
+\begin{equation}\begin{aligned}
+	\label{lutt_change}
+	\mathcal{N}_L^\text{lm} - \mathcal{N}_L^\text{sc} = 1
+\end{aligned}\end{equation}
+where \(\mathcal{N}_L^\text{lm},\mathcal{N}_L^\text{sc}\) are the Luttinger volumes at the local moment and strong-coupling fixed points respectively.
+This equation expresses the fact that the Luttinger volume of the bath increases by \(1\) when the system is tuned from LM to SC, and this happens because the single-particle impurity excitation in the lower-Hubbard at the atomic limit gets transferred to the bath Greens function in the process.
+The quantity which tracks this transfer is therefore \(\mathcal{N}_\text{imp}\), the number of poles minus the number of zeros in the impurity Greens function at and below the Fermi surface:
+\begin{equation}\begin{aligned}
+	\label{imp_count_def}
+	\mathcal{N}_\text{imp} = \begin{cases}
+		1 & \text{ at LM}\\
+		0 & \text{ at SC}
+	\end{cases}\implies \Delta \mathcal{N}_\text{imp} = 1
+\end{aligned}\end{equation}
+The Luttinger volume \(\mathcal{N}_L\) is related to this impurity count by the equation
+\begin{equation}\begin{aligned}
+	\mathcal{N}_L = \mathcal{N} - \mathcal{N}_\text{imp}
+\end{aligned}\end{equation}
+where \(\mathcal{N}\) is the total number of electrons in the system, accounting for the spin degeneracy.
+If we keep this total number fixed (isolated system), the changes in the impurity count and Luttinger volume become constrained:
+\begin{equation}\begin{aligned}
+	\Delta \mathcal{N}_L = - \Delta \mathcal{N}_\text{imp}~.
+\end{aligned}\end{equation}
+Eq.~\ref{imp_count_def} then readily implies eq.~\ref{lutt_change}.
+
+In order to connect this impurity topological change with the bulk model, we write the total number of particles in the bulk system in the following manner:
+\begin{equation}\begin{aligned}
+	\mathcal{N} = \mathcal{N}_\text{loc} + \mathcal{N}_\text{deloc}
+\end{aligned}\end{equation}
+\(\mathcal{N}_\text{loc}\) is the number of real poles minus the number of zeros of the local Greens function.
+\(\mathcal{N}_\text{deloc}\) is the number of real poles minus the number of zeros of the \(k-\)space Greens functions.
+The former (latter) contributes only in the insulating (metallic) phase, because in the metallic (insulating) phase, the local (\(k-\)space) Greens function develop imaginary self-energy and the real poles in these Greens functions get replaced by imaginary poles.
+Together, these two terms accurately count the total number of particles in both these phases.
+These two terms are defined as
+\begin{equation}\begin{aligned}
+	\mathcal{N}_\text{loc} = \sum_i \mathcal{N}_i = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_i(z)\right], ~ ~ ~\mathcal{N}_\text{deloc} = \sum_k \mathcal{N}_k = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_k(z)\right] = \mathcal{N}_L
+\end{aligned}\end{equation}
+\(G_i(z)\) is the local Greens function at site \(i\) of the bulk model, and \(G_k(z)\) is the \(k-\)space Greens function in the bulk model.
+\(N_\text{deloc}\) is just the Luttinger volume \(\mathcal{N}_L\) of the bulk system.
+With this, the total number of particles in the bulk can be expressed as
+\begin{equation}\begin{aligned}
+	\label{bulk_total}
+	\mathcal{N} = \sum_i \mathcal{N}_i + \mathcal{N}_\text{L}
+\end{aligned}\end{equation}
+From eq.~\ref{greens_func_siam}, we know that the bulk local Greens function is equal to that of the auxiliary model, and that gives \(\sum_i \mathcal{N}_i = \mathcal{N}_\text{imp}\sum_i = \mathcal{N} \mathcal{N}_\text{imp}\).
+There we used the fact that for a half-filled system, the total number of sites is equal to the total number of particles in the system.
+Substituting this into eq.~\ref{bulk_total} and again using \(\Delta \mathcal{N} = 0\) gives
+\begin{equation}\begin{aligned}
+	\mathcal{N} = \mathcal{N} \mathcal{N}_\text{imp} + \mathcal{N}_\text{L} \implies \Delta \mathcal{N}_\text{L} = - \mathcal{N} \Delta \mathcal{N}_\text{imp}
+\end{aligned}\end{equation}
+We already know that \(\Delta \mathcal{N}_\text{imp}=1\) across the transition, so we get
+\begin{equation}\begin{aligned}
+	\mathcal{N}_L^\text{metal} - \mathcal{N}_L^\text{insulator} = \mathcal{N}\left(\mathcal{N}_\text{imp}^\text{sc} - \mathcal{N}_\text{imp}^\text{lm}\right) = \mathcal{N}
+\end{aligned}\end{equation}
+The metal-insulator transition is therefore characterised by a change in the topological quantity \(\mathcal{N}_L\).
+The topological nature arises from the fact that it can be expressed in terms of winding numbers related to the corresponding Greens functions.
+\(\mathcal{N}_\text{imp}\), which derives from the impurity Greens function \(G_d\), is related to the winding numbers of the curves \(\text{Det}[G_d^{-1}(\Gamma^<)]\) and \(\text{Det}[G_d^{-1}(\Gamma^0)]\).
+The winding number is simply the number of times this function encircles the origin when traced on the curves \(\Gamma^<\) and \(\Gamma^0\) that enclose all poles inside and on the Fermi surface respectively.
+An example of such a winding number is shown in fig.~\ref{imp_winding}.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[scale=0.2]{../figures/luttinger_top_change.png}
+	\caption{The green lines describe the winding number related to the impurity Greens function, while the blue lines do it for the bath.
+At the local moment fixed point \(V=0\), the impurity has a winding number of 1 because the curve encircles the origin once.
+At the strong-coupling fixed point, this winding number becomes zero, indicated by the fact that the curve does not encircle the origin even once.
+The reduction in the winding number on the part of the impurity is directly linked to the increase in the winding number of the bath - it encircles the origin once at the local moment fixed point but twice at strong-coupling.}
+	\label{imp_winding}
+\end{figure}
 
@@
 \textit{This transfer of spectral weight across energy scales of the order of \(U\), as well as the lack of poles at zero energies, is referred to as mottness}~\cite{phillips2006mottness}.
-\begin{figure}[!htpb]
+\begin{figure}[!htb]
 	\centering
@@
  \end{aligned}\end{equation}
- \begin{figure}[htpb]
+ \begin{figure}[!htb]
  	\centering
@@
  \end{aligned}\end{equation}
- \begin{figure}[htpb!]
+ \begin{figure}[!htb]
  	\centering
@@
  This entire procedure is depicted in fig.~\ref{dimer-bath}.
- \begin{figure}[htpb]
+ \begin{figure}[!htb]
  	\centering
@@
 These choices are shown in fig.~\ref{off-diag-contrib}.
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
@@
 \end{aligned}\end{equation}
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering

### 2022-03-31 notes/notes.tex
tiled to obtain periodic models

@@
 \xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
-\epsilon_{\vec{q}} &=& -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})~
 \end{eqnarray}
-where \(\epsilon_{\vec{q}}\) is the tight-binding dispersion.
+where \(\epsilon_{\vec{q}} = -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})\) is the tight-binding dispersion.
 
@@
 \begin{equation}\begin{aligned}
-	\Sigma(\vec k,\omega) = G_0(\vec k,\omega)^{-1} - G(\vec k,\omega)^{-1}
-\end{aligned}\end{equation}
-where the $G_{0}(\vec k, \omega)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system.
+	\Sigma(\vec k,\omega) = \left(G^{(0)}(\vec k,\omega)\right)^{-1} - G(\vec k,\omega)^{-1}
+\end{aligned}\end{equation}
+where $\left(G^{(0)}(\vec k,\omega)\right)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system.
 Substituting this as well as the full Greens function $G_{H-H}(\vec k, \omega)$ into Dyson's equation gives
 \begin{equation}\begin{aligned}
-	\Sigma_{H-H}(\vec k,\omega) &= \omega +t^{H-H}\xi_{\vec k} - \left\{\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}\\
-&= 	 \omega +t^{H-H}\xi_{\vec k} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}
+	\label{self-energy1}
+	\Sigma_{H-H}(\vec k,\omega) &= \left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left\{\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}\\
+&= \left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}
 \end{aligned}\end{equation}
@@
 One can apply a test to this method: it involves considering the case of infinite number of nearest-neighbours $w\to\infty$ (the coordination number, and effectively the dimension).
-Here, as has been argued in the DMFT literature, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$ such that the kinetic energy of the associated tight-binding lattice model is finite.
-This allows for the competition between the kinetic and potential terms of the Hamiltonian to drive a metal-insulator transition in the limit of $w\to\infty$ as well.
-Further, it has been argued in the DMFT literature that the Greens function matrix of the Hubbard model on the Bethe lattice with $w\to\infty$ becomes purely local (i.e., it has vanishing inter-site matrix elements).
-We can also see this from eqs.\eqref{green_eq_final_siam}- the nearest-neighbour inverse Greens function vanishes in the limit of $w \to \infty$:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}_{H-H}(\omega)\right)_{ij}^\sigma = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn} \implies \lim_{w \to \infty}\left(\mathcal{G}_{H-H}(\omega)\right)_{ij}^\sigma \to 0
-\end{aligned}\end{equation}
-There we used the fact since at half-filling on an $SU(2)$ symmetric model, we expect $\left<\hat n_{i \uparrow} \right> = \frac{1}{2}$, the orthonormal expansion of $c^\dagger_{i \sigma}\ket{\Phi_0} = \sum_n d^p_n \ket{\Phi_n}$ and \(c^\dagger_{i+1,\sigma}\ket{\Phi_0}=z^p_n\ket{\Phi_n}\) are constrained such that $\sum_n |d^p_n|^2 = \sum_n |z^p_n|^2 = \frac{1}{2}$, so that the only term that scales with $w$ is $w$ itself.
-This result then implies that $G^{H-H}$ matrix has no $k$ dependence.
-
-In this limit, the self-energy also simplifies:
-\begin{equation}\begin{aligned}
-	\lim_{w \to \infty}\Sigma_H(\vec k,\omega) = = \omega +t^{H-H}\xi_{\vec k} - \left\{\sum_n \left[|d^p_n|^2  \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}- |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}
-\end{aligned}\end{equation}
-We can now see that even in the limit of $w\to\infty$, the competition between ${g}_{0}$ (the on-site repulsion) and the hopping related kinetic energy ($t^{H}\xi_{\vec{k}}$) can lead to a metal-insulator transition.
+In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
+This allows a metal-insulator transition in the limit of $w\to\infty$ as well.
+In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}.
+This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy1}.
+Applying the limit of \(w\to \infty\) on that equation gives
+\begin{equation}\begin{aligned}
+	\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}\right\} = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux,dd}(\omega)\right\}^{-1}
+\end{aligned}\end{equation}
+where \(G^{(0)}(\vec k,\omega)\) is the non-interacting Greens function and \(G_\text{aux,dd}(\omega)\) is the site-diagonal Greens function of the auxiliary model.
+It is clear from the final form that only the diagonal term \(G_\text{aux,dd}(\omega)\) of the interacting Greens function affects the self-energy while the off-diagonal part \(G_\text{aux,dz}\) fails to contribute as \(w \to \infty\).
+Even the non-interacting part Greens function can be shown to be diagonal in the limit of \(w\to\infty\)~\cite{kuramoto_manybody}.
+From its definition in time domain, we have
+\begin{equation}\begin{aligned}
+	G^{(0)}(\vec k, t) = -i\theta(t) \left<\left\{c_{\vec k}(t), c^\dagger_{\vec k}\right\} \right> = -i\theta(t) \left<\left\{e^{i H^{(0)}t} c_{\vec k} e^{-i H^{(0)}t}, c^\dagger_{\vec k}\right\} \right> = -i\theta(t) e^{-i \epsilon_{\vec k}t}\left[ \left<1 - \hat n_{\vec k}\right> + \left<\hat n_{\vec k}\right>\right] = -i \theta(t) e^{-i \epsilon_{\vec k}t}
+\end{aligned}\end{equation}
+A quick Fourier transform to \(\omega-\)domain shows that this is identical to the \(G^{(0)}(\vec k, \omega)\) defined just above eq.~\ref{self-energy}.
+We note that \(|G^{(0)}(\vec k, t)| \leq 1\).
+Using the Fourier transform  definition
+\begin{equation}\begin{aligned}
+	f(\vec k) = \frac{1}{d_N}\sum_{\vec r_i}h(\vec r_i) e^{i \vec{k}\cdot\vec{r}_i}
+\end{aligned}\end{equation}
+where \(d_N\) is a factor that only depends on the total number of sites and not on the coordination number, we can write
+\begin{equation}\begin{aligned}
+	|G^{(0)}(\vec k, t)|^2 = \frac{1}{d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}
+\end{aligned}\end{equation}
+From the inequality \(|G^{(0)}(\vec k, t)| \leq 1\), we get
+\begin{equation}\begin{aligned}
+	1 \geq \frac{1}{N}\sum_k |G^{(0)}(\vec k, t)|^2 = \frac{1}{N d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* \underbrace{\sum_k e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}}_{N \delta_{\vec r_i = \vec r_j}} = \frac{1}{d_N^2}\sum_{\vec r_i} |G^{(0)}(\vec r_i, t)|^2
+\end{aligned}\end{equation}
+For a coordination number of \(w\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
+Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{w}\).
+In contrast, there is only one local Greens function, that for \(\vec r_i=0\).
+The local Greens function therefore scales independent of \(w\).
+This implies that
+\begin{equation}\begin{aligned}
+	\lim_{w\to \infty}G^{(0)}(\vec k,\omega) = G^{(0)}(\vec r=0,\omega)
+\end{aligned}\end{equation}
+Since both the non-interacting and the interaction Greens functions lose their non-locality, the self-energy becomes completely local in the limit of \(w \to \infty\).
 
@@
 \begin{gather}
-\label{green_eq_final_siam}
+\label{green_eq_final_2siam}
 	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
@@
 \begin{equation}\begin{aligned}
-	\label{greens_func_siam}
 	&\left(G_{H-H}(\omega)\right)_\text{loc} = \left(\mathcal{G}_{H-H}(\omega)\right)_{ii}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn} - |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\right] = G_\text{aux}(d_1,d_1;\omega)\\
@@
 \end{gather}
-On a 2D square lattice with lattice spacing $a$, this simplifies to
+On a 2D square lattice with lattice spacing $a$, this simplifies to (same as eq.~\ref{2dsquaretb})
 \begin{eqnarray}
-	\label{2dsquaretb}
 \xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
@@
 \begin{equation}\begin{aligned}
-	\label{k_Gf_siam}
-	G_{H-H} (\vec k, \omega) = G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) \right.\\
-	+ \left.G_\text{aux}(0_2,d_1;\omega)\right]
+	G_{H-H} (\vec k, \omega) = G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] \\
+	 + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]
 \end{aligned}\end{equation}
@@
 Since both the non-interacting and the interaction Greens functions lose their non-locality, the self-energy becomes completely local in the limit of \(w \to \infty\).
+
+\chapter{The Periodic Anderson and Kondo models}
+The heavy Fermion systems are described by periodic versions of the single impurity models, where instead a lattice of impurities \(\left\{ d_i \right\} \) hybridises with a conduction bath lattice \(\left\{ i \right\} \).
+The periodic Anderson model is defined by the Hamiltonian
+\begin{equation}\begin{aligned}
+	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right)  - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma}
+\end{aligned}\end{equation}
+
+As before, we will work with a generalised form of it where we also consider a spin-exchange interaction between the impurity sites and the bath sites:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right) + J \sum_i \vec{S}_{d_i}\cdot\vec{s}_i - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma}
+\end{aligned}\end{equation}
+One can also introduce an RKKY interaction \(J_\text{RKKY}\) between the nearest neighbour impurity spins:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right) + J \sum_i \vec{S}_{d_i}\cdot\vec{s}_i - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma} \\
+	+ J^\prime\sum_{\left<d_i,d_j \right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
+\end{aligned}\end{equation}
+
+\section{Creating a bulk periodic Anderson model by tiling with generalised single-impurity Anderson models: no RKKY}
+
+The auxiliary model we will be using is a generalised SIAM with attractive interaction on the bath zeroth site and explicit particle-hole asymetry on the impurity:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux} = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s}_0 + \eta \sum_\sigma\tau_{d\sigma}
+\end{aligned}\end{equation}
+where \(\tau = \hat n - 1/2\).
+
+We will use this as the auxiliary model to study the Hubbard model.
+We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
+Note that the impurity level and the conduction bath can be tuned to half-filling by setting \(\eta=0\) and \(\mu=0\) respectively.
+To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(d_i\) of the impurity lattice, and the bath sites will constitute the bulk lattice sites.
+We will also identity the zeroth site of the SIAM lattice as one particular site \(i\) of the conduction bath lattice:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux}(d_i) = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) +J \vec{S}_{d_i}\cdot\vec{s}_i + \eta \sum_\sigma\tau_{d_i\sigma}
+\end{aligned}\end{equation}
+Once we have this local Hamiltonian for a particular site, we translate this over all \(N\) sites \(\left\{\left(d_i,i\right) \right\} \):
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{full} = \sum_{i} \mathcal{H}_\text{aux}(d_i) = N\sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) +J \sum_i\vec{S}_{d_i}\cdot\vec{s}_i \\
+	+ \eta \sum_{i,\sigma}\tau_{d_i\sigma}
+\end{aligned}\end{equation}
+
+We end up with a generalised periodic Anderson model:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{GPAM} = \sum_{k\sigma}\left(\left(\epsilon_k\right)_\text{GPAM} - \mu_\text{GPAM}\right)\tau_{k\sigma} - \frac{U_\text{GPAM}}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V_\text{GPAM} \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right)\\
+	+ J_\text{GPAM} \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + \eta_\text{GPAM} \sum_{i,\sigma}\tau_{d_i\sigma}
+\end{aligned}\end{equation}
+The mapping between the parameters of the auxiliary model and that of the bulk are
+\begin{equation}\begin{aligned}
+	\label{map_pam_bulk}
+	\left(\epsilon_k\right)_\text{GPAM} = N\epsilon_k, ~ ~ \mu_\text{GPAM} = N\mu, ~ ~ U_\text{GPAM} = U, ~ ~ V_\text{GPAM} = V, ~ ~ J_\text{GPAM} = J, ~ ~ \eta_\text{GPAM} = \eta
+\end{aligned}\end{equation}
+
+\section{Creating a bulk periodic Anderson model by tiling with two-impurity Anderson models: with RKKY}
+
+This time we will use a two-impurity model with a spin-exchange coupling between the impurities as the auxiliary model:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux} = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\sum_{i=1,2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right)^2 + \sum_{i=1,2}\left[V \sum_{\sigma} \left(c^\dagger_{0_i\sigma} c_{d_i\sigma} + h.c.\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i}\right] + \eta \sum_\sigma\tau_{d\sigma}\\
+ + J^\prime\vec{S}_{d_1}\cdot\vec{S}_{d_2}
+\end{aligned}\end{equation}
+where \(\tau = \hat n - 1/2\).
+
+We will use this as the auxiliary model to study the Hubbard model.
+We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
+Note that the impurity level and the conduction bath can be tuned to half-filling by setting \(\eta=0\) and \(\mu=0\) respectively.
+To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity sites \(d_1 \) and \(d_2\) as particular nearest-neighbour sites \(d_i, d_{j}\) of the impurity lattice, and the bath sites will constitute the bulk lattice sites.
+We will also identity the bath sites \(0_1,0_2\) as two particular nearest-neighbour sites \(i,j\) of the conduction bath lattice:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux}(d_i, d_{j}) = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left[\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + \left(\hat n_{d_{j} \uparrow} - \hat n_{d_{j} \downarrow} \right) ^2\right] + V \sum_{\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + c^\dagger_{j,\sigma} c_{d_{j},\sigma} + h.c.\right)\\
+ + J \left(\vec{S}_{d_i}\cdot\vec{s}_i + \vec{S}_{d_{j}}\cdot\vec{s}_{j}\right) + \eta \sum_\sigma\left(\tau_{d_i\sigma} + \tau_{d_{j}\sigma}\right)+ J^\prime\vec{S}_{d_i}\cdot\vec{S}_{d_j}\\
+\end{aligned}\end{equation}
+Once we have this local Hamiltonian for a particular site, we translate this over all nearest-neighbour pairs \((i,j)\) of the lattice.
+There are \(Nw/2\) of these.
+To ensure the bulk model scales as \(N\), we divide this sum by \(w/2\).
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{full} = \frac{2}{w}\sum_{\left<i,j\right>} \mathcal{H}_\text{aux}(d_i) = N\sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - 2\frac{U}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + 2V \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) \\
+	 + 2J \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + 2\eta \sum_{i,\sigma}\tau_{d_i\sigma} + \frac{2}{w}J^\prime\sum_{\left<i,j\right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
+\end{aligned}\end{equation}
+
+We end up with a generalised periodic Anderson model with RKKY interaction:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{GPAM} = \sum_{k\sigma}\left(\left(\epsilon_k\right)_\text{GPAM} - \mu_\text{GPAM}\right)\tau_{k\sigma} - \frac{U_\text{GPAM}}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V_\text{GPAM} \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right)\\
+	+ J_\text{GPAM} \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + \eta_\text{GPAM} \sum_{i,\sigma}\tau_{d_i\sigma} + J^\prime_\text{GPAM}\sum_{\left<i,j\right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
+\end{aligned}\end{equation}
+The mapping between the parameters of the auxiliary model and that of the bulk are
+\begin{equation}\begin{aligned}
+	\label{map_pam_bulk}
+	\left(\epsilon_k\right)_\text{GPAM} = N\epsilon_k, ~ ~ \mu_\text{GPAM} = N\mu, ~ ~ U_\text{GPAM} = 2U, ~ ~ V_\text{GPAM} = 2V, ~ ~ J_\text{GPAM} = 2J, ~ ~ \eta_\text{GPAM} = 2\eta, ~ ~ J^\prime_\text{GPAM} = \frac{2}{w}J^\prime
+\end{aligned}\end{equation}
 
@@
 	\Delta K = -K n_j\frac{4 U_b + K}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}}
+\end{aligned}\end{equation}
+
+\chapter{Zero temperature Greens function in frequency domain}
+
+\label{appx-spectral-func}
+The impurity retarded Green's function (assuming the Hamiltonian to be time-independent, which it is) is defined as
+\begin{equation}\begin{aligned}
+	G_{dd}^\sigma(t) = -i\theta(t) \left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right>
+\end{aligned}\end{equation}
+where the average \(\left< \right>\) is over a canonical ensemble at temperature \(T\), and \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in.
+The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term.
+What follows is a standard calculation where we write the Green's function in the Lehmann-Kallen representation.
+The ensemble average for an arbitrary operator \(\hat M\) can be written in terms of the exact eigenstates of the fixed point Hamiltonian:
+\begin{equation}\begin{aligned}
+	H^* \ket{n} &= E_n^* \ket{n}, ~ ~ ~\left<\hat M \right> &\equiv \frac{1}{Z}\sum_n \bra{n} \hat M \ket{n} e^{-\beta E_n^*}
+\end{aligned}\end{equation}
+where \(Z = \sum_n e^{-\beta E_n^*}\) is the fixed point partition function and \(\left\{ \ket{n} \right\} \) is the set of eigenfunctions of the fixed point Hamiltonian. We can therefore write
+\begin{equation}\begin{aligned}
+	&\left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right> \\
+	&= \frac{1}{Z}\sum_{m}e^{-\beta E_m}\bra{m}\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\} \ket{m}\\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( \mathcal{O}_{\sigma}(t)\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma}(t)\right) \ket{m} && \left[\sum_n \ket{n}\bra{n} = 1\right]  \\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\right) \ket{m}\\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\left( e^{i\left( E_m - E_n \right)  t}\bra{m}\mathcal{O}_{\sigma}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} \ket{m} + e^{i\left( E_n - E_m \right)  t}\bra{m}\mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma} \ket{m}\right)\\
+	&= \frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
+\end{aligned}\end{equation}
+The time-domain impurity Green's function can thus be written as (this is the so-called Lehmann-Kallen representation)
+\begin{equation}\begin{aligned}
+	G_{dd}^\sigma = -i\theta(t)\frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
+\end{aligned}\end{equation}
+We are interested in the frequency domain form.
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega) &= \int_{-\infty}^\infty dt e^{i \omega t}G_{d d}^\sigma(t) \\
+			       &= \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t}
+\end{aligned}\end{equation}
+To evaluate the time-integral, we will use the integral representation of the Heaviside function:
+\begin{equation}\begin{aligned}
+	\theta(t) = \frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty \frac{1}{x- i\eta}e^{ixt}dx
+\end{aligned}\end{equation}
+With this definition, the integral in \(G_{dd}^\sigma(\omega)\) becomes
+\begin{equation}\begin{aligned}
+	\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t} &= \left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta}\int_{-\infty}^\infty dt e^{i\left( \omega + E_m - E_n + x\right)t} \\
+									     &=\left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta} 2\pi \delta\left( \omega + E_m - E_n + x\right) \\
+									     &=\left(-i\right)\frac{1}{i}\lim_{\eta \to 0^+} \frac{-1}{\omega + E_m - E_n- i\eta} \\
+									     &=\frac{1}{\omega + E_m - E_n} \\
+\end{aligned}\end{equation}
+The frequency-domain Green's function is thus
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
+\end{aligned}\end{equation}
+The zero temperature Green's function is obtained by taking the limit of \(\beta \to \infty\).
+In both the partition function as well as inside the summation, the only term that will survive is the exponential of the ground state energy \(E_0\).
+\begin{equation*}\begin{aligned}
+	Z \equiv \sum_m e^{-\beta E_m} \implies \lim_{\beta \to \infty}Z = d_0 e^{-\beta E_0}, && E_0 \equiv \text{min}\left\{ E_n \right\} 
+\end{aligned}\end{equation*}
+where \(d_0\) is the degeneracy of the ground state. The Greens function then simplifies to
+\begin{equation}\begin{aligned}
+	\label{Gf_lk}
+	G_{d d}^\sigma(\omega, \beta \to \infty) &= \frac{1}{d_0e^{-\beta E_0}}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left[e^{-\beta E_m}\delta_{E_m, E_0} + e^{-\beta E_n}\delta_{E_n, E_0}\right]\frac{1}{\omega + E_m - E_n}\\
+						 &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n}\right]\\
+\end{aligned}\end{equation}
+The label 0 sums over all states \(\ket{0}\) with energy \(E_0\).
+The spectral function is the imaginary part of this Green's function.
+To extract the imaginary part, we insert an infinitesimal imaginary part in the denominator:
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega, \eta) = \frac{1}{d_0}\lim_{\eta \to 0^-}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n + i\eta} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n + i\eta}\right]\\
+\end{aligned}\end{equation}
+The spectral function at zero temperature can then be written as
+\begin{equation}\begin{aligned}
+	\mathcal{A(\omega)} &= -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] \\
+			    &= \frac{1}{d_0}\frac{1}{\pi}\text{ Im }\left[\lim_{\eta \to 0^-}\sum_{n,0}\left(\frac{-i\eta ||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2}{\left(\omega + E_0 - E_n\right)^2 + \eta^2} + \frac{-i\eta ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2}{\left(\omega - E_0 + E_n\right)^2 + \eta^2}\right)\right]\\
+			    &= \frac{1}{d_0}\frac{1}{\pi}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\pi\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\pi\delta\left(\omega - E_0 + E_n\right)\right]\\
+			    &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]\\
 \end{aligned}\end{equation}
@@
 
-\chapter{Zero temperature Greens function in frequency domain}
-
-\label{appx-spectral-func}
-The impurity retarded Green's function (assuming the Hamiltonian to be time-independent, which it is) is defined as
-\begin{equation}\begin{aligned}
-	G_{dd}^\sigma(t) = -i\theta(t) \left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right>
-\end{aligned}\end{equation}
-where the average \(\left< \right>\) is over a canonical ensemble at temperature \(T\), and \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in.
-The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term.
-What follows is a standard calculation where we write the Green's function in the Lehmann-Kallen representation.
-The ensemble average for an arbitrary operator \(\hat M\) can be written in terms of the exact eigenstates of the fixed point Hamiltonian:
-\begin{equation}\begin{aligned}
-	H^* \ket{n} &= E_n^* \ket{n}, ~ ~ ~\left<\hat M \right> &\equiv \frac{1}{Z}\sum_n \bra{n} \hat M \ket{n} e^{-\beta E_n^*}
-\end{aligned}\end{equation}
-where \(Z = \sum_n e^{-\beta E_n^*}\) is the fixed point partition function and \(\left\{ \ket{n} \right\} \) is the set of eigenfunctions of the fixed point Hamiltonian. We can therefore write
-\begin{equation}\begin{aligned}
-	&\left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right> \\
-	&= \frac{1}{Z}\sum_{m}e^{-\beta E_m}\bra{m}\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\} \ket{m}\\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( \mathcal{O}_{\sigma}(t)\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma}(t)\right) \ket{m} && \left[\sum_n \ket{n}\bra{n} = 1\right]  \\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\right) \ket{m}\\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\left( e^{i\left( E_m - E_n \right)  t}\bra{m}\mathcal{O}_{\sigma}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} \ket{m} + e^{i\left( E_n - E_m \right)  t}\bra{m}\mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma} \ket{m}\right)\\
-	&= \frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
-\end{aligned}\end{equation}
-The time-domain impurity Green's function can thus be written as (this is the so-called Lehmann-Kallen representation)
-\begin{equation}\begin{aligned}
-	G_{dd}^\sigma = -i\theta(t)\frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
-\end{aligned}\end{equation}
-We are interested in the frequency domain form.
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega) &= \int_{-\infty}^\infty dt e^{i \omega t}G_{d d}^\sigma(t) \\
-			       &= \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t}
-\end{aligned}\end{equation}
-To evaluate the time-integral, we will use the integral representation of the Heaviside function:
-\begin{equation}\begin{aligned}
-	\theta(t) = \frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty \frac{1}{x- i\eta}e^{ixt}dx
-\end{aligned}\end{equation}
-With this definition, the integral in \(G_{dd}^\sigma(\omega)\) becomes
-\begin{equation}\begin{aligned}
-	\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t} &= \left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta}\int_{-\infty}^\infty dt e^{i\left( \omega + E_m - E_n + x\right)t} \\
-									     &=\left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta} 2\pi \delta\left( \omega + E_m - E_n + x\right) \\
-									     &=\left(-i\right)\frac{1}{i}\lim_{\eta \to 0^+} \frac{-1}{\omega + E_m - E_n- i\eta} \\
-									     &=\frac{1}{\omega + E_m - E_n} \\
-\end{aligned}\end{equation}
-The frequency-domain Green's function is thus
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
-\end{aligned}\end{equation}
-The zero temperature Green's function is obtained by taking the limit of \(\beta \to \infty\).
-In both the partition function as well as inside the summation, the only term that will survive is the exponential of the ground state energy \(E_0\).
-\begin{equation*}\begin{aligned}
-	Z \equiv \sum_m e^{-\beta E_m} \implies \lim_{\beta \to \infty}Z = d_0 e^{-\beta E_0}, && E_0 \equiv \text{min}\left\{ E_n \right\} 
-\end{aligned}\end{equation*}
-where \(d_0\) is the degeneracy of the ground state. The Greens function then simplifies to
-\begin{equation}\begin{aligned}
-	\label{Gf_lk}
-	G_{d d}^\sigma(\omega, \beta \to \infty) &= \frac{1}{d_0e^{-\beta E_0}}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left[e^{-\beta E_m}\delta_{E_m, E_0} + e^{-\beta E_n}\delta_{E_n, E_0}\right]\frac{1}{\omega + E_m - E_n}\\
-						 &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n}\right]\\
-\end{aligned}\end{equation}
-The label 0 sums over all states \(\ket{0}\) with energy \(E_0\).
-The spectral function is the imaginary part of this Green's function.
-To extract the imaginary part, we insert an infinitesimal imaginary part in the denominator:
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega, \eta) = \frac{1}{d_0}\lim_{\eta \to 0^-}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n + i\eta} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n + i\eta}\right]\\
-\end{aligned}\end{equation}
-The spectral function at zero temperature can then be written as
-\begin{equation}\begin{aligned}
-	\mathcal{A(\omega)} &= -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] \\
-			    &= \frac{1}{d_0}\frac{1}{\pi}\text{ Im }\left[\lim_{\eta \to 0^-}\sum_{n,0}\left(\frac{-i\eta ||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2}{\left(\omega + E_0 - E_n\right)^2 + \eta^2} + \frac{-i\eta ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2}{\left(\omega - E_0 + E_n\right)^2 + \eta^2}\right)\right]\\
-			    &= \frac{1}{d_0}\frac{1}{\pi}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\pi\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\pi\delta\left(\omega - E_0 + E_n\right)\right]\\
-			    &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]\\
-\end{aligned}\end{equation}
-
 \chapter{Topological interpretation of the Wilson ratio}

### 2022-03-31 notes/notes.tex
argued for the minimal model

@@
 \documentclass[12pt]{report}
+% \documentclass{nature}
 \usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk,pifont,enumitem}
@@
 \section{What is the minimal impurity model for a Mott metal-insulator transition?}
+\label{sec:min_model}
 The Hubbard model is one of the fundamental models for strong electronic correlation; in its simplest form, it features a single band of conduction electrons hopping on a lattice and interacting via local correlations that provide a cost \(U\) if any site is doubly occupied:
@@
 
+\section{What, then, are the minimal ingredients for a metal-insulator transition?}
+We now return to the question posed at the very beginning in section~\ref{sec:min_model}: What is the minimal auxiliary model that can demonstrate a metal-insulator transition in the bulk?
+To answer this question, we first recall all the relevant RG equations in the positive \(U\) regime:
+\begin{gather}
+	\Delta U_b = 0, ~ ~\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\frac{J^2}{d_2},\\
+	\Delta V = -\frac{3n_j V}{8}\left[\left(J + 4U_b/3\right) \left(\frac{1}{d_2} + \frac{1}{d_1}\right) + 4U_b/3\left(\frac{1}{d_3} + \frac{1}{d_0}\right)\right],\\
+	\Delta J = -\frac{n_j J\left(J + 4U_b\right)}{d_2}~.
+\end{gather}
+where \(d_1 > d_2 > d_3 > d_0\).
+We now consider various models with increasing number of parameters.
+
+\subsection{Only impurity correlation and hybridisation \(U,V\)}
+If we had only \(U\) and \(V\), the RG equations simplify to
+\begin{equation}\begin{aligned}
+	\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) < 0,~ ~ ~\Delta V = 0
+\end{aligned}\end{equation}
+\(U\) is irrelevant while the hybridisation \(V\) is marginal, so the fixed point is where the impurity is screened. The bulk model will always be metallic. There is no transition in such a model.
+
+\subsection{Impurity correlation, hybridisation and spin-exchange between impurity and bath \(U,V,J\)}
+If we now add a spin-exchange coupling \(J\) between the impurity and the bath into the Hamiltonian, we obtain the generalised SIAM studied in chapter~\ref{chap:urg1}.
+As discussed in that chapter, this is again similar to the previous case - the only stable fixed point is one of strong-coupling, and the bulk metal will never have an insulating phase.
+
+\subsection{Impurity correlation, hybridisation and local pairing interaction on the bath \(U,V,U_b\)}
+If we replace the \(J\) with an local interaction \(U_b\) on the bath, the RG equations undergo some changes:
+\begin{gather}
+	\Delta U_b = 0, ~ ~\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) = \frac{4V^2U}{\left(\omega - D/2 + U_b/2\right)^2 - U^2/4},\\
+	\Delta V = -n_j V U_b\left[\frac{\omega - D/2 + U_b/2}{\left(\omega - D/2 + U_b/2\right)^2 - U^2/4} + \frac{1}{\omega - D/2 + U_b/2}\right]~.
+\end{gather}
+This regime is interesting because it shows a variety of behaviour:
+\begin{itemize}
+	\item For \(U_b>0\), the correlation \(U\) is irrelevant and \(V\) is relevant. This will produce a metal (see fig.~\ref{noJ_Ub_gt_0}).
+	\item For \(U_b<0\), both \(U\) and \(V\) are irrelevant, but \(V\) decays much faster than \(U\), and \(U\) saturates to a non-zero appreciable value which although lower than the bare value is much greater than 0 (see fig.~\ref{noJ_Ub_lt_0}).
+This behaviour is enhanced by making \(U_b\) more negative; \(V\) decays even faster to zero, while \(U\) saturates at higher values.
+If the bare bandwidth is increased, the fixed point value of \(U\) actually decreases, so it appears that on taking the thermodynamic limit, \(U\) renormalises to zero (see fig.~\ref{noJ_Ub_lt_0_D}).
+\end{itemize}
+
+Neither of these cases give rise to an insulator, because \(U\) never renormalises to a non-zero fixed point value in the thermodynamic limit.
+
+\begin{center}
+	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=0.05_D=10_U.pdf}
+	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=0.05_D=10_V.pdf}
+	\captionof{figure}{RG flows of \(U\) (left panel) and \(V\) (right panel) in the regime \(U_b>0\), for the auxiliary model with \(U,V,U_b\).
+The impurity correlation \(U\) is irrelevant while the hybridisation \(V\) is relevant, leading to a metallic phase in the bulk.}
+	\label{noJ_Ub_gt_0}
+
+	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=-0.10_D=10_U.pdf}
+	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=-0.10_D=10_V.pdf}
+	\captionof{figure}{RG flows of \(U\) (left panel) and \(V\) (right panel) in the regime \(U_b<0\), for the auxiliary model with \(U,V,U_b\).
+The hybridisation \(V\) is sharply irrelevant, renormalising to zero, while the impurity correlation \(U\) survives at the fixed point.}
+	\label{noJ_Ub_lt_0}
+
+	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=-0.10_D=100_U.pdf}
+	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=-0.10_D=100_V.pdf}
+	\captionof{figure}{RG flows of \(U\) and \(V\) in the regime \(U_b<0\) at a larger bandwidth, for the auxiliary model with \(U,V,U_b\).
+\(U\) now renormalises to zero, so an insulator is not possible in the thermodynamic limit.}
+	\label{noJ_Ub_lt_0_D}
+\end{center}
+
+\subsection{The full model?}
+We are therefore ultimately led to a model with all four parameters.
+This was studied in chapter~\ref{siam-attr-chap}, and was shown to display both metallic and insulating phases.
+This makes it clear that {\it the minimal model must have all three kinds of correlation: magnetic \((U,J)\), delocalisation \((V)\) and pair formation \((U_b)\)}.
+
+\subsection{Possibly a more minimal model: \(U,J,U_b\)}
+In the presence of these three couplings, the RG equations become
+\begin{equation}\begin{aligned}
+	\Delta U = -n_j J^2/d_2,~ ~ ~ \Delta J = -n_j J(J+4U_b)/d_2
+\end{aligned}\end{equation}
+Since \(J > 0\), \(\Delta U\) is always positive, so \(U\) is always relevant.
+For \(4U_b > -J\), \(\Delta J\) is also positive, and \(J\) is relevant.
+We end up in a metallic phase.
+However, for \(4U_b < -J\), \(J\) becomes irrelevant, and the fixed point is that of a local moment decoupled from the bath, which describes an insulating state in the bulk.
+
 \chapter{From the auxiliary model to the bulk - single site approach}
@@
 \begin{equation}\begin{aligned}
-	\label{map_pam_bulk}
 	\left(\epsilon_k\right)_\text{GPAM} = N\epsilon_k, ~ ~ \mu_\text{GPAM} = N\mu, ~ ~ U_\text{GPAM} = 2U, ~ ~ V_\text{GPAM} = 2V, ~ ~ J_\text{GPAM} = 2J, ~ ~ \eta_\text{GPAM} = 2\eta, ~ ~ J^\prime_\text{GPAM} = \frac{2}{w}J^\prime

### 2022-04-01 notes/notes.tex
obtained self-energy variation

@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=0.00.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=3.00.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=5.00.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=10.00.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub=0_U_by_delta=25.00.pdf}
+	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=0.00.pdf}
+	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=3.00.pdf}
+	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=5.00.pdf}
+	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=10.00.pdf}
+	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=25.00.pdf}
 	\caption{Impurity spectral function for multiple values of \(U\). The increase in value of \(U\) is accompanied by the appearance of the side-peaks.}
@@
 This allows us to calculate the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
-\section{Analytic consistency checks}
-\subsection{Single-particle Greens function and self energy for the Hubbard dimer}
-The simplest test involves choosing $H^H = H^D$ and then calculating the momentum space Greens function at $k=0$, $G(k=0, \uparrow)$, for the Hubbard dimer \(\left(N = 2, w = 1 \right)\).
-The discrete set of momenta are \(\left\{ \vec k_n \right\} = 0, \frac{\pi}{a}\).
-For $k=0$, we have
-\begin{equation}\begin{aligned}
-	\xi_{\vec k = 0} = e^{ikr} = 1
-\end{aligned}\end{equation}
-Substituting this into eq.~\ref{k_Gf} gives
-\begin{equation}\begin{aligned}
-	\label{Gk_dim}
-	G(k=0,\uparrow) = \sum_n\left[\left(|C^0_{n}|^2 + {C^0_{n}}^* C^1_{n} \right)\frac{1}{g_n} - \left(|\overline C^0_{n}|^2 + {\overline C^0_{n}}^* \overline C^1_{n}\right)\frac{1}{\overline{g_n}}\right]
-\end{aligned}\end{equation}
-The expansion in terms of the exact eigenstates takes the form:
-\begin{equation}\begin{aligned}
-	c^\dagger_{0 \uparrow}\ket{\tilde \Phi_0} = x\ket{3+ \uparrow} + y\ket{3- \uparrow}, && c^\dagger_{1 \uparrow}\ket{\tilde \Phi_0} = x\ket{3+ \uparrow} - y\ket{3- \uparrow}\\
-	c_{0 \uparrow}\ket{\tilde \Phi_0} = y\ket{1+ \downarrow} + x\ket{1- \downarrow}, && c_{1 \uparrow}\ket{\tilde \Phi_0} = y\ket{1+ \downarrow} - x\ket{1- \downarrow}\\
-\end{aligned}\end{equation}
-where $\ket{(3,1)\pm (\uparrow, \downarrow)}$ are the $N=(3,1), S^z = (+\frac{1}{2}, -\frac{1}{2})$ eigenstates of even $(+)$ and odd \((-)\) parity:
-\begin{equation}\begin{aligned}
-	H^D\ket{3\pm \uparrow} = \pm t \ket{3\pm \uparrow}, ~ ~ ~H^D\ket{1\pm \downarrow} = \mp t \ket{1\pm \downarrow}\\
-\end{aligned}\end{equation}
-and \(x = \frac{a_2 - a_1}{2}, y = \frac{a_2 + a_1}{2}\). The orthogonal basis is therefore
-\begin{equation}\begin{aligned}
-	\left\{ \ket{n} \right\} = \ket{3+ \uparrow}, \ket{3- \uparrow}, ~ ~ ~\left\{ \ket{\overline n} \right\} = \ket{1+ \downarrow}, \ket{1- \downarrow}
-\end{aligned}\end{equation}
-The coefficients can thus be determined:
-\begin{gather*}
-	C^0_\pm = \braket{3\pm \uparrow|c^\dagger_{0 \uparrow} |\tilde \Phi_0} = x, y, ~ ~ ~ C^1_\pm = \braket{3\pm \uparrow|c^\dagger_{1 \uparrow} |\tilde \Phi_0} = x, -y\\
-	\overline C^0_\pm = \braket{1 \pm \downarrow|c_{0 \uparrow} |\tilde \Phi_0} = y, x, ~ ~ ~\overline C^1_\pm = \braket{1 \pm \downarrow|c_{1 \uparrow} |\tilde \Phi_0} = y, -x\\
-	g_\pm = \bra{3 \pm \uparrow}\left( \omega + E_{GS} - H^D\right) \ket{3 \pm \uparrow} = \omega + E_{GS} \mp t, ~ ~ ~\overline{g_\pm} = \bra{1 \pm \downarrow}\left(-\omega + E_{GS} - H^D\right) \ket{1 \pm \downarrow} = -\omega + E_{GS} \pm t\\
-\end{gather*}
-We can see that $|C^0_-|^2 + {C^0_-}^* C^1_- = y^2 - y^2 = 0$ and $|\overline C^0_-|^2 + {\overline C^0_-}^* \overline C^1_- = x^2 - x^2 = 0$.
-So we do not need to consider those terms.
-With this preparation, we can now calculate the Greens function:
-\begin{equation}\begin{aligned}
-	G(k=0, \omega) = \left(|C^0_{+}|^2 + {C^0_{+}}^* C^1_{+} \right)\frac{1}{g_+} - \left(|\overline C^0_{+}|^2 + {C^0_{+}}^* \overline C^1_{+}\right)\frac{1}{\overline{g_+}} = \frac{2x^2}{\omega + E_{GS} - t} - \frac{2y^2}{-\omega + E_{GS} + t}
-\end{aligned}\end{equation}
-The final step is to recognize that $2x^2 = \frac{a_1^2 + a_2^2 -2a_1a_2}{2} = \frac{1}{2} - \frac{2t}{\Delta}$, $2y^2 = \frac{a_1^2 + a_2^2 + 2a_1a_2}{2} = \frac{1}{2} + \frac{2t}{\Delta}$ and $E_{GS} = -\frac{\Delta}{2}$.
-Then,
-\begin{equation}\begin{aligned}
-	G(k=0, \omega) = \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} - \frac{\frac{1}{2} + \frac{2t}{\Delta}}{-\omega - \frac{\Delta}{2} + t} = \frac{\frac{1}{2} - \frac{2t}{\Delta}}{\omega - \frac{\Delta}{2} - t} + \frac{\frac{1}{2} + \frac{2t}{\Delta}}{\omega + \frac{\Delta}{2} - t}
-\end{aligned}\end{equation}
-
-\subsection{On the Bethe lattice}
+
+\section{Analytic consistency check - On the Bethe lattice}
 Another test involves considering the case of a Bethe lattice with infinite number of nearest neighbours $w\to\infty$ (the coordination number).

### 2022-04-08 notes/notes.tex
added Adz plot as well
corrected the non-int part of self-energy

@@
-\documentclass[12pt]{report}
+\documentclass{report}
 % \documentclass{nature}
@@
 
+\subsection{Attractive correlation \(U_b\) instead of \(V\): \(U,J,U_b\)}
+In the presence of these three couplings, the RG equations become
+\begin{equation}\begin{aligned}
+	\Delta U = -n_j J^2/d_2,~ ~ ~ \Delta J = -n_j J(J+4U_b)/d_2
+\end{aligned}\end{equation}
+Since \(J > 0\), \(\Delta U\) is always positive, so \(U\) is always relevant.
+For \(4U_b > -J\), \(\Delta J\) is also positive, and \(J\) is relevant.
+We end up in a metallic phase.
+However, for \(4U_b < -J\), \(J\) becomes irrelevant, and the fixed point is that of a local moment decoupled from the bath, which describes an insulating state in the bulk.
+
 \subsection{The full model?}
@@
 This makes it clear that {\it the minimal model must have all three kinds of correlation: magnetic \((U,J)\), delocalisation \((V)\) and pair formation \((U_b)\)}.
-
-\subsection{Possibly a more minimal model: \(U,J,U_b\)}
-In the presence of these three couplings, the RG equations become
-\begin{equation}\begin{aligned}
-	\Delta U = -n_j J^2/d_2,~ ~ ~ \Delta J = -n_j J(J+4U_b)/d_2
-\end{aligned}\end{equation}
-Since \(J > 0\), \(\Delta U\) is always positive, so \(U\) is always relevant.
-For \(4U_b > -J\), \(\Delta J\) is also positive, and \(J\) is relevant.
-We end up in a metallic phase.
-However, for \(4U_b < -J\), \(J\) becomes irrelevant, and the fixed point is that of a local moment decoupled from the bath, which describes an insulating state in the bulk.
 
@@
 	\left(G_{H-H}(\omega)\right)_\text{n-n} = \left(G_{H-H}(\omega)\right)_{i,i+1}^p - \left(G_{H-H}(-\omega)\right)_{i+1,i}^h = \frac{1}{w}\sum_n \left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn} \right.\\
- - \left.\left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]= G(\omega)_\text{aux,dz}
+ - \left.\left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]= \frac{1}{w}G(\omega)_\text{aux,dz}
 \end{aligned}\end{equation}
@@
 
-With the knowledge of the momentum-space Greens function $G_\text{H-H}(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
-\begin{equation}\begin{aligned}
-	\Sigma(\vec k,\omega) = \left(G^{(0)}(\vec k,\omega)\right)^{-1} - G(\vec k,\omega)^{-1}
-\end{aligned}\end{equation}
-where $\left(G^{(0)}(\vec k,\omega)\right)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system.
-Substituting this as well as the full Greens function $G_{H-H}(\vec k, \omega)$ into Dyson's equation gives
+From the local Greens function, we can write down the local self-energy using Dyson's equation: \(\Sigma = \left(G^{(0)}\right)^{-1} - G^{-1}\).
+\(G^{(0)}\) is the non-interacting Greens function.
+Here, non-interacting is defined as the absence of \(U,J\) in the bulk model, and hence the absence of \(U,U_b,J\) in the auxiliary model.
+In real space, the local and nearest-neighbour self-energies are therefore
+\begin{equation}\begin{aligned}
+	\left(\Sigma_\text{H-H}(\omega)\right)_\text{loc} = \left(\left(G_{H-H}(\omega)\right)_\text{loc}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_\text{loc}\right)^{-1} = \left(G(\omega)_\text{aux,dd}^{(0)}\right)^{-1} - \frac{1}{w}\left(G(\omega)_\text{aux,dd}\right)^{-1} \\
+	\left(\Sigma_\text{H-H}(\omega)\right)_\text{n-n} = \left(\left(G_{H-H}(\omega)\right)_\text{n-n}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_\text{n-n}\right)^{-1} = \left(G(\omega)_\text{aux,dz}^{(0)}\right)^{-1} - \frac{1}{w}\left(G(\omega)_\text{aux,dz}\right)^{-1}\\
+\end{aligned}\end{equation}
+
+The \(k-\)space self-energy can be similarly obtained from the \(k-\)space Greens functions
 \begin{equation}\begin{aligned}
 	\label{self-energy1}
-	\Sigma_{H-H}(\vec k,\omega) &= \left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left\{\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec{k}}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\right\}^{-1}\\
-&= \left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}
-\end{aligned}\end{equation}
-This allows us to calculate the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
-
-%\clearpage
+	\Sigma_{H-H}(\vec k,\omega) = \left(\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_{\vec k}\right)^{-1} = \frac{1}{G(\omega)_\text{aux,dd}^{(0)} + \frac{\xi_{\vec k}}{w}G(\omega)_\text{aux,dz}^{(0)}} -  \frac{1}{G(\omega)_\text{aux,dd} + \frac{\xi_{\vec k}}{w}G(\omega)_\text{aux,dz}}
+\end{aligned}\end{equation}
+Just to clarify the notation, we reiterate that bulk quantities with a superscript \((0)\) are for the non-interacting Hamiltonian and defined at \(U_\text{H-H}=J_\text{H-H}=0\), while the auxiliary model quantities with that superscript are evaluated in the non-interacting auxiliary model at \(U=J=U_b=0\).
+The non-interacting model is simply a resonant-level model with the impurity level at zero energy.
+Such a model is exactly solvable, and the corresponding Greens functions are given by
+\begin{equation}\begin{aligned}
+	G(\omega + i\eta)_\text{aux,dd}^{(0)} = \frac{1}{\omega + i\left(\Delta + \eta\right)}, ~ ~ ~ G(\omega + i\eta)_\text{aux,dz}^{(0)} = \sum_{\vec k} G(\omega)^{(0)}_{\vec k} V G(\omega + i\eta)_\text{aux,dd}^{(0)}
+\end{aligned}\end{equation}
+where \(\Delta = \pi \rho V^2\) is the hybridisation parameter, assuming a uniform density of states \(\rho\), and \(G(\omega)^{(0)}_{\vec k}\) is the free electron Greens function at momentum \(\vec k\).
+
 \section{Evidence for the Mott MIT}
@@
 \(q\) runs over the momentum states that are being decoupled at this RG step: \(|q| = \Lambda_j\).
-\(E_{1,0}\) are the diagonal parts of the Hamiltonian at \(\hat n_{d\overline \beta}=0,1\) respectively.
+\(E_{1,0}\) are the diagonal parts of the Hamiltonian at \(\hat n_{d\overline \beta}=1,0\) respectively.
 We have \(\hat n_{d\beta}=1\) in the intermediate state because of the \(c^\dagger_{d\beta}\) in front of the Greens function.
@@
 \begin{equation}\begin{aligned}
-	-\frac{1}{2}V J n_j \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)c^\dagger_{k\overline\beta} c_{d\overline\beta}
+	-\frac{1}{4}V J n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)c^\dagger_{k\overline\beta} c_{d\overline\beta}
 \end{aligned}\end{equation}

### 2022-04-14 notes/notes.tex
added modified figures that were obtained with the RG

@@
 \usepackage[T1]{fontenc}
-\usepackage[sfdefault]{roboto}
 
@@
 \begin{center}
-	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=0.100.pdf}\\
-	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=10.000.pdf}\\
-	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=50.000.pdf}
+	\includegraphics[width=0.7\textwidth]{../figures/overlaps_gs-J=0.100.pdf}\\
+	\includegraphics[width=0.7\textwidth]{../figures/overlaps_gs-J=10.000.pdf}\\
+	\includegraphics[width=0.7\textwidth]{../figures/overlaps_gs-J=50.000.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=0.100.pdf}\\
-	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=10.000.pdf}\\
-	\includegraphics[width=0.75\textwidth]{../figures/corrs_gs-J=50.000.pdf}
+	\includegraphics[width=0.7\textwidth]{../figures/corrs_gs-J=0.100.pdf}\\
+	\includegraphics[width=0.7\textwidth]{../figures/corrs_gs-J=10.000.pdf}\\
+	\includegraphics[width=0.7\textwidth]{../figures/corrs_gs-J=50.000.pdf}
 \end{center}
@@
 \(t^2/\delta E\) is the small parameter for the expansion, \(t\) being the tight-binding hopping.
-\(\mathcal{F}\) is the strength of the local Fermi liquid \((\mathcal{F} \hat n_{1 \uparrow} \hat n_{1 \downarrow})\).
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/gap-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/par-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-01-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-
+	\includegraphics[width=0.32\textwidth]{../figures/EE-d-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
 \end{center}
@@
 \begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-
-	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r1p-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-od-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/r-opp-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+
+	\includegraphics[width=0.3\textwidth]{../figures/r-par-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-ising-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.3\textwidth]{../figures/r-charge-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
 \end{center}
+
+\section{Presence of sub-dominant pair fluctuations}
+\begin{center}
+	\includegraphics[width=0.4\textwidth]{../figures/odlro-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\captionof{figure}{Growth of pair fluctuations \(p^\dagger_d p_0\) between the impurity and the zeroth site towards the critical point, \(p^\dagger=c^\dagger_\uparrow c^\dagger_\downarrow\) being the local pair creation operator.
+This comes at the cost of the spin-flip fluctuations \(S_d^+ s_0^- + \text{h.c.}\).
+which decrease towards the transition.}
+	\label{pair_fluc}
+\end{center}
+
+The behaviour of the various kinds of correlation functions (for eg., the reduction of the impurity compensation \(\vec{S}_d\cdot\vec{s}_0\)) shown above indicate that the Kondo cloud that screens the impurity is getting destroyed as \(U_b/J\) increases in magnitude.
+To shed some light on the nature of the fluctuations that faciliate this process, we also plot the average pair fluctuation in the ground state as a function of \(U_b/J\), in fig.~\ref{pair_fluc}.
+The pair fluctuations are terms that transfer an electron pair between the impurity and zeroth sites: \(c^\dagger_{d \uparrow}c^\dagger_{d \downarrow} c_{0 \downarrow}c_{0 \uparrow}\).
+It can be seen from the figure that while the spin-flip fluctuations decrease (since the Kondo cloud is formed out of these spin-flip fluctuations, this is consistent with the destruction of the Kondo cloud discussed in this paragraph), the pair fluctuations pick up.
+Since the spin subspace and charge subspace cannot coincide on the same site, we can then conclude that it is the growth of these pair fluctuations brought about by the presence of the purely local interaction \(U_b\) that make the screening of the impurity spin very poor.
 
@@
 
-\begin{figure}[!htb]
-	\centering
+\begin{center}
 \includegraphics[width=0.45\textwidth]{../figures/spec_func_width_fit.pdf}
-\end{figure}
+\end{center}
 
@@
 
+\section{Nature of the wavefunctions}
+In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full wavefunction \(\Psi\) is then obtained by constructing liner combinations of the eigenstates \(\psi_i\) of the local Hamiltonians such that \(\Psi\) satisfies Bloch's theorem: \(\Psi_{\vec k}(\vec r) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r - \vec R_i)\).
+To satisfy Bloch's theorem means to behave in acertain way under a translation operation by some lattice distance \(\vec R = \sum_i n_i \vec a_i\):
+\begin{equation}\begin{aligned}
+\Psi_{\vec k}(\vec r + \vec R) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r + \vec R - \vec R_i) = e^{i \vec{k}\cdot\vec{R}}\sum_i e^{i \vec{k}\cdot\left(\vec{R}_i - \vec R\right)} \psi_i(\vec r - (\vec R_i - \vec R)) = e^{\vec{k}\cdot\vec{R}}\Psi(\vec r)
+\end{aligned}\end{equation}
+At the end, we used the fact that \(\vec r_i - \vec R\) is just another lattice vector \(\vec R_j\). The bulk Hamiltonian obtained in eq.~\ref{siam_to_hubb},
+\begin{equation}\begin{aligned}
+	H_\text{H-H}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i} \mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i\right\}\right)~,
+\end{aligned}\end{equation}
+also enjoys a Bloch's theorem. This is because the tiling procedure restores the translation symmetry of the lattice:
+\begin{equation}\begin{aligned}
+	H_\text{H-H}(\left\{\vec r_k + \vec R\right\}) =  \sum_{\vec R_i}\mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i + \vec R\right\}\right) = \sum_{\vec R_i} \mathcal{H}_{\text{aux},\tilde i}\left(\left\{\vec r_k - \vec R\right\}\right) = H_\text{H-H}(\left\{\vec r_k\right\})
+\end{aligned}\end{equation}
+There we used the fact that \(\vec r_k + \vec R\) simply translates the auxiliary model defined by the coordinate \(i\) to a new auxiliary model at the modified coordinate \(\tilde i: \vec R_i^\prime = \vec R_i + \vec R\).
+Since this transformation from one auxiliary model to another simply shuffles the group of all auxiliary models, the sum over the group remains the sum, and we recover the same bulk model.
+
+To build eigenstates that satisfy Bloch's theorem, we approximate the eigenstates of the auxiliary models to highly localised forms \(\psi_{\text{aux}}\left( \vec r_d - \vec R_i, \vec r_{0} - \vec R_i \right) \) which involve only the impurity electron \(\vec r_d\) and the zeroth site \(\vec r_0\) of the auxiliary model.
+With this approximation, the wavefunction for each auxiliary model is neglible outside the lattice site \(\vec R_i\).
+The Bloch function can now be constructed~\cite{stoyanova}:
+\begin{equation}\begin{aligned}
+	\label{bloch-states}
+	\Psi_{\vec k}(\vec r) = \sum_{i} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec r_d - \vec R_i, \vec r_{0} - \vec R_i\right)
+\end{aligned}\end{equation}
+Applying the full Hamiltonian on this state gives
+\begin{equation}\begin{aligned}
+	H_\text{H-H} \Psi_{\vec k}(\vec r) = \sum_{\vec R_i}\sum_{j} \mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i\right\}\right) e^{i \vec{k}\cdot\vec{R}_j} \psi_\text{aux}\left(\vec r_d - \vec R_j, \vec r_{0} - \vec R_j\right)
+\end{aligned}\end{equation}
+From the local nature of the wavefunctions, we have \(\mathcal{H}_\text{aux,i}\psi_\text{aux,j} = \delta_{ij} E \psi_\text{aux,j}\), where \(E\) is the energy eigenvalue of the auxiliary model.
+Substituting this gives
+\begin{equation}\begin{aligned}
+	H_\text{H-H} \Psi_{\vec k}(\vec r) = E\left(\left\{\vec r_k - \vec R_i\right\}\right) e^{i \vec{k}\cdot\vec{R}_j} \psi_\text{aux}\left(\vec r_d - \vec R_j, \vec r_{0} - \vec R_j\right) = E \Psi_{\vec k}(\vec r)
+\end{aligned}\end{equation}
+The states constructed in eq.~\ref{bloch-states} are therefore eigenstates of the full Hamiltonian with the same eigenvalue \(E\) as the auxiliary model.
+
+That \(\Psi_{\vec k}\) transforms like Bloch functions can be easily verified:
+\begin{equation}\begin{aligned}
+	\Psi_{\vec k}(\vec r + \vec R) = \sum_{i} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec r_d + \vec R - \vec R_i, \vec r_0 + \vec R - \vec R_{i}\right) = e^{i \vec{k}\cdot\vec{R}}\sum_{j} e^{i \vec{k}\cdot\vec{R}_j} \psi_\text{aux}\left(\vec r_d - \vec R_j, \vec r_{0} + \vec R - \vec R_j\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}(\vec r)
+\end{aligned}\end{equation}
+In the last equation, we transformed \(\vec R_i \to \vec R_j = \vec R_i - \vec R\).
+
+Within the auxiliary model wavefunction \(\psi_\text{aux}\left(\vec r_d - \vec R_i, \vec r_0 - \vec R_i\right) \), the role of the impurity is to imitate the effect of correlations, while the role of the zeroth site is to introduce non-locality.
+Since it is the impurity site (and in general, the cluster) that is designed to be the closest to the bulk model in terms of local correlation, we will extract on-site measures of correlation only from the cluster sites, and involve the bath site only in the non-local measures.
+
 \section{Single-particle Green's function}
-We now define the Greens function {\it operators}:
-\begin{equation}\begin{aligned}
-	\mathcal{G}_{H-H} = \frac{1}{\omega^\prime - \left(H_{H-H} - E_\text{gs}^\prime\right) }, \mathcal{G}_\text{aux}(i) = \frac{1}{\omega - \left(\mathcal{H}_\text{aux}(i) - E_\text{gs}\right)}
-\end{aligned}\end{equation}
-Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian, while the primed quantities \(E_\text{gs}^\prime\) and \(\omega^\prime\) are the same quantities but for the full model \(\mathcal{H}_{H-H}\).
-From the relation eq.~\ref{siam_to_hubb} we know that while the auxiliary model is intensive, the full Hamiltonian is extensive (scales with system size).
-This means that we must have \(\omega^\prime = N\omega\) and \(E_\text{gs}^\prime = N E_\text{gs}\).
+We define \(\ket{\Phi_0(\vec k)}\) as the ground state of the bulk model, and it has a representation in terms of the auxiliary model eigenstates: \(\ket{\Phi_0} = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_{\text{aux}, i}\).
+To obtain Greens functions, we start by calculating real-space matrix elements of the bulk and auxiliary Hamiltonians.
+The states that we will consider are local excitations on top of the ground state: \(\ket{i} \equiv c^\dagger_{i\sigma}\ket{\Phi_0}\).
+\(i\) represents a lattice site.
+Sandwiching eq.~\ref{siam_to_hubb} between \(\ket{i}\) and \(\bra{i}\), we get
+\begin{equation}\begin{aligned}
+	\braket{i | H_\text{H-H} | i} = \sum_j \braket{i | \mathcal{H}_\text{aux,j} | i}
+\end{aligned}\end{equation}
+As discussed above, the local nature of the auxiliary models (onsite matrix element only on the impurity and non-local matrix element only between impurity and zeroth site) renders all diagonal matrix elements zero, except the one for \(i=j\):
+\begin{equation}\begin{aligned}
+	\braket{i | H_\text{H-H} | i} = \braket{i | \mathcal{H}_\text{aux,i} | i} = \braket{\psi_\text{aux} | c_{i\sigma} e^{-i \vec{k}\cdot\vec{R}_i} \mathcal{H}_\text{aux,i} e^{i \vec{k}\cdot\vec{R}_i} c^\dagger_{i\sigma} | \psi_\text{aux}} = \braket{\psi_\text{aux} | c_{i\sigma} \mathcal{H}_\text{aux,i} c^\dagger_{i\sigma} | \psi_\text{aux}} = \braket{\psi_\text{aux} | c_{d\sigma} \mathcal{H}_\text{aux} c^\dagger_{d\sigma} | \psi_\text{aux}}
+\end{aligned}\end{equation}
+At the last step, we recognised \(i\) as the impurity site and rewrote the expression entirely in terms of a site-independent auxiliary model.
+Similarly, the off-diagonal matrix element between two nearest-neighbour sites \(i,j\) is obtained as
+\begin{equation}\begin{aligned}
+	\braket{i | H_\text{H-H} | j} = \braket{i | \left(\mathcal{H}_\text{aux,i} + \mathcal{H}_\text{aux,j}\right) | j} = \frac{1}{w}\braket{\psi_\text{aux} | c_{i\sigma} e^{-i \vec{k}\cdot\vec{R}_i} \left(\mathcal{H}_\text{aux,i,j} + \mathcal{H}_\text{aux,j,i}\right) e^{i \vec{k}\cdot\vec{R}_j} c^\dagger_{j\sigma} | \psi_\text{aux}} \\
+	= \frac{1}{w}e^{i \vec{k}\cdot\left(\vec{R}_j - \vec{R}_i\right)}\braket{\psi_\text{aux} | \left(c_{d\sigma}\mathcal{H}_\text{aux} c^\dagger_{0\sigma} + c_{0\sigma}\mathcal{H}_\text{aux} c^\dagger_{d\sigma}\right) | \psi_\text{aux}}
+\end{aligned}\end{equation}
+\(\mathcal{H}_\text{aux,i,j}\) is the auxiliary model with \(i\) as the impurity site and \(j\) as the bath zeroth site.
+
+We now define the Greens {\it operators}:
+\begin{equation}\begin{aligned}
+	\mathcal{G}_{H-H} = \frac{1}{\omega - \left(H_{H-H} - E_\text{gs}\right) }, \mathcal{G}_\text{aux}(i) = \frac{1}{\omega - \left(\mathcal{H}_\text{aux}(i) - E_\text{gs}\right)}
+\end{aligned}\end{equation}
+Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian and also of the full model \(\mathcal{H}_{H-H}\).
 Rewriting eq.~\ref{siam_to_hubb} in terms of the operators \(\mathcal{G}\), we get
 \begin{equation}\begin{aligned}
-\sum_i \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i)\right) = N\omega + N E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_i \mathcal{G}^{-1}_\text{aux}(i) = \mathcal{G}^{-1}_{H-H}~,
+\sum_i \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i)\right) = \omega + E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_i \mathcal{G}^{-1}_\text{aux}(i) = \mathcal{G}^{-1}_{H-H}~,
 \end{aligned}\end{equation}
@@
 
-\chapter{Derivation of RG equations}
-\section{\(U_b\)-free terms}
-\subsection{Renormalisation of the impurity energy \(\epsilon_d\)}
-The coupling \(\epsilon_d\) is renormalised by three kinds of vertices: \(V^2\), \(J^2\) and \(K^2\).
+\chapter{Derivation of RG equations for the impurity model with \(U,V,J,K,U_b,\eta\)}
+
+\section{The Hamiltonian}
+
+The Hamiltonian for the impurity problem is
+\begin{equation}\begin{aligned}
+	\mathcal{H} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{1}{2} U \left( \tau_{d \uparrow} - \tau_{d \downarrow} \right) ^2 + \frac{1}{2}\eta \left(\tau_{d \uparrow} + \tau_{d \downarrow}\right) + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} + K \vec{C}_d\cdot\vec{C} - U_b\left(\tau_{0 \uparrow} - \tau_{0 \downarrow}\right)^2
+\end{aligned}\end{equation}
+wher \(\tau \equiv \hat n -\frac{1}{2}\).
+The first term is the kinetic energy term with a dispersion \(\epsilon_k\).
+The second term is the particle-hole symmetric impurity correlation term that sets the uncorrelated half-filled level \(\tau_{d\uparrow} = - \tau_{d \downarrow} = \pm \frac{1}{2}\) at energy \(-U/2\) below the Fermi surface, and the correlated doublon and holon states \(\tau_{d\downarrow} = \tau_{d \uparrow} = \pm \frac{1}{2}\) at the Fermi surface.
+The particle-hole symmetry is in the fact that the term is invariant under \(\tau_{d\sigma} \to-\tau_{d\sigma}\), and manifests in the symmetric positioning of the doublon and holon levels with respect to each other.
+The third term is the particle-hole asymmetry term that explicitly measures the deviation away from particle-hole symmetry - it is non-zero only when we are away from half-filling.
+The fourth, fifth and sixth terms describe various mechanisms in which the impurity can hybridise with the conduction bath.
+The first of these is a single-particle hopping \(V\), the second mechanism is through spin-flip scattering, and the third is through isospin-flip scattering.
+The single-particle hybridisation \(V\) allows the impurity electron to tunnel into the conduction bath and this leads to a frequency-dependent self-energy renormalisation of the impurity, implying that the impurity electron can spend  large amount of time in the bath~\cite{coleman2015}.
+\(\vec S_d = \frac{1}{2}\sum_{\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{d\alpha}c_{d\beta} \) is the impurity spin, while \(\vec C_d = \frac{1}{2}\sum_{\alpha\beta} \psi^\dagger_\alpha \vec \sigma_{\alpha\beta}\psi_\beta\) is the impurity isospin, where \(\psi = \left(c_{d\uparrow} ~ ~ ~ ~ c^\dagger_{d \downarrow}\right)\)~
+\cite{anderson1958random,nambu_1960}.
+The former acts on the \(2-\)dimensional Hilbert-space formed by the magnetic up and down states on the impurity, while the latter acts on the \(2-\)dimensional space formed by the doublon and holon states.
+The former reacts to a magnetic field, while the latter responds to a chemical potential.
+Such a chemical potential term that couples with the isospin is already present in the Hamiltonian - it is the assymetry term \(\eta\).
+In fact, that term can be rewritten as \(\eta C_d^z\), because \(C^z_d = \frac{1}{2}\left(\hat n_{d \uparrow} + \hat n_{d \downarrow} - 1\right) = \frac{1}{2}\left( \tau_{d \uparrow} + \tau_{d \downarrow} \right) \).
+The bath operators \(\vec s\) and \(\vec C\) are defined in the same way as the operator counterparts: \(\vec s = \sum_{kk^\prime\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{k\alpha}c_{k^\prime\beta}, \vec C = \sum_{kk^\prime\alpha\beta}{\psi^k}^\dagger_\alpha\vec\sigma_{\alpha\beta}\psi^{k^\prime}_\beta\), where \(\psi^k = \left(c_{k\alpha} ~ ~ ~ ~ c^\dagger_{k^\prime\beta}\right) \).
+The final seventh term is a local particle-hole symmetric correlation on the zeroth site of the bath.
+For \(U_b>0\), this term promotes half-filling on the zeroth site, while for \(U_b<0\), a doublon or holon is more favourable on that site.
+
+We first Fourier transform the \(U_b\)-term to \(k-\)space.
+In \(k-\)space, the diagonal contribution (to \(H_D\)) coming from this term is the single-particle self-energy \(-U_b\left(\hat n_{q \beta}\right)^2\) which can be made particle-hole symmetric in the form:
+\begin{equation}\begin{aligned}
+	-U_b\left(\tau_{q \beta}\right)^2
+\end{aligned}\end{equation}
+where \(q\) is the \(k-\)state being decoupled and \(\tau \equiv \hat n - 1/2\).
+In the initial state \(\ket{\Psi}_i\), we have \(\langle \hat n_{q\beta} \rangle = 1/2 \implies \tau_{q\beta} = 0\), so the contribution of \(U_b\) to that state is 0.
+For both hole excitations \(c_{q\beta}\ket{\Psi}_i\) as well as particle excitations \(c^\dagger_{q\beta}\ket{\Psi}_i\), the intermediate state energy lowers to \(-U_b/4\).
+
+The off-diagonal part is
+\begin{equation}\begin{aligned}
+	-\frac{U_b}{2}\sum_{kk^\prime\sigma}c^\dagger_{k\sigma}c_{k^\prime\sigma} + U_b \sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_1 \uparrow}c_{k_2 \uparrow} c^\dagger_{k^\prime_1 \downarrow}c_{k^\prime_2 \downarrow}
+\end{aligned}\end{equation}
+We ignore the potential scattering arising from the first term.
+
+\section{Renormalisation of the impurity energy levels}
+A single site has four degrees of freedom arising from the spin-degeneracy, and can be represented by the Hamiltonian
+\begin{equation}\begin{aligned}
+	H = \epsilon_0 \ket{0}\bra{0} + \epsilon_1 \sum_\sigma\ket{\sigma}\bra{\sigma} + \epsilon_2 \ket{2}\bra{2}
+\end{aligned}\end{equation}
+\(\ket{0},\ket{2}\) are the holon and doublon states, while \(\ket{\sigma}\) is the state where the site is singly-occupied by a particle of spin \(\sigma\).
+We will obtain the renormalisation to the energy levels \(\epsilon_0,\epsilon_1\) and \(\epsilon_2\), and thereby calculate the renormalisation in \(U\) and \(\eta\).
+This can be done by noting that \(\epsilon_1 = -\frac{U}{2}\), and \(\epsilon_2 = \eta\).
+A qualifier is, however, needed here.
+In the bare Hamiltonian, the energies of the doublon and holon states are negatives of each other, and this would correspond to requiring \(\epsilon_2 = -\epsilon_0\).
+This may not hold true under renormalisation, and the way we account for this is that at each step of the RG, we subtract a constant energy from the Hamiltonian so as to set the energy of the holon state to 0.
+This means that the energy of the singly-occupied and doublon states become \(\epsilon_1 - \epsilon_0\) and \(\epsilon_2 - \epsilon_0\).
+And since we have identified \(\epsilon_1\) and \(\epsilon_2\) as \(-\frac{U}{2}\) and \(\eta\) respectively, we can use \(\Delta U = -2\left(\Delta \epsilon_1 - \Delta \epsilon_0\right), \Delta \eta = \Delta \epsilon_2 - \Delta \epsilon_0 \).
+
+We need to look at three kinds of scattering vertices here: \(V^2\), \(J^2\) and \(K^2\).
 We will consider these processes one after another.
@@
 \chapter{Simple results for the Greens functions}
-\section{Relation between single-particle Greens function and the Greens function operator $(T=0)$}
+\section{Relation between single-particle Greens function and the Greens operator $(T=0)$}
  The single-particle Greens function is defined as the solution of the equation:
@@
  \end{aligned}\end{equation}
- If we now define a Greens function operator
+ If we now define a Greens operator
  \begin{equation}\begin{aligned}

### 2022-04-17 notes/notes.tex
proved that a general superposition is always an eigenstate

@@
 
-To build eigenstates that satisfy Bloch's theorem, we approximate the eigenstates of the auxiliary models to highly localised forms \(\psi_{\text{aux}}\left( \vec r_d - \vec R_i, \vec r_{0} - \vec R_i \right) \) which involve only the impurity electron \(\vec r_d\) and the zeroth site \(\vec r_0\) of the auxiliary model.
-With this approximation, the wavefunction for each auxiliary model is neglible outside the lattice site \(\vec R_i\).
-The Bloch function can now be constructed~\cite{stoyanova}:
+We can use the auxiliary model eigenstates \(\psi_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\} \right) \equiv \psi_\text{aux,i}\) to construct eigenstates of the bulk Hamiltonian.
+The following combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
 \begin{equation}\begin{aligned}
 	\label{bloch-states}
-	\Psi_{\vec k}(\vec r) = \sum_{i} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec r_d - \vec R_i, \vec r_{0} - \vec R_i\right)
-\end{aligned}\end{equation}
-Applying the full Hamiltonian on this state gives
-\begin{equation}\begin{aligned}
-	H_\text{H-H} \Psi_{\vec k}(\vec r) = \sum_{\vec R_i}\sum_{j} \mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i\right\}\right) e^{i \vec{k}\cdot\vec{R}_j} \psi_\text{aux}\left(\vec r_d - \vec R_j, \vec r_{0} - \vec R_j\right)
-\end{aligned}\end{equation}
-From the local nature of the wavefunctions, we have \(\mathcal{H}_\text{aux,i}\psi_\text{aux,j} = \delta_{ij} E \psi_\text{aux,j}\), where \(E\) is the energy eigenvalue of the auxiliary model.
-Substituting this gives
-\begin{equation}\begin{aligned}
-	H_\text{H-H} \Psi_{\vec k}(\vec r) = E\left(\left\{\vec r_k - \vec R_i\right\}\right) e^{i \vec{k}\cdot\vec{R}_j} \psi_\text{aux}\left(\vec r_d - \vec R_j, \vec r_{0} - \vec R_j\right) = E \Psi_{\vec k}(\vec r)
-\end{aligned}\end{equation}
-The states constructed in eq.~\ref{bloch-states} are therefore eigenstates of the full Hamiltonian with the same eigenvalue \(E\) as the auxiliary model.
+	\Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right) = \sum_{i} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux,i}
+\end{aligned}\end{equation}
+To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
+\begin{equation}\begin{aligned}
+	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \sum_{ij}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux,i}} H_\text{H-H}\ket{\psi_\text{aux,j}} = \sum_{i}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i}\sum_j e^{i\vec k^\prime\cdot\left(\vec R_i - \vec{R}_j\right)} \bra{\psi_\text{aux,i}} H_\text{H-H}\ket{\psi_\text{aux,j}}
+\end{aligned}\end{equation}
+We define \(\vec L = \vec R_i - \vec R_j\), and sum over \(\vec L\): 
+\begin{equation}\begin{aligned}
+\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \sum_{\vec R_i}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i}\sum_{\vec L} e^{i\vec k^\prime\cdot\vec L} \bra{\psi_{\text{aux},\vec R_i}} H_\text{H-H}\ket{\psi_{\text{aux},\vec R_i - \vec L}}
+\end{aligned}\end{equation}
+The sum over \(\vec L\) can be split into two summations, one over the distance \(L\) and another over the directions \(\vec a(L)\).
+Also note that because of translation symmetry, the matrix element will depend only on the distance \(L\) and not the direction: \(M(L) \equiv \bra{\psi_{\text{aux},\vec R_i}} H_\text{H-H}\ket{\psi_{\text{aux},\vec R_i - \vec L}}\).
+\begin{equation}\begin{aligned}
+	\bra{\Psi_{\vec k^\prime}(\vec r)}H_\text{H-H} \ket{\Psi_{\vec k}(\vec r)} = \sum_{\vec R_i}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i}\sum_{L} M(L) \sum_{\vec a(L)}e^{i\vec k^\prime\cdot\vec a(L)} = \delta_{\vec k, \vec k^\prime}\sum_{L} M(L) \xi_{\vec k}\left(L\right)
+\end{aligned}\end{equation}
+Here, \(\vec a(L)\) sums over all the primitive vectors connecting any single site with all its neighbours at a distance \(L\), and \(\xi_{\vec k} = \sum_{\vec a(L)}e^{i\vec k^\prime\cdot\vec a(L)}\).
+The Kronecker delta in front ensures that the Hamiltonian \(H_\text{H-H}\) is diagonal in the basis of the constructed eigenstates.
+The eigenvalue corresponding to \(\ket{\Psi_{\vec k}}\) is \(\sum_{L} M(L) \xi_{\vec k}\left(L\right)\).
 
@@
 \begin{equation}\begin{aligned}
-	\Psi_{\vec k}(\vec r + \vec R) = \sum_{i} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec r_d + \vec R - \vec R_i, \vec r_0 + \vec R - \vec R_{i}\right) = e^{i \vec{k}\cdot\vec{R}}\sum_{j} e^{i \vec{k}\cdot\vec{R}_j} \psi_\text{aux}\left(\vec r_d - \vec R_j, \vec r_{0} + \vec R - \vec R_j\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}(\vec r)
-\end{aligned}\end{equation}
-In the last equation, we transformed \(\vec R_i \to \vec R_j = \vec R_i - \vec R\).
-
-Within the auxiliary model wavefunction \(\psi_\text{aux}\left(\vec r_d - \vec R_i, \vec r_0 - \vec R_i\right) \), the role of the impurity is to imitate the effect of correlations, while the role of the zeroth site is to introduce non-locality.
-Since it is the impurity site (and in general, the cluster) that is designed to be the closest to the bulk model in terms of local correlation, we will extract on-site measures of correlation only from the cluster sites, and involve the bath site only in the non-local measures.
+	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \sum_{\vec R_i} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\left\{\vec r_k - \vec R_i + \vec R\right\}\right) = \sum_{\vec R_j} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\left\{\vec r_k - \vec R_j\right\}\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\vec r\right)
+\end{aligned}\end{equation}
+In the last equation, we transformed \(\vec R_i \to \vec R_j = \vec R_i - \vec R\). The wavefunction can be even brought into the familiar Bloch function form:
+\begin{equation}\begin{aligned}
+	\Psi_{\vec k}\left(\left\{\vec r_k\right\}\right) = e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right) = e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
+\end{aligned}\end{equation}
+where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
+This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
 

### 2022-04-19 notes/notes.tex
rewrote matrix element in terms of auxiliary model

@@
 In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full wavefunction \(\Psi\) is then obtained by constructing liner combinations of the eigenstates \(\psi_i\) of the local Hamiltonians such that \(\Psi\) satisfies Bloch's theorem: \(\Psi_{\vec k}(\vec r) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r - \vec R_i)\).
-To satisfy Bloch's theorem means to behave in acertain way under a translation operation by some lattice distance \(\vec R = \sum_i n_i \vec a_i\):
-\begin{equation}\begin{aligned}
-\Psi_{\vec k}(\vec r + \vec R) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r + \vec R - \vec R_i) = e^{i \vec{k}\cdot\vec{R}}\sum_i e^{i \vec{k}\cdot\left(\vec{R}_i - \vec R\right)} \psi_i(\vec r - (\vec R_i - \vec R)) = e^{\vec{k}\cdot\vec{R}}\Psi(\vec r)
-\end{aligned}\end{equation}
-At the end, we used the fact that \(\vec r_i - \vec R\) is just another lattice vector \(\vec R_j\). The bulk Hamiltonian obtained in eq.~\ref{siam_to_hubb},
-\begin{equation}\begin{aligned}
-	H_\text{H-H}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i} \mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i\right\}\right)~,
+To satisfy Bloch's theorem means to behave in acertain way under a translation operation \(T(\vec R)\) by some lattice distance \(\vec R = \sum_i n_i \vec a_i\):
+\begin{equation}\begin{aligned}
+T(\vec R)\Psi_{\vec k}\left(\vec r\right) = \Psi_{\vec k}(\vec r + \vec R) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r + \vec R - \vec R_i) = e^{i \vec{k}\cdot\vec{R}}\sum_i e^{i \vec{k}\cdot\left(\vec{R}_i - \vec R\right)} \psi_i(\vec r - (\vec R_i - \vec R)) = e^{\vec{k}\cdot\vec{R}}\Psi(\vec r)
+\end{aligned}\end{equation}
+At the end, we used the fact that \(\vec r_i - \vec R\) is just another lattice vector \(\vec R_j\).
+Note that the translation operator has been defined as an operation that simply advances the argument of the wavefunction from \(\vec r\) to \(\vec r + \vec R\).
+An equivalent definition can be given in terms of their action on position eigenkets: \(T(\vec R)\ket{\vec r} = \ket{\vec r - \vec R}\).
+These translation operators share eigenstates with the momentum operator:
+\begin{equation}\begin{aligned}
+	T\left( \vec R \right) \ket{\vec k} = \sum_{\vec r_i} e^{i \vec{k}\cdot\vec{r}_i}T\left( \vec R \right)\ket{\vec r_i} = e^{i \vec{k}\cdot\vec{R}}\sum_{\vec r_i} e^{i \vec{k}\cdot\left(\vec{r}_i - \vec R\right)}\ket{\vec r_i - \vec R} = e^{i \vec{k}\cdot\vec{R}} \ket{\vec k}
+\end{aligned}\end{equation}
+
+The bulk Hamiltonian obtained in eq.~\ref{siam_to_hubb},
+\begin{equation}\begin{aligned}
+	H_\text{H-H}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i} \mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i\right\}\right) \equiv \sum_{\vec R_i} \mathcal{H}_\text{aux}\left(\vec R_i\right)~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	H_\text{H-H}(\left\{\vec r_k + \vec R\right\}) =  \sum_{\vec R_i}\mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i + \vec R\right\}\right) = \sum_{\vec R_i} \mathcal{H}_{\text{aux},\tilde i}\left(\left\{\vec r_k - \vec R\right\}\right) = H_\text{H-H}(\left\{\vec r_k\right\})
+	H_\text{H-H}\left(\left\{\vec r_k + \vec R\right\}\right) =  \sum_{\vec R_i}\mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i + \vec R\right\}\right) = \sum_{\vec R_i} \mathcal{H}_{\text{aux},\tilde i}\left(\left\{\vec r_k - \vec R\right\}\right) = H_\text{H-H}(\left\{\vec r_k\right\})
 \end{aligned}\end{equation}
@@
 
-We can use the auxiliary model eigenstates \(\psi_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\} \right) \equiv \psi_\text{aux,i}\) to construct eigenstates of the bulk Hamiltonian.
+We can use the auxiliary model eigenstates \(\psi_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\} \right) \equiv \psi_\text{aux}\left(\vec R_i\right)\) to construct eigenstates of the bulk Hamiltonian.
 The following combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
@@
 	\label{bloch-states}
-	\Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right) = \sum_{i} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux,i}
+	\Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right) = \sum_{i} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \sum_{ij}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux,i}} H_\text{H-H}\ket{\psi_\text{aux,j}} = \sum_{i}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i}\sum_j e^{i\vec k^\prime\cdot\left(\vec R_i - \vec{R}_j\right)} \bra{\psi_\text{aux,i}} H_\text{H-H}\ket{\psi_\text{aux,j}}
+	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \sum_{ij}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi_\text{aux,j}} = \sum_{i}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i}\sum_j e^{i\vec k^\prime\cdot\left(\vec R_i - \vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi_\text{aux,j}}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \sum_{\vec R_i}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i}\sum_{\vec L} e^{i\vec k^\prime\cdot\vec L} \bra{\psi_{\text{aux},\vec R_i}} H_\text{H-H}\ket{\psi_{\text{aux},\vec R_i - \vec L}}
+\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \sum_{\vec R_i}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i}\sum_{\vec L} e^{i\vec k^\prime\cdot\vec L} \bra{\psi_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi_\text{aux}\left(\vec R_i- \vec L\right)}
 \end{aligned}\end{equation}
 The sum over \(\vec L\) can be split into two summations, one over the distance \(L\) and another over the directions \(\vec a(L)\).
-Also note that because of translation symmetry, the matrix element will depend only on the distance \(L\) and not the direction: \(M(L) \equiv \bra{\psi_{\text{aux},\vec R_i}} H_\text{H-H}\ket{\psi_{\text{aux},\vec R_i - \vec L}}\).
+Also note that because of translation symmetry, the matrix element will depend only on the distance \(L\) and not the direction: \(M(L) \equiv \bra{\psi_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi_\text{aux}\left(\vec R_i- \vec L\right)}\).
 \begin{equation}\begin{aligned}
@@
 \begin{equation}\begin{aligned}
-	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \sum_{\vec R_i} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\left\{\vec r_k - \vec R_i + \vec R\right\}\right) = \sum_{\vec R_j} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\left\{\vec r_k - \vec R_j\right\}\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\vec r\right)
+	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \sum_{\vec R_i} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R\right) = \sum_{\vec R_j} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\vec r\right)
 \end{aligned}\end{equation}
@@
 \section{Single-particle Green's function}
-We define \(\ket{\Phi_0(\vec k)}\) as the ground state of the bulk model, and it has a representation in terms of the auxiliary model eigenstates: \(\ket{\Phi_0} = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_{\text{aux}, i}\).
+We define \(\ket{\Phi_0(\vec k)}\) as the ground state of the bulk model, and it has an expression in terms of the auxiliary model eigenstates: \(\ket{\Phi_0(\vec k)} = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left( \vec R_i \right) \).
 To obtain Greens functions, we start by calculating real-space matrix elements of the bulk and auxiliary Hamiltonians.
-The states that we will consider are local excitations on top of the ground state: \(\ket{i} \equiv c^\dagger_{i\sigma}\ket{\Phi_0}\).
+The states that we will consider are local excitations on top of the ground state: \(\ket{i} \equiv c^\dagger_{i\sigma}\ket{\Phi_0\left( \vec k \right) }\).
 \(i\) represents a lattice site.
@@
 \begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = \sum_j \braket{i | \mathcal{H}_\text{aux,j} | i}
-\end{aligned}\end{equation}
+	\label{diag_mat_ele_1}
+	\braket{i | H_\text{H-H} | i} = \sum_{\vec R_j} \braket{\Phi_0\left( \vec k \right) | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma} | \Phi_0\left( \vec k \right) } = \sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi_\text{aux}\left( \vec R_n \right) | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma}  | \psi_\text{aux}\left( \vec R_m \right)}
+\end{aligned}\end{equation}
+There are, in general, three auxiliary models in the final expression on the right hand side - one at \(\vec R_n\), one at \(\vec R_m\) and another at \(\vec R_j\).
+In order to rewrite everything in terms of a single auxiliary model at the origin \(\vec R_0\) of the lattice, we will use the translation operators:
+\begin{equation}\begin{aligned}
+	\ket{\psi_\text{aux}\left( \vec R_m \right)} = \ket{\psi_\text{aux}\left( \left\{\vec r_k - \vec R_m\right\} \right)} = \ket{\psi_\text{aux}\left( \left\{\vec r_k - \vec R_0 + \left(\vec R_0 - \vec R_m\right)\right\} \right)} = T\left( \vec R_0 - \vec R_m \right) \ket{\psi_\text{aux}\left( \left\{\vec r_k - \vec R_0\right\} \right)} \\
+	= T\left(\vec R_0 - \vec R_m\right) \ket{\psi_\text{aux}\left(\vec R_0\right)}
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	\ket{\psi_\text{aux}\left( \vec R_n \right)} = T\left(\vec R_0 - \vec R_n\right) \ket{\psi_\text{aux}\left(\vec R_0\right)}
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux}\left( \vec R_j \right) = T\left(\vec R_0 - \vec R_j\right) \mathcal{H}_\text{aux}\left( \vec R_0 \right) T^\dagger\left(\vec R_0 - \vec R_j\right)
+\end{aligned}\end{equation}
+Substituting these forms into the expression in eq.~\ref{diag_mat_ele_1} gives
+\begin{equation}\begin{aligned}
+	&\braket{i | H_\text{H-H} | i} \\
+	&= \sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi_\text{aux}\left( \vec R_0 \right) | T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma}  T\left( \vec R_0 - \vec R_m \right)| \psi_\text{aux}\left( \vec R_0 \right)}
+\end{aligned}\end{equation}
+We will now absorb some of the translation operators into the creation and annihilation operators \(c_{i\sigma}\) that describe the excitation:
+\begin{equation}\begin{aligned}
+	T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right) &= T^\dagger\left( \vec R_0 - \vec R_n \right) c_{\sigma}\left( \vec R_i \right)  T^\dagger\left(\vec R_j - \vec R_0\right) \\
+												    &= T^\dagger\left( \vec R_0 - \vec R_n \right) T^\dagger \left(\vec R_j - \vec R_0\right) T\left(\vec R_j - \vec R_0\right) c_{\sigma}\left( \vec R_i \right)  T^\dagger\left(\vec R_j - \vec R_0\right)\\
+												    &=T^\dagger\left(\vec R_j - \vec R_n\right) c_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)
+\end{aligned}\end{equation}
+There, we used \(T^\dagger(\vec R_1) T^\dagger (\vec R_2) = T^\dagger(\vec R_1 + \vec R_2)\). For the creation operator, we similarly get
+\begin{equation}\begin{aligned}
+	T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma} T\left( \vec R_0 - \vec R_m \right) = \left[T^\dagger\left( \vec R_0 - \vec R_m \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\right]^\dagger = c^\dagger_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right) T\left(\vec R_j - \vec R_m\right)
+\end{aligned}\end{equation}
+Substituting these forms gives
+\begin{equation}\begin{aligned}
+	&\braket{i | H_\text{H-H} | i} \\
+	&= \sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi_\text{aux}\left( \vec R_0 \right) | T^\dagger\left(\vec R_j - \vec R_n\right) c_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right) T\left(\vec R_j - \vec R_m\right)| \psi_\text{aux}\left( \vec R_0 \right)}
+\end{aligned}\end{equation}
+To resolve the remaining translation operators, we will now insert momentum eigenkets \(1 = \sum_{\vec k}\ket{\vec k}\bra{\vec k}\) in between the operators.
+These eigenkets can be any state with a definite momentum, the simplest case being the eigenstates of a tight-binding Hamiltonian obtained by setting \(U=J=0\) in the bulk model.
+\begin{equation}\begin{aligned}
+	&\braket{i | H_\text{H-H} | i} \\
+	=& \sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \bra{\psi_\text{aux}\left( \vec R_0 \right)} \sum_{\vec k_2}\ket{\vec k_2}\bra{\vec k_2}T^\dagger\left(\vec R_j - \vec R_n\right) c_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\\
+	 &\sum_{\vec k_1}T\left(\vec R_j - \vec R_m\right)\ket{\vec k_1}\bra{\vec k_1} \ket{\psi_\text{aux}\left( \vec R_0 \right)}
+\end{aligned}\end{equation}
+From the definition of the translation operators shown above, we get \(T\left(\vec R_j - \vec R_m\right)\ket{\vec k_1} = e^{i \vec{k}_1\cdot\left(\vec{R}_j - \vec R_m\right)}\ket{\vec k_1}\) and \(\bra{\vec k_2}T^\dagger\left(\vec R_j - \vec R_n\right) = \bra{\vec k_2}e^{-i \vec{k}_2\cdot\left(\vec{R}_j - \vec R_n\right)}\).
+Substituting this gives
+\begin{equation}\begin{aligned}
+	&\braket{i | H_\text{H-H} | i} \\
+	=& \sum_{\vec R_j, \vec R_m, \vec R_n}\sum_{\vec k_1,\vec k_2} e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right)} e^{i\vec{R}_n\cdot\left(\vec{k}_2 - \vec k\right)} e^{i\vec{R}_m\cdot\left(\vec{k} - \vec k_1\right)} \bra{\psi_\text{aux}\left( \vec R_0 \right)} \ket{\vec k_2}\bra{\vec k_2} c_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\\
+	 &\ket{\vec k_1}\bra{\vec k_1} \ket{\psi_\text{aux}\left( \vec R_0 \right)}\\
+	=& \sum_{\vec R_j}\sum_{\vec k_1,\vec k_2} e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right)} \delta_{\vec{k},\vec k_2} \delta_{\vec{k},\vec k_1} \bra{\psi_\text{aux}\left( \vec R_0 \right)} \ket{\vec k_2}\bra{\vec k_2} c_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\ket{\vec k_1}\bra{\vec k_1} \ket{\psi_\text{aux}\left( \vec R_0 \right)}\\
+	=& \sum_{\vec R_j} \braket{\psi_\text{aux}\left( \vec R_0 \right) | \vec k}\bra{\vec k} c_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\ket{\vec k}\braket{\vec k | \psi_\text{aux}\left( \vec R_0 \right)}\\
+\end{aligned}\end{equation}
+Since \(\vec R_i + \vec R_0 - \vec R_j\) is a lattice translation vector, summing over \(\vec R_j\) means that \(\vec R_i + \vec R_0 - \vec R_j\) sums over all lattice sites \(\vec R_k\).
+This is equivalent to stating the translation symmetry of the lattice.
+Redefining \(\vec R_j\) to be equal to \(\vec R_k\), we get
+\begin{equation}\begin{aligned}
+	\braket{i | H_\text{H-H} | i} = |\braket{\psi_\text{aux}\left( \vec R_0 \right) | \vec k}|^2 \bra{\vec k} \sum_{\vec R_j} c_{\sigma}\left(\vec R_j\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left(\vec R_j\right)\ket{\vec k}
+\end{aligned}\end{equation}
+Even though it is computationally easier to consider the state \(\ket{\vec k}\) as the momentum eigenstates of the tight-binding kind, there is a more illuminating interpretation of this expression if we consider them as the eigenstates \(\ket{\Phi\left( \vec k \right) }\) of the full bulk model.
+With this choice, the expression can be seen as the sum of effects of creating a single-particle excitation \(c^\dagger_\sigma\) on the ground state \(\ket{\Phi_0\left( \vec k \right) }\), at increasingly larger distances \(\vec R_j\) from the auxiliary model at \(\vec R_0\).
+The excitation is made to evolve through the auxiliary model \(\mathcal{H}_\text{aux}\left( \vec R_0 \right) \) centred at \(\vec R_0\).
+The excitation is ultimately annihilated and the state returns to the ground state.
+However, since we are describing the excitation of the bulk ground state using an auxiliary model Hamiltonian, we also need to multply this with the fidelity between the full ground state and the auxiliary model ground state.
+That is taken care of by the inner-product multiplying the matrix element.
+That inner product can be thought of as an overlap between a separable state and an entangled state - the full Hamiltonian state is obtained by entangling the overlapping auxiliary models, while the single auxiliary model groundstate is the separable state in this context.
+The inner product then becomes a measure of entanglement of the bulk ground state - the more the overlap with the separable state, the lower the entanglement: \(\varepsilon(\vec R_0,\vec k) \equiv 1 - |\braket{\psi_\text{aux}\left(  \right) | \Phi_0(\vec k)}|^2\).
+\begin{equation}\begin{aligned}
+	\braket{i | H_\text{H-H} | i} = \left( 1 - \varepsilon(\vec R_0,\vec k) \right) \bra{\Phi_0(\vec k)} \sum_{\vec R_j} c_{\sigma}\left(\vec R_j\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left(\vec R_j\right)\ket{\Phi_0(\vec k)}
+\end{aligned}\end{equation}
+The more is the entanglement content within the groundstate, the lower is the contribution from a single auxiliary model \(\mathcal{H}_\text{aux}\left( \vec R_0 \right)\).
+This makes sense between the contributions will then be distributed across all the auxiliary models.
+On the other hand, when the entanglement is low, any single auxiliary model provides a large contribution, which can be understood from the fact that any single auxiliary model is sufficient to describe the full ground state.
+
+\clearpage
 As discussed above, the local nature of the auxiliary models (onsite matrix element only on the impurity and non-local matrix element only between impurity and zeroth site) renders all diagonal matrix elements zero, except the one for \(i=j\):

### 2022-04-19 notes/notes.tex
completed obtaining matrix element with corrected normalisation factor

@@
 
-We can use the auxiliary model eigenstates \(\psi_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\} \right) \equiv \psi_\text{aux}\left(\vec R_i\right)\) to construct eigenstates of the bulk Hamiltonian.
+We can use the auxiliary model eigenstates \(\psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\} \right) \equiv \psi^n_\text{aux}\left(\vec R_i\right)\) to construct eigenstates of the bulk Hamiltonian.
+\(n=0\) is the ground state of the auxiliary model, and higher values denote the excited states.
 The following combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
@@
 	\label{bloch-states}
-	\Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right) = \sum_{i} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i\right)
-\end{aligned}\end{equation}
-To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
-\begin{equation}\begin{aligned}
-	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \sum_{ij}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi_\text{aux,j}} = \sum_{i}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i}\sum_j e^{i\vec k^\prime\cdot\left(\vec R_i - \vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi_\text{aux,j}}
+	\Psi^n_{\vec k}\left(\left\{ \vec r_k \right\} \right) = \frac{1}{\sqrt N}\sum_{i} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i\right)
+\end{aligned}\end{equation}
+where \(N\) is the total number of lattice sites.
+The interpretation is that the set of \(n=0\) states form the lowest band in the spectrum of the lattice.
+Higher values of \(n\) produce the more energetic bands.
+The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\)To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
+\begin{equation}\begin{aligned}
+	&\bra{\Psi^n_{\vec k^\prime}}H_\text{H-H} \ket{\Psi^n_{\vec k}}\\
+	&= \frac{1}{N}\sum_{ij}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi^n_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi^n_\text{aux}\left(\vec R_j\right)} = \frac{1}{N}\sum_{i,j}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i} e^{i\vec k^\prime\cdot\left(\vec R_i - \vec{R}_j\right)} \bra{\psi^n_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi^n_\text{aux}\left(\vec R_j\right)}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \sum_{\vec R_i}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i}\sum_{\vec L} e^{i\vec k^\prime\cdot\vec L} \bra{\psi_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi_\text{aux}\left(\vec R_i- \vec L\right)}
-\end{aligned}\end{equation}
-The sum over \(\vec L\) can be split into two summations, one over the distance \(L\) and another over the directions \(\vec a(L)\).
-Also note that because of translation symmetry, the matrix element will depend only on the distance \(L\) and not the direction: \(M(L) \equiv \bra{\psi_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi_\text{aux}\left(\vec R_i- \vec L\right)}\).
-\begin{equation}\begin{aligned}
-	\bra{\Psi_{\vec k^\prime}(\vec r)}H_\text{H-H} \ket{\Psi_{\vec k}(\vec r)} = \sum_{\vec R_i}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i}\sum_{L} M(L) \sum_{\vec a(L)}e^{i\vec k^\prime\cdot\vec a(L)} = \delta_{\vec k, \vec k^\prime}\sum_{L} M(L) \xi_{\vec k}\left(L\right)
-\end{aligned}\end{equation}
-Here, \(\vec a(L)\) sums over all the primitive vectors connecting any single site with all its neighbours at a distance \(L\), and \(\xi_{\vec k} = \sum_{\vec a(L)}e^{i\vec k^\prime\cdot\vec a(L)}\).
+\bra{\Psi^n_{\vec k^\prime}}H_\text{H-H} \ket{\Psi^n_{\vec k}} = \frac{1}{N}\sum_{\vec R_i}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i}\sum_{\vec L} e^{i\vec k^\prime\cdot\vec L} \bra{\psi^n_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi^n_\text{aux}\left(\vec R_i- \vec L\right)}
+\end{aligned}\end{equation}
+Note that because of translation symmetry, the matrix element will depend only on the distance \(\vec L\) and not the position \(\vec R_i\): \(C(-\vec L) \equiv \bra{\psi^n_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi^n_\text{aux}\left(\vec R_i- \vec L\right)}\).
+\begin{equation}\begin{aligned}
+	\bra{\Psi^n_{\vec k^\prime}(\vec r)}H_\text{H-H} \ket{\Psi^n_{\vec k}(\vec r)} = \frac{1}{N}\sum_{\vec R_i}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i}\sum_{\vec L} C(-\vec L) e^{i\vec k^\prime\cdot\vec L} = \frac{1}{N}\delta_{\vec k, \vec k^\prime}\times N\sum_{L} C(\vec L) e^{-i\vec k\cdot\vec L} = \delta_{\vec k, \vec k^\prime} \sum_{L} C(\vec L) e^{-i\vec k\cdot\vec L}
+\end{aligned}\end{equation}
 The Kronecker delta in front ensures that the Hamiltonian \(H_\text{H-H}\) is diagonal in the basis of the constructed eigenstates.
-The eigenvalue corresponding to \(\ket{\Psi_{\vec k}}\) is \(\sum_{L} M(L) \xi_{\vec k}\left(L\right)\).
-
-That \(\Psi_{\vec k}\) transforms like Bloch functions can be easily verified:
-\begin{equation}\begin{aligned}
-	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \sum_{\vec R_i} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R\right) = \sum_{\vec R_j} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\vec r\right)
+The eigenvalue corresponding to \(\ket{\Psi^n_{\vec k}}\) is \(\sum_{L} C(\vec L) e^{-i\vec k\cdot\vec L}\).
+For thr ground state \(\vec k=0,n=0\), this can be simplified into
+\begin{equation}\begin{aligned}
+	\sum_{L} C(\vec L) &= \sum_{\vec L}\bra{\psi^0_\text{aux}\left(\vec R_0\right)} H_\text{H-H}\ket{\psi^0_\text{aux}\left(\vec R_0 - \vec L\right)} = \sum_{\vec L,\vec R_j}\bra{\psi^0_\text{aux}\left(\vec R_0\right)} H_\text{aux}\left(\vec R_j\right) T\left( \vec L \right) \ket{\psi^0_\text{aux}\left(\vec R_0\right)}\\
+			   &=\sum_{\vec L,\vec R_j}\bra{\psi^0_\text{aux}\left(\vec R_0\right)} T(\vec R_0 - \vec R_j) H_\text{aux}\left(\vec R_0\right)T^\dagger(\vec R_0 - \vec R_j) T\left( \vec L \right) \ket{\psi^0_\text{aux}\left(\vec R_0\right)}\\
+			   &=\sum_{\vec L,\vec R_j}\bra{\psi^0_\text{aux}\left(\vec R_0\right)} T(\vec R_0 - \vec R_j) H_\text{aux}\left(\vec R_0\right) T\left(\vec L + \vec R_j - \vec R_0\right) \ket{\psi^0_\text{aux}\left(\vec R_0\right)}\\
+\end{aligned}\end{equation}
+To resolve the remaining translation operators, we will now insert the eigenstates \(\ket{\Psi_{\vec k}}\) of the full model: \(1 = \sum_{\vec k,n}\ket{\Psi^n_{\vec k}}\bra{\Psi^n_{\vec k}}\) in between the operators.
+These eigenkets can in general be any state with a definite momentum, the simplest case being the eigenstates of a tight-binding Hamiltonian obtained by setting \(U=J=0\) in the bulk model.
+We have chosen the eigenstates of the full model for our purpose.
+We already know, from Bloch's theorem, that \(T(\vec R)\ket{\Psi_{\vec k}} = e^{i \vec{k}\cdot\vec{R}}\ket{\Psi_{\vec k}}\).
+\begin{equation}\begin{aligned}
+	\sum_{L} C(\vec L) &= \sum_{n,\vec L,\vec R_j, \vec k_1, \vec k_2}\bra{\psi^0_\text{aux}\left(\vec R_0\right)} \ket{\Psi^n_{\vec k_2}}\bra{\Psi^n_{\vec k_2}} T^\dagger(-\vec R_0 + \vec R_j) H_\text{aux}\left(\vec R_0\right) T\left(\vec L + \vec R_j - \vec R_0\right) \ket{\Psi^n_{\vec k_1}}\bra{\Psi^n_{\vec k_1}}\ket{\psi^0_\text{aux}\left(\vec R_0\right)}\\
+			   &= \sum_{n,\vec L,\vec R_j, \vec k_1, \vec k_2}\bra{\psi^0_\text{aux}\left(\vec R_0\right)} \ket{\Psi^n_{\vec k_2}}\bra{\Psi^n_{\vec k_2}} e^{-i \vec k_2 \cdot \left(-\vec R_0 + \vec R_j\right)} H_\text{aux}\left(\vec R_0\right) e^{i \vec k_1 \cdot \left(\vec L + \vec R_j - \vec R_0\right)} \ket{\Psi^n_{\vec k_1}}\bra{\Psi^n_{\vec k_1}}\ket{\psi^0_\text{aux}\left(\vec R_0\right)}\\
+			   &= \sum_{n,\vec L,\vec k_1, \vec k_2}e^{i \vec{\Psi^n_{\vec k_1}}\cdot\vec{L}}\bra{\psi^0_\text{aux}\left(\vec R_0\right)} \ket{\Psi^n_{\vec k_2}}\bra{\Psi^n_{\vec k_2}} N\delta_{\vec k_1,\vec k_2} H_\text{aux}\left(\vec R_0\right) \ket{\Psi^n_{\vec k_1}}\bra{k_1}\ket{\psi^0_\text{aux}\left(\vec R_0\right)}\\
+			   &= N\sum_{n,\vec L, \vec k}e^{i \vec{k}\cdot\vec{L}} |\braket{\psi^0_\text{aux}\left(\vec R_0\right) | \Psi_{\vec k}^n}|^2 \bra{\Psi_{\vec k}^n} H_\text{aux}\left(\vec R_0\right) \ket{\Psi_{\vec k}^n}\\
+			   &= N^2 |\braket{\psi^0_\text{aux}\left(\vec R_0\right) | \Psi_\text{gs}}|^2 \bra{\Psi_\text{gs}} H_\text{aux}\left(\vec R_0\right) \ket{\Psi_\text{gs}}\\
+\end{aligned}\end{equation}
+\(\ket{\Psi_\text{gs}}\) is the ground state of the bulk model, and can be expressed as a sum over the auxiliary models at varying distances from \(\vec R_0\).
+This form allows a systematic method of improving the energy eigenvalue estimate, because the interacting in the impurity model is extremely localised, so the overlap between two auxiliary models decreases rapidly with distance.
+The majority of the contribution will come from the auxiliary model at \(\vec R_0\), and improvements are then made by considering auxiliary models at further distances.
+
+It is easy to verify that \(\Psi^n_{\vec k}\) transforms like Bloch functions:
+\begin{equation}\begin{aligned}
+	\Psi^n_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\sqrt N}\sum_{\vec R_i} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i - \vec R\right) = \frac{1}{\sqrt N}\sum_{\vec R_j} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi^n_\text{aux}\left(\vec R_j\right) = e^{i \vec{k}\cdot\vec{R}} \Psi^n_{\vec k}\left(\vec r\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Psi_{\vec k}\left(\left\{\vec r_k\right\}\right) = e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right) = e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
-\end{aligned}\end{equation}
-where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
+	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\sqrt N}e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right) = e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
+\end{aligned}\end{equation}
+where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\sqrt N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
 This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
@@
 \section{Single-particle Green's function}
-We define \(\ket{\Phi_0(\vec k)}\) as the ground state of the bulk model, and it has an expression in terms of the auxiliary model eigenstates: \(\ket{\Phi_0(\vec k)} = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left( \vec R_i \right) \).
+In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}} = \ket{\Psi^{n=0}_{\vec k=0}} = \frac{1}{\sqrt N}\sum_{\vec R}\ket{\psi^0_\text{aux}\left( \vec R \right)}\) of the bulk Hamiltonian.
 To obtain Greens functions, we start by calculating real-space matrix elements of the bulk and auxiliary Hamiltonians.
-The states that we will consider are local excitations on top of the ground state: \(\ket{i} \equiv c^\dagger_{i\sigma}\ket{\Phi_0\left( \vec k \right) }\).
+The states that we will consider are local excitations on top of the ground state: \(\ket{i} \equiv c^\dagger_{i\sigma}\ket{\Psi_\text{gs} }\).
 \(i\) represents a lattice site.
@@
 	\label{diag_mat_ele_1}
-	\braket{i | H_\text{H-H} | i} = \sum_{\vec R_j} \braket{\Phi_0\left( \vec k \right) | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma} | \Phi_0\left( \vec k \right) } = \sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi_\text{aux}\left( \vec R_n \right) | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma}  | \psi_\text{aux}\left( \vec R_m \right)}
+	\braket{i | H_\text{H-H} | i} = \sum_{\vec R_j} \braket{\Psi_\text{gs} | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma} | \Psi_\text{gs} } = \frac{1}{N}\sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi^0_\text{aux}\left( \vec R_n \right) | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma}  | \psi^0_\text{aux}\left( \vec R_m \right)}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\ket{\psi_\text{aux}\left( \vec R_m \right)} = \ket{\psi_\text{aux}\left( \left\{\vec r_k - \vec R_m\right\} \right)} = \ket{\psi_\text{aux}\left( \left\{\vec r_k - \vec R_0 + \left(\vec R_0 - \vec R_m\right)\right\} \right)} = T\left( \vec R_0 - \vec R_m \right) \ket{\psi_\text{aux}\left( \left\{\vec r_k - \vec R_0\right\} \right)} \\
-	= T\left(\vec R_0 - \vec R_m\right) \ket{\psi_\text{aux}\left(\vec R_0\right)}
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-	\ket{\psi_\text{aux}\left( \vec R_n \right)} = T\left(\vec R_0 - \vec R_n\right) \ket{\psi_\text{aux}\left(\vec R_0\right)}
+	\ket{\psi^0_\text{aux}\left( \vec R_m \right)} = \ket{\psi^0_\text{aux}\left( \left\{\vec r_k - \vec R_m\right\} \right)} = \ket{\psi^0_\text{aux}\left( \left\{\vec r_k - \vec R_0 + \left(\vec R_0 - \vec R_m\right)\right\} \right)} = T\left( \vec R_0 - \vec R_m \right) \ket{\psi^0_\text{aux}\left( \left\{\vec r_k - \vec R_0\right\} \right)} \\
+	= T\left(\vec R_0 - \vec R_m\right) \ket{\psi^0_\text{aux}\left(\vec R_0\right)}
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	\ket{\psi^0_\text{aux}\left( \vec R_n \right)} = T\left(\vec R_0 - \vec R_n\right) \ket{\psi^0_\text{aux}\left(\vec R_0\right)}
 \end{aligned}\end{equation}
@@
 	&\braket{i | H_\text{H-H} | i} \\
-	&= \sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi_\text{aux}\left( \vec R_0 \right) | T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma}  T\left( \vec R_0 - \vec R_m \right)| \psi_\text{aux}\left( \vec R_0 \right)}
+	&= \frac{1}{N}\sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi^0_\text{aux}\left( \vec R_0 \right) | T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma}  T\left( \vec R_0 - \vec R_m \right)| \psi^0_\text{aux}\left( \vec R_0 \right)}
 \end{aligned}\end{equation}
@@
 												    &= T^\dagger\left( \vec R_0 - \vec R_n \right) T^\dagger \left(\vec R_j - \vec R_0\right) T\left(\vec R_j - \vec R_0\right) c_{\sigma}\left( \vec R_i \right)  T^\dagger\left(\vec R_j - \vec R_0\right)\\
-												    &=T^\dagger\left(\vec R_j - \vec R_n\right) c_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)
+												    &=T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma} T\left( \vec R_0 - \vec R_m \right) = \left[T^\dagger\left( \vec R_0 - \vec R_m \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\right]^\dagger = c^\dagger_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right) T\left(\vec R_j - \vec R_m\right)
-\end{aligned}\end{equation}
+	T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma} T\left( \vec R_0 - \vec R_m \right) = \left[T^\dagger\left( \vec R_0 - \vec R_m \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\right]^\dagger = c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)
+\end{aligned}\end{equation}
+The operator \(c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\) creates an electron of spin \(\sigma\) at the position \(\vec R_i - \vec R_j + \vec R_0\).
+It will be represented as \(c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\).
 Substituting these forms gives
@@
 	&\braket{i | H_\text{H-H} | i} \\
-	&= \sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi_\text{aux}\left( \vec R_0 \right) | T^\dagger\left(\vec R_j - \vec R_n\right) c_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right) T\left(\vec R_j - \vec R_m\right)| \psi_\text{aux}\left( \vec R_0 \right)}
+	&= \frac{1}{N}\sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi^0_\text{aux}\left( \vec R_0 \right) | T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)| \psi^0_\text{aux}\left( \vec R_0 \right)}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
+	\braket{i | H_\text{H-H} | i} = \frac{1}{N}\sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \bra{\psi^0_\text{aux}\left( \vec R_0 \right)} \sum_{\vec k_2}\ket{\vec k_2}\bra{\vec k_2}T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\\
+	 \sum_{\vec k_1}T\left(\vec R_j - \vec R_m\right)\ket{\vec k_1}\bra{\vec k_1} \ket{\psi^0_\text{aux}\left( \vec R_0 \right)}
+\end{aligned}\end{equation}
+From the definition of the translation operators shown above, we get 
+\begin{equation}\begin{aligned}
+T\left(\vec R_j - \vec R_m\right)\ket{\vec k_1} = e^{i \vec{k}_1\cdot\left(\vec{R}_j - \vec R_m\right)}\ket{\vec k_1}, ~ ~\bra{\vec k_2}T^\dagger\left(\vec R_j - \vec R_n\right) = \bra{\vec k_2}e^{-i \vec{k}_2\cdot\left(\vec{R}_j - \vec R_n\right)}~.
+\end{aligned}\end{equation}
+ Substituting this gives
+\begin{equation}\begin{aligned}
 	&\braket{i | H_\text{H-H} | i} \\
-	=& \sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \bra{\psi_\text{aux}\left( \vec R_0 \right)} \sum_{\vec k_2}\ket{\vec k_2}\bra{\vec k_2}T^\dagger\left(\vec R_j - \vec R_n\right) c_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\\
-	 &\sum_{\vec k_1}T\left(\vec R_j - \vec R_m\right)\ket{\vec k_1}\bra{\vec k_1} \ket{\psi_\text{aux}\left( \vec R_0 \right)}
-\end{aligned}\end{equation}
-From the definition of the translation operators shown above, we get \(T\left(\vec R_j - \vec R_m\right)\ket{\vec k_1} = e^{i \vec{k}_1\cdot\left(\vec{R}_j - \vec R_m\right)}\ket{\vec k_1}\) and \(\bra{\vec k_2}T^\dagger\left(\vec R_j - \vec R_n\right) = \bra{\vec k_2}e^{-i \vec{k}_2\cdot\left(\vec{R}_j - \vec R_n\right)}\).
-Substituting this gives
-\begin{equation}\begin{aligned}
-	&\braket{i | H_\text{H-H} | i} \\
-	=& \sum_{\vec R_j, \vec R_m, \vec R_n}\sum_{\vec k_1,\vec k_2} e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right)} e^{i\vec{R}_n\cdot\left(\vec{k}_2 - \vec k\right)} e^{i\vec{R}_m\cdot\left(\vec{k} - \vec k_1\right)} \bra{\psi_\text{aux}\left( \vec R_0 \right)} \ket{\vec k_2}\bra{\vec k_2} c_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\\
-	 &\ket{\vec k_1}\bra{\vec k_1} \ket{\psi_\text{aux}\left( \vec R_0 \right)}\\
-	=& \sum_{\vec R_j}\sum_{\vec k_1,\vec k_2} e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right)} \delta_{\vec{k},\vec k_2} \delta_{\vec{k},\vec k_1} \bra{\psi_\text{aux}\left( \vec R_0 \right)} \ket{\vec k_2}\bra{\vec k_2} c_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\ket{\vec k_1}\bra{\vec k_1} \ket{\psi_\text{aux}\left( \vec R_0 \right)}\\
-	=& \sum_{\vec R_j} \braket{\psi_\text{aux}\left( \vec R_0 \right) | \vec k}\bra{\vec k} c_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left( \vec R_i - \vec R_j + \vec R_0\right)\ket{\vec k}\braket{\vec k | \psi_\text{aux}\left( \vec R_0 \right)}\\
+	=& \frac{1}{N} \sum_{\vec R_j, \vec R_m, \vec R_n}\sum_{\vec k_1,\vec k_2} e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right)} e^{i\vec{R}_n\cdot\left(\vec{k}_2 - \vec k\right)} e^{i\vec{R}_m\cdot\left(\vec{k} - \vec k_1\right)} \bra{\psi^0_\text{aux}\left( \vec R_0 \right)} \ket{\vec k_2}\bra{\vec k_2} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\\
+	 &\ket{\vec k_1}\bra{\vec k_1} \ket{\psi^0_\text{aux}\left( \vec R_0 \right)}\\
+	=& \frac{1}{N} \sum_{\vec R_j}\sum_{\vec k_1,\vec k_2} e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right)} N^2 \delta_{\vec{k},\vec k_2} \delta_{\vec{k},\vec k_1} \bra{\psi^0_\text{aux}\left( \vec R_0 \right)} \ket{\vec k_2}\bra{\vec k_2} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\vec k_1}\bra{\vec k_1} \ket{\psi^0_\text{aux}\left( \vec R_0 \right)}\\
+	=& N \sum_{\vec R_j} \braket{\psi^0_\text{aux}\left( \vec R_0 \right) | \vec k}\bra{\vec k} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\vec k}\braket{\vec k | \psi^0_\text{aux}\left( \vec R_0 \right)}\\
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = |\braket{\psi_\text{aux}\left( \vec R_0 \right) | \vec k}|^2 \bra{\vec k} \sum_{\vec R_j} c_{\sigma}\left(\vec R_j\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left(\vec R_j\right)\ket{\vec k}
+	\braket{i | H_\text{H-H} | i} = N |\braket{\psi^0_\text{aux}\left( \vec R_0 \right) | \vec k}|^2 \bra{\vec k} \sum_{\vec R_j} c_{\sigma}\left(\vec R_j\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left(\vec R_j\right)\ket{\vec k}
 \end{aligned}\end{equation}
 Even though it is computationally easier to consider the state \(\ket{\vec k}\) as the momentum eigenstates of the tight-binding kind, there is a more illuminating interpretation of this expression if we consider them as the eigenstates \(\ket{\Phi\left( \vec k \right) }\) of the full bulk model.
-With this choice, the expression can be seen as the sum of effects of creating a single-particle excitation \(c^\dagger_\sigma\) on the ground state \(\ket{\Phi_0\left( \vec k \right) }\), at increasingly larger distances \(\vec R_j\) from the auxiliary model at \(\vec R_0\).
+With this choice, the expression can be seen as the sum of effects of creating a single-particle excitation \(c^\dagger_\sigma\) on the ground state \(\ket{\Psi_\text{gs} }\), at increasingly larger distances \(\vec R_j\) from the auxiliary model at \(\vec R_0\).
 The excitation is made to evolve through the auxiliary model \(\mathcal{H}_\text{aux}\left( \vec R_0 \right) \) centred at \(\vec R_0\).
@@
 That inner product can be thought of as an overlap between a separable state and an entangled state - the full Hamiltonian state is obtained by entangling the overlapping auxiliary models, while the single auxiliary model groundstate is the separable state in this context.
-The inner product then becomes a measure of entanglement of the bulk ground state - the more the overlap with the separable state, the lower the entanglement: \(\varepsilon(\vec R_0,\vec k) \equiv 1 - |\braket{\psi_\text{aux}\left(  \right) | \Phi_0(\vec k)}|^2\).
-\begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = \left( 1 - \varepsilon(\vec R_0,\vec k) \right) \bra{\Phi_0(\vec k)} \sum_{\vec R_j} c_{\sigma}\left(\vec R_j\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left(\vec R_j\right)\ket{\Phi_0(\vec k)}
+The inner product then becomes a measure of entanglement of the bulk ground state - the more the overlap with the separable state, the lower the entanglement: \(\varepsilon(\vec R_0,\vec k) \equiv 1 - |\braket{\psi^0_\text{aux}\left(  \right) | \Phi_0(\vec k)}|^2\).
+\begin{equation}\begin{aligned}
+	\braket{i | H_\text{H-H} | i} = N \left( 1 - \varepsilon(\vec R_0,\vec k) \right) \bra{\Phi_0(\vec k)} \sum_{\vec R_j} c_{\sigma}\left(\vec R_j\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left(\vec R_j\right)\ket{\Phi_0(\vec k)}
 \end{aligned}\end{equation}

### 2022-04-20 notes/notes.tex
proved orthonormality of eigenstates

@@
 	\label{bloch-states}
-	\Psi^n_{\vec k}\left(\left\{ \vec r_k \right\} \right) = \frac{1}{\sqrt N}\sum_{i} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i\right)
+	\ket{\Psi^n_{\vec k}\left(\left\{ \vec r_k \right\} \right)} = \frac{1}{\sqrt N}\sum_{\vec R_i} e^{i \vec{k}\cdot\vec{R}_i} \ket{\psi^n_\text{aux}\left(\vec R_i\right)}
 \end{aligned}\end{equation}
@@
 Higher values of \(n\) produce the more energetic bands.
-The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\)To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
+The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\).
+These states form an orthonormal basis:
+\begin{flalign*}
+	&\braket{\Psi^m_{\vec k^\prime} | \Psi^n_{\vec k}} \\
+	&= \frac{1}{N}\sum_{\vec R_i, \vec R_j} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}^m\left( \vec R_j \right) | \psi_\text{aux}^n\left( \vec R_i \right)} = \frac{1}{N}\sum_{\vec R_i, \vec R_j} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}^m\left( \vec R_0 \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}^n\left( \vec R_0 \right)}\\
+	&= \frac{1}{N}\sum_{\vec R_i, \vec R_j, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}^m\left( \vec R_0 \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}^n\left( \vec R_0 \right)}\\
+	&= \frac{1}{N}\sum_{\vec R_i, \vec R_j, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}^m\left( \vec R_0 \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}^n\left( \vec R_0 \right)} \\
+	&= N \delta_{\vec k, \vec k^\prime}\braket{\psi_\text{aux}^m\left( \vec R_0 \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}^n\left( \vec R_0 \right)}, ~ ~ ~ \left[\because \sum_{\vec R_i}e^{i \vec R_i \left( \vec k - \vec q \right) }\sum_{\vec R_j}e^{i \vec R_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q} \right]\\
+	&= \delta_{\vec k, \vec k^\prime}\int \prod_{\vec r_k}d\vec r_k~ \psi_\text{aux}^m\left( \left\{\vec r_k\right\} \right) e^{i \vec k \cdot \sum \vec r_k} \prod_{\vec r_k^\prime} d\vec r_k^\prime~ e^{-i \vec k \cdot \sum \vec r^\prime_k} \psi_\text{aux}^n\left( \left\{\vec r_k^\prime\right\} \right)
+\end{flalign*}
+The local nature of the auxiliary model wavefunctions ensures that the product of two auxiliary model wavefunctions will be non-zero only in the common region: \(\psi_\text{aux}^m\left( \left\{\vec r_k\right\} \right) \psi_\text{aux}^n\left( \left\{\vec r_k^\prime\right\}\right) \simeq \delta_{\vec r_k, \vec r_k^\prime} \psi_\text{aux}^m\left( \left\{\vec r_k\right\} \right) \psi_\text{aux}^n\left( \left\{\vec r_k\right\}\right)\).
+Substituting this and dropping the \(\prod\) for brevity gives
+\begin{equation}\begin{aligned}
+	\braket{\Psi^m_{\vec k^\prime} | \Psi^n_{\vec k}} = \delta_{\vec k, \vec k^\prime}\int d\vec r_k~ d\vec r_k^\prime~ \delta_{\vec r_k, \vec r_k^\prime} \psi_\text{aux}^m\left(\left\{\vec r_k\right\}\right) \psi_\text{aux}^n\left(\left\{\vec r_k\right\}\right) e^{i \vec k \cdot \sum \left(\vec r_k - \vec r^\prime_k\right) } = \delta_{\vec k, \vec k^\prime}\int d\vec r_k \psi_\text{aux}^m\left(\left\{\vec r_k\right\}\right) \psi_\text{aux}^n\left(\left\{\vec r_k\right\}\right) = \delta_{\vec k,\vec k^\prime}\delta_{m,n}
+\end{aligned}\end{equation}
+At the last step, we used the orthonormality of the eigenstates of the auxiliary model: \(\int \prod_{\vec r_k} d\vec r_k \psi_\text{aux}^m\left(\left\{\vec r_k\right\}\right) \psi_\text{aux}^n\left(\left\{\vec r_k\right\}\right) = \delta_{m,n}\).
+
+To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
 \begin{equation}\begin{aligned}

### 2022-04-23 notes/notes.tex
--no-message

--- 2022-04-19 notes/notes.tex
@@
 
-We can use the auxiliary model eigenstates \(\psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\} \right) \equiv \psi^n_\text{aux}\left(\vec R_i\right)\) to construct eigenstates of the bulk Hamiltonian.
+We can use the auxiliary model zero-bandwidth wavefunctions 
+\begin{equation}\begin{aligned}
+\psi^n_\text{aux}\left(\vec r_d - \vec R_i, \vec r_0 - \left(\vec R_i + \vec a\right)  \right) \equiv \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
+\end{aligned}\end{equation}
+with the impurity position \(\vec R_i\) and zeroth site position \(\vec R_i + \vec a\), to construct eigenstates of the bulk Hamiltonian.
+\(\vec R_i\) is a lattice vector, while \(\vec a\) is one of the \(w\) vectors that connect a lattice site with its nearest neighbours.
+This two site wavefunction can be obtained by first studying the full auxiliary model \(\mathcal{H}_\text{aux}\) under a renormalisation group, obtaining a fixed-point Hamiltonian in the IR, obtaining the IR eigenstate and then tracing out all lattice sites except the impurity and the zeroth site from this eigenstate.
 \(n=0\) is the ground state of the auxiliary model, and higher values denote the excited states.
-The following combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
-\begin{equation}\begin{aligned}
-	\label{bloch-states}
-	\Psi^n_{\vec k}\left(\left\{ \vec r_k \right\} \right) = \frac{1}{\sqrt N}\sum_{i} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i\right)
+
+The following un-normalised combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
+\begin{equation}\begin{aligned}
+	\ket{\Psi^n_{\vec k}} = \frac{1}{w \sqrt N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
 \end{aligned}\end{equation}
@@
 Higher values of \(n\) produce the more energetic bands.
-The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\)To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
-\begin{equation}\begin{aligned}
-	&\bra{\Psi^n_{\vec k^\prime}}H_\text{H-H} \ket{\Psi^n_{\vec k}}\\
-	&= \frac{1}{N}\sum_{ij}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi^n_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi^n_\text{aux}\left(\vec R_j\right)} = \frac{1}{N}\sum_{i,j}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i} e^{i\vec k^\prime\cdot\left(\vec R_i - \vec{R}_j\right)} \bra{\psi^n_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi^n_\text{aux}\left(\vec R_j\right)}
-\end{aligned}\end{equation}
-We define \(\vec L = \vec R_i - \vec R_j\), and sum over \(\vec L\): 
-\begin{equation}\begin{aligned}
-\bra{\Psi^n_{\vec k^\prime}}H_\text{H-H} \ket{\Psi^n_{\vec k}} = \frac{1}{N}\sum_{\vec R_i}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i}\sum_{\vec L} e^{i\vec k^\prime\cdot\vec L} \bra{\psi^n_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi^n_\text{aux}\left(\vec R_i- \vec L\right)}
-\end{aligned}\end{equation}
-Note that because of translation symmetry, the matrix element will depend only on the distance \(\vec L\) and not the position \(\vec R_i\): \(C(-\vec L) \equiv \bra{\psi^n_\text{aux}\left(\vec R_i\right)} H_\text{H-H}\ket{\psi^n_\text{aux}\left(\vec R_i- \vec L\right)}\).
-\begin{equation}\begin{aligned}
-	\bra{\Psi^n_{\vec k^\prime}(\vec r)}H_\text{H-H} \ket{\Psi^n_{\vec k}(\vec r)} = \frac{1}{N}\sum_{\vec R_i}e^{i\left(\vec{k} - \vec k^\prime\right)\cdot\vec{R}_i}\sum_{\vec L} C(-\vec L) e^{i\vec k^\prime\cdot\vec L} = \frac{1}{N}\delta_{\vec k, \vec k^\prime}\times N\sum_{L} C(\vec L) e^{-i\vec k\cdot\vec L} = \delta_{\vec k, \vec k^\prime} \sum_{L} C(\vec L) e^{-i\vec k\cdot\vec L}
-\end{aligned}\end{equation}
-The Kronecker delta in front ensures that the Hamiltonian \(H_\text{H-H}\) is diagonal in the basis of the constructed eigenstates.
-The eigenvalue corresponding to \(\ket{\Psi^n_{\vec k}}\) is \(\sum_{L} C(\vec L) e^{-i\vec k\cdot\vec L}\).
-For thr ground state \(\vec k=0,n=0\), this can be simplified into
-\begin{equation}\begin{aligned}
-	\sum_{L} C(\vec L) &= \sum_{\vec L}\bra{\psi^0_\text{aux}\left(\vec R_0\right)} H_\text{H-H}\ket{\psi^0_\text{aux}\left(\vec R_0 - \vec L\right)} = \sum_{\vec L,\vec R_j}\bra{\psi^0_\text{aux}\left(\vec R_0\right)} H_\text{aux}\left(\vec R_j\right) T\left( \vec L \right) \ket{\psi^0_\text{aux}\left(\vec R_0\right)}\\
-			   &=\sum_{\vec L,\vec R_j}\bra{\psi^0_\text{aux}\left(\vec R_0\right)} T(\vec R_0 - \vec R_j) H_\text{aux}\left(\vec R_0\right)T^\dagger(\vec R_0 - \vec R_j) T\left( \vec L \right) \ket{\psi^0_\text{aux}\left(\vec R_0\right)}\\
-			   &=\sum_{\vec L,\vec R_j}\bra{\psi^0_\text{aux}\left(\vec R_0\right)} T(\vec R_0 - \vec R_j) H_\text{aux}\left(\vec R_0\right) T\left(\vec L + \vec R_j - \vec R_0\right) \ket{\psi^0_\text{aux}\left(\vec R_0\right)}\\
-\end{aligned}\end{equation}
-To resolve the remaining translation operators, we will now insert the eigenstates \(\ket{\Psi_{\vec k}}\) of the full model: \(1 = \sum_{\vec k,n}\ket{\Psi^n_{\vec k}}\bra{\Psi^n_{\vec k}}\) in between the operators.
-These eigenkets can in general be any state with a definite momentum, the simplest case being the eigenstates of a tight-binding Hamiltonian obtained by setting \(U=J=0\) in the bulk model.
-We have chosen the eigenstates of the full model for our purpose.
-We already know, from Bloch's theorem, that \(T(\vec R)\ket{\Psi_{\vec k}} = e^{i \vec{k}\cdot\vec{R}}\ket{\Psi_{\vec k}}\).
-\begin{equation}\begin{aligned}
-	\sum_{L} C(\vec L) &= \sum_{n,\vec L,\vec R_j, \vec k_1, \vec k_2}\bra{\psi^0_\text{aux}\left(\vec R_0\right)} \ket{\Psi^n_{\vec k_2}}\bra{\Psi^n_{\vec k_2}} T^\dagger(-\vec R_0 + \vec R_j) H_\text{aux}\left(\vec R_0\right) T\left(\vec L + \vec R_j - \vec R_0\right) \ket{\Psi^n_{\vec k_1}}\bra{\Psi^n_{\vec k_1}}\ket{\psi^0_\text{aux}\left(\vec R_0\right)}\\
-			   &= \sum_{n,\vec L,\vec R_j, \vec k_1, \vec k_2}\bra{\psi^0_\text{aux}\left(\vec R_0\right)} \ket{\Psi^n_{\vec k_2}}\bra{\Psi^n_{\vec k_2}} e^{-i \vec k_2 \cdot \left(-\vec R_0 + \vec R_j\right)} H_\text{aux}\left(\vec R_0\right) e^{i \vec k_1 \cdot \left(\vec L + \vec R_j - \vec R_0\right)} \ket{\Psi^n_{\vec k_1}}\bra{\Psi^n_{\vec k_1}}\ket{\psi^0_\text{aux}\left(\vec R_0\right)}\\
-			   &= \sum_{n,\vec L,\vec k_1, \vec k_2}e^{i \vec{\Psi^n_{\vec k_1}}\cdot\vec{L}}\bra{\psi^0_\text{aux}\left(\vec R_0\right)} \ket{\Psi^n_{\vec k_2}}\bra{\Psi^n_{\vec k_2}} N\delta_{\vec k_1,\vec k_2} H_\text{aux}\left(\vec R_0\right) \ket{\Psi^n_{\vec k_1}}\bra{k_1}\ket{\psi^0_\text{aux}\left(\vec R_0\right)}\\
-			   &= N\sum_{n,\vec L, \vec k}e^{i \vec{k}\cdot\vec{L}} |\braket{\psi^0_\text{aux}\left(\vec R_0\right) | \Psi_{\vec k}^n}|^2 \bra{\Psi_{\vec k}^n} H_\text{aux}\left(\vec R_0\right) \ket{\Psi_{\vec k}^n}\\
-			   &= N^2 |\braket{\psi^0_\text{aux}\left(\vec R_0\right) | \Psi_\text{gs}}|^2 \bra{\Psi_\text{gs}} H_\text{aux}\left(\vec R_0\right) \ket{\Psi_\text{gs}}\\
-\end{aligned}\end{equation}
-\(\ket{\Psi_\text{gs}}\) is the ground state of the bulk model, and can be expressed as a sum over the auxiliary models at varying distances from \(\vec R_0\).
+The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\).
+We will actually work only in the lowest band \(n=0\), so we will drop the band index from now on and keep in mind that only the auxiliary model ground states appear in the formulation:
+\begin{equation}\begin{aligned}
+	\label{bloch-states}
+	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
+\end{aligned}\end{equation}
+where \(\lambda_{\vec k}\) is a normalisation factor and is defined by \(|\lambda_{\vec k}|^2 = |\braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}|^2 \); \(\ket{\vec k}\) is the momentum eigenstate for momentum \(\vec k\), and \(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
+Becuase of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(w\) choices.
+
+It is easy to verify that \(\Psi_{\vec k}\left(\left\{ \vec r_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \(\vec R\):
+\begin{equation}\begin{aligned}
+	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
+\end{aligned}\end{equation}
+In the last equation, we transformed \(\vec R_i \to \vec R_j = \vec R_i - \vec R\).
+Note that the argument \(\vec a\) does not change under a translation of the system, because that vector always represents the difference between the impurity lattice position and its nearest neighbours, irrespective of the absolute position of the impurity.
+
+The wavefunction can be even brought into the familiar Bloch function form:
+\begin{equation}\begin{aligned}
+	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\vec k} w N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\vec k} w N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
+	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
+\end{aligned}\end{equation}
+where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
+This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
+
+It is straightforward to show that these states form an orthonormal basis. We start by writing down the inner product of two distinct such states:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
+	&= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
+	&= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+\end{aligned}\end{equation}
+At this point, we insert a complete basis of momentum eigenkets \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+	&= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
+	&= \frac{1}{|\lambda_{\vec k}|^2 w^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+\end{aligned}\end{equation}
+At the last step, we used the summation form of the Kronecker delta function: \(\sum_{\vec R_i}e^{i \vec R_i \left( \vec k - \vec q \right) }\sum_{\vec R_j}e^{i \vec R_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\).
+The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \(\vec a, \vec a^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\vec k}\):
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\vec k}|^2 w^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\vec k}|^2 = \frac{1}{|\lambda_{\vec k}|^2 w^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\vec k}|^2 = \delta_{\vec k, \vec k^\prime}
+\end{aligned}\end{equation}
+This concludes the proof of orthonormality.
+
+To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
+\begin{equation}\begin{aligned}
+	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
+	&= \frac{1}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+	&= \frac{1}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}
+\end{aligned}\end{equation}
+To resolve the translation operators, we will now insert the momentum eigenstates \(\ket{\vec k}\) of the full model: \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) in between the operators.
+\begin{equation}\begin{aligned}
+	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+	&= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+	&= \frac{N}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+	&= \frac{N}{|\lambda_{\vec k}|^2 w^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+	&= \frac{N}{|\lambda_{\vec k}|^2 w^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\vec k}|^2}\\
+	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}
+\end{aligned}\end{equation}
+The momentum eigenket \(\ket{\vec k}\) can be expressed as a sum over position eigenkets at varying distances from \(\vec R_0\).
 This form allows a systematic method of improving the energy eigenvalue estimate, because the interacting in the impurity model is extremely localised, so the overlap between two auxiliary models decreases rapidly with distance.
-The majority of the contribution will come from the auxiliary model at \(\vec R_0\), and improvements are then made by considering auxiliary models at further distances.
-
-It is easy to verify that \(\Psi^n_{\vec k}\) transforms like Bloch functions:
-\begin{equation}\begin{aligned}
-	\Psi^n_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\sqrt N}\sum_{\vec R_i} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i - \vec R\right) = \frac{1}{\sqrt N}\sum_{\vec R_j} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi^n_\text{aux}\left(\vec R_j\right) = e^{i \vec{k}\cdot\vec{R}} \Psi^n_{\vec k}\left(\vec r\right)
-\end{aligned}\end{equation}
-In the last equation, we transformed \(\vec R_i \to \vec R_j = \vec R_i - \vec R\). The wavefunction can be even brought into the familiar Bloch function form:
-\begin{equation}\begin{aligned}
-	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\sqrt N}e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right) = e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
-\end{aligned}\end{equation}
-where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\sqrt N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
-This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
+The majority of the contribution will come from the state at \(\vec R_0\), and improvements are then made by considering auxiliary models at further distances.
 
 \section{Single-particle Green's function}
-In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}} = \ket{\Psi^{n=0}_{\vec k=0}} = \frac{1}{\sqrt N}\sum_{\vec R}\ket{\psi^0_\text{aux}\left( \vec R \right)}\) of the bulk Hamiltonian.
+In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}} = \ket{\Psi^{n=0}_{\vec k=0}} = \frac{1}{\lambda_0 w N}\sum_{\vec R, \vec a}\ket{\psi_\text{aux}\left( \vec R, \vec a \right)}\) of the bulk Hamiltonian.
 To obtain Greens functions, we start by calculating real-space matrix elements of the bulk and auxiliary Hamiltonians.
@@
 	\label{diag_mat_ele_1}
-	\braket{i | H_\text{H-H} | i} = \sum_{\vec R_j} \braket{\Psi_\text{gs} | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma} | \Psi_\text{gs} } = \frac{1}{N}\sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi^0_\text{aux}\left( \vec R_n \right) | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma}  | \psi^0_\text{aux}\left( \vec R_m \right)}
+	\braket{i | H_\text{H-H} | i} = \frac{1}{|\lambda_0|^2 w^2 N^2}\sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime}} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi_\text{aux}\left( \vec R_n, \vec a^\prime \right) | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma}  | \psi_\text{aux}\left( \vec R_m, \vec a \right)}
 \end{aligned}\end{equation}
@@
 In order to rewrite everything in terms of a single auxiliary model at the origin \(\vec R_0\) of the lattice, we will use the translation operators:
-\begin{equation}\begin{aligned}
-	\ket{\psi^0_\text{aux}\left( \vec R_m \right)} = \ket{\psi^0_\text{aux}\left( \left\{\vec r_k - \vec R_m\right\} \right)} = \ket{\psi^0_\text{aux}\left( \left\{\vec r_k - \vec R_0 + \left(\vec R_0 - \vec R_m\right)\right\} \right)} = T\left( \vec R_0 - \vec R_m \right) \ket{\psi^0_\text{aux}\left( \left\{\vec r_k - \vec R_0\right\} \right)} \\
-	= T\left(\vec R_0 - \vec R_m\right) \ket{\psi^0_\text{aux}\left(\vec R_0\right)}
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-	\ket{\psi^0_\text{aux}\left( \vec R_n \right)} = T\left(\vec R_0 - \vec R_n\right) \ket{\psi^0_\text{aux}\left(\vec R_0\right)}
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
+\begin{gather}
+	\ket{\psi_\text{aux}\left( \vec R_m, \vec a \right)} = T\left(\vec R_0 - \vec R_m\right) \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}, ~ \ket{\psi_\text{aux}\left( \vec R_n, \vec a^\prime \right)} = T\left(\vec R_0 - \vec R_n\right) \ket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)}\\
 	\mathcal{H}_\text{aux}\left( \vec R_j \right) = T\left(\vec R_0 - \vec R_j\right) \mathcal{H}_\text{aux}\left( \vec R_0 \right) T^\dagger\left(\vec R_0 - \vec R_j\right)
-\end{aligned}\end{equation}
+\end{gather}
 Substituting these forms into the expression in eq.~\ref{diag_mat_ele_1} gives
 \begin{equation}\begin{aligned}
-	&\braket{i | H_\text{H-H} | i} \\
-	&= \frac{1}{N}\sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi^0_\text{aux}\left( \vec R_0 \right) | T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma}  T\left( \vec R_0 - \vec R_m \right)| \psi^0_\text{aux}\left( \vec R_0 \right)}
+	&\braket{i | H_\text{H-H} | i} =\\
+	&\sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_0|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma}  T\left( \vec R_0 - \vec R_m \right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}
 \end{aligned}\end{equation}
@@
 	&\braket{i | H_\text{H-H} | i} \\
-	&= \frac{1}{N}\sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi^0_\text{aux}\left( \vec R_0 \right) | T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)| \psi^0_\text{aux}\left( \vec R_0 \right)}
-\end{aligned}\end{equation}
-To resolve the remaining translation operators, we will now insert momentum eigenkets \(1 = \sum_{\vec k}\ket{\vec k}\bra{\vec k}\) in between the operators.
-These eigenkets can be any state with a definite momentum, the simplest case being the eigenstates of a tight-binding Hamiltonian obtained by setting \(U=J=0\) in the bulk model.
-\begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = \frac{1}{N}\sum_{\vec R_j, \vec R_m, \vec R_n} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \bra{\psi^0_\text{aux}\left( \vec R_0 \right)} \sum_{\vec k_2}\ket{\vec k_2}\bra{\vec k_2}T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\\
-	 \sum_{\vec k_1}T\left(\vec R_j - \vec R_m\right)\ket{\vec k_1}\bra{\vec k_1} \ket{\psi^0_\text{aux}\left( \vec R_0 \right)}
-\end{aligned}\end{equation}
-From the definition of the translation operators shown above, we get 
-\begin{equation}\begin{aligned}
-T\left(\vec R_j - \vec R_m\right)\ket{\vec k_1} = e^{i \vec{k}_1\cdot\left(\vec{R}_j - \vec R_m\right)}\ket{\vec k_1}, ~ ~\bra{\vec k_2}T^\dagger\left(\vec R_j - \vec R_n\right) = \bra{\vec k_2}e^{-i \vec{k}_2\cdot\left(\vec{R}_j - \vec R_n\right)}~.
+	&= \sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_0|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime\right) | T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}
+\end{aligned}\end{equation}
+To resolve the remaining translation operators, we will now insert the eigenstates \(1 = \sum_{\vec k}\ket{\Psi_{\vec k}}\bra{\Psi_{\vec k}}\) in between the operators.
+\begin{equation}\begin{aligned}
+	\braket{i | H_\text{H-H} | i} = \sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime, \vec k_1, \vec k_2}} \frac{e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_0|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | \Psi_{\vec k_2}}\bra{\Psi_{\vec k_2}}T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)\\
+	\ket{\Psi_{\vec k_1}}\braket{\Psi_{\vec k_1} | \psi_\text{aux}\left( \vec R_0, \vec a \right)}
+\end{aligned}\end{equation}
+From Bloch's theorem, we have
+\begin{equation}\begin{aligned}
+T\left(\vec R_j - \vec R_m\right)\ket{\Psi_{\vec k_1}} = e^{i \vec{k}_1\cdot\left(\vec{R}_j - \vec R_m\right)}\ket{\Psi_{\vec k_1}}, ~ ~\bra{\Psi_{\vec k_2}}T^\dagger\left(\vec R_j - \vec R_n\right) = \bra{\Psi_{\vec k_2}}e^{-i \vec{k}_2\cdot\left(\vec{R}_j - \vec R_n\right)}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	&\braket{i | H_\text{H-H} | i} \\
-	=& \frac{1}{N} \sum_{\vec R_j, \vec R_m, \vec R_n}\sum_{\vec k_1,\vec k_2} e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right)} e^{i\vec{R}_n\cdot\left(\vec{k}_2 - \vec k\right)} e^{i\vec{R}_m\cdot\left(\vec{k} - \vec k_1\right)} \bra{\psi^0_\text{aux}\left( \vec R_0 \right)} \ket{\vec k_2}\bra{\vec k_2} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\\
-	 &\ket{\vec k_1}\bra{\vec k_1} \ket{\psi^0_\text{aux}\left( \vec R_0 \right)}\\
-	=& \frac{1}{N} \sum_{\vec R_j}\sum_{\vec k_1,\vec k_2} e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right)} N^2 \delta_{\vec{k},\vec k_2} \delta_{\vec{k},\vec k_1} \bra{\psi^0_\text{aux}\left( \vec R_0 \right)} \ket{\vec k_2}\bra{\vec k_2} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\vec k_1}\bra{\vec k_1} \ket{\psi^0_\text{aux}\left( \vec R_0 \right)}\\
-	=& N \sum_{\vec R_j} \braket{\psi^0_\text{aux}\left( \vec R_0 \right) | \vec k}\bra{\vec k} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\vec k}\braket{\vec k | \psi^0_\text{aux}\left( \vec R_0 \right)}\\
+	&\braket{i | H_\text{H-H} | i} =\\
+	& \sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime, \vec k_1, \vec k_2}} \frac{e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right) + i\vec{R}_n\cdot\left(\vec{k}_2 - \vec k\right) + i\vec{R}_m\cdot\left(\vec{k} - \vec k_1\right)}}{|\lambda_0|^2 w^2 N^2}  \braket{\psi_\text{aux}\left( \vec R_0 \right) | \Psi_{\vec k_2}}\bra{\Psi_{\vec k_2}} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\Psi_{\vec k_1}}\braket{\Psi_{\vec k_1} | \psi_\text{aux}\left( \vec R_0 \right)}\\
+	&= \frac{1}{N} \sum_{\vec R_j}\sum_{\vec k_1,\vec k_2} e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right)} N^2 \delta_{\vec{k},\vec k_2} \delta_{\vec{k},\vec k_1} \bra{\psi^0_\text{aux}\left( \vec R_0 \right)} \ket{\vec k_2}\bra{\vec k_2} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\vec k_1}\bra{\vec k_1} \ket{\psi^0_\text{aux}\left( \vec R_0 \right)}\\
+	&= N \sum_{\vec R_j} \braket{\psi^0_\text{aux}\left( \vec R_0 \right) | \vec k}\bra{\vec k} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\vec k}\braket{\vec k | \psi^0_\text{aux}\left( \vec R_0 \right)}\\
 \end{aligned}\end{equation}

### 2022-04-24 notes/notes.tex
--no-message

@@
 	\label{bloch-states}
-	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
-\end{aligned}\end{equation}
-where \(\lambda_{\vec k}\) is a normalisation factor and is defined by \(|\lambda_{\vec k}|^2 = |\braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}|^2 \); \(\ket{\vec k}\) is the momentum eigenstate for momentum \(\vec k\), and \(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
+	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
+\end{aligned}\end{equation}
+where \(\lambda_{\ket{\vec k}}\) is a normalisation factor and is defined by \(|\lambda_{\ket{\vec k}}|^2 = |\braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}|^2 \); \(\ket{\vec k}\) is the momentum eigenstate for momentum \(\vec k\), and \(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
 Becuase of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(w\) choices.
@@
 \begin{equation}\begin{aligned}
-	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
+	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\vec k} w N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\vec k} w N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
+	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} w N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
 	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
 \end{aligned}\end{equation}
-where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
+where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
 This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
@@
 	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
-	&= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
-	&= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-	&= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
-	&= \frac{1}{|\lambda_{\vec k}|^2 w^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
+						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
 \end{aligned}\end{equation}
 At the last step, we used the summation form of the Kronecker delta function: \(\sum_{\vec R_i}e^{i \vec R_i \left( \vec k - \vec q \right) }\sum_{\vec R_j}e^{i \vec R_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\).
-The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \(\vec a, \vec a^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\vec k}\):
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\vec k}|^2 w^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\vec k}|^2 = \frac{1}{|\lambda_{\vec k}|^2 w^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\vec k}|^2 = \delta_{\vec k, \vec k^\prime}
+The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \(\vec a, \vec a^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\ket{\vec k}}\):
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
-	&= \frac{1}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \frac{1}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}
+	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \frac{N}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \frac{N}{|\lambda_{\vec k}|^2 w^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \frac{N}{|\lambda_{\vec k}|^2 w^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\vec k}|^2}\\
+	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 w^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 w^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
 	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}
@@
 \section{Single-particle Green's function}
-In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}} = \ket{\Psi^{n=0}_{\vec k=0}} = \frac{1}{\lambda_0 w N}\sum_{\vec R, \vec a}\ket{\psi_\text{aux}\left( \vec R, \vec a \right)}\) of the bulk Hamiltonian.
+In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}} = \ket{\Psi^{n=0}_{\vec k=\vec k_0}} = \frac{1}{\lambda_{\ket{\vec k_0}} w N}\sum_{\vec R, \vec a}\ket{\psi_\text{aux}\left( \vec R, \vec a \right)}\) of the bulk Hamiltonian.
+Note that \(\vec k_0\) is simply the Bloch momentum of the ground state.
 To obtain Greens functions, we start by calculating real-space matrix elements of the bulk and auxiliary Hamiltonians.
@@
 	\label{diag_mat_ele_1}
-	\braket{i | H_\text{H-H} | i} = \frac{1}{|\lambda_0|^2 w^2 N^2}\sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime}} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi_\text{aux}\left( \vec R_n, \vec a^\prime \right) | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma}  | \psi_\text{aux}\left( \vec R_m, \vec a \right)}
+	\braket{i | H_\text{H-H} | i} = \frac{1}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2}\sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime}} e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi_\text{aux}\left( \vec R_n, \vec a^\prime \right) | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma}  | \psi_\text{aux}\left( \vec R_m, \vec a \right)}
 \end{aligned}\end{equation}
@@
 	&\braket{i | H_\text{H-H} | i} =\\
-	&\sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_0|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma}  T\left( \vec R_0 - \vec R_m \right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}
+	&\sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma}  T\left( \vec R_0 - \vec R_m \right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}
 \end{aligned}\end{equation}
@@
 	&\braket{i | H_\text{H-H} | i} \\
-	&= \sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_0|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime\right) | T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}
+	&= \sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime\right) | T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = \sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime, \vec k_1, \vec k_2}} \frac{e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_0|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | \Psi_{\vec k_2}}\bra{\Psi_{\vec k_2}}T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)\\
+	\braket{i | H_\text{H-H} | i} = \sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime, \vec k_1, \vec k_2}} \frac{e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | \Psi_{\vec k_2}}\bra{\Psi_{\vec k_2}}T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)\\
 	\ket{\Psi_{\vec k_1}}\braket{\Psi_{\vec k_1} | \psi_\text{aux}\left( \vec R_0, \vec a \right)}
@@
 	&\braket{i | H_\text{H-H} | i} =\\
-	& \sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime, \vec k_1, \vec k_2}} \frac{e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right) + i\vec{R}_n\cdot\left(\vec{k}_2 - \vec k\right) + i\vec{R}_m\cdot\left(\vec{k} - \vec k_1\right)}}{|\lambda_0|^2 w^2 N^2}  \braket{\psi_\text{aux}\left( \vec R_0 \right) | \Psi_{\vec k_2}}\bra{\Psi_{\vec k_2}} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\Psi_{\vec k_1}}\braket{\Psi_{\vec k_1} | \psi_\text{aux}\left( \vec R_0 \right)}\\
-	&= \frac{1}{N} \sum_{\vec R_j}\sum_{\vec k_1,\vec k_2} e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right)} N^2 \delta_{\vec{k},\vec k_2} \delta_{\vec{k},\vec k_1} \bra{\psi^0_\text{aux}\left( \vec R_0 \right)} \ket{\vec k_2}\bra{\vec k_2} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\vec k_1}\bra{\vec k_1} \ket{\psi^0_\text{aux}\left( \vec R_0 \right)}\\
-	&= N \sum_{\vec R_j} \braket{\psi^0_\text{aux}\left( \vec R_0 \right) | \vec k}\bra{\vec k} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\vec k}\braket{\vec k | \psi^0_\text{aux}\left( \vec R_0 \right)}\\
+	& \sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime, \vec k_1, \vec k_2}} \frac{e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right) + i\vec{R}_n\cdot\left(\vec{k}_2 - \vec k\right) + i\vec{R}_m\cdot\left(\vec{k_0} - \vec k_1\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2}  \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | \Psi_{\vec k_2}}\bra{\Psi_{\vec k_2}} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\Psi_{\vec k_1}}\\
+	&\times\braket{\Psi_{\vec k_1} | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+	&= \frac{1}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \sum_{\vec R_j, \vec a, \vec a^\prime \atop{\vec k_1,\vec k_2}} N^2 \delta_{\vec{k_0},\vec k_2} \delta_{\vec{k_0},\vec k_1} \braket{\psi^0_\text{aux}\left( \vec R_0, \vec a^\prime \right) | \Psi_{\vec k}}\bra{\Psi_{\vec k_0}} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\Psi_{\vec k_0}}\braket{\Psi_{\vec k_0} | \psi^0_\text{aux}\left( \vec R_0, \vec a \right)}\\
+	&= \frac{1}{|\lambda_{\ket{\vec k_0}}|^2 w^2} \sum_{\vec a, \vec a^\prime} \braket{\psi^0_\text{aux}\left( \vec R_0, \vec a \right) | \Psi_{\vec k_0}} \braket{\Psi_{\vec k_0} | \psi^0_\text{aux}\left( \vec R_0, \vec a \right)} \sum_{\vec R_j} \bra{\Psi_{\vec k_0}} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\Psi_{\vec k_0}}\\
+	&= \frac{|\lambda_{\ket{\Psi_\text{gs}}}|^2}{|\lambda_{\ket{\vec k_0}}|^2}\sum_{\vec R_j} \bra{\Psi_\text{gs}} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\Psi_\text{gs}}\\
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = N |\braket{\psi^0_\text{aux}\left( \vec R_0 \right) | \vec k}|^2 \bra{\vec k} \sum_{\vec R_j} c_{\sigma}\left(\vec R_j\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left(\vec R_j\right)\ket{\vec k}
-\end{aligned}\end{equation}
-Even though it is computationally easier to consider the state \(\ket{\vec k}\) as the momentum eigenstates of the tight-binding kind, there is a more illuminating interpretation of this expression if we consider them as the eigenstates \(\ket{\Phi\left( \vec k \right) }\) of the full bulk model.
-With this choice, the expression can be seen as the sum of effects of creating a single-particle excitation \(c^\dagger_\sigma\) on the ground state \(\ket{\Psi_\text{gs} }\), at increasingly larger distances \(\vec R_j\) from the auxiliary model at \(\vec R_0\).
+	\braket{i | H_\text{H-H} | i} = \frac{|\lambda_{\ket{\Psi_\text{gs}}}|^2}{|\lambda_{\ket{\vec k_0}}|^2}\sum_{\vec R_j} \bra{\Psi_\text{gs}} c_{\vec R_j,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_j,\sigma}\ket{\Psi_\text{gs}}
+\end{aligned}\end{equation}
+This expression can be seen as the sum of effects of creating a single-particle excitation \(c^\dagger_\sigma\) on the ground state \(\ket{\Psi_\text{gs} }\), at increasingly larger distances \(\vec R_j\) from the auxiliary model at \(\vec R_0\).
 The excitation is made to evolve through the auxiliary model \(\mathcal{H}_\text{aux}\left( \vec R_0 \right) \) centred at \(\vec R_0\).
@@
 However, since we are describing the excitation of the bulk ground state using an auxiliary model Hamiltonian, we also need to multply this with the fidelity between the full ground state and the auxiliary model ground state.
-That is taken care of by the inner-product multiplying the matrix element.
-That inner product can be thought of as an overlap between a separable state and an entangled state - the full Hamiltonian state is obtained by entangling the overlapping auxiliary models, while the single auxiliary model groundstate is the separable state in this context.
-The inner product then becomes a measure of entanglement of the bulk ground state - the more the overlap with the separable state, the lower the entanglement: \(\varepsilon(\vec R_0,\vec k) \equiv 1 - |\braket{\psi^0_\text{aux}\left(  \right) | \Phi_0(\vec k)}|^2\).
+That is taken care of by the inner-product in the numerator multiplying the matrix element.
+That inner product can be thought of as an overlap between a separable state and an entangled state - the full Hamiltonian state is obtained by entangling the overlapping auxiliary models, while the single auxiliary model ground state is the separable state in this context.
+The inner product in the numerator then becomes a measure of entanglement of the bulk ground state - the more the overlap with the separable state, the lower the entanglement: \(\varepsilon(\vec R_0,\Psi_\text{gs}) \equiv 1 - |\braket{\psi^0_\text{aux}\left(\vec R_0\right) | \Psi_\text{gs}}|^2 \).
+The inner product in the denominator is also an entanglement: \(\varepsilon(\vec R_0, \ket{\vec k}) = 1 - |\braket{\psi^0_\text{aux}\left(\vec R_0\right) | \ket{\vec k}}|^2\).
+This can be thought of as the entanglement within each auxiliary model ground state, with the momentum eigenstates \(\ket{\vec k}\) acting as the separable states.
 \begin{equation}\begin{aligned}
@@
 \section{Important Remarks}
+\subsection{Entanglement as an order parameter for the transition}
+The spectral weights in the diagonal Greens function can be written in terms of a geometric measure of entanglement:
+\begin{equation}\begin{aligned}
+	d_n^p = \braket{\Phi_n | c^\dagger_{d\sigma} | \Phi_0} = \braket{\Phi_n | c^\dagger_{d\sigma} \sum_n \ket{\phi_m} \bra{\phi_m} | \Phi_0}
+\end{aligned}\end{equation}
+where, \(\ket{\phi_m}\) are the eigenstates of the Hamiltonian composed of a two-site system (formed by the impurity site and the zeroth site) in direct product with the rest of the lattice sites.
+The two site system interacts only via a spin-exchange coupling \(J\), and the impurity and bath sites have local correlations \(U\) and \(U_b\) respectively.
+The ground state is the spin-singlet in direct product with the ground state of the tight-binding chain formed by the remaining sites.
+The summation involves inner products of the ground state \(\ket{\Phi_0}\) with the eigenstates \(\ket{\phi_m}\).
+Only two states out of all \(\ket{\phi_m}\) give non-zero overlap - the spin singlet state \(\ket{SS}\) and the charge triplet-zero state \(\ket{CT}\).
+These two non-zero overlaps give rise to non-zero entanglement: \(\varepsilon_\text{SS} = 1 - |\braket{\Phi_0 | SS}|^2, \varepsilon_\text{CT} = 1 - |\braket{\Phi_0 | CT}|^2\).
+The spectral weight becomes
+\begin{equation}\begin{aligned}
+	d_n^p = \bra{\Phi_n} | c^\dagger_{d\sigma} \left(\ket{SS} + \ket{CT} \right) \left(\sqrt{1 - \varepsilon_\text{SS}} + \sqrt{1 - \varepsilon_\text{CT}}\right)
+\end{aligned}\end{equation}
+The total spectral weight can be written as
+\begin{equation}\begin{aligned}
+	|d_n^p|^2 = |\bra{\Phi_n} | c^\dagger_{d\sigma} \left(\ket{SS} + \ket{CT} \right)|^2 \left(2 - \varepsilon_\text{SS} - \varepsilon_\text{CT} + 2\sqrt{1 - \varepsilon_\text{SS}}\sqrt{1 - \varepsilon_\text{CT}}\right)
+\end{aligned}\end{equation}
+Near the metal, the ground state is, to a very good approximation, the state \(\ket{SS}\).
+One can then say that the entanglement \(\varepsilon_\text{SS}\) is poor - the entangled state is very close to the "separable" state.
+The term separable is used here in the sense that the metallic state defines a limit of the system.
+As \(U_b\) increases, the e
+
 \subsection{Topological nature of the transition}

### 2022-04-28 gen-siam-manuscript/notes.tex
Added k-space self-energy to notes

--- 2022-04-24 notes/notes.tex
@@
 That inner product can be thought of as an overlap between a separable state and an entangled state - the full Hamiltonian state is obtained by entangling the overlapping auxiliary models, while the single auxiliary model ground state is the separable state in this context.
-The inner product in the numerator then becomes a measure of entanglement of the bulk ground state - the more the overlap with the separable state, the lower the entanglement: \(\varepsilon(\vec R_0,\Psi_\text{gs}) \equiv 1 - |\braket{\psi^0_\text{aux}\left(\vec R_0\right) | \Psi_\text{gs}}|^2 \).
-The inner product in the denominator is also an entanglement: \(\varepsilon(\vec R_0, \ket{\vec k}) = 1 - |\braket{\psi^0_\text{aux}\left(\vec R_0\right) | \ket{\vec k}}|^2\).
+The inner product in the numerator then becomes a measure of entanglement of the bulk ground state - the more the overlap with the separable state, the lower the entanglement: \(\varepsilon(\ket{\Psi_\text{gs}}) \equiv 1 - |\braket{\psi^0_\text{aux}\left(\vec R_0\right) | \Psi_\text{gs}}|^2 \).
+The inner product in the denominator is also an entanglement: \(\varepsilon( \ket{\vec k}) = 1 - |\braket{\psi^0_\text{aux}\left(\vec R_0\right) | \ket{\vec k}}|^2\).
 This can be thought of as the entanglement within each auxiliary model ground state, with the momentum eigenstates \(\ket{\vec k}\) acting as the separable states.
 \begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = N \left( 1 - \varepsilon(\vec R_0,\vec k) \right) \bra{\Phi_0(\vec k)} \sum_{\vec R_j} c_{\sigma}\left(\vec R_j\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left(\vec R_j\right)\ket{\Phi_0(\vec k)}
+	\braket{i | H_\text{H-H} | i} = \frac{1 - \varepsilon\left( \ket{\Psi_\text{gs}}\right)}{1 - \varepsilon\left( \vec k\right)}\sum_{\vec R_j} \bra{\Psi_\text{gs}} c_{\vec R_j,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_j,\sigma}\ket{\Psi_\text{gs}}
 \end{aligned}\end{equation}
@@
 On the other hand, when the entanglement is low, any single auxiliary model provides a large contribution, which can be understood from the fact that any single auxiliary model is sufficient to describe the full ground state.
+The numerator, therefore, is maximum in the metal and minimum (zero) in the insulator.
+Similarly, the denominator is minimum in the metal.
+This is because, in the metal, the auxiliary model ground states are delocalised, so the entanglement between multiple \(\vec k\)-states will be lower compared to the insulating phase, where the ground state is completely localised.
+This shows the entire fraction in front is maximum in the metal and minimum (zero) in the insulator.
 
@@
 
-\section{Important Remarks}
+\section{\(k-\)space picture of the MIT in terms of the momentum-resolved self-energy \(\Sigma(\vec k,\omega)\)}
+
+From the self-energy expressions obtained above, one can track the self-energy of the lattice model through the metal-insulator transition.
+In fig.~\ref{four-self}, we have provided these plots at specific values of \(U_b/J\) to show how the transition plays out in the Brillouin zone.
+{\it These plots can also be viewed as a video \href{https://abhirup-m.github.io/misc-sigma/}{\underline{here}}.}
+
+\begin{center}
+\begin{tabular}{c|c}
+\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.02500-4.pdf} &
+\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.10310-4.pdf}\\
+\hline
+\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.15735-4.pdf} &
+\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.23594-4.pdf}\\
+\hline
+\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.25000-4.pdf} &
+\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=0.25010-4.pdf}
+\end{tabular}
+\captionof{figure}{Each of the 6 frames shows \(A(\vec k)\) at four values of \(\omega\).
+First 4 are before the transition (\(-U_b/J < 0.25\)), fifth is exactly at the transition \((-U_b/J = 0.25)\) and last one is after the transition (\(-U_b/J > 0.25\)).
+Available as video \href{https://abhirup-m.github.io/misc-sigma/}{\underline{here}}.}
+\label{four-self}
+\end{center}
+
+In each frame, the top left figure represents the self-energy at \(\omega=0\).
+If we track this particular figure across the frames, we find that at small \(-U_b/J\), the self-energy near the Fermi surface was smaller than those near the Brillouin zone edges, indicating the presence of a prominent Fermi liquid.
+As \(U_b\) increases, we find that this distinction of the Fermi surface becomes less-prominent; at the critical point,we see that the self-energy near the Fermi surface self-energy has become more than that near the edges, signalling that the quasiparticle excitations have become scrambled because of the increased correlations in the bath.
+
+If we, on the other hand, track the bottom right figure in each frame (\(\omega = U/2\)), we find that deep in the metallic regime, the self-energy is quite high.
+This is because of the low spectral weight at large \(\omega\).
+As the correlations are increased, we find that  this self-energy decreases, particular in comparison to the values at the Brillouin zone edges.
+This is because of the appearance of the Hubbard side-peaks in the local spectral function
+.
+
+In the insulating phase, we find that the momentum-dependence has vanished (the system is in the perfectly local atomic limit).
+The self-energy at the Hubbard side-bands (bottom right) is high, because the quasiparticle excitations are highly-renormalised and the single-particle picture description is not possible.
+The self-energy inside the gap (other three figures) diverges and the poles of the Greens function have been replaced by zeroes, so we have instead plotted the inverse self-energy.
+
+These plots are available as videos \href{https://abhirup-m.github.io/misc-sigma/}{\underline{here}}.
+
+\clearpage
+\section{Some important remarks}
 \subsection{Entanglement as an order parameter for the transition}
@@
 The term separable is used here in the sense that the metallic state defines a limit of the system.
-As \(U_b\) increases, the e
+As \(U_b\) increases, \(\varepsilon_\text{SS}\) increases.
+On the other hand, the entanglement with the charge triplet is maximum in the metal, because the ground state does not have much of the charge triplet.
+Towards the MIT, this contribution increases, and the entanglement decreases.
 

### 2022-04-28 gen-siam-manuscript/gen-siam.tex
started shaping manuscript

--- 2022-04-23 notes/notes.tex
@@
-\documentclass{report}
-% \documentclass{nature}
-\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk,pifont,enumitem}
-% \usepackage[draft]{graphicx}
-\usepackage{graphicx}
+\documentclass[reprint,prb,superscriptaddress]{revtex4-2}
+\usepackage{braket,amsmath,graphicx,float,color,ulem,soul,lipsum}
 \usepackage[hidelinks]{hyperref}
-\usepackage[margin=0.5in,top=0.3in,bottom=1.4in]{geometry}
-
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-
-\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}
-\newlist{todolist}{itemize}{2}
-\setlist[todolist]{label=$\square$}
-\newcommand{\cmark}{\ding{51}}%
-
-\newcommand{\comment}[1]{{}}
-\renewcommand{\arraystretch}{2}
-\setlength\delimitershortfall{-2pt}
-\setcounter{tocdepth}{1}
-\pagestyle{headings}
-\setlength{\headheight}{52pt}
-\numberwithin{equation}{section}
-\allowdisplaybreaks
-\bibliographystyle{ieeetr}
-
-\title{A New Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Systems}
-\author{Abhirup Mukherjee, Siddhartha Lal}
-\affil{Indian Institute of Science Education and Research Kolkata, Mohanpur}
+\bibliographystyle{apsrev4-1}
+\begin{document}
+
+\title{Local metal-insulator transition in a generalised impurity Anderson model}
+\author{Abhirup Mukherjee}
+\email{am18ip014@iiserkol.ac.in }
+\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
+\author{Siddhartha Lal}
+\email{slal@iiserkol.ac.in}
+\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
+
 \date{\today}
 
-\begin{document}
+\begin{abstract}
+
+\end{abstract}
+
 \maketitle
-\tableofcontents
-\newpage
-\chapter{Introduction}
-
-\section{What is the minimal impurity model for a Mott metal-insulator transition?}
-\label{sec:min_model}
+
+%\tableofcontents
+
+\section{Introduction}
+
 The Hubbard model is one of the fundamental models for strong electronic correlation; in its simplest form, it features a single band of conduction electrons hopping on a lattice and interacting via local correlations that provide a cost \(U\) if any site is doubly occupied:
@@
 For eg, a correlated impurity interacting with a conduction bath is a potential auxiliary model for the Hubbard Hamiltonian:
-\begin{equation}
-\label{clus_bath_siam}
-\mathcal{H}_\text{SIAM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow} - t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)
-\end{equation}
 The impurity has onsite energy \(\epsilon_d\) and an onsite correlation \(U\). It hybridises into the bath through \(V\).
@@
 \includegraphics[width=0.5\textwidth]{../figures/dos_diff.pdf}
-\caption{Various kinds of bath that an impurity can hybridise into.
+\caption{Two kinds of bath that an impurity can hybridise into.
 The left panel shows a non-interacting conduction band with a flat density of states.
@@
 
-\section{Philosophy of auxiliary model methods}
-The present method is a realisation of the general method of using simpler systems called auxiliary models to study bulk systems~\cite{martin_2016}.
-In general, a full Hamiltonian can be separated into the Hamiltonians for a particular subsystem \(S\), the rest of the system \(R\), and the interactions between \(S\) and \(R\).
-\begin{equation}\begin{aligned}
-	\mathcal{H} = \mathcal{H}_S\ket{S}\bra{S} + \mathcal{H}_R \ket{R}\bra{R} + \mathcal{H}_{SR} \ket{S}\bra{R} + \mathcal{H}_{RS}\ket{S}\bra{R} = \begin{bmatrix} & \mathcal{H}_{R} && \mathcal{H}_{RS} & \\ & \mathcal{H}_{RS}^* && \mathcal{H}_{S} & \end{bmatrix}
-\end{aligned}\end{equation}
-where \(\ket{S}\) and \(\ket{R}\) actually represents sums over all basis kets of \(S\) and \(R\) respectively.
-As an example, we can split the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows (fig.~\ref{cluster-bath}):
-\begin{equation}\begin{aligned}
-	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_S} + \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_R}\\
-		      & -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{SR} + H_{RS}}\\
-\end{aligned}\end{equation}
-The Greens function of the full Hamiltonian can also be split in a similar fashion:
-\begin{equation}\begin{aligned}
-	G(\omega) = \begin{bmatrix} G_S && G_{SR} \\ G_{RS} && G_R \end{bmatrix}
-\end{aligned}\end{equation}
-Each Greens function can be written in terms of the non-interacting counterpart and the self-energy through the Dyson equation: \(\Sigma_i = 1/G_{i,0} - 1/G_i\).
-
-The subsystem \(S\) is usually taken to be the "cluster", and consequently, \(R\) represents the "bath".
-The smaller system is typically chosen such that its eigenstates are known exactly.
-Progress is then made by choosing a simpler version of \(H_R\) and a simpler form also for its coupling \(H_{RS}\) with the smaller system.
-This combination of the cluster and the simpler bath is then called the \textit{auxiliary system}.
-A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{RS}\).
-Such a construction is shown in fig.~\ref{cluster-bath}.
+\section{The generalised Anderson impurity model}
+
+The impurity models we will work with couple the impurity to a single site in the lattice.
+We will refer to that specific site as the zeroth site throughout.
+We recall the Hamiltonian of the Anderson impurity model with a half-filled impurity site:
+\begin{equation} 
+	\mathcal{H} = \frac{- U}{2} \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\vec k,\sigma} \epsilon_{\vec k} \tau_{\vec k,\sigma} + V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)~,
+ \end{equation}
+where \(\tau_{\vec k,\sigma} \equiv \hat n_{\vec k,\sigma} - 1/2\).
+Also, \(c_{d\sigma}\) and \(c_{0\sigma}\) are the fermionic annihilation operators of spin \(\sigma\) for the impurity and zeroth sites respectively.
+\(U\) is the repulsive correlation on the impurity site, and the impurity is at particle-hole symmetry.
+\(V\) is the momentum-independent hybridisation parameter that couples the impurity with the lattice.
+We will work with a constant density of states in the bath.
+
+In order to enhance the Anderson impurity model, we introduce two extra two-particle interaction terms into the Hamiltonian:
+\begin{itemize}
+	\item a spin-exchange term \(J \vec{S}_d\cdot\vec{s}_0\) between the impurity and the zeroth site 
+	\item a local correlation term \(U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}\) on the zeroth site
+\end{itemize}
+
+The full generalised Anderson model Hamiltonian, at particle-hole symmetry, is
+\begin{equation}\begin{aligned}
+	\mathcal{H} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} + \epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} + K \vec{C_d}\cdot\vec{C}
+\end{aligned}\end{equation}
+
 \begin{figure}[!htb]
 	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/cluster-bath.pdf}
-	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$.
-\textit{Right}: Extraction of the auxiliary (cluster+bath) system from the full lattice.
-The central site on left becomes the impurity site (red) on the right (with an onsite repulsion $\epsilon_d$), while the rest of the $N-1$ sites on the left form a conduction bath (green circles) (with dispersion $\epsilon_k$ and correlation modelled by the self-energy $\Sigma_k(\omega)$) that hybridizes with the impurity through the coupling $V$.}
-	\label{cluster-bath}
-\end{figure}
-\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model}.
-To allow computing quantities, one would need to make the bath (which is a much larger system) simpler than the cluster (which is a single site).
-This distinction breaks the translational symmetry of the Hubbard model.
-For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath does not means we have broken the symmetry between the cluster and the bath.
-
-\subsection*{Dynamical mean-field theory - an example of an auxiliary model approach}
-Dynamical mean-field theory is an approximation scheme that use impurity models to obtain Greens functions of bulk systems of strong correlation~\cite{kotliar1996,kotliar1992}.
-The essential idea is to find the most suitable impurity model that replicates the full Hamiltonian.
-This is done through the following algorithm.
-Given a bulk Hamiltonian with on=site correlation \(U\) and a non-interacting \(k-\)space Greens function \(G_{k,0}\) for the bath:
-\begin{itemize}
-	\item[1.] We first create an impurity model with on-site correlation \(U\) and non-interacting impurity Greens function \(G_{i,0} = \sum_k G_{k,0}\).
-		\[\mathcal{H}_\text{aux} = H_\text{imp}(U) -t \sum_\sigma \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + H_\text{bath}\left(t,G_{i,0}\right)\]
-
-	\item[2.] This impurity model is solved using some method like numerical renormalisation group, and the self-energy \(\Sigma_\text{aux}\) of the impurity is obtained.
-
-	\item[3.] The impurity self-energy is now {\it equated} with the bath momentum-space self-energy:
-		\[\Sigma_{k}(\omega) = \Sigma_\text{aux}(\omega)\]
-		Since the impurity is purely local, this is an approximation that involves replacing a non-local quantity by its purely local component: \(\Sigma_{k}(\omega) = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}}\Sigma_{\vec r}(\omega) \simeq \Sigma_{\vec r = 0}(\omega)\).
-This approximation is a result of the single-site nature of the cluster of the chosen auxiliary model - larger clusters with more impurities can generate non-local components.
-This local approximation becomes exact in the limit of large system dimension \(w\), because it can be shown that the non-local components of the self-energy scale as \(w^{-3/2}\).
-
-	\item[4.] With this updated bath self-energy, we now create a new \(k-\)space Greens function for the bath:
-		\[G_{i}(\omega) = \sum_k G_{k}(\omega) = \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_k(\omega)} = \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_\text{aux}(\omega)}\]
-	This interacting Greens function is then used to obtain the updated non-interacting Greens function, using Dyson's equation:
-	\[G_{i,0} = \frac{1}{1/G_{i} + \Sigma_\text{aux}}\]
-	\item[5.] Repeat the algorithm from step 1 with the updated \(G_{i,0}\), until \(\Sigma_\text{aux}\) stops changing.
-\end{itemize}
-The stopping condition is the consistency relation that makes the bath and impurity self-energies equal.
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/dmft.pdf}
-\end{figure}
-
-\section{A "bottoms-up" approach to using auxiliary models}
-As mentioned in the previous section, the question we are posing is the following: what is the simplest auxiliary model of impurity in a bath that can capture the metal-insulator transition in a Hubbard-like model of correlated electrons.
-We approach this problem in a constructionist/bottoms-up way: we first identity an appropriate quantum impurity model (fig.~\ref{cluster-bath}) that shows an impurity phase transition, and then create a bulk model out of this auxiliary model.
-The bulk model hence created will then show a metal-insulator transition.
-The impurity models are studied using the recently-developed unitary renormalisation group method~\cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome}, and this analysis is shown in chapters~\ref{chap:urg1}~and~\ref{siam-attr-chap}.
-The leap to the bulk model is then made by applying lattice translation operators on the auxiliary model.
-This process is shown in chapter~\ref{chap:tile}.
-This process, referred to as tiling here, relates the auxiliary model Hamiltonian with that of the bulk, and hence allows connecting the Greens functions and other related quantities across dimensions.
-One nice outcome is that since the auxiliary model has multiple sites, there is a real-space off-diagonal component of the self-energy, and this leads to a \(k-\)dependence in the self-energy of the bulk, which is in contrast with the lack of \(k-\)dependence in single-site DMFT.
-
-In our approach, the auxiliary models can be chosen in various ways. The simplest choice is of course the single-impurity Anderson model of eq.~\ref{clus_bath_siam}:
-\begin{equation}
-\mathcal{H}_\text{SIAM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow} - t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)
-\end{equation}
-This model does not show any impurity phase transition - the impurity is always screened~\cite{hrk_wilson_1980,wilson1975,bullaNRGreview}.
-Correlation can be introduced into the auxiliary model in two ways:
-\begin{itemize}
-	\item[1.] The impurity or the bath can be made to have additional interaction: 
-\begin{gather}
-\mathcal{H}_\text{aux} = H_\text{SIAM} + J \vec{S}_d\cdot\vec{s}_0\\
-\mathcal{H}_\text{aux} = H_\text{SIAM} + J \vec{S}_d\cdot\vec{s}_0 - U_b \left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
-\end{gather}
-The first example has a spin-exchange interaction between the impurity site and the zeroth site, while the second example additionally has a correlation locally on the zeroth site.
-\item[2.] The second method is to make the cluster itself more complicated. That is, one can introduce multiple impurity sites that are connected via the hopping:
-\begin{equation}
-\mathcal{H}_\text{aux} = -\frac{U}{2}\sum_{d_i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right) ^2 + V\sum_{d_i}\sum_\sigma\left( c^\dagger_{d_i\sigma}c_{0\sigma} + \text{h.c.} \right) + \text{K.E.} - t\sum_{\sigma}\left(c^\dagger_{d_1\sigma}c_{d_2\sigma} + \text{h.c.}\right)
-\end{equation}
-
-\end{itemize}
-
-\begin{figure}[!htb]
- 	\centering
- 	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.pdf}
- 	\caption{Cluster+bath construction of auxiliary model.
-It consists of a cluster (red square) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink).
-The other sites (green) form the rest of the bath.
-Just the cluster and the zeroth site have onsite correlations.}
- \end{figure}
- The next step in the programme is to tile the real-space lattice with this cluster+bath Hamiltonian \(\tilde H\) to restore translational invariance (shown in a later section), and obtain a new bulk Hamiltonian for correlated electrons, $\tilde H = T\left[ \mathcal{H}_\text{aux} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the cluster-bath (auxiliary model) Hamiltonian to span the target real-space lattice.
-Given a general auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}\), the result of tiling can be written very generally as
- \begin{equation}\begin{aligned}
-	 \tilde H = \sum_{\left\{i_1,i_2,...\right\}} \mathcal{H}_\text{aux}\left(\left\{i_1,i_2,...\right\}\right)
- \end{aligned}\end{equation}
-where \(\left\{i_1,i_2,...\right\}\) represents the indices for the members of the cluster.
-To reiterate, what that means is that we have placed the cluster+bath system at all lattice point sets \(\left\{i_1,i_2,...\right\}\) to reconstruct a new model of correlated electrons.
-The answer to how closely $\tilde H$ approximates a target model of correlated electrons lies in (i) the choice of the cluster-bath construction of the auxiliary model, and (ii) the accuracy of the URG procedure on the auxiliary model.
-
-\chapter{Physics of the generalised single-impurity Anderson model}
-\label{chap:urg1}
-\section{Introduction of spin-exchange and charge isospin-exchange interactions into the SIAM: the generalised SIAM}
-We will now study the generalised SIAM obtained by introducing spin-exchange and charge isospin-exchange interactions between the impurity and the conduction bath~\cite{zitko_2006}.
-Such terms are generated when one does a Schrieffer-Wolff transformation on the SIAM, but we will find it prudent to keep these terms in the bare model itself.
-
-The spin-exchange interaction has the form
-\begin{equation}\begin{aligned}
-	J \vec{S_d}\cdot\vec{s} = J \left[S_d^z s^z + \frac{1}{2}\left( S_d^+ s^- + S_d^- s^+ \right) \right] ~,
-\end{aligned}\end{equation}
-where \(\vec S_d = \left(S_d^x, S_d^y, S_d^z\right) = \sum_{\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{d\alpha}c_{d\beta}\) is the impurity spin operator, \(\vec s = \sum_{kk^\prime\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{k\alpha}c_{k^\prime\beta}\) is the spin operator for the conduction bath and \(J\) is the spin-exchange coupling.
-The bath spin operator actually acts locally, as can be seen by Fourier transforming to real space (using the definition \(f(k) = \frac{1}{\sqrt N}\sum_r g(r)\exp(ikr)\)):
-\begin{equation}\begin{aligned}
-	\vec s = \sum_{k k^\prime r r^\prime} \frac{1}{N} e^{ikr - ik^\prime r^\prime} \vec \sigma_{\alpha\beta} c^\dagger_{r\alpha} c_{r^\prime\beta} = \sum_{rr^\prime}\frac{1}{N}\vec \sigma_{\alpha\beta} c^\dagger_{r\alpha} c_{r^\prime\beta} N \delta(r)\delta(r^\prime) = \vec \sigma_{\alpha\beta} c^\dagger_{0\alpha} c_{0\beta}
-\end{aligned}\end{equation}
-
-In order to introduce the charge isospin coupling, we define the Nambu spinor \cite{anderson1958random,nambu_1960} \(\psi^k = \left( c_{k\uparrow} \quad c^\dagger_{k\downarrow} \right)\), and the charge isospin \cite{zitko_2006} for the mobile conduction electrons
-\begin{equation}\begin{aligned}
-\vec C = \sum_{kk^\prime} {\psi^k}^\dagger \vec S \psi^{k^\prime} = \frac{1}{2}\sum_{kk^\prime\alpha\beta} {\psi^k_\alpha}^\dagger \vec \sigma_{\alpha\beta} \psi^{k^\prime}_\beta
-\end{aligned}\end{equation}
-The various components of the isospin are
-\begin{equation}\begin{aligned}
-	C^z &= \sum_{kk^\prime\sigma}\frac{1}{2} {\psi^k_\sigma}^\dagger \sigma^z_{\sigma\sigma} \psi^{k^\prime}_\sigma = \frac{1}{2}\sum_{kk^\prime\sigma}\left(c^\dagger_{k\sigma}c_{k^\prime \sigma} - \frac{1}{2}\delta_{kk^\prime}\right)\label{diagonalCz}\\
-	C^x &= \sum_{kk^\prime\sigma}\frac{1}{2} {\psi^k_\sigma}^\dagger \sigma^x_{\sigma\overline\sigma} \psi^{k^\prime}_{\overline\sigma} = \sum_{kk^\prime\sigma} \frac{\sigma}{4}\left( c^\dagger_{k\sigma}c^\dagger_{k^\prime\overline\sigma} + \text{h.c.} \right) \\
-	C^y &= \sum_{kk^\prime\sigma}\frac{1}{2} {\psi^k_\sigma}^\dagger \sigma^y_{\sigma\overline\sigma} \psi^{k^\prime}_{\overline\sigma} = \sum_{kk^\prime\sigma} - \frac{i\sigma}{4}\left( c^\dagger_{k\sigma}c^\dagger_{k^\prime\overline\sigma} - \text{h.c.} \right)\\
-\end{aligned}\end{equation}
-It is easy to verify that these operators satisfy the SU(2) commutation algebra.
-For example, if we write \(C^x = A + A^\dagger\) and \(C^y = B + B^\dagger\), then \(\left[ C^x, C^y \right] = \left[ A, B^\dagger \right] - \text{h.c.}\), where
-\begin{equation}\begin{aligned}
-	\left[ A, B^\dagger \right] = \frac{1}{4}\sum_{kk^\prime,qq^\prime}\left[ c^\dagger_{k\uparrow}c^\dagger_{k^\prime \downarrow}, i c_{q^\prime \downarrow}c_{q \uparrow} \right] = \frac{i}{4}\sum_{kq}\left(c^\dagger_{k\uparrow}c_{q \uparrow} - c_{k \downarrow}c^\dagger_{q \downarrow}\right)
-\end{aligned}\end{equation}
-and therefore
-\begin{equation}\begin{aligned}
-	\implies \left[ C^x, C^y \right] = \frac{i}{2}\sum_{kq}\left(c^\dagger_{k\uparrow}c_{q \uparrow} - c_{k \downarrow}c^\dagger_{q \downarrow}\right) = i C^z
-\end{aligned}\end{equation}
-There are similar operators for the impurity electron:
-\begin{equation}\begin{aligned}
-	\psi_d = \left( c_{d\uparrow} \quad c^\dagger_{d\downarrow}\right), &&\vec C_d = \frac{1}{2}\sum_{\beta} {\psi_{d,\alpha}}^\dagger \vec \sigma_{\alpha\beta} \psi_{d,\beta}
-\end{aligned}\end{equation}
-The full charge-Kondo interaction can now be written down in terms of these isospins:
-\begin{equation}\begin{aligned}
-	K \vec{C_d}\cdot\vec{C} = K \left[C_d^z C^z + \frac{1}{2}\left(C_d^+ C^-+ C_d^- C^+\right)\right]
-\end{aligned}\end{equation}
-where \(C^\pm \equiv C^x \pm iC^y\).
-\begin{equation}\begin{aligned}
-	C^+ = \sum_{kk^\prime} c^\dagger_{k\uparrow}c^\dagger_{k^\prime\downarrow}, && C^- = \sum_{kk^\prime}c_{k^\prime\downarrow}c_{k\uparrow}
-\end{aligned}\end{equation}
-The full generalised Anderson model Hamiltonian, at particle-hole symmetry, is
-\begin{equation}\begin{aligned}
-	\mathcal{H} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} + \epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} + K \vec{C_d}\cdot\vec{C}
-\end{aligned}\end{equation}
-
-For the URG analysis, at each RG step, we decouple the electronic states \(q\beta\) on the \(k-\)space shell of radius\(\Lambda_j\).
-For simplicity, we will only consider those diagonal terms in the denominator that either have both \(q\beta\) and \(q\overline\beta\) or  both \(q\beta\) and \(d\) or both \(q\overline\beta\) and \(d\).
-Terms that have purely \(q\overline\beta\) will not be considered.
-Also, the scattering between just \(d\) and \(q\overline\beta\) can be ignored since it is diagonal in \(q\beta\).
-The diagonal (number-preserving) part is
-\begin{equation}\begin{aligned}
-	H_D = \sum_\beta\epsilon_q\tau_{q\beta} + \epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + J S^z_ds^z_{q} + K C^z_d C^z_q\\
-\end{aligned}\end{equation}
-where \(s_q^z = \frac{1}{2}\left(\hat n_{q\uparrow} - \hat n_{q\downarrow}\right)\) and \(C_q^z = \frac{1}{2}\left(\hat n_{q \uparrow} + \hat n_{q \downarrow} - 1\right)\). The off-diagonal part is:
-\begin{equation}\begin{aligned}
-	H_X = \sum_{\beta=\uparrow,\downarrow}\left[V c^\dagger_{d\beta}c_{q\beta} + \frac{1}{2}J \sum_{k<\Lambda_N}\left\{\left(\hat n_{d \beta} - \hat n_{d \overline\beta}\right) \frac{1}{2} c^\dagger_{k\beta}c_{q\beta} + c^\dagger_{d\beta}c_{d\overline\beta}c^\dagger_{k\overline\beta}c_{q \beta}\right\} + \frac{1}{2}K \sum_{k<\Lambda_N}\left\{\left(\hat n_d -1\right)\frac{1}{2}c^\dagger_{k\beta}c_{q\beta} + \right.\right.\\
-\left.\left.c^\dagger_{d\beta}c^\dagger_{d\overline\beta}c_{k\overline\beta}c_{q\beta}\right\}\right] + \text{h.c.}~.
-\end{aligned}\end{equation}
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/zeromode.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/zeromode_bare.pdf}
 	\caption{While we have studied the full model under renormalisation group, often we will turn to a simplified zero-bandwidth version of the model that is obtained by ignoring the kinetic energy part of the Hamiltonian.
@@
 
-\section{RG equations for generalised SIAM}
-\begin{equation}\begin{aligned}
-	\Delta \epsilon_d &= 2V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + \frac{n_j}{2}\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right),\\
-	\Delta V &= -\frac{3n_j V}{8}\left[J\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)\right],\\
-	\Delta J &= -\frac{n_j J^2}{\omega - \frac{D}{2} + \frac{J}{4}},\\ 
-	\Delta K &= -\frac{n_j K^2}{\omega - \frac{D}{2} + \frac{K}{4}}
-\end{aligned}\end{equation}
-In terms of \(U = -2\epsilon_d\), the equations become
-\begin{gather}
-	\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\left(\frac{J^2}{d_2} - \frac{K^2}{d_3}\right),\\
-	\Delta V = -\frac{3n_j V}{8}\left[J\left(\frac{1}{d_2} + \frac{1}{d_1}\right) + K \left(\frac{1}{d_3} + \frac{1}{d_0}\right)\right],\\
-	\Delta J = -\frac{n_j J^2}{d_2}, \quad\quad\Delta K = -\frac{n_j K^2}{d_3}
-\end{gather}
-\(d_i\) are the denominators:
-\begin{equation}\begin{aligned}
-	\label{denominators}
-	d_0 = \omega - \frac{D}{2} - \frac{U}{2} + \frac{K}{4}, \quad d_1 = \omega - \frac{D}{2} + \frac{U}{2} + \frac{J}{4}, \quad d_2 = \omega - \frac{D}{2} + \frac{J}{4}, \quad d_3 = \omega - \frac{D}{2} + \frac{K}{4}
-\end{aligned}\end{equation}
-
-\section{Nature of coupling RG flows}
-\subsection{Repulsive interaction on impurity: \(U>0\)}
-For the Hamiltonians with positive on-site correlation, we will assume that the spin-exchange coupling is positive and charge isospin-exchange coupling is negative: \(J>0, K<0\).
-This choice is motivated by the signs of the corresponding terms when they are generated via a Schrieffer-Wolff transformation~\cite{schrieffer1966}.
-The impurity-bath hybridisation \(V\) is always positive.
-The sign of the couplings lead to inequalities among the denominators which we will utilise at various points.
-First of all, since \(U>0\), we have \(d_1 - d_2 = \frac{U}{2} > 0\).
-Secondly, since \(K<0\), we have \(d_2 - d_3 = \frac{J-K}{4} > 0\).
-And finally, we have \(d_3 - d_0 = \frac{U}{2} > 0\).
-Combining these, we can write
-\begin{equation}\begin{aligned}
-	\label{ineq_den}
-	d_1 > d_2 > d_3 > d_0
-\end{aligned}\end{equation}
-
-The strong coupling regime is defined as the range of values of \(\omega\) where the hybridisation is relevant.
-This is ensured by the assumption \(d_1<0\).
-From eq.~\ref{ineq_den}, we can then conclude that all denominators are negative: \(d_i = - |d_i|\).
-The simplest consequence of this is the RG flow of \(K\):
-\begin{equation}\begin{aligned}
-	\Delta K= -\frac{n_j K^2}{d_3} = \frac{n_j K^2}{|d_3|} > 0 \implies K_{j+1} > K_j \implies K_0 = -|K_0|, K^* \to 0
-\end{aligned}\end{equation}
-\(K_j\) is the value of \(K\) after the \(j^\text{th}\) RG step, \(K_0\) representing the bare value.
-In other words, since \(d_3 < 0\), the RG equation for \(K\) provides an algebraic increment, and the negative \(K\) increases and flows towards zero.
-The \(*\) indicates a fixed point value.
-The isospin coupling is irrelevant in this regime, and we will ignore it.
-
-The coupling \(J\), on the other hand, is relevant and flows from a small positive value towards a large value at strong coupling.
-\begin{equation}\begin{aligned}
-	\Delta J= -\frac{n_j J^2}{d_2} = \frac{n_j J^2}{|d_2|} > 0 \implies J_{j+1} > J_j \implies J_0 \to \text{ large } J^* ~(\text{strong coupling})
-\end{aligned}\end{equation}
-The value of \(J^*\) is obtained when the denominator \(d_2\) vanishes.
-
-Because of the RG irrelevance of \(K\), we can simplify the RG equation for \(V\):
-\begin{equation}\begin{aligned}
-	\Delta V = -\frac{3n_j VJ}{8}\left(\frac{1}{d_2} + \frac{1}{d_1}\right) = \frac{3n_j VJ}{8}\left(\frac{1}{|d_2|} + \frac{1}{|d_1|}\right) > 0
-\end{aligned}\end{equation}
-Since both the denominators are positive, \(V\) is relevant. The fixed point value \(V^*\) is attained when the denominator \(d_1\) vanishes (\(d_1\) will vanish earlier than \(d_2\)).
-
-We can compare the rate of flows of \(V\) and \(J\):
-\begin{equation}\begin{aligned}
-	\frac{\Delta V}{\Delta J} = \frac{3V}{8J}\left(1 + \frac{|d_2|}{|d_1|}\right) > \frac{3V}{4J}
-\end{aligned}\end{equation}
-There we used the fact that \(|d_2| > |d_1|\).
-We finally come to the RG equation for \(U\):
-\begin{equation}\begin{aligned}
-	\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\frac{J^2}{d_2} = -4V^2\left(U + \frac{J}{4}\right)\frac{n_j}{d_0 d_1} - \frac{n_j J^2}{d_2}
-\end{aligned}\end{equation}
-For \(V>J\), we can expect \(U\) to be irrelevant. On the other hand, \(V<J\) makes \(U\) relevant.
-
-In short, the \(U>0\) regime is characterised by an irrelevant isospin-exchange coupling \(K\) and a relevant spin-exchange coupling \(J\), and the following set of RG equations for the remaining couplings \(U\) and \(V\):
-\begin{equation}\begin{aligned}
-	\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\frac{J^2}{d_2}, \quad \Delta V = -\frac{3n_j VJ}{8}\left(\frac{1}{d_2} + \frac{1}{d_1}\right)
-\end{aligned}\end{equation}
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U_gt_0,U.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U_gt_0,J.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U_gt_0,V.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U_gt_0,U.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U_gt_0,J.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U_gt_0,V.pdf}
-\end{figure}
-
-\subsection{Attractive interaction on impurity: \(U<0\)}
-Here, we have \(J<0\) and \(K>0\). The denominators satisfy the following inequality in this regime:
-\begin{equation}\begin{aligned}
-	d_0 > d_3 > d_2 > d_1
-\end{aligned}\end{equation}
-
-The strong coupling regime here corresponds to \(d_0 < 0\).
-This again means that all the denominators are negative.
-The spin-exchange coupling \(J\) is now irrelevant, because its bare value is negative while its RG equation is positive: \(\Delta J>0\).
-Moreover, the isospin coupling \(K\) is now positive and so is its RG equation: \(\Delta K>0\), which means it flows to strong coupling.
-\(V\) also flows to strong coupling.
-The RG equation for \(U\) can be written as
-\begin{equation}\begin{aligned}
-	\Delta U = 4V^2\left(\frac{K}{4} - U\right)\frac{n_j}{d_0 d_1} + \frac{n_j K^2}{d_3}
-\end{aligned}\end{equation}
-The first term is necessarily positive, while the second term is negative.
-This means that for roughly \(V_0 > J_0\), we  will have \(\Delta U > 0\), and since \(U_0 < 0\), this amounts to an irrelevant flow of \(U\) towards zero.
-On the other hand, for \(J_0 > V_0\), we will have \(\Delta U < 0\), and this corresponds to a relevant flow of \(U\) towards large negative value.
-
-In other words, the RG flows in this regime can be exactly mapped to those in the positive \(U\) regime.
-The general statement is: in the strong coupling regime of positive(negative) \(U\), \(V\) is always relevant, \(J\)(\(K\)) is relevant, \(K\)(\(J\)) is irrelevant, and \(U\) is relevant when \(J(K) > V\), otherwise \(U\) is irrelevant.
-
-\section{Effective Hamiltonian and ground state}
-The fixed point Hamiltonian can, in general, be written as
-\begin{equation}\begin{aligned}
-	\mathcal{H}^* = \sum_{\sigma, k}\epsilon_k \tau_{k\sigma} - \frac{U^*}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2  + \sum_{\sigma, k < \Lambda^*}\left( V^* c^\dagger_{k\sigma}c_{d\sigma} + \text{h.c.} \right) + J^* \vec{S_d}\cdot\vec{s} + K^* \vec{C_d}\cdot\vec{C}
-\end{aligned}\end{equation}
-The first term is the kinetic energy of all the electrons.
-The next two terms are the impurity-diagonal pieces, featuring the renormalised interaction \(U^*\).
-The next three terms are the residual interactions between the impurity and the metal, with the renormalised couplings \(V^*, J^*\) and \(K^*\).
-The summations in these terms extend from the fixed point momentum cutoff \(\Lambda^*\) to 0.
-This is the region of momentum space  which the URG was unable to decouple.
-The operators \(\vec s\) and \(\vec C\) represent the macroscopic magnetic and charge spins formed by the remaining electrons that are lying inside the window \(\left[ 0, \Lambda^* \right] \):
-\begin{equation}\begin{aligned}
-	\vec s = \sum_{kk^\prime<\Lambda^*\atop{\alpha\beta}} c^\dagger_{k\alpha}\vec \sigma_{\alpha\beta}c_{k^\prime\beta}
-\end{aligned}\end{equation}
-Our goal here is to write down the ground state wavefunction for this low-energy Hamiltonian.
-
-To make progress, we will simplify the effective Hamiltonian by taking the zero bandwidth limit.
-This reduces it to a two-site problem.
-One site is of course the impurity site, and this site will be labeled as site 1.
-The other site will be formed by the center of mass degree of freedom of the conduction electrons, and will be labeled as site 2.
-The Hamiltonian for this two-site problem is
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{IR} = - \frac{U^*}{2}\left(\hat n_{1 \uparrow} - \hat n_{1 \downarrow}\right)^2 + V^*\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.} \right) + J^*\vec{S_1}\cdot\vec{S_2} + K^* \vec{C_1}\cdot\vec{C_2}
-\end{aligned}\end{equation}
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.4\textwidth]{../figures/two_site_problem.png}
-	\caption{Two-site effective problem of fixed point Hamiltonian}
-	\label{twosite}
-
-\end{figure}
-The subscripts on the operators designate the site on which they act; \(\hat n_1\) is the number operator for the first site.
-
-We will adopt the following notation to represent the states in this Hilbert space.
-A general state will be represented in the Fock space basis as \(\ket{n_{1 \uparrow}n_{1 \downarrow}n_{2 \uparrow}n_{2 \downarrow}}\).
-For example,
-\begin{equation}\begin{aligned}
-	\ket{1101} = c^\dagger_{1 \uparrow}c^\dagger_{1 \downarrow}c^\dagger_{2 \downarrow}\ket{-}
-\end{aligned}\end{equation}
-\(\ket{-}\) is the vacuum state.
-
-For \(U>0\), the ground state is given by
-\begin{gather}
-	\label{gstate}
-	\ket{\Psi}_\text{1} = c_s \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c_c \frac{1}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right), \quad E_1 =  -V^*\sqrt{\gamma^2 + 4} -\frac{1}{4}U^* - \frac{3}{8}{J^*}
-\end{gather}
-where $\gamma = \frac{1}{2{V^*}}\left[ \frac{1}{4}\left( 3J^* + K^* \right) + \frac{1}{2}U^* \right]$. The probabilities for the spin and charge sectors for the ground state are
-\begin{equation}\begin{aligned}
-	\label{coeff_def}
-	\left(c_s\right)^2 = \frac{1}{2\sqrt{\gamma^2 + 4}}\left(\sqrt{\gamma^2 + 4} + \gamma\right), \quad \left(c_c \right)^2 = \frac{1}{2\sqrt{\gamma^2 + 4}}\left(\sqrt{\gamma^2 + 4} - \gamma\right)~.
-\end{aligned}\end{equation}
-For (roughly) \(J_0 > V_0\), we get \(J^* \gg V^*\) and \(U^* \gg U_0\) so that \(\gamma \gg 1\).
-This gives \(\left( c_s \right) ^2 \sim 1\) and \(\left( c_c \right) ^2 \sim 0\).
-The entire contribution to the ground state then comes from the spin sectors of the two sites.
-This is calculated numerically in fig.~\ref{cs_cc}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/coeffs_vs_J.pdf}
-	\caption{Variation of relative weights \(c_s\) and \(c_c\) with \(J_0\)}
-	\label{cs_cc}
-\end{figure}
-
-In the other regime of \(U<0\), the two competing states are \(\ket{\Psi}_1\) defined above (with energy \(E_1\)), and \(\ket{\Psi_2}\), the charge singlet: \(\ket{\Psi}_2 = \frac{1}{\sqrt 2}\left( \ket{2,0} - \ket{0,2} \right)\) having energy \(E_2\).
-\begin{equation}\begin{aligned}
-	E_2 = -\frac{3}{4}K^*, \quad E_1 - E_2 = -\frac{1}{4}\sqrt{\left( \frac{1}{2}K^* + U^* \right)^2 + (4V^*)^2} - \frac{1}{4}U^* + \frac{3}{4}K^*
-\end{aligned}\end{equation}
-For \(V_0 \gg K_0\), the largest energy scale will be \(V^*\), and we can then approximate this difference as
-\begin{equation}\begin{aligned}
-	E_1 - E_2 \simeq -V^* < 0
-\end{aligned}\end{equation}
-In such a case, \(\ket{\Psi}_1\) will therefore be the ground state. In the other regime \(V_0 \ll K_0\), the largest energy scale will be \(K^*\), and we can then write
-\begin{equation}\begin{aligned}
-	E_1 - E_2 \simeq - \frac{1}{8}K^* + \frac{3}{4}K^* > 0
-\end{aligned}\end{equation}
-In this case, the ground state will be \(\ket{\Psi}_2\).
-There exists, therefore, a phase transition at a critical plane \((U_c, K_c, V_c)\), where the ground state changes between the charge singlet \(\ket{\Psi}_2\) and the spin singlet + charge triplet \(\ket{\Psi}_1\).
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/E1_vs_E3.pdf}
-\end{figure}
-
-\section{Approach towards the thermodynamic limit}
-
-{\bf \Large [Update with V vs D plots]}
-
-The URG method works strictly on finite systems and leads to finite values of fixed point couplings.
-The behaviour of the Hamiltonian in the thermodynamic limit can then be determined using finite-size scaling where we increase the bandwidth and decrease the width of each RG step.
-When applied to the fixed point value of the impurity-bath hybridisation parameter \(V\) (fig.~\ref{V_vs_D}), it can be seen that the fixed point value increases as the system size is increased, implying that the continuum limit of \(V^*\) is \(\infty\).
-This holds for both \(V_0 > J_0\) and \(V_0 < J_0\), as shown in the two panels of fig.~\ref{V_vs_D}.
-\begin{figure}[!htb]
-	\centering
-	\hspace*{\fill}
-	\includegraphics[width=0.4\textwidth]{../figures/Vstar_vs_D_smallV.pdf}
-	\hspace*{\fill}
-	\includegraphics[width=0.4\textwidth]{../figures/Vstar_vs_D_largeV.pdf}
-	\hspace*{\fill}
-	\caption{Variation of fixed point value \(V^*\) with increasing bandwith \(D_0\), for both \(V_0 > J_0\) and \(V_0 < J_0\).}
-	\label{V_vs_D}
-\end{figure}
-
-In a similar manner, we checked the variation of the spin and charge probabilities, \(c_s\) and \(c_c\), in the ground state, with increasing bandwith. The result is shown in fig.~\ref{c_vs_D}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/coeffs_vs_D.pdf}
-	\caption{Variation of spin and charge fractions, \(c_s\) and \(c_c\), of the ground state, as a function of bare bandwidth \(D_0\).
-Left and right panels show the cases of \(J_0 < V_0\) and \(J_0 > V_0\) respectively.}
-	\label{c_vs_D}
-\end{figure}
-For both \(V_0 < J_0\) and \(V_0 > J_0\), we see that the spin contribution increases towards unity while the charge contribution vanishes.
-This indicates that at large bandwidth, the ground state becomes purely a spin singlet, formed purely by singly-occupied impurity states.
-\begin{equation}\begin{aligned}
-	\label{gstate_kondo}
-	\lim_{D_0 \to \infty} \ket{\Psi}_1 = \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) 
-\end{aligned}\end{equation}
-
-\section{Effective temperature scale at the fixed point}
-We will first change the discrete RG equation to a continuum equation by interpreting \(\Delta J\) as \(\frac{\Delta J}{\Delta \ln D}\), where the denominator is unity: \(\Delta \ln D = 1\).
-Now, since the bandwidth is decreasing under the RG, we can write \(\Delta \ln D = -d \ln D\).
-The continuum equation (for \(K=0\)) becomes
-\begin{equation}\begin{aligned}
-	\frac{\:\mathrm{d}J}{\:\mathrm{d}\ln D} = n(0)J^2 \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}
-\end{aligned}\end{equation}
-where we have replaced by the number of states at each shell with that at the Fermi surface (uniform DOS).
-We can define a dimensionless quantity \(g \equiv \frac{J}{\frac{D}{2}} - \omega\).
-In terms of \(g\), the continuum RG equation becomes
-\begin{equation}\begin{aligned}
-	-\frac{\:\mathrm{d}g}{\:\mathrm{d}\ln D} + \frac{D g}{2\omega - D} = \frac{n(0) g^2}{1 - \frac{g}{4}}
-\end{aligned}\end{equation}
-Now, for the specific case where \(D\) is small (\(D \to 0\)), we can simplify and integrate this equation:
-\begin{equation}\begin{aligned}
-	\frac{\:\mathrm{d}g}{\:\mathrm{d}\ln D} &= \frac{n(0) g^2}{\frac{g}{4} - 1}\\
-	\implies \left[\frac{1}{g} + \frac{1}{4}\ln g\right]_{g_0}^{g^*} &= n(0)\ln D\big\vert_{D_0}^{D^*}
-\end{aligned}\end{equation}
-\(g^*(_0), D^*(_0)\) are the fixed point (bare) values of \(g, D\).
-From the denominator structure, the fixed-point value is \(g^* =  4\).
-This gives an estimate of the bandwidth of the emergent window:
-\begin{equation}\begin{aligned}
-	D^* = D_0 \left( \frac{4}{g_0} \right)^\frac{1}{4n(0)}\exp\left\{-\frac{1}{n(0)}\left(\frac{1}{g_0} - \frac{1}{4}\right)\right\}
-\end{aligned}\end{equation}
-We can now define a temperature scale~\cite{wilson1975,hrk_wilson_1980} for the fixed-point theory:
-\begin{equation}\begin{aligned}
-	T_K \equiv \frac{2N^*}{\pi}D^* = \frac{2N^*}{\pi}D_0 \left( \frac{4}{g_0} \right)^\frac{1}{4n(0)}\exp\left\{-\frac{1}{n(0)}\left(\frac{1}{g_0} - \frac{1}{4}\right)\right\}
-\end{aligned}\end{equation}
-The factor of \(2N^*\) is inserted to make the Kondo temperature intensive (we will see below that the \(N^*\) allows it to  be written in terms of parameters of the two-site Hamiltonian) - \(2N^*\) is the total number of momentum states in the fixed point theory.
-The factor of \(\frac{1}{\pi}\) is for aesthetic reasons.
-Since we have and will primarily work with \(\omega=0\), the fixed point condition can be used to write \(D^* = \frac{J^* + K^*}{2}\).
-\begin{equation}\begin{aligned}
-	T_K = \frac{2N^*}{\pi}\frac{1}{2}\left(J^* + K^*\right) = \frac{1}{\pi}\left(j + k\right)
-\end{aligned}\end{equation}
-\section{Impurity susceptibilities}
-\subsection{Spin susceptibility}
-The spin susceptibility is defined as
-\begin{equation}\begin{aligned}
-	\label{chi_def}
-	\chi(\beta) = \beta \left(\left<\left(S_d^z\right)^2\right> - \left<S_d^z\right>^2\right)
-\end{aligned}\end{equation}
-There is an alternate way of calculating this. We insert a fictitious magnetic field that couples only to the impurity site. The Hamiltonian in the presence of this field is
-\begin{equation}\begin{aligned}
-	\label{field_ham}
-	\mathcal{H}^\prime(B) = \mathcal{H} + B S_d^z
-\end{aligned}\end{equation}
-The susceptibility is then given by
-\begin{equation}\begin{aligned}
-	\label{chi_exp}
-	\chi(\beta) &= \lim_{B \to 0}\frac{1}{\beta}\left[\frac{1}{Z(B)} \frac{\partial^2{Z(B)}}{\partial{B^2}}-\frac{1}{Z(B)^2} \left(\frac{\partial{Z(B)}}{\partial{B}}\right)^2\right]
-\end{aligned}\end{equation}
-where \(Z(B)\) is the partition function of the Hamiltonian \(\mathcal{H}^\prime(B)\).
-The following is to prove that the RHS of eqs.~\ref{chi_def} and \ref{chi_exp} are the same.
-We start with \ref{chi_exp}.
-The first derivative can be written as
-\begin{equation}\begin{aligned}
-	\frac{\partial{Z(B)}}{\partial{B}} = \text{Trace}\left[\frac{\partial{}}{\partial{B}} \exp\left\{-\beta\left( \mathcal{H} + BS_d^z \right) \right\}\right] = \text{Trace}\left[-\beta S_d^z \exp\left\{-\beta\left( \mathcal{H} + BS_d^z \right) \right\}\right]
-\end{aligned}\end{equation}
-which means the first term becomes
-\begin{equation}\begin{aligned}
-	\lim_{B \to 0}-\frac{1}{Z(B)^2} \left(\frac{\partial{Z(B)}}{\partial{B}}\right)^2 = -\left(\beta \frac{1}{\text{Trace}\left[\exp\left\{-\beta\mathcal{H}\right\}\right]} \text{Trace}\left[S_d^z \exp\left\{-\beta\mathcal{H}\right\}\right]\right)^2 = -\beta^2 \left<S_d^z\right>^2
-\end{aligned}\end{equation}
-The second derivative is
-\begin{equation}\begin{aligned}
-	\frac{\partial^2{Z(B)}}{\partial{B^2}} = \text{Trace}\left[-\beta S_d^z  \frac{\partial{}}{\partial{B}}\exp\left\{-\beta \left( \mathcal{H} + BS_d^z \right) \right\}\right] = \text{Trace}\left[\beta^2 \left(S_d^z\right)^2 \exp\left\{-\beta \left( \mathcal{H} + BS_d^z \right) \right\}\right]
-\end{aligned}\end{equation}
-so the second term becomes
-\begin{equation}\begin{aligned}
-	\lim_{B \to 0}\frac{1}{Z(B)} \frac{\partial^2{Z(B)}}{\partial{B^2}} = \beta^2 \frac{1}{\text{Trace}\left[\exp\left\{-\beta \mathcal{H}\right\}\right]}\text{Trace}\left[\left(S_d^z\right)^2 \exp\left\{-\beta \mathcal{H}\right\}\right] = \beta^2 \left<\left(S_d^z\right)^2 \right>
-\end{aligned}\end{equation}
-The full thing becomes
-\begin{equation}\begin{aligned}
-	\lim_{B \to 0}\frac{1}{\beta}\left[\frac{1}{Z(B)} \frac{\partial^2{Z(B)}}{\partial{B^2}}-\frac{1}{Z(B)^2} \left(\frac{\partial{Z(B)}}{\partial{B}}\right)^2\right] = \frac{1}{\beta}\left(-\beta^2 \left<S_d^z\right>^2 + \beta^2 \left<\left(S_d^z\right)^2 \right>\right) \\
-	= \beta \left(\left<\left(S_d^z\right)^2\right> - \left<S_d^z\right>^2\right) 
-\end{aligned}\end{equation}
-This completes the proof.
-
-To calculate the impurity susceptibility, we take the zero bandwidth Hamiltonian \(\mathcal{H}_{IR}\) and insert a magnetic field to obtain the Hamiltonian in eq.~\eqref{field_ham}.
-For a particular regime of \(U\), only one of \(J\) or \(K\) will be non-zero.
-We then numerically diagonalise this Hamiltonian to obtain the partition function \(Z(B)\) and its derivatives.
-The spin susceptibility can then be calculated using eq.~\eqref{chi_exp}.
-The results for \(U>0\) are shown in fig.~\ref{chi}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.49\textwidth]{../figures/chiT.pdf}
-	\includegraphics[width=0.49\textwidth]{../figures/chiT_large.pdf}
-	\includegraphics[width=0.49\textwidth]{../figures/chi.pdf}
-	\caption{Spin susceptibility of the impurity times temperature, for two sets of bare parameters, in \(U>0\).
-At low temperatures, it becomes linear because \(\chi\) itself becomes constant (screening), while at high temperatures, \(\chi\times T\) becomes constant because of the paramagnetic \(\sim 1/T\) form of \(\chi\).
-For the right panel with a larger value of the spin-exchange coupling, the \(\chi\) tries to go towards the local moment value of \(1/4\) but eventually drops back to the free orbital value of \(1/8\).}
-	\label{chi}
-\end{figure}
-
-\subsection{Charge susceptibility}
-We can similarly define the charge susceptibility as
-\begin{equation}\begin{aligned}
-	\label{zero_chi_charge}
-	\chi(\beta) = \beta \left(\left<\left(C_d^z\right)^2\right> - \left<C_d^z\right>^2\right) = \lim_{B_c \to 0}\frac{1}{\beta}\left[\frac{1}{Z(B_c)} \frac{\partial^2{Z(B_c)}}{\partial{B_c^2}}-\frac{1}{Z(B_c)^2} \left(\frac{\partial{Z(B_c)}}{\partial{B_c}}\right)^2\right]
-\end{aligned}\end{equation}
-where \(B_c\) is now a field that couples to the impurity charge-isospin:
-\begin{equation}\begin{aligned}
-	\label{charge_field}
-	\mathcal{H}^\prime(B_c) = \mathcal{H} + B_c C_d^z
-\end{aligned}\end{equation}
-The charge susceptibility for \(U<0\) is shown in fig.~\ref{chi_charge}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.49\textwidth]{../figures/chic.pdf}
-	\includegraphics[width=0.49\textwidth]{../figures/chic_T.pdf}
-	\caption{Charge susceptibility for the impurity at \(U<0\), for two sets of bare parameters. The physics is very similar to that of the spin susceptibility in \(U>0\).}
-	\label{chi_charge}
-\end{figure}
-
-It is interesting to look at the behaviour of the charge susceptibility in the positive \(U\) regime, fig.~\ref{chi_charge_posU}.
-It  is seen that for \(J_0<V_0\), the charge susceptibility is very similar to the spin susceptibility, with a reduced saturation value.
-This is because, for that range of bare values, the ground state consists of a comparable mixture of the spin and charge states (see fig.~\ref{cs_cc}).
-This means that the magnetic field term in eq.~\eqref{charge_field} can couple to the charge component of the ground state, and give a non-zero charge susceptibility at zero temperature.
-On the other hand, for \(J_0 > V_0\), we see that \(\chi_c\) vanishes at low temperatures.
-This can again be understood from the ground state.
-For that range of bare values, the ground state can be approximated by purely the singlet, because the charge fraction \(c_-^c\) becomes very small.
-This means that the field \(B_c \) has nothing to couple with.
-Alternatively, it can be said that since the ground state has only terms with \(\hat n_d=1\), no number fluctuation is possible, and the impurity isospin is not susceptible at all to charge polarisation.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.48\textwidth]{../figures/chiC_posU_J0=10.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/chiC_posU_J0=40.pdf}
-	\caption{Charge susceptibility of the impurity in the positive \(U\) regime, for two values of \(J_0\).
-The smaller bare value leads to a spin+charge mixed ground state, and hence a non-zero \(\chi_c\) at zero temperature.
-The larger \(J_0\), however, leads to a purely spin ground state without any number fluctuation, and this gives vanishing \(\chi_c\) at zero temperature.}
-	\label{chi_charge_posU}
-\end{figure}
-
-From eq.~\eqref{gstate_kondo}, we know that in the thermodynamic limit, the ground state of \(U>0\) regime reduces to a screened local moment.
-That then implies that the charge susceptibility vanishes at low temperatures, owing to lack of any charge content in the ground state in the large bandwidth limit.
-\begin{equation}\begin{aligned}
-	\lim_{D_0 \to \infty}\chi_c(U>0, T \to 0) = 0
-\end{aligned}\end{equation}
-
-\section{Specific heat}
-The specific heat is calculated by diagonalizing the fixed point Hamiltonian, numerically.
-The obtained spectrum is denoted by \(\left\{ \mathcal{E}_i \right\} \).
-The total average energy of the impurity+cloud at temperature \(T\) is then
-\begin{equation}\begin{aligned}
-	\left<\mathcal{E} \right> = \frac{1}{Z}\sum_{i} \mathcal{E}_i e^{-\beta \mathcal{E}_i}
-\end{aligned}\end{equation}
-where \(Z = \sum_{i} e^{-\beta E_i}\) is the partition function. The specific heat of this system is thus
-\begin{equation}\begin{aligned}
-	C_V &= \frac{\partial{\left<\mathcal{E} \right>}}{\partial{T}} \\
-	    &= -\frac{1}{k_B T^2} \frac{\partial{\left<\mathcal{E} \right>}}{\partial{\beta}} \\
-	    &= \frac{1}{k_B T^2}\left[\frac{1}{Z}\sum_i \mathcal{E}_i^2 e^{-\beta \mathcal{E}_i} - \left(\frac{1}{Z}\sum_i \mathcal{E}_i e^{-\beta \mathcal{E}_i}\right)^2 \right] 
-\end{aligned}\end{equation}
-In the absence of impurity, the eigenvalues of the Hamiltonian are \(\left\{\mathcal{E}_i^0\right\}\) with a partition function \(Z^0 = \sum_{i} e^{-\beta E_i^0}\), so the bath specific heat is
-\begin{equation}\begin{aligned}
-	C_V^0 &= \frac{1}{k_B T^2}\left[\frac{1}{Z_0}\sum_i \mathcal{E}_i^2 e^{-\beta \mathcal{E}_i^0} - \left(\frac{1}{Z_0}\sum_i \mathcal{E}_i^0 e^{-\beta \mathcal{E}_i^0}\right)^2 \right] 
-\end{aligned}\end{equation}
-The impurity specific heat is the difference.
-\begin{equation}\begin{aligned}
-	C_V^\text{imp} = C_V - C_V^0
-\end{aligned}\end{equation}
-These values were calculated numerically and plotted against temperature in fig.~\ref{cv}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.6\textwidth]{../figures/Cv.pdf}
-	\caption{Impurity specific heat}
-	\label{cv}
-\end{figure}
-
-\section{Renormalization of impurity spectral function}
-In this section we will obtain the impurity spectral function~\cite{costi2000,rosch_costi2003,bullaNRGreview}, which is defined in terms of the impurity Green's function as
-\begin{equation}\begin{aligned}
-	\mathcal{A(\omega)} = -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] 
-\end{aligned}\end{equation}
-The zero temperature retarded Green's function for the impurity, in the frequency domain, can be written as (see Appendix.~\ref{appx-spectral-func})
-\begin{equation}\begin{aligned}
-	\mathcal{A(\omega)} = \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]
-\end{aligned}\end{equation}
-where \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in.
-The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term
-Since this is in terms of the exact eigenstates, it is a discrete sum of delta-functions.
-In practice, we get a continuous distribution.
-To compare with experiment, we need to convert the discrete sum into a continuous function.
-Following \cite{bullaNRGreview}, we replace the delta-functions at \(\pm x_n \equiv \pm(E_n - E_0)\) by normalized Gaussian functions
-\begin{equation}\begin{aligned}
-	\delta(\omega \pm x_n) \to \frac{1}{\eta_n\sqrt \pi}e^{-\left(\frac{\omega \pm x_n}{\eta_n}\right)^2}
-\end{aligned}\end{equation}
-The parameter \(\eta_n\) determines the height and width of the Gaussian, and is chosen such that the higher energy poles are broader than the lower energy ones:
-\begin{equation}\begin{aligned}
-	\eta_n = 4\Delta + \frac{1}{2}|x_n| 
-\end{aligned}\end{equation}
-\(\Delta = \pi \rho(0)V^2\) is the relevant energy scale for the non-interacting \((U=0)\) problem, \(\rho(0)\) being the density of states of the conduction bath at the Fermi energy.
-As a result, the function that we will numerically compute and plot is
-\begin{equation}\begin{aligned}
-	\mathcal{A(\omega)} &= \sum_{n,0}\frac{1}{d_0 \sqrt \pi \eta_n}\left[||\bra{0}c_{d\sigma}\ket{n}||^2e^{-\left(\frac{\omega - x_n}{\eta_n}\right)^2} + ||\bra{n}c_{d\sigma}\ket{0}||^2e^{-\left(\frac{\omega + x_n}{\eta_n}\right)^2}\right]
-\end{aligned}\end{equation}
-From the results of Langreth \cite{langreth1966}, we know that the spectral function at zero frequency is fixed by the occupancy of the impurity.
-Since we are in the particle-hole symmetric regime, this occupancy is fixed at 1, and hence so is the spectral function height at \(\omega = 0\).
-This result has been used to fix the spectral function height at the center during the computations.
-The fixed-point Hamiltonian \(H^*\) is diagonalized numerically to obtain \(\left\{E_n, \ket{n}\right\}\), for various values of the couplings.
-The intention here is to get an idea of how the spectral function morphs under the RG.
-Doing an actual reverse RG (described in \ref{rev_rg}) would require us to diagonalize a huge Hamiltonian.
-We take the simpler route of tuning the \(U\) from zero to soem large value.
-This should mimic the journey from the IR theory \((U=0)\) to the UV theory \((U \gg 0)\).
-
-The spectral function is plotted for three sets of values in fig.~\ref{spec_func}.
-For low values of \(U\), the profile is that of a single peak at zero frequency.
-This is expected because at the low energy effective theory, the high energy Hubbard side bands have been integrated out.
-As \(U\) increases, shoulder-like structures appear on either side of the peak, which finally, at larger \(U\), develop into two side-peaks.
-This is the microscopic theory, where high energy features are also relevant.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=0.00.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=3.00.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=5.00.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=10.00.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=25.00.pdf}
-	\caption{Impurity spectral function for multiple values of \(U\). The increase in value of \(U\) is accompanied by the appearance of the side-peaks.}
-	\label{spec_func}
-\end{figure}
-The physics of the three peaks can now be looked into.
-Since the central peak is at zero energy, it has to do with excitations that do not cost any energy.
-There are two such excitations: excitations within the spin sector and within the charge sector.
-\begin{equation}\begin{aligned}
-	\ket{\uparrow} \mathrel{\mathlarger{\mathlarger{\mathop{\rightleftarrows}}^{J S_d^-}_{JS_d^+}}}\ket{\downarrow}, &&&&\ket{\Uparrow} \mathrel{\mathlarger{\mathlarger{\mathop{\rightleftarrows}}^{K C_d^-}_{K C_d^+}}}\ket{\Downarrow}\\
-\end{aligned}\end{equation}
-The thick arrow \(\Uparrow\) represents the charge isospin.
-At particle-hole symmetry, both the spin configurations has energy of \(\epsilon_d\), while the charge configurations have energy of \(2\epsilon_d + U=0\) and 0.
-Hence, no energy is required for these excitations, which is why see a macroscopic number of cloud electrons resonating with the impurity at the Fermi surface.
-Also note that if \(\hat S_i\) and \(\hat C_j\) are two operators of the spin and charge sector (\(i,j \in \left\{ x,y,z \right\} \)), then
-\begin{equation}\begin{aligned}
-	\hat S_i \hat C_j = \hat C_j \hat S_i = 0
-\end{aligned}\end{equation}
-We can see this by applying that operator on a basis state. Since the set of four states 
-\begin{equation}\begin{aligned}
-	\ket{\hat S_i = \pm \frac{1}{2}, \hat C_j = 0}, \ket{\hat S_i = 0, \hat C_j = \pm\frac{1}{2}}
-\end{aligned}\end{equation}
-are all independent, they form a basis. If we apply the operator on these states:
-\begin{equation}\begin{aligned}
-	\hat S_i \hat C_j \ket{\hat S_i} &= 0, &&&&\hat C_j \hat S_i \ket{S_i} = S_i \hat C_j \ket{S_i} = 0\\
-	\hat C_j \hat S_i \ket{C_j} &= 0, &&&&\hat S_i \hat C_j \ket{\hat C_j} = C_j \hat S_i \ket{\hat C_j} = 0 \\
-\end{aligned}\end{equation}
-This shows that each operator acts only on its own subspace. \(S_i\) does not act on the charge sector, and vice-versa. There is no single-particle excitation here.
-
-The physics of the side-peaks is that of single number fluctuations on the impurity. These are brought about by the term \(Vc^\dagger_{0\sigma}c_{d\sigma} + \text{h.c.}\).
-\begin{equation}\begin{aligned}
-	\left( \epsilon_d  \right) \ket{\sigma} & \mathrel{\mathlarger{\mathlarger{\mathop{\rightleftarrows}}^{V c^\dagger_{d\overline\sigma}/V c_{d\sigma}}_{V c_{d\overline\sigma}/V c^\dagger_{d\sigma}}}} &\ket{n_d=2,0} \left( 0 \right) \\
-\end{aligned}\end{equation}
-These transitions involve energy transfer of the order of \(\epsilon_d\).
-This is why, at very small \(U\), they remain absorbed inside the central peak.
-These transitions do not involve any spin or charge-flip, rather they take the impurity between the spin and charge sectors.
-
-\section{Effective Hamiltonian for excitations of the Kondo cloud}
-To find an effective Hamiltonian for the excitations of the Kondo cloud, we will integrate out the impurity part of the wavefunction. The Schrodinger equation for the \(J > K\) ground state is
-\begin{equation}\begin{aligned}
-	E_g &\left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right] \\
-	    &= \mathcal{H} \left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]\\
-	    &= \mathcal{H}_0^* \left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]\\
-	    &+V\sum_{\beta}\left[c^\dagger_{2\beta}c_{1\beta} - c_{2\beta}c^\dagger_{1\beta}\right]\left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]\\
-	    &+ J \vec{S_d}\cdot\vec{s}\left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]\\
-	    &+ K \vec{C_d}\cdot\vec{c}\left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]
-\end{aligned}\end{equation}
-The last two lines gives
-\begin{equation}\begin{aligned}
-\frac{1}{2}Jc_-^s \left[s^z \left(\ket{\uparrow, \downarrow} + \ket{\downarrow, \uparrow}\right) +  s^+ \ket{\downarrow, \downarrow} - s^-\ket{\uparrow, \uparrow}\right] + \frac{1}{2}Kc^c_- \left[c^z\left(\ket{\uparrow\downarrow, 0} - \ket{0, \uparrow\downarrow}\right) + c^+\ket{0, 0} \right.\\
-+ \left.c^-\ket{2, 2}\right]
-\end{aligned}\end{equation}
-The second line gives
-\begin{equation}\begin{aligned}
-	V c^\dagger_{2\uparrow}\left[c_-^s \left(\ket{0, \downarrow}\right) + c^c_- \left(\ket{\downarrow, 0}\right)\right] + V c^\dagger_{2 \downarrow}\left[c_-^s \left(- \ket{0, \uparrow}\right) + c^c_- \left(\ket{\uparrow, 0}\right)\right] \\
-	- Vc_{2 \uparrow}\left[c_-^s \left(- \ket{ \uparrow\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow, \uparrow\downarrow}\right)\right] - V c_{2 \downarrow}\left[c_-^s \left(-\ket{ \uparrow\downarrow, \downarrow}\right) + c^c_- \left(\ket{ \downarrow, \uparrow\downarrow}\right)\right]
-\end{aligned}\end{equation}
-We will now write down four equations by comparing the coefficients of \(\ket{ \uparrow}, \ket{ \downarrow}, \ket{0}\) and \(\ket{2}\) of the impurity sector:
-\begin{equation}\begin{aligned}
-	\left( E_g - H_0^* \right) c_-^s \ket{\downarrow} &= V c^c_- \left( c^\dagger_{2 \downarrow}\ket{0} - c_{2 \uparrow}\ket{2} \right) + \frac{1}{2}J c^s_-\left( s^z\ket{ \downarrow} - s^-\ket{\uparrow} \right) && \left[\text{eq.
-from }\ket{\uparrow}\right] \\
-	\left( -E_g + H_0^* \right) c_-^s \ket{\uparrow} &= V c^c_- \left( c^\dagger_{2 \uparrow}\ket{0} - c^\dagger_{2 \downarrow}\ket{2} \right) + \frac{1}{2}J c^s_-\left( s^z\ket{\uparrow} + s^+\ket{ \downarrow} \right)&& \left[\text{eq.
-from }\ket{\downarrow}\right] \\
-	\left( E_g - H_0^* \right) c_-^c \ket{2} &= V c^s_- \left( c^\dagger_{2 \uparrow}\ket{ \downarrow} - c^\dagger_{2 \downarrow}\ket{ \uparrow} \right) + \frac{1}{2}K c^c_-\left( -c^z\ket{2} + c^+\ket{0} \right) && \left[\text{eq.
-from }\ket{0}\right] \\
-	\left( E_g - H_0^* \right) c_-^c \ket{0} &= V c^s_- \left( c_{2 \uparrow}\ket{ \uparrow} + c_{2 \downarrow}\ket{ \downarrow} \right) + \frac{1}{2}K c^c_-\left( c^z\ket{0} + c^-\ket{2} \right) && \left[\text{eq.
-from }\ket{2}\right]
-\end{aligned}\end{equation}
-These can be rearranged into
-\begin{equation}\begin{aligned}
-	\left( E_g - H_0^* - \frac{1}{2}J s^z\right) \ket{\downarrow} &= V \lambda^{-1} \left( c^\dagger_{2 \downarrow}\ket{0} - c_{2 \uparrow}\ket{2} \right) - \frac{1}{2}J s^-\ket{\uparrow} \\
-	\left( E_g - H_0^*  + \frac{1}{2}J s^z\right) \ket{\uparrow} &= V \lambda^{-1} \left( c_{2 \downarrow}\ket{2} - c^\dagger_{2 \uparrow}\ket{0}\right) - \frac{1}{2}J s^+\ket{ \downarrow} \\
-	\left( E_g - H_0^*  + \frac{1}{2}K c^z\right)  \ket{2} &= V \lambda \left( c^\dagger_{2 \uparrow}\ket{ \downarrow} - c^\dagger_{2 \downarrow}\ket{ \uparrow} \right) + \frac{1}{2}K c^+\ket{0}  \\
-	\left( E_g - H_0^* - \frac{1}{2}K c^z\right)  \ket{0} &= V \lambda \left( c_{2 \uparrow}\ket{ \uparrow} + c_{2 \downarrow}\ket{ \downarrow} \right) + \frac{1}{2}K c^-\ket{2} 
-\end{aligned}\end{equation}
-where \(\lambda = \frac{c^s_-}{c^c_-}\). We want to find the effective Hamiltonian in the subspace of \(\ket{\downarrow}\). We first eliminate the charge sector from these equations:
-\begin{equation}\begin{aligned}
-	\ket{0} =& V\lambda\left[\frac{1}{A^K_-}c_{2 \uparrow} + \frac{K}{2}\frac{1}{A^K_-}c^- \frac{1}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left(\frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \uparrow}- c^\dagger_{2 \downarrow}\right)\right]\ket{ \uparrow} \\
-		 &+V\lambda\left[\frac{1}{A^K_-}c_{2 \downarrow} + \frac{K}{2}\frac{1}{A^K_-}c^- \frac{1}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left(c^\dagger_{2 \uparrow} + \frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \downarrow}\right)\right]\ket{ \downarrow}\\
-	\ket{2} &= \frac{V\lambda}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left[\left(c^\dagger_{2 \uparrow} + \frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \downarrow}\right)\ket{ \downarrow} + \left(\frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \uparrow}- c^\dagger_{2 \downarrow}\right)\ket{ \uparrow}\right]
-\end{aligned}\end{equation}
-where
-\begin{equation}\begin{aligned}
-	A^K_\pm = E_g - H_0^* \pm \frac{1}{2}Kc^z
-\end{aligned}\end{equation}
-For ease of labeling, we will think of these equations as
-\begin{equation}\begin{aligned}
-	\ket{0} = a_0^\uparrow \ket{ \uparrow} + a_0^\downarrow\ket{ \downarrow}, \ket{2} = a_2^\uparrow \ket{ \uparrow} + a_2^\downarrow\ket{ \downarrow}
-\end{aligned}\end{equation}
-The remaining two equations can then be written as
-\begin{equation}\begin{aligned}
-	A^J_-\ket{ \downarrow} &= \frac{V}{\lambda}\left[ c^\dagger_{2 \downarrow}\left(a_0^\uparrow \ket{ \uparrow} + a_0^\downarrow\ket{ \downarrow}\right) - c_{2 \uparrow}\left(a_2^\uparrow \ket{ \uparrow} + a_2^\downarrow\ket{ \downarrow}\right) \right] - \frac{J}{2}s^- \ket{ \uparrow}\\
-	A^J_+\ket{\uparrow} &= \frac{V}{\lambda}\left[ c_{2 \downarrow}\left(a_2^\uparrow \ket{ \uparrow} + a_2^\downarrow\ket{ \downarrow}\right) - c^\dagger_{2 \uparrow}\left(a_0^\uparrow \ket{ \uparrow} + a_0^\downarrow\ket{ \downarrow}\right) \right]  - \frac{J}{2}s^+ \ket{ \downarrow}\\
-\end{aligned}\end{equation}
-where 
-\begin{equation}\begin{aligned}
-	A^J_\pm = E_g - H_0^* \pm \frac{1}{2}Js^z
-\end{aligned}\end{equation}
-Eliminating \(\ket{\downarrow}\) and solving for \(\ket{\uparrow}\) gives
-\begin{equation}\begin{aligned}
-	A^J_+ \ket{\uparrow} =&  \frac{V}{\lambda}\left( c_{2 \downarrow}a_2^\uparrow - c^\dagger_{2 \uparrow}a_0^\uparrow \right) \ket{\uparrow} + \left( \frac{V}{\lambda}c_{2 \downarrow}a_2^\downarrow - \frac{V}{\lambda}c^\dagger_{2 \uparrow}a_0^\downarrow - \frac{J}{2}s^+ \right) \ket{\downarrow}\\
-			     =& \frac{V}{\lambda}\left( c_{2 \downarrow}a_2^\uparrow - c^\dagger_{2 \uparrow}a_0^\uparrow \right) \ket{\uparrow} \\
-			     +& \left[ \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow\right) - \frac{J}{2}s^+ \right] \frac{1}{A^J_- - \frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\downarrow - c_{2 \uparrow}a_2^\downarrow \right) }\left[\frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow\right) - \frac{J}{2}s^-\right] \ket{\uparrow}
-\end{aligned}\end{equation}
-The effective Hamiltonian for the \(\ket{\uparrow}\) state is
-\begin{equation}\begin{aligned}
-	\label{full_ham}
-	H_0^* - \frac{J}{2}s^z + \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\uparrow - c^\dagger_{2 \uparrow}a_0^\uparrow \right) + \left[ \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow\right) - \frac{J}{2}s^+ \right] \frac{1}{A^J_- - \frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\downarrow - c_{2 \uparrow}a_2^\downarrow \right) }\\
-	\times\left[\frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow\right) - \frac{J}{2}s^-\right]
-\end{aligned}\end{equation}
-To get a clearer picture of this effective Hamiltonian, we will keep up to two-particle interactions. We first write down the full forms of \(a_{0,2}^\sigma\):
-\begin{equation}\begin{aligned}
-	a_0^\sigma &= V\lambda\left[\frac{1}{A^K_-}c_{2 \sigma} + \frac{K}{2}\frac{1}{A^K_-}c^- \frac{1}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left(\frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \sigma}- \sigma c^\dagger_{2 \sigma}\right)\right]\\
-	a_2^\sigma &= \frac{V\lambda}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left(-\sigma c^\dagger_{2 -\sigma} + \frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \sigma}\right)
-\end{aligned}\end{equation}
-We will first look at the special case of \(K = 0\). There, the above expressions simplify to
-\begin{equation}\begin{aligned}
-	a_0^\sigma &= V\lambda\frac{1}{A^K_-}c_{2 \sigma} = \frac{V \lambda}{E_g}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c_{2\sigma} + \mathcal{O}({H_0^*}^3)\\
-	a_2^\sigma &= -\sigma V\lambda\frac{1}{A^K_+}c^\dagger_{2 -\sigma} = -\sigma\frac{V \lambda}{E_g}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c^\dagger_{2 -\sigma} + \mathcal{O}({H_0^*}^3)\\
-\end{aligned}\end{equation}
-We will make use of the following commutators:
-\begin{equation}\begin{aligned}
-	&\left[\left(H_0^*\right)^m, c_{2\sigma}\right] = - \sum_k \frac{\epsilon^m_k}{\sqrt{N^*}}c_{k\sigma}, && \left[\left(H_0^*\right)^m, c^\dagger_{2\sigma}\right] = \sum_k \frac{\epsilon_k^m}{\sqrt{N^*}}c^\dagger_{k\sigma}, && m = 1, 2\\
-	&\left[\left(H_0^*\right)^m, s^+\right] = \sum_{kk^\prime}\left(\epsilon_k^m - \epsilon_{k^\prime}^m\right)c^\dagger_{k\beta}c_{k^\prime \overline \beta} , &&&& m = 1, 2\\
-	&\left[\left(s^z\right)^m, c_{2\sigma}\right] = - \left(\frac{\sigma}{2}\right)^mc_{2\sigma}, && \left[\left(s^z\right)^m, c^\dagger_{2\sigma}\right] = \left(\frac{\sigma}{2}\right)^mc^\dagger_{2\sigma}, && m = 1, 2\\
-	&\left[\left(c^z\right)^m, c_{2\sigma}\right] = - \left(\frac{1}{2}\right)^mc_{2\sigma}, && \left[\left(c^z\right)^m, c^\dagger_{2\sigma}\right] = \left(\frac{1}{2}\right)^mc^\dagger_{2\sigma}, && m = 1, 2\\
-\end{aligned}\end{equation}
-Now we evaluate the various terms in the effective Hamiltonian.
-\begin{flalign*}
-	{{c_{2 \downarrow}a_2^\uparrow}} &= -\frac{V \lambda}{E_g}c_{2 \downarrow}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c^\dagger_{2\downarrow}\\
-				     &= -\frac{V \lambda}{E_g}\left[c_{2 \downarrow} + \frac{1}{E_g}\left(H_0^* \right)c_{2 \downarrow} + \sum_k \frac{\epsilon_k}{E_g\sqrt{N^*}}c_{k\downarrow} + \frac{1}{E_g^2}\left(H_0^* \right)^2c_{2 \downarrow} + \sum_k \frac{\epsilon^2_k}{E_g^2\sqrt{N^*}}c_{k\downarrow}\right]c^\dagger_{2\downarrow}\\
-				     &= -\frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]c_{2 \downarrow}c^\dagger_{2\downarrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\\
-{{c_{2 \uparrow}a_2^\downarrow }}&= -\frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]c_{2 \uparrow}c^\dagger_{2\uparrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right) c_{k\uparrow}c^\dagger_{k^\prime\uparrow}\\
-{{c^\dagger_{2 \uparrow}a_0^\uparrow}} &= c^\dagger_{2 \uparrow} \frac{V \lambda}{E_g}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c_{2 \uparrow}\\
-					   &= \frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]c^\dagger_{2 \uparrow}c_{2\uparrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c^\dagger_{k\uparrow}c_{k^\prime\uparrow}\\
-{{c^\dagger_{2 \downarrow}a_0^\downarrow}} &= \frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]c^\dagger_{2 \downarrow}c_{2\downarrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\\
-{{c_{2 \downarrow}a_2^\downarrow }}&= \frac{V \lambda}{E_g}c_{2 \downarrow}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c^\dagger_{2\uparrow}\\
-				       &=\frac{V \lambda}{E_g}\left[1 + \frac{1}{E_g}\left(H_0^* \right)\right]c_{2 \downarrow}c^\dagger_{2\uparrow} + \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c_{k\downarrow}c^\dagger_{k^\prime\uparrow}\\
-{{c_{2 \uparrow}a_2^\uparrow}} &=-\frac{V \lambda}{E_g}\left[1 + \frac{1}{E_g}\left(H_0^* \right)\right]c_{2 \uparrow}c^\dagger_{2\downarrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c_{k\uparrow}c^\dagger_{k^\prime\downarrow}\\
-{{c^\dagger_{2 \uparrow}a_0^\downarrow }}&= \frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g}\right]c^\dagger_{2 \uparrow}c_{2\downarrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c^\dagger_{k\uparrow}c_{k^\prime\downarrow}\\
-{{c^\dagger_{2 \downarrow}a_0^\uparrow}} &= \frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g}\right]c^\dagger_{2 \downarrow}c_{2\uparrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c^\dagger_{k\downarrow}c_{k^\prime\uparrow}\\
-{{c_{2 \downarrow}a_2^\uparrow - c^\dagger_{2 \uparrow}a_0^\uparrow}} &= -\frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]\times 2 + \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)\left(c^\dagger_{k\uparrow}c_{k^\prime\uparrow} - c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\right)\\
-{{c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow }}&= \frac{V \lambda}{E_g}\left[1 + \frac{1}{E_g}\left(H_0^* \right)\right]c_{2 \downarrow}c^\dagger_{2\uparrow} \times 2 + \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)\left(c_{k\downarrow}c^\dagger_{k^\prime\uparrow} + c^\dagger_{k\uparrow}c_{k^\prime\downarrow}\right)\\
-{{c^\dagger_{2 \downarrow}a_0^\downarrow - c_{2 \uparrow}a_2^\downarrow}} &= \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)\left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right)\\
-	{{c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow}} &= \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)\left(c_{k\uparrow}c^\dagger_{k^\prime\downarrow} - c^\dagger_{k\downarrow}c_{k^\prime\uparrow}\right)
-\end{flalign*}
-In all the expressions, we have dropped terms that have more than 4 operators in product.
-Also, in the last four equations, we have substituted \(\hat n_{2 \uparrow} - \hat n_{2 \downarrow} = 1\), because this is the effective Hamiltonian for the state with \(s^z = \frac{1}{2}\).
-We now substitute these expressions into the effective Hamiltonian:
-\begin{equation}\begin{aligned}
-	&H_0^* - \frac{J}{2}s^z -\frac{2V^2}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right] + \frac{V^2 }{E_g N^*}\sum_{kk^\prime} \xi_k \left(c^\dagger_{k\uparrow}c_{k^\prime\uparrow} - c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\right) \\
-	&+ \left[ \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow\right)\right] \frac{1}{A^J_- - \frac{V^2}{E_g N^*}\sum_{kk^\prime} \xi_k \left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right) }\left[\frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow\right)\right]\\
-	&+ \left[ \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow\right) \right] \frac{1}{A^J_- - \frac{V^2}{E_g N^*}\sum_{kk^\prime} \xi_k \left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right) }\left[ - \frac{J}{2}s^-\right]\\
-	&+ \left[- \frac{J}{2}s^+ \right] \frac{1}{A^J_- - \frac{V^2}{E_g N^*}\sum_{kk^\prime} \xi_k \left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right) }\left[\frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow\right)\right]\\
-	&+ \frac{J^2}{4}\left[s^+ \right] \frac{1}{A^J_- - \frac{V^2}{E_g N^*}\sum_{kk^\prime} \xi_k \left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right) }\left[s^-\right]\\
-\end{aligned}\end{equation}
-where \(\xi_k = \frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\). We first consider only zeroth order terms of the central propagator.
-\begin{equation}\begin{aligned}
-	&H_0^* - \frac{J}{2}\underbrace{s^z}_{\frac{1}{2}} -\frac{2V^2}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right] + \frac{V^2 }{E_g N^*}\sum_{kk^\prime} \left(\xi_k \right)\left(c^\dagger_{k\uparrow}c_{k^\prime\uparrow} - c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\right) \\
-	&+ \frac{V^4}{E^2_g {N^*}^2 \left( E_g + \frac{J}{4} \right) }\sum_{kk^\prime}\left(\xi_{k^\prime} + 2 - \xi_k \right)c^\dagger_{k\uparrow}c_{k^\prime\downarrow}\sum_{kk^\prime} \left(\xi_k + \xi_{k^\prime}\right)c^\dagger_{k\downarrow}c_{k^\prime\uparrow}\\
-	&+ \frac{V^2 J}{2E_g \left( E_g + \frac{J}{4} \right){N^*}}\sum_{kk^\prime}\left(\xi_{k^\prime} + 2 - \xi_k \right)c^\dagger_{k\uparrow}c_{k^\prime\downarrow}\sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow}\\
-	&+ \frac{JV^2}{2E_g \left( E_g + \frac{J}{4} \right)N^*} \sum_{kk^\prime}c^\dagger_{k \uparrow}c_{k^\prime \downarrow}\sum_{kk^\prime} \left(\xi_k + \xi_{k^\prime}\right)c^\dagger_{k\downarrow}c_{k^\prime\uparrow}\\
-	&+ \frac{J^2}{4\left( E_g + \frac{J}{4} \right)}\underbrace{s^+ s^-}_{s^z + \frac{1}{2}= 1}
-\end{aligned}\end{equation}
-We have set \(s^z = -\frac{1}{2}\) in the denominator, hence the \(E_g = \frac{J}{4}\).
-If we also consider the first and second order terms from the central propagator, note that they will produce terms of more than quartic interactions in the first three terms.
-For the last term, we get
-\begin{equation}\begin{aligned}
-	\frac{J^2}{4\left( E_g + \frac{J}{4} \right)}s^+\left[\frac{H_0^*}{E_g + \frac{J}{4}} + \left(\frac{H_0^*}{E_g + \frac{J}{4}}\right)^2\right]s^-
-\end{aligned}\end{equation}
-Using the commutator of \(H_0^*\) with \(s^+\) to bring \(H_0^*\) to the left, and using \(s^+ s^- = s^z + \frac{1}{2} = 1\), we get
-\begin{equation}\begin{aligned}
-	\frac{J^2}{4\left( E_g + \frac{J}{4} \right)}\left[\frac{H_0^*}{E_g + \frac{J}{4}} + \left(\frac{H_0^*}{E_g + \frac{J}{4}}\right)^2 - \sum_{kk^\prime qq^\prime} \left( \xi_k^J - \xi_{k^\prime}^J \right)  c^\dagger_{k \uparrow}c_{k^\prime \downarrow}c^\dagger_{q \downarrow}c_{q^\prime \uparrow}\right]
-\end{aligned}\end{equation}
-where \(\xi_k^J = \frac{\epsilon_k }{E_g + \frac{J}{4}}+ \frac{\epsilon_k^2}{\left(E_g + \frac{J}{4}\right)^2}\). The full effective Hamiltonian, for \(K=0\), up to quartic interactions, is
-\begin{equation}\begin{aligned}
-	H_0^* + \frac{J}{4}\left(\frac{J}{E_g + \frac{J}{4}} - 1\right) - \frac{2V^2}{E_g} + \frac{V^2 }{E_g N^*}\sum_{kk^\prime} \left(\xi_k \right)\left(c^\dagger_{k\uparrow}c_{k^\prime\uparrow} - c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\right) - \frac{2V^2}{E_g}\left[\frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right] \\
-	+ \frac{J^2}{4\left( E_g + \frac{J}{4} \right) }\left[\frac{H_0^*}{E_g + \frac{J}{4}} + \left(  \frac{H_0^*}{E_g + \frac{J}{4}}\right)^2 \right] + \sum_{kk^\prime q q^\prime} F_{kk^\prime qq^\prime}c^\dagger_{k \uparrow}c_{k^\prime \downarrow}c^\dagger_{q \downarrow}c_{q^\prime \uparrow}
-\end{aligned}\end{equation}
-The coefficient \(F_{kk^\prime qq^\prime}\) is
-\begin{equation}\begin{aligned}
-	\label{off_diag_coeff}
-	F_{kk^\prime qq^\prime} = \frac{V^2}{E_g N^* (E_g + \frac{J}{4})}\left[\frac{V^2}{E_g N^*}\left( \xi_{k^\prime} + 2 - \xi_k \right)\left( \xi_q + \xi_{q^\prime} \right) + \frac{J}{2}\left( \xi_{k^\prime} + 2 - \xi_k + \xi_q + \xi_{q^\prime} \right)  \right] \\
-+ \frac{J^2}{4\left( E_g + \frac{J}{4} \right)} \left(\xi_{k^\prime}^J - \xi_{k}^J\right)
-\end{aligned}\end{equation}
-There are two main types of interactions that gets generated upon integrating out the impurity.
-One is the Fermi liquid type interactions arising from the \({H_0^*}^2\) terms.
-The Fermi liquid part of the Hamiltonian is
-\begin{equation}\begin{aligned}
-	\left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right)^2} - \frac{2V^2}{E_g^2}\right] H_0^* + \left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right)^2} - \frac{2V^2}{E_g^3}\right] {H_0^*}^2 \\
-	= \left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right)^2} - \frac{2V^2}{E_g^2}\right] \left[ H_0^* + \sum_{kk^\prime \sigma \sigma^\prime} f_{kk^\prime} \hat n_{k\sigma} \hat n_{k^\prime \sigma^\prime}\right]
-\end{aligned}\end{equation}
-where the Landau parameter is given by
-\begin{equation}\begin{aligned}
-	\label{fermiliq}
-	f_{kk^\prime} = \left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right)^2} - \frac{2V^2}{E_g^2}\right]^{-1}\left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right) ^3} - \frac{2V^2}{E_g^3}\right]\epsilon_k \epsilon_{k^\prime}
-\end{aligned}\end{equation}
-The more interesting interaction is the off-diagonal term
-\begin{equation}\begin{aligned}
-	 \sum_{kk^\prime q q^\prime} F_{kk^\prime qq^\prime}c^\dagger_{k \uparrow}c_{k^\prime \downarrow}c^\dagger_{q \downarrow}c_{q^\prime \uparrow}
-\end{aligned}\end{equation}
-This interaction arises from the enhanced entanglement between the impurity and the conduction electrons; removing the impurity from the singlet and the triplet generates these off-diagonal scatterings.
-As such, this is an indicator of the macroscopic entanglement of the singlet formed at the IR fixed point, and plotted in fig.~\ref{mutI}.
-
-We also wish to point out that this scattering is a signature of the change in Luttinger's count in going from the free orbital or local moment fixed point to the strong coupling fixed point, as shown in eq.~\eqref{luttinger_change}.
-Both this off-diagonal scattering as well as the change in Luttinger's count are a direct consequence of the non-number conserving term \(V c^\dagger_{k} c_d\) in the full Hamiltonian.
-The topological change of Luttinger's count is concomitant with the presence of the off-diagonal scattering term in the effective Hamiltonian.
-\textit{Just the Fermi liquid piece in eq.~\eqref{fermiliq} will give neither the enhanced mutual information nor the change in Luttinger's count}.
-
-\section{Obtaining the real space low energy Hamiltonian: the local Fermi liquid}
-The next step is to obtain the lowest excitations of the fixed point Hamiltonian, in real space.
-We will work in the \(U>0\) regime.
-For \(V,J \gg 1\), the impurity couples very strongly with the zeroth site, and at zeroth order, it suffices to say that the zeroth site decouples from the rest of the lattice.
-This zeroth Hamiltonian then consists of two sites interacting with each other through \(V\) and \(J\) (the two site problem analysed before).
-\begin{gather}
-	H^*_0 = \sum_{\sigma}\left( V^* c^\dagger_{0\sigma}c_{d\sigma} + \text{h.c.} \right) + J^* \vec{S_d}\cdot\vec{s} - \frac{1}{2}U^*\left( \hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 \\
-	\ket{\Psi}_1 = {c_s} \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + {c_c} \frac{1}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right), \quad E_1 =  -V^*\sqrt{\gamma^2 + 4} -\frac{1}{4}U^* - \frac{3}{8}{J^*}
-\end{gather}
-These were obtained in eq.~\eqref{gstate}. The quantities \(\gamma\) and \(c_{s,c}\) were defined in and around eq.~\eqref{coeff_def}.
-
-We start with the ground state \(\ket{\Psi}_1\) and the star graph as the zeroth level ground state and Hamiltonian, and then add a nearest-neighbour hopping term as a perturbation of the zeroth Hamiltonian.
-We know that the ground state for the interacting part is predominantly the spin-singlet (it was shown while calculating the ground states of the effective zero-mode Hamiltonian that the ground state is a mixture of singlet and triplet, and the triplet part dies out at large system sizes, see eq.~\eqref{gstate_kondo}), so we will take that as our reference state and treat the hopping part that connects the origin to the first site,
-\begin{equation}\begin{aligned}
-	H_X = t\sum_{\vec r_1,\sigma} c^\dagger_{0\sigma}c_{\vec r_1,\sigma} +\text{h.c.} \equiv v^\dagger + v
-\end{aligned}\end{equation}
-as a weak perturbation.
-\(\vec r_1\) here sums over the sites that are nearest to the origin.
-Once this perturbation is taken care of up to a certain order, we will have a decoupled singlet formed by the impurity and the zeroth site, and the rest of the lattice formed by \(N-1\) sites along with the interaction induced by the perturbation.
-To be precise, the goal is to integrate out the perturbation and generate an effective Hamiltonian in the subspace of the minimal energy states of the two site Hamiltonian, and this effective Hamiltonian will therefore describe the lowest excitations on top of the ground state \(\ket{\Psi}_1\).
-The minimal energy subspace is given by the states:
-\begin{equation}\begin{aligned}
-	\ket{\Phi}_{i} = \ket{\Psi}_1 \otimes \ket{\hat n_{1 \uparrow}, \hat n_{1 \downarrow}}, ~\text{ where }i \in \begin{cases}
-		0: & \hat n_{1 \uparrow} = \hat n_{1 \downarrow} = 0\\
-		1: & 1 - \hat n_{1 \uparrow} =  \hat n_{1 \downarrow} = 0\\
-		2: & \hat n_{1 \uparrow} = 1 - \hat n_{1 \downarrow} = 0\\
-		3: & 1 - \hat n_{1 \uparrow} =  1 - \hat n_{1 \downarrow} = 0
-	\end{cases} 
-\end{aligned}\end{equation}
-
-The effective Hamiltonian will be calculated using perturbation theory in \(\frac{H_X^{n}}{{H_0^*}^{n-1}}\).
-Since an odd number of scattering processes cannot bring the initial state back to itself, such orders will be absent from the effective Hamiltonian.
-
- \subsection{Second order effective Hamiltonian}
- We first consider the case of \(n=2\). The renormalisation of the effective Hamiltonian in the ground state subspace, at this order, is given by
-\begin{equation}\begin{aligned}
-	\Delta H = \sum_{ij,n}\ket{\Phi}_i \bra{\Phi_i}H_X \ket{\Psi}_n \frac{1}{E_\text{gs} - E_n} \bra{\Psi}_n H_X \ket{\Phi}_j \bra{\Phi_j} = \sum_{ij}\ket{\Phi}_i \bra{\Phi_j} \bra{\Phi_i}v + v^\dagger \ket{\Psi}_n \frac{1}{E_\text{gs} - E_n} \bra{\Psi}_n v + v^\dagger \ket{\Phi}_j~.
-\end{aligned}\end{equation}
-Here, \(\ket{\Psi}_n\) are the eigenstates of the two site problem, with eigenvalue \(E_n\).
-The total scattering process can be described as \(H_X\) acting on \(\ket{\Phi}_j\) to excite to \(\ket{\Psi}_n\), and then a subsequent \(H_X\) acting on \(\ket{\Psi}_n\) to decay back to \(\ket{\Phi}_j\) and into the ground state manifold.
-Since \(\ket{\Phi}_{i,j}\) are eigenstates of the two site Hamiltonian, they are all eigenstates of the total number operator \(\hat n_{d0} = \sum_\sigma \left(\hat n_{d\sigma} + \hat n_{0\sigma}\right) \) for the two site model, with eigenvalue \(2\).
-Since we are to finally return to the ground state manifold, only those processes in \(H_X^2\) are allowed that conserve \(\hat n_{d0}\).
-These processes are \(v, v^\dagger\) and \(v^\dagger,v\).
-This also means that the total number of particles on site 1 will remain constant in the process, and we wil have \(\ket{\Phi}_i = \ket{\Phi}_j\).
-\begin{equation}\begin{aligned}
-	\Delta H = \sum_{i}\ket{\Phi}_i \bra{\Phi_i} \frac{1}{E_\text{gs} - E_n} \left(\bra{\Phi_i}v^\dagger \ket{\Psi}_n \bra{\Psi}_n v \ket{\Phi}_i + \bra{\Phi_i} v \ket{\Psi}_n \bra{\Psi}_n v^\dagger \ket{\Phi}_i\right) ~.
-\end{aligned}\end{equation}
-If we define the matrix element \(v_{ni} \equiv \bra{\Psi}_n v \ket{\Phi}_i\) of \(v\) and the excitation energy \(\delta E_{n} = E_n - E_\text{gs}\), we can write the renormalisation as
-\begin{equation}\begin{aligned}
-	\Delta H = \sum_{i,n}\frac{|v_{ni}|^2 + |v_{in}|^2}{-\delta E_{n}} \ket{\Phi}_i \bra{\Phi_i}~.
-\end{aligned}\end{equation}
-
-We now look at each \(\ket{\Phi_i}\) separately. For \(\ket{\Phi_i} = \ket{\Phi}_0 = \ket{\Psi}_1 \otimes \ket{0,0}\), we can write
-\begin{equation}\begin{aligned}
-	v^\dagger \ket{\Phi}_i = 0, ~ v \ket{\Phi}_i = \frac{t}{\sqrt 2}\sum_\sigma \overline\sigma\left({c_s^-} \ket{\sigma, 0} + {c_c^-} \ket{0, \sigma}\right) \ket{\overline\sigma}
-\end{aligned}\end{equation}
-The first relation gives \(v_{in} = \bra{\Phi}_i v \ket{\Psi}_n = \left(\bra{\Psi}_n v^\dagger \ket{\Phi}_i\right)^* = 0\).
-The set of states that give non-zero \(v^\dagger_{in}\) are specific elements of the set of eigenstates that have a total of either 1 or 3 electrons on the impurity and zeroth sites:
-\begin{equation}\begin{aligned}
-	\ket{\Psi}_n = \ket{\Psi}_{\pm,\sigma}^{s, p} = -\sqrt 2\left(a_{1,\pm}\ket{\sigma,p} + a_{2,\pm} \ket{p,\sigma}\right)\otimes\ket{s},~~ \sigma = \uparrow,\downarrow, ~~ E^{s,p}_{\pm, \sigma} = -\frac{U}{4} \pm \frac{1}{2}\Delta~;
-\end{aligned}\end{equation}
-here, \(s\) is a string from the set \(\left\{0, \uparrow, \downarrow, 2\right\} \) and represents the configuration of the first site \(\ket{s}\) in direct product with the impurity and zeroth site entangled composite state, and \(p\) is either \(2\) or 0 such that \(p+1 (= 1\text{ or }3)\) represents the total number of electrons on the impurity and zeroth sites.
-For \(\ket{\Phi}_0\), only \(s=\overline\sigma\) and \(p=0\) give non-zero inner product.
-The coefficients are defined as \(a_{1,\pm}=\frac{4V}{\sqrt 2 \mathcal{N}_\pm}, a_{2,\pm}=\frac{U \pm 2\Delta}{\sqrt 2 \mathcal{N}_\pm}\).
-The inner product is
-\begin{equation}\begin{aligned}
-	\label{vni}
-	v_{\pm\sigma,i} = \braket{\Psi_{\pm,\sigma}^{\overline\sigma,0} | v | \Phi_i} = \sigma t \left[a_{1,\pm}{c_s^-} + a_{2,\pm} {c_c^-}\right]
-\end{aligned}\end{equation}
-\(\mathcal{N}_\pm = \sqrt{16V^2 + \left(U \pm 2\Delta\right)^2}\) is the normalisation factor and \(\Delta = \frac{1}{2}\sqrt{U^2 + 16V^2}\). The renormalisation for this value of \(i\) then becomes
-\begin{equation}\begin{aligned}
-	\label{eff_ham_0}
-	\left(\Delta H\right)_{i=0} = \ket{\Phi}_0 \bra{\Phi}_0 \sum_{n}\frac{|v_{ni}|^2}{-\delta E_{n}} = \ket{\Phi}_0 \bra{\Phi}_0 \sum_{\sigma,\pm}\frac{|v_{\pm\sigma,i}|^2}{-\delta E_{\pm}^\sigma} = -\ket{\Phi}_0 \bra{\Phi}_0 2t^2\sum_{\pm}\frac{\left[a_{1,\pm}{c_s^-} + a_{2,\pm} {c_c^-}\right]^2}{\delta E_{\pm}^\sigma}
-\end{aligned}\end{equation}
-where \(\delta E_{\pm}^\sigma = E^\sigma_{\pm} - E_\text{gs}\).
-
-For \(i=1\), we have \(\ket{\Phi}_1 = \ket{\Psi}_1 \otimes \ket{\uparrow}\). Carrying out a similar calculation above, we get
-\begin{gather}
-	v\ket{\Phi}_1 = t \frac{1}{\sqrt 2}\left({c_s^-}\ket{\uparrow, 0, 2} + {c_c^-}\ket{0, \uparrow, 2}\right), ~ ~ ~\ket{\psi}_n = \ket{\Psi}^{2,0}_{\pm,\uparrow}, ~ ~ ~ v_{ni} = -t\left({c_s^-} a_{1,\pm} + {c_c^-} a_{2,\pm}\right) \label{vvdag_i1}\\
-	v^\dagger\ket{\Phi}_1 = t \frac{1}{\sqrt 2}\left({c_s^-}\ket{\uparrow, 2, 0} - {c_c^-}\ket{2, \uparrow, 0}\right), ~ ~ ~\ket{\psi}_n = \ket{\Psi}^{0,2}_{\pm,\uparrow}, ~ ~ ~ v_{in} = -t\left({c_s^-} a_{1,\pm} - {c_c^-} a_{2,\pm}\right)\label{vvdag_i1_2}\\
-	\left(\Delta H\right)_{i=1} = -\ket{\Phi}_1 \bra{\Phi}_1 2t^2\sum_{\pm}\frac{a_{1,\pm}^2 {c_s^-}^2 + a_{2,\pm}^2 {c_c^-}^2}{\delta E_{\pm}^\sigma}
-\end{gather}
-
-The total Hamiltonian \(H_0^* + H_X\) is invariant under the transformations \(c^\dagger_\sigma \to c_\sigma, t \to -t\).
-Since the renormalisation only involves even powers of \(t\), we can conclude that the renormalisation for \(i=2\)  and \(i=3\) will be the same as that of \(i=1\) and \(i=0\) respectively.
-The total renormalisation at second order is
-\begin{equation}\begin{aligned}
-	\Delta H &= -\sum_{i=0}^3\ket{\Phi}_i \bra{\Phi}_i 2t^2\sum_{\pm}\frac{a_{1,\pm}^2 {c_s^-}^2 + a_{2,\pm}^2 {c_c^-}^2}{\delta E_{\pm}^\sigma} - \left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right)4t^2\sum_{\pm}\frac{a_{1,\pm} a_{2,\pm} {c_s^-} {c_c^-}}{\delta E_{\pm}^\sigma}\\
-		 &= -\sum_{i=0}^3\ket{\Phi}_i \bra{\Phi}_i t^2\sum_{\pm}\frac{1}{\mathcal{N}_\pm^2}\frac{\left(4V{c_s^-}\right)^2 + \left(U \pm 2\Delta\right)^2 {c_c^-}^2}{\delta E_{\pm}^\sigma} - \left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right)\sum_{\pm}\frac{t^2}{\mathcal{N}_\pm^2}\frac{8V {c_s^-} \left(U \pm 2\Delta\right) {c_c^-}}{\delta E_{\pm}^\sigma}
-\end{aligned}\end{equation}
-Since the \(\ket{\hat n_{1\sigma}, \hat n_{1\overline\sigma}}\) form a complete set, we have \(\sum_{i=0}^3\ket{\Phi}_i \bra{\Phi}_i = \ket{\Psi}_1 \bra{\Psi}_1\), and the first term becomes a constant.
-The second term is a local Fermi liquid term on the first site:
-\begin{equation}\begin{aligned}
-	\Delta H &= \ket{\Psi}_1 \bra{\Psi}_1\left[\mathrm{constant} - \left\{\hat n_{1 \uparrow}\hat n_{1 \downarrow} + \left(1 - \hat n_{1 \uparrow}\right) \left(1 - \hat n_{1 \downarrow}\right)\right\}\sum_{\pm}\frac{t^2}{\mathcal{N}_\pm^2}\frac{8V {c_s^-} \left(U \pm 2\Delta\right) {c_c^-}}{\delta E_{\pm}^\sigma}\right]\\
-		 &= \ket{\Psi}_1 \bra{\Psi}_1\left[\mathrm{constant} + \left(\hat n_{1 \uparrow} - \hat n_{1 \downarrow}\right)^2 \sum_{\pm}\frac{t^2}{\mathcal{N}_\pm^2}\frac{8V {c_s^-} \left(U \pm 2\Delta\right) {c_c^-}}{\delta E_{\pm}^\sigma}\right]\\
-\end{aligned}\end{equation}
-
-In the strong coupling regime, we have \(J,V \gg U\), and we can then approximate:
-\begin{equation}\begin{aligned}
-	\delta E_{\pm}^\sigma \simeq \frac{3J}{8} + \sqrt{4V^2 - \left(\frac{3J}{8}\right)^2} \mp V, ~~U \pm 2\Delta \simeq \pm 4V, \text{ and }~~ \mathcal{N}_\pm^2 \simeq 32V^2
-\end{aligned}\end{equation}
-Substituting this gives
-\begin{equation}\begin{aligned}
-	\Delta H = \ket{\Psi}_1 \bra{\Psi}_1\left[\mathrm{constant} - \left(\hat n_{1 \uparrow} - \hat n_{1 \downarrow}\right)^2 \frac{2t^2V {c_s^-} {c_c^-}}{2\left(\frac{3J}{8}\right)^2 + 3V^2 + \frac{3J}{4}\sqrt{4V^2 + \left(\frac{3J}{8}\right)^2}}\right]\\
-\end{aligned}\end{equation}
-
-\subsection{Fourth order effective Hamiltonian}
-Using fourth order perturbation theory, we can write the effective Hamiltonian renormalisation at that order in the form
-\begin{equation}\begin{aligned}
-	\label{eff_ham_4}
-	\Delta H &= -\sum_{i}\ket{\Phi}_i\bra{\Phi}_i\left[\sum_{lmn}\frac{\braket{\Phi_i | H_X | \Psi_l}\braket{\Psi_l | H_X | \Psi_m}\braket{\Psi_m | H_X | \Psi_n}\braket{\Psi_n | H_X | \Phi_i}}{\delta E_l ~ \delta E_m ~ \delta E_n} + \Delta^{(2)}H \sum_{n} \frac{|\braket{\Psi_n | H_X | \Phi_i}|^2}{\left(\delta E_n\right)^2}\right]~,\\
-		 &= -\sum_{i}\ket{\Phi}_i\bra{\Phi}_i\left[\sum_{m}\frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 + \Delta^{(2)}H \sum_{n} \frac{1}{\left(\delta E_n\right)^2}\big\Vert\left(H_X\right)_{ni}\big\Vert^2\right]~.
-\end{aligned}\end{equation}
-We can have at most two successive \(v^\dagger\) or two successive \(v\) act on a particular state.
-Any more would lead to \(c^\dagger_\sigma \ket{\hat n_\sigma =2} = 0\).
-This limits the possible scattering processes (in the first term) to the following channels:
-\begin{equation}\begin{aligned}
-	a.~v v^\dagger v v^\dagger,~~b.~v^\dagger v v^\dagger v,~~c.~v v v^\dagger v^\dagger,~~d.~v^\dagger v^\dagger v v~.
-\end{aligned}\end{equation}
-
-We start with \(i=0\).
-Out of the four channels \(a\) through \(d\), only \(b\) and \(d\) survive.
-For \(i=0\), we already know the relevant \(\ket{\Psi}_n\) and hence the \(\left(H_X\right)_{ni} = v_{ni}\), from eq.~\eqref{vni}.
-\begin{equation}\begin{aligned}
-	v_{\pm\sigma,i} = \braket{\Psi_{\pm,\sigma}^{\overline\sigma,0} | v | \Phi_i} = \sigma t \left[a_{1,\pm}{c_s^-} + a_{2,\pm} {c_c^-}\right] = \sigma t \mathcal{S}^-_\pm
-\end{aligned}\end{equation}
-where we have defined the sum and difference \(\mathcal{S}^\pm_\pm = a_{1,\pm}{c_s^\pm} + a_{2,\pm} {c_c^\pm}, ~ ~ \mathcal{D}^\pm_\pm = a_{1,\pm}{c_s^\pm} - a_{2,\pm} {c_c^\pm}\).
-For channel \(b\), we then proceed as follows:
-\begin{gather}
-	\ket{\Psi}_{\pm,\sigma}^{\overline\sigma, 0} = -\sqrt 2\left(a_{1,\pm}\ket{\sigma,0} + a_{2,\pm} \ket{0,\sigma}\right)\otimes\ket{\overline\sigma}\\
-	v^\dagger\ket{\Psi}_n = v^\dagger\ket{\Psi}^{\overline\sigma,0}_{\pm,\sigma} = \sqrt 2 t \left(a_{1,\pm}\ket{\sigma,\overline\sigma} + a_{2,\pm} \ket{0,\sigma\overline\sigma}\right)\otimes\ket{0}\\
-	\ket{\Psi}_m = \begin{cases}
-	\frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow})\right)\otimes\ket{0} \\
-	\frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2})\right)\otimes\ket{0}\\ 
-	\left[ \frac{c^+_s}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) +  \frac{c^+_c}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right] \otimes\ket{0}
-	\end{cases}
-	\implies \left(H_X\right)_{m,\pm\sigma} = \begin{cases}
-		t a_{1\pm}\\
-		\overline\sigma t a_{2\pm}\\
-		\sigma t \left(a_{1\pm} {c_s^+} + a_{2\pm}{c_c^+}\right) = \sigma t \mathcal{S}^+_\pm
-	\end{cases}\label{psi_m}\\
-	 \frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 = \begin{cases}
-	 \frac{1}{\delta E_\mathrm{ST}}\left(\sum_{\sigma,\pm}\frac{t^2}{\delta E_\pm}\sigma a_{1\pm}\mathcal{S}^-_\pm\right)^2 = 0\\
-	 \frac{1}{\delta E_\mathrm{CS}}\left(\sum_{\pm,\sigma} \frac{t^2}{\delta E_\pm}a_{2\pm}\mathcal{S}^-_\pm\right)^2 =  \frac{4t^4}{\delta E_\mathrm{CS}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{2\pm}\mathcal{S}^-_\pm\right)^2\\
-	 \frac{1}{\delta E_\mathrm{2}}\left(-\sum_{\pm,\sigma}\frac{t^2}{\delta E_\pm}\mathcal{S}^+_\pm\mathcal{S}^-_\pm\right)^2 = \frac{4t^4}{\delta E_\mathrm{2}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}\mathcal{S}^+_\pm\mathcal{S}^-_\pm\right)^2
-	\end{cases}
-\end{gather}
-\(E_\mathrm{ST}, E_\mathrm{CS}\) and \(E_2\) are the energies of the spin triplet zero, charge singlet and spin singlet+charge triplet excited states of the set \(\ket{\Psi}_m\) in eq.~\eqref{psi_m}.
-
-We now turn to channel \(d\):
-\begin{gather}
-	v\ket{\Psi}_n = v\ket{\Psi}^{\overline\sigma,0}_{\pm,\sigma} = \sqrt 2 t \sigma a_{2\pm} \ket{0,0}\otimes\ket{2},~ ~ ~\ket{\Psi}_m = \ket{0,0,2}, ~ ~ ~ \left(H_X\right)_{m,\pm\sigma} = \sqrt 2 t \sigma a_{2\pm}\\
-\frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 = \frac{8t^4}{\delta E_{00}} \left(\sum_\pm \frac{1}{\delta E_\pm}a_{2\pm}\mathcal{S}^-_\pm\right)^2
-\end{gather}
-\(E_{00}\) is the energy of the state \(\ket{0,0,2}\).
-
-Having accounted for both channels, we will calculate the second part of the effective Hamiltonian in eq.~\eqref{eff_ham_4}, the part involving \(\Delta^{(2)} H\).
-We already know, from eq.~\eqref{eff_ham_0}, that
-\begin{equation}\begin{aligned}
-	\Delta^{(2)} H_{i=0} = -2t^2\sum_\pm \frac{1}{\delta E_\pm}\left(\mathcal{S}^-_\pm\right)^2
-\end{aligned}\end{equation}
-Also, from the expression of \(v_{\pm\sigma,i}\), we get
-\begin{equation}\begin{aligned}
-	\sum_{n} \frac{1}{\left(\delta E_n\right)^2}\big\Vert\left(H_X\right)_{ni}\big\Vert^2 =	\sum_{\pm} \frac{2t^2}{\left(\delta E_\pm\right)^2}\left(\mathcal{S}^-_\pm\right)^2
-\end{aligned}\end{equation}
-Combining it all, the total renormalisation in \(i=0\) is
-\begin{equation}\begin{aligned}
-	- \ket{\Phi}_0 \bra{\Phi}_0 4t^4\left[ \left(\frac{1}{\delta E_\mathrm{CS}} + \frac{2}{\delta E_{00}}\right)  \left(\sum_{\pm}\frac{a_{2\pm}\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \frac{1}{\delta E_\mathrm{2}}\left(\sum_{\pm}\frac{\mathcal{S}^+_\pm\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 - \sum_\pm \frac{\left(\mathcal{S}^-_\pm\right)^2}{\delta E_\pm}\sum_{\pm} \left(\frac{\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2\right]\\
-\end{aligned}\end{equation}
-
-We now come to \(i=1\): \(\ket{\Phi}_1 = \ket{\Psi}_1 \otimes \ket{\uparrow}\).
-Channels \(a\) and \(b\) are non-zero here.
-We start with channel \(b: v^\dagger v v^\dagger v\).
-We already know, from eq.~\eqref{vvdag_i1}, that
-\begin{gather}
-v\ket{\Phi}_1 = t \frac{1}{\sqrt 2}\left({c_s^-}\ket{\uparrow, 0, 2} + {c_c^-}\ket{0, \uparrow, 2}\right), ~ ~ ~ \ket{\psi}_n = \ket{\Psi}^{2,0}_{\pm,\uparrow} = -\sqrt 2\left(a_{1,\pm}\ket{\uparrow,0} + a_{2,\pm} \ket{0,\uparrow}\right)\otimes\ket{2}, ~ ~ ~ \left(H_X\right)_{ni} = -t \mathcal{S}^-_\pm
-\end{gather}
-Moving forward:
-\begin{gather}
-v^\dagger \ket{\Psi}_n = \sqrt 2 t \left(a_{1,\pm}\ket{\uparrow,\uparrow}\otimes\ket{\downarrow} - a_{1,\pm}\ket{\uparrow,\downarrow}\otimes\ket{\uparrow} - a_{2,\pm} \ket{0,2}\otimes\ket{\uparrow}\right)\\
-	\ket{\Psi}_m = \begin{cases}
-	\frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow})\right)\otimes\ket{\uparrow} \\
-	\frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2})\right)\otimes\ket{\uparrow}\\ 
-	\left[ \frac{c^+_s}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) +  \frac{c^+_c}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right] \otimes\ket{\uparrow}\\
-	\ket{\uparrow,\uparrow}\otimes\ket{\downarrow}
-	\end{cases}
-	\implies \left(H_X\right)_{m,\pm}\left(H_X\right)_{\pm,i} = \begin{cases}
-		t^2 a_{1\pm} \mathcal{S}^-_\pm\\
-		-t^2 a_{2\pm}\mathcal{S}^-_\pm\\
-		t^2 \mathcal{S}^+_\pm\mathcal{S}^-_\pm\\
-		-\sqrt 2 t^2 a_{1\pm}\mathcal{S}^-_\pm
-	\end{cases}\\
-	\frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 = \begin{cases}
-	 \frac{t^4}{\delta E_\mathrm{ST}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{1\pm}\mathcal{S}^-_\pm\right)^2 \\
-	 \frac{t^4}{\delta E_\mathrm{CS}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{2\pm}\mathcal{S}^-_\pm\right)^2\\
-	 \frac{t^4}{\delta E_\mathrm{2}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}\mathcal{S}^+_\pm\mathcal{S}^-_\pm\right)^2\\
-	 \frac{2 t^4}{\delta E_\mathrm{\uparrow \uparrow}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{1\pm}\mathcal{S}^-_\pm\right)^2\\
-	\end{cases}
-\end{gather}
-\(E_{\uparrow \uparrow}\) is the energy of the upwards polarised state \(\ket{\uparrow,\uparrow}\otimes\ket{\downarrow}\).
-
-Next is channel \(a : v v^\dagger v v^\dagger\). Using eq.~\eqref{vvdag_i1_2} and following the same steps as above, we get:
-\begin{gather}
-	v^\dagger\ket{\Phi}_1 = t \frac{1}{\sqrt 2}\left({c_s^-}\ket{\uparrow, 2, 0} - {c_c^-}\ket{2, \uparrow, 0}\right), ~ ~ ~\ket{\Psi}_n = \ket{\Psi}^{0,2}_{\pm,\uparrow} = -\sqrt 2\left(a_{1,\pm}\ket{\uparrow,2} + a_{2,\pm} \ket{2,\uparrow}\right)\otimes\ket{0}, ~ ~ ~ \left(H_X\right)_{ni} = -t \mathcal{D}^-_\pm\\
-	v \ket{\Psi}_n = \sqrt 2 t\left(a_{1,\pm}\ket{\uparrow,\uparrow}\otimes\ket{\downarrow} - a_{1,\pm}\ket{\uparrow,\downarrow}\otimes\ket{\uparrow} + a_{2,\pm} \ket{2,0}\otimes\ket{\uparrow}\right)\\
-		\ket{\Psi}_m = \begin{cases}
-		\frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow})\right)\otimes\ket{\uparrow} \\
-		\frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2})\right)\otimes\ket{\uparrow}\\ 
-		\left[ \frac{c^+_s}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) +  \frac{c^+_c}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right] \otimes\ket{\uparrow}\\
-		\ket{\uparrow,\uparrow}\otimes\ket{\downarrow}
-		\end{cases}
-		\implies \left(H_X\right)_{m,\pm}\left(H_X\right)_{\pm,i} = \begin{cases}
-			t^2 a_{1\pm} \mathcal{D}^-_\pm\\
-			-t^2 a_{2\pm}\mathcal{D}^-_\pm\\
-			t^2 \mathcal{D}^+_\pm\mathcal{D}^-_\pm\\
-			-\sqrt 2 t^2 a_{1\pm}\mathcal{D}^-_\pm
-		\end{cases}\\
-		\frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 = \begin{cases}
-		\frac{1}{\delta E_\mathrm{ST}}\left(\sum_{\pm}\frac{t^2}{\delta E_\pm}a_{1\pm}\mathcal{D}^-_\pm\right)^2 \\
-		\frac{t^4}{\delta E_\mathrm{CS}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{2\pm}\mathcal{D}^-_\pm\right)^2\\
-		\frac{t^4}{\delta E_\mathrm{2}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}\mathcal{D}^+_\pm\mathcal{D}^-_\pm\right)^2\\
-		\frac{2 t^4}{\delta E_\mathrm{\uparrow \uparrow}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{1\pm}\mathcal{D}^-_\pm\right)^2\\
-		\end{cases}
-\end{gather}
-
-For the final part, we again use \(\Delta^{(2)} H_{i=1} = -t^2\sum_\pm \frac{1}{\delta E_\pm} \left[\left(\mathcal{S}^-_\pm\right)^2 + \left(\mathcal{D}^-_\pm\right)^2\right]\).
-Also, since \(\left(H_X\right)_{ni} = \left(v + v^\dagger\right)_{ni}\), we have
-\begin{equation}\begin{aligned}
-\sum_{n} \frac{1}{\left(\delta E_n\right)^2}\big\Vert\left(H_X\right)_{ni}\big\Vert^2 =	t^2\sum_{\pm} \left[\left(\frac{\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \left(\frac{\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right]
-\end{aligned}\end{equation}
-
-Combining all the terms, we get
-\begin{equation}\begin{aligned}
-	- \ket{\Phi}_1 \bra{\Phi}_1 4t^4\left[\left(\frac{1}{\delta E_\mathrm{ST}} + \frac{2}{\delta E_{\uparrow \uparrow}}\right) \left\{\left(\frac{1}{2}\sum_{\pm}\frac{a_{1\pm}\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \left(\frac{1}{2}\sum_{\pm}\frac{a_{1\pm}\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right\} + \frac{1}{\delta E_\mathrm{CS}} \left\{\left(\frac{1}{2}\sum_{\pm}\frac{a_{2\pm}\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2  \right.
-\right.\\
-	+ \left.
-\left.
-\left(\frac{1}{2}\sum_{\pm}\frac{a_{2\pm}\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right\} + \frac{1}{\delta E_\mathrm{2}}\left\{\left(\frac{1}{2}\sum_{\pm}\frac{\mathcal{S}^+_\pm\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \left(\frac{1}{2}\sum_{\pm}\frac{\mathcal{D}^+_\pm\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right\} \right.
-\\
-- \left.\sum_\pm \frac{1}{\delta E_\pm} \frac{1}{2}\left\{\left(\mathcal{S}^-_\pm\right)^2 + \left(\mathcal{D}^-_\pm\right)^2\right\}\sum_\pm \frac{1}{2}\left\{\left(\frac{\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \left(\frac{\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right\}\right]\\
-\end{aligned}\end{equation}
-If we define some quantities: \(F_{(1,2)} = \sum_{\pm}\frac{a_{(1,2)\pm}\mathcal{S}^-_\pm}{\delta E_\pm}, G_{(1,2)} = \sum_{\pm}\frac{a_{(1,2)\pm}\mathcal{D}^-_\pm}{\delta E_\pm}, P = \sum_{\pm}\frac{\mathcal{S}^+_\pm\mathcal{S}^-_\pm}{\delta E_\pm}, Q = \sum_{\pm}\frac{\mathcal{D}^+_\pm\mathcal{D}^-_\pm}{\delta E_\pm}, X_n = \sum_\pm \frac{\left(\mathcal{S}_\pm^-\right)^2}{\left(\delta E_\pm\right)^n}, Y_n = \sum_\pm \frac{\left(\mathcal{D}_\pm^-\right)^2}{\left(\delta E_\pm\right)^n}\), the total renormalisation from second and fourth order can be written as
-\begin{gather}
-	-\left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right) 4t^4 \left[\frac{1}{2t^2}X_1 + \left(\frac{1}{\delta E_\mathrm{CS}} + \frac{2}{\delta E_{00}}\right) F_{2}^2 + \frac{1}{\delta E_\mathrm{2}}P^2 - X_1 X_2\right]\nonumber\\
-	- \left(\ket{\Phi}_1 \bra{\Phi}_1 + \ket{\Phi}_2 \bra{\Phi}_2\right) t^4\left[\frac{1}{t^2}\left(X_1 + Y_1\right) + \left(\frac{1}{\delta E_\mathrm{ST}} + \frac{2}{\delta E_{\uparrow \uparrow}}\right) \left(F_1^2 + G_1^2\right) + \frac{1}{\delta E_\mathrm{CS}} \left(F_2^2 + G_2^2\right)\right.\nonumber\\
-\left. + \frac{1}{\delta E_\mathrm{2}} \left(P^2 + Q^2\right) - \left(X_1 + Y_1\right) \left(X_2 + Y_2\right)\right]
-\end{gather}
-The excitation energies are given by
-\begin{equation}
-	\delta E_\mathrm{CS} = \delta E_{00} = \frac{3J}{8} + \frac{U}{4} + \alpha, ~ ~ \delta E_{\uparrow \uparrow} = \delta E_\mathrm{ST}  = -\frac{U}{4} + \frac{5J}{8} + \alpha, ~ ~ \delta E_2 = 2\alpha, ~ ~ \delta E_\pm = \frac{3J}{8} + \alpha \pm \frac{1}{2}\Delta, ~ ~ \alpha \equiv \sqrt{V^2 \gamma^2 + 4V^2}
-\end{equation}
-where \(V\gamma = \frac{3J}{8} + \frac{U}{4}\) and \(\Delta = \sqrt{\frac{U^2}{4} + 4V^2}\). The effective Hamiltonian can be expressed in the general form
-\begin{equation}
-	H_\text{eff} = \ket{\Psi}_1\bra{\Psi}_1\otimes \left[\text{constant} + \alpha_\text{spin} \mathcal{\hat{P}}_\text{spin} + \alpha_\text{charge} \mathcal{\hat{P}}_\text{charge}\right] 
-\end{equation}
-\(\mathcal{\hat  P}_\text{charge}\) and \(\mathcal{\hat P}_\text{spin}\) are projection operators for, respectively, the charge \((\hat n_1 \neq 1)\) and spin \(\left(\hat n_1=1\right) \) sectors of the first site.
-Since \(\mathcal{\hat P}_\text{charge} + \mathcal{\hat P}_\text{spin} = 1\), we can eliminate one of the terms and rewrite the effective Hamiltonian in the simpler form
-\begin{equation}\begin{aligned}
-	H_\text{eff} = \ket{\Psi}_1\bra{\Psi}_1\otimes \left[\text{constant} + \mathcal{F} \mathcal{\hat P}_\text{charge}\right] 
-\end{aligned}\end{equation}
-where \(\mathcal{F} \equiv \alpha_\text{charge} - \alpha_\text{spin}\) is the net energy of the charge sector above the spin sector.
-
-We will now look at the extreme strong coupling regime \(J \gg V \gg U,t\). There, all the expressions simplify:
-\begin{gather}
-	V\gamma \simeq \frac{3J}{8},~ ~ \Delta \simeq 2V,~ ~ \alpha \simeq \frac{3J}{8}, ~ ~ c_s^+ = -c_c^- \simeq 0, ~ ~ c_s^- = c_c^+ \simeq 1, ~ ~ \mathcal{N}_\pm \simeq 4\sqrt 2 V, ~ ~ a_{1,\pm} \simeq \frac{1}{2}, ~ ~ a_{2,\pm} \simeq \pm \frac{1}{2}~,\nonumber\\
-	\delta E_\pm = \delta E_\mathrm{CS} = \delta E_{00} = \delta E_2 \simeq \frac{3J}{4}, ~ ~ \delta E_\mathrm{ST} = \delta E_{\uparrow \uparrow} \simeq J, ~ ~ \mathcal{S}^-_\pm = \mathcal{D}^-_\pm \simeq \frac{1}{2}, ~ ~ \mathcal{S}^+_\pm = -\mathcal{D}^+_\pm \simeq \pm \frac{1}{2},~\nonumber\\
-	F_1 = G_1 \simeq \frac{2}{3J}, ~ ~ F_2 = G_2 \simeq 0, ~ ~ P = Q \simeq 0,~ ~ X_1 = Y_1 \simeq \frac{2}{3J}, ~ ~ X_2 = Y_2 \simeq \frac{8}{9J^2}
-\end{gather}
-The effective Hamiltonian becomes
-\begin{equation}\begin{aligned}
-	&-\left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right) \frac{4t^2}{3J}\left[1 - \frac{16 t^2}{9 J^3}\right] - \left(\ket{\Phi}_1 \bra{\Phi}_1 + \ket{\Phi}_2 \bra{\Phi}_2\right) \frac{4t^2}{3J}\left[1 + \frac{2t^2}{9 J^2} \right]\\
-	=&-\frac{4t^2}{3J}\sum_i \ket{\Phi}_i \bra{\Phi}_i +  \left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right) \frac{64 t^4}{27 J^3} - \left(\ket{\Phi}_1 \bra{\Phi}_1 + \ket{\Phi}_2 \bra{\Phi}_2\right) \frac{8t^4}{27 J^3}\\
-	=& \ket{\Psi}_1 \bra{\Psi}_1 \left[\text{constant} + \frac{64 t^4}{27 J^3} \mathcal{P}_\text{charge}  - \frac{8t^4}{27 J^3}\mathcal{P}_\text{spin}\right] 
-\end{aligned}\end{equation}
-\(\mathcal{P}_\text{spin}\) and \(\mathcal{P}_\text{charge}\) project, respectively,  onto the spin and charge sectors of the first site.
-The fact that the charge sector comes with a positive factor means that the holon-doublon states are repulsive, and this renormalisation of the states generates an effective particle-hole symmetric Fermi liquid interaction on the first site - also known as the local Fermi liquid (LFL)~\cite{nozieres1974fermi}.
-
-\section{Destruction of the Abrikosov-Suhl resonance: passage from strong coupling to local moment}
-
-We will now tune the parameters of the fixed point Hamiltonian and study the variation of quantities related to the effective Hamiltonian like the local FL strength \(\mathcal{F}\), the gap in the spectrum of the zeroth Hamiltonian \(H_0^*\) and the value of the small parameter \(t^2/\delta E\), as well as various measures of entanglement like entanglement entropy, mutual information and spin-spin correlations between various sets of members of the real-space impurity+lattice construction.
-We will trace a specific path through the space of values of fixed point couplings: we will start from the strong coupling regime \(U \ll J,V\) and go towards the local moment regime \(U \gg J,V\).
-The context of this study is that the technique of dynamical mean-field theory (DMFT) obtains a metal-insulator transition in the 2D Hubbard model by studying the Anderson impurity model as the auxiliary system for the Hubbard; there, the local moment regime of the impurity corresponds to the insulator in the bulk.
-Our goal here is to study what precisely happens in the effective Hamiltonian in the journey from the metal to the insulator, and draw a concrete connection between this modification of the effective Hamiltonian, and the simultaneous change of the impurity spectral function in fig.~\ref{spec_func}.
-This is done with the knowledge that the local moment phase of the generalised SIAM is never RG-stable.
-
-\subsection*{Perturbation theory parameters}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-\end{center}
-The vanishing of the gap and the growth of the small parameter indicates the breakdown of perturbation theory around the singlet; this simply shows that there is a degeneracy in the local moment regime, and the effective Hamiltonian will have to be obtained using degenerate perturbation theory.
-The presence of degeneracy also suggests that the effective Hamiltonian will be of the non-Fermi liquid type.
-
-\subsection*{\(k-\)space correlations within the Kondo cloud}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-\end{center}
-
-The mutual information \(I(d:k)\) between the impurity and the cloud vanishes as \(U/J\) is increased.
-This is a signature of the loss of entanglement and the breakdown of the singlet.
-The reduction of the mutual information within the cloud, \(I(k_1:k_2)\), shows that the Kondo cloud is being killed as \(U/J\) is increased; it ultimately drops to zero, characteristic of a decoupled tight-binding chain.
-The four-Fermion off-diagonal term also vanishes as \(U/J\) increases and this is again a signature of the reduction in the spin-flip processes.
-The diagonal correlation \(\left<\hat n_{k \uparrow} \hat n_{q \downarrow} \right>\) increasing to 1 shows the formation of a filled Fermi sea.
-
-\subsection*{Mutual information between various real space members}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-\end{center}
-The impurity-zeroth site mutual information \(I(d:0)\) remains unchanged at the maximum for an appreciable range of values, and this shows the stability of the singlet.
-Meanwhile, the mutual information between the zeroth site and the site nearest to it (\(I(0:1)\)) grows, because when the singlet weakens, the zeroth site is able to entangle more with the other sites.
-It finally saturates to its maximum value, which is the value produced as result of the tight-binding hopping.
-The mutual information between the impurity and sites beyond the zeroth site (\(I(d:1)\)) show a non-monotonic behaviour; it first increases as the entanglement that was initially restricted to just the impurity and the zeroth sites begins "seeping" into the other sites as well.
-Beyond a critical value of \(U/J\), \(I(d:1)\) starts dropping, because the entanglement has now mostly shifted out of the singlet and into the conduction bath.
-
-\subsection*{Impurity entanglement entropy and spin-spin correlations}
-
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-
-\end{center}
-
-The von-Neumann entanglement entropy \(S(d)\) of the impurity shows pretty straightforward behaviour.
-It is maximum for \(U \ll J\) because it is in a singlet configuration.
-For \(U \gg J\), the singlet weakens and the impurity begins to decouple from the bath, leading to a reduction in \(S(d)\).
-At sufficiently low values of \(J/U\), the impurity decouples from the zeroth site and the total system can be factorised into a local moment in product with a tight-binding chain, so that the impurity site will now have zero entanglement entropy.
-The spin-spin correlation \(\vec{S}_d\cdot\vec{S}_0\) is most negative at large \(J\), showing maximum screening at strong-coupling.
-It decreases to 0 as the singlet breaks.
-This reduction in the spin-spin correlation between the impurity and the zeroth site is accompanied by the appearance of antiferromagnetic spin-spin correlation \(\vec{S}_0\cdot\vec{S}_1, \vec{S}_0\cdot\vec{S}_3\) between the zeroth site and odd-numbered sites like 1 and 3.
-This can be understood on the following grounds:since the tight-binding hopping only connects same spin states, an electron on the first site has to have spin opposite to that on the zeroth site in order to hop onto that site.
-This requirement of opposite spin is what induces an antiferromagnetic superexchange interaction \(J_1\) between the zeroth site and the first site.
-This interaction strength increases as \(J\) is decreased, because \(J_1 \sim t^2/J\).
-By the same argument, a ferromagnetic superexchange interaction is induced between the impurity site and the first site, as well as between the zeroth site and the other even-numbered sites.
-These are also seen in the plots.
-
-\subsection*{Real-space correlations}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=1_over_U,V=3J,N=4,U=1.000,1.000,50.pdf}
-
-	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-\end{center}
-
-The increase of single-particle hopping correlation is another signature of the "handover" of entanglement from the singlet to the tight-binding chain.
-Exactly the same can be said for the four-Fermion interaction as well.
-
-\subsection*{Real-space correlations as function of distance}
-\begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/corr-di-min-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/corr-di-max-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-
-	\includegraphics[width=0.45\textwidth]{../figures/corr-all-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/I-all-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-\end{center}
-
-The first thing to note in the first two figures is the difference in the order of magnitudes; the correlations are very small in the first figure, because the impurity is being screened almost completely by the zeroth site at \(J \gg U\).
-This changes in the second figure where, because \(U \gg J\), the singlet has become entangled with the other sites, and the impurity is being screened by multiple sites.
-The mutual information all vary similarly with distance in the bottom right figure.
-
-\subsection*{Impurity spectral function}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=0.100.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=9.000.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=16.000.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=20.250.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=36.000.pdf}
-\end{center}
-
-\section{Calculating the \(T=0\) Wilson ratio from low energy excitations}
-The total system now consists of two decoupled parts - the singlet composed of the impurity and the zeroth site, and the remaining lattice composed of N-1 sites with a tight-binding dispersion and a local interaction at the 1-th site.
-The effective Hamiltonian for the remaining lattice is
-\begin{equation}\begin{aligned}
-	\sum_{i=1\atop{\sigma}}^\infty t\left(c^\dagger_{i\sigma}c_{i+1 \sigma} + c^\dagger_{i+1 \sigma}c_{i\sigma}\right) + u \hat n_{1 \uparrow} \hat n_{1 \downarrow}
-\end{aligned}\end{equation}
-We have rewritten the holon term in terms of the spin and doublon operators.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.7\textwidth]{../figures/lattice_eff.png}
-	\caption{\textit{Left}: The nearest-neighbor hopping described by the effective Hamiltonian.
-The red circle is the impurity.
-The black cloud at the center demarcates the collection of electrons at the origin of the lattice (which couple to the impurity).
-The green circles represent lattice sites that are nearest to the origin.
-The blue circles represent next-nearest sites.
-\textit{Right}: After treating the hopping between origin and its nearest neighbors as perturbation, we get a system consisting of two decoupled parts: one part is the impurity+cloud singlet, the other part is the rest of the lattice sites.
-The effect of the hopping between the origin and the green sites is a repulsion term on the green sites.}
-\end{figure}
-We will now invoke the mean-field approximation in simplifying this term.
-We will be dealing with thermodynamic quantities soon, so the operators will be replaced by their thermodynamic values, that is, the values that minimize the free energy functional.
-\begin{equation}\begin{aligned}
-	\hat n_{1 \uparrow} \hat n_{1 \downarrow} \to \langle \hat n_{1 \uparrow} \hat n_{1 \downarrow}\rangle = \langle  \delta n_{1 \uparrow} \delta n_{1 \downarrow}\rangle + \langle  n_{1 \uparrow}\rangle\langle  n_{1 \downarrow}\rangle
-\end{aligned}\end{equation}
-where \(\delta n_{1\sigma} \equiv n_{1 \sigma} - \langle  n_{1\sigma} \rangle\) is the fluctuation of the particle number above the ground state.
-The mean-field approximation then involves dropping the first term which is a quadratic fluctuation - since we are interested in values of quantities at \( T \to 0\), this quadratic fluctuation is very small.
-The interaction we are left with is
-\begin{equation}\begin{aligned}
-	u\langle  n_{1 \uparrow}\rangle\langle  n_{1 \downarrow}\rangle = \sum_{kq\sigma}f_{kq}\langle  n_{k \sigma}\rangle\langle  n_{q \overline\sigma}\rangle
-\end{aligned}\end{equation}
-This interaction converts the problem to that of a Landau Fermi liquid, with the quasiparticle energy functional being given by
-\begin{equation}\begin{aligned}
-	\epsilon_{k\sigma} = \epsilon_k + \sum_{q}f_{kq}\left<\hat n_{q \overline\sigma}\right>
-\end{aligned}\end{equation}
-From the form of the quasiparticle energy functional, we can see that there is no spin-parallel term, so we can write
-\begin{equation}\begin{aligned}
-	\label{rel_landau}
-	f_{kk^\prime\sigma\sigma} = 0,  f_{kk^\prime\sigma\overline\sigma} = f_{kk^\prime}
-\end{aligned}\end{equation}
-We will now use this Fermi liquid form to extract the Wilson ratio. We will make use of the following definitions/results:
-\begin{gather}
-	dn_{k\sigma} = \frac{\partial{n}}{\partial{\epsilon_{k\sigma}}}\left( d\epsilon_{k\sigma} - d\mu \right) ~ ~ \left[\text{follows from differentiating FD distribution}\right] \\
-	C_V = \frac{\:\mathrm{d}\epsilon}{\:\mathrm{d}T}, ~ ~ \chi^{s,c} = \frac{\:\mathrm{d}}{\:\mathrm{d}(B, \mu)}\left(n_\uparrow \mp n_\downarrow\right), ~ ~ 2f_0^{s,a} = \sum_k\left(f_{kk^\prime \uparrow \uparrow} \pm f_{kk^\prime \uparrow \downarrow}\right), ~ ~ F_0^{s,a} = \rho(0) f_0^{s,a}
-\end{gather}
-\subsection{Low-\(T\) Specific heat}
-\begin{equation}\begin{aligned}
-	C &= \frac{\:\mathrm{d}}{\:\mathrm{d}T}\sum_{k\sigma}\epsilon_{k\sigma}n_{k\sigma} \\
-	    &\approx \sum_{k\sigma}\epsilon^0_{k\sigma} \frac{\:\mathrm{d}n_{k\sigma}}{\:\mathrm{d}T} && \left[\text{no quasiparticles at ground state}\right] \\
-	    &\approx \sum_{k\sigma}\epsilon^0_{k\sigma} \frac{\:\mathrm{d}n_{k\sigma}}{\:\mathrm{d}T} && \left[\text{same expression as Fermi gas but with modified distribution function}\right] \\
-	    &= \rho(0) T
-\end{aligned}\end{equation}
-where \(\rho\) is the total quasiparticle DOS with contributions from conduction bath and impurity.
-\begin{equation}\begin{aligned}
-	\rho \sim \text{Im }\text{Trace}\left[G\right] = \text{Im}\sum_{d\sigma}G_{dd}^\sigma + \text{Im}\sum_{k\sigma}G_{kk}^\sigma = \rho_0 + \rho_\text{imp}
-\end{aligned}\end{equation}
-which gives
-\begin{equation}\begin{aligned}
-	C_{imp} \equiv C - C_0 = \rho_{imp}(0)T
-\end{aligned}\end{equation}
-
-\subsection{Low-\(T\) Charge Susceptibility}
-\begin{equation}\begin{aligned}
-	\chi^c &= \frac{\:\mathrm{d}N}{\:\mathrm{d}\mu}\\
-\end{aligned}\end{equation}
-Due to change in chemical potential, \(\delta\epsilon_{k\sigma}\) is isotropic and SU(2)-symmetric. Hence
-\begin{equation}\begin{aligned}
-	d\epsilon_{k\sigma} &= \sum_{k^\prime\sigma^\prime}f_{kk^\prime\sigma\sigma^\prime}d n_{k^\prime\sigma^\prime}\\
-			    &= d n\sum_{k^\prime}\left(f_{kk^\prime\uparrow \uparrow} + f_{kk^\prime \uparrow \downarrow}\right) && \left[dn = dn_{k^\prime \uparrow} = dn_{k \downarrow}\right] \\
-			    &= 2dn f_0^s
-\end{aligned}\end{equation}
-Therefore,
-\begin{equation}\begin{aligned}
-	dN &= \sum_{k\sigma}dn_{k\sigma} = \sum_{k\sigma}\frac{\partial{n}}{\partial{\epsilon_{k\sigma}}}\left( d\epsilon_{k\sigma} - d\mu \right) = \sum_{k\sigma}-\frac{1}{2}\rho\left(2dn f_0^s - d\mu \right) = -\rho(0) d N f_0^s + d\mu \rho(0) \\
-	   &\approx d\mu \rho(0) - \rho(0) f_0^s d\mu \rho(0) \left[\text{substitute \(dN\) back into itself}\right] \\
-	\implies \frac{\:\mathrm{d}N}{\:\mathrm{d}\mu} &= \rho(0)\left( 1 - \rho(0)f_0^s \right) \implies \chi^c_{imp} = \rho(0)_{imp} - \rho(0)f_0^s \\
-\end{aligned}\end{equation}
-At an intermediate state, we substituted \(dN\) back into itself and kept only the leading order term.
-This is justified because \(f_{kk^\prime}\) goes as \(\frac{1}{N J}\).
-At the fixed point and for a thermodynamically large system, both \(J\) and \(N\) are very large, so keeping only the leading order suffices.
-
-From a previous calculation, we know that the charge susceptibility at \(T=0\) is zero (eq.~\eqref{zero_chi_charge}), so we can write down the following relation:
-\begin{equation}\begin{aligned}
-	\label{fp_constraint}
-	f_0^s = \frac{\rho(0)_{imp}}{\rho(0)}
-\end{aligned}\end{equation}
-
-\subsection{Low-\(T\) Spin Susceptibility}
-\begin{equation}\begin{aligned}
-	\chi^s &= \frac{\:\mathrm{d}m}{\:\mathrm{d}\mu}\\
-\end{aligned}\end{equation}
-Due to change in magnetic field, change in \(\epsilon_{k\sigma}\) should be isotropic and SU(2)-\text{anti}symmetric. Hence
-\begin{equation}\begin{aligned}
-	d\epsilon_{k\sigma} &= -\frac{1}{2}dB \sigma + \sum_{k^\prime\sigma^\prime}f_{kk^\prime\sigma\sigma^\prime}d n_{k^\prime\sigma^\prime}\\
-			    &= -\frac{1}{2}dB \sigma + d n_{\sigma}\sum_{k^\prime}\left(f_{kk^\prime\uparrow \uparrow} - f_{kk^\prime \uparrow \downarrow}\right) && \left[dn_{k^\prime \uparrow} = -dn_{k \downarrow}\right] \\
-			    &= -\frac{1}{2}dB \sigma + 2dn_\sigma f_0^a
-\end{aligned}\end{equation}
-Since the total number remains constant, \(\mu=0\). Therefore,
-\begin{equation}\begin{aligned}
-	dm &= \sum_{k}\left(dn_{k \uparrow} - dn_{k \downarrow}\right) = -\frac{1}{2}\sum_{k}\rho\left( d\epsilon_{k \uparrow} - d\epsilon_{k \downarrow} \right) = -\frac{1}{2}\sum_{k}\rho\left(-dB + 2f_0^a \left(dn_{k \uparrow} - dn_{k \downarrow}\right)\right) \\
-	   &= dB\rho(0) - dm \rho(0)f_0^a \approx dB\rho(0) - \rho(0)f_0^aB\rho(0) ~ \left[\text{substitute \(dm\) back into itself}\right] \\
-	\implies \frac{\:\mathrm{d}m}{\:\mathrm{d}B} &= \rho(0)\left( 1 - \rho(0)f_0^a \right) \implies \chi^s_{imp} = \rho(0)_{imp} - \rho(0)f_0^a \\
-\end{aligned}\end{equation}
-
-\subsection{Wilson ratio}
-The Wilson ratio for the impurity~\cite{wilson1975,nozieres1974fermi,hewson1993} is defined as
-\begin{equation}\begin{aligned}
-	R = \frac{\chi^s_{imp}}{\frac{C_{imp}}{T}}
-\end{aligned}\end{equation}
-From eq.~\eqref{rel_landau}, we have \(f_0^s = -f_0^a\), which, when combined with eq.~\eqref{fp_constraint}, gives
-\begin{equation}\begin{aligned}
-	\chi^s_{imp} &= 2\rho(0)_{imp}
-\end{aligned}\end{equation}
-The Wilson ratio becomes
-\begin{equation}\begin{aligned}
-	R = \frac{2\rho(0)_{imp}}{\rho(0)_{imp}} = 2
-\end{aligned}\end{equation}
-
-\section{Luttinger's and Friedel's sum rules}
-\label{lutt_theorem}
-In this section, we will compute Luttinger's sum for the various fixed-point theories.
-Luttinger's sum is essentially the volume enclosed by the Fermi surface~\cite{luttinger1960fermi,oshikawa2000topological,seki2017topological}, and Luttinger's theorem states that this volume counts the number of electrons in the system~\cite{luttinger1960fermi,oshikawa2000topological,seki2017topological}.
-
-We first consider the strong-coupling fixed point Hamiltonian, which is essentially just a resonant-level model:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{res} = \sum_{k\sigma}\epsilon_k \hat n_{k\sigma} + \sum_{k\sigma}\left(V_k c^\dagger_{k\sigma} c_{d\sigma} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-The impurity Green's function is given by~\cite{anderson_1961,hewson1993,coleman2015}
-\begin{equation}\begin{aligned}
-	G_{d}(z) &= \frac{1}{z - \Sigma_d}\ket{d\sigma}\bra{d\sigma}, ~ ~ \Sigma_d = \sum_k \frac{V^2}{z - \epsilon_k}
-\end{aligned}\end{equation}
-\(\Sigma_d(z)\) is zero at the free orbital fixed point. The conduction electron Green's function is 
-\begin{gather}
-	G_{k}(z) = G_k^0(z) + \left[G_k^0(z)V_k\right]^2 G_{d}(z), ~ ~ G_k^0 = \frac{1}{z - \epsilon_k}, ~ ~ G_c^0(z) = \sum_k G_k^0(z)\ket{k}\bra{k}~,\\
-	G_c(z) = \sum_k G_k(z)\ket{k}\bra{k} = G_c^0 + \left[G_k^0(z)V_k\right]^2 G_{d}(z)\ket{k}\bra{k} 
-\end{gather}
-The total number of electrons is given by the sum of the number of electrons in the conduction bath and at the impurity~\cite{hewson1993,langreth1966}:
-\begin{equation}\begin{aligned}
-	\label{tot_num}
-	N &= \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_{d}(z) + G_c(z)\right] = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_{d}(z) + G_c^0(z) + \left[G_k^0(z)V_k\right]^2 G_{d}(z)\ket{k}\bra{k}\right]
-\end{aligned}\end{equation}
-Since the eigenstates of the system are situated at real poles, the contour \(\Gamma\) encloses only the real axes and hence picks out those real poles to count the total number of particles.
-
-Since \(1/G_{c}^0(z) = z - \sum_k \epsilon_k \hat n_k\), we can write \(\text{Tr}\left[G_{c}^{0}(z)\right] = \text{Tr}\left[G_{c}^{0} \frac{\partial{}}{\partial{z}}\left(1/G_{c}^{0}\right)\right]\) and hence
-\begin{equation}\begin{aligned}
-	\label{simple_bath}
-	\text{Tr}\left[G_c(z)\right] &=\frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{c}^{0}\right)\right] + \sum_k\left[G_k^0(z)V_k\right]^2 G_{d}(z)
-\end{aligned}\end{equation}
-
-The impurity part can, on the other hand, be written as
-\begin{equation}\begin{aligned}
-	\label{self_id}
-	\text{Tr}\left[G_{d}(z)\right] &= \text{Tr}\left[ \frac{\ket{d}\bra{d}}{z - \Sigma_d(z)}\right] = \text{Tr}\left[ \frac{\ket{d}\bra{d}}{z - \Sigma_d(z)}\frac{\partial{\left(z\right)}}{\partial{z}} \right] = \text{Tr}\left[ G_{d}(z)\frac{\partial{G_{d}^{-1}(z)}}{\partial{z}} \right] + \text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right]\\
-\end{aligned}\end{equation}
-The fist term can be written as \(\text{Tr}\left[ G_{d}(z)\frac{\partial{G_{d}^{-1}(z)}}{\partial{z}} \right] = \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}G_{d}^{-1}(z)\right]\).
-The second part can be written as \(\frac{\partial{}}{\partial{z}}{\Sigma_d(z)} = -\sum_k V^2 {G_k^0}^2\).
-Together, we get
-\begin{equation}\begin{aligned}
-	\label{simple_imp}
-	\text{Tr}\left[G_{d}(z)\right] = \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{d}\right)\right] - \text{Tr}\left[ G_{d}(z)\sum_k V^2 {G_k^0}^2\right]\\
-\end{aligned}\end{equation}
-Substituting eqs.~\ref{simple_bath} and \ref{simple_imp} into eq.~\ref{tot_num}, we get
-\begin{equation}\begin{aligned}
-	N = \oint \frac{dz}{2\pi i}n_F(z) \left[\frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{d}\right)\right] + \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{c}^{0}\right)\right]\right]
-\end{aligned}\end{equation}
-At \(T=0\), \(n_F\) is defined as 1 below the FS, \(\frac{1}{2}\) at the FS and 0 above it.
-\begin{equation}\begin{aligned}
-N  = \left[\oint_{\Gamma_<} + \frac{1}{2}\oint_{\Gamma_0}\right]\frac{dz}{2\pi i}\left[\frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{1/G_d(z)\right\} + \frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{1/G_{c}^{0}(z)\right\} \right]
-\end{aligned}\end{equation}
-Following Seki and Yunoki~\cite{seki2017topological}, we can define a winding number for a Green's function \(G(z)\):
-\begin{equation}\begin{aligned}
-	n_{\text{Det} G^{-1}}(C) = \oint_{C} \frac{dz}{2\pi i} \frac{\partial{\ln\text{Det }G^{-1}(z)}}{\partial{z}} = \oint_{\text{Det} G^{-1}(C)} \frac{\mathrm{d}\; \text{Det }G^{-1}}{\text{Det }G^{-1}}
-\end{aligned}\end{equation}
-Since \(n_{\text{Det } G^{-1}(C)}\) counts the number of times the curve \(\text{Det } G^{-1}(C)\) winds around the origin, it is integer-valued and topological.
-Seki and Yunoki also show that the this number is given by
-\begin{equation}\begin{aligned}
-n_{\text{Det }G^{-1}(C)} = P_{\text{Det }G}(C) - Z_{\text{Det }G}(C)
-\end{aligned}\end{equation}
-where \(P_{f(z)}(C)\) is the number of poles of \(f(z)\) enclosed by the contour \(C\), and \(Z\) is the corresponding number of zeros.
-The total number of particles in the resonant level model can thus be written as
-\begin{equation}\begin{aligned}
-	N =& \underbrace{P_{\text{Det }G_d}(\Gamma_<) - Z_{\text{Det }G_d}(\Gamma_<)}_{N_\text{imp}^<} + \underbrace{\frac{1}{2}\left[P_{\text{Det }G_d}(\Gamma_0) - Z_{\text{Det }G_d}(\Gamma_0)\right]}_{N_\text{imp}^0} + \underbrace{P_{\text{Det }G_{c}^{0}}(\Gamma_<) - Z_{\text{Det }G_{c}^{0}}(\Gamma_<)}_{N_\text{L}^<} \\
-	  &+ \underbrace{\frac{1}{2}\left[P_{\text{Det }G_{c}^{0}}(\Gamma_0) - Z_{\text{Det }G_{c}^{0}}(\Gamma_0)\right]}_{N_\text{L}^0}\\
-	  =& N_\text{imp}^< + \frac{1}{2}N_\text{imp}^0 + N_L^< + \frac{1}{2}N_L^0
-\end{aligned}\end{equation}
-The average number of particles can thus be expressed purely in terms of the number of real poles and real zeros of the impurity and the conduction electron Green's functions.
-\(N_\text{imp}^<\left(N_\text{imp}^<\right)\) is the number of poles minus the number of zeros of the impurity Greens function inside (on) the Fermi surface.
-\(N_\text{imp} = N_\text{imp}^0 + \frac{1}{2}N_\text{imp}^0\)  therefore gives the total number of localised eigenstates of the system.
-Similarly, \(N_L^<\left( N_L^0 \right) \) gives the number of real poles in the conduction electron Greens function minus the number of real zeros, and \(N_L = N_L^< + \frac{1}{2}N_L^0\) gives the total number of delocalised eigenstates of the system.
-\begin{equation}\begin{aligned}
-	\label{total_lutt}
-	N = N_\text{imp} + N_L
-\end{aligned}\end{equation}
-Note that this also holds at the free orbital fixed point, because it is a special case of the strong-coupling fixed point with \(V=0\).
-
-If we are the local moment fixed point with particle-hole symmetry, we instead have the Hamiltonian
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{lm} = \sum_{k\sigma}\epsilon_k \hat n_{k\sigma} + H_\text{imp}
-\end{aligned}\end{equation}
-where \(H_\text{imp} = -(U/2)\hat n_d + U\hat n_{d \uparrow} \hat n_{d \downarrow}\) is the impurity Hamiltonian.
-In this atomic limit, the impurity Greens function is given by~\cite{phillips2012advanced}
-\begin{equation}\begin{aligned}
-	\label{lm_sigma}
-	G_d = \frac{1}{z - \Sigma_d(z)}, ~ ~ ~\Sigma_d = \frac{U^2}{4}\frac{1}{z}
-\end{aligned}\end{equation}
-Since \(V=0\) at this fixed point, the total number of particles is given by
-\begin{equation}\begin{aligned}
-	\label{total_num_lm}
-	N = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_{d}(z) + G_c^0(z)\right]
-\end{aligned}\end{equation}
-We again use eq.~\ref{self_id} to write
-\begin{equation}\begin{aligned}
-	\text{Tr}\left[G_{d}(z)\right] = \text{Tr}\left[ G_{d}(z)\frac{\partial{G_{d}^{-1}(z)}}{\partial{z}} \right] + \text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right] = \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{d}\right)\right] + \text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right]
-\end{aligned}\end{equation}
-Performing the integral for the second term gives
-\begin{equation}\begin{aligned}
-	\left(\int_{\Gamma_<} + \frac{1}{2}\int_{\Gamma_0}\right)\frac{dz}{2\pi i}\text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right] = 0
-\end{aligned}\end{equation}
-Here we used the form of \(\Sigma_d\) in eq.~\ref{lm_sigma}. Repeating the same steps as before, we recover eq.~\ref{total_lutt}.
-
-We now compare the Luttinger volume across the fixed points.
-At the local moment fixed point, the impurity Greens function has a single pole at \(z<0\) and a zero at \(z=0\), so \(N_\text{imp} = 1 - 1/2 = 1/2\), and eq.~\ref{total_lutt} becomes
-\begin{equation}\begin{aligned}
-	N = 1/2 + N_\text{L}^{LM}
-\end{aligned}\end{equation}
-The same thing happens at the free orbital fixed point; there, \(G_d\) has a single pole at \(z=0\), so \(N_\text{imp} = 1/2\) and we again get \(N = 1/2 + N_\text{L}^{FO}\).
-The change happens when we go to the strong-coupling resonant-level fixed point.
-There, the impurity self-energy can be written as~\cite{anderson_1961,hewson1993,coleman2015}
-\begin{equation}\begin{aligned}
-	\Sigma_d^\text{sc} = \text{Re}\left[\Sigma_d^\text{sc}\right] - i\Delta
-\end{aligned}\end{equation}
-That is, the self-energy becomes imaginary, so the real pole that existed at the free orbital fixed point moves off the real axis.
-We therefore have \(N_\text{imp} = 0\).
-Assuming the number of particles \(N\) remained constant, we obtain \(N = N_\text{L}^{SC}\).
-The change in the Fermi volume in going from the local moment to the strong coupling fixed point is therefore by \(1/2\).
-If one defines new a Luttinger volume \(\mathcal{N}_L = 2N_L\) to also account for the spin degeneracy, we can write:
-\begin{equation}\begin{aligned}
-	\label{luttinger_change}
-	\Delta \mathcal{N}_L = 1
-\end{aligned}\end{equation}
-This is a specific case of the more general result for Kondo lattices obtained by Oshikawa using flux-insertion arguments\cite{oshikawa2000topological}.
-
-The scattering phase shift suffered by the conduction electrons at the Fermi surface, off the impurity, can be calculated from the impurity occupancy, using the Friedel sum rule.
-From the ground state wavefunction, we can calculate the average number of particles on the impurity:
-\begin{equation}\begin{aligned}
-	\left<n_d \right> = \bra{\Psi}_1\sum_\sigma \hat n_{d\sigma} \ket{\Psi}_1
-\end{aligned}\end{equation}
-\(\ket{\Psi}_1\) is the lower energy state in eq.~\eqref{gstate}. Performing the inner product gives
-\begin{equation}\begin{aligned}
-	\left<n_d \right> = \left( c_s^- \right)^2 + \left( c_c^- \right)^2 = 1
-\end{aligned}\end{equation}
-The phase shift is thus
-\begin{equation}\begin{aligned}
-	\frac{1}{\pi}\sum_\sigma \delta_\sigma(0) = \left<n_d \right> \implies \delta_\sigma(0) = \frac{\pi}{2}
-\end{aligned}\end{equation}
-There we used \(\delta_\uparrow = \delta_\downarrow\) because the model is SU(2)-symmetric. This line of arguments was first presented for the Kondo model in \cite{martin1982fermi}.
-
-The change in Luttinger's number also allows us to calculate the Wilson ratio of the system, from eq.~\eqref{wilson_luttinger}.
-\begin{equation}\begin{aligned}
-	R = 1 + \sin^2 \left( \frac{\pi}{2}\Delta \mathcal{N}_L \right) = 1 + \sin^2 \frac{\pi}{2} = 2
-\end{aligned}\end{equation}
-\section{Reverse RG analysis}\label{rev_rg}
-The goal here is to chart the journey starting from the IR fixed point towards the UV regime, by following one particular wavefunction.
-We will start with a very simple IR ground state wavefunction, and then go back towards the UV ground state by applying the inverse unitary operator \(U^\dagger\):
-\begin{equation*}\begin{aligned}
-	U : \underbrace{\ket{1,2,...,N}}_\text{UV ground state} \rightarrow \ket{1,2,...,N-1}\ket{N} \rightarrow ... \rightarrow \underbrace{\ket{1,2,...,N^*}\ket{N^*+1}...\ket{N}}_\text{IR ground state}
-\end{aligned}\end{equation*}
-\begin{equation*}\begin{aligned}
-	U^\dagger : \underbrace{\ket{1,2,...,N^*}\ket{N^*+1}...\ket{N}}_\text{IR ground state} \rightarrow \ket{1,2,...,N^*+1}\ket{N^*+2}...\ket{N} \rightarrow ...
-\rightarrow\underbrace{\ket{1,,2,...,N}}_\text{UV ground state}
-\end{aligned}\end{equation*}
-The first process is the forward RG which we used to obtain the scaling equations.
-The second process is the reverse RG which we will undertake now.
-The method has already been applied to study the renormalisation of entanglement in various models of strong correlation~\cite{siddharthacpi,anirban_kondo,anirban_mott_ent}.
-In general, we start with an IR wavefunction that consists a certain number of momentum states \(n_1\) still entangled with the impurity, and the remaining momentum states \(n_2\) disentangled from the impurity.
-The former are said to be part of the emergent Kondo cloud, while the latter are said to be part of the integrals of motion (IOMs) and appear in direct product with the cloud+impurity system in the ground state wavefunction.
-Each momentum state is tagged with two conduction bath levels, one above the Fermi surface and one below.
-These will be represented as \(k,\pm\).
-If we represent the emergent cloud momentum states as \(\left\{k_i\right\} \) and the IOM states as \(\left\{q_i\right\}\), the ground state wavefunction can be written as
-\begin{equation}\begin{aligned}
-	\ket{\Psi}_0 = \left(\otimes_{i=1}^{n_2}\ket{q_i,-,\uparrow}\ket{q_i,-,\downarrow}\right)\ket{\Phi}_\text{cloud}\left(\otimes_{i=1}^{n_2}\ket{q_i,+,\uparrow}\ket{q_i,+,\downarrow}\right)
-\end{aligned}\end{equation}
-Throughout, we have assumed that the IOMs below the Fermi surface are occupied while those above are unoccupied. This means:
-\begin{equation}\begin{aligned}
-	\ket{\Psi}_0 = \left(\otimes_{i=1}^{n_2}\ket{\hat n_{q_i,-,\uparrow}=1}\ket{\hat n_{q_i,-,\downarrow}=1}\right)\ket{\Phi}_\text{cloud}\left(\otimes_{i=1}^{n_2}\ket{\hat n_{q_i,+,\uparrow}=0}\ket{\hat n_{q_i,+,\downarrow}=0}\right)
-\end{aligned}\end{equation}
-\(\ket{\Phi}_\text{cloud}\) will be obtained by diagonalising a small system of \(n_1\) conduction bath \(k\) states.
-This completes the construction of the IR ground state \(\ket{\Psi}_0\).
-The algorithm of reverse RG then involves applying unitary transformations on this IR wavefunction; the unitary transformations will be the inverse of those that were applied during the forward RG algorithm.
-Since the forwards RG transformations decoupled \(k\) states and transformed them into the IOMS, the inverse transformations will take the momentum states in the IOMs and re-entangle them with the impurity+cloud system, one at a time.
-This is shown in fig.~\ref{rev-rg}.
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.4\textwidth]{../figures/reverse-rg.png}
-	\caption{We start with a Hamiltonian with an impurity site (red) coupled with two conduction electrons (dark green), with four other decoupled electrons (bright green).
-The dotted rectangle represents the emergent window \(\left( -\Lambda_j, \Lambda_j \right) \) at each step; the electrons inside that rectangle are still entangled with the impurity, while the ones inside have been decoupled.
-The next step of reverse RG involves applying the inverse transformation on the Hamiltonian, which will couple two more electrons from the IOMS (hence four dark green circles in the second step), leading to an enlargement of the emergent window.
-The unitary varies for each step, hence the notation \(U_j\).}
-	\label{rev-rg}
-\end{figure}
-
-The next step is to write down the unitaries that will take us from the IR ground state to the UV ground state.
-In the forward RG, we used the following unitary for decoupling the shell \(\epsilon_q\) and spin \(\beta\) is
-\begin{equation}\begin{aligned}
-	U_{q\beta} = \frac{1}{\sqrt 2}\left[1 + \eta_{0 \beta} + \eta_{1\beta}^\dagger\right]~.
-\end{aligned}\end{equation}
-Here, the subscripts \(0\) and \(1\) indicate it decouples an electron above and below the Fermi surface respectively. The inverse transformation for re-entangling \(q\beta\) is
-\begin{equation}\begin{aligned}
-	U^\dagger_{q\beta} = \frac{1}{\sqrt 2}\left[1 + \eta_{0 \beta}^\dagger + \eta_{1\beta}\right]~.
-\end{aligned}\end{equation}
-In the \(U>0\) regime, the \(\eta\)s are given by
-\begin{equation}\begin{aligned}
-	\eta_{0\beta}^\dagger = V \left[\frac{1}{d_0}\left( 1 - \hat n_{d\overline\beta} \right) + \frac{1}{d_1}\hat n_{d\overline\beta}  \right]c^\dagger_{q\beta}c_{d\beta} + \frac{1}{d_2}\frac{J}{2}\sum_{k} \left( S_d^z \beta c^\dagger_{q\beta}c_{k\beta} + c^\dagger_{d\overline\beta}c_{d\beta}c^\dagger_{q\beta}c_{k\overline\beta}\right) ~,\\
-	\eta_{1\beta} = V \left[\frac{1}{d_1}\left( 1 - \hat n_{d\overline\beta} \right) + \frac{1}{d_0}\hat n_{d\overline\beta}  \right]c^\dagger_{d\beta}c_{q\beta} + \frac{1}{d_2}\frac{J}{2}\sum_{k} \left( S_d^z \beta c^\dagger_{k\beta}c_{q\beta} + c^\dagger_{d\beta}c_{d\overline\beta}c^\dagger_{k\overline\beta}c_{q\beta}\right)~;
-\end{aligned}\end{equation}
-since \(K\) is irrelevant, we have set \(K=0\) here. The denominators have already been defined in eq.~\eqref{denominators}.
-\begin{equation}\begin{aligned}
-	d_0 = \omega - \frac{D}{2} - \frac{U}{2} + \frac{K}{4}, \quad d_1 = \omega - \frac{D}{2} + \frac{U}{2} + \frac{J}{4}, \quad d_2 = \omega - \frac{D}{2} + \frac{J}{4}, \quad d_3 = \omega - \frac{D}{2} + \frac{K}{4}
-\end{aligned}\end{equation}
-
-The wavefunction after reversing one step of the RG will thus be
-\begin{equation}\begin{aligned}
-	\ket{\Psi}_1 = U^\dagger_{q \uparrow}U^\dagger_{q \downarrow}\ket{\Psi}_0
-\end{aligned}\end{equation}
-Here, \(q\) is the first momentum state immediately outside the emergent cloud.
-Re-entangling further momentum states using their respective unitaries lead to the sequence of wavefunctions \(\ket{\Psi}_2, \ket{\Psi}_3\) and so on.
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/mut_I_ee.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/mut_I_ie.pdf}
-	\caption{\textit{Left}: Mutual information between two conduction electrons inside the cloud.
-\textit{Right}: Mutual information between a conduction electron inside the cloud and an impurity electron.
-Both the measures increase towards the strong coupling fixed point, because of the distillation of the Kondo cloud brought about by the RG flow.}
-	\label{mutI}
-\end{figure}
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/corr_same.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/corr_opp.pdf}
-	\caption{Increase in the diagonal correlation functions between cloud electrons under RG flow towards the strong coupling fixed point.
-This is consistent with the Fermi liquid pieces generated in the \(k-\)space effective Hamiltonian of the Kondo cloud.}
-\end{figure}
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/corr_od.pdf}
-	\caption{Growth of the off-diagonal correlation function between Kondo cloud electrons towards the strong coupling fixed point.
-This is the direct cause of the screening of the impurity spin, and is a reflection of the off-diagonal two-particle scattering terms in the \(k-\)space effective Hamiltonian of the Kondo cloud.}
-\end{figure}
-
-The results of the reverse RG study are depicted in the following plots.
-We have used two types of quantities in the process - mutual information and correlation functions.
-The mutual information between two subsystems \(A\) and \(B\) in a wavefunction with many subsystems is defined as
-\begin{equation}\begin{aligned}
-	I(A: B) = S_A + S_B - S_{AB}
-\end{aligned}\end{equation}
-where \(S_{ij..q}\) is the von-Neumann entropy of the reduced density matrix obtained after tracing out all degrees of freedom except those in the subscript of \(S\).
-
-The mutual information between two electrons inside the entangled cloud increases as we go towards the IR fixed point.
-This can be understood in the following manner; as the wavefunction flows towards a smaller sized emergent cloud, the entanglement between those electrons gets distilled out.
-
-We have also computed some correlation functions.
-All of them increase towards the IR fixed point.
-The increase in the correlation function \(\left<\hat n_{k_1 \uparrow} \hat n_{k_2 \downarrow} \right>\) arises from the crystallization of the spin singlet at the fixed point.
-The increase in the correlation function \(\left<\hat n_{k \uparrow} \hat n_{k \downarrow} \right>\) arises from the charge triplet content of the wavefunction, showing the increase of the charge contribution on the momenta.
-The increase in the off-diagonal correlation function \(\left< c^\dagger_{k \uparrow}c_{k^\prime \downarrow}c^\dagger_{q \downarrow}c_{q^\prime \uparrow}\right>\) shows that the there is a large and non-trivial interaction between the electrons of the cloud that is being mediated by the impurity electron.
-This interaction is not of the Fermi liquid type, but instead was obtained in the effective Hamiltonian for the Kondo cloud.
-
-\chapter{Effect of minimal attractive correlation in the bath}
-\label{siam-attr-chap}
-
-\section{The modified hamiltonian}
-We will include a local particle-hole symmetric correlation of strength \(U_b\) on the origin of the lattice:
-\begin{equation}\begin{aligned}
-	\mathcal{H} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} + \epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
-\end{aligned}\end{equation}
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/zeromode.pdf}
-	\caption{While we have studied the full model under renormalisation group, often we will turn to a simplified zero-bandwidth version of the model that is obtained by ignoring the kinetic energy part of the Hamiltonian.
-This zero-bandwidth model is effectively a two site model.}
-\end{figure}
-
-\section{RG Equations}
+\section{RG Equations for the model}
 The derivation of the RG equations are shown at the end. \(n_j\) is the number of \(k-\)states at the \(j^\text{th}\) isoenergetic shell. 
 \begin{gather}
-	\Delta U_b = 0, ~ ~\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\left(\frac{J^2}{d_2} - \frac{K^2}{d_3}\right),\\
-	\Delta V = -\frac{3n_j V}{8}\left[\left(J + 4U_b/3\right) \left(\frac{1}{d_2} + \frac{1}{d_1}\right) + \left(K + 4U_b/3\right)\left(\frac{1}{d_3} + \frac{1}{d_0}\right)\right],\\
-	\Delta J = -\frac{n_j J\left(J + 4U_b\right)}{d_2},~ ~\Delta K = -\frac{n_j K\left(K + 4U_b\right)}{d_3}
+	\Delta U_b = 0, ~ ~\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\frac{J^2}{d_2},\\
+	\Delta V = -\frac{3n_j V}{8}\left[\left(J + 4U_b/3\right) \left(\frac{1}{d_2} + \frac{1}{d_1}\right) + 4U_b/3\left(\frac{1}{d_3} + \frac{1}{d_0}\right)\right],\\
+	\Delta J = -\frac{n_j J\left(J + 4U_b\right)}{d_2}
 \end{gather}
@@
 The denominators are
-\begin{equation}\begin{aligned}
-	d_0 = \omega - \frac{D}{2} + \frac{U_b}{2} - \frac{U}{2} + \frac{K}{4}, \quad d_1 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{U}{2} + \frac{J}{4}, \quad d_2 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}, \quad d_3 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}
-\end{aligned}\end{equation}
+\begin{gather}
+	d_0 = \omega - \frac{D}{2} + \frac{U_b}{2} - \frac{U}{2}, \quad d_1 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{U}{2} + \frac{J}{4},\\
+	\quad d_2 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4},\quad d_3 = \omega - \frac{D}{2} + \frac{U_b}{2}
+\end{gather}
 
@@
 
-\section{Phase diagram}
-
-\begin{center}
-	\includegraphics[width=0.9\textwidth]{../figures/phase-map-MIT.pdf}
-\end{center}
-
-\begin{center}
+\section{RG flows and phase diagram}
+
+\begin{widetext}
+
+\begin{figure}[!htb]
+	\includegraphics[width=0.7\textwidth]{../figures/phase-map-MIT.pdf}
+\end{figure}
+
+\end{widetext}
+\begin{table}
+\centering
 \begin{tabular}{|c|c|c|c|c|}
@@
 \end{tabular}
-\end{center}
+\end{table}
+
+\section{Low-energy effective Hamiltonian and the ground state}
+
+\subsection{Screened regime: \(-U_b/J < 1/4 \)}
+
+The fixed point Hamiltonian can, in general, be written as
+\begin{equation}\begin{aligned}
+	\mathcal{H}^* = \sum_{\sigma, k}\epsilon_k \tau_{k\sigma} - \frac{U^*}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2  + \sum_{\sigma, k < \Lambda^*}\left( V^* c^\dagger_{k\sigma}c_{d\sigma} + \text{h.c.} \right) + J^* \vec{S_d}\cdot\vec{s}
+\end{aligned}\end{equation}
+The first term is the kinetic energy of all the electrons.
+The next two terms are the impurity-diagonal pieces, featuring the renormalised interaction \(U^*\).
+The next three terms are the residual interactions between the impurity and the metal, with the renormalised couplings \(V^*, J^*\) and \(K^*\).
+The summations in these terms extend from the fixed point momentum cutoff \(\Lambda^*\) to 0.
+This is the region of momentum space  which the URG was unable to decouple.
+The operators \(\vec s\) and \(\vec C\) represent the macroscopic magnetic and charge spins formed by the remaining electrons that are lying inside the window \(\left[ 0, \Lambda^* \right] \):
+\begin{equation}\begin{aligned}
+	\vec s = \sum_{kk^\prime<\Lambda^*\atop{\alpha\beta}} c^\dagger_{k\alpha}\vec \sigma_{\alpha\beta}c_{k^\prime\beta}
+\end{aligned}\end{equation}
+Our goal here is to write down the ground state wavefunction for this low-energy Hamiltonian.
+
+To make progress, we will simplify the effective Hamiltonian by taking the zero bandwidth limit.
+This reduces it to a two-site problem.
+One site is of course the impurity site, and this site will be labeled as site 1.
+The other site will be formed by the center of mass degree of freedom of the conduction electrons, and will be labeled as site 2.
+The Hamiltonian for this two-site problem is
+\begin{equation}\begin{aligned}
+	\mathcal{H}_{IR} = - \frac{U^*}{2}\left(\hat n_{1 \uparrow} - \hat n_{1 \downarrow}\right)^2 + V^*\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.} \right) + J^*\vec{S_1}\cdot\vec{S_2} + K^* \vec{C_1}\cdot\vec{C_2}
+\end{aligned}\end{equation}
+
+The subscripts on the operators designate the site on which they act; \(\hat n_1\) is the number operator for the first site.
+
+We will adopt the following notation to represent the states in this Hilbert space.
+A general state will be represented in the Fock space basis as \(\ket{n_{1 \uparrow}n_{1 \downarrow}n_{2 \uparrow}n_{2 \downarrow}}\).
+For example,
+\begin{equation}\begin{aligned}
+	\ket{1101} = c^\dagger_{1 \uparrow}c^\dagger_{1 \downarrow}c^\dagger_{2 \downarrow}\ket{-}
+\end{aligned}\end{equation}
+\(\ket{-}\) is the vacuum state.
+
+For \(U>0\), the ground state is given by
+\begin{gather}
+	\label{gstate}
+	\ket{\Psi}_\text{1} = c_s \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c_c \frac{1}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right), \quad E_1 =  -V^*\sqrt{\gamma^2 + 4} -\frac{1}{4}U^* - \frac{3}{8}{J^*}
+\end{gather}
+where $\gamma = \frac{1}{2{V^*}}\left[ \frac{1}{4}\left( 3J^* + K^* \right) + \frac{1}{2}U^* \right]$. The probabilities for the spin and charge sectors for the ground state are
+\begin{equation}\begin{aligned}
+	\label{coeff_def}
+	\left(c_s\right)^2 = \frac{1}{2\sqrt{\gamma^2 + 4}}\left(\sqrt{\gamma^2 + 4} + \gamma\right),\\
+	\left(c_c \right)^2 = \frac{1}{2\sqrt{\gamma^2 + 4}}\left(\sqrt{\gamma^2 + 4} - \gamma\right)~.
+\end{aligned}\end{equation}
+For (roughly) \(J_0 > V_0\), we get \(J^* \gg V^*\) and \(U^* \gg U_0\) so that \(\gamma \gg 1\).
+This gives \(\left( c_s \right) ^2 \sim 1\) and \(\left( c_c \right) ^2 \sim 0\).
+The entire contribution to the ground state then comes from the spin sectors of the two sites.
+This is calculated numerically in fig.~\ref{cs_cc}.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../figures/coeffs_vs_J.pdf}
+	\caption{Variation of relative weights \(c_s\) and \(c_c\) with \(J_0\)}
+	\label{cs_cc}
+\end{figure}
+
+In the other regime of \(U<0\), the two competing states are \(\ket{\Psi}_1\) defined above (with energy \(E_1\)), and \(\ket{\Psi_2}\), the charge singlet: \(\ket{\Psi}_2 = \frac{1}{\sqrt 2}\left( \ket{2,0} - \ket{0,2} \right)\) having energy \(E_2\).
+\begin{equation}\begin{aligned}
+	E_2 = -\frac{3}{4}K^*, \quad E_1 - E_2 = -\frac{1}{4}\sqrt{\left( \frac{1}{2}K^* + U^* \right)^2 + (4V^*)^2} - \frac{1}{4}U^* + \frac{3}{4}K^*
+\end{aligned}\end{equation}
+For \(V_0 \gg K_0\), the largest energy scale will be \(V^*\), and we can then approximate this difference as
+\begin{equation}\begin{aligned}
+	E_1 - E_2 \simeq -V^* < 0
+\end{aligned}\end{equation}
+In such a case, \(\ket{\Psi}_1\) will therefore be the ground state. In the other regime \(V_0 \ll K_0\), the largest energy scale will be \(K^*\), and we can then write
+\begin{equation}\begin{aligned}
+	E_1 - E_2 \simeq - \frac{1}{8}K^* + \frac{3}{4}K^* > 0
+\end{aligned}\end{equation}
+In this case, the ground state will be \(\ket{\Psi}_2\).
+There exists, therefore, a phase transition at a critical plane \((U_c, K_c, V_c)\), where the ground state changes between the charge singlet \(\ket{\Psi}_2\) and the spin singlet + charge triplet \(\ket{\Psi}_1\).
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../figures/E1_vs_E3.pdf}
+\end{figure}
+
+\subsection{Unscreened regime: \(-U_b/J > 1/4 \)}
+
+\subsection{Approach towards the thermodynamic limit}
+
+{\bf \Large [Update with V vs D plots]}
+
+The URG method works strictly on finite systems and leads to finite values of fixed point couplings.
+The behaviour of the Hamiltonian in the thermodynamic limit can then be determined using finite-size scaling where we increase the bandwidth and decrease the width of each RG step.
+When applied to the fixed point value of the impurity-bath hybridisation parameter \(V\) (fig.~\ref{V_vs_D}), it can be seen that the fixed point value increases as the system size is increased, implying that the continuum limit of \(V^*\) is \(\infty\).
+This holds for both \(V_0 > J_0\) and \(V_0 < J_0\), as shown in the two panels of fig.~\ref{V_vs_D}.
+
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.4\textwidth]{../figures/Vstar_vs_D_smallV.pdf}
+	\includegraphics[width=0.4\textwidth]{../figures/Vstar_vs_D_largeV.pdf}
+	\caption{Variation of fixed point value \(V^*\) with increasing bandwith \(D_0\), for both \(V_0 > J_0\) and \(V_0 < J_0\).}
+	\label{V_vs_D}
+\end{figure}
+
+In a similar manner, we checked the variation of the spin and charge probabilities, \(c_s\) and \(c_c\), in the ground state, with increasing bandwith. The result is shown in fig.~\ref{c_vs_D}.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.45\textwidth]{../figures/coeffs_vs_D.pdf}
+	\caption{Variation of spin and charge fractions, \(c_s\) and \(c_c\), of the ground state, as a function of bare bandwidth \(D_0\).
+Left and right panels show the cases of \(J_0 < V_0\) and \(J_0 > V_0\) respectively.}
+	\label{c_vs_D}
+\end{figure}
+For both \(V_0 < J_0\) and \(V_0 > J_0\), we see that the spin contribution increases towards unity while the charge contribution vanishes.
+This indicates that at large bandwidth, the ground state becomes purely a spin singlet, formed purely by singly-occupied impurity states.
+\begin{equation}\begin{aligned}
+	\label{gstate_kondo}
+	\lim_{D_0 \to \infty} \ket{\Psi}_1 = \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) 
+\end{aligned}\end{equation}
+
+\subsection{The critical point: \(-U_b/J = 1/4 \)}
 
@@
 \subsection*{Overlap of ground state against spin singlet and charge triplet zero states}
-\begin{center}
-	\includegraphics[width=0.7\textwidth]{../figures/overlaps_gs-J=0.100.pdf}\\
-	\includegraphics[width=0.7\textwidth]{../figures/overlaps_gs-J=10.000.pdf}\\
-	\includegraphics[width=0.7\textwidth]{../figures/overlaps_gs-J=50.000.pdf}
-\end{center}
-
-\subsection*{Spin and charge correlations in ground state}
-\begin{center}
-	\includegraphics[width=0.7\textwidth]{../figures/corrs_gs-J=0.100.pdf}\\
-	\includegraphics[width=0.7\textwidth]{../figures/corrs_gs-J=10.000.pdf}\\
-	\includegraphics[width=0.7\textwidth]{../figures/corrs_gs-J=50.000.pdf}
-\end{center}
-
-\section{Evolution of various correlation measures and other quantities}
-
-\subsection*{Perturbation theoretic terms}
-These quantities are related to the local Fermi liquid of the Kondo strong coupling fixed point and the perturbation theory associated with it.
-\(min(\delta E)\) is the gap in the spectrum of the two-site Hamiltonian; this which acts as the denominator for the perturbation theoretic calculations.
-\(t^2/\delta E\) is the small parameter for the expansion, \(t\) being the tight-binding hopping.
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/gap-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/par-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-\end{center}
-
-\subsection*{Correlation within the Kondo cloud}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-\end{center}
-
-\subsection*{Mutual information between various real space members}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-01-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-\end{center}
-
-\subsection*{Impurity entanglement entropy and spin-spin correlations}
-
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/EE-d-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-\end{center}
-
-\subsection*{Real-space correlations}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/r1p-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-od-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-opp-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-
-	\includegraphics[width=0.3\textwidth]{../figures/r-par-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-ising-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-charge-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-\end{center}
-
-\section{Presence of sub-dominant pair fluctuations}
-\begin{center}
+
+\begin{figure}
+	\includegraphics[width=0.5\textwidth]{../figures/overlaps_gs-J=10.000.pdf}\\
+	\includegraphics[width=0.5\textwidth]{../figures/corrs_gs-J=10.000.pdf}
+\end{figure}
+
+\subsection{Presence of sub-dominant pair fluctuations}
+
+\begin{figure}
 	\includegraphics[width=0.4\textwidth]{../figures/odlro-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\captionof{figure}{Growth of pair fluctuations \(p^\dagger_d p_0\) between the impurity and the zeroth site towards the critical point, \(p^\dagger=c^\dagger_\uparrow c^\dagger_\downarrow\) being the local pair creation operator.
+	\caption{Growth of pair fluctuations \(p^\dagger_d p_0\) between the impurity and the zeroth site towards the critical point, \(p^\dagger=c^\dagger_\uparrow c^\dagger_\downarrow\) being the local pair creation operator.
 This comes at the cost of the spin-flip fluctuations \(S_d^+ s_0^- + \text{h.c.}\).
@@
 	\label{pair_fluc}
-\end{center}
+\end{figure}
 
@@
 
-\section{Spectral functions}
+\subsection*{Correlations in ground state}
+\begin{figure*}
+	\includegraphics[width=0.45\textwidth]{../figures/corr-k-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/mi-dk-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/mi-01-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/mi-d0-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.45\textwidth]{../figures/EE-d-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+\end{figure*}
 
@@
 \begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.100.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.145.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.188.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.250.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.26.pdf}
+	\includegraphics[width=0.2\textwidth]{../figures/spec_func_Ub_by_J=-0.100.pdf}
+	\includegraphics[width=0.2\textwidth]{../figures/spec_func_Ub_by_J=-0.250.pdf}
+	\includegraphics[width=0.2\textwidth]{../figures/spec_func_Ub_by_J=-0.26.pdf}
 \end{center}
 
-\subsection{Impurity-bath off-diagonal spectral function \(A_{dz}(\omega)\)}
-These are the frequency-domain spectral functions for the off-diagonal retarded propagator \(-i\theta(t)\left<\left\{c_{d\sigma}(t),c^\dagger_{0\sigma}\right\}  \right>\):
-\begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.100.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.145.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.188.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.250.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.26.pdf}
-\end{center}
-
-\subsection{Bath spectral function \(A_{00}(\omega)\)}
-\begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_Ub_by_J=-0.000.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_Ub_by_J=-0.125.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_Ub_by_J=-0.250.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_Ub_by_J=-0.26.pdf}
-\end{center}
-
-\subsection{Width of central peak of \(A_{dd}\)}
-
-\begin{center}
-\includegraphics[width=0.45\textwidth]{../figures/spec_func_width_fit.pdf}
-\end{center}
-
-\section{What, then, are the minimal ingredients for a metal-insulator transition?}
-We now return to the question posed at the very beginning in section~\ref{sec:min_model}: What is the minimal auxiliary model that can demonstrate a metal-insulator transition in the bulk?
-To answer this question, we first recall all the relevant RG equations in the positive \(U\) regime:
-\begin{gather}
-	\Delta U_b = 0, ~ ~\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\frac{J^2}{d_2},\\
-	\Delta V = -\frac{3n_j V}{8}\left[\left(J + 4U_b/3\right) \left(\frac{1}{d_2} + \frac{1}{d_1}\right) + 4U_b/3\left(\frac{1}{d_3} + \frac{1}{d_0}\right)\right],\\
-	\Delta J = -\frac{n_j J\left(J + 4U_b\right)}{d_2}~.
-\end{gather}
-where \(d_1 > d_2 > d_3 > d_0\).
-We now consider various models with increasing number of parameters.
-
-\subsection{Only impurity correlation and hybridisation \(U,V\)}
-If we had only \(U\) and \(V\), the RG equations simplify to
-\begin{equation}\begin{aligned}
-	\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) < 0,~ ~ ~\Delta V = 0
-\end{aligned}\end{equation}
-\(U\) is irrelevant while the hybridisation \(V\) is marginal, so the fixed point is where the impurity is screened. The bulk model will always be metallic. There is no transition in such a model.
-
-\subsection{Impurity correlation, hybridisation and spin-exchange between impurity and bath \(U,V,J\)}
-If we now add a spin-exchange coupling \(J\) between the impurity and the bath into the Hamiltonian, we obtain the generalised SIAM studied in chapter~\ref{chap:urg1}.
-As discussed in that chapter, this is again similar to the previous case - the only stable fixed point is one of strong-coupling, and the bulk metal will never have an insulating phase.
-
-\subsection{Impurity correlation, hybridisation and local pairing interaction on the bath \(U,V,U_b\)}
-If we replace the \(J\) with an local interaction \(U_b\) on the bath, the RG equations undergo some changes:
-\begin{gather}
-	\Delta U_b = 0, ~ ~\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) = \frac{4V^2U}{\left(\omega - D/2 + U_b/2\right)^2 - U^2/4},\\
-	\Delta V = -n_j V U_b\left[\frac{\omega - D/2 + U_b/2}{\left(\omega - D/2 + U_b/2\right)^2 - U^2/4} + \frac{1}{\omega - D/2 + U_b/2}\right]~.
-\end{gather}
-This regime is interesting because it shows a variety of behaviour:
+\section{Conclusions}
+
 \begin{itemize}
-	\item For \(U_b>0\), the correlation \(U\) is irrelevant and \(V\) is relevant. This will produce a metal (see fig.~\ref{noJ_Ub_gt_0}).
-	\item For \(U_b<0\), both \(U\) and \(V\) are irrelevant, but \(V\) decays much faster than \(U\), and \(U\) saturates to a non-zero appreciable value which although lower than the bare value is much greater than 0 (see fig.~\ref{noJ_Ub_lt_0}).
-This behaviour is enhanced by making \(U_b\) more negative; \(V\) decays even faster to zero, while \(U\) saturates at higher values.
-If the bare bandwidth is increased, the fixed point value of \(U\) actually decreases, so it appears that on taking the thermodynamic limit, \(U\) renormalises to zero (see fig.~\ref{noJ_Ub_lt_0_D}).
+	\item discuss why the model is minimal
 \end{itemize}
 
-Neither of these cases give rise to an insulator, because \(U\) never renormalises to a non-zero fixed point value in the thermodynamic limit.
-
-\begin{center}
-	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=0.05_D=10_U.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=0.05_D=10_V.pdf}
-	\captionof{figure}{RG flows of \(U\) (left panel) and \(V\) (right panel) in the regime \(U_b>0\), for the auxiliary model with \(U,V,U_b\).
-The impurity correlation \(U\) is irrelevant while the hybridisation \(V\) is relevant, leading to a metallic phase in the bulk.}
-	\label{noJ_Ub_gt_0}
-
-	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=-0.10_D=10_U.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=-0.10_D=10_V.pdf}
-	\captionof{figure}{RG flows of \(U\) (left panel) and \(V\) (right panel) in the regime \(U_b<0\), for the auxiliary model with \(U,V,U_b\).
-The hybridisation \(V\) is sharply irrelevant, renormalising to zero, while the impurity correlation \(U\) survives at the fixed point.}
-	\label{noJ_Ub_lt_0}
-
-	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=-0.10_D=100_U.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=-0.10_D=100_V.pdf}
-	\captionof{figure}{RG flows of \(U\) and \(V\) in the regime \(U_b<0\) at a larger bandwidth, for the auxiliary model with \(U,V,U_b\).
-\(U\) now renormalises to zero, so an insulator is not possible in the thermodynamic limit.}
-	\label{noJ_Ub_lt_0_D}
-\end{center}
-
-\subsection{Attractive correlation \(U_b\) instead of \(V\): \(U,J,U_b\)}
-In the presence of these three couplings, the RG equations become
-\begin{equation}\begin{aligned}
-	\Delta U = -n_j J^2/d_2,~ ~ ~ \Delta J = -n_j J(J+4U_b)/d_2
-\end{aligned}\end{equation}
-Since \(J > 0\), \(\Delta U\) is always positive, so \(U\) is always relevant.
-For \(4U_b > -J\), \(\Delta J\) is also positive, and \(J\) is relevant.
-We end up in a metallic phase.
-However, for \(4U_b < -J\), \(J\) becomes irrelevant, and the fixed point is that of a local moment decoupled from the bath, which describes an insulating state in the bulk.
-
-\subsection{The full model?}
-We are therefore ultimately led to a model with all four parameters.
-This was studied in chapter~\ref{siam-attr-chap}, and was shown to display both metallic and insulating phases.
-This makes it clear that {\it the minimal model must have all three kinds of correlation: magnetic \((U,J)\), delocalisation \((V)\) and pair formation \((U_b)\)}.
-
-\chapter{From the auxiliary model to the bulk - single site approach}
-\label{chap:tile}
-
-\section{Creating \(N-\)site Hubbard Hamiltonian from Anderson impurity embedded in an interacting bath}
-
-Previously, we have worked out the grounstate phases of a single-impurity model with an interacting bath:
-\begin{equation}\begin{aligned}
-	\label{siam_attr}
-	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
-\end{aligned}\end{equation}
-
-We will use this as the auxiliary model to study the Hubbard model.
-We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
-Note that the impurity level is explicitly at half-filling, because the correlation term \(\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is symmetric under a particle-hole transformation \(\hat n_{d\sigma} \to 1 - \hat n_{d\sigma}\).
-Moreover, the conduction bath is also at half-filling, because we have set the chemical potential \(\mu\) to zero.
-These two ensure that the bulk model is also at half-filling.
-At the end of this section, we will also mention how the tiling works out in the presence of a non-zero filling.
-
-To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(i\) of the lattice, and the bath coupled to the impurity as the set of remaining \(N-1\) sites in the lattice.
-We will also identity the zeroth site of the SIAM lattice as one of the nearest neighbours \(j\) of \(i\):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(i,j) = -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n} \left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2
-\end{aligned}\end{equation}
-The tight-binding term sums over all nearest pairs \((m,n)\) that do not involve the site \(i\).
-In general \(i\) will have \(w\) nearest neighbours for a lattice with coordination number \(w\).
-The total local Hamiltonian for the site \(i\) is obtained by averaging over the Hamiltonians \(\mathcal{H}_\text{aux}(i,j)\) for all nearest neighbours \(j\) of \(i\):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(i) &= \frac{1}{w}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{w}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right)  \right.\\
-				  &\left. +J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\\
-				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
-				  &\left.- U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]
-\end{aligned}\end{equation}
-Once we have this local Hamiltonian for a particular site, we translate this over all sites \(i\):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& \sum_i \mathcal{H}_\text{aux}(i) = \sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
-				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\right]\\
-	=& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
-				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j\right]\right]
-\end{aligned}\end{equation}
-In the entire tight-binding term \(\sum_i\sum_{<m,n>,\sigma}^{m \neq i \neq n}\), each pair will appear \(N-2\) times, because that is the total number of sites that do not involve either \(m\) or \(n\).
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - 2t\left(N-2\right)\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{w}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
-				  &+ \left. J \vec{S_i}\cdot\vec{S}_j\right]\\
-				  &=-\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(2t (N-2) - \frac{2V}{w}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{w} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
-\end{aligned}\end{equation}
-We end up with a Hubbard-Heisenberg model:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j
-\end{aligned}\end{equation}
-The mapping between the parameters is
-\begin{equation}\begin{aligned}
-	\label{map_aux_bulk}
-	t_{H-H} = \left(2t (N-2) - \frac{2V}{w}\right),~ ~ U_{H-H} = \left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{w}
-\end{aligned}\end{equation}
-The conclusion is that we can tile Anderson models with interacting baths into a Hubbard-Heisenberg model:
-\begin{equation}\begin{aligned}
-	\label{siam_to_hubb}
-	\sum_i \mathcal{H}_\text{aux}(i) = \mathcal{H}_{H-H}
-\end{aligned}\end{equation}
-
-As mentioned before, no chemical potential \(\mu\) is generated becuase the auxiliary model was at half-filling, both in the impurity as well as in the bath.
-We can change the chemical potential by introducing two terms:
-\begin{equation}\begin{aligned}
-	\eta \sum_\sigma\left(n_{d\sigma} - \frac{1}{2}\right), \mu \sum_{i,\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
-\end{aligned}\end{equation}
-The first term is the particle-hole asymmetry term, and tuning that term moves the impurity away from half-filling.
-The second term is the usual chemical potential in the bath.
-Introducing these terms in the auxiliary model changes the bulk model into:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j + \mu_\text{H-H}\sum_{i\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
-\end{aligned}\end{equation}
-The only change is the generation of the last term. The mappings between the existing parameters and their auxiliary model counterparts remain the same, while \(\mu_\text{H-H}\) is given by
-\begin{equation}\begin{aligned}
-	\mu_\text{H-H} = \eta + \left(N-1\right) \mu
-\end{aligned}\end{equation}
-In the discussion henceforth, we will assume all the models are at half-filling. We will come back to the doped case at a later point in time.
-
-\section{Nature of the wavefunctions}
-In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full wavefunction \(\Psi\) is then obtained by constructing liner combinations of the eigenstates \(\psi_i\) of the local Hamiltonians such that \(\Psi\) satisfies Bloch's theorem: \(\Psi_{\vec k}(\vec r) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r - \vec R_i)\).
-To satisfy Bloch's theorem means to behave in acertain way under a translation operation \(T(\vec R)\) by some lattice distance \(\vec R = \sum_i n_i \vec a_i\):
-\begin{equation}\begin{aligned}
-T(\vec R)\Psi_{\vec k}\left(\vec r\right) = \Psi_{\vec k}(\vec r + \vec R) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r + \vec R - \vec R_i) = e^{i \vec{k}\cdot\vec{R}}\sum_i e^{i \vec{k}\cdot\left(\vec{R}_i - \vec R\right)} \psi_i(\vec r - (\vec R_i - \vec R)) = e^{\vec{k}\cdot\vec{R}}\Psi(\vec r)
-\end{aligned}\end{equation}
-At the end, we used the fact that \(\vec r_i - \vec R\) is just another lattice vector \(\vec R_j\).
-Note that the translation operator has been defined as an operation that simply advances the argument of the wavefunction from \(\vec r\) to \(\vec r + \vec R\).
-An equivalent definition can be given in terms of their action on position eigenkets: \(T(\vec R)\ket{\vec r} = \ket{\vec r - \vec R}\).
-These translation operators share eigenstates with the momentum operator:
-\begin{equation}\begin{aligned}
-	T\left( \vec R \right) \ket{\vec k} = \sum_{\vec r_i} e^{i \vec{k}\cdot\vec{r}_i}T\left( \vec R \right)\ket{\vec r_i} = e^{i \vec{k}\cdot\vec{R}}\sum_{\vec r_i} e^{i \vec{k}\cdot\left(\vec{r}_i - \vec R\right)}\ket{\vec r_i - \vec R} = e^{i \vec{k}\cdot\vec{R}} \ket{\vec k}
-\end{aligned}\end{equation}
-
-The bulk Hamiltonian obtained in eq.~\ref{siam_to_hubb},
-\begin{equation}\begin{aligned}
-	H_\text{H-H}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i} \mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i\right\}\right) \equiv \sum_{\vec R_i} \mathcal{H}_\text{aux}\left(\vec R_i\right)~,
-\end{aligned}\end{equation}
-also enjoys a Bloch's theorem. This is because the tiling procedure restores the translation symmetry of the lattice:
-\begin{equation}\begin{aligned}
-	H_\text{H-H}\left(\left\{\vec r_k + \vec R\right\}\right) =  \sum_{\vec R_i}\mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i + \vec R\right\}\right) = \sum_{\vec R_i} \mathcal{H}_{\text{aux},\tilde i}\left(\left\{\vec r_k - \vec R\right\}\right) = H_\text{H-H}(\left\{\vec r_k\right\})
-\end{aligned}\end{equation}
-There we used the fact that \(\vec r_k + \vec R\) simply translates the auxiliary model defined by the coordinate \(i\) to a new auxiliary model at the modified coordinate \(\tilde i: \vec R_i^\prime = \vec R_i + \vec R\).
-Since this transformation from one auxiliary model to another simply shuffles the group of all auxiliary models, the sum over the group remains the sum, and we recover the same bulk model.
-
-We can use the auxiliary model zero-bandwidth wavefunctions 
-\begin{equation}\begin{aligned}
-\psi^n_\text{aux}\left(\vec r_d - \vec R_i, \vec r_0 - \left(\vec R_i + \vec a\right)  \right) \equiv \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
-\end{aligned}\end{equation}
-with the impurity position \(\vec R_i\) and zeroth site position \(\vec R_i + \vec a\), to construct eigenstates of the bulk Hamiltonian.
-\(\vec R_i\) is a lattice vector, while \(\vec a\) is one of the \(w\) vectors that connect a lattice site with its nearest neighbours.
-This two site wavefunction can be obtained by first studying the full auxiliary model \(\mathcal{H}_\text{aux}\) under a renormalisation group, obtaining a fixed-point Hamiltonian in the IR, obtaining the IR eigenstate and then tracing out all lattice sites except the impurity and the zeroth site from this eigenstate.
-\(n=0\) is the ground state of the auxiliary model, and higher values denote the excited states.
-
-The following un-normalised combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
-\begin{equation}\begin{aligned}
-	\ket{\Psi^n_{\vec k}} = \frac{1}{w \sqrt N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
-\end{aligned}\end{equation}
-where \(N\) is the total number of lattice sites.
-The interpretation is that the set of \(n=0\) states form the lowest band in the spectrum of the lattice.
-Higher values of \(n\) produce the more energetic bands.
-The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\).
-We will actually work only in the lowest band \(n=0\), so we will drop the band index from now on and keep in mind that only the auxiliary model ground states appear in the formulation:
-\begin{equation}\begin{aligned}
-	\label{bloch-states}
-	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
-\end{aligned}\end{equation}
-where \(\lambda_{\vec k}\) is a normalisation factor and is defined by \(|\lambda_{\vec k}|^2 = |\braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}|^2 \); \(\ket{\vec k}\) is the momentum eigenstate for momentum \(\vec k\), and \(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
-Becuase of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(w\) choices.
-
-It is easy to verify that \(\Psi_{\vec k}\left(\left\{ \vec r_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \(\vec R\):
-\begin{equation}\begin{aligned}
-	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
-\end{aligned}\end{equation}
-In the last equation, we transformed \(\vec R_i \to \vec R_j = \vec R_i - \vec R\).
-Note that the argument \(\vec a\) does not change under a translation of the system, because that vector always represents the difference between the impurity lattice position and its nearest neighbours, irrespective of the absolute position of the impurity.
-
-The wavefunction can be even brought into the familiar Bloch function form:
-\begin{equation}\begin{aligned}
-	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\vec k} w N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\vec k} w N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
-	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
-\end{aligned}\end{equation}
-where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\vec k} w N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
-This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
-
-It is straightforward to show that these states form an orthonormal basis. We start by writing down the inner product of two distinct such states:
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
-	&= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
-	&= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-\end{aligned}\end{equation}
-At this point, we insert a complete basis of momentum eigenkets \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators:
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-	&= \frac{1}{\lambda_{\vec k}^* \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
-	&= \frac{1}{|\lambda_{\vec k}|^2 w^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-\end{aligned}\end{equation}
-At the last step, we used the summation form of the Kronecker delta function: \(\sum_{\vec R_i}e^{i \vec R_i \left( \vec k - \vec q \right) }\sum_{\vec R_j}e^{i \vec R_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\).
-The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \(\vec a, \vec a^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\vec k}\):
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\vec k}|^2 w^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\vec k}|^2 = \frac{1}{|\lambda_{\vec k}|^2 w^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\vec k}|^2 = \delta_{\vec k, \vec k^\prime}
-\end{aligned}\end{equation}
-This concludes the proof of orthonormality.
-
-To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
-\begin{equation}\begin{aligned}
-	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
-	&= \frac{1}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \frac{1}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}
-\end{aligned}\end{equation}
-To resolve the translation operators, we will now insert the momentum eigenstates \(\ket{\vec k}\) of the full model: \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) in between the operators.
-\begin{equation}\begin{aligned}
-	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \frac{N}{\lambda^*_{\vec k^\prime} \lambda_{\vec k} w^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \frac{N}{|\lambda_{\vec k}|^2 w^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \frac{N}{|\lambda_{\vec k}|^2 w^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\vec k}|^2}\\
-	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}
-\end{aligned}\end{equation}
-The momentum eigenket \(\ket{\vec k}\) can be expressed as a sum over position eigenkets at varying distances from \(\vec R_0\).
-This form allows a systematic method of improving the energy eigenvalue estimate, because the interacting in the impurity model is extremely localised, so the overlap between two auxiliary models decreases rapidly with distance.
-The majority of the contribution will come from the state at \(\vec R_0\), and improvements are then made by considering auxiliary models at further distances.
-
-\section{Single-particle Green's function}
-In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}} = \ket{\Psi^{n=0}_{\vec k=0}} = \frac{1}{\lambda_0 w N}\sum_{\vec R, \vec a}\ket{\psi_\text{aux}\left( \vec R, \vec a \right)}\) of the bulk Hamiltonian.
-To obtain Greens functions, we start by calculating real-space matrix elements of the bulk and auxiliary Hamiltonians.
-The states that we will consider are local excitations on top of the ground state: \(\ket{i} \equiv c^\dagger_{i\sigma}\ket{\Psi_\text{gs} }\).
-\(i\) represents a lattice site.
-Sandwiching eq.~\ref{siam_to_hubb} between \(\ket{i}\) and \(\bra{i}\), we get
-\begin{equation}\begin{aligned}
-	\label{diag_mat_ele_1}
-	\braket{i | H_\text{H-H} | i} = \frac{1}{|\lambda_0|^2 w^2 N^2}\sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime}} e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi_\text{aux}\left( \vec R_n, \vec a^\prime \right) | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma}  | \psi_\text{aux}\left( \vec R_m, \vec a \right)}
-\end{aligned}\end{equation}
-There are, in general, three auxiliary models in the final expression on the right hand side - one at \(\vec R_n\), one at \(\vec R_m\) and another at \(\vec R_j\).
-In order to rewrite everything in terms of a single auxiliary model at the origin \(\vec R_0\) of the lattice, we will use the translation operators:
-\begin{gather}
-	\ket{\psi_\text{aux}\left( \vec R_m, \vec a \right)} = T\left(\vec R_0 - \vec R_m\right) \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}, ~ \ket{\psi_\text{aux}\left( \vec R_n, \vec a^\prime \right)} = T\left(\vec R_0 - \vec R_n\right) \ket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)}\\
-	\mathcal{H}_\text{aux}\left( \vec R_j \right) = T\left(\vec R_0 - \vec R_j\right) \mathcal{H}_\text{aux}\left( \vec R_0 \right) T^\dagger\left(\vec R_0 - \vec R_j\right)
-\end{gather}
-Substituting these forms into the expression in eq.~\ref{diag_mat_ele_1} gives
-\begin{equation}\begin{aligned}
-	&\braket{i | H_\text{H-H} | i} =\\
-	&\sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_0|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma}  T\left( \vec R_0 - \vec R_m \right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}
-\end{aligned}\end{equation}
-We will now absorb some of the translation operators into the creation and annihilation operators \(c_{i\sigma}\) that describe the excitation:
-\begin{equation}\begin{aligned}
-	T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right) &= T^\dagger\left( \vec R_0 - \vec R_n \right) c_{\sigma}\left( \vec R_i \right)  T^\dagger\left(\vec R_j - \vec R_0\right) \\
-												    &= T^\dagger\left( \vec R_0 - \vec R_n \right) T^\dagger \left(\vec R_j - \vec R_0\right) T\left(\vec R_j - \vec R_0\right) c_{\sigma}\left( \vec R_i \right)  T^\dagger\left(\vec R_j - \vec R_0\right)\\
-												    &=T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}
-\end{aligned}\end{equation}
-There, we used \(T^\dagger(\vec R_1) T^\dagger (\vec R_2) = T^\dagger(\vec R_1 + \vec R_2)\). For the creation operator, we similarly get
-\begin{equation}\begin{aligned}
-	T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma} T\left( \vec R_0 - \vec R_m \right) = \left[T^\dagger\left( \vec R_0 - \vec R_m \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\right]^\dagger = c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)
-\end{aligned}\end{equation}
-The operator \(c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\) creates an electron of spin \(\sigma\) at the position \(\vec R_i - \vec R_j + \vec R_0\).
-It will be represented as \(c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\).
-Substituting these forms gives
-\begin{equation}\begin{aligned}
-	&\braket{i | H_\text{H-H} | i} \\
-	&= \sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_0|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime\right) | T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}
-\end{aligned}\end{equation}
-To resolve the remaining translation operators, we will now insert the eigenstates \(1 = \sum_{\vec k}\ket{\Psi_{\vec k}}\bra{\Psi_{\vec k}}\) in between the operators.
-\begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = \sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime, \vec k_1, \vec k_2}} \frac{e^{i\vec{k}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_0|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | \Psi_{\vec k_2}}\bra{\Psi_{\vec k_2}}T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)\\
-	\ket{\Psi_{\vec k_1}}\braket{\Psi_{\vec k_1} | \psi_\text{aux}\left( \vec R_0, \vec a \right)}
-\end{aligned}\end{equation}
-From Bloch's theorem, we have
-\begin{equation}\begin{aligned}
-T\left(\vec R_j - \vec R_m\right)\ket{\Psi_{\vec k_1}} = e^{i \vec{k}_1\cdot\left(\vec{R}_j - \vec R_m\right)}\ket{\Psi_{\vec k_1}}, ~ ~\bra{\Psi_{\vec k_2}}T^\dagger\left(\vec R_j - \vec R_n\right) = \bra{\Psi_{\vec k_2}}e^{-i \vec{k}_2\cdot\left(\vec{R}_j - \vec R_n\right)}~.
-\end{aligned}\end{equation}
- Substituting this gives
-\begin{equation}\begin{aligned}
-	&\braket{i | H_\text{H-H} | i} =\\
-	& \sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime, \vec k_1, \vec k_2}} \frac{e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right) + i\vec{R}_n\cdot\left(\vec{k}_2 - \vec k\right) + i\vec{R}_m\cdot\left(\vec{k} - \vec k_1\right)}}{|\lambda_0|^2 w^2 N^2}  \braket{\psi_\text{aux}\left( \vec R_0 \right) | \Psi_{\vec k_2}}\bra{\Psi_{\vec k_2}} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\Psi_{\vec k_1}}\braket{\Psi_{\vec k_1} | \psi_\text{aux}\left( \vec R_0 \right)}\\
-	&= \frac{1}{N} \sum_{\vec R_j}\sum_{\vec k_1,\vec k_2} e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right)} N^2 \delta_{\vec{k},\vec k_2} \delta_{\vec{k},\vec k_1} \bra{\psi^0_\text{aux}\left( \vec R_0 \right)} \ket{\vec k_2}\bra{\vec k_2} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\vec k_1}\bra{\vec k_1} \ket{\psi^0_\text{aux}\left( \vec R_0 \right)}\\
-	&= N \sum_{\vec R_j} \braket{\psi^0_\text{aux}\left( \vec R_0 \right) | \vec k}\bra{\vec k} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\vec k}\braket{\vec k | \psi^0_\text{aux}\left( \vec R_0 \right)}\\
-\end{aligned}\end{equation}
-Since \(\vec R_i + \vec R_0 - \vec R_j\) is a lattice translation vector, summing over \(\vec R_j\) means that \(\vec R_i + \vec R_0 - \vec R_j\) sums over all lattice sites \(\vec R_k\).
-This is equivalent to stating the translation symmetry of the lattice.
-Redefining \(\vec R_j\) to be equal to \(\vec R_k\), we get
-\begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = N |\braket{\psi^0_\text{aux}\left( \vec R_0 \right) | \vec k}|^2 \bra{\vec k} \sum_{\vec R_j} c_{\sigma}\left(\vec R_j\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left(\vec R_j\right)\ket{\vec k}
-\end{aligned}\end{equation}
-Even though it is computationally easier to consider the state \(\ket{\vec k}\) as the momentum eigenstates of the tight-binding kind, there is a more illuminating interpretation of this expression if we consider them as the eigenstates \(\ket{\Phi\left( \vec k \right) }\) of the full bulk model.
-With this choice, the expression can be seen as the sum of effects of creating a single-particle excitation \(c^\dagger_\sigma\) on the ground state \(\ket{\Psi_\text{gs} }\), at increasingly larger distances \(\vec R_j\) from the auxiliary model at \(\vec R_0\).
-The excitation is made to evolve through the auxiliary model \(\mathcal{H}_\text{aux}\left( \vec R_0 \right) \) centred at \(\vec R_0\).
-The excitation is ultimately annihilated and the state returns to the ground state.
-However, since we are describing the excitation of the bulk ground state using an auxiliary model Hamiltonian, we also need to multply this with the fidelity between the full ground state and the auxiliary model ground state.
-That is taken care of by the inner-product multiplying the matrix element.
-That inner product can be thought of as an overlap between a separable state and an entangled state - the full Hamiltonian state is obtained by entangling the overlapping auxiliary models, while the single auxiliary model groundstate is the separable state in this context.
-The inner product then becomes a measure of entanglement of the bulk ground state - the more the overlap with the separable state, the lower the entanglement: \(\varepsilon(\vec R_0,\vec k) \equiv 1 - |\braket{\psi^0_\text{aux}\left(  \right) | \Phi_0(\vec k)}|^2\).
-\begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = N \left( 1 - \varepsilon(\vec R_0,\vec k) \right) \bra{\Phi_0(\vec k)} \sum_{\vec R_j} c_{\sigma}\left(\vec R_j\right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\sigma}\left(\vec R_j\right)\ket{\Phi_0(\vec k)}
-\end{aligned}\end{equation}
-The more is the entanglement content within the groundstate, the lower is the contribution from a single auxiliary model \(\mathcal{H}_\text{aux}\left( \vec R_0 \right)\).
-This makes sense between the contributions will then be distributed across all the auxiliary models.
-On the other hand, when the entanglement is low, any single auxiliary model provides a large contribution, which can be understood from the fact that any single auxiliary model is sufficient to describe the full ground state.
-
-\clearpage
-As discussed above, the local nature of the auxiliary models (onsite matrix element only on the impurity and non-local matrix element only between impurity and zeroth site) renders all diagonal matrix elements zero, except the one for \(i=j\):
-\begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = \braket{i | \mathcal{H}_\text{aux,i} | i} = \braket{\psi_\text{aux} | c_{i\sigma} e^{-i \vec{k}\cdot\vec{R}_i} \mathcal{H}_\text{aux,i} e^{i \vec{k}\cdot\vec{R}_i} c^\dagger_{i\sigma} | \psi_\text{aux}} = \braket{\psi_\text{aux} | c_{i\sigma} \mathcal{H}_\text{aux,i} c^\dagger_{i\sigma} | \psi_\text{aux}} = \braket{\psi_\text{aux} | c_{d\sigma} \mathcal{H}_\text{aux} c^\dagger_{d\sigma} | \psi_\text{aux}}
-\end{aligned}\end{equation}
-At the last step, we recognised \(i\) as the impurity site and rewrote the expression entirely in terms of a site-independent auxiliary model.
-Similarly, the off-diagonal matrix element between two nearest-neighbour sites \(i,j\) is obtained as
-\begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | j} = \braket{i | \left(\mathcal{H}_\text{aux,i} + \mathcal{H}_\text{aux,j}\right) | j} = \frac{1}{w}\braket{\psi_\text{aux} | c_{i\sigma} e^{-i \vec{k}\cdot\vec{R}_i} \left(\mathcal{H}_\text{aux,i,j} + \mathcal{H}_\text{aux,j,i}\right) e^{i \vec{k}\cdot\vec{R}_j} c^\dagger_{j\sigma} | \psi_\text{aux}} \\
-	= \frac{1}{w}e^{i \vec{k}\cdot\left(\vec{R}_j - \vec{R}_i\right)}\braket{\psi_\text{aux} | \left(c_{d\sigma}\mathcal{H}_\text{aux} c^\dagger_{0\sigma} + c_{0\sigma}\mathcal{H}_\text{aux} c^\dagger_{d\sigma}\right) | \psi_\text{aux}}
-\end{aligned}\end{equation}
-\(\mathcal{H}_\text{aux,i,j}\) is the auxiliary model with \(i\) as the impurity site and \(j\) as the bath zeroth site.
-
-We now define the Greens {\it operators}:
-\begin{equation}\begin{aligned}
-	\mathcal{G}_{H-H} = \frac{1}{\omega - \left(H_{H-H} - E_\text{gs}\right) }, \mathcal{G}_\text{aux}(i) = \frac{1}{\omega - \left(\mathcal{H}_\text{aux}(i) - E_\text{gs}\right)}
-\end{aligned}\end{equation}
-Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian and also of the full model \(\mathcal{H}_{H-H}\).
-Rewriting eq.~\ref{siam_to_hubb} in terms of the operators \(\mathcal{G}\), we get
-\begin{equation}\begin{aligned}
-\sum_i \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i)\right) = \omega + E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_i \mathcal{G}^{-1}_\text{aux}(i) = \mathcal{G}^{-1}_{H-H}~,
-\end{aligned}\end{equation}
-We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model.
-Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(\mathcal{H}_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate.
-We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{w}\sum_j \sum_{k \in \text{NN of j}}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(j,k) c^\dagger_{i\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-The superscript \(p\) indicates that this is the particle propagation matrix element.
-Under the single site approximation, we ignore the hopping between multiple impurity that reside in separate instances of the auxiliary model.
-Therefore, the only operator \(\mathcal{G}^{-1}_\text{aux}(j)\) that affects the matrix element is \(j=i, k \in \text{NN of i}\).
-Moreover, because of translation invariance, all \(k\) are equivalent.
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \frac{1}{w} w\times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i) c^\dagger_{i\sigma} | \Phi_0} = \braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{d\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-where we have identified site \(i\) in the auxiliary model as the impurity.
-By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}(d)\), we get from the spectral representation
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{m,n} \braket{\Phi_0 | c_{d\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux}(d) \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d\sigma} | \Phi_0} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}
-\end{aligned}\end{equation}
-There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(\mathcal{H}_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\).
-We also defined \(d^p_n = \bra{\Phi_n}c^\dagger_{d\sigma}\ket{\Phi_0}\).
-The hole propagation matrix element can be obtained similarly:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn} 
-\end{aligned}\end{equation}
-where \(d^h_n = \bra{\Phi_n}c_{d\sigma}\ket{\Phi_0}\).
-The off-diagonal matrix elements can also be obtained similarly.
-The difference from the diagonal case is that only one out of the \(w\) nearest-neighbour pairs contributes to the matrix element:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{i,i+1} \equiv \braket{\Phi_0 | c_{i,\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{w}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i,i+1) c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{w}\braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{z,\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-Here, we identity \(i+1\) as the bath zero mode \(z\) and \(i\) as the impurity \(d\).
-We again define matrix elements \(z_n^p = \braket{\Phi_n | c^\dagger_{z\sigma} | \Phi_0}, z_n^h = \braket{\Phi_n | c_{z\sigma} | \Phi_0}\).
-Thus, the spectral representation of the matrix element is obtained as
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}
-\end{aligned}\end{equation}
-The hole counterpart is
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}
-\end{aligned}\end{equation}
-In summary, the spectral representation of the matrix elements of the four inverse Greens operators are given by
-\begin{gather}
-\label{green_eq_final_siam}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn}\\
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}
-\end{gather}
-
-In order to obtain the matrix elements of the Greens operators \(\mathcal{G}_{H-H}\) (as compared to its inverse), we note that we have just observed that the matrix elements of the inverse Greens operators are related to the matrix elements of another inverse operator through some coefficients.
-We can, therefore, use the identity
-\begin{equation}\begin{aligned}
-\left(\hat O\right)_{ij} = \bra{i} \hat O \ket{j} = \sum_{m,n} \braket{i|m} \left(\hat O\right)_{mn} \braket{n|j} \implies \left(\hat O^{-1}\right)_{ij} = \sum_{m,n} \braket{i|m} \left(\hat O^{-1}\right)_{mn} \braket{n|j}
-\end{aligned}\end{equation}
-We can now identify \(\left(\hat O^{-1}\right)_{mn}\) as the matrix elements of \(\mathcal{G}_\text{aux}^{-1}\) in our expressions.
-Using the above relation, we can therefore write the spectral representation of the matrix elements of the Greens operators as
-\begin{gather}
-	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\\
-	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}_\text{aux}(d, -\omega) \right)_{nn}
-\end{gather}
-
-The Lehmann-Kallen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements.
-Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
-\begin{equation}\begin{aligned}
-	\label{greens_func_siam}
-	\left(G_{H-H}(\omega)\right)_\text{loc} = \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right] \\
-	= G(\omega)_\text{aux,dd}
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-	\left(G_{H-H}(\omega)\right)_\text{n-n} = \left(G_{H-H}(\omega)\right)_{i,i+1}^p - \left(G_{H-H}(-\omega)\right)_{i+1,i}^h = \frac{1}{w}\sum_n \left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn} \right.\\
- - \left.\left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]= \frac{1}{w}G(\omega)_\text{aux,dz}
-\end{aligned}\end{equation}
-
-\section{Spectral functions and self-energies}
-
-The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
-\end{aligned}\end{equation}
-where $\vec{r_i}$ is the position vector of a particular lattice site.
-Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites.
-As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
-As we do not have real space Greens function that are more non-local than nearest neighbour, we will attempt to obtain momentum space Greens function from these two contributions:
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
-\end{aligned}\end{equation}
-The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, w\right]\right\}$.
-\begin{equation}\begin{aligned}
-	\label{k_Gf_siam}
-	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} = G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k}\\
-			     &= \sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
-\end{aligned}\end{equation}
-where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\). For example, on a d-dimensional hypercubic lattice, we obtain
-\begin{equation}\begin{aligned}
-	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i
-\end{aligned}\end{equation}
-On a 2D square lattice with lattice spacing $a$, this simplifies to
-\begin{eqnarray}
-	\label{2dsquaretb}
-\xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
-\end{eqnarray}
-where \(\epsilon_{\vec{q}} = -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})\) is the tight-binding dispersion.
-
-We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
-\begin{equation}\begin{aligned}
-	A_\text{H-H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega))\\ 
-	&= -\frac{1}{\pi} \textrm{Im}\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\\
-	&= A_\text{aux,dd} + \frac{\xi_{\vec k}}{w} A_\text{aux,dz}
-\end{aligned}\end{equation}
-where 
-\begin{eqnarray}
-G_\text{aux,dd} &=& \sum_n\left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\nonumber\\
-G_\text{aux,dz} &=& \sum_n\left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
-\end{eqnarray}
-and the spectral function $A_\text{aux,dd}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dd}$~,~$A_\text{aux,dz}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dz}$.
-Further,
-\begin{equation}\begin{aligned}
-A_\text{H-H}(\vec{r}=0,\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{r}=0,\omega)) 
-= A_\text{aux,dd}
-\label{main}
-\end{aligned}\end{equation}
-
-From the local Greens function, we can write down the local self-energy using Dyson's equation: \(\Sigma = \left(G^{(0)}\right)^{-1} - G^{-1}\).
-\(G^{(0)}\) is the non-interacting Greens function.
-Here, non-interacting is defined as the absence of \(U,J\) in the bulk model, and hence the absence of \(U,U_b,J\) in the auxiliary model.
-In real space, the local and nearest-neighbour self-energies are therefore
-\begin{equation}\begin{aligned}
-	\left(\Sigma_\text{H-H}(\omega)\right)_\text{loc} = \left(\left(G_{H-H}(\omega)\right)_\text{loc}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_\text{loc}\right)^{-1} = \left(G(\omega)_\text{aux,dd}^{(0)}\right)^{-1} - \frac{1}{w}\left(G(\omega)_\text{aux,dd}\right)^{-1} \\
-	\left(\Sigma_\text{H-H}(\omega)\right)_\text{n-n} = \left(\left(G_{H-H}(\omega)\right)_\text{n-n}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_\text{n-n}\right)^{-1} = \left(G(\omega)_\text{aux,dz}^{(0)}\right)^{-1} - \frac{1}{w}\left(G(\omega)_\text{aux,dz}\right)^{-1}\\
-\end{aligned}\end{equation}
-
-The \(k-\)space self-energy can be similarly obtained from the \(k-\)space Greens functions
-\begin{equation}\begin{aligned}
-	\label{self-energy1}
-	\Sigma_{H-H}(\vec k,\omega) = \left(\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_{\vec k}\right)^{-1} = \frac{1}{G(\omega)_\text{aux,dd}^{(0)} + \frac{\xi_{\vec k}}{w}G(\omega)_\text{aux,dz}^{(0)}} -  \frac{1}{G(\omega)_\text{aux,dd} + \frac{\xi_{\vec k}}{w}G(\omega)_\text{aux,dz}}
-\end{aligned}\end{equation}
-Just to clarify the notation, we reiterate that bulk quantities with a superscript \((0)\) are for the non-interacting Hamiltonian and defined at \(U_\text{H-H}=J_\text{H-H}=0\), while the auxiliary model quantities with that superscript are evaluated in the non-interacting auxiliary model at \(U=J=U_b=0\).
-The non-interacting model is simply a resonant-level model with the impurity level at zero energy.
-Such a model is exactly solvable, and the corresponding Greens functions are given by
-\begin{equation}\begin{aligned}
-	G(\omega + i\eta)_\text{aux,dd}^{(0)} = \frac{1}{\omega + i\left(\Delta + \eta\right)}, ~ ~ ~ G(\omega + i\eta)_\text{aux,dz}^{(0)} = \sum_{\vec k} G(\omega)^{(0)}_{\vec k} V G(\omega + i\eta)_\text{aux,dd}^{(0)}
-\end{aligned}\end{equation}
-where \(\Delta = \pi \rho V^2\) is the hybridisation parameter, assuming a uniform density of states \(\rho\), and \(G(\omega)^{(0)}_{\vec k}\) is the free electron Greens function at momentum \(\vec k\).
-
-\section{Evidence for the Mott MIT}
-Through the URG study of the generalised SIAM with correlation (eq.~\ref{siam_attr}) shown in chapter \ref{siam-attr-chap}, we can conclude the following about that model:
-\begin{itemize}
-	\item For \(U_b > J/4\), the couplings \(J\) and \(V\) become irrelevant while \(U\) is relevant, which means that \textbf{the impurity gets cut off from the bath at low energies}.
-\begin{center}
-	\includegraphics[width=0.7\textwidth]{../figures/phase-map-MIT.pdf}
-\end{center}
-\item The impurity spectral function \(A_{dd}(\omega)\) and the impurity-bath real space off-diagonal Greens function \(A_{d0}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
-The gap in the diagonal spectral function shows that the impurity site cannot fluctuate through gapless excitations, while the vanishing of the off-diagonal spectral function shows that an electron on the impurity site cannot delocalise out of that site.
-Other measures like mutual information and spin-spin correlations also show a sharp change on crossing that value, demonstrating \textbf{the destruction of the Kondo cloud and the stabilisation of the local moment on the impurity}.
-
-\begin{figure}[!htb]
-\centering
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_Ub_by_J=-0.100.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_Ub_by_J=-0.250.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_Ub_by_J=-0.26.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.100.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.250.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.26.pdf}
-	\caption{Evolution of diagonal and off-diagonal spectral functions across the transition.}
-	\label{spec_func_mit}
-\end{figure}
-
-\begin{figure}[!htb]
-\centering
-	\includegraphics[width=0.3\textwidth]{../figures/corr-k-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/corr-d0-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r1p-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\caption{Evolution of correlation functions and mutual information across the transition.}
-\end{figure}
-
-	\item In the context of the auxiliary model, this represents an \textbf{impurity phase transition} from the completely-screened spin-singlet phase to the unscreened local moment phase.
-
-\begin{figure}[!htb]
-\centering
-	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=10.000.pdf}
-	\caption{Evolution of the zero-bandwidth ground state across the transition.}
-\end{figure}
-
-Using the mappings between the auxiliary model parameters and the bulk parameters (eq.~\ref{map_aux_bulk}), one can define a critical value \(r^{*}\) of the ratio \(r = U_{H-H}/J_{H-H}\) at the critical points \(-U_b/J=1/4\) \textit{for a given and fixed value of \(U\)}.
-We will now argue that this critical point describes a metal-insulator transition.
-For \(r < r^{*}\), the well-defined low-\(\omega\) central peak in the impurity spectral function, as well as the large mutual and information correlations, in the ground state, among the members of the Kondo cloud or between the impurity and the zeroth site show that the impurity and the bath are very strongly entangled, and the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) are non-zero at low \(\omega\).
-This means that both the local and the nearest-neighbour Greens functions, that are related to these parameters via eq.~\ref{greens_func_siam}, have poles at low\(-\omega\) and support the propagation of electrons through gapless excitations.
-Since the spectral function is also very simply related to that of the auxiliary model (eq.\eqref{main}), the former also shows the same zero-energy resonance.
-
-On the other side \(r > r^{*}\) of the critical point, we know that the impurity gets decoupled from the bath, such that the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) vanish.
-This is simply the loss of spectral weight at low-\(\omega\) because of the removal of the gapless excitations, and is demonstrated through both the diagonal and off-diagonal spectral functions in fig.~\ref{spec_func_mit}.
-This then implies that the bulk Greens functions will also gap out at low energies, and that describes an insulating phase where the electrons get "jammed" in the local states.
-By the same argument as above, the bulk spectral function also sees a gap in this phase when the impurity spectral function is gapped (see eq.\eqref{main}).
-
-Finally, using eqs.\eqref{map_aux_bulk} and the criticality condition $U_{b}^{*}=-\frac{J^{*}}{4}$, we can offer a functional form for the critical value of the parameter $r^{*} = U_{H-H}^{*}/J_{H-H}^{*}$
-\begin{eqnarray}
-r^{*} &=& \frac{U_{H-H}^{*}}{J_{H-H}^{*}} = \frac{w}{4}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)
-\end{eqnarray}
-where $U^{*}$ and $J^{*}$ are the values of the on-site and Kondo couplings of the auxiliary model at the auxiliary model (i.e., the generalised SIAM with a correlated bath) at the transition between the Kondo screened and the local moment phases.
-Parametrising the bath correlation coupling as $U_{b}=-\frac{U}{10}$, we obtain $U^{*}/J^{*}=5/2$, and $r^{*} = 2$ for the 2D square lattice Hubbard-Heisenberg model (with coordination number $w=4$).
-In general, $w=2d$ for the $d$-dimensional hypercubic lattice, and
-$r^{*}_\text{hyperc.} = \frac{d}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)$.
-The growth of $r^{*}$ with $d$ indicates that the MIT is increasingly rendered difficult in a higher dimensional hypercubic lattice, as it is easier for electrons to delocalise and a very large on-site repulsion is needed to overcome this.
-\end{itemize}
-
-\section{Important Remarks}
-\subsection{Topological nature of the transition}
-As shown in section~\ref{lutt_theorem}, there is a difference in the value of the Luttinger volume between the local moment (LM) and the strong-coupling (SC) fixed points.
-If we define \(\mathcal{N}_L\) as the Luttinger volume with the spin-degeneracy accounted for, we can write
-\begin{equation}\begin{aligned}
-	\label{lutt_change}
-	\mathcal{N}_L^\text{lm} - \mathcal{N}_L^\text{sc} = 1
-\end{aligned}\end{equation}
-where \(\mathcal{N}_L^\text{lm},\mathcal{N}_L^\text{sc}\) are the Luttinger volumes at the local moment and strong-coupling fixed points respectively.
-This equation expresses the fact that the Luttinger volume of the bath increases by \(1\) when the system is tuned from LM to SC, and this happens because the single-particle impurity excitation in the lower-Hubbard at the atomic limit gets transferred to the bath Greens function in the process.
-The quantity which tracks this transfer is therefore \(\mathcal{N}_\text{imp}\), the number of poles minus the number of zeros in the impurity Greens function at and below the Fermi surface:
-\begin{equation}\begin{aligned}
-	\label{imp_count_def}
-	\mathcal{N}_\text{imp} = \begin{cases}
-		1 & \text{ at LM}\\
-		0 & \text{ at SC}
-	\end{cases}\implies \Delta \mathcal{N}_\text{imp} = 1
-\end{aligned}\end{equation}
-The Luttinger volume \(\mathcal{N}_L\) is related to this impurity count by the equation
-\begin{equation}\begin{aligned}
-	\mathcal{N}_L = \mathcal{N} - \mathcal{N}_\text{imp}
-\end{aligned}\end{equation}
-where \(\mathcal{N}\) is the total number of electrons in the system, accounting for the spin degeneracy.
-If we keep this total number fixed (isolated system), the changes in the impurity count and Luttinger volume become constrained:
-\begin{equation}\begin{aligned}
-	\Delta \mathcal{N}_L = - \Delta \mathcal{N}_\text{imp}~.
-\end{aligned}\end{equation}
-Eq.~\ref{imp_count_def} then readily implies eq.~\ref{lutt_change}.
-
-In order to connect this impurity topological change with the bulk model, we write the total number of particles in the bulk system in the following manner:
-\begin{equation}\begin{aligned}
-	\mathcal{N} = \mathcal{N}_\text{loc} + \mathcal{N}_\text{deloc}
-\end{aligned}\end{equation}
-\(\mathcal{N}_\text{loc}\) is the number of real poles minus the number of zeros of the local Greens function.
-\(\mathcal{N}_\text{deloc}\) is the number of real poles minus the number of zeros of the \(k-\)space Greens functions.
-The former (latter) contributes only in the insulating (metallic) phase, because in the metallic (insulating) phase, the local (\(k-\)space) Greens function develop imaginary self-energy and the real poles in these Greens functions get replaced by imaginary poles.
-Together, these two terms accurately count the total number of particles in both these phases.
-These two terms are defined as
-\begin{equation}\begin{aligned}
-	\mathcal{N}_\text{loc} = \sum_i \mathcal{N}_i = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_i(z)\right], ~ ~ ~\mathcal{N}_\text{deloc} = \sum_k \mathcal{N}_k = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_k(z)\right] = \mathcal{N}_L
-\end{aligned}\end{equation}
-\(G_i(z)\) is the local Greens function at site \(i\) of the bulk model, and \(G_k(z)\) is the \(k-\)space Greens function in the bulk model.
-\(N_\text{deloc}\) is just the Luttinger volume \(\mathcal{N}_L\) of the bulk system.
-With this, the total number of particles in the bulk can be expressed as
-\begin{equation}\begin{aligned}
-	\label{bulk_total}
-	\mathcal{N} = \sum_i \mathcal{N}_i + \mathcal{N}_\text{L}
-\end{aligned}\end{equation}
-From eq.~\ref{greens_func_siam}, we know that the bulk local Greens function is equal to that of the auxiliary model, and that gives \(\sum_i \mathcal{N}_i = \mathcal{N}_\text{imp}\sum_i = \mathcal{N} \mathcal{N}_\text{imp}\).
-There we used the fact that for a half-filled system, the total number of sites is equal to the total number of particles in the system.
-Substituting this into eq.~\ref{bulk_total} and again using \(\Delta \mathcal{N} = 0\) gives
-\begin{equation}\begin{aligned}
-	\mathcal{N} = \mathcal{N} \mathcal{N}_\text{imp} + \mathcal{N}_\text{L} \implies \Delta \mathcal{N}_\text{L} = - \mathcal{N} \Delta \mathcal{N}_\text{imp}
-\end{aligned}\end{equation}
-We already know that \(\Delta \mathcal{N}_\text{imp}=1\) across the transition, so we get
-\begin{equation}\begin{aligned}
-	\mathcal{N}_L^\text{metal} - \mathcal{N}_L^\text{insulator} = \mathcal{N}\left(\mathcal{N}_\text{imp}^\text{sc} - \mathcal{N}_\text{imp}^\text{lm}\right) = \mathcal{N}
-\end{aligned}\end{equation}
-The metal-insulator transition is therefore characterised by a change in the topological quantity \(\mathcal{N}_L\).
-The topological nature arises from the fact that it can be expressed in terms of winding numbers related to the corresponding Greens functions.
-\(\mathcal{N}_\text{imp}\), which derives from the impurity Greens function \(G_d\), is related to the winding numbers of the curves \(\text{Det}[G_d^{-1}(\Gamma^<)]\) and \(\text{Det}[G_d^{-1}(\Gamma^0)]\).
-The winding number is simply the number of times this function encircles the origin when traced on the curves \(\Gamma^<\) and \(\Gamma^0\) that enclose all poles inside and on the Fermi surface respectively.
-An example of such a winding number is shown in fig.~\ref{imp_winding}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[scale=0.2]{../figures/luttinger_top_change.png}
-	\caption{The green lines describe the winding number related to the impurity Greens function, while the blue lines do it for the bath.
-At the local moment fixed point \(V=0\), the impurity has a winding number of 1 because the curve encircles the origin once.
-At the strong-coupling fixed point, this winding number becomes zero, indicated by the fact that the curve does not encircle the origin even once.
-The reduction in the winding number on the part of the impurity is directly linked to the increase in the winding number of the bath - it encircles the origin once at the local moment fixed point but twice at strong-coupling.}
-	\label{imp_winding}
-\end{figure}
-
-\subsection{Greens function in the insulating phase: the Hubbard bands and mottness}
-In the insulating state, the cluster becomes a local moment and the bulk system reduces to the atomic limit \(H = -\frac{U}{2}\sum_i\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\).
-The Greens function in this limit is given in Appendix~\ref{atomic limit}.
-From eq.~\ref{atomic_limit_gf}, we have
-\begin{equation}\begin{aligned}
-	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 + \left<\tau_{i }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i}\right>}{\omega + \frac{U}{2}}
-\end{aligned}\end{equation}
-where \(\tau_i = \sum_\sigma \hat n_{i,\sigma} - 1\).
-At half-filling \(\left<\tau_{i}\right>=0\), the low and high-energy poles have equal spectral weights.
-\textit{This is different from the situation in a band insulator, where the valence band has all the spectral weight in the ground state while the conduction band is empty.} On doping holes into the system such that \(\left<\tau_{i}\right> = -x < 0\), spectral weight is transferred from the upper Hubbard band at \(\omega = U/2\) to the lower one at \(\omega = -U/2\):
-
-\begin{equation}\begin{aligned}
-	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 - x}{\omega - \frac{U}{2}} + \frac{1 + x}{\omega + \frac{U}{2}}
-\end{aligned}\end{equation}
-\textit{This transfer of spectral weight across energy scales of the order of \(U\), as well as the lack of poles at zero energies, is referred to as mottness}~\cite{phillips2006mottness}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/hubbard_bands.pdf}
-	\caption{Structure of the Greens function in the atomic limit.
-The two poles at \(\omega = \pm \frac{U}{2}\) form the two Hubbard bands.
-Doping the system leads to transfer of spectral weight between the bands.}
-\end{figure}
-
-\subsection{Nature of propagation: metal vs insulator}
-In the metallic state, the impurity in the auxiliary model hybridises with the bath through both 1-particle and 2-particle interactions.
-For any two auxiliary models differing by the locations \(i_1, i_2\) of the impurity, the baths will always overlap.
-This means that an electron that starts out from the impurity site at \(i_1\) can hop into the bath, and eventually reach \(i_2\) by hopping out of the other bath and into the other impurity.
-Such processes connect all sites of the lattice and \textit{allow spectral flow}.
-
-In the insulating state, each auxiliary model separates into an impurity and a bath that decoupled from each other.
-This means that the impurity cannot hybridise into the bath, and hence cannot tunnel into any other impurity.
-This leads to the atomic limit of the system, where each site develops a local moment configuration because of the repulsive local correlation, but these local moments cannot communicate with each other, either through spin-exchange processes or by breaking into holons and doublons.
-Any attempt at spectral flow fails because the boundaries of the system become disconnected from each other.
-
-A more accurate picture of the insulating and metallic phases can be obtained by working with a more complicated choice of the cluster.
-For instance, instead of a single impurity, one can take two correlated impurities interacting with each other through a single-particle hopping, and this cluster then interacts with the bath through the usual interactions.
-The ground state of such a cluster is actually a quantum liquid, consisting of the entangled spin and charge degrees of freedom.
-In the metallic state, various members of this liquid such as the holons, doublons and the spinons are free to propagate across the system through the baths.
-In the insulating state, it is this cluster that then gets decoupled from the other clusters.
-The composite degrees of freedom are then unable to propagate outside the cluster, and \textit{the holons and the doublons are bound to each other}~\cite{Mott_1949} within the confines of the cluster.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=0.55\textwidth]{../figures/metal_prop.pdf}
-	\caption{Propagation of electrons from one cluster to another through the bath, in the metallic state}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.75\textwidth]{../figures/ins_prop.pdf}
-	\caption{The clusters get isolated from each other in the insulator, because they get decoupled from their baths.}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.85\textwidth]{../figures/ins_prop_cluster.pdf}
-	\caption{Each cluster is a quantum liquid composed of spin \(\left(\uparrow,\downarrow\right) \) and charge \(\left(0,2\right) \) degrees of freedom.
-In the insulating state, these degrees of freedom get bound within the cluster and are unable to propagate outside.}
-\end{figure}
-
-\subsection{Presence of two self-energies under symmetry-breaking}
-The effective Hamiltonian that describes either the metallic or the insulating phase has $\mathrm{SU}(2)$ symmetry in both the spin and charge sectors.
-Since the repulsive correlation on the impurity picks out the spin sector, we focus on that for now.
-Applying a small magnetic field on the impurity breaks this spin-rotation symmetry and picks out either the up or the down state on the impurity, leading to two kinds of self-energies, one for each spin state~\cite{logan_2014,Logan_2015}.
-The Hamiltonian has the form \(H(h)_i = -\frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - h\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)\).
-The unique groundstate is \(\ket{\hat n_{i,\sigma = \text{sgn}(h)}=1,\hat n_{i,\sigma = -\text{sgn}(h)}=0}\), with an energy of \(E_\text{gs} = -\frac{U}{2} - h\).
-The Greens function is easiest to obtain from the Lehmann-Kallen representation (eq.~\ref{Gf_lk}):
-\begin{equation}\begin{aligned}
-	G_{i,\sigma} = \sum_{n}\left[||\bra{\text{GS}}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_\text{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{\text{GS}}||^2\frac{1}{\omega - E_\text{GS} + E_n}\right]\\
-\end{aligned}\end{equation}
-We have \(c_{i,\sigma}\ket{\text{GS}} = \ket{\hat n_i = 0}\delta_{\sigma,\text{sgn}(h)}\) and \(c^\dagger_{i,\sigma}\ket{\text{GS}} = \ket{\hat n_i = 2}\delta_{\sigma,-\text{sgn}(h)}\), so that the only excited states that give non-zero inner product is \(\ket{n}=\ket{\hat n_i = 0}\) for the second term and \(\ket{n}=\ket{\hat n_i=2}\) for the first term, with energies \(E_n=0\).
-Substituting these, we get
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(h) = \frac{\delta_{\sigma,-\text{sgn}(h)}}{\omega - \frac{U}{2} - h} + \frac{\delta_{\sigma,\text{sgn}(h)}}{\omega + \frac{U}{2} + h} = \frac{1}{\omega + \left(\frac{U}{2}+h\right)\sigma \times \text{sgn}(h) }
-\end{aligned}\end{equation}
-Taking the limit of \(h \to 0^\pm\) then gives
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(h=0^\pm) = \frac{1}{\omega \pm \frac{U}{2}\sigma}
-\end{aligned}\end{equation}
-The self-energies arising from the correlation \(U\) can also be obtained using Dyson's equation \(\Sigma = G^{-1} - G_0^{-1}\), where \(G_0^{-1} = \omega\) is the Greens function at \(U=0\).
-Using Dyson's equation, we get
-\begin{equation}\begin{aligned}
-	\Sigma_{i,\sigma} = \pm\frac{U}{2}\sigma
-\end{aligned}\end{equation}
-
-\section{Analytic consistency check - On the Bethe lattice}
-One can apply a test to this method: it involves considering the case of infinite number of nearest-neighbours $w\to\infty$ (the coordination number, and effectively the dimension).
-In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
-This allows a metal-insulator transition in the limit of $w\to\infty$ as well.
-In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}.
-This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy1}.
-Applying the limit of \(w\to \infty\) on that equation gives
-\begin{equation}\begin{aligned}
-	\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}\right\} = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux,dd}(\omega)\right\}^{-1}
-\end{aligned}\end{equation}
-where \(G^{(0)}(\vec k,\omega)\) is the non-interacting Greens function and \(G_\text{aux,dd}(\omega)\) is the site-diagonal Greens function of the auxiliary model.
-It is clear from the final form that only the diagonal term \(G_\text{aux,dd}(\omega)\) of the interacting Greens function affects the self-energy while the off-diagonal part \(G_\text{aux,dz}\) fails to contribute as \(w \to \infty\).
-Even the non-interacting part Greens function can be shown to be diagonal in the limit of \(w\to\infty\)~\cite{kuramoto_manybody}.
-From its definition in time domain, we have
-\begin{equation}\begin{aligned}
-	G^{(0)}(\vec k, t) = -i\theta(t) \left<\left\{c_{\vec k}(t), c^\dagger_{\vec k}\right\} \right> = -i\theta(t) \left<\left\{e^{i H^{(0)}t} c_{\vec k} e^{-i H^{(0)}t}, c^\dagger_{\vec k}\right\} \right> = -i\theta(t) e^{-i \epsilon_{\vec k}t}\left[ \left<1 - \hat n_{\vec k}\right> + \left<\hat n_{\vec k}\right>\right] = -i \theta(t) e^{-i \epsilon_{\vec k}t}
-\end{aligned}\end{equation}
-A quick Fourier transform to \(\omega-\)domain shows that this is identical to the \(G^{(0)}(\vec k, \omega)\) defined just above eq.~\ref{self-energy}.
-We note that \(|G^{(0)}(\vec k, t)| \leq 1\).
-Using the Fourier transform  definition
-\begin{equation}\begin{aligned}
-	f(\vec k) = \frac{1}{d_N}\sum_{\vec r_i}h(\vec r_i) e^{i \vec{k}\cdot\vec{r}_i}
-\end{aligned}\end{equation}
-where \(d_N\) is a factor that only depends on the total number of sites and not on the coordination number, we can write
-\begin{equation}\begin{aligned}
-	|G^{(0)}(\vec k, t)|^2 = \frac{1}{d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}
-\end{aligned}\end{equation}
-From the inequality \(|G^{(0)}(\vec k, t)| \leq 1\), we get
-\begin{equation}\begin{aligned}
-	1 \geq \frac{1}{N}\sum_k |G^{(0)}(\vec k, t)|^2 = \frac{1}{N d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* \underbrace{\sum_k e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}}_{N \delta_{\vec r_i = \vec r_j}} = \frac{1}{d_N^2}\sum_{\vec r_i} |G^{(0)}(\vec r_i, t)|^2
-\end{aligned}\end{equation}
-For a coordination number of \(w\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
-Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{w}\).
-In contrast, there is only one local Greens function, that for \(\vec r_i=0\).
-The local Greens function therefore scales independent of \(w\).
-This implies that
-\begin{equation}\begin{aligned}
-	\lim_{w\to \infty}G^{(0)}(\vec k,\omega) = G^{(0)}(\vec r=0,\omega)
-\end{aligned}\end{equation}
-Since both the non-interacting and the interaction Greens functions lose their non-locality, the self-energy becomes completely local in the limit of \(w \to \infty\).
-
-\chapter{Going to larger clusters - the two site approach}
-
-\section{Why expand the cluster?}
-The previous chapter dealt with treating the Hubbard-Heisenberg model using an auxiliary model that has a single-site cluster:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux} =  \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s}_0 - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
-\end{aligned}\end{equation}
-This was able to describe an impurity phase transition from screened strong-coupling phase to local moment weak coupling phase, upon tuning \(U_b/J\).
-This then leads to a metal-insulator transition in the bulk, owing to the relations between the Greens functions and spectral functions obtained earlier.
-The single-site nature of the cluster (there was only a single impurity) has the following consequences:
-\begin{itemize}
-	\item [1.] The \(k-\)space self-energy of the bath has only minimal \(k-\)dependence arising from nearest-neighbour non-locality between the impurity and the zeroth site of the bath.
-	\item [2.] The local moment phase (which reduces to a set of decoupled clusters) becomes just the atomic limit, because each cluster has just one impurity.
-\end{itemize}
-
-In this chapter, we will improve on these two points by considering a larger cluster that has two impurities interacting with each other:
-\begin{equation}\begin{aligned}
-	\label{dimer_ham}
-	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right]\\
-	 -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right) + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
-\end{aligned}\end{equation}
-\(d_1\) and \(d_2\), or \(d_i\) in general, represent the two impurity sites in the dimer.
-They interact with each other through the same hopping parameter \(t\) as the bath.
-Each of the impurities has its own correlation \(U\) and hybridisation with the bath through \(V\) and \(J\).
-Each impurity site \(d_i\) couples with a bath site \(0_i\).
-\(0_1\) and \(0_2\) are assumed to be adjacent to each other, connected by the hopping \(t\).
-The setup is shown in fig.~\ref{two-imp-cluster}.
-
-Note that this chapter only sets out the relations between such an auxiliary model and the corresponding bulk model (in this case, a Hubbard-Heisenberg), but does not describe the physics of this new auxiliary model.
-That requires performing a renormalisation group calculation for \(H_\text{aux}\), and that will be provided at a later point in time.
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.6\textwidth]{../figures/two-site-cluster.pdf}
-	\caption{Two-impurity SIAM hybridising with a bath}
-	\label{two-imp-cluster}
-\end{figure}
-
-\section{Solution of the Hubbard dimer using the Anderson molecule}
-This section tries to see how far we can we can go if we just work with the Anderson molecule as the smallest unit of tiling.
-We will attempt to reproduce the entire spectrum of a Hubbard dimer by creating a new Hamiltonian made up purely of Anderson molecules.
-This will guide us in deciding how to generalize the "tiling method" for a general $N-$site Hubbard model, as well as give indications as to whether we need a different smallest unit for tiling.
-
-The Hubbard dimer and Anderson molecules (zero-mode) are defined by the following respective Hamiltonians:
-\begin{equation}\begin{aligned}
-	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat n_{i \uparrow}\hat n_{i \downarrow} - \mu^H \sum_{\sigma, i=1,2}\hat n_{i\sigma}\\
-	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \epsilon_d^A \sum_{\sigma}\hat n_{d\sigma} + U^A\hat n_{d \uparrow}\hat n_{d \downarrow}
-\end{aligned}\end{equation}
-In the first Hamiltonian, the indices \(i=1,2\) refer to the two lattice sites that constitute the dimer.
-In the second Hamiltonian, the subscript \(d\) indicates the impurity site, while the subscript \(z\) indicates the zero-mode site.
-First, we will assume that the Hubbard dimer is at half-filling (\(\frac{1}{2}U^H = \mu^H\)):
-\begin{equation}\begin{aligned}
-	\label{hubb_dimer}
-	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \left(\frac{1}{2}U^H- \mu^H\right) \sum_{\sigma, i=1,2}\hat n_{i\sigma} + \text{constant}\\
-	    &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
-\end{aligned}\end{equation}
-Since the Hubbard Hamiltonian is at half-filling, we will also place the impurity at half-filling by setting \(\epsilon_d^A = -\frac{1}{2}U^A\):
-\begin{equation}\begin{aligned}
-	\label{and_dimer}
-	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \left(\epsilon_d^A + \frac{1}{2}U^A\right) \sum_{\sigma}\hat \tau_{d\sigma} + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow} + \text{constant}\\
-	    &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow}
-\end{aligned}\end{equation}
-The first step is to recreate the Hubbard dimer Hamiltonian eq.~\ref{hubb_dimer} using the Anderson molecule Hamiltonian eq.~\ref{and_dimer}:
-\begin{equation}\begin{aligned}
-	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
-	    &= \frac{1}{2}\left[-t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + t^H\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\right] + \frac{1}{2} 2U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
-	    &= \frac{1}{2}\left[-t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right)\bigg\vert_{z \to 2, d \to 1\atop{t^A \to t^H}} + t^A\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\bigg\vert_{d \to 2,z \to 1\atop{t^A \to t^H}} \right] \\
-	    &+ \frac{1}{2} \left(U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 1\atop{U^A \to 2U^H}} + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 2\atop{U^A \to 2U^H}}\right)\\
-	    &=\frac{1}{2}\left[H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 1, z \to 2\right) + H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 2, z \to 1\right)\right]
-\end{aligned}\end{equation}
-The conclusion we can draw from this is that the Hubbard dimer Hamiltonian can be obtained from the Anderson dimer Hamiltonian in the following fashion:
-\begin{itemize}
-	\item The essential idea is that we have to create a local Hubbard Hamiltonian for each site of the Hubbard lattice by replacing the impurity label \(d\) in the Anderson dimer with the label of the particular site.
-So if there are two sites, we will get two local Hamiltonians obtained by replacing \(d\) with 1 and 2 respectively.
-For each local Hamiltonian, the zero-mode label \(z\) is replaced by the site that is nearest to the one that \(d\) is being replaced by.
-So, if \(d \to 1(2)\), then \(z \to 2(1)\).
-	\item This, however, is not the only change that we must make, in order to get the local Hamiltonian for a particular site.
-Along with \(d\) and \(z\), we must also make the transformations \(t^A \to t^H, U^A \to 2U^H\).
-	\item Finally, once we have the local Hamiltonians for sites 1 and 2, we average them to get the total Hubbard Hamiltonian.
-\end{itemize}
-Note that we expect most of these "rules" to be specific for the dimer, and there will be generalizations to most of them for a general \(N-\)site Hubbard Hamiltonian.
-
-The wavefunctions for the \(N=2\) sector can also be connected through these transformations.
-Since both the Hamiltonians are analytically solvable, we can write down their groundstate wavefunctions [CITE PAVARINI]:
-\begin{equation}\begin{aligned}
-	\ket{\Psi^H_\text{GS}} &= a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) - a_2(U^H,t^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
-	\ket{\Psi^A_\text{GS}} &= a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) - a_2(\frac{1}{2}U^A,t^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
-	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right), E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right)
-\end{aligned}\end{equation}
-where 
-\begin{equation}\begin{aligned}
-	a_1(U,t) \equiv \frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) - U \right) }}, && a_2(U,t) \equiv \sqrt{\frac{\Delta(U,t) - U}{2\Delta(U,t)}}, &&\Delta(U,t) \equiv \sqrt{U^2 + 16t^2}\\
-\end{aligned}\end{equation}
-$a_1,a_2$ satisfy $a_1(-U,t) = -a_2(U,t)$ and $a_1(U,t)a_2(U,t)= \frac{2t}{\Delta(U,t)}$.
-From the forms of the wavefunctions and eigenenergies, we can immediately write down
-\begin{equation}\begin{aligned}
-	\ket{\Psi^H_\text{GS}} &= \frac{1}{2}\left[\ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 1, z \to 2\right) + \ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 2, z \to 1\right)\right]\\
-	E^H_\text{GS} &= E^A_\text{GS}\left(t^A, U^A \to t^H, 2U^H\right)
-\end{aligned}\end{equation}
-This shows that the rules laid out before work for the Hamiltonians, as well as the wavefunctions and energy eigenvalues of the \(N=2,0,4\) sector.
-These sectors specifically work because it is only in these sectors can we ensure that \(n_d = n_z\), which is required for the Hubbard Hamiltonian because \(n_1 = n_2\).
-In the other sectors (\(N=1,3\)), the impurity site and the zero-mode sites have to be singly-occupied in some part, and since the impurity site incurs a single-occupation cost of \(-\frac{U^H}{2}\) which is not borne by the zero-mode site, there is an intrinsic dissimilarity between the two sites of the Anderson molecule in this regime.
-This dissimilarity does not exist for the Hubbard model, so we cannot hope to connect the two models in this regime.
-Going forward, we will switch to using Hubbard dimers as the smallest tiling unit for a general Hubbard model.
-
-\comment{
-\section{Strategy by starting from a zero bandwidth model}
-We start with a SIAM (with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian.
-The fixed point Hamiltonian will in general involve the impurity site (with renormalised parameters $\epsilon_d^*, U^*$) interacting with a smaller number of momentum states.
-
- To obtain a comparatively simple but physically well-motivated auxiliary model, we identify $\sum_k c_k = \sqrt N c_0$; \(c_0\) is the operator for the zeroth site (the site nearest to the impurity).
-We will call the set of all \(N-2\) sites apart from the impurity and this zeroth site as the "effective bath".
-The fixed point Hamiltonian can be separated into these parts: an isolated impurity part, an isolated zeroth site part, an isolated effective bath part, hopping between impurity and the zeroth site and hopping between the zeroth site and the effective bath.
-\textit{As a simplification, we will ignore the correlation term \((U)\) on the effective bath}.
-In preparation of a symmetrization procedure, we will relabel the impurity site as 0, and the zeroth site as 1.
-With all these steps, the Hamiltonian takes the form:
- \begin{equation}\begin{aligned}
- 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow}}_\text{imp.
-\& zero-mode isolated} - \underbrace{t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{0-1 coupling} - \underbrace{t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{1 \& eff.
-bath coupling} - \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff.
-bath isolated}
- \end{aligned}\end{equation}
- \begin{figure}[!htb]
- 	\centering
- 	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.png}
- 	\caption{Correlated asymmetric Anderson molecule schematic version.
-It consists of an impurity site (blue) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink).
-The other sites (green) form the rest of the bath.
-Just the impurity site and the zeroth site have onsite repulsion.}
- 	\label{and_mol}
- \end{figure}
- This Hamiltonian is depicted in fig.~\ref{and_mol}.
-Such a Hamiltonian is, however, explicitly asymmetric between the sites 0 and 1 (the effective bath couples only to 1).
-To rectify that, we will symmetrize the coupling between the effective bath and the sites 0 and 1, by exchanging the sites 0 and 1.
-The resultant Hamiltonian is
- \begin{equation}\begin{aligned}
- 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow} - t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{2-site Hubbard model} +\underbrace{- t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)- t^A\sum_{j \in \atop{\text{NN of 0}}}\left(c^\dagger_{0\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{dimer \& eff.
-bath coupling} \\
- 	- \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff. bath isolated}
- \end{aligned}\end{equation}
-
- To further simplify this Hamiltonian, \textit{we will combine the nearest neighbour sites of \(1\) and \(0\) into a single site}.
- \begin{equation}\begin{aligned}
- 	c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}
- \end{aligned}\end{equation}
- This single site will act as the zeroth site of the effective bath, and it means that both sites of the Hubbard dimer hybridizes with the effective through just a single site.
-With this assumption, the Hamiltonian for "a Hubbard dimer hopping into an effective bath" takes the simple form
- \begin{equation}\begin{aligned}
- 	\label{dimer_p_bat}
- 	\tilde H^D = H^D(0,1) - t^D \sum_{\sigma}\left(c^\dagger_{0\sigma}c_{z\sigma} + c^\dagger_{1\sigma}c_{z\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}
- \end{aligned}\end{equation}
- \(H^D(0,1)\) is the Hubbard dimer Hamiltonian (shown in fig.~\ref{hubb-dim}):
- \begin{equation}\begin{aligned}
- 	\label{dimer_ham}
- 	H^D(0,1) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)
- \end{aligned}\end{equation}
- \begin{figure}[!htb]
- 	\centering
- 	\includegraphics[width=0.4\textwidth]{../figures/hubb_dim.png}
- 	\caption{Hubbard dimer schematic version. It again consists of two sites, like the Anderson molecule, but now both sites have onsite repulsion, and their is again inter-site hopping.}
- 	\label{hubb-dim}
- \end{figure}
- This entire procedure is depicted in fig.~\ref{dimer-bath}.
- \begin{figure}[!htb]
- 	\centering
- 	\includegraphics[width=\textwidth]{../figures/dimer_bath.pdf}
- 	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.
-We first add the asymmetric Hamiltonians to get a symmetrized Hamiltonian.
-In the symmetrized Hamiltonian, the dimer has \(w\) entry points into the bath, \(w\) being the coordination number of the lattice.
-We then merge these \(w\) lattice sites (enclosed in the black box) into a single lattice site.}
- 	\label{dimer-bath} 
- \end{figure}
- We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice.
-The next step in the programme is to tile the real-space lattice with this dimer+bath Hamiltonian \(\tilde H_D\) to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H = T\left[ \tilde H^{D} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the dimer Hamiltonian to span the target real-space lattice.
-We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.
- \begin{equation}\begin{aligned}
- 	\tilde H &= \frac{2}{Nw}\sum_{\left<ij\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\tilde H^D((0,1,z) \to (i, j, l))\\
- 		 &= \frac{2}{N}U^D\sum_{i} \tau_{i \uparrow}\tau_{i \downarrow} - \frac{2}{Nw}\left(1 + \frac{Nw}{2}\right)t^D\sum_{\left<ij\right>}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)
- \end{aligned}\end{equation}
- What that means is that we have placed the Hubbard dimer+bath system at all nearest neighbour pairs to reconstruct a new Hubbard model.
-If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as dropping the correlation on the bath sites, we can write
- \begin{equation}\begin{aligned}
- 	\tilde H = \mathcal{U} H^H \mathcal{U}^{-1} = TZ\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right]Z^{-1} T^{-1}~,
- \end{aligned}\end{equation}
- where $\mathcal{U} = TZ\mathcal{U}_{A}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation that maps from the original to the reconstructed Hubbard Hamiltonian.
- The existence of $U$ is contingent on how good the approximations are.
-
- We mention the two approximations made along the entire journey from the original Hubbard model to the reconstructed one here.
- \begin{itemize}
- 	\item We have replaced the full Hubbard model by an auxiliary system described by the SIAM Hamiltonian in eq.~\ref{clus_bath_siam}.
-The accuracy of this assumption is determined by the choice of the SIAM parameters, particular the self-energy and repulsion of the bath.
-As discussed before, the very choice of th cluster and bath spoil the translational invariance of the parent model.
- 	\item We then perform a unitary RG on $H^A$.
-This leads to a fixed-point Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$.
-At this point, we go from the fixed point Hamiltonian to the dimer+bath Hamiltonian in eq.~\ref{dimer_p_bat}.
-If we represent this transformation from the fixed point Hamiltonian to the Hamiltonian in eq.~\ref{dimer_p_bat} by an operator \(Z\), we can write $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$.
-This constitutes the second approximation we make.
-\end{itemize}
-}
-
-\section{Creating \(N-\)site Hubbard Hamiltonian from Hubbard dimer embedded in a bath}
-Similar to the previous chapter, we will now tile the lattice with the two-site auxiliary model
-\begin{equation}\begin{aligned}
-	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right]\\
-	 -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right) + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
-\end{aligned}\end{equation}
-For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site.
-Note that a uniform number of nearest neighbours means that there is perfect translational invariance on the lattice, which means there cannot be any edge sites.
-This is achieved by applying periodic boundary conditions on the edges of the lattice.
-For example, a square 2d lattice will have to be placed on a 2-torus.
-
-The first step is to identity the two impurity sites \(d_1\) and \(d_2\) and the two bath sites \(0_1\) and \(0_2\) as sitting on a square arrangement of the lattice.
-\(d_i\) form one arm of the square, while \(0_i\) form the opposite arm.
-This square arrangement is shown in fig.~\ref{square-arms}, and is dictated by the auxiliary model chosen and shown in fig.~\ref{two-imp-cluster}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.3\textwidth]{../figures/square_arms.pdf}
-	\caption{Placing the impurity and bath sites \(d_i,0_i\) on a chosen square of the lattice. The chosen square is marked in blue, the impurity sites in orange and the bath sites in green.}
-	\label{square-arms}
-\end{figure}
-The sites at the vertices of the square are labelled as \(i,j,k,l\). With this identification, the Hamiltonian becomes
-\begin{equation}\begin{aligned}
-	H_\text{aux}(i,j,k,l) = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \frac{U}{2}\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.} + c^\dagger_{j\sigma}c_{l\sigma} + \text{h.c.}\right) + J \vec{S}_{i}\cdot\vec{s}_{k} \right.\\
-+ \left.
-J \vec{S}_{j}\cdot\vec{s}_{l} - U_b\left(\hat n_{k \uparrow} - \hat n_{k \downarrow}\right)^2 - U_b\left(\hat n_{l \uparrow} - \hat n_{l \downarrow}\right)^2\right] -t \sum_\sigma \left(c^\dagger_{i,\sigma}c_{j,\sigma} + \text{h.c.}\right) -t \sum_{\left<m,n \right>, \sigma}^{m,n \notin \left\{i,j\right\}}\left(c^\dagger_{m\sigma,n\sigma} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-As before, the kinetic energy part sums over all nearest neighbour pairs that involve neither \(i\) nor \(j\).
-For a given arm \(i-j\), the square can be rotated along the axis \(i-j\) to give one square arrangements for each dimension perpendicular to the axis along \(i-j\).
-Since there are \(w/2\) dimensions, the number of such squares is \(w/2 - 1\).
-For each such square, we can obtain another square by reflecting the square in the plane of \(i-j-l-k-i\) and across the line \(i-j\).
-The total number of squares is therefore \(w - 2\).
-The upshot is that given \(i-j\), there are multiple ways of choosing \(k\); if \(\left\{\vec a\right\}\) represents the set of \(w\) primitive vectors that connect a particular lattice site to its nearest neighbours, \(k\) can be situated at all \(\vec r_i + \vec a\) for which \(\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0\).
-Choosing \(k\) then automatically fixes \(l\) at \(\vec r_j + \vec a\).
-The condition \(\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0\) simply means we only take those \(\vec a\) that are perpendicular to \(\vec r_j - \vec r_i\).
-Since there are \(w\) number of \(\vec a\) in total and 2 of them are parallel, the total number of choices of \(k,l\) is \(w-2\).
-For a 2D lattice, we have \(w=4\), so there are only two possible choices of the square.
-They are shown in fig.~\ref{square-arms-all}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.6\textwidth]{../figures/square_arms_all.pdf}
-	\caption{Placing the impurity and bath sites \(d_i,0_i\) on a chosen square of the lattice. The chosen square is marked in blue, the impurity sites in orange and the bath sites in green.}
-	\label{square-arms-all}
-\end{figure}
-
-The Hamiltonian for an arm \(i-j\) is then obtained by averaging over these squares:
-\begin{equation}\begin{aligned}
-	H_\text{aux}(i,j) = \frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
-\end{aligned}\end{equation}
-The final step is to sum over all nearest neighbour arms \(i-j\):
-\begin{equation}\begin{aligned}
-	\label{22siam_to_hubb}
-	H_\text{full} = \sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
-\end{aligned}\end{equation}
-
-There are four kinds of terms:
-\begin{itemize}
-	\item the first kind, \(A(i), A(j)\), depend only on either \(i\) or \(j\).
-They can be summed over easily by noting that the internal summation gives a constant factor of \(w-2\) which is canceled by the factor of \(1/(w-2)\) in the front, and the external summation gives \(\sum_{i,j}A(i) = \frac{w}{2} \sum_i A(i)\), because \(i\) is a member of \(w/2\) distinct nearest-neighbour pairs.
-	\item The second kind, \(B(i,j)\) depends on both \(i\) and \(j\).
-The internal summation is again cancelled by the prefactor.
-The external summation simply sums over all nearest-neighbour values of \(A(i,j)\).
-	\item The third kind, \(C(i,k), C(j,l)\), depend on \(i\) and \(k\).
-Here, the total summation \(\sum_{i,j,k}C(i,k)\) gives \((w-2)\sum_{\left<i,k\right>}\left(C(i,k) + C(k,i)\right)\), because the pair \((i,k)\) occurs \(w-2\) times corresponding to the \(w-2\) vectors \(\vec r_j - \vec r_i\) that are perpendicular to \(\vec r_i - \vec r_k\).
-The factor is again cancelled by the existing prefactor.
-	\item The fourth kind, \(D(k), D(l), E(k,l)\), depend on just \(k\), just \(l\) or both \(k\) and \(l\).
-For each pair \(i-j\) in the external summation, the particular pair \(k-l\) appears only once.
-When \(i-j\) is summed over, a factor of \(2(w/2-1)\) is generated because there are that many squares that involve \(k-l\).
-This factor cancels the inverse factor in front, giving \(\sum_{\left<k\right>} D(k), \sum_{\left<k,l \right>}E(k,l)\).
-\end{itemize}
-
- The full Hamiltonian reads
-\begin{equation}\begin{aligned}
-	H_\text{full} =& w\sum_i\left[- \frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\right] - t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + 4V\sum_{\sigma, \left<i,k\right>}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.}\right)\\
-		      &+ 4J \sum_{\left<i,k\right>}\left(\vec{S}_{i}\cdot\vec{S}_{k}\right) - 2 U_b\sum_k\left(\hat n_{k \uparrow} - \hat n_{k \downarrow}\right)^2 - \frac{Nw/2}{w-2}t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)\\
-	=& -\frac{1}{2}\left(Uw + 4U_b\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{Nw/2}{w-2}t + t - 4V\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 4J \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
-\end{aligned}\end{equation}
-The bulk model hence obtained is again a Hubbard-Heisenberg model.
-In eq.~\ref{2siam_to_hubb}, the total number of terms in the outer summation is \(Nw/2\).
-In order to make sure that this full Hamiltonian scales as \(N\), we divide this by \(w/2\):
-\begin{equation}\begin{aligned}
-	\label{2siam_to_hubb}
-	H_\text{full} &= \frac{2}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) = \frac{2}{w}\sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
-		      &= -\frac{1}{2}\left(2U + 8U_b/w\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{N}{w-2}t + 2t/w - 8V/w\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 8J/w \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
-\end{aligned}\end{equation}
-The mappings between the parameters of the auxiliary model and the bulk are
-\begin{equation}\begin{aligned}
-	t_\text{H-H} = \left(\frac{N}{w-2}t + 2t/w - 8V/w\right),~ ~ ~ U_\text{H-H} = 2U + 8U_b/w,~ ~ ~ J_\text{H-H} = 8J/w
-\end{aligned}\end{equation}
-
-We could have also inserted a spin-exchange interaction between the two impurities in the auxiliary model:
-\begin{equation}\begin{aligned}
-	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right] -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right)\\
-	+ J_d \vec{S}_{d_1}\cdot\vec{S}_{d_2} + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
-\end{aligned}\end{equation}
-In the presence of this term, the bulk Hamiltonian remains the same, but the expression of \(J_\text{H-H}\) changes.
-Since this term is similar in form to the term preceding it, we can easily obtain the updated expression:
-\begin{equation}\begin{aligned}
-	J_\text{H-H} = \frac{2}{w}\left(4J + 2J_d\right)
-\end{aligned}\end{equation}
-
-\section{Single-particle Green's function}
-We now define the Greens function {\it operators}:
-\begin{equation}\begin{aligned}
-	\mathcal{G}_{H-H} = \frac{1}{\omega^\prime - \left(H_{H-H} - E_\text{gs}^\prime\right) }, \mathcal{G}_\text{aux}(i,j) = \frac{1}{\omega - \left(\mathcal{H}_\text{aux}(i,j) - E_\text{gs}\right)}
-\end{aligned}\end{equation}
-Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian, while the primed quantities \(E_\text{gs}^\prime\) and \(\omega^\prime\) are the same quantities but for the full model \(\mathcal{H}_{H-H}\).
-While the auxiliary model is intensive, the full Hamiltonian is extensive and scales as \(N\):
-\begin{equation}\begin{aligned}
-	H_\text{full} &= \frac{2}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) \sim N H_\text{aux}(d_1,d_2)~.
-\end{aligned}\end{equation}
-This means that we must have \(\omega^\prime = N\omega\) and \(E_\text{gs}^\prime = N E_\text{gs}\).
-Rewriting eq.~\ref{2siam_to_hubb} in terms of the operators \(\mathcal{G}\), we get
-\begin{equation}\begin{aligned}
-\sum_{\left<i,j \right>} \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i,j)\right) = N\omega + N E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_{\left<i,j \right>} \mathcal{G}^{-1}_\text{aux}(i,j) = \mathcal{G}^{-1}_{H-H}~,
-\end{aligned}\end{equation}
-We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model.
-Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(\mathcal{H}_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate.
-We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-The superscript \(p\) indicates that this is the particle propagation matrix element.
-Under the auxiliary model approximation, we ignore the virtual entanglement between separate clusters.
-Therefore, the only operators \(\mathcal{G}^{-1}_\text{aux}(k,l)\) that affect the matrix element are those that satisfy \(i \in \left(k,l\right)\).
-There are \(w\) such pairs: \(\left\{k,l\right\} = \left\{i,j\right\} \forall~ j \in \text{NN of i}\).
-Moreover, because of translation invariance, all \(j \in \text{NN of i}\) are equivalent.
-These configurations are shown in fig.~\ref{diag_conrib}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/diagonal_contributors.pdf}
-	\caption{The various configurations of auxiliary models that contribute to the diagonal matrix element at site \(i\). Orange colour represents impurities and green represents bath sites.}
-	\label{diag_conrib}
-\end{figure}
-
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0} = \frac{2}{w} \times w \times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i, i+1) c^\dagger_{i\sigma} | \Phi_0} = 2\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-where we have identified site \(i\) in the auxiliary model as one of the impurities \(d_1\).
-We could very well have chosen \(d_2\) since the model is symmetric in \(d_1,d_2\).
-\(\mathcal{G}^{-1}_\text{aux}(d_1,d_2)\) is the Greens operator corresponding to the Hamiltonian in eq.~\ref{dimer_ham}.
-
-By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}\), we get from the spectral representation
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = 2\sum_{m,n} \braket{\Phi_0 | c_{d_1\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux} \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d_1\sigma} | \Phi_0} = 2\sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
-\end{aligned}\end{equation}
-There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(\mathcal{H}_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\).
-We also defined \(d^p_{i,n} = \bra{\Phi_n}c^\dagger_{d_i\sigma}\ket{\Phi_0}\).
-The hole propagation matrix element can be obtained similarly:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = 2\sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn} 
-\end{aligned}\end{equation}
-where \(d^h_{i,n} = \bra{\Phi_n}c_{d_i\sigma}\ket{\Phi_0}\).
-
-The off-diagonal matrix elements between two nearest-neighbour sites \(i\) and \(i+1\) can also be obtained similarly. Several  auxiliary models can contribute to such a matrix element:
-\begin{itemize}
-	\item those auxiliary models that have \(i\) and \(i+1\) as the two impurities. These give the contribution \\
-		\(\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0}\). 
-	\begin{equation}\begin{aligned}
-		\frac{2}{w}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0} = \frac{2}{w}\sum_{n} \left(d^p_{1,n}\right)^*d^p_{2,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
-	\end{aligned}\end{equation}
-	\item those that have \(i\) as an impurity and \(i+1\) as the corresponding bath site. There will be \(w-2\) of these in number:
-	\begin{equation}
-		(w-2) \times \frac{2}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{0_1\sigma} | \Phi_0} = \frac{2}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
-	\end{equation}
-		where \(z^p_{i,n} = \braket{\Phi_n | c^\dagger_{0_i,\sigma} | \Phi_0}\).
-	\item those that have \(i+1\) as an impurity site and \(i\) as the corresponding bath site. There are again \(w-2\) of these:
-	\begin{equation}
-		(w-2) \times \frac{2}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{0_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0} = \frac{2}{w}\left(z^p_{1,n}\right)^* d^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
-	\end{equation}
-\end{itemize}
-These choices are shown in fig.~\ref{off-diag-contrib}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/offdiagonal_contributors.pdf}
-	\caption{Auxiliary models that contribute to the off-diagonal matrix element. \(j \equiv i+1\)}
-	\label{off-diag-contrib}
-\end{figure}
-
-Adding all contributions gives
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}
-\end{aligned}\end{equation}
-The hole counterpart is
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}
-\end{aligned}\end{equation}
-where \(z^h_{i,n} = \bra{\Phi_n}c_{z_i\sigma}\ket{\Phi_0}\).
-
-The off-diagonal matrix element between next-to-nearest-neighbour sites \(i,i+2\) can also be obtained, provided their positions are related as \(\vec r_{i+2} = \vec r_i + \vec a + \vec a^\prime\), where \(\vec a\) and \(\vec a^\prime\) are primitive vectors that connect any lattice site to its nearest-neighbours, and \(\vec{a}\cdot\vec{a}^\prime = 0\).
-This is shown in fig.~\ref{next-near}.
-
-\par\noindent
-\begin{minipage}{0.6\textwidth}
-The essence is that the two sites have to form the two most separated vertices of a right-angled triangle.
-To find the auxiliary models that contribute to this matrix element, note that there is only one square that can be formed keeping both \(i\) and \(i+2\) on it - we call this square \(ABCD\), where \(A\) is the vertex \(i\) and \(C\) is the vertex \(i+2\).
-We can set \(A=d_1, C=0_2\).
-The other two vertices \(B\) and \(D\) can have two possible configurations:\(B=d_2,D=0_1\) and \(B=0_1,D=d_2\).
-Two more configurations can be obtained by taking each of these two configurations and keeping \(B,D\) unchanged but exchanging \(A\) and \(C\).
-These four configurations are shown in fig.~\ref{nn-configs}.
-\end{minipage}
-\hspace*{\fill}
-\begin{minipage}{0.35\textwidth}
-	\centering
-	\includegraphics[width=0.9\textwidth]{../figures/next-near.pdf}
-	\captionof{figure}{The kind of next-nearest neighbour sites that can be connected by the auxiliary model.}
-	\label{next-near}
-\end{minipage}
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/nn-offdiagonal_contributors.pdf}
-	\caption{Auxiliary model configurations that contribute to the next-nearest neighbour matrix elements. \(j \equiv i+2\)}
-	\label{nn-configs}
-\end{figure}
-
-These four configurations give
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} &= \frac{2}{w(w-2)}\left[\braket{\Phi_0|c_{d_1\sigma}\mathcal{G}^{-1}_\text{aux}(d_1,d_2)c^\dagger_{0_2,\sigma}|\Phi_0} + \braket{\Phi_0|c_{0_2\sigma}\mathcal{G}^{-1}_\text{aux}(d_1,d_2)c^\dagger_{d_1,\sigma}|\Phi_0}\right] \\
-										 &= \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}
-\end{aligned}\end{equation}
-
-In summary, the spectral representation of the matrix elements of the inverse Greens operators are given by
-\begin{gather}
-\label{green_eq_final_2siam}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}~,\\
-	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}~,\\
-	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}_\text{H-H}^{-1}\left( -\omega \right) \right)^h_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^h_{1,n}\right)^* z^h_{2,n} + \left(z^h_{2,n}\right)^* d^h_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~.
-\end{gather}
-
-In order to obtain the matrix elements of the Greens operators \(\mathcal{G}_{H-H}\) (as compared to its inverse), we note that we have just observed that the matrix elements of the inverse Greens operators are related to the matrix elements of another inverse operator through some coefficients.
-We can, therefore, use the identity
-\begin{equation}\begin{aligned}
-\left(\hat O\right)_{ij} = \bra{i} \hat O \ket{j} = \sum_{m,n} \braket{i|m} \left(\hat O\right)_{mn} \braket{n|j} \implies \left(\hat O^{-1}\right)_{ij} = \sum_{m,n} \braket{i|m} \left(\hat O^{-1}\right)_{mn} \braket{n|j}
-\end{aligned}\end{equation}
-We can now identify \(\left(\hat O^{-1}\right)_{mn}\) as the matrix elements of \(\mathcal{G}_\text{aux}^{-1}\) in our expressions.
-Using the above relation, we can therefore write the spectral representation of the matrix elements of the Greens operators as
-\begin{gather}
-	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w}\sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn}~,\\
-	\left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w}\sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}~,\\
-	\left(\mathcal{G}_\text{H-H}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}_\text{H-H}\left( -\omega \right) \right)^h_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^h_{1,n}\right)^* z^h_{2,n} + \left(z^h_{2,n}\right)^* d^h_{1,n}\right] \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~.
-\end{gather}
-
-The Lehmann-Kallen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements.
-Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
-\begin{equation}\begin{aligned}
-	&\left(G_{H-H}(\omega)\right)_\text{loc} = \left(\mathcal{G}_{H-H}(\omega)\right)_{ii}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn} - |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\right] = G_\text{aux}(d_1,d_1;\omega)\\
-	&\left(G_{H-H}(\omega)\right)_\text{n-n} = \left(\mathcal{G}_{H-H}(\omega)\right)_{i,i+1}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{i+1,i}^h\\
-						&\frac{2}{w}\sum_n \left\{\left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn} - \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}\right\}\\
-						&= \frac{2}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right]\\
-						&\left(G_\text{H-H}\right)_\text{n-n-n} = \frac{2}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right] 
-\end{aligned}\end{equation}
-
-\section{Spectral functions and self-energies}
-
-The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
-\end{aligned}\end{equation}
-where $\vec{r_i}$ is the position vector of a particular lattice site.
-Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites.
-As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
-As we do not have real space Greens function that are more non-local than next-nearest neighbour, we will attempt to obtain momentum space Greens function from these contributions:
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
-\end{aligned}\end{equation}
-The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, w\right]\right\}$.
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} + G_{H-H} (\omega)_\text{n-n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {b_i}}= G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k} + G_{H-H} (\omega)_\text{n-n-n} \xi^\prime_{\vec k}
-\end{aligned}\end{equation}
-where we defined \(\left\{b_i\right\} \) as the set of vectors that connect a particular lattice site with its next-nearest-neighbours,\(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\) and \(\xi^\prime_{\vec k} \equiv \sum_{j} e^{i \vec{k}\cdot\vec {b_j}}\).
-Note that \(b_j\) is simply \(a_i + a{i^\prime}\) where \(a_i\) and \(a_{i^\prime}\) are orthogonal.
-On a d-dimensional hypercubic lattice, we obtain
-\begin{gather}
-	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i\\
-\end{gather}
-On a 2D square lattice with lattice spacing $a$, this simplifies to (same as eq.~\ref{2dsquaretb})
-\begin{eqnarray}
-\xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
-\end{eqnarray}
-where \(\epsilon_{\vec{q}} = -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})\) is the tight-binding dispersion.
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) = G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] \\
-	 + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]
-\end{aligned}\end{equation}
-
-We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
-\begin{equation}\begin{aligned}
-	A_\text{H-H}(\vec{k},\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega)) =A_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[A_\text{aux}(d_1,d_2;\omega) + A_\text{aux}(d_1,0_1;\omega) + A_\text{aux}(0_1,d_1;\omega)\right]\\
-	 + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[A_\text{aux}(d_1,0_2;\omega) + A_\text{aux}(0_2,d_1;\omega)\right]
-\end{aligned}\end{equation}
-where the spectral function $A_\text{aux}=-\frac{1}{\pi}\textrm{Im}G_\text{aux}$.
-
-With the knowledge of the momentum-space Greens function $G_\text{H-H}(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
-\begin{equation}\begin{aligned}
-	\Sigma(\vec k,\omega) = \left(G^{(0)}(\vec k,\omega)\right)^{-1} - G(\vec k,\omega)^{-1}
-\end{aligned}\end{equation}
-where $\left(G^{(0)}(\vec k,\omega)\right)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system.
-Substituting this as well as the full Greens function $G_{H-H}(\vec k, \omega)$ into Dyson's equation gives
-\begin{equation}\begin{aligned}
-	\label{self-energy}
-	&\Sigma_{H-H}(\vec k,\omega) = \left(G^{(0)}(\vec k,\omega)\right)^{-1} -\\
-	&\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}
-\end{aligned}\end{equation}
-This allows us to calculate the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
-
-\section{Analytic consistency check - On the Bethe lattice}
-Another test involves considering the case of a Bethe lattice with infinite number of nearest neighbours $w\to\infty$ (the coordination number).
-In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
-This allows a metal-insulator transition in the limit of $w\to\infty$ as well.
-In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}.
-This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy}.
-Applying the limit of \(w\to \infty\) on that equation gives
-\begin{equation}\begin{aligned}
-	&\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left[G^{(0)}(\vec k,\omega)\right]^{-1} -\right.\\
-	&\left.\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}\right\}\\
-	& = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux}(d_1,d_1;\omega)\right\}^{-1} 
-\end{aligned}\end{equation}
-where \(G_\text{aux}^{(0)}(\vec k,\omega)\) is the non-interacting Greens function.
-It is clear from the final form that only the diagonal term \(G_\text{aux}(d_1,d_1;\omega)\) of the interacting Greens function affects the self-energy.
-Even the non-interacting part Greens function can be shown to be diagonal in the limit of \(w\to\infty\)~\cite{kuramoto_manybody}.
-From its definition in time domain, we have
-\begin{equation}\begin{aligned}
-	G^{(0)}(\vec k, t) = -i\theta(t) \left<\left\{c_{\vec k}(t), c^\dagger_{\vec k}\right\} \right> = -i\theta(t) \left<\left\{e^{i H^{(0)}t} c_{\vec k} e^{-i H^{(0)}t}, c^\dagger_{\vec k}\right\} \right> = -i\theta(t) e^{-i \epsilon_{\vec k}t}\left[ \left<1 - \hat n_{\vec k}\right> + \left<\hat n_{\vec k}\right>\right] = -i \theta(t) e^{-i \epsilon_{\vec k}t}
-\end{aligned}\end{equation}
-A quick Fourier transform to \(\omega-\)domain shows that this is identical to the \(G^{(0)}(\vec k, \omega)\) defined just above eq.~\ref{self-energy}.
-We note that \(|G^{(0)}(\vec k, t)| \leq 1\).
-Using the Fourier transform  definition
-\begin{equation}\begin{aligned}
-	f(\vec k) = \frac{1}{d_N}\sum_{\vec r_i}h(\vec r_i) e^{i \vec{k}\cdot\vec{r}_i}
-\end{aligned}\end{equation}
-where \(d_N\) is a factor that only depends on the total number of sites and not on the coordination number, we can write
-\begin{equation}\begin{aligned}
-	|G^{(0)}(\vec k, t)|^2 = \frac{1}{d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}
-\end{aligned}\end{equation}
-From the inequality \(|G^{(0)}(\vec k, t)| \leq 1\), we get
-\begin{equation}\begin{aligned}
-	1 \geq \frac{1}{N}\sum_k |G^{(0)}(\vec k, t)|^2 = \frac{1}{N d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* \underbrace{\sum_k e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}}_{N \delta_{\vec r_i = \vec r_j}} = \frac{1}{d_N^2}\sum_{\vec r_i} |G^{(0)}(\vec r_i, t)|^2
-\end{aligned}\end{equation}
-For a coordination number of \(w\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
-Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{w}\).
-In contrast, there is only one local Greens function, that for \(\vec r_i=0\).
-The local Greens function therefore scales independent of \(w\).
-This implies that
-\begin{equation}\begin{aligned}
-	\lim_{w\to \infty}G^{(0)}(\vec k,\omega) = G^{(0)}(\vec r=0,\omega)
-\end{aligned}\end{equation}
-Since both the non-interacting and the interaction Greens functions lose their non-locality, the self-energy becomes completely local in the limit of \(w \to \infty\).
-
-\chapter{The Periodic Anderson and Kondo models}
-The heavy Fermion systems are described by periodic versions of the single impurity models, where instead a lattice of impurities \(\left\{ d_i \right\} \) hybridises with a conduction bath lattice \(\left\{ i \right\} \).
-The periodic Anderson model is defined by the Hamiltonian
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right)  - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-
-As before, we will work with a generalised form of it where we also consider a spin-exchange interaction between the impurity sites and the bath sites:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right) + J \sum_i \vec{S}_{d_i}\cdot\vec{s}_i - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-One can also introduce an RKKY interaction \(J_\text{RKKY}\) between the nearest neighbour impurity spins:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right) + J \sum_i \vec{S}_{d_i}\cdot\vec{s}_i - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma} \\
-	+ J^\prime\sum_{\left<d_i,d_j \right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
-\end{aligned}\end{equation}
-
-\section{Creating a bulk periodic Anderson model by tiling with generalised single-impurity Anderson models: no RKKY}
-
-The auxiliary model we will be using is a generalised SIAM with attractive interaction on the bath zeroth site and explicit particle-hole asymetry on the impurity:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux} = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s}_0 + \eta \sum_\sigma\tau_{d\sigma}
-\end{aligned}\end{equation}
-where \(\tau = \hat n - 1/2\).
-
-We will use this as the auxiliary model to study the Hubbard model.
-We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
-Note that the impurity level and the conduction bath can be tuned to half-filling by setting \(\eta=0\) and \(\mu=0\) respectively.
-To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(d_i\) of the impurity lattice, and the bath sites will constitute the bulk lattice sites.
-We will also identity the zeroth site of the SIAM lattice as one particular site \(i\) of the conduction bath lattice:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(d_i) = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) +J \vec{S}_{d_i}\cdot\vec{s}_i + \eta \sum_\sigma\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-Once we have this local Hamiltonian for a particular site, we translate this over all \(N\) sites \(\left\{\left(d_i,i\right) \right\} \):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} = \sum_{i} \mathcal{H}_\text{aux}(d_i) = N\sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) +J \sum_i\vec{S}_{d_i}\cdot\vec{s}_i \\
-	+ \eta \sum_{i,\sigma}\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-
-We end up with a generalised periodic Anderson model:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{GPAM} = \sum_{k\sigma}\left(\left(\epsilon_k\right)_\text{GPAM} - \mu_\text{GPAM}\right)\tau_{k\sigma} - \frac{U_\text{GPAM}}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V_\text{GPAM} \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right)\\
-	+ J_\text{GPAM} \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + \eta_\text{GPAM} \sum_{i,\sigma}\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-The mapping between the parameters of the auxiliary model and that of the bulk are
-\begin{equation}\begin{aligned}
-	\label{map_pam_bulk}
-	\left(\epsilon_k\right)_\text{GPAM} = N\epsilon_k, ~ ~ \mu_\text{GPAM} = N\mu, ~ ~ U_\text{GPAM} = U, ~ ~ V_\text{GPAM} = V, ~ ~ J_\text{GPAM} = J, ~ ~ \eta_\text{GPAM} = \eta
-\end{aligned}\end{equation}
-
-\section{Creating a bulk periodic Anderson model by tiling with two-impurity Anderson models: with RKKY}
-
-This time we will use a two-impurity model with a spin-exchange coupling between the impurities as the auxiliary model:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux} = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\sum_{i=1,2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right)^2 + \sum_{i=1,2}\left[V \sum_{\sigma} \left(c^\dagger_{0_i\sigma} c_{d_i\sigma} + h.c.\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i}\right] + \eta \sum_\sigma\tau_{d\sigma}\\
- + J^\prime\vec{S}_{d_1}\cdot\vec{S}_{d_2}
-\end{aligned}\end{equation}
-where \(\tau = \hat n - 1/2\).
-
-We will use this as the auxiliary model to study the Hubbard model.
-We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
-Note that the impurity level and the conduction bath can be tuned to half-filling by setting \(\eta=0\) and \(\mu=0\) respectively.
-To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity sites \(d_1 \) and \(d_2\) as particular nearest-neighbour sites \(d_i, d_{j}\) of the impurity lattice, and the bath sites will constitute the bulk lattice sites.
-We will also identity the bath sites \(0_1,0_2\) as two particular nearest-neighbour sites \(i,j\) of the conduction bath lattice:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(d_i, d_{j}) = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left[\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + \left(\hat n_{d_{j} \uparrow} - \hat n_{d_{j} \downarrow} \right) ^2\right] + V \sum_{\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + c^\dagger_{j,\sigma} c_{d_{j},\sigma} + h.c.\right)\\
- + J \left(\vec{S}_{d_i}\cdot\vec{s}_i + \vec{S}_{d_{j}}\cdot\vec{s}_{j}\right) + \eta \sum_\sigma\left(\tau_{d_i\sigma} + \tau_{d_{j}\sigma}\right)+ J^\prime\vec{S}_{d_i}\cdot\vec{S}_{d_j}\\
-\end{aligned}\end{equation}
-Once we have this local Hamiltonian for a particular site, we translate this over all nearest-neighbour pairs \((i,j)\) of the lattice.
-There are \(Nw/2\) of these.
-To ensure the bulk model scales as \(N\), we divide this sum by \(w/2\).
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} = \frac{2}{w}\sum_{\left<i,j\right>} \mathcal{H}_\text{aux}(d_i) = N\sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - 2\frac{U}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + 2V \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) \\
-	 + 2J \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + 2\eta \sum_{i,\sigma}\tau_{d_i\sigma} + \frac{2}{w}J^\prime\sum_{\left<i,j\right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
-\end{aligned}\end{equation}
-
-We end up with a generalised periodic Anderson model with RKKY interaction:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{GPAM} = \sum_{k\sigma}\left(\left(\epsilon_k\right)_\text{GPAM} - \mu_\text{GPAM}\right)\tau_{k\sigma} - \frac{U_\text{GPAM}}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V_\text{GPAM} \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right)\\
-	+ J_\text{GPAM} \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + \eta_\text{GPAM} \sum_{i,\sigma}\tau_{d_i\sigma} + J^\prime_\text{GPAM}\sum_{\left<i,j\right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
-\end{aligned}\end{equation}
-The mapping between the parameters of the auxiliary model and that of the bulk are
-\begin{equation}\begin{aligned}
-	\left(\epsilon_k\right)_\text{GPAM} = N\epsilon_k, ~ ~ \mu_\text{GPAM} = N\mu, ~ ~ U_\text{GPAM} = 2U, ~ ~ V_\text{GPAM} = 2V, ~ ~ J_\text{GPAM} = 2J, ~ ~ \eta_\text{GPAM} = 2\eta, ~ ~ J^\prime_\text{GPAM} = \frac{2}{w}J^\prime
-\end{aligned}\end{equation}
-
-\chapter{Future goals}
-\begin{enumerate}
-\item The Mott metal-insulator transition:
-	\begin{todolist}
-	\item[\cmark] Obtain the metal insulator transition of the 2D Hubbard-Heisenberg model on the square lattice from the present formalism. 
-	\item Determine the nature of the bath $\Sigma (k,\omega)$ in the metallic phase, insulating phase as well as at criticality.
-	\item Investigate nature of the zero-temperature transition (order of transition, order parameter, etc)
-	\end{todolist}
-
-\item Higher-order Greens functions:
-	\begin{todolist}
-	\item Provide expressions for two-particle Greens functions.
-	\item Calculate explicitly the Greens functions for holon-doublon and spinon-spinon excitations as they are likely to contain more information regarding the ground state.
-	\item Obtain spectral functions for such excitations
-	\end{todolist}
-
-\item Benchmarking against ED and/or finite size scaling:
-	\begin{todolist}
-	\item ground state energy
-	\item double occupancy
-	\end{todolist}
-
-\item Upgrade to two-site cluster:
-	\begin{todolist}
-	\item Study a two-impurity model under renormalisation group
-	\item[\cmark] Derive the tiling and Greens function relations for such a two-impurity model 
-	\item Demonstrate Mott MIT here.
-	\item Investigate the nature of many-particle entanglement in such a cluster
-	\item look for signs of a quantum liquid.
-	\end{todolist}
-
-\item Once we have a handle on the zero temperature features, we intend to compute Greens functions at non zero temperatures.
-
-\item This method can also be extended to various other models of strong correlation:
-	\begin{enumerate}
-		\item Heisenberg model, by starting from a Kondo model effective Hamiltonian
-		\item Periodic Anderson model, by starting from a SIAM with a dispersive bath
-		\item Periodic Kondo model, by starting from a Kondo model with a dispersive bath
-	\end{enumerate}
-\end{enumerate}
-
-\begin{appendices}
-
-\appendixtitleon
-
-\chapter{Derivation of RG equations for the impurity model with \(U,V,J,K,U_b,\eta\)}
-
-\section{The Hamiltonian}
-
-The Hamiltonian for the impurity problem is
-\begin{equation}\begin{aligned}
-	\mathcal{H} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{1}{2} U \left( \tau_{d \uparrow} - \tau_{d \downarrow} \right) ^2 + \frac{1}{2}\eta \left(\tau_{d \uparrow} + \tau_{d \downarrow}\right) + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} + K \vec{C}_d\cdot\vec{C} - U_b\left(\tau_{0 \uparrow} - \tau_{0 \downarrow}\right)^2
-\end{aligned}\end{equation}
-wher \(\tau \equiv \hat n -\frac{1}{2}\).
-The first term is the kinetic energy term with a dispersion \(\epsilon_k\).
-The second term is the particle-hole symmetric impurity correlation term that sets the uncorrelated half-filled level \(\tau_{d\uparrow} = - \tau_{d \downarrow} = \pm \frac{1}{2}\) at energy \(-U/2\) below the Fermi surface, and the correlated doublon and holon states \(\tau_{d\downarrow} = \tau_{d \uparrow} = \pm \frac{1}{2}\) at the Fermi surface.
-The particle-hole symmetry is in the fact that the term is invariant under \(\tau_{d\sigma} \to-\tau_{d\sigma}\), and manifests in the symmetric positioning of the doublon and holon levels with respect to each other.
-The third term is the particle-hole asymmetry term that explicitly measures the deviation away from particle-hole symmetry - it is non-zero only when we are away from half-filling.
-The fourth, fifth and sixth terms describe various mechanisms in which the impurity can hybridise with the conduction bath.
-The first of these is a single-particle hopping \(V\), the second mechanism is through spin-flip scattering, and the third is through isospin-flip scattering.
-The single-particle hybridisation \(V\) allows the impurity electron to tunnel into the conduction bath and this leads to a frequency-dependent self-energy renormalisation of the impurity, implying that the impurity electron can spend  large amount of time in the bath~\cite{coleman2015}.
-\(\vec S_d = \frac{1}{2}\sum_{\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{d\alpha}c_{d\beta} \) is the impurity spin, while \(\vec C_d = \frac{1}{2}\sum_{\alpha\beta} \psi^\dagger_\alpha \vec \sigma_{\alpha\beta}\psi_\beta\) is the impurity isospin, where \(\psi = \left(c_{d\uparrow} ~ ~ ~ ~ c^\dagger_{d \downarrow}\right)\)~
-\cite{anderson1958random,nambu_1960}.
-The former acts on the \(2-\)dimensional Hilbert-space formed by the magnetic up and down states on the impurity, while the latter acts on the \(2-\)dimensional space formed by the doublon and holon states.
-The former reacts to a magnetic field, while the latter responds to a chemical potential.
-Such a chemical potential term that couples with the isospin is already present in the Hamiltonian - it is the assymetry term \(\eta\).
-In fact, that term can be rewritten as \(\eta C_d^z\), because \(C^z_d = \frac{1}{2}\left(\hat n_{d \uparrow} + \hat n_{d \downarrow} - 1\right) = \frac{1}{2}\left( \tau_{d \uparrow} + \tau_{d \downarrow} \right) \).
-The bath operators \(\vec s\) and \(\vec C\) are defined in the same way as the operator counterparts: \(\vec s = \sum_{kk^\prime\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{k\alpha}c_{k^\prime\beta}, \vec C = \sum_{kk^\prime\alpha\beta}{\psi^k}^\dagger_\alpha\vec\sigma_{\alpha\beta}\psi^{k^\prime}_\beta\), where \(\psi^k = \left(c_{k\alpha} ~ ~ ~ ~ c^\dagger_{k^\prime\beta}\right) \).
-The final seventh term is a local particle-hole symmetric correlation on the zeroth site of the bath.
-For \(U_b>0\), this term promotes half-filling on the zeroth site, while for \(U_b<0\), a doublon or holon is more favourable on that site.
-
-We first Fourier transform the \(U_b\)-term to \(k-\)space.
-In \(k-\)space, the diagonal contribution (to \(H_D\)) coming from this term is the single-particle self-energy \(-U_b\left(\hat n_{q \beta}\right)^2\) which can be made particle-hole symmetric in the form:
-\begin{equation}\begin{aligned}
-	-U_b\left(\tau_{q \beta}\right)^2
-\end{aligned}\end{equation}
-where \(q\) is the \(k-\)state being decoupled and \(\tau \equiv \hat n - 1/2\).
-In the initial state \(\ket{\Psi}_i\), we have \(\langle \hat n_{q\beta} \rangle = 1/2 \implies \tau_{q\beta} = 0\), so the contribution of \(U_b\) to that state is 0.
-For both hole excitations \(c_{q\beta}\ket{\Psi}_i\) as well as particle excitations \(c^\dagger_{q\beta}\ket{\Psi}_i\), the intermediate state energy lowers to \(-U_b/4\).
-
-The off-diagonal part is
-\begin{equation}\begin{aligned}
-	-\frac{U_b}{2}\sum_{kk^\prime\sigma}c^\dagger_{k\sigma}c_{k^\prime\sigma} + U_b \sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_1 \uparrow}c_{k_2 \uparrow} c^\dagger_{k^\prime_1 \downarrow}c_{k^\prime_2 \downarrow}
-\end{aligned}\end{equation}
-We ignore the potential scattering arising from the first term.
-
-\section{Renormalisation of the impurity energy levels}
-A single site has four degrees of freedom arising from the spin-degeneracy, and can be represented by the Hamiltonian
-\begin{equation}\begin{aligned}
-	H = \epsilon_0 \ket{0}\bra{0} + \epsilon_1 \sum_\sigma\ket{\sigma}\bra{\sigma} + \epsilon_2 \ket{2}\bra{2}
-\end{aligned}\end{equation}
-\(\ket{0},\ket{2}\) are the holon and doublon states, while \(\ket{\sigma}\) is the state where the site is singly-occupied by a particle of spin \(\sigma\).
-We will obtain the renormalisation to the energy levels \(\epsilon_0,\epsilon_1\) and \(\epsilon_2\), and thereby calculate the renormalisation in \(U\) and \(\eta\).
-This can be done by noting that \(\epsilon_1 = -\frac{U}{2}\), and \(\epsilon_2 = \eta\).
-A qualifier is, however, needed here.
-In the bare Hamiltonian, the energies of the doublon and holon states are negatives of each other, and this would correspond to requiring \(\epsilon_2 = -\epsilon_0\).
-This may not hold true under renormalisation, and the way we account for this is that at each step of the RG, we subtract a constant energy from the Hamiltonian so as to set the energy of the holon state to 0.
-This means that the energy of the singly-occupied and doublon states become \(\epsilon_1 - \epsilon_0\) and \(\epsilon_2 - \epsilon_0\).
-And since we have identified \(\epsilon_1\) and \(\epsilon_2\) as \(-\frac{U}{2}\) and \(\eta\) respectively, we can use \(\Delta U = -2\left(\Delta \epsilon_1 - \Delta \epsilon_0\right), \Delta \eta = \Delta \epsilon_2 - \Delta \epsilon_0 \).
-
-We need to look at three kinds of scattering vertices here: \(V^2\), \(J^2\) and \(K^2\).
+\acknowledgments
+Abhirup Mukherjee thanks IISER Kolkata for funding through a research fellowship.
+S.
+Lal thanks the SERB, Govt.
+of India for funding through MATRICS grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
+
+\appendix*
+
+\begin{widetext}
+\section{Derivation of RG equations for the generalised Anderson impurity model}
+
+\subsection{Renormalisation of the impurity energy \(\epsilon_d\)}
+The coupling \(\epsilon_d\) is renormalised by three kinds of vertices: \(V^2\), \(J^2\) and \(K^2\).
 We will consider these processes one after another.
@@
 
-We will follow the same strategy with \(K\) - we will calculate the renormalisation in \(K^+\). The first term is
-\begin{equation}\begin{aligned}
-	\frac{1}{2} K U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \downarrow} c^\dagger_{q \uparrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D} C_d^+ c_{k \downarrow} c_{q \uparrow} = -\frac{1}{2}\frac{K U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}} \sum_{k,k^\prime} C_d^+ c_{k \downarrow} c_{k^\prime \uparrow}
-\end{aligned}\end{equation}
-The second term in the same sector is obtained by flipping the spins of \(k\) and \(q\):
-\begin{equation}\begin{aligned}
-	\frac{1}{2} K U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \uparrow} c^\dagger_{q \downarrow}c_{k^\prime \downarrow} \frac{1}{\omega - H_D} C_d^+ c_{q \downarrow} c_{k \uparrow} = -\frac{1}{2}\frac{K U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}} \sum_{k,k^\prime} C_d^+ c_{k \downarrow} c_{k^\prime \uparrow}
-\end{aligned}\end{equation}
-
-The terms in the hole sector give identical contributions. The RG equation for \(K\) is
-\begin{equation}\begin{aligned}
-	\Delta K = -K n_j\frac{4 U_b + K}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}}
-\end{aligned}\end{equation}
-
-\chapter{Zero temperature Greens function in frequency domain}
-
-\label{appx-spectral-func}
-The impurity retarded Green's function (assuming the Hamiltonian to be time-independent, which it is) is defined as
-\begin{equation}\begin{aligned}
-	G_{dd}^\sigma(t) = -i\theta(t) \left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right>
-\end{aligned}\end{equation}
-where the average \(\left< \right>\) is over a canonical ensemble at temperature \(T\), and \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in.
-The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term.
-What follows is a standard calculation where we write the Green's function in the Lehmann-Kallen representation.
-The ensemble average for an arbitrary operator \(\hat M\) can be written in terms of the exact eigenstates of the fixed point Hamiltonian:
-\begin{equation}\begin{aligned}
-	H^* \ket{n} &= E_n^* \ket{n}, ~ ~ ~\left<\hat M \right> &\equiv \frac{1}{Z}\sum_n \bra{n} \hat M \ket{n} e^{-\beta E_n^*}
-\end{aligned}\end{equation}
-where \(Z = \sum_n e^{-\beta E_n^*}\) is the fixed point partition function and \(\left\{ \ket{n} \right\} \) is the set of eigenfunctions of the fixed point Hamiltonian. We can therefore write
-\begin{equation}\begin{aligned}
-	&\left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right> \\
-	&= \frac{1}{Z}\sum_{m}e^{-\beta E_m}\bra{m}\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\} \ket{m}\\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( \mathcal{O}_{\sigma}(t)\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma}(t)\right) \ket{m} && \left[\sum_n \ket{n}\bra{n} = 1\right]  \\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\right) \ket{m}\\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\left( e^{i\left( E_m - E_n \right)  t}\bra{m}\mathcal{O}_{\sigma}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} \ket{m} + e^{i\left( E_n - E_m \right)  t}\bra{m}\mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma} \ket{m}\right)\\
-	&= \frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
-\end{aligned}\end{equation}
-The time-domain impurity Green's function can thus be written as (this is the so-called Lehmann-Kallen representation)
-\begin{equation}\begin{aligned}
-	G_{dd}^\sigma = -i\theta(t)\frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
-\end{aligned}\end{equation}
-We are interested in the frequency domain form.
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega) &= \int_{-\infty}^\infty dt e^{i \omega t}G_{d d}^\sigma(t) \\
-			       &= \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t}
-\end{aligned}\end{equation}
-To evaluate the time-integral, we will use the integral representation of the Heaviside function:
-\begin{equation}\begin{aligned}
-	\theta(t) = \frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty \frac{1}{x- i\eta}e^{ixt}dx
-\end{aligned}\end{equation}
-With this definition, the integral in \(G_{dd}^\sigma(\omega)\) becomes
-\begin{equation}\begin{aligned}
-	\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t} &= \left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta}\int_{-\infty}^\infty dt e^{i\left( \omega + E_m - E_n + x\right)t} \\
-									     &=\left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta} 2\pi \delta\left( \omega + E_m - E_n + x\right) \\
-									     &=\left(-i\right)\frac{1}{i}\lim_{\eta \to 0^+} \frac{-1}{\omega + E_m - E_n- i\eta} \\
-									     &=\frac{1}{\omega + E_m - E_n} \\
-\end{aligned}\end{equation}
-The frequency-domain Green's function is thus
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
-\end{aligned}\end{equation}
-The zero temperature Green's function is obtained by taking the limit of \(\beta \to \infty\).
-In both the partition function as well as inside the summation, the only term that will survive is the exponential of the ground state energy \(E_0\).
-\begin{equation*}\begin{aligned}
-	Z \equiv \sum_m e^{-\beta E_m} \implies \lim_{\beta \to \infty}Z = d_0 e^{-\beta E_0}, && E_0 \equiv \text{min}\left\{ E_n \right\} 
-\end{aligned}\end{equation*}
-where \(d_0\) is the degeneracy of the ground state. The Greens function then simplifies to
-\begin{equation}\begin{aligned}
-	\label{Gf_lk}
-	G_{d d}^\sigma(\omega, \beta \to \infty) &= \frac{1}{d_0e^{-\beta E_0}}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left[e^{-\beta E_m}\delta_{E_m, E_0} + e^{-\beta E_n}\delta_{E_n, E_0}\right]\frac{1}{\omega + E_m - E_n}\\
-						 &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n}\right]\\
-\end{aligned}\end{equation}
-The label 0 sums over all states \(\ket{0}\) with energy \(E_0\).
-The spectral function is the imaginary part of this Green's function.
-To extract the imaginary part, we insert an infinitesimal imaginary part in the denominator:
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega, \eta) = \frac{1}{d_0}\lim_{\eta \to 0^-}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n + i\eta} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n + i\eta}\right]\\
-\end{aligned}\end{equation}
-The spectral function at zero temperature can then be written as
-\begin{equation}\begin{aligned}
-	\mathcal{A(\omega)} &= -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] \\
-			    &= \frac{1}{d_0}\frac{1}{\pi}\text{ Im }\left[\lim_{\eta \to 0^-}\sum_{n,0}\left(\frac{-i\eta ||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2}{\left(\omega + E_0 - E_n\right)^2 + \eta^2} + \frac{-i\eta ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2}{\left(\omega - E_0 + E_n\right)^2 + \eta^2}\right)\right]\\
-			    &= \frac{1}{d_0}\frac{1}{\pi}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\pi\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\pi\delta\left(\omega - E_0 + E_n\right)\right]\\
-			    &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]\\
-\end{aligned}\end{equation}
-
-\chapter{Some analytic results for the Hubbard dimer and the Hubbard model}
-\section{Spectrum of the Hubbard dimer}
-Here we document the spectrum of the Hubbard dimer Hamiltonian in eqs.~\ref{hubb_dimer}.
-\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-	eigenstate & symbol & eigenvalue \\
-	\hline
-	$\ket{0,0}$ & $\ket{0}$ & \( \frac{U^H}{2}\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,0} \pm \ket{0,\sigma}\right)$ & $\ket{0\sigma_\pm}$ & \(\mp t^H\)\\
-	$\ket{\sigma,\sigma}$ & $\ket{\sigma\sigma}$ & \( -\frac{U^H}{2}\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow}\right)$ & $\ket{ST}$ & \( -\frac{U^H}{2}\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2}\right)$ & $\ket{CS}$ & \( \frac{U^H}{2}\)\\
-	$a_1(U^H, t^H) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_2(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{-}$ & \(-\frac{1}{2}\Delta(U^H, t^H)\)\\
-	$-a_2(U^H, t^H) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{+}$ & \(\frac{1}{2}\Delta(U^H, t^H)\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,2} \pm \ket{2,\sigma}\right)$ & $\ket{2\sigma_\pm}$ & \(\pm t^H\)\\
-	$\ket{2,2}$ & $\ket{4}$ & \( \frac{U^H}{2}\)\\
-\hline
-	\end{tabular}
-	\captionof{table}{Spectrum of Hubbard dimer at half-filling}
-	\label{hubb_dim_spectrum}
-\end{center}
-
-\section{Greens function of Hubbard model in the atomic limit}
-\label{atomic limit}
-The atomic limit is described by the Hamiltonian \(H = -\frac{U}{2}\sum_i\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\).
-Since the Hamiltonian has decoupled into \(\sum_i \equiv N\) single-site Hamiltonians, we can easily write down the retarded Greens function for a single site by identifying the ground state configuration of a site.
-The ground states are of course \(\ket{\Psi}_i = \ket{\uparrow},\ket{\downarrow}\), in the absence of any symmetry-breaking.
-The finite temperature retarded Greens function in the time domain is given by
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(T,t) = -i\theta(t) \frac{1}{Z}\sum_n e^{-\beta E_n} \braket{n | \left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} | n}
-\end{aligned}\end{equation}
-where \(n\) labels the eigenstates of the \(H\). At \(T \to 0\), only the ground states will survive in the exponential and the partition function \(Z\), such that the formula then reduces to
-\begin{equation}\begin{aligned}
-G_{i,\sigma}(T \to 0,t) = -i\theta(t)\braket{GS | \left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} | GS}
-\end{aligned}\end{equation}
-Since the Hamiltonian is simple, we can compute the time-dependent operator \(c_{i\sigma}(t) = e^{iH t} c_{i\sigma} e^{-iHt}\). Using the BCH lemma, we have
-\begin{equation}\begin{aligned}
-	e^{iH t} c_{i\sigma} e^{-iHt} = \sum_{n=0}^\infty \left(it\right)^n \frac{1}{n!}\left[H,c_{i\sigma}\right]_n
-\end{aligned}\end{equation}
-where \(\left[H,c_{i\sigma}\right]_n = \left[H,\left[H,c_{i\sigma}\right]_{n-1}\right],\left[H,c_{i\sigma}\right]_0=c_{i\sigma}\). The first two non-trivial commutators are
-\begin{equation}\begin{aligned}
-	\left[H, c_{i\sigma}\right]_1 = -U \tau_{i\overline\sigma}c_{i\sigma},~ ~\text{and} ~~\left[H, c_{i\sigma}\right]_2 = \frac{1}{4}U^2 c_{i\sigma}~,
-\end{aligned}\end{equation}
-such that
-\begin{equation}\begin{aligned}
-	e^{iH t} c_{i\sigma} e^{-iHt} =& \left[c_{i\sigma} + \frac{i^2 t^2}{2!}\frac{U^2}{2^2} c_{i\sigma} + \frac{i^4 t^4}{4!}\frac{U^4}{2^4} c_{i\sigma} + \ldots\right] + \left[- \frac{it}{1!}U\tau_{i\overline\sigma}c_{i\sigma} - \frac{i^3 t^3}{3!}\frac{U^3}{4}\tau_{i\overline\sigma}c_{i\sigma} + \ldots \right]\\
-				       &= c_{i\sigma} \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] 
-\end{aligned}\end{equation}
-Using this, we can write
-\begin{equation}\begin{aligned}
-	\left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} = \left\{c_{i\sigma},c^\dagger_{i\sigma}\right\} \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] = \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right]
-\end{aligned}\end{equation}
-and the Greens function becomes
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(T \to 0,t) = -i\theta(t) \braket{GS | \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] | GS} = -i\theta(t)\left[\cos \frac{Ut}{2} - 2i\sin \frac{Ut}{2} \left<\tau_{i\overline\sigma} \right>\right]
-\end{aligned}\end{equation}
-We now Fourier transform to frequency domain:
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(\omega) = -i\int_{0}^\infty \mathrm{dt} e^{i\omega t}\left[\cos \frac{Ut}{2} - 2i\sin \frac{Ut}{2} \left<\tau_{i\overline\sigma} \right>\right] = \frac{1 + \left<\tau_{i\overline\sigma }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i\overline\sigma}\right>}{\omega + \frac{U}{2}}
-\end{aligned}\end{equation}
-The spin-total Greens function for the site \(i\) is
-\begin{equation}\begin{aligned}
-	\label{atomic_limit_gf}
-	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 + \left<\tau_{i }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i}\right>}{\omega + \frac{U}{2}}
-\end{aligned}\end{equation}
-At half-filling, we have \(\tau_i = 1\).
-\section{Local Greens function for the Hubbard dimer}
-From the spectral representation, we have the following expression for the local Greens function for the Hubbard dimer at site $0$:
-\begin{equation}\begin{aligned}
-	G_{D,00}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}c_{i\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
-\end{aligned}\end{equation}
-$m,n$ sum over the exact eigenstates.
-$E_m, E_n$ are the corresponding energies.
-We are interested in teh $T \to 0$ Greens function.
-In that limit, all exponentials except that for the ground state $E_{gs}$ will die out.
-The exponential inside the summation will then cancel the exponential in the partition function.
-\begin{equation}\begin{aligned}
-	G_{D,00}^\sigma(\omega, T \to 0) &= \sum_{n}\left[||\bra{GS}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
-					&= \sum_{n}\left[||\bra{n}c^\dagger_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
-\end{aligned}\end{equation}
-
-The ground state $\ket{GS}$ is just the state $\ket{-}$ in the table \ref{hubb_dim_spectrum}. We will choose to look at $\sigma = \uparrow`$. Then,
-\begin{equation}\begin{aligned}
-	c_{1\uparrow}\ket{-} &= \frac{a_1}{\sqrt 2}\ket{0, \downarrow} + \frac{a_2}{\sqrt 2}\ket{\downarrow,0}\\
-	c^\dagger_{1\uparrow}\ket{-} &= -\frac{a_1}{\sqrt 2}\ket{2, \uparrow} + \frac{a_2}{\sqrt 2}\ket{\uparrow,2}\\
-\end{aligned}\end{equation}
-The set of states $\ket{n}$ that give non-zero inner product $\ket{GS}$ are therefore
-\begin{equation}\begin{aligned}
-	\left\{ \ket{n} \right\} &= \ket{0\downarrow_\pm}\\
-	||\bra{n}c_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left(a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \pm 2a_1a_2\right)\\
-	\left\{ E_n \right\} &= \mp t
-\end{aligned}\end{equation}
-for the second inner product, and
-\begin{equation}\begin{aligned}
-	\left\{\ket{n}\right\} &= \ket{2\uparrow_\pm}\\
-	||\bra{n}c^\dagger_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left( a_2 \mp a_1 \right)^2 = \frac{1}{4}\left(1 \mp 2a_1a_2\right)\\
-	\left\{ E_n \right\} &= \pm t
-\end{aligned}\end{equation}
-for the first. The Greens function is therefore
-\begin{equation}\begin{aligned}
-	\label{dimer_local_G}
-	G_{D,00}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(t - \frac{\Delta}{2}\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(t + \frac{\Delta}{2}\right) ^2} = G_{D,00}^\downarrow(\omega, T \to 0)~.
-\end{aligned}\end{equation}
-In the atomic limit $(t=0)$, the Greens function simplifies to
-\begin{equation}\begin{aligned}
-	G_{D,00}^\uparrow(\omega, T \to 0) \bigg\vert_\text{atomic} = \frac{\omega}{\omega^2 - \frac{1}{4}U^2}
-\end{aligned}\end{equation}
-In the atomic limit, the singly-occupied state has zero energy:
-\begin{equation}\begin{aligned}
-	E_1(t=0) = \bra{1,0}\left(U \tau_{0 \uparrow}\tau_{0 \downarrow} + U \tau_{1 \uparrow}\tau_{1 \downarrow}\right) \ket{1,0} = 0
-\end{aligned}\end{equation}
-We can write the atomic limit Greens function in terms of this energy and the self energy:
-\begin{equation}\begin{aligned}
-	G_{D,00}^\uparrow(\omega, T \to 0) \bigg\vert_\text{atomic} = \frac{1}{\omega - E_1(t=0) - \Sigma(t=0)} = \frac{1}{\omega - 0 -\frac{U^2}{4\omega}}
-\end{aligned}\end{equation}
-The self energy in the atomic limit can be read off as 
-\begin{equation}\begin{aligned}
-	\label{dimer_selfenergy}
-\Sigma(t=0) = \frac{U^2}{4\omega}
-\end{aligned}\end{equation}
-The site local spectral function can also be calculated from the local Greens function:
-\begin{eqnarray}
-A(0\uparrow, \omega) &=& - \frac{1}{\pi}\text{Im }G_{D,00}^\uparrow(\omega)\nonumber\\
-			     &=& \left( \frac{1}{4} - \frac{t}{\Delta} \right)\left[\delta(\omega - \frac{1}{2}\Delta - t) + \delta(\omega + \frac{1}{2}\Delta + t)\right]\nonumber\\ 
-			     &&+ \left( \frac{1}{4} + \frac{t}{\Delta} \right) \left[\delta(\omega - \frac{1}{2}\Delta + t) + \delta(\omega + \frac{1}{2}\Delta - t)\right]\\ 
-			     &=& A(0\downarrow, \omega)~.\nonumber
-\end{eqnarray}
-Finally, the inter-site Greens function for the Hubbard dimer is given by
-\begin{equation}
-\label{dimer_intersite_G}
-G_{D,01}^\uparrow(\omega, T \to 0) = \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{t - \frac{\Delta}{2}}{\omega^2 - \left(t - \frac{\Delta}{2}\right)^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{t + \frac{\Delta}{2}}{\omega^2 - \left(t + \frac{\Delta}{2}\right)^2} = G_{D,01}^\downarrow(\omega, T \to 0)~.
-\end{equation}
-Using the diagonal and off-diagonal real space Greens functions, we can now compute the momentum-space Greens functions.
-The two momentum states are $ka = 0, \pi$.
-By Fourier transforming, these two Greens functions can be written as
-\begin{equation}\begin{aligned}
-	\label{Gk0}
-	G(k=0, \sigma) = \sum_r e^{ikr} G(r, \sigma) = G(r=0, \sigma) + G(r=a, \sigma) = \frac{1/2 + 2t/\Delta}{\omega -t + \Delta/2} + \frac{1/2 - 2t/\Delta}{\omega - t - \Delta/2}\\
-	G(k=\pi, \sigma) = \sum_r e^{ikr} G(r, \sigma) = G(r=0, \sigma) - G(r=a, \sigma) = \frac{1/2 + 2t/\Delta}{\omega + t - \Delta/2} + \frac{1/2 - 2t/\Delta}{\omega + t + \Delta/2}\\
-\end{aligned}\end{equation}
-
-\section{Contributions of various excitations to the site local spectral function}
-The site local spectral function is
-\begin{equation}\begin{aligned}
-	A(0\uparrow, \omega) = \left( \frac{1}{4} - \frac{t}{\Delta} \right)\left[\delta(\omega - \frac{\Delta}{2} - t) + \delta(\omega + \frac{\Delta}{2} + t)\right]\nonumber + \left( \frac{1}{4} + \frac{t}{\Delta} \right) \left[\delta(\omega - \frac{\Delta}{2} + t) + \delta(\omega + \frac{\Delta}{2} - t)\right]
-\end{aligned}\end{equation}
-If the eigenstates of the $N=1, S^z = - \frac{1}{2}$ sector are $\ket{1 \pm \downarrow}$ and those of $N=3, S^z = \frac{1}{2}$ sector are $\ket{3 \pm \uparrow}$, this spectral function originates from the expression:
-\begin{equation}\begin{aligned}
-	A(0\uparrow, \omega) =& \braket{1 \downarrow_- | c_{0 \uparrow} | \text{GS}} \delta\left(\omega + \frac{\Delta}{2} + t\right) + \braket{2 \uparrow_+ | c^\dagger_{0 \uparrow} | \text{GS}}\delta\left(\omega - \frac{\Delta}{2} - t\right) \\
-			      &+ \braket{1 \downarrow_+ | c_{0 \uparrow} | \text{GS}}\delta\left(\omega + \frac{\Delta}{2} - t\right) + \braket{2 \uparrow_- | c^\dagger_{0 \uparrow} | \text{GS}}\delta(\omega - \frac{\Delta}{2} + t)
-\end{aligned}\end{equation}
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.9\textwidth]{../figures/dimer-peaks.png}
-	\caption{Position, weight and nature of each of the peaks in the Hubbard dimer site local spectral function}
-\end{figure}
-
-\chapter{Simple results for the Greens functions}
-\section{Relation between single-particle Greens function and the Greens operator $(T=0)$}
- The single-particle Greens function is defined as the solution of the equation:
- \begin{equation}\begin{aligned}
-	 \left(i\partial_t - H(\vec r)\right)G(\vec r,\vec r^\prime, t) = \delta(\vec r - \vec r^\prime)
- \end{aligned}\end{equation}
- and is given by the expression
- \begin{equation}\begin{aligned}
-	 G(\vec r,\vec r^\prime, t) = -i \theta(t) \left< \left\{ c(\vec r, t) c^\dagger(\vec r^\prime, 0)\right\} \right>
- \end{aligned}\end{equation}
- This solution can be written in the Lehmann-Kallen representation  and at $T=0$ as
- \begin{equation}\begin{aligned}
-	 G(\vec r \sigma, \vec r^\prime \sigma, \omega) = \sum_{n}\left[\frac{\bra{GS}c({\vec r,\sigma})\ket{n}\bra{n}c^\dagger(\vec r^\prime,\sigma)\ket{GS}}{\omega + E_{GS} - E_n} + \frac{\bra{GS}c^\dagger(\vec r^\prime,\sigma)\ket{n}\bra{n}c({\vec r,\sigma})\ket{GS}}{\omega + E_n - E_{GS}}\right]
- \end{aligned}\end{equation}
- The sum is over the exact eigenstates of the Hamiltonian. In what follows, we will represent $\vec r,\sigma \equiv \nu$ and $\vec r^\prime,\sigma \equiv \nu^\prime$.
- \begin{equation}\begin{aligned}
-	 G(\nu, \nu^\prime, \omega) &= \sum_{n}\left[\frac{\bra{GS}c(\nu)\ket{n}\bra{n}c^\dagger(\nu^\prime)\ket{GS}}{\omega + E_{GS} - E_n} + \frac{\bra{GS}c^\dagger(\nu^\prime)\ket{n}\bra{n}c(\nu)\ket{GS}}{\omega + E_n - E_{GS}}\right]\\
-							&= \bra{GS}c(\nu)\frac{1}{\omega + E_{GS} - H}c^\dagger(\nu^\prime)\ket{GS} + \bra{GS}c^\dagger(\nu^\prime)\frac{1}{\omega + H - E_{GS}}c(\nu)\ket{GS}\\
- \end{aligned}\end{equation}
- If we now define a Greens operator
- \begin{equation}\begin{aligned}
-	 \label{inv_G_func}
-	 \mathcal{G}(\omega, H) = \frac{1}{\omega - (H - E_\text{GS})}
- \end{aligned}\end{equation}
- we can write the single-particle Greens function as a sum of the matrix elements of this operator:
- \begin{equation}\begin{aligned}
-	 \label{G_mat_el}
-	 G(\nu, \nu^\prime, \omega) = \bra{\nu} \mathcal{G}(\omega, H) \ket{\nu^\prime} - \bra{\overline{\nu^\prime}} \mathcal{G}(-\omega, H) \ket{\overline\nu} = \mathcal{G}(\omega, H)_{\nu,\nu^\prime} - \mathcal{G}(-\omega, H)_{\overline{\nu^\prime}, \overline\nu}
- \end{aligned}\end{equation}
- where we have defined the states $\ket{\nu} \equiv c^\dagger(\nu)\ket{GS}$ and $\ket{\overline\nu} \equiv c(\nu)\ket{GS}$.
-The two matrix elements can also be represented in their individual spectral representations:
- \begin{equation}\begin{aligned}
-	 \label{G_mat_spec}
- 	\mathcal{G}(\omega, H)_{\nu,\nu^\prime} = \sum_{n}\frac{\bra{GS}c(\nu)\ket{n}\bra{n}c^\dagger(\nu^\prime)\ket{GS}}{\omega + E_{GS} - E_n}\\
-	\mathcal{G}(\omega, H)_{\overline{\nu^\prime}, \overline\nu} = \sum_{n}\frac{\bra{GS}c^\dagger(\nu^\prime)\ket{n}\bra{n}c(\nu)\ket{GS}}{\omega + E_\text{GS} - E_n}
- \end{aligned}\end{equation}
-
-\section{Writing single-particle excitations of ground state in terms of $N=3, S^z = \frac{1}{2}$ eigenstates}
-The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates $\ket{3\pm\uparrow}$ defined in table \ref{hubb_dim_spectrum}.
-\begin{equation}\begin{aligned}
-	\ket{3\pm \uparrow} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{3\pm \uparrow} = \pm t\ket{3\pm \uparrow}
-\end{aligned}\end{equation}
-In terms of these eigenstates, we can write
-\begin{equation}\begin{aligned}
-	c^\dagger_{0\uparrow}\ket{\text{GS}} 
-	&= c^\dagger_{0\uparrow}\left[a_1 \ket{SS} + a_2 \ket{CT}\right] \\
-	&= a_2 \frac{1}{\sqrt 2}\ket{\uparrow,2} - a_1 \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
-	&= \left(x + y\right) \frac{1}{\sqrt 2}\ket{\uparrow,2} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
-	&=x\ket{3+ \uparrow} + y\ket{3- \uparrow}
-\end{aligned}\end{equation}
-where $x + y \equiv a_2$ and $x-y \equiv -a_1$. Similarly, for the other site excitation, we can write
-\begin{equation}\begin{aligned}
-	c^\dagger_{1\uparrow}\ket{\text{GS}} 
-	&= c^\dagger_{1\uparrow}\left[a_1 \ket{SS} + a_2 \ket{CT}\right] \\
-	&= a_2 \frac{1}{\sqrt 2}\ket{2, \uparrow} - a_1 \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
-	&=  \left(x + y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
-	&=x\ket{3+ \uparrow} - y\ket{3- \uparrow}
-\end{aligned}\end{equation}
-Solving for $x$ and $y$ gives
-\begin{equation}\begin{aligned}
-	x = \frac{a_2 - a_1}{2}, && y = \frac{a_2 + a_1}{2}
-\end{aligned}\end{equation}
-Similarly, we can also write the single-hole excitation $c_{0 \uparrow}\ket{GS}$ in terms of the $N=1, S^z = -\frac{1}{2}$ eigenstates, $\ket{1\pm \downarrow}$:
-\begin{equation}\begin{aligned}
-	\ket{1\pm \downarrow} = \frac{1}{\sqrt 2}\left(\ket{\downarrow, 0} \pm \ket{0, \downarrow}\right), && H^D \ket{1\pm \downarrow} = \mp t\ket{1\pm \downarrow}
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-	c_{0 \uparrow}\ket{GS} = a_1 \frac{1}{\sqrt 2}\ket{0, \downarrow} + a_2 \frac{1}{\sqrt 2}\ket{\downarrow, 0} = y\ket{1+ \downarrow} + x\ket{1- \downarrow}\\
-	c_{1 \uparrow}\ket{GS} = a_1 \frac{1}{\sqrt 2}\ket{\downarrow, 0} + a_2 \frac{1}{\sqrt 2}\ket{0, \downarrow} = y\ket{1+ \downarrow} - x\ket{1- \downarrow}\\
-\end{aligned}\end{equation}
-
-\section{Matrix elements of $G^{-1}$ between single-particle momentum excitations, for the Hubbard dimer}
-\begin{equation}\begin{aligned}
-	G^{-1} \equiv \omega + E_\text{GS} - H_D
-\end{aligned}\end{equation}
-The particle excitation momentum space kets are $\ket{k_0} = \frac{1}{\sqrt 2}\left(\ket{0} + \ket{1}\right) ,\ket{k_\pi} = \frac{1}{\sqrt 2}\left(\ket{0} - \ket{1}\right)$. Therefore,
-\begin{equation}\begin{aligned}
-	\left(G^{-1}\right)_{k_0 k_0} &= \frac{1}{2}\left(\bra{0} + \bra{1}\right)\left(\omega + E_\text{GS} - H_D\right)\left(\ket{0} + \ket{1}\right)\\
-				      &= \frac{1}{2}\left(2x\bra{+}\right)\left(\omega + E_\text{GS} - H_D\right)\left(2x\ket{+}\right)\\
-				      &= 2x^2\left(\omega + E_\text{GS} - t\right)\\
-\end{aligned}\end{equation}
-At the final step, we used $\braket{+,+} = 1$ and $\braket{+|H_D|+} = t$.
-
-\chapter{Topological interpretation of the Wilson ratio}
-From the Friedel sum rule\cite{langer1961friedel}, we can relate the phase shift \(\delta(0)\) due to scattering (at the Fermi surface) off a local impurity to the number of electrons bound in the potential well produced by that impurity:
-\begin{equation}\begin{aligned}
-\widetilde N = \frac{1}{2\pi i}\text{Tr }\ln S(0) = \int_\Gamma dz\partial_z \frac{1}{2\pi i}\text{Tr }\ln S(0)
-\end{aligned}\end{equation}
-From the optical theorem, we can write
-\begin{equation}\begin{aligned}
-	S = 1 + TG_0 = \frac{G}{G_0} && \left[G = G_0 + G_0 T G_0\right]
-\end{aligned}\end{equation}
-This allows us to write \cite{anirbanurg1}
-\begin{equation}\begin{aligned}
-\widetilde N = \int_\Gamma dz\partial_z \frac{1}{2\pi i}\text{Tr }\ln \frac{G}{G_0}
-\end{aligned}\end{equation}
-Since \(\text{Tr }\ln \hat O = \sum_\lambda \ln O_\lambda = \ln \prod_\lambda O_\lambda = \ln \text{Det} \hat O\), we get
-\begin{equation}\begin{aligned}
-\widetilde N &= \int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln \text{Det } \frac{G}{G_0}\\
-      &= -\int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln \frac{\text{Det } G_0}{\text{Det } G}\\
-      &\equiv -\int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln D\\
-      &= -\int_{\Gamma(D)}\frac{dD}{D}
-\end{aligned}\end{equation}
-From the work of Seki and Yunoki \cite{seki2017topological}, we know that this quantity is essentially the winding number of the curve \(\Gamma(D)\) in the complex plane spanned by the real and imaginary parts of \(D\), and is equal to the change in Luttinger's volume \(V_L\) at \(T=0\).
-\begin{equation}\begin{aligned}
-\widetilde N &= -\int_{\Gamma(D)}\frac{dD}{D} = -\Delta V_L
-\end{aligned}\end{equation}
-The incoming electrons can have \(\sigma = \uparrow,\downarrow\).
-Since the impurity singlet ground state is rotationally invariant, we have \(\delta_\uparrow = \delta_\downarrow = \delta(0)\).
-\begin{equation}\begin{aligned}
-\widetilde N &= \frac{1}{\pi}\sum_\sigma\delta_\sigma(0)\\
-\implies \delta(0) &= \frac{\pi}{2}\widetilde N = -\frac{\pi}{2}\Delta V_L
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-\label{wilson_luttinger}
-R &= 1 + \sin^2 \left(\frac{\pi}{2}\widetilde N\right)\\
-  &= 1 + \sin^2 \left(\frac{\pi}{2}\Delta V_L\right)
-\end{aligned}\end{equation}
-We note that this connection between \(R\) and \(\Delta V_L\) has not been obtained in the existing literature thus far.
-In the unitary limit, \(\delta(0) = \frac{\pi}{2}\), giving \(\Delta V_L = -1 = -\tilde N\) \cite{martin1982fermi} (i.e., one electronic state from the impurity has been absorbed into the Luttinger volume of the conduction bath), such that \(R = 2\) in this limit.
-In this way, we see that a change in the topological quantum number \(\tilde N\) causes the well known renormalisation of the Wilson ratio R from its non-interacting value \((1)\) to the value \((2)\) obtained for the local Fermi liquid \cite{nozieres1974fermi}.
-
-\end{appendices}
-
-\bibliography{notes}
+\end{widetext}
+
+\bibliography{gen-siam}
 \end{document}

### 2022-04-29 gen-siam-manuscript/gen-siam.tex
added new RG plots

@@
 
-This difference in the type of conduction baths is utilised in dynamical mean-field theory to describe various phases of the bulk system.
+This difference in the type of conduction baths is utilized in dynamical mean-field theory to describe various phases of the bulk system.
 This is done through the DMFT algorithm: one starts with a non-interacting bath, but depending on the value of \(U\), the conduction bath then gets modified and we ultimately end up with something that is different from what we started with.
@@
 Above a critical \(U_c\), the impurity spectral function gets gapped out, and that then describes the insulating phase in the bulk.
-\textit{This leaves open the following question: What is the minimal correlation one can insert into the non-interacting bath (of a single-impurity Anderson model) that can capture both the metallic and insulating phases of the bulk model?}
+\textit{This leaves open the following question}: What is the minimal correlation one can insert into the non-interacting bath (of a single-impurity Anderson model) that can capture both the metallic and insulating phases of the bulk model?
 
@@
 \begin{itemize}
-	\item a spin-exchange term \(J \vec{S}_d\cdot\vec{s}_0\) between the impurity and the zeroth site 
+	\item a spin-exchange term \(J \vec{S}_d\cdot\vec{s}_0\) between the impurity spin \(\vec S_d\) and the spin \(\vec s_0\) of the zeroth site 
 	\item a local correlation term \(U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}\) on the zeroth site
@@
 
-The full generalised Anderson model Hamiltonian, at particle-hole symmetry, is
+With these additional terms, the generalised Anderson impurity model, at particle-hole symmetry, is
 \begin{equation}\begin{aligned}
-	\mathcal{H} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} + \epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} + K \vec{C_d}\cdot\vec{C}
+	\mathcal{H} = \frac{- U}{2} \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\vec k,\sigma} \epsilon_{\vec k} \tau_{\vec k,\sigma} + V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)\\
+	+ J \vec{S}_d\cdot\vec{s}_0 + U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}
 \end{aligned}\end{equation}
+All the terms in the Hamiltonian have been depicted schematically in fig.~\ref{zeromode-bare}.
 
@@
 This zero-bandwidth model is effectively a two site model.}
+	\label{zeromode-bare}
 \end{figure}
@@
 \section{RG Equations for the model}
-The derivation of the RG equations are shown at the end. \(n_j\) is the number of \(k-\)states at the \(j^\text{th}\) isoenergetic shell. 
+We now perform a renormalisation group analysis of the MCK Hamiltonian using the recently developed URG method \cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome,1dhubjhep}.
+The RG proceeds {by applying unitary transformations in order to block-diagonalize the Hamiltonian by removing number fluctuations of the high energy degrees of freedom}.
+Given the most energetic electronic state at the \(j^\text{th}\) RG step is \(\ket{j}\) and defined by the energy \(D_{(j)}\), the Hamiltonian will in general not conserve the number of particles in this state: \(\left[H_{(j)}, \hat n_{j}\right] \neq 0\).
+The unitary transformation \(U_{(j)}\) will remove this number fluctuation at the next RG step~\cite{anirbanurg1,anirbanurg2}:
+\begin{equation}\begin{aligned}
+	H_{(j-1)} = U_{(j)} H_{(j)} U^\dagger_{(j)}~, ~\left[H_{(j-1)}, \hat n_{j}\right] =0~.
+\end{aligned}\end{equation}
+The unitary transformations are given in terms of a fermionic generator \(\eta_{(j)}\)~\cite{anirbanurg1,anirbanurg2}:
+\begin{equation}\begin{aligned}
+	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ \quad\left\{ \eta_{(j)},\eta_{(j)}^\dagger \right\}_\pm = 1~,
+\end{aligned}\end{equation}
+where \(\left\{A,B\right\}_\pm = AB \pm BA\). The generator itself is given by the expression~\cite{anirbanurg1,anirbanurg2}
+\begin{equation}\begin{aligned}
+	\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} \text{Tr}\left(H_{(j)}c_{j}\right)~.
+\end{aligned}\end{equation}
+The operator \(\hat \omega_{(j)}\) encodes the quantum fluctuation scales arising from the interplay of the kinetic energy terms and the interaction terms in the Hamiltonian:
+\begin{equation}\begin{aligned}
+	\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)}~.
+\end{aligned}\end{equation}
+\(H^i_{(j)}\) is that part of \(H_{(j)}\) that commutes with \(\hat n_j\) but does not commute with at least one \(\hat n_l\) for \(l < j\).
+The RG flow continues up to energy \(D^*\), where a fixed point is reached from the vanishing of the RG function.
+
+The derivation of the RG equations for the generalised Anderson impurity model Hamiltonian is shown in the appendix. We provide below the RG equations for a given quantum fluctuation scale \(\omega\):
 \begin{gather}
-	\Delta U_b = 0, ~ ~\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\frac{J^2}{d_2},\\
-	\Delta V = -\frac{3n_j V}{8}\left[\left(J + 4U_b/3\right) \left(\frac{1}{d_2} + \frac{1}{d_1}\right) + 4U_b/3\left(\frac{1}{d_3} + \frac{1}{d_0}\right)\right],\\
-	\Delta J = -\frac{n_j J\left(J + 4U_b\right)}{d_2}
+	\Delta U_b = 0~,\\
+	\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\frac{J^2}{d_2}~,\\
+	\Delta V = -\frac{3n_j V}{8}\left[J\left(\frac{1}{d_2} + \frac{1}{d_1}\right) +  \frac{4U_b}{3}\sum_{i=1}^4 \frac{1}{d_i}\right]~,\\
+	\Delta J = -\frac{n_j J\left(J + 4U_b\right)}{d_2}~.
 \end{gather}
+The denominators \(d_i\) used in these equations are given by
+\begin{gather}
+	d_0 = \omega - \frac{D}{2} + \frac{U_b}{2} - \frac{U}{2}~,\\
+	d_1 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{U}{2} + \frac{J}{4}~,\\
+	d_2 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}~,\\
+	d_3 = \omega - \frac{D}{2} + \frac{U_b}{2}~.
+\end{gather}
+The symbols used in the RG equations have the following meanings: \(\Delta U\) represents the renormalisation in the coupling \(U\) in going from the \(j^\text{th}\) Hamiltonian to the \(\left( j-1 \right) ^\text{th}\) Hamiltonian by decoupling the isoenergetic shell at energy \(D_{(j)}\).
+\(n_j\) is the number of electronic states on the shell \(D_{(j)}\).
 
-The denominators are
-\begin{gather}
-	d_0 = \omega - \frac{D}{2} + \frac{U_b}{2} - \frac{U}{2}, \quad d_1 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{U}{2} + \frac{J}{4},\\
-	\quad d_2 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4},\quad d_3 = \omega - \frac{D}{2} + \frac{U_b}{2}
-\end{gather}
-
-\paragraph{Important points regarding notation}
-\begin{itemize}
-	\item The labels \(U_0,J_0,V_0\) that may occur in the axes of the plots or anywhere else represent the bare values of the couplings \(U,J\) and \(V\). 
-	\item Throughout the upcoming results, the bare value of \(U_b\) is set to the negative of the bare value of \(U_0\): \(U_b = -U_0/10\).
-This means that whenever we vary \(U_0\) along the axis of a plot, we are simultaneous varying \(U_b\).
-\end{itemize}
+We will discuss the consequences of these RG equations in the next sections, but we clarify here that the labels \(U_0,J_0,V_0\) that will occur in the axes of the plots or anywhere else represent the bare values of the couplings \(U,J\) and \(V\).
+We also point out here that throughout the upcoming results, the bare value of \(U_b\) is set to the negative of the bare value of \(U_0\): \(U_b = -U_0/10\).
+This means that whenever we vary \(U_0\) along the axis of a plot, we are simultaneous varying \(U_b\).	The reason for choosing the negative sign of \(U_b\) will be clarified in the next section.
 
 \section{RG flows and phase diagram}
+
+We start the discussion on the nature of the RG flows by pointing out the spin-exchange coupling \(J\) has a critical point \(\left( \Delta J = 0 \right) \) at \(U_b = -J/4\).
+Since \(J\) is positive, this means that we can capture both relevant and irrelevant RG flows of \(J\) by keeping \(U_b\) negative.
+\(U_b\) is found to be marginal under the RG transformation, and we set \(U_b\) to \(-U_0/10\) hereafter.
+We will work in the regime of quantum fluctuations where all the denominators are negative: \(d_i < 0 ~\forall~i\).
+
+\subsection{RG flows for \(4U_b + J > 0\)}
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.45\textwidth]{../figures/J_Ub.pdf}
+	\caption{JUb}
+	\label{fig:-figures-J_Ub-pdf}
+\end{figure}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.45\textwidth]{../figures/U_Ub.pdf}
+	\caption{JUb}
+	\label{fig:-figures-J_Ub-pdf}
+\end{figure}
 

### 2022-04-29 gen-siam-manuscript/gen-siam.tex
finished manuscript upto phase diagram

@@
 \begin{abstract}
-
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
 \end{abstract}
@@
 
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
+
 \section{The generalised Anderson impurity model}
@@
 
-With these additional terms, the generalised Anderson impurity model, at particle-hole symmetry, is
+With these additional terms, the {\it generalised Anderson impurity model} (hence referred to as the GAIM), at particle-hole symmetry, is
 \begin{equation}\begin{aligned}
+	\label{GIAM-ham}
 	\mathcal{H} = \frac{- U}{2} \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\vec k,\sigma} \epsilon_{\vec k} \tau_{\vec k,\sigma} + V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)\\
@@
 
-\section{RG Equations for the model}
-We now perform a renormalisation group analysis of the MCK Hamiltonian using the recently developed URG method \cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome,1dhubjhep}.
-The RG proceeds {by applying unitary transformations in order to block-diagonalize the Hamiltonian by removing number fluctuations of the high energy degrees of freedom}.
-Given the most energetic electronic state at the \(j^\text{th}\) RG step is \(\ket{j}\) and defined by the energy \(D_{(j)}\), the Hamiltonian will in general not conserve the number of particles in this state: \(\left[H_{(j)}, \hat n_{j}\right] \neq 0\).
-The unitary transformation \(U_{(j)}\) will remove this number fluctuation at the next RG step~\cite{anirbanurg1,anirbanurg2}:
+\section{Method and RG Equations}
+
+\subsection{The unitary RG method}
+The focus here is on obtaining the low-energy phases of the GAIM.
+To accomplish this, we perform a renormalisation group analysis of the associated Hamiltonian (eq.~\ref{GIAM-ham}) using the recently developed unitary renormalisation group (URG) method \cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome,1dhubjhep,Mukherjee_mott_merg,anirban_kondo}.
+The unitary RG transformations lead to a series of Hamiltonians \(H_{(j)}\) related to the Hamiltonian at the previous step through a unitary transformation; the unitary transformations are defined by the requirement that they remove number fluctuations in high-energy \(k-\)states, thus making the Hamiltonian progressively more block-diagonal in momentum space.
+The high-energy degrees of freedom that get decoupled in the process become integrals of motion (IOMs) for the Hamiltonian and enter the Hamiltonian only in a purely number-diagonal form.
+
+To be more precise, we first choose a complete basis \(\left\{ \ket{j} \right\} \) and arrange these states from high-energy (UV) to low-energy (IR).
+Typically we take these states to be the momentum eigenstates \(\left(\ket{j} = \left\{\ket{\vec k \uparrow}, \ket{\vec k \downarrow}\right\}\right)\), and the isoenergetic shells \(\left\{D_{(j)}\right\}\) then define the sequence of states, such that the momenta far away from the Fermi surface (taken to be at higher \(j\) and having \(|D_{(j)}| \gg |\epsilon_F|\)) are taken to be the UV states while those near the Fermi surface (taken to be at lower \(j\) and having \(D_{(j)} \sim \epsilon_F\)) comprise the IR states.
+This scheme is shown in fig.~\ref{urg-scheme}.
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.45\textwidth]{../figures/urg-scheme.pdf}
+	\caption{High energy - low energy scheme defined and used in the URG method.
+The states away from the Fermi surface form the UV subspace and are decoupled first, leading to a Hamiltonian which is more block-diagonal and comprised of only the IR states near the Fermi surface.}
+	\label{urg-scheme}
+\end{figure}
+
+At a given RG step \(j\), the Hamiltonian \(H_{(j)}\) involves number fluctuations between the \(k-\)states that have energies lower than \(D_{(j+1)}\).
+So the most energetic states that are still non-trivially present in \(H_{(j)}\) are those on the energy contour \(D_{(j)}\), and the Hamiltonian \(H_{(j)}\) will, in general, not conserve the number of particles in this energy (or momentum) state: \(\left[H_{(j)}, \hat n_{j}\right] \neq 0\).
+The unitary transformation \(U_{(j)}\) is then defined so as to remove this number fluctuation at the next RG step~\cite{anirbanurg1,anirbanurg2}:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-The unitary transformations are given in terms of a fermionic generator \(\eta_{(j)}\)~\cite{anirbanurg1,anirbanurg2}:
+
+The unitary transformations can be expressed in terms of a generator \(\eta_{(j)}\) that has fermionic algebra~\cite{anirbanurg1,anirbanurg2}:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-The operator \(\hat \omega_{(j)}\) encodes the quantum fluctuation scales arising from the interplay of the kinetic energy terms and the interaction terms in the Hamiltonian:
+The important operator \(\hat \omega_{(j)}\) originates from the quantum fluctuations that exist in the problem because of the non-commutation of the kinetic energy terms and the interaction terms in the Hamiltonian:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-\(H^i_{(j)}\) is that part of \(H_{(j)}\) that commutes with \(\hat n_j\) but does not commute with at least one \(\hat n_l\) for \(l < j\).
+\(H^i_{(j)}\) is the part of \(H_{(j)}\) that commutes with \(\hat n_j\) but does {\it not} commute with at least one \(\hat n_l\) for \(l < j\).
 The RG flow continues up to energy \(D^*\), where a fixed point is reached from the vanishing of the RG function.
+
+\subsection{URG equations for the GAIM}
 
@@
 
-We will discuss the consequences of these RG equations in the next sections, but we clarify here that the labels \(U_0,J_0,V_0\) that will occur in the axes of the plots or anywhere else represent the bare values of the couplings \(U,J\) and \(V\).
+We will discuss the consequences of these RG equations in the next sections, but we clarify here that the labels \(U_0,J_0,V_0\) that might occur in the figures or elsewhere in the text represent the bare values of the associated couplings \(U,J\) and \(V\).
 We also point out here that throughout the upcoming results, the bare value of \(U_b\) is set to the negative of the bare value of \(U_0\): \(U_b = -U_0/10\).
-This means that whenever we vary \(U_0\) along the axis of a plot, we are simultaneous varying \(U_b\).	The reason for choosing the negative sign of \(U_b\) will be clarified in the next section.
+This means that whenever we vary \(U_0\) along the axis of a plot, we are simultaneous varying \(U_b\).
+The reason for choosing the negative sign of \(U_b\) will be clarified in the next section.
 
@@
 
-We start the discussion on the nature of the RG flows by pointing out the spin-exchange coupling \(J\) has a critical point \(\left( \Delta J = 0 \right) \) at \(U_b = -J/4\).
-Since \(J\) is positive, this means that we can capture both relevant and irrelevant RG flows of \(J\) by keeping \(U_b\) negative.
+We start the discussion on the nature of the RG flows by noting that the bath correlation \(U_b\) is marginal, and the spin-exchange coupling \(J\) has a critical point \(\left( \Delta J = 0 \right) \) at \(U_b = -J/4\).
+We will look at the RG flows of the couplings \(U,V\) and \(J\) on both sides of this critical point, and see what phases they lead to.
+We will work in the regime of quantum fluctuations where all the denominators are negative: \(d_i < 0 ~\forall~i\).
+Before we start, note that:
+\begin{itemize}
+	\item Since \(J\) is positive, this means that we can capture both relevant and irrelevant RG flows of \(J\) by keeping \(U_b\) negative.
 \(U_b\) is found to be marginal under the RG transformation, and we set \(U_b\) to \(-U_0/10\) hereafter.
-We will work in the regime of quantum fluctuations where all the denominators are negative: \(d_i < 0 ~\forall~i\).
+	\item The critical point has been chosen from the RG equation of \(J\) and not of \(V\); this is because, the RG irrelevance of \(J\) is sufficient to make \(V\) irrelevant as well, and on the other hand, the RG relevance of \(J\) is sufficient to screen the impurity.
+\end{itemize}
 
-\subsection{RG flows for \(4U_b + J > 0\)}
+\subsection{RG flows for \(4U_b + J_0 > 0\)}
+
+In this regime, \(J\) is relevant and flows to large positive values.
+It is also easy to deduce from its RG equation that \(V\) is also relevant.
+\(U\) is more non-trivial, because its RG equation involves both \(V\) and \(J\).
+Nevertheless, the RG equations were solved numerically with bare values of the couplings and the bandwidth, and it was found that while \(V\) and \(J\) are relevant, \(U\) is irrelevant.
+These findings are shown in the blue curves of fig.~\ref{rg-flow}.
+The fixed point values can be summarised as:
+\begin{equation}\begin{aligned}
+	U^* = 0, ~ ~ ~ ~ V^* \gg 1, ~ ~ ~ ~ J^* \gg 1, ~ ~ ~ ~ U_b \sim \mathcal{O}(1)
+\end{aligned}\end{equation}
+
+\subsection{RG flows for \(4U_b + J_0 < 0\)}
+
+The RG \(\beta\)-function function for \(J\) changes sign as we tune \(U_b\) to less than \(-J_0/4\), and \(J\) becomes irrelevant.
+As for \(V\), note that in the RG equation for \(V\), it is \(J\) that drives \(V\) to be relevant while \(U_b\) drives \(V\) to irrelevance; if \(J\) itself is irrelevant, then \(\Delta V\) will be dominated by \(U_b\) and \(V\) will be ultimately irrelevant.
+The behaviour of \(U\) is again non-trivial and ananlytically not tractable, so we solve the RG equations numerically.
+It turns out that although \(U\) is slightly irrelevant, it saturates to an appreciable value near the fixed point.
+These RG flows are shown in the purple curves of fig.~\ref{rg-flow}.
+The fixed point values in this regime can be summarised as:
+\begin{equation}\begin{aligned}
+	U^* \sim \mathcal{O}(1), ~ ~ ~ ~ V^* =0, ~ ~ ~ ~ J^* =0, ~ ~ ~ ~ U_b \sim \mathcal{O}(1)
+\end{aligned}\end{equation}
+
+\begin{figure*}[!htb]
+	\centering
+	\includegraphics[width=0.32\textwidth]{../figures/J_Ub.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/U_Ub.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/V_Ub.pdf}
+	\caption{Variation of couplings \(U,V\) and \(J\) along the RG transformations.
+x-axis represents the RG steps, the rightmost point is the first RG step and leftmost point is the final RG step.
+The values of the bare couplings are given in the title.
+All values are in units of the half-bandwidth \(D_0\), which is chosen to be 10.
+The blue curves represent the flows for \(4U_b + J > 0\), where \(J\) is relevant.
+The purple curves represent the RG flows for \(4U_b + J < 0\), where \(J\) is irrelevant.
+The red curves are exactly at the critical point, where \(J\) is marginal.}
+	\label{rg-flow}
+\end{figure*}
+
+\subsection{Phase diagram: impurity phase transition}
+
+The low-energy RG phase diagram is obtained by solving the RG equations for ranges of couplings, and is shown in fig.~\ref{phase-diag}.
+There are four distinct phases in the space of couplings \(U_0 \text{ vs } J_0\), with \(U_b\) constrained at \(-U_0/10\) and \(V_0\) set to \(2J_0\).
+The purple phase (phase B in the legend) is composed of those Hamiltonians which lead to RG relevant \(V,J\) and RG irrelevant \(U\).
+In other words, this is the phase where the impurity moment is screened by the conduction electrons.
+This is the low-energy phase of the usual Anderson impurity model that has \(U\) and \(V\).
+The red phase (phase C in the legend) consists of those Hamiltonians which produce irrelevant \(J,V\) and a relevant \(U\); here, the conduction electrons fail to screen the impurity and a residual local moment survives on the impurity at low energies.
+The light green phase (phase D in the legend) lies in between these two phases, and is defined by non-negligible \(V^*, U^*\) but zero \(J^*\).
+In this phase, the impurity still gets screened, but there is more charge content on the impurity site compared to phase B.
+On going to the thermodynamic limit by increasing the bandwidth \(D_0\), this light green phase disappears.
+The gray phase (phase A in the legend) is a ``dead" phase where \(U,V,J\) are all RG irrelevant.
+The various phases are summarised in table.~\ref{summary-phases}.
+
+The black line in fig.~\ref{phase-diag} represents a line of critical points \(U_b = J_0\), and separates the two major phases of the impurity.
+Such a {\it phase transition} between the screened impurity and the local moment phases is absent in the usual Anderson impurity model without the attractive correlation \(U_b\).
+In fact, only the purply screened phase is adiabatically connected the Anderson impurity model.
+
+\begin{table}[!htb]
+\centering
+\begin{tabular}{|c|c|c|}
+\hline
+phase & RG flow & fixed point \\ 
+\hline
+B & \(\Delta U <0, \Delta J,\Delta V>0\) & \(U^* \ll V^* \ll J^*\) \\ 
+D &  \(\Delta U, \Delta J < 0,\Delta V>0\) & \(J^* < U^* \ll V^*\) \\
+C &  \(\Delta U > 0, \Delta J,\Delta V<0\) & \(U^* \gg 1,  V^*, J^* = 0\)\\
+A &  \(\Delta U, \Delta J,\Delta V < 0\) & \(U^*, V^*, J^* = 0\) \\
+\hline
+\end{tabular}
+\caption{Summary of the various fixed point phases}
+\label{summary-phases}
+\end{table}
+
+\begin{figure}[!htb]
+	\includegraphics[width=0.5\textwidth]{../figures/phase-map-MIT.pdf}
+	\caption{Phase diagram of the GAIM, in the space of couplings \(U_0\) and \(J_0\).
+\(U_b\) is set to \(-U_0/10\) and \(V_0\) is set to \(2J_0\).
+The various phases \(A\) through \(D\) are characterised in the text.}
+	\label{phase-diag}
+\end{figure}
+
+\section{Low-energy effective Hamiltonian and the ground state}
+
+The RG fixed point Hamiltonian describes the low-energy phase of the system.
+In general, if the RG fixed point is reached at an energy scale \(D^*\), the fixed point Hamiltonian \(\mathcal{H}^*\) is obtained simply from the fixed point values of the couplings, and by noting that the states above \(D^*\) are now part of the IOMs:
+\begin{equation}\begin{aligned}
+	\mathcal{H}^* = \frac{- U^*}{2} \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma} + U_b^* \hat n_{0 \uparrow} \hat n_{0 \downarrow} \\
+	+ V^*\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + J^* \vec{S}_d\cdot\vec{s}_0
+\end{aligned}\end{equation}
+
+\subsection{Screened regime: \(-U_b/J < 1/4 \)}
 
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/J_Ub.pdf}
-	\caption{JUb}
-	\label{fig:-figures-J_Ub-pdf}
+	\includegraphics[width=0.5\textwidth]{../figures/J_bandwidth.pdf}
+	% \caption{../figures/J_bandwidth.pdf}
+	% \label{fig:-figures-J_bandwidth-pdf}
 \end{figure}
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/U_Ub.pdf}
-	\caption{JUb}
-	\label{fig:-figures-J_Ub-pdf}
-\end{figure}
-
-\begin{widetext}
-
-\begin{figure}[!htb]
-	\includegraphics[width=0.7\textwidth]{../figures/phase-map-MIT.pdf}
-\end{figure}
-
-\end{widetext}
-\begin{table}
-\centering
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-phase & RG flow & fixed point & GS & 2-site GS \\ 
-\hline
-blue & \(\Delta U <0, \Delta J,\Delta V>0\) & \(U^* \ll V^* \ll J^*\) & SS & \(\ket{SS}=\ket{\uparrow,\downarrow} - \ket{\downarrow, \uparrow}\)  \\ 
-green &  \(\Delta U < 0, \Delta J < 0,\Delta V>0\) & \(J^* < U^* \ll V^*\) & SS + CT-0 & \(c\ket{SS} + \sqrt{1-c^2}\ket{CT-0}\)  \\  
-red &  \(\Delta U > 0, \Delta J,\Delta V<0\) & \(U^* \gg 1,  V^* = J^* = 0\) & decoupled LM & \(\left\{\ket{\uparrow}, \ket{\downarrow} \right\} \otimes \left\{\ket{0}, \ket{2}\right\} \) \\
-gray &  \(\Delta U, \Delta J,\Delta V < 0\) & \(U^* = V^* = J^* = 0\) & lattice & \(\left\{\ket{\uparrow}, \ket{\downarrow}, \ket{0}, \ket{2} \right\} \otimes \left\{\ket{0}, \ket{2}\right\}\) \\
-\hline
-\end{tabular}
-\end{table}
-
-\section{Low-energy effective Hamiltonian and the ground state}
-
-\subsection{Screened regime: \(-U_b/J < 1/4 \)}
-
 The fixed point Hamiltonian can, in general, be written as

### 2022-05-01 gen-siam-manuscript/gen-siam.tex
almost finished work sections, pairing fluctuation and part of entanglement left

@@
 \documentclass[reprint,prb,superscriptaddress]{revtex4-2}
-\usepackage{braket,amsmath,graphicx,float,color,ulem,soul,lipsum}
-\usepackage[hidelinks]{hyperref}
+\usepackage{braket,amsmath,graphicx,color}
+\usepackage{hyperref}
 \bibliographystyle{apsrev4-1}
@@
 
-The Hubbard model is one of the fundamental models for strong electronic correlation; in its simplest form, it features a single band of conduction electrons hopping on a lattice and interacting via local correlations that provide a cost \(U\) if any site is doubly occupied:
-\[H_\text{hubb} = -t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}+\text{h.c.}\right) + U\sum_i \hat n_{i \uparrow} \hat n_{i \downarrow} - \mu \sum_{i,\sigma}\hat n_{i\sigma}\]
-The model can be made particle-hole symmetric by choosing \(\mu = U/2\):
-\[H_\text{hubb} = -t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}+\text{h.c.}\right) - \frac{U}{2}\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\]
+The Hubbard model is one of the fundamental models for strong electronic correlation; in its simplest form, it features a single band of conduction electrons hopping on a lattice and interacting via local correlations that provide a cost \(U\) if any site is doubly occupied.
 There are two trivial limits of the model.
@@
 We will refer to that specific site as the zeroth site throughout.
-We recall the Hamiltonian of the Anderson impurity model with a half-filled impurity site:
+We recall the Hamiltonian of the Anderson impurity model (AIM) with a half-filled impurity site:
 \begin{equation} 
@@
 
-In order to enhance the Anderson impurity model, we introduce two extra two-particle interaction terms into the Hamiltonian:
+In order to enhance the Anderson impurity model (AIM), we introduce two extra two-particle interaction terms into the Hamiltonian:
 \begin{itemize}
 	\item a spin-exchange term \(J \vec{S}_d\cdot\vec{s}_0\) between the impurity spin \(\vec S_d\) and the spin \(\vec s_0\) of the zeroth site 
-	\item a local correlation term \(U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}\) on the zeroth site
+	\item a local particle-hole symmetric correlation term \(-U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}\) on the zeroth site
 \end{itemize}
 
-With these additional terms, the {\it generalised Anderson impurity model} (hence referred to as the GAIM), at particle-hole symmetry, is
+With these additional terms, the {\it generalised Anderson impurity model} (henceforth referred to as the GAIM), at particle-hole symmetry, is
 \begin{equation}\begin{aligned}
 	\label{GIAM-ham}
-	\mathcal{H} = \frac{- U}{2} \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\vec k,\sigma} \epsilon_{\vec k} \tau_{\vec k,\sigma} + V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)\\
-	+ J \vec{S}_d\cdot\vec{s}_0 + U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}
+	\mathcal{H} = -\frac{1}{2}U \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\vec k,\sigma} \epsilon_{\vec k} \tau_{\vec k,\sigma} + J \vec{S}_d\cdot\vec{s}_0 \\
+	+ V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}
 \end{aligned}\end{equation}
-All the terms in the Hamiltonian have been depicted schematically in fig.~\ref{zeromode-bare}.
+All the terms in the Hamiltonian have been depicted schematically in Fig.~\ref{zeromode-bare}.
 
@@
 Typically we take these states to be the momentum eigenstates \(\left(\ket{j} = \left\{\ket{\vec k \uparrow}, \ket{\vec k \downarrow}\right\}\right)\), and the isoenergetic shells \(\left\{D_{(j)}\right\}\) then define the sequence of states, such that the momenta far away from the Fermi surface (taken to be at higher \(j\) and having \(|D_{(j)}| \gg |\epsilon_F|\)) are taken to be the UV states while those near the Fermi surface (taken to be at lower \(j\) and having \(D_{(j)} \sim \epsilon_F\)) comprise the IR states.
-This scheme is shown in fig.~\ref{urg-scheme}.
+This scheme is shown in Fig.~\ref{urg-scheme}.
 
@@
 
-The derivation of the RG equations for the generalised Anderson impurity model Hamiltonian is shown in the appendix. We provide below the RG equations for a given quantum fluctuation scale \(\omega\):
+The derivation of the RG equations for the generalised Anderson impurity model (GAIM) Hamiltonian is shown in the appendix.
+We provide below the RG equations for a given quantum fluctuation scale \(\omega\):
 \begin{gather}
@@
 \begin{gather}
-	d_0 = \omega - \frac{D}{2} + \frac{U_b}{2} - \frac{U}{2}~,\\
-	d_1 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{U}{2} + \frac{J}{4}~,\\
-	d_2 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}~,\\
-	d_3 = \omega - \frac{D}{2} + \frac{U_b}{2}~.
+	d_0 = \omega - \frac{D}{2} + \frac{U_b}{2} - \frac{U}{2}~,d_2 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}~,\\
+	d_1 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{U}{2} + \frac{J}{4}~,d_3 = \omega - \frac{D}{2} + \frac{U_b}{2}~.
 \end{gather}
@@
 
-We start the discussion on the nature of the RG flows by noting that the bath correlation \(U_b\) is marginal, and the spin-exchange coupling \(J\) has a critical point \(\left( \Delta J = 0 \right) \) at \(U_b = -J/4\).
-We will look at the RG flows of the couplings \(U,V\) and \(J\) on both sides of this critical point, and see what phases they lead to.
+We start the discussion on the nature of the RG flows by noting that the bath correlation \(U_b\) is marginal, and the spin-exchange coupling \(J\) has a critical point \(\left( \Delta J = 0 \right) \) at \(r \equiv -U_b/J = 1/4 \equiv r_c\).
+We will look at the RG flows of the couplings \(U,V\) and \(J\) on both sides of this critical point by tuning the ratio \(r\) across the critical value \(r_c\), and see what phases they lead to.
 We will work in the regime of quantum fluctuations where all the denominators are negative: \(d_i < 0 ~\forall~i\).
@@
 
-\subsection{RG flows for \(4U_b + J_0 > 0\)}
+\subsection{RG flows for \(r < r_c\)}
 
@@
 Nevertheless, the RG equations were solved numerically with bare values of the couplings and the bandwidth, and it was found that while \(V\) and \(J\) are relevant, \(U\) is irrelevant.
-These findings are shown in the blue curves of fig.~\ref{rg-flow}.
+These findings are shown in the blue curves of Fig.~\ref{rg-flow}.
 The fixed point values can be summarised as:
@@
 
-\subsection{RG flows for \(4U_b + J_0 < 0\)}
+\subsection{RG flows for \(r > r_c\)}
 
-The RG \(\beta\)-function function for \(J\) changes sign as we tune \(U_b\) to less than \(-J_0/4\), and \(J\) becomes irrelevant.
+The RG \(\beta\)-function function for \(J\) changes sign as \(r\) grows greater than \(r_c\) upon tuning \(U_b\) to less than \(-J_0/4\), and \(J\) becomes irrelevant.
 As for \(V\), note that in the RG equation for \(V\), it is \(J\) that drives \(V\) to be relevant while \(U_b\) drives \(V\) to irrelevance; if \(J\) itself is irrelevant, then \(\Delta V\) will be dominated by \(U_b\) and \(V\) will be ultimately irrelevant.
-The behaviour of \(U\) is again non-trivial and ananlytically not tractable, so we solve the RG equations numerically.
+The behaviour of \(U\) is again non-trivial and analytically not tractable, so we solve the RG equations numerically.
 It turns out that although \(U\) is slightly irrelevant, it saturates to an appreciable value near the fixed point.
-These RG flows are shown in the purple curves of fig.~\ref{rg-flow}.
+These RG flows are shown in the purple curves of Fig.~\ref{rg-flow}.
 The fixed point values in this regime can be summarised as:
@@
 
-\begin{figure*}[!htb]
+\begin{figure}[!htb]
 	\centering
-	\includegraphics[width=0.32\textwidth]{../figures/J_Ub.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_Ub.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/V_Ub.pdf}
-	\caption{Variation of couplings \(U,V\) and \(J\) along the RG transformations.
+	\includegraphics[width=0.48\textwidth]{../figures/J_Ub.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/U_Ub.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/V_Ub.pdf}
+	\caption{Variation of couplings \(U,V\) and \(J\) along the RG transformations, for three values of the transition-tuning ratio \(r\).
 x-axis represents the RG steps, the rightmost point is the first RG step and leftmost point is the final RG step.
@@
 All values are in units of the half-bandwidth \(D_0\), which is chosen to be 10.
-The blue curves represent the flows for \(4U_b + J > 0\), where \(J\) is relevant.
-The purple curves represent the RG flows for \(4U_b + J < 0\), where \(J\) is irrelevant.
-The red curves are exactly at the critical point, where \(J\) is marginal.}
+The blue curves represent the flows for \(r > r_c\), where \(J\) is relevant.
+The purple curves represent the RG flows for \(r < r_c\), where \(J\) is irrelevant.
+The red curves are exactly at the critical point \(r = r_c\), where \(J\) is marginal.}
 	\label{rg-flow}
-\end{figure*}
+\end{figure}
 
@@
 
-The low-energy RG phase diagram is obtained by solving the RG equations for ranges of couplings, and is shown in fig.~\ref{phase-diag}.
+The low-energy RG phase diagram is obtained by solving the RG equations for ranges of couplings, and is shown in Fig.~\ref{phase-diag}.
 There are four distinct phases in the space of couplings \(U_0 \text{ vs } J_0\), with \(U_b\) constrained at \(-U_0/10\) and \(V_0\) set to \(2J_0\).
-The purple phase (phase B in the legend) is composed of those Hamiltonians which lead to RG relevant \(V,J\) and RG irrelevant \(U\).
+The red phase (phase A in the legend) is composed of those Hamiltonians which lead to RG relevant \(V,J\) and RG irrelevant \(U\).
 In other words, this is the phase where the impurity moment is screened by the conduction electrons.
-This is the low-energy phase of the usual Anderson impurity model that has \(U\) and \(V\).
-The red phase (phase C in the legend) consists of those Hamiltonians which produce irrelevant \(J,V\) and a relevant \(U\); here, the conduction electrons fail to screen the impurity and a residual local moment survives on the impurity at low energies.
-The light green phase (phase D in the legend) lies in between these two phases, and is defined by non-negligible \(V^*, U^*\) but zero \(J^*\).
+This is the low-energy phase of the AIM that has \(U\) and \(V\).
+The blue phase (phase B in the legend) consists of those Hamiltonians which produce irrelevant \(J,V\) and a relevant \(U\); here, the conduction electrons fail to screen the impurity and a residual local moment survives on the impurity at low energies.
+The yellow phase (phase C in the legend) lies in between these two phases, and is defined by non-negligible \(V^*, U^*\) but zero \(J^*\).
 In this phase, the impurity still gets screened, but there is more charge content on the impurity site compared to phase B.
 On going to the thermodynamic limit by increasing the bandwidth \(D_0\), this light green phase disappears.
-The gray phase (phase A in the legend) is a ``dead" phase where \(U,V,J\) are all RG irrelevant.
+The gray phase (phase D in the legend) is a ``dead" phase where \(U,V,J\) are all RG irrelevant.
 The various phases are summarised in table.~\ref{summary-phases}.
 
-The black line in fig.~\ref{phase-diag} represents a line of critical points \(U_b = J_0\), and separates the two major phases of the impurity.
-Such a {\it phase transition} between the screened impurity and the local moment phases is absent in the usual Anderson impurity model without the attractive correlation \(U_b\).
-In fact, only the purply screened phase is adiabatically connected the Anderson impurity model.
+The black line in Fig.~\ref{phase-diag} represents a line of critical points \(U_b = J_0\), and separates the two major phases of the impurity.
+Such a {\it phase transition} between the screened impurity and the local moment phases is absent in the AIM without the attractive correlation \(U_b\).
+In fact, only the purple screened phase is adiabatically connected the AIM.
 
@@
 \hline
-B & \(\Delta U <0, \Delta J,\Delta V>0\) & \(U^* \ll V^* \ll J^*\) \\ 
-D &  \(\Delta U, \Delta J < 0,\Delta V>0\) & \(J^* < U^* \ll V^*\) \\
-C &  \(\Delta U > 0, \Delta J,\Delta V<0\) & \(U^* \gg 1,  V^*, J^* = 0\)\\
-A &  \(\Delta U, \Delta J,\Delta V < 0\) & \(U^*, V^*, J^* = 0\) \\
+A & \(\Delta U <0, ~ ~ \Delta J,\Delta V>0\) & \(U^* \ll V^* \ll J^*\) \\ 
+B &  \(\Delta U > 0, ~ ~ \Delta J,\Delta V<0\) & \(U^* \gg 1, ~ ~V^*, J^* = 0\)\\
+C &  \(\Delta U, \Delta J < 0,~ ~\Delta V>0\) & \(J^* < U^* \ll V^*\) \\
+D &  \(\Delta U, \Delta J,\Delta V < 0\) & \(U^*, V^*, J^* = 0\) \\
 \hline
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}^* = \frac{- U^*}{2} \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma} + U_b^* \hat n_{0 \uparrow} \hat n_{0 \downarrow} \\
+	\mathcal{H}^* = -\frac{1}{2}U^*\left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma} - U_b^* \hat n_{0 \uparrow} \hat n_{0 \downarrow} \\
 	+ V^*\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + J^* \vec{S}_d\cdot\vec{s}_0
@@
 
-\subsection{Screened regime: \(-U_b/J < 1/4 \)}
+\subsection{Screened regime}
+\(U\) is irrelevant in this regime.
+Moreover, as we go towards the thermodynamic limit by increasing the bandwidth \(D_0\), we find that \(J^* \gg V^*\) (see Fig.~\ref{J_bandwidth}), and the fixed point Hamiltonian is determined purely by the spin-exchange part; combining this with the local bath correlation \(U_b\) that is marginal then gives the low-energy Hamiltonian for the screened regime:
+\begin{equation}
+	H_\text{eff}^\text{sc} = J^* \vec{S}_d\cdot\vec{s}_0 - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow} + \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma}
+\end{equation}
+
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../figures/J_bandwidth.pdf}
+	\caption{Increase of \(J^*\) in comparison to \(V^*\) when going towards the thermodynamic limit.}
+	\label{J_bandwidth}
+\end{figure}
+
+Since the high momentum modes have been decoupled, the ground state in this regime can be estimated by compressing the kinetic energy to the zero bandwidth limit: 
+\begin{equation}\begin{aligned}
+	\sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma} \sim \epsilon_F \sum_{\vec k_F,\sigma}\tau_{\vec k_F,\sigma}
+\end{aligned}\end{equation}
+Choosing the chemical potential such that \(\epsilon_F\) vanishes results in a {\it two-site Hamiltonian} composed of the impurity site and the zeroth site (see Fig.~\ref{zero-bw}):
+\begin{equation}
+	\label{two-site}
+	H_\text{eff}^\text{sc} \sim J^* \vec{S}_d\cdot\vec{s}_0 - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}
+\end{equation}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../figures/zeromode_eff.pdf}
+	\caption{Two site Hamiltonian obtained by taking the zero bandwidth limit of the effective Hamiltonian in the screened regime.}
+	\label{zero-bw}
+\end{figure}
+This model is easily solved and the ground state is a maximally-entangled spin singlet formed by \(\vec S_d\) and \(\vec s_0\); the ground state energy is \(E_\text{gs}^\text{sc} = -\frac{3}{4}J^* - U_b\):
+\begin{equation}\begin{aligned}
+	\ket{\Psi}_\text{gs}^\text{sc} = \frac{1}{\sqrt 2}\left(\ket{\uparrow_d,\downarrow_0} - \ket{\downarrow_d,\uparrow_0}\right)
+\end{aligned}\end{equation}
+where \(\left\{\uparrow_d, \downarrow_d\right\}, \left\{\uparrow_0, \downarrow_0\right\}\) are the spin states of the impurity and zeroth sites respectively.
+As mentioned before, this regime in the GAIM is adiabatically connected to the AIM, and indeed, such a spin-singlet ground state is also obtained in the AIM from other methods like Poor Man's scaling~\cite{anderson1969exact,anderson1970}, numerical renormalisation group~\cite{wilson1975,hrk_wilson_1980}, Bethe ansatz~\cite{}, conformal field theory methods~\cite{}[CITE] and the URG analysis of the Kondo model~\cite{anirban_kondo}.
+
+\subsection{Unscreened regime}
+
+This regime is simpler than the screened regime, because both \(V\) and \(J\) are irrelevant, and only \(U\) is relevant.
+The effective Hamiltonian then consists of an impurity spin that is decoupled from the conduction bath:
+\begin{equation}\begin{aligned}
+	H_\text{eff}^\text{uns} = -\frac{1}{2}U^*\left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow} + \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma}
+\end{aligned}\end{equation}
+The impurity site has a doubly-degenerate ground state \(\left\{ \ket{\uparrow_d}.\ket{\downarrow_d}\right\}\), and the total ground state is the impurity state in direct product with the ground state \(\ket{\Psi}_\text{gs, bath}\) of the conduction bath Hamiltonian \(H_\text{eff, bath}^\text{uns} =  - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow} + \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma}\):
+\begin{equation}\begin{aligned}
+	\ket{\Psi}_\text{gs}^\text{uns} = \ket{\sigma_d}\otimes\ket{\Psi}_\text{gs, bath}, ~ ~ ~ \sigma = \uparrow,\downarrow
+\end{aligned}\end{equation}
+
+\subsection{The critical point: \(4U_b + J = 0\)}
+
+Along the critical points, \(J\) is marginal and \(U\) is irrelevant, while \(V\) is slightly relevant (see Fig.~\ref{rg-flow}).
+This leads to enhanced fluctuations in both the spin and charge sectors of the impurity site.
+The effective Hamiltonian is
+\begin{equation}\begin{aligned}
+	H_\text{eff}^\text{crit} = \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma} - U_b^* \hat n_{0 \uparrow} \hat n_{0 \downarrow} + J^* \vec{S}_d\cdot\vec{s}_0\\
+	+ V^*\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) 
+\end{aligned}\end{equation}
+Since the interactions are marginal or only slightly relevant, the kinetic energy is no longer negligible compared to them, and it is not possible to faithfully take a zero bandwidth limit of the problem.
+\subsection{Nature of ground state near the critical point}
+
+We can obtain more insight on the change in the ground state as the system moves towards the transition by tracking its overlap with the singlet state \(\ket{\text{ss}} \equiv \ket{\Psi}_\text{gs}^\text{sc}\) and the entangled state among the charge isospin triplets, \(\ket{\text{ct}} \equiv \frac{1}{\sqrt 2}\left(\ket{\uparrow_d \downarrow_d,0} + \ket{0,\uparrow_0 \downarrow_0}\right)\).
+The ground state \(\ket{\Psi}_\text{gs}\)is obtained by numerically solving the fixed point Hamiltonian for various bare values of the couplings.
+The overlaps are shown in Fig.~\ref{overlaps}, and we see a continuous increase in the charge content at the cost of the spin content as \(r\) approaches the critical value \(r_c = 0.25\).
+The spin and charge overlaps approach equality towards the transition, leading to an {\it extra emergent symmetry of spin-charge interchange} at the critical point.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/J_bandwidth.pdf}
-	% \caption{../figures/J_bandwidth.pdf}
-	% \label{fig:-figures-J_bandwidth-pdf}
-\end{figure}
-The fixed point Hamiltonian can, in general, be written as
-\begin{equation}\begin{aligned}
-	\mathcal{H}^* = \sum_{\sigma, k}\epsilon_k \tau_{k\sigma} - \frac{U^*}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2  + \sum_{\sigma, k < \Lambda^*}\left( V^* c^\dagger_{k\sigma}c_{d\sigma} + \text{h.c.} \right) + J^* \vec{S_d}\cdot\vec{s}
-\end{aligned}\end{equation}
-The first term is the kinetic energy of all the electrons.
-The next two terms are the impurity-diagonal pieces, featuring the renormalised interaction \(U^*\).
-The next three terms are the residual interactions between the impurity and the metal, with the renormalised couplings \(V^*, J^*\) and \(K^*\).
-The summations in these terms extend from the fixed point momentum cutoff \(\Lambda^*\) to 0.
-This is the region of momentum space  which the URG was unable to decouple.
-The operators \(\vec s\) and \(\vec C\) represent the macroscopic magnetic and charge spins formed by the remaining electrons that are lying inside the window \(\left[ 0, \Lambda^* \right] \):
-\begin{equation}\begin{aligned}
-	\vec s = \sum_{kk^\prime<\Lambda^*\atop{\alpha\beta}} c^\dagger_{k\alpha}\vec \sigma_{\alpha\beta}c_{k^\prime\beta}
-\end{aligned}\end{equation}
-Our goal here is to write down the ground state wavefunction for this low-energy Hamiltonian.
-
-To make progress, we will simplify the effective Hamiltonian by taking the zero bandwidth limit.
-This reduces it to a two-site problem.
-One site is of course the impurity site, and this site will be labeled as site 1.
-The other site will be formed by the center of mass degree of freedom of the conduction electrons, and will be labeled as site 2.
-The Hamiltonian for this two-site problem is
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{IR} = - \frac{U^*}{2}\left(\hat n_{1 \uparrow} - \hat n_{1 \downarrow}\right)^2 + V^*\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.} \right) + J^*\vec{S_1}\cdot\vec{S_2} + K^* \vec{C_1}\cdot\vec{C_2}
-\end{aligned}\end{equation}
-
-The subscripts on the operators designate the site on which they act; \(\hat n_1\) is the number operator for the first site.
-
-We will adopt the following notation to represent the states in this Hilbert space.
-A general state will be represented in the Fock space basis as \(\ket{n_{1 \uparrow}n_{1 \downarrow}n_{2 \uparrow}n_{2 \downarrow}}\).
-For example,
-\begin{equation}\begin{aligned}
-	\ket{1101} = c^\dagger_{1 \uparrow}c^\dagger_{1 \downarrow}c^\dagger_{2 \downarrow}\ket{-}
-\end{aligned}\end{equation}
-\(\ket{-}\) is the vacuum state.
-
-For \(U>0\), the ground state is given by
-\begin{gather}
-	\label{gstate}
-	\ket{\Psi}_\text{1} = c_s \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c_c \frac{1}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right), \quad E_1 =  -V^*\sqrt{\gamma^2 + 4} -\frac{1}{4}U^* - \frac{3}{8}{J^*}
-\end{gather}
-where $\gamma = \frac{1}{2{V^*}}\left[ \frac{1}{4}\left( 3J^* + K^* \right) + \frac{1}{2}U^* \right]$. The probabilities for the spin and charge sectors for the ground state are
-\begin{equation}\begin{aligned}
-	\label{coeff_def}
-	\left(c_s\right)^2 = \frac{1}{2\sqrt{\gamma^2 + 4}}\left(\sqrt{\gamma^2 + 4} + \gamma\right),\\
-	\left(c_c \right)^2 = \frac{1}{2\sqrt{\gamma^2 + 4}}\left(\sqrt{\gamma^2 + 4} - \gamma\right)~.
-\end{aligned}\end{equation}
-For (roughly) \(J_0 > V_0\), we get \(J^* \gg V^*\) and \(U^* \gg U_0\) so that \(\gamma \gg 1\).
-This gives \(\left( c_s \right) ^2 \sim 1\) and \(\left( c_c \right) ^2 \sim 0\).
-The entire contribution to the ground state then comes from the spin sectors of the two sites.
-This is calculated numerically in fig.~\ref{cs_cc}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/coeffs_vs_J.pdf}
-	\caption{Variation of relative weights \(c_s\) and \(c_c\) with \(J_0\)}
-	\label{cs_cc}
+\includegraphics[width=0.5\textwidth]{../figures/corrs_gs.pdf}
+\caption{Overlap of the RG fixed point ground state \(\ket{\Psi}_\text{gs}\) with the spin singlet state \(\ket{\text{ss}}\) and the charge triplet state \(\ket{\text{ct}}\), for a range of values of the transition tuning ratio \(r\).
+Beyond the critical point \(r > 0.25\), both these overlaps vanish.}
+	\label{overlaps}
 \end{figure}
 
-In the other regime of \(U<0\), the two competing states are \(\ket{\Psi}_1\) defined above (with energy \(E_1\)), and \(\ket{\Psi_2}\), the charge singlet: \(\ket{\Psi}_2 = \frac{1}{\sqrt 2}\left( \ket{2,0} - \ket{0,2} \right)\) having energy \(E_2\).
-\begin{equation}\begin{aligned}
-	E_2 = -\frac{3}{4}K^*, \quad E_1 - E_2 = -\frac{1}{4}\sqrt{\left( \frac{1}{2}K^* + U^* \right)^2 + (4V^*)^2} - \frac{1}{4}U^* + \frac{3}{4}K^*
-\end{aligned}\end{equation}
-For \(V_0 \gg K_0\), the largest energy scale will be \(V^*\), and we can then approximate this difference as
-\begin{equation}\begin{aligned}
-	E_1 - E_2 \simeq -V^* < 0
-\end{aligned}\end{equation}
-In such a case, \(\ket{\Psi}_1\) will therefore be the ground state. In the other regime \(V_0 \ll K_0\), the largest energy scale will be \(K^*\), and we can then write
-\begin{equation}\begin{aligned}
-	E_1 - E_2 \simeq - \frac{1}{8}K^* + \frac{3}{4}K^* > 0
-\end{aligned}\end{equation}
-In this case, the ground state will be \(\ket{\Psi}_2\).
-There exists, therefore, a phase transition at a critical plane \((U_c, K_c, V_c)\), where the ground state changes between the charge singlet \(\ket{\Psi}_2\) and the spin singlet + charge triplet \(\ket{\Psi}_1\).
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/E1_vs_E3.pdf}
-\end{figure}
+\section{Descriptors of the transition}
 
-\subsection{Unscreened regime: \(-U_b/J > 1/4 \)}
+In this section, we will discuss various diagnostics that track the impurity phase transition; these diagnostics or probes will also answer other interesting questions:
+\begin{itemize}
+	\item[1.] What are the fluctuations that force the transition?
+	\item[2.] How do entanglement measures behave across the transition?
+	\item[3.] How does the Kondo screening cloud~\cite{}[CITE] respond as the system is driven critical?
+\end{itemize}
 
-\subsection{Approach towards the thermodynamic limit}
+\subsection{Impurity spectral function}
 
-{\bf \Large [Update with V vs D plots]}
+One of the most obvious indicators of the transition is the appearance of a gap in the spectral function \(A_d(\omega)\) of the impurity.
+In the AIM, the spectral function \(A_d\) has a single peak structure for small \(U\), and two additional side peaks appear at large \(U\).
+Although the central peak keeps getting sharper as \(U\) is increased, it never disappears, simply because the impurity is always able to bind with the zeroth site and form a single site; indeed, it is the local Fermi liquid excitations that appear on top of this singlet ground state that gives rise to the central Abrikosov-Suhl resonance in the spectral function~\cite{}[lots of CITE here].
 
-The URG method works strictly on finite systems and leads to finite values of fixed point couplings.
-The behaviour of the Hamiltonian in the thermodynamic limit can then be determined using finite-size scaling where we increase the bandwidth and decrease the width of each RG step.
-When applied to the fixed point value of the impurity-bath hybridisation parameter \(V\) (fig.~\ref{V_vs_D}), it can be seen that the fixed point value increases as the system size is increased, implying that the continuum limit of \(V^*\) is \(\infty\).
-This holds for both \(V_0 > J_0\) and \(V_0 < J_0\), as shown in the two panels of fig.~\ref{V_vs_D}.
+In contrast, the GAIM shows the appearance of a gap as \(r\) crosses \(1/4\) (see Fig.~\ref{spec-func}); the three-peak form survives only up to the critical point.
+The spectral functions are calculated by numerically diagonalising the effective Hamiltonian obtained from the RG.
+In the unscreened regime \(r > 0.25\), the impurity spectral function has a two peaks at energies \(\omega = \pm U/2\) corresponding to the fluctuations that create a particle or a hole on the impurity site.
+The appearance of the gap shows that exactly at \(r=0.25\), the zero-energy pole in the impurity Greens function \(G_d(\omega)\) gets replaced by a zero; this is accompanied by a zero energy divergence in the impurity self-energy \(\Sigma_d = 1/G_d^{(0)}(\omega) - 1/G_d(\omega)\).
+The expression of the self-energy follows from Dyson's equation, \(G_d^{(0)}(\omega)\) being the self-energy of the impurity at \(U=0\).
 
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{../figures/Vstar_vs_D_smallV.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/Vstar_vs_D_largeV.pdf}
-	\caption{Variation of fixed point value \(V^*\) with increasing bandwith \(D_0\), for both \(V_0 > J_0\) and \(V_0 < J_0\).}
-	\label{V_vs_D}
+	\includegraphics[width=0.5\textwidth]{../figures/Add.pdf}
+	\caption{Impurity spectral function \(A_d(\omega)\) at three values of the ratio \(r\).
+The central large plot is exactly at the critical point \(r=0.25\), the left (blue) inset is at \(r < 0.25\) and the right (violet) inset is at \(r > 0.25\).}
+	\label{spec-func}
 \end{figure}
 
-In a similar manner, we checked the variation of the spin and charge probabilities, \(c_s\) and \(c_c\), in the ground state, with increasing bandwith. The result is shown in fig.~\ref{c_vs_D}.
-\begin{figure}[!htb]
+\subsection{Using geometric entanglement to track the transition}
+
+The impurity Greens function can be given a spectral representation in terms of the eigenstates \(\left\{\ket{\Psi}_n\right\}\) of the GAIM:
+\begin{equation}\begin{aligned}
+G_d(\omega) = \sum_n \left[ \frac{|\braket{\Psi_\text{gs} | c_{d\sigma} | \Psi_n}|^2}{\omega + E_\text{gs} - E_n} + \frac{|\braket{\Psi_n | c_{d\sigma} | \Psi_\text{gs}}|^2}{\omega - E_\text{gs} + E_n}\right]
+\end{aligned}\end{equation}
+We will now introduce a complete basis into the expression.
+The basis will be the set of eigenstates of the Hamiltonian  \(H = H_1 + H_2\), where \(H_1\) is the two-site Hamiltonian in eq.~\ref{two-site}, and \(H_2\) is a tight-binding Hamiltonian formed by the remaining sites.
+Since the Hamiltonians are decoupled, the eigenstates \(\ket{\Psi}_{m,n}\) will be direct product states formed by combining the eigenstates \(\ket{\phi}_m,\ket{\psi}_n\) of the individual Hamiltonians \(H_1\) and \(H_2\) respectively: \(\ket{\Phi}_{m,n} = \ket{\phi}_m\otimes\ket{\psi}_n\).
+Inserting this basis leads to the expression:
+\begin{equation}\begin{aligned}
+	\label{summation}
+	\ket{\Psi}_\text{gs} = \sum_{m,n} \ket{\Phi}_{m,n} \left(\bra{\phi_{m}}\otimes\bra{\psi_n}\right)\ket{\Psi_\text{gs}}
+\end{aligned}\end{equation}
+The ground state of \(H_1\) is the spin singlet: \(\ket{\phi}_0 = \ket{\text{ss}}\).
+We denote the ground state of the tight-binding Hamiltonian \(H_2\) by \(\ket{\psi}_0\).
+Because of the highly renormalised couplings \(V\) and \(J\), the impurity site is almost maximally entangled with the zeroth site, such that the ground state \(\ket{\Psi}_\text{gs}\) in the \(r < 0.25\) regime can be thought of as a direct product of the two-site ground state, \(c\ket{\text{ss}} + \sqrt{1-c^2}\ket{\text{ct}}\), in direct product with the tight-binding ground state:
+\begin{equation}\begin{aligned}
+	\ket{\Psi}_\text{gs} \simeq \left(c\ket{\text{ss}} + \sqrt{1-c^2}\ket{\text{ct}}\right)  \otimes \ket{\psi}_0 = \ket{\Phi}_\text{ss} + \ket{\Phi}_\text{ct}
+\end{aligned}\end{equation}
+where \(\ket{\Phi}_\text{ss(ct)} = \ket{\text{ss}\left( \text{ct} \right)}\otimes\ket{\psi}_0 \).
+This suggests that not all terms in the summation of eq.~\ref{summation} contribute; out of all \(\left\{ \ket{\psi}_n \right\} \), only the ground state \(n=0\) contributes, while only \(\ket{ss}\) and \(\ket{ct}\) contribute from the set \(\left\{ \ket{\phi}_m \right\} \).
+The summation then simplifies to
+\begin{equation}\begin{aligned}
+	\ket{\Psi}_\text{gs} = \ket{\Phi}_{ss}\braket{\text{ss}|\Psi^{(2)}_\text{gs}} + \ket{\Phi}_{ct}\braket{\text{ct}|\Psi^{(2)}_\text{gs}}~,
+\end{aligned}\end{equation}
+where \(\ket{\Psi^{(2)}_\text{gs}}\) is the two-site part of the ground state and can be obtained by starting with the full ground state \(\ket{\Psi}_\text{gs}\) and tracing over the other lattice sites of the system.
+
+{\color{blue}We assume that the global phase of the wavefunctions are real}, and since the internal weights of the wavefunctions are real as well, the overlaps \(\braket{\text{ss}|\Psi^{(2)}_\text{gs}},\braket{\text{ct}|\Psi^{(2)}_\text{gs}}\) are also real.
+We can use these overlaps to define a geometric measure of entanglement:
+\begin{equation}\begin{aligned}
+	\varepsilon\left(\psi_1,\psi_2\right) = 1 - |\braket{\psi_1 | \psi_2}|^2
+\end{aligned}\end{equation}
+[CITE]
+If \(\ket{\psi_1}\) is thought of as a separable state, then \(\ket{\psi_2}\) should be less entangled if it's overlap with \(\ket{\psi_1}\) is large, which is indeed borne out by the definition.
+The overlaps then become \(\braket{\text{ss}|\Psi^{(2)}_\text{gs}} = \sqrt{1 - \varepsilon\left(ss,\Psi^{(2)}_\text{gs}\right)}\), and similarly for the state \(\ket{\text{ct}}\).
+For brevity, we will use the notation \(\varepsilon_\text{ss} \equiv \varepsilon\left(ss,\Psi^{(2)}_\text{gs}\right), \varepsilon_\text{ct} \equiv \varepsilon\left(ct,\Psi^{(2)}_\text{gs}\right)\).
+The Greens function can now be written in terms of these measures:
+\begin{widetext}
+\begin{equation}\begin{aligned}
+	G_d(\omega) = \sum_n \left[\left(1 - \varepsilon_\text{ss} \right) \left(\frac{|\braket{\Phi_\text{ss} | c_{d\sigma} | \Psi_n}|^2}{\omega + E_\text{gs} - E_n} + \frac{|\braket{\Psi_n | c_{d\sigma} | \Phi_\text{ss}}|^2}{\omega - E_\text{gs} + E_n}\right) + \left(1 - \varepsilon_\text{ct} \right) \left(\frac{|\braket{\Phi_\text{ct} | c_{d\sigma} | \Psi_n}|^2}{\omega + E_\text{gs} - E_n} + \frac{|\braket{\Psi_n | c_{d\sigma} | \Phi_\text{ct}}|^2}{\omega - E_\text{gs} + E_n}\right)\right.\\
+	+ \left.
+\sqrt{\left(1 - \varepsilon_\text{ss} \right)}\sqrt{\left(1 - \varepsilon_\text{ct} \right)} \left(\frac{\braket{\Phi_\text{ss} | c_{d\sigma} | \Psi_n}\braket{\Psi_n | c^\dagger_{d\sigma} | \Phi_\text{ct}} + \text{h.c.}}{\omega + E_\text{gs} - E_n} + \frac{\braket{\Phi_\text{ct} | c_{d\sigma} | \Psi_n}\braket{\Psi_n | c^\dagger_{d\sigma} | \Phi_\text{ss}} + \text{h.c.}}{\omega - E_\text{gs} + E_n}\right)\right]
+\end{aligned}\end{equation}
+\end{widetext}
+
+\begin{figure}[htpb]
 	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/coeffs_vs_D.pdf}
-	\caption{Variation of spin and charge fractions, \(c_s\) and \(c_c\), of the ground state, as a function of bare bandwidth \(D_0\).
-Left and right panels show the cases of \(J_0 < V_0\) and \(J_0 > V_0\) respectively.}
-	\label{c_vs_D}
+	\includegraphics[width=0.5\textwidth]{../figures/entanglement.pdf}
+	\caption{Variation of \(\sqrt{\left(1 - \varepsilon_\text{ss} \right)}\sqrt{\left(1 - \varepsilon_\text{ct} \right)}\) as \(r\) is increased towards the critical value 0.25.
+Inset shows the variation of the individual measures \(\varepsilon_\text{ss},\varepsilon_\text{ct}\).}
+	\label{entng}
 \end{figure}
-For both \(V_0 < J_0\) and \(V_0 > J_0\), we see that the spin contribution increases towards unity while the charge contribution vanishes.
-This indicates that at large bandwidth, the ground state becomes purely a spin singlet, formed purely by singly-occupied impurity states.
-\begin{equation}\begin{aligned}
-	\label{gstate_kondo}
-	\lim_{D_0 \to \infty} \ket{\Psi}_1 = \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) 
-\end{aligned}\end{equation}
 
-\subsection{The critical point: \(-U_b/J = 1/4 \)}
-
-\section{Evolution of the groundstate across the transition}
-
-\subsection*{Overlap of ground state against spin singlet and charge triplet zero states}
-
-\begin{figure}
-	\includegraphics[width=0.5\textwidth]{../figures/overlaps_gs-J=10.000.pdf}\\
-	\includegraphics[width=0.5\textwidth]{../figures/corrs_gs-J=10.000.pdf}
-\end{figure}
+This expression is interesting because it relates the Greens function (measurable when converted into a spectral function) to measures of entanglement.
+These measures have been plotted up to the critical point in Fig.~\ref{entng}.
+While \(\varepsilon_\text{ss},\varepsilon_\text{ct}\) (plotted in the inset) are very similar to the overlaps plotted in Fig.~\ref{overlaps}, the cross-term \(\sqrt{\left(1 - \varepsilon_\text{ss} \right)}\sqrt{\left(1 - \varepsilon_\text{ct} \right)}\) plotted in the main figure has an overall monotonic incremental behaviour towards the transition.
+We can now use the knowledge of the behaviour of these measures to make some statements about the nature of the transition from the Greens function.
+Since \(\varepsilon_\text{ss}\) increases towards the transition, we find that the first major term in the Greens function decreases; this shows that scattering within the spin sector loses weight.
+On the other hand, since \(\varepsilon_\text{ct}\) decreases, the second major term in \(G_d\) increases, reflecting the growth in the participation of the charge sector in the scattering processes.
+The final major term also increases, due to the monotonic growth of \(\sqrt{\left(1 - \varepsilon_\text{ss} \right)}\sqrt{\left(1 - \varepsilon_\text{ct} \right)}\), showing that there is a continual increase in the {\it mixing of the spin and charge sectors}.
 
@@
 \begin{figure}
-	\includegraphics[width=0.4\textwidth]{../figures/odlro-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
+	\includegraphics[width=0.49\textwidth]{../figures/odlro.pdf}
 	\caption{Growth of pair fluctuations \(p^\dagger_d p_0\) between the impurity and the zeroth site towards the critical point, \(p^\dagger=c^\dagger_\uparrow c^\dagger_\downarrow\) being the local pair creation operator.
-This comes at the cost of the spin-flip fluctuations \(S_d^+ s_0^- + \text{h.c.}\).
-which decrease towards the transition.}
+This comes at the cost of the spin-flip fluctuations \(S_d^+ s_0^- + \text{h.c.}\), which decrease towards the transition.}
 	\label{pair_fluc}
@@
 
-The behaviour of the various kinds of correlation functions (for eg., the reduction of the impurity compensation \(\vec{S}_d\cdot\vec{s}_0\)) shown above indicate that the Kondo cloud that screens the impurity is getting destroyed as \(U_b/J\) increases in magnitude.
-To shed some light on the nature of the fluctuations that faciliate this process, we also plot the average pair fluctuation in the ground state as a function of \(U_b/J\), in fig.~\ref{pair_fluc}.
-The pair fluctuations are terms that transfer an electron pair between the impurity and zeroth sites: \(c^\dagger_{d \uparrow}c^\dagger_{d \downarrow} c_{0 \downarrow}c_{0 \uparrow}\).
-It can be seen from the figure that while the spin-flip fluctuations decrease (since the Kondo cloud is formed out of these spin-flip fluctuations, this is consistent with the destruction of the Kondo cloud discussed in this paragraph), the pair fluctuations pick up.
-Since the spin subspace and charge subspace cannot coincide on the same site, we can then conclude that it is the growth of these pair fluctuations brought about by the presence of the purely local interaction \(U_b\) that make the screening of the impurity spin very poor.
+\subsection{Mutual information and entanglement entropy in the ground state: fate of the Kondo cloud}
+Since the system has to undergo a phase transition into an unscreened phase for \(r > 0.25\), it is clear that the Kondo screening cloud must disappear.
+Indeed, this is captured by various entanglement measures like mutual information and entanglement entropy.
+The entanglement entropy of subsystem \(A\) with the rest is defined as
+\begin{equation}\begin{aligned}
+	S(A) = \text{Tr}\left[\rho_A \ln \rho_A\right]
+\end{aligned}\end{equation}
+where \(\rho_A\) is the reduced density matrix obtained by tracing the full density matrix \(\rho = \ket{\Psi}_\text{gs} \bra{\Psi}_\text{gs}\) over all subsystems apart from \(A\).
+The mutual information between two subsystems \(A\) and \(B\) is defined as
+\begin{equation}\begin{aligned}
+	I(A:B) = S(A) + S(B) - S(A \cup B)
+\end{aligned}\end{equation}
+where \(S(A \cup B)\) is the entanglement entropy of \(A\) and \(B\) with the rest.
+I(A:B) represents the amount of information that can be gained about \(B\) on measuring \(A\), or vice-versa.
+If the ground state \(\ket{\Psi}_\text{gs}\) is a separable state where \(A\) is a disentangled from the rest, then its entanglement entropy \(S(A)\) will be \(0\).
+On the other hand, if the ground state cannot be written in separable form, \(S(A)\) becomes non-zero, and the maximum value it can take is \(\ln d\), where \(d\) is the dimension of the Hilbert space of \(A\).
 
-\subsection*{Correlations in ground state}
-\begin{figure*}
-	\includegraphics[width=0.45\textwidth]{../figures/corr-k-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/mi-dk-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/mi-01-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/mi-d0-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/EE-d-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-\end{figure*}
+In the AIM or the Kondo model ground state, the impurity forms a maximally entangled singlet with the zeroth site.
+This in turn leads to entanglement in \(k-\)space between the conduction electrons that screen the impurity and form the Kondo cloud~\cite{anirban_kondo}.
 
-\subsection{Impurity spectral function \(A_{dd}(\omega)\)}
-These are the frequency-domain spectral functions for the retarded propagator \(-i\theta(t)\left<\left\{c_{d\sigma}(t),c^\dagger_{d\sigma}\right\}  \right>\):
-\begin{center}
-	\includegraphics[width=0.2\textwidth]{../figures/spec_func_Ub_by_J=-0.100.pdf}
-	\includegraphics[width=0.2\textwidth]{../figures/spec_func_Ub_by_J=-0.250.pdf}
-	\includegraphics[width=0.2\textwidth]{../figures/spec_func_Ub_by_J=-0.26.pdf}
-\end{center}
+\begin{figure}[!htb]
+\includegraphics[width=0.49\textwidth]{../figures/I_k.pdf}
+\caption{caption}
+\end{figure}
+\begin{figure}[!htb]
+\includegraphics[width=0.49\textwidth]{../figures/I_r.pdf}
+\caption{caption}
+\end{figure}
+\begin{figure}[!htb]
+\includegraphics[width=0.49\textwidth]{../figures/S_imp.pdf}
+\caption{caption}
+\end{figure}
 
 \section{Conclusions}
+CC
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
 

### 2022-05-02 gen-siam-manuscript/gen-siam.tex
only pair fluctuation text is left

@@
-\documentclass[reprint,prb,superscriptaddress]{revtex4-2}
+\documentclass[reprint,superscriptaddress,floatfix]{revtex4-2}
 \usepackage{braket,amsmath,graphicx,color}
@@
 
+\subsection{Presence of sub-dominant pair fluctuations}
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.49\textwidth]{../figures/odlro.pdf}
+	\caption{Growth of pair fluctuations \(p^\dagger_d p_0\) between the impurity and the zeroth site towards the critical point, \(p^\dagger=c^\dagger_\uparrow c^\dagger_\downarrow\) being the local pair creation operator.
+This comes at the cost of the spin-flip fluctuations \(S_d^+ s_0^- + \text{h.c.}\), which decrease towards the transition.}
+	\label{pair_fluc}
+\end{figure}
+
 \section{Low-energy effective Hamiltonian and the ground state}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/zeromode_eff.pdf}
+	\includegraphics[width=0.4\textwidth]{../figures/zeromode_eff.pdf}
 	\caption{Two site Hamiltonian obtained by taking the zero bandwidth limit of the effective Hamiltonian in the screened regime.}
@@
 
-In this section, we will discuss various diagnostics that track the impurity phase transition; these diagnostics or probes will also answer other interesting questions:
+In this section, we will discuss various diagnostics that track the impurity phase transition; these diagnostics or probes will answer several interesting questions:
 \begin{itemize}
-	\item[1.] What are the fluctuations that force the transition?
+	\item[1.] How is spectral weight transferred across energy scales, as the system undergoes the transition?
 	\item[2.] How do entanglement measures behave across the transition?
@@
 
-\subsection{Presence of sub-dominant pair fluctuations}
-
-\begin{figure}
-	\includegraphics[width=0.49\textwidth]{../figures/odlro.pdf}
-	\caption{Growth of pair fluctuations \(p^\dagger_d p_0\) between the impurity and the zeroth site towards the critical point, \(p^\dagger=c^\dagger_\uparrow c^\dagger_\downarrow\) being the local pair creation operator.
-This comes at the cost of the spin-flip fluctuations \(S_d^+ s_0^- + \text{h.c.}\), which decrease towards the transition.}
-	\label{pair_fluc}
-\end{figure}
-
 \subsection{Mutual information and entanglement entropy in the ground state: fate of the Kondo cloud}
@@
 Indeed, this is captured by various entanglement measures like mutual information and entanglement entropy.
-The entanglement entropy of subsystem \(A\) with the rest is defined as
+The entanglement entropy \(S(A)\) of subsystem \(A\) with the rest of the system is defined as the von Neumann entropy of the reduced density matrix \(\rho_A\),
 \begin{equation}\begin{aligned}
-	S(A) = \text{Tr}\left[\rho_A \ln \rho_A\right]
+	S(A) = -\text{Tr}\left[\rho_A \ln \rho_A\right]~,
 \end{aligned}\end{equation}
-where \(\rho_A\) is the reduced density matrix obtained by tracing the full density matrix \(\rho = \ket{\Psi}_\text{gs} \bra{\Psi}_\text{gs}\) over all subsystems apart from \(A\).
-The mutual information between two subsystems \(A\) and \(B\) is defined as
+where \(\rho_A\) is obtained by tracing the full density matrix \(\rho = \ket{\Psi}_\text{gs} \bra{\Psi}_\text{gs}\) over all subsystems apart from \(A\).
+The mutual information between two subsystems \(A\) and \(B\) is then defined using this entanglement entropy:
 \begin{equation}\begin{aligned}
-	I(A:B) = S(A) + S(B) - S(A \cup B)
+	I(A:B) = S(A) + S(B) - S(A \cup B)~,
 \end{aligned}\end{equation}
 where \(S(A \cup B)\) is the entanglement entropy of \(A\) and \(B\) with the rest.
-I(A:B) represents the amount of information that can be gained about \(B\) on measuring \(A\), or vice-versa.
+\(I(A:B)\) represents the amount of information obtained about \(B\) on measuring \(A\), or vice-versa.
 If the ground state \(\ket{\Psi}_\text{gs}\) is a separable state where \(A\) is a disentangled from the rest, then its entanglement entropy \(S(A)\) will be \(0\).
@@
 
-In the AIM or the Kondo model ground state, the impurity forms a maximally entangled singlet with the zeroth site.
+In the AIM or the Kondo model ground state, the impurity forms a maximally entangled singlet with the zeroth site~\cite{wilson1975,hewson1993,hrk_wilson_1980}.
 This in turn leads to entanglement in \(k-\)space between the conduction electrons that screen the impurity and form the Kondo cloud~\cite{anirban_kondo}.
+These features change once we turn on the attractive correlation \(U_b\) and drive the system across the transition, as plotted in Figs.~\ref{mut_inf_k} and \ref{mut_inf_r}.
+The \(k-\)space mutual information \(I(\vec k_1:\vec k_2)\) between two distinct \(k-\)states plotted in the red curve of Fig.~\ref{mut_inf_k} is essentially the entanglement within the Kondo cloud, and we find that this entanglement decreases towards the transition, signalling the weakening of the Kondo cloud.
+This is also supported by the reduction in the mutual information \(I(d \uparrow: \vec k \downarrow)\) between the impurity and \(k-\)space states plotted along the blue curve in the same figure.
+Beyond the transition, \(I(d \uparrow: \vec k \downarrow)\) drops to zero, because the impurity is no longer coupled to the bath, while \(I(\vec k_1:\vec k_2)\) takes on a larger value because they are connected by the \(U_b-\)term and are no longer sharing entanglement with the impurtiy.
 
@@
 \includegraphics[width=0.49\textwidth]{../figures/I_k.pdf}
-\caption{caption}
+\caption{Mutual information in \(k-\)space, across the transition.
+Red curve is the mutual information between two distinct \(k-\) states inside the Kondo cloud.
+Blue curve is the mutual information between a \(k-\)state and the impurity state of opposite spin.}
+\label{mut_inf_k}
 \end{figure}
+
 \begin{figure}[!htb]
 \includegraphics[width=0.49\textwidth]{../figures/I_r.pdf}
-\caption{caption}
-\end{figure}
-\begin{figure}[!htb]
-\includegraphics[width=0.49\textwidth]{../figures/S_imp.pdf}
-\caption{caption}
+\caption{Mutual information in \(r-\)space, across the transition.
+Red curve is the mutual information between the zeroth site and the site next to it.
+Blue curve is the mutual information between a \(k-\)state and the impurity state of opposite spin.
+The former is zero before the transition because the zeroth site is locked in a singlet with the impurity, and becomes zero after  the transition because the singlet has now decoupled and the zeroth site is free to entangle with the other sites.}
+\label{mut_inf_r}
 \end{figure}

### 2022-05-03 gen-siam-manuscript/gen-siam.tex
completed work sections and appendix

@@
 \affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, W.B. 741246, India}
+\author{N. S. Vidhyadhiraja}
+\email{raja@jncasr.ac.in}
+\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
+\author{A. Taraphder}
+\email{arghya@phy.iitkgp.ernet.in}
+\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
 \author{Siddhartha Lal}
@@
 \begin{itemize}
-	\item a spin-exchange term \(J \vec{S}_d\cdot\vec{s}_0\) between the impurity spin \(\vec S_d\) and the spin \(\vec s_0\) of the zeroth site 
+	\item a spin-exchange term \(J \vec{S}_d\cdot\vec{S}_0\) between the impurity spin \(\vec S_d\) and the spin \(\vec S_0\) of the zeroth site 
 	\item a local particle-hole symmetric correlation term \(-U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}\) on the zeroth site
@@
 	\label{GIAM-ham}
-	\mathcal{H} = -\frac{1}{2}U \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\vec k,\sigma} \epsilon_{\vec k} \tau_{\vec k,\sigma} + J \vec{S}_d\cdot\vec{s}_0 \\
+	\mathcal{H} = -\frac{1}{2}U \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\vec k,\sigma} \epsilon_{\vec k} \tau_{\vec k,\sigma} + J \vec{S}_d\cdot\vec{S}_0 \\
 	+ V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}
@@
 
-\subsection{Presence of sub-dominant pair fluctuations}
+\subsection{Growth of charge isospin fluctuations in the bath}
+The low-energy phase of the AIM is characterised by enhanced spin-fluctuation \(\left<S_d^+S_0^- + \text{h.c.}\right>\); these fluctuations arise from the Kondo cloud and they serve to screen the local moment.
+For the system to undergo a transition into an unscreened regime, these fluctuations must get replaced by those of a different kind.
+This is shown in Fig.~\ref{pair_fluc}, where we plot not only the spin fluctuations mentioned, but also two-particle charge fluctuations \(\left<c^\dagger_{\vec k \uparrow} c^\dagger_{\vec k \downarrow} c_{\vec k^\prime \uparrow} c_{\vec k^\prime \downarrow}\right>\) in the bath that transfer holons and doublons across \(k-\)states.
+We find that while the former decrease towards the transition, the latter pick up; the spin-fluctuations are getting replaced by the charge fluctuations.
+This is substantied by the inset of the same figure, which shows the behaviour of these fluctuations even after the transition.
+While the spin-fluctuations vanish beyond the transition, the charge fluctuations undergo an abrupt increase.
 
@@
 	\includegraphics[width=0.49\textwidth]{../figures/odlro.pdf}
-	\caption{Growth of pair fluctuations \(p^\dagger_d p_0\) between the impurity and the zeroth site towards the critical point, \(p^\dagger=c^\dagger_\uparrow c^\dagger_\downarrow\) being the local pair creation operator.
-This comes at the cost of the spin-flip fluctuations \(S_d^+ s_0^- + \text{h.c.}\), which decrease towards the transition.}
+	\caption{Growth in the pair-fluctuation terms \(c^\dagger_{k \uparrow}c^\dagger_{k \downarrow} c_{k^\prime \downarrow}c_{k^\prime \uparrow}\), as \(r \to 0.25\).
+This comes at the cost of the spin-flip fluctuations \(S_d^+ S_0^- + \text{h.c.}\), which decrease towards the transition.
+The inset plots the same quantities but for a larger range of \(r\), and the pair fluctuations are seen to pick up abruplty after the transition while the spin fluctuations vanish.}
 	\label{pair_fluc}
@@
 	\mathcal{H}^* = -\frac{1}{2}U^*\left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma} - U_b^* \hat n_{0 \uparrow} \hat n_{0 \downarrow} \\
-	+ V^*\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + J^* \vec{S}_d\cdot\vec{s}_0
+	+ V^*\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + J^* \vec{S}_d\cdot\vec{S}_0
 \end{aligned}\end{equation}
@@
 \begin{equation}
-	H_\text{eff}^\text{sc} = J^* \vec{S}_d\cdot\vec{s}_0 - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow} + \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma}
+	H_\text{eff}^\text{sc} = J^* \vec{S}_d\cdot\vec{S}_0 - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow} + \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma}
 \end{equation}
@@
 	\label{two-site}
-	H_\text{eff}^\text{sc} \sim J^* \vec{S}_d\cdot\vec{s}_0 - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}
+	H_\text{eff}^\text{sc} \sim J^* \vec{S}_d\cdot\vec{S}_0 - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}
 \end{equation}
@@
 \end{figure}
-This model is easily solved and the ground state is a maximally-entangled spin singlet formed by \(\vec S_d\) and \(\vec s_0\); the ground state energy is \(E_\text{gs}^\text{sc} = -\frac{3}{4}J^* - U_b\):
+This model is easily solved and the ground state is a maximally-entangled spin singlet formed by \(\vec S_d\) and \(\vec S_0\); the ground state energy is \(E_\text{gs}^\text{sc} = -\frac{3}{4}J^* - U_b\):
 \begin{equation}\begin{aligned}
@@
 \begin{equation}\begin{aligned}
-	H_\text{eff}^\text{crit} = \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma} - U_b^* \hat n_{0 \uparrow} \hat n_{0 \downarrow} + J^* \vec{S}_d\cdot\vec{s}_0\\
+	H_\text{eff}^\text{crit} = \sum_{\sigma,\vec k:|\epsilon_{\vec k}| < D^*} \epsilon_{\vec k} \tau_{\vec k,\sigma} - U_b^* \hat n_{0 \uparrow} \hat n_{0 \downarrow} + J^* \vec{S}_d\cdot\vec{S}_0\\
 	+ V^*\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) 
@@
 
-\section{Conclusions}
+\section{Discussions and Outlook}
 CC
@@
 
+\bibliography{gen-siam}
+
 \appendix*
@@
 
-\subsection{Renormalisation of the impurity energy \(\epsilon_d\)}
-The coupling \(\epsilon_d\) is renormalised by three kinds of vertices: \(V^2\), \(J^2\) and \(K^2\).
-We will consider these processes one after another.
+\subsection{Some preliminaries}
+The Hamiltonian we are working with is the generalised Anderson impurity model (Eq.~\ref{GIAM-ham}):
+\begin{equation}\begin{aligned}
+	\mathcal{H} = -\frac{1}{2}U \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\vec k,\sigma} \epsilon_{\vec k} \tau_{\vec k,\sigma} + J \sum_{\vec k,\vec k^\prime,\atop{\alpha,\beta}}\vec{S}_d\cdot\vec{\sigma}_{\alpha\beta}c^\dagger_{\vec k,\alpha}c_{\vec k^\prime,\beta} + V\sum_{\vec k,\sigma} \left( c^\dagger_{d\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) - U_b \sum_{\vec k,\vec k^\prime,\sigma}c^\dagger_{\vec k,\sigma}c_{\vec k^\prime,\sigma} \\
++ U_b \sum_{\vec k_1,\vec k_2,\atop{\vec k_3,\vec k_4}}c^\dagger_{\vec k_1 \uparrow} c_{\vec k_2 \uparrow} c^\dagger_{\vec k_3 \downarrow} c_{\vec k_4 \downarrow}
+\end{aligned}\end{equation}
+The renormalisation in the Hamiltonian \(H_{(j)}\) at the \(j^\text{th}\) RG step, upon decoupling an electronic state \(q\beta\), is given by the expression:
+\begin{equation}\begin{aligned}
+	\left(\Delta H_{(j)}\right)_{\vec q,\beta} = H_{(j-1)} - H_{(j)} = c^\dagger_{\vec q,\beta} T_{\vec q,\beta} \frac{1}{\omega_e - H_D} T^\dagger_{\vec q,\beta}c_{\vec q,\beta} + T^\dagger_{\vec q,\beta} c_{\vec q,\beta} \frac{1}{\omega_h - H_D} c^\dagger_{\vec q,\beta}T_{\vec q,\beta}~,
+\end{aligned}\end{equation}
+where \(\omega_{e,h}\) are the quantum fluctuation scales for the electron and hole scattering channels, \(H_D\) is the part of the Hamiltonian that is diagonal in \(k-\)space, and \(T_{\vec q,\beta} + T_{\vec q,\beta}^\dagger\) is the part of the Hamiltonian that does not commute with \(\hat n_{\vec q,\beta}\) (in short, it is the part that is off-diagonal with respect to a particular state \(\vec q,\beta\)).
+This off-diagonal part is made up of contributions from \(V,J\) and \(U_b\):
+\begin{equation}\begin{aligned}
+	T_{\vec q \uparrow} = \left[V c^\dagger_{d \uparrow}  + J \sum_{\vec k}S_d^+ c^\dagger_{\vec k \downarrow}  + U_b \sum_{\vec k_1,\vec k_2,\vec k_3}c^\dagger_{\vec k_1 \uparrow} c^\dagger_{\vec k_3 \downarrow} c_{\vec k_4 \downarrow}\right] c_{\vec q \uparrow} ~,
+\end{aligned}\end{equation}
+while the diagonal part is given by
+\begin{equation}\begin{aligned}
+	H_D = \epsilon_{\vec q} \tau_{q\uparrow} + \frac{1}{4}J S_d^z\left(\hat n_{q \uparrow} - \hat n_{q \downarrow}\right) - U_b \left(\tau_{\vec q,\uparrow}\right)^2~,
+\end{aligned}\end{equation}
+where we have rewritten \(\hat n_{\vec q,\beta}\) in terms of \(\tau_{\vec q,\beta} \equiv \hat n_{\vec q,\beta} - \frac{1}{2}\) in the contribution from \(U_b\).
+Note that we have ignored a potential scattering term in the off-diagonal part \(T_{\vec q\beta}\).
+In the initial state \(\ket{\Psi}_i\), we have \(\langle \hat n_{q\beta} \rangle = 1/2 \implies \tau_{q\beta} = 0\), so the contribution of \(U_b\) to that state is 0.
+For both hole excitations \(c_{q\beta}\ket{\Psi}_i\) as well as particle excitations \(c^\dagger_{q\beta}\ket{\Psi}_i\), the intermediate state energy lowers to \(-U_b/4\).
+Because the diagonal contribution from \(U_b\) always changes the energy of the excited energy by \(-U_b/4\),  the denominator will simply change by \(U_b/4\) (\(H_D\) comes with a minus sign in the denominator).
+We will suppress this change for now and substitute in all the denominators at the end.
+
 We define \(n_j\) as the number of states being decoupled on each side of the Fermi surface, at the \(j^\text{th}\) RG step.
@@
 Since \(\tau_{q \uparrow} = -\frac{1}{2}\) in the excited state, the kinetic energy for \(\ket{\Psi}_\text{int}\) is \(\epsilon_q \tau_{q \uparrow} = \left(-D\right)\times\left(-\frac{1}{2}\right) = D/2\).
+
+\subsection{Renormalisation of \(U_b\)}
+\(U_b\) can renormalise only via itself. The relevant renormalisation term in the particle sector is
+\begin{equation}\begin{aligned}
+	U_b^2 \sum_{q\beta}\sum_{k_1,k_2,k_3,k_1^\prime,k_2^\prime,k_3^\prime} c^\dagger_{q\beta}c_{k_1\beta}c^\dagger_{k_3\overline\beta}c_{k_1^\prime\overline\beta}\frac{1}{\omega - H_D}c^\dagger_{k_2^\prime\overline\beta}c_{k_3^\prime\overline\beta}c^\dagger_{k_2\beta}c_{q\beta}
+\end{aligned}\end{equation}
+In order to renormalise \(U_b\), we need to contract one more pair of momenta.
+There are two choices.
+The first is by setting \(k_3 = k_3^\prime = q\).
+The two internal states, then, are \(q\beta\) and \(q\overline\beta\).
+As discussed above, the intermediate state energy is \(-U_b/4\).
+We therefore have
+\begin{equation}\begin{aligned}
+	\frac{U_b^2 n_j}{\omega - D/2 + \frac{U_b}{2}}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c_{k_1\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2^\prime\overline\beta}c^\dagger_{k_2\beta} = \frac{U_b^2 n_j}{\omega - D/2 + \frac{U_b}{2}}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_2^\prime\overline\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
+\end{aligned}\end{equation}
+Another way to contract the momenta is by setting \(k_1^\prime = k_2^\prime = q\), which gives a renormalisation of
+\begin{equation}\begin{aligned}
+	\frac{U_b^2 n_j}{\omega - D/2 + \frac{U_b}{2}}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c_{k_1\beta}c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta} = -\frac{U_b^2 n_j}{\omega - D/2}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
+\end{aligned}\end{equation}
+The two contributions cancel each other. The same cancellation happens in the hole sector as well.
+
+\subsection{Renormalisation of the impurity correlation \(U\)}
+The coupling \(U\) is renormalised by two kinds of vertices: \(V^2\) and \(J^2\). We will consider these processes one at a time. For convenience, we define \(\epsilon_d = -U/2\).
 
@@
 \end{aligned}\end{equation}
-Combining all this, we can write \(E_1 = \frac{D}{2} - \frac{K}{4}\) and \(E_0 = \frac{D}{2} + \epsilon_d - \frac{J}{4}\).
+Combining all this, we can write \(E_1 = \frac{D}{2}\) and \(E_0 = \frac{D}{2} + \epsilon_d - \frac{J}{4}\).
 In order to relate \(\omega_0\) with \(\omega_1\) with the common fluctuation scale \(\omega\) for the conduction electrons, we will replace these quantum fluctuation scales by the current renormalised values of the single-particle self-energy for the initial state from which we started scattering.
@@
 	\label{ren_ed_Vp}
-	V^2 n_j\sum_{\beta}\left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)
+	V^2 n_j\sum_{\beta}\left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} + \epsilon_d}\right)
 \end{aligned}\end{equation}
@@
 	\label{ren_ed_Vh}
-	V^2 n_j\sum_{\beta}\hat n_{d\beta}\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right)
+	V^2 n_j\sum_{\beta}\hat n_{d\beta}\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} + \epsilon_d} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right)
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
-The final kind of scattering is the \(K^2\) type. Similar to the \(J^2\) term, we get the following contribution:
-\begin{equation}\begin{aligned}
-	\label{ren_ed_Kpp}
-	\frac{K^2}{4}\sum_{q\beta}c^\dagger_{q\beta}c^\dagger_{q\overline\beta}c_{d\overline\beta}c_{d\beta} \frac{1}{\omega - H_D}c^\dagger_{d\beta}c^\dagger_{d\overline\beta}c_{q\overline\beta}c_{q\beta} = \frac{K^2}{2} n_j\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} \left(1 - \hat n_{d \uparrow}\right) \left( 1 - \hat n_{d \downarrow} \right)
-\end{aligned}\end{equation}
-in the particle sector. This is again because \(E = \frac{D}{2} - \frac{K}{4}\) in the intermediate state and \(\omega^\prime = \omega\). In the hole sector, we get
-\begin{equation}\begin{aligned}
-	\label{ren_ed_Kph}
-	\frac{K^2}{2} n_j\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} \hat n_{d\uparrow}\hat n_{d \downarrow}~.
-\end{aligned}\end{equation}
 
-We now have all possible renormalisation to the impurity energy \(\epsilon_d\).
+We now have all possible renormalisation to the impurity correlation \(U\).
 To actually compute the renormalisation, we will first calculate the renormalisation in the energies \(\epsilon_0, \epsilon_1\) and \(\epsilon_2\) of the impurity states \(\ket{\hat n_d = 0}, \ket{\hat n_d = 1}, \ket{\hat n_d = 2}\) respectively.
@@
 \end{itemize}
-From eqs.~\ref{ren_ed_Vp}, \ref{ren_ed_Vh}, \ref{ren_ed_Jpp}, \ref{ren_ed_Jph}, \ref{ren_ed_Kpp} and \ref{ren_ed_Kph}, we write
+From eqs.~\ref{ren_ed_Vp}, \ref{ren_ed_Vh}, \ref{ren_ed_Jpp} and \ref{ren_ed_Jph}, we write
 \begin{equation}\begin{aligned}
-	\Delta \epsilon_0 = \Delta \epsilon_2 = \frac{2V^2 n_j}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}} + \frac{K^2 n_j/2}{\omega - \frac{D}{2} + \frac{K}{4}}, && \Delta \epsilon_1 = \frac{2V^2 n_j}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} + \frac{J^2 n_j/2}{\omega - \frac{D}{2} + \frac{J}{4}}
+	\Delta U = \Delta \epsilon_2 + \Delta \epsilon_0 - 2\Delta \epsilon_1 = -\frac{4V^2 n_j}{\omega + \frac{U_b}{2} - \frac{D}{2} - U/2} + \frac{4V^2 n_j}{\omega + \frac{U_b}{2} - \frac{D}{2} + U/2 + \frac{J}{4}} - \frac{J^2n_j}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~,
 \end{aligned}\end{equation}
-We had started with a particle-hole symmetric Hamiltonian \((2\epsilon_d + U = 0)\); the fact that \(\Delta \epsilon_0 = \Delta \epsilon_2\) means the RG transformation has preserved that symmetry.
-The renormalisation of \(\epsilon_d\) is simply the renormalisation in the energy difference between the singly-occupied and vacant impurity levels: \(\Delta \epsilon_d = \Delta \epsilon_1 - \Delta \epsilon_0\).
-This gives our first RG equation:
-\begin{equation}\begin{aligned}
-	\Delta \epsilon_d = 2V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + \frac{n_j}{2}\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right)
-\end{aligned}\end{equation}
+where we have restored the contribution from \(U_b\) in the denominator.
 
 \subsection{Renormalisation of the hybridisation \(V\)}
-Renormalisation of \(V\) happens through two kinds of processes: \(VJ\) and \(VK\).
-In order words, the two vertices involve one single-particle scattering and one spin or isospin exchange respectively.
-We first look at the vertices that involve a spin-exchange scattering.
-
-Within spin-exchange, the scattering can be either via \(S_d^z\) or through \(S_d^\pm\). For the first kind, we have the following contribution in the particle sector:
+Renormalisation of \(V\) happens through two kinds of processes: \(VJ\) and \(VU_b\).
+Within the first kind, the scattering can be either via \(S_d^z\) or through \(S_d^\pm\).
+For the first kind, we have the following contribution in the particle sector:
 \begin{equation}\begin{aligned}
@@
 \begin{equation}\begin{aligned}
-	-\frac{3n_j}{8}V J \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
+	-\frac{3n_j}{8}V J \left(\frac{1}{\omega +U_b/4 - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega +U_b/4 - \frac{D}{2} + U/2 + \frac{J}{4}}\right) \sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
 \end{aligned}\end{equation}
 
-We now look at the \(VK\) processes. The first one is
-\begin{equation}\begin{aligned}
-	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{4}K \sum_{k} \left(\hat n_{d} - 1\right) c^\dagger_{k\beta}c_{q\beta} = -\frac{1}{8}V K n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \hat n_{d\overline \beta}c^\dagger_{k\beta}c_{d\beta}
-\end{aligned}\end{equation}
-The exchanged process again gives the Hermitian conjugate, so the combined contribution is
-\begin{equation}\begin{aligned}
-	-\frac{1}{8}V K n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \hat n_{d\overline \beta} \left(c^\dagger_{k\beta}c_{d\beta} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-
-The isospin-flip vertex gives
-\begin{equation}\begin{aligned}
-	\sum_{q\beta} V c^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{2}K \sum_{k} c^\dagger_{d\beta}c^\dagger_{d\overline\beta} c_{k\overline\beta} c_{q\beta} = \frac{1}{4}K V n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) c^\dagger_{d\overline\beta}c_{k\overline\beta}~.
-\end{aligned}\end{equation}
-Combining with Hermitian conjugate gives
-\begin{equation}\begin{aligned}
-	\frac{1}{4}K V n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) \left(c^\dagger_{d\overline\beta}c_{k\overline\beta} + \text{h.c.}\right)~.
-\end{aligned}\end{equation}
-
-After obtaining the hole sector contributions, the total renormalisation from \(VK\) processes is
-\begin{equation}\begin{aligned}
-	-\frac{3n_j}{4}V K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)~.
-\end{aligned}\end{equation}
-
-The RG equation for \(V\) is
-\begin{equation}\begin{aligned}
-	\Delta V = -\frac{3n_j V}{8}\left[J\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)\right]
-\end{aligned}\end{equation}
-
-\subsection{Renormalisation of the exchange couplings \(J\) and \(K\)}
-We will just note the renormalisation in \(J^z\), which will be equal to \(J^\pm\) due to spin-rotation symmetry.
-The terms that renormalise \(J^z\) are of the form \(S_d^\pm S_d^\mp\).
-In the particle sector, we have
-\begin{equation}\begin{aligned}
-	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^\pm c^\dagger_{q\mp}c_{k^\prime\pm} \frac{1}{\omega - H_D}S_d^\mp c^\dagger_{k\pm}c_{q\mp} = -n_j \frac{1}{4}J^2 \left(\frac{1}{2} \pm S_d^z\right) \sum_{kk^\prime}c^\dagger_{k \pm}c_{k\pm} \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
-The denominator is determined using \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\) and \(\omega^\prime = \omega + \epsilon_d\).
-In the hole sector, we similarly have
-\begin{equation}\begin{aligned}
-	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^\mp c^\dagger_{k\pm}c_{q\mp} \frac{1}{\omega - H_D}S_d^\pm c^\dagger_{q\mp}c_{k^\prime\pm} = n_j \frac{1}{4}J^2 \left(\frac{1}{2} \mp S_d^z\right) \sum_{kk^\prime}c^\dagger_{k \pm}c_{k\pm} \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
-Adding all four expressions and dropping the constant part, we get
-\begin{equation}\begin{aligned}
-	-n_j \frac{1}{2}J^2 S_d^z \sum_{kk^\prime}\left(c^\dagger_{k \uparrow}c_{k^\prime \uparrow} - c^\dagger_{k \downarrow}c_{k^\prime \downarrow}\right) \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
-We can now directly read off the RG equation for \(J\):
-\begin{equation}\begin{aligned}
-	\Delta J = -\frac{n_j J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
-\end{aligned}\end{equation}
-
-Since the spin and charge degrees of freedom are treated on an equal footing in the model, we obtain the RG equation for \(K\) by simply changing \(J \to K\):
-\begin{equation}\begin{aligned}
-	\Delta K = -\frac{n_j K^2}{\omega - \frac{D}{2} + \frac{K}{4}}
-\end{aligned}\end{equation}
-
-\section{\(U_b\)-included terms}
-
-We first Fourier transform the \(U_b\)-term to \(k-\)space.
-In \(k-\)space, the diagonal contribution (to \(H_D\)) coming from this term is the single-particle self-energy \(-U_b\left(\hat n_{q \beta}\right)^2\) which can be made particle-hole symmetric in the form:
-\begin{equation}\begin{aligned}
-	-U_b\left(\tau_{q \beta}\right)^2
-\end{aligned}\end{equation}
-where \(q\) is the \(k-\)state being decoupled and \(\tau \equiv \hat n - 1/2\).
-In the initial state \(\ket{\Psi}_i\), we have \(\langle \hat n_{q\beta} \rangle = 1/2 \implies \tau_{q\beta} = 0\), so the contribution of \(U_b\) to that state is 0.
-For both hole excitations \(c_{q\beta}\ket{\Psi}_i\) as well as particle excitations \(c^\dagger_{q\beta}\ket{\Psi}_i\), the intermediate state energy lowers to \(-U_b/4\).
-
-The off-diagonal part is
-\begin{equation}\begin{aligned}
-	-\frac{U_b}{2}\sum_{kk^\prime\sigma}c^\dagger_{k\sigma}c_{k^\prime\sigma} + U_b \sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_1 \uparrow}c_{k_2 \uparrow} c^\dagger_{k^\prime_1 \downarrow}c_{k^\prime_2 \downarrow}
-\end{aligned}\end{equation}
-We ignore the potential scattering arising from the first term.
-
-\subsection{Renormalisation of \(U_b\)}
-\(U_b\) can renormalise only via itself. The relevant renormalisation term in the particle sector is
-\begin{equation}\begin{aligned}
-	U_b^2 \sum_{q\beta}\sum_{k_1,k_2,k_3,k_1^\prime,k_2^\prime,k_3^\prime} c^\dagger_{q\beta}c_{k_1\beta}c^\dagger_{k_3\overline\beta}c_{k_1^\prime\overline\beta}\frac{1}{\omega - H_D}c^\dagger_{k_2^\prime\overline\beta}c_{k_3^\prime\overline\beta}c^\dagger_{k_2\beta}c_{q\beta}
-\end{aligned}\end{equation}
-In order to renormalise \(U_b\), we need to contract one more pair of momenta.
-There are two choices.
-The first is by setting \(k_3 = k_3^\prime = q\).
-The two internal states, then, are \(q\beta\) and \(q\overline\beta\).
-As discussed above, the intermediate state energy is \(-U_b/4\).
-We therefore have
-\begin{equation}\begin{aligned}
-	\frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c_{k_1\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2^\prime\overline\beta}c^\dagger_{k_2\beta} = \frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_2^\prime\overline\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
-\end{aligned}\end{equation}
-Another way to contract the momenta is by setting \(k_1^\prime = k_2^\prime = q\), which gives a renormalisation of
-\begin{equation}\begin{aligned}
-	\frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c_{k_1\beta}c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta} = -\frac{U_b^2 n_j}{\omega - D/2}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
-\end{aligned}\end{equation}
-The two contributions cancel each other. The same cancellation happens in the hole sector as well.
-
-\subsection{Renormalisation of \(U\)}
-\(U_b\) does not have any new renormalisation term on account of \(U_b\). \(U_b\) does however modify the existing RG equation for \(U\), by shifting the denominator. The existing RG equation is
-\begin{equation}\begin{aligned}
-	\Delta U &= -4V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) - n_j\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right)~.
-\end{aligned}\end{equation}
-On accounting for the contribution of \(U_b\) to the denominator, we get
-\begin{equation}\begin{aligned}
-	\Delta U &= -4V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} - \epsilon_d + \frac{J}{4}}\right) - n_j\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right)~.
-\end{aligned}\end{equation}
-
-\subsection{Renormalisation of \(V\)}
-The single-particle  hybridisation \(V\) renormalises through terms of \(V U_b\) and \(U_b V\) kind. The first term gives
+The renormalisation in \(V\) from \(U_b\) arises through terms of \(V U_b\) and \(U_b V\) kind. The first term gives
 \begin{equation}\begin{aligned}
@@
 
-Combining with the already existing RG equations, the complete RG equation for \(V\) becomes
+Combining with the renormalisation from \(J\), the complete RG equation for \(V\) becomes
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
+The RG equation for \(V\) is
+\begin{equation}\begin{aligned}
+	\Delta V = -\frac{3n_j V}{8}\left[J\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)\right]
+\end{aligned}\end{equation}
 
-\subsection{Renormalisation of \(J\) and \(K\)}
-We will track the entire renormalisation purely from that of \(J^+\), by virtue of the SU(2) symmetry. \(J^+\) renormalises through the \(J U_b\) terms. One of the terms is
+\subsection{Renormalisation of the spin-exchange coupling \(J\)}
+The term \(J \vec{S_d}\cdot\vec{S}_0\) can be split into three parts: \(J^z S_d^z, \frac{1}{2}J^+ S_d^+ S_0^-\) and \(\frac{1}{2}J^- S_d^- S_0^+\).
+We will only calculate the renormalisation in \(J^+\), which will be equal to that of \(J^-,J^z\) due to spin-rotation symmetry.
+The terms that renormalise \(J^+\) are of the form \(S_d^+ S_d^z\) and \(S_d^z S_d^+\).
+In the particle sector, we have
+\begin{equation}\begin{aligned}
+	-\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^+ c^\dagger_{q\downarrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D}S_d^z c^\dagger_{k \downarrow}c_{q \downarrow} = n_j \frac{1}{4}J^2 \left(-\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~,\\
+	\sum_{q} \sum_{kk^\prime} \frac{1}{4}J^2 S_d^z c^\dagger_{q \uparrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D} S_d^+ c^\dagger_{k\downarrow}c_{q \uparrow} = -n_j \frac{1}{4}J^2 \left(\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~.
+\end{aligned}\end{equation}
+The denominator is determined using \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\) and \(\omega^\prime = \omega + \epsilon_d\).
+In the hole sector, we similarly have
+\begin{equation}\begin{aligned}
+	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^+ c^\dagger_{k\downarrow}c_{q \uparrow} \frac{1}{\omega - H_D}S_d^z c^\dagger_{q \uparrow}c_{k^\prime \uparrow} = n_j \frac{1}{4}J^2 \left(-\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~,\\
+	-\sum_{q} \sum_{kk^\prime} \frac{1}{4}J^2 S_d^z c^\dagger_{k \downarrow}c_{q \downarrow} \frac{1}{\omega - H_D} S_d^+ c^\dagger_{q\downarrow}c_{k^\prime \uparrow} = -n_j \frac{1}{4}J^2 \left(\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~.
+\end{aligned}\end{equation}
+
+The renormalisation due to \(U_b\) also happens through multiple terms. One of the terms is
 \begin{equation}\begin{aligned}
@@
 
-Adding all these terms and combining with the existing RG equation, we get the updated RG equation for \(J\):
+Combining all these terms, we get the updated RG equation for \(J\):
 \begin{equation}\begin{aligned}
@@
 
-\bibliography{gen-siam}
 \end{document}

### 2022-05-04 gen-siam-manuscript/gen-siam.tex
added corectec figures

@@
 
-The Hubbard model is one of the fundamental models for strong electronic correlation; in its simplest form, it features a single band of conduction electrons hopping on a lattice and interacting via local correlations that provide a cost \(U\) if any site is doubly occupied.
+The Hubbard model has become one of the fundamental and prototypical models for describing strongly correlated systems in quantum condensed matter physics.
+strong electronic correlation; in its simplest form, it features a single band of conduction electrons hopping on a lattice and interacting via local correlations that provide a cost \(U\) if any site is doubly occupied.
 There are two trivial limits of the model.
@@
 \centering
-\includegraphics[width=0.5\textwidth]{../figures/dos_diff.pdf}
+\includegraphics[width=0.5\textwidth]{dos_diff.pdf}
 \caption{Two kinds of bath that an impurity can hybridise into.
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/zeromode_bare.pdf}
+	\includegraphics[width=0.45\textwidth]{zeromode_bare.pdf}
 	\caption{While we have studied the full model under renormalisation group, often we will turn to a simplified zero-bandwidth version of the model that is obtained by ignoring the kinetic energy part of the Hamiltonian.
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/urg-scheme.pdf}
+	\includegraphics[width=0.45\textwidth]{urg-scheme.pdf}
 	\caption{High energy - low energy scheme defined and used in the URG method.
@@
 	\centering
-	\includegraphics[width=0.48\textwidth]{../figures/J_Ub.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/U_Ub.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/V_Ub.pdf}
+	\includegraphics[width=0.48\textwidth]{J_Ub.pdf}
+	\includegraphics[width=0.48\textwidth]{U_Ub.pdf}
+	\includegraphics[width=0.48\textwidth]{V_Ub.pdf}
 	\caption{Variation of couplings \(U,V\) and \(J\) along the RG transformations, for three values of the transition-tuning ratio \(r\).
@@
 \begin{figure}[!htb]
-	\includegraphics[width=0.5\textwidth]{../figures/phase-map-MIT.pdf}
+	\includegraphics[width=0.5\textwidth]{phase-map-MIT.pdf}
 	\caption{Phase diagram of the GAIM, in the space of couplings \(U_0\) and \(J_0\).
@@
 	\centering
-	\includegraphics[width=0.49\textwidth]{../figures/odlro.pdf}
+	\includegraphics[width=0.49\textwidth]{odlro.pdf}
 	\caption{Growth in the pair-fluctuation terms \(c^\dagger_{k \uparrow}c^\dagger_{k \downarrow} c_{k^\prime \downarrow}c_{k^\prime \uparrow}\), as \(r \to 0.25\).
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/J_bandwidth.pdf}
+	\includegraphics[width=0.5\textwidth]{J_bandwidth.pdf}
 	\caption{Increase of \(J^*\) in comparison to \(V^*\) when going towards the thermodynamic limit.}
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{../figures/zeromode_eff.pdf}
+	\includegraphics[width=0.4\textwidth]{zeromode_eff.pdf}
 	\caption{Two site Hamiltonian obtained by taking the zero bandwidth limit of the effective Hamiltonian in the screened regime.}
@@
 	\centering
-\includegraphics[width=0.5\textwidth]{../figures/corrs_gs.pdf}
+\includegraphics[width=0.5\textwidth]{corrs_gs.pdf}
 \caption{Overlap of the RG fixed point ground state \(\ket{\Psi}_\text{gs}\) with the spin singlet state \(\ket{\text{ss}}\) and the charge triplet state \(\ket{\text{ct}}\), for a range of values of the transition tuning ratio \(r\).
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/Add.pdf}
+	\includegraphics[width=0.5\textwidth]{Add.pdf}
 	\caption{Impurity spectral function \(A_d(\omega)\) at three values of the ratio \(r\).
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/entanglement.pdf}
+	\includegraphics[width=0.5\textwidth]{entanglement.pdf}
 	\caption{Variation of \(\sqrt{\left(1 - \varepsilon_\text{ss} \right)}\sqrt{\left(1 - \varepsilon_\text{ct} \right)}\) as \(r\) is increased towards the critical value 0.25.
@@
 \begin{figure}[!htb]
-\includegraphics[width=0.49\textwidth]{../figures/I_k.pdf}
+\includegraphics[width=0.49\textwidth]{I_k.pdf}
 \caption{Mutual information in \(k-\)space, across the transition.
@@
 \begin{figure}[!htb]
-\includegraphics[width=0.49\textwidth]{../figures/I_r.pdf}
+\includegraphics[width=0.49\textwidth]{I_r.pdf}
 \caption{Mutual information in \(r-\)space, across the transition.

### 2022-05-04 gen-siam-manuscript/gen-siam.tex
started writing introduction

@@
 
-\title{Local metal-insulator transition in a generalised impurity Anderson model}
+\title{Local metal-insulator transition in a generalised Anderson impurity model}
 \author{Abhirup Mukherjee}
@@
 
-The Hubbard model has become one of the fundamental and prototypical models for describing strongly correlated systems in quantum condensed matter physics.
-strong electronic correlation; in its simplest form, it features a single band of conduction electrons hopping on a lattice and interacting via local correlations that provide a cost \(U\) if any site is doubly occupied.
-There are two trivial limits of the model.
-At \(U=0\), the bath consists of just a kinetic energy part, and the ground state is just a filled Fermi sea.
-At \(t=0\), each lattice site decouples from the rest and becomes a local moment, which under symmetry-breaking becomes a Neel antiferromagnet.
-This suggests that on increasing \(U/t\) beyond some critical value, the system might undergo a phase transition from a metallic state to an insulating state~\cite{Mott_1949}.
-This transition is reflected in the local spectral function - while it has a well-defined zero energy peak in the metallic phase, it is gapped in the insulating phase.
+Quantum impurity models, owing to their simple construction, have often served as testbeds for analytical and numerical methods, as well as experimental techniques.
+They consist of one or more local correlated quantum system(s) coupled with (typically non-interacting) bosonic or fermionic conduction bath channel(s).
+Even though the impurity itself is simple, the interaction with the bath often leads to novel phases, and such impurity systems often lead to interesting phenomena that have far-reaching consequences and require fundamental theoretical breakthroughs in order to understand them.
+One of the most well-studied impurity models is the single-impurity Anderson model; it consists of a single impurity site of spin-half electrons and local correlation \(U\) hybridising with a non-interacting conduction bath through a coupling \(V\).
 
@@
 Auxiliary models are simpler versions of the full Hamiltonian that are able to capture the essential physics.
-For eg, a correlated impurity interacting with a conduction bath is a potential auxiliary model for the Hubbard Hamiltonian:
+For example, a correlated impurity interacting with a conduction bath is a potential auxiliary model for the Hubbard Hamiltonian:
 The impurity has onsite energy \(\epsilon_d\) and an onsite correlation \(U\). It hybridises into the bath through \(V\).
@@
 
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.48\textwidth]{J_Ub.pdf}
+	\includegraphics[width=0.48\textwidth]{U_Ub.pdf}
+	\includegraphics[width=0.48\textwidth]{V_Ub.pdf}
+	\caption{Variation of couplings \(U,V\) and \(J\) along the RG transformations, for three values of the transition-tuning ratio \(r\).
+x-axis represents the RG steps, the rightmost point is the first RG step and leftmost point is the final RG step.
+The values of the bare couplings are given in the title.
+All values are in units of the half-bandwidth \(D_0\), which is chosen to be 10.
+The blue curves represent the flows for \(r > r_c\), where \(J\) is relevant.
+The purple curves represent the RG flows for \(r < r_c\), where \(J\) is irrelevant.
+The red curves are exactly at the critical point \(r = r_c\), where \(J\) is marginal.}
+	\label{rg-flow}
+\end{figure}
+
 \subsection{RG flows for \(r < r_c\)}
@@
 \end{aligned}\end{equation}
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.48\textwidth]{J_Ub.pdf}
-	\includegraphics[width=0.48\textwidth]{U_Ub.pdf}
-	\includegraphics[width=0.48\textwidth]{V_Ub.pdf}
-	\caption{Variation of couplings \(U,V\) and \(J\) along the RG transformations, for three values of the transition-tuning ratio \(r\).
-x-axis represents the RG steps, the rightmost point is the first RG step and leftmost point is the final RG step.
-The values of the bare couplings are given in the title.
-All values are in units of the half-bandwidth \(D_0\), which is chosen to be 10.
-The blue curves represent the flows for \(r > r_c\), where \(J\) is relevant.
-The purple curves represent the RG flows for \(r < r_c\), where \(J\) is irrelevant.
-The red curves are exactly at the critical point \(r = r_c\), where \(J\) is marginal.}
-	\label{rg-flow}
-\end{figure}
 
@@
 We find that while the former decrease towards the transition, the latter pick up; the spin-fluctuations are getting replaced by the charge fluctuations.
-This is substantied by the inset of the same figure, which shows the behaviour of these fluctuations even after the transition.
+This is substantiated by the inset of the same figure, which shows the behaviour of these fluctuations for a larger range across the transition.
 While the spin-fluctuations vanish beyond the transition, the charge fluctuations undergo an abrupt increase.
+
+{\color{blue}The death of the spin-fluctuations and the simultaneous growth in the charge fluctuations can be attributed to the presence of the attractive correlation term \(U_b\) in the Hamiltonian.
+Indeed, \(c^\dagger_{\vec k \uparrow} c^\dagger_{\vec k \downarrow} c_{\vec k^\prime \uparrow} c_{\vec k^\prime \downarrow}\) is just the \(k-\)space Fourier transform of the \(U_b\) term.
+The presence of such terms force the conduction bath to shift spectral weight from the spin sector to the charge sector, destabilising the singlet ground state in the process.}
 
@@
 This comes at the cost of the spin-flip fluctuations \(S_d^+ S_0^- + \text{h.c.}\), which decrease towards the transition.
-The inset plots the same quantities but for a larger range of \(r\), and the pair fluctuations are seen to pick up abruplty after the transition while the spin fluctuations vanish.}
+The inset plots the same quantities but for a larger range of \(r\), and the pair fluctuations are seen to pick up abruptly after the transition while the spin fluctuations vanish.}
 	\label{pair_fluc}
@@
 
-The impurity Greens function can be given a spectral representation in terms of the eigenstates \(\left\{\ket{\Psi}_n\right\}\) of the GAIM:
+Given a ground state \(\ket{\Psi}_\text{gs}\) and a spectrum of energies \(\left\{ E_n \right\} \), the impurity Greens function can be given a spectral representation in terms of the eigenstates \(\left\{\ket{\Psi}_n\right\}\) of the GAIM:
 \begin{equation}\begin{aligned}
@@
 
-{\color{blue}We assume that the global phase of the wavefunctions are real}, and since the internal weights of the wavefunctions are real as well, the overlaps \(\braket{\text{ss}|\Psi^{(2)}_\text{gs}},\braket{\text{ct}|\Psi^{(2)}_\text{gs}}\) are also real.
+We assume that the global phase of the wavefunctions are real, and since the internal weights of the wavefunctions are real as well, the overlaps \(\braket{\text{ss}|\Psi^{(2)}_\text{gs}},\braket{\text{ct}|\Psi^{(2)}_\text{gs}}\) are also real.
 We can use these overlaps to define a geometric measure of entanglement:
@@
 
-\subsection{Mutual information and entanglement entropy in the ground state: fate of the Kondo cloud}
+\subsection{Mutual information and spin/charge correlations in ground state: fate of the Kondo cloud}
 Since the system has to undergo a phase transition into an unscreened phase for \(r > 0.25\), it is clear that the Kondo screening cloud must disappear.
 Indeed, this is captured by various entanglement measures like mutual information and entanglement entropy.
-The entanglement entropy \(S(A)\) of subsystem \(A\) with the rest of the system is defined as the von Neumann entropy of the reduced density matrix \(\rho_A\),
+The entanglement entropy (EE) \(S(A)\) of subsystem \(A\) with the rest of the system is defined as the von Neumann entropy of the reduced density matrix \(\rho_A\),
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-where \(S(A \cup B)\) is the entanglement entropy of \(A\) and \(B\) with the rest.
+where \(S(A \cup B)\) is the EE of \(A\) and \(B\) with the rest.
 \(I(A:B)\) represents the amount of information obtained about \(B\) on measuring \(A\), or vice-versa.
-If the ground state \(\ket{\Psi}_\text{gs}\) is a separable state where \(A\) is a disentangled from the rest, then its entanglement entropy \(S(A)\) will be \(0\).
-On the other hand, if the ground state cannot be written in separable form, \(S(A)\) becomes non-zero, and the maximum value it can take is \(\ln d\), where \(d\) is the dimension of the Hilbert space of \(A\).
-
-In the AIM or the Kondo model ground state, the impurity forms a maximally entangled singlet with the zeroth site~\cite{wilson1975,hewson1993,hrk_wilson_1980}.
-This in turn leads to entanglement in \(k-\)space between the conduction electrons that screen the impurity and form the Kondo cloud~\cite{anirban_kondo}.
-These features change once we turn on the attractive correlation \(U_b\) and drive the system across the transition, as plotted in Figs.~\ref{mut_inf_k} and \ref{mut_inf_r}.
-The \(k-\)space mutual information \(I(\vec k_1:\vec k_2)\) between two distinct \(k-\)states plotted in the red curve of Fig.~\ref{mut_inf_k} is essentially the entanglement within the Kondo cloud, and we find that this entanglement decreases towards the transition, signalling the weakening of the Kondo cloud.
-This is also supported by the reduction in the mutual information \(I(d \uparrow: \vec k \downarrow)\) between the impurity and \(k-\)space states plotted along the blue curve in the same figure.
-Beyond the transition, \(I(d \uparrow: \vec k \downarrow)\) drops to zero, because the impurity is no longer coupled to the bath, while \(I(\vec k_1:\vec k_2)\) takes on a larger value because they are connected by the \(U_b-\)term and are no longer sharing entanglement with the impurtiy.
+If the ground state \(\ket{\Psi}_\text{gs}\) is a state that is separable in terms of \(A\) and \(B\), then the system can be split into two disjoint parts, one of which is coupled to A and the other coupled to B.
+The total EE from both \(A\) and \(B\) is then just a sum of its parts: \(S(A\cup B) = S(A) + S(B)\), such that \(I(A:B) = 0\).
+On the other hand, if the ground state cannot be written in separable form, the EE of the sum, \(S(A \cup B)\) is more than the sum of its parts because of the additional entanglement between \(A\) and \(B\), and we get \(I(A:B) > 0\).
 
@@
 
+In the AIM or the Kondo model ground state, the impurity forms a maximally entangled singlet with the zeroth site~\cite{wilson1975,hewson1993,hrk_wilson_1980}.
+This in turn leads to entanglement in \(k-\)space between the conduction electrons that screen the impurity and form the Kondo cloud~\cite{anirban_kondo}.
+These features change once we turn on the attractive correlation \(U_b\) and drive the system across the transition, as plotted in Figs.~\ref{mut_inf_k} and \ref{mut_inf_r}.
+The \(k-\)space mutual information \(I(\vec k_1:\vec k_2)\) between two distinct \(k-\)states plotted in the red curve of Fig.~\ref{mut_inf_k} is essentially the entanglement within the Kondo cloud, and we find that this entanglement decreases towards the transition, signalling the weakening of the Kondo cloud.
+This is also supported by the reduction in the mutual information \(I(d \uparrow: \vec k \downarrow)\) between the impurity and \(k-\)space states plotted along the blue curve in the same figure.
+Beyond the transition, \(I(d \uparrow: \vec k \downarrow)\) drops to zero, because the impurity is no longer coupled to the bath, while \(I(\vec k_1:\vec k_2)\) takes on a larger value because they are connected by the \(U_b-\)term and are no longer sharing entanglement with the impurity.
+
 \begin{figure}[!htb]
@@
 \label{mut_inf_r}
+\end{figure}
+
+{\color{blue}Apart from the mutual information, we also computed two complimentary measures of correlation in the ground state, the spin-flip and the charge isospin correlations, \(\left<S_d^+ S_0^- \right>\) and \(\left<c^\dagger_{ 0 \uparrow} c^\dagger_{0 \downarrow} c_{d \downarrow} c_{d \uparrow} \right>\) respectively.
+These are shown in Fig.~\ref{charge-spin}, and show opposite tendencies.
+While the spin-flips decrease due to the destruction of the Kondo cloud, the charge isospin fluctuations grow because of the attractive correlation \(U_b\).
+Both drop to zero abruptly beyond the transition, because the impurity entirely decouples from the bath.}
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{odlro_d0.pdf}
+	\caption{Variation of spin-flip correlation and charge isospin-flip correlation across the transition.}
+	\label{charge-spin}
 \end{figure}
@@
 
-\begin{widetext}
 \section{Derivation of RG equations for the generalised Anderson impurity model}
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H} = -\frac{1}{2}U \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\vec k,\sigma} \epsilon_{\vec k} \tau_{\vec k,\sigma} + J \sum_{\vec k,\vec k^\prime,\atop{\alpha,\beta}}\vec{S}_d\cdot\vec{\sigma}_{\alpha\beta}c^\dagger_{\vec k,\alpha}c_{\vec k^\prime,\beta} + V\sum_{\vec k,\sigma} \left( c^\dagger_{d\sigma}c_{\vec k,\sigma} + \text{h.c.}\right) - U_b \sum_{\vec k,\vec k^\prime,\sigma}c^\dagger_{\vec k,\sigma}c_{\vec k^\prime,\sigma} \\
-+ U_b \sum_{\vec k_1,\vec k_2,\atop{\vec k_3,\vec k_4}}c^\dagger_{\vec k_1 \uparrow} c_{\vec k_2 \uparrow} c^\dagger_{\vec k_3 \downarrow} c_{\vec k_4 \downarrow}
+	\mathcal{H} = -\frac{1}{2}U \left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 + \sum_{\vec k,\sigma} \epsilon_{\vec k} \tau_{\vec k,\sigma} + J \vec{S}_d\cdot\vec{S}_0 \\
+	+ V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) - U_b \hat n_{0 \uparrow} \hat n_{0 \downarrow}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(\Delta H_{(j)}\right)_{\vec q,\beta} = H_{(j-1)} - H_{(j)} = c^\dagger_{\vec q,\beta} T_{\vec q,\beta} \frac{1}{\omega_e - H_D} T^\dagger_{\vec q,\beta}c_{\vec q,\beta} + T^\dagger_{\vec q,\beta} c_{\vec q,\beta} \frac{1}{\omega_h - H_D} c^\dagger_{\vec q,\beta}T_{\vec q,\beta}~,
+	&\left(\Delta H_{(j)}\right)_{\vec q,\beta} = H_{(j-1)} - H_{(j)} \\
+	&= c^\dagger_{\vec q,\beta} T_{\vec q,\beta} \frac{1}{\omega_e - H_D} T^\dagger_{\vec q,\beta}c_{\vec q,\beta} + T^\dagger_{\vec q,\beta} c_{\vec q,\beta} \frac{1}{\omega_h - H_D} c^\dagger_{\vec q,\beta}T_{\vec q,\beta}~,
 \end{aligned}\end{equation}
 where \(\omega_{e,h}\) are the quantum fluctuation scales for the electron and hole scattering channels, \(H_D\) is the part of the Hamiltonian that is diagonal in \(k-\)space, and \(T_{\vec q,\beta} + T_{\vec q,\beta}^\dagger\) is the part of the Hamiltonian that does not commute with \(\hat n_{\vec q,\beta}\) (in short, it is the part that is off-diagonal with respect to a particular state \(\vec q,\beta\)).
-This off-diagonal part is made up of contributions from \(V,J\) and \(U_b\):
-\begin{equation}\begin{aligned}
-	T_{\vec q \uparrow} = \left[V c^\dagger_{d \uparrow}  + J \sum_{\vec k}S_d^+ c^\dagger_{\vec k \downarrow}  + U_b \sum_{\vec k_1,\vec k_2,\vec k_3}c^\dagger_{\vec k_1 \uparrow} c^\dagger_{\vec k_3 \downarrow} c_{\vec k_4 \downarrow}\right] c_{\vec q \uparrow} ~,
-\end{aligned}\end{equation}
-while the diagonal part is given by
-\begin{equation}\begin{aligned}
-	H_D = \epsilon_{\vec q} \tau_{q\uparrow} + \frac{1}{4}J S_d^z\left(\hat n_{q \uparrow} - \hat n_{q \downarrow}\right) - U_b \left(\tau_{\vec q,\uparrow}\right)^2~,
-\end{aligned}\end{equation}
+This off-diagonal part is made up of contributions from \(V,J\) and \(U_b\): \(T_{\vec q \uparrow} = \left[V c^\dagger_{d \uparrow}  + J \sum_{\vec k}S_d^+ c^\dagger_{\vec k \downarrow}  + U_b \sum_{\vec k_1,\vec k_2,\vec k_3}c^\dagger_{\vec k_1 \uparrow} c^\dagger_{\vec k_3 \downarrow} c_{\vec k_4 \downarrow}\right] c_{\vec q \uparrow}\),
+while the diagonal part is given by \(H_D = \epsilon_{\vec q} \tau_{q\uparrow} + \frac{1}{4}J S_d^z\left(\hat n_{q \uparrow} - \hat n_{q \downarrow}\right) - U_b \left(\tau_{\vec q,\uparrow}\right)^2\),
 where we have rewritten \(\hat n_{\vec q,\beta}\) in terms of \(\tau_{\vec q,\beta} \equiv \hat n_{\vec q,\beta} - \frac{1}{2}\) in the contribution from \(U_b\).
+
 Note that we have ignored a potential scattering term in the off-diagonal part \(T_{\vec q\beta}\).
-In the initial state \(\ket{\Psi}_i\), we have \(\langle \hat n_{q\beta} \rangle = 1/2 \implies \tau_{q\beta} = 0\), so the contribution of \(U_b\) to that state is 0.
-For both hole excitations \(c_{q\beta}\ket{\Psi}_i\) as well as particle excitations \(c^\dagger_{q\beta}\ket{\Psi}_i\), the intermediate state energy lowers to \(-U_b/4\).
 Because the diagonal contribution from \(U_b\) always changes the energy of the excited energy by \(-U_b/4\),  the denominator will simply change by \(U_b/4\) (\(H_D\) comes with a minus sign in the denominator).
 We will suppress this change for now and substitute in all the denominators at the end.
-
 We define \(n_j\) as the number of states being decoupled on each side of the Fermi surface, at the \(j^\text{th}\) RG step.
 In order to treat both spin and isospin exchanges democratically, we take \(\ket{\Psi}_i = \frac{1}{2}\left(\ket{0} + \ket{q\uparrow} + \ket{q\downarrow} + \ket{q\uparrow, q\downarrow}\right) \) as the \textit{initial} state for the scattering processes.
-The intermediate states \(\ket{\Psi}_\text{int}\) in the particle sector \(\left(c_{q\beta}\ket{\Psi}_i\right)\) and hole sector \(\left(c^\dagger_{q\beta}\ket{\Psi}_i\right)\) will then have both spin and isospin excitations which can couple with the corresponding impurity degree of freedom.
-We will assume that states  \(q > k_F~\left(\epsilon_q > 0\right) \) above the Fermi surface can have only particle excitations and states below the Fermi surface can only have hole excitations.
-The kinetic energy part \(\epsilon_q \tau_{q\beta}\) of \(H_D\) for \(\ket{\Psi}_i\) is then zero, whereas it is always \(D/2\) for \(\ket{\Psi}_\text{int}\).
-To demonstrate this for a typical \(q < k_F\), the hole excitation is \(c_{q \uparrow}\ket{\Psi}_i = \frac{1}{\sqrt 2}\left(\ket{0} + \ket{q \downarrow}\right)\).
-This has an isospin term in the form of the \textit{holon} and a spin term in the form of the down state.
-Since \(\tau_{q \uparrow} = -\frac{1}{2}\) in the excited state, the kinetic energy for \(\ket{\Psi}_\text{int}\) is \(\epsilon_q \tau_{q \uparrow} = \left(-D\right)\times\left(-\frac{1}{2}\right) = D/2\).
+The kinetic energy for \(\ket{\Psi}_\text{int}\) is \(\epsilon_q \tau_{q \uparrow} = \left(-D\right)\times\left(-\frac{1}{2}\right) = D/2\).
 
@@
 \begin{equation}\begin{aligned}
-	U_b^2 \sum_{q\beta}\sum_{k_1,k_2,k_3,k_1^\prime,k_2^\prime,k_3^\prime} c^\dagger_{q\beta}c_{k_1\beta}c^\dagger_{k_3\overline\beta}c_{k_1^\prime\overline\beta}\frac{1}{\omega - H_D}c^\dagger_{k_2^\prime\overline\beta}c_{k_3^\prime\overline\beta}c^\dagger_{k_2\beta}c_{q\beta}
+	U_b^2 \sum_{q\beta}\sum_{k_1,k_2,k_3,\atop{k_1^\prime,k_2^\prime,k_3^\prime}} c^\dagger_{q\beta}c_{k_1\beta}c^\dagger_{k_3\overline\beta}c_{k_1^\prime\overline\beta}\frac{1}{\omega - H_D}c^\dagger_{k_2^\prime\overline\beta}c_{k_3^\prime\overline\beta}c^\dagger_{k_2\beta}c_{q\beta}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\frac{U_b^2 n_j}{\omega - D/2 + \frac{U_b}{2}}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c_{k_1\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2^\prime\overline\beta}c^\dagger_{k_2\beta} = \frac{U_b^2 n_j}{\omega - D/2 + \frac{U_b}{2}}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_2^\prime\overline\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
+	\frac{U_b^2 n_j}{\omega - D/2 + \frac{U_b}{2}}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c_{k_1\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2^\prime\overline\beta}c^\dagger_{k_2\beta} \\
+	= \frac{U_b^2 n_j}{\omega - D/2 + \frac{U_b}{2}}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_2^\prime\overline\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\frac{U_b^2 n_j}{\omega - D/2 + \frac{U_b}{2}}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c_{k_1\beta}c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta} = -\frac{U_b^2 n_j}{\omega - D/2}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
+	\frac{U_b^2 n_j}{\omega - D/2 + \frac{U_b}{2}}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c_{k_1\beta}c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta} \\
+	= -\frac{U_b^2 n_j}{\omega - D/2}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\sum_{q\beta}c^\dagger_{q\beta}c_{d\beta}\frac{V^2}{\omega - H_D}c^\dagger_{d\beta}c_{q\beta} = \sum_{q\beta}V^2 \hat n_{q\beta} \left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega - E_0} + \frac{\hat n_{d \overline\beta}}{\omega^\prime - E_1}\right) = V^2 n_j\sum_{\beta}\left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega_0 - E_0} + \frac{\hat n_{d \overline\beta}}{\omega_1 - E_1}\right)
+	&\sum_{q\beta}c^\dagger_{q\beta}c_{d\beta}\frac{V^2}{\omega - H_D}c^\dagger_{d\beta}c_{q\beta}\\
+	&= \sum_{q\beta}V^2 \hat n_{q\beta} \left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega - E_0} + \frac{\hat n_{d \overline\beta}}{\omega^\prime - E_1}\right) \\
+	&= V^2 n_j\sum_{\beta}\left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega_0 - E_0} + \frac{\hat n_{d \overline\beta}}{\omega_1 - E_1}\right)
 \end{aligned}\end{equation}
 \(q\) runs over the momentum states that are being decoupled at this RG step: \(|q| = \Lambda_j\).
-\(E_{1,0}\) are the diagonal parts of the Hamiltonian at \(\hat n_{d\overline \beta}=1,0\) respectively.
-We have \(\hat n_{d\beta}=1\) in the intermediate state because of the \(c^\dagger_{d\beta}\) in front of the Greens function.
-Applying \(c_{q\beta}\) on the initial state \(\ket{\Psi}_i\) leaves us with \(C^z_q = - \frac{1}{2}\) and \(s^z_q = \frac{1}{2}\overline\beta\).
-We also know that
-\begin{equation}\begin{aligned}
-	\hat n_{d\beta}=1,
-	\begin{cases}
-		\hat n_{d\overline\beta}=0 &\implies S_d^z = \frac{1}{2}\beta, C_d^z = 0, \epsilon_d\left(\hat n_{d\uparrow} - \hat n_{d \downarrow}\right)^2 = \epsilon_d\\	
-		\hat n_{d\overline\beta}=1 &\implies S_d^z = 0, C_d^z = \frac{1}{2}, \epsilon_d\left(\hat n_{d\uparrow} - \hat n_{d \downarrow}\right)^2 = 0
-	\end{cases}
-\end{aligned}\end{equation}
-Combining all this, we can write \(E_1 = \frac{D}{2}\) and \(E_0 = \frac{D}{2} + \epsilon_d - \frac{J}{4}\).
+\(E_{1,0}\) are the diagonal parts of the Hamiltonian at \(\hat n_{d\overline \beta}=1,0\) respectively: \(E_1 = \frac{D}{2}\) and \(E_0 = \frac{D}{2} + \epsilon_d - \frac{J}{4}\).
 In order to relate \(\omega_0\) with \(\omega_1\) with the common fluctuation scale \(\omega\) for the conduction electrons, we will replace these quantum fluctuation scales by the current renormalised values of the single-particle self-energy for the initial state from which we started scattering.
@@
 	\label{ren_ed_Jpp}
-	\frac{J^2}{4}\sum_{q\beta}c^\dagger_{d\overline\beta}c_{d\beta}c^\dagger_{q\beta}c_{-q\overline\beta} \frac{1}{\omega - H_D}c^\dagger_{d\beta}c_{d\overline\beta}c^\dagger_{q\overline\beta}c_{q\beta} = \frac{J^2}{4} n_j\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{\beta}\hat n_{d\overline\beta}\left( 1 - \hat n_{d\beta} \right)
+	\frac{J^2}{4}\sum_{q\beta}c^\dagger_{d\overline\beta}c_{d\beta}c^\dagger_{q\beta}c_{-q\overline\beta} \frac{1}{\omega - H_D}c^\dagger_{d\beta}c_{d\overline\beta}c^\dagger_{q\overline\beta}c_{q\beta}\\
+	= \frac{J^2}{4} n_j\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{\beta}\hat n_{d\overline\beta}\left( 1 - \hat n_{d\beta} \right)
 \end{aligned}\end{equation}
@@
 
-We now have all possible renormalisation to the impurity correlation \(U\).
-To actually compute the renormalisation, we will first calculate the renormalisation in the energies \(\epsilon_0, \epsilon_1\) and \(\epsilon_2\) of the impurity states \(\ket{\hat n_d = 0}, \ket{\hat n_d = 1}, \ket{\hat n_d = 2}\) respectively.
-The renormalisation of these states are given by the following terms:
-\begin{itemize}
-	\item \(\Delta \epsilon_0\) is given by the renormalisation of the term \(\left(1 - \hat n_{d\uparrow}\right)\left(1 - \hat n_{d \downarrow}\right)\)
-	\item \(\Delta \epsilon_1\) is given by the renormalisation of either \(\left(1 - \hat n_{d\uparrow}\right)\hat n_{d \downarrow}\) or \(\left(1 - \hat n_{d\downarrow}\right)\hat n_{d \uparrow}\)
-	\item \(\Delta \epsilon_2\) is given by the renormalisation of \(\hat n_{d\uparrow}\hat n_{d \downarrow}\)
-\end{itemize}
 From eqs.~\ref{ren_ed_Vp}, \ref{ren_ed_Vh}, \ref{ren_ed_Jpp} and \ref{ren_ed_Jph}, we write
 \begin{equation}\begin{aligned}
-	\Delta U = \Delta \epsilon_2 + \Delta \epsilon_0 - 2\Delta \epsilon_1 = -\frac{4V^2 n_j}{\omega + \frac{U_b}{2} - \frac{D}{2} - U/2} + \frac{4V^2 n_j}{\omega + \frac{U_b}{2} - \frac{D}{2} + U/2 + \frac{J}{4}} - \frac{J^2n_j}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~,
+	&\Delta U = \Delta \epsilon_2 + \Delta \epsilon_0 - 2\Delta \epsilon_1 = -\frac{4V^2 n_j}{\omega + \frac{U_b}{2} - \frac{D}{2} - U/2} \\
+	&+ \frac{4V^2 n_j}{\omega + \frac{U_b}{2} - \frac{D}{2} + U/2 + \frac{J}{4}} - \frac{J^2n_j}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{4}J \sum_{k} \left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) c^\dagger_{k\beta}c_{q\beta} = \frac{1}{4}V J n_j \frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right)\sum_{k\beta} \left(1 - \hat n_{d\overline\beta}\right) c_{d\beta}c^\dagger_{k\beta}
+	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{4}J \sum_{k} \left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) c^\dagger_{k\beta}c_{q\beta} \\
+	= \frac{1}{4}V J n_j \frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right)\sum_{k\beta} \left(1 - \hat n_{d\overline\beta}\right) c_{d\beta}c^\dagger_{k\beta}
 \end{aligned}\end{equation}
@@
 
-Note that the \(c_{d\beta}\) in front of the Greens function resulted in \(\left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) \to \left(1 - \hat n_{d\overline\beta}\right)\).
-The intermediate state is characterised by \(\hat n_{d\beta} = 1 - \hat n_{d \overline \beta} = 1\), which means that \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\).
-Moreover, the initial state gives \(\omega_1^\prime = \omega + \epsilon_d\) while the final state gives \(\omega^\prime_2 = \omega\).
-Therefore, the renormalisation becomes
+Substituting the energies and the \(\omega-\)scales, we get
 \begin{equation}\begin{aligned}
-	-\frac{n_j}{4}V J \frac{1}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right)\sum_{k\beta}\left(1 - \hat n_{d\overline\beta}\right) c^\dagger_{k\beta} c_{d\beta}
+	-\left(\frac{\frac{n_j}{4}V J \frac{1}{2}}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{\frac{n_j}{4}V J \frac{1}{2}}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right)\sum_{k\beta}\left(1 - \hat n_{d\overline\beta}\right) c^\dagger_{k\beta} c_{d\beta}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	-\frac{n_j}{8}V J \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta}\left(1 - \hat n_{d\overline\beta}\right)\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
+	-\frac{n_j}{8}V J \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta}\left(1 - \hat n_{d\overline\beta}\right)\\
+	\times \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
 \end{aligned}\end{equation}
 
-We now consider the spin-exchange processes involving \(S_d^\pm\):
+If we similarly calculate the contributions from the spin-exchange processes involving \(S_d^\pm\), we get
 \begin{equation}\begin{aligned}
-	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{2}J \sum_{k} c^\dagger_{d\beta}c_{d\overline\beta} c^\dagger_{k\overline\beta}c_{q\beta} = \frac{1}{2}V J n_j \frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) c_{d\overline\beta}c^\dagger_{k\overline\beta}
-\end{aligned}\end{equation}
-We again have \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4},\omega_1^\prime = \omega + \epsilon_d\) and \(\omega_2^\prime = \omega\), which gives
-\begin{equation}\begin{aligned}
-	-\frac{1}{4}V J n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)c^\dagger_{k\overline\beta} c_{d\overline\beta}
-\end{aligned}\end{equation}
-Combining this with the Hermitian conjugate obtained from exchanging the processes gives
-\begin{equation}\begin{aligned}
-	-\frac{1}{4}V J n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)\left(c^\dagger_{k\overline\beta} c_{d\overline\beta} + \text{h.c.}\right)
+	-\frac{1}{4}V J n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)\\
+	\times \left(c^\dagger_{k\overline\beta} c_{d\overline\beta} + \text{h.c.}\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	-\frac{3n_j}{8}V J \left(\frac{1}{\omega +U_b/4 - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega +U_b/4 - \frac{D}{2} + U/2 + \frac{J}{4}}\right) \sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
+	-\frac{3n_j}{8}V J \left(\frac{1}{\omega +U_b/4 - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega +U_b/4 - \frac{D}{2} + U/2 + \frac{J}{4}}\right)\\
+	\times\sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	&\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{k\beta} \hat n_{q\overline\beta} \frac{1}{\omega - H_D} c^\dagger_{d\beta}c_{q\beta} \\
-	&= n_jU_b V\sum_{k\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_1 - E_1} + \frac{1}{\omega^\prime_1 - E_1}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_0 - E_0} + \frac{1}{\omega_0^\prime - E_0}\right)\right] c^\dagger_{d\beta}
-\end{aligned}\end{equation}
-\(E_1\) and \(E_0\) are the intermediate state energies for \(\hat n_{d\overline\beta}=1\) and 0 respectively.
-\(\omega_{1,0}\) are the quantum fluctuation scales for the corresponding initial states.
-\(\omega^\prime_{1,0}\) are the fluctuation scales for the corresponding final states.
-The intermediate energies are \(E_1 = D/2 - U_b/4 - K/4,~ ~ ~ E_0 = D/2 - U_b/4 - U/2 - J/4\).
-The fluctuation scales are \(\omega_1 = \omega - U/2= \omega_0^\prime,~ ~ ~ \omega_1^\prime = \omega = \omega_0\).
-Substituting these gives
-\begin{equation}\begin{aligned}
-	-n_jU_b V\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
-+\left.
-\frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+	&\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{k\beta} \hat n_{q\overline\beta} \frac{1}{\omega - H_D} c^\dagger_{d\beta}c_{q\beta} = \\
+	&-\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{n_jU_b V}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} + \frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right) \right.\\
+	&+ \left.\frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
-	+ \left.\frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+	&-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)\left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} \right.\right.\\
+	&+ \left.\left.
+\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} \right.\right.\\
+	&+\left.\left. \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
 \end{aligned}\end{equation}
 
+\begin{widetext}
 In the hole sector, we have
 \begin{equation}\begin{aligned}
-	&\sum_{q\beta}\sum_{k}U_b V \hat n_{q\overline\beta} c^\dagger_{k\beta}c_{q\beta} \frac{1}{\omega - H_D} c^\dagger_{q\beta}c_{d\beta}\\
-	&-\sum_{q\beta}\sum_{k}U_b V \left(1 - \hat n_{q\overline\beta}\right) c^\dagger_{k\beta}c_{q\beta} \frac{1}{\omega - H_D} c^\dagger_{q\beta}c_{d\beta}\\
+	&\sum_{q\beta}\sum_{k}U_b V \hat n_{q\overline\beta} c^\dagger_{k\beta}c_{q\beta} \frac{1}{\omega - H_D} c^\dagger_{q\beta}c_{d\beta} -\sum_{q\beta}\sum_{k}U_b V \left(1 - \hat n_{q\overline\beta}\right) c^\dagger_{k\beta}c_{q\beta} \frac{1}{\omega - H_D} c^\dagger_{q\beta}c_{d\beta}\\
 	&= -n_jU_b V\sum_{k\beta} c^\dagger_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_1 - E_1} + \frac{1}{\omega^\prime_1 - E_1}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_0 - E_0} + \frac{1}{\omega_0^\prime - E_0}\right)\right] c_{d\beta}
@@
 \begin{equation}\begin{aligned}
-	-n_jU_b V\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{1 - \hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
-+\left. \frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+	-n_jU_b V\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{1 - \hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right) + \frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \frac{1}{2}\left[\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
-+\left. \left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+	-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \frac{1}{2}\left[\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right) + \left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
 \end{aligned}\end{equation}
-
-Combining with the renormalisation from \(J\), the complete RG equation for \(V\) becomes
-\begin{equation}\begin{aligned}
-	\Delta V =& -\frac{3n_j V}{8}\left[\left(\frac{J}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} + \frac{J}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}}\right) + K \left(\frac{K}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{K}{\omega - \frac{D}{2} + \frac{U_b}{4} - \frac{U}{2} + \frac{K}{4}}\right)\right]\\
-		 &-\frac{n_jU_b}{2}\left[\left(\frac{V}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) + \left(\frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]\\
-		 &=-\frac{n_j V}{8}\left[\left(\frac{3J + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} + \frac{3J + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}}\right) + \left(\frac{3K + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{3K + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} - \frac{U}{2} + \frac{K}{4}}\right)\right]
-\end{aligned}\end{equation}
-The RG equation for \(V\) is
-\begin{equation}\begin{aligned}
-	\Delta V = -\frac{3n_j V}{8}\left[J\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)\right]
-\end{aligned}\end{equation}
+\end{widetext}
 
@@
 \begin{equation}\begin{aligned}
-	-\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^+ c^\dagger_{q\downarrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D}S_d^z c^\dagger_{k \downarrow}c_{q \downarrow} = n_j \frac{1}{4}J^2 \left(-\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~,\\
-	\sum_{q} \sum_{kk^\prime} \frac{1}{4}J^2 S_d^z c^\dagger_{q \uparrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D} S_d^+ c^\dagger_{k\downarrow}c_{q \uparrow} = -n_j \frac{1}{4}J^2 \left(\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~.
+	-\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^+ c^\dagger_{q\downarrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D}S_d^z c^\dagger_{k \downarrow}c_{q \downarrow} \\
+	= n_j \frac{1}{4}J^2 \left(-\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~,\\
+	\sum_{q} \sum_{kk^\prime} \frac{1}{4}J^2 S_d^z c^\dagger_{q \uparrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D} S_d^+ c^\dagger_{k\downarrow}c_{q \uparrow} \\
+	= -n_j \frac{1}{4}J^2 \left(\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^+ c^\dagger_{k\downarrow}c_{q \uparrow} \frac{1}{\omega - H_D}S_d^z c^\dagger_{q \uparrow}c_{k^\prime \uparrow} = n_j \frac{1}{4}J^2 \left(-\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~,\\
-	-\sum_{q} \sum_{kk^\prime} \frac{1}{4}J^2 S_d^z c^\dagger_{k \downarrow}c_{q \downarrow} \frac{1}{\omega - H_D} S_d^+ c^\dagger_{q\downarrow}c_{k^\prime \uparrow} = -n_j \frac{1}{4}J^2 \left(\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~.
+	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^+ c^\dagger_{k\downarrow}c_{q \uparrow} \frac{1}{\omega - H_D}S_d^z c^\dagger_{q \uparrow}c_{k^\prime \uparrow}\\
+	= n_j \frac{1}{4}J^2 \left(-\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~,\\
+	-\sum_{q} \sum_{kk^\prime} \frac{1}{4}J^2 S_d^z c^\dagger_{k \downarrow}c_{q \downarrow} \frac{1}{\omega - H_D} S_d^+ c^\dagger_{q\downarrow}c_{k^\prime \uparrow} \\
+	= -n_j \frac{1}{4}J^2 \left(\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} S_d^+ c^\dagger_{q \downarrow} c_{k \uparrow} \frac{1}{\omega - H_D} \hat n_{q \uparrow} c^\dagger_{k^\prime \downarrow}c_{q \downarrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
+	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} S_d^+ c^\dagger_{q \downarrow} c_{k \uparrow} \frac{1}{\omega - H_D} \hat n_{q \uparrow} c^\dagger_{k^\prime \downarrow}c_{q \downarrow} \\
+	= -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \downarrow} c^\dagger_{q \uparrow} c_{k \uparrow} \frac{1}{\omega - H_D}S_d^+ c^\dagger_{k^\prime \downarrow} c_{q \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
+	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \downarrow} c^\dagger_{q \uparrow} c_{k \uparrow} \frac{1}{\omega - H_D}S_d^+ c^\dagger_{k^\prime \downarrow} c_{q \uparrow} \\
+	= -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{q \uparrow} \frac{1}{\omega - H_D} \hat n_{q \downarrow} c^\dagger_{q \uparrow}c_{k \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
+	-\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}~,\\
+	-\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
 \end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \uparrow} c^\dagger_{k^\prime \downarrow} c_{q \downarrow} \frac{1}{\omega - H_D}S_d^+ c^\dagger_{q \downarrow} c_{k \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
-\end{aligned}\end{equation}
-
-Combining all these terms, we get the updated RG equation for \(J\):
-\begin{equation}\begin{aligned}
-	\Delta J = -J n_j\frac{4 U_b + J}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}}
-\end{aligned}\end{equation}
-
-\end{widetext}
-
 \end{document}

### 2022-05-05 gen-siam-manuscript/gen-siam.tex
--no-message

@@
 One of the most well-studied impurity models is the single-impurity Anderson model; it consists of a single impurity site of spin-half electrons and local correlation \(U\) hybridising with a non-interacting conduction bath through a coupling \(V\).
+One of the most well-studied of these is the single-impurity Anderson model~\cite{anderson_1961,anderson_1978} (AIM), consisting of a single correlated impurity site coupled with a non-interacting conduction bath.
+The model combines localisation arising from Mott physics~\cite{Mott_1949,vanvleck_1953} and delocalisation of the impurity arising from virtual resonance with the conduction bath~\cite{friedel_1956}.
 

### 2022-05-05 gen-siam-manuscript/gen-siam.tex
completed introduction and started conclusions

--- 2022-05-04 gen-siam-manuscript/gen-siam.tex
@@
 \usepackage{braket,amsmath,graphicx,color}
-\usepackage{hyperref}
-\bibliographystyle{apsrev4-1}
+\usepackage[hidelinks]{hyperref}
+\bibliographystyle{apsrev4-2}
 \begin{document}
@@
 They consist of one or more local correlated quantum system(s) coupled with (typically non-interacting) bosonic or fermionic conduction bath channel(s).
-Even though the impurity itself is simple, the interaction with the bath often leads to novel phases, and such impurity systems often lead to interesting phenomena that have far-reaching consequences and require fundamental theoretical breakthroughs in order to understand them.
-One of the most well-studied impurity models is the single-impurity Anderson model; it consists of a single impurity site of spin-half electrons and local correlation \(U\) hybridising with a non-interacting conduction bath through a coupling \(V\).
+Even though the impurity itself is usually simple, the interaction with the bath is what turns it into a correlated many-body problem, and leads to novel emergent phases.
+Such impurity systems often give rise to interesting phenomena that have far-reaching consequences and require fundamental theoretical breakthroughs in order to understand them.
+One of the most well-studied of these is the single-impurity Anderson model~\cite{anderson_1961,anderson_1978} (AIM), consisting of a single impurity site with local correlation \(U\) hybridising with a non-interacting fermionic conduction bath through a coupling \(V\).
+The model combines impurity localisation arising from Mott physics~\cite{Mott_1949,vanvleck_1953} and impurity delocalisation arising from virtual resonance with the conduction bath~\cite{friedel_1956}.
+In order to obtain its low-energy behaviour, the AIM (along with its \(U \to \infty\) limit, the Kondo model, as well as the \(U \to -\infty\) limit~\cite{schrieffer1966,taraphder_1991}) has been studied using several analytical and numerical techniques like the Coulomb gas approach~\cite{anderson1969exact,anderson1970exact}, perturbative renormalisation group~\cite{anderson1970,haldane1978scaling,jefferson_1977}, numerical renormalisation group (NRG)~\cite{wilson1975,hrk_wilson_1980}, the Bethe ansatz~\cite{andrei_1980,andreiKondoreview,Wiegmann_1981,tsvelickKondoreview}, bosonization~\cite{kotliar_1996,Duki_2011,borda_2008}, functional renormalisation group~\cite{streib_2013} and, most recently, a unitary renormalisation group approach~\cite{anirban_kondo}.
+The general conclusion for the positive \(U\) case at \(T=0\) is that on the particle-hole symmetric (that is, half-filled) line where the holon and doublon impurity levels are degenerate with each other, the impurity local moment is always screened by the conduction bath through enhanced spin-flip scattering at low-energies, leading to a macroscopic singlet ground state and local Fermi liquid gapless excitations~\cite{nozaki2012,mora_2015}; there is no transition to any unscreened phase for a half-filled impurity.
+The group of conduction electrons that participate in forming the singlet and perform the screening are commonly referred to as the Kondo cloud~\cite{sorensen_erik_affleck_1996,affleck_ian_2001,simon_pascal_2003,martin2010,martin2019}.
+Because of technological advances, it has become possible to create such Kondo systems and observe this Kondo cloud in quantum dots using scanning tunnelling spectroscopy (STS) and other techniques~\cite{Goldhaber-Gordon1998,Cronenwett1998,Schmid_Weis1998,pustilnik_glazman_2004,Borzenets2020,neel_berndt_2008,Zhao2005}.
 
-One method of studying Hubbard models is through auxiliary models, described in the next section.
-Auxiliary models are simpler versions of the full Hamiltonian that are able to capture the essential physics.
-For example, a correlated impurity interacting with a conduction bath is a potential auxiliary model for the Hubbard Hamiltonian:
-The impurity has onsite energy \(\epsilon_d\) and an onsite correlation \(U\). It hybridises into the bath through \(V\).
+Even though the AIM as well as the Kondo model have been successfully solved, they find use as auxiliary models in the dynamical mean-field theory~\cite{kuramoto1987,Cox1988,metzner_volhardt_1989,kotliar1992}(DMFT)-based methods of solving bulk lattice problems.
+Once a bulk model is given in terms of some parameters, the workflow of DMFT in solving this model typically involves (i) starting with an AIM (with a non-interacting bath) defined by the bulk parameters, (ii) calculating its self-energy using impurity solvers like exact diagonalisation~\cite{stanescu_2006,capone2007,sakai_2009}, NRG~\cite{bulla_1998,bulla_1999,bulla2001,zitzler_2004}, quantum Monte Carlo~\cite{hirsch1986,rozenberg1997,gull_2011} or density-matrix renormalisation group~\cite{white1992,peschel_1999,garcia2004,schollwock2005,hallberg2006,garcia2007,garcia2007_prb} (DMRG), (iii) equating the bath \(k-\)space self-energy to the impurity self-energy obtained in the previous step, and (iv) restarting the process with a new AIM defined by the new self-energy.
+This continues iteratively until the impurity self-energy converges and becomes equal to the bath self-energy.
+The results can be shown to become asymptotically exact in the limit of infinite dimensionality \((d=\infty)\).
+Improvements, like introducing non-locality in the self-energy, can be introduced by replacing the single impurity with a cluster of multiple impurities~\cite{parcollet_2004,maier_2005,kotliar_rmp_2006,ohashi_2008}.
 
-If the impurity site hybridises with a {\it non-interacting} bath defined by a uniform density of states, the impurity spectral function is found to have a well-defined Kondo resonance at low temperatures.
-Increasing the impurity correlation \(U\) only serves to reduce the width of the central peak at the cost of the appearance of side bands at energy scales of the order of \(U\), but the resonance never dies.
-The situation is however different if the impurity is embedded in a correlated conduction bath with a non-trivial density of states.
-For the case of a conduction band with the DOS shown in the right of the figure below, the impurity hybridises into a reduced bandwidth because of the correlation on the lattice~\cite{held_2013}.
-
-This difference in the type of conduction baths is utilized in dynamical mean-field theory to describe various phases of the bulk system.
-This is done through the DMFT algorithm: one starts with a non-interacting bath, but depending on the value of \(U\), the conduction bath then gets modified and we ultimately end up with something that is different from what we started with.
-For small \(U\), the bath does not change much and we retain the central resonance of the impurity spectral function.
-This then describes a metal in the bulk.
-For larger values of \(U\), however, the bath changes significantly such that its density of states becomes non-constant.
-Above a critical \(U_c\), the impurity spectral function gets gapped out, and that then describes the insulating phase in the bulk.
-\textit{This leaves open the following question}: What is the minimal correlation one can insert into the non-interacting bath (of a single-impurity Anderson model) that can capture both the metallic and insulating phases of the bulk model?
+One of the primary motivations and applications of DMFT has been the study of the Mott metal-insulator transition (MIT)~\cite{Mott_1949} in the Hubbard model~\cite{gutzwiller_1963,kanamori_1963,hubbard1963electron}.
+The Hubbard model is believed to lie at the heart of the high-\(T_c\) problem and has achieved cult status in the field of strongly-correlated electrons because of the array of interesting phases it hosts~\cite{keimer2015quantum,arovas_2022,qin_2022}, ranging from antiferromagnetic long-range order and spin liquids to spin- and charge-density waves and unconventional superconductivity.
+The model has been found to be relevant to several materials like the high-\(T_c\) copper oxides~\cite{zhangrice-physrevb.37.3759}, the high-\(T_c\) nickelates~\cite{Kitatani2020} and organic salts~\cite{scriven_2009}.
+Using the AIM as the auxiliary model, an MIT was demonstrated in the \(d=\infty\) Hubbard model at zero temperature and half-filling~\cite{zhang_1993}.
+The transition is seen through the evolution of the real-space local spectral function (schematically shown in Fig.~\ref{spec-func_scheme}), and the behaviour until the transition is very similar to that of the impurity spectral function in the AIM~\cite{hewson1993}.
 
@@
 	\centering
-\includegraphics[width=0.5\textwidth]{dos_diff.pdf}
-\caption{Two kinds of bath that an impurity can hybridise into.
-The left panel shows a non-interacting conduction band with a flat density of states.
-The right panel shows an interacting bath with an energy-dependent density of states.
-In the latter case, the impurity "feels" a reduced effective bandwidth defined by the width of the central peak.}
+	\includegraphics[width=0.35\textwidth]{spec_func.pdf}
+	\caption{Schematic description of the evolution of the density of states across the transition~\cite{zhang_1993}.}
+	\label{spec-func_scheme}
 \end{figure}
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
+Despite the success of DMFT and its cluster-variants, certain points remain to be addressed:
+\begin{itemize}
+	\item What is the minimal impurity model that can act as an auxiliary model for describing an MIT of the Mott kind?
+	\item Having obtained such a minimal model, can we create a formalism that relates (in a transparent and tractable manner) the physics of the bulk to that of the auxiliary model?
+	\item Can we then, using such a formulation, try to extract the fluctuations that destabilise the metal and lead to the Mott insulator, as well as study other aspects of the MIT?
+\end{itemize}
+The reliance of DMFT on the iterative route towards self-consistency means that the impurity auxiliary model gets highly correlated in the process~\cite{held2008}, and no single impurity model can be related to the bulk; for the same reason, it is also not possible, at present, to relate the properties of the auxiliary models to those of the full model.
+In this {\color{blue}work}, we will focus mostly on the first question, but we will provide hints about the third question as well.
+Since it has already been established that the AIM does not feature a transition, it is incapable of describing an MIT.
+This warrants the introduction of additional physics that can destabilise the Kondo cloud.
+
+The paper is structured as follows.
+Sec.~\ref{def-ham} describes the extended model that we will be studying in this {\color{blue}work}.
+In Sec.~\ref{method}, we talk about the renormalisation group technique that we employ to study the model and the RG equations obtained from them.
+Sec.~\ref{phase} lays out the phase diagram and demonstrates the phase transition.
+Sec.~\ref{eff-ham} gives the effective Hamiltonians in various phases and the zero-bandwidth limits of the ground states.
+In Sec.~\ref{descr}, we give additional insight into the transition by tracking it via entanglement measures and two-particle correlations.
+We conclude in Sec.~\ref{concl} with some discussions and possible future directions.
+
+\subsection*{Summary of results}
+
+\begin{itemize}
+	\item {\color{blue}Indeed}, we find that on extending the AIM with a spin-exchange interaction \(J\) between the impurity site and the site it is coupled to (zeroth site), and an attractive correlation \(U_b\) on the zeroth site, the enhanced model shows a phase transition under a renormalisation group treatment, at a critical value \(\left(-U_b/J\right)_c=1/4\).
+	\item The ground state can be shown to evolve from a singlet between the impurity and the zeroth site to a decoupled local moment on the impurity, through a correlated state with both spin and charge content.
+	\item The transition can be tracked through the variation of the geometric entanglement, which starts from zero in the screened phase and reaches its maximum value of 1 in the local moment phase.
+	\item The impurity spectral function shows a three-peak structure at the critical point, similar to the AIM, and develops a gap beyond that.
+\end{itemize}
 
 \section{The generalised Anderson impurity model}
+\label{def-ham}
 
@@
 \section{Method and RG Equations}
+\label{method}
 
@@
 The focus here is on obtaining the low-energy phases of the GAIM.
-To accomplish this, we perform a renormalisation group analysis of the associated Hamiltonian (eq.~\ref{GIAM-ham}) using the recently developed unitary renormalisation group (URG) method \cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome,1dhubjhep,Mukherjee_mott_merg,anirban_kondo}.
+To accomplish this, we perform a renormalisation group analysis of the associated Hamiltonian (eq.~\ref{GIAM-ham}) using the recently developed unitary renormalisation group (URG) method \cite{anirbanurg1,anirbanurg2}.
+The method has been applied on a wide variety of problems involving quantum spins and correlated fermions, like the Kagome antiferromagnet~\cite{santanukagome}, the 1D~\cite{1dhubjhep} and 2D Hubbard models, with~\cite{anirbanmott2} and without hole doping~\cite{anirbanmott1}, the reduced-BCS pairing hamiltonian~\cite{siddharthacpi}, the single-channel ~\cite{anirban_kondo} as well as multi-channel~\cite{patra_mck} Kondo problems, and other fermionic lattice problems with and without translation invariance~\cite{anirbanurg1,anirbanurg2}.
 The unitary RG transformations lead to a series of Hamiltonians \(H_{(j)}\) related to the Hamiltonian at the previous step through a unitary transformation; the unitary transformations are defined by the requirement that they remove number fluctuations in high-energy \(k-\)states, thus making the Hamiltonian progressively more block-diagonal in momentum space.
@@
 \section{RG flows and phase diagram}
+\label{phase}
 
@@
 \begin{figure}[!htb]
-	\includegraphics[width=0.5\textwidth]{phase-map-MIT.pdf}
+	\includegraphics[width=0.48\textwidth]{phase-map-MIT.pdf}
 	\caption{Phase diagram of the GAIM, in the space of couplings \(U_0\) and \(J_0\).
@@
 \section{Low-energy effective Hamiltonian and the ground state}
+\label{eff-ham}
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{J_bandwidth.pdf}
+	\includegraphics[width=0.48\textwidth]{J_bandwidth.pdf}
 	\caption{Increase of \(J^*\) in comparison to \(V^*\) when going towards the thermodynamic limit.}
@@
 \end{equation}
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
@@
 \end{aligned}\end{equation}
-Since the interactions are marginal or only slightly relevant, the kinetic energy is no longer negligible compared to them, and it is not possible to faithfully take a zero bandwidth limit of the problem.
+
 \subsection{Nature of ground state near the critical point}
@@
 
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
-\includegraphics[width=0.5\textwidth]{corrs_gs.pdf}
+\includegraphics[width=0.48\textwidth]{corrs_gs.pdf}
 \caption{Overlap of the RG fixed point ground state \(\ket{\Psi}_\text{gs}\) with the spin singlet state \(\ket{\text{ss}}\) and the charge triplet state \(\ket{\text{ct}}\), for a range of values of the transition tuning ratio \(r\).
@@
 \section{Descriptors of the transition}
+\label{descr}
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{Add.pdf}
+	\includegraphics[width=0.48\textwidth]{Add.pdf}
 	\caption{Impurity spectral function \(A_d(\omega)\) at three values of the ratio \(r\).
@@
 
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
-	\includegraphics[width=0.5\textwidth]{entanglement.pdf}
+	\includegraphics[width=0.48\textwidth]{entanglement.pdf}
 	\caption{Variation of \(\sqrt{\left(1 - \varepsilon_\text{ss} \right)}\sqrt{\left(1 - \varepsilon_\text{ct} \right)}\) as \(r\) is increased towards the critical value 0.25.
@@
 
-\begin{figure}[htpb]
+\begin{figure}[!htb]
 	\centering
-	\includegraphics[width=0.5\textwidth]{odlro_d0.pdf}
+	\includegraphics[width=0.48\textwidth]{odlro_d0.pdf}
 	\caption{Variation of spin-flip correlation and charge isospin-flip correlation across the transition.}
@@
 \section{Discussions and Outlook}
-CC
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
+\label{concl}
+
+In summary, we have shown that adding spin-exchange physics between impurity and bath and local atractive correlation in the bath lead to a model with multiple phases.
+We have demonstrated this phase transition under a renormalisation group treatment, and provided the effective Hamiltonians and simplified wavefunctions for the various phases.
+The phase transition can be observed through the discontinuous behaviour in the ground state, as well as through the appearance of a gap in the impurity spectral function.
+We also draw a connection between the change in the spectral function and some geometric measures of entanglement; this allows tracking the phase transition via these measures.
+
+Having summarised the main results, we now discuss some additional interesting features.
+We note that the GAIM as defined here represents the most minimal impurity model that supports a phase transition - both the \(J\) and \(U_b\) are crucial to stabilising the local moment.
+With just \(J\) or just \(U_b\), the low-energy phase is always of the local Fermi liquid kind.
+The introduction of the attractive \(U_b\) term is most interesting because it shows that pairing fluctuations in the bath are necessary to suppress the Kondo physics arising from spin fluctuations(fig.~\ref{pair_fluc}).
+Moreover, we find that there is a subdominant tendency towards transfer of local ``Cooper pairs" between the impurity and zeroth sites (Fig.~\ref{charge-spin}).
+This is reminiscent of a similar subdominant superconducting tendency in the half-filled Hubbard model as observed from a unitary RG treatment~\cite{anirbanmott1,anirbanmott2}.
 
 \begin{itemize}
-	\item discuss why the model is minimal
+	\item mention that entanglement acts like an order parameter
 \end{itemize}

### 2022-05-05 gen-siam-manuscript/gen-siam.tex
completed introduction

@@
 \usepackage{braket,amsmath,graphicx,color}
-\usepackage[hidelinks]{hyperref}
-\bibliographystyle{apsrev4-2}
+\usepackage{hyperref}
+\bibliographystyle{apsrev4-1}
 \begin{document}
@@
 where \(\left\{\uparrow_d, \downarrow_d\right\}, \left\{\uparrow_0, \downarrow_0\right\}\) are the spin states of the impurity and zeroth sites respectively.
-As mentioned before, this regime in the GAIM is adiabatically connected to the AIM, and indeed, such a spin-singlet ground state is also obtained in the AIM from other methods like Poor Man's scaling~\cite{anderson1969exact,anderson1970}, numerical renormalisation group~\cite{wilson1975,hrk_wilson_1980}, Bethe ansatz~\cite{}, conformal field theory methods~\cite{}[CITE] and the URG analysis of the Kondo model~\cite{anirban_kondo}.
+As mentioned before, this regime in the GAIM is adiabatically connected to the AIM, and indeed, such a spin-singlet ground state is also obtained in the AIM from other methods like Poor Man's scaling~\cite{anderson1969exact,anderson1970}, numerical renormalisation group~\cite{wilson1975,hrk_wilson_1980}, the Bethe ansatz~\cite{andrei_1980,andreiKondoreview,Wiegmann_1981,tsvelickKondoreview}, bosonization~\cite{kotliar_1996,Duki_2011,borda_2008}, functional renormalisation group~\cite{streib_2013} and the URG analysis of the Kondo model~\cite{anirban_kondo}.
 
@@
 	\item[2.] How do entanglement measures behave across the transition?
-	\item[3.] How does the Kondo screening cloud~\cite{}[CITE] respond as the system is driven critical?
+	\item[3.] How does the Kondo screening cloud~\cite{sorensen_erik_affleck_1996,affleck_ian_2001,simon_pascal_2003,martin2010,martin2019} respond as the system is driven critical?
 \end{itemize}
@@
 We assume that the global phase of the wavefunctions are real, and since the internal weights of the wavefunctions are real as well, the overlaps \(\braket{\text{ss}|\Psi^{(2)}_\text{gs}},\braket{\text{ct}|\Psi^{(2)}_\text{gs}}\) are also real.
-We can use these overlaps to define a geometric measure of entanglement:
+We can use these overlaps to define a geometric measure of entanglement~\cite{shimony1995degree,wei2003geometric,horodecki2009quantum}:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-[CITE]
 If \(\ket{\psi_1}\) is thought of as a separable state, then \(\ket{\psi_2}\) should be less entangled if it's overlap with \(\ket{\psi_1}\) is large, which is indeed borne out by the definition.
@@
 On the other hand, if the ground state cannot be written in separable form, the EE of the sum, \(S(A \cup B)\) is more than the sum of its parts because of the additional entanglement between \(A\) and \(B\), and we get \(I(A:B) > 0\).
+In recent times, such measures of entanglement have often been used to study Kondo impurity~\cite{Srensen2006}, heavy-fermionic~\cite{parisen_2019} and other impurity systems~\cite{dong_2021}.
 
@@
 
-Having summarised the main results, we now discuss some additional interesting features.
+Having summarised the main results, we now discuss some additional notable insights.
 We note that the GAIM as defined here represents the most minimal impurity model that supports a phase transition - both the \(J\) and \(U_b\) are crucial to stabilising the local moment.
@@
 This is reminiscent of a similar subdominant superconducting tendency in the half-filled Hubbard model as observed from a unitary RG treatment~\cite{anirbanmott1,anirbanmott2}.
+It is also intriguing to see that the geometric entanglement \(\chi = \sqrt{1 -\varepsilon_\text{SS}}\sqrt{1 -\varepsilon_\text{CT}}\) emerges as an order parameter for the impurity transition: it is zero in the local moment phase and non-zero in the screened phase.
+The discontinuous change in \(\chi\) is intimately connected to the fact that this phase transition is topological in nature~\cite{oshikawa2000topological,seki2017topological} -  the Luttinger volume of the conduction bath changes by 1~\cite{martin-physrevlett.48.362}.
 
-\begin{itemize}
-	\item mention that entanglement acts like an order parameter
-\end{itemize}
+Future studies can involve working with a general filling on the impurity site; this might allow the pair fluctuations between the impurity and zeroth site to become the dominant interaction, leading to a "local superconducting instability".
+Another important application of this model involves the following: Given a suitable analytical framework, the auxiliary model obtained here can be ``tiled" throughout the lattice to create a bulk model, and the impurity phase transition observed here will then get promoted to a bulk metal-insulator transition.
+Finer details like electronic differentiation in \(k-\)space can also be captured by taking more number of impurities in the auxiliary model~\cite{sakai_2009}.
 
@@
 \end{aligned}\end{equation}
+\end{widetext}
 \(E_1 = D/2 - U_b/4 - U/2 - J/4,~ ~ ~ E_0 = D/2 - U_b/4 - K/4\).
@@
 \begin{equation}\begin{aligned}
-	-n_jU_b V\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{1 - \hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right) + \frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+	-\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{1 - \hat n_{d\overline\beta}}{2}\left(\frac{n_jU_b V}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} + \frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right)\right.\\
+	+ \left.\frac{\hat n_{d\overline\beta}}{2}\left(\frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \frac{1}{2}\left[\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right) + \left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+	-\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \left[\left(\frac{n_jU_b V/2}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} + \frac{n_jU_b V/2}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right) \right.\\
+	+ \left.\left(\frac{n_jU_b V/2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{n_jU_b V/2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
 \end{aligned}\end{equation}
-\end{widetext}
 

### 2022-05-06 gen-siam-manuscript/gen-siam.tex
Added universal phase diagram to conclusions

@@
 	\item Can we then, using such a formulation, try to extract the fluctuations that destabilise the metal and lead to the Mott insulator, as well as study other aspects of the MIT?
+	\item {\color{blue}Can such an impurity model give rise to a universal phase diagram consisting of a gapped ordered phase that leads into a superconducting phase below a metallic phase, as is often encountered in strongly-correlated systems?}
 \end{itemize}
 The reliance of DMFT on the iterative route towards self-consistency means that the impurity auxiliary model gets highly correlated in the process~\cite{held2008}, and no single impurity model can be related to the bulk; for the same reason, it is also not possible, at present, to relate the properties of the auxiliary models to those of the full model.
-In this {\color{blue}work}, we will focus mostly on the first question, but we will provide hints about the third question as well.
+In this {\color{blue}paper}, we will focus mostly on the first question, but we will provide hints about the third question as well.
 Since it has already been established that the AIM does not feature a transition, it is incapable of describing an MIT.
 This warrants the introduction of additional physics that can destabilise the Kondo cloud.
-
-The paper is structured as follows.
-Sec.~\ref{def-ham} describes the extended model that we will be studying in this {\color{blue}work}.
-In Sec.~\ref{method}, we talk about the renormalisation group technique that we employ to study the model and the RG equations obtained from them.
-Sec.~\ref{phase} lays out the phase diagram and demonstrates the phase transition.
-Sec.~\ref{eff-ham} gives the effective Hamiltonians in various phases and the zero-bandwidth limits of the ground states.
-In Sec.~\ref{descr}, we give additional insight into the transition by tracking it via entanglement measures and two-particle correlations.
-We conclude in Sec.~\ref{concl} with some discussions and possible future directions.
 
@@
 \end{itemize}
+
+\subsection*{Layout of the {\color{blue}paper}}
+
+The paper is structured as follows.
+Sec.~\ref{def-ham} describes the extended model that we will be studying in this {\color{blue}paper}.
+In Sec.~\ref{method}, we talk about the renormalisation group technique that we employ to study the model and the RG equations obtained from them.
+Sec.~\ref{phase} lays out the phase diagram and demonstrates the phase transition.
+Sec.~\ref{eff-ham} gives the effective Hamiltonians in various phases and the zero-bandwidth limits of the ground states.
+In Sec.~\ref{descr}, we give additional insight into the transition by tracking it via entanglement measures and two-particle correlations.
+We conclude in Sec.~\ref{concl} with some discussions and possible future directions.
 
@@
 
-In summary, we have shown that adding spin-exchange physics between impurity and bath and local atractive correlation in the bath lead to a model with multiple phases.
+In summary, we have shown that adding spin-exchange physics between impurity and bath and local attractive correlation in the bath lead to a model with multiple phases.
 We have demonstrated this phase transition under a renormalisation group treatment, and provided the effective Hamiltonians and simplified wavefunctions for the various phases.
@@
 
-Future studies can involve working with a general filling on the impurity site; this might allow the pair fluctuations between the impurity and zeroth site to become the dominant interaction, leading to a "local superconducting instability".
-Another important application of this model involves the following: Given a suitable analytical framework, the auxiliary model obtained here can be ``tiled" throughout the lattice to create a bulk model, and the impurity phase transition observed here will then get promoted to a bulk metal-insulator transition.
-Finer details like electronic differentiation in \(k-\)space can also be captured by taking more number of impurities in the auxiliary model~\cite{sakai_2009}.
+Possible directions for future studies include working with a general filling on the impurity site; this might allow the pair fluctuations between the impurity and zeroth site to become the dominant interaction, leading to a ``local superconducting instability".
+An important application of this model involves the following: Given a suitable analytical framework that restores translation symmetry, the auxiliary model obtained here can be ``tiled" throughout the lattice to create a bulk model, and the impurity phase transition observed here will then get promoted to a bulk metal-insulator transition.
+Finer details like electronic differentiation in \(k-\)space can be captured by considering more number of impurities connected to each other through single-particle hopping or RRKY-like interaction~\cite{Ferrero2007,sakai_2009}.
+In general, the presence of multiple and varied classes of correlations in the auxiliary model - localisation tendency from Mott physics, delocalisation tendency from the spin and charge fluctuations, and pairing tendency from the local correlation term - makes this a strong candidate for describing various kinds of phases (Fig.~\ref{universal}).
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.48\textwidth]{universal_phase_diagram.pdf}
+	\caption{Phase diagram for strongly-correlated electronic systems}
+	\label{universal}
+\end{figure}
 
 \acknowledgments
-Abhirup Mukherjee thanks IISER Kolkata for funding through a research fellowship.
-S.
-Lal thanks the SERB, Govt.
-of India for funding through MATRICS grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
+AM thanks IISER Kolkata for funding through a research fellowship. S. Lal thanks the SERB, Govt. of India for funding through MATRICS grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
 
@@
 
-\section{Derivation of RG equations for the generalised Anderson impurity model}
+\section{Derivation of RG equations}
 

### 2022-05-06 gen-siam-manuscript/gen-siam.tex
Added final figures

@@
 \bibliographystyle{apsrev4-1}
+\allowdisplaybreaks
+
 \begin{document}
@@
 \begin{equation}\begin{aligned}
+	\label{green_spectral}
 G_d(\omega) = \sum_n \left[ \frac{|\braket{\Psi_\text{gs} | c_{d\sigma} | \Psi_n}|^2}{\omega + E_\text{gs} - E_n} + \frac{|\braket{\Psi_n | c_{d\sigma} | \Psi_\text{gs}}|^2}{\omega - E_\text{gs} + E_n}\right]
@@
 \begin{equation}\begin{aligned}
+	\label{gs-ss}
 	\ket{\Psi}_\text{gs} = \ket{\Phi}_{ss}\braket{\text{ss}|\Psi^{(2)}_\text{gs}} + \ket{\Phi}_{ct}\braket{\text{ct}|\Psi^{(2)}_\text{gs}}~,
@@
 
-\appendix*
+\appendix
 
@@
 This is simply the Hermitian conjugate of the previous contribution. Combining this with the previous then gives
+
+\begin{widetext}
 \begin{equation}\begin{aligned}
-	-\frac{n_j}{8}V J \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta}\left(1 - \hat n_{d\overline\beta}\right)\\
-	\times \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
+	-\frac{n_j}{8}V J \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta}\left(1 - \hat n_{d\overline\beta}\right) \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	-\frac{1}{4}V J n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)\\
-	\times \left(c^\dagger_{k\overline\beta} c_{d\overline\beta} + \text{h.c.}\right)
+	-\frac{1}{4}V J n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)  \left(c^\dagger_{k\overline\beta} c_{d\overline\beta} + \text{h.c.}\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	-\frac{3n_j}{8}V J \left(\frac{1}{\omega +U_b/4 - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega +U_b/4 - \frac{D}{2} + U/2 + \frac{J}{4}}\right)\\
-	\times\sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
+	-\frac{3n_j}{8}V J \left(\frac{1}{\omega +U_b/4 - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega +U_b/4 - \frac{D}{2} + U/2 + \frac{J}{4}}\right)\sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	&\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{k\beta} \hat n_{q\overline\beta} \frac{1}{\omega - H_D} c^\dagger_{d\beta}c_{q\beta} = \\
-	&-\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{n_jU_b V}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} + \frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right) \right.\\
-	&+ \left.\frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+	-\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{n_jU_b V}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} + \frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
 \end{aligned}\end{equation}
 
-The second term is of the form
-\begin{equation}\begin{aligned}
-	\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{d\beta} \frac{1}{\omega - H_D} \hat n_{q\overline\beta} c^\dagger_{k\beta}c_{q\beta}
-\end{aligned}\end{equation}
+The second term is of the form \(\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{d\beta} \frac{1}{\omega - H_D} \hat n_{q\overline\beta} c^\dagger_{k\beta}c_{q\beta}\),
 and this is just the Hermitian conjugate of the previous term, so these two terms together lead to
 \begin{equation}\begin{aligned}
-	&-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)\left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} \right.\right.\\
-	&+ \left.\left.
-\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} \right.\right.\\
-	&+\left.\left. \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+	-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)\left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} \right.\right.\\
+	+\left.\left. \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
 \end{aligned}\end{equation}
 
-\begin{widetext}
 In the hole sector, we have
 \begin{equation}\begin{aligned}
-	&\sum_{q\beta}\sum_{k}U_b V \hat n_{q\overline\beta} c^\dagger_{k\beta}c_{q\beta} \frac{1}{\omega - H_D} c^\dagger_{q\beta}c_{d\beta} -\sum_{q\beta}\sum_{k}U_b V \left(1 - \hat n_{q\overline\beta}\right) c^\dagger_{k\beta}c_{q\beta} \frac{1}{\omega - H_D} c^\dagger_{q\beta}c_{d\beta}\\
-	&= -n_jU_b V\sum_{k\beta} c^\dagger_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_1 - E_1} + \frac{1}{\omega^\prime_1 - E_1}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_0 - E_0} + \frac{1}{\omega_0^\prime - E_0}\right)\right] c_{d\beta}
+	-n_jU_b V\sum_{k\beta} c^\dagger_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_1 - E_1} + \frac{1}{\omega^\prime_1 - E_1}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_0 - E_0} + \frac{1}{\omega_0^\prime - E_0}\right)\right] c_{d\beta}
 \end{aligned}\end{equation}
-\end{widetext}
 \(E_1 = D/2 - U_b/4 - U/2 - J/4,~ ~ ~ E_0 = D/2 - U_b/4 - K/4\).
@@
 \begin{equation}\begin{aligned}
-	-\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{1 - \hat n_{d\overline\beta}}{2}\left(\frac{n_jU_b V}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} + \frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right)\right.\\
-	+ \left.\frac{\hat n_{d\overline\beta}}{2}\left(\frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+	-\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{1 - \hat n_{d\overline\beta}}{2}\left(\frac{n_jU_b V}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} + \frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right) + \frac{\hat n_{d\overline\beta}}{2}\left(\frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{n_jU_b V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	-\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \left[\left(\frac{n_jU_b V/2}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} + \frac{n_jU_b V/2}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right) \right.\\
-	+ \left.\left(\frac{n_jU_b V/2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{n_jU_b V/2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+	-\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \left[\left(\frac{n_jU_b V/2}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4}} + \frac{n_jU_b V/2}{\omega - \frac{D}{2} + \frac{U_b}{4}}\right) + \left(\frac{n_jU_b V/2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{n_jU_b V/2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	-\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^+ c^\dagger_{q\downarrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D}S_d^z c^\dagger_{k \downarrow}c_{q \downarrow} \\
-	= n_j \frac{1}{4}J^2 \left(-\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~,\\
-	\sum_{q} \sum_{kk^\prime} \frac{1}{4}J^2 S_d^z c^\dagger_{q \uparrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D} S_d^+ c^\dagger_{k\downarrow}c_{q \uparrow} \\
-	= -n_j \frac{1}{4}J^2 \left(\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~.
+	-\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^+ c^\dagger_{q\downarrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D}S_d^z c^\dagger_{k \downarrow}c_{q \downarrow} = n_j \frac{1}{4}J^2 \left(-\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~,\\
+	\sum_{q} \sum_{kk^\prime} \frac{1}{4}J^2 S_d^z c^\dagger_{q \uparrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D} S_d^+ c^\dagger_{k\downarrow}c_{q \uparrow} = -n_j \frac{1}{4}J^2 \left(\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~.
 \end{aligned}\end{equation}
+\end{widetext}
 The denominator is determined using \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\) and \(\omega^\prime = \omega + \epsilon_d\).
@@
 	-\sum_{q} \sum_{kk^\prime} \frac{1}{4}J^2 S_d^z c^\dagger_{k \downarrow}c_{q \downarrow} \frac{1}{\omega - H_D} S_d^+ c^\dagger_{q\downarrow}c_{k^\prime \uparrow} \\
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
 	= -n_j \frac{1}{4}J^2 \left(\frac{1}{2}S_d^+\right) \sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow} \frac{1}{\omega + \frac{U_b}{2} - \frac{D}{2} + \frac{J}{4}}~.
@@
 \end{aligned}\end{equation}
+
+\section{Expressing correlations in terms of entanglement}
+
+In Sec.~\ref{descr}, we related the impurity Greens function to the geometric measures of entanglement \(\varepsilon_\text{SS}\) and \(\varepsilon_\text{CT}\).
+We do the same here but for a general real-space static correlation \(\left< O_2 O_1^\dagger\right>\) at \(T=0\), where \(O_1, O_2\) are at most two-particle operators that act on the combined Hilbert space of the impurity site and the zeroth site.
+\begin{equation}\begin{aligned}
+	\left<O_2 O_1^\dagger\right> = \braket{\Psi_\text{gs} | O_2 O_1^\dagger | \Psi_\text{gs}}
+\end{aligned}\end{equation}
+Following Eq.~\ref{gs-ss}, we can rewrite the ground states in terms of the entanglement measures mentioned above.
+\begin{equation}\begin{aligned}
+	\ket{\Psi}_\text{gs} = \ket{\Phi}_{ss}\sqrt{1 - \varepsilon_\text{ss}} + \ket{\Phi}_{ct}\sqrt{1 - \varepsilon_\text{ss}}~,
+\end{aligned}\end{equation}
+where \(\ket{\Phi}_\text{ss(ct)}\) are the zero spin and zero charge isospin eigenstates of the Hamiltonian \(H = H_1 + H_2\) defined below Eq.~\ref{green_spectral}.
+Substituting this in the correlation gives
+\begin{equation}\begin{aligned}
+	&\left<O_2 O_1^\dagger\right> =\\
+	&\left(1 - \varepsilon_\text{ss}\right) \braket{\Phi_\text{ss} | O_2 O_1^\dagger | \Phi_\text{ss}} + \left(1 - \varepsilon_\text{ct}\right) \braket{\Phi_\text{ct} | O_2 O_1^\dagger | \Phi_\text{ct}}\\
+	&+ \sqrt{1 - \varepsilon_\text{ss}}\sqrt{1 - \varepsilon_\text{ct}}\left(\braket{\Phi_\text{ss} | O_2 O_1^\dagger | \Phi_\text{ct}} + \braket{\Phi_\text{ct} | O_2 O_1^\dagger | \Phi_\text{ss}}\right)
+\end{aligned}\end{equation}
+This allows any general correlation function to be written as a function of the entanglement measures and the matrix elements of the fluctuation \(O_1 O_2^\dagger\) between the two-site eigenstates.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.48\textwidth]{compens.pdf}
+	\includegraphics[width=0.48\textwidth]{corr_1p.pdf}
+	\caption{a}
+	\label{fig2}
+\end{figure}
+
+{\bf TODO}
+1. refer to these figures and the general relation in the discussions
+
 \end{document}

### 2022-05-06 gen-siam-manuscript/gen-siam.tex
sir's suggestions regarding the figures

@@
 \usepackage{braket,amsmath,graphicx,color}
-\usepackage{hyperref}
+\usepackage[hidelinks]{hyperref}
 \bibliographystyle{apsrev4-1}
@@
 	\centering
-	\includegraphics[width=0.35\textwidth]{spec_func.pdf}
+	\includegraphics[width=0.48\textwidth]{DMFT.pdf}
 	\caption{Schematic description of the evolution of the density of states across the transition~\cite{zhang_1993}.}
@@
 \begin{itemize}
-	\item {\color{blue}Indeed}, we find that on extending the AIM with a spin-exchange interaction \(J\) between the impurity site and the site it is coupled to (zeroth site), and an attractive correlation \(U_b\) on the zeroth site, the enhanced model shows a phase transition under a renormalisation group treatment, at a critical value \(\left(-U_b/J\right)_c=1/4\).
+	\item We find that on extending the AIM with a spin-exchange interaction \(J\) between the impurity site and the site it is coupled to (zeroth site), and an attractive correlation \(U_b\) on the zeroth site, the enhanced model shows a phase transition under a renormalisation group treatment, at a critical value \(\left(-U_b/J\right)_c=1/4\).
 	\item The ground state can be shown to evolve from a singlet between the impurity and the zeroth site to a decoupled local moment on the impurity, through a correlated state with both spin and charge content.
@@
 
-\subsection*{Layout of the {\color{blue}paper}}
-
-The paper is structured as follows.
-Sec.~\ref{def-ham} describes the extended model that we will be studying in this {\color{blue}paper}.
+The rest of the work is structured as follows.
+Sec.~\ref{def-ham} describes the extended model that we will be studying throughout.
 In Sec.~\ref{method}, we talk about the renormalisation group technique that we employ to study the model and the RG equations obtained from them.
@@
 We can now use the knowledge of the behaviour of these measures to make some statements about the nature of the transition from the Greens function.
+
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.48\textwidth]{corr_1p.pdf}
+	\caption{Growth in the single-particle correlation towards the transition.}
+	\label{one-particle}
+\end{figure}
+
 Since \(\varepsilon_\text{ss}\) increases towards the transition, we find that the first major term in the Greens function decreases; this shows that scattering within the spin sector loses weight.
@@
 The final major term also increases, due to the monotonic growth of \(\sqrt{\left(1 - \varepsilon_\text{ss} \right)}\sqrt{\left(1 - \varepsilon_\text{ct} \right)}\), showing that there is a continual increase in the {\it mixing of the spin and charge sectors}.
+This mixing is mediated by 1-particle correlations that transform spin degrees of freedom into charge, and indeed, the enhancement in the mixing is demonstrated by the growth of the 1-particle correlation in Fig.~\ref{one-particle}.
+
+{\color{blue}Generalising this result, any general one-particle or two-particle fluctuation \(\left<O_1 O_2^\dagger \right>\) that acts on the combined Hilbert space of the impurity and the zeroth site can be expressed in terms of these entanglement measures \(\varepsilon_\text{ss},\varepsilon_\text{ct}\).
+The details and the final expression are given in Appendix~\ref{general-ent}.
+As a demonstration, the spin-spin correlation between the impurity and the zeroth site is shown in Fig.~\ref{compens}.
+From the general expression in Fig.~\ref{gen-entng}, we know that only the singlet overlap will be non-zero, which means this correlation is related only to \(\varepsilon_\text{ss}\).
+Since \(\varepsilon_\text{ss}\) increases towards the transition (Fig.~\ref{entng}), the prefactor \(1 - \varepsilon_\text{ss}\) decreases, which then leads to the decrease in the magnitude of the correlation in Fig.~\ref{compens}.}
+
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.48\textwidth]{compens.pdf}
+	\caption{Spin-spin correlation between impurity and zeroth site}
+	\label{compens}
+\end{figure}
 
@@
 The discontinuous change in \(\chi\) is intimately connected to the fact that this phase transition is topological in nature~\cite{oshikawa2000topological,seki2017topological} -  the Luttinger volume of the conduction bath changes by 1~\cite{martin-physrevlett.48.362}.
+The fact that any general 1-particle or 2-particle correlation between the impurity and the zeroth site can also be similarly rewritten in terms of \(\varepsilon_\text{ss},\varepsilon_\text{ct}\)(Eq.~\ref{gen-entng}) means that measurable quantities can be related to entanglement.
 
@@
 Finer details like electronic differentiation in \(k-\)space can be captured by considering more number of impurities connected to each other through single-particle hopping or RRKY-like interaction~\cite{Ferrero2007,sakai_2009}.
-In general, the presence of multiple and varied classes of correlations in the auxiliary model - localisation tendency from Mott physics, delocalisation tendency from the spin and charge fluctuations, and pairing tendency from the local correlation term - makes this a strong candidate for describing various kinds of phases (Fig.~\ref{universal}).
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.48\textwidth]{universal_phase_diagram.pdf}
-	\caption{Phase diagram for strongly-correlated electronic systems}
-	\label{universal}
-\end{figure}
+In general, the presence of multiple and varied classes of correlations in the auxiliary model - localisation tendency from Mott physics, delocalisation tendency from the spin and charge fluctuations, and pairing tendency from the local correlation term - makes this a strong candidate for describing various kinds of phases.
 
@@
 \section{Expressing correlations in terms of entanglement}
+\label{general-ent}
 
@@
 \begin{equation}\begin{aligned}
+	\label{gen-entng}
 	&\left<O_2 O_1^\dagger\right> =\\
@@
 This allows any general correlation function to be written as a function of the entanglement measures and the matrix elements of the fluctuation \(O_1 O_2^\dagger\) between the two-site eigenstates.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.48\textwidth]{compens.pdf}
-	\includegraphics[width=0.48\textwidth]{corr_1p.pdf}
-	\caption{a}
-	\label{fig2}
-\end{figure}
-
-{\bf TODO}
-1. refer to these figures and the general relation in the discussions
 

### 2022-05-31 gen-siam-manuscript/gen-siam.tex
Added abstract

@@
 \begin{abstract}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborumLorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
+We propose a minimal impurity model as the auxiliary model that can be used to study metal-insulator transitions in bulk models like the Hubbard.
+The minimal model is obtained by adding spin-exchange physics and local bath correlation into the single impurity Anderson model.
+We prove this by demonstrating the presence of both metallic (screened) as well as insulating (unscreened) phases through a renormalisation group treatment of such a model.
+We show that this impurity phase transition is brought about by increased charge isospin fluctuations in the bath; indeed, it is these fluctuations that destabilise the Kondo cloud and lead to a breakdown of screening.
+This transition is characterised by a measure of many-particle entanglement \(\left(\chi\right)\) which acts as an order parameter - it is non-zero in the screened phase and reduces to zero in the unscreened phase.
+This is made possible by relating the impurity Greens function to \(\chi\), and it turns out that such relations exist for any 1-particle or 2-particle impurity-bath correlation.
+Such an auxiliary model approach to studying bulk systems of strong correlation is qualitatively different from a more conventional approach like dynamical mean-field theory or its cluster variants.
+There is no need to obtain the impurity model self-consistently, and this makes it possible to directly relate the thermodynamics of the bulk model to that of the impurity.
 \end{abstract}

### 2022-07-23 notes/notes.tex
obtained renormalisation from removing impurity

@@
-\documentclass{report}
+\documentclass[12pt]{report}
 % \documentclass{nature}
@@
 \usepackage[hidelinks]{hyperref}
-\usepackage[margin=0.5in,top=0.3in,bottom=1.4in]{geometry}
+\usepackage[margin=0.7in,top=0.3in,bottom=1.4in]{geometry}
 
@@
 \subsection{Bath spectral function \(A_{00}(\omega)\)}
-\begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_Ub_by_J=-0.000.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_Ub_by_J=-0.125.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_Ub_by_J=-0.250.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_00_Ub_by_J=-0.26.pdf}
-\end{center}
+In order to calculate the spectral function \(A_{00}(\omega)\) of the site connected to the impurity (referred to as the zeroth site), we will use the following strategy.
+We will decouple the impurity states from the fixed point Hamiltonian using a single URG transformation.
+This will of course generate correlations on the zeroth site.
+The resulting Hamiltonian will be an Anderson impurity model with the hopping between the zeroth site and the rest of the chain acting as the effective hybridisation.
+Schematically, we will have
+\begin{equation}\begin{aligned}
+	H^* = H_\text{imp} + V_\text{imp-0} + H_\text{0} + H_\text{0-1} + H_\text{rest} ~ \mathlarger{\xrightarrow{\text{decouple imp.}}} ~ E_\text{imp} + \tilde H_\text{0} + H_\text{0-1} + H_\text{rest} = H_\text{new imp} \\
+	+ V_\text{new imp - rest} + H_\text{rest}
+\end{aligned}\end{equation}
+
+Since the impurity is not coupled with any site beyond the zeroth site, the parts of the Hamiltonian that involve "rest" will not change in the process.
+This also means that the decoupling can be performed by looking at the smaller Hamiltonian
+\begin{equation}\begin{aligned}
+	H_\text{imp+0} = H_\text{imp} + H_\text{0} + V_\text{imp-0} = -\frac{U^*}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right)^2 - U_b \left( \hat n_{0 \uparrow} - \hat n_{0 \downarrow} \right)^2 + J^*S_d^z S_0^z + {V^*}\sum_\sigma \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) \\
+	+ \frac{J^*}{2}\left( c^\dagger_{d \uparrow}c_{d \downarrow} c^\dagger_{0 \downarrow} c_{0 \uparrow} + \text{h.c.} \right) 
+\end{aligned}\end{equation}
+
+\paragraph{Renormalisation from \({V^*}\)}
+From the off-diagonal term involving \({V^*}\), we generate the following term, in the particle sector for \(0\):
+\begin{equation}\begin{aligned}
+	{V^*} \sum_\sigma c^\dagger_{0\sigma}c_{d\sigma} \frac{1}{\tilde \omega - H_d} {V^*} c^\dagger_{d\sigma}c_{0\sigma} = |V^*|^2 \sum_\sigma c^\dagger_{0\sigma}c_{d\sigma} \frac{1}{\tilde \omega + \frac{U^*}{2}\left( 1 - \hat n_{d\bar\sigma} \right)^2 + U_b \hat n_{0\bar\sigma} + \frac{J^*}{4}\left( 1 - \hat n_{d\bar\sigma} \right) \hat n_{0\bar\sigma} } c^\dagger_{d\sigma}c_{0\sigma}
+\end{aligned}\end{equation}
+where \(\tilde \omega\) is the quantum fluctuation operator for the impurity site and \(H_d = -\frac{U^*}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right)^2 - U_b \left( \hat n_{0 \uparrow} - \hat n_{0 \downarrow} \right)^2 + J^*S_d^z S_0^z \), is the diagonal part of the Hamiltonian for the imp+0 system.
+In order to resolve the operators in the denominator, we expand the unity in the numerator using the identity \(1 = \hat n_{d\bar\sigma}\hat n_{0\bar\sigma} + \hat n_{d\bar\sigma}\hat h_{0\bar\sigma} + \hat h_{d\bar\sigma}\hat n_{0\bar\sigma} + \hat h_{d\bar\sigma}\hat h_{0\bar\sigma}\), where \(\hat h = 1 - \hat n\) is hole operator.
+On Substituting this, we get
+\begin{equation}\begin{aligned}
+	\sum_\sigma {V^*} c^\dagger_{0\sigma}c_{d\sigma} \frac{1}{\tilde \omega - H_d} {V^*} c^\dagger_{d\sigma}c_{0\sigma} &= |V^*|^2 \sum_\sigma c^\dagger_{0\sigma}c_{d\sigma} \frac{\hat h_{d\bar\sigma}\hat h_{0\bar\sigma} + \hat h_{d\bar\sigma}\hat n_{0\bar\sigma} + \hat n_{d\bar\sigma}\hat h_{0\bar\sigma} + \hat n_{d\bar\sigma}\hat n_{0\bar\sigma}}{\tilde \omega + \frac{U^*}{2}\hat h_{d\bar\sigma} + U_b \hat n_{0\bar\sigma} + \frac{J^*}{4}\hat h_{d\bar\sigma} \hat n_{0\bar\sigma} } c^\dagger_{d\sigma}c_{0\sigma}\\
+															    &= |V^*|^2 \sum_\sigma \hat h_{d\sigma} \hat n_{0\sigma}\left[\frac{\hat h_{d\bar\sigma}\hat h_{0\bar\sigma}}{\tilde\omega_{00} + \frac{U^*}{2}} + \frac{\hat h_{d\bar\sigma}\hat n_{0\bar\sigma}}{\tilde\omega_{01} + \frac{U^*}{2} + U_b + \frac{J^*}{4}} + \frac{\hat n_{d\bar\sigma}\hat h_{0\bar\sigma}}{\tilde\omega_{10}} + \frac{\hat n_{d\bar\sigma}\hat n_{0\bar\sigma}}{\tilde\omega_{11} + U_b}\right]
+\end{aligned}\end{equation}
+\(\tilde\omega_{(0,1),(0,1)}\) represents the quantum fluctuation scale corresponding to the configuration in the numerator.
+
+In order to "freeze" the impurity dynamics, we will substitute \(\hat n_{d\sigma} = \hat n_{d\bar\sigma} = \frac{1}{2}\), because of the \(\mathbb{Z}_2\) symmetry and the particle-hole symmetry of the impurity levels.
+This gives
+\begin{equation}\begin{aligned}
+	\frac{1}{4}|V^*|^2 \sum_\sigma \hat n_{0\sigma} \left[\frac{\hat h_{0\bar\sigma}}{\tilde\omega_{00} + \frac{U^*}{2}} + \frac{\hat n_{0\bar\sigma}}{\tilde\omega_{01} + \frac{U^*}{2} + U_b + \frac{J^*}{4}} + \frac{\hat h_{0\bar\sigma}}{\tilde\omega_{10}} + \frac{\hat n_{0\bar\sigma}}{\tilde\omega_{11} + U_b}\right]
+\end{aligned}\end{equation}
+
+The state that most closely represents the metallic ground state is \(\bar \omega_{10}\), we take that as the reference quantum fluctuation scale \(\bar\omega\).
+It is of the order of \(\bar\omega \sim -\frac{J^*}{4} - \frac{U^*}{2} - U_b\).
+We will now relate the other scales to \(\bar\omega\) by expressing them in terms of the energy of the initial state:
+\begin{equation}\begin{aligned}
+	\tilde\omega_{00} \sim -U_b = \bar\omega + \frac{J^*}{4} + \frac{U^*}{2}, ~~ \tilde\omega_{01} \sim 0 = \bar\omega + \frac{J^*}{4} + \frac{U^*}{2} + U_b, ~~ \tilde\omega_{11} \sim -\frac{U^*}{2} = \bar\omega + \frac{J^*}{4} + U_b
+\end{aligned}\end{equation}
+Substituting these gives
+\begin{equation}\begin{aligned}
+	\frac{1}{4}|V^*|^2 \sum_\sigma \hat n_{0\sigma} \left[\hat h_{0\bar\sigma}\alpha_1 + \hat n_{0\bar\sigma}\alpha_2\right]
+\end{aligned}\end{equation}
+where \(\alpha_1 = \left(\bar\omega + U^* + \frac{J^*}{4}\right)^{-1} + \left(\bar\omega\right)^{-1}\) and \(\alpha_2 = \left(\bar\omega + U^* + 2U_b + \frac{J^*}{2}\right)^{-1} + \left(\bar\omega + 2U_b + \frac{J^*}{4}\right)^{-1}\).
+
+Because of the particle-hole symmetry on the impurity as well as in the bath, the renormalisation from the hole sector is obtained simply by transforming \(\hat n \leftrightarrow \hat h\):
+\begin{equation}\begin{aligned}
+	\frac{1}{4}|V^*|^2 \sum_\sigma \hat h_{0\sigma} \left[\hat n_{0\bar\sigma}\alpha_1 + \hat h_{0\bar\sigma}\alpha_2\right]
+\end{aligned}\end{equation}
+
+The total renormalisation arising from \(V\) is therefore
+\begin{equation}\begin{aligned}
+	\frac{1}{4}|V^*|^2 \sum_\sigma \left[\alpha_1 \left( \hat n_{0\sigma}\hat h_{0\bar\sigma} + \hat h_{0\sigma}\hat n_{0\bar\sigma}\right) + \alpha_2 \left( \hat n_{0\sigma}\hat n_{0\bar\sigma} + \hat h_{0\sigma}\hat h_{0\bar\sigma}\right)\right] = \frac{1}{2}|V*|^2 \left(\alpha_1 - \alpha_2\right) \left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2 + \text{constant}
+\end{aligned}\end{equation}
+
+\paragraph{Renormalisation from \(J\)}
+The renormalisation arising from decoupling the Kondo coupling has two terms. The first term arises when the spin of the zeroth site is initially up:
+\begin{equation}\begin{aligned}
+	\frac{{J^*}^2}{4}c^\dagger_{d \downarrow}c_{d \uparrow} c^\dagger_{0 \uparrow}c_{0 \downarrow} \frac{1}{\tilde \omega - H_d} c^\dagger_{0 \downarrow}c_{0 \uparrow} c^\dagger_{d \uparrow}c_{d \downarrow} = c^\dagger_{d \downarrow}c_{d \uparrow} c^\dagger_{0 \uparrow}c_{0 \downarrow} \frac{{J^*}^2/4}{\tilde \omega + \frac{U^*}{2} + U_b + \frac{J^*}{4}} c^\dagger_{0 \downarrow}c_{0 \uparrow} c^\dagger_{d \uparrow}c_{d \downarrow} = \frac{{J^*}^2}{4}\frac{\hat n_{d \downarrow} \hat h_{d \uparrow} \hat n_{ 0 \uparrow} \hat h_{0 \downarrow}}{\tilde \omega + \frac{U^*}{2} + U_b + \frac{J^*}{4}}
+\end{aligned}\end{equation}
+The quantum fluctuation scale \(\tilde \omega\) for this process can be similarly related to \(\bar\omega\): \(\tilde\omega \sim -\frac{U^*}{2} - U_b - \frac{J^*}{4} = \bar\omega\). This gives
+\begin{equation}\begin{aligned}
+	\frac{{J^*}^2}{4}\frac{\hat n_{d \downarrow} \hat h_{d \uparrow} \hat n_{ 0 \uparrow} \hat h_{0 \downarrow}}{\bar\omega + \frac{U^*}{2} + U_b + \frac{3J^*}{4}} = \frac{{J^*}^2}{16}\frac{\hat n_{ 0 \uparrow} \hat h_{0 \downarrow}}{\bar\omega + \frac{U^*}{2} + U_b + \frac{J^*}{4}}
+\end{aligned}\end{equation}
+as the renormalisation for this configuration.
+At the final step, we substituted \(\hat n_{d\sigma} = \hat h_{d\sigma} = \frac{1}{2}\).
+For the other configuration where the spin of the zeroth site is down, we get
+\begin{equation}\begin{aligned}
+	\frac{{J^*}^2}{16}\frac{\hat n_{ 0 \downarrow} \hat h_{0 \uparrow}}{\bar\omega + \frac{U^*}{2} + U_b + \frac{J^*}{4}}
+\end{aligned}\end{equation}
+Adding both sectors, we get
+\begin{equation}\begin{aligned}
+	\frac{{J^*}^2}{16}\frac{1}{\bar\omega + \frac{U^*}{2} + U_b + \frac{J^*}{4}} \left(\hat n_{ 0\uparrow} - \hat n_{0 \downarrow}\right)^2
+\end{aligned}\end{equation}
+
+\paragraph{Total renormalisation}
+Adding the contributions from both \(V^*\) and \(J^*\),  the net renormalisation is the generation of a local correlation term \(-U_0\left(\hat n_{ 0\uparrow} - \hat n_{0 \downarrow}\right)^2\) on the zeroth site, where \(U_0\) is given by
+\begin{equation}\begin{aligned}
+	U_0 = -\frac{{J^*}^2}{16}\frac{1}{\bar\omega + \frac{U^*}{2} + U_b + \frac{J^*}{4}} - \frac{1}{2}|V^*|^2\left(\frac{1}{\bar\omega + U^* + \frac{J^*}{4}} + \frac{1}{\bar\omega} - \frac{1}{\bar\omega + U^* + 2U_b + \frac{J^*}{2}} - \frac{1}{\bar\omega + 2U_b + \frac{J^*}{4}}\right)
+\end{aligned}\end{equation}
+
+Deep in the metallic regime, we have the following hierarchy of energy scales: \(|J^*| > |\bar\omega| \gg |V^*| \gg |U_b| \gg |U^*| \simeq 0\).
 

### 2023-01-30 notes/notes.tex
combined gen siam chapters into thesis
--no-message
cosmetic changes

@@
-\documentclass[12pt]{report}
-% \documentclass{nature}
-\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk,pifont,enumitem}
+\documentclass{report}
+\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk,enumitem}
 % \usepackage[draft]{graphicx}
@@
 \usepackage[hidelinks]{hyperref}
-\usepackage[margin=0.7in,top=0.3in,bottom=1.4in]{geometry}
-
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-
-\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}
-\newlist{todolist}{itemize}{2}
-\setlist[todolist]{label=$\square$}
-\newcommand{\cmark}{\ding{51}}%
+\usepackage[margin=0.5in,bottom=1in]{geometry}
 
 \newcommand{\comment}[1]{{}}
-\renewcommand{\arraystretch}{2}
-\setlength\delimitershortfall{-2pt}
 \setcounter{tocdepth}{1}
-\pagestyle{headings}
-\setlength{\headheight}{52pt}
 \numberwithin{equation}{section}
 \allowdisplaybreaks
-\bibliographystyle{ieeetr}
+\bibliographystyle{unsrt}
 
@@
 \item The Mott metal-insulator transition:
-	\begin{todolist}
-	\item[\cmark] Obtain the metal insulator transition of the 2D Hubbard-Heisenberg model on the square lattice from the present formalism. 
+	\begin{itemize}
+	\item Obtain the metal insulator transition of the 2D Hubbard-Heisenberg model on the square lattice from the present formalism. 
 	\item Determine the nature of the bath $\Sigma (k,\omega)$ in the metallic phase, insulating phase as well as at criticality.
 	\item Investigate nature of the zero-temperature transition (order of transition, order parameter, etc)
-	\end{todolist}
+	\end{itemize}
 
 \item Higher-order Greens functions:
-	\begin{todolist}
+	\begin{itemize}
 	\item Provide expressions for two-particle Greens functions.
@@
 	\item Obtain spectral functions for such excitations
-	\end{todolist}
+	\end{itemize}
 
 \item Benchmarking against ED and/or finite size scaling:
-	\begin{todolist}
+	\begin{itemize}
 	\item ground state energy
 	\item double occupancy
-	\end{todolist}
+	\end{itemize}
 
 \item Upgrade to two-site cluster:
-	\begin{todolist}
+	\begin{itemize}
 	\item Study a two-impurity model under renormalisation group
-	\item[\cmark] Derive the tiling and Greens function relations for such a two-impurity model 
+	\item Derive the tiling and Greens function relations for such a two-impurity model 
 	\item Demonstrate Mott MIT here.
@@
 	\item look for signs of a quantum liquid.
-	\end{todolist}
+	\end{itemize}
 

### 2023-02-02 notes/notes.tex
updated some older figures and removed unnecessary ones

@@
 \usepackage[hidelinks]{hyperref}
-\usepackage[margin=0.5in,bottom=1in]{geometry}
+\usepackage[margin=0.7in,bottom=1in]{geometry}
 
@@
 
-\title{A New Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Systems}
+\title{\bf An Unitary RG-based Auxiliary Model Approach\\ to Strongly-Correlated Systems}
 \author{Abhirup Mukherjee, Siddhartha Lal}
@@
 	\item For \(U_b > J/4\), the couplings \(J\) and \(V\) become irrelevant while \(U\) is relevant, which means that \textbf{the impurity gets cut off from the bath at low energies}.
-\begin{center}
-	\includegraphics[width=0.7\textwidth]{../figures/phase-map-MIT.pdf}
-\end{center}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.48\textwidth]{../figures/phase-map-MIT.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/spectral-function.pdf}
+	\caption{{\it Left:} Phase diagram. {\it Right:} Impurity spectral function}
+	\label{spec_func_mit}
+\end{figure}
+
 \item The impurity spectral function \(A_{dd}(\omega)\) and the impurity-bath real space off-diagonal Greens function \(A_{d0}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
@@
 \centering
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_Ub_by_J=-0.100.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_Ub_by_J=-0.250.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_Ub_by_J=-0.26.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.100.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.250.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.26.pdf}
-	\caption{Evolution of diagonal and off-diagonal spectral functions across the transition.}
-	\label{spec_func_mit}
+	\includegraphics[width=0.48\textwidth]{../figures/corrs_gs.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/spin-charge-corr-full.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/mutinfo-d0-01-full.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/doub_occ.pdf}
 \end{figure}
 
-\begin{figure}[!htb]
-\centering
-	\includegraphics[width=0.3\textwidth]{../figures/corr-k-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/corr-d0-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r1p-t=1.000,J=10.000,0.000,30,V=3J,Ubath=-U_by_10,N=6,U=1.000,889.513,30.pdf}
-	\caption{Evolution of correlation functions and mutual information across the transition.}
-\end{figure}
-
 	\item In the context of the auxiliary model, this represents an \textbf{impurity phase transition} from the completely-screened spin-singlet phase to the unscreened local moment phase.
-
-\begin{figure}[!htb]
-\centering
-	\includegraphics[width=0.75\textwidth]{../figures/overlaps_gs-J=10.000.pdf}
-	\caption{Evolution of the zero-bandwidth ground state across the transition.}
-\end{figure}
 
@@
 On the other side \(r > r^{*}\) of the critical point, we know that the impurity gets decoupled from the bath, such that the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) vanish.
-This is simply the loss of spectral weight at low-\(\omega\) because of the removal of the gapless excitations, and is demonstrated through both the diagonal and off-diagonal spectral functions in fig.~\ref{spec_func_mit}.
+This is simply the loss of spectral weight at low-\(\omega\) because of the removal of the gapless excitations, and is demonstrated through the impurity spectral function in fig.~\ref{spec_func_mit}.
 This then implies that the bulk Greens functions will also gap out at low energies, and that describes an insulating phase where the electrons get "jammed" in the local states.
@@
 
+\comment{
 \section{\(k-\)space picture of the MIT in terms of the momentum-resolved self-energy \(\Sigma(\vec k,\omega)\)}
@@
 These plots are available as videos \href{https://abhirup-m.github.io/misc-sigma/}{\underline{here}}.
-
-\clearpage
+}
+
 \section{Some important remarks}

### 2023-02-17 notes/notes.tex
added k-space proof

@@
 The answer to how closely $\tilde H$ approximates a target model of correlated electrons lies in (i) the choice of the cluster-bath construction of the auxiliary model, and (ii) the accuracy of the URG procedure on the auxiliary model.
+
+\chapter{From the auxiliary model to the bulk - single site approach}
+\label{chap:tile}
+
+\section{Creating \(N-\)site Hubbard Hamiltonian from Anderson impurity embedded in an interacting bath}
+
+Previously, we have worked out the grounstate phases of a single-impurity model with an interacting bath:
+\begin{equation}\begin{aligned}
+	\label{siam_attr}
+	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
+\end{aligned}\end{equation}
+
+We will use this as the auxiliary model to study the Hubbard model.
+We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
+Note that the impurity level is explicitly at half-filling, because the correlation term \(\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is symmetric under a particle-hole transformation \(\hat n_{d\sigma} \to 1 - \hat n_{d\sigma}\).
+Moreover, the conduction bath is also at half-filling, because we have set the chemical potential \(\mu\) to zero.
+These two ensure that the bulk model is also at half-filling.
+At the end of this section, we will also mention how the tiling works out in the presence of a non-zero filling.
+
+To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(i\) of the lattice, and the bath coupled to the impurity as the set of remaining \(N-1\) sites in the lattice.
+We will also identity the zeroth site of the SIAM lattice as one of the nearest neighbours \(j\) of \(i\):
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux}(i,j) = -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n} \left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2
+\end{aligned}\end{equation}
+The tight-binding term sums over all nearest pairs \((m,n)\) that do not involve the site \(i\).
+In general \(i\) will have \(w\) nearest neighbours for a lattice with coordination number \(w\).
+The total local Hamiltonian for the site \(i\) is obtained by averaging over the Hamiltonians \(\mathcal{H}_\text{aux}(i,j)\) for all nearest neighbours \(j\) of \(i\):
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux}(i) &= \frac{1}{w}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{w}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right)  \right.\\
+				  &\left. +J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\\
+				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
+				  &\left.- U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]
+\end{aligned}\end{equation}
+Once we have this local Hamiltonian for a particular site, we translate this over all sites \(i\):
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{full} =& \sum_i \mathcal{H}_\text{aux}(i) = \sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
+				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\right]\\
+	=& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
+				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j\right]\right]
+\end{aligned}\end{equation}
+In the entire tight-binding term \(\sum_i\sum_{<m,n>,\sigma}^{m \neq i \neq n}\), each pair will appear \(N-2\) times, because that is the total number of sites that do not involve either \(m\) or \(n\).
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{full} =& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - 2t\left(N-2\right)\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{w}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
+				  &+ \left. J \vec{S_i}\cdot\vec{S}_j\right]\\
+				  &=-\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(2t (N-2) - \frac{2V}{w}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{w} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
+\end{aligned}\end{equation}
+We end up with a Hubbard-Heisenberg model:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j
+\end{aligned}\end{equation}
+The mapping between the parameters is
+\begin{equation}\begin{aligned}
+	\label{map_aux_bulk}
+	t_{H-H} = \left(2t (N-2) - \frac{2V}{w}\right),~ ~ U_{H-H} = \left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{w}
+\end{aligned}\end{equation}
+The conclusion is that we can tile Anderson models with interacting baths into a Hubbard-Heisenberg model:
+\begin{equation}\begin{aligned}
+	\label{siam_to_hubb}
+	\sum_i \mathcal{H}_\text{aux}(i) = \mathcal{H}_{H-H}
+\end{aligned}\end{equation}
+
+As mentioned before, no chemical potential \(\mu\) is generated becuase the auxiliary model was at half-filling, both in the impurity as well as in the bath.
+We can change the chemical potential by introducing two terms:
+\begin{equation}\begin{aligned}
+	\eta \sum_\sigma\left(n_{d\sigma} - \frac{1}{2}\right), \mu \sum_{i,\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
+\end{aligned}\end{equation}
+The first term is the particle-hole asymmetry term, and tuning that term moves the impurity away from half-filling.
+The second term is the usual chemical potential in the bath.
+Introducing these terms in the auxiliary model changes the bulk model into:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j + \mu_\text{H-H}\sum_{i\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
+\end{aligned}\end{equation}
+The only change is the generation of the last term. The mappings between the existing parameters and their auxiliary model counterparts remain the same, while \(\mu_\text{H-H}\) is given by
+\begin{equation}\begin{aligned}
+	\mu_\text{H-H} = \eta + \left(N-1\right) \mu
+\end{aligned}\end{equation}
+In the discussion henceforth, we will assume all the models are at half-filling. We will come back to the doped case at a later point in time.
+
+\section{Nature of the wavefunctions}
+In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full wavefunction \(\Psi\) is then obtained by constructing liner combinations of the eigenstates \(\psi_i\) of the local Hamiltonians such that \(\Psi\) satisfies Bloch's theorem: \(\Psi_{\vec k}(\vec r) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r - \vec R_i)\).
+Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation \(T(\vec R)\) by some lattice distance \(\vec R = \sum_i n_i \vec a_i\):
+\begin{equation}\begin{aligned}
+T(\vec R)\Psi_{\vec k}\left(\vec r\right) = \Psi_{\vec k}(\vec r + \vec R) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r + \vec R - \vec R_i) = e^{i \vec{k}\cdot\vec{R}}\sum_i e^{i \vec{k}\cdot\left(\vec{R}_i - \vec R\right)} \psi_i(\vec r - (\vec R_i - \vec R)) = e^{\vec{k}\cdot\vec{R}}\Psi(\vec r)
+\end{aligned}\end{equation}
+At the end, we used the fact that \(\vec r_i - \vec R\) is just another lattice vector \(\vec R_j\).
+Note that the translation operator has been defined as an operation that simply advances the argument of the wavefunction from \(\vec r\) to \(\vec r + \vec R\).
+An equivalent definition can be given in terms of their action on position eigenkets: \(T(\vec R)\ket{\vec r} = \ket{\vec r - \vec R}\).
+These translation operators share eigenstates with the momentum operator:
+\begin{equation}\begin{aligned}
+	T\left( \vec R \right) \ket{\vec k} = \sum_{\vec r_i} e^{i \vec{k}\cdot\vec{r}_i}T\left( \vec R \right)\ket{\vec r_i} = e^{i \vec{k}\cdot\vec{R}}\sum_{\vec r_i} e^{i \vec{k}\cdot\left(\vec{r}_i - \vec R\right)}\ket{\vec r_i - \vec R} = e^{i \vec{k}\cdot\vec{R}} \ket{\vec k}
+\end{aligned}\end{equation}
+
+The bulk Hamiltonian obtained in eq.~\ref{siam_to_hubb},
+\begin{equation}\begin{aligned}
+	H_\text{H-H}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i} \mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i\right\}\right) \equiv \sum_{\vec R_i} \mathcal{H}_\text{aux}\left(\vec R_i\right)~,
+\end{aligned}\end{equation}
+also enjoys a Bloch's theorem. This is because the tiling procedure restores the translation symmetry of the lattice:
+\begin{equation}\begin{aligned}
+	H_\text{H-H}\left(\left\{\vec r_k + \vec R\right\}\right) =  \sum_{\vec R_i}\mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i + \vec R\right\}\right) = \sum_{\vec R_i} \mathcal{H}_{\text{aux},\tilde i}\left(\left\{\vec r_k - \vec R\right\}\right) = H_\text{H-H}(\left\{\vec r_k\right\})
+\end{aligned}\end{equation}
+There we used the fact that \(\vec r_k + \vec R\) simply translates the auxiliary model defined by the coordinate \(i\) to a new auxiliary model at the modified coordinate \(\tilde i: \vec R_i^\prime = \vec R_i + \vec R\).
+Since this transformation from one auxiliary model to another simply shuffles the group of all auxiliary models, the sum over the group remains the sum, and we recover the same bulk model.
+
+We can use the auxiliary model zero-bandwidth wavefunctions 
+\begin{equation}\begin{aligned}
+\psi^n_\text{aux}\left(\vec r_d - \vec R_i, \vec r_0 - \left(\vec R_i + \vec a\right)  \right) \equiv \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
+\end{aligned}\end{equation}
+with the impurity position \(\vec R_i\) and zeroth site position \(\vec R_i + \vec a\), to construct eigenstates of the bulk Hamiltonian.
+\(\vec R_i\) is a lattice vector, while \(\vec a\) is one of the \(w\) vectors that connect a lattice site with its nearest neighbours.
+This two site wavefunction can be obtained by first studying the full auxiliary model \(\mathcal{H}_\text{aux}\) under a renormalisation group, obtaining a fixed-point Hamiltonian in the IR, obtaining the IR eigenstate and then tracing out all lattice sites except the impurity and the zeroth site from this eigenstate.
+\(n=0\) is the ground state of the auxiliary model, and higher values denote the excited states.
+
+The following un-normalised combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
+\begin{equation}\begin{aligned}
+	\ket{\Psi^n_{\vec k}} = \frac{1}{w \sqrt N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
+\end{aligned}\end{equation}
+where \(N\) is the total number of lattice sites.
+The interpretation is that the set of \(n=0\) states form the lowest band in the spectrum of the lattice.
+Higher values of \(n\) produce the more energetic bands.
+The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\).
+We will actually work only in the lowest band \(n=0\), so we will drop the band index from now on and keep in mind that only the auxiliary model ground states appear in the formulation:
+\begin{equation}\begin{aligned}
+	\label{bloch-states}
+	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
+\end{aligned}\end{equation}
+where \(\lambda_{\ket{\vec k}}\) is a normalisation factor and is defined by \(|\lambda_{\ket{\vec k}}|^2 = |\braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}|^2 \); \(\ket{\vec k}\) is the momentum eigenstate for momentum \(\vec k\), and \(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
+Becuase of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(w\) choices.
+
+It is easy to verify that \(\Psi_{\vec k}\left(\left\{ \vec r_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \(\vec R\):
+\begin{equation}\begin{aligned}
+	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
+\end{aligned}\end{equation}
+In the last equation, we transformed \(\vec R_i \to \vec R_j = \vec R_i - \vec R\).
+Note that the argument \(\vec a\) does not change under a translation of the system, because that vector always represents the difference between the impurity lattice position and its nearest neighbours, irrespective of the absolute position of the impurity.
+
+The wavefunction can be even brought into the familiar Bloch function form:
+\begin{equation}\begin{aligned}
+	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} w N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
+	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
+\end{aligned}\end{equation}
+where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
+This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
+
+It is straightforward to show that these states form an orthonormal basis. We start by writing down the inner product of two distinct such states:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+\end{aligned}\end{equation}
+At this point, we insert a complete basis of momentum eigenkets \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
+						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+\end{aligned}\end{equation}
+At the last step, we used the summation form of the Kronecker delta function: \(\sum_{\vec R_i}e^{i \vec R_i \left( \vec k - \vec q \right) }\sum_{\vec R_j}e^{i \vec R_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\).
+The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \(\vec a, \vec a^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\ket{\vec k}}\):
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
+\end{aligned}\end{equation}
+This concludes the proof of orthonormality.
+
+To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
+\begin{equation}\begin{aligned}
+	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}
+\end{aligned}\end{equation}
+To resolve the translation operators, we will now insert the momentum eigenstates \(\ket{\vec k}\) of the full model: \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) in between the operators.
+\begin{equation}\begin{aligned}
+	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 w^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 w^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
+	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}
+\end{aligned}\end{equation}
+The momentum eigenket \(\ket{\vec k}\) can be expressed as a sum over position eigenkets at varying distances from \(\vec R_0\).
+This form allows a systematic method of improving the energy eigenvalue estimate, because the interacting in the impurity model is extremely localised, so the overlap between two auxiliary models decreases rapidly with distance.
+The majority of the contribution will come from the state at \(\vec R_0\), and improvements are then made by considering auxiliary models at further distances.
+
+\section{Single-particle Green's function}
+In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{aux}}\) of the auxiliary models.
+In this section, we will relate real-sapce Greens functions of the bulk lattice to those of the auxiliary model.
+We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
+We define the time-domain Greens function between two points \(\vec R\) and \(\vec R + \vec r\) as
+\begin{equation}\begin{aligned}
+	G(\vec r, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c(\vec R + r,t), c^\dagger(\vec R) \right\} | \Psi_\text{gs}}
+\end{aligned}\end{equation}
+We also define a Green operator \(\mathcal{G}(\omega)\):
+\begin{equation}\begin{aligned}
+	\mathcal{G}(\omega) = \frac{1}{\omega - (H_\text{H-H} - E_\text{gs})}~,
+\end{aligned}\end{equation}
+where \(\omega\) is the frequency scale for the excitations. This operator can be related to the Greens function through the relation (eq.~\eqref{inv_G_func})
+\begin{equation}\begin{aligned}\label{greens_func_bulk}
+	G(\vec r, \omega) &= \braket{\Psi_\text{gs} | c(\vec R + r) \mathcal{G}(\omega) c^\dagger(\vec R) | \Psi_\text{gs}} - \braket{\Psi_\text{gs} | c^\dagger(\vec R) \mathcal{G}(-\omega) c(\vec R + r) | \Psi_\text{gs}}\\
+			  &= \sum_n\left[\braket{\Psi_\text{gs} | c(\vec R + r) \lambda^-_n \frac{\left(H_\text{H-H}\right)^n}{(\omega + E_\text{gs})^{n+1}} c^\dagger(\vec R) | \Psi_\text{gs}} + \braket{\Psi_\text{gs} | c^\dagger(\vec R) \lambda^+_n \frac{\left(H_\text{H-H}\right)^n}{(\omega - E_\text{gs})^{n+1}} c(\vec R + r) | \Psi_\text{gs}}\right]\\
+			  &= \sum_n\left[ \frac{\lambda^-_n}{(\omega + E_\text{gs})^{n+1}} \mathcal{U}(\vec r)^{(n)}_> + \frac{\lambda^+_n}{(\omega - E_\text{gs})^{n+1}} \mathcal{U}(\vec r)^{(n)}_<\right]
+\end{aligned}\end{equation}
+where we have defined \(\lambda_n^\pm\) using \(1/(1\pm y) = \sum_n \lambda^\pm_n y^n\), and the retarded and advanced propagation matrix elements \(\mathcal{U}(\vec r)^{(n)}_>  = \braket{\Psi_\text{gs} | c(\vec R + r) \left(H_\text{H-H}\right)^n c^\dagger(\vec R) | \Psi_\text{gs}}, \quad \mathcal{U}(\vec r)^{(n)}_<  = \braket{\Psi_\text{gs} | c^\dagger(\vec R) \left(H_\text{H-H}\right)^n c(\vec R + r) | \Psi_\text{gs}}\).
+These matrix elements will now be expressed in terms of auxiliary model properties, starting with the retarded one. By combining with eq.~\eqref{siam_to_hubb} and eq.~\eqref{bloch-states}, we get
+\begin{equation}\begin{aligned}\label{retarded_matrix_element}
+	\mathcal{U}(\vec r)^{(n)}_> = \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_i) | c_{\vec R + \vec r, \sigma} \left[\sum_{\vec R_c}\mathcal{H}\left( \vec R_c \right)\right]^n  c_{\vec R, \sigma}^\dagger | \psi_\text{aux}(\vec R_j)}~,
+\end{aligned}\end{equation}
+where \(\vec k_0\) is the crystal momentum in the ground-state, and \(\ket{\psi}_\text{aux}(\vec R) = \frac{1}{w}\sum_{\vec a}^{\text{NN of }\vec R} \ket{\psi}_\text{aux}(\vec R, \vec a)\).
+The exponentiated sum can be simplified by inserting the momentum eigenbasis \(\left\{ \ket{\vec k}\bra{\vec k}\right\} \) of the auxiliary model Hilbert space, and shifting all the Hamiltonians \(\mathcal{H}\left( \vec R_c \right)\) to the origin \(\vec R_0\), using translation operators:
+\begin{equation}\begin{aligned}
+	\left[\sum_{\vec R_c}\mathcal{H}\left( \vec R_c \right)\right]^n &= \left[\sum_{\vec R_c,\vec k,\vec k^\prime}T^\dagger_{\vec R_c - \vec R_0}\ket{\vec k}\bra{\vec k}\mathcal{H}(\vec R_0)\ket{\vec k^\prime}\bra{\vec k^\prime}T_{\vec R_c - \vec R_0}\right]^n = \left[\sum_{\vec k,\vec k^\prime}\ket{\vec k}\bra{\vec k^\prime}\mathcal{H}_{\vec k, \vec k^\prime}(\vec R_0)\sum_{\vec R_c}e^{i \left( \vec k^\prime - \vec k \right) \cdot \left(\vec R_c - \vec R_0\right)}\right]^n\\
+									 &= \left[\sum_{\vec k}\ket{\vec k}\bra{\vec k}\mathcal{H}_{\vec k, \vec k}(\vec R_0)\right]^n = \sum_{\vec k}\ket{\vec k}\bra{\vec k}\left(N_\text{aux}\mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n~,
+\end{aligned}\end{equation}
+where \(N_\text{aux}\) is the number of sites in the auxiliary mode, and we used
+\begin{gather}
+	\mathcal{H}(\vec R_c) = T^\dagger_{\vec R_c - \vec R_0}\mathcal{H}(\vec R_0)T_{\vec R_c - \vec R_0}~,\quad \sum_{\vec R_c}e^{i \left( \vec k^\prime - \vec k \right) \cdot \left(\vec R_c - \vec R_0\right)}  = N_\text{aux}\delta_{\vec k, \vec k^\prime}~,
+\end{gather}
+We also defined the Hamiltonian matrix element \(\mathcal{H}_{\vec k, \vec k^\prime}(\vec R_0) = \braket{\vec k | \mathcal{H}(\vec R_0) | \vec k^\prime}\).
+Substituting this back into eq.~\eqref{retarded_matrix_element} gives
+\begin{equation}\begin{aligned}
+	\mathcal{U}(\vec r)^{(n)}_> = \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec k} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_i) | c_{\vec R + \vec r, \sigma} | \vec k}\left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n \braket{\vec k | c_{\vec R, \sigma}^\dagger | \psi_\text{aux}(\vec R_j)}~,
+\end{aligned}\end{equation}
+We shift the ground-states \(\ket{\psi_\text{aux}}\) to \(\vec R_0\) as well, using the translation operators:
+\begin{equation}\begin{aligned}
+	\sum_{\vec R_j}e^{i\vec R_j \cdot \vec k_0}\braket{\vec k | c_{\vec R, \sigma}^\dagger | \psi_\text{aux}(\vec R_j)} &= \sum_{\vec R_j}e^{i\vec R_j \cdot \vec k_0}\braket{\vec k | c_{\vec R, \sigma}^\dagger T^\dagger_{\vec R_j - \vec R_0} | \psi_\text{aux}(\vec R_0)} = \sum_{\vec R_j, \vec q}e^{i\vec R_j \cdot \vec k_0}\braket{\vec k | c_{\vec R, \sigma}^\dagger e^{-i\vec q\cdot(\vec R_j - \vec R_0)} | \vec q}\braket{\vec q | \psi_\text{aux}(\vec R_0)}\\
+															    &= N e^{i\vec R_0 \cdot \vec k_0}\braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}\braket{\vec k_0 | \psi_\text{aux}(\vec R_0)}\\
+\end{aligned}\end{equation}
+All the position variation is then transferred to the creation and annihilation operators, leading to the simpler form
+\begin{equation}\begin{aligned}
+	\mathcal{U}(\vec r)^{(n)}_> &= \frac{1}{\lambda_{\vec k_0}^2}\sum_{\vec k} \braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} \braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}|\braket{\psi_\text{aux}(\vec R_0) | \vec k_0}|^2\left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n \\
+				    &= \sum_{\vec k} \braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} \braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}\left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n~.
+\end{aligned}\end{equation}
+The advanced correlation \(\mathcal{U}(\vec r)^{(n)}_<\) can be obtained similarly:
+\begin{equation}\begin{aligned}
+	\mathcal{U}(\vec r)^{(n)}_< = \sum_{\vec k} \braket{\vec k_0 | c_{\vec R, \sigma}^\dagger | \vec k} \braket{\vec k | c_{\vec R + \vec r, \sigma} | \vec k_0}\left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n~.
+\end{aligned}\end{equation}
+Substituting this into eq.~\eqref{greens_func_bulk} gives
+\begin{equation}\begin{aligned}
+	G(\vec r, \omega) &= \sum_{\vec k}\left[\frac{\braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} \braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}}{\omega + E_\text{gs}}\sum_n\frac{\lambda^-_n \left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n}{(\omega + E_\text{gs})^{n}} + \frac{\braket{\vec k_0 | c_{\vec R, \sigma}^\dagger | \vec k} \braket{\vec k | c_{\vec R + \vec r, \sigma} | \vec k_0}}{\omega - E_\text{gs}}\sum_n \frac{\lambda^+_n \left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n}{(\omega - E_\text{gs})^{n}}\right]\\
+	&= \sum_{\vec k}\left[\frac{\braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} \braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}}{\omega + E_\text{gs} - N\mathcal{H}_{\vec k, \vec k}(\vec R_0)} + \frac{\braket{\vec k_0 | c_{\vec R, \sigma}^\dagger | \vec k} \braket{\vec k | c_{\vec R + \vec r, \sigma} | \vec k_0}}{\omega - E_\text{gs} + N\mathcal{H}_{\vec k, \vec k}(\vec R_0)}\right]
+\end{aligned}\end{equation}
+Because of strong correlations in the model, the ground-state energy \(\varepsilon_\text{gs}\) of the auxiliary model can be approximated as \(\varepsilon_\text{gs} \sim E_\text{egs}/N\).
+Moreover, the operator matrix elements in the numerator evaluate to simple phase factors:
+\begin{eqnarray}
+	&\braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} &= \sum_{\vec q} e^{-i\vec q \cdot \left( \vec R + \vec r \right)} \braket{\vec k_0 | c_{\vec q, \sigma} | \vec k} = \sum_{\vec q} \theta(|\vec q| - |\vec k_F|) e^{-i\vec q \cdot \left( \vec R + \vec r \right)} \braket{\vec k_0 + \vec q | \vec k} \\
+	 &&=  \theta(|\vec k - \vec k_0| - |\vec k_F|) e^{-i\left(\vec k - \vec k_0\right) \cdot \left( \vec R + \vec r \right)} \\
+	&\braket{\vec k_0 | c^\dagger_{\vec R, \sigma} | \vec k} &= \sum_{\vec q} e^{i\vec q \cdot \vec R} \braket{\vec k_0 | c^\dagger_{\vec q, \sigma} | \vec k} = \sum_{\vec q} \theta(|\vec k_F| - |\vec q|) e^{i\vec q \cdot \left( \vec R + \vec r \right)} \braket{\vec k_0 - \vec q | \vec k} \\
+	 &&=  \theta(|\vec k_F| - |\vec k_0 - \vec k|) e^{i\left(\vec k - \vec k_0\right) \cdot \left( \vec R + \vec r \right)} \\
+	 &\braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k}\braket{\vec k | c^\dagger_{\vec R, \sigma} | \vec k_0} &= \theta(|\vec k - \vec k_0| - |\vec k_F|)e^{-i\left(\vec k - \vec k_0\right) \cdot \vec r},\\
+	&\braket{\vec k_0 | c_{\vec R, \sigma}^\dagger | \vec k} \braket{\vec k | c_{\vec R + \vec r, \sigma} | \vec k_0} &= \theta(|\vec k_F| - |\vec k_0 - \vec k|)e^{i\left(\vec k - \vec k_0\right) \cdot \vec r}
+\end{eqnarray}
+With these inputs, we can write down the final form of the Greens function:
+\begin{equation}\begin{aligned}
+	G(\vec r, \Omega) = \sum_{\vec k}\left[\frac{\theta(|\vec k - \vec k_0| - |\vec k_F|) e^{i\left(\vec k - \vec k_0\right) \cdot \vec r}}{\omega + N\varepsilon_\text{gs} - N\mathcal{H}_{\vec k, \vec k}} + \frac{\theta(|\vec k_F| - |\vec k_0 - \vec k|) e^{-i\left(\vec k - \vec k_0\right) \cdot \vec r}}{\omega - N\varepsilon_\text{gs} + N\mathcal{H}_{\vec k, \vec k}}\right]
+\end{aligned}\end{equation}
+In this expression, the state \(\ket{\vec k}\) represents one of total momentum.
+One can write this in terms of single-particle excitations \(\ket{\vec q},~\vec q = \vec k - \vec k_0\), which is equal to \(c^\dagger_q \ket{\vec k_0}\) when \(q > 0\) and \(c_q \ket{\vec k_0}\) when \(q < 0\).
+In terms of these single-particle excitations, the Greens function can be written as
+\begin{equation}\begin{aligned}
+	G(\vec r, \Omega) = \sum_{\vec q}\left[\frac{\theta(|\vec q| - |\vec k_F|) e^{i\vec q \cdot \vec r}}{\omega + N\varepsilon_\text{gs} - N\mathcal{E}^p_{\vec q}} + \frac{\theta(|\vec k_F| - |- \vec q|) e^{-i\vec q \cdot \vec r}}{\omega - N\varepsilon_\text{gs} + N\mathcal{E}^h_{\vec q}}\right]~,
+\end{aligned}\end{equation}
+where the matrix elements \(\mathcal{E}^p\) and \(\mathcal{E}^h\) for the particle and hole excitations are given by \(\mathcal{E}^p_{\vec q} = \mathcal{H}_{\vec k_0 + \vec q, \vec k_0 + \vec q} = \braket{\vec k_0 | c_{\vec q} \mathcal{H} c^\dagger_{\vec q} | \vec k_0}\) and \(\mathcal{E}^h_{\vec q} = \mathcal{H}_{\vec k_0 - \vec q, \vec k_0 - \vec q} = \braket{\vec k_0 | c^\dagger_{\vec q} \mathcal{H} c_{\vec q} | \vec k_0}\).
+
+By substituting this for all the auxiliary model terms and by using the unitarity condition \(T^\dagger T = 1\), we get
+\begin{equation}\begin{aligned}
+	\mathcal{U}(\vec r) &= \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_c} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_0) | T_{\vec R_i - \vec R_0} c_{\vec R + \vec r, \sigma} T^\dagger_{\vec R_c - \vec R_0} \mathcal{H}\left(\vec R_0\right) T_{\vec R_c - \vec R_0} c_{\vec R, \sigma}^\dagger T^\dagger_{\vec R_j - \vec R_0} | \psi_\text{aux}(\vec R_0)}\\
+					     &= \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_c} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_0) | T_{\vec R_i - \vec R_c} c_{\vec R + \vec r + \vec R_0 - \vec R_c, \sigma} \mathcal{H}\left(\vec R_0\right) c_{\vec R + \vec R_0 - \vec R_c, \sigma}^\dagger T^\dagger_{\vec R_j - \vec R_c} | \psi_\text{aux}(\vec R_0)}
+\end{aligned}\end{equation}
+Since each summation is over all lattice translation vectors, we can make the substitutions \(\vec R_{i(j)} \to \vec R_{i(j)} - \vec R_c\), followed by \(\vec R_c \to \vec R + \vec R_0 - \vec R_c\), to get
+\begin{equation}\begin{aligned}
+	\mathcal{U}(\vec r) &= \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_c} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_0) | T_{\vec R_i} c_{\vec R_c + \vec r, \sigma} \mathcal{H}\left(\vec R_0\right) c_{\vec R_c, \sigma}^\dagger T^\dagger_{\vec R_j} | \psi_\text{aux}(\vec R_0)}\\
+					     &=\frac{1}{\lambda_{\vec k_0}^2}\sum_{\vec R_c} \braket{\psi_\text{aux}(\vec R_0) | \tilde c_{\vec R_c + \vec r, \sigma} \mathcal{H}\left(\vec R_0\right) \tilde c_{\vec R_c, \sigma}^\dagger | \psi_\text{aux}(\vec R_0)}
+\end{aligned}\end{equation}
+where we have defined the modified creation operator 
+\begin{equation}\begin{aligned}
+	\tilde c^\dagger_{\vec R_c} = c^\dagger_{\vec R_c} \frac{1}{N}\sum_{\vec R_j} e^{i \vec R_j \cdot \vec k_0} T^\dagger_{\vec R_j} = c^\dagger_{\vec R_c} \frac{1}{N}\sum_{\vec R_j, \vec k} e^{i \vec R_j \cdot \vec k_0} e^{-i \vec R_j \cdot \vec k} \ket{\vec k}\bra{\vec k} = c^\dagger_{\vec R_c} \frac{1}{N}\sum_{\vec k} N \delta_{\vec k,\vec k_0} \ket{\vec k}\bra{\vec k} = c^\dagger_{\vec R_c} \ket{\vec k_0}\bra{\vec k_0}~.
+\end{aligned}\end{equation}
+\(\ket{\vec k}\) is the many-body eigenstate of the kinetic energy operator, with total momentum \(\vec k\).
+Because of translation invariance, the matrix element \(\mathcal{C}(\vec R + \vec r, \vec R)\) is independent of the absolute position \(\vec R\) and depends only on the relative distance \(\vec r\).
+The above relation ensures that in order to calculate the correlation \(\mathcal{C}(\vec r)\) in the bulk Hamiltonian, we need only solve the auxiliary model at \(\vec R_0\) and calculate the matrix elements of the operators \(\tilde c_{\vec R_c + \vec r, \sigma} \mathcal{H}\left(\vec R_0\right) \tilde c_{\vec R_c, \sigma}^\dagger\) in the auxiliary model ground-state.
+
+As discussed above, the local nature of the auxiliary models (onsite matrix element only on the impurity and non-local matrix element only between impurity and zeroth site) renders all diagonal matrix elements zero, except the one for \(i=j\):
+\begin{equation}\begin{aligned}
+	\braket{i | H_\text{H-H} | i} = \braket{i | \mathcal{H}_\text{aux,i} | i} = \braket{\psi_\text{aux} | c_{i\sigma} e^{-i \vec{k}\cdot\vec{R}_i} \mathcal{H}_\text{aux,i} e^{i \vec{k}\cdot\vec{R}_i} c^\dagger_{i\sigma} | \psi_\text{aux}} = \braket{\psi_\text{aux} | c_{i\sigma} \mathcal{H}_\text{aux,i} c^\dagger_{i\sigma} | \psi_\text{aux}} = \braket{\psi_\text{aux} | c_{d\sigma} \mathcal{H}_\text{aux} c^\dagger_{d\sigma} | \psi_\text{aux}}
+\end{aligned}\end{equation}
+At the last step, we recognised \(i\) as the impurity site and rewrote the expression entirely in terms of a site-independent auxiliary model.
+Similarly, the off-diagonal matrix element between two nearest-neighbour sites \(i,j\) is obtained as
+\begin{equation}\begin{aligned}
+	\braket{i | H_\text{H-H} | j} = \braket{i | \left(\mathcal{H}_\text{aux,i} + \mathcal{H}_\text{aux,j}\right) | j} = \frac{1}{w}\braket{\psi_\text{aux} | c_{i\sigma} e^{-i \vec{k}\cdot\vec{R}_i} \left(\mathcal{H}_\text{aux,i,j} + \mathcal{H}_\text{aux,j,i}\right) e^{i \vec{k}\cdot\vec{R}_j} c^\dagger_{j\sigma} | \psi_\text{aux}} \\
+	= \frac{1}{w}e^{i \vec{k}\cdot\left(\vec{R}_j - \vec{R}_i\right)}\braket{\psi_\text{aux} | \left(c_{d\sigma}\mathcal{H}_\text{aux} c^\dagger_{0\sigma} + c_{0\sigma}\mathcal{H}_\text{aux} c^\dagger_{d\sigma}\right) | \psi_\text{aux}}
+\end{aligned}\end{equation}
+\(\mathcal{H}_\text{aux,i,j}\) is the auxiliary model with \(i\) as the impurity site and \(j\) as the bath zeroth site.
+
+We now define the Greens {\it operators}:
+\begin{equation}\begin{aligned}
+	\mathcal{G}_{H-H} = \frac{1}{\omega - \left(H_{H-H} - E_\text{gs}\right) }, \mathcal{G}_\text{aux}(i) = \frac{1}{\omega - \left(\mathcal{H}_\text{aux}(i) - E_\text{gs}\right)}
+\end{aligned}\end{equation}
+Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian and also of the full model \(\mathcal{H}_{H-H}\).
+Rewriting eq.~\ref{siam_to_hubb} in terms of the operators \(\mathcal{G}\), we get
+\begin{equation}\begin{aligned}
+\sum_i \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i)\right) = \omega + E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_i \mathcal{G}^{-1}_\text{aux}(i) = \mathcal{G}^{-1}_{H-H}~,
+\end{aligned}\end{equation}
+We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model.
+Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(\mathcal{H}_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate.
+We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{w}\sum_j \sum_{k \in \text{NN of j}}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(j,k) c^\dagger_{i\sigma} | \Phi_0}
+\end{aligned}\end{equation}
+The superscript \(p\) indicates that this is the particle propagation matrix element.
+Under the single site approximation, we ignore the hopping between multiple impurity that reside in separate instances of the auxiliary model.
+Therefore, the only operator \(\mathcal{G}^{-1}_\text{aux}(j)\) that affects the matrix element is \(j=i, k \in \text{NN of i}\).
+Moreover, because of translation invariance, all \(k\) are equivalent.
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \frac{1}{w} w\times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i) c^\dagger_{i\sigma} | \Phi_0} = \braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{d\sigma} | \Phi_0}
+\end{aligned}\end{equation}
+where we have identified site \(i\) in the auxiliary model as the impurity.
+By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}(d)\), we get from the spectral representation
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{m,n} \braket{\Phi_0 | c_{d\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux}(d) \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d\sigma} | \Phi_0} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}
+\end{aligned}\end{equation}
+There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(\mathcal{H}_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\).
+We also defined \(d^p_n = \bra{\Phi_n}c^\dagger_{d\sigma}\ket{\Phi_0}\).
+The hole propagation matrix element can be obtained similarly:
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn} 
+\end{aligned}\end{equation}
+where \(d^h_n = \bra{\Phi_n}c_{d\sigma}\ket{\Phi_0}\).
+The off-diagonal matrix elements can also be obtained similarly.
+The difference from the diagonal case is that only one out of the \(w\) nearest-neighbour pairs contributes to the matrix element:
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{i,i+1} \equiv \braket{\Phi_0 | c_{i,\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{w}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i,i+1) c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{w}\braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{z,\sigma} | \Phi_0}
+\end{aligned}\end{equation}
+Here, we identity \(i+1\) as the bath zero mode \(z\) and \(i\) as the impurity \(d\).
+We again define matrix elements \(z_n^p = \braket{\Phi_n | c^\dagger_{z\sigma} | \Phi_0}, z_n^h = \braket{\Phi_n | c_{z\sigma} | \Phi_0}\).
+Thus, the spectral representation of the matrix element is obtained as
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}
+\end{aligned}\end{equation}
+The hole counterpart is
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}
+\end{aligned}\end{equation}
+In summary, the spectral representation of the matrix elements of the four inverse Greens operators are given by
+\begin{gather}
+\label{green_eq_final_siam}
+	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn}\\
+	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}
+\end{gather}
+
+In order to obtain the matrix elements of the Greens operators \(\mathcal{G}_{H-H}\) (as compared to its inverse), we note that we have just observed that the matrix elements of the inverse Greens operators are related to the matrix elements of another inverse operator through some coefficients.
+We can, therefore, use the identity
+\begin{equation}\begin{aligned}
+\left(\hat O\right)_{ij} = \bra{i} \hat O \ket{j} = \sum_{m,n} \braket{i|m} \left(\hat O\right)_{mn} \braket{n|j} \implies \left(\hat O^{-1}\right)_{ij} = \sum_{m,n} \braket{i|m} \left(\hat O^{-1}\right)_{mn} \braket{n|j}
+\end{aligned}\end{equation}
+We can now identify \(\left(\hat O^{-1}\right)_{mn}\) as the matrix elements of \(\mathcal{G}_\text{aux}^{-1}\) in our expressions.
+Using the above relation, we can therefore write the spectral representation of the matrix elements of the Greens operators as
+\begin{gather}
+	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\\
+	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}_\text{aux}(d, -\omega) \right)_{nn}
+\end{gather}
+
+The Lehmann-Kallen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements.
+Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
+\begin{equation}\begin{aligned}
+	\label{greens_func_siam}
+	\left(G_{H-H}(\omega)\right)_\text{loc} = \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right] \\
+	= G(\omega)_\text{aux,dd}
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	\left(G_{H-H}(\omega)\right)_\text{n-n} = \left(G_{H-H}(\omega)\right)_{i,i+1}^p - \left(G_{H-H}(-\omega)\right)_{i+1,i}^h = \frac{1}{w}\sum_n \left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn} \right.\\
+ - \left.\left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]= \frac{1}{w}G(\omega)_\text{aux,dz}
+\end{aligned}\end{equation}
+
+\section{Spectral functions and self-energies}
+
+The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
+\begin{equation}\begin{aligned}
+	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
+\end{aligned}\end{equation}
+where $\vec{r_i}$ is the position vector of a particular lattice site.
+Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites.
+As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
+As we do not have real space Greens function that are more non-local than nearest neighbour, we will attempt to obtain momentum space Greens function from these two contributions:
+\begin{equation}\begin{aligned}
+	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
+\end{aligned}\end{equation}
+The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, w\right]\right\}$.
+\begin{equation}\begin{aligned}
+	\label{k_Gf_siam}
+	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} = G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k}\\
+			     &= \sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
+\end{aligned}\end{equation}
+where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\). For example, on a d-dimensional hypercubic lattice, we obtain
+\begin{equation}\begin{aligned}
+	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i
+\end{aligned}\end{equation}
+On a 2D square lattice with lattice spacing $a$, this simplifies to
+\begin{eqnarray}
+	\label{2dsquaretb}
+\xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
+\end{eqnarray}
+where \(\epsilon_{\vec{q}} = -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})\) is the tight-binding dispersion.
+
+We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
+\begin{equation}\begin{aligned}
+	A_\text{H-H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega))\\ 
+	&= -\frac{1}{\pi} \textrm{Im}\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\\
+	&= A_\text{aux,dd} + \frac{\xi_{\vec k}}{w} A_\text{aux,dz}
+\end{aligned}\end{equation}
+where 
+\begin{eqnarray}
+G_\text{aux,dd} &=& \sum_n\left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\nonumber\\
+G_\text{aux,dz} &=& \sum_n\left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
+\end{eqnarray}
+and the spectral function $A_\text{aux,dd}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dd}$~,~$A_\text{aux,dz}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dz}$.
+Further,
+\begin{equation}\begin{aligned}
+A_\text{H-H}(\vec{r}=0,\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{r}=0,\omega)) 
+= A_\text{aux,dd}
+\label{main}
+\end{aligned}\end{equation}
+
+From the local Greens function, we can write down the local self-energy using Dyson's equation: \(\Sigma = \left(G^{(0)}\right)^{-1} - G^{-1}\).
+\(G^{(0)}\) is the non-interacting Greens function.
+Here, non-interacting is defined as the absence of \(U,J\) in the bulk model, and hence the absence of \(U,U_b,J\) in the auxiliary model.
+In real space, the local and nearest-neighbour self-energies are therefore
+\begin{equation}\begin{aligned}
+	\left(\Sigma_\text{H-H}(\omega)\right)_\text{loc} = \left(\left(G_{H-H}(\omega)\right)_\text{loc}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_\text{loc}\right)^{-1} = \left(G(\omega)_\text{aux,dd}^{(0)}\right)^{-1} - \frac{1}{w}\left(G(\omega)_\text{aux,dd}\right)^{-1} \\
+	\left(\Sigma_\text{H-H}(\omega)\right)_\text{n-n} = \left(\left(G_{H-H}(\omega)\right)_\text{n-n}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_\text{n-n}\right)^{-1} = \left(G(\omega)_\text{aux,dz}^{(0)}\right)^{-1} - \frac{1}{w}\left(G(\omega)_\text{aux,dz}\right)^{-1}\\
+\end{aligned}\end{equation}
+
+The \(k-\)space self-energy can be similarly obtained from the \(k-\)space Greens functions
+\begin{equation}\begin{aligned}
+	\label{self-energy1}
+	\Sigma_{H-H}(\vec k,\omega) = \left(\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_{\vec k}\right)^{-1} = \frac{1}{G(\omega)_\text{aux,dd}^{(0)} + \frac{\xi_{\vec k}}{w}G(\omega)_\text{aux,dz}^{(0)}} -  \frac{1}{G(\omega)_\text{aux,dd} + \frac{\xi_{\vec k}}{w}G(\omega)_\text{aux,dz}}
+\end{aligned}\end{equation}
+Just to clarify the notation, we reiterate that bulk quantities with a superscript \((0)\) are for the non-interacting Hamiltonian and defined at \(U_\text{H-H}=J_\text{H-H}=0\), while the auxiliary model quantities with that superscript are evaluated in the non-interacting auxiliary model at \(U=J=U_b=0\).
+The non-interacting model is simply a resonant-level model with the impurity level at zero energy.
+Such a model is exactly solvable, and the corresponding Greens functions are given by
+\begin{equation}\begin{aligned}
+	G(\omega + i\eta)_\text{aux,dd}^{(0)} = \frac{1}{\omega + i\left(\Delta + \eta\right)}, ~ ~ ~ G(\omega + i\eta)_\text{aux,dz}^{(0)} = \sum_{\vec k} G(\omega)^{(0)}_{\vec k} V G(\omega + i\eta)_\text{aux,dd}^{(0)}
+\end{aligned}\end{equation}
+where \(\Delta = \pi \rho V^2\) is the hybridisation parameter, assuming a uniform density of states \(\rho\), and \(G(\omega)^{(0)}_{\vec k}\) is the free electron Greens function at momentum \(\vec k\).
+
+\section{Evidence for the Mott MIT}
+Through the URG study of the generalised SIAM with correlation (eq.~\ref{siam_attr}) shown in chapter \ref{siam-attr-chap}, we can conclude the following about that model:
+\begin{itemize}
+	\item For \(U_b > J/4\), the couplings \(J\) and \(V\) become irrelevant while \(U\) is relevant, which means that \textbf{the impurity gets cut off from the bath at low energies}.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.48\textwidth]{../figures/phase-map-MIT.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/spectral-function.pdf}
+	\caption{{\it Left:} Phase diagram. {\it Right:} Impurity spectral function}
+	\label{spec_func_mit}
+\end{figure}
+
+\item The impurity spectral function \(A_{dd}(\omega)\) and the impurity-bath real space off-diagonal Greens function \(A_{d0}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
+The gap in the diagonal spectral function shows that the impurity site cannot fluctuate through gapless excitations, while the vanishing of the off-diagonal spectral function shows that an electron on the impurity site cannot delocalise out of that site.
+Other measures like mutual information and spin-spin correlations also show a sharp change on crossing that value, demonstrating \textbf{the destruction of the Kondo cloud and the stabilisation of the local moment on the impurity}.
+
+\begin{figure}[!htb]
+\centering
+	\includegraphics[width=0.48\textwidth]{../figures/corrs_gs.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/spin-charge-corr-full.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/mutinfo-d0-01-full.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/doub_occ.pdf}
+\end{figure}
+
+	\item In the context of the auxiliary model, this represents an \textbf{impurity phase transition} from the completely-screened spin-singlet phase to the unscreened local moment phase.
+
+Using the mappings between the auxiliary model parameters and the bulk parameters (eq.~\ref{map_aux_bulk}), one can define a critical value \(r^{*}\) of the ratio \(r = U_{H-H}/J_{H-H}\) at the critical points \(-U_b/J=1/4\) \textit{for a given and fixed value of \(U\)}.
+We will now argue that this critical point describes a metal-insulator transition.
+For \(r < r^{*}\), the well-defined low-\(\omega\) central peak in the impurity spectral function, as well as the large mutual and information correlations, in the ground state, among the members of the Kondo cloud or between the impurity and the zeroth site show that the impurity and the bath are very strongly entangled, and the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) are non-zero at low \(\omega\).
+This means that both the local and the nearest-neighbour Greens functions, that are related to these parameters via eq.~\ref{greens_func_siam}, have poles at low\(-\omega\) and support the propagation of electrons through gapless excitations.
+Since the spectral function is also very simply related to that of the auxiliary model (eq.\eqref{main}), the former also shows the same zero-energy resonance.
+
+On the other side \(r > r^{*}\) of the critical point, we know that the impurity gets decoupled from the bath, such that the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) vanish.
+This is simply the loss of spectral weight at low-\(\omega\) because of the removal of the gapless excitations, and is demonstrated through the impurity spectral function in fig.~\ref{spec_func_mit}.
+This then implies that the bulk Greens functions will also gap out at low energies, and that describes an insulating phase where the electrons get "jammed" in the local states.
+By the same argument as above, the bulk spectral function also sees a gap in this phase when the impurity spectral function is gapped (see eq.\eqref{main}).
+
+Finally, using eqs.\eqref{map_aux_bulk} and the criticality condition $U_{b}^{*}=-\frac{J^{*}}{4}$, we can offer a functional form for the critical value of the parameter $r^{*} = U_{H-H}^{*}/J_{H-H}^{*}$
+\begin{eqnarray}
+r^{*} &=& \frac{U_{H-H}^{*}}{J_{H-H}^{*}} = \frac{w}{4}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)
+\end{eqnarray}
+where $U^{*}$ and $J^{*}$ are the values of the on-site and Kondo couplings of the auxiliary model at the auxiliary model (i.e., the generalised SIAM with a correlated bath) at the transition between the Kondo screened and the local moment phases.
+Parametrising the bath correlation coupling as $U_{b}=-\frac{U}{10}$, we obtain $U^{*}/J^{*}=5/2$, and $r^{*} = 2$ for the 2D square lattice Hubbard-Heisenberg model (with coordination number $w=4$).
+In general, $w=2d$ for the $d$-dimensional hypercubic lattice, and
+$r^{*}_\text{hyperc.} = \frac{d}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)$.
+The growth of $r^{*}$ with $d$ indicates that the MIT is increasingly rendered difficult in a higher dimensional hypercubic lattice, as it is easier for electrons to delocalise and a very large on-site repulsion is needed to overcome this.
+\end{itemize}
+
+\comment{
+\section{\(k-\)space picture of the MIT in terms of the momentum-resolved self-energy \(\Sigma(\vec k,\omega)\)}
+
+From the self-energy expressions obtained above, one can track the self-energy of the lattice model through the metal-insulator transition.
+In fig.~\ref{four-self}, we have provided these plots at specific values of \(U_b/J\) to show how the transition plays out in the Brillouin zone.
+{\it These plots can also be viewed as a video \href{https://abhirup-m.github.io/misc-sigma/}{\underline{here}}.}
+
+\begin{center}
+\begin{tabular}{c|c}
+\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.02500-4.pdf} &
+\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.10310-4.pdf}\\
+\hline
+\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.15735-4.pdf} &
+\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.23594-4.pdf}\\
+\hline
+\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.25000-4.pdf} &
+\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=0.25010-4.pdf}
+\end{tabular}
+\captionof{figure}{Each of the 6 frames shows \(A(\vec k)\) at four values of \(\omega\).
+First 4 are before the transition (\(-U_b/J < 0.25\)), fifth is exactly at the transition \((-U_b/J = 0.25)\) and last one is after the transition (\(-U_b/J > 0.25\)).
+Available as video \href{https://abhirup-m.github.io/misc-sigma/}{\underline{here}}.}
+\label{four-self}
+\end{center}
+
+In each frame, the top left figure represents the self-energy at \(\omega=0\).
+If we track this particular figure across the frames, we find that at small \(-U_b/J\), the self-energy near the Fermi surface was smaller than those near the Brillouin zone edges, indicating the presence of a prominent Fermi liquid.
+As \(U_b\) increases, we find that this distinction of the Fermi surface becomes less-prominent; at the critical point,we see that the self-energy near the Fermi surface self-energy has become more than that near the edges, signalling that the quasiparticle excitations have become scrambled because of the increased correlations in the bath.
+
+If we, on the other hand, track the bottom right figure in each frame (\(\omega = U/2\)), we find that deep in the metallic regime, the self-energy is quite high.
+This is because of the low spectral weight at large \(\omega\).
+As the correlations are increased, we find that  this self-energy decreases, particular in comparison to the values at the Brillouin zone edges.
+This is because of the appearance of the Hubbard side-peaks in the local spectral function
+.
+
+In the insulating phase, we find that the momentum-dependence has vanished (the system is in the perfectly local atomic limit).
+The self-energy at the Hubbard side-bands (bottom right) is high, because the quasiparticle excitations are highly-renormalised and the single-particle picture description is not possible.
+The self-energy inside the gap (other three figures) diverges and the poles of the Greens function have been replaced by zeroes, so we have instead plotted the inverse self-energy.
+
+These plots are available as videos \href{https://abhirup-m.github.io/misc-sigma/}{\underline{here}}.
+}
+
+\section{Some important remarks}
+\subsection{Entanglement as an order parameter for the transition}
+The spectral weights in the diagonal Greens function can be written in terms of a geometric measure of entanglement:
+\begin{equation}\begin{aligned}
+	d_n^p = \braket{\Phi_n | c^\dagger_{d\sigma} | \Phi_0} = \braket{\Phi_n | c^\dagger_{d\sigma} \sum_n \ket{\phi_m} \bra{\phi_m} | \Phi_0}
+\end{aligned}\end{equation}
+where, \(\ket{\phi_m}\) are the eigenstates of the Hamiltonian composed of a two-site system (formed by the impurity site and the zeroth site) in direct product with the rest of the lattice sites.
+The two site system interacts only via a spin-exchange coupling \(J\), and the impurity and bath sites have local correlations \(U\) and \(U_b\) respectively.
+The ground state is the spin-singlet in direct product with the ground state of the tight-binding chain formed by the remaining sites.
+The summation involves inner products of the ground state \(\ket{\Phi_0}\) with the eigenstates \(\ket{\phi_m}\).
+Only two states out of all \(\ket{\phi_m}\) give non-zero overlap - the spin singlet state \(\ket{SS}\) and the charge triplet-zero state \(\ket{CT}\).
+These two non-zero overlaps give rise to non-zero entanglement: \(\varepsilon_\text{SS} = 1 - |\braket{\Phi_0 | SS}|^2, \varepsilon_\text{CT} = 1 - |\braket{\Phi_0 | CT}|^2\).
+The spectral weight becomes
+\begin{equation}\begin{aligned}
+	d_n^p = \bra{\Phi_n} | c^\dagger_{d\sigma} \left(\ket{SS} + \ket{CT} \right) \left(\sqrt{1 - \varepsilon_\text{SS}} + \sqrt{1 - \varepsilon_\text{CT}}\right)
+\end{aligned}\end{equation}
+The total spectral weight can be written as
+\begin{equation}\begin{aligned}
+	|d_n^p|^2 = |\bra{\Phi_n} | c^\dagger_{d\sigma} \left(\ket{SS} + \ket{CT} \right)|^2 \left(2 - \varepsilon_\text{SS} - \varepsilon_\text{CT} + 2\sqrt{1 - \varepsilon_\text{SS}}\sqrt{1 - \varepsilon_\text{CT}}\right)
+\end{aligned}\end{equation}
+Near the metal, the ground state is, to a very good approximation, the state \(\ket{SS}\).
+One can then say that the entanglement \(\varepsilon_\text{SS}\) is poor - the entangled state is very close to the "separable" state.
+The term separable is used here in the sense that the metallic state defines a limit of the system.
+As \(U_b\) increases, \(\varepsilon_\text{SS}\) increases.
+On the other hand, the entanglement with the charge triplet is maximum in the metal, because the ground state does not have much of the charge triplet.
+Towards the MIT, this contribution increases, and the entanglement decreases.
+
+\subsection{Topological nature of the transition}
+As shown in section~\ref{lutt_theorem}, there is a difference in the value of the Luttinger volume between the local moment (LM) and the strong-coupling (SC) fixed points.
+If we define \(\mathcal{N}_L\) as the Luttinger volume with the spin-degeneracy accounted for, we can write
+\begin{equation}\begin{aligned}
+	\label{lutt_change}
+	\mathcal{N}_L^\text{lm} - \mathcal{N}_L^\text{sc} = 1
+\end{aligned}\end{equation}
+where \(\mathcal{N}_L^\text{lm},\mathcal{N}_L^\text{sc}\) are the Luttinger volumes at the local moment and strong-coupling fixed points respectively.
+This equation expresses the fact that the Luttinger volume of the bath increases by \(1\) when the system is tuned from LM to SC, and this happens because the single-particle impurity excitation in the lower-Hubbard at the atomic limit gets transferred to the bath Greens function in the process.
+The quantity which tracks this transfer is therefore \(\mathcal{N}_\text{imp}\), the number of poles minus the number of zeros in the impurity Greens function at and below the Fermi surface:
+\begin{equation}\begin{aligned}
+	\label{imp_count_def}
+	\mathcal{N}_\text{imp} = \begin{cases}
+		1 & \text{ at LM}\\
+		0 & \text{ at SC}
+	\end{cases}\implies \Delta \mathcal{N}_\text{imp} = 1
+\end{aligned}\end{equation}
+The Luttinger volume \(\mathcal{N}_L\) is related to this impurity count by the equation
+\begin{equation}\begin{aligned}
+	\mathcal{N}_L = \mathcal{N} - \mathcal{N}_\text{imp}
+\end{aligned}\end{equation}
+where \(\mathcal{N}\) is the total number of electrons in the system, accounting for the spin degeneracy.
+If we keep this total number fixed (isolated system), the changes in the impurity count and Luttinger volume become constrained:
+\begin{equation}\begin{aligned}
+	\Delta \mathcal{N}_L = - \Delta \mathcal{N}_\text{imp}~.
+\end{aligned}\end{equation}
+Eq.~\ref{imp_count_def} then readily implies eq.~\ref{lutt_change}.
+
+In order to connect this impurity topological change with the bulk model, we write the total number of particles in the bulk system in the following manner:
+\begin{equation}\begin{aligned}
+	\mathcal{N} = \mathcal{N}_\text{loc} + \mathcal{N}_\text{deloc}
+\end{aligned}\end{equation}
+\(\mathcal{N}_\text{loc}\) is the number of real poles minus the number of zeros of the local Greens function.
+\(\mathcal{N}_\text{deloc}\) is the number of real poles minus the number of zeros of the \(k-\)space Greens functions.
+The former (latter) contributes only in the insulating (metallic) phase, because in the metallic (insulating) phase, the local (\(k-\)space) Greens function develop imaginary self-energy and the real poles in these Greens functions get replaced by imaginary poles.
+Together, these two terms accurately count the total number of particles in both these phases.
+These two terms are defined as
+\begin{equation}\begin{aligned}
+	\mathcal{N}_\text{loc} = \sum_i \mathcal{N}_i = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_i(z)\right], ~ ~ ~\mathcal{N}_\text{deloc} = \sum_k \mathcal{N}_k = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_k(z)\right] = \mathcal{N}_L
+\end{aligned}\end{equation}
+\(G_i(z)\) is the local Greens function at site \(i\) of the bulk model, and \(G_k(z)\) is the \(k-\)space Greens function in the bulk model.
+\(N_\text{deloc}\) is just the Luttinger volume \(\mathcal{N}_L\) of the bulk system.
+With this, the total number of particles in the bulk can be expressed as
+\begin{equation}\begin{aligned}
+	\label{bulk_total}
+	\mathcal{N} = \sum_i \mathcal{N}_i + \mathcal{N}_\text{L}
+\end{aligned}\end{equation}
+From eq.~\ref{greens_func_siam}, we know that the bulk local Greens function is equal to that of the auxiliary model, and that gives \(\sum_i \mathcal{N}_i = \mathcal{N}_\text{imp}\sum_i = \mathcal{N} \mathcal{N}_\text{imp}\).
+There we used the fact that for a half-filled system, the total number of sites is equal to the total number of particles in the system.
+Substituting this into eq.~\ref{bulk_total} and again using \(\Delta \mathcal{N} = 0\) gives
+\begin{equation}\begin{aligned}
+	\mathcal{N} = \mathcal{N} \mathcal{N}_\text{imp} + \mathcal{N}_\text{L} \implies \Delta \mathcal{N}_\text{L} = - \mathcal{N} \Delta \mathcal{N}_\text{imp}
+\end{aligned}\end{equation}
+We already know that \(\Delta \mathcal{N}_\text{imp}=1\) across the transition, so we get
+\begin{equation}\begin{aligned}
+	\mathcal{N}_L^\text{metal} - \mathcal{N}_L^\text{insulator} = \mathcal{N}\left(\mathcal{N}_\text{imp}^\text{sc} - \mathcal{N}_\text{imp}^\text{lm}\right) = \mathcal{N}
+\end{aligned}\end{equation}
+The metal-insulator transition is therefore characterised by a change in the topological quantity \(\mathcal{N}_L\).
+The topological nature arises from the fact that it can be expressed in terms of winding numbers related to the corresponding Greens functions.
+\(\mathcal{N}_\text{imp}\), which derives from the impurity Greens function \(G_d\), is related to the winding numbers of the curves \(\text{Det}[G_d^{-1}(\Gamma^<)]\) and \(\text{Det}[G_d^{-1}(\Gamma^0)]\).
+The winding number is simply the number of times this function encircles the origin when traced on the curves \(\Gamma^<\) and \(\Gamma^0\) that enclose all poles inside and on the Fermi surface respectively.
+An example of such a winding number is shown in fig.~\ref{imp_winding}.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[scale=0.2]{../figures/luttinger_top_change.png}
+	\caption{The green lines describe the winding number related to the impurity Greens function, while the blue lines do it for the bath.
+At the local moment fixed point \(V=0\), the impurity has a winding number of 1 because the curve encircles the origin once.
+At the strong-coupling fixed point, this winding number becomes zero, indicated by the fact that the curve does not encircle the origin even once.
+The reduction in the winding number on the part of the impurity is directly linked to the increase in the winding number of the bath - it encircles the origin once at the local moment fixed point but twice at strong-coupling.}
+	\label{imp_winding}
+\end{figure}
+
+\subsection{Greens function in the insulating phase: the Hubbard bands and mottness}
+In the insulating state, the cluster becomes a local moment and the bulk system reduces to the atomic limit \(H = -\frac{U}{2}\sum_i\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\).
+The Greens function in this limit is given in Appendix~\ref{atomic limit}.
+From eq.~\ref{atomic_limit_gf}, we have
+\begin{equation}\begin{aligned}
+	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 + \left<\tau_{i }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i}\right>}{\omega + \frac{U}{2}}
+\end{aligned}\end{equation}
+where \(\tau_i = \sum_\sigma \hat n_{i,\sigma} - 1\).
+At half-filling \(\left<\tau_{i}\right>=0\), the low and high-energy poles have equal spectral weights.
+\textit{This is different from the situation in a band insulator, where the valence band has all the spectral weight in the ground state while the conduction band is empty.} On doping holes into the system such that \(\left<\tau_{i}\right> = -x < 0\), spectral weight is transferred from the upper Hubbard band at \(\omega = U/2\) to the lower one at \(\omega = -U/2\):
+
+\begin{equation}\begin{aligned}
+	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 - x}{\omega - \frac{U}{2}} + \frac{1 + x}{\omega + \frac{U}{2}}
+\end{aligned}\end{equation}
+\textit{This transfer of spectral weight across energy scales of the order of \(U\), as well as the lack of poles at zero energies, is referred to as mottness}~\cite{phillips2006mottness}.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../figures/hubbard_bands.pdf}
+	\caption{Structure of the Greens function in the atomic limit.
+The two poles at \(\omega = \pm \frac{U}{2}\) form the two Hubbard bands.
+Doping the system leads to transfer of spectral weight between the bands.}
+\end{figure}
+
+\subsection{Nature of propagation: metal vs insulator}
+In the metallic state, the impurity in the auxiliary model hybridises with the bath through both 1-particle and 2-particle interactions.
+For any two auxiliary models differing by the locations \(i_1, i_2\) of the impurity, the baths will always overlap.
+This means that an electron that starts out from the impurity site at \(i_1\) can hop into the bath, and eventually reach \(i_2\) by hopping out of the other bath and into the other impurity.
+Such processes connect all sites of the lattice and \textit{allow spectral flow}.
+
+In the insulating state, each auxiliary model separates into an impurity and a bath that decoupled from each other.
+This means that the impurity cannot hybridise into the bath, and hence cannot tunnel into any other impurity.
+This leads to the atomic limit of the system, where each site develops a local moment configuration because of the repulsive local correlation, but these local moments cannot communicate with each other, either through spin-exchange processes or by breaking into holons and doublons.
+Any attempt at spectral flow fails because the boundaries of the system become disconnected from each other.
+
+A more accurate picture of the insulating and metallic phases can be obtained by working with a more complicated choice of the cluster.
+For instance, instead of a single impurity, one can take two correlated impurities interacting with each other through a single-particle hopping, and this cluster then interacts with the bath through the usual interactions.
+The ground state of such a cluster is actually a quantum liquid, consisting of the entangled spin and charge degrees of freedom.
+In the metallic state, various members of this liquid such as the holons, doublons and the spinons are free to propagate across the system through the baths.
+In the insulating state, it is this cluster that then gets decoupled from the other clusters.
+The composite degrees of freedom are then unable to propagate outside the cluster, and \textit{the holons and the doublons are bound to each other}~\cite{Mott_1949} within the confines of the cluster.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=0.55\textwidth]{../figures/metal_prop.pdf}
+	\caption{Propagation of electrons from one cluster to another through the bath, in the metallic state}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=0.75\textwidth]{../figures/ins_prop.pdf}
+	\caption{The clusters get isolated from each other in the insulator, because they get decoupled from their baths.}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=0.85\textwidth]{../figures/ins_prop_cluster.pdf}
+	\caption{Each cluster is a quantum liquid composed of spin \(\left(\uparrow,\downarrow\right) \) and charge \(\left(0,2\right) \) degrees of freedom.
+In the insulating state, these degrees of freedom get bound within the cluster and are unable to propagate outside.}
+\end{figure}
+
+\subsection{Presence of two self-energies under symmetry-breaking}
+The effective Hamiltonian that describes either the metallic or the insulating phase has $\mathrm{SU}(2)$ symmetry in both the spin and charge sectors.
+Since the repulsive correlation on the impurity picks out the spin sector, we focus on that for now.
+Applying a small magnetic field on the impurity breaks this spin-rotation symmetry and picks out either the up or the down state on the impurity, leading to two kinds of self-energies, one for each spin state~\cite{logan_2014,Logan_2015}.
+The Hamiltonian has the form \(H(h)_i = -\frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - h\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)\).
+The unique groundstate is \(\ket{\hat n_{i,\sigma = \text{sgn}(h)}=1,\hat n_{i,\sigma = -\text{sgn}(h)}=0}\), with an energy of \(E_\text{gs} = -\frac{U}{2} - h\).
+The Greens function is easiest to obtain from the Lehmann-Kallen representation (eq.~\ref{Gf_lk}):
+\begin{equation}\begin{aligned}
+	G_{i,\sigma} = \sum_{n}\left[||\bra{\text{GS}}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_\text{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{\text{GS}}||^2\frac{1}{\omega - E_\text{GS} + E_n}\right]\\
+\end{aligned}\end{equation}
+We have \(c_{i,\sigma}\ket{\text{GS}} = \ket{\hat n_i = 0}\delta_{\sigma,\text{sgn}(h)}\) and \(c^\dagger_{i,\sigma}\ket{\text{GS}} = \ket{\hat n_i = 2}\delta_{\sigma,-\text{sgn}(h)}\), so that the only excited states that give non-zero inner product is \(\ket{n}=\ket{\hat n_i = 0}\) for the second term and \(\ket{n}=\ket{\hat n_i=2}\) for the first term, with energies \(E_n=0\).
+Substituting these, we get
+\begin{equation}\begin{aligned}
+	G_{i,\sigma}(h) = \frac{\delta_{\sigma,-\text{sgn}(h)}}{\omega - \frac{U}{2} - h} + \frac{\delta_{\sigma,\text{sgn}(h)}}{\omega + \frac{U}{2} + h} = \frac{1}{\omega + \left(\frac{U}{2}+h\right)\sigma \times \text{sgn}(h) }
+\end{aligned}\end{equation}
+Taking the limit of \(h \to 0^\pm\) then gives
+\begin{equation}\begin{aligned}
+	G_{i,\sigma}(h=0^\pm) = \frac{1}{\omega \pm \frac{U}{2}\sigma}
+\end{aligned}\end{equation}
+The self-energies arising from the correlation \(U\) can also be obtained using Dyson's equation \(\Sigma = G^{-1} - G_0^{-1}\), where \(G_0^{-1} = \omega\) is the Greens function at \(U=0\).
+Using Dyson's equation, we get
+\begin{equation}\begin{aligned}
+	\Sigma_{i,\sigma} = \pm\frac{U}{2}\sigma
+\end{aligned}\end{equation}
+
+\section{Analytic consistency check - On the Bethe lattice}
+One can apply a test to this method: it involves considering the case of infinite number of nearest-neighbours $w\to\infty$ (the coordination number, and effectively the dimension).
+In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
+This allows a metal-insulator transition in the limit of $w\to\infty$ as well.
+In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}.
+This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy1}.
+Applying the limit of \(w\to \infty\) on that equation gives
+\begin{equation}\begin{aligned}
+	\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}\right\} = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux,dd}(\omega)\right\}^{-1}
+\end{aligned}\end{equation}
+where \(G^{(0)}(\vec k,\omega)\) is the non-interacting Greens function and \(G_\text{aux,dd}(\omega)\) is the site-diagonal Greens function of the auxiliary model.
+It is clear from the final form that only the diagonal term \(G_\text{aux,dd}(\omega)\) of the interacting Greens function affects the self-energy while the off-diagonal part \(G_\text{aux,dz}\) fails to contribute as \(w \to \infty\).
+Even the non-interacting part Greens function can be shown to be diagonal in the limit of \(w\to\infty\)~\cite{kuramoto_manybody}.
+From its definition in time domain, we have
+\begin{equation}\begin{aligned}
+	G^{(0)}(\vec k, t) = -i\theta(t) \left<\left\{c_{\vec k}(t), c^\dagger_{\vec k}\right\} \right> = -i\theta(t) \left<\left\{e^{i H^{(0)}t} c_{\vec k} e^{-i H^{(0)}t}, c^\dagger_{\vec k}\right\} \right> = -i\theta(t) e^{-i \epsilon_{\vec k}t}\left[ \left<1 - \hat n_{\vec k}\right> + \left<\hat n_{\vec k}\right>\right] = -i \theta(t) e^{-i \epsilon_{\vec k}t}
+\end{aligned}\end{equation}
+A quick Fourier transform to \(\omega-\)domain shows that this is identical to the \(G^{(0)}(\vec k, \omega)\) defined just above eq.~\ref{self-energy}.
+We note that \(|G^{(0)}(\vec k, t)| \leq 1\).
+Using the Fourier transform  definition
+\begin{equation}\begin{aligned}
+	f(\vec k) = \frac{1}{d_N}\sum_{\vec r_i}h(\vec r_i) e^{i \vec{k}\cdot\vec{r}_i}
+\end{aligned}\end{equation}
+where \(d_N\) is a factor that only depends on the total number of sites and not on the coordination number, we can write
+\begin{equation}\begin{aligned}
+	|G^{(0)}(\vec k, t)|^2 = \frac{1}{d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}
+\end{aligned}\end{equation}
+From the inequality \(|G^{(0)}(\vec k, t)| \leq 1\), we get
+\begin{equation}\begin{aligned}
+	1 \geq \frac{1}{N}\sum_k |G^{(0)}(\vec k, t)|^2 = \frac{1}{N d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* \underbrace{\sum_k e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}}_{N \delta_{\vec r_i = \vec r_j}} = \frac{1}{d_N^2}\sum_{\vec r_i} |G^{(0)}(\vec r_i, t)|^2
+\end{aligned}\end{equation}
+For a coordination number of \(w\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
+Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{w}\).
+In contrast, there is only one local Greens function, that for \(\vec r_i=0\).
+The local Greens function therefore scales independent of \(w\).
+This implies that
+\begin{equation}\begin{aligned}
+	\lim_{w\to \infty}G^{(0)}(\vec k,\omega) = G^{(0)}(\vec r=0,\omega)
+\end{aligned}\end{equation}
+Since both the non-interacting and the interaction Greens functions lose their non-locality, the self-energy becomes completely local in the limit of \(w \to \infty\).
+
+\chapter{Going to larger clusters - the two site approach}
+
+\section{Why expand the cluster?}
+The previous chapter dealt with treating the Hubbard-Heisenberg model using an auxiliary model that has a single-site cluster:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux} =  \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s}_0 - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
+\end{aligned}\end{equation}
+This was able to describe an impurity phase transition from screened strong-coupling phase to local moment weak coupling phase, upon tuning \(U_b/J\).
+This then leads to a metal-insulator transition in the bulk, owing to the relations between the Greens functions and spectral functions obtained earlier.
+The single-site nature of the cluster (there was only a single impurity) has the following consequences:
+\begin{itemize}
+	\item [1.] The \(k-\)space self-energy of the bath has only minimal \(k-\)dependence arising from nearest-neighbour non-locality between the impurity and the zeroth site of the bath.
+	\item [2.] The local moment phase (which reduces to a set of decoupled clusters) becomes just the atomic limit, because each cluster has just one impurity.
+\end{itemize}
+
+In this chapter, we will improve on these two points by considering a larger cluster that has two impurities interacting with each other:
+\begin{equation}\begin{aligned}
+	\label{dimer_ham}
+	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right]\\
+	 -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right) + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
+\end{aligned}\end{equation}
+\(d_1\) and \(d_2\), or \(d_i\) in general, represent the two impurity sites in the dimer.
+They interact with each other through the same hopping parameter \(t\) as the bath.
+Each of the impurities has its own correlation \(U\) and hybridisation with the bath through \(V\) and \(J\).
+Each impurity site \(d_i\) couples with a bath site \(0_i\).
+\(0_1\) and \(0_2\) are assumed to be adjacent to each other, connected by the hopping \(t\).
+The setup is shown in fig.~\ref{two-imp-cluster}.
+
+Note that this chapter only sets out the relations between such an auxiliary model and the corresponding bulk model (in this case, a Hubbard-Heisenberg), but does not describe the physics of this new auxiliary model.
+That requires performing a renormalisation group calculation for \(H_\text{aux}\), and that will be provided at a later point in time.
+
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../figures/two-site-cluster.pdf}
+	\caption{Two-impurity SIAM hybridising with a bath}
+	\label{two-imp-cluster}
+\end{figure}
+
+\section{Solution of the Hubbard dimer using the Anderson molecule}
+This section tries to see how far we can we can go if we just work with the Anderson molecule as the smallest unit of tiling.
+We will attempt to reproduce the entire spectrum of a Hubbard dimer by creating a new Hamiltonian made up purely of Anderson molecules.
+This will guide us in deciding how to generalize the "tiling method" for a general $N-$site Hubbard model, as well as give indications as to whether we need a different smallest unit for tiling.
+
+The Hubbard dimer and Anderson molecules (zero-mode) are defined by the following respective Hamiltonians:
+\begin{equation}\begin{aligned}
+	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat n_{i \uparrow}\hat n_{i \downarrow} - \mu^H \sum_{\sigma, i=1,2}\hat n_{i\sigma}\\
+	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \epsilon_d^A \sum_{\sigma}\hat n_{d\sigma} + U^A\hat n_{d \uparrow}\hat n_{d \downarrow}
+\end{aligned}\end{equation}
+In the first Hamiltonian, the indices \(i=1,2\) refer to the two lattice sites that constitute the dimer.
+In the second Hamiltonian, the subscript \(d\) indicates the impurity site, while the subscript \(z\) indicates the zero-mode site.
+First, we will assume that the Hubbard dimer is at half-filling (\(\frac{1}{2}U^H = \mu^H\)):
+\begin{equation}\begin{aligned}
+	\label{hubb_dimer}
+	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \left(\frac{1}{2}U^H- \mu^H\right) \sum_{\sigma, i=1,2}\hat n_{i\sigma} + \text{constant}\\
+	    &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
+\end{aligned}\end{equation}
+Since the Hubbard Hamiltonian is at half-filling, we will also place the impurity at half-filling by setting \(\epsilon_d^A = -\frac{1}{2}U^A\):
+\begin{equation}\begin{aligned}
+	\label{and_dimer}
+	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \left(\epsilon_d^A + \frac{1}{2}U^A\right) \sum_{\sigma}\hat \tau_{d\sigma} + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow} + \text{constant}\\
+	    &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow}
+\end{aligned}\end{equation}
+The first step is to recreate the Hubbard dimer Hamiltonian eq.~\ref{hubb_dimer} using the Anderson molecule Hamiltonian eq.~\ref{and_dimer}:
+\begin{equation}\begin{aligned}
+	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
+	    &= \frac{1}{2}\left[-t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + t^H\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\right] + \frac{1}{2} 2U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
+	    &= \frac{1}{2}\left[-t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right)\bigg\vert_{z \to 2, d \to 1\atop{t^A \to t^H}} + t^A\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\bigg\vert_{d \to 2,z \to 1\atop{t^A \to t^H}} \right] \\
+	    &+ \frac{1}{2} \left(U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 1\atop{U^A \to 2U^H}} + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 2\atop{U^A \to 2U^H}}\right)\\
+	    &=\frac{1}{2}\left[H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 1, z \to 2\right) + H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 2, z \to 1\right)\right]
+\end{aligned}\end{equation}
+The conclusion we can draw from this is that the Hubbard dimer Hamiltonian can be obtained from the Anderson dimer Hamiltonian in the following fashion:
+\begin{itemize}
+	\item The essential idea is that we have to create a local Hubbard Hamiltonian for each site of the Hubbard lattice by replacing the impurity label \(d\) in the Anderson dimer with the label of the particular site.
+So if there are two sites, we will get two local Hamiltonians obtained by replacing \(d\) with 1 and 2 respectively.
+For each local Hamiltonian, the zero-mode label \(z\) is replaced by the site that is nearest to the one that \(d\) is being replaced by.
+So, if \(d \to 1(2)\), then \(z \to 2(1)\).
+	\item This, however, is not the only change that we must make, in order to get the local Hamiltonian for a particular site.
+Along with \(d\) and \(z\), we must also make the transformations \(t^A \to t^H, U^A \to 2U^H\).
+	\item Finally, once we have the local Hamiltonians for sites 1 and 2, we average them to get the total Hubbard Hamiltonian.
+\end{itemize}
+Note that we expect most of these "rules" to be specific for the dimer, and there will be generalizations to most of them for a general \(N-\)site Hubbard Hamiltonian.
+
+The wavefunctions for the \(N=2\) sector can also be connected through these transformations.
+Since both the Hamiltonians are analytically solvable, we can write down their groundstate wavefunctions [CITE PAVARINI]:
+\begin{equation}\begin{aligned}
+	\ket{\Psi^H_\text{GS}} &= a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) - a_2(U^H,t^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
+	\ket{\Psi^A_\text{GS}} &= a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) - a_2(\frac{1}{2}U^A,t^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
+	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right), E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right)
+\end{aligned}\end{equation}
+where 
+\begin{equation}\begin{aligned}
+	a_1(U,t) \equiv \frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) - U \right) }}, && a_2(U,t) \equiv \sqrt{\frac{\Delta(U,t) - U}{2\Delta(U,t)}}, &&\Delta(U,t) \equiv \sqrt{U^2 + 16t^2}\\
+\end{aligned}\end{equation}
+$a_1,a_2$ satisfy $a_1(-U,t) = -a_2(U,t)$ and $a_1(U,t)a_2(U,t)= \frac{2t}{\Delta(U,t)}$.
+From the forms of the wavefunctions and eigenenergies, we can immediately write down
+\begin{equation}\begin{aligned}
+	\ket{\Psi^H_\text{GS}} &= \frac{1}{2}\left[\ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 1, z \to 2\right) + \ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 2, z \to 1\right)\right]\\
+	E^H_\text{GS} &= E^A_\text{GS}\left(t^A, U^A \to t^H, 2U^H\right)
+\end{aligned}\end{equation}
+This shows that the rules laid out before work for the Hamiltonians, as well as the wavefunctions and energy eigenvalues of the \(N=2,0,4\) sector.
+These sectors specifically work because it is only in these sectors can we ensure that \(n_d = n_z\), which is required for the Hubbard Hamiltonian because \(n_1 = n_2\).
+In the other sectors (\(N=1,3\)), the impurity site and the zero-mode sites have to be singly-occupied in some part, and since the impurity site incurs a single-occupation cost of \(-\frac{U^H}{2}\) which is not borne by the zero-mode site, there is an intrinsic dissimilarity between the two sites of the Anderson molecule in this regime.
+This dissimilarity does not exist for the Hubbard model, so we cannot hope to connect the two models in this regime.
+Going forward, we will switch to using Hubbard dimers as the smallest tiling unit for a general Hubbard model.
+
+\comment{
+\section{Strategy by starting from a zero bandwidth model}
+We start with a SIAM (with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian.
+The fixed point Hamiltonian will in general involve the impurity site (with renormalised parameters $\epsilon_d^*, U^*$) interacting with a smaller number of momentum states.
+
+ To obtain a comparatively simple but physically well-motivated auxiliary model, we identify $\sum_k c_k = \sqrt N c_0$; \(c_0\) is the operator for the zeroth site (the site nearest to the impurity).
+We will call the set of all \(N-2\) sites apart from the impurity and this zeroth site as the "effective bath".
+The fixed point Hamiltonian can be separated into these parts: an isolated impurity part, an isolated zeroth site part, an isolated effective bath part, hopping between impurity and the zeroth site and hopping between the zeroth site and the effective bath.
+\textit{As a simplification, we will ignore the correlation term \((U)\) on the effective bath}.
+In preparation of a symmetrization procedure, we will relabel the impurity site as 0, and the zeroth site as 1.
+With all these steps, the Hamiltonian takes the form:
+ \begin{equation}\begin{aligned}
+ 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow}}_\text{imp.
+\& zero-mode isolated} - \underbrace{t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{0-1 coupling} - \underbrace{t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{1 \& eff.
+bath coupling} - \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff.
+bath isolated}
+ \end{aligned}\end{equation}
+ \begin{figure}[!htb]
+ 	\centering
+ 	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.png}
+ 	\caption{Correlated asymmetric Anderson molecule schematic version.
+It consists of an impurity site (blue) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink).
+The other sites (green) form the rest of the bath.
+Just the impurity site and the zeroth site have onsite repulsion.}
+ 	\label{and_mol}
+ \end{figure}
+ This Hamiltonian is depicted in fig.~\ref{and_mol}.
+Such a Hamiltonian is, however, explicitly asymmetric between the sites 0 and 1 (the effective bath couples only to 1).
+To rectify that, we will symmetrize the coupling between the effective bath and the sites 0 and 1, by exchanging the sites 0 and 1.
+The resultant Hamiltonian is
+ \begin{equation}\begin{aligned}
+ 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow} - t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{2-site Hubbard model} +\underbrace{- t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)- t^A\sum_{j \in \atop{\text{NN of 0}}}\left(c^\dagger_{0\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{dimer \& eff.
+bath coupling} \\
+ 	- \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff. bath isolated}
+ \end{aligned}\end{equation}
+
+ To further simplify this Hamiltonian, \textit{we will combine the nearest neighbour sites of \(1\) and \(0\) into a single site}.
+ \begin{equation}\begin{aligned}
+ 	c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}
+ \end{aligned}\end{equation}
+ This single site will act as the zeroth site of the effective bath, and it means that both sites of the Hubbard dimer hybridizes with the effective through just a single site.
+With this assumption, the Hamiltonian for "a Hubbard dimer hopping into an effective bath" takes the simple form
+ \begin{equation}\begin{aligned}
+ 	\label{dimer_p_bat}
+ 	\tilde H^D = H^D(0,1) - t^D \sum_{\sigma}\left(c^\dagger_{0\sigma}c_{z\sigma} + c^\dagger_{1\sigma}c_{z\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}
+ \end{aligned}\end{equation}
+ \(H^D(0,1)\) is the Hubbard dimer Hamiltonian (shown in fig.~\ref{hubb-dim}):
+ \begin{equation}\begin{aligned}
+ 	\label{dimer_ham}
+ 	H^D(0,1) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)
+ \end{aligned}\end{equation}
+ \begin{figure}[!htb]
+ 	\centering
+ 	\includegraphics[width=0.4\textwidth]{../figures/hubb_dim.png}
+ 	\caption{Hubbard dimer schematic version. It again consists of two sites, like the Anderson molecule, but now both sites have onsite repulsion, and their is again inter-site hopping.}
+ 	\label{hubb-dim}
+ \end{figure}
+ This entire procedure is depicted in fig.~\ref{dimer-bath}.
+ \begin{figure}[!htb]
+ 	\centering
+ 	\includegraphics[width=\textwidth]{../figures/dimer_bath.pdf}
+ 	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.
+We first add the asymmetric Hamiltonians to get a symmetrized Hamiltonian.
+In the symmetrized Hamiltonian, the dimer has \(w\) entry points into the bath, \(w\) being the coordination number of the lattice.
+We then merge these \(w\) lattice sites (enclosed in the black box) into a single lattice site.}
+ 	\label{dimer-bath} 
+ \end{figure}
+ We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice.
+The next step in the programme is to tile the real-space lattice with this dimer+bath Hamiltonian \(\tilde H_D\) to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H = T\left[ \tilde H^{D} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the dimer Hamiltonian to span the target real-space lattice.
+We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.
+ \begin{equation}\begin{aligned}
+ 	\tilde H &= \frac{2}{Nw}\sum_{\left<ij\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\tilde H^D((0,1,z) \to (i, j, l))\\
+ 		 &= \frac{2}{N}U^D\sum_{i} \tau_{i \uparrow}\tau_{i \downarrow} - \frac{2}{Nw}\left(1 + \frac{Nw}{2}\right)t^D\sum_{\left<ij\right>}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)
+ \end{aligned}\end{equation}
+ What that means is that we have placed the Hubbard dimer+bath system at all nearest neighbour pairs to reconstruct a new Hubbard model.
+If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as dropping the correlation on the bath sites, we can write
+ \begin{equation}\begin{aligned}
+ 	\tilde H = \mathcal{U} H^H \mathcal{U}^{-1} = TZ\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right]Z^{-1} T^{-1}~,
+ \end{aligned}\end{equation}
+ where $\mathcal{U} = TZ\mathcal{U}_{A}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation that maps from the original to the reconstructed Hubbard Hamiltonian.
+ The existence of $U$ is contingent on how good the approximations are.
+
+ We mention the two approximations made along the entire journey from the original Hubbard model to the reconstructed one here.
+ \begin{itemize}
+ 	\item We have replaced the full Hubbard model by an auxiliary system described by the SIAM Hamiltonian in eq.~\ref{clus_bath_siam}.
+The accuracy of this assumption is determined by the choice of the SIAM parameters, particular the self-energy and repulsion of the bath.
+As discussed before, the very choice of th cluster and bath spoil the translational invariance of the parent model.
+ 	\item We then perform a unitary RG on $H^A$.
+This leads to a fixed-point Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$.
+At this point, we go from the fixed point Hamiltonian to the dimer+bath Hamiltonian in eq.~\ref{dimer_p_bat}.
+If we represent this transformation from the fixed point Hamiltonian to the Hamiltonian in eq.~\ref{dimer_p_bat} by an operator \(Z\), we can write $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$.
+This constitutes the second approximation we make.
+\end{itemize}
+}
+
+\section{Creating \(N-\)site Hubbard Hamiltonian from Hubbard dimer embedded in a bath}
+Similar to the previous chapter, we will now tile the lattice with the two-site auxiliary model
+\begin{equation}\begin{aligned}
+	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right]\\
+	 -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right) + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
+\end{aligned}\end{equation}
+For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site.
+Note that a uniform number of nearest neighbours means that there is perfect translational invariance on the lattice, which means there cannot be any edge sites.
+This is achieved by applying periodic boundary conditions on the edges of the lattice.
+For example, a square 2d lattice will have to be placed on a 2-torus.
+
+The first step is to identity the two impurity sites \(d_1\) and \(d_2\) and the two bath sites \(0_1\) and \(0_2\) as sitting on a square arrangement of the lattice.
+\(d_i\) form one arm of the square, while \(0_i\) form the opposite arm.
+This square arrangement is shown in fig.~\ref{square-arms}, and is dictated by the auxiliary model chosen and shown in fig.~\ref{two-imp-cluster}.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.3\textwidth]{../figures/square_arms.pdf}
+	\caption{Placing the impurity and bath sites \(d_i,0_i\) on a chosen square of the lattice. The chosen square is marked in blue, the impurity sites in orange and the bath sites in green.}
+	\label{square-arms}
+\end{figure}
+The sites at the vertices of the square are labelled as \(i,j,k,l\). With this identification, the Hamiltonian becomes
+\begin{equation}\begin{aligned}
+	H_\text{aux}(i,j,k,l) = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \frac{U}{2}\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.} + c^\dagger_{j\sigma}c_{l\sigma} + \text{h.c.}\right) + J \vec{S}_{i}\cdot\vec{s}_{k} \right.\\
++ \left.
+J \vec{S}_{j}\cdot\vec{s}_{l} - U_b\left(\hat n_{k \uparrow} - \hat n_{k \downarrow}\right)^2 - U_b\left(\hat n_{l \uparrow} - \hat n_{l \downarrow}\right)^2\right] -t \sum_\sigma \left(c^\dagger_{i,\sigma}c_{j,\sigma} + \text{h.c.}\right) -t \sum_{\left<m,n \right>, \sigma}^{m,n \notin \left\{i,j\right\}}\left(c^\dagger_{m\sigma,n\sigma} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+As before, the kinetic energy part sums over all nearest neighbour pairs that involve neither \(i\) nor \(j\).
+For a given arm \(i-j\), the square can be rotated along the axis \(i-j\) to give one square arrangements for each dimension perpendicular to the axis along \(i-j\).
+Since there are \(w/2\) dimensions, the number of such squares is \(w/2 - 1\).
+For each such square, we can obtain another square by reflecting the square in the plane of \(i-j-l-k-i\) and across the line \(i-j\).
+The total number of squares is therefore \(w - 2\).
+The upshot is that given \(i-j\), there are multiple ways of choosing \(k\); if \(\left\{\vec a\right\}\) represents the set of \(w\) primitive vectors that connect a particular lattice site to its nearest neighbours, \(k\) can be situated at all \(\vec r_i + \vec a\) for which \(\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0\).
+Choosing \(k\) then automatically fixes \(l\) at \(\vec r_j + \vec a\).
+The condition \(\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0\) simply means we only take those \(\vec a\) that are perpendicular to \(\vec r_j - \vec r_i\).
+Since there are \(w\) number of \(\vec a\) in total and 2 of them are parallel, the total number of choices of \(k,l\) is \(w-2\).
+For a 2D lattice, we have \(w=4\), so there are only two possible choices of the square.
+They are shown in fig.~\ref{square-arms-all}.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../figures/square_arms_all.pdf}
+	\caption{Placing the impurity and bath sites \(d_i,0_i\) on a chosen square of the lattice. The chosen square is marked in blue, the impurity sites in orange and the bath sites in green.}
+	\label{square-arms-all}
+\end{figure}
+
+The Hamiltonian for an arm \(i-j\) is then obtained by averaging over these squares:
+\begin{equation}\begin{aligned}
+	H_\text{aux}(i,j) = \frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
+\end{aligned}\end{equation}
+The final step is to sum over all nearest neighbour arms \(i-j\):
+\begin{equation}\begin{aligned}
+	\label{22siam_to_hubb}
+	H_\text{full} = \sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
+\end{aligned}\end{equation}
+
+There are four kinds of terms:
+\begin{itemize}
+	\item the first kind, \(A(i), A(j)\), depend only on either \(i\) or \(j\).
+They can be summed over easily by noting that the internal summation gives a constant factor of \(w-2\) which is canceled by the factor of \(1/(w-2)\) in the front, and the external summation gives \(\sum_{i,j}A(i) = \frac{w}{2} \sum_i A(i)\), because \(i\) is a member of \(w/2\) distinct nearest-neighbour pairs.
+	\item The second kind, \(B(i,j)\) depends on both \(i\) and \(j\).
+The internal summation is again cancelled by the prefactor.
+The external summation simply sums over all nearest-neighbour values of \(A(i,j)\).
+	\item The third kind, \(C(i,k), C(j,l)\), depend on \(i\) and \(k\).
+Here, the total summation \(\sum_{i,j,k}C(i,k)\) gives \((w-2)\sum_{\left<i,k\right>}\left(C(i,k) + C(k,i)\right)\), because the pair \((i,k)\) occurs \(w-2\) times corresponding to the \(w-2\) vectors \(\vec r_j - \vec r_i\) that are perpendicular to \(\vec r_i - \vec r_k\).
+The factor is again cancelled by the existing prefactor.
+	\item The fourth kind, \(D(k), D(l), E(k,l)\), depend on just \(k\), just \(l\) or both \(k\) and \(l\).
+For each pair \(i-j\) in the external summation, the particular pair \(k-l\) appears only once.
+When \(i-j\) is summed over, a factor of \(2(w/2-1)\) is generated because there are that many squares that involve \(k-l\).
+This factor cancels the inverse factor in front, giving \(\sum_{\left<k\right>} D(k), \sum_{\left<k,l \right>}E(k,l)\).
+\end{itemize}
+
+ The full Hamiltonian reads
+\begin{equation}\begin{aligned}
+	H_\text{full} =& w\sum_i\left[- \frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\right] - t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + 4V\sum_{\sigma, \left<i,k\right>}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.}\right)\\
+		      &+ 4J \sum_{\left<i,k\right>}\left(\vec{S}_{i}\cdot\vec{S}_{k}\right) - 2 U_b\sum_k\left(\hat n_{k \uparrow} - \hat n_{k \downarrow}\right)^2 - \frac{Nw/2}{w-2}t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)\\
+	=& -\frac{1}{2}\left(Uw + 4U_b\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{Nw/2}{w-2}t + t - 4V\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 4J \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
+\end{aligned}\end{equation}
+The bulk model hence obtained is again a Hubbard-Heisenberg model.
+In eq.~\ref{2siam_to_hubb}, the total number of terms in the outer summation is \(Nw/2\).
+In order to make sure that this full Hamiltonian scales as \(N\), we divide this by \(w/2\):
+\begin{equation}\begin{aligned}
+	\label{2siam_to_hubb}
+	H_\text{full} &= \frac{2}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) = \frac{2}{w}\sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
+		      &= -\frac{1}{2}\left(2U + 8U_b/w\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{N}{w-2}t + 2t/w - 8V/w\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 8J/w \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
+\end{aligned}\end{equation}
+The mappings between the parameters of the auxiliary model and the bulk are
+\begin{equation}\begin{aligned}
+	t_\text{H-H} = \left(\frac{N}{w-2}t + 2t/w - 8V/w\right),~ ~ ~ U_\text{H-H} = 2U + 8U_b/w,~ ~ ~ J_\text{H-H} = 8J/w
+\end{aligned}\end{equation}
+
+We could have also inserted a spin-exchange interaction between the two impurities in the auxiliary model:
+\begin{equation}\begin{aligned}
+	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right] -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right)\\
+	+ J_d \vec{S}_{d_1}\cdot\vec{S}_{d_2} + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
+\end{aligned}\end{equation}
+In the presence of this term, the bulk Hamiltonian remains the same, but the expression of \(J_\text{H-H}\) changes.
+Since this term is similar in form to the term preceding it, we can easily obtain the updated expression:
+\begin{equation}\begin{aligned}
+	J_\text{H-H} = \frac{2}{w}\left(4J + 2J_d\right)
+\end{aligned}\end{equation}
+
+\section{Single-particle Green's function}
+We now define the Greens function {\it operators}:
+\begin{equation}\begin{aligned}
+	\mathcal{G}_{H-H} = \frac{1}{\omega^\prime - \left(H_{H-H} - E_\text{gs}^\prime\right) }, \mathcal{G}_\text{aux}(i,j) = \frac{1}{\omega - \left(\mathcal{H}_\text{aux}(i,j) - E_\text{gs}\right)}
+\end{aligned}\end{equation}
+Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian, while the primed quantities \(E_\text{gs}^\prime\) and \(\omega^\prime\) are the same quantities but for the full model \(\mathcal{H}_{H-H}\).
+While the auxiliary model is intensive, the full Hamiltonian is extensive and scales as \(N\):
+\begin{equation}\begin{aligned}
+	H_\text{full} &= \frac{2}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) \sim N H_\text{aux}(d_1,d_2)~.
+\end{aligned}\end{equation}
+This means that we must have \(\omega^\prime = N\omega\) and \(E_\text{gs}^\prime = N E_\text{gs}\).
+Rewriting eq.~\ref{2siam_to_hubb} in terms of the operators \(\mathcal{G}\), we get
+\begin{equation}\begin{aligned}
+\sum_{\left<i,j \right>} \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i,j)\right) = N\omega + N E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_{\left<i,j \right>} \mathcal{G}^{-1}_\text{aux}(i,j) = \mathcal{G}^{-1}_{H-H}~,
+\end{aligned}\end{equation}
+We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model.
+Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(\mathcal{H}_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate.
+We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0}
+\end{aligned}\end{equation}
+The superscript \(p\) indicates that this is the particle propagation matrix element.
+Under the auxiliary model approximation, we ignore the virtual entanglement between separate clusters.
+Therefore, the only operators \(\mathcal{G}^{-1}_\text{aux}(k,l)\) that affect the matrix element are those that satisfy \(i \in \left(k,l\right)\).
+There are \(w\) such pairs: \(\left\{k,l\right\} = \left\{i,j\right\} \forall~ j \in \text{NN of i}\).
+Moreover, because of translation invariance, all \(j \in \text{NN of i}\) are equivalent.
+These configurations are shown in fig.~\ref{diag_conrib}.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../figures/diagonal_contributors.pdf}
+	\caption{The various configurations of auxiliary models that contribute to the diagonal matrix element at site \(i\). Orange colour represents impurities and green represents bath sites.}
+	\label{diag_conrib}
+\end{figure}
+
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0} = \frac{2}{w} \times w \times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i, i+1) c^\dagger_{i\sigma} | \Phi_0} = 2\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}
+\end{aligned}\end{equation}
+where we have identified site \(i\) in the auxiliary model as one of the impurities \(d_1\).
+We could very well have chosen \(d_2\) since the model is symmetric in \(d_1,d_2\).
+\(\mathcal{G}^{-1}_\text{aux}(d_1,d_2)\) is the Greens operator corresponding to the Hamiltonian in eq.~\ref{dimer_ham}.
+
+By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}\), we get from the spectral representation
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = 2\sum_{m,n} \braket{\Phi_0 | c_{d_1\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux} \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d_1\sigma} | \Phi_0} = 2\sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+\end{aligned}\end{equation}
+There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(\mathcal{H}_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\).
+We also defined \(d^p_{i,n} = \bra{\Phi_n}c^\dagger_{d_i\sigma}\ket{\Phi_0}\).
+The hole propagation matrix element can be obtained similarly:
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = 2\sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn} 
+\end{aligned}\end{equation}
+where \(d^h_{i,n} = \bra{\Phi_n}c_{d_i\sigma}\ket{\Phi_0}\).
+
+The off-diagonal matrix elements between two nearest-neighbour sites \(i\) and \(i+1\) can also be obtained similarly. Several  auxiliary models can contribute to such a matrix element:
+\begin{itemize}
+	\item those auxiliary models that have \(i\) and \(i+1\) as the two impurities. These give the contribution \\
+		\(\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0}\). 
+	\begin{equation}\begin{aligned}
+		\frac{2}{w}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0} = \frac{2}{w}\sum_{n} \left(d^p_{1,n}\right)^*d^p_{2,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+	\end{aligned}\end{equation}
+	\item those that have \(i\) as an impurity and \(i+1\) as the corresponding bath site. There will be \(w-2\) of these in number:
+	\begin{equation}
+		(w-2) \times \frac{2}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{0_1\sigma} | \Phi_0} = \frac{2}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+	\end{equation}
+		where \(z^p_{i,n} = \braket{\Phi_n | c^\dagger_{0_i,\sigma} | \Phi_0}\).
+	\item those that have \(i+1\) as an impurity site and \(i\) as the corresponding bath site. There are again \(w-2\) of these:
+	\begin{equation}
+		(w-2) \times \frac{2}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{0_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0} = \frac{2}{w}\left(z^p_{1,n}\right)^* d^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+	\end{equation}
+\end{itemize}
+These choices are shown in fig.~\ref{off-diag-contrib}.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../figures/offdiagonal_contributors.pdf}
+	\caption{Auxiliary models that contribute to the off-diagonal matrix element. \(j \equiv i+1\)}
+	\label{off-diag-contrib}
+\end{figure}
+
+Adding all contributions gives
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}
+\end{aligned}\end{equation}
+The hole counterpart is
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}
+\end{aligned}\end{equation}
+where \(z^h_{i,n} = \bra{\Phi_n}c_{z_i\sigma}\ket{\Phi_0}\).
+
+The off-diagonal matrix element between next-to-nearest-neighbour sites \(i,i+2\) can also be obtained, provided their positions are related as \(\vec r_{i+2} = \vec r_i + \vec a + \vec a^\prime\), where \(\vec a\) and \(\vec a^\prime\) are primitive vectors that connect any lattice site to its nearest-neighbours, and \(\vec{a}\cdot\vec{a}^\prime = 0\).
+This is shown in fig.~\ref{next-near}.
+
+\par\noindent
+\begin{minipage}{0.6\textwidth}
+The essence is that the two sites have to form the two most separated vertices of a right-angled triangle.
+To find the auxiliary models that contribute to this matrix element, note that there is only one square that can be formed keeping both \(i\) and \(i+2\) on it - we call this square \(ABCD\), where \(A\) is the vertex \(i\) and \(C\) is the vertex \(i+2\).
+We can set \(A=d_1, C=0_2\).
+The other two vertices \(B\) and \(D\) can have two possible configurations:\(B=d_2,D=0_1\) and \(B=0_1,D=d_2\).
+Two more configurations can be obtained by taking each of these two configurations and keeping \(B,D\) unchanged but exchanging \(A\) and \(C\).
+These four configurations are shown in fig.~\ref{nn-configs}.
+\end{minipage}
+\hspace*{\fill}
+\begin{minipage}{0.35\textwidth}
+	\centering
+	\includegraphics[width=0.9\textwidth]{../figures/next-near.pdf}
+	\captionof{figure}{The kind of next-nearest neighbour sites that can be connected by the auxiliary model.}
+	\label{next-near}
+\end{minipage}
+
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../figures/nn-offdiagonal_contributors.pdf}
+	\caption{Auxiliary model configurations that contribute to the next-nearest neighbour matrix elements. \(j \equiv i+2\)}
+	\label{nn-configs}
+\end{figure}
+
+These four configurations give
+\begin{equation}\begin{aligned}
+	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} &= \frac{2}{w(w-2)}\left[\braket{\Phi_0|c_{d_1\sigma}\mathcal{G}^{-1}_\text{aux}(d_1,d_2)c^\dagger_{0_2,\sigma}|\Phi_0} + \braket{\Phi_0|c_{0_2\sigma}\mathcal{G}^{-1}_\text{aux}(d_1,d_2)c^\dagger_{d_1,\sigma}|\Phi_0}\right] \\
+										 &= \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}
+\end{aligned}\end{equation}
+
+In summary, the spectral representation of the matrix elements of the inverse Greens operators are given by
+\begin{gather}
+\label{green_eq_final_2siam}
+	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
+	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn}~,\\
+	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}~,\\
+	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}~,\\
+	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
+	\left(\mathcal{G}_\text{H-H}^{-1}\left( -\omega \right) \right)^h_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^h_{1,n}\right)^* z^h_{2,n} + \left(z^h_{2,n}\right)^* d^h_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~.
+\end{gather}
+
+In order to obtain the matrix elements of the Greens operators \(\mathcal{G}_{H-H}\) (as compared to its inverse), we note that we have just observed that the matrix elements of the inverse Greens operators are related to the matrix elements of another inverse operator through some coefficients.
+We can, therefore, use the identity
+\begin{equation}\begin{aligned}
+\left(\hat O\right)_{ij} = \bra{i} \hat O \ket{j} = \sum_{m,n} \braket{i|m} \left(\hat O\right)_{mn} \braket{n|j} \implies \left(\hat O^{-1}\right)_{ij} = \sum_{m,n} \braket{i|m} \left(\hat O^{-1}\right)_{mn} \braket{n|j}
+\end{aligned}\end{equation}
+We can now identify \(\left(\hat O^{-1}\right)_{mn}\) as the matrix elements of \(\mathcal{G}_\text{aux}^{-1}\) in our expressions.
+Using the above relation, we can therefore write the spectral representation of the matrix elements of the Greens operators as
+\begin{gather}
+	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~,\\
+	\left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}~,\\
+	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w}\sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn}~,\\
+	\left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w}\sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}~,\\
+	\left(\mathcal{G}_\text{H-H}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~,\\
+	\left(\mathcal{G}_\text{H-H}\left( -\omega \right) \right)^h_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^h_{1,n}\right)^* z^h_{2,n} + \left(z^h_{2,n}\right)^* d^h_{1,n}\right] \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~.
+\end{gather}
+
+The Lehmann-Kallen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements.
+Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
+\begin{equation}\begin{aligned}
+	&\left(G_{H-H}(\omega)\right)_\text{loc} = \left(\mathcal{G}_{H-H}(\omega)\right)_{ii}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn} - |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\right] = G_\text{aux}(d_1,d_1;\omega)\\
+	&\left(G_{H-H}(\omega)\right)_\text{n-n} = \left(\mathcal{G}_{H-H}(\omega)\right)_{i,i+1}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{i+1,i}^h\\
+						&\frac{2}{w}\sum_n \left\{\left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn} - \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}\right\}\\
+						&= \frac{2}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right]\\
+						&\left(G_\text{H-H}\right)_\text{n-n-n} = \frac{2}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right] 
+\end{aligned}\end{equation}
+
+\section{Spectral functions and self-energies}
+
+The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
+\begin{equation}\begin{aligned}
+	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
+\end{aligned}\end{equation}
+where $\vec{r_i}$ is the position vector of a particular lattice site.
+Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites.
+As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
+As we do not have real space Greens function that are more non-local than next-nearest neighbour, we will attempt to obtain momentum space Greens function from these contributions:
+\begin{equation}\begin{aligned}
+	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
+\end{aligned}\end{equation}
+The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, w\right]\right\}$.
+\begin{equation}\begin{aligned}
+	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} + G_{H-H} (\omega)_\text{n-n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {b_i}}= G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k} + G_{H-H} (\omega)_\text{n-n-n} \xi^\prime_{\vec k}
+\end{aligned}\end{equation}
+where we defined \(\left\{b_i\right\} \) as the set of vectors that connect a particular lattice site with its next-nearest-neighbours,\(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\) and \(\xi^\prime_{\vec k} \equiv \sum_{j} e^{i \vec{k}\cdot\vec {b_j}}\).
+Note that \(b_j\) is simply \(a_i + a{i^\prime}\) where \(a_i\) and \(a_{i^\prime}\) are orthogonal.
+On a d-dimensional hypercubic lattice, we obtain
+\begin{gather}
+	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i\\
+\end{gather}
+On a 2D square lattice with lattice spacing $a$, this simplifies to (same as eq.~\ref{2dsquaretb})
+\begin{eqnarray}
+\xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
+\end{eqnarray}
+where \(\epsilon_{\vec{q}} = -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})\) is the tight-binding dispersion.
+\begin{equation}\begin{aligned}
+	G_{H-H} (\vec k, \omega) = G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] \\
+	 + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]
+\end{aligned}\end{equation}
+
+We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
+\begin{equation}\begin{aligned}
+	A_\text{H-H}(\vec{k},\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega)) =A_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[A_\text{aux}(d_1,d_2;\omega) + A_\text{aux}(d_1,0_1;\omega) + A_\text{aux}(0_1,d_1;\omega)\right]\\
+	 + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[A_\text{aux}(d_1,0_2;\omega) + A_\text{aux}(0_2,d_1;\omega)\right]
+\end{aligned}\end{equation}
+where the spectral function $A_\text{aux}=-\frac{1}{\pi}\textrm{Im}G_\text{aux}$.
+
+With the knowledge of the momentum-space Greens function $G_\text{H-H}(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
+\begin{equation}\begin{aligned}
+	\Sigma(\vec k,\omega) = \left(G^{(0)}(\vec k,\omega)\right)^{-1} - G(\vec k,\omega)^{-1}
+\end{aligned}\end{equation}
+where $\left(G^{(0)}(\vec k,\omega)\right)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system.
+Substituting this as well as the full Greens function $G_{H-H}(\vec k, \omega)$ into Dyson's equation gives
+\begin{equation}\begin{aligned}
+	\label{self-energy}
+	&\Sigma_{H-H}(\vec k,\omega) = \left(G^{(0)}(\vec k,\omega)\right)^{-1} -\\
+	&\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}
+\end{aligned}\end{equation}
+This allows us to calculate the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
+
+\section{Analytic consistency check - On the Bethe lattice}
+Another test involves considering the case of a Bethe lattice with infinite number of nearest neighbours $w\to\infty$ (the coordination number).
+In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
+This allows a metal-insulator transition in the limit of $w\to\infty$ as well.
+In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}.
+This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy}.
+Applying the limit of \(w\to \infty\) on that equation gives
+\begin{equation}\begin{aligned}
+	&\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left[G^{(0)}(\vec k,\omega)\right]^{-1} -\right.\\
+	&\left.\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}\right\}\\
+	& = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux}(d_1,d_1;\omega)\right\}^{-1} 
+\end{aligned}\end{equation}
+where \(G_\text{aux}^{(0)}(\vec k,\omega)\) is the non-interacting Greens function.
+It is clear from the final form that only the diagonal term \(G_\text{aux}(d_1,d_1;\omega)\) of the interacting Greens function affects the self-energy.
+Even the non-interacting part Greens function can be shown to be diagonal in the limit of \(w\to\infty\)~\cite{kuramoto_manybody}.
+From its definition in time domain, we have
+\begin{equation}\begin{aligned}
+	G^{(0)}(\vec k, t) = -i\theta(t) \left<\left\{c_{\vec k}(t), c^\dagger_{\vec k}\right\} \right> = -i\theta(t) \left<\left\{e^{i H^{(0)}t} c_{\vec k} e^{-i H^{(0)}t}, c^\dagger_{\vec k}\right\} \right> = -i\theta(t) e^{-i \epsilon_{\vec k}t}\left[ \left<1 - \hat n_{\vec k}\right> + \left<\hat n_{\vec k}\right>\right] = -i \theta(t) e^{-i \epsilon_{\vec k}t}
+\end{aligned}\end{equation}
+A quick Fourier transform to \(\omega-\)domain shows that this is identical to the \(G^{(0)}(\vec k, \omega)\) defined just above eq.~\ref{self-energy}.
+We note that \(|G^{(0)}(\vec k, t)| \leq 1\).
+Using the Fourier transform  definition
+\begin{equation}\begin{aligned}
+	f(\vec k) = \frac{1}{d_N}\sum_{\vec r_i}h(\vec r_i) e^{i \vec{k}\cdot\vec{r}_i}
+\end{aligned}\end{equation}
+where \(d_N\) is a factor that only depends on the total number of sites and not on the coordination number, we can write
+\begin{equation}\begin{aligned}
+	|G^{(0)}(\vec k, t)|^2 = \frac{1}{d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}
+\end{aligned}\end{equation}
+From the inequality \(|G^{(0)}(\vec k, t)| \leq 1\), we get
+\begin{equation}\begin{aligned}
+	1 \geq \frac{1}{N}\sum_k |G^{(0)}(\vec k, t)|^2 = \frac{1}{N d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* \underbrace{\sum_k e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}}_{N \delta_{\vec r_i = \vec r_j}} = \frac{1}{d_N^2}\sum_{\vec r_i} |G^{(0)}(\vec r_i, t)|^2
+\end{aligned}\end{equation}
+For a coordination number of \(w\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
+Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{w}\).
+In contrast, there is only one local Greens function, that for \(\vec r_i=0\).
+The local Greens function therefore scales independent of \(w\).
+This implies that
+\begin{equation}\begin{aligned}
+	\lim_{w\to \infty}G^{(0)}(\vec k,\omega) = G^{(0)}(\vec r=0,\omega)
+\end{aligned}\end{equation}
+Since both the non-interacting and the interaction Greens functions lose their non-locality, the self-energy becomes completely local in the limit of \(w \to \infty\).
+
+\chapter{The Periodic Anderson and Kondo models}
+The heavy Fermion systems are described by periodic versions of the single impurity models, where instead a lattice of impurities \(\left\{ d_i \right\} \) hybridises with a conduction bath lattice \(\left\{ i \right\} \).
+The periodic Anderson model is defined by the Hamiltonian
+\begin{equation}\begin{aligned}
+	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right)  - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma}
+\end{aligned}\end{equation}
+
+As before, we will work with a generalised form of it where we also consider a spin-exchange interaction between the impurity sites and the bath sites:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right) + J \sum_i \vec{S}_{d_i}\cdot\vec{s}_i - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma}
+\end{aligned}\end{equation}
+One can also introduce an RKKY interaction \(J_\text{RKKY}\) between the nearest neighbour impurity spins:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right) + J \sum_i \vec{S}_{d_i}\cdot\vec{s}_i - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma} \\
+	+ J^\prime\sum_{\left<d_i,d_j \right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
+\end{aligned}\end{equation}
+
+\section{Creating a bulk periodic Anderson model by tiling with generalised single-impurity Anderson models: no RKKY}
+
+The auxiliary model we will be using is a generalised SIAM with attractive interaction on the bath zeroth site and explicit particle-hole asymetry on the impurity:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux} = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s}_0 + \eta \sum_\sigma\tau_{d\sigma}
+\end{aligned}\end{equation}
+where \(\tau = \hat n - 1/2\).
+
+We will use this as the auxiliary model to study the Hubbard model.
+We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
+Note that the impurity level and the conduction bath can be tuned to half-filling by setting \(\eta=0\) and \(\mu=0\) respectively.
+To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(d_i\) of the impurity lattice, and the bath sites will constitute the bulk lattice sites.
+We will also identity the zeroth site of the SIAM lattice as one particular site \(i\) of the conduction bath lattice:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux}(d_i) = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) +J \vec{S}_{d_i}\cdot\vec{s}_i + \eta \sum_\sigma\tau_{d_i\sigma}
+\end{aligned}\end{equation}
+Once we have this local Hamiltonian for a particular site, we translate this over all \(N\) sites \(\left\{\left(d_i,i\right) \right\} \):
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{full} = \sum_{i} \mathcal{H}_\text{aux}(d_i) = N\sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) +J \sum_i\vec{S}_{d_i}\cdot\vec{s}_i \\
+	+ \eta \sum_{i,\sigma}\tau_{d_i\sigma}
+\end{aligned}\end{equation}
+
+We end up with a generalised periodic Anderson model:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{GPAM} = \sum_{k\sigma}\left(\left(\epsilon_k\right)_\text{GPAM} - \mu_\text{GPAM}\right)\tau_{k\sigma} - \frac{U_\text{GPAM}}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V_\text{GPAM} \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right)\\
+	+ J_\text{GPAM} \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + \eta_\text{GPAM} \sum_{i,\sigma}\tau_{d_i\sigma}
+\end{aligned}\end{equation}
+The mapping between the parameters of the auxiliary model and that of the bulk are
+\begin{equation}\begin{aligned}
+	\label{map_pam_bulk}
+	\left(\epsilon_k\right)_\text{GPAM} = N\epsilon_k, ~ ~ \mu_\text{GPAM} = N\mu, ~ ~ U_\text{GPAM} = U, ~ ~ V_\text{GPAM} = V, ~ ~ J_\text{GPAM} = J, ~ ~ \eta_\text{GPAM} = \eta
+\end{aligned}\end{equation}
+
+\section{Creating a bulk periodic Anderson model by tiling with two-impurity Anderson models: with RKKY}
+
+This time we will use a two-impurity model with a spin-exchange coupling between the impurities as the auxiliary model:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux} = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\sum_{i=1,2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right)^2 + \sum_{i=1,2}\left[V \sum_{\sigma} \left(c^\dagger_{0_i\sigma} c_{d_i\sigma} + h.c.\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i}\right] + \eta \sum_\sigma\tau_{d\sigma}\\
+ + J^\prime\vec{S}_{d_1}\cdot\vec{S}_{d_2}
+\end{aligned}\end{equation}
+where \(\tau = \hat n - 1/2\).
+
+We will use this as the auxiliary model to study the Hubbard model.
+We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
+Note that the impurity level and the conduction bath can be tuned to half-filling by setting \(\eta=0\) and \(\mu=0\) respectively.
+To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity sites \(d_1 \) and \(d_2\) as particular nearest-neighbour sites \(d_i, d_{j}\) of the impurity lattice, and the bath sites will constitute the bulk lattice sites.
+We will also identity the bath sites \(0_1,0_2\) as two particular nearest-neighbour sites \(i,j\) of the conduction bath lattice:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux}(d_i, d_{j}) = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left[\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + \left(\hat n_{d_{j} \uparrow} - \hat n_{d_{j} \downarrow} \right) ^2\right] + V \sum_{\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + c^\dagger_{j,\sigma} c_{d_{j},\sigma} + h.c.\right)\\
+ + J \left(\vec{S}_{d_i}\cdot\vec{s}_i + \vec{S}_{d_{j}}\cdot\vec{s}_{j}\right) + \eta \sum_\sigma\left(\tau_{d_i\sigma} + \tau_{d_{j}\sigma}\right)+ J^\prime\vec{S}_{d_i}\cdot\vec{S}_{d_j}\\
+\end{aligned}\end{equation}
+Once we have this local Hamiltonian for a particular site, we translate this over all nearest-neighbour pairs \((i,j)\) of the lattice.
+There are \(Nw/2\) of these.
+To ensure the bulk model scales as \(N\), we divide this sum by \(w/2\).
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{full} = \frac{2}{w}\sum_{\left<i,j\right>} \mathcal{H}_\text{aux}(d_i) = N\sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - 2\frac{U}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + 2V \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) \\
+	 + 2J \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + 2\eta \sum_{i,\sigma}\tau_{d_i\sigma} + \frac{2}{w}J^\prime\sum_{\left<i,j\right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
+\end{aligned}\end{equation}
+
+We end up with a generalised periodic Anderson model with RKKY interaction:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{GPAM} = \sum_{k\sigma}\left(\left(\epsilon_k\right)_\text{GPAM} - \mu_\text{GPAM}\right)\tau_{k\sigma} - \frac{U_\text{GPAM}}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V_\text{GPAM} \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right)\\
+	+ J_\text{GPAM} \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + \eta_\text{GPAM} \sum_{i,\sigma}\tau_{d_i\sigma} + J^\prime_\text{GPAM}\sum_{\left<i,j\right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
+\end{aligned}\end{equation}
+The mapping between the parameters of the auxiliary model and that of the bulk are
+\begin{equation}\begin{aligned}
+	\left(\epsilon_k\right)_\text{GPAM} = N\epsilon_k, ~ ~ \mu_\text{GPAM} = N\mu, ~ ~ U_\text{GPAM} = 2U, ~ ~ V_\text{GPAM} = 2V, ~ ~ J_\text{GPAM} = 2J, ~ ~ \eta_\text{GPAM} = 2\eta, ~ ~ J^\prime_\text{GPAM} = \frac{2}{w}J^\prime
+\end{aligned}\end{equation}
+
+\chapter{Future goals}
+\begin{enumerate}
+\item The Mott metal-insulator transition:
+	\begin{itemize}
+	\item Obtain the metal insulator transition of the 2D Hubbard-Heisenberg model on the square lattice from the present formalism. 
+	\item Determine the nature of the bath $\Sigma (k,\omega)$ in the metallic phase, insulating phase as well as at criticality.
+	\item Investigate nature of the zero-temperature transition (order of transition, order parameter, etc)
+	\end{itemize}
+
+\item Higher-order Greens functions:
+	\begin{itemize}
+	\item Provide expressions for two-particle Greens functions.
+	\item Calculate explicitly the Greens functions for holon-doublon and spinon-spinon excitations as they are likely to contain more information regarding the ground state.
+	\item Obtain spectral functions for such excitations
+	\end{itemize}
+
+\item Benchmarking against ED and/or finite size scaling:
+	\begin{itemize}
+	\item ground state energy
+	\item double occupancy
+	\end{itemize}
+
+\item Upgrade to two-site cluster:
+	\begin{itemize}
+	\item Study a two-impurity model under renormalisation group
+	\item Derive the tiling and Greens function relations for such a two-impurity model 
+	\item Demonstrate Mott MIT here.
+	\item Investigate the nature of many-particle entanglement in such a cluster
+	\item look for signs of a quantum liquid.
+	\end{itemize}
+
+\item Once we have a handle on the zero temperature features, we intend to compute Greens functions at non zero temperatures.
+
+\item This method can also be extended to various other models of strong correlation:
+	\begin{enumerate}
+		\item Heisenberg model, by starting from a Kondo model effective Hamiltonian
+		\item Periodic Anderson model, by starting from a SIAM with a dispersive bath
+		\item Periodic Kondo model, by starting from a Kondo model with a dispersive bath
+	\end{enumerate}
+\end{enumerate}
+
+\begin{appendices}
+
+\appendixtitleon
+
+\chapter{Derivation of RG equations for the impurity model with \(U,V,J,K,U_b,\eta\)}
+
+\section{The Hamiltonian}
+
+The Hamiltonian for the impurity problem is
+\begin{equation}\begin{aligned}
+	\mathcal{H} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{1}{2} U \left( \tau_{d \uparrow} - \tau_{d \downarrow} \right) ^2 + \frac{1}{2}\eta \left(\tau_{d \uparrow} + \tau_{d \downarrow}\right) + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} + K \vec{C}_d\cdot\vec{C} - U_b\left(\tau_{0 \uparrow} - \tau_{0 \downarrow}\right)^2
+\end{aligned}\end{equation}
+wher \(\tau \equiv \hat n -\frac{1}{2}\).
+The first term is the kinetic energy term with a dispersion \(\epsilon_k\).
+The second term is the particle-hole symmetric impurity correlation term that sets the uncorrelated half-filled level \(\tau_{d\uparrow} = - \tau_{d \downarrow} = \pm \frac{1}{2}\) at energy \(-U/2\) below the Fermi surface, and the correlated doublon and holon states \(\tau_{d\downarrow} = \tau_{d \uparrow} = \pm \frac{1}{2}\) at the Fermi surface.
+The particle-hole symmetry is in the fact that the term is invariant under \(\tau_{d\sigma} \to-\tau_{d\sigma}\), and manifests in the symmetric positioning of the doublon and holon levels with respect to each other.
+The third term is the particle-hole asymmetry term that explicitly measures the deviation away from particle-hole symmetry - it is non-zero only when we are away from half-filling.
+The fourth, fifth and sixth terms describe various mechanisms in which the impurity can hybridise with the conduction bath.
+The first of these is a single-particle hopping \(V\), the second mechanism is through spin-flip scattering, and the third is through isospin-flip scattering.
+The single-particle hybridisation \(V\) allows the impurity electron to tunnel into the conduction bath and this leads to a frequency-dependent self-energy renormalisation of the impurity, implying that the impurity electron can spend  large amount of time in the bath~\cite{coleman2015}.
+\(\vec S_d = \frac{1}{2}\sum_{\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{d\alpha}c_{d\beta} \) is the impurity spin, while \(\vec C_d = \frac{1}{2}\sum_{\alpha\beta} \psi^\dagger_\alpha \vec \sigma_{\alpha\beta}\psi_\beta\) is the impurity isospin, where \(\psi = \left(c_{d\uparrow} ~ ~ ~ ~ c^\dagger_{d \downarrow}\right)\)~
+\cite{anderson1958random,nambu_1960}.
+The former acts on the \(2-\)dimensional Hilbert-space formed by the magnetic up and down states on the impurity, while the latter acts on the \(2-\)dimensional space formed by the doublon and holon states.
+The former reacts to a magnetic field, while the latter responds to a chemical potential.
+Such a chemical potential term that couples with the isospin is already present in the Hamiltonian - it is the assymetry term \(\eta\).
+In fact, that term can be rewritten as \(\eta C_d^z\), because \(C^z_d = \frac{1}{2}\left(\hat n_{d \uparrow} + \hat n_{d \downarrow} - 1\right) = \frac{1}{2}\left( \tau_{d \uparrow} + \tau_{d \downarrow} \right) \).
+The bath operators \(\vec s\) and \(\vec C\) are defined in the same way as the operator counterparts: \(\vec s = \sum_{kk^\prime\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{k\alpha}c_{k^\prime\beta}, \vec C = \sum_{kk^\prime\alpha\beta}{\psi^k}^\dagger_\alpha\vec\sigma_{\alpha\beta}\psi^{k^\prime}_\beta\), where \(\psi^k = \left(c_{k\alpha} ~ ~ ~ ~ c^\dagger_{k^\prime\beta}\right) \).
+The final seventh term is a local particle-hole symmetric correlation on the zeroth site of the bath.
+For \(U_b>0\), this term promotes half-filling on the zeroth site, while for \(U_b<0\), a doublon or holon is more favourable on that site.
+
+We first Fourier transform the \(U_b\)-term to \(k-\)space.
+In \(k-\)space, the diagonal contribution (to \(H_D\)) coming from this term is the single-particle self-energy \(-U_b\left(\hat n_{q \beta}\right)^2\) which can be made particle-hole symmetric in the form:
+\begin{equation}\begin{aligned}
+	-U_b\left(\tau_{q \beta}\right)^2
+\end{aligned}\end{equation}
+where \(q\) is the \(k-\)state being decoupled and \(\tau \equiv \hat n - 1/2\).
+In the initial state \(\ket{\Psi}_i\), we have \(\langle \hat n_{q\beta} \rangle = 1/2 \implies \tau_{q\beta} = 0\), so the contribution of \(U_b\) to that state is 0.
+For both hole excitations \(c_{q\beta}\ket{\Psi}_i\) as well as particle excitations \(c^\dagger_{q\beta}\ket{\Psi}_i\), the intermediate state energy lowers to \(-U_b/4\).
+
+The off-diagonal part is
+\begin{equation}\begin{aligned}
+	-\frac{U_b}{2}\sum_{kk^\prime\sigma}c^\dagger_{k\sigma}c_{k^\prime\sigma} + U_b \sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_1 \uparrow}c_{k_2 \uparrow} c^\dagger_{k^\prime_1 \downarrow}c_{k^\prime_2 \downarrow}
+\end{aligned}\end{equation}
+We ignore the potential scattering arising from the first term.
+
+\section{Renormalisation of the impurity energy levels}
+A single site has four degrees of freedom arising from the spin-degeneracy, and can be represented by the Hamiltonian
+\begin{equation}\begin{aligned}
+	H = \epsilon_0 \ket{0}\bra{0} + \epsilon_1 \sum_\sigma\ket{\sigma}\bra{\sigma} + \epsilon_2 \ket{2}\bra{2}
+\end{aligned}\end{equation}
+\(\ket{0},\ket{2}\) are the holon and doublon states, while \(\ket{\sigma}\) is the state where the site is singly-occupied by a particle of spin \(\sigma\).
+We will obtain the renormalisation to the energy levels \(\epsilon_0,\epsilon_1\) and \(\epsilon_2\), and thereby calculate the renormalisation in \(U\) and \(\eta\).
+This can be done by noting that \(\epsilon_1 = -\frac{U}{2}\), and \(\epsilon_2 = \eta\).
+A qualifier is, however, needed here.
+In the bare Hamiltonian, the energies of the doublon and holon states are negatives of each other, and this would correspond to requiring \(\epsilon_2 = -\epsilon_0\).
+This may not hold true under renormalisation, and the way we account for this is that at each step of the RG, we subtract a constant energy from the Hamiltonian so as to set the energy of the holon state to 0.
+This means that the energy of the singly-occupied and doublon states become \(\epsilon_1 - \epsilon_0\) and \(\epsilon_2 - \epsilon_0\).
+And since we have identified \(\epsilon_1\) and \(\epsilon_2\) as \(-\frac{U}{2}\) and \(\eta\) respectively, we can use \(\Delta U = -2\left(\Delta \epsilon_1 - \Delta \epsilon_0\right), \Delta \eta = \Delta \epsilon_2 - \Delta \epsilon_0 \).
+
+We need to look at three kinds of scattering vertices here: \(V^2\), \(J^2\) and \(K^2\).
+We will consider these processes one after another.
+We define \(n_j\) as the number of states being decoupled on each side of the Fermi surface, at the \(j^\text{th}\) RG step.
+In order to treat both spin and isospin exchanges democratically, we take \(\ket{\Psi}_i = \frac{1}{2}\left(\ket{0} + \ket{q\uparrow} + \ket{q\downarrow} + \ket{q\uparrow, q\downarrow}\right) \) as the \textit{initial} state for the scattering processes.
+The intermediate states \(\ket{\Psi}_\text{int}\) in the particle sector \(\left(c_{q\beta}\ket{\Psi}_i\right)\) and hole sector \(\left(c^\dagger_{q\beta}\ket{\Psi}_i\right)\) will then have both spin and isospin excitations which can couple with the corresponding impurity degree of freedom.
+We will assume that states  \(q > k_F~\left(\epsilon_q > 0\right) \) above the Fermi surface can have only particle excitations and states below the Fermi surface can only have hole excitations.
+The kinetic energy part \(\epsilon_q \tau_{q\beta}\) of \(H_D\) for \(\ket{\Psi}_i\) is then zero, whereas it is always \(D/2\) for \(\ket{\Psi}_\text{int}\).
+To demonstrate this for a typical \(q < k_F\), the hole excitation is \(c_{q \uparrow}\ket{\Psi}_i = \frac{1}{\sqrt 2}\left(\ket{0} + \ket{q \downarrow}\right)\).
+This has an isospin term in the form of the \textit{holon} and a spin term in the form of the down state.
+Since \(\tau_{q \uparrow} = -\frac{1}{2}\) in the excited state, the kinetic energy for \(\ket{\Psi}_\text{int}\) is \(\epsilon_q \tau_{q \uparrow} = \left(-D\right)\times\left(-\frac{1}{2}\right) = D/2\).
+
+The renormalisation arising from the first kind of terms, in the particle sector, is
+\begin{equation}\begin{aligned}
+	\sum_{q\beta}c^\dagger_{q\beta}c_{d\beta}\frac{V^2}{\omega - H_D}c^\dagger_{d\beta}c_{q\beta} = \sum_{q\beta}V^2 \hat n_{q\beta} \left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega - E_0} + \frac{\hat n_{d \overline\beta}}{\omega^\prime - E_1}\right) = V^2 n_j\sum_{\beta}\left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega_0 - E_0} + \frac{\hat n_{d \overline\beta}}{\omega_1 - E_1}\right)
+\end{aligned}\end{equation}
+\(q\) runs over the momentum states that are being decoupled at this RG step: \(|q| = \Lambda_j\).
+\(E_{1,0}\) are the diagonal parts of the Hamiltonian at \(\hat n_{d\overline \beta}=1,0\) respectively.
+We have \(\hat n_{d\beta}=1\) in the intermediate state because of the \(c^\dagger_{d\beta}\) in front of the Greens function.
+Applying \(c_{q\beta}\) on the initial state \(\ket{\Psi}_i\) leaves us with \(C^z_q = - \frac{1}{2}\) and \(s^z_q = \frac{1}{2}\overline\beta\).
+We also know that
+\begin{equation}\begin{aligned}
+	\hat n_{d\beta}=1,
+	\begin{cases}
+		\hat n_{d\overline\beta}=0 &\implies S_d^z = \frac{1}{2}\beta, C_d^z = 0, \epsilon_d\left(\hat n_{d\uparrow} - \hat n_{d \downarrow}\right)^2 = \epsilon_d\\	
+		\hat n_{d\overline\beta}=1 &\implies S_d^z = 0, C_d^z = \frac{1}{2}, \epsilon_d\left(\hat n_{d\uparrow} - \hat n_{d \downarrow}\right)^2 = 0
+	\end{cases}
+\end{aligned}\end{equation}
+Combining all this, we can write \(E_1 = \frac{D}{2} - \frac{K}{4}\) and \(E_0 = \frac{D}{2} + \epsilon_d - \frac{J}{4}\).
+In order to relate \(\omega_0\) with \(\omega_1\) with the common fluctuation scale \(\omega\) for the conduction electrons, we will replace these quantum fluctuation scales by the current renormalised values of the single-particle self-energy for the initial state from which we started scattering.
+For \(\hat n_{d\overline\beta}=0\), there is no additional self-energy because the impurity does not have any spin: \(\omega_0 = \omega\).
+For \(\hat n_{d\overline\beta} = 1\), we have an additional self-energy of \(\epsilon_d\) arising from the correlation on the impurity: \(\omega_1 = \omega + \epsilon_d\).
+Substituting the values of \(E_{0,1}\) and \(\omega_{0,1}\), we get
+\begin{equation}\begin{aligned}
+	\label{ren_ed_Vp}
+	V^2 n_j\sum_{\beta}\left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)
+\end{aligned}\end{equation}
+Performing a similar calculation for the hole sector gives the contribution:
+\begin{equation}\begin{aligned}
+	\label{ren_ed_Vh}
+	V^2 n_j\sum_{\beta}\hat n_{d\beta}\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right)
+\end{aligned}\end{equation}
+We now come to the second type of terms: spin-spin. We first look at the particle sector:
+\begin{equation}\begin{aligned}
+	\label{ren_ed_Jpp}
+	\frac{J^2}{4}\sum_{q\beta}c^\dagger_{d\overline\beta}c_{d\beta}c^\dagger_{q\beta}c_{-q\overline\beta} \frac{1}{\omega - H_D}c^\dagger_{d\beta}c_{d\overline\beta}c^\dagger_{q\overline\beta}c_{q\beta} = \frac{J^2}{4} n_j\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{\beta}\hat n_{d\overline\beta}\left( 1 - \hat n_{d\beta} \right)
+\end{aligned}\end{equation}
+The diagonal part in the denominator was simple to deduce in this case, because the nature of the scattering requires the spins \(S_d^z\) and \(\frac{\beta}{2}\left(\hat n_{q\beta} - \hat n_{q \overline\beta}\right)\) to be anti-parallel.
+This ensures that the intermediate state has an energy of \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\), and the quantum fluctuation scale is \(\omega^\prime = \omega + \epsilon_d\), such that \(\omega^\prime - E = \omega - \frac{D}{2} + \frac{J}{4}\).
+In the hole sector, we have
+\begin{equation}\begin{aligned}
+	\label{ren_ed_Jph}
+	\frac{J^2}{4} n_j\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{\beta}\hat n_{d\beta}\left( 1 - \hat n_{d\overline\beta} \right)
+\end{aligned}\end{equation}
+The final kind of scattering is the \(K^2\) type. Similar to the \(J^2\) term, we get the following contribution:
+\begin{equation}\begin{aligned}
+	\label{ren_ed_Kpp}
+	\frac{K^2}{4}\sum_{q\beta}c^\dagger_{q\beta}c^\dagger_{q\overline\beta}c_{d\overline\beta}c_{d\beta} \frac{1}{\omega - H_D}c^\dagger_{d\beta}c^\dagger_{d\overline\beta}c_{q\overline\beta}c_{q\beta} = \frac{K^2}{2} n_j\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} \left(1 - \hat n_{d \uparrow}\right) \left( 1 - \hat n_{d \downarrow} \right)
+\end{aligned}\end{equation}
+in the particle sector. This is again because \(E = \frac{D}{2} - \frac{K}{4}\) in the intermediate state and \(\omega^\prime = \omega\). In the hole sector, we get
+\begin{equation}\begin{aligned}
+	\label{ren_ed_Kph}
+	\frac{K^2}{2} n_j\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} \hat n_{d\uparrow}\hat n_{d \downarrow}~.
+\end{aligned}\end{equation}
+
+We now have all possible renormalisation to the impurity energy \(\epsilon_d\).
+To actually compute the renormalisation, we will first calculate the renormalisation in the energies \(\epsilon_0, \epsilon_1\) and \(\epsilon_2\) of the impurity states \(\ket{\hat n_d = 0}, \ket{\hat n_d = 1}, \ket{\hat n_d = 2}\) respectively.
+The renormalisation of these states are given by the following terms:
+\begin{itemize}
+	\item \(\Delta \epsilon_0\) is given by the renormalisation of the term \(\left(1 - \hat n_{d\uparrow}\right)\left(1 - \hat n_{d \downarrow}\right)\)
+	\item \(\Delta \epsilon_1\) is given by the renormalisation of either \(\left(1 - \hat n_{d\uparrow}\right)\hat n_{d \downarrow}\) or \(\left(1 - \hat n_{d\downarrow}\right)\hat n_{d \uparrow}\)
+	\item \(\Delta \epsilon_2\) is given by the renormalisation of \(\hat n_{d\uparrow}\hat n_{d \downarrow}\)
+\end{itemize}
+From eqs.~\ref{ren_ed_Vp}, \ref{ren_ed_Vh}, \ref{ren_ed_Jpp}, \ref{ren_ed_Jph}, \ref{ren_ed_Kpp} and \ref{ren_ed_Kph}, we write
+\begin{equation}\begin{aligned}
+	\Delta \epsilon_0 = \Delta \epsilon_2 = \frac{2V^2 n_j}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}} + \frac{K^2 n_j/2}{\omega - \frac{D}{2} + \frac{K}{4}}, && \Delta \epsilon_1 = \frac{2V^2 n_j}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} + \frac{J^2 n_j/2}{\omega - \frac{D}{2} + \frac{J}{4}}
+\end{aligned}\end{equation}
+We had started with a particle-hole symmetric Hamiltonian \((2\epsilon_d + U = 0)\); the fact that \(\Delta \epsilon_0 = \Delta \epsilon_2\) means the RG transformation has preserved that symmetry.
+The renormalisation of \(\epsilon_d\) is simply the renormalisation in the energy difference between the singly-occupied and vacant impurity levels: \(\Delta \epsilon_d = \Delta \epsilon_1 - \Delta \epsilon_0\).
+This gives our first RG equation:
+\begin{equation}\begin{aligned}
+	\Delta \epsilon_d = 2V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + \frac{n_j}{2}\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right)
+\end{aligned}\end{equation}
+
+\subsection{Renormalisation of the hybridisation \(V\)}
+Renormalisation of \(V\) happens through two kinds of processes: \(VJ\) and \(VK\).
+In order words, the two vertices involve one single-particle scattering and one spin or isospin exchange respectively.
+We first look at the vertices that involve a spin-exchange scattering.
+
+Within spin-exchange, the scattering can be either via \(S_d^z\) or through \(S_d^\pm\). For the first kind, we have the following contribution in the particle sector:
+\begin{equation}\begin{aligned}
+	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{4}J \sum_{k} \left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) c^\dagger_{k\beta}c_{q\beta} = \frac{1}{4}V J n_j \frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right)\sum_{k\beta} \left(1 - \hat n_{d\overline\beta}\right) c_{d\beta}c^\dagger_{k\beta}
+\end{aligned}\end{equation}
+The transformation from \(\frac{1}{\omega - H_D}\) to \(\frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right)\) is made so that we can account for both the initial state and the final state energies through the two fluctuation scales \(\omega^\prime_1\) and \(\omega_2^\prime\) respectively; we calculate the denominators for both the initial and final states, and then take the mean of the two (hence the factor of half in front).
+This was not required previously because in the earlier scattering processes, the impurity returned to its initial state at the end, at least in terms of \(\epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right)^2 \), and so we had \(\omega_1^\prime = \omega_2^\prime = \omega^\prime\).
+
+Note that the \(c_{d\beta}\) in front of the Greens function resulted in \(\left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) \to \left(1 - \hat n_{d\overline\beta}\right)\).
+The intermediate state is characterised by \(\hat n_{d\beta} = 1 - \hat n_{d \overline \beta} = 1\), which means that \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\).
+Moreover, the initial state gives \(\omega_1^\prime = \omega + \epsilon_d\) while the final state gives \(\omega^\prime_2 = \omega\).
+Therefore, the renormalisation becomes
+\begin{equation}\begin{aligned}
+	-\frac{n_j}{4}V J \frac{1}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right)\sum_{k\beta}\left(1 - \hat n_{d\overline\beta}\right) c^\dagger_{k\beta} c_{d\beta}
+\end{aligned}\end{equation}
+One can generate another such process by exchanging the single-particle process and the spin-exchange process:
+\begin{equation}\begin{aligned}
+	\sum_{q\beta} \frac{1}{4}J \sum_{k} \left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) c^\dagger_{q\beta}c_{k\beta} \frac{1}{\omega - H_D} V c^\dagger_{d\beta} c_{q\beta}
+\end{aligned}\end{equation}
+This is simply the Hermitian conjugate of the previous contribution. Combining this with the previous then gives
+\begin{equation}\begin{aligned}
+	-\frac{n_j}{8}V J \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta}\left(1 - \hat n_{d\overline\beta}\right)\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+
+We now consider the spin-exchange processes involving \(S_d^\pm\):
+\begin{equation}\begin{aligned}
+	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{2}J \sum_{k} c^\dagger_{d\beta}c_{d\overline\beta} c^\dagger_{k\overline\beta}c_{q\beta} = \frac{1}{2}V J n_j \frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) c_{d\overline\beta}c^\dagger_{k\overline\beta}
+\end{aligned}\end{equation}
+We again have \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4},\omega_1^\prime = \omega + \epsilon_d\) and \(\omega_2^\prime = \omega\), which gives
+\begin{equation}\begin{aligned}
+	-\frac{1}{4}V J n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)c^\dagger_{k\overline\beta} c_{d\overline\beta}
+\end{aligned}\end{equation}
+Combining this with the Hermitian conjugate obtained from exchanging the processes gives
+\begin{equation}\begin{aligned}
+	-\frac{1}{4}V J n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)\left(c^\dagger_{k\overline\beta} c_{d\overline\beta} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+
+The contributions from the hole sector are obtained making the transformation \(\hat n_{d\overline\beta} \to 1 - \hat n_{d\overline\beta}\) on the particle sector contributions.
+The total renormalisation to \(V\) from \(VJ\) processes are
+\begin{equation}\begin{aligned}
+	-\frac{3n_j}{8}V J \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+
+We now look at the \(VK\) processes. The first one is
+\begin{equation}\begin{aligned}
+	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{4}K \sum_{k} \left(\hat n_{d} - 1\right) c^\dagger_{k\beta}c_{q\beta} = -\frac{1}{8}V K n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \hat n_{d\overline \beta}c^\dagger_{k\beta}c_{d\beta}
+\end{aligned}\end{equation}
+The exchanged process again gives the Hermitian conjugate, so the combined contribution is
+\begin{equation}\begin{aligned}
+	-\frac{1}{8}V K n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \hat n_{d\overline \beta} \left(c^\dagger_{k\beta}c_{d\beta} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+
+The isospin-flip vertex gives
+\begin{equation}\begin{aligned}
+	\sum_{q\beta} V c^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{2}K \sum_{k} c^\dagger_{d\beta}c^\dagger_{d\overline\beta} c_{k\overline\beta} c_{q\beta} = \frac{1}{4}K V n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) c^\dagger_{d\overline\beta}c_{k\overline\beta}~.
+\end{aligned}\end{equation}
+Combining with Hermitian conjugate gives
+\begin{equation}\begin{aligned}
+	\frac{1}{4}K V n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) \left(c^\dagger_{d\overline\beta}c_{k\overline\beta} + \text{h.c.}\right)~.
+\end{aligned}\end{equation}
+
+After obtaining the hole sector contributions, the total renormalisation from \(VK\) processes is
+\begin{equation}\begin{aligned}
+	-\frac{3n_j}{4}V K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)~.
+\end{aligned}\end{equation}
+
+The RG equation for \(V\) is
+\begin{equation}\begin{aligned}
+	\Delta V = -\frac{3n_j V}{8}\left[J\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)\right]
+\end{aligned}\end{equation}
+
+\subsection{Renormalisation of the exchange couplings \(J\) and \(K\)}
+We will just note the renormalisation in \(J^z\), which will be equal to \(J^\pm\) due to spin-rotation symmetry.
+The terms that renormalise \(J^z\) are of the form \(S_d^\pm S_d^\mp\).
+In the particle sector, we have
+\begin{equation}\begin{aligned}
+	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^\pm c^\dagger_{q\mp}c_{k^\prime\pm} \frac{1}{\omega - H_D}S_d^\mp c^\dagger_{k\pm}c_{q\mp} = -n_j \frac{1}{4}J^2 \left(\frac{1}{2} \pm S_d^z\right) \sum_{kk^\prime}c^\dagger_{k \pm}c_{k\pm} \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
+\end{aligned}\end{equation}
+The denominator is determined using \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\) and \(\omega^\prime = \omega + \epsilon_d\).
+In the hole sector, we similarly have
+\begin{equation}\begin{aligned}
+	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^\mp c^\dagger_{k\pm}c_{q\mp} \frac{1}{\omega - H_D}S_d^\pm c^\dagger_{q\mp}c_{k^\prime\pm} = n_j \frac{1}{4}J^2 \left(\frac{1}{2} \mp S_d^z\right) \sum_{kk^\prime}c^\dagger_{k \pm}c_{k\pm} \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
+\end{aligned}\end{equation}
+Adding all four expressions and dropping the constant part, we get
+\begin{equation}\begin{aligned}
+	-n_j \frac{1}{2}J^2 S_d^z \sum_{kk^\prime}\left(c^\dagger_{k \uparrow}c_{k^\prime \uparrow} - c^\dagger_{k \downarrow}c_{k^\prime \downarrow}\right) \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
+\end{aligned}\end{equation}
+We can now directly read off the RG equation for \(J\):
+\begin{equation}\begin{aligned}
+	\Delta J = -\frac{n_j J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
+\end{aligned}\end{equation}
+
+Since the spin and charge degrees of freedom are treated on an equal footing in the model, we obtain the RG equation for \(K\) by simply changing \(J \to K\):
+\begin{equation}\begin{aligned}
+	\Delta K = -\frac{n_j K^2}{\omega - \frac{D}{2} + \frac{K}{4}}
+\end{aligned}\end{equation}
+
+\section{\(U_b\)-included terms}
+
+We first Fourier transform the \(U_b\)-term to \(k-\)space.
+In \(k-\)space, the diagonal contribution (to \(H_D\)) coming from this term is the single-particle self-energy \(-U_b\left(\hat n_{q \beta}\right)^2\) which can be made particle-hole symmetric in the form:
+\begin{equation}\begin{aligned}
+	-U_b\left(\tau_{q \beta}\right)^2
+\end{aligned}\end{equation}
+where \(q\) is the \(k-\)state being decoupled and \(\tau \equiv \hat n - 1/2\).
+In the initial state \(\ket{\Psi}_i\), we have \(\langle \hat n_{q\beta} \rangle = 1/2 \implies \tau_{q\beta} = 0\), so the contribution of \(U_b\) to that state is 0.
+For both hole excitations \(c_{q\beta}\ket{\Psi}_i\) as well as particle excitations \(c^\dagger_{q\beta}\ket{\Psi}_i\), the intermediate state energy lowers to \(-U_b/4\).
+
+The off-diagonal part is
+\begin{equation}\begin{aligned}
+	-\frac{U_b}{2}\sum_{kk^\prime\sigma}c^\dagger_{k\sigma}c_{k^\prime\sigma} + U_b \sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_1 \uparrow}c_{k_2 \uparrow} c^\dagger_{k^\prime_1 \downarrow}c_{k^\prime_2 \downarrow}
+\end{aligned}\end{equation}
+We ignore the potential scattering arising from the first term.
+
+\subsection{Renormalisation of \(U_b\)}
+\(U_b\) can renormalise only via itself. The relevant renormalisation term in the particle sector is
+\begin{equation}\begin{aligned}
+	U_b^2 \sum_{q\beta}\sum_{k_1,k_2,k_3,k_1^\prime,k_2^\prime,k_3^\prime} c^\dagger_{q\beta}c_{k_1\beta}c^\dagger_{k_3\overline\beta}c_{k_1^\prime\overline\beta}\frac{1}{\omega - H_D}c^\dagger_{k_2^\prime\overline\beta}c_{k_3^\prime\overline\beta}c^\dagger_{k_2\beta}c_{q\beta}
+\end{aligned}\end{equation}
+In order to renormalise \(U_b\), we need to contract one more pair of momenta.
+There are two choices.
+The first is by setting \(k_3 = k_3^\prime = q\).
+The two internal states, then, are \(q\beta\) and \(q\overline\beta\).
+As discussed above, the intermediate state energy is \(-U_b/4\).
+We therefore have
+\begin{equation}\begin{aligned}
+	\frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c_{k_1\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2^\prime\overline\beta}c^\dagger_{k_2\beta} = \frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_2^\prime\overline\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
+\end{aligned}\end{equation}
+Another way to contract the momenta is by setting \(k_1^\prime = k_2^\prime = q\), which gives a renormalisation of
+\begin{equation}\begin{aligned}
+	\frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c_{k_1\beta}c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta} = -\frac{U_b^2 n_j}{\omega - D/2}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
+\end{aligned}\end{equation}
+The two contributions cancel each other. The same cancellation happens in the hole sector as well.
+
+\subsection{Renormalisation of \(U\)}
+\(U_b\) does not have any new renormalisation term on account of \(U_b\). \(U_b\) does however modify the existing RG equation for \(U\), by shifting the denominator. The existing RG equation is
+\begin{equation}\begin{aligned}
+	\Delta U &= -4V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) - n_j\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right)~.
+\end{aligned}\end{equation}
+On accounting for the contribution of \(U_b\) to the denominator, we get
+\begin{equation}\begin{aligned}
+	\Delta U &= -4V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} - \epsilon_d + \frac{J}{4}}\right) - n_j\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right)~.
+\end{aligned}\end{equation}
+
+\subsection{Renormalisation of \(V\)}
+The single-particle  hybridisation \(V\) renormalises through terms of \(V U_b\) and \(U_b V\) kind. The first term gives
+\begin{equation}\begin{aligned}
+	&\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{k\beta} \hat n_{q\overline\beta} \frac{1}{\omega - H_D} c^\dagger_{d\beta}c_{q\beta} \\
+	&= n_jU_b V\sum_{k\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_1 - E_1} + \frac{1}{\omega^\prime_1 - E_1}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_0 - E_0} + \frac{1}{\omega_0^\prime - E_0}\right)\right] c^\dagger_{d\beta}
+\end{aligned}\end{equation}
+\(E_1\) and \(E_0\) are the intermediate state energies for \(\hat n_{d\overline\beta}=1\) and 0 respectively.
+\(\omega_{1,0}\) are the quantum fluctuation scales for the corresponding initial states.
+\(\omega^\prime_{1,0}\) are the fluctuation scales for the corresponding final states.
+The intermediate energies are \(E_1 = D/2 - U_b/4 - K/4,~ ~ ~ E_0 = D/2 - U_b/4 - U/2 - J/4\).
+The fluctuation scales are \(\omega_1 = \omega - U/2= \omega_0^\prime,~ ~ ~ \omega_1^\prime = \omega = \omega_0\).
+Substituting these gives
+\begin{equation}\begin{aligned}
+	-n_jU_b V\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
++\left.
+\frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+\end{aligned}\end{equation}
+
+The second term is of the form
+\begin{equation}\begin{aligned}
+	\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{d\beta} \frac{1}{\omega - H_D} \hat n_{q\overline\beta} c^\dagger_{k\beta}c_{q\beta}
+\end{aligned}\end{equation}
+and this is just the Hermitian conjugate of the previous term, so these two terms together lead to
+\begin{equation}\begin{aligned}
+	-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
+	+ \left.\frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+\end{aligned}\end{equation}
+
+In the hole sector, we have
+\begin{equation}\begin{aligned}
+	&\sum_{q\beta}\sum_{k}U_b V \hat n_{q\overline\beta} c^\dagger_{k\beta}c_{q\beta} \frac{1}{\omega - H_D} c^\dagger_{q\beta}c_{d\beta}\\
+	&-\sum_{q\beta}\sum_{k}U_b V \left(1 - \hat n_{q\overline\beta}\right) c^\dagger_{k\beta}c_{q\beta} \frac{1}{\omega - H_D} c^\dagger_{q\beta}c_{d\beta}\\
+	&= -n_jU_b V\sum_{k\beta} c^\dagger_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_1 - E_1} + \frac{1}{\omega^\prime_1 - E_1}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_0 - E_0} + \frac{1}{\omega_0^\prime - E_0}\right)\right] c_{d\beta}
+\end{aligned}\end{equation}
+\(E_1 = D/2 - U_b/4 - U/2 - J/4,~ ~ ~ E_0 = D/2 - U_b/4 - K/4\).
+The fluctuation scales are \(\omega_1 = \omega = \omega_0^\prime,~ ~ ~ \omega_1^\prime = \omega - U/2 = \omega_0\).
+Substituting these gives
+\begin{equation}\begin{aligned}
+	-n_jU_b V\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{1 - \hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
++\left. \frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+\end{aligned}\end{equation}
+The other term, obtained by exchanging \(V\) and \(U_b\), gives the Hermitian conjugate, so the overall contribution from the hole sector is the same as the total contribution from the particle sector, but with \(\hat n_{d\overline\beta} \to 1 - \hat n_{d\overline\beta}\).
+Combining both the sectors, we get
+\begin{equation}\begin{aligned}
+	-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \frac{1}{2}\left[\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
++\left. \left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
+\end{aligned}\end{equation}
+
+Combining with the already existing RG equations, the complete RG equation for \(V\) becomes
+\begin{equation}\begin{aligned}
+	\Delta V =& -\frac{3n_j V}{8}\left[\left(\frac{J}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} + \frac{J}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}}\right) + K \left(\frac{K}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{K}{\omega - \frac{D}{2} + \frac{U_b}{4} - \frac{U}{2} + \frac{K}{4}}\right)\right]\\
+		 &-\frac{n_jU_b}{2}\left[\left(\frac{V}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) + \left(\frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]\\
+		 &=-\frac{n_j V}{8}\left[\left(\frac{3J + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} + \frac{3J + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}}\right) + \left(\frac{3K + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{3K + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} - \frac{U}{2} + \frac{K}{4}}\right)\right]
+\end{aligned}\end{equation}
+
+\subsection{Renormalisation of \(J\) and \(K\)}
+We will track the entire renormalisation purely from that of \(J^+\), by virtue of the SU(2) symmetry. \(J^+\) renormalises through the \(J U_b\) terms. One of the terms is
+\begin{equation}\begin{aligned}
+	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} S_d^+ c^\dagger_{q \downarrow} c_{k \uparrow} \frac{1}{\omega - H_D} \hat n_{q \uparrow} c^\dagger_{k^\prime \downarrow}c_{q \downarrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
+\end{aligned}\end{equation}
+The factor of half in front is the same half factor that appears in front of the \(S_1^+ S_2^-, S_1^-S_2^+\) terms when we rewrite \(\vec{S}_1\cdot\vec{S}_2\) in terms of \(S^z, S^\pm\).
+Another term is obtained by switching \(J\) and \(U_b\):
+\begin{equation}\begin{aligned}
+	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \downarrow} c^\dagger_{q \uparrow} c_{k \uparrow} \frac{1}{\omega - H_D}S_d^+ c^\dagger_{k^\prime \downarrow} c_{q \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
+\end{aligned}\end{equation}
+
+The corresponding terms in the hole sector are
+\begin{equation}\begin{aligned}
+	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{q \uparrow} \frac{1}{\omega - H_D} \hat n_{q \downarrow} c^\dagger_{q \uparrow}c_{k \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \uparrow} c^\dagger_{k^\prime \downarrow} c_{q \downarrow} \frac{1}{\omega - H_D}S_d^+ c^\dagger_{q \downarrow} c_{k \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
+\end{aligned}\end{equation}
+
+Adding all these terms and combining with the existing RG equation, we get the updated RG equation for \(J\):
+\begin{equation}\begin{aligned}
+	\Delta J = -J n_j\frac{4 U_b + J}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}}
+\end{aligned}\end{equation}
+
+We will follow the same strategy with \(K\) - we will calculate the renormalisation in \(K^+\). The first term is
+\begin{equation}\begin{aligned}
+	\frac{1}{2} K U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \downarrow} c^\dagger_{q \uparrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D} C_d^+ c_{k \downarrow} c_{q \uparrow} = -\frac{1}{2}\frac{K U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}} \sum_{k,k^\prime} C_d^+ c_{k \downarrow} c_{k^\prime \uparrow}
+\end{aligned}\end{equation}
+The second term in the same sector is obtained by flipping the spins of \(k\) and \(q\):
+\begin{equation}\begin{aligned}
+	\frac{1}{2} K U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \uparrow} c^\dagger_{q \downarrow}c_{k^\prime \downarrow} \frac{1}{\omega - H_D} C_d^+ c_{q \downarrow} c_{k \uparrow} = -\frac{1}{2}\frac{K U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}} \sum_{k,k^\prime} C_d^+ c_{k \downarrow} c_{k^\prime \uparrow}
+\end{aligned}\end{equation}
+
+The terms in the hole sector give identical contributions. The RG equation for \(K\) is
+\begin{equation}\begin{aligned}
+	\Delta K = -K n_j\frac{4 U_b + K}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}}
+\end{aligned}\end{equation}
+
+\chapter{Zero temperature Greens function in frequency domain}
+
+\label{appx-spectral-func}
+The impurity retarded Green's function (assuming the Hamiltonian to be time-independent, which it is) is defined as
+\begin{equation}\begin{aligned}
+	G_{dd}^\sigma(t) = -i\theta(t) \left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right>
+\end{aligned}\end{equation}
+where the average \(\left< \right>\) is over a canonical ensemble at temperature \(T\), and \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in.
+The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term.
+What follows is a standard calculation where we write the Green's function in the Lehmann-Kallen representation.
+The ensemble average for an arbitrary operator \(\hat M\) can be written in terms of the exact eigenstates of the fixed point Hamiltonian:
+\begin{equation}\begin{aligned}
+	H^* \ket{n} &= E_n^* \ket{n}, ~ ~ ~\left<\hat M \right> &\equiv \frac{1}{Z}\sum_n \bra{n} \hat M \ket{n} e^{-\beta E_n^*}
+\end{aligned}\end{equation}
+where \(Z = \sum_n e^{-\beta E_n^*}\) is the fixed point partition function and \(\left\{ \ket{n} \right\} \) is the set of eigenfunctions of the fixed point Hamiltonian. We can therefore write
+\begin{equation}\begin{aligned}
+	&\left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right> \\
+	&= \frac{1}{Z}\sum_{m}e^{-\beta E_m}\bra{m}\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\} \ket{m}\\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( \mathcal{O}_{\sigma}(t)\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma}(t)\right) \ket{m} && \left[\sum_n \ket{n}\bra{n} = 1\right]  \\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\right) \ket{m}\\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\left( e^{i\left( E_m - E_n \right)  t}\bra{m}\mathcal{O}_{\sigma}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} \ket{m} + e^{i\left( E_n - E_m \right)  t}\bra{m}\mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma} \ket{m}\right)\\
+	&= \frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
+\end{aligned}\end{equation}
+The time-domain impurity Green's function can thus be written as (this is the so-called Lehmann-Kallen representation)
+\begin{equation}\begin{aligned}
+	G_{dd}^\sigma = -i\theta(t)\frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
+\end{aligned}\end{equation}
+We are interested in the frequency domain form.
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega) &= \int_{-\infty}^\infty dt e^{i \omega t}G_{d d}^\sigma(t) \\
+			       &= \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t}
+\end{aligned}\end{equation}
+To evaluate the time-integral, we will use the integral representation of the Heaviside function:
+\begin{equation}\begin{aligned}
+	\theta(t) = \frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty \frac{1}{x- i\eta}e^{ixt}dx
+\end{aligned}\end{equation}
+With this definition, the integral in \(G_{dd}^\sigma(\omega)\) becomes
+\begin{equation}\begin{aligned}
+	\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t} &= \left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta}\int_{-\infty}^\infty dt e^{i\left( \omega + E_m - E_n + x\right)t} \\
+									     &=\left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta} 2\pi \delta\left( \omega + E_m - E_n + x\right) \\
+									     &=\left(-i\right)\frac{1}{i}\lim_{\eta \to 0^+} \frac{-1}{\omega + E_m - E_n- i\eta} \\
+									     &=\frac{1}{\omega + E_m - E_n} \\
+\end{aligned}\end{equation}
+The frequency-domain Green's function is thus
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
+\end{aligned}\end{equation}
+The zero temperature Green's function is obtained by taking the limit of \(\beta \to \infty\).
+In both the partition function as well as inside the summation, the only term that will survive is the exponential of the ground state energy \(E_0\).
+\begin{equation*}\begin{aligned}
+	Z \equiv \sum_m e^{-\beta E_m} \implies \lim_{\beta \to \infty}Z = d_0 e^{-\beta E_0}, && E_0 \equiv \text{min}\left\{ E_n \right\} 
+\end{aligned}\end{equation*}
+where \(d_0\) is the degeneracy of the ground state. The Greens function then simplifies to
+\begin{equation}\begin{aligned}
+	\label{Gf_lk}
+	G_{d d}^\sigma(\omega, \beta \to \infty) &= \frac{1}{d_0e^{-\beta E_0}}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left[e^{-\beta E_m}\delta_{E_m, E_0} + e^{-\beta E_n}\delta_{E_n, E_0}\right]\frac{1}{\omega + E_m - E_n}\\
+						 &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n}\right]\\
+\end{aligned}\end{equation}
+The label 0 sums over all states \(\ket{0}\) with energy \(E_0\).
+The spectral function is the imaginary part of this Green's function.
+To extract the imaginary part, we insert an infinitesimal imaginary part in the denominator:
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega, \eta) = \frac{1}{d_0}\lim_{\eta \to 0^-}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n + i\eta} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n + i\eta}\right]\\
+\end{aligned}\end{equation}
+The spectral function at zero temperature can then be written as
+\begin{equation}\begin{aligned}
+	\mathcal{A(\omega)} &= -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] \\
+			    &= \frac{1}{d_0}\frac{1}{\pi}\text{ Im }\left[\lim_{\eta \to 0^-}\sum_{n,0}\left(\frac{-i\eta ||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2}{\left(\omega + E_0 - E_n\right)^2 + \eta^2} + \frac{-i\eta ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2}{\left(\omega - E_0 + E_n\right)^2 + \eta^2}\right)\right]\\
+			    &= \frac{1}{d_0}\frac{1}{\pi}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\pi\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\pi\delta\left(\omega - E_0 + E_n\right)\right]\\
+			    &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]\\
+\end{aligned}\end{equation}
+
+\chapter{Some analytic results for the Hubbard dimer and the Hubbard model}
+\section{Spectrum of the Hubbard dimer}
+Here we document the spectrum of the Hubbard dimer Hamiltonian in eqs.~\ref{hubb_dimer}.
+\begin{center}
+	\begin{tabular}{|c|c|c|}
+	\hline
+	eigenstate & symbol & eigenvalue \\
+	\hline
+	$\ket{0,0}$ & $\ket{0}$ & \( \frac{U^H}{2}\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,0} \pm \ket{0,\sigma}\right)$ & $\ket{0\sigma_\pm}$ & \(\mp t^H\)\\
+	$\ket{\sigma,\sigma}$ & $\ket{\sigma\sigma}$ & \( -\frac{U^H}{2}\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow}\right)$ & $\ket{ST}$ & \( -\frac{U^H}{2}\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2}\right)$ & $\ket{CS}$ & \( \frac{U^H}{2}\)\\
+	$a_1(U^H, t^H) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_2(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{-}$ & \(-\frac{1}{2}\Delta(U^H, t^H)\)\\
+	$-a_2(U^H, t^H) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{+}$ & \(\frac{1}{2}\Delta(U^H, t^H)\)\\
+	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,2} \pm \ket{2,\sigma}\right)$ & $\ket{2\sigma_\pm}$ & \(\pm t^H\)\\
+	$\ket{2,2}$ & $\ket{4}$ & \( \frac{U^H}{2}\)\\
+\hline
+	\end{tabular}
+	\captionof{table}{Spectrum of Hubbard dimer at half-filling}
+	\label{hubb_dim_spectrum}
+\end{center}
+
+\section{Greens function of Hubbard model in the atomic limit}
+\label{atomic limit}
+The atomic limit is described by the Hamiltonian \(H = -\frac{U}{2}\sum_i\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\).
+Since the Hamiltonian has decoupled into \(\sum_i \equiv N\) single-site Hamiltonians, we can easily write down the retarded Greens function for a single site by identifying the ground state configuration of a site.
+The ground states are of course \(\ket{\Psi}_i = \ket{\uparrow},\ket{\downarrow}\), in the absence of any symmetry-breaking.
+The finite temperature retarded Greens function in the time domain is given by
+\begin{equation}\begin{aligned}
+	G_{i,\sigma}(T,t) = -i\theta(t) \frac{1}{Z}\sum_n e^{-\beta E_n} \braket{n | \left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} | n}
+\end{aligned}\end{equation}
+where \(n\) labels the eigenstates of the \(H\). At \(T \to 0\), only the ground states will survive in the exponential and the partition function \(Z\), such that the formula then reduces to
+\begin{equation}\begin{aligned}
+G_{i,\sigma}(T \to 0,t) = -i\theta(t)\braket{GS | \left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} | GS}
+\end{aligned}\end{equation}
+Since the Hamiltonian is simple, we can compute the time-dependent operator \(c_{i\sigma}(t) = e^{iH t} c_{i\sigma} e^{-iHt}\). Using the BCH lemma, we have
+\begin{equation}\begin{aligned}
+	e^{iH t} c_{i\sigma} e^{-iHt} = \sum_{n=0}^\infty \left(it\right)^n \frac{1}{n!}\left[H,c_{i\sigma}\right]_n
+\end{aligned}\end{equation}
+where \(\left[H,c_{i\sigma}\right]_n = \left[H,\left[H,c_{i\sigma}\right]_{n-1}\right],\left[H,c_{i\sigma}\right]_0=c_{i\sigma}\). The first two non-trivial commutators are
+\begin{equation}\begin{aligned}
+	\left[H, c_{i\sigma}\right]_1 = -U \tau_{i\overline\sigma}c_{i\sigma},~ ~\text{and} ~~\left[H, c_{i\sigma}\right]_2 = \frac{1}{4}U^2 c_{i\sigma}~,
+\end{aligned}\end{equation}
+such that
+\begin{equation}\begin{aligned}
+	e^{iH t} c_{i\sigma} e^{-iHt} =& \left[c_{i\sigma} + \frac{i^2 t^2}{2!}\frac{U^2}{2^2} c_{i\sigma} + \frac{i^4 t^4}{4!}\frac{U^4}{2^4} c_{i\sigma} + \ldots\right] + \left[- \frac{it}{1!}U\tau_{i\overline\sigma}c_{i\sigma} - \frac{i^3 t^3}{3!}\frac{U^3}{4}\tau_{i\overline\sigma}c_{i\sigma} + \ldots \right]\\
+				       &= c_{i\sigma} \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] 
+\end{aligned}\end{equation}
+Using this, we can write
+\begin{equation}\begin{aligned}
+	\left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} = \left\{c_{i\sigma},c^\dagger_{i\sigma}\right\} \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] = \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right]
+\end{aligned}\end{equation}
+and the Greens function becomes
+\begin{equation}\begin{aligned}
+	G_{i,\sigma}(T \to 0,t) = -i\theta(t) \braket{GS | \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] | GS} = -i\theta(t)\left[\cos \frac{Ut}{2} - 2i\sin \frac{Ut}{2} \left<\tau_{i\overline\sigma} \right>\right]
+\end{aligned}\end{equation}
+We now Fourier transform to frequency domain:
+\begin{equation}\begin{aligned}
+	G_{i,\sigma}(\omega) = -i\int_{0}^\infty \mathrm{dt} e^{i\omega t}\left[\cos \frac{Ut}{2} - 2i\sin \frac{Ut}{2} \left<\tau_{i\overline\sigma} \right>\right] = \frac{1 + \left<\tau_{i\overline\sigma }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i\overline\sigma}\right>}{\omega + \frac{U}{2}}
+\end{aligned}\end{equation}
+The spin-total Greens function for the site \(i\) is
+\begin{equation}\begin{aligned}
+	\label{atomic_limit_gf}
+	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 + \left<\tau_{i }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i}\right>}{\omega + \frac{U}{2}}
+\end{aligned}\end{equation}
+At half-filling, we have \(\tau_i = 1\).
+\section{Local Greens function for the Hubbard dimer}
+From the spectral representation, we have the following expression for the local Greens function for the Hubbard dimer at site $0$:
+\begin{equation}\begin{aligned}
+	G_{D,00}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}c_{i\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
+\end{aligned}\end{equation}
+$m,n$ sum over the exact eigenstates.
+$E_m, E_n$ are the corresponding energies.
+We are interested in teh $T \to 0$ Greens function.
+In that limit, all exponentials except that for the ground state $E_{gs}$ will die out.
+The exponential inside the summation will then cancel the exponential in the partition function.
+\begin{equation}\begin{aligned}
+	G_{D,00}^\sigma(\omega, T \to 0) &= \sum_{n}\left[||\bra{GS}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
+					&= \sum_{n}\left[||\bra{n}c^\dagger_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
+\end{aligned}\end{equation}
+
+The ground state $\ket{GS}$ is just the state $\ket{-}$ in the table \ref{hubb_dim_spectrum}. We will choose to look at $\sigma = \uparrow`$. Then,
+\begin{equation}\begin{aligned}
+	c_{1\uparrow}\ket{-} &= \frac{a_1}{\sqrt 2}\ket{0, \downarrow} + \frac{a_2}{\sqrt 2}\ket{\downarrow,0}\\
+	c^\dagger_{1\uparrow}\ket{-} &= -\frac{a_1}{\sqrt 2}\ket{2, \uparrow} + \frac{a_2}{\sqrt 2}\ket{\uparrow,2}\\
+\end{aligned}\end{equation}
+The set of states $\ket{n}$ that give non-zero inner product $\ket{GS}$ are therefore
+\begin{equation}\begin{aligned}
+	\left\{ \ket{n} \right\} &= \ket{0\downarrow_\pm}\\
+	||\bra{n}c_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left(a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \pm 2a_1a_2\right)\\
+	\left\{ E_n \right\} &= \mp t
+\end{aligned}\end{equation}
+for the second inner product, and
+\begin{equation}\begin{aligned}
+	\left\{\ket{n}\right\} &= \ket{2\uparrow_\pm}\\
+	||\bra{n}c^\dagger_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left( a_2 \mp a_1 \right)^2 = \frac{1}{4}\left(1 \mp 2a_1a_2\right)\\
+	\left\{ E_n \right\} &= \pm t
+\end{aligned}\end{equation}
+for the first. The Greens function is therefore
+\begin{equation}\begin{aligned}
+	\label{dimer_local_G}
+	G_{D,00}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(t - \frac{\Delta}{2}\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(t + \frac{\Delta}{2}\right) ^2} = G_{D,00}^\downarrow(\omega, T \to 0)~.
+\end{aligned}\end{equation}
+In the atomic limit $(t=0)$, the Greens function simplifies to
+\begin{equation}\begin{aligned}
+	G_{D,00}^\uparrow(\omega, T \to 0) \bigg\vert_\text{atomic} = \frac{\omega}{\omega^2 - \frac{1}{4}U^2}
+\end{aligned}\end{equation}
+In the atomic limit, the singly-occupied state has zero energy:
+\begin{equation}\begin{aligned}
+	E_1(t=0) = \bra{1,0}\left(U \tau_{0 \uparrow}\tau_{0 \downarrow} + U \tau_{1 \uparrow}\tau_{1 \downarrow}\right) \ket{1,0} = 0
+\end{aligned}\end{equation}
+We can write the atomic limit Greens function in terms of this energy and the self energy:
+\begin{equation}\begin{aligned}
+	G_{D,00}^\uparrow(\omega, T \to 0) \bigg\vert_\text{atomic} = \frac{1}{\omega - E_1(t=0) - \Sigma(t=0)} = \frac{1}{\omega - 0 -\frac{U^2}{4\omega}}
+\end{aligned}\end{equation}
+The self energy in the atomic limit can be read off as 
+\begin{equation}\begin{aligned}
+	\label{dimer_selfenergy}
+\Sigma(t=0) = \frac{U^2}{4\omega}
+\end{aligned}\end{equation}
+The site local spectral function can also be calculated from the local Greens function:
+\begin{eqnarray}
+A(0\uparrow, \omega) &=& - \frac{1}{\pi}\text{Im }G_{D,00}^\uparrow(\omega)\nonumber\\
+			     &=& \left( \frac{1}{4} - \frac{t}{\Delta} \right)\left[\delta(\omega - \frac{1}{2}\Delta - t) + \delta(\omega + \frac{1}{2}\Delta + t)\right]\nonumber\\ 
+			     &&+ \left( \frac{1}{4} + \frac{t}{\Delta} \right) \left[\delta(\omega - \frac{1}{2}\Delta + t) + \delta(\omega + \frac{1}{2}\Delta - t)\right]\\ 
+			     &=& A(0\downarrow, \omega)~.\nonumber
+\end{eqnarray}
+Finally, the inter-site Greens function for the Hubbard dimer is given by
+\begin{equation}
+\label{dimer_intersite_G}
+G_{D,01}^\uparrow(\omega, T \to 0) = \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{t - \frac{\Delta}{2}}{\omega^2 - \left(t - \frac{\Delta}{2}\right)^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{t + \frac{\Delta}{2}}{\omega^2 - \left(t + \frac{\Delta}{2}\right)^2} = G_{D,01}^\downarrow(\omega, T \to 0)~.
+\end{equation}
+Using the diagonal and off-diagonal real space Greens functions, we can now compute the momentum-space Greens functions.
+The two momentum states are $ka = 0, \pi$.
+By Fourier transforming, these two Greens functions can be written as
+\begin{equation}\begin{aligned}
+	\label{Gk0}
+	G(k=0, \sigma) = \sum_r e^{ikr} G(r, \sigma) = G(r=0, \sigma) + G(r=a, \sigma) = \frac{1/2 + 2t/\Delta}{\omega -t + \Delta/2} + \frac{1/2 - 2t/\Delta}{\omega - t - \Delta/2}\\
+	G(k=\pi, \sigma) = \sum_r e^{ikr} G(r, \sigma) = G(r=0, \sigma) - G(r=a, \sigma) = \frac{1/2 + 2t/\Delta}{\omega + t - \Delta/2} + \frac{1/2 - 2t/\Delta}{\omega + t + \Delta/2}\\
+\end{aligned}\end{equation}
+
+\section{Contributions of various excitations to the site local spectral function}
+The site local spectral function is
+\begin{equation}\begin{aligned}
+	A(0\uparrow, \omega) = \left( \frac{1}{4} - \frac{t}{\Delta} \right)\left[\delta(\omega - \frac{\Delta}{2} - t) + \delta(\omega + \frac{\Delta}{2} + t)\right]\nonumber + \left( \frac{1}{4} + \frac{t}{\Delta} \right) \left[\delta(\omega - \frac{\Delta}{2} + t) + \delta(\omega + \frac{\Delta}{2} - t)\right]
+\end{aligned}\end{equation}
+If the eigenstates of the $N=1, S^z = - \frac{1}{2}$ sector are $\ket{1 \pm \downarrow}$ and those of $N=3, S^z = \frac{1}{2}$ sector are $\ket{3 \pm \uparrow}$, this spectral function originates from the expression:
+\begin{equation}\begin{aligned}
+	A(0\uparrow, \omega) =& \braket{1 \downarrow_- | c_{0 \uparrow} | \text{GS}} \delta\left(\omega + \frac{\Delta}{2} + t\right) + \braket{2 \uparrow_+ | c^\dagger_{0 \uparrow} | \text{GS}}\delta\left(\omega - \frac{\Delta}{2} - t\right) \\
+			      &+ \braket{1 \downarrow_+ | c_{0 \uparrow} | \text{GS}}\delta\left(\omega + \frac{\Delta}{2} - t\right) + \braket{2 \uparrow_- | c^\dagger_{0 \uparrow} | \text{GS}}\delta(\omega - \frac{\Delta}{2} + t)
+\end{aligned}\end{equation}
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.9\textwidth]{../figures/dimer-peaks.png}
+	\caption{Position, weight and nature of each of the peaks in the Hubbard dimer site local spectral function}
+\end{figure}
+
+\chapter{Simple results for the Greens functions}
+\section{Relation between single-particle Greens function and the Greens operator $(T=0)$}
+ The single-particle Greens function is defined as the solution of the equation:
+ \begin{equation}\begin{aligned}
+	 \left(i\partial_t - H(\vec r)\right)G(\vec r,\vec r^\prime, t) = \delta(\vec r - \vec r^\prime)
+ \end{aligned}\end{equation}
+ and is given by the expression
+ \begin{equation}\begin{aligned}
+	 G(\vec r,\vec r^\prime, t) = -i \theta(t) \left< \left\{ c(\vec r, t) c^\dagger(\vec r^\prime, 0)\right\} \right>
+ \end{aligned}\end{equation}
+ This solution can be written in the Lehmann-Kallen representation  and at $T=0$ as
+ \begin{equation}\begin{aligned}
+	 G(\vec r \sigma, \vec r^\prime \sigma, \omega) = \sum_{n}\left[\frac{\bra{GS}c({\vec r,\sigma})\ket{n}\bra{n}c^\dagger(\vec r^\prime,\sigma)\ket{GS}}{\omega + E_{GS} - E_n} + \frac{\bra{GS}c^\dagger(\vec r^\prime,\sigma)\ket{n}\bra{n}c({\vec r,\sigma})\ket{GS}}{\omega + E_n - E_{GS}}\right]
+ \end{aligned}\end{equation}
+ The sum is over the exact eigenstates of the Hamiltonian. In what follows, we will represent $\vec r,\sigma \equiv \nu$ and $\vec r^\prime,\sigma \equiv \nu^\prime$.
+ \begin{equation}\begin{aligned}
+	 G(\nu, \nu^\prime, \omega) &= \sum_{n}\left[\frac{\bra{GS}c(\nu)\ket{n}\bra{n}c^\dagger(\nu^\prime)\ket{GS}}{\omega + E_{GS} - E_n} + \frac{\bra{GS}c^\dagger(\nu^\prime)\ket{n}\bra{n}c(\nu)\ket{GS}}{\omega + E_n - E_{GS}}\right]\\
+							&= \bra{GS}c(\nu)\frac{1}{\omega + E_{GS} - H}c^\dagger(\nu^\prime)\ket{GS} + \bra{GS}c^\dagger(\nu^\prime)\frac{1}{\omega + H - E_{GS}}c(\nu)\ket{GS}\\
+ \end{aligned}\end{equation}
+ If we now define a Greens operator
+ \begin{equation}\begin{aligned}
+	 \label{inv_G_func}
+	 \mathcal{G}(\omega, H) = \frac{1}{\omega - (H - E_\text{GS})}
+ \end{aligned}\end{equation}
+ we can write the single-particle Greens function as a sum of the matrix elements of this operator:
+ \begin{equation}\begin{aligned}
+	 \label{G_mat_el}
+	 G(\nu, \nu^\prime, \omega) = \bra{\nu} \mathcal{G}(\omega, H) \ket{\nu^\prime} - \bra{\overline{\nu^\prime}} \mathcal{G}(-\omega, H) \ket{\overline\nu} = \mathcal{G}(\omega, H)_{\nu,\nu^\prime} - \mathcal{G}(-\omega, H)_{\overline{\nu^\prime}, \overline\nu}
+ \end{aligned}\end{equation}
+ where we have defined the states $\ket{\nu} \equiv c^\dagger(\nu)\ket{GS}$ and $\ket{\overline\nu} \equiv c(\nu)\ket{GS}$.
+The two matrix elements can also be represented in their individual spectral representations:
+ \begin{equation}\begin{aligned}
+	 \label{G_mat_spec}
+ 	\mathcal{G}(\omega, H)_{\nu,\nu^\prime} = \sum_{n}\frac{\bra{GS}c(\nu)\ket{n}\bra{n}c^\dagger(\nu^\prime)\ket{GS}}{\omega + E_{GS} - E_n}\\
+	\mathcal{G}(\omega, H)_{\overline{\nu^\prime}, \overline\nu} = \sum_{n}\frac{\bra{GS}c^\dagger(\nu^\prime)\ket{n}\bra{n}c(\nu)\ket{GS}}{\omega + E_\text{GS} - E_n}
+ \end{aligned}\end{equation}
+
+\section{Writing single-particle excitations of ground state in terms of $N=3, S^z = \frac{1}{2}$ eigenstates}
+The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates $\ket{3\pm\uparrow}$ defined in table \ref{hubb_dim_spectrum}.
+\begin{equation}\begin{aligned}
+	\ket{3\pm \uparrow} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{3\pm \uparrow} = \pm t\ket{3\pm \uparrow}
+\end{aligned}\end{equation}
+In terms of these eigenstates, we can write
+\begin{equation}\begin{aligned}
+	c^\dagger_{0\uparrow}\ket{\text{GS}} 
+	&= c^\dagger_{0\uparrow}\left[a_1 \ket{SS} + a_2 \ket{CT}\right] \\
+	&= a_2 \frac{1}{\sqrt 2}\ket{\uparrow,2} - a_1 \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
+	&= \left(x + y\right) \frac{1}{\sqrt 2}\ket{\uparrow,2} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
+	&=x\ket{3+ \uparrow} + y\ket{3- \uparrow}
+\end{aligned}\end{equation}
+where $x + y \equiv a_2$ and $x-y \equiv -a_1$. Similarly, for the other site excitation, we can write
+\begin{equation}\begin{aligned}
+	c^\dagger_{1\uparrow}\ket{\text{GS}} 
+	&= c^\dagger_{1\uparrow}\left[a_1 \ket{SS} + a_2 \ket{CT}\right] \\
+	&= a_2 \frac{1}{\sqrt 2}\ket{2, \uparrow} - a_1 \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
+	&=  \left(x + y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
+	&=x\ket{3+ \uparrow} - y\ket{3- \uparrow}
+\end{aligned}\end{equation}
+Solving for $x$ and $y$ gives
+\begin{equation}\begin{aligned}
+	x = \frac{a_2 - a_1}{2}, && y = \frac{a_2 + a_1}{2}
+\end{aligned}\end{equation}
+Similarly, we can also write the single-hole excitation $c_{0 \uparrow}\ket{GS}$ in terms of the $N=1, S^z = -\frac{1}{2}$ eigenstates, $\ket{1\pm \downarrow}$:
+\begin{equation}\begin{aligned}
+	\ket{1\pm \downarrow} = \frac{1}{\sqrt 2}\left(\ket{\downarrow, 0} \pm \ket{0, \downarrow}\right), && H^D \ket{1\pm \downarrow} = \mp t\ket{1\pm \downarrow}
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	c_{0 \uparrow}\ket{GS} = a_1 \frac{1}{\sqrt 2}\ket{0, \downarrow} + a_2 \frac{1}{\sqrt 2}\ket{\downarrow, 0} = y\ket{1+ \downarrow} + x\ket{1- \downarrow}\\
+	c_{1 \uparrow}\ket{GS} = a_1 \frac{1}{\sqrt 2}\ket{\downarrow, 0} + a_2 \frac{1}{\sqrt 2}\ket{0, \downarrow} = y\ket{1+ \downarrow} - x\ket{1- \downarrow}\\
+\end{aligned}\end{equation}
+
+\section{Matrix elements of $G^{-1}$ between single-particle momentum excitations, for the Hubbard dimer}
+\begin{equation}\begin{aligned}
+	G^{-1} \equiv \omega + E_\text{GS} - H_D
+\end{aligned}\end{equation}
+The particle excitation momentum space kets are $\ket{k_0} = \frac{1}{\sqrt 2}\left(\ket{0} + \ket{1}\right) ,\ket{k_\pi} = \frac{1}{\sqrt 2}\left(\ket{0} - \ket{1}\right)$. Therefore,
+\begin{equation}\begin{aligned}
+	\left(G^{-1}\right)_{k_0 k_0} &= \frac{1}{2}\left(\bra{0} + \bra{1}\right)\left(\omega + E_\text{GS} - H_D\right)\left(\ket{0} + \ket{1}\right)\\
+				      &= \frac{1}{2}\left(2x\bra{+}\right)\left(\omega + E_\text{GS} - H_D\right)\left(2x\ket{+}\right)\\
+				      &= 2x^2\left(\omega + E_\text{GS} - t\right)\\
+\end{aligned}\end{equation}
+At the final step, we used $\braket{+,+} = 1$ and $\braket{+|H_D|+} = t$.
+
+\chapter{Topological interpretation of the Wilson ratio}
+From the Friedel sum rule\cite{langer1961friedel}, we can relate the phase shift \(\delta(0)\) due to scattering (at the Fermi surface) off a local impurity to the number of electrons bound in the potential well produced by that impurity:
+\begin{equation}\begin{aligned}
+\widetilde N = \frac{1}{2\pi i}\text{Tr }\ln S(0) = \int_\Gamma dz\partial_z \frac{1}{2\pi i}\text{Tr }\ln S(0)
+\end{aligned}\end{equation}
+From the optical theorem, we can write
+\begin{equation}\begin{aligned}
+	S = 1 + TG_0 = \frac{G}{G_0} && \left[G = G_0 + G_0 T G_0\right]
+\end{aligned}\end{equation}
+This allows us to write \cite{anirbanurg1}
+\begin{equation}\begin{aligned}
+\widetilde N = \int_\Gamma dz\partial_z \frac{1}{2\pi i}\text{Tr }\ln \frac{G}{G_0}
+\end{aligned}\end{equation}
+Since \(\text{Tr }\ln \hat O = \sum_\lambda \ln O_\lambda = \ln \prod_\lambda O_\lambda = \ln \text{Det} \hat O\), we get
+\begin{equation}\begin{aligned}
+\widetilde N &= \int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln \text{Det } \frac{G}{G_0}\\
+      &= -\int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln \frac{\text{Det } G_0}{\text{Det } G}\\
+      &\equiv -\int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln D\\
+      &= -\int_{\Gamma(D)}\frac{dD}{D}
+\end{aligned}\end{equation}
+From the work of Seki and Yunoki \cite{seki2017topological}, we know that this quantity is essentially the winding number of the curve \(\Gamma(D)\) in the complex plane spanned by the real and imaginary parts of \(D\), and is equal to the change in Luttinger's volume \(V_L\) at \(T=0\).
+\begin{equation}\begin{aligned}
+\widetilde N &= -\int_{\Gamma(D)}\frac{dD}{D} = -\Delta V_L
+\end{aligned}\end{equation}
+The incoming electrons can have \(\sigma = \uparrow,\downarrow\).
+Since the impurity singlet ground state is rotationally invariant, we have \(\delta_\uparrow = \delta_\downarrow = \delta(0)\).
+\begin{equation}\begin{aligned}
+\widetilde N &= \frac{1}{\pi}\sum_\sigma\delta_\sigma(0)\\
+\implies \delta(0) &= \frac{\pi}{2}\widetilde N = -\frac{\pi}{2}\Delta V_L
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+\label{wilson_luttinger}
+R &= 1 + \sin^2 \left(\frac{\pi}{2}\widetilde N\right)\\
+  &= 1 + \sin^2 \left(\frac{\pi}{2}\Delta V_L\right)
+\end{aligned}\end{equation}
+We note that this connection between \(R\) and \(\Delta V_L\) has not been obtained in the existing literature thus far.
+In the unitary limit, \(\delta(0) = \frac{\pi}{2}\), giving \(\Delta V_L = -1 = -\tilde N\) \cite{martin1982fermi} (i.e., one electronic state from the impurity has been absorbed into the Luttinger volume of the conduction bath), such that \(R = 2\) in this limit.
+In this way, we see that a change in the topological quantum number \(\tilde N\) causes the well known renormalisation of the Wilson ratio R from its non-interacting value \((1)\) to the value \((2)\) obtained for the local Fermi liquid \cite{nozieres1974fermi}.
 
@@
 
-\chapter{From the auxiliary model to the bulk - single site approach}
-\label{chap:tile}
-
-\section{Creating \(N-\)site Hubbard Hamiltonian from Anderson impurity embedded in an interacting bath}
-
-Previously, we have worked out the grounstate phases of a single-impurity model with an interacting bath:
-\begin{equation}\begin{aligned}
-	\label{siam_attr}
-	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
-\end{aligned}\end{equation}
-
-We will use this as the auxiliary model to study the Hubbard model.
-We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
-Note that the impurity level is explicitly at half-filling, because the correlation term \(\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is symmetric under a particle-hole transformation \(\hat n_{d\sigma} \to 1 - \hat n_{d\sigma}\).
-Moreover, the conduction bath is also at half-filling, because we have set the chemical potential \(\mu\) to zero.
-These two ensure that the bulk model is also at half-filling.
-At the end of this section, we will also mention how the tiling works out in the presence of a non-zero filling.
-
-To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(i\) of the lattice, and the bath coupled to the impurity as the set of remaining \(N-1\) sites in the lattice.
-We will also identity the zeroth site of the SIAM lattice as one of the nearest neighbours \(j\) of \(i\):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(i,j) = -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n} \left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2
-\end{aligned}\end{equation}
-The tight-binding term sums over all nearest pairs \((m,n)\) that do not involve the site \(i\).
-In general \(i\) will have \(w\) nearest neighbours for a lattice with coordination number \(w\).
-The total local Hamiltonian for the site \(i\) is obtained by averaging over the Hamiltonians \(\mathcal{H}_\text{aux}(i,j)\) for all nearest neighbours \(j\) of \(i\):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(i) &= \frac{1}{w}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{w}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right)  \right.\\
-				  &\left. +J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\\
-				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
-				  &\left.- U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]
-\end{aligned}\end{equation}
-Once we have this local Hamiltonian for a particular site, we translate this over all sites \(i\):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& \sum_i \mathcal{H}_\text{aux}(i) = \sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
-				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\right]\\
-	=& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
-				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j\right]\right]
-\end{aligned}\end{equation}
-In the entire tight-binding term \(\sum_i\sum_{<m,n>,\sigma}^{m \neq i \neq n}\), each pair will appear \(N-2\) times, because that is the total number of sites that do not involve either \(m\) or \(n\).
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - 2t\left(N-2\right)\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{w}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
-				  &+ \left. J \vec{S_i}\cdot\vec{S}_j\right]\\
-				  &=-\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(2t (N-2) - \frac{2V}{w}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{w} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
-\end{aligned}\end{equation}
-We end up with a Hubbard-Heisenberg model:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j
-\end{aligned}\end{equation}
-The mapping between the parameters is
-\begin{equation}\begin{aligned}
-	\label{map_aux_bulk}
-	t_{H-H} = \left(2t (N-2) - \frac{2V}{w}\right),~ ~ U_{H-H} = \left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{w}
-\end{aligned}\end{equation}
-The conclusion is that we can tile Anderson models with interacting baths into a Hubbard-Heisenberg model:
-\begin{equation}\begin{aligned}
-	\label{siam_to_hubb}
-	\sum_i \mathcal{H}_\text{aux}(i) = \mathcal{H}_{H-H}
-\end{aligned}\end{equation}
-
-As mentioned before, no chemical potential \(\mu\) is generated becuase the auxiliary model was at half-filling, both in the impurity as well as in the bath.
-We can change the chemical potential by introducing two terms:
-\begin{equation}\begin{aligned}
-	\eta \sum_\sigma\left(n_{d\sigma} - \frac{1}{2}\right), \mu \sum_{i,\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
-\end{aligned}\end{equation}
-The first term is the particle-hole asymmetry term, and tuning that term moves the impurity away from half-filling.
-The second term is the usual chemical potential in the bath.
-Introducing these terms in the auxiliary model changes the bulk model into:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j + \mu_\text{H-H}\sum_{i\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
-\end{aligned}\end{equation}
-The only change is the generation of the last term. The mappings between the existing parameters and their auxiliary model counterparts remain the same, while \(\mu_\text{H-H}\) is given by
-\begin{equation}\begin{aligned}
-	\mu_\text{H-H} = \eta + \left(N-1\right) \mu
-\end{aligned}\end{equation}
-In the discussion henceforth, we will assume all the models are at half-filling. We will come back to the doped case at a later point in time.
-
-\section{Nature of the wavefunctions}
-In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full wavefunction \(\Psi\) is then obtained by constructing liner combinations of the eigenstates \(\psi_i\) of the local Hamiltonians such that \(\Psi\) satisfies Bloch's theorem: \(\Psi_{\vec k}(\vec r) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r - \vec R_i)\).
-To satisfy Bloch's theorem means to behave in acertain way under a translation operation \(T(\vec R)\) by some lattice distance \(\vec R = \sum_i n_i \vec a_i\):
-\begin{equation}\begin{aligned}
-T(\vec R)\Psi_{\vec k}\left(\vec r\right) = \Psi_{\vec k}(\vec r + \vec R) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r + \vec R - \vec R_i) = e^{i \vec{k}\cdot\vec{R}}\sum_i e^{i \vec{k}\cdot\left(\vec{R}_i - \vec R\right)} \psi_i(\vec r - (\vec R_i - \vec R)) = e^{\vec{k}\cdot\vec{R}}\Psi(\vec r)
-\end{aligned}\end{equation}
-At the end, we used the fact that \(\vec r_i - \vec R\) is just another lattice vector \(\vec R_j\).
-Note that the translation operator has been defined as an operation that simply advances the argument of the wavefunction from \(\vec r\) to \(\vec r + \vec R\).
-An equivalent definition can be given in terms of their action on position eigenkets: \(T(\vec R)\ket{\vec r} = \ket{\vec r - \vec R}\).
-These translation operators share eigenstates with the momentum operator:
-\begin{equation}\begin{aligned}
-	T\left( \vec R \right) \ket{\vec k} = \sum_{\vec r_i} e^{i \vec{k}\cdot\vec{r}_i}T\left( \vec R \right)\ket{\vec r_i} = e^{i \vec{k}\cdot\vec{R}}\sum_{\vec r_i} e^{i \vec{k}\cdot\left(\vec{r}_i - \vec R\right)}\ket{\vec r_i - \vec R} = e^{i \vec{k}\cdot\vec{R}} \ket{\vec k}
-\end{aligned}\end{equation}
-
-The bulk Hamiltonian obtained in eq.~\ref{siam_to_hubb},
-\begin{equation}\begin{aligned}
-	H_\text{H-H}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i} \mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i\right\}\right) \equiv \sum_{\vec R_i} \mathcal{H}_\text{aux}\left(\vec R_i\right)~,
-\end{aligned}\end{equation}
-also enjoys a Bloch's theorem. This is because the tiling procedure restores the translation symmetry of the lattice:
-\begin{equation}\begin{aligned}
-	H_\text{H-H}\left(\left\{\vec r_k + \vec R\right\}\right) =  \sum_{\vec R_i}\mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i + \vec R\right\}\right) = \sum_{\vec R_i} \mathcal{H}_{\text{aux},\tilde i}\left(\left\{\vec r_k - \vec R\right\}\right) = H_\text{H-H}(\left\{\vec r_k\right\})
-\end{aligned}\end{equation}
-There we used the fact that \(\vec r_k + \vec R\) simply translates the auxiliary model defined by the coordinate \(i\) to a new auxiliary model at the modified coordinate \(\tilde i: \vec R_i^\prime = \vec R_i + \vec R\).
-Since this transformation from one auxiliary model to another simply shuffles the group of all auxiliary models, the sum over the group remains the sum, and we recover the same bulk model.
-
-We can use the auxiliary model zero-bandwidth wavefunctions 
-\begin{equation}\begin{aligned}
-\psi^n_\text{aux}\left(\vec r_d - \vec R_i, \vec r_0 - \left(\vec R_i + \vec a\right)  \right) \equiv \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
-\end{aligned}\end{equation}
-with the impurity position \(\vec R_i\) and zeroth site position \(\vec R_i + \vec a\), to construct eigenstates of the bulk Hamiltonian.
-\(\vec R_i\) is a lattice vector, while \(\vec a\) is one of the \(w\) vectors that connect a lattice site with its nearest neighbours.
-This two site wavefunction can be obtained by first studying the full auxiliary model \(\mathcal{H}_\text{aux}\) under a renormalisation group, obtaining a fixed-point Hamiltonian in the IR, obtaining the IR eigenstate and then tracing out all lattice sites except the impurity and the zeroth site from this eigenstate.
-\(n=0\) is the ground state of the auxiliary model, and higher values denote the excited states.
-
-The following un-normalised combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
-\begin{equation}\begin{aligned}
-	\ket{\Psi^n_{\vec k}} = \frac{1}{w \sqrt N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
-\end{aligned}\end{equation}
-where \(N\) is the total number of lattice sites.
-The interpretation is that the set of \(n=0\) states form the lowest band in the spectrum of the lattice.
-Higher values of \(n\) produce the more energetic bands.
-The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\).
-We will actually work only in the lowest band \(n=0\), so we will drop the band index from now on and keep in mind that only the auxiliary model ground states appear in the formulation:
-\begin{equation}\begin{aligned}
-	\label{bloch-states}
-	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
-\end{aligned}\end{equation}
-where \(\lambda_{\ket{\vec k}}\) is a normalisation factor and is defined by \(|\lambda_{\ket{\vec k}}|^2 = |\braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}|^2 \); \(\ket{\vec k}\) is the momentum eigenstate for momentum \(\vec k\), and \(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
-Becuase of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(w\) choices.
-
-It is easy to verify that \(\Psi_{\vec k}\left(\left\{ \vec r_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \(\vec R\):
-\begin{equation}\begin{aligned}
-	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
-\end{aligned}\end{equation}
-In the last equation, we transformed \(\vec R_i \to \vec R_j = \vec R_i - \vec R\).
-Note that the argument \(\vec a\) does not change under a translation of the system, because that vector always represents the difference between the impurity lattice position and its nearest neighbours, irrespective of the absolute position of the impurity.
-
-The wavefunction can be even brought into the familiar Bloch function form:
-\begin{equation}\begin{aligned}
-	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} w N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
-	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
-\end{aligned}\end{equation}
-where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
-This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
-
-It is straightforward to show that these states form an orthonormal basis. We start by writing down the inner product of two distinct such states:
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
-	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
-	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-\end{aligned}\end{equation}
-At this point, we insert a complete basis of momentum eigenkets \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators:
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
-						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-\end{aligned}\end{equation}
-At the last step, we used the summation form of the Kronecker delta function: \(\sum_{\vec R_i}e^{i \vec R_i \left( \vec k - \vec q \right) }\sum_{\vec R_j}e^{i \vec R_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\).
-The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \(\vec a, \vec a^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\ket{\vec k}}\):
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
-\end{aligned}\end{equation}
-This concludes the proof of orthonormality.
-
-To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
-\begin{equation}\begin{aligned}
-	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
-	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}
-\end{aligned}\end{equation}
-To resolve the translation operators, we will now insert the momentum eigenstates \(\ket{\vec k}\) of the full model: \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) in between the operators.
-\begin{equation}\begin{aligned}
-	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 w^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 w^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
-	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}
-\end{aligned}\end{equation}
-The momentum eigenket \(\ket{\vec k}\) can be expressed as a sum over position eigenkets at varying distances from \(\vec R_0\).
-This form allows a systematic method of improving the energy eigenvalue estimate, because the interacting in the impurity model is extremely localised, so the overlap between two auxiliary models decreases rapidly with distance.
-The majority of the contribution will come from the state at \(\vec R_0\), and improvements are then made by considering auxiliary models at further distances.
-
-\section{Single-particle Green's function}
-In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}} = \ket{\Psi^{n=0}_{\vec k=\vec k_0}} = \frac{1}{\lambda_{\ket{\vec k_0}} w N}\sum_{\vec R, \vec a}\ket{\psi_\text{aux}\left( \vec R, \vec a \right)}\) of the bulk Hamiltonian.
-Note that \(\vec k_0\) is simply the Bloch momentum of the ground state.
-To obtain Greens functions, we start by calculating real-space matrix elements of the bulk and auxiliary Hamiltonians.
-The states that we will consider are local excitations on top of the ground state: \(\ket{i} \equiv c^\dagger_{i\sigma}\ket{\Psi_\text{gs} }\).
-\(i\) represents a lattice site.
-Sandwiching eq.~\ref{siam_to_hubb} between \(\ket{i}\) and \(\bra{i}\), we get
-\begin{equation}\begin{aligned}
-	\label{diag_mat_ele_1}
-	\braket{i | H_\text{H-H} | i} = \frac{1}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2}\sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime}} e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi_\text{aux}\left( \vec R_n, \vec a^\prime \right) | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma}  | \psi_\text{aux}\left( \vec R_m, \vec a \right)}
-\end{aligned}\end{equation}
-There are, in general, three auxiliary models in the final expression on the right hand side - one at \(\vec R_n\), one at \(\vec R_m\) and another at \(\vec R_j\).
-In order to rewrite everything in terms of a single auxiliary model at the origin \(\vec R_0\) of the lattice, we will use the translation operators:
-\begin{gather}
-	\ket{\psi_\text{aux}\left( \vec R_m, \vec a \right)} = T\left(\vec R_0 - \vec R_m\right) \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}, ~ \ket{\psi_\text{aux}\left( \vec R_n, \vec a^\prime \right)} = T\left(\vec R_0 - \vec R_n\right) \ket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)}\\
-	\mathcal{H}_\text{aux}\left( \vec R_j \right) = T\left(\vec R_0 - \vec R_j\right) \mathcal{H}_\text{aux}\left( \vec R_0 \right) T^\dagger\left(\vec R_0 - \vec R_j\right)
-\end{gather}
-Substituting these forms into the expression in eq.~\ref{diag_mat_ele_1} gives
-\begin{equation}\begin{aligned}
-	&\braket{i | H_\text{H-H} | i} =\\
-	&\sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma}  T\left( \vec R_0 - \vec R_m \right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}
-\end{aligned}\end{equation}
-We will now absorb some of the translation operators into the creation and annihilation operators \(c_{i\sigma}\) that describe the excitation:
-\begin{equation}\begin{aligned}
-	T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right) &= T^\dagger\left( \vec R_0 - \vec R_n \right) c_{\sigma}\left( \vec R_i \right)  T^\dagger\left(\vec R_j - \vec R_0\right) \\
-												    &= T^\dagger\left( \vec R_0 - \vec R_n \right) T^\dagger \left(\vec R_j - \vec R_0\right) T\left(\vec R_j - \vec R_0\right) c_{\sigma}\left( \vec R_i \right)  T^\dagger\left(\vec R_j - \vec R_0\right)\\
-												    &=T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}
-\end{aligned}\end{equation}
-There, we used \(T^\dagger(\vec R_1) T^\dagger (\vec R_2) = T^\dagger(\vec R_1 + \vec R_2)\). For the creation operator, we similarly get
-\begin{equation}\begin{aligned}
-	T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma} T\left( \vec R_0 - \vec R_m \right) = \left[T^\dagger\left( \vec R_0 - \vec R_m \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\right]^\dagger = c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)
-\end{aligned}\end{equation}
-The operator \(c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\) creates an electron of spin \(\sigma\) at the position \(\vec R_i - \vec R_j + \vec R_0\).
-It will be represented as \(c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\).
-Substituting these forms gives
-\begin{equation}\begin{aligned}
-	&\braket{i | H_\text{H-H} | i} \\
-	&= \sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime\right) | T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}
-\end{aligned}\end{equation}
-To resolve the remaining translation operators, we will now insert the eigenstates \(1 = \sum_{\vec k}\ket{\Psi_{\vec k}}\bra{\Psi_{\vec k}}\) in between the operators.
-\begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = \sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime, \vec k_1, \vec k_2}} \frac{e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | \Psi_{\vec k_2}}\bra{\Psi_{\vec k_2}}T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)\\
-	\ket{\Psi_{\vec k_1}}\braket{\Psi_{\vec k_1} | \psi_\text{aux}\left( \vec R_0, \vec a \right)}
-\end{aligned}\end{equation}
-From Bloch's theorem, we have
-\begin{equation}\begin{aligned}
-T\left(\vec R_j - \vec R_m\right)\ket{\Psi_{\vec k_1}} = e^{i \vec{k}_1\cdot\left(\vec{R}_j - \vec R_m\right)}\ket{\Psi_{\vec k_1}}, ~ ~\bra{\Psi_{\vec k_2}}T^\dagger\left(\vec R_j - \vec R_n\right) = \bra{\Psi_{\vec k_2}}e^{-i \vec{k}_2\cdot\left(\vec{R}_j - \vec R_n\right)}~.
-\end{aligned}\end{equation}
- Substituting this gives
-\begin{equation}\begin{aligned}
-	&\braket{i | H_\text{H-H} | i} =\\
-	& \sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime, \vec k_1, \vec k_2}} \frac{e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right) + i\vec{R}_n\cdot\left(\vec{k}_2 - \vec k\right) + i\vec{R}_m\cdot\left(\vec{k_0} - \vec k_1\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2}  \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | \Psi_{\vec k_2}}\bra{\Psi_{\vec k_2}} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\Psi_{\vec k_1}}\\
-	&\times\braket{\Psi_{\vec k_1} | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-	&= \frac{1}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \sum_{\vec R_j, \vec a, \vec a^\prime \atop{\vec k_1,\vec k_2}} N^2 \delta_{\vec{k_0},\vec k_2} \delta_{\vec{k_0},\vec k_1} \braket{\psi^0_\text{aux}\left( \vec R_0, \vec a^\prime \right) | \Psi_{\vec k}}\bra{\Psi_{\vec k_0}} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\Psi_{\vec k_0}}\braket{\Psi_{\vec k_0} | \psi^0_\text{aux}\left( \vec R_0, \vec a \right)}\\
-	&= \frac{1}{|\lambda_{\ket{\vec k_0}}|^2 w^2} \sum_{\vec a, \vec a^\prime} \braket{\psi^0_\text{aux}\left( \vec R_0, \vec a \right) | \Psi_{\vec k_0}} \braket{\Psi_{\vec k_0} | \psi^0_\text{aux}\left( \vec R_0, \vec a \right)} \sum_{\vec R_j} \bra{\Psi_{\vec k_0}} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\Psi_{\vec k_0}}\\
-	&= \frac{|\lambda_{\ket{\Psi_\text{gs}}}|^2}{|\lambda_{\ket{\vec k_0}}|^2}\sum_{\vec R_j} \bra{\Psi_\text{gs}} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\Psi_\text{gs}}\\
-\end{aligned}\end{equation}
-Since \(\vec R_i + \vec R_0 - \vec R_j\) is a lattice translation vector, summing over \(\vec R_j\) means that \(\vec R_i + \vec R_0 - \vec R_j\) sums over all lattice sites \(\vec R_k\).
-This is equivalent to stating the translation symmetry of the lattice.
-Redefining \(\vec R_j\) to be equal to \(\vec R_k\), we get
-\begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = \frac{|\lambda_{\ket{\Psi_\text{gs}}}|^2}{|\lambda_{\ket{\vec k_0}}|^2}\sum_{\vec R_j} \bra{\Psi_\text{gs}} c_{\vec R_j,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_j,\sigma}\ket{\Psi_\text{gs}}
-\end{aligned}\end{equation}
-This expression can be seen as the sum of effects of creating a single-particle excitation \(c^\dagger_\sigma\) on the ground state \(\ket{\Psi_\text{gs} }\), at increasingly larger distances \(\vec R_j\) from the auxiliary model at \(\vec R_0\).
-The excitation is made to evolve through the auxiliary model \(\mathcal{H}_\text{aux}\left( \vec R_0 \right) \) centred at \(\vec R_0\).
-The excitation is ultimately annihilated and the state returns to the ground state.
-However, since we are describing the excitation of the bulk ground state using an auxiliary model Hamiltonian, we also need to multply this with the fidelity between the full ground state and the auxiliary model ground state.
-That is taken care of by the inner-product in the numerator multiplying the matrix element.
-That inner product can be thought of as an overlap between a separable state and an entangled state - the full Hamiltonian state is obtained by entangling the overlapping auxiliary models, while the single auxiliary model ground state is the separable state in this context.
-The inner product in the numerator then becomes a measure of entanglement of the bulk ground state - the more the overlap with the separable state, the lower the entanglement: \(\varepsilon(\ket{\Psi_\text{gs}}) \equiv 1 - |\braket{\psi^0_\text{aux}\left(\vec R_0\right) | \Psi_\text{gs}}|^2 \).
-The inner product in the denominator is also an entanglement: \(\varepsilon( \ket{\vec k}) = 1 - |\braket{\psi^0_\text{aux}\left(\vec R_0\right) | \ket{\vec k}}|^2\).
-This can be thought of as the entanglement within each auxiliary model ground state, with the momentum eigenstates \(\ket{\vec k}\) acting as the separable states.
-\begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = \frac{1 - \varepsilon\left( \ket{\Psi_\text{gs}}\right)}{1 - \varepsilon\left( \vec k\right)}\sum_{\vec R_j} \bra{\Psi_\text{gs}} c_{\vec R_j,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_j,\sigma}\ket{\Psi_\text{gs}}
-\end{aligned}\end{equation}
-The more is the entanglement content within the groundstate, the lower is the contribution from a single auxiliary model \(\mathcal{H}_\text{aux}\left( \vec R_0 \right)\).
-This makes sense between the contributions will then be distributed across all the auxiliary models.
-On the other hand, when the entanglement is low, any single auxiliary model provides a large contribution, which can be understood from the fact that any single auxiliary model is sufficient to describe the full ground state.
-The numerator, therefore, is maximum in the metal and minimum (zero) in the insulator.
-Similarly, the denominator is minimum in the metal.
-This is because, in the metal, the auxiliary model ground states are delocalised, so the entanglement between multiple \(\vec k\)-states will be lower compared to the insulating phase, where the ground state is completely localised.
-This shows the entire fraction in front is maximum in the metal and minimum (zero) in the insulator.
-
-\clearpage
-As discussed above, the local nature of the auxiliary models (onsite matrix element only on the impurity and non-local matrix element only between impurity and zeroth site) renders all diagonal matrix elements zero, except the one for \(i=j\):
-\begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = \braket{i | \mathcal{H}_\text{aux,i} | i} = \braket{\psi_\text{aux} | c_{i\sigma} e^{-i \vec{k}\cdot\vec{R}_i} \mathcal{H}_\text{aux,i} e^{i \vec{k}\cdot\vec{R}_i} c^\dagger_{i\sigma} | \psi_\text{aux}} = \braket{\psi_\text{aux} | c_{i\sigma} \mathcal{H}_\text{aux,i} c^\dagger_{i\sigma} | \psi_\text{aux}} = \braket{\psi_\text{aux} | c_{d\sigma} \mathcal{H}_\text{aux} c^\dagger_{d\sigma} | \psi_\text{aux}}
-\end{aligned}\end{equation}
-At the last step, we recognised \(i\) as the impurity site and rewrote the expression entirely in terms of a site-independent auxiliary model.
-Similarly, the off-diagonal matrix element between two nearest-neighbour sites \(i,j\) is obtained as
-\begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | j} = \braket{i | \left(\mathcal{H}_\text{aux,i} + \mathcal{H}_\text{aux,j}\right) | j} = \frac{1}{w}\braket{\psi_\text{aux} | c_{i\sigma} e^{-i \vec{k}\cdot\vec{R}_i} \left(\mathcal{H}_\text{aux,i,j} + \mathcal{H}_\text{aux,j,i}\right) e^{i \vec{k}\cdot\vec{R}_j} c^\dagger_{j\sigma} | \psi_\text{aux}} \\
-	= \frac{1}{w}e^{i \vec{k}\cdot\left(\vec{R}_j - \vec{R}_i\right)}\braket{\psi_\text{aux} | \left(c_{d\sigma}\mathcal{H}_\text{aux} c^\dagger_{0\sigma} + c_{0\sigma}\mathcal{H}_\text{aux} c^\dagger_{d\sigma}\right) | \psi_\text{aux}}
-\end{aligned}\end{equation}
-\(\mathcal{H}_\text{aux,i,j}\) is the auxiliary model with \(i\) as the impurity site and \(j\) as the bath zeroth site.
-
-We now define the Greens {\it operators}:
-\begin{equation}\begin{aligned}
-	\mathcal{G}_{H-H} = \frac{1}{\omega - \left(H_{H-H} - E_\text{gs}\right) }, \mathcal{G}_\text{aux}(i) = \frac{1}{\omega - \left(\mathcal{H}_\text{aux}(i) - E_\text{gs}\right)}
-\end{aligned}\end{equation}
-Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian and also of the full model \(\mathcal{H}_{H-H}\).
-Rewriting eq.~\ref{siam_to_hubb} in terms of the operators \(\mathcal{G}\), we get
-\begin{equation}\begin{aligned}
-\sum_i \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i)\right) = \omega + E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_i \mathcal{G}^{-1}_\text{aux}(i) = \mathcal{G}^{-1}_{H-H}~,
-\end{aligned}\end{equation}
-We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model.
-Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(\mathcal{H}_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate.
-We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{w}\sum_j \sum_{k \in \text{NN of j}}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(j,k) c^\dagger_{i\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-The superscript \(p\) indicates that this is the particle propagation matrix element.
-Under the single site approximation, we ignore the hopping between multiple impurity that reside in separate instances of the auxiliary model.
-Therefore, the only operator \(\mathcal{G}^{-1}_\text{aux}(j)\) that affects the matrix element is \(j=i, k \in \text{NN of i}\).
-Moreover, because of translation invariance, all \(k\) are equivalent.
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \frac{1}{w} w\times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i) c^\dagger_{i\sigma} | \Phi_0} = \braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{d\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-where we have identified site \(i\) in the auxiliary model as the impurity.
-By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}(d)\), we get from the spectral representation
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{m,n} \braket{\Phi_0 | c_{d\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux}(d) \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d\sigma} | \Phi_0} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}
-\end{aligned}\end{equation}
-There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(\mathcal{H}_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\).
-We also defined \(d^p_n = \bra{\Phi_n}c^\dagger_{d\sigma}\ket{\Phi_0}\).
-The hole propagation matrix element can be obtained similarly:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn} 
-\end{aligned}\end{equation}
-where \(d^h_n = \bra{\Phi_n}c_{d\sigma}\ket{\Phi_0}\).
-The off-diagonal matrix elements can also be obtained similarly.
-The difference from the diagonal case is that only one out of the \(w\) nearest-neighbour pairs contributes to the matrix element:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{i,i+1} \equiv \braket{\Phi_0 | c_{i,\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{w}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i,i+1) c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{w}\braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{z,\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-Here, we identity \(i+1\) as the bath zero mode \(z\) and \(i\) as the impurity \(d\).
-We again define matrix elements \(z_n^p = \braket{\Phi_n | c^\dagger_{z\sigma} | \Phi_0}, z_n^h = \braket{\Phi_n | c_{z\sigma} | \Phi_0}\).
-Thus, the spectral representation of the matrix element is obtained as
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}
-\end{aligned}\end{equation}
-The hole counterpart is
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}
-\end{aligned}\end{equation}
-In summary, the spectral representation of the matrix elements of the four inverse Greens operators are given by
-\begin{gather}
-\label{green_eq_final_siam}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn}\\
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}
-\end{gather}
-
-In order to obtain the matrix elements of the Greens operators \(\mathcal{G}_{H-H}\) (as compared to its inverse), we note that we have just observed that the matrix elements of the inverse Greens operators are related to the matrix elements of another inverse operator through some coefficients.
-We can, therefore, use the identity
-\begin{equation}\begin{aligned}
-\left(\hat O\right)_{ij} = \bra{i} \hat O \ket{j} = \sum_{m,n} \braket{i|m} \left(\hat O\right)_{mn} \braket{n|j} \implies \left(\hat O^{-1}\right)_{ij} = \sum_{m,n} \braket{i|m} \left(\hat O^{-1}\right)_{mn} \braket{n|j}
-\end{aligned}\end{equation}
-We can now identify \(\left(\hat O^{-1}\right)_{mn}\) as the matrix elements of \(\mathcal{G}_\text{aux}^{-1}\) in our expressions.
-Using the above relation, we can therefore write the spectral representation of the matrix elements of the Greens operators as
-\begin{gather}
-	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\\
-	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}_\text{aux}(d, -\omega) \right)_{nn}
-\end{gather}
-
-The Lehmann-Kallen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements.
-Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
-\begin{equation}\begin{aligned}
-	\label{greens_func_siam}
-	\left(G_{H-H}(\omega)\right)_\text{loc} = \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right] \\
-	= G(\omega)_\text{aux,dd}
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-	\left(G_{H-H}(\omega)\right)_\text{n-n} = \left(G_{H-H}(\omega)\right)_{i,i+1}^p - \left(G_{H-H}(-\omega)\right)_{i+1,i}^h = \frac{1}{w}\sum_n \left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn} \right.\\
- - \left.\left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]= \frac{1}{w}G(\omega)_\text{aux,dz}
-\end{aligned}\end{equation}
-
-\section{Spectral functions and self-energies}
-
-The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
-\end{aligned}\end{equation}
-where $\vec{r_i}$ is the position vector of a particular lattice site.
-Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites.
-As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
-As we do not have real space Greens function that are more non-local than nearest neighbour, we will attempt to obtain momentum space Greens function from these two contributions:
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
-\end{aligned}\end{equation}
-The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, w\right]\right\}$.
-\begin{equation}\begin{aligned}
-	\label{k_Gf_siam}
-	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} = G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k}\\
-			     &= \sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
-\end{aligned}\end{equation}
-where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\). For example, on a d-dimensional hypercubic lattice, we obtain
-\begin{equation}\begin{aligned}
-	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i
-\end{aligned}\end{equation}
-On a 2D square lattice with lattice spacing $a$, this simplifies to
-\begin{eqnarray}
-	\label{2dsquaretb}
-\xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
-\end{eqnarray}
-where \(\epsilon_{\vec{q}} = -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})\) is the tight-binding dispersion.
-
-We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
-\begin{equation}\begin{aligned}
-	A_\text{H-H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega))\\ 
-	&= -\frac{1}{\pi} \textrm{Im}\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\\
-	&= A_\text{aux,dd} + \frac{\xi_{\vec k}}{w} A_\text{aux,dz}
-\end{aligned}\end{equation}
-where 
-\begin{eqnarray}
-G_\text{aux,dd} &=& \sum_n\left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\nonumber\\
-G_\text{aux,dz} &=& \sum_n\left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
-\end{eqnarray}
-and the spectral function $A_\text{aux,dd}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dd}$~,~$A_\text{aux,dz}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dz}$.
-Further,
-\begin{equation}\begin{aligned}
-A_\text{H-H}(\vec{r}=0,\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{r}=0,\omega)) 
-= A_\text{aux,dd}
-\label{main}
-\end{aligned}\end{equation}
-
-From the local Greens function, we can write down the local self-energy using Dyson's equation: \(\Sigma = \left(G^{(0)}\right)^{-1} - G^{-1}\).
-\(G^{(0)}\) is the non-interacting Greens function.
-Here, non-interacting is defined as the absence of \(U,J\) in the bulk model, and hence the absence of \(U,U_b,J\) in the auxiliary model.
-In real space, the local and nearest-neighbour self-energies are therefore
-\begin{equation}\begin{aligned}
-	\left(\Sigma_\text{H-H}(\omega)\right)_\text{loc} = \left(\left(G_{H-H}(\omega)\right)_\text{loc}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_\text{loc}\right)^{-1} = \left(G(\omega)_\text{aux,dd}^{(0)}\right)^{-1} - \frac{1}{w}\left(G(\omega)_\text{aux,dd}\right)^{-1} \\
-	\left(\Sigma_\text{H-H}(\omega)\right)_\text{n-n} = \left(\left(G_{H-H}(\omega)\right)_\text{n-n}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_\text{n-n}\right)^{-1} = \left(G(\omega)_\text{aux,dz}^{(0)}\right)^{-1} - \frac{1}{w}\left(G(\omega)_\text{aux,dz}\right)^{-1}\\
-\end{aligned}\end{equation}
-
-The \(k-\)space self-energy can be similarly obtained from the \(k-\)space Greens functions
-\begin{equation}\begin{aligned}
-	\label{self-energy1}
-	\Sigma_{H-H}(\vec k,\omega) = \left(\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_{\vec k}\right)^{-1} = \frac{1}{G(\omega)_\text{aux,dd}^{(0)} + \frac{\xi_{\vec k}}{w}G(\omega)_\text{aux,dz}^{(0)}} -  \frac{1}{G(\omega)_\text{aux,dd} + \frac{\xi_{\vec k}}{w}G(\omega)_\text{aux,dz}}
-\end{aligned}\end{equation}
-Just to clarify the notation, we reiterate that bulk quantities with a superscript \((0)\) are for the non-interacting Hamiltonian and defined at \(U_\text{H-H}=J_\text{H-H}=0\), while the auxiliary model quantities with that superscript are evaluated in the non-interacting auxiliary model at \(U=J=U_b=0\).
-The non-interacting model is simply a resonant-level model with the impurity level at zero energy.
-Such a model is exactly solvable, and the corresponding Greens functions are given by
-\begin{equation}\begin{aligned}
-	G(\omega + i\eta)_\text{aux,dd}^{(0)} = \frac{1}{\omega + i\left(\Delta + \eta\right)}, ~ ~ ~ G(\omega + i\eta)_\text{aux,dz}^{(0)} = \sum_{\vec k} G(\omega)^{(0)}_{\vec k} V G(\omega + i\eta)_\text{aux,dd}^{(0)}
-\end{aligned}\end{equation}
-where \(\Delta = \pi \rho V^2\) is the hybridisation parameter, assuming a uniform density of states \(\rho\), and \(G(\omega)^{(0)}_{\vec k}\) is the free electron Greens function at momentum \(\vec k\).
-
-\section{Evidence for the Mott MIT}
-Through the URG study of the generalised SIAM with correlation (eq.~\ref{siam_attr}) shown in chapter \ref{siam-attr-chap}, we can conclude the following about that model:
-\begin{itemize}
-	\item For \(U_b > J/4\), the couplings \(J\) and \(V\) become irrelevant while \(U\) is relevant, which means that \textbf{the impurity gets cut off from the bath at low energies}.
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.48\textwidth]{../figures/phase-map-MIT.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/spectral-function.pdf}
-	\caption{{\it Left:} Phase diagram. {\it Right:} Impurity spectral function}
-	\label{spec_func_mit}
-\end{figure}
-
-\item The impurity spectral function \(A_{dd}(\omega)\) and the impurity-bath real space off-diagonal Greens function \(A_{d0}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
-The gap in the diagonal spectral function shows that the impurity site cannot fluctuate through gapless excitations, while the vanishing of the off-diagonal spectral function shows that an electron on the impurity site cannot delocalise out of that site.
-Other measures like mutual information and spin-spin correlations also show a sharp change on crossing that value, demonstrating \textbf{the destruction of the Kondo cloud and the stabilisation of the local moment on the impurity}.
-
-\begin{figure}[!htb]
-\centering
-	\includegraphics[width=0.48\textwidth]{../figures/corrs_gs.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/spin-charge-corr-full.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/mutinfo-d0-01-full.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/doub_occ.pdf}
-\end{figure}
-
-	\item In the context of the auxiliary model, this represents an \textbf{impurity phase transition} from the completely-screened spin-singlet phase to the unscreened local moment phase.
-
-Using the mappings between the auxiliary model parameters and the bulk parameters (eq.~\ref{map_aux_bulk}), one can define a critical value \(r^{*}\) of the ratio \(r = U_{H-H}/J_{H-H}\) at the critical points \(-U_b/J=1/4\) \textit{for a given and fixed value of \(U\)}.
-We will now argue that this critical point describes a metal-insulator transition.
-For \(r < r^{*}\), the well-defined low-\(\omega\) central peak in the impurity spectral function, as well as the large mutual and information correlations, in the ground state, among the members of the Kondo cloud or between the impurity and the zeroth site show that the impurity and the bath are very strongly entangled, and the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) are non-zero at low \(\omega\).
-This means that both the local and the nearest-neighbour Greens functions, that are related to these parameters via eq.~\ref{greens_func_siam}, have poles at low\(-\omega\) and support the propagation of electrons through gapless excitations.
-Since the spectral function is also very simply related to that of the auxiliary model (eq.\eqref{main}), the former also shows the same zero-energy resonance.
-
-On the other side \(r > r^{*}\) of the critical point, we know that the impurity gets decoupled from the bath, such that the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) vanish.
-This is simply the loss of spectral weight at low-\(\omega\) because of the removal of the gapless excitations, and is demonstrated through the impurity spectral function in fig.~\ref{spec_func_mit}.
-This then implies that the bulk Greens functions will also gap out at low energies, and that describes an insulating phase where the electrons get "jammed" in the local states.
-By the same argument as above, the bulk spectral function also sees a gap in this phase when the impurity spectral function is gapped (see eq.\eqref{main}).
-
-Finally, using eqs.\eqref{map_aux_bulk} and the criticality condition $U_{b}^{*}=-\frac{J^{*}}{4}$, we can offer a functional form for the critical value of the parameter $r^{*} = U_{H-H}^{*}/J_{H-H}^{*}$
-\begin{eqnarray}
-r^{*} &=& \frac{U_{H-H}^{*}}{J_{H-H}^{*}} = \frac{w}{4}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)
-\end{eqnarray}
-where $U^{*}$ and $J^{*}$ are the values of the on-site and Kondo couplings of the auxiliary model at the auxiliary model (i.e., the generalised SIAM with a correlated bath) at the transition between the Kondo screened and the local moment phases.
-Parametrising the bath correlation coupling as $U_{b}=-\frac{U}{10}$, we obtain $U^{*}/J^{*}=5/2$, and $r^{*} = 2$ for the 2D square lattice Hubbard-Heisenberg model (with coordination number $w=4$).
-In general, $w=2d$ for the $d$-dimensional hypercubic lattice, and
-$r^{*}_\text{hyperc.} = \frac{d}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)$.
-The growth of $r^{*}$ with $d$ indicates that the MIT is increasingly rendered difficult in a higher dimensional hypercubic lattice, as it is easier for electrons to delocalise and a very large on-site repulsion is needed to overcome this.
-\end{itemize}
-
-\comment{
-\section{\(k-\)space picture of the MIT in terms of the momentum-resolved self-energy \(\Sigma(\vec k,\omega)\)}
-
-From the self-energy expressions obtained above, one can track the self-energy of the lattice model through the metal-insulator transition.
-In fig.~\ref{four-self}, we have provided these plots at specific values of \(U_b/J\) to show how the transition plays out in the Brillouin zone.
-{\it These plots can also be viewed as a video \href{https://abhirup-m.github.io/misc-sigma/}{\underline{here}}.}
-
-\begin{center}
-\begin{tabular}{c|c}
-\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.02500-4.pdf} &
-\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.10310-4.pdf}\\
-\hline
-\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.15735-4.pdf} &
-\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.23594-4.pdf}\\
-\hline
-\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.25000-4.pdf} &
-\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=0.25010-4.pdf}
-\end{tabular}
-\captionof{figure}{Each of the 6 frames shows \(A(\vec k)\) at four values of \(\omega\).
-First 4 are before the transition (\(-U_b/J < 0.25\)), fifth is exactly at the transition \((-U_b/J = 0.25)\) and last one is after the transition (\(-U_b/J > 0.25\)).
-Available as video \href{https://abhirup-m.github.io/misc-sigma/}{\underline{here}}.}
-\label{four-self}
-\end{center}
-
-In each frame, the top left figure represents the self-energy at \(\omega=0\).
-If we track this particular figure across the frames, we find that at small \(-U_b/J\), the self-energy near the Fermi surface was smaller than those near the Brillouin zone edges, indicating the presence of a prominent Fermi liquid.
-As \(U_b\) increases, we find that this distinction of the Fermi surface becomes less-prominent; at the critical point,we see that the self-energy near the Fermi surface self-energy has become more than that near the edges, signalling that the quasiparticle excitations have become scrambled because of the increased correlations in the bath.
-
-If we, on the other hand, track the bottom right figure in each frame (\(\omega = U/2\)), we find that deep in the metallic regime, the self-energy is quite high.
-This is because of the low spectral weight at large \(\omega\).
-As the correlations are increased, we find that  this self-energy decreases, particular in comparison to the values at the Brillouin zone edges.
-This is because of the appearance of the Hubbard side-peaks in the local spectral function
-.
-
-In the insulating phase, we find that the momentum-dependence has vanished (the system is in the perfectly local atomic limit).
-The self-energy at the Hubbard side-bands (bottom right) is high, because the quasiparticle excitations are highly-renormalised and the single-particle picture description is not possible.
-The self-energy inside the gap (other three figures) diverges and the poles of the Greens function have been replaced by zeroes, so we have instead plotted the inverse self-energy.
-
-These plots are available as videos \href{https://abhirup-m.github.io/misc-sigma/}{\underline{here}}.
-}
-
-\section{Some important remarks}
-\subsection{Entanglement as an order parameter for the transition}
-The spectral weights in the diagonal Greens function can be written in terms of a geometric measure of entanglement:
-\begin{equation}\begin{aligned}
-	d_n^p = \braket{\Phi_n | c^\dagger_{d\sigma} | \Phi_0} = \braket{\Phi_n | c^\dagger_{d\sigma} \sum_n \ket{\phi_m} \bra{\phi_m} | \Phi_0}
-\end{aligned}\end{equation}
-where, \(\ket{\phi_m}\) are the eigenstates of the Hamiltonian composed of a two-site system (formed by the impurity site and the zeroth site) in direct product with the rest of the lattice sites.
-The two site system interacts only via a spin-exchange coupling \(J\), and the impurity and bath sites have local correlations \(U\) and \(U_b\) respectively.
-The ground state is the spin-singlet in direct product with the ground state of the tight-binding chain formed by the remaining sites.
-The summation involves inner products of the ground state \(\ket{\Phi_0}\) with the eigenstates \(\ket{\phi_m}\).
-Only two states out of all \(\ket{\phi_m}\) give non-zero overlap - the spin singlet state \(\ket{SS}\) and the charge triplet-zero state \(\ket{CT}\).
-These two non-zero overlaps give rise to non-zero entanglement: \(\varepsilon_\text{SS} = 1 - |\braket{\Phi_0 | SS}|^2, \varepsilon_\text{CT} = 1 - |\braket{\Phi_0 | CT}|^2\).
-The spectral weight becomes
-\begin{equation}\begin{aligned}
-	d_n^p = \bra{\Phi_n} | c^\dagger_{d\sigma} \left(\ket{SS} + \ket{CT} \right) \left(\sqrt{1 - \varepsilon_\text{SS}} + \sqrt{1 - \varepsilon_\text{CT}}\right)
-\end{aligned}\end{equation}
-The total spectral weight can be written as
-\begin{equation}\begin{aligned}
-	|d_n^p|^2 = |\bra{\Phi_n} | c^\dagger_{d\sigma} \left(\ket{SS} + \ket{CT} \right)|^2 \left(2 - \varepsilon_\text{SS} - \varepsilon_\text{CT} + 2\sqrt{1 - \varepsilon_\text{SS}}\sqrt{1 - \varepsilon_\text{CT}}\right)
-\end{aligned}\end{equation}
-Near the metal, the ground state is, to a very good approximation, the state \(\ket{SS}\).
-One can then say that the entanglement \(\varepsilon_\text{SS}\) is poor - the entangled state is very close to the "separable" state.
-The term separable is used here in the sense that the metallic state defines a limit of the system.
-As \(U_b\) increases, \(\varepsilon_\text{SS}\) increases.
-On the other hand, the entanglement with the charge triplet is maximum in the metal, because the ground state does not have much of the charge triplet.
-Towards the MIT, this contribution increases, and the entanglement decreases.
-
-\subsection{Topological nature of the transition}
-As shown in section~\ref{lutt_theorem}, there is a difference in the value of the Luttinger volume between the local moment (LM) and the strong-coupling (SC) fixed points.
-If we define \(\mathcal{N}_L\) as the Luttinger volume with the spin-degeneracy accounted for, we can write
-\begin{equation}\begin{aligned}
-	\label{lutt_change}
-	\mathcal{N}_L^\text{lm} - \mathcal{N}_L^\text{sc} = 1
-\end{aligned}\end{equation}
-where \(\mathcal{N}_L^\text{lm},\mathcal{N}_L^\text{sc}\) are the Luttinger volumes at the local moment and strong-coupling fixed points respectively.
-This equation expresses the fact that the Luttinger volume of the bath increases by \(1\) when the system is tuned from LM to SC, and this happens because the single-particle impurity excitation in the lower-Hubbard at the atomic limit gets transferred to the bath Greens function in the process.
-The quantity which tracks this transfer is therefore \(\mathcal{N}_\text{imp}\), the number of poles minus the number of zeros in the impurity Greens function at and below the Fermi surface:
-\begin{equation}\begin{aligned}
-	\label{imp_count_def}
-	\mathcal{N}_\text{imp} = \begin{cases}
-		1 & \text{ at LM}\\
-		0 & \text{ at SC}
-	\end{cases}\implies \Delta \mathcal{N}_\text{imp} = 1
-\end{aligned}\end{equation}
-The Luttinger volume \(\mathcal{N}_L\) is related to this impurity count by the equation
-\begin{equation}\begin{aligned}
-	\mathcal{N}_L = \mathcal{N} - \mathcal{N}_\text{imp}
-\end{aligned}\end{equation}
-where \(\mathcal{N}\) is the total number of electrons in the system, accounting for the spin degeneracy.
-If we keep this total number fixed (isolated system), the changes in the impurity count and Luttinger volume become constrained:
-\begin{equation}\begin{aligned}
-	\Delta \mathcal{N}_L = - \Delta \mathcal{N}_\text{imp}~.
-\end{aligned}\end{equation}
-Eq.~\ref{imp_count_def} then readily implies eq.~\ref{lutt_change}.
-
-In order to connect this impurity topological change with the bulk model, we write the total number of particles in the bulk system in the following manner:
-\begin{equation}\begin{aligned}
-	\mathcal{N} = \mathcal{N}_\text{loc} + \mathcal{N}_\text{deloc}
-\end{aligned}\end{equation}
-\(\mathcal{N}_\text{loc}\) is the number of real poles minus the number of zeros of the local Greens function.
-\(\mathcal{N}_\text{deloc}\) is the number of real poles minus the number of zeros of the \(k-\)space Greens functions.
-The former (latter) contributes only in the insulating (metallic) phase, because in the metallic (insulating) phase, the local (\(k-\)space) Greens function develop imaginary self-energy and the real poles in these Greens functions get replaced by imaginary poles.
-Together, these two terms accurately count the total number of particles in both these phases.
-These two terms are defined as
-\begin{equation}\begin{aligned}
-	\mathcal{N}_\text{loc} = \sum_i \mathcal{N}_i = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_i(z)\right], ~ ~ ~\mathcal{N}_\text{deloc} = \sum_k \mathcal{N}_k = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_k(z)\right] = \mathcal{N}_L
-\end{aligned}\end{equation}
-\(G_i(z)\) is the local Greens function at site \(i\) of the bulk model, and \(G_k(z)\) is the \(k-\)space Greens function in the bulk model.
-\(N_\text{deloc}\) is just the Luttinger volume \(\mathcal{N}_L\) of the bulk system.
-With this, the total number of particles in the bulk can be expressed as
-\begin{equation}\begin{aligned}
-	\label{bulk_total}
-	\mathcal{N} = \sum_i \mathcal{N}_i + \mathcal{N}_\text{L}
-\end{aligned}\end{equation}
-From eq.~\ref{greens_func_siam}, we know that the bulk local Greens function is equal to that of the auxiliary model, and that gives \(\sum_i \mathcal{N}_i = \mathcal{N}_\text{imp}\sum_i = \mathcal{N} \mathcal{N}_\text{imp}\).
-There we used the fact that for a half-filled system, the total number of sites is equal to the total number of particles in the system.
-Substituting this into eq.~\ref{bulk_total} and again using \(\Delta \mathcal{N} = 0\) gives
-\begin{equation}\begin{aligned}
-	\mathcal{N} = \mathcal{N} \mathcal{N}_\text{imp} + \mathcal{N}_\text{L} \implies \Delta \mathcal{N}_\text{L} = - \mathcal{N} \Delta \mathcal{N}_\text{imp}
-\end{aligned}\end{equation}
-We already know that \(\Delta \mathcal{N}_\text{imp}=1\) across the transition, so we get
-\begin{equation}\begin{aligned}
-	\mathcal{N}_L^\text{metal} - \mathcal{N}_L^\text{insulator} = \mathcal{N}\left(\mathcal{N}_\text{imp}^\text{sc} - \mathcal{N}_\text{imp}^\text{lm}\right) = \mathcal{N}
-\end{aligned}\end{equation}
-The metal-insulator transition is therefore characterised by a change in the topological quantity \(\mathcal{N}_L\).
-The topological nature arises from the fact that it can be expressed in terms of winding numbers related to the corresponding Greens functions.
-\(\mathcal{N}_\text{imp}\), which derives from the impurity Greens function \(G_d\), is related to the winding numbers of the curves \(\text{Det}[G_d^{-1}(\Gamma^<)]\) and \(\text{Det}[G_d^{-1}(\Gamma^0)]\).
-The winding number is simply the number of times this function encircles the origin when traced on the curves \(\Gamma^<\) and \(\Gamma^0\) that enclose all poles inside and on the Fermi surface respectively.
-An example of such a winding number is shown in fig.~\ref{imp_winding}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[scale=0.2]{../figures/luttinger_top_change.png}
-	\caption{The green lines describe the winding number related to the impurity Greens function, while the blue lines do it for the bath.
-At the local moment fixed point \(V=0\), the impurity has a winding number of 1 because the curve encircles the origin once.
-At the strong-coupling fixed point, this winding number becomes zero, indicated by the fact that the curve does not encircle the origin even once.
-The reduction in the winding number on the part of the impurity is directly linked to the increase in the winding number of the bath - it encircles the origin once at the local moment fixed point but twice at strong-coupling.}
-	\label{imp_winding}
-\end{figure}
-
-\subsection{Greens function in the insulating phase: the Hubbard bands and mottness}
-In the insulating state, the cluster becomes a local moment and the bulk system reduces to the atomic limit \(H = -\frac{U}{2}\sum_i\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\).
-The Greens function in this limit is given in Appendix~\ref{atomic limit}.
-From eq.~\ref{atomic_limit_gf}, we have
-\begin{equation}\begin{aligned}
-	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 + \left<\tau_{i }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i}\right>}{\omega + \frac{U}{2}}
-\end{aligned}\end{equation}
-where \(\tau_i = \sum_\sigma \hat n_{i,\sigma} - 1\).
-At half-filling \(\left<\tau_{i}\right>=0\), the low and high-energy poles have equal spectral weights.
-\textit{This is different from the situation in a band insulator, where the valence band has all the spectral weight in the ground state while the conduction band is empty.} On doping holes into the system such that \(\left<\tau_{i}\right> = -x < 0\), spectral weight is transferred from the upper Hubbard band at \(\omega = U/2\) to the lower one at \(\omega = -U/2\):
-
-\begin{equation}\begin{aligned}
-	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 - x}{\omega - \frac{U}{2}} + \frac{1 + x}{\omega + \frac{U}{2}}
-\end{aligned}\end{equation}
-\textit{This transfer of spectral weight across energy scales of the order of \(U\), as well as the lack of poles at zero energies, is referred to as mottness}~\cite{phillips2006mottness}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/hubbard_bands.pdf}
-	\caption{Structure of the Greens function in the atomic limit.
-The two poles at \(\omega = \pm \frac{U}{2}\) form the two Hubbard bands.
-Doping the system leads to transfer of spectral weight between the bands.}
-\end{figure}
-
-\subsection{Nature of propagation: metal vs insulator}
-In the metallic state, the impurity in the auxiliary model hybridises with the bath through both 1-particle and 2-particle interactions.
-For any two auxiliary models differing by the locations \(i_1, i_2\) of the impurity, the baths will always overlap.
-This means that an electron that starts out from the impurity site at \(i_1\) can hop into the bath, and eventually reach \(i_2\) by hopping out of the other bath and into the other impurity.
-Such processes connect all sites of the lattice and \textit{allow spectral flow}.
-
-In the insulating state, each auxiliary model separates into an impurity and a bath that decoupled from each other.
-This means that the impurity cannot hybridise into the bath, and hence cannot tunnel into any other impurity.
-This leads to the atomic limit of the system, where each site develops a local moment configuration because of the repulsive local correlation, but these local moments cannot communicate with each other, either through spin-exchange processes or by breaking into holons and doublons.
-Any attempt at spectral flow fails because the boundaries of the system become disconnected from each other.
-
-A more accurate picture of the insulating and metallic phases can be obtained by working with a more complicated choice of the cluster.
-For instance, instead of a single impurity, one can take two correlated impurities interacting with each other through a single-particle hopping, and this cluster then interacts with the bath through the usual interactions.
-The ground state of such a cluster is actually a quantum liquid, consisting of the entangled spin and charge degrees of freedom.
-In the metallic state, various members of this liquid such as the holons, doublons and the spinons are free to propagate across the system through the baths.
-In the insulating state, it is this cluster that then gets decoupled from the other clusters.
-The composite degrees of freedom are then unable to propagate outside the cluster, and \textit{the holons and the doublons are bound to each other}~\cite{Mott_1949} within the confines of the cluster.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=0.55\textwidth]{../figures/metal_prop.pdf}
-	\caption{Propagation of electrons from one cluster to another through the bath, in the metallic state}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.75\textwidth]{../figures/ins_prop.pdf}
-	\caption{The clusters get isolated from each other in the insulator, because they get decoupled from their baths.}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.85\textwidth]{../figures/ins_prop_cluster.pdf}
-	\caption{Each cluster is a quantum liquid composed of spin \(\left(\uparrow,\downarrow\right) \) and charge \(\left(0,2\right) \) degrees of freedom.
-In the insulating state, these degrees of freedom get bound within the cluster and are unable to propagate outside.}
-\end{figure}
-
-\subsection{Presence of two self-energies under symmetry-breaking}
-The effective Hamiltonian that describes either the metallic or the insulating phase has $\mathrm{SU}(2)$ symmetry in both the spin and charge sectors.
-Since the repulsive correlation on the impurity picks out the spin sector, we focus on that for now.
-Applying a small magnetic field on the impurity breaks this spin-rotation symmetry and picks out either the up or the down state on the impurity, leading to two kinds of self-energies, one for each spin state~\cite{logan_2014,Logan_2015}.
-The Hamiltonian has the form \(H(h)_i = -\frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - h\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)\).
-The unique groundstate is \(\ket{\hat n_{i,\sigma = \text{sgn}(h)}=1,\hat n_{i,\sigma = -\text{sgn}(h)}=0}\), with an energy of \(E_\text{gs} = -\frac{U}{2} - h\).
-The Greens function is easiest to obtain from the Lehmann-Kallen representation (eq.~\ref{Gf_lk}):
-\begin{equation}\begin{aligned}
-	G_{i,\sigma} = \sum_{n}\left[||\bra{\text{GS}}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_\text{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{\text{GS}}||^2\frac{1}{\omega - E_\text{GS} + E_n}\right]\\
-\end{aligned}\end{equation}
-We have \(c_{i,\sigma}\ket{\text{GS}} = \ket{\hat n_i = 0}\delta_{\sigma,\text{sgn}(h)}\) and \(c^\dagger_{i,\sigma}\ket{\text{GS}} = \ket{\hat n_i = 2}\delta_{\sigma,-\text{sgn}(h)}\), so that the only excited states that give non-zero inner product is \(\ket{n}=\ket{\hat n_i = 0}\) for the second term and \(\ket{n}=\ket{\hat n_i=2}\) for the first term, with energies \(E_n=0\).
-Substituting these, we get
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(h) = \frac{\delta_{\sigma,-\text{sgn}(h)}}{\omega - \frac{U}{2} - h} + \frac{\delta_{\sigma,\text{sgn}(h)}}{\omega + \frac{U}{2} + h} = \frac{1}{\omega + \left(\frac{U}{2}+h\right)\sigma \times \text{sgn}(h) }
-\end{aligned}\end{equation}
-Taking the limit of \(h \to 0^\pm\) then gives
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(h=0^\pm) = \frac{1}{\omega \pm \frac{U}{2}\sigma}
-\end{aligned}\end{equation}
-The self-energies arising from the correlation \(U\) can also be obtained using Dyson's equation \(\Sigma = G^{-1} - G_0^{-1}\), where \(G_0^{-1} = \omega\) is the Greens function at \(U=0\).
-Using Dyson's equation, we get
-\begin{equation}\begin{aligned}
-	\Sigma_{i,\sigma} = \pm\frac{U}{2}\sigma
-\end{aligned}\end{equation}
-
-\section{Analytic consistency check - On the Bethe lattice}
-One can apply a test to this method: it involves considering the case of infinite number of nearest-neighbours $w\to\infty$ (the coordination number, and effectively the dimension).
-In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
-This allows a metal-insulator transition in the limit of $w\to\infty$ as well.
-In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}.
-This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy1}.
-Applying the limit of \(w\to \infty\) on that equation gives
-\begin{equation}\begin{aligned}
-	\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}\right\} = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux,dd}(\omega)\right\}^{-1}
-\end{aligned}\end{equation}
-where \(G^{(0)}(\vec k,\omega)\) is the non-interacting Greens function and \(G_\text{aux,dd}(\omega)\) is the site-diagonal Greens function of the auxiliary model.
-It is clear from the final form that only the diagonal term \(G_\text{aux,dd}(\omega)\) of the interacting Greens function affects the self-energy while the off-diagonal part \(G_\text{aux,dz}\) fails to contribute as \(w \to \infty\).
-Even the non-interacting part Greens function can be shown to be diagonal in the limit of \(w\to\infty\)~\cite{kuramoto_manybody}.
-From its definition in time domain, we have
-\begin{equation}\begin{aligned}
-	G^{(0)}(\vec k, t) = -i\theta(t) \left<\left\{c_{\vec k}(t), c^\dagger_{\vec k}\right\} \right> = -i\theta(t) \left<\left\{e^{i H^{(0)}t} c_{\vec k} e^{-i H^{(0)}t}, c^\dagger_{\vec k}\right\} \right> = -i\theta(t) e^{-i \epsilon_{\vec k}t}\left[ \left<1 - \hat n_{\vec k}\right> + \left<\hat n_{\vec k}\right>\right] = -i \theta(t) e^{-i \epsilon_{\vec k}t}
-\end{aligned}\end{equation}
-A quick Fourier transform to \(\omega-\)domain shows that this is identical to the \(G^{(0)}(\vec k, \omega)\) defined just above eq.~\ref{self-energy}.
-We note that \(|G^{(0)}(\vec k, t)| \leq 1\).
-Using the Fourier transform  definition
-\begin{equation}\begin{aligned}
-	f(\vec k) = \frac{1}{d_N}\sum_{\vec r_i}h(\vec r_i) e^{i \vec{k}\cdot\vec{r}_i}
-\end{aligned}\end{equation}
-where \(d_N\) is a factor that only depends on the total number of sites and not on the coordination number, we can write
-\begin{equation}\begin{aligned}
-	|G^{(0)}(\vec k, t)|^2 = \frac{1}{d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}
-\end{aligned}\end{equation}
-From the inequality \(|G^{(0)}(\vec k, t)| \leq 1\), we get
-\begin{equation}\begin{aligned}
-	1 \geq \frac{1}{N}\sum_k |G^{(0)}(\vec k, t)|^2 = \frac{1}{N d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* \underbrace{\sum_k e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}}_{N \delta_{\vec r_i = \vec r_j}} = \frac{1}{d_N^2}\sum_{\vec r_i} |G^{(0)}(\vec r_i, t)|^2
-\end{aligned}\end{equation}
-For a coordination number of \(w\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
-Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{w}\).
-In contrast, there is only one local Greens function, that for \(\vec r_i=0\).
-The local Greens function therefore scales independent of \(w\).
-This implies that
-\begin{equation}\begin{aligned}
-	\lim_{w\to \infty}G^{(0)}(\vec k,\omega) = G^{(0)}(\vec r=0,\omega)
-\end{aligned}\end{equation}
-Since both the non-interacting and the interaction Greens functions lose their non-locality, the self-energy becomes completely local in the limit of \(w \to \infty\).
-
-\chapter{Going to larger clusters - the two site approach}
-
-\section{Why expand the cluster?}
-The previous chapter dealt with treating the Hubbard-Heisenberg model using an auxiliary model that has a single-site cluster:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux} =  \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s}_0 - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
-\end{aligned}\end{equation}
-This was able to describe an impurity phase transition from screened strong-coupling phase to local moment weak coupling phase, upon tuning \(U_b/J\).
-This then leads to a metal-insulator transition in the bulk, owing to the relations between the Greens functions and spectral functions obtained earlier.
-The single-site nature of the cluster (there was only a single impurity) has the following consequences:
-\begin{itemize}
-	\item [1.] The \(k-\)space self-energy of the bath has only minimal \(k-\)dependence arising from nearest-neighbour non-locality between the impurity and the zeroth site of the bath.
-	\item [2.] The local moment phase (which reduces to a set of decoupled clusters) becomes just the atomic limit, because each cluster has just one impurity.
-\end{itemize}
-
-In this chapter, we will improve on these two points by considering a larger cluster that has two impurities interacting with each other:
-\begin{equation}\begin{aligned}
-	\label{dimer_ham}
-	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right]\\
-	 -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right) + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
-\end{aligned}\end{equation}
-\(d_1\) and \(d_2\), or \(d_i\) in general, represent the two impurity sites in the dimer.
-They interact with each other through the same hopping parameter \(t\) as the bath.
-Each of the impurities has its own correlation \(U\) and hybridisation with the bath through \(V\) and \(J\).
-Each impurity site \(d_i\) couples with a bath site \(0_i\).
-\(0_1\) and \(0_2\) are assumed to be adjacent to each other, connected by the hopping \(t\).
-The setup is shown in fig.~\ref{two-imp-cluster}.
-
-Note that this chapter only sets out the relations between such an auxiliary model and the corresponding bulk model (in this case, a Hubbard-Heisenberg), but does not describe the physics of this new auxiliary model.
-That requires performing a renormalisation group calculation for \(H_\text{aux}\), and that will be provided at a later point in time.
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.6\textwidth]{../figures/two-site-cluster.pdf}
-	\caption{Two-impurity SIAM hybridising with a bath}
-	\label{two-imp-cluster}
-\end{figure}
-
-\section{Solution of the Hubbard dimer using the Anderson molecule}
-This section tries to see how far we can we can go if we just work with the Anderson molecule as the smallest unit of tiling.
-We will attempt to reproduce the entire spectrum of a Hubbard dimer by creating a new Hamiltonian made up purely of Anderson molecules.
-This will guide us in deciding how to generalize the "tiling method" for a general $N-$site Hubbard model, as well as give indications as to whether we need a different smallest unit for tiling.
-
-The Hubbard dimer and Anderson molecules (zero-mode) are defined by the following respective Hamiltonians:
-\begin{equation}\begin{aligned}
-	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat n_{i \uparrow}\hat n_{i \downarrow} - \mu^H \sum_{\sigma, i=1,2}\hat n_{i\sigma}\\
-	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \epsilon_d^A \sum_{\sigma}\hat n_{d\sigma} + U^A\hat n_{d \uparrow}\hat n_{d \downarrow}
-\end{aligned}\end{equation}
-In the first Hamiltonian, the indices \(i=1,2\) refer to the two lattice sites that constitute the dimer.
-In the second Hamiltonian, the subscript \(d\) indicates the impurity site, while the subscript \(z\) indicates the zero-mode site.
-First, we will assume that the Hubbard dimer is at half-filling (\(\frac{1}{2}U^H = \mu^H\)):
-\begin{equation}\begin{aligned}
-	\label{hubb_dimer}
-	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \left(\frac{1}{2}U^H- \mu^H\right) \sum_{\sigma, i=1,2}\hat n_{i\sigma} + \text{constant}\\
-	    &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
-\end{aligned}\end{equation}
-Since the Hubbard Hamiltonian is at half-filling, we will also place the impurity at half-filling by setting \(\epsilon_d^A = -\frac{1}{2}U^A\):
-\begin{equation}\begin{aligned}
-	\label{and_dimer}
-	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \left(\epsilon_d^A + \frac{1}{2}U^A\right) \sum_{\sigma}\hat \tau_{d\sigma} + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow} + \text{constant}\\
-	    &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow}
-\end{aligned}\end{equation}
-The first step is to recreate the Hubbard dimer Hamiltonian eq.~\ref{hubb_dimer} using the Anderson molecule Hamiltonian eq.~\ref{and_dimer}:
-\begin{equation}\begin{aligned}
-	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
-	    &= \frac{1}{2}\left[-t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + t^H\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\right] + \frac{1}{2} 2U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
-	    &= \frac{1}{2}\left[-t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right)\bigg\vert_{z \to 2, d \to 1\atop{t^A \to t^H}} + t^A\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\bigg\vert_{d \to 2,z \to 1\atop{t^A \to t^H}} \right] \\
-	    &+ \frac{1}{2} \left(U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 1\atop{U^A \to 2U^H}} + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 2\atop{U^A \to 2U^H}}\right)\\
-	    &=\frac{1}{2}\left[H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 1, z \to 2\right) + H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 2, z \to 1\right)\right]
-\end{aligned}\end{equation}
-The conclusion we can draw from this is that the Hubbard dimer Hamiltonian can be obtained from the Anderson dimer Hamiltonian in the following fashion:
-\begin{itemize}
-	\item The essential idea is that we have to create a local Hubbard Hamiltonian for each site of the Hubbard lattice by replacing the impurity label \(d\) in the Anderson dimer with the label of the particular site.
-So if there are two sites, we will get two local Hamiltonians obtained by replacing \(d\) with 1 and 2 respectively.
-For each local Hamiltonian, the zero-mode label \(z\) is replaced by the site that is nearest to the one that \(d\) is being replaced by.
-So, if \(d \to 1(2)\), then \(z \to 2(1)\).
-	\item This, however, is not the only change that we must make, in order to get the local Hamiltonian for a particular site.
-Along with \(d\) and \(z\), we must also make the transformations \(t^A \to t^H, U^A \to 2U^H\).
-	\item Finally, once we have the local Hamiltonians for sites 1 and 2, we average them to get the total Hubbard Hamiltonian.
-\end{itemize}
-Note that we expect most of these "rules" to be specific for the dimer, and there will be generalizations to most of them for a general \(N-\)site Hubbard Hamiltonian.
-
-The wavefunctions for the \(N=2\) sector can also be connected through these transformations.
-Since both the Hamiltonians are analytically solvable, we can write down their groundstate wavefunctions [CITE PAVARINI]:
-\begin{equation}\begin{aligned}
-	\ket{\Psi^H_\text{GS}} &= a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) - a_2(U^H,t^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
-	\ket{\Psi^A_\text{GS}} &= a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) - a_2(\frac{1}{2}U^A,t^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
-	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right), E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right)
-\end{aligned}\end{equation}
-where 
-\begin{equation}\begin{aligned}
-	a_1(U,t) \equiv \frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) - U \right) }}, && a_2(U,t) \equiv \sqrt{\frac{\Delta(U,t) - U}{2\Delta(U,t)}}, &&\Delta(U,t) \equiv \sqrt{U^2 + 16t^2}\\
-\end{aligned}\end{equation}
-$a_1,a_2$ satisfy $a_1(-U,t) = -a_2(U,t)$ and $a_1(U,t)a_2(U,t)= \frac{2t}{\Delta(U,t)}$.
-From the forms of the wavefunctions and eigenenergies, we can immediately write down
-\begin{equation}\begin{aligned}
-	\ket{\Psi^H_\text{GS}} &= \frac{1}{2}\left[\ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 1, z \to 2\right) + \ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 2, z \to 1\right)\right]\\
-	E^H_\text{GS} &= E^A_\text{GS}\left(t^A, U^A \to t^H, 2U^H\right)
-\end{aligned}\end{equation}
-This shows that the rules laid out before work for the Hamiltonians, as well as the wavefunctions and energy eigenvalues of the \(N=2,0,4\) sector.
-These sectors specifically work because it is only in these sectors can we ensure that \(n_d = n_z\), which is required for the Hubbard Hamiltonian because \(n_1 = n_2\).
-In the other sectors (\(N=1,3\)), the impurity site and the zero-mode sites have to be singly-occupied in some part, and since the impurity site incurs a single-occupation cost of \(-\frac{U^H}{2}\) which is not borne by the zero-mode site, there is an intrinsic dissimilarity between the two sites of the Anderson molecule in this regime.
-This dissimilarity does not exist for the Hubbard model, so we cannot hope to connect the two models in this regime.
-Going forward, we will switch to using Hubbard dimers as the smallest tiling unit for a general Hubbard model.
-
-\comment{
-\section{Strategy by starting from a zero bandwidth model}
-We start with a SIAM (with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian.
-The fixed point Hamiltonian will in general involve the impurity site (with renormalised parameters $\epsilon_d^*, U^*$) interacting with a smaller number of momentum states.
-
- To obtain a comparatively simple but physically well-motivated auxiliary model, we identify $\sum_k c_k = \sqrt N c_0$; \(c_0\) is the operator for the zeroth site (the site nearest to the impurity).
-We will call the set of all \(N-2\) sites apart from the impurity and this zeroth site as the "effective bath".
-The fixed point Hamiltonian can be separated into these parts: an isolated impurity part, an isolated zeroth site part, an isolated effective bath part, hopping between impurity and the zeroth site and hopping between the zeroth site and the effective bath.
-\textit{As a simplification, we will ignore the correlation term \((U)\) on the effective bath}.
-In preparation of a symmetrization procedure, we will relabel the impurity site as 0, and the zeroth site as 1.
-With all these steps, the Hamiltonian takes the form:
- \begin{equation}\begin{aligned}
- 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow}}_\text{imp.
-\& zero-mode isolated} - \underbrace{t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{0-1 coupling} - \underbrace{t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{1 \& eff.
-bath coupling} - \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff.
-bath isolated}
- \end{aligned}\end{equation}
- \begin{figure}[!htb]
- 	\centering
- 	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.png}
- 	\caption{Correlated asymmetric Anderson molecule schematic version.
-It consists of an impurity site (blue) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink).
-The other sites (green) form the rest of the bath.
-Just the impurity site and the zeroth site have onsite repulsion.}
- 	\label{and_mol}
- \end{figure}
- This Hamiltonian is depicted in fig.~\ref{and_mol}.
-Such a Hamiltonian is, however, explicitly asymmetric between the sites 0 and 1 (the effective bath couples only to 1).
-To rectify that, we will symmetrize the coupling between the effective bath and the sites 0 and 1, by exchanging the sites 0 and 1.
-The resultant Hamiltonian is
- \begin{equation}\begin{aligned}
- 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow} - t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{2-site Hubbard model} +\underbrace{- t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)- t^A\sum_{j \in \atop{\text{NN of 0}}}\left(c^\dagger_{0\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{dimer \& eff.
-bath coupling} \\
- 	- \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff. bath isolated}
- \end{aligned}\end{equation}
-
- To further simplify this Hamiltonian, \textit{we will combine the nearest neighbour sites of \(1\) and \(0\) into a single site}.
- \begin{equation}\begin{aligned}
- 	c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}
- \end{aligned}\end{equation}
- This single site will act as the zeroth site of the effective bath, and it means that both sites of the Hubbard dimer hybridizes with the effective through just a single site.
-With this assumption, the Hamiltonian for "a Hubbard dimer hopping into an effective bath" takes the simple form
- \begin{equation}\begin{aligned}
- 	\label{dimer_p_bat}
- 	\tilde H^D = H^D(0,1) - t^D \sum_{\sigma}\left(c^\dagger_{0\sigma}c_{z\sigma} + c^\dagger_{1\sigma}c_{z\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}
- \end{aligned}\end{equation}
- \(H^D(0,1)\) is the Hubbard dimer Hamiltonian (shown in fig.~\ref{hubb-dim}):
- \begin{equation}\begin{aligned}
- 	\label{dimer_ham}
- 	H^D(0,1) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)
- \end{aligned}\end{equation}
- \begin{figure}[!htb]
- 	\centering
- 	\includegraphics[width=0.4\textwidth]{../figures/hubb_dim.png}
- 	\caption{Hubbard dimer schematic version. It again consists of two sites, like the Anderson molecule, but now both sites have onsite repulsion, and their is again inter-site hopping.}
- 	\label{hubb-dim}
- \end{figure}
- This entire procedure is depicted in fig.~\ref{dimer-bath}.
- \begin{figure}[!htb]
- 	\centering
- 	\includegraphics[width=\textwidth]{../figures/dimer_bath.pdf}
- 	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.
-We first add the asymmetric Hamiltonians to get a symmetrized Hamiltonian.
-In the symmetrized Hamiltonian, the dimer has \(w\) entry points into the bath, \(w\) being the coordination number of the lattice.
-We then merge these \(w\) lattice sites (enclosed in the black box) into a single lattice site.}
- 	\label{dimer-bath} 
- \end{figure}
- We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice.
-The next step in the programme is to tile the real-space lattice with this dimer+bath Hamiltonian \(\tilde H_D\) to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H = T\left[ \tilde H^{D} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the dimer Hamiltonian to span the target real-space lattice.
-We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.
- \begin{equation}\begin{aligned}
- 	\tilde H &= \frac{2}{Nw}\sum_{\left<ij\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\tilde H^D((0,1,z) \to (i, j, l))\\
- 		 &= \frac{2}{N}U^D\sum_{i} \tau_{i \uparrow}\tau_{i \downarrow} - \frac{2}{Nw}\left(1 + \frac{Nw}{2}\right)t^D\sum_{\left<ij\right>}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)
- \end{aligned}\end{equation}
- What that means is that we have placed the Hubbard dimer+bath system at all nearest neighbour pairs to reconstruct a new Hubbard model.
-If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as dropping the correlation on the bath sites, we can write
- \begin{equation}\begin{aligned}
- 	\tilde H = \mathcal{U} H^H \mathcal{U}^{-1} = TZ\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right]Z^{-1} T^{-1}~,
- \end{aligned}\end{equation}
- where $\mathcal{U} = TZ\mathcal{U}_{A}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation that maps from the original to the reconstructed Hubbard Hamiltonian.
- The existence of $U$ is contingent on how good the approximations are.
-
- We mention the two approximations made along the entire journey from the original Hubbard model to the reconstructed one here.
- \begin{itemize}
- 	\item We have replaced the full Hubbard model by an auxiliary system described by the SIAM Hamiltonian in eq.~\ref{clus_bath_siam}.
-The accuracy of this assumption is determined by the choice of the SIAM parameters, particular the self-energy and repulsion of the bath.
-As discussed before, the very choice of th cluster and bath spoil the translational invariance of the parent model.
- 	\item We then perform a unitary RG on $H^A$.
-This leads to a fixed-point Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$.
-At this point, we go from the fixed point Hamiltonian to the dimer+bath Hamiltonian in eq.~\ref{dimer_p_bat}.
-If we represent this transformation from the fixed point Hamiltonian to the Hamiltonian in eq.~\ref{dimer_p_bat} by an operator \(Z\), we can write $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$.
-This constitutes the second approximation we make.
-\end{itemize}
-}
-
-\section{Creating \(N-\)site Hubbard Hamiltonian from Hubbard dimer embedded in a bath}
-Similar to the previous chapter, we will now tile the lattice with the two-site auxiliary model
-\begin{equation}\begin{aligned}
-	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right]\\
-	 -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right) + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
-\end{aligned}\end{equation}
-For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site.
-Note that a uniform number of nearest neighbours means that there is perfect translational invariance on the lattice, which means there cannot be any edge sites.
-This is achieved by applying periodic boundary conditions on the edges of the lattice.
-For example, a square 2d lattice will have to be placed on a 2-torus.
-
-The first step is to identity the two impurity sites \(d_1\) and \(d_2\) and the two bath sites \(0_1\) and \(0_2\) as sitting on a square arrangement of the lattice.
-\(d_i\) form one arm of the square, while \(0_i\) form the opposite arm.
-This square arrangement is shown in fig.~\ref{square-arms}, and is dictated by the auxiliary model chosen and shown in fig.~\ref{two-imp-cluster}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.3\textwidth]{../figures/square_arms.pdf}
-	\caption{Placing the impurity and bath sites \(d_i,0_i\) on a chosen square of the lattice. The chosen square is marked in blue, the impurity sites in orange and the bath sites in green.}
-	\label{square-arms}
-\end{figure}
-The sites at the vertices of the square are labelled as \(i,j,k,l\). With this identification, the Hamiltonian becomes
-\begin{equation}\begin{aligned}
-	H_\text{aux}(i,j,k,l) = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \frac{U}{2}\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.} + c^\dagger_{j\sigma}c_{l\sigma} + \text{h.c.}\right) + J \vec{S}_{i}\cdot\vec{s}_{k} \right.\\
-+ \left.
-J \vec{S}_{j}\cdot\vec{s}_{l} - U_b\left(\hat n_{k \uparrow} - \hat n_{k \downarrow}\right)^2 - U_b\left(\hat n_{l \uparrow} - \hat n_{l \downarrow}\right)^2\right] -t \sum_\sigma \left(c^\dagger_{i,\sigma}c_{j,\sigma} + \text{h.c.}\right) -t \sum_{\left<m,n \right>, \sigma}^{m,n \notin \left\{i,j\right\}}\left(c^\dagger_{m\sigma,n\sigma} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-As before, the kinetic energy part sums over all nearest neighbour pairs that involve neither \(i\) nor \(j\).
-For a given arm \(i-j\), the square can be rotated along the axis \(i-j\) to give one square arrangements for each dimension perpendicular to the axis along \(i-j\).
-Since there are \(w/2\) dimensions, the number of such squares is \(w/2 - 1\).
-For each such square, we can obtain another square by reflecting the square in the plane of \(i-j-l-k-i\) and across the line \(i-j\).
-The total number of squares is therefore \(w - 2\).
-The upshot is that given \(i-j\), there are multiple ways of choosing \(k\); if \(\left\{\vec a\right\}\) represents the set of \(w\) primitive vectors that connect a particular lattice site to its nearest neighbours, \(k\) can be situated at all \(\vec r_i + \vec a\) for which \(\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0\).
-Choosing \(k\) then automatically fixes \(l\) at \(\vec r_j + \vec a\).
-The condition \(\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0\) simply means we only take those \(\vec a\) that are perpendicular to \(\vec r_j - \vec r_i\).
-Since there are \(w\) number of \(\vec a\) in total and 2 of them are parallel, the total number of choices of \(k,l\) is \(w-2\).
-For a 2D lattice, we have \(w=4\), so there are only two possible choices of the square.
-They are shown in fig.~\ref{square-arms-all}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.6\textwidth]{../figures/square_arms_all.pdf}
-	\caption{Placing the impurity and bath sites \(d_i,0_i\) on a chosen square of the lattice. The chosen square is marked in blue, the impurity sites in orange and the bath sites in green.}
-	\label{square-arms-all}
-\end{figure}
-
-The Hamiltonian for an arm \(i-j\) is then obtained by averaging over these squares:
-\begin{equation}\begin{aligned}
-	H_\text{aux}(i,j) = \frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
-\end{aligned}\end{equation}
-The final step is to sum over all nearest neighbour arms \(i-j\):
-\begin{equation}\begin{aligned}
-	\label{22siam_to_hubb}
-	H_\text{full} = \sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
-\end{aligned}\end{equation}
-
-There are four kinds of terms:
-\begin{itemize}
-	\item the first kind, \(A(i), A(j)\), depend only on either \(i\) or \(j\).
-They can be summed over easily by noting that the internal summation gives a constant factor of \(w-2\) which is canceled by the factor of \(1/(w-2)\) in the front, and the external summation gives \(\sum_{i,j}A(i) = \frac{w}{2} \sum_i A(i)\), because \(i\) is a member of \(w/2\) distinct nearest-neighbour pairs.
-	\item The second kind, \(B(i,j)\) depends on both \(i\) and \(j\).
-The internal summation is again cancelled by the prefactor.
-The external summation simply sums over all nearest-neighbour values of \(A(i,j)\).
-	\item The third kind, \(C(i,k), C(j,l)\), depend on \(i\) and \(k\).
-Here, the total summation \(\sum_{i,j,k}C(i,k)\) gives \((w-2)\sum_{\left<i,k\right>}\left(C(i,k) + C(k,i)\right)\), because the pair \((i,k)\) occurs \(w-2\) times corresponding to the \(w-2\) vectors \(\vec r_j - \vec r_i\) that are perpendicular to \(\vec r_i - \vec r_k\).
-The factor is again cancelled by the existing prefactor.
-	\item The fourth kind, \(D(k), D(l), E(k,l)\), depend on just \(k\), just \(l\) or both \(k\) and \(l\).
-For each pair \(i-j\) in the external summation, the particular pair \(k-l\) appears only once.
-When \(i-j\) is summed over, a factor of \(2(w/2-1)\) is generated because there are that many squares that involve \(k-l\).
-This factor cancels the inverse factor in front, giving \(\sum_{\left<k\right>} D(k), \sum_{\left<k,l \right>}E(k,l)\).
-\end{itemize}
-
- The full Hamiltonian reads
-\begin{equation}\begin{aligned}
-	H_\text{full} =& w\sum_i\left[- \frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\right] - t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + 4V\sum_{\sigma, \left<i,k\right>}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.}\right)\\
-		      &+ 4J \sum_{\left<i,k\right>}\left(\vec{S}_{i}\cdot\vec{S}_{k}\right) - 2 U_b\sum_k\left(\hat n_{k \uparrow} - \hat n_{k \downarrow}\right)^2 - \frac{Nw/2}{w-2}t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)\\
-	=& -\frac{1}{2}\left(Uw + 4U_b\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{Nw/2}{w-2}t + t - 4V\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 4J \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
-\end{aligned}\end{equation}
-The bulk model hence obtained is again a Hubbard-Heisenberg model.
-In eq.~\ref{2siam_to_hubb}, the total number of terms in the outer summation is \(Nw/2\).
-In order to make sure that this full Hamiltonian scales as \(N\), we divide this by \(w/2\):
-\begin{equation}\begin{aligned}
-	\label{2siam_to_hubb}
-	H_\text{full} &= \frac{2}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) = \frac{2}{w}\sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
-		      &= -\frac{1}{2}\left(2U + 8U_b/w\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{N}{w-2}t + 2t/w - 8V/w\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 8J/w \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
-\end{aligned}\end{equation}
-The mappings between the parameters of the auxiliary model and the bulk are
-\begin{equation}\begin{aligned}
-	t_\text{H-H} = \left(\frac{N}{w-2}t + 2t/w - 8V/w\right),~ ~ ~ U_\text{H-H} = 2U + 8U_b/w,~ ~ ~ J_\text{H-H} = 8J/w
-\end{aligned}\end{equation}
-
-We could have also inserted a spin-exchange interaction between the two impurities in the auxiliary model:
-\begin{equation}\begin{aligned}
-	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right] -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right)\\
-	+ J_d \vec{S}_{d_1}\cdot\vec{S}_{d_2} + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
-\end{aligned}\end{equation}
-In the presence of this term, the bulk Hamiltonian remains the same, but the expression of \(J_\text{H-H}\) changes.
-Since this term is similar in form to the term preceding it, we can easily obtain the updated expression:
-\begin{equation}\begin{aligned}
-	J_\text{H-H} = \frac{2}{w}\left(4J + 2J_d\right)
-\end{aligned}\end{equation}
-
-\section{Single-particle Green's function}
-We now define the Greens function {\it operators}:
-\begin{equation}\begin{aligned}
-	\mathcal{G}_{H-H} = \frac{1}{\omega^\prime - \left(H_{H-H} - E_\text{gs}^\prime\right) }, \mathcal{G}_\text{aux}(i,j) = \frac{1}{\omega - \left(\mathcal{H}_\text{aux}(i,j) - E_\text{gs}\right)}
-\end{aligned}\end{equation}
-Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian, while the primed quantities \(E_\text{gs}^\prime\) and \(\omega^\prime\) are the same quantities but for the full model \(\mathcal{H}_{H-H}\).
-While the auxiliary model is intensive, the full Hamiltonian is extensive and scales as \(N\):
-\begin{equation}\begin{aligned}
-	H_\text{full} &= \frac{2}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) \sim N H_\text{aux}(d_1,d_2)~.
-\end{aligned}\end{equation}
-This means that we must have \(\omega^\prime = N\omega\) and \(E_\text{gs}^\prime = N E_\text{gs}\).
-Rewriting eq.~\ref{2siam_to_hubb} in terms of the operators \(\mathcal{G}\), we get
-\begin{equation}\begin{aligned}
-\sum_{\left<i,j \right>} \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i,j)\right) = N\omega + N E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_{\left<i,j \right>} \mathcal{G}^{-1}_\text{aux}(i,j) = \mathcal{G}^{-1}_{H-H}~,
-\end{aligned}\end{equation}
-We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model.
-Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(\mathcal{H}_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate.
-We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-The superscript \(p\) indicates that this is the particle propagation matrix element.
-Under the auxiliary model approximation, we ignore the virtual entanglement between separate clusters.
-Therefore, the only operators \(\mathcal{G}^{-1}_\text{aux}(k,l)\) that affect the matrix element are those that satisfy \(i \in \left(k,l\right)\).
-There are \(w\) such pairs: \(\left\{k,l\right\} = \left\{i,j\right\} \forall~ j \in \text{NN of i}\).
-Moreover, because of translation invariance, all \(j \in \text{NN of i}\) are equivalent.
-These configurations are shown in fig.~\ref{diag_conrib}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/diagonal_contributors.pdf}
-	\caption{The various configurations of auxiliary models that contribute to the diagonal matrix element at site \(i\). Orange colour represents impurities and green represents bath sites.}
-	\label{diag_conrib}
-\end{figure}
-
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0} = \frac{2}{w} \times w \times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i, i+1) c^\dagger_{i\sigma} | \Phi_0} = 2\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-where we have identified site \(i\) in the auxiliary model as one of the impurities \(d_1\).
-We could very well have chosen \(d_2\) since the model is symmetric in \(d_1,d_2\).
-\(\mathcal{G}^{-1}_\text{aux}(d_1,d_2)\) is the Greens operator corresponding to the Hamiltonian in eq.~\ref{dimer_ham}.
-
-By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}\), we get from the spectral representation
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = 2\sum_{m,n} \braket{\Phi_0 | c_{d_1\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux} \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d_1\sigma} | \Phi_0} = 2\sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
-\end{aligned}\end{equation}
-There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(\mathcal{H}_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\).
-We also defined \(d^p_{i,n} = \bra{\Phi_n}c^\dagger_{d_i\sigma}\ket{\Phi_0}\).
-The hole propagation matrix element can be obtained similarly:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = 2\sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn} 
-\end{aligned}\end{equation}
-where \(d^h_{i,n} = \bra{\Phi_n}c_{d_i\sigma}\ket{\Phi_0}\).
-
-The off-diagonal matrix elements between two nearest-neighbour sites \(i\) and \(i+1\) can also be obtained similarly. Several  auxiliary models can contribute to such a matrix element:
-\begin{itemize}
-	\item those auxiliary models that have \(i\) and \(i+1\) as the two impurities. These give the contribution \\
-		\(\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0}\). 
-	\begin{equation}\begin{aligned}
-		\frac{2}{w}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0} = \frac{2}{w}\sum_{n} \left(d^p_{1,n}\right)^*d^p_{2,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
-	\end{aligned}\end{equation}
-	\item those that have \(i\) as an impurity and \(i+1\) as the corresponding bath site. There will be \(w-2\) of these in number:
-	\begin{equation}
-		(w-2) \times \frac{2}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{0_1\sigma} | \Phi_0} = \frac{2}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
-	\end{equation}
-		where \(z^p_{i,n} = \braket{\Phi_n | c^\dagger_{0_i,\sigma} | \Phi_0}\).
-	\item those that have \(i+1\) as an impurity site and \(i\) as the corresponding bath site. There are again \(w-2\) of these:
-	\begin{equation}
-		(w-2) \times \frac{2}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{0_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0} = \frac{2}{w}\left(z^p_{1,n}\right)^* d^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
-	\end{equation}
-\end{itemize}
-These choices are shown in fig.~\ref{off-diag-contrib}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/offdiagonal_contributors.pdf}
-	\caption{Auxiliary models that contribute to the off-diagonal matrix element. \(j \equiv i+1\)}
-	\label{off-diag-contrib}
-\end{figure}
-
-Adding all contributions gives
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}
-\end{aligned}\end{equation}
-The hole counterpart is
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}
-\end{aligned}\end{equation}
-where \(z^h_{i,n} = \bra{\Phi_n}c_{z_i\sigma}\ket{\Phi_0}\).
-
-The off-diagonal matrix element between next-to-nearest-neighbour sites \(i,i+2\) can also be obtained, provided their positions are related as \(\vec r_{i+2} = \vec r_i + \vec a + \vec a^\prime\), where \(\vec a\) and \(\vec a^\prime\) are primitive vectors that connect any lattice site to its nearest-neighbours, and \(\vec{a}\cdot\vec{a}^\prime = 0\).
-This is shown in fig.~\ref{next-near}.
-
-\par\noindent
-\begin{minipage}{0.6\textwidth}
-The essence is that the two sites have to form the two most separated vertices of a right-angled triangle.
-To find the auxiliary models that contribute to this matrix element, note that there is only one square that can be formed keeping both \(i\) and \(i+2\) on it - we call this square \(ABCD\), where \(A\) is the vertex \(i\) and \(C\) is the vertex \(i+2\).
-We can set \(A=d_1, C=0_2\).
-The other two vertices \(B\) and \(D\) can have two possible configurations:\(B=d_2,D=0_1\) and \(B=0_1,D=d_2\).
-Two more configurations can be obtained by taking each of these two configurations and keeping \(B,D\) unchanged but exchanging \(A\) and \(C\).
-These four configurations are shown in fig.~\ref{nn-configs}.
-\end{minipage}
-\hspace*{\fill}
-\begin{minipage}{0.35\textwidth}
-	\centering
-	\includegraphics[width=0.9\textwidth]{../figures/next-near.pdf}
-	\captionof{figure}{The kind of next-nearest neighbour sites that can be connected by the auxiliary model.}
-	\label{next-near}
-\end{minipage}
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/nn-offdiagonal_contributors.pdf}
-	\caption{Auxiliary model configurations that contribute to the next-nearest neighbour matrix elements. \(j \equiv i+2\)}
-	\label{nn-configs}
-\end{figure}
-
-These four configurations give
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} &= \frac{2}{w(w-2)}\left[\braket{\Phi_0|c_{d_1\sigma}\mathcal{G}^{-1}_\text{aux}(d_1,d_2)c^\dagger_{0_2,\sigma}|\Phi_0} + \braket{\Phi_0|c_{0_2\sigma}\mathcal{G}^{-1}_\text{aux}(d_1,d_2)c^\dagger_{d_1,\sigma}|\Phi_0}\right] \\
-										 &= \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}
-\end{aligned}\end{equation}
-
-In summary, the spectral representation of the matrix elements of the inverse Greens operators are given by
-\begin{gather}
-\label{green_eq_final_2siam}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}~,\\
-	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}~,\\
-	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}_\text{H-H}^{-1}\left( -\omega \right) \right)^h_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^h_{1,n}\right)^* z^h_{2,n} + \left(z^h_{2,n}\right)^* d^h_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~.
-\end{gather}
-
-In order to obtain the matrix elements of the Greens operators \(\mathcal{G}_{H-H}\) (as compared to its inverse), we note that we have just observed that the matrix elements of the inverse Greens operators are related to the matrix elements of another inverse operator through some coefficients.
-We can, therefore, use the identity
-\begin{equation}\begin{aligned}
-\left(\hat O\right)_{ij} = \bra{i} \hat O \ket{j} = \sum_{m,n} \braket{i|m} \left(\hat O\right)_{mn} \braket{n|j} \implies \left(\hat O^{-1}\right)_{ij} = \sum_{m,n} \braket{i|m} \left(\hat O^{-1}\right)_{mn} \braket{n|j}
-\end{aligned}\end{equation}
-We can now identify \(\left(\hat O^{-1}\right)_{mn}\) as the matrix elements of \(\mathcal{G}_\text{aux}^{-1}\) in our expressions.
-Using the above relation, we can therefore write the spectral representation of the matrix elements of the Greens operators as
-\begin{gather}
-	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w}\sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn}~,\\
-	\left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w}\sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}~,\\
-	\left(\mathcal{G}_\text{H-H}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}_\text{H-H}\left( -\omega \right) \right)^h_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^h_{1,n}\right)^* z^h_{2,n} + \left(z^h_{2,n}\right)^* d^h_{1,n}\right] \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~.
-\end{gather}
-
-The Lehmann-Kallen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements.
-Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
-\begin{equation}\begin{aligned}
-	&\left(G_{H-H}(\omega)\right)_\text{loc} = \left(\mathcal{G}_{H-H}(\omega)\right)_{ii}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn} - |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\right] = G_\text{aux}(d_1,d_1;\omega)\\
-	&\left(G_{H-H}(\omega)\right)_\text{n-n} = \left(\mathcal{G}_{H-H}(\omega)\right)_{i,i+1}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{i+1,i}^h\\
-						&\frac{2}{w}\sum_n \left\{\left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn} - \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}\right\}\\
-						&= \frac{2}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right]\\
-						&\left(G_\text{H-H}\right)_\text{n-n-n} = \frac{2}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right] 
-\end{aligned}\end{equation}
-
-\section{Spectral functions and self-energies}
-
-The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
-\end{aligned}\end{equation}
-where $\vec{r_i}$ is the position vector of a particular lattice site.
-Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites.
-As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
-As we do not have real space Greens function that are more non-local than next-nearest neighbour, we will attempt to obtain momentum space Greens function from these contributions:
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
-\end{aligned}\end{equation}
-The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, w\right]\right\}$.
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} + G_{H-H} (\omega)_\text{n-n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {b_i}}= G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k} + G_{H-H} (\omega)_\text{n-n-n} \xi^\prime_{\vec k}
-\end{aligned}\end{equation}
-where we defined \(\left\{b_i\right\} \) as the set of vectors that connect a particular lattice site with its next-nearest-neighbours,\(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\) and \(\xi^\prime_{\vec k} \equiv \sum_{j} e^{i \vec{k}\cdot\vec {b_j}}\).
-Note that \(b_j\) is simply \(a_i + a{i^\prime}\) where \(a_i\) and \(a_{i^\prime}\) are orthogonal.
-On a d-dimensional hypercubic lattice, we obtain
-\begin{gather}
-	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i\\
-\end{gather}
-On a 2D square lattice with lattice spacing $a$, this simplifies to (same as eq.~\ref{2dsquaretb})
-\begin{eqnarray}
-\xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
-\end{eqnarray}
-where \(\epsilon_{\vec{q}} = -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})\) is the tight-binding dispersion.
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) = G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] \\
-	 + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]
-\end{aligned}\end{equation}
-
-We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
-\begin{equation}\begin{aligned}
-	A_\text{H-H}(\vec{k},\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega)) =A_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[A_\text{aux}(d_1,d_2;\omega) + A_\text{aux}(d_1,0_1;\omega) + A_\text{aux}(0_1,d_1;\omega)\right]\\
-	 + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[A_\text{aux}(d_1,0_2;\omega) + A_\text{aux}(0_2,d_1;\omega)\right]
-\end{aligned}\end{equation}
-where the spectral function $A_\text{aux}=-\frac{1}{\pi}\textrm{Im}G_\text{aux}$.
-
-With the knowledge of the momentum-space Greens function $G_\text{H-H}(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
-\begin{equation}\begin{aligned}
-	\Sigma(\vec k,\omega) = \left(G^{(0)}(\vec k,\omega)\right)^{-1} - G(\vec k,\omega)^{-1}
-\end{aligned}\end{equation}
-where $\left(G^{(0)}(\vec k,\omega)\right)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system.
-Substituting this as well as the full Greens function $G_{H-H}(\vec k, \omega)$ into Dyson's equation gives
-\begin{equation}\begin{aligned}
-	\label{self-energy}
-	&\Sigma_{H-H}(\vec k,\omega) = \left(G^{(0)}(\vec k,\omega)\right)^{-1} -\\
-	&\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}
-\end{aligned}\end{equation}
-This allows us to calculate the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
-
-\section{Analytic consistency check - On the Bethe lattice}
-Another test involves considering the case of a Bethe lattice with infinite number of nearest neighbours $w\to\infty$ (the coordination number).
-In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
-This allows a metal-insulator transition in the limit of $w\to\infty$ as well.
-In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}.
-This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy}.
-Applying the limit of \(w\to \infty\) on that equation gives
-\begin{equation}\begin{aligned}
-	&\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left[G^{(0)}(\vec k,\omega)\right]^{-1} -\right.\\
-	&\left.\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}\right\}\\
-	& = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux}(d_1,d_1;\omega)\right\}^{-1} 
-\end{aligned}\end{equation}
-where \(G_\text{aux}^{(0)}(\vec k,\omega)\) is the non-interacting Greens function.
-It is clear from the final form that only the diagonal term \(G_\text{aux}(d_1,d_1;\omega)\) of the interacting Greens function affects the self-energy.
-Even the non-interacting part Greens function can be shown to be diagonal in the limit of \(w\to\infty\)~\cite{kuramoto_manybody}.
-From its definition in time domain, we have
-\begin{equation}\begin{aligned}
-	G^{(0)}(\vec k, t) = -i\theta(t) \left<\left\{c_{\vec k}(t), c^\dagger_{\vec k}\right\} \right> = -i\theta(t) \left<\left\{e^{i H^{(0)}t} c_{\vec k} e^{-i H^{(0)}t}, c^\dagger_{\vec k}\right\} \right> = -i\theta(t) e^{-i \epsilon_{\vec k}t}\left[ \left<1 - \hat n_{\vec k}\right> + \left<\hat n_{\vec k}\right>\right] = -i \theta(t) e^{-i \epsilon_{\vec k}t}
-\end{aligned}\end{equation}
-A quick Fourier transform to \(\omega-\)domain shows that this is identical to the \(G^{(0)}(\vec k, \omega)\) defined just above eq.~\ref{self-energy}.
-We note that \(|G^{(0)}(\vec k, t)| \leq 1\).
-Using the Fourier transform  definition
-\begin{equation}\begin{aligned}
-	f(\vec k) = \frac{1}{d_N}\sum_{\vec r_i}h(\vec r_i) e^{i \vec{k}\cdot\vec{r}_i}
-\end{aligned}\end{equation}
-where \(d_N\) is a factor that only depends on the total number of sites and not on the coordination number, we can write
-\begin{equation}\begin{aligned}
-	|G^{(0)}(\vec k, t)|^2 = \frac{1}{d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}
-\end{aligned}\end{equation}
-From the inequality \(|G^{(0)}(\vec k, t)| \leq 1\), we get
-\begin{equation}\begin{aligned}
-	1 \geq \frac{1}{N}\sum_k |G^{(0)}(\vec k, t)|^2 = \frac{1}{N d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* \underbrace{\sum_k e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}}_{N \delta_{\vec r_i = \vec r_j}} = \frac{1}{d_N^2}\sum_{\vec r_i} |G^{(0)}(\vec r_i, t)|^2
-\end{aligned}\end{equation}
-For a coordination number of \(w\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
-Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{w}\).
-In contrast, there is only one local Greens function, that for \(\vec r_i=0\).
-The local Greens function therefore scales independent of \(w\).
-This implies that
-\begin{equation}\begin{aligned}
-	\lim_{w\to \infty}G^{(0)}(\vec k,\omega) = G^{(0)}(\vec r=0,\omega)
-\end{aligned}\end{equation}
-Since both the non-interacting and the interaction Greens functions lose their non-locality, the self-energy becomes completely local in the limit of \(w \to \infty\).
-
-\chapter{The Periodic Anderson and Kondo models}
-The heavy Fermion systems are described by periodic versions of the single impurity models, where instead a lattice of impurities \(\left\{ d_i \right\} \) hybridises with a conduction bath lattice \(\left\{ i \right\} \).
-The periodic Anderson model is defined by the Hamiltonian
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right)  - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-
-As before, we will work with a generalised form of it where we also consider a spin-exchange interaction between the impurity sites and the bath sites:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right) + J \sum_i \vec{S}_{d_i}\cdot\vec{s}_i - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-One can also introduce an RKKY interaction \(J_\text{RKKY}\) between the nearest neighbour impurity spins:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right) + J \sum_i \vec{S}_{d_i}\cdot\vec{s}_i - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma} \\
-	+ J^\prime\sum_{\left<d_i,d_j \right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
-\end{aligned}\end{equation}
-
-\section{Creating a bulk periodic Anderson model by tiling with generalised single-impurity Anderson models: no RKKY}
-
-The auxiliary model we will be using is a generalised SIAM with attractive interaction on the bath zeroth site and explicit particle-hole asymetry on the impurity:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux} = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s}_0 + \eta \sum_\sigma\tau_{d\sigma}
-\end{aligned}\end{equation}
-where \(\tau = \hat n - 1/2\).
-
-We will use this as the auxiliary model to study the Hubbard model.
-We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
-Note that the impurity level and the conduction bath can be tuned to half-filling by setting \(\eta=0\) and \(\mu=0\) respectively.
-To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(d_i\) of the impurity lattice, and the bath sites will constitute the bulk lattice sites.
-We will also identity the zeroth site of the SIAM lattice as one particular site \(i\) of the conduction bath lattice:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(d_i) = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) +J \vec{S}_{d_i}\cdot\vec{s}_i + \eta \sum_\sigma\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-Once we have this local Hamiltonian for a particular site, we translate this over all \(N\) sites \(\left\{\left(d_i,i\right) \right\} \):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} = \sum_{i} \mathcal{H}_\text{aux}(d_i) = N\sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) +J \sum_i\vec{S}_{d_i}\cdot\vec{s}_i \\
-	+ \eta \sum_{i,\sigma}\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-
-We end up with a generalised periodic Anderson model:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{GPAM} = \sum_{k\sigma}\left(\left(\epsilon_k\right)_\text{GPAM} - \mu_\text{GPAM}\right)\tau_{k\sigma} - \frac{U_\text{GPAM}}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V_\text{GPAM} \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right)\\
-	+ J_\text{GPAM} \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + \eta_\text{GPAM} \sum_{i,\sigma}\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-The mapping between the parameters of the auxiliary model and that of the bulk are
-\begin{equation}\begin{aligned}
-	\label{map_pam_bulk}
-	\left(\epsilon_k\right)_\text{GPAM} = N\epsilon_k, ~ ~ \mu_\text{GPAM} = N\mu, ~ ~ U_\text{GPAM} = U, ~ ~ V_\text{GPAM} = V, ~ ~ J_\text{GPAM} = J, ~ ~ \eta_\text{GPAM} = \eta
-\end{aligned}\end{equation}
-
-\section{Creating a bulk periodic Anderson model by tiling with two-impurity Anderson models: with RKKY}
-
-This time we will use a two-impurity model with a spin-exchange coupling between the impurities as the auxiliary model:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux} = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\sum_{i=1,2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right)^2 + \sum_{i=1,2}\left[V \sum_{\sigma} \left(c^\dagger_{0_i\sigma} c_{d_i\sigma} + h.c.\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i}\right] + \eta \sum_\sigma\tau_{d\sigma}\\
- + J^\prime\vec{S}_{d_1}\cdot\vec{S}_{d_2}
-\end{aligned}\end{equation}
-where \(\tau = \hat n - 1/2\).
-
-We will use this as the auxiliary model to study the Hubbard model.
-We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
-Note that the impurity level and the conduction bath can be tuned to half-filling by setting \(\eta=0\) and \(\mu=0\) respectively.
-To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity sites \(d_1 \) and \(d_2\) as particular nearest-neighbour sites \(d_i, d_{j}\) of the impurity lattice, and the bath sites will constitute the bulk lattice sites.
-We will also identity the bath sites \(0_1,0_2\) as two particular nearest-neighbour sites \(i,j\) of the conduction bath lattice:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(d_i, d_{j}) = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left[\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + \left(\hat n_{d_{j} \uparrow} - \hat n_{d_{j} \downarrow} \right) ^2\right] + V \sum_{\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + c^\dagger_{j,\sigma} c_{d_{j},\sigma} + h.c.\right)\\
- + J \left(\vec{S}_{d_i}\cdot\vec{s}_i + \vec{S}_{d_{j}}\cdot\vec{s}_{j}\right) + \eta \sum_\sigma\left(\tau_{d_i\sigma} + \tau_{d_{j}\sigma}\right)+ J^\prime\vec{S}_{d_i}\cdot\vec{S}_{d_j}\\
-\end{aligned}\end{equation}
-Once we have this local Hamiltonian for a particular site, we translate this over all nearest-neighbour pairs \((i,j)\) of the lattice.
-There are \(Nw/2\) of these.
-To ensure the bulk model scales as \(N\), we divide this sum by \(w/2\).
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} = \frac{2}{w}\sum_{\left<i,j\right>} \mathcal{H}_\text{aux}(d_i) = N\sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - 2\frac{U}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + 2V \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) \\
-	 + 2J \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + 2\eta \sum_{i,\sigma}\tau_{d_i\sigma} + \frac{2}{w}J^\prime\sum_{\left<i,j\right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
-\end{aligned}\end{equation}
-
-We end up with a generalised periodic Anderson model with RKKY interaction:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{GPAM} = \sum_{k\sigma}\left(\left(\epsilon_k\right)_\text{GPAM} - \mu_\text{GPAM}\right)\tau_{k\sigma} - \frac{U_\text{GPAM}}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V_\text{GPAM} \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right)\\
-	+ J_\text{GPAM} \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + \eta_\text{GPAM} \sum_{i,\sigma}\tau_{d_i\sigma} + J^\prime_\text{GPAM}\sum_{\left<i,j\right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
-\end{aligned}\end{equation}
-The mapping between the parameters of the auxiliary model and that of the bulk are
-\begin{equation}\begin{aligned}
-	\left(\epsilon_k\right)_\text{GPAM} = N\epsilon_k, ~ ~ \mu_\text{GPAM} = N\mu, ~ ~ U_\text{GPAM} = 2U, ~ ~ V_\text{GPAM} = 2V, ~ ~ J_\text{GPAM} = 2J, ~ ~ \eta_\text{GPAM} = 2\eta, ~ ~ J^\prime_\text{GPAM} = \frac{2}{w}J^\prime
-\end{aligned}\end{equation}
-
-\chapter{Future goals}
-\begin{enumerate}
-\item The Mott metal-insulator transition:
-	\begin{itemize}
-	\item Obtain the metal insulator transition of the 2D Hubbard-Heisenberg model on the square lattice from the present formalism. 
-	\item Determine the nature of the bath $\Sigma (k,\omega)$ in the metallic phase, insulating phase as well as at criticality.
-	\item Investigate nature of the zero-temperature transition (order of transition, order parameter, etc)
-	\end{itemize}
-
-\item Higher-order Greens functions:
-	\begin{itemize}
-	\item Provide expressions for two-particle Greens functions.
-	\item Calculate explicitly the Greens functions for holon-doublon and spinon-spinon excitations as they are likely to contain more information regarding the ground state.
-	\item Obtain spectral functions for such excitations
-	\end{itemize}
-
-\item Benchmarking against ED and/or finite size scaling:
-	\begin{itemize}
-	\item ground state energy
-	\item double occupancy
-	\end{itemize}
-
-\item Upgrade to two-site cluster:
-	\begin{itemize}
-	\item Study a two-impurity model under renormalisation group
-	\item Derive the tiling and Greens function relations for such a two-impurity model 
-	\item Demonstrate Mott MIT here.
-	\item Investigate the nature of many-particle entanglement in such a cluster
-	\item look for signs of a quantum liquid.
-	\end{itemize}
-
-\item Once we have a handle on the zero temperature features, we intend to compute Greens functions at non zero temperatures.
-
-\item This method can also be extended to various other models of strong correlation:
-	\begin{enumerate}
-		\item Heisenberg model, by starting from a Kondo model effective Hamiltonian
-		\item Periodic Anderson model, by starting from a SIAM with a dispersive bath
-		\item Periodic Kondo model, by starting from a Kondo model with a dispersive bath
-	\end{enumerate}
-\end{enumerate}
-
-\begin{appendices}
-
-\appendixtitleon
-
-\chapter{Derivation of RG equations for the impurity model with \(U,V,J,K,U_b,\eta\)}
-
-\section{The Hamiltonian}
-
-The Hamiltonian for the impurity problem is
-\begin{equation}\begin{aligned}
-	\mathcal{H} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{1}{2} U \left( \tau_{d \uparrow} - \tau_{d \downarrow} \right) ^2 + \frac{1}{2}\eta \left(\tau_{d \uparrow} + \tau_{d \downarrow}\right) + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} + K \vec{C}_d\cdot\vec{C} - U_b\left(\tau_{0 \uparrow} - \tau_{0 \downarrow}\right)^2
-\end{aligned}\end{equation}
-wher \(\tau \equiv \hat n -\frac{1}{2}\).
-The first term is the kinetic energy term with a dispersion \(\epsilon_k\).
-The second term is the particle-hole symmetric impurity correlation term that sets the uncorrelated half-filled level \(\tau_{d\uparrow} = - \tau_{d \downarrow} = \pm \frac{1}{2}\) at energy \(-U/2\) below the Fermi surface, and the correlated doublon and holon states \(\tau_{d\downarrow} = \tau_{d \uparrow} = \pm \frac{1}{2}\) at the Fermi surface.
-The particle-hole symmetry is in the fact that the term is invariant under \(\tau_{d\sigma} \to-\tau_{d\sigma}\), and manifests in the symmetric positioning of the doublon and holon levels with respect to each other.
-The third term is the particle-hole asymmetry term that explicitly measures the deviation away from particle-hole symmetry - it is non-zero only when we are away from half-filling.
-The fourth, fifth and sixth terms describe various mechanisms in which the impurity can hybridise with the conduction bath.
-The first of these is a single-particle hopping \(V\), the second mechanism is through spin-flip scattering, and the third is through isospin-flip scattering.
-The single-particle hybridisation \(V\) allows the impurity electron to tunnel into the conduction bath and this leads to a frequency-dependent self-energy renormalisation of the impurity, implying that the impurity electron can spend  large amount of time in the bath~\cite{coleman2015}.
-\(\vec S_d = \frac{1}{2}\sum_{\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{d\alpha}c_{d\beta} \) is the impurity spin, while \(\vec C_d = \frac{1}{2}\sum_{\alpha\beta} \psi^\dagger_\alpha \vec \sigma_{\alpha\beta}\psi_\beta\) is the impurity isospin, where \(\psi = \left(c_{d\uparrow} ~ ~ ~ ~ c^\dagger_{d \downarrow}\right)\)~
-\cite{anderson1958random,nambu_1960}.
-The former acts on the \(2-\)dimensional Hilbert-space formed by the magnetic up and down states on the impurity, while the latter acts on the \(2-\)dimensional space formed by the doublon and holon states.
-The former reacts to a magnetic field, while the latter responds to a chemical potential.
-Such a chemical potential term that couples with the isospin is already present in the Hamiltonian - it is the assymetry term \(\eta\).
-In fact, that term can be rewritten as \(\eta C_d^z\), because \(C^z_d = \frac{1}{2}\left(\hat n_{d \uparrow} + \hat n_{d \downarrow} - 1\right) = \frac{1}{2}\left( \tau_{d \uparrow} + \tau_{d \downarrow} \right) \).
-The bath operators \(\vec s\) and \(\vec C\) are defined in the same way as the operator counterparts: \(\vec s = \sum_{kk^\prime\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{k\alpha}c_{k^\prime\beta}, \vec C = \sum_{kk^\prime\alpha\beta}{\psi^k}^\dagger_\alpha\vec\sigma_{\alpha\beta}\psi^{k^\prime}_\beta\), where \(\psi^k = \left(c_{k\alpha} ~ ~ ~ ~ c^\dagger_{k^\prime\beta}\right) \).
-The final seventh term is a local particle-hole symmetric correlation on the zeroth site of the bath.
-For \(U_b>0\), this term promotes half-filling on the zeroth site, while for \(U_b<0\), a doublon or holon is more favourable on that site.
-
-We first Fourier transform the \(U_b\)-term to \(k-\)space.
-In \(k-\)space, the diagonal contribution (to \(H_D\)) coming from this term is the single-particle self-energy \(-U_b\left(\hat n_{q \beta}\right)^2\) which can be made particle-hole symmetric in the form:
-\begin{equation}\begin{aligned}
-	-U_b\left(\tau_{q \beta}\right)^2
-\end{aligned}\end{equation}
-where \(q\) is the \(k-\)state being decoupled and \(\tau \equiv \hat n - 1/2\).
-In the initial state \(\ket{\Psi}_i\), we have \(\langle \hat n_{q\beta} \rangle = 1/2 \implies \tau_{q\beta} = 0\), so the contribution of \(U_b\) to that state is 0.
-For both hole excitations \(c_{q\beta}\ket{\Psi}_i\) as well as particle excitations \(c^\dagger_{q\beta}\ket{\Psi}_i\), the intermediate state energy lowers to \(-U_b/4\).
-
-The off-diagonal part is
-\begin{equation}\begin{aligned}
-	-\frac{U_b}{2}\sum_{kk^\prime\sigma}c^\dagger_{k\sigma}c_{k^\prime\sigma} + U_b \sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_1 \uparrow}c_{k_2 \uparrow} c^\dagger_{k^\prime_1 \downarrow}c_{k^\prime_2 \downarrow}
-\end{aligned}\end{equation}
-We ignore the potential scattering arising from the first term.
-
-\section{Renormalisation of the impurity energy levels}
-A single site has four degrees of freedom arising from the spin-degeneracy, and can be represented by the Hamiltonian
-\begin{equation}\begin{aligned}
-	H = \epsilon_0 \ket{0}\bra{0} + \epsilon_1 \sum_\sigma\ket{\sigma}\bra{\sigma} + \epsilon_2 \ket{2}\bra{2}
-\end{aligned}\end{equation}
-\(\ket{0},\ket{2}\) are the holon and doublon states, while \(\ket{\sigma}\) is the state where the site is singly-occupied by a particle of spin \(\sigma\).
-We will obtain the renormalisation to the energy levels \(\epsilon_0,\epsilon_1\) and \(\epsilon_2\), and thereby calculate the renormalisation in \(U\) and \(\eta\).
-This can be done by noting that \(\epsilon_1 = -\frac{U}{2}\), and \(\epsilon_2 = \eta\).
-A qualifier is, however, needed here.
-In the bare Hamiltonian, the energies of the doublon and holon states are negatives of each other, and this would correspond to requiring \(\epsilon_2 = -\epsilon_0\).
-This may not hold true under renormalisation, and the way we account for this is that at each step of the RG, we subtract a constant energy from the Hamiltonian so as to set the energy of the holon state to 0.
-This means that the energy of the singly-occupied and doublon states become \(\epsilon_1 - \epsilon_0\) and \(\epsilon_2 - \epsilon_0\).
-And since we have identified \(\epsilon_1\) and \(\epsilon_2\) as \(-\frac{U}{2}\) and \(\eta\) respectively, we can use \(\Delta U = -2\left(\Delta \epsilon_1 - \Delta \epsilon_0\right), \Delta \eta = \Delta \epsilon_2 - \Delta \epsilon_0 \).
-
-We need to look at three kinds of scattering vertices here: \(V^2\), \(J^2\) and \(K^2\).
-We will consider these processes one after another.
-We define \(n_j\) as the number of states being decoupled on each side of the Fermi surface, at the \(j^\text{th}\) RG step.
-In order to treat both spin and isospin exchanges democratically, we take \(\ket{\Psi}_i = \frac{1}{2}\left(\ket{0} + \ket{q\uparrow} + \ket{q\downarrow} + \ket{q\uparrow, q\downarrow}\right) \) as the \textit{initial} state for the scattering processes.
-The intermediate states \(\ket{\Psi}_\text{int}\) in the particle sector \(\left(c_{q\beta}\ket{\Psi}_i\right)\) and hole sector \(\left(c^\dagger_{q\beta}\ket{\Psi}_i\right)\) will then have both spin and isospin excitations which can couple with the corresponding impurity degree of freedom.
-We will assume that states  \(q > k_F~\left(\epsilon_q > 0\right) \) above the Fermi surface can have only particle excitations and states below the Fermi surface can only have hole excitations.
-The kinetic energy part \(\epsilon_q \tau_{q\beta}\) of \(H_D\) for \(\ket{\Psi}_i\) is then zero, whereas it is always \(D/2\) for \(\ket{\Psi}_\text{int}\).
-To demonstrate this for a typical \(q < k_F\), the hole excitation is \(c_{q \uparrow}\ket{\Psi}_i = \frac{1}{\sqrt 2}\left(\ket{0} + \ket{q \downarrow}\right)\).
-This has an isospin term in the form of the \textit{holon} and a spin term in the form of the down state.
-Since \(\tau_{q \uparrow} = -\frac{1}{2}\) in the excited state, the kinetic energy for \(\ket{\Psi}_\text{int}\) is \(\epsilon_q \tau_{q \uparrow} = \left(-D\right)\times\left(-\frac{1}{2}\right) = D/2\).
-
-The renormalisation arising from the first kind of terms, in the particle sector, is
-\begin{equation}\begin{aligned}
-	\sum_{q\beta}c^\dagger_{q\beta}c_{d\beta}\frac{V^2}{\omega - H_D}c^\dagger_{d\beta}c_{q\beta} = \sum_{q\beta}V^2 \hat n_{q\beta} \left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega - E_0} + \frac{\hat n_{d \overline\beta}}{\omega^\prime - E_1}\right) = V^2 n_j\sum_{\beta}\left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega_0 - E_0} + \frac{\hat n_{d \overline\beta}}{\omega_1 - E_1}\right)
-\end{aligned}\end{equation}
-\(q\) runs over the momentum states that are being decoupled at this RG step: \(|q| = \Lambda_j\).
-\(E_{1,0}\) are the diagonal parts of the Hamiltonian at \(\hat n_{d\overline \beta}=1,0\) respectively.
-We have \(\hat n_{d\beta}=1\) in the intermediate state because of the \(c^\dagger_{d\beta}\) in front of the Greens function.
-Applying \(c_{q\beta}\) on the initial state \(\ket{\Psi}_i\) leaves us with \(C^z_q = - \frac{1}{2}\) and \(s^z_q = \frac{1}{2}\overline\beta\).
-We also know that
-\begin{equation}\begin{aligned}
-	\hat n_{d\beta}=1,
-	\begin{cases}
-		\hat n_{d\overline\beta}=0 &\implies S_d^z = \frac{1}{2}\beta, C_d^z = 0, \epsilon_d\left(\hat n_{d\uparrow} - \hat n_{d \downarrow}\right)^2 = \epsilon_d\\	
-		\hat n_{d\overline\beta}=1 &\implies S_d^z = 0, C_d^z = \frac{1}{2}, \epsilon_d\left(\hat n_{d\uparrow} - \hat n_{d \downarrow}\right)^2 = 0
-	\end{cases}
-\end{aligned}\end{equation}
-Combining all this, we can write \(E_1 = \frac{D}{2} - \frac{K}{4}\) and \(E_0 = \frac{D}{2} + \epsilon_d - \frac{J}{4}\).
-In order to relate \(\omega_0\) with \(\omega_1\) with the common fluctuation scale \(\omega\) for the conduction electrons, we will replace these quantum fluctuation scales by the current renormalised values of the single-particle self-energy for the initial state from which we started scattering.
-For \(\hat n_{d\overline\beta}=0\), there is no additional self-energy because the impurity does not have any spin: \(\omega_0 = \omega\).
-For \(\hat n_{d\overline\beta} = 1\), we have an additional self-energy of \(\epsilon_d\) arising from the correlation on the impurity: \(\omega_1 = \omega + \epsilon_d\).
-Substituting the values of \(E_{0,1}\) and \(\omega_{0,1}\), we get
-\begin{equation}\begin{aligned}
-	\label{ren_ed_Vp}
-	V^2 n_j\sum_{\beta}\left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)
-\end{aligned}\end{equation}
-Performing a similar calculation for the hole sector gives the contribution:
-\begin{equation}\begin{aligned}
-	\label{ren_ed_Vh}
-	V^2 n_j\sum_{\beta}\hat n_{d\beta}\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right)
-\end{aligned}\end{equation}
-We now come to the second type of terms: spin-spin. We first look at the particle sector:
-\begin{equation}\begin{aligned}
-	\label{ren_ed_Jpp}
-	\frac{J^2}{4}\sum_{q\beta}c^\dagger_{d\overline\beta}c_{d\beta}c^\dagger_{q\beta}c_{-q\overline\beta} \frac{1}{\omega - H_D}c^\dagger_{d\beta}c_{d\overline\beta}c^\dagger_{q\overline\beta}c_{q\beta} = \frac{J^2}{4} n_j\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{\beta}\hat n_{d\overline\beta}\left( 1 - \hat n_{d\beta} \right)
-\end{aligned}\end{equation}
-The diagonal part in the denominator was simple to deduce in this case, because the nature of the scattering requires the spins \(S_d^z\) and \(\frac{\beta}{2}\left(\hat n_{q\beta} - \hat n_{q \overline\beta}\right)\) to be anti-parallel.
-This ensures that the intermediate state has an energy of \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\), and the quantum fluctuation scale is \(\omega^\prime = \omega + \epsilon_d\), such that \(\omega^\prime - E = \omega - \frac{D}{2} + \frac{J}{4}\).
-In the hole sector, we have
-\begin{equation}\begin{aligned}
-	\label{ren_ed_Jph}
-	\frac{J^2}{4} n_j\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{\beta}\hat n_{d\beta}\left( 1 - \hat n_{d\overline\beta} \right)
-\end{aligned}\end{equation}
-The final kind of scattering is the \(K^2\) type. Similar to the \(J^2\) term, we get the following contribution:
-\begin{equation}\begin{aligned}
-	\label{ren_ed_Kpp}
-	\frac{K^2}{4}\sum_{q\beta}c^\dagger_{q\beta}c^\dagger_{q\overline\beta}c_{d\overline\beta}c_{d\beta} \frac{1}{\omega - H_D}c^\dagger_{d\beta}c^\dagger_{d\overline\beta}c_{q\overline\beta}c_{q\beta} = \frac{K^2}{2} n_j\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} \left(1 - \hat n_{d \uparrow}\right) \left( 1 - \hat n_{d \downarrow} \right)
-\end{aligned}\end{equation}
-in the particle sector. This is again because \(E = \frac{D}{2} - \frac{K}{4}\) in the intermediate state and \(\omega^\prime = \omega\). In the hole sector, we get
-\begin{equation}\begin{aligned}
-	\label{ren_ed_Kph}
-	\frac{K^2}{2} n_j\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} \hat n_{d\uparrow}\hat n_{d \downarrow}~.
-\end{aligned}\end{equation}
-
-We now have all possible renormalisation to the impurity energy \(\epsilon_d\).
-To actually compute the renormalisation, we will first calculate the renormalisation in the energies \(\epsilon_0, \epsilon_1\) and \(\epsilon_2\) of the impurity states \(\ket{\hat n_d = 0}, \ket{\hat n_d = 1}, \ket{\hat n_d = 2}\) respectively.
-The renormalisation of these states are given by the following terms:
-\begin{itemize}
-	\item \(\Delta \epsilon_0\) is given by the renormalisation of the term \(\left(1 - \hat n_{d\uparrow}\right)\left(1 - \hat n_{d \downarrow}\right)\)
-	\item \(\Delta \epsilon_1\) is given by the renormalisation of either \(\left(1 - \hat n_{d\uparrow}\right)\hat n_{d \downarrow}\) or \(\left(1 - \hat n_{d\downarrow}\right)\hat n_{d \uparrow}\)
-	\item \(\Delta \epsilon_2\) is given by the renormalisation of \(\hat n_{d\uparrow}\hat n_{d \downarrow}\)
-\end{itemize}
-From eqs.~\ref{ren_ed_Vp}, \ref{ren_ed_Vh}, \ref{ren_ed_Jpp}, \ref{ren_ed_Jph}, \ref{ren_ed_Kpp} and \ref{ren_ed_Kph}, we write
-\begin{equation}\begin{aligned}
-	\Delta \epsilon_0 = \Delta \epsilon_2 = \frac{2V^2 n_j}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}} + \frac{K^2 n_j/2}{\omega - \frac{D}{2} + \frac{K}{4}}, && \Delta \epsilon_1 = \frac{2V^2 n_j}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} + \frac{J^2 n_j/2}{\omega - \frac{D}{2} + \frac{J}{4}}
-\end{aligned}\end{equation}
-We had started with a particle-hole symmetric Hamiltonian \((2\epsilon_d + U = 0)\); the fact that \(\Delta \epsilon_0 = \Delta \epsilon_2\) means the RG transformation has preserved that symmetry.
-The renormalisation of \(\epsilon_d\) is simply the renormalisation in the energy difference between the singly-occupied and vacant impurity levels: \(\Delta \epsilon_d = \Delta \epsilon_1 - \Delta \epsilon_0\).
-This gives our first RG equation:
-\begin{equation}\begin{aligned}
-	\Delta \epsilon_d = 2V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + \frac{n_j}{2}\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right)
-\end{aligned}\end{equation}
-
-\subsection{Renormalisation of the hybridisation \(V\)}
-Renormalisation of \(V\) happens through two kinds of processes: \(VJ\) and \(VK\).
-In order words, the two vertices involve one single-particle scattering and one spin or isospin exchange respectively.
-We first look at the vertices that involve a spin-exchange scattering.
-
-Within spin-exchange, the scattering can be either via \(S_d^z\) or through \(S_d^\pm\). For the first kind, we have the following contribution in the particle sector:
-\begin{equation}\begin{aligned}
-	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{4}J \sum_{k} \left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) c^\dagger_{k\beta}c_{q\beta} = \frac{1}{4}V J n_j \frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right)\sum_{k\beta} \left(1 - \hat n_{d\overline\beta}\right) c_{d\beta}c^\dagger_{k\beta}
-\end{aligned}\end{equation}
-The transformation from \(\frac{1}{\omega - H_D}\) to \(\frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right)\) is made so that we can account for both the initial state and the final state energies through the two fluctuation scales \(\omega^\prime_1\) and \(\omega_2^\prime\) respectively; we calculate the denominators for both the initial and final states, and then take the mean of the two (hence the factor of half in front).
-This was not required previously because in the earlier scattering processes, the impurity returned to its initial state at the end, at least in terms of \(\epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right)^2 \), and so we had \(\omega_1^\prime = \omega_2^\prime = \omega^\prime\).
-
-Note that the \(c_{d\beta}\) in front of the Greens function resulted in \(\left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) \to \left(1 - \hat n_{d\overline\beta}\right)\).
-The intermediate state is characterised by \(\hat n_{d\beta} = 1 - \hat n_{d \overline \beta} = 1\), which means that \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\).
-Moreover, the initial state gives \(\omega_1^\prime = \omega + \epsilon_d\) while the final state gives \(\omega^\prime_2 = \omega\).
-Therefore, the renormalisation becomes
-\begin{equation}\begin{aligned}
-	-\frac{n_j}{4}V J \frac{1}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right)\sum_{k\beta}\left(1 - \hat n_{d\overline\beta}\right) c^\dagger_{k\beta} c_{d\beta}
-\end{aligned}\end{equation}
-One can generate another such process by exchanging the single-particle process and the spin-exchange process:
-\begin{equation}\begin{aligned}
-	\sum_{q\beta} \frac{1}{4}J \sum_{k} \left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) c^\dagger_{q\beta}c_{k\beta} \frac{1}{\omega - H_D} V c^\dagger_{d\beta} c_{q\beta}
-\end{aligned}\end{equation}
-This is simply the Hermitian conjugate of the previous contribution. Combining this with the previous then gives
-\begin{equation}\begin{aligned}
-	-\frac{n_j}{8}V J \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta}\left(1 - \hat n_{d\overline\beta}\right)\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-
-We now consider the spin-exchange processes involving \(S_d^\pm\):
-\begin{equation}\begin{aligned}
-	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{2}J \sum_{k} c^\dagger_{d\beta}c_{d\overline\beta} c^\dagger_{k\overline\beta}c_{q\beta} = \frac{1}{2}V J n_j \frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) c_{d\overline\beta}c^\dagger_{k\overline\beta}
-\end{aligned}\end{equation}
-We again have \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4},\omega_1^\prime = \omega + \epsilon_d\) and \(\omega_2^\prime = \omega\), which gives
-\begin{equation}\begin{aligned}
-	-\frac{1}{4}V J n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)c^\dagger_{k\overline\beta} c_{d\overline\beta}
-\end{aligned}\end{equation}
-Combining this with the Hermitian conjugate obtained from exchanging the processes gives
-\begin{equation}\begin{aligned}
-	-\frac{1}{4}V J n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)\left(c^\dagger_{k\overline\beta} c_{d\overline\beta} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-
-The contributions from the hole sector are obtained making the transformation \(\hat n_{d\overline\beta} \to 1 - \hat n_{d\overline\beta}\) on the particle sector contributions.
-The total renormalisation to \(V\) from \(VJ\) processes are
-\begin{equation}\begin{aligned}
-	-\frac{3n_j}{8}V J \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-
-We now look at the \(VK\) processes. The first one is
-\begin{equation}\begin{aligned}
-	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{4}K \sum_{k} \left(\hat n_{d} - 1\right) c^\dagger_{k\beta}c_{q\beta} = -\frac{1}{8}V K n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \hat n_{d\overline \beta}c^\dagger_{k\beta}c_{d\beta}
-\end{aligned}\end{equation}
-The exchanged process again gives the Hermitian conjugate, so the combined contribution is
-\begin{equation}\begin{aligned}
-	-\frac{1}{8}V K n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \hat n_{d\overline \beta} \left(c^\dagger_{k\beta}c_{d\beta} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-
-The isospin-flip vertex gives
-\begin{equation}\begin{aligned}
-	\sum_{q\beta} V c^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{2}K \sum_{k} c^\dagger_{d\beta}c^\dagger_{d\overline\beta} c_{k\overline\beta} c_{q\beta} = \frac{1}{4}K V n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) c^\dagger_{d\overline\beta}c_{k\overline\beta}~.
-\end{aligned}\end{equation}
-Combining with Hermitian conjugate gives
-\begin{equation}\begin{aligned}
-	\frac{1}{4}K V n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) \left(c^\dagger_{d\overline\beta}c_{k\overline\beta} + \text{h.c.}\right)~.
-\end{aligned}\end{equation}
-
-After obtaining the hole sector contributions, the total renormalisation from \(VK\) processes is
-\begin{equation}\begin{aligned}
-	-\frac{3n_j}{4}V K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)~.
-\end{aligned}\end{equation}
-
-The RG equation for \(V\) is
-\begin{equation}\begin{aligned}
-	\Delta V = -\frac{3n_j V}{8}\left[J\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)\right]
-\end{aligned}\end{equation}
-
-\subsection{Renormalisation of the exchange couplings \(J\) and \(K\)}
-We will just note the renormalisation in \(J^z\), which will be equal to \(J^\pm\) due to spin-rotation symmetry.
-The terms that renormalise \(J^z\) are of the form \(S_d^\pm S_d^\mp\).
-In the particle sector, we have
-\begin{equation}\begin{aligned}
-	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^\pm c^\dagger_{q\mp}c_{k^\prime\pm} \frac{1}{\omega - H_D}S_d^\mp c^\dagger_{k\pm}c_{q\mp} = -n_j \frac{1}{4}J^2 \left(\frac{1}{2} \pm S_d^z\right) \sum_{kk^\prime}c^\dagger_{k \pm}c_{k\pm} \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
-The denominator is determined using \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\) and \(\omega^\prime = \omega + \epsilon_d\).
-In the hole sector, we similarly have
-\begin{equation}\begin{aligned}
-	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^\mp c^\dagger_{k\pm}c_{q\mp} \frac{1}{\omega - H_D}S_d^\pm c^\dagger_{q\mp}c_{k^\prime\pm} = n_j \frac{1}{4}J^2 \left(\frac{1}{2} \mp S_d^z\right) \sum_{kk^\prime}c^\dagger_{k \pm}c_{k\pm} \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
-Adding all four expressions and dropping the constant part, we get
-\begin{equation}\begin{aligned}
-	-n_j \frac{1}{2}J^2 S_d^z \sum_{kk^\prime}\left(c^\dagger_{k \uparrow}c_{k^\prime \uparrow} - c^\dagger_{k \downarrow}c_{k^\prime \downarrow}\right) \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
-We can now directly read off the RG equation for \(J\):
-\begin{equation}\begin{aligned}
-	\Delta J = -\frac{n_j J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
-\end{aligned}\end{equation}
-
-Since the spin and charge degrees of freedom are treated on an equal footing in the model, we obtain the RG equation for \(K\) by simply changing \(J \to K\):
-\begin{equation}\begin{aligned}
-	\Delta K = -\frac{n_j K^2}{\omega - \frac{D}{2} + \frac{K}{4}}
-\end{aligned}\end{equation}
-
-\section{\(U_b\)-included terms}
-
-We first Fourier transform the \(U_b\)-term to \(k-\)space.
-In \(k-\)space, the diagonal contribution (to \(H_D\)) coming from this term is the single-particle self-energy \(-U_b\left(\hat n_{q \beta}\right)^2\) which can be made particle-hole symmetric in the form:
-\begin{equation}\begin{aligned}
-	-U_b\left(\tau_{q \beta}\right)^2
-\end{aligned}\end{equation}
-where \(q\) is the \(k-\)state being decoupled and \(\tau \equiv \hat n - 1/2\).
-In the initial state \(\ket{\Psi}_i\), we have \(\langle \hat n_{q\beta} \rangle = 1/2 \implies \tau_{q\beta} = 0\), so the contribution of \(U_b\) to that state is 0.
-For both hole excitations \(c_{q\beta}\ket{\Psi}_i\) as well as particle excitations \(c^\dagger_{q\beta}\ket{\Psi}_i\), the intermediate state energy lowers to \(-U_b/4\).
-
-The off-diagonal part is
-\begin{equation}\begin{aligned}
-	-\frac{U_b}{2}\sum_{kk^\prime\sigma}c^\dagger_{k\sigma}c_{k^\prime\sigma} + U_b \sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_1 \uparrow}c_{k_2 \uparrow} c^\dagger_{k^\prime_1 \downarrow}c_{k^\prime_2 \downarrow}
-\end{aligned}\end{equation}
-We ignore the potential scattering arising from the first term.
-
-\subsection{Renormalisation of \(U_b\)}
-\(U_b\) can renormalise only via itself. The relevant renormalisation term in the particle sector is
-\begin{equation}\begin{aligned}
-	U_b^2 \sum_{q\beta}\sum_{k_1,k_2,k_3,k_1^\prime,k_2^\prime,k_3^\prime} c^\dagger_{q\beta}c_{k_1\beta}c^\dagger_{k_3\overline\beta}c_{k_1^\prime\overline\beta}\frac{1}{\omega - H_D}c^\dagger_{k_2^\prime\overline\beta}c_{k_3^\prime\overline\beta}c^\dagger_{k_2\beta}c_{q\beta}
-\end{aligned}\end{equation}
-In order to renormalise \(U_b\), we need to contract one more pair of momenta.
-There are two choices.
-The first is by setting \(k_3 = k_3^\prime = q\).
-The two internal states, then, are \(q\beta\) and \(q\overline\beta\).
-As discussed above, the intermediate state energy is \(-U_b/4\).
-We therefore have
-\begin{equation}\begin{aligned}
-	\frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c_{k_1\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2^\prime\overline\beta}c^\dagger_{k_2\beta} = \frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_2^\prime\overline\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
-\end{aligned}\end{equation}
-Another way to contract the momenta is by setting \(k_1^\prime = k_2^\prime = q\), which gives a renormalisation of
-\begin{equation}\begin{aligned}
-	\frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c_{k_1\beta}c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta} = -\frac{U_b^2 n_j}{\omega - D/2}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
-\end{aligned}\end{equation}
-The two contributions cancel each other. The same cancellation happens in the hole sector as well.
-
-\subsection{Renormalisation of \(U\)}
-\(U_b\) does not have any new renormalisation term on account of \(U_b\). \(U_b\) does however modify the existing RG equation for \(U\), by shifting the denominator. The existing RG equation is
-\begin{equation}\begin{aligned}
-	\Delta U &= -4V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) - n_j\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right)~.
-\end{aligned}\end{equation}
-On accounting for the contribution of \(U_b\) to the denominator, we get
-\begin{equation}\begin{aligned}
-	\Delta U &= -4V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} - \epsilon_d + \frac{J}{4}}\right) - n_j\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right)~.
-\end{aligned}\end{equation}
-
-\subsection{Renormalisation of \(V\)}
-The single-particle  hybridisation \(V\) renormalises through terms of \(V U_b\) and \(U_b V\) kind. The first term gives
-\begin{equation}\begin{aligned}
-	&\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{k\beta} \hat n_{q\overline\beta} \frac{1}{\omega - H_D} c^\dagger_{d\beta}c_{q\beta} \\
-	&= n_jU_b V\sum_{k\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_1 - E_1} + \frac{1}{\omega^\prime_1 - E_1}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_0 - E_0} + \frac{1}{\omega_0^\prime - E_0}\right)\right] c^\dagger_{d\beta}
-\end{aligned}\end{equation}
-\(E_1\) and \(E_0\) are the intermediate state energies for \(\hat n_{d\overline\beta}=1\) and 0 respectively.
-\(\omega_{1,0}\) are the quantum fluctuation scales for the corresponding initial states.
-\(\omega^\prime_{1,0}\) are the fluctuation scales for the corresponding final states.
-The intermediate energies are \(E_1 = D/2 - U_b/4 - K/4,~ ~ ~ E_0 = D/2 - U_b/4 - U/2 - J/4\).
-The fluctuation scales are \(\omega_1 = \omega - U/2= \omega_0^\prime,~ ~ ~ \omega_1^\prime = \omega = \omega_0\).
-Substituting these gives
-\begin{equation}\begin{aligned}
-	-n_jU_b V\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
-+\left.
-\frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
-\end{aligned}\end{equation}
-
-The second term is of the form
-\begin{equation}\begin{aligned}
-	\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{d\beta} \frac{1}{\omega - H_D} \hat n_{q\overline\beta} c^\dagger_{k\beta}c_{q\beta}
-\end{aligned}\end{equation}
-and this is just the Hermitian conjugate of the previous term, so these two terms together lead to
-\begin{equation}\begin{aligned}
-	-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
-	+ \left.\frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
-\end{aligned}\end{equation}
-
-In the hole sector, we have
-\begin{equation}\begin{aligned}
-	&\sum_{q\beta}\sum_{k}U_b V \hat n_{q\overline\beta} c^\dagger_{k\beta}c_{q\beta} \frac{1}{\omega - H_D} c^\dagger_{q\beta}c_{d\beta}\\
-	&-\sum_{q\beta}\sum_{k}U_b V \left(1 - \hat n_{q\overline\beta}\right) c^\dagger_{k\beta}c_{q\beta} \frac{1}{\omega - H_D} c^\dagger_{q\beta}c_{d\beta}\\
-	&= -n_jU_b V\sum_{k\beta} c^\dagger_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_1 - E_1} + \frac{1}{\omega^\prime_1 - E_1}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_0 - E_0} + \frac{1}{\omega_0^\prime - E_0}\right)\right] c_{d\beta}
-\end{aligned}\end{equation}
-\(E_1 = D/2 - U_b/4 - U/2 - J/4,~ ~ ~ E_0 = D/2 - U_b/4 - K/4\).
-The fluctuation scales are \(\omega_1 = \omega = \omega_0^\prime,~ ~ ~ \omega_1^\prime = \omega - U/2 = \omega_0\).
-Substituting these gives
-\begin{equation}\begin{aligned}
-	-n_jU_b V\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{1 - \hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
-+\left. \frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
-\end{aligned}\end{equation}
-The other term, obtained by exchanging \(V\) and \(U_b\), gives the Hermitian conjugate, so the overall contribution from the hole sector is the same as the total contribution from the particle sector, but with \(\hat n_{d\overline\beta} \to 1 - \hat n_{d\overline\beta}\).
-Combining both the sectors, we get
-\begin{equation}\begin{aligned}
-	-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \frac{1}{2}\left[\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
-+\left. \left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
-\end{aligned}\end{equation}
-
-Combining with the already existing RG equations, the complete RG equation for \(V\) becomes
-\begin{equation}\begin{aligned}
-	\Delta V =& -\frac{3n_j V}{8}\left[\left(\frac{J}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} + \frac{J}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}}\right) + K \left(\frac{K}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{K}{\omega - \frac{D}{2} + \frac{U_b}{4} - \frac{U}{2} + \frac{K}{4}}\right)\right]\\
-		 &-\frac{n_jU_b}{2}\left[\left(\frac{V}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) + \left(\frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]\\
-		 &=-\frac{n_j V}{8}\left[\left(\frac{3J + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} + \frac{3J + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}}\right) + \left(\frac{3K + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{3K + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} - \frac{U}{2} + \frac{K}{4}}\right)\right]
-\end{aligned}\end{equation}
-
-\subsection{Renormalisation of \(J\) and \(K\)}
-We will track the entire renormalisation purely from that of \(J^+\), by virtue of the SU(2) symmetry. \(J^+\) renormalises through the \(J U_b\) terms. One of the terms is
-\begin{equation}\begin{aligned}
-	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} S_d^+ c^\dagger_{q \downarrow} c_{k \uparrow} \frac{1}{\omega - H_D} \hat n_{q \uparrow} c^\dagger_{k^\prime \downarrow}c_{q \downarrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
-\end{aligned}\end{equation}
-The factor of half in front is the same half factor that appears in front of the \(S_1^+ S_2^-, S_1^-S_2^+\) terms when we rewrite \(\vec{S}_1\cdot\vec{S}_2\) in terms of \(S^z, S^\pm\).
-Another term is obtained by switching \(J\) and \(U_b\):
-\begin{equation}\begin{aligned}
-	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \downarrow} c^\dagger_{q \uparrow} c_{k \uparrow} \frac{1}{\omega - H_D}S_d^+ c^\dagger_{k^\prime \downarrow} c_{q \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
-\end{aligned}\end{equation}
-
-The corresponding terms in the hole sector are
-\begin{equation}\begin{aligned}
-	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{q \uparrow} \frac{1}{\omega - H_D} \hat n_{q \downarrow} c^\dagger_{q \uparrow}c_{k \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \uparrow} c^\dagger_{k^\prime \downarrow} c_{q \downarrow} \frac{1}{\omega - H_D}S_d^+ c^\dagger_{q \downarrow} c_{k \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
-\end{aligned}\end{equation}
-
-Adding all these terms and combining with the existing RG equation, we get the updated RG equation for \(J\):
-\begin{equation}\begin{aligned}
-	\Delta J = -J n_j\frac{4 U_b + J}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}}
-\end{aligned}\end{equation}
-
-We will follow the same strategy with \(K\) - we will calculate the renormalisation in \(K^+\). The first term is
-\begin{equation}\begin{aligned}
-	\frac{1}{2} K U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \downarrow} c^\dagger_{q \uparrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D} C_d^+ c_{k \downarrow} c_{q \uparrow} = -\frac{1}{2}\frac{K U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}} \sum_{k,k^\prime} C_d^+ c_{k \downarrow} c_{k^\prime \uparrow}
-\end{aligned}\end{equation}
-The second term in the same sector is obtained by flipping the spins of \(k\) and \(q\):
-\begin{equation}\begin{aligned}
-	\frac{1}{2} K U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \uparrow} c^\dagger_{q \downarrow}c_{k^\prime \downarrow} \frac{1}{\omega - H_D} C_d^+ c_{q \downarrow} c_{k \uparrow} = -\frac{1}{2}\frac{K U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}} \sum_{k,k^\prime} C_d^+ c_{k \downarrow} c_{k^\prime \uparrow}
-\end{aligned}\end{equation}
-
-The terms in the hole sector give identical contributions. The RG equation for \(K\) is
-\begin{equation}\begin{aligned}
-	\Delta K = -K n_j\frac{4 U_b + K}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}}
-\end{aligned}\end{equation}
-
-\chapter{Zero temperature Greens function in frequency domain}
-
-\label{appx-spectral-func}
-The impurity retarded Green's function (assuming the Hamiltonian to be time-independent, which it is) is defined as
-\begin{equation}\begin{aligned}
-	G_{dd}^\sigma(t) = -i\theta(t) \left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right>
-\end{aligned}\end{equation}
-where the average \(\left< \right>\) is over a canonical ensemble at temperature \(T\), and \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in.
-The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term.
-What follows is a standard calculation where we write the Green's function in the Lehmann-Kallen representation.
-The ensemble average for an arbitrary operator \(\hat M\) can be written in terms of the exact eigenstates of the fixed point Hamiltonian:
-\begin{equation}\begin{aligned}
-	H^* \ket{n} &= E_n^* \ket{n}, ~ ~ ~\left<\hat M \right> &\equiv \frac{1}{Z}\sum_n \bra{n} \hat M \ket{n} e^{-\beta E_n^*}
-\end{aligned}\end{equation}
-where \(Z = \sum_n e^{-\beta E_n^*}\) is the fixed point partition function and \(\left\{ \ket{n} \right\} \) is the set of eigenfunctions of the fixed point Hamiltonian. We can therefore write
-\begin{equation}\begin{aligned}
-	&\left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right> \\
-	&= \frac{1}{Z}\sum_{m}e^{-\beta E_m}\bra{m}\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\} \ket{m}\\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( \mathcal{O}_{\sigma}(t)\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma}(t)\right) \ket{m} && \left[\sum_n \ket{n}\bra{n} = 1\right]  \\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\right) \ket{m}\\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\left( e^{i\left( E_m - E_n \right)  t}\bra{m}\mathcal{O}_{\sigma}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} \ket{m} + e^{i\left( E_n - E_m \right)  t}\bra{m}\mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma} \ket{m}\right)\\
-	&= \frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
-\end{aligned}\end{equation}
-The time-domain impurity Green's function can thus be written as (this is the so-called Lehmann-Kallen representation)
-\begin{equation}\begin{aligned}
-	G_{dd}^\sigma = -i\theta(t)\frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
-\end{aligned}\end{equation}
-We are interested in the frequency domain form.
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega) &= \int_{-\infty}^\infty dt e^{i \omega t}G_{d d}^\sigma(t) \\
-			       &= \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t}
-\end{aligned}\end{equation}
-To evaluate the time-integral, we will use the integral representation of the Heaviside function:
-\begin{equation}\begin{aligned}
-	\theta(t) = \frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty \frac{1}{x- i\eta}e^{ixt}dx
-\end{aligned}\end{equation}
-With this definition, the integral in \(G_{dd}^\sigma(\omega)\) becomes
-\begin{equation}\begin{aligned}
-	\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t} &= \left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta}\int_{-\infty}^\infty dt e^{i\left( \omega + E_m - E_n + x\right)t} \\
-									     &=\left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta} 2\pi \delta\left( \omega + E_m - E_n + x\right) \\
-									     &=\left(-i\right)\frac{1}{i}\lim_{\eta \to 0^+} \frac{-1}{\omega + E_m - E_n- i\eta} \\
-									     &=\frac{1}{\omega + E_m - E_n} \\
-\end{aligned}\end{equation}
-The frequency-domain Green's function is thus
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
-\end{aligned}\end{equation}
-The zero temperature Green's function is obtained by taking the limit of \(\beta \to \infty\).
-In both the partition function as well as inside the summation, the only term that will survive is the exponential of the ground state energy \(E_0\).
-\begin{equation*}\begin{aligned}
-	Z \equiv \sum_m e^{-\beta E_m} \implies \lim_{\beta \to \infty}Z = d_0 e^{-\beta E_0}, && E_0 \equiv \text{min}\left\{ E_n \right\} 
-\end{aligned}\end{equation*}
-where \(d_0\) is the degeneracy of the ground state. The Greens function then simplifies to
-\begin{equation}\begin{aligned}
-	\label{Gf_lk}
-	G_{d d}^\sigma(\omega, \beta \to \infty) &= \frac{1}{d_0e^{-\beta E_0}}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left[e^{-\beta E_m}\delta_{E_m, E_0} + e^{-\beta E_n}\delta_{E_n, E_0}\right]\frac{1}{\omega + E_m - E_n}\\
-						 &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n}\right]\\
-\end{aligned}\end{equation}
-The label 0 sums over all states \(\ket{0}\) with energy \(E_0\).
-The spectral function is the imaginary part of this Green's function.
-To extract the imaginary part, we insert an infinitesimal imaginary part in the denominator:
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega, \eta) = \frac{1}{d_0}\lim_{\eta \to 0^-}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n + i\eta} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n + i\eta}\right]\\
-\end{aligned}\end{equation}
-The spectral function at zero temperature can then be written as
-\begin{equation}\begin{aligned}
-	\mathcal{A(\omega)} &= -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] \\
-			    &= \frac{1}{d_0}\frac{1}{\pi}\text{ Im }\left[\lim_{\eta \to 0^-}\sum_{n,0}\left(\frac{-i\eta ||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2}{\left(\omega + E_0 - E_n\right)^2 + \eta^2} + \frac{-i\eta ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2}{\left(\omega - E_0 + E_n\right)^2 + \eta^2}\right)\right]\\
-			    &= \frac{1}{d_0}\frac{1}{\pi}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\pi\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\pi\delta\left(\omega - E_0 + E_n\right)\right]\\
-			    &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]\\
-\end{aligned}\end{equation}
-
-\chapter{Some analytic results for the Hubbard dimer and the Hubbard model}
-\section{Spectrum of the Hubbard dimer}
-Here we document the spectrum of the Hubbard dimer Hamiltonian in eqs.~\ref{hubb_dimer}.
-\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-	eigenstate & symbol & eigenvalue \\
-	\hline
-	$\ket{0,0}$ & $\ket{0}$ & \( \frac{U^H}{2}\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,0} \pm \ket{0,\sigma}\right)$ & $\ket{0\sigma_\pm}$ & \(\mp t^H\)\\
-	$\ket{\sigma,\sigma}$ & $\ket{\sigma\sigma}$ & \( -\frac{U^H}{2}\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow}\right)$ & $\ket{ST}$ & \( -\frac{U^H}{2}\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2}\right)$ & $\ket{CS}$ & \( \frac{U^H}{2}\)\\
-	$a_1(U^H, t^H) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_2(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{-}$ & \(-\frac{1}{2}\Delta(U^H, t^H)\)\\
-	$-a_2(U^H, t^H) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{+}$ & \(\frac{1}{2}\Delta(U^H, t^H)\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,2} \pm \ket{2,\sigma}\right)$ & $\ket{2\sigma_\pm}$ & \(\pm t^H\)\\
-	$\ket{2,2}$ & $\ket{4}$ & \( \frac{U^H}{2}\)\\
-\hline
-	\end{tabular}
-	\captionof{table}{Spectrum of Hubbard dimer at half-filling}
-	\label{hubb_dim_spectrum}
-\end{center}
-
-\section{Greens function of Hubbard model in the atomic limit}
-\label{atomic limit}
-The atomic limit is described by the Hamiltonian \(H = -\frac{U}{2}\sum_i\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\).
-Since the Hamiltonian has decoupled into \(\sum_i \equiv N\) single-site Hamiltonians, we can easily write down the retarded Greens function for a single site by identifying the ground state configuration of a site.
-The ground states are of course \(\ket{\Psi}_i = \ket{\uparrow},\ket{\downarrow}\), in the absence of any symmetry-breaking.
-The finite temperature retarded Greens function in the time domain is given by
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(T,t) = -i\theta(t) \frac{1}{Z}\sum_n e^{-\beta E_n} \braket{n | \left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} | n}
-\end{aligned}\end{equation}
-where \(n\) labels the eigenstates of the \(H\). At \(T \to 0\), only the ground states will survive in the exponential and the partition function \(Z\), such that the formula then reduces to
-\begin{equation}\begin{aligned}
-G_{i,\sigma}(T \to 0,t) = -i\theta(t)\braket{GS | \left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} | GS}
-\end{aligned}\end{equation}
-Since the Hamiltonian is simple, we can compute the time-dependent operator \(c_{i\sigma}(t) = e^{iH t} c_{i\sigma} e^{-iHt}\). Using the BCH lemma, we have
-\begin{equation}\begin{aligned}
-	e^{iH t} c_{i\sigma} e^{-iHt} = \sum_{n=0}^\infty \left(it\right)^n \frac{1}{n!}\left[H,c_{i\sigma}\right]_n
-\end{aligned}\end{equation}
-where \(\left[H,c_{i\sigma}\right]_n = \left[H,\left[H,c_{i\sigma}\right]_{n-1}\right],\left[H,c_{i\sigma}\right]_0=c_{i\sigma}\). The first two non-trivial commutators are
-\begin{equation}\begin{aligned}
-	\left[H, c_{i\sigma}\right]_1 = -U \tau_{i\overline\sigma}c_{i\sigma},~ ~\text{and} ~~\left[H, c_{i\sigma}\right]_2 = \frac{1}{4}U^2 c_{i\sigma}~,
-\end{aligned}\end{equation}
-such that
-\begin{equation}\begin{aligned}
-	e^{iH t} c_{i\sigma} e^{-iHt} =& \left[c_{i\sigma} + \frac{i^2 t^2}{2!}\frac{U^2}{2^2} c_{i\sigma} + \frac{i^4 t^4}{4!}\frac{U^4}{2^4} c_{i\sigma} + \ldots\right] + \left[- \frac{it}{1!}U\tau_{i\overline\sigma}c_{i\sigma} - \frac{i^3 t^3}{3!}\frac{U^3}{4}\tau_{i\overline\sigma}c_{i\sigma} + \ldots \right]\\
-				       &= c_{i\sigma} \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] 
-\end{aligned}\end{equation}
-Using this, we can write
-\begin{equation}\begin{aligned}
-	\left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} = \left\{c_{i\sigma},c^\dagger_{i\sigma}\right\} \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] = \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right]
-\end{aligned}\end{equation}
-and the Greens function becomes
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(T \to 0,t) = -i\theta(t) \braket{GS | \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] | GS} = -i\theta(t)\left[\cos \frac{Ut}{2} - 2i\sin \frac{Ut}{2} \left<\tau_{i\overline\sigma} \right>\right]
-\end{aligned}\end{equation}
-We now Fourier transform to frequency domain:
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(\omega) = -i\int_{0}^\infty \mathrm{dt} e^{i\omega t}\left[\cos \frac{Ut}{2} - 2i\sin \frac{Ut}{2} \left<\tau_{i\overline\sigma} \right>\right] = \frac{1 + \left<\tau_{i\overline\sigma }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i\overline\sigma}\right>}{\omega + \frac{U}{2}}
-\end{aligned}\end{equation}
-The spin-total Greens function for the site \(i\) is
-\begin{equation}\begin{aligned}
-	\label{atomic_limit_gf}
-	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 + \left<\tau_{i }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i}\right>}{\omega + \frac{U}{2}}
-\end{aligned}\end{equation}
-At half-filling, we have \(\tau_i = 1\).
-\section{Local Greens function for the Hubbard dimer}
-From the spectral representation, we have the following expression for the local Greens function for the Hubbard dimer at site $0$:
-\begin{equation}\begin{aligned}
-	G_{D,00}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}c_{i\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
-\end{aligned}\end{equation}
-$m,n$ sum over the exact eigenstates.
-$E_m, E_n$ are the corresponding energies.
-We are interested in teh $T \to 0$ Greens function.
-In that limit, all exponentials except that for the ground state $E_{gs}$ will die out.
-The exponential inside the summation will then cancel the exponential in the partition function.
-\begin{equation}\begin{aligned}
-	G_{D,00}^\sigma(\omega, T \to 0) &= \sum_{n}\left[||\bra{GS}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
-					&= \sum_{n}\left[||\bra{n}c^\dagger_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
-\end{aligned}\end{equation}
-
-The ground state $\ket{GS}$ is just the state $\ket{-}$ in the table \ref{hubb_dim_spectrum}. We will choose to look at $\sigma = \uparrow`$. Then,
-\begin{equation}\begin{aligned}
-	c_{1\uparrow}\ket{-} &= \frac{a_1}{\sqrt 2}\ket{0, \downarrow} + \frac{a_2}{\sqrt 2}\ket{\downarrow,0}\\
-	c^\dagger_{1\uparrow}\ket{-} &= -\frac{a_1}{\sqrt 2}\ket{2, \uparrow} + \frac{a_2}{\sqrt 2}\ket{\uparrow,2}\\
-\end{aligned}\end{equation}
-The set of states $\ket{n}$ that give non-zero inner product $\ket{GS}$ are therefore
-\begin{equation}\begin{aligned}
-	\left\{ \ket{n} \right\} &= \ket{0\downarrow_\pm}\\
-	||\bra{n}c_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left(a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \pm 2a_1a_2\right)\\
-	\left\{ E_n \right\} &= \mp t
-\end{aligned}\end{equation}
-for the second inner product, and
-\begin{equation}\begin{aligned}
-	\left\{\ket{n}\right\} &= \ket{2\uparrow_\pm}\\
-	||\bra{n}c^\dagger_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left( a_2 \mp a_1 \right)^2 = \frac{1}{4}\left(1 \mp 2a_1a_2\right)\\
-	\left\{ E_n \right\} &= \pm t
-\end{aligned}\end{equation}
-for the first. The Greens function is therefore
-\begin{equation}\begin{aligned}
-	\label{dimer_local_G}
-	G_{D,00}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(t - \frac{\Delta}{2}\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(t + \frac{\Delta}{2}\right) ^2} = G_{D,00}^\downarrow(\omega, T \to 0)~.
-\end{aligned}\end{equation}
-In the atomic limit $(t=0)$, the Greens function simplifies to
-\begin{equation}\begin{aligned}
-	G_{D,00}^\uparrow(\omega, T \to 0) \bigg\vert_\text{atomic} = \frac{\omega}{\omega^2 - \frac{1}{4}U^2}
-\end{aligned}\end{equation}
-In the atomic limit, the singly-occupied state has zero energy:
-\begin{equation}\begin{aligned}
-	E_1(t=0) = \bra{1,0}\left(U \tau_{0 \uparrow}\tau_{0 \downarrow} + U \tau_{1 \uparrow}\tau_{1 \downarrow}\right) \ket{1,0} = 0
-\end{aligned}\end{equation}
-We can write the atomic limit Greens function in terms of this energy and the self energy:
-\begin{equation}\begin{aligned}
-	G_{D,00}^\uparrow(\omega, T \to 0) \bigg\vert_\text{atomic} = \frac{1}{\omega - E_1(t=0) - \Sigma(t=0)} = \frac{1}{\omega - 0 -\frac{U^2}{4\omega}}
-\end{aligned}\end{equation}
-The self energy in the atomic limit can be read off as 
-\begin{equation}\begin{aligned}
-	\label{dimer_selfenergy}
-\Sigma(t=0) = \frac{U^2}{4\omega}
-\end{aligned}\end{equation}
-The site local spectral function can also be calculated from the local Greens function:
-\begin{eqnarray}
-A(0\uparrow, \omega) &=& - \frac{1}{\pi}\text{Im }G_{D,00}^\uparrow(\omega)\nonumber\\
-			     &=& \left( \frac{1}{4} - \frac{t}{\Delta} \right)\left[\delta(\omega - \frac{1}{2}\Delta - t) + \delta(\omega + \frac{1}{2}\Delta + t)\right]\nonumber\\ 
-			     &&+ \left( \frac{1}{4} + \frac{t}{\Delta} \right) \left[\delta(\omega - \frac{1}{2}\Delta + t) + \delta(\omega + \frac{1}{2}\Delta - t)\right]\\ 
-			     &=& A(0\downarrow, \omega)~.\nonumber
-\end{eqnarray}
-Finally, the inter-site Greens function for the Hubbard dimer is given by
-\begin{equation}
-\label{dimer_intersite_G}
-G_{D,01}^\uparrow(\omega, T \to 0) = \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{t - \frac{\Delta}{2}}{\omega^2 - \left(t - \frac{\Delta}{2}\right)^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{t + \frac{\Delta}{2}}{\omega^2 - \left(t + \frac{\Delta}{2}\right)^2} = G_{D,01}^\downarrow(\omega, T \to 0)~.
-\end{equation}
-Using the diagonal and off-diagonal real space Greens functions, we can now compute the momentum-space Greens functions.
-The two momentum states are $ka = 0, \pi$.
-By Fourier transforming, these two Greens functions can be written as
-\begin{equation}\begin{aligned}
-	\label{Gk0}
-	G(k=0, \sigma) = \sum_r e^{ikr} G(r, \sigma) = G(r=0, \sigma) + G(r=a, \sigma) = \frac{1/2 + 2t/\Delta}{\omega -t + \Delta/2} + \frac{1/2 - 2t/\Delta}{\omega - t - \Delta/2}\\
-	G(k=\pi, \sigma) = \sum_r e^{ikr} G(r, \sigma) = G(r=0, \sigma) - G(r=a, \sigma) = \frac{1/2 + 2t/\Delta}{\omega + t - \Delta/2} + \frac{1/2 - 2t/\Delta}{\omega + t + \Delta/2}\\
-\end{aligned}\end{equation}
-
-\section{Contributions of various excitations to the site local spectral function}
-The site local spectral function is
-\begin{equation}\begin{aligned}
-	A(0\uparrow, \omega) = \left( \frac{1}{4} - \frac{t}{\Delta} \right)\left[\delta(\omega - \frac{\Delta}{2} - t) + \delta(\omega + \frac{\Delta}{2} + t)\right]\nonumber + \left( \frac{1}{4} + \frac{t}{\Delta} \right) \left[\delta(\omega - \frac{\Delta}{2} + t) + \delta(\omega + \frac{\Delta}{2} - t)\right]
-\end{aligned}\end{equation}
-If the eigenstates of the $N=1, S^z = - \frac{1}{2}$ sector are $\ket{1 \pm \downarrow}$ and those of $N=3, S^z = \frac{1}{2}$ sector are $\ket{3 \pm \uparrow}$, this spectral function originates from the expression:
-\begin{equation}\begin{aligned}
-	A(0\uparrow, \omega) =& \braket{1 \downarrow_- | c_{0 \uparrow} | \text{GS}} \delta\left(\omega + \frac{\Delta}{2} + t\right) + \braket{2 \uparrow_+ | c^\dagger_{0 \uparrow} | \text{GS}}\delta\left(\omega - \frac{\Delta}{2} - t\right) \\
-			      &+ \braket{1 \downarrow_+ | c_{0 \uparrow} | \text{GS}}\delta\left(\omega + \frac{\Delta}{2} - t\right) + \braket{2 \uparrow_- | c^\dagger_{0 \uparrow} | \text{GS}}\delta(\omega - \frac{\Delta}{2} + t)
-\end{aligned}\end{equation}
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.9\textwidth]{../figures/dimer-peaks.png}
-	\caption{Position, weight and nature of each of the peaks in the Hubbard dimer site local spectral function}
-\end{figure}
-
-\chapter{Simple results for the Greens functions}
-\section{Relation between single-particle Greens function and the Greens operator $(T=0)$}
- The single-particle Greens function is defined as the solution of the equation:
- \begin{equation}\begin{aligned}
-	 \left(i\partial_t - H(\vec r)\right)G(\vec r,\vec r^\prime, t) = \delta(\vec r - \vec r^\prime)
- \end{aligned}\end{equation}
- and is given by the expression
- \begin{equation}\begin{aligned}
-	 G(\vec r,\vec r^\prime, t) = -i \theta(t) \left< \left\{ c(\vec r, t) c^\dagger(\vec r^\prime, 0)\right\} \right>
- \end{aligned}\end{equation}
- This solution can be written in the Lehmann-Kallen representation  and at $T=0$ as
- \begin{equation}\begin{aligned}
-	 G(\vec r \sigma, \vec r^\prime \sigma, \omega) = \sum_{n}\left[\frac{\bra{GS}c({\vec r,\sigma})\ket{n}\bra{n}c^\dagger(\vec r^\prime,\sigma)\ket{GS}}{\omega + E_{GS} - E_n} + \frac{\bra{GS}c^\dagger(\vec r^\prime,\sigma)\ket{n}\bra{n}c({\vec r,\sigma})\ket{GS}}{\omega + E_n - E_{GS}}\right]
- \end{aligned}\end{equation}
- The sum is over the exact eigenstates of the Hamiltonian. In what follows, we will represent $\vec r,\sigma \equiv \nu$ and $\vec r^\prime,\sigma \equiv \nu^\prime$.
- \begin{equation}\begin{aligned}
-	 G(\nu, \nu^\prime, \omega) &= \sum_{n}\left[\frac{\bra{GS}c(\nu)\ket{n}\bra{n}c^\dagger(\nu^\prime)\ket{GS}}{\omega + E_{GS} - E_n} + \frac{\bra{GS}c^\dagger(\nu^\prime)\ket{n}\bra{n}c(\nu)\ket{GS}}{\omega + E_n - E_{GS}}\right]\\
-							&= \bra{GS}c(\nu)\frac{1}{\omega + E_{GS} - H}c^\dagger(\nu^\prime)\ket{GS} + \bra{GS}c^\dagger(\nu^\prime)\frac{1}{\omega + H - E_{GS}}c(\nu)\ket{GS}\\
- \end{aligned}\end{equation}
- If we now define a Greens operator
- \begin{equation}\begin{aligned}
-	 \label{inv_G_func}
-	 \mathcal{G}(\omega, H) = \frac{1}{\omega - (H - E_\text{GS})}
- \end{aligned}\end{equation}
- we can write the single-particle Greens function as a sum of the matrix elements of this operator:
- \begin{equation}\begin{aligned}
-	 \label{G_mat_el}
-	 G(\nu, \nu^\prime, \omega) = \bra{\nu} \mathcal{G}(\omega, H) \ket{\nu^\prime} - \bra{\overline{\nu^\prime}} \mathcal{G}(-\omega, H) \ket{\overline\nu} = \mathcal{G}(\omega, H)_{\nu,\nu^\prime} - \mathcal{G}(-\omega, H)_{\overline{\nu^\prime}, \overline\nu}
- \end{aligned}\end{equation}
- where we have defined the states $\ket{\nu} \equiv c^\dagger(\nu)\ket{GS}$ and $\ket{\overline\nu} \equiv c(\nu)\ket{GS}$.
-The two matrix elements can also be represented in their individual spectral representations:
- \begin{equation}\begin{aligned}
-	 \label{G_mat_spec}
- 	\mathcal{G}(\omega, H)_{\nu,\nu^\prime} = \sum_{n}\frac{\bra{GS}c(\nu)\ket{n}\bra{n}c^\dagger(\nu^\prime)\ket{GS}}{\omega + E_{GS} - E_n}\\
-	\mathcal{G}(\omega, H)_{\overline{\nu^\prime}, \overline\nu} = \sum_{n}\frac{\bra{GS}c^\dagger(\nu^\prime)\ket{n}\bra{n}c(\nu)\ket{GS}}{\omega + E_\text{GS} - E_n}
- \end{aligned}\end{equation}
-
-\section{Writing single-particle excitations of ground state in terms of $N=3, S^z = \frac{1}{2}$ eigenstates}
-The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates $\ket{3\pm\uparrow}$ defined in table \ref{hubb_dim_spectrum}.
-\begin{equation}\begin{aligned}
-	\ket{3\pm \uparrow} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{3\pm \uparrow} = \pm t\ket{3\pm \uparrow}
-\end{aligned}\end{equation}
-In terms of these eigenstates, we can write
-\begin{equation}\begin{aligned}
-	c^\dagger_{0\uparrow}\ket{\text{GS}} 
-	&= c^\dagger_{0\uparrow}\left[a_1 \ket{SS} + a_2 \ket{CT}\right] \\
-	&= a_2 \frac{1}{\sqrt 2}\ket{\uparrow,2} - a_1 \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
-	&= \left(x + y\right) \frac{1}{\sqrt 2}\ket{\uparrow,2} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
-	&=x\ket{3+ \uparrow} + y\ket{3- \uparrow}
-\end{aligned}\end{equation}
-where $x + y \equiv a_2$ and $x-y \equiv -a_1$. Similarly, for the other site excitation, we can write
-\begin{equation}\begin{aligned}
-	c^\dagger_{1\uparrow}\ket{\text{GS}} 
-	&= c^\dagger_{1\uparrow}\left[a_1 \ket{SS} + a_2 \ket{CT}\right] \\
-	&= a_2 \frac{1}{\sqrt 2}\ket{2, \uparrow} - a_1 \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
-	&=  \left(x + y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
-	&=x\ket{3+ \uparrow} - y\ket{3- \uparrow}
-\end{aligned}\end{equation}
-Solving for $x$ and $y$ gives
-\begin{equation}\begin{aligned}
-	x = \frac{a_2 - a_1}{2}, && y = \frac{a_2 + a_1}{2}
-\end{aligned}\end{equation}
-Similarly, we can also write the single-hole excitation $c_{0 \uparrow}\ket{GS}$ in terms of the $N=1, S^z = -\frac{1}{2}$ eigenstates, $\ket{1\pm \downarrow}$:
-\begin{equation}\begin{aligned}
-	\ket{1\pm \downarrow} = \frac{1}{\sqrt 2}\left(\ket{\downarrow, 0} \pm \ket{0, \downarrow}\right), && H^D \ket{1\pm \downarrow} = \mp t\ket{1\pm \downarrow}
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-	c_{0 \uparrow}\ket{GS} = a_1 \frac{1}{\sqrt 2}\ket{0, \downarrow} + a_2 \frac{1}{\sqrt 2}\ket{\downarrow, 0} = y\ket{1+ \downarrow} + x\ket{1- \downarrow}\\
-	c_{1 \uparrow}\ket{GS} = a_1 \frac{1}{\sqrt 2}\ket{\downarrow, 0} + a_2 \frac{1}{\sqrt 2}\ket{0, \downarrow} = y\ket{1+ \downarrow} - x\ket{1- \downarrow}\\
-\end{aligned}\end{equation}
-
-\section{Matrix elements of $G^{-1}$ between single-particle momentum excitations, for the Hubbard dimer}
-\begin{equation}\begin{aligned}
-	G^{-1} \equiv \omega + E_\text{GS} - H_D
-\end{aligned}\end{equation}
-The particle excitation momentum space kets are $\ket{k_0} = \frac{1}{\sqrt 2}\left(\ket{0} + \ket{1}\right) ,\ket{k_\pi} = \frac{1}{\sqrt 2}\left(\ket{0} - \ket{1}\right)$. Therefore,
-\begin{equation}\begin{aligned}
-	\left(G^{-1}\right)_{k_0 k_0} &= \frac{1}{2}\left(\bra{0} + \bra{1}\right)\left(\omega + E_\text{GS} - H_D\right)\left(\ket{0} + \ket{1}\right)\\
-				      &= \frac{1}{2}\left(2x\bra{+}\right)\left(\omega + E_\text{GS} - H_D\right)\left(2x\ket{+}\right)\\
-				      &= 2x^2\left(\omega + E_\text{GS} - t\right)\\
-\end{aligned}\end{equation}
-At the final step, we used $\braket{+,+} = 1$ and $\braket{+|H_D|+} = t$.
-
-\chapter{Topological interpretation of the Wilson ratio}
-From the Friedel sum rule\cite{langer1961friedel}, we can relate the phase shift \(\delta(0)\) due to scattering (at the Fermi surface) off a local impurity to the number of electrons bound in the potential well produced by that impurity:
-\begin{equation}\begin{aligned}
-\widetilde N = \frac{1}{2\pi i}\text{Tr }\ln S(0) = \int_\Gamma dz\partial_z \frac{1}{2\pi i}\text{Tr }\ln S(0)
-\end{aligned}\end{equation}
-From the optical theorem, we can write
-\begin{equation}\begin{aligned}
-	S = 1 + TG_0 = \frac{G}{G_0} && \left[G = G_0 + G_0 T G_0\right]
-\end{aligned}\end{equation}
-This allows us to write \cite{anirbanurg1}
-\begin{equation}\begin{aligned}
-\widetilde N = \int_\Gamma dz\partial_z \frac{1}{2\pi i}\text{Tr }\ln \frac{G}{G_0}
-\end{aligned}\end{equation}
-Since \(\text{Tr }\ln \hat O = \sum_\lambda \ln O_\lambda = \ln \prod_\lambda O_\lambda = \ln \text{Det} \hat O\), we get
-\begin{equation}\begin{aligned}
-\widetilde N &= \int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln \text{Det } \frac{G}{G_0}\\
-      &= -\int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln \frac{\text{Det } G_0}{\text{Det } G}\\
-      &\equiv -\int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln D\\
-      &= -\int_{\Gamma(D)}\frac{dD}{D}
-\end{aligned}\end{equation}
-From the work of Seki and Yunoki \cite{seki2017topological}, we know that this quantity is essentially the winding number of the curve \(\Gamma(D)\) in the complex plane spanned by the real and imaginary parts of \(D\), and is equal to the change in Luttinger's volume \(V_L\) at \(T=0\).
-\begin{equation}\begin{aligned}
-\widetilde N &= -\int_{\Gamma(D)}\frac{dD}{D} = -\Delta V_L
-\end{aligned}\end{equation}
-The incoming electrons can have \(\sigma = \uparrow,\downarrow\).
-Since the impurity singlet ground state is rotationally invariant, we have \(\delta_\uparrow = \delta_\downarrow = \delta(0)\).
-\begin{equation}\begin{aligned}
-\widetilde N &= \frac{1}{\pi}\sum_\sigma\delta_\sigma(0)\\
-\implies \delta(0) &= \frac{\pi}{2}\widetilde N = -\frac{\pi}{2}\Delta V_L
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-\label{wilson_luttinger}
-R &= 1 + \sin^2 \left(\frac{\pi}{2}\widetilde N\right)\\
-  &= 1 + \sin^2 \left(\frac{\pi}{2}\Delta V_L\right)
-\end{aligned}\end{equation}
-We note that this connection between \(R\) and \(\Delta V_L\) has not been obtained in the existing literature thus far.
-In the unitary limit, \(\delta(0) = \frac{\pi}{2}\), giving \(\Delta V_L = -1 = -\tilde N\) \cite{martin1982fermi} (i.e., one electronic state from the impurity has been absorbed into the Luttinger volume of the conduction bath), such that \(R = 2\) in this limit.
-In this way, we see that a change in the topological quantum number \(\tilde N\) causes the well known renormalisation of the Wilson ratio R from its non-interacting value \((1)\) to the value \((2)\) obtained for the local Fermi liquid \cite{nozieres1974fermi}.
-
 \end{appendices}

### 2023-03-02 notes/notes.tex
--no-message

@@
 \begin{equation}\begin{aligned}
+	\left[\sum_{\vec R_c}\mathcal{H}\left( \vec R_c \right)\right]^n = \left[\sum_{\vec R_c}T^\dagger_{\vec R_c -\vec R_0} \mathcal{H}\left( \vec R_0 \right)T_{\vec R_c -\vec R_0} \right]^n = \sum_{\left\{ \vec R_{i} \right\} }T^\dagger_{\vec R_1 -\vec R_0} \mathcal{H}\left( \vec R_0 \right)T^\dagger_{\vec R_2 -\vec R_1}\ldots \mathcal{H}\left( \vec R_0 \right)T_{\vec R_n -\vec R_{0}}
+\end{aligned}\end{equation}
+
+\begin{equation}\begin{aligned}
 	\left[\sum_{\vec R_c}\mathcal{H}\left( \vec R_c \right)\right]^n &= \left[\sum_{\vec R_c,\vec k,\vec k^\prime}T^\dagger_{\vec R_c - \vec R_0}\ket{\vec k}\bra{\vec k}\mathcal{H}(\vec R_0)\ket{\vec k^\prime}\bra{\vec k^\prime}T_{\vec R_c - \vec R_0}\right]^n = \left[\sum_{\vec k,\vec k^\prime}\ket{\vec k}\bra{\vec k^\prime}\mathcal{H}_{\vec k, \vec k^\prime}(\vec R_0)\sum_{\vec R_c}e^{i \left( \vec k^\prime - \vec k \right) \cdot \left(\vec R_c - \vec R_0\right)}\right]^n\\
@@
 \begin{equation}\begin{aligned}
-	G(\vec r, \Omega) = \sum_{\vec k}\left[\frac{\theta(|\vec k - \vec k_0| - |\vec k_F|) e^{i\left(\vec k - \vec k_0\right) \cdot \vec r}}{\omega + N\varepsilon_\text{gs} - N\mathcal{H}_{\vec k, \vec k}} + \frac{\theta(|\vec k_F| - |\vec k_0 - \vec k|) e^{-i\left(\vec k - \vec k_0\right) \cdot \vec r}}{\omega - N\varepsilon_\text{gs} + N\mathcal{H}_{\vec k, \vec k}}\right]
+	G(\vec r, \omega) = \sum_{\vec k}\left[\frac{\theta(|\vec k - \vec k_0| - |\vec k_F|) e^{i\left(\vec k - \vec k_0\right) \cdot \vec r}}{\omega + N\varepsilon_\text{gs} - N\mathcal{H}_{\vec k, \vec k}} + \frac{\theta(|\vec k_F| - |\vec k_0 - \vec k|) e^{-i\left(\vec k - \vec k_0\right) \cdot \vec r}}{\omega - N\varepsilon_\text{gs} + N\mathcal{H}_{\vec k, \vec k}}\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G(\vec r, \Omega) = \sum_{\vec q}\left[\frac{\theta(|\vec q| - |\vec k_F|) e^{i\vec q \cdot \vec r}}{\omega + N\varepsilon_\text{gs} - N\mathcal{E}^p_{\vec q}} + \frac{\theta(|\vec k_F| - |- \vec q|) e^{-i\vec q \cdot \vec r}}{\omega - N\varepsilon_\text{gs} + N\mathcal{E}^h_{\vec q}}\right]~,
+	G(\vec r, \omega) = \sum_{\vec q}\left[\frac{\theta(|\vec q| - |\vec k_F|) e^{i\vec q \cdot \vec r}}{\omega + N\varepsilon_\text{gs} - N\mathcal{E}^p_{\vec q}} + \frac{\theta(|\vec k_F| - |- \vec q|) e^{-i\vec q \cdot \vec r}}{\omega - N\varepsilon_\text{gs} + N\mathcal{E}^h_{\vec q}}\right]~,
 \end{aligned}\end{equation}
 where the matrix elements \(\mathcal{E}^p\) and \(\mathcal{E}^h\) for the particle and hole excitations are given by \(\mathcal{E}^p_{\vec q} = \mathcal{H}_{\vec k_0 + \vec q, \vec k_0 + \vec q} = \braket{\vec k_0 | c_{\vec q} \mathcal{H} c^\dagger_{\vec q} | \vec k_0}\) and \(\mathcal{E}^h_{\vec q} = \mathcal{H}_{\vec k_0 - \vec q, \vec k_0 - \vec q} = \braket{\vec k_0 | c^\dagger_{\vec q} \mathcal{H} c_{\vec q} | \vec k_0}\).
+For models with strong local correlations, it might be more convenient to express these \(k-\)space single-particle matrix elements in terms of real-space fluctuations:
+\begin{equation}\begin{aligned}
+\mathcal{E}^h_{\vec q} = \sum_{\vec x_{+},\vec x_{-}}e^{i\left( \vec x_+ - \vec x_- \right) \cdot \vec q}\braket{\vec k_0 | c^\dagger_{\vec x_-} \mathcal{H} c_{\vec x_+} | \vec k_0}, \quad \mathcal{E}^p_{\vec q} = \sum_{\vec x_{+},\vec x_{-}}e^{i\left(\vec x_+ - \vec x_- \right) \cdot \vec q}\braket{\vec k_0 | c_{\vec x_+} \mathcal{H} c^\dagger_{\vec x_-} | \vec k_0}
+\end{aligned}\end{equation}
+Guided by the fact that our auxiliary model has an emergent self-consistency at the impurity site, we retain distances \(|\vec x_+ - \vec x_-|\) up to one lattice spacing \(\vec a\) from the impurity, in the summation:
+\begin{equation}\begin{aligned}
+	\mathcal{E}^h_{\vec q} \to \braket{\vec k_0 | c^\dagger_{\vec R_0} \mathcal{H}\left(\vec R_0\right) c_{\vec R_0} | \vec k_0} + \sum_{\vec a}\left(e^{i\vec a \cdot \vec q}\braket{\vec k_0 | c^\dagger_{\vec R_0 + \vec a} \mathcal{H}\left(\vec R_0\right) c_{\vec R_0}| \vec k_0} + \text{h.c.}\right),\\
+	\quad \mathcal{E}^p_{\vec q} \to \braket{\vec k_0 | c_{\vec R_0} \mathcal{H}\left(\vec R_0\right) c^\dagger_{\vec R_0} | \vec k_0} + \sum_{\vec a}\left(e^{i\vec a \cdot \vec q}\braket{\vec k_0 | c_{\vec R_0} \mathcal{H}\left(\vec R_0\right) c_{\vec R_0 + \vec a}^\dagger| \vec k_0} + \text{h.c.}\right)
+\end{aligned}\end{equation}
+
+\clearpage
 

### 2023-03-03 notes/notes.tex
clarified the normalisation proof

@@
 \end{aligned}\end{equation}
-where \(\lambda_{\ket{\vec k}}\) is a normalisation factor and is defined by \(|\lambda_{\ket{\vec k}}|^2 = |\braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}|^2 \); \(\ket{\vec k}\) is the momentum eigenstate for momentum \(\vec k\), and \(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
-Becuase of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(w\) choices.
+where \(\lambda_{\ket{\vec k}}\) is a normalisation factor. To determine this, we compute the norm of the trail eigenstates:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k} | \Psi_{\vec k}} &= \frac{1}{w^2 \lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, a, a^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime, \vec a^\prime) | \psi_\text{aux}(\vec R, \vec a)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, }e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime) | \psi_\text{aux}(\vec R)}\\
+					       &=\frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) | \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)}\\
+					       &= \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i (\vec{k} - \vec q)\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{q} N^2 \delta_{\vec{k},\vec q}|\braket{\psi_\text{aux}(\vec R_0) | \vec q}|^2\\
+\end{aligned}\end{equation}
+By requiring this norm to be unity, we obtain \(\lambda_{\vec k}^2 = |\braket{\psi_\text{aux}(\vec R_0) | \vec k}|^2\).
+In the above exercise, we defined a state \(\ket{\psi_\text{aux}(\vec R)} = (1/w)\sum_{\vec a}\ket{\psi_\text{aux}(\vec R, \vec a)}\) by averaging over the neasest neighbours of \(\vec R\), and inserted the total momentum basis \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators.
+\(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
+Because of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(w\) choices.
 

### 2023-03-03 notes/notes.tex
added the new Hamiltonian expansion approach

@@
 \begin{equation}\begin{aligned}
-	\mathcal{G}(\omega) = \frac{1}{\omega - (H_\text{H-H} - E_\text{gs})}~,
-\end{aligned}\end{equation}
-where \(\omega\) is the frequency scale for the excitations. This operator can be related to the Greens function through the relation (eq.~\eqref{inv_G_func})
+	\mathcal{G}(\omega) = \frac{1}{\omega - (H_\text{H-H} - E_\text{gs})} = \frac{1}{\omega + E_\text{gs} - \sum_{\vec R_i} \mathcal{H}_\text{aux}(\vec R_i)}~,
+\end{aligned}\end{equation}
+where \(\omega\) is the frequency scale for the excitations, and we used eq.~\ref{siam_to_hubb} to write the operator in terms of the auxiliary model Hamiltonian.
+This operator can be related to the Greens function through the relation (eq.~\eqref{inv_G_func})
 \begin{equation}\begin{aligned}\label{greens_func_bulk}
-	G(\vec r, \omega) &= \braket{\Psi_\text{gs} | c(\vec R + r) \mathcal{G}(\omega) c^\dagger(\vec R) | \Psi_\text{gs}} - \braket{\Psi_\text{gs} | c^\dagger(\vec R) \mathcal{G}(-\omega) c(\vec R + r) | \Psi_\text{gs}}\\
+	G(\vec r, \omega) &= \braket{\Psi_\text{gs} | c(\vec R + r) \mathcal{G}(\omega) c^\dagger(\vec R) | \Psi_\text{gs}} - \braket{\Psi_\text{gs} | c^\dagger(\vec R) \mathcal{G}(-\omega) c(\vec R + r) | \Psi_\text{gs}}
+\end{aligned}\end{equation}
+In order to simplify the expression for the operator \(\mathcal{G}(\omega)\), we rewrite the sum over the auxiliary models in terms of a uniform piece \(\sum_{i}\mathcal{H}_\text{aux}(\vec R_0)\) and a difference piece \(\Delta(i) = \mathcal{H}_\text{aux}(\vec R_i) - \mathcal{H}_\text{aux}(\vec R_0)\):
+\begin{equation}\begin{aligned}
+	\sum_{\vec R_i} \mathcal{H}_\text{aux}(\vec R_i) = \sum_{\vec R_i} \left[\mathcal{H}_\text{aux}(\vec R_0) + \Delta(\vec R_i)\right] = N \mathcal{H}_\text{aux}(\vec R_0) + \sum_{\vec R_i} \Delta(\vec R_i);
+\end{aligned}\end{equation}
+\(\vec R_0\) is the origin of the lattice, and \(N\) is the number of lattice sites.
+The difference piece is smaller than the uniform sum piece, and we can then expand the Greens operator in powers of this difference:
+\begin{equation}\begin{aligned}
+	\mathcal{G}(\omega) &= \frac{1}{N}\frac{1}{\frac{1}{N}\omega + \frac{1}{N}E_\text{gs} - \mathcal{H}_\text{aux}(\vec R_0)}\left[1 + \frac{1}{\frac{1}{N}\omega + \frac{1}{N}E_\text{gs} - \mathcal{H}_\text{aux}(\vec R_0)}\sum_{\vec R_i} \frac{1}{N}\Delta(\vec R_i) + \ldots \right]
+\end{aligned}\end{equation}
+In general, if the auxiliary model can be written as \(\mathcal{H}_\text{aux} = H_\text{imp} + H_\text{imp-bath} + H_\text{bath}\) where \(H_\text{imp}\) is the impurity-only part of the Hamiltonian and \(H_\text{imp-bath}\) is the impurity-bath interaction, the difference piece has the form \(\Delta(\vec R_i) = H_\text{imp}(\vec R_i) + H_\text{imp-bath}(\vec R_i) - H_\text{imp}(\vec R_0) - H_\text{imp-bath}(\vec R_0)\).
+For a model with translation symmetry in the bath, this difference piece will be small.
+
+In the limit of large \(N\), we retain only the leading piece in the expansion presently, resulting in the Greens operator of the bulk becoming equal to the Greens operator for suitably scaled auxiliary model.
+On substituting this relation into the expression for the single-particle Greens function, we get
+\begin{equation}\begin{aligned}
+	G(\vec r, \omega) &= \braket{\Psi_\text{gs} | c(\vec R + r) \frac{1}{\omega + E_\text{gs} - N\mathcal{H}_\text{aux}(\vec R_0)} c^\dagger(\vec R) | \Psi_\text{gs}} - \braket{\Psi_\text{gs} | c^\dagger(\vec R) \frac{1}{-\omega + E_\text{gs} - N\mathcal{H}_\text{aux}(\vec R_0)} c(\vec R + r) | \Psi_\text{gs}}
+\end{aligned}\end{equation}
+We will now express the ground-state in terms of the auxiliary model states, following eq.~\ref{bloch-states}. The first term in the previous equation takes the form
+\begin{equation}\begin{aligned}
+	\frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i,\vec R_j}e^{i\vec k_0\cdot\left(\vec R_j - \vec R_i\right)} \braket{\psi_\text{aux}(\vec R_i) | c(\vec R + r) \frac{1}{\omega + E_\text{gs} - N\mathcal{H}_\text{aux}(\vec R_0)} c^\dagger(\vec R) | \psi_\text{aux}(\vec R_j)}~.
+\end{aligned}\end{equation}
+We again simplify the wavefunction by keeping only the uniform piece and dropping the difference pieces:
+\begin{equation}\begin{aligned}
+	\frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j} e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j)} =  \frac{1}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)} + \ket{\psi_\text{diff}(\vec k_0)}
+\end{aligned}\end{equation}
+where \(\ket{\psi_\text{diff}(\vec k_0)} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j} \left[e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j)} - e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)}\right]\).
+By retaining only the first term, the first term of the Greens function can be expressed as
+\begin{equation}\begin{aligned}
+	\frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i,\vec R_j}e^{i\vec k_0\cdot\left(\vec R_j - \vec R_i\right)} \braket{\psi_\text{aux}(\vec R_i) | c(\vec R + r) \frac{1}{\omega + E_\text{gs} - N\mathcal{H}_\text{aux}(\vec R_0)} c^\dagger(\vec R) | \psi_\text{aux}(\vec R_j)}\\
+	\simeq \frac{1}{\lambda_{\vec k_0}^2}\braket{\psi_\text{aux}(\vec R_0) | c(\vec R + r) \frac{1}{\omega + E_\text{gs} - N\mathcal{H}_\text{aux}(\vec R_0)} c^\dagger(\vec R) | \psi_\text{aux}(\vec R_0)}
+\end{aligned}\end{equation}
+The error can be estimated by calculating the norm of the difference piece:
+\begin{equation}\begin{aligned}
+	\braket{\psi_\text{diff}(\vec k_0) | \psi_\text{diff}(\vec k_0)} = \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j} e^{i \vec k_0 \cdot(\vec R_j - \vec R_i)}\braket{\psi_\text{aux}(\vec R_i) | \psi_\text{aux}(\vec R_j) } + \frac{1}{\lambda_{\vec k_0}^2} - \\
+	\frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_j} \left(e^{i \vec k_0 \cdot \left( \vec R_j - \vec R_0 \right)}  \braket{\psi_\text{aux}(\vec R_0) | \psi_\text{aux}(\vec R_j) } + \text{h.c.}\right)
+\end{aligned}\end{equation}
+
+\clearpage
+\begin{equation}\begin{aligned}
 			  &= \sum_n\left[\braket{\Psi_\text{gs} | c(\vec R + r) \lambda^-_n \frac{\left(H_\text{H-H}\right)^n}{(\omega + E_\text{gs})^{n+1}} c^\dagger(\vec R) | \Psi_\text{gs}} + \braket{\Psi_\text{gs} | c^\dagger(\vec R) \lambda^+_n \frac{\left(H_\text{H-H}\right)^n}{(\omega - E_\text{gs})^{n+1}} c(\vec R + r) | \Psi_\text{gs}}\right]\\

### 2023-03-06 notes/notes.tex
cleaning up the notes with new approach

--- 2023-03-02 notes/notes.tex
@@
 The tight-binding term sums over all nearest pairs \((m,n)\) that do not involve the site \(i\).
-In general \(i\) will have \(w\) nearest neighbours for a lattice with coordination number \(w\).
+In general \(i\) will have \(\mathcal{Z}\) nearest neighbours for a lattice with coordination number \(\mathcal{Z}\).
 The total local Hamiltonian for the site \(i\) is obtained by averaging over the Hamiltonians \(\mathcal{H}_\text{aux}(i,j)\) for all nearest neighbours \(j\) of \(i\):
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(i) &= \frac{1}{w}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{w}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right)  \right.\\
+	\mathcal{H}_\text{aux}(i) &= \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right)  \right.\\
 				  &\left. +J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\\
-				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
+				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
 				  &\left.- U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& \sum_i \mathcal{H}_\text{aux}(i) = \sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
+	\mathcal{H}_\text{full} =& \sum_i \mathcal{H}_\text{aux}(i) = \sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
 				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\right]\\
-	=& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{w}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
+	=& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
 				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j\right]\right]
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - 2t\left(N-2\right)\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{w}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
+	\mathcal{H}_\text{full} =& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - 2t\left(N-2\right)\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{\mathcal{Z}}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
 				  &+ \left. J \vec{S_i}\cdot\vec{S}_j\right]\\
-				  &=-\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(2t (N-2) - \frac{2V}{w}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{w} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
+				  &=-\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(2t (N-2) - \frac{2V}{\mathcal{Z}}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{\mathcal{Z}} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
 \end{aligned}\end{equation}
@@
 	\label{map_aux_bulk}
-	t_{H-H} = \left(2t (N-2) - \frac{2V}{w}\right),~ ~ U_{H-H} = \left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{w}
+	t_{H-H} = \left(2t (N-2) - \frac{2V}{\mathcal{Z}}\right),~ ~ U_{H-H} = \left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{\mathcal{Z}}
 \end{aligned}\end{equation}
@@
 with the impurity position \(\vec R_i\) and zeroth site position \(\vec R_i + \vec a\), to construct eigenstates of the bulk Hamiltonian.
-\(\vec R_i\) is a lattice vector, while \(\vec a\) is one of the \(w\) vectors that connect a lattice site with its nearest neighbours.
+\(\vec R_i\) is a lattice vector, while \(\vec a\) is one of the \(\mathcal{Z}\) vectors that connect a lattice site with its nearest neighbours.
 This two site wavefunction can be obtained by first studying the full auxiliary model \(\mathcal{H}_\text{aux}\) under a renormalisation group, obtaining a fixed-point Hamiltonian in the IR, obtaining the IR eigenstate and then tracing out all lattice sites except the impurity and the zeroth site from this eigenstate.
@@
 \begin{equation}\begin{aligned}
-	\ket{\Psi^n_{\vec k}} = \frac{1}{w \sqrt N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
+	\ket{\Psi^n_{\vec k}} = \frac{1}{\mathcal{Z} \sqrt N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
 \end{aligned}\end{equation}
@@
 	\label{bloch-states}
-	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
-\end{aligned}\end{equation}
-where \(\lambda_{\ket{\vec k}}\) is a normalisation factor and is defined by \(|\lambda_{\ket{\vec k}}|^2 = |\braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}|^2 \); \(\ket{\vec k}\) is the momentum eigenstate for momentum \(\vec k\), and \(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
-Becuase of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(w\) choices.
+	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
+\end{aligned}\end{equation}
+where \(\lambda_{\ket{\vec k}}\) is a normalisation factor. To determine this, we compute the norm of the trail eigenstates:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k} | \Psi_{\vec k}} &= \frac{1}{\mathcal{Z}^2 \lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, a, a^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime, \vec a^\prime) | \psi_\text{aux}(\vec R, \vec a)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, }e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime) | \psi_\text{aux}(\vec R)}\\
+					       &=\frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) | \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)}\\
+					       &= \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i (\vec{k} - \vec q)\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{q} N^2 \delta_{\vec{k},\vec q}|\braket{\psi_\text{aux}(\vec R_0) | \vec q}|^2\\
+\end{aligned}\end{equation}
+By requiring this norm to be unity, we obtain \(\lambda_{\vec k}^2 = |\braket{\psi_\text{aux}(\vec R_0) | \vec k}|^2\). In the above exercise, we defined a state 
+\begin{equation}\begin{aligned}\label{zeroth_site_average}
+	\ket{\psi_\text{aux}(\vec R)} = (1/w)\sum_{\vec a}\ket{\psi_\text{aux}(\vec R, \vec a)}~,
+\end{aligned}\end{equation}
+by averaging over the neasest neighbours of \(\vec R\), and inserted the total momentum basis \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators.
+\(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
+Because of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(\mathcal{Z}\) choices.
 
@@
 \begin{equation}\begin{aligned}
-	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
+	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} w N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
+	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} \mathcal{Z} N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
 	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
 \end{aligned}\end{equation}
-where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} w N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
+where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
 This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
@@
 	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
-	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
-	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
-						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
+						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 w^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
-	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}
+	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} w^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 w^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 w^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
+	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
 	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}
@@
 \begin{equation}\begin{aligned}
-	G(\vec r, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c(\vec R + r,t), c^\dagger(\vec R) \right\} | \Psi_\text{gs}}
-\end{aligned}\end{equation}
-We also define a Green operator \(\mathcal{G}(\omega)\):
-\begin{equation}\begin{aligned}
-	\mathcal{G}(\omega) = \frac{1}{\omega - (H_\text{H-H} - E_\text{gs})}~,
-\end{aligned}\end{equation}
-where \(\omega\) is the frequency scale for the excitations. This operator can be related to the Greens function through the relation (eq.~\eqref{inv_G_func})
-\begin{equation}\begin{aligned}\label{greens_func_bulk}
-	G(\vec r, \omega) &= \braket{\Psi_\text{gs} | c(\vec R + r) \mathcal{G}(\omega) c^\dagger(\vec R) | \Psi_\text{gs}} - \braket{\Psi_\text{gs} | c^\dagger(\vec R) \mathcal{G}(-\omega) c(\vec R + r) | \Psi_\text{gs}}\\
-			  &= \sum_n\left[\braket{\Psi_\text{gs} | c(\vec R + r) \lambda^-_n \frac{\left(H_\text{H-H}\right)^n}{(\omega + E_\text{gs})^{n+1}} c^\dagger(\vec R) | \Psi_\text{gs}} + \braket{\Psi_\text{gs} | c^\dagger(\vec R) \lambda^+_n \frac{\left(H_\text{H-H}\right)^n}{(\omega - E_\text{gs})^{n+1}} c(\vec R + r) | \Psi_\text{gs}}\right]\\
-			  &= \sum_n\left[ \frac{\lambda^-_n}{(\omega + E_\text{gs})^{n+1}} \mathcal{U}(\vec r)^{(n)}_> + \frac{\lambda^+_n}{(\omega - E_\text{gs})^{n+1}} \mathcal{U}(\vec r)^{(n)}_<\right]
-\end{aligned}\end{equation}
-where we have defined \(\lambda_n^\pm\) using \(1/(1\pm y) = \sum_n \lambda^\pm_n y^n\), and the retarded and advanced propagation matrix elements \(\mathcal{U}(\vec r)^{(n)}_>  = \braket{\Psi_\text{gs} | c(\vec R + r) \left(H_\text{H-H}\right)^n c^\dagger(\vec R) | \Psi_\text{gs}}, \quad \mathcal{U}(\vec r)^{(n)}_<  = \braket{\Psi_\text{gs} | c^\dagger(\vec R) \left(H_\text{H-H}\right)^n c(\vec R + r) | \Psi_\text{gs}}\).
-These matrix elements will now be expressed in terms of auxiliary model properties, starting with the retarded one. By combining with eq.~\eqref{siam_to_hubb} and eq.~\eqref{bloch-states}, we get
-\begin{equation}\begin{aligned}\label{retarded_matrix_element}
-	\mathcal{U}(\vec r)^{(n)}_> = \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_i) | c_{\vec R + \vec r, \sigma} \left[\sum_{\vec R_c}\mathcal{H}\left( \vec R_c \right)\right]^n  c_{\vec R, \sigma}^\dagger | \psi_\text{aux}(\vec R_j)}~,
-\end{aligned}\end{equation}
-where \(\vec k_0\) is the crystal momentum in the ground-state, and \(\ket{\psi}_\text{aux}(\vec R) = \frac{1}{w}\sum_{\vec a}^{\text{NN of }\vec R} \ket{\psi}_\text{aux}(\vec R, \vec a)\).
-The exponentiated sum can be simplified by inserting the momentum eigenbasis \(\left\{ \ket{\vec k}\bra{\vec k}\right\} \) of the auxiliary model Hilbert space, and shifting all the Hamiltonians \(\mathcal{H}\left( \vec R_c \right)\) to the origin \(\vec R_0\), using translation operators:
-\begin{equation}\begin{aligned}
-	\left[\sum_{\vec R_c}\mathcal{H}\left( \vec R_c \right)\right]^n = \left[\sum_{\vec R_c}T^\dagger_{\vec R_c -\vec R_0} \mathcal{H}\left( \vec R_0 \right)T_{\vec R_c -\vec R_0} \right]^n = \sum_{\left\{ \vec R_{i} \right\} }T^\dagger_{\vec R_1 -\vec R_0} \mathcal{H}\left( \vec R_0 \right)T^\dagger_{\vec R_2 -\vec R_1}\ldots \mathcal{H}\left( \vec R_0 \right)T_{\vec R_n -\vec R_{0}}
-\end{aligned}\end{equation}
-
-\begin{equation}\begin{aligned}
-	\left[\sum_{\vec R_c}\mathcal{H}\left( \vec R_c \right)\right]^n &= \left[\sum_{\vec R_c,\vec k,\vec k^\prime}T^\dagger_{\vec R_c - \vec R_0}\ket{\vec k}\bra{\vec k}\mathcal{H}(\vec R_0)\ket{\vec k^\prime}\bra{\vec k^\prime}T_{\vec R_c - \vec R_0}\right]^n = \left[\sum_{\vec k,\vec k^\prime}\ket{\vec k}\bra{\vec k^\prime}\mathcal{H}_{\vec k, \vec k^\prime}(\vec R_0)\sum_{\vec R_c}e^{i \left( \vec k^\prime - \vec k \right) \cdot \left(\vec R_c - \vec R_0\right)}\right]^n\\
-									 &= \left[\sum_{\vec k}\ket{\vec k}\bra{\vec k}\mathcal{H}_{\vec k, \vec k}(\vec R_0)\right]^n = \sum_{\vec k}\ket{\vec k}\bra{\vec k}\left(N_\text{aux}\mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n~,
-\end{aligned}\end{equation}
-where \(N_\text{aux}\) is the number of sites in the auxiliary mode, and we used
-\begin{gather}
-	\mathcal{H}(\vec R_c) = T^\dagger_{\vec R_c - \vec R_0}\mathcal{H}(\vec R_0)T_{\vec R_c - \vec R_0}~,\quad \sum_{\vec R_c}e^{i \left( \vec k^\prime - \vec k \right) \cdot \left(\vec R_c - \vec R_0\right)}  = N_\text{aux}\delta_{\vec k, \vec k^\prime}~,
-\end{gather}
-We also defined the Hamiltonian matrix element \(\mathcal{H}_{\vec k, \vec k^\prime}(\vec R_0) = \braket{\vec k | \mathcal{H}(\vec R_0) | \vec k^\prime}\).
-Substituting this back into eq.~\eqref{retarded_matrix_element} gives
-\begin{equation}\begin{aligned}
-	\mathcal{U}(\vec r)^{(n)}_> = \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec k} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_i) | c_{\vec R + \vec r, \sigma} | \vec k}\left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n \braket{\vec k | c_{\vec R, \sigma}^\dagger | \psi_\text{aux}(\vec R_j)}~,
-\end{aligned}\end{equation}
-We shift the ground-states \(\ket{\psi_\text{aux}}\) to \(\vec R_0\) as well, using the translation operators:
-\begin{equation}\begin{aligned}
-	\sum_{\vec R_j}e^{i\vec R_j \cdot \vec k_0}\braket{\vec k | c_{\vec R, \sigma}^\dagger | \psi_\text{aux}(\vec R_j)} &= \sum_{\vec R_j}e^{i\vec R_j \cdot \vec k_0}\braket{\vec k | c_{\vec R, \sigma}^\dagger T^\dagger_{\vec R_j - \vec R_0} | \psi_\text{aux}(\vec R_0)} = \sum_{\vec R_j, \vec q}e^{i\vec R_j \cdot \vec k_0}\braket{\vec k | c_{\vec R, \sigma}^\dagger e^{-i\vec q\cdot(\vec R_j - \vec R_0)} | \vec q}\braket{\vec q | \psi_\text{aux}(\vec R_0)}\\
-															    &= N e^{i\vec R_0 \cdot \vec k_0}\braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}\braket{\vec k_0 | \psi_\text{aux}(\vec R_0)}\\
-\end{aligned}\end{equation}
-All the position variation is then transferred to the creation and annihilation operators, leading to the simpler form
-\begin{equation}\begin{aligned}
-	\mathcal{U}(\vec r)^{(n)}_> &= \frac{1}{\lambda_{\vec k_0}^2}\sum_{\vec k} \braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} \braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}|\braket{\psi_\text{aux}(\vec R_0) | \vec k_0}|^2\left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n \\
-				    &= \sum_{\vec k} \braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} \braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}\left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n~.
-\end{aligned}\end{equation}
-The advanced correlation \(\mathcal{U}(\vec r)^{(n)}_<\) can be obtained similarly:
-\begin{equation}\begin{aligned}
-	\mathcal{U}(\vec r)^{(n)}_< = \sum_{\vec k} \braket{\vec k_0 | c_{\vec R, \sigma}^\dagger | \vec k} \braket{\vec k | c_{\vec R + \vec r, \sigma} | \vec k_0}\left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n~.
-\end{aligned}\end{equation}
-Substituting this into eq.~\eqref{greens_func_bulk} gives
-\begin{equation}\begin{aligned}
-	G(\vec r, \omega) &= \sum_{\vec k}\left[\frac{\braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} \braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}}{\omega + E_\text{gs}}\sum_n\frac{\lambda^-_n \left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n}{(\omega + E_\text{gs})^{n}} + \frac{\braket{\vec k_0 | c_{\vec R, \sigma}^\dagger | \vec k} \braket{\vec k | c_{\vec R + \vec r, \sigma} | \vec k_0}}{\omega - E_\text{gs}}\sum_n \frac{\lambda^+_n \left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n}{(\omega - E_\text{gs})^{n}}\right]\\
-	&= \sum_{\vec k}\left[\frac{\braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} \braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}}{\omega + E_\text{gs} - N\mathcal{H}_{\vec k, \vec k}(\vec R_0)} + \frac{\braket{\vec k_0 | c_{\vec R, \sigma}^\dagger | \vec k} \braket{\vec k | c_{\vec R + \vec r, \sigma} | \vec k_0}}{\omega - E_\text{gs} + N\mathcal{H}_{\vec k, \vec k}(\vec R_0)}\right]
-\end{aligned}\end{equation}
-Because of strong correlations in the model, the ground-state energy \(\varepsilon_\text{gs}\) of the auxiliary model can be approximated as \(\varepsilon_\text{gs} \sim E_\text{egs}/N\).
-Moreover, the operator matrix elements in the numerator evaluate to simple phase factors:
-\begin{eqnarray}
-	&\braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} &= \sum_{\vec q} e^{-i\vec q \cdot \left( \vec R + \vec r \right)} \braket{\vec k_0 | c_{\vec q, \sigma} | \vec k} = \sum_{\vec q} \theta(|\vec q| - |\vec k_F|) e^{-i\vec q \cdot \left( \vec R + \vec r \right)} \braket{\vec k_0 + \vec q | \vec k} \\
-	 &&=  \theta(|\vec k - \vec k_0| - |\vec k_F|) e^{-i\left(\vec k - \vec k_0\right) \cdot \left( \vec R + \vec r \right)} \\
-	&\braket{\vec k_0 | c^\dagger_{\vec R, \sigma} | \vec k} &= \sum_{\vec q} e^{i\vec q \cdot \vec R} \braket{\vec k_0 | c^\dagger_{\vec q, \sigma} | \vec k} = \sum_{\vec q} \theta(|\vec k_F| - |\vec q|) e^{i\vec q \cdot \left( \vec R + \vec r \right)} \braket{\vec k_0 - \vec q | \vec k} \\
-	 &&=  \theta(|\vec k_F| - |\vec k_0 - \vec k|) e^{i\left(\vec k - \vec k_0\right) \cdot \left( \vec R + \vec r \right)} \\
-	 &\braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k}\braket{\vec k | c^\dagger_{\vec R, \sigma} | \vec k_0} &= \theta(|\vec k - \vec k_0| - |\vec k_F|)e^{-i\left(\vec k - \vec k_0\right) \cdot \vec r},\\
-	&\braket{\vec k_0 | c_{\vec R, \sigma}^\dagger | \vec k} \braket{\vec k | c_{\vec R + \vec r, \sigma} | \vec k_0} &= \theta(|\vec k_F| - |\vec k_0 - \vec k|)e^{i\left(\vec k - \vec k_0\right) \cdot \vec r}
-\end{eqnarray}
-With these inputs, we can write down the final form of the Greens function:
-\begin{equation}\begin{aligned}
-	G(\vec r, \omega) = \sum_{\vec k}\left[\frac{\theta(|\vec k - \vec k_0| - |\vec k_F|) e^{i\left(\vec k - \vec k_0\right) \cdot \vec r}}{\omega + N\varepsilon_\text{gs} - N\mathcal{H}_{\vec k, \vec k}} + \frac{\theta(|\vec k_F| - |\vec k_0 - \vec k|) e^{-i\left(\vec k - \vec k_0\right) \cdot \vec r}}{\omega - N\varepsilon_\text{gs} + N\mathcal{H}_{\vec k, \vec k}}\right]
-\end{aligned}\end{equation}
-In this expression, the state \(\ket{\vec k}\) represents one of total momentum.
-One can write this in terms of single-particle excitations \(\ket{\vec q},~\vec q = \vec k - \vec k_0\), which is equal to \(c^\dagger_q \ket{\vec k_0}\) when \(q > 0\) and \(c_q \ket{\vec k_0}\) when \(q < 0\).
-In terms of these single-particle excitations, the Greens function can be written as
-\begin{equation}\begin{aligned}
-	G(\vec r, \omega) = \sum_{\vec q}\left[\frac{\theta(|\vec q| - |\vec k_F|) e^{i\vec q \cdot \vec r}}{\omega + N\varepsilon_\text{gs} - N\mathcal{E}^p_{\vec q}} + \frac{\theta(|\vec k_F| - |- \vec q|) e^{-i\vec q \cdot \vec r}}{\omega - N\varepsilon_\text{gs} + N\mathcal{E}^h_{\vec q}}\right]~,
-\end{aligned}\end{equation}
-where the matrix elements \(\mathcal{E}^p\) and \(\mathcal{E}^h\) for the particle and hole excitations are given by \(\mathcal{E}^p_{\vec q} = \mathcal{H}_{\vec k_0 + \vec q, \vec k_0 + \vec q} = \braket{\vec k_0 | c_{\vec q} \mathcal{H} c^\dagger_{\vec q} | \vec k_0}\) and \(\mathcal{E}^h_{\vec q} = \mathcal{H}_{\vec k_0 - \vec q, \vec k_0 - \vec q} = \braket{\vec k_0 | c^\dagger_{\vec q} \mathcal{H} c_{\vec q} | \vec k_0}\).
-For models with strong local correlations, it might be more convenient to express these \(k-\)space single-particle matrix elements in terms of real-space fluctuations:
-\begin{equation}\begin{aligned}
-\mathcal{E}^h_{\vec q} = \sum_{\vec x_{+},\vec x_{-}}e^{i\left( \vec x_+ - \vec x_- \right) \cdot \vec q}\braket{\vec k_0 | c^\dagger_{\vec x_-} \mathcal{H} c_{\vec x_+} | \vec k_0}, \quad \mathcal{E}^p_{\vec q} = \sum_{\vec x_{+},\vec x_{-}}e^{i\left(\vec x_+ - \vec x_- \right) \cdot \vec q}\braket{\vec k_0 | c_{\vec x_+} \mathcal{H} c^\dagger_{\vec x_-} | \vec k_0}
-\end{aligned}\end{equation}
-Guided by the fact that our auxiliary model has an emergent self-consistency at the impurity site, we retain distances \(|\vec x_+ - \vec x_-|\) up to one lattice spacing \(\vec a\) from the impurity, in the summation:
-\begin{equation}\begin{aligned}
-	\mathcal{E}^h_{\vec q} \to \braket{\vec k_0 | c^\dagger_{\vec R_0} \mathcal{H}\left(\vec R_0\right) c_{\vec R_0} | \vec k_0} + \sum_{\vec a}\left(e^{i\vec a \cdot \vec q}\braket{\vec k_0 | c^\dagger_{\vec R_0 + \vec a} \mathcal{H}\left(\vec R_0\right) c_{\vec R_0}| \vec k_0} + \text{h.c.}\right),\\
-	\quad \mathcal{E}^p_{\vec q} \to \braket{\vec k_0 | c_{\vec R_0} \mathcal{H}\left(\vec R_0\right) c^\dagger_{\vec R_0} | \vec k_0} + \sum_{\vec a}\left(e^{i\vec a \cdot \vec q}\braket{\vec k_0 | c_{\vec R_0} \mathcal{H}\left(\vec R_0\right) c_{\vec R_0 + \vec a}^\dagger| \vec k_0} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-
-\clearpage
-
-By substituting this for all the auxiliary model terms and by using the unitarity condition \(T^\dagger T = 1\), we get
-\begin{equation}\begin{aligned}
-	\mathcal{U}(\vec r) &= \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_c} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_0) | T_{\vec R_i - \vec R_0} c_{\vec R + \vec r, \sigma} T^\dagger_{\vec R_c - \vec R_0} \mathcal{H}\left(\vec R_0\right) T_{\vec R_c - \vec R_0} c_{\vec R, \sigma}^\dagger T^\dagger_{\vec R_j - \vec R_0} | \psi_\text{aux}(\vec R_0)}\\
-					     &= \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_c} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_0) | T_{\vec R_i - \vec R_c} c_{\vec R + \vec r + \vec R_0 - \vec R_c, \sigma} \mathcal{H}\left(\vec R_0\right) c_{\vec R + \vec R_0 - \vec R_c, \sigma}^\dagger T^\dagger_{\vec R_j - \vec R_c} | \psi_\text{aux}(\vec R_0)}
-\end{aligned}\end{equation}
-Since each summation is over all lattice translation vectors, we can make the substitutions \(\vec R_{i(j)} \to \vec R_{i(j)} - \vec R_c\), followed by \(\vec R_c \to \vec R + \vec R_0 - \vec R_c\), to get
-\begin{equation}\begin{aligned}
-	\mathcal{U}(\vec r) &= \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_c} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_0) | T_{\vec R_i} c_{\vec R_c + \vec r, \sigma} \mathcal{H}\left(\vec R_0\right) c_{\vec R_c, \sigma}^\dagger T^\dagger_{\vec R_j} | \psi_\text{aux}(\vec R_0)}\\
-					     &=\frac{1}{\lambda_{\vec k_0}^2}\sum_{\vec R_c} \braket{\psi_\text{aux}(\vec R_0) | \tilde c_{\vec R_c + \vec r, \sigma} \mathcal{H}\left(\vec R_0\right) \tilde c_{\vec R_c, \sigma}^\dagger | \psi_\text{aux}(\vec R_0)}
-\end{aligned}\end{equation}
-where we have defined the modified creation operator 
-\begin{equation}\begin{aligned}
-	\tilde c^\dagger_{\vec R_c} = c^\dagger_{\vec R_c} \frac{1}{N}\sum_{\vec R_j} e^{i \vec R_j \cdot \vec k_0} T^\dagger_{\vec R_j} = c^\dagger_{\vec R_c} \frac{1}{N}\sum_{\vec R_j, \vec k} e^{i \vec R_j \cdot \vec k_0} e^{-i \vec R_j \cdot \vec k} \ket{\vec k}\bra{\vec k} = c^\dagger_{\vec R_c} \frac{1}{N}\sum_{\vec k} N \delta_{\vec k,\vec k_0} \ket{\vec k}\bra{\vec k} = c^\dagger_{\vec R_c} \ket{\vec k_0}\bra{\vec k_0}~.
-\end{aligned}\end{equation}
-\(\ket{\vec k}\) is the many-body eigenstate of the kinetic energy operator, with total momentum \(\vec k\).
-Because of translation invariance, the matrix element \(\mathcal{C}(\vec R + \vec r, \vec R)\) is independent of the absolute position \(\vec R\) and depends only on the relative distance \(\vec r\).
-The above relation ensures that in order to calculate the correlation \(\mathcal{C}(\vec r)\) in the bulk Hamiltonian, we need only solve the auxiliary model at \(\vec R_0\) and calculate the matrix elements of the operators \(\tilde c_{\vec R_c + \vec r, \sigma} \mathcal{H}\left(\vec R_0\right) \tilde c_{\vec R_c, \sigma}^\dagger\) in the auxiliary model ground-state.
-
-As discussed above, the local nature of the auxiliary models (onsite matrix element only on the impurity and non-local matrix element only between impurity and zeroth site) renders all diagonal matrix elements zero, except the one for \(i=j\):
-\begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | i} = \braket{i | \mathcal{H}_\text{aux,i} | i} = \braket{\psi_\text{aux} | c_{i\sigma} e^{-i \vec{k}\cdot\vec{R}_i} \mathcal{H}_\text{aux,i} e^{i \vec{k}\cdot\vec{R}_i} c^\dagger_{i\sigma} | \psi_\text{aux}} = \braket{\psi_\text{aux} | c_{i\sigma} \mathcal{H}_\text{aux,i} c^\dagger_{i\sigma} | \psi_\text{aux}} = \braket{\psi_\text{aux} | c_{d\sigma} \mathcal{H}_\text{aux} c^\dagger_{d\sigma} | \psi_\text{aux}}
-\end{aligned}\end{equation}
-At the last step, we recognised \(i\) as the impurity site and rewrote the expression entirely in terms of a site-independent auxiliary model.
-Similarly, the off-diagonal matrix element between two nearest-neighbour sites \(i,j\) is obtained as
-\begin{equation}\begin{aligned}
-	\braket{i | H_\text{H-H} | j} = \braket{i | \left(\mathcal{H}_\text{aux,i} + \mathcal{H}_\text{aux,j}\right) | j} = \frac{1}{w}\braket{\psi_\text{aux} | c_{i\sigma} e^{-i \vec{k}\cdot\vec{R}_i} \left(\mathcal{H}_\text{aux,i,j} + \mathcal{H}_\text{aux,j,i}\right) e^{i \vec{k}\cdot\vec{R}_j} c^\dagger_{j\sigma} | \psi_\text{aux}} \\
-	= \frac{1}{w}e^{i \vec{k}\cdot\left(\vec{R}_j - \vec{R}_i\right)}\braket{\psi_\text{aux} | \left(c_{d\sigma}\mathcal{H}_\text{aux} c^\dagger_{0\sigma} + c_{0\sigma}\mathcal{H}_\text{aux} c^\dagger_{d\sigma}\right) | \psi_\text{aux}}
-\end{aligned}\end{equation}
-\(\mathcal{H}_\text{aux,i,j}\) is the auxiliary model with \(i\) as the impurity site and \(j\) as the bath zeroth site.
-
-We now define the Greens {\it operators}:
-\begin{equation}\begin{aligned}
-	\mathcal{G}_{H-H} = \frac{1}{\omega - \left(H_{H-H} - E_\text{gs}\right) }, \mathcal{G}_\text{aux}(i) = \frac{1}{\omega - \left(\mathcal{H}_\text{aux}(i) - E_\text{gs}\right)}
-\end{aligned}\end{equation}
-Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian and also of the full model \(\mathcal{H}_{H-H}\).
-Rewriting eq.~\ref{siam_to_hubb} in terms of the operators \(\mathcal{G}\), we get
-\begin{equation}\begin{aligned}
-\sum_i \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i)\right) = \omega + E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_i \mathcal{G}^{-1}_\text{aux}(i) = \mathcal{G}^{-1}_{H-H}~,
-\end{aligned}\end{equation}
-We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model.
-Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(\mathcal{H}_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate.
-We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \frac{1}{w}\sum_j \sum_{k \in \text{NN of j}}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(j,k) c^\dagger_{i\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-The superscript \(p\) indicates that this is the particle propagation matrix element.
-Under the single site approximation, we ignore the hopping between multiple impurity that reside in separate instances of the auxiliary model.
-Therefore, the only operator \(\mathcal{G}^{-1}_\text{aux}(j)\) that affects the matrix element is \(j=i, k \in \text{NN of i}\).
-Moreover, because of translation invariance, all \(k\) are equivalent.
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \frac{1}{w} w\times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i) c^\dagger_{i\sigma} | \Phi_0} = \braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{d\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-where we have identified site \(i\) in the auxiliary model as the impurity.
-By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}(d)\), we get from the spectral representation
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{m,n} \braket{\Phi_0 | c_{d\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux}(d) \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d\sigma} | \Phi_0} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}
-\end{aligned}\end{equation}
-There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(\mathcal{H}_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\).
-We also defined \(d^p_n = \bra{\Phi_n}c^\dagger_{d\sigma}\ket{\Phi_0}\).
-The hole propagation matrix element can be obtained similarly:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn} 
-\end{aligned}\end{equation}
-where \(d^h_n = \bra{\Phi_n}c_{d\sigma}\ket{\Phi_0}\).
-The off-diagonal matrix elements can also be obtained similarly.
-The difference from the diagonal case is that only one out of the \(w\) nearest-neighbour pairs contributes to the matrix element:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{i,i+1} \equiv \braket{\Phi_0 | c_{i,\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{w}\braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i,i+1) c^\dagger_{i+1,\sigma} | \Phi_0} = \frac{1}{w}\braket{\Phi_0 | c_{d\sigma} \mathcal{G}^{-1}_\text{aux}(d) c^\dagger_{z,\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-Here, we identity \(i+1\) as the bath zero mode \(z\) and \(i\) as the impurity \(d\).
-We again define matrix elements \(z_n^p = \braket{\Phi_n | c^\dagger_{z\sigma} | \Phi_0}, z_n^h = \braket{\Phi_n | c_{z\sigma} | \Phi_0}\).
-Thus, the spectral representation of the matrix element is obtained as
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}
-\end{aligned}\end{equation}
-The hole counterpart is
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}
-\end{aligned}\end{equation}
-In summary, the spectral representation of the matrix elements of the four inverse Greens operators are given by
-\begin{gather}
-\label{green_eq_final_siam}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega)\right)_{nn}\\
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}^{-1}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}^{-1}_\text{aux}(d, -\omega) \right)_{nn}
-\end{gather}
-
-In order to obtain the matrix elements of the Greens operators \(\mathcal{G}_{H-H}\) (as compared to its inverse), we note that we have just observed that the matrix elements of the inverse Greens operators are related to the matrix elements of another inverse operator through some coefficients.
-We can, therefore, use the identity
-\begin{equation}\begin{aligned}
-\left(\hat O\right)_{ij} = \bra{i} \hat O \ket{j} = \sum_{m,n} \braket{i|m} \left(\hat O\right)_{mn} \braket{n|j} \implies \left(\hat O^{-1}\right)_{ij} = \sum_{m,n} \braket{i|m} \left(\hat O^{-1}\right)_{mn} \braket{n|j}
-\end{aligned}\end{equation}
-We can now identify \(\left(\hat O^{-1}\right)_{mn}\) as the matrix elements of \(\mathcal{G}_\text{aux}^{-1}\) in our expressions.
-Using the above relation, we can therefore write the spectral representation of the matrix elements of the Greens operators as
-\begin{gather}
-	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\\
-	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{1}{w} \sum_n \left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn}, ~ ~ ~ \left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{1}{w} \sum_n \left(d^h_n\right)^* z^h_n \left(\mathcal{G}_\text{aux}(d, -\omega) \right)_{nn}
-\end{gather}
-
-The Lehmann-Kallen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements.
-Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
-\begin{equation}\begin{aligned}
-	\label{greens_func_siam}
-	\left(G_{H-H}(\omega)\right)_\text{loc} = \left(G_{H-H}(\omega)\right)_{ii}^p - \left(G_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right] \\
-	= G(\omega)_\text{aux,dd}
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-	\left(G_{H-H}(\omega)\right)_\text{n-n} = \left(G_{H-H}(\omega)\right)_{i,i+1}^p - \left(G_{H-H}(-\omega)\right)_{i+1,i}^h = \frac{1}{w}\sum_n \left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega) \right)_{nn} \right.\\
- - \left.\left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]= \frac{1}{w}G(\omega)_\text{aux,dz}
-\end{aligned}\end{equation}
+	G_\text{H-H}(\vec r, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c(\vec R + r,t), c^\dagger(\vec R) \right\} | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+where the bulk Hamiltonian \(H_\text{H-H}\) leads to the dynamics of the annihilation operator: \(c(\vec R + r,t) = e^{i H_\text{H-H} t}c(\vec R + r)e^{-i H_\text{H-H} t}\).
+Following eq.~\ref{siam_to_hubb}, the exponential can be written as:
+\begin{equation}\begin{aligned}
+e^{i H_\text{H-H} t} = \exp\left[\sum_i t\mathcal{H}_\text{aux}(\vec R_i)\right] 
+\end{aligned}\end{equation}
+In order to simplify this expression, we rewrite the sum over the auxiliary models in terms of a uniform piece \(\sum_{i}\mathcal{H}_\text{aux}(\vec R_0)\) and a difference piece \(\Delta(i) = \mathcal{H}_\text{aux}(\vec R_i) - \mathcal{H}_\text{aux}(\vec R_0)\):
+\begin{equation}\begin{aligned}
+	\sum_{\vec R_i} \mathcal{H}_\text{aux}(\vec R_i) = \sum_{\vec R_i} \left[\mathcal{H}_\text{aux}(\vec R_0) + \Delta(\vec R_i)\right] = N \left[\mathcal{H}_\text{aux}(\vec R_0) + \frac{1}{N}\sum_{\vec R_i} \Delta(\vec R_i)\right];
+\end{aligned}\end{equation}
+\(\vec R_0\) is the origin of the lattice, and \(N\) is the number of lattice sites.
+The uniform piece \(\sum_{i}\mathcal{H}_\text{aux}(\vec R_0)\) acts as the "center-of-mass" Hamiltonian - it responds to spectral flow brought about by changes in boundary conditions.
+The other piece acts as a "relative motion" Hamiltonian and is insensitive to changes in the boundary conditions, because any spectral flow of the auxiliary model Hamiltonians gets cancelled out in the difference operation.
+While the COM Hamiltonian is a thermodynamically large object, the number of terms in teh difference piece is only of the order of unity (the sum over \(\vec R_i\) is cancelled out by the \(1/N\) factor).
+We can therefore expand the exponential in the ratio of the relative piece to the COM piece:
+\begin{equation}\begin{aligned}
+	e^{i H_\text{H-H} t} = e^{i t N \mathcal{H}_\text{aux}(\vec R_0)}\left[1 + \frac{1}{N \mathcal{H}_\text{aux}(\vec R_0)}\sum_{\vec R_i} \Delta(\vec R_i) + \ldots\right];
+\end{aligned}\end{equation}
+In the limit of large \(N\), we retain only the leading piece in the expansion, resulting in the full bulk model in the time-dependence getting replaced by \(N\) times the COM piece:
+\begin{equation}\begin{aligned}
+	c(\vec R + r,t) \simeq e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}
+\end{aligned}\end{equation}
+On substituting this into the expression for the single-particle Greens function, we get
+\begin{equation}\begin{aligned}
+	G_\text{H-H}(\vec r, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R) \right\} | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+We will now express the ground-state in terms of the auxiliary model states, following eq.~\ref{bloch-states}:
+\begin{equation}\begin{aligned}
+	\ket{\Psi_\text{gs}} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j} e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j)}~.
+\end{aligned}\end{equation}
+We again simplify the wavefunction by keeping only the uniform piece and dropping the difference pieces:
+\begin{equation}\begin{aligned}
+	\ket{\Psi_\text{gs}} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j} e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j)} = \sum_{\vec a \in \text{NN of}\vec R_0}\frac{1}{\mathcal{Z}\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0, \vec a)} + \ket{\psi_\text{diff}(\vec k_0)}
+\end{aligned}\end{equation}
+where \(\ket{\psi_\text{diff}(\vec k_0)} = \ket{\Psi_\text{gs}} - \frac{1}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j} \left[e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j)} - e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)}\right]\), and we have brought back the explicit sum over the nearest neighbours \(\vec a\) of the impurity site (following eq.~\ref{zeroth_site_average}).
+By retaining only the auxiliary model state with the impurity at \(\vec R_0\) and the , the Greens function can be expressed as
+\begin{equation}\begin{aligned}
+	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2}i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R) \right\} | \psi_\text{aux}(\vec R_0)}~.
+\end{aligned}\end{equation}
+Because of translation symmetry of the bulk lattice, the initial point \(\vec R\) of the excitation can be shifted to the origin \(\vec R_0\) without any loss of generality:
+\begin{equation}\begin{aligned}
+	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2}i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0)}~.
+\end{aligned}\end{equation}
+In this form, the only Hamiltonian involved in the expression is the COM Hamiltonian at \(\vec R_0\), and \(G_\text{H-H}(\vec r, t)\) is therefore captured by the auxiliary model Greens function \(\mathcal{G}\) for the propagation of an excitation between the impurity site \(\vec R_0\) and a bath site at a distance \(\vec r\) from the impurity:
+\begin{equation}\begin{aligned}
+	\label{greens_func_relation}
+	G_\text{H-H}(\vec r, t) &= \frac{1}{\lambda_{\vec k_0}^2}\mathcal{G}(d,d+\vec r;t)~.
+\end{aligned}\end{equation}
+The cursive script symbol \(\mathcal{G}\) has been used to denote the Greens function for the auxiliary model \(\mathcal{H}\).
+
+The difference in the COM wavefunction and the full wavefunction can be estimated by calculating the norm of the difference piece:
+\begin{equation}\begin{aligned}
+	||\ket{\Psi_\text{gs}} - \frac{1}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)}||^2 &= |1 + \frac{1}{\lambda_{\vec k_0}^2} - \left[\frac{1}{\lambda_{\vec k_0}}e^{i \vec{k_0}\cdot\vec{R_0}}\braket{\Psi_\text{gs} | \psi_\text{aux}(\vec R_0)} + \text{h.c.}\right]| \\
+	&=|1 + \frac{1}{\lambda_{\vec k_0}^2} - \frac{1}{\lambda_{\vec k_0}^2 N}\sum_{\vec R_j} \left(e^{i \vec k_0 \cdot \left( \vec R_j - \vec R_0 \right)}  \braket{\psi_\text{aux}(\vec R_0) | \psi_\text{aux}(\vec R_j) } + \text{h.c.}\right)|\\
+	&=|1 + \frac{1}{\lambda_{\vec k_0}^2} - \frac{1}{\lambda_{\vec k_0}^2 N}\sum_{\vec R_j,\vec q} \left(e^{i \left(\vec k_0 - \vec q\right)\cdot \left( \vec R_j - \vec R_0 \right)}\lambda_{\vec q}^2 + \text{h.c.}\right)|\\
+	&= |1 - \frac{1}{\lambda_{\vec k_0}^2}|
+\end{aligned}\end{equation}
+By choosing an appropriate auxiliary model, the overlap factor \(\lambda_{\vec k_0}\) can be brought close to unity, leading to a smaller difference.
+
+The local Greens function \((\vec r=0)\)of the full model can thus be computed from the impurity local Greens function \(\mathcal{G}_{dd}\) of the auxiliary model.
+The nearest neighbour Greens function is given by the auxiliary model Greens function \(\mathcal{G}_{dz}\) between the impurity site and the bath zeroth site coupled to it.
+By using these real-space Greens functions, one can then compute \(k-\)space Greens functions of the full model.
+Moreover, this approach holds for any \(n-\)-particle Greens function; we just need to compute the corresponding correlator in the auxiliary model.
 
@@
 As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
-As we do not have real space Greens function that are more non-local than nearest neighbour, we will attempt to obtain momentum space Greens function from these two contributions:
+Given that our auxiliary model shows an emergent self-consistency on the impurity site and on the link between the impurity and the zeroth site, we approximate the \(k-\)space Greens functions from the local and nearest-neighbour contributions, by usingthe mapping between the bulk Greens function \(G\) and auxiliary model Greens functions \(\mathcal{G}\)(eq.~\ref{greens_func_relation}):
 \begin{equation}\begin{aligned}
@@
 	\label{k_Gf_siam}
-	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} = G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k}\\
-			     &= \sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right) \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
-\end{aligned}\end{equation}
-where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\). For example, on a d-dimensional hypercubic lattice, we obtain
-\begin{equation}\begin{aligned}
-	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i
-\end{aligned}\end{equation}
-On a 2D square lattice with lattice spacing $a$, this simplifies to
-\begin{eqnarray}
-	\label{2dsquaretb}
-\xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
-\end{eqnarray}
-where \(\epsilon_{\vec{q}} = -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})\) is the tight-binding dispersion.
-
-We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
-\begin{equation}\begin{aligned}
-	A_\text{H-H}(\vec{k},\omega) &= -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega))\\ 
-	&= -\frac{1}{\pi} \textrm{Im}\sum_n\left[\left(|d^p_n|^2 + \frac{\xi_{\vec k}}{w}\left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(|d^h_n|^2 + \frac{\xi_{\vec k}}{w}\left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\\
-	&= A_\text{aux,dd} + \frac{\xi_{\vec k}}{w} A_\text{aux,dz}
-\end{aligned}\end{equation}
-where 
-\begin{eqnarray}
-G_\text{aux,dd} &=& \sum_n\left[|d^p_n|^2 \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - |d^h_n|^2 \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]\nonumber\\
-G_\text{aux,dz} &=& \sum_n\left[\left(d^p_n\right)^* z^p_n \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn} - \left(z^h_n\right)^* d^h_n \left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\right]
-\end{eqnarray}
-and the spectral function $A_\text{aux,dd}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dd}$~,~$A_\text{aux,dz}=-\frac{1}{\pi}\textrm{Im}G_\text{aux,dz}$.
-Further,
-\begin{equation}\begin{aligned}
-A_\text{H-H}(\vec{r}=0,\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{r}=0,\omega)) 
-= A_\text{aux,dd}
-\label{main}
-\end{aligned}\end{equation}
+	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{G}_{dd}(\omega) + \mathcal{G}_{dz}(\omega) \xi_{\vec k}\right]~,
+\end{aligned}\end{equation}
+where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\), it being essentially the disperson in units of the hopping strength \(t\).
+For example, on a d-dimensional hypercubic lattice, we obtain
+\begin{equation}\begin{aligned}
+	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i~,
+\end{aligned}\end{equation}
+leading to \(2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}\) on a 2D square lattice.
+
+The spectral function is simply the imaginary part of the Greens function: \(A_\text{H-H} = -\frac{1}{\pi}\text{Im}\left[G_{H-H}\right] \); as a result, they have similar relations with their auxiliary model counterparts:
+\begin{equation}\begin{aligned}
+	\left(A_\text{H-H}\right)_\text{loc}(\omega) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{A}_{dd}~,\\
+	A_\text{H-H}(\vec{k},\omega) = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{A}_{dd} + \xi_{\vec k} \mathcal{A}_{dz} \right]~,
+\end{aligned}\end{equation}
+where \(\left(A_\text{H-H}\right)_\text{loc}(\omega)\) and \(A_\text{H-H}(\vec{k},\omega)\) are the local and \(k-\)space spectral functions, respectively, of the bulk model, and \(\mathcal{A}_{dd}\) and \(\mathcal{A}_{dz}\) are the auxiliary model spectral functions for local and nearest neighbour fluctuations respectively.
 
@@
 \begin{equation}\begin{aligned}
-	\left(\Sigma_\text{H-H}(\omega)\right)_\text{loc} = \left(\left(G_{H-H}(\omega)\right)_\text{loc}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_\text{loc}\right)^{-1} = \left(G(\omega)_\text{aux,dd}^{(0)}\right)^{-1} - \frac{1}{w}\left(G(\omega)_\text{aux,dd}\right)^{-1} \\
-	\left(\Sigma_\text{H-H}(\omega)\right)_\text{n-n} = \left(\left(G_{H-H}(\omega)\right)_\text{n-n}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_\text{n-n}\right)^{-1} = \left(G(\omega)_\text{aux,dz}^{(0)}\right)^{-1} - \frac{1}{w}\left(G(\omega)_\text{aux,dz}\right)^{-1}\\
+	\left(\Sigma_\text{H-H}(\omega)\right)_\text{loc} = \left(\left(G_{H-H}(\omega)\right)_\text{loc}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_\text{loc}\right)^{-1} = \left(G(\omega)_\text{aux,dd}^{(0)}\right)^{-1} - \frac{1}{\mathcal{Z}}\left(G(\omega)_\text{aux,dd}\right)^{-1} \\
+	\left(\Sigma_\text{H-H}(\omega)\right)_\text{n-n} = \left(\left(G_{H-H}(\omega)\right)_\text{n-n}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_\text{n-n}\right)^{-1} = \left(G(\omega)_\text{aux,dz}^{(0)}\right)^{-1} - \frac{1}{\mathcal{Z}}\left(G(\omega)_\text{aux,dz}\right)^{-1}\\
 \end{aligned}\end{equation}
@@
 	\label{self-energy1}
-	\Sigma_{H-H}(\vec k,\omega) = \left(\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_{\vec k}\right)^{-1} = \frac{1}{G(\omega)_\text{aux,dd}^{(0)} + \frac{\xi_{\vec k}}{w}G(\omega)_\text{aux,dz}^{(0)}} -  \frac{1}{G(\omega)_\text{aux,dd} + \frac{\xi_{\vec k}}{w}G(\omega)_\text{aux,dz}}
+	\Sigma_{H-H}(\vec k,\omega) = \left(\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_{\vec k}\right)^{-1} = \frac{1}{G(\omega)_\text{aux,dd}^{(0)} + \frac{\xi_{\vec k}}{\mathcal{Z}}G(\omega)_\text{aux,dz}^{(0)}} -  \frac{1}{G(\omega)_\text{aux,dd} + \frac{\xi_{\vec k}}{\mathcal{Z}}G(\omega)_\text{aux,dz}}
 \end{aligned}\end{equation}
@@
 \begin{eqnarray}
-r^{*} &=& \frac{U_{H-H}^{*}}{J_{H-H}^{*}} = \frac{w}{4}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)
+	r^{*} &=& \frac{U_{H-H}^{*}}{J_{H-H}^{*}} = \frac{\mathcal{Z}}{4}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)
 \end{eqnarray}
@@
 One can apply a test to this method: it involves considering the case of infinite number of nearest-neighbours $w\to\infty$ (the coordination number, and effectively the dimension).
-In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
+In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{\mathcal{Z}}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
 This allows a metal-insulator transition in the limit of $w\to\infty$ as well.
@@
 \begin{equation}\begin{aligned}
-	\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{w} G_\text{aux,dz}\right]^{-1}\right\} = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux,dd}(\omega)\right\}^{-1}
+	\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{\mathcal{Z}} G_\text{aux,dz}\right]^{-1}\right\} = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux,dd}(\omega)\right\}^{-1}
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
-For a coordination number of \(w\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
-Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{w}\).
+For a coordination number of \(\mathcal{Z}\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
+Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{\mathcal{Z}}\).
 In contrast, there is only one local Greens function, that for \(\vec r_i=0\).
@@
 \begin{equation}\begin{aligned}
-	H_\text{aux}(i,j) = \frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
+	H_\text{aux}(i,j) = \frac{1}{\mathcal{Z} - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
 \end{aligned}\end{equation}
@@
 	\label{22siam_to_hubb}
-	H_\text{full} = \sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
+	H_\text{full} = \sum_{\left<i,j\right>}\frac{1}{\mathcal{Z} - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
 \end{aligned}\end{equation}
@@
 	\item the first kind, \(A(i), A(j)\), depend only on either \(i\) or \(j\).
-They can be summed over easily by noting that the internal summation gives a constant factor of \(w-2\) which is canceled by the factor of \(1/(w-2)\) in the front, and the external summation gives \(\sum_{i,j}A(i) = \frac{w}{2} \sum_i A(i)\), because \(i\) is a member of \(w/2\) distinct nearest-neighbour pairs.
+They can be summed over easily by noting that the internal summation gives a constant factor of \(w-2\) which is canceled by the factor of \(1/(w-2)\) in the front, and the external summation gives \(\sum_{i,j}A(i) = \frac{\mathcal{Z}}{2} \sum_i A(i)\), because \(i\) is a member of \(w/2\) distinct nearest-neighbour pairs.
 	\item The second kind, \(B(i,j)\) depends on both \(i\) and \(j\).
@@
 	\label{2siam_to_hubb}
-	H_\text{full} &= \frac{2}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) = \frac{2}{w}\sum_{\left<i,j\right>}\frac{1}{w - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
+	H_\text{full} &= \frac{2}{\mathcal{Z}}\sum_{\left<i,j\right>} H_\text{aux}(i,j) = \frac{2}{\mathcal{Z}}\sum_{\left<i,j\right>}\frac{1}{\mathcal{Z} - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
 		      &= -\frac{1}{2}\left(2U + 8U_b/w\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{N}{w-2}t + 2t/w - 8V/w\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 8J/w \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
@@
 \begin{equation}\begin{aligned}
-	J_\text{H-H} = \frac{2}{w}\left(4J + 2J_d\right)
+	J_\text{H-H} = \frac{2}{\mathcal{Z}}\left(4J + 2J_d\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	H_\text{full} &= \frac{2}{w}\sum_{\left<i,j\right>} H_\text{aux}(i,j) \sim N H_\text{aux}(d_1,d_2)~.
+	H_\text{full} &= \frac{2}{\mathcal{Z}}\sum_{\left<i,j\right>} H_\text{aux}(i,j) \sim N H_\text{aux}(d_1,d_2)~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0} = \frac{2}{w} \times w \times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i, i+1) c^\dagger_{i\sigma} | \Phi_0} = 2\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0} = \frac{2}{\mathcal{Z}} \times w \times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i, i+1) c^\dagger_{i\sigma} | \Phi_0} = 2\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}
 \end{aligned}\end{equation}
@@
 	\begin{equation}\begin{aligned}
-		\frac{2}{w}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0} = \frac{2}{w}\sum_{n} \left(d^p_{1,n}\right)^*d^p_{2,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+		\frac{2}{\mathcal{Z}}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0} = \frac{2}{\mathcal{Z}}\sum_{n} \left(d^p_{1,n}\right)^*d^p_{2,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
 	\end{aligned}\end{equation}
@@
 	\begin{equation}
-		(w-2) \times \frac{2}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{0_1\sigma} | \Phi_0} = \frac{2}{w}\left(d^p_{1,n}\right)^* z^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+		(w-2) \times \frac{2}{\mathcal{Z}}\frac{1}{\mathcal{Z}-2}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{0_1\sigma} | \Phi_0} = \frac{2}{\mathcal{Z}}\left(d^p_{1,n}\right)^* z^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
 	\end{equation}
@@
 	\begin{equation}
-		(w-2) \times \frac{2}{w}\frac{1}{w-2}\braket{\Phi_0 | c_{0_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0} = \frac{2}{w}\left(z^p_{1,n}\right)^* d^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+		(w-2) \times \frac{2}{w}\frac{1}{\mathcal{Z}-2}\braket{\Phi_0 | c_{0_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0} = \frac{2}{w}\left(z^p_{1,n}\right)^* d^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
 	\end{equation}
@@
 For a coordination number of \(w\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
-Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{w}\).
+Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{\mathcal{Z}}\).
 In contrast, there is only one local Greens function, that for \(\vec r_i=0\).

### 2023-03-06 notes/notes.tex
added 1/Z factors

@@
 \end{aligned}\end{equation}
+Because of translation symmetry of the bulk lattice, the initial point \(\vec R\) of the excitation can be shifted to the origin \(\vec R_0\) without any loss of generality:
+\begin{equation}\begin{aligned}
+	G_\text{H-H}(\vec r, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
 We will now express the ground-state in terms of the auxiliary model states, following eq.~\ref{bloch-states}:
 \begin{equation}\begin{aligned}
-	\ket{\Psi_\text{gs}} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j} e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j)}~.
-\end{aligned}\end{equation}
-We again simplify the wavefunction by keeping only the uniform piece and dropping the difference pieces:
-\begin{equation}\begin{aligned}
-	\ket{\Psi_\text{gs}} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j} e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j)} = \sum_{\vec a \in \text{NN of}\vec R_0}\frac{1}{\mathcal{Z}\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0, \vec a)} + \ket{\psi_\text{diff}(\vec k_0)}
-\end{aligned}\end{equation}
-where \(\ket{\psi_\text{diff}(\vec k_0)} = \ket{\Psi_\text{gs}} - \frac{1}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j} \left[e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j)} - e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)}\right]\), and we have brought back the explicit sum over the nearest neighbours \(\vec a\) of the impurity site (following eq.~\ref{zeroth_site_average}).
-By retaining only the auxiliary model state with the impurity at \(\vec R_0\) and the , the Greens function can be expressed as
-\begin{equation}\begin{aligned}
-	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2}i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R) \right\} | \psi_\text{aux}(\vec R_0)}~.
-\end{aligned}\end{equation}
-Because of translation symmetry of the bulk lattice, the initial point \(\vec R\) of the excitation can be shifted to the origin \(\vec R_0\) without any loss of generality:
-\begin{equation}\begin{aligned}
-	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2}i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0)}~.
-\end{aligned}\end{equation}
-In this form, the only Hamiltonian involved in the expression is the COM Hamiltonian at \(\vec R_0\), and \(G_\text{H-H}(\vec r, t)\) is therefore captured by the auxiliary model Greens function \(\mathcal{G}\) for the propagation of an excitation between the impurity site \(\vec R_0\) and a bath site at a distance \(\vec r\) from the impurity:
+	\ket{\Psi_\text{gs}} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j, \vec a \in \text{NN of }\vec R_j} e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j, \vec a)}~,
+\end{aligned}\end{equation}
+where we have brought back the explicit sum over the nearest neighbours \(\vec a\) of the impurity site (following eq.~\ref{zeroth_site_average}).
+We again simplify the wavefunction by keeping only the uniform piece and dropping the difference pieces.
+\begin{equation}\begin{aligned}
+	\ket{\Psi_\text{gs}} = \sum_{\vec a \in \text{NN of}\vec R_0}\frac{1}{\mathcal{Z}\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0, \vec a)} + \ket{\psi_\text{diff}(\vec k_0)}
+\end{aligned}\end{equation}
+where \(\ket{\psi_\text{diff}(\vec k_0)} = \ket{\Psi_\text{gs}} - \frac{1}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j} \left[e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j)} - e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)}\right]\).
+Specifically, for the local Greens function, we keep the states with \(\vec R_j = \vec R_0\), leading to the expression
+\begin{equation}\begin{aligned}\label{greens_func_approx}
+	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{Z}^2}i\theta(t) \sum_{\vec a_1, \vec a_2}\braket{\psi_\text{aux}(\vec R_0, \vec a_2) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a_1)}~.
+\end{aligned}\end{equation}
+Because of the symmetry of the lattice, all Greens functions obtained for various positions of the zeroth site \(\vec a_1\) and \(\vec a_2\) are equal to their mean:
+\begin{equation}\begin{aligned}
+	G_\text{H-H}(\vec r=0, t) &= -\frac{1}{\lambda_{\vec k_0}^2 }i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0)}~.
+\end{aligned}\end{equation}
+In this form, the only Hamiltonian involved in the expression is the COM Hamiltonian at \(\vec R_0\), and \(G_\text{H-H}(\vec r=0, t)\) is therefore captured by the impurity Greens function \(\mathcal{G}\) in the auxiliary model \(N \mathcal{H}_\text{aux}(\vec R_0)\):
 \begin{equation}\begin{aligned}
 	\label{greens_func_relation}
-	G_\text{H-H}(\vec r, t) &= \frac{1}{\lambda_{\vec k_0}^2}\mathcal{G}(d,d+\vec r;t)~.
-\end{aligned}\end{equation}
-The cursive script symbol \(\mathcal{G}\) has been used to denote the Greens function for the auxiliary model \(\mathcal{H}\).
+	G_\text{H-H}(\vec r=0, t) &= \frac{1}{\lambda_{\vec k_0}^2}\mathcal{G}_{dd}(t)~.
+\end{aligned}\end{equation}
+The cursive script symbol \(\mathcal{G}_{dd}\) has been used to denote the impurity Greens function for the auxiliary model \(N \mathcal{H}_\text{aux}(\vec R_0)\).
+
+For the nearest neighbour Greens function \(G_\text{H-H}(\vec r=\vec a, t)\), we keep only the terms with \(\vec a_1 = \vec a_2\) in the summation of eq.~\ref{greens_func_approx}:
+\begin{equation}\begin{aligned}
+	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{Z}^2}i\theta(t) \sum_{\vec a_1}\braket{\psi_\text{aux}(\vec R_0, \vec a_1) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a_1)}~.
+\end{aligned}\end{equation}
+Again, because of the lattice symmetry, all values of \(\vec a_1\) lead to the same impurity-bath Greens function \(\mathcal{G}_{dz}\) on the auxiliary model:
+\begin{equation}\begin{aligned}
+	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{Z}}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} = \frac{1}{\lambda_{\vec k_0}^2 \mathcal{Z}} \mathcal{G}_{dz}(t)~.
+\end{aligned}\end{equation}
 
@@
 
-The local Greens function \((\vec r=0)\)of the full model can thus be computed from the impurity local Greens function \(\mathcal{G}_{dd}\) of the auxiliary model.
-The nearest neighbour Greens function is given by the auxiliary model Greens function \(\mathcal{G}_{dz}\) between the impurity site and the bath zeroth site coupled to it.
+The local and nearest-neighbour Greens functions of the full model can thus be computed from the impurity local Greens function \(\mathcal{G}_{dd}\) and the impurity-bath zeroth site Greens function \(\mathcal{G}_{dz}\) on the COM auxiliary model \(N \mathcal{H}_\text{aux}(\vec R_0)\).
 By using these real-space Greens functions, one can then compute \(k-\)space Greens functions of the full model.
@@
 \end{aligned}\end{equation}
-The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, w\right]\right\}$.
+The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, \mathcal{Z}\right]\right\}$.
 \begin{equation}\begin{aligned}
 	\label{k_Gf_siam}
-	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{G}_{dd}(\omega) + \mathcal{G}_{dz}(\omega) \xi_{\vec k}\right]~,
+	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^{\mathcal{Z}} e^{i \vec{k}\cdot\vec {a_i}} = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{G}_{dd}(\omega) + \frac{1}{\mathcal{Z}}\mathcal{G}_{dz}(\omega) \xi_{\vec k}\right]~,
 \end{aligned}\end{equation}
@@
 	\left(A_\text{H-H}\right)_\text{loc}(\omega) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{A}_{dd}~,\\
-	A_\text{H-H}(\vec{k},\omega) = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{A}_{dd} + \xi_{\vec k} \mathcal{A}_{dz} \right]~,
+	A_\text{H-H}(\vec{k},\omega) = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{A}_{dd} + \xi_{\vec k} \frac{1}{\mathcal{Z}^2}\mathcal{A}_{dz} \right]~,
 \end{aligned}\end{equation}

### 2023-03-07 notes/notes.tex
--no-message

@@
 The tight-binding term sums over all nearest pairs \((m,n)\) that do not involve the site \(i\).
-In general \(i\) will have \(\mathcal{Z}\) nearest neighbours for a lattice with coordination number \(\mathcal{Z}\).
+In general \(i\) will have \(\mathcal{W}\) nearest neighbours for a lattice with coordination number \(\mathcal{W}\).
 The total local Hamiltonian for the site \(i\) is obtained by averaging over the Hamiltonians \(\mathcal{H}_\text{aux}(i,j)\) for all nearest neighbours \(j\) of \(i\):
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(i) &= \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right)  \right.\\
+	\mathcal{H}_\text{aux}(i) &= \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right)  \right.\\
 				  &\left. +J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\\
-				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
+				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
 				  &\left.- U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& \sum_i \mathcal{H}_\text{aux}(i) = \sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
+	\mathcal{H}_\text{full} =& \sum_i \mathcal{H}_\text{aux}(i) = \sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
 				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\right]\\
-	=& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
+	=& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
 				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j\right]\right]
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - 2t\left(N-2\right)\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{\mathcal{Z}}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
+	\mathcal{H}_\text{full} =& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - 2t\left(N-2\right)\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{\mathcal{W}}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
 				  &+ \left. J \vec{S_i}\cdot\vec{S}_j\right]\\
-				  &=-\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(2t (N-2) - \frac{2V}{\mathcal{Z}}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{\mathcal{Z}} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
+				  &=-\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(2t (N-2) - \frac{2V}{\mathcal{W}}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{\mathcal{W}} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
 \end{aligned}\end{equation}
@@
 	\label{map_aux_bulk}
-	t_{H-H} = \left(2t (N-2) - \frac{2V}{\mathcal{Z}}\right),~ ~ U_{H-H} = \left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{\mathcal{Z}}
+	t_{H-H} = \left(2t (N-2) - \frac{2V}{\mathcal{W}}\right),~ ~ U_{H-H} = \left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{\mathcal{W}}
 \end{aligned}\end{equation}
@@
 with the impurity position \(\vec R_i\) and zeroth site position \(\vec R_i + \vec a\), to construct eigenstates of the bulk Hamiltonian.
-\(\vec R_i\) is a lattice vector, while \(\vec a\) is one of the \(\mathcal{Z}\) vectors that connect a lattice site with its nearest neighbours.
+\(\vec R_i\) is a lattice vector, while \(\vec a\) is one of the \(\mathcal{W}\) vectors that connect a lattice site with its nearest neighbours.
 This two site wavefunction can be obtained by first studying the full auxiliary model \(\mathcal{H}_\text{aux}\) under a renormalisation group, obtaining a fixed-point Hamiltonian in the IR, obtaining the IR eigenstate and then tracing out all lattice sites except the impurity and the zeroth site from this eigenstate.
@@
 \begin{equation}\begin{aligned}
-	\ket{\Psi^n_{\vec k}} = \frac{1}{\mathcal{Z} \sqrt N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
+	\ket{\Psi^n_{\vec k}} = \frac{1}{\mathcal{W} \sqrt N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
 \end{aligned}\end{equation}
@@
 	\label{bloch-states}
-	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
+	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k} | \Psi_{\vec k}} &= \frac{1}{\mathcal{Z}^2 \lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, a, a^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime, \vec a^\prime) | \psi_\text{aux}(\vec R, \vec a)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, }e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime) | \psi_\text{aux}(\vec R)}\\
+	\braket{\Psi_{\vec k} | \Psi_{\vec k}} &= \frac{1}{\mathcal{W}^2 \lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, a, a^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime, \vec a^\prime) | \psi_\text{aux}(\vec R, \vec a)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, }e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime) | \psi_\text{aux}(\vec R)}\\
 					       &=\frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) | \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)}\\
@@
 \(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
-Because of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(\mathcal{Z}\) choices.
+Because of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(\mathcal{W}\) choices.
 
@@
 \begin{equation}\begin{aligned}
-	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
+	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} \mathcal{Z} N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
+	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} \mathcal{W} N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
 	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
 \end{aligned}\end{equation}
-where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
+where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
 This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
@@
 	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
-	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
-	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
-						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
+						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
-	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}
+	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
+	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
 	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}
@@
 \begin{equation}\begin{aligned}
-	\ket{\Psi_\text{gs}} = \sum_{\vec a \in \text{NN of}\vec R_0}\frac{1}{\mathcal{Z}\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0, \vec a)} + \ket{\psi_\text{diff}(\vec k_0)}
+	\ket{\Psi_\text{gs}} = \sum_{\vec a \in \text{NN of}\vec R_0}\frac{1}{\mathcal{W}\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0, \vec a)} + \ket{\psi_\text{diff}(\vec k_0)}
 \end{aligned}\end{equation}
 where \(\ket{\psi_\text{diff}(\vec k_0)} = \ket{\Psi_\text{gs}} - \frac{1}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j} \left[e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j)} - e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)}\right]\).
-Specifically, for the local Greens function, we keep the states with \(\vec R_j = \vec R_0\), leading to the expression
+Specifically, for the local Greens function \(G_\text{H-H}(\vec r=0, t)\), we keep the states with \(\vec R_j = \vec R_0\), leading to the expression
 \begin{equation}\begin{aligned}\label{greens_func_approx}
-	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{Z}^2}i\theta(t) \sum_{\vec a_1, \vec a_2}\braket{\psi_\text{aux}(\vec R_0, \vec a_2) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a_1)}~.
-\end{aligned}\end{equation}
-Because of the symmetry of the lattice, all Greens functions obtained for various positions of the zeroth site \(\vec a_1\) and \(\vec a_2\) are equal to their mean:
-\begin{equation}\begin{aligned}
-	G_\text{H-H}(\vec r=0, t) &= -\frac{1}{\lambda_{\vec k_0}^2 }i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0)}~.
+	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}^2}i\theta(t) \sum_{\vec a_1, \vec a_2}\braket{\psi_\text{aux}(\vec R_0, \vec a_2) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a_1)}~.
+\end{aligned}\end{equation}
+Because of the symmetry of the lattice, all Greens functions obtained for various positions of the zeroth site \(\vec a_1\) and \(\vec a_2\) are equal to their mean, and the local Greens function simplifies to
+\begin{equation}\begin{aligned}
+	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) &= -\frac{1}{\lambda_{\vec k_0}^2 }i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0)}~.
 \end{aligned}\end{equation}
@@
 	\label{greens_func_relation}
-	G_\text{H-H}(\vec r=0, t) &= \frac{1}{\lambda_{\vec k_0}^2}\mathcal{G}_{dd}(t)~.
+	G_\text{loc}(t) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{G}_{dd}(t)~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{Z}^2}i\theta(t) \sum_{\vec a_1}\braket{\psi_\text{aux}(\vec R_0, \vec a_1) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a_1)}~.
+	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}^2}i\theta(t) \sum_{\vec a_1}\braket{\psi_\text{aux}(\vec R_0, \vec a_1) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a_1)}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{Z}}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} = \frac{1}{\lambda_{\vec k_0}^2 \mathcal{Z}} \mathcal{G}_{dz}(t)~.
+	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} = \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}} \mathcal{G}_{dz}(t)~.
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
-The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, \mathcal{Z}\right]\right\}$.
+The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, \mathcal{W}\right]\right\}$.
 \begin{equation}\begin{aligned}
 	\label{k_Gf_siam}
-	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^{\mathcal{Z}} e^{i \vec{k}\cdot\vec {a_i}} = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{G}_{dd}(\omega) + \frac{1}{\mathcal{Z}}\mathcal{G}_{dz}(\omega) \xi_{\vec k}\right]~,
+	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^{\mathcal{W}} e^{i \vec{k}\cdot\vec {a_i}} = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{G}_{dd}(\omega) + \frac{1}{\mathcal{W}}\xi_{\vec k}\mathcal{G}_{dz}(\omega) \right]~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(A_\text{H-H}\right)_\text{loc}(\omega) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{A}_{dd}~,\\
-	A_\text{H-H}(\vec{k},\omega) = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{A}_{dd} + \xi_{\vec k} \frac{1}{\mathcal{Z}^2}\mathcal{A}_{dz} \right]~,
+	\left(A_\text{H-H}\right)_\text{loc}(\omega) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{A}_{dd}~,\qquad A_\text{H-H}(\vec{k},\omega) = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{A}_{dd} + \frac{1}{\mathcal{W}}\xi_{\vec k}\mathcal{A}_{dz} \right]~,
 \end{aligned}\end{equation}
@@
 
-From the local Greens function, we can write down the local self-energy using Dyson's equation: \(\Sigma = \left(G^{(0)}\right)^{-1} - G^{-1}\).
-\(G^{(0)}\) is the non-interacting Greens function.
-Here, non-interacting is defined as the absence of \(U,J\) in the bulk model, and hence the absence of \(U,U_b,J\) in the auxiliary model.
-In real space, the local and nearest-neighbour self-energies are therefore
-\begin{equation}\begin{aligned}
-	\left(\Sigma_\text{H-H}(\omega)\right)_\text{loc} = \left(\left(G_{H-H}(\omega)\right)_\text{loc}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_\text{loc}\right)^{-1} = \left(G(\omega)_\text{aux,dd}^{(0)}\right)^{-1} - \frac{1}{\mathcal{Z}}\left(G(\omega)_\text{aux,dd}\right)^{-1} \\
-	\left(\Sigma_\text{H-H}(\omega)\right)_\text{n-n} = \left(\left(G_{H-H}(\omega)\right)_\text{n-n}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_\text{n-n}\right)^{-1} = \left(G(\omega)_\text{aux,dz}^{(0)}\right)^{-1} - \frac{1}{\mathcal{Z}}\left(G(\omega)_\text{aux,dz}\right)^{-1}\\
-\end{aligned}\end{equation}
-
-The \(k-\)space self-energy can be similarly obtained from the \(k-\)space Greens functions
-\begin{equation}\begin{aligned}
-	\label{self-energy1}
-	\Sigma_{H-H}(\vec k,\omega) = \left(\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)}\right)^{-1} - \left(\left(G_{H-H}(\omega)\right)_{\vec k}\right)^{-1} = \frac{1}{G(\omega)_\text{aux,dd}^{(0)} + \frac{\xi_{\vec k}}{\mathcal{Z}}G(\omega)_\text{aux,dz}^{(0)}} -  \frac{1}{G(\omega)_\text{aux,dd} + \frac{\xi_{\vec k}}{\mathcal{Z}}G(\omega)_\text{aux,dz}}
-\end{aligned}\end{equation}
-Just to clarify the notation, we reiterate that bulk quantities with a superscript \((0)\) are for the non-interacting Hamiltonian and defined at \(U_\text{H-H}=J_\text{H-H}=0\), while the auxiliary model quantities with that superscript are evaluated in the non-interacting auxiliary model at \(U=J=U_b=0\).
+From the knowledge of Greens function, one can write down self-energies using Dyson's equation \(\Sigma = \left(G^{(0)}\right)^{-1} - G^{-1}\), where \(G^{(0)}\) is the non-interacting Greens function.
 The non-interacting model is simply a resonant-level model with the impurity level at zero energy.
@@
 where \(\Delta = \pi \rho V^2\) is the hybridisation parameter, assuming a uniform density of states \(\rho\), and \(G(\omega)^{(0)}_{\vec k}\) is the free electron Greens function at momentum \(\vec k\).
+
+Following Dyson's equation, the \(k-\)space self-energy can be obtained from the \(k-\)space Greens functions:
+\begin{equation}\begin{aligned}
+	\label{self-energy1}
+	\Sigma_{H-H}(\vec k,\omega) = 1/\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)} - 1/\left(G_{H-H}(\omega)\right)_{\vec k} = \left(\frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{W}}\mathcal{G}_{dz}(\omega)}\right)^{(0)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{W}}\mathcal{G}_{dz}(\omega)}~,
+\end{aligned}\end{equation}
+where the superscript \((0)\) indicates that the entire term has to be calculated from the non-interacting auxiliary model.
 
@@
 
-\item The impurity spectral function \(A_{dd}(\omega)\) and the impurity-bath real space off-diagonal Greens function \(A_{d0}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
-The gap in the diagonal spectral function shows that the impurity site cannot fluctuate through gapless excitations, while the vanishing of the off-diagonal spectral function shows that an electron on the impurity site cannot delocalise out of that site.
+\item The impurity spectral function \(\mathcal{A}_{dd}(\omega)\) and the impurity-bath real space off-diagonal Greens function \(\mathcal{A}_{d0}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
+We show the former in fig.~\ref{spec_func_mit}.
+The gap in the diagonal spectral function show the absence of any gapless excitations that can allow the impurity configuration to, while the vanishing of the off-diagonal spectral function shows that this is because the entanglement between the impurity and the bath has been pinched out.
 Other measures like mutual information and spin-spin correlations also show a sharp change on crossing that value, demonstrating \textbf{the destruction of the Kondo cloud and the stabilisation of the local moment on the impurity}.
@@
 \begin{eqnarray}
-	r^{*} &=& \frac{U_{H-H}^{*}}{J_{H-H}^{*}} = \frac{\mathcal{Z}}{4}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)
+	r^{*} &=& \frac{U_{H-H}^{*}}{J_{H-H}^{*}} = \frac{\mathcal{W}}{4}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)
 \end{eqnarray}
 where $U^{*}$ and $J^{*}$ are the values of the on-site and Kondo couplings of the auxiliary model at the auxiliary model (i.e., the generalised SIAM with a correlated bath) at the transition between the Kondo screened and the local moment phases.
-Parametrising the bath correlation coupling as $U_{b}=-\frac{U}{10}$, we obtain $U^{*}/J^{*}=5/2$, and $r^{*} = 2$ for the 2D square lattice Hubbard-Heisenberg model (with coordination number $w=4$).
-In general, $w=2d$ for the $d$-dimensional hypercubic lattice, and
+Parametrising the bath correlation coupling as $U_{b}=-\frac{U}{10}$, we obtain $U^{*}/J^{*}=5/2$, and $r^{*} = 2$ for the 2D square lattice Hubbard-Heisenberg model (with coordination number $\mathcal{W}=4$).
+In general, $\mathcal{W}=2d$ for the $d$-dimensional hypercubic lattice, and
 $r^{*}_\text{hyperc.} = \frac{d}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)$.
@@
 \subsection{Entanglement as an order parameter for the transition}
-The spectral weights in the diagonal Greens function can be written in terms of a geometric measure of entanglement:
-\begin{equation}\begin{aligned}
-	d_n^p = \braket{\Phi_n | c^\dagger_{d\sigma} | \Phi_0} = \braket{\Phi_n | c^\dagger_{d\sigma} \sum_n \ket{\phi_m} \bra{\phi_m} | \Phi_0}
-\end{aligned}\end{equation}
-where, \(\ket{\phi_m}\) are the eigenstates of the Hamiltonian composed of a two-site system (formed by the impurity site and the zeroth site) in direct product with the rest of the lattice sites.
-The two site system interacts only via a spin-exchange coupling \(J\), and the impurity and bath sites have local correlations \(U\) and \(U_b\) respectively.
-The ground state is the spin-singlet in direct product with the ground state of the tight-binding chain formed by the remaining sites.
-The summation involves inner products of the ground state \(\ket{\Phi_0}\) with the eigenstates \(\ket{\phi_m}\).
-Only two states out of all \(\ket{\phi_m}\) give non-zero overlap - the spin singlet state \(\ket{SS}\) and the charge triplet-zero state \(\ket{CT}\).
-These two non-zero overlaps give rise to non-zero entanglement: \(\varepsilon_\text{SS} = 1 - |\braket{\Phi_0 | SS}|^2, \varepsilon_\text{CT} = 1 - |\braket{\Phi_0 | CT}|^2\).
-The spectral weight becomes
-\begin{equation}\begin{aligned}
-	d_n^p = \bra{\Phi_n} | c^\dagger_{d\sigma} \left(\ket{SS} + \ket{CT} \right) \left(\sqrt{1 - \varepsilon_\text{SS}} + \sqrt{1 - \varepsilon_\text{CT}}\right)
-\end{aligned}\end{equation}
-The total spectral weight can be written as
-\begin{equation}\begin{aligned}
-	|d_n^p|^2 = |\bra{\Phi_n} | c^\dagger_{d\sigma} \left(\ket{SS} + \ket{CT} \right)|^2 \left(2 - \varepsilon_\text{SS} - \varepsilon_\text{CT} + 2\sqrt{1 - \varepsilon_\text{SS}}\sqrt{1 - \varepsilon_\text{CT}}\right)
-\end{aligned}\end{equation}
-Near the metal, the ground state is, to a very good approximation, the state \(\ket{SS}\).
-One can then say that the entanglement \(\varepsilon_\text{SS}\) is poor - the entangled state is very close to the "separable" state.
-The term separable is used here in the sense that the metallic state defines a limit of the system.
-As \(U_b\) increases, \(\varepsilon_\text{SS}\) increases.
-On the other hand, the entanglement with the charge triplet is maximum in the metal, because the ground state does not have much of the charge triplet.
-Towards the MIT, this contribution increases, and the entanglement decreases.
+More refined version exists in the e-SIAM manuscript.
 
@@
 \section{Analytic consistency check - On the Bethe lattice}
-One can apply a test to this method: it involves considering the case of infinite number of nearest-neighbours $w\to\infty$ (the coordination number, and effectively the dimension).
-In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{\mathcal{Z}}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
-This allows a metal-insulator transition in the limit of $w\to\infty$ as well.
+We now apply our approach to the case of infinite number of nearest-neighbours $\mathcal{W}\to\infty$ (the coordination number, and effectively the dimension).
+In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{\mathcal{W}}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
+This allows a metal-insulator transition in the limit of $\mathcal{W}\to\infty$ as well.
 In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}.
@@
 \begin{equation}\begin{aligned}
-	\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{\mathcal{Z}} G_\text{aux,dz}\right]^{-1}\right\} = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux,dd}(\omega)\right\}^{-1}
+	\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{\mathcal{W}} G_\text{aux,dz}\right]^{-1}\right\} = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux,dd}(\omega)\right\}^{-1}
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
-For a coordination number of \(\mathcal{Z}\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
-Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{\mathcal{Z}}\).
+For a coordination number of \(\mathcal{W}\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
+Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{\mathcal{W}}\).
 In contrast, there is only one local Greens function, that for \(\vec r_i=0\).
@@
 \begin{equation}\begin{aligned}
-	H_\text{aux}(i,j) = \frac{1}{\mathcal{Z} - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
+	H_\text{aux}(i,j) = \frac{1}{\mathcal{W} - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
 \end{aligned}\end{equation}
@@
 	\label{22siam_to_hubb}
-	H_\text{full} = \sum_{\left<i,j\right>}\frac{1}{\mathcal{Z} - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
+	H_\text{full} = \sum_{\left<i,j\right>}\frac{1}{\mathcal{W} - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
 \end{aligned}\end{equation}
@@
 	\item the first kind, \(A(i), A(j)\), depend only on either \(i\) or \(j\).
-They can be summed over easily by noting that the internal summation gives a constant factor of \(w-2\) which is canceled by the factor of \(1/(w-2)\) in the front, and the external summation gives \(\sum_{i,j}A(i) = \frac{\mathcal{Z}}{2} \sum_i A(i)\), because \(i\) is a member of \(w/2\) distinct nearest-neighbour pairs.
+They can be summed over easily by noting that the internal summation gives a constant factor of \(w-2\) which is canceled by the factor of \(1/(w-2)\) in the front, and the external summation gives \(\sum_{i,j}A(i) = \frac{\mathcal{W}}{2} \sum_i A(i)\), because \(i\) is a member of \(w/2\) distinct nearest-neighbour pairs.
 	\item The second kind, \(B(i,j)\) depends on both \(i\) and \(j\).
@@
 	\label{2siam_to_hubb}
-	H_\text{full} &= \frac{2}{\mathcal{Z}}\sum_{\left<i,j\right>} H_\text{aux}(i,j) = \frac{2}{\mathcal{Z}}\sum_{\left<i,j\right>}\frac{1}{\mathcal{Z} - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
+	H_\text{full} &= \frac{2}{\mathcal{W}}\sum_{\left<i,j\right>} H_\text{aux}(i,j) = \frac{2}{\mathcal{W}}\sum_{\left<i,j\right>}\frac{1}{\mathcal{W} - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
 		      &= -\frac{1}{2}\left(2U + 8U_b/w\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{N}{w-2}t + 2t/w - 8V/w\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 8J/w \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
@@
 \begin{equation}\begin{aligned}
-	J_\text{H-H} = \frac{2}{\mathcal{Z}}\left(4J + 2J_d\right)
+	J_\text{H-H} = \frac{2}{\mathcal{W}}\left(4J + 2J_d\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	H_\text{full} &= \frac{2}{\mathcal{Z}}\sum_{\left<i,j\right>} H_\text{aux}(i,j) \sim N H_\text{aux}(d_1,d_2)~.
+	H_\text{full} &= \frac{2}{\mathcal{W}}\sum_{\left<i,j\right>} H_\text{aux}(i,j) \sim N H_\text{aux}(d_1,d_2)~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0} = \frac{2}{\mathcal{Z}} \times w \times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i, i+1) c^\dagger_{i\sigma} | \Phi_0} = 2\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}
+	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0} = \frac{2}{\mathcal{W}} \times w \times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i, i+1) c^\dagger_{i\sigma} | \Phi_0} = 2\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}
 \end{aligned}\end{equation}
@@
 	\begin{equation}\begin{aligned}
-		\frac{2}{\mathcal{Z}}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0} = \frac{2}{\mathcal{Z}}\sum_{n} \left(d^p_{1,n}\right)^*d^p_{2,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+		\frac{2}{\mathcal{W}}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0} = \frac{2}{\mathcal{W}}\sum_{n} \left(d^p_{1,n}\right)^*d^p_{2,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
 	\end{aligned}\end{equation}
@@
 	\begin{equation}
-		(w-2) \times \frac{2}{\mathcal{Z}}\frac{1}{\mathcal{Z}-2}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{0_1\sigma} | \Phi_0} = \frac{2}{\mathcal{Z}}\left(d^p_{1,n}\right)^* z^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+		(w-2) \times \frac{2}{\mathcal{W}}\frac{1}{\mathcal{W}-2}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{0_1\sigma} | \Phi_0} = \frac{2}{\mathcal{W}}\left(d^p_{1,n}\right)^* z^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
 	\end{equation}
@@
 	\begin{equation}
-		(w-2) \times \frac{2}{w}\frac{1}{\mathcal{Z}-2}\braket{\Phi_0 | c_{0_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0} = \frac{2}{w}\left(z^p_{1,n}\right)^* d^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
+		(w-2) \times \frac{2}{w}\frac{1}{\mathcal{W}-2}\braket{\Phi_0 | c_{0_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0} = \frac{2}{w}\left(z^p_{1,n}\right)^* d^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
 	\end{equation}
@@
 \section{Analytic consistency check - On the Bethe lattice}
-Another test involves considering the case of a Bethe lattice with infinite number of nearest neighbours $w\to\infty$ (the coordination number).
+Another test involves considering the case of a Bethe lattice with infinite number of nearest neighbours $\mathcal{W}\to\infty$ (the coordination number).
 In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
-This allows a metal-insulator transition in the limit of $w\to\infty$ as well.
+This allows a metal-insulator transition in the limit of $\mathcal{W}\to\infty$ as well.
 In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}.
@@
 For a coordination number of \(w\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
-Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{\mathcal{Z}}\).
+Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{\mathcal{W}}\).
 In contrast, there is only one local Greens function, that for \(\vec r_i=0\).

### 2023-03-07 notes/notes.tex
cleaned up extra stuff

@@
 \end{aligned}\end{equation}
-where \(\lambda_{\ket{\vec k}}\) is a normalisation factor. To determine this, we compute the norm of the trail eigenstates:
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k} | \Psi_{\vec k}} &= \frac{1}{\mathcal{W}^2 \lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, a, a^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime, \vec a^\prime) | \psi_\text{aux}(\vec R, \vec a)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, }e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime) | \psi_\text{aux}(\vec R)}\\
-					       &=\frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) | \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)}\\
-					       &= \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i (\vec{k} - \vec q)\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{q} N^2 \delta_{\vec{k},\vec q}|\braket{\psi_\text{aux}(\vec R_0) | \vec q}|^2\\
-\end{aligned}\end{equation}
-By requiring this norm to be unity, we obtain \(\lambda_{\vec k}^2 = |\braket{\psi_\text{aux}(\vec R_0) | \vec k}|^2\). In the above exercise, we defined a state 
-\begin{equation}\begin{aligned}\label{zeroth_site_average}
-	\ket{\psi_\text{aux}(\vec R)} = (1/w)\sum_{\vec a}\ket{\psi_\text{aux}(\vec R, \vec a)}~,
-\end{aligned}\end{equation}
-by averaging over the neasest neighbours of \(\vec R\), and inserted the total momentum basis \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators.
-\(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
-Because of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(\mathcal{W}\) choices.
-
-It is easy to verify that \(\Psi_{\vec k}\left(\left\{ \vec r_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \(\vec R\):
-\begin{equation}\begin{aligned}
-	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
-\end{aligned}\end{equation}
-In the last equation, we transformed \(\vec R_i \to \vec R_j = \vec R_i - \vec R\).
-Note that the argument \(\vec a\) does not change under a translation of the system, because that vector always represents the difference between the impurity lattice position and its nearest neighbours, irrespective of the absolute position of the impurity.
-
-The wavefunction can be even brought into the familiar Bloch function form:
-\begin{equation}\begin{aligned}
-	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} \mathcal{W} N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
-	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
-\end{aligned}\end{equation}
-where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
-This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
-
-It is straightforward to show that these states form an orthonormal basis. We start by writing down the inner product of two distinct such states:
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
-	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
-	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-\end{aligned}\end{equation}
-At this point, we insert a complete basis of momentum eigenkets \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators:
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
-						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-\end{aligned}\end{equation}
-At the last step, we used the summation form of the Kronecker delta function: \(\sum_{\vec R_i}e^{i \vec R_i \left( \vec k - \vec q \right) }\sum_{\vec R_j}e^{i \vec R_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\).
-The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \(\vec a, \vec a^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\ket{\vec k}}\):
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
-\end{aligned}\end{equation}
-This concludes the proof of orthonormality.
-
-To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
-\begin{equation}\begin{aligned}
-	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
-	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}
-\end{aligned}\end{equation}
-To resolve the translation operators, we will now insert the momentum eigenstates \(\ket{\vec k}\) of the full model: \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) in between the operators.
-\begin{equation}\begin{aligned}
-	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
-	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}
-\end{aligned}\end{equation}
-The momentum eigenket \(\ket{\vec k}\) can be expressed as a sum over position eigenkets at varying distances from \(\vec R_0\).
-This form allows a systematic method of improving the energy eigenvalue estimate, because the interacting in the impurity model is extremely localised, so the overlap between two auxiliary models decreases rapidly with distance.
-The majority of the contribution will come from the state at \(\vec R_0\), and improvements are then made by considering auxiliary models at further distances.
+where \(\lambda_{\ket{\vec k}}\) is a normalisation factor.
 
@@
 It is clear from the final form that only the diagonal term \(G_\text{aux,dd}(\omega)\) of the interacting Greens function affects the self-energy while the off-diagonal part \(G_\text{aux,dz}\) fails to contribute as \(w \to \infty\).
-Even the non-interacting part Greens function can be shown to be diagonal in the limit of \(w\to\infty\)~\cite{kuramoto_manybody}.
-From its definition in time domain, we have
-\begin{equation}\begin{aligned}
-	G^{(0)}(\vec k, t) = -i\theta(t) \left<\left\{c_{\vec k}(t), c^\dagger_{\vec k}\right\} \right> = -i\theta(t) \left<\left\{e^{i H^{(0)}t} c_{\vec k} e^{-i H^{(0)}t}, c^\dagger_{\vec k}\right\} \right> = -i\theta(t) e^{-i \epsilon_{\vec k}t}\left[ \left<1 - \hat n_{\vec k}\right> + \left<\hat n_{\vec k}\right>\right] = -i \theta(t) e^{-i \epsilon_{\vec k}t}
-\end{aligned}\end{equation}
-A quick Fourier transform to \(\omega-\)domain shows that this is identical to the \(G^{(0)}(\vec k, \omega)\) defined just above eq.~\ref{self-energy}.
-We note that \(|G^{(0)}(\vec k, t)| \leq 1\).
-Using the Fourier transform  definition
-\begin{equation}\begin{aligned}
-	f(\vec k) = \frac{1}{d_N}\sum_{\vec r_i}h(\vec r_i) e^{i \vec{k}\cdot\vec{r}_i}
-\end{aligned}\end{equation}
-where \(d_N\) is a factor that only depends on the total number of sites and not on the coordination number, we can write
-\begin{equation}\begin{aligned}
-	|G^{(0)}(\vec k, t)|^2 = \frac{1}{d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}
-\end{aligned}\end{equation}
-From the inequality \(|G^{(0)}(\vec k, t)| \leq 1\), we get
-\begin{equation}\begin{aligned}
-	1 \geq \frac{1}{N}\sum_k |G^{(0)}(\vec k, t)|^2 = \frac{1}{N d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* \underbrace{\sum_k e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}}_{N \delta_{\vec r_i = \vec r_j}} = \frac{1}{d_N^2}\sum_{\vec r_i} |G^{(0)}(\vec r_i, t)|^2
-\end{aligned}\end{equation}
-For a coordination number of \(\mathcal{W}\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
-Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{\mathcal{W}}\).
-In contrast, there is only one local Greens function, that for \(\vec r_i=0\).
-The local Greens function therefore scales independent of \(w\).
-This implies that
-\begin{equation}\begin{aligned}
-	\lim_{w\to \infty}G^{(0)}(\vec k,\omega) = G^{(0)}(\vec r=0,\omega)
-\end{aligned}\end{equation}
-Since both the non-interacting and the interaction Greens functions lose their non-locality, the self-energy becomes completely local in the limit of \(w \to \infty\).
-
-\chapter{Going to larger clusters - the two site approach}
-
-\section{Why expand the cluster?}
-The previous chapter dealt with treating the Hubbard-Heisenberg model using an auxiliary model that has a single-site cluster:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux} =  \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s}_0 - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
-\end{aligned}\end{equation}
-This was able to describe an impurity phase transition from screened strong-coupling phase to local moment weak coupling phase, upon tuning \(U_b/J\).
-This then leads to a metal-insulator transition in the bulk, owing to the relations between the Greens functions and spectral functions obtained earlier.
-The single-site nature of the cluster (there was only a single impurity) has the following consequences:
-\begin{itemize}
-	\item [1.] The \(k-\)space self-energy of the bath has only minimal \(k-\)dependence arising from nearest-neighbour non-locality between the impurity and the zeroth site of the bath.
-	\item [2.] The local moment phase (which reduces to a set of decoupled clusters) becomes just the atomic limit, because each cluster has just one impurity.
-\end{itemize}
-
-In this chapter, we will improve on these two points by considering a larger cluster that has two impurities interacting with each other:
-\begin{equation}\begin{aligned}
-	\label{dimer_ham}
-	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right]\\
-	 -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right) + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
-\end{aligned}\end{equation}
-\(d_1\) and \(d_2\), or \(d_i\) in general, represent the two impurity sites in the dimer.
-They interact with each other through the same hopping parameter \(t\) as the bath.
-Each of the impurities has its own correlation \(U\) and hybridisation with the bath through \(V\) and \(J\).
-Each impurity site \(d_i\) couples with a bath site \(0_i\).
-\(0_1\) and \(0_2\) are assumed to be adjacent to each other, connected by the hopping \(t\).
-The setup is shown in fig.~\ref{two-imp-cluster}.
-
-Note that this chapter only sets out the relations between such an auxiliary model and the corresponding bulk model (in this case, a Hubbard-Heisenberg), but does not describe the physics of this new auxiliary model.
-That requires performing a renormalisation group calculation for \(H_\text{aux}\), and that will be provided at a later point in time.
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.6\textwidth]{../figures/two-site-cluster.pdf}
-	\caption{Two-impurity SIAM hybridising with a bath}
-	\label{two-imp-cluster}
-\end{figure}
-
-\section{Solution of the Hubbard dimer using the Anderson molecule}
-This section tries to see how far we can we can go if we just work with the Anderson molecule as the smallest unit of tiling.
-We will attempt to reproduce the entire spectrum of a Hubbard dimer by creating a new Hamiltonian made up purely of Anderson molecules.
-This will guide us in deciding how to generalize the "tiling method" for a general $N-$site Hubbard model, as well as give indications as to whether we need a different smallest unit for tiling.
-
-The Hubbard dimer and Anderson molecules (zero-mode) are defined by the following respective Hamiltonians:
-\begin{equation}\begin{aligned}
-	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat n_{i \uparrow}\hat n_{i \downarrow} - \mu^H \sum_{\sigma, i=1,2}\hat n_{i\sigma}\\
-	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \epsilon_d^A \sum_{\sigma}\hat n_{d\sigma} + U^A\hat n_{d \uparrow}\hat n_{d \downarrow}
-\end{aligned}\end{equation}
-In the first Hamiltonian, the indices \(i=1,2\) refer to the two lattice sites that constitute the dimer.
-In the second Hamiltonian, the subscript \(d\) indicates the impurity site, while the subscript \(z\) indicates the zero-mode site.
-First, we will assume that the Hubbard dimer is at half-filling (\(\frac{1}{2}U^H = \mu^H\)):
-\begin{equation}\begin{aligned}
-	\label{hubb_dimer}
-	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow} + \left(\frac{1}{2}U^H- \mu^H\right) \sum_{\sigma, i=1,2}\hat n_{i\sigma} + \text{constant}\\
-	    &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
-\end{aligned}\end{equation}
-Since the Hubbard Hamiltonian is at half-filling, we will also place the impurity at half-filling by setting \(\epsilon_d^A = -\frac{1}{2}U^A\):
-\begin{equation}\begin{aligned}
-	\label{and_dimer}
-	H^A &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + \left(\epsilon_d^A + \frac{1}{2}U^A\right) \sum_{\sigma}\hat \tau_{d\sigma} + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow} + \text{constant}\\
-	    &= -t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right) + U^A\hat \tau_{d \uparrow}\hat \tau_{d \downarrow}
-\end{aligned}\end{equation}
-The first step is to recreate the Hubbard dimer Hamiltonian eq.~\ref{hubb_dimer} using the Anderson molecule Hamiltonian eq.~\ref{and_dimer}:
-\begin{equation}\begin{aligned}
-	H^H &= -t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
-	    &= \frac{1}{2}\left[-t^H\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) + t^H\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\right] + \frac{1}{2} 2U^H\sum_{i=1,2}\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\\
-	    &= \frac{1}{2}\left[-t^A\sum_{\sigma}\left(c^\dagger_{d\sigma}c_{z\sigma} + \text{h.c.}\right)\bigg\vert_{z \to 2, d \to 1\atop{t^A \to t^H}} + t^A\sum_{\sigma}\left(c^\dagger_{2\sigma}c_{1\sigma} + \text{h.c.}\right)\bigg\vert_{d \to 2,z \to 1\atop{t^A \to t^H}} \right] \\
-	    &+ \frac{1}{2} \left(U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 1\atop{U^A \to 2U^H}} + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}\bigg\vert_{d \to 2\atop{U^A \to 2U^H}}\right)\\
-	    &=\frac{1}{2}\left[H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 1, z \to 2\right) + H^A\left(t^A \to t^H, U^A \to 2U^H, d \to 2, z \to 1\right)\right]
-\end{aligned}\end{equation}
-The conclusion we can draw from this is that the Hubbard dimer Hamiltonian can be obtained from the Anderson dimer Hamiltonian in the following fashion:
-\begin{itemize}
-	\item The essential idea is that we have to create a local Hubbard Hamiltonian for each site of the Hubbard lattice by replacing the impurity label \(d\) in the Anderson dimer with the label of the particular site.
-So if there are two sites, we will get two local Hamiltonians obtained by replacing \(d\) with 1 and 2 respectively.
-For each local Hamiltonian, the zero-mode label \(z\) is replaced by the site that is nearest to the one that \(d\) is being replaced by.
-So, if \(d \to 1(2)\), then \(z \to 2(1)\).
-	\item This, however, is not the only change that we must make, in order to get the local Hamiltonian for a particular site.
-Along with \(d\) and \(z\), we must also make the transformations \(t^A \to t^H, U^A \to 2U^H\).
-	\item Finally, once we have the local Hamiltonians for sites 1 and 2, we average them to get the total Hubbard Hamiltonian.
-\end{itemize}
-Note that we expect most of these "rules" to be specific for the dimer, and there will be generalizations to most of them for a general \(N-\)site Hubbard Hamiltonian.
-
-The wavefunctions for the \(N=2\) sector can also be connected through these transformations.
-Since both the Hamiltonians are analytically solvable, we can write down their groundstate wavefunctions [CITE PAVARINI]:
-\begin{equation}\begin{aligned}
-	\ket{\Psi^H_\text{GS}} &= a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{\uparrow_1, \downarrow_2} - \ket{\downarrow_1, \uparrow_2}\right) - a_2(U^H,t^H){\sqrt 2}\left(\ket{\uparrow_1\downarrow_1, } - \ket{,\uparrow_2\downarrow_2}\right)\\
-	\ket{\Psi^A_\text{GS}} &= a_1(\frac{1}{2}U^A, t^A)\frac{1}{\sqrt 2}\left(\ket{\uparrow_d, \downarrow_z} - \ket{\downarrow_d, \uparrow_z}\right) - a_2(\frac{1}{2}U^A,t^A){\sqrt 2}\left(\ket{\uparrow_d\downarrow_d, } - \ket{,\uparrow_z\downarrow_z}\right)\\
-	E^H_\text{GS} &=  -\frac{1}{2}\Delta\left( U^H, t^H \right), E^A_\text{GS} =  -\frac{1}{2}\Delta\left( \frac{1}{2}U^A, t^A \right)
-\end{aligned}\end{equation}
-where 
-\begin{equation}\begin{aligned}
-	a_1(U,t) \equiv \frac{4t}{\sqrt{2\Delta(U,t)\left( \Delta(U,t) - U \right) }}, && a_2(U,t) \equiv \sqrt{\frac{\Delta(U,t) - U}{2\Delta(U,t)}}, &&\Delta(U,t) \equiv \sqrt{U^2 + 16t^2}\\
-\end{aligned}\end{equation}
-$a_1,a_2$ satisfy $a_1(-U,t) = -a_2(U,t)$ and $a_1(U,t)a_2(U,t)= \frac{2t}{\Delta(U,t)}$.
-From the forms of the wavefunctions and eigenenergies, we can immediately write down
-\begin{equation}\begin{aligned}
-	\ket{\Psi^H_\text{GS}} &= \frac{1}{2}\left[\ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 1, z \to 2\right) + \ket{\Psi^A_\text{GS}}\left(t^A, U^A \to t^H, 2U^H, d \to 2, z \to 1\right)\right]\\
-	E^H_\text{GS} &= E^A_\text{GS}\left(t^A, U^A \to t^H, 2U^H\right)
-\end{aligned}\end{equation}
-This shows that the rules laid out before work for the Hamiltonians, as well as the wavefunctions and energy eigenvalues of the \(N=2,0,4\) sector.
-These sectors specifically work because it is only in these sectors can we ensure that \(n_d = n_z\), which is required for the Hubbard Hamiltonian because \(n_1 = n_2\).
-In the other sectors (\(N=1,3\)), the impurity site and the zero-mode sites have to be singly-occupied in some part, and since the impurity site incurs a single-occupation cost of \(-\frac{U^H}{2}\) which is not borne by the zero-mode site, there is an intrinsic dissimilarity between the two sites of the Anderson molecule in this regime.
-This dissimilarity does not exist for the Hubbard model, so we cannot hope to connect the two models in this regime.
-Going forward, we will switch to using Hubbard dimers as the smallest tiling unit for a general Hubbard model.
-
-\comment{
-\section{Strategy by starting from a zero bandwidth model}
-We start with a SIAM (with a correlated bath having a non-trivial self-energy), and solve it using the unitary renormalisation group approach to get to a fixed-point Hamiltonian.
-The fixed point Hamiltonian will in general involve the impurity site (with renormalised parameters $\epsilon_d^*, U^*$) interacting with a smaller number of momentum states.
-
- To obtain a comparatively simple but physically well-motivated auxiliary model, we identify $\sum_k c_k = \sqrt N c_0$; \(c_0\) is the operator for the zeroth site (the site nearest to the impurity).
-We will call the set of all \(N-2\) sites apart from the impurity and this zeroth site as the "effective bath".
-The fixed point Hamiltonian can be separated into these parts: an isolated impurity part, an isolated zeroth site part, an isolated effective bath part, hopping between impurity and the zeroth site and hopping between the zeroth site and the effective bath.
-\textit{As a simplification, we will ignore the correlation term \((U)\) on the effective bath}.
-In preparation of a symmetrization procedure, we will relabel the impurity site as 0, and the zeroth site as 1.
-With all these steps, the Hamiltonian takes the form:
- \begin{equation}\begin{aligned}
- 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow}}_\text{imp.
-\& zero-mode isolated} - \underbrace{t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{0-1 coupling} - \underbrace{t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{1 \& eff.
-bath coupling} - \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff.
-bath isolated}
- \end{aligned}\end{equation}
- \begin{figure}[!htb]
- 	\centering
- 	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.png}
- 	\caption{Correlated asymmetric Anderson molecule schematic version.
-It consists of an impurity site (blue) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink).
-The other sites (green) form the rest of the bath.
-Just the impurity site and the zeroth site have onsite repulsion.}
- 	\label{and_mol}
- \end{figure}
- This Hamiltonian is depicted in fig.~\ref{and_mol}.
-Such a Hamiltonian is, however, explicitly asymmetric between the sites 0 and 1 (the effective bath couples only to 1).
-To rectify that, we will symmetrize the coupling between the effective bath and the sites 0 and 1, by exchanging the sites 0 and 1.
-The resultant Hamiltonian is
- \begin{equation}\begin{aligned}
- 	\underbrace{U^A\tau_{0 \uparrow}\tau_{0 \downarrow} + U^A\tau_{1 \uparrow}\tau_{1 \downarrow} - t^A\sum_{\sigma}\left(c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.}\right)}_\text{2-site Hubbard model} +\underbrace{- t^A\sum_{j \in \atop{\text{NN of 1}}}\left(c^\dagger_{1\sigma}c_{j\sigma} + \text{h.c.}\right)- t^A\sum_{j \in \atop{\text{NN of 0}}}\left(c^\dagger_{0\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{dimer \& eff.
-bath coupling} \\
- 	- \underbrace{t^A \sum_{\left<ij \right>}^{\text{eff.} \atop{\text{bath}}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_\text{eff. bath isolated}
- \end{aligned}\end{equation}
-
- To further simplify this Hamiltonian, \textit{we will combine the nearest neighbour sites of \(1\) and \(0\) into a single site}.
- \begin{equation}\begin{aligned}
- 	c_z \equiv \left(\sum_{j \in \atop{\text{NN of 1}}} + \sum_{j \in \atop{\text{NN of 0}}}\right)c_{j}
- \end{aligned}\end{equation}
- This single site will act as the zeroth site of the effective bath, and it means that both sites of the Hubbard dimer hybridizes with the effective through just a single site.
-With this assumption, the Hamiltonian for "a Hubbard dimer hopping into an effective bath" takes the simple form
- \begin{equation}\begin{aligned}
- 	\label{dimer_p_bat}
- 	\tilde H^D = H^D(0,1) - t^D \sum_{\sigma}\left(c^\dagger_{0\sigma}c_{z\sigma} + c^\dagger_{1\sigma}c_{z\sigma} + \text{h.c.}\right) + \sum_{\vec k}^\text{eff. bath}\epsilon_{\vec k}\hat n_{\vec k}
- \end{aligned}\end{equation}
- \(H^D(0,1)\) is the Hubbard dimer Hamiltonian (shown in fig.~\ref{hubb-dim}):
- \begin{equation}\begin{aligned}
- 	\label{dimer_ham}
- 	H^D(0,1) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)
- \end{aligned}\end{equation}
- \begin{figure}[!htb]
- 	\centering
- 	\includegraphics[width=0.4\textwidth]{../figures/hubb_dim.png}
- 	\caption{Hubbard dimer schematic version. It again consists of two sites, like the Anderson molecule, but now both sites have onsite repulsion, and their is again inter-site hopping.}
- 	\label{hubb-dim}
- \end{figure}
- This entire procedure is depicted in fig.~\ref{dimer-bath}.
- \begin{figure}[!htb]
- 	\centering
- 	\includegraphics[width=\textwidth]{../figures/dimer_bath.pdf}
- 	\caption{The process of symmetrizing the Rg fixed point Hamiltonian and then creating a dimer+bath Hamiltonian.
-We first add the asymmetric Hamiltonians to get a symmetrized Hamiltonian.
-In the symmetrized Hamiltonian, the dimer has \(w\) entry points into the bath, \(w\) being the coordination number of the lattice.
-We then merge these \(w\) lattice sites (enclosed in the black box) into a single lattice site.}
- 	\label{dimer-bath} 
- \end{figure}
- We  can thus obtain a family of Hamiltonians \(\tilde H^D(i,j)\) obtained by setting \(0\) and \(1\) by setting the two sites of the dimer to any nearest-neighbour \(i,j\) on the lattice and the effective bath to the rest \(N-2\) sites of the lattice.
-The next step in the programme is to tile the real-space lattice with this dimer+bath Hamiltonian \(\tilde H_D\) to restore translational invariance (shown in a later section), and obtain a new Hubbard Hamiltonian, $\tilde H = T\left[ \tilde H^{D} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the dimer Hamiltonian to span the target real-space lattice.
-We quote the final form of $\tilde H$ here to explain what the tiling means, but the explanation is given in a later section.
- \begin{equation}\begin{aligned}
- 	\tilde H &= \frac{2}{Nw}\sum_{\left<ij\right>}\frac{1}{2(w-1)}\sum_{l \in \text{NN of (i,j)}}\tilde H^D((0,1,z) \to (i, j, l))\\
- 		 &= \frac{2}{N}U^D\sum_{i} \tau_{i \uparrow}\tau_{i \downarrow} - \frac{2}{Nw}\left(1 + \frac{Nw}{2}\right)t^D\sum_{\left<ij\right>}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)
- \end{aligned}\end{equation}
- What that means is that we have placed the Hubbard dimer+bath system at all nearest neighbour pairs to reconstruct a new Hubbard model.
-If we assume that the tiling mostly rectifies the explicit symmetry-breaking made while choosing the auxiliary system as well as dropping the correlation on the bath sites, we can write
- \begin{equation}\begin{aligned}
- 	\tilde H = \mathcal{U} H^H \mathcal{U}^{-1} = TZ\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right]Z^{-1} T^{-1}~,
- \end{aligned}\end{equation}
- where $\mathcal{U} = TZ\mathcal{U}_{A}$ is some transformation that is either a unitary, or, at the very least, a similarity transformation that maps from the original to the reconstructed Hubbard Hamiltonian.
- The existence of $U$ is contingent on how good the approximations are.
-
- We mention the two approximations made along the entire journey from the original Hubbard model to the reconstructed one here.
- \begin{itemize}
- 	\item We have replaced the full Hubbard model by an auxiliary system described by the SIAM Hamiltonian in eq.~\ref{clus_bath_siam}.
-The accuracy of this assumption is determined by the choice of the SIAM parameters, particular the self-energy and repulsion of the bath.
-As discussed before, the very choice of th cluster and bath spoil the translational invariance of the parent model.
- 	\item We then perform a unitary RG on $H^A$.
-This leads to a fixed-point Hamiltonian $\mathcal{U}_A H^A \mathcal{U}_A^\dagger$.
-At this point, we go from the fixed point Hamiltonian to the dimer+bath Hamiltonian in eq.~\ref{dimer_p_bat}.
-If we represent this transformation from the fixed point Hamiltonian to the Hamiltonian in eq.~\ref{dimer_p_bat} by an operator \(Z\), we can write $H^D = Z\left[\mathcal{U}_A H^A \mathcal{U}_A^\dagger \right] Z^{-1}$.
-This constitutes the second approximation we make.
-\end{itemize}
-}
-
-\section{Creating \(N-\)site Hubbard Hamiltonian from Hubbard dimer embedded in a bath}
-Similar to the previous chapter, we will now tile the lattice with the two-site auxiliary model
-\begin{equation}\begin{aligned}
-	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right]\\
-	 -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right) + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
-\end{aligned}\end{equation}
-For concreteness, we will consider a lattice of \(N\) lattice sites and \(w\) nearest neighbours for each site.
-Note that a uniform number of nearest neighbours means that there is perfect translational invariance on the lattice, which means there cannot be any edge sites.
-This is achieved by applying periodic boundary conditions on the edges of the lattice.
-For example, a square 2d lattice will have to be placed on a 2-torus.
-
-The first step is to identity the two impurity sites \(d_1\) and \(d_2\) and the two bath sites \(0_1\) and \(0_2\) as sitting on a square arrangement of the lattice.
-\(d_i\) form one arm of the square, while \(0_i\) form the opposite arm.
-This square arrangement is shown in fig.~\ref{square-arms}, and is dictated by the auxiliary model chosen and shown in fig.~\ref{two-imp-cluster}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.3\textwidth]{../figures/square_arms.pdf}
-	\caption{Placing the impurity and bath sites \(d_i,0_i\) on a chosen square of the lattice. The chosen square is marked in blue, the impurity sites in orange and the bath sites in green.}
-	\label{square-arms}
-\end{figure}
-The sites at the vertices of the square are labelled as \(i,j,k,l\). With this identification, the Hamiltonian becomes
-\begin{equation}\begin{aligned}
-	H_\text{aux}(i,j,k,l) = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \frac{U}{2}\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.} + c^\dagger_{j\sigma}c_{l\sigma} + \text{h.c.}\right) + J \vec{S}_{i}\cdot\vec{s}_{k} \right.\\
-+ \left.
-J \vec{S}_{j}\cdot\vec{s}_{l} - U_b\left(\hat n_{k \uparrow} - \hat n_{k \downarrow}\right)^2 - U_b\left(\hat n_{l \uparrow} - \hat n_{l \downarrow}\right)^2\right] -t \sum_\sigma \left(c^\dagger_{i,\sigma}c_{j,\sigma} + \text{h.c.}\right) -t \sum_{\left<m,n \right>, \sigma}^{m,n \notin \left\{i,j\right\}}\left(c^\dagger_{m\sigma,n\sigma} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-As before, the kinetic energy part sums over all nearest neighbour pairs that involve neither \(i\) nor \(j\).
-For a given arm \(i-j\), the square can be rotated along the axis \(i-j\) to give one square arrangements for each dimension perpendicular to the axis along \(i-j\).
-Since there are \(w/2\) dimensions, the number of such squares is \(w/2 - 1\).
-For each such square, we can obtain another square by reflecting the square in the plane of \(i-j-l-k-i\) and across the line \(i-j\).
-The total number of squares is therefore \(w - 2\).
-The upshot is that given \(i-j\), there are multiple ways of choosing \(k\); if \(\left\{\vec a\right\}\) represents the set of \(w\) primitive vectors that connect a particular lattice site to its nearest neighbours, \(k\) can be situated at all \(\vec r_i + \vec a\) for which \(\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0\).
-Choosing \(k\) then automatically fixes \(l\) at \(\vec r_j + \vec a\).
-The condition \(\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0\) simply means we only take those \(\vec a\) that are perpendicular to \(\vec r_j - \vec r_i\).
-Since there are \(w\) number of \(\vec a\) in total and 2 of them are parallel, the total number of choices of \(k,l\) is \(w-2\).
-For a 2D lattice, we have \(w=4\), so there are only two possible choices of the square.
-They are shown in fig.~\ref{square-arms-all}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.6\textwidth]{../figures/square_arms_all.pdf}
-	\caption{Placing the impurity and bath sites \(d_i,0_i\) on a chosen square of the lattice. The chosen square is marked in blue, the impurity sites in orange and the bath sites in green.}
-	\label{square-arms-all}
-\end{figure}
-
-The Hamiltonian for an arm \(i-j\) is then obtained by averaging over these squares:
-\begin{equation}\begin{aligned}
-	H_\text{aux}(i,j) = \frac{1}{\mathcal{W} - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
-\end{aligned}\end{equation}
-The final step is to sum over all nearest neighbour arms \(i-j\):
-\begin{equation}\begin{aligned}
-	\label{22siam_to_hubb}
-	H_\text{full} = \sum_{\left<i,j\right>}\frac{1}{\mathcal{W} - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)
-\end{aligned}\end{equation}
-
-There are four kinds of terms:
-\begin{itemize}
-	\item the first kind, \(A(i), A(j)\), depend only on either \(i\) or \(j\).
-They can be summed over easily by noting that the internal summation gives a constant factor of \(w-2\) which is canceled by the factor of \(1/(w-2)\) in the front, and the external summation gives \(\sum_{i,j}A(i) = \frac{\mathcal{W}}{2} \sum_i A(i)\), because \(i\) is a member of \(w/2\) distinct nearest-neighbour pairs.
-	\item The second kind, \(B(i,j)\) depends on both \(i\) and \(j\).
-The internal summation is again cancelled by the prefactor.
-The external summation simply sums over all nearest-neighbour values of \(A(i,j)\).
-	\item The third kind, \(C(i,k), C(j,l)\), depend on \(i\) and \(k\).
-Here, the total summation \(\sum_{i,j,k}C(i,k)\) gives \((w-2)\sum_{\left<i,k\right>}\left(C(i,k) + C(k,i)\right)\), because the pair \((i,k)\) occurs \(w-2\) times corresponding to the \(w-2\) vectors \(\vec r_j - \vec r_i\) that are perpendicular to \(\vec r_i - \vec r_k\).
-The factor is again cancelled by the existing prefactor.
-	\item The fourth kind, \(D(k), D(l), E(k,l)\), depend on just \(k\), just \(l\) or both \(k\) and \(l\).
-For each pair \(i-j\) in the external summation, the particular pair \(k-l\) appears only once.
-When \(i-j\) is summed over, a factor of \(2(w/2-1)\) is generated because there are that many squares that involve \(k-l\).
-This factor cancels the inverse factor in front, giving \(\sum_{\left<k\right>} D(k), \sum_{\left<k,l \right>}E(k,l)\).
-\end{itemize}
-
- The full Hamiltonian reads
-\begin{equation}\begin{aligned}
-	H_\text{full} =& w\sum_i\left[- \frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\right] - t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + 4V\sum_{\sigma, \left<i,k\right>}\left(c^\dagger_{i\sigma}c_{k\sigma} + \text{h.c.}\right)\\
-		      &+ 4J \sum_{\left<i,k\right>}\left(\vec{S}_{i}\cdot\vec{S}_{k}\right) - 2 U_b\sum_k\left(\hat n_{k \uparrow} - \hat n_{k \downarrow}\right)^2 - \frac{Nw/2}{w-2}t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)\\
-	=& -\frac{1}{2}\left(Uw + 4U_b\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{Nw/2}{w-2}t + t - 4V\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 4J \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
-\end{aligned}\end{equation}
-The bulk model hence obtained is again a Hubbard-Heisenberg model.
-In eq.~\ref{2siam_to_hubb}, the total number of terms in the outer summation is \(Nw/2\).
-In order to make sure that this full Hamiltonian scales as \(N\), we divide this by \(w/2\):
-\begin{equation}\begin{aligned}
-	\label{2siam_to_hubb}
-	H_\text{full} &= \frac{2}{\mathcal{W}}\sum_{\left<i,j\right>} H_\text{aux}(i,j) = \frac{2}{\mathcal{W}}\sum_{\left<i,j\right>}\frac{1}{\mathcal{W} - 2}\sum_{\vec r_k = \vec r_i + \vec a \atop{\vec r_l = \vec r_j + \vec a}}^{\vec a \times \left(\vec r_j - \vec r_i\right) \neq 0}H_\text{aux}(i,j,k,l)\\
-		      &= -\frac{1}{2}\left(2U + 8U_b/w\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - \left(\frac{N}{w-2}t + 2t/w - 8V/w\right) \sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}\right) + 8J/w \sum_{\left<i,j \right>} \vec{S}_i\cdot\vec{S}_j
-\end{aligned}\end{equation}
-The mappings between the parameters of the auxiliary model and the bulk are
-\begin{equation}\begin{aligned}
-	t_\text{H-H} = \left(\frac{N}{w-2}t + 2t/w - 8V/w\right),~ ~ ~ U_\text{H-H} = 2U + 8U_b/w,~ ~ ~ J_\text{H-H} = 8J/w
-\end{aligned}\end{equation}
-
-We could have also inserted a spin-exchange interaction between the two impurities in the auxiliary model:
-\begin{equation}\begin{aligned}
-	H_\text{aux} = \sum_{i=1,2} \left[- \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right)^2 + V\sum_{\sigma}\left(c^\dagger_{d_i\sigma}c_{0_i\sigma} + \text{h.c.}\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i} - U_b\left(\hat n_{0_i \uparrow} - \hat n_{0_i \downarrow}\right)^2\right] -t \sum_\sigma \left(c^\dagger_{d_1,\sigma}c_{d_2,\sigma} + \text{h.c.}\right)\\
-	+ J_d \vec{S}_{d_1}\cdot\vec{S}_{d_2} + \sum_{k\sigma}\epsilon_k \tau_{k\sigma}
-\end{aligned}\end{equation}
-In the presence of this term, the bulk Hamiltonian remains the same, but the expression of \(J_\text{H-H}\) changes.
-Since this term is similar in form to the term preceding it, we can easily obtain the updated expression:
-\begin{equation}\begin{aligned}
-	J_\text{H-H} = \frac{2}{\mathcal{W}}\left(4J + 2J_d\right)
-\end{aligned}\end{equation}
-
-\section{Single-particle Green's function}
-We now define the Greens function {\it operators}:
-\begin{equation}\begin{aligned}
-	\mathcal{G}_{H-H} = \frac{1}{\omega^\prime - \left(H_{H-H} - E_\text{gs}^\prime\right) }, \mathcal{G}_\text{aux}(i,j) = \frac{1}{\omega - \left(\mathcal{H}_\text{aux}(i,j) - E_\text{gs}\right)}
-\end{aligned}\end{equation}
-Here, \(E_\text{gs}\) and \(\omega\) are the ground state energy and frequency scale for the auxiliary model Hamiltonian, while the primed quantities \(E_\text{gs}^\prime\) and \(\omega^\prime\) are the same quantities but for the full model \(\mathcal{H}_{H-H}\).
-While the auxiliary model is intensive, the full Hamiltonian is extensive and scales as \(N\):
-\begin{equation}\begin{aligned}
-	H_\text{full} &= \frac{2}{\mathcal{W}}\sum_{\left<i,j\right>} H_\text{aux}(i,j) \sim N H_\text{aux}(d_1,d_2)~.
-\end{aligned}\end{equation}
-This means that we must have \(\omega^\prime = N\omega\) and \(E_\text{gs}^\prime = N E_\text{gs}\).
-Rewriting eq.~\ref{2siam_to_hubb} in terms of the operators \(\mathcal{G}\), we get
-\begin{equation}\begin{aligned}
-\sum_{\left<i,j \right>} \left(\omega + E_\text{gs} - \mathcal{G}^{-1}_\text{aux}(i,j)\right) = N\omega + N E_\text{gs} - \mathcal{G}^{-1}_{H-H} \implies \sum_{\left<i,j \right>} \mathcal{G}^{-1}_\text{aux}(i,j) = \mathcal{G}^{-1}_{H-H}~,
-\end{aligned}\end{equation}
-We will now take matrix elements of the full Greens function and obtain these matrix elements in terms of those of the auxiliary model.
-Let \(\left\{ \ket{\Phi}_n \right\} \) be the set of eigenstates of \(\mathcal{H}_\text{aux}\), and \(\ket{\Phi}_0\) be the groundstate.
-We assume that the ground state of \(H_{H-H}\) is captured well by the auxiliary model, such that the real-space diagonal matrix element for particle propagation is obtained by sandwiching the Greens function between the states \(c^\dagger_{i\sigma}\ket{\Phi}_0\):
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} \equiv \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_{H-H} c^\dagger_{i\sigma} | \Phi_0} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-The superscript \(p\) indicates that this is the particle propagation matrix element.
-Under the auxiliary model approximation, we ignore the virtual entanglement between separate clusters.
-Therefore, the only operators \(\mathcal{G}^{-1}_\text{aux}(k,l)\) that affect the matrix element are those that satisfy \(i \in \left(k,l\right)\).
-There are \(w\) such pairs: \(\left\{k,l\right\} = \left\{i,j\right\} \forall~ j \in \text{NN of i}\).
-Moreover, because of translation invariance, all \(j \in \text{NN of i}\) are equivalent.
-These configurations are shown in fig.~\ref{diag_conrib}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/diagonal_contributors.pdf}
-	\caption{The various configurations of auxiliary models that contribute to the diagonal matrix element at site \(i\). Orange colour represents impurities and green represents bath sites.}
-	\label{diag_conrib}
-\end{figure}
-
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\right)^p_{ii} = \sum_{\left<k,l\right>} \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(k,l) c^\dagger_{i\sigma} | \Phi_0} = \frac{2}{\mathcal{W}} \times w \times \braket{\Phi_0 | c_{i\sigma} \mathcal{G}^{-1}_\text{aux}(i, i+1) c^\dagger_{i\sigma} | \Phi_0} = 2\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0}
-\end{aligned}\end{equation}
-where we have identified site \(i\) in the auxiliary model as one of the impurities \(d_1\).
-We could very well have chosen \(d_2\) since the model is symmetric in \(d_1,d_2\).
-\(\mathcal{G}^{-1}_\text{aux}(d_1,d_2)\) is the Greens operator corresponding to the Hamiltonian in eq.~\ref{dimer_ham}.
-
-By inserting \(1 = \sum_n \ket{\Phi_n}\bra{\Phi_n}\) on both sides of \(\mathcal{G}^{-1}_\text{aux}\), we get from the spectral representation
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = 2\sum_{m,n} \braket{\Phi_0 | c_{d_1\sigma} \ket{\Phi_m}\bra{\Phi_m}\mathcal{G}^{-1}_\text{aux} \ket{\Phi_n}\bra{\Phi_n} c^\dagger_{d_1\sigma} | \Phi_0} = 2\sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
-\end{aligned}\end{equation}
-There we used the fact that since \(\ket{\Phi_m}\) are eigenstates of \(\mathcal{H}_\text{aux}\) and hence of \(\mathcal{G}^{-1}_\text{aux}\), we can set \(m=n\).
-We also defined \(d^p_{i,n} = \bra{\Phi_n}c^\dagger_{d_i\sigma}\ket{\Phi_0}\).
-The hole propagation matrix element can be obtained similarly:
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = 2\sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn} 
-\end{aligned}\end{equation}
-where \(d^h_{i,n} = \bra{\Phi_n}c_{d_i\sigma}\ket{\Phi_0}\).
-
-The off-diagonal matrix elements between two nearest-neighbour sites \(i\) and \(i+1\) can also be obtained similarly. Several  auxiliary models can contribute to such a matrix element:
-\begin{itemize}
-	\item those auxiliary models that have \(i\) and \(i+1\) as the two impurities. These give the contribution \\
-		\(\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0}\). 
-	\begin{equation}\begin{aligned}
-		\frac{2}{\mathcal{W}}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_2\sigma} | \Phi_0} = \frac{2}{\mathcal{W}}\sum_{n} \left(d^p_{1,n}\right)^*d^p_{2,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
-	\end{aligned}\end{equation}
-	\item those that have \(i\) as an impurity and \(i+1\) as the corresponding bath site. There will be \(w-2\) of these in number:
-	\begin{equation}
-		(w-2) \times \frac{2}{\mathcal{W}}\frac{1}{\mathcal{W}-2}\braket{\Phi_0 | c_{d_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{0_1\sigma} | \Phi_0} = \frac{2}{\mathcal{W}}\left(d^p_{1,n}\right)^* z^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
-	\end{equation}
-		where \(z^p_{i,n} = \braket{\Phi_n | c^\dagger_{0_i,\sigma} | \Phi_0}\).
-	\item those that have \(i+1\) as an impurity site and \(i\) as the corresponding bath site. There are again \(w-2\) of these:
-	\begin{equation}
-		(w-2) \times \frac{2}{w}\frac{1}{\mathcal{W}-2}\braket{\Phi_0 | c_{0_1\sigma} \mathcal{G}^{-1}_\text{aux}(d_1,d_2) c^\dagger_{d_1\sigma} | \Phi_0} = \frac{2}{w}\left(z^p_{1,n}\right)^* d^p_{1,n} \left(\mathcal{G}^{-1}\left(\omega\right) _\text{aux}\right)_{nn}
-	\end{equation}
-\end{itemize}
-These choices are shown in fig.~\ref{off-diag-contrib}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/offdiagonal_contributors.pdf}
-	\caption{Auxiliary models that contribute to the off-diagonal matrix element. \(j \equiv i+1\)}
-	\label{off-diag-contrib}
-\end{figure}
-
-Adding all contributions gives
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}
-\end{aligned}\end{equation}
-The hole counterpart is
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}
-\end{aligned}\end{equation}
-where \(z^h_{i,n} = \bra{\Phi_n}c_{z_i\sigma}\ket{\Phi_0}\).
-
-The off-diagonal matrix element between next-to-nearest-neighbour sites \(i,i+2\) can also be obtained, provided their positions are related as \(\vec r_{i+2} = \vec r_i + \vec a + \vec a^\prime\), where \(\vec a\) and \(\vec a^\prime\) are primitive vectors that connect any lattice site to its nearest-neighbours, and \(\vec{a}\cdot\vec{a}^\prime = 0\).
-This is shown in fig.~\ref{next-near}.
-
-\par\noindent
-\begin{minipage}{0.6\textwidth}
-The essence is that the two sites have to form the two most separated vertices of a right-angled triangle.
-To find the auxiliary models that contribute to this matrix element, note that there is only one square that can be formed keeping both \(i\) and \(i+2\) on it - we call this square \(ABCD\), where \(A\) is the vertex \(i\) and \(C\) is the vertex \(i+2\).
-We can set \(A=d_1, C=0_2\).
-The other two vertices \(B\) and \(D\) can have two possible configurations:\(B=d_2,D=0_1\) and \(B=0_1,D=d_2\).
-Two more configurations can be obtained by taking each of these two configurations and keeping \(B,D\) unchanged but exchanging \(A\) and \(C\).
-These four configurations are shown in fig.~\ref{nn-configs}.
-\end{minipage}
-\hspace*{\fill}
-\begin{minipage}{0.35\textwidth}
-	\centering
-	\includegraphics[width=0.9\textwidth]{../figures/next-near.pdf}
-	\captionof{figure}{The kind of next-nearest neighbour sites that can be connected by the auxiliary model.}
-	\label{next-near}
-\end{minipage}
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/nn-offdiagonal_contributors.pdf}
-	\caption{Auxiliary model configurations that contribute to the next-nearest neighbour matrix elements. \(j \equiv i+2\)}
-	\label{nn-configs}
-\end{figure}
-
-These four configurations give
-\begin{equation}\begin{aligned}
-	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} &= \frac{2}{w(w-2)}\left[\braket{\Phi_0|c_{d_1\sigma}\mathcal{G}^{-1}_\text{aux}(d_1,d_2)c^\dagger_{0_2,\sigma}|\Phi_0} + \braket{\Phi_0|c_{0_2\sigma}\mathcal{G}^{-1}_\text{aux}(d_1,d_2)c^\dagger_{d_1,\sigma}|\Phi_0}\right] \\
-										 &= \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}
-\end{aligned}\end{equation}
-
-In summary, the spectral representation of the matrix elements of the inverse Greens operators are given by
-\begin{gather}
-\label{green_eq_final_2siam}
-	\left(\mathcal{G}^{-1}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}^{-1}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}^{-1}_\text{aux}(-\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}^{-1}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega) \right)_{nn}~,\\
-	\left(\mathcal{G}^{-1}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w} \sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}^{-1}_\text{aux}(-\omega) \right)_{nn}~,\\
-	\left(\mathcal{G}_\text{H-H}^{-1}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}_\text{H-H}^{-1}\left( -\omega \right) \right)^h_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^h_{1,n}\right)^* z^h_{2,n} + \left(z^h_{2,n}\right)^* d^h_{1,n}\right] \left(\mathcal{G}^{-1}_\text{aux}(\omega)\right)_{nn}~.
-\end{gather}
-
-In order to obtain the matrix elements of the Greens operators \(\mathcal{G}_{H-H}\) (as compared to its inverse), we note that we have just observed that the matrix elements of the inverse Greens operators are related to the matrix elements of another inverse operator through some coefficients.
-We can, therefore, use the identity
-\begin{equation}\begin{aligned}
-\left(\hat O\right)_{ij} = \bra{i} \hat O \ket{j} = \sum_{m,n} \braket{i|m} \left(\hat O\right)_{mn} \braket{n|j} \implies \left(\hat O^{-1}\right)_{ij} = \sum_{m,n} \braket{i|m} \left(\hat O^{-1}\right)_{mn} \braket{n|j}
-\end{aligned}\end{equation}
-We can now identify \(\left(\hat O^{-1}\right)_{mn}\) as the matrix elements of \(\mathcal{G}_\text{aux}^{-1}\) in our expressions.
-Using the above relation, we can therefore write the spectral representation of the matrix elements of the Greens operators as
-\begin{gather}
-	\left(\mathcal{G}_{H-H}(\omega)\right)^p_{ii} = \sum_{n} |d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}_{H-H}(-\omega)\right)^h_{ii} = \sum_{n} |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}_{H-H}\left(\omega\right) \right)^p_{i,i+1} = \frac{2}{w}\sum_n \left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn}~,\\
-	\left(\mathcal{G}_{H-H}\left(-\omega\right) \right)^h_{i,i+1} = \frac{2}{w}\sum_n \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}~,\\
-	\left(\mathcal{G}_\text{H-H}\left( \omega \right) \right)^p_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^p_{1,n}\right)^* z^p_{2,n} + \left(z^p_{2,n}\right)^* d^p_{1,n}\right] \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~,\\
-	\left(\mathcal{G}_\text{H-H}\left( -\omega \right) \right)^h_{i,i+2} = \frac{2}{w(w-2)}\sum_n \left[\left(d^h_{1,n}\right)^* z^h_{2,n} + \left(z^h_{2,n}\right)^* d^h_{1,n}\right] \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn}~.
-\end{gather}
-
-The Lehmann-Kallen spectral representation of the single-particle Greens functions can now be written in terms of these matrix elements.
-Using eq.~\ref{G_mat_el}, we write the on-site ($\left(G_{H-H}(\omega)\right)_\text{loc}$) and nearest neighbour ($\left(G_{H-H}(\omega)\right)_\text{n-n}$) Greens functions as
-\begin{equation}\begin{aligned}
-	&\left(G_{H-H}(\omega)\right)_\text{loc} = \left(\mathcal{G}_{H-H}(\omega)\right)_{ii}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{ii}^h = \sum_n \left[|d^p_{1,n}|^2 \left(\mathcal{G}_\text{aux}(\omega)\right)_{nn} - |d^h_{1,n}|^2 \left(\mathcal{G}_\text{aux}(-\omega)\right)_{nn}\right] = G_\text{aux}(d_1,d_1;\omega)\\
-	&\left(G_{H-H}(\omega)\right)_\text{n-n} = \left(\mathcal{G}_{H-H}(\omega)\right)_{i,i+1}^p - \left(\mathcal{G}_{H-H}(-\omega)\right)_{i+1,i}^h\\
-						&\frac{2}{w}\sum_n \left\{\left[\left(d^p_{1,n}\right)^*d^p_{2,n} + \left(d^p_{1,n}\right)^* z^p_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(\omega) \right)_{nn} - \left[\left(d^h_{1,n}\right)^*d^h_{2,n} + \left(d^h_{1,n}\right)^* z^h_{1,n} + \text{h.c.}\right] \left(\mathcal{G}_\text{aux}(-\omega) \right)_{nn}\right\}\\
-						&= \frac{2}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right]\\
-						&\left(G_\text{H-H}\right)_\text{n-n-n} = \frac{2}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right] 
-\end{aligned}\end{equation}
-
-\section{Spectral functions and self-energies}
-
-The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
-\end{aligned}\end{equation}
-where $\vec{r_i}$ is the position vector of a particular lattice site.
-Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites.
-As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
-As we do not have real space Greens function that are more non-local than next-nearest neighbour, we will attempt to obtain momentum space Greens function from these contributions:
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
-\end{aligned}\end{equation}
-The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, w\right]\right\}$.
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}} + G_{H-H} (\omega)_\text{n-n-n}\sum_{i=1}^w e^{i \vec{k}\cdot\vec {b_i}}= G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n} \xi_{\vec k} + G_{H-H} (\omega)_\text{n-n-n} \xi^\prime_{\vec k}
-\end{aligned}\end{equation}
-where we defined \(\left\{b_i\right\} \) as the set of vectors that connect a particular lattice site with its next-nearest-neighbours,\(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\) and \(\xi^\prime_{\vec k} \equiv \sum_{j} e^{i \vec{k}\cdot\vec {b_j}}\).
-Note that \(b_j\) is simply \(a_i + a{i^\prime}\) where \(a_i\) and \(a_{i^\prime}\) are orthogonal.
-On a d-dimensional hypercubic lattice, we obtain
-\begin{gather}
-	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i\\
-\end{gather}
-On a 2D square lattice with lattice spacing $a$, this simplifies to (same as eq.~\ref{2dsquaretb})
-\begin{eqnarray}
-\xi_{\vec{q}} &=& 2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}~,\nonumber\\
-\end{eqnarray}
-where \(\epsilon_{\vec{q}} = -2t^{H}(\cos q_{x}a_{x} + \cos q_{y}a_{y})\) is the tight-binding dispersion.
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) = G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] \\
-	 + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]
-\end{aligned}\end{equation}
-
-We can now compute the $k$-space spectral function $A_{H}(\vec{k},\omega)$ and the real-space local spectral function $A_{H}(\vec{r}=0,\omega)$ as
-\begin{equation}\begin{aligned}
-	A_\text{H-H}(\vec{k},\omega) = -\frac{1}{\pi} \textrm{Im}(G_{H-H}(\vec{k},\omega)) =A_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[A_\text{aux}(d_1,d_2;\omega) + A_\text{aux}(d_1,0_1;\omega) + A_\text{aux}(0_1,d_1;\omega)\right]\\
-	 + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[A_\text{aux}(d_1,0_2;\omega) + A_\text{aux}(0_2,d_1;\omega)\right]
-\end{aligned}\end{equation}
-where the spectral function $A_\text{aux}=-\frac{1}{\pi}\textrm{Im}G_\text{aux}$.
-
-With the knowledge of the momentum-space Greens function $G_\text{H-H}(\vec k, \omega)$, we can now use Dyson's equation to calculate the self-energy for propagation of momentum excitations:
-\begin{equation}\begin{aligned}
-	\Sigma(\vec k,\omega) = \left(G^{(0)}(\vec k,\omega)\right)^{-1} - G(\vec k,\omega)^{-1}
-\end{aligned}\end{equation}
-where $\left(G^{(0)}(\vec k,\omega)\right)^{-1}  = \omega -\epsilon_{k} = \omega +t^{H-H}\xi_{k}$ is the inverse $k-$space Greens function for the appropriate non-interacting tight-binding system.
-Substituting this as well as the full Greens function $G_{H-H}(\vec k, \omega)$ into Dyson's equation gives
-\begin{equation}\begin{aligned}
-	\label{self-energy}
-	&\Sigma_{H-H}(\vec k,\omega) = \left(G^{(0)}(\vec k,\omega)\right)^{-1} -\\
-	&\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}
-\end{aligned}\end{equation}
-This allows us to calculate the full self-energy $\Sigma (\vec{k},\omega)$ for the Hubbard model on the 2D square lattice.
-
-\section{Analytic consistency check - On the Bethe lattice}
-Another test involves considering the case of a Bethe lattice with infinite number of nearest neighbours $\mathcal{W}\to\infty$ (the coordination number).
-In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{w}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
-This allows a metal-insulator transition in the limit of $\mathcal{W}\to\infty$ as well.
-In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}.
-This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy}.
-Applying the limit of \(w\to \infty\) on that equation gives
-\begin{equation}\begin{aligned}
-	&\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left[G^{(0)}(\vec k,\omega)\right]^{-1} -\right.\\
-	&\left.\left [G_\text{aux}(d_1,d_1;\omega) + \frac{2\xi_{\vec k}}{w}\left[G_\text{aux}(d_1,d_2;\omega) + G_\text{aux}(d_1,0_1;\omega) + G_\text{aux}(0_1,d_1;\omega)\right] + \frac{2\xi^\prime_{\vec k}}{w(w-2)} \left[G_\text{aux}(d_1,0_2;\omega) + G_\text{aux}(0_2,d_1;\omega)\right]\right]^{-1}\right\}\\
-	& = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux}(d_1,d_1;\omega)\right\}^{-1} 
-\end{aligned}\end{equation}
-where \(G_\text{aux}^{(0)}(\vec k,\omega)\) is the non-interacting Greens function.
-It is clear from the final form that only the diagonal term \(G_\text{aux}(d_1,d_1;\omega)\) of the interacting Greens function affects the self-energy.
-Even the non-interacting part Greens function can be shown to be diagonal in the limit of \(w\to\infty\)~\cite{kuramoto_manybody}.
-From its definition in time domain, we have
-\begin{equation}\begin{aligned}
-	G^{(0)}(\vec k, t) = -i\theta(t) \left<\left\{c_{\vec k}(t), c^\dagger_{\vec k}\right\} \right> = -i\theta(t) \left<\left\{e^{i H^{(0)}t} c_{\vec k} e^{-i H^{(0)}t}, c^\dagger_{\vec k}\right\} \right> = -i\theta(t) e^{-i \epsilon_{\vec k}t}\left[ \left<1 - \hat n_{\vec k}\right> + \left<\hat n_{\vec k}\right>\right] = -i \theta(t) e^{-i \epsilon_{\vec k}t}
-\end{aligned}\end{equation}
-A quick Fourier transform to \(\omega-\)domain shows that this is identical to the \(G^{(0)}(\vec k, \omega)\) defined just above eq.~\ref{self-energy}.
-We note that \(|G^{(0)}(\vec k, t)| \leq 1\).
-Using the Fourier transform  definition
-\begin{equation}\begin{aligned}
-	f(\vec k) = \frac{1}{d_N}\sum_{\vec r_i}h(\vec r_i) e^{i \vec{k}\cdot\vec{r}_i}
-\end{aligned}\end{equation}
-where \(d_N\) is a factor that only depends on the total number of sites and not on the coordination number, we can write
-\begin{equation}\begin{aligned}
-	|G^{(0)}(\vec k, t)|^2 = \frac{1}{d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}
-\end{aligned}\end{equation}
-From the inequality \(|G^{(0)}(\vec k, t)| \leq 1\), we get
-\begin{equation}\begin{aligned}
-	1 \geq \frac{1}{N}\sum_k |G^{(0)}(\vec k, t)|^2 = \frac{1}{N d_N^2}\sum_{\vec r_i, \vec r_j} G^{(0)}(\vec r_i, t)\left(G^{(0)}(\vec r_j, t)\right)^* \underbrace{\sum_k e^{i \vec k \cdot \left(\vec r_i - \vec r_j\right) t}}_{N \delta_{\vec r_i = \vec r_j}} = \frac{1}{d_N^2}\sum_{\vec r_i} |G^{(0)}(\vec r_i, t)|^2
-\end{aligned}\end{equation}
-For a coordination number of \(w\), there are \(w\) number of \(\vec r_i\) that are equivalent: \(\sum_{\vec r_i \in \text{NN}}|G^{(0)}(\vec r_i, t)|^2\).
-Adding these equal Greens functions and ignoring the \(w-\)independent prefactor in front, we obtain \(|G^{(0)}(\vec r_i, t)|^2 \sim \frac{1}{\mathcal{W}}\).
-In contrast, there is only one local Greens function, that for \(\vec r_i=0\).
-The local Greens function therefore scales independent of \(w\).
-This implies that
-\begin{equation}\begin{aligned}
-	\lim_{w\to \infty}G^{(0)}(\vec k,\omega) = G^{(0)}(\vec r=0,\omega)
-\end{aligned}\end{equation}
-Since both the non-interacting and the interaction Greens functions lose their non-locality, the self-energy becomes completely local in the limit of \(w \to \infty\).
-
-\chapter{The Periodic Anderson and Kondo models}
-The heavy Fermion systems are described by periodic versions of the single impurity models, where instead a lattice of impurities \(\left\{ d_i \right\} \) hybridises with a conduction bath lattice \(\left\{ i \right\} \).
-The periodic Anderson model is defined by the Hamiltonian
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right)  - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-
-As before, we will work with a generalised form of it where we also consider a spin-exchange interaction between the impurity sites and the bath sites:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right) + J \sum_i \vec{S}_{d_i}\cdot\vec{s}_i - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-One can also introduce an RKKY interaction \(J_\text{RKKY}\) between the nearest neighbour impurity spins:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{PAM} = \sum_{k\sigma} \left(\epsilon_k - \mu\right)\tau_{k\sigma} + V\sum_{i,\sigma} \left(c^\dagger_{d_i\sigma}c_{i\sigma} + \text{h.c.} \right) + J \sum_i \vec{S}_{d_i}\cdot\vec{s}_i - \frac{U}{2}\sum_i \left(\hat n_{d_i,\uparrow} - \hat n_{d_i,\uparrow}\right)^2 + \eta \sum_i\tau_{d_i\sigma} \\
-	+ J^\prime\sum_{\left<d_i,d_j \right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
-\end{aligned}\end{equation}
-
-\section{Creating a bulk periodic Anderson model by tiling with generalised single-impurity Anderson models: no RKKY}
-
-The auxiliary model we will be using is a generalised SIAM with attractive interaction on the bath zeroth site and explicit particle-hole asymetry on the impurity:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux} = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s}_0 + \eta \sum_\sigma\tau_{d\sigma}
-\end{aligned}\end{equation}
-where \(\tau = \hat n - 1/2\).
-
-We will use this as the auxiliary model to study the Hubbard model.
-We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
-Note that the impurity level and the conduction bath can be tuned to half-filling by setting \(\eta=0\) and \(\mu=0\) respectively.
-To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(d_i\) of the impurity lattice, and the bath sites will constitute the bulk lattice sites.
-We will also identity the zeroth site of the SIAM lattice as one particular site \(i\) of the conduction bath lattice:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(d_i) = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) +J \vec{S}_{d_i}\cdot\vec{s}_i + \eta \sum_\sigma\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-Once we have this local Hamiltonian for a particular site, we translate this over all \(N\) sites \(\left\{\left(d_i,i\right) \right\} \):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} = \sum_{i} \mathcal{H}_\text{aux}(d_i) = N\sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) +J \sum_i\vec{S}_{d_i}\cdot\vec{s}_i \\
-	+ \eta \sum_{i,\sigma}\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-
-We end up with a generalised periodic Anderson model:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{GPAM} = \sum_{k\sigma}\left(\left(\epsilon_k\right)_\text{GPAM} - \mu_\text{GPAM}\right)\tau_{k\sigma} - \frac{U_\text{GPAM}}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V_\text{GPAM} \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right)\\
-	+ J_\text{GPAM} \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + \eta_\text{GPAM} \sum_{i,\sigma}\tau_{d_i\sigma}
-\end{aligned}\end{equation}
-The mapping between the parameters of the auxiliary model and that of the bulk are
-\begin{equation}\begin{aligned}
-	\label{map_pam_bulk}
-	\left(\epsilon_k\right)_\text{GPAM} = N\epsilon_k, ~ ~ \mu_\text{GPAM} = N\mu, ~ ~ U_\text{GPAM} = U, ~ ~ V_\text{GPAM} = V, ~ ~ J_\text{GPAM} = J, ~ ~ \eta_\text{GPAM} = \eta
-\end{aligned}\end{equation}
-
-\section{Creating a bulk periodic Anderson model by tiling with two-impurity Anderson models: with RKKY}
-
-This time we will use a two-impurity model with a spin-exchange coupling between the impurities as the auxiliary model:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux} = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\sum_{i=1,2}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right)^2 + \sum_{i=1,2}\left[V \sum_{\sigma} \left(c^\dagger_{0_i\sigma} c_{d_i\sigma} + h.c.\right) + J \vec{S}_{d_i}\cdot\vec{s}_{0_i}\right] + \eta \sum_\sigma\tau_{d\sigma}\\
- + J^\prime\vec{S}_{d_1}\cdot\vec{S}_{d_2}
-\end{aligned}\end{equation}
-where \(\tau = \hat n - 1/2\).
-
-We will use this as the auxiliary model to study the Hubbard model.
-We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
-Note that the impurity level and the conduction bath can be tuned to half-filling by setting \(\eta=0\) and \(\mu=0\) respectively.
-To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity sites \(d_1 \) and \(d_2\) as particular nearest-neighbour sites \(d_i, d_{j}\) of the impurity lattice, and the bath sites will constitute the bulk lattice sites.
-We will also identity the bath sites \(0_1,0_2\) as two particular nearest-neighbour sites \(i,j\) of the conduction bath lattice:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(d_i, d_{j}) = \sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - \frac{U}{2}\left[\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + \left(\hat n_{d_{j} \uparrow} - \hat n_{d_{j} \downarrow} \right) ^2\right] + V \sum_{\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + c^\dagger_{j,\sigma} c_{d_{j},\sigma} + h.c.\right)\\
- + J \left(\vec{S}_{d_i}\cdot\vec{s}_i + \vec{S}_{d_{j}}\cdot\vec{s}_{j}\right) + \eta \sum_\sigma\left(\tau_{d_i\sigma} + \tau_{d_{j}\sigma}\right)+ J^\prime\vec{S}_{d_i}\cdot\vec{S}_{d_j}\\
-\end{aligned}\end{equation}
-Once we have this local Hamiltonian for a particular site, we translate this over all nearest-neighbour pairs \((i,j)\) of the lattice.
-There are \(Nw/2\) of these.
-To ensure the bulk model scales as \(N\), we divide this sum by \(w/2\).
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} = \frac{2}{w}\sum_{\left<i,j\right>} \mathcal{H}_\text{aux}(d_i) = N\sum_{k\sigma}\left(\epsilon_k - \mu\right)\tau_{k\sigma} - 2\frac{U}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + 2V \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right) \\
-	 + 2J \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + 2\eta \sum_{i,\sigma}\tau_{d_i\sigma} + \frac{2}{w}J^\prime\sum_{\left<i,j\right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
-\end{aligned}\end{equation}
-
-We end up with a generalised periodic Anderson model with RKKY interaction:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{GPAM} = \sum_{k\sigma}\left(\left(\epsilon_k\right)_\text{GPAM} - \mu_\text{GPAM}\right)\tau_{k\sigma} - \frac{U_\text{GPAM}}{2}\sum_{i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow} \right) ^2 + V_\text{GPAM} \sum_{i,\sigma} \left(c^\dagger_{i\sigma} c_{d_i\sigma} + h.c.\right)\\
-	+ J_\text{GPAM} \sum_i\vec{S}_{d_i}\cdot\vec{s}_i + \eta_\text{GPAM} \sum_{i,\sigma}\tau_{d_i\sigma} + J^\prime_\text{GPAM}\sum_{\left<i,j\right>}\vec{S}_{d_i}\cdot\vec{S}_{d_j}
-\end{aligned}\end{equation}
-The mapping between the parameters of the auxiliary model and that of the bulk are
-\begin{equation}\begin{aligned}
-	\left(\epsilon_k\right)_\text{GPAM} = N\epsilon_k, ~ ~ \mu_\text{GPAM} = N\mu, ~ ~ U_\text{GPAM} = 2U, ~ ~ V_\text{GPAM} = 2V, ~ ~ J_\text{GPAM} = 2J, ~ ~ \eta_\text{GPAM} = 2\eta, ~ ~ J^\prime_\text{GPAM} = \frac{2}{w}J^\prime
-\end{aligned}\end{equation}
-
-\chapter{Future goals}
-\begin{enumerate}
-\item The Mott metal-insulator transition:
-	\begin{itemize}
-	\item Obtain the metal insulator transition of the 2D Hubbard-Heisenberg model on the square lattice from the present formalism. 
-	\item Determine the nature of the bath $\Sigma (k,\omega)$ in the metallic phase, insulating phase as well as at criticality.
-	\item Investigate nature of the zero-temperature transition (order of transition, order parameter, etc)
-	\end{itemize}
-
-\item Higher-order Greens functions:
-	\begin{itemize}
-	\item Provide expressions for two-particle Greens functions.
-	\item Calculate explicitly the Greens functions for holon-doublon and spinon-spinon excitations as they are likely to contain more information regarding the ground state.
-	\item Obtain spectral functions for such excitations
-	\end{itemize}
-
-\item Benchmarking against ED and/or finite size scaling:
-	\begin{itemize}
-	\item ground state energy
-	\item double occupancy
-	\end{itemize}
-
-\item Upgrade to two-site cluster:
-	\begin{itemize}
-	\item Study a two-impurity model under renormalisation group
-	\item Derive the tiling and Greens function relations for such a two-impurity model 
-	\item Demonstrate Mott MIT here.
-	\item Investigate the nature of many-particle entanglement in such a cluster
-	\item look for signs of a quantum liquid.
-	\end{itemize}
-
-\item Once we have a handle on the zero temperature features, we intend to compute Greens functions at non zero temperatures.
-
-\item This method can also be extended to various other models of strong correlation:
-	\begin{enumerate}
-		\item Heisenberg model, by starting from a Kondo model effective Hamiltonian
-		\item Periodic Anderson model, by starting from a SIAM with a dispersive bath
-		\item Periodic Kondo model, by starting from a Kondo model with a dispersive bath
-	\end{enumerate}
-\end{enumerate}
 
@@
 
-\chapter{Physics of the generalised single-impurity Anderson model}
-\label{chap:urg1}
-\section{Introduction of spin-exchange and charge isospin-exchange interactions into the SIAM: the generalised SIAM}
-We will now study the generalised SIAM obtained by introducing spin-exchange and charge isospin-exchange interactions between the impurity and the conduction bath~\cite{zitko_2006}.
-Such terms are generated when one does a Schrieffer-Wolff transformation on the SIAM, but we will find it prudent to keep these terms in the bare model itself.
-
-The spin-exchange interaction has the form
-\begin{equation}\begin{aligned}
-	J \vec{S_d}\cdot\vec{s} = J \left[S_d^z s^z + \frac{1}{2}\left( S_d^+ s^- + S_d^- s^+ \right) \right] ~,
-\end{aligned}\end{equation}
-where \(\vec S_d = \left(S_d^x, S_d^y, S_d^z\right) = \sum_{\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{d\alpha}c_{d\beta}\) is the impurity spin operator, \(\vec s = \sum_{kk^\prime\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{k\alpha}c_{k^\prime\beta}\) is the spin operator for the conduction bath and \(J\) is the spin-exchange coupling.
-The bath spin operator actually acts locally, as can be seen by Fourier transforming to real space (using the definition \(f(k) = \frac{1}{\sqrt N}\sum_r g(r)\exp(ikr)\)):
-\begin{equation}\begin{aligned}
-	\vec s = \sum_{k k^\prime r r^\prime} \frac{1}{N} e^{ikr - ik^\prime r^\prime} \vec \sigma_{\alpha\beta} c^\dagger_{r\alpha} c_{r^\prime\beta} = \sum_{rr^\prime}\frac{1}{N}\vec \sigma_{\alpha\beta} c^\dagger_{r\alpha} c_{r^\prime\beta} N \delta(r)\delta(r^\prime) = \vec \sigma_{\alpha\beta} c^\dagger_{0\alpha} c_{0\beta}
-\end{aligned}\end{equation}
-
-In order to introduce the charge isospin coupling, we define the Nambu spinor \cite{anderson1958random,nambu_1960} \(\psi^k = \left( c_{k\uparrow} \quad c^\dagger_{k\downarrow} \right)\), and the charge isospin \cite{zitko_2006} for the mobile conduction electrons
-\begin{equation}\begin{aligned}
-\vec C = \sum_{kk^\prime} {\psi^k}^\dagger \vec S \psi^{k^\prime} = \frac{1}{2}\sum_{kk^\prime\alpha\beta} {\psi^k_\alpha}^\dagger \vec \sigma_{\alpha\beta} \psi^{k^\prime}_\beta
-\end{aligned}\end{equation}
-The various components of the isospin are
-\begin{equation}\begin{aligned}
-	C^z &= \sum_{kk^\prime\sigma}\frac{1}{2} {\psi^k_\sigma}^\dagger \sigma^z_{\sigma\sigma} \psi^{k^\prime}_\sigma = \frac{1}{2}\sum_{kk^\prime\sigma}\left(c^\dagger_{k\sigma}c_{k^\prime \sigma} - \frac{1}{2}\delta_{kk^\prime}\right)\label{diagonalCz}\\
-	C^x &= \sum_{kk^\prime\sigma}\frac{1}{2} {\psi^k_\sigma}^\dagger \sigma^x_{\sigma\overline\sigma} \psi^{k^\prime}_{\overline\sigma} = \sum_{kk^\prime\sigma} \frac{\sigma}{4}\left( c^\dagger_{k\sigma}c^\dagger_{k^\prime\overline\sigma} + \text{h.c.} \right) \\
-	C^y &= \sum_{kk^\prime\sigma}\frac{1}{2} {\psi^k_\sigma}^\dagger \sigma^y_{\sigma\overline\sigma} \psi^{k^\prime}_{\overline\sigma} = \sum_{kk^\prime\sigma} - \frac{i\sigma}{4}\left( c^\dagger_{k\sigma}c^\dagger_{k^\prime\overline\sigma} - \text{h.c.} \right)\\
-\end{aligned}\end{equation}
-It is easy to verify that these operators satisfy the SU(2) commutation algebra.
-For example, if we write \(C^x = A + A^\dagger\) and \(C^y = B + B^\dagger\), then \(\left[ C^x, C^y \right] = \left[ A, B^\dagger \right] - \text{h.c.}\), where
-\begin{equation}\begin{aligned}
-	\left[ A, B^\dagger \right] = \frac{1}{4}\sum_{kk^\prime,qq^\prime}\left[ c^\dagger_{k\uparrow}c^\dagger_{k^\prime \downarrow}, i c_{q^\prime \downarrow}c_{q \uparrow} \right] = \frac{i}{4}\sum_{kq}\left(c^\dagger_{k\uparrow}c_{q \uparrow} - c_{k \downarrow}c^\dagger_{q \downarrow}\right)
-\end{aligned}\end{equation}
-and therefore
-\begin{equation}\begin{aligned}
-	\implies \left[ C^x, C^y \right] = \frac{i}{2}\sum_{kq}\left(c^\dagger_{k\uparrow}c_{q \uparrow} - c_{k \downarrow}c^\dagger_{q \downarrow}\right) = i C^z
-\end{aligned}\end{equation}
-There are similar operators for the impurity electron:
-\begin{equation}\begin{aligned}
-	\psi_d = \left( c_{d\uparrow} \quad c^\dagger_{d\downarrow}\right), &&\vec C_d = \frac{1}{2}\sum_{\beta} {\psi_{d,\alpha}}^\dagger \vec \sigma_{\alpha\beta} \psi_{d,\beta}
-\end{aligned}\end{equation}
-The full charge-Kondo interaction can now be written down in terms of these isospins:
-\begin{equation}\begin{aligned}
-	K \vec{C_d}\cdot\vec{C} = K \left[C_d^z C^z + \frac{1}{2}\left(C_d^+ C^-+ C_d^- C^+\right)\right]
-\end{aligned}\end{equation}
-where \(C^\pm \equiv C^x \pm iC^y\).
-\begin{equation}\begin{aligned}
-	C^+ = \sum_{kk^\prime} c^\dagger_{k\uparrow}c^\dagger_{k^\prime\downarrow}, && C^- = \sum_{kk^\prime}c_{k^\prime\downarrow}c_{k\uparrow}
-\end{aligned}\end{equation}
-The full generalised Anderson model Hamiltonian, at particle-hole symmetry, is
-\begin{equation}\begin{aligned}
-	\mathcal{H} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} + \epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} + K \vec{C_d}\cdot\vec{C}
-\end{aligned}\end{equation}
-
-For the URG analysis, at each RG step, we decouple the electronic states \(q\beta\) on the \(k-\)space shell of radius\(\Lambda_j\).
-For simplicity, we will only consider those diagonal terms in the denominator that either have both \(q\beta\) and \(q\overline\beta\) or  both \(q\beta\) and \(d\) or both \(q\overline\beta\) and \(d\).
-Terms that have purely \(q\overline\beta\) will not be considered.
-Also, the scattering between just \(d\) and \(q\overline\beta\) can be ignored since it is diagonal in \(q\beta\).
-The diagonal (number-preserving) part is
-\begin{equation}\begin{aligned}
-	H_D = \sum_\beta\epsilon_q\tau_{q\beta} + \epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + J S^z_ds^z_{q} + K C^z_d C^z_q\\
-\end{aligned}\end{equation}
-where \(s_q^z = \frac{1}{2}\left(\hat n_{q\uparrow} - \hat n_{q\downarrow}\right)\) and \(C_q^z = \frac{1}{2}\left(\hat n_{q \uparrow} + \hat n_{q \downarrow} - 1\right)\). The off-diagonal part is:
-\begin{equation}\begin{aligned}
-	H_X = \sum_{\beta=\uparrow,\downarrow}\left[V c^\dagger_{d\beta}c_{q\beta} + \frac{1}{2}J \sum_{k<\Lambda_N}\left\{\left(\hat n_{d \beta} - \hat n_{d \overline\beta}\right) \frac{1}{2} c^\dagger_{k\beta}c_{q\beta} + c^\dagger_{d\beta}c_{d\overline\beta}c^\dagger_{k\overline\beta}c_{q \beta}\right\} + \frac{1}{2}K \sum_{k<\Lambda_N}\left\{\left(\hat n_d -1\right)\frac{1}{2}c^\dagger_{k\beta}c_{q\beta} + \right.\right.\\
-\left.\left.c^\dagger_{d\beta}c^\dagger_{d\overline\beta}c_{k\overline\beta}c_{q\beta}\right\}\right] + \text{h.c.}~.
-\end{aligned}\end{equation}
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/zeromode.pdf}
-	\caption{While we have studied the full model under renormalisation group, often we will turn to a simplified zero-bandwidth version of the model that is obtained by ignoring the kinetic energy part of the Hamiltonian.
-This zero-bandwidth model is effectively a two site model.}
-\end{figure}
-
-\section{RG equations for generalised SIAM}
-\begin{equation}\begin{aligned}
-	\Delta \epsilon_d &= 2V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + \frac{n_j}{2}\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right),\\
-	\Delta V &= -\frac{3n_j V}{8}\left[J\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)\right],\\
-	\Delta J &= -\frac{n_j J^2}{\omega - \frac{D}{2} + \frac{J}{4}},\\ 
-	\Delta K &= -\frac{n_j K^2}{\omega - \frac{D}{2} + \frac{K}{4}}
-\end{aligned}\end{equation}
-In terms of \(U = -2\epsilon_d\), the equations become
-\begin{gather}
-	\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\left(\frac{J^2}{d_2} - \frac{K^2}{d_3}\right),\\
-	\Delta V = -\frac{3n_j V}{8}\left[J\left(\frac{1}{d_2} + \frac{1}{d_1}\right) + K \left(\frac{1}{d_3} + \frac{1}{d_0}\right)\right],\\
-	\Delta J = -\frac{n_j J^2}{d_2}, \quad\quad\Delta K = -\frac{n_j K^2}{d_3}
-\end{gather}
-\(d_i\) are the denominators:
-\begin{equation}\begin{aligned}
-	\label{denominators}
-	d_0 = \omega - \frac{D}{2} - \frac{U}{2} + \frac{K}{4}, \quad d_1 = \omega - \frac{D}{2} + \frac{U}{2} + \frac{J}{4}, \quad d_2 = \omega - \frac{D}{2} + \frac{J}{4}, \quad d_3 = \omega - \frac{D}{2} + \frac{K}{4}
-\end{aligned}\end{equation}
-
-\section{Nature of coupling RG flows}
-\subsection{Repulsive interaction on impurity: \(U>0\)}
-For the Hamiltonians with positive on-site correlation, we will assume that the spin-exchange coupling is positive and charge isospin-exchange coupling is negative: \(J>0, K<0\).
-This choice is motivated by the signs of the corresponding terms when they are generated via a Schrieffer-Wolff transformation~\cite{schrieffer1966}.
-The impurity-bath hybridisation \(V\) is always positive.
-The sign of the couplings lead to inequalities among the denominators which we will utilise at various points.
-First of all, since \(U>0\), we have \(d_1 - d_2 = \frac{U}{2} > 0\).
-Secondly, since \(K<0\), we have \(d_2 - d_3 = \frac{J-K}{4} > 0\).
-And finally, we have \(d_3 - d_0 = \frac{U}{2} > 0\).
-Combining these, we can write
-\begin{equation}\begin{aligned}
-	\label{ineq_den}
-	d_1 > d_2 > d_3 > d_0
-\end{aligned}\end{equation}
-
-The strong coupling regime is defined as the range of values of \(\omega\) where the hybridisation is relevant.
-This is ensured by the assumption \(d_1<0\).
-From eq.~\ref{ineq_den}, we can then conclude that all denominators are negative: \(d_i = - |d_i|\).
-The simplest consequence of this is the RG flow of \(K\):
-\begin{equation}\begin{aligned}
-	\Delta K= -\frac{n_j K^2}{d_3} = \frac{n_j K^2}{|d_3|} > 0 \implies K_{j+1} > K_j \implies K_0 = -|K_0|, K^* \to 0
-\end{aligned}\end{equation}
-\(K_j\) is the value of \(K\) after the \(j^\text{th}\) RG step, \(K_0\) representing the bare value.
-In other words, since \(d_3 < 0\), the RG equation for \(K\) provides an algebraic increment, and the negative \(K\) increases and flows towards zero.
-The \(*\) indicates a fixed point value.
-The isospin coupling is irrelevant in this regime, and we will ignore it.
-
-The coupling \(J\), on the other hand, is relevant and flows from a small positive value towards a large value at strong coupling.
-\begin{equation}\begin{aligned}
-	\Delta J= -\frac{n_j J^2}{d_2} = \frac{n_j J^2}{|d_2|} > 0 \implies J_{j+1} > J_j \implies J_0 \to \text{ large } J^* ~(\text{strong coupling})
-\end{aligned}\end{equation}
-The value of \(J^*\) is obtained when the denominator \(d_2\) vanishes.
-
-Because of the RG irrelevance of \(K\), we can simplify the RG equation for \(V\):
-\begin{equation}\begin{aligned}
-	\Delta V = -\frac{3n_j VJ}{8}\left(\frac{1}{d_2} + \frac{1}{d_1}\right) = \frac{3n_j VJ}{8}\left(\frac{1}{|d_2|} + \frac{1}{|d_1|}\right) > 0
-\end{aligned}\end{equation}
-Since both the denominators are positive, \(V\) is relevant. The fixed point value \(V^*\) is attained when the denominator \(d_1\) vanishes (\(d_1\) will vanish earlier than \(d_2\)).
-
-We can compare the rate of flows of \(V\) and \(J\):
-\begin{equation}\begin{aligned}
-	\frac{\Delta V}{\Delta J} = \frac{3V}{8J}\left(1 + \frac{|d_2|}{|d_1|}\right) > \frac{3V}{4J}
-\end{aligned}\end{equation}
-There we used the fact that \(|d_2| > |d_1|\).
-We finally come to the RG equation for \(U\):
-\begin{equation}\begin{aligned}
-	\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\frac{J^2}{d_2} = -4V^2\left(U + \frac{J}{4}\right)\frac{n_j}{d_0 d_1} - \frac{n_j J^2}{d_2}
-\end{aligned}\end{equation}
-For \(V>J\), we can expect \(U\) to be irrelevant. On the other hand, \(V<J\) makes \(U\) relevant.
-
-In short, the \(U>0\) regime is characterised by an irrelevant isospin-exchange coupling \(K\) and a relevant spin-exchange coupling \(J\), and the following set of RG equations for the remaining couplings \(U\) and \(V\):
-\begin{equation}\begin{aligned}
-	\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\frac{J^2}{d_2}, \quad \Delta V = -\frac{3n_j VJ}{8}\left(\frac{1}{d_2} + \frac{1}{d_1}\right)
-\end{aligned}\end{equation}
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U_gt_0,U.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U_gt_0,J.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_irr,U_gt_0,V.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U_gt_0,U.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U_gt_0,J.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/U_rel,U_gt_0,V.pdf}
-\end{figure}
-
-\subsection{Attractive interaction on impurity: \(U<0\)}
-Here, we have \(J<0\) and \(K>0\). The denominators satisfy the following inequality in this regime:
-\begin{equation}\begin{aligned}
-	d_0 > d_3 > d_2 > d_1
-\end{aligned}\end{equation}
-
-The strong coupling regime here corresponds to \(d_0 < 0\).
-This again means that all the denominators are negative.
-The spin-exchange coupling \(J\) is now irrelevant, because its bare value is negative while its RG equation is positive: \(\Delta J>0\).
-Moreover, the isospin coupling \(K\) is now positive and so is its RG equation: \(\Delta K>0\), which means it flows to strong coupling.
-\(V\) also flows to strong coupling.
-The RG equation for \(U\) can be written as
-\begin{equation}\begin{aligned}
-	\Delta U = 4V^2\left(\frac{K}{4} - U\right)\frac{n_j}{d_0 d_1} + \frac{n_j K^2}{d_3}
-\end{aligned}\end{equation}
-The first term is necessarily positive, while the second term is negative.
-This means that for roughly \(V_0 > J_0\), we  will have \(\Delta U > 0\), and since \(U_0 < 0\), this amounts to an irrelevant flow of \(U\) towards zero.
-On the other hand, for \(J_0 > V_0\), we will have \(\Delta U < 0\), and this corresponds to a relevant flow of \(U\) towards large negative value.
-
-In other words, the RG flows in this regime can be exactly mapped to those in the positive \(U\) regime.
-The general statement is: in the strong coupling regime of positive(negative) \(U\), \(V\) is always relevant, \(J\)(\(K\)) is relevant, \(K\)(\(J\)) is irrelevant, and \(U\) is relevant when \(J(K) > V\), otherwise \(U\) is irrelevant.
-
-\section{Effective Hamiltonian and ground state}
-The fixed point Hamiltonian can, in general, be written as
-\begin{equation}\begin{aligned}
-	\mathcal{H}^* = \sum_{\sigma, k}\epsilon_k \tau_{k\sigma} - \frac{U^*}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2  + \sum_{\sigma, k < \Lambda^*}\left( V^* c^\dagger_{k\sigma}c_{d\sigma} + \text{h.c.} \right) + J^* \vec{S_d}\cdot\vec{s} + K^* \vec{C_d}\cdot\vec{C}
-\end{aligned}\end{equation}
-The first term is the kinetic energy of all the electrons.
-The next two terms are the impurity-diagonal pieces, featuring the renormalised interaction \(U^*\).
-The next three terms are the residual interactions between the impurity and the metal, with the renormalised couplings \(V^*, J^*\) and \(K^*\).
-The summations in these terms extend from the fixed point momentum cutoff \(\Lambda^*\) to 0.
-This is the region of momentum space  which the URG was unable to decouple.
-The operators \(\vec s\) and \(\vec C\) represent the macroscopic magnetic and charge spins formed by the remaining electrons that are lying inside the window \(\left[ 0, \Lambda^* \right] \):
-\begin{equation}\begin{aligned}
-	\vec s = \sum_{kk^\prime<\Lambda^*\atop{\alpha\beta}} c^\dagger_{k\alpha}\vec \sigma_{\alpha\beta}c_{k^\prime\beta}
-\end{aligned}\end{equation}
-Our goal here is to write down the ground state wavefunction for this low-energy Hamiltonian.
-
-To make progress, we will simplify the effective Hamiltonian by taking the zero bandwidth limit.
-This reduces it to a two-site problem.
-One site is of course the impurity site, and this site will be labeled as site 1.
-The other site will be formed by the center of mass degree of freedom of the conduction electrons, and will be labeled as site 2.
-The Hamiltonian for this two-site problem is
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{IR} = - \frac{U^*}{2}\left(\hat n_{1 \uparrow} - \hat n_{1 \downarrow}\right)^2 + V^*\sum_{\sigma}\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.} \right) + J^*\vec{S_1}\cdot\vec{S_2} + K^* \vec{C_1}\cdot\vec{C_2}
-\end{aligned}\end{equation}
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.4\textwidth]{../figures/two_site_problem.png}
-	\caption{Two-site effective problem of fixed point Hamiltonian}
-	\label{twosite}
-
-\end{figure}
-The subscripts on the operators designate the site on which they act; \(\hat n_1\) is the number operator for the first site.
-
-We will adopt the following notation to represent the states in this Hilbert space.
-A general state will be represented in the Fock space basis as \(\ket{n_{1 \uparrow}n_{1 \downarrow}n_{2 \uparrow}n_{2 \downarrow}}\).
-For example,
-\begin{equation}\begin{aligned}
-	\ket{1101} = c^\dagger_{1 \uparrow}c^\dagger_{1 \downarrow}c^\dagger_{2 \downarrow}\ket{-}
-\end{aligned}\end{equation}
-\(\ket{-}\) is the vacuum state.
-
-For \(U>0\), the ground state is given by
-\begin{gather}
-	\label{gstate}
-	\ket{\Psi}_\text{1} = c_s \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c_c \frac{1}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right), \quad E_1 =  -V^*\sqrt{\gamma^2 + 4} -\frac{1}{4}U^* - \frac{3}{8}{J^*}
-\end{gather}
-where $\gamma = \frac{1}{2{V^*}}\left[ \frac{1}{4}\left( 3J^* + K^* \right) + \frac{1}{2}U^* \right]$. The probabilities for the spin and charge sectors for the ground state are
-\begin{equation}\begin{aligned}
-	\label{coeff_def}
-	\left(c_s\right)^2 = \frac{1}{2\sqrt{\gamma^2 + 4}}\left(\sqrt{\gamma^2 + 4} + \gamma\right), \quad \left(c_c \right)^2 = \frac{1}{2\sqrt{\gamma^2 + 4}}\left(\sqrt{\gamma^2 + 4} - \gamma\right)~.
-\end{aligned}\end{equation}
-For (roughly) \(J_0 > V_0\), we get \(J^* \gg V^*\) and \(U^* \gg U_0\) so that \(\gamma \gg 1\).
-This gives \(\left( c_s \right) ^2 \sim 1\) and \(\left( c_c \right) ^2 \sim 0\).
-The entire contribution to the ground state then comes from the spin sectors of the two sites.
-This is calculated numerically in fig.~\ref{cs_cc}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/coeffs_vs_J.pdf}
-	\caption{Variation of relative weights \(c_s\) and \(c_c\) with \(J_0\)}
-	\label{cs_cc}
-\end{figure}
-
-In the other regime of \(U<0\), the two competing states are \(\ket{\Psi}_1\) defined above (with energy \(E_1\)), and \(\ket{\Psi_2}\), the charge singlet: \(\ket{\Psi}_2 = \frac{1}{\sqrt 2}\left( \ket{2,0} - \ket{0,2} \right)\) having energy \(E_2\).
-\begin{equation}\begin{aligned}
-	E_2 = -\frac{3}{4}K^*, \quad E_1 - E_2 = -\frac{1}{4}\sqrt{\left( \frac{1}{2}K^* + U^* \right)^2 + (4V^*)^2} - \frac{1}{4}U^* + \frac{3}{4}K^*
-\end{aligned}\end{equation}
-For \(V_0 \gg K_0\), the largest energy scale will be \(V^*\), and we can then approximate this difference as
-\begin{equation}\begin{aligned}
-	E_1 - E_2 \simeq -V^* < 0
-\end{aligned}\end{equation}
-In such a case, \(\ket{\Psi}_1\) will therefore be the ground state. In the other regime \(V_0 \ll K_0\), the largest energy scale will be \(K^*\), and we can then write
-\begin{equation}\begin{aligned}
-	E_1 - E_2 \simeq - \frac{1}{8}K^* + \frac{3}{4}K^* > 0
-\end{aligned}\end{equation}
-In this case, the ground state will be \(\ket{\Psi}_2\).
-There exists, therefore, a phase transition at a critical plane \((U_c, K_c, V_c)\), where the ground state changes between the charge singlet \(\ket{\Psi}_2\) and the spin singlet + charge triplet \(\ket{\Psi}_1\).
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/E1_vs_E3.pdf}
-\end{figure}
-
-\section{Approach towards the thermodynamic limit}
-
-{\bf \Large [Update with V vs D plots]}
-
-The URG method works strictly on finite systems and leads to finite values of fixed point couplings.
-The behaviour of the Hamiltonian in the thermodynamic limit can then be determined using finite-size scaling where we increase the bandwidth and decrease the width of each RG step.
-When applied to the fixed point value of the impurity-bath hybridisation parameter \(V\) (fig.~\ref{V_vs_D}), it can be seen that the fixed point value increases as the system size is increased, implying that the continuum limit of \(V^*\) is \(\infty\).
-This holds for both \(V_0 > J_0\) and \(V_0 < J_0\), as shown in the two panels of fig.~\ref{V_vs_D}.
-\begin{figure}[!htb]
-	\centering
-	\hspace*{\fill}
-	\includegraphics[width=0.4\textwidth]{../figures/Vstar_vs_D_smallV.pdf}
-	\hspace*{\fill}
-	\includegraphics[width=0.4\textwidth]{../figures/Vstar_vs_D_largeV.pdf}
-	\hspace*{\fill}
-	\caption{Variation of fixed point value \(V^*\) with increasing bandwith \(D_0\), for both \(V_0 > J_0\) and \(V_0 < J_0\).}
-	\label{V_vs_D}
-\end{figure}
-
-In a similar manner, we checked the variation of the spin and charge probabilities, \(c_s\) and \(c_c\), in the ground state, with increasing bandwith. The result is shown in fig.~\ref{c_vs_D}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/coeffs_vs_D.pdf}
-	\caption{Variation of spin and charge fractions, \(c_s\) and \(c_c\), of the ground state, as a function of bare bandwidth \(D_0\).
-Left and right panels show the cases of \(J_0 < V_0\) and \(J_0 > V_0\) respectively.}
-	\label{c_vs_D}
-\end{figure}
-For both \(V_0 < J_0\) and \(V_0 > J_0\), we see that the spin contribution increases towards unity while the charge contribution vanishes.
-This indicates that at large bandwidth, the ground state becomes purely a spin singlet, formed purely by singly-occupied impurity states.
-\begin{equation}\begin{aligned}
-	\label{gstate_kondo}
-	\lim_{D_0 \to \infty} \ket{\Psi}_1 = \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) 
-\end{aligned}\end{equation}
-
-\section{Effective temperature scale at the fixed point}
-We will first change the discrete RG equation to a continuum equation by interpreting \(\Delta J\) as \(\frac{\Delta J}{\Delta \ln D}\), where the denominator is unity: \(\Delta \ln D = 1\).
-Now, since the bandwidth is decreasing under the RG, we can write \(\Delta \ln D = -d \ln D\).
-The continuum equation (for \(K=0\)) becomes
-\begin{equation}\begin{aligned}
-	\frac{\:\mathrm{d}J}{\:\mathrm{d}\ln D} = n(0)J^2 \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}
-\end{aligned}\end{equation}
-where we have replaced by the number of states at each shell with that at the Fermi surface (uniform DOS).
-We can define a dimensionless quantity \(g \equiv \frac{J}{\frac{D}{2}} - \omega\).
-In terms of \(g\), the continuum RG equation becomes
-\begin{equation}\begin{aligned}
-	-\frac{\:\mathrm{d}g}{\:\mathrm{d}\ln D} + \frac{D g}{2\omega - D} = \frac{n(0) g^2}{1 - \frac{g}{4}}
-\end{aligned}\end{equation}
-Now, for the specific case where \(D\) is small (\(D \to 0\)), we can simplify and integrate this equation:
-\begin{equation}\begin{aligned}
-	\frac{\:\mathrm{d}g}{\:\mathrm{d}\ln D} &= \frac{n(0) g^2}{\frac{g}{4} - 1}\\
-	\implies \left[\frac{1}{g} + \frac{1}{4}\ln g\right]_{g_0}^{g^*} &= n(0)\ln D\big\vert_{D_0}^{D^*}
-\end{aligned}\end{equation}
-\(g^*(_0), D^*(_0)\) are the fixed point (bare) values of \(g, D\).
-From the denominator structure, the fixed-point value is \(g^* =  4\).
-This gives an estimate of the bandwidth of the emergent window:
-\begin{equation}\begin{aligned}
-	D^* = D_0 \left( \frac{4}{g_0} \right)^\frac{1}{4n(0)}\exp\left\{-\frac{1}{n(0)}\left(\frac{1}{g_0} - \frac{1}{4}\right)\right\}
-\end{aligned}\end{equation}
-We can now define a temperature scale~\cite{wilson1975,hrk_wilson_1980} for the fixed-point theory:
-\begin{equation}\begin{aligned}
-	T_K \equiv \frac{2N^*}{\pi}D^* = \frac{2N^*}{\pi}D_0 \left( \frac{4}{g_0} \right)^\frac{1}{4n(0)}\exp\left\{-\frac{1}{n(0)}\left(\frac{1}{g_0} - \frac{1}{4}\right)\right\}
-\end{aligned}\end{equation}
-The factor of \(2N^*\) is inserted to make the Kondo temperature intensive (we will see below that the \(N^*\) allows it to  be written in terms of parameters of the two-site Hamiltonian) - \(2N^*\) is the total number of momentum states in the fixed point theory.
-The factor of \(\frac{1}{\pi}\) is for aesthetic reasons.
-Since we have and will primarily work with \(\omega=0\), the fixed point condition can be used to write \(D^* = \frac{J^* + K^*}{2}\).
-\begin{equation}\begin{aligned}
-	T_K = \frac{2N^*}{\pi}\frac{1}{2}\left(J^* + K^*\right) = \frac{1}{\pi}\left(j + k\right)
-\end{aligned}\end{equation}
-\section{Impurity susceptibilities}
-\subsection{Spin susceptibility}
-The spin susceptibility is defined as
-\begin{equation}\begin{aligned}
-	\label{chi_def}
-	\chi(\beta) = \beta \left(\left<\left(S_d^z\right)^2\right> - \left<S_d^z\right>^2\right)
-\end{aligned}\end{equation}
-There is an alternate way of calculating this. We insert a fictitious magnetic field that couples only to the impurity site. The Hamiltonian in the presence of this field is
-\begin{equation}\begin{aligned}
-	\label{field_ham}
-	\mathcal{H}^\prime(B) = \mathcal{H} + B S_d^z
-\end{aligned}\end{equation}
-The susceptibility is then given by
-\begin{equation}\begin{aligned}
-	\label{chi_exp}
-	\chi(\beta) &= \lim_{B \to 0}\frac{1}{\beta}\left[\frac{1}{Z(B)} \frac{\partial^2{Z(B)}}{\partial{B^2}}-\frac{1}{Z(B)^2} \left(\frac{\partial{Z(B)}}{\partial{B}}\right)^2\right]
-\end{aligned}\end{equation}
-where \(Z(B)\) is the partition function of the Hamiltonian \(\mathcal{H}^\prime(B)\).
-The following is to prove that the RHS of eqs.~\ref{chi_def} and \ref{chi_exp} are the same.
-We start with \ref{chi_exp}.
-The first derivative can be written as
-\begin{equation}\begin{aligned}
-	\frac{\partial{Z(B)}}{\partial{B}} = \text{Trace}\left[\frac{\partial{}}{\partial{B}} \exp\left\{-\beta\left( \mathcal{H} + BS_d^z \right) \right\}\right] = \text{Trace}\left[-\beta S_d^z \exp\left\{-\beta\left( \mathcal{H} + BS_d^z \right) \right\}\right]
-\end{aligned}\end{equation}
-which means the first term becomes
-\begin{equation}\begin{aligned}
-	\lim_{B \to 0}-\frac{1}{Z(B)^2} \left(\frac{\partial{Z(B)}}{\partial{B}}\right)^2 = -\left(\beta \frac{1}{\text{Trace}\left[\exp\left\{-\beta\mathcal{H}\right\}\right]} \text{Trace}\left[S_d^z \exp\left\{-\beta\mathcal{H}\right\}\right]\right)^2 = -\beta^2 \left<S_d^z\right>^2
-\end{aligned}\end{equation}
-The second derivative is
-\begin{equation}\begin{aligned}
-	\frac{\partial^2{Z(B)}}{\partial{B^2}} = \text{Trace}\left[-\beta S_d^z  \frac{\partial{}}{\partial{B}}\exp\left\{-\beta \left( \mathcal{H} + BS_d^z \right) \right\}\right] = \text{Trace}\left[\beta^2 \left(S_d^z\right)^2 \exp\left\{-\beta \left( \mathcal{H} + BS_d^z \right) \right\}\right]
-\end{aligned}\end{equation}
-so the second term becomes
-\begin{equation}\begin{aligned}
-	\lim_{B \to 0}\frac{1}{Z(B)} \frac{\partial^2{Z(B)}}{\partial{B^2}} = \beta^2 \frac{1}{\text{Trace}\left[\exp\left\{-\beta \mathcal{H}\right\}\right]}\text{Trace}\left[\left(S_d^z\right)^2 \exp\left\{-\beta \mathcal{H}\right\}\right] = \beta^2 \left<\left(S_d^z\right)^2 \right>
-\end{aligned}\end{equation}
-The full thing becomes
-\begin{equation}\begin{aligned}
-	\lim_{B \to 0}\frac{1}{\beta}\left[\frac{1}{Z(B)} \frac{\partial^2{Z(B)}}{\partial{B^2}}-\frac{1}{Z(B)^2} \left(\frac{\partial{Z(B)}}{\partial{B}}\right)^2\right] = \frac{1}{\beta}\left(-\beta^2 \left<S_d^z\right>^2 + \beta^2 \left<\left(S_d^z\right)^2 \right>\right) \\
-	= \beta \left(\left<\left(S_d^z\right)^2\right> - \left<S_d^z\right>^2\right) 
-\end{aligned}\end{equation}
-This completes the proof.
-
-To calculate the impurity susceptibility, we take the zero bandwidth Hamiltonian \(\mathcal{H}_{IR}\) and insert a magnetic field to obtain the Hamiltonian in eq.~\eqref{field_ham}.
-For a particular regime of \(U\), only one of \(J\) or \(K\) will be non-zero.
-We then numerically diagonalise this Hamiltonian to obtain the partition function \(Z(B)\) and its derivatives.
-The spin susceptibility can then be calculated using eq.~\eqref{chi_exp}.
-The results for \(U>0\) are shown in fig.~\ref{chi}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.49\textwidth]{../figures/chiT.pdf}
-	\includegraphics[width=0.49\textwidth]{../figures/chiT_large.pdf}
-	\includegraphics[width=0.49\textwidth]{../figures/chi.pdf}
-	\caption{Spin susceptibility of the impurity times temperature, for two sets of bare parameters, in \(U>0\).
-At low temperatures, it becomes linear because \(\chi\) itself becomes constant (screening), while at high temperatures, \(\chi\times T\) becomes constant because of the paramagnetic \(\sim 1/T\) form of \(\chi\).
-For the right panel with a larger value of the spin-exchange coupling, the \(\chi\) tries to go towards the local moment value of \(1/4\) but eventually drops back to the free orbital value of \(1/8\).}
-	\label{chi}
-\end{figure}
-
-\subsection{Charge susceptibility}
-We can similarly define the charge susceptibility as
-\begin{equation}\begin{aligned}
-	\label{zero_chi_charge}
-	\chi(\beta) = \beta \left(\left<\left(C_d^z\right)^2\right> - \left<C_d^z\right>^2\right) = \lim_{B_c \to 0}\frac{1}{\beta}\left[\frac{1}{Z(B_c)} \frac{\partial^2{Z(B_c)}}{\partial{B_c^2}}-\frac{1}{Z(B_c)^2} \left(\frac{\partial{Z(B_c)}}{\partial{B_c}}\right)^2\right]
-\end{aligned}\end{equation}
-where \(B_c\) is now a field that couples to the impurity charge-isospin:
-\begin{equation}\begin{aligned}
-	\label{charge_field}
-	\mathcal{H}^\prime(B_c) = \mathcal{H} + B_c C_d^z
-\end{aligned}\end{equation}
-The charge susceptibility for \(U<0\) is shown in fig.~\ref{chi_charge}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.49\textwidth]{../figures/chic.pdf}
-	\includegraphics[width=0.49\textwidth]{../figures/chic_T.pdf}
-	\caption{Charge susceptibility for the impurity at \(U<0\), for two sets of bare parameters. The physics is very similar to that of the spin susceptibility in \(U>0\).}
-	\label{chi_charge}
-\end{figure}
-
-It is interesting to look at the behaviour of the charge susceptibility in the positive \(U\) regime, fig.~\ref{chi_charge_posU}.
-It  is seen that for \(J_0<V_0\), the charge susceptibility is very similar to the spin susceptibility, with a reduced saturation value.
-This is because, for that range of bare values, the ground state consists of a comparable mixture of the spin and charge states (see fig.~\ref{cs_cc}).
-This means that the magnetic field term in eq.~\eqref{charge_field} can couple to the charge component of the ground state, and give a non-zero charge susceptibility at zero temperature.
-On the other hand, for \(J_0 > V_0\), we see that \(\chi_c\) vanishes at low temperatures.
-This can again be understood from the ground state.
-For that range of bare values, the ground state can be approximated by purely the singlet, because the charge fraction \(c_-^c\) becomes very small.
-This means that the field \(B_c \) has nothing to couple with.
-Alternatively, it can be said that since the ground state has only terms with \(\hat n_d=1\), no number fluctuation is possible, and the impurity isospin is not susceptible at all to charge polarisation.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.48\textwidth]{../figures/chiC_posU_J0=10.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/chiC_posU_J0=40.pdf}
-	\caption{Charge susceptibility of the impurity in the positive \(U\) regime, for two values of \(J_0\).
-The smaller bare value leads to a spin+charge mixed ground state, and hence a non-zero \(\chi_c\) at zero temperature.
-The larger \(J_0\), however, leads to a purely spin ground state without any number fluctuation, and this gives vanishing \(\chi_c\) at zero temperature.}
-	\label{chi_charge_posU}
-\end{figure}
-
-From eq.~\eqref{gstate_kondo}, we know that in the thermodynamic limit, the ground state of \(U>0\) regime reduces to a screened local moment.
-That then implies that the charge susceptibility vanishes at low temperatures, owing to lack of any charge content in the ground state in the large bandwidth limit.
-\begin{equation}\begin{aligned}
-	\lim_{D_0 \to \infty}\chi_c(U>0, T \to 0) = 0
-\end{aligned}\end{equation}
-
-\section{Specific heat}
-The specific heat is calculated by diagonalizing the fixed point Hamiltonian, numerically.
-The obtained spectrum is denoted by \(\left\{ \mathcal{E}_i \right\} \).
-The total average energy of the impurity+cloud at temperature \(T\) is then
-\begin{equation}\begin{aligned}
-	\left<\mathcal{E} \right> = \frac{1}{Z}\sum_{i} \mathcal{E}_i e^{-\beta \mathcal{E}_i}
-\end{aligned}\end{equation}
-where \(Z = \sum_{i} e^{-\beta E_i}\) is the partition function. The specific heat of this system is thus
-\begin{equation}\begin{aligned}
-	C_V &= \frac{\partial{\left<\mathcal{E} \right>}}{\partial{T}} \\
-	    &= -\frac{1}{k_B T^2} \frac{\partial{\left<\mathcal{E} \right>}}{\partial{\beta}} \\
-	    &= \frac{1}{k_B T^2}\left[\frac{1}{Z}\sum_i \mathcal{E}_i^2 e^{-\beta \mathcal{E}_i} - \left(\frac{1}{Z}\sum_i \mathcal{E}_i e^{-\beta \mathcal{E}_i}\right)^2 \right] 
-\end{aligned}\end{equation}
-In the absence of impurity, the eigenvalues of the Hamiltonian are \(\left\{\mathcal{E}_i^0\right\}\) with a partition function \(Z^0 = \sum_{i} e^{-\beta E_i^0}\), so the bath specific heat is
-\begin{equation}\begin{aligned}
-	C_V^0 &= \frac{1}{k_B T^2}\left[\frac{1}{Z_0}\sum_i \mathcal{E}_i^2 e^{-\beta \mathcal{E}_i^0} - \left(\frac{1}{Z_0}\sum_i \mathcal{E}_i^0 e^{-\beta \mathcal{E}_i^0}\right)^2 \right] 
-\end{aligned}\end{equation}
-The impurity specific heat is the difference.
-\begin{equation}\begin{aligned}
-	C_V^\text{imp} = C_V - C_V^0
-\end{aligned}\end{equation}
-These values were calculated numerically and plotted against temperature in fig.~\ref{cv}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.6\textwidth]{../figures/Cv.pdf}
-	\caption{Impurity specific heat}
-	\label{cv}
-\end{figure}
-
-\section{Renormalization of impurity spectral function}
-In this section we will obtain the impurity spectral function~\cite{costi2000,rosch_costi2003,bullaNRGreview}, which is defined in terms of the impurity Green's function as
-\begin{equation}\begin{aligned}
-	\mathcal{A(\omega)} = -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] 
-\end{aligned}\end{equation}
-The zero temperature retarded Green's function for the impurity, in the frequency domain, can be written as (see Appendix.~\ref{appx-spectral-func})
-\begin{equation}\begin{aligned}
-	\mathcal{A(\omega)} = \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]
-\end{aligned}\end{equation}
-where \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in.
-The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term
-Since this is in terms of the exact eigenstates, it is a discrete sum of delta-functions.
-In practice, we get a continuous distribution.
-To compare with experiment, we need to convert the discrete sum into a continuous function.
-Following \cite{bullaNRGreview}, we replace the delta-functions at \(\pm x_n \equiv \pm(E_n - E_0)\) by normalized Gaussian functions
-\begin{equation}\begin{aligned}
-	\delta(\omega \pm x_n) \to \frac{1}{\eta_n\sqrt \pi}e^{-\left(\frac{\omega \pm x_n}{\eta_n}\right)^2}
-\end{aligned}\end{equation}
-The parameter \(\eta_n\) determines the height and width of the Gaussian, and is chosen such that the higher energy poles are broader than the lower energy ones:
-\begin{equation}\begin{aligned}
-	\eta_n = 4\Delta + \frac{1}{2}|x_n| 
-\end{aligned}\end{equation}
-\(\Delta = \pi \rho(0)V^2\) is the relevant energy scale for the non-interacting \((U=0)\) problem, \(\rho(0)\) being the density of states of the conduction bath at the Fermi energy.
-As a result, the function that we will numerically compute and plot is
-\begin{equation}\begin{aligned}
-	\mathcal{A(\omega)} &= \sum_{n,0}\frac{1}{d_0 \sqrt \pi \eta_n}\left[||\bra{0}c_{d\sigma}\ket{n}||^2e^{-\left(\frac{\omega - x_n}{\eta_n}\right)^2} + ||\bra{n}c_{d\sigma}\ket{0}||^2e^{-\left(\frac{\omega + x_n}{\eta_n}\right)^2}\right]
-\end{aligned}\end{equation}
-From the results of Langreth \cite{langreth1966}, we know that the spectral function at zero frequency is fixed by the occupancy of the impurity.
-Since we are in the particle-hole symmetric regime, this occupancy is fixed at 1, and hence so is the spectral function height at \(\omega = 0\).
-This result has been used to fix the spectral function height at the center during the computations.
-The fixed-point Hamiltonian \(H^*\) is diagonalized numerically to obtain \(\left\{E_n, \ket{n}\right\}\), for various values of the couplings.
-The intention here is to get an idea of how the spectral function morphs under the RG.
-Doing an actual reverse RG (described in \ref{rev_rg}) would require us to diagonalize a huge Hamiltonian.
-We take the simpler route of tuning the \(U\) from zero to soem large value.
-This should mimic the journey from the IR theory \((U=0)\) to the UV theory \((U \gg 0)\).
-
-The spectral function is plotted for three sets of values in fig.~\ref{spec_func}.
-For low values of \(U\), the profile is that of a single peak at zero frequency.
-This is expected because at the low energy effective theory, the high energy Hubbard side bands have been integrated out.
-As \(U\) increases, shoulder-like structures appear on either side of the peak, which finally, at larger \(U\), develop into two side-peaks.
-This is the microscopic theory, where high energy features are also relevant.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=0.00.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=3.00.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=5.00.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=10.00.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/spec_func_Ub=0_U_by_delta=25.00.pdf}
-	\caption{Impurity spectral function for multiple values of \(U\). The increase in value of \(U\) is accompanied by the appearance of the side-peaks.}
-	\label{spec_func}
-\end{figure}
-The physics of the three peaks can now be looked into.
-Since the central peak is at zero energy, it has to do with excitations that do not cost any energy.
-There are two such excitations: excitations within the spin sector and within the charge sector.
-\begin{equation}\begin{aligned}
-	\ket{\uparrow} \mathrel{\mathlarger{\mathlarger{\mathop{\rightleftarrows}}^{J S_d^-}_{JS_d^+}}}\ket{\downarrow}, &&&&\ket{\Uparrow} \mathrel{\mathlarger{\mathlarger{\mathop{\rightleftarrows}}^{K C_d^-}_{K C_d^+}}}\ket{\Downarrow}\\
-\end{aligned}\end{equation}
-The thick arrow \(\Uparrow\) represents the charge isospin.
-At particle-hole symmetry, both the spin configurations has energy of \(\epsilon_d\), while the charge configurations have energy of \(2\epsilon_d + U=0\) and 0.
-Hence, no energy is required for these excitations, which is why see a macroscopic number of cloud electrons resonating with the impurity at the Fermi surface.
-Also note that if \(\hat S_i\) and \(\hat C_j\) are two operators of the spin and charge sector (\(i,j \in \left\{ x,y,z \right\} \)), then
-\begin{equation}\begin{aligned}
-	\hat S_i \hat C_j = \hat C_j \hat S_i = 0
-\end{aligned}\end{equation}
-We can see this by applying that operator on a basis state. Since the set of four states 
-\begin{equation}\begin{aligned}
-	\ket{\hat S_i = \pm \frac{1}{2}, \hat C_j = 0}, \ket{\hat S_i = 0, \hat C_j = \pm\frac{1}{2}}
-\end{aligned}\end{equation}
-are all independent, they form a basis. If we apply the operator on these states:
-\begin{equation}\begin{aligned}
-	\hat S_i \hat C_j \ket{\hat S_i} &= 0, &&&&\hat C_j \hat S_i \ket{S_i} = S_i \hat C_j \ket{S_i} = 0\\
-	\hat C_j \hat S_i \ket{C_j} &= 0, &&&&\hat S_i \hat C_j \ket{\hat C_j} = C_j \hat S_i \ket{\hat C_j} = 0 \\
-\end{aligned}\end{equation}
-This shows that each operator acts only on its own subspace. \(S_i\) does not act on the charge sector, and vice-versa. There is no single-particle excitation here.
-
-The physics of the side-peaks is that of single number fluctuations on the impurity. These are brought about by the term \(Vc^\dagger_{0\sigma}c_{d\sigma} + \text{h.c.}\).
-\begin{equation}\begin{aligned}
-	\left( \epsilon_d  \right) \ket{\sigma} & \mathrel{\mathlarger{\mathlarger{\mathop{\rightleftarrows}}^{V c^\dagger_{d\overline\sigma}/V c_{d\sigma}}_{V c_{d\overline\sigma}/V c^\dagger_{d\sigma}}}} &\ket{n_d=2,0} \left( 0 \right) \\
-\end{aligned}\end{equation}
-These transitions involve energy transfer of the order of \(\epsilon_d\).
-This is why, at very small \(U\), they remain absorbed inside the central peak.
-These transitions do not involve any spin or charge-flip, rather they take the impurity between the spin and charge sectors.
-
-\section{Effective Hamiltonian for excitations of the Kondo cloud}
-To find an effective Hamiltonian for the excitations of the Kondo cloud, we will integrate out the impurity part of the wavefunction. The Schrodinger equation for the \(J > K\) ground state is
-\begin{equation}\begin{aligned}
-	E_g &\left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right] \\
-	    &= \mathcal{H} \left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]\\
-	    &= \mathcal{H}_0^* \left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]\\
-	    &+V\sum_{\beta}\left[c^\dagger_{2\beta}c_{1\beta} - c_{2\beta}c^\dagger_{1\beta}\right]\left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]\\
-	    &+ J \vec{S_d}\cdot\vec{s}\left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]\\
-	    &+ K \vec{C_d}\cdot\vec{c}\left[c_-^s \left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right]
-\end{aligned}\end{equation}
-The last two lines gives
-\begin{equation}\begin{aligned}
-\frac{1}{2}Jc_-^s \left[s^z \left(\ket{\uparrow, \downarrow} + \ket{\downarrow, \uparrow}\right) +  s^+ \ket{\downarrow, \downarrow} - s^-\ket{\uparrow, \uparrow}\right] + \frac{1}{2}Kc^c_- \left[c^z\left(\ket{\uparrow\downarrow, 0} - \ket{0, \uparrow\downarrow}\right) + c^+\ket{0, 0} \right.\\
-+ \left.c^-\ket{2, 2}\right]
-\end{aligned}\end{equation}
-The second line gives
-\begin{equation}\begin{aligned}
-	V c^\dagger_{2\uparrow}\left[c_-^s \left(\ket{0, \downarrow}\right) + c^c_- \left(\ket{\downarrow, 0}\right)\right] + V c^\dagger_{2 \downarrow}\left[c_-^s \left(- \ket{0, \uparrow}\right) + c^c_- \left(\ket{\uparrow, 0}\right)\right] \\
-	- Vc_{2 \uparrow}\left[c_-^s \left(- \ket{ \uparrow\downarrow, \uparrow}\right) + c^c_- \left(\ket{\uparrow, \uparrow\downarrow}\right)\right] - V c_{2 \downarrow}\left[c_-^s \left(-\ket{ \uparrow\downarrow, \downarrow}\right) + c^c_- \left(\ket{ \downarrow, \uparrow\downarrow}\right)\right]
-\end{aligned}\end{equation}
-We will now write down four equations by comparing the coefficients of \(\ket{ \uparrow}, \ket{ \downarrow}, \ket{0}\) and \(\ket{2}\) of the impurity sector:
-\begin{equation}\begin{aligned}
-	\left( E_g - H_0^* \right) c_-^s \ket{\downarrow} &= V c^c_- \left( c^\dagger_{2 \downarrow}\ket{0} - c_{2 \uparrow}\ket{2} \right) + \frac{1}{2}J c^s_-\left( s^z\ket{ \downarrow} - s^-\ket{\uparrow} \right) && \left[\text{eq.
-from }\ket{\uparrow}\right] \\
-	\left( -E_g + H_0^* \right) c_-^s \ket{\uparrow} &= V c^c_- \left( c^\dagger_{2 \uparrow}\ket{0} - c^\dagger_{2 \downarrow}\ket{2} \right) + \frac{1}{2}J c^s_-\left( s^z\ket{\uparrow} + s^+\ket{ \downarrow} \right)&& \left[\text{eq.
-from }\ket{\downarrow}\right] \\
-	\left( E_g - H_0^* \right) c_-^c \ket{2} &= V c^s_- \left( c^\dagger_{2 \uparrow}\ket{ \downarrow} - c^\dagger_{2 \downarrow}\ket{ \uparrow} \right) + \frac{1}{2}K c^c_-\left( -c^z\ket{2} + c^+\ket{0} \right) && \left[\text{eq.
-from }\ket{0}\right] \\
-	\left( E_g - H_0^* \right) c_-^c \ket{0} &= V c^s_- \left( c_{2 \uparrow}\ket{ \uparrow} + c_{2 \downarrow}\ket{ \downarrow} \right) + \frac{1}{2}K c^c_-\left( c^z\ket{0} + c^-\ket{2} \right) && \left[\text{eq.
-from }\ket{2}\right]
-\end{aligned}\end{equation}
-These can be rearranged into
-\begin{equation}\begin{aligned}
-	\left( E_g - H_0^* - \frac{1}{2}J s^z\right) \ket{\downarrow} &= V \lambda^{-1} \left( c^\dagger_{2 \downarrow}\ket{0} - c_{2 \uparrow}\ket{2} \right) - \frac{1}{2}J s^-\ket{\uparrow} \\
-	\left( E_g - H_0^*  + \frac{1}{2}J s^z\right) \ket{\uparrow} &= V \lambda^{-1} \left( c_{2 \downarrow}\ket{2} - c^\dagger_{2 \uparrow}\ket{0}\right) - \frac{1}{2}J s^+\ket{ \downarrow} \\
-	\left( E_g - H_0^*  + \frac{1}{2}K c^z\right)  \ket{2} &= V \lambda \left( c^\dagger_{2 \uparrow}\ket{ \downarrow} - c^\dagger_{2 \downarrow}\ket{ \uparrow} \right) + \frac{1}{2}K c^+\ket{0}  \\
-	\left( E_g - H_0^* - \frac{1}{2}K c^z\right)  \ket{0} &= V \lambda \left( c_{2 \uparrow}\ket{ \uparrow} + c_{2 \downarrow}\ket{ \downarrow} \right) + \frac{1}{2}K c^-\ket{2} 
-\end{aligned}\end{equation}
-where \(\lambda = \frac{c^s_-}{c^c_-}\). We want to find the effective Hamiltonian in the subspace of \(\ket{\downarrow}\). We first eliminate the charge sector from these equations:
-\begin{equation}\begin{aligned}
-	\ket{0} =& V\lambda\left[\frac{1}{A^K_-}c_{2 \uparrow} + \frac{K}{2}\frac{1}{A^K_-}c^- \frac{1}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left(\frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \uparrow}- c^\dagger_{2 \downarrow}\right)\right]\ket{ \uparrow} \\
-		 &+V\lambda\left[\frac{1}{A^K_-}c_{2 \downarrow} + \frac{K}{2}\frac{1}{A^K_-}c^- \frac{1}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left(c^\dagger_{2 \uparrow} + \frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \downarrow}\right)\right]\ket{ \downarrow}\\
-	\ket{2} &= \frac{V\lambda}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left[\left(c^\dagger_{2 \uparrow} + \frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \downarrow}\right)\ket{ \downarrow} + \left(\frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \uparrow}- c^\dagger_{2 \downarrow}\right)\ket{ \uparrow}\right]
-\end{aligned}\end{equation}
-where
-\begin{equation}\begin{aligned}
-	A^K_\pm = E_g - H_0^* \pm \frac{1}{2}Kc^z
-\end{aligned}\end{equation}
-For ease of labeling, we will think of these equations as
-\begin{equation}\begin{aligned}
-	\ket{0} = a_0^\uparrow \ket{ \uparrow} + a_0^\downarrow\ket{ \downarrow}, \ket{2} = a_2^\uparrow \ket{ \uparrow} + a_2^\downarrow\ket{ \downarrow}
-\end{aligned}\end{equation}
-The remaining two equations can then be written as
-\begin{equation}\begin{aligned}
-	A^J_-\ket{ \downarrow} &= \frac{V}{\lambda}\left[ c^\dagger_{2 \downarrow}\left(a_0^\uparrow \ket{ \uparrow} + a_0^\downarrow\ket{ \downarrow}\right) - c_{2 \uparrow}\left(a_2^\uparrow \ket{ \uparrow} + a_2^\downarrow\ket{ \downarrow}\right) \right] - \frac{J}{2}s^- \ket{ \uparrow}\\
-	A^J_+\ket{\uparrow} &= \frac{V}{\lambda}\left[ c_{2 \downarrow}\left(a_2^\uparrow \ket{ \uparrow} + a_2^\downarrow\ket{ \downarrow}\right) - c^\dagger_{2 \uparrow}\left(a_0^\uparrow \ket{ \uparrow} + a_0^\downarrow\ket{ \downarrow}\right) \right]  - \frac{J}{2}s^+ \ket{ \downarrow}\\
-\end{aligned}\end{equation}
-where 
-\begin{equation}\begin{aligned}
-	A^J_\pm = E_g - H_0^* \pm \frac{1}{2}Js^z
-\end{aligned}\end{equation}
-Eliminating \(\ket{\downarrow}\) and solving for \(\ket{\uparrow}\) gives
-\begin{equation}\begin{aligned}
-	A^J_+ \ket{\uparrow} =&  \frac{V}{\lambda}\left( c_{2 \downarrow}a_2^\uparrow - c^\dagger_{2 \uparrow}a_0^\uparrow \right) \ket{\uparrow} + \left( \frac{V}{\lambda}c_{2 \downarrow}a_2^\downarrow - \frac{V}{\lambda}c^\dagger_{2 \uparrow}a_0^\downarrow - \frac{J}{2}s^+ \right) \ket{\downarrow}\\
-			     =& \frac{V}{\lambda}\left( c_{2 \downarrow}a_2^\uparrow - c^\dagger_{2 \uparrow}a_0^\uparrow \right) \ket{\uparrow} \\
-			     +& \left[ \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow\right) - \frac{J}{2}s^+ \right] \frac{1}{A^J_- - \frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\downarrow - c_{2 \uparrow}a_2^\downarrow \right) }\left[\frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow\right) - \frac{J}{2}s^-\right] \ket{\uparrow}
-\end{aligned}\end{equation}
-The effective Hamiltonian for the \(\ket{\uparrow}\) state is
-\begin{equation}\begin{aligned}
-	\label{full_ham}
-	H_0^* - \frac{J}{2}s^z + \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\uparrow - c^\dagger_{2 \uparrow}a_0^\uparrow \right) + \left[ \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow\right) - \frac{J}{2}s^+ \right] \frac{1}{A^J_- - \frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\downarrow - c_{2 \uparrow}a_2^\downarrow \right) }\\
-	\times\left[\frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow\right) - \frac{J}{2}s^-\right]
-\end{aligned}\end{equation}
-To get a clearer picture of this effective Hamiltonian, we will keep up to two-particle interactions. We first write down the full forms of \(a_{0,2}^\sigma\):
-\begin{equation}\begin{aligned}
-	a_0^\sigma &= V\lambda\left[\frac{1}{A^K_-}c_{2 \sigma} + \frac{K}{2}\frac{1}{A^K_-}c^- \frac{1}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left(\frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \sigma}- \sigma c^\dagger_{2 \sigma}\right)\right]\\
-	a_2^\sigma &= \frac{V\lambda}{A^K_+ - \left( \frac{K}{2} \right) ^2 c^+ \frac{1}{A^K_-}c^-}\left(-\sigma c^\dagger_{2 -\sigma} + \frac{K}{2}c^+ \frac{1}{A^K_-}c_{2 \sigma}\right)
-\end{aligned}\end{equation}
-We will first look at the special case of \(K = 0\). There, the above expressions simplify to
-\begin{equation}\begin{aligned}
-	a_0^\sigma &= V\lambda\frac{1}{A^K_-}c_{2 \sigma} = \frac{V \lambda}{E_g}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c_{2\sigma} + \mathcal{O}({H_0^*}^3)\\
-	a_2^\sigma &= -\sigma V\lambda\frac{1}{A^K_+}c^\dagger_{2 -\sigma} = -\sigma\frac{V \lambda}{E_g}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c^\dagger_{2 -\sigma} + \mathcal{O}({H_0^*}^3)\\
-\end{aligned}\end{equation}
-We will make use of the following commutators:
-\begin{equation}\begin{aligned}
-	&\left[\left(H_0^*\right)^m, c_{2\sigma}\right] = - \sum_k \frac{\epsilon^m_k}{\sqrt{N^*}}c_{k\sigma}, && \left[\left(H_0^*\right)^m, c^\dagger_{2\sigma}\right] = \sum_k \frac{\epsilon_k^m}{\sqrt{N^*}}c^\dagger_{k\sigma}, && m = 1, 2\\
-	&\left[\left(H_0^*\right)^m, s^+\right] = \sum_{kk^\prime}\left(\epsilon_k^m - \epsilon_{k^\prime}^m\right)c^\dagger_{k\beta}c_{k^\prime \overline \beta} , &&&& m = 1, 2\\
-	&\left[\left(s^z\right)^m, c_{2\sigma}\right] = - \left(\frac{\sigma}{2}\right)^mc_{2\sigma}, && \left[\left(s^z\right)^m, c^\dagger_{2\sigma}\right] = \left(\frac{\sigma}{2}\right)^mc^\dagger_{2\sigma}, && m = 1, 2\\
-	&\left[\left(c^z\right)^m, c_{2\sigma}\right] = - \left(\frac{1}{2}\right)^mc_{2\sigma}, && \left[\left(c^z\right)^m, c^\dagger_{2\sigma}\right] = \left(\frac{1}{2}\right)^mc^\dagger_{2\sigma}, && m = 1, 2\\
-\end{aligned}\end{equation}
-Now we evaluate the various terms in the effective Hamiltonian.
-\begin{flalign*}
-	{{c_{2 \downarrow}a_2^\uparrow}} &= -\frac{V \lambda}{E_g}c_{2 \downarrow}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c^\dagger_{2\downarrow}\\
-				     &= -\frac{V \lambda}{E_g}\left[c_{2 \downarrow} + \frac{1}{E_g}\left(H_0^* \right)c_{2 \downarrow} + \sum_k \frac{\epsilon_k}{E_g\sqrt{N^*}}c_{k\downarrow} + \frac{1}{E_g^2}\left(H_0^* \right)^2c_{2 \downarrow} + \sum_k \frac{\epsilon^2_k}{E_g^2\sqrt{N^*}}c_{k\downarrow}\right]c^\dagger_{2\downarrow}\\
-				     &= -\frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]c_{2 \downarrow}c^\dagger_{2\downarrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\\
-{{c_{2 \uparrow}a_2^\downarrow }}&= -\frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]c_{2 \uparrow}c^\dagger_{2\uparrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right) c_{k\uparrow}c^\dagger_{k^\prime\uparrow}\\
-{{c^\dagger_{2 \uparrow}a_0^\uparrow}} &= c^\dagger_{2 \uparrow} \frac{V \lambda}{E_g}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c_{2 \uparrow}\\
-					   &= \frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]c^\dagger_{2 \uparrow}c_{2\uparrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c^\dagger_{k\uparrow}c_{k^\prime\uparrow}\\
-{{c^\dagger_{2 \downarrow}a_0^\downarrow}} &= \frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]c^\dagger_{2 \downarrow}c_{2\downarrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\\
-{{c_{2 \downarrow}a_2^\downarrow }}&= \frac{V \lambda}{E_g}c_{2 \downarrow}\left[ 1 + \frac{1}{E_g}\left(H_0^* \right) + \frac{1}{E_g^2}\left(H_0^* \right)^2\right] c^\dagger_{2\uparrow}\\
-				       &=\frac{V \lambda}{E_g}\left[1 + \frac{1}{E_g}\left(H_0^* \right)\right]c_{2 \downarrow}c^\dagger_{2\uparrow} + \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c_{k\downarrow}c^\dagger_{k^\prime\uparrow}\\
-{{c_{2 \uparrow}a_2^\uparrow}} &=-\frac{V \lambda}{E_g}\left[1 + \frac{1}{E_g}\left(H_0^* \right)\right]c_{2 \uparrow}c^\dagger_{2\downarrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c_{k\uparrow}c^\dagger_{k^\prime\downarrow}\\
-{{c^\dagger_{2 \uparrow}a_0^\downarrow }}&= \frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g}\right]c^\dagger_{2 \uparrow}c_{2\downarrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c^\dagger_{k\uparrow}c_{k^\prime\downarrow}\\
-{{c^\dagger_{2 \downarrow}a_0^\uparrow}} &= \frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g}\right]c^\dagger_{2 \downarrow}c_{2\uparrow} - \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)c^\dagger_{k\downarrow}c_{k^\prime\uparrow}\\
-{{c_{2 \downarrow}a_2^\uparrow - c^\dagger_{2 \uparrow}a_0^\uparrow}} &= -\frac{V \lambda}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right]\times 2 + \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)\left(c^\dagger_{k\uparrow}c_{k^\prime\uparrow} - c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\right)\\
-{{c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow }}&= \frac{V \lambda}{E_g}\left[1 + \frac{1}{E_g}\left(H_0^* \right)\right]c_{2 \downarrow}c^\dagger_{2\uparrow} \times 2 + \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)\left(c_{k\downarrow}c^\dagger_{k^\prime\uparrow} + c^\dagger_{k\uparrow}c_{k^\prime\downarrow}\right)\\
-{{c^\dagger_{2 \downarrow}a_0^\downarrow - c_{2 \uparrow}a_2^\downarrow}} &= \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)\left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right)\\
-	{{c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow}} &= \frac{V \lambda}{E_g N^*}\sum_{kk^\prime} \left(\frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\right)\left(c_{k\uparrow}c^\dagger_{k^\prime\downarrow} - c^\dagger_{k\downarrow}c_{k^\prime\uparrow}\right)
-\end{flalign*}
-In all the expressions, we have dropped terms that have more than 4 operators in product.
-Also, in the last four equations, we have substituted \(\hat n_{2 \uparrow} - \hat n_{2 \downarrow} = 1\), because this is the effective Hamiltonian for the state with \(s^z = \frac{1}{2}\).
-We now substitute these expressions into the effective Hamiltonian:
-\begin{equation}\begin{aligned}
-	&H_0^* - \frac{J}{2}s^z -\frac{2V^2}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right] + \frac{V^2 }{E_g N^*}\sum_{kk^\prime} \xi_k \left(c^\dagger_{k\uparrow}c_{k^\prime\uparrow} - c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\right) \\
-	&+ \left[ \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow\right)\right] \frac{1}{A^J_- - \frac{V^2}{E_g N^*}\sum_{kk^\prime} \xi_k \left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right) }\left[\frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow\right)\right]\\
-	&+ \left[ \frac{V}{\lambda}\left(c_{2 \downarrow}a_2^\downarrow - c^\dagger_{2 \uparrow}a_0^\downarrow\right) \right] \frac{1}{A^J_- - \frac{V^2}{E_g N^*}\sum_{kk^\prime} \xi_k \left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right) }\left[ - \frac{J}{2}s^-\right]\\
-	&+ \left[- \frac{J}{2}s^+ \right] \frac{1}{A^J_- - \frac{V^2}{E_g N^*}\sum_{kk^\prime} \xi_k \left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right) }\left[\frac{V}{\lambda}\left( c^\dagger_{2 \downarrow}a_0^\uparrow - c_{2 \uparrow}a_2^\uparrow\right)\right]\\
-	&+ \frac{J^2}{4}\left[s^+ \right] \frac{1}{A^J_- - \frac{V^2}{E_g N^*}\sum_{kk^\prime} \xi_k \left(c_{k\uparrow}c^\dagger_{k^\prime\uparrow} - c^\dagger_{k\downarrow}c_{k^\prime\downarrow}\right) }\left[s^-\right]\\
-\end{aligned}\end{equation}
-where \(\xi_k = \frac{\epsilon_k }{E_g}+ \frac{\epsilon_k^2}{E_g^2}\). We first consider only zeroth order terms of the central propagator.
-\begin{equation}\begin{aligned}
-	&H_0^* - \frac{J}{2}\underbrace{s^z}_{\frac{1}{2}} -\frac{2V^2}{E_g}\left[1 + \frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right] + \frac{V^2 }{E_g N^*}\sum_{kk^\prime} \left(\xi_k \right)\left(c^\dagger_{k\uparrow}c_{k^\prime\uparrow} - c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\right) \\
-	&+ \frac{V^4}{E^2_g {N^*}^2 \left( E_g + \frac{J}{4} \right) }\sum_{kk^\prime}\left(\xi_{k^\prime} + 2 - \xi_k \right)c^\dagger_{k\uparrow}c_{k^\prime\downarrow}\sum_{kk^\prime} \left(\xi_k + \xi_{k^\prime}\right)c^\dagger_{k\downarrow}c_{k^\prime\uparrow}\\
-	&+ \frac{V^2 J}{2E_g \left( E_g + \frac{J}{4} \right){N^*}}\sum_{kk^\prime}\left(\xi_{k^\prime} + 2 - \xi_k \right)c^\dagger_{k\uparrow}c_{k^\prime\downarrow}\sum_{kk^\prime}c^\dagger_{k \downarrow}c_{k^\prime \uparrow}\\
-	&+ \frac{JV^2}{2E_g \left( E_g + \frac{J}{4} \right)N^*} \sum_{kk^\prime}c^\dagger_{k \uparrow}c_{k^\prime \downarrow}\sum_{kk^\prime} \left(\xi_k + \xi_{k^\prime}\right)c^\dagger_{k\downarrow}c_{k^\prime\uparrow}\\
-	&+ \frac{J^2}{4\left( E_g + \frac{J}{4} \right)}\underbrace{s^+ s^-}_{s^z + \frac{1}{2}= 1}
-\end{aligned}\end{equation}
-We have set \(s^z = -\frac{1}{2}\) in the denominator, hence the \(E_g = \frac{J}{4}\).
-If we also consider the first and second order terms from the central propagator, note that they will produce terms of more than quartic interactions in the first three terms.
-For the last term, we get
-\begin{equation}\begin{aligned}
-	\frac{J^2}{4\left( E_g + \frac{J}{4} \right)}s^+\left[\frac{H_0^*}{E_g + \frac{J}{4}} + \left(\frac{H_0^*}{E_g + \frac{J}{4}}\right)^2\right]s^-
-\end{aligned}\end{equation}
-Using the commutator of \(H_0^*\) with \(s^+\) to bring \(H_0^*\) to the left, and using \(s^+ s^- = s^z + \frac{1}{2} = 1\), we get
-\begin{equation}\begin{aligned}
-	\frac{J^2}{4\left( E_g + \frac{J}{4} \right)}\left[\frac{H_0^*}{E_g + \frac{J}{4}} + \left(\frac{H_0^*}{E_g + \frac{J}{4}}\right)^2 - \sum_{kk^\prime qq^\prime} \left( \xi_k^J - \xi_{k^\prime}^J \right)  c^\dagger_{k \uparrow}c_{k^\prime \downarrow}c^\dagger_{q \downarrow}c_{q^\prime \uparrow}\right]
-\end{aligned}\end{equation}
-where \(\xi_k^J = \frac{\epsilon_k }{E_g + \frac{J}{4}}+ \frac{\epsilon_k^2}{\left(E_g + \frac{J}{4}\right)^2}\). The full effective Hamiltonian, for \(K=0\), up to quartic interactions, is
-\begin{equation}\begin{aligned}
-	H_0^* + \frac{J}{4}\left(\frac{J}{E_g + \frac{J}{4}} - 1\right) - \frac{2V^2}{E_g} + \frac{V^2 }{E_g N^*}\sum_{kk^\prime} \left(\xi_k \right)\left(c^\dagger_{k\uparrow}c_{k^\prime\uparrow} - c_{k\downarrow}c^\dagger_{k^\prime\downarrow}\right) - \frac{2V^2}{E_g}\left[\frac{H_0^*}{E_g} + \left(\frac{H_0^*}{E_g}\right)^2\right] \\
-	+ \frac{J^2}{4\left( E_g + \frac{J}{4} \right) }\left[\frac{H_0^*}{E_g + \frac{J}{4}} + \left(  \frac{H_0^*}{E_g + \frac{J}{4}}\right)^2 \right] + \sum_{kk^\prime q q^\prime} F_{kk^\prime qq^\prime}c^\dagger_{k \uparrow}c_{k^\prime \downarrow}c^\dagger_{q \downarrow}c_{q^\prime \uparrow}
-\end{aligned}\end{equation}
-The coefficient \(F_{kk^\prime qq^\prime}\) is
-\begin{equation}\begin{aligned}
-	\label{off_diag_coeff}
-	F_{kk^\prime qq^\prime} = \frac{V^2}{E_g N^* (E_g + \frac{J}{4})}\left[\frac{V^2}{E_g N^*}\left( \xi_{k^\prime} + 2 - \xi_k \right)\left( \xi_q + \xi_{q^\prime} \right) + \frac{J}{2}\left( \xi_{k^\prime} + 2 - \xi_k + \xi_q + \xi_{q^\prime} \right)  \right] \\
-+ \frac{J^2}{4\left( E_g + \frac{J}{4} \right)} \left(\xi_{k^\prime}^J - \xi_{k}^J\right)
-\end{aligned}\end{equation}
-There are two main types of interactions that gets generated upon integrating out the impurity.
-One is the Fermi liquid type interactions arising from the \({H_0^*}^2\) terms.
-The Fermi liquid part of the Hamiltonian is
-\begin{equation}\begin{aligned}
-	\left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right)^2} - \frac{2V^2}{E_g^2}\right] H_0^* + \left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right)^2} - \frac{2V^2}{E_g^3}\right] {H_0^*}^2 \\
-	= \left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right)^2} - \frac{2V^2}{E_g^2}\right] \left[ H_0^* + \sum_{kk^\prime \sigma \sigma^\prime} f_{kk^\prime} \hat n_{k\sigma} \hat n_{k^\prime \sigma^\prime}\right]
-\end{aligned}\end{equation}
-where the Landau parameter is given by
-\begin{equation}\begin{aligned}
-	\label{fermiliq}
-	f_{kk^\prime} = \left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right)^2} - \frac{2V^2}{E_g^2}\right]^{-1}\left[\frac{J^2}{4\left( E_g + \frac{J}{4} \right) ^3} - \frac{2V^2}{E_g^3}\right]\epsilon_k \epsilon_{k^\prime}
-\end{aligned}\end{equation}
-The more interesting interaction is the off-diagonal term
-\begin{equation}\begin{aligned}
-	 \sum_{kk^\prime q q^\prime} F_{kk^\prime qq^\prime}c^\dagger_{k \uparrow}c_{k^\prime \downarrow}c^\dagger_{q \downarrow}c_{q^\prime \uparrow}
-\end{aligned}\end{equation}
-This interaction arises from the enhanced entanglement between the impurity and the conduction electrons; removing the impurity from the singlet and the triplet generates these off-diagonal scatterings.
-As such, this is an indicator of the macroscopic entanglement of the singlet formed at the IR fixed point, and plotted in fig.~\ref{mutI}.
-
-We also wish to point out that this scattering is a signature of the change in Luttinger's count in going from the free orbital or local moment fixed point to the strong coupling fixed point, as shown in eq.~\eqref{luttinger_change}.
-Both this off-diagonal scattering as well as the change in Luttinger's count are a direct consequence of the non-number conserving term \(V c^\dagger_{k} c_d\) in the full Hamiltonian.
-The topological change of Luttinger's count is concomitant with the presence of the off-diagonal scattering term in the effective Hamiltonian.
-\textit{Just the Fermi liquid piece in eq.~\eqref{fermiliq} will give neither the enhanced mutual information nor the change in Luttinger's count}.
-
-\section{Obtaining the real space low energy Hamiltonian: the local Fermi liquid}
-The next step is to obtain the lowest excitations of the fixed point Hamiltonian, in real space.
-We will work in the \(U>0\) regime.
-For \(V,J \gg 1\), the impurity couples very strongly with the zeroth site, and at zeroth order, it suffices to say that the zeroth site decouples from the rest of the lattice.
-This zeroth Hamiltonian then consists of two sites interacting with each other through \(V\) and \(J\) (the two site problem analysed before).
-\begin{gather}
-	H^*_0 = \sum_{\sigma}\left( V^* c^\dagger_{0\sigma}c_{d\sigma} + \text{h.c.} \right) + J^* \vec{S_d}\cdot\vec{s} - \frac{1}{2}U^*\left( \hat n_{d \uparrow} - \hat n_{d \downarrow}\right)^2 \\
-	\ket{\Psi}_1 = {c_s} \frac{1}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) + {c_c} \frac{1}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right), \quad E_1 =  -V^*\sqrt{\gamma^2 + 4} -\frac{1}{4}U^* - \frac{3}{8}{J^*}
-\end{gather}
-These were obtained in eq.~\eqref{gstate}. The quantities \(\gamma\) and \(c_{s,c}\) were defined in and around eq.~\eqref{coeff_def}.
-
-We start with the ground state \(\ket{\Psi}_1\) and the star graph as the zeroth level ground state and Hamiltonian, and then add a nearest-neighbour hopping term as a perturbation of the zeroth Hamiltonian.
-We know that the ground state for the interacting part is predominantly the spin-singlet (it was shown while calculating the ground states of the effective zero-mode Hamiltonian that the ground state is a mixture of singlet and triplet, and the triplet part dies out at large system sizes, see eq.~\eqref{gstate_kondo}), so we will take that as our reference state and treat the hopping part that connects the origin to the first site,
-\begin{equation}\begin{aligned}
-	H_X = t\sum_{\vec r_1,\sigma} c^\dagger_{0\sigma}c_{\vec r_1,\sigma} +\text{h.c.} \equiv v^\dagger + v
-\end{aligned}\end{equation}
-as a weak perturbation.
-\(\vec r_1\) here sums over the sites that are nearest to the origin.
-Once this perturbation is taken care of up to a certain order, we will have a decoupled singlet formed by the impurity and the zeroth site, and the rest of the lattice formed by \(N-1\) sites along with the interaction induced by the perturbation.
-To be precise, the goal is to integrate out the perturbation and generate an effective Hamiltonian in the subspace of the minimal energy states of the two site Hamiltonian, and this effective Hamiltonian will therefore describe the lowest excitations on top of the ground state \(\ket{\Psi}_1\).
-The minimal energy subspace is given by the states:
-\begin{equation}\begin{aligned}
-	\ket{\Phi}_{i} = \ket{\Psi}_1 \otimes \ket{\hat n_{1 \uparrow}, \hat n_{1 \downarrow}}, ~\text{ where }i \in \begin{cases}
-		0: & \hat n_{1 \uparrow} = \hat n_{1 \downarrow} = 0\\
-		1: & 1 - \hat n_{1 \uparrow} =  \hat n_{1 \downarrow} = 0\\
-		2: & \hat n_{1 \uparrow} = 1 - \hat n_{1 \downarrow} = 0\\
-		3: & 1 - \hat n_{1 \uparrow} =  1 - \hat n_{1 \downarrow} = 0
-	\end{cases} 
-\end{aligned}\end{equation}
-
-The effective Hamiltonian will be calculated using perturbation theory in \(\frac{H_X^{n}}{{H_0^*}^{n-1}}\).
-Since an odd number of scattering processes cannot bring the initial state back to itself, such orders will be absent from the effective Hamiltonian.
-
- \subsection{Second order effective Hamiltonian}
- We first consider the case of \(n=2\). The renormalisation of the effective Hamiltonian in the ground state subspace, at this order, is given by
-\begin{equation}\begin{aligned}
-	\Delta H = \sum_{ij,n}\ket{\Phi}_i \bra{\Phi_i}H_X \ket{\Psi}_n \frac{1}{E_\text{gs} - E_n} \bra{\Psi}_n H_X \ket{\Phi}_j \bra{\Phi_j} = \sum_{ij}\ket{\Phi}_i \bra{\Phi_j} \bra{\Phi_i}v + v^\dagger \ket{\Psi}_n \frac{1}{E_\text{gs} - E_n} \bra{\Psi}_n v + v^\dagger \ket{\Phi}_j~.
-\end{aligned}\end{equation}
-Here, \(\ket{\Psi}_n\) are the eigenstates of the two site problem, with eigenvalue \(E_n\).
-The total scattering process can be described as \(H_X\) acting on \(\ket{\Phi}_j\) to excite to \(\ket{\Psi}_n\), and then a subsequent \(H_X\) acting on \(\ket{\Psi}_n\) to decay back to \(\ket{\Phi}_j\) and into the ground state manifold.
-Since \(\ket{\Phi}_{i,j}\) are eigenstates of the two site Hamiltonian, they are all eigenstates of the total number operator \(\hat n_{d0} = \sum_\sigma \left(\hat n_{d\sigma} + \hat n_{0\sigma}\right) \) for the two site model, with eigenvalue \(2\).
-Since we are to finally return to the ground state manifold, only those processes in \(H_X^2\) are allowed that conserve \(\hat n_{d0}\).
-These processes are \(v, v^\dagger\) and \(v^\dagger,v\).
-This also means that the total number of particles on site 1 will remain constant in the process, and we wil have \(\ket{\Phi}_i = \ket{\Phi}_j\).
-\begin{equation}\begin{aligned}
-	\Delta H = \sum_{i}\ket{\Phi}_i \bra{\Phi_i} \frac{1}{E_\text{gs} - E_n} \left(\bra{\Phi_i}v^\dagger \ket{\Psi}_n \bra{\Psi}_n v \ket{\Phi}_i + \bra{\Phi_i} v \ket{\Psi}_n \bra{\Psi}_n v^\dagger \ket{\Phi}_i\right) ~.
-\end{aligned}\end{equation}
-If we define the matrix element \(v_{ni} \equiv \bra{\Psi}_n v \ket{\Phi}_i\) of \(v\) and the excitation energy \(\delta E_{n} = E_n - E_\text{gs}\), we can write the renormalisation as
-\begin{equation}\begin{aligned}
-	\Delta H = \sum_{i,n}\frac{|v_{ni}|^2 + |v_{in}|^2}{-\delta E_{n}} \ket{\Phi}_i \bra{\Phi_i}~.
-\end{aligned}\end{equation}
-
-We now look at each \(\ket{\Phi_i}\) separately. For \(\ket{\Phi_i} = \ket{\Phi}_0 = \ket{\Psi}_1 \otimes \ket{0,0}\), we can write
-\begin{equation}\begin{aligned}
-	v^\dagger \ket{\Phi}_i = 0, ~ v \ket{\Phi}_i = \frac{t}{\sqrt 2}\sum_\sigma \overline\sigma\left({c_s^-} \ket{\sigma, 0} + {c_c^-} \ket{0, \sigma}\right) \ket{\overline\sigma}
-\end{aligned}\end{equation}
-The first relation gives \(v_{in} = \bra{\Phi}_i v \ket{\Psi}_n = \left(\bra{\Psi}_n v^\dagger \ket{\Phi}_i\right)^* = 0\).
-The set of states that give non-zero \(v^\dagger_{in}\) are specific elements of the set of eigenstates that have a total of either 1 or 3 electrons on the impurity and zeroth sites:
-\begin{equation}\begin{aligned}
-	\ket{\Psi}_n = \ket{\Psi}_{\pm,\sigma}^{s, p} = -\sqrt 2\left(a_{1,\pm}\ket{\sigma,p} + a_{2,\pm} \ket{p,\sigma}\right)\otimes\ket{s},~~ \sigma = \uparrow,\downarrow, ~~ E^{s,p}_{\pm, \sigma} = -\frac{U}{4} \pm \frac{1}{2}\Delta~;
-\end{aligned}\end{equation}
-here, \(s\) is a string from the set \(\left\{0, \uparrow, \downarrow, 2\right\} \) and represents the configuration of the first site \(\ket{s}\) in direct product with the impurity and zeroth site entangled composite state, and \(p\) is either \(2\) or 0 such that \(p+1 (= 1\text{ or }3)\) represents the total number of electrons on the impurity and zeroth sites.
-For \(\ket{\Phi}_0\), only \(s=\overline\sigma\) and \(p=0\) give non-zero inner product.
-The coefficients are defined as \(a_{1,\pm}=\frac{4V}{\sqrt 2 \mathcal{N}_\pm}, a_{2,\pm}=\frac{U \pm 2\Delta}{\sqrt 2 \mathcal{N}_\pm}\).
-The inner product is
-\begin{equation}\begin{aligned}
-	\label{vni}
-	v_{\pm\sigma,i} = \braket{\Psi_{\pm,\sigma}^{\overline\sigma,0} | v | \Phi_i} = \sigma t \left[a_{1,\pm}{c_s^-} + a_{2,\pm} {c_c^-}\right]
-\end{aligned}\end{equation}
-\(\mathcal{N}_\pm = \sqrt{16V^2 + \left(U \pm 2\Delta\right)^2}\) is the normalisation factor and \(\Delta = \frac{1}{2}\sqrt{U^2 + 16V^2}\). The renormalisation for this value of \(i\) then becomes
-\begin{equation}\begin{aligned}
-	\label{eff_ham_0}
-	\left(\Delta H\right)_{i=0} = \ket{\Phi}_0 \bra{\Phi}_0 \sum_{n}\frac{|v_{ni}|^2}{-\delta E_{n}} = \ket{\Phi}_0 \bra{\Phi}_0 \sum_{\sigma,\pm}\frac{|v_{\pm\sigma,i}|^2}{-\delta E_{\pm}^\sigma} = -\ket{\Phi}_0 \bra{\Phi}_0 2t^2\sum_{\pm}\frac{\left[a_{1,\pm}{c_s^-} + a_{2,\pm} {c_c^-}\right]^2}{\delta E_{\pm}^\sigma}
-\end{aligned}\end{equation}
-where \(\delta E_{\pm}^\sigma = E^\sigma_{\pm} - E_\text{gs}\).
-
-For \(i=1\), we have \(\ket{\Phi}_1 = \ket{\Psi}_1 \otimes \ket{\uparrow}\). Carrying out a similar calculation above, we get
-\begin{gather}
-	v\ket{\Phi}_1 = t \frac{1}{\sqrt 2}\left({c_s^-}\ket{\uparrow, 0, 2} + {c_c^-}\ket{0, \uparrow, 2}\right), ~ ~ ~\ket{\psi}_n = \ket{\Psi}^{2,0}_{\pm,\uparrow}, ~ ~ ~ v_{ni} = -t\left({c_s^-} a_{1,\pm} + {c_c^-} a_{2,\pm}\right) \label{vvdag_i1}\\
-	v^\dagger\ket{\Phi}_1 = t \frac{1}{\sqrt 2}\left({c_s^-}\ket{\uparrow, 2, 0} - {c_c^-}\ket{2, \uparrow, 0}\right), ~ ~ ~\ket{\psi}_n = \ket{\Psi}^{0,2}_{\pm,\uparrow}, ~ ~ ~ v_{in} = -t\left({c_s^-} a_{1,\pm} - {c_c^-} a_{2,\pm}\right)\label{vvdag_i1_2}\\
-	\left(\Delta H\right)_{i=1} = -\ket{\Phi}_1 \bra{\Phi}_1 2t^2\sum_{\pm}\frac{a_{1,\pm}^2 {c_s^-}^2 + a_{2,\pm}^2 {c_c^-}^2}{\delta E_{\pm}^\sigma}
-\end{gather}
-
-The total Hamiltonian \(H_0^* + H_X\) is invariant under the transformations \(c^\dagger_\sigma \to c_\sigma, t \to -t\).
-Since the renormalisation only involves even powers of \(t\), we can conclude that the renormalisation for \(i=2\)  and \(i=3\) will be the same as that of \(i=1\) and \(i=0\) respectively.
-The total renormalisation at second order is
-\begin{equation}\begin{aligned}
-	\Delta H &= -\sum_{i=0}^3\ket{\Phi}_i \bra{\Phi}_i 2t^2\sum_{\pm}\frac{a_{1,\pm}^2 {c_s^-}^2 + a_{2,\pm}^2 {c_c^-}^2}{\delta E_{\pm}^\sigma} - \left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right)4t^2\sum_{\pm}\frac{a_{1,\pm} a_{2,\pm} {c_s^-} {c_c^-}}{\delta E_{\pm}^\sigma}\\
-		 &= -\sum_{i=0}^3\ket{\Phi}_i \bra{\Phi}_i t^2\sum_{\pm}\frac{1}{\mathcal{N}_\pm^2}\frac{\left(4V{c_s^-}\right)^2 + \left(U \pm 2\Delta\right)^2 {c_c^-}^2}{\delta E_{\pm}^\sigma} - \left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right)\sum_{\pm}\frac{t^2}{\mathcal{N}_\pm^2}\frac{8V {c_s^-} \left(U \pm 2\Delta\right) {c_c^-}}{\delta E_{\pm}^\sigma}
-\end{aligned}\end{equation}
-Since the \(\ket{\hat n_{1\sigma}, \hat n_{1\overline\sigma}}\) form a complete set, we have \(\sum_{i=0}^3\ket{\Phi}_i \bra{\Phi}_i = \ket{\Psi}_1 \bra{\Psi}_1\), and the first term becomes a constant.
-The second term is a local Fermi liquid term on the first site:
-\begin{equation}\begin{aligned}
-	\Delta H &= \ket{\Psi}_1 \bra{\Psi}_1\left[\mathrm{constant} - \left\{\hat n_{1 \uparrow}\hat n_{1 \downarrow} + \left(1 - \hat n_{1 \uparrow}\right) \left(1 - \hat n_{1 \downarrow}\right)\right\}\sum_{\pm}\frac{t^2}{\mathcal{N}_\pm^2}\frac{8V {c_s^-} \left(U \pm 2\Delta\right) {c_c^-}}{\delta E_{\pm}^\sigma}\right]\\
-		 &= \ket{\Psi}_1 \bra{\Psi}_1\left[\mathrm{constant} + \left(\hat n_{1 \uparrow} - \hat n_{1 \downarrow}\right)^2 \sum_{\pm}\frac{t^2}{\mathcal{N}_\pm^2}\frac{8V {c_s^-} \left(U \pm 2\Delta\right) {c_c^-}}{\delta E_{\pm}^\sigma}\right]\\
-\end{aligned}\end{equation}
-
-In the strong coupling regime, we have \(J,V \gg U\), and we can then approximate:
-\begin{equation}\begin{aligned}
-	\delta E_{\pm}^\sigma \simeq \frac{3J}{8} + \sqrt{4V^2 - \left(\frac{3J}{8}\right)^2} \mp V, ~~U \pm 2\Delta \simeq \pm 4V, \text{ and }~~ \mathcal{N}_\pm^2 \simeq 32V^2
-\end{aligned}\end{equation}
-Substituting this gives
-\begin{equation}\begin{aligned}
-	\Delta H = \ket{\Psi}_1 \bra{\Psi}_1\left[\mathrm{constant} - \left(\hat n_{1 \uparrow} - \hat n_{1 \downarrow}\right)^2 \frac{2t^2V {c_s^-} {c_c^-}}{2\left(\frac{3J}{8}\right)^2 + 3V^2 + \frac{3J}{4}\sqrt{4V^2 + \left(\frac{3J}{8}\right)^2}}\right]\\
-\end{aligned}\end{equation}
-
-\subsection{Fourth order effective Hamiltonian}
-Using fourth order perturbation theory, we can write the effective Hamiltonian renormalisation at that order in the form
-\begin{equation}\begin{aligned}
-	\label{eff_ham_4}
-	\Delta H &= -\sum_{i}\ket{\Phi}_i\bra{\Phi}_i\left[\sum_{lmn}\frac{\braket{\Phi_i | H_X | \Psi_l}\braket{\Psi_l | H_X | \Psi_m}\braket{\Psi_m | H_X | \Psi_n}\braket{\Psi_n | H_X | \Phi_i}}{\delta E_l ~ \delta E_m ~ \delta E_n} + \Delta^{(2)}H \sum_{n} \frac{|\braket{\Psi_n | H_X | \Phi_i}|^2}{\left(\delta E_n\right)^2}\right]~,\\
-		 &= -\sum_{i}\ket{\Phi}_i\bra{\Phi}_i\left[\sum_{m}\frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 + \Delta^{(2)}H \sum_{n} \frac{1}{\left(\delta E_n\right)^2}\big\Vert\left(H_X\right)_{ni}\big\Vert^2\right]~.
-\end{aligned}\end{equation}
-We can have at most two successive \(v^\dagger\) or two successive \(v\) act on a particular state.
-Any more would lead to \(c^\dagger_\sigma \ket{\hat n_\sigma =2} = 0\).
-This limits the possible scattering processes (in the first term) to the following channels:
-\begin{equation}\begin{aligned}
-	a.~v v^\dagger v v^\dagger,~~b.~v^\dagger v v^\dagger v,~~c.~v v v^\dagger v^\dagger,~~d.~v^\dagger v^\dagger v v~.
-\end{aligned}\end{equation}
-
-We start with \(i=0\).
-Out of the four channels \(a\) through \(d\), only \(b\) and \(d\) survive.
-For \(i=0\), we already know the relevant \(\ket{\Psi}_n\) and hence the \(\left(H_X\right)_{ni} = v_{ni}\), from eq.~\eqref{vni}.
-\begin{equation}\begin{aligned}
-	v_{\pm\sigma,i} = \braket{\Psi_{\pm,\sigma}^{\overline\sigma,0} | v | \Phi_i} = \sigma t \left[a_{1,\pm}{c_s^-} + a_{2,\pm} {c_c^-}\right] = \sigma t \mathcal{S}^-_\pm
-\end{aligned}\end{equation}
-where we have defined the sum and difference \(\mathcal{S}^\pm_\pm = a_{1,\pm}{c_s^\pm} + a_{2,\pm} {c_c^\pm}, ~ ~ \mathcal{D}^\pm_\pm = a_{1,\pm}{c_s^\pm} - a_{2,\pm} {c_c^\pm}\).
-For channel \(b\), we then proceed as follows:
-\begin{gather}
-	\ket{\Psi}_{\pm,\sigma}^{\overline\sigma, 0} = -\sqrt 2\left(a_{1,\pm}\ket{\sigma,0} + a_{2,\pm} \ket{0,\sigma}\right)\otimes\ket{\overline\sigma}\\
-	v^\dagger\ket{\Psi}_n = v^\dagger\ket{\Psi}^{\overline\sigma,0}_{\pm,\sigma} = \sqrt 2 t \left(a_{1,\pm}\ket{\sigma,\overline\sigma} + a_{2,\pm} \ket{0,\sigma\overline\sigma}\right)\otimes\ket{0}\\
-	\ket{\Psi}_m = \begin{cases}
-	\frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow})\right)\otimes\ket{0} \\
-	\frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2})\right)\otimes\ket{0}\\ 
-	\left[ \frac{c^+_s}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) +  \frac{c^+_c}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right] \otimes\ket{0}
-	\end{cases}
-	\implies \left(H_X\right)_{m,\pm\sigma} = \begin{cases}
-		t a_{1\pm}\\
-		\overline\sigma t a_{2\pm}\\
-		\sigma t \left(a_{1\pm} {c_s^+} + a_{2\pm}{c_c^+}\right) = \sigma t \mathcal{S}^+_\pm
-	\end{cases}\label{psi_m}\\
-	 \frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 = \begin{cases}
-	 \frac{1}{\delta E_\mathrm{ST}}\left(\sum_{\sigma,\pm}\frac{t^2}{\delta E_\pm}\sigma a_{1\pm}\mathcal{S}^-_\pm\right)^2 = 0\\
-	 \frac{1}{\delta E_\mathrm{CS}}\left(\sum_{\pm,\sigma} \frac{t^2}{\delta E_\pm}a_{2\pm}\mathcal{S}^-_\pm\right)^2 =  \frac{4t^4}{\delta E_\mathrm{CS}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{2\pm}\mathcal{S}^-_\pm\right)^2\\
-	 \frac{1}{\delta E_\mathrm{2}}\left(-\sum_{\pm,\sigma}\frac{t^2}{\delta E_\pm}\mathcal{S}^+_\pm\mathcal{S}^-_\pm\right)^2 = \frac{4t^4}{\delta E_\mathrm{2}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}\mathcal{S}^+_\pm\mathcal{S}^-_\pm\right)^2
-	\end{cases}
-\end{gather}
-\(E_\mathrm{ST}, E_\mathrm{CS}\) and \(E_2\) are the energies of the spin triplet zero, charge singlet and spin singlet+charge triplet excited states of the set \(\ket{\Psi}_m\) in eq.~\eqref{psi_m}.
-
-We now turn to channel \(d\):
-\begin{gather}
-	v\ket{\Psi}_n = v\ket{\Psi}^{\overline\sigma,0}_{\pm,\sigma} = \sqrt 2 t \sigma a_{2\pm} \ket{0,0}\otimes\ket{2},~ ~ ~\ket{\Psi}_m = \ket{0,0,2}, ~ ~ ~ \left(H_X\right)_{m,\pm\sigma} = \sqrt 2 t \sigma a_{2\pm}\\
-\frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 = \frac{8t^4}{\delta E_{00}} \left(\sum_\pm \frac{1}{\delta E_\pm}a_{2\pm}\mathcal{S}^-_\pm\right)^2
-\end{gather}
-\(E_{00}\) is the energy of the state \(\ket{0,0,2}\).
-
-Having accounted for both channels, we will calculate the second part of the effective Hamiltonian in eq.~\eqref{eff_ham_4}, the part involving \(\Delta^{(2)} H\).
-We already know, from eq.~\eqref{eff_ham_0}, that
-\begin{equation}\begin{aligned}
-	\Delta^{(2)} H_{i=0} = -2t^2\sum_\pm \frac{1}{\delta E_\pm}\left(\mathcal{S}^-_\pm\right)^2
-\end{aligned}\end{equation}
-Also, from the expression of \(v_{\pm\sigma,i}\), we get
-\begin{equation}\begin{aligned}
-	\sum_{n} \frac{1}{\left(\delta E_n\right)^2}\big\Vert\left(H_X\right)_{ni}\big\Vert^2 =	\sum_{\pm} \frac{2t^2}{\left(\delta E_\pm\right)^2}\left(\mathcal{S}^-_\pm\right)^2
-\end{aligned}\end{equation}
-Combining it all, the total renormalisation in \(i=0\) is
-\begin{equation}\begin{aligned}
-	- \ket{\Phi}_0 \bra{\Phi}_0 4t^4\left[ \left(\frac{1}{\delta E_\mathrm{CS}} + \frac{2}{\delta E_{00}}\right)  \left(\sum_{\pm}\frac{a_{2\pm}\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \frac{1}{\delta E_\mathrm{2}}\left(\sum_{\pm}\frac{\mathcal{S}^+_\pm\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 - \sum_\pm \frac{\left(\mathcal{S}^-_\pm\right)^2}{\delta E_\pm}\sum_{\pm} \left(\frac{\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2\right]\\
-\end{aligned}\end{equation}
-
-We now come to \(i=1\): \(\ket{\Phi}_1 = \ket{\Psi}_1 \otimes \ket{\uparrow}\).
-Channels \(a\) and \(b\) are non-zero here.
-We start with channel \(b: v^\dagger v v^\dagger v\).
-We already know, from eq.~\eqref{vvdag_i1}, that
-\begin{gather}
-v\ket{\Phi}_1 = t \frac{1}{\sqrt 2}\left({c_s^-}\ket{\uparrow, 0, 2} + {c_c^-}\ket{0, \uparrow, 2}\right), ~ ~ ~ \ket{\psi}_n = \ket{\Psi}^{2,0}_{\pm,\uparrow} = -\sqrt 2\left(a_{1,\pm}\ket{\uparrow,0} + a_{2,\pm} \ket{0,\uparrow}\right)\otimes\ket{2}, ~ ~ ~ \left(H_X\right)_{ni} = -t \mathcal{S}^-_\pm
-\end{gather}
-Moving forward:
-\begin{gather}
-v^\dagger \ket{\Psi}_n = \sqrt 2 t \left(a_{1,\pm}\ket{\uparrow,\uparrow}\otimes\ket{\downarrow} - a_{1,\pm}\ket{\uparrow,\downarrow}\otimes\ket{\uparrow} - a_{2,\pm} \ket{0,2}\otimes\ket{\uparrow}\right)\\
-	\ket{\Psi}_m = \begin{cases}
-	\frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow})\right)\otimes\ket{\uparrow} \\
-	\frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2})\right)\otimes\ket{\uparrow}\\ 
-	\left[ \frac{c^+_s}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) +  \frac{c^+_c}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right] \otimes\ket{\uparrow}\\
-	\ket{\uparrow,\uparrow}\otimes\ket{\downarrow}
-	\end{cases}
-	\implies \left(H_X\right)_{m,\pm}\left(H_X\right)_{\pm,i} = \begin{cases}
-		t^2 a_{1\pm} \mathcal{S}^-_\pm\\
-		-t^2 a_{2\pm}\mathcal{S}^-_\pm\\
-		t^2 \mathcal{S}^+_\pm\mathcal{S}^-_\pm\\
-		-\sqrt 2 t^2 a_{1\pm}\mathcal{S}^-_\pm
-	\end{cases}\\
-	\frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 = \begin{cases}
-	 \frac{t^4}{\delta E_\mathrm{ST}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{1\pm}\mathcal{S}^-_\pm\right)^2 \\
-	 \frac{t^4}{\delta E_\mathrm{CS}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{2\pm}\mathcal{S}^-_\pm\right)^2\\
-	 \frac{t^4}{\delta E_\mathrm{2}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}\mathcal{S}^+_\pm\mathcal{S}^-_\pm\right)^2\\
-	 \frac{2 t^4}{\delta E_\mathrm{\uparrow \uparrow}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{1\pm}\mathcal{S}^-_\pm\right)^2\\
-	\end{cases}
-\end{gather}
-\(E_{\uparrow \uparrow}\) is the energy of the upwards polarised state \(\ket{\uparrow,\uparrow}\otimes\ket{\downarrow}\).
-
-Next is channel \(a : v v^\dagger v v^\dagger\). Using eq.~\eqref{vvdag_i1_2} and following the same steps as above, we get:
-\begin{gather}
-	v^\dagger\ket{\Phi}_1 = t \frac{1}{\sqrt 2}\left({c_s^-}\ket{\uparrow, 2, 0} - {c_c^-}\ket{2, \uparrow, 0}\right), ~ ~ ~\ket{\Psi}_n = \ket{\Psi}^{0,2}_{\pm,\uparrow} = -\sqrt 2\left(a_{1,\pm}\ket{\uparrow,2} + a_{2,\pm} \ket{2,\uparrow}\right)\otimes\ket{0}, ~ ~ ~ \left(H_X\right)_{ni} = -t \mathcal{D}^-_\pm\\
-	v \ket{\Psi}_n = \sqrt 2 t\left(a_{1,\pm}\ket{\uparrow,\uparrow}\otimes\ket{\downarrow} - a_{1,\pm}\ket{\uparrow,\downarrow}\otimes\ket{\uparrow} + a_{2,\pm} \ket{2,0}\otimes\ket{\uparrow}\right)\\
-		\ket{\Psi}_m = \begin{cases}
-		\frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow})\right)\otimes\ket{\uparrow} \\
-		\frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2})\right)\otimes\ket{\uparrow}\\ 
-		\left[ \frac{c^+_s}{\sqrt 2}\left(\ket{\uparrow, \downarrow} - \ket{\downarrow, \uparrow}\right) +  \frac{c^+_c}{\sqrt 2}\left(\ket{\uparrow\downarrow, 0} + \ket{0, \uparrow\downarrow}\right)\right] \otimes\ket{\uparrow}\\
-		\ket{\uparrow,\uparrow}\otimes\ket{\downarrow}
-		\end{cases}
-		\implies \left(H_X\right)_{m,\pm}\left(H_X\right)_{\pm,i} = \begin{cases}
-			t^2 a_{1\pm} \mathcal{D}^-_\pm\\
-			-t^2 a_{2\pm}\mathcal{D}^-_\pm\\
-			t^2 \mathcal{D}^+_\pm\mathcal{D}^-_\pm\\
-			-\sqrt 2 t^2 a_{1\pm}\mathcal{D}^-_\pm
-		\end{cases}\\
-		\frac{1}{\delta E_m}\big\Vert\sum_n \frac{1}{\delta E_n}\left(H_X\right) _{mn}\left(H_X\right)_{ni}\big\Vert^2 = \begin{cases}
-		\frac{1}{\delta E_\mathrm{ST}}\left(\sum_{\pm}\frac{t^2}{\delta E_\pm}a_{1\pm}\mathcal{D}^-_\pm\right)^2 \\
-		\frac{t^4}{\delta E_\mathrm{CS}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{2\pm}\mathcal{D}^-_\pm\right)^2\\
-		\frac{t^4}{\delta E_\mathrm{2}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}\mathcal{D}^+_\pm\mathcal{D}^-_\pm\right)^2\\
-		\frac{2 t^4}{\delta E_\mathrm{\uparrow \uparrow}}\left(\sum_{\pm}\frac{1}{\delta E_\pm}a_{1\pm}\mathcal{D}^-_\pm\right)^2\\
-		\end{cases}
-\end{gather}
-
-For the final part, we again use \(\Delta^{(2)} H_{i=1} = -t^2\sum_\pm \frac{1}{\delta E_\pm} \left[\left(\mathcal{S}^-_\pm\right)^2 + \left(\mathcal{D}^-_\pm\right)^2\right]\).
-Also, since \(\left(H_X\right)_{ni} = \left(v + v^\dagger\right)_{ni}\), we have
-\begin{equation}\begin{aligned}
-\sum_{n} \frac{1}{\left(\delta E_n\right)^2}\big\Vert\left(H_X\right)_{ni}\big\Vert^2 =	t^2\sum_{\pm} \left[\left(\frac{\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \left(\frac{\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right]
-\end{aligned}\end{equation}
-
-Combining all the terms, we get
-\begin{equation}\begin{aligned}
-	- \ket{\Phi}_1 \bra{\Phi}_1 4t^4\left[\left(\frac{1}{\delta E_\mathrm{ST}} + \frac{2}{\delta E_{\uparrow \uparrow}}\right) \left\{\left(\frac{1}{2}\sum_{\pm}\frac{a_{1\pm}\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \left(\frac{1}{2}\sum_{\pm}\frac{a_{1\pm}\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right\} + \frac{1}{\delta E_\mathrm{CS}} \left\{\left(\frac{1}{2}\sum_{\pm}\frac{a_{2\pm}\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2  \right.
-\right.\\
-	+ \left.
-\left.
-\left(\frac{1}{2}\sum_{\pm}\frac{a_{2\pm}\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right\} + \frac{1}{\delta E_\mathrm{2}}\left\{\left(\frac{1}{2}\sum_{\pm}\frac{\mathcal{S}^+_\pm\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \left(\frac{1}{2}\sum_{\pm}\frac{\mathcal{D}^+_\pm\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right\} \right.
-\\
-- \left.\sum_\pm \frac{1}{\delta E_\pm} \frac{1}{2}\left\{\left(\mathcal{S}^-_\pm\right)^2 + \left(\mathcal{D}^-_\pm\right)^2\right\}\sum_\pm \frac{1}{2}\left\{\left(\frac{\mathcal{S}^-_\pm}{\delta E_\pm}\right)^2 + \left(\frac{\mathcal{D}^-_\pm}{\delta E_\pm}\right)^2\right\}\right]\\
-\end{aligned}\end{equation}
-If we define some quantities: \(F_{(1,2)} = \sum_{\pm}\frac{a_{(1,2)\pm}\mathcal{S}^-_\pm}{\delta E_\pm}, G_{(1,2)} = \sum_{\pm}\frac{a_{(1,2)\pm}\mathcal{D}^-_\pm}{\delta E_\pm}, P = \sum_{\pm}\frac{\mathcal{S}^+_\pm\mathcal{S}^-_\pm}{\delta E_\pm}, Q = \sum_{\pm}\frac{\mathcal{D}^+_\pm\mathcal{D}^-_\pm}{\delta E_\pm}, X_n = \sum_\pm \frac{\left(\mathcal{S}_\pm^-\right)^2}{\left(\delta E_\pm\right)^n}, Y_n = \sum_\pm \frac{\left(\mathcal{D}_\pm^-\right)^2}{\left(\delta E_\pm\right)^n}\), the total renormalisation from second and fourth order can be written as
-\begin{gather}
-	-\left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right) 4t^4 \left[\frac{1}{2t^2}X_1 + \left(\frac{1}{\delta E_\mathrm{CS}} + \frac{2}{\delta E_{00}}\right) F_{2}^2 + \frac{1}{\delta E_\mathrm{2}}P^2 - X_1 X_2\right]\nonumber\\
-	- \left(\ket{\Phi}_1 \bra{\Phi}_1 + \ket{\Phi}_2 \bra{\Phi}_2\right) t^4\left[\frac{1}{t^2}\left(X_1 + Y_1\right) + \left(\frac{1}{\delta E_\mathrm{ST}} + \frac{2}{\delta E_{\uparrow \uparrow}}\right) \left(F_1^2 + G_1^2\right) + \frac{1}{\delta E_\mathrm{CS}} \left(F_2^2 + G_2^2\right)\right.\nonumber\\
-\left. + \frac{1}{\delta E_\mathrm{2}} \left(P^2 + Q^2\right) - \left(X_1 + Y_1\right) \left(X_2 + Y_2\right)\right]
-\end{gather}
-The excitation energies are given by
-\begin{equation}
-	\delta E_\mathrm{CS} = \delta E_{00} = \frac{3J}{8} + \frac{U}{4} + \alpha, ~ ~ \delta E_{\uparrow \uparrow} = \delta E_\mathrm{ST}  = -\frac{U}{4} + \frac{5J}{8} + \alpha, ~ ~ \delta E_2 = 2\alpha, ~ ~ \delta E_\pm = \frac{3J}{8} + \alpha \pm \frac{1}{2}\Delta, ~ ~ \alpha \equiv \sqrt{V^2 \gamma^2 + 4V^2}
-\end{equation}
-where \(V\gamma = \frac{3J}{8} + \frac{U}{4}\) and \(\Delta = \sqrt{\frac{U^2}{4} + 4V^2}\). The effective Hamiltonian can be expressed in the general form
-\begin{equation}
-	H_\text{eff} = \ket{\Psi}_1\bra{\Psi}_1\otimes \left[\text{constant} + \alpha_\text{spin} \mathcal{\hat{P}}_\text{spin} + \alpha_\text{charge} \mathcal{\hat{P}}_\text{charge}\right] 
-\end{equation}
-\(\mathcal{\hat  P}_\text{charge}\) and \(\mathcal{\hat P}_\text{spin}\) are projection operators for, respectively, the charge \((\hat n_1 \neq 1)\) and spin \(\left(\hat n_1=1\right) \) sectors of the first site.
-Since \(\mathcal{\hat P}_\text{charge} + \mathcal{\hat P}_\text{spin} = 1\), we can eliminate one of the terms and rewrite the effective Hamiltonian in the simpler form
-\begin{equation}\begin{aligned}
-	H_\text{eff} = \ket{\Psi}_1\bra{\Psi}_1\otimes \left[\text{constant} + \mathcal{F} \mathcal{\hat P}_\text{charge}\right] 
-\end{aligned}\end{equation}
-where \(\mathcal{F} \equiv \alpha_\text{charge} - \alpha_\text{spin}\) is the net energy of the charge sector above the spin sector.
-
-We will now look at the extreme strong coupling regime \(J \gg V \gg U,t\). There, all the expressions simplify:
-\begin{gather}
-	V\gamma \simeq \frac{3J}{8},~ ~ \Delta \simeq 2V,~ ~ \alpha \simeq \frac{3J}{8}, ~ ~ c_s^+ = -c_c^- \simeq 0, ~ ~ c_s^- = c_c^+ \simeq 1, ~ ~ \mathcal{N}_\pm \simeq 4\sqrt 2 V, ~ ~ a_{1,\pm} \simeq \frac{1}{2}, ~ ~ a_{2,\pm} \simeq \pm \frac{1}{2}~,\nonumber\\
-	\delta E_\pm = \delta E_\mathrm{CS} = \delta E_{00} = \delta E_2 \simeq \frac{3J}{4}, ~ ~ \delta E_\mathrm{ST} = \delta E_{\uparrow \uparrow} \simeq J, ~ ~ \mathcal{S}^-_\pm = \mathcal{D}^-_\pm \simeq \frac{1}{2}, ~ ~ \mathcal{S}^+_\pm = -\mathcal{D}^+_\pm \simeq \pm \frac{1}{2},~\nonumber\\
-	F_1 = G_1 \simeq \frac{2}{3J}, ~ ~ F_2 = G_2 \simeq 0, ~ ~ P = Q \simeq 0,~ ~ X_1 = Y_1 \simeq \frac{2}{3J}, ~ ~ X_2 = Y_2 \simeq \frac{8}{9J^2}
-\end{gather}
-The effective Hamiltonian becomes
-\begin{equation}\begin{aligned}
-	&-\left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right) \frac{4t^2}{3J}\left[1 - \frac{16 t^2}{9 J^3}\right] - \left(\ket{\Phi}_1 \bra{\Phi}_1 + \ket{\Phi}_2 \bra{\Phi}_2\right) \frac{4t^2}{3J}\left[1 + \frac{2t^2}{9 J^2} \right]\\
-	=&-\frac{4t^2}{3J}\sum_i \ket{\Phi}_i \bra{\Phi}_i +  \left(\ket{\Phi}_0 \bra{\Phi}_0 + \ket{\Phi}_3 \bra{\Phi}_3\right) \frac{64 t^4}{27 J^3} - \left(\ket{\Phi}_1 \bra{\Phi}_1 + \ket{\Phi}_2 \bra{\Phi}_2\right) \frac{8t^4}{27 J^3}\\
-	=& \ket{\Psi}_1 \bra{\Psi}_1 \left[\text{constant} + \frac{64 t^4}{27 J^3} \mathcal{P}_\text{charge}  - \frac{8t^4}{27 J^3}\mathcal{P}_\text{spin}\right] 
-\end{aligned}\end{equation}
-\(\mathcal{P}_\text{spin}\) and \(\mathcal{P}_\text{charge}\) project, respectively,  onto the spin and charge sectors of the first site.
-The fact that the charge sector comes with a positive factor means that the holon-doublon states are repulsive, and this renormalisation of the states generates an effective particle-hole symmetric Fermi liquid interaction on the first site - also known as the local Fermi liquid (LFL)~\cite{nozieres1974fermi}.
-
-\section{Destruction of the Abrikosov-Suhl resonance: passage from strong coupling to local moment}
-
-We will now tune the parameters of the fixed point Hamiltonian and study the variation of quantities related to the effective Hamiltonian like the local FL strength \(\mathcal{F}\), the gap in the spectrum of the zeroth Hamiltonian \(H_0^*\) and the value of the small parameter \(t^2/\delta E\), as well as various measures of entanglement like entanglement entropy, mutual information and spin-spin correlations between various sets of members of the real-space impurity+lattice construction.
-We will trace a specific path through the space of values of fixed point couplings: we will start from the strong coupling regime \(U \ll J,V\) and go towards the local moment regime \(U \gg J,V\).
-The context of this study is that the technique of dynamical mean-field theory (DMFT) obtains a metal-insulator transition in the 2D Hubbard model by studying the Anderson impurity model as the auxiliary system for the Hubbard; there, the local moment regime of the impurity corresponds to the insulator in the bulk.
-Our goal here is to study what precisely happens in the effective Hamiltonian in the journey from the metal to the insulator, and draw a concrete connection between this modification of the effective Hamiltonian, and the simultaneous change of the impurity spectral function in fig.~\ref{spec_func}.
-This is done with the knowledge that the local moment phase of the generalised SIAM is never RG-stable.
-
-\subsection*{Perturbation theory parameters}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/gap-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/par-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/lfl-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-\end{center}
-The vanishing of the gap and the growth of the small parameter indicates the breakdown of perturbation theory around the singlet; this simply shows that there is a degeneracy in the local moment regime, and the effective Hamiltonian will have to be obtained using degenerate perturbation theory.
-The presence of degeneracy also suggests that the effective Hamiltonian will be of the non-Fermi liquid type.
-
-\subsection*{\(k-\)space correlations within the Kondo cloud}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-\end{center}
-
-The mutual information \(I(d:k)\) between the impurity and the cloud vanishes as \(U/J\) is increased.
-This is a signature of the loss of entanglement and the breakdown of the singlet.
-The reduction of the mutual information within the cloud, \(I(k_1:k_2)\), shows that the Kondo cloud is being killed as \(U/J\) is increased; it ultimately drops to zero, characteristic of a decoupled tight-binding chain.
-The four-Fermion off-diagonal term also vanishes as \(U/J\) increases and this is again a signature of the reduction in the spin-flip processes.
-The diagonal correlation \(\left<\hat n_{k \uparrow} \hat n_{q \downarrow} \right>\) increasing to 1 shows the formation of a filled Fermi sea.
-
-\subsection*{Mutual information between various real space members}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-01-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d1-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-\end{center}
-The impurity-zeroth site mutual information \(I(d:0)\) remains unchanged at the maximum for an appreciable range of values, and this shows the stability of the singlet.
-Meanwhile, the mutual information between the zeroth site and the site nearest to it (\(I(0:1)\)) grows, because when the singlet weakens, the zeroth site is able to entangle more with the other sites.
-It finally saturates to its maximum value, which is the value produced as result of the tight-binding hopping.
-The mutual information between the impurity and sites beyond the zeroth site (\(I(d:1)\)) show a non-monotonic behaviour; it first increases as the entanglement that was initially restricted to just the impurity and the zeroth sites begins "seeping" into the other sites as well.
-Beyond a critical value of \(U/J\), \(I(d:1)\) starts dropping, because the entanglement has now mostly shifted out of the singlet and into the conduction bath.
-
-\subsection*{Impurity entanglement entropy and spin-spin correlations}
-
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/EE-d-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d1-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-02-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-03-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-
-\end{center}
-
-The von-Neumann entanglement entropy \(S(d)\) of the impurity shows pretty straightforward behaviour.
-It is maximum for \(U \ll J\) because it is in a singlet configuration.
-For \(U \gg J\), the singlet weakens and the impurity begins to decouple from the bath, leading to a reduction in \(S(d)\).
-At sufficiently low values of \(J/U\), the impurity decouples from the zeroth site and the total system can be factorised into a local moment in product with a tight-binding chain, so that the impurity site will now have zero entanglement entropy.
-The spin-spin correlation \(\vec{S}_d\cdot\vec{S}_0\) is most negative at large \(J\), showing maximum screening at strong-coupling.
-It decreases to 0 as the singlet breaks.
-This reduction in the spin-spin correlation between the impurity and the zeroth site is accompanied by the appearance of antiferromagnetic spin-spin correlation \(\vec{S}_0\cdot\vec{S}_1, \vec{S}_0\cdot\vec{S}_3\) between the zeroth site and odd-numbered sites like 1 and 3.
-This can be understood on the following grounds:since the tight-binding hopping only connects same spin states, an electron on the first site has to have spin opposite to that on the zeroth site in order to hop onto that site.
-This requirement of opposite spin is what induces an antiferromagnetic superexchange interaction \(J_1\) between the zeroth site and the first site.
-This interaction strength increases as \(J\) is decreased, because \(J_1 \sim t^2/J\).
-By the same argument, a ferromagnetic superexchange interaction is induced between the impurity site and the first site, as well as between the zeroth site and the other even-numbered sites.
-These are also seen in the plots.
-
-\subsection*{Real-space correlations}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/r1p-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-od-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-opp-t=1.000,J=1_over_U,V=3J,N=4,U=1.000,1.000,50.pdf}
-
-	\includegraphics[width=0.3\textwidth]{../figures/r-par-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-ising-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-charge-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-\end{center}
-
-The increase of single-particle hopping correlation is another signature of the "handover" of entanglement from the singlet to the tight-binding chain.
-Exactly the same can be said for the four-Fermion interaction as well.
-
-\subsection*{Real-space correlations as function of distance}
-\begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/corr-di-min-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/corr-di-max-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-
-	\includegraphics[width=0.45\textwidth]{../figures/corr-all-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/I-all-t=1.000,U=1,V=3J,N=6,J=100.000,0.010,40.pdf}
-\end{center}
-
-The first thing to note in the first two figures is the difference in the order of magnitudes; the correlations are very small in the first figure, because the impurity is being screened almost completely by the zeroth site at \(J \gg U\).
-This changes in the second figure where, because \(U \gg J\), the singlet has become entangled with the other sites, and the impurity is being screened by multiple sites.
-The mutual information all vary similarly with distance in the bottom right figure.
-
-\subsection*{Impurity spectral function}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=0.100.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=9.000.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=16.000.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=20.250.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/spec-func-gen-siam-U_by_J=36.000.pdf}
-\end{center}
-
-\section{Calculating the \(T=0\) Wilson ratio from low energy excitations}
-The total system now consists of two decoupled parts - the singlet composed of the impurity and the zeroth site, and the remaining lattice composed of N-1 sites with a tight-binding dispersion and a local interaction at the 1-th site.
-The effective Hamiltonian for the remaining lattice is
-\begin{equation}\begin{aligned}
-	\sum_{i=1\atop{\sigma}}^\infty t\left(c^\dagger_{i\sigma}c_{i+1 \sigma} + c^\dagger_{i+1 \sigma}c_{i\sigma}\right) + u \hat n_{1 \uparrow} \hat n_{1 \downarrow}
-\end{aligned}\end{equation}
-We have rewritten the holon term in terms of the spin and doublon operators.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.7\textwidth]{../figures/lattice_eff.png}
-	\caption{\textit{Left}: The nearest-neighbor hopping described by the effective Hamiltonian.
-The red circle is the impurity.
-The black cloud at the center demarcates the collection of electrons at the origin of the lattice (which couple to the impurity).
-The green circles represent lattice sites that are nearest to the origin.
-The blue circles represent next-nearest sites.
-\textit{Right}: After treating the hopping between origin and its nearest neighbors as perturbation, we get a system consisting of two decoupled parts: one part is the impurity+cloud singlet, the other part is the rest of the lattice sites.
-The effect of the hopping between the origin and the green sites is a repulsion term on the green sites.}
-\end{figure}
-We will now invoke the mean-field approximation in simplifying this term.
-We will be dealing with thermodynamic quantities soon, so the operators will be replaced by their thermodynamic values, that is, the values that minimize the free energy functional.
-\begin{equation}\begin{aligned}
-	\hat n_{1 \uparrow} \hat n_{1 \downarrow} \to \langle \hat n_{1 \uparrow} \hat n_{1 \downarrow}\rangle = \langle  \delta n_{1 \uparrow} \delta n_{1 \downarrow}\rangle + \langle  n_{1 \uparrow}\rangle\langle  n_{1 \downarrow}\rangle
-\end{aligned}\end{equation}
-where \(\delta n_{1\sigma} \equiv n_{1 \sigma} - \langle  n_{1\sigma} \rangle\) is the fluctuation of the particle number above the ground state.
-The mean-field approximation then involves dropping the first term which is a quadratic fluctuation - since we are interested in values of quantities at \( T \to 0\), this quadratic fluctuation is very small.
-The interaction we are left with is
-\begin{equation}\begin{aligned}
-	u\langle  n_{1 \uparrow}\rangle\langle  n_{1 \downarrow}\rangle = \sum_{kq\sigma}f_{kq}\langle  n_{k \sigma}\rangle\langle  n_{q \overline\sigma}\rangle
-\end{aligned}\end{equation}
-This interaction converts the problem to that of a Landau Fermi liquid, with the quasiparticle energy functional being given by
-\begin{equation}\begin{aligned}
-	\epsilon_{k\sigma} = \epsilon_k + \sum_{q}f_{kq}\left<\hat n_{q \overline\sigma}\right>
-\end{aligned}\end{equation}
-From the form of the quasiparticle energy functional, we can see that there is no spin-parallel term, so we can write
-\begin{equation}\begin{aligned}
-	\label{rel_landau}
-	f_{kk^\prime\sigma\sigma} = 0,  f_{kk^\prime\sigma\overline\sigma} = f_{kk^\prime}
-\end{aligned}\end{equation}
-We will now use this Fermi liquid form to extract the Wilson ratio. We will make use of the following definitions/results:
-\begin{gather}
-	dn_{k\sigma} = \frac{\partial{n}}{\partial{\epsilon_{k\sigma}}}\left( d\epsilon_{k\sigma} - d\mu \right) ~ ~ \left[\text{follows from differentiating FD distribution}\right] \\
-	C_V = \frac{\:\mathrm{d}\epsilon}{\:\mathrm{d}T}, ~ ~ \chi^{s,c} = \frac{\:\mathrm{d}}{\:\mathrm{d}(B, \mu)}\left(n_\uparrow \mp n_\downarrow\right), ~ ~ 2f_0^{s,a} = \sum_k\left(f_{kk^\prime \uparrow \uparrow} \pm f_{kk^\prime \uparrow \downarrow}\right), ~ ~ F_0^{s,a} = \rho(0) f_0^{s,a}
-\end{gather}
-\subsection{Low-\(T\) Specific heat}
-\begin{equation}\begin{aligned}
-	C &= \frac{\:\mathrm{d}}{\:\mathrm{d}T}\sum_{k\sigma}\epsilon_{k\sigma}n_{k\sigma} \\
-	    &\approx \sum_{k\sigma}\epsilon^0_{k\sigma} \frac{\:\mathrm{d}n_{k\sigma}}{\:\mathrm{d}T} && \left[\text{no quasiparticles at ground state}\right] \\
-	    &\approx \sum_{k\sigma}\epsilon^0_{k\sigma} \frac{\:\mathrm{d}n_{k\sigma}}{\:\mathrm{d}T} && \left[\text{same expression as Fermi gas but with modified distribution function}\right] \\
-	    &= \rho(0) T
-\end{aligned}\end{equation}
-where \(\rho\) is the total quasiparticle DOS with contributions from conduction bath and impurity.
-\begin{equation}\begin{aligned}
-	\rho \sim \text{Im }\text{Trace}\left[G\right] = \text{Im}\sum_{d\sigma}G_{dd}^\sigma + \text{Im}\sum_{k\sigma}G_{kk}^\sigma = \rho_0 + \rho_\text{imp}
-\end{aligned}\end{equation}
-which gives
-\begin{equation}\begin{aligned}
-	C_{imp} \equiv C - C_0 = \rho_{imp}(0)T
-\end{aligned}\end{equation}
-
-\subsection{Low-\(T\) Charge Susceptibility}
-\begin{equation}\begin{aligned}
-	\chi^c &= \frac{\:\mathrm{d}N}{\:\mathrm{d}\mu}\\
-\end{aligned}\end{equation}
-Due to change in chemical potential, \(\delta\epsilon_{k\sigma}\) is isotropic and SU(2)-symmetric. Hence
-\begin{equation}\begin{aligned}
-	d\epsilon_{k\sigma} &= \sum_{k^\prime\sigma^\prime}f_{kk^\prime\sigma\sigma^\prime}d n_{k^\prime\sigma^\prime}\\
-			    &= d n\sum_{k^\prime}\left(f_{kk^\prime\uparrow \uparrow} + f_{kk^\prime \uparrow \downarrow}\right) && \left[dn = dn_{k^\prime \uparrow} = dn_{k \downarrow}\right] \\
-			    &= 2dn f_0^s
-\end{aligned}\end{equation}
-Therefore,
-\begin{equation}\begin{aligned}
-	dN &= \sum_{k\sigma}dn_{k\sigma} = \sum_{k\sigma}\frac{\partial{n}}{\partial{\epsilon_{k\sigma}}}\left( d\epsilon_{k\sigma} - d\mu \right) = \sum_{k\sigma}-\frac{1}{2}\rho\left(2dn f_0^s - d\mu \right) = -\rho(0) d N f_0^s + d\mu \rho(0) \\
-	   &\approx d\mu \rho(0) - \rho(0) f_0^s d\mu \rho(0) \left[\text{substitute \(dN\) back into itself}\right] \\
-	\implies \frac{\:\mathrm{d}N}{\:\mathrm{d}\mu} &= \rho(0)\left( 1 - \rho(0)f_0^s \right) \implies \chi^c_{imp} = \rho(0)_{imp} - \rho(0)f_0^s \\
-\end{aligned}\end{equation}
-At an intermediate state, we substituted \(dN\) back into itself and kept only the leading order term.
-This is justified because \(f_{kk^\prime}\) goes as \(\frac{1}{N J}\).
-At the fixed point and for a thermodynamically large system, both \(J\) and \(N\) are very large, so keeping only the leading order suffices.
-
-From a previous calculation, we know that the charge susceptibility at \(T=0\) is zero (eq.~\eqref{zero_chi_charge}), so we can write down the following relation:
-\begin{equation}\begin{aligned}
-	\label{fp_constraint}
-	f_0^s = \frac{\rho(0)_{imp}}{\rho(0)}
-\end{aligned}\end{equation}
-
-\subsection{Low-\(T\) Spin Susceptibility}
-\begin{equation}\begin{aligned}
-	\chi^s &= \frac{\:\mathrm{d}m}{\:\mathrm{d}\mu}\\
-\end{aligned}\end{equation}
-Due to change in magnetic field, change in \(\epsilon_{k\sigma}\) should be isotropic and SU(2)-\text{anti}symmetric. Hence
-\begin{equation}\begin{aligned}
-	d\epsilon_{k\sigma} &= -\frac{1}{2}dB \sigma + \sum_{k^\prime\sigma^\prime}f_{kk^\prime\sigma\sigma^\prime}d n_{k^\prime\sigma^\prime}\\
-			    &= -\frac{1}{2}dB \sigma + d n_{\sigma}\sum_{k^\prime}\left(f_{kk^\prime\uparrow \uparrow} - f_{kk^\prime \uparrow \downarrow}\right) && \left[dn_{k^\prime \uparrow} = -dn_{k \downarrow}\right] \\
-			    &= -\frac{1}{2}dB \sigma + 2dn_\sigma f_0^a
-\end{aligned}\end{equation}
-Since the total number remains constant, \(\mu=0\). Therefore,
-\begin{equation}\begin{aligned}
-	dm &= \sum_{k}\left(dn_{k \uparrow} - dn_{k \downarrow}\right) = -\frac{1}{2}\sum_{k}\rho\left( d\epsilon_{k \uparrow} - d\epsilon_{k \downarrow} \right) = -\frac{1}{2}\sum_{k}\rho\left(-dB + 2f_0^a \left(dn_{k \uparrow} - dn_{k \downarrow}\right)\right) \\
-	   &= dB\rho(0) - dm \rho(0)f_0^a \approx dB\rho(0) - \rho(0)f_0^aB\rho(0) ~ \left[\text{substitute \(dm\) back into itself}\right] \\
-	\implies \frac{\:\mathrm{d}m}{\:\mathrm{d}B} &= \rho(0)\left( 1 - \rho(0)f_0^a \right) \implies \chi^s_{imp} = \rho(0)_{imp} - \rho(0)f_0^a \\
-\end{aligned}\end{equation}
-
-\subsection{Wilson ratio}
-The Wilson ratio for the impurity~\cite{wilson1975,nozieres1974fermi,hewson1993} is defined as
-\begin{equation}\begin{aligned}
-	R = \frac{\chi^s_{imp}}{\frac{C_{imp}}{T}}
-\end{aligned}\end{equation}
-From eq.~\eqref{rel_landau}, we have \(f_0^s = -f_0^a\), which, when combined with eq.~\eqref{fp_constraint}, gives
-\begin{equation}\begin{aligned}
-	\chi^s_{imp} &= 2\rho(0)_{imp}
-\end{aligned}\end{equation}
-The Wilson ratio becomes
-\begin{equation}\begin{aligned}
-	R = \frac{2\rho(0)_{imp}}{\rho(0)_{imp}} = 2
-\end{aligned}\end{equation}
-
-\section{Luttinger's and Friedel's sum rules}
-\label{lutt_theorem}
-In this section, we will compute Luttinger's sum for the various fixed-point theories.
-Luttinger's sum is essentially the volume enclosed by the Fermi surface~\cite{luttinger1960fermi,oshikawa2000topological,seki2017topological}, and Luttinger's theorem states that this volume counts the number of electrons in the system~\cite{luttinger1960fermi,oshikawa2000topological,seki2017topological}.
-
-We first consider the strong-coupling fixed point Hamiltonian, which is essentially just a resonant-level model:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{res} = \sum_{k\sigma}\epsilon_k \hat n_{k\sigma} + \sum_{k\sigma}\left(V_k c^\dagger_{k\sigma} c_{d\sigma} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-The impurity Green's function is given by~\cite{anderson_1961,hewson1993,coleman2015}
-\begin{equation}\begin{aligned}
-	G_{d}(z) &= \frac{1}{z - \Sigma_d}\ket{d\sigma}\bra{d\sigma}, ~ ~ \Sigma_d = \sum_k \frac{V^2}{z - \epsilon_k}
-\end{aligned}\end{equation}
-\(\Sigma_d(z)\) is zero at the free orbital fixed point. The conduction electron Green's function is 
-\begin{gather}
-	G_{k}(z) = G_k^0(z) + \left[G_k^0(z)V_k\right]^2 G_{d}(z), ~ ~ G_k^0 = \frac{1}{z - \epsilon_k}, ~ ~ G_c^0(z) = \sum_k G_k^0(z)\ket{k}\bra{k}~,\\
-	G_c(z) = \sum_k G_k(z)\ket{k}\bra{k} = G_c^0 + \left[G_k^0(z)V_k\right]^2 G_{d}(z)\ket{k}\bra{k} 
-\end{gather}
-The total number of electrons is given by the sum of the number of electrons in the conduction bath and at the impurity~\cite{hewson1993,langreth1966}:
-\begin{equation}\begin{aligned}
-	\label{tot_num}
-	N &= \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_{d}(z) + G_c(z)\right] = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_{d}(z) + G_c^0(z) + \left[G_k^0(z)V_k\right]^2 G_{d}(z)\ket{k}\bra{k}\right]
-\end{aligned}\end{equation}
-Since the eigenstates of the system are situated at real poles, the contour \(\Gamma\) encloses only the real axes and hence picks out those real poles to count the total number of particles.
-
-Since \(1/G_{c}^0(z) = z - \sum_k \epsilon_k \hat n_k\), we can write \(\text{Tr}\left[G_{c}^{0}(z)\right] = \text{Tr}\left[G_{c}^{0} \frac{\partial{}}{\partial{z}}\left(1/G_{c}^{0}\right)\right]\) and hence
-\begin{equation}\begin{aligned}
-	\label{simple_bath}
-	\text{Tr}\left[G_c(z)\right] &=\frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{c}^{0}\right)\right] + \sum_k\left[G_k^0(z)V_k\right]^2 G_{d}(z)
-\end{aligned}\end{equation}
-
-The impurity part can, on the other hand, be written as
-\begin{equation}\begin{aligned}
-	\label{self_id}
-	\text{Tr}\left[G_{d}(z)\right] &= \text{Tr}\left[ \frac{\ket{d}\bra{d}}{z - \Sigma_d(z)}\right] = \text{Tr}\left[ \frac{\ket{d}\bra{d}}{z - \Sigma_d(z)}\frac{\partial{\left(z\right)}}{\partial{z}} \right] = \text{Tr}\left[ G_{d}(z)\frac{\partial{G_{d}^{-1}(z)}}{\partial{z}} \right] + \text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right]\\
-\end{aligned}\end{equation}
-The fist term can be written as \(\text{Tr}\left[ G_{d}(z)\frac{\partial{G_{d}^{-1}(z)}}{\partial{z}} \right] = \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}G_{d}^{-1}(z)\right]\).
-The second part can be written as \(\frac{\partial{}}{\partial{z}}{\Sigma_d(z)} = -\sum_k V^2 {G_k^0}^2\).
-Together, we get
-\begin{equation}\begin{aligned}
-	\label{simple_imp}
-	\text{Tr}\left[G_{d}(z)\right] = \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{d}\right)\right] - \text{Tr}\left[ G_{d}(z)\sum_k V^2 {G_k^0}^2\right]\\
-\end{aligned}\end{equation}
-Substituting eqs.~\ref{simple_bath} and \ref{simple_imp} into eq.~\ref{tot_num}, we get
-\begin{equation}\begin{aligned}
-	N = \oint \frac{dz}{2\pi i}n_F(z) \left[\frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{d}\right)\right] + \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{c}^{0}\right)\right]\right]
-\end{aligned}\end{equation}
-At \(T=0\), \(n_F\) is defined as 1 below the FS, \(\frac{1}{2}\) at the FS and 0 above it.
-\begin{equation}\begin{aligned}
-N  = \left[\oint_{\Gamma_<} + \frac{1}{2}\oint_{\Gamma_0}\right]\frac{dz}{2\pi i}\left[\frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{1/G_d(z)\right\} + \frac{\partial{}}{\partial{z}} \ln \text{Det} \left\{1/G_{c}^{0}(z)\right\} \right]
-\end{aligned}\end{equation}
-Following Seki and Yunoki~\cite{seki2017topological}, we can define a winding number for a Green's function \(G(z)\):
-\begin{equation}\begin{aligned}
-	n_{\text{Det} G^{-1}}(C) = \oint_{C} \frac{dz}{2\pi i} \frac{\partial{\ln\text{Det }G^{-1}(z)}}{\partial{z}} = \oint_{\text{Det} G^{-1}(C)} \frac{\mathrm{d}\; \text{Det }G^{-1}}{\text{Det }G^{-1}}
-\end{aligned}\end{equation}
-Since \(n_{\text{Det } G^{-1}(C)}\) counts the number of times the curve \(\text{Det } G^{-1}(C)\) winds around the origin, it is integer-valued and topological.
-Seki and Yunoki also show that the this number is given by
-\begin{equation}\begin{aligned}
-n_{\text{Det }G^{-1}(C)} = P_{\text{Det }G}(C) - Z_{\text{Det }G}(C)
-\end{aligned}\end{equation}
-where \(P_{f(z)}(C)\) is the number of poles of \(f(z)\) enclosed by the contour \(C\), and \(Z\) is the corresponding number of zeros.
-The total number of particles in the resonant level model can thus be written as
-\begin{equation}\begin{aligned}
-	N =& \underbrace{P_{\text{Det }G_d}(\Gamma_<) - Z_{\text{Det }G_d}(\Gamma_<)}_{N_\text{imp}^<} + \underbrace{\frac{1}{2}\left[P_{\text{Det }G_d}(\Gamma_0) - Z_{\text{Det }G_d}(\Gamma_0)\right]}_{N_\text{imp}^0} + \underbrace{P_{\text{Det }G_{c}^{0}}(\Gamma_<) - Z_{\text{Det }G_{c}^{0}}(\Gamma_<)}_{N_\text{L}^<} \\
-	  &+ \underbrace{\frac{1}{2}\left[P_{\text{Det }G_{c}^{0}}(\Gamma_0) - Z_{\text{Det }G_{c}^{0}}(\Gamma_0)\right]}_{N_\text{L}^0}\\
-	  =& N_\text{imp}^< + \frac{1}{2}N_\text{imp}^0 + N_L^< + \frac{1}{2}N_L^0
-\end{aligned}\end{equation}
-The average number of particles can thus be expressed purely in terms of the number of real poles and real zeros of the impurity and the conduction electron Green's functions.
-\(N_\text{imp}^<\left(N_\text{imp}^<\right)\) is the number of poles minus the number of zeros of the impurity Greens function inside (on) the Fermi surface.
-\(N_\text{imp} = N_\text{imp}^0 + \frac{1}{2}N_\text{imp}^0\)  therefore gives the total number of localised eigenstates of the system.
-Similarly, \(N_L^<\left( N_L^0 \right) \) gives the number of real poles in the conduction electron Greens function minus the number of real zeros, and \(N_L = N_L^< + \frac{1}{2}N_L^0\) gives the total number of delocalised eigenstates of the system.
-\begin{equation}\begin{aligned}
-	\label{total_lutt}
-	N = N_\text{imp} + N_L
-\end{aligned}\end{equation}
-Note that this also holds at the free orbital fixed point, because it is a special case of the strong-coupling fixed point with \(V=0\).
-
-If we are the local moment fixed point with particle-hole symmetry, we instead have the Hamiltonian
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{lm} = \sum_{k\sigma}\epsilon_k \hat n_{k\sigma} + H_\text{imp}
-\end{aligned}\end{equation}
-where \(H_\text{imp} = -(U/2)\hat n_d + U\hat n_{d \uparrow} \hat n_{d \downarrow}\) is the impurity Hamiltonian.
-In this atomic limit, the impurity Greens function is given by~\cite{phillips2012advanced}
-\begin{equation}\begin{aligned}
-	\label{lm_sigma}
-	G_d = \frac{1}{z - \Sigma_d(z)}, ~ ~ ~\Sigma_d = \frac{U^2}{4}\frac{1}{z}
-\end{aligned}\end{equation}
-Since \(V=0\) at this fixed point, the total number of particles is given by
-\begin{equation}\begin{aligned}
-	\label{total_num_lm}
-	N = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_{d}(z) + G_c^0(z)\right]
-\end{aligned}\end{equation}
-We again use eq.~\ref{self_id} to write
-\begin{equation}\begin{aligned}
-	\text{Tr}\left[G_{d}(z)\right] = \text{Tr}\left[ G_{d}(z)\frac{\partial{G_{d}^{-1}(z)}}{\partial{z}} \right] + \text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right] = \frac{\partial{}}{\partial{z}}\left[\ln \text{Det}\left(1/G_{d}\right)\right] + \text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right]
-\end{aligned}\end{equation}
-Performing the integral for the second term gives
-\begin{equation}\begin{aligned}
-	\left(\int_{\Gamma_<} + \frac{1}{2}\int_{\Gamma_0}\right)\frac{dz}{2\pi i}\text{Tr}\left[ G_{d}(z)\frac{\partial{\Sigma_d(z)}}{\partial{z}} \right] = 0
-\end{aligned}\end{equation}
-Here we used the form of \(\Sigma_d\) in eq.~\ref{lm_sigma}. Repeating the same steps as before, we recover eq.~\ref{total_lutt}.
-
-We now compare the Luttinger volume across the fixed points.
-At the local moment fixed point, the impurity Greens function has a single pole at \(z<0\) and a zero at \(z=0\), so \(N_\text{imp} = 1 - 1/2 = 1/2\), and eq.~\ref{total_lutt} becomes
-\begin{equation}\begin{aligned}
-	N = 1/2 + N_\text{L}^{LM}
-\end{aligned}\end{equation}
-The same thing happens at the free orbital fixed point; there, \(G_d\) has a single pole at \(z=0\), so \(N_\text{imp} = 1/2\) and we again get \(N = 1/2 + N_\text{L}^{FO}\).
-The change happens when we go to the strong-coupling resonant-level fixed point.
-There, the impurity self-energy can be written as~\cite{anderson_1961,hewson1993,coleman2015}
-\begin{equation}\begin{aligned}
-	\Sigma_d^\text{sc} = \text{Re}\left[\Sigma_d^\text{sc}\right] - i\Delta
-\end{aligned}\end{equation}
-That is, the self-energy becomes imaginary, so the real pole that existed at the free orbital fixed point moves off the real axis.
-We therefore have \(N_\text{imp} = 0\).
-Assuming the number of particles \(N\) remained constant, we obtain \(N = N_\text{L}^{SC}\).
-The change in the Fermi volume in going from the local moment to the strong coupling fixed point is therefore by \(1/2\).
-If one defines new a Luttinger volume \(\mathcal{N}_L = 2N_L\) to also account for the spin degeneracy, we can write:
-\begin{equation}\begin{aligned}
-	\label{luttinger_change}
-	\Delta \mathcal{N}_L = 1
-\end{aligned}\end{equation}
-This is a specific case of the more general result for Kondo lattices obtained by Oshikawa using flux-insertion arguments\cite{oshikawa2000topological}.
-
-The scattering phase shift suffered by the conduction electrons at the Fermi surface, off the impurity, can be calculated from the impurity occupancy, using the Friedel sum rule.
-From the ground state wavefunction, we can calculate the average number of particles on the impurity:
-\begin{equation}\begin{aligned}
-	\left<n_d \right> = \bra{\Psi}_1\sum_\sigma \hat n_{d\sigma} \ket{\Psi}_1
-\end{aligned}\end{equation}
-\(\ket{\Psi}_1\) is the lower energy state in eq.~\eqref{gstate}. Performing the inner product gives
-\begin{equation}\begin{aligned}
-	\left<n_d \right> = \left( c_s^- \right)^2 + \left( c_c^- \right)^2 = 1
-\end{aligned}\end{equation}
-The phase shift is thus
-\begin{equation}\begin{aligned}
-	\frac{1}{\pi}\sum_\sigma \delta_\sigma(0) = \left<n_d \right> \implies \delta_\sigma(0) = \frac{\pi}{2}
-\end{aligned}\end{equation}
-There we used \(\delta_\uparrow = \delta_\downarrow\) because the model is SU(2)-symmetric. This line of arguments was first presented for the Kondo model in \cite{martin1982fermi}.
-
-The change in Luttinger's number also allows us to calculate the Wilson ratio of the system, from eq.~\eqref{wilson_luttinger}.
-\begin{equation}\begin{aligned}
-	R = 1 + \sin^2 \left( \frac{\pi}{2}\Delta \mathcal{N}_L \right) = 1 + \sin^2 \frac{\pi}{2} = 2
-\end{aligned}\end{equation}
-\section{Reverse RG analysis}\label{rev_rg}
-The goal here is to chart the journey starting from the IR fixed point towards the UV regime, by following one particular wavefunction.
-We will start with a very simple IR ground state wavefunction, and then go back towards the UV ground state by applying the inverse unitary operator \(U^\dagger\):
-\begin{equation*}\begin{aligned}
-	U : \underbrace{\ket{1,2,...,N}}_\text{UV ground state} \rightarrow \ket{1,2,...,N-1}\ket{N} \rightarrow ... \rightarrow \underbrace{\ket{1,2,...,N^*}\ket{N^*+1}...\ket{N}}_\text{IR ground state}
-\end{aligned}\end{equation*}
-\begin{equation*}\begin{aligned}
-	U^\dagger : \underbrace{\ket{1,2,...,N^*}\ket{N^*+1}...\ket{N}}_\text{IR ground state} \rightarrow \ket{1,2,...,N^*+1}\ket{N^*+2}...\ket{N} \rightarrow ...
-\rightarrow\underbrace{\ket{1,,2,...,N}}_\text{UV ground state}
-\end{aligned}\end{equation*}
-The first process is the forward RG which we used to obtain the scaling equations.
-The second process is the reverse RG which we will undertake now.
-The method has already been applied to study the renormalisation of entanglement in various models of strong correlation~\cite{siddharthacpi,anirban_kondo,anirban_mott_ent}.
-In general, we start with an IR wavefunction that consists a certain number of momentum states \(n_1\) still entangled with the impurity, and the remaining momentum states \(n_2\) disentangled from the impurity.
-The former are said to be part of the emergent Kondo cloud, while the latter are said to be part of the integrals of motion (IOMs) and appear in direct product with the cloud+impurity system in the ground state wavefunction.
-Each momentum state is tagged with two conduction bath levels, one above the Fermi surface and one below.
-These will be represented as \(k,\pm\).
-If we represent the emergent cloud momentum states as \(\left\{k_i\right\} \) and the IOM states as \(\left\{q_i\right\}\), the ground state wavefunction can be written as
-\begin{equation}\begin{aligned}
-	\ket{\Psi}_0 = \left(\otimes_{i=1}^{n_2}\ket{q_i,-,\uparrow}\ket{q_i,-,\downarrow}\right)\ket{\Phi}_\text{cloud}\left(\otimes_{i=1}^{n_2}\ket{q_i,+,\uparrow}\ket{q_i,+,\downarrow}\right)
-\end{aligned}\end{equation}
-Throughout, we have assumed that the IOMs below the Fermi surface are occupied while those above are unoccupied. This means:
-\begin{equation}\begin{aligned}
-	\ket{\Psi}_0 = \left(\otimes_{i=1}^{n_2}\ket{\hat n_{q_i,-,\uparrow}=1}\ket{\hat n_{q_i,-,\downarrow}=1}\right)\ket{\Phi}_\text{cloud}\left(\otimes_{i=1}^{n_2}\ket{\hat n_{q_i,+,\uparrow}=0}\ket{\hat n_{q_i,+,\downarrow}=0}\right)
-\end{aligned}\end{equation}
-\(\ket{\Phi}_\text{cloud}\) will be obtained by diagonalising a small system of \(n_1\) conduction bath \(k\) states.
-This completes the construction of the IR ground state \(\ket{\Psi}_0\).
-The algorithm of reverse RG then involves applying unitary transformations on this IR wavefunction; the unitary transformations will be the inverse of those that were applied during the forward RG algorithm.
-Since the forwards RG transformations decoupled \(k\) states and transformed them into the IOMS, the inverse transformations will take the momentum states in the IOMs and re-entangle them with the impurity+cloud system, one at a time.
-This is shown in fig.~\ref{rev-rg}.
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.4\textwidth]{../figures/reverse-rg.png}
-	\caption{We start with a Hamiltonian with an impurity site (red) coupled with two conduction electrons (dark green), with four other decoupled electrons (bright green).
-The dotted rectangle represents the emergent window \(\left( -\Lambda_j, \Lambda_j \right) \) at each step; the electrons inside that rectangle are still entangled with the impurity, while the ones inside have been decoupled.
-The next step of reverse RG involves applying the inverse transformation on the Hamiltonian, which will couple two more electrons from the IOMS (hence four dark green circles in the second step), leading to an enlargement of the emergent window.
-The unitary varies for each step, hence the notation \(U_j\).}
-	\label{rev-rg}
-\end{figure}
-
-The next step is to write down the unitaries that will take us from the IR ground state to the UV ground state.
-In the forward RG, we used the following unitary for decoupling the shell \(\epsilon_q\) and spin \(\beta\) is
-\begin{equation}\begin{aligned}
-	U_{q\beta} = \frac{1}{\sqrt 2}\left[1 + \eta_{0 \beta} + \eta_{1\beta}^\dagger\right]~.
-\end{aligned}\end{equation}
-Here, the subscripts \(0\) and \(1\) indicate it decouples an electron above and below the Fermi surface respectively. The inverse transformation for re-entangling \(q\beta\) is
-\begin{equation}\begin{aligned}
-	U^\dagger_{q\beta} = \frac{1}{\sqrt 2}\left[1 + \eta_{0 \beta}^\dagger + \eta_{1\beta}\right]~.
-\end{aligned}\end{equation}
-In the \(U>0\) regime, the \(\eta\)s are given by
-\begin{equation}\begin{aligned}
-	\eta_{0\beta}^\dagger = V \left[\frac{1}{d_0}\left( 1 - \hat n_{d\overline\beta} \right) + \frac{1}{d_1}\hat n_{d\overline\beta}  \right]c^\dagger_{q\beta}c_{d\beta} + \frac{1}{d_2}\frac{J}{2}\sum_{k} \left( S_d^z \beta c^\dagger_{q\beta}c_{k\beta} + c^\dagger_{d\overline\beta}c_{d\beta}c^\dagger_{q\beta}c_{k\overline\beta}\right) ~,\\
-	\eta_{1\beta} = V \left[\frac{1}{d_1}\left( 1 - \hat n_{d\overline\beta} \right) + \frac{1}{d_0}\hat n_{d\overline\beta}  \right]c^\dagger_{d\beta}c_{q\beta} + \frac{1}{d_2}\frac{J}{2}\sum_{k} \left( S_d^z \beta c^\dagger_{k\beta}c_{q\beta} + c^\dagger_{d\beta}c_{d\overline\beta}c^\dagger_{k\overline\beta}c_{q\beta}\right)~;
-\end{aligned}\end{equation}
-since \(K\) is irrelevant, we have set \(K=0\) here. The denominators have already been defined in eq.~\eqref{denominators}.
-\begin{equation}\begin{aligned}
-	d_0 = \omega - \frac{D}{2} - \frac{U}{2} + \frac{K}{4}, \quad d_1 = \omega - \frac{D}{2} + \frac{U}{2} + \frac{J}{4}, \quad d_2 = \omega - \frac{D}{2} + \frac{J}{4}, \quad d_3 = \omega - \frac{D}{2} + \frac{K}{4}
-\end{aligned}\end{equation}
-
-The wavefunction after reversing one step of the RG will thus be
-\begin{equation}\begin{aligned}
-	\ket{\Psi}_1 = U^\dagger_{q \uparrow}U^\dagger_{q \downarrow}\ket{\Psi}_0
-\end{aligned}\end{equation}
-Here, \(q\) is the first momentum state immediately outside the emergent cloud.
-Re-entangling further momentum states using their respective unitaries lead to the sequence of wavefunctions \(\ket{\Psi}_2, \ket{\Psi}_3\) and so on.
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/mut_I_ee.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/mut_I_ie.pdf}
-	\caption{\textit{Left}: Mutual information between two conduction electrons inside the cloud.
-\textit{Right}: Mutual information between a conduction electron inside the cloud and an impurity electron.
-Both the measures increase towards the strong coupling fixed point, because of the distillation of the Kondo cloud brought about by the RG flow.}
-	\label{mutI}
-\end{figure}
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/corr_same.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/corr_opp.pdf}
-	\caption{Increase in the diagonal correlation functions between cloud electrons under RG flow towards the strong coupling fixed point.
-This is consistent with the Fermi liquid pieces generated in the \(k-\)space effective Hamiltonian of the Kondo cloud.}
-\end{figure}
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.45\textwidth]{../figures/corr_od.pdf}
-	\caption{Growth of the off-diagonal correlation function between Kondo cloud electrons towards the strong coupling fixed point.
-This is the direct cause of the screening of the impurity spin, and is a reflection of the off-diagonal two-particle scattering terms in the \(k-\)space effective Hamiltonian of the Kondo cloud.}
-\end{figure}
-
-The results of the reverse RG study are depicted in the following plots.
-We have used two types of quantities in the process - mutual information and correlation functions.
-The mutual information between two subsystems \(A\) and \(B\) in a wavefunction with many subsystems is defined as
-\begin{equation}\begin{aligned}
-	I(A: B) = S_A + S_B - S_{AB}
-\end{aligned}\end{equation}
-where \(S_{ij..q}\) is the von-Neumann entropy of the reduced density matrix obtained after tracing out all degrees of freedom except those in the subscript of \(S\).
-
-The mutual information between two electrons inside the entangled cloud increases as we go towards the IR fixed point.
-This can be understood in the following manner; as the wavefunction flows towards a smaller sized emergent cloud, the entanglement between those electrons gets distilled out.
-
-We have also computed some correlation functions.
-All of them increase towards the IR fixed point.
-The increase in the correlation function \(\left<\hat n_{k_1 \uparrow} \hat n_{k_2 \downarrow} \right>\) arises from the crystallization of the spin singlet at the fixed point.
-The increase in the correlation function \(\left<\hat n_{k \uparrow} \hat n_{k \downarrow} \right>\) arises from the charge triplet content of the wavefunction, showing the increase of the charge contribution on the momenta.
-The increase in the off-diagonal correlation function \(\left< c^\dagger_{k \uparrow}c_{k^\prime \downarrow}c^\dagger_{q \downarrow}c_{q^\prime \uparrow}\right>\) shows that the there is a large and non-trivial interaction between the electrons of the cloud that is being mediated by the impurity electron.
-This interaction is not of the Fermi liquid type, but instead was obtained in the effective Hamiltonian for the Kondo cloud.
-
-\chapter{Effect of minimal attractive correlation in the bath}
-\label{siam-attr-chap}
-
-\section{The modified hamiltonian}
-We will include a local particle-hole symmetric correlation of strength \(U_b\) on the origin of the lattice:
-\begin{equation}\begin{aligned}
-	\mathcal{H} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} + \epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
-\end{aligned}\end{equation}
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/zeromode.pdf}
-	\caption{While we have studied the full model under renormalisation group, often we will turn to a simplified zero-bandwidth version of the model that is obtained by ignoring the kinetic energy part of the Hamiltonian.
-This zero-bandwidth model is effectively a two site model.}
-\end{figure}
-
-\section{RG Equations}
-The derivation of the RG equations are shown at the end. \(n_j\) is the number of \(k-\)states at the \(j^\text{th}\) isoenergetic shell. 
-\begin{gather}
-	\Delta U_b = 0, ~ ~\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\left(\frac{J^2}{d_2} - \frac{K^2}{d_3}\right),\\
-	\Delta V = -\frac{3n_j V}{8}\left[\left(J + 4U_b/3\right) \left(\frac{1}{d_2} + \frac{1}{d_1}\right) + \left(K + 4U_b/3\right)\left(\frac{1}{d_3} + \frac{1}{d_0}\right)\right],\\
-	\Delta J = -\frac{n_j J\left(J + 4U_b\right)}{d_2},~ ~\Delta K = -\frac{n_j K\left(K + 4U_b\right)}{d_3}
-\end{gather}
-
-The denominators are
-\begin{equation}\begin{aligned}
-	d_0 = \omega - \frac{D}{2} + \frac{U_b}{2} - \frac{U}{2} + \frac{K}{4}, \quad d_1 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{U}{2} + \frac{J}{4}, \quad d_2 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}, \quad d_3 = \omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}
-\end{aligned}\end{equation}
-
-\paragraph{Important points regarding notation}
-\begin{itemize}
-	\item The labels \(U_0,J_0,V_0\) that may occur in the axes of the plots or anywhere else represent the bare values of the couplings \(U,J\) and \(V\). 
-	\item Throughout the upcoming results, the bare value of \(U_b\) is set to the negative of the bare value of \(U_0\): \(U_b = -U_0/10\).
-This means that whenever we vary \(U_0\) along the axis of a plot, we are simultaneous varying \(U_b\).
-\end{itemize}
-
-\section{Phase diagram}
-
-\begin{center}
-	\includegraphics[width=0.9\textwidth]{../figures/phase-map-MIT.pdf}
-\end{center}
-
-\begin{center}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-phase & RG flow & fixed point & GS & 2-site GS \\ 
-\hline
-blue & \(\Delta U <0, \Delta J,\Delta V>0\) & \(U^* \ll V^* \ll J^*\) & SS & \(\ket{SS}=\ket{\uparrow,\downarrow} - \ket{\downarrow, \uparrow}\)  \\ 
-green &  \(\Delta U < 0, \Delta J < 0,\Delta V>0\) & \(J^* < U^* \ll V^*\) & SS + CT-0 & \(c\ket{SS} + \sqrt{1-c^2}\ket{CT-0}\)  \\  
-red &  \(\Delta U > 0, \Delta J,\Delta V<0\) & \(U^* \gg 1,  V^* = J^* = 0\) & decoupled LM & \(\left\{\ket{\uparrow}, \ket{\downarrow} \right\} \otimes \left\{\ket{0}, \ket{2}\right\} \) \\
-gray &  \(\Delta U, \Delta J,\Delta V < 0\) & \(U^* = V^* = J^* = 0\) & lattice & \(\left\{\ket{\uparrow}, \ket{\downarrow}, \ket{0}, \ket{2} \right\} \otimes \left\{\ket{0}, \ket{2}\right\}\) \\
-\hline
-\end{tabular}
-\end{center}
-
-\section{Evolution of the groundstate across the transition}
-
-\subsection*{Overlap of ground state against spin singlet and charge triplet zero states}
-\begin{center}
-	\includegraphics[width=0.7\textwidth]{../figures/overlaps_gs-J=0.100.pdf}\\
-	\includegraphics[width=0.7\textwidth]{../figures/overlaps_gs-J=10.000.pdf}\\
-	\includegraphics[width=0.7\textwidth]{../figures/overlaps_gs-J=50.000.pdf}
-\end{center}
-
-\subsection*{Spin and charge correlations in ground state}
-\begin{center}
-	\includegraphics[width=0.7\textwidth]{../figures/corrs_gs-J=0.100.pdf}\\
-	\includegraphics[width=0.7\textwidth]{../figures/corrs_gs-J=10.000.pdf}\\
-	\includegraphics[width=0.7\textwidth]{../figures/corrs_gs-J=50.000.pdf}
-\end{center}
-
-\section{Evolution of various correlation measures and other quantities}
-
-\subsection*{Perturbation theoretic terms}
-These quantities are related to the local Fermi liquid of the Kondo strong coupling fixed point and the perturbation theory associated with it.
-\(min(\delta E)\) is the gap in the spectrum of the two-site Hamiltonian; this which acts as the denominator for the perturbation theoretic calculations.
-\(t^2/\delta E\) is the small parameter for the expansion, \(t\) being the tight-binding hopping.
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/gap-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/par-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-\end{center}
-
-\subsection*{Correlation within the Kondo cloud}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-dk-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-diag-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-k-od-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-\end{center}
-
-\subsection*{Mutual information between various real space members}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-01-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/mi-d0-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-\end{center}
-
-\subsection*{Impurity entanglement entropy and spin-spin correlations}
-
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/EE-d-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/corr-d0-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-vec-corr-01-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-\end{center}
-
-\subsection*{Real-space correlations}
-\begin{center}
-	\includegraphics[width=0.32\textwidth]{../figures/r1p-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-od-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/r-opp-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-
-	\includegraphics[width=0.3\textwidth]{../figures/r-par-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-ising-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\includegraphics[width=0.3\textwidth]{../figures/r-charge-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-\end{center}
-
-\section{Presence of sub-dominant pair fluctuations}
-\begin{center}
-	\includegraphics[width=0.4\textwidth]{../figures/odlro-D=1000.00000,t=1.00000,J=30.00000,V=1.50000J,Ub=-Uby10,N=4,U=59.85787,93.55363,25.pdf}
-	\captionof{figure}{Growth of pair fluctuations \(p^\dagger_d p_0\) between the impurity and the zeroth site towards the critical point, \(p^\dagger=c^\dagger_\uparrow c^\dagger_\downarrow\) being the local pair creation operator.
-This comes at the cost of the spin-flip fluctuations \(S_d^+ s_0^- + \text{h.c.}\).
-which decrease towards the transition.}
-	\label{pair_fluc}
-\end{center}
-
-The behaviour of the various kinds of correlation functions (for eg., the reduction of the impurity compensation \(\vec{S}_d\cdot\vec{s}_0\)) shown above indicate that the Kondo cloud that screens the impurity is getting destroyed as \(U_b/J\) increases in magnitude.
-To shed some light on the nature of the fluctuations that faciliate this process, we also plot the average pair fluctuation in the ground state as a function of \(U_b/J\), in fig.~\ref{pair_fluc}.
-The pair fluctuations are terms that transfer an electron pair between the impurity and zeroth sites: \(c^\dagger_{d \uparrow}c^\dagger_{d \downarrow} c_{0 \downarrow}c_{0 \uparrow}\).
-It can be seen from the figure that while the spin-flip fluctuations decrease (since the Kondo cloud is formed out of these spin-flip fluctuations, this is consistent with the destruction of the Kondo cloud discussed in this paragraph), the pair fluctuations pick up.
-Since the spin subspace and charge subspace cannot coincide on the same site, we can then conclude that it is the growth of these pair fluctuations brought about by the presence of the purely local interaction \(U_b\) that make the screening of the impurity spin very poor.
-
-\section{Spectral functions}
-
-\subsection{Impurity spectral function \(A_{dd}(\omega)\)}
-These are the frequency-domain spectral functions for the retarded propagator \(-i\theta(t)\left<\left\{c_{d\sigma}(t),c^\dagger_{d\sigma}\right\}  \right>\):
-\begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.100.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.145.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.188.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.250.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_Ub_by_J=-0.26.pdf}
-\end{center}
-
-\subsection{Impurity-bath off-diagonal spectral function \(A_{dz}(\omega)\)}
-These are the frequency-domain spectral functions for the off-diagonal retarded propagator \(-i\theta(t)\left<\left\{c_{d\sigma}(t),c^\dagger_{0\sigma}\right\}  \right>\):
-\begin{center}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.100.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.145.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.188.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.250.pdf}
-	\includegraphics[width=0.45\textwidth]{../figures/spec_func_d0_Ub_by_J=-0.26.pdf}
-\end{center}
-
-\subsection{Bath spectral function \(A_{00}(\omega)\)}
-In order to calculate the spectral function \(A_{00}(\omega)\) of the site connected to the impurity (referred to as the zeroth site), we will use the following strategy.
-We will decouple the impurity states from the fixed point Hamiltonian using a single URG transformation.
-This will of course generate correlations on the zeroth site.
-The resulting Hamiltonian will be an Anderson impurity model with the hopping between the zeroth site and the rest of the chain acting as the effective hybridisation.
-Schematically, we will have
-\begin{equation}\begin{aligned}
-	H^* = H_\text{imp} + V_\text{imp-0} + H_\text{0} + H_\text{0-1} + H_\text{rest} ~ \mathlarger{\xrightarrow{\text{decouple imp.}}} ~ E_\text{imp} + \tilde H_\text{0} + H_\text{0-1} + H_\text{rest} = H_\text{new imp} \\
-	+ V_\text{new imp - rest} + H_\text{rest}
-\end{aligned}\end{equation}
-
-Since the impurity is not coupled with any site beyond the zeroth site, the parts of the Hamiltonian that involve "rest" will not change in the process.
-This also means that the decoupling can be performed by looking at the smaller Hamiltonian
-\begin{equation}\begin{aligned}
-	H_\text{imp+0} = H_\text{imp} + H_\text{0} + V_\text{imp-0} = -\frac{U^*}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right)^2 - U_b \left( \hat n_{0 \uparrow} - \hat n_{0 \downarrow} \right)^2 + J^*S_d^z S_0^z + {V^*}\sum_\sigma \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) \\
-	+ \frac{J^*}{2}\left( c^\dagger_{d \uparrow}c_{d \downarrow} c^\dagger_{0 \downarrow} c_{0 \uparrow} + \text{h.c.} \right) 
-\end{aligned}\end{equation}
-
-\paragraph{Renormalisation from \({V^*}\)}
-From the off-diagonal term involving \({V^*}\), we generate the following term, in the particle sector for \(0\):
-\begin{equation}\begin{aligned}
-	{V^*} \sum_\sigma c^\dagger_{0\sigma}c_{d\sigma} \frac{1}{\tilde \omega - H_d} {V^*} c^\dagger_{d\sigma}c_{0\sigma} = |V^*|^2 \sum_\sigma c^\dagger_{0\sigma}c_{d\sigma} \frac{1}{\tilde \omega + \frac{U^*}{2}\left( 1 - \hat n_{d\bar\sigma} \right)^2 + U_b \hat n_{0\bar\sigma} + \frac{J^*}{4}\left( 1 - \hat n_{d\bar\sigma} \right) \hat n_{0\bar\sigma} } c^\dagger_{d\sigma}c_{0\sigma}
-\end{aligned}\end{equation}
-where \(\tilde \omega\) is the quantum fluctuation operator for the impurity site and \(H_d = -\frac{U^*}{2}\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right)^2 - U_b \left( \hat n_{0 \uparrow} - \hat n_{0 \downarrow} \right)^2 + J^*S_d^z S_0^z \), is the diagonal part of the Hamiltonian for the imp+0 system.
-In order to resolve the operators in the denominator, we expand the unity in the numerator using the identity \(1 = \hat n_{d\bar\sigma}\hat n_{0\bar\sigma} + \hat n_{d\bar\sigma}\hat h_{0\bar\sigma} + \hat h_{d\bar\sigma}\hat n_{0\bar\sigma} + \hat h_{d\bar\sigma}\hat h_{0\bar\sigma}\), where \(\hat h = 1 - \hat n\) is hole operator.
-On Substituting this, we get
-\begin{equation}\begin{aligned}
-	\sum_\sigma {V^*} c^\dagger_{0\sigma}c_{d\sigma} \frac{1}{\tilde \omega - H_d} {V^*} c^\dagger_{d\sigma}c_{0\sigma} &= |V^*|^2 \sum_\sigma c^\dagger_{0\sigma}c_{d\sigma} \frac{\hat h_{d\bar\sigma}\hat h_{0\bar\sigma} + \hat h_{d\bar\sigma}\hat n_{0\bar\sigma} + \hat n_{d\bar\sigma}\hat h_{0\bar\sigma} + \hat n_{d\bar\sigma}\hat n_{0\bar\sigma}}{\tilde \omega + \frac{U^*}{2}\hat h_{d\bar\sigma} + U_b \hat n_{0\bar\sigma} + \frac{J^*}{4}\hat h_{d\bar\sigma} \hat n_{0\bar\sigma} } c^\dagger_{d\sigma}c_{0\sigma}\\
-															    &= |V^*|^2 \sum_\sigma \hat h_{d\sigma} \hat n_{0\sigma}\left[\frac{\hat h_{d\bar\sigma}\hat h_{0\bar\sigma}}{\tilde\omega_{00} + \frac{U^*}{2}} + \frac{\hat h_{d\bar\sigma}\hat n_{0\bar\sigma}}{\tilde\omega_{01} + \frac{U^*}{2} + U_b + \frac{J^*}{4}} + \frac{\hat n_{d\bar\sigma}\hat h_{0\bar\sigma}}{\tilde\omega_{10}} + \frac{\hat n_{d\bar\sigma}\hat n_{0\bar\sigma}}{\tilde\omega_{11} + U_b}\right]
-\end{aligned}\end{equation}
-\(\tilde\omega_{(0,1),(0,1)}\) represents the quantum fluctuation scale corresponding to the configuration in the numerator.
-
-In order to "freeze" the impurity dynamics, we will substitute \(\hat n_{d\sigma} = \hat n_{d\bar\sigma} = \frac{1}{2}\), because of the \(\mathbb{Z}_2\) symmetry and the particle-hole symmetry of the impurity levels.
-This gives
-\begin{equation}\begin{aligned}
-	\frac{1}{4}|V^*|^2 \sum_\sigma \hat n_{0\sigma} \left[\frac{\hat h_{0\bar\sigma}}{\tilde\omega_{00} + \frac{U^*}{2}} + \frac{\hat n_{0\bar\sigma}}{\tilde\omega_{01} + \frac{U^*}{2} + U_b + \frac{J^*}{4}} + \frac{\hat h_{0\bar\sigma}}{\tilde\omega_{10}} + \frac{\hat n_{0\bar\sigma}}{\tilde\omega_{11} + U_b}\right]
-\end{aligned}\end{equation}
-
-The state that most closely represents the metallic ground state is \(\bar \omega_{10}\), we take that as the reference quantum fluctuation scale \(\bar\omega\).
-It is of the order of \(\bar\omega \sim -\frac{J^*}{4} - \frac{U^*}{2} - U_b\).
-We will now relate the other scales to \(\bar\omega\) by expressing them in terms of the energy of the initial state:
-\begin{equation}\begin{aligned}
-	\tilde\omega_{00} \sim -U_b = \bar\omega + \frac{J^*}{4} + \frac{U^*}{2}, ~~ \tilde\omega_{01} \sim 0 = \bar\omega + \frac{J^*}{4} + \frac{U^*}{2} + U_b, ~~ \tilde\omega_{11} \sim -\frac{U^*}{2} = \bar\omega + \frac{J^*}{4} + U_b
-\end{aligned}\end{equation}
-Substituting these gives
-\begin{equation}\begin{aligned}
-	\frac{1}{4}|V^*|^2 \sum_\sigma \hat n_{0\sigma} \left[\hat h_{0\bar\sigma}\alpha_1 + \hat n_{0\bar\sigma}\alpha_2\right]
-\end{aligned}\end{equation}
-where \(\alpha_1 = \left(\bar\omega + U^* + \frac{J^*}{4}\right)^{-1} + \left(\bar\omega\right)^{-1}\) and \(\alpha_2 = \left(\bar\omega + U^* + 2U_b + \frac{J^*}{2}\right)^{-1} + \left(\bar\omega + 2U_b + \frac{J^*}{4}\right)^{-1}\).
-
-Because of the particle-hole symmetry on the impurity as well as in the bath, the renormalisation from the hole sector is obtained simply by transforming \(\hat n \leftrightarrow \hat h\):
-\begin{equation}\begin{aligned}
-	\frac{1}{4}|V^*|^2 \sum_\sigma \hat h_{0\sigma} \left[\hat n_{0\bar\sigma}\alpha_1 + \hat h_{0\bar\sigma}\alpha_2\right]
-\end{aligned}\end{equation}
-
-The total renormalisation arising from \(V\) is therefore
-\begin{equation}\begin{aligned}
-	\frac{1}{4}|V^*|^2 \sum_\sigma \left[\alpha_1 \left( \hat n_{0\sigma}\hat h_{0\bar\sigma} + \hat h_{0\sigma}\hat n_{0\bar\sigma}\right) + \alpha_2 \left( \hat n_{0\sigma}\hat n_{0\bar\sigma} + \hat h_{0\sigma}\hat h_{0\bar\sigma}\right)\right] = \frac{1}{2}|V*|^2 \left(\alpha_1 - \alpha_2\right) \left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2 + \text{constant}
-\end{aligned}\end{equation}
-
-\paragraph{Renormalisation from \(J\)}
-The renormalisation arising from decoupling the Kondo coupling has two terms. The first term arises when the spin of the zeroth site is initially up:
-\begin{equation}\begin{aligned}
-	\frac{{J^*}^2}{4}c^\dagger_{d \downarrow}c_{d \uparrow} c^\dagger_{0 \uparrow}c_{0 \downarrow} \frac{1}{\tilde \omega - H_d} c^\dagger_{0 \downarrow}c_{0 \uparrow} c^\dagger_{d \uparrow}c_{d \downarrow} = c^\dagger_{d \downarrow}c_{d \uparrow} c^\dagger_{0 \uparrow}c_{0 \downarrow} \frac{{J^*}^2/4}{\tilde \omega + \frac{U^*}{2} + U_b + \frac{J^*}{4}} c^\dagger_{0 \downarrow}c_{0 \uparrow} c^\dagger_{d \uparrow}c_{d \downarrow} = \frac{{J^*}^2}{4}\frac{\hat n_{d \downarrow} \hat h_{d \uparrow} \hat n_{ 0 \uparrow} \hat h_{0 \downarrow}}{\tilde \omega + \frac{U^*}{2} + U_b + \frac{J^*}{4}}
-\end{aligned}\end{equation}
-The quantum fluctuation scale \(\tilde \omega\) for this process can be similarly related to \(\bar\omega\): \(\tilde\omega \sim -\frac{U^*}{2} - U_b - \frac{J^*}{4} = \bar\omega\). This gives
-\begin{equation}\begin{aligned}
-	\frac{{J^*}^2}{4}\frac{\hat n_{d \downarrow} \hat h_{d \uparrow} \hat n_{ 0 \uparrow} \hat h_{0 \downarrow}}{\bar\omega + \frac{U^*}{2} + U_b + \frac{3J^*}{4}} = \frac{{J^*}^2}{16}\frac{\hat n_{ 0 \uparrow} \hat h_{0 \downarrow}}{\bar\omega + \frac{U^*}{2} + U_b + \frac{J^*}{4}}
-\end{aligned}\end{equation}
-as the renormalisation for this configuration.
-At the final step, we substituted \(\hat n_{d\sigma} = \hat h_{d\sigma} = \frac{1}{2}\).
-For the other configuration where the spin of the zeroth site is down, we get
-\begin{equation}\begin{aligned}
-	\frac{{J^*}^2}{16}\frac{\hat n_{ 0 \downarrow} \hat h_{0 \uparrow}}{\bar\omega + \frac{U^*}{2} + U_b + \frac{J^*}{4}}
-\end{aligned}\end{equation}
-Adding both sectors, we get
-\begin{equation}\begin{aligned}
-	\frac{{J^*}^2}{16}\frac{1}{\bar\omega + \frac{U^*}{2} + U_b + \frac{J^*}{4}} \left(\hat n_{ 0\uparrow} - \hat n_{0 \downarrow}\right)^2
-\end{aligned}\end{equation}
-
-\paragraph{Total renormalisation}
-Adding the contributions from both \(V^*\) and \(J^*\),  the net renormalisation is the generation of a local correlation term \(-U_0\left(\hat n_{ 0\uparrow} - \hat n_{0 \downarrow}\right)^2\) on the zeroth site, where \(U_0\) is given by
-\begin{equation}\begin{aligned}
-	U_0 = -\frac{{J^*}^2}{16}\frac{1}{\bar\omega + \frac{U^*}{2} + U_b + \frac{J^*}{4}} - \frac{1}{2}|V^*|^2\left(\frac{1}{\bar\omega + U^* + \frac{J^*}{4}} + \frac{1}{\bar\omega} - \frac{1}{\bar\omega + U^* + 2U_b + \frac{J^*}{2}} - \frac{1}{\bar\omega + 2U_b + \frac{J^*}{4}}\right)
-\end{aligned}\end{equation}
-
-Deep in the metallic regime, we have the following hierarchy of energy scales: \(|J^*| > |\bar\omega| \gg |V^*| \gg |U_b| \gg |U^*| \simeq 0\).
-
-\subsection{Width of central peak of \(A_{dd}\)}
-
-\begin{center}
-\includegraphics[width=0.45\textwidth]{../figures/spec_func_width_fit.pdf}
-\end{center}
-
-\section{What, then, are the minimal ingredients for a metal-insulator transition?}
-We now return to the question posed at the very beginning in section~\ref{sec:min_model}: What is the minimal auxiliary model that can demonstrate a metal-insulator transition in the bulk?
-To answer this question, we first recall all the relevant RG equations in the positive \(U\) regime:
-\begin{gather}
-	\Delta U_b = 0, ~ ~\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) - n_j\frac{J^2}{d_2},\\
-	\Delta V = -\frac{3n_j V}{8}\left[\left(J + 4U_b/3\right) \left(\frac{1}{d_2} + \frac{1}{d_1}\right) + 4U_b/3\left(\frac{1}{d_3} + \frac{1}{d_0}\right)\right],\\
-	\Delta J = -\frac{n_j J\left(J + 4U_b\right)}{d_2}~.
-\end{gather}
-where \(d_1 > d_2 > d_3 > d_0\).
-We now consider various models with increasing number of parameters.
-
-\subsection{Only impurity correlation and hybridisation \(U,V\)}
-If we had only \(U\) and \(V\), the RG equations simplify to
-\begin{equation}\begin{aligned}
-	\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) < 0,~ ~ ~\Delta V = 0
-\end{aligned}\end{equation}
-\(U\) is irrelevant while the hybridisation \(V\) is marginal, so the fixed point is where the impurity is screened. The bulk model will always be metallic. There is no transition in such a model.
-
-\subsection{Impurity correlation, hybridisation and spin-exchange between impurity and bath \(U,V,J\)}
-If we now add a spin-exchange coupling \(J\) between the impurity and the bath into the Hamiltonian, we obtain the generalised SIAM studied in chapter~\ref{chap:urg1}.
-As discussed in that chapter, this is again similar to the previous case - the only stable fixed point is one of strong-coupling, and the bulk metal will never have an insulating phase.
-
-\subsection{Impurity correlation, hybridisation and local pairing interaction on the bath \(U,V,U_b\)}
-If we replace the \(J\) with an local interaction \(U_b\) on the bath, the RG equations undergo some changes:
-\begin{gather}
-	\Delta U_b = 0, ~ ~\Delta U = 4V^2 n_j\left(\frac{1}{d_1} - \frac{1}{d_0}\right) = \frac{4V^2U}{\left(\omega - D/2 + U_b/2\right)^2 - U^2/4},\\
-	\Delta V = -n_j V U_b\left[\frac{\omega - D/2 + U_b/2}{\left(\omega - D/2 + U_b/2\right)^2 - U^2/4} + \frac{1}{\omega - D/2 + U_b/2}\right]~.
-\end{gather}
-This regime is interesting because it shows a variety of behaviour:
-\begin{itemize}
-	\item For \(U_b>0\), the correlation \(U\) is irrelevant and \(V\) is relevant. This will produce a metal (see fig.~\ref{noJ_Ub_gt_0}).
-	\item For \(U_b<0\), both \(U\) and \(V\) are irrelevant, but \(V\) decays much faster than \(U\), and \(U\) saturates to a non-zero appreciable value which although lower than the bare value is much greater than 0 (see fig.~\ref{noJ_Ub_lt_0}).
-This behaviour is enhanced by making \(U_b\) more negative; \(V\) decays even faster to zero, while \(U\) saturates at higher values.
-If the bare bandwidth is increased, the fixed point value of \(U\) actually decreases, so it appears that on taking the thermodynamic limit, \(U\) renormalises to zero (see fig.~\ref{noJ_Ub_lt_0_D}).
-\end{itemize}
-
-Neither of these cases give rise to an insulator, because \(U\) never renormalises to a non-zero fixed point value in the thermodynamic limit.
-
-\begin{center}
-	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=0.05_D=10_U.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=0.05_D=10_V.pdf}
-	\captionof{figure}{RG flows of \(U\) (left panel) and \(V\) (right panel) in the regime \(U_b>0\), for the auxiliary model with \(U,V,U_b\).
-The impurity correlation \(U\) is irrelevant while the hybridisation \(V\) is relevant, leading to a metallic phase in the bulk.}
-	\label{noJ_Ub_gt_0}
-
-	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=-0.10_D=10_U.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=-0.10_D=10_V.pdf}
-	\captionof{figure}{RG flows of \(U\) (left panel) and \(V\) (right panel) in the regime \(U_b<0\), for the auxiliary model with \(U,V,U_b\).
-The hybridisation \(V\) is sharply irrelevant, renormalising to zero, while the impurity correlation \(U\) survives at the fixed point.}
-	\label{noJ_Ub_lt_0}
-
-	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=-0.10_D=100_U.pdf}
-	\includegraphics[width=0.4\textwidth]{../figures/no_J_Ub=-0.10_D=100_V.pdf}
-	\captionof{figure}{RG flows of \(U\) and \(V\) in the regime \(U_b<0\) at a larger bandwidth, for the auxiliary model with \(U,V,U_b\).
-\(U\) now renormalises to zero, so an insulator is not possible in the thermodynamic limit.}
-	\label{noJ_Ub_lt_0_D}
-\end{center}
-
-\subsection{Attractive correlation \(U_b\) instead of \(V\): \(U,J,U_b\)}
-In the presence of these three couplings, the RG equations become
-\begin{equation}\begin{aligned}
-	\Delta U = -n_j J^2/d_2,~ ~ ~ \Delta J = -n_j J(J+4U_b)/d_2
-\end{aligned}\end{equation}
-Since \(J > 0\), \(\Delta U\) is always positive, so \(U\) is always relevant.
-For \(4U_b > -J\), \(\Delta J\) is also positive, and \(J\) is relevant.
-We end up in a metallic phase.
-However, for \(4U_b < -J\), \(J\) becomes irrelevant, and the fixed point is that of a local moment decoupled from the bath, which describes an insulating state in the bulk.
-
-\subsection{The full model?}
-We are therefore ultimately led to a model with all four parameters.
-This was studied in chapter~\ref{siam-attr-chap}, and was shown to display both metallic and insulating phases.
-This makes it clear that {\it the minimal model must have all three kinds of correlation: magnetic \((U,J)\), delocalisation \((V)\) and pair formation \((U_b)\)}.
+\chapter{Properties of the Bloch states}
+To determine this, we compute the norm of the trail eigenstates:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k} | \Psi_{\vec k}} &= \frac{1}{\mathcal{W}^2 \lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, a, a^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime, \vec a^\prime) | \psi_\text{aux}(\vec R, \vec a)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, }e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime) | \psi_\text{aux}(\vec R)}\\
+					       &=\frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) | \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)}\\
+					       &= \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i (\vec{k} - \vec q)\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{q} N^2 \delta_{\vec{k},\vec q}|\braket{\psi_\text{aux}(\vec R_0) | \vec q}|^2\\
+\end{aligned}\end{equation}
+By requiring this norm to be unity, we obtain \(\lambda_{\vec k}^2 = |\braket{\psi_\text{aux}(\vec R_0) | \vec k}|^2\). In the above exercise, we defined a state 
+\begin{equation}\begin{aligned}\label{zeroth_site_average}
+	\ket{\psi_\text{aux}(\vec R)} = (1/w)\sum_{\vec a}\ket{\psi_\text{aux}(\vec R, \vec a)}~,
+\end{aligned}\end{equation}
+by averaging over the neasest neighbours of \(\vec R\), and inserted the total momentum basis \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators.
+\(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
+Because of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(\mathcal{W}\) choices.
+
+It is easy to verify that \(\Psi_{\vec k}\left(\left\{ \vec r_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \(\vec R\):
+\begin{equation}\begin{aligned}
+	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
+\end{aligned}\end{equation}
+In the last equation, we transformed \(\vec R_i \to \vec R_j = \vec R_i - \vec R\).
+Note that the argument \(\vec a\) does not change under a translation of the system, because that vector always represents the difference between the impurity lattice position and its nearest neighbours, irrespective of the absolute position of the impurity.
+
+The wavefunction can be even brought into the familiar Bloch function form:
+\begin{equation}\begin{aligned}
+	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} \mathcal{W} N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
+	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
+\end{aligned}\end{equation}
+where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
+This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
+
+It is straightforward to show that these states form an orthonormal basis. We start by writing down the inner product of two distinct such states:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+\end{aligned}\end{equation}
+At this point, we insert a complete basis of momentum eigenkets \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
+						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+\end{aligned}\end{equation}
+At the last step, we used the summation form of the Kronecker delta function: \(\sum_{\vec R_i}e^{i \vec R_i \left( \vec k - \vec q \right) }\sum_{\vec R_j}e^{i \vec R_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\).
+The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \(\vec a, \vec a^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\ket{\vec k}}\):
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
+\end{aligned}\end{equation}
+This concludes the proof of orthonormality.
+
+To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
+\begin{equation}\begin{aligned}
+	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}
+\end{aligned}\end{equation}
+To resolve the translation operators, we will now insert the momentum eigenstates \(\ket{\vec k}\) of the full model: \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) in between the operators.
+\begin{equation}\begin{aligned}
+	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
+	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}
+\end{aligned}\end{equation}
+The momentum eigenket \(\ket{\vec k}\) can be expressed as a sum over position eigenkets at varying distances from \(\vec R_0\).
+This form allows a systematic method of improving the energy eigenvalue estimate, because the interacting in the impurity model is extremely localised, so the overlap between two auxiliary models decreases rapidly with distance.
+The majority of the contribution will come from the state at \(\vec R_0\), and improvements are then made by considering auxiliary models at further distances.
 

### 2023-03-08 notes/notes.tex
added correlation functions

@@
 
-\section{Single-particle Green's function}
+\section{Mapping greens functions from the bulk to the auxiliary model}
 In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{aux}}\) of the auxiliary models.
@@
 Moreover, this approach holds for any \(n-\)-particle Greens function; we just need to compute the corresponding correlator in the auxiliary model.
+
+A particular example of this relation between the Greens functions is the following: static correlation functions of the form \(\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger \mathcal{O}_2 | \Psi_\text{gs}}\) can be written in terms of auxiliary model correlations:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} \simeq \frac{1}{\lambda_{\vec k_0}^2}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1^\dagger(d) \mathcal{O}_2(d) | \psi_\text{aux}(\vec R_0, \vec a)}\\
+	\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} \simeq \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1^\dagger(z) \mathcal{O}_2(d) | \psi_\text{aux}(\vec R_0, \vec a)}~,
+\end{aligned}\end{equation}
+where \(\mathcal{O}_{1,2}\) are operators that describe the correlation we are computing, and the arguments \((d)\) and \((z)\) indicate that the corresponding operator acts at the impurity site and the bath zeroth site respectively.
 

### 2023-03-09 notes/notes.tex
obtained an intiial form of Adz

@@
 \appendixtitleon
-
-\chapter{Derivation of RG equations for the impurity model with \(U,V,J,K,U_b,\eta\)}
-
-\section{The Hamiltonian}
-
-The Hamiltonian for the impurity problem is
-\begin{equation}\begin{aligned}
-	\mathcal{H} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{1}{2} U \left( \tau_{d \uparrow} - \tau_{d \downarrow} \right) ^2 + \frac{1}{2}\eta \left(\tau_{d \uparrow} + \tau_{d \downarrow}\right) + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} + K \vec{C}_d\cdot\vec{C} - U_b\left(\tau_{0 \uparrow} - \tau_{0 \downarrow}\right)^2
-\end{aligned}\end{equation}
-wher \(\tau \equiv \hat n -\frac{1}{2}\).
-The first term is the kinetic energy term with a dispersion \(\epsilon_k\).
-The second term is the particle-hole symmetric impurity correlation term that sets the uncorrelated half-filled level \(\tau_{d\uparrow} = - \tau_{d \downarrow} = \pm \frac{1}{2}\) at energy \(-U/2\) below the Fermi surface, and the correlated doublon and holon states \(\tau_{d\downarrow} = \tau_{d \uparrow} = \pm \frac{1}{2}\) at the Fermi surface.
-The particle-hole symmetry is in the fact that the term is invariant under \(\tau_{d\sigma} \to-\tau_{d\sigma}\), and manifests in the symmetric positioning of the doublon and holon levels with respect to each other.
-The third term is the particle-hole asymmetry term that explicitly measures the deviation away from particle-hole symmetry - it is non-zero only when we are away from half-filling.
-The fourth, fifth and sixth terms describe various mechanisms in which the impurity can hybridise with the conduction bath.
-The first of these is a single-particle hopping \(V\), the second mechanism is through spin-flip scattering, and the third is through isospin-flip scattering.
-The single-particle hybridisation \(V\) allows the impurity electron to tunnel into the conduction bath and this leads to a frequency-dependent self-energy renormalisation of the impurity, implying that the impurity electron can spend  large amount of time in the bath~\cite{coleman2015}.
-\(\vec S_d = \frac{1}{2}\sum_{\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{d\alpha}c_{d\beta} \) is the impurity spin, while \(\vec C_d = \frac{1}{2}\sum_{\alpha\beta} \psi^\dagger_\alpha \vec \sigma_{\alpha\beta}\psi_\beta\) is the impurity isospin, where \(\psi = \left(c_{d\uparrow} ~ ~ ~ ~ c^\dagger_{d \downarrow}\right)\)~
-\cite{anderson1958random,nambu_1960}.
-The former acts on the \(2-\)dimensional Hilbert-space formed by the magnetic up and down states on the impurity, while the latter acts on the \(2-\)dimensional space formed by the doublon and holon states.
-The former reacts to a magnetic field, while the latter responds to a chemical potential.
-Such a chemical potential term that couples with the isospin is already present in the Hamiltonian - it is the assymetry term \(\eta\).
-In fact, that term can be rewritten as \(\eta C_d^z\), because \(C^z_d = \frac{1}{2}\left(\hat n_{d \uparrow} + \hat n_{d \downarrow} - 1\right) = \frac{1}{2}\left( \tau_{d \uparrow} + \tau_{d \downarrow} \right) \).
-The bath operators \(\vec s\) and \(\vec C\) are defined in the same way as the operator counterparts: \(\vec s = \sum_{kk^\prime\alpha\beta}\vec \sigma_{\alpha\beta}c^\dagger_{k\alpha}c_{k^\prime\beta}, \vec C = \sum_{kk^\prime\alpha\beta}{\psi^k}^\dagger_\alpha\vec\sigma_{\alpha\beta}\psi^{k^\prime}_\beta\), where \(\psi^k = \left(c_{k\alpha} ~ ~ ~ ~ c^\dagger_{k^\prime\beta}\right) \).
-The final seventh term is a local particle-hole symmetric correlation on the zeroth site of the bath.
-For \(U_b>0\), this term promotes half-filling on the zeroth site, while for \(U_b<0\), a doublon or holon is more favourable on that site.
-
-We first Fourier transform the \(U_b\)-term to \(k-\)space.
-In \(k-\)space, the diagonal contribution (to \(H_D\)) coming from this term is the single-particle self-energy \(-U_b\left(\hat n_{q \beta}\right)^2\) which can be made particle-hole symmetric in the form:
-\begin{equation}\begin{aligned}
-	-U_b\left(\tau_{q \beta}\right)^2
-\end{aligned}\end{equation}
-where \(q\) is the \(k-\)state being decoupled and \(\tau \equiv \hat n - 1/2\).
-In the initial state \(\ket{\Psi}_i\), we have \(\langle \hat n_{q\beta} \rangle = 1/2 \implies \tau_{q\beta} = 0\), so the contribution of \(U_b\) to that state is 0.
-For both hole excitations \(c_{q\beta}\ket{\Psi}_i\) as well as particle excitations \(c^\dagger_{q\beta}\ket{\Psi}_i\), the intermediate state energy lowers to \(-U_b/4\).
-
-The off-diagonal part is
-\begin{equation}\begin{aligned}
-	-\frac{U_b}{2}\sum_{kk^\prime\sigma}c^\dagger_{k\sigma}c_{k^\prime\sigma} + U_b \sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_1 \uparrow}c_{k_2 \uparrow} c^\dagger_{k^\prime_1 \downarrow}c_{k^\prime_2 \downarrow}
-\end{aligned}\end{equation}
-We ignore the potential scattering arising from the first term.
-
-\section{Renormalisation of the impurity energy levels}
-A single site has four degrees of freedom arising from the spin-degeneracy, and can be represented by the Hamiltonian
-\begin{equation}\begin{aligned}
-	H = \epsilon_0 \ket{0}\bra{0} + \epsilon_1 \sum_\sigma\ket{\sigma}\bra{\sigma} + \epsilon_2 \ket{2}\bra{2}
-\end{aligned}\end{equation}
-\(\ket{0},\ket{2}\) are the holon and doublon states, while \(\ket{\sigma}\) is the state where the site is singly-occupied by a particle of spin \(\sigma\).
-We will obtain the renormalisation to the energy levels \(\epsilon_0,\epsilon_1\) and \(\epsilon_2\), and thereby calculate the renormalisation in \(U\) and \(\eta\).
-This can be done by noting that \(\epsilon_1 = -\frac{U}{2}\), and \(\epsilon_2 = \eta\).
-A qualifier is, however, needed here.
-In the bare Hamiltonian, the energies of the doublon and holon states are negatives of each other, and this would correspond to requiring \(\epsilon_2 = -\epsilon_0\).
-This may not hold true under renormalisation, and the way we account for this is that at each step of the RG, we subtract a constant energy from the Hamiltonian so as to set the energy of the holon state to 0.
-This means that the energy of the singly-occupied and doublon states become \(\epsilon_1 - \epsilon_0\) and \(\epsilon_2 - \epsilon_0\).
-And since we have identified \(\epsilon_1\) and \(\epsilon_2\) as \(-\frac{U}{2}\) and \(\eta\) respectively, we can use \(\Delta U = -2\left(\Delta \epsilon_1 - \Delta \epsilon_0\right), \Delta \eta = \Delta \epsilon_2 - \Delta \epsilon_0 \).
-
-We need to look at three kinds of scattering vertices here: \(V^2\), \(J^2\) and \(K^2\).
-We will consider these processes one after another.
-We define \(n_j\) as the number of states being decoupled on each side of the Fermi surface, at the \(j^\text{th}\) RG step.
-In order to treat both spin and isospin exchanges democratically, we take \(\ket{\Psi}_i = \frac{1}{2}\left(\ket{0} + \ket{q\uparrow} + \ket{q\downarrow} + \ket{q\uparrow, q\downarrow}\right) \) as the \textit{initial} state for the scattering processes.
-The intermediate states \(\ket{\Psi}_\text{int}\) in the particle sector \(\left(c_{q\beta}\ket{\Psi}_i\right)\) and hole sector \(\left(c^\dagger_{q\beta}\ket{\Psi}_i\right)\) will then have both spin and isospin excitations which can couple with the corresponding impurity degree of freedom.
-We will assume that states  \(q > k_F~\left(\epsilon_q > 0\right) \) above the Fermi surface can have only particle excitations and states below the Fermi surface can only have hole excitations.
-The kinetic energy part \(\epsilon_q \tau_{q\beta}\) of \(H_D\) for \(\ket{\Psi}_i\) is then zero, whereas it is always \(D/2\) for \(\ket{\Psi}_\text{int}\).
-To demonstrate this for a typical \(q < k_F\), the hole excitation is \(c_{q \uparrow}\ket{\Psi}_i = \frac{1}{\sqrt 2}\left(\ket{0} + \ket{q \downarrow}\right)\).
-This has an isospin term in the form of the \textit{holon} and a spin term in the form of the down state.
-Since \(\tau_{q \uparrow} = -\frac{1}{2}\) in the excited state, the kinetic energy for \(\ket{\Psi}_\text{int}\) is \(\epsilon_q \tau_{q \uparrow} = \left(-D\right)\times\left(-\frac{1}{2}\right) = D/2\).
-
-The renormalisation arising from the first kind of terms, in the particle sector, is
-\begin{equation}\begin{aligned}
-	\sum_{q\beta}c^\dagger_{q\beta}c_{d\beta}\frac{V^2}{\omega - H_D}c^\dagger_{d\beta}c_{q\beta} = \sum_{q\beta}V^2 \hat n_{q\beta} \left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega - E_0} + \frac{\hat n_{d \overline\beta}}{\omega^\prime - E_1}\right) = V^2 n_j\sum_{\beta}\left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega_0 - E_0} + \frac{\hat n_{d \overline\beta}}{\omega_1 - E_1}\right)
-\end{aligned}\end{equation}
-\(q\) runs over the momentum states that are being decoupled at this RG step: \(|q| = \Lambda_j\).
-\(E_{1,0}\) are the diagonal parts of the Hamiltonian at \(\hat n_{d\overline \beta}=1,0\) respectively.
-We have \(\hat n_{d\beta}=1\) in the intermediate state because of the \(c^\dagger_{d\beta}\) in front of the Greens function.
-Applying \(c_{q\beta}\) on the initial state \(\ket{\Psi}_i\) leaves us with \(C^z_q = - \frac{1}{2}\) and \(s^z_q = \frac{1}{2}\overline\beta\).
-We also know that
-\begin{equation}\begin{aligned}
-	\hat n_{d\beta}=1,
-	\begin{cases}
-		\hat n_{d\overline\beta}=0 &\implies S_d^z = \frac{1}{2}\beta, C_d^z = 0, \epsilon_d\left(\hat n_{d\uparrow} - \hat n_{d \downarrow}\right)^2 = \epsilon_d\\	
-		\hat n_{d\overline\beta}=1 &\implies S_d^z = 0, C_d^z = \frac{1}{2}, \epsilon_d\left(\hat n_{d\uparrow} - \hat n_{d \downarrow}\right)^2 = 0
-	\end{cases}
-\end{aligned}\end{equation}
-Combining all this, we can write \(E_1 = \frac{D}{2} - \frac{K}{4}\) and \(E_0 = \frac{D}{2} + \epsilon_d - \frac{J}{4}\).
-In order to relate \(\omega_0\) with \(\omega_1\) with the common fluctuation scale \(\omega\) for the conduction electrons, we will replace these quantum fluctuation scales by the current renormalised values of the single-particle self-energy for the initial state from which we started scattering.
-For \(\hat n_{d\overline\beta}=0\), there is no additional self-energy because the impurity does not have any spin: \(\omega_0 = \omega\).
-For \(\hat n_{d\overline\beta} = 1\), we have an additional self-energy of \(\epsilon_d\) arising from the correlation on the impurity: \(\omega_1 = \omega + \epsilon_d\).
-Substituting the values of \(E_{0,1}\) and \(\omega_{0,1}\), we get
-\begin{equation}\begin{aligned}
-	\label{ren_ed_Vp}
-	V^2 n_j\sum_{\beta}\left( 1 - \hat n_{d\beta} \right)\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)
-\end{aligned}\end{equation}
-Performing a similar calculation for the hole sector gives the contribution:
-\begin{equation}\begin{aligned}
-	\label{ren_ed_Vh}
-	V^2 n_j\sum_{\beta}\hat n_{d\beta}\left( \frac{1-\hat n_{d \overline\beta }}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} + \frac{\hat n_{d \overline\beta}}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right)
-\end{aligned}\end{equation}
-We now come to the second type of terms: spin-spin. We first look at the particle sector:
-\begin{equation}\begin{aligned}
-	\label{ren_ed_Jpp}
-	\frac{J^2}{4}\sum_{q\beta}c^\dagger_{d\overline\beta}c_{d\beta}c^\dagger_{q\beta}c_{-q\overline\beta} \frac{1}{\omega - H_D}c^\dagger_{d\beta}c_{d\overline\beta}c^\dagger_{q\overline\beta}c_{q\beta} = \frac{J^2}{4} n_j\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{\beta}\hat n_{d\overline\beta}\left( 1 - \hat n_{d\beta} \right)
-\end{aligned}\end{equation}
-The diagonal part in the denominator was simple to deduce in this case, because the nature of the scattering requires the spins \(S_d^z\) and \(\frac{\beta}{2}\left(\hat n_{q\beta} - \hat n_{q \overline\beta}\right)\) to be anti-parallel.
-This ensures that the intermediate state has an energy of \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\), and the quantum fluctuation scale is \(\omega^\prime = \omega + \epsilon_d\), such that \(\omega^\prime - E = \omega - \frac{D}{2} + \frac{J}{4}\).
-In the hole sector, we have
-\begin{equation}\begin{aligned}
-	\label{ren_ed_Jph}
-	\frac{J^2}{4} n_j\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} \sum_{\beta}\hat n_{d\beta}\left( 1 - \hat n_{d\overline\beta} \right)
-\end{aligned}\end{equation}
-The final kind of scattering is the \(K^2\) type. Similar to the \(J^2\) term, we get the following contribution:
-\begin{equation}\begin{aligned}
-	\label{ren_ed_Kpp}
-	\frac{K^2}{4}\sum_{q\beta}c^\dagger_{q\beta}c^\dagger_{q\overline\beta}c_{d\overline\beta}c_{d\beta} \frac{1}{\omega - H_D}c^\dagger_{d\beta}c^\dagger_{d\overline\beta}c_{q\overline\beta}c_{q\beta} = \frac{K^2}{2} n_j\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} \left(1 - \hat n_{d \uparrow}\right) \left( 1 - \hat n_{d \downarrow} \right)
-\end{aligned}\end{equation}
-in the particle sector. This is again because \(E = \frac{D}{2} - \frac{K}{4}\) in the intermediate state and \(\omega^\prime = \omega\). In the hole sector, we get
-\begin{equation}\begin{aligned}
-	\label{ren_ed_Kph}
-	\frac{K^2}{2} n_j\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} \hat n_{d\uparrow}\hat n_{d \downarrow}~.
-\end{aligned}\end{equation}
-
-We now have all possible renormalisation to the impurity energy \(\epsilon_d\).
-To actually compute the renormalisation, we will first calculate the renormalisation in the energies \(\epsilon_0, \epsilon_1\) and \(\epsilon_2\) of the impurity states \(\ket{\hat n_d = 0}, \ket{\hat n_d = 1}, \ket{\hat n_d = 2}\) respectively.
-The renormalisation of these states are given by the following terms:
-\begin{itemize}
-	\item \(\Delta \epsilon_0\) is given by the renormalisation of the term \(\left(1 - \hat n_{d\uparrow}\right)\left(1 - \hat n_{d \downarrow}\right)\)
-	\item \(\Delta \epsilon_1\) is given by the renormalisation of either \(\left(1 - \hat n_{d\uparrow}\right)\hat n_{d \downarrow}\) or \(\left(1 - \hat n_{d\downarrow}\right)\hat n_{d \uparrow}\)
-	\item \(\Delta \epsilon_2\) is given by the renormalisation of \(\hat n_{d\uparrow}\hat n_{d \downarrow}\)
-\end{itemize}
-From eqs.~\ref{ren_ed_Vp}, \ref{ren_ed_Vh}, \ref{ren_ed_Jpp}, \ref{ren_ed_Jph}, \ref{ren_ed_Kpp} and \ref{ren_ed_Kph}, we write
-\begin{equation}\begin{aligned}
-	\Delta \epsilon_0 = \Delta \epsilon_2 = \frac{2V^2 n_j}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}} + \frac{K^2 n_j/2}{\omega - \frac{D}{2} + \frac{K}{4}}, && \Delta \epsilon_1 = \frac{2V^2 n_j}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} + \frac{J^2 n_j/2}{\omega - \frac{D}{2} + \frac{J}{4}}
-\end{aligned}\end{equation}
-We had started with a particle-hole symmetric Hamiltonian \((2\epsilon_d + U = 0)\); the fact that \(\Delta \epsilon_0 = \Delta \epsilon_2\) means the RG transformation has preserved that symmetry.
-The renormalisation of \(\epsilon_d\) is simply the renormalisation in the energy difference between the singly-occupied and vacant impurity levels: \(\Delta \epsilon_d = \Delta \epsilon_1 - \Delta \epsilon_0\).
-This gives our first RG equation:
-\begin{equation}\begin{aligned}
-	\Delta \epsilon_d = 2V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + \frac{n_j}{2}\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right)
-\end{aligned}\end{equation}
-
-\subsection{Renormalisation of the hybridisation \(V\)}
-Renormalisation of \(V\) happens through two kinds of processes: \(VJ\) and \(VK\).
-In order words, the two vertices involve one single-particle scattering and one spin or isospin exchange respectively.
-We first look at the vertices that involve a spin-exchange scattering.
-
-Within spin-exchange, the scattering can be either via \(S_d^z\) or through \(S_d^\pm\). For the first kind, we have the following contribution in the particle sector:
-\begin{equation}\begin{aligned}
-	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{4}J \sum_{k} \left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) c^\dagger_{k\beta}c_{q\beta} = \frac{1}{4}V J n_j \frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right)\sum_{k\beta} \left(1 - \hat n_{d\overline\beta}\right) c_{d\beta}c^\dagger_{k\beta}
-\end{aligned}\end{equation}
-The transformation from \(\frac{1}{\omega - H_D}\) to \(\frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right)\) is made so that we can account for both the initial state and the final state energies through the two fluctuation scales \(\omega^\prime_1\) and \(\omega_2^\prime\) respectively; we calculate the denominators for both the initial and final states, and then take the mean of the two (hence the factor of half in front).
-This was not required previously because in the earlier scattering processes, the impurity returned to its initial state at the end, at least in terms of \(\epsilon_d \left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right)^2 \), and so we had \(\omega_1^\prime = \omega_2^\prime = \omega^\prime\).
-
-Note that the \(c_{d\beta}\) in front of the Greens function resulted in \(\left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) \to \left(1 - \hat n_{d\overline\beta}\right)\).
-The intermediate state is characterised by \(\hat n_{d\beta} = 1 - \hat n_{d \overline \beta} = 1\), which means that \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\).
-Moreover, the initial state gives \(\omega_1^\prime = \omega + \epsilon_d\) while the final state gives \(\omega^\prime_2 = \omega\).
-Therefore, the renormalisation becomes
-\begin{equation}\begin{aligned}
-	-\frac{n_j}{4}V J \frac{1}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right)\sum_{k\beta}\left(1 - \hat n_{d\overline\beta}\right) c^\dagger_{k\beta} c_{d\beta}
-\end{aligned}\end{equation}
-One can generate another such process by exchanging the single-particle process and the spin-exchange process:
-\begin{equation}\begin{aligned}
-	\sum_{q\beta} \frac{1}{4}J \sum_{k} \left(\hat n_{d\beta} - \hat n_{d\overline\beta}\right) c^\dagger_{q\beta}c_{k\beta} \frac{1}{\omega - H_D} V c^\dagger_{d\beta} c_{q\beta}
-\end{aligned}\end{equation}
-This is simply the Hermitian conjugate of the previous contribution. Combining this with the previous then gives
-\begin{equation}\begin{aligned}
-	-\frac{n_j}{8}V J \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta}\left(1 - \hat n_{d\overline\beta}\right)\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-
-We now consider the spin-exchange processes involving \(S_d^\pm\):
-\begin{equation}\begin{aligned}
-	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{2}J \sum_{k} c^\dagger_{d\beta}c_{d\overline\beta} c^\dagger_{k\overline\beta}c_{q\beta} = \frac{1}{2}V J n_j \frac{1}{2}\left(\frac{1}{\omega^\prime_1 - E} + \frac{1}{\omega^\prime_2 - E}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) c_{d\overline\beta}c^\dagger_{k\overline\beta}
-\end{aligned}\end{equation}
-We again have \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4},\omega_1^\prime = \omega + \epsilon_d\) and \(\omega_2^\prime = \omega\), which gives
-\begin{equation}\begin{aligned}
-	-\frac{1}{4}V J n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)c^\dagger_{k\overline\beta} c_{d\overline\beta}
-\end{aligned}\end{equation}
-Combining this with the Hermitian conjugate obtained from exchanging the processes gives
-\begin{equation}\begin{aligned}
-	-\frac{1}{4}V J n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right)\left(c^\dagger_{k\overline\beta} c_{d\overline\beta} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-
-The contributions from the hole sector are obtained making the transformation \(\hat n_{d\overline\beta} \to 1 - \hat n_{d\overline\beta}\) on the particle sector contributions.
-The total renormalisation to \(V\) from \(VJ\) processes are
-\begin{equation}\begin{aligned}
-	-\frac{3n_j}{8}V J \left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) \sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-
-We now look at the \(VK\) processes. The first one is
-\begin{equation}\begin{aligned}
-	\sum_{q\beta} Vc^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{4}K \sum_{k} \left(\hat n_{d} - 1\right) c^\dagger_{k\beta}c_{q\beta} = -\frac{1}{8}V K n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \hat n_{d\overline \beta}c^\dagger_{k\beta}c_{d\beta}
-\end{aligned}\end{equation}
-The exchanged process again gives the Hermitian conjugate, so the combined contribution is
-\begin{equation}\begin{aligned}
-	-\frac{1}{8}V K n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \hat n_{d\overline \beta} \left(c^\dagger_{k\beta}c_{d\beta} + \text{h.c.}\right)
-\end{aligned}\end{equation}
-
-The isospin-flip vertex gives
-\begin{equation}\begin{aligned}
-	\sum_{q\beta} V c^\dagger_{q\beta} c_{d\beta} \frac{1}{\omega - H_D}\frac{1}{2}K \sum_{k} c^\dagger_{d\beta}c^\dagger_{d\overline\beta} c_{k\overline\beta} c_{q\beta} = \frac{1}{4}K V n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) c^\dagger_{d\overline\beta}c_{k\overline\beta}~.
-\end{aligned}\end{equation}
-Combining with Hermitian conjugate gives
-\begin{equation}\begin{aligned}
-	\frac{1}{4}K V n_j \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta} \left(1 - \hat n_{d\beta}\right) \left(c^\dagger_{d\overline\beta}c_{k\overline\beta} + \text{h.c.}\right)~.
-\end{aligned}\end{equation}
-
-After obtaining the hole sector contributions, the total renormalisation from \(VK\) processes is
-\begin{equation}\begin{aligned}
-	-\frac{3n_j}{4}V K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right) \sum_{k\beta}\left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right)~.
-\end{aligned}\end{equation}
-
-The RG equation for \(V\) is
-\begin{equation}\begin{aligned}
-	\Delta V = -\frac{3n_j V}{8}\left[J\left(\frac{1}{\omega - \frac{D}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) + K \left(\frac{1}{\omega - \frac{D}{2} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}}\right)\right]
-\end{aligned}\end{equation}
-
-\subsection{Renormalisation of the exchange couplings \(J\) and \(K\)}
-We will just note the renormalisation in \(J^z\), which will be equal to \(J^\pm\) due to spin-rotation symmetry.
-The terms that renormalise \(J^z\) are of the form \(S_d^\pm S_d^\mp\).
-In the particle sector, we have
-\begin{equation}\begin{aligned}
-	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^\pm c^\dagger_{q\mp}c_{k^\prime\pm} \frac{1}{\omega - H_D}S_d^\mp c^\dagger_{k\pm}c_{q\mp} = -n_j \frac{1}{4}J^2 \left(\frac{1}{2} \pm S_d^z\right) \sum_{kk^\prime}c^\dagger_{k \pm}c_{k\pm} \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
-The denominator is determined using \(E = \frac{D}{2} + \epsilon_d - \frac{J}{4}\) and \(\omega^\prime = \omega + \epsilon_d\).
-In the hole sector, we similarly have
-\begin{equation}\begin{aligned}
-	\sum_{q} \sum_{kk^\prime}\frac{1}{4}J^2 S_d^\mp c^\dagger_{k\pm}c_{q\mp} \frac{1}{\omega - H_D}S_d^\pm c^\dagger_{q\mp}c_{k^\prime\pm} = n_j \frac{1}{4}J^2 \left(\frac{1}{2} \mp S_d^z\right) \sum_{kk^\prime}c^\dagger_{k \pm}c_{k\pm} \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
-Adding all four expressions and dropping the constant part, we get
-\begin{equation}\begin{aligned}
-	-n_j \frac{1}{2}J^2 S_d^z \sum_{kk^\prime}\left(c^\dagger_{k \uparrow}c_{k^\prime \uparrow} - c^\dagger_{k \downarrow}c_{k^\prime \downarrow}\right) \frac{1}{\omega - \frac{D}{2} + \frac{J}{4}}~.
-\end{aligned}\end{equation}
-We can now directly read off the RG equation for \(J\):
-\begin{equation}\begin{aligned}
-	\Delta J = -\frac{n_j J^2}{\omega - \frac{D}{2} + \frac{J}{4}}
-\end{aligned}\end{equation}
-
-Since the spin and charge degrees of freedom are treated on an equal footing in the model, we obtain the RG equation for \(K\) by simply changing \(J \to K\):
-\begin{equation}\begin{aligned}
-	\Delta K = -\frac{n_j K^2}{\omega - \frac{D}{2} + \frac{K}{4}}
-\end{aligned}\end{equation}
-
-\section{\(U_b\)-included terms}
-
-We first Fourier transform the \(U_b\)-term to \(k-\)space.
-In \(k-\)space, the diagonal contribution (to \(H_D\)) coming from this term is the single-particle self-energy \(-U_b\left(\hat n_{q \beta}\right)^2\) which can be made particle-hole symmetric in the form:
-\begin{equation}\begin{aligned}
-	-U_b\left(\tau_{q \beta}\right)^2
-\end{aligned}\end{equation}
-where \(q\) is the \(k-\)state being decoupled and \(\tau \equiv \hat n - 1/2\).
-In the initial state \(\ket{\Psi}_i\), we have \(\langle \hat n_{q\beta} \rangle = 1/2 \implies \tau_{q\beta} = 0\), so the contribution of \(U_b\) to that state is 0.
-For both hole excitations \(c_{q\beta}\ket{\Psi}_i\) as well as particle excitations \(c^\dagger_{q\beta}\ket{\Psi}_i\), the intermediate state energy lowers to \(-U_b/4\).
-
-The off-diagonal part is
-\begin{equation}\begin{aligned}
-	-\frac{U_b}{2}\sum_{kk^\prime\sigma}c^\dagger_{k\sigma}c_{k^\prime\sigma} + U_b \sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_1 \uparrow}c_{k_2 \uparrow} c^\dagger_{k^\prime_1 \downarrow}c_{k^\prime_2 \downarrow}
-\end{aligned}\end{equation}
-We ignore the potential scattering arising from the first term.
-
-\subsection{Renormalisation of \(U_b\)}
-\(U_b\) can renormalise only via itself. The relevant renormalisation term in the particle sector is
-\begin{equation}\begin{aligned}
-	U_b^2 \sum_{q\beta}\sum_{k_1,k_2,k_3,k_1^\prime,k_2^\prime,k_3^\prime} c^\dagger_{q\beta}c_{k_1\beta}c^\dagger_{k_3\overline\beta}c_{k_1^\prime\overline\beta}\frac{1}{\omega - H_D}c^\dagger_{k_2^\prime\overline\beta}c_{k_3^\prime\overline\beta}c^\dagger_{k_2\beta}c_{q\beta}
-\end{aligned}\end{equation}
-In order to renormalise \(U_b\), we need to contract one more pair of momenta.
-There are two choices.
-The first is by setting \(k_3 = k_3^\prime = q\).
-The two internal states, then, are \(q\beta\) and \(q\overline\beta\).
-As discussed above, the intermediate state energy is \(-U_b/4\).
-We therefore have
-\begin{equation}\begin{aligned}
-	\frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c_{k_1\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2^\prime\overline\beta}c^\dagger_{k_2\beta} = \frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_1^\prime,k_2^\prime} c^\dagger_{k_2^\prime\overline\beta}c_{k_1^\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
-\end{aligned}\end{equation}
-Another way to contract the momenta is by setting \(k_1^\prime = k_2^\prime = q\), which gives a renormalisation of
-\begin{equation}\begin{aligned}
-	\frac{U_b^2 n_j}{\omega - D/2 + U_b/4}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c_{k_1\beta}c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta} = -\frac{U_b^2 n_j}{\omega - D/2}\sum_{\beta}\sum_{k_1,k_2,k_3,k_3^\prime} c^\dagger_{k_3 \overline\beta}c_{k_3\prime\overline\beta}c^\dagger_{k_2\beta}c_{k_1\beta}
-\end{aligned}\end{equation}
-The two contributions cancel each other. The same cancellation happens in the hole sector as well.
-
-\subsection{Renormalisation of \(U\)}
-\(U_b\) does not have any new renormalisation term on account of \(U_b\). \(U_b\) does however modify the existing RG equation for \(U\), by shifting the denominator. The existing RG equation is
-\begin{equation}\begin{aligned}
-	\Delta U &= -4V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} - \epsilon_d + \frac{J}{4}}\right) - n_j\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{K}{4}}\right)~.
-\end{aligned}\end{equation}
-On accounting for the contribution of \(U_b\) to the denominator, we get
-\begin{equation}\begin{aligned}
-	\Delta U &= -4V^2 n_j\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \epsilon_d + \frac{K}{4}} - \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} - \epsilon_d + \frac{J}{4}}\right) - n_j\left(\frac{J^2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} - \frac{K^2}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right)~.
-\end{aligned}\end{equation}
-
-\subsection{Renormalisation of \(V\)}
-The single-particle  hybridisation \(V\) renormalises through terms of \(V U_b\) and \(U_b V\) kind. The first term gives
-\begin{equation}\begin{aligned}
-	&\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{k\beta} \hat n_{q\overline\beta} \frac{1}{\omega - H_D} c^\dagger_{d\beta}c_{q\beta} \\
-	&= n_jU_b V\sum_{k\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_1 - E_1} + \frac{1}{\omega^\prime_1 - E_1}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_0 - E_0} + \frac{1}{\omega_0^\prime - E_0}\right)\right] c^\dagger_{d\beta}
-\end{aligned}\end{equation}
-\(E_1\) and \(E_0\) are the intermediate state energies for \(\hat n_{d\overline\beta}=1\) and 0 respectively.
-\(\omega_{1,0}\) are the quantum fluctuation scales for the corresponding initial states.
-\(\omega^\prime_{1,0}\) are the fluctuation scales for the corresponding final states.
-The intermediate energies are \(E_1 = D/2 - U_b/4 - K/4,~ ~ ~ E_0 = D/2 - U_b/4 - U/2 - J/4\).
-The fluctuation scales are \(\omega_1 = \omega - U/2= \omega_0^\prime,~ ~ ~ \omega_1^\prime = \omega = \omega_0\).
-Substituting these gives
-\begin{equation}\begin{aligned}
-	-n_jU_b V\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
-+\left.
-\frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
-\end{aligned}\end{equation}
-
-The second term is of the form
-\begin{equation}\begin{aligned}
-	\sum_{q\beta}\sum_{k}U_b V c^\dagger_{q\beta}c_{d\beta} \frac{1}{\omega - H_D} \hat n_{q\overline\beta} c^\dagger_{k\beta}c_{q\beta}
-\end{aligned}\end{equation}
-and this is just the Hermitian conjugate of the previous term, so these two terms together lead to
-\begin{equation}\begin{aligned}
-	-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
-	+ \left.\frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
-\end{aligned}\end{equation}
-
-In the hole sector, we have
-\begin{equation}\begin{aligned}
-	&\sum_{q\beta}\sum_{k}U_b V \hat n_{q\overline\beta} c^\dagger_{k\beta}c_{q\beta} \frac{1}{\omega - H_D} c^\dagger_{q\beta}c_{d\beta}\\
-	&-\sum_{q\beta}\sum_{k}U_b V \left(1 - \hat n_{q\overline\beta}\right) c^\dagger_{k\beta}c_{q\beta} \frac{1}{\omega - H_D} c^\dagger_{q\beta}c_{d\beta}\\
-	&= -n_jU_b V\sum_{k\beta} c^\dagger_{k\beta} \left[\frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_1 - E_1} + \frac{1}{\omega^\prime_1 - E_1}\right) + \frac{1-\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega_0 - E_0} + \frac{1}{\omega_0^\prime - E_0}\right)\right] c_{d\beta}
-\end{aligned}\end{equation}
-\(E_1 = D/2 - U_b/4 - U/2 - J/4,~ ~ ~ E_0 = D/2 - U_b/4 - K/4\).
-The fluctuation scales are \(\omega_1 = \omega = \omega_0^\prime,~ ~ ~ \omega_1^\prime = \omega - U/2 = \omega_0\).
-Substituting these gives
-\begin{equation}\begin{aligned}
-	-n_jU_b V\sum_{k\beta} c^\dagger_{d\beta} c_{k\beta} \left[\frac{1 - \hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
-+\left. \frac{\hat n_{d\overline\beta}}{2}\left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
-\end{aligned}\end{equation}
-The other term, obtained by exchanging \(V\) and \(U_b\), gives the Hermitian conjugate, so the overall contribution from the hole sector is the same as the total contribution from the particle sector, but with \(\hat n_{d\overline\beta} \to 1 - \hat n_{d\overline\beta}\).
-Combining both the sectors, we get
-\begin{equation}\begin{aligned}
-	-n_jU_b V\sum_{k\beta} \left(c^\dagger_{d\beta} c_{k\beta} + \text{h.c.}\right) \frac{1}{2}\left[\left(\frac{1}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) \right.\\
-+\left. \left(\frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{1}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]
-\end{aligned}\end{equation}
-
-Combining with the already existing RG equations, the complete RG equation for \(V\) becomes
-\begin{equation}\begin{aligned}
-	\Delta V =& -\frac{3n_j V}{8}\left[\left(\frac{J}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} + \frac{J}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}}\right) + K \left(\frac{K}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{K}{\omega - \frac{D}{2} + \frac{U_b}{4} - \frac{U}{2} + \frac{K}{4}}\right)\right]\\
-		 &-\frac{n_jU_b}{2}\left[\left(\frac{V}{\omega - \frac{D}{2} - \frac{U}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}}\right) + \left(\frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}} + \frac{V}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}}\right)\right]\\
-		 &=-\frac{n_j V}{8}\left[\left(\frac{3J + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{J}{4}} + \frac{3J + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{U}{2} + \frac{J}{4}}\right) + \left(\frac{3K + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} + \frac{K}{4}} + \frac{3K + 4U_b}{\omega - \frac{D}{2} + \frac{U_b}{4} - \frac{U}{2} + \frac{K}{4}}\right)\right]
-\end{aligned}\end{equation}
-
-\subsection{Renormalisation of \(J\) and \(K\)}
-We will track the entire renormalisation purely from that of \(J^+\), by virtue of the SU(2) symmetry. \(J^+\) renormalises through the \(J U_b\) terms. One of the terms is
-\begin{equation}\begin{aligned}
-	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} S_d^+ c^\dagger_{q \downarrow} c_{k \uparrow} \frac{1}{\omega - H_D} \hat n_{q \uparrow} c^\dagger_{k^\prime \downarrow}c_{q \downarrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
-\end{aligned}\end{equation}
-The factor of half in front is the same half factor that appears in front of the \(S_1^+ S_2^-, S_1^-S_2^+\) terms when we rewrite \(\vec{S}_1\cdot\vec{S}_2\) in terms of \(S^z, S^\pm\).
-Another term is obtained by switching \(J\) and \(U_b\):
-\begin{equation}\begin{aligned}
-	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \downarrow} c^\dagger_{q \uparrow} c_{k \uparrow} \frac{1}{\omega - H_D}S_d^+ c^\dagger_{k^\prime \downarrow} c_{q \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
-\end{aligned}\end{equation}
-
-The corresponding terms in the hole sector are
-\begin{equation}\begin{aligned}
-	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{q \uparrow} \frac{1}{\omega - H_D} \hat n_{q \downarrow} c^\dagger_{q \uparrow}c_{k \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-	\frac{1}{2} J U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \uparrow} c^\dagger_{k^\prime \downarrow} c_{q \downarrow} \frac{1}{\omega - H_D}S_d^+ c^\dagger_{q \downarrow} c_{k \uparrow} = -\frac{1}{2}\frac{J U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}} \sum_{k,k^\prime} S_d^+ c^\dagger_{k^\prime \downarrow} c_{k \uparrow}
-\end{aligned}\end{equation}
-
-Adding all these terms and combining with the existing RG equation, we get the updated RG equation for \(J\):
-\begin{equation}\begin{aligned}
-	\Delta J = -J n_j\frac{4 U_b + J}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{J}{4}}
-\end{aligned}\end{equation}
-
-We will follow the same strategy with \(K\) - we will calculate the renormalisation in \(K^+\). The first term is
-\begin{equation}\begin{aligned}
-	\frac{1}{2} K U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \downarrow} c^\dagger_{q \uparrow}c_{k^\prime \uparrow} \frac{1}{\omega - H_D} C_d^+ c_{k \downarrow} c_{q \uparrow} = -\frac{1}{2}\frac{K U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}} \sum_{k,k^\prime} C_d^+ c_{k \downarrow} c_{k^\prime \uparrow}
-\end{aligned}\end{equation}
-The second term in the same sector is obtained by flipping the spins of \(k\) and \(q\):
-\begin{equation}\begin{aligned}
-	\frac{1}{2} K U_b \sum_{q} \sum_{k,k^\prime} \hat n_{q \uparrow} c^\dagger_{q \downarrow}c_{k^\prime \downarrow} \frac{1}{\omega - H_D} C_d^+ c_{q \downarrow} c_{k \uparrow} = -\frac{1}{2}\frac{K U_b n_j}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}} \sum_{k,k^\prime} C_d^+ c_{k \downarrow} c_{k^\prime \uparrow}
-\end{aligned}\end{equation}
-
-The terms in the hole sector give identical contributions. The RG equation for \(K\) is
-\begin{equation}\begin{aligned}
-	\Delta K = -K n_j\frac{4 U_b + K}{\omega - \frac{D}{2} + \frac{U_b}{2} + \frac{K}{4}}
-\end{aligned}\end{equation}
 

### 2023-03-20 notes/tilingProject.tex
added k-space spectral function and some clarifications

--- 2023-03-09 notes/notes.tex
@@
 \documentclass{report}
-\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk,enumitem}
+\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk,enumitem,cite,graphicx}
 % \usepackage[draft]{graphicx}
@@
 
-\title{\bf An Unitary RG-based Auxiliary Model Approach\\ to Strongly-Correlated Systems}
+\title{\bf An Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems}
 \author{Abhirup Mukherjee, Siddhartha Lal}
@@
 
-\section{A "bottoms-up" approach to using auxiliary models}
+\section{A ``bottoms-up" approach to using auxiliary models}
 As mentioned in the previous section, the question we are posing is the following: what is the simplest auxiliary model of impurity in a bath that can capture the metal-insulator transition in a Hubbard-like model of correlated electrons.
@@
 The bulk model hence created will then show a metal-insulator transition.
-The impurity models are studied using the recently-developed unitary renormalisation group method~\cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome}, and this analysis is shown in chapters~\ref{chap:urg1}~and~\ref{siam-attr-chap}.
+The impurity models are studied using the recently-developed unitary renormalisation group method~\cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome}.
 The leap to the bulk model is then made by applying lattice translation operators on the auxiliary model.
@@
 
+The strategy, therefore, is to relate Hamiltonians, wavefunctions and hence correlation functions of the bulk model to those of the auxiliary model.
+One can then substitute the information obtained from solutions of the auxiliary model, and thereby calculate quantities on the bulk lattice model.
+
 \chapter{From the auxiliary model to the bulk - single site approach}
@@
 \end{aligned}\end{equation}
-We end up with a Hubbard-Heisenberg model:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j
-\end{aligned}\end{equation}
-The mapping between the parameters is
+We end up with a Hubbard-Heisenberg model, of the form:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{1}{\mathcal{W}}t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{\mathcal{W}}J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j
+\end{aligned}\end{equation}
+where the bulk parameters are related to the auxiliary model couplings through the mapping:
 \begin{equation}\begin{aligned}
 	\label{map_aux_bulk}
-	t_{H-H} = \left(2t (N-2) - \frac{2V}{\mathcal{W}}\right),~ ~ U_{H-H} = \left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = \frac{2J}{\mathcal{W}}
+	t_{H-H} = \left(2t \mathcal{W}(N-2) - 2V\right),~ ~ U_{H-H} = \left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = 2J
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j + \mu_\text{H-H}\sum_{i\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
+	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{1}{\mathcal{W}}t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{\mathcal{W}}J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j + \mu_\text{H-H}\sum_{i\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
 \end{aligned}\end{equation}
@@
 \section{Evidence for the Mott MIT}
-Through the URG study of the generalised SIAM with correlation (eq.~\ref{siam_attr}) shown in chapter \ref{siam-attr-chap}, we can conclude the following about that model:
+Through the URG study of the extended SIAM with correlation (eq.~\ref{siam_attr}), we can conclude the following about that model:
 \begin{itemize}
@@
 	\includegraphics[width=0.48\textwidth]{../figures/spectral-function.pdf}
-	\caption{{\it Left:} Phase diagram. {\it Right:} Impurity spectral function}
+	\caption{{\it Left:} Phase diagram. {\it Right:} Local spectral function}
 	\label{spec_func_mit}
+\end{figure}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.32\textwidth]{../figures/kspace_specfunc_0.0000_0.0000.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/kspace_specfunc_0.0000_1.5708.pdf}
+	\includegraphics[width=0.32\textwidth]{../figures/kspace_specfunc_1.5708_1.5708.pdf}
+	\caption{Momentum-space spectral functions \(A_{\vec k}(\omega)\)}
 \end{figure}
@@
 We will now argue that this critical point describes a metal-insulator transition.
-For \(r < r^{*}\), the well-defined low-\(\omega\) central peak in the impurity spectral function, as well as the large mutual and information correlations, in the ground state, among the members of the Kondo cloud or between the impurity and the zeroth site show that the impurity and the bath are very strongly entangled, and the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) are non-zero at low \(\omega\).
-This means that both the local and the nearest-neighbour Greens functions, that are related to these parameters via eq.~\ref{greens_func_siam}, have poles at low\(-\omega\) and support the propagation of electrons through gapless excitations.
-Since the spectral function is also very simply related to that of the auxiliary model (eq.\eqref{main}), the former also shows the same zero-energy resonance.
-
-On the other side \(r > r^{*}\) of the critical point, we know that the impurity gets decoupled from the bath, such that the weighted poles \(\left(|d^p_n|^2 + \left(d^p_n\right)^* z^p_n\right) \left(\mathcal{G}_\text{aux}(d, \omega)\right)_{nn}\) and \(\left(|d^h_n|^2 + \left(z^h_n\right)^* d^h_n\right)\left(\mathcal{G}_\text{aux}(d, -\omega)\right)_{nn}\) vanish.
-This is simply the loss of spectral weight at low-\(\omega\) because of the removal of the gapless excitations, and is demonstrated through the impurity spectral function in fig.~\ref{spec_func_mit}.
-This then implies that the bulk Greens functions will also gap out at low energies, and that describes an insulating phase where the electrons get "jammed" in the local states.
-By the same argument as above, the bulk spectral function also sees a gap in this phase when the impurity spectral function is gapped (see eq.\eqref{main}).
+For \(r < r^{*}\), the well-defined low-\(\omega\) central peak in the impurity spectral function, as well as the large mutual and information correlations, in the ground state, among the members of the Kondo cloud or between the impurity and the zeroth site show that the impurity and the bath are very strongly entangled.
+This means that both the local and the nearest-neighbour Greens functions have poles at low\(-\omega\) and support the propagation of electrons through gapless excitations.
+Since the spectral function is also very simply related to that of the auxiliary model, the former also shows the same zero-energy resonance.
+
+On the other side \(r > r^{*}\) of the critical point, we know that the impurity gets decoupled from the bath, leading to the transformation of poles into zeros in the Greens functions.
+This is demonstrated through the gapping of the impurity spectral function in fig.~\ref{spec_func_mit}, and it describes an insulating phase where the electrons get "jammed" in the local states.
+By the same argument as above, the bulk spectral function also sees a gap in this phase when the impurity spectral function is gapped.
 
@@
 \begin{eqnarray}
-	r^{*} &=& \frac{U_{H-H}^{*}}{J_{H-H}^{*}} = \frac{\mathcal{W}}{4}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)
+	r^{*} &=& \frac{U_{H-H}^{*}}{J_{H-H}^{*}} = \frac{1}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{4}\right)
 \end{eqnarray}
-where $U^{*}$ and $J^{*}$ are the values of the on-site and Kondo couplings of the auxiliary model at the auxiliary model (i.e., the generalised SIAM with a correlated bath) at the transition between the Kondo screened and the local moment phases.
-Parametrising the bath correlation coupling as $U_{b}=-\frac{U}{10}$, we obtain $U^{*}/J^{*}=5/2$, and $r^{*} = 2$ for the 2D square lattice Hubbard-Heisenberg model (with coordination number $\mathcal{W}=4$).
-In general, $\mathcal{W}=2d$ for the $d$-dimensional hypercubic lattice, and
-$r^{*}_\text{hyperc.} = \frac{d}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)$.
+where $U^{*}$ and $J^{*}$ are the values of the on-site and Kondo couplings of the auxiliary model at the auxiliary model (i.e., the extended SIAM with a correlated bath) at the transition between the Kondo screened and the local moment phases.
+Parametrising the bath correlation coupling as $U_{b}=-\frac{U}{10}$, we obtain $U^{*}/J^{*}=5/2$, and $r^{*} = 2$ for the 2D square lattice Hubbard-Heisenberg model.
+% In general, $\mathcal{W}=2d$ for the $d$-dimensional hypercubic lattice, and 
+% $r^{*}_\text{hyperc.} = \frac{d}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)$.
 The growth of $r^{*}$ with $d$ indicates that the MIT is increasingly rendered difficult in a higher dimensional hypercubic lattice, as it is easier for electrons to delocalise and a very large on-site repulsion is needed to overcome this.
@@
 \subsection{Topological nature of the transition}
-As shown in section~\ref{lutt_theorem}, there is a difference in the value of the Luttinger volume between the local moment (LM) and the strong-coupling (SC) fixed points.
+Since the impurity charge hybridising with the bath contributes to the total Luttinger volume of the system~\cite{martin1982fermi}, decoupling of the impurity from the conduction bath leads to a difference in the value of the Luttinger volume between the local moment (LM) and the strong-coupling (SC) fixed points.
 If we define \(\mathcal{N}_L\) as the Luttinger volume with the spin-degeneracy accounted for, we can write
@@
 \end{aligned}\end{equation}
-From eq.~\ref{greens_func_siam}, we know that the bulk local Greens function is equal to that of the auxiliary model, and that gives \(\sum_i \mathcal{N}_i = \mathcal{N}_\text{imp}\sum_i = \mathcal{N} \mathcal{N}_\text{imp}\).
+From eq.~\ref{greens_func_relation}, we know that the bulk local Greens function is proportional to that of the auxiliary model, and that gives \(\sum_i \mathcal{N}_i = \mathcal{N}_\text{imp}\sum_i = \mathcal{N} \mathcal{N}_\text{imp}\).
 There we used the fact that for a half-filled system, the total number of sites is equal to the total number of particles in the system.
@@
 \section{Spectrum of the Hubbard dimer}
-Here we document the spectrum of the Hubbard dimer Hamiltonian in eqs.~\ref{hubb_dimer}.
+Here we document the spectrum of the Hubbard dimer Hamiltonian.
 \begin{center}
@@
 
-\bibliography{notes}
+\bibliography{tilingProject}
 \end{document}

### 2023-03-20 notes/tilingProject.tex
corrected critical value of bulk

@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(i,j) = -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n} \left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2
+	\mathcal{H}_\text{aux}(i,j) = -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n} \left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j - \frac{1}{2}U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2
 \end{aligned}\end{equation}
@@
 	\mathcal{H}_\text{aux}(i) &= \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right)  \right.\\
-				  &\left. +J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\\
+				  &\left. +J \vec{S_i}\cdot\vec{S}_j - \frac{1}{2}U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\\
 				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
-				  &\left.- U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]
+				  &\left.- \frac{1}{2}U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]
 \end{aligned}\end{equation}
@@
 	\mathcal{H}_\text{full} =& \sum_i \mathcal{H}_\text{aux}(i) = \sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
-				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j - U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\right]\\
-	=& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
+				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j - \frac{1}{2}U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\right]\\
+	=& -\frac{1}{2}\left(U + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
 				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j\right]\right]
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& -\left(\frac{U}{2} + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - 2t\left(N-2\right)\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{\mathcal{W}}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
+	\mathcal{H}_\text{full} =& -\frac{1}{2}\left(U + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - 2t\left(N-2\right)\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{\mathcal{W}}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
 				  &+ \left. J \vec{S_i}\cdot\vec{S}_j\right]\\
-				  &=-\left(\frac{U}{2} + U_b\right) \sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(2t (N-2) - \frac{2V}{\mathcal{W}}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{\mathcal{W}} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
+				  &=-\frac{1}{2}\left(U + U_b\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(2t (N-2) - \frac{2V}{\mathcal{W}}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{\mathcal{W}} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{1}{\mathcal{W}}t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{\mathcal{W}}J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j
+	\mathcal{H}_{H-H} = - \frac{1}{2}U_\text{H-H}\sum_{i} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{1}{\mathcal{W}}t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{\mathcal{W}}J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j
 \end{aligned}\end{equation}
@@
 	\label{map_aux_bulk}
-	t_{H-H} = \left(2t \mathcal{W}(N-2) - 2V\right),~ ~ U_{H-H} = \left(\frac{U}{2} + U_b\right), ~ ~ J_{H-H} = 2J
+	t_{H-H} = \left(2t \mathcal{W}(N-2) - 2V\right),~ ~ U_{H-H} = U + U_b, ~ ~ J_{H-H} = 2J
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_{H-H} = -\sum_{i} U_\text{H-H} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{1}{\mathcal{W}}t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{\mathcal{W}}J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j + \mu_\text{H-H}\sum_{i\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
+	\mathcal{H}_{H-H} = -\frac{1}{2}U_\text{H-H} \sum_{i} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{1}{\mathcal{W}}t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{\mathcal{W}}J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j + \mu_\text{H-H}\sum_{i\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
 \end{aligned}\end{equation}
@@
 	\includegraphics[width=0.48\textwidth]{../figures/phase-map-MIT.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/spectral-function.pdf}
-	\caption{{\it Left:} Phase diagram. {\it Right:} Local spectral function}
+	\includegraphics[width=0.48\textwidth]{../figures/spectral-function-(0, 0).pdf}
+	\caption{{\it Left:} Phase diagram. {\it Right:} Local spectral function on impurity site}
 	\label{spec_func_mit}
@@
 
-Finally, using eqs.\eqref{map_aux_bulk} and the criticality condition $U_{b}^{*}=-\frac{J^{*}}{4}$, we can offer a functional form for the critical value of the parameter $r^{*} = U_{H-H}^{*}/J_{H-H}^{*}$
-\begin{eqnarray}
-	r^{*} &=& \frac{U_{H-H}^{*}}{J_{H-H}^{*}} = \frac{1}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{4}\right)
-\end{eqnarray}
+Finally, using relations \eqref{map_aux_bulk} between the auxiliary model couplings and the bulk parameters, we can offer a functional form for the critical value of the parameter $r^{*} = U_{H-H}^{*}/J_{H-H}^{*}$.
+Using \(U_{H-H}^{*} = U^* + U_b\) and \(J_{H-H}^{*} = 2J^*\) (following \eqref{map_aux_bulk}), we get
+\begin{equation}\begin{aligned}
+	r^{*} &=& \frac{1}{2}\left(\frac{U^{*}}{J^{*}} + \frac{U_b}{J^*}\right)
+\end{aligned}\end{equation}
 where $U^{*}$ and $J^{*}$ are the values of the on-site and Kondo couplings of the auxiliary model at the auxiliary model (i.e., the extended SIAM with a correlated bath) at the transition between the Kondo screened and the local moment phases.
-Parametrising the bath correlation coupling as $U_{b}=-\frac{U}{10}$, we obtain $U^{*}/J^{*}=5/2$, and $r^{*} = 2$ for the 2D square lattice Hubbard-Heisenberg model.
+By using the auxiliary model criticality condition \(-4U_b = J^*\), the bulk criticality parameter \(r^*\) takes the form
+\begin{equation}\begin{aligned}
+	r^{*} &=& \frac{1}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{4}\right)
+\end{aligned}\end{equation}
+Parametrising the bath correlation coupling as $U_{b}=-\frac{U}{10}$, we obtain $U^{*}/J^{*}=5/2$, and $r^{*} = 9/8$ for the 2D square lattice Hubbard-Heisenberg model.
+The reduction in the value of \(r\) from \(2.5\) in the auxiliary model to \(~1.1\) in the bulk model can be attributed to (i) the reduction in the effective bulk repulsion \(U\) due to the competition coming from the attractive \(U_b\), and (ii) increased hybdridisation through \(J\) due to the presence of multiple auxiliary models that connect two lattice sites.
 % In general, $\mathcal{W}=2d$ for the $d$-dimensional hypercubic lattice, and 

### 2023-05-05 notes/tilingProject.tex
added entanglement plots
kspace correlations

@@
 
+\section{Correlation functions in momentum space}
+Similar to Greens functions, our formalism also allows calculating \(k-\)space correlation functions \(\chi(\vec q)\) from knowledge of local and nearst-neighbour correlations \(\chi_\text{loc}\) and \(\chi_\text{nn}\).
+This is seen by Fourier transforming a generic real-space correlation function \(\chi(\vec r)\) corresponding to the operator \(\mathcal{O}\):
+\begin{equation}\begin{aligned}
+	\chi(\vec r) = \left<\mathcal{O}_1^\dagger (\vec R + \vec r) \mathcal{O}_2(\vec R)\right> = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\left<\mathcal{O}_1^\dagger (\vec q) \mathcal{O}_2(\vec k)\right>
+\end{aligned}\end{equation}
+Since the response should not depend on \(\vec R\) (owing to translation invariance), we have
+\begin{equation}\begin{aligned}
+	\chi(\vec r) = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\delta_{\vec k + \vec q, 0}\left<\mathcal{O}_1^\dagger (\vec q) \mathcal{O}_2(\vec k)\right> = \frac{1}{N}\sum_{\vec k} e^{-i \vec k \cdot \vec r}\left<\mathcal{O}_1^\dagger (-\vec k) \mathcal{O}_2(\vec k)\right>
+\end{aligned}\end{equation}
+By inverting the Fourier transform, we therefore get
+\begin{equation}\begin{aligned}
+	\chi(\vec k) &\equiv \left<\mathcal{O}_1^\dagger (-\vec k) \mathcal{O}_2(\vec k)\right> = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}} \chi(\vec r) \simeq \chi_\text{loc} + \xi_{\vec k} \chi_\text{nn} \\
+	&= \frac{1}{\lambda_{\vec k_0}^2}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1^\dagger(d) \mathcal{O}_2(d) | \psi_\text{aux}(\vec R_0, \vec a)} + \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1^\dagger(z) \mathcal{O}_2(d) | \psi_\text{aux}(\vec R_0, \vec a)}
+\end{aligned}\end{equation}
+
 \section{Evidence for the Mott MIT}
@@
 \centering
-	\includegraphics[width=0.48\textwidth]{../figures/corrs_gs.pdf}
+	% \includegraphics[width=0.48\textwidth]{../figures/corrs_gs.pdf}
 	\includegraphics[width=0.48\textwidth]{../figures/spin-charge-corr-full.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/mutinfo-d0-01-full.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/doub_occ.pdf}
+	\includegraphics[width=0.48\textwidth]{../figures/impEE-mutinfo-d0.pdf}
+	% \includegraphics[width=0.48\textwidth]{../figures/doub_occ.pdf}
 \end{figure}

### 2023-05-09 notes/tilingProject.tex
added 0-1 correlations to kpsace

@@
 where \(\ket{\psi_\text{diff}(\vec k_0)} = \ket{\Psi_\text{gs}} - \frac{1}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j} \left[e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j)} - e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)}\right]\).
-Specifically, for the local Greens function \(G_\text{H-H}(\vec r=0, t)\), we keep the states with \(\vec R_j = \vec R_0\), leading to the expression
+The Greens funtion takes the form
+\begin{equation}\begin{aligned}
+G_\text{H-H}(\vec r, t) =  \frac{-i\theta(t)}{\mathcal{W}^2 \lambda_{\vec k_0}^2}\sum_{\vec a_1, \vec a_2 \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a_1) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a_2)}~.
+\end{aligned}\end{equation}
+Specifically, for the local Greens function \(G_\text{H-H}(\vec r=0, t)\), we keep the states with \(\vec a_1 = \vec a_2\), leading to the expression
 \begin{equation}\begin{aligned}\label{greens_func_approx}
-	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}^2}i\theta(t) \sum_{\vec a_1, \vec a_2}\braket{\psi_\text{aux}(\vec R_0, \vec a_2) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a_1)}~.
-\end{aligned}\end{equation}
-Because of the symmetry of the lattice, all Greens functions obtained for various positions of the zeroth site \(\vec a_1\) and \(\vec a_2\) are equal to their mean, and the local Greens function simplifies to
-\begin{equation}\begin{aligned}
-	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) &= -\frac{1}{\lambda_{\vec k_0}^2 }i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0)}~.
-\end{aligned}\end{equation}
-In this form, the only Hamiltonian involved in the expression is the COM Hamiltonian at \(\vec R_0\), and \(G_\text{H-H}(\vec r=0, t)\) is therefore captured by the impurity Greens function \(\mathcal{G}\) in the auxiliary model \(N \mathcal{H}_\text{aux}(\vec R_0)\):
+	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) =  \frac{-i\theta(t)}{\mathcal{W}^2 \lambda_{\vec k_0}^2}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)}~.
+\end{aligned}\end{equation}
+Because of the symmetry of the lattice, all Greens functions obtained for various positions of the zeroth site \(\vec a\) are equal, and the local Greens function simplifies to
+\begin{equation}\begin{aligned}
+	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) &= -\frac{1}{\mathcal{W}\lambda_{\vec k_0}^2 }i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0)}~.
+\end{aligned}\end{equation}
+In this form, the only Hamiltonian involved in the expression is the COM Hamiltonian at \(\vec R_0\), and \(G_\text{H-H}(\vec r=0, t)\) is therefore captured by the impurity Greens function \(\mathcal{G}\) in the auxiliary model \(N \mathcal{H}_\text{aux}(\vec R_0)\) with ground-state \(\ket{\psi_\text{aux}(\vec R_0)}\):
 \begin{equation}\begin{aligned}
 	\label{greens_func_relation}
-	G_\text{loc}(t) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{G}_{dd}(t)~.
+	G_\text{loc}(t) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{G}_{dd}(t)~,\quad \mathcal{G}_{dd}(t) = -i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0)}~.
 \end{aligned}\end{equation}
@@
 
-For the nearest neighbour Greens function \(G_\text{H-H}(\vec r=\vec a, t)\), we keep only the terms with \(\vec a_1 = \vec a_2\) in the summation of eq.~\ref{greens_func_approx}:
-\begin{equation}\begin{aligned}
-	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}^2}i\theta(t) \sum_{\vec a_1}\braket{\psi_\text{aux}(\vec R_0, \vec a_1) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a_1)}~.
-\end{aligned}\end{equation}
-Again, because of the lattice symmetry, all values of \(\vec a_1\) lead to the same impurity-bath Greens function \(\mathcal{G}_{dz}\) on the auxiliary model:
-\begin{equation}\begin{aligned}
-	G_\text{H-H}(\vec r, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} = \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}} \mathcal{G}_{dz}(t)~.
+For the nearest neighbour Greens function \(G_\text{H-H}(\vec r=\vec a, t)\), we keep only the terms with \(\vec a_1 = \vec a_2 = \vec a\) in the summation of eq.~\ref{greens_func_approx}:
+\begin{equation}\begin{aligned}
+	G_\text{H-H}(\vec r=\vec a, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}^2}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + \vec a)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} = \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}^2} \mathcal{G}_{dz}(t)~.
 \end{aligned}\end{equation}
@@
 By choosing an appropriate auxiliary model, the overlap factor \(\lambda_{\vec k_0}\) can be brought close to unity, leading to a smaller difference.
-
 The local and nearest-neighbour Greens functions of the full model can thus be computed from the impurity local Greens function \(\mathcal{G}_{dd}\) and the impurity-bath zeroth site Greens function \(\mathcal{G}_{dz}\) on the COM auxiliary model \(N \mathcal{H}_\text{aux}(\vec R_0)\).
 By using these real-space Greens functions, one can then compute \(k-\)space Greens functions of the full model.
-Moreover, this approach holds for any \(n-\)-particle Greens function; we just need to compute the corresponding correlator in the auxiliary model.
-
-A particular example of this relation between the Greens functions is the following: static correlation functions of the form \(\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger \mathcal{O}_2 | \Psi_\text{gs}}\) can be written in terms of auxiliary model correlations:
-\begin{equation}\begin{aligned}
-	\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} \simeq \frac{1}{\lambda_{\vec k_0}^2}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1^\dagger(d) \mathcal{O}_2(d) | \psi_\text{aux}(\vec R_0, \vec a)}\\
-	\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} \simeq \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1^\dagger(z) \mathcal{O}_2(d) | \psi_\text{aux}(\vec R_0, \vec a)}~,
-\end{aligned}\end{equation}
-where \(\mathcal{O}_{1,2}\) are operators that describe the correlation we are computing, and the arguments \((d)\) and \((z)\) indicate that the corresponding operator acts at the impurity site and the bath zeroth site respectively.
+
+\section{Static correlation functions}
+This approach also holds for higher-order static correlation functions.
+For example, a general local correlation of the form \(\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\) corresponding to operators \(\mathcal{O}_1\) and \(\mathcal{O}_2\) can be estimated, using this method, in terms of auxiliary model quantities.
+For that, we first express the correlation at sites \(\vec R_0\) as well as its nearest neighbours:
+\begin{equation}\begin{aligned}
+	\frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} + \frac{1}{\mathcal{W}}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + \vec a) | \Psi_\text{gs}}\right]
+\end{aligned}\end{equation}
+This is enabled by the translation symmetry of the problem, and it allows us to involve both the impurity site and the bath zeroth site in the relations.
+By keeping only the uniform part of the ground-state wavefunction, we get
+\begin{equation}\begin{aligned}
+	\label{local_correlation}
+	\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} \simeq& \frac{1}{2\lambda_{\vec k_0}^2}\left[\frac{1}{\mathcal{W} }\braket{\psi_\text{aux}(\vec R_0) | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0) | \psi_\text{aux}(\vec R_0)} \right.
+\\
+													   &+ \left.\frac{1}{\mathcal{W}^3}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1^\dagger(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + \vec a) | \psi_\text{aux}(\vec R_0, \vec a)}\right]\\
+	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1^\dagger(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1^\dagger(z) \mathcal{O}_2(z)}_\text{aux}\right]
+\end{aligned}\end{equation}
+In the above expression, where the arguments \((d)\) and \((z)\) indicate that the corresponding operator acts at the impurity site and the bath zeroth site respectively, and the subscript \(\text{aux}\) indicates that the averaging is carried out in the impurity model.
+
+Similar expressions hold for non-local correlation functions.
+\begin{equation}\begin{aligned}
+	\label{nonlocal_correlation}
+	&\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) | \Psi_\text{gs}} \\
+	=& \frac{1}{4}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1^\dagger(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) + \mathcal{O}_1^\dagger(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1^\dagger(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \Psi_\text{gs}}\right]\\
+	\simeq& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1^\dagger(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) | \psi_\text{aux}(\vec R_0, \vec a)} \right.
+\\
+	      &\left.\braket{\psi_\text{aux}(\vec R_0, -\vec a) | \mathcal{O}_1^\dagger(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1^\dagger(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \psi_\text{aux}(\vec R_0, -\vec a)}\right]\\
+	=& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1^\dagger(d) \mathcal{O}_2(z) + \mathcal{O}_1^\dagger(z) \mathcal{O}_2(1) + \mathcal{O}_1^\dagger(z) \mathcal{O}_2(d) + \mathcal{O}_1^\dagger(1) \mathcal{O}_2(z)}_\text{aux}\right]
+\end{aligned}\end{equation}
+In the first equation, the first two terms were introduced to incorporate effects arisingfrom the bath zeroth and first sites (guided by the dynamics of the transition in the underlying extended Anderson model), while the last two terms were introduced to symmetrise the effects of choosing \(\vec R_0\) as \(d\) and \(\vec R_0 + \vec a\) as \(z\), and not other way round.
+The argument \((1)\) in the operators indicate that theu act at the first site of the bath (beyond the bath zeroth site).
+
+The next-nearest correlation function is relatively simpler, becuase only those terms contribute that involve both the impurity as well as the first site.
+If \(\vec a^\prime\) denotes the relative vector between a given site and one of its next-nearest neighbours, we can write
+\begin{equation}\begin{aligned}
+	\label{nnn_correlation}
+	\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) | \Psi_\text{gs}} =& \frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) + \mathcal{O}_1^\dagger(\vec R_0 - \vec a^\prime) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\right]\\
+	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1^\dagger(d) \mathcal{O}_2(1) + \mathcal{O}_1^\dagger(1) \mathcal{O}_2(d)}_\text{aux}\right]
+\end{aligned}\end{equation}
 
@@
 \begin{equation}\begin{aligned}
-	\chi(\vec k) &\equiv \left<\mathcal{O}_1^\dagger (-\vec k) \mathcal{O}_2(\vec k)\right> = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}} \chi(\vec r) \simeq \chi_\text{loc} + \xi_{\vec k} \chi_\text{nn} \\
-	&= \frac{1}{\lambda_{\vec k_0}^2}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1^\dagger(d) \mathcal{O}_2(d) | \psi_\text{aux}(\vec R_0, \vec a)} + \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1^\dagger(z) \mathcal{O}_2(d) | \psi_\text{aux}(\vec R_0, \vec a)}
+	\chi(\vec k) &\equiv \left<\mathcal{O}_1^\dagger (-\vec k) \mathcal{O}_2(\vec k)\right> = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}} \chi(\vec r) \simeq \chi_\text{loc} + \xi_{\vec k} \chi_\text{nn} + \Xi_{\vec k}\chi_\text{nnn}~,
+\end{aligned}\end{equation}
+where \(\chi_\text{loc},\chi_\text{nn},\chi_\text{nnn}\) are local, nearest-neighbour and next-nearest-neighbour correlation functions, with dispersions \(\xi_{\vec k} = 2\left[\cos(k_x a) + \cos\left(k_y a\right)\right] \) and \(\Xi_{\vec k} = 2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right] \).
+Following eqs.~\ref{local_correlation} through \ref{nnn_correlation}, these can be cast into impurity model correlation functions:
+\begin{equation}\begin{aligned}
+	\chi(\vec k)=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1^\dagger(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1^\dagger(z) \mathcal{O}_2(z)}_\text{aux}\right]\\
+		    &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1^\dagger(d) \mathcal{O}_2(z) + \mathcal{O}_1^\dagger(z) \mathcal{O}_2(1) + \mathcal{O}_1^\dagger(z) \mathcal{O}_2(d) + \mathcal{O}_1^\dagger(1) \mathcal{O}_2(z)}_\text{aux}\right] \\
+		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1^\dagger(d) \mathcal{O}_2(1) + \mathcal{O}_1^\dagger(1) \mathcal{O}_2(d)}_\text{aux}\right]
 \end{aligned}\end{equation}

### 2023-05-11 notes/tilingProject.tex
added expression for VNE

@@
 This approach also holds for higher-order static correlation functions.
-For example, a general local correlation of the form \(\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\) corresponding to operators \(\mathcal{O}_1\) and \(\mathcal{O}_2\) can be estimated, using this method, in terms of auxiliary model quantities.
+For example, a general local correlation of the form \(\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\) corresponding to operators \(\mathcal{O}_1\) and \(\mathcal{O}_2\) can be estimated, using this method, in terms of auxiliary model quantities.
 For that, we first express the correlation at sites \(\vec R_0\) as well as its nearest neighbours:
 \begin{equation}\begin{aligned}
-	\frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} + \frac{1}{\mathcal{W}}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + \vec a) | \Psi_\text{gs}}\right]
+	\frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} + \frac{1}{\mathcal{W}}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + \vec a) | \Psi_\text{gs}}\right]
 \end{aligned}\end{equation}
@@
 	\label{local_correlation}
-	\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} \simeq& \frac{1}{2\lambda_{\vec k_0}^2}\left[\frac{1}{\mathcal{W} }\braket{\psi_\text{aux}(\vec R_0) | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0) | \psi_\text{aux}(\vec R_0)} \right.
+	\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} \simeq& \frac{1}{2\lambda_{\vec k_0}^2}\left[\frac{1}{\mathcal{W} }\braket{\psi_\text{aux}(\vec R_0) | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \psi_\text{aux}(\vec R_0)} \right.
 \\
-													   &+ \left.\frac{1}{\mathcal{W}^3}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1^\dagger(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + \vec a) | \psi_\text{aux}(\vec R_0, \vec a)}\right]\\
-	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1^\dagger(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1^\dagger(z) \mathcal{O}_2(z)}_\text{aux}\right]
+													   &+ \left.\frac{1}{\mathcal{W}^3}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + \vec a) | \psi_\text{aux}(\vec R_0, \vec a)}\right]\\
+	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]
 \end{aligned}\end{equation}
@@
 	\label{nonlocal_correlation}
-	&\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) | \Psi_\text{gs}} \\
-	=& \frac{1}{4}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1^\dagger(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) + \mathcal{O}_1^\dagger(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1^\dagger(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \Psi_\text{gs}}\right]\\
-	\simeq& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1^\dagger(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) | \psi_\text{aux}(\vec R_0, \vec a)} \right.
+	&\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) | \Psi_\text{gs}} \\
+	=& \frac{1}{4}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) + \mathcal{O}_1(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \Psi_\text{gs}}\right]\\
+	\simeq& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) | \psi_\text{aux}(\vec R_0, \vec a)} \right.
 \\
-	      &\left.\braket{\psi_\text{aux}(\vec R_0, -\vec a) | \mathcal{O}_1^\dagger(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1^\dagger(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \psi_\text{aux}(\vec R_0, -\vec a)}\right]\\
-	=& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1^\dagger(d) \mathcal{O}_2(z) + \mathcal{O}_1^\dagger(z) \mathcal{O}_2(1) + \mathcal{O}_1^\dagger(z) \mathcal{O}_2(d) + \mathcal{O}_1^\dagger(1) \mathcal{O}_2(z)}_\text{aux}\right]
+	      &\left.\braket{\psi_\text{aux}(\vec R_0, -\vec a) | \mathcal{O}_1(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \psi_\text{aux}(\vec R_0, -\vec a)}\right]\\
+	=& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right]
 \end{aligned}\end{equation}
@@
 	\label{nnn_correlation}
-	\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) | \Psi_\text{gs}} =& \frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1^\dagger(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) + \mathcal{O}_1^\dagger(\vec R_0 - \vec a^\prime) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\right]\\
-	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1^\dagger(d) \mathcal{O}_2(1) + \mathcal{O}_1^\dagger(1) \mathcal{O}_2(d)}_\text{aux}\right]
+	\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) | \Psi_\text{gs}} =& \frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) + \mathcal{O}_1(\vec R_0 - \vec a^\prime) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\right]\\
+	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\chi(\vec r) = \left<\mathcal{O}_1^\dagger (\vec R + \vec r) \mathcal{O}_2(\vec R)\right> = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\left<\mathcal{O}_1^\dagger (\vec q) \mathcal{O}_2(\vec k)\right>
+	\chi(\vec r) = \left<\mathcal{O}_1 (\vec R + \vec r) \mathcal{O}_2(\vec R)\right> = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right>
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\chi(\vec r) = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\delta_{\vec k + \vec q, 0}\left<\mathcal{O}_1^\dagger (\vec q) \mathcal{O}_2(\vec k)\right> = \frac{1}{N}\sum_{\vec k} e^{-i \vec k \cdot \vec r}\left<\mathcal{O}_1^\dagger (-\vec k) \mathcal{O}_2(\vec k)\right>
+	\chi(\vec r) = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\delta_{\vec k + \vec q, 0}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right> = \frac{1}{N}\sum_{\vec k} e^{-i \vec k \cdot \vec r}\left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right>
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\chi(\vec k) &\equiv \left<\mathcal{O}_1^\dagger (-\vec k) \mathcal{O}_2(\vec k)\right> = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}} \chi(\vec r) \simeq \chi_\text{loc} + \xi_{\vec k} \chi_\text{nn} + \Xi_{\vec k}\chi_\text{nnn}~,
+	\chi(\vec k) &\equiv \left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right> = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}} \chi(\vec r) \simeq \chi_\text{loc} + \xi_{\vec k} \chi_\text{nn} + \Xi_{\vec k}\chi_\text{nnn}~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\chi(\vec k)=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1^\dagger(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1^\dagger(z) \mathcal{O}_2(z)}_\text{aux}\right]\\
-		    &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1^\dagger(d) \mathcal{O}_2(z) + \mathcal{O}_1^\dagger(z) \mathcal{O}_2(1) + \mathcal{O}_1^\dagger(z) \mathcal{O}_2(d) + \mathcal{O}_1^\dagger(1) \mathcal{O}_2(z)}_\text{aux}\right] \\
-		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1^\dagger(d) \mathcal{O}_2(1) + \mathcal{O}_1^\dagger(1) \mathcal{O}_2(d)}_\text{aux}\right]
-\end{aligned}\end{equation}
+	\chi(\vec k)=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]\\
+		    &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right] \\
+		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
+\end{aligned}\end{equation}
+
+\section{Momentum-space entanglement}
+The density matrix of the full Hamiltonian in ground-state is simply \(\rho = \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\).
+In order to calculate entanglement measures in and among \(k-\)space states, we begin by obtaining an expression for the von-Neumann entropy of a \(\vec k-\)state, in terms of auxiliary model computables.
+The reduced density matrix for the momentum state involves a partial trace over its configurations:
+\begin{equation}\begin{aligned}
+	\rho_{\vec k,\sigma} = \sum_{n_{\vec k,\sigma}=0,1}\braket{n_{k,\sigma} | \Psi_\text{gs}}\braket{\Psi_\text{gs} | n_{\vec k,\sigma}} = \sum_{n_{\vec k,\sigma}=0,1}|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2
+\end{aligned}\end{equation}
+where \(\ket{n_{\vec k,\sigma}}\) represents a state in Fock space with \(n_{\vec k,\sigma}\) number of particles in the single particle state with momentum \(\vec k\) and spin \(\sigma\).
+We now Fourier transform the overlap and retain terms up to the next-nearest neighbour:
+\begin{equation}\begin{aligned}
+	|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2 \simeq \braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0,\sigma} | \Psi_\text{gs}} + \xi_{\vec k}\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a,\sigma} | \Psi_\text{gs}} + \Xi_{\vec k}\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a^\prime,\sigma} | \Psi_\text{gs}}
+\end{aligned}\end{equation}
+where \(\vec a\) and \(\vec a^\prime\) are nearest and next-nearest neighbour sites to \(\vec R_0\), and \(\xi_{\vec k}\) and \(\Xi_{\vec k}\) have been defined above.
+Following the eqs.~\ref{local_correlation} through \ref{nnn_correlation}, we can identify \(\hat O_1^\dagger(\vec R) = \hat O_2(\vec R) = \ket{n_{\vec R_0,\sigma}}\bra{n_{\vec R,\sigma}}\), so that we have, for example, \(\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a,\sigma} | \Psi_\text{gs}} = \braket{\hat O_1(\vec R_0) \hat O_2(\vec R_0 + \vec a)}\).
+The, using eqs.~\ref{local_correlation} through \ref{nnn_correlation}, the Fourier transform becomes:
+\begin{equation}\begin{aligned}
+	|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2 \simeq& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux} | n_{d,\sigma}}\braket{n_{d,\sigma} | \psi_\text{aux}} + \frac{1}{\mathcal{W}}\braket{\psi_\text{aux} | n_{z,\sigma}}\braket{n_{z,\sigma} | \psi_\text{aux}}\right]\\
+							      &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{z,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{d,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{z,\sigma}}\right) \psi_\text{aux}}\right] \\
+		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{d,\sigma}}\right) \psi_\text{aux}}\right]
+\end{aligned}\end{equation}
+The \(k-\)space reduced density matrix takes the form
+\begin{equation}\begin{aligned}
+	\rho_{\vec k,\sigma} =& \sum_{n_{(d,z,1),\sigma}=0,1}\frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux} | n_{d,\sigma}}\braket{n_{d,\sigma} | \psi_\text{aux}} + \frac{1}{\mathcal{W}}\braket{\psi_\text{aux} | n_{z,\sigma}}\braket{n_{z,\sigma} | \psi_\text{aux}}\right]\\
+							      &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{z,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{d,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{z,\sigma}}\right) \psi_\text{aux}}\right] \\
+		    &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{d,\sigma}}\right) \psi_\text{aux}}\right]
+\end{aligned}\end{equation}
+The von-Neumann entropy \(S_\text{EE}(\vec k)\) can then be calculated by taking the trace of the operator \(\rho_{\vec k,\sigma}\ln \rho_{\vec k,\sigma}\).
 

### 2023-05-12 notes/tilingProject.tex
created movies and begain implementing entanglement

@@
 \begin{equation}\begin{aligned}
-	\rho_{\vec k,\sigma} =& \sum_{n_{(d,z,1),\sigma}=0,1}\frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux} | n_{d,\sigma}}\braket{n_{d,\sigma} | \psi_\text{aux}} + \frac{1}{\mathcal{W}}\braket{\psi_\text{aux} | n_{z,\sigma}}\braket{n_{z,\sigma} | \psi_\text{aux}}\right]\\
-							      &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{z,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{d,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{z,\sigma}}\right) \psi_\text{aux}}\right] \\
-		    &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{d,\sigma}}\right) \psi_\text{aux}}\right]
-\end{aligned}\end{equation}
+	\rho_{\vec k,\sigma} =& \sum_{n_{(d,z,1),\sigma}=0,1}\frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{d\sigma}} + \frac{1}{\mathcal{W}}|\alpha_{n_{z\sigma}}|^2\right]\\
+							      &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{z\sigma}} + \bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{d\sigma}} + \bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{z\sigma}} + \bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{1\sigma}}\right] \\
+		    &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{d\sigma}} + \bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{1\sigma}}\right]
+\end{aligned}\end{equation}
+where \(\bar\psi_{n_{d\sigma}} = \braket{n_{d,\sigma} | \psi_\text{aux}}\) and similar definitions exist for \(\alpha_{n_{z\sigma}}\) and \(\alpha_{n_{1\sigma}}\).
 The von-Neumann entropy \(S_\text{EE}(\vec k)\) can then be calculated by taking the trace of the operator \(\rho_{\vec k,\sigma}\ln \rho_{\vec k,\sigma}\).

### 2023-05-17 notes/tilingProject.tex
finalised the k space plots and videos of spin and pairing correlations

@@
 \begin{equation}\begin{aligned}
-	\ket{\Psi^n_{\vec k}} = \frac{1}{\mathcal{W} \sqrt N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
+	\ket{\Psi^n_{\vec k}} = \frac{1}{\sqrt{\mathcal{W} N}}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
 \end{aligned}\end{equation}
@@
 	\label{bloch-states}
-	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
+	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} \sqrt{\mathcal{W} N}}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\ket{\Psi_\text{gs}} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j, \vec a \in \text{NN of }\vec R_j} e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j, \vec a)}~,
+	\ket{\Psi_\text{gs}} = \frac{1}{\lambda_{\vec k_0} \sqrt{\mathcal{W} N}}\sum_{\vec R_j, \vec a \in \text{NN of }\vec R_j} e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j, \vec a)}~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\ket{\Psi_\text{gs}} = \sum_{\vec a \in \text{NN of}\vec R_0}\frac{1}{\mathcal{W}\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0, \vec a)} + \ket{\psi_\text{diff}(\vec k_0)}
-\end{aligned}\end{equation}
-where \(\ket{\psi_\text{diff}(\vec k_0)} = \ket{\Psi_\text{gs}} - \frac{1}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k_0} N}\sum_{\vec R_j} \left[e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j)} - e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)}\right]\).
+	\ket{\Psi_\text{gs}} = \sum_{\vec a \in \text{NN of}\vec R_0}\frac{1}{\sqrt \mathcal{W}\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0, \vec a)} + \ket{\psi_\text{diff}(\vec k_0)}
+\end{aligned}\end{equation}
+where \(\ket{\psi_\text{diff}(\vec k_0)} = \ket{\Psi_\text{gs}} - \frac{\sqrt \mathcal{W}}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)}\).
 The Greens funtion takes the form
 \begin{equation}\begin{aligned}
-G_\text{H-H}(\vec r, t) =  \frac{-i\theta(t)}{\mathcal{W}^2 \lambda_{\vec k_0}^2}\sum_{\vec a_1, \vec a_2 \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a_1) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a_2)}~.
+G_\text{H-H}(\vec r, t) =  \frac{-i\theta(t)}{\mathcal{W} \lambda_{\vec k_0}^2}\sum_{\vec a_1, \vec a_2 \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a_1) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a_2)}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}\label{greens_func_approx}
-	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) =  \frac{-i\theta(t)}{\mathcal{W}^2 \lambda_{\vec k_0}^2}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)}~.
+	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) =  \frac{-i\theta(t)}{\mathcal{W} \lambda_{\vec k_0}^2}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) &= -\frac{1}{\mathcal{W}\lambda_{\vec k_0}^2 }i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0)}~.
+	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) &= -\frac{1}{\lambda_{\vec k_0}^2 }i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0)}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G_\text{H-H}(\vec r=\vec a, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}^2}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + \vec a)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} = \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}^2} \mathcal{G}_{dz}(t)~.
+	G_\text{H-H}(\vec r=\vec a, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + \vec a)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} = \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}} \mathcal{G}_{dz}(t)~.
 \end{aligned}\end{equation}
@@
 	\label{local_correlation}
-	\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} \simeq& \frac{1}{2\lambda_{\vec k_0}^2}\left[\frac{1}{\mathcal{W} }\braket{\psi_\text{aux}(\vec R_0) | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \psi_\text{aux}(\vec R_0)} \right.
+	\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} \simeq& \frac{1}{2\lambda_{\vec k_0}^2}\left[\frac{1}{\mathcal{W} }\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0, \vec a) \mathcal{O}_2(\vec R_0) | \psi_\text{aux}(\vec R_0)} \right.
 \\
-													   &+ \left.\frac{1}{\mathcal{W}^3}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + \vec a) | \psi_\text{aux}(\vec R_0, \vec a)}\right]\\
-	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]
+													   &+ \left.\frac{1}{\mathcal{W}^2}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + \vec a) | \psi_\text{aux}(\vec R_0, \vec a)}\right]\\
+	=& \frac{1}{2\lambda_{\vec k_0}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]
 \end{aligned}\end{equation}
@@
 	=& \frac{1}{4}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) + \mathcal{O}_1(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \Psi_\text{gs}}\right]\\
-	\simeq& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) | \psi_\text{aux}(\vec R_0, \vec a)} \right.
+	\simeq& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) | \psi_\text{aux}(\vec R_0, \vec a)} \right.
 \\
 	      &\left.\braket{\psi_\text{aux}(\vec R_0, -\vec a) | \mathcal{O}_1(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \psi_\text{aux}(\vec R_0, -\vec a)}\right]\\
-	=& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right]
+	=& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right]
 \end{aligned}\end{equation}
@@
 	\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) | \Psi_\text{gs}} =& \frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) + \mathcal{O}_1(\vec R_0 - \vec a^\prime) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\right]\\
-	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
+	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\rho_{\vec k,\sigma} =& \sum_{n_{(d,z,1),\sigma}=0,1}\frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{d\sigma}} + \frac{1}{\mathcal{W}}|\alpha_{n_{z\sigma}}|^2\right]\\
+	\rho_{\vec k,\sigma} =& \sum_{n_{(d,z,1),\sigma}=0,1}\frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{d\sigma}} + \frac{1}{\mathcal{W}}\bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{z\sigma}}\right]\\
 							      &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{z\sigma}} + \bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{d\sigma}} + \bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{z\sigma}} + \bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{1\sigma}}\right] \\

### 2023-05-24 TilingProjectDraft/tilingProject.tex
finished draft for Arghya sir

--- 2023-05-17 notes/tilingProject.tex
@@
 \usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk,enumitem,cite,graphicx}
-% \usepackage[draft]{graphicx}
-\usepackage{graphicx}
+\graphicspath{{figures}}
 \usepackage[hidelinks]{hyperref}
@@
 
-\newcommand{\comment}[1]{{}}
 \setcounter{tocdepth}{1}
@@
 
-\title{\bf An Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems}
-\author{Abhirup Mukherjee, Siddhartha Lal}
-\affil{Indian Institute of Science Education and Research Kolkata, Mohanpur}
+\title{\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems}
+\author{Abhirup Mukherjee, N.S. Vidhyadhiraja, A. Taraphder, Siddhartha Lal}
+% \affil{Indian Institute of Science Education and Research Kolkata, Mohanpur}
 \date{\today}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{../figures/dos_diff.pdf}
+\includegraphics[width=0.5\textwidth]{dos_diff.pdf}
 \caption{Various kinds of bath that an impurity can hybridise into.
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/cluster-bath.pdf}
+	\includegraphics[width=0.8\textwidth]{cluster-bath.pdf}
 	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$.
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/dmft.pdf}
+	\includegraphics[width=0.8\textwidth]{dmft.pdf}
 \end{figure}
@@
 \begin{gather}
-\mathcal{H}_\text{aux} = H_\text{SIAM} + J \vec{S}_d\cdot\vec{s}_0\\
-\mathcal{H}_\text{aux} = H_\text{SIAM} + J \vec{S}_d\cdot\vec{s}_0 - U_b \left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
+\mathcal{H}_\text{aux} = H_\text{SIAM} + J \vec{S}_d\cdot\vec{s}_0 - \frac{1}{2}U_b \left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
 \end{gather}
-The first example has a spin-exchange interaction between the impurity site and the zeroth site, while the second example additionally has a correlation locally on the zeroth site.
+The additional terms are (i) a spin-exchange interaction between the impurity site and the zeroth site, and (ii) a local correlation on the zeroth site.
 \item[2.] The second method is to make the cluster itself more complicated. That is, one can introduce multiple impurity sites that are connected via the hopping:
@@
  	\centering
- 	\includegraphics[width=0.6\textwidth]{../figures/gen_siam.pdf}
+ 	\includegraphics[width=0.6\textwidth]{gen_siam.pdf}
  	\caption{Cluster+bath construction of auxiliary model.
@@
 
-\section{Creating \(N-\)site Hubbard Hamiltonian from Anderson impurity embedded in an interacting bath}
+\section{Creating a Hubbard-Heisenberg Hamiltonian from an extended Anderson impurity model}
 
@@
 	\label{siam_attr}
-	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
+	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
 \end{aligned}\end{equation}
@@
 where \(\lambda_{\ket{\vec k}}\) is a normalisation factor.
+
+To determine the normalisation factor, we compute the norm of the trial eigenstates:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k} | \Psi_{\vec k}} &= \frac{1}{\mathcal{W}^2 \lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, a, a^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime, \vec a^\prime) | \psi_\text{aux}(\vec R, \vec a)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, }e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime) | \psi_\text{aux}(\vec R)}\\
+					       &=\frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) | \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)}\\
+					       &= \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i (\vec{k} - \vec q)\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{q} N^2 \delta_{\vec{k},\vec q}|\braket{\psi_\text{aux}(\vec R_0) | \vec q}|^2\\
+\end{aligned}\end{equation}
+By requiring this norm to be unity, we obtain \(\lambda_{\vec k}^2 = |\braket{\psi_\text{aux}(\vec R_0) | \vec k}|^2\). In the above exercise, we defined a state 
+\begin{equation}\begin{aligned}\label{zeroth_site_average}
+	\ket{\psi_\text{aux}(\vec R)} = (1/w)\sum_{\vec a}\ket{\psi_\text{aux}(\vec R, \vec a)}~,
+\end{aligned}\end{equation}
+by averaging over the neasest neighbours of \(\vec R\), and inserted the total momentum basis \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators.
+\(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
+Because of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(\mathcal{W}\) choices.
 
@@
 The non-interacting model is simply a resonant-level model with the impurity level at zero energy.
-Such a model is exactly solvable, and the corresponding Greens functions are given by
-\begin{equation}\begin{aligned}
-	G(\omega + i\eta)_\text{aux,dd}^{(0)} = \frac{1}{\omega + i\left(\Delta + \eta\right)}, ~ ~ ~ G(\omega + i\eta)_\text{aux,dz}^{(0)} = \sum_{\vec k} G(\omega)^{(0)}_{\vec k} V G(\omega + i\eta)_\text{aux,dd}^{(0)}
-\end{aligned}\end{equation}
-where \(\Delta = \pi \rho V^2\) is the hybridisation parameter, assuming a uniform density of states \(\rho\), and \(G(\omega)^{(0)}_{\vec k}\) is the free electron Greens function at momentum \(\vec k\).
-
 Following Dyson's equation, the \(k-\)space self-energy can be obtained from the \(k-\)space Greens functions:
@@
 	\label{self-energy1}
-	\Sigma_{H-H}(\vec k,\omega) = 1/\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)} - 1/\left(G_{H-H}(\omega)\right)_{\vec k} = \left(\frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{W}}\mathcal{G}_{dz}(\omega)}\right)^{(0)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{W}}\mathcal{G}_{dz}(\omega)}~,
-\end{aligned}\end{equation}
-where the superscript \((0)\) indicates that the entire term has to be calculated from the non-interacting auxiliary model.
+	\Sigma_{H-H}(\vec k,\omega) = 1/\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)} - 1/\left(G_{H-H}(\omega)\right)_{\vec k} = \frac{\left(\lambda_{\vec k_0}^{(0)}\right)^2}{\mathcal{G}^{(0)}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{W}}\mathcal{G}^{(0)}_{dz}(\omega)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{W}}\mathcal{G}_{dz}(\omega)}~,
+\end{aligned}\end{equation}
+where the superscript \((0)\) indicates that the corresponding term has to be calculated from the non-interacting auxiliary model.
 
@@
 
-\section{Evidence for the Mott MIT}
-Through the URG study of the extended SIAM with correlation (eq.~\ref{siam_attr}), we can conclude the following about that model:
-\begin{itemize}
-	\item For \(U_b > J/4\), the couplings \(J\) and \(V\) become irrelevant while \(U\) is relevant, which means that \textbf{the impurity gets cut off from the bath at low energies}.
+\section{The Mott MIT: a local perspective}
+\subsection{Gapping of the local spectral function and vanishing of correlations}
+At a critical value \(U_b = -J/4\) of the local correlation \(U_b\) on the bath zeroth site, the couplings \(J\) and \(V\) of the auxiliary model become irrelevant while \(U\) becomes remains non-zero, leading to a low-energy phase where the impurity is cutt off from the conduction bath.
+This is the local moment phase, where low-energy excitations have been gapped out.
 \begin{figure}[htpb]
 	\centering
-	\includegraphics[width=0.48\textwidth]{../figures/phase-map-MIT.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/spectral-function-(0, 0).pdf}
-	\caption{{\it Left:} Phase diagram. {\it Right:} Local spectral function on impurity site}
+	\includegraphics[width=0.48\textwidth]{phase-map-MIT.pdf}
+	\includegraphics[width=0.48\textwidth]{spectral-function_dd.pdf}
+	\caption{{\it Left:} Phase diagram of the extended SIAM auxiliary model.
+As the parameter \(r\) is tuned through 0.25, the metallic blue phase changes into the insulating violet phase.
+{\it Right:} Local spectral function of the auxiliary model.
+It shows a hard gap for \(r/r_c > 1\).}
 	\label{spec_func_mit}
 \end{figure}
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.32\textwidth]{../figures/kspace_specfunc_0.0000_0.0000.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/kspace_specfunc_0.0000_1.5708.pdf}
-	\includegraphics[width=0.32\textwidth]{../figures/kspace_specfunc_1.5708_1.5708.pdf}
-	\caption{Momentum-space spectral functions \(A_{\vec k}(\omega)\)}
-\end{figure}
-
-\item The impurity spectral function \(\mathcal{A}_{dd}(\omega)\) and the impurity-bath real space off-diagonal Greens function \(\mathcal{A}_{d0}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
+
+The impurity local spectral function \(\mathcal{A}_{dd}(\omega)\) and the impurity-bath real space off-diagonal spectral function \(\mathcal{A}_{d0}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
 We show the former in fig.~\ref{spec_func_mit}.
-The gap in the diagonal spectral function show the absence of any gapless excitations that can allow the impurity configuration to, while the vanishing of the off-diagonal spectral function shows that this is because the entanglement between the impurity and the bath has been pinched out.
-Other measures like mutual information and spin-spin correlations also show a sharp change on crossing that value, demonstrating \textbf{the destruction of the Kondo cloud and the stabilisation of the local moment on the impurity}.
+The gap in the former shows the absence of any gapless excitations that can allow the impurity configuration to fluctuate, while the vanishing of the off-diagonal spectral function shows that this is because the entanglement between the impurity and the bath has been quenched.
+
+In Fig.~\ref{spin-charge-correlations}, we show the behaviour of the spin-flip and charge isospin-flip correlations between two neighbouring real space sites, as well as the mutual real space entanglement and mutual information.
+Both show a sharp fall on crossing the transition, demonstrating the destruction of the Kondo cloud and the stabilisation of the local moment on the impurity.
+Importantly, they charge correlations show a rise very close to the transition (can be seen as a single elevated blue point near \(r = 0.25\) in the left panel of Fig.~\ref{spin-charge-correlations}); this indicates that the transition is precipitated by the growth of pairing correlations.
 
@@
 \centering
-	% \includegraphics[width=0.48\textwidth]{../figures/corrs_gs.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/spin-charge-corr-full.pdf}
-	\includegraphics[width=0.48\textwidth]{../figures/impEE-mutinfo-d0.pdf}
-	% \includegraphics[width=0.48\textwidth]{../figures/doub_occ.pdf}
-\end{figure}
-
-	\item In the context of the auxiliary model, this represents an \textbf{impurity phase transition} from the completely-screened spin-singlet phase to the unscreened local moment phase.
-
+	\includegraphics[width=0.48\textwidth]{spin-charge-corr-full.pdf}
+	\includegraphics[width=0.48\textwidth]{impEE-mutinfo-d0.pdf}
+	\caption{{\it Left}: Spin-flip correlations(red) and charge-flip correlations(blue) in real space.
+The former increases as the system moves into the Kondo regime, and then vanishes at the transition.
+The latter decreases as the charge content is removed from the ground state in the Kondo regime, but shows a sudden increase at the transition.
+{\it Right}: Real space Entanglement and mutual information.
+Both vanish in the local moment phase.}
+	\label{spin-charge-correlations}
+\end{figure}
+
+\subsection{Value of the critical paramter for the bulk model}
 Using the mappings between the auxiliary model parameters and the bulk parameters (eq.~\ref{map_aux_bulk}), one can define a critical value \(r^{*}\) of the ratio \(r = U_{H-H}/J_{H-H}\) at the critical points \(-U_b/J=1/4\) \textit{for a given and fixed value of \(U\)}.
@@
 The reduction in the value of \(r\) from \(2.5\) in the auxiliary model to \(~1.1\) in the bulk model can be attributed to (i) the reduction in the effective bulk repulsion \(U\) due to the competition coming from the attractive \(U_b\), and (ii) increased hybdridisation through \(J\) due to the presence of multiple auxiliary models that connect two lattice sites.
-% In general, $\mathcal{W}=2d$ for the $d$-dimensional hypercubic lattice, and 
-% $r^{*}_\text{hyperc.} = \frac{d}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{2}\right)$.
-The growth of $r^{*}$ with $d$ indicates that the MIT is increasingly rendered difficult in a higher dimensional hypercubic lattice, as it is easier for electrons to delocalise and a very large on-site repulsion is needed to overcome this.
-\end{itemize}
-
-\comment{
-\section{\(k-\)space picture of the MIT in terms of the momentum-resolved self-energy \(\Sigma(\vec k,\omega)\)}
-
-From the self-energy expressions obtained above, one can track the self-energy of the lattice model through the metal-insulator transition.
-In fig.~\ref{four-self}, we have provided these plots at specific values of \(U_b/J\) to show how the transition plays out in the Brillouin zone.
-{\it These plots can also be viewed as a video \href{https://abhirup-m.github.io/misc-sigma/}{\underline{here}}.}
-
-\begin{center}
-\begin{tabular}{c|c}
-\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.02500-4.pdf} &
-\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.10310-4.pdf}\\
-\hline
-\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.15735-4.pdf} &
-\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.23594-4.pdf}\\
-\hline
-\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=-0.25000-4.pdf} &
-\includegraphics[height=0.3\textheight]{../figures/sigma-4-Ub_by_J=0.25010-4.pdf}
-\end{tabular}
-\captionof{figure}{Each of the 6 frames shows \(A(\vec k)\) at four values of \(\omega\).
-First 4 are before the transition (\(-U_b/J < 0.25\)), fifth is exactly at the transition \((-U_b/J = 0.25)\) and last one is after the transition (\(-U_b/J > 0.25\)).
-Available as video \href{https://abhirup-m.github.io/misc-sigma/}{\underline{here}}.}
-\label{four-self}
-\end{center}
-
-In each frame, the top left figure represents the self-energy at \(\omega=0\).
-If we track this particular figure across the frames, we find that at small \(-U_b/J\), the self-energy near the Fermi surface was smaller than those near the Brillouin zone edges, indicating the presence of a prominent Fermi liquid.
-As \(U_b\) increases, we find that this distinction of the Fermi surface becomes less-prominent; at the critical point,we see that the self-energy near the Fermi surface self-energy has become more than that near the edges, signalling that the quasiparticle excitations have become scrambled because of the increased correlations in the bath.
-
-If we, on the other hand, track the bottom right figure in each frame (\(\omega = U/2\)), we find that deep in the metallic regime, the self-energy is quite high.
-This is because of the low spectral weight at large \(\omega\).
-As the correlations are increased, we find that  this self-energy decreases, particular in comparison to the values at the Brillouin zone edges.
-This is because of the appearance of the Hubbard side-peaks in the local spectral function
-.
-
-In the insulating phase, we find that the momentum-dependence has vanished (the system is in the perfectly local atomic limit).
-The self-energy at the Hubbard side-bands (bottom right) is high, because the quasiparticle excitations are highly-renormalised and the single-particle picture description is not possible.
-The self-energy inside the gap (other three figures) diverges and the poles of the Greens function have been replaced by zeroes, so we have instead plotted the inverse self-energy.
-
-These plots are available as videos \href{https://abhirup-m.github.io/misc-sigma/}{\underline{here}}.
-}
-
-\section{Some important remarks}
-\subsection{Entanglement as an order parameter for the transition}
-More refined version exists in the e-SIAM manuscript.
-
-\subsection{Topological nature of the transition}
+
+\section{Momentum-space picture of the MIT}
+In order to understand the nature of the transition in momentum space, we employ the expression obtained in the previous sections and compute the spectral function, self-energy and correlation functions in the top right quadrant of the first Brillouin zone.
+We first show the \(k-\)space spectral functions near zero frequency, in Fig.~\ref{kspace_specfunc}.
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=\textwidth]{kspace-spectral-function-all.pdf}\hspace{\fill}
+\caption{\(k-\)space dependence of single-particle spectral function, \(A_{\vec k}(\omega \sim 0)\), at four values of the tuning parameter \(r\).
+The \(\vec k\) values are taken from the top right quadrant of the first Brillouin zone.
+In the metallic phase (\(r < r_c\)), the spectral function shows a \(k-\)dependence, indicating the presence of gapless excitations.
+Close to the transition (and beyond it), the momentum dependence gets removed and there is no spectral weight left in the infrared regime.}
+\label{kspace_specfunc}
+\end{figure}
+
+In Fig.~\ref{kspace_selfenergy}, we plot the momentum dependence of the single-particle self-energy, similar to the spectral function.
+The self-energy is flat in \(k-\)space away from the transition, consistent with the fact that the correlations are small in that regime.
+Close to the transition, the correlations pick up, and lead to a momentum-dependence of the self-energy, renormalising the Fermi liquid in the process and ultimately destroying it.
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=\textwidth]{kspace-imagsigma-all.pdf}\hspace{\fill}
+\caption{\(k-\)space dependence of imaginary part of the self-energy, \(\Sigma_{\vec k}(\omega \sim 0)\), at four values of the tuning parameter \(r\).
+In the metallic phase (\(r \ll r_c\)), the self-energy is quite small, indicating that the phase consists of an uncorrelated Fermi liquid.
+It increases close to the transition (and beyond it).}
+\label{kspace_selfenergy}
+\end{figure}
+
+In Figs.~\ref{spin_kspace},\ref{charge_kspace} and \ref{pair_kspace}, we show the momentum dependence of two-particle correlation functions.
+In every figure, each panel shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
+Moving from the left panel to the right is equivalent to moving upwards in the top right quadrant of the first Brillouin zone.
+In each panel, moving upwards amounts to tuning the system towards the transition.
+The spin-spin correlations (in Fig.~\ref{spin_kspace}) are large near the \(\vec k = \left( 0,0 \right) \) point, presumably because of the dominance of the Kondo cloud at long wavelengths.
+They vanish in the local moment phase (flat blue region near the top).
+The charge and pairing correlations (Figs.~\ref{charge_kspace} and \ref{pair_kspace}) disappear as the system moves into the Kondo regime, but reappear exactly at the transition.
+This is tied to the non-Fermi liquid theory at the QCP, as seen in the auxiliary model.
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=\textwidth]{spin_kspace_all.pdf}
+\caption{Momentum dependence of spin-spin correlation \(\left<\vec{S}_{-\vec k}\cdot\vec{S}_{\vec k} \right>\).
+Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
+Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone.
+In each figure, moving upwards amounts to tuning the system towards the transition.
+The flat blue region at the top is the local moment phase, void of any non-local correlations.}
+\label{spin_kspace}
+\end{figure}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=\textwidth]{charge_kspace_all.pdf}
+\caption{Momentum dependence of charge-charge correlation \(\left<\vec{C}_{-\vec k}\cdot\vec{C}_{\vec k} \right>\), where \(\vec C\) is the charge isospin associated with the doublet formed by the doublon and holon states.
+Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
+Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone.
+In each figure, moving upwards amounts to tuning the system towards the transition.
+The flat blue region at the top is the local moment phase, void of any non-local correlations.}
+\label{charge_kspace}
+\end{figure}
+
+\begin{figure}[!htb]
+\includegraphics[width=\textwidth]{pair_kspace_all.pdf}
+\caption{Momentum dependence of pairing correlation \(\left<c^\dagger_{-k\uparrow}c^\dagger_{-k\downarrow}c_{k\downarrow}c_{k\uparrow}\right>\).
+Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
+Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone.
+In each figure, moving upwards amounts to tuning the system towards the transition.
+The flat blue region at the top is the local moment phase, void of any non-local correlations.}
+\label{pair_kspace}
+\end{figure}
+
+{\color{blue} In order to provide a second way of visualising these correlations, we have provided some videos that show their variation in the \(k_x-k_y\) plane as a function of \(r/r_c\).
+The videos for the spin-spin correlation and the pairing correlations are named ``ss\_rspace.gif" and ``pairing\_rspace.gif", respectively.
+Each frame of the video shows a colormap of the correlation in the top right quadrant of the first Brillouin zone, at a {\it specific value of \(r\)}.
+The movie then shows the {\it evolution of this \(k-\)space colormap} as \(r\) is tuned towards and into the transition.}
+
+\section{Topological nature of the transition}
 Since the impurity charge hybridising with the bath contributes to the total Luttinger volume of the system~\cite{martin1982fermi}, decoupling of the impurity from the conduction bath leads to a difference in the value of the Luttinger volume between the local moment (LM) and the strong-coupling (SC) fixed points.
@@
 	\centering
-	\includegraphics[scale=0.2]{../figures/luttinger_top_change.png}
+	\includegraphics[scale=0.2]{luttinger_top_change.png}
 	\caption{The green lines describe the winding number related to the impurity Greens function, while the blue lines do it for the bath.
@@
 
-\subsection{Greens function in the insulating phase: the Hubbard bands and mottness}
+\section{Greens function in the insulating phase: the Hubbard bands and mottness}
 In the insulating state, the cluster becomes a local moment and the bulk system reduces to the atomic limit \(H = -\frac{U}{2}\sum_i\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\).
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/hubbard_bands.pdf}
+	\includegraphics[width=0.5\textwidth]{hubbard_bands.pdf}
 	\caption{Structure of the Greens function in the atomic limit.
@@
 
-\subsection{Nature of propagation: metal vs insulator}
+\section{Nature of propagation: metal vs insulator}
 In the metallic state, the impurity in the auxiliary model hybridises with the bath through both 1-particle and 2-particle interactions.
@@
 	\centering
-	\includegraphics[width=0.55\textwidth]{../figures/metal_prop.pdf}
+	\includegraphics[width=0.55\textwidth]{metal_prop.pdf}
 	\caption{Propagation of electrons from one cluster to another through the bath, in the metallic state}
@@
 	\centering
-	\includegraphics[width=0.75\textwidth]{../figures/ins_prop.pdf}
+	\includegraphics[width=0.75\textwidth]{ins_prop.pdf}
 	\caption{The clusters get isolated from each other in the insulator, because they get decoupled from their baths.}
@@
 	\centering
-	\includegraphics[width=0.85\textwidth]{../figures/ins_prop_cluster.pdf}
+	\includegraphics[width=0.85\textwidth]{ins_prop_cluster.pdf}
 	\caption{Each cluster is a quantum liquid composed of spin \(\left(\uparrow,\downarrow\right) \) and charge \(\left(0,2\right) \) degrees of freedom.
@@
 
-\subsection{Presence of two self-energies under symmetry-breaking}
+\section{Presence of two self-energies under symmetry-breaking}
 The effective Hamiltonian that describes either the metallic or the insulating phase has $\mathrm{SU}(2)$ symmetry in both the spin and charge sectors.
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{../figures/dimer-peaks.png}
+	\includegraphics[width=0.9\textwidth]{dimer-peaks.png}
 	\caption{Position, weight and nature of each of the peaks in the Hubbard dimer site local spectral function}
@@
 \chapter{Properties of the Bloch states}
-To determine this, we compute the norm of the trail eigenstates:
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k} | \Psi_{\vec k}} &= \frac{1}{\mathcal{W}^2 \lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, a, a^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime, \vec a^\prime) | \psi_\text{aux}(\vec R, \vec a)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, }e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime) | \psi_\text{aux}(\vec R)}\\
-					       &=\frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) | \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)}\\
-					       &= \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i (\vec{k} - \vec q)\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{q} N^2 \delta_{\vec{k},\vec q}|\braket{\psi_\text{aux}(\vec R_0) | \vec q}|^2\\
-\end{aligned}\end{equation}
-By requiring this norm to be unity, we obtain \(\lambda_{\vec k}^2 = |\braket{\psi_\text{aux}(\vec R_0) | \vec k}|^2\). In the above exercise, we defined a state 
-\begin{equation}\begin{aligned}\label{zeroth_site_average}
-	\ket{\psi_\text{aux}(\vec R)} = (1/w)\sum_{\vec a}\ket{\psi_\text{aux}(\vec R, \vec a)}~,
-\end{aligned}\end{equation}
-by averaging over the neasest neighbours of \(\vec R\), and inserted the total momentum basis \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators.
-\(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
-Because of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(\mathcal{W}\) choices.
-
+
+\section{Translation invariance}
 It is easy to verify that \(\Psi_{\vec k}\left(\left\{ \vec r_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \(\vec R\):
@@
 
+\section{Orthonormality}
 It is straightforward to show that these states form an orthonormal basis. We start by writing down the inner product of two distinct such states:
@@
 
+\section{Eigenstates}
 To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:

### 2023-05-26 TilingProjectDraft/tilingProject.tex
recalculated VNE in kspace with more terms

@@
 \documentclass{report}
-\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,authblk,enumitem,cite,graphicx}
-\graphicspath{{figures}}
+\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,enumitem,cite,graphicx}
 \usepackage[hidelinks]{hyperref}
@@
 \section{Momentum-space entanglement}
+\subsection{\(k-\)space von-Neumann entropy}
 The density matrix of the full Hamiltonian in ground-state is simply \(\rho = \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\).
-In order to calculate entanglement measures in and among \(k-\)space states, we begin by obtaining an expression for the von-Neumann entropy of a \(\vec k-\)state, in terms of auxiliary model computables.
+In order to calculate entanglement measures in and among \(k-\)space states, we begin by obtaining an expression for the von-Neumann entropy of a \(\vec k-\)state, in terms of auxiliary model quantities.
 The reduced density matrix for the momentum state involves a partial trace over its configurations:
@@
 \begin{equation}\begin{aligned}
-	|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2 \simeq \braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0,\sigma} | \Psi_\text{gs}} + \xi_{\vec k}\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a,\sigma} | \Psi_\text{gs}} + \Xi_{\vec k}\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a^\prime,\sigma} | \Psi_\text{gs}}
+	|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2 \simeq& |\braket{n_{\vec R_0,\sigma} | \Psi_\text{gs}}|^2  + \xi_{\vec k}^2|\braket{n_{\vec R_0 + \vec a,\sigma} | \Psi_\text{gs}}|^2 + \Xi_{\vec k}^2|\braket{n_{\vec R_0 + \vec a^\prime,\sigma} | \Psi_\text{gs}}|^2 + 2\xi_{\vec k}\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a,\sigma} | \Psi_\text{gs}}\\
+							      & + 2\Xi_{\vec k}\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a^\prime,\sigma} | \Psi_\text{gs}} + 2\xi_{\vec k}\Xi_{\vec k}\braket{\Psi_\text{gs} | n_{\vec R_0 + \vec a^\prime,\sigma}}\braket{n_{\vec R_0 + \vec a,\sigma} | \Psi_\text{gs}}\\
+	=& \left(1 + \xi_{\vec k}^2 + \Xi_{\vec k}^2\right)|\braket{n_{\vec R_0,\sigma} | \Psi_\text{gs}}|^2 + 2\xi_{\vec k}\left(1 + \Xi_{\vec k}\right)\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a,\sigma} | \Psi_\text{gs}} \\
+							      & + 2\Xi_{\vec k}\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a^\prime,\sigma} | \Psi_\text{gs}} 
 \end{aligned}\end{equation}
@@
 Following the eqs.~\ref{local_correlation} through \ref{nnn_correlation}, we can identify \(\hat O_1^\dagger(\vec R) = \hat O_2(\vec R) = \ket{n_{\vec R_0,\sigma}}\bra{n_{\vec R,\sigma}}\), so that we have, for example, \(\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a,\sigma} | \Psi_\text{gs}} = \braket{\hat O_1(\vec R_0) \hat O_2(\vec R_0 + \vec a)}\).
-The, using eqs.~\ref{local_correlation} through \ref{nnn_correlation}, the Fourier transform becomes:
-\begin{equation}\begin{aligned}
-	|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2 \simeq& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux} | n_{d,\sigma}}\braket{n_{d,\sigma} | \psi_\text{aux}} + \frac{1}{\mathcal{W}}\braket{\psi_\text{aux} | n_{z,\sigma}}\braket{n_{z,\sigma} | \psi_\text{aux}}\right]\\
-							      &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{z,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{d,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{z,\sigma}}\right) \psi_\text{aux}}\right] \\
-		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{d,\sigma}}\right) \psi_\text{aux}}\right]
+Then, using eqs.~\ref{local_correlation} through \ref{nnn_correlation}, the Fourier transform becomes:
+\begin{equation}\begin{aligned}
+	|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2 \simeq& \frac{1 + \xi_{\vec k}^2 + \Xi_{\vec k}^2}{3\lambda_{\vec k_0}^2}\left[\braket{\psi_\text{aux} | n_{d,\sigma}}\braket{n_{d,\sigma} | \psi_\text{aux}} + \frac{1}{\mathcal{W}}\braket{\psi_\text{aux} | n_{z,\sigma}}\braket{n_{z,\sigma} | \psi_\text{aux}} + \frac{1}{\mathcal{W}}\braket{\psi_\text{aux} | n_{1,\sigma}}\braket{n_{1,\sigma} | \psi_\text{aux}}\right]\\
+							      &+ \frac{2\xi_{\vec k}\left(1 + \Xi_{\vec k}\right)}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{z,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{d,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{z,\sigma}}\right) \psi_\text{aux}}\right] \\
+							      &+ \frac{2\Xi_{\vec k}}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{d,\sigma}}\right) \psi_\text{aux}}\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\rho_{\vec k,\sigma} =& \sum_{n_{(d,z,1),\sigma}=0,1}\frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{d\sigma}} + \frac{1}{\mathcal{W}}\bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{z\sigma}}\right]\\
-							      &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{z\sigma}} + \bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{d\sigma}} + \bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{z\sigma}} + \bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{1\sigma}}\right] \\
-		    &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{d\sigma}} + \bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{1\sigma}}\right]
-\end{aligned}\end{equation}
-where \(\bar\psi_{n_{d\sigma}} = \braket{n_{d,\sigma} | \psi_\text{aux}}\) and similar definitions exist for \(\alpha_{n_{z\sigma}}\) and \(\alpha_{n_{1\sigma}}\).
+	\rho_{\vec k,\sigma} =& \sum_{n_{(d,z,1),\sigma}=0,1}\frac{1 + \xi_{\vec k}^2 + \Xi_{\vec k}^2}{3\lambda_{\vec k_0}^2}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{d\sigma}} + \frac{1}{\mathcal{W}}\bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{z\sigma}} + \frac{1}{\mathcal{W}}\bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{1\sigma}}\right] + \sum_{n_{(d,1),\sigma}=0,1}\frac{\Xi_{\vec k}}{\lambda_{\vec k_0}^2 \mathcal{W}}\left[\bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{d\sigma}} + \bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{1\sigma}}\right]\\
+							      &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{\xi_{\vec k}\left(1 + \Xi_{\vec k}\right)}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{z\sigma}} + \bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{d\sigma}} + \bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{z\sigma}} + \bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{1\sigma}}\right]
+\end{aligned}\end{equation}
+where \(\bar\psi_{n_{d\sigma}} = \braket{n_{d,\sigma} | \psi_\text{aux}}\) and similar definitions exist for \(\bar\psi_{n_{z\sigma}}\) and \(\bar\psi_{n_{1\sigma}}\).
 The von-Neumann entropy \(S_\text{EE}(\vec k)\) can then be calculated by taking the trace of the operator \(\rho_{\vec k,\sigma}\ln \rho_{\vec k,\sigma}\).

### 2023-05-29 TilingProjectDraft/tilingProject.tex
--no-message

@@
 \begin{equation}\begin{aligned}
-	\rho_{\vec k,\sigma} = \sum_{n_{\vec k,\sigma}=0,1}\braket{n_{k,\sigma} | \Psi_\text{gs}}\braket{\Psi_\text{gs} | n_{\vec k,\sigma}} = \sum_{n_{\vec k,\sigma}=0,1}|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2
+	\rho\left(\vec k\sigma\right) = \sum_{n_{\vec k,\sigma}=0,1}\braket{n_{k,\sigma} | \Psi_\text{gs}}\braket{\Psi_\text{gs} | n_{\vec k,\sigma}} = \sum_{n_{\vec k,\sigma}=0,1}|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2
 \end{aligned}\end{equation}
 where \(\ket{n_{\vec k,\sigma}}\) represents a state in Fock space with \(n_{\vec k,\sigma}\) number of particles in the single particle state with momentum \(\vec k\) and spin \(\sigma\).
-We now Fourier transform the overlap and retain terms up to the next-nearest neighbour:
+We now Fourier transform the overlap and retain terms up to the next-nearest neighbour, by expanding \(\ket{n_{\vec k\sigma}}\) as \(\ket{n_{\vec R_0,\sigma}} + \xi_{\vec k}\ket{n_{\vec R_0 + \vec a,\sigma}} + \Xi_{\vec k}\ket{n_{\vec R_0 + \vec a^\prime,\sigma}}\), where \(\vec a\) and \(\vec a^\prime\) are nearest and next-nearest neighbour sites to \(\vec R_0\), and \(\xi_{\vec k}\) and \(\Xi_{\vec k}\) have been defined above.
+The overlap takes the form
 \begin{equation}\begin{aligned}
@@
 	=& \left(1 + \xi_{\vec k}^2 + \Xi_{\vec k}^2\right)|\braket{n_{\vec R_0,\sigma} | \Psi_\text{gs}}|^2 + 2\xi_{\vec k}\left(1 + \Xi_{\vec k}\right)\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a,\sigma} | \Psi_\text{gs}} \\
-							      & + 2\Xi_{\vec k}\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a^\prime,\sigma} | \Psi_\text{gs}} 
-\end{aligned}\end{equation}
-where \(\vec a\) and \(\vec a^\prime\) are nearest and next-nearest neighbour sites to \(\vec R_0\), and \(\xi_{\vec k}\) and \(\Xi_{\vec k}\) have been defined above.
+	 & + 2\Xi_{\vec k}\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a^\prime,\sigma} | \Psi_\text{gs}}~.\label{overlap_ftransform}
+\end{aligned}\end{equation}
 Following the eqs.~\ref{local_correlation} through \ref{nnn_correlation}, we can identify \(\hat O_1^\dagger(\vec R) = \hat O_2(\vec R) = \ket{n_{\vec R_0,\sigma}}\bra{n_{\vec R,\sigma}}\), so that we have, for example, \(\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a,\sigma} | \Psi_\text{gs}} = \braket{\hat O_1(\vec R_0) \hat O_2(\vec R_0 + \vec a)}\).
@@
 \begin{equation}\begin{aligned}
-	|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2 \simeq& \frac{1 + \xi_{\vec k}^2 + \Xi_{\vec k}^2}{3\lambda_{\vec k_0}^2}\left[\braket{\psi_\text{aux} | n_{d,\sigma}}\braket{n_{d,\sigma} | \psi_\text{aux}} + \frac{1}{\mathcal{W}}\braket{\psi_\text{aux} | n_{z,\sigma}}\braket{n_{z,\sigma} | \psi_\text{aux}} + \frac{1}{\mathcal{W}}\braket{\psi_\text{aux} | n_{1,\sigma}}\braket{n_{1,\sigma} | \psi_\text{aux}}\right]\\
-							      &+ \frac{2\xi_{\vec k}\left(1 + \Xi_{\vec k}\right)}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{z,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{d,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{z,\sigma}}\right) \psi_\text{aux}}\right] \\
-							      &+ \frac{2\Xi_{\vec k}}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{d,\sigma}}\right) \psi_\text{aux}}\right]
-\end{aligned}\end{equation}
+|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2 \simeq& \frac{1 + \xi_{\vec k}^2 + \Xi_{\vec k}^2}{3\lambda_{\vec k_0}^2}\left[\braket{n_{d,\sigma} | \rho_\text{aux} | n_{d,\sigma}} + \frac{1}{\mathcal{W}}\braket{n_{z,\sigma} | \rho_\text{aux} | n_{z,\sigma}} + \frac{1}{\mathcal{W}}\braket{n_{1,\sigma} | \rho_\text{aux} | n_{1,\sigma}}\right]\\
+							      &+ \frac{2\xi_{\vec k}\left(1 + \Xi_{\vec k}\right)}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{n_{d,\sigma} | \rho_\text{aux} | n_{z,\sigma}} + \braket{n_{z,\sigma} | \rho_\text{aux} | n_{d,\sigma}} + \braket{n_{z,\sigma} | \rho_\text{aux} | n_{1,\sigma}} + \braket{n_{1,\sigma} | \rho_\text{aux} | n_{z,\sigma}} \right] \\
+							      &+ \frac{2\Xi_{\vec k}}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{n_{1,\sigma} | \rho_\text{aux} | n_{d,\sigma}} + \braket{n_{d,\sigma} | \rho_\text{aux} | n_{1,\sigma}}\right]
+\end{aligned}\end{equation}
+where \(\rho_\text{aux} \equiv \ket{\psi_\text{aux}}\bra{\psi_\text{aux}}\) is the density matrix corresponding to the auxiliary model ground state.
 The \(k-\)space reduced density matrix takes the form
 \begin{equation}\begin{aligned}
-	\rho_{\vec k,\sigma} =& \sum_{n_{(d,z,1),\sigma}=0,1}\frac{1 + \xi_{\vec k}^2 + \Xi_{\vec k}^2}{3\lambda_{\vec k_0}^2}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{d\sigma}} + \frac{1}{\mathcal{W}}\bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{z\sigma}} + \frac{1}{\mathcal{W}}\bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{1\sigma}}\right] + \sum_{n_{(d,1),\sigma}=0,1}\frac{\Xi_{\vec k}}{\lambda_{\vec k_0}^2 \mathcal{W}}\left[\bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{d\sigma}} + \bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{1\sigma}}\right]\\
-							      &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{\xi_{\vec k}\left(1 + \Xi_{\vec k}\right)}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{z\sigma}} + \bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{d\sigma}} + \bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{z\sigma}} + \bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{1\sigma}}\right]
-\end{aligned}\end{equation}
-where \(\bar\psi_{n_{d\sigma}} = \braket{n_{d,\sigma} | \psi_\text{aux}}\) and similar definitions exist for \(\bar\psi_{n_{z\sigma}}\) and \(\bar\psi_{n_{1\sigma}}\).
-The von-Neumann entropy \(S_\text{EE}(\vec k)\) can then be calculated by taking the trace of the operator \(\rho_{\vec k,\sigma}\ln \rho_{\vec k,\sigma}\).
+	\rho\left(\vec k\sigma\right) =& \sum_{n_{(d,z,1),\sigma}=0,1}\frac{1 + \xi_{\vec k}^2 + \Xi_{\vec k}^2}{3\lambda_{\vec k_0}^2}\left[\braket{n_{d,\sigma} | \rho_\text{aux} | n_{d,\sigma}} + \frac{1}{\mathcal{W}}\braket{n_{z,\sigma} | \rho_\text{aux} | n_{z,\sigma}} + \frac{1}{\mathcal{W}}\braket{n_{1,\sigma} | \rho_\text{aux} | n_{1,\sigma}}\right] \\
+				       &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{\xi_{\vec k}\left(1 + \Xi_{\vec k}\right)}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{n_{d,\sigma} | \rho_\text{aux} | n_{z,\sigma}} + \braket{n_{z,\sigma} | \rho_\text{aux} | n_{d,\sigma}} + \braket{n_{z,\sigma} | \rho_\text{aux} | n_{1,\sigma}} + \braket{n_{1,\sigma} | \rho_\text{aux} | n_{z,\sigma}} \right]\label{density_matrix_ksapce}\\
+				       &+ \sum_{n_{(d,1),\sigma}=0,1}\frac{\Xi_{\vec k}}{\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{n_{1,\sigma} | \rho_\text{aux} | n_{d,\sigma}} + \braket{n_{d,\sigma} | \rho_\text{aux} | n_{1,\sigma}}\right]~.
+\end{aligned}\end{equation}
+The von-Neumann entropy \(S_\text{EE}(\vec k)\) can then be calculated by taking the trace of the operator \(\rho\left(\vec k\sigma\right)\ln \rho\left(\vec k\sigma\right)\).
+
+\subsection{\(k-\)space mutual information}
+Another measure of manybody correlations would be the mutual information between two momentum-space states.
+For eg., the mutual information \(I_2\) between the states \(\ket{\vec k, \sigma}\) and \(\ket{-\vec k, \sigma}\) is defined as
+\begin{equation}\begin{aligned}
+	I_2(\vec :-\vec k) = S_\text{EE}(\vec k) + S_\text{EE}(-\vec k) - S_\text{EE}(\vec k,-\vec k)~,
+\end{aligned}\end{equation}
+where \(S_\text{EE}(\pm\vec k)\) is the von-Neumann entropy associated with the reduced density matrix \(\rho\left(\vec k\sigma\right)\) that has \(\pm \vec k\) traced out, and \(S_\text{EE}(\vec k,-\vec k)\) is associated with the density matrix \(\rho\left(\vec k \sigma, -\vec k \sigma\right)\) that has both \(\vec k\) and \(-\vec k\) traced out.
+\(\rho\left(\vec k\sigma\right)\) has already been computed in eq.~\ref{density_matrix_ksapce}.
+In order to calculate \(\rho\left(\vec k \sigma, -\vec k \sigma\right)\), we trace out the configurations of \(-\vec k\) from the density matrix \(\rho\left(\vec k\sigma\right)\):
+\begin{equation}\begin{aligned}
+	\rho\left(\vec k \sigma, -\vec k \sigma\right) = \sum_{n_{-\vec k\sigma}=0,1} \braket{n_{-\vec k\sigma}| \rho\left(\vec k\sigma\right) | n_{-\vec k\sigma}}
+\end{aligned}\end{equation}
+By following an approach similar to the one that led to eq.~\ref{overlap_ftransform}, we Fourier transform the \(k-\)space terms:
+\begin{equation}\begin{aligned}
+	&\rho\left(\vec k \sigma, -\vec k \sigma\right) \\
+	&= \sum_{n_{(\vec R_0,\vec R_0 + \vec a,\vec R_0  +\vec a^\prime),\sigma}=0,1}\left[\braket{n_{\vec R_0,\sigma}| \rho\left(\vec k\sigma\right) | n_{\vec R_0, \sigma}} + \xi_{-\vec k}^2\braket{n_{\vec R_0 + \vec a,\sigma}| \rho\left(\vec k\sigma\right) | n_{\vec R_0 + \vec a, \sigma}} + \Xi_{-\vec k}^2\braket{n_{\vec R_0 + \vec a^\prime,\sigma}| \rho\left(\vec k\sigma\right) | n_{\vec R_0 + \vec a^\prime, \sigma}} \right.\\
+	&\left.+ 2\xi_{-\vec k}\braket{n_{\vec R_0 + \vec a,\sigma}| \rho\left(\vec k\sigma\right) | n_{\vec R_0, \sigma}} + 2\Xi_{-\vec k}\braket{n_{\vec R_0 + \vec a^\prime,\sigma}| \rho\left(\vec k\sigma\right) | n_{\vec R_0, \sigma}} + 2\xi_{-\vec k}\Xi_{-\vec k}\braket{n_{\vec R_0 + \vec a^\prime,\sigma}| \rho\left(\vec k\sigma\right) | n_{\vec R_0 + \vec a, \sigma}}\right]\\
+	&= \sum_{n_{(d,z,1),\sigma}=0,1}\frac{1 + \xi_{\vec k}^2 + \Xi_{\vec k}^2}{3\lambda_{\vec k_0}^2}\left[\braket{n_{d,\sigma} | \rho\left(\vec k\sigma\right) | n_{d,\sigma}} + \frac{1}{\mathcal{W}}\braket{n_{z,\sigma} | \rho\left(\vec k\sigma\right) | n_{z,\sigma}} + \frac{1}{\mathcal{W}}\braket{n_{1,\sigma} | \rho\left(\vec k\sigma\right) | n_{1,\sigma}}\right] \\
+				       &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{\xi_{\vec k}\left(1 + \Xi_{\vec k}\right)}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{n_{d,\sigma} | \rho\left(\vec k\sigma\right) | n_{z,\sigma}} + \braket{n_{z,\sigma} | \rho\left(\vec k\sigma\right) | n_{d,\sigma}} + \braket{n_{z,\sigma} | \rho\left(\vec k\sigma\right) | n_{1,\sigma}} + \braket{n_{1,\sigma} | \rho\left(\vec k\sigma\right) | n_{z,\sigma}} \right]\\
+				       &+ \sum_{n_{(d,1),\sigma}=0,1}\frac{\Xi_{\vec k}}{\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{n_{1,\sigma} | \rho\left(\vec k\sigma\right) | n_{d,\sigma}} + \braket{n_{d,\sigma} | \rho\left(\vec k\sigma\right) | n_{1,\sigma}}\right]~.
+\end{aligned}\end{equation}
 

### 2023-06-02 TilingProjectDraft/tilingProject.tex
added entanglement implementation

--- 2023-05-24 TilingProjectDraft/tilingProject.tex
@@
 \begin{equation}\begin{aligned}
-	\chi(\vec k)=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]\\
-		    &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right] \\
-		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
+	\chi(\vec k)=& \frac{1}{2\lambda_{\vec k_0}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]\\
+		    &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right] \\
+		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
 \end{aligned}\end{equation}
@@
 \section{Momentum-space entanglement}
-The density matrix of the full Hamiltonian in ground-state is simply \(\rho = \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\).
-In order to calculate entanglement measures in and among \(k-\)space states, we begin by obtaining an expression for the von-Neumann entropy of a \(\vec k-\)state, in terms of auxiliary model computables.
-The reduced density matrix for the momentum state involves a partial trace over its configurations:
-\begin{equation}\begin{aligned}
-	\rho_{\vec k,\sigma} = \sum_{n_{\vec k,\sigma}=0,1}\braket{n_{k,\sigma} | \Psi_\text{gs}}\braket{\Psi_\text{gs} | n_{\vec k,\sigma}} = \sum_{n_{\vec k,\sigma}=0,1}|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2
-\end{aligned}\end{equation}
-where \(\ket{n_{\vec k,\sigma}}\) represents a state in Fock space with \(n_{\vec k,\sigma}\) number of particles in the single particle state with momentum \(\vec k\) and spin \(\sigma\).
-We now Fourier transform the overlap and retain terms up to the next-nearest neighbour:
-\begin{equation}\begin{aligned}
-	|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2 \simeq \braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0,\sigma} | \Psi_\text{gs}} + \xi_{\vec k}\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a,\sigma} | \Psi_\text{gs}} + \Xi_{\vec k}\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a^\prime,\sigma} | \Psi_\text{gs}}
-\end{aligned}\end{equation}
-where \(\vec a\) and \(\vec a^\prime\) are nearest and next-nearest neighbour sites to \(\vec R_0\), and \(\xi_{\vec k}\) and \(\Xi_{\vec k}\) have been defined above.
-Following the eqs.~\ref{local_correlation} through \ref{nnn_correlation}, we can identify \(\hat O_1^\dagger(\vec R) = \hat O_2(\vec R) = \ket{n_{\vec R_0,\sigma}}\bra{n_{\vec R,\sigma}}\), so that we have, for example, \(\braket{\Psi_\text{gs} | n_{\vec R_0,\sigma}}\braket{n_{\vec R_0 + \vec a,\sigma} | \Psi_\text{gs}} = \braket{\hat O_1(\vec R_0) \hat O_2(\vec R_0 + \vec a)}\).
-The, using eqs.~\ref{local_correlation} through \ref{nnn_correlation}, the Fourier transform becomes:
-\begin{equation}\begin{aligned}
-	|\braket{\Psi_\text{gs} | n_{\vec k,\sigma}}|^2 \simeq& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux} | n_{d,\sigma}}\braket{n_{d,\sigma} | \psi_\text{aux}} + \frac{1}{\mathcal{W}}\braket{\psi_\text{aux} | n_{z,\sigma}}\braket{n_{z,\sigma} | \psi_\text{aux}}\right]\\
-							      &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{z,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{z,\sigma}}\bra{n_{d,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{z,\sigma}}\right) \psi_\text{aux}}\right] \\
-		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\braket{\psi_\text{aux} \left(\ket{n_{d,\sigma}}\bra{n_{1,\sigma}} + \ket{n_{1,\sigma}}\bra{n_{d,\sigma}}\right) \psi_\text{aux}}\right]
-\end{aligned}\end{equation}
-The \(k-\)space reduced density matrix takes the form
-\begin{equation}\begin{aligned}
-	\rho_{\vec k,\sigma} =& \sum_{n_{(d,z,1),\sigma}=0,1}\frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{d\sigma}} + \frac{1}{\mathcal{W}}\bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{z\sigma}}\right]\\
-							      &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{z\sigma}} + \bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{d\sigma}} + \bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{z\sigma}} + \bar\psi^\dagger_{n_{z\sigma}}\bar\psi_{n_{1\sigma}}\right] \\
-		    &+ \sum_{n_{(d,z,1),\sigma}=0,1}\frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}^2}\left[\bar\psi^\dagger_{n_{1\sigma}}\bar\psi_{n_{d\sigma}} + \bar\psi^\dagger_{n_{d\sigma}}\bar\psi_{n_{1\sigma}}\right]
-\end{aligned}\end{equation}
-where \(\bar\psi_{n_{d\sigma}} = \braket{n_{d,\sigma} | \psi_\text{aux}}\) and similar definitions exist for \(\alpha_{n_{z\sigma}}\) and \(\alpha_{n_{1\sigma}}\).
-The von-Neumann entropy \(S_\text{EE}(\vec k)\) can then be calculated by taking the trace of the operator \(\rho_{\vec k,\sigma}\ln \rho_{\vec k,\sigma}\).
+
+\begin{itemize}
+	\item \(n_{\vec R_0}\rho n_{\vec R_0}\) + \(n_{\vec R_0 + \vec a}\rho n_{\vec R_0 + \vec a}\)
+	\item \(e^{i \vec{q}\cdot\vec{a}}c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\rho n_{\vec R_0}\) + h.c. + 
+	      \(e^{-i \vec{q}\cdot\vec{a}}c^\dagger_{\vec R_0}c_{\vec R_0 + \vec a}\rho n_{\vec R_0}\) + h.c.
+	\item \(c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0 + \vec a}\rho n_{\vec R_0}\) + h.c.
+	\item   \(e^{2i\vec{q}\cdot\vec{a}}c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\rho c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\) + h.c. + 
+		\(c^\dagger_{\vec R_0}c_{\vec R_0 + \vec a}\rho c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\) + h.c.
+	\item \(e^{i \vec{q}\cdot\vec{a}} n_{\vec R_0 + \vec a}\rho c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\) + h.c.
++ \(e^{-i \vec{q}\cdot\vec{a}} n_{\vec R_0 + \vec a}\rho c^\dagger_{\vec R_0}c_{\vec R_0 + \vec a}\) + h.c.
+\end{itemize}
+\subsection{\(k-\)space von-Neumann entropy}
+The density matrix of the full Hamiltonian in ground-state is simply \(\rho_\text{gs} = \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\).
+In order to calculate entanglement measures in and among \(k-\)space states, we begin by obtaining an expression for the von-Neumann entropy of a \(\vec k-\)state, in terms of auxiliary model quantities.
+The full ground state \(\ket{\Psi_\text{gs}}\) can be written in the basis of the Fock states of momentum \(\vec k\sigma\):
+\begin{equation}\begin{aligned}
+	\Psi_\text{gs} = \sin\theta_{\vec k\sigma} \ket{n_{\vec k\sigma} = 0}\otimes\ket{\phi_{\vec k\sigma}} + \cos\theta_{\vec k\sigma} \ket{n_{\vec k\sigma} = 1}\otimes\ket{\bar\phi_{\vec k\sigma}}
+\end{aligned}\end{equation}
+where \(\ket{n_{\vec k\sigma}}\) is the state with occupancy \(n_{\vec k\sigma}\) from the Hilbert space of \(\vec k\sigma\).
+\(\ket{\phi_{\vec k\sigma}}\) and \(\ket{\bar\phi_{\vec k\sigma}}\) are the normalised states representing the configuration of the remaining degrees of freedom in the full state \(\Psi_\text{gs}\) when \(\hat n_{k\sigma}\) is 0 and 1 respectively.
+\(\sin \theta_{\vec k}\) and \(\cos\theta_{\vec k\sigma}\) are the probabilities of obtaining \(n_{\vec k\sigma}\) to be 0 and 1 respectively, in the full ground state.
+
+The reduced density matrix for the momentum state \(\vec k\sigma\) is then obtained simply by tracing over the states \(\ket{n_{\vec k\sigma}}\):
+\begin{equation}\begin{aligned}
+	\rho_{\vec k\sigma} = \sum_{n_{\vec k\sigma}=0,1} \braket{n_{\vec k\sigma} | \rho_\text{gs} | n_{\vec k\sigma}} = \sin^2\theta_{\vec k\sigma} \ket{\phi_{\vec k\sigma}}\bra{\phi_{\vec k\sigma}} + \cos^2\theta_{\vec k\sigma} \ket{\bar\phi_{\vec k\sigma}}\bra{\bar\phi_{\vec k\sigma}}\label{red_matrix}
+\end{aligned}\end{equation}
+If the eigenvalues of the operators \(\ket{\phi_{\vec k\sigma}}\bra{\phi_{\vec k\sigma}}\) and \(\ket{\bar\phi_{\vec k\sigma}}\bra{\bar\phi_{\vec k\sigma}}\) are \(\left\{ \lambda_n \right\} \) and \(\left\{ \bar\lambda_n \right\} \) respectively, the von-Neumann entropy is given by
+\begin{equation}\begin{aligned}
+	S_\text{EE}\left(\rho_{\vec k\sigma}\right) = \sum_n \left( \sin^2\theta_{\vec k\sigma}\lambda_n + \cos^2\theta_{\vec k\sigma}\bar\lambda_n \right) 
+\end{aligned}\end{equation}
+
+In order to connect with the auxiliary model, we will need to obtain the reduced density matrix without tracing out any states.
+We will, instead, project on to the appropriate states with the particle number operator \(\hat n_{\vec k\sigma}\) and the hole number operator \(\hat h_{\vec k\sigma} = 1 - \hat n_{\vec k\sigma}\).
+The reduced density matrix can be obtained by applying such projectors:
+\begin{equation}\begin{aligned}
+	\rho_{\vec k\sigma} \equiv \hat n_{\vec k\sigma}\rho_\text{gs} \hat n_{\vec k\sigma} + \hat h_{\vec k\sigma}\rho_\text{gs} \hat h_{\vec k\sigma} = \sin^2\theta_{\vec k\sigma} \ket{0}\bra{0}\otimes\ket{\phi_{\vec k\sigma}}\bra{\phi_{\vec k\sigma}} + \cos^2\theta_{\vec k\sigma} \ket{1}\bra{1}\otimes\ket{\bar\phi_{\vec k\sigma}}\bra{\bar\phi_{\vec k\sigma}}\label{red_matrix_projection}
+\end{aligned}\end{equation}
+where \(\ket{1}\) and \(\ket{0}\) are the \(n_{\vec k\sigma}=1\) and 0 states respectively. In the basis \(\left\{ \ket{0}, \ket{1} \right\} \), the reduced density matrix can be represented as
+\begin{equation}\begin{aligned}
+	\rho_{\vec k\sigma} = \begin{pmatrix}\sin^2\theta_{\vec k\sigma} \ket{\phi_{\vec k\sigma}}\bra{\phi_{\vec k\sigma}} & 0 \\ \\
+	0 & \cos^2\theta_{\vec k\sigma} \ket{\bar\phi_{\vec k\sigma}}\bra{\bar\phi_{\vec k\sigma}}
+	\end{pmatrix} ~,
+\end{aligned}\end{equation}
+such that the eigenvalues of this matrix are the same as those of the operator in eq.~\ref{red_matrix}; the projection method would therefore give the same von-Neumann entropy as that obtained using the partial traces.
+
+We will now Fourier transform the reduced matrix from the definition in eq.~\ref{red_matrix_projection}, and retain terms up to the nearest neighbour, by expanding \(c_{\vec k\sigma}\) as \(c_{\vec R_0,\sigma} + \xi_{\vec k}c_{\vec R_0 + \vec a,\sigma}\), where \(\vec a\) is the nearest neighbour site to \(\vec R_0\), and \(\xi_{\vec k}\) has been defined above.
+\begin{equation}\begin{aligned}
+	\hat n_{\vec k\sigma}\ket{\Psi_\text{gs}} \to  \left[ \hat n_{\vec R_0,\sigma} + \sum_{\vec a} \hat n_{\vec R_0 + \vec a,\sigma} + \sum_{\vec a}\left( e^{i \vec{k}\cdot\vec{a}}c^\dagger_{\vec R_0,\sigma}c_{\vec R_0 + \vec a,\sigma} + \text{h.c.} \right) \right]\ket{\Psi_\text{gs}}
+\end{aligned}\end{equation}
+We also expand the ground state wavefunction: \(\ket{\Psi}_\text{gs} \simeq \ket{\psi_\text{aux}} = \frac{1}{\sqrt \mathcal{W}}\sum_{\vec a \in \text{NN of }\vec R_0}\ket{\psi_\text{aux}(\vec R_0,\vec a)}\), so that we get
+\begin{equation}\begin{aligned}
+	\hat n_{\vec k\sigma}\ket{\Psi_\text{gs}} &= \frac{1}{\sqrt \mathcal{W}}\left[ \hat n_{\vec R_0,\sigma} \sum_{\vec a}\ket{\psi_\text{aux}(\vec R_0,\vec a)} + \sum_{\vec a} \hat n_{\vec R_0 + \vec a,\sigma}\ket{\psi_\text{aux}(\vec R_0,\vec a)} + \sum_{\vec a}\left( e^{i \vec{k}\cdot\vec{a}}c^\dagger_{\vec R_0,\sigma}c_{\vec R_0 + \vec a,\sigma} + \text{h.c.} \right) \ket{\psi_\text{aux}(\vec R_0,\vec a)}\right]\\
+						  &=\hat n_{d,\sigma} \ket{\psi_\text{aux}} + \hat n_{z,\sigma}\ket{\psi_\text{aux}} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right) \ket{\psi_\text{aux}}
+\end{aligned}\end{equation}
+By taking the outer product with its hermitian conjugate, we get the reduced density matrix:
+\begin{equation}\begin{aligned}
+	\rho_{\vec k\sigma} \simeq \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_\text{aux} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]\label{density_matrix_kspace}
+\end{aligned}\end{equation}
+The von-Neumann entropy \(S_\text{EE}(\vec k)\) can then be calculated by taking the trace of the operator \(\rho_{\vec k\sigma}\ln \rho_{\vec k\sigma}\).
+
+\subsection{\(k-\)space mutual information}
+Another measure of many-body correlations would be the mutual information between two momentum-space states.
+The mutual information \(I_2\) between the states \(\ket{\vec k, \sigma}\) and \(\ket{-\vec k, \sigma}\) is defined as
+\begin{equation}\begin{aligned}
+	I_2(\vec k\sigma:-\vec k\sigma) = S_\text{EE}(\rho_{\vec k\sigma}) + S_\text{EE}(\rho_{-\vec k\sigma}) - S_\text{EE}(\rho_{\vec k\sigma, -\vec k\sigma})~,
+\end{aligned}\end{equation}
+where \(S_\text{EE}(\rho)\) is the von-Neumann entropy associated with the density matrix \(\rho\).
+The reduced density matrices \(\rho_{\pm\vec k\sigma}\) can be computed using eq.~\ref{density_matrix_kspace}; the reduced density matrix \(\rho_{\vec k\sigma, \vec k\sigma}\) has both the states \(\pm \vec k\) traced out, and it can be obtained by substituting \(\rho_{\vec k\sigma}\) back into eq.~\ref{density_matrix_kspace}:
+\begin{equation}\begin{aligned}
+	\rho_{\vec k\sigma, -\vec k\sigma} &= \hat n_{-\vec k\sigma}\rho_{\vec k\sigma}\hat n_{-\vec k\sigma} + \hat h_{-\vec k\sigma}\rho_{\vec k\sigma}\hat h_{-\vec k\sigma} \\
+					   &= \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{-\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{-\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]
+\end{aligned}\end{equation}
 
@@
 \subsection{Gapping of the local spectral function and vanishing of correlations}
-At a critical value \(U_b = -J/4\) of the local correlation \(U_b\) on the bath zeroth site, the couplings \(J\) and \(V\) of the auxiliary model become irrelevant while \(U\) becomes remains non-zero, leading to a low-energy phase where the impurity is cutt off from the conduction bath.
+At a critical value \(U_b = -J/4\) of the local correlation \(U_b\) on the bath zeroth site, the couplings \(J\) and \(V\) of the auxiliary model become irrelevant while \(U\) becomes remains non-zero, leading to a low-energy phase where the impurity is cut off from the conduction bath.
 This is the local moment phase, where low-energy excitations have been gapped out.

### 2023-06-03 TilingProjectDraft/tilingProject.tex
obtained videos of entanglement

@@
 \end{aligned}\end{equation}
-By taking the outer product with its hermitian conjugate, we get the reduced density matrix:
-\begin{equation}\begin{aligned}
-	\rho_{\vec k\sigma} \simeq \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_\text{aux} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]\label{density_matrix_kspace}
+By taking the outer product with its hermitian conjugate and then adding the hole counterpart \(\hat h_{\vec k\sigma}\rho_\text{gs} \hat h_{\vec k\sigma}\), we get the reduced density matrix:
+\begin{equation}\begin{aligned}
+	\rho_{\vec k\sigma} \simeq& \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_\text{aux} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]\\
+				  &+ \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right] \rho_\text{aux} \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right]\label{density_matrix_kspace}
 \end{aligned}\end{equation}
@@
 Another measure of many-body correlations would be the mutual information between two momentum-space states.
-The mutual information \(I_2\) between the states \(\ket{\vec k, \sigma}\) and \(\ket{-\vec k, \sigma}\) is defined as
-\begin{equation}\begin{aligned}
-	I_2(\vec k\sigma:-\vec k\sigma) = S_\text{EE}(\rho_{\vec k\sigma}) + S_\text{EE}(\rho_{-\vec k\sigma}) - S_\text{EE}(\rho_{\vec k\sigma, -\vec k\sigma})~,
+The mutual information \(I_2\) between the states \(\ket{\vec k, \sigma}\) and \(\ket{\vec q, \sigma}\) is defined as
+\begin{equation}\begin{aligned}
+	I_2(\vec k\sigma:\vec q\sigma) = S_\text{EE}(\rho_{\vec k\sigma}) + S_\text{EE}(\rho_{\vec q\sigma}) - S_\text{EE}(\rho_{\vec k\sigma, \vec q\sigma})~,
 \end{aligned}\end{equation}
 where \(S_\text{EE}(\rho)\) is the von-Neumann entropy associated with the density matrix \(\rho\).
-The reduced density matrices \(\rho_{\pm\vec k\sigma}\) can be computed using eq.~\ref{density_matrix_kspace}; the reduced density matrix \(\rho_{\vec k\sigma, \vec k\sigma}\) has both the states \(\pm \vec k\) traced out, and it can be obtained by substituting \(\rho_{\vec k\sigma}\) back into eq.~\ref{density_matrix_kspace}:
-\begin{equation}\begin{aligned}
-	\rho_{\vec k\sigma, -\vec k\sigma} &= \hat n_{-\vec k\sigma}\rho_{\vec k\sigma}\hat n_{-\vec k\sigma} + \hat h_{-\vec k\sigma}\rho_{\vec k\sigma}\hat h_{-\vec k\sigma} \\
-					   &= \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{-\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{-\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]
+The reduced density matrices \(\rho_{\vec k\sigma}\) and \(\rho_{\vec q\sigma}\) can be computed using eq.~\ref{density_matrix_kspace}; the reduced density matrix \(\rho_{\vec q\sigma, \vec k\sigma}\) has both the states \(\vec k\sigma\) and \(\vec q\sigma\) traced out, and it can be obtained by substituting \(\rho_{\vec k\sigma}\) back into eq.~\ref{density_matrix_kspace}:
+\begin{equation}\begin{aligned}
+	&\rho_{\vec k\sigma, \vec q\sigma} \\
+	=& \hat n_{\vec q\sigma}\rho_{\vec k\sigma}\hat n_{\vec q\sigma} + \hat h_{\vec q\sigma}\rho_{\vec k\sigma}\hat h_{\vec q\sigma}\\
+	=& \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]\\
+				  &+ \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right]\\
+	=& \left[\left(\hat n_{d,\sigma} + \hat n_{z,\sigma}\right)^2 + \frac{\xi_{\vec q} + \xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)+ \frac{\xi_{\vec q} \xi_{\vec k}}{\mathcal{W}}\left( \hat n_{d\sigma} - \hat n_{0\sigma} \right)^2 \right] \rho_{\vec k\sigma} \times\\
+	 &\left[\left(\hat n_{d,\sigma} + \hat n_{z,\sigma}\right)^2 + \frac{\xi_{\vec q} + \xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)+ \frac{\xi_{\vec q} \xi_{\vec k}}{\mathcal{W}}\left( \hat n_{d\sigma} - \hat n_{0\sigma} \right)^2 \right]\\
+				  &+ \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right]
 \end{aligned}\end{equation}

### 2023-06-20 TilingProjectDraft/tilingProject.tex
added entanglement plots in draft

@@
 \label{pair_kspace}
+\end{figure}
+
+\begin{figure}[!htb]
+\includegraphics[width=\textwidth]{vne_kspace_all.pdf}
+\caption{Momentum dependence of \(k-\)space von Neumann entanglement entropy \(S_\text{EE}(\vec k)\) and \(k-\)space mutual information \(I_2(\vec k:-\vec k)\).
+The first two frames (from the left) show the variation in entanglement of a \(k-\)space in the \(k_x\) direction as the transition parameter \(r\) is tuned through the metal-insulator transition, for two values of \(k_y\).
+The last two frames show the distribution of mutual information between two states \(\vec k\) and \(-\vec k\), in the \(k_x-k_y\) plane, for two values of \(r\).
+\(r/r_c=0.9\) represents a highly correlated metal, while \(r/r_c=1\) represents the non-Fermi liquid metal formed at the transition.}
+\label{entanglement_kspace}
 \end{figure}

### 2023-07-19 TilingProjectDraft/tilingProject.tex
generated all of the plots again
jotted down points for pseudogap

@@
 \section{Momentum-space entanglement}
-
-\begin{itemize}
-	\item \(n_{\vec R_0}\rho n_{\vec R_0}\) + \(n_{\vec R_0 + \vec a}\rho n_{\vec R_0 + \vec a}\)
-	\item \(e^{i \vec{q}\cdot\vec{a}}c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\rho n_{\vec R_0}\) + h.c. + 
-	      \(e^{-i \vec{q}\cdot\vec{a}}c^\dagger_{\vec R_0}c_{\vec R_0 + \vec a}\rho n_{\vec R_0}\) + h.c.
-	\item \(c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0 + \vec a}\rho n_{\vec R_0}\) + h.c.
-	\item   \(e^{2i\vec{q}\cdot\vec{a}}c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\rho c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\) + h.c. + 
-		\(c^\dagger_{\vec R_0}c_{\vec R_0 + \vec a}\rho c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\) + h.c.
-	\item \(e^{i \vec{q}\cdot\vec{a}} n_{\vec R_0 + \vec a}\rho c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\) + h.c.
-+ \(e^{-i \vec{q}\cdot\vec{a}} n_{\vec R_0 + \vec a}\rho c^\dagger_{\vec R_0}c_{\vec R_0 + \vec a}\) + h.c.
-\end{itemize}
-\subsection{\(k-\)space von-Neumann entropy}
 The density matrix of the full Hamiltonian in ground-state is simply \(\rho_\text{gs} = \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\).
 In order to calculate entanglement measures in and among \(k-\)space states, we begin by obtaining an expression for the von-Neumann entropy of a \(\vec k-\)state, in terms of auxiliary model quantities.
+
+\subsection{\(k-\)space von-Neumann entropy}
 The full ground state \(\ket{\Psi_\text{gs}}\) can be written in the basis of the Fock states of momentum \(\vec k\sigma\):
@@
 The movie then shows the {\it evolution of this \(k-\)space colormap} as \(r\) is tuned towards and into the transition.}
+
+\section{Emergence of effectively pseudogapped Anderson model at the MIT}
+\begin{itemize}
+\item The RG equation (in the weak coupling limit) of the \(J-U_b\) model that emerges in the Kondo limit of the eSIAM is similar to that of the pseudogapped Anderson model~\cite{fritzvojta2004} that has a bath density of states of the form \(|\omega|^\alpha\).
+If we define the dimensionless Kondo coupling \(g = \rho J\) and the dimensionless bath coupling \(u = \rho U_b\), the RG equation for \(g\),
+\begin{equation}\begin{aligned}
+	g \simeq g^2 + 4gu~,
+\end{aligned}\end{equation}
+can be mapped to the corresponding RG equation for the pseudogapped Kondo model,
+\begin{equation}\begin{aligned}
+	g = g^2 - \alpha g~,
+\end{aligned}\end{equation}
+with the identification \(\alpha = -4u = -4\rho U_b\).
+\item Following the work by Si and Kotliar~\cite{kotliarsi_1993}, the impurity self-energy of the \(J-U_b\) model takes the form
+	\begin{equation}\begin{aligned}
+		\Sigma_{dd} \sim |\omega|^{\gamma_{dd}}~,
+	\end{aligned}\end{equation}
+	where the exponent \(\gamma_{dd}\) can be written in terms of the phase shifts (at the RG fixed point) \(\delta^*_\text{sp}\) and \(\delta^*_\text{ch}\) suffered by the conduction electrons due to the potentials \(J\) and \(U_b\) respectively in the Hamiltonian:
+	\begin{equation}\begin{aligned}
+		\gamma_{dd} = \frac{5}{4} - \left[ \frac{1}{\pi}\left( \delta^*_\text{sp} + \delta^*_\text{ch} \right) - \frac{1}{2}  \right]^2 - \left( \frac{\delta^*_\text{ch}}{\pi} \right)^2~.
+	\end{aligned}\end{equation}
+	The phase shifts are given by \(\delta^*_\text{sp}=\arctan\left( \pi g/2 \right) \) and \(\delta^*_\text{ch}=\arctan\left( \pi u/2 \right) \).
+In the small coupling limit, these can be approximated as \(\delta^*_\text{sp}=\pi g/2\) and \(\delta^*_\text{ch}=\pi u/2\).
+\item We now focus on the critical point \(g = -4u\) of our model.
+At this point, the phase shifts get related to each other: \(\delta^*_\text{sp} = -4\delta^*_\text{ch}\), so that the exponent of the self-energy takes the form
+	\begin{equation}\begin{aligned}
+		\gamma_{dd} \simeq 1 - \frac{3}{\pi}\delta^*_\text{ch} = 1 + \frac{3}{8}\alpha
+	\end{aligned}\end{equation}
+	where we have used the fact that for our model, the effective pseudogap parameter \(\alpha\) is set to \(-4u\). The local self-energy then vanishes as
+	\begin{equation}\begin{aligned}
+		\Sigma_{dd} \sim |\omega|^{1 + \frac{3}{8}\alpha}
+	\end{aligned}\end{equation}
+	This can be compared with the expression \(\sim|\omega|^{2-3\alpha}\) of the impurity self-energy obtained in ref.~\cite{fritzvojta2004}.
+\item In a similar manner, the self-energy \(\Sigma_{d0}\) for scattering processes that connect the impurity site and the bath zeroth site can also be obtained.
+The exponent \(\gamma_{d0}\) for this self-energy is given by \(\gamma_{d0} = 2 - 2\gamma_{dd}\), so that this non-local self-energy diverges as
+	\begin{equation}\begin{aligned}
+		\Sigma_{d0} \sim |\omega|^{- \frac{3}{4}\alpha}
+	\end{aligned}\end{equation}
+\item By using our tiling approach, the \(k-\)space self-energy at the critical point can be written as
+	\begin{equation}\begin{aligned}
+		\Sigma(\vec k,\omega) = \Sigma_{dd} + \frac{1}{\mathcal{W}}\xi_{\vec k}\Sigma_{d0}
+	\end{aligned}\end{equation}
+	This expression suggests that at the critical point, all points in the Brillouin zone except those at the Fermi surface get gapped out.
+
+\end{itemize}
 

### 2023-07-19 TilingProjectDraft/tilingProject.tex
correct figures

@@
 \author{Abhirup Mukherjee, N.S. Vidhyadhiraja, A. Taraphder, Siddhartha Lal}
-% \affil{Indian Institute of Science Education and Research Kolkata, Mohanpur}
 \date{\today}
@@
 
-Previously, we have worked out the grounstate phases of a single-impurity model with an interacting bath:
+Previously, we have worked out the ground-state phases of a single-impurity model with an interacting bath:
 \begin{equation}\begin{aligned}
@@
 
-As mentioned before, no chemical potential \(\mu\) is generated becuase the auxiliary model was at half-filling, both in the impurity as well as in the bath.
+As mentioned before, no chemical potential \(\mu\) is generated because the auxiliary model was at half-filling, both in the impurity as well as in the bath.
 We can change the chemical potential by introducing two terms:
@@
 \(\vec R_0\) is the origin of the lattice, and \(N\) is the number of lattice sites.
-The uniform piece \(\sum_{i}\mathcal{H}_\text{aux}(\vec R_0)\) acts as the "center-of-mass" Hamiltonian - it responds to spectral flow brought about by changes in boundary conditions.
+The uniform piece \(\sum_{i}\mathcal{H}_\text{aux}(\vec R_0)\) acts as the ``center-of-mass" Hamiltonian - it responds to spectral flow brought about by changes in boundary conditions.
 The other piece acts as a "relative motion" Hamiltonian and is insensitive to changes in the boundary conditions, because any spectral flow of the auxiliary model Hamiltonians gets cancelled out in the difference operation.
-While the COM Hamiltonian is a thermodynamically large object, the number of terms in teh difference piece is only of the order of unity (the sum over \(\vec R_i\) is cancelled out by the \(1/N\) factor).
+While the COM Hamiltonian is a thermodynamically large object, the number of terms in the difference piece is of the order of unity (the sum over \(\vec R_i\) is cancelled out by the \(1/N\) factor).
 We can therefore expand the exponential in the ratio of the relative piece to the COM piece:
@@
 \end{aligned}\end{equation}
-In the first equation, the first two terms were introduced to incorporate effects arisingfrom the bath zeroth and first sites (guided by the dynamics of the transition in the underlying extended Anderson model), while the last two terms were introduced to symmetrise the effects of choosing \(\vec R_0\) as \(d\) and \(\vec R_0 + \vec a\) as \(z\), and not other way round.
-The argument \((1)\) in the operators indicate that theu act at the first site of the bath (beyond the bath zeroth site).
-
-The next-nearest correlation function is relatively simpler, becuase only those terms contribute that involve both the impurity as well as the first site.
+In the first equation, the first two terms were introduced to incorporate effects arising from the bath zeroth and first sites (guided by the dynamics of the transition in the underlying extended Anderson model), while the last two terms were introduced to symmetrise the effects of choosing \(\vec R_0\) as \(d\) and \(\vec R_0 + \vec a\) as \(z\), and not other way round.
+The argument \((1)\) in the operators indicate that they act at the first site of the bath (beyond the bath zeroth site).
+
+The next-nearest correlation function is relatively simpler, because only those terms contribute that involve both the impurity as well as the first site.
 If \(\vec a^\prime\) denotes the relative vector between a given site and one of its next-nearest neighbours, we can write
@@
 As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
-Given that our auxiliary model shows an emergent self-consistency on the impurity site and on the link between the impurity and the zeroth site, we approximate the \(k-\)space Greens functions from the local and nearest-neighbour contributions, by usingthe mapping between the bulk Greens function \(G\) and auxiliary model Greens functions \(\mathcal{G}\)(eq.~\ref{greens_func_relation}):
+Given that our auxiliary model shows an emergent self-consistency on the impurity site and on the link between the impurity and the zeroth site, we approximate the \(k-\)space Greens functions from the local and nearest-neighbour contributions, by using the mapping between the bulk Greens function \(G\) and auxiliary model Greens functions \(\mathcal{G}\)(eq.~\ref{greens_func_relation}):
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\), it being essentially the disperson in units of the hopping strength \(t\).
+where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\), it being essentially the dispersion in units of the hopping strength \(t\).
 For example, on a d-dimensional hypercubic lattice, we obtain
@@
 \section{Correlation functions in momentum space}
-Similar to Greens functions, our formalism also allows calculating \(k-\)space correlation functions \(\chi(\vec q)\) from knowledge of local and nearst-neighbour correlations \(\chi_\text{loc}\) and \(\chi_\text{nn}\).
+Similar to Greens functions, our formalism also allows calculating \(k-\)space correlation functions \(\chi(\vec q)\) from knowledge of local and nearest-neighbour correlations \(\chi_\text{loc}\) and \(\chi_\text{nn}\).
 This is seen by Fourier transforming a generic real-space correlation function \(\chi(\vec r)\) corresponding to the operator \(\mathcal{O}\):
@@
 \centering
-\includegraphics[width=\textwidth]{spin_kspace_all.pdf}
+\includegraphics[width=\textwidth]{spin_rspace_all.pdf}
 \caption{Momentum dependence of spin-spin correlation \(\left<\vec{S}_{-\vec k}\cdot\vec{S}_{\vec k} \right>\).
@@
 \centering
-\includegraphics[width=\textwidth]{charge_kspace_all.pdf}
+\includegraphics[width=\textwidth]{charge_rspace_all.pdf}
 \caption{Momentum dependence of charge-charge correlation \(\left<\vec{C}_{-\vec k}\cdot\vec{C}_{\vec k} \right>\), where \(\vec C\) is the charge isospin associated with the doublet formed by the doublon and holon states.
@@
 \begin{figure}[!htb]
-\includegraphics[width=\textwidth]{pair_kspace_all.pdf}
+\includegraphics[width=\textwidth]{pair_rspace_all.pdf}
 \caption{Momentum dependence of pairing correlation \(\left<c^\dagger_{-k\uparrow}c^\dagger_{-k\downarrow}c_{k\downarrow}c_{k\uparrow}\right>\).
@@
 \section{Emergence of effectively pseudogapped Anderson model at the MIT}
-\begin{itemize}
-\item The RG equation (in the weak coupling limit) of the \(J-U_b\) model that emerges in the Kondo limit of the eSIAM is similar to that of the pseudogapped Anderson model~\cite{fritzvojta2004} that has a bath density of states of the form \(|\omega|^\alpha\).
+%\begin{itemize}
+%\item 
+We begin by recalling that the RG equation (in the weak coupling limit) of the \(J-U_b\) model that emerges in the Kondo limit of the eSIAM is similar to that of the pseudogapped Anderson model~\cite{fritzvojta2004} that has a bath density of states of the form \(\rho\sim |\omega|^\alpha\).
 If we define the dimensionless Kondo coupling \(g = \rho J\) and the dimensionless bath coupling \(u = \rho U_b\), the RG equation for \(g\),
 \begin{equation}\begin{aligned}
-	g \simeq g^2 + 4gu~,
+	\Delta g \simeq g^2 + 4gu~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	g = g^2 - \alpha g~,
+	\Delta g = g^2 - \alpha g~,
 \end{aligned}\end{equation}
 with the identification \(\alpha = -4u = -4\rho U_b\).
-\item Following the work by Si and Kotliar~\cite{kotliarsi_1993}, the impurity self-energy of the \(J-U_b\) model takes the form
+Specifically, this corresponds to a Kondo model that is coupled to a conduction bath with a single-particle density of states that is vanishing (pseudogapped): $\rho\sim |\omega|^{\alpha}$~.
+\par
+Now, following the work by Si and Kotliar~\cite{kotliarsi_1993}, the impurity self-energy of the \(J-U_b\) model takes the form
 	\begin{equation}\begin{aligned}
@@
 In the small coupling limit, these can be approximated as \(\delta^*_\text{sp}=\pi g/2\) and \(\delta^*_\text{ch}=\pi u/2\).
-\item We now focus on the critical point \(g = -4u\) of our model.
+\par 
+We now focus on the quantum critical point \(g = -4u\) of our model.
 At this point, the phase shifts get related to each other: \(\delta^*_\text{sp} = -4\delta^*_\text{ch}\), so that the exponent of the self-energy takes the form
@@
 	\begin{equation}\begin{aligned}
-		\Sigma_{dd} \sim |\omega|^{1 + \frac{3}{8}\alpha}
-	\end{aligned}\end{equation}
-	This can be compared with the expression \(\sim|\omega|^{2-3\alpha}\) of the impurity self-energy obtained in ref.~\cite{fritzvojta2004}.
-\item In a similar manner, the self-energy \(\Sigma_{d0}\) for scattering processes that connect the impurity site and the bath zeroth site can also be obtained.
+		\Sigma_{dd} \sim |\omega|^{\gamma_{dd}}\simeq |\omega|^{1 + \frac{3}{8}\alpha}
+	\end{aligned}\end{equation}
+The power-law exponent $\gamma_{dd}=1 + \frac{3}{8}\alpha$ lies in the following range: $1\leq \gamma_{dd} \leq 2$.
+This can be compared with the expression \(\sim|\omega|^{2-3\alpha}\) of the impurity self-energy obtained in ref.~\cite{fritzvojta2004} where the power law exponent ranges between $1/2$ and $2$.
+In a similar manner, the self-energy \(\Sigma_{d0}\) for scattering processes that connect the impurity site and the bath zeroth site can also be obtained.
 The exponent \(\gamma_{d0}\) for this self-energy is given by \(\gamma_{d0} = 2 - 2\gamma_{dd}\), so that this non-local self-energy diverges as
 	\begin{equation}\begin{aligned}
-		\Sigma_{d0} \sim |\omega|^{- \frac{3}{4}\alpha}
-	\end{aligned}\end{equation}
-\item By using our tiling approach, the \(k-\)space self-energy at the critical point can be written as
+		\Sigma_{d0} \sim |\omega|^{- \frac{3}{4}\alpha}~.
+	\end{aligned}\end{equation}
+\par 
+By using our tiling approach, the \(k-\)space self-energy at the critical point can be written as
 	\begin{equation}\begin{aligned}
@@
 	\end{aligned}\end{equation}
-	This expression suggests that at the critical point, all points in the Brillouin zone except those at the Fermi surface get gapped out.
-
-\end{itemize}
+	%This expression suggests that at the critical point, all points in the Brillouin zone except those at the Fermi surface get gapped out. 
+	It is clear that the divergent $\Sigma_{d0}$ does not affect the single-particle self-energy $\Sigma(\vec k,\omega)$ precisely at the Fermi surface, i.e., for $\xi_{\vec{k}}= 0$; $\Sigma(\vec k,\omega)$ diverges everywhere else in the Brillouin zone.
+This corresponds to a gapless non-Fermi liquid metal present at the QCP, corresponding to a system with Landau quasiparticle poles precisely on the Fermi surface but which are destroyed everywhere else.
+Now, following the arguments laid out in Ref.\cite{sujan2023}, the single-particle spectral function $A(\omega,\vec{k})$ will vanish (i.e., be pseudogapped) for excitations away from the Fermi surface
+\begin{equation}
+A(\omega,\vec{k}) \sim \frac{1}{\mathcal{W}}\xi_{\vec k}|\omega|^{\frac{3}{4}\alpha}~.
+\end{equation}	
+This clearly corresponds to the vanishing of the residue of the Landau quasiparticle precisely at the metal-insulator transition, and the emergence of a gapless non-Fermi liquid ``local quantum critical" metal~\cite{Si2001}.
+Further, the fact that the single-particle self-energy $\Sigma$ vanishes precisely at the Fermi surface signals the fact that the Luttinger's count for states on the Fermi surface is preserved and identical to that in the Fermi liquid phase.
+%This guarantees that the system at the QCP remains gapless, and corresponds to a ``local quantum critical" metal~\cite{Si2001}.
+
+%\end{itemize}
 
@@
 The Hamiltonian has the form \(H(h)_i = -\frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - h\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)\).
-The unique groundstate is \(\ket{\hat n_{i,\sigma = \text{sgn}(h)}=1,\hat n_{i,\sigma = -\text{sgn}(h)}=0}\), with an energy of \(E_\text{gs} = -\frac{U}{2} - h\).
+The unique ground-state is \(\ket{\hat n_{i,\sigma = \text{sgn}(h)}=1,\hat n_{i,\sigma = -\text{sgn}(h)}=0}\), with an energy of \(E_\text{gs} = -\frac{U}{2} - h\).
 The Greens function is easiest to obtain from the Lehmann-Kallen representation (eq.~\ref{Gf_lk}):
@@
 This allows a metal-insulator transition in the limit of $\mathcal{W}\to\infty$ as well.
-In this limit, the dependence of the self-energy on the interacting Greens functin can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}.
+In this limit, the dependence of the self-energy on the interacting Greens function can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}.
 This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy1}.
@@
 It is clear from the final form that only the diagonal term \(G_\text{aux,dd}(\omega)\) of the interacting Greens function affects the self-energy while the off-diagonal part \(G_\text{aux,dz}\) fails to contribute as \(w \to \infty\).
-
+\par
+\textbf{MAKE CONNECTION BETWEEN COM and Q.IMP PROBLEM}
 \begin{appendices}

### 2023-07-20 TilingProjectDraft/tilingProject.tex
clarified the Greens functions at the transition

@@
 At \(U=0\), the bath consists of just a kinetic energy part, and the ground state is just a filled Fermi sea.
-At \(t=0\), each lattice site decouples from the rest and becomes a local moment, which under symmetry-breaking becomes a Neel antiferromagnet.
+At \(t=0\), each lattice site decouples from the rest and becomes a local moment, which under symmetry-breaking becomes a Néel antiferromagnet.
 This suggests that on increasing \(U/t\) beyond some critical value, the system might undergo a phase transition from a metallic state to an insulating state~\cite{Mott_1949}.
@@
 Auxiliary models are simpler versions of the full Hamiltonian that are able to capture the essential physics.
-For eg, a correlated impurity interacting with a conduction bath is a potential auxiliary model for the Hubbard Hamiltonian:
+For example, a correlated impurity interacting with a conduction bath is a potential auxiliary model for the Hubbard Hamiltonian:
 \begin{equation}
@@
 Specifically, for the local Greens function \(G_\text{H-H}(\vec r=0, t)\), we keep the states with \(\vec a_1 = \vec a_2\), leading to the expression
-\begin{equation}\begin{aligned}\label{greens_func_approx}
+\begin{equation}\begin{aligned}
+	\label{greens_func_approx}
 	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) =  \frac{-i\theta(t)}{\mathcal{W} \lambda_{\vec k_0}^2}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)}~.
@@
 
-For the nearest neighbour Greens function \(G_\text{H-H}(\vec r=\vec a, t)\), we keep only the terms with \(\vec a_1 = \vec a_2 = \vec a\) in the summation of eq.~\ref{greens_func_approx}:
-\begin{equation}\begin{aligned}
-	G_\text{H-H}(\vec r=\vec a, t) &= -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + \vec a)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} = \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}} \mathcal{G}_{dz}(t)~.
+For the nearest neighbour Greens function \(G_\text{near-n} \equiv G_\text{H-H}(\vec r=\vec a, t)\), we keep only the terms with \(\vec a_1 = \vec a_2 = \vec a\) in the summation of eq.~\ref{greens_func_approx}:
+\begin{equation}\begin{aligned}
+	G_\text{near-n} \equiv G_\text{H-H}(\vec r=\vec a, t) = -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + \vec a)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} \\
+	= \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}} \mathcal{G}_{dz}(t)~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) = \frac{1}{N}\sum_{\vec r, \vec r_j}e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}G_{H-H} (|\vec{r_i} - \vec {r_j}|, \omega)
-\end{aligned}\end{equation}
-where $\vec{r_i}$ is the position vector of a particular lattice site.
-Because of translation invariance, the real space Greens function depends only on the relative vector between any two sites.
-As a result, $\vec r=0$ gives the local Greens function, $|\vec r|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
-Given that our auxiliary model shows an emergent self-consistency on the impurity site and on the link between the impurity and the zeroth site, we approximate the \(k-\)space Greens functions from the local and nearest-neighbour contributions, by using the mapping between the bulk Greens function \(G\) and auxiliary model Greens functions \(\mathcal{G}\)(eq.~\ref{greens_func_relation}):
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) \simeq \frac{1}{N}\sum_{\vec{r_i} = \vec {r_j}}\left(G_{H-H} (\omega)\right) _\text{loc} + \frac{1}{N}\sum_{|\vec{r_i} - \vec {r_j}|=a} e^{i \vec{k}\cdot\left(\vec{r_i} - \vec {r_j}\right)}\left(G_{H-H} (\omega)\right)_\text{n-n}
-\end{aligned}\end{equation}
-The first summation produces a factor of $N$, while the second summation can be factorized into a sum over all sites (which again returns $N$) and a sum over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, \mathcal{W}\right]\right\}$.
+	G_{H-H} (\vec k, \omega) = \frac{1}{N \mathcal{W}}\sum_{\vec r, \vec R}e^{i \vec{k}\cdot\left(\vec r + \vec R\right)}G_{H-H} (\vec r + \vec R, \omega)
+\end{aligned}\end{equation}
+where $\vec R$ sums over all lattice sites and \(\vec r\) sums over all nearest-neighbours of that site, such that \(\vec R + \vec r\) sums over all possible real space Greens functions.
+The distance \(\vec r + \vec R\) has been measured with respect to some chosen central lattice site.
+Because of translation invariance, the real space Greens function depends only on the relative vector between two sites.
+As a result, $\vec r + \vec R = 0$ gives the local Greens function, $|\vec r + \vec R|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
+Given that our auxiliary model shows an emergent self-consistency on the impurity site and on the link between the impurity and the zeroth site, we approximate the \(k-\)space Greens functions from the local and nearest-neighbour contributions:
+\begin{equation}\begin{aligned}
+	G_{H-H} (\vec k, \omega) &= \frac{1}{N \mathcal{W}}\sum_{\vec r, \vec R}\left[e^{i \vec{k}\cdot\left(\vec r + \vec R\right)}G_{H-H} (\vec r + \vec R, \omega) - G_\text{H-H}(0,\omega) - e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}(\vec r,\omega) + G_\text{H-H}(0,\omega) + e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}(\vec r,\omega)\right]\\
+				 &= G_\text{H-H}(0,\omega) + \sum_r e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}(\vec r,\omega) + \frac{1}{N \mathcal{W}}\sum_{\vec r, \vec R}\left[e^{i \vec{k}\cdot\left(\vec r + \vec R\right)}G_{H-H} (\vec r + \vec R, \omega) - G_\text{H-H}(0,\omega) - e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}(\vec r,\omega)\right]
+\end{aligned}\end{equation}
+The difference term in the square brackets is smaller than the sum outside, so we drop the former.
+We identify the first term \(G_\text{H-H}(0,\omega)\) as the local Greens function \(G_\text{loc}\) and those inside the second term, \(G_\text{H-H}(\vec r, \omega)\) as the nearest neighbour Greens function \(G_\text{near-n}\) (assuming symmetry under rotation by \(\pi/2\)).
+The second sum is over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, \mathcal{W}\right]\right\}$.
+Combining all this and by using the mappings to the auxiliary model (eqs.~\ref{greens_func_relation} and \ref{greens_func_approx}), we get
 \begin{equation}\begin{aligned}
 	\label{k_Gf_siam}
-	G_{H-H} (\vec k, \omega) &\simeq G_{H-H} (\omega)_\text{loc} + G_{H-H} (\omega)_\text{n-n}\sum_{i=1}^{\mathcal{W}} e^{i \vec{k}\cdot\vec {a_i}} = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{G}_{dd}(\omega) + \frac{1}{\mathcal{W}}\xi_{\vec k}\mathcal{G}_{dz}(\omega) \right]~,
+	G_{H-H} (\vec k, \omega) &\simeq G_\text{loc}(\omega) + G_\text{near-n}(\omega)\sum_{i=1}^{\mathcal{W}} e^{i \vec{k}\cdot\vec {a_i}} = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{G}_{dd}(\omega) + \frac{1}{\mathcal{W}}\xi_{\vec k}\mathcal{G}_{dz}(\omega) \right]~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left(A_\text{H-H}\right)_\text{loc}(\omega) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{A}_{dd}~,\qquad A_\text{H-H}(\vec{k},\omega) = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{A}_{dd} + \frac{1}{\mathcal{W}}\xi_{\vec k}\mathcal{A}_{dz} \right]~,
+	A_\text{loc}(\omega) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{A}_{dd}~,\qquad A_\text{near-n}(\omega) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{A}_{dz}~,\qquad A_\text{H-H}(\vec{k},\omega) = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{A}_{dd} + \frac{1}{\mathcal{W}}\xi_{\vec k}\mathcal{A}_{dz} \right]~,
 \end{aligned}\end{equation}
@@
 
-The impurity local spectral function \(\mathcal{A}_{dd}(\omega)\) and the impurity-bath real space off-diagonal spectral function \(\mathcal{A}_{d0}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
+The impurity local spectral function \(\mathcal{A}_{dd}(\omega)\) and the impurity-bath real space off-diagonal spectral function \(\mathcal{A}_{dz}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
 We show the former in fig.~\ref{spec_func_mit}.
@@
 	\begin{equation}\begin{aligned}
-		\Sigma_{dd} \sim |\omega|^{\gamma_{dd}}\simeq |\omega|^{1 + \frac{3}{8}\alpha}
+		\Sigma_{dd} \sim |\omega|^{\gamma_{dd}} = |\omega|^{1 + \frac{3}{8}\alpha}
 	\end{aligned}\end{equation}
@@
 This can be compared with the expression \(\sim|\omega|^{2-3\alpha}\) of the impurity self-energy obtained in ref.~\cite{fritzvojta2004} where the power law exponent ranges between $1/2$ and $2$.
-In a similar manner, the self-energy \(\Sigma_{d0}\) for scattering processes that connect the impurity site and the bath zeroth site can also be obtained.
-The exponent \(\gamma_{d0}\) for this self-energy is given by \(\gamma_{d0} = 2 - 2\gamma_{dd}\), so that this non-local self-energy diverges as
-	\begin{equation}\begin{aligned}
-		\Sigma_{d0} \sim |\omega|^{- \frac{3}{4}\alpha}~.
-	\end{aligned}\end{equation}
-\par 
-By using our tiling approach, the \(k-\)space self-energy at the critical point can be written as
-	\begin{equation}\begin{aligned}
-		\Sigma(\vec k,\omega) = \Sigma_{dd} + \frac{1}{\mathcal{W}}\xi_{\vec k}\Sigma_{d0}
-	\end{aligned}\end{equation}
-	%This expression suggests that at the critical point, all points in the Brillouin zone except those at the Fermi surface get gapped out. 
-	It is clear that the divergent $\Sigma_{d0}$ does not affect the single-particle self-energy $\Sigma(\vec k,\omega)$ precisely at the Fermi surface, i.e., for $\xi_{\vec{k}}= 0$; $\Sigma(\vec k,\omega)$ diverges everywhere else in the Brillouin zone.
+In a similar manner, the self-energy \(\Sigma_{dz}\) for scattering processes that connect the impurity site and the bath zeroth site can also be obtained.
+The exponent \(\gamma_{dz}\) for this self-energy is given by \(\gamma_{dz} = 2 - 2\gamma_{dd}\), so that this non-local self-energy diverges as
+\begin{equation}\begin{aligned}
+	\Sigma_{dz} \sim |\omega|^{- \frac{3}{4}\alpha}~.
+\end{aligned}\end{equation}
+The divergence of the non-local self-energy \(\Sigma_{dz}\) leads to the vanishing of the nearest-neighbour Greens function \(\mathcal{G}_{dz}\) as \(\omega \to 0\): 
+\begin{equation}\begin{aligned}
+	\mathcal{G}_{dz}(\omega)  \sim 1/(\mathcal{G}_{dz}^{-1} - \Sigma_{dz}(\omega)) \sim \omega^{3\alpha/4}.
+\end{aligned}\end{equation}
+
+By using our tiling approach (eq.~\ref{k_Gf_siam}), the \(k-\)space Greens function of the lattice problem, at the critical point, can be shown to become independent of the momentum, through the vanishing of the momentum dependent contribution coming from \(\mathcal{G}_{dz}\):
+\begin{equation}\begin{aligned}
+	G_\text{H-H}(\vec k,\omega) = G_\text{loc}(\omega) + \frac{\xi_{\vec k}}{\lambda_{\vec k_0}^2\mathcal{W}}\mathcal{G}_{dz}(\omega) = G_\text{loc}(\omega)
+\end{aligned}\end{equation}
+This leads to the spectral function \(A(\omega,\vec k)\) losing all momentum dependence for the gapless excitations. Moreover, the self-energies vanish
+
+It is clear that the divergent $\Sigma_{dz}$ does not affect the single-particle self-energy $\Sigma(\vec k,\omega)$ precisely at the Fermi surface, i.e., for $\xi_{\vec{k}}= 0$; $\Sigma(\vec k,\omega)$ diverges everywhere else in the Brillouin zone.
 This corresponds to a gapless non-Fermi liquid metal present at the QCP, corresponding to a system with Landau quasiparticle poles precisely on the Fermi surface but which are destroyed everywhere else.
@@
 Further, the fact that the single-particle self-energy $\Sigma$ vanishes precisely at the Fermi surface signals the fact that the Luttinger's count for states on the Fermi surface is preserved and identical to that in the Fermi liquid phase.
-%This guarantees that the system at the QCP remains gapless, and corresponds to a ``local quantum critical" metal~\cite{Si2001}.
-
-%\end{itemize}
 

### 2023-07-22 TilingProjectDraft/tilingProject.tex
--no-message

@@
 \begin{equation}\begin{aligned}
-	G_\text{near-n} \equiv G_\text{H-H}(\vec r=\vec a, t) = -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + \vec a)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} \\
+	\label{greens_func_relation_near}
+	G_\text{near-n}(t) \equiv G_\text{H-H}(\vec r=\vec a, t) = -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + \vec a)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} \\
 	= \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}} \mathcal{G}_{dz}(t)~.
+\end{aligned}\end{equation}
+These relations can be easily carried over to frequency domain: 
+\begin{equation}\begin{aligned}
+	G_\text{loc}(\omega) = \int \mathrm{dt}~e^{-i\omega t} G_\text{loc}(t) = \frac{1}{\lambda_{\vec k_0}^2}\int \mathrm{dt}~e^{-i\omega t} \mathcal{G}_{dd}(t) = \frac{1}{\lambda_{\vec k_0}^2} \mathcal{G}_{dd}(\omega)~.
 \end{aligned}\end{equation}
@@
 
-\section{Spectral functions and self-energies}
+\section{\(k-\)space Greens functions and self-energies}
 
@@
 
-From the knowledge of Greens function, one can write down self-energies using Dyson's equation \(\Sigma = \left(G^{(0)}\right)^{-1} - G^{-1}\), where \(G^{(0)}\) is the non-interacting Greens function.
-The non-interacting model is simply a resonant-level model with the impurity level at zero energy.
-Following Dyson's equation, the \(k-\)space self-energy can be obtained from the \(k-\)space Greens functions:
-\begin{equation}\begin{aligned}
-	\label{self-energy1}
-	\Sigma_{H-H}(\vec k,\omega) = 1/\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)} - 1/\left(G_{H-H}(\omega)\right)_{\vec k} = \frac{\left(\lambda_{\vec k_0}^{(0)}\right)^2}{\mathcal{G}^{(0)}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{W}}\mathcal{G}^{(0)}_{dz}(\omega)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{W}}\mathcal{G}_{dz}(\omega)}~,
-\end{aligned}\end{equation}
-where the superscript \((0)\) indicates that the corresponding term has to be calculated from the non-interacting auxiliary model.
+A similar decomposition can be used to map the self-energies of the lattice model to those of the impurity model. We approximate the full \(k-\)space self-energy as
+\begin{equation}\begin{aligned}
+	\label{selfenergykspace}
+	\Sigma(\vec k,\omega) \simeq \Sigma_\text{loc}(\omega) + \xi_{\vec k}\Sigma_\text{near-n}(\omega)~,
+\end{aligned}\end{equation}
+where \(\Sigma_\text{loc}(\omega) = \Sigma_\text{H-H}(\vec r=0,\omega)\) is the local self-energy and \(\Sigma_\text{near-n}(\omega) = \Sigma_\text{H-H}(\vec r=a, \omega)\) is the self-energy arising from processes that connect a site with its nearest neighbour.
+Following Dyson's equation, these self-energies can be written in terms of the real space Greens functions:
+\begin{equation}\begin{aligned}
+	\Sigma_\text{loc}(\omega) = \left( G_\text{loc}^{(0)} \right) ^{-1} - \left( G_\text{loc} \right) ^{-1} = \lambda_{\vec k_0}^2\left[\left( \mathcal{G}_{dd}^{(0)} \right) ^{-1} - \left( \mathcal{G}_{dd} \right) ^{-1}\right]~,
+\end{aligned}\end{equation}
+where \(G_\text{loc}^{(0)}\) and \(\mathcal{G}_{dd}^{(0)}\) are the local non-interacting Greens functions of the full model and the impurity model respectively, and we have used eq.~\ref{greens_func_relation}.
+In the same way, following eq.~\ref{greens_func_relation_near}, the nearest-neighbour self-energy can be written as
+\begin{equation}\begin{aligned}
+	\Sigma_\text{near-n}(\omega) = \mathcal{W}\lambda_{\vec k_0}^2\left[\left( \mathcal{G}_{dz}^{(0)} \right) ^{-1} - \left( \mathcal{G}_{dz} \right) ^{-1}\right]~,
+\end{aligned}\end{equation}
+where \(\mathcal{G}_{dz}^{(0)}\) is the nearest-neighbour non-interacting Greens functions of impurity model.
+
+Substituting these in eq.~\ref{selfenergykspace} allows us to express the \(k-\)space self-energy in terms of auxiliary model objects:
+\begin{equation}\begin{aligned}
+	\Sigma(\vec k,\omega) = \lambda_{\vec k_0}^2\left[ \left( \mathcal{G}_{dd}^{(0)} \right) ^{-1} - \left( \mathcal{G}_{dd} \right) ^{-1} + \xi_{\vec k}\left( \mathcal{G}_{dz}^{(0)} \right) ^{-1} - \xi_{\vec k}\left( \mathcal{G}_{dz} \right) ^{-1} \right] = \lambda_{\vec k_0}^2\left[ \Sigma_{dd}(\omega) + \xi_{\vec k}\Sigma_{dz}(\omega) \right]~,
+\end{aligned}\end{equation}
+where \(\Sigma_{dd}\) and \(\Sigma_{dz}\) are the impurity and impurity-zeroth site self-energies of the impurity model.
 
@@
 \end{aligned}\end{equation}
-This leads to the spectral function \(A(\omega,\vec k)\) losing all momentum dependence for the gapless excitations. Moreover, the self-energies vanish
+This leads to the spectral function \(A(\omega,\vec k)\) losing all momentum dependence for the gapless excitations. Moreover, the self-energies vanish .
 

### 2023-07-24 TilingProjectDraft/tilingProject.tex
--no-message

@@
 
-A similar decomposition can be used to map the self-energies of the lattice model to those of the impurity model. We approximate the full \(k-\)space self-energy as
+A similar decomposition can be used to map the single-particle \(k-\)space self-energy \(\Sigma(\vec k,\omega)\) of the lattice model to impurity model quantities.
+We approximate \(\Sigma(\vec k,\omega)\) as
 \begin{equation}\begin{aligned}
@@
 where \(\Sigma_\text{loc}(\omega) = \Sigma_\text{H-H}(\vec r=0,\omega)\) is the local self-energy and \(\Sigma_\text{near-n}(\omega) = \Sigma_\text{H-H}(\vec r=a, \omega)\) is the self-energy arising from processes that connect a site with its nearest neighbour.
-Following Dyson's equation, these self-energies can be written in terms of the real space Greens functions:
-\begin{equation}\begin{aligned}
-	\Sigma_\text{loc}(\omega) = \left( G_\text{loc}^{(0)} \right) ^{-1} - \left( G_\text{loc} \right) ^{-1} = \lambda_{\vec k_0}^2\left[\left( \mathcal{G}_{dd}^{(0)} \right) ^{-1} - \left( \mathcal{G}_{dd} \right) ^{-1}\right]~,
+Following Dyson's equation, \(\Sigma(\vec k,\omega)\) can be written in terms of the momentum-space Greens functions, which can be mapped to the auxiliary model Greens functions following eq.~\ref{k_Gf_siam}:
+\begin{equation}\begin{aligned}
+	\Sigma(\vec k,\omega) = \left[ G_{H-H}^{(0)}(\vec k, \omega) \right]^{-1} - \left[ G_{H-H}(\vec k, \omega) \right]^{-1} = \left[ \mathcal{G}^{(0)}_{dd}(\omega) + \frac{1}{\mathcal{W}}\xi_{\vec k}\mathcal{G}^{(0)}_{dz}(\omega) \right]^{-1} - \left[ \mathcal{G}_{dd}(\omega) + \frac{1}{\mathcal{W}}\xi_{\vec k}\mathcal{G}_{dz}(\omega) \right]^{-1}~,
 \end{aligned}\end{equation}
@@
 The videos for the spin-spin correlation and the pairing correlations are named ``ss\_rspace.gif" and ``pairing\_rspace.gif", respectively.
-Each frame of the video shows a colormap of the correlation in the top right quadrant of the first Brillouin zone, at a {\it specific value of \(r\)}.
-The movie then shows the {\it evolution of this \(k-\)space colormap} as \(r\) is tuned towards and into the transition.}
+Each frame of the video shows a colourmap of the correlation in the top right quadrant of the first Brillouin zone, at a {\it specific value of \(r\)}.
+The movie then shows the {\it evolution of this \(k-\)space colourmap} as \(r\) is tuned towards and into the transition.}
 

### 2023-07-25 TilingProjectDraft/tilingProject.tex
Added argument for the divergence of sigma nonloc

--- 2023-07-20 TilingProjectDraft/tilingProject.tex
@@
-\documentclass{report}
-\usepackage{amsthm,amsmath,amssymb,braket,multirow,caption,relsize,tocbibind,color,appendix,enumitem,cite,graphicx}
-\usepackage[hidelinks]{hyperref}
-\usepackage[margin=0.7in,bottom=1in]{geometry}
-
-\setcounter{tocdepth}{1}
-\numberwithin{equation}{section}
-\allowdisplaybreaks
-\bibliographystyle{unsrt}
+\documentclass[prb]{revtex4-2}
+
+\usepackage{braket,amsmath,amssymb,color,graphicx,hyperref,bookmark}
+\bibliographystyle{apsrev4-2}
+
+\begin{document}
 
@@
 \author{Abhirup Mukherjee, N.S. Vidhyadhiraja, A. Taraphder, Siddhartha Lal}
-\date{\today}
-
-\begin{document}
 \maketitle
-\tableofcontents
-\newpage
-\chapter{Introduction}
 
 \section{What is the minimal impurity model for a Mott metal-insulator transition?}
-\label{sec:min_model}
+
 The Hubbard model is one of the fundamental models for strong electronic correlation; in its simplest form, it features a single band of conduction electrons hopping on a lattice and interacting via local correlations that provide a cost \(U\) if any site is doubly occupied:
@@
 The leap to the bulk model is then made by applying lattice translation operators on the auxiliary model.
-This process is shown in chapter~\ref{chap:tile}.
 This process, referred to as tiling here, relates the auxiliary model Hamiltonian with that of the bulk, and hence allows connecting the Greens functions and other related quantities across dimensions.
@@
 
-\chapter{From the auxiliary model to the bulk - single site approach}
-\label{chap:tile}
-
 \section{Creating a Hubbard-Heisenberg Hamiltonian from an extended Anderson impurity model}
@@
 
-From the knowledge of Greens function, one can write down self-energies using Dyson's equation \(\Sigma = \left(G^{(0)}\right)^{-1} - G^{-1}\), where \(G^{(0)}\) is the non-interacting Greens function.
-The non-interacting model is simply a resonant-level model with the impurity level at zero energy.
-Following Dyson's equation, the \(k-\)space self-energy can be obtained from the \(k-\)space Greens functions:
+From the knowledge of the momentum-space Greens function, one can write down the lattice self-energy \(\Sigma(\vec k,\omega)\) using Dyson's equation:
 \begin{equation}\begin{aligned}
@@
 The exponent \(\gamma_{dz}\) for this self-energy is given by \(\gamma_{dz} = 2 - 2\gamma_{dd}\), so that this non-local self-energy diverges as
-\begin{equation}\begin{aligned}
+\begin{equation}\begin{aligned}\label{selfenergydivergence}
 	\Sigma_{dz} \sim |\omega|^{- \frac{3}{4}\alpha}~.
 \end{aligned}\end{equation}
-The divergence of the non-local self-energy \(\Sigma_{dz}\) leads to the vanishing of the nearest-neighbour Greens function \(\mathcal{G}_{dz}\) as \(\omega \to 0\): 
-\begin{equation}\begin{aligned}
-	\mathcal{G}_{dz}(\omega)  \sim 1/(\mathcal{G}_{dz}^{-1} - \Sigma_{dz}(\omega)) \sim \omega^{3\alpha/4}.
-\end{aligned}\end{equation}
-
-By using our tiling approach (eq.~\ref{k_Gf_siam}), the \(k-\)space Greens function of the lattice problem, at the critical point, can be shown to become independent of the momentum, through the vanishing of the momentum dependent contribution coming from \(\mathcal{G}_{dz}\):
-\begin{equation}\begin{aligned}
-	G_\text{H-H}(\vec k,\omega) = G_\text{loc}(\omega) + \frac{\xi_{\vec k}}{\lambda_{\vec k_0}^2\mathcal{W}}\mathcal{G}_{dz}(\omega) = G_\text{loc}(\omega)
-\end{aligned}\end{equation}
-This leads to the spectral function \(A(\omega,\vec k)\) losing all momentum dependence for the gapless excitations. Moreover, the self-energies vanish
-
-It is clear that the divergent $\Sigma_{dz}$ does not affect the single-particle self-energy $\Sigma(\vec k,\omega)$ precisely at the Fermi surface, i.e., for $\xi_{\vec{k}}= 0$; $\Sigma(\vec k,\omega)$ diverges everywhere else in the Brillouin zone.
+
+We will now relate the auxiliary model self-energies \(\Sigma_{dd}\) and \(\Sigma_{dz}\) with their auxiliary model counterparts using the lattice Dyson equation.
+We consider self-energy matrices \(\Sigma\) and \(\Sigma_\text{aux}\) constructed out of real-space self-energies:
+\begin{equation}\begin{aligned}
+	\Sigma(\omega) = \begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} ,\quad \Sigma_\text{aux}(\omega) = \begin{bmatrix} \Sigma_{dd}(\omega) && \Sigma_{dz}(\omega) \\ \Sigma_{dz}(\omega) && \Sigma_{dd}(\omega)\end{bmatrix}~,
+\end{aligned}\end{equation}
+where \(\Sigma_\text{loc}\) is the real-space local self-energy and \(\Sigma_\text{near-n}\) is the self-energy for nearest-neighbour scattering processes. Using Dyson's equation, we can write
+\begin{equation}\begin{aligned}
+	\begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} = \begin{bmatrix} G^{(0)}_\text{loc}(\omega) && G^{(0)}_\text{near-n}(\omega) \\ G^{(0)}_\text{near-n}(\omega) && G^{(0)}_\text{loc}(\omega)\end{bmatrix}^{-1} - \begin{bmatrix} G_\text{loc}(\omega) && G_\text{near-n}(\omega) \\ G_\text{near-n}(\omega) && G_\text{loc}(\omega)\end{bmatrix}^{-1}~,
+\end{aligned}\end{equation}
+and
+\begin{equation}\begin{aligned}
+	\begin{bmatrix} \Sigma_{dd}(\omega) && \Sigma_{dz}(\omega) \\ \Sigma_{dz}(\omega) && \Sigma_{dd}(\omega)\end{bmatrix} = \begin{bmatrix} \mathcal{G}^{(0)}_{dd}(\omega) && \mathcal{G}^{(0)}_{dz}(\omega) \\ \mathcal{G}^{(0)}_{dz}(\omega) && \mathcal{G}^{(0)}_{dd}(\omega)\end{bmatrix}^{-1} - \begin{bmatrix} \mathcal{G}_{dd}(\omega) && \mathcal{G}_{dz}(\omega) \\ \mathcal{G}_{dz}(\omega) && \mathcal{G}_{dd}(\omega)\end{bmatrix}^{-1}~,
+\end{aligned}\end{equation}
+where the superscript \((0)\) indicates that the corresponding quantity has to be calculated from the non-interacting model.
+We now evaluate the second inverse matrix in each of the two equations, and expression the lattice Greens functions in terms of the auxiliary mode Greens functions (using eqs.~\ref{greens_func_relation} and \ref{greens_func_relation_near}).
+We get
+\begin{equation}\begin{aligned}
+	\begin{bmatrix} \Sigma_{dd}(\omega) && \Sigma_{dz}(\omega) \\ \Sigma_{dz}(\omega) && \Sigma_{dd}(\omega)\end{bmatrix} &= 1/\mathcal{G}^{(0)} - \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2}\begin{bmatrix} \mathcal{G}_{dd} && \mathcal{G}_{dz} \\ \mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}^{-1}~,\\
+	\begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} &= 1/G^{(0)} - \frac{1}{\lambda_{\vec k_0}^2}\frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{W}^2}\begin{bmatrix} \mathcal{G}_{dd} && \frac{1}{\mathcal{W}}\mathcal{G}_{dz} \\ \frac{1}{\mathcal{W}}\mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}^{-1}~.
+\end{aligned}\end{equation}
+This allows us to write down expressions for the off-diagonal self-energies, in terms of Greens functions, without evaluating the non-singular contribution coming from the non-interacting matrix:
+\begin{equation}\begin{aligned}
+	\Sigma_{dz} = \left(1/\mathcal{G}^{(0)}\right)_{dz} - \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2} \mathcal{G}_{dz},\quad \Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} - \frac{1}{\mathcal{W}\lambda_{\vec k_0}^2}\frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{W}^2} \mathcal{G}_{dz}
+\end{aligned}\end{equation}
+The divergence of \(\Sigma_{dz}\) shown in eq.~\ref{selfenergydivergence} as \(\omega \to 0\) has to arise from the second term in the expression for \(\Sigma_{dz}\) in the last equation, because the non-interacting Greens function has well-defined poles which kill the first term.
+The second term in the expression for \(\Sigma_\text{near-n}\) is very similar to this diverging term in \(\Sigma_{dz}\), differing only through the presence of some finite non-zero factors of \(\lambda_{\vec k_0}^2\) and \(\mathcal{W}\).
+We therefore conclude that the non-local self-energy of the lattice model is also divergent:
+\begin{equation}\begin{aligned}
+	\Sigma_\text{near-n}\left( \omega \right) \sim \omega^{-3\alpha/4}~.
+\end{aligned}\end{equation}
+By a similar argument, the local self-energy is found to vanish as \(\omega \to 0\). Using our tiling approach, we can approximate the \(k-\)space self-energy in terms of these two self-energies:
+\begin{equation}\begin{aligned}
+	\Sigma(\vec k, \omega) \simeq \Sigma_\text{loc} + \xi_{\vec k}\Sigma_\text{near-n}
+\end{aligned}\end{equation}
+It is clear from the expression that the divergent $\Sigma_\text{near-n}$ does not affect the single-particle self-energy $\Sigma(\vec k,\omega)$ at the Fermi surface, i.e., for $\xi_{\vec{k}}= 0$, but $\Sigma(\vec k,\omega)$ diverges everywhere else in the Brillouin zone.
 This corresponds to a gapless non-Fermi liquid metal present at the QCP, corresponding to a system with Landau quasiparticle poles precisely on the Fermi surface but which are destroyed everywhere else.
+
 Now, following the arguments laid out in Ref.\cite{sujan2023}, the single-particle spectral function $A(\omega,\vec{k})$ will vanish (i.e., be pseudogapped) for excitations away from the Fermi surface
 \begin{equation}
-A(\omega,\vec{k}) \sim \frac{1}{\mathcal{W}}\xi_{\vec k}|\omega|^{\frac{3}{4}\alpha}~.
+A(\vec{k},\omega) \sim |\omega|^{\frac{3}{4}\alpha}~.
 \end{equation}	
-This clearly corresponds to the vanishing of the residue of the Landau quasiparticle precisely at the metal-insulator transition, and the emergence of a gapless non-Fermi liquid ``local quantum critical" metal~\cite{Si2001}.
-Further, the fact that the single-particle self-energy $\Sigma$ vanishes precisely at the Fermi surface signals the fact that the Luttinger's count for states on the Fermi surface is preserved and identical to that in the Fermi liquid phase.
+This corresponds to the vanishing of the residue of the Landau quasiparticle precisely at the metal-insulator transition, and the emergence of a gapless non-Fermi liquid ``local quantum critical" metal~\cite{Si2001}.
+Further, the fact that the single-particle self-energy $\Sigma(\vec k, \omega)$ vanishes precisely at the Fermi surface signals the fact that the Luttinger's count for states on the Fermi surface is preserved and identical to that in the Fermi liquid phase.
 
@@
 It is clear from the final form that only the diagonal term \(G_\text{aux,dd}(\omega)\) of the interacting Greens function affects the self-energy while the off-diagonal part \(G_\text{aux,dz}\) fails to contribute as \(w \to \infty\).
-\par
-\textbf{MAKE CONNECTION BETWEEN COM and Q.IMP PROBLEM}
-\begin{appendices}
-
-\appendixtitleon
-
-\chapter{Zero temperature Greens function in frequency domain}
+
+\appendix
+
+\section{Zero temperature Greens function in frequency domain}
 
@@
 
-\chapter{Some analytic results for the Hubbard dimer and the Hubbard model}
 \section{Spectrum of the Hubbard dimer}
@@
 	\end{tabular}
-	\captionof{table}{Spectrum of Hubbard dimer at half-filling}
+	%\captionof{table}{Spectrum of Hubbard dimer at half-filling}
 	\label{hubb_dim_spectrum}
@@
 
-\section{Contributions of various excitations to the site local spectral function}
 The site local spectral function is
@@
 
-\chapter{Simple results for the Greens functions}
 \section{Relation between single-particle Greens function and the Greens operator $(T=0)$}
@@
 
-\chapter{Topological interpretation of the Wilson ratio}
+\section{Topological interpretation of the Wilson ratio}
 From the Friedel sum rule\cite{langer1961friedel}, we can relate the phase shift \(\delta(0)\) due to scattering (at the Fermi surface) off a local impurity to the number of electrons bound in the potential well produced by that impurity:
@@
 
-\chapter{Properties of the Bloch states}
-
-\section{Translation invariance}
+\section{Properties of the Bloch states}
+
+\subsection{Translation invariance}
 It is easy to verify that \(\Psi_{\vec k}\left(\left\{ \vec r_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \(\vec R\):
@@
 
-\section{Orthonormality}
+\subsection{Orthonormality}
 It is straightforward to show that these states form an orthonormal basis. We start by writing down the inner product of two distinct such states:
@@
 
-\section{Eigenstates}
+\subsection{Eigenstates}
 To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
@@
 
-\end{appendices}
-
 \bibliography{tilingProject}

### 2023-07-26 TilingProjectDraft/tilingProject.tex
final touches to pseudogap

@@
 \author{Abhirup Mukherjee, N.S. Vidhyadhiraja, A. Taraphder, Siddhartha Lal}
+\date{\today}
 \maketitle
+\tableofcontents
 
 \section{What is the minimal impurity model for a Mott metal-insulator transition?}
-
 The Hubbard model is one of the fundamental models for strong electronic correlation; in its simplest form, it features a single band of conduction electrons hopping on a lattice and interacting via local correlations that provide a cost \(U\) if any site is doubly occupied:
@@
 
-The following un-normalised combination of the auxiliary model eigenstates satisfies Bloch's theorem~\cite{stoyanova}:
+The following un-normalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:
 \begin{equation}\begin{aligned}
@@
 				 &= G_\text{H-H}(0,\omega) + \sum_r e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}(\vec r,\omega) + \frac{1}{N \mathcal{W}}\sum_{\vec r, \vec R}\left[e^{i \vec{k}\cdot\left(\vec r + \vec R\right)}G_{H-H} (\vec r + \vec R, \omega) - G_\text{H-H}(0,\omega) - e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}(\vec r,\omega)\right]
+\label{auxGreen}
 \end{aligned}\end{equation}
@@
 where the superscript \((0)\) indicates that the corresponding term has to be calculated from the non-interacting auxiliary model.
+
+By expanding in terms of the small parameter $\frac{\lambda_{\vec k_0}^2}{\mathcal{W}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}}$, this expression for $\Sigma_{H-H}(\vec k,\omega)$ can be recast in the following form:
+\begin{equation}\begin{aligned}
+	\Sigma_{H-H}(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~\label{selfenergy1}
+\end{aligned}\end{equation}
+where $\Sigma_\text{loc}$ and $\Sigma_\text{near-n}$ correspond to the local and nearest-neighbour self-energies defined on the real-space lattice 
+\begin{eqnarray}
+\Sigma_\text{loc}(\omega) &=& \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^{(0)}} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}}~,\\ 
+\tilde{\Sigma}(\vec k, \omega)&=&\xi_{\vec k}\Sigma_\text{near-n}~,~\Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{W}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}^2}~.
+\end{eqnarray}
+We note that the form of $\Sigma(\vec k, \omega)$ obtained by us is similar to the form proposed on phenomenological grounds in the generalised DMFT + $\Sigma$ approach~\cite{sadovskii2012}.
 
@@
 
-We will now relate the auxiliary model self-energies \(\Sigma_{dd}\) and \(\Sigma_{dz}\) with their auxiliary model counterparts using the lattice Dyson equation.
+We will now relate the auxiliary model self-energies \(\Sigma_{dd}\) and \(\Sigma_{dz}\) with their bulk (or lattice) model counterparts using the lattice Dyson equation.
 We consider self-energy matrices \(\Sigma\) and \(\Sigma_\text{aux}\) constructed out of real-space self-energies:
@@
 \begin{equation}\begin{aligned}
-	\begin{bmatrix} \Sigma_{dd}(\omega) && \Sigma_{dz}(\omega) \\ \Sigma_{dz}(\omega) && \Sigma_{dd}(\omega)\end{bmatrix} &= 1/\mathcal{G}^{(0)} - \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2}\begin{bmatrix} \mathcal{G}_{dd} && \mathcal{G}_{dz} \\ \mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}^{-1}~,\\
-	\begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} &= 1/G^{(0)} - \frac{1}{\lambda_{\vec k_0}^2}\frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{W}^2}\begin{bmatrix} \mathcal{G}_{dd} && \frac{1}{\mathcal{W}}\mathcal{G}_{dz} \\ \frac{1}{\mathcal{W}}\mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}^{-1}~.
+	\begin{bmatrix} \Sigma_{dd}(\omega) && \Sigma_{dz}(\omega) \\ \Sigma_{dz}(\omega) && \Sigma_{dd}(\omega)\end{bmatrix} &= 1/\mathcal{G}^{(0)} - \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2}\begin{bmatrix} \mathcal{G}_{dd} && -\mathcal{G}_{dz} \\ -\mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}~,\\
+	\begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} &= 1/G^{(0)} - \frac{1}{\lambda_{\vec k_0}^2}\frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{W}^2}\begin{bmatrix} \mathcal{G}_{dd} && -\frac{1}{\mathcal{W}}\mathcal{G}_{dz} \\ -\frac{1}{\mathcal{W}}\mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Sigma_{dz} = \left(1/\mathcal{G}^{(0)}\right)_{dz} - \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2} \mathcal{G}_{dz},\quad \Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} - \frac{1}{\mathcal{W}\lambda_{\vec k_0}^2}\frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{W}^2} \mathcal{G}_{dz}
-\end{aligned}\end{equation}
-The divergence of \(\Sigma_{dz}\) shown in eq.~\ref{selfenergydivergence} as \(\omega \to 0\) has to arise from the second term in the expression for \(\Sigma_{dz}\) in the last equation, because the non-interacting Greens function has well-defined poles which kill the first term.
-The second term in the expression for \(\Sigma_\text{near-n}\) is very similar to this diverging term in \(\Sigma_{dz}\), differing only through the presence of some finite non-zero factors of \(\lambda_{\vec k_0}^2\) and \(\mathcal{W}\).
-We therefore conclude that the non-local self-energy of the lattice model is also divergent:
+	\Sigma_{dz} = \left(1/\mathcal{G}^{(0)}\right)_{dz} + \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2} \mathcal{G}_{dz},\quad \Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{1}{\mathcal{W}\lambda_{\vec k_0}^2}\frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{W}^2} \mathcal{G}_{dz}
+\end{aligned}\end{equation}
+The divergence of \(\Sigma_{dz}\) shown in eq.~\ref{selfenergydivergence} as \(\omega \to 0\) has to arise from the second term in the expression for \(\Sigma_{dz}\) above as it contains the effects of inter-particle correlations.
+%, because the non-interacting Greens function has well-defined poles which kill the first term. 
+Importantly, we note that the second term in the expression for \(\Sigma_\text{near-n}\) is very similar to the diverging term in \(\Sigma_{dz}\), differing only through the presence of some finite (i.e., non-divergent) non-zero factors of \(\lambda_{\vec k_0}^2\) and \(\mathcal{W}\).
+We therefore conclude that the non-local self-energy of the lattice model $\Sigma_\text{near-n}$ contains the same power-law divergence  as $\Sigma_{dz}$ upon taking the limit $\omega\to 0$:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-By a similar argument, the local self-energy is found to vanish as \(\omega \to 0\). Using our tiling approach, we can approximate the \(k-\)space self-energy in terms of these two self-energies:
-\begin{equation}\begin{aligned}
-	\Sigma(\vec k, \omega) \simeq \Sigma_\text{loc} + \xi_{\vec k}\Sigma_\text{near-n}
-\end{aligned}\end{equation}
+By a similar argument, the local self-energy is found to vanish as \(\omega \to 0\).
+We have seen above that we can approximate the \(k-\)space self-energy in terms of these two real-space self-energies (eq.\eqref{selfenergy1}):
+\begin{equation}\begin{aligned}
+	\Sigma(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~~\textrm{where}~\tilde{\Sigma}(\vec k, \omega)=\xi_{\vec k}\Sigma_\text{near-n}~,
+\end{aligned}\end{equation}
+and $\xi_{\vec{k}}$ is the electronic lattice dispersion (in units of the hopping amplitude $t$).
 It is clear from the expression that the divergent $\Sigma_\text{near-n}$ does not affect the single-particle self-energy $\Sigma(\vec k,\omega)$ at the Fermi surface, i.e., for $\xi_{\vec{k}}= 0$, but $\Sigma(\vec k,\omega)$ diverges everywhere else in the Brillouin zone.
@@
 
-Now, following the arguments laid out in Ref.\cite{sujan2023}, the single-particle spectral function $A(\omega,\vec{k})$ will vanish (i.e., be pseudogapped) for excitations away from the Fermi surface
+Now, following the arguments laid out in Ref.\cite{sujan2023}, the single-particle spectral function $A(\omega,\vec{k})$ will vanish (i.e., be pseudogapped) for excitations away from a critical Fermi surface~(see Chapter 8 of Ref.\cite{carr2010})
 \begin{equation}

### 2023-07-26 TilingProjectDraft/tilingProject.tex
modified entanglement measures

@@
 \documentclass[prb]{revtex4-2}
-
 \usepackage{braket,amsmath,amssymb,color,graphicx,hyperref,bookmark}
@@
 	\begin{bmatrix} \Sigma_{dd}(\omega) && \Sigma_{dz}(\omega) \\ \Sigma_{dz}(\omega) && \Sigma_{dd}(\omega)\end{bmatrix} &= 1/\mathcal{G}^{(0)} - \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2}\begin{bmatrix} \mathcal{G}_{dd} && -\mathcal{G}_{dz} \\ -\mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}~,\\
-	\begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} &= 1/G^{(0)} - \frac{1}{\lambda_{\vec k_0}^2}\frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{W}^2}\begin{bmatrix} \mathcal{G}_{dd} && -\frac{1}{\mathcal{W}}\mathcal{G}_{dz} \\ -\frac{1}{\mathcal{W}}\mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}~.
+	\begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} &= 1/G^{(0)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{W}^2}\begin{bmatrix} \mathcal{G}_{dd} && -\frac{1}{\mathcal{W}}\mathcal{G}_{dz} \\ -\frac{1}{\mathcal{W}}\mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Sigma_{dz} = \left(1/\mathcal{G}^{(0)}\right)_{dz} + \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2} \mathcal{G}_{dz},\quad \Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{1}{\mathcal{W}\lambda_{\vec k_0}^2}\frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{W}^2} \mathcal{G}_{dz}
+	\Sigma_{dz} = \left(1/\mathcal{G}^{(0)}\right)_{dz} + \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2} \mathcal{G}_{dz},\quad \Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{W}}\frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{W}^2} \mathcal{G}_{dz}
 \end{aligned}\end{equation}
@@
 \section{Analytic consistency check - On the Bethe lattice}
-We now apply our approach to the case of infinite number of nearest-neighbours $\mathcal{W}\to\infty$ (the coordination number, and effectively the dimension).
-In such a model, the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{\mathcal{W}}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that the kinetic energy of the associated tight-binding lattice model remains finite and in competition with the localising physics of \(U\) and the magnetic ordering physics of \(J\).
-This allows a metal-insulator transition in the limit of $\mathcal{W}\to\infty$ as well.
-In this limit, the dependence of the self-energy on the interacting Greens function can be shown to arise from only the site-diagonal terms~\cite{Muller-Hartmann1989,georges_kotliar_1992}.
-This can be demonstrated from the present formalism as well, using eq.\eqref{self-energy1}.
-Applying the limit of \(w\to \infty\) on that equation gives
-\begin{equation}\begin{aligned}
-	\Sigma_{H-H}(\vec k,\omega) = \lim_{w\to \infty} \left\{\left(G^{(0)}(\vec k,\omega)\right)^{-1} - \left [G_\text{aux,dd} + \frac{\xi_{\vec k}}{\mathcal{W}} G_\text{aux,dz}\right]^{-1}\right\} = \lim_{w\to \infty}\left\{G^{(0)}(\vec k,\omega) - G_\text{aux,dd}(\omega)\right\}^{-1}
-\end{aligned}\end{equation}
-where \(G^{(0)}(\vec k,\omega)\) is the non-interacting Greens function and \(G_\text{aux,dd}(\omega)\) is the site-diagonal Greens function of the auxiliary model.
-It is clear from the final form that only the diagonal term \(G_\text{aux,dd}(\omega)\) of the interacting Greens function affects the self-energy while the off-diagonal part \(G_\text{aux,dz}\) fails to contribute as \(w \to \infty\).
+We now apply our approach to the case of infinite number of nearest-neighbours $\mathcal{W}\to\infty$ (the coordination number, and effectively the dimension), where the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{\mathcal{W}}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that DMFT obtains a metal-insulator transition in that limit~\cite{georges1996}.
+It is well known from the works of Müller-Hartmann as well as Metzner and Vollhardt that self-energy arising from the correlations loses all momentum-dependence and becomes purely local~\cite{Muller-Hartmann1989,metzner_volhardt_1989}.
+This simplification is what makes DMFT exact in the limit of infinite dimensions.
+This simplification is also explicit in our formalism, as can be seen in the expression of the self-energy (eq.~\ref{selfenergy1}).
+Upon taking the limit of \(\mathcal{W}\to\infty\), the non-local terms drop out:
+\begin{equation}\begin{aligned}
+	\lim_{\mathcal{W}\to\infty}\Sigma_{H-H}(\vec k,\omega) = \frac{\left(\lambda_{\vec k_0}^{(0)}\right)^2}{\mathcal{G}^{(0)}_{dd}(\omega)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega)} = \Sigma_\text{loc}(\omega)~,
+\end{aligned}\end{equation}
+making the self-energy completely local.
 

### 2023-07-27 TilingProjectDraft/tilingProject.tex
finalised entanglement measures and computed rc2 - rc1

@@
 	=& \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]\\
-				  &+ \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right]\\
-	=& \left[\left(\hat n_{d,\sigma} + \hat n_{z,\sigma}\right)^2 + \frac{\xi_{\vec q} + \xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)+ \frac{\xi_{\vec q} \xi_{\vec k}}{\mathcal{W}}\left( \hat n_{d\sigma} - \hat n_{0\sigma} \right)^2 \right] \rho_{\vec k\sigma} \times\\
-	 &\left[\left(\hat n_{d,\sigma} + \hat n_{z,\sigma}\right)^2 + \frac{\xi_{\vec q} + \xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)+ \frac{\xi_{\vec q} \xi_{\vec k}}{\mathcal{W}}\left( \hat n_{d\sigma} - \hat n_{0\sigma} \right)^2 \right]\\
 				  &+ \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right]
@@
 \includegraphics[width=\textwidth]{vne_kspace_all.pdf}
-\caption{Momentum dependence of \(k-\)space von Neumann entanglement entropy \(S_\text{EE}(\vec k)\) and \(k-\)space mutual information \(I_2(\vec k:-\vec k)\).
-The first two frames (from the left) show the variation in entanglement of a \(k-\)space in the \(k_x\) direction as the transition parameter \(r\) is tuned through the metal-insulator transition, for two values of \(k_y\).
-The last two frames show the distribution of mutual information between two states \(\vec k\) and \(-\vec k\), in the \(k_x-k_y\) plane, for two values of \(r\).
-\(r/r_c=0.9\) represents a highly correlated metal, while \(r/r_c=1\) represents the non-Fermi liquid metal formed at the transition.}
+\caption{Momentum dependence of \(k-\)space von Neumann entanglement entropy \(S_\text{EE}(\vec k)\).
+The four frames (from the left) show the variation in entanglement of a \(k-\)space in the \(k_x-k_y\) plane as the transition parameter \(r\) is tuned through the metal-insulator transition.
+\(r/r_c=0.5\) represents a very weakly correlated metal, \(r/r_c=0.8,0.9\) represents a highly correlated metal in the Kondo phase of the auxiliary model, and \(r/r_c \sim 1\) represents the non-Fermi liquid metal formed at the transition.}
 \label{entanglement_kspace}
+\end{figure}
+
+\begin{figure}[!htb]
+\includegraphics[width=\textwidth]{mutinfo_kspace_all.pdf}
+\caption{Momentum dependence of \(k-\)space mutual information \(I_2(\vec k: -\vec k)\).
+The four frames (from the left) show the variation in entanglement between the \(\vec k\) and \(-\vec k\) states in the \(k_x-k_y\) plane as the transition parameter \(r\) is tuned through the metal-insulator transition.
+\(r/r_c=0.5\) represents a very weakly correlated metal, \(r/r_c=0.8,0.9\) represents a highly correlated metal in the Kondo phase of the auxiliary model, and \(r/r_c \sim 1\) represents the non-Fermi liquid metal formed at the transition.}
+\label{mutinfo_kspace}
 \end{figure}

### 2023-07-27 TilingProjectDraft/tilingProject.tex
made some changes to the introduction

@@
 
-Previously, we have worked out the ground-state phases of a single-impurity model with an interacting bath:
+The standard Anderson model consists of a correlated impurity site coupled with a non-interacting conduction bath.
+The double occupancy cost on the impurity is \(U\), while the single-particle hopping strength between the impurity and the conduction bath is \(V\).
+Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes.
+We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath site connected to the impurity.
+The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
 \begin{equation}\begin{aligned}
 	\label{siam_attr}
-	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + \sum_{k\sigma} \left(V_{k} c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
-\end{aligned}\end{equation}
-
-We will use this as the auxiliary model to study the Hubbard model.
-We do this by first recreating the Hubbard model upon tiling the lattice with instances of this auxiliary model Hamiltonian.
+	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + V \sum_{k\sigma} \left(c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2~,
+\end{aligned}\end{equation}
+where \(c_{d\sigma}\) is the impurity electron operator, \(c_{k\sigma}\) is the conduction bath electron operator, \(\vec S_d\) is the impurity spin operator and \(\vec s\) is the operator for the local spin in the conduction bath.
+We have found that the e-SIAM has a stable local moment phase for \(U_b < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)).
+We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of a coexistence region at finite temperatures.
+
+We will now use the e-SIAM to recreate the Hubbard model, by tiling the lattice with instances of this auxiliary model Hamiltonian.
 Note that the impurity level is explicitly at half-filling, because the correlation term \(\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is symmetric under a particle-hole transformation \(\hat n_{d\sigma} \to 1 - \hat n_{d\sigma}\).

### 2023-07-27 TilingProjectDraft/tilingProject.tex
corrected typos

@@
 Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes.
-We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath site connected to the impurity.
+We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model).
 The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
@@
 \begin{equation}\begin{aligned}
-	\label{self-energy1}
+	\label{selfenergy1}
 	\Sigma_{H-H}(\vec k,\omega) = 1/\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)} - 1/\left(G_{H-H}(\omega)\right)_{\vec k} = \frac{\left(\lambda_{\vec k_0}^{(0)}\right)^2}{\mathcal{G}^{(0)}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{W}}\mathcal{G}^{(0)}_{dz}(\omega)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{W}}\mathcal{G}_{dz}(\omega)}~,
@@
 \begin{equation}\begin{aligned}
-	\Sigma_{H-H}(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~\label{selfenergy1}
+	\Sigma_{H-H}(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~\label{selfenergy2}
 \end{aligned}\end{equation}
@@
 This simplification is what makes DMFT exact in the limit of infinite dimensions.
-This simplification is also explicit in our formalism, as can be seen in the expression of the self-energy (eq.~\ref{selfenergy1}).
+This simplification is also explicit in our formalism, as can be seen in the expression of the Self-energy (eq.~\eqref{selfenergy1}).
 Upon taking the limit of \(\mathcal{W}\to\infty\), the non-local terms drop out:

### 2023-08-11 TilingProjectDraft/tilingProject.tex
obtained actions

@@
 
+\subsection{Extending the Anderson impurity model: Identifying the correct auxiliary model}
 The standard Anderson model consists of a correlated impurity site coupled with a non-interacting conduction bath.
@@
 Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes.
-We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model).
+We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model).
 The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
@@
 We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of a coexistence region at finite temperatures.
-
-We will now use the e-SIAM to recreate the Hubbard model, by tiling the lattice with instances of this auxiliary model Hamiltonian.
 Note that the impurity level is explicitly at half-filling, because the correlation term \(\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is symmetric under a particle-hole transformation \(\hat n_{d\sigma} \to 1 - \hat n_{d\sigma}\).
@@
 
+\subsection{Formal description of the tiling procedure}
+We will now use the e-SIAM to recreate the Hubbard model, by tiling the lattice with instances of this auxiliary model Hamiltonian.
+We will now formally define the procedure.
+We first identify a local auxiliary model; this will act as the ``unit cell" for our tiling procedure.
+For this, we place the impurity orbitals at a reference site \(\vec R_0\) of our lattice, and the bath zeroth site at a nearest-neighbour site \(\vec R_0 + \vec a\), and call the corresponding e-SIAM Hamiltonian \(\mathcal{H}_\text{aux}(\vec R_0, \vec a)\).
+The auxiliary model at \(\vec R_0\) can then be obtained by averaging over all nearest neighbours:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux}(\vec R_0) = \frac{1}{\mathcal{W}}\sum_{\vec a}\mathcal{H}_\text{aux}(\vec R_0, \vec a)~,
+\end{aligned}\end{equation}
+where \(\vec a\) is summed over all nearest-neighbours of \(\vec R_0\) and \(\mathcal{W}\) is the number of such nearest-neighbours.
+In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice.
+For this, we define {\it many-particle} translation operators \(T(\vec a)\) in the usual manner: for a local fermionic operator \(c(\vec r)\), we have \(T(\vec a) c(\vec r) T^\dagger(\vec a) = c(\vec r + \vec a)\).
+It can also work on many-particle operators: \(T(\vec a) c(\vec r^\prime) c(\vec r) T^\dagger(\vec a) = T(\vec a) c(\vec r^\prime) T^\dagger(\vec a) T(\vec a) c(\vec r) T^\dagger(\vec a) = c(\vec r^\prime + \vec a) c(\vec r + \vec a)\).
+It acts similarly on the auxiliary model Hamiltonian:
+\begin{equation}\begin{aligned}
+	T(\vec a)\mathcal{H}_\text{aux}(\vec R_0)T^\dagger(\vec a) = \mathcal{H}_\text{aux}(\vec R_0 + \vec a)~.
+\end{aligned}\end{equation}
+The full bulk model can then be expressed as
+\begin{equation}\begin{aligned}
+	\label{tiledHamiltonian}
+	\mathcal{H}_\text{full} = \sum_{\vec r}T(\vec r)\mathcal{H}_\text{aux}(\vec R_0)T^\dagger(\vec r)~ = \sum_{\vec r} \mathcal{H}_\text{aux}(\vec r) = \frac{1}{\mathcal{W}}\sum_{\vec r, \vec a}\mathcal{H}_\text{aux}(\vec r, \vec a),
+\end{aligned}\end{equation}
+where \(\vec r\) sums over all lattice sites.
+
+\subsection{Tiling towards a Hubbard-Heisenberg model}
 To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(i\) of the lattice, and the bath coupled to the impurity as the set of remaining \(N-1\) sites in the lattice.
@@
 
+\subsection{Translation symmetry and a conserved total momentum}
+From the form in eq.~\ref{tiledHamiltonian}, the tiled Hamiltonian is symmetric under discrete many-body translations:
+\begin{equation}\begin{aligned}\label{translationSymmetry}
+	T(\vec r)\mathcal{H}_\text{full}T^\dagger(\vec r) = \sum_{\vec r^\prime}T(\vec r + \vec r^\prime)\mathcal{H}_\text{aux}(\vec R_0)T^\dagger(\vec r + \vec r^\prime) = \sum_{\vec r^\prime}T(\vec r^\prime)\mathcal{H}_\text{aux}(\vec R_0)T^\dagger(\vec r^\prime) = \mathcal{H}_\text{full}~.
+\end{aligned}\end{equation}
+There we used the fact that \(\vec r + \vec r^\prime\) simply translates the auxiliary model defined by the coordinate \(\vec r^\prime + \vec R_0\) to a new auxiliary model at the modified coordinate \(\vec r + \vec r^\prime + \vec R_0\).
+Since this transformation from one auxiliary model to another simply shuffles the group of all auxiliary models, the sum over the group remains the sum, and we recover the same bulk model.
+
+The fact that the Hamiltonian \(\mathcal{H}_\text{full}\) commutes with the many-body translation operator implies that the total momentum \(\vec k\) is a conserved quantity.
+This is in fact because the many-body translation operators can be obtained in terms of \(\vec k\): \(T(\vec r) = \exp\left\{ i \vec{k}\cdot\vec{r} \right\} \).
+
+\subsection{Moving away from half-filling}
 As mentioned before, no chemical potential \(\mu\) is generated because the auxiliary model was at half-filling, both in the impurity as well as in the bath.
@@
 
-\section{Nature of the wavefunctions}
-In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full wavefunction \(\Psi\) is then obtained by constructing liner combinations of the eigenstates \(\psi_i\) of the local Hamiltonians such that \(\Psi\) satisfies Bloch's theorem: \(\Psi_{\vec k}(\vec r) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r - \vec R_i)\).
+\section{Effective action for the Hubbard-Heisenberg model and the eSIAM}
+In order to better understand the similarities and differences between the tiling approach outlined here and the approach adopted in dynamical mean-field approximations, we compute the effective action for the local impurity as well as the impurity-zeroth site system, in both the auxiliary and bulk models.
+This will be done in the limit of infinite coordination number, in order to create a tractable effective theory.
+
+\subsection{Local theory for the Hubbard-Heisenberg model}
+We will first work with the Hubbard-Heisenberg model.
+Let us recall that within the eSIAM, most of the dynamics is governed by the physics of the impurity site and the bath site coupled to the impurity.
+Accordingly, we will first obtain an effective action within the Hubbard-Heisenberg model for the small system consisting of a local site and all its nearest-neighbours.
+
+We choose a certain local site that we call \(0\), whose nearest-neighbours will be denoted as \(\left\{ {\bar 0} \right\} \).
+The action for the full Hubbard-Heisenberg model can be formally separated into three parts:
+\begin{equation}\begin{aligned}
+S_\text{H-H} = S_{0,{\bar 0}} + S^{(0,{\bar 0})} + S_\text{int}~,
+\end{aligned}\end{equation}
+where \(S_{0,{\bar 0}}\) represents the part of the action that involves only the sites \(0\) and $\left\{ {\bar 0} \right\}$, \(S^{(0,{\bar 0})}\) represents the part that has all the sites apart from \(0\) and \(\left\{ {\bar 0} \right\} \), while \(S_\text{int}\) contains all terms that connect these two parts.
+These three parts have the forms
+\begin{equation}\begin{aligned}
+S_{0,{\bar 0}} = \sum_{i=0,{\bar 0}}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau)  - t\sum_{{\bar 0},\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{0\sigma}(\tau)c_{{\bar 0}\sigma}(\tau) + \text{h.c.}\right] \\
+- \frac{U}{2}\sum_{i=0,{\bar 0}}\int_0^\beta\mathrm{d\tau}~\left(n_{i \uparrow}(\tau) - n_{i \downarrow}(\tau)\right)^2 + J\sum_{{\bar 0}}\int_0^\beta\mathrm{d\tau} \vec{S}_0(\tau)\cdot\vec{S}_{{\bar 0}}(\tau)~,
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+S^{(0,{\bar 0})} = \sum_{j\neq(0,{\bar 0})}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{j\sigma}(\tau)\partial_\tau c_{j\sigma}(\tau)  - t\sum_{\left<j,l\right>\neq (0,{\bar 0}),\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{j\sigma}(\tau)c_{l\sigma}(\tau) + \text{h.c.}\right] \\
+- \frac{U}{2}\sum_{j\neq(0,{\bar 0})}\int_0^\beta\mathrm{d\tau}~\left(n_{j\uparrow}(\tau) - n_{j\downarrow}(\tau)\right)^2 + J\sum_{\left<j,l\right>\neq(0,{\bar 0})}\int_0^\beta\mathrm{d\tau} \vec{S}_l(\tau)\cdot\vec{S}_j(\tau)~,
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+S_\text{int} = -t\sum_{i \in {\bar 0}}\sum_{j \in \text{NN of}~i}\sum_\sigma \int_0^\beta\mathrm{d\tau}~\left(c^\dagger_{i\sigma}(\tau) c_{j\sigma}(\tau) + \text{h.c.}\right) + J\sum_{i \in {\bar 0}}\sum_{j \in \text{NN of}~i}\int_0^\beta\mathrm{d\tau}\vec{S}_i(\tau)\cdot\vec{S}_j(\tau) = S_\text{int}^\text{hop} + S_\text{int}^\text{spin}
+\end{aligned}\end{equation}
+
+In order to obtain an effective theory \(S^{0,{\bar 0}}_\text{eff}\) purely for the local system \((0,{\bar 0})\), we need to trace over all the other degrees of freedom.
+This partial trace will be carried out over the states of the so-called ``cavity" system \(S^{(0,{\bar 0})}\).
+The effective action can be constructed by tracing over scattering processes of all orders that leave the final action diagonal in the system \((0,{\bar 0})\).
+The formal expression can be written as
+\begin{equation}\begin{aligned}
+	S^{0,{\bar 0}}_\text{eff} = S_{0,{\bar 0}} + \sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} + \sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})}
+\end{aligned}\end{equation}
+where, as mentioned before, the average is carried out in the cavity system \(S^{(0,{\bar 0})}\). Each hopping term in the expansion is of the form
+\begin{equation}\begin{aligned}
+	\left(S_\text{int}^\text{hop}\right)^{2n} =& t^{2n}\sum_\sigma\sum_{(i_1, i_1^\prime)\ldots, (i_n, i_n^\prime)} ~\sum_{(j_1, j_1^\prime)\ldots, (j_n, j_n^\prime)} \int_0^\beta d\tau_{1}\ldots d\tau_{n}d\tau_{1}^\prime\ldots d\tau_{j_n}^\prime\\
+			   &c^\dagger_{i_1\sigma}(\tau_{i_1})c^\dagger_{i_2\sigma}(\tau_{2})\ldots c^\dagger_{i_n\sigma}(\tau_{n}) c_{i_1^\prime\sigma}(\tau_{1}^\prime)c_{i_2^\prime\sigma}(\tau_{2}^\prime)\ldots c_{i_n^\prime\sigma}(\tau_{n}^\prime)\left<c_{j_1\sigma}(\tau_{1})c_{j_2\sigma}(\tau_{2})\ldots c_{j_n\sigma} ~ c^\dagger_{j_1^\prime\sigma}(\tau_{1}^\prime)\ldots c^\dagger_{j_n^\prime\sigma}(\tau_{n}^\prime) \right>_{(0,{\bar 0})}\\
+	=& t^{2n}\sum_\sigma\sum_{(i_1, i_1^\prime)\ldots, (i_n, i_n^\prime)} ~\sum_{(j_1, j_1^\prime)\ldots, (j_n, j_n^\prime)} \int_0^\beta d\tau_{1}\ldots d\tau_{j_n}^\prime c^\dagger_{i_1\sigma}(\tau_{i_1})\ldots c^\dagger_{i_n\sigma}(\tau_{n})~c_{i_1^\prime\sigma}(\tau_{1}^\prime)\ldots c_{i_n^\prime\sigma}(\tau_{n}^\prime)\\
+	 &G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right)~,
+\end{aligned}\end{equation}
+where the indices \(i_1\) through \(i_n\) and their primed counterparts run through \(\bar 0\), while \(j_l\) (\(\in \left\{j_1,\ldots,j_n^\prime\right\}\)) runs through the nearest-neighbours of the corresponding \(i_l\) index.
+The \(n-\)particle Greens function \(G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right)\) for the cavity system is defined in the usual fashion
+\begin{equation}\begin{aligned}
+	G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right) = \left<c_{j_1\sigma}(\tau_{1})c_{j_2\sigma}(\tau_{2})\ldots c_{j_n\sigma} ~ c^\dagger_{j_1^\prime\sigma}(\tau_{1}^\prime)\ldots c^\dagger_{j_n^\prime\sigma}(\tau_{n}^\prime) \right>_{(0,{\bar 0})}
+\end{aligned}\end{equation}
+In the limit of infinite coordination number, only the \(n=1\) term survives:
+\begin{equation}\begin{aligned}
+	\lim_{\mathcal{W}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} = t^2\sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)\sum_{j,j^\prime}G_1^{(0,\bar 0)}\left(j\tau; j^\prime\tau^\prime\right) \\
+	= \sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)~,
+\end{aligned}\end{equation}
+where we have defined the bath hybridisation function \(\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)\) as
+\begin{equation}\begin{aligned}
+	\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime) = t^2\sum_{j \in \text{NN of}~i}\sum_{j^\prime \in \text{NN of}~i^\prime}G_1^{(0,\bar 0)}\left(j\sigma\tau; j^\prime\sigma\tau^\prime\right)~.
+\end{aligned}\end{equation}
+
+Under similar approximations, the spin term in the action reduces to
+\begin{equation}\begin{aligned}
+	\lim_{\mathcal{W}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})} = \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\chi(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)~,
+\end{aligned}\end{equation}
+where the susceptibility \(\chi_{ii^\prime}(\tau - \tau^\prime)\) is defined as 
+\begin{equation}\begin{aligned}
+	\chi_{ii^\prime}(\tau - \tau^\prime) = J^2\sum_{j \in \text{NN of}~i}\sum_{j^\prime \in \text{NN of}~i^\prime}\vec{S}_{j}(\tau)\cdot\vec{S}_{j^\prime}(\tau^\prime)~.
+\end{aligned}\end{equation}
+The effective action for the \(0,\bar 0\) system, in the limit of large coordination number, simplifies to
+\begin{equation}\begin{aligned}
+	S^{0,{\bar 0}}_\text{eff} =& \sum_{i=0,{\bar 0}}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau)  - t\sum_{{\bar 0},\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{0\sigma}(\tau)c_{{\bar 0}\sigma}(\tau) + \text{h.c.}\right] - \frac{U}{2}\sum_{i=0,{\bar 0}}\int_0^\beta\mathrm{d\tau}~\left(n_{i \uparrow}(\tau) - n_{i \downarrow}(\tau)\right)^2 \\
+				   &+ J\sum_{{\bar 0}}\int_0^\beta\mathrm{d\tau} \vec{S}_0(\tau)\cdot\vec{S}_{{\bar 0}}(\tau) + \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{ii^\prime}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
+\end{aligned}\end{equation}
+
+One can also write down an effective action purely for the local site \(0\).
+The sites \(\bar 0\) will now be a part of the environment action \(S^{(0)}\) instead of the system action, but since the system is thermodynamically large, the cavity action can be assumed to remain the same, such the expectation values are calculated in the same system.
+As a result, the hybridisation and susceptibility functions remain unchanged.
+\(S_\text{int}\) is now made of terms that connect \(0\) and \(\bar 0\), so the transformation from \(S^{(0,\bar 0)}\) can be made by replacing the set \(\left\{ j \right\} \) with the set \(\bar 0\), and the set \(\bar 0\) itself will be replaced by the local site \(0\).
+We quote the final form of the local effective action:
+\begin{equation}\begin{aligned}
+	S^{0}_\text{eff} =& \sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{0\sigma}(\tau)\partial_\tau c_{0\sigma}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{0\uparrow}(\tau) - n_{0\downarrow}(\tau)\right)^2 \\
+			  &+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\Delta_{00,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{00}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
+\end{aligned}\end{equation}
+
+\subsection{Local theory for the extended SIAM}
+The Hamiltonian for the extended SIAM model is shown in eq.~\ref{siam_attr}.
+We will denote the impurity with the label \(d\) and the bath sites with the label \(c\).
+Among the bath sites, we will represent the site coupled to the impurity with \(z\).
+The full action has the form
+\begin{equation}\begin{aligned}
+	S_\text{ES} = \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - t\sum_{\left<i,j \right> \in c,\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{i\sigma}(\tau)c_{j\sigma}(\tau) + \text{h.c.}\right] - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right]\\
++ J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{U_b}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 ~,
+\end{aligned}\end{equation}
+As in the Hubbard-Heisenberg model, we first obtain an effective action for the pair of sites \((d,z)\).
+As in the previous calculation, this will again generate a hybridisation function \(\Delta_{zz,\sigma}\) for the bath site nearest to the zeroth site.
+No susceptibility will be generated however, because there is no spin-exchange coupling within the bath.
+The net result is
+\begin{equation}\begin{aligned}
+	S^{d,z}_\text{eff} =& \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right] + J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) \\
+	&- \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{U_b}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 \\
+	&+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\sum_{\sigma}\Delta_{zz,\sigma}(\tau - \tau^\prime)c^\dagger_{z\sigma}(\tau)c_{z\sigma}(\tau^\prime)
+\end{aligned}\end{equation}
+This hybridisation \(\Delta_{zz,\sigma}\) is calculated in the cavity model of the eSIAM, obtained by removing the impurity and the zeroth site from the full model; it is a completely non-interacting system.
+
+One can go one step further and also remove the zeroth site in order to obtain a theory for the impurity site.
+With this choice, the cavity model now also includes the zeroth site, and hence contains the correlation term associated with \(U_b\).
+The one-particle connection \(V\) will lead to a modified hybridisation \(\mathcal{F}\) for this effective theory; the Kondo terms will generate a susceptibility.
+The resultant action is
+\begin{equation}\begin{aligned}
+	S^{d}_\text{eff} =& \sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{d\sigma}(\tau)\partial_\tau c_{d\sigma}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 \\
+			  &+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\mathcal{F}_{\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{d}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
+\end{aligned}\end{equation}
+where \(\mathcal{F}\) is defined in terms of the local correlator of the zeroth site
+\begin{equation}\begin{aligned}
+	\mathcal{F}_\sigma(\tau - \tau^\prime) = V^2 G_1^{(d)}\left(z\sigma\tau; z\sigma\tau^\prime\right) = V^2 \left<c_{z\sigma}(\tau)c^\dagger_{z\sigma}(\tau^\prime)\right>_{(d)}
+\end{aligned}\end{equation}
+with the average computed in the interacting cavity model that has the impurity site removed.
+The interaction arises from the \(U_b-\)term.
+The susceptibility is also calculated in this interacting cavity model, and follows the same definition as in the bulk model:
+\begin{equation}\begin{aligned}
+	\chi_{d}(\tau - \tau^\prime) = J^2\vec{S}_{z}(\tau)\cdot\vec{S}_{z}(\tau^\prime)~.
+\end{aligned}\end{equation}
+
+\section{Form of the eigenstates: Bloch's theorem}
+In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\vec k}(\vec r)} = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \ket{\psi_i(\vec r - \vec R_i)}\).
 Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation \(T(\vec R)\) by some lattice distance \(\vec R = \sum_i n_i \vec a_i\):
 \begin{equation}\begin{aligned}
-T(\vec R)\Psi_{\vec k}\left(\vec r\right) = \Psi_{\vec k}(\vec r + \vec R) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r + \vec R - \vec R_i) = e^{i \vec{k}\cdot\vec{R}}\sum_i e^{i \vec{k}\cdot\left(\vec{R}_i - \vec R\right)} \psi_i(\vec r - (\vec R_i - \vec R)) = e^{\vec{k}\cdot\vec{R}}\Psi(\vec r)
-\end{aligned}\end{equation}
-At the end, we used the fact that \(\vec r_i - \vec R\) is just another lattice vector \(\vec R_j\).
-Note that the translation operator has been defined as an operation that simply advances the argument of the wavefunction from \(\vec r\) to \(\vec r + \vec R\).
-An equivalent definition can be given in terms of their action on position eigenkets: \(T(\vec R)\ket{\vec r} = \ket{\vec r - \vec R}\).
-These translation operators share eigenstates with the momentum operator:
+	T(\vec R)\ket{\Psi_{\vec k}\left(\vec r\right)} = \ket{\Psi_{\vec k}(\vec r + \vec R)} = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \ket{\psi_i(\vec r + \vec R - \vec R_i)} = e^{i \vec{k}\cdot\vec{R}}\sum_i e^{i \vec{k}\cdot\left(\vec{R}_i - \vec R\right)} \ket{\psi_i(\vec r - (\vec R_i - \vec R))} = e^{\vec{k}\cdot\vec{R}}\ket{\Psi(\vec r)}
+\end{aligned}\end{equation}
+At the end, we used the fact that \(\vec r_i - \vec R\) is just another lattice vector \(\vec R_j\). As mentioned before, these translation operators share eigenstates with the momentum operator:
 \begin{equation}\begin{aligned}
@@
 
-The bulk Hamiltonian obtained in eq.~\ref{siam_to_hubb},
-\begin{equation}\begin{aligned}
-	H_\text{H-H}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i} \mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i\right\}\right) \equiv \sum_{\vec R_i} \mathcal{H}_\text{aux}\left(\vec R_i\right)~,
-\end{aligned}\end{equation}
-also enjoys a Bloch's theorem. This is because the tiling procedure restores the translation symmetry of the lattice:
-\begin{equation}\begin{aligned}
-	H_\text{H-H}\left(\left\{\vec r_k + \vec R\right\}\right) =  \sum_{\vec R_i}\mathcal{H}_\text{aux,i}\left(\left\{\vec r_k - \vec R_i + \vec R\right\}\right) = \sum_{\vec R_i} \mathcal{H}_{\text{aux},\tilde i}\left(\left\{\vec r_k - \vec R\right\}\right) = H_\text{H-H}(\left\{\vec r_k\right\})
-\end{aligned}\end{equation}
-There we used the fact that \(\vec r_k + \vec R\) simply translates the auxiliary model defined by the coordinate \(i\) to a new auxiliary model at the modified coordinate \(\tilde i: \vec R_i^\prime = \vec R_i + \vec R\).
-Since this transformation from one auxiliary model to another simply shuffles the group of all auxiliary models, the sum over the group remains the sum, and we recover the same bulk model.
-
-We can use the auxiliary model zero-bandwidth wavefunctions 
-\begin{equation}\begin{aligned}
-\psi^n_\text{aux}\left(\vec r_d - \vec R_i, \vec r_0 - \left(\vec R_i + \vec a\right)  \right) \equiv \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
+The eigenstates of bulk Hamiltonian obtained in eq.~\ref{siam_to_hubb} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}).
+This means that we can use the auxiliary model eigenstates
+\begin{equation}\begin{aligned}
+\psi^n_\text{aux}\left(\vec R_i, \vec a\right)~,
 \end{aligned}\end{equation}
@@
 \(\vec R_i\) is a lattice vector, while \(\vec a\) is one of the \(\mathcal{W}\) vectors that connect a lattice site with its nearest neighbours.
-This two site wavefunction can be obtained by first studying the full auxiliary model \(\mathcal{H}_\text{aux}\) under a renormalisation group, obtaining a fixed-point Hamiltonian in the IR, obtaining the IR eigenstate and then tracing out all lattice sites except the impurity and the zeroth site from this eigenstate.
+The \(n\) in the superscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
 \(n=0\) is the ground state of the auxiliary model, and higher values denote the excited states.
-
 The following un-normalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:

### 2024-01-29 dWaveESIAM.tex
--no-message

\documentclass{revtex4-2}
\usepackage{amsmath}
\begin{document}
\title{URG analysis of the extended Kondo model with d-wave interaction}
\author{Abhirup Mukherjee, Siddhartha Lal}
\maketitle
\section{Hamiltonian}
We consider an impurity spin \(\vec S_d\) interacting with a two-dimensional tight-binding conduction bath through the d-wave channel :
\begin{equation}\begin{aligned}
	J \vec{S}_d\cdot\vec{S_f},\quad \vec S_f = \frac{1}{2}\sum_{\sigma,\sigma^\prime}\vec \tau_{\sigma,\sigma^\prime}f^\dagger_{\sigma}f_{\sigma^\prime}.
\end{aligned}\end{equation}
where \(\vec \tau\) is the vector of sigma matrices. The spin \(\vec S_f\) is constructed in terms of the d-wave electron \(f_{\sigma} = \frac{1}{2}\left(c^\dagger_{L,\sigma} + c^\dagger_{R,\sigma} - c^\dagger_{U\sigma} - c^\dagger_{D\sigma}\right) \), where \(L,R,U\) and \(D\) indicate electrons at the positions \((x,y)=\left(-a,0\right), \left( a,0 \right) , \left( 0,a \right) \) and \(\left( 0,-a \right) \) respectively, \(a\) being the lattice spacing of the conduction bath lattice. We also consider local bath correlations in the \(d-\)wave channel:
\begin{equation}\begin{aligned}
	-\frac{W}{2}\left(f^\dagger_{\uparrow}f_{\uparrow} - f^\dagger_{\downarrow}f_{\downarrow}\right)^2.
\end{aligned}\end{equation}
In order to facilitate a momentum-space decoupling RG scheme, we Fourier transform the \(d-\)wave operator to momentum space:
\begin{equation}\begin{aligned}
	f_{\sigma} = \frac{1}{2}\left(c^\dagger_{L,\sigma} + c^\dagger_{R,\sigma} - c^\dagger_{U\sigma} - c^\dagger_{D\sigma}\right) = \frac{1}{2}\sum_{\vec k}c^\dagger_{\vec k,\sigma}\left[e^{-ik^x a} + e^{ik^x a} - e^{-ik^y a} - e^{ik^y a}\right] =\sum_{\vec k}\left[\cos\left( ak^x \right) - \cos\left( ak^y \right) \right] c^\dagger_{\vec k,\sigma}~.
\end{aligned}\end{equation}
The Kondo interaction term takes the following form in momentum space:
\begin{equation}\begin{aligned}
	J \vec{S}_d\cdot\vec{S_f} = \frac{1}{2}J \sum_{\vec k_1, \vec k_2, \sigma,\sigma^\prime}\vec{S}_d\cdot\vec{\tau}_{\sigma,\sigma^\prime}c^\dagger_{\vec k_1\sigma}c_{\vec k_2,\sigma^\prime}\prod_{i=1,2}\left[\cos\left( ak_i^x \right) - \cos\left( ak_i^y \right) \right]~.
\end{aligned}\end{equation}
The local correlation term can be similarly written in momentum space:
\begin{equation}\begin{aligned}
	-\frac{W}{2}\left(f^\dagger_{\uparrow}f_{\uparrow} - f^\dagger_{\downarrow}f_{\downarrow}\right)^2 = -\frac{W}{2}\sum_{\vec k_1,\vec k_2, \vec k_3, \vec k_4,\sigma}\left(c^\dagger_{\vec k_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma}c_{\vec k_4,\sigma} - c^\dagger_{\vec k_1\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3\bar\sigma}c_{\vec k_4,\bar\sigma}\right)\prod_{i=1,2,3,4}\left[\cos\left( ak_i^x \right) - \cos\left( ak_i^y \right) \right]~.
\end{aligned}\end{equation}
Combining all the terms, the Hamiltonian can be formally written as
\begin{equation}\begin{aligned}
	H = \sum_{\vec k,\sigma}\varepsilon_{\vec k}c^\dagger_{\vec k,\sigma}c_{\vec k,\sigma} + \frac{1}{2}\sum_{\vec k_1, \vec k_2, \sigma,\sigma^\prime}J_{\vec k_1, \vec k_2}\vec{S}_d\cdot\vec{\tau}_{\sigma,\sigma^\prime}c^\dagger_{\vec k_1\sigma}c_{\vec k_2,\sigma^\prime} - \frac{1}{2}\sum_{\vec k_1,\vec k_2, \vec k_3, \vec k_4,\sigma,\sigma^\prime}W_{\vec k_1,\vec k_2,\vec k_3,\vec k_4} \sigma\sigma^\prime c^\dagger_{\vec k_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec k_4,\sigma^\prime}~.
\end{aligned}\end{equation}
with 
\begin{equation}\begin{aligned}
	\varepsilon_{\vec k} &= -2t\left[\cos\left(ak^x\right) + \cos\left(ak^y\right)\right], \\
	J_{\vec k_1, \vec k_2} &= J\prod_{i=1,2}\left[\cos\left( ak_i^x \right) - \cos\left( ak_i^y \right) \right], \\
	W_{\vec k_1,\vec k_2,\vec k_3,\vec k_4}  &= W\prod_{i=1,2,3,4}\left[\cos\left( ak_i^x \right) - \cos\left( ak_i^y \right) \right].
\end{aligned}\end{equation}
The coupling \(W_{\vec k_1,\vec k_2,\vec k_3,\vec k_4}\) has certain symmetries. It is independent of the sequence of momentum indices. It remains invariant if any number of the momenta undergo rotation by an integer multiple of \(\pi/2\). It also remains invariant if an even number of momenta are reflected about the nodal point in the corresponding quadrant.

\section{RG scheme}
At any given step \(j\) of the RG procedure, we decouple the states \(\left\{ \vec q \right\} \) on the isoenergetic surface of energy \(\varepsilon_j\). The diagonal Hamiltonian \(H_D\) for this step consists of all terms that do not change the occupancy of the states \(\left\{\vec q\right\}\):
\begin{equation}\begin{aligned}
	H_D^{(j)} = \varepsilon_j\sum_{q,\sigma}\tau_{q,\sigma} + \sum_{\vec q}J_{\vec q, \vec q}S_d^z\left(\hat n_{\vec q, \uparrow} - \hat n_{\vec q, \downarrow}\right) - \frac{1}{2}\sum_{\vec q_1, \vec q_2}W_{\vec q_1, \vec q_1, \vec q_2, \vec q_2}\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \downarrow}\right)\left(\hat n_{\vec q_2, \uparrow} - \hat n_{\vec q_2, \downarrow}\right)~.
\end{aligned}\end{equation}
The three terms, respectively, are the kinetic energy of the momentum states on the isoenergetic shell that we are decoupling, the Ising interaction energy between the impurity spin and the spins formed by these momentum states and, finally, the local correlation energy associated with these states arising from the \(W\) term.

The off-diagonal part of the Hamiltonian on the other hand leads to scattering in the states \(\left\{ \vec q \right\} \):
\begin{equation}\begin{aligned}
	H_X^{(j)} =& \underbrace{\sum_{\vec k, \vec q, \sigma,\sigma^\prime}J_{\vec k, \vec q} \vec{S}_d\cdot\vec{\tau}_{\sigma,\sigma^\prime}\left[c^\dagger_{\vec q\sigma}c_{\vec k,\sigma} + \text{h.c.}\right]}_{T_1^\dagger + T_1} \\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec k_3, \vec k_4,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec k_4,\sigma^\prime} + \text{h.c.}\right]}_{T_2^\dagger + T_2}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec k_4,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} + \text{h.c.}\right]}_{T_3^\dagger + T_3}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2,\vec k_3,\vec q_2,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec q_2} \sigma\sigma^\prime \left(c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime} + c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime}c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}\right)}_{T_4 + T_5^\dagger}\\
		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec q_3,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec q_3} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec q_3,\sigma^\prime} + \text{h.c.}\right]}_{T_6 + T_6^\dagger}~.
\end{aligned}\end{equation}
The first term \(T_1\) is an impurity-mediated scattering between the states \(\vec q\) at energy \(\varepsilon_j\) and the states \(\vec k\) at energies below \(\varepsilon_j\). Terms \(T_2\) through \(T_6\) involve two-particle scattering between these momentum states involving an increasing number of states from the isoenergetic shell \(\varepsilon_j\), through the Hubbard-like local term \(W\). The renormalisation of the Hamiltonian is constructed from the general expression
\begin{equation}\begin{aligned}
	\Delta H^{(j)} = H_X \frac{1}{\omega- H_D} H_X~.
\end{aligned}\end{equation}

\section{Renormalisation of the bath correlation term \(W\)}
In order to lead to a renormalisation of the \(W-\)term, there must be a total of four uncontracted momentum indices \(k_i\) and two contracted indices \(q_1, q_2\). The following combinations of scattering processes are compatible: (i) \(T_2^\dagger G T_6 + T_6^\dagger G T_2\), (ii) \(T_3^\dagger G T_3 + T_3 G T_3^\dagger\) and (iii) \(T_4^\dagger G T_4 + T_5^\dagger G T_5\).

The first term is of the form
\begin{equation}\begin{aligned}
	T_2^\dagger G T_6 = \sum \sigma_1\sigma_1^\prime W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} c^\dagger_{\vec q_1, \sigma_1}c_{\vec k_2,\sigma_1}c^\dagger_{\vec k_3,\sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime} \frac{1}{\omega - H_D}\sigma_1\sigma_2^\prime W_{\vec q_1,\vec q_2,\vec q_2,\vec k_2^\prime} \hat n_{\vec q_2,\sigma_2^\prime}c^\dagger_{\vec k_2^\prime,\sigma_1}c_{\vec q_1,\sigma_1}~.
\end{aligned}\end{equation}
The change in occupancy of the state \(\vec q_1\sigma_1\) from 1 to 0 leads to an excited state energy \(H_D = \varepsilon(q_1)\tau_{q_1\sigma_1} - \frac{1}{2}W\left(\vec q_1\right)\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \uparrow}\right)^2 = -\frac{1}{2}\varepsilon(q_1) - \frac{1}{2}W\left(\vec q_1\right)\), where \(W\left(\vec q_1\right)\) is a shorthand for \(W\left(\vec q_1,\vec q_1,\vec q_1,\vec q_1\right)\). The number operator \(\hat n_{\vec q_2,\sigma_2^\prime}\) projects the initial state to that in which \(\vec q_2\) is occupied. The operator \(c_{\vec q_1,\sigma_1}\) can be combined with its hermitian conjugate on the other side to give another number operator, leading to another projection. Both the number operators reduce to unity upon acting on the projected states:
\begin{equation}\begin{aligned}
	T_2^\dagger G T_6 = \sum \sigma_1^2\sigma_1^\prime W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} W_{\vec q_1,\vec q_2,\vec q_2,\vec k_2^\prime} c_{\vec k_2,\sigma_1}c^\dagger_{\vec k_3,\sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime} c^\dagger_{\vec k_2^\prime,\sigma_1}\frac{1}{\omega + \frac{1}{2}\varepsilon(q_1) + \frac{1}{2}W\left(\vec q_1\right)}\sum_{\sigma_2^\prime}\sigma_2^\prime  ~.
\end{aligned}\end{equation}
Since there is a sum over the spin factor \(\sigma_2^\prime = \pm 1\), this term vanishes identically. The particle-hole transformed term \(T_6^\dagger G T_2\) vanishes for the same reason.

We now consider the second term \(T_3^\dagger G T_3\):
\begin{equation}\begin{aligned}
	T_3^\dagger G T_3 &= \frac{1}{4}\sum W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} \frac{1}{\omega - H_D} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime} \sigma\sigma^\prime c^\dagger_{\vec k^\prime_4,\sigma^\prime} c_{\vec q_2,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} c_{\vec q_1,\sigma}\\
			  &= \frac{1}{4}\sum  \hat n_{\vec q_1,\sigma} \hat n_{\vec q_2,\sigma^\prime} c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} \frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left[\sqrt{W\left(\vec q_1\right)} + \sigma\sigma^\prime\sqrt{W\left(\vec q_2\right)}\right]^2}\\
			  &= \frac{1}{4}\sum c^\dagger_{\vec k^\prime_4,\sigma^\prime} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma}c_{\vec k_2,\sigma}  \sum_{\vec q_1, \vec q_2}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left[\sqrt{W\left(\vec q_1\right)} + \sigma\sigma^\prime\sqrt{W\left(\vec q_2\right)}\right]^2}~,
\end{aligned}\end{equation}
where the final sum over \(\vec q_1, \vec q_2\) is over all the states that are occupied.

The particle-hole transformed term is \(T_3 G T_3^\dagger\):
\begin{equation}\begin{aligned}
	T_3 G T_3^\dagger &= \frac{1}{4}\sum  W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime} \sigma\sigma^\prime c^\dagger_{\vec k^\prime_4,\sigma^\prime} c_{\vec q_2,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} c_{\vec q_1,\sigma}\frac{1}{\omega - H_D}W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} \\
			  &= \frac{1}{4}\sum \left(1 - \hat n_{\vec q_1,\sigma}\right) \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right) c^\dagger_{\vec k^\prime_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma}  c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left[\sqrt{W\left(\vec q_1\right)} + \sigma\sigma^\prime\sqrt{W\left(\vec q_2\right)}\right]^2}\\
			  &= \frac{1}{4}\sum c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} \sum_{\vec q_1, \vec q_2}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left[\sqrt{W\left(\vec q_1\right)} + \sigma\sigma^\prime\sqrt{W\left(\vec q_2\right)}\right]^2}~,
\end{aligned}\end{equation}

\end{document}

### 2024-01-29 dWaveESIAM.tex
completed Ub renormalisation

@@
 \begin{equation}\begin{aligned}
-	H_D^{(j)} = \varepsilon_j\sum_{q,\sigma}\tau_{q,\sigma} + \sum_{\vec q}J_{\vec q, \vec q}S_d^z\left(\hat n_{\vec q, \uparrow} - \hat n_{\vec q, \downarrow}\right) - \frac{1}{2}\sum_{\vec q_1, \vec q_2}W_{\vec q_1, \vec q_1, \vec q_2, \vec q_2}\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \downarrow}\right)\left(\hat n_{\vec q_2, \uparrow} - \hat n_{\vec q_2, \downarrow}\right)~.
+	H_D^{(j)} = \varepsilon_j\sum_{q,\sigma}\tau_{q,\sigma} + \sum_{\vec q}J_{\vec q, \vec q}S_d^z\left(\hat n_{\vec q, \uparrow} - \hat n_{\vec q, \downarrow}\right) - \frac{1}{2}\sum_{\vec q_1}W_{\vec q_1, \vec q_1, \vec q_1, \vec q_1}\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \downarrow}\right)^2~.
 \end{aligned}\end{equation}
+where \(\tau = \hat n - 1/2\).
 The three terms, respectively, are the kinetic energy of the momentum states on the isoenergetic shell that we are decoupling, the Ising interaction energy between the impurity spin and the spins formed by these momentum states and, finally, the local correlation energy associated with these states arising from the \(W\) term.
@@
 		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec k_4,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} + \text{h.c.}\right]}_{T_3^\dagger + T_3}\\
-		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2,\vec k_3,\vec q_2,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec q_2} \sigma\sigma^\prime \left(c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime} + c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime}c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}\right)}_{T_4 + T_5^\dagger}\\
+		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2,\vec k_3,\vec q_2,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec q_2} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime}}_{T_4}\\
+		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2,\vec k_3,\vec q_2,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec q_2} \sigma\sigma^\prime c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime}c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}}_{T_5}\\
 		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec q_3,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec q_3} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec q_3,\sigma^\prime} + \text{h.c.}\right]}_{T_6 + T_6^\dagger}~.
@@
 The first term \(T_1\) is an impurity-mediated scattering between the states \(\vec q\) at energy \(\varepsilon_j\) and the states \(\vec k\) at energies below \(\varepsilon_j\).
-Terms \(T_2\) through \(T_6\) involve two-particle scattering between these momentum states involving an increasing number of states from the isoenergetic shell \(\varepsilon_j\), through the Hubbard-like local term \(W\).
+Terms \(T_2\) through \(T_6\) involve two-particle scattering between these momentum states involving an increasing number of participating states from the isoenergetic shell \(\varepsilon_j\), through the Hubbard-like local term \(W\).
 The renormalisation of the Hamiltonian is constructed from the general expression
@@
 In order to lead to a renormalisation of the \(W-\)term, there must be a total of four uncontracted momentum indices \(k_i\) and two contracted indices \(q_1, q_2\).
-The following combinations of scattering processes are compatible: (i) \(T_2^\dagger G T_6 + T_6^\dagger G T_2\), (ii) \(T_3^\dagger G T_3 + T_3 G T_3^\dagger\) and (iii) \(T_4^\dagger G T_4 + T_5^\dagger G T_5\).
+The following combinations of scattering processes are compatible: (i) \(T_2^\dagger G T_6 + T_6^\dagger G T_2\), (ii) \(T_3^\dagger G T_3 + T_3 G T_3^\dagger\), (iii) \(T_4 G T_4\), (iv) \(T_5 G T_5\) and (v) \(T_4 G T_5 + T_5 G T_4\).
 
@@
 \end{aligned}\end{equation}
-The change in occupancy of the state \(\vec q_1\sigma_1\) from 1 to 0 leads to an excited state energy \(H_D = \varepsilon(q_1)\tau_{q_1\sigma_1} - \frac{1}{2}W\left(\vec q_1\right)\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \uparrow}\right)^2 = -\frac{1}{2}\varepsilon(q_1) - \frac{1}{2}W\left(\vec q_1\right)\), where \(W\left(\vec q_1\right)\) is a shorthand for \(W\left(\vec q_1,\vec q_1,\vec q_1,\vec q_1\right)\).
+The change in occupancy of the state \(\vec q_1\sigma_1\) from 1 to 0 leads to an excited state energy \(H_D = \varepsilon(q_1)\tau_{q_1\sigma_1} - \frac{1}{2}W_{\vec q_1}\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \uparrow}\right)^2 = -\frac{1}{2}\varepsilon(q_1) - \frac{1}{2}W_{\vec q_1}\), where \(W_{\vec q_1}\) is a shorthand for \(W_{\vec q_1,\vec q_1,\vec q_1,\vec q_1}\).
 The number operator \(\hat n_{\vec q_2,\sigma_2^\prime}\) projects the initial state to that in which \(\vec q_2\) is occupied.
@@
 \begin{equation}\begin{aligned}
-	T_2^\dagger G T_6 = \sum \sigma_1^2\sigma_1^\prime W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} W_{\vec q_1,\vec q_2,\vec q_2,\vec k_2^\prime} c_{\vec k_2,\sigma_1}c^\dagger_{\vec k_3,\sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime} c^\dagger_{\vec k_2^\prime,\sigma_1}\frac{1}{\omega + \frac{1}{2}\varepsilon(q_1) + \frac{1}{2}W\left(\vec q_1\right)}\sum_{\sigma_2^\prime}\sigma_2^\prime  ~.
+	T_2^\dagger G T_6 = \sum \sigma_1^2\sigma_1^\prime W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} W_{\vec q_1,\vec q_2,\vec q_2,\vec k_2^\prime} c_{\vec k_2,\sigma_1}c^\dagger_{\vec k_3,\sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime} c^\dagger_{\vec k_2^\prime,\sigma_1}\frac{1}{\omega + \frac{1}{2}\varepsilon(q_1) + \frac{1}{2}W_{\vec q_1}}\sum_{\sigma_2^\prime}\sigma_2^\prime  ~.
 \end{aligned}\end{equation}
@@
 	T_3^\dagger G T_3 &= \frac{1}{4}\sum W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} \frac{1}{\omega - H_D} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime} \sigma\sigma^\prime c^\dagger_{\vec k^\prime_4,\sigma^\prime} c_{\vec q_2,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} c_{\vec q_1,\sigma}\\
-			  &= \frac{1}{4}\sum  \hat n_{\vec q_1,\sigma} \hat n_{\vec q_2,\sigma^\prime} c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} \frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left[\sqrt{W\left(\vec q_1\right)} + \sigma\sigma^\prime\sqrt{W\left(\vec q_2\right)}\right]^2}\\
-			  &= \frac{1}{4}\sum c^\dagger_{\vec k^\prime_4,\sigma^\prime} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma}c_{\vec k_2,\sigma}  \sum_{\vec q_1, \vec q_2}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left[\sqrt{W\left(\vec q_1\right)} + \sigma\sigma^\prime\sqrt{W\left(\vec q_2\right)}\right]^2}~,
+			  &= \frac{1}{4}\sum  \hat n_{\vec q_1,\sigma} \hat n_{\vec q_2,\sigma^\prime} c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} \frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}\\
+			  &= \frac{1}{4}\sum_{4^\prime,4,2^\prime,2,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k^\prime_4,\sigma^\prime} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma}c_{\vec k_2,\sigma}  \sum_{\vec q_1, \vec q_2 \in \text{PS}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~,
 \end{aligned}\end{equation}
-where the final sum over \(\vec q_1, \vec q_2\) is over all the states that are occupied.
+where \(\vec q_1, \vec q_2\) are summed over all momentum states in the isoenergetic shell and in the particle sector (PS) (states are occupied in the ground state).
 
@@
 	T_3 G T_3^\dagger &= \frac{1}{4}\sum  W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime} \sigma\sigma^\prime c^\dagger_{\vec k^\prime_4,\sigma^\prime} c_{\vec q_2,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} c_{\vec q_1,\sigma}\frac{1}{\omega - H_D}W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} \\
-			  &= \frac{1}{4}\sum \left(1 - \hat n_{\vec q_1,\sigma}\right) \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right) c^\dagger_{\vec k^\prime_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma}  c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left[\sqrt{W\left(\vec q_1\right)} + \sigma\sigma^\prime\sqrt{W\left(\vec q_2\right)}\right]^2}\\
-			  &= \frac{1}{4}\sum c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} \sum_{\vec q_1, \vec q_2}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left[\sqrt{W\left(\vec q_1\right)} + \sigma\sigma^\prime\sqrt{W\left(\vec q_2\right)}\right]^2}~,
+			  &= \frac{1}{4}\sum \left(1 - \hat n_{\vec q_1,\sigma}\right) \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right) c^\dagger_{\vec k^\prime_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma}  c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega - \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}\\
+			  &= \frac{1}{4}\sum_{4^\prime,4,2^\prime,2,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k^\prime_4,\sigma^\prime}  c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma}  c_{\vec k_2,\sigma} \sum_{\vec q_1, \vec q_2 \in \text{HS}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega - \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~,
+\end{aligned}\end{equation}
+where the hole projectors \(\left(1 - \hat n_{\vec q_1,\sigma}\right) \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right)\) force the momenta \(\vec q_1,\vec q_2\) to extend over all states in the hole sector (states that are unoccupied in the ground state).
+The change in the sign of \(\left[\varepsilon(q_1) + \varepsilon(q_2)\right]\) in the denominator compared to the denominator in \(T_3^\dagger G T_3\) is for the same reason.
+
+The remaining sets of terms that we need to consider are:
+\begin{equation}\begin{aligned}
+	T_4 G T_4 &= \frac{1}{4}\sum  W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_1,\sigma^\prime}c_{\vec q_2,\sigma^\prime} \frac{1}{\omega - H_D}W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime}c^\dagger_{\vec k_3,\sigma}c_{\vec q_1,\sigma}\\
+		  &= \frac{1}{4}\sum \hat n_{\vec q_1,\sigma} \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right) c_{\vec k_2,\sigma}c^\dagger_{\vec k_1,\sigma^\prime}c_{\vec k_4,\sigma^\prime}c^\dagger_{\vec k_3,\sigma} \frac{W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4}}{\omega + \frac{1}{2}\varepsilon\left(q_1\right) - \frac{1}{2}\varepsilon\left(q_2\right) + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}  \\
+		  &= -\frac{1}{4}\sum_{1,2,3,4,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k_1,\sigma^\prime}c_{\vec k_4,\sigma^\prime}c^\dagger_{\vec k_3,\sigma}c_{\vec k_2,\sigma} \sum_{\vec q_1 \in \text{PS}, \atop{\vec q_2 \in \text{HS}}}\frac{W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4}}{\omega + \frac{1}{2}\varepsilon\left(q_1\right) - \frac{1}{2}\varepsilon\left(q_2\right) + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~.
+\end{aligned}\end{equation}
+
+\begin{equation}\begin{aligned}
+	T_5 G T_5 &= \frac{1}{4}\sum  W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} \sigma\sigma^\prime c^\dagger_{\vec k_1,\sigma^\prime}c_{\vec q_2,\sigma^\prime}c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma} \frac{1}{\omega - H_D}W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec k_3,\sigma}c_{\vec q_1,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime}\\
+		  &= \frac{1}{4}\sum \hat n_{\vec q_1,\sigma} \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right) c^\dagger_{\vec k_1,\sigma^\prime}c_{\vec k_2,\sigma}c^\dagger_{\vec k_3,\sigma}c_{\vec k_4,\sigma^\prime} \frac{W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4}}{\omega + \frac{1}{2}\varepsilon\left(q_1\right) - \frac{1}{2}\varepsilon\left(q_2\right) + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}  \\
+		  &= -\frac{1}{4}\sum_{1,2,3,4,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k_1,\sigma^\prime} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k_3,\sigma} c_{\vec k_2,\sigma} \sum_{\vec q_1 \in \text{PS}, \atop{\vec q_2 \in \text{HS}}}\frac{W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4}}{\omega + \frac{1}{2}\varepsilon\left(q_1\right) - \frac{1}{2}\varepsilon\left(q_2\right) + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~.
+\end{aligned}\end{equation}
+
+\begin{equation}\begin{aligned}
+	T_4 G T_5 &= \frac{1}{4}\sum  W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_1,\sigma^\prime}c_{\vec q_2,\sigma^\prime} \frac{1}{\omega - H_D}W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec k_3,\sigma}c_{\vec q_1,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime}\\
+		  &= -\frac{1}{4}\sum \hat n_{\vec q_1,\sigma} \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right) c_{\vec k_2,\sigma} c^\dagger_{\vec k_1,\sigma^\prime}c^\dagger_{\vec k_3,\sigma}c_{\vec k_4,\sigma^\prime} \frac{W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4}}{\omega + \frac{1}{2}\varepsilon\left(q_1\right) - \frac{1}{2}\varepsilon\left(q_2\right) + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}  \\
+		  &= -\frac{1}{4}\sum_{1,2,3,4,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k_1,\sigma^\prime}c_{\vec k_4,\sigma^\prime}c^\dagger_{\vec k_3,\sigma} c_{\vec k_2,\sigma} \sum_{\vec q_1 \in \text{PS}, \atop{\vec q_2 \in \text{HS}}}\frac{W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4}}{\omega + \frac{1}{2}\varepsilon\left(q_1\right) - \frac{1}{2}\varepsilon\left(q_2\right) + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~.
+\end{aligned}\end{equation}
+
+\begin{equation}\begin{aligned}
+	T_5 G T_4 &= \frac{1}{4}\sum W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec k_3,\sigma}c_{\vec q_2,\sigma}c^\dagger_{\vec q_1,\sigma^\prime}c_{\vec k_4,\sigma^\prime} \frac{1}{\omega - H_D} W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} \sigma\sigma^\prime c^\dagger_{\vec q_2,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec k_1,\sigma^\prime}c_{\vec q_1,\sigma^\prime}\\
+		  &= -\frac{1}{4}\sum \hat n_{\vec q_1,\sigma} \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right) c^\dagger_{\vec k_3,\sigma}c_{\vec k_4,\sigma^\prime} c_{\vec k_2,\sigma} c^\dagger_{\vec k_1,\sigma^\prime} \frac{W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4}}{\omega + \frac{1}{2}\varepsilon\left(q_1\right) - \frac{1}{2}\varepsilon\left(q_2\right) + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}  \\
+		  &= -\frac{1}{4}\sum_{1,2,3,4,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k_3,\sigma} c_{\vec k_2,\sigma} c^\dagger_{\vec k_1,\sigma^\prime}c_{\vec k_4,\sigma^\prime}\sum_{\vec q_1 \in \text{PS}, \atop{\vec q_2 \in \text{HS}}}\frac{W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2} W_{\vec q_1, \vec k_3, \vec q_2, \vec k_4}}{\omega + \frac{1}{2}\varepsilon\left(q_1\right) - \frac{1}{2}\varepsilon\left(q_2\right) + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~.
 \end{aligned}\end{equation}

### 2024-02-01 dWaveESIAM.tex
--no-message

@@
 \documentclass{revtex4-2}
-\usepackage{amsmath}
+\usepackage{amsmath,hyperref}
 \begin{document}
@@
 \begin{equation}\begin{aligned}
-	H_D^{(j)} = \varepsilon_j\sum_{q,\sigma}\tau_{q,\sigma} + \sum_{\vec q}J_{\vec q, \vec q}S_d^z\left(\hat n_{\vec q, \uparrow} - \hat n_{\vec q, \downarrow}\right) - \frac{1}{2}\sum_{\vec q_1}W_{\vec q_1, \vec q_1, \vec q_1, \vec q_1}\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \downarrow}\right)^2~.
+	H_D^{(j)} = \varepsilon_j\sum_{q,\sigma}\tau_{q,\sigma} + \frac{1}{2}\sum_{\vec q}J_{\vec q, \vec q}S_d^z\left(\hat n_{\vec q, \uparrow} - \hat n_{\vec q, \downarrow}\right) - \frac{1}{2}\sum_{\vec q_1}W_{\vec q_1, \vec q_1, \vec q_1, \vec q_1}\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \downarrow}\right)^2~.
 \end{aligned}\end{equation}
@@
 		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2,\vec k_3,\vec q_2,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2,\vec k_3,\vec q_2} \sigma\sigma^\prime c^\dagger_{\vec k_3,\sigma^\prime}c_{\vec q_2,\sigma^\prime}c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}}_{T_5}\\
-		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec q_3,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec q_3} \sigma\sigma^\prime \left[c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec q_3,\sigma^\prime} + \text{h.c.}\right]}_{T_6 + T_6^\dagger}~.
+		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec q_3,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec q_3} \sigma\sigma^\prime \left[c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec q_3,\sigma^\prime}c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma} + \text{h.c.}\right]}_{T_6^\dagger + T_6}~,\\
+		   & \underbrace{+\sum_{\vec k, \vec q, \sigma,\sigma^\prime}J_{\vec q^\prime, \vec q} \vec{S}_d\cdot\vec{\tau}_{\sigma,\sigma^\prime}\left[c^\dagger_{\vec q\sigma}c_{\vec q^\prime,\sigma}\right]}_{T_7}~.\\
 \end{aligned}\end{equation}
@@
 
+\subsection{Correlated scattering involve one electron on the shell \(\varepsilon_j\)}
 The first term is of the form
 \begin{equation}\begin{aligned}
-	T_2^\dagger G T_6 = \sum \sigma_1\sigma_1^\prime W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} c^\dagger_{\vec q_1, \sigma_1}c_{\vec k_2,\sigma_1}c^\dagger_{\vec k_3,\sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime} \frac{1}{\omega - H_D}\sigma_1\sigma_2^\prime W_{\vec q_1,\vec q_2,\vec q_2,\vec k_2^\prime} \hat n_{\vec q_2,\sigma_2^\prime}c^\dagger_{\vec k_2^\prime,\sigma_1}c_{\vec q_1,\sigma_1}~.
+	T_6^\dagger G T_2 = \sum \sigma_1\sigma_1^\prime W_{\vec k_3,\vec k_4,\vec k_1,\vec q_1} c^\dagger_{\vec k_3, \sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime}c^\dagger_{\vec k_1,\sigma_1}c_{\vec q_1,\sigma_1} \frac{1}{\omega - H_D}W_{\vec q_1,\vec q_2,\vec q_2,\vec k_2} \left(-\hat n_{\vec q_2,\bar\sigma_1}c^\dagger_{\vec q_1,\sigma_1}c_{\vec k_2,\sigma_1} + \hat n_{\vec q_2,\sigma_1}c^\dagger_{\vec q_1,\sigma_1}c_{\vec k_2,\sigma_1} \right.\\
+	\left.+ c^\dagger_{\vec q_1,\sigma_1}\left(1 - \hat n_{\vec q_2,\bar\sigma_1}\right) c_{\vec k_2,\sigma_1}\right)~.
 \end{aligned}\end{equation}
 The change in occupancy of the state \(\vec q_1\sigma_1\) from 1 to 0 leads to an excited state energy \(H_D = \varepsilon(q_1)\tau_{q_1\sigma_1} - \frac{1}{2}W_{\vec q_1}\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \uparrow}\right)^2 = -\frac{1}{2}\varepsilon(q_1) - \frac{1}{2}W_{\vec q_1}\), where \(W_{\vec q_1}\) is a shorthand for \(W_{\vec q_1,\vec q_1,\vec q_1,\vec q_1}\).
-The number operator \(\hat n_{\vec q_2,\sigma_2^\prime}\) projects the initial state to that in which \(\vec q_2\) is occupied.
-The operator \(c_{\vec q_1,\sigma_1}\) can be combined with its hermitian conjugate on the other side to give another number operator, leading to another projection.
-Both the number operators reduce to unity upon acting on the projected states:
+We consider the first two terms for now.
+The number operators \(\hat n_{\vec q_2,\sigma_1}, \hat n_{\vec q_2,\bar\sigma_1}\) project the initial state to that in which \(\vec q_2\) is occupied, henceforth referred to as the particle sector (PS).
+The operator \(c_{\vec q_1,\sigma_1}\) can be combined with its Hermitian conjugate on the other side to give another number operator, leading to another projection.
+Since the two terms are otherwise identical, their opposite signs lead to them cancelling each other.
+The remaining term involves the hole projection operator \(1 - \hat n_{\vec q_2,\sigma_1}\) which projects onto the set of initial states in which the momentum state \(\vec q_2\) is unoccupied, henceforth referred to as the hole sector (HS).
+Evaluating this term in the same way leads to
+\begin{equation}\begin{aligned}\label{t2t61}
+	T_2^\dagger G T_6 = -\sum_{\left\{\vec k_i\right\}, \sigma_1\sigma_1^\prime}  c^\dagger_{\vec k_3,\sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime} c^\dagger_{\vec k_1,\sigma_1} c_{\vec k_2,\sigma_1}\sum_{\vec q_1\in\text{PS},\atop{\vec q_2 \in \text{HS}}}\frac{W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} W_{\vec q_1,\vec q_2,\vec q_2,\vec k_1}}{\omega + \frac{1}{2}\varepsilon(q_1) + \frac{1}{2}W_{\vec q_1}}  ~.
+\end{aligned}\end{equation}
+The particle-hole transformed term \(T_6^\dagger G T_2\) can be evaluated in the same way:
+\begin{equation}\begin{aligned}\label{t6dagt2}
+	T_6^\dagger G T_2 = \sum W_{\vec q_1,\vec q_2,\vec q_2,\vec k_2}\left(-c^\dagger_{\vec q_1,\sigma_1}c_{\vec k_2,\sigma_1}\hat n_{\vec q_2,\bar\sigma_1} + c^\dagger_{\vec q_1,\sigma_1}c_{\vec k_2,\sigma_1}\hat n_{\vec q_2,\sigma_1} + c^\dagger_{\vec q_1,\sigma_1}\left(1 - \hat n_{\vec q_2,\bar\sigma_1}\right) c_{\vec k_2,\sigma_1}\right) \frac{1}{\omega - H_D}\times \\
+	\sigma_1\sigma_1^\prime W_{\vec k_3,\vec k_4,\vec k_1,\vec q_1} c^\dagger_{\vec k_3, \sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime}c^\dagger_{\vec k_1,\sigma_1}c_{\vec q_1,\sigma_1} ~.
+\end{aligned}\end{equation}
+For such a scattering process, the excited energy is given by \(H_D = \varepsilon(q_1)\tau_{q_1\sigma_1} - \frac{1}{2}W_{\vec q_1}\left(\hat n_{\vec q_1, \uparrow} - \hat n_{\vec q_1, \uparrow}\right)^2 = \frac{1}{2}\varepsilon(q_1) - \frac{1}{2}W_{\vec q_1}\).
+The change of the sign in front of \(\varepsilon(\vec q_1)\) arises from the fact that in this process, the state \(\vec q_1\) is occupied in the intermediate excited state, owing to the \(c^\dagger_{\vec q_1,\sigma_1}\) operator to the right of the Greens function.
+Cancelling the first two terms in eq.~\ref{t6dagt2} (just as in the previous process) and evaluating the last term gives
+\begin{equation}\begin{aligned}\label{t2t62}
+	T_6^\dagger G T_2 = \sum_{\left\{\vec k_i\right\}, \sigma_1\sigma_1^\prime}  c^\dagger_{\vec k_3, \sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime}c^\dagger_{\vec k_1,\sigma_1} c_{\vec k_2,\sigma_1}\sum_{\vec q_1, \vec q_2\in\text{HS}}\frac{W_{\vec k_3,\vec k_4,\vec k_1,\vec q_1} W_{\vec q_1,\vec q_2,\vec q_2,\vec k_2}}{\omega - \frac{1}{2}\varepsilon(q_1) + \frac{1}{2}W_{\vec q_1}}~.
+\end{aligned}\end{equation}
+
+We now assume that the Brillouin zone of the lattice in which our conduction bath is embedded is symmetrical about the Fermi surface.
+This essentially amounts to working at particle-hole symmetry, by setting the chemical potential of the bath to zero.
+This symmetry leads to two consequences:
+\begin{itemize}
+	\item If this is the case, the states in the particle sector will reside on the isoenergetic shell of energy \(-|\varepsilon_j|\), while those in the hole sector will reside at energy \(|\varepsilon_j|\), at equal distances from the Fermi surface (which lies at zero energy).
+This ensures that in the denominators of the RG equation, we have the simplification
 \begin{equation}\begin{aligned}
-	T_2^\dagger G T_6 = \sum \sigma_1^2\sigma_1^\prime W_{\vec q_1,\vec k_2,\vec k_3,\vec k_4} W_{\vec q_1,\vec q_2,\vec q_2,\vec k_2^\prime} c_{\vec k_2,\sigma_1}c^\dagger_{\vec k_3,\sigma_1^\prime}c_{\vec k_4,\sigma_1^\prime} c^\dagger_{\vec k_2^\prime,\sigma_1}\frac{1}{\omega + \frac{1}{2}\varepsilon(q_1) + \frac{1}{2}W_{\vec q_1}}\sum_{\sigma_2^\prime}\sigma_2^\prime  ~.
+	\varepsilon(\vec q_1)\bigg|_\text{PS} = -\varepsilon(\vec q_2)\bigg|_\text{HS} = -|\varepsilon_j|~.
 \end{aligned}\end{equation}
-Since there is a sum over the spin factor \(\sigma_2^\prime = \pm 1\), this term vanishes identically. The particle-hole transformed term \(T_6^\dagger G T_2\) vanishes for the same reason.
+\item We also consider the symmetry of of the coupling \(W_{\vec q_1,\vec k_1, \vec q_2, \vec k_2}\) to reflections about the nodal point in the same quadrant of the Brillouin zone.
+For any momentum \(\vec q_1\) in the hole sector, we can find a corresponding point \(\vec \tilde q_1\) in the particle sector by reflecting about the nodal point.
+This corresponds to the transformation \(q_x \to \pi - q_x, q_y \to \pi - q_y\), leading to a sign change of the factor \(\left[\cos\left( aq_1^x \right) - \cos\left( aq_1^y \right) \right]\).
+This leaves the product \(W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}\) unchanged.
+The diagonal coupling \(W_{\vec q_1}\) also remains unchanged by themselves, since it involves a product of four copies of the factor.
+\end{itemize}
+These two features ensure that the inner summations over \(\vec q_1,\vec q_2\) are identical in eqs.~\ref{t2t61} and \ref{t2t62}, leading to the vanishing of the total renormalisation \(T_6^\dagger G T_2 + T_2^\dagger G T_6\).
 
+\subsection{Scattering across the Fermi surface involving two electrons on the shell \(\varepsilon_j\)}
 We now consider the second term \(T_3^\dagger G T_3\):
 \begin{equation}\begin{aligned}
-	T_3^\dagger G T_3 &= \frac{1}{4}\sum W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} \frac{1}{\omega - H_D} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime} \sigma\sigma^\prime c^\dagger_{\vec k^\prime_4,\sigma^\prime} c_{\vec q_2,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} c_{\vec q_1,\sigma}\\
-			  &= \frac{1}{4}\sum  \hat n_{\vec q_1,\sigma} \hat n_{\vec q_2,\sigma^\prime} c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} \frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}\\
-			  &= \frac{1}{4}\sum_{4^\prime,4,2^\prime,2,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k^\prime_4,\sigma^\prime} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma}c_{\vec k_2,\sigma}  \sum_{\vec q_1, \vec q_2 \in \text{PS}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~,
+	T_3^\dagger G T_3 &= \frac{1}{4}\sum W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} \frac{1}{\omega - H_D} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime} \sigma\sigma^\prime c^\dagger_{\vec k_1,\sigma^\prime} c_{\vec q_2,\sigma^\prime} c^\dagger_{\vec k_3,\sigma} c_{\vec q_1,\sigma}\\
+			  &= \frac{1}{4}\sum  \hat n_{\vec q_1,\sigma} \hat n_{\vec q_2,\sigma^\prime} c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k_1,\sigma^\prime} c^\dagger_{\vec k_3,\sigma} \frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}\\
+			  &= \frac{1}{4}\sum_{1,2,3,4,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k_1,\sigma^\prime} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k_3,\sigma}c_{\vec k_2,\sigma}  \sum_{\vec q_1, \vec q_2 \in \text{PS}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	T_3 G T_3^\dagger &= \frac{1}{4}\sum  W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime} \sigma\sigma^\prime c^\dagger_{\vec k^\prime_4,\sigma^\prime} c_{\vec q_2,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma} c_{\vec q_1,\sigma}\frac{1}{\omega - H_D}W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} \\
-			  &= \frac{1}{4}\sum \left(1 - \hat n_{\vec q_1,\sigma}\right) \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right) c^\dagger_{\vec k^\prime_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma}  c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega - \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}\\
-			  &= \frac{1}{4}\sum_{4^\prime,4,2^\prime,2,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k^\prime_4,\sigma^\prime}  c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k^\prime_2,\sigma}  c_{\vec k_2,\sigma} \sum_{\vec q_1, \vec q_2 \in \text{HS}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime}}{\omega - \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~,
+	T_3 G T_3^\dagger &= \frac{1}{4}\sum  W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1} \sigma\sigma^\prime c^\dagger_{\vec k_1,\sigma^\prime} c_{\vec q_2,\sigma^\prime} c^\dagger_{\vec k_3,\sigma} c_{\vec q_1,\sigma}\frac{1}{\omega - H_D}W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} \\
+			  &= \frac{1}{4}\sum \left(1 - \hat n_{\vec q_1,\sigma}\right) \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right) c^\dagger_{\vec k_1,\sigma^\prime} c^\dagger_{\vec k_3,\sigma}  c_{\vec k_2,\sigma} c_{\vec k_4,\sigma^\prime}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}}{\omega - \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}\\
+			  &= \frac{1}{4}\sum_{1,2,3,4,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k_1,\sigma^\prime}  c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k_3,\sigma}  c_{\vec k_2,\sigma} \sum_{\vec q_1, \vec q_2 \in \text{HS}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}}{\omega - \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~,
 \end{aligned}\end{equation}
-where the hole projectors \(\left(1 - \hat n_{\vec q_1,\sigma}\right) \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right)\) force the momenta \(\vec q_1,\vec q_2\) to extend over all states in the hole sector (states that are unoccupied in the ground state).
+where the hole projectors \(\left(1 - \hat n_{\vec q_1,\sigma}\right) \left(1 - \hat n_{\vec q_2,\sigma^\prime}\right)\) force the momenta \(\vec q_1,\vec q_2\) to extend over the states only in the hole sector (states that are unoccupied in the ground state).
 The change in the sign of \(\left[\varepsilon(q_1) + \varepsilon(q_2)\right]\) in the denominator compared to the denominator in \(T_3^\dagger G T_3\) is for the same reason.
 
+We can obtain two additional terms by switching the sequence of operators on the right hand side of the propagator:
+\begin{equation}\begin{aligned}
+	T_3^\dagger G \overline T_3 &= \frac{1}{4}\sum W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma}c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} \frac{1}{\omega - H_D} W_{\vec q_1,\vec k_2^\prime, \vec q_2, \vec k_4^\prime} \sigma\sigma^\prime c^\dagger_{\vec k_3,\sigma} c_{\vec q_1,\sigma} c^\dagger_{\vec k_1,\sigma^\prime} c_{\vec q_2,\sigma^\prime}\\
+			  &= \frac{1}{4}\sum_{1,2,3,4,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k_1,\sigma^\prime} c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k_3,\sigma}c_{\vec k_2,\sigma}  \sum_{\vec q_1, \vec q_2 \in \text{PS}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~,
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+	T_3 G \overline T_3^\dagger &= \frac{1}{4}\sum  W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1} \sigma\sigma^\prime c^\dagger_{\vec k_1,\sigma^\prime} c_{\vec q_2,\sigma^\prime} c^\dagger_{\vec k_3,\sigma} c_{\vec q_1,\sigma}\frac{1}{\omega - H_D}W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} \sigma\sigma^\prime c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma} \\
+			  &= \frac{1}{4}\sum_{1,2,3,4,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k_1,\sigma^\prime}  c_{\vec k_4,\sigma^\prime} c^\dagger_{\vec k_3,\sigma}  c_{\vec k_2,\sigma} \sum_{\vec q_1, \vec q_2 \in \text{HS}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}}{\omega - \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)}~,
+\end{aligned}\end{equation}
+
+\subsection{Forward and tangential scattering involving two electrons on the shell \(\varepsilon_j\)}
 The remaining sets of terms that we need to consider are:
@@
 
+\subsection{Net renormalisation for the bath correlation term}
+Adding contributions from all these terms, the total renormalisation in the Hamiltonian in the context of \(W\) comes out to be
+\begin{equation}\begin{aligned}
+	\Delta H = \sum_{1,2,3,4,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k_3,\sigma} c_{\vec k_2,\sigma} c^\dagger_{\vec k_1,\sigma^\prime}c_{\vec k_4,\sigma^\prime}&\left[\frac{1}{2}\sum_{\vec q_1, \vec q_2 \in \text{PS}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)} \right.
+\\
+		  &\left.
++ \frac{1}{2}\sum_{\vec q_1, \vec q_2 \in \text{HS}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}}{\omega - \frac{1}{2}\left[\varepsilon(q_1) + \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)} \right.
+\\
+		  &\left.
+- \sum_{\vec q_1 \in \text{PS}, \atop{\vec q_2 \in \text{HS}}}\frac{W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}}{\omega + \frac{1}{2}\left[\varepsilon(q_1) - \varepsilon(q_2)\right] + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)} \right]
+\end{aligned}\end{equation}
+
+Following the arguments laid down below eq.~\ref{t2t62}, we know that the following relation holds:
+\begin{equation}\begin{aligned}
+	\varepsilon(\vec q_1)\bigg|_\text{PS} = -\varepsilon(\vec q_2)\bigg|_\text{HS} = -|\varepsilon_j|~.
+\end{aligned}\end{equation}
+Following the same arguments, we also know that the product coupling \(W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}\) and the diagonal couplings \(W_{\vec q_1}\) and \(W_{\vec q_2}\) remain unchanged if \(\vec q_2\) is transformed between the particle and hole sectors.
+Using these properties, we get
+\begin{equation}\begin{aligned}
+	\Delta H &= \sum_{1,2,3,4,\atop{\sigma,\sigma^\prime}} c^\dagger_{\vec k_3,\sigma} c_{\vec k_2,\sigma} c^\dagger_{\vec k_1,\sigma^\prime}c_{\vec k_4,\sigma^\prime}\sum_{\vec q_1, \vec q_2 \in \text{HS}}W_{\vec q_1,\vec k_2, \vec q_2, \vec k_4} W_{\vec q_1,\vec k_3, \vec q_2, \vec k_1}\\
+		 &\times\left[\frac{1/2}{\omega - |\varepsilon_j| + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)} + \frac{1/2}{\omega - |\varepsilon_j| + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)} - \frac{1}{\omega - |\varepsilon_j| + \frac{1}{2}\left(W_{\vec q_1} + W_{\vec q_2}\right)} \right]\\
+		 &= 0~.
+\end{aligned}\end{equation}
+
+\section{Renormalisation of the Kondo scattering term \(J\)}
+We take a closer look at the Kondo scattering terms \(T_1\) and \(T_7\) in \(H_X\):
+\begin{equation}\begin{aligned}
+	T_1^\dagger + T_7 =& \frac{1}{2}\underbrace{\sum_{\vec k,\vec q,\sigma}J_{\vec k,\vec q}S_d^z \sigma c^\dagger_{\vec q,\sigma} c_{\vec k,\sigma}}_{T_{1,z}^\dagger} + \frac{1}{2}\underbrace{\sum_{\vec k,\vec q}J_{\vec k,\vec q} S_d^+ c^\dagger_{\vec q,\downarrow} c_{\vec k,\uparrow}}_{T_{1,+-}^\dagger} + \frac{1}{2}\underbrace{\sum_{\vec k,\vec q}S_d^- c^\dagger_{\vec q,\uparrow} c_{\vec k,\downarrow}}_{T_{1,-+}^\dagger} \\
+			   &\frac{1}{2}\underbrace{\sum_{\vec q^\prime,\vec q,\sigma}J_{\vec q^\prime,\vec q}S_d^z \sigma c^\dagger_{\vec q,\sigma} c_{\vec q^\prime,\sigma}}_{T_{7,z}^\dagger} + \frac{1}{2}\underbrace{\sum_{\vec q^\prime,\vec q}J_{\vec q^\prime,\vec q} S_d^+ c^\dagger_{\vec q,\downarrow} c_{\vec q^\prime,\uparrow}}_{T_{7,+-}^\dagger} + \frac{1}{2}\underbrace{\sum_{\vec q^\prime,\vec q}S_d^- c^\dagger_{\vec q,\uparrow} c_{\vec q^\prime,\downarrow}}_{T_{7,-+}^\dagger}
+\end{aligned}\end{equation}
+We note that scattering processes involving the pairs \(\left(T_{1,\pm \mp}^\dagger, T_{1,\pm \mp}\right)\), \(\left(T_{1,z}, T_6\right)\) and \(\left(T_{7,z}, T_6\right) \) will renormalise the \(S_d^z\) term, while those involving the pairs \(\left(T_{1,z}, T_{1,\pm \mp}\right)\) and \(\left(T_{1,\pm \mp}, T_6\right)\) will renormalise the \(S_d^\pm\) terms.
+
+We first consider the renormalisation to the \(S_d^z\) term, arising purely from the Kondo terms:
+\begin{equation}\begin{aligned}
+	\sum_{\sigma=\pm}T_{1,\sigma\bar\sigma}^\dagger G T_{1,\sigma\bar\sigma} = \sum_{\sigma=\pm}\frac{1}{4}\sum_{\vec k_2,\vec q}J_{\vec k_2,\vec q} S_d^\sigma c^\dagger_{\vec q,\bar\sigma} c_{\vec k_2,\sigma} \frac{1}{\omega - H_D}\sum_{\vec k_1,\vec q}J_{\vec k_1,\vec q} S_d^{\bar\sigma} c^\dagger_{\vec k_1,\sigma} c_{\vec q,\bar\sigma}~,
+\end{aligned}\end{equation}
+where \(c_{k,+(-)} \equiv c_{k,\uparrow(\downarrow)}\).
+The excitation energy for such processes is given by \(H_D = |\varepsilon_j| - J_{\vec q}/4 - W_{\vec q}/2\), due to the fact that the impurity spin flip and the spin flip of the conduction bath state \(\vec q\) occurs in an anti-parallel fashion.
+Substituting this, performing the usual contraction and projection of the state \(\vec q\) and carrying out the spin manipulation \(S_d^\sigma S_d^{\bar\sigma} = \frac{1}{2} + \sigma S_d^z\) results in the expression
+\begin{equation}\begin{aligned}
+	\sum_{\sigma=\pm}T_{1,\sigma\bar\sigma}^\dagger G T_{1,\sigma\bar\sigma} &= \sum_{\sigma=\pm}\frac{1}{4}\sum_{\vec k_2,\vec k_1} \left(\frac{1}{2} + \sigma S_d^z\right) c_{\vec k_2,\sigma} c^\dagger_{\vec k_1,\sigma}\sum_{\vec q}  \hat n_{\vec q,\bar\sigma} \frac{J_{\vec k_2,\vec q} J_{\vec k_1,\vec q}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2}\\
+										 &= -\frac{1}{4}\sum_{\vec k_2,\vec k_1} S_d^z \left(c^\dagger_{\vec k_1,\uparrow}c_{\vec k_2,\uparrow} - c^\dagger_{\vec k_1,\downarrow}c_{\vec k_2,\downarrow}\right)\sum_{\vec q \in \text{PS}} \frac{J_{\vec k_2,\vec q} J_{\vec k_1,\vec q}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2} + \bigg[\text{pot.
+scatt.
+terms}\bigg]~.
+\end{aligned}\end{equation}
+The particle-hole exchanged partner is
+\begin{equation}\begin{aligned}
+	\sum_{\sigma=\pm}T_{1,\sigma\bar\sigma} G T^\dagger_{1,\sigma\bar\sigma} &= \sum_{\sigma=\pm}\frac{1}{4} \sum_{\vec k_1,\vec q}J_{\vec k_1,\vec q} S_d^{\bar\sigma} c^\dagger_{\vec k_1,\sigma} c_{\vec q,\bar\sigma} \frac{1}{\omega - H_D}\sum_{\vec k_2,\vec q}J_{\vec k_2,\vec q} S_d^\sigma c^\dagger_{\vec q,\bar\sigma} c_{\vec k_2,\sigma}\\
+										 &= \sum_{\sigma=\pm}\frac{1}{4}\sum_{\vec k_2,\vec k_1} \left(\frac{1}{2} + \bar\sigma S_d^z\right) c^\dagger_{\vec k_1,\sigma} c_{\vec k_2,\sigma} \sum_{\vec q} \left(1 - \hat n_{\vec q,\bar\sigma}\right) \frac{J_{\vec k_2,\vec q} J_{\vec k_1,\vec q}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2}\\
+										 &= -\frac{1}{4}\sum_{\vec k_2,\vec k_1, \sigma} S_d^z \sigma c^\dagger_{\vec k_1,\sigma}c_{\vec k,\sigma} \sum_{\vec q \in \text{HS}} \frac{J_{\vec k_2,\vec q} J_{\vec k_1,\vec q}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2} + \bigg[\text{pot.
+scatt.
+terms}\bigg]~.
+\end{aligned}\end{equation}
+
+Next, we consider scattering processes involving \(T_6\):
+\begin{equation}\begin{aligned}
+	T_{1,z}^\dagger G T_6 = \frac{1}{4}\sum_{\vec k_1,\vec k_2,\vec q,\sigma}\sigma J_{\vec k_2,\vec q}S_d^z c^\dagger_{\vec q,\sigma} c_{\vec k_2,\sigma} \frac{1}{\omega - H_D}W_{\vec q,\vec q,\vec q,\vec k_1} \left[-c^\dagger_{\vec k_1,\sigma}c_{\vec q,\sigma}\hat n_{\vec q,\bar\sigma} + c^\dagger_{\vec k_1,\sigma}c_{\vec q,\sigma}\hat n_{\vec q,\sigma} + c^\dagger_{\vec k_1,\sigma}\left(1 - \hat n_{-\vec q,\sigma}\right) c_{\vec q,\sigma}\right]~.
+\end{aligned}\end{equation}
+For the same reasons as those outlined above eq.~\ref{t2t61}, the first two terms on the right-hand side of the Greens function cancel each other. The remaining term evaluates to
+\begin{equation}\begin{aligned}
+	T_{1,z}^\dagger G T_6 = \frac{1}{4}\sum_{\vec k_1,\vec k_2,\sigma}\sigma  S_d^z c_{\vec k_2,\sigma}c^\dagger_{\vec k_1,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_2,\vec q} W_{\vec q,\vec q,\vec q,\vec k_1}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2} = -\frac{1}{4}\sum_{\vec k_1,\vec k_2,\sigma} S_d^z \sigma c^\dagger_{\vec k_1,\sigma} c_{\vec k_2,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_2,\vec q} W_{\vec q,\vec q,\vec q,\vec k_1}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2}~.
+\end{aligned}\end{equation}
+Another scattering process is obtained by switching the operators \(T_1\) and \(T_6\):
+\begin{equation}\begin{aligned}
+	T_{6}^\dagger G T_{1,z} &= \frac{1}{4} \sum_{\vec k_1,\vec k_2,\vec q,\sigma} \left[-c^\dagger_{\vec q,\sigma_1}c_{\vec k_2,\sigma_1}\hat n_{-\vec q,\bar\sigma_1} + c^\dagger_{\vec q,\sigma_1}c_{\vec k_2,\sigma_1}\hat n_{-\vec q,\sigma_1} + c^\dagger_{\vec q,\sigma_1}\left(1 - \hat n_{-\vec q,\sigma_1}\right) c_{\vec k_2,\sigma_1}\right] \frac{W_{\vec q,\vec q,\vec q,\vec k_2} J_{\vec k_1,\vec q}}{\omega - H_D} \sigma S_d^z c^\dagger_{\vec k_1,\sigma} c_{\vec q,\sigma}\\
+				&=-\frac{1}{4}\sum_{\vec k_1,\vec k_2,\sigma} S_d^z \sigma c^\dagger_{\vec k_1,\sigma} c_{\vec k_2,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_1,\vec q} W_{\vec q,\vec q,\vec q,\vec k_2}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2}
+\end{aligned}\end{equation}
+One can also construct
+
 \end{document}

### 2024-02-01 dWaveESIAM.tex
--no-message

@@
 		   &\underbrace{- \frac{1}{2}\sum_{\vec q_1,\vec k_2, \vec q_2, \vec q_3,\sigma,\sigma^\prime}W_{\vec q_1,\vec k_2, \vec q_2, \vec q_3} \sigma\sigma^\prime \left[c^\dagger_{\vec q_2,\sigma^\prime}c_{\vec q_3,\sigma^\prime}c^\dagger_{\vec q_1,\sigma}c_{\vec k_2,\sigma} + \text{h.c.}\right]}_{T_6^\dagger + T_6}~,\\
-		   & \underbrace{+\sum_{\vec k, \vec q, \sigma,\sigma^\prime}J_{\vec q^\prime, \vec q} \vec{S}_d\cdot\vec{\tau}_{\sigma,\sigma^\prime}\left[c^\dagger_{\vec q\sigma}c_{\vec q^\prime,\sigma}\right]}_{T_7}~.\\
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	T_{1,z}^\dagger G T_6 = \frac{1}{4}\sum_{\vec k_1,\vec k_2,\vec q,\sigma}\sigma J_{\vec k_2,\vec q}S_d^z c^\dagger_{\vec q,\sigma} c_{\vec k_2,\sigma} \frac{1}{\omega - H_D}W_{\vec q,\vec q,\vec q,\vec k_1} \left[-c^\dagger_{\vec k_1,\sigma}c_{\vec q,\sigma}\hat n_{\vec q,\bar\sigma} + c^\dagger_{\vec k_1,\sigma}c_{\vec q,\sigma}\hat n_{\vec q,\sigma} + c^\dagger_{\vec k_1,\sigma}\left(1 - \hat n_{-\vec q,\sigma}\right) c_{\vec q,\sigma}\right]~.
+	T_{1,z}^\dagger G T_6 = \frac{1}{4}\sum_{\vec k_1,\vec q,\sigma}\sigma J_{\vec k_2,\vec q}S_d^z c^\dagger_{\vec q,\sigma} c_{\vec k_2,\sigma} \frac{1}{\omega - H_D} W_{\vec q,\vec q,\vec q,\vec k_1} \left(-c^\dagger_{k_1\sigma}c_{q\sigma}\hat n_{\vec q\sigma} - \hat n_{\vec q\sigma} c^\dagger_{k_1\sigma}c_{q\sigma} + 2 c^\dagger_{k_1\sigma}c_{q\sigma}\hat n_{\vec q\bar\sigma} + 2\hat n_{\vec q\bar\sigma} c^\dagger_{k_1\sigma}c_{q\sigma}\right)~.
 \end{aligned}\end{equation}
-For the same reasons as those outlined above eq.~\ref{t2t61}, the first two terms on the right-hand side of the Greens function cancel each other. The remaining term evaluates to
+For the same reasons as those outlined above eq.~\ref{t2t61}, the first three terms on the right-hand side of the Greens function cancel each other. The remaining term evaluates to
 \begin{equation}\begin{aligned}
-	T_{1,z}^\dagger G T_6 = \frac{1}{4}\sum_{\vec k_1,\vec k_2,\sigma}\sigma  S_d^z c_{\vec k_2,\sigma}c^\dagger_{\vec k_1,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_2,\vec q} W_{\vec q,\vec q,\vec q,\vec k_1}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2} = -\frac{1}{4}\sum_{\vec k_1,\vec k_2,\sigma} S_d^z \sigma c^\dagger_{\vec k_1,\sigma} c_{\vec k_2,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_2,\vec q} W_{\vec q,\vec q,\vec q,\vec k_1}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2}~.
+	T_{1,z}^\dagger G T_6 = \frac{1}{2}\sum_{\vec k_1,\vec k_2,\sigma}\sigma S_d^z c_{\vec k_2,\sigma}c^\dagger_{\vec k_1,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_2,\vec q} W_{\vec q,\vec q,\vec q,\vec k_1}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2} = -\frac{1}{2}\sum_{\vec k_1,\vec k_2,\sigma} S_d^z \sigma c^\dagger_{\vec k_1,\sigma} c_{\vec k_2,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_2,\vec q} W_{\vec q,\vec q,\vec q,\vec k_1}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	T_{6}^\dagger G T_{1,z} &= \frac{1}{4} \sum_{\vec k_1,\vec k_2,\vec q,\sigma} \left[-c^\dagger_{\vec q,\sigma_1}c_{\vec k_2,\sigma_1}\hat n_{-\vec q,\bar\sigma_1} + c^\dagger_{\vec q,\sigma_1}c_{\vec k_2,\sigma_1}\hat n_{-\vec q,\sigma_1} + c^\dagger_{\vec q,\sigma_1}\left(1 - \hat n_{-\vec q,\sigma_1}\right) c_{\vec k_2,\sigma_1}\right] \frac{W_{\vec q,\vec q,\vec q,\vec k_2} J_{\vec k_1,\vec q}}{\omega - H_D} \sigma S_d^z c^\dagger_{\vec k_1,\sigma} c_{\vec q,\sigma}\\
-				&=-\frac{1}{4}\sum_{\vec k_1,\vec k_2,\sigma} S_d^z \sigma c^\dagger_{\vec k_1,\sigma} c_{\vec k_2,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_1,\vec q} W_{\vec q,\vec q,\vec q,\vec k_2}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2}
+	T_{6}^\dagger G T_{1,z} &= \frac{1}{4} \sum_{\vec k_1,\vec k_2,\vec q,\sigma} \left(2\hat n_{\vec q\bar\sigma} c^\dagger_{q\sigma}c_{k_2\sigma}\right) \frac{W_{\vec q,\vec q,\vec q,\vec k_2} J_{\vec k_1,\vec q}}{\omega - H_D} \sigma S_d^z c^\dagger_{\vec k_1,\sigma} c_{\vec q,\sigma} = -\frac{1}{2}\sum_{\vec k_1,\vec k_2,\sigma} S_d^z \sigma c^\dagger_{\vec k_1,\sigma} c_{\vec k_2,\sigma} \sum_{\vec q\in\text{PS}}\frac{J_{\vec k_2,\vec q} W_{\vec q,\vec q,\vec q,\vec k_1}}{\omega - |\varepsilon_j| + J_{\vec q}/4 + W_{\vec q}/2}
 \end{aligned}\end{equation}
-One can also construct
+One can also construct the particle-hole exchanged processes:
+\begin{equation}\begin{aligned}
+	T_6 G T_{1,z}^\dagger = \frac{1}{4}\sum_{\vec k_1, \vec k_2, \vec q, \sigma}\left(-c^\dagger_{k_1\sigma}c_{q\sigma}\hat n_{\vec q\sigma} - \hat n_{\vec q\sigma} c^\dagger_{k_1\sigma}c_{q\sigma} + 2 c^\dagger_{k_1\sigma}c_{q\sigma}\hat n_{\vec q\bar\sigma} + 2\hat n_{\vec q\bar\sigma} c^\dagger_{k_1\sigma}c_{q\sigma}\right) \frac{J_{\vec k_2,\vec q} W_{\vec q,\vec q,\vec q,\vec k_1}}{\omega - H_D} \sigma S_d^z c^\dagger_{\vec q,\sigma} c_{\vec k_2,\sigma} = ~.
+\end{aligned}\end{equation}
 

### 2024-02-08 dwaveNumerics/dWaveRgFlow (copy).jl
have a working version of the dWave rg flow

@@ -1,0 +1,122 @@
+using LinearAlgebra
+
+
+function mapTo2D(points, kx_arr, ky_arr)
+    kx = (points .- 1) .% num_kspace .+ 1
+    ky = div.((points .- 1), num_kspace) .+ 1
+    return kx_arr[kx], ky_arr[ky]
+end
+
+
+function isogeometricContour(kx_start, num_kspace)
+    if kx_start > div(num_kspace, 2)
+       kx_start =  num_kspace - kx_start
+    end
+    contourPoints = []
+    kx_points_left = 1:kx_start
+    kx_points_right = num_kspace + 1 .- kx_points_left
+    
+    ky_points_lowerleft = kx_start + 1 .- kx_points_left
+    ky_points_upperleft = num_kspace - kx_start .+ kx_points_left
+    ky_points_lowerright = kx_start - num_kspace .+ kx_points_right
+    ky_points_upperright = 2 * num_kspace - kx_start + 1 .- kx_points_right
+    
+    push!(contourPoints, (kx_points_left .+ num_kspace .* (ky_points_lowerleft .- 1))...)
+    push!(contourPoints, (kx_points_left .+ num_kspace .* (ky_points_upperleft .- 1))...)
+    push!(contourPoints, (kx_points_right .+ num_kspace .* (ky_points_lowerright .- 1))...)
+    push!(contourPoints, (kx_points_right .+ num_kspace .* (ky_points_upperright .- 1))...)
+
+    return contourPoints
+end
+
+
+function dispersionFlattened(t, kx_arr, ky_arr)
+    kx_arr_flattened = repeat(kx_arr, inner=length(ky_arr))
+    ky_arr_flattened = repeat(ky_arr, outer=length(kx_arr))
+    return-2*t.*(cos.(kx_arr_flattened) + cos.(ky_arr_flattened))
+end
+
+
+function getDOS(num_kspace, dispersionArray)
+    delta_k = 2 * pi / num_kspace
+    kspaceDos = 1 / delta_k
+    densityOfStates = zeros(num_kspace * num_kspace)
+    Threads.@threads for j in 0:num_kspace-1
+        for i in 1:num_kspace
+            E_xy = dispersionArray[j * num_kspace + i]
+            E_xpy = dispersionArray[j * num_kspace + i % num_kspace + 1]
+            E_xyp = dispersionArray[(j * num_kspace + num_kspace) % num_kspace^2 + i]
[…]

### 2024-02-08 dwaveNumerics/dWaveRgFlow.jl

@@ -1,0 +1,126 @@
+using LinearAlgebra
+
+
+function isogeometricContour(kx_start, num_kspace)
+    if kx_start > div(num_kspace, 2)
+       kx_start =  num_kspace - kx_start
+    end
+    contourPoints = []
+    kx_points_left = 1:kx_start
+    kx_points_right = num_kspace + 1 .- kx_points_left
+    
+    ky_points_lowerleft = kx_start + 1 .- kx_points_left
+    ky_points_upperleft = num_kspace - kx_start .+ kx_points_left
+    ky_points_lowerright = kx_start - num_kspace .+ kx_points_right
+    ky_points_upperright = 2 * num_kspace - kx_start + 1 .- kx_points_right
+    
+    push!(contourPoints, (kx_points_left .+ num_kspace .* (ky_points_lowerleft .- 1))...)
+    push!(contourPoints, (kx_points_left .+ num_kspace .* (ky_points_upperleft .- 1))...)
+    push!(contourPoints, (kx_points_right .+ num_kspace .* (ky_points_lowerright .- 1))...)
+    push!(contourPoints, (kx_points_right .+ num_kspace .* (ky_points_upperright .- 1))...)
+
+    return contourPoints
+end
+
+
+function dispersionFlattened(t, kx_arr, ky_arr)
+    kx_arr_flattened = repeat(kx_arr, inner=length(ky_arr))
+    ky_arr_flattened = repeat(ky_arr, outer=length(kx_arr))
+    return -2*t.*(cos.(kx_arr_flattened) + cos.(ky_arr_flattened))
+end
+
+
+function getDOS(num_kspace, dispersionArray)
+    delta_k = 2 * pi / num_kspace
+    kspaceDos = 1 / delta_k
+    densityOfStates = zeros(num_kspace * num_kspace)
+    Threads.@threads for j in 0:num_kspace-1
+        for i in 1:num_kspace
+            E_xy = dispersionArray[j * num_kspace + i]
+            E_xpy = dispersionArray[j * num_kspace + i % num_kspace + 1]
+            E_xyp = dispersionArray[(j * num_kspace + num_kspace) % num_kspace^2 + i]
+            dE_xydk = sqrt((E_xpy - E_xy)^2 / delta_k^2
+                           + (E_xyp - E_xy)^2 / delta_k^2
+                           )
[…]

### 2024-02-08 dwaveNumerics/dWaveRgFlow.jl
normalised DOS

@@ -46,7 +46,8 @@ function getDOS(num_kspace, dispersionArray)
         end
     end
     replace!(densityOfStates, Inf=>maximum(densityOfStates[densityOfStates .≠ Inf]))
-    return densityOfStates
+	normalisation = sum([dos * abs(dispersionArray[i % num_kspace + 1] - dispersionArray[i]) for (i, dos) in enumerate(densityOfStates)]) / num_kspace^2
+    return densityOfStates / normalisation
 end
 
 
@@ -97,7 +98,7 @@ function main(num_kspace_half, t, J_init, W_val)
 				end
                 for qpoint in cutoffPoints
 				    denominator = omega - abs(energyCutoff) / 2 + kondoJArray[qpoint, qpoint, stepIndex] / 4 + bathInt(qpoint, qpoint, qpoint) / 2
-                    kondoJArray[innerIndex1,innerIndex2,stepIndex+1] += -4 * deltaD * densityOfStates[qpoint] * (kondoJArray[innerIndex1, qpoint, stepIndex] * kondoJArray[innerIndex2, qpoint, stepIndex] + 4 * kondoJArray[qpoint, qpoint, stepIndex] * bathInt(innerIndex1,innerIndex2,qpoint)) / denominator
+					kondoJArray[innerIndex1,innerIndex2,stepIndex+1] += -4 * deltaD * densityOfStates[qpoint] * (kondoJArray[innerIndex1, qpoint, stepIndex] * kondoJArray[innerIndex2, qpoint, stepIndex] + 4 * kondoJArray[qpoint, qpoint, stepIndex] * bathInt(innerIndex1,innerIndex2,qpoint)) / denominator
                 end
                 if kondoJArray[innerIndex1,innerIndex2,stepIndex+1] * kondoJArray[innerIndex1,innerIndex2,stepIndex] < 0
                     kondoJArray[innerIndex1,innerIndex2,stepIndex+1] = kondoJArray[innerIndex1,innerIndex2,stepIndex]

### 2024-02-09 dwaveNumerics/dWaveRgFlow.jl
corrected node cooordinates

@@ -67,6 +67,7 @@ end
 
 
 function main(num_kspace_half, t, J_init, W_val)
+    @assert num_kspace_half % 2 == 0
     num_kspace = 2 * num_kspace_half + 1
     kx_arr = range(-pi, stop=pi, length=num_kspace)
     ky_arr = copy(kx_arr)
@@ -97,16 +98,18 @@ function main(num_kspace_half, t, J_init, W_val)
 		Threads.@threads for innerIndex1 in innerIndicesArr
 		    for innerIndex2 in innerIndicesArr
 				denominators = [omega - abs(energyCutoff) / 2 + kondoJArray[qpoint, qpoint, stepIndex] / 4 + bathInt(qpoint, qpoint, qpoint) / 2 for qpoint in cutoffPoints]
-				if ! all(<(0), denominators)
-                    flags[innerIndex1,innerIndex2] = 0
-			    end
+				# if ! all(<(0), denominators)
+                #     flags[innerIndex1,innerIndex2] = 0
+			    # end
 				if flags[innerIndex1,innerIndex2] == 0
 				    continue
 				end
 				for (qpoint, denominator) in zip(cutoffPoints, denominators)
-					kondoJArray[innerIndex1,innerIndex2,stepIndex+1] += -4 * deltaD * densityOfStates[qpoint] * (kondoJArray[innerIndex1, qpoint, stepIndex] * kondoJArray[innerIndex2, qpoint, stepIndex] + 4 * kondoJArray[qpoint, qpoint, stepIndex] * bathInt(innerIndex1,innerIndex2,qpoint)) / denominator
+				    if  denominator < 0
+							kondoJArray[innerIndex1,innerIndex2,stepIndex+1] += -4 * deltaD * densityOfStates[qpoint] * (kondoJArray[innerIndex1, qpoint, stepIndex] * kondoJArray[innerIndex2, qpoint, stepIndex] + 4 * kondoJArray[qpoint, qpoint, stepIndex] * bathInt(innerIndex1,innerIndex2,qpoint)) / denominator
+					end
                 end
-                if kondoJArray[innerIndex1,innerIndex2,stepIndex+1] * kondoJArray[innerIndex1,innerIndex2,stepIndex] <= 0
+                if kondoJArray[innerIndex1,innerIndex2,stepIndex+1] * kondoJArray[innerIndex1,innerIndex2,stepIndex] <= 0 && stepIndex > 1
[…]

### 2024-03-15 TilingProjectDraft/tilingProject.tex
rewriting parts of the notes

@@
-\documentclass[prb]{revtex4-2}
-\usepackage{braket,amsmath,amssymb,color,graphicx,hyperref,bookmark}
+\documentclass[reprint,hidelinks]{revtex4-2}
+\usepackage{braket,amsmath,color,graphicx,bookmark,bm}
 \bibliographystyle{apsrev4-2}
@@
 For example, a correlated impurity interacting with a conduction bath is a potential auxiliary model for the Hubbard Hamiltonian:
-\begin{equation}
+\begin{equation}\begin{aligned}
 \label{clus_bath_siam}
-\mathcal{H}_\text{SIAM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow} - t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)
-\end{equation}
+\mathcal{H}_\text{SIAM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow} - t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) \\
++ V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) 
+\end{aligned}\end{equation}
 The impurity has onsite energy \(\epsilon_d\) and an onsite correlation \(U\). It hybridises into the bath through \(V\).
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H} = \mathcal{H}_S\ket{S}\bra{S} + \mathcal{H}_R \ket{R}\bra{R} + \mathcal{H}_{SR} \ket{S}\bra{R} + \mathcal{H}_{RS}\ket{S}\bra{R} = \begin{bmatrix} & \mathcal{H}_{R} && \mathcal{H}_{RS} & \\ & \mathcal{H}_{RS}^* && \mathcal{H}_{S} & \end{bmatrix}
+	\mathcal{H} &= \mathcal{H}_S\ket{S}\bra{S} + \mathcal{H}_R \ket{R}\bra{R} + \mathcal{H}_{SR} \ket{S}\bra{R} + \mathcal{H}_{RS}\ket{S}\bra{R} \\
+		    &= \begin{bmatrix} & \mathcal{H}_{R} && \mathcal{H}_{RS} & \\ & \mathcal{H}_{RS}^* && \mathcal{H}_{S} & \end{bmatrix}
 \end{aligned}\end{equation}
@@
 As an example, we can split the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows (fig.~\ref{cluster-bath}):
-\begin{equation}\begin{aligned}
-	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_S} + \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_R}\\
-		      & -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{SR} + H_{RS}}\\
-\end{aligned}\end{equation}
+\begin{widetext}
+\begin{equation}\begin{aligned}
+	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_S} + \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_R} -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N.
+of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{SR} + H_{RS}}\\
+\end{aligned}\end{equation}
+\end{widetext}
 The Greens function of the full Hamiltonian can also be split in a similar fashion:
@@
 Such a construction is shown in fig.~\ref{cluster-bath}.
-\begin{figure}[!htb]
+\begin{figure*}[!htb]
 	\centering
-	\includegraphics[width=0.8\textwidth]{cluster-bath.pdf}
+	\includegraphics[width=0.5\textwidth]{cluster-bath.pdf}
 	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$.
@@
 	\label{cluster-bath}
-\end{figure}
+\end{figure*}
 \textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model}.
@@
 		\[\Sigma_{k}(\omega) = \Sigma_\text{aux}(\omega)\]
-		Since the impurity is purely local, this is an approximation that involves replacing a non-local quantity by its purely local component: \(\Sigma_{k}(\omega) = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}}\Sigma_{\vec r}(\omega) \simeq \Sigma_{\vec r = 0}(\omega)\).
+		Since the impurity is purely local, this is an approximation that involves replacing a non-local quantity by its purely local component: \(\Sigma_{k}(\omega) = \sum_{{\bf r}}e^{i \vec{k}\cdot\vec{r}}\Sigma_{{\bf r}}(\omega) \simeq \Sigma_{{\bf r} = 0}(\omega)\).
 This approximation is a result of the single-site nature of the cluster of the chosen auxiliary model - larger clusters with more impurities can generate non-local components.
@@
 	\item[4.] With this updated bath self-energy, we now create a new \(k-\)space Greens function for the bath:
-		\[G_{i}(\omega) = \sum_k G_{k}(\omega) = \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_k(\omega)} = \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_\text{aux}(\omega)}\]
+		\begin{equation}\begin{aligned}
+		G_{i}(\omega) &= \sum_k G_{k}(\omega) \\
+			      &= \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_k(\omega)} \\
+			      &= \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_\text{aux}(\omega)}
+		\end{aligned}\end{equation}
 	This interacting Greens function is then used to obtain the updated non-interacting Greens function, using Dyson's equation:
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{dmft.pdf}
+	\includegraphics[width=0.4\textwidth]{dmft_scheme.pdf}
 \end{figure}
@@
 In our approach, the auxiliary models can be chosen in various ways. The simplest choice is of course the single-impurity Anderson model of eq.~\ref{clus_bath_siam}:
-\begin{equation}
-\mathcal{H}_\text{SIAM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow} - t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)
-\end{equation}
+\begin{equation}\begin{aligned}
+\mathcal{H}_\text{SIAM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow} - t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) \\
++ V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) 
+\end{aligned}\end{equation}
 This model does not show any impurity phase transition - the impurity is always screened~\cite{hrk_wilson_1980,wilson1975,bullaNRGreview}.
@@
 \item[2.] The second method is to make the cluster itself more complicated. That is, one can introduce multiple impurity sites that are connected via the hopping:
-\begin{equation}
-\mathcal{H}_\text{aux} = -\frac{U}{2}\sum_{d_i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right) ^2 + V\sum_{d_i}\sum_\sigma\left( c^\dagger_{d_i\sigma}c_{0\sigma} + \text{h.c.} \right) + \text{K.E.} - t\sum_{\sigma}\left(c^\dagger_{d_1\sigma}c_{d_2\sigma} + \text{h.c.}\right)
-\end{equation}
+	\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux} = -\frac{U}{2}\sum_{d_i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right) ^2 + V\sum_{d_i}\sum_\sigma\left( c^\dagger_{d_i\sigma}c_{0\sigma} + \text{h.c.} \right) \\
+	+ \text{K.E.} - t\sum_{\sigma}\left(c^\dagger_{d_1\sigma}c_{d_2\sigma} + \text{h.c.}\right)
+	\end{aligned}\end{equation}
 
@@
  	\centering
- 	\includegraphics[width=0.6\textwidth]{gen_siam.pdf}
+ 	\includegraphics[width=0.48\textwidth]{gen_siam.pdf}
  	\caption{Cluster+bath construction of auxiliary model.
@@
 \section{Creating a Hubbard-Heisenberg Hamiltonian from an extended Anderson impurity model}
+
+\subsection{Formal description of the tiling procedure}
+We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian.
+The first step is of course to identify an impurity model that can act as a good auxiliary model for out lattice model.
+The local behaviour of this impurity model should reflect the essential local physics of the lattice model.
+Typically, we will consider impurity model geometries where the real-space bath site connected directly to the impurity also harbours some kind of local interaction.
+We will henceforth refer to this site as the zeroth site.
+In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout.
+In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}_1\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z}_1)\).
+The subscript \(1\) indicates that \({\bf z}_1\) is the first zeroth site, and that there can be multiple such zeroth sites \(\left\{ {\bf z}_i \right\} \), depending on the lattice geometry.
+The unit cell at the position \({\bf r}_d\) is then obtained by placing the zeroth site on all nearest-neighbours of \({\bf r}_d\) and averaging over these configurations:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux}({\bf r}_d) = \frac{1}{\mathcal{Z}}\sum_{{\bf z}_1\in\text{NN}({\bf r}_d)}\mathcal{H}_\text{aux}({\bf r}_d, {\bf z}_1)~,
+\end{aligned}\end{equation}
+where \({\bf z}_1\) is summed over all nearest-neighbours of \({\bf r}_d\) and \(\mathcal{Z}\) is the number of such nearest-neighbours.
+
+In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice.
+For this, we define {\it many-particle global} translation operators \(T({\bf a})\) that translate all positions by a vector \({\bf a}\).
+In terms of manybody states and operators, their action is defined as
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a}) \ket{\bf r_1, \bf r_2,\ldots} &= \ket{\bf r_1 + a, \bf r_2 + a,\ldots}\\
+	T^\dagger({\bf a}) \mathcal{O}\left(\bf r_1, \bf r_2,\ldots\right)T({\bf a}) &= \mathcal{O}\left(\bf r_1 + a, \bf r_2 + a,\ldots\right)~,
+\end{aligned}\end{equation}
+where \(\)
+For example, for a local fermionic creation operator \(c^\dagger({\bf r})\), we have 
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a}) c^\dagger({\bf r}) T({\bf a}) = c^\dagger({\bf r} + {\bf a})
+\end{aligned}\end{equation}
+It acts similarly on the auxiliary model Hamiltonian:
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a})\mathcal{H}_\text{aux}({\bf r}_d)T({\bf a}) = \mathcal{H}_\text{aux}({\bf r}_d + {\bf a})~,
+\end{aligned}\end{equation}
+translating all sites by the vector \({\bf a}\).
+The auxiliary model, being an impurity model, lacks translation symmetry.
+The lattice model does remain invariant under global translation operations.
+In order to reconstruct the full lattice model and restore its translation invariance, we translate the unit cell across all sites of the lattice:
+\begin{equation}\begin{aligned}
+	\label{tilingPrescription}
+	\mathcal{H}_\text{full} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})\\
+				&= \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r} - {\bf r}_d)~ \\
+				&= \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}_1\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d, {\bf z}_1)T({\bf r} - {\bf r}_d)~ \\
+\end{aligned}\end{equation}
+where \({\bf r}\) sums over all lattice sites.
 
@@
 	\label{siam_attr}
-	\mathcal{H}_\text{aux} = \sum_{k\sigma}\epsilon_k \tau_{k\sigma} - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2 + V \sum_{k\sigma} \left(c^\dagger_{k\sigma} c_{d\sigma} + h.c.\right) +J \vec{S_d}\cdot\vec{s} - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2~,
-\end{aligned}\end{equation}
-where \(c_{d\sigma}\) is the impurity electron operator, \(c_{k\sigma}\) is the conduction bath electron operator, \(\vec S_d\) is the impurity spin operator and \(\vec s\) is the operator for the local spin in the conduction bath.
+	\mathcal{H}_\text{E-S} = \mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} + \mathcal{H}_\text{imp-cbath}~,
+\end{aligned}\end{equation}
+where \(\mathcal{H}_\text{cbath} = -t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the mostly non-interacting conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site, \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 + V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath.
+Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath.
 We have found that the e-SIAM has a stable local moment phase for \(U_b < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)).
-We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of a coexistence region at finite temperatures.
-Note that the impurity level is explicitly at half-filling, because the correlation term \(\left( \hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is symmetric under a particle-hole transformation \(\hat n_{d\sigma} \to 1 - \hat n_{d\sigma}\).
-Moreover, the conduction bath is also at half-filling, because we have set the chemical potential \(\mu\) to zero.
-These two ensure that the bulk model is also at half-filling.
-At the end of this section, we will also mention how the tiling works out in the presence of a non-zero filling.
-
-\subsection{Formal description of the tiling procedure}
-We will now use the e-SIAM to recreate the Hubbard model, by tiling the lattice with instances of this auxiliary model Hamiltonian.
-We will now formally define the procedure.
-We first identify a local auxiliary model; this will act as the ``unit cell" for our tiling procedure.
-For this, we place the impurity orbitals at a reference site \(\vec R_0\) of our lattice, and the bath zeroth site at a nearest-neighbour site \(\vec R_0 + \vec a\), and call the corresponding e-SIAM Hamiltonian \(\mathcal{H}_\text{aux}(\vec R_0, \vec a)\).
-The auxiliary model at \(\vec R_0\) can then be obtained by averaging over all nearest neighbours:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(\vec R_0) = \frac{1}{\mathcal{W}}\sum_{\vec a}\mathcal{H}_\text{aux}(\vec R_0, \vec a)~,
-\end{aligned}\end{equation}
-where \(\vec a\) is summed over all nearest-neighbours of \(\vec R_0\) and \(\mathcal{W}\) is the number of such nearest-neighbours.
-In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice.
-For this, we define {\it many-particle} translation operators \(T(\vec a)\) in the usual manner: for a local fermionic operator \(c(\vec r)\), we have \(T(\vec a) c(\vec r) T^\dagger(\vec a) = c(\vec r + \vec a)\).
-It can also work on many-particle operators: \(T(\vec a) c(\vec r^\prime) c(\vec r) T^\dagger(\vec a) = T(\vec a) c(\vec r^\prime) T^\dagger(\vec a) T(\vec a) c(\vec r) T^\dagger(\vec a) = c(\vec r^\prime + \vec a) c(\vec r + \vec a)\).
-It acts similarly on the auxiliary model Hamiltonian:
-\begin{equation}\begin{aligned}
-	T(\vec a)\mathcal{H}_\text{aux}(\vec R_0)T^\dagger(\vec a) = \mathcal{H}_\text{aux}(\vec R_0 + \vec a)~.
-\end{aligned}\end{equation}
-The full bulk model can then be expressed as
-\begin{equation}\begin{aligned}
-	\label{tiledHamiltonian}
-	\mathcal{H}_\text{full} = \sum_{\vec r}T(\vec r)\mathcal{H}_\text{aux}(\vec R_0)T^\dagger(\vec r)~ = \sum_{\vec r} \mathcal{H}_\text{aux}(\vec r) = \frac{1}{\mathcal{W}}\sum_{\vec r, \vec a}\mathcal{H}_\text{aux}(\vec r, \vec a),
-\end{aligned}\end{equation}
-where \(\vec r\) sums over all lattice sites.
+We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of an optical gap in the local spectral function beyond a certain value of interaction strength.
+Note that the impurity site and the conduction bath are both at half-filling.
 
 \subsection{Tiling towards a Hubbard-Heisenberg model}
+In this subsection, we provide an explicit example of constructing a lattice model.
+We will consider a slightly more generalised version of the extended SIAM described in the previous section, and show that that model leads to a form of a Hubbard-Heisenberg model upon restoring translation invariance via repeated translation operations.
+In order to generalise the extended SIAM, we make the following changes.
+We allow the possibility of multiple zeroth sites (bath sites that harbour local interaction) \({\bf z}_i\).
+This can lead to various kinds of interactions with the impurity site, as well as purely on the zeroth sites.
+We allow the conduction bath to reside in a lattice of arbitrary geometry:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{cbath} = -t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
+	- \frac{1}{2  Z}\sum_{{\bf z}_i \in \text{NN}({\bf r}_d)}U_b({\bf z}_i)\left(\hat n_{{\bf z}_i, \uparrow} - \hat n_{{\bf z}_i, \downarrow}\right)^2~,
+\end{aligned}\end{equation}
+where \(\left<{\bf r}_i, {\bf r}_j\right>\neq {\bf r}_d\) indicates that the sum is over all nearest-neighbour pairs of sites avoiding the impurity site \({\bf r}_d\), and \({\bf z}_i={\bf z}_1, {\bf z}_2, \ldots\) is summed over all the bath zeroth sites (\(Z\) in number).
+Note that the auxiliary coordination number \(Z\) can in general be different from the lattice model coordination number \(\mathcal{Z}\).
+We also allow the impurity site \({\bf r}_d\) to have arbitrary filling, by introducing an assymetry parameter \(\eta\) which quantifies the amount of doping:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{imp} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 + \eta\sum_\sigma \hat n_{{\bf r}_d\sigma}~.
+\end{aligned}\end{equation}
+The interaction Hamiltonian can also be generalised to:
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{imp-cbath} &= \sum_{{\bf z}_i,{\bf z}_j}\sum_{\alpha,\alpha^\prime}\frac{1}{ Z}J({\bf z}_i - {\bf z}_j) {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \sigma}_{\alpha,\alpha^\prime}c^\dagger_{{\bf z}_i,\alpha}c_{{\bf z}_j,\alpha^\prime} \\
+				     &+  \sum_{\sigma, {\bf z}_i} \frac{1}{\sqrt Z}V\left({\bf r}_d - {\bf z}_i\right) \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}_i}\sigma} + h.c.\right)
+\end{aligned}\end{equation}
+where \({\bf z}_i\) and \({\bf z}_j\) sum over the bath zeroth sites of the impurity model, and \(\boldsymbol \sigma\) is the vector of Pauli matrices.% The bath zeroth sites, being locally connected to the impurity, typically reside on the sites that are nearest to the impurity.
+This means that we can write \({\bf r}_0 = {\bf r}_d + {\bf a}\), where \({\bf a}\) is a primitive lattice vector that connects \({\bf r}_d\) with its nearest neighbours.
+
+We now follow the prescription laid out in eq.~\ref{tilingPrescription}. The tiled Hamiltonian can be written as 
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{full} = \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}_1\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\left[\mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} \right.\\
+\left.+ \mathcal{H}_\text{imp-cbath}\right]T({\bf r} - {\bf r}_d)~.
+\end{aligned}\end{equation}
+We consider the effect of the translation operations on each part of the Hamiltonian. We first have
+\begin{equation}\begin{aligned}
+	&\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}_1\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}({\bf r}_d, {\bf z}_1)T({\bf r} - {\bf r}_d) \\
+	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\right.\\
+	 &\left.- \sum_{{\bf z}_1\in\text{NN}({\bf r}_d)}\sum_{{\bf z}_i}\frac{U_b({\bf z}_i)}{2Z \mathcal{Z}}\left(\hat n_{{\bf z}_i, \uparrow} - \hat n_{{\bf z}_i, \downarrow}\right)^2\right]T({\bf r} - {\bf r}_d) \\
+	=& -t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
+	 &- \frac{1}{2\mathcal{Z}Z}\sum_{\bf r}\sum_{{\bf z}_1\in\text{NN}\left({\bf r}\right) }\sum_{{\bf z}_i \in \text{NN}({\bf r})} U_b({\bf z}_i)  \left(\hat n_{{\bf z}_i, \uparrow} - \hat n_{{\bf z}_i, \downarrow}\right)^2 \\
+	=& -t(N-2)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
+	 &- \frac{1}{2}\overline{U_b}\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2\\
+\end{aligned}\end{equation}
+where \(\overline{U_b} = \sum_{\bf a} \frac{1}{z}U_b({\bf a})\) is the average of \(U_b({\bf a})\) over the bath zeroth sites in the auxliary model.
+The inequality \(\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}\) ensures that each nearest-neighbour pair appears in \(N-2\) instances of the auxiliary model, \(N\) being the total number of lattice sites.
+The two instances that do not contribute are the ones in which the impurity site itself is at \({\bf r}_i\) or \({\bf r}_j\).
+In the first step, the factor of \(\mathcal{Z}\) is cancelled out by the trivial sum over \({\bf r}_0\).
+
+The next part is
+\begin{equation}\begin{aligned}
+	&\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf r}_0\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp}T({\bf r} - {\bf r}_d) \\
+	=& -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 + \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}~.
+\end{aligned}\end{equation}
+This is obtained simply by replacing the impurity position \({\bf r}_d\) with the translated position \({\bf r}\), generating a translation-invariant Hubbard term (the first term) and a finite chemical potential (second term).
+
+We now consider the final term:
+\begin{widetext}
+\begin{equation}\begin{aligned}
+	&\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf r}_0\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}T({\bf r} - {\bf r}_d)\\
+	&=\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf r}_0\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\left[\sum_{{\bf a},{\bf a}^\prime}\sum_{\alpha,\alpha^\prime}\frac{1}{Z}J({\bf a} - {\bf a}^\prime) {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \sigma}c^\dagger_{{\bf r}_d + {\bf a},\alpha}c_{{\bf r}_d + {\bf a}^\prime,\alpha^\prime} + \sum_{{\bf a}, \sigma} \frac{1}{\sqrt Z}V\left({\bf a}\right) \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf r}_d + {\bf a}},\sigma} + h.c.\right)\right]T({\bf r} - {\bf r}_d)
+\end{aligned}\end{equation}
+\end{widetext}
+\clearpage
+
 To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(i\) of the lattice, and the bath coupled to the impurity as the set of remaining \(N-1\) sites in the lattice.
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(i,j) = -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n} \left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right) ^2 + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j - \frac{1}{2}U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2
+	\mathcal{H}_\text{aux}(i,j) = -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n} \left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right) ^2 \\
+	+ V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j - \frac{1}{2}U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2 
 \end{aligned}\end{equation}
 The tight-binding term sums over all nearest pairs \((m,n)\) that do not involve the site \(i\).
-In general \(i\) will have \(\mathcal{W}\) nearest neighbours for a lattice with coordination number \(\mathcal{W}\).
+In general \(i\) will have \(\mathcal{Z}\) nearest neighbours for a lattice with coordination number \(\mathcal{Z}\).
 The total local Hamiltonian for the site \(i\) is obtained by averaging over the Hamiltonians \(\mathcal{H}_\text{aux}(i,j)\) for all nearest neighbours \(j\) of \(i\):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(i) &= \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right)  \right.\\
+\begin{widetext}
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{aux}(i) &= \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right)  \right.\\
 				  &\left. +J \vec{S_i}\cdot\vec{S}_j - \frac{1}{2}U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\\
-				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j \right.\\
-				  &\left.- \frac{1}{2}U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]
+				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j - \frac{1}{2}U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& \sum_i \mathcal{H}_\text{aux}(i) = \sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
+	\mathcal{H}_\text{full} =& \sum_i \mathcal{H}_\text{aux}(i) = \sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
 				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j - \frac{1}{2}U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\right]\\
-	=& -\frac{1}{2}\left(U + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{W}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
-				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j\right]\right]
+	=& -\frac{1}{2}\left(U + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) + J \vec{S_i}\cdot\vec{S}_j\right]\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& -\frac{1}{2}\left(U + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - 2t\left(N-2\right)\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{\mathcal{W}}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\\
-				  &+ \left. J \vec{S_i}\cdot\vec{S}_j\right]\\
-				  &=-\frac{1}{2}\left(U + U_b\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(2t (N-2) - \frac{2V}{\mathcal{W}}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{\mathcal{W}} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
-\end{aligned}\end{equation}
+	\mathcal{H}_\text{full} =& -\frac{1}{2}\left(U + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - 2t\left(N-2\right)\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{\mathcal{Z}}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) + J \vec{S_i}\cdot\vec{S}_j\right]\\
+				  &=-\frac{1}{2}\left(U + U_b\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(2t (N-2) - \frac{2V}{\mathcal{Z}}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{\mathcal{Z}} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
+\end{aligned}\end{equation}
+\end{widetext}
 We end up with a Hubbard-Heisenberg model, of the form:
 \begin{equation}\begin{aligned}
-	\mathcal{H}_{H-H} = - \frac{1}{2}U_\text{H-H}\sum_{i} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{1}{\mathcal{W}}t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{\mathcal{W}}J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j
+	\mathcal{H}_{H-H} = - \frac{1}{2}U_\text{H-H}\sum_{i} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{\mathcal{Z}}J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j\\
+	- \frac{1}{\mathcal{Z}}t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) \\
 \end{aligned}\end{equation}
@@
 	\label{map_aux_bulk}
-	t_{H-H} = \left(2t \mathcal{W}(N-2) - 2V\right),~ ~ U_{H-H} = U + U_b, ~ ~ J_{H-H} = 2J
+	t_{H-H} &= \left(2t \mathcal{Z}(N-2) - 2V\right),\\
+	U_{H-H} &= U + U_b,\\
+	J_{H-H} &= 2J
 \end{aligned}\end{equation}
@@
 \subsection{Translation symmetry and a conserved total momentum}
-From the form in eq.~\ref{tiledHamiltonian}, the tiled Hamiltonian is symmetric under discrete many-body translations:
+From the form in eq.~\ref{tilingPrescription}, the tiled Hamiltonian is symmetric under discrete many-body translations:
 \begin{equation}\begin{aligned}\label{translationSymmetry}
-	T(\vec r)\mathcal{H}_\text{full}T^\dagger(\vec r) = \sum_{\vec r^\prime}T(\vec r + \vec r^\prime)\mathcal{H}_\text{aux}(\vec R_0)T^\dagger(\vec r + \vec r^\prime) = \sum_{\vec r^\prime}T(\vec r^\prime)\mathcal{H}_\text{aux}(\vec R_0)T^\dagger(\vec r^\prime) = \mathcal{H}_\text{full}~.
-\end{aligned}\end{equation}
-There we used the fact that \(\vec r + \vec r^\prime\) simply translates the auxiliary model defined by the coordinate \(\vec r^\prime + \vec R_0\) to a new auxiliary model at the modified coordinate \(\vec r + \vec r^\prime + \vec R_0\).
+	T({\bf r})\mathcal{H}_\text{full}T^\dagger({\bf r}) = \sum_{{\bf r}^\prime}T({\bf r} + {\bf r}^\prime)\mathcal{H}_\text{aux}({\bf r_0})T^\dagger({\bf r} + {\bf r}^\prime) = \sum_{{\bf r}^\prime}T({\bf r}^\prime)\mathcal{H}_\text{aux}({\bf r_0})T^\dagger({\bf r}^\prime) = \mathcal{H}_\text{full}~.
+\end{aligned}\end{equation}
+There we used the fact that \({\bf r} + {\bf r}^\prime\) simply translates the auxiliary model defined by the coordinate \({\bf r}^\prime + {\bf r_0}\) to a new auxiliary model at the modified coordinate \({\bf r} + {\bf r}^\prime + {\bf r_0}\).
 Since this transformation from one auxiliary model to another simply shuffles the group of all auxiliary models, the sum over the group remains the sum, and we recover the same bulk model.
@@
 The fact that the Hamiltonian \(\mathcal{H}_\text{full}\) commutes with the many-body translation operator implies that the total momentum \(\vec k\) is a conserved quantity.
-This is in fact because the many-body translation operators can be obtained in terms of \(\vec k\): \(T(\vec r) = \exp\left\{ i \vec{k}\cdot\vec{r} \right\} \).
+This is in fact because the many-body translation operators can be obtained in terms of \(\vec k\): \(T({\bf r}) = \exp\left\{ i \vec{k}\cdot\vec{r} \right\} \).
 
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_{H-H} = -\frac{1}{2}U_\text{H-H} \sum_{i} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{1}{\mathcal{W}}t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{\mathcal{W}}J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j + \mu_\text{H-H}\sum_{i\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
+	\mathcal{H}_{H-H} = -\frac{1}{2}U_\text{H-H} \sum_{i} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{1}{\mathcal{Z}}t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{\mathcal{Z}}J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j + \mu_\text{H-H}\sum_{i\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\lim_{\mathcal{W}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} = t^2\sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)\sum_{j,j^\prime}G_1^{(0,\bar 0)}\left(j\tau; j^\prime\tau^\prime\right) \\
+	\lim_{\mathcal{Z}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} = t^2\sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)\sum_{j,j^\prime}G_1^{(0,\bar 0)}\left(j\tau; j^\prime\tau^\prime\right) \\
 	= \sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)~,
@@
 \begin{equation}\begin{aligned}
-	\lim_{\mathcal{W}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})} = \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\chi(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)~,
+	\lim_{\mathcal{Z}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})} = \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\chi(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)~,
 \end{aligned}\end{equation}
@@
 \section{Form of the eigenstates: Bloch's theorem}
-In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\vec k}(\vec r)} = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \ket{\psi_i(\vec r - \vec R_i)}\).
-Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation \(T(\vec R)\) by some lattice distance \(\vec R = \sum_i n_i \vec a_i\):
-\begin{equation}\begin{aligned}
-	T(\vec R)\ket{\Psi_{\vec k}\left(\vec r\right)} = \ket{\Psi_{\vec k}(\vec r + \vec R)} = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \ket{\psi_i(\vec r + \vec R - \vec R_i)} = e^{i \vec{k}\cdot\vec{R}}\sum_i e^{i \vec{k}\cdot\left(\vec{R}_i - \vec R\right)} \ket{\psi_i(\vec r - (\vec R_i - \vec R))} = e^{\vec{k}\cdot\vec{R}}\ket{\Psi(\vec r)}
-\end{aligned}\end{equation}
-At the end, we used the fact that \(\vec r_i - \vec R\) is just another lattice vector \(\vec R_j\). As mentioned before, these translation operators share eigenstates with the momentum operator:
-\begin{equation}\begin{aligned}
-	T\left( \vec R \right) \ket{\vec k} = \sum_{\vec r_i} e^{i \vec{k}\cdot\vec{r}_i}T\left( \vec R \right)\ket{\vec r_i} = e^{i \vec{k}\cdot\vec{R}}\sum_{\vec r_i} e^{i \vec{k}\cdot\left(\vec{r}_i - \vec R\right)}\ket{\vec r_i - \vec R} = e^{i \vec{k}\cdot\vec{R}} \ket{\vec k}
+In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\vec k}({\bf r})} = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \ket{\psi_i({\bf r} - {\bf r}_i)}\).
+Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation \(T({\bf r})\) by some lattice distance \({\bf r} = \sum_i n_i {\bf a}_i\):
+\begin{equation}\begin{aligned}
+	T({\bf r})\ket{\Psi_{\vec k}\left({\bf r}\right)} = \ket{\Psi_{\vec k}({\bf r} + {\bf r})} = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \ket{\psi_i({\bf r} + {\bf r} - {\bf r}_i)} = e^{i \vec{k}\cdot\vec{R}}\sum_i e^{i \vec{k}\cdot\left(\vec{R}_i - {\bf r}\right)} \ket{\psi_i({\bf r} - ({\bf r}_i - {\bf r}))} = e^{\vec{k}\cdot\vec{R}}\ket{\Psi({\bf r})}
+\end{aligned}\end{equation}
+At the end, we used the fact that \({\bf r}_i - {\bf r}\) is just another lattice vector \({\bf r}_j\). As mentioned before, these translation operators share eigenstates with the momentum operator:
+\begin{equation}\begin{aligned}
+	T\left( {\bf r} \right) \ket{\vec k} = \sum_{{\bf r}_i} e^{i \vec{k}\cdot\vec{r}_i}T\left( {\bf r} \right)\ket{{\bf r}_i} = e^{i \vec{k}\cdot\vec{R}}\sum_{{\bf r}_i} e^{i \vec{k}\cdot\left(\vec{r}_i - {\bf r}\right)}\ket{{\bf r}_i - {\bf r}} = e^{i \vec{k}\cdot\vec{R}} \ket{\vec k}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-\psi^n_\text{aux}\left(\vec R_i, \vec a\right)~,
-\end{aligned}\end{equation}
-with the impurity position \(\vec R_i\) and zeroth site position \(\vec R_i + \vec a\), to construct eigenstates of the bulk Hamiltonian.
-\(\vec R_i\) is a lattice vector, while \(\vec a\) is one of the \(\mathcal{W}\) vectors that connect a lattice site with its nearest neighbours.
+\psi^n_\text{aux}\left({\bf r}_i, {\bf a}\right)~,
+\end{aligned}\end{equation}
+with the impurity position \({\bf r}_i\) and zeroth site position \({\bf r}_i + {\bf a}\), to construct eigenstates of the bulk Hamiltonian.
+\({\bf r}_i\) is a lattice vector, while \({\bf a}\) is one of the \(\mathcal{Z}\) vectors that connect a lattice site with its nearest neighbours.
 The \(n\) in the superscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
@@
 \begin{equation}\begin{aligned}
-	\ket{\Psi^n_{\vec k}} = \frac{1}{\sqrt{\mathcal{W} N}}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left(\vec R_i, \vec a\right)
+	\ket{\Psi^n_{\vec k}} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_i, {\bf a}} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left({\bf r}_i, {\bf a}\right)
 \end{aligned}\end{equation}
@@
 	\label{bloch-states}
-	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} \sqrt{\mathcal{W} N}}\sum_{\vec R_i, \vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i, \vec a\right)~,
+	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} \sqrt{\mathcal{Z} N}}\sum_{{\bf r}_i, {\bf a}} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left({\bf r}_i, {\bf a}\right)~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k} | \Psi_{\vec k}} &= \frac{1}{\mathcal{W}^2 \lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, a, a^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime, \vec a^\prime) | \psi_\text{aux}(\vec R, \vec a)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, }e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R^\prime) | \psi_\text{aux}(\vec R)}\\
-					       &=\frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) | \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i \vec{k}\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) | T^\dagger(\vec R - \vec R^\prime) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)}\\
-					       &= \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{\vec R, \vec R^\prime, q}e^{i (\vec{k} - \vec q)\cdot(\vec R - \vec R^\prime)}\braket{\psi_\text{aux}(\vec R_0) \ket{\vec q}\bra{\vec q} \psi_\text{aux}(\vec R_0)} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{q} N^2 \delta_{\vec{k},\vec q}|\braket{\psi_\text{aux}(\vec R_0) | \vec q}|^2\\
-\end{aligned}\end{equation}
-By requiring this norm to be unity, we obtain \(\lambda_{\vec k}^2 = |\braket{\psi_\text{aux}(\vec R_0) | \vec k}|^2\). In the above exercise, we defined a state 
+	\braket{\Psi_{\vec k} | \Psi_{\vec k}} &= \frac{1}{\mathcal{Z}^2 \lambda_{\vec k}^2 N^2}\sum_{{\bf r}, {\bf r}^\prime, a, a^\prime}e^{i \vec{k}\cdot({\bf r} - {\bf r}^\prime)}\braket{\psi_\text{aux}({\bf r}^\prime, {\bf a}^\prime) | \psi_\text{aux}({\bf r}, {\bf a})} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{{\bf r}, {\bf r}^\prime, }e^{i \vec{k}\cdot({\bf r} - {\bf r}^\prime)}\braket{\psi_\text{aux}({\bf r}^\prime) | \psi_\text{aux}({\bf r})}\\
+					       &=\frac{1}{\lambda_{\vec k}^2 N^2}\sum_{{\bf r}, {\bf r}^\prime}e^{i \vec{k}\cdot({\bf r} - {\bf r}^\prime)}\braket{\psi_\text{aux}({\bf r_0}) | T^\dagger({\bf r} - {\bf r}^\prime) | \psi_\text{aux}({\bf r_0})} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{{\bf r}, {\bf r}^\prime, q}e^{i \vec{k}\cdot({\bf r} - {\bf r}^\prime)}\braket{\psi_\text{aux}({\bf r_0}) | T^\dagger({\bf r} - {\bf r}^\prime) \ket{\vec q}\bra{\vec q} \psi_\text{aux}({\bf r_0})}\\
+					       &= \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{{\bf r}, {\bf r}^\prime, q}e^{i (\vec{k} - \vec q)\cdot({\bf r} - {\bf r}^\prime)}\braket{\psi_\text{aux}({\bf r_0}) \ket{\vec q}\bra{\vec q} \psi_\text{aux}({\bf r_0})} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{q} N^2 \delta_{\vec{k},\vec q}|\braket{\psi_\text{aux}({\bf r_0}) | \vec q}|^2\\
+\end{aligned}\end{equation}
+By requiring this norm to be unity, we obtain \(\lambda_{\vec k}^2 = |\braket{\psi_\text{aux}({\bf r_0}) | \vec k}|^2\). In the above exercise, we defined a state 
 \begin{equation}\begin{aligned}\label{zeroth_site_average}
-	\ket{\psi_\text{aux}(\vec R)} = (1/w)\sum_{\vec a}\ket{\psi_\text{aux}(\vec R, \vec a)}~,
-\end{aligned}\end{equation}
-by averaging over the neasest neighbours of \(\vec R\), and inserted the total momentum basis \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators.
-\(\vec R_0\) is any particular lattice site which we define as the origin of the lattice.
-Because of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \(\vec a\) we choose among the \(\mathcal{W}\) choices.
+	\ket{\psi_\text{aux}({\bf r})} = (1/w)\sum_{{\bf a}}\ket{\psi_\text{aux}({\bf r}, {\bf a})}~,
+\end{aligned}\end{equation}
+by averaging over the neasest neighbours of \({\bf r}\), and inserted the total momentum basis \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators.
+\({\bf r_0}\) is any particular lattice site which we define as the origin of the lattice.
+Because of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \({\bf a}\) we choose among the \(\mathcal{Z}\) choices.
 
@@
 We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
-We define the time-domain Greens function between two points \(\vec R\) and \(\vec R + \vec r\) as
-\begin{equation}\begin{aligned}
-	G_\text{H-H}(\vec r, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c(\vec R + r,t), c^\dagger(\vec R) \right\} | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-where the bulk Hamiltonian \(H_\text{H-H}\) leads to the dynamics of the annihilation operator: \(c(\vec R + r,t) = e^{i H_\text{H-H} t}c(\vec R + r)e^{-i H_\text{H-H} t}\).
+We define the time-domain Greens function between two points \({\bf r}\) and \({\bf r} + {\bf r}\) as
+\begin{equation}\begin{aligned}
+	G_\text{H-H}({\bf r}, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c({\bf r} + r,t), c^\dagger({\bf r}) \right\} | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+where the bulk Hamiltonian \(H_\text{H-H}\) leads to the dynamics of the annihilation operator: \(c({\bf r} + r,t) = e^{i H_\text{H-H} t}c({\bf r} + r)e^{-i H_\text{H-H} t}\).
 Following eq.~\ref{siam_to_hubb}, the exponential can be written as:
 \begin{equation}\begin{aligned}
-e^{i H_\text{H-H} t} = \exp\left[\sum_i t\mathcal{H}_\text{aux}(\vec R_i)\right] 
-\end{aligned}\end{equation}
-In order to simplify this expression, we rewrite the sum over the auxiliary models in terms of a uniform piece \(\sum_{i}\mathcal{H}_\text{aux}(\vec R_0)\) and a difference piece \(\Delta(i) = \mathcal{H}_\text{aux}(\vec R_i) - \mathcal{H}_\text{aux}(\vec R_0)\):
-\begin{equation}\begin{aligned}
-	\sum_{\vec R_i} \mathcal{H}_\text{aux}(\vec R_i) = \sum_{\vec R_i} \left[\mathcal{H}_\text{aux}(\vec R_0) + \Delta(\vec R_i)\right] = N \left[\mathcal{H}_\text{aux}(\vec R_0) + \frac{1}{N}\sum_{\vec R_i} \Delta(\vec R_i)\right];
-\end{aligned}\end{equation}
-\(\vec R_0\) is the origin of the lattice, and \(N\) is the number of lattice sites.
-The uniform piece \(\sum_{i}\mathcal{H}_\text{aux}(\vec R_0)\) acts as the ``center-of-mass" Hamiltonian - it responds to spectral flow brought about by changes in boundary conditions.
+e^{i H_\text{H-H} t} = \exp\left[\sum_i t\mathcal{H}_\text{aux}({\bf r}_i)\right] 
+\end{aligned}\end{equation}
+In order to simplify this expression, we rewrite the sum over the auxiliary models in terms of a uniform piece \(\sum_{i}\mathcal{H}_\text{aux}({\bf r_0})\) and a difference piece \(\Delta(i) = \mathcal{H}_\text{aux}({\bf r}_i) - \mathcal{H}_\text{aux}({\bf r_0})\):
+\begin{equation}\begin{aligned}
+	\sum_{{\bf r}_i} \mathcal{H}_\text{aux}({\bf r}_i) = \sum_{{\bf r}_i} \left[\mathcal{H}_\text{aux}({\bf r_0}) + \Delta({\bf r}_i)\right] = N \left[\mathcal{H}_\text{aux}({\bf r_0}) + \frac{1}{N}\sum_{{\bf r}_i} \Delta({\bf r}_i)\right];
+\end{aligned}\end{equation}
+\({\bf r_0}\) is the origin of the lattice, and \(N\) is the number of lattice sites.
+The uniform piece \(\sum_{i}\mathcal{H}_\text{aux}({\bf r_0})\) acts as the ``center-of-mass" Hamiltonian - it responds to spectral flow brought about by changes in boundary conditions.
 The other piece acts as a "relative motion" Hamiltonian and is insensitive to changes in the boundary conditions, because any spectral flow of the auxiliary model Hamiltonians gets cancelled out in the difference operation.
-While the COM Hamiltonian is a thermodynamically large object, the number of terms in the difference piece is of the order of unity (the sum over \(\vec R_i\) is cancelled out by the \(1/N\) factor).
+While the COM Hamiltonian is a thermodynamically large object, the number of terms in the difference piece is of the order of unity (the sum over \({\bf r}_i\) is cancelled out by the \(1/N\) factor).
 We can therefore expand the exponential in the ratio of the relative piece to the COM piece:
 \begin{equation}\begin{aligned}
-	e^{i H_\text{H-H} t} = e^{i t N \mathcal{H}_\text{aux}(\vec R_0)}\left[1 + \frac{1}{N \mathcal{H}_\text{aux}(\vec R_0)}\sum_{\vec R_i} \Delta(\vec R_i) + \ldots\right];
+	e^{i H_\text{H-H} t} = e^{i t N \mathcal{H}_\text{aux}({\bf r_0})}\left[1 + \frac{1}{N \mathcal{H}_\text{aux}({\bf r_0})}\sum_{{\bf r}_i} \Delta({\bf r}_i) + \ldots\right];
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	c(\vec R + r,t) \simeq e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}
+	c({\bf r} + r,t) \simeq e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r} + r)e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G_\text{H-H}(\vec r, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R) \right\} | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-Because of translation symmetry of the bulk lattice, the initial point \(\vec R\) of the excitation can be shifted to the origin \(\vec R_0\) without any loss of generality:
-\begin{equation}\begin{aligned}
-	G_\text{H-H}(\vec r, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \Psi_\text{gs}}~.
+	G_\text{H-H}({\bf r}, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r} + r)e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}, c^\dagger({\bf r}) \right\} | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+Because of translation symmetry of the bulk lattice, the initial point \({\bf r}\) of the excitation can be shifted to the origin \({\bf r_0}\) without any loss of generality:
+\begin{equation}\begin{aligned}
+	G_\text{H-H}({\bf r}, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r_0} + r)e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}, c^\dagger({\bf r_0}) \right\} | \Psi_\text{gs}}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\ket{\Psi_\text{gs}} = \frac{1}{\lambda_{\vec k_0} \sqrt{\mathcal{W} N}}\sum_{\vec R_j, \vec a \in \text{NN of }\vec R_j} e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}(\vec R_j, \vec a)}~,
-\end{aligned}\end{equation}
-where we have brought back the explicit sum over the nearest neighbours \(\vec a\) of the impurity site (following eq.~\ref{zeroth_site_average}).
+	\ket{\Psi_\text{gs}} = \frac{1}{\lambda_{\vec k_0} \sqrt{\mathcal{Z} N}}\sum_{{\bf r}_j, {\bf a} \in \text{NN of }{\bf r}_j} e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}({\bf r}_j, {\bf a})}~,
+\end{aligned}\end{equation}
+where we have brought back the explicit sum over the nearest neighbours \({\bf a}\) of the impurity site (following eq.~\ref{zeroth_site_average}).
 We again simplify the wavefunction by keeping only the uniform piece and dropping the difference pieces.
 \begin{equation}\begin{aligned}
-	\ket{\Psi_\text{gs}} = \sum_{\vec a \in \text{NN of}\vec R_0}\frac{1}{\sqrt \mathcal{W}\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0, \vec a)} + \ket{\psi_\text{diff}(\vec k_0)}
-\end{aligned}\end{equation}
-where \(\ket{\psi_\text{diff}(\vec k_0)} = \ket{\Psi_\text{gs}} - \frac{\sqrt \mathcal{W}}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)}\).
+	\ket{\Psi_\text{gs}} = \sum_{{\bf a} \in \text{NN of}{\bf r_0}}\frac{1}{\sqrt \mathcal{Z}\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}({\bf r_0}, {\bf a})} + \ket{\psi_\text{diff}(\vec k_0)}
+\end{aligned}\end{equation}
+where \(\ket{\psi_\text{diff}(\vec k_0)} = \ket{\Psi_\text{gs}} - \frac{\sqrt \mathcal{Z}}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}({\bf r_0})}\).
 The Greens funtion takes the form
 \begin{equation}\begin{aligned}
-G_\text{H-H}(\vec r, t) =  \frac{-i\theta(t)}{\mathcal{W} \lambda_{\vec k_0}^2}\sum_{\vec a_1, \vec a_2 \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a_1) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a_2)}~.
-\end{aligned}\end{equation}
-Specifically, for the local Greens function \(G_\text{H-H}(\vec r=0, t)\), we keep the states with \(\vec a_1 = \vec a_2\), leading to the expression
+G_\text{H-H}({\bf r}, t) =  \frac{-i\theta(t)}{\mathcal{Z} \lambda_{\vec k_0}^2}\sum_{{\bf a}_1, {\bf a}_2 \in \text{NN of }{\bf r_0}}\braket{\psi_\text{aux}({\bf r_0}, {\bf a}_1) | \left\{ e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r_0} + r)e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}, c^\dagger({\bf r_0}) \right\} | \psi_\text{aux}({\bf r_0}, {\bf a}_2)}~.
+\end{aligned}\end{equation}
+Specifically, for the local Greens function \(G_\text{H-H}({\bf r}=0, t)\), we keep the states with \({\bf a}_1 = {\bf a}_2\), leading to the expression
 \begin{equation}\begin{aligned}
 	\label{greens_func_approx}
-	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) =  \frac{-i\theta(t)}{\mathcal{W} \lambda_{\vec k_0}^2}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + r)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)}~.
-\end{aligned}\end{equation}
-Because of the symmetry of the lattice, all Greens functions obtained for various positions of the zeroth site \(\vec a\) are equal, and the local Greens function simplifies to
-\begin{equation}\begin{aligned}
-	G_\text{loc}(t) \equiv G_\text{H-H}(\vec r=0, t) &= -\frac{1}{\lambda_{\vec k_0}^2 }i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0)}~.
-\end{aligned}\end{equation}
-In this form, the only Hamiltonian involved in the expression is the COM Hamiltonian at \(\vec R_0\), and \(G_\text{H-H}(\vec r=0, t)\) is therefore captured by the impurity Greens function \(\mathcal{G}\) in the auxiliary model \(N \mathcal{H}_\text{aux}(\vec R_0)\) with ground-state \(\ket{\psi_\text{aux}(\vec R_0)}\):
+	G_\text{loc}(t) \equiv G_\text{H-H}({\bf r}=0, t) =  \frac{-i\theta(t)}{\mathcal{Z} \lambda_{\vec k_0}^2}\sum_{{\bf a} \in \text{NN of }{\bf r_0}}\braket{\psi_\text{aux}({\bf r_0}, {\bf a}) | \left\{ e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r_0} + r)e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}, c^\dagger({\bf r_0}) \right\} | \psi_\text{aux}({\bf r_0}, {\bf a})}~.
+\end{aligned}\end{equation}
+Because of the symmetry of the lattice, all Greens functions obtained for various positions of the zeroth site \({\bf a}\) are equal, and the local Greens function simplifies to
+\begin{equation}\begin{aligned}
+	G_\text{loc}(t) \equiv G_\text{H-H}({\bf r}=0, t) &= -\frac{1}{\lambda_{\vec k_0}^2 }i\theta(t) \braket{\psi_\text{aux}({\bf r_0}) | \left\{ e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r_0})e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}, c^\dagger({\bf r_0}) \right\} | \psi_\text{aux}({\bf r_0})}~.
+\end{aligned}\end{equation}
+In this form, the only Hamiltonian involved in the expression is the COM Hamiltonian at \({\bf r_0}\), and \(G_\text{H-H}({\bf r}=0, t)\) is therefore captured by the impurity Greens function \(\mathcal{G}\) in the auxiliary model \(N \mathcal{H}_\text{aux}({\bf r_0})\) with ground-state \(\ket{\psi_\text{aux}({\bf r_0})}\):
 \begin{equation}\begin{aligned}
 	\label{greens_func_relation}
-	G_\text{loc}(t) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{G}_{dd}(t)~,\quad \mathcal{G}_{dd}(t) = -i\theta(t) \braket{\psi_\text{aux}(\vec R_0) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0)}~.
-\end{aligned}\end{equation}
-The cursive script symbol \(\mathcal{G}_{dd}\) has been used to denote the impurity Greens function for the auxiliary model \(N \mathcal{H}_\text{aux}(\vec R_0)\).
-
-For the nearest neighbour Greens function \(G_\text{near-n} \equiv G_\text{H-H}(\vec r=\vec a, t)\), we keep only the terms with \(\vec a_1 = \vec a_2 = \vec a\) in the summation of eq.~\ref{greens_func_approx}:
+	G_\text{loc}(t) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{G}_{dd}(t)~,\quad \mathcal{G}_{dd}(t) = -i\theta(t) \braket{\psi_\text{aux}({\bf r_0}) | \left\{ e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r_0})e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}, c^\dagger({\bf r_0}) \right\} | \psi_\text{aux}({\bf r_0})}~.
+\end{aligned}\end{equation}
+The cursive script symbol \(\mathcal{G}_{dd}\) has been used to denote the impurity Greens function for the auxiliary model \(N \mathcal{H}_\text{aux}({\bf r_0})\).
+
+For the nearest neighbour Greens function \(G_\text{near-n} \equiv G_\text{H-H}({\bf r}={\bf a}, t)\), we keep only the terms with \({\bf a}_1 = {\bf a}_2 = {\bf a}\) in the summation of eq.~\ref{greens_func_approx}:
 \begin{equation}\begin{aligned}
 	\label{greens_func_relation_near}
-	G_\text{near-n}(t) \equiv G_\text{H-H}(\vec r=\vec a, t) = -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}}i\theta(t) \braket{\psi_\text{aux}(\vec R_0, \vec a) | \left\{ e^{i N \mathcal{H}_\text{aux}(\vec R_0) t}c(\vec R_0 + \vec a)e^{-i N \mathcal{H}_\text{aux}(\vec R_0) t}, c^\dagger(\vec R_0) \right\} | \psi_\text{aux}(\vec R_0, \vec a)} \\
-	= \frac{1}{\lambda_{\vec k_0}^2 \mathcal{W}} \mathcal{G}_{dz}(t)~.
+	G_\text{near-n}(t) \equiv G_\text{H-H}({\bf r}={\bf a}, t) = -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{Z}}i\theta(t) \braket{\psi_\text{aux}({\bf r_0}, {\bf a}) | \left\{ e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r_0} + {\bf a})e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}, c^\dagger({\bf r_0}) \right\} | \psi_\text{aux}({\bf r_0}, {\bf a})} \\
+	= \frac{1}{\lambda_{\vec k_0}^2 \mathcal{Z}} \mathcal{G}_{dz}(t)~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	||\ket{\Psi_\text{gs}} - \frac{1}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}(\vec R_0)}||^2 &= |1 + \frac{1}{\lambda_{\vec k_0}^2} - \left[\frac{1}{\lambda_{\vec k_0}}e^{i \vec{k_0}\cdot\vec{R_0}}\braket{\Psi_\text{gs} | \psi_\text{aux}(\vec R_0)} + \text{h.c.}\right]| \\
-	&=|1 + \frac{1}{\lambda_{\vec k_0}^2} - \frac{1}{\lambda_{\vec k_0}^2 N}\sum_{\vec R_j} \left(e^{i \vec k_0 \cdot \left( \vec R_j - \vec R_0 \right)}  \braket{\psi_\text{aux}(\vec R_0) | \psi_\text{aux}(\vec R_j) } + \text{h.c.}\right)|\\
-	&=|1 + \frac{1}{\lambda_{\vec k_0}^2} - \frac{1}{\lambda_{\vec k_0}^2 N}\sum_{\vec R_j,\vec q} \left(e^{i \left(\vec k_0 - \vec q\right)\cdot \left( \vec R_j - \vec R_0 \right)}\lambda_{\vec q}^2 + \text{h.c.}\right)|\\
+	||\ket{\Psi_\text{gs}} - \frac{1}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}({\bf r_0})}||^2 &= |1 + \frac{1}{\lambda_{\vec k_0}^2} - \left[\frac{1}{\lambda_{\vec k_0}}e^{i \vec{k_0}\cdot\vec{r_0}}\braket{\Psi_\text{gs} | \psi_\text{aux}({\bf r_0})} + \text{h.c.}\right]| \\
+	&=|1 + \frac{1}{\lambda_{\vec k_0}^2} - \frac{1}{\lambda_{\vec k_0}^2 N}\sum_{{\bf r}_j} \left(e^{i \vec k_0 \cdot \left( {\bf r}_j - {\bf r_0} \right)}  \braket{\psi_\text{aux}({\bf r_0}) | \psi_\text{aux}({\bf r}_j) } + \text{h.c.}\right)|\\
+	&=|1 + \frac{1}{\lambda_{\vec k_0}^2} - \frac{1}{\lambda_{\vec k_0}^2 N}\sum_{{\bf r}_j,\vec q} \left(e^{i \left(\vec k_0 - \vec q\right)\cdot \left( {\bf r}_j - {\bf r_0} \right)}\lambda_{\vec q}^2 + \text{h.c.}\right)|\\
 	&= |1 - \frac{1}{\lambda_{\vec k_0}^2}|
@@
 By choosing an appropriate auxiliary model, the overlap factor \(\lambda_{\vec k_0}\) can be brought close to unity, leading to a smaller difference.
-The local and nearest-neighbour Greens functions of the full model can thus be computed from the impurity local Greens function \(\mathcal{G}_{dd}\) and the impurity-bath zeroth site Greens function \(\mathcal{G}_{dz}\) on the COM auxiliary model \(N \mathcal{H}_\text{aux}(\vec R_0)\).
+The local and nearest-neighbour Greens functions of the full model can thus be computed from the impurity local Greens function \(\mathcal{G}_{dd}\) and the impurity-bath zeroth site Greens function \(\mathcal{G}_{dz}\) on the COM auxiliary model \(N \mathcal{H}_\text{aux}({\bf r_0})\).
 By using these real-space Greens functions, one can then compute \(k-\)space Greens functions of the full model.
@@
 This approach also holds for higher-order static correlation functions.
-For example, a general local correlation of the form \(\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\) corresponding to operators \(\mathcal{O}_1\) and \(\mathcal{O}_2\) can be estimated, using this method, in terms of auxiliary model quantities.
-For that, we first express the correlation at sites \(\vec R_0\) as well as its nearest neighbours:
-\begin{equation}\begin{aligned}
-	\frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} + \frac{1}{\mathcal{W}}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + \vec a) | \Psi_\text{gs}}\right]
+For example, a general local correlation of the form \(\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0}) | \Psi_\text{gs}}\) corresponding to operators \(\mathcal{O}_1\) and \(\mathcal{O}_2\) can be estimated, using this method, in terms of auxiliary model quantities.
+For that, we first express the correlation at sites \({\bf r_0}\) as well as its nearest neighbours:
+\begin{equation}\begin{aligned}
+	\frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0}) | \Psi_\text{gs}} + \frac{1}{\mathcal{Z}}\sum_{{\bf a} \in \text{NN of }{\bf r_0}}\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0} + {\bf a}) \mathcal{O}_2({\bf r_0} + {\bf a}) | \Psi_\text{gs}}\right]
 \end{aligned}\end{equation}
@@
 	\label{local_correlation}
-	\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}} \simeq& \frac{1}{2\lambda_{\vec k_0}^2}\left[\frac{1}{\mathcal{W} }\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0, \vec a) \mathcal{O}_2(\vec R_0) | \psi_\text{aux}(\vec R_0)} \right.
+	\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0}) | \Psi_\text{gs}} \simeq& \frac{1}{2\lambda_{\vec k_0}^2}\left[\frac{1}{\mathcal{Z} }\sum_{{\bf a} \in \text{NN of }{\bf r_0}}\braket{\psi_\text{aux}({\bf r_0}, {\bf a}) | \mathcal{O}_1({\bf r_0}, {\bf a}) \mathcal{O}_2({\bf r_0}) | \psi_\text{aux}({\bf r_0})} \right.
 \\
-													   &+ \left.\frac{1}{\mathcal{W}^2}\sum_{\vec a \in \text{NN of }\vec R_0}\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + \vec a) | \psi_\text{aux}(\vec R_0, \vec a)}\right]\\
-	=& \frac{1}{2\lambda_{\vec k_0}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]
+													   &+ \left.\frac{1}{\mathcal{Z}^2}\sum_{{\bf a} \in \text{NN of }{\bf r_0}}\braket{\psi_\text{aux}({\bf r_0}, {\bf a}) | \mathcal{O}_1({\bf r_0} + {\bf a}) \mathcal{O}_2({\bf r_0} + {\bf a}) | \psi_\text{aux}({\bf r_0}, {\bf a})}\right]\\
+	=& \frac{1}{2\lambda_{\vec k_0}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{Z}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]
 \end{aligned}\end{equation}
@@
 	\label{nonlocal_correlation}
-	&\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) | \Psi_\text{gs}} \\
-	=& \frac{1}{4}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) + \mathcal{O}_1(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \Psi_\text{gs}}\right]\\
-	\simeq& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\psi_\text{aux}(\vec R_0, \vec a) | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a) + \mathcal{O}_1(\vec R_0 + \vec a) \mathcal{O}_2(\vec R_0 + 2\vec a) | \psi_\text{aux}(\vec R_0, \vec a)} \right.
+	&\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0} + {\bf a}) | \Psi_\text{gs}} \\
+	=& \frac{1}{4}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0} + {\bf a}) + \mathcal{O}_1({\bf r_0} + {\bf a}) \mathcal{O}_2({\bf r_0} + 2{\bf a}) + \mathcal{O}_1({\bf r_0} - {\bf a}) \mathcal{O}_2({\bf r_0}) + \mathcal{O}_1({\bf r_0} - 2{\bf a}) \mathcal{O}_2({\bf r_0} - {\bf a}) | \Psi_\text{gs}}\right]\\
+	\simeq& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{Z}}\left[\braket{\psi_\text{aux}({\bf r_0}, {\bf a}) | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0} + {\bf a}) + \mathcal{O}_1({\bf r_0} + {\bf a}) \mathcal{O}_2({\bf r_0} + 2{\bf a}) | \psi_\text{aux}({\bf r_0}, {\bf a})} \right.
 \\
-	      &\left.\braket{\psi_\text{aux}(\vec R_0, -\vec a) | \mathcal{O}_1(\vec R_0 - \vec a) \mathcal{O}_2(\vec R_0) + \mathcal{O}_1(\vec R_0 - 2\vec a) \mathcal{O}_2(\vec R_0 - \vec a) | \psi_\text{aux}(\vec R_0, -\vec a)}\right]\\
-	=& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right]
-\end{aligned}\end{equation}
-In the first equation, the first two terms were introduced to incorporate effects arising from the bath zeroth and first sites (guided by the dynamics of the transition in the underlying extended Anderson model), while the last two terms were introduced to symmetrise the effects of choosing \(\vec R_0\) as \(d\) and \(\vec R_0 + \vec a\) as \(z\), and not other way round.
+	      &\left.\braket{\psi_\text{aux}({\bf r_0}, -{\bf a}) | \mathcal{O}_1({\bf r_0} - {\bf a}) \mathcal{O}_2({\bf r_0}) + \mathcal{O}_1({\bf r_0} - 2{\bf a}) \mathcal{O}_2({\bf r_0} - {\bf a}) | \psi_\text{aux}({\bf r_0}, -{\bf a})}\right]\\
+	=& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{Z}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right]
+\end{aligned}\end{equation}
+In the first equation, the first two terms were introduced to incorporate effects arising from the bath zeroth and first sites (guided by the dynamics of the transition in the underlying extended Anderson model), while the last two terms were introduced to symmetrise the effects of choosing \({\bf r_0}\) as \(d\) and \({\bf r_0} + {\bf a}\) as \(z\), and not other way round.
 The argument \((1)\) in the operators indicate that they act at the first site of the bath (beyond the bath zeroth site).
@@
 The next-nearest correlation function is relatively simpler, because only those terms contribute that involve both the impurity as well as the first site.
-If \(\vec a^\prime\) denotes the relative vector between a given site and one of its next-nearest neighbours, we can write
+If \({\bf a}^\prime\) denotes the relative vector between a given site and one of its next-nearest neighbours, we can write
 \begin{equation}\begin{aligned}
 	\label{nnn_correlation}
-	\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) | \Psi_\text{gs}} =& \frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1(\vec R_0) \mathcal{O}_2(\vec R_0 + \vec a^\prime) + \mathcal{O}_1(\vec R_0 - \vec a^\prime) \mathcal{O}_2(\vec R_0) | \Psi_\text{gs}}\right]\\
-	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
+	\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0} + {\bf a}^\prime) | \Psi_\text{gs}} =& \frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0} + {\bf a}^\prime) + \mathcal{O}_1({\bf r_0} - {\bf a}^\prime) \mathcal{O}_2({\bf r_0}) | \Psi_\text{gs}}\right]\\
+	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{Z}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) = \frac{1}{N \mathcal{W}}\sum_{\vec r, \vec R}e^{i \vec{k}\cdot\left(\vec r + \vec R\right)}G_{H-H} (\vec r + \vec R, \omega)
-\end{aligned}\end{equation}
-where $\vec R$ sums over all lattice sites and \(\vec r\) sums over all nearest-neighbours of that site, such that \(\vec R + \vec r\) sums over all possible real space Greens functions.
-The distance \(\vec r + \vec R\) has been measured with respect to some chosen central lattice site.
+	G_{H-H} (\vec k, \omega) = \frac{1}{N \mathcal{Z}}\sum_{{\bf r}, {\bf r}}e^{i \vec{k}\cdot\left({\bf r} + {\bf r}\right)}G_{H-H} ({\bf r} + {\bf r}, \omega)
+\end{aligned}\end{equation}
+where ${\bf r}$ sums over all lattice sites and \({\bf r}\) sums over all nearest-neighbours of that site, such that \({\bf r} + {\bf r}\) sums over all possible real space Greens functions.
+The distance \({\bf r} + {\bf r}\) has been measured with respect to some chosen central lattice site.
 Because of translation invariance, the real space Greens function depends only on the relative vector between two sites.
-As a result, $\vec r + \vec R = 0$ gives the local Greens function, $|\vec r + \vec R|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
+As a result, ${\bf r} + {\bf r} = 0$ gives the local Greens function, $|{\bf r} + {\bf r}|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
 Given that our auxiliary model shows an emergent self-consistency on the impurity site and on the link between the impurity and the zeroth site, we approximate the \(k-\)space Greens functions from the local and nearest-neighbour contributions:
 \begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) &= \frac{1}{N \mathcal{W}}\sum_{\vec r, \vec R}\left[e^{i \vec{k}\cdot\left(\vec r + \vec R\right)}G_{H-H} (\vec r + \vec R, \omega) - G_\text{H-H}(0,\omega) - e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}(\vec r,\omega) + G_\text{H-H}(0,\omega) + e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}(\vec r,\omega)\right]\\
-				 &= G_\text{H-H}(0,\omega) + \sum_r e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}(\vec r,\omega) + \frac{1}{N \mathcal{W}}\sum_{\vec r, \vec R}\left[e^{i \vec{k}\cdot\left(\vec r + \vec R\right)}G_{H-H} (\vec r + \vec R, \omega) - G_\text{H-H}(0,\omega) - e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}(\vec r,\omega)\right]
+	G_{H-H} (\vec k, \omega) &= \frac{1}{N \mathcal{Z}}\sum_{{\bf r}, {\bf r}}\left[e^{i \vec{k}\cdot\left({\bf r} + {\bf r}\right)}G_{H-H} ({\bf r} + {\bf r}, \omega) - G_\text{H-H}(0,\omega) - e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}({\bf r},\omega) + G_\text{H-H}(0,\omega) + e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}({\bf r},\omega)\right]\\
+				 &= G_\text{H-H}(0,\omega) + \sum_r e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}({\bf r},\omega) + \frac{1}{N \mathcal{Z}}\sum_{{\bf r}, {\bf r}}\left[e^{i \vec{k}\cdot\left({\bf r} + {\bf r}\right)}G_{H-H} ({\bf r} + {\bf r}, \omega) - G_\text{H-H}(0,\omega) - e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}({\bf r},\omega)\right]
 \label{auxGreen}
@@
 The difference term in the square brackets is smaller than the sum outside, so we drop the former.
-We identify the first term \(G_\text{H-H}(0,\omega)\) as the local Greens function \(G_\text{loc}\) and those inside the second term, \(G_\text{H-H}(\vec r, \omega)\) as the nearest neighbour Greens function \(G_\text{near-n}\) (assuming symmetry under rotation by \(\pi/2\)).
-The second sum is over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ \vec a_i: i \in \left[1, \mathcal{W}\right]\right\}$.
+We identify the first term \(G_\text{H-H}(0,\omega)\) as the local Greens function \(G_\text{loc}\) and those inside the second term, \(G_\text{H-H}({\bf r}, \omega)\) as the nearest neighbour Greens function \(G_\text{near-n}\) (assuming symmetry under rotation by \(\pi/2\)).
+The second sum is over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ {\bf a}_i: i \in \left[1, \mathcal{Z}\right]\right\}$.
 Combining all this and by using the mappings to the auxiliary model (eqs.~\ref{greens_func_relation} and \ref{greens_func_approx}), we get
@@
 	\label{k_Gf_siam}
-	G_{H-H} (\vec k, \omega) &\simeq G_\text{loc}(\omega) + G_\text{near-n}(\omega)\sum_{i=1}^{\mathcal{W}} e^{i \vec{k}\cdot\vec {a_i}} = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{G}_{dd}(\omega) + \frac{1}{\mathcal{W}}\xi_{\vec k}\mathcal{G}_{dz}(\omega) \right]~,
+	G_{H-H} (\vec k, \omega) &\simeq G_\text{loc}(\omega) + G_\text{near-n}(\omega)\sum_{i=1}^{\mathcal{Z}} e^{i \vec{k}\cdot\vec {a_i}} = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{G}_{dd}(\omega) + \frac{1}{\mathcal{Z}}\xi_{\vec k}\mathcal{G}_{dz}(\omega) \right]~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	A_\text{loc}(\omega) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{A}_{dd}~,\qquad A_\text{near-n}(\omega) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{A}_{dz}~,\qquad A_\text{H-H}(\vec{k},\omega) = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{A}_{dd} + \frac{1}{\mathcal{W}}\xi_{\vec k}\mathcal{A}_{dz} \right]~,
+	A_\text{loc}(\omega) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{A}_{dd}~,\qquad A_\text{near-n}(\omega) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{A}_{dz}~,\qquad A_\text{H-H}(\vec{k},\omega) = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{A}_{dd} + \frac{1}{\mathcal{Z}}\xi_{\vec k}\mathcal{A}_{dz} \right]~,
 \end{aligned}\end{equation}
@@
 	\label{selfenergy1}
-	\Sigma_{H-H}(\vec k,\omega) = 1/\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)} - 1/\left(G_{H-H}(\omega)\right)_{\vec k} = \frac{\left(\lambda_{\vec k_0}^{(0)}\right)^2}{\mathcal{G}^{(0)}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{W}}\mathcal{G}^{(0)}_{dz}(\omega)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{W}}\mathcal{G}_{dz}(\omega)}~,
+	\Sigma_{H-H}(\vec k,\omega) = 1/\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)} - 1/\left(G_{H-H}(\omega)\right)_{\vec k} = \frac{\left(\lambda_{\vec k_0}^{(0)}\right)^2}{\mathcal{G}^{(0)}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{Z}}\mathcal{G}^{(0)}_{dz}(\omega)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{Z}}\mathcal{G}_{dz}(\omega)}~,
 \end{aligned}\end{equation}
@@
 
-By expanding in terms of the small parameter $\frac{\lambda_{\vec k_0}^2}{\mathcal{W}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}}$, this expression for $\Sigma_{H-H}(\vec k,\omega)$ can be recast in the following form:
+By expanding in terms of the small parameter $\frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}}$, this expression for $\Sigma_{H-H}(\vec k,\omega)$ can be recast in the following form:
 \begin{equation}\begin{aligned}
@@
 \Sigma_\text{loc}(\omega) &=& \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^{(0)}} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}}~,\\ 
-\tilde{\Sigma}(\vec k, \omega)&=&\xi_{\vec k}\Sigma_\text{near-n}~,~\Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{W}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}^2}~.
+\tilde{\Sigma}(\vec k, \omega)&=&\xi_{\vec k}\Sigma_\text{near-n}~,~\Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}^2}~.
 \end{eqnarray}
@@
 Similar to Greens functions, our formalism also allows calculating \(k-\)space correlation functions \(\chi(\vec q)\) from knowledge of local and nearest-neighbour correlations \(\chi_\text{loc}\) and \(\chi_\text{nn}\).
-This is seen by Fourier transforming a generic real-space correlation function \(\chi(\vec r)\) corresponding to the operator \(\mathcal{O}\):
-\begin{equation}\begin{aligned}
-	\chi(\vec r) = \left<\mathcal{O}_1 (\vec R + \vec r) \mathcal{O}_2(\vec R)\right> = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right>
-\end{aligned}\end{equation}
-Since the response should not depend on \(\vec R\) (owing to translation invariance), we have
-\begin{equation}\begin{aligned}
-	\chi(\vec r) = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot \vec r}e^{i \left(\vec k + \vec q\right) \cdot \vec R}\delta_{\vec k + \vec q, 0}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right> = \frac{1}{N}\sum_{\vec k} e^{-i \vec k \cdot \vec r}\left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right>
+This is seen by Fourier transforming a generic real-space correlation function \(\chi({\bf r})\) corresponding to the operator \(\mathcal{O}\):
+\begin{equation}\begin{aligned}
+	\chi({\bf r}) = \left<\mathcal{O}_1 ({\bf r} + {\bf r}) \mathcal{O}_2({\bf r})\right> = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot {\bf r}}e^{i \left(\vec k + \vec q\right) \cdot {\bf r}}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right>
+\end{aligned}\end{equation}
+Since the response should not depend on \({\bf r}\) (owing to translation invariance), we have
+\begin{equation}\begin{aligned}
+	\chi({\bf r}) = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot {\bf r}}e^{i \left(\vec k + \vec q\right) \cdot {\bf r}}\delta_{\vec k + \vec q, 0}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right> = \frac{1}{N}\sum_{\vec k} e^{-i \vec k \cdot {\bf r}}\left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right>
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\chi(\vec k) &\equiv \left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right> = \sum_{\vec r}e^{i \vec{k}\cdot\vec{r}} \chi(\vec r) \simeq \chi_\text{loc} + \xi_{\vec k} \chi_\text{nn} + \Xi_{\vec k}\chi_\text{nnn}~,
+	\chi(\vec k) &\equiv \left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right> = \sum_{{\bf r}}e^{i \vec{k}\cdot\vec{r}} \chi({\bf r}) \simeq \chi_\text{loc} + \xi_{\vec k} \chi_\text{nn} + \Xi_{\vec k}\chi_\text{nnn}~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\chi(\vec k)=& \frac{1}{2\lambda_{\vec k_0}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{W}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]\\
-		    &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right] \\
-		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{W}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
+	\chi(\vec k)=& \frac{1}{2\lambda_{\vec k_0}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{Z}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]\\
+		    &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{Z}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right] \\
+		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{Z}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
 \end{aligned}\end{equation}
@@
 
-We will now Fourier transform the reduced matrix from the definition in eq.~\ref{red_matrix_projection}, and retain terms up to the nearest neighbour, by expanding \(c_{\vec k\sigma}\) as \(c_{\vec R_0,\sigma} + \xi_{\vec k}c_{\vec R_0 + \vec a,\sigma}\), where \(\vec a\) is the nearest neighbour site to \(\vec R_0\), and \(\xi_{\vec k}\) has been defined above.
-\begin{equation}\begin{aligned}
-	\hat n_{\vec k\sigma}\ket{\Psi_\text{gs}} \to  \left[ \hat n_{\vec R_0,\sigma} + \sum_{\vec a} \hat n_{\vec R_0 + \vec a,\sigma} + \sum_{\vec a}\left( e^{i \vec{k}\cdot\vec{a}}c^\dagger_{\vec R_0,\sigma}c_{\vec R_0 + \vec a,\sigma} + \text{h.c.} \right) \right]\ket{\Psi_\text{gs}}
-\end{aligned}\end{equation}
-We also expand the ground state wavefunction: \(\ket{\Psi}_\text{gs} \simeq \ket{\psi_\text{aux}} = \frac{1}{\sqrt \mathcal{W}}\sum_{\vec a \in \text{NN of }\vec R_0}\ket{\psi_\text{aux}(\vec R_0,\vec a)}\), so that we get
-\begin{equation}\begin{aligned}
-	\hat n_{\vec k\sigma}\ket{\Psi_\text{gs}} &= \frac{1}{\sqrt \mathcal{W}}\left[ \hat n_{\vec R_0,\sigma} \sum_{\vec a}\ket{\psi_\text{aux}(\vec R_0,\vec a)} + \sum_{\vec a} \hat n_{\vec R_0 + \vec a,\sigma}\ket{\psi_\text{aux}(\vec R_0,\vec a)} + \sum_{\vec a}\left( e^{i \vec{k}\cdot\vec{a}}c^\dagger_{\vec R_0,\sigma}c_{\vec R_0 + \vec a,\sigma} + \text{h.c.} \right) \ket{\psi_\text{aux}(\vec R_0,\vec a)}\right]\\
-						  &=\hat n_{d,\sigma} \ket{\psi_\text{aux}} + \hat n_{z,\sigma}\ket{\psi_\text{aux}} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right) \ket{\psi_\text{aux}}
+We will now Fourier transform the reduced matrix from the definition in eq.~\ref{red_matrix_projection}, and retain terms up to the nearest neighbour, by expanding \(c_{\vec k\sigma}\) as \(c_{{\bf r_0},\sigma} + \xi_{\vec k}c_{{\bf r_0} + {\bf a},\sigma}\), where \({\bf a}\) is the nearest neighbour site to \({\bf r_0}\), and \(\xi_{\vec k}\) has been defined above.
+\begin{equation}\begin{aligned}
+	\hat n_{\vec k\sigma}\ket{\Psi_\text{gs}} \to  \left[ \hat n_{{\bf r_0},\sigma} + \sum_{{\bf a}} \hat n_{{\bf r_0} + {\bf a},\sigma} + \sum_{{\bf a}}\left( e^{i \vec{k}\cdot\vec{a}}c^\dagger_{{\bf r_0},\sigma}c_{{\bf r_0} + {\bf a},\sigma} + \text{h.c.} \right) \right]\ket{\Psi_\text{gs}}
+\end{aligned}\end{equation}
+We also expand the ground state wavefunction: \(\ket{\Psi}_\text{gs} \simeq \ket{\psi_\text{aux}} = \frac{1}{\sqrt \mathcal{Z}}\sum_{{\bf a} \in \text{NN of }{\bf r_0}}\ket{\psi_\text{aux}({\bf r_0},{\bf a})}\), so that we get
+\begin{equation}\begin{aligned}
+	\hat n_{\vec k\sigma}\ket{\Psi_\text{gs}} &= \frac{1}{\sqrt \mathcal{Z}}\left[ \hat n_{{\bf r_0},\sigma} \sum_{{\bf a}}\ket{\psi_\text{aux}({\bf r_0},{\bf a})} + \sum_{{\bf a}} \hat n_{{\bf r_0} + {\bf a},\sigma}\ket{\psi_\text{aux}({\bf r_0},{\bf a})} + \sum_{{\bf a}}\left( e^{i \vec{k}\cdot\vec{a}}c^\dagger_{{\bf r_0},\sigma}c_{{\bf r_0} + {\bf a},\sigma} + \text{h.c.} \right) \ket{\psi_\text{aux}({\bf r_0},{\bf a})}\right]\\
+						  &=\hat n_{d,\sigma} \ket{\psi_\text{aux}} + \hat n_{z,\sigma}\ket{\psi_\text{aux}} + \frac{\xi_{\vec k}}{\sqrt \mathcal{Z}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right) \ket{\psi_\text{aux}}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\rho_{\vec k\sigma} \simeq& \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_\text{aux} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]\\
-				  &+ \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right] \rho_\text{aux} \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right]\label{density_matrix_kspace}
+	\rho_{\vec k\sigma} \simeq& \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{Z}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_\text{aux} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{Z}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]\\
+				  &+ \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{Z}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right] \rho_\text{aux} \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{Z}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right]\label{density_matrix_kspace}
 \end{aligned}\end{equation}
@@
 	=& \hat n_{\vec q\sigma}\rho_{\vec k\sigma}\hat n_{\vec q\sigma} + \hat h_{\vec q\sigma}\rho_{\vec k\sigma}\hat h_{\vec q\sigma}\\
-	=& \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]\\
-				  &+ \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right]
+	=& \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{Z}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{Z}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]\\
+				  &+ \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{Z}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{Z}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right]
 \end{aligned}\end{equation}
@@
 	\begin{bmatrix} \Sigma_{dd}(\omega) && \Sigma_{dz}(\omega) \\ \Sigma_{dz}(\omega) && \Sigma_{dd}(\omega)\end{bmatrix} &= 1/\mathcal{G}^{(0)} - \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2}\begin{bmatrix} \mathcal{G}_{dd} && -\mathcal{G}_{dz} \\ -\mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}~,\\
-	\begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} &= 1/G^{(0)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{W}^2}\begin{bmatrix} \mathcal{G}_{dd} && -\frac{1}{\mathcal{W}}\mathcal{G}_{dz} \\ -\frac{1}{\mathcal{W}}\mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}~.
+	\begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} &= 1/G^{(0)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{Z}^2}\begin{bmatrix} \mathcal{G}_{dd} && -\frac{1}{\mathcal{Z}}\mathcal{G}_{dz} \\ -\frac{1}{\mathcal{Z}}\mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Sigma_{dz} = \left(1/\mathcal{G}^{(0)}\right)_{dz} + \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2} \mathcal{G}_{dz},\quad \Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{W}}\frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{W}^2} \mathcal{G}_{dz}
+	\Sigma_{dz} = \left(1/\mathcal{G}^{(0)}\right)_{dz} + \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2} \mathcal{G}_{dz},\quad \Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{Z}^2} \mathcal{G}_{dz}
 \end{aligned}\end{equation}
@@
 %, because the non-interacting Greens function has well-defined poles which kill the first term. 
-Importantly, we note that the second term in the expression for \(\Sigma_\text{near-n}\) is very similar to the diverging term in \(\Sigma_{dz}\), differing only through the presence of some finite (i.e., non-divergent) non-zero factors of \(\lambda_{\vec k_0}^2\) and \(\mathcal{W}\).
+Importantly, we note that the second term in the expression for \(\Sigma_\text{near-n}\) is very similar to the diverging term in \(\Sigma_{dz}\), differing only through the presence of some finite (i.e., non-divergent) non-zero factors of \(\lambda_{\vec k_0}^2\) and \(\mathcal{Z}\).
 We therefore conclude that the non-local self-energy of the lattice model $\Sigma_\text{near-n}$ contains the same power-law divergence  as $\Sigma_{dz}$ upon taking the limit $\omega\to 0$:
@@
 \section{Analytic consistency check - On the Bethe lattice}
-We now apply our approach to the case of infinite number of nearest-neighbours $\mathcal{W}\to\infty$ (the coordination number, and effectively the dimension), where the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{\mathcal{W}}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that DMFT obtains a metal-insulator transition in that limit~\cite{georges1996}.
+We now apply our approach to the case of infinite number of nearest-neighbours $\mathcal{Z}\to\infty$ (the coordination number, and effectively the dimension), where the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{\mathcal{Z}}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that DMFT obtains a metal-insulator transition in that limit~\cite{georges1996}.
 It is well known from the works of Müller-Hartmann as well as Metzner and Vollhardt that self-energy arising from the correlations loses all momentum-dependence and becomes purely local~\cite{Muller-Hartmann1989,metzner_volhardt_1989}.
@@
 This simplification is also explicit in our formalism, as can be seen in the expression of the Self-energy (eq.~\eqref{selfenergy1}).
-Upon taking the limit of \(\mathcal{W}\to\infty\), the non-local terms drop out:
-\begin{equation}\begin{aligned}
-	\lim_{\mathcal{W}\to\infty}\Sigma_{H-H}(\vec k,\omega) = \frac{\left(\lambda_{\vec k_0}^{(0)}\right)^2}{\mathcal{G}^{(0)}_{dd}(\omega)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega)} = \Sigma_\text{loc}(\omega)~,
+Upon taking the limit of \(\mathcal{Z}\to\infty\), the non-local terms drop out:
+\begin{equation}\begin{aligned}
+	\lim_{\mathcal{Z}\to\infty}\Sigma_{H-H}(\vec k,\omega) = \frac{\left(\lambda_{\vec k_0}^{(0)}\right)^2}{\mathcal{G}^{(0)}_{dd}(\omega)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega)} = \Sigma_\text{loc}(\omega)~,
 \end{aligned}\end{equation}
@@
  \begin{equation}\begin{aligned}
-	 \left(i\partial_t - H(\vec r)\right)G(\vec r,\vec r^\prime, t) = \delta(\vec r - \vec r^\prime)
+	 \left(i\partial_t - H({\bf r})\right)G({\bf r},{\bf r}^\prime, t) = \delta({\bf r} - {\bf r}^\prime)
  \end{aligned}\end{equation}
@@
  \begin{equation}\begin{aligned}
-	 G(\vec r,\vec r^\prime, t) = -i \theta(t) \left< \left\{ c(\vec r, t) c^\dagger(\vec r^\prime, 0)\right\} \right>
+	 G({\bf r},{\bf r}^\prime, t) = -i \theta(t) \left< \left\{ c({\bf r}, t) c^\dagger({\bf r}^\prime, 0)\right\} \right>
  \end{aligned}\end{equation}
@@
  \begin{equation}\begin{aligned}
-	 G(\vec r \sigma, \vec r^\prime \sigma, \omega) = \sum_{n}\left[\frac{\bra{GS}c({\vec r,\sigma})\ket{n}\bra{n}c^\dagger(\vec r^\prime,\sigma)\ket{GS}}{\omega + E_{GS} - E_n} + \frac{\bra{GS}c^\dagger(\vec r^\prime,\sigma)\ket{n}\bra{n}c({\vec r,\sigma})\ket{GS}}{\omega + E_n - E_{GS}}\right]
- \end{aligned}\end{equation}
- The sum is over the exact eigenstates of the Hamiltonian. In what follows, we will represent $\vec r,\sigma \equiv \nu$ and $\vec r^\prime,\sigma \equiv \nu^\prime$.
+	 G({\bf r} \sigma, {\bf r}^\prime \sigma, \omega) = \sum_{n}\left[\frac{\bra{GS}c({{\bf r},\sigma})\ket{n}\bra{n}c^\dagger({\bf r}^\prime,\sigma)\ket{GS}}{\omega + E_{GS} - E_n} + \frac{\bra{GS}c^\dagger({\bf r}^\prime,\sigma)\ket{n}\bra{n}c({{\bf r},\sigma})\ket{GS}}{\omega + E_n - E_{GS}}\right]
+ \end{aligned}\end{equation}
+ The sum is over the exact eigenstates of the Hamiltonian. In what follows, we will represent ${\bf r},\sigma \equiv \nu$ and ${\bf r}^\prime,\sigma \equiv \nu^\prime$.
  \begin{equation}\begin{aligned}
@@
 \subsection{Translation invariance}
-It is easy to verify that \(\Psi_{\vec k}\left(\left\{ \vec r_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \(\vec R\):
-\begin{equation}\begin{aligned}
-	\Psi_{\vec k}\left(\left\{\vec r_k + \vec R\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i,\vec a} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left(\vec R_i - \vec R, \vec a\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_j, \vec a} e^{i \vec{k}\cdot\left(\vec{R}_j + \vec R\right)} \psi_\text{aux}\left(\vec R_j, \vec a\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ \vec r_k \right\} \right)
-\end{aligned}\end{equation}
-In the last equation, we transformed \(\vec R_i \to \vec R_j = \vec R_i - \vec R\).
-Note that the argument \(\vec a\) does not change under a translation of the system, because that vector always represents the difference between the impurity lattice position and its nearest neighbours, irrespective of the absolute position of the impurity.
+It is easy to verify that \(\Psi_{\vec k}\left(\left\{ {\bf r}_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \({\bf r}\):
+\begin{equation}\begin{aligned}
+	\Psi_{\vec k}\left(\left\{{\bf r}_k + {\bf r}\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i,{\bf a}} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left({\bf r}_i - {\bf r}, {\bf a}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_j, {\bf a}} e^{i \vec{k}\cdot\left(\vec{R}_j + {\bf r}\right)} \psi_\text{aux}\left({\bf r}_j, {\bf a}\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ {\bf r}_k \right\} \right)
+\end{aligned}\end{equation}
+In the last equation, we transformed \({\bf r}_i \to {\bf r}_j = {\bf r}_i - {\bf r}\).
+Note that the argument \({\bf a}\) does not change under a translation of the system, because that vector always represents the difference between the impurity lattice position and its nearest neighbours, irrespective of the absolute position of the impurity.
 
@@
 \begin{equation}\begin{aligned}
-	\Psi^n_{\vec k}\left(\left\{\vec r_k\right\}\right) = \sum_{\vec R_i, \vec a} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} \mathcal{W} N} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i, \vec a} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ \vec r_d - \vec R_i, \vec r_0 - \vec R_i - \vec a \right\} \right) \\
-	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{\vec r_k\right\}\right)
-\end{aligned}\end{equation}
-where \(\vec r_\text{COM} = \frac{1}{N}\sum_k \vec r_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{\vec r_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{W} N}\sum_{\vec R_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k\vec r_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{\vec r_k - \vec R_i\right\}\right)\) is the translation symmetric function.
+	\Psi^n_{\vec k}\left(\left\{{\bf r}_k\right\}\right) = \sum_{{\bf r}_i, {\bf a}} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} \mathcal{Z} N} \psi_\text{aux}\left(\left\{ {\bf r}_d - {\bf r}_i, {\bf r_0} - {\bf r}_i - {\bf a} \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i, {\bf a}} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k{\bf r}_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ {\bf r}_d - {\bf r}_i, {\bf r_0} - {\bf r}_i - {\bf a} \right\} \right) \\
+	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{{\bf r}_k\right\}\right)
+\end{aligned}\end{equation}
+where \({\bf r}_\text{COM} = \frac{1}{N}\sum_k {\bf r}_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{{\bf r}_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k{\bf r}_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{{\bf r}_k - {\bf r}_i\right\}\right)\) is the translation symmetric function.
 This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
@@
 	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
-	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_j, \vec a^\prime \right) | \psi_\text{aux}\left( \vec R_i, \vec a \right)} \\
-	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T^\dagger\left( \vec R_0 - \vec R_j \right) T\left( \vec R_0 - \vec R_i \right) | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r}_j, {\bf a}^\prime \right) | \psi_\text{aux}\left( {\bf r}_i, {\bf a} \right)} \\
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) T^\dagger\left( {\bf r_0} - {\bf r}_j \right) T\left( {\bf r_0} - {\bf r}_i \right) | \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) T\left( \vec R_j - \vec R_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec a, \vec a^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) e^{i \vec q \cdot \left( \vec R_j - \vec R_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( \vec R_0, \vec a \right)} \\
-						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2} \delta_{\vec k, \vec k^\prime}\sum_{\vec a, \vec a^\prime}\braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
-\end{aligned}\end{equation}
-At the last step, we used the summation form of the Kronecker delta function: \(\sum_{\vec R_i}e^{i \vec R_i \left( \vec k - \vec q \right) }\sum_{\vec R_j}e^{i \vec R_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\).
-The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \(\vec a, \vec a^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\ket{\vec k}}\):
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2 } \delta_{\vec k, \vec k^\prime}\sum_{\vec a,\vec a^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) T\left( {\bf r}_j - {\bf r}_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
+						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) e^{i \vec q \cdot \left( {\bf r}_j - {\bf r}_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)} \\
+						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2} \delta_{\vec k, \vec k^\prime}\sum_{{\bf a}, {\bf a}^\prime}\braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
+\end{aligned}\end{equation}
+At the last step, we used the summation form of the Kronecker delta function: \(\sum_{{\bf r}_i}e^{i {\bf r}_i \left( \vec k - \vec q \right) }\sum_{{\bf r}_j}e^{i {\bf r}_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\).
+The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \({\bf a}, {\bf a}^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\ket{\vec k}}\):
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2 } \delta_{\vec k, \vec k^\prime}\sum_{{\bf a},{\bf a}^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_j, \vec a^\prime\right)} H_\text{aux}\left(\vec R_k\right) \ket{\psi_\text{aux}\left(\vec R_i, \vec a\right)}\\
-	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_0 - \vec R_j} T_{\vec R_0 - \vec R_k} H_\text{aux}\left(\vec R_0\right) T^\dagger_{\vec R_0 - \vec R_k} T_{\vec R_0 - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_k, \vec a, \vec a^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i} \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}
+	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r}_j, {\bf a}^\prime\right)} H_\text{aux}\left({\bf r}_k\right) \ket{\psi_\text{aux}\left({\bf r}_i, {\bf a}\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)} T^\dagger_{{\bf r_0} - {\bf r}_j} T_{{\bf r_0} - {\bf r}_k} H_\text{aux}\left({\bf r_0}\right) T^\dagger_{{\bf r_0} - {\bf r}_k} T_{{\bf r_0} - {\bf r}_i} \ket{\psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)} T^\dagger_{{\bf r}_k - {\bf r}_j} H_\text{aux}\left({\bf r_0}\right) T_{{\bf r}_k - {\bf r}_i} \ket{\psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{\vec R_k - \vec R_j} H_\text{aux}\left(\vec R_0\right) T_{\vec R_k - \vec R_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \sum_{\vec R_i, \vec R_j, \vec R_k, \atop{\vec a, \vec a^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2 N^2} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left(\vec R_k - \vec R_j\right) } e^{i \vec q \cdot \left(\vec R_k - \vec R_i\right)} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{W}^2}\sum_{\vec a, \vec a^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left(\vec R_0\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2}\delta_{kk^\prime}\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}\\
-								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{W}^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k} \underbrace{\sum_{\vec a, \vec a^\prime} \braket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left(\vec R_0, \vec a\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
-	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left(\vec R_0\right) | \vec k}
-\end{aligned}\end{equation}
-The momentum eigenket \(\ket{\vec k}\) can be expressed as a sum over position eigenkets at varying distances from \(\vec R_0\).
+	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, \atop{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{{\bf r}_k - {\bf r}_j} H_\text{aux}\left({\bf r_0}\right) T_{{\bf r}_k - {\bf r}_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+								   &= \sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, \atop{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left({\bf r}_k - {\bf r}_j\right) } e^{i \vec q \cdot \left({\bf r}_k - {\bf r}_i\right)} \braket{\vec q^\prime | H_\text{aux}\left({\bf r_0}\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2}\sum_{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left({\bf r_0}\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2}\delta_{kk^\prime}\sum_{{\bf a}, {\bf a}^\prime} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k} \underbrace{\sum_{{\bf a}, {\bf a}^\prime} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
+	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k}
+\end{aligned}\end{equation}
+The momentum eigenket \(\ket{\vec k}\) can be expressed as a sum over position eigenkets at varying distances from \({\bf r_0}\).
 This form allows a systematic method of improving the energy eigenvalue estimate, because the interacting in the impurity model is extremely localised, so the overlap between two auxiliary models decreases rapidly with distance.
-The majority of the contribution will come from the state at \(\vec R_0\), and improvements are then made by considering auxiliary models at further distances.
+The majority of the contribution will come from the state at \({\bf r_0}\), and improvements are then made by considering auxiliary models at further distances.
 

### 2024-03-17 TilingProjectDraft/tilingProject.tex
--no-message

@@
 The Hubbard model is one of the fundamental models for strong electronic correlation; in its simplest form, it features a single band of conduction electrons hopping on a lattice and interacting via local correlations that provide a cost \(U\) if any site is doubly occupied:
-\[H_\text{hubb} = -t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}+\text{h.c.}\right) + U\sum_i \hat n_{i \uparrow} \hat n_{i \downarrow} - \mu \sum_{i,\sigma}\hat n_{i\sigma}\]
+\begin{equation}\begin{aligned}
+	H_\text{hubb} = -t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}+\text{h.c.}\right) + U\sum_i \hat n_{i \uparrow} \hat n_{i \downarrow} - \mu \sum_{i,\sigma}\hat n_{i\sigma}~.
+\end{aligned}\end{equation}
 The model can be made particle-hole symmetric by choosing \(\mu = U/2\):
@@
 In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout.
-In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}_1\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z}_1)\).
-The subscript \(1\) indicates that \({\bf z}_1\) is the first zeroth site, and that there can be multiple such zeroth sites \(\left\{ {\bf z}_i \right\} \), depending on the lattice geometry.
+In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})\).
 The unit cell at the position \({\bf r}_d\) is then obtained by placing the zeroth site on all nearest-neighbours of \({\bf r}_d\) and averaging over these configurations:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}({\bf r}_d) = \frac{1}{\mathcal{Z}}\sum_{{\bf z}_1\in\text{NN}({\bf r}_d)}\mathcal{H}_\text{aux}({\bf r}_d, {\bf z}_1)~,
-\end{aligned}\end{equation}
-where \({\bf z}_1\) is summed over all nearest-neighbours of \({\bf r}_d\) and \(\mathcal{Z}\) is the number of such nearest-neighbours.
+\begin{equation}\begin{aligned}\label{unitCellHamiltonian}
+	\mathcal{H}_\text{aux}({\bf r}_d) = \frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})~,
+\end{aligned}\end{equation}
+where \({\bf z}\) is summed over all nearest-neighbours of \({\bf r}_d\) and \(\mathcal{Z}\) is the number of such nearest-neighbours.
 
@@
 In terms of manybody states and operators, their action is defined as
-\begin{equation}\begin{aligned}
+\begin{equation}\begin{aligned}\label{translationDefinition}
 	T^\dagger({\bf a}) \ket{\bf r_1, \bf r_2,\ldots} &= \ket{\bf r_1 + a, \bf r_2 + a,\ldots}\\
@@
 	\label{tilingPrescription}
-	\mathcal{H}_\text{full} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})\\
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})\\
 				&= \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r} - {\bf r}_d)~ \\
-				&= \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}_1\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d, {\bf z}_1)T({\bf r} - {\bf r}_d)~ \\
+				&= \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d)~ \\
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
-where \(\mathcal{H}_\text{cbath} = -t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the mostly non-interacting conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site, \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 + V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath.
+where \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the mostly non-interacting conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site, \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 - V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath.
 Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath.
@@
 
-\subsection{Tiling towards a Hubbard-Heisenberg model}
+\subsection{Tiling towards a Hubbard-Heisenberg model with an s-wave impurity model}
 In this subsection, we provide an explicit example of constructing a lattice model.
-We will consider a slightly more generalised version of the extended SIAM described in the previous section, and show that that model leads to a form of a Hubbard-Heisenberg model upon restoring translation invariance via repeated translation operations.
-In order to generalise the extended SIAM, we make the following changes.
-We allow the possibility of multiple zeroth sites (bath sites that harbour local interaction) \({\bf z}_i\).
-This can lead to various kinds of interactions with the impurity site, as well as purely on the zeroth sites.
-We allow the conduction bath to reside in a lattice of arbitrary geometry:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{cbath} = -t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
-	- \frac{1}{2  Z}\sum_{{\bf z}_i \in \text{NN}({\bf r}_d)}U_b({\bf z}_i)\left(\hat n_{{\bf z}_i, \uparrow} - \hat n_{{\bf z}_i, \downarrow}\right)^2~,
-\end{aligned}\end{equation}
-where \(\left<{\bf r}_i, {\bf r}_j\right>\neq {\bf r}_d\) indicates that the sum is over all nearest-neighbour pairs of sites avoiding the impurity site \({\bf r}_d\), and \({\bf z}_i={\bf z}_1, {\bf z}_2, \ldots\) is summed over all the bath zeroth sites (\(Z\) in number).
-Note that the auxiliary coordination number \(Z\) can in general be different from the lattice model coordination number \(\mathcal{Z}\).
-We also allow the impurity site \({\bf r}_d\) to have arbitrary filling, by introducing an assymetry parameter \(\eta\) which quantifies the amount of doping:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{imp} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 + \eta\sum_\sigma \hat n_{{\bf r}_d\sigma}~.
-\end{aligned}\end{equation}
-The interaction Hamiltonian can also be generalised to:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{imp-cbath} &= \sum_{{\bf z}_i,{\bf z}_j}\sum_{\alpha,\alpha^\prime}\frac{1}{ Z}J({\bf z}_i - {\bf z}_j) {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \sigma}_{\alpha,\alpha^\prime}c^\dagger_{{\bf z}_i,\alpha}c_{{\bf z}_j,\alpha^\prime} \\
-				     &+  \sum_{\sigma, {\bf z}_i} \frac{1}{\sqrt Z}V\left({\bf r}_d - {\bf z}_i\right) \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}_i}\sigma} + h.c.\right)
-\end{aligned}\end{equation}
-where \({\bf z}_i\) and \({\bf z}_j\) sum over the bath zeroth sites of the impurity model, and \(\boldsymbol \sigma\) is the vector of Pauli matrices.% The bath zeroth sites, being locally connected to the impurity, typically reside on the sites that are nearest to the impurity.
-This means that we can write \({\bf r}_0 = {\bf r}_d + {\bf a}\), where \({\bf a}\) is a primitive lattice vector that connects \({\bf r}_d\) with its nearest neighbours.
+We will consider a slightly more generalised version of the extended SIAM described in the previous section, where the impurity site couples to the conduction bath purely through the s-wave channel.
+We will show that that model leads to a form of a Hubbard-Heisenberg model upon restoring translation invariance via repeated translation operations.
+The generalisation involve allowing an arbitrary filling on the impurity site and in the conduction bath, through two additional parameter: (i) a particle-hole assymetry parameter \(\eta\) for the impurity site, and (ii) a chemical potential for the conduction bath.
+The first term modifies the impurity Hamiltonian \(\mathcal{H}_\text{imp}\) into
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{imp} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 - \eta\sum_\sigma \hat n_{{\bf r}_d\sigma}~.
+\end{aligned}\end{equation}
+where we have placed the impurity site at the position \({\bf r}_d\). The second term modifies the conduction bath Hamiltonian \(\mathcal{H}_\text{cbath}\):
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
+	- \frac{1}{2}U_b\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
+\end{aligned}\end{equation}
+where \(\left<{\bf r}_i, {\bf r}_j\right>\neq {\bf r}_d\) indicates that the sum is over all nearest-neighbour pairs of sites avoiding the impurity site \({\bf r}_d\).
+
+In this notation, the interaction Hamiltonian can be written as
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{imp-cbath} &= \sum_{\sigma,\sigma^\prime}\frac{1}{ Z}J {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \\
+				     &-  \sum_{\sigma} V \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)
+\end{aligned}\end{equation}
+where \(\boldsymbol \tau = \left( \tau_x, \tau_y, \tau_z \right) \) is the vector of Pauli matrices. \(\sigma\) and \(\sigma^\prime\) can be \(\pm 1\) and represent up and down configurations.
 
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} = \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}_1\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\left[\mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} \right.\\
+	\mathcal{H}_\text{tiled} = \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\left[\mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} \right.\\
 \left.+ \mathcal{H}_\text{imp-cbath}\right]T({\bf r} - {\bf r}_d)~.
@@
 \begin{equation}\begin{aligned}
-	&\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}_1\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}({\bf r}_d, {\bf z}_1)T({\bf r} - {\bf r}_d) \\
-	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\right.\\
-	 &\left.- \sum_{{\bf z}_1\in\text{NN}({\bf r}_d)}\sum_{{\bf z}_i}\frac{U_b({\bf z}_i)}{2Z \mathcal{Z}}\left(\hat n_{{\bf z}_i, \uparrow} - \hat n_{{\bf z}_i, \downarrow}\right)^2\right]T({\bf r} - {\bf r}_d) \\
-	=& -t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
-	 &- \frac{1}{2\mathcal{Z}Z}\sum_{\bf r}\sum_{{\bf z}_1\in\text{NN}\left({\bf r}\right) }\sum_{{\bf z}_i \in \text{NN}({\bf r})} U_b({\bf z}_i)  \left(\hat n_{{\bf z}_i, \uparrow} - \hat n_{{\bf z}_i, \downarrow}\right)^2 \\
-	=& -t(N-2)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
-	 &- \frac{1}{2}\overline{U_b}\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2\\
-\end{aligned}\end{equation}
-where \(\overline{U_b} = \sum_{\bf a} \frac{1}{z}U_b({\bf a})\) is the average of \(U_b({\bf a})\) over the bath zeroth sites in the auxliary model.
-The inequality \(\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}\) ensures that each nearest-neighbour pair appears in \(N-2\) instances of the auxiliary model, \(N\) being the total number of lattice sites.
-The two instances that do not contribute are the ones in which the impurity site itself is at \({\bf r}_i\) or \({\bf r}_j\).
-In the first step, the factor of \(\mathcal{Z}\) is cancelled out by the trivial sum over \({\bf r}_0\).
+	&\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d) \\
+	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-\frac{1}{\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \right.\\
+	 &\left.- \frac{U_b}{2\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}\right]T({\bf r} - {\bf r}_d) \\
+	=& -\frac{1}{\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
+	 &- \frac{U_b}{2\mathcal{Z}}\sum_{\bf r}\sum_{{\bf z}\in\text{NN}\left({\bf r}\right)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i}\sum_{{\bf r} \neq {\bf r}_i}\hat n_{{\bf r}_i,\sigma}\\
+	=& -\frac{1}{\mathcal{Z}}(N-2)t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
+	 &- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+\end{aligned}\end{equation}
+In the first step, the factor of \(\mathcal{Z}\) is cancelled out by the trivial sum over \({\bf r}_0\) in the first and third terms.
+At the last step, the three terms simplified for the following reasons.
+The inequality \(\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}\) in the first term ensures that each nearest-neighbour pair appears in \(N-2\) instances of the auxiliary model, \(N\) being the total number of lattice sites; the two instances that do not contribute are the ones in which the impurity site itself is at \({\bf r}_i\) or \({\bf r}_j\).
+For the second term, the double sum \(\sum_{\bf r}\sum_{{\bf z} \in \text{NN}({\bf r})}\) evaluates to \(\mathcal{Z}\sum_{\bf r}\), because each point on the lattice appears \(\mathcal{W}\) times in the summation.
+This factor of \(\mathcal{W}\) cancels the one in the denominator.
+In the third term, the inner summation simply evaluates to \(N-1\), and we finally replace the dummy index \({\bf r}_i\) with \({\bf r}\).
 
@@
 	&\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf r}_0\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp}T({\bf r} - {\bf r}_d) \\
-	=& -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 + \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}~.
+	=& -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}~.
 \end{aligned}\end{equation}
@@
 We now consider the final term:
-\begin{widetext}
-\begin{equation}\begin{aligned}
-	&\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf r}_0\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}T({\bf r} - {\bf r}_d)\\
-	&=\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf r}_0\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\left[\sum_{{\bf a},{\bf a}^\prime}\sum_{\alpha,\alpha^\prime}\frac{1}{Z}J({\bf a} - {\bf a}^\prime) {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \sigma}c^\dagger_{{\bf r}_d + {\bf a},\alpha}c_{{\bf r}_d + {\bf a}^\prime,\alpha^\prime} + \sum_{{\bf a}, \sigma} \frac{1}{\sqrt Z}V\left({\bf a}\right) \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf r}_d + {\bf a}},\sigma} + h.c.\right)\right]T({\bf r} - {\bf r}_d)
-\end{aligned}\end{equation}
-\end{widetext}
+\begin{equation}\begin{aligned}
+	&\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}T({\bf r} - {\bf r}_d)\\
+	&=\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\left[\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
+				     &-  \left.\sum_{\sigma} V \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]T({\bf r} - {\bf r}_d)\\
+	&=\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r})}\left[\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
+				     &-  \left.\sum_{\sigma} V\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]\\
+					 &=\frac{2}{\mathcal{Z}}\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]\\
+\end{aligned}\end{equation}
+At the last step, each nearest-neighbour pair of sites \({\bf r}_i, {\bf r}_j\) appear 2 times in the summation, because any site is a member of two distinct nearest-neighbour pairs.
+We have also defined \({\bf S}_{{\bf r}_j} =\sum_{\sigma,\sigma^\prime} {\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime}\) as the local spin operator.
+
+The total tiled Hamiltonian is therefore
+\begin{equation}\begin{aligned}
+	&\mathcal{H}_\text{tiled} \\
+	&= -\frac{N-2}{\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>,\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+	&- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}\\
+	& + \frac{2}{\mathcal{Z}}\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]
+\end{aligned}\end{equation}
+While constructing the tiled Hamiltonian, we have added extra copies of the non-interacting Hamiltonian \(\mathcal{H}_\text{cbath-nint} = -\frac{1}{\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\) for the conduction bath (this results in the factors of \(N-2\) and \(N-1\) in front of the first and third terms).
+Upon removing these repeated terms, the tiled Hamiltonian becomes
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}\\
+							 &= -\frac{1}{\mathcal{Z}}(t + 2V)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
+							 &- \frac{1}{2}\left(U + U_b\right)\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \left(\eta + 2\mu\right) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} \\
+							 &+ \frac{2}{\mathcal{Z}}J\sum_{\left< {\bf r}_i, {\bf r}_j\right>} {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j}
+\end{aligned}\end{equation}
+
+The result of the tiling operations is a Hubbard-Heisenberg model, of the form
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{HH} &= -\frac{1}{\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 \\
+						  &- \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma} + \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j}~,
+\end{aligned}\end{equation}
+where the tilde symbol indicates that the parameters are for the lattice model (and not the auxiliary model).
+By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to each other:
+\begin{equation}\begin{aligned}
+	\tilde t = t+2V,~~ \tilde U = U + U_b, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
+\end{aligned}\end{equation}
+In summary, the appropriate method for reconstructing the lattice model Hamiltonian is therefore
+\begin{equation}\begin{aligned}\label{tilingPrescriptionFinal}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}~,
+\end{aligned}\end{equation}
+using which the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.
+
+\subsection{Translation symmetry and a conserved total momentum}
+From the form in eq.~\ref{tilingPrescriptionFinal}, the tiled Hamiltonian is symmetric under global many-body translations of the kind defined in eq.~\ref{translationDefinition}, by arbitrary lattice spacings:
+\begin{equation}\begin{aligned}\label{translationSymmetry}
+	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})T({\bf a}) = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r + a}) = \sum_{{\bf r}^\prime}\mathcal{H}_\text{aux}({\bf r}^\prime)\\
+	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{cbath-nint}T({\bf a}) = \mathcal{H}_\text{cbath-nint}\\
+	&\implies T({\bf a})^\dagger\mathcal{H}_\text{tiled}T({\bf a}) = \mathcal{H}_\text{tiled}~.
+\end{aligned}\end{equation}
+In the first equation, we used the fact that the translation operator simply translates the auxiliary model at the position \({\bf r}\) into another one at the position \({\bf r} + {\bf a}\).
+Since both are part of the summation, the summation remains unchanged.
+The second equation uses the fact that the Hamiltonian \(\mathcal{H}_\text{cbath-nint}\) is that of a tight-binding model and is therefore translation-invariant.
+The fact that the Hamiltonian \(\mathcal{H}_\text{tiled}\) commutes with the many-body translation operator implies that the total crystal momentum \(\vec k\) is a conserved quantity.
+
+\section{Form of the eigenstates: Bloch's theorem}
+In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\bf k}({\bf r})} = \sum_{{\bf r}_i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_i({\bf r} - {\bf r}_i)}\).
+Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation \(T({\bf a})\) by some lattice distance \({\bf a}\):
+\begin{equation}\begin{aligned}
+	T({\bf a})\ket{\Psi_{{\bf k}}\left({\bf r}\right)} = \ket{\Psi_{{\bf k}}({\bf r} + {\bf a})} = e^{-i{\bf k}\cdot{\bf a}}\ket{\Psi({\bf r})}
+\end{aligned}\end{equation}
+These translation operators share eigenstates with the crystal momentum operator:
+\begin{equation}\begin{aligned}
+	T\left( {\bf r} \right) \ket{{\bf k}} = e^{-i {\bf k}\cdot{\bf r}} \ket{{\bf k}}~.
+\end{aligned}\end{equation}
+As a result, the eigenstates can be labelled using the crystal momentum value \({\bf k}\), along with a band index \(n\).
+The eigenstates \(\ket{\Psi_{{\bf k},n}}\) of the lattice Hamiltonians obtained using eq.~\ref{tilingPrescriptionFinal} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}).
+This means that the eigenstates \(\psi_n\left({\bf r}_d\right)\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) defined in eq.~\ref{unitCellHamiltonian} can be used to construct eigenstates of the lattice Hamiltonian.
+The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
+
+The state \(\psi_n\left({\bf r}_d\right)\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself is an averaged Hamiltonian over \(\mathcal{Z}\) zeroth sites.
+Accordingly, we can express the averaged eigenstate \(\psi_n\left({\bf r}_d\right)\) as
+\begin{equation}\begin{aligned}
+	\ket{\psi_n\left({\bf r}_d\right)} = \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z} \in \text{NN}({\bf r}_d)}\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}~,
+\end{aligned}\end{equation}
+where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\).
+With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:
+\begin{equation}\begin{aligned}
+	\ket{\Psi_{{\bf k}, n}} = \frac{1}{\sqrt N}\sum_{{\bf r}} e^{i {\bf k}\cdot{\bf r}} \ket{\psi_{n}\left({\bf r}\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}, {\bf a}} e^{i {\bf k}\cdot{\bf r}} \ket{\psi_{n}\left({\bf r}, {\bf a}\right)}
+\end{aligned}\end{equation}
+where \(N\) is the total number of lattice sites.
+The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands.
+The ground state is obtained by setting \({\bf k}\) and \(n\) to 0:
+\begin{equation}\begin{aligned}
+	\ket{\Psi_\text{gs}} = \frac{1}{\sqrt N}\sum_{{\bf r}} e^{i {\bf k}\cdot{\bf r}} \ket{\psi_\text{gs}\left({\bf r}\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}, {\bf a}} e^{i {\bf k}\cdot{\bf r}} \ket{\psi_\text{gs}\left({\bf r}, {\bf a}\right)}
+\end{aligned}\end{equation}
+
+\section{Mapping greens functions from the bulk to the auxiliary model}
+In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{gs}}\) of the auxiliary models.
+In this section, we will relate real-space Greens functions of the bulk lattice to those of the auxiliary model.
+We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
+We define the time-domain Greens function between two points \({\bf r}_1\) and \({\bf r}_2 \) at zero temperature as
+\begin{equation}\begin{aligned}
+	\tilde G({\bf r}_2 - {\bf r}_1, T) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c({\bf r}_2, T), c^\dagger({\bf r}_1) \right\} | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(T\): \(c({\bf r},t) = e^{iT H_\text{tiled} }c({\bf r})e^{-i T H_\text{tiled}}\).
+By introducing the Fourier transform \(\tilde G({\bf r}_2 - {\bf r}_1, T) = \int d\omega~\tilde G({\bf r}_2 - {\bf r}_1, \omega)\), the frequency-domain Greens function can be cast in its spectral representation
+\begin{equation}\begin{aligned}
+	\tilde G({\bf r}_2 - {\bf r}_1, \omega) = \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0 \in \text{GS}}\sum_n \left[\frac{\braket{n_0|c({\bf r}_2)|n}\braket{n|c^\dagger({\bf r}_1)|n_0}}{\omega + E_\text{gs} - E_n} \right.\\
+\left.+ \frac{\braket{n_0|c^\dagger({\bf r}_1)|n}\braket{n|c({\bf r}_2)|n_0}}{\omega - E_\text{gs} + E_n}\right] ~,
+\end{aligned}\end{equation}
+where \(n_0\) sums over the ground state(s) of the system, \(n\) sums over all eigenstates and \(\mathcal{D}_\text{gs}\) is the groundstate degeneracy.
+
 \clearpage
 
-To begin this procedure, we first create the unit of tiling - this is done by identifying the impurity as a particular site \(i\) of the lattice, and the bath coupled to the impurity as the set of remaining \(N-1\) sites in the lattice.
-We will also identity the zeroth site of the SIAM lattice as one of the nearest neighbours \(j\) of \(i\):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(i,j) = -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n} \left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right) ^2 \\
-	+ V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j - \frac{1}{2}U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2 
-\end{aligned}\end{equation}
-The tight-binding term sums over all nearest pairs \((m,n)\) that do not involve the site \(i\).
-In general \(i\) will have \(\mathcal{Z}\) nearest neighbours for a lattice with coordination number \(\mathcal{Z}\).
-The total local Hamiltonian for the site \(i\) is obtained by averaging over the Hamiltonians \(\mathcal{H}_\text{aux}(i,j)\) for all nearest neighbours \(j\) of \(i\):
-\begin{widetext}
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux}(i) &= \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}} \mathcal{H}_\text{aux}(i,j) = - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right)  \right.\\
-				  &\left. +J \vec{S_i}\cdot\vec{S}_j - \frac{1}{2}U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\\
-				  &= - \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) +J \vec{S_i}\cdot\vec{S}_j - \frac{1}{2}U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]
-\end{aligned}\end{equation}
-Once we have this local Hamiltonian for a particular site, we translate this over all sites \(i\):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& \sum_i \mathcal{H}_\text{aux}(i) = \sum_i\left[- \frac{U}{2}\left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 -2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) \right.\right.\\
-				  &\left.\left. + J \vec{S_i}\cdot\vec{S}_j - \frac{1}{2}U_b\left(\hat n_{j \uparrow} - \hat n_{j \downarrow}\right)^2\right]\right]\\
-	=& -\frac{1}{2}\left(U + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \sum_i\left[-2t\sum_{<m,n>,\sigma}^{m \neq i \neq n}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) +  \frac{1}{\mathcal{Z}}\sum_{j \in \text{NN of i}}\left[V \sum_{\sigma} \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) + J \vec{S_i}\cdot\vec{S}_j\right]\right]
-\end{aligned}\end{equation}
-In the entire tight-binding term \(\sum_i\sum_{<m,n>,\sigma}^{m \neq i \neq n}\), each pair will appear \(N-2\) times, because that is the total number of sites that do not involve either \(m\) or \(n\).
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{full} =& -\frac{1}{2}\left(U + U_b\right) \sum_i \left( \hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - 2t\left(N-2\right)\sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2}{\mathcal{Z}}\sum_{<i,j>}\left[\sum_\sigma V \left(c^\dagger_{j\sigma} c_{i\sigma} + h.c.\right) + J \vec{S_i}\cdot\vec{S}_j\right]\\
-				  &=-\frac{1}{2}\left(U + U_b\right)\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \left(2t (N-2) - \frac{2V}{\mathcal{Z}}\right) \sum_{<m,n>,\sigma}\left(c^\dagger_{m\sigma}c_{n\sigma} + \text{h.c.}\right) + \frac{2J}{\mathcal{Z}} \sum_{<i,j>} \vec{S_i}\cdot\vec{S}_j
-\end{aligned}\end{equation}
-\end{widetext}
-We end up with a Hubbard-Heisenberg model, of the form:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{H-H} = - \frac{1}{2}U_\text{H-H}\sum_{i} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 + \frac{1}{\mathcal{Z}}J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j\\
-	- \frac{1}{\mathcal{Z}}t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) \\
-\end{aligned}\end{equation}
-where the bulk parameters are related to the auxiliary model couplings through the mapping:
-\begin{equation}\begin{aligned}
-	\label{map_aux_bulk}
-	t_{H-H} &= \left(2t \mathcal{Z}(N-2) - 2V\right),\\
-	U_{H-H} &= U + U_b,\\
-	J_{H-H} &= 2J
-\end{aligned}\end{equation}
-The conclusion is that we can tile Anderson models with interacting baths into a Hubbard-Heisenberg model:
-\begin{equation}\begin{aligned}
-	\label{siam_to_hubb}
-	\sum_i \mathcal{H}_\text{aux}(i) = \mathcal{H}_{H-H}
-\end{aligned}\end{equation}
-
-\subsection{Translation symmetry and a conserved total momentum}
-From the form in eq.~\ref{tilingPrescription}, the tiled Hamiltonian is symmetric under discrete many-body translations:
-\begin{equation}\begin{aligned}\label{translationSymmetry}
-	T({\bf r})\mathcal{H}_\text{full}T^\dagger({\bf r}) = \sum_{{\bf r}^\prime}T({\bf r} + {\bf r}^\prime)\mathcal{H}_\text{aux}({\bf r_0})T^\dagger({\bf r} + {\bf r}^\prime) = \sum_{{\bf r}^\prime}T({\bf r}^\prime)\mathcal{H}_\text{aux}({\bf r_0})T^\dagger({\bf r}^\prime) = \mathcal{H}_\text{full}~.
-\end{aligned}\end{equation}
-There we used the fact that \({\bf r} + {\bf r}^\prime\) simply translates the auxiliary model defined by the coordinate \({\bf r}^\prime + {\bf r_0}\) to a new auxiliary model at the modified coordinate \({\bf r} + {\bf r}^\prime + {\bf r_0}\).
-Since this transformation from one auxiliary model to another simply shuffles the group of all auxiliary models, the sum over the group remains the sum, and we recover the same bulk model.
-
-The fact that the Hamiltonian \(\mathcal{H}_\text{full}\) commutes with the many-body translation operator implies that the total momentum \(\vec k\) is a conserved quantity.
-This is in fact because the many-body translation operators can be obtained in terms of \(\vec k\): \(T({\bf r}) = \exp\left\{ i \vec{k}\cdot\vec{r} \right\} \).
-
-\subsection{Moving away from half-filling}
-As mentioned before, no chemical potential \(\mu\) is generated because the auxiliary model was at half-filling, both in the impurity as well as in the bath.
-We can change the chemical potential by introducing two terms:
-\begin{equation}\begin{aligned}
-	\eta \sum_\sigma\left(n_{d\sigma} - \frac{1}{2}\right), \mu \sum_{i,\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
-\end{aligned}\end{equation}
-The first term is the particle-hole asymmetry term, and tuning that term moves the impurity away from half-filling.
-The second term is the usual chemical potential in the bath.
-Introducing these terms in the auxiliary model changes the bulk model into:
-\begin{equation}\begin{aligned}
-	\mathcal{H}_{H-H} = -\frac{1}{2}U_\text{H-H} \sum_{i} \left(\hat n_{i \uparrow} - \hat n_{i \downarrow} \right)^2 - \frac{1}{\mathcal{Z}}t_\text{H-H}\sum_{<i,j>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{\mathcal{Z}}J_\text{H-H}\sum_{<i,j>} \vec{S}_i\cdot\vec{S}_j + \mu_\text{H-H}\sum_{i\sigma}\left(\hat n_{i\sigma} - \frac{1}{2}\right)
-\end{aligned}\end{equation}
-The only change is the generation of the last term. The mappings between the existing parameters and their auxiliary model counterparts remain the same, while \(\mu_\text{H-H}\) is given by
-\begin{equation}\begin{aligned}
-	\mu_\text{H-H} = \eta + \left(N-1\right) \mu
-\end{aligned}\end{equation}
-In the discussion henceforth, we will assume all the models are at half-filling. We will come back to the doped case at a later point in time.
-
-\section{Effective action for the Hubbard-Heisenberg model and the eSIAM}
-In order to better understand the similarities and differences between the tiling approach outlined here and the approach adopted in dynamical mean-field approximations, we compute the effective action for the local impurity as well as the impurity-zeroth site system, in both the auxiliary and bulk models.
-This will be done in the limit of infinite coordination number, in order to create a tractable effective theory.
-
-\subsection{Local theory for the Hubbard-Heisenberg model}
-We will first work with the Hubbard-Heisenberg model.
-Let us recall that within the eSIAM, most of the dynamics is governed by the physics of the impurity site and the bath site coupled to the impurity.
-Accordingly, we will first obtain an effective action within the Hubbard-Heisenberg model for the small system consisting of a local site and all its nearest-neighbours.
-
-We choose a certain local site that we call \(0\), whose nearest-neighbours will be denoted as \(\left\{ {\bar 0} \right\} \).
-The action for the full Hubbard-Heisenberg model can be formally separated into three parts:
-\begin{equation}\begin{aligned}
-S_\text{H-H} = S_{0,{\bar 0}} + S^{(0,{\bar 0})} + S_\text{int}~,
-\end{aligned}\end{equation}
-where \(S_{0,{\bar 0}}\) represents the part of the action that involves only the sites \(0\) and $\left\{ {\bar 0} \right\}$, \(S^{(0,{\bar 0})}\) represents the part that has all the sites apart from \(0\) and \(\left\{ {\bar 0} \right\} \), while \(S_\text{int}\) contains all terms that connect these two parts.
-These three parts have the forms
-\begin{equation}\begin{aligned}
-S_{0,{\bar 0}} = \sum_{i=0,{\bar 0}}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau)  - t\sum_{{\bar 0},\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{0\sigma}(\tau)c_{{\bar 0}\sigma}(\tau) + \text{h.c.}\right] \\
-- \frac{U}{2}\sum_{i=0,{\bar 0}}\int_0^\beta\mathrm{d\tau}~\left(n_{i \uparrow}(\tau) - n_{i \downarrow}(\tau)\right)^2 + J\sum_{{\bar 0}}\int_0^\beta\mathrm{d\tau} \vec{S}_0(\tau)\cdot\vec{S}_{{\bar 0}}(\tau)~,
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-S^{(0,{\bar 0})} = \sum_{j\neq(0,{\bar 0})}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{j\sigma}(\tau)\partial_\tau c_{j\sigma}(\tau)  - t\sum_{\left<j,l\right>\neq (0,{\bar 0}),\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{j\sigma}(\tau)c_{l\sigma}(\tau) + \text{h.c.}\right] \\
-- \frac{U}{2}\sum_{j\neq(0,{\bar 0})}\int_0^\beta\mathrm{d\tau}~\left(n_{j\uparrow}(\tau) - n_{j\downarrow}(\tau)\right)^2 + J\sum_{\left<j,l\right>\neq(0,{\bar 0})}\int_0^\beta\mathrm{d\tau} \vec{S}_l(\tau)\cdot\vec{S}_j(\tau)~,
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-S_\text{int} = -t\sum_{i \in {\bar 0}}\sum_{j \in \text{NN of}~i}\sum_\sigma \int_0^\beta\mathrm{d\tau}~\left(c^\dagger_{i\sigma}(\tau) c_{j\sigma}(\tau) + \text{h.c.}\right) + J\sum_{i \in {\bar 0}}\sum_{j \in \text{NN of}~i}\int_0^\beta\mathrm{d\tau}\vec{S}_i(\tau)\cdot\vec{S}_j(\tau) = S_\text{int}^\text{hop} + S_\text{int}^\text{spin}
-\end{aligned}\end{equation}
-
-In order to obtain an effective theory \(S^{0,{\bar 0}}_\text{eff}\) purely for the local system \((0,{\bar 0})\), we need to trace over all the other degrees of freedom.
-This partial trace will be carried out over the states of the so-called ``cavity" system \(S^{(0,{\bar 0})}\).
-The effective action can be constructed by tracing over scattering processes of all orders that leave the final action diagonal in the system \((0,{\bar 0})\).
-The formal expression can be written as
-\begin{equation}\begin{aligned}
-	S^{0,{\bar 0}}_\text{eff} = S_{0,{\bar 0}} + \sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} + \sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})}
-\end{aligned}\end{equation}
-where, as mentioned before, the average is carried out in the cavity system \(S^{(0,{\bar 0})}\). Each hopping term in the expansion is of the form
-\begin{equation}\begin{aligned}
-	\left(S_\text{int}^\text{hop}\right)^{2n} =& t^{2n}\sum_\sigma\sum_{(i_1, i_1^\prime)\ldots, (i_n, i_n^\prime)} ~\sum_{(j_1, j_1^\prime)\ldots, (j_n, j_n^\prime)} \int_0^\beta d\tau_{1}\ldots d\tau_{n}d\tau_{1}^\prime\ldots d\tau_{j_n}^\prime\\
-			   &c^\dagger_{i_1\sigma}(\tau_{i_1})c^\dagger_{i_2\sigma}(\tau_{2})\ldots c^\dagger_{i_n\sigma}(\tau_{n}) c_{i_1^\prime\sigma}(\tau_{1}^\prime)c_{i_2^\prime\sigma}(\tau_{2}^\prime)\ldots c_{i_n^\prime\sigma}(\tau_{n}^\prime)\left<c_{j_1\sigma}(\tau_{1})c_{j_2\sigma}(\tau_{2})\ldots c_{j_n\sigma} ~ c^\dagger_{j_1^\prime\sigma}(\tau_{1}^\prime)\ldots c^\dagger_{j_n^\prime\sigma}(\tau_{n}^\prime) \right>_{(0,{\bar 0})}\\
-	=& t^{2n}\sum_\sigma\sum_{(i_1, i_1^\prime)\ldots, (i_n, i_n^\prime)} ~\sum_{(j_1, j_1^\prime)\ldots, (j_n, j_n^\prime)} \int_0^\beta d\tau_{1}\ldots d\tau_{j_n}^\prime c^\dagger_{i_1\sigma}(\tau_{i_1})\ldots c^\dagger_{i_n\sigma}(\tau_{n})~c_{i_1^\prime\sigma}(\tau_{1}^\prime)\ldots c_{i_n^\prime\sigma}(\tau_{n}^\prime)\\
-	 &G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right)~,
-\end{aligned}\end{equation}
-where the indices \(i_1\) through \(i_n\) and their primed counterparts run through \(\bar 0\), while \(j_l\) (\(\in \left\{j_1,\ldots,j_n^\prime\right\}\)) runs through the nearest-neighbours of the corresponding \(i_l\) index.
-The \(n-\)particle Greens function \(G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right)\) for the cavity system is defined in the usual fashion
-\begin{equation}\begin{aligned}
-	G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right) = \left<c_{j_1\sigma}(\tau_{1})c_{j_2\sigma}(\tau_{2})\ldots c_{j_n\sigma} ~ c^\dagger_{j_1^\prime\sigma}(\tau_{1}^\prime)\ldots c^\dagger_{j_n^\prime\sigma}(\tau_{n}^\prime) \right>_{(0,{\bar 0})}
-\end{aligned}\end{equation}
-In the limit of infinite coordination number, only the \(n=1\) term survives:
-\begin{equation}\begin{aligned}
-	\lim_{\mathcal{Z}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} = t^2\sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)\sum_{j,j^\prime}G_1^{(0,\bar 0)}\left(j\tau; j^\prime\tau^\prime\right) \\
-	= \sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)~,
-\end{aligned}\end{equation}
-where we have defined the bath hybridisation function \(\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)\) as
-\begin{equation}\begin{aligned}
-	\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime) = t^2\sum_{j \in \text{NN of}~i}\sum_{j^\prime \in \text{NN of}~i^\prime}G_1^{(0,\bar 0)}\left(j\sigma\tau; j^\prime\sigma\tau^\prime\right)~.
-\end{aligned}\end{equation}
-
-Under similar approximations, the spin term in the action reduces to
-\begin{equation}\begin{aligned}
-	\lim_{\mathcal{Z}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})} = \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\chi(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)~,
-\end{aligned}\end{equation}
-where the susceptibility \(\chi_{ii^\prime}(\tau - \tau^\prime)\) is defined as 
-\begin{equation}\begin{aligned}
-	\chi_{ii^\prime}(\tau - \tau^\prime) = J^2\sum_{j \in \text{NN of}~i}\sum_{j^\prime \in \text{NN of}~i^\prime}\vec{S}_{j}(\tau)\cdot\vec{S}_{j^\prime}(\tau^\prime)~.
-\end{aligned}\end{equation}
-The effective action for the \(0,\bar 0\) system, in the limit of large coordination number, simplifies to
-\begin{equation}\begin{aligned}
-	S^{0,{\bar 0}}_\text{eff} =& \sum_{i=0,{\bar 0}}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau)  - t\sum_{{\bar 0},\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{0\sigma}(\tau)c_{{\bar 0}\sigma}(\tau) + \text{h.c.}\right] - \frac{U}{2}\sum_{i=0,{\bar 0}}\int_0^\beta\mathrm{d\tau}~\left(n_{i \uparrow}(\tau) - n_{i \downarrow}(\tau)\right)^2 \\
-				   &+ J\sum_{{\bar 0}}\int_0^\beta\mathrm{d\tau} \vec{S}_0(\tau)\cdot\vec{S}_{{\bar 0}}(\tau) + \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{ii^\prime}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
-\end{aligned}\end{equation}
-
-One can also write down an effective action purely for the local site \(0\).
-The sites \(\bar 0\) will now be a part of the environment action \(S^{(0)}\) instead of the system action, but since the system is thermodynamically large, the cavity action can be assumed to remain the same, such the expectation values are calculated in the same system.
-As a result, the hybridisation and susceptibility functions remain unchanged.
-\(S_\text{int}\) is now made of terms that connect \(0\) and \(\bar 0\), so the transformation from \(S^{(0,\bar 0)}\) can be made by replacing the set \(\left\{ j \right\} \) with the set \(\bar 0\), and the set \(\bar 0\) itself will be replaced by the local site \(0\).
-We quote the final form of the local effective action:
-\begin{equation}\begin{aligned}
-	S^{0}_\text{eff} =& \sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{0\sigma}(\tau)\partial_\tau c_{0\sigma}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{0\uparrow}(\tau) - n_{0\downarrow}(\tau)\right)^2 \\
-			  &+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\Delta_{00,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{00}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
-\end{aligned}\end{equation}
-
-\subsection{Local theory for the extended SIAM}
-The Hamiltonian for the extended SIAM model is shown in eq.~\ref{siam_attr}.
-We will denote the impurity with the label \(d\) and the bath sites with the label \(c\).
-Among the bath sites, we will represent the site coupled to the impurity with \(z\).
-The full action has the form
-\begin{equation}\begin{aligned}
-	S_\text{ES} = \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - t\sum_{\left<i,j \right> \in c,\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{i\sigma}(\tau)c_{j\sigma}(\tau) + \text{h.c.}\right] - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right]\\
-+ J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{U_b}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 ~,
-\end{aligned}\end{equation}
-As in the Hubbard-Heisenberg model, we first obtain an effective action for the pair of sites \((d,z)\).
-As in the previous calculation, this will again generate a hybridisation function \(\Delta_{zz,\sigma}\) for the bath site nearest to the zeroth site.
-No susceptibility will be generated however, because there is no spin-exchange coupling within the bath.
-The net result is
-\begin{equation}\begin{aligned}
-	S^{d,z}_\text{eff} =& \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right] + J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) \\
-	&- \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{U_b}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 \\
-	&+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\sum_{\sigma}\Delta_{zz,\sigma}(\tau - \tau^\prime)c^\dagger_{z\sigma}(\tau)c_{z\sigma}(\tau^\prime)
-\end{aligned}\end{equation}
-This hybridisation \(\Delta_{zz,\sigma}\) is calculated in the cavity model of the eSIAM, obtained by removing the impurity and the zeroth site from the full model; it is a completely non-interacting system.
-
-One can go one step further and also remove the zeroth site in order to obtain a theory for the impurity site.
-With this choice, the cavity model now also includes the zeroth site, and hence contains the correlation term associated with \(U_b\).
-The one-particle connection \(V\) will lead to a modified hybridisation \(\mathcal{F}\) for this effective theory; the Kondo terms will generate a susceptibility.
-The resultant action is
-\begin{equation}\begin{aligned}
-	S^{d}_\text{eff} =& \sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{d\sigma}(\tau)\partial_\tau c_{d\sigma}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 \\
-			  &+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\mathcal{F}_{\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{d}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
-\end{aligned}\end{equation}
-where \(\mathcal{F}\) is defined in terms of the local correlator of the zeroth site
-\begin{equation}\begin{aligned}
-	\mathcal{F}_\sigma(\tau - \tau^\prime) = V^2 G_1^{(d)}\left(z\sigma\tau; z\sigma\tau^\prime\right) = V^2 \left<c_{z\sigma}(\tau)c^\dagger_{z\sigma}(\tau^\prime)\right>_{(d)}
-\end{aligned}\end{equation}
-with the average computed in the interacting cavity model that has the impurity site removed.
-The interaction arises from the \(U_b-\)term.
-The susceptibility is also calculated in this interacting cavity model, and follows the same definition as in the bulk model:
-\begin{equation}\begin{aligned}
-	\chi_{d}(\tau - \tau^\prime) = J^2\vec{S}_{z}(\tau)\cdot\vec{S}_{z}(\tau^\prime)~.
-\end{aligned}\end{equation}
-
-\section{Form of the eigenstates: Bloch's theorem}
-In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\vec k}({\bf r})} = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \ket{\psi_i({\bf r} - {\bf r}_i)}\).
-Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation \(T({\bf r})\) by some lattice distance \({\bf r} = \sum_i n_i {\bf a}_i\):
-\begin{equation}\begin{aligned}
-	T({\bf r})\ket{\Psi_{\vec k}\left({\bf r}\right)} = \ket{\Psi_{\vec k}({\bf r} + {\bf r})} = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \ket{\psi_i({\bf r} + {\bf r} - {\bf r}_i)} = e^{i \vec{k}\cdot\vec{R}}\sum_i e^{i \vec{k}\cdot\left(\vec{R}_i - {\bf r}\right)} \ket{\psi_i({\bf r} - ({\bf r}_i - {\bf r}))} = e^{\vec{k}\cdot\vec{R}}\ket{\Psi({\bf r})}
-\end{aligned}\end{equation}
-At the end, we used the fact that \({\bf r}_i - {\bf r}\) is just another lattice vector \({\bf r}_j\). As mentioned before, these translation operators share eigenstates with the momentum operator:
-\begin{equation}\begin{aligned}
-	T\left( {\bf r} \right) \ket{\vec k} = \sum_{{\bf r}_i} e^{i \vec{k}\cdot\vec{r}_i}T\left( {\bf r} \right)\ket{{\bf r}_i} = e^{i \vec{k}\cdot\vec{R}}\sum_{{\bf r}_i} e^{i \vec{k}\cdot\left(\vec{r}_i - {\bf r}\right)}\ket{{\bf r}_i - {\bf r}} = e^{i \vec{k}\cdot\vec{R}} \ket{\vec k}
-\end{aligned}\end{equation}
-
-The eigenstates of bulk Hamiltonian obtained in eq.~\ref{siam_to_hubb} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}).
-This means that we can use the auxiliary model eigenstates
-\begin{equation}\begin{aligned}
-\psi^n_\text{aux}\left({\bf r}_i, {\bf a}\right)~,
-\end{aligned}\end{equation}
-with the impurity position \({\bf r}_i\) and zeroth site position \({\bf r}_i + {\bf a}\), to construct eigenstates of the bulk Hamiltonian.
-\({\bf r}_i\) is a lattice vector, while \({\bf a}\) is one of the \(\mathcal{Z}\) vectors that connect a lattice site with its nearest neighbours.
-The \(n\) in the superscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
-\(n=0\) is the ground state of the auxiliary model, and higher values denote the excited states.
-The following un-normalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:
-\begin{equation}\begin{aligned}
-	\ket{\Psi^n_{\vec k}} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_i, {\bf a}} e^{i \vec{k}\cdot\vec{R}_i} \psi^n_\text{aux}\left({\bf r}_i, {\bf a}\right)
-\end{aligned}\end{equation}
-where \(N\) is the total number of lattice sites.
-The interpretation is that the set of \(n=0\) states form the lowest band in the spectrum of the lattice.
-Higher values of \(n\) produce the more energetic bands.
-The ground state is obtained by setting \(\vec k\) and \(n\) to 0: \(\ket{\Psi_{\vec k=0}^{n=0}} \equiv \ket{\Psi_\text{gs}}\).
-We will actually work only in the lowest band \(n=0\), so we will drop the band index from now on and keep in mind that only the auxiliary model ground states appear in the formulation:
-\begin{equation}\begin{aligned}
-	\label{bloch-states}
-	\ket{\Psi_{\vec k}} = \frac{1}{\lambda_{\ket{\vec k}} \sqrt{\mathcal{Z} N}}\sum_{{\bf r}_i, {\bf a}} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left({\bf r}_i, {\bf a}\right)~,
-\end{aligned}\end{equation}
-where \(\lambda_{\ket{\vec k}}\) is a normalisation factor.
-
-To determine the normalisation factor, we compute the norm of the trial eigenstates:
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k} | \Psi_{\vec k}} &= \frac{1}{\mathcal{Z}^2 \lambda_{\vec k}^2 N^2}\sum_{{\bf r}, {\bf r}^\prime, a, a^\prime}e^{i \vec{k}\cdot({\bf r} - {\bf r}^\prime)}\braket{\psi_\text{aux}({\bf r}^\prime, {\bf a}^\prime) | \psi_\text{aux}({\bf r}, {\bf a})} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{{\bf r}, {\bf r}^\prime, }e^{i \vec{k}\cdot({\bf r} - {\bf r}^\prime)}\braket{\psi_\text{aux}({\bf r}^\prime) | \psi_\text{aux}({\bf r})}\\
-					       &=\frac{1}{\lambda_{\vec k}^2 N^2}\sum_{{\bf r}, {\bf r}^\prime}e^{i \vec{k}\cdot({\bf r} - {\bf r}^\prime)}\braket{\psi_\text{aux}({\bf r_0}) | T^\dagger({\bf r} - {\bf r}^\prime) | \psi_\text{aux}({\bf r_0})} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{{\bf r}, {\bf r}^\prime, q}e^{i \vec{k}\cdot({\bf r} - {\bf r}^\prime)}\braket{\psi_\text{aux}({\bf r_0}) | T^\dagger({\bf r} - {\bf r}^\prime) \ket{\vec q}\bra{\vec q} \psi_\text{aux}({\bf r_0})}\\
-					       &= \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{{\bf r}, {\bf r}^\prime, q}e^{i (\vec{k} - \vec q)\cdot({\bf r} - {\bf r}^\prime)}\braket{\psi_\text{aux}({\bf r_0}) \ket{\vec q}\bra{\vec q} \psi_\text{aux}({\bf r_0})} = \frac{1}{\lambda_{\vec k}^2 N^2}\sum_{q} N^2 \delta_{\vec{k},\vec q}|\braket{\psi_\text{aux}({\bf r_0}) | \vec q}|^2\\
-\end{aligned}\end{equation}
-By requiring this norm to be unity, we obtain \(\lambda_{\vec k}^2 = |\braket{\psi_\text{aux}({\bf r_0}) | \vec k}|^2\). In the above exercise, we defined a state 
-\begin{equation}\begin{aligned}\label{zeroth_site_average}
-	\ket{\psi_\text{aux}({\bf r})} = (1/w)\sum_{{\bf a}}\ket{\psi_\text{aux}({\bf r}, {\bf a})}~,
-\end{aligned}\end{equation}
-by averaging over the neasest neighbours of \({\bf r}\), and inserted the total momentum basis \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators.
-\({\bf r_0}\) is any particular lattice site which we define as the origin of the lattice.
-Because of the symmetry of the lattice, the inner product in the definition of \(\lambda\) will be the same irrespective of which \({\bf a}\) we choose among the \(\mathcal{Z}\) choices.
-
-\section{Mapping greens functions from the bulk to the auxiliary model}
-In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{aux}}\) of the auxiliary models.
-In this section, we will relate real-sapce Greens functions of the bulk lattice to those of the auxiliary model.
-We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
-We define the time-domain Greens function between two points \({\bf r}\) and \({\bf r} + {\bf r}\) as
-\begin{equation}\begin{aligned}
-	G_\text{H-H}({\bf r}, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c({\bf r} + r,t), c^\dagger({\bf r}) \right\} | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-where the bulk Hamiltonian \(H_\text{H-H}\) leads to the dynamics of the annihilation operator: \(c({\bf r} + r,t) = e^{i H_\text{H-H} t}c({\bf r} + r)e^{-i H_\text{H-H} t}\).
 Following eq.~\ref{siam_to_hubb}, the exponential can be written as:
@@
 \appendix
-
+\begin{widetext}
+\section{Effective action for the Hubbard-Heisenberg model and the eSIAM}
+In order to better understand the similarities and differences between the tiling approach outlined here and the approach adopted in dynamical mean-field approximations, we compute the effective action for the local impurity as well as the impurity-zeroth site system, in both the auxiliary and bulk models.
+This will be done in the limit of infinite coordination number, in order to create a tractable effective theory.
+
+\subsection{Local theory for the Hubbard-Heisenberg model}
+We will first work with the Hubbard-Heisenberg model.
+Let us recall that within the eSIAM, most of the dynamics is governed by the physics of the impurity site and the bath site coupled to the impurity.
+Accordingly, we will first obtain an effective action within the Hubbard-Heisenberg model for the small system consisting of a local site and all its nearest-neighbours.
+
+We choose a certain local site that we call \(0\), whose nearest-neighbours will be denoted as \(\left\{ {\bar 0} \right\} \).
+The action for the full Hubbard-Heisenberg model can be formally separated into three parts:
+\begin{equation}\begin{aligned}
+S_\text{H-H} = S_{0,{\bar 0}} + S^{(0,{\bar 0})} + S_\text{int}~,
+\end{aligned}\end{equation}
+where \(S_{0,{\bar 0}}\) represents the part of the action that involves only the sites \(0\) and $\left\{ {\bar 0} \right\}$, \(S^{(0,{\bar 0})}\) represents the part that has all the sites apart from \(0\) and \(\left\{ {\bar 0} \right\} \), while \(S_\text{int}\) contains all terms that connect these two parts.
+These three parts have the forms
+\begin{equation}\begin{aligned}
+S_{0,{\bar 0}} = \sum_{i=0,{\bar 0}}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau)  - t\sum_{{\bar 0},\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{0\sigma}(\tau)c_{{\bar 0}\sigma}(\tau) + \text{h.c.}\right] \\
+- \frac{U}{2}\sum_{i=0,{\bar 0}}\int_0^\beta\mathrm{d\tau}~\left(n_{i \uparrow}(\tau) - n_{i \downarrow}(\tau)\right)^2 + J\sum_{{\bar 0}}\int_0^\beta\mathrm{d\tau} \vec{S}_0(\tau)\cdot\vec{S}_{{\bar 0}}(\tau)~,
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+S^{(0,{\bar 0})} = \sum_{j\neq(0,{\bar 0})}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{j\sigma}(\tau)\partial_\tau c_{j\sigma}(\tau)  - t\sum_{\left<j,l\right>\neq (0,{\bar 0}),\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{j\sigma}(\tau)c_{l\sigma}(\tau) + \text{h.c.}\right] \\
+- \frac{U}{2}\sum_{j\neq(0,{\bar 0})}\int_0^\beta\mathrm{d\tau}~\left(n_{j\uparrow}(\tau) - n_{j\downarrow}(\tau)\right)^2 + J\sum_{\left<j,l\right>\neq(0,{\bar 0})}\int_0^\beta\mathrm{d\tau} \vec{S}_l(\tau)\cdot\vec{S}_j(\tau)~,
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+S_\text{int} = -t\sum_{i \in {\bar 0}}\sum_{j \in \text{NN of}~i}\sum_\sigma \int_0^\beta\mathrm{d\tau}~\left(c^\dagger_{i\sigma}(\tau) c_{j\sigma}(\tau) + \text{h.c.}\right) + J\sum_{i \in {\bar 0}}\sum_{j \in \text{NN of}~i}\int_0^\beta\mathrm{d\tau}\vec{S}_i(\tau)\cdot\vec{S}_j(\tau) = S_\text{int}^\text{hop} + S_\text{int}^\text{spin}
+\end{aligned}\end{equation}
+
+In order to obtain an effective theory \(S^{0,{\bar 0}}_\text{eff}\) purely for the local system \((0,{\bar 0})\), we need to trace over all the other degrees of freedom.
+This partial trace will be carried out over the states of the so-called ``cavity" system \(S^{(0,{\bar 0})}\).
+The effective action can be constructed by tracing over scattering processes of all orders that leave the final action diagonal in the system \((0,{\bar 0})\).
+The formal expression can be written as
+\begin{equation}\begin{aligned}
+	S^{0,{\bar 0}}_\text{eff} = S_{0,{\bar 0}} + \sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} + \sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})}
+\end{aligned}\end{equation}
+where, as mentioned before, the average is carried out in the cavity system \(S^{(0,{\bar 0})}\). Each hopping term in the expansion is of the form
+\begin{equation}\begin{aligned}
+	\left(S_\text{int}^\text{hop}\right)^{2n} =& t^{2n}\sum_\sigma\sum_{(i_1, i_1^\prime)\ldots, (i_n, i_n^\prime)} ~\sum_{(j_1, j_1^\prime)\ldots, (j_n, j_n^\prime)} \int_0^\beta d\tau_{1}\ldots d\tau_{n}d\tau_{1}^\prime\ldots d\tau_{j_n}^\prime\\
+			   &c^\dagger_{i_1\sigma}(\tau_{i_1})c^\dagger_{i_2\sigma}(\tau_{2})\ldots c^\dagger_{i_n\sigma}(\tau_{n}) c_{i_1^\prime\sigma}(\tau_{1}^\prime)c_{i_2^\prime\sigma}(\tau_{2}^\prime)\ldots c_{i_n^\prime\sigma}(\tau_{n}^\prime)\left<c_{j_1\sigma}(\tau_{1})c_{j_2\sigma}(\tau_{2})\ldots c_{j_n\sigma} ~ c^\dagger_{j_1^\prime\sigma}(\tau_{1}^\prime)\ldots c^\dagger_{j_n^\prime\sigma}(\tau_{n}^\prime) \right>_{(0,{\bar 0})}\\
+	=& t^{2n}\sum_\sigma\sum_{(i_1, i_1^\prime)\ldots, (i_n, i_n^\prime)} ~\sum_{(j_1, j_1^\prime)\ldots, (j_n, j_n^\prime)} \int_0^\beta d\tau_{1}\ldots d\tau_{j_n}^\prime c^\dagger_{i_1\sigma}(\tau_{i_1})\ldots c^\dagger_{i_n\sigma}(\tau_{n})~c_{i_1^\prime\sigma}(\tau_{1}^\prime)\ldots c_{i_n^\prime\sigma}(\tau_{n}^\prime)\\
+	 &G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right)~,
+\end{aligned}\end{equation}
+where the indices \(i_1\) through \(i_n\) and their primed counterparts run through \(\bar 0\), while \(j_l\) (\(\in \left\{j_1,\ldots,j_n^\prime\right\}\)) runs through the nearest-neighbours of the corresponding \(i_l\) index.
+The \(n-\)particle Greens function \(G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right)\) for the cavity system is defined in the usual fashion
+\begin{equation}\begin{aligned}
+	G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right) = \left<c_{j_1\sigma}(\tau_{1})c_{j_2\sigma}(\tau_{2})\ldots c_{j_n\sigma} ~ c^\dagger_{j_1^\prime\sigma}(\tau_{1}^\prime)\ldots c^\dagger_{j_n^\prime\sigma}(\tau_{n}^\prime) \right>_{(0,{\bar 0})}
+\end{aligned}\end{equation}
+In the limit of infinite coordination number, only the \(n=1\) term survives:
+\begin{equation}\begin{aligned}
+	\lim_{\mathcal{Z}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} = t^2\sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)\sum_{j,j^\prime}G_1^{(0,\bar 0)}\left(j\tau; j^\prime\tau^\prime\right) \\
+	= \sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)~,
+\end{aligned}\end{equation}
+where we have defined the bath hybridisation function \(\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)\) as
+\begin{equation}\begin{aligned}
+	\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime) = t^2\sum_{j \in \text{NN of}~i}\sum_{j^\prime \in \text{NN of}~i^\prime}G_1^{(0,\bar 0)}\left(j\sigma\tau; j^\prime\sigma\tau^\prime\right)~.
+\end{aligned}\end{equation}
+
+Under similar approximations, the spin term in the action reduces to
+\begin{equation}\begin{aligned}
+	\lim_{\mathcal{Z}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})} = \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\chi(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)~,
+\end{aligned}\end{equation}
+where the susceptibility \(\chi_{ii^\prime}(\tau - \tau^\prime)\) is defined as 
+\begin{equation}\begin{aligned}
+	\chi_{ii^\prime}(\tau - \tau^\prime) = J^2\sum_{j \in \text{NN of}~i}\sum_{j^\prime \in \text{NN of}~i^\prime}\vec{S}_{j}(\tau)\cdot\vec{S}_{j^\prime}(\tau^\prime)~.
+\end{aligned}\end{equation}
+The effective action for the \(0,\bar 0\) system, in the limit of large coordination number, simplifies to
+\begin{equation}\begin{aligned}
+	S^{0,{\bar 0}}_\text{eff} =& \sum_{i=0,{\bar 0}}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau)  - t\sum_{{\bar 0},\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{0\sigma}(\tau)c_{{\bar 0}\sigma}(\tau) + \text{h.c.}\right] - \frac{U}{2}\sum_{i=0,{\bar 0}}\int_0^\beta\mathrm{d\tau}~\left(n_{i \uparrow}(\tau) - n_{i \downarrow}(\tau)\right)^2 \\
+				   &+ J\sum_{{\bar 0}}\int_0^\beta\mathrm{d\tau} \vec{S}_0(\tau)\cdot\vec{S}_{{\bar 0}}(\tau) + \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{ii^\prime}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
+\end{aligned}\end{equation}
+
+One can also write down an effective action purely for the local site \(0\).
+The sites \(\bar 0\) will now be a part of the environment action \(S^{(0)}\) instead of the system action, but since the system is thermodynamically large, the cavity action can be assumed to remain the same, such the expectation values are calculated in the same system.
+As a result, the hybridisation and susceptibility functions remain unchanged.
+\(S_\text{int}\) is now made of terms that connect \(0\) and \(\bar 0\), so the transformation from \(S^{(0,\bar 0)}\) can be made by replacing the set \(\left\{ j \right\} \) with the set \(\bar 0\), and the set \(\bar 0\) itself will be replaced by the local site \(0\).
+We quote the final form of the local effective action:
+\begin{equation}\begin{aligned}
+	S^{0}_\text{eff} =& \sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{0\sigma}(\tau)\partial_\tau c_{0\sigma}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{0\uparrow}(\tau) - n_{0\downarrow}(\tau)\right)^2 \\
+			  &+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\Delta_{00,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{00}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
+\end{aligned}\end{equation}
+
+\subsection{Local theory for the extended SIAM}
+The Hamiltonian for the extended SIAM model is shown in eq.~\ref{siam_attr}.
+We will denote the impurity with the label \(d\) and the bath sites with the label \(c\).
+Among the bath sites, we will represent the site coupled to the impurity with \(z\).
+The full action has the form
+\begin{equation}\begin{aligned}
+	S_\text{ES} = \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - t\sum_{\left<i,j \right> \in c,\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{i\sigma}(\tau)c_{j\sigma}(\tau) + \text{h.c.}\right] - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right]\\
++ J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{U_b}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 ~,
+\end{aligned}\end{equation}
+As in the Hubbard-Heisenberg model, we first obtain an effective action for the pair of sites \((d,z)\).
+As in the previous calculation, this will again generate a hybridisation function \(\Delta_{zz,\sigma}\) for the bath site nearest to the zeroth site.
+No susceptibility will be generated however, because there is no spin-exchange coupling within the bath.
+The net result is
+\begin{equation}\begin{aligned}
+	S^{d,z}_\text{eff} =& \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right] + J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) \\
+	&- \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{U_b}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 \\
+	&+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\sum_{\sigma}\Delta_{zz,\sigma}(\tau - \tau^\prime)c^\dagger_{z\sigma}(\tau)c_{z\sigma}(\tau^\prime)
+\end{aligned}\end{equation}
+This hybridisation \(\Delta_{zz,\sigma}\) is calculated in the cavity model of the eSIAM, obtained by removing the impurity and the zeroth site from the full model; it is a completely non-interacting system.
+
+One can go one step further and also remove the zeroth site in order to obtain a theory for the impurity site.
+With this choice, the cavity model now also includes the zeroth site, and hence contains the correlation term associated with \(U_b\).
+The one-particle connection \(V\) will lead to a modified hybridisation \(\mathcal{F}\) for this effective theory; the Kondo terms will generate a susceptibility.
+The resultant action is
+\begin{equation}\begin{aligned}
+	S^{d}_\text{eff} =& \sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{d\sigma}(\tau)\partial_\tau c_{d\sigma}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 \\
+			  &+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\mathcal{F}_{\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{d}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
+\end{aligned}\end{equation}
+where \(\mathcal{F}\) is defined in terms of the local correlator of the zeroth site
+\begin{equation}\begin{aligned}
+	\mathcal{F}_\sigma(\tau - \tau^\prime) = V^2 G_1^{(d)}\left(z\sigma\tau; z\sigma\tau^\prime\right) = V^2 \left<c_{z\sigma}(\tau)c^\dagger_{z\sigma}(\tau^\prime)\right>_{(d)}
+\end{aligned}\end{equation}
+with the average computed in the interacting cavity model that has the impurity site removed.
+The interaction arises from the \(U_b-\)term.
+The susceptibility is also calculated in this interacting cavity model, and follows the same definition as in the bulk model:
+\begin{equation}\begin{aligned}
+	\chi_{d}(\tau - \tau^\prime) = J^2\vec{S}_{z}(\tau)\cdot\vec{S}_{z}(\tau^\prime)~.
+\end{aligned}\end{equation}
 \section{Zero temperature Greens function in frequency domain}
@@
 The majority of the contribution will come from the state at \({\bf r_0}\), and improvements are then made by considering auxiliary models at further distances.
-
+\end{widetext}
 \bibliography{tilingProject}

### 2024-03-19 TilingProjectDraft/tilingProject.tex
updated real space Greens function section

@@
 Such a construction is shown in fig.~\ref{cluster-bath}.
-\begin{figure*}[!htb]
+\begin{figure}[!htb]
 	\centering
-	\includegraphics[width=0.5\textwidth]{cluster-bath.pdf}
+	\includegraphics[width=0.48\textwidth]{clusterBath.pdf}
 	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$.
@@
 	\label{cluster-bath}
-\end{figure*}
+\end{figure}
 \textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model}.
@@
  	\centering
- 	\includegraphics[width=0.48\textwidth]{gen_siam.pdf}
+ 	\includegraphics[width=0.4\textwidth]{gen_siam.pdf}
  	\caption{Cluster+bath construction of auxiliary model.
@@
 
-\subsection{Formal description of the tiling procedure}
+\subsection{Formal description of the tiling procedure}\label{formalDescription}
 We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian.
@@
 \begin{equation}\begin{aligned}\label{translationDefinition}
-	T^\dagger({\bf a}) \ket{\bf r_1, \bf r_2,\ldots} &= \ket{\bf r_1 + a, \bf r_2 + a,\ldots}\\
-	T^\dagger({\bf a}) \mathcal{O}\left(\bf r_1, \bf r_2,\ldots\right)T({\bf a}) &= \mathcal{O}\left(\bf r_1 + a, \bf r_2 + a,\ldots\right)~,
-\end{aligned}\end{equation}
-where \(\)
+	&T^\dagger({\bf a}) \ket{{\bf r}_1, {\bf r}_2,\ldots} = \ket{{\bf r}_1 + {\bf a}}\otimes\ket{{\bf r}_2 + {\bf a}}\ldots\otimes\ket{{\bf r}_n + {\bf a}}\\
+	&T^\dagger({\bf a}) \mathcal{O}\left({\bf r}_1, {\bf r}_2,\ldots\right)T({\bf a}) = \mathcal{O}\left({\bf r}_1 + {\bf a}, {\bf r}_2 + {\bf a},\ldots\right)~,
+\end{aligned}\end{equation}
+where \(\ket{{\bf r}_1, {\bf r}_2,\ldots}\) is a state in the manyparticle Fock-space basis with the particles localised at the specified positions.
 For example, for a local fermionic creation operator \(c^\dagger({\bf r})\), we have
 \begin{equation}\begin{aligned}
-	T^\dagger({\bf a}) c^\dagger({\bf r}) T({\bf a}) = c^\dagger({\bf r} + {\bf a})
+	T^\dagger({\bf a}) c^\dagger({\bf r}) T({\bf a}) = c^\dagger({\bf r} + {\bf a})~.
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
-translating all sites by the vector \({\bf a}\).
+translating all sites by the vector \({\bf a}\). By introducing the Fourier transform to momentum space,
+\begin{equation}\begin{aligned}
+	\ket{{\bf r}_1, {\bf r}_2,\ldots} = \otimes_{j=1}^N \int d{\bf k}_j e^{-i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf k}_j}~,
+\end{aligned}\end{equation}
+it is easy to see that the total momentum states are eigenstates of the global translation operators:
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a})\ket{{\bf k}_1, {\bf k}_2,\ldots} &= \otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} T^\dagger({\bf a})\ket{{\bf r}_j}~,\\
+							    &=\otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf r}_j + {\bf a}}\\
+							    &=e^{-i {\bf a}_j\cdot{\bf k}_\text{tot}}\ket{{\bf k}_1, {\bf k}_2,\ldots},
+\end{aligned}\end{equation}
+where \({\bf k}_\text{tot} = \sum_j {\bf k}_j\) is the total momentum.
+
 The auxiliary model, being an impurity model, lacks translation symmetry.
@@
 \end{aligned}\end{equation}
-where \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the mostly non-interacting conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site, \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 - V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath.
+where 
+\begin{itemize}
+	\item \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the mostly non-interacting conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site,
+	\item \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and
+	\item \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 - V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath.
+\end{itemize}
 Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath.
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{HH} &= -\frac{1}{\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 \\
-						  &- \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma} + \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j}~,
+	\mathcal{H}_\text{HH} &= -\frac{1}{\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+						  &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
 \end{aligned}\end{equation}
@@
 \section{Form of the eigenstates: Bloch's theorem}
-In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\bf k}({\bf r})} = \sum_{{\bf r}_i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_i({\bf r} - {\bf r}_i)}\).
-Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation \(T({\bf a})\) by some lattice distance \({\bf a}\):
-\begin{equation}\begin{aligned}
-	T({\bf a})\ket{\Psi_{{\bf k}}\left({\bf r}\right)} = \ket{\Psi_{{\bf k}}({\bf r} + {\bf a})} = e^{-i{\bf k}\cdot{\bf a}}\ket{\Psi({\bf r})}
-\end{aligned}\end{equation}
-These translation operators share eigenstates with the crystal momentum operator:
-\begin{equation}\begin{aligned}
-	T\left( {\bf r} \right) \ket{{\bf k}} = e^{-i {\bf k}\cdot{\bf r}} \ket{{\bf k}}~.
-\end{aligned}\end{equation}
-As a result, the eigenstates can be labelled using the crystal momentum value \({\bf k}\), along with a band index \(n\).
-The eigenstates \(\ket{\Psi_{{\bf k},n}}\) of the lattice Hamiltonians obtained using eq.~\ref{tilingPrescriptionFinal} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}).
-This means that the eigenstates \(\psi_n\left({\bf r}_d\right)\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) defined in eq.~\ref{unitCellHamiltonian} can be used to construct eigenstates of the lattice Hamiltonian.
+In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\bf k}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_i}\), where \({\bf r}_i\) sums over the positions of the local Hamiltonians.
+Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation by an arbitrary number of lattice spacings \({n\bf a}\):
+\begin{equation}\begin{aligned}
+	T^\dagger(n{\bf a})\ket{\Psi_{{\bf k}}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_{i + n}} = e^{-in{\bf k}\cdot{\bf a}}\ket{\Psi_{\bf k}}
+\end{aligned}\end{equation}
+The definition and some properties of these global translation operations were provided in subsection~\ref{formalDescription}.
+It was shown there that they share eigenstates with the total momentum operator.
+In a lattice model, this continuous symmetry gets lowered to its discrete form: the total {\it crystal} momentum is conserved by any scattering process.
+As a result, the eigenstates can be labelled using the combined index \(s = \left({\bf k}, n\right) \) where \({\bf k}\) is the total crystal momentum and \(n\) is a band index \(n\).
+
+The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using eq.~\ref{tilingPrescriptionFinal} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}).
+This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) defined in eq.~\ref{unitCellHamiltonian} can be used to construct eigenstates of the lattice Hamiltonian.
 The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
 
-The state \(\psi_n\left({\bf r}_d\right)\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself is an averaged Hamiltonian over \(\mathcal{Z}\) zeroth sites.
-Accordingly, we can express the averaged eigenstate \(\psi_n\left({\bf r}_d\right)\) as
+The state \(\ket{\psi_n\left({\bf r}_d\right)}\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself has been averaged over \(\mathcal{Z}\) zeroth sites.
+Accordingly, we can express the averaged eigenstate \(\ket{\psi_n\left({\bf r}_d\right)}\) as
 \begin{equation}\begin{aligned}
@@
 With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:
-\begin{equation}\begin{aligned}
-	\ket{\Psi_{{\bf k}, n}} = \frac{1}{\sqrt N}\sum_{{\bf r}} e^{i {\bf k}\cdot{\bf r}} \ket{\psi_{n}\left({\bf r}\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}, {\bf a}} e^{i {\bf k}\cdot{\bf r}} \ket{\psi_{n}\left({\bf r}, {\bf a}\right)}
-\end{aligned}\end{equation}
-where \(N\) is the total number of lattice sites.
+\begin{equation}\begin{aligned}\label{eigenstateProposal}
+	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} \\
+				&= \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d, {\bf z}\right)}~,
+\end{aligned}\end{equation}
+where \(N\) is the total number of lattice sites and \({\bf r}_d\) is summed over all lattice spacings.
 The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands.
-The ground state is obtained by setting \({\bf k}\) and \(n\) to 0:
-\begin{equation}\begin{aligned}
-	\ket{\Psi_\text{gs}} = \frac{1}{\sqrt N}\sum_{{\bf r}} e^{i {\bf k}\cdot{\bf r}} \ket{\psi_\text{gs}\left({\bf r}\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}, {\bf a}} e^{i {\bf k}\cdot{\bf r}} \ket{\psi_\text{gs}\left({\bf r}, {\bf a}\right)}
+The ground state \(s = s_0\) is obtained by setting \({\bf k}\) and \(n\) to 0:
+\begin{equation}\begin{aligned}
+	\ket{\Psi_\text{gs}} \equiv \ket{\Psi_{s_0}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)} \\
+			     &= \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d, {\bf z}\right)}
 \end{aligned}\end{equation}
@@
 \section{Mapping greens functions from the bulk to the auxiliary model}
-In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{gs}}\) of the auxiliary models.
+In the previous part, we proposed a form for the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{gs}}\) of the auxiliary models.
 In this section, we will relate real-space Greens functions of the bulk lattice to those of the auxiliary model.
@@
 \end{aligned}\end{equation}
-where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(T\): \(c({\bf r},t) = e^{iT H_\text{tiled} }c({\bf r})e^{-i T H_\text{tiled}}\).
-By introducing the Fourier transform \(\tilde G({\bf r}_2 - {\bf r}_1, T) = \int d\omega~\tilde G({\bf r}_2 - {\bf r}_1, \omega)\), the frequency-domain Greens function can be cast in its spectral representation
-\begin{equation}\begin{aligned}
-	\tilde G({\bf r}_2 - {\bf r}_1, \omega) = \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0 \in \text{GS}}\sum_n \left[\frac{\braket{n_0|c({\bf r}_2)|n}\braket{n|c^\dagger({\bf r}_1)|n_0}}{\omega + E_\text{gs} - E_n} \right.\\
-\left.+ \frac{\braket{n_0|c^\dagger({\bf r}_1)|n}\braket{n|c({\bf r}_2)|n_0}}{\omega - E_\text{gs} + E_n}\right] ~,
-\end{aligned}\end{equation}
-where \(n_0\) sums over the ground state(s) of the system, \(n\) sums over all eigenstates and \(\mathcal{D}_\text{gs}\) is the groundstate degeneracy.
+where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(T\): 
+\begin{equation}\begin{aligned}
+	c({\bf r},t) = e^{iT H_\text{tiled} }c({\bf r})e^{-i T H_\text{tiled}}~.
+\end{aligned}\end{equation}
+By introducing the Fourier transform \(g(T) = \int d\omega~ e^{-i\omega T}f(\omega)\), the frequency-domain Greens function can be cast in its spectral representation
+\begin{equation}\begin{aligned}\label{spectralRepresentation}
+	&\tilde G({\bf r}_2 - {\bf r}_1, \tilde\omega) \\
+	&= \frac{1}{\mathcal{D}_\text{gs}}\sum_{s_0 \in \text{GS}}\sum_s \left[\frac{F_p^*(s, {\bf r}_2)F_p(s, {\bf r}_1)}{\tilde\omega - \left( \tilde E_s - \tilde E_\text{gs} \right) } + \frac{F_h(s, {\bf r}_1)F_h^*(s, {\bf r}_2)}{\tilde\omega + \left( \tilde E_s - \tilde E_\text{gs} \right) }\right] ~,
+\end{aligned}\end{equation}
+where \(s_0=\left({\bf k}_0, n_0\right)\) sums over the ground state(s) of the system (with energy \(\tilde E_\text{gs}\) and degeneracy \(\mathcal{D}_\text{gs}\)) and \(s=\left({\bf k}, n\right)\) sums over all eigenstates (with energies \(\tilde E_s\)).
+The coefficients \(F_p(s, {\bf r}) = \braket{\Psi_{s}|c^\dagger({\bf r})|\Psi_{s_0}}\) and \(F_h(s, {\bf r}) = \braket{\Psi_{s}|c({\bf r})|\Psi_{s_0}}\) represent spectral weights for particle and hole excitations from the ground state \(\ket{s_0}\) into the excited state \(\ket{s}\).
+
+In order to make contact with the auxiliary models, the first simplification  that we carry out is of the eigenenergies \(\tilde E_s\)in the denominators.
+The label \(s\) involves a total momentum \({\bf k}\) and a band index \(n\).
+Guided by the relation eq.~\ref{tilingPrescriptionFinal} between the Hamiltonians, we assume a separation of the total energy into an impurity model contribution \(E_n\) coming from \(\mathcal{H}_\text{aux}\) and a contribution \(\varepsilon({\bf k})\) coming from the non-interacting background Hamiltonian \(\mathcal{H}_\text{cbath-nint}\):
+\begin{equation}\begin{aligned}
+	E_s \simeq N E_n + (N-3) \varepsilon_{\bf k}~.
+\end{aligned}\end{equation}
+where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\).
+Replacing \(N-3\) with \(N\) for a system of large number of particles, the spectral representation can be written as
+\begin{equation}\begin{aligned}
+	&\tilde G({\bf r}_2 - {\bf r}_1, \tilde\omega) \\
+	&= \frac{1}{\mathcal{D}_\text{gs}}\sum_{s_0 \in \text{GS}}\sum_s \left[\frac{F_p^*(s, {\bf r}_2)F_p(s, {\bf r}_1)}{\tilde\omega - N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) } \right.\\
+	&\left. + \frac{F_h(s, {\bf r}_1)F_h^*(s, {\bf r}_2)}{\tilde\omega + N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) }\right] ~,
+\end{aligned}\end{equation}
+where the absence of the tilde in the denominators indicates that those energies arise from the auxiliary model Hamiltonian.
+
+In order to rewrite this expression in terms of quantities that can be computed purely from the auxiliary models, we replace the eigenstates with the forms given in eq.~\ref{eigenstateProposal}:
+\begin{equation}\begin{aligned}\label{spectralWeightsAuxiliary}
+	F_p^*(s, {\bf r}_2) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{i {\bf k}\cdot{\bf r}_d - {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_{n_0}({\bf r}_d^\prime)|c({\bf r}_2)|\psi_{n}({\bf r}_d)}\\
+	F_p(s, {\bf r}_1) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{-i {\bf k}\cdot{\bf r}_d + {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_n({\bf r}_d)|c^\dagger({\bf r}_1)|\psi_{n_0}({\bf r}_d^\prime)}~,
+\end{aligned}\end{equation}
+where \({\bf k}_0\) is the crystal momentum value in the ground state.
+
+Within the impurity model, the lattice site that most closely resembles the bulk lattice model is of course the impurity site; in order to ensure that all terms in eq.~\ref{spectralRepresentation} involve the impurity site, we approximate the states within \(F_p(s,{\bf r}_1)\) of eq.~\ref{spectralWeightsAuxiliary} purely in terms of the auxiliary model at \({\bf r}_1\):
+\begin{equation}\begin{aligned}
+	\ket{\Psi_s} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} \left[e^{i {\bf k}\cdot{\bf r}_1} \ket{\psi_{n}\left({\bf r}_1\right)} + \ket{\psi_{n}}_\text{diff}\right]\\
+		     &\simeq \sqrt N e^{i {\bf k}\cdot{\bf r}_1} \ket{\psi_{n}\left({\bf r}_1\right)}.
+\end{aligned}\end{equation}
+This amounts to retaining the spatially uniform part of the wavefunction and dropping the modulating difference term \(\ket{\psi_{n}}_\text{diff} = e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} - e^{i {\bf k}\cdot{\bf r}_1} \ket{\psi_{n}\left({\bf r}_1\right)}\).
+Replacing the exact forms in \(F_p(s, {\bf r}_1)\) with this approximation results in the expression
+\begin{equation}\begin{aligned}
+	F_p(s, {\bf r}_1) \simeq N e^{-i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_1} \braket{\psi_n({\bf r}_1)|c^\dagger({\bf r}_1)|\psi_{n_0}({\bf r}_1)}~.
+\end{aligned}\end{equation}
+For the other term, we make the less drastic approximation of retaining the matrix elements between the same auxiliary models \({\bf r}_d = {\bf r}_d^\prime\), leading to
+\begin{equation}\begin{aligned}
+	F_p^*(s, {\bf r}_2) = \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_d)|c({\bf r}_2)|\psi_{n}({\bf r}_d)}~.
+\end{aligned}\end{equation}
+The summation can be transferred on to the annihilation operator by using translation operators:
+\begin{equation}\begin{aligned}
+	&\braket{\psi_{n_0}({\bf r}_d)|c({\bf r}_2)|\psi_{n}({\bf r}_d)} \\
+	&= \braket{\psi_{n_0}({\bf r}_1)|T\left({\bf r}_d - {\bf r}_1\right) c({\bf r}_2) T^\dagger\left({\bf r}_d - {\bf r}_1\right) |\psi_{n}({\bf r}_1)}\\
+	&= \braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_2 - {\bf r}_1 + {\bf r}_d) |\psi_{n}({\bf r}_1)}~,
+\end{aligned}\end{equation}
+leading to the more useful form
+\begin{equation}\begin{aligned}
+	&F_p^*(s, {\bf r}_2) \\
+	&= \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_2 - {\bf r}_1 + {\bf r}_d) |\psi_{n}({\bf r}_1)}\\
+	&= \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_1 - {\bf r}_2 + {\bf r}_d\right)} \braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_d) |\psi_{n}({\bf r}_1)}~.
+\end{aligned}\end{equation}
+In the second step, we redefined the dummy variable \({\bf r}_d \to {\bf r}_d - {\bf r}_2 + {\bf r}_1\).
+We make similar simplifications in the hole excitation coefficients \(F_h\) and \(F_h^*\) as well.
+
+The complete expression for \(\tilde G_\text{loc}(\tilde\omega)\) now looks like
+\begin{widetext}
+\begin{equation}\begin{aligned}
+	\tilde G({\bf r}_2 - {\bf r}_1, \tilde\omega) &= \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,{\bf k}_0}\sum_{{\bf k}, n}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_d - {\bf r}_2\right)} \left[\frac{\braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_d) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c^\dagger({\bf r}_1)|\psi_{n_0}({\bf r}_1)}}{\tilde\omega - N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) } \right.\\
+					  &\left.+ \frac{\braket{\psi_{n_0}({\bf r}_1)| c^\dagger({\bf r}_1) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c({\bf r}_d)|\psi_{n_0}({\bf r}_1)}}{\tilde\omega + N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) }\right] ~,\\
+					  &= \frac{1}{N}\sum_{{\bf k}_0, {\bf k}}\sum_{{\bf r}_d} e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_d\right)} \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,n}\left[\frac{\braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_d) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c^\dagger({\bf r}_1)|\psi_{n_0}({\bf r}_1)}}{\omega - \left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) } \right.\\
+					  &\left.+ \frac{\braket{\psi_{n_0}({\bf r}_1)| c^\dagger({\bf r}_1) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c({\bf r}_d)|\psi_{n_0}({\bf r}_1)}}{\omega + \left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) }\right] ~,
+\end{aligned}\end{equation}
+\end{widetext}
+where \(\omega = \tilde\omega/N\) is the frequency scale for the auxiliary model.
+We can define partial Greens functions \(G_p({\bf r}_d, {\bf r}_1)\) and \(G_h({\bf r}_d, {\bf r}_1)\) for the auxiliary model that involve only the positive and negative frequency poles respectively.
+In terms of these, the lattice model Greens function can be written in a more intuitive form.
+Assuming a unique momentum \({\bf k}_0\) for the ground state and adjusting the ground state non-interacting energy \(\varepsilon_{{\bf k}0}\) to zero, we get
+\begin{equation}\begin{aligned}
+	\tilde G({\bf r}_2 - {\bf r}_1, \tilde\omega) &= \frac{1}{N}\sum_{{\bf k}}\sum_{{\bf r}_d} e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_d\right)} \\
+					  &\times\left[G_p\left({\bf r}_d,{\bf r}_1;\omega - \varepsilon_{\bf k}\right) + G_h\left({\bf r}_d,{\bf r}_1;\omega + \varepsilon_{\bf k}\right)\right]
+\end{aligned}\end{equation}
+
+\subsection{Nearest-neighbour Greens function}
 

### 2024-03-19 TilingProjectDraft/tilingProject.tex
completed kspace Greens function

@@
 \centering
-\includegraphics[width=0.5\textwidth]{dos_diff.pdf}
+\includegraphics[width=0.45\textwidth]{dos_diff.pdf}
 \caption{Various kinds of bath that an impurity can hybridise into.
@@
 
-\section{Creating a Hubbard-Heisenberg Hamiltonian from an extended Anderson impurity model}
+\section{The Tiling Algorithm}
 
@@
 In the previous part, we proposed a form for the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{gs}}\) of the auxiliary models.
-In this section, we will relate real-space Greens functions of the bulk lattice to those of the auxiliary model.
+In this section, we will relate one-particle Greens functions of the bulk lattice to those of the auxiliary model.
 We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
-We define the time-domain Greens function between two points \({\bf r}_1\) and \({\bf r}_2 \) at zero temperature as
-\begin{equation}\begin{aligned}
-	\tilde G({\bf r}_2 - {\bf r}_1, T) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c({\bf r}_2, T), c^\dagger({\bf r}_1) \right\} | \Psi_\text{gs}}~.
+We define the time-domain Greens function between two quantum numbers \(\nu_1\) and \(\nu_2 \) at zero temperature as
+\begin{equation}\begin{aligned}
+	\tilde G(\nu_2, \nu_1; T) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c(\nu_2, T), c^\dagger(\nu_1) \right\} | \Psi_\text{gs}}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	c({\bf r},t) = e^{iT H_\text{tiled} }c({\bf r})e^{-i T H_\text{tiled}}~.
-\end{aligned}\end{equation}
+	c(\nu,t) = e^{iT H_\text{tiled} }c(\nu)e^{-i T H_\text{tiled}}~.
+\end{aligned}\end{equation}
+The quantum number \(\nu\) typically refers to position or momentum: setting \(\nu_1={\bf r}_1, \nu_2={\bf r}_2\) will lead to a real-space Greens function between the two spatial points.
 By introducing the Fourier transform \(g(T) = \int d\omega~ e^{-i\omega T}f(\omega)\), the frequency-domain Greens function can be cast in its spectral representation
 \begin{equation}\begin{aligned}\label{spectralRepresentation}
-	&\tilde G({\bf r}_2 - {\bf r}_1, \tilde\omega) \\
-	&= \frac{1}{\mathcal{D}_\text{gs}}\sum_{s_0 \in \text{GS}}\sum_s \left[\frac{F_p^*(s, {\bf r}_2)F_p(s, {\bf r}_1)}{\tilde\omega - \left( \tilde E_s - \tilde E_\text{gs} \right) } + \frac{F_h(s, {\bf r}_1)F_h^*(s, {\bf r}_2)}{\tilde\omega + \left( \tilde E_s - \tilde E_\text{gs} \right) }\right] ~,
+	&\tilde G(\nu_2, \nu_1; \tilde\omega) \\
+	&= \frac{1}{\mathcal{D}_\text{gs}}\sum_{s_0 \in \text{GS}}\sum_s \left[\frac{F_p^*(s, \nu_2)F_p(s, \nu_1)}{\tilde\omega - \left( \tilde E_s - \tilde E_\text{gs} \right) } + \frac{F_h(s, \nu_1)F_h^*(s, \nu_2)}{\tilde\omega + \left( \tilde E_s - \tilde E_\text{gs} \right) }\right] ~,
 \end{aligned}\end{equation}
 where \(s_0=\left({\bf k}_0, n_0\right)\) sums over the ground state(s) of the system (with energy \(\tilde E_\text{gs}\) and degeneracy \(\mathcal{D}_\text{gs}\)) and \(s=\left({\bf k}, n\right)\) sums over all eigenstates (with energies \(\tilde E_s\)).
-The coefficients \(F_p(s, {\bf r}) = \braket{\Psi_{s}|c^\dagger({\bf r})|\Psi_{s_0}}\) and \(F_h(s, {\bf r}) = \braket{\Psi_{s}|c({\bf r})|\Psi_{s_0}}\) represent spectral weights for particle and hole excitations from the ground state \(\ket{s_0}\) into the excited state \(\ket{s}\).
+The coefficients \(F_p(s, \nu) = \braket{\Psi_{s}|c^\dagger(\nu)|\Psi_{s_0}}\) and \(F_h(s, \nu) = \braket{\Psi_{s}|c(\nu)|\Psi_{s_0}}\) represent spectral weights for particle and hole excitations from the ground state \(\ket{s_0}\) into the excited state \(\ket{s}\).
 
@@
 The label \(s\) involves a total momentum \({\bf k}\) and a band index \(n\).
-Guided by the relation eq.~\ref{tilingPrescriptionFinal} between the Hamiltonians, we assume a separation of the total energy into an impurity model contribution \(E_n\) coming from \(\mathcal{H}_\text{aux}\) and a contribution \(\varepsilon({\bf k})\) coming from the non-interacting background Hamiltonian \(\mathcal{H}_\text{cbath-nint}\):
-\begin{equation}\begin{aligned}
-	E_s \simeq N E_n + (N-3) \varepsilon_{\bf k}~.
-\end{aligned}\end{equation}
-where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\).
+Guided by the relation eq.~\ref{tilingPrescriptionFinal} between the Hamiltonians, we assume a separation of the total energy into an impurity model contribution \(E_n\) coming from \(\mathcal{H}_\text{aux}\) and a contribution \(\varepsilon({\bf k})\) coming from the non-interacting background Hamiltonian \(\mathcal{H}_\text{cbath-nint}\): \(E_s \simeq N E_n + (N-3) \varepsilon_{\bf k}\)~, where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\).
 Replacing \(N-3\) with \(N\) for a system of large number of particles, the spectral representation can be written as
 \begin{equation}\begin{aligned}
-	&\tilde G({\bf r}_2 - {\bf r}_1, \tilde\omega) \\
-	&= \frac{1}{\mathcal{D}_\text{gs}}\sum_{s_0 \in \text{GS}}\sum_s \left[\frac{F_p^*(s, {\bf r}_2)F_p(s, {\bf r}_1)}{\tilde\omega - N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) } \right.\\
-	&\left. + \frac{F_h(s, {\bf r}_1)F_h^*(s, {\bf r}_2)}{\tilde\omega + N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) }\right] ~,
+	&\tilde G(\nu_2, \nu_1; \tilde\omega) \\
+	&= \frac{1}{\mathcal{D}_\text{gs}}\sum_{s_0 \in \text{GS}}\sum_s \left[\frac{F_p^*(s, \nu_2)F_p(s, \nu_1)}{\tilde\omega - N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) } \right.\\
+	&\left. + \frac{F_h(s, \nu_1)F_h^*(s, \nu_2)}{\tilde\omega + N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) }\right] ~,
 \end{aligned}\end{equation}
 where the absence of the tilde in the denominators indicates that those energies arise from the auxiliary model Hamiltonian.
-
 In order to rewrite this expression in terms of quantities that can be computed purely from the auxiliary models, we replace the eigenstates with the forms given in eq.~\ref{eigenstateProposal}:
 \begin{equation}\begin{aligned}\label{spectralWeightsAuxiliary}
-	F_p^*(s, {\bf r}_2) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{i {\bf k}\cdot{\bf r}_d - {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_{n_0}({\bf r}_d^\prime)|c({\bf r}_2)|\psi_{n}({\bf r}_d)}\\
-	F_p(s, {\bf r}_1) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{-i {\bf k}\cdot{\bf r}_d + {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_n({\bf r}_d)|c^\dagger({\bf r}_1)|\psi_{n_0}({\bf r}_d^\prime)}~,
+	&F_p^*(s, \nu_2) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{i {\bf k}\cdot{\bf r}_d - {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_{n_0}({\bf r}_d^\prime)|c(\nu_2)|\psi_{n}({\bf r}_d)}\\
+	&F_p(s, \nu_1) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{-i {\bf k}\cdot{\bf r}_d + {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_n({\bf r}_d)|c^\dagger(\nu_1)|\psi_{n_0}({\bf r}_d^\prime)}~,
 \end{aligned}\end{equation}
@@
 
-Within the impurity model, the lattice site that most closely resembles the bulk lattice model is of course the impurity site; in order to ensure that all terms in eq.~\ref{spectralRepresentation} involve the impurity site, we approximate the states within \(F_p(s,{\bf r}_1)\) of eq.~\ref{spectralWeightsAuxiliary} purely in terms of the auxiliary model at \({\bf r}_1\):
+\subsection{Real-space Greens functions}
+We first consider one-particle Greens functions for the propagation of excitations between two spatial points \(\nu_1={\bf r}_1\) and \(\nu_2={\bf r}_2\).
+Within the impurity model, the lattice site that most closely resembles the bulk lattice model is of course the impurity site; in order to ensure that all terms in eq.~\ref{spectralRepresentation} involve the impurity site, we approximate the states within \(F_p(s,\nu_1) = F_p(s,{\bf r}_1)\) of eq.~\ref{spectralWeightsAuxiliary} purely in terms of the auxiliary model at \({\bf r}_1\):
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-For the other term, we make the less drastic approximation of retaining the matrix elements between the same auxiliary models \({\bf r}_d = {\bf r}_d^\prime\), leading to
+For the other term \(F_p(s,\nu_2) = F_p(s,{\bf r}_2)\), we make the less drastic approximation of retaining the matrix elements between the same auxiliary models \({\bf r}_d = {\bf r}_d^\prime\), leading to
 \begin{equation}\begin{aligned}
@@
 	&= \braket{\psi_{n_0}({\bf r}_1)|T\left({\bf r}_d - {\bf r}_1\right) c({\bf r}_2) T^\dagger\left({\bf r}_d - {\bf r}_1\right) |\psi_{n}({\bf r}_1)}\\
-	&= \braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_2 - {\bf r}_1 + {\bf r}_d) |\psi_{n}({\bf r}_1)}~,
+	&= \braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_2 + {\bf r}_1 - {\bf r}_d) |\psi_{n}({\bf r}_1)}~,
 \end{aligned}\end{equation}
@@
 	&F_p^*(s, {\bf r}_2) \\
-	&= \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_2 - {\bf r}_1 + {\bf r}_d) |\psi_{n}({\bf r}_1)}\\
-	&= \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_1 - {\bf r}_2 + {\bf r}_d\right)} \braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_d) |\psi_{n}({\bf r}_1)}~.
-\end{aligned}\end{equation}
-In the second step, we redefined the dummy variable \({\bf r}_d \to {\bf r}_d - {\bf r}_2 + {\bf r}_1\).
-We make similar simplifications in the hole excitation coefficients \(F_h\) and \(F_h^*\) as well.
+	&= \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_2 + {\bf r}_1 - {\bf r}_d) |\psi_{n}({\bf r}_1)}\\
+	&= \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_1 + {\bf r}_2 - {\bf r}_d\right)} \braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_d) |\psi_{n}({\bf r}_1)}~.
+\end{aligned}\end{equation}
+In the second step, we redefined the dummy variable \({\bf r}_d \to {\bf r}_1 + {\bf r}_2 - {\bf r}_d\).
+
+Having obtained the particle spectral coefficients, we can obtain the hole counterparts by mapping them onto each other.
+This can be done by noting that under our assumptions of \({\bf r}_d = {\bf r}_d^\prime\) in eq.~\ref{spectralWeightsAuxiliary}, we have the following relations:
+\begin{equation}\begin{aligned}
+	F_h &= F_p^*\left({\bf k}\leftrightarrow{\bf k}_0, n \leftrightarrow n_0\right),\\
+	F_h^* &= F_p\left({\bf k}\leftrightarrow{\bf k}_0, n \leftrightarrow n_0\right)~.
+\end{aligned}\end{equation}
+Using these, we get
+\begin{equation}\begin{aligned}\label{spectralParticleHoleRelation}
+	F_h &= \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}_0- {\bf k}\right)\cdot\left({\bf r}_1 + {\bf r}_2 - {\bf r}_d\right)} \braket{\psi_{n}({\bf r}_1)| c({\bf r}_d) |\psi_{n_0}({\bf r}_1)},\\
+	F_h^* &= N e^{-i \left({\bf k}_0 - {\bf k}\right)\cdot{\bf r}_1} \braket{\psi_{n_0}({\bf r}_1)|c^\dagger({\bf r}_1)|\psi_{n}({\bf r}_1)}~.
+\end{aligned}\end{equation}
 
@@
 \begin{equation}\begin{aligned}
-	\tilde G({\bf r}_2 - {\bf r}_1, \tilde\omega) &= \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,{\bf k}_0}\sum_{{\bf k}, n}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_d - {\bf r}_2\right)} \left[\frac{\braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_d) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c^\dagger({\bf r}_1)|\psi_{n_0}({\bf r}_1)}}{\tilde\omega - N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) } \right.\\
-					  &\left.+ \frac{\braket{\psi_{n_0}({\bf r}_1)| c^\dagger({\bf r}_1) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c({\bf r}_d)|\psi_{n_0}({\bf r}_1)}}{\tilde\omega + N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) }\right] ~,\\
-					  &= \frac{1}{N}\sum_{{\bf k}_0, {\bf k}}\sum_{{\bf r}_d} e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_d\right)} \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,n}\left[\frac{\braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_d) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c^\dagger({\bf r}_1)|\psi_{n_0}({\bf r}_1)}}{\omega - \left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) } \right.\\
-					  &\left.+ \frac{\braket{\psi_{n_0}({\bf r}_1)| c^\dagger({\bf r}_1) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c({\bf r}_d)|\psi_{n_0}({\bf r}_1)}}{\omega + \left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) }\right] ~,
+	\tilde G({\bf r}_2 - {\bf r}_1; \tilde\omega) &= \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,{\bf k}_0}\sum_{{\bf k}, n}\sum_{{\bf r}_d}  \left[e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_d\right)}\frac{\braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_d) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c^\dagger({\bf r}_1)|\psi_{n_0}({\bf r}_1)}}{\tilde\omega - N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) } \right.\\
+					  &\left.+ e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_d\right)}\frac{\braket{\psi_{n_0}({\bf r}_1)| c^\dagger({\bf r}_1) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c({\bf r}_d)|\psi_{n_0}({\bf r}_1)}}{\tilde\omega + N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) }\right] ~,\\
+					  &= \frac{1}{N}\sum_{{\bf k}_0, {\bf k}}\sum_{{\bf r}_d}  \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,n}\left[e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_d\right)}\frac{\braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_d) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c^\dagger({\bf r}_1)|\psi_{n_0}({\bf r}_1)}}{\omega - \left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) } \right.\\
+					  &\left.+ e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_d\right)}\frac{\braket{\psi_{n_0}({\bf r}_1)| c^\dagger({\bf r}_1) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c({\bf r}_d)|\psi_{n_0}({\bf r}_1)}}{\omega + \left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) }\right] ~,
 \end{aligned}\end{equation}
@@
 Assuming a unique momentum \({\bf k}_0\) for the ground state and adjusting the ground state non-interacting energy \(\varepsilon_{{\bf k}0}\) to zero, we get
-\begin{equation}\begin{aligned}
-	\tilde G({\bf r}_2 - {\bf r}_1, \tilde\omega) &= \frac{1}{N}\sum_{{\bf k}}\sum_{{\bf r}_d} e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_d\right)} \\
-					  &\times\left[G_p\left({\bf r}_d,{\bf r}_1;\omega - \varepsilon_{\bf k}\right) + G_h\left({\bf r}_d,{\bf r}_1;\omega + \varepsilon_{\bf k}\right)\right]
-\end{aligned}\end{equation}
-
-\subsection{Nearest-neighbour Greens function}
+\begin{equation}\begin{aligned}\label{GreensFunctionRealSpace}
+	&\tilde G({\bf r}_2 - {\bf r}_1; \tilde\omega) \\
+	&= \frac{1}{N}\sum_{{\bf k}}\sum_{{\bf r}_d}  \left[e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_d\right)}G_p\left({\bf r}_d,{\bf r}_1;\omega - \varepsilon_{\bf k}\right) \right.\\
+	&\left.+ e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_d\right)}G_h\left({\bf r}_d,{\bf r}_1;\omega + \varepsilon_{\bf k}\right)\right]
+\end{aligned}\end{equation}
+
+\subsection{Momentum-space Greens functions}
+We now consider Greens functions at a particular momentum \({\bf K}\), obtained by setting \(\nu_1=\nu_2={\bf K}\). The spectral coefficients are of the form
+\begin{equation}\begin{aligned}
+	F_p^*(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{i {\bf k}\cdot{\bf r}_d - {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_{n_0}({\bf r}_d^\prime)|c({\bf K})|\psi_{n}({\bf r}_d)}\\
+	F_p(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{-i {\bf k}\cdot{\bf r}_d + {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_n({\bf r}_d)|c^\dagger({\bf K})|\psi_{n_0}({\bf r}_d^\prime)}~.
+\end{aligned}\end{equation}
+Similar to the approach for the real-space Greens function, we simplify \(F^*_p(s, {\bf K})\) by retaining only the \({\bf r}_d = {\bf r}_d^\prime\) members, and then translating the arbitrary point \({\bf r}_d\) to a common reference point \({\bf r}_c\) in the lattice:
+\begin{equation}\begin{aligned}
+	&F_p^*(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_d)|c({\bf K})|\psi_{n}({\bf r}_d)}~,\\
+	&\braket{\psi_{n_0}({\bf r}_d)|c({\bf K})|\psi_{n}({\bf r}_d)}\\
+	&= \braket{\psi_{n_0}({\bf r}_c)| T\left({\bf r}_d - {\bf r}_c\right) c({\bf K}) T^\dagger\left({\bf r}_d - {\bf r}_c\right) |\psi_{n}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+The effect of the translation operators on the \(k-\)space annihilation operator can be easily deduced by transforming it to real-space, using the Fourier transform definition
+\begin{equation}\begin{aligned}\label{fourTransf}
+	c({\bf K}) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r})~.
+\end{aligned}\end{equation}
+Upon applying this, we get
+\begin{equation}\begin{aligned}
+	&T\left({\bf r}_d - {\bf r}_c\right) c({\bf K}) T^\dagger\left({\bf r}_d - {\bf r}_c\right)\\
+	&= \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}T\left({\bf r}_d - {\bf r}_c\right) c({\bf r}) T^\dagger\left({\bf r}_d - {\bf r}_c\right)\\
+	&= \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r} - {\bf r}_d + {\bf r}_c)\\
+	&= e^{-i{\bf K}\cdot\left({\bf r}_d - {\bf r}_c\right)}c({\bf K})~.
+\end{aligned}\end{equation}
+With this, the final form of \(F_p^*(s, {\bf K})\) becomes
+\begin{equation}\begin{aligned}
+	F_p^*(s, {\bf K}) = \frac{1}{N}e^{i {\bf K}\cdot{\bf r}_c}\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}\\
+	\times\sum_{{\bf r}_d}e^{i \left(-{\bf K} + {\bf k} - {\bf k}_0\right)\cdot{\bf r}_d}
+\end{aligned}\end{equation}
+The sum over \({\bf r}_d\) evaluates to \(\sum_{{\bf r}_d}e^{i \left({\bf K} + {\bf k} - {\bf k}_0\right)\cdot{\bf r}_d} = N \delta_{{\bf K}, {\bf k} - {\bf k}_0}\), leading to
+\begin{equation}\begin{aligned}
+	F_p^*(s, {\bf K}) = e^{i {\bf K}\cdot{\bf r}_c}\delta_{{\bf K}, {\bf k} - {\bf k}_0}\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}
+\end{aligned}\end{equation}
+
+For the other coefficient \(F_p(s, {\bf K})\), we again proceed similar to the previous subsection: we retain only the uniform part of the wavefunction, placing all the impurity models at the reference point \({\bf r}_c\):
+\begin{equation}\begin{aligned}
+	F_p(s, {\bf K}) = Ne^{-i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_c} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf K})|\psi_{n_0}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+In order to introduce the impurity site operator in the expression, we Fourier transform \(c^\dagger({\bf K})\) (following eq.~\ref{fourTransf}), and keep only that real-space mode that lies on the impurity reference point \({\bf r}_c\):
+\begin{equation}\begin{aligned}
+	F_p(s, {\bf K}) = e^{-i \left({\bf k} - {\bf k}_0 + {\bf K}\right)\cdot{\bf r}_c} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+
+Using eq.~\ref{spectralParticleHoleRelation}, we obtain the hole transition coefficients:
+\begin{equation}\begin{aligned}
+	F_h(s, {\bf K}) &= e^{i {\bf K}\cdot{\bf r}_c}\delta_{-{\bf K}, {\bf k} - {\bf k}_0}\braket{\psi_{n}({\bf r}_c)|c({\bf K})|\psi_{n_0}({\bf r}_c)},\\
+	F_h^*(s, {\bf K}) &= e^{-i \left({\bf k}_0 - {\bf k} + {\bf K}\right)\cdot{\bf r}_c} \braket{\psi_{n_0}({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+
+The complete expression for the momentum space Greens function is therefore
+\begin{widetext}
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}; \tilde\omega) = \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,{\bf k}_0 \in \text{GS}}\sum_{n,{\bf k}} e^{-i {\bf K}\cdot{\bf r}_c}\left[\delta_{{\bf K}, {\bf k} - {\bf k}_0}\frac{\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}\braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}}{\tilde\omega - N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) } \right.
+\\
+	+ \left.\delta_{{\bf K}, -{\bf k} + {\bf k}_0}\frac{\braket{\psi_{n}({\bf r}_c)|c({\bf K})|\psi_{n_0}({\bf r}_c)}\braket{\psi_{n_0}({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n}({\bf r}_c)}}{\tilde\omega + N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) }\right] ~.
+\end{aligned}\end{equation}
+\end{widetext}
+Once again assuming the uniqueness of \({\bf k}_0\), setting \(\varepsilon_{{\bf k}0}\) to zero and choosing the reference point \({\bf r}_c\) such that \({\bf K}\cdot{\bf r}_c = 0\), we have
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}; \tilde\omega) = G_p\left({\bf r}_c, {\bf K}; \omega - \varepsilon_{{\bf k}_0 + {\bf K}}\right) + G_h\left({\bf r}_c, {\bf K}; \omega + \varepsilon_{{\bf k}_0 - {\bf K}}\right).
+\end{aligned}\end{equation}
+As a consistency check, one can Fourier transform the expression in eq.~\ref{GreensFunctionRealSpace} to recover the above expression.
 

### 2024-03-21 TilingProjectDraft/tilingProject.tex
completed updating the tiling relations

--- 2024-03-19 TilingProjectDraft/tilingProject.tex
@@
 \begin{itemize}
-	\item \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the mostly non-interacting conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site,
+	\item \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site,
 	\item \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and
@@
 The ground state \(s = s_0\) is obtained by setting \({\bf k}\) and \(n\) to 0:
-\begin{equation}\begin{aligned}
+\begin{equation}\begin{aligned}\label{groundstateProposal}
 	\ket{\Psi_\text{gs}} \equiv \ket{\Psi_{s_0}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)} \\
@@
 
-\section{Mapping greens functions from the bulk to the auxiliary model}
+\section{1-particle Greens Functions}
 In the previous part, we proposed a form for the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{gs}}\) of the auxiliary models.
-In this section, we will relate real-space Greens functions of the bulk lattice to those of the auxiliary model.
+In this section, we will relate one-particle Greens functions of the bulk lattice to those of the auxiliary model.
 We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
-We define the time-domain Greens function between two points \({\bf r}_1\) and \({\bf r}_2 \) at zero temperature as
-\begin{equation}\begin{aligned}
-	\tilde G({\bf r}_2 - {\bf r}_1, T) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c({\bf r}_2, T), c^\dagger({\bf r}_1) \right\} | \Psi_\text{gs}}~.
+We define the retarded time-domain Greens function between two quantum numbers \(\nu_1\) and \(\nu_2 \) at zero temperature as
+\begin{equation}\begin{aligned}
+	\tilde G(\nu_2, \nu_1; T) = -i\theta(T) \braket{\Psi_\text{gs} | \left\{ c(\nu_2, T), c^\dagger(\nu_1) \right\} | \Psi_\text{gs}}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	c({\bf r},t) = e^{iT H_\text{tiled} }c({\bf r})e^{-i T H_\text{tiled}}~.
-\end{aligned}\end{equation}
+	c(\nu,t) = e^{iT H_\text{tiled} }c(\nu)e^{-i T H_\text{tiled}}~.
+\end{aligned}\end{equation}
+The quantum number \(\nu\) typically refers to position or momentum: setting \(\nu_1={\bf r}_1, \nu_2={\bf r}_2\) will lead to a real-space Greens function between the two spatial points.
 By introducing the Fourier transform \(g(T) = \int d\omega~ e^{-i\omega T}f(\omega)\), the frequency-domain Greens function can be cast in its spectral representation
 \begin{equation}\begin{aligned}\label{spectralRepresentation}
-	&\tilde G({\bf r}_2 - {\bf r}_1, \tilde\omega) \\
-	&= \frac{1}{\mathcal{D}_\text{gs}}\sum_{s_0 \in \text{GS}}\sum_s \left[\frac{F_p^*(s, {\bf r}_2)F_p(s, {\bf r}_1)}{\tilde\omega - \left( \tilde E_s - \tilde E_\text{gs} \right) } + \frac{F_h(s, {\bf r}_1)F_h^*(s, {\bf r}_2)}{\tilde\omega + \left( \tilde E_s - \tilde E_\text{gs} \right) }\right] ~,
+	&\tilde G(\nu_2, \nu_1; \tilde\omega) \\
+	&= \frac{1}{\mathcal{D}_\text{gs}}\sum_{s_0 \in \text{GS}}\sum_s \left[\frac{F_{c^\dagger}^*(s, \nu_2)F_{c^\dagger}(s, \nu_1)}{\tilde\omega - \left( \tilde E_s - \tilde E_\text{gs} \right) } + \frac{F_{c}(s, \nu_1)F_{c}^*(s, \nu_2)}{\tilde\omega + \left( \tilde E_s - \tilde E_\text{gs} \right) }\right] ~,
 \end{aligned}\end{equation}
 where \(s_0=\left({\bf k}_0, n_0\right)\) sums over the ground state(s) of the system (with energy \(\tilde E_\text{gs}\) and degeneracy \(\mathcal{D}_\text{gs}\)) and \(s=\left({\bf k}, n\right)\) sums over all eigenstates (with energies \(\tilde E_s\)).
-The coefficients \(F_p(s, {\bf r}) = \braket{\Psi_{s}|c^\dagger({\bf r})|\Psi_{s_0}}\) and \(F_h(s, {\bf r}) = \braket{\Psi_{s}|c({\bf r})|\Psi_{s_0}}\) represent spectral weights for particle and hole excitations from the ground state \(\ket{s_0}\) into the excited state \(\ket{s}\).
+The coefficients
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}(s, \nu) = \braket{\Psi_{s}|c^\dagger(\nu)|\Psi_{s_0}},\\
+	F_{c}(s, \nu) = \braket{\Psi_{s}|c(\nu)|\Psi_{s_0}}~,
+\end{aligned}\end{equation}
+represent spectral weights for particle and hole excitations from the ground state \(\ket{s_0}\) into the excited state \(\ket{s}\).
 
@@
 The label \(s\) involves a total momentum \({\bf k}\) and a band index \(n\).
-Guided by the relation eq.~\ref{tilingPrescriptionFinal} between the Hamiltonians, we assume a separation of the total energy into an impurity model contribution \(E_n\) coming from \(\mathcal{H}_\text{aux}\) and a contribution \(\varepsilon({\bf k})\) coming from the non-interacting background Hamiltonian \(\mathcal{H}_\text{cbath-nint}\):
-\begin{equation}\begin{aligned}
-	E_s \simeq N E_n + (N-3) \varepsilon_{\bf k}~.
-\end{aligned}\end{equation}
-where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\).
+Guided by the relation eq.~\ref{tilingPrescriptionFinal} between the Hamiltonians, we assume a separation of the total energy into an impurity model contribution \(E_n\) coming from \(\mathcal{H}_\text{aux}\) and a contribution \(\varepsilon({\bf k})\) coming from the non-interacting background Hamiltonian \(\mathcal{H}_\text{cbath-nint}\): \(E_s \simeq N E_n - (N-3) \varepsilon_{\bf k}\)~, where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\).
 Replacing \(N-3\) with \(N\) for a system of large number of particles, the spectral representation can be written as
 \begin{equation}\begin{aligned}
-	&\tilde G({\bf r}_2 - {\bf r}_1, \tilde\omega) \\
-	&= \frac{1}{\mathcal{D}_\text{gs}}\sum_{s_0 \in \text{GS}}\sum_s \left[\frac{F_p^*(s, {\bf r}_2)F_p(s, {\bf r}_1)}{\tilde\omega - N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) } \right.\\
-	&\left. + \frac{F_h(s, {\bf r}_1)F_h^*(s, {\bf r}_2)}{\tilde\omega + N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) }\right] ~,
+	&\tilde G(\nu_2, \nu_1; \tilde\omega) \\
+	&= \frac{1}{\mathcal{D}_\text{gs}}\sum_{s_0 \in \text{GS}}\sum_s \left[\frac{F_{c^\dagger}^*(s, \nu_2)F_{c^\dagger}(s, \nu_1)}{\tilde\omega - N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) } \right.\\
+	&\left. + \frac{F_{c}(s, \nu_1)F_{c}^*(s, \nu_2)}{\tilde\omega + N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) }\right] ~,
 \end{aligned}\end{equation}
 where the absence of the tilde in the denominators indicates that those energies arise from the auxiliary model Hamiltonian.
-
 In order to rewrite this expression in terms of quantities that can be computed purely from the auxiliary models, we replace the eigenstates with the forms given in eq.~\ref{eigenstateProposal}:
 \begin{equation}\begin{aligned}\label{spectralWeightsAuxiliary}
-	F_p^*(s, {\bf r}_2) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{i {\bf k}\cdot{\bf r}_d - {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_{n_0}({\bf r}_d^\prime)|c({\bf r}_2)|\psi_{n}({\bf r}_d)}\\
-	F_p(s, {\bf r}_1) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{-i {\bf k}\cdot{\bf r}_d + {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_n({\bf r}_d)|c^\dagger({\bf r}_1)|\psi_{n_0}({\bf r}_d^\prime)}~,
+	&F_{c^\dagger}^*(s, \nu_2) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{i {\bf k}\cdot{\bf r}_d - {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_{n_0}({\bf r}_d^\prime)|c(\nu_2)|\psi_{n}({\bf r}_d)}\\
+	&F_{c^\dagger}(s, \nu_1) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{-i {\bf k}\cdot{\bf r}_d + {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_n({\bf r}_d)|c^\dagger(\nu_1)|\psi_{n_0}({\bf r}_d^\prime)}~,
 \end{aligned}\end{equation}
@@
 
-Within the impurity model, the lattice site that most closely resembles the bulk lattice model is of course the impurity site; in order to ensure that all terms in eq.~\ref{spectralRepresentation} involve the impurity site, we approximate the states within \(F_p(s,{\bf r}_1)\) of eq.~\ref{spectralWeightsAuxiliary} purely in terms of the auxiliary model at \({\bf r}_1\):
-\begin{equation}\begin{aligned}
-	\ket{\Psi_s} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} \left[e^{i {\bf k}\cdot{\bf r}_1} \ket{\psi_{n}\left({\bf r}_1\right)} + \ket{\psi_{n}}_\text{diff}\right]\\
-		     &\simeq \sqrt N e^{i {\bf k}\cdot{\bf r}_1} \ket{\psi_{n}\left({\bf r}_1\right)}.
-\end{aligned}\end{equation}
-This amounts to retaining the spatially uniform part of the wavefunction and dropping the modulating difference term \(\ket{\psi_{n}}_\text{diff} = e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} - e^{i {\bf k}\cdot{\bf r}_1} \ket{\psi_{n}\left({\bf r}_1\right)}\).
-Replacing the exact forms in \(F_p(s, {\bf r}_1)\) with this approximation results in the expression
-\begin{equation}\begin{aligned}
-	F_p(s, {\bf r}_1) \simeq N e^{-i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_1} \braket{\psi_n({\bf r}_1)|c^\dagger({\bf r}_1)|\psi_{n_0}({\bf r}_1)}~.
-\end{aligned}\end{equation}
-For the other term, we make the less drastic approximation of retaining the matrix elements between the same auxiliary models \({\bf r}_d = {\bf r}_d^\prime\), leading to
-\begin{equation}\begin{aligned}
-	F_p^*(s, {\bf r}_2) = \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_d)|c({\bf r}_2)|\psi_{n}({\bf r}_d)}~.
+\subsection{Real-space Greens functions}
+We first consider one-particle Greens functions \(\tilde G({\bf r}; \tilde\omega)\) for the propagation of excitations between two spatial points \(\nu_1={\bf r}_c\) and \(\nu_2={\bf r}_c + {\bf r}\), where \({\bf r}_c\) is a fixed reference point in the lattice.
+Within the impurity model, the lattice site that most closely resembles the bulk lattice model is of course the impurity site; in order to ensure that all terms in eq.~\ref{spectralRepresentation} involve the impurity site, we approximate the states within \(F_{c^\dagger}(s,\nu_1) = F_{c^\dagger}(s,{\bf r}_c)\) of eq.~\ref{spectralWeightsAuxiliary} purely in terms of the auxiliary model at \({\bf r}_c\):
+\begin{equation}\begin{aligned}\label{eigenstateUniform}
+	\ket{\Psi_s} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} \left[e^{i {\bf k}\cdot{\bf r}_c} \ket{\psi_{n}\left({\bf r}_c\right)} + \ket{\psi_{n}}_\text{diff}\right]\\
+		     &\simeq \sqrt N e^{i {\bf k}\cdot{\bf r}_c} \ket{\psi_{n}\left({\bf r}_c\right)}.
+\end{aligned}\end{equation}
+This amounts to retaining the spatially uniform part of the wavefunction and dropping the modulating difference term \(\ket{\psi_{n}}_\text{diff} = e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} - e^{i {\bf k}\cdot{\bf r}_c} \ket{\psi_{n}\left({\bf r}_c\right)}\).
+Replacing the exact forms in \(F_{c^\dagger}(s, {\bf r}_c)\) with this approximation results in the expression
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}(s, {\bf r}_c) \simeq N e^{-i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_c} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+For the other term \(F_{c^\dagger}(s,\nu_2) = F_{c^\dagger}(s,{\bf r}_2)\), we make the less drastic approximation of retaining the matrix elements between the same auxiliary models \({\bf r}_d = {\bf r}_d^\prime\), leading to
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}^*(s, {\bf r}_2) = \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_d)|c({\bf r}_2)|\psi_{n}({\bf r}_d)}~.
 \end{aligned}\end{equation}
@@
 	&\braket{\psi_{n_0}({\bf r}_d)|c({\bf r}_2)|\psi_{n}({\bf r}_d)} \\
-	&= \braket{\psi_{n_0}({\bf r}_1)|T\left({\bf r}_d - {\bf r}_1\right) c({\bf r}_2) T^\dagger\left({\bf r}_d - {\bf r}_1\right) |\psi_{n}({\bf r}_1)}\\
-	&= \braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_2 - {\bf r}_1 + {\bf r}_d) |\psi_{n}({\bf r}_1)}~,
+	&= \braket{\psi_{n_0}({\bf r}_c)|T\left({\bf r}_d - {\bf r}_c\right) c({\bf r}_2) T^\dagger\left({\bf r}_d - {\bf r}_c\right) |\psi_{n}({\bf r}_c)}\\
+	&= \braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_2 + {\bf r}_c - {\bf r}_d) |\psi_{n}({\bf r}_c)}~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	&F_p^*(s, {\bf r}_2) \\
-	&= \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_2 - {\bf r}_1 + {\bf r}_d) |\psi_{n}({\bf r}_1)}\\
-	&= \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_1 - {\bf r}_2 + {\bf r}_d\right)} \braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_d) |\psi_{n}({\bf r}_1)}~.
-\end{aligned}\end{equation}
-In the second step, we redefined the dummy variable \({\bf r}_d \to {\bf r}_d - {\bf r}_2 + {\bf r}_1\).
-We make similar simplifications in the hole excitation coefficients \(F_h\) and \(F_h^*\) as well.
+	&F_{c^\dagger}^*(s, {\bf r}_2) \\
+	&= \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_2 + {\bf r}_c - {\bf r}_d) |\psi_{n}({\bf r}_c)}\\
+	&= \frac{1}{N}\sum_{{\bf r}_x} e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_x\right)} \braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_c + {\bf r}_x) |\psi_{n}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+In the second step, we introduced a new dummy variable \({\bf r}_x = {\bf r}_2 - {\bf r}_d\) that tracks the propagation of excitations into the auxiliary model.
+
+Having obtained the particle spectral coefficients, we can obtain the hole counterparts by mapping them onto each other.
+This can be done by noting that under our assumptions of \({\bf r}_d = {\bf r}_d^\prime\) in eq.~\ref{spectralWeightsAuxiliary}, we have the following relations:
+\begin{equation}\begin{aligned}
+	F_{c} &= F_{c^\dagger}^*\left({\bf k}\leftrightarrow{\bf k}_0, n \leftrightarrow n_0\right),\\
+	F_{c}^* &= F_{c^\dagger}\left({\bf k}\leftrightarrow{\bf k}_0, n \leftrightarrow n_0\right)~.
+\end{aligned}\end{equation}
+Using these, we get
+\begin{equation}\begin{aligned}\label{spectralParticleHoleRelation}
+	F_{c} &= \frac{1}{N}\sum_{{\bf r}_x} e^{i \left({\bf k}_0- {\bf k}\right)\cdot\left({\bf r}_2 - {\bf r}_x\right)} \braket{\psi_{n}({\bf r}_c)| c({\bf r}_x) |\psi_{n_0}({\bf r}_c)},\\
+	F_{c}^* &= N e^{-i \left({\bf k}_0 - {\bf k}\right)\cdot{\bf r}_c} \braket{\psi_{n_0}({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n}({\bf r}_c)}~.
+\end{aligned}\end{equation}
 
@@
 \begin{equation}\begin{aligned}
-	\tilde G({\bf r}_2 - {\bf r}_1, \tilde\omega) &= \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,{\bf k}_0}\sum_{{\bf k}, n}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_d - {\bf r}_2\right)} \left[\frac{\braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_d) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c^\dagger({\bf r}_1)|\psi_{n_0}({\bf r}_1)}}{\tilde\omega - N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) } \right.\\
-					  &\left.+ \frac{\braket{\psi_{n_0}({\bf r}_1)| c^\dagger({\bf r}_1) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c({\bf r}_d)|\psi_{n_0}({\bf r}_1)}}{\tilde\omega + N\left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) }\right] ~,\\
-					  &= \frac{1}{N}\sum_{{\bf k}_0, {\bf k}}\sum_{{\bf r}_d} e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_d\right)} \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,n}\left[\frac{\braket{\psi_{n_0}({\bf r}_1)| c({\bf r}_d) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c^\dagger({\bf r}_1)|\psi_{n_0}({\bf r}_1)}}{\omega - \left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) } \right.\\
-					  &\left.+ \frac{\braket{\psi_{n_0}({\bf r}_1)| c^\dagger({\bf r}_1) |\psi_{n}({\bf r}_1)} \braket{\psi_n({\bf r}_1)|c({\bf r}_d)|\psi_{n_0}({\bf r}_1)}}{\omega + \left( E_n - E_{n_0} + \varepsilon_{\bf k} - \varepsilon_{{\bf k}0}\right) }\right] ~,
+	\tilde G({\bf r}; \tilde\omega) &= \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,{\bf k}_0}\sum_{{\bf k}, n}\sum_{{\bf r}_x}  \left[e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}\frac{\braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_x) |\psi_{n}({\bf r}_c)} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}}{\tilde\omega - N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) } \right.\\
+					  &\left.+ e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}\frac{\braket{\psi_{n_0}({\bf r}_c)| c^\dagger({\bf r}_c) |\psi_{n}({\bf r}_c)} \braket{\psi_n({\bf r}_c)|c({\bf r}_x)|\psi_{n_0}({\bf r}_c)}}{\tilde\omega + N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) }\right] ~,\\
+					  &= \frac{1}{N}\sum_{{\bf k}_0, {\bf k}}\sum_{{\bf r}_x}  \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,n}\left[e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}\frac{\braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_x) |\psi_{n}({\bf r}_c)} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}}{\omega - \left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) } \right.\\
+					  &\left.+ e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}\frac{\braket{\psi_{n_0}({\bf r}_c)| c^\dagger({\bf r}_c) |\psi_{n}({\bf r}_c)} \braket{\psi_n({\bf r}_c)|c({\bf r}_x)|\psi_{n_0}({\bf r}_c)}}{\omega + \left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) }\right] ~,
 \end{aligned}\end{equation}
@@
 where \(\omega = \tilde\omega/N\) is the frequency scale for the auxiliary model.
-We can define partial Greens functions \(G_p({\bf r}_d, {\bf r}_1)\) and \(G_h({\bf r}_d, {\bf r}_1)\) for the auxiliary model that involve only the positive and negative frequency poles respectively.
+We can define an auxiliary model Greens functions \(G(d,{\bf r}_x; T) = -i\theta(T)\braket{\psi_\text{gs} | \left\{c^\dagger_{{\bf d}\sigma}, c_{{\bf d} + {\bf r}_x\sigma}\right\} | \psi_\text{gs}}\) for the propagation of excitations that start from the impurity site and extend up to a distance \({\bf r}_x\) into the auxiliary model; the subscripts \(p\) and \(h\) indicate that that Greens function involves only the positive and negative frequency poles respectively.
 In terms of these, the lattice model Greens function can be written in a more intuitive form.
@@
 \begin{equation}\begin{aligned}
-	\tilde G({\bf r}_2 - {\bf r}_1, \tilde\omega) &= \frac{1}{N}\sum_{{\bf k}}\sum_{{\bf r}_d} e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_d\right)} \\
-					  &\times\left[G_p\left({\bf r}_d,{\bf r}_1;\omega - \varepsilon_{\bf k}\right) + G_h\left({\bf r}_d,{\bf r}_1;\omega + \varepsilon_{\bf k}\right)\right]
-\end{aligned}\end{equation}
-
-\subsection{Nearest-neighbour Greens function}
+	&\tilde G({\bf r}; \tilde\omega) \\
+	&= \frac{1}{N}\sum_{{\bf k}}\sum_{{\bf r}_x}  \left[e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}G_p\left({\bf r}_x;\omega + \varepsilon_{\bf k}\right) \right.\\
+	&\left.+ e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}G_h\left({\bf r}_x;\omega - \varepsilon_{\bf k}\right)\right]
+\end{aligned}\end{equation}
+
+\subsection{Momentum-space Greens functions}
+We now consider Greens functions at a particular momentum \({\bf K}\), obtained by setting \(\nu_1=\nu_2={\bf K}\). The spectral coefficients are of the form
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{i {\bf k}\cdot{\bf r}_d - {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_{n_0}({\bf r}_d^\prime)|c({\bf K})|\psi_{n}({\bf r}_d)}\\
+	F_{c^\dagger}(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{-i {\bf k}\cdot{\bf r}_d + {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_n({\bf r}_d)|c^\dagger({\bf K})|\psi_{n_0}({\bf r}_d^\prime)}~.
+\end{aligned}\end{equation}
+Similar to the approach for the real-space Greens function, we simplify \(F^*_p(s, {\bf K})\) by retaining only the \({\bf r}_d = {\bf r}_d^\prime\) members, and then translating the arbitrary point \({\bf r}_d\) to a common reference point \({\bf r}_c\) in the lattice:
+\begin{equation}\begin{aligned}
+	&F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_d)|c({\bf K})|\psi_{n}({\bf r}_d)}~,\\
+	&\braket{\psi_{n_0}({\bf r}_d)|c({\bf K})|\psi_{n}({\bf r}_d)}\\
+	&= \braket{\psi_{n_0}({\bf r}_c)| T\left({\bf r}_d - {\bf r}_c\right) c({\bf K}) T^\dagger\left({\bf r}_d - {\bf r}_c\right) |\psi_{n}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+The effect of the translation operators on the \(k-\)space annihilation operator can be easily deduced by transforming it to real-space, using the Fourier transform definition
+\begin{equation}\begin{aligned}\label{fourTransf}
+	c({\bf K}) = \frac{1}{N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}c({\bf r})~.
+\end{aligned}\end{equation}
+Upon applying this, we get
+\begin{equation}\begin{aligned}\label{translationOnField}
+	&T\left({\bf r}_d - {\bf r}_c\right) c({\bf K}) T^\dagger\left({\bf r}_d - {\bf r}_c\right)\\
+	&= \frac{1}{N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}T\left({\bf r}_d - {\bf r}_c\right) c({\bf r}) T^\dagger\left({\bf r}_d - {\bf r}_c\right)\\
+	&= \frac{1}{N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}c({\bf r} - {\bf r}_d + {\bf r}_c)\\
+	&= e^{i{\bf K}\cdot\left({\bf r}_d - {\bf r}_c\right)}c({\bf K})~.
+\end{aligned}\end{equation}
+With this, the final form of \(F_{c^\dagger}^*(s, {\bf K})\) becomes
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}e^{-i {\bf K}\cdot{\bf r}_c}\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}\\
+	\times\sum_{{\bf r}_d}e^{i \left({\bf K} + {\bf k} - {\bf k}_0\right)\cdot{\bf r}_d}
+\end{aligned}\end{equation}
+The sum over \({\bf r}_d\) evaluates to \(\sum_{{\bf r}_d}e^{i \left({\bf K} + {\bf k} - {\bf k}_0\right)\cdot{\bf r}_d} = N \delta_{{\bf K}, - {\bf k} + {\bf k}_0}\), leading to
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}^*(s, {\bf K}) = e^{-i {\bf K}\cdot{\bf r}_c}\delta_{{\bf K}, - {\bf k} + {\bf k}_0}\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}
+\end{aligned}\end{equation}
+
+For the other coefficient \(F_{c^\dagger}(s, {\bf K})\), we again proceed similar to the previous subsection: we retain only the uniform part of the wavefunction, placing all the impurity models at the reference point \({\bf r}_c\):
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}(s, {\bf K}) = Ne^{-i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_c} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf K})|\psi_{n_0}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+In order to introduce the impurity site operator in the expression, we Fourier transform \(c^\dagger({\bf K})\) (following eq.~\ref{fourTransf}), and keep only that real-space mode that lies on the impurity reference point \({\bf r}_c\):
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}(s, {\bf K}) = e^{-i \left({\bf k} - {\bf k}_0 + {\bf K}\right)\cdot{\bf r}_c} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+
+Using eq.~\ref{spectralParticleHoleRelation}, we obtain the hole transition coefficients:
+\begin{equation}\begin{aligned}
+	F_{c}(s, {\bf K}) &= e^{-i {\bf K}\cdot{\bf r}_c}\delta_{{\bf K}, {\bf k} - {\bf k}_0}\braket{\psi_{n}({\bf r}_c)|c({\bf K})|\psi_{n_0}({\bf r}_c)},\\
+	F_{c}^*(s, {\bf K}) &= e^{-i \left({\bf k}_0 - {\bf k} + {\bf K}\right)\cdot{\bf r}_c} \braket{\psi_{n_0}({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+
+The complete expression for the momentum space Greens function is therefore
+\begin{widetext}
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}; \tilde\omega) = \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,{\bf k}_0 \in \text{GS}}\sum_{n,{\bf k}} e^{-i {\bf K}\cdot{\bf r}_c}\left[\delta_{{\bf K}, - {\bf k} + {\bf k}_0}\frac{\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}\braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}}{\tilde\omega - N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) } \right.
+\\
+	+ \left.\delta_{{\bf K}, {\bf k} - {\bf k}_0}\frac{\braket{\psi_{n}({\bf r}_c)|c({\bf K})|\psi_{n_0}({\bf r}_c)}\braket{\psi_{n_0}({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n}({\bf r}_c)}}{\tilde\omega + N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) }\right] ~.
+\end{aligned}\end{equation}
+\end{widetext}
+Once again assuming the uniqueness of \({\bf k}_0\), setting \(\varepsilon_{{\bf k}0}\) to zero and choosing the reference point \({\bf r}_c\) such that \({\bf K}\cdot{\bf r}_c = 0\), we have
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}; \tilde\omega) = G_p\left({\bf r}_c, {\bf K}; \omega + \varepsilon_{{\bf k}_0 - {\bf K}}\right) + G_h\left({\bf r}_c, {\bf K}; \omega - \varepsilon_{{\bf k}_0 + {\bf K}}\right),
+\end{aligned}\end{equation}
+where we have identified \({\bf r}_c\) as the impurity site and defined an auxiliary model Greens function \(G\left(d, {\bf K}; T\right) = -i\theta(T)\braket{\psi_\text{gs} | \left\{c^\dagger_{d\sigma}, c_{{\bf K},\sigma}\right\} | \psi_\text{gs}} \) for propagation of excitations from the \(d(f)-\)orbital impurity state \(\ket{d\sigma}\) into a momentum state of the conduction bath.
+
+\subsection{Spectral function and self-energies}
+Having obtained the one-particle Greens functions in both real and momentum-space, one can directly obtain the corresponding spectral functions \(\tilde A(\nu_2,\nu_1; \omega)\) and self-energies \(\tilde \Sigma(\nu_2,\nu_1; \omega)\), using standard relations.
+For eg., in momentum space, we have
+\begin{equation}\begin{aligned}
+	&\tilde A({\bf K}; \omega) \\
+	&= -\frac{1}{\pi}\text{Im}\left[\tilde G({\bf K}; \tilde\omega)\right]  \\
+	&= -\frac{1}{\pi}\text{Im}\left[G_p\left(d, {\bf K}; \omega + \varepsilon_{{\bf k}_0 - {\bf K}}\right) + G_h\left(d, {\bf K}; \omega - \varepsilon_{{\bf k}_0 + {\bf K}}\right)\right],\\
+\end{aligned}\end{equation}
+and
+\begin{equation}\begin{aligned}
+	\tilde \Sigma({\bf K}; \omega) = \left(\tilde G^{(0)}({\bf K}; \tilde\omega)\right)^{-1} - \left(\tilde G({\bf K}; \tilde\omega)\right)^{-1},
+\end{aligned}\end{equation}
+where \(\text{Im}[\cdot]\) is the imaginary part, and \(\tilde G^{(0)}\) is the non-interacting Greens function that is obtained by setting \(U = U_b = 0\) within the auxiliary model.
+
+%TODO
+%By expanding in terms of the small parameter $\frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}}$, this expression for $\Sigma_{H-H}(\vec k,\omega)$ can be recast in the following form:
+%\begin{equation}\begin{aligned}
+%	\Sigma_{H-H}(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~\label{selfenergy2}
+%\end{aligned}\end{equation}
+%where $\Sigma_\text{loc}$ and $\Sigma_\text{near-n}$ correspond to the local and nearest-neighbour self-energies defined on the real-space lattice 
+%\begin{eqnarray}
+%\Sigma_\text{loc}(\omega) &=& \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^{(0)}} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}}~,\\ 
+%\tilde{\Sigma}(\vec k, \omega)&=&\xi_{\vec k}\Sigma_\text{near-n}~,~\Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}^2}~.
+%\end{eqnarray}
+%We note that the form of $\Sigma(\vec k, \omega)$ obtained by us is similar to the form proposed on phenomenological grounds in the generalised DMFT + $\Sigma$ approach~\cite{sadovskii2012}.
+
+\section{Two-particle static correlators}
+Properties of the ground state can be probed using static correlation functions that are expectation values of two-particle excitation operators.
+A general correlation function in real space is of the form
+\begin{equation}\begin{aligned}
+	&\tilde{\mathcal{C}}_{\left\{ \sigma_i \right\} }({\bf r}_3, {\bf r}_2, {\bf r}_1) \\
+	&= \braket{c^\dagger_{\sigma_4}\left({\bf r}_c + {\bf r}_3\right)c_{\sigma_3}^\dagger\left({\bf r}_c + {\bf r}_2\right)c_{\sigma_2}\left({\bf r}_c + {\bf r}_1\right)c_{\sigma_1}\left({\bf r}_c\right)}~,
+\end{aligned}\end{equation}
+where the expectation value is in the ground state \(\ket{\Psi_\text{gs}}\). We replace the full ground state with the ground state of the auxiliary model at \({\bf r}_c\):
+\begin{equation}\begin{aligned}
+	\tilde{\mathcal{C}}_{\left\{ \sigma_i \right\} }&({\bf r}_3, {\bf r}_2, {\bf r}_1) \\
+	=& \langle\psi_\text{gs}({\bf r}_c) | c^\dagger_{\sigma_4}\left({\bf r}_c + {\bf r}_3\right)c_{\sigma_3}^\dagger\left({\bf r}_c + {\bf r}_2\right)c_{\sigma_2}\left({\bf r}_c + {\bf r}_1\right)\\
+	&c_{\sigma_1}\left({\bf r}_c\right) | \psi_\text{gs}({\bf r}_c)\rangle~.
+\end{aligned}\end{equation}
+
+One can also look at \(k-\)space correlations, of the spin or charge kind. The spin-spin correlations are of the form
+\begin{equation}\begin{aligned}
+	&\tilde{\mathcal{C}}_{\sigma_1,\sigma_2}({\bf K}_1, {\bf K}_2) \\
+	&= \braket{c^\dagger_{\bar\sigma_1}\left({\bf K}_1\right)c_{\bar\sigma_2}^\dagger\left({\bf K}_2\right)c_{\sigma_2}\left({\bf K}_2\right)c_{\sigma_1}\left({\bf K}_1\right)}~.
+\end{aligned}\end{equation}
+We frame this in terms of the auxiliary model by (i) making the substitution again for the ground states, and (ii) by Fourier transforming the creation operators to real space and retaining just the impurity site operator:
+\begin{equation}\begin{aligned}
+	&\tilde{\mathcal{C}}_{\sigma_1,\sigma_2}({\bf K}_1, {\bf K}_2) \\
+	&= \langle\psi_\text{gs}({\bf r}_c) | c^\dagger_{\bar\sigma_1}\left({\bf r}_c\right)c_{\bar\sigma_2}^\dagger\left({\bf r}_c\right)c_{\sigma_2}\left({\bf K}_2\right)c_{\sigma_1}\left({\bf K}_1\right) | \psi_\text{gs}({\bf r}_c)\rangle~.
+\end{aligned}\end{equation}
+Of course, one can also Fourier transform the other operators, so one can average over both possibilities to symmetrise the expression:
+\begin{equation}\begin{aligned}
+	&\tilde{\mathcal{C}}_{\sigma_1,\sigma_2}({\bf K}_1, {\bf K}_2) \\
+	&= \frac{1}{2}\langle\psi_\text{gs}({\bf r}_c) | \left[c^\dagger_{\bar\sigma_1}\left({\bf r}_c\right)c_{\bar\sigma_2}^\dagger\left({\bf r}_c\right)c_{\sigma_2}\left({\bf K}_2\right)c_{\sigma_1}\left({\bf K}_1\right) \right.\\
+	&\left.+ c^\dagger_{\bar\sigma_1}\left({\bf K}_1\right)c_{\bar\sigma_2}^\dagger\left({\bf K}_2\right)c_{\sigma_2}\left({\bf r}_c\right)c_{\sigma_1}\left({\bf r}_c\right) \right] | \psi_\text{gs}({\bf r}_c)\rangle~.
+\end{aligned}\end{equation}
+
+\section{Entanglement measures}
+\subsection{Entanglement entropy}
+Given the \(T=0\) density matrix \(\tilde\rho_\text{gs} = \ket{\Psi}_\text{gs}\bra{{\Psi}_\text{gs}}\) of the lattice model and a fermionic two-level subspace \(\nu\), the reduced density matrix for the {\it complement} subspace of \(\nu\) can be obtained by tracing over the configurations of that subspace
+\begin{equation}\begin{aligned}
+	&\overline\rho_{\nu} \\
+	&= \sum_{n_{\nu}=0,1}\braket{n_{\nu}|\tilde\rho_\text{gs}|n_{\nu}}\\
+	&= \rho_{\nu}^{(0,0)} + \rho_{\nu}^{(1,1)}~,
+\end{aligned}\end{equation}
+where \(\ket{n_{\nu}}\) is a state in the Hilbert space of \(\nu\) with fixed occupancy that can be 0 or 1, such that \(c^\dagger_\nu\ket{0}=\ket{1}\) and \(c_\nu\ket{1}=\ket{0}\).
+The entanglement entropy of the subspace \(\nu\) is then obtained straightforwardly from the eigenvalues of \(\overline\rho_{\nu}\), also known as the entanglement spectrum for this subspace:
+\begin{equation}\begin{aligned}
+	\tilde S_\text{EE}(\nu) = -\text{Tr}\left[\overline\rho_{\nu}\ln \overline\rho_{\nu}\right]  ~.
+\end{aligned}\end{equation}
+
+In order to facilitate expressing this in terms of auxiliary model quantities, we rewrite the total density matrix in the following manner:
+\begin{equation}\begin{aligned}
+	\tilde\rho_\text{gs} = \sum_{n_\nu=0,1}\sum_{n_\nu^\prime=0,1}\ket{n_{\nu^\prime}}\bra{n_{\nu}}\otimes\rho_\nu^{(n_\nu, n_\nu^\prime)}~.
+\end{aligned}\end{equation}
+which then allows a convenient form for the reduced density matrix in a block-diagonal form:
+\begin{equation}\begin{aligned}
+	\overline\rho_{\nu} = c^\dagger_\nu \tilde\rho_\text{gs} c_\nu + n_\nu \tilde\rho_\text{gs} n_\nu = \begin{pmatrix} 0 & 0 \\ 0 & \rho_{\nu}^{(0,0)} + \rho_{\nu}^{(1,1)} \end{pmatrix} ~.
+\end{aligned}\end{equation}
+Even though the matrix on the right has an additional zero block that should technically not be present in \(\overline\rho_{\nu}\), it does not make any difference for our purposes since that block only contributes zero eigenvalues which do not alter the entanglement entropy.
+
+We first consider entanglement in real-space, setting the subspace \(\nu\) to \(\nu=({\bf r}_c,\sigma)\), where \({\bf r}_c\) is the previously chosen reference point on the lattice.
+The expression for the enlarged \(\overline\rho_{\nu}\) becomes
+\begin{equation}\begin{aligned}
+	\overline\rho_{{\bf r}_c,\sigma} = c^\dagger_{{\bf r}_c,\sigma} \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}} c_{{\bf r}_c,\sigma} + n_{{\bf r}_c,\sigma} \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}} n_{{\bf r}_c,\sigma}~.
+\end{aligned}\end{equation}
+As has been done before, we simplify \(\Psi_\text{gs}\) by retaining only the uniform part of the eigenstate at \({\bf r}_c\) (following eq.~\ref{eigenstateUniform}), leading to the expression
+\begin{equation}\begin{aligned}
+	\overline\rho_{{\bf r}_c,\sigma} = c^\dagger_{{\bf r}_c,\sigma} \rho_\text{gs}({\bf r}_c) c_{{\bf r}_c,\sigma} + n_{{\bf r}_c,\sigma} \rho_\text{gs}({\bf r}_c) n_{{\bf r}_c,\sigma}
+\end{aligned}\end{equation}
+where \(\rho_\text{gs}({\bf r}_c) = \ket{\psi_\text{gs}({\bf r}_c)}\bra{\psi_\text{gs}({\bf r}_c)}\) is the \(T=0\) density matrix for the auxiliary model at \({\bf r}_c\).
+This is simply the reduced density matrix of the impurity site for the auxiliary model at \({\bf r}_c\), leading to the following simple relation for the local entanglement entropy of the lattice model:
+\begin{equation}\begin{aligned}
+	\tilde S_\text{EE}^{\text{(loc)}} = S_\text{EE}^{(\text{imp.})}~.
+\end{aligned}\end{equation}
+
+We now come to the \(k-\)space entanglement entropy, defined by \(\nu = ({\bf K},\sigma)\) and the reduced density matrix
+\begin{equation}\begin{aligned}
+	\overline\rho_{{\bf K},\sigma} = c^\dagger_{{\bf K},\sigma} \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}} c_{{\bf K},\sigma} + n_{{\bf K},\sigma} \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}} n_{{\bf K},\sigma}~.
+\end{aligned}\end{equation}
+We again replace the states with the uniform part, while we expand the operators on the right of the density matrix (\(c\) and \(n\)) in a Fourier series in order to extract an impurity site operator:
+\begin{equation}\begin{aligned}
+	\overline\rho_{{\bf K},\sigma} = c^\dagger_{{\bf K},\sigma} \rho_\text{gs}({\bf r}_c) c_{{\bf r}_c,\sigma} + n_{{\bf K},\sigma} \rho_\text{gs}({\bf r}_c) n_{{\bf r}_c,\sigma}~.
+\end{aligned}\end{equation}
+The eigenvalues of this operator can be used to compute the entanglement entropy of the state \({\bf K}\sigma\).
 
@@
 
-Following eq.~\ref{siam_to_hubb}, the exponential can be written as:
-\begin{equation}\begin{aligned}
-e^{i H_\text{H-H} t} = \exp\left[\sum_i t\mathcal{H}_\text{aux}({\bf r}_i)\right] 
-\end{aligned}\end{equation}
-In order to simplify this expression, we rewrite the sum over the auxiliary models in terms of a uniform piece \(\sum_{i}\mathcal{H}_\text{aux}({\bf r_0})\) and a difference piece \(\Delta(i) = \mathcal{H}_\text{aux}({\bf r}_i) - \mathcal{H}_\text{aux}({\bf r_0})\):
-\begin{equation}\begin{aligned}
-	\sum_{{\bf r}_i} \mathcal{H}_\text{aux}({\bf r}_i) = \sum_{{\bf r}_i} \left[\mathcal{H}_\text{aux}({\bf r_0}) + \Delta({\bf r}_i)\right] = N \left[\mathcal{H}_\text{aux}({\bf r_0}) + \frac{1}{N}\sum_{{\bf r}_i} \Delta({\bf r}_i)\right];
-\end{aligned}\end{equation}
-\({\bf r_0}\) is the origin of the lattice, and \(N\) is the number of lattice sites.
-The uniform piece \(\sum_{i}\mathcal{H}_\text{aux}({\bf r_0})\) acts as the ``center-of-mass" Hamiltonian - it responds to spectral flow brought about by changes in boundary conditions.
-The other piece acts as a "relative motion" Hamiltonian and is insensitive to changes in the boundary conditions, because any spectral flow of the auxiliary model Hamiltonians gets cancelled out in the difference operation.
-While the COM Hamiltonian is a thermodynamically large object, the number of terms in the difference piece is of the order of unity (the sum over \({\bf r}_i\) is cancelled out by the \(1/N\) factor).
-We can therefore expand the exponential in the ratio of the relative piece to the COM piece:
-\begin{equation}\begin{aligned}
-	e^{i H_\text{H-H} t} = e^{i t N \mathcal{H}_\text{aux}({\bf r_0})}\left[1 + \frac{1}{N \mathcal{H}_\text{aux}({\bf r_0})}\sum_{{\bf r}_i} \Delta({\bf r}_i) + \ldots\right];
-\end{aligned}\end{equation}
-In the limit of large \(N\), we retain only the leading piece in the expansion, resulting in the full bulk model in the time-dependence getting replaced by \(N\) times the COM piece:
-\begin{equation}\begin{aligned}
-	c({\bf r} + r,t) \simeq e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r} + r)e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}
-\end{aligned}\end{equation}
-On substituting this into the expression for the single-particle Greens function, we get
-\begin{equation}\begin{aligned}
-	G_\text{H-H}({\bf r}, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r} + r)e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}, c^\dagger({\bf r}) \right\} | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-Because of translation symmetry of the bulk lattice, the initial point \({\bf r}\) of the excitation can be shifted to the origin \({\bf r_0}\) without any loss of generality:
-\begin{equation}\begin{aligned}
-	G_\text{H-H}({\bf r}, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r_0} + r)e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}, c^\dagger({\bf r_0}) \right\} | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-We will now express the ground-state in terms of the auxiliary model states, following eq.~\ref{bloch-states}:
-\begin{equation}\begin{aligned}
-	\ket{\Psi_\text{gs}} = \frac{1}{\lambda_{\vec k_0} \sqrt{\mathcal{Z} N}}\sum_{{\bf r}_j, {\bf a} \in \text{NN of }{\bf r}_j} e^{i \vec{k}_0\cdot\vec{R}_j} \ket{\psi_\text{aux}({\bf r}_j, {\bf a})}~,
-\end{aligned}\end{equation}
-where we have brought back the explicit sum over the nearest neighbours \({\bf a}\) of the impurity site (following eq.~\ref{zeroth_site_average}).
-We again simplify the wavefunction by keeping only the uniform piece and dropping the difference pieces.
-\begin{equation}\begin{aligned}
-	\ket{\Psi_\text{gs}} = \sum_{{\bf a} \in \text{NN of}{\bf r_0}}\frac{1}{\sqrt \mathcal{Z}\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}({\bf r_0}, {\bf a})} + \ket{\psi_\text{diff}(\vec k_0)}
-\end{aligned}\end{equation}
-where \(\ket{\psi_\text{diff}(\vec k_0)} = \ket{\Psi_\text{gs}} - \frac{\sqrt \mathcal{Z}}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}({\bf r_0})}\).
-The Greens funtion takes the form
-\begin{equation}\begin{aligned}
-G_\text{H-H}({\bf r}, t) =  \frac{-i\theta(t)}{\mathcal{Z} \lambda_{\vec k_0}^2}\sum_{{\bf a}_1, {\bf a}_2 \in \text{NN of }{\bf r_0}}\braket{\psi_\text{aux}({\bf r_0}, {\bf a}_1) | \left\{ e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r_0} + r)e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}, c^\dagger({\bf r_0}) \right\} | \psi_\text{aux}({\bf r_0}, {\bf a}_2)}~.
-\end{aligned}\end{equation}
-Specifically, for the local Greens function \(G_\text{H-H}({\bf r}=0, t)\), we keep the states with \({\bf a}_1 = {\bf a}_2\), leading to the expression
-\begin{equation}\begin{aligned}
-	\label{greens_func_approx}
-	G_\text{loc}(t) \equiv G_\text{H-H}({\bf r}=0, t) =  \frac{-i\theta(t)}{\mathcal{Z} \lambda_{\vec k_0}^2}\sum_{{\bf a} \in \text{NN of }{\bf r_0}}\braket{\psi_\text{aux}({\bf r_0}, {\bf a}) | \left\{ e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r_0} + r)e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}, c^\dagger({\bf r_0}) \right\} | \psi_\text{aux}({\bf r_0}, {\bf a})}~.
-\end{aligned}\end{equation}
-Because of the symmetry of the lattice, all Greens functions obtained for various positions of the zeroth site \({\bf a}\) are equal, and the local Greens function simplifies to
-\begin{equation}\begin{aligned}
-	G_\text{loc}(t) \equiv G_\text{H-H}({\bf r}=0, t) &= -\frac{1}{\lambda_{\vec k_0}^2 }i\theta(t) \braket{\psi_\text{aux}({\bf r_0}) | \left\{ e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r_0})e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}, c^\dagger({\bf r_0}) \right\} | \psi_\text{aux}({\bf r_0})}~.
-\end{aligned}\end{equation}
-In this form, the only Hamiltonian involved in the expression is the COM Hamiltonian at \({\bf r_0}\), and \(G_\text{H-H}({\bf r}=0, t)\) is therefore captured by the impurity Greens function \(\mathcal{G}\) in the auxiliary model \(N \mathcal{H}_\text{aux}({\bf r_0})\) with ground-state \(\ket{\psi_\text{aux}({\bf r_0})}\):
-\begin{equation}\begin{aligned}
-	\label{greens_func_relation}
-	G_\text{loc}(t) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{G}_{dd}(t)~,\quad \mathcal{G}_{dd}(t) = -i\theta(t) \braket{\psi_\text{aux}({\bf r_0}) | \left\{ e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r_0})e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}, c^\dagger({\bf r_0}) \right\} | \psi_\text{aux}({\bf r_0})}~.
-\end{aligned}\end{equation}
-The cursive script symbol \(\mathcal{G}_{dd}\) has been used to denote the impurity Greens function for the auxiliary model \(N \mathcal{H}_\text{aux}({\bf r_0})\).
-
-For the nearest neighbour Greens function \(G_\text{near-n} \equiv G_\text{H-H}({\bf r}={\bf a}, t)\), we keep only the terms with \({\bf a}_1 = {\bf a}_2 = {\bf a}\) in the summation of eq.~\ref{greens_func_approx}:
-\begin{equation}\begin{aligned}
-	\label{greens_func_relation_near}
-	G_\text{near-n}(t) \equiv G_\text{H-H}({\bf r}={\bf a}, t) = -\frac{1}{\lambda_{\vec k_0}^2 \mathcal{Z}}i\theta(t) \braket{\psi_\text{aux}({\bf r_0}, {\bf a}) | \left\{ e^{i N \mathcal{H}_\text{aux}({\bf r_0}) t}c({\bf r_0} + {\bf a})e^{-i N \mathcal{H}_\text{aux}({\bf r_0}) t}, c^\dagger({\bf r_0}) \right\} | \psi_\text{aux}({\bf r_0}, {\bf a})} \\
-	= \frac{1}{\lambda_{\vec k_0}^2 \mathcal{Z}} \mathcal{G}_{dz}(t)~.
-\end{aligned}\end{equation}
-These relations can be easily carried over to frequency domain: 
-\begin{equation}\begin{aligned}
-	G_\text{loc}(\omega) = \int \mathrm{dt}~e^{-i\omega t} G_\text{loc}(t) = \frac{1}{\lambda_{\vec k_0}^2}\int \mathrm{dt}~e^{-i\omega t} \mathcal{G}_{dd}(t) = \frac{1}{\lambda_{\vec k_0}^2} \mathcal{G}_{dd}(\omega)~.
-\end{aligned}\end{equation}
-
-The difference in the COM wavefunction and the full wavefunction can be estimated by calculating the norm of the difference piece:
-\begin{equation}\begin{aligned}
-	||\ket{\Psi_\text{gs}} - \frac{1}{\lambda_{\vec k_0}} e^{i\vec{k}_0\cdot\vec{R}_0} \ket{\psi_\text{aux}({\bf r_0})}||^2 &= |1 + \frac{1}{\lambda_{\vec k_0}^2} - \left[\frac{1}{\lambda_{\vec k_0}}e^{i \vec{k_0}\cdot\vec{r_0}}\braket{\Psi_\text{gs} | \psi_\text{aux}({\bf r_0})} + \text{h.c.}\right]| \\
-	&=|1 + \frac{1}{\lambda_{\vec k_0}^2} - \frac{1}{\lambda_{\vec k_0}^2 N}\sum_{{\bf r}_j} \left(e^{i \vec k_0 \cdot \left( {\bf r}_j - {\bf r_0} \right)}  \braket{\psi_\text{aux}({\bf r_0}) | \psi_\text{aux}({\bf r}_j) } + \text{h.c.}\right)|\\
-	&=|1 + \frac{1}{\lambda_{\vec k_0}^2} - \frac{1}{\lambda_{\vec k_0}^2 N}\sum_{{\bf r}_j,\vec q} \left(e^{i \left(\vec k_0 - \vec q\right)\cdot \left( {\bf r}_j - {\bf r_0} \right)}\lambda_{\vec q}^2 + \text{h.c.}\right)|\\
-	&= |1 - \frac{1}{\lambda_{\vec k_0}^2}|
-\end{aligned}\end{equation}
-By choosing an appropriate auxiliary model, the overlap factor \(\lambda_{\vec k_0}\) can be brought close to unity, leading to a smaller difference.
-The local and nearest-neighbour Greens functions of the full model can thus be computed from the impurity local Greens function \(\mathcal{G}_{dd}\) and the impurity-bath zeroth site Greens function \(\mathcal{G}_{dz}\) on the COM auxiliary model \(N \mathcal{H}_\text{aux}({\bf r_0})\).
-By using these real-space Greens functions, one can then compute \(k-\)space Greens functions of the full model.
-
+\begin{widetext}
 \section{Static correlation functions}
@@
 \end{aligned}\end{equation}
-
-\section{\(k-\)space Greens functions and self-energies}
-
-The momentum space Greens function can be expressed as a Fourier transform of the real space Greens functions:
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) = \frac{1}{N \mathcal{Z}}\sum_{{\bf r}, {\bf r}}e^{i \vec{k}\cdot\left({\bf r} + {\bf r}\right)}G_{H-H} ({\bf r} + {\bf r}, \omega)
-\end{aligned}\end{equation}
-where ${\bf r}$ sums over all lattice sites and \({\bf r}\) sums over all nearest-neighbours of that site, such that \({\bf r} + {\bf r}\) sums over all possible real space Greens functions.
-The distance \({\bf r} + {\bf r}\) has been measured with respect to some chosen central lattice site.
-Because of translation invariance, the real space Greens function depends only on the relative vector between two sites.
-As a result, ${\bf r} + {\bf r} = 0$ gives the local Greens function, $|{\bf r} + {\bf r}|=a$ gives the nearest-neighbour Greens function and so on ($a$ being the lattice spacing).
-Given that our auxiliary model shows an emergent self-consistency on the impurity site and on the link between the impurity and the zeroth site, we approximate the \(k-\)space Greens functions from the local and nearest-neighbour contributions:
-\begin{equation}\begin{aligned}
-	G_{H-H} (\vec k, \omega) &= \frac{1}{N \mathcal{Z}}\sum_{{\bf r}, {\bf r}}\left[e^{i \vec{k}\cdot\left({\bf r} + {\bf r}\right)}G_{H-H} ({\bf r} + {\bf r}, \omega) - G_\text{H-H}(0,\omega) - e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}({\bf r},\omega) + G_\text{H-H}(0,\omega) + e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}({\bf r},\omega)\right]\\
-				 &= G_\text{H-H}(0,\omega) + \sum_r e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}({\bf r},\omega) + \frac{1}{N \mathcal{Z}}\sum_{{\bf r}, {\bf r}}\left[e^{i \vec{k}\cdot\left({\bf r} + {\bf r}\right)}G_{H-H} ({\bf r} + {\bf r}, \omega) - G_\text{H-H}(0,\omega) - e^{i\vec{k}\cdot\vec{r}}G_\text{H-H}({\bf r},\omega)\right]
-\label{auxGreen}
-\end{aligned}\end{equation}
-The difference term in the square brackets is smaller than the sum outside, so we drop the former.
-We identify the first term \(G_\text{H-H}(0,\omega)\) as the local Greens function \(G_\text{loc}\) and those inside the second term, \(G_\text{H-H}({\bf r}, \omega)\) as the nearest neighbour Greens function \(G_\text{near-n}\) (assuming symmetry under rotation by \(\pi/2\)).
-The second sum is over all the primitive vectors connecting any single site with all its nearest neighbours, $\left\{ {\bf a}_i: i \in \left[1, \mathcal{Z}\right]\right\}$.
-Combining all this and by using the mappings to the auxiliary model (eqs.~\ref{greens_func_relation} and \ref{greens_func_approx}), we get
-\begin{equation}\begin{aligned}
-	\label{k_Gf_siam}
-	G_{H-H} (\vec k, \omega) &\simeq G_\text{loc}(\omega) + G_\text{near-n}(\omega)\sum_{i=1}^{\mathcal{Z}} e^{i \vec{k}\cdot\vec {a_i}} = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{G}_{dd}(\omega) + \frac{1}{\mathcal{Z}}\xi_{\vec k}\mathcal{G}_{dz}(\omega) \right]~,
-\end{aligned}\end{equation}
-where we defined \(\xi_{\vec k} \equiv \sum_{i=1}^w e^{i \vec{k}\cdot\vec {a_i}}\), it being essentially the dispersion in units of the hopping strength \(t\).
-For example, on a d-dimensional hypercubic lattice, we obtain
-\begin{equation}\begin{aligned}
-	\xi_{\vec k} = \sum_{i=1}^d \left(e^{i k_i {a_i}} + e^{-i k_i {a_i}}\right) = 2\sum_{i=1}^d \cos k_i a_i~,
-\end{aligned}\end{equation}
-leading to \(2(\cos q_{x}a + \cos q_{y}a)\equiv \frac{-\epsilon_{\vec{q}}}{t^{H}}\) on a 2D square lattice.
-
-The spectral function is simply the imaginary part of the Greens function: \(A_\text{H-H} = -\frac{1}{\pi}\text{Im}\left[G_{H-H}\right] \); as a result, they have similar relations with their auxiliary model counterparts:
-\begin{equation}\begin{aligned}
-	A_\text{loc}(\omega) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{A}_{dd}~,\qquad A_\text{near-n}(\omega) = \frac{1}{\lambda_{\vec k_0}^2}\mathcal{A}_{dz}~,\qquad A_\text{H-H}(\vec{k},\omega) = \frac{1}{\lambda_{\vec k_0}^2}\left[\mathcal{A}_{dd} + \frac{1}{\mathcal{Z}}\xi_{\vec k}\mathcal{A}_{dz} \right]~,
-\end{aligned}\end{equation}
-where \(\left(A_\text{H-H}\right)_\text{loc}(\omega)\) and \(A_\text{H-H}(\vec{k},\omega)\) are the local and \(k-\)space spectral functions, respectively, of the bulk model, and \(\mathcal{A}_{dd}\) and \(\mathcal{A}_{dz}\) are the auxiliary model spectral functions for local and nearest neighbour fluctuations respectively.
-
-From the knowledge of the momentum-space Greens function, one can write down the lattice self-energy \(\Sigma(\vec k,\omega)\) using Dyson's equation:
-\begin{equation}\begin{aligned}
-	\label{selfenergy1}
-	\Sigma_{H-H}(\vec k,\omega) = 1/\left(G_{H-H}(\omega)\right)_{\vec k}^{(0)} - 1/\left(G_{H-H}(\omega)\right)_{\vec k} = \frac{\left(\lambda_{\vec k_0}^{(0)}\right)^2}{\mathcal{G}^{(0)}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{Z}}\mathcal{G}^{(0)}_{dz}(\omega)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega) + \frac{\xi_{\vec k}}{\mathcal{Z}}\mathcal{G}_{dz}(\omega)}~,
-\end{aligned}\end{equation}
-where the superscript \((0)\) indicates that the corresponding term has to be calculated from the non-interacting auxiliary model.
-
-By expanding in terms of the small parameter $\frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}}$, this expression for $\Sigma_{H-H}(\vec k,\omega)$ can be recast in the following form:
-\begin{equation}\begin{aligned}
-	\Sigma_{H-H}(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~\label{selfenergy2}
-\end{aligned}\end{equation}
-where $\Sigma_\text{loc}$ and $\Sigma_\text{near-n}$ correspond to the local and nearest-neighbour self-energies defined on the real-space lattice 
-\begin{eqnarray}
-\Sigma_\text{loc}(\omega) &=& \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^{(0)}} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}}~,\\ 
-\tilde{\Sigma}(\vec k, \omega)&=&\xi_{\vec k}\Sigma_\text{near-n}~,~\Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}^2}~.
-\end{eqnarray}
-We note that the form of $\Sigma(\vec k, \omega)$ obtained by us is similar to the form proposed on phenomenological grounds in the generalised DMFT + $\Sigma$ approach~\cite{sadovskii2012}.
 
@@
 	\centering
-	\includegraphics[scale=0.2]{luttinger_top_change.png}
+	\includegraphics[width=0.4\textwidth]{luttinger_top_change.png}
 	\caption{The green lines describe the winding number related to the impurity Greens function, while the blue lines do it for the bath.
@@
 \end{figure}
+
+\clearpage
+\section*{Appendices}
+\appendix
+\section{Effective action for the Hubbard-Heisenberg model and the eSIAM}
+In order to better understand the similarities and differences between the tiling approach outlined here and the approach adopted in dynamical mean-field approximations, we compute the effective action for the local impurity as well as the impurity-zeroth site system, in both the auxiliary and bulk models.
+This will be done in the limit of infinite coordination number, in order to create a tractable effective theory.
+
+\subsection{Local theory for the Hubbard-Heisenberg model}
+We will first work with the Hubbard-Heisenberg model.
+Let us recall that within the eSIAM, most of the dynamics is governed by the physics of the impurity site and the bath site coupled to the impurity.
+Accordingly, we will first obtain an effective action within the Hubbard-Heisenberg model for the small system consisting of a local site and all its nearest-neighbours.
+
+We choose a certain local site that we call \(0\), whose nearest-neighbours will be denoted as \(\left\{ {\bar 0} \right\} \).
+The action for the full Hubbard-Heisenberg model can be formally separated into three parts:
+\begin{equation}\begin{aligned}
+S_\text{H-H} = S_{0,{\bar 0}} + S^{(0,{\bar 0})} + S_\text{int}~,
+\end{aligned}\end{equation}
+where \(S_{0,{\bar 0}}\) represents the part of the action that involves only the sites \(0\) and $\left\{ {\bar 0} \right\}$, \(S^{(0,{\bar 0})}\) represents the part that has all the sites apart from \(0\) and \(\left\{ {\bar 0} \right\} \), while \(S_\text{int}\) contains all terms that connect these two parts.
+These three parts have the forms
+\begin{equation}\begin{aligned}
+S_{0,{\bar 0}} = \sum_{i=0,{\bar 0}}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau)  - t\sum_{{\bar 0},\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{0\sigma}(\tau)c_{{\bar 0}\sigma}(\tau) + \text{h.c.}\right] \\
+- \frac{U}{2}\sum_{i=0,{\bar 0}}\int_0^\beta\mathrm{d\tau}~\left(n_{i \uparrow}(\tau) - n_{i \downarrow}(\tau)\right)^2 + J\sum_{{\bar 0}}\int_0^\beta\mathrm{d\tau} \vec{S}_0(\tau)\cdot\vec{S}_{{\bar 0}}(\tau)~,
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+S^{(0,{\bar 0})} = \sum_{j\neq(0,{\bar 0})}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{j\sigma}(\tau)\partial_\tau c_{j\sigma}(\tau)  - t\sum_{\left<j,l\right>\neq (0,{\bar 0}),\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{j\sigma}(\tau)c_{l\sigma}(\tau) + \text{h.c.}\right] \\
+- \frac{U}{2}\sum_{j\neq(0,{\bar 0})}\int_0^\beta\mathrm{d\tau}~\left(n_{j\uparrow}(\tau) - n_{j\downarrow}(\tau)\right)^2 + J\sum_{\left<j,l\right>\neq(0,{\bar 0})}\int_0^\beta\mathrm{d\tau} \vec{S}_l(\tau)\cdot\vec{S}_j(\tau)~,
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+S_\text{int} = -t\sum_{i \in {\bar 0}}\sum_{j \in \text{NN of}~i}\sum_\sigma \int_0^\beta\mathrm{d\tau}~\left(c^\dagger_{i\sigma}(\tau) c_{j\sigma}(\tau) + \text{h.c.}\right) + J\sum_{i \in {\bar 0}}\sum_{j \in \text{NN of}~i}\int_0^\beta\mathrm{d\tau}\vec{S}_i(\tau)\cdot\vec{S}_j(\tau) = S_\text{int}^\text{hop} + S_\text{int}^\text{spin}
+\end{aligned}\end{equation}
+
+In order to obtain an effective theory \(S^{0,{\bar 0}}_\text{eff}\) purely for the local system \((0,{\bar 0})\), we need to trace over all the other degrees of freedom.
+This partial trace will be carried out over the states of the so-called ``cavity" system \(S^{(0,{\bar 0})}\).
+The effective action can be constructed by tracing over scattering processes of all orders that leave the final action diagonal in the system \((0,{\bar 0})\).
+The formal expression can be written as
+\begin{equation}\begin{aligned}
+	S^{0,{\bar 0}}_\text{eff} = S_{0,{\bar 0}} + \sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} + \sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})}
+\end{aligned}\end{equation}
+where, as mentioned before, the average is carried out in the cavity system \(S^{(0,{\bar 0})}\). Each hopping term in the expansion is of the form
+\begin{equation}\begin{aligned}
+	\left(S_\text{int}^\text{hop}\right)^{2n} =& t^{2n}\sum_\sigma\sum_{(i_1, i_1^\prime)\ldots, (i_n, i_n^\prime)} ~\sum_{(j_1, j_1^\prime)\ldots, (j_n, j_n^\prime)} \int_0^\beta d\tau_{1}\ldots d\tau_{n}d\tau_{1}^\prime\ldots d\tau_{j_n}^\prime\\
+			   &c^\dagger_{i_1\sigma}(\tau_{i_1})c^\dagger_{i_2\sigma}(\tau_{2})\ldots c^\dagger_{i_n\sigma}(\tau_{n}) c_{i_1^\prime\sigma}(\tau_{1}^\prime)c_{i_2^\prime\sigma}(\tau_{2}^\prime)\ldots c_{i_n^\prime\sigma}(\tau_{n}^\prime)\left<c_{j_1\sigma}(\tau_{1})c_{j_2\sigma}(\tau_{2})\ldots c_{j_n\sigma} ~ c^\dagger_{j_1^\prime\sigma}(\tau_{1}^\prime)\ldots c^\dagger_{j_n^\prime\sigma}(\tau_{n}^\prime) \right>_{(0,{\bar 0})}\\
+	=& t^{2n}\sum_\sigma\sum_{(i_1, i_1^\prime)\ldots, (i_n, i_n^\prime)} ~\sum_{(j_1, j_1^\prime)\ldots, (j_n, j_n^\prime)} \int_0^\beta d\tau_{1}\ldots d\tau_{j_n}^\prime c^\dagger_{i_1\sigma}(\tau_{i_1})\ldots c^\dagger_{i_n\sigma}(\tau_{n})~c_{i_1^\prime\sigma}(\tau_{1}^\prime)\ldots c_{i_n^\prime\sigma}(\tau_{n}^\prime)\\
+	 &G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right)~,
+\end{aligned}\end{equation}
+where the indices \(i_1\) through \(i_n\) and their primed counterparts run through \(\bar 0\), while \(j_l\) (\(\in \left\{j_1,\ldots,j_n^\prime\right\}\)) runs through the nearest-neighbours of the corresponding \(i_l\) index.
+The \(n-\)particle Greens function \(G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right)\) for the cavity system is defined in the usual fashion
+\begin{equation}\begin{aligned}
+	G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right) = \left<c_{j_1\sigma}(\tau_{1})c_{j_2\sigma}(\tau_{2})\ldots c_{j_n\sigma} ~ c^\dagger_{j_1^\prime\sigma}(\tau_{1}^\prime)\ldots c^\dagger_{j_n^\prime\sigma}(\tau_{n}^\prime) \right>_{(0,{\bar 0})}
+\end{aligned}\end{equation}
+In the limit of infinite coordination number, only the \(n=1\) term survives:
+\begin{equation}\begin{aligned}
+	\lim_{\mathcal{Z}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} = t^2\sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)\sum_{j,j^\prime}G_1^{(0,\bar 0)}\left(j\tau; j^\prime\tau^\prime\right) \\
+	= \sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)~,
+\end{aligned}\end{equation}
+where we have defined the bath hybridisation function \(\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)\) as
+\begin{equation}\begin{aligned}
+	\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime) = t^2\sum_{j \in \text{NN of}~i}\sum_{j^\prime \in \text{NN of}~i^\prime}G_1^{(0,\bar 0)}\left(j\sigma\tau; j^\prime\sigma\tau^\prime\right)~.
+\end{aligned}\end{equation}
+
+Under similar approximations, the spin term in the action reduces to
+\begin{equation}\begin{aligned}
+	\lim_{\mathcal{Z}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})} = \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\chi(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)~,
+\end{aligned}\end{equation}
+where the susceptibility \(\chi_{ii^\prime}(\tau - \tau^\prime)\) is defined as 
+\begin{equation}\begin{aligned}
+	\chi_{ii^\prime}(\tau - \tau^\prime) = J^2\sum_{j \in \text{NN of}~i}\sum_{j^\prime \in \text{NN of}~i^\prime}\vec{S}_{j}(\tau)\cdot\vec{S}_{j^\prime}(\tau^\prime)~.
+\end{aligned}\end{equation}
+The effective action for the \(0,\bar 0\) system, in the limit of large coordination number, simplifies to
+\begin{equation}\begin{aligned}
+	S^{0,{\bar 0}}_\text{eff} =& \sum_{i=0,{\bar 0}}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau)  - t\sum_{{\bar 0},\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{0\sigma}(\tau)c_{{\bar 0}\sigma}(\tau) + \text{h.c.}\right] - \frac{U}{2}\sum_{i=0,{\bar 0}}\int_0^\beta\mathrm{d\tau}~\left(n_{i \uparrow}(\tau) - n_{i \downarrow}(\tau)\right)^2 \\
+				   &+ J\sum_{{\bar 0}}\int_0^\beta\mathrm{d\tau} \vec{S}_0(\tau)\cdot\vec{S}_{{\bar 0}}(\tau) + \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{ii^\prime}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
+\end{aligned}\end{equation}
+
+One can also write down an effective action purely for the local site \(0\).
+The sites \(\bar 0\) will now be a part of the environment action \(S^{(0)}\) instead of the system action, but since the system is thermodynamically large, the cavity action can be assumed to remain the same, such the expectation values are calculated in the same system.
+As a result, the hybridisation and susceptibility functions remain unchanged.
+\(S_\text{int}\) is now made of terms that connect \(0\) and \(\bar 0\), so the transformation from \(S^{(0,\bar 0)}\) can be made by replacing the set \(\left\{ j \right\} \) with the set \(\bar 0\), and the set \(\bar 0\) itself will be replaced by the local site \(0\).
+We quote the final form of the local effective action:
+\begin{equation}\begin{aligned}
+	S^{0}_\text{eff} =& \sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{0\sigma}(\tau)\partial_\tau c_{0\sigma}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{0\uparrow}(\tau) - n_{0\downarrow}(\tau)\right)^2 \\
+			  &+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\Delta_{00,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{00}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
+\end{aligned}\end{equation}
+
+\subsection{Local theory for the extended SIAM}
+The Hamiltonian for the extended SIAM model is shown in eq.~\ref{siam_attr}.
+We will denote the impurity with the label \(d\) and the bath sites with the label \(c\).
+Among the bath sites, we will represent the site coupled to the impurity with \(z\).
+The full action has the form
+\begin{equation}\begin{aligned}
+	S_\text{ES} = \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - t\sum_{\left<i,j \right> \in c,\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{i\sigma}(\tau)c_{j\sigma}(\tau) + \text{h.c.}\right] - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right]\\
++ J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{U_b}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 ~,
+\end{aligned}\end{equation}
+As in the Hubbard-Heisenberg model, we first obtain an effective action for the pair of sites \((d,z)\).
+As in the previous calculation, this will again generate a hybridisation function \(\Delta_{zz,\sigma}\) for the bath site nearest to the zeroth site.
+No susceptibility will be generated however, because there is no spin-exchange coupling within the bath.
+The net result is
+\begin{equation}\begin{aligned}
+	S^{d,z}_\text{eff} =& \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right] + J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) \\
+	&- \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{U_b}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 \\
+	&+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\sum_{\sigma}\Delta_{zz,\sigma}(\tau - \tau^\prime)c^\dagger_{z\sigma}(\tau)c_{z\sigma}(\tau^\prime)
+\end{aligned}\end{equation}
+This hybridisation \(\Delta_{zz,\sigma}\) is calculated in the cavity model of the eSIAM, obtained by removing the impurity and the zeroth site from the full model; it is a completely non-interacting system.
+
+One can go one step further and also remove the zeroth site in order to obtain a theory for the impurity site.
+With this choice, the cavity model now also includes the zeroth site, and hence contains the correlation term associated with \(U_b\).
+The one-particle connection \(V\) will lead to a modified hybridisation \(\mathcal{F}\) for this effective theory; the Kondo terms will generate a susceptibility.
+The resultant action is
+\begin{equation}\begin{aligned}
+	S^{d}_\text{eff} =& \sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{d\sigma}(\tau)\partial_\tau c_{d\sigma}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 \\
+			  &+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\mathcal{F}_{\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{d}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
+\end{aligned}\end{equation}
+where \(\mathcal{F}\) is defined in terms of the local correlator of the zeroth site
+\begin{equation}\begin{aligned}
+	\mathcal{F}_\sigma(\tau - \tau^\prime) = V^2 G_1^{(d)}\left(z\sigma\tau; z\sigma\tau^\prime\right) = V^2 \left<c_{z\sigma}(\tau)c^\dagger_{z\sigma}(\tau^\prime)\right>_{(d)}
+\end{aligned}\end{equation}
+with the average computed in the interacting cavity model that has the impurity site removed.
+The interaction arises from the \(U_b-\)term.
+The susceptibility is also calculated in this interacting cavity model, and follows the same definition as in the bulk model:
+\begin{equation}\begin{aligned}
+	\chi_{d}(\tau - \tau^\prime) = J^2\vec{S}_{z}(\tau)\cdot\vec{S}_{z}(\tau^\prime)~.
+\end{aligned}\end{equation}
+\section{Zero temperature Greens function in frequency domain}
+
+\label{appx-spectral-func}
+The impurity retarded Green's function (assuming the Hamiltonian to be time-independent, which it is) is defined as
+\begin{equation}\begin{aligned}
+	G_{dd}^\sigma(t) = -i\theta(t) \left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right>
+\end{aligned}\end{equation}
+where the average \(\left< \right>\) is over a canonical ensemble at temperature \(T\), and \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in.
+The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term.
+What follows is a standard calculation where we write the Green's function in the Lehmann-Kallen representation.
+The ensemble average for an arbitrary operator \(\hat M\) can be written in terms of the exact eigenstates of the fixed point Hamiltonian:
+\begin{equation}\begin{aligned}
+	H^* \ket{n} &= E_n^* \ket{n}, ~ ~ ~\left<\hat M \right> &\equiv \frac{1}{Z}\sum_n \bra{n} \hat M \ket{n} e^{-\beta E_n^*}
+\end{aligned}\end{equation}
+where \(Z = \sum_n e^{-\beta E_n^*}\) is the fixed point partition function and \(\left\{ \ket{n} \right\} \) is the set of eigenfunctions of the fixed point Hamiltonian. We can therefore write
+\begin{equation}\begin{aligned}
+	&\left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right> \\
+	&= \frac{1}{Z}\sum_{m}e^{-\beta E_m}\bra{m}\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\} \ket{m}\\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( \mathcal{O}_{\sigma}(t)\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma}(t)\right) \ket{m} && \left[\sum_n \ket{n}\bra{n} = 1\right]  \\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\right) \ket{m}\\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\left( e^{i\left( E_m - E_n \right)  t}\bra{m}\mathcal{O}_{\sigma}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} \ket{m} + e^{i\left( E_n - E_m \right)  t}\bra{m}\mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma} \ket{m}\right)\\
+	&= \frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
+\end{aligned}\end{equation}
+The time-domain impurity Green's function can thus be written as (this is the so-called Lehmann-Kallen representation)
+\begin{equation}\begin{aligned}
+	G_{dd}^\sigma = -i\theta(t)\frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
+\end{aligned}\end{equation}
+We are interested in the frequency domain form.
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega) &= \int_{-\infty}^\infty dt e^{i \omega t}G_{d d}^\sigma(t) \\
+			       &= \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t}
+\end{aligned}\end{equation}
+To evaluate the time-integral, we will use the integral representation of the Heaviside function:
+\begin{equation}\begin{aligned}
+	\theta(t) = \frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty \frac{1}{x- i\eta}e^{ixt}dx
+\end{aligned}\end{equation}
+With this definition, the integral in \(G_{dd}^\sigma(\omega)\) becomes
+\begin{equation}\begin{aligned}
+	\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t} &= \left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta}\int_{-\infty}^\infty dt e^{i\left( \omega + E_m - E_n + x\right)t} \\
+									     &=\left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta} 2\pi \delta\left( \omega + E_m - E_n + x\right) \\
+									     &=\left(-i\right)\frac{1}{i}\lim_{\eta \to 0^+} \frac{-1}{\omega + E_m - E_n- i\eta} \\
+									     &=\frac{1}{\omega + E_m - E_n} \\
+\end{aligned}\end{equation}
+The frequency-domain Green's function is thus
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
+\end{aligned}\end{equation}
+The zero temperature Green's function is obtained by taking the limit of \(\beta \to \infty\).
+In both the partition function as well as inside the summation, the only term that will survive is the exponential of the ground state energy \(E_0\).
+\begin{equation*}\begin{aligned}
+	Z \equiv \sum_m e^{-\beta E_m} \implies \lim_{\beta \to \infty}Z = d_0 e^{-\beta E_0}, && E_0 \equiv \text{min}\left\{ E_n \right\} 
+\end{aligned}\end{equation*}
+where \(d_0\) is the degeneracy of the ground state. The Greens function then simplifies to
+\begin{equation}\begin{aligned}
+	\label{Gf_lk}
+	G_{d d}^\sigma(\omega, \beta \to \infty) &= \frac{1}{d_0e^{-\beta E_0}}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left[e^{-\beta E_m}\delta_{E_m, E_0} + e^{-\beta E_n}\delta_{E_n, E_0}\right]\frac{1}{\omega + E_m - E_n}\\
+						 &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n}\right]\\
+\end{aligned}\end{equation}
+The label 0 sums over all states \(\ket{0}\) with energy \(E_0\).
+The spectral function is the imaginary part of this Green's function.
+To extract the imaginary part, we insert an infinitesimal imaginary part in the denominator:
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega, \eta) = \frac{1}{d_0}\lim_{\eta \to 0^-}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n + i\eta} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n + i\eta}\right]\\
+\end{aligned}\end{equation}
+The spectral function at zero temperature can then be written as
+\begin{equation}\begin{aligned}
+	\mathcal{A(\omega)} &= -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] \\
+			    &= \frac{1}{d_0}\frac{1}{\pi}\text{ Im }\left[\lim_{\eta \to 0^-}\sum_{n,0}\left(\frac{-i\eta ||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2}{\left(\omega + E_0 - E_n\right)^2 + \eta^2} + \frac{-i\eta ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2}{\left(\omega - E_0 + E_n\right)^2 + \eta^2}\right)\right]\\
+			    &= \frac{1}{d_0}\frac{1}{\pi}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\pi\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\pi\delta\left(\omega - E_0 + E_n\right)\right]\\
+			    &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]\\
+\end{aligned}\end{equation}
+
+\section{Properties of the Bloch states}
+
+\subsection{Translation invariance}
+It is easy to verify that \(\Psi_{\vec k}\left(\left\{ {\bf r}_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \({\bf r}\):
+\begin{equation}\begin{aligned}
+	\Psi_{\vec k}\left(\left\{{\bf r}_k + {\bf r}\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i,{\bf a}} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left({\bf r}_i - {\bf r}, {\bf a}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_j, {\bf a}} e^{i \vec{k}\cdot\left(\vec{R}_j + {\bf r}\right)} \psi_\text{aux}\left({\bf r}_j, {\bf a}\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ {\bf r}_k \right\} \right)
+\end{aligned}\end{equation}
+In the last equation, we transformed \({\bf r}_i \to {\bf r}_j = {\bf r}_i - {\bf r}\).
+Note that the argument \({\bf a}\) does not change under a translation of the system, because that vector always represents the difference between the impurity lattice position and its nearest neighbours, irrespective of the absolute position of the impurity.
+
+The wavefunction can be even brought into the familiar Bloch function form:
+\begin{equation}\begin{aligned}
+	\Psi^n_{\vec k}\left(\left\{{\bf r}_k\right\}\right) = \sum_{{\bf r}_i, {\bf a}} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} \mathcal{Z} N} \psi_\text{aux}\left(\left\{ {\bf r}_d - {\bf r}_i, {\bf r_0} - {\bf r}_i - {\bf a} \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i, {\bf a}} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k{\bf r}_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ {\bf r}_d - {\bf r}_i, {\bf r_0} - {\bf r}_i - {\bf a} \right\} \right) \\
+	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{{\bf r}_k\right\}\right)
+\end{aligned}\end{equation}
+where \({\bf r}_\text{COM} = \frac{1}{N}\sum_k {\bf r}_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{{\bf r}_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k{\bf r}_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{{\bf r}_k - {\bf r}_i\right\}\right)\) is the translation symmetric function.
+This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
+
+\subsection{Orthonormality}
+It is straightforward to show that these states form an orthonormal basis. We start by writing down the inner product of two distinct such states:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r}_j, {\bf a}^\prime \right) | \psi_\text{aux}\left( {\bf r}_i, {\bf a} \right)} \\
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) T^\dagger\left( {\bf r_0} - {\bf r}_j \right) T\left( {\bf r_0} - {\bf r}_i \right) | \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
+\end{aligned}\end{equation}
+At this point, we insert a complete basis of momentum eigenkets \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) T\left( {\bf r}_j - {\bf r}_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
+						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) e^{i \vec q \cdot \left( {\bf r}_j - {\bf r}_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)} \\
+						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2} \delta_{\vec k, \vec k^\prime}\sum_{{\bf a}, {\bf a}^\prime}\braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
+\end{aligned}\end{equation}
+At the last step, we used the summation form of the Kronecker delta function: \(\sum_{{\bf r}_i}e^{i {\bf r}_i \left( \vec k - \vec q \right) }\sum_{{\bf r}_j}e^{i {\bf r}_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\).
+The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \({\bf a}, {\bf a}^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\ket{\vec k}}\):
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2 } \delta_{\vec k, \vec k^\prime}\sum_{{\bf a},{\bf a}^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
+\end{aligned}\end{equation}
+This concludes the proof of orthonormality.
+
+\subsection{Eigenstates}
+To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
+\begin{equation}\begin{aligned}
+	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r}_j, {\bf a}^\prime\right)} H_\text{aux}\left({\bf r}_k\right) \ket{\psi_\text{aux}\left({\bf r}_i, {\bf a}\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)} T^\dagger_{{\bf r_0} - {\bf r}_j} T_{{\bf r_0} - {\bf r}_k} H_\text{aux}\left({\bf r_0}\right) T^\dagger_{{\bf r_0} - {\bf r}_k} T_{{\bf r_0} - {\bf r}_i} \ket{\psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)} T^\dagger_{{\bf r}_k - {\bf r}_j} H_\text{aux}\left({\bf r_0}\right) T_{{\bf r}_k - {\bf r}_i} \ket{\psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}
+\end{aligned}\end{equation}
+To resolve the translation operators, we will now insert the momentum eigenstates \(\ket{\vec k}\) of the full model: \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) in between the operators.
+\begin{equation}\begin{aligned}
+	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, \atop{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{{\bf r}_k - {\bf r}_j} H_\text{aux}\left({\bf r_0}\right) T_{{\bf r}_k - {\bf r}_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+								   &= \sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, \atop{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left({\bf r}_k - {\bf r}_j\right) } e^{i \vec q \cdot \left({\bf r}_k - {\bf r}_i\right)} \braket{\vec q^\prime | H_\text{aux}\left({\bf r_0}\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2}\sum_{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left({\bf r_0}\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2}\delta_{kk^\prime}\sum_{{\bf a}, {\bf a}^\prime} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k} \underbrace{\sum_{{\bf a}, {\bf a}^\prime} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
+	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k}
+\end{aligned}\end{equation}
+The momentum eigenket \(\ket{\vec k}\) can be expressed as a sum over position eigenkets at varying distances from \({\bf r_0}\).
+This form allows a systematic method of improving the energy eigenvalue estimate, because the interacting in the impurity model is extremely localised, so the overlap between two auxiliary models decreases rapidly with distance.
+The majority of the contribution will come from the state at \({\bf r_0}\), and improvements are then made by considering auxiliary models at further distances.
 
@@
 
-\appendix
-\begin{widetext}
-\section{Effective action for the Hubbard-Heisenberg model and the eSIAM}
-In order to better understand the similarities and differences between the tiling approach outlined here and the approach adopted in dynamical mean-field approximations, we compute the effective action for the local impurity as well as the impurity-zeroth site system, in both the auxiliary and bulk models.
-This will be done in the limit of infinite coordination number, in order to create a tractable effective theory.
-
-\subsection{Local theory for the Hubbard-Heisenberg model}
-We will first work with the Hubbard-Heisenberg model.
-Let us recall that within the eSIAM, most of the dynamics is governed by the physics of the impurity site and the bath site coupled to the impurity.
-Accordingly, we will first obtain an effective action within the Hubbard-Heisenberg model for the small system consisting of a local site and all its nearest-neighbours.
-
-We choose a certain local site that we call \(0\), whose nearest-neighbours will be denoted as \(\left\{ {\bar 0} \right\} \).
-The action for the full Hubbard-Heisenberg model can be formally separated into three parts:
-\begin{equation}\begin{aligned}
-S_\text{H-H} = S_{0,{\bar 0}} + S^{(0,{\bar 0})} + S_\text{int}~,
-\end{aligned}\end{equation}
-where \(S_{0,{\bar 0}}\) represents the part of the action that involves only the sites \(0\) and $\left\{ {\bar 0} \right\}$, \(S^{(0,{\bar 0})}\) represents the part that has all the sites apart from \(0\) and \(\left\{ {\bar 0} \right\} \), while \(S_\text{int}\) contains all terms that connect these two parts.
-These three parts have the forms
-\begin{equation}\begin{aligned}
-S_{0,{\bar 0}} = \sum_{i=0,{\bar 0}}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau)  - t\sum_{{\bar 0},\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{0\sigma}(\tau)c_{{\bar 0}\sigma}(\tau) + \text{h.c.}\right] \\
-- \frac{U}{2}\sum_{i=0,{\bar 0}}\int_0^\beta\mathrm{d\tau}~\left(n_{i \uparrow}(\tau) - n_{i \downarrow}(\tau)\right)^2 + J\sum_{{\bar 0}}\int_0^\beta\mathrm{d\tau} \vec{S}_0(\tau)\cdot\vec{S}_{{\bar 0}}(\tau)~,
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-S^{(0,{\bar 0})} = \sum_{j\neq(0,{\bar 0})}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{j\sigma}(\tau)\partial_\tau c_{j\sigma}(\tau)  - t\sum_{\left<j,l\right>\neq (0,{\bar 0}),\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{j\sigma}(\tau)c_{l\sigma}(\tau) + \text{h.c.}\right] \\
-- \frac{U}{2}\sum_{j\neq(0,{\bar 0})}\int_0^\beta\mathrm{d\tau}~\left(n_{j\uparrow}(\tau) - n_{j\downarrow}(\tau)\right)^2 + J\sum_{\left<j,l\right>\neq(0,{\bar 0})}\int_0^\beta\mathrm{d\tau} \vec{S}_l(\tau)\cdot\vec{S}_j(\tau)~,
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-S_\text{int} = -t\sum_{i \in {\bar 0}}\sum_{j \in \text{NN of}~i}\sum_\sigma \int_0^\beta\mathrm{d\tau}~\left(c^\dagger_{i\sigma}(\tau) c_{j\sigma}(\tau) + \text{h.c.}\right) + J\sum_{i \in {\bar 0}}\sum_{j \in \text{NN of}~i}\int_0^\beta\mathrm{d\tau}\vec{S}_i(\tau)\cdot\vec{S}_j(\tau) = S_\text{int}^\text{hop} + S_\text{int}^\text{spin}
-\end{aligned}\end{equation}
-
-In order to obtain an effective theory \(S^{0,{\bar 0}}_\text{eff}\) purely for the local system \((0,{\bar 0})\), we need to trace over all the other degrees of freedom.
-This partial trace will be carried out over the states of the so-called ``cavity" system \(S^{(0,{\bar 0})}\).
-The effective action can be constructed by tracing over scattering processes of all orders that leave the final action diagonal in the system \((0,{\bar 0})\).
-The formal expression can be written as
-\begin{equation}\begin{aligned}
-	S^{0,{\bar 0}}_\text{eff} = S_{0,{\bar 0}} + \sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} + \sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})}
-\end{aligned}\end{equation}
-where, as mentioned before, the average is carried out in the cavity system \(S^{(0,{\bar 0})}\). Each hopping term in the expansion is of the form
-\begin{equation}\begin{aligned}
-	\left(S_\text{int}^\text{hop}\right)^{2n} =& t^{2n}\sum_\sigma\sum_{(i_1, i_1^\prime)\ldots, (i_n, i_n^\prime)} ~\sum_{(j_1, j_1^\prime)\ldots, (j_n, j_n^\prime)} \int_0^\beta d\tau_{1}\ldots d\tau_{n}d\tau_{1}^\prime\ldots d\tau_{j_n}^\prime\\
-			   &c^\dagger_{i_1\sigma}(\tau_{i_1})c^\dagger_{i_2\sigma}(\tau_{2})\ldots c^\dagger_{i_n\sigma}(\tau_{n}) c_{i_1^\prime\sigma}(\tau_{1}^\prime)c_{i_2^\prime\sigma}(\tau_{2}^\prime)\ldots c_{i_n^\prime\sigma}(\tau_{n}^\prime)\left<c_{j_1\sigma}(\tau_{1})c_{j_2\sigma}(\tau_{2})\ldots c_{j_n\sigma} ~ c^\dagger_{j_1^\prime\sigma}(\tau_{1}^\prime)\ldots c^\dagger_{j_n^\prime\sigma}(\tau_{n}^\prime) \right>_{(0,{\bar 0})}\\
-	=& t^{2n}\sum_\sigma\sum_{(i_1, i_1^\prime)\ldots, (i_n, i_n^\prime)} ~\sum_{(j_1, j_1^\prime)\ldots, (j_n, j_n^\prime)} \int_0^\beta d\tau_{1}\ldots d\tau_{j_n}^\prime c^\dagger_{i_1\sigma}(\tau_{i_1})\ldots c^\dagger_{i_n\sigma}(\tau_{n})~c_{i_1^\prime\sigma}(\tau_{1}^\prime)\ldots c_{i_n^\prime\sigma}(\tau_{n}^\prime)\\
-	 &G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right)~,
-\end{aligned}\end{equation}
-where the indices \(i_1\) through \(i_n\) and their primed counterparts run through \(\bar 0\), while \(j_l\) (\(\in \left\{j_1,\ldots,j_n^\prime\right\}\)) runs through the nearest-neighbours of the corresponding \(i_l\) index.
-The \(n-\)particle Greens function \(G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right)\) for the cavity system is defined in the usual fashion
-\begin{equation}\begin{aligned}
-	G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right) = \left<c_{j_1\sigma}(\tau_{1})c_{j_2\sigma}(\tau_{2})\ldots c_{j_n\sigma} ~ c^\dagger_{j_1^\prime\sigma}(\tau_{1}^\prime)\ldots c^\dagger_{j_n^\prime\sigma}(\tau_{n}^\prime) \right>_{(0,{\bar 0})}
-\end{aligned}\end{equation}
-In the limit of infinite coordination number, only the \(n=1\) term survives:
-\begin{equation}\begin{aligned}
-	\lim_{\mathcal{Z}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} = t^2\sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)\sum_{j,j^\prime}G_1^{(0,\bar 0)}\left(j\tau; j^\prime\tau^\prime\right) \\
-	= \sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)~,
-\end{aligned}\end{equation}
-where we have defined the bath hybridisation function \(\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)\) as
-\begin{equation}\begin{aligned}
-	\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime) = t^2\sum_{j \in \text{NN of}~i}\sum_{j^\prime \in \text{NN of}~i^\prime}G_1^{(0,\bar 0)}\left(j\sigma\tau; j^\prime\sigma\tau^\prime\right)~.
-\end{aligned}\end{equation}
-
-Under similar approximations, the spin term in the action reduces to
-\begin{equation}\begin{aligned}
-	\lim_{\mathcal{Z}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})} = \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\chi(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)~,
-\end{aligned}\end{equation}
-where the susceptibility \(\chi_{ii^\prime}(\tau - \tau^\prime)\) is defined as 
-\begin{equation}\begin{aligned}
-	\chi_{ii^\prime}(\tau - \tau^\prime) = J^2\sum_{j \in \text{NN of}~i}\sum_{j^\prime \in \text{NN of}~i^\prime}\vec{S}_{j}(\tau)\cdot\vec{S}_{j^\prime}(\tau^\prime)~.
-\end{aligned}\end{equation}
-The effective action for the \(0,\bar 0\) system, in the limit of large coordination number, simplifies to
-\begin{equation}\begin{aligned}
-	S^{0,{\bar 0}}_\text{eff} =& \sum_{i=0,{\bar 0}}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau)  - t\sum_{{\bar 0},\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{0\sigma}(\tau)c_{{\bar 0}\sigma}(\tau) + \text{h.c.}\right] - \frac{U}{2}\sum_{i=0,{\bar 0}}\int_0^\beta\mathrm{d\tau}~\left(n_{i \uparrow}(\tau) - n_{i \downarrow}(\tau)\right)^2 \\
-				   &+ J\sum_{{\bar 0}}\int_0^\beta\mathrm{d\tau} \vec{S}_0(\tau)\cdot\vec{S}_{{\bar 0}}(\tau) + \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{ii^\prime}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
-\end{aligned}\end{equation}
-
-One can also write down an effective action purely for the local site \(0\).
-The sites \(\bar 0\) will now be a part of the environment action \(S^{(0)}\) instead of the system action, but since the system is thermodynamically large, the cavity action can be assumed to remain the same, such the expectation values are calculated in the same system.
-As a result, the hybridisation and susceptibility functions remain unchanged.
-\(S_\text{int}\) is now made of terms that connect \(0\) and \(\bar 0\), so the transformation from \(S^{(0,\bar 0)}\) can be made by replacing the set \(\left\{ j \right\} \) with the set \(\bar 0\), and the set \(\bar 0\) itself will be replaced by the local site \(0\).
-We quote the final form of the local effective action:
-\begin{equation}\begin{aligned}
-	S^{0}_\text{eff} =& \sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{0\sigma}(\tau)\partial_\tau c_{0\sigma}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{0\uparrow}(\tau) - n_{0\downarrow}(\tau)\right)^2 \\
-			  &+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\Delta_{00,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{00}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
-\end{aligned}\end{equation}
-
-\subsection{Local theory for the extended SIAM}
-The Hamiltonian for the extended SIAM model is shown in eq.~\ref{siam_attr}.
-We will denote the impurity with the label \(d\) and the bath sites with the label \(c\).
-Among the bath sites, we will represent the site coupled to the impurity with \(z\).
-The full action has the form
-\begin{equation}\begin{aligned}
-	S_\text{ES} = \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - t\sum_{\left<i,j \right> \in c,\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{i\sigma}(\tau)c_{j\sigma}(\tau) + \text{h.c.}\right] - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right]\\
-+ J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{U_b}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 ~,
-\end{aligned}\end{equation}
-As in the Hubbard-Heisenberg model, we first obtain an effective action for the pair of sites \((d,z)\).
-As in the previous calculation, this will again generate a hybridisation function \(\Delta_{zz,\sigma}\) for the bath site nearest to the zeroth site.
-No susceptibility will be generated however, because there is no spin-exchange coupling within the bath.
-The net result is
-\begin{equation}\begin{aligned}
-	S^{d,z}_\text{eff} =& \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right] + J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) \\
-	&- \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{U_b}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 \\
-	&+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\sum_{\sigma}\Delta_{zz,\sigma}(\tau - \tau^\prime)c^\dagger_{z\sigma}(\tau)c_{z\sigma}(\tau^\prime)
-\end{aligned}\end{equation}
-This hybridisation \(\Delta_{zz,\sigma}\) is calculated in the cavity model of the eSIAM, obtained by removing the impurity and the zeroth site from the full model; it is a completely non-interacting system.
-
-One can go one step further and also remove the zeroth site in order to obtain a theory for the impurity site.
-With this choice, the cavity model now also includes the zeroth site, and hence contains the correlation term associated with \(U_b\).
-The one-particle connection \(V\) will lead to a modified hybridisation \(\mathcal{F}\) for this effective theory; the Kondo terms will generate a susceptibility.
-The resultant action is
-\begin{equation}\begin{aligned}
-	S^{d}_\text{eff} =& \sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{d\sigma}(\tau)\partial_\tau c_{d\sigma}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 \\
-			  &+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\mathcal{F}_{\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{d}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
-\end{aligned}\end{equation}
-where \(\mathcal{F}\) is defined in terms of the local correlator of the zeroth site
-\begin{equation}\begin{aligned}
-	\mathcal{F}_\sigma(\tau - \tau^\prime) = V^2 G_1^{(d)}\left(z\sigma\tau; z\sigma\tau^\prime\right) = V^2 \left<c_{z\sigma}(\tau)c^\dagger_{z\sigma}(\tau^\prime)\right>_{(d)}
-\end{aligned}\end{equation}
-with the average computed in the interacting cavity model that has the impurity site removed.
-The interaction arises from the \(U_b-\)term.
-The susceptibility is also calculated in this interacting cavity model, and follows the same definition as in the bulk model:
-\begin{equation}\begin{aligned}
-	\chi_{d}(\tau - \tau^\prime) = J^2\vec{S}_{z}(\tau)\cdot\vec{S}_{z}(\tau^\prime)~.
-\end{aligned}\end{equation}
-\section{Zero temperature Greens function in frequency domain}
-
-\label{appx-spectral-func}
-The impurity retarded Green's function (assuming the Hamiltonian to be time-independent, which it is) is defined as
-\begin{equation}\begin{aligned}
-	G_{dd}^\sigma(t) = -i\theta(t) \left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right>
-\end{aligned}\end{equation}
-where the average \(\left< \right>\) is over a canonical ensemble at temperature \(T\), and \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in.
-The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term.
-What follows is a standard calculation where we write the Green's function in the Lehmann-Kallen representation.
-The ensemble average for an arbitrary operator \(\hat M\) can be written in terms of the exact eigenstates of the fixed point Hamiltonian:
-\begin{equation}\begin{aligned}
-	H^* \ket{n} &= E_n^* \ket{n}, ~ ~ ~\left<\hat M \right> &\equiv \frac{1}{Z}\sum_n \bra{n} \hat M \ket{n} e^{-\beta E_n^*}
-\end{aligned}\end{equation}
-where \(Z = \sum_n e^{-\beta E_n^*}\) is the fixed point partition function and \(\left\{ \ket{n} \right\} \) is the set of eigenfunctions of the fixed point Hamiltonian. We can therefore write
-\begin{equation}\begin{aligned}
-	&\left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right> \\
-	&= \frac{1}{Z}\sum_{m}e^{-\beta E_m}\bra{m}\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\} \ket{m}\\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( \mathcal{O}_{\sigma}(t)\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma}(t)\right) \ket{m} && \left[\sum_n \ket{n}\bra{n} = 1\right]  \\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\right) \ket{m}\\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\left( e^{i\left( E_m - E_n \right)  t}\bra{m}\mathcal{O}_{\sigma}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} \ket{m} + e^{i\left( E_n - E_m \right)  t}\bra{m}\mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma} \ket{m}\right)\\
-	&= \frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
-\end{aligned}\end{equation}
-The time-domain impurity Green's function can thus be written as (this is the so-called Lehmann-Kallen representation)
-\begin{equation}\begin{aligned}
-	G_{dd}^\sigma = -i\theta(t)\frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
-\end{aligned}\end{equation}
-We are interested in the frequency domain form.
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega) &= \int_{-\infty}^\infty dt e^{i \omega t}G_{d d}^\sigma(t) \\
-			       &= \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t}
-\end{aligned}\end{equation}
-To evaluate the time-integral, we will use the integral representation of the Heaviside function:
-\begin{equation}\begin{aligned}
-	\theta(t) = \frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty \frac{1}{x- i\eta}e^{ixt}dx
-\end{aligned}\end{equation}
-With this definition, the integral in \(G_{dd}^\sigma(\omega)\) becomes
-\begin{equation}\begin{aligned}
-	\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t} &= \left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta}\int_{-\infty}^\infty dt e^{i\left( \omega + E_m - E_n + x\right)t} \\
-									     &=\left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta} 2\pi \delta\left( \omega + E_m - E_n + x\right) \\
-									     &=\left(-i\right)\frac{1}{i}\lim_{\eta \to 0^+} \frac{-1}{\omega + E_m - E_n- i\eta} \\
-									     &=\frac{1}{\omega + E_m - E_n} \\
-\end{aligned}\end{equation}
-The frequency-domain Green's function is thus
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
-\end{aligned}\end{equation}
-The zero temperature Green's function is obtained by taking the limit of \(\beta \to \infty\).
-In both the partition function as well as inside the summation, the only term that will survive is the exponential of the ground state energy \(E_0\).
-\begin{equation*}\begin{aligned}
-	Z \equiv \sum_m e^{-\beta E_m} \implies \lim_{\beta \to \infty}Z = d_0 e^{-\beta E_0}, && E_0 \equiv \text{min}\left\{ E_n \right\} 
-\end{aligned}\end{equation*}
-where \(d_0\) is the degeneracy of the ground state. The Greens function then simplifies to
-\begin{equation}\begin{aligned}
-	\label{Gf_lk}
-	G_{d d}^\sigma(\omega, \beta \to \infty) &= \frac{1}{d_0e^{-\beta E_0}}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left[e^{-\beta E_m}\delta_{E_m, E_0} + e^{-\beta E_n}\delta_{E_n, E_0}\right]\frac{1}{\omega + E_m - E_n}\\
-						 &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n}\right]\\
-\end{aligned}\end{equation}
-The label 0 sums over all states \(\ket{0}\) with energy \(E_0\).
-The spectral function is the imaginary part of this Green's function.
-To extract the imaginary part, we insert an infinitesimal imaginary part in the denominator:
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega, \eta) = \frac{1}{d_0}\lim_{\eta \to 0^-}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n + i\eta} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n + i\eta}\right]\\
-\end{aligned}\end{equation}
-The spectral function at zero temperature can then be written as
-\begin{equation}\begin{aligned}
-	\mathcal{A(\omega)} &= -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] \\
-			    &= \frac{1}{d_0}\frac{1}{\pi}\text{ Im }\left[\lim_{\eta \to 0^-}\sum_{n,0}\left(\frac{-i\eta ||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2}{\left(\omega + E_0 - E_n\right)^2 + \eta^2} + \frac{-i\eta ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2}{\left(\omega - E_0 + E_n\right)^2 + \eta^2}\right)\right]\\
-			    &= \frac{1}{d_0}\frac{1}{\pi}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\pi\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\pi\delta\left(\omega - E_0 + E_n\right)\right]\\
-			    &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]\\
-\end{aligned}\end{equation}
-
-\section{Spectrum of the Hubbard dimer}
-Here we document the spectrum of the Hubbard dimer Hamiltonian.
-\begin{center}
-	\begin{tabular}{|c|c|c|}
-	\hline
-	eigenstate & symbol & eigenvalue \\
-	\hline
-	$\ket{0,0}$ & $\ket{0}$ & \( \frac{U^H}{2}\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,0} \pm \ket{0,\sigma}\right)$ & $\ket{0\sigma_\pm}$ & \(\mp t^H\)\\
-	$\ket{\sigma,\sigma}$ & $\ket{\sigma\sigma}$ & \( -\frac{U^H}{2}\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} + \ket{\downarrow,\uparrow}\right)$ & $\ket{ST}$ & \( -\frac{U^H}{2}\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{2,0} - \ket{0,2}\right)$ & $\ket{CS}$ & \( \frac{U^H}{2}\)\\
-	$a_1(U^H, t^H) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_2(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{-}$ & \(-\frac{1}{2}\Delta(U^H, t^H)\)\\
-	$-a_2(U^H, t^H) \frac{1}{\sqrt 2}\left(\ket{\uparrow,\downarrow} - \ket{\downarrow,\uparrow}\right) + a_1(U^H, t^H)\frac{1}{\sqrt 2}\left(\ket{2,0} + \ket{0,2}\right)$ & $\ket{+}$ & \(\frac{1}{2}\Delta(U^H, t^H)\)\\
-	$ \frac{1}{\sqrt 2}\left(\ket{\sigma,2} \pm \ket{2,\sigma}\right)$ & $\ket{2\sigma_\pm}$ & \(\pm t^H\)\\
-	$\ket{2,2}$ & $\ket{4}$ & \( \frac{U^H}{2}\)\\
-\hline
-	\end{tabular}
-	%\captionof{table}{Spectrum of Hubbard dimer at half-filling}
-	\label{hubb_dim_spectrum}
-\end{center}
-
-\section{Greens function of Hubbard model in the atomic limit}
-\label{atomic limit}
-The atomic limit is described by the Hamiltonian \(H = -\frac{U}{2}\sum_i\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\).
-Since the Hamiltonian has decoupled into \(\sum_i \equiv N\) single-site Hamiltonians, we can easily write down the retarded Greens function for a single site by identifying the ground state configuration of a site.
-The ground states are of course \(\ket{\Psi}_i = \ket{\uparrow},\ket{\downarrow}\), in the absence of any symmetry-breaking.
-The finite temperature retarded Greens function in the time domain is given by
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(T,t) = -i\theta(t) \frac{1}{Z}\sum_n e^{-\beta E_n} \braket{n | \left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} | n}
-\end{aligned}\end{equation}
-where \(n\) labels the eigenstates of the \(H\). At \(T \to 0\), only the ground states will survive in the exponential and the partition function \(Z\), such that the formula then reduces to
-\begin{equation}\begin{aligned}
-G_{i,\sigma}(T \to 0,t) = -i\theta(t)\braket{GS | \left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} | GS}
-\end{aligned}\end{equation}
-Since the Hamiltonian is simple, we can compute the time-dependent operator \(c_{i\sigma}(t) = e^{iH t} c_{i\sigma} e^{-iHt}\). Using the BCH lemma, we have
-\begin{equation}\begin{aligned}
-	e^{iH t} c_{i\sigma} e^{-iHt} = \sum_{n=0}^\infty \left(it\right)^n \frac{1}{n!}\left[H,c_{i\sigma}\right]_n
-\end{aligned}\end{equation}
-where \(\left[H,c_{i\sigma}\right]_n = \left[H,\left[H,c_{i\sigma}\right]_{n-1}\right],\left[H,c_{i\sigma}\right]_0=c_{i\sigma}\). The first two non-trivial commutators are
-\begin{equation}\begin{aligned}
-	\left[H, c_{i\sigma}\right]_1 = -U \tau_{i\overline\sigma}c_{i\sigma},~ ~\text{and} ~~\left[H, c_{i\sigma}\right]_2 = \frac{1}{4}U^2 c_{i\sigma}~,
-\end{aligned}\end{equation}
-such that
-\begin{equation}\begin{aligned}
-	e^{iH t} c_{i\sigma} e^{-iHt} =& \left[c_{i\sigma} + \frac{i^2 t^2}{2!}\frac{U^2}{2^2} c_{i\sigma} + \frac{i^4 t^4}{4!}\frac{U^4}{2^4} c_{i\sigma} + \ldots\right] + \left[- \frac{it}{1!}U\tau_{i\overline\sigma}c_{i\sigma} - \frac{i^3 t^3}{3!}\frac{U^3}{4}\tau_{i\overline\sigma}c_{i\sigma} + \ldots \right]\\
-				       &= c_{i\sigma} \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] 
-\end{aligned}\end{equation}
-Using this, we can write
-\begin{equation}\begin{aligned}
-	\left\{c_{i\sigma}(t),c^\dagger_{i\sigma}\right\} = \left\{c_{i\sigma},c^\dagger_{i\sigma}\right\} \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] = \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right]
-\end{aligned}\end{equation}
-and the Greens function becomes
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(T \to 0,t) = -i\theta(t) \braket{GS | \left[\cos\left(Ut/2\right) - 2i\tau_{i\overline\sigma}\sin \left(Ut/2\right) \right] | GS} = -i\theta(t)\left[\cos \frac{Ut}{2} - 2i\sin \frac{Ut}{2} \left<\tau_{i\overline\sigma} \right>\right]
-\end{aligned}\end{equation}
-We now Fourier transform to frequency domain:
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(\omega) = -i\int_{0}^\infty \mathrm{dt} e^{i\omega t}\left[\cos \frac{Ut}{2} - 2i\sin \frac{Ut}{2} \left<\tau_{i\overline\sigma} \right>\right] = \frac{1 + \left<\tau_{i\overline\sigma }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i\overline\sigma}\right>}{\omega + \frac{U}{2}}
-\end{aligned}\end{equation}
-The spin-total Greens function for the site \(i\) is
-\begin{equation}\begin{aligned}
-	\label{atomic_limit_gf}
-	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 + \left<\tau_{i }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i}\right>}{\omega + \frac{U}{2}}
-\end{aligned}\end{equation}
-At half-filling, we have \(\tau_i = 1\).
-\section{Local Greens function for the Hubbard dimer}
-From the spectral representation, we have the following expression for the local Greens function for the Hubbard dimer at site $0$:
-\begin{equation}\begin{aligned}
-	G_{D,00}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}c_{i\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
-\end{aligned}\end{equation}
-$m,n$ sum over the exact eigenstates.
-$E_m, E_n$ are the corresponding energies.
-We are interested in teh $T \to 0$ Greens function.
-In that limit, all exponentials except that for the ground state $E_{gs}$ will die out.
-The exponential inside the summation will then cancel the exponential in the partition function.
-\begin{equation}\begin{aligned}
-	G_{D,00}^\sigma(\omega, T \to 0) &= \sum_{n}\left[||\bra{GS}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
-					&= \sum_{n}\left[||\bra{n}c^\dagger_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{GS}||^2\frac{1}{\omega + E_n - E_{GS}}\right]\\
-\end{aligned}\end{equation}
-
-The ground state $\ket{GS}$ is just the state $\ket{-}$ in the table \ref{hubb_dim_spectrum}. We will choose to look at $\sigma = \uparrow`$. Then,
-\begin{equation}\begin{aligned}
-	c_{1\uparrow}\ket{-} &= \frac{a_1}{\sqrt 2}\ket{0, \downarrow} + \frac{a_2}{\sqrt 2}\ket{\downarrow,0}\\
-	c^\dagger_{1\uparrow}\ket{-} &= -\frac{a_1}{\sqrt 2}\ket{2, \uparrow} + \frac{a_2}{\sqrt 2}\ket{\uparrow,2}\\
-\end{aligned}\end{equation}
-The set of states $\ket{n}$ that give non-zero inner product $\ket{GS}$ are therefore
-\begin{equation}\begin{aligned}
-	\left\{ \ket{n} \right\} &= \ket{0\downarrow_\pm}\\
-	||\bra{n}c_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left(a_2 \pm a_1 \right)^2 = \frac{1}{4}\left(1 \pm 2a_1a_2\right)\\
-	\left\{ E_n \right\} &= \mp t
-\end{aligned}\end{equation}
-for the second inner product, and
-\begin{equation}\begin{aligned}
-	\left\{\ket{n}\right\} &= \ket{2\uparrow_\pm}\\
-	||\bra{n}c^\dagger_{\uparrow\sigma}\ket{GS}||^2 &= \frac{1}{4}\left( a_2 \mp a_1 \right)^2 = \frac{1}{4}\left(1 \mp 2a_1a_2\right)\\
-	\left\{ E_n \right\} &= \pm t
-\end{aligned}\end{equation}
-for the first. The Greens function is therefore
-\begin{equation}\begin{aligned}
-	\label{dimer_local_G}
-	G_{D,00}^\uparrow(\omega, T \to 0) &= \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(t - \frac{\Delta}{2}\right) ^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{\omega}{\omega^2 - \left(t + \frac{\Delta}{2}\right) ^2} = G_{D,00}^\downarrow(\omega, T \to 0)~.
-\end{aligned}\end{equation}
-In the atomic limit $(t=0)$, the Greens function simplifies to
-\begin{equation}\begin{aligned}
-	G_{D,00}^\uparrow(\omega, T \to 0) \bigg\vert_\text{atomic} = \frac{\omega}{\omega^2 - \frac{1}{4}U^2}
-\end{aligned}\end{equation}
-In the atomic limit, the singly-occupied state has zero energy:
-\begin{equation}\begin{aligned}
-	E_1(t=0) = \bra{1,0}\left(U \tau_{0 \uparrow}\tau_{0 \downarrow} + U \tau_{1 \uparrow}\tau_{1 \downarrow}\right) \ket{1,0} = 0
-\end{aligned}\end{equation}
-We can write the atomic limit Greens function in terms of this energy and the self energy:
-\begin{equation}\begin{aligned}
-	G_{D,00}^\uparrow(\omega, T \to 0) \bigg\vert_\text{atomic} = \frac{1}{\omega - E_1(t=0) - \Sigma(t=0)} = \frac{1}{\omega - 0 -\frac{U^2}{4\omega}}
-\end{aligned}\end{equation}
-The self energy in the atomic limit can be read off as 
-\begin{equation}\begin{aligned}
-	\label{dimer_selfenergy}
-\Sigma(t=0) = \frac{U^2}{4\omega}
-\end{aligned}\end{equation}
-The site local spectral function can also be calculated from the local Greens function:
-\begin{eqnarray}
-A(0\uparrow, \omega) &=& - \frac{1}{\pi}\text{Im }G_{D,00}^\uparrow(\omega)\nonumber\\
-			     &=& \left( \frac{1}{4} - \frac{t}{\Delta} \right)\left[\delta(\omega - \frac{1}{2}\Delta - t) + \delta(\omega + \frac{1}{2}\Delta + t)\right]\nonumber\\ 
-			     &&+ \left( \frac{1}{4} + \frac{t}{\Delta} \right) \left[\delta(\omega - \frac{1}{2}\Delta + t) + \delta(\omega + \frac{1}{2}\Delta - t)\right]\\ 
-			     &=& A(0\downarrow, \omega)~.\nonumber
-\end{eqnarray}
-Finally, the inter-site Greens function for the Hubbard dimer is given by
-\begin{equation}
-\label{dimer_intersite_G}
-G_{D,01}^\uparrow(\omega, T \to 0) = \left( \frac{1}{2} + \frac{2t}{\Delta} \right) \frac{t - \frac{\Delta}{2}}{\omega^2 - \left(t - \frac{\Delta}{2}\right)^2} + \left( \frac{1}{2} - \frac{2t}{\Delta} \right) \frac{t + \frac{\Delta}{2}}{\omega^2 - \left(t + \frac{\Delta}{2}\right)^2} = G_{D,01}^\downarrow(\omega, T \to 0)~.
-\end{equation}
-Using the diagonal and off-diagonal real space Greens functions, we can now compute the momentum-space Greens functions.
-The two momentum states are $ka = 0, \pi$.
-By Fourier transforming, these two Greens functions can be written as
-\begin{equation}\begin{aligned}
-	\label{Gk0}
-	G(k=0, \sigma) = \sum_r e^{ikr} G(r, \sigma) = G(r=0, \sigma) + G(r=a, \sigma) = \frac{1/2 + 2t/\Delta}{\omega -t + \Delta/2} + \frac{1/2 - 2t/\Delta}{\omega - t - \Delta/2}\\
-	G(k=\pi, \sigma) = \sum_r e^{ikr} G(r, \sigma) = G(r=0, \sigma) - G(r=a, \sigma) = \frac{1/2 + 2t/\Delta}{\omega + t - \Delta/2} + \frac{1/2 - 2t/\Delta}{\omega + t + \Delta/2}\\
-\end{aligned}\end{equation}
-
-The site local spectral function is
-\begin{equation}\begin{aligned}
-	A(0\uparrow, \omega) = \left( \frac{1}{4} - \frac{t}{\Delta} \right)\left[\delta(\omega - \frac{\Delta}{2} - t) + \delta(\omega + \frac{\Delta}{2} + t)\right]\nonumber + \left( \frac{1}{4} + \frac{t}{\Delta} \right) \left[\delta(\omega - \frac{\Delta}{2} + t) + \delta(\omega + \frac{\Delta}{2} - t)\right]
-\end{aligned}\end{equation}
-If the eigenstates of the $N=1, S^z = - \frac{1}{2}$ sector are $\ket{1 \pm \downarrow}$ and those of $N=3, S^z = \frac{1}{2}$ sector are $\ket{3 \pm \uparrow}$, this spectral function originates from the expression:
-\begin{equation}\begin{aligned}
-	A(0\uparrow, \omega) =& \braket{1 \downarrow_- | c_{0 \uparrow} | \text{GS}} \delta\left(\omega + \frac{\Delta}{2} + t\right) + \braket{2 \uparrow_+ | c^\dagger_{0 \uparrow} | \text{GS}}\delta\left(\omega - \frac{\Delta}{2} - t\right) \\
-			      &+ \braket{1 \downarrow_+ | c_{0 \uparrow} | \text{GS}}\delta\left(\omega + \frac{\Delta}{2} - t\right) + \braket{2 \uparrow_- | c^\dagger_{0 \uparrow} | \text{GS}}\delta(\omega - \frac{\Delta}{2} + t)
-\end{aligned}\end{equation}
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.9\textwidth]{dimer-peaks.png}
-	\caption{Position, weight and nature of each of the peaks in the Hubbard dimer site local spectral function}
-\end{figure}
-
-\section{Relation between single-particle Greens function and the Greens operator $(T=0)$}
- The single-particle Greens function is defined as the solution of the equation:
- \begin{equation}\begin{aligned}
-	 \left(i\partial_t - H({\bf r})\right)G({\bf r},{\bf r}^\prime, t) = \delta({\bf r} - {\bf r}^\prime)
- \end{aligned}\end{equation}
- and is given by the expression
- \begin{equation}\begin{aligned}
-	 G({\bf r},{\bf r}^\prime, t) = -i \theta(t) \left< \left\{ c({\bf r}, t) c^\dagger({\bf r}^\prime, 0)\right\} \right>
- \end{aligned}\end{equation}
- This solution can be written in the Lehmann-Kallen representation  and at $T=0$ as
- \begin{equation}\begin{aligned}
-	 G({\bf r} \sigma, {\bf r}^\prime \sigma, \omega) = \sum_{n}\left[\frac{\bra{GS}c({{\bf r},\sigma})\ket{n}\bra{n}c^\dagger({\bf r}^\prime,\sigma)\ket{GS}}{\omega + E_{GS} - E_n} + \frac{\bra{GS}c^\dagger({\bf r}^\prime,\sigma)\ket{n}\bra{n}c({{\bf r},\sigma})\ket{GS}}{\omega + E_n - E_{GS}}\right]
- \end{aligned}\end{equation}
- The sum is over the exact eigenstates of the Hamiltonian. In what follows, we will represent ${\bf r},\sigma \equiv \nu$ and ${\bf r}^\prime,\sigma \equiv \nu^\prime$.
- \begin{equation}\begin{aligned}
-	 G(\nu, \nu^\prime, \omega) &= \sum_{n}\left[\frac{\bra{GS}c(\nu)\ket{n}\bra{n}c^\dagger(\nu^\prime)\ket{GS}}{\omega + E_{GS} - E_n} + \frac{\bra{GS}c^\dagger(\nu^\prime)\ket{n}\bra{n}c(\nu)\ket{GS}}{\omega + E_n - E_{GS}}\right]\\
-							&= \bra{GS}c(\nu)\frac{1}{\omega + E_{GS} - H}c^\dagger(\nu^\prime)\ket{GS} + \bra{GS}c^\dagger(\nu^\prime)\frac{1}{\omega + H - E_{GS}}c(\nu)\ket{GS}\\
- \end{aligned}\end{equation}
- If we now define a Greens operator
- \begin{equation}\begin{aligned}
-	 \label{inv_G_func}
-	 \mathcal{G}(\omega, H) = \frac{1}{\omega - (H - E_\text{GS})}
- \end{aligned}\end{equation}
- we can write the single-particle Greens function as a sum of the matrix elements of this operator:
- \begin{equation}\begin{aligned}
-	 \label{G_mat_el}
-	 G(\nu, \nu^\prime, \omega) = \bra{\nu} \mathcal{G}(\omega, H) \ket{\nu^\prime} - \bra{\overline{\nu^\prime}} \mathcal{G}(-\omega, H) \ket{\overline\nu} = \mathcal{G}(\omega, H)_{\nu,\nu^\prime} - \mathcal{G}(-\omega, H)_{\overline{\nu^\prime}, \overline\nu}
- \end{aligned}\end{equation}
- where we have defined the states $\ket{\nu} \equiv c^\dagger(\nu)\ket{GS}$ and $\ket{\overline\nu} \equiv c(\nu)\ket{GS}$.
-The two matrix elements can also be represented in their individual spectral representations:
- \begin{equation}\begin{aligned}
-	 \label{G_mat_spec}
- 	\mathcal{G}(\omega, H)_{\nu,\nu^\prime} = \sum_{n}\frac{\bra{GS}c(\nu)\ket{n}\bra{n}c^\dagger(\nu^\prime)\ket{GS}}{\omega + E_{GS} - E_n}\\
-	\mathcal{G}(\omega, H)_{\overline{\nu^\prime}, \overline\nu} = \sum_{n}\frac{\bra{GS}c^\dagger(\nu^\prime)\ket{n}\bra{n}c(\nu)\ket{GS}}{\omega + E_\text{GS} - E_n}
- \end{aligned}\end{equation}
-
-\section{Writing single-particle excitations of ground state in terms of $N=3, S^z = \frac{1}{2}$ eigenstates}
-The excited state $c^\dagger_{0\uparrow}\ket{\text{GS}}$ can actually be written in terms of the $N=3$, $S^z = + \frac{1}{2}$ eigenstates $\ket{3\pm\uparrow}$ defined in table \ref{hubb_dim_spectrum}.
-\begin{equation}\begin{aligned}
-	\ket{3\pm \uparrow} = \frac{1}{\sqrt 2}\left(\ket{\uparrow, 2} \pm \ket{2, \uparrow}\right), && H^D \ket{3\pm \uparrow} = \pm t\ket{3\pm \uparrow}
-\end{aligned}\end{equation}
-In terms of these eigenstates, we can write
-\begin{equation}\begin{aligned}
-	c^\dagger_{0\uparrow}\ket{\text{GS}} 
-	&= c^\dagger_{0\uparrow}\left[a_1 \ket{SS} + a_2 \ket{CT}\right] \\
-	&= a_2 \frac{1}{\sqrt 2}\ket{\uparrow,2} - a_1 \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
-	&= \left(x + y\right) \frac{1}{\sqrt 2}\ket{\uparrow,2} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow}\\
-	&=x\ket{3+ \uparrow} + y\ket{3- \uparrow}
-\end{aligned}\end{equation}
-where $x + y \equiv a_2$ and $x-y \equiv -a_1$. Similarly, for the other site excitation, we can write
-\begin{equation}\begin{aligned}
-	c^\dagger_{1\uparrow}\ket{\text{GS}} 
-	&= c^\dagger_{1\uparrow}\left[a_1 \ket{SS} + a_2 \ket{CT}\right] \\
-	&= a_2 \frac{1}{\sqrt 2}\ket{2, \uparrow} - a_1 \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
-	&=  \left(x + y\right) \frac{1}{\sqrt 2}\ket{2, \uparrow} + \left(x - y\right) \frac{1}{\sqrt 2}\ket{\uparrow, 2}\\
-	&=x\ket{3+ \uparrow} - y\ket{3- \uparrow}
-\end{aligned}\end{equation}
-Solving for $x$ and $y$ gives
-\begin{equation}\begin{aligned}
-	x = \frac{a_2 - a_1}{2}, && y = \frac{a_2 + a_1}{2}
-\end{aligned}\end{equation}
-Similarly, we can also write the single-hole excitation $c_{0 \uparrow}\ket{GS}$ in terms of the $N=1, S^z = -\frac{1}{2}$ eigenstates, $\ket{1\pm \downarrow}$:
-\begin{equation}\begin{aligned}
-	\ket{1\pm \downarrow} = \frac{1}{\sqrt 2}\left(\ket{\downarrow, 0} \pm \ket{0, \downarrow}\right), && H^D \ket{1\pm \downarrow} = \mp t\ket{1\pm \downarrow}
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-	c_{0 \uparrow}\ket{GS} = a_1 \frac{1}{\sqrt 2}\ket{0, \downarrow} + a_2 \frac{1}{\sqrt 2}\ket{\downarrow, 0} = y\ket{1+ \downarrow} + x\ket{1- \downarrow}\\
-	c_{1 \uparrow}\ket{GS} = a_1 \frac{1}{\sqrt 2}\ket{\downarrow, 0} + a_2 \frac{1}{\sqrt 2}\ket{0, \downarrow} = y\ket{1+ \downarrow} - x\ket{1- \downarrow}\\
-\end{aligned}\end{equation}
-
-\section{Matrix elements of $G^{-1}$ between single-particle momentum excitations, for the Hubbard dimer}
-\begin{equation}\begin{aligned}
-	G^{-1} \equiv \omega + E_\text{GS} - H_D
-\end{aligned}\end{equation}
-The particle excitation momentum space kets are $\ket{k_0} = \frac{1}{\sqrt 2}\left(\ket{0} + \ket{1}\right) ,\ket{k_\pi} = \frac{1}{\sqrt 2}\left(\ket{0} - \ket{1}\right)$. Therefore,
-\begin{equation}\begin{aligned}
-	\left(G^{-1}\right)_{k_0 k_0} &= \frac{1}{2}\left(\bra{0} + \bra{1}\right)\left(\omega + E_\text{GS} - H_D\right)\left(\ket{0} + \ket{1}\right)\\
-				      &= \frac{1}{2}\left(2x\bra{+}\right)\left(\omega + E_\text{GS} - H_D\right)\left(2x\ket{+}\right)\\
-				      &= 2x^2\left(\omega + E_\text{GS} - t\right)\\
-\end{aligned}\end{equation}
-At the final step, we used $\braket{+,+} = 1$ and $\braket{+|H_D|+} = t$.
-
-\section{Topological interpretation of the Wilson ratio}
-From the Friedel sum rule\cite{langer1961friedel}, we can relate the phase shift \(\delta(0)\) due to scattering (at the Fermi surface) off a local impurity to the number of electrons bound in the potential well produced by that impurity:
-\begin{equation}\begin{aligned}
-\widetilde N = \frac{1}{2\pi i}\text{Tr }\ln S(0) = \int_\Gamma dz\partial_z \frac{1}{2\pi i}\text{Tr }\ln S(0)
-\end{aligned}\end{equation}
-From the optical theorem, we can write
-\begin{equation}\begin{aligned}
-	S = 1 + TG_0 = \frac{G}{G_0} && \left[G = G_0 + G_0 T G_0\right]
-\end{aligned}\end{equation}
-This allows us to write \cite{anirbanurg1}
-\begin{equation}\begin{aligned}
-\widetilde N = \int_\Gamma dz\partial_z \frac{1}{2\pi i}\text{Tr }\ln \frac{G}{G_0}
-\end{aligned}\end{equation}
-Since \(\text{Tr }\ln \hat O = \sum_\lambda \ln O_\lambda = \ln \prod_\lambda O_\lambda = \ln \text{Det} \hat O\), we get
-\begin{equation}\begin{aligned}
-\widetilde N &= \int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln \text{Det } \frac{G}{G_0}\\
-      &= -\int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln \frac{\text{Det } G_0}{\text{Det } G}\\
-      &\equiv -\int_\Gamma dz\partial_z \frac{1}{2\pi i}\ln D\\
-      &= -\int_{\Gamma(D)}\frac{dD}{D}
-\end{aligned}\end{equation}
-From the work of Seki and Yunoki \cite{seki2017topological}, we know that this quantity is essentially the winding number of the curve \(\Gamma(D)\) in the complex plane spanned by the real and imaginary parts of \(D\), and is equal to the change in Luttinger's volume \(V_L\) at \(T=0\).
-\begin{equation}\begin{aligned}
-\widetilde N &= -\int_{\Gamma(D)}\frac{dD}{D} = -\Delta V_L
-\end{aligned}\end{equation}
-The incoming electrons can have \(\sigma = \uparrow,\downarrow\).
-Since the impurity singlet ground state is rotationally invariant, we have \(\delta_\uparrow = \delta_\downarrow = \delta(0)\).
-\begin{equation}\begin{aligned}
-\widetilde N &= \frac{1}{\pi}\sum_\sigma\delta_\sigma(0)\\
-\implies \delta(0) &= \frac{\pi}{2}\widetilde N = -\frac{\pi}{2}\Delta V_L
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-\label{wilson_luttinger}
-R &= 1 + \sin^2 \left(\frac{\pi}{2}\widetilde N\right)\\
-  &= 1 + \sin^2 \left(\frac{\pi}{2}\Delta V_L\right)
-\end{aligned}\end{equation}
-We note that this connection between \(R\) and \(\Delta V_L\) has not been obtained in the existing literature thus far.
-In the unitary limit, \(\delta(0) = \frac{\pi}{2}\), giving \(\Delta V_L = -1 = -\tilde N\) \cite{martin1982fermi} (i.e., one electronic state from the impurity has been absorbed into the Luttinger volume of the conduction bath), such that \(R = 2\) in this limit.
-In this way, we see that a change in the topological quantum number \(\tilde N\) causes the well known renormalisation of the Wilson ratio R from its non-interacting value \((1)\) to the value \((2)\) obtained for the local Fermi liquid \cite{nozieres1974fermi}.
-
-\section{Properties of the Bloch states}
-
-\subsection{Translation invariance}
-It is easy to verify that \(\Psi_{\vec k}\left(\left\{ {\bf r}_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \({\bf r}\):
-\begin{equation}\begin{aligned}
-	\Psi_{\vec k}\left(\left\{{\bf r}_k + {\bf r}\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i,{\bf a}} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left({\bf r}_i - {\bf r}, {\bf a}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_j, {\bf a}} e^{i \vec{k}\cdot\left(\vec{R}_j + {\bf r}\right)} \psi_\text{aux}\left({\bf r}_j, {\bf a}\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ {\bf r}_k \right\} \right)
-\end{aligned}\end{equation}
-In the last equation, we transformed \({\bf r}_i \to {\bf r}_j = {\bf r}_i - {\bf r}\).
-Note that the argument \({\bf a}\) does not change under a translation of the system, because that vector always represents the difference between the impurity lattice position and its nearest neighbours, irrespective of the absolute position of the impurity.
-
-The wavefunction can be even brought into the familiar Bloch function form:
-\begin{equation}\begin{aligned}
-	\Psi^n_{\vec k}\left(\left\{{\bf r}_k\right\}\right) = \sum_{{\bf r}_i, {\bf a}} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} \mathcal{Z} N} \psi_\text{aux}\left(\left\{ {\bf r}_d - {\bf r}_i, {\bf r_0} - {\bf r}_i - {\bf a} \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i, {\bf a}} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k{\bf r}_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ {\bf r}_d - {\bf r}_i, {\bf r_0} - {\bf r}_i - {\bf a} \right\} \right) \\
-	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{{\bf r}_k\right\}\right)
-\end{aligned}\end{equation}
-where \({\bf r}_\text{COM} = \frac{1}{N}\sum_k {\bf r}_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{{\bf r}_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k{\bf r}_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{{\bf r}_k - {\bf r}_i\right\}\right)\) is the translation symmetric function.
-This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
-
-\subsection{Orthonormality}
-It is straightforward to show that these states form an orthonormal basis. We start by writing down the inner product of two distinct such states:
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
-	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r}_j, {\bf a}^\prime \right) | \psi_\text{aux}\left( {\bf r}_i, {\bf a} \right)} \\
-	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) T^\dagger\left( {\bf r_0} - {\bf r}_j \right) T\left( {\bf r_0} - {\bf r}_i \right) | \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
-\end{aligned}\end{equation}
-At this point, we insert a complete basis of momentum eigenkets \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators:
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) T\left( {\bf r}_j - {\bf r}_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
-						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) e^{i \vec q \cdot \left( {\bf r}_j - {\bf r}_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)} \\
-						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2} \delta_{\vec k, \vec k^\prime}\sum_{{\bf a}, {\bf a}^\prime}\braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
-\end{aligned}\end{equation}
-At the last step, we used the summation form of the Kronecker delta function: \(\sum_{{\bf r}_i}e^{i {\bf r}_i \left( \vec k - \vec q \right) }\sum_{{\bf r}_j}e^{i {\bf r}_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\).
-The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \({\bf a}, {\bf a}^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\ket{\vec k}}\):
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2 } \delta_{\vec k, \vec k^\prime}\sum_{{\bf a},{\bf a}^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
-\end{aligned}\end{equation}
-This concludes the proof of orthonormality.
-
-\subsection{Eigenstates}
-To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
-\begin{equation}\begin{aligned}
-	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r}_j, {\bf a}^\prime\right)} H_\text{aux}\left({\bf r}_k\right) \ket{\psi_\text{aux}\left({\bf r}_i, {\bf a}\right)}\\
-	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)} T^\dagger_{{\bf r_0} - {\bf r}_j} T_{{\bf r_0} - {\bf r}_k} H_\text{aux}\left({\bf r_0}\right) T^\dagger_{{\bf r_0} - {\bf r}_k} T_{{\bf r_0} - {\bf r}_i} \ket{\psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
-	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)} T^\dagger_{{\bf r}_k - {\bf r}_j} H_\text{aux}\left({\bf r_0}\right) T_{{\bf r}_k - {\bf r}_i} \ket{\psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}
-\end{aligned}\end{equation}
-To resolve the translation operators, we will now insert the momentum eigenstates \(\ket{\vec k}\) of the full model: \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) in between the operators.
-\begin{equation}\begin{aligned}
-	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, \atop{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{{\bf r}_k - {\bf r}_j} H_\text{aux}\left({\bf r_0}\right) T_{{\bf r}_k - {\bf r}_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
-								   &= \sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, \atop{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left({\bf r}_k - {\bf r}_j\right) } e^{i \vec q \cdot \left({\bf r}_k - {\bf r}_i\right)} \braket{\vec q^\prime | H_\text{aux}\left({\bf r_0}\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
-								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2}\sum_{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left({\bf r_0}\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
-								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2}\delta_{kk^\prime}\sum_{{\bf a}, {\bf a}^\prime} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
-								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k} \underbrace{\sum_{{\bf a}, {\bf a}^\prime} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
-	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k}
-\end{aligned}\end{equation}
-The momentum eigenket \(\ket{\vec k}\) can be expressed as a sum over position eigenkets at varying distances from \({\bf r_0}\).
-This form allows a systematic method of improving the energy eigenvalue estimate, because the interacting in the impurity model is extremely localised, so the overlap between two auxiliary models decreases rapidly with distance.
-The majority of the contribution will come from the state at \({\bf r_0}\), and improvements are then made by considering auxiliary models at further distances.
 \end{widetext}

### 2024-03-22 TilingProjectDraft/tilingProject.tex
charge correlations

@@
 \begin{equation}\begin{aligned}
-	&\tilde{\mathcal{C}}_{\left\{ \sigma_i \right\} }({\bf r}_3, {\bf r}_2, {\bf r}_1) \\
+	&\tilde{G}^{(2)}_{\left\{ \sigma_i \right\} }({\bf r}_3, {\bf r}_2, {\bf r}_1) \\
 	&= \braket{c^\dagger_{\sigma_4}\left({\bf r}_c + {\bf r}_3\right)c_{\sigma_3}^\dagger\left({\bf r}_c + {\bf r}_2\right)c_{\sigma_2}\left({\bf r}_c + {\bf r}_1\right)c_{\sigma_1}\left({\bf r}_c\right)}~,
@@
 \begin{equation}\begin{aligned}
-	\tilde{\mathcal{C}}_{\left\{ \sigma_i \right\} }&({\bf r}_3, {\bf r}_2, {\bf r}_1) \\
+	\tilde{G}^{(2)}_{\left\{ \sigma_i \right\} }&({\bf r}_3, {\bf r}_2, {\bf r}_1) \\
 	=& \langle\psi_\text{gs}({\bf r}_c) | c^\dagger_{\sigma_4}\left({\bf r}_c + {\bf r}_3\right)c_{\sigma_3}^\dagger\left({\bf r}_c + {\bf r}_2\right)c_{\sigma_2}\left({\bf r}_c + {\bf r}_1\right)\\
@@
 
-One can also look at \(k-\)space correlations, of the spin or charge kind. The spin-spin correlations are of the form
-\begin{equation}\begin{aligned}
-	&\tilde{\mathcal{C}}_{\sigma_1,\sigma_2}({\bf K}_1, {\bf K}_2) \\
-	&= \braket{c^\dagger_{\bar\sigma_1}\left({\bf K}_1\right)c_{\bar\sigma_2}^\dagger\left({\bf K}_2\right)c_{\sigma_2}\left({\bf K}_2\right)c_{\sigma_1}\left({\bf K}_1\right)}~.
-\end{aligned}\end{equation}
-We frame this in terms of the auxiliary model by (i) making the substitution again for the ground states, and (ii) by Fourier transforming the creation operators to real space and retaining just the impurity site operator:
-\begin{equation}\begin{aligned}
-	&\tilde{\mathcal{C}}_{\sigma_1,\sigma_2}({\bf K}_1, {\bf K}_2) \\
-	&= \langle\psi_\text{gs}({\bf r}_c) | c^\dagger_{\bar\sigma_1}\left({\bf r}_c\right)c_{\bar\sigma_2}^\dagger\left({\bf r}_c\right)c_{\sigma_2}\left({\bf K}_2\right)c_{\sigma_1}\left({\bf K}_1\right) | \psi_\text{gs}({\bf r}_c)\rangle~.
-\end{aligned}\end{equation}
-Of course, one can also Fourier transform the other operators, so one can average over both possibilities to symmetrise the expression:
-\begin{equation}\begin{aligned}
-	&\tilde{\mathcal{C}}_{\sigma_1,\sigma_2}({\bf K}_1, {\bf K}_2) \\
-	&= \frac{1}{2}\langle\psi_\text{gs}({\bf r}_c) | \left[c^\dagger_{\bar\sigma_1}\left({\bf r}_c\right)c_{\bar\sigma_2}^\dagger\left({\bf r}_c\right)c_{\sigma_2}\left({\bf K}_2\right)c_{\sigma_1}\left({\bf K}_1\right) \right.\\
-	&\left.+ c^\dagger_{\bar\sigma_1}\left({\bf K}_1\right)c_{\bar\sigma_2}^\dagger\left({\bf K}_2\right)c_{\sigma_2}\left({\bf r}_c\right)c_{\sigma_1}\left({\bf r}_c\right) \right] | \psi_\text{gs}({\bf r}_c)\rangle~.
+One can also look at \(k-\)space correlations, of the spin or charge kind. The spin-flip correlations are of the form
+\begin{equation}\begin{aligned}
+	&\tilde{\mathcal{S}}_\text{flip}({\bf K}_1, {\bf K}_2) \\
+	&= \frac{1}{2}\sum_{\sigma=\pm 1}\braket{c^\dagger_{\bar\sigma}\left({\bf K}_1\right)c_{\sigma}^\dagger\left({\bf K}_2\right)c_{\bar\sigma}\left({\bf K}_2\right)c_{\sigma}\left({\bf K}_1\right)}~.
+\end{aligned}\end{equation}
+We frame this in terms of the auxiliary model by (i) making the substitution again for the ground states, and (ii) by Fourier transforming the operators \(c^\dagger_{\bar\sigma}\left({\bf K}_1\right)\) and \(c_{\bar\sigma}\left({\bf K}_2\right)\) to real space and retaining just the impurity site operator:
+\begin{equation}\begin{aligned}
+	&\tilde{\mathcal{S}}_\text{flip}({\bf K}_1, {\bf K}_2) \\
+	&= \frac{1}{2}\sum_{\sigma=\pm 1}\langle\psi_\text{gs}({\bf r}_c) | c^\dagger_{\bar\sigma}\left({\bf r}_c\right)c_{\sigma}^\dagger\left({\bf K}_2\right)c_{\bar\sigma}\left({\bf r}_c\right)c_{\sigma}\left({\bf K}_1\right) | \psi_\text{gs}({\bf r}_c)\rangle~.
+\end{aligned}\end{equation}
+Of course, one can also Fourier transform the other operators (with spin \(\sigma\)), so one can average over both possibilities to symmetrise the expression:
+\begin{equation}\begin{aligned}
+	&\tilde{\mathcal{S}}_\text{flip}({\bf K}_1, {\bf K}_2) \\
+	&= \frac{1}{4}\sum_{\sigma=\pm 1}\langle\psi_\text{gs}({\bf r}_c) | \left[c^\dagger_{\bar\sigma}\left({\bf r}_c\right)c_{\sigma}^\dagger\left({\bf K}_2\right)c_{\bar\sigma}\left({\bf r}_c\right)c_{\sigma}\left({\bf K}_1\right) \right.\\
+	& \quad \left.
++~ c^\dagger_{\bar\sigma}\left({\bf K}_1\right)c_{\sigma}^\dagger\left({\bf r}_c\right)c_{\bar\sigma}\left({\bf K}_2\right)c_{\sigma}\left({\bf r}_c\right) \right] | \psi_\text{gs}({\bf r}_c)\rangle~.
+\end{aligned}\end{equation}
+
+In a similar fashion, one can probe nature of charge-fluctuation driven correlations using
+\begin{equation}\begin{aligned}
+	&\tilde{\mathcal{C}}_\text{flip}({\bf K}_1, {\bf K}_2) \\
+	&= \frac{1}{2}\braket{\left[c^\dagger_{\uparrow}\left({\bf K}_2\right)c_{\downarrow}^\dagger\left({\bf K}_2\right)c_{\downarrow}\left({\bf K}_1\right)c_{\uparrow}\left({\bf K}_1\right) + \text{h.c.}\right] }~.
 \end{aligned}\end{equation}

### 2024-03-23 TilingProjectDraft/tilingProject.tex
finished correlations, entanglement and pwave tiling

--- 2024-03-21 TilingProjectDraft/tilingProject.tex
@@
 \subsection{Tiling towards a Hubbard-Heisenberg model with an s-wave impurity model}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.4\textwidth]{pWaveEsiam.pdf}
+	\caption{Caption.}
+	\label{pWaveEsiam}
+\end{figure}
 In this subsection, we provide an explicit example of constructing a lattice model.
-We will consider a slightly more generalised version of the extended SIAM described in the previous section, where the impurity site couples to the conduction bath purely through the s-wave channel.
+We will consider a slightly more generalised version of the extended SIAM described in the previous section, where the impurity site coupled to the conduction bath purely through the s-wave channel.
 We will show that that model leads to a form of a Hubbard-Heisenberg model upon restoring translation invariance via repeated translation operations.
-The generalisation involve allowing an arbitrary filling on the impurity site and in the conduction bath, through two additional parameter: (i) a particle-hole assymetry parameter \(\eta\) for the impurity site, and (ii) a chemical potential for the conduction bath.
+The generalisation involve allowing an arbitrary filling on the impurity site and in the conduction bath, through two additional parameter: (i) a particle-hole assymetry parameter \(\eta\) for the impurity site, (ii) a chemical potential for the conduction bath, and (iii) embedding the impurity into the lattice of the 2D conduction bath.
+This modified impurity model is shown in Fig.~\ref{pWaveEsiam}.
 The first term modifies the impurity Hamiltonian \(\mathcal{H}_\text{imp}\) into
-\begin{equation}\begin{aligned}
+\begin{equation}\begin{aligned}\label{onsiteHamiltonian}
 	\mathcal{H}_\text{imp} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 - \eta\sum_\sigma \hat n_{{\bf r}_d\sigma}~.
@@
 where we have placed the impurity site at the position \({\bf r}_d\). The second term modifies the conduction bath Hamiltonian \(\mathcal{H}_\text{cbath}\):
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
-	- \frac{1}{2}U_b\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
+\begin{equation}\begin{aligned}\label{bathHamiltonian}
+	\mathcal{H}_\text{cbath} &= -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
+							 &- \frac{1}{2 \mathcal{Z}}U_b\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
 \end{aligned}\end{equation}
@@
 In this notation, the interaction Hamiltonian can be written as
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{imp-cbath} &= \sum_{\sigma,\sigma^\prime}\frac{1}{ Z}J {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \\
-				     &-  \sum_{\sigma} V \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)
+\begin{equation}\begin{aligned}\label{interactionHamiltonian}
+	\mathcal{H}_\text{imp-cbath} &= \frac{J}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}\sum_{{\bf z}\in\text{NN}({\bf r}_d)} {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \\
+								 & - \frac{V}{\sqrt{\mathcal{Z}}}\sum_{\sigma} \sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{tiled} = \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\left[\mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} \right.\\
+	\mathcal{H}_\text{tiled} = \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} \right.\\
 \left.+ \mathcal{H}_\text{imp-cbath}\right]T({\bf r} - {\bf r}_d)~.
 \end{aligned}\end{equation}
+Note that in comparison to eq.~\ref{tilingPrescription}, we have dropped the sum over the zeroth sites, because our impurity model Hamiltonian (defined using eqs.~\ref{onsiteHamiltonian} through \ref{interactionHamiltonian}) already contains a sum over these zeroth sites.
+
 We consider the effect of the translation operations on each part of the Hamiltonian. We first have
 \begin{equation}\begin{aligned}
-	&\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d) \\
-	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-\frac{1}{\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \right.\\
+	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d) \\
+	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \right.\\
 	 &\left.- \frac{U_b}{2\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}\right]T({\bf r} - {\bf r}_d) \\
-	=& -\frac{1}{\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
+	=& -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
 	 &- \frac{U_b}{2\mathcal{Z}}\sum_{\bf r}\sum_{{\bf z}\in\text{NN}\left({\bf r}\right)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i}\sum_{{\bf r} \neq {\bf r}_i}\hat n_{{\bf r}_i,\sigma}\\
-	=& -\frac{1}{\mathcal{Z}}(N-2)t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
+	=& -\frac{1}{\sqrt\mathcal{Z}}(N-2)t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
 	 &- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
@@
 \begin{equation}\begin{aligned}
-	&\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf r}_0\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp}T({\bf r} - {\bf r}_d) \\
+	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp}T({\bf r} - {\bf r}_d) \\
 	=& -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}~.
@@
 \begin{equation}\begin{aligned}
-	&\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}T({\bf r} - {\bf r}_d)\\
-	&=\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\left[\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
-				     &-  \left.\sum_{\sigma} V \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]T({\bf r} - {\bf r}_d)\\
-	&=\frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r})}\left[\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
-				     &-  \left.\sum_{\sigma} V\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]\\
-					 &=\frac{2}{\mathcal{Z}}\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]\\
+	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp-cbath}T({\bf r} - {\bf r}_d)\\
+	&=\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
+				     &-  \left. \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma} V \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]T({\bf r} - {\bf r}_d)\\
+	&=\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r})}\left[\frac{1}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
+				     &-  \frac{1}{\sqrt\mathcal{Z}}\left.\sum_{\sigma} V\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]\\
+					 &=\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]\\
 \end{aligned}\end{equation}
@@
 	&\mathcal{H}_\text{tiled} \\
-	&= -\frac{N-2}{\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>,\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+	&= -\frac{N-2}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>,\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
 	&- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}\\
-	& + \frac{2}{\mathcal{Z}}\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]
-\end{aligned}\end{equation}
-While constructing the tiled Hamiltonian, we have added extra copies of the non-interacting Hamiltonian \(\mathcal{H}_\text{cbath-nint} = -\frac{1}{\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\) for the conduction bath (this results in the factors of \(N-2\) and \(N-1\) in front of the first and third terms).
+	& + \sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]
+\end{aligned}\end{equation}
+While constructing the tiled Hamiltonian, we have added extra copies of the non-interacting Hamiltonian \(\mathcal{H}_\text{cbath-nint} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\) for the conduction bath (this results in the factors of \(N-2\) and \(N-1\) in front of the first and third terms).
 Upon removing these repeated terms, the tiled Hamiltonian becomes
@@
 	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}\\
-							 &= -\frac{1}{\mathcal{Z}}(t + 2V)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
+							 &= -\frac{1}{\sqrt\mathcal{Z}}(t + 2V)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
 							 &- \frac{1}{2}\left(U + U_b\right)\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \left(\eta + 2\mu\right) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} \\
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{HH} &= -\frac{1}{\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+	\mathcal{H}_\text{HH} &= -\frac{1}{\sqrt\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
 						  &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
@@
 Properties of the ground state can be probed using static correlation functions that are expectation values of two-particle excitation operators.
-A general correlation function in real space is of the form
-\begin{equation}\begin{aligned}
-	&\tilde{\mathcal{C}}_{\left\{ \sigma_i \right\} }({\bf r}_3, {\bf r}_2, {\bf r}_1) \\
-	&= \braket{c^\dagger_{\sigma_4}\left({\bf r}_c + {\bf r}_3\right)c_{\sigma_3}^\dagger\left({\bf r}_c + {\bf r}_2\right)c_{\sigma_2}\left({\bf r}_c + {\bf r}_1\right)c_{\sigma_1}\left({\bf r}_c\right)}~,
-\end{aligned}\end{equation}
-where the expectation value is in the ground state \(\ket{\Psi_\text{gs}}\). We replace the full ground state with the ground state of the auxiliary model at \({\bf r}_c\):
-\begin{equation}\begin{aligned}
-	\tilde{\mathcal{C}}_{\left\{ \sigma_i \right\} }&({\bf r}_3, {\bf r}_2, {\bf r}_1) \\
-	=& \langle\psi_\text{gs}({\bf r}_c) | c^\dagger_{\sigma_4}\left({\bf r}_c + {\bf r}_3\right)c_{\sigma_3}^\dagger\left({\bf r}_c + {\bf r}_2\right)c_{\sigma_2}\left({\bf r}_c + {\bf r}_1\right)\\
-	&c_{\sigma_1}\left({\bf r}_c\right) | \psi_\text{gs}({\bf r}_c)\rangle~.
-\end{aligned}\end{equation}
-
-One can also look at \(k-\)space correlations, of the spin or charge kind. The spin-spin correlations are of the form
-\begin{equation}\begin{aligned}
-	&\tilde{\mathcal{C}}_{\sigma_1,\sigma_2}({\bf K}_1, {\bf K}_2) \\
-	&= \braket{c^\dagger_{\bar\sigma_1}\left({\bf K}_1\right)c_{\bar\sigma_2}^\dagger\left({\bf K}_2\right)c_{\sigma_2}\left({\bf K}_2\right)c_{\sigma_1}\left({\bf K}_1\right)}~.
-\end{aligned}\end{equation}
-We frame this in terms of the auxiliary model by (i) making the substitution again for the ground states, and (ii) by Fourier transforming the creation operators to real space and retaining just the impurity site operator:
-\begin{equation}\begin{aligned}
-	&\tilde{\mathcal{C}}_{\sigma_1,\sigma_2}({\bf K}_1, {\bf K}_2) \\
-	&= \langle\psi_\text{gs}({\bf r}_c) | c^\dagger_{\bar\sigma_1}\left({\bf r}_c\right)c_{\bar\sigma_2}^\dagger\left({\bf r}_c\right)c_{\sigma_2}\left({\bf K}_2\right)c_{\sigma_1}\left({\bf K}_1\right) | \psi_\text{gs}({\bf r}_c)\rangle~.
-\end{aligned}\end{equation}
-Of course, one can also Fourier transform the other operators, so one can average over both possibilities to symmetrise the expression:
-\begin{equation}\begin{aligned}
-	&\tilde{\mathcal{C}}_{\sigma_1,\sigma_2}({\bf K}_1, {\bf K}_2) \\
-	&= \frac{1}{2}\langle\psi_\text{gs}({\bf r}_c) | \left[c^\dagger_{\bar\sigma_1}\left({\bf r}_c\right)c_{\bar\sigma_2}^\dagger\left({\bf r}_c\right)c_{\sigma_2}\left({\bf K}_2\right)c_{\sigma_1}\left({\bf K}_1\right) \right.\\
-	&\left.+ c^\dagger_{\bar\sigma_1}\left({\bf K}_1\right)c_{\bar\sigma_2}^\dagger\left({\bf K}_2\right)c_{\sigma_2}\left({\bf r}_c\right)c_{\sigma_1}\left({\bf r}_c\right) \right] | \psi_\text{gs}({\bf r}_c)\rangle~.
+We will consider spin and charge correlations, in real and momentum space.
+
+We first consider spin-spin correlations in real space, defined as
+\begin{equation}\begin{aligned}
+	\tilde{S}_\text{flip}({\bf r}) = \frac{1}{2}\braket{S^+\left({\bf r}_c + {\bf r}\right)S^-\left({\bf r}_c\right) + \text{h.c.}}~,
+\end{aligned}\end{equation}
+where \(S^-(\nu) = c^\dagger(\nu,\downarrow)c(\nu, \uparrow)\) and \(S^+ = \left( S^- \right)^\dagger \) are the spin-flip operators, and the expectation value is in the ground state \(\ket{\Psi_\text{gs}}\).
+We replace the full ground state with the ground state of the auxiliary model at \({\bf r}_c\):
+\begin{equation}\begin{aligned}
+	\tilde{S}_\text{flip}({\bf r}) = \frac{1}{2}\braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf d} + {\bf r}\right)S^-\left({\bf d}\right) + \text{h.c.} | \psi_\text{gs}({\bf r}_c)}~,
+\end{aligned}\end{equation}
+where we have interpereted the site at \({\bf r}_c\) as the impurity site \({\bf d}\) for the auxiliary model in question.
+The final expression therefore involves the spin-flip correlation function between the impurity site and a site in the bath, within a single auxiliary model.
+
+Charge correlations involve flips of the charge isospin states (instead of the spin states), and are defined as
+\begin{equation}\begin{aligned}
+	\tilde{C}_\text{flip}({\bf r}) = \frac{1}{2}\braket{C^+\left({\bf r}_c + {\bf r}\right)C^-\left({\bf r}_c\right) + \text{h.c.}}~,
+\end{aligned}\end{equation}
+where \(C^-(\nu) = c(\nu,\downarrow)c(\nu, \uparrow)\) and \(C^+ = \left( C^- \right)^\dagger \). Making identical substitutions here gives
+\begin{equation}\begin{aligned}
+	\tilde{C}_\text{flip}({\bf r}) = \frac{1}{2}\braket{\psi_\text{gs}({\bf r}_c) | C^+\left({\bf d} + {\bf r}\right)C^-\left({\bf d}\right) + \text{h.c.} | \psi_\text{gs}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+
+One can also look at \(k-\)space correlations, of the spin or charge kind:
+\begin{equation}\begin{aligned}
+	\tilde{S}_\text{flip}({\bf K}_1, {\bf K}_2) &= \frac{1}{2}\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right) + \text{h.c.}}~,\\
+	\tilde{C}_\text{flip}({\bf K}_1, {\bf K}_2) &= \frac{1}{2}\braket{C^+\left({\bf K}_1\right)C^-\left({\bf K}_2\right) + \text{h.c.}}~.
+\end{aligned}\end{equation}
+We again consider the spin-flip correlation first. In order to introduce the impurity site, we rewrite the expectation values as
+\begin{equation}\begin{aligned}
+	&\tilde{S}_\text{flip}({\bf K}_1, {\bf K}_2) \\
+	&= \frac{1}{2}\left[\sqrt{\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)}\braket{S^-\left({\bf K}_2\right)S^+\left({\bf K}_1\right)}} + \text{h.c.}\right] ~.
+\end{aligned}\end{equation}
+We frame this in terms of the auxiliary model by (i) making the substitution again for the ground states, and (ii) by fourier transforming the first operator within each expectation value to real space and retaining just the impurity site operator:
+\begin{equation}\begin{aligned}
+	&\tilde{S}_\text{flip}({\bf K}_1, {\bf K}_2) \\
+	&= \frac{1}{2}\left[\sqrt{\braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf d}\right)S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}}\right. \\
+	&\left.\times\sqrt{\braket{\psi_\text{gs}{({\bf r}_c)} | S^-\left({\bf d}\right)S^+\left({\bf K}_1\right) | \psi_\text{gs}{({\bf r}_c)}}} + \text{h.c.}\right] ~.
+\end{aligned}\end{equation}
+Performing similar manipulations with the charge isospin-flip correlation gives
+\begin{equation}\begin{aligned}
+	&\tilde{C}_\text{flip}({\bf K}_1, {\bf K}_2) \\
+	&= \frac{1}{2}\left[\sqrt{\braket{\psi_\text{gs}({\bf r}_c) | C^+\left({\bf d}\right)C^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}}\right. \\
+	&\left.\times\sqrt{\braket{\psi_\text{gs}{({\bf r}_c)} | C^-\left({\bf d}\right)C^+\left({\bf K}_1\right) | \psi_\text{gs}{({\bf r}_c)}}} + \text{h.c.}\right] ~.
 \end{aligned}\end{equation}
@@
 \section{Entanglement measures}
-\subsection{Entanglement entropy}
+
 Given the \(T=0\) density matrix \(\tilde\rho_\text{gs} = \ket{\Psi}_\text{gs}\bra{{\Psi}_\text{gs}}\) of the lattice model and a fermionic two-level subspace \(\nu\), the reduced density matrix for the {\it complement} subspace of \(\nu\) can be obtained by tracing over the configurations of that subspace
@@
 
+We might also be interested in entanglement entropy of subsystems with multiple sites.
+The reduced density matrix for the composite subsystem of the sites \({\bf r}_c\) and \({\bf r}_c + {\bf r}\) is obtained by tracing out the site \({\bf r}_c + {\bf r}\) from \(\overline\rho_{{\bf r}_c,\sigma}\).
+That then gives
+\begin{equation}\begin{aligned}
+	\overline\rho_{({\bf r}_c, {\bf r}_c + {\bf r}),\sigma} = c^\dagger_{{\bf r}_c + {\bf r},\sigma} \overline\rho_{{\bf r}_c,\sigma} c_{{\bf r}_c + {\bf r},\sigma} + n_{{\bf r}_c + {\bf r},\sigma} \overline\rho_{{\bf r}_c,\sigma} n_{{\bf r}_c + {\bf r},\sigma}~.
+\end{aligned}\end{equation}
+
 We now come to the \(k-\)space entanglement entropy, defined by \(\nu = ({\bf K},\sigma)\) and the reduced density matrix
@@
 \end{aligned}\end{equation}
-We again replace the states with the uniform part, while we expand the operators on the right of the density matrix (\(c\) and \(n\)) in a Fourier series in order to extract an impurity site operator:
-\begin{equation}\begin{aligned}
-	\overline\rho_{{\bf K},\sigma} = c^\dagger_{{\bf K},\sigma} \rho_\text{gs}({\bf r}_c) c_{{\bf r}_c,\sigma} + n_{{\bf K},\sigma} \rho_\text{gs}({\bf r}_c) n_{{\bf r}_c,\sigma}~.
+We again replace the states with the uniform part, while we expand the operators on one side of the density matrix in a Fourier series in order to extract an impurity site operator:
+\begin{equation}\begin{aligned}
+	\overline\rho_{{\bf K},\sigma} &= \frac{1}{2}\left[c^\dagger_{{\bf K},\sigma} \rho_\text{gs}({\bf r}_c) c_{{\bf r}_c,\sigma} + n_{{\bf K},\sigma} \rho_\text{gs}({\bf r}_c) n_{{\bf r}_c,\sigma} \right.\\
+	&+ \left. c^\dagger_{{\bf r}_c,\sigma} \rho_\text{gs}({\bf r}_c) c_{{\bf K},\sigma} + n_{{\bf r}_c,\sigma} \rho_\text{gs}({\bf r}_c) n_{{\bf K},\sigma}\right. ~.
 \end{aligned}\end{equation}
 The eigenvalues of this operator can be used to compute the entanglement entropy of the state \({\bf K}\sigma\).
+Using the same approach as that for the real space case, the reduced density matrix for two \(k-\)states is again obtained by tracing out the second \(k-\)state from this density matrix:
+\begin{equation}\begin{aligned}
+	\overline\rho_{({\bf K}_1, {\bf K}_2),\sigma} &= \frac{1}{2}\left[c^\dagger_{{\bf K}_2,\sigma} \overline\rho_{{\bf K}_1,\sigma} c_{{\bf r}_c,\sigma} + n_{{\bf K}_2,\sigma} \overline\rho_{{\bf K}_1,\sigma} n_{{\bf r}_c,\sigma} \right.\\
+	&+ \left. c^\dagger_{{\bf r}_c,\sigma} \overline\rho_{{\bf K}_1,\sigma} c_{{\bf K}_2,\sigma} + n_{{\bf r}_c,\sigma} \overline\rho_{{\bf K}_1,\sigma} n_{{\bf K}_2,\sigma}\right] ~.
+\end{aligned}\end{equation}
+
+Other measures like mutual information can be obtained by using these elementary measures.
 
@@
 \begin{widetext}
-\section{Static correlation functions}
-This approach also holds for higher-order static correlation functions.
-For example, a general local correlation of the form \(\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0}) | \Psi_\text{gs}}\) corresponding to operators \(\mathcal{O}_1\) and \(\mathcal{O}_2\) can be estimated, using this method, in terms of auxiliary model quantities.
-For that, we first express the correlation at sites \({\bf r_0}\) as well as its nearest neighbours:
-\begin{equation}\begin{aligned}
-	\frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0}) | \Psi_\text{gs}} + \frac{1}{\mathcal{Z}}\sum_{{\bf a} \in \text{NN of }{\bf r_0}}\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0} + {\bf a}) \mathcal{O}_2({\bf r_0} + {\bf a}) | \Psi_\text{gs}}\right]
-\end{aligned}\end{equation}
-This is enabled by the translation symmetry of the problem, and it allows us to involve both the impurity site and the bath zeroth site in the relations.
-By keeping only the uniform part of the ground-state wavefunction, we get
-\begin{equation}\begin{aligned}
-	\label{local_correlation}
-	\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0}) | \Psi_\text{gs}} \simeq& \frac{1}{2\lambda_{\vec k_0}^2}\left[\frac{1}{\mathcal{Z} }\sum_{{\bf a} \in \text{NN of }{\bf r_0}}\braket{\psi_\text{aux}({\bf r_0}, {\bf a}) | \mathcal{O}_1({\bf r_0}, {\bf a}) \mathcal{O}_2({\bf r_0}) | \psi_\text{aux}({\bf r_0})} \right.
-\\
-													   &+ \left.\frac{1}{\mathcal{Z}^2}\sum_{{\bf a} \in \text{NN of }{\bf r_0}}\braket{\psi_\text{aux}({\bf r_0}, {\bf a}) | \mathcal{O}_1({\bf r_0} + {\bf a}) \mathcal{O}_2({\bf r_0} + {\bf a}) | \psi_\text{aux}({\bf r_0}, {\bf a})}\right]\\
-	=& \frac{1}{2\lambda_{\vec k_0}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{Z}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]
-\end{aligned}\end{equation}
-In the above expression, where the arguments \((d)\) and \((z)\) indicate that the corresponding operator acts at the impurity site and the bath zeroth site respectively, and the subscript \(\text{aux}\) indicates that the averaging is carried out in the impurity model.
-
-Similar expressions hold for non-local correlation functions.
-\begin{equation}\begin{aligned}
-	\label{nonlocal_correlation}
-	&\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0} + {\bf a}) | \Psi_\text{gs}} \\
-	=& \frac{1}{4}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0} + {\bf a}) + \mathcal{O}_1({\bf r_0} + {\bf a}) \mathcal{O}_2({\bf r_0} + 2{\bf a}) + \mathcal{O}_1({\bf r_0} - {\bf a}) \mathcal{O}_2({\bf r_0}) + \mathcal{O}_1({\bf r_0} - 2{\bf a}) \mathcal{O}_2({\bf r_0} - {\bf a}) | \Psi_\text{gs}}\right]\\
-	\simeq& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{Z}}\left[\braket{\psi_\text{aux}({\bf r_0}, {\bf a}) | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0} + {\bf a}) + \mathcal{O}_1({\bf r_0} + {\bf a}) \mathcal{O}_2({\bf r_0} + 2{\bf a}) | \psi_\text{aux}({\bf r_0}, {\bf a})} \right.
-\\
-	      &\left.\braket{\psi_\text{aux}({\bf r_0}, -{\bf a}) | \mathcal{O}_1({\bf r_0} - {\bf a}) \mathcal{O}_2({\bf r_0}) + \mathcal{O}_1({\bf r_0} - 2{\bf a}) \mathcal{O}_2({\bf r_0} - {\bf a}) | \psi_\text{aux}({\bf r_0}, -{\bf a})}\right]\\
-	=& \frac{1}{4\lambda_{\vec k_0}^2 \mathcal{Z}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right]
-\end{aligned}\end{equation}
-In the first equation, the first two terms were introduced to incorporate effects arising from the bath zeroth and first sites (guided by the dynamics of the transition in the underlying extended Anderson model), while the last two terms were introduced to symmetrise the effects of choosing \({\bf r_0}\) as \(d\) and \({\bf r_0} + {\bf a}\) as \(z\), and not other way round.
-The argument \((1)\) in the operators indicate that they act at the first site of the bath (beyond the bath zeroth site).
-
-The next-nearest correlation function is relatively simpler, because only those terms contribute that involve both the impurity as well as the first site.
-If \({\bf a}^\prime\) denotes the relative vector between a given site and one of its next-nearest neighbours, we can write
-\begin{equation}\begin{aligned}
-	\label{nnn_correlation}
-	\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0} + {\bf a}^\prime) | \Psi_\text{gs}} =& \frac{1}{2}\left[\braket{\Psi_\text{gs} | \mathcal{O}_1({\bf r_0}) \mathcal{O}_2({\bf r_0} + {\bf a}^\prime) + \mathcal{O}_1({\bf r_0} - {\bf a}^\prime) \mathcal{O}_2({\bf r_0}) | \Psi_\text{gs}}\right]\\
-	=& \frac{1}{2\lambda_{\vec k_0}^2 \mathcal{Z}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
-\end{aligned}\end{equation}
-
-\section{Correlation functions in momentum space}
-Similar to Greens functions, our formalism also allows calculating \(k-\)space correlation functions \(\chi(\vec q)\) from knowledge of local and nearest-neighbour correlations \(\chi_\text{loc}\) and \(\chi_\text{nn}\).
-This is seen by Fourier transforming a generic real-space correlation function \(\chi({\bf r})\) corresponding to the operator \(\mathcal{O}\):
-\begin{equation}\begin{aligned}
-	\chi({\bf r}) = \left<\mathcal{O}_1 ({\bf r} + {\bf r}) \mathcal{O}_2({\bf r})\right> = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot {\bf r}}e^{i \left(\vec k + \vec q\right) \cdot {\bf r}}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right>
-\end{aligned}\end{equation}
-Since the response should not depend on \({\bf r}\) (owing to translation invariance), we have
-\begin{equation}\begin{aligned}
-	\chi({\bf r}) = \frac{1}{N^2}\sum_{\vec k, \vec q} e^{i \vec q \cdot {\bf r}}e^{i \left(\vec k + \vec q\right) \cdot {\bf r}}\delta_{\vec k + \vec q, 0}\left<\mathcal{O}_1 (\vec q) \mathcal{O}_2(\vec k)\right> = \frac{1}{N}\sum_{\vec k} e^{-i \vec k \cdot {\bf r}}\left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right>
-\end{aligned}\end{equation}
-By inverting the Fourier transform, we therefore get
-\begin{equation}\begin{aligned}
-	\chi(\vec k) &\equiv \left<\mathcal{O}_1 (-\vec k) \mathcal{O}_2(\vec k)\right> = \sum_{{\bf r}}e^{i \vec{k}\cdot\vec{r}} \chi({\bf r}) \simeq \chi_\text{loc} + \xi_{\vec k} \chi_\text{nn} + \Xi_{\vec k}\chi_\text{nnn}~,
-\end{aligned}\end{equation}
-where \(\chi_\text{loc},\chi_\text{nn},\chi_\text{nnn}\) are local, nearest-neighbour and next-nearest-neighbour correlation functions, with dispersions \(\xi_{\vec k} = 2\left[\cos(k_x a) + \cos\left(k_y a\right)\right] \) and \(\Xi_{\vec k} = 2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right] \).
-Following eqs.~\ref{local_correlation} through \ref{nnn_correlation}, these can be cast into impurity model correlation functions:
-\begin{equation}\begin{aligned}
-	\chi(\vec k)=& \frac{1}{2\lambda_{\vec k_0}^2}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(d)}_\text{aux} + \frac{1}{\mathcal{Z}}\braket{\mathcal{O}_1(z) \mathcal{O}_2(z)}_\text{aux}\right]\\
-		    &+ \frac{2\left[\cos(k_x a) + \cos\left(k_y a\right)\right]}{4\lambda_{\vec k_0}^2 \mathcal{Z}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(z) + \mathcal{O}_1(z) \mathcal{O}_2(1) + \mathcal{O}_1(z) \mathcal{O}_2(d) + \mathcal{O}_1(1) \mathcal{O}_2(z)}_\text{aux}\right] \\
-		    &+ \frac{2\left[\cos \left(ak_x + ak_y\right) + \cos \left( ak_x - ak_y \right) \right]}{2\lambda_{\vec k_0}^2 \mathcal{Z}}\left[\braket{\mathcal{O}_1(d) \mathcal{O}_2(1) + \mathcal{O}_1(1) \mathcal{O}_2(d)}_\text{aux}\right]
-\end{aligned}\end{equation}
-
-\section{Momentum-space entanglement}
-The density matrix of the full Hamiltonian in ground-state is simply \(\rho_\text{gs} = \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\).
-In order to calculate entanglement measures in and among \(k-\)space states, we begin by obtaining an expression for the von-Neumann entropy of a \(\vec k-\)state, in terms of auxiliary model quantities.
-
-\subsection{\(k-\)space von-Neumann entropy}
-The full ground state \(\ket{\Psi_\text{gs}}\) can be written in the basis of the Fock states of momentum \(\vec k\sigma\):
-\begin{equation}\begin{aligned}
-	\Psi_\text{gs} = \sin\theta_{\vec k\sigma} \ket{n_{\vec k\sigma} = 0}\otimes\ket{\phi_{\vec k\sigma}} + \cos\theta_{\vec k\sigma} \ket{n_{\vec k\sigma} = 1}\otimes\ket{\bar\phi_{\vec k\sigma}}
-\end{aligned}\end{equation}
-where \(\ket{n_{\vec k\sigma}}\) is the state with occupancy \(n_{\vec k\sigma}\) from the Hilbert space of \(\vec k\sigma\).
-\(\ket{\phi_{\vec k\sigma}}\) and \(\ket{\bar\phi_{\vec k\sigma}}\) are the normalised states representing the configuration of the remaining degrees of freedom in the full state \(\Psi_\text{gs}\) when \(\hat n_{k\sigma}\) is 0 and 1 respectively.
-\(\sin \theta_{\vec k}\) and \(\cos\theta_{\vec k\sigma}\) are the probabilities of obtaining \(n_{\vec k\sigma}\) to be 0 and 1 respectively, in the full ground state.
-
-The reduced density matrix for the momentum state \(\vec k\sigma\) is then obtained simply by tracing over the states \(\ket{n_{\vec k\sigma}}\):
-\begin{equation}\begin{aligned}
-	\rho_{\vec k\sigma} = \sum_{n_{\vec k\sigma}=0,1} \braket{n_{\vec k\sigma} | \rho_\text{gs} | n_{\vec k\sigma}} = \sin^2\theta_{\vec k\sigma} \ket{\phi_{\vec k\sigma}}\bra{\phi_{\vec k\sigma}} + \cos^2\theta_{\vec k\sigma} \ket{\bar\phi_{\vec k\sigma}}\bra{\bar\phi_{\vec k\sigma}}\label{red_matrix}
-\end{aligned}\end{equation}
-If the eigenvalues of the operators \(\ket{\phi_{\vec k\sigma}}\bra{\phi_{\vec k\sigma}}\) and \(\ket{\bar\phi_{\vec k\sigma}}\bra{\bar\phi_{\vec k\sigma}}\) are \(\left\{ \lambda_n \right\} \) and \(\left\{ \bar\lambda_n \right\} \) respectively, the von-Neumann entropy is given by
-\begin{equation}\begin{aligned}
-	S_\text{EE}\left(\rho_{\vec k\sigma}\right) = \sum_n \left( \sin^2\theta_{\vec k\sigma}\lambda_n + \cos^2\theta_{\vec k\sigma}\bar\lambda_n \right) 
-\end{aligned}\end{equation}
-
-In order to connect with the auxiliary model, we will need to obtain the reduced density matrix without tracing out any states.
-We will, instead, project on to the appropriate states with the particle number operator \(\hat n_{\vec k\sigma}\) and the hole number operator \(\hat h_{\vec k\sigma} = 1 - \hat n_{\vec k\sigma}\).
-The reduced density matrix can be obtained by applying such projectors:
-\begin{equation}\begin{aligned}
-	\rho_{\vec k\sigma} \equiv \hat n_{\vec k\sigma}\rho_\text{gs} \hat n_{\vec k\sigma} + \hat h_{\vec k\sigma}\rho_\text{gs} \hat h_{\vec k\sigma} = \sin^2\theta_{\vec k\sigma} \ket{0}\bra{0}\otimes\ket{\phi_{\vec k\sigma}}\bra{\phi_{\vec k\sigma}} + \cos^2\theta_{\vec k\sigma} \ket{1}\bra{1}\otimes\ket{\bar\phi_{\vec k\sigma}}\bra{\bar\phi_{\vec k\sigma}}\label{red_matrix_projection}
-\end{aligned}\end{equation}
-where \(\ket{1}\) and \(\ket{0}\) are the \(n_{\vec k\sigma}=1\) and 0 states respectively. In the basis \(\left\{ \ket{0}, \ket{1} \right\} \), the reduced density matrix can be represented as
-\begin{equation}\begin{aligned}
-	\rho_{\vec k\sigma} = \begin{pmatrix}\sin^2\theta_{\vec k\sigma} \ket{\phi_{\vec k\sigma}}\bra{\phi_{\vec k\sigma}} & 0 \\ \\
-	0 & \cos^2\theta_{\vec k\sigma} \ket{\bar\phi_{\vec k\sigma}}\bra{\bar\phi_{\vec k\sigma}}
-	\end{pmatrix} ~,
-\end{aligned}\end{equation}
-such that the eigenvalues of this matrix are the same as those of the operator in eq.~\ref{red_matrix}; the projection method would therefore give the same von-Neumann entropy as that obtained using the partial traces.
-
-We will now Fourier transform the reduced matrix from the definition in eq.~\ref{red_matrix_projection}, and retain terms up to the nearest neighbour, by expanding \(c_{\vec k\sigma}\) as \(c_{{\bf r_0},\sigma} + \xi_{\vec k}c_{{\bf r_0} + {\bf a},\sigma}\), where \({\bf a}\) is the nearest neighbour site to \({\bf r_0}\), and \(\xi_{\vec k}\) has been defined above.
-\begin{equation}\begin{aligned}
-	\hat n_{\vec k\sigma}\ket{\Psi_\text{gs}} \to  \left[ \hat n_{{\bf r_0},\sigma} + \sum_{{\bf a}} \hat n_{{\bf r_0} + {\bf a},\sigma} + \sum_{{\bf a}}\left( e^{i \vec{k}\cdot\vec{a}}c^\dagger_{{\bf r_0},\sigma}c_{{\bf r_0} + {\bf a},\sigma} + \text{h.c.} \right) \right]\ket{\Psi_\text{gs}}
-\end{aligned}\end{equation}
-We also expand the ground state wavefunction: \(\ket{\Psi}_\text{gs} \simeq \ket{\psi_\text{aux}} = \frac{1}{\sqrt \mathcal{Z}}\sum_{{\bf a} \in \text{NN of }{\bf r_0}}\ket{\psi_\text{aux}({\bf r_0},{\bf a})}\), so that we get
-\begin{equation}\begin{aligned}
-	\hat n_{\vec k\sigma}\ket{\Psi_\text{gs}} &= \frac{1}{\sqrt \mathcal{Z}}\left[ \hat n_{{\bf r_0},\sigma} \sum_{{\bf a}}\ket{\psi_\text{aux}({\bf r_0},{\bf a})} + \sum_{{\bf a}} \hat n_{{\bf r_0} + {\bf a},\sigma}\ket{\psi_\text{aux}({\bf r_0},{\bf a})} + \sum_{{\bf a}}\left( e^{i \vec{k}\cdot\vec{a}}c^\dagger_{{\bf r_0},\sigma}c_{{\bf r_0} + {\bf a},\sigma} + \text{h.c.} \right) \ket{\psi_\text{aux}({\bf r_0},{\bf a})}\right]\\
-						  &=\hat n_{d,\sigma} \ket{\psi_\text{aux}} + \hat n_{z,\sigma}\ket{\psi_\text{aux}} + \frac{\xi_{\vec k}}{\sqrt \mathcal{Z}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right) \ket{\psi_\text{aux}}
-\end{aligned}\end{equation}
-By taking the outer product with its hermitian conjugate and then adding the hole counterpart \(\hat h_{\vec k\sigma}\rho_\text{gs} \hat h_{\vec k\sigma}\), we get the reduced density matrix:
-\begin{equation}\begin{aligned}
-	\rho_{\vec k\sigma} \simeq& \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{Z}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_\text{aux} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{Z}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]\\
-				  &+ \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{Z}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right] \rho_\text{aux} \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec k}}{\sqrt \mathcal{Z}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right]\label{density_matrix_kspace}
-\end{aligned}\end{equation}
-The von-Neumann entropy \(S_\text{EE}(\vec k)\) can then be calculated by taking the trace of the operator \(\rho_{\vec k\sigma}\ln \rho_{\vec k\sigma}\).
-
-\subsection{\(k-\)space mutual information}
-Another measure of many-body correlations would be the mutual information between two momentum-space states.
-The mutual information \(I_2\) between the states \(\ket{\vec k, \sigma}\) and \(\ket{\vec q, \sigma}\) is defined as
-\begin{equation}\begin{aligned}
-	I_2(\vec k\sigma:\vec q\sigma) = S_\text{EE}(\rho_{\vec k\sigma}) + S_\text{EE}(\rho_{\vec q\sigma}) - S_\text{EE}(\rho_{\vec k\sigma, \vec q\sigma})~,
-\end{aligned}\end{equation}
-where \(S_\text{EE}(\rho)\) is the von-Neumann entropy associated with the density matrix \(\rho\).
-The reduced density matrices \(\rho_{\vec k\sigma}\) and \(\rho_{\vec q\sigma}\) can be computed using eq.~\ref{density_matrix_kspace}; the reduced density matrix \(\rho_{\vec q\sigma, \vec k\sigma}\) has both the states \(\vec k\sigma\) and \(\vec q\sigma\) traced out, and it can be obtained by substituting \(\rho_{\vec k\sigma}\) back into eq.~\ref{density_matrix_kspace}:
-\begin{equation}\begin{aligned}
-	&\rho_{\vec k\sigma, \vec q\sigma} \\
-	=& \hat n_{\vec q\sigma}\rho_{\vec k\sigma}\hat n_{\vec q\sigma} + \hat h_{\vec q\sigma}\rho_{\vec k\sigma}\hat h_{\vec q\sigma}\\
-	=& \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{Z}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{Z}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]\\
-				  &+ \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{Z}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{Z}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right]
-\end{aligned}\end{equation}
 

### 2024-03-24 dwaveNumerics/multiOrbKondoRGFlow.jl
started rewriting dWave esiam

@@ -10,7 +10,7 @@ tightBindDispersion(t::Float64, kx_arr_flat::Array{Float64}, ky_arr_flat::Array{
 
 # d-wave and p-wave generation functions
 dwaveKdep(kx::Float64, ky::Float64) = cos.(kx) - cos.(ky)
-pwaveKdep(kx::Float64, ky::Float64) = cos.(kx) + cos.(ky)
+pwaveKdep(kx_arr::Vector{Float64}, ky_arr::Vector{Float64}) = cos(kx_arr[1] - kx_arr[2] + kx_arr[3] - kx_arr[4]) + cos(ky_arr[1] - ky_arr[2] + ky_arr[3] - ky_arr[4])
 
 function getdensityOfStates(num_kspace::Int64, dispersionArray::Vector{Float64})
 	# momentum space interval is 2pi/N
@@ -63,7 +63,7 @@ function getIsoEnergeticContour(dispersionArray::Vector{Float64}, num_kspace::In
 end
 
 
-function stepwiseRenormalisation(innerIndicesArr::Vector{Float64}, energyCutoff::Float64, cutoffPoints::Vector{Float64}, proceed_flags::Vector{Int64}, kondoJArrayPrev::Array{Float64, 2}, kondoJArrayNext::Array{Float64, 2}, bathInt, num_kspace::Int64, deltaEnergy::Float64, densityOfStates::Vector{Float64})
+function stepwiseRenormalisation(innerIndicesArr::Vector{Int64}, energyCutoff::Float64, cutoffPoints::Vector{Int64}, proceed_flags::Matrix{Int64}, kondoJArrayPrev::Array{Float64, 2}, kondoJArrayNext::Array{Float64, 2}, bathInt, num_kspace::Int64, deltaEnergy::Float64, densityOfStates::Vector{Float64})
     omega = -abs(energyCutoff) / 2
     Threads.@threads for (innerIndex1, innerIndex2) in collect(Iterators.product(innerIndicesArr, innerIndicesArr))
         denominators = [omega - abs(energyCutoff) / 2 + kondoJArrayPrev[qpoint, qpoint] / 4 + 
@@ -143,8 +143,8 @@ function multiOrbKondoRGFlow(num_kspace_half::Int64, t::Float64, J_init::Float64
 	# bath interaction does not renormalise, so we don't need to make it into a matrix. A function
[…]

### 2024-03-26 TilingProjectDraft/tilingProject.tex
incorporated dWave esiam notes iinto tiling notes

@@
 One can then substitute the information obtained from solutions of the auxiliary model, and thereby calculate quantities on the bulk lattice model.
+
+\section{Extending the Anderson impurity model}
+We consider an impurity spin \(\vec S_d\) interacting with a two-dimensional tight-binding conduction bath through a general interaction of the form
+\begin{equation}\begin{aligned}
+		\sum_{{\bf k}_1, {\bf k}_2, \sigma_1, \sigma_2} J_{{\bf k}_1, {\bf k}_2} \vec{S}_d\cdot\frac{1}{2}\vec{\tau}_{\sigma_1,\sigma_2} c^\dagger_{{\bf k}_1,\sigma_1}c_{{\bf k}_2,\sigma_2}
+\end{aligned}\end{equation}
+where \(\vec \tau\) is the vector of sigma matrices and \({\bf k}_1,{\bf k}_2\) are momentum states of the conduction bath.
+The precise form of \(J_{{\bf k}_1, {\bf k}_2}\) depends on the symmetry of the symmetry of the impurity-bath interaction.
+We consider the following three cases:
+
+(i)~a d-wave interaction, where the impurity couples with a coherent d-wave combination \(f_\sigma\) of the bath sites closest to it: \(f_\sigma \equiv \frac{1}{2}\left(c^\dagger_{L,\sigma} + c^\dagger_{R,\sigma} - c^\dagger_{U\sigma} - c^\dagger_{D\sigma}\right)\), where \(L,R,U\) and \(D\) indicate electrons at the positions \((x,y)=\left(-a,0\right), \left( a,0 \right) , \left( 0,a \right) \) and \(\left( 0,-a \right) \) respectively, \(a\) being the lattice spacing of the conduction bath lattice.
+The corresponding interaction (in real space) is of the form \(\vec{S}_d\cdot\sum_{\sigma_1,\sigma_2}\frac{1}{2}\vec{\tau}_{\sigma_1,\sigma_2}f^\dagger_{\sigma_1}f_{\sigma_2}\).
+When fourier-transformed to momentum space, it gives rise to the momentum-dependent Kondo coupling
+\begin{equation}\begin{aligned}\label{J_dwave}
+	J_{{\bf k}_1, {\bf k}_2} = J\prod_{i=1,2}\left[\cos\left( ak_i^x \right) - \cos\left( ak_i^y \right) \right]~.
+\end{aligned}\end{equation}
+For reference, we define the Fourier transforms as \(c^\dagger_{L(R),\sigma} = \sum_{{\bf k}}c^\dagger_{{\bf k},\sigma}e^{-(+)ik^x a}\), \(c^\dagger_{U(D),\sigma} = \sum_{{\bf k}}c^\dagger_{{\bf k},\sigma}e^{-(+)ik^y a}\).
+
+(ii)~a p-wave interaction, where the impurity couples with the p-wave electron \(p_\sigma \equiv \frac{1}{2}\left(c^\dagger_{L,\sigma} + c^\dagger_{R,\sigma} + c^\dagger_{U\sigma} + c^\dagger_{D\sigma}\right)\).
+The momentum-dependent Kondo coupling in this case is
+\begin{equation}\begin{aligned}\label{J_pwave}
+	J_{{\bf k}_1, {\bf k}_2} = J\prod_{i=1,2}\left[\cos\left( ak_i^x \right) + \cos\left( ak_i^y \right) \right]
+\end{aligned}\end{equation}
+Since we are considering a 2-dimensional conduction bath in the tight-binding limit, such a Kondo coupling vanishes close to the Fermi surface.
+As a result, this case is not interesting for our purpose.
+
+(iii)~a p-wave interaction, but without the off-site terms in the bath.
+This amounts to considering the Kondo interaction term \(J\vec{S}_d\cdot\sum_{\sigma_1,\sigma_2}\frac{1}{2}\vec{\tau}_{\sigma_1,\sigma_2}\frac{1}{4}\sum_{i=L,R,U,D}c^\dagger_{i,\sigma_1}c_{i,\sigma_2}\).
+The momentum-dependent Kondo coupling in this case is
+\begin{equation}\begin{aligned}\label{J_pwave_nooffsite}
+	J_{{\bf k}_1, {\bf k}_2} \equiv \frac{1}{2}J \cos\left[ a\left( k_1^x - k_2^x \right) + x\to y \right]
+\end{aligned}\end{equation}
+This does not vanish identically on the Fermi surface, and is therefore of potential interest to us.
+
+We also consider correlation terms on the bath sites \(L,R,U\) and \(D\). In momentum space, it is of the general form
+\begin{equation}\begin{aligned}
+-\frac{1}{2}\sum_{1, 2, 3, 4}\sum_\sigma W_{1,2,3,4}~ c^\dagger_{{\bf k}_1,\sigma}c_{{\bf k}_2,\sigma}\left(c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} - c^\dagger_{{\bf k}_3,\bar\sigma}c_{{\bf k}_4,\bar\sigma}\right) ~,
+\end{aligned}\end{equation}
+where the form of \(W_{\left\{{\bf k}_i\right\}}\) is again determined by the orbitals participating in the interaction.
+We ignore the p-wave interaction (for the same reason as above) and consider just the d-wave interaction and a p-wave interaction without off-site terms.
+These two cases lead to the following Hamiltonian structures:
+(i)~a d-wave interaction, of the form \(-\frac{W}{2}\left(f^\dagger_{\uparrow}f_{\uparrow} - f^\dagger_{\downarrow}f_{\downarrow}\right)^2\) in real space, leading to the momentum-dependence
+\begin{equation}\begin{aligned}\label{W_dwave}
+	W_{1,2,3,4} = W\prod_{i=1,2,3,4}\left[\cos\left( ak_i^x \right) - \cos\left( ak_i^y \right) \right]~.
+\end{aligned}\end{equation}
+(ii)~a p-wave interaction without off-site terms, \(-\frac{W}{2}\sum_{i=L,R,U,D}\left(c^\dagger_{i,\uparrow}c_{i,\uparrow} - c^\dagger_{i,\downarrow}c_{i,\downarrow}\right)^2\), leading to the following form in momentum space:
+\begin{equation}\begin{aligned}\label{W_pwave_nooffsite}
+	W_{\left\{{\bf k}_i\right\}} = \frac{1}{4}W\left[\cos\left(a\left(k_1^x - k_2^x + k_3^x - k_4^x\right)\right) + x \to y\right]~.
+\end{aligned}\end{equation}
+
+To summarise, the total Hamiltonian we consider is of the form
+\begin{equation}\begin{aligned}\label{hamiltonian}
+	&-2t\sum_{kx,k y}\left[\cos(ak_x) + \cos(ak_y)\right] c^\dagger_{{\bf k},\sigma}c_{{\bf k},\sigma} + \\
+	 &\sum_{{\bf k}_1, {\bf k}_2, \sigma_1, \sigma_2} J_{{\bf k}_1, {\bf k}_2} \vec{S}_d\cdot\frac{1}{2}\vec{\tau}_{\sigma_1,\sigma_2} c^\dagger_{{\bf k}_1,\sigma_1}c_{{\bf k}_2,\sigma_2} -\\
+	 &\frac{1}{2}\sum_{1, 2, 3, 4}\sum_\sigma W_{1,2,3,4}~ c^\dagger_{{\bf k}_1,\sigma}c_{{\bf k}_2,\sigma}\left(c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} - c^\dagger_{{\bf k}_3,\bar\sigma}c_{{\bf k}_4,\bar\sigma}\right)~,
+\end{aligned}\end{equation}
+where \(J_{\left\{ {\bf k}_i \right\} }\) takes one of the two forms in eqs.~\ref{J_dwave} and \ref{J_pwave_nooffsite}, and \(W_{\left\{{\bf k}_i\right\}}\) can similarly take either of the two forms in eqs.~\ref{W_dwave} and \ref{W_pwave_nooffsite}.
 
@@
 By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to each other:
-\begin{equation}\begin{aligned}
+\begin{equation}\begin{aligned}\label{couplingsMappings}
 	\tilde t = t+2V,~~ \tilde U = U + U_b, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
@@
 \subsection{Value of the critical paramter for the bulk model}
-Using the mappings between the auxiliary model parameters and the bulk parameters (eq.~\ref{map_aux_bulk}), one can define a critical value \(r^{*}\) of the ratio \(r = U_{H-H}/J_{H-H}\) at the critical points \(-U_b/J=1/4\) \textit{for a given and fixed value of \(U\)}.
+Using the mappings between the auxiliary model parameters and the bulk parameters (eq.~\ref{couplingsMappings}), one can define a critical value \(r^{*}\) of the ratio \(r = U_{H-H}/J_{H-H}\) at the critical points \(-U_b/J=1/4\) \textit{for a given and fixed value of \(U\)}.
 We will now argue that this critical point describes a metal-insulator transition.
@@
 
-Finally, using relations \eqref{map_aux_bulk} between the auxiliary model couplings and the bulk parameters, we can offer a functional form for the critical value of the parameter $r^{*} = U_{H-H}^{*}/J_{H-H}^{*}$.
-Using \(U_{H-H}^{*} = U^* + U_b\) and \(J_{H-H}^{*} = 2J^*\) (following \eqref{map_aux_bulk}), we get
+Finally, using relations \eqref{couplingsMappings} between the auxiliary model couplings and the bulk parameters, we can offer a functional form for the critical value of the parameter $r^{*} = U_{H-H}^{*}/J_{H-H}^{*}$.
+Using \(U_{H-H}^{*} = U^* + U_b\) and \(J_{H-H}^{*} = 2J^*\) (following \eqref{couplingsMappings}), we get
 \begin{equation}\begin{aligned}
@@
 In the insulating state, the cluster becomes a local moment and the bulk system reduces to the atomic limit \(H = -\frac{U}{2}\sum_i\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\).
-The Greens function in this limit is given in Appendix~\ref{atomic limit}.
-From eq.~\ref{atomic_limit_gf}, we have
+The Greens function in this limit is that of the atomic limit of the Hubbard model:
 \begin{equation}\begin{aligned}
@@
 
+\section{Derivation of RG equations for the embedded e-SIAM}
+\subsection{RG scheme}
+At any given step \(j\) of the RG procedure, we decouple the states \(\left\{ {\bf q} \right\} \) on the isoenergetic surface of energy \(\varepsilon_j\).
+The diagonal Hamiltonian \(H_D\) for this step consists of all terms that do not change the occupancy of the states \(\left\{{\bf q}\right\}\):
+\begin{equation}\begin{aligned}
+	H_D^{(j)} = \varepsilon_j\sum_{q,\sigma}\tau_{q,\sigma} + \frac{1}{2}\sum_{{\bf q}}J_{{\bf q}, {\bf q}}S_d^z\left(\hat n_{{\bf q}, \uparrow} - \hat n_{{\bf q}, \downarrow}\right) - \frac{1}{2}\sum_{{\bf q}}W_{\bf q}\left(\hat n_{{\bf q}, \uparrow} - \hat n_{{\bf q}, \downarrow}\right)^2~,
+\end{aligned}\end{equation}
+where \(\tau = \hat n - 1/2\) and \(W_{{\bf q}}\) is a shorthand for \(W_{{\bf q},{\bf q},{\bf q},{\bf q}}\).
+The three terms, respectively, are the kinetic energy of the momentum states on the isoenergetic shell that we are decoupling, the spin-correlation energy between the impurity spin and the spins formed by these momentum states and, finally, the local correlation energy associated with these states arising from the \(W\) term.
+The off-diagonal part of the Hamiltonian on the other hand leads to scattering in the states \(\left\{ {\bf q} \right\} \).
+We now list these terms, classified by the coupling they originate from.
+
+\textbf{Arising from the Kondo spin-exchange term}
+\begin{equation}\begin{aligned}
+	T_{KZ1}^\dagger + T_{KZ1} &= \frac{1}{2}\sum_{{\bf k}, {\bf q}, \sigma}\sigma J_{{\bf k}, {\bf q}} S_d^z  \left[c^\dagger_{{\bf q}\sigma}c_{{\bf k},\sigma} + \text{h.c.}\right],\\
+	T_{KZ2}^\dagger + T_{KZ2} &= \frac{1}{2}\sum_{{\bf q}, \sigma}\sigma J_{{\bf q}, {\bf \bar q}} S_d^z  \left[c^\dagger_{{\bf q}\sigma}c_{{\bf \bar q},\sigma} + \text{h.c.}\right],\\
+	T_{KT1}^\dagger + T_{KT1} &= \frac{1}{2}\sum_{{\bf k}, {\bf q}}J_{{\bf k}, {\bf q}} \left[S_d^+\left(c^\dagger_{{\bf q}\downarrow}c_{{\bf k}\uparrow} + c^\dagger_{{\bf k}\downarrow}c_{{\bf q}\uparrow}\right) + \text{h.c.}\right],\\
+	T_{KT2}^\dagger + T_{KT2} &= \frac{1}{2}\sum_{{\bf q}}J_{{\bf q}, {\bf \bar q}} \left[S_d^+\left(c^\dagger_{{\bf q}\downarrow}c_{{\bf \bar q}\uparrow} + c^\dagger_{{\bf \bar q}\downarrow}c_{{\bf q}\uparrow}\right) + \text{h.c.}\right],\\
+\end{aligned}\end{equation}
+\textbf{Arising from spin-preserving scattering within conduction bath}
+\begin{equation}\begin{aligned}
+	T_{P1}^\dagger + T_{P1} &= -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3, {\bf k}_4 < \varepsilon_j}\sum_{\sigma} \left[W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4}c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} + \text{h.c.}\right]\\
+	T_{P2}^\dagger + T_{P3} &= -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2 < \varepsilon_j}\sum_{\sigma} W_{{\bf q},{\bf k}_2,{\bf \bar q}, {\bf \bar q}} c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma} n_{{\bf \bar q},\sigma} -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_1 < \varepsilon_j}\sum_{\sigma} W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}} c^\dagger_{{\bf k}_1,\sigma}c_{{\bf q},\sigma} n_{{\bf q},\sigma}
+\end{aligned}\end{equation}
+\textbf{Arising from spin-flip scattering within conduction bath}
+\begin{equation}\begin{aligned}
+	T_{F1}^\dagger + T_{F1} &= \sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3, {\bf k}_4 < \varepsilon_j}\sum_{\sigma} \left[W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4}c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\bar\sigma}c_{{\bf k}_4,\bar\sigma} + \text{h.c.}\right]\\
+	T_{F2} &= \sum_{{\bf q}, {\bf q}^\prime \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3 < \varepsilon_j}\sum_{\sigma}W_{{\bf q},{\bf q}^\prime,{\bf k}_2,{\bf k}_3} c^\dagger_{{\bf q},\sigma}c_{{\bf q}^\prime,\sigma}c^\dagger_{{\bf k}_2,\bar\sigma}c_{{\bf k}_3,\bar\sigma}\\
+	T_{F3} &= \sum_{{\bf q}, {\bf q}^\prime \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3 < \varepsilon_j}\sum_{\sigma} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf q}^\prime} c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\bar\sigma}c_{{\bf q}^\prime,\bar\sigma} \\
+	T_{F4}^\dagger + T_{F4} &= \sum_{{\bf q}, {\bf q}^\prime, \in \varepsilon_j}\sum_{{\bf k}_1 < \varepsilon_j}\sum_{\sigma} \left[W_{{\bf q},{\bf q},{\bf q}^{\prime}, {\bf k}_1} n_{{\bf q},\sigma} c^\dagger_{{\bf q}^{\prime},\bar\sigma}c_{{\bf k}_1,\bar\sigma} + \text{h.c.}\right]
+\end{aligned}\end{equation}
+In all of the terms \(T_{P[i]}\) and \(T_{F[i]}\), the factor of \(1/2\) in front has been cancelled out by a factor of 2 coming from the multiple possibilities of arranging the momentum labels.
+
+The renormalisation of the Hamiltonian is constructed from the general expression
+\begin{equation}\begin{aligned}
+	\Delta H^{(j)} = H_X \frac{1}{\omega- H_D} H_X~.
+\end{aligned}\end{equation}
+
+The states on the isoenergetic shell \(\pm|\varepsilon_j|\) come in particle-hole pairs \(\left( {\bf q}, {\bf \bar q} \right) \) with energies of opposite signs (relative to the Fermi energy).
+If \({\bf q}\) is defined as the hole state (unoccupied in the absence of quantum fluctuations), it will have positive energy, while the particle state \({\bf \bar q}\) will be of negative energy and hence below the Fermi surface.
+To be more specific, given a state \({\bf q}\) with energy \(\pm|\varepsilon_j|\), we define its particle-hole transformed counterpart as the state \({\bf \bar q} = \boldsymbol{\pi} + {\bf q}\), having energy \(\mp|\varepsilon_j|\) and residing in the opposite quadrant of the Brillouin zone.
+Given this definition, we have the important property that
+\begin{equation}\begin{aligned}\label{particleHoleRelation}
+	J_{{\bf k}, {\bf \bar q}} &= -J_{{\bf k}, {\bf q}},\\
+	W_{\left\{{\bf k}\right\}, {\bf \bar q}} &= -W_{\left\{{\bf k}\right\}, {\bf q}}~.
+\end{aligned}\end{equation}
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.35\textwidth]{particleHoleRelation.pdf}
+	\caption{Particle and hole states.}
+	\label{fig:particleHoleRelation-pdf}
+\end{figure}
+\subsection{Renormalisation of the bath correlation term {\it W}}
+The bath correlation term \(W\) can undergo renormalisation only via scattering processes arising from itself.
+Irrespective of whether the state \({\bf q}\) being decoupled is in a particle or hole configuration in the initial many-body state, the propagator \(G = 1/(\omega - H_D)\) of the intermediate excited state is uniform, and equal to
+\begin{equation}\begin{aligned}\label{propagatorW}
+	G_W = 1/\left(\omega - |\varepsilon_j|/2 + W_{\bf q}/2)\right)~,
+\end{aligned}\end{equation}
+where \(W_{\bf q}\) is the same whether \({\bf q}\) is above or below the Fermi surface.
+The \(|\varepsilon_j|/2\) in \(H_D\) arises from the excited nature of the state after the initial scattering process.
+
+\paragraph*{Scattering arising purely from spin-preserving processes}
+In this subsection, we calculate the renormalisation to \(W\) arising from the terms \(T_{P1}\), \(T_{P2}\) and \(T_{P3}\). The first term is
+\begin{equation}\begin{aligned}
+	T_{P1}^\dagger G_W T_{P3} &= \sum_\sigma\sum_{{\bf k}_1, {\bf k}_2, {\bf k}_3, {\bf k}_4} \sum_{\bf q} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4}c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} G_W W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}} c^\dagger_{{\bf k}_1,\sigma}c_{{\bf q},\sigma} n_{{\bf q},\sigma}\\
+							  &= -\sum_\sigma\sum_{{\bf k}_1, {\bf k}_2, {\bf k}_3, {\bf k}_4} c^\dagger_{{\bf k}_1,\sigma} c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} \sum_{\bf q \in \text{PS}} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4} G_W W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}}~.
+\end{aligned}\end{equation}
+The operators acting on the states being decoupled contract to form a number operator \(n_{{\bf q},\sigma}\) which projects the sum over \({\bf q}\) into the states that are initial occupied (particle sector, PS).
+
+The second such contribution is obtained by flipping the sequence of scattering processes:
+\begin{equation}\begin{aligned}
+	T_{P3} G_W T_{P1}^\dagger &= \sum_\sigma\sum_{{\bf k}_1, {\bf k}_2, {\bf k}_3, {\bf k}_4} \sum_{\bf q} W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}} c^\dagger_{{\bf k}_1,\sigma}c_{{\bf q},\sigma} n_{{\bf q},\sigma} G_W W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4}c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} \\
+							  &= \sum_\sigma\sum_{{\bf k}_1, {\bf k}_2, {\bf k}_3, {\bf k}_4} c^\dagger_{{\bf k}_1,\sigma} c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} \sum_{\bf q \in \text{HS}} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4} G_W W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}}~.
+\end{aligned}\end{equation}
+By virtue of eq.~\ref{particleHoleRelation}, the product of couplings \(W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4} G_W W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}}\) is the same irrespective of whether \({\bf q}\) belongs to the particle or hole sector.
+The two contributions therefore cancel each other.
+Moreover, the remaining contributions \(T_{P3}^\dagger G_W T_{P1}\) and \(T_{P1}G_W T_{P2}^\dagger\) are effectively hermitian conjugates of the two contributions considered above, and therefore also cancel each other.
+
+\paragraph*{Scattering arising from spin-flip processes}
+We now come to the processes that involve spin-flips. Considering \(T_{F1}\) and \(T_{F4}\) first, we get
+\begin{equation}\begin{aligned}
+	T_{F1}^\dagger G_W T_{F4} &= \sum_\sigma\sum_{{\bf k}_1, {\bf k}_2, {\bf k}_3, {\bf k}_4} \sum_{\bf q} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4}c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\bar\sigma}c_{{\bf k}_4,\bar\sigma} G_W W_{{\bf k}_1, {\bf q}, {\bf q}, {\bf q}}  c^\dagger_{{\bf k}_1\sigma} c_{{\bf q}\sigma} n_{{\bf q} \bar \sigma} \\
+							  &= -\sum_{1,2,3,4}\sum_\sigma c^\dagger_{{\bf k}_1\sigma} c_{{\bf k}_2\sigma} c^\dagger_{{\bf k}_3\bar\sigma} c_{{\bf k}_4\bar \sigma} \sum_{\bf q \in \text{PS}} W_{{\bf q}, {\bf k}_2, {\bf k}_4, {\bf k}_4} G_W W_{{\bf k}_1, {\bf q}, {\bf q}, {\bf q}}~,\\
+	T_{F4} G_W T_{F1}^\dagger &= \sum_\sigma\sum_{{\bf k}_1, {\bf k}_2, {\bf k}_3, {\bf k}_4} \sum_{\bf q}W_{{\bf k}_1, {\bf q}, {\bf q}, {\bf q}}  c^\dagger_{{\bf k}_1\sigma} c_{{\bf q}\sigma} n_{{\bf q} \bar \sigma} G_W W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4}c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\bar\sigma}c_{{\bf k}_4,\bar\sigma}  \\
+							  &= \sum_{1,2,3,4}\sum_\sigma c^\dagger_{{\bf k}_1\sigma} c_{{\bf k}_2\sigma} c^\dagger_{{\bf k}_3\bar\sigma} c_{{\bf k}_4\bar \sigma} \sum_{\bf q \in \text{HS}} W_{{\bf q}, {\bf k}_2, {\bf k}_4, {\bf k}_4} G_W W_{{\bf k}_1, {\bf q}, {\bf q}, {\bf q}}~.
+\end{aligned}\end{equation}
+By the same arguments as in the previous subsection, these terms cancel each other out.
+Their hermitian conjugate contributions \(T_{F1} G_W T_{F4}^\dagger\) and \(T_{F4}^\dagger G_W T_{F1}\) also cancel out.
+The other two terms are \(T_{F2}\) and \(T_{F3}\), and their contributions also cancel out for the same reason:
+\begin{equation}\begin{aligned}
+	T_{F2} G_W T_{F2} &= \sum_\sigma\sum_{{\bf k}_1, {\bf k}_2, {\bf k}_3, {\bf k}_4} \sum_{\bf q}W_{{\bf q},{\bf \bar q},{\bf k}_3,{\bf k}_4} c^\dagger_{{\bf q},\sigma}c_{{\bf \bar q},\sigma}c^\dagger_{{\bf k}_3,\bar\sigma}c_{{\bf k}_4,\bar\sigma} G_W W_{{\bf \bar q},{\bf q},{\bf k}_1,{\bf k}_2} c^\dagger_{{\bf \bar q},\sigma}c_{{\bf q},\sigma}c^\dagger_{{\bf k}_1,\bar\sigma}c_{{\bf k}_2,\bar\sigma} \\
+							  &= \sum_{1,2,3,4}\sum_\sigma c^\dagger_{{\bf k}_1\sigma} c_{{\bf k}_2\sigma} c^\dagger_{{\bf k}_3\bar\sigma} c_{{\bf k}_4\bar \sigma} \sum_{\bf q \in \text{PS}} W_{{\bf q},{\bf \bar q},{\bf k}_3,{\bf k}_4} G_W W_{{\bf \bar q},{\bf q},{\bf k}_1,{\bf k}_2}~,\\
+	T_{F3} G_W T_{F3} &= \sum_\sigma\sum_{{\bf k}_1, {\bf k}_2, {\bf k}_3, {\bf k}_4} \sum_{\bf q} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf \bar q}} c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\bar\sigma}c_{{\bf \bar q},\bar\sigma} G_W W_{{\bf \bar q},{\bf k}_4,{\bf k}_1,{\bf q}} c^\dagger_{{\bf \bar q},\bar\sigma} c_{{\bf k}_4,\bar\sigma} c^\dagger_{{\bf k}_1,\sigma} c_{{\bf q},\sigma} \\
+							  &= -\sum_{1,2,3,4}\sum_\sigma c^\dagger_{{\bf k}_1\sigma} c_{{\bf k}_2\sigma} c^\dagger_{{\bf k}_3\bar\sigma} c_{{\bf k}_4\bar \sigma} \sum_{\bf q \in \text{PS}} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf \bar q}} G_W W_{{\bf \bar q},{\bf k}_4,{\bf k}_1,{\bf q}}~,
+\end{aligned}\end{equation}
+
+\paragraph*{Scattering involving both spin-flip and spin-preserving processes}
+These processes involve the combination of terms like \(T_{P1}\) with \(T_{F4}\), and \(T_{P2}\) with \(T_{F1}\). These again cancel each other out for the same reasons as outline above.
+
+\paragraph*{Net renormalisation for the bath correlation term}
+Since all the contributions cancel out in pairs, the bath correlation term \(W\) is {\it marginal}.
+
+\subsection{Renormalisation of the Kondo scattering term {\it J}}
+We focus on the renormalisation of the spin-flip part of the Kondo interaction.
+For these processes, the intermediate many-body state always involves the impurity spin being anti-correlated with the conduction electron spin, such that the propagator for that state is \(G_J = 1/\left(\omega - |\varepsilon_j|/2 + J_{\bf q}/4 + W_{\bf q}/2)\right) \).
+\paragraph*{Impurity-mediated spin-flip scattering purely through Kondo-like processes}
+The following processes arising from the Kondo term renormalise the spin-flip interaction:
+\begin{equation}\begin{aligned}\label{kondoRenorm1}
+	T^\dagger_{KT1} G_J \left(T_{KZ1} + T_{KZ1}^\dagger\right) &= \frac{1}{4}\sum_{{\bf k}_1, {\bf k}_1, {\bf q}}~J_{{\bf q}, {\bf k}_2} S_d^+ \left[-c^\dagger_{{\bf q}\downarrow} c_{{\bf k}_2 \uparrow} G_J c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf q} \downarrow} + c^\dagger_{{\bf k}_2\downarrow} c_{{\bf q} \uparrow} G_J c^\dagger_{{\bf q}\uparrow} c_{{\bf k}_1 \uparrow}\right]J_{{\bf k}_1,{\bf q}} S_d^z\\
+								&= -\frac{1}{8}\sum_{{\bf k}_1, {\bf k}_1, {\bf q}}~J_{{\bf q}, {\bf k}_2} S_d^+ \left[ c^\dagger_{{\bf k}_1 \downarrow}c_{{\bf k}_2 \uparrow} G_J n_{{\bf q} \downarrow} + c^\dagger_{{\bf k}_2\downarrow} c_{{\bf k}_1 \uparrow}(1 - n_{{\bf q} \uparrow}) G_J \right]J_{{\bf k}_1,{\bf q}}\\
+								&= -\frac{1}{8}\sum_{{\bf k}_1, {\bf k}_1}~ S_d^+ c^\dagger_{{\bf k}_1 \downarrow}c_{{\bf k}_2 \uparrow}\sum_{{\bf q} \in \text{PS}}\left[J_{{\bf q}, {\bf k}_2} J_{{\bf k}_1,{\bf q}} + J_{{\bf \bar q}, {\bf k}_1} J_{{\bf k}_2,{\bf \bar q}} \right]G_J~.
+\end{aligned}\end{equation}
+In getting the final expression, we used the sigma matrix relation \(S_d^+ S_d^z = -\frac{1}{2}S_d^+\), and absorbed the projector \(1 - n_{{\bf q} \uparrow}\) into the sum over the particle sector by replacing \(q\) with its particle-hole transformed counterpart \(\bar q\).
+An identical contribution is obtained by switching the sequence of processes:
+\begin{equation}\begin{aligned}\label{kondoRenorm2}
+	 \left(T_{KZ1} + T_{KZ1}^\dagger\right) G_J T^\dagger_{KT1} &= \frac{1}{4}\sum_{{\bf k}_1, {\bf k}_1, {\bf q}}~J_{{\bf k}_1,{\bf q}} S_d^z\left[- c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf q} \downarrow}G_J c^\dagger_{{\bf q}\downarrow} c_{{\bf k}_2 \uparrow} +c^\dagger_{{\bf q}\uparrow} c_{{\bf k}_1 \uparrow} G_J c^\dagger_{{\bf k}_2\downarrow} c_{{\bf q} \uparrow} \right] J_{{\bf q}, {\bf k}_2} S_d^+ \\
+								&= -\frac{1}{8}\sum_{{\bf k}_1, {\bf k}_1}~ S_d^+ c^\dagger_{{\bf k}_1 \downarrow}c_{{\bf k}_2 \uparrow}\sum_{{\bf q} \in \text{PS}}\left[J_{{\bf \bar q}, {\bf k}_2} J_{{\bf k}_1,{\bf \bar q}} + J_{{\bf q}, {\bf k}_1} J_{{\bf k}_2,{\bf q}} \right]G_J~.
+\end{aligned}\end{equation}
+
+\paragraph*{Scattering processes involving interplay between the Kondo interaction and conduction bath interaction}
+Looking at \(T_{KT1}^\dagger\) first, we have
+\begin{equation}\begin{aligned}\label{t7t6}
+	T_{KT1}^\dagger G_J \left(T_{F4} + T_{F4}^\dagger\right) &= \frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2,{\bf q}} J_{{\bf k}_2, {\bf q}}S_d^+ \left(c^\dagger_{{\bf q}\downarrow}c_{{\bf k}_2\uparrow}  G_J W_{{\bf q}, {\bf q}, {\bf k}_1, {\bf q}} n_{q \uparrow} c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf q} \downarrow} + c^\dagger_{{\bf k}_2\downarrow}c_{{\bf q}\uparrow}  G_J W_{{\bf \bar q}, {\bf \bar q}, {\bf q}, {\bf k}_1} n_{\bar q \downarrow} c^\dagger_{{\bf q} \uparrow} c_{{\bf k}_1 \uparrow}\right) ~.
+\end{aligned}\end{equation}
+For either of the two choices of the functional form of \(W\), it is easy to show that \(W_{{\bf q}, {\bf q}, {\bf k}_1, {\bf q}} = W_{{\bf \bar q}, {\bf \bar q}, {\bf q}, {\bf k}_1}\).
+\begin{equation}\begin{aligned}\label{KT1F4}
+	T_{KT1}^\dagger G_J \left(T_{F4} + T_{F4}^\dagger\right) &= \frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2,{\bf q}} J_{{\bf k}_2, {\bf q}} W_{{\bf q}, {\bf q}, {\bf k}_1, {\bf q}} G_J S_d^+ \left[-c^\dagger_{{\bf k}_1 \downarrow}c_{{\bf k}_2\uparrow} n_{{\bf q}\downarrow} n_{q \uparrow} + c^\dagger_{{\bf k}_2\downarrow} c_{{\bf k}_1 \uparrow} (1 - n_{{\bf q}\uparrow}) n_{\bar q \downarrow}\right] ~.
+\end{aligned}\end{equation}
+
+Another contribution is obtained by switching the sequence of the scattering processes:
+\begin{equation}\begin{aligned}\label{F4KT1}
+	\left(T_{F4} + T_{F4}^\dagger\right) G_J T_{KT1}^\dagger &= \frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2,{\bf q}} \left(W_{{\bf q}, {\bf q}, {\bf k}_1, {\bf q}} n_{\bar q \uparrow} c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf q} \downarrow} G_J c^\dagger_{{\bf q}\downarrow}c_{{\bf k}_2\uparrow} + W_{{\bf \bar q}, {\bf \bar q}, {\bf q}, {\bf k}_1} n_{q \downarrow} c^\dagger_{{\bf q} \uparrow} c_{{\bf k}_1 \uparrow} G_J c^\dagger_{{\bf k}_2\downarrow}c_{{\bf q}\uparrow} \right) J_{{\bf k}_2, {\bf q}}S_d^+\\
+															 &= \frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2,{\bf q}} \left(c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf k}_2\uparrow} n_{\bar q \uparrow} (1 - n_{{\bf q} \downarrow}) - c^\dagger_{{\bf k}_2\downarrow}c_{{\bf k}_1 \uparrow}n_{q \downarrow} n_{{\bf q} \uparrow}\right) W_{{\bf q}, {\bf q}, {\bf k}_1, {\bf q}} G_J J_{{\bf k}_2, {\bf q}}S_d^+
+\end{aligned}\end{equation}
+The two contributions (eqs.~\ref{KT1F4} and \ref{F4KT1}) arising from \(T_{KT1}\) cancel each other.
+
+We now consider the other spin-exchange process \(T_{KT2}^\dagger\). One such contribution is
+\begin{equation}\begin{aligned}\label{kondoRenorm3}
+	T_{KT2}^\dagger G_J T_{F3} &= \frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2,{\bf q}} J_{{\bf q}, {\bf \bar q}}S_d^+ \left(c^\dagger_{{\bf q}\downarrow}c_{{\bf \bar q}\uparrow} G_J c^\dagger_{{\bf \bar q} \uparrow} c_{{\bf k}_2 \uparrow} c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf q} \downarrow} + c^\dagger_{{\bf \bar q}\downarrow}c_{{\bf q}\uparrow}  G_J  c^\dagger_{{\bf q} \uparrow} c_{{\bf k}_2 \uparrow} c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf \bar q} \downarrow}\right)W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}\\
+							   &= -\frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2,{\bf q}} S_d^+ c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf k}_2 \uparrow}\left[n_{{\bf q}\downarrow}(1 - n_{{\bf \bar q}\uparrow}) + n_{{\bf \bar q}\downarrow}(1 - n_{{\bf q}\uparrow}) \right] J_{{\bf q}, {\bf \bar q}} G_J W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}\\
+							   &= -\frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2} S_d^+ c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf k}_2 \uparrow}\sum_{{\bf q} \in \text{PS}}\left(J_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} + J_{{\bf \bar q}, {\bf q}} W_{{\bf q}, {\bf k}_2, {\bf k}_1, {\bf \bar q}}\right)G_J~.
+\end{aligned}\end{equation}
+An identical contribution is obtained from the reversed term:
+\begin{equation}\begin{aligned}\label{kondoRenorm4}
+	T_{F3}G_J T_{KT2}^\dagger  &= \frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2,{\bf q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}\left(c^\dagger_{{\bf \bar q} \uparrow} c_{{\bf k}_2 \uparrow} c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf q} \downarrow} G_J c^\dagger_{{\bf q}\downarrow}c_{{\bf \bar q}\uparrow} +  c^\dagger_{{\bf q} \uparrow} c_{{\bf k}_2 \uparrow} c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf \bar q} \downarrow} G_J c^\dagger_{{\bf \bar q}\downarrow}c_{{\bf q}\uparrow} \right)J_{{\bf q}, {\bf \bar q}}S_d^+ \\
+							   &= -\frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2} S_d^+ c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf k}_2 \uparrow}\sum_{{\bf q} \in \text{PS}}\left(J_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} + J_{{\bf \bar q}, {\bf q}} W_{{\bf q}, {\bf k}_2, {\bf k}_1, {\bf \bar q}}\right)G_J~.
+\end{aligned}\end{equation}
+
+\paragraph*{Net renormalisation to the Kondo interaction}
+Combining the results from eqs.~\ref{kondoRenorm1}, \ref{kondoRenorm2}, \ref{kondoRenorm3} and \ref{kondoRenorm4}, as well as using the properties \(J_{{\bf \bar q}, {\bf k}_1} J_{{\bf k}_2,{\bf \bar q}} = J_{{\bf q}, {\bf k}_2} J_{{\bf k}_1,{\bf q}}\) and \(J_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} = J_{{\bf \bar q}, {\bf q}} W_{{\bf q}, {\bf k}_2, {\bf k}_1, {\bf \bar q}}\), the total renormalisation in the momentum-resolved Kondo coupling \(J^{(j)}\) at the \(j^\text{th}\) step amounts to
+\begin{equation}\begin{aligned}
+	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{\frac{1}{2}\left(J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + J^{(j)}_{{\bf k}_1,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_2}\right) + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}
+\end{aligned}\end{equation}
+
 \end{widetext}

### 2024-03-27 TilingProjectDraft/tilingProject.tex
obtained specific forms for p-wave and d-wave case

@@
 \section{Extending the Anderson impurity model}
+\subsection{Hamiltonian}
 We consider an impurity spin \(\vec S_d\) interacting with a two-dimensional tight-binding conduction bath through a general interaction of the form
@@
 
-(i)~a d-wave interaction, where the impurity couples with a coherent d-wave combination \(f_\sigma\) of the bath sites closest to it: \(f_\sigma \equiv \frac{1}{2}\left(c^\dagger_{L,\sigma} + c^\dagger_{R,\sigma} - c^\dagger_{U\sigma} - c^\dagger_{D\sigma}\right)\), where \(L,R,U\) and \(D\) indicate electrons at the positions \((x,y)=\left(-a,0\right), \left( a,0 \right) , \left( 0,a \right) \) and \(\left( 0,-a \right) \) respectively, \(a\) being the lattice spacing of the conduction bath lattice.
-The corresponding interaction (in real space) is of the form \(\vec{S}_d\cdot\sum_{\sigma_1,\sigma_2}\frac{1}{2}\vec{\tau}_{\sigma_1,\sigma_2}f^\dagger_{\sigma_1}f_{\sigma_2}\).
+(i)~a d-wave interaction, where the impurity couples with a coherent d-wave combination \(f_\sigma\) of the bath sites closest to it: 
+\begin{equation}\begin{aligned}
+	f_\sigma \equiv \frac{1}{2}\left(c^\dagger_{L,\sigma} + c^\dagger_{R,\sigma} - c^\dagger_{U\sigma} - c^\dagger_{D\sigma}\right)~,
+\end{aligned}\end{equation}
+where \(L,R,U\) and \(D\) indicate electrons at the positions \((x,y)=\left(-a,0\right), \left( a,0 \right) , \left( 0,a \right) \) and \(\left( 0,-a \right) \) respectively, \(a\) being the lattice spacing of the conduction bath lattice.
+The corresponding interaction (in real space) is of the form
+\begin{equation}\begin{aligned}
+	\vec{S}_d\cdot\sum_{\sigma_1,\sigma_2}\frac{1}{2}\vec{\tau}_{\sigma_1,\sigma_2}f^\dagger_{\sigma_1}f_{\sigma_2}~.
+\end{aligned}\end{equation}
 When fourier-transformed to momentum space, it gives rise to the momentum-dependent Kondo coupling 
 \begin{equation}\begin{aligned}\label{J_dwave}
-	J_{{\bf k}_1, {\bf k}_2} = J\prod_{i=1,2}\left[\cos\left( ak_i^x \right) - \cos\left( ak_i^y \right) \right]~.
-\end{aligned}\end{equation}
-For reference, we define the Fourier transforms as \(c^\dagger_{L(R),\sigma} = \sum_{{\bf k}}c^\dagger_{{\bf k},\sigma}e^{-(+)ik^x a}\), \(c^\dagger_{U(D),\sigma} = \sum_{{\bf k}}c^\dagger_{{\bf k},\sigma}e^{-(+)ik^y a}\).
-
-(ii)~a p-wave interaction, where the impurity couples with the p-wave electron \(p_\sigma \equiv \frac{1}{2}\left(c^\dagger_{L,\sigma} + c^\dagger_{R,\sigma} + c^\dagger_{U\sigma} + c^\dagger_{D\sigma}\right)\).
-The momentum-dependent Kondo coupling in this case is
-\begin{equation}\begin{aligned}\label{J_pwave}
-	J_{{\bf k}_1, {\bf k}_2} = J\prod_{i=1,2}\left[\cos\left( ak_i^x \right) + \cos\left( ak_i^y \right) \right]
-\end{aligned}\end{equation}
-Since we are considering a 2-dimensional conduction bath in the tight-binding limit, such a Kondo coupling vanishes close to the Fermi surface.
-As a result, this case is not interesting for our purpose.
-
-(iii)~a p-wave interaction, but without the off-site terms in the bath.
-This amounts to considering the Kondo interaction term \(J\vec{S}_d\cdot\sum_{\sigma_1,\sigma_2}\frac{1}{2}\vec{\tau}_{\sigma_1,\sigma_2}\frac{1}{4}\sum_{i=L,R,U,D}c^\dagger_{i,\sigma_1}c_{i,\sigma_2}\).
+	J_{{\bf k}_1, {\bf k}_2} = J f_\mathcal{D}\left({\bf k}_1\right) f_\mathcal{D}\left({\bf k}_2\right) ~,
+\end{aligned}\end{equation}
+where \(f_\mathcal{D}({\bf k}) = \cos\left( ak_x \right) - \cos\left( ak_y \right) \) is the \(d-\)wave symmetric functional form in \(k-\)space.
+For future reference, we define the Fourier transforms as 
+\begin{equation}\begin{aligned}
+	c^\dagger_{L(R),\sigma} = \sum_{{\bf k}}c^\dagger_{{\bf k},\sigma}e^{+(-)ik_x a},\\
+	c^\dagger_{U(D),\sigma} = \sum_{{\bf k}}c^\dagger_{{\bf k},\sigma}e^{+(-)ik^y a}~.
+\end{aligned}\end{equation}
+(ii)~a p-wave interaction, but without the off-site terms in the bath. This amounts to considering the Kondo interaction term 
+\begin{equation}\begin{aligned}
+	J\vec{S}_d\cdot\sum_{\sigma_1,\sigma_2}\frac{1}{2}\vec{\tau}_{\sigma_1,\sigma_2}\frac{1}{4}\sum_{i=L,R,U,D}c^\dagger_{i,\sigma_1}c_{i,\sigma_2}~.
+\end{aligned}\end{equation}
 The momentum-dependent Kondo coupling in this case is 
 \begin{equation}\begin{aligned}\label{J_pwave_nooffsite}
-	J_{{\bf k}_1, {\bf k}_2} \equiv \frac{1}{2}J \cos\left[ a\left( k_1^x - k_2^x \right) + x\to y \right]
-\end{aligned}\end{equation}
-This does not vanish identically on the Fermi surface, and is therefore of potential interest to us.
+	J_{{\bf k}_1, {\bf k}_2} \equiv \frac{1}{2}J f_\mathcal{P}\left( {\bf k}_1, {\bf k}_2\right) ~,
+\end{aligned}\end{equation}
+where \(f_\mathcal{P}(\left\{{\bf k}_i\right\}) = \cos\left( ak_{1x} - ak_{2x} + ak_{3x} - \ldots\right) + x\to y \) is the form for the \(p-\)wave symmetric function.
 
@@
 where the form of \(W_{\left\{{\bf k}_i\right\}}\) is again determined by the orbitals participating in the interaction.
-We ignore the p-wave interaction (for the same reason as above) and consider just the d-wave interaction and a p-wave interaction without off-site terms.
-These two cases lead to the following Hamiltonian structures:
-(i)~a d-wave interaction, of the form \(-\frac{W}{2}\left(f^\dagger_{\uparrow}f_{\uparrow} - f^\dagger_{\downarrow}f_{\downarrow}\right)^2\) in real space, leading to the momentum-dependence
+We consider the d-wave interaction and a p-wave interaction without off-site terms, as above.
+These two cases lead to the following Hamiltonian structures:\\
+(i)~a d-wave interaction, of the form 
+\begin{equation}\begin{aligned}
+	-\frac{W}{2}\left(f^\dagger_{\uparrow}f_{\uparrow} - f^\dagger_{\downarrow}f_{\downarrow}\right)^2~,
+\end{aligned}\end{equation}
+in real space, leading to the momentum-dependence
 \begin{equation}\begin{aligned}\label{W_dwave}
-	W_{1,2,3,4} = W\prod_{i=1,2,3,4}\left[\cos\left( ak_i^x \right) - \cos\left( ak_i^y \right) \right]~.
-\end{aligned}\end{equation}
-(ii)~a p-wave interaction without off-site terms, \(-\frac{W}{2}\sum_{i=L,R,U,D}\left(c^\dagger_{i,\uparrow}c_{i,\uparrow} - c^\dagger_{i,\downarrow}c_{i,\downarrow}\right)^2\), leading to the following form in momentum space:
+	W_{1,2,3,4} = W\prod_{i=1,2,3,4}f_\mathcal{D}(k_i)~.
+\end{aligned}\end{equation}
+(ii)~a p-wave interaction without off-site terms, 
+\begin{equation}\begin{aligned}
+	-\frac{W}{2}\frac{1}{4}\sum_{i=L,R,U,D}\left(c^\dagger_{i,\uparrow}c_{i,\uparrow} - c^\dagger_{i,\downarrow}c_{i,\downarrow}\right)^2~,
+\end{aligned}\end{equation}
+leading to the following form in momentum space:
 \begin{equation}\begin{aligned}\label{W_pwave_nooffsite}
-	W_{\left\{{\bf k}_i\right\}} = \frac{1}{4}W\left[\cos\left(a\left(k_1^x - k_2^x + k_3^x - k_4^x\right)\right) + x \to y\right]~.
+	W_{\left\{{\bf k}_i\right\}} = \frac{1}{2}W f_\mathcal{P}\left({\bf k}_1, {\bf k}_2, {\bf k}_3, {\bf k}_4\right) ~.
 \end{aligned}\end{equation}
@@
 where \(J_{\left\{ {\bf k}_i \right\} }\) takes one of the two forms in eqs.~\ref{J_dwave} and \ref{J_pwave_nooffsite}, and \(W_{\left\{{\bf k}_i\right\}}\) can similarly take either of the two forms in eqs.~\ref{W_dwave} and \ref{W_pwave_nooffsite}.
+\subsection{Results}
+We studied the low-energy physics of this model through a unitary renormalisation group calculation that decouples the high-energy modes of the conduction bath and incorporates their effects in the form of renormalised Hamiltonian couplings.
+We find that the bath interaction \(W\) remains marginal (does not undergo any renormalisation), while the renormalisation in the momentum-resolved Kondo coupling \(J^{(j)}\) at the \(j^\text{th}\) step is of the form
+\begin{equation}\begin{aligned}\label{KondoRGequation}
+	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}~,
+\end{aligned}\end{equation}
+where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, and the sum is over all momentum states \({\bf q}\) in the particle sector (PS) of the shell \(\varepsilon_j\) (that is, all states that are occupied at \(T=0\) and in the absence of any quantum fluctuations).
+We now consider some specific cases of these results.
+
+\subsubsection{Same symmetries in the Kondo coupling and bath interaction}
+Assuming that both the Kondo interaction and the bath interaction couple to the \(d-\)wave channel, we have the microscopic functional forms 
+\begin{equation}\begin{aligned}
+	J^{(0)}_{{\bf k},{\bf q}} &= J f_\mathcal{D}({\bf k}) f_\mathcal{D}({\bf q})~,\\
+	J^{(0)}_{{\bf \bar q},{\bf q}} &= J f_\mathcal{D}(\pi + {\bf q}) f_\mathcal{D}({\bf q}) = -Jf_\mathcal{D}({\bf q})^2 ~,
+\end{aligned}\end{equation}
+and
+\begin{equation}\begin{aligned}
+	W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} = -W f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf q})^2~,
+\end{aligned}\end{equation}
+where \(f_\mathcal{D}({\bf k}) = \cos\left( ak_{x} \right) - \cos\left( ak_y \right) \) is the \(d-\)wave symmetric functional form in \(k-\)space
+The numerator of the RG equations becomes
+\begin{equation}\begin{aligned}
+	f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf q})^4\left[J^2 + 4JW\right] ~.
+\end{aligned}\end{equation}
+Since a factor of \(f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)\) factors out of the RG equation, the Kondo coupling will preserve its momentum dependence during the RG equation, and we can study the RG flow of the amplitude \(J\):
+\begin{equation}\begin{aligned}
+	\Delta J = \sum_{{\bf q} \in \text{PS}} \frac{-\left(J^2 + 4JW\right) f_\mathcal{D}({\bf q})^4}{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{2}f_\mathcal{D}({\bf q})^4}~.
+\end{aligned}\end{equation}
+
+\subsubsection{Different symmetries in the Kondo coupling and bath interaction}
+One can also study the case when the bath interaction has \(p-\)wave symmetry:
+\begin{equation}\begin{aligned}
+	W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} =& \frac{1}{2}W f_\mathcal{P}\left(\pi + {\bf q}, {\bf k}_2, {\bf k}_1, {\bf q}\right) ~,\\
+	=& -\frac{1}{2}Wf_\mathcal{P}\left({\bf k}_1, {\bf k}_2\right)~.
+\end{aligned}\end{equation}
+This choice does not preserve the momentum-dependence of the Kondo coupling, because we can no longer pull out a factor of \(f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)\) from the RG equation.
+At the first step, the RG equation is of the form
+\begin{equation}\begin{aligned}
+	&\Delta J^{(0)}_{{\bf k}_1, {\bf k}_2} =\\
+	&-\sum_{{\bf q} \in \text{PS}} \frac{f_\mathcal{D}({\bf q})^2\left[{J}^2 f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1) + 2JW f_\mathcal{P}\left({\bf k}_1, {\bf k}_2\right)\right] }{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{4}}~.
+\end{aligned}\end{equation}
+The presence of the \(f_\mathcal{P}\) function in the second term leads to a new \(k-\)space dependence of the Kondo coupling at the second step, hence leading to a modified RG equation if one makes the \(k-\)dependence explicit.
 
@@
 In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout.
+
 In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})\).
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{pWaveEsiam.pdf}
+	\includegraphics[width=0.3\textwidth]{pWaveEsiam.pdf}
 	\caption{Caption.}
@@
 
-\textbf{Arising from the Kondo spin-exchange term}
+\subsubsection*{Arising from the Kondo spin-exchange term}
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-\textbf{Arising from spin-preserving scattering within conduction bath}
+\subsubsection*{Arising from spin-preserving scattering within conduction bath}
 \begin{equation}\begin{aligned}
 	T_{P1}^\dagger + T_{P1} &= -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3, {\bf k}_4 < \varepsilon_j}\sum_{\sigma} \left[W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4}c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} + \text{h.c.}\right]\\
-	T_{P2}^\dagger + T_{P3} &= -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2 < \varepsilon_j}\sum_{\sigma} W_{{\bf q},{\bf k}_2,{\bf \bar q}, {\bf \bar q}} c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma} n_{{\bf \bar q},\sigma} -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_1 < \varepsilon_j}\sum_{\sigma} W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}} c^\dagger_{{\bf k}_1,\sigma}c_{{\bf q},\sigma} n_{{\bf q},\sigma}
-\end{aligned}\end{equation}
-\textbf{Arising from spin-flip scattering within conduction bath}
+	T_{P2}^\dagger + T_{P3} &= -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2 < \varepsilon_j}\sum_{\sigma} W_{{\bf q},{\bf k}_2,{\bf \bar q}, {\bf \bar q}} c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma} n_{{\bf \bar q},\sigma} -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_1 < \varepsilon_j}\sum_{\sigma} W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}} c^\dagger_{{\bf k}_1,\sigma}c_{{\bf q},\sigma} n_{{\bf q},\sigma}\\
+	T_{P4} &= -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3 < \varepsilon_j}\sum_{\sigma}W_{{\bf q},{\bf \bar q},{\bf k}_2,{\bf k}_3} c^\dagger_{{\bf q},\sigma}c_{{\bf \bar q},\sigma}c^\dagger_{{\bf k}_2,\sigma}c_{{\bf k}_3,\sigma}\\
+	T_{P5} &= -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3 < \varepsilon_j}\sum_{\sigma} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf \bar q}} c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\sigma}c_{{\bf \bar q},\sigma}\\
+		   &= +\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3 < \varepsilon_j}\sum_{\sigma} W_{{\bf q},{\bf k}_3,{\bf k}_2,{\bf \bar q}} c^\dagger_{{\bf q},\sigma}c_{{\bf \bar q},\sigma}c^\dagger_{{\bf k}_2,\sigma}c_{{\bf k}_3,\sigma}\\
+		   &= -T_{P4}
+\end{aligned}\end{equation}
+\subsubsection*{Arising from spin-flip scattering within conduction bath}
 \begin{equation}\begin{aligned}
@@
 In all of the terms \(T_{P[i]}\) and \(T_{F[i]}\), the factor of \(1/2\) in front has been cancelled out by a factor of 2 coming from the multiple possibilities of arranging the momentum labels.
+We will henceforth ignore \(T_{P4}\) and \(T_{P5}\) because they cancel each other out.
 
@@
 
-\paragraph*{Scattering arising purely from spin-preserving processes}
+\subsubsection*{Scattering arising purely from spin-preserving processes}
 In this subsection, we calculate the renormalisation to \(W\) arising from the terms \(T_{P1}\), \(T_{P2}\) and \(T_{P3}\). The first term is
@@
 
-\paragraph*{Scattering arising from spin-flip processes}
+\subsubsection*{Scattering arising from spin-flip processes}
 We now come to the processes that involve spin-flips. Considering \(T_{F1}\) and \(T_{F4}\) first, we get
@@
 
-\paragraph*{Scattering involving both spin-flip and spin-preserving processes}
+\subsubsection*{Scattering involving both spin-flip and spin-preserving processes}
 These processes involve the combination of terms like \(T_{P1}\) with \(T_{F4}\), and \(T_{P2}\) with \(T_{F1}\). These again cancel each other out for the same reasons as outline above.
 
-\paragraph*{Net renormalisation for the bath correlation term}
+\subsubsection*{Net renormalisation for the bath correlation term}
 Since all the contributions cancel out in pairs, the bath correlation term \(W\) is {\it marginal}.
@@
 For these processes, the intermediate many-body state always involves the impurity spin being anti-correlated with the conduction electron spin, such that the propagator for that state is \(G_J = 1/\left(\omega - |\varepsilon_j|/2 + J_{\bf q}/4 + W_{\bf q}/2)\right) \).
-\paragraph*{Impurity-mediated spin-flip scattering purely through Kondo-like processes}
+\subsubsection*{Impurity-mediated spin-flip scattering purely through Kondo-like processes}
 The following processes arising from the Kondo term renormalise the spin-flip interaction:
@@
 
-\paragraph*{Scattering processes involving interplay between the Kondo interaction and conduction bath interaction}
+\subsubsection*{Scattering processes involving interplay between the Kondo interaction and conduction bath interaction}
 Looking at \(T_{KT1}^\dagger\) first, we have
@@
 
-\paragraph*{Net renormalisation to the Kondo interaction}
-Combining the results from eqs.~\ref{kondoRenorm1}, \ref{kondoRenorm2}, \ref{kondoRenorm3} and \ref{kondoRenorm4}, as well as using the properties \(J_{{\bf \bar q}, {\bf k}_1} J_{{\bf k}_2,{\bf \bar q}} = J_{{\bf q}, {\bf k}_2} J_{{\bf k}_1,{\bf q}}\) and \(J_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} = J_{{\bf \bar q}, {\bf q}} W_{{\bf q}, {\bf k}_2, {\bf k}_1, {\bf \bar q}}\), the total renormalisation in the momentum-resolved Kondo coupling \(J^{(j)}\) at the \(j^\text{th}\) step amounts to
-\begin{equation}\begin{aligned}
-	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{\frac{1}{2}\left(J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + J^{(j)}_{{\bf k}_1,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_2}\right) + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}
+\subsubsection*{Net renormalisation to the Kondo interaction}
+Combining the results from eqs.~\ref{kondoRenorm1}, \ref{kondoRenorm2}, \ref{kondoRenorm3} and \ref{kondoRenorm4}, as well as using the properties \(J_{{\bf \bar q}, {\bf k}_1} J_{{\bf k}_2,{\bf \bar q}} = J_{{\bf q}, {\bf k}_2} J_{{\bf k}_1,{\bf q}} = J_{{\bf k}_2, {\bf q}} J_{{\bf q},{\bf k}_1}\) and \(J_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} = J_{{\bf \bar q}, {\bf q}} W_{{\bf q}, {\bf k}_2, {\bf k}_1, {\bf \bar q}}\), the total renormalisation in the momentum-resolved Kondo coupling \(J^{(j)}\) at the \(j^\text{th}\) step amounts to
+\begin{equation}\begin{aligned}
+	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}
 \end{aligned}\end{equation}

### 2024-03-27 dwaveNumerics/multiOrbKondoRGFlow.jl

@@ -10,7 +10,7 @@ tightBindDispersion(t::Float64, kx_arr_flat::Array{Float64}, ky_arr_flat::Array{
 
 # d-wave and p-wave generation functions
 dwaveKdep(kx::Float64, ky::Float64) = cos.(kx) - cos.(ky)
-pwaveKdep(kx_arr::Vector{Float64}, ky_arr::Vector{Float64}) = cos(kx_arr[1] - kx_arr[2] + kx_arr[3] - kx_arr[4]) + cos(ky_arr[1] - ky_arr[2] + ky_arr[3] - ky_arr[4])
+pwaveKdep(kx_arr::Vector, ky_arr::Vector) = cos.(kx_arr[1] .- kx_arr[2] .+ kx_arr[3] .- kx_arr[4]) .+ cos.(ky_arr[1] .- ky_arr[2] .+ ky_arr[3] .- ky_arr[4])
 
 function getdensityOfStates(num_kspace::Int64, dispersionArray::Vector{Float64})
 	# momentum space interval is 2pi/N
@@ -65,27 +65,31 @@ end
 
 function stepwiseRenormalisation(innerIndicesArr::Vector{Int64}, energyCutoff::Float64, cutoffPoints::Vector{Int64}, proceed_flags::Matrix{Int64}, kondoJArrayPrev::Array{Float64, 2}, kondoJArrayNext::Array{Float64, 2}, bathInt, num_kspace::Int64, deltaEnergy::Float64, densityOfStates::Vector{Float64})
     omega = -abs(energyCutoff) / 2
+    denominators = [omega - abs(energyCutoff) / 2 + kondoJArrayPrev[qpoint, qpoint] / 4 + 
+            bathInt(qpoint, qpoint, qpoint, qpoint) / 2 for qpoint in cutoffPoints]
+    
+    # only consider those terms whose denominator haven't gone through zeros
+    cutoffPoints = cutoffPoints[denominators .< 0]
+    denominators = denominators[denominators .< 0]
+    # println(length(cutoffPoints))
+    # println(diag(kondoJArrayPrev[cutoffPoints, cutoffPoints]) .* bathInt(cutoffPoints, cutoffPoints, innerIndicesArr[1], innerIndicesArr[2]))
+    # println(kondoJArrayPrev[innerIndicesArr[1], cutoffPoints] .* kondoJArrayPrev[innerIndicesArr[2], cutoffPoints])
[…]

### 2024-03-28 TilingProjectDraft/tilingProject.tex
rewrote k-space RG in python

@@
 \begin{equation}\begin{aligned}
-	\mathcal{H} &= \mathcal{H}_S\ket{S}\bra{S} + \mathcal{H}_R \ket{R}\bra{R} + \mathcal{H}_{SR} \ket{S}\bra{R} + \mathcal{H}_{RS}\ket{S}\bra{R} \\
-		    &= \begin{bmatrix} & \mathcal{H}_{R} && \mathcal{H}_{RS} & \\ & \mathcal{H}_{RS}^* && \mathcal{H}_{S} & \end{bmatrix}
+	\mathcal{H} &= \mathcal{H}_S\ket{S}\bra{S} + \mathcal{H}_R \ket{R}\bra{R} + \mathcal{H}_{SR} \ket{S}\bra{R} \\
+				&+ \mathcal{H}_{RS}\ket{S}\bra{R} = \begin{bmatrix} & \mathcal{H}_{R} && \mathcal{H}_{RS} & \\ & \mathcal{H}_{RS}^* && \mathcal{H}_{S} & \end{bmatrix}
 \end{aligned}\end{equation}
 where \(\ket{S}\) and \(\ket{R}\) actually represents sums over all basis kets of \(S\) and \(R\) respectively.
-As an example, we can split the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice as follows (fig.~\ref{cluster-bath}):
-\begin{widetext}
-\begin{equation}\begin{aligned}
-	H_\text{hubb} &= \overbrace{U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}}^{H_S} + \underbrace{U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} -t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right)}_{H_R} -\underbrace{t^H\sum_{\sigma,\atop{i \in \text{N.N.
-of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)}_{H_{SR} + H_{RS}}\\
-\end{aligned}\end{equation}
-\end{widetext}
+As an example, we can split the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice into three parts \(H_\text{hubb} = H_S + H_R + H_{SR} + H_{RS}\) (fig.~\ref{cluster-bath}), where
+\begin{equation}\begin{aligned}
+	H_S &= U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}\\
+	H_R &= U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} \\
+		&-t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right) \\
+	H_{SR} + H_{Rs} &= - t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)~.
+\end{aligned}\end{equation}
 The Greens function of the full Hamiltonian can also be split in a similar fashion:
@@
 	J^{(0)}_{{\bf k},{\bf q}} &= J f_\mathcal{D}({\bf k}) f_\mathcal{D}({\bf q})~,\\
-	J^{(0)}_{{\bf \bar q},{\bf q}} &= J f_\mathcal{D}(\pi + {\bf q}) f_\mathcal{D}({\bf q}) = -Jf_\mathcal{D}({\bf q})^2 ~,
+	J^{(0)}_{{\bf \bar q},{\bf q}} &= J f_\mathcal{D}(\pi + {\bf q}) f_\mathcal{D}({\bf q}) = Jf_\mathcal{D}({\bf q})^2 ~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} = -W f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf q})^2~,
+	W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} = W f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf q})^2~,
 \end{aligned}\end{equation}
@@
 	&\Delta J^{(0)}_{{\bf k}_1, {\bf k}_2} =\\
-	&-\sum_{{\bf q} \in \text{PS}} \frac{f_\mathcal{D}({\bf q})^2\left[{J}^2 f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1) + 2JW f_\mathcal{P}\left({\bf k}_1, {\bf k}_2\right)\right] }{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{4}}~.
+	&-\sum_{{\bf q} \in \text{PS}} \frac{f_\mathcal{D}({\bf q})^2\left[{J}^2 f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1) - 2JW f_\mathcal{P}\left({\bf k}_1, {\bf k}_2\right)\right] }{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{4}}~.
 \end{aligned}\end{equation}
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{luttinger_top_change.png}
+	\includegraphics[width=0.4\textwidth]{windingNumbers.pdf}
 	\caption{The green lines describe the winding number related to the impurity Greens function, while the blue lines do it for the bath.

### 2024-03-28 dwaveNumerics/multiOrbKondoRGFlow.py

@@ -1,0 +1,222 @@
+import numpy as np
+from itertools import product
+from tqdm import tqdm
+from multiprocessing import Pool
+
+K_MIN = -np.pi
+K_MAX = np.pi
+
+
+def getHolePoint(point, size):
+    kx_val, ky_val = map1Dto2D(point, size)
+    kx_new = (
+        kx_val + (K_MAX - K_MIN) / 2
+        if kx_val < (K_MAX + K_MIN) / 2
+        else kx_val - (K_MAX - K_MIN) / 2
+    )
+    ky_new = (
+        ky_val + (K_MAX - K_MIN) / 2
+        if ky_val < (K_MAX + K_MIN) / 2
+        else ky_val - (K_MAX - K_MIN) / 2
+    )
+    new_point = map2Dto1D(kx_new, ky_new, size)
+    return new_point
+
+
+def bathIntFunc(k_points, bathIntType, size):
+    assert bathIntType in ("d", "p")
+    k_points = np.asarray(k_points)
+    kx_arr, ky_arr = map1Dto2D(k_points, size)
+    if bathIntType == "d":
+        return np.prod(np.cos(kx_arr) - np.cos(ky_arr))
+    else:
+        return 0.5 * (
+            np.cos(kx_arr[0] + kx_arr[2] - kx_arr[1] - kx_arr[3])
+            + np.cos(ky_arr[0] + ky_arr[2] - ky_arr[1] - ky_arr[3])
+        )
+
+
+def map2Dto1D(kx_val, ky_val, size):
+    k_1Darr = np.linspace(K_MIN, K_MAX, size)
+    kx_index = np.argmin(np.abs(k_1Darr - kx_val))
+    ky_index = np.argmin(np.abs(k_1Darr - ky_val))
+    return ky_index * size + kx_index
+
+
+def map1Dto2D(points, size):
+    kx = points % size
+    ky = points // size
+    k_1Darr = np.linspace(K_MIN, K_MAX, size)
+    return k_1Darr[kx], k_1Darr[ky]
+
+
+def tightBindDispersion(size, hop_t):
+    k_1Darr = np.linspace(K_MIN, K_MAX, size)
+    kx_arr, ky_arr = np.meshgrid(k_1Darr, k_1Darr)
+    return -2 * hop_t * (np.cos(kx_arr) + np.cos(ky_arr))
+
+
+def getDensityofStates(size, dispersionFunc, hop_t):
[…]

### 2024-03-30 TilingProjectDraft/tilingProject.tex
added some symmetry results

@@
 where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, and the sum is over all momentum states \({\bf q}\) in the particle sector (PS) of the shell \(\varepsilon_j\) (that is, all states that are occupied at \(T=0\) and in the absence of any quantum fluctuations).
+The Kondo coupling and the RG equation as well have certain symmetries under transformations in the Brillouin zone.
+If any one of the momenta \({\bf k}_1\) or \({\bf k}_2\) are translated by \(\pi\) (\(k_{1x} \to k_{1x} + \pi, k_{1y} \to k_{1y}+\pi\)), the coupling as well as the RG equation changes sign.
+Translating both the momenta leads to the reversal of the sign change.
+\begin{equation}\begin{aligned}
+	\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2} = \Delta J^{(j)}_{{\bf k}_1, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2}~.
+\end{aligned}\end{equation}
+These transformations involve translating one or both momenta through the center of the Brillouin zone. Further symmetries are obtained by translating both momenta through the \(x-\) or \(y-\)axes:
+\begin{equation}\begin{aligned}
+	\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2} = \Delta J^{(j)}_{{\bf k}_1, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2}~.
+\end{aligned}\end{equation}
+
 We now consider some specific cases of these results.

### 2024-03-30 dwaveNumerics/probes.jl
further modularisation, for testing

@@ -125,7 +125,7 @@ function getInStateScattFlowBool(kondoJArray::Array{Float64,3}, num_kspace_half:
 end
 
 
-function getGlobalFlowBool(kondoJArray::Array{Float64,3}, num_kspace_half::Int64)
+function getGlobalFlowBool(kondoJArray::Array{Float64,3}, num_kspace_half::Int64, stepIndex::Int64)
     num_kspace = 2 * num_kspace_half + 1
     bare_J_squared = reshape(
         diag(kondoJArray[:, :, 1] * kondoJArray[:, :, 1]'),
@@ -134,7 +134,7 @@ function getGlobalFlowBool(kondoJArray::Array{Float64,3}, num_kspace_half::Int64
     results =
         sign.(
             reshape(
-                diag(kondoJArray[:, :, end] * kondoJArray[:, :, end]'),
+                diag(kondoJArray[:, :, stepIndex] * kondoJArray[:, :, stepIndex]'),
                 (num_kspace, num_kspace),
             ) .- bare_J_squared
         )
@@ -142,7 +142,7 @@ function getGlobalFlowBool(kondoJArray::Array{Float64,3}, num_kspace_half::Int64
 end
 
 
-function getGlobalFlow(kondoJArray::Array{Float64,3}, num_kspace_half::Int64)
+function getGlobalFlow(kondoJArray::Array{Float64,3}, num_kspace_half::Int64, stepIndex::Int64)
     num_kspace = 2 * num_kspace_half + 1
     bare_J_squared = reshape(
         diag(kondoJArray[:, :, 1] * kondoJArray[:, :, 1]'),
@@ -150,7 +150,7 @@ function getGlobalFlow(kondoJArray::Array{Float64,3}, num_kspace_half::Int64)
     )
     results =
         reshape(
-            diag(kondoJArray[:, :, end] * kondoJArray[:, :, end]'),
+            diag(kondoJArray[:, :, stepIndex] * kondoJArray[:, :, stepIndex]'),
             (num_kspace, num_kspace),
         ) ./ bare_J_squared
     return results

### 2024-03-30 dwaveNumerics/mOrbRG.jl
corrections

@@ -142,9 +142,9 @@ function initialiseKondoJ(num_kspace, orbital, num_steps, J_init)
             k2x, k2y = map1DTo2D(p2, num_kspace)
             if orbital == "d"
                 kondoJArray[p1, p2, 1] =
-                    J_init * (cos(k1x) - cos(k1y) + cos(k2x) - cos(k2y))
+                J_init * (cos(k1x) - cos(k1y)) * (cos(k2x) - cos(k2y))
             else
-                kondoJArray[p1, p2, 1] = J_init * (cos(k1x - k2x) + cos(k1y - k2y))
+                kondoJArray[p1, p2, 1] = 0.5 * J_init * (cos(k1x - k2x) + cos(k1y - k2y))
             end
         end
     end
@@ -175,7 +175,8 @@ function main(num_kspace_half::Int64, J_init::Float64, bathIntStr::Float64, orbi
     # incoming and outgoing momentum indices, while the third dimension stores the 
     # behaviour along the RG flow. For example, J[i][j][k] reveals the value of J 
     # for the momentum pair (i,j) at the k^th Rg step.
-    kondoJArray = initialiseKondoJ(num_kspace, orbital, length(cutOffEnergies), J_init) #Array{Float64}(undef, num_kspace^2, num_kspace^2, length(cutOffEnergies))
+    kondoJArray = initialiseKondoJ(num_kspace, orbital, length(cutOffEnergies), J_init) 
+    #kondoJArray = Array{Float64}(undef, num_kspace^2, num_kspace^2, length(cutOffEnergies))
 
     # bare value of J is given by J(k1, k2) = J_init × [cos(k1x) - cos(k1y)] × [cos(k2x) - cos(k2y)] 
     # Threads.@threads for p1 = 1:num_kspace^2
@@ -208,7 +209,8 @@ function main(num_kspace_half::Int64, J_init::Float64, bathIntStr::Float64, orbi
         cutoffPoints = getIsoEngCont(dispersionArray, energyCutoff)
 
         # these cutoff points will no longer participate in the RG flow, so disable their flags
-        proceed_flags[cutoffPoints, :] .= proceed_flags[:, cutoffPoints] .= 0
+        proceed_flags[cutoffPoints, :] .= 0
+        proceed_flags[:, cutoffPoints] .= 0
 
         # if there are no enabled flags (i.e., all are zero), stop the RG flow
         if all(==(0), proceed_flags)

### 2024-03-30 dwaveNumerics/Tests/test_helpers.jl
started writing tests

@@ -1,0 +1,41 @@
+using Test
+include("../source/helpers.jl")
+include("../source/constants.jl")
+
+const SIZE_BZ = [3, 101, 1001]
+const KX_VALUES = [K_MIN, K_MAX, K_MIN, K_MAX, 0]
+const KY_VALUES = [K_MIN, K_MIN, K_MAX, K_MAX, 0]
+
+POINTS(num_kspace) = [
+    1,
+    num_kspace,
+    num_kspace^2 - num_kspace + 1,
+    num_kspace^2,
+    Int(0.5 * num_kspace^2 + 0.5),
+]
+
+@testset "Mapping 1D To 2D" begin
+    @testset for num_kspace in SIZE_BZ
+        points_subset = POINTS(num_kspace)
+        @testset for (test, testPoint) in enumerate(points_subset)
+            @test map1DTo2D(testPoint, num_kspace) ≈ [KX_VALUES[test], KY_VALUES[test]]
+        end
+        @test map1DTo2D(points_subset, num_kspace) ≈ [KX_VALUES, KY_VALUES]
+    end
+end
+
+@testset "Mapping 2D To 1D" begin
+    @testset for num_kspace in SIZE_BZ
+        points_subset = POINTS(num_kspace)
+        @testset for test in eachindex(KX_VALUES)
+            @test map2DTo1D(KX_VALUES[test], KY_VALUES[test], num_kspace) ≈ points_subset[test]
+        end
+        @test map2DTo1D(KX_VALUES, KY_VALUES, num_kspace) ≈ points_subset
+    end
+end
+
+
+@testset "Tight-binding Dispersion" begin
+    @test tightBindDisp(KX_VALUES, KY_VALUES) == [tightBindDisp(kx, ky) for (kx, ky) in zip(KX_VALUES, KY_VALUES)]
+end
+

### 2024-03-30 dwaveNumerics/source/helpers.jl

@@ -46,6 +46,9 @@ end
 function tightBindDisp(kx_vals::Vector{Float64}, ky_vals::Vector{Float64})
     return -2 * HOP_T .* (cos.(kx_vals) + cos.(ky_vals))
 end
+function tightBindDisp(kx_val::Float64, ky_val::Float64)
+    return -2 * HOP_T .* (cos.(kx_val) + cos.(ky_val))
+end
 
 
 function teleportToAllQuads(point::Int64, num_kspace::Int64)

### 2024-04-04 TilingProjectDraft/tilingProject.tex
modularised plotting components

@@
 \end{aligned}\end{equation}
-These transformations involve translating one or both momenta through the center of the Brillouin zone. Further symmetries are obtained by translating both momenta through the \(x-\) or \(y-\)axes:
-\begin{equation}\begin{aligned}
-	\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2} = \Delta J^{(j)}_{{\bf k}_1, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2}~.
-\end{aligned}\end{equation}
+These transformations involve translating one or both momenta through the center of the Brillouin zone.
 
 We now consider some specific cases of these results.
-
-\subsubsection{Same symmetries in the Kondo coupling and bath interaction}
+\paragraph{Same symmetries in the Kondo coupling and bath interaction}
 Assuming that both the Kondo interaction and the bath interaction couple to the \(d-\)wave channel, we have the microscopic functional forms 
@@
 \begin{equation}\begin{aligned}
-	f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf q})^4\left[J^2 + 4JW\right] ~.
+	f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf q})^2\left[J^2 + 4JWf_\mathcal{D}({\bf q})^2\right] ~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Delta J = \sum_{{\bf q} \in \text{PS}} \frac{-\left(J^2 + 4JW\right) f_\mathcal{D}({\bf q})^4}{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{2}f_\mathcal{D}({\bf q})^4}~.
-\end{aligned}\end{equation}
-
-\subsubsection{Different symmetries in the Kondo coupling and bath interaction}
+	\Delta J = \sum_{{\bf q} \in \text{PS}} \frac{-f_\mathcal{D}({\bf q})^2\left[J^2 + 4JWf_\mathcal{D}({\bf q})^2\right]}{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{2}f_\mathcal{D}({\bf q})^4}~.
+\end{aligned}\end{equation}
+
+\paragraph{Different symmetries in the Kondo coupling and bath interaction}
 One can also study the case when the bath interaction has \(p-\)wave symmetry:

### 2024-04-04 dwaveNumerics/Tests/test_helpers.jl

@@ -2,22 +2,22 @@ using Test
 include("../source/helpers.jl")
 
 @testset "Mapping 1D To 2D" begin
-    @testset for num_kspace in SIZE_BZ
-        points_subset = POINTS(num_kspace)
+    @testset for size_BZ in SIZE_BZ
+        points_subset = POINTS(size_BZ)
         @testset for (test, testPoint) in enumerate(points_subset)
-            @test map1DTo2D(testPoint, num_kspace) ≈ [KX_VALUES[test], KY_VALUES[test]]
+            @test map1DTo2D(testPoint, size_BZ) ≈ [KX_VALUES[test], KY_VALUES[test]]
         end
-        @test map1DTo2D(points_subset, num_kspace) ≈ [KX_VALUES, KY_VALUES]
+        @test map1DTo2D(points_subset, size_BZ) ≈ [KX_VALUES, KY_VALUES]
     end
 end
 
 @testset "Mapping 2D To 1D" begin
-    @testset for num_kspace in SIZE_BZ
-        points_subset = POINTS(num_kspace)
+    @testset for size_BZ in SIZE_BZ
+        points_subset = POINTS(size_BZ)
         @testset for test in eachindex(KX_VALUES)
-            @test map2DTo1D(KX_VALUES[test], KY_VALUES[test], num_kspace) ≈ points_subset[test]
+            @test map2DTo1D(KX_VALUES[test], KY_VALUES[test], size_BZ) ≈ points_subset[test]
         end
-        @test map2DTo1D(KX_VALUES, KY_VALUES, num_kspace) ≈ points_subset
+        @test map2DTo1D(KX_VALUES, KY_VALUES, size_BZ) ≈ points_subset
     end
 end
 

### 2024-04-04 dwaveNumerics/Tests/test_probes.jl

@@ -6,16 +6,7 @@ include("../source/helpers.jl")
 
 @testset "Flow of totalScatterProb" begin
     kondoJArray = rand(Float64, (SIZE_BZ[1]^2, SIZE_BZ[1]^2, 3))
-    filePath = randstring(15)
-    results_norm, results_unnorm, results_bool = totalScatterProb(kondoJArray, 3, filePath)
-    @test isfile(filePath)
-    @test isfile(filePath * "-bool")
-    if isfile(filePath)
-        rm(filePath)
-    end
-    if isfile(filePath * "-bool")
-        rm(filePath * "-bool")
-    end
+    results_norm, results_unnorm, results_bool = scattProb(kondoJArray, 3)
     @testset for p1 in 1:SIZE_BZ[1]^2
         @test results_unnorm[p1] ≈ sum([kondoJArray[p1, p2, 3]^2 for p2 in 1:SIZE_BZ[1]^2]) atol = 1e-10
         @test results_bool[p1] == tolerantSign(sum([kondoJArray[p1, p2, 3]^2 for p2 in 1:SIZE_BZ[1]^2]), sum([kondoJArray[p1, p2, 1]^2 for p2 in 1:SIZE_BZ[1]^2]))

### 2024-04-04 dwaveNumerics/Tests/test_rgflow.jl

@@ -27,30 +27,30 @@ end
 end
 
 
-function kondoArraySymmetriesCheck(kondoJArray, orbital, num_kspace)
+function kondoArraySymmetriesCheck(kondoJArray, orbital, size_BZ)
     if orbital == "p"
         # check that the diagonal elements J(k,k) are all unity for the p-wave case
         @test all(diag(kondoJArray[:, :]) .== 1)
     else
         # check that J(k_1,k_2) is zero if k1 and k2 are on the 
         # kx=ky lines, for the d-wave case
-        kx_equals_ky = [1:num_kspace+1:num_kspace^2;
-            num_kspace^2-num_kspace+1:num_kspace-1:num_kspace]
+        kx_equals_ky = [1:size_BZ+1:size_BZ^2;
+            size_BZ^2-size_BZ+1:size_BZ-1:size_BZ]
         @testset for (p1, p2) in Iterators.product(kx_equals_ky, kx_equals_ky)
             @test kondoJArray[p1, p2] ≈ 0 atol = 1e-10
         end
     end
 
     # J(k,q_x=0,q_y) == J(k,q_x=2π,q_y)
-    @test kondoJArray[1:num_kspace:num_kspace^2-num_kspace+1, :] ≈ kondoJArray[num_kspace:num_kspace:num_kspace^2, :] atol = 1e-10
+    @test kondoJArray[1:size_BZ:size_BZ^2-size_BZ+1, :] ≈ kondoJArray[size_BZ:size_BZ:size_BZ^2, :] atol = 1e-10
 
     # J(k,q_y=0,q_x) == J(k,q_y=2π,q_x)
-    @test kondoJArray[1:1:num_kspace, :] ≈ kondoJArray[num_kspace^2-num_kspace+1:1:num_kspace^2, :] atol = 1e-10
+    @test kondoJArray[1:1:size_BZ, :] ≈ kondoJArray[size_BZ^2-size_BZ+1:1:size_BZ^2, :] atol = 1e-10
 
     # J(k,q) == -J(k,q+π)
-    @testset for p1 in 1:num_kspace^2
-        for p2 in 1:num_kspace^2
-            @test kondoJArray[p1, p2] ≈ -kondoJArray[p1, particleHoleTransf(p2, num_kspace)] atol = 1e-10
+    @testset for p1 in 1:size_BZ^2
+        for p2 in 1:size_BZ^2
[…]

### 2024-04-04 dwaveNumerics/caller.jl

@@ -1,55 +1,0 @@
-#### IMPORTS ####
-using Distributed
-addprocs(parse(Int, ARGS[8]))
-
-using SharedArrays
-@everywhere using ProgressMeter
-@everywhere using Plots
-@everywhere using Measures
-@everywhere using LaTeXStrings
-@everywhere using DelimitedFiles
-@everywhere include("source/mOrbRG.jl")
-@everywhere include("source/probes.jl")
-const SIZE = (750, 300)
-scale = 1.5
-discreteCgrad = cgrad(:BuPu_3, 3, categorical=true, rev=true)
-animName(orbital, num_kspace, scale, W_by_J_max, W_by_J_min) = "kondoUb_kspaceRG_$(orbital)_wave_$(num_kspace)_$(round(W_by_J_min, digits=3))_$(round(W_by_J_max, digits=3))_$(SIZE[1] * scale)x$(SIZE[2] * scale)"
-
-function getRgFlow(num_kspace_half, J_val, W_by_J_range, orbitals)
-    num_kspace = 2 * num_kspace_half + 1
-    k_vals = collect(range(K_MIN, K_MAX, length=num_kspace)) ./ pi
-    results1_arr = SharedArray{Float64}(length(W_by_J_range), num_kspace * num_kspace)
-    results2_arr = SharedArray{Float64}(length(W_by_J_range), num_kspace * num_kspace)
-    @time @sync @distributed for (j, W_by_J) in collect(enumerate(W_by_J_range))
-        savePath = "data/$(orbitals[1])_$(num_kspace_half)_$(round(J_val, digits=3))_$(round(W_by_J, digits=3))"
-        kondoJArray, _ = main(num_kspace_half, J_val, J_val * W_by_J, orbitals[1], orbitals[2])
-        _, results_unnorm, results_bool = totalScatterProb(kondoJArray, num_kspace_half + 1, savePath)
-        results1_arr[j, :] = results_bool
-        results2_arr[j, :] = results_unnorm
-    end
-    max_r = maximum(log10.(results2_arr))
-    min_r = minimum(log10.(results2_arr))
-    pdfFileNames = []
-    anim = @animate for (j, W_by_J) in enumerate(W_by_J_range)
-        hm1 = heatmap(k_vals, k_vals, results1_arr[j, :, :],
-            cmap=discreteCgrad)
[…]

### 2024-04-04 dwaveNumerics/source/helpers.jl

@@ -2,41 +2,41 @@ include("./constants.jl")
 
 # helper functions for switching back and forth between the 1D flattened representation (1 → N^2) 
 # and the 2D representation ((1 → N)×(1 → N))
-function map1DTo2D(point::Int64, num_kspace::Int64)
+function map1DTo2D(point::Int64, size_BZ::Int64)
     # Convert overall point to row and column values.
     # These serve as indices of kx and ky
-    kx_index = (point - 1) % num_kspace + 1
-    ky_index = div((point - 1), num_kspace) + 1
+    kx_index = (point - 1) % size_BZ + 1
+    ky_index = div((point - 1), size_BZ) + 1
 
     # construct a 1D array of possible k values, and convert
     # kx_index and ky_index into values
-    k_values = range(K_MIN, stop=K_MAX, length=num_kspace)
+    k_values = range(K_MIN, stop=K_MAX, length=size_BZ)
     return [k_values[kx_index], k_values[ky_index]]
 end
-function map1DTo2D(point::Vector{Int64}, num_kspace::Int64)
+function map1DTo2D(point::Vector{Int64}, size_BZ::Int64)
     # same as above, but for multiple points. In this case,
     # two tuples are returned, for kx values and ky values.
-    kx_index = (point .- 1) .% num_kspace .+ 1
-    ky_index = div.((point .- 1), num_kspace) .+ 1
-    k_values = range(K_MIN, stop=K_MAX, length=num_kspace)
+    kx_index = (point .- 1) .% size_BZ .+ 1
+    ky_index = div.((point .- 1), size_BZ) .+ 1
+    k_values = range(K_MIN, stop=K_MAX, length=size_BZ)
     return [k_values[kx_index], k_values[ky_index]]
 end
 
-function map2DTo1D(kx_val::Float64, ky_val::Float64, num_kspace::Int64)
+function map2DTo1D(kx_val::Float64, ky_val::Float64, size_BZ::Int64)
     # obtain the indices, given the values of kx and ky
-    k_values = range(K_MIN, stop=K_MAX, length=num_kspace)
+    k_values = range(K_MIN, stop=K_MAX, length=size_BZ)
[…]

### 2024-04-04 dwaveNumerics/source/mOrbRG.jl

@@ -1,34 +1,30 @@
 using ProgressMeter
 include("./rgFlow.jl")
 
-function main(num_kspace_half::Int64, J_init::Float64, bathIntStr::Float64, impOrbital::String, bathOrbital::String)
+function main(size_BZ::Int64, J_val::Float64, bathIntStr::Float64, orbitals::Vector{String})
     # ensure that [0, \pi] has odd number of states, so 
     # that the nodal point is well-defined.
-    @assert num_kspace_half % 2 == 0
+    @assert size_BZ != 0
 
     # ensure that the choice of orbitals is d or p
+    impOrbital, bathOrbital = orbitals
     @assert bathOrbital in ["p", "d", "poff"]
     @assert impOrbital in ["p", "d", "poff"]
 
-    # num_kspace_half is the number of points from 0 until pi,
-    # so that the total number of k-points along an axis is 
-    # num_kspace_half(for [antinode, pi)) + 1(for node) + num_kspace_half(for (node, antinode])
-    num_kspace = 2 * num_kspace_half + 1
+    densityOfStates, dispersionArray = getDensityOfStates(tightBindDisp, size_BZ)
 
-    densityOfStates, dispersionArray = getDensityOfStates(tightBindDisp, num_kspace)
-
-    cutOffEnergies = getCutOffEnergy(num_kspace)
+    cutOffEnergies = getCutOffEnergy(size_BZ)
 
     # Kondo coupling must be stored in a 3D matrix. Two of the dimensions store the 
     # incoming and outgoing momentum indices, while the third dimension stores the 
     # behaviour along the RG flow. For example, J[i][j][k] reveals the value of J 
     # for the momentum pair (i,j) at the k^th Rg step.
-    kondoJArray = initialiseKondoJ(num_kspace, impOrbital, num_kspace_half + 1, J_init)
+    kondoJArray = initialiseKondoJ(size_BZ, impOrbital, trunc(Int, (size_BZ + 1) / 2), J_val)
 
     # define flags to track whether the RG flow for a particular J_{k1, k2} needs to be stopped 
     # (perhaps because it has gone to zero, or its denominator has gone to zero). These flags are
     # initialised to one, which means that by default, the RG can proceed for all the momenta.
-    proceed_flags = fill(1, num_kspace^2, num_kspace^2)
+    proceed_flags = fill(1, size_BZ^2, size_BZ^2)
 
[…]

### 2024-04-04 dwaveNumerics/source/probes.jl

@@ -1,13 +1,101 @@
 using LinearAlgebra
 using DelimitedFiles
+using Plots
 
-function totalScatterProb(kondoJArray::Array{Float64,3}, stepIndex::Int64, savePath::String)
+animName(orbitals, size_BZ, scale, W_by_J_min, W_by_J_max, J_val) = "kondoUb_kspaceRG_$(orbitals[1])_$(orbitals[2])_wave_$(size_BZ)_$(round(W_by_J_min, digits=4))_$(size_BZ)_$(round(W_by_J_max, digits=4))_$(round(J_val, digits=4))_$(SIZE[1] * scale)x$(SIZE[2] * scale)"
+discreteCgrad = cgrad(:BuPu_3, 3, categorical=true)
+
+function scattProb(kondoJArray::Array{Float64,3}, stepIndex::Int64)
     bare_J_squared = diag(kondoJArray[:, :, 1] * kondoJArray[:, :, 1]')
     results_unnorm = diag(kondoJArray[:, :, stepIndex] * kondoJArray[:, :, stepIndex]')
     results_norm = results_unnorm ./ bare_J_squared
     results_bool = [tolerantSign(results_norm_i, 1) for results_norm_i in results_norm]
-
-    writedlm(savePath, results_norm)
-    writedlm(savePath * "-bool", results_norm)
     return results_norm, results_unnorm, results_bool
+end
+
+
+function plotHeatmaps(results1, results2, k_vals, plots, cmap_left, titles)
+    minima = minimum.([results1, results2])
+    maxima = maximum.([results1, results2])
+    heatmap!(plots[1], k_vals, k_vals, results1,
+        cmap=cmap_left,
+        clims=(minima[1], maxima[1]),
+        title=titles[1],
+        titlefontsize=11
+    )
+    heatmap!(plots[2], k_vals, k_vals, results2,
+        cmap=:matter,
+        clims=(minima[2], maxima[2]),
+        title=titles[2],
+        titlefontsize=11
+    )
+    return plots
+end
+
+function manager(size_BZ::Int64, J_val::Float64, W_by_J_range::Vector{Float64}, orbitals::Vector{String}, probes::Vector{String}, figScale::Float64)
+    @assert size_BZ % 2 != 0
+    results_arr = zeros((length(probes), length(W_by_J_range), size_BZ^2))
[…]

### 2024-04-04 dwaveNumerics/source/rgFlow.jl

@@ -3,8 +3,8 @@ using ProgressMeter
 include("./helpers.jl")
 
 
-function getCutOffEnergy(num_kspace)
-    kx_pos_arr = collect(range(K_MIN, K_MAX, length=num_kspace))
+function getCutOffEnergy(size_BZ)
+    kx_pos_arr = collect(range(K_MIN, K_MAX, length=size_BZ))
     kx_holesector = kx_pos_arr[kx_pos_arr.>=0]
     cutOffEnergies = -tightBindDisp(kx_holesector, 0 .* kx_holesector)
     cutOffEnergies = cutOffEnergies[cutOffEnergies.>=-TOLERANCE]
@@ -12,11 +12,11 @@ function getCutOffEnergy(num_kspace)
 end
 
 
-function highLowSeparation(dispersionArray::Vector{Float64}, energyCutoff::Float64, proceed_flags::Matrix{Int64}, num_kspace::Int64)
+function highLowSeparation(dispersionArray::Vector{Float64}, energyCutoff::Float64, proceed_flags::Matrix{Int64}, size_BZ::Int64)
 
     # get the k-points that will be decoupled at this step, by getting the isoenergetic contour at the cutoff energy.
     cutoffPoints = unique(getIsoEngCont(dispersionArray, energyCutoff))
-    cutoffHolePoints = particleHoleTransf(cutoffPoints, num_kspace)
+    cutoffHolePoints = particleHoleTransf(cutoffPoints, size_BZ)
 
     # these cutoff points will no longer participate in the RG flow, so disable their flags
     proceed_flags[cutoffPoints, :] .= 0
@@ -30,12 +30,12 @@ function highLowSeparation(dispersionArray::Vector{Float64}, energyCutoff::Float
     innerIndicesArr = [
         point for (point, energy) in enumerate(dispersionArray) if
         abs(energy) < (abs(energyCutoff) - TOLERANCE) &&
-        map1DTo2D(point, num_kspace)[1] <= 0.5 * (K_MAX + K_MIN)
+        map1DTo2D(point, size_BZ)[1] <= 0.5 * (K_MAX + K_MIN)
     ]
     excludedIndicesArr = [
         point for (point, energy) in enumerate(dispersionArray) if
         abs(energy) < (abs(energyCutoff) - TOLERANCE) &&
-        map1DTo2D(point, num_kspace)[1] > 0.5 * (K_MAX + K_MIN)
[…]

### 2024-04-04 dwaveNumerics/source/mOrbRG.jl
reorganisation

@@ -1,66 +1,0 @@
-using ProgressMeter
-include("./rgFlow.jl")
-
-function main(size_BZ::Int64, J_val::Float64, bathIntStr::Float64, orbitals::Vector{String})
-    # ensure that [0, \pi] has odd number of states, so 
-    # that the nodal point is well-defined.
-    @assert size_BZ != 0
-
-    # ensure that the choice of orbitals is d or p
-    impOrbital, bathOrbital = orbitals
-    @assert bathOrbital in ["p", "d", "poff"]
-    @assert impOrbital in ["p", "d", "poff"]
-
-    densityOfStates, dispersionArray = getDensityOfStates(tightBindDisp, size_BZ)
-
-    cutOffEnergies = getCutOffEnergy(size_BZ)
-
-    # Kondo coupling must be stored in a 3D matrix. Two of the dimensions store the 
-    # incoming and outgoing momentum indices, while the third dimension stores the 
-    # behaviour along the RG flow. For example, J[i][j][k] reveals the value of J 
-    # for the momentum pair (i,j) at the k^th Rg step.
-    kondoJArray = initialiseKondoJ(size_BZ, impOrbital, trunc(Int, (size_BZ + 1) / 2), J_val)
-
-    # define flags to track whether the RG flow for a particular J_{k1, k2} needs to be stopped 
-    # (perhaps because it has gone to zero, or its denominator has gone to zero). These flags are
-    # initialised to one, which means that by default, the RG can proceed for all the momenta.
-    proceed_flags = fill(1, size_BZ^2, size_BZ^2)
-
-    # Run the RG flow starting from the maximum energy, down to the penultimate energy (ΔE), in steps of ΔE
-    @showprogress for (stepIndex, energyCutoff) in enumerate(cutOffEnergies[1:end-1])
-        deltaEnergy = abs(cutOffEnergies[stepIndex+1] - cutOffEnergies[stepIndex])
-
-        # set the Kondo coupling of all subsequent steps equal to that of the present step 
-        # for now, so that we can just add the renormalisation to it later
-        kondoJArray[:, :, stepIndex+1] = kondoJArray[:, :, stepIndex]
-
-        # if there are no enabled flags (i.e., all are zero), stop the RG flow
-        if all(==(0), proceed_flags)
-            kondoJArray[:, :, stepIndex+2:end] .= kondoJArray[:, :, stepIndex]
-            break
-        end
-
[…]

### 2024-04-04 dwaveNumerics/source/main.jl

@@ -1,0 +1,131 @@
+using ProgressMeter
+using Plots, Measures, LaTeXStrings
+include("./rgFlow.jl")
+include("./probes.jl")
+
+function momentumSpaceRG(size_BZ::Int64, J_val::Float64, bathIntStr::Float64, orbitals::Vector{String})
+    # ensure that [0, \pi] has odd number of states, so 
+    # that the nodal point is well-defined.
+    @assert size_BZ != 0
+
+    # ensure that the choice of orbitals is d or p
+    impOrbital, bathOrbital = orbitals
+    @assert bathOrbital in ["p", "d", "poff"]
+    @assert impOrbital in ["p", "d", "poff"]
+
+    densityOfStates, dispersionArray = getDensityOfStates(tightBindDisp, size_BZ)
+
+    cutOffEnergies = getCutOffEnergy(size_BZ)
+
+    # Kondo coupling must be stored in a 3D matrix. Two of the dimensions store the 
+    # incoming and outgoing momentum indices, while the third dimension stores the 
+    # behaviour along the RG flow. For example, J[i][j][k] reveals the value of J 
+    # for the momentum pair (i,j) at the k^th Rg step.
+    kondoJArray = initialiseKondoJ(size_BZ, impOrbital, trunc(Int, (size_BZ + 1) / 2), J_val)
+
+    # define flags to track whether the RG flow for a particular J_{k1, k2} needs to be stopped 
+    # (perhaps because it has gone to zero, or its denominator has gone to zero). These flags are
+    # initialised to one, which means that by default, the RG can proceed for all the momenta.
+    proceed_flags = fill(1, size_BZ^2, size_BZ^2)
+
+    # Run the RG flow starting from the maximum energy, down to the penultimate energy (ΔE), in steps of ΔE
+    @showprogress for (stepIndex, energyCutoff) in enumerate(cutOffEnergies[1:end-1])
+        deltaEnergy = abs(cutOffEnergies[stepIndex+1] - cutOffEnergies[stepIndex])
+
+        # set the Kondo coupling of all subsequent steps equal to that of the present step 
+        # for now, so that we can just add the renormalisation to it later
+        kondoJArray[:, :, stepIndex+1] = kondoJArray[:, :, stepIndex]
+
+        # if there are no enabled flags (i.e., all are zero), stop the RG flow
+        if all(==(0), proceed_flags)
[…]

### 2024-04-04 dwaveNumerics/source/probes.jl

@@ -14,6 +14,19 @@ function scattProb(kondoJArray::Array{Float64,3}, stepIndex::Int64)
 end
 
 
+function kondoCoupFSMap(size_BZ, kondoJArrayFull)
+    node = trunc(Int64, 0.25 * (size_BZ - 1) * (size_BZ + 1) + 1)
+    antinode = trunc(Int64, trunc(Int, 0.5 * (size_BZ - 1) + 1))
+    results1 = kondoJArrayFull[node, :, end]
+    results2 = kondoJArrayFull[antinode, :, end]
+    return [results1, results2]
+end
+
+
+function kondoCoupDiagMap(size_BZ, kondoJArrayFull)
+    return [kondoJArrayFull[i, i, end] for i in 1:size_BZ^2]
+end
+
 function plotHeatmaps(results1, results2, k_vals, plots, cmap_left, titles)
     minima = minimum.([results1, results2])
     maxima = maximum.([results1, results2])
@@ -32,70 +45,3 @@ function plotHeatmaps(results1, results2, k_vals, plots, cmap_left, titles)
     return plots
 end
 
-function manager(size_BZ::Int64, J_val::Float64, W_by_J_range::Vector{Float64}, orbitals::Vector{String}, probes::Vector{String}, figScale::Float64)
-    @assert size_BZ % 2 != 0
-    results_arr = zeros((length(probes), length(W_by_J_range), size_BZ^2))
-    savePaths = ["data/$(orbitals)_$(size_BZ)_$(round(J_val, digits=3))_$(round(W_by_J, digits=3))" for W_by_J in W_by_J_range]
-    for (j, W_by_J) in enumerate(W_by_J_range)
-        kondoJArrayFull, dispersionArray = main(size_BZ, J_val, J_val * W_by_J, orbitals)
-        writedlm(savePaths[j], kondoJArrayFull[:,:,[1, end]])
-    end
-    k_vals = range(K_MIN, stop=K_MAX, length=size_BZ) ./ pi
-    for probe in probes
-        pdfFileNames = []
-        anim = @animate for (W_by_J, savePath) in zip(W_by_J_range, savePaths)
-            kondoJArrayFull = readdlm(savePath)
-            kondoJArrayFull = reshape(kondoJArrayFull, (size_BZ^2, size_BZ^2, 2))
-            p1 = plot()
-            p2 = plot()
-            if probe == "scattProb"
[…]

### 2024-04-11 dwaveNumerics/caller.jl
simplified plot by removing the bare figure

@@ -1,3 +1,4 @@
 include("./source/main.jl")
 
-manager(25, -2., 0.1, [0, 0.5], ["p", "p"], ["scattProb"])
+manager(33, -2.0, 0.1, [0.0, 0.05], ["p", "p"], ["scattProb", "kondoCoupNodeMap", "kondoCoupAntinodeMap", "kondoCoupOffNodeMap", "kondoCoupOffAntinodeMap"], figScale=1.0)
+# manager(73, -2., 0.1, [0, -0.815,-0.817, -0.819], ["p", "p"], ["scattProb", "kondoCoupNodeMap", "kondoCoupAntinodeMap", "kondoCoupOffNodeMap", "kondoCoupOffAntinodeMap"], figScale=1.)

### 2024-04-11 dwaveNumerics/source/main.jl

@@ -130,7 +130,7 @@ function manager(size_BZ::Int64, omega_by_t::Float64, J_val::Float64, W_by_J_ran
                 save(pdfFileName, fig, pt_per_unit=100)
             end
         end
-        plotName = animName(orbitals, size_BZ, figScale, minimum(W_by_J_range), maximum(W_by_J_range), J_val)
+        plotName = animName(orbitals, size_BZ, omega_by_t, figScale, minimum(W_by_J_range), maximum(W_by_J_range), J_val)
         run(`pdfunite $pdfFileNames $(plotName)-$(replace(probeName, " " => "-")).pdf`)
         run(`rm $pdfFileNames`)
         # gif(anim, plotName * "-$(replace(probeName, " " => "-")).gif", fps=0.5)

### 2024-04-11 dwaveNumerics/source/probes.jl

@@ -84,16 +84,16 @@ function mapProbeNameToProbe(probeName, size_BZ, kondoJArrayFull, W_by_J, disper
         drawPoint = offantinode ./ pi
     end
     fig = Figure()
-    titlelayout = GridLayout(fig[0, 1:6])
+    titlelayout = GridLayout(fig[0, 1:4])
     header = trunc(size_BZ * W_by_J, digits=2)
-    Label(titlelayout[1, 1:6], L"NW/J=%$header", justification=:center, padding=(0, 0, -20, 0))
-    axes = [Axis(fig[1, 2*i-1], xlabel=L"\mathrm{k_x}", ylabel=L"\mathrm{k_y}", title=title) for (i, title) in enumerate(titles)]
-    axes = plotHeatmaps((results_bool, results, results_bare),
-        fig, axes, cmaps, size_BZ)
+    Label(titlelayout[1, 1:4], L"NW/J=%$header", justification=:center, padding=(0, 0, -20, 0))
+    axes = [Axis(fig[1, 2*i-1], xlabel=L"\mathrm{k_x}", ylabel=L"\mathrm{k_y}", title=title) for (i, title) in enumerate(titles[1:2])]
+    axes = plotHeatmaps((results_bool, results),
+			fig, axes[1:2], cmaps, size_BZ)
     if probeName in ["kondoCoupNodeMap", "kondoCoupAntinodeMap", "kondoCoupOffNodeMap", "kondoCoupOffAntinodeMap"]
         [scatter!(ax, [drawPoint[1]], [drawPoint[2]], markersize=20, color=:grey, strokewidth=2, strokecolor=:white) for ax in axes]
     end
-    [colsize!(fig.layout, i, Aspect(1, 1.0)) for i in [1, 3, 5]]
+    [colsize!(fig.layout, i, Aspect(1, 1.0)) for i in [1, 3]]
     resize_to_layout!(fig)
     return fig
 end

### 2024-04-11 TilingProjectDraft/tilingProject.tex
added plots to notes

@@
 \section{Extending the Anderson impurity model}
+We have already shown in a previous work that by including a local attractive interacting on the conduction bath site coupled to the impurity site of the Anderson impurity model, one can obtain an impurity phase transition from a screened phase to an unscreened local moment phase.
+This occurs at a certain critical value of the attractive interaction strength.
+We now consider a more realistic form of this model, by embedding the impurity site into the lattice of a 2D  conduction bath and accounting for the lowering of the \(s-\)wave symmetry of the interactions down to just the \(C_4\) symmetry of the 2D square lattice.
+
 \subsection{Hamiltonian}
@@
 where \(J_{\left\{ {\bf k}_i \right\} }\) takes one of the two forms in eqs.~\ref{J_dwave} and \ref{J_pwave_nooffsite}, and \(W_{\left\{{\bf k}_i\right\}}\) can similarly take either of the two forms in eqs.~\ref{W_dwave} and \ref{W_pwave_nooffsite}.
-\subsection{Results}
+\subsection{Unitary RG analysis of the model}
 We studied the low-energy physics of this model through a unitary renormalisation group calculation that decouples the high-energy modes of the conduction bath and incorporates their effects in the form of renormalised Hamiltonian couplings.
@@
 The presence of the \(f_\mathcal{P}\) function in the second term leads to a new \(k-\)space dependence of the Kondo coupling at the second step, hence leading to a modified RG equation if one makes the \(k-\)dependence explicit.
+
+\subsection{Presence of a local pseuodogapping transition with electronic differentiation in momentum space}
+We find that upon tuning the ratio \(W/J\) of the bath interaction strength \(W\) and the Kondo coupling  \(J\), the impurity site undergoes a transition from a screened paramagnetic phase to an unscreened local moment phase, similar to the extended-SIAM.
+The transition starts through the removal, from the Kondo cloud, of the antinodal points of the conduction bath Fermi surface.
+This is followed by the sequential removal of points away from the antinodes, with the nodal points being removed at the very end.
+This electronic differentiation is a novel feature of this model that arises because of the more realistic embedding of the impurity site into the conduction bath lattice.
+
+We quantify the removal of these points by the vanishing (up to a tolerance) of the average renormalised scattering probability 
+\begin{equation}\begin{aligned}
+	\Gamma^*({\bf k}) = \sum_{{\bf q} < \Lambda^*} \left(J^*_{{\bf k}, {\bf q}}\right)^2~,
+\end{aligned}\end{equation}
+where the other momentum \({\bf q}\) is summed over all the momentum states that reside within the fixed point window.
+The quantity \(\Gamma({\bf k})\) therefore quantifies the degree to which the state \({\bf k}\) is participating in screening the impurity at low energies.
+The \(k-\)space forms of this quantity at various values of \(W/J\) is shown in fig.~\ref{gamma_kxky}, and the difference in the behaviour of the nodal and antinodel points is apparent.
+More insights in the difference of the behaviour is obtained by studying the fixed point distribution of the couplings \(J_{{\bf k}, {\bf q}}\) for \({\bf k}\) at a node and at an antinode.
+This is shown in fig.~\ref{kondoMaps}.
+
+\begin{figure*}[htpb]
+	\centering
+	\includegraphics[width=0.49\textwidth]{scattProb-1.pdf}
+	\includegraphics[width=0.49\textwidth]{scattProb-2.pdf}\\
+	\includegraphics[width=0.49\textwidth]{scattProb-3.pdf}
+	\includegraphics[width=0.49\textwidth]{scattProb-4.pdf}\\
+	\includegraphics[width=0.49\textwidth]{scattProb-5.pdf}
+	\includegraphics[width=0.49\textwidth]{scattProb-6.pdf}
+	\caption{Variation of \(\Gamma\) as \(W/J\) is increased from left to right and top to bottom.
+In each pair of plots, the right figure shows the dependence of \(\Gamma\) on \(k_x/\pi\) and \(k_y/\pi\), while the left figure shows whether \(\Gamma({\bf k}\) is relevant (violet) or irrelevant (grey).
+As can be seen in the right pair of figures of the top row, the antinodal points are the first state to be removed from the Kondo cloud, while the left pair of figures of the bottom row shows that the node is the last to be removed.}
+	\label{gamma_kxky}
+\end{figure*}
+
+\begin{figure*}[htpb]
+	\centering
+	\includegraphics[width=0.49\textwidth]{kondoCoupNodeMap-1.pdf}
+	\includegraphics[width=0.49\textwidth]{kondoCoupNodeMap-6.pdf}\\
+	\includegraphics[width=0.49\textwidth]{kondoCoupAntinodeMap-1.pdf}
+	\includegraphics[width=0.49\textwidth]{kondoCoupAntinodeMap-6.pdf}
+	\caption{Distribution of Kondo coupling scattering processes.
+While the nodes are connected mostly through forward and backscattering processes, the antinodes also involve tangential scattering processes.}
+	\label{kondoMaps}
+\end{figure*}
 

### 2024-04-12 TilingProjectDraft/tilingProject.tex
improved notes and plots

@@
 \bibliographystyle{apsrev4-2}
-
 \begin{document}
 
-\title{\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems}
+\title{\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electrons}
 \author{Abhirup Mukherjee, N.S. Vidhyadhiraja, A. Taraphder, Siddhartha Lal}
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{dmft_scheme.pdf}
+	\includegraphics[width=0.35\textwidth]{dmft_scheme.pdf}
 \end{figure}
@@
 The bulk model hence created will then show a metal-insulator transition.
+
 The impurity models are studied using the recently-developed unitary renormalisation group method~\cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome}.
@@
  	\centering
- 	\includegraphics[width=0.4\textwidth]{gen_siam.pdf}
+ 	\includegraphics[width=0.35\textwidth]{gen_siam.pdf}
  	\caption{Cluster+bath construction of auxiliary model.
@@
 \section{Extending the Anderson impurity model}
-We have already shown in a previous work that by including a local attractive interacting on the conduction bath site coupled to the impurity site of the Anderson impurity model, one can obtain an impurity phase transition from a screened phase to an unscreened local moment phase.
-This occurs at a certain critical value of the attractive interaction strength.
+We have shown in a previous work that by including a local attractive interacting on the conduction bath site coupled to the impurity site of the Anderson impurity model, one can obtain an impurity phase transition from a screened phase to an unscreened local moment phase at a certain critical value of the attractive interaction strength.
 We now consider a more realistic form of this model, by embedding the impurity site into the lattice of a 2D  conduction bath and accounting for the lowering of the \(s-\)wave symmetry of the interactions down to just the \(C_4\) symmetry of the 2D square lattice.
-
+A general structure of such a model is shown in fig.~\ref{embededEsiam}; one of the sites of the 2D square lattice is identified as the impurity, while the four nearest-neghbours interact directly with this impurity site.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.2\textwidth]{pWaveEsiam.pdf}
+	\caption{General structure of an embedded extended SIAM, where the impurity site is a part of the 2D square lattice.
+The four nearest-neghbour sites (dark blue) interact with the impurity site through one or more processes, and can host local interactions.
+The other lattice sites (light blue) are completely non-interacting.}
+	\label{embededEsiam}
+\end{figure}
 \subsection{Hamiltonian}
-We consider an impurity spin \(\vec S_d\) interacting with a two-dimensional tight-binding conduction bath through a general interaction of the form
-\begin{equation}\begin{aligned}
-		\sum_{{\bf k}_1, {\bf k}_2, \sigma_1, \sigma_2} J_{{\bf k}_1, {\bf k}_2} \vec{S}_d\cdot\frac{1}{2}\vec{\tau}_{\sigma_1,\sigma_2} c^\dagger_{{\bf k}_1,\sigma_1}c_{{\bf k}_2,\sigma_2}
-\end{aligned}\end{equation}
-where \(\vec \tau\) is the vector of sigma matrices and \({\bf k}_1,{\bf k}_2\) are momentum states of the conduction bath.
-The precise form of \(J_{{\bf k}_1, {\bf k}_2}\) depends on the symmetry of the symmetry of the impurity-bath interaction.
-We consider the following three cases:
-
-(i)~a d-wave interaction, where the impurity couples with a coherent d-wave combination \(f_\sigma\) of the bath sites closest to it: 
-\begin{equation}\begin{aligned}
-	f_\sigma \equiv \frac{1}{2}\left(c^\dagger_{L,\sigma} + c^\dagger_{R,\sigma} - c^\dagger_{U\sigma} - c^\dagger_{D\sigma}\right)~,
-\end{aligned}\end{equation}
-where \(L,R,U\) and \(D\) indicate electrons at the positions \((x,y)=\left(-a,0\right), \left( a,0 \right) , \left( 0,a \right) \) and \(\left( 0,-a \right) \) respectively, \(a\) being the lattice spacing of the conduction bath lattice.
-The corresponding interaction (in real space) is of the form
-\begin{equation}\begin{aligned}
-	\vec{S}_d\cdot\sum_{\sigma_1,\sigma_2}\frac{1}{2}\vec{\tau}_{\sigma_1,\sigma_2}f^\dagger_{\sigma_1}f_{\sigma_2}~.
-\end{aligned}\end{equation}
-When fourier-transformed to momentum space, it gives rise to the momentum-dependent Kondo coupling 
-\begin{equation}\begin{aligned}\label{J_dwave}
-	J_{{\bf k}_1, {\bf k}_2} = J f_\mathcal{D}\left({\bf k}_1\right) f_\mathcal{D}\left({\bf k}_2\right) ~,
-\end{aligned}\end{equation}
-where \(f_\mathcal{D}({\bf k}) = \cos\left( ak_x \right) - \cos\left( ak_y \right) \) is the \(d-\)wave symmetric functional form in \(k-\)space.
-For future reference, we define the Fourier transforms as 
-\begin{equation}\begin{aligned}
-	c^\dagger_{L(R),\sigma} = \sum_{{\bf k}}c^\dagger_{{\bf k},\sigma}e^{+(-)ik_x a},\\
-	c^\dagger_{U(D),\sigma} = \sum_{{\bf k}}c^\dagger_{{\bf k},\sigma}e^{+(-)ik^y a}~.
-\end{aligned}\end{equation}
-(ii)~a p-wave interaction, but without the off-site terms in the bath. This amounts to considering the Kondo interaction term 
-\begin{equation}\begin{aligned}
-	J\vec{S}_d\cdot\sum_{\sigma_1,\sigma_2}\frac{1}{2}\vec{\tau}_{\sigma_1,\sigma_2}\frac{1}{4}\sum_{i=L,R,U,D}c^\dagger_{i,\sigma_1}c_{i,\sigma_2}~.
+We consider an impurity spin \(\vec S_d\) interacting with a two-dimensional tight-binding conduction bath through a highly localised interaction, described by the Hamiltonian
+\begin{equation}\begin{aligned}
+	\mathcal{H} = H_\text{cbath} + H_\text{imp-cbath} + H_\text{cbath-int}~,
+\end{aligned}\end{equation}
+where \(H_\text{cbath}\) is the kinetic energy arising out of nearest-neighbour hopping processes,
+\begin{equation}\begin{aligned}
+	H_\text{cbath} = -2t\sum_{{\bf k}}\left[\cos(ak_x) + \cos(ak_y)\right] c^\dagger_{{\bf k},\sigma}c_{{\bf k},\sigma}~.
+\end{aligned}\end{equation}
+The form of the impurity-bath interaction \(H_\text{imp-cbath}\) and the local interaction \(H_\text{cbath-int}\) in the bath can be of various forms, depending in the choice of the bath orbital which participates in the interaction.
+We now consider some interesting cases:
+\paragraph{\(d-\)wave interactions:} This is the case when a coherent \(d-\)wave combination of the bath sites closest to the impurity participates in the interaction:
+\begin{equation}\begin{aligned}
+	d_{\sigma} &= \frac{1}{2}\left(c^\dagger_{L,\sigma} + c^\dagger_{R,\sigma} - c^\dagger_{U\sigma} - c^\dagger_{D\sigma}\right)~,
+\end{aligned}\end{equation}
+leading to the interaction terms
+\begin{equation}\begin{aligned}
+	H^{(d)}_\text{imp-cbath} &= J\vec{S}_d\cdot\frac{1}{2}\sum_{\sigma_1,\sigma_2}\vec{\tau}_{\sigma_1,\sigma_2} d^\dagger_{\sigma_1}d_{\sigma_2}~,\\
+	H^{(d)}_\text{cbath-int} &= -\frac{W}{2}\left(d^\dagger_{\uparrow}d_{\uparrow} - d^\dagger_{\downarrow}d_{\downarrow}\right)^2~,
+\end{aligned}\end{equation}
+where \(\vec \tau\) is the vector of sigma matrices, \(\sigma_1,\sigma_2\) are spin indices, and \(L,R,U,D\) represent the four lattice sites ({\it L}eft, {\it R}ight, {\it U}p, {\it D}own) closest to the impurity.
+When Fourier-transformed to momentum space, it gives rise to the momentum-dependent couplings
+\begin{equation}\begin{aligned}\label{d-wave k-space}
+	J_{{\bf k}_1, {\bf k}_2} = J f_{\pi}\left({\bf k}_1\right) f_{\pi}\left({\bf k}_2\right) ~,\quad W_{\left\{ k_i \right\} } = W\prod_{i=1,2,3,4}f_{\pi}(k_i)~,
+\end{aligned}\end{equation}
+where \(f_{\pi}({\bf k}) = \cos\left( ak_x \right) - \cos\left( ak_y \right) \) is the \(d-\)wave symmetric functional form in \(k-\)space.
+\paragraph{\(p-\)wave interaction:} One can also consider the case when the \(p-\)wave orbital of the nearest sites participates in the interaction:
+\begin{equation}\begin{aligned}
+	p_{\sigma} &= \frac{1}{2}\left(c^\dagger_{L,\sigma} + c^\dagger_{R,\sigma} + c^\dagger_{U\sigma} + c^\dagger_{D\sigma}\right)~,\\
+	H^{(p)}_\text{imp-cbath} &= J\vec{S}_d\cdot\frac{1}{2}\sum_{\sigma_1,\sigma_2}\vec{\tau}_{\sigma_1,\sigma_2} p^\dagger_{\sigma_1}p_{\sigma_2}~,\\
+	H^{(p)}_\text{cbath-int} &= -\frac{W}{2}\left(p^\dagger_{\uparrow}p_{\uparrow} - p^\dagger_{\downarrow}p_{\downarrow}\right)^2~.
 \end{aligned}\end{equation}
 The momentum-dependent Kondo coupling in this case is 
-\begin{equation}\begin{aligned}\label{J_pwave_nooffsite}
-	J_{{\bf k}_1, {\bf k}_2} \equiv \frac{1}{2}J f_\mathcal{P}\left( {\bf k}_1, {\bf k}_2\right) ~,
-\end{aligned}\end{equation}
-where \(f_\mathcal{P}(\left\{{\bf k}_i\right\}) = \cos\left( ak_{1x} - ak_{2x} + ak_{3x} - \ldots\right) + x\to y \) is the form for the \(p-\)wave symmetric function.
-
-We also consider correlation terms on the bath sites \(L,R,U\) and \(D\). In momentum space, it is of the general form
-\begin{equation}\begin{aligned}
--\frac{1}{2}\sum_{1, 2, 3, 4}\sum_\sigma W_{1,2,3,4}~ c^\dagger_{{\bf k}_1,\sigma}c_{{\bf k}_2,\sigma}\left(c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} - c^\dagger_{{\bf k}_3,\bar\sigma}c_{{\bf k}_4,\bar\sigma}\right) ~,
-\end{aligned}\end{equation}
-where the form of \(W_{\left\{{\bf k}_i\right\}}\) is again determined by the orbitals participating in the interaction.
-We consider the d-wave interaction and a p-wave interaction without off-site terms, as above.
-These two cases lead to the following Hamiltonian structures:\\
-(i)~a d-wave interaction, of the form 
-\begin{equation}\begin{aligned}
-	-\frac{W}{2}\left(f^\dagger_{\uparrow}f_{\uparrow} - f^\dagger_{\downarrow}f_{\downarrow}\right)^2~,
-\end{aligned}\end{equation}
-in real space, leading to the momentum-dependence
-\begin{equation}\begin{aligned}\label{W_dwave}
-	W_{1,2,3,4} = W\prod_{i=1,2,3,4}f_\mathcal{D}(k_i)~.
-\end{aligned}\end{equation}
-(ii)~a p-wave interaction without off-site terms, 
-\begin{equation}\begin{aligned}
-	-\frac{W}{2}\frac{1}{4}\sum_{i=L,R,U,D}\left(c^\dagger_{i,\uparrow}c_{i,\uparrow} - c^\dagger_{i,\downarrow}c_{i,\downarrow}\right)^2~,
-\end{aligned}\end{equation}
-leading to the following form in momentum space:
-\begin{equation}\begin{aligned}\label{W_pwave_nooffsite}
-	W_{\left\{{\bf k}_i\right\}} = \frac{1}{2}W f_\mathcal{P}\left({\bf k}_1, {\bf k}_2, {\bf k}_3, {\bf k}_4\right) ~.
-\end{aligned}\end{equation}
-
-To summarise, the total Hamiltonian we consider is of the form
-\begin{equation}\begin{aligned}\label{hamiltonian}
-	&-2t\sum_{kx,k y}\left[\cos(ak_x) + \cos(ak_y)\right] c^\dagger_{{\bf k},\sigma}c_{{\bf k},\sigma} + \\
-	 &\sum_{{\bf k}_1, {\bf k}_2, \sigma_1, \sigma_2} J_{{\bf k}_1, {\bf k}_2} \vec{S}_d\cdot\frac{1}{2}\vec{\tau}_{\sigma_1,\sigma_2} c^\dagger_{{\bf k}_1,\sigma_1}c_{{\bf k}_2,\sigma_2} -\\
-	 &\frac{1}{2}\sum_{1, 2, 3, 4}\sum_\sigma W_{1,2,3,4}~ c^\dagger_{{\bf k}_1,\sigma}c_{{\bf k}_2,\sigma}\left(c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} - c^\dagger_{{\bf k}_3,\bar\sigma}c_{{\bf k}_4,\bar\sigma}\right)~,
-\end{aligned}\end{equation}
-where \(J_{\left\{ {\bf k}_i \right\} }\) takes one of the two forms in eqs.~\ref{J_dwave} and \ref{J_pwave_nooffsite}, and \(W_{\left\{{\bf k}_i\right\}}\) can similarly take either of the two forms in eqs.~\ref{W_dwave} and \ref{W_pwave_nooffsite}.
+\begin{equation}\begin{aligned}\label{p-wave k-space}
+	J_{{\bf k}_1, {\bf k}_2} = J f_{{2\pi}}\left({\bf k}_1\right) f_{{2\pi}}\left({\bf k}_2\right) ~, \quad W_{\left\{ k_i \right\} } = W\prod_{i=1,2,3,4}f_{{2\pi}}(k_i)~,
+\end{aligned}\end{equation}
+where \(f_{2\pi}({\bf k}) = \cos\left( ak_x \right) + \cos\left( ak_y \right)\) is the form for the \(p-\)wave symmetric function.
+
+Note that both these interactions involve not only local terms as well as quasi-local terms in the form of off-site interactions that connect the impurity site with multiple bath sites.
+An example of such a term is \(\vec{S}_d\cdot\frac{1}{2}\sum_{\sigma_1,\sigma_2}\vec{\tau}_{\sigma_1,\sigma_2} c^\dagger_{R,\sigma_1}c_{U,\sigma_2}\), which couples the impurity site with both the right and up sites in the bath.
+One can consider simple modifications of these cases by retaining only the on-site terms in the interaction Hamiltonian.
+This gives us the modified \(d-\)wave and \(p-\)wave symmetries:
+\begin{equation}\begin{aligned}
+	H^{(\bar d(\bar p))}_\text{imp-cbath} &= J\vec{S}_d\cdot\frac{1}{2}\sum_{\sigma_1,\sigma_2}\vec{\tau}_{\sigma_1,\sigma_2} \sum_{i \in \left\{L,R,U,D\right\}} \lambda_i c^\dagger_{i,\sigma_1}c_{i,\sigma_2}~,\\
+	H^{(\bar d(\bar p))}_\text{cbath-int} &= -\frac{W}{2}\sum_{i \in \left\{L,R,U,D\right\}} \lambda_i \left(c^\dagger_{i, \uparrow}c_{i, \uparrow} - c^\dagger_{i, \downarrow}c_{i, \downarrow}\right) ~,
+\end{aligned}\end{equation}
+where \(\lambda_R = \lambda_L = \lambda_U = \lambda_D = 1\) for the \(\bar p\)-wave case, but \(\lambda_R = \lambda_L = -\lambda_U = -\lambda_D = 1\) for the \(\bar d\)-wave case.
+The \(k-\)dependent couplings have the form
+\begin{equation}\begin{aligned}
+	J_{{\bf k}_1, {\bf k}_2} &= J f_{\bar d(\bar p)}\left({\bf k}_1 -{\bf k}_2\right),\\
+	W_{\left\{ \bf k_i \right\} } &= Wf_{\bar d(\bar p)}\left({\bf k}_1 -{\bf k}_2 + {\bf k}_3 -{\bf k}_4\right) ,
+\end{aligned}\end{equation}
+where 
+\begin{equation}\begin{aligned}
+	&f_{\bar d(\bar p)}\left({\bf k}_1 -{\bf k}_2 + {\bf k}_3 -{\bf k}_4\right) \\
+	&= \frac{1}{2}\left[\lambda_R \cos\left(k_{1x} - k_{2x} + k_{3x} - k_{4x}\right) \right.\\
+	&\quad\left. + \lambda_U \cos\left(k_{1y} - k_{2y} + k_{3y} - k_{4y}\right)\right] ~.
+\end{aligned}\end{equation}
+
 \subsection{Unitary RG analysis of the model}
@@
 We now consider some specific cases of these results.
-\paragraph{Same symmetries in the Kondo coupling and bath interaction}
-Assuming that both the Kondo interaction and the bath interaction couple to the \(d-\)wave channel, we have the microscopic functional forms 
-\begin{equation}\begin{aligned}
-	J^{(0)}_{{\bf k},{\bf q}} &= J f_\mathcal{D}({\bf k}) f_\mathcal{D}({\bf q})~,\\
-	J^{(0)}_{{\bf \bar q},{\bf q}} &= J f_\mathcal{D}(\pi + {\bf q}) f_\mathcal{D}({\bf q}) = Jf_\mathcal{D}({\bf q})^2 ~,
-\end{aligned}\end{equation}
-and
-\begin{equation}\begin{aligned}
-	W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} = W f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf q})^2~,
-\end{aligned}\end{equation}
-where \(f_\mathcal{D}({\bf k}) = \cos\left( ak_{x} \right) - \cos\left( ak_y \right) \) is the \(d-\)wave symmetric functional form in \(k-\)space
-The numerator of the RG equations becomes
-\begin{equation}\begin{aligned}
-	f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf q})^2\left[J^2 + 4JWf_\mathcal{D}({\bf q})^2\right] ~.
-\end{aligned}\end{equation}
-Since a factor of \(f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)\) factors out of the RG equation, the Kondo coupling will preserve its momentum dependence during the RG equation, and we can study the RG flow of the amplitude \(J\):
-\begin{equation}\begin{aligned}
-	\Delta J = \sum_{{\bf q} \in \text{PS}} \frac{-f_\mathcal{D}({\bf q})^2\left[J^2 + 4JWf_\mathcal{D}({\bf q})^2\right]}{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{2}f_\mathcal{D}({\bf q})^4}~.
-\end{aligned}\end{equation}
-
-\paragraph{Different symmetries in the Kondo coupling and bath interaction}
-One can also study the case when the bath interaction has \(p-\)wave symmetry:
-\begin{equation}\begin{aligned}
-	W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} =& \frac{1}{2}W f_\mathcal{P}\left(\pi + {\bf q}, {\bf k}_2, {\bf k}_1, {\bf q}\right) ~,\\
-	=& -\frac{1}{2}Wf_\mathcal{P}\left({\bf k}_1, {\bf k}_2\right)~.
-\end{aligned}\end{equation}
-This choice does not preserve the momentum-dependence of the Kondo coupling, because we can no longer pull out a factor of \(f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)\) from the RG equation.
-At the first step, the RG equation is of the form
+\paragraph{Interactions with off-site terms:}
+The case with the complete \(d-\)wave and \(p-\)wave terms enjoy a factorisation of the momentum space couplings into functions of the participating momenta, as shown in eq.~\ref{d-wave k-space} and \ref{p-wave k-space}.
+This factorisation also translates into the RG equation, ensuring that the momentum space Kondo coupling retains its form, and renormalisation occurs only in the magnitude \(J\), through the equation
+\begin{equation}\begin{aligned}
+	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} &= f_{{2\pi}(\pi)}\left({\bf k}_1\right) f_{{2\pi}(\pi)}\left({\bf k}_2\right) \Delta J~,\\
+\Delta J &= \sum_{{\bf q} \in \text{PS}} \frac{-f_{2\pi(\pi)}({\bf q})^2\left[J^2 + 4JWf_{2\pi(\pi)}({\bf q})^2\right]}{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_{2\pi(\pi)}({\bf q})^2 + \frac{W}{2}f_{2\pi(\pi)}({\bf q})^4}~.
+\end{aligned}\end{equation}
+\paragraph{Interactions without off-site terms:}
+This choice does not lead to a factorisation of the momentum-space dependence, and the form of the Kondo coupling therefore morphs during the RG flow, allowing the emergence of new degrees of freedom that screen the impurity at low-energies.
+At the first step, the RG equation can be written down explicitly as
 \begin{equation}\begin{aligned}
 	&\Delta J^{(0)}_{{\bf k}_1, {\bf k}_2} =\\
-	&-\sum_{{\bf q} \in \text{PS}} \frac{f_\mathcal{D}({\bf q})^2\left[{J}^2 f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1) - 2JW f_\mathcal{P}\left({\bf k}_1, {\bf k}_2\right)\right] }{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{4}}~.
-\end{aligned}\end{equation}
-The presence of the \(f_\mathcal{P}\) function in the second term leads to a new \(k-\)space dependence of the Kondo coupling at the second step, hence leading to a modified RG equation if one makes the \(k-\)dependence explicit.
+	&-\sum_{{\bf q} \in \text{PS}} \frac{J^2 f_{\bar p(\bar d)}\left({\bf k}_2 - {\bf q}\right) f_{\bar p(\bar d)}\left({\bf q} - {\bf k}_1\right) - 4JW f_{\bar p(\bar d)}\left({\bf k}_2 - {\bf k}_1\right)}{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{4}}
+\end{aligned}\end{equation}
+The first term in the numerator does not depend only on the momentum difference \({\bf k}_2 - {\bf k}_1\), unlike the bare Kondo coupling.
+This leads to a new \(k-\)space dependence of the Kondo coupling at the second step, hence leading to a modified RG equation if one makes the \(k-\)dependence explicit.
 
@@
 \subsection{Tiling towards a Hubbard-Heisenberg model with an s-wave impurity model}
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.3\textwidth]{pWaveEsiam.pdf}
-	\caption{Caption.}
-	\label{pWaveEsiam}
-\end{figure}
 In this subsection, we provide an explicit example of constructing a lattice model.

### 2024-04-12 dwaveNumerics/caller.jl

@@ -1,4 +1,3 @@
 include("./source/main.jl")
 
-manager(33, -2.0, 0.1, [0.0, 0.05], ["p", "p"], ["scattProb", "kondoCoupNodeMap", "kondoCoupAntinodeMap", "kondoCoupOffNodeMap", "kondoCoupOffAntinodeMap"], figScale=1.0)
-# manager(73, -2., 0.1, [0, -0.815,-0.817, -0.819], ["p", "p"], ["scattProb", "kondoCoupNodeMap", "kondoCoupAntinodeMap", "kondoCoupOffNodeMap", "kondoCoupOffAntinodeMap"], figScale=1.)
+manager(13, -2., 0.1, [0, -0.815,-0.817, -0.819, -0.82, -0.9], ["p", "p"], ["scattProb", "kondoCoupNodeMap", "kondoCoupAntinodeMap", "kondoCoupOffNodeMap", "kondoCoupOffAntinodeMap"], figScale=4.)

### 2024-04-12 dwaveNumerics/source/main.jl

@@ -8,7 +8,7 @@ end
 @everywhere using JLD2
 @everywhere using ProgressMeter
 set_theme!(theme_latexfonts())
-update_theme!(fontsize=24)
+update_theme!(fontsize=30)
 
 @everywhere include("./rgFlow.jl")
 @everywhere include("./probes.jl")
@@ -127,7 +127,7 @@ function manager(size_BZ::Int64, omega_by_t::Float64, J_val::Float64, W_by_J_ran
                 # calculate and plot the probe result, then save the fig.
                 fig = mapProbeNameToProbe(probeName, size_BZ, kondoJArrayEnds, W_by_J, dispersion, fixedpointEnergy)
                 display(fig)
-                save(pdfFileName, fig, pt_per_unit=100)
+                save(pdfFileName, fig, pt_per_unit=figScale)
             end
         end
         plotName = animName(orbitals, size_BZ, omega_by_t, figScale, minimum(W_by_J_range), maximum(W_by_J_range), J_val)

### 2024-04-12 dwaveNumerics/source/probes.jl

@@ -18,7 +18,7 @@ function scattProb(kondoJArray::Array{Float64,3}, stepIndex::Int64, size_BZ::Int
     end
     results_bool = tolerantSign.(abs.(results ./ results_bare), RG_RELEVANCE_TOL)
     results[results_bool.<0] .= NaN
-    return results, results_bare, results_bool
+    return results ./ results_bare, results_bare, results_bool
 end
 
 
@@ -51,45 +51,45 @@ function mapProbeNameToProbe(probeName, size_BZ, kondoJArrayFull, W_by_J, disper
     cmaps = [DISCRETE_CGRAD, :matter, :matter]
     if probeName == "scattProb"
         results, results_bare, results_bool = scattProb(kondoJArrayFull, size(kondoJArrayFull)[3], size_BZ, dispersion, fixedpointEnergy)
-        titles[1] = L"\mathrm{relevance/irrelevance~of~}\Gamma(k)"
-        titles[2] = L"\Gamma(k) = \sum_q J(k,q)^2"
+        titles[1] = L"\mathrm{rel(irrel)evance~of~}\Gamma(k)"
+        titles[2] = L"\Gamma/\Gamma^{(0)}"
         titles[3] = L"\Gamma^{(0)}(k) = \sum_q J(k,q)^2"
     elseif probeName == "kondoCoupNodeMap"
         node = (-pi / 2, -pi / 2)
         results, results_bare, results_bool = kondoCoupMap(node, size_BZ, kondoJArrayFull)
-        titles[1] = L"\mathrm{relevance/irrelevance~of~}J(k,q_\mathrm{node})"
+        titles[1] = L"\mathrm{rel(irrel)evance~of~}J(k,q_\mathrm{node})"
         titles[2] = L"J(k,q_\mathrm{node})"
         titles[3] = L"J^{(0)}(k,q_\mathrm{node})"
         drawPoint = (-0.5, -0.5)
     elseif probeName == "kondoCoupAntinodeMap"
         antinode = (0.0, -pi)
         results, results_bare, results_bool = kondoCoupMap(antinode, size_BZ, kondoJArrayFull)
-        titles[1] = L"\mathrm{relevance/irrelevance~of~}J(k,q_\mathrm{antin.})"
+        titles[1] = L"\mathrm{rel(irrel)evance~of~}J(k,q_\mathrm{antin.})"
[…]

### 2024-04-23 TilingProjectDraft/tilingProject.tex
added spin correlation as probe

@@
 We now consider a more realistic form of this model, by embedding the impurity site into the lattice of a 2D  conduction bath and accounting for the lowering of the \(s-\)wave symmetry of the interactions down to just the \(C_4\) symmetry of the 2D square lattice.
-A general structure of such a model is shown in fig.~\ref{embededEsiam}; one of the sites of the 2D square lattice is identified as the impurity, while the four nearest-neghbours interact directly with this impurity site.
+A general structure of such a model is shown in fig.~\ref{embeddedEsiam}; one of the sites of the 2D square lattice is identified as the impurity, while the four nearest-neghbours interact directly with this impurity site.
 \begin{figure}[htpb]
@@
 The other lattice sites (light blue) are completely non-interacting.}
-	\label{embededEsiam}
+	\label{embeddedEsiam}
 \end{figure}
@@
 
-\subsection{Tiling towards a Hubbard-Heisenberg model with an s-wave impurity model}
+\subsection{Tiling towards a Hubbard-Heisenberg model with an embedded extended SIAM}
 In this subsection, we provide an explicit example of constructing a lattice model.
@@
 We will show that that model leads to a form of a Hubbard-Heisenberg model upon restoring translation invariance via repeated translation operations.
-The generalisation involve allowing an arbitrary filling on the impurity site and in the conduction bath, through two additional parameter: (i) a particle-hole assymetry parameter \(\eta\) for the impurity site, (ii) a chemical potential for the conduction bath, and (iii) embedding the impurity into the lattice of the 2D conduction bath.
-This modified impurity model is shown in Fig.~\ref{pWaveEsiam}.
+The generalisation involve allowing an arbitrary filling on the impurity site and in the conduction bath, through two additional parameter: (i) a particle-hole asymmetry parameter \(\eta\) for the impurity site, (ii) a chemical potential for the conduction bath, and (iii) embedding the impurity into the lattice of the 2D conduction bath.
+This modified impurity model is shown in Fig.~\ref{embeddedEsiam}.
 The first term modifies the impurity Hamiltonian \(\mathcal{H}_\text{imp}\) into

### 2024-04-23 dwaveNumerics/caller.jl

@@ -1,42 +1,5 @@
 include("./source/main.jl")
 
 J_val = 0.1
-size_BZ = 53
-node = map2DTo1D(-pi/2, -pi/2, size_BZ)
-antinode = map2DTo1D(-pi, 0., size_BZ)
-labels = ["p", "poff", "d", "doff"]
-for J_sym in labels
-    row_results = [["N", "N"] for _ in labels]
-    for (j, W_sym) in enumerate(labels)
-        noderesults = [0, 0, 0]
-        antinoderesults = [0, 0, 0]
-        for (i, W_by_J) in enumerate([0, 1., -1.])
-            kondoJArrayFull, dispersion, fixedpointEnergy = momentumSpaceRG(size_BZ, -2., J_val, J_val * W_by_J, [J_sym, W_sym]; progressbarEnabled=false)
-            _, _, results_bool = scattProb(kondoJArrayFull, size(kondoJArrayFull)[3], size_BZ, dispersion, fixedpointEnergy)
-            noderesults[i] = results_bool[node]
-            antinoderesults[i] = results_bool[antinode]
-        end
-        if noderesults[2] < 0 && antinoderesults[2] < 0 && (noderesults[1] >= 0 || antinoderesults[1] >= 0)
-            row_results[j][1] = "Y"
-        end
-        if noderesults[3] < 0 && antinoderesults[3] < 0 && (noderesults[1] >= 0 || antinoderesults[1] >= 0)
-            row_results[j][2] = "Y"
-        end
-    end
-    println(join(join.(row_results, ""), "\t"))
-end
-
-# manager(33, -2.0, 0.1, collect(0:-0.5:-1), ["p", "doff"], ["scattProb"], figScale=1.0)
-#
-# Columns labels are for W-symmetry.
-# Row labels are for J-symmetry.
-# First(second) character in each entry is for W>(<)0.
-# N means no transition. Y means there is a transition.
-#
-# W      p      poff    d     doff 
-# J    |-------------------------
-# p    | NY     NN     NN     NN
-# poff | NN     NY     NN     NN
-# d    | NN     NN     NN     NN
-# doff | NN     NN     NN     NY
-#
+size_BZ = 45
+manager(size_BZ, -2.0, J_val, [0.0, -1.3, -2.3, -2.9, -3.9, -4.9, -28.0] ./ size_BZ, ("p", "p"), ["spinFlipCorrMap"])

### 2024-04-23 dwaveNumerics/source/constants.jl

@@ -14,7 +14,7 @@ using Makie
 (@isdefined FIG_SIZE) || const FIG_SIZE = (700, 350)
 (@isdefined RG_RELEVANCE_TOL) || const RG_RELEVANCE_TOL = 1e-2
 
-const ALLOWED_PROBES = ["scattProb", "kondoCoupNodeMap", "kondoCoupAntinodeMap", "kondoCoupOffNodeMap", "kondoCoupOffAntinodeMap"]
+const ALLOWED_PROBES = ["scattProb", "kondoCoupNodeMap", "kondoCoupAntinodeMap", "kondoCoupOffNodeMap", "kondoCoupOffAntinodeMap", "spinFlipCorrMap"]
 # for testing. 
 (@isdefined SIZE_BZ) || const SIZE_BZ = [5, 101, 1001]
 (@isdefined KX_VALUES) || const KX_VALUES = [K_MIN, K_MAX, K_MIN, K_MAX, 0]

### 2024-04-23 dwaveNumerics/source/main.jl

@@ -16,76 +16,15 @@ update_theme!(fontsize=30)
 # file name format for saving plots and animations
 animName(orbitals, size_BZ, omega_by_t, scale, W_by_J_min, W_by_J_max, J_val) = "$(orbitals[1])-$(orbitals[2])_$(size_BZ)_$(omega_by_t)_$(round(W_by_J_min, digits=4))_$(round(W_by_J_max, digits=4))_$(round(J_val, digits=4))_$(FIG_SIZE[1] * scale)x$(FIG_SIZE[2] * scale)"
 
-@everywhere function momentumSpaceRG(size_BZ::Int64, omega_by_t::Float64, J_val::Float64, bathIntStr::Float64, orbitals::Vector{String}; progressbarEnabled=false)
 
-    # ensure that the choice of orbitals is d or p
-    impOrbital, bathOrbital = orbitals
-    @assert bathOrbital in ["p", "d", "poff", "doff"]
-    @assert impOrbital in ["p", "d", "poff", "doff"]
-
-    densityOfStates, dispersionArray = getDensityOfStates(tightBindDisp, size_BZ)
-
-    cutOffEnergies = getCutOffEnergy(size_BZ)
-
-    # Kondo coupling must be stored in a 3D matrix. Two of the dimensions store the 
-    # incoming and outgoing momentum indices, while the third dimension stores the 
-    # behaviour along the RG flow. For example, J[i][j][k] reveals the value of J 
-    # for the momentum pair (i,j) at the k^th Rg step.
-    kondoJArray = initialiseKondoJ(size_BZ, impOrbital, trunc(Int, (size_BZ + 1) / 2), J_val)
-
-    # define flags to track whether the RG flow for a particular J_{k1, k2} needs to be stopped 
-    # (perhaps because it has gone to zero, or its denominator has gone to zero). These flags are
-    # initialised to one, which means that by default, the RG can proceed for all the momenta.
-    proceed_flags = fill(1, size_BZ^2, size_BZ^2)
-
-    # Run the RG flow starting from the maximum energy, down to the penultimate energy (ΔE), in steps of ΔE
-
-    fixedpointEnergy = minimum(cutOffEnergies)
-    @showprogress enabled = progressbarEnabled for (stepIndex, energyCutoff) in enumerate(cutOffEnergies[1:end-1])
-        deltaEnergy = abs(cutOffEnergies[stepIndex+1] - cutOffEnergies[stepIndex])
-
-        # set the Kondo coupling of all subsequent steps equal to that of the present step 
[…]

### 2024-04-23 dwaveNumerics/source/probes.jl

@@ -1,6 +1,8 @@
 using LinearAlgebra
 using CairoMakie
 using Makie
+include("../../../fermionise/source/fermionise.jl")
+include("../../../fermionise/source/models.jl")
 
 function scattProb(kondoJArray::Array{Float64,3}, stepIndex::Int64, size_BZ::Int64, dispersion::Vector{Float64}, fixedpointEnergy::Float64)
     results = zeros(size_BZ^2)
@@ -32,6 +34,35 @@ function kondoCoupMap(k_vals, size_BZ, kondoJArrayFull)
 end
 
 
+function spinFlipCorrMap(size_BZ::Int64, kondoJArrayFull, W_val::Float64, orbitals::Tuple{String,String})
+    k_indices = collect(1:size_BZ^2)
+    results = zeros(length(k_indices))
+    trunc_dim = 4
+    basis = BasisStates(trunc_dim * 2 + 2)
+
+    # operator list for the operator S_d^+ c^†_{k ↓} c_{k ↑} + h.c.
+    spinFlipCorrOplist = [("+-+-", 1., [1, 2, 4, 3]), ("+-+-", 1., [2, 1, 3, 4])]
+
+    @showprogress for k_index in k_indices
+        other_k_indices = k_indices[k_indices .≠ k_index]
+        chosenIndices = [[k_index]; other_k_indices[sortperm(kondoJArrayFull[k_index, other_k_indices, end], rev=true)][1:trunc_dim-1]]
+        mapSeq = Dict(index => i for (i, index) in enumerate(chosenIndices))
+
+        Ek_arr = Dict(mapSeq[index] => tightBindDisp(map1DTo2D(index, size_BZ)...) for index in chosenIndices)
+        kondoDict = Dict(Tuple(mapSeq[p] for p in points) => kondoJArrayFull[points..., end]
+                         for points in Iterators.product(chosenIndices, chosenIndices))
+        bathIntDict = Dict(Tuple(mapSeq[p] for p in points) => bathIntForm(W_val, orbitals[2], size_BZ, points)
+                           for points in Iterators.product(chosenIndices, chosenIndices, chosenIndices, chosenIndices))
+        oplist = KondoKSpace(Ek_arr, kondoDict, bathIntDict)
+        fixedPointHamMatrix = generalOperatorMatrix(basis, oplist)
[…]

### 2024-04-23 dwaveNumerics/source/rgFlow.jl

@@ -256,3 +256,65 @@ function stepwiseRenormalisation(
     kondoJArrayNext, proceed_flags = symmetriseRGFlow(innerIndicesArr, excludedVertexPairs, mixedVertexPairs, size_BZ, kondoJArrayNext, kondoJArrayPrev, proceed_flags)
     return kondoJArrayNext, proceed_flags
 end
+
+@everywhere function momentumSpaceRG(size_BZ::Int64, omega_by_t::Float64, J_val::Float64, bathIntStr::Float64, orbitals::Tuple{String,String}; progressbarEnabled=false)
+
+    impOrbital, bathOrbital = orbitals
+
+    densityOfStates, dispersionArray = getDensityOfStates(tightBindDisp, size_BZ)
+
+    cutOffEnergies = getCutOffEnergy(size_BZ)
+
+    # Kondo coupling must be stored in a 3D matrix. Two of the dimensions store the 
+    # incoming and outgoing momentum indices, while the third dimension stores the 
+    # behaviour along the RG flow. For example, J[i][j][k] reveals the value of J 
+    # for the momentum pair (i,j) at the k^th Rg step.
+    kondoJArray = initialiseKondoJ(size_BZ, impOrbital, trunc(Int, (size_BZ + 1) / 2), J_val)
+
+    # define flags to track whether the RG flow for a particular J_{k1, k2} needs to be stopped 
+    # (perhaps because it has gone to zero, or its denominator has gone to zero). These flags are
+    # initialised to one, which means that by default, the RG can proceed for all the momenta.
+    proceed_flags = fill(1, size_BZ^2, size_BZ^2)
+
+    # Run the RG flow starting from the maximum energy, down to the penultimate energy (ΔE), in steps of ΔE
+
+    fixedpointEnergy = minimum(cutOffEnergies)
+    @showprogress enabled = progressbarEnabled for (stepIndex, energyCutoff) in enumerate(cutOffEnergies[1:end-1])
+        deltaEnergy = abs(cutOffEnergies[stepIndex+1] - cutOffEnergies[stepIndex])
+
+        # set the Kondo coupling of all subsequent steps equal to that of the present step 
+        # for now, so that we can just add the renormalisation to it later
+        kondoJArray[:, :, stepIndex+1] = kondoJArray[:, :, stepIndex]
+
+        # if there are no enabled flags (i.e., all are zero), stop the RG flow
+        if all(==(0), proceed_flags)
[…]

### 2024-04-23 dwaveNumerics/caller.jl
some more parallelisation

@@ -2,4 +2,5 @@ include("./source/main.jl")
 
 J_val = 0.1
 size_BZ = 45
-manager(size_BZ, -2.0, J_val, [0.0, -1.3, -2.3, -2.9, -3.9, -4.9, -28.0] ./ size_BZ, ("p", "p"), ["spinFlipCorrMap"])
+manager(size_BZ, -2.0, J_val, [0.0, -2.9, -28.0] ./ size_BZ, ("p", "p"), ["spinFlipCorrMap"])
+# manager(size_BZ, -2.0, J_val, [0.0, -1.3, -2.3, -2.9, -3.9, -4.9, -28.0] ./ size_BZ, ("p", "p"), ["spinFlipCorrMap"])

### 2024-04-23 dwaveNumerics/source/main.jl

@@ -17,7 +17,7 @@ update_theme!(fontsize=30)
 animName(orbitals, size_BZ, omega_by_t, scale, W_by_J_min, W_by_J_max, J_val) = "$(orbitals[1])-$(orbitals[2])_$(size_BZ)_$(omega_by_t)_$(round(W_by_J_min, digits=4))_$(round(W_by_J_max, digits=4))_$(round(J_val, digits=4))_$(FIG_SIZE[1] * scale)x$(FIG_SIZE[2] * scale)"
 
 
-function manager(size_BZ::Int64, omega_by_t::Float64, J_val::Float64, W_by_J_range::Vector{Float64}, orbitals::Tuple{String,String}, probes::Vector{String}; figScale::Float64=1.0; saveDir::String="./data/")
+function manager(size_BZ::Int64, omega_by_t::Float64, J_val::Float64, W_by_J_range::Vector{Float64}, orbitals::Tuple{String,String}, probes::Vector{String}; figScale::Float64=1.0, saveDir::String="./data/")
     # ensure that [0, \pi] has odd number of states, so 
     # that the nodal point is well-defined.
     @assert (size_BZ - 5) % 4 == 0 "Size of Brillouin zone must be of the form N = 4n+5, n=0,1,2..., so that all the nodes and antinodes are well-defined."

### 2024-04-23 dwaveNumerics/source/probes.jl

@@ -1,8 +1,8 @@
 using LinearAlgebra
 using CairoMakie
 using Makie
-include("../../../fermionise/source/fermionise.jl")
-include("../../../fermionise/source/models.jl")
+@everywhere include("../../../fermionise/source/fermionise.jl")
+@everywhere include("../../../fermionise/source/models.jl")
 
 function scattProb(kondoJArray::Array{Float64,3}, stepIndex::Int64, size_BZ::Int64, dispersion::Vector{Float64}, fixedpointEnergy::Float64)
     results = zeros(size_BZ^2)
@@ -34,32 +34,27 @@ function kondoCoupMap(k_vals, size_BZ, kondoJArrayFull)
 end
 
 
-function spinFlipCorrMap(size_BZ::Int64, kondoJArrayFull, W_val::Float64, orbitals::Tuple{String,String})
+function spinFlipCorrMap(k_index::Int64, size_BZ::Int64, kondoJArrayFull, W_val::Float64, orbitals::Tuple{String,String})
     k_indices = collect(1:size_BZ^2)
-    results = zeros(length(k_indices))
-    trunc_dim = 4
+    # operator list for the operator S_d^+ c^†_{k ↓} c_{k ↑} + h.c.
+    spinFlipCorrOplist = [("+-+-", 1.0, [1, 2, 4, 3]), ("+-+-", 1.0, [2, 1, 3, 4])]
+
+    trunc_dim = 3
     basis = BasisStates(trunc_dim * 2 + 2)
 
-    # operator list for the operator S_d^+ c^†_{k ↓} c_{k ↑} + h.c.
-    spinFlipCorrOplist = [("+-+-", 1., [1, 2, 4, 3]), ("+-+-", 1., [2, 1, 3, 4])]
+    other_k_indices = k_indices[k_indices.≠k_index]
+    chosenIndices = [[k_index]; other_k_indices[sortperm(kondoJArrayFull[k_index, other_k_indices, end], rev=true)][1:trunc_dim-1]]
+    mapSeq = Dict(index => i for (i, index) in enumerate(chosenIndices))
 
-    @showprogress for k_index in k_indices
-        other_k_indices = k_indices[k_indices .≠ k_index]
-        chosenIndices = [[k_index]; other_k_indices[sortperm(kondoJArrayFull[k_index, other_k_indices, end], rev=true)][1:trunc_dim-1]]
-        mapSeq = Dict(index => i for (i, index) in enumerate(chosenIndices))
-
[…]

### 2024-06-10 TilingProjectDraft/tilingProject.tex
simplified large parts of the codebase

@@
 \begin{equation}\begin{aligned}
-	\tilde S_\text{EE}^{\text{(loc)}} = S_\text{EE}^{(\text{imp.})}~.
-\end{aligned}\end{equation}
+	\tilde S_\text{EE}({\bf r}_c;\sigma) = S_\text{EE}(d;\sigma)~,
+\end{aligned}\end{equation}
+where \(S_\text{EE}(d)\) is the entanglement entropy of the impurity site.
 
@@
 \begin{equation}\begin{aligned}
-	\overline\rho_{({\bf r}_c, {\bf r}_c + {\bf r}),\sigma} = c^\dagger_{{\bf r}_c + {\bf r},\sigma} \overline\rho_{{\bf r}_c,\sigma} c_{{\bf r}_c + {\bf r},\sigma} + n_{{\bf r}_c + {\bf r},\sigma} \overline\rho_{{\bf r}_c,\sigma} n_{{\bf r}_c + {\bf r},\sigma}~.
-\end{aligned}\end{equation}
+	\overline\rho_{({\bf r}_c, {\bf r}_c + {\bf r}),\sigma} = c^\dagger_{{\bf r}_c + {\bf r},\sigma} \overline\rho_{{\bf r}_c,\sigma} c_{{\bf r}_c + {\bf r},\sigma} + n_{{\bf r}_c + {\bf r},\sigma} \overline\rho_{{\bf r}_c,\sigma} n_{{\bf r}_c + {\bf r},\sigma}~,
+\end{aligned}\end{equation}
+leading to the expression
+\begin{equation}\begin{aligned}
+	\tilde S_\text{EE}\left({\bf r}_c, {\bf r}_c + {\bf r};\sigma\right) = S_\text{EE}(d, {\bf r};\sigma)~,
+\end{aligned}\end{equation}
+where \(S_\text{EE}(d, r)\) is the entanglement entropy of the impurity site and the conduction bath site at a distance \({\bf r}\) from it.
 
@@
 \end{aligned}\end{equation}
-The eigenvalues of this operator can be used to compute the entanglement entropy of the state \({\bf K}\sigma\).
+The eigenvalues of this operator can be used to compute the entanglement entropy of the state \({\bf K}\sigma\). If we define an {\it off-site} entanglement entropy 
+\begin{equation}\begin{aligned}
+	S^\prime_{\text{EE}}(\nu_1,\nu_2) = -\text{Tr}\left[\rho_{\nu_1,\nu_2}\ln \rho_{\nu_1,\nu_2}\right]
+\end{aligned}\end{equation}
+with 
+\begin{equation}\begin{aligned}
+	\rho_{\nu_1,\nu_2} = (c^\dagger_{\nu_1} \tilde\rho_\text{gs} c_{\nu_2} + n_{\nu_1} \tilde\rho_\text{gs} n_{\nu_2}) + \text{h.c.}~,
+\end{aligned}\end{equation}
+we can frame the expression for the \(k-\)space entanglement entropy in terms of the auxiliary model off-site entanglement entropy:
+\begin{equation}\begin{aligned}
+	S_\text{EE}({\bf K};\sigma) = S^\prime_\text{EE}\left(d, {\bf K};\sigma\right) 
+\end{aligned}\end{equation}
+
 Using the same approach as that for the real space case, the reduced density matrix for two \(k-\)states is again obtained by tracing out the second \(k-\)state from this density matrix:
@@
 	&+ \left. c^\dagger_{{\bf r}_c,\sigma} \overline\rho_{{\bf K}_1,\sigma} c_{{\bf K}_2,\sigma} + n_{{\bf r}_c,\sigma} \overline\rho_{{\bf K}_1,\sigma} n_{{\bf K}_2,\sigma}\right] ~.
+\end{aligned}\end{equation}
+This straightforwardly leads to the relation
+\begin{equation}\begin{aligned}
+	S_\text{EE}({\bf K}_1,{\bf K}_2;\sigma) = S^\prime_\text{EE}\left(d, {\bf K}_1;\sigma\right) + S^\prime_\text{EE}\left(d, {\bf K}_2;\sigma\right)
 \end{aligned}\end{equation}

### 2024-06-10 dwaveNumerics/caller.jl

@@ -1,8 +1,0 @@
-include("./source/main.jl")
-
-manager(5, -2.0, 1.0, [0.0], ("p", "p"), ["scattProb"])
-
-J_val = 0.1
-size_BZ = 25
-manager(size_BZ, -2.0, J_val, [-9.4, -9.5, -9.65] ./ size_BZ, ("p", "p"), ["scattProb", "spinFlipCorrMap"])
-# manager(size_BZ, -2.0, J_val, collect(-18:-0.1:-18.2) ./ size_BZ, ("p", "p"), ["scattProb", "spinFlipCorrMap"])

### 2024-06-10 dwaveNumerics/source/main.jl

@@ -1,142 +1,0 @@
-using JLD2
-using ProgressMeter
-include("./rgFlow.jl")
-include("./probes.jl")
-include("./plotting.jl")
-
-# file name format for saving plots and animations
-animName(orbitals, size_BZ, omega_by_t, scale, W_by_J_min, W_by_J_max, J_val) = "$(orbitals[1])-$(orbitals[2])_$(size_BZ)_$(omega_by_t)_$(round(W_by_J_min, digits=4))_$(round(W_by_J_max, digits=4))_$(round(J_val, digits=4))_$(FIG_SIZE[1] * scale)x$(FIG_SIZE[2] * scale)"
-
-
-function manager(size_BZ::Int64, omega_by_t::Float64, J_val::Float64, W_by_J_range::Vector{Float64}, orbitals::Tuple{String,String}, probes::Vector{String}; figScale::Float64=1.0, saveDir::String="./data/")
-
-    # determines whether the inner loops (RG iteration, for a single value of W)
-    # should show progress bars.
-    progressbarEnabled = length(W_by_J_range) == 1 ? true : false
-
-    # file paths for saving RG flow results, specifically bare and fixed point values of J as well as the dispersion
-    savePaths = [saveDir * "$(orbitals)_$(size_BZ)_$(round(J_val, digits=3))_$(round(W_by_J, digits=3)).jld2" for W_by_J in W_by_J_range]
-
-    # create the data save directory if it doesn't already exist
-    isdir(saveDir) || mkdir(saveDir)
-
-    # loop over all given values of W/J, get the fixed point distribution J(k1,k2) and save them in files
-    @showprogress Threads.@threads for (j, W_by_J) in collect(enumerate(W_by_J_range))
-        kondoJArrayFull, dispersion = momentumSpaceRG(size_BZ, omega_by_t, J_val, J_val * W_by_J, orbitals; progressbarEnabled=progressbarEnabled)
-        jldopen(savePaths[j], "w") do file
-            file["kondoJArray"] = kondoJArrayFull[:, :, [1, end]]
-            file["dispersion"] = dispersion
-        end
-    end
-
-    # loop over the various probes that has been requested
-    @showprogress for probeName in probes
-        pdfFileNames = ["fig_$(W_by_J)_$probeName.pdf" for W_by_J in W_by_J_range]
-
-        # loop over each value of W/J to calculate the probe for that value
[…]

### 2024-06-10 dwaveNumerics/source/plotting.jl

@@ -1,58 +1,0 @@
-using Plots
-using LaTeXStrings
-using Measures
-(@isdefined DISCRETE_CGRAD) || const DISCRETE_CGRAD = cgrad(:BuPu_3, 3, categorical=true)
-
-function plotHeatmaps(results_arr, x_arr, y_arr, cmaps, subtitles)
-    plots = []
-    for (i, result) in enumerate(results_arr)
-        reshaped_result = reshape(result, (length(x_arr), length(y_arr)))
-        hmap = heatmap(x_arr, y_arr, reshaped_result, xlabel=L"$ak_x/\pi$", ylabel=L"$ak_y/\pi$", c=cmaps[i], title=subtitles[i], top_margin=3mm, left_margin=5mm, bottom_margin=5mm
-        )
-        push!(plots, hmap)
-    end
-    return plots
-end
-
-
-function mainPlotter(results_arr::Vector{Vector{Float64}}, probeName::String, size_BZ::Int64, titleText::LaTeXString)
-    subtitles = Vector{LaTeXString}(undef, length(results_arr))
-    cmaps = [DISCRETE_CGRAD, :BuPu_3, :BuPu_3]
-    if probeName == "scattProb"
-        subtitles[1] = L"\mathrm{rel(irrel)evance~of~}\Gamma(k)"
-        subtitles[2] = L"\Gamma(k)/\Gamma^{(0)}(k)"
-    elseif probeName == "kondoCoupNodeMap"
-        subtitles[1] = L"\mathrm{rel(irrel)evance~of~}J(k,q_\mathrm{node})"
-        subtitles[2] = L"J(k,q_\mathrm{node})"
-        drawPoint = (-0.5, -0.5)
-    elseif probeName == "kondoCoupAntinodeMap"
-        subtitles[1] = L"\mathrm{rel(irrel)evance~of~}J(k,q_\mathrm{antin.})"
-        subtitles[2] = L"J(k,q_\mathrm{antin.})"
-        drawPoint = (0, -1)
-    elseif probeName == "kondoCoupOffNodeMap"
-        offnode = (-pi / 2 + 4 * pi / size_BZ, -pi / 2 + 4 * pi / size_BZ)
-        subtitles[1] = L"\mathrm{rel(irrel)evance~of~}J(k,q^\prime_\mathrm{node})"
-        subtitles[2] = L"J(k,q^\prime_\mathrm{node})"
-        drawPoint = offnode ./ pi
[…]

### 2024-06-10 numerics/caller.jl

@@ -1,0 +1,38 @@
+include("./source/main.jl")
+include("./source/plotting.jl")
+
+J_val = 0.1
+size_BZ = 33
+omega_by_t = -2.0
+W_by_J_arr = -1.0 .* [57.5, 59, 60, 62] ./ size_BZ
+orbitals = ("p", "p")
+savePaths = rgFlowData(size_BZ, omega_by_t, J_val, W_by_J_arr, orbitals)
+
+fig, axes = plt.subplots(length(savePaths), 2)
+for (i, savePath) in enumerate(savePaths)
+    jldopen(savePath, "r"; compress=true) do file
+    kondoJArray = file["kondoJArray"]
+    dispersion = file["dispersion"]
+    W_val = file["W_val"]
+    size_BZ = file["size_BZ"]
+    orbitals = file["orbitals"]
+
+    averageKondoScale = sum(abs.(kondoJArray[:, :, 1])) / length(kondoJArray[:, :, 1])
+    @assert averageKondoScale > RG_RELEVANCE_TOL
+    kondoJArray[:, :, end] .= ifelse.(abs.(kondoJArray[:, :, end]) ./ averageKondoScale .> RG_RELEVANCE_TOL, kondoJArray[:, :, end], 0)
+    dispersion = file["dispersion"]
+
+    # reshape to 1D array of size N^2 into 2D array of size NxN, so that we can plot it as kx vs ky.
+    # kondoJArray = reshape(kondoJArray[:,:,[1,end]], (size_BZ^2, size_BZ^2, 2))
+
+    results_arr = scattProb(kondoJArray, size_BZ, dispersion)
+    results_arr[1] .= log10.(results_arr[1])
+    x_arr = y_arr = range(K_MIN, stop=K_MAX, length=size_BZ) ./ pi
+    subtitles = [L"\mathrm{rel(irrel)evance~of~}\Gamma(k)", L"\Gamma(k)/\Gamma^{(0)}(k)"]
+    fig, axes[i-1, 0:1] = plotHeatmaps(axes[i-1, 0:1], results_arr, x_arr, y_arr)
+    end
+end
+fig.show()
+# fig = plot(figs..., size=(250 * 2, 250 * length(savePaths)), layout = grid(length(savePaths), 2))
[…]

### 2024-06-10 numerics/source/constants.jl

@@ -9,7 +9,7 @@
 (@isdefined HOP_T) || const HOP_T = 1.0
 
 (@isdefined FIG_SIZE) || const FIG_SIZE = (700, 350)
-(@isdefined RG_RELEVANCE_TOL) || const RG_RELEVANCE_TOL = 1e-2
+(@isdefined RG_RELEVANCE_TOL) || const RG_RELEVANCE_TOL = 1e-5
 
 (@isdefined ALLOWED_PROBES) || const ALLOWED_PROBES = ["scattProb", "kondoCoupNodeMap", "kondoCoupAntinodeMap", "kondoCoupOffNodeMap", "kondoCoupOffAntinodeMap", "spinFlipCorrMap"]
 (@isdefined PLOT_SIZE) || const PLOT_SIZE = (400, 300)

### 2024-06-10 numerics/source/helpers.jl

@@ -136,7 +136,7 @@ function tolerantSign(quant, boundary)
 end
 
 
-function blockSpectrum(size_BZ::Int64, dispersion::Vector{Float64}, kondoJArray::Array{Float64,3}, W_val::Float64, orbitals::Tuple{String,String}; trunc_dim::Int64=2)
+function getBlockSpectrum(size_BZ::Int64, dispersion::Vector{Float64}, kondoJArray::Array{Float64,3}, W_val::Float64, orbitals::Tuple{String,String}; trunc_dim::Int64=2)
 
     # generate basis states for constructing prototype Hamiltonians which
     # will be diagonalised to obtain correlations
@@ -174,8 +174,8 @@ function blockSpectrum(size_BZ::Int64, dispersion::Vector{Float64}, kondoJArray:
         end
         matrixSet = fermions.generalOperatorMatrix(basis, operatorList, collect(keys(uniqueHamiltonianSequences)))
         eigenSet = fetch.([Threads.@spawn fermions.getSpectrum(matrix) for matrix in matrixSet])
-        push!(spectrumSet, eigenInfo)
+        push!(spectrumSet, eigenSet)
         push!(sequenceSets, uniqueHamiltonianSequences)
     end
-    return energyContour, spectrumSet, sequenceSets
+    return energyContours, spectrumSet, sequenceSets
 end

### 2024-06-10 numerics/source/main.jl

@@ -1,0 +1,92 @@
+using JLD2
+using ProgressMeter
+include("./rgFlow.jl")
+include("./probes.jl")
+
+# file name format for saving plots and animations
+animName(orbitals, size_BZ, omega_by_t, scale, W_by_J_min, W_by_J_max, J_val) = "$(orbitals[1])-$(orbitals[2])_$(size_BZ)_$(omega_by_t)_$(round(W_by_J_min, digits=4))_$(round(W_by_J_max, digits=4))_$(round(J_val, digits=4))_$(FIG_SIZE[1] * scale)x$(FIG_SIZE[2] * scale)"
+
+
+function rgFlowData(size_BZ::Int64, omega_by_t::Float64, J_val::Float64, W_by_J_range::Vector{Float64}, orbitals::Tuple{String,String}; saveDir::String="./data/")
+    # determines whether the inner loops (RG iteration, for a single value of W)
+    # should show progress bars.
+    progressbarEnabled = length(W_by_J_range) == 1 ? true : false
+
+    # file paths for saving RG flow results, specifically bare and fixed point values of J as well as the dispersion
+    savePaths = [saveDir * "$(orbitals)_$(size_BZ)_$(round(J_val, digits=5))_$(round(W_by_J, digits=5)).jld2" for W_by_J in W_by_J_range]
+
+    # create the data save directory if it doesn't already exist
+    isdir(saveDir) || mkdir(saveDir)
+
+    # loop over all given values of W/J, get the fixed point distribution J(k1,k2) and save them in files
+    @showprogress for (j, W_by_J) in collect(enumerate(W_by_J_range))
+        W_val = J_val * W_by_J
+        kondoJArrayFull, dispersion = momentumSpaceRG(size_BZ, omega_by_t, J_val, W_val, orbitals; progressbarEnabled=progressbarEnabled)
+        jldopen(savePaths[j], "w") do file
+            file["kondoJArray"] = kondoJArrayFull
+            file["dispersion"] = dispersion
+            file["W_val"] = W_val
+            file["size_BZ"] = size_BZ
+            file["orbitals"] = orbitals
+        end
+    end
+    return savePaths
+end
+
+
+function getCorrelations(savePaths, corrDefArray; tile=false)
+    correlationResults = []
+    for savePath in savePaths
+        jldopen(savePath, "r"; compress=true) do file
+        kondoJArray = file["kondoJArray"]
+        dispersion = file["dispersion"]
[…]

### 2024-06-10 numerics/source/plotting.jl

@@ -1,0 +1,14 @@
+import PythonPlot
+const plt = PythonPlot
+using LaTeXStrings
+using Measures
+# DISCRETE_CGRAD = cgrad(:seaborn_rocket_gradient, 2, categorical=true)
+
+function plotHeatmaps(axes, results_arr, x_arr, y_arr)
+    for (ax, result) in zip(axes, results_arr)
+        reshaped_result = reshape(result, (length(x_arr), length(y_arr)))
+        image = ax.imshow(reshaped_result, aspect=1, origin="lower")
+        fig.colorbar(image, cax=ax)
+    end
+    return fig, axes
+end

### 2024-06-10 numerics/source/probes.jl

@@ -33,9 +33,12 @@ function scattProb(kondoJArray::Array{Float64,3}, size_BZ::Int64, dispersion::Ve
     end
 
     # get a boolean representation of results for visualisation, using the mapping
-    results_bool = ifelse.(abs.(results) .> TOLERANCE, 1, 0)
+    results_scaled = results ./ results_bare
+    results_bool = ifelse.(abs.(results_scaled) .> RG_RELEVANCE_TOL, 1, 0)
+    results_scaled[abs.(results_scaled) .< 1e-3] .= 1e-3
+    results_scaled[results_bool .== 0] .= 0
 
-    return results ./ results_bare, results_bool
+    return results_scaled, results_bool
 end
 
 
@@ -94,19 +97,7 @@ function sampleKondoIntAndBathInt(sequenceSet::Vector{Vector{Int64}}, dispersion
 end
 
 
-function correlationMap(size_BZ::Int64, dispersion::Vector{Float64}, kondoJArray::Array{Float64,3}, W_val::Float64, orbitals::Tuple{String,String}, correlationDefinition; trunc_dim::Int64=2)
-
-    _, resultsScattProbBool = scattProb(kondoJArray, size_BZ, dispersion)
-
-    # get all possible indices of momentum states within the Brillouin zone
-    k_indices = collect(1:size_BZ^2)
-
-    for index in k_indices
-        if resultsScattProbBool[index] == -1
-            kondoJArray[index, :, end] .= 0
-            kondoJArray[:, index, end] .= 0
-        end
-    end
+function correlationMap(size_BZ, energyContours, spectrumSet, sequenceSets, correlationDefinition)
 
     # initialise zero array for storing correlations
     results = zeros(size_BZ^2)
@@ -115,45 +106,16 @@ function correlationMap(size_BZ::Int64, dispersion::Vector{Float64}, kondoJArray
     # appears in the computation. Needed to finally average over all combinations.
     contributorCounter = zeros(size_BZ^2)
 
-    # generate basis states for constructing prototype Hamiltonians which
-    # will be diagonalised to obtain correlations
-    basis = fermions.BasisStates(trunc_dim * 2 + 2; totOccupancy=[trunc_dim + 1])
-
     # define correlation operators for all k-states within Brillouin zone.
-    correlationOperatorList = [correlationDefinition(i) for i in 1:trunc_dim]
+    correlationOperatorList = [correlationDefinition(i) for i in 1:length(sequenceSets[1])]
 
     # loop over energy scales and calculate correlation values at each stage.
[…]

### 2024-06-10 numerics/caller.jl
--no-message

@@ -2,13 +2,15 @@ include("./source/main.jl")
 include("./source/plotting.jl")
 
 J_val = 0.1
-size_BZ = 33
+size_BZ = 13
 omega_by_t = -2.0
 W_by_J_arr = -1.0 .* [57.5, 59, 60, 62] ./ size_BZ
 orbitals = ("p", "p")
 savePaths = rgFlowData(size_BZ, omega_by_t, J_val, W_by_J_arr, orbitals)
+x_arr = range(K_MIN, stop=K_MAX, length=size_BZ) ./ pi
+collatedResults = []
+saveName = "$(orbitals[1])-$(orbitals[2])_$(size_BZ)_$(omega_by_t)_$(round(minimum(W_by_J_arr), digits=4))_$(round(maximum(W_by_J_arr), digits=4))_$(round(J_val, digits=4))"
 
-fig, axes = plt.subplots(length(savePaths), 2)
 for (i, savePath) in enumerate(savePaths)
     jldopen(savePath, "r"; compress=true) do file
     kondoJArray = file["kondoJArray"]
@@ -22,17 +24,9 @@ for (i, savePath) in enumerate(savePaths)
     kondoJArray[:, :, end] .= ifelse.(abs.(kondoJArray[:, :, end]) ./ averageKondoScale .> RG_RELEVANCE_TOL, kondoJArray[:, :, end], 0)
     dispersion = file["dispersion"]
 
-    # reshape to 1D array of size N^2 into 2D array of size NxN, so that we can plot it as kx vs ky.
-    # kondoJArray = reshape(kondoJArray[:,:,[1,end]], (size_BZ^2, size_BZ^2, 2))
-
     results_arr = scattProb(kondoJArray, size_BZ, dispersion)
-    results_arr[1] .= log10.(results_arr[1])
-    x_arr = y_arr = range(K_MIN, stop=K_MAX, length=size_BZ) ./ pi
-    subtitles = [L"\mathrm{rel(irrel)evance~of~}\Gamma(k)", L"\Gamma(k)/\Gamma^{(0)}(k)"]
-    fig, axes[i-1, 0:1] = plotHeatmaps(axes[i-1, 0:1], results_arr, x_arr, y_arr)
+    push!(collatedResults, [log10.(results_arr[1]), results_arr[2]])
     end
 end
-fig.show()
[…]

### 2024-06-10 numerics/source/plotting.jl

@@ -1,14 +1,13 @@
-import PythonPlot
-const plt = PythonPlot
-using LaTeXStrings
-using Measures
-# DISCRETE_CGRAD = cgrad(:seaborn_rocket_gradient, 2, categorical=true)
+using PyPlot
 
-function plotHeatmaps(axes, results_arr, x_arr, y_arr)
-    for (ax, result) in zip(axes, results_arr)
-        reshaped_result = reshape(result, (length(x_arr), length(y_arr)))
-        image = ax.imshow(reshaped_result, aspect=1, origin="lower")
-        fig.colorbar(image, cax=ax)
+function plotHeatmaps(x_arr, collatedResults, saveName)
+    fig, axes = PyPlot.subplots(size(collatedResults)...)
+    for (i, results_arr) in enumerate(collatedResults)
+        for (ax, result) in zip(axes[i], results_arr)
+            reshaped_result = reshape(result, (length(x_arr), length(y_arr)))
+            image = ax.imshow(reshaped_result, aspect=1, origin="lower")
+            fig.colorbar(image, cax=ax)
+        end
     end
-    return fig, axes
 end
+

### 2024-06-20 numerics/caller.jl
added README with partial implementation details

@@ -86,8 +86,6 @@ function corr()
         end
     end
 
-    # saveName = "spin-$(orbitals[1])-$(orbitals[2])_$(size_BZ)_$(omega_by_t)_$(round(minimum(W_by_J_arr), digits=4))_$(round(maximum(W_by_J_arr), digits=4))_$(round(J_val, digits=4)).pdf"
-    # plotHeatmaps([x_arr, x_arr], [L"$ak_x/\pi$", L"$ak_y/\pi$"], [L"$\chi_s(d, \vec k)$", L"relevance of $\chi_s(d, \vec k)$"], collatedResultsSpin, saveName)
     saveName = "charge-$(orbitals[1])-$(orbitals[2])_$(size_BZ)_$(omega_by_t)_$(round(minimum(W_by_J_arr), digits=4))_$(round(maximum(W_by_J_arr), digits=4))_$(round(J_val, digits=4)).pdf"
     plotHeatmaps([x_arr, x_arr], [L"ak_x/\pi", L"ak_y/\pi"], [L"\chi_s(d, \vec{k})", L"\chi_c(\vec{k})", L"n_{k\uparrow}n_{k\downarrow}"], subFigTitles, collatedResultsCharge, saveName)
     saveName = "vne-$(orbitals[1])-$(orbitals[2])_$(size_BZ)_$(omega_by_t)_$(round(minimum(W_by_J_arr), digits=4))_$(round(maximum(W_by_J_arr), digits=4))_$(round(J_val, digits=4)).pdf"

### 2024-08-09 numerics/caller.jl
added phase diagram

@@ -8,99 +8,58 @@ include("./source/rgFlow.jl")
 include("./source/probes.jl")
 include("./source/plotting.jl")
 const J_val = 0.1
-const fractionBZ = 0.01
-const size_BZ = 17
 const omega_by_t = -2.0
-const W_by_J_arr = -1.0 .* [0, 24, 25, 26.5, 27] ./ size_BZ
 const orbitals = ("p", "p")
-const savePaths = rgFlowData(size_BZ, omega_by_t, J_val, W_by_J_arr, orbitals)
-const x_arr = range(K_MIN, stop=K_MAX, length=size_BZ) ./ pi
 const cmap = :YlOrBr
+fractionBZ = 0.2
+size_BZ = 17
+W_val_arr = -1.0 .* [2.6, 2.8] ./ size_BZ
+x_arr = range(K_MIN, stop=K_MAX, length=size_BZ) ./ pi
 
-function probe()
+node = map2DTo1D(float(π)/2, float(π)/2, size_BZ)
+antinode = map2DTo1D(float(π), 0.0, size_BZ)
+genpoint = map2DTo1D(float(3 * π / 4), 0.0, size_BZ)
+
+densityOfStates, dispersion = getDensityOfStates(tightBindDisp, size_BZ)
+kondoJArrays = Dict()
+for W_val in W_val_arr
+    kondoJArray, _ = momentumSpaceRG(size_BZ, omega_by_t, J_val, W_val, orbitals)
+    averageKondoScale = sum(abs.(kondoJArray[:, :, 1])) / length(kondoJArray[:, :, 1])
+    @assert averageKondoScale > RG_RELEVANCE_TOL
+    kondoJArray[:, :, end] .= ifelse.(abs.(kondoJArray[:, :, end]) ./ averageKondoScale .> RG_RELEVANCE_TOL, kondoJArray[:, :, end], 0)
+    kondoJArrays[W_val] = kondoJArray
+end
+
+function probe(kondoJArrays, dispersion)
     collatedResults = []
     subFigTitles = []
-    for (i, savePath) in enumerate(savePaths)
-        jldopen(savePath, "r"; compress=true) do file
-        kondoJArray = file["kondoJArray"]
-        dispersion = file["dispersion"]
-        W_val = file["W_val"]
-        size_BZ = file["size_BZ"]
-        orbitals = file["orbitals"]
-        dispersion = file["dispersion"]
+    @time for W_val in W_val_arr
[…]

### 2024-08-09 numerics/callerPhaseDiagram.jl

@@ -1,0 +1,47 @@
+using ProgressMeter, Measures, CairoMakie
+
+const TRUNC_DIM = 2
+include("./source/constants.jl")
+include("./source/helpers.jl")
+include("./source/rgFlow.jl")
+include("./source/probes.jl")
+
+const colorSet = resample_cmap(:YlOrBr, 3)
+function getPhase(J_val, W_val)
+    kondoJArray, dispersion = momentumSpaceRG(size_BZ, omega_by_t, J_val, W_val, orbitals)
+    averageKondoScale = sum(abs.(kondoJArray[:, :, 1])) / length(kondoJArray[:, :, 1])
+    @assert averageKondoScale > RG_RELEVANCE_TOL
+    kondoJArray[:, :, end] .= ifelse.(abs.(kondoJArray[:, :, end]) ./ averageKondoScale .> RG_RELEVANCE_TOL, kondoJArray[:, :, end], 0)
+    scattProbBool = scattProb(kondoJArray, size_BZ, dispersion, fractionBZ)[2]
+    if all(>(0), scattProbBool[fermiPoints])
+        return 1
+    elseif all(==(0), scattProbBool[fermiPoints])
+        return 3
+    else
+        return 2
+    end
+end
+
+const omega_by_t::Float64 = -2.0
+const orbitals::Tuple{String, String} = ("p", "p")
+const numPoints::Int64 = 100
+const fractionBZ::Float64 = 0.3
+const size_BZ::Int64 = 17
+
+densityOfStates, dispersionArray = getDensityOfStates(tightBindDisp, size_BZ)
+node = map2DTo1D(float(π)/2, float(π)/2, size_BZ)
+antinode = map2DTo1D(float(π), 0.0, size_BZ)
+fermiPoints = unique(getIsoEngCont(dispersionArray, 0.0))
+
+W_val_arr = -1.0 * range(0.0, stop=0.3, length=numPoints)
+J_val_arr = 1.0 * range(0.05, stop=0.6, length=numPoints)
+
+@time phaseDiagram = [getPhase(J_val_arr[i], W_val_arr[j]) for (i, j) in Iterators.product(1:numPoints, 1:numPoints)]
+println(unique(phaseDiagram))
+f = Figure()
+ax = Axis(f[1, 1])
+heatmap!(ax, J_val_arr, -1 .* W_val_arr, phaseDiagram;
[…]

### 2024-08-09 numerics/python/mOrbRG.py

@@ -1,250 +1,0 @@
-import numpy as np
-from itertools import product
-from tqdm import tqdm
-from multiprocessing import Pool
-
-K_MIN = -np.pi
-K_MAX = np.pi
-
-
-def getHolePoint(point, size):
-    kx_val, ky_val = map1Dto2D(point, size)
-    kx_new = (
-        kx_val + (K_MAX - K_MIN) / 2
-        if kx_val < (K_MAX + K_MIN) / 2
-        else kx_val - (K_MAX - K_MIN) / 2
-    )
-    ky_new = (
-        ky_val + (K_MAX - K_MIN) / 2
-        if ky_val < (K_MAX + K_MIN) / 2
-        else ky_val - (K_MAX - K_MIN) / 2
-    )
-    new_point = map2Dto1D(kx_new, ky_new, size)
-    return new_point
-
-
-def bathIntFunc(k_points, bathIntType, size):
-    assert bathIntType in ("d", "p")
-    k_points = np.asarray(k_points)
-    kx_arr, ky_arr = map1Dto2D(k_points, size)
-    if bathIntType == "d":
-        return np.prod(np.cos(kx_arr) - np.cos(ky_arr))
-    else:
-        return 0.5 * (
-            np.cos(kx_arr[0] + kx_arr[2] - kx_arr[1] - kx_arr[3])
-            + np.cos(ky_arr[0] + ky_arr[2] - ky_arr[1] - ky_arr[3])
-        )
-
-
-def map2Dto1D(kx_val, ky_val, size):
-    k_1Darr = np.linspace(K_MIN, K_MAX, size)
-    kx_index = np.argmin(np.abs(k_1Darr - kx_val))
-    ky_index = np.argmin(np.abs(k_1Darr - ky_val))
-    return ky_index * size + kx_index
-
-
-def map1Dto2D(points, size):
-    kx = points % size
-    ky = points // size
-    k_1Darr = np.linspace(K_MIN, K_MAX, size)
-    return k_1Darr[kx], k_1Darr[ky]
-
-
-def tightBindDispersion(size, hop_t):
-    k_1Darr = np.linspace(K_MIN, K_MAX, size)
-    kx_arr, ky_arr = np.meshgrid(k_1Darr, k_1Darr)
-    return -2 * hop_t * (np.cos(kx_arr) + np.cos(ky_arr))
-
-
-def getDensityofStates(size, dispersionFunc, hop_t):
[…]

### 2024-08-09 numerics/source/helpers.jl

@@ -166,95 +166,34 @@ function propagateIndices(index::Int64, size_BZ::Int64)
 end
 
 
-function getIterativeSpectrum(size_BZ::Int64, dispersion::Vector{Float64}, kondoJArray::Array{Float64,3}, W_val::Float64, orbitals::Tuple{String,String}, fractionBZ::Float64)
+function getIterativeSpectrum(size_BZ::Int64, dispersion::Vector{Float64}, kondoJArray::Matrix{Float64}, W_val::Float64, orbitals::Tuple{String,String}, fractionBZ::Float64)
     retainSize = 30
     energyContours = dispersion[1:trunc(Int, (size_BZ + 1)/2)] |> sort
     energyShells = energyContours[abs.(energyContours) ./ maximum(energyContours) .< fractionBZ]
     println("Working with ", length(energyShells), " shells.")
     southWestQuadrantIndices = [p for p in 1:size_BZ^2 if map1DTo2D(p, size_BZ)[1] <= 0 && map1DTo2D(p, size_BZ)[2] <= 0]
-    activeStates = Int64[]
-    numStatesFamily = Int64[]
     activeStatesArr = Vector{Vector{Int}}()
     newStatesArr = Vector{Int64}[]
-    currentStates = Int64[]
-    @showprogress desc="Hamiltonian family" for energy in energyShells
+    for energy in energyShells
         onShellStates = filter(x -> abs(dispersion[x] - energy) < TOLERANCE, southWestQuadrantIndices)
         kxvals, _ = map1DTo2D(onShellStates, size_BZ)
         for (point1, point2) in zip(onShellStates[sortperm(kxvals)], onShellStates[sortperm(kxvals, rev=true)])
-            if point1 ∈ currentStates || point2 ∈ currentStates
+            if !isempty(activeStatesArr) && (point1 ∈ activeStatesArr[end] || point2 ∈ activeStatesArr[end])
                 break
             end
             push!(newStatesArr, [point1, point2])
-            push!(currentStates, point1, point2)
-            push!(activeStatesArr, copy(currentStates))
-            push!(numStatesFamily, length(currentStates))
-        end
-    end
-    initBasis = fermions.BasisStates(2 + 2 * numStatesFamily[1]; 
-                                     occCriteria=x -> x == 1 + numStatesFamily[1],
-                                     localConstraint=x -> x[1] + x[2] == 1)
[…]

### 2024-08-09 numerics/source/main.jl

@@ -1,24 +1,0 @@
-using JLD2
-using ProgressMeter
-include("./constants.jl")
-include("./rgFlow.jl")
-include("./probes.jl")
-
-# file name format for saving plots and animations
-animName(orbitals, size_BZ, omega_by_t, scale, W_by_J_min, W_by_J_max, J_val) = "$(orbitals[1])-$(orbitals[2])_$(size_BZ)_$(omega_by_t)_$(round(W_by_J_min, digits=4))_$(round(W_by_J_max, digits=4))_$(round(J_val, digits=4))_$(FIG_SIZE[1] * scale)x$(FIG_SIZE[2] * scale)"
-
-
-function getCorrelations(size_BZ::Int64, dispersion::Vector{Float64}, kondoJArray::Array{Float64, 3}, W_val::Float64, orbitals::Tuple{String,String}, corrDefArray, cutoffFraction::Float64; twoParticle=0, tile=false)
-    correlationResults = [[] for _ in corrDefArray]
-    basis, suitableIndices, uniqueSequences, gstatesSet = getBlockSpectrum(size_BZ, dispersion, kondoJArray, W_val , orbitals, cutoffFraction)
-    for (i, correlationDefinition) in enumerate(corrDefArray)
-        if tile
-            results = correlationMap(size_BZ, basis, dispersion, suitableIndices, uniqueSequences, gstatesSet, correlationDefinition; twoParticle=twoParticle)
-        else
-            results = correlationMap(size_BZ, basis, dispersion, suitableIndices, uniqueSequences, gstatesSet, correlationDefinition; twoParticle=twoParticle)
-        end
-        push!(correlationResults[i], results...)
-    end
-    return correlationResults
-end
-

### 2024-08-09 numerics/source/models.jl

@@ -1,4 +1,4 @@
-function kondoKSpace(sequence::Vector{Int64}, dispersion::Vector{Float64}, kondoJArray::Array{Float64,3}, bathIntFunc; specialIndices=Int64[], tolerance::Float64=1e-16)
+function kondoKSpace(sequence::Vector{Int64}, dispersion::Vector{Float64}, kondoJArray::Matrix{Float64}, bathIntFunc; specialIndices=Int64[], tolerance::Float64=1e-16)
     specialIndices = ifelse(isempty(specialIndices), sequence, specialIndices)
 
     operatorList = Dict{Tuple{String,Vector{Int64}},Float64}()
@@ -6,6 +6,9 @@ function kondoKSpace(sequence::Vector{Int64}, dispersion::Vector{Float64}, kondo
     for (momIndex, index) in enumerate(specialIndices)
         energy = dispersion[index]
         energy = abs(energy) > tolerance ? energy : 0
+        if energy == 0
+            continue
+        end
         merge!(+, operatorList, Dict(("n", [2 * momIndex + 1]) => energy))
         merge!(+, operatorList, Dict(("n", [2 * momIndex + 2]) => energy))
     end
@@ -74,6 +77,7 @@ function kondoKSpace(sequence::Vector{Int64}, dispersion::Vector{Float64}, kondo
               )
 
     end
+    operatorList = [(k..., v) for (k,v) in operatorList]
     return operatorList
 end
 

### 2024-08-09 numerics/source/probes.jl

@@ -51,18 +51,16 @@ function kondoCoupMap(k_vals::Tuple{Float64,Float64}, size_BZ::Int64, kondoJArra
 end
 
 
-function correlationMap(gstates::Vector{Dict{BitVector, Float64}}, (corrDef, numLegs), mapStateToIndex)
+function correlationMap(savePath::String, corrDef::Function, numLegs::Int64, mapStateToIndex::Dict{Int64, Int64}, size_BZ::Int64)
 
     # initialise zero array for storing correlations
-    # results = ifelse(twoParticle == 0, zeros(size_BZ^2), zeros(size_BZ^2, size_BZ^2))
     results = zeros(repeat([size_BZ^2], numLegs)...)
 
     suitableIndices = collect(keys(mapStateToIndex))
-    corrDefArr = []
     for k_inds in combinations(suitableIndices, numLegs)
         hamInds = [mapStateToIndex[ind] for ind in k_inds]
         corrOperator = corrDef(hamInds...)
-        results[k_inds...] = sum([abs(fermions.gstateCorrelation(gstate, corrOperator)) for gstate in gstates]) / length(gstates)
+        results[k_inds...] = IterCorrelation(savePath, corrOperator)
     end
 
     Threads.@threads for index in suitableIndices

### 2024-09-08 iterDiagAlgorithm/iterDiagAlgo.tex
wrote up algorithm for iterative diagonalisation

\documentclass[reprint]{revtex4-2}
\usepackage{braket,amsmath,amssymb,color,graphicx,bookmark,bm}
\begin{document}

\title{Iterative Ground State Approach Algorithm}
\begin{abstract}
	The following is the algorithm for performing an iterative diagonalization of fermionic systems. It is mostly similar to DMRG and NRG, and allows obtaining the low-energy spectrum large many-body Hamiltonians.
\end{abstract}
\date{\today}
\maketitle

%

\section{Structure of Hamiltonian and Operators}
\subsection{Jordan-Wigner Matrix Representation of Fermionic Operators}
For a single qubit, the creation/annihilation matrices are
\begin{equation}\begin{aligned}
	c = \begin{pmatrix}0 & 1 \\ 0 & 0\end{pmatrix}, c^\dagger = \begin{pmatrix}0 & 0 \\ 1 & 0\end{pmatrix}~,
\end{aligned}\end{equation}
given the convention that \(\ket{1} = (0 ~ ~ 1)\) is the occupied state. For a many-body system, these must be replaced with field operators that have the canonical fermionic algebra. For a system of \(N\) 1-particle levels, this can be accomplished through a {\it Jordan-Wigner}-like transformation
\begin{equation}\begin{aligned}
	c_j = \left(\otimes_1^j \sigma_z\right) \otimes c \otimes \left(\otimes_1^{N-j} \mathbb{I}\right) ~, j \in [0, N-1]~,
\end{aligned}\end{equation}
where \(\sigma_z = \begin{pmatrix} 1 & 0 \\ 0 & -1 \end{pmatrix} \) and \(\mathbb{I} = \begin{pmatrix} 1 & 0 \\ 0 & 1 \end{pmatrix} \). For example, for spinless electrons on a three-site lattice, we can have three fermionic operators: \(c_{1}\),\(c_{2}\), and \(c_{3}\). Following the above expression, their matrices are\\
\begin{equation*}\begin{aligned}
	c_1 = c \otimes \mathbb{I} \otimes \mathbb{I} = \begin{bmatrix}
0 & 0 & 1 & 0 & 0 & 0 &  0 &  0 \\
0 & 0 & 0 & 1 & 0 & 0 &  0 &  0 \\
0 & 0 & 0 & 0 & 0 & 0 &  0 &  0 \\
0 & 0 & 0 & 0 & 0 & 0 &  0 &  0 \\
0 & 0 & 0 & 0 & 0 & 0 & -1 &  0 \\
0 & 0 & 0 & 0 & 0 & 0 &  0 & -1 \\
0 & 0 & 0 & 0 & 0 & 0 &  0 &  0 \\
0 & 0 & 0 & 0 & 0 & 0 &  0 &  0 
\end{bmatrix}~,\\
	c_2 = \sigma \otimes c \otimes \mathbb{I} = \begin{bmatrix}
0 & 0 & 1 & 0 & 0 & 0 &  0 &  0 \\
 0 & 0 & 0 & 1 & 0 & 0 &  0 &  0 \\
 0 & 0 & 0 & 0 & 0 & 0 &  0 &  0 \\
 0 & 0 & 0 & 0 & 0 & 0 &  0 &  0 \\
 0 & 0 & 0 & 0 & 0 & 0 & -1 &  0 \\
 0 & 0 & 0 & 0 & 0 & 0 &  0 & -1 \\
 0 & 0 & 0 & 0 & 0 & 0 &  0 &  0 \\
 0 & 0 & 0 & 0 & 0 & 0 &  0 &  0 
\end{bmatrix}~,\\
		c_3 = \sigma \otimes \sigma \otimes c = \begin{bmatrix}
	0 & 1 & 0 &  0 & 0 &  0 & 0 & 0 \\
	0 & 0 & 0 &  0 & 0 &  0 & 0 & 0 \\
	0 & 0 & 0 & -1 & 0 &  0 & 0 & 0 \\
	0 & 0 & 0 &  0 & 0 &  0 & 0 & 0 \\
	0 & 0 & 0 &  0 & 0 & -1 & 0 & 0 \\
	0 & 0 & 0 &  0 & 0 &  0 & 0 & 0 \\
	0 & 0 & 0 &  0 & 0 &  0 & 0 & 1 \\
	0 & 0 & 0 &  0 & 0 &  0 & 0 & 0 
\end{bmatrix}~,\\
\end{aligned}\end{equation*}

For later use, we define the {\it antisymmetriser matrix} \(S(j)\) and identity matrix \(\mathbb{I}(j)\),
\begin{equation}\begin{aligned}
	S(j) &= \otimes_1^j \sigma_z = \sigma_z \otimes \ldots j\text{ times } \ldots \otimes \sigma_z,\\
	\mathbb{I}(j) &= \otimes_1^{N-j} \mathbb{I} = \mathbb{I} \otimes  \ldots j\text{ times } \ldots \otimes \mathbb{I}~,
\end{aligned}\end{equation}
to express the fermionic representation compactly:
\begin{equation}\begin{aligned}\label{jordanwigner}
	c_j = S(j) \otimes c \otimes \mathbb{I}(N-j)~.
\end{aligned}\end{equation}

\subsection{Structure of Hamiltonian}
We consider a general impurity model, of \(L\) number of sites (excluding the impurity site):
\begin{equation}\begin{aligned}\label{hamiltonian}
	H_\text{sys}(L) = H_\text{imp} + H_\text{imp-bath} +  
	- t\sum_{\sigma, j = 1}^{L-1}\left(c^\dagger_{j,\sigma}c_{j+1,\sigma} + \text{h.c.}\right) ~,
\end{aligned}\end{equation}
where \(H_\text{imp}\) is the Hamiltonian for the decoupled impurity site and \(H_\text{imp-bath}\) is the impurity-bath coupling. Such a system has \(2L+2\) single-particle levels in the full system (2 spin levels for each of the \(L+1\) sites).

Iteration scheme (the initial number of states is \(L_0\)):
\begin{equation}\begin{aligned}\label{iterationScheme}
	H_0(L_0) &= H_\text{sys}(L_0)~,\\
	H_{r+1}(L_0) &= H_r(L_0) + \Delta H_r(L_0), ~ r \geq 0~,\\
	\Delta H_r(L_0) &= - t\sum_{\sigma}\left(c^\dagger_{L_0 + r,\sigma}c_{L_0 + r+1,\sigma} + \text{h.c.}\right).
\end{aligned}\end{equation}
\(H_0\) is the initial Hamiltonian, consisting of \(L_0\) lattice sites in the bath, \(H_{r+1}(L_0)\) is the Hamiltonian after \(r+1\) iterations having started with \(L_0\) sites, and \(\Delta H_r(L_0)\) is the increment term that gets added to \(H_r(L_0)\) during the \((r+1)^\text{th}\) iteration to give rise to \(H_{r+1}(L_0)\).

%\section{Getting Together Everything That We Need}
%The broad idea of the algorithm (described in the next section) is the following: At any given step, we diagonalise the Hamiltonian for a given number of step, truncate the set of eigenstates to a manageable size, transform all operators to this rotated truncated basis, add a new site to the model to generate a new Hamiltonian, and then start from the first step. In preparation for describing the algorithm in more detail, we now describe various mathematical objects that we will use in the process.
%
%\subsection{Specifications}
%\begin{itemize}
%	\item \(H_r\) is the Hamiltonian at the start of any given step \(r\) of the iteration.
%	\item \(D_\text{tr}\) is the maximum number of eigenstates that are retained from any single symmetry sector any given step of the iteration.
%	\item The basis for representing the Hamiltonian at any given step is denoted as \(\mathcal{B}_r\). Its dimensions are \(D_r \times N_r\), obtained by stacking the basis vectors column-wise:
%\begin{equation}\begin{aligned}
%	\mathcal{B}_r = \left[\underbrace{V_1}_{D_r \times 1};\quad V_2; \quad \ldots V_{N_r}\right]_{D_r \times N_r} ~,
%\end{aligned}\end{equation}
%where \(V_1, V_2\), etc are the basis vectors represented as column vectors.
%	\item We start the iteration by considering \(L_0\) sites in the conduction bath, the initial Hamiltonian being \(H_0(L_0)\).
%\end{itemize}
%
%\subsection{Using Symmetries}
%Typically, our Hamiltonians will enjoy a global \(U(1)\) symmetry (overall number conservation) and overall magnetisation conservation. This will be preserved under the transformations, and will hold for the Hamiltonian at any step. We can therefore classify our basis \(\mathcal{B}_r\) into sectors \(\left\{\mathcal{B}_r^{(\nu)}\right\} \) according to the quantum numbers \(\nu\) of the symmetries. For the above example of total particle number conservation and total magnetisation conservation, \(\nu\) refers to the tuples \((N, m_z)\) of eigenvalues of the total number operator and the total magnetisation operator. The size (dimension) of each basis vector is \(D_r\).
%
%We are also gonna need to track the indices \(C^{(\nu)}\) of the columns of \(\mathcal{B}_r\) at which a particular subspace \(\mathcal{B}_r^{(\nu)}\) has non-zero values. As an illustration, consider the following artificial example where the values \(x_i\) form the symmetry block with \(\nu=1\), \(z\) forms the block \(\nu=2\) and \(y_i\) form \(\nu=3\):
%\begin{equation}\begin{aligned}
%	\mathcal{B}_r = \begin{bmatrix} 
%		x_1 & x_3 & 0 & 0 & 0 \\
%		x_2 & x_4 & 0 & 0 & 0 \\
%		0 & 0 & z & 0 & 0 \\
%		0 & 0 & 0 & y_1 & y_1 \\
%		0 & 0 & 0 & y_2 & y_2 \\
%	\end{bmatrix} ~,\quad
%	\mathcal{B}_r^{(1)} = \begin{bmatrix} 
%		x_1 & x_3 \\
%		x_2 & x_4 \\
%		0 & 0 \\
%		0 & 0 \\
%		0 & 0 \\
%	\end{bmatrix} ~,\quad
%	\mathcal{B}_r^{(2)} = \begin{bmatrix} 
%		0 \\
%		0 \\
%		z \\
%		0 \\
%		0 \\
%	\end{bmatrix} ~,\quad
%	\mathcal{B}_r^{(3)} = \begin{bmatrix} 
%		0 & 0 \\
%		0 & 0 \\
%		0 & 0\\
%		y_1 & y_1 \\
%		y_2 & y_2 \\
%	\end{bmatrix} ~,\quad
%	\begin{aligned}
%	& C^{(1)} =[1, 2],\\
%	& C^{(2)} =[3], \\
%	& C^{(3)} =[4, 5]~.
%    \end{aligned}
%\end{aligned}\end{equation}
%
%\subsection{Adding new sites}
%We also have \(L_r + 1\) fermionic field operators \(\left\{ c_j \right\} \), written in the basis \(\mathcal{B}_r\) at any given step, where \(L_r\) is the number of lattice sites present in the system at this step. These operators act on \(L_r+1\) number of sites; in order to go from one step of the iteration to the next, we will need to expand the system by adding one or more sites. This addition of sites requires the antisymmetrization of new field operators (acting purely on the new sites) against the existing \(L_r + 1\) operators (acting on the old sites). This antisymmetrization, in turn, requires a large antisymmetrization operator \(S_r = \otimes_1^{L_r+1}\sigma_z\).

\section{The Algorithm}
\subsection{Iterative Diagonalization}
Let the starting Hamiltonian be \(H_0(L_0)\), consisting of \(L_0\) single-particle levels (hence a Hilbert space dimension of \(2^{L_0}\)). We start with a single-particle computational basis and construct the \(L_0\) fermionic operators \(c_1, c_2, \ldots, c_{L_0}\) in this basis, using eq.~\ref{jordanwigner}. We also keep track of a large antisymmetriser matrix \(S(L_0)\) that will be used to attach new sites when we expand the system. Let \(M_s\) be the maximum number of eigenstates we retain in the spectrum at any given step. The value of \(M_s\) should be chosen so that a \(M_s\times M_s\) matrix can be diagonalised in reasonable time.
\begin{itemize}
	\item[{\it S1.}] Construct the complete Hamiltonian matrix \(H_0\) in our present basis using the field operators \(\left\{c_j\right\}\). Diagonalise the Hamiltonian (of size \(D_0 \times D_0\)) and obtain the eigenvalues \({E_n}\) and eigenstates \({X_n}\). Each \(X_n\) is a column vector of size \(D_0\).
	\item[{\it S2.}] Retain at most \(M_s\) number of eigenstates, preferring the ones with lower energy. The reduced basis for this rotated truncated subspace is constructed by stacking the column vectors \(X_n\) horizontally:
		\begin{equation}\begin{aligned}
			R = [X_1 X_2 \ldots X_{M_s}]_{D_0\times M_s}~.
		\end{aligned}\end{equation}
		This matrix also acts as the transformation to rotates and truncate all operators from the old basis into the new one.
	\item[{\it S3.}] We rotate our Hamiltonian \(H_0\), our fermionic operators \(\left\{ c_j \right\} \) and the large antisymmetrizer matrix \(S(L_0)\) into the new reduced basis, using the transformation \(\mathcal{O} \to R^\dagger \mathcal{O} R\).
	\item[{\it S4.}] We now need to expand our system by adding the increment Hamiltonian \(\Delta H_0\). Let the number of {\it new } 1-particle levels in \(\Delta H_0\) be \(L_\Delta\). These new levels will be indexed as \(L_0+1,\ldots,L_0+L_\Delta\). We need to define antisymmetrized fermionic operators for the new sites:
		\begin{equation}\begin{aligned}
			c_{L_0+1} &= c \otimes \mathbb{I}(2^{L_\Delta - 1}),\\
			c_{L_0+2} &= \sigma_z \otimes c \otimes \mathbb{I}(2^{L_\Delta - 2}),\\
					   &~~ \ldots~\\
			~c_{L_0+L_\Delta} &= (\otimes_1^{L_\Delta-1} \sigma) \otimes c ~.
		\end{aligned}\end{equation}
		These have to be calculated in the local computational basis (of size \(2^{L_\Delta}\)) of the new levels. 
	\item[{\it S5.}] Combining the new sites with the old sites leads to a combined Hilbert space dimension of \((M_s + 2^{L_\Delta}) \times (M_s + 2^{L_\Delta})\). To allow all operators to act on the enlarged Hilbert space, we expand both sets of operators:
	\begin{equation}\begin{aligned}
		c_j &= S(L_0) \otimes c_j;~~j=L_0 +1, \ldots, L_\Delta~,\\
		c_j &= c_j \otimes \mathbb{I}(2^{L_\Delta});~ ~ j=1, 2, \ldots, L_0~,\\
		H_0 &\to H_0 \otimes \mathbb{I}(2^{L_\Delta}),\\
		S(L_1) &= S(L_0) \otimes \mathbb{I}(2^{L_\Delta})~.
	\end{aligned}\end{equation}
	where \(\mathbb{I}(2^{L_\Delta})\) is an identity matrix of dimension \(2^{L_\Delta} \times 2^{L_\Delta}\). Note that the operators in the last three equations are the rotated ones (following Step 3).
\item[{\it S6.}] Using the transformed operators \(c_{L_0+1},\ldots,c_{L_0 + L_\Delta}\) for the new sites, construct the difference Hamiltonian matrix \(\Delta H_0\) and hence the updated Hamiltonian \(H_1 = H_0 + \Delta H_0\) for the next step. Repeat the process starting from step 2 with the new Hamiltonian \(H_1\), the new operators \(c_j\) and the new matrix \(S(L_1)\) replacing the old counterparts.
\end{itemize}

\subsection{Static Correlations}
We are in general interested in \(n-\)point correlations of the form \(\left<\mathcal{O}_1 \mathcal{O}_2 \ldots \mathcal{O}_n\right>\), where \(\mathcal{O}_i\) are operators that act on 1-particle Hilbert spaces. Let the earliest step of the iterative diagonalisation procedure at which all these operators have entered the system be \(r\). At this step \(r\), construct the correlation operator \(\mathcal{O}_1 \mathcal{O}_2 \ldots \mathcal{O}_n\) using the fermionic matrices \(c_j\) at that step (recall that these matrices will be highly rotated versions of the matrices we started with). Having constructed the operator \(O\), we expand and rotate it after the completion of every future step: \(O_{n+1} = (R_n^\dagger O_n R_n)\otimes \mathbb{I}(2^{L_\Delta})\), where \(R_n\) is the rotation matrix for the \(n^\text{th}\) step. The last step \(n^*\) of the iterative diagonalisation consists of only a diagonalisation and no expansion, resulting in a final set of eigenstates \(\left\{ X_i \right\} \). The form of the correlation operator in this basis is \(O_{n^*} = R^\dagger_{n^*-1} O_{n^*-1} R_{n^*}\). The expectation value can now be calculated using the matrix \(O_{n^*}\) and the ground state of \(\left\{ X_i \right\} \).

\section{Examples and Benchmarks}
\subsection{Single-Impurity Anderson Model}
The single-impurity Anderson model at half-filling is obtained by setting \(H_\text{imp}=-\frac{U}{2}\left(n_{d \uparrow} - n_{d \downarrow}\right)^2 \) and \(H_\text{imp-bath} = -V\sum_\sigma \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)\) in eq.~\ref{hamiltonian}. We studied this model using the above approach to benchmark the ground state energy and spin-flip correlation \(\left<\frac{1}{2}S_d^+ S_0^- + \text{h.c.} \right>\) against exact diagonalization (ED). In order to extend the ED to a larger number of sites, we restricted ourselves to just the \(N=2\) sector, \(N\) being the total occupancy. We find very good agreement for \(M_s \sim 1000\) and above. These results are shown in Fig.~\ref{comparisonSIAM}.
\begin{figure*}[!htpb]
\centering
\includegraphics[width=0.48\textwidth]{energy.pdf}
\includegraphics[width=0.48\textwidth]{spinflipcomparison.pdf}
\label{comparisonSIAM}
\end{figure*}
\end{document}

### 2024-09-08 numerics/caller.jl

@@ -10,10 +10,10 @@ include("./source/plotting.jl")
 const J_val = 0.1
 const omega_by_t = -2.0
 const orbitals = ("p", "p")
-const cmap = :YlOrBr
-fractionBZ = 0.2
-size_BZ = 17
-W_val_arr = -1.0 .* [2.6, 2.8] ./ size_BZ
+const cmap = :cherry
+fractionBZ = 0.1
+size_BZ = 9
+W_val_arr = -1.0 .* [0, 1] ./ size_BZ
 x_arr = range(K_MIN, stop=K_MAX, length=size_BZ) ./ pi
 
 node = map2DTo1D(float(π)/2, float(π)/2, size_BZ)
@@ -36,7 +36,7 @@ function probe(kondoJArrays, dispersion)
     @time for W_val in W_val_arr
         push!(subFigTitles, L"W/J=%$(round(W_val, digits=3))")
         results_arr = scattProb(kondoJArrays[W_val], size_BZ, dispersion, fractionBZ)
-        push!(collatedResults, [results_arr[2]])
+        push!(collatedResults, [results_arr[1], results_arr[2]])
     end
     saveName = "scattprob-$(orbitals[1])-$(orbitals[2])_$(size_BZ)_$(omega_by_t)_$(round(J_val, digits=4)).pdf"
     plotHeatmaps([x_arr, x_arr], [L"$ak_x/\pi$", L"$ak_y/\pi$"], [L"$\Gamma/\Gamma_0$", L"relevance of $\Gamma$"], subFigTitles, collatedResults, saveName)
@@ -50,16 +50,15 @@ function corr(kondoJArrays, dispersion)
     @showprogress for W_val in W_val_arr
         push!(subFigTitles, L"W/J=%$(round(W_val, digits=3))")
 
-        # set W_val to zero so that it does not interfere with the spin-flip fluctuations.
-        @time savePaths, activeStatesArr = getIterativeSpectrum(size_BZ, dispersion, kondoJArrays[W_val][:, :, end], 0.0, orbitals, fractionBZ)
+        @time savePaths, activeStatesArr = getIterativeSpectrum(size_BZ, dispersion, kondoJArrays[W_val][:, :, end], 0 * W_val, orbitals, fractionBZ)
[…]

### 2024-09-08 numerics/callerPhaseDiagram.jl

@@ -1,4 +1,4 @@
-using ProgressMeter, Measures, CairoMakie
+using ProgressMeter, Measures, CairoMakie, LaTeXStrings
 
 const TRUNC_DIM = 2
 include("./source/constants.jl")
@@ -6,42 +6,35 @@ include("./source/helpers.jl")
 include("./source/rgFlow.jl")
 include("./source/probes.jl")
 
-const colorSet = resample_cmap(:YlOrBr, 3)
-function getPhase(J_val, W_val)
-    kondoJArray, dispersion = momentumSpaceRG(size_BZ, omega_by_t, J_val, W_val, orbitals)
-    averageKondoScale = sum(abs.(kondoJArray[:, :, 1])) / length(kondoJArray[:, :, 1])
-    @assert averageKondoScale > RG_RELEVANCE_TOL
-    kondoJArray[:, :, end] .= ifelse.(abs.(kondoJArray[:, :, end]) ./ averageKondoScale .> RG_RELEVANCE_TOL, kondoJArray[:, :, end], 0)
-    scattProbBool = scattProb(kondoJArray, size_BZ, dispersion, fractionBZ)[2]
-    if all(>(0), scattProbBool[fermiPoints])
-        return 1
-    elseif all(==(0), scattProbBool[fermiPoints])
-        return 3
-    else
-        return 2
-    end
-end
+const cmap = resample_cmap(:cherry, 20)[1:end-1]
+const linecmap = :Dark2_3
+const phaseMaps = Dict("FL" => 2, "PG" => 1, "MI" => 3)
+const scatterLabels = ["N gaps", "AN gaps", "MP gaps"]
+const colorSet = resample_cmap(cmap, length(phaseMaps))
+const lineColorSet = resample_cmap(linecmap, 3)
+const labelSet = LaTeXString.([sort(collect(phaseMaps), by=last) .|> first; scatterLabels])
 
 const omega_by_t::Float64 = -2.0
 const orbitals::Tuple{String, String} = ("p", "p")
-const numPoints::Int64 = 100
+const numPoints::Int64 = 150
 const fractionBZ::Float64 = 0.3
 const size_BZ::Int64 = 17
 
-densityOfStates, dispersionArray = getDensityOfStates(tightBindDisp, size_BZ)
-node = map2DTo1D(float(π)/2, float(π)/2, size_BZ)
[…]

### 2024-09-08 numerics/source/helpers.jl

@@ -1,3 +1,5 @@
+using fermions
+
 include("models.jl")
 # helper functions for switching back and forth between the 1D flattened representation (1 → N^2) 
 # and the 2D representation ((1 → N)×(1 → N))
@@ -177,11 +179,8 @@ function getIterativeSpectrum(size_BZ::Int64, dispersion::Vector{Float64}, kondo
     for energy in energyShells
         onShellStates = filter(x -> abs(dispersion[x] - energy) < TOLERANCE, southWestQuadrantIndices)
         kxvals, _ = map1DTo2D(onShellStates, size_BZ)
-        for (point1, point2) in zip(onShellStates[sortperm(kxvals)], onShellStates[sortperm(kxvals, rev=true)])
-            if !isempty(activeStatesArr) && (point1 ∈ activeStatesArr[end] || point2 ∈ activeStatesArr[end])
-                break
-            end
-            push!(newStatesArr, [point1, point2])
+        for point in onShellStates[sortperm(kxvals)]
+            push!(newStatesArr, [point])
             if isempty(activeStatesArr)
                 push!(activeStatesArr, newStatesArr[end])
             else
@@ -189,11 +188,64 @@ function getIterativeSpectrum(size_BZ::Int64, dispersion::Vector{Float64}, kondo
             end
         end
     end
-    display(newStatesArr)
-    hamiltonianFamily = fetch.([Threads.@spawn kondoKSpace(activeStates, dispersion, kondoJArray, states -> bathIntForm(W_val, orbitals[2], size_BZ, states);
-                                                           specialIndices=newStates) for (activeStates, newStates) in zip(activeStatesArr, newStatesArr)])
+    hamiltonianFamily = fetch.([Threads.@spawn kondoKSpace(activeStates, dispersion, 10 .* kondoJArray, states -> bathIntForm(W_val, orbitals[2], size_BZ, states);
+                                                           specialIndices=newStates)
+                                for (activeStates, newStates) in zip(activeStatesArr, newStatesArr)])
     display(hamiltonianFamily[1])
     display(hamiltonianFamily[2])
     spectrumSavePaths = IterDiag(hamiltonianFamily, retainSize)
     return spectrumSavePaths, activeStatesArr
 end
+
+
[…]

### 2024-09-08 numerics/source/models.jl

@@ -3,12 +3,15 @@ function kondoKSpace(sequence::Vector{Int64}, dispersion::Vector{Float64}, kondo
 
     operatorList = Dict{Tuple{String,Vector{Int64}},Float64}()
 
-    for (momIndex, index) in enumerate(specialIndices)
-        energy = dispersion[index]
-        energy = abs(energy) > tolerance ? energy : 0
-        if energy == 0
+    for (momIndex, index) in enumerate(sequence)
+        if index ∉ specialIndices
             continue
         end
+        energy = dispersion[index]
+        # energy = abs(energy) > tolerance ? energy : 0
+        # if energy == 0
+        #     continue
+        # end
         merge!(+, operatorList, Dict(("n", [2 * momIndex + 1]) => energy))
         merge!(+, operatorList, Dict(("n", [2 * momIndex + 2]) => energy))
     end
@@ -52,30 +55,31 @@ function kondoKSpace(sequence::Vector{Int64}, dispersion::Vector{Float64}, kondo
     end end
 
     # bath interaction terms, for all quartets of momenta
-    for pairs in Iterators.product(repeat([enumerate(sequence)], 4)...)# for (i2, index2) in enumerate(sequence) for (i3, index3) in enumerate(sequence) for (i4, index4) in enumerate(sequence)
-        momIndices = Tuple(pair[2] for pair in pairs)
-        index4tuples = Tuple(pair[1] for pair in pairs)
-        if isempty(intersect(index4tuples, specialIndices))
-            continue
+    # for pairs in Iterators.product(repeat([enumerate(sequence)], 4)...)
+    for (i1, index1) in enumerate(sequence) for (i2, index2) in enumerate(sequence)
+            momIndices = [index1, index1, index2, index2]
+            index4tuples = [i1, i1, i2, i2]
+            if isempty(intersect(momIndices, specialIndices))
+                continue
+            end
+            bathIntVal = bathIntFunc(momIndices)
+            if abs(bathIntVal) ≤ tolerance
+                continue
+            end
+
+            # get the up and down indices for all momenta
+            upIndices = collect(2 .* index4tuples .+ 1)
[…]

### 2024-09-08 numerics/test.jl

@@ -1,0 +1,15 @@
+f = Figure(size=(400, 300), figure_padding=8)
+ax = Axis(f[1, 1], xlabel=L"Kondo Int. $(J)$", ylabel=L"Bath Int. $(-W)$",
+          xlabelsize=14, ylabelsize=14,)
+heatmap!(ax, J_val_arr, -1 .* W_val_arr, phaseDiagram;
+         colormap=cmap, thickness_scaling=1.5, legend=true)
+
+sc1 = scatterlines!(ax, J_val_arr[nodeGap .!= nothing][trunc.(Int, range(1, stop=end, length=40))], -1. * nodeGap[nodeGap .!= nothing][trunc.(Int, range(1, stop=end, length=40))],
+       color=lineColorSet[1], marker=:rect, markersize=7, strokecolor=:gray, strokewidth=1)
+sc2 = scatterlines!(ax, J_val_arr[antiNodeGap .!= nothing][trunc.(Int, range(1, stop=end, length=40))], -1. * antiNodeGap[antiNodeGap .!= nothing][trunc.(Int, range(1, stop=end, length=40))],
+             color=lineColorSet[2], marker=:circle, markersize=7, strokecolor=:gray, strokewidth=1)
+sc3 = scatterlines!(ax, J_val_arr[midPointGap .!= nothing][trunc.(Int, range(1, stop=end, length=40))], -1. * midPointGap[midPointGap .!= nothing][trunc.(Int, range(1, stop=end, length=40))],
+             color=lineColorSet[3], marker=:star6, markersize=7, strokecolor=:gray, strokewidth=1)
+legnd = [[PolyElement(color=col) for col in colorSet]; [sc1, sc2, sc3]]
+axislegend(ax, legnd, labelSet, labelsize=12, markersize=2)
+save("phaseDiagram.pdf", f, pt_per_unit=2)

### 2024-10-20 TilingProjectDraft/tilingProject.tex
added plots to notes
added phase diagram
added figures and discussion

@@
 \usepackage{braket,amsmath,color,graphicx,bookmark,bm}
+\graphicspath{{./figures/}}
 \bibliographystyle{apsrev4-2}
@@
 
+\section{Low-energy description of the embedded eSIAM}
 \subsection{Presence of a local pseuodogapping transition with electronic differentiation in momentum space}
@@
 The \(k-\)space forms of this quantity at various values of \(W/J\) is shown in fig.~\ref{gamma_kxky}, and the difference in the behaviour of the nodal and antinodel points is apparent.
-More insights in the difference of the behaviour is obtained by studying the fixed point distribution of the couplings \(J_{{\bf k}, {\bf q}}\) for \({\bf k}\) at a node and at an antinode.
-This is shown in fig.~\ref{kondoMaps}.
-
-\begin{figure*}[htpb]
+
+\begin{figure}[!htpb]
 	\centering
-	\includegraphics[width=0.49\textwidth]{scattProb-1.pdf}
-	\includegraphics[width=0.49\textwidth]{scattProb-2.pdf}\\
-	\includegraphics[width=0.49\textwidth]{scattProb-3.pdf}
-	\includegraphics[width=0.49\textwidth]{scattProb-4.pdf}\\
-	\includegraphics[width=0.49\textwidth]{scattProb-5.pdf}
-	\includegraphics[width=0.49\textwidth]{scattProb-6.pdf}
+	\includegraphics[width=0.23\textwidth]{scattProb-3.pdf}
+	\includegraphics[width=0.23\textwidth]{scattProb-5.pdf}
+	\includegraphics[width=0.23\textwidth]{scattProb-6.pdf}
+	\includegraphics[width=0.23\textwidth]{scattProb-7.pdf}
 	\caption{Variation of \(\Gamma\) as \(W/J\) is increased from left to right and top to bottom.
-In each pair of plots, the right figure shows the dependence of \(\Gamma\) on \(k_x/\pi\) and \(k_y/\pi\), while the left figure shows whether \(\Gamma({\bf k}\) is relevant (violet) or irrelevant (grey).
-As can be seen in the right pair of figures of the top row, the antinodal points are the first state to be removed from the Kondo cloud, while the left pair of figures of the bottom row shows that the node is the last to be removed.}
+Each plot shows whether \(\Gamma({\bf k}\) is relevant (black) or irrelevant (white).
+The antinodal points are the first state to be removed from the Kondo cloud, while the node is the last to be removed.}
 	\label{gamma_kxky}
-\end{figure*}
-
-\begin{figure*}[htpb]
+\end{figure}
+
+\subsection{Spin-correlations across the pseudogap}
+In figures.~\ref{spinCorr} and \ref{vneKspace}, we show the evolution of the spin-flip correlations \(\chi_s(d,\vec k) = \left<S_d^+ S_{\vec k}^- + \text{h.c.}\right>\) and entanglement entropy \(S_\text{EE}(\vec k)\), both in \(k-\)space, as the system is tuned through the pseudogap.
+At vanishing value of the interaction \(W\), the spin correlations are concentrated around the antinode, because of the \(p-\)wave nature of the Kondo interaction.
+At the entry into the pseudogap, the correlations become more pronounced near the nodes and become suppressed near the antinodes, signalling that the latter parts will gap out first.
+The last three figures \((W/J=-1.74, -1.83, -1.84)\) show how \(k-\)points starting from the antinode progressively exit the Kondo cloud, the node being the last to decouple from the impurity.
+
+\begin{figure}[htpb]
 	\centering
-	\includegraphics[width=0.49\textwidth]{kondoCoupNodeMap-1.pdf}
-	\includegraphics[width=0.49\textwidth]{kondoCoupNodeMap-6.pdf}\\
-	\includegraphics[width=0.49\textwidth]{kondoCoupAntinodeMap-1.pdf}
-	\includegraphics[width=0.49\textwidth]{kondoCoupAntinodeMap-6.pdf}
-	\caption{Distribution of Kondo coupling scattering processes.
-While the nodes are connected mostly through forward and backscattering processes, the antinodes also involve tangential scattering processes.}
-	\label{kondoMaps}
-\end{figure*}
+	\includegraphics[width=0.23\textwidth]{SF-3.pdf}
+	\includegraphics[width=0.23\textwidth]{SF-4.pdf}
+	\includegraphics[width=0.23\textwidth]{SF-5.pdf}
+	\includegraphics[width=0.23\textwidth]{SF-6.pdf}
+	\caption{\(k-\)space distribution of spin-flip scattering correlation \(\chi_s(d,\vec k)\) (defined in the main text).
+The last three figures \((W/J=-1.74, -1.83, -1.84)\) show how \(k-\)points starting from the antinode progressively exit the Kondo cloud, the node being the last \(k-\)point to decouple from the impurity.}
+	\label{spinCorr}
+\end{figure}
+
+As a second probe of the pseudogapping phenomenon, we have also studied the entanglement entropy (EE) \(S_\text{EE}(\vec k)\), which is just the von Neumann entropy \(-\text{Tr}\left[\rho \ln \rho\right] \) of the reduced density matrix \(\rho_{\vec k}\) for each \(k-\)state.
+In accordance with the Kondo spin correlations \(\chi_s\), the EE shows the sequential decoupling, from the impurity, of the antinodes followed by the nodes.
+
+Studies of \(k-\)space mutual information, \(I_2(\vec k, k_\text{N})\) and \(I_2(\vec k, k_\text{AN})\), between any given \(k-\)state and the node and antinode respectively, have revealed that each point interacts most strongly with it's own neighbourhood (see Supplementary Materials).
+This feature is in contrast to the charge-transfer correlations in the bath, that show ``long-ranged" interactions between the node and the antinode.
+These correlations will be discussed immediately after this, and are primarily responsible for driving the impurity transition and destabilising the Kondo cloud.
+\begin{figure}[!htpb]
+	\centering
+	\includegraphics[width=0.23\textwidth]{I2_k_d-1.pdf}
+	\includegraphics[width=0.23\textwidth]{I2_k_d-2.pdf}
+	\caption{\(k-\)space distribution of entanglement entropy.
+The pseudogapping occurs through (i) suppression of entanglement at \(W/J=-1.74\) near the nodes (compared to \(W=0\)), (ii) vanishing of entanglement near the antinodes, (iii) vanishing of entanglement at all points except the node.}
+	\label{vneKspace}
+\end{figure}
+
+\subsection{Charge correlations}
+In order to study the mechanism behind the destabilisation of the Kondo cloud through the pseudogap, we calculate the \(k-\)space double occupancy \(\left<n_{\vec k \uparrow} n_{\vec k \downarrow}\right>\) and \(k-\)space charge-transfer correlation \(\chi_c(\vec k, \vec q) = \left<c^\dagger_{\vec k \uparrow} c^\dagger_{\vec k \downarrow} c_{\vec q \downarrow}c_{\vec q \uparrow}\right>\) (Fig.~\ref{cfnode}).
+We find that the entry into the pseudogap is marked by an increase of doubly-occupied states near the antinode in comparison to \(W=0\).
+These pairs likely lead to the concomitant vanishing of spin-correlations near the antinode at the same value of \(W\), as seen in Fig.~\ref{spinCorr}.
+More insight on the nature of these correlations are obtained from the fluctuations \(\chi_c(\vec k, \vec q)\) starting from the node \((\vec q = k_\text{N})\) and antinode \(\left( \vec q = k_\text{AN}\right) \).
+Interestingly, we find strong pair-transfer interactions between the node and antinode.
+Within the pseudogap, this leads to charge-isospin flip correlations between the decoupled antinodal region and the still-coupled nodal region.
+\begin{figure}[!htpb]
+	\centering
+	\includegraphics[width=0.23\textwidth]{doubOcc-1.pdf}
+	\includegraphics[width=0.23\textwidth]{doubOcc-3.pdf}
+	\includegraphics[width=0.23\textwidth]{cfantinode-3.pdf}
+	\includegraphics[width=0.23\textwidth]{cfnode-3.pdf}
+	\caption{{\it Top panels}: Distribution of double occupancy at \(W=0\) and \(W=-1.74\) (entry into the pseudogap).
+While the double occupancy is concentrated near the nodes at \(W=0\), it rises near the antinodes at the start of the pseudogap, signalling its destabilisation.
+{\it Bottom panels}: Charge-transfer correlation \(\chi_c\) (defined in main text) starting from antinode (left) and node (right), at the beginning of the pseudogap phase.
+Strong node-antinode correlations are clearly visible.}
+	\label{cfnode}
+\end{figure}
 
@@
 	\mathcal{H}_\text{HH} &= -\frac{1}{\sqrt\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
-						  &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
+						  &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
 \end{aligned}\end{equation}
@@
 
+% \begin{figure*}[htpb]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{charge-p-p_37_-2.0_-1.7297_-0.0_0.1.pdf}
+% \end{figure*}
+% \begin{figure*}[htpb]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{vne-p-p_37_-2.0_-1.7297_-0.0_0.1.pdf}
+% \end{figure*}
+
 \clearpage
@@
 \subsection{Gapping of the local spectral function and vanishing of correlations}
-At a critical value \(U_b = -J/4\) of the local correlation \(U_b\) on the bath zeroth site, the couplings \(J\) and \(V\) of the auxiliary model become irrelevant while \(U\) becomes remains non-zero, leading to a low-energy phase where the impurity is cut off from the conduction bath.
+% At a critical value \(U_b = -J/4\) of the local correlation \(U_b\) on the bath zeroth site, the couplings \(J\) and \(V\) of the auxiliary model become irrelevant while \(U\) becomes remains non-zero, leading to a low-energy phase where the impurity is cut off from the conduction bath.
 This is the local moment phase, where low-energy excitations have been gapped out.
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.48\textwidth]{phase-map-MIT.pdf}
-	\includegraphics[width=0.48\textwidth]{spectral-function_dd.pdf}
-	\caption{{\it Left:} Phase diagram of the extended SIAM auxiliary model.
+% \begin{figure}[htpb]
+% 	\centering
+% 	\includegraphics[width=0.48\textwidth]{phase-map-MIT.pdf}
+% 	\includegraphics[width=0.48\textwidth]{spectral-function_dd.pdf}
+% 	\caption{{\it Left:} Phase diagram of the extended SIAM auxiliary model.
 As the parameter \(r\) is tuned through 0.25, the metallic blue phase changes into the insulating violet phase.
@@
 It shows a hard gap for \(r/r_c > 1\).}
-	\label{spec_func_mit}
-\end{figure}
-
-The impurity local spectral function \(\mathcal{A}_{dd}(\omega)\) and the impurity-bath real space off-diagonal spectral function \(\mathcal{A}_{dz}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
+% 	\label{spec_func_mit}
+% \end{figure}
+%
+% The impurity local spectral function \(\mathcal{A}_{dd}(\omega)\) and the impurity-bath real space off-diagonal spectral function \(\mathcal{A}_{dz}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
 We show the former in fig.~\ref{spec_func_mit}.
 The gap in the former shows the absence of any gapless excitations that can allow the impurity configuration to fluctuate, while the vanishing of the off-diagonal spectral function shows that this is because the entanglement between the impurity and the bath has been quenched.
-
-In Fig.~\ref{spin-charge-correlations}, we show the behaviour of the spin-flip and charge isospin-flip correlations between two neighbouring real space sites, as well as the mutual real space entanglement and mutual information.
+%
+% In Fig.~\ref{spin-charge-correlations}, we show the behaviour of the spin-flip and charge isospin-flip correlations between two neighbouring real space sites, as well as the mutual real space entanglement and mutual information.
 Both show a sharp fall on crossing the transition, demonstrating the destruction of the Kondo cloud and the stabilisation of the local moment on the impurity.
 Importantly, they charge correlations show a rise very close to the transition (can be seen as a single elevated blue point near \(r = 0.25\) in the left panel of Fig.~\ref{spin-charge-correlations}); this indicates that the transition is precipitated by the growth of pairing correlations.
-
-\begin{figure}[!htb]
-\centering
-	\includegraphics[width=0.48\textwidth]{spin-charge-corr-full.pdf}
-	\includegraphics[width=0.48\textwidth]{impEE-mutinfo-d0.pdf}
-	\caption{{\it Left}: Spin-flip correlations(red) and charge-flip correlations(blue) in real space.
+%
+% \begin{figure}[!htb]
+% \centering
+% 	\includegraphics[width=0.48\textwidth]{spin-charge-corr-full.pdf}
+% 	\includegraphics[width=0.48\textwidth]{impEE-mutinfo-d0.pdf}
+% 	\caption{{\it Left}: Spin-flip correlations(red) and charge-flip correlations(blue) in real space.
 The former increases as the system moves into the Kondo regime, and then vanishes at the transition.
@@
 Both vanish in the local moment phase.}
-	\label{spin-charge-correlations}
-\end{figure}
+% 	\label{spin-charge-correlations}
+% \end{figure}
 
@@
 \section{Momentum-space picture of the MIT}
-In order to understand the nature of the transition in momentum space, we employ the expression obtained in the previous sections and compute the spectral function, self-energy and correlation functions in the top right quadrant of the first Brillouin zone.
+% In order to understand the nature of the transition in momentum space, we employ the expression obtained in the previous sections and compute the spectral function, self-energy and correlation functions in the top right quadrant of the first Brillouin zone.
 We first show the \(k-\)space spectral functions near zero frequency, in Fig.~\ref{kspace_specfunc}.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=\textwidth]{kspace-spectral-function-all.pdf}\hspace{\fill}
-\caption{\(k-\)space dependence of single-particle spectral function, \(A_{\vec k}(\omega \sim 0)\), at four values of the tuning parameter \(r\).
+%
+% \begin{figure}[!htb]
+% \centering
+% \includegraphics[width=\textwidth]{kspace-spectral-function-all.pdf}\hspace{\fill}
+% \caption{\(k-\)space dependence of single-particle spectral function, \(A_{\vec k}(\omega \sim 0)\), at four values of the tuning parameter \(r\).
 The \(\vec k\) values are taken from the top right quadrant of the first Brillouin zone.
@@
 Close to the transition (and beyond it), the momentum dependence gets removed and there is no spectral weight left in the infrared regime.}
-\label{kspace_specfunc}
-\end{figure}
-
-In Fig.~\ref{kspace_selfenergy}, we plot the momentum dependence of the single-particle self-energy, similar to the spectral function.
+% \label{kspace_specfunc}
+% \end{figure}
+%
+% In Fig.~\ref{kspace_selfenergy}, we plot the momentum dependence of the single-particle self-energy, similar to the spectral function.
 The self-energy is flat in \(k-\)space away from the transition, consistent with the fact that the correlations are small in that regime.
 Close to the transition, the correlations pick up, and lead to a momentum-dependence of the self-energy, renormalising the Fermi liquid in the process and ultimately destroying it.
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=\textwidth]{kspace-imagsigma-all.pdf}\hspace{\fill}
-\caption{\(k-\)space dependence of imaginary part of the self-energy, \(\Sigma_{\vec k}(\omega \sim 0)\), at four values of the tuning parameter \(r\).
+% \begin{figure}[!htb]
+% \centering
+% \includegraphics[width=\textwidth]{kspace-imagsigma-all.pdf}\hspace{\fill}
+% \caption{\(k-\)space dependence of imaginary part of the self-energy, \(\Sigma_{\vec k}(\omega \sim 0)\), at four values of the tuning parameter \(r\).
 In the metallic phase (\(r \ll r_c\)), the self-energy is quite small, indicating that the phase consists of an uncorrelated Fermi liquid.
 It increases close to the transition (and beyond it).}
-\label{kspace_selfenergy}
-\end{figure}
-
-In Figs.~\ref{spin_kspace},\ref{charge_kspace} and \ref{pair_kspace}, we show the momentum dependence of two-particle correlation functions.
+% \label{kspace_selfenergy}
+% \end{figure}
+%
+% In Figs.~\ref{spin_kspace},\ref{charge_kspace} and \ref{pair_kspace}, we show the momentum dependence of two-particle correlation functions.
 In every figure, each panel shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
@@
 This is tied to the non-Fermi liquid theory at the QCP, as seen in the auxiliary model.
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=\textwidth]{spin_rspace_all.pdf}
-\caption{Momentum dependence of spin-spin correlation \(\left<\vec{S}_{-\vec k}\cdot\vec{S}_{\vec k} \right>\).
+% \begin{figure}[!htb]
+% \centering
+% \includegraphics[width=\textwidth]{spin_rspace_all.pdf}
+% \caption{Momentum dependence of spin-spin correlation \(\left<\vec{S}_{-\vec k}\cdot\vec{S}_{\vec k} \right>\).
 Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
@@
 The flat blue region at the top is the local moment phase, void of any non-local correlations.}
-\label{spin_kspace}
-\end{figure}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=\textwidth]{charge_rspace_all.pdf}
-\caption{Momentum dependence of charge-charge correlation \(\left<\vec{C}_{-\vec k}\cdot\vec{C}_{\vec k} \right>\), where \(\vec C\) is the charge isospin associated with the doublet formed by the doublon and holon states.
+% \label{spin_kspace}
+% \end{figure}
+%
+% \begin{figure}[!htb]
+% \centering
+% \includegraphics[width=\textwidth]{charge_rspace_all.pdf}
+% \caption{Momentum dependence of charge-charge correlation \(\left<\vec{C}_{-\vec k}\cdot\vec{C}_{\vec k} \right>\), where \(\vec C\) is the charge isospin associated with the doublet formed by the doublon and holon states.
 Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
@@
 The flat blue region at the top is the local moment phase, void of any non-local correlations.}
-\label{charge_kspace}
-\end{figure}
-
-\begin{figure}[!htb]
-\includegraphics[width=\textwidth]{pair_rspace_all.pdf}
-\caption{Momentum dependence of pairing correlation \(\left<c^\dagger_{-k\uparrow}c^\dagger_{-k\downarrow}c_{k\downarrow}c_{k\uparrow}\right>\).
+% \label{charge_kspace}
+% \end{figure}
+%
+% \begin{figure}[!htb]
+% \includegraphics[width=\textwidth]{pair_rspace_all.pdf}
+% \caption{Momentum dependence of pairing correlation \(\left<c^\dagger_{-k\uparrow}c^\dagger_{-k\downarrow}c_{k\downarrow}c_{k\uparrow}\right>\).
 Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
@@
 The flat blue region at the top is the local moment phase, void of any non-local correlations.}
-\label{pair_kspace}
-\end{figure}
-
-\begin{figure}[!htb]
-\includegraphics[width=\textwidth]{vne_kspace_all.pdf}
-\caption{Momentum dependence of \(k-\)space von Neumann entanglement entropy \(S_\text{EE}(\vec k)\).
+% \label{pair_kspace}
+% \end{figure}
+%
+% \begin{figure}[!htb]
+% \includegraphics[width=\textwidth]{vne_kspace_all.pdf}
+% \caption{Momentum dependence of \(k-\)space von Neumann entanglement entropy \(S_\text{EE}(\vec k)\).
 The four frames (from the left) show the variation in entanglement of a \(k-\)space in the \(k_x-k_y\) plane as the transition parameter \(r\) is tuned through the metal-insulator transition.
 \(r/r_c=0.5\) represents a very weakly correlated metal, \(r/r_c=0.8,0.9\) represents a highly correlated metal in the Kondo phase of the auxiliary model, and \(r/r_c \sim 1\) represents the non-Fermi liquid metal formed at the transition.}
-\label{entanglement_kspace}
-\end{figure}
-
-\begin{figure}[!htb]
-\includegraphics[width=\textwidth]{mutinfo_kspace_all.pdf}
-\caption{Momentum dependence of \(k-\)space mutual information \(I_2(\vec k: -\vec k)\).
+% \label{entanglement_kspace}
+% \end{figure}
+%
+% \begin{figure}[!htb]
+% \includegraphics[width=\textwidth]{mutinfo_kspace_all.pdf}
+% \caption{Momentum dependence of \(k-\)space mutual information \(I_2(\vec k: -\vec k)\).
 The four frames (from the left) show the variation in entanglement between the \(\vec k\) and \(-\vec k\) states in the \(k_x-k_y\) plane as the transition parameter \(r\) is tuned through the metal-insulator transition.
 \(r/r_c=0.5\) represents a very weakly correlated metal, \(r/r_c=0.8,0.9\) represents a highly correlated metal in the Kondo phase of the auxiliary model, and \(r/r_c \sim 1\) represents the non-Fermi liquid metal formed at the transition.}
-\label{mutinfo_kspace}
-\end{figure}
-
-{\color{blue} In order to provide a second way of visualising these correlations, we have provided some videos that show their variation in the \(k_x-k_y\) plane as a function of \(r/r_c\).
+% \label{mutinfo_kspace}
+% \end{figure}
+%
+% {\color{blue} In order to provide a second way of visualising these correlations, we have provided some videos that show their variation in the \(k_x-k_y\) plane as a function of \(r/r_c\).
 The videos for the spin-spin correlation and the pairing correlations are named ``ss\_rspace.gif" and ``pairing\_rspace.gif", respectively.

### 2024-10-20 numerics/caller.jl

@@ -1,7 +1,7 @@
 using Distributed
 
 if length(Sys.cpu_info()) > 10 && nprocs() == 1
-    addprocs(div(length(Sys.cpu_info()), 10))
+    addprocs(5)
 end
 using JLD2
 using LinearAlgebra
@@ -16,12 +16,12 @@ global const J_val = 0.1
 global const omega_by_t = -2.0
 @everywhere global const orbitals = ("p", "p")
 global const maxSize = 500
-WmaxSize = 500
+WmaxSize = 400
 
-numShells = 1
+numShells = 5
 size_BZ = 41
 # W_val_arr = -1.0 .* [0.0] ./ size_BZ
-W_val_arr = -1.0 .* [0, 3.5, 7.13, 7.3, 7.5, 7.564] ./ size_BZ
+W_val_arr = -1.0 .* [0, 3.5, 7.13, 7.3, 7.5, 7.564, 7.6] ./ size_BZ
 # W_val_arr = -1.0 .* [0, 2.8, 5.6, 5.7, 5.82, 5.89, 5.92] ./ size_BZ
 x_arr = collect(range(K_MIN, stop=K_MAX, length=size_BZ) ./ pi)
 label(W_val) = L"$W/J=%$(round(W_val/J_val, digits=2))$\n$M_s=%$(maxSize)$"
@@ -115,7 +115,7 @@ function corr(kondoJArrays, dispersion)
             end
 
             for name in keys(corrResults)
-                push!(saveNames[name], plotHeatmap(corrResults[name], (x_arr, x_arr), (L"$ak_x/\pi$", L"$ak_y/\pi$"), plotTitles[name], label(W_val)))
+                push!(saveNames[name], plotHeatmap(abs.(corrResults[name]), (x_arr, x_arr), (L"$ak_x/\pi$", L"$ak_y/\pi$"), plotTitles[name], label(W_val)))
             end
         end
     end

### 2024-10-24 numerics/caller.jl
extended by keeping more states, and created final polished plots

@@ -1,7 +1,7 @@
 using Distributed
 
 if length(Sys.cpu_info()) > 10 && nprocs() == 1
-    addprocs(5)
+    addprocs(0)
 end
 using JLD2
 using LinearAlgebra
@@ -16,15 +16,18 @@ global const J_val = 0.1
 global const omega_by_t = -2.0
 @everywhere global const orbitals = ("p", "p")
 global const maxSize = 500
-WmaxSize = 400
+WmaxSize = 500
 
+colmap = reverse(ColorSchemes.cherry)
 numShells = 5
 size_BZ = 41
-# W_val_arr = -1.0 .* [0.0] ./ size_BZ
+bathIntLegs = 3
+# W_val_arr = -1.0 .* [7.3] ./ size_BZ
 W_val_arr = -1.0 .* [0, 3.5, 7.13, 7.3, 7.5, 7.564, 7.6] ./ size_BZ
 # W_val_arr = -1.0 .* [0, 2.8, 5.6, 5.7, 5.82, 5.89, 5.92] ./ size_BZ
 x_arr = collect(range(K_MIN, stop=K_MAX, length=size_BZ) ./ pi)
-label(W_val) = L"$W/J=%$(round(W_val/J_val, digits=2))$\n$M_s=%$(maxSize)$"
+getlabel(W_val) = L"$W/J=%$(round(W_val/J_val, digits=2))$\n$M_s=%$(maxSize)$"
+getlabelNoSize(W_val) = L"$\frac{W}{J}=%$(round(W_val/J_val, digits=2))$"
 
 function RGFlow(W_val_arr, size_BZ)
     kondoJArrays = Dict{Float64, Array{Float64, 3}}()
@@ -43,7 +46,11 @@ function probe(kondoJArrays, dispersion)
     saveNames = String[]
     for W_val in W_val_arr
         results_scaled, results_bool = scattProb(size_BZ, kondoJArrays[W_val], dispersion)
-        push!(saveNames, plotHeatmap(results_bool, (x_arr, x_arr), (L"$ak_x/\pi$", L"$ak_y/\pi$"), L"$\Gamma/\Gamma_0$", label(W_val)))
+
+        quadrantResult = results_bool[filter(p -> all(map1DTo2D(p, size_BZ) .≥ 0), 1:size_BZ^2)]
[…]

### 2024-10-24 numerics/source/plotting.jl

@@ -1,19 +1,40 @@
 using CairoMakie, Random, Measures, LaTeXStrings, ColorSchemes
+
+# set_theme!(theme_latexfonts())
 set_theme!(merge(theme_ggplot2(), theme_latexfonts()))
-colmap = reverse(ColorSchemes.cherry)
-fontsize = 26
+update_theme!(
+              figure_padding = 0,
+              fontsize=28,
+              Axis = (
+                leftspinevisible = true,
+                bottomspinevisible = true,
+                rightspinevisible = true,
+                topspinevisible = true,
+                spinewidth = 1.5,
+                     ),
+              ScatterLines = (
+                       linewidth = 6,
+                       markersize=20,
+                      ),
+              Legend = (
+                        patchsize=(50,20),
+                        halign = :right,
+                        valign = :top,
+                       ),
+             )
+
+# colmap = ColorSchemes.cherry
 function plotHeatmap(
         matrixData::Union{Vector{Int64}, Vector{Float64}},
         axisVals::NTuple{2, Vector{Float64}},
         axisLabels::NTuple{2, LaTeXString},
         title::LaTeXString,
         annotation::LaTeXString,
+        colmap,
     )
     matrix = reshape(matrixData, length.(axisVals))
 
-    figure = Figure(size = (500, 400), 
-                    fontsize = fontsize, 
-                   )
+    figure = Figure(size=(300, 300))
     ax = Axis(figure[1, 1],
               xlabel = axisLabels[1], 
               ylabel=axisLabels[2], 
@@ -25,6 +46,7 @@ function plotHeatmap(
              colormap=colmap,
             )
 
+    fontsize = 28
     gl = GridLayout(figure[1, 1], tellwidth = false, tellheight = false, valign=:top, halign=:right)
     Box(gl[1, 1], color = RGBAf(0, 0, 0, 0.4), strokewidth=0, strokecolor=RGBAf(0, 0, 0, 0.8))
     Label(gl[1, 1], annotation, padding = (5, 5, 5, 5), fontsize=div(fontsize, 1.3), color=:white)
@@ -34,7 +56,6 @@ function plotHeatmap(
              limits=colorbarLimits,
              colormap=colmap,
             )
-
     savename = joinpath("figures", randstring(5) * ".pdf")
     save(savename, figure)
     return savename

### 2024-10-24 numerics/source/probes.jl

@@ -122,7 +122,7 @@ end
                                      maxSize;
                                      symmetries=Char['N', 'S'],
                                      magzReq=(m, N) -> -1 ≤ m ≤ 2,
-                                     occReq=(x, N) -> div(N, 2) - 5 ≤ x ≤ div(N, 2) + 5,
+                                     occReq=(x, N) -> div(N, 2) - 3 ≤ x ≤ div(N, 2) + 3,
                                      #=corrMagzReq=(m, N) -> m == ifelse(isodd(div(N, 2)), 1, 0),=#
                                      #=corrOccReq=(x, N) -> x == div(N, 2),=#
                                      correlationDefDict=correlationDefDict,

### 2024-11-24 TilingProjectDraft/tilingProject.tex
extended by keeping more states, and created final polished plots
corrected analytic tiling expressions for static correlations, enhanced iterdiag notes

@@
 	\centering
+	\includegraphics[width=0.23\textwidth]{SF-1.pdf}
 	\includegraphics[width=0.23\textwidth]{SF-3.pdf}
-	\includegraphics[width=0.23\textwidth]{SF-4.pdf}
 	\includegraphics[width=0.23\textwidth]{SF-5.pdf}
@@
 These correlations will be discussed immediately after this, and are primarily responsible for driving the impurity transition and destabilising the Kondo cloud.
-\begin{figure}[!htpb]
-	\centering
-	\includegraphics[width=0.23\textwidth]{I2_k_d-1.pdf}
-	\includegraphics[width=0.23\textwidth]{I2_k_d-2.pdf}
-	\caption{\(k-\)space distribution of entanglement entropy.
-The pseudogapping occurs through (i) suppression of entanglement at \(W/J=-1.74\) near the nodes (compared to \(W=0\)), (ii) vanishing of entanglement near the antinodes, (iii) vanishing of entanglement at all points except the node.}
-	\label{vneKspace}
-\end{figure}
 
@@
 \begin{equation}\begin{aligned}\label{fourTransf}
-	c({\bf K}) = \frac{1}{N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}c({\bf r})~.
+	c({\bf K}) = \frac{1}{\sqrt N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}c({\bf r})~.
 \end{aligned}\end{equation}
@@
 \end{aligned}\end{equation}
-We again consider the spin-flip correlation first. In order to introduce the impurity site, we rewrite the expectation values as
-\begin{equation}\begin{aligned}
-	&\tilde{S}_\text{flip}({\bf K}_1, {\bf K}_2) \\
-	&= \frac{1}{2}\left[\sqrt{\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)}\braket{S^-\left({\bf K}_2\right)S^+\left({\bf K}_1\right)}} + \text{h.c.}\right] ~.
-\end{aligned}\end{equation}
-We frame this in terms of the auxiliary model by (i) making the substitution again for the ground states, and (ii) by fourier transforming the first operator within each expectation value to real space and retaining just the impurity site operator:
-\begin{equation}\begin{aligned}
-	&\tilde{S}_\text{flip}({\bf K}_1, {\bf K}_2) \\
-	&= \frac{1}{2}\left[\sqrt{\braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf d}\right)S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}}\right. \\
-	&\left.\times\sqrt{\braket{\psi_\text{gs}{({\bf r}_c)} | S^-\left({\bf d}\right)S^+\left({\bf K}_1\right) | \psi_\text{gs}{({\bf r}_c)}}} + \text{h.c.}\right] ~.
-\end{aligned}\end{equation}
-Performing similar manipulations with the charge isospin-flip correlation gives
-\begin{equation}\begin{aligned}
-	&\tilde{C}_\text{flip}({\bf K}_1, {\bf K}_2) \\
-	&= \frac{1}{2}\left[\sqrt{\braket{\psi_\text{gs}({\bf r}_c) | C^+\left({\bf d}\right)C^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}}\right. \\
-	&\left.\times\sqrt{\braket{\psi_\text{gs}{({\bf r}_c)} | C^-\left({\bf d}\right)C^+\left({\bf K}_1\right) | \psi_\text{gs}{({\bf r}_c)}}} + \text{h.c.}\right] ~.
+We again consider the spin-flip correlation first.
+In order to introduce the impurity site, we rewrite the expectation values sum of all coherent scattering processes involving the impurity site and the two \(k-\)states.
+Using eq.~\ref{eigenstateProposal}, we express the correlation in terms of a single auxiliary model:
+\begin{equation}\begin{aligned}
+	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} \\
+	&= \frac{1}{N}\sum_{{\bf r}_d}\braket{\psi_\text{gs}({\bf r}_d) | S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_d)}~,
+\end{aligned}\end{equation}
+where \({\bf r}_d\) is the location of the impurity site, and we average over the correlation values calculated over all possible auxiliary models.
+Assuming translation invariance, the static correlation values should be equal on every auxiliary model, allowing us to replace the average with the value at the reference origin \({\bf r}_c\):
+\begin{equation}\begin{aligned}\label{correlationAuxiliary}
+	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} = \braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+Using the definition \(S^+(\nu) = c^\dagger_{\nu \uparrow} c_{nu \downarrow}\), one can Fourier transform the fermionic operators in eq.~\ref{correlationAuxiliary},
+\begin{equation}\begin{aligned}
+	c_{{\bf k}\sigma} = \sum_{\bf r} e^{i {\bf k}\cdot{\bf r}} c_{{\bf r}\sigma},
+\end{aligned}\end{equation}
+and retain the only impurity site contribution \({\bf r}={\bf r}_c\) in order to introduce the dynamics of the impurity site. Carrying this out for one and two fermionic operators gives
+\begin{equation}\begin{aligned}\label{correlationAuxiliaryProcess}
+	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} \\
+	&= \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf r}_c \uparrow} c_{{\bf K}_1 \downarrow} S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}\\
+	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf K}_1 \uparrow} c_{{\bf r}_c \downarrow} S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}\\
+	&+ \braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf K}_1\right) c^\dagger_{{\bf r}_c \downarrow} c_{{\bf K}_2 \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
+	&+ \braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf K}_1\right) c^\dagger_{{\bf K}_2 \downarrow} c_{{\bf r}_c \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
+	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf r}_c \uparrow} c_{{\bf K}_1 \downarrow} c^\dagger_{{\bf r}_c \downarrow} c_{{\bf K}_2 \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
+	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf r}_c \uparrow} c_{{\bf K}_1 \downarrow} c^\dagger_{{\bf K}_2 \downarrow} c_{{\bf r}_c \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
+	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf K}_1 \uparrow} c_{{\bf r}_c \downarrow} c^\dagger_{{\bf r}_c \downarrow} c_{{\bf K}_2 \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
+	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf K}_1 \uparrow} c_{{\bf r}_c \downarrow} c^\dagger_{{\bf K}_2 \downarrow} c_{{\bf r}_c \uparrow} | \psi_\text{gs}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+We haven't considered three-particle dynamics on the impurity site because those would involve only one momentum state and would hence be incoherent for the other momentum state; for the same reason, certain two-particle terms have also been ignored.
+Henceforth, we replace the index \({\bf r}_c\) with \(d\), indicating that it is the position of the impurity site.
+By introducing the off-site spin operator \(S^+_{\nu_1,\nu_2} = c^\dagger_{\nu_1 \uparrow} c_{\nu_2 \downarrow}\) that flips an effective spin across multiple orbitals, we can express eq.~\ref{correlationAuxiliaryProcess} in a more illuminating form:
+\begin{equation}\begin{aligned}
+	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} =\\
+	& \braket{(S^+_{d, {\bf K}_1} + S^+_{{\bf K}_1,d}) S^-({\bf K}_2) + S^+({\bf K}_1) (S^-_{d, {\bf K}_2} + S^-_{{\bf K}_2, d}) \right.\\
+	&+ \left.S^+_{d, {\bf K}_1} (S^-_{{\bf K}_2, d} + S^-_{d, {\bf K}_2}) + (S^+_{{\bf K}_1, d} + S^+_{{\bf K}_1, d}) S^-_{{\bf K}_2, d}}~.
+\end{aligned}\end{equation}
+This allows us to visualise the \(k-\)space correlation function through various scattering processes within the auxiliary model: the net correlation between \({\bf K}_1\) and \({\bf K}_2\) occur either through (i) simultaneous and opposite flips of the spin on one momentum state and the shared spin on the impurity site and another momentum state, or (ii) the simultaneous flips of spins shared between all three members.
+
+The charge correlations can be treated exactly the same way.
+We quote the final result here, in terms of the off-site charge operators \(C^+_{\nu_1, \nu_2} = c^\dagger_{\nu_1 \uparrow} c^\dagger_{\nu_2 \downarrow}\) :
+\begin{equation}\begin{aligned}
+	&\left<C^+({\bf K}_1) C^-({\bf K}_2)\right> = \\
+	& \braket{(C^+_{d, {\bf K}_1} + C^+_{{\bf K}_1,d}) C^-({\bf K}_2) + C^+({\bf K}_1) (C^-_{d, {\bf K}_2} + C^-_{{\bf K}_2, d}) \right.\\
+	&+ \left.C^+_{d, {\bf K}_1} (C^-_{{\bf K}_2, d} + C^-_{d, {\bf K}_2}) + (C^+_{{\bf K}_1, d} + C^+_{{\bf K}_1, d}) C^-_{{\bf K}_2, d}}~.
 \end{aligned}\end{equation}

### 2024-11-24 iterDiagAlgorithm/iterDiagAlgo.tex
corrected analytic tiling expressions for static correlations, enhanced iterdiag notes

@@
 	The following is the algorithm for performing an iterative diagonalization of fermionic systems.
-It is mostly similar to DMRG and NRG, and allows obtaining the low-energy spectrum large many-body Hamiltonians.
+It is mostly similar to DMRG and NRG, and allows obtaining the low-energy spectrum of large many-body Hamiltonians.
 \end{abstract}
@@
 
-%
+\section{Introduction}
+The broad idea is the following.
+We have a Hamiltonian describing an interacting set of states (in real or momentum space).
+We can express the total Hamiltonian in an incremental fashion: \(H = \sum_i H_i\), where \(H_{i+1}\) involves more number of states than \(H_i\).
+For example, a tight-binding model can be written in that form, with the definition \(H_i = c^\dagger_{i+1}c_i + \text{h.c.}\).
+The iterative diagonalisation method obtains the low-energy spectrum of this problem in the following manner: We first diagonalise the Hamiltonian \(H\) for a smaller value of \(i\), small enough such that this can be done exactly.
+We then truncate the spectrum to a predefined size, and rotate all existing operators to this truncated basis, including the Hamiltonian \(H\).
+We then consider the "bonding Hamiltonian" \(\Delta H\) between the existing sites and the new sites, and rotate the same into the truncated basis.
+Adding the previous rotated Hamiltonian \(H\) and the rotated increment Hamiltonian \(\Delta H\) gives us a truncated but effective Hamiltonian for the increased number of sites.
+We again diagonalise this, and again retain only a fixed number of states in the spectrum.
+We keep repeating this until we reach the required number of sites.
 
@@
 These results are shown in Fig.~\ref{comparisonSIAM}.
-\begin{figure*}[!htpb]
-\centering
+\begin{widetext}
 \includegraphics[width=0.48\textwidth]{energy.pdf}
@@
 \label{comparisonSIAM}
-\end{figure*}
+\end{widetext}
 \end{document}

### 2024-12-15 TilingProjectDraft/tilingProject.tex
updated notes with new plots

@@
 \section{Low-energy description of the embedded eSIAM}
+\subsection{Zero temperature phase diagram}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.23\textwidth]{phaseDiagram.pdf}
+	\includegraphics[width=0.24\textwidth]{impSpecFuncTrunc_49.pdf}
+	\caption{{\bf Left}: Zero temperature phase diagram of the embedded impurity model, obtained by tracking impurity-bath spin correlations.
+The pink phase is characterised by perfect Kondo screening and local Fermi liquid excitations (L-FL), leading to non-zero spin-correlations all over the Fermi surface of the conduction electrons.
+The red phase is a local pseudogap (L-PG)  phase, where a part of the Fermi surface (starting from the antinodal regions) no longer participates in Kondo screening.
+This leads to "Fermi arc"-like behaviour in the spin-correlations.
+The black phase is a local moment (LM) phase, where the impurity is completely decoupled from the conduction electrons.
+{\bf Right}: Local spectral function of the impurity site.
+The blue curve is the normal Kondo resonance in the absence of any bath interaction.
+The yellow and green curves show the sharpening the spectral function through the locally pseudogapped phase, as momentum states are expelled from the Kondo cloud.
+The final pink curve shows the charge gap in the local moment phase.}
+	\label{phaseDiagram}
+\end{figure}
+
 \subsection{Presence of a local pseuodogapping transition with electronic differentiation in momentum space}
@@
 \subsection{Spin-correlations across the pseudogap}
-In figures.~\ref{spinCorr} and \ref{vneKspace}, we show the evolution of the spin-flip correlations \(\chi_s(d,\vec k) = \left<S_d^+ S_{\vec k}^- + \text{h.c.}\right>\) and entanglement entropy \(S_\text{EE}(\vec k)\), both in \(k-\)space, as the system is tuned through the pseudogap.
+In figure ~\ref{spinCorr}, we show the evolution of the spin-flip correlations \(\chi_s(d,\vec k) = \left<S_d^+ S_{\vec k}^- + \text{h.c.}\right>\) in \(k-\)space, as the system is tuned through the pseudogap.
 At vanishing value of the interaction \(W\), the spin correlations are concentrated around the antinode, because of the \(p-\)wave nature of the Kondo interaction.
@@
 	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} =\\
-	& \braket{(S^+_{d, {\bf K}_1} + S^+_{{\bf K}_1,d}) S^-({\bf K}_2) + S^+({\bf K}_1) (S^-_{d, {\bf K}_2} + S^-_{{\bf K}_2, d}) \right.\\
-	&+ \left.S^+_{d, {\bf K}_1} (S^-_{{\bf K}_2, d} + S^-_{d, {\bf K}_2}) + (S^+_{{\bf K}_1, d} + S^+_{{\bf K}_1, d}) S^-_{{\bf K}_2, d}}~.
+	& \braket{(S^+_{d, {\bf K}_1} + S^+_{{\bf K}_1,d}) S^-({\bf K}_2) + S^+({\bf K}_1) (S^-_{d, {\bf K}_2} + S^-_{{\bf K}_2, d})} \\
+	&+ \braket{S^+_{d, {\bf K}_1} (S^-_{{\bf K}_2, d} + S^-_{d, {\bf K}_2}) + (S^+_{{\bf K}_1, d} + S^+_{{\bf K}_1, d}) S^-_{{\bf K}_2, d}}~.
 \end{aligned}\end{equation}
@@
 	&\left<C^+({\bf K}_1) C^-({\bf K}_2)\right> = \\
-	& \braket{(C^+_{d, {\bf K}_1} + C^+_{{\bf K}_1,d}) C^-({\bf K}_2) + C^+({\bf K}_1) (C^-_{d, {\bf K}_2} + C^-_{{\bf K}_2, d}) \right.\\
-	&+ \left.C^+_{d, {\bf K}_1} (C^-_{{\bf K}_2, d} + C^-_{d, {\bf K}_2}) + (C^+_{{\bf K}_1, d} + C^+_{{\bf K}_1, d}) C^-_{{\bf K}_2, d}}~.
+	& \braket{(C^+_{d, {\bf K}_1} + C^+_{{\bf K}_1,d}) C^-({\bf K}_2) + C^+({\bf K}_1) (C^-_{d, {\bf K}_2} + C^-_{{\bf K}_2, d})}\\
+	&+ \braket{C^+_{d, {\bf K}_1} (C^-_{{\bf K}_2, d} + C^-_{d, {\bf K}_2}) + (C^+_{{\bf K}_1, d} + C^+_{{\bf K}_1, d}) C^-_{{\bf K}_2, d}}~.
 \end{aligned}\end{equation}
@@
 
+\section{Momentum-space picture of the MIT}
+In order to understand the nature of the transition in momentum space, we employ the expression obtained in the previous sections and compute the spectral function, self-energy and correlation functions in the top right quadrant of the first Brillouin zone.
+We first show the \(k-\)space spectral functions near zero frequency, in Fig.~\ref{kspace_specfunc}.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.23\textwidth]{tiledSF-1.pdf}
+	\includegraphics[width=0.23\textwidth]{tiledSF-2.pdf}
+	\caption{tiledSF.pdf}
+	\label{fig:tiledSF-pdf}
+\end{figure}
 % \begin{figure*}[htpb]
@@
 We first show the \(k-\)space spectral functions near zero frequency, in Fig.~\ref{kspace_specfunc}.
+% \begin{figure}[htpb]
+% 	\centering
+% 	\includegraphics[width=0.8\textwidth]{tiledSF.pdf}
+% 	\caption{tiledSF.pdf}
+% 	\label{fig:tiledSF-pdf}
+% \end{figure}
 %

### 2024-12-18 numerics/caller.jl
improved data saving mechanism, also made specfunc height fixing automatic

@@ -1,10 +1,9 @@
-using Distributed
+using Distributed, Serialization, Random
 
 if length(Sys.cpu_info()) > 10 && nprocs() == 1
     addprocs(20)
 end
-using JLD2
-using LinearAlgebra
+@everywhere using JLD2, LinearAlgebra
 
 @everywhere include("./source/constants.jl")
 include("./source/helpers.jl")
@@ -14,14 +13,14 @@ include("./source/plotting.jl")
 
 global J_val = 0.1
 @everywhere global orbitals = ("p", "p")
-maxSize = 400
-WmaxSize = 400
+maxSize = 10
+WmaxSize = 10
 
 colmap = reverse(ColorSchemes.cherry)
 numShells = 1
 bathIntLegs = 3
 NiceValues(size_BZ) = Dict{Int64, Vector{Float64}}(
-                                                   13 => -1.0 .* [0., 1., 1.5, 1.55, 1.6, 1.61] ./ size_BZ,
+                         13 => -1.0 .* [0., 1., 1.5, 1.55, 1.6, 1.61] ./ size_BZ,
                          33 => -1.0 .* [0, 2.8, 5.6, 5.89, 5.92, 5.93] ./ size_BZ,
                          41 => -1.0 .* [0, 3.5, 7.13, 7.3, 7.5, 7.564, 7.6] ./ size_BZ,
                          49 => -1.0 .* [0, 4.1, 8.19, 8.55, 8.77, 8.8] ./ size_BZ,
@@ -63,10 +62,69 @@ function ScattProb(size_BZ::Int64)
 end
 
 
-function ImpurityCorrelations(size_BZ::Int64)
+function KondoCouplingMap(size_BZ::Int64)
     x_arr = get_x_arr(size_BZ)
-    #=W_val_arr = -1. .* [0., 0.1,]=#
-    W_val_arr = NiceValues(size_BZ)[4:4]
+    W_val_arr = NiceValues(size_BZ)[1:5]
+    @time kondoJArrays, dispersion = RGFlow(W_val_arr, size_BZ)
+    saveNames = Dict(name => [] for name in ["renormalised-map-node", "renormalised-map-antinode"])
+    corrResults = Dict(W_val => Dict() for W_val in W_val_arr)
+    bareMapNode = nothing
+    bareMapAntinode = nothing
+    for W_val in W_val_arr
+        results, results_bare, results_bool = kondoCoupMap((π/2, π/2), size_BZ, kondoJArrays[W_val]; 
[…]

### 2024-12-18 numerics/source/constants.jl

@@ -1,9 +1,13 @@
+(@isdefined SAVEDIR) || const SAVEDIR = "saveData"
+
 # define the edges of the Brillouin zone
 (@isdefined K_MIN) || const K_MIN = -pi
 (@isdefined K_MAX) || const K_MAX = pi
 
 # tolerance for identifying energy contours
 (@isdefined TOLERANCE) || const TOLERANCE = 1e-8
+
+(@isdefined GLOBALFIELD) || const GLOBALFIELD = 1e-5
 
 # overlap integral 't' set to 1
 (@isdefined HOP_T) || const HOP_T = 1.0

### 2024-12-18 numerics/source/plotting.jl

@@ -33,10 +33,13 @@ function plotHeatmap(
         axisLabels::NTuple{2, Union{String, LaTeXString}},
         title::Union{String, LaTeXString},
         annotation::Union{String, LaTeXString},
-        colmap,
+        colmap;
+        figSize::NTuple{2, Int64}=(300, 250),
+        figPad::Union{NTuple{4, Float64}, Float64}=0.,
+        colorScale::Function=identity,
     )
     matrixData = reshape(matrixData, length.(axisVals))
-    figure = Figure(size=(300, 250))
+    figure = Figure(size=figSize, figure_padding=figPad)
     ax = Axis(figure[1, 1],
               xlabel = axisLabels[1], 
               ylabel=axisLabels[2], 
@@ -46,6 +49,7 @@ function plotHeatmap(
              axisVals..., 
              matrixData; 
              colormap=colmap,
+             colorscale=colorScale,
             )
 
     fontsize = 28
@@ -53,7 +57,11 @@ function plotHeatmap(
     Box(gl[1, 1], color = RGBAf(0, 0, 0, 0.4), strokewidth=0, strokecolor=RGBAf(0, 0, 0, 0.8))
     Label(gl[1, 1], annotation, padding = (5, 5, 5, 5), fontsize=div(fontsize, 1.6), color=:white)
 
-    colorbarLimits = ifelse(minimum(matrixData) < maximum(matrixData), (minimum(matrixData), maximum(matrixData)), (minimum(matrixData)*(1-1e-5), minimum(matrixData)*(1+1e-5)))
+    if minimum(matrixData) < maximum(matrixData)
+        colorbarLimits = (minimum(matrixData), maximum(matrixData))
+    else
+        colorbarLimits = (minimum(matrixData)*(1-1e-5) - 1e-5, minimum(matrixData)*(1+1e-5) + 1e-5)
+    end
     Colorbar(figure[1, 2]; 
              limits=colorbarLimits,
              colormap=colmap,

### 2024-12-18 numerics/source/probes.jl

@@ -1,8 +1,7 @@
 ##### Functions for calculating various probes          #####
 ##### (correlation functions, Greens functions, etc)    #####
 
-@everywhere using ProgressMeter, Combinatorics
-@everywhere using Fermions
+@everywhere using ProgressMeter, Combinatorics, FileIO, Fermions
 #=include("/home/abhirup/storage/programmingProjects/fermions.jl/src/iterDiag.jl")=#
 
 """
@@ -40,12 +39,21 @@ end
 Return the map of Kondo couplings M_k(q) = J^2_{k,q} given the state k.
 Useful for visualising how a single state k interacts with all other states q.
 """
-function kondoCoupMap(k_vals::Tuple{Float64,Float64}, size_BZ::Int64, kondoJArrayFull::Array{Float64,3})
-    kspacePoint = map2DTo1D(k_vals..., size_BZ)
-    results = kondoJArrayFull[kspacePoint, :, end] .^ 2
-    results_bare = kondoJArrayFull[kspacePoint, :, 1] .^ 2
+function kondoCoupMap(
+        kx_ky::Tuple{Float64,Float64},
+        size_BZ::Int64,
+        kondoJArrayFull::Array{Float64,3};
+        mapAmong::Union{Function, Nothing}=nothing
+    )
+    kspacePoint = map2DTo1D(kx_ky..., size_BZ)
+    otherPoints = collect(1:size_BZ^2)
+    if !isnothing(mapAmong)
+        filter!(p -> mapAmong(map1DTo2D(p, size_BZ)...), otherPoints)
+    end
+    results = zeros(size_BZ^2) 
+    results[otherPoints] .= kondoJArrayFull[kspacePoint, otherPoints, end]
+    results_bare = kondoJArrayFull[kspacePoint, :, 1]
     results_bool = [r / r_b <= RG_RELEVANCE_TOL ? -1 : 1 for (r, r_b) in zip(results, results_bare)]
-    results[results_bool.<0] .= NaN
     return results, results_bare, results_bool
 end
 
@@ -224,13 +232,28 @@ end
         hamiltDetails::Dict,
         numShells::Int64,
         correlationFuncDict::Dict,
-        maxSize::Int64;
+        maxSize::Int64,
+        savePath::String;
         vneFuncDict::Dict=Dict(),
         mutInfoFuncDict::Dict=Dict(),
         bathIntLegs::Int64=2,
         noSelfCorr::Vector{String}=String[],
         addPerStep::Int64=1,
+        numProcs::Int64=1,
[…]

### 2024-12-18 numerics/source/rgFlow.jl

@@ -218,8 +218,8 @@ end
         progressbarEnabled=false
     )
 
-    savePath = joinpath("RGSaveData", "L=$(size_BZ),omega=$(omega_by_t),J=$(J_val),W=$(bathIntStr),orb=$(join(orbitals))")
-    mkpath("RGSaveData")
+    savePath = joinpath(SAVEDIR, "rgflow-$(size_BZ)-$(omega_by_t)-$(J_val)-$(bathIntStr)-$(join(orbitals))")
+    mkpath(SAVEDIR)
     if isfile(savePath)
         return deserialize(savePath)
     end
@@ -288,6 +288,6 @@ end
         kondoJArray[:, :, stepIndex+1] = round.(kondoJArrayNext, digits=trunc(Int, -log10(TOLERANCE)))
         proceed_flags = proceed_flags_updated
     end
-    serialize(savePath, (kondoJArray, dispersionArray))
+    serialize(savePath, (kondoJArray[:, :, [1, size(kondoJArray)[3]]], dispersionArray))
     return kondoJArray, dispersionArray
 end

### 2024-12-18 TilingProjectDraft/tilingProject.tex
jotted down some points regarding the non-Fermi liquid

@@
 
+\subsection{Nature of the metal near the transition}
+Some thoughts about the nature of the metal near the transition:
+\begin{itemize}
+	\item Typically, there arises some kind of degeneracy close to points of Kondo breakdown.
+In this model, this presumably happens when each Fermi surface point \(k\) starting from the antinodes begin to decouple from the Kondo cloud; at every such point, the local moment state \(\ket{\sigma_d,n_k=0(2)}\) and the singlet state \(\sum_\sigma \sigma\ket{\sigma_d,-\sigma_k}\) become degenerate.
+	\item This also should lead to the orthogonality catastrophe for the local Fermi liquid arising from these \(k-\)points.
+Overall, these two features can probably be combined together using the observation (-> verify) that the embedded eSIAM is a collection of radial eSIAMs.
+	\item With regards to the metal arising from the singular nodal points just before the transition, we can carry out the following calculation.
+In order to obtain the low-lying excitations, we treat the largest Kondo scattering terms (which turn out to be the ones at and between the nodes) as a perturbation above the bath interaction term, and ignore all other Kondo scattering terms (which are either already irrelevant or much smaller than the ones at the node).
+Integrating out the impurity dynamics in this fashion should (-> verify) lead to density-density interactions at the node (\(\mathcal{U}n_{k \uparrow} n_{k \downarrow}\) as well as between the nodes (\(\mathcal{U}n_{k \uparrow} n_{{k + Q} \downarrow}\), where \(Q = \left(\pi, \pi\right) \)).
+The low-lying excitations are therefore described by a Hatsugai-Kohmoto model (HKM).
+	\item The emergence of the HKM indicates that the nodal points harbour a non-Fermi liquid.
+Since the model is exactly solvable, one can try to calculate various diagnostics such as the quasiparticle residue and the self-energy.
+It is also interesting to note that a similar trick was employed in our 1CK work to obtain the effective theory for the Kondo cloud; there, because of the more democratic nature of the Kondo interaction (in \(k-\)space), the effective theory had all kinds of terms (not just the HKM).
+That was of course associated with local Fermi liquid behaviour.
+It appears, therefore, that the selective irrelevance of certain \(k-\)modes on the Fermi surface in terms of Kondo screening transforms the "all-to-all" Kondo cloud theory into the non-Fermi liquid HKM near the transition.
+\end{itemize}
+
 \section{The Tiling Algorithm}
 
-\subsection{Formal description of the tiling procedure}\label{formalDescription}
+\subsection{Formal description of the tiling procedure}
 We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian.
@@
 \begin{equation}\begin{aligned}\label{propagatorW}
+	G_W = 1/\left(\omega - |\varepsilon_j|/2 + W_{\bf q}/2)\right)
+\end{itemize}
+
+\section{The Tiling Algorithm}
+
+\subsection{Formal description of the tiling procedure}\label{formalDescription}
+We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian.
+The first step is of course to identify an impurity model that can act as a good auxiliary model for out lattice model.
+The local behaviour of this impurity model should reflect the essential local physics of the lattice model.
+Typically, we will consider impurity model geometries where the real-space bath site connected directly to the impurity also harbours some kind of local interaction.
+We will henceforth refer to this site as the zeroth site.
+In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout.
+
+In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})\).
+The unit cell at the position \({\bf r}_d\) is then obtained by placing the zeroth site on all nearest-neighbours of \({\bf r}_d\) and averaging over these configurations:
+\begin{equation}\begin{aligned}\label{unitCellHamiltonian}
+	\mathcal{H}_\text{aux}({\bf r}_d) = \frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})~,
+\end{aligned}\end{equation}
+where \({\bf z}\) is summed over all nearest-neighbours of \({\bf r}_d\) and \(\mathcal{Z}\) is the number of such nearest-neighbours.
+
+In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice.
+For this, we define {\it many-particle global} translation operators \(T({\bf a})\) that translate all positions by a vector \({\bf a}\).
+In terms of manybody states and operators, their action is defined as
+\begin{equation}\begin{aligned}\label{translationDefinition}
+	&T^\dagger({\bf a}) \ket{{\bf r}_1, {\bf r}_2,\ldots} = \ket{{\bf r}_1 + {\bf a}}\otimes\ket{{\bf r}_2 + {\bf a}}\ldots\otimes\ket{{\bf r}_n + {\bf a}}\\
+	&T^\dagger({\bf a}) \mathcal{O}\left({\bf r}_1, {\bf r}_2,\ldots\right)T({\bf a}) = \mathcal{O}\left({\bf r}_1 + {\bf a}, {\bf r}_2 + {\bf a},\ldots\right)~,
+\end{aligned}\end{equation}
+where \(\ket{{\bf r}_1, {\bf r}_2,\ldots}\) is a state in the manyparticle Fock-space basis with the particles localised at the specified positions.
+For example, for a local fermionic creation operator \(c^\dagger({\bf r})\), we have
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a}) c^\dagger({\bf r}) T({\bf a}) = c^\dagger({\bf r} + {\bf a})~.
+\end{aligned}\end{equation}
+It acts similarly on the auxiliary model Hamiltonian:
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a})\mathcal{H}_\text{aux}({\bf r}_d)T({\bf a}) = \mathcal{H}_\text{aux}({\bf r}_d + {\bf a})~,
+\end{aligned}\end{equation}
+translating all sites by the vector \({\bf a}\). By introducing the Fourier transform to momentum space,
+\begin{equation}\begin{aligned}
+	\ket{{\bf r}_1, {\bf r}_2,\ldots} = \otimes_{j=1}^N \int d{\bf k}_j e^{-i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf k}_j}~,
+\end{aligned}\end{equation}
+it is easy to see that the total momentum states are eigenstates of the global translation operators:
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a})\ket{{\bf k}_1, {\bf k}_2,\ldots} &= \otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} T^\dagger({\bf a})\ket{{\bf r}_j}~,\\
+							    &=\otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf r}_j + {\bf a}}\\
+							    &=e^{-i {\bf a}_j\cdot{\bf k}_\text{tot}}\ket{{\bf k}_1, {\bf k}_2,\ldots},
+\end{aligned}\end{equation}
+where \({\bf k}_\text{tot} = \sum_j {\bf k}_j\) is the total momentum.
+
+The auxiliary model, being an impurity model, lacks translation symmetry.
+The lattice model does remain invariant under global translation operations.
+In order to reconstruct the full lattice model and restore its translation invariance, we translate the unit cell across all sites of the lattice:
+\begin{equation}\begin{aligned}
+	\label{tilingPrescription}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})\\
+				&= \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r} - {\bf r}_d)~ \\
+				&= \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d)~ \\
+\end{aligned}\end{equation}
+where \({\bf r}\) sums over all lattice sites.
+
+\subsection{Extending the Anderson impurity model: Identifying the correct auxiliary model}
+The standard Anderson model consists of a correlated impurity site coupled with a non-interacting conduction bath.
+The double occupancy cost on the impurity is \(U\), while the single-particle hopping strength between the impurity and the conduction bath is \(V\).
+Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes.
+We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model).
+The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
+\begin{equation}\begin{aligned}
+	\label{siam_attr}
+	\mathcal{H}_\text{E-S} = \mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} + \mathcal{H}_\text{imp-cbath}~,
+\end{aligned}\end{equation}
+where 
+\begin{itemize}
+	\item \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site,
+	\item \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and
+	\item \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 - V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath.
+\end{itemize}
+Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath.
+We have found that the e-SIAM has a stable local moment phase for \(U_b < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)).
+We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of an optical gap in the local spectral function beyond a certain value of interaction strength.
+Note that the impurity site and the conduction bath are both at half-filling.
+
+\subsection{Tiling towards a Hubbard-Heisenberg model with an embedded extended SIAM}
+In this subsection, we provide an explicit example of constructing a lattice model.
+We will consider a slightly more generalised version of the extended SIAM described in the previous section, where the impurity site coupled to the conduction bath purely through the s-wave channel.
+We will show that that model leads to a form of a Hubbard-Heisenberg model upon restoring translation invariance via repeated translation operations.
+The generalisation involve allowing an arbitrary filling on the impurity site and in the conduction bath, through two additional parameter: (i) a particle-hole asymmetry parameter \(\eta\) for the impurity site, (ii) a chemical potential for the conduction bath, and (iii) embedding the impurity into the lattice of the 2D conduction bath.
+This modified impurity model is shown in Fig.~\ref{embeddedEsiam}.
+The first term modifies the impurity Hamiltonian \(\mathcal{H}_\text{imp}\) into
+\begin{equation}\begin{aligned}\label{onsiteHamiltonian}
+	\mathcal{H}_\text{imp} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 - \eta\sum_\sigma \hat n_{{\bf r}_d\sigma}~.
+\end{aligned}\end{equation}
+where we have placed the impurity site at the position \({\bf r}_d\). The second term modifies the conduction bath Hamiltonian \(\mathcal{H}_\text{cbath}\):
+\begin{equation}\begin{aligned}\label{bathHamiltonian}
+	\mathcal{H}_\text{cbath} &= -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
+							 &- \frac{1}{2 \mathcal{Z}}U_b\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
+\end{aligned}\end{equation}
+where \(\left<{\bf r}_i, {\bf r}_j\right>\neq {\bf r}_d\) indicates that the sum is over all nearest-neighbour pairs of sites avoiding the impurity site \({\bf r}_d\).
+
+In this notation, the interaction Hamiltonian can be written as
+\begin{equation}\begin{aligned}\label{interactionHamiltonian}
+	\mathcal{H}_\text{imp-cbath} &= \frac{J}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}\sum_{{\bf z}\in\text{NN}({\bf r}_d)} {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \\
+								 & - \frac{V}{\sqrt{\mathcal{Z}}}\sum_{\sigma} \sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)
+\end{aligned}\end{equation}
+where \(\boldsymbol \tau = \left( \tau_x, \tau_y, \tau_z \right) \) is the vector of Pauli matrices. \(\sigma\) and \(\sigma^\prime\) can be \(\pm 1\) and represent up and down configurations.
+
+We now follow the prescription laid out in eq.~\ref{tilingPrescription}. The tiled Hamiltonian can be written as 
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{tiled} = \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} \right.\\
+\left.+ \mathcal{H}_\text{imp-cbath}\right]T({\bf r} - {\bf r}_d)~.
+\end{aligned}\end{equation}
+Note that in comparison to eq.~\ref{tilingPrescription}, we have dropped the sum over the zeroth sites, because our impurity model Hamiltonian (defined using eqs.~\ref{onsiteHamiltonian} through \ref{interactionHamiltonian}) already contains a sum over these zeroth sites.
+
+We consider the effect of the translation operations on each part of the Hamiltonian. We first have
+\begin{equation}\begin{aligned}
+	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d) \\
+	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \right.\\
+	 &\left.- \frac{U_b}{2\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}\right]T({\bf r} - {\bf r}_d) \\
+	=& -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
+	 &- \frac{U_b}{2\mathcal{Z}}\sum_{\bf r}\sum_{{\bf z}\in\text{NN}\left({\bf r}\right)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i}\sum_{{\bf r} \neq {\bf r}_i}\hat n_{{\bf r}_i,\sigma}\\
+	=& -\frac{1}{\sqrt\mathcal{Z}}(N-2)t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
+	 &- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+\end{aligned}\end{equation}
+In the first step, the factor of \(\mathcal{Z}\) is cancelled out by the trivial sum over \({\bf r}_0\) in the first and third terms.
+At the last step, the three terms simplified for the following reasons.
+The inequality \(\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}\) in the first term ensures that each nearest-neighbour pair appears in \(N-2\) instances of the auxiliary model, \(N\) being the total number of lattice sites; the two instances that do not contribute are the ones in which the impurity site itself is at \({\bf r}_i\) or \({\bf r}_j\).
+For the second term, the double sum \(\sum_{\bf r}\sum_{{\bf z} \in \text{NN}({\bf r})}\) evaluates to \(\mathcal{Z}\sum_{\bf r}\), because each point on the lattice appears \(\mathcal{W}\) times in the summation.
+This factor of \(\mathcal{W}\) cancels the one in the denominator.
+In the third term, the inner summation simply evaluates to \(N-1\), and we finally replace the dummy index \({\bf r}_i\) with \({\bf r}\).
+
+The next part is
+\begin{equation}\begin{aligned}
+	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp}T({\bf r} - {\bf r}_d) \\
+	=& -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}~.
+\end{aligned}\end{equation}
+This is obtained simply by replacing the impurity position \({\bf r}_d\) with the translated position \({\bf r}\), generating a translation-invariant Hubbard term (the first term) and a finite chemical potential (second term).
+
+We now consider the final term:
+\begin{equation}\begin{aligned}
+	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp-cbath}T({\bf r} - {\bf r}_d)\\
+	&=\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
+				     &-  \left. \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma} V \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]T({\bf r} - {\bf r}_d)\\
+	&=\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r})}\left[\frac{1}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
+				     &-  \frac{1}{\sqrt\mathcal{Z}}\left.\sum_{\sigma} V\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]\\
+					 &=\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]\\
+\end{aligned}\end{equation}
+At the last step, each nearest-neighbour pair of sites \({\bf r}_i, {\bf r}_j\) appear 2 times in the summation, because any site is a member of two distinct nearest-neighbour pairs.
+We have also defined \({\bf S}_{{\bf r}_j} =\sum_{\sigma,\sigma^\prime} {\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime}\) as the local spin operator.
+
+The total tiled Hamiltonian is therefore
+\begin{equation}\begin{aligned}
+	&\mathcal{H}_\text{tiled} \\
+	&= -\frac{N-2}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>,\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+	&- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}\\
+	& + \sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]
+\end{aligned}\end{equation}
+While constructing the tiled Hamiltonian, we have added extra copies of the non-interacting Hamiltonian \(\mathcal{H}_\text{cbath-nint} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\) for the conduction bath (this results in the factors of \(N-2\) and \(N-1\) in front of the first and third terms).
+Upon removing these repeated terms, the tiled Hamiltonian becomes
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}\\
+							 &= -\frac{1}{\sqrt\mathcal{Z}}(t + 2V)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
+							 &- \frac{1}{2}\left(U + U_b\right)\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \left(\eta + 2\mu\right) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} \\
+							 &+ \frac{2}{\mathcal{Z}}J\sum_{\left< {\bf r}_i, {\bf r}_j\right>} {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j}
+\end{aligned}\end{equation}
+
+The result of the tiling operations is a Hubbard-Heisenberg model, of the form
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{HH} &= -\frac{1}{\sqrt\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+						  &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
+\end{aligned}\end{equation}
+where the tilde symbol indicates that the parameters are for the lattice model (and not the auxiliary model).
+By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to each other:
+\begin{equation}\begin{aligned}\label{couplingsMappings}
+	\tilde t = t+2V,~~ \tilde U = U + U_b, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
+\end{aligned}\end{equation}
+In summary, the appropriate method for reconstructing the lattice model Hamiltonian is therefore
+\begin{equation}\begin{aligned}\label{tilingPrescriptionFinal}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}~,
+\end{aligned}\end{equation}
+using which the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.
+
+\subsection{Translation symmetry and a conserved total momentum}
+From the form in eq.~\ref{tilingPrescriptionFinal}, the tiled Hamiltonian is symmetric under global many-body translations of the kind defined in eq.~\ref{translationDefinition}, by arbitrary lattice spacings:
+\begin{equation}\begin{aligned}\label{translationSymmetry}
+	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})T({\bf a}) = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r + a}) = \sum_{{\bf r}^\prime}\mathcal{H}_\text{aux}({\bf r}^\prime)\\
+	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{cbath-nint}T({\bf a}) = \mathcal{H}_\text{cbath-nint}\\
+	&\implies T({\bf a})^\dagger\mathcal{H}_\text{tiled}T({\bf a}) = \mathcal{H}_\text{tiled}~.
+\end{aligned}\end{equation}
+In the first equation, we used the fact that the translation operator simply translates the auxiliary model at the position \({\bf r}\) into another one at the position \({\bf r} + {\bf a}\).
+Since both are part of the summation, the summation remains unchanged.
+The second equation uses the fact that the Hamiltonian \(\mathcal{H}_\text{cbath-nint}\) is that of a tight-binding model and is therefore translation-invariant.
+The fact that the Hamiltonian \(\mathcal{H}_\text{tiled}\) commutes with the many-body translation operator implies that the total crystal momentum \(\vec k\) is a conserved quantity.
+
+\section{Form of the eigenstates: Bloch's theorem}
+In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\bf k}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_i}\), where \({\bf r}_i\) sums over the positions of the local Hamiltonians.
+Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation by an arbitrary number of lattice spacings \({n\bf a}\):
+\begin{equation}\begin{aligned}
+	T^\dagger(n{\bf a})\ket{\Psi_{{\bf k}}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_{i + n}} = e^{-in{\bf k}\cdot{\bf a}}\ket{\Psi_{\bf k}}
+\end{aligned}\end{equation}
+The definition and some properties of these global translation operations were provided in subsection~\ref{formalDescription}.
+It was shown there that they share eigenstates with the total momentum operator.
+In a lattice model, this continuous symmetry gets lowered to its discrete form: the total {\it crystal} momentum is conserved by any scattering process.
+As a result, the eigenstates can be labelled using the combined index \(s = \left({\bf k}, n\right) \) where \({\bf k}\) is the total crystal momentum and \(n\) is a band index \(n\).
+
+The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using eq.~\ref{tilingPrescriptionFinal} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}).
+This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) defined in eq.~\ref{unitCellHamiltonian} can be used to construct eigenstates of the lattice Hamiltonian.
+The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
+
+The state \(\ket{\psi_n\left({\bf r}_d\right)}\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself has been averaged over \(\mathcal{Z}\) zeroth sites.
+Accordingly, we can express the averaged eigenstate \(\ket{\psi_n\left({\bf r}_d\right)}\) as
+\begin{equation}\begin{aligned}
+	\ket{\psi_n\left({\bf r}_d\right)} = \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z} \in \text{NN}({\bf r}_d)}\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}~,
+\end{aligned}\end{equation}
+where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\).
+With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:
+\begin{equation}\begin{aligned}\label{eigenstateProposal}
+	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} \\
+				&= \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d, {\bf z}\right)}~,
+\end{aligned}\end{equation}
+where \(N\) is the total number of lattice sites and \({\bf r}_d\) is summed over all lattice spacings.
+The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands.
+The ground state \(s = s_0\) is obtained by setting \({\bf k}\) and \(n\) to 0:
+\begin{equation}\begin{aligned}\label{groundstateProposal}
+	\ket{\Psi_\text{gs}} \equiv \ket{\Psi_{s_0}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)} \\
+			     &= \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d, {\bf z}\right)}
+\end{aligned}\end{equation}
+
+\section{1-particle Greens Functions}
+In the previous part, we proposed a form for the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{gs}}\) of the auxiliary models.
+In this section, we will relate one-particle Greens functions of the bulk lattice to those of the auxiliary model.
+We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
+We define the retarded time-domain Greens function between two quantum numbers \(\nu_1\) and \(\nu_2 \) at zero temperature as
+\begin{equation}\begin{aligned}
+	\tilde G(\nu_2, \nu_1; T) = -i\theta(T) \braket{\Psi_\text{gs} | \left\{ c(\nu_2, T), c^\dagger(\nu_1) \right\} | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(T\): 
+\begin{equation}\begin{aligned}
+	c(\nu,t) = e^{iT H_\text{tiled} }c(\nu)e^{-i T H_\text{tiled}}~.
+\end{aligned}\end{equation}
+The quantum number \(\nu\) typically refers to position or momentum: setting \(\nu_1={\bf r}_1, \nu_2={\bf r}_2\) will lead to a real-space Greens function between the two spatial points.
+By introducing the Fourier transform \(g(T) = \int d\omega~ e^{-i\omega T}f(\omega)\), the frequency-domain Greens function can be cast in its spectral representation
+\begin{equation}\begin{aligned}\label{spectralRepresentation}
+	&\tilde G(\nu_2, \nu_1; \tilde\omega) \\
+	&= \frac{1}{\mathcal{D}_\text{gs}}\sum_{s_0 \in \text{GS}}\sum_s \left[\frac{F_{c^\dagger}^*(s, \nu_2)F_{c^\dagger}(s, \nu_1)}{\tilde\omega - \left( \tilde E_s - \tilde E_\text{gs} \right) } + \frac{F_{c}(s, \nu_1)F_{c}^*(s, \nu_2)}{\tilde\omega + \left( \tilde E_s - \tilde E_\text{gs} \right) }\right] ~,
+\end{aligned}\end{equation}
+where \(s_0=\left({\bf k}_0, n_0\right)\) sums over the ground state(s) of the system (with energy \(\tilde E_\text{gs}\) and degeneracy \(\mathcal{D}_\text{gs}\)) and \(s=\left({\bf k}, n\right)\) sums over all eigenstates (with energies \(\tilde E_s\)).
+The coefficients
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}(s, \nu) = \braket{\Psi_{s}|c^\dagger(\nu)|\Psi_{s_0}},\\
+	F_{c}(s, \nu) = \braket{\Psi_{s}|c(\nu)|\Psi_{s_0}}~,
+\end{aligned}\end{equation}
+represent spectral weights for particle and hole excitations from the ground state \(\ket{s_0}\) into the excited state \(\ket{s}\).
+
+In order to make contact with the auxiliary models, the first simplification  that we carry out is of the eigenenergies \(\tilde E_s\)in the denominators.
+The label \(s\) involves a total momentum \({\bf k}\) and a band index \(n\).
+Guided by the relation eq.~\ref{tilingPrescriptionFinal} between the Hamiltonians, we assume a separation of the total energy into an impurity model contribution \(E_n\) coming from \(\mathcal{H}_\text{aux}\) and a contribution \(\varepsilon({\bf k})\) coming from the non-interacting background Hamiltonian \(\mathcal{H}_\text{cbath-nint}\): \(E_s \simeq N E_n - (N-3) \varepsilon_{\bf k}\)~, where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\).
+Replacing \(N-3\) with \(N\) for a system of large number of particles, the spectral representation can be written as
+\begin{equation}\begin{aligned}
+	&\tilde G(\nu_2, \nu_1; \tilde\omega) \\
+	&= \frac{1}{\mathcal{D}_\text{gs}}\sum_{s_0 \in \text{GS}}\sum_s \left[\frac{F_{c^\dagger}^*(s, \nu_2)F_{c^\dagger}(s, \nu_1)}{\tilde\omega - N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) } \right.\\
+	&\left. + \frac{F_{c}(s, \nu_1)F_{c}^*(s, \nu_2)}{\tilde\omega + N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) }\right] ~,
+\end{aligned}\end{equation}
+where the absence of the tilde in the denominators indicates that those energies arise from the auxiliary model Hamiltonian.
+In order to rewrite this expression in terms of quantities that can be computed purely from the auxiliary models, we replace the eigenstates with the forms given in eq.~\ref{eigenstateProposal}:
+\begin{equation}\begin{aligned}\label{spectralWeightsAuxiliary}
+	&F_{c^\dagger}^*(s, \nu_2) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{i {\bf k}\cdot{\bf r}_d - {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_{n_0}({\bf r}_d^\prime)|c(\nu_2)|\psi_{n}({\bf r}_d)}\\
+	&F_{c^\dagger}(s, \nu_1) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{-i {\bf k}\cdot{\bf r}_d + {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_n({\bf r}_d)|c^\dagger(\nu_1)|\psi_{n_0}({\bf r}_d^\prime)}~,
+\end{aligned}\end{equation}
+where \({\bf k}_0\) is the crystal momentum value in the ground state.
+
+\subsection{Real-space Greens functions}
+We first consider one-particle Greens functions \(\tilde G({\bf r}; \tilde\omega)\) for the propagation of excitations between two spatial points \(\nu_1={\bf r}_c\) and \(\nu_2={\bf r}_c + {\bf r}\), where \({\bf r}_c\) is a fixed reference point in the lattice.
+Within the impurity model, the lattice site that most closely resembles the bulk lattice model is of course the impurity site; in order to ensure that all terms in eq.~\ref{spectralRepresentation} involve the impurity site, we approximate the states within \(F_{c^\dagger}(s,\nu_1) = F_{c^\dagger}(s,{\bf r}_c)\) of eq.~\ref{spectralWeightsAuxiliary} purely in terms of the auxiliary model at \({\bf r}_c\):
+\begin{equation}\begin{aligned}\label{eigenstateUniform}
+	\ket{\Psi_s} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} \left[e^{i {\bf k}\cdot{\bf r}_c} \ket{\psi_{n}\left({\bf r}_c\right)} + \ket{\psi_{n}}_\text{diff}\right]\\
+		     &\simeq \sqrt N e^{i {\bf k}\cdot{\bf r}_c} \ket{\psi_{n}\left({\bf r}_c\right)}.
+\end{aligned}\end{equation}
+This amounts to retaining the spatially uniform part of the wavefunction and dropping the modulating difference term \(\ket{\psi_{n}}_\text{diff} = e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} - e^{i {\bf k}\cdot{\bf r}_c} \ket{\psi_{n}\left({\bf r}_c\right)}\).
+Replacing the exact forms in \(F_{c^\dagger}(s, {\bf r}_c)\) with this approximation results in the expression
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}(s, {\bf r}_c) \simeq N e^{-i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_c} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+For the other term \(F_{c^\dagger}(s,\nu_2) = F_{c^\dagger}(s,{\bf r}_2)\), we make the less drastic approximation of retaining the matrix elements between the same auxiliary models \({\bf r}_d = {\bf r}_d^\prime\), leading to
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}^*(s, {\bf r}_2) = \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_d)|c({\bf r}_2)|\psi_{n}({\bf r}_d)}~.
+\end{aligned}\end{equation}
+The summation can be transferred on to the annihilation operator by using translation operators:
+\begin{equation}\begin{aligned}
+	&\braket{\psi_{n_0}({\bf r}_d)|c({\bf r}_2)|\psi_{n}({\bf r}_d)} \\
+	&= \braket{\psi_{n_0}({\bf r}_c)|T\left({\bf r}_d - {\bf r}_c\right) c({\bf r}_2) T^\dagger\left({\bf r}_d - {\bf r}_c\right) |\psi_{n}({\bf r}_c)}\\
+	&= \braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_2 + {\bf r}_c - {\bf r}_d) |\psi_{n}({\bf r}_c)}~,
+\end{aligned}\end{equation}
+leading to the more useful form
+\begin{equation}\begin{aligned}
+	&F_{c^\dagger}^*(s, {\bf r}_2) \\
+	&= \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_2 + {\bf r}_c - {\bf r}_d) |\psi_{n}({\bf r}_c)}\\
+	&= \frac{1}{N}\sum_{{\bf r}_x} e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_x\right)} \braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_c + {\bf r}_x) |\psi_{n}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+In the second step, we introduced a new dummy variable \({\bf r}_x = {\bf r}_2 - {\bf r}_d\) that tracks the propagation of excitations into the auxiliary model.
+
+Having obtained the particle spectral coefficients, we can obtain the hole counterparts by mapping them onto each other.
+This can be done by noting that under our assumptions of \({\bf r}_d = {\bf r}_d^\prime\) in eq.~\ref{spectralWeightsAuxiliary}, we have the following relations:
+\begin{equation}\begin{aligned}
+	F_{c} &= F_{c^\dagger}^*\left({\bf k}\leftrightarrow{\bf k}_0, n \leftrightarrow n_0\right),\\
+	F_{c}^* &= F_{c^\dagger}\left({\bf k}\leftrightarrow{\bf k}_0, n \leftrightarrow n_0\right)~.
+\end{aligned}\end{equation}
+Using these, we get
+\begin{equation}\begin{aligned}\label{spectralParticleHoleRelation}
+	F_{c} &= \frac{1}{N}\sum_{{\bf r}_x} e^{i \left({\bf k}_0- {\bf k}\right)\cdot\left({\bf r}_2 - {\bf r}_x\right)} \braket{\psi_{n}({\bf r}_c)| c({\bf r}_x) |\psi_{n_0}({\bf r}_c)},\\
+	F_{c}^* &= N e^{-i \left({\bf k}_0 - {\bf k}\right)\cdot{\bf r}_c} \braket{\psi_{n_0}({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+
+The complete expression for \(\tilde G_\text{loc}(\tilde\omega)\) now looks like
+\begin{widetext}
+\begin{equation}\begin{aligned}
+	\tilde G({\bf r}; \tilde\omega) &= \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,{\bf k}_0}\sum_{{\bf k}, n}\sum_{{\bf r}_x}  \left[e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}\frac{\braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_x) |\psi_{n}({\bf r}_c)} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}}{\tilde\omega - N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) } \right.\\
+					  &\left.+ e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}\frac{\braket{\psi_{n_0}({\bf r}_c)| c^\dagger({\bf r}_c) |\psi_{n}({\bf r}_c)} \braket{\psi_n({\bf r}_c)|c({\bf r}_x)|\psi_{n_0}({\bf r}_c)}}{\tilde\omega + N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) }\right] ~,\\
+					  &= \frac{1}{N}\sum_{{\bf k}_0, {\bf k}}\sum_{{\bf r}_x}  \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,n}\left[e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}\frac{\braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_x) |\psi_{n}({\bf r}_c)} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}}{\omega - \left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) } \right.\\
+					  &\left.+ e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}\frac{\braket{\psi_{n_0}({\bf r}_c)| c^\dagger({\bf r}_c) |\psi_{n}({\bf r}_c)} \braket{\psi_n({\bf r}_c)|c({\bf r}_x)|\psi_{n_0}({\bf r}_c)}}{\omega + \left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) }\right] ~,
+\end{aligned}\end{equation}
+\end{widetext}
+where \(\omega = \tilde\omega/N\) is the frequency scale for the auxiliary model.
+We can define an auxiliary model Greens functions \(G(d,{\bf r}_x; T) = -i\theta(T)\braket{\psi_\text{gs} | \left\{c^\dagger_{{\bf d}\sigma}, c_{{\bf d} + {\bf r}_x\sigma}\right\} | \psi_\text{gs}}\) for the propagation of excitations that start from the impurity site and extend up to a distance \({\bf r}_x\) into the auxiliary model; the subscripts \(p\) and \(h\) indicate that that Greens function involves only the positive and negative frequency poles respectively.
+In terms of these, the lattice model Greens function can be written in a more intuitive form.
+Assuming a unique momentum \({\bf k}_0\) for the ground state and adjusting the ground state non-interacting energy \(\varepsilon_{{\bf k}0}\) to zero, we get
+\begin{equation}\begin{aligned}
+	&\tilde G({\bf r}; \tilde\omega) \\
+	&= \frac{1}{N}\sum_{{\bf k}}\sum_{{\bf r}_x}  \left[e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}G_p\left({\bf r}_x;\omega + \varepsilon_{\bf k}\right) \right.\\
+	&\left.+ e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}G_h\left({\bf r}_x;\omega - \varepsilon_{\bf k}\right)\right]
+\end{aligned}\end{equation}
+
+\subsection{Momentum-space Greens functions}
+We now consider Greens functions at a particular momentum \({\bf K}\), obtained by setting \(\nu_1=\nu_2={\bf K}\). The spectral coefficients are of the form
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{i {\bf k}\cdot{\bf r}_d - {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_{n_0}({\bf r}_d^\prime)|c({\bf K})|\psi_{n}({\bf r}_d)}\\
+	F_{c^\dagger}(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{-i {\bf k}\cdot{\bf r}_d + {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_n({\bf r}_d)|c^\dagger({\bf K})|\psi_{n_0}({\bf r}_d^\prime)}~.
+\end{aligned}\end{equation}
+Similar to the approach for the real-space Greens function, we simplify \(F^*_p(s, {\bf K})\) by retaining only the \({\bf r}_d = {\bf r}_d^\prime\) members, and then translating the arbitrary point \({\bf r}_d\) to a common reference point \({\bf r}_c\) in the lattice:
+\begin{equation}\begin{aligned}
+	&F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_d)|c({\bf K})|\psi_{n}({\bf r}_d)}~,\\
+	&\braket{\psi_{n_0}({\bf r}_d)|c({\bf K})|\psi_{n}({\bf r}_d)}\\
+	&= \braket{\psi_{n_0}({\bf r}_c)| T\left({\bf r}_d - {\bf r}_c\right) c({\bf K}) T^\dagger\left({\bf r}_d - {\bf r}_c\right) |\psi_{n}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+The effect of the translation operators on the \(k-\)space annihilation operator can be easily deduced by transforming it to real-space, using the Fourier transform definition
+\begin{equation}\begin{aligned}\label{fourTransf}
+	c({\bf K}) = \frac{1}{\sqrt N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}c({\bf r})~.
+\end{aligned}\end{equation}
+Upon applying this, we get
+\begin{equation}\begin{aligned}\label{translationOnField}
+	&T\left({\bf r}_d - {\bf r}_c\right) c({\bf K}) T^\dagger\left({\bf r}_d - {\bf r}_c\right)\\
+	&= \frac{1}{N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}T\left({\bf r}_d - {\bf r}_c\right) c({\bf r}) T^\dagger\left({\bf r}_d - {\bf r}_c\right)\\
+	&= \frac{1}{N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}c({\bf r} - {\bf r}_d + {\bf r}_c)\\
+	&= e^{i{\bf K}\cdot\left({\bf r}_d - {\bf r}_c\right)}c({\bf K})~.
+\end{aligned}\end{equation}
+With this, the final form of \(F_{c^\dagger}^*(s, {\bf K})\) becomes
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}e^{-i {\bf K}\cdot{\bf r}_c}\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}\\
+	\times\sum_{{\bf r}_d}e^{i \left({\bf K} + {\bf k} - {\bf k}_0\right)\cdot{\bf r}_d}
+\end{aligned}\end{equation}
+The sum over \({\bf r}_d\) evaluates to \(\sum_{{\bf r}_d}e^{i \left({\bf K} + {\bf k} - {\bf k}_0\right)\cdot{\bf r}_d} = N \delta_{{\bf K}, - {\bf k} + {\bf k}_0}\), leading to
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}^*(s, {\bf K}) = e^{-i {\bf K}\cdot{\bf r}_c}\delta_{{\bf K}, - {\bf k} + {\bf k}_0}\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}
+\end{aligned}\end{equation}
+
+For the other coefficient \(F_{c^\dagger}(s, {\bf K})\), we again proceed similar to the previous subsection: we retain only the uniform part of the wavefunction, placing all the impurity models at the reference point \({\bf r}_c\):
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}(s, {\bf K}) = Ne^{-i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_c} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf K})|\psi_{n_0}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+In order to introduce the impurity site operator in the expression, we Fourier transform \(c^\dagger({\bf K})\) (following eq.~\ref{fourTransf}), and keep only that real-space mode that lies on the impurity reference point \({\bf r}_c\):
+\begin{equation}\begin{aligned}
+	F_{c^\dagger}(s, {\bf K}) = e^{-i \left({\bf k} - {\bf k}_0 + {\bf K}\right)\cdot{\bf r}_c} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+
+Using eq.~\ref{spectralParticleHoleRelation}, we obtain the hole transition coefficients:
+\begin{equation}\begin{aligned}
+	F_{c}(s, {\bf K}) &= e^{-i {\bf K}\cdot{\bf r}_c}\delta_{{\bf K}, {\bf k} - {\bf k}_0}\braket{\psi_{n}({\bf r}_c)|c({\bf K})|\psi_{n_0}({\bf r}_c)},\\
+	F_{c}^*(s, {\bf K}) &= e^{-i \left({\bf k}_0 - {\bf k} + {\bf K}\right)\cdot{\bf r}_c} \braket{\psi_{n_0}({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+
+The complete expression for the momentum space Greens function is therefore
+\begin{widetext}
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}; \tilde\omega) = \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,{\bf k}_0 \in \text{GS}}\sum_{n,{\bf k}} e^{-i {\bf K}\cdot{\bf r}_c}\left[\delta_{{\bf K}, - {\bf k} + {\bf k}_0}\frac{\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}\braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}}{\tilde\omega - N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) } \right.
+\\
+	+ \left.\delta_{{\bf K}, {\bf k} - {\bf k}_0}\frac{\braket{\psi_{n}({\bf r}_c)|c({\bf K})|\psi_{n_0}({\bf r}_c)}\braket{\psi_{n_0}({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n}({\bf r}_c)}}{\tilde\omega + N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) }\right] ~.
+\end{aligned}\end{equation}
+\end{widetext}
+Once again assuming the uniqueness of \({\bf k}_0\), setting \(\varepsilon_{{\bf k}0}\) to zero and choosing the reference point \({\bf r}_c\) such that \({\bf K}\cdot{\bf r}_c = 0\), we have
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}; \tilde\omega) = G_p\left({\bf r}_c, {\bf K}; \omega + \varepsilon_{{\bf k}_0 - {\bf K}}\right) + G_h\left({\bf r}_c, {\bf K}; \omega - \varepsilon_{{\bf k}_0 + {\bf K}}\right),
+\end{aligned}\end{equation}
+where we have identified \({\bf r}_c\) as the impurity site and defined an auxiliary model Greens function \(G\left(d, {\bf K}; T\right) = -i\theta(T)\braket{\psi_\text{gs} | \left\{c^\dagger_{d\sigma}, c_{{\bf K},\sigma}\right\} | \psi_\text{gs}} \) for propagation of excitations from the \(d(f)-\)orbital impurity state \(\ket{d\sigma}\) into a momentum state of the conduction bath.
+
+\subsection{Spectral function and self-energies}
+Having obtained the one-particle Greens functions in both real and momentum-space, one can directly obtain the corresponding spectral functions \(\tilde A(\nu_2,\nu_1; \omega)\) and self-energies \(\tilde \Sigma(\nu_2,\nu_1; \omega)\), using standard relations.
+For eg., in momentum space, we have
+\begin{equation}\begin{aligned}
+	&\tilde A({\bf K}; \omega) \\
+	&= -\frac{1}{\pi}\text{Im}\left[\tilde G({\bf K}; \tilde\omega)\right]  \\
+	&= -\frac{1}{\pi}\text{Im}\left[G_p\left(d, {\bf K}; \omega + \varepsilon_{{\bf k}_0 - {\bf K}}\right) + G_h\left(d, {\bf K}; \omega - \varepsilon_{{\bf k}_0 + {\bf K}}\right)\right],\\
+\end{aligned}\end{equation}
+and
+\begin{equation}\begin{aligned}
+	\tilde \Sigma({\bf K}; \omega) = \left(\tilde G^{(0)}({\bf K}; \tilde\omega)\right)^{-1} - \left(\tilde G({\bf K}; \tilde\omega)\right)^{-1},
+\end{aligned}\end{equation}
+where \(\text{Im}[\cdot]\) is the imaginary part, and \(\tilde G^{(0)}\) is the non-interacting Greens function that is obtained by setting \(U = U_b = 0\) within the auxiliary model.
+
+%TODO
+%By expanding in terms of the small parameter $\frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}}$, this expression for $\Sigma_{H-H}(\vec k,\omega)$ can be recast in the following form:
+%\begin{equation}\begin{aligned}
+%	\Sigma_{H-H}(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~\label{selfenergy2}
+%\end{aligned}\end{equation}
+%where $\Sigma_\text{loc}$ and $\Sigma_\text{near-n}$ correspond to the local and nearest-neighbour self-energies defined on the real-space lattice 
+%\begin{eqnarray}
+%\Sigma_\text{loc}(\omega) &=& \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^{(0)}} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}}~,\\ 
+%\tilde{\Sigma}(\vec k, \omega)&=&\xi_{\vec k}\Sigma_\text{near-n}~,~\Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}^2}~.
+%\end{eqnarray}
+%We note that the form of $\Sigma(\vec k, \omega)$ obtained by us is similar to the form proposed on phenomenological grounds in the generalised DMFT + $\Sigma$ approach~\cite{sadovskii2012}.
+
+\section{Two-particle static correlators}
+Properties of the ground state can be probed using static correlation functions that are expectation values of two-particle excitation operators.
+We will consider spin and charge correlations, in real and momentum space.
+
+We first consider spin-spin correlations in real space, defined as
+\begin{equation}\begin{aligned}
+	\tilde{S}_\text{flip}({\bf r}) = \frac{1}{2}\braket{S^+\left({\bf r}_c + {\bf r}\right)S^-\left({\bf r}_c\right) + \text{h.c.}}~,
+\end{aligned}\end{equation}
+where \(S^-(\nu) = c^\dagger(\nu,\downarrow)c(\nu, \uparrow)\) and \(S^+ = \left( S^- \right)^\dagger \) are the spin-flip operators, and the expectation value is in the ground state \(\ket{\Psi_\text{gs}}\).
+We replace the full ground state with the ground state of the auxiliary model at \({\bf r}_c\):
+\begin{equation}\begin{aligned}
+	\tilde{S}_\text{flip}({\bf r}) = \frac{1}{2}\braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf d} + {\bf r}\right)S^-\left({\bf d}\right) + \text{h.c.} | \psi_\text{gs}({\bf r}_c)}~,
+\end{aligned}\end{equation}
+where we have interpereted the site at \({\bf r}_c\) as the impurity site \({\bf d}\) for the auxiliary model in question.
+The final expression therefore involves the spin-flip correlation function between the impurity site and a site in the bath, within a single auxiliary model.
+
+Charge correlations involve flips of the charge isospin states (instead of the spin states), and are defined as
+\begin{equation}\begin{aligned}
+	\tilde{C}_\text{flip}({\bf r}) = \frac{1}{2}\braket{C^+\left({\bf r}_c + {\bf r}\right)C^-\left({\bf r}_c\right) + \text{h.c.}}~,
+\end{aligned}\end{equation}
+where \(C^-(\nu) = c(\nu,\downarrow)c(\nu, \uparrow)\) and \(C^+ = \left( C^- \right)^\dagger \). Making identical substitutions here gives
+\begin{equation}\begin{aligned}
+	\tilde{C}_\text{flip}({\bf r}) = \frac{1}{2}\braket{\psi_\text{gs}({\bf r}_c) | C^+\left({\bf d} + {\bf r}\right)C^-\left({\bf d}\right) + \text{h.c.} | \psi_\text{gs}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+
+One can also look at \(k-\)space correlations, of the spin or charge kind:
+\begin{equation}\begin{aligned}
+	\tilde{S}_\text{flip}({\bf K}_1, {\bf K}_2) &= \frac{1}{2}\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right) + \text{h.c.}}~,\\
+	\tilde{C}_\text{flip}({\bf K}_1, {\bf K}_2) &= \frac{1}{2}\braket{C^+\left({\bf K}_1\right)C^-\left({\bf K}_2\right) + \text{h.c.}}~.
+\end{aligned}\end{equation}
+We again consider the spin-flip correlation first.
+In order to introduce the impurity site, we rewrite the expectation values sum of all coherent scattering processes involving the impurity site and the two \(k-\)states.
+Using eq.~\ref{eigenstateProposal}, we express the correlation in terms of a single auxiliary model:
+\begin{equation}\begin{aligned}
+	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} \\
+	&= \frac{1}{N}\sum_{{\bf r}_d}\braket{\psi_\text{gs}({\bf r}_d) | S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_d)}~,
+\end{aligned}\end{equation}
+where \({\bf r}_d\) is the location of the impurity site, and we average over the correlation values calculated over all possible auxiliary models.
+Assuming translation invariance, the static correlation values should be equal on every auxiliary model, allowing us to replace the average with the value at the reference origin \({\bf r}_c\):
+\begin{equation}\begin{aligned}\label{correlationAuxiliary}
+	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} = \braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+Using the definition \(S^+(\nu) = c^\dagger_{\nu \uparrow} c_{nu \downarrow}\), one can Fourier transform the fermionic operators in eq.~\ref{correlationAuxiliary},
+\begin{equation}\begin{aligned}
+	c_{{\bf k}\sigma} = \sum_{\bf r} e^{i {\bf k}\cdot{\bf r}} c_{{\bf r}\sigma},
+\end{aligned}\end{equation}
+and retain the only impurity site contribution \({\bf r}={\bf r}_c\) in order to introduce the dynamics of the impurity site. Carrying this out for one and two fermionic operators gives
+\begin{equation}\begin{aligned}\label{correlationAuxiliaryProcess}
+	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} \\
+	&= \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf r}_c \uparrow} c_{{\bf K}_1 \downarrow} S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}\\
+	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf K}_1 \uparrow} c_{{\bf r}_c \downarrow} S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}\\
+	&+ \braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf K}_1\right) c^\dagger_{{\bf r}_c \downarrow} c_{{\bf K}_2 \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
+	&+ \braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf K}_1\right) c^\dagger_{{\bf K}_2 \downarrow} c_{{\bf r}_c \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
+	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf r}_c \uparrow} c_{{\bf K}_1 \downarrow} c^\dagger_{{\bf r}_c \downarrow} c_{{\bf K}_2 \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
+	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf r}_c \uparrow} c_{{\bf K}_1 \downarrow} c^\dagger_{{\bf K}_2 \downarrow} c_{{\bf r}_c \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
+	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf K}_1 \uparrow} c_{{\bf r}_c \downarrow} c^\dagger_{{\bf r}_c \downarrow} c_{{\bf K}_2 \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
+	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf K}_1 \uparrow} c_{{\bf r}_c \downarrow} c^\dagger_{{\bf K}_2 \downarrow} c_{{\bf r}_c \uparrow} | \psi_\text{gs}({\bf r}_c)}~.
+\end{aligned}\end{equation}
+We haven't considered three-particle dynamics on the impurity site because those would involve only one momentum state and would hence be incoherent for the other momentum state; for the same reason, certain two-particle terms have also been ignored.
+Henceforth, we replace the index \({\bf r}_c\) with \(d\), indicating that it is the position of the impurity site.
+By introducing the off-site spin operator \(S^+_{\nu_1,\nu_2} = c^\dagger_{\nu_1 \uparrow} c_{\nu_2 \downarrow}\) that flips an effective spin across multiple orbitals, we can express eq.~\ref{correlationAuxiliaryProcess} in a more illuminating form:
+\begin{equation}\begin{aligned}
+	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} =\\
+	& \braket{(S^+_{d, {\bf K}_1} + S^+_{{\bf K}_1,d}) S^-({\bf K}_2) + S^+({\bf K}_1) (S^-_{d, {\bf K}_2} + S^-_{{\bf K}_2, d})} \\
+	&+ \braket{S^+_{d, {\bf K}_1} (S^-_{{\bf K}_2, d} + S^-_{d, {\bf K}_2}) + (S^+_{{\bf K}_1, d} + S^+_{{\bf K}_1, d}) S^-_{{\bf K}_2, d}}~.
+\end{aligned}\end{equation}
+This allows us to visualise the \(k-\)space correlation function through various scattering processes within the auxiliary model: the net correlation between \({\bf K}_1\) and \({\bf K}_2\) occur either through (i) simultaneous and opposite flips of the spin on one momentum state and the shared spin on the impurity site and another momentum state, or (ii) the simultaneous flips of spins shared between all three members.
+
+The charge correlations can be treated exactly the same way.
+We quote the final result here, in terms of the off-site charge operators \(C^+_{\nu_1, \nu_2} = c^\dagger_{\nu_1 \uparrow} c^\dagger_{\nu_2 \downarrow}\) :
+\begin{equation}\begin{aligned}
+	&\left<C^+({\bf K}_1) C^-({\bf K}_2)\right> = \\
+	& \braket{(C^+_{d, {\bf K}_1} + C^+_{{\bf K}_1,d}) C^-({\bf K}_2) + C^+({\bf K}_1) (C^-_{d, {\bf K}_2} + C^-_{{\bf K}_2, d})}\\
+	&+ \braket{C^+_{d, {\bf K}_1} (C^-_{{\bf K}_2, d} + C^-_{d, {\bf K}_2}) + (C^+_{{\bf K}_1, d} + C^+_{{\bf K}_1, d}) C^-_{{\bf K}_2, d}}~.
+\end{aligned}\end{equation}
+
+\section{Entanglement measures}
+
+Given the \(T=0\) density matrix \(\tilde\rho_\text{gs} = \ket{\Psi}_\text{gs}\bra{{\Psi}_\text{gs}}\) of the lattice model and a fermionic two-level subspace \(\nu\), the reduced density matrix for the {\it complement} subspace of \(\nu\) can be obtained by tracing over the configurations of that subspace
+\begin{equation}\begin{aligned}
+	&\overline\rho_{\nu} \\
+	&= \sum_{n_{\nu}=0,1}\braket{n_{\nu}|\tilde\rho_\text{gs}|n_{\nu}}\\
+	&= \rho_{\nu}^{(0,0)} + \rho_{\nu}^{(1,1)}~,
+\end{aligned}\end{equation}
+where \(\ket{n_{\nu}}\) is a state in the Hilbert space of \(\nu\) with fixed occupancy that can be 0 or 1, such that \(c^\dagger_\nu\ket{0}=\ket{1}\) and \(c_\nu\ket{1}=\ket{0}\).
+The entanglement entropy of the subspace \(\nu\) is then obtained straightforwardly from the eigenvalues of \(\overline\rho_{\nu}\), also known as the entanglement spectrum for this subspace:
+\begin{equation}\begin{aligned}
+	\tilde S_\text{EE}(\nu) = -\text{Tr}\left[\overline\rho_{\nu}\ln \overline\rho_{\nu}\right]  ~.
+\end{aligned}\end{equation}
+
+In order to facilitate expressing this in terms of auxiliary model quantities, we rewrite the total density matrix in the following manner:
+\begin{equation}\begin{aligned}
+	\tilde\rho_\text{gs} = \sum_{n_\nu=0,1}\sum_{n_\nu^\prime=0,1}\ket{n_{\nu^\prime}}\bra{n_{\nu}}\otimes\rho_\nu^{(n_\nu, n_\nu^\prime)}~.
+\end{aligned}\end{equation}
+which then allows a convenient form for the reduced density matrix in a block-diagonal form:
+\begin{equation}\begin{aligned}
+	\overline\rho_{\nu} = c^\dagger_\nu \tilde\rho_\text{gs} c_\nu + n_\nu \tilde\rho_\text{gs} n_\nu = \begin{pmatrix} 0 & 0 \\ 0 & \rho_{\nu}^{(0,0)} + \rho_{\nu}^{(1,1)} \end{pmatrix} ~.
+\end{aligned}\end{equation}
+Even though the matrix on the right has an additional zero block that should technically not be present in \(\overline\rho_{\nu}\), it does not make any difference for our purposes since that block only contributes zero eigenvalues which do not alter the entanglement entropy.
+
+We first consider entanglement in real-space, setting the subspace \(\nu\) to \(\nu=({\bf r}_c,\sigma)\), where \({\bf r}_c\) is the previously chosen reference point on the lattice.
+The expression for the enlarged \(\overline\rho_{\nu}\) becomes
+\begin{equation}\begin{aligned}
+	\overline\rho_{{\bf r}_c,\sigma} = c^\dagger_{{\bf r}_c,\sigma} \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}} c_{{\bf r}_c,\sigma} + n_{{\bf r}_c,\sigma} \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}} n_{{\bf r}_c,\sigma}~.
+\end{aligned}\end{equation}
+As has been done before, we simplify \(\Psi_\text{gs}\) by retaining only the uniform part of the eigenstate at \({\bf r}_c\) (following eq.~\ref{eigenstateUniform}), leading to the expression
+\begin{equation}\begin{aligned}
+	\overline\rho_{{\bf r}_c,\sigma} = c^\dagger_{{\bf r}_c,\sigma} \rho_\text{gs}({\bf r}_c) c_{{\bf r}_c,\sigma} + n_{{\bf r}_c,\sigma} \rho_\text{gs}({\bf r}_c) n_{{\bf r}_c,\sigma}
+\end{aligned}\end{equation}
+where \(\rho_\text{gs}({\bf r}_c) = \ket{\psi_\text{gs}({\bf r}_c)}\bra{\psi_\text{gs}({\bf r}_c)}\) is the \(T=0\) density matrix for the auxiliary model at \({\bf r}_c\).
+This is simply the reduced density matrix of the impurity site for the auxiliary model at \({\bf r}_c\), leading to the following simple relation for the local entanglement entropy of the lattice model:
+\begin{equation}\begin{aligned}
+	\tilde S_\text{EE}({\bf r}_c;\sigma) = S_\text{EE}(d;\sigma)~,
+\end{aligned}\end{equation}
+where \(S_\text{EE}(d)\) is the entanglement entropy of the impurity site.
+
+We might also be interested in entanglement entropy of subsystems with multiple sites.
+The reduced density matrix for the composite subsystem of the sites \({\bf r}_c\) and \({\bf r}_c + {\bf r}\) is obtained by tracing out the site \({\bf r}_c + {\bf r}\) from \(\overline\rho_{{\bf r}_c,\sigma}\).
+That then gives
+\begin{equation}\begin{aligned}
+	\overline\rho_{({\bf r}_c, {\bf r}_c + {\bf r}),\sigma} = c^\dagger_{{\bf r}_c + {\bf r},\sigma} \overline\rho_{{\bf r}_c,\sigma} c_{{\bf r}_c + {\bf r},\sigma} + n_{{\bf r}_c + {\bf r},\sigma} \overline\rho_{{\bf r}_c,\sigma} n_{{\bf r}_c + {\bf r},\sigma}~,
+\end{aligned}\end{equation}
+leading to the expression
+\begin{equation}\begin{aligned}
+	\tilde S_\text{EE}\left({\bf r}_c, {\bf r}_c + {\bf r};\sigma\right) = S_\text{EE}(d, {\bf r};\sigma)~,
+\end{aligned}\end{equation}
+where \(S_\text{EE}(d, r)\) is the entanglement entropy of the impurity site and the conduction bath site at a distance \({\bf r}\) from it.
+
+We now come to the \(k-\)space entanglement entropy, defined by \(\nu = ({\bf K},\sigma)\) and the reduced density matrix
+\begin{equation}\begin{aligned}
+	\overline\rho_{{\bf K},\sigma} = c^\dagger_{{\bf K},\sigma} \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}} c_{{\bf K},\sigma} + n_{{\bf K},\sigma} \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}} n_{{\bf K},\sigma}~.
+\end{aligned}\end{equation}
+We again replace the states with the uniform part, while we expand the operators on one side of the density matrix in a Fourier series in order to extract an impurity site operator:
+\begin{equation}\begin{aligned}
+	\overline\rho_{{\bf K},\sigma} &= \frac{1}{2}\left[c^\dagger_{{\bf K},\sigma} \rho_\text{gs}({\bf r}_c) c_{{\bf r}_c,\sigma} + n_{{\bf K},\sigma} \rho_\text{gs}({\bf r}_c) n_{{\bf r}_c,\sigma} \right.\\
+	&+ \left. c^\dagger_{{\bf r}_c,\sigma} \rho_\text{gs}({\bf r}_c) c_{{\bf K},\sigma} + n_{{\bf r}_c,\sigma} \rho_\text{gs}({\bf r}_c) n_{{\bf K},\sigma}\right. ~.
+\end{aligned}\end{equation}
+The eigenvalues of this operator can be used to compute the entanglement entropy of the state \({\bf K}\sigma\). If we define an {\it off-site} entanglement entropy 
+\begin{equation}\begin{aligned}
+	S^\prime_{\text{EE}}(\nu_1,\nu_2) = -\text{Tr}\left[\rho_{\nu_1,\nu_2}\ln \rho_{\nu_1,\nu_2}\right]
+\end{aligned}\end{equation}
+with 
+\begin{equation}\begin{aligned}
+	\rho_{\nu_1,\nu_2} = (c^\dagger_{\nu_1} \tilde\rho_\text{gs} c_{\nu_2} + n_{\nu_1} \tilde\rho_\text{gs} n_{\nu_2}) + \text{h.c.}~,
+\end{aligned}\end{equation}
+we can frame the expression for the \(k-\)space entanglement entropy in terms of the auxiliary model off-site entanglement entropy:
+\begin{equation}\begin{aligned}
+	S_\text{EE}({\bf K};\sigma) = S^\prime_\text{EE}\left(d, {\bf K};\sigma\right) 
+\end{aligned}\end{equation}
+
+Using the same approach as that for the real space case, the reduced density matrix for two \(k-\)states is again obtained by tracing out the second \(k-\)state from this density matrix:
+\begin{equation}\begin{aligned}
+	\overline\rho_{({\bf K}_1, {\bf K}_2),\sigma} &= \frac{1}{2}\left[c^\dagger_{{\bf K}_2,\sigma} \overline\rho_{{\bf K}_1,\sigma} c_{{\bf r}_c,\sigma} + n_{{\bf K}_2,\sigma} \overline\rho_{{\bf K}_1,\sigma} n_{{\bf r}_c,\sigma} \right.\\
+	&+ \left. c^\dagger_{{\bf r}_c,\sigma} \overline\rho_{{\bf K}_1,\sigma} c_{{\bf K}_2,\sigma} + n_{{\bf r}_c,\sigma} \overline\rho_{{\bf K}_1,\sigma} n_{{\bf K}_2,\sigma}\right] ~.
+\end{aligned}\end{equation}
+This straightforwardly leads to the relation
+\begin{equation}\begin{aligned}
+	S_\text{EE}({\bf K}_1,{\bf K}_2;\sigma) = S^\prime_\text{EE}\left(d, {\bf K}_1;\sigma\right) + S^\prime_\text{EE}\left(d, {\bf K}_2;\sigma\right)
+\end{aligned}\end{equation}
+
+Other measures like mutual information can be obtained by using these elementary measures.
+
+\section{Momentum-space picture of the MIT}
+In order to understand the nature of the transition in momentum space, we employ the expression obtained in the previous sections and compute the spectral function, self-energy and correlation functions in the top right quadrant of the first Brillouin zone.
+We first show the \(k-\)space spectral functions near zero frequency, in Fig.~\ref{kspace_specfunc}.
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.23\textwidth]{tiledSF-1.pdf}
+	\includegraphics[width=0.23\textwidth]{tiledSF-2.pdf}
+	\caption{tiledSF.pdf}
+	\label{fig:tiledSF-pdf}
+\end{figure}
+% \begin{figure*}[htpb]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{charge-p-p_37_-2.0_-1.7297_-0.0_0.1.pdf}
+% \end{figure*}
+% \begin{figure*}[htpb]
+% 	\centering
+% 	\includegraphics[width=\textwidth]{vne-p-p_37_-2.0_-1.7297_-0.0_0.1.pdf}
+% \end{figure*}
+
+\clearpage
+
+\begin{widetext}
+
+\section{The Mott MIT: a local perspective}
+\subsection{Gapping of the local spectral function and vanishing of correlations}
+% At a critical value \(U_b = -J/4\) of the local correlation \(U_b\) on the bath zeroth site, the couplings \(J\) and \(V\) of the auxiliary model become irrelevant while \(U\) becomes remains non-zero, leading to a low-energy phase where the impurity is cut off from the conduction bath.
+This is the local moment phase, where low-energy excitations have been gapped out.
+% \begin{figure}[htpb]
+% 	\centering
+% 	\includegraphics[width=0.48\textwidth]{phase-map-MIT.pdf}
+% 	\includegraphics[width=0.48\textwidth]{spectral-function_dd.pdf}
+% 	\caption{{\it Left:} Phase diagram of the extended SIAM auxiliary model.
+As the parameter \(r\) is tuned through 0.25, the metallic blue phase changes into the insulating violet phase.
+{\it Right:} Local spectral function of the auxiliary model.
+It shows a hard gap for \(r/r_c > 1\).}
+% 	\label{spec_func_mit}
+% \end{figure}
+%
+% The impurity local spectral function \(\mathcal{A}_{dd}(\omega)\) and the impurity-bath real space off-diagonal spectral function \(\mathcal{A}_{dz}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
+We show the former in fig.~\ref{spec_func_mit}.
+The gap in the former shows the absence of any gapless excitations that can allow the impurity configuration to fluctuate, while the vanishing of the off-diagonal spectral function shows that this is because the entanglement between the impurity and the bath has been quenched.
+%
+% In Fig.~\ref{spin-charge-correlations}, we show the behaviour of the spin-flip and charge isospin-flip correlations between two neighbouring real space sites, as well as the mutual real space entanglement and mutual information.
+Both show a sharp fall on crossing the transition, demonstrating the destruction of the Kondo cloud and the stabilisation of the local moment on the impurity.
+Importantly, they charge correlations show a rise very close to the transition (can be seen as a single elevated blue point near \(r = 0.25\) in the left panel of Fig.~\ref{spin-charge-correlations}); this indicates that the transition is precipitated by the growth of pairing correlations.
+%
+% \begin{figure}[!htb]
+% \centering
+% 	\includegraphics[width=0.48\textwidth]{spin-charge-corr-full.pdf}
+% 	\includegraphics[width=0.48\textwidth]{impEE-mutinfo-d0.pdf}
+% 	\caption{{\it Left}: Spin-flip correlations(red) and charge-flip correlations(blue) in real space.
+The former increases as the system moves into the Kondo regime, and then vanishes at the transition.
+The latter decreases as the charge content is removed from the ground state in the Kondo regime, but shows a sudden increase at the transition.
+{\it Right}: Real space Entanglement and mutual information.
+Both vanish in the local moment phase.}
+% 	\label{spin-charge-correlations}
+% \end{figure}
+
+\subsection{Value of the critical paramter for the bulk model}
+Using the mappings between the auxiliary model parameters and the bulk parameters (eq.~\ref{couplingsMappings}), one can define a critical value \(r^{*}\) of the ratio \(r = U_{H-H}/J_{H-H}\) at the critical points \(-U_b/J=1/4\) \textit{for a given and fixed value of \(U\)}.
+We will now argue that this critical point describes a metal-insulator transition.
+For \(r < r^{*}\), the well-defined low-\(\omega\) central peak in the impurity spectral function, as well as the large mutual and information correlations, in the ground state, among the members of the Kondo cloud or between the impurity and the zeroth site show that the impurity and the bath are very strongly entangled.
+This means that both the local and the nearest-neighbour Greens functions have poles at low\(-\omega\) and support the propagation of electrons through gapless excitations.
+Since the spectral function is also very simply related to that of the auxiliary model, the former also shows the same zero-energy resonance.
+
+On the other side \(r > r^{*}\) of the critical point, we know that the impurity gets decoupled from the bath, leading to the transformation of poles into zeros in the Greens functions.
+This is demonstrated through the gapping of the impurity spectral function in fig.~\ref{spec_func_mit}, and it describes an insulating phase where the electrons get "jammed" in the local states.
+By the same argument as above, the bulk spectral function also sees a gap in this phase when the impurity spectral function is gapped.
+
+Finally, using relations \eqref{couplingsMappings} between the auxiliary model couplings and the bulk parameters, we can offer a functional form for the critical value of the parameter $r^{*} = U_{H-H}^{*}/J_{H-H}^{*}$.
+Using \(U_{H-H}^{*} = U^* + U_b\) and \(J_{H-H}^{*} = 2J^*\) (following \eqref{couplingsMappings}), we get
+\begin{equation}\begin{aligned}
+	r^{*} &=& \frac{1}{2}\left(\frac{U^{*}}{J^{*}} + \frac{U_b}{J^*}\right)
+\end{aligned}\end{equation}
+where $U^{*}$ and $J^{*}$ are the values of the on-site and Kondo couplings of the auxiliary model at the auxiliary model (i.e., the extended SIAM with a correlated bath) at the transition between the Kondo screened and the local moment phases.
+By using the auxiliary model criticality condition \(-4U_b = J^*\), the bulk criticality parameter \(r^*\) takes the form
+\begin{equation}\begin{aligned}
+	r^{*} &=& \frac{1}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{4}\right)
+\end{aligned}\end{equation}
+Parametrising the bath correlation coupling as $U_{b}=-\frac{U}{10}$, we obtain $U^{*}/J^{*}=5/2$, and $r^{*} = 9/8$ for the 2D square lattice Hubbard-Heisenberg model.
+The reduction in the value of \(r\) from \(2.5\) in the auxiliary model to \(~1.1\) in the bulk model can be attributed to (i) the reduction in the effective bulk repulsion \(U\) due to the competition coming from the attractive \(U_b\), and (ii) increased hybdridisation through \(J\) due to the presence of multiple auxiliary models that connect two lattice sites.
+
+\section{Momentum-space picture of the MIT}
+% In order to understand the nature of the transition in momentum space, we employ the expression obtained in the previous sections and compute the spectral function, self-energy and correlation functions in the top right quadrant of the first Brillouin zone.
+We first show the \(k-\)space spectral functions near zero frequency, in Fig.~\ref{kspace_specfunc}.
+% \begin{figure}[htpb]
+% 	\centering
+% 	\includegraphics[width=0.8\textwidth]{tiledSF.pdf}
+% 	\caption{tiledSF.pdf}
+% 	\label{fig:tiledSF-pdf}
+% \end{figure}
+%
+% \begin{figure}[!htb]
+% \centering
+% \includegraphics[width=\textwidth]{kspace-spectral-function-all.pdf}\hspace{\fill}
+% \caption{\(k-\)space dependence of single-particle spectral function, \(A_{\vec k}(\omega \sim 0)\), at four values of the tuning parameter \(r\).
+The \(\vec k\) values are taken from the top right quadrant of the first Brillouin zone.
+In the metallic phase (\(r < r_c\)), the spectral function shows a \(k-\)dependence, indicating the presence of gapless excitations.
+Close to the transition (and beyond it), the momentum dependence gets removed and there is no spectral weight left in the infrared regime.}
+% \label{kspace_specfunc}
+% \end{figure}
+%
+% In Fig.~\ref{kspace_selfenergy}, we plot the momentum dependence of the single-particle self-energy, similar to the spectral function.
+The self-energy is flat in \(k-\)space away from the transition, consistent with the fact that the correlations are small in that regime.
+Close to the transition, the correlations pick up, and lead to a momentum-dependence of the self-energy, renormalising the Fermi liquid in the process and ultimately destroying it.
+% \begin{figure}[!htb]
+% \centering
+% \includegraphics[width=\textwidth]{kspace-imagsigma-all.pdf}\hspace{\fill}
+% \caption{\(k-\)space dependence of imaginary part of the self-energy, \(\Sigma_{\vec k}(\omega \sim 0)\), at four values of the tuning parameter \(r\).
+In the metallic phase (\(r \ll r_c\)), the self-energy is quite small, indicating that the phase consists of an uncorrelated Fermi liquid.
+It increases close to the transition (and beyond it).}
+% \label{kspace_selfenergy}
+% \end{figure}
+%
+% In Figs.~\ref{spin_kspace},\ref{charge_kspace} and \ref{pair_kspace}, we show the momentum dependence of two-particle correlation functions.
+In every figure, each panel shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
+Moving from the left panel to the right is equivalent to moving upwards in the top right quadrant of the first Brillouin zone.
+In each panel, moving upwards amounts to tuning the system towards the transition.
+The spin-spin correlations (in Fig.~\ref{spin_kspace}) are large near the \(\vec k = \left( 0,0 \right) \) point, presumably because of the dominance of the Kondo cloud at long wavelengths.
+They vanish in the local moment phase (flat blue region near the top).
+The charge and pairing correlations (Figs.~\ref{charge_kspace} and \ref{pair_kspace}) disappear as the system moves into the Kondo regime, but reappear exactly at the transition.
+This is tied to the non-Fermi liquid theory at the QCP, as seen in the auxiliary model.
+% \begin{figure}[!htb]
+% \centering
+% \includegraphics[width=\textwidth]{spin_rspace_all.pdf}
+% \caption{Momentum dependence of spin-spin correlation \(\left<\vec{S}_{-\vec k}\cdot\vec{S}_{\vec k} \right>\).
+Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
+Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone.
+In each figure, moving upwards amounts to tuning the system towards the transition.
+The flat blue region at the top is the local moment phase, void of any non-local correlations.}
+% \label{spin_kspace}
+% \end{figure}
+%
+% \begin{figure}[!htb]
+% \centering
+% \includegraphics[width=\textwidth]{charge_rspace_all.pdf}
+% \caption{Momentum dependence of charge-charge correlation \(\left<\vec{C}_{-\vec k}\cdot\vec{C}_{\vec k} \right>\), where \(\vec C\) is the charge isospin associated with the doublet formed by the doublon and holon states.
+Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
+Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone.
+In each figure, moving upwards amounts to tuning the system towards the transition.
+The flat blue region at the top is the local moment phase, void of any non-local correlations.}
+% \label{charge_kspace}
+% \end{figure}
+%
+% \begin{figure}[!htb]
+% \includegraphics[width=\textwidth]{pair_rspace_all.pdf}
+% \caption{Momentum dependence of pairing correlation \(\left<c^\dagger_{-k\uparrow}c^\dagger_{-k\downarrow}c_{k\downarrow}c_{k\uparrow}\right>\).
+Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
+Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone.
+In each figure, moving upwards amounts to tuning the system towards the transition.
+The flat blue region at the top is the local moment phase, void of any non-local correlations.}
+% \label{pair_kspace}
+% \end{figure}
+%
+% \begin{figure}[!htb]
+% \includegraphics[width=\textwidth]{vne_kspace_all.pdf}
+% \caption{Momentum dependence of \(k-\)space von Neumann entanglement entropy \(S_\text{EE}(\vec k)\).
+The four frames (from the left) show the variation in entanglement of a \(k-\)space in the \(k_x-k_y\) plane as the transition parameter \(r\) is tuned through the metal-insulator transition.
+\(r/r_c=0.5\) represents a very weakly correlated metal, \(r/r_c=0.8,0.9\) represents a highly correlated metal in the Kondo phase of the auxiliary model, and \(r/r_c \sim 1\) represents the non-Fermi liquid metal formed at the transition.}
+% \label{entanglement_kspace}
+% \end{figure}
+%
+% \begin{figure}[!htb]
+% \includegraphics[width=\textwidth]{mutinfo_kspace_all.pdf}
+% \caption{Momentum dependence of \(k-\)space mutual information \(I_2(\vec k: -\vec k)\).
+The four frames (from the left) show the variation in entanglement between the \(\vec k\) and \(-\vec k\) states in the \(k_x-k_y\) plane as the transition parameter \(r\) is tuned through the metal-insulator transition.
+\(r/r_c=0.5\) represents a very weakly correlated metal, \(r/r_c=0.8,0.9\) represents a highly correlated metal in the Kondo phase of the auxiliary model, and \(r/r_c \sim 1\) represents the non-Fermi liquid metal formed at the transition.}
+% \label{mutinfo_kspace}
+% \end{figure}
+%
+% {\color{blue} In order to provide a second way of visualising these correlations, we have provided some videos that show their variation in the \(k_x-k_y\) plane as a function of \(r/r_c\).
+The videos for the spin-spin correlation and the pairing correlations are named ``ss\_rspace.gif" and ``pairing\_rspace.gif", respectively.
+Each frame of the video shows a colourmap of the correlation in the top right quadrant of the first Brillouin zone, at a {\it specific value of \(r\)}.
+The movie then shows the {\it evolution of this \(k-\)space colourmap} as \(r\) is tuned towards and into the transition.}
+
+\section{Emergence of effectively pseudogapped Anderson model at the MIT}
+%\begin{itemize}
+%\item 
+We begin by recalling that the RG equation (in the weak coupling limit) of the \(J-U_b\) model that emerges in the Kondo limit of the eSIAM is similar to that of the pseudogapped Anderson model~\cite{fritzvojta2004} that has a bath density of states of the form \(\rho\sim |\omega|^\alpha\).
+If we define the dimensionless Kondo coupling \(g = \rho J\) and the dimensionless bath coupling \(u = \rho U_b\), the RG equation for \(g\),
+\begin{equation}\begin{aligned}
+	\Delta g \simeq g^2 + 4gu~,
+\end{aligned}\end{equation}
+can be mapped to the corresponding RG equation for the pseudogapped Kondo model,
+\begin{equation}\begin{aligned}
+	\Delta g = g^2 - \alpha g~,
+\end{aligned}\end{equation}
+with the identification \(\alpha = -4u = -4\rho U_b\).
+Specifically, this corresponds to a Kondo model that is coupled to a conduction bath with a single-particle density of states that is vanishing (pseudogapped): $\rho\sim |\omega|^{\alpha}$~.
+\par
+Now, following the work by Si and Kotliar~\cite{kotliarsi_1993}, the impurity self-energy of the \(J-U_b\) model takes the form
+	\begin{equation}\begin{aligned}
+		\Sigma_{dd} \sim |\omega|^{\gamma_{dd}}~,
+	\end{aligned}\end{equation}
+	where the exponent \(\gamma_{dd}\) can be written in terms of the phase shifts (at the RG fixed point) \(\delta^*_\text{sp}\) and \(\delta^*_\text{ch}\) suffered by the conduction electrons due to the potentials \(J\) and \(U_b\) respectively in the Hamiltonian:
+	\begin{equation}\begin{aligned}
+		\gamma_{dd} = \frac{5}{4} - \left[ \frac{1}{\pi}\left( \delta^*_\text{sp} + \delta^*_\text{ch} \right) - \frac{1}{2}  \right]^2 - \left( \frac{\delta^*_\text{ch}}{\pi} \right)^2~.
+	\end{aligned}\end{equation}
+	The phase shifts are given by \(\delta^*_\text{sp}=\arctan\left( \pi g/2 \right) \) and \(\delta^*_\text{ch}=\arctan\left( \pi u/2 \right) \).
+In the small coupling limit, these can be approximated as \(\delta^*_\text{sp}=\pi g/2\) and \(\delta^*_\text{ch}=\pi u/2\).
+\par 
+We now focus on the quantum critical point \(g = -4u\) of our model.
+At this point, the phase shifts get related to each other: \(\delta^*_\text{sp} = -4\delta^*_\text{ch}\), so that the exponent of the self-energy takes the form
+	\begin{equation}\begin{aligned}
+		\gamma_{dd} \simeq 1 - \frac{3}{\pi}\delta^*_\text{ch} = 1 + \frac{3}{8}\alpha
+	\end{aligned}\end{equation}
+	where we have used the fact that for our model, the effective pseudogap parameter \(\alpha\) is set to \(-4u\). The local self-energy then vanishes as
+	\begin{equation}\begin{aligned}
+		\Sigma_{dd} \sim |\omega|^{\gamma_{dd}} = |\omega|^{1 + \frac{3}{8}\alpha}
+	\end{aligned}\end{equation}
+The power-law exponent $\gamma_{dd}=1 + \frac{3}{8}\alpha$ lies in the following range: $1\leq \gamma_{dd} \leq 2$.
+This can be compared with the expression \(\sim|\omega|^{2-3\alpha}\) of the impurity self-energy obtained in ref.~\cite{fritzvojta2004} where the power law exponent ranges between $1/2$ and $2$.
+In a similar manner, the self-energy \(\Sigma_{dz}\) for scattering processes that connect the impurity site and the bath zeroth site can also be obtained.
+The exponent \(\gamma_{dz}\) for this self-energy is given by \(\gamma_{dz} = 2 - 2\gamma_{dd}\), so that this non-local self-energy diverges as
+\begin{equation}\begin{aligned}\label{selfenergydivergence}
+	\Sigma_{dz} \sim |\omega|^{- \frac{3}{4}\alpha}~.
+\end{aligned}\end{equation}
+
+We will now relate the auxiliary model self-energies \(\Sigma_{dd}\) and \(\Sigma_{dz}\) with their bulk (or lattice) model counterparts using the lattice Dyson equation.
+We consider self-energy matrices \(\Sigma\) and \(\Sigma_\text{aux}\) constructed out of real-space self-energies:
+\begin{equation}\begin{aligned}
+	\Sigma(\omega) = \begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} ,\quad \Sigma_\text{aux}(\omega) = \begin{bmatrix} \Sigma_{dd}(\omega) && \Sigma_{dz}(\omega) \\ \Sigma_{dz}(\omega) && \Sigma_{dd}(\omega)\end{bmatrix}~,
+\end{aligned}\end{equation}
+where \(\Sigma_\text{loc}\) is the real-space local self-energy and \(\Sigma_\text{near-n}\) is the self-energy for nearest-neighbour scattering processes. Using Dyson's equation, we can write
+\begin{equation}\begin{aligned}
+	\begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} = \begin{bmatrix} G^{(0)}_\text{loc}(\omega) && G^{(0)}_\text{near-n}(\omega) \\ G^{(0)}_\text{near-n}(\omega) && G^{(0)}_\text{loc}(\omega)\end{bmatrix}^{-1} - \begin{bmatrix} G_\text{loc}(\omega) && G_\text{near-n}(\omega) \\ G_\text{near-n}(\omega) && G_\text{loc}(\omega)\end{bmatrix}^{-1}~,
+\end{aligned}\end{equation}
+and
+\begin{equation}\begin{aligned}
+	\begin{bmatrix} \Sigma_{dd}(\omega) && \Sigma_{dz}(\omega) \\ \Sigma_{dz}(\omega) && \Sigma_{dd}(\omega)\end{bmatrix} = \begin{bmatrix} \mathcal{G}^{(0)}_{dd}(\omega) && \mathcal{G}^{(0)}_{dz}(\omega) \\ \mathcal{G}^{(0)}_{dz}(\omega) && \mathcal{G}^{(0)}_{dd}(\omega)\end{bmatrix}^{-1} - \begin{bmatrix} \mathcal{G}_{dd}(\omega) && \mathcal{G}_{dz}(\omega) \\ \mathcal{G}_{dz}(\omega) && \mathcal{G}_{dd}(\omega)\end{bmatrix}^{-1}~,
+\end{aligned}\end{equation}
+where the superscript \((0)\) indicates that the corresponding quantity has to be calculated from the non-interacting model.
+We now evaluate the second inverse matrix in each of the two equations, and expression the lattice Greens functions in terms of the auxiliary mode Greens functions (using eqs.~\ref{greens_func_relation} and \ref{greens_func_relation_near}).
+We get
+\begin{equation}\begin{aligned}
+	\begin{bmatrix} \Sigma_{dd}(\omega) && \Sigma_{dz}(\omega) \\ \Sigma_{dz}(\omega) && \Sigma_{dd}(\omega)\end{bmatrix} &= 1/\mathcal{G}^{(0)} - \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2}\begin{bmatrix} \mathcal{G}_{dd} && -\mathcal{G}_{dz} \\ -\mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}~,\\
+	\begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} &= 1/G^{(0)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{Z}^2}\begin{bmatrix} \mathcal{G}_{dd} && -\frac{1}{\mathcal{Z}}\mathcal{G}_{dz} \\ -\frac{1}{\mathcal{Z}}\mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}~.
+\end{aligned}\end{equation}
+This allows us to write down expressions for the off-diagonal self-energies, in terms of Greens functions, without evaluating the non-singular contribution coming from the non-interacting matrix:
+\begin{equation}\begin{aligned}
+	\Sigma_{dz} = \left(1/\mathcal{G}^{(0)}\right)_{dz} + \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2} \mathcal{G}_{dz},\quad \Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{Z}^2} \mathcal{G}_{dz}
+\end{aligned}\end{equation}
+The divergence of \(\Sigma_{dz}\) shown in eq.~\ref{selfenergydivergence} as \(\omega \to 0\) has to arise from the second term in the expression for \(\Sigma_{dz}\) above as it contains the effects of inter-particle correlations.
+%, because the non-interacting Greens function has well-defined poles which kill the first term. 
+Importantly, we note that the second term in the expression for \(\Sigma_\text{near-n}\) is very similar to the diverging term in \(\Sigma_{dz}\), differing only through the presence of some finite (i.e., non-divergent) non-zero factors of \(\lambda_{\vec k_0}^2\) and \(\mathcal{Z}\).
+We therefore conclude that the non-local self-energy of the lattice model $\Sigma_\text{near-n}$ contains the same power-law divergence  as $\Sigma_{dz}$ upon taking the limit $\omega\to 0$:
+\begin{equation}\begin{aligned}
+	\Sigma_\text{near-n}\left( \omega \right) \sim \omega^{-3\alpha/4}~.
+\end{aligned}\end{equation}
+By a similar argument, the local self-energy is found to vanish as \(\omega \to 0\).
+We have seen above that we can approximate the \(k-\)space self-energy in terms of these two real-space self-energies (eq.\eqref{selfenergy1}):
+\begin{equation}\begin{aligned}
+	\Sigma(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~~\textrm{where}~\tilde{\Sigma}(\vec k, \omega)=\xi_{\vec k}\Sigma_\text{near-n}~,
+\end{aligned}\end{equation}
+and $\xi_{\vec{k}}$ is the electronic lattice dispersion (in units of the hopping amplitude $t$).
+It is clear from the expression that the divergent $\Sigma_\text{near-n}$ does not affect the single-particle self-energy $\Sigma(\vec k,\omega)$ at the Fermi surface, i.e., for $\xi_{\vec{k}}= 0$, but $\Sigma(\vec k,\omega)$ diverges everywhere else in the Brillouin zone.
+This corresponds to a gapless non-Fermi liquid metal present at the QCP, corresponding to a system with Landau quasiparticle poles precisely on the Fermi surface but which are destroyed everywhere else.
+
+Now, following the arguments laid out in Ref.\cite{sujan2023}, the single-particle spectral function $A(\omega,\vec{k})$ will vanish (i.e., be pseudogapped) for excitations away from a critical Fermi surface~(see Chapter 8 of Ref.\cite{carr2010})
+\begin{equation}
+A(\vec{k},\omega) \sim |\omega|^{\frac{3}{4}\alpha}~.
+\end{equation}	
+This corresponds to the vanishing of the residue of the Landau quasiparticle precisely at the metal-insulator transition, and the emergence of a gapless non-Fermi liquid ``local quantum critical" metal~\cite{Si2001}.
+Further, the fact that the single-particle self-energy $\Sigma(\vec k, \omega)$ vanishes precisely at the Fermi surface signals the fact that the Luttinger's count for states on the Fermi surface is preserved and identical to that in the Fermi liquid phase.
+
+\section{Topological nature of the transition}
+Since the impurity charge hybridising with the bath contributes to the total Luttinger volume of the system~\cite{martin1982fermi}, decoupling of the impurity from the conduction bath leads to a difference in the value of the Luttinger volume between the local moment (LM) and the strong-coupling (SC) fixed points.
+If we define \(\mathcal{N}_L\) as the Luttinger volume with the spin-degeneracy accounted for, we can write
+\begin{equation}\begin{aligned}
+	\label{lutt_change}
+	\mathcal{N}_L^\text{lm} - \mathcal{N}_L^\text{sc} = 1
+\end{aligned}\end{equation}
+where \(\mathcal{N}_L^\text{lm},\mathcal{N}_L^\text{sc}\) are the Luttinger volumes at the local moment and strong-coupling fixed points respectively.
+This equation expresses the fact that the Luttinger volume of the bath increases by \(1\) when the system is tuned from LM to SC, and this happens because the single-particle impurity excitation in the lower-Hubbard at the atomic limit gets transferred to the bath Greens function in the process.
+The quantity which tracks this transfer is therefore \(\mathcal{N}_\text{imp}\), the number of poles minus the number of zeros in the impurity Greens function at and below the Fermi surface:
+\begin{equation}\begin{aligned}
+	\label{imp_count_def}
+	\mathcal{N}_\text{imp} = \begin{cases}
+		1 & \text{ at LM}\\
+		0 & \text{ at SC}
+	\end{cases}\implies \Delta \mathcal{N}_\text{imp} = 1
+\end{aligned}\end{equation}
+The Luttinger volume \(\mathcal{N}_L\) is related to this impurity count by the equation
+\begin{equation}\begin{aligned}
+	\mathcal{N}_L = \mathcal{N} - \mathcal{N}_\text{imp}
+\end{aligned}\end{equation}
+where \(\mathcal{N}\) is the total number of electrons in the system, accounting for the spin degeneracy.
+If we keep this total number fixed (isolated system), the changes in the impurity count and Luttinger volume become constrained:
+\begin{equation}\begin{aligned}
+	\Delta \mathcal{N}_L = - \Delta \mathcal{N}_\text{imp}~.
+\end{aligned}\end{equation}
+Eq.~\ref{imp_count_def} then readily implies eq.~\ref{lutt_change}.
+
+In order to connect this impurity topological change with the bulk model, we write the total number of particles in the bulk system in the following manner:
+\begin{equation}\begin{aligned}
+	\mathcal{N} = \mathcal{N}_\text{loc} + \mathcal{N}_\text{deloc}
+\end{aligned}\end{equation}
+\(\mathcal{N}_\text{loc}\) is the number of real poles minus the number of zeros of the local Greens function.
+\(\mathcal{N}_\text{deloc}\) is the number of real poles minus the number of zeros of the \(k-\)space Greens functions.
+The former (latter) contributes only in the insulating (metallic) phase, because in the metallic (insulating) phase, the local (\(k-\)space) Greens function develop imaginary self-energy and the real poles in these Greens functions get replaced by imaginary poles.
+Together, these two terms accurately count the total number of particles in both these phases.
+These two terms are defined as
+\begin{equation}\begin{aligned}
+	\mathcal{N}_\text{loc} = \sum_i \mathcal{N}_i = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_i(z)\right], ~ ~ ~\mathcal{N}_\text{deloc} = \sum_k \mathcal{N}_k = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_k(z)\right] = \mathcal{N}_L
+\end{aligned}\end{equation}
+\(G_i(z)\) is the local Greens function at site \(i\) of the bulk model, and \(G_k(z)\) is the \(k-\)space Greens function in the bulk model.
+\(N_\text{deloc}\) is just the Luttinger volume \(\mathcal{N}_L\) of the bulk system.
+With this, the total number of particles in the bulk can be expressed as
+\begin{equation}\begin{aligned}
+	\label{bulk_total}
+	\mathcal{N} = \sum_i \mathcal{N}_i + \mathcal{N}_\text{L}
+\end{aligned}\end{equation}
+From eq.~\ref{greens_func_relation}, we know that the bulk local Greens function is proportional to that of the auxiliary model, and that gives \(\sum_i \mathcal{N}_i = \mathcal{N}_\text{imp}\sum_i = \mathcal{N} \mathcal{N}_\text{imp}\).
+There we used the fact that for a half-filled system, the total number of sites is equal to the total number of particles in the system.
+Substituting this into eq.~\ref{bulk_total} and again using \(\Delta \mathcal{N} = 0\) gives
+\begin{equation}\begin{aligned}
+	\mathcal{N} = \mathcal{N} \mathcal{N}_\text{imp} + \mathcal{N}_\text{L} \implies \Delta \mathcal{N}_\text{L} = - \mathcal{N} \Delta \mathcal{N}_\text{imp}
+\end{aligned}\end{equation}
+We already know that \(\Delta \mathcal{N}_\text{imp}=1\) across the transition, so we get
+\begin{equation}\begin{aligned}
+	\mathcal{N}_L^\text{metal} - \mathcal{N}_L^\text{insulator} = \mathcal{N}\left(\mathcal{N}_\text{imp}^\text{sc} - \mathcal{N}_\text{imp}^\text{lm}\right) = \mathcal{N}
+\end{aligned}\end{equation}
+The metal-insulator transition is therefore characterised by a change in the topological quantity \(\mathcal{N}_L\).
+The topological nature arises from the fact that it can be expressed in terms of winding numbers related to the corresponding Greens functions.
+\(\mathcal{N}_\text{imp}\), which derives from the impurity Greens function \(G_d\), is related to the winding numbers of the curves \(\text{Det}[G_d^{-1}(\Gamma^<)]\) and \(\text{Det}[G_d^{-1}(\Gamma^0)]\).
+The winding number is simply the number of times this function encircles the origin when traced on the curves \(\Gamma^<\) and \(\Gamma^0\) that enclose all poles inside and on the Fermi surface respectively.
+An example of such a winding number is shown in fig.~\ref{imp_winding}.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.4\textwidth]{windingNumbers.pdf}
+	\caption{The green lines describe the winding number related to the impurity Greens function, while the blue lines do it for the bath.
+At the local moment fixed point \(V=0\), the impurity has a winding number of 1 because the curve encircles the origin once.
+At the strong-coupling fixed point, this winding number becomes zero, indicated by the fact that the curve does not encircle the origin even once.
+The reduction in the winding number on the part of the impurity is directly linked to the increase in the winding number of the bath - it encircles the origin once at the local moment fixed point but twice at strong-coupling.}
+	\label{imp_winding}
+\end{figure}
+
+\clearpage
+\section*{Appendices}
+\appendix
+\section{Effective action for the Hubbard-Heisenberg model and the eSIAM}
+In order to better understand the similarities and differences between the tiling approach outlined here and the approach adopted in dynamical mean-field approximations, we compute the effective action for the local impurity as well as the impurity-zeroth site system, in both the auxiliary and bulk models.
+This will be done in the limit of infinite coordination number, in order to create a tractable effective theory.
+
+\subsection{Local theory for the Hubbard-Heisenberg model}
+We will first work with the Hubbard-Heisenberg model.
+Let us recall that within the eSIAM, most of the dynamics is governed by the physics of the impurity site and the bath site coupled to the impurity.
+Accordingly, we will first obtain an effective action within the Hubbard-Heisenberg model for the small system consisting of a local site and all its nearest-neighbours.
+
+We choose a certain local site that we call \(0\), whose nearest-neighbours will be denoted as \(\left\{ {\bar 0} \right\} \).
+The action for the full Hubbard-Heisenberg model can be formally separated into three parts:
+\begin{equation}\begin{aligned}
+S_\text{H-H} = S_{0,{\bar 0}} + S^{(0,{\bar 0})} + S_\text{int}~,
+\end{aligned}\end{equation}
+where \(S_{0,{\bar 0}}\) represents the part of the action that involves only the sites \(0\) and $\left\{ {\bar 0} \right\}$, \(S^{(0,{\bar 0})}\) represents the part that has all the sites apart from \(0\) and \(\left\{ {\bar 0} \right\} \), while \(S_\text{int}\) contains all terms that connect these two parts.
+These three parts have the forms
+\begin{equation}\begin{aligned}
+S_{0,{\bar 0}} = \sum_{i=0,{\bar 0}}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau)  - t\sum_{{\bar 0},\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{0\sigma}(\tau)c_{{\bar 0}\sigma}(\tau) + \text{h.c.}\right] \\
+- \frac{U}{2}\sum_{i=0,{\bar 0}}\int_0^\beta\mathrm{d\tau}~\left(n_{i \uparrow}(\tau) - n_{i \downarrow}(\tau)\right)^2 + J\sum_{{\bar 0}}\int_0^\beta\mathrm{d\tau} \vec{S}_0(\tau)\cdot\vec{S}_{{\bar 0}}(\tau)~,
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+S^{(0,{\bar 0})} = \sum_{j\neq(0,{\bar 0})}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{j\sigma}(\tau)\partial_\tau c_{j\sigma}(\tau)  - t\sum_{\left<j,l\right>\neq (0,{\bar 0}),\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{j\sigma}(\tau)c_{l\sigma}(\tau) + \text{h.c.}\right] \\
+- \frac{U}{2}\sum_{j\neq(0,{\bar 0})}\int_0^\beta\mathrm{d\tau}~\left(n_{j\uparrow}(\tau) - n_{j\downarrow}(\tau)\right)^2 + J\sum_{\left<j,l\right>\neq(0,{\bar 0})}\int_0^\beta\mathrm{d\tau} \vec{S}_l(\tau)\cdot\vec{S}_j(\tau)~,
+\end{aligned}\end{equation}
+\begin{equation}\begin{aligned}
+S_\text{int} = -t\sum_{i \in {\bar 0}}\sum_{j \in \text{NN of}~i}\sum_\sigma \int_0^\beta\mathrm{d\tau}~\left(c^\dagger_{i\sigma}(\tau) c_{j\sigma}(\tau) + \text{h.c.}\right) + J\sum_{i \in {\bar 0}}\sum_{j \in \text{NN of}~i}\int_0^\beta\mathrm{d\tau}\vec{S}_i(\tau)\cdot\vec{S}_j(\tau) = S_\text{int}^\text{hop} + S_\text{int}^\text{spin}
+\end{aligned}\end{equation}
+
+In order to obtain an effective theory \(S^{0,{\bar 0}}_\text{eff}\) purely for the local system \((0,{\bar 0})\), we need to trace over all the other degrees of freedom.
+This partial trace will be carried out over the states of the so-called ``cavity" system \(S^{(0,{\bar 0})}\).
+The effective action can be constructed by tracing over scattering processes of all orders that leave the final action diagonal in the system \((0,{\bar 0})\).
+The formal expression can be written as
+\begin{equation}\begin{aligned}
+	S^{0,{\bar 0}}_\text{eff} = S_{0,{\bar 0}} + \sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} + \sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})}
+\end{aligned}\end{equation}
+where, as mentioned before, the average is carried out in the cavity system \(S^{(0,{\bar 0})}\). Each hopping term in the expansion is of the form
+\begin{equation}\begin{aligned}
+	\left(S_\text{int}^\text{hop}\right)^{2n} =& t^{2n}\sum_\sigma\sum_{(i_1, i_1^\prime)\ldots, (i_n, i_n^\prime)} ~\sum_{(j_1, j_1^\prime)\ldots, (j_n, j_n^\prime)} \int_0^\beta d\tau_{1}\ldots d\tau_{n}d\tau_{1}^\prime\ldots d\tau_{j_n}^\prime\\
+			   &c^\dagger_{i_1\sigma}(\tau_{i_1})c^\dagger_{i_2\sigma}(\tau_{2})\ldots c^\dagger_{i_n\sigma}(\tau_{n}) c_{i_1^\prime\sigma}(\tau_{1}^\prime)c_{i_2^\prime\sigma}(\tau_{2}^\prime)\ldots c_{i_n^\prime\sigma}(\tau_{n}^\prime)\left<c_{j_1\sigma}(\tau_{1})c_{j_2\sigma}(\tau_{2})\ldots c_{j_n\sigma} ~ c^\dagger_{j_1^\prime\sigma}(\tau_{1}^\prime)\ldots c^\dagger_{j_n^\prime\sigma}(\tau_{n}^\prime) \right>_{(0,{\bar 0})}\\
+	=& t^{2n}\sum_\sigma\sum_{(i_1, i_1^\prime)\ldots, (i_n, i_n^\prime)} ~\sum_{(j_1, j_1^\prime)\ldots, (j_n, j_n^\prime)} \int_0^\beta d\tau_{1}\ldots d\tau_{j_n}^\prime c^\dagger_{i_1\sigma}(\tau_{i_1})\ldots c^\dagger_{i_n\sigma}(\tau_{n})~c_{i_1^\prime\sigma}(\tau_{1}^\prime)\ldots c_{i_n^\prime\sigma}(\tau_{n}^\prime)\\
+	 &G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right)~,
+\end{aligned}\end{equation}
+where the indices \(i_1\) through \(i_n\) and their primed counterparts run through \(\bar 0\), while \(j_l\) (\(\in \left\{j_1,\ldots,j_n^\prime\right\}\)) runs through the nearest-neighbours of the corresponding \(i_l\) index.
+The \(n-\)particle Greens function \(G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right)\) for the cavity system is defined in the usual fashion
+\begin{equation}\begin{aligned}
+	G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right) = \left<c_{j_1\sigma}(\tau_{1})c_{j_2\sigma}(\tau_{2})\ldots c_{j_n\sigma} ~ c^\dagger_{j_1^\prime\sigma}(\tau_{1}^\prime)\ldots c^\dagger_{j_n^\prime\sigma}(\tau_{n}^\prime) \right>_{(0,{\bar 0})}
+\end{aligned}\end{equation}
+In the limit of infinite coordination number, only the \(n=1\) term survives:
+\begin{equation}\begin{aligned}
+	\lim_{\mathcal{Z}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} = t^2\sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)\sum_{j,j^\prime}G_1^{(0,\bar 0)}\left(j\tau; j^\prime\tau^\prime\right) \\
+	= \sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)~,
+\end{aligned}\end{equation}
+where we have defined the bath hybridisation function \(\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)\) as
+\begin{equation}\begin{aligned}
+	\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime) = t^2\sum_{j \in \text{NN of}~i}\sum_{j^\prime \in \text{NN of}~i^\prime}G_1^{(0,\bar 0)}\left(j\sigma\tau; j^\prime\sigma\tau^\prime\right)~.
+\end{aligned}\end{equation}
+
+Under similar approximations, the spin term in the action reduces to
+\begin{equation}\begin{aligned}
+	\lim_{\mathcal{Z}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})} = \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\chi(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)~,
+\end{aligned}\end{equation}
+where the susceptibility \(\chi_{ii^\prime}(\tau - \tau^\prime)\) is defined as 
+\begin{equation}\begin{aligned}
+	\chi_{ii^\prime}(\tau - \tau^\prime) = J^2\sum_{j \in \text{NN of}~i}\sum_{j^\prime \in \text{NN of}~i^\prime}\vec{S}_{j}(\tau)\cdot\vec{S}_{j^\prime}(\tau^\prime)~.
+\end{aligned}\end{equation}
+The effective action for the \(0,\bar 0\) system, in the limit of large coordination number, simplifies to
+\begin{equation}\begin{aligned}
+	S^{0,{\bar 0}}_\text{eff} =& \sum_{i=0,{\bar 0}}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau)  - t\sum_{{\bar 0},\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{0\sigma}(\tau)c_{{\bar 0}\sigma}(\tau) + \text{h.c.}\right] - \frac{U}{2}\sum_{i=0,{\bar 0}}\int_0^\beta\mathrm{d\tau}~\left(n_{i \uparrow}(\tau) - n_{i \downarrow}(\tau)\right)^2 \\
+				   &+ J\sum_{{\bar 0}}\int_0^\beta\mathrm{d\tau} \vec{S}_0(\tau)\cdot\vec{S}_{{\bar 0}}(\tau) + \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{ii^\prime}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
+\end{aligned}\end{equation}
+
+One can also write down an effective action purely for the local site \(0\).
+The sites \(\bar 0\) will now be a part of the environment action \(S^{(0)}\) instead of the system action, but since the system is thermodynamically large, the cavity action can be assumed to remain the same, such the expectation values are calculated in the same system.
+As a result, the hybridisation and susceptibility functions remain unchanged.
+\(S_\text{int}\) is now made of terms that connect \(0\) and \(\bar 0\), so the transformation from \(S^{(0,\bar 0)}\) can be made by replacing the set \(\left\{ j \right\} \) with the set \(\bar 0\), and the set \(\bar 0\) itself will be replaced by the local site \(0\).
+We quote the final form of the local effective action:
+\begin{equation}\begin{aligned}
+	S^{0}_\text{eff} =& \sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{0\sigma}(\tau)\partial_\tau c_{0\sigma}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{0\uparrow}(\tau) - n_{0\downarrow}(\tau)\right)^2 \\
+			  &+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\Delta_{00,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{00}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
+\end{aligned}\end{equation}
+
+\subsection{Local theory for the extended SIAM}
+The Hamiltonian for the extended SIAM model is shown in eq.~\ref{siam_attr}.
+We will denote the impurity with the label \(d\) and the bath sites with the label \(c\).
+Among the bath sites, we will represent the site coupled to the impurity with \(z\).
+The full action has the form
+\begin{equation}\begin{aligned}
+	S_\text{ES} = \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - t\sum_{\left<i,j \right> \in c,\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{i\sigma}(\tau)c_{j\sigma}(\tau) + \text{h.c.}\right] - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right]\\
++ J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{U_b}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 ~,
+\end{aligned}\end{equation}
+As in the Hubbard-Heisenberg model, we first obtain an effective action for the pair of sites \((d,z)\).
+As in the previous calculation, this will again generate a hybridisation function \(\Delta_{zz,\sigma}\) for the bath site nearest to the zeroth site.
+No susceptibility will be generated however, because there is no spin-exchange coupling within the bath.
+The net result is
+\begin{equation}\begin{aligned}
+	S^{d,z}_\text{eff} =& \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right] + J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) \\
+	&- \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{U_b}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 \\
+	&+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\sum_{\sigma}\Delta_{zz,\sigma}(\tau - \tau^\prime)c^\dagger_{z\sigma}(\tau)c_{z\sigma}(\tau^\prime)
+\end{aligned}\end{equation}
+This hybridisation \(\Delta_{zz,\sigma}\) is calculated in the cavity model of the eSIAM, obtained by removing the impurity and the zeroth site from the full model; it is a completely non-interacting system.
+
+One can go one step further and also remove the zeroth site in order to obtain a theory for the impurity site.
+With this choice, the cavity model now also includes the zeroth site, and hence contains the correlation term associated with \(U_b\).
+The one-particle connection \(V\) will lead to a modified hybridisation \(\mathcal{F}\) for this effective theory; the Kondo terms will generate a susceptibility.
+The resultant action is
+\begin{equation}\begin{aligned}
+	S^{d}_\text{eff} =& \sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{d\sigma}(\tau)\partial_\tau c_{d\sigma}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 \\
+			  &+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\mathcal{F}_{\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{d}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
+\end{aligned}\end{equation}
+where \(\mathcal{F}\) is defined in terms of the local correlator of the zeroth site
+\begin{equation}\begin{aligned}
+	\mathcal{F}_\sigma(\tau - \tau^\prime) = V^2 G_1^{(d)}\left(z\sigma\tau; z\sigma\tau^\prime\right) = V^2 \left<c_{z\sigma}(\tau)c^\dagger_{z\sigma}(\tau^\prime)\right>_{(d)}
+\end{aligned}\end{equation}
+with the average computed in the interacting cavity model that has the impurity site removed.
+The interaction arises from the \(U_b-\)term.
+The susceptibility is also calculated in this interacting cavity model, and follows the same definition as in the bulk model:
+\begin{equation}\begin{aligned}
+	\chi_{d}(\tau - \tau^\prime) = J^2\vec{S}_{z}(\tau)\cdot\vec{S}_{z}(\tau^\prime)~.
+\end{aligned}\end{equation}
+\section{Zero temperature Greens function in frequency domain}
+
+\label{appx-spectral-func}
+The impurity retarded Green's function (assuming the Hamiltonian to be time-independent, which it is) is defined as
+\begin{equation}\begin{aligned}
+	G_{dd}^\sigma(t) = -i\theta(t) \left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right>
+\end{aligned}\end{equation}
+where the average \(\left< \right>\) is over a canonical ensemble at temperature \(T\), and \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in.
+The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term.
+What follows is a standard calculation where we write the Green's function in the Lehmann-Kallen representation.
+The ensemble average for an arbitrary operator \(\hat M\) can be written in terms of the exact eigenstates of the fixed point Hamiltonian:
+\begin{equation}\begin{aligned}
+	H^* \ket{n} &= E_n^* \ket{n}, ~ ~ ~\left<\hat M \right> &\equiv \frac{1}{Z}\sum_n \bra{n} \hat M \ket{n} e^{-\beta E_n^*}
+\end{aligned}\end{equation}
+where \(Z = \sum_n e^{-\beta E_n^*}\) is the fixed point partition function and \(\left\{ \ket{n} \right\} \) is the set of eigenfunctions of the fixed point Hamiltonian. We can therefore write
+\begin{equation}\begin{aligned}
+	&\left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right> \\
+	&= \frac{1}{Z}\sum_{m}e^{-\beta E_m}\bra{m}\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\} \ket{m}\\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( \mathcal{O}_{\sigma}(t)\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma}(t)\right) \ket{m} && \left[\sum_n \ket{n}\bra{n} = 1\right]  \\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\right) \ket{m}\\
+	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\left( e^{i\left( E_m - E_n \right)  t}\bra{m}\mathcal{O}_{\sigma}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} \ket{m} + e^{i\left( E_n - E_m \right)  t}\bra{m}\mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma} \ket{m}\right)\\
+	&= \frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
+\end{aligned}\end{equation}
+The time-domain impurity Green's function can thus be written as (this is the so-called Lehmann-Kallen representation)
+\begin{equation}\begin{aligned}
+	G_{dd}^\sigma = -i\theta(t)\frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
+\end{aligned}\end{equation}
+We are interested in the frequency domain form.
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega) &= \int_{-\infty}^\infty dt e^{i \omega t}G_{d d}^\sigma(t) \\
+			       &= \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t}
+\end{aligned}\end{equation}
+To evaluate the time-integral, we will use the integral representation of the Heaviside function:
+\begin{equation}\begin{aligned}
+	\theta(t) = \frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty \frac{1}{x- i\eta}e^{ixt}dx
+\end{aligned}\end{equation}
+With this definition, the integral in \(G_{dd}^\sigma(\omega)\) becomes
+\begin{equation}\begin{aligned}
+	\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t} &= \left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta}\int_{-\infty}^\infty dt e^{i\left( \omega + E_m - E_n + x\right)t} \\
+									     &=\left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta} 2\pi \delta\left( \omega + E_m - E_n + x\right) \\
+									     &=\left(-i\right)\frac{1}{i}\lim_{\eta \to 0^+} \frac{-1}{\omega + E_m - E_n- i\eta} \\
+									     &=\frac{1}{\omega + E_m - E_n} \\
+\end{aligned}\end{equation}
+The frequency-domain Green's function is thus
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
+\end{aligned}\end{equation}
+The zero temperature Green's function is obtained by taking the limit of \(\beta \to \infty\).
+In both the partition function as well as inside the summation, the only term that will survive is the exponential of the ground state energy \(E_0\).
+\begin{equation*}\begin{aligned}
+	Z \equiv \sum_m e^{-\beta E_m} \implies \lim_{\beta \to \infty}Z = d_0 e^{-\beta E_0}, && E_0 \equiv \text{min}\left\{ E_n \right\} 
+\end{aligned}\end{equation*}
+where \(d_0\) is the degeneracy of the ground state. The Greens function then simplifies to
+\begin{equation}\begin{aligned}
+	\label{Gf_lk}
+	G_{d d}^\sigma(\omega, \beta \to \infty) &= \frac{1}{d_0e^{-\beta E_0}}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left[e^{-\beta E_m}\delta_{E_m, E_0} + e^{-\beta E_n}\delta_{E_n, E_0}\right]\frac{1}{\omega + E_m - E_n}\\
+						 &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n}\right]\\
+\end{aligned}\end{equation}
+The label 0 sums over all states \(\ket{0}\) with energy \(E_0\).
+The spectral function is the imaginary part of this Green's function.
+To extract the imaginary part, we insert an infinitesimal imaginary part in the denominator:
+\begin{equation}\begin{aligned}
+	G_{d d}^\sigma(\omega, \eta) = \frac{1}{d_0}\lim_{\eta \to 0^-}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n + i\eta} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n + i\eta}\right]\\
+\end{aligned}\end{equation}
+The spectral function at zero temperature can then be written as
+\begin{equation}\begin{aligned}
+	\mathcal{A(\omega)} &= -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] \\
+			    &= \frac{1}{d_0}\frac{1}{\pi}\text{ Im }\left[\lim_{\eta \to 0^-}\sum_{n,0}\left(\frac{-i\eta ||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2}{\left(\omega + E_0 - E_n\right)^2 + \eta^2} + \frac{-i\eta ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2}{\left(\omega - E_0 + E_n\right)^2 + \eta^2}\right)\right]\\
+			    &= \frac{1}{d_0}\frac{1}{\pi}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\pi\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\pi\delta\left(\omega - E_0 + E_n\right)\right]\\
+			    &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]\\
+\end{aligned}\end{equation}
+
+\section{Properties of the Bloch states}
+
+\subsection{Translation invariance}
+It is easy to verify that \(\Psi_{\vec k}\left(\left\{ {\bf r}_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \({\bf r}\):
+\begin{equation}\begin{aligned}
+	\Psi_{\vec k}\left(\left\{{\bf r}_k + {\bf r}\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i,{\bf a}} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left({\bf r}_i - {\bf r}, {\bf a}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_j, {\bf a}} e^{i \vec{k}\cdot\left(\vec{R}_j + {\bf r}\right)} \psi_\text{aux}\left({\bf r}_j, {\bf a}\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ {\bf r}_k \right\} \right)
+\end{aligned}\end{equation}
+In the last equation, we transformed \({\bf r}_i \to {\bf r}_j = {\bf r}_i - {\bf r}\).
+Note that the argument \({\bf a}\) does not change under a translation of the system, because that vector always represents the difference between the impurity lattice position and its nearest neighbours, irrespective of the absolute position of the impurity.
+
+The wavefunction can be even brought into the familiar Bloch function form:
+\begin{equation}\begin{aligned}
+	\Psi^n_{\vec k}\left(\left\{{\bf r}_k\right\}\right) = \sum_{{\bf r}_i, {\bf a}} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} \mathcal{Z} N} \psi_\text{aux}\left(\left\{ {\bf r}_d - {\bf r}_i, {\bf r_0} - {\bf r}_i - {\bf a} \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i, {\bf a}} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k{\bf r}_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ {\bf r}_d - {\bf r}_i, {\bf r_0} - {\bf r}_i - {\bf a} \right\} \right) \\
+	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{{\bf r}_k\right\}\right)
+\end{aligned}\end{equation}
+where \({\bf r}_\text{COM} = \frac{1}{N}\sum_k {\bf r}_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{{\bf r}_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k{\bf r}_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{{\bf r}_k - {\bf r}_i\right\}\right)\) is the translation symmetric function.
+This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
+
+\subsection{Orthonormality}
+It is straightforward to show that these states form an orthonormal basis. We start by writing down the inner product of two distinct such states:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r}_j, {\bf a}^\prime \right) | \psi_\text{aux}\left( {\bf r}_i, {\bf a} \right)} \\
+	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) T^\dagger\left( {\bf r_0} - {\bf r}_j \right) T\left( {\bf r_0} - {\bf r}_i \right) | \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
+\end{aligned}\end{equation}
+At this point, we insert a complete basis of momentum eigenkets \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators:
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) T\left( {\bf r}_j - {\bf r}_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
+						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) e^{i \vec q \cdot \left( {\bf r}_j - {\bf r}_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)} \\
+						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2} \delta_{\vec k, \vec k^\prime}\sum_{{\bf a}, {\bf a}^\prime}\braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
+\end{aligned}\end{equation}
+At the last step, we used the summation form of the Kronecker delta function: \(\sum_{{\bf r}_i}e^{i {\bf r}_i \left( \vec k - \vec q \right) }\sum_{{\bf r}_j}e^{i {\bf r}_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\).
+The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \({\bf a}, {\bf a}^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\ket{\vec k}}\):
+\begin{equation}\begin{aligned}
+	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2 } \delta_{\vec k, \vec k^\prime}\sum_{{\bf a},{\bf a}^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
+\end{aligned}\end{equation}
+This concludes the proof of orthonormality.
+
+\subsection{Eigenstates}
+To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
+\begin{equation}\begin{aligned}
+	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r}_j, {\bf a}^\prime\right)} H_\text{aux}\left({\bf r}_k\right) \ket{\psi_\text{aux}\left({\bf r}_i, {\bf a}\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)} T^\dagger_{{\bf r_0} - {\bf r}_j} T_{{\bf r_0} - {\bf r}_k} H_\text{aux}\left({\bf r_0}\right) T^\dagger_{{\bf r_0} - {\bf r}_k} T_{{\bf r_0} - {\bf r}_i} \ket{\psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)} T^\dagger_{{\bf r}_k - {\bf r}_j} H_\text{aux}\left({\bf r_0}\right) T_{{\bf r}_k - {\bf r}_i} \ket{\psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}
+\end{aligned}\end{equation}
+To resolve the translation operators, we will now insert the momentum eigenstates \(\ket{\vec k}\) of the full model: \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) in between the operators.
+\begin{equation}\begin{aligned}
+	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, \atop{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{{\bf r}_k - {\bf r}_j} H_\text{aux}\left({\bf r_0}\right) T_{{\bf r}_k - {\bf r}_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+								   &= \sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, \atop{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left({\bf r}_k - {\bf r}_j\right) } e^{i \vec q \cdot \left({\bf r}_k - {\bf r}_i\right)} \braket{\vec q^\prime | H_\text{aux}\left({\bf r_0}\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2}\sum_{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left({\bf r_0}\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2}\delta_{kk^\prime}\sum_{{\bf a}, {\bf a}^\prime} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
+								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k} \underbrace{\sum_{{\bf a}, {\bf a}^\prime} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
+	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k}
+\end{aligned}\end{equation}
+The momentum eigenket \(\ket{\vec k}\) can be expressed as a sum over position eigenkets at varying distances from \({\bf r_0}\).
+This form allows a systematic method of improving the energy eigenvalue estimate, because the interacting in the impurity model is extremely localised, so the overlap between two auxiliary models decreases rapidly with distance.
+The majority of the contribution will come from the state at \({\bf r_0}\), and improvements are then made by considering auxiliary models at further distances.
+
+\section{Greens function in the insulating phase: the Hubbard bands and mottness}
+In the insulating state, the cluster becomes a local moment and the bulk system reduces to the atomic limit \(H = -\frac{U}{2}\sum_i\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\).
+The Greens function in this limit is that of the atomic limit of the Hubbard model:
+\begin{equation}\begin{aligned}
+	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 + \left<\tau_{i }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i}\right>}{\omega + \frac{U}{2}}
+\end{aligned}\end{equation}
+where \(\tau_i = \sum_\sigma \hat n_{i,\sigma} - 1\).
+At half-filling \(\left<\tau_{i}\right>=0\), the low and high-energy poles have equal spectral weights.
+\textit{This is different from the situation in a band insulator, where the valence band has all the spectral weight in the ground state while the conduction band is empty.} On doping holes into the system such that \(\left<\tau_{i}\right> = -x < 0\), spectral weight is transferred from the upper Hubbard band at \(\omega = U/2\) to the lower one at \(\omega = -U/2\):
+
+\begin{equation}\begin{aligned}
+	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 - x}{\omega - \frac{U}{2}} + \frac{1 + x}{\omega + \frac{U}{2}}
+\end{aligned}\end{equation}
+\textit{This transfer of spectral weight across energy scales of the order of \(U\), as well as the lack of poles at zero energies, is referred to as mottness}~\cite{phillips2006mottness}.
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{hubbard_bands.pdf}
+	\caption{Structure of the Greens function in the atomic limit.
+The two poles at \(\omega = \pm \frac{U}{2}\) form the two Hubbard bands.
+Doping the system leads to transfer of spectral weight between the bands.}
+\end{figure}
+
+\section{Nature of propagation: metal vs insulator}
+In the metallic state, the impurity in the auxiliary model hybridises with the bath through both 1-particle and 2-particle interactions.
+For any two auxiliary models differing by the locations \(i_1, i_2\) of the impurity, the baths will always overlap.
+This means that an electron that starts out from the impurity site at \(i_1\) can hop into the bath, and eventually reach \(i_2\) by hopping out of the other bath and into the other impurity.
+Such processes connect all sites of the lattice and \textit{allow spectral flow}.
+
+In the insulating state, each auxiliary model separates into an impurity and a bath that decoupled from each other.
+This means that the impurity cannot hybridise into the bath, and hence cannot tunnel into any other impurity.
+This leads to the atomic limit of the system, where each site develops a local moment configuration because of the repulsive local correlation, but these local moments cannot communicate with each other, either through spin-exchange processes or by breaking into holons and doublons.
+Any attempt at spectral flow fails because the boundaries of the system become disconnected from each other.
+
+A more accurate picture of the insulating and metallic phases can be obtained by working with a more complicated choice of the cluster.
+For instance, instead of a single impurity, one can take two correlated impurities interacting with each other through a single-particle hopping, and this cluster then interacts with the bath through the usual interactions.
+The ground state of such a cluster is actually a quantum liquid, consisting of the entangled spin and charge degrees of freedom.
+In the metallic state, various members of this liquid such as the holons, doublons and the spinons are free to propagate across the system through the baths.
+In the insulating state, it is this cluster that then gets decoupled from the other clusters.
+The composite degrees of freedom are then unable to propagate outside the cluster, and \textit{the holons and the doublons are bound to each other}~\cite{Mott_1949} within the confines of the cluster.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=0.55\textwidth]{metal_prop.pdf}
+	\caption{Propagation of electrons from one cluster to another through the bath, in the metallic state}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=0.75\textwidth]{ins_prop.pdf}
+	\caption{The clusters get isolated from each other in the insulator, because they get decoupled from their baths.}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=0.85\textwidth]{ins_prop_cluster.pdf}
+	\caption{Each cluster is a quantum liquid composed of spin \(\left(\uparrow,\downarrow\right) \) and charge \(\left(0,2\right) \) degrees of freedom.
+In the insulating state, these degrees of freedom get bound within the cluster and are unable to propagate outside.}
+\end{figure}
+
+\section{Presence of two self-energies under symmetry-breaking}
+The effective Hamiltonian that describes either the metallic or the insulating phase has $\mathrm{SU}(2)$ symmetry in both the spin and charge sectors.
+Since the repulsive correlation on the impurity picks out the spin sector, we focus on that for now.
+Applying a small magnetic field on the impurity breaks this spin-rotation symmetry and picks out either the up or the down state on the impurity, leading to two kinds of self-energies, one for each spin state~\cite{logan_2014,Logan_2015}.
+The Hamiltonian has the form \(H(h)_i = -\frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - h\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)\).
+The unique ground-state is \(\ket{\hat n_{i,\sigma = \text{sgn}(h)}=1,\hat n_{i,\sigma = -\text{sgn}(h)}=0}\), with an energy of \(E_\text{gs} = -\frac{U}{2} - h\).
+The Greens function is easiest to obtain from the Lehmann-Kallen representation (eq.~\ref{Gf_lk}):
+\begin{equation}\begin{aligned}
+	G_{i,\sigma} = \sum_{n}\left[||\bra{\text{GS}}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_\text{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{\text{GS}}||^2\frac{1}{\omega - E_\text{GS} + E_n}\right]\\
+\end{aligned}\end{equation}
+We have \(c_{i,\sigma}\ket{\text{GS}} = \ket{\hat n_i = 0}\delta_{\sigma,\text{sgn}(h)}\) and \(c^\dagger_{i,\sigma}\ket{\text{GS}} = \ket{\hat n_i = 2}\delta_{\sigma,-\text{sgn}(h)}\), so that the only excited states that give non-zero inner product is \(\ket{n}=\ket{\hat n_i = 0}\) for the second term and \(\ket{n}=\ket{\hat n_i=2}\) for the first term, with energies \(E_n=0\).
+Substituting these, we get
+\begin{equation}\begin{aligned}
+	G_{i,\sigma}(h) = \frac{\delta_{\sigma,-\text{sgn}(h)}}{\omega - \frac{U}{2} - h} + \frac{\delta_{\sigma,\text{sgn}(h)}}{\omega + \frac{U}{2} + h} = \frac{1}{\omega + \left(\frac{U}{2}+h\right)\sigma \times \text{sgn}(h) }
+\end{aligned}\end{equation}
+Taking the limit of \(h \to 0^\pm\) then gives
+\begin{equation}\begin{aligned}
+	G_{i,\sigma}(h=0^\pm) = \frac{1}{\omega \pm \frac{U}{2}\sigma}
+\end{aligned}\end{equation}
+The self-energies arising from the correlation \(U\) can also be obtained using Dyson's equation \(\Sigma = G^{-1} - G_0^{-1}\), where \(G_0^{-1} = \omega\) is the Greens function at \(U=0\).
+Using Dyson's equation, we get
+\begin{equation}\begin{aligned}
+	\Sigma_{i,\sigma} = \pm\frac{U}{2}\sigma
+\end{aligned}\end{equation}
+
+\section{Analytic consistency check - On the Bethe lattice}
+We now apply our approach to the case of infinite number of nearest-neighbours $\mathcal{Z}\to\infty$ (the coordination number, and effectively the dimension), where the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{\mathcal{Z}}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that DMFT obtains a metal-insulator transition in that limit~\cite{georges1996}.
+It is well known from the works of Müller-Hartmann as well as Metzner and Vollhardt that self-energy arising from the correlations loses all momentum-dependence and becomes purely local~\cite{Muller-Hartmann1989,metzner_volhardt_1989}.
+This simplification is what makes DMFT exact in the limit of infinite dimensions.
+This simplification is also explicit in our formalism, as can be seen in the expression of the Self-energy (eq.~\eqref{selfenergy1}).
+Upon taking the limit of \(\mathcal{Z}\to\infty\), the non-local terms drop out:
+\begin{equation}\begin{aligned}
+	\lim_{\mathcal{Z}\to\infty}\Sigma_{H-H}(\vec k,\omega) = \frac{\left(\lambda_{\vec k_0}^{(0)}\right)^2}{\mathcal{G}^{(0)}_{dd}(\omega)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega)} = \Sigma_\text{loc}(\omega)~,
+\end{aligned}\end{equation}
+making the self-energy completely local.
+
+\section{Derivation of RG equations for the embedded e-SIAM}
+\subsection{RG scheme}
+At any given step \(j\) of the RG procedure, we decouple the states \(\left\{ {\bf q} \right\} \) on the isoenergetic surface of energy \(\varepsilon_j\).
+The diagonal Hamiltonian \(H_D\) for this step consists of all terms that do not change the occupancy of the states \(\left\{{\bf q}\right\}\):
+\begin{equation}\begin{aligned}
+	H_D^{(j)} = \varepsilon_j\sum_{q,\sigma}\tau_{q,\sigma} + \frac{1}{2}\sum_{{\bf q}}J_{{\bf q}, {\bf q}}S_d^z\left(\hat n_{{\bf q}, \uparrow} - \hat n_{{\bf q}, \downarrow}\right) - \frac{1}{2}\sum_{{\bf q}}W_{\bf q}\left(\hat n_{{\bf q}, \uparrow} - \hat n_{{\bf q}, \downarrow}\right)^2~,
+\end{aligned}\end{equation}
+where \(\tau = \hat n - 1/2\) and \(W_{{\bf q}}\) is a shorthand for \(W_{{\bf q},{\bf q},{\bf q},{\bf q}}\).
+The three terms, respectively, are the kinetic energy of the momentum states on the isoenergetic shell that we are decoupling, the spin-correlation energy between the impurity spin and the spins formed by these momentum states and, finally, the local correlation energy associated with these states arising from the \(W\) term.
+The off-diagonal part of the Hamiltonian on the other hand leads to scattering in the states \(\left\{ {\bf q} \right\} \).
+We now list these terms, classified by the coupling they originate from.
+
+\subsubsection*{Arising from the Kondo spin-exchange term}
+\begin{equation}\begin{aligned}
+	T_{KZ1}^\dagger + T_{KZ1} &= \frac{1}{2}\sum_{{\bf k}, {\bf q}, \sigma}\sigma J_{{\bf k}, {\bf q}} S_d^z  \left[c^\dagger_{{\bf q}\sigma}c_{{\bf k},\sigma} + \text{h.c.}\right],\\
+	T_{KZ2}^\dagger + T_{KZ2} &= \frac{1}{2}\sum_{{\bf q}, \sigma}\sigma J_{{\bf q}, {\bf \bar q}} S_d^z  \left[c^\dagger_{{\bf q}\sigma}c_{{\bf \bar q},\sigma} + \text{h.c.}\right],\\
+	T_{KT1}^\dagger + T_{KT1} &= \frac{1}{2}\sum_{{\bf k}, {\bf q}}J_{{\bf k}, {\bf q}} \left[S_d^+\left(c^\dagger_{{\bf q}\downarrow}c_{{\bf k}\uparrow} + c^\dagger_{{\bf k}\downarrow}c_{{\bf q}\uparrow}\right) + \text{h.c.}\right],\\
+	T_{KT2}^\dagger + T_{KT2} &= \frac{1}{2}\sum_{{\bf q}}J_{{\bf q}, {\bf \bar q}} \left[S_d^+\left(c^\dagger_{{\bf q}\downarrow}c_{{\bf \bar q}\uparrow} + c^\dagger_{{\bf \bar q}\downarrow}c_{{\bf q}\uparrow}\right) + \text{h.c.}\right],\\
+\end{aligned}\end{equation}
+\subsubsection*{Arising from spin-preserving scattering within conduction bath}
+\begin{equation}\begin{aligned}
+	T_{P1}^\dagger + T_{P1} &= -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3, {\bf k}_4 < \varepsilon_j}\sum_{\sigma} \left[W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4}c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} + \text{h.c.}\right]\\
+	T_{P2}^\dagger + T_{P3} &= -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2 < \varepsilon_j}\sum_{\sigma} W_{{\bf q},{\bf k}_2,{\bf \bar q}, {\bf \bar q}} c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma} n_{{\bf \bar q},\sigma} -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_1 < \varepsilon_j}\sum_{\sigma} W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}} c^\dagger_{{\bf k}_1,\sigma}c_{{\bf q},\sigma} n_{{\bf q},\sigma}\\
+	T_{P4} &= -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3 < \varepsilon_j}\sum_{\sigma}W_{{\bf q},{\bf \bar q},{\bf k}_2,{\bf k}_3} c^\dagger_{{\bf q},\sigma}c_{{\bf \bar q},\sigma}c^\dagger_{{\bf k}_2,\sigma}c_{{\bf k}_3,\sigma}\\
+	T_{P5} &= -\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3 < \varepsilon_j}\sum_{\sigma} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf \bar q}} c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\sigma}c_{{\bf \bar q},\sigma}\\
+		   &= +\sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3 < \varepsilon_j}\sum_{\sigma} W_{{\bf q},{\bf k}_3,{\bf k}_2,{\bf \bar q}} c^\dagger_{{\bf q},\sigma}c_{{\bf \bar q},\sigma}c^\dagger_{{\bf k}_2,\sigma}c_{{\bf k}_3,\sigma}\\
+		   &= -T_{P4}
+\end{aligned}\end{equation}
+\subsubsection*{Arising from spin-flip scattering within conduction bath}
+\begin{equation}\begin{aligned}
+	T_{F1}^\dagger + T_{F1} &= \sum_{{\bf q} \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3, {\bf k}_4 < \varepsilon_j}\sum_{\sigma} \left[W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4}c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\bar\sigma}c_{{\bf k}_4,\bar\sigma} + \text{h.c.}\right]\\
+	T_{F2} &= \sum_{{\bf q}, {\bf q}^\prime \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3 < \varepsilon_j}\sum_{\sigma}W_{{\bf q},{\bf q}^\prime,{\bf k}_2,{\bf k}_3} c^\dagger_{{\bf q},\sigma}c_{{\bf q}^\prime,\sigma}c^\dagger_{{\bf k}_2,\bar\sigma}c_{{\bf k}_3,\bar\sigma}\\
+	T_{F3} &= \sum_{{\bf q}, {\bf q}^\prime \in \varepsilon_j}\sum_{{\bf k}_2, {\bf k}_3 < \varepsilon_j}\sum_{\sigma} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf q}^\prime} c^\dagger_{{\bf q},\sigma}c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\bar\sigma}c_{{\bf q}^\prime,\bar\sigma} \\
+	T_{F4}^\dagger + T_{F4} &= \sum_{{\bf q}, {\bf q}^\prime, \in \varepsilon_j}\sum_{{\bf k}_1 < \varepsilon_j}\sum_{\sigma} \left[W_{{\bf q},{\bf q},{\bf q}^{\prime}, {\bf k}_1} n_{{\bf q},\sigma} c^\dagger_{{\bf q}^{\prime},\bar\sigma}c_{{\bf k}_1,\bar\sigma} + \text{h.c.}\right]
+\end{aligned}\end{equation}
+In all of the terms \(T_{P[i]}\) and \(T_{F[i]}\), the factor of \(1/2\) in front has been cancelled out by a factor of 2 coming from the multiple possibilities of arranging the momentum labels.
+We will henceforth ignore \(T_{P4}\) and \(T_{P5}\) because they cancel each other out.
+
+The renormalisation of the Hamiltonian is constructed from the general expression
+\begin{equation}\begin{aligned}
+	\Delta H^{(j)} = H_X \frac{1}{\omega- H_D} H_X~.
+\end{aligned}\end{equation}
+
+The states on the isoenergetic shell \(\pm|\varepsilon_j|\) come in particle-hole pairs \(\left( {\bf q}, {\bf \bar q} \right) \) with energies of opposite signs (relative to the Fermi energy).
+If \({\bf q}\) is defined as the hole state (unoccupied in the absence of quantum fluctuations), it will have positive energy, while the particle state \({\bf \bar q}\) will be of negative energy and hence below the Fermi surface.
+To be more specific, given a state \({\bf q}\) with energy \(\pm|\varepsilon_j|\), we define its particle-hole transformed counterpart as the state \({\bf \bar q} = \boldsymbol{\pi} + {\bf q}\), having energy \(\mp|\varepsilon_j|\) and residing in the opposite quadrant of the Brillouin zone.
+Given this definition, we have the important property that
+\begin{equation}\begin{aligned}\label{particleHoleRelation}
+	J_{{\bf k}, {\bf \bar q}} &= -J_{{\bf k}, {\bf q}},\\
+	W_{\left\{{\bf k}\right\}, {\bf \bar q}} &= -W_{\left\{{\bf k}\right\}, {\bf q}}~.
+\end{aligned}\end{equation}
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.35\textwidth]{particleHoleRelation.pdf}
+	\caption{Particle and hole states.}
+	\label{fig:particleHoleRelation-pdf}
+\end{figure}
+\subsection{Renormalisation of the bath correlation term {\it W}}
+The bath correlation term \(W\) can undergo renormalisation only via scattering processes arising from itself.
+Irrespective of whether the state \({\bf q}\) being decoupled is in a particle or hole configuration in the initial many-body state, the propagator \(G = 1/(\omega - H_D)\) of the intermediate excited state is uniform, and equal to
+\begin{equation}\begin{aligned}\label{propagatorW}
 	G_W = 1/\left(\omega - |\varepsilon_j|/2 + W_{\bf q}/2)\right)~,

### 2025-01-17 TilingProjectDraft/tilingProject.tex
obtained effective Hamiltonian for Kondo terms, still need to deal with the kinetic energy

@@
 \title{\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electrons}
-\author{Abhirup Mukherjee, N.S. Vidhyadhiraja, A. Taraphder, Siddhartha Lal}
+\author{Abhirup Mukherjee, Siddhartha Lal}
+\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, Mohanpur Campus, West Bengal 741246, India}
 \date{\today}
@@
 
-\subsection{Nature of the metal near the transition}
+\subsection{Comments on the nature of the metal near the transition}
 Some thoughts about the nature of the metal near the transition:
@@
 \end{itemize}
+
+\subsection{Low-energy effective theory for gapless excitations near the transition}
+As the bath interaction \(W\) is tuned through the L-PG phase, the nodal region is the last to decouple from the impurity.
+This allows us to write down a simpler Kondo model near the transition, where only the nodal region is hybridising with the impurity spin through Kondo interactions.
+This is done by retaining only those scattering processes that originate from (or end at) the nodal point, \(\vec k_N = \left(\pi/2, \pi/2\right)\).
+The other leg of the scattering vertices will involve \(k-\)space points in the immediate vicinity of the node (\(\vec k_N + \vec q, |\vec q| \ll \pi\)), since these are the strongest.
+For these points, the Kondo terms can be written as
+\begin{widetext}
+\begin{equation}\begin{aligned}
+	\tilde H_\text{imp-cbath} = \frac{1}{2}\sum_{\vec q, |\vec q| \ll \pi}\sum_{\alpha,\beta} J^*(\vec k_N, \vec k_N + \vec q)\vec{S}_d\cdot\vec{\sigma}_{\alpha\beta}\left(c^\dagger_{\vec k_N,\alpha}c_{\vec k_N + \vec q,\beta} + c^\dagger_{\vec k_N + \vec q,\alpha}c_{\vec k_N,\beta}\right) ~,
+\end{aligned}\end{equation}
+where the scattered momentum \(\vec k_N + \vec q\) resides in a small ball around the node \(\vec k_N\).
+\(J^*(\vec k_N, \vec k_N + \vec q)\) is the low-energy fixed point value of the coupling for such scattering processes.
+Throughout the rest of this section, we use the shorthand \(J^*(\vec q)\) to represent \(J^*(\vec k_N, \vec k_N + \vec q)\).
+
+From symmetry considerations, we need to consider other processes as well: the Kondo term changes sign under \(\vec k_N \to \vec k_N + \vec Q\) in one leg of the vertex (where \(\vec Q = \left( -\pi, -\pi \right) \), and remains invariant under transformation of both legs.
+This leads to three more classes of terms in the Hamiltonian:
+\begin{equation}\begin{aligned}
+	\tilde H_\text{imp-cbath} =& \frac{1}{2}\sum_{\vec q,\alpha,\beta}J^*(\vec q)\vec{S}_d\cdot\vec{\sigma}_{\alpha\beta}\left(c^\dagger_{\vec k_N,\alpha}c_{\vec k_N + \vec q,\beta} + c^\dagger_{\vec k_N + \vec q,\alpha}c_{\vec k_N,\beta} + c^\dagger_{\vec k_N + \vec Q,\alpha}c_{\vec k_N + \vec Q + \vec q,\beta} + c^\dagger_{\vec k_N + \vec Q + \vec q,\alpha}c_{\vec k_N + \vec Q,\beta}\right) ~,\\
+			   & - \frac{1}{2}\sum_{\vec q}\sum_{\alpha,\beta}J^*(\vec q)\vec{S}_d\cdot\vec{\sigma}_{\alpha\beta}\left(c^\dagger_{\vec k_N + \vec Q,\alpha}c_{\vec k_N + \vec q,\beta} + c^\dagger_{\vec k_N + \vec q,\alpha}c_{\vec k_N + \vec Q,\beta} + c^\dagger_{\vec k_N,\alpha}c_{\vec k_N + \vec Q + \vec q,\beta} + c^\dagger_{\vec k_N + \vec Q + \vec q,\alpha}c_{\vec k_N,\beta}\right) ~.
+\end{aligned}\end{equation}
+\end{widetext}
+
+In order to simplify the Hamiltonian, we define new fermionic operators
+\begin{equation}\begin{aligned}
+	a_{\vec k, \sigma} = \frac{1}{\sqrt 2}\left(c_{\vec k,\sigma} + c_{\vec k + \vec Q, \sigma}\right)~,
+	b_{\vec k, \sigma} = \frac{1}{\sqrt 2}\left(c_{\vec k,\sigma} - c_{\vec k + \vec Q, \sigma}\right)~,
+\end{aligned}\end{equation}
+where \(\vec k\) is the momentum quantum number (chosen to lie in a small window around \(\left( \pi/2,\pi/2 \right) \)) and \(\sigma\) is the spin quantum number.
+That the operators are fermionic can be easily verified:
+\begin{equation}\begin{aligned}
+	\left\{ a_{\vec k,\sigma}, a^\dagger_{\vec k^\prime,\sigma^\prime} \right\} &= \left[\delta_{\vec k, \vec k^\prime} + \frac{1}{2}\left(\delta_{\vec k + \vec Q, \vec k^\prime} + \delta_{\vec k, \vec k^\prime + \vec Q}\right)  \right] \delta_{\sigma,\sigma^\prime} \\
+	&= \delta_{\vec k, \vec k^\prime}\delta_{\sigma,\sigma^\prime}~,\\
+	\left\{ b_{\vec k,\sigma}, b^\dagger_{\vec k^\prime,\sigma^\prime} \right\} &= \left[\delta_{\vec k, \vec k^\prime} - \frac{1}{2}\left(\delta_{\vec k + \vec Q, \vec k^\prime} + \delta_{\vec k, \vec k^\prime + \vec Q}\right)  \right] \delta_{\sigma,\sigma^\prime} \\
+	&= \delta_{\vec k, \vec k^\prime}\delta_{\sigma,\sigma^\prime}~,\\
+	\left\{ a_{\vec k,\sigma}, b^\dagger_{\vec k^\prime,\sigma^\prime} \right\} &= \left\{ b_{\vec k,\sigma}, a^\dagger_{\vec k^\prime,\sigma^\prime} \right\} = 0~,
+\end{aligned}\end{equation}
+where both \(\vec k\) and \(\vec k^\prime\) are chosen from a small window around the node, so their difference is also small and it is therefore guaranteed that \(|\vec k - \vec k^\prime| \neq |\vec Q|\), rendering both \(\delta_{\vec k + \vec Q, \vec k^\prime}\) and \(\delta_{\vec k, \vec k^\prime + \vec Q}\) zero.
+For convenience, we define the new number operators
+\begin{equation}\begin{aligned}
+	N_{\vec k,\sigma} = a^\dagger_{\vec k}a_{\vec k},~ \bar N_{\vec k,\sigma} = b^\dagger_{\vec k}b_{\vec k}~.
+\end{aligned}\end{equation}
+
+We have the following useful relation between the corresponding number operators:
+\begin{equation}\begin{aligned}\label{numberOperatorRelation}
+	\hat n_{\vec k,\sigma} + \hat n_{\vec k + \vec Q, \sigma} = N_{\vec k, \sigma} + \bar N_{\vec k,\sigma}~.
+\end{aligned}\end{equation}
+
+The Hamiltonian takes the following form in terms of these new degrees of freedom:
+\begin{equation}\begin{aligned}
+	&\tilde H_\text{imp-cbath} = \\
+	&\sum_{\vec q,\alpha,\beta}J^*(\vec q)\vec{S}_d\cdot\vec{\sigma}_{\alpha\beta} \left(b^\dagger_{\vec k_N,\alpha}b_{\vec k_N + \vec q,\beta} + b^\dagger_{\vec k_N + \vec q,\alpha}b_{\vec k_N,\beta}\right)~.
+\end{aligned}\end{equation}
+We now proceed to rewrite the other parts of the Hamiltonian in terms of these new degrees of freedom. The kinetic energy can be written as
+\begin{equation}\begin{aligned}
+	\tilde H_\text{cbath} &= \sum_{\vec q,\sigma}\varepsilon_{\vec k_N + \vec q}\left(\hat n_{\vec k_N + \vec q,\sigma} - \hat n_{\vec k_N + \vec Q + \vec q,\sigma}\right)\\
+				&= \sum_{\vec q,\sigma}\varepsilon_{\vec k_N + \vec q}\left(a^\dagger_{\vec k_N + \vec q,\sigma} b_{\vec k_N + \vec q,\sigma} + b^\dagger_{\vec k_N + \vec q,\sigma} a_{\vec k_N + \vec q,\sigma}\right)~.
+\end{aligned}\end{equation}
+
+We also consider a simplified form of the bath interaction, taking into account the density-density correlations in \(k-\)space:
+\begin{widetext}
+\begin{equation}\begin{aligned}
+	\tilde H_\text{cbath-int} =& -W\sum_{\vec q,\sigma}\left(\hat n_{\vec k + \vec q,\sigma} + \hat n_{\vec k + \vec Q + \vec q,\sigma}\right) + W\sum_{\vec q_1,\vec q_2}\left( \hat n_{\vec k_N + \vec q_1, \uparrow} + \hat n_{\vec k_N + \vec Q + \vec q_1, \uparrow} \right) \left( \hat n_{\vec k_N + \vec q_2, \downarrow} + \hat n_{\vec k_N + \vec Q + \vec q_2, \downarrow} \right)~,\\
+	=& -W\sum_{\vec q,\sigma}\left(N_{\vec k_N + \vec q,\sigma} + \bar N_{\vec k_N + \vec q,\sigma}\right) + W\sum_{\vec q_1,\vec q_2}\left( N_{\vec k_N + \vec q_1,\uparrow} + \bar N_{\vec k_N + \vec q_1,\uparrow} \right) \left( N_{\vec k_N + \vec q_2,\downarrow} + \bar N_{\vec k_N + \vec q_2,\downarrow} \right)~.
+\end{aligned}\end{equation}
+\end{widetext}
+We used eq.~\ref{numberOperatorRelation} in order to obtain the final form.
+Since the Hamiltonian is defined in a small window around the nodal point, the kinetic energy is the smallest term in the Hamiltonian.
+We therefore ignore it for the time-being, and address the two other terms.
+Since both \(\tilde H_\text{imp-cbath}\) and \(\tilde H_\text{cbath-int}\) commute with \(N_{\vec k, \sigma}\), we replace the local objects \(\sum_{\vec q}N_{\vec k_N + \vec q,\sigma}\) in \(\tilde H_\text{cbath-int}\) with \(\frac{1}{2}\) since the bath is always at half-filling.
+This results in a simplified Hamiltonian for just the \(b^\dagger\) degrees of freedom:
+\begin{equation}\begin{aligned}
+	\tilde H =& -\frac{1}{2}W\sum_{\vec q,\sigma}\bar N_{\vec k_N + \vec q,\sigma} + W\sum_{\vec q_1,\vec q_2}\bar N_{\vec k_N + \vec q_1,\uparrow} \bar N_{\vec k_N + \vec q_2,\downarrow}\\
+			  &+ \sum_{\vec q,\alpha,\beta}J^*(\vec q)\vec{S}_d\cdot\vec{\sigma}_{\alpha\beta} \left(b^\dagger_{\vec k_N,\alpha}b_{\vec k_N + \vec q,\beta} + b^\dagger_{\vec k_N + \vec q,\alpha}b_{\vec k_N,\beta}\right)
+\end{aligned}\end{equation}
+
+For bath interaction strength close to the critical value (\(W \lesssim W_c\)), the fixed point coupling value \(J^*\) is much smaller than \(W\).
+In order to obtain the gapless excitations of the system arising from the presence of the impurity site, we integrate out the impurity dynamics via a Schrieffer-Wolff transformation.
+The perturbation term \(\mathcal{V}\) then consists of Hamiltonian terms that modify the impurity configuration,
+\begin{equation}\begin{aligned}
+	\mathcal{V} &= V + V^\dagger,\\
+	V^\dagger &= \frac{1}{2}\sum_{\vec q}J^*(\vec q)\vec{S}_d^+ \left(b^\dagger_{\vec k_N,\downarrow}b_{\vec k_N + \vec q, \uparrow} + b^\dagger_{\vec k_N + \vec q,\downarrow}b_{\vec k_N, \uparrow}\right)~,
+\end{aligned}\end{equation}
+while the ``non-interacting" Hamiltonian is
+\begin{equation}\begin{aligned}
+	H_D &= -\frac{1}{2}W\sum_{\vec q,\sigma}\bar N_{\vec k_N + \vec q,\sigma} + W\sum_{\vec q_1,\vec q_2}\bar N_{\vec k_N + \vec q_1,\uparrow} \bar N_{\vec k_N + \vec q_2,\downarrow}~.
+\end{aligned}\end{equation}
+The renormalisation in the dynamics of \(b^\dagger_{\vec k,\sigma}\) are given by
+\begin{equation}\begin{aligned}
+	\Delta \tilde H &= \mathcal{P}_L \mathcal{V}^\dagger \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L\\
+					&= \mathcal{P}_L \left[V \mathcal{P}_H\frac{1}{E_L - H_D} V^\dagger + V^\dagger \mathcal{P}_H\frac{1}{E_L - H_D} V \right]\mathcal{P}_L~,
+\end{aligned}\end{equation}
+where \(E_L\) is the energy of the ground state of \(H_D\), \(-(E_L - H_D)\) is the excitation energy of the state generated upon applying the perturbation \(V\), and \(\mathcal{P}_{L(H)}\) projects onto the low(high)-energy subspace.
+For the present Hamiltonian, the low-energy state (associated with \(E_L\)) is the one that minimises the bath interaction term \(\tilde H_\text{cbath-int}\); since the coupling \(W\) is negative, it projects out the spin sector of each \(k-\)state at low energies, leading to the following ground state:
+\begin{equation}\begin{aligned}
+	\ket{L} = \otimes_{\vec q}\frac{1}{\sqrt 2}\left(b^\dagger_{\vec k_N + \vec q, \uparrow}b^\dagger_{\vec k_N + \vec q, \downarrow} + 1\right) \ket{0}
+\end{aligned}\end{equation}
+where \(\ket{0}\) is the \(\bar N_{k \uparrow} = \bar N_{k \downarrow} = 0\) state.
+The state \(\ket{L}\) is at zero energy.
+High-energy states are obtained by applying, on the state \(\ket{L}\), the excitation operator \(b^\dagger_{\vec k_N,\sigma}b_{\vec k_N + \vec q,\bar\sigma}\) or its hermitian conjugate.
+The operator converts a double and a hole to spin states, incurring a total excitation cost of \(-W = |W|\).
+
+We now calculate the various terms in \(\Delta \tilde H\):
+\begin{widetext}
+\begin{equation}\begin{aligned}
+	&\mathcal{P}_L V^\dagger \mathcal{P}_H\frac{1}{E_L - H_D} V \mathcal{P}_L \\
+	&= -\frac{{J^*(q)}^2}{4W}\left(\frac{1}{2} + S_d^z\right) \sum_{\vec q}\left(b^\dagger_{\vec k_N,\downarrow}b_{\vec k_N + \vec q, \uparrow} + b^\dagger_{\vec k_N + \vec q,\downarrow}b_{\vec k_N, \uparrow}\right) \left(b^\dagger_{\vec k_N,\uparrow}b_{\vec k_N + \vec q, \downarrow} + b^\dagger_{\vec k_N + \vec q,\uparrow}b_{\vec k_N, \downarrow}\right)\\
+	&= -\frac{{J^*(q)}^2}{4W}\left(\frac{1}{2} + S_d^z\right) \sum_{\vec q}\left[\bar N_{\vec k_N, \downarrow}\left( 1 - \bar N_{\vec k_N + \vec q, \uparrow} \right) + \bar N_{\vec k_N + \vec q, \downarrow}\left( 1 - \bar N_{\vec k_N, \uparrow} \right) + b^\dagger_{\vec k_N, \downarrow} b^\dagger_{\vec k_N, \uparrow}b_{\vec k_N + \vec q, \downarrow} b_{\vec k_N + \vec q, \uparrow} + \text{h.c.}\right]~, \\
+	&\mathcal{P}_L V \mathcal{P}_H\frac{1}{E_L - H_D} V^\dagger \mathcal{P}_L \\
+	&= -\frac{{J^*(q)}^2}{4W}\left(\frac{1}{2} - S_d^z\right) \sum_{\vec q}\left[\bar N_{\vec k_N, \uparrow}\left( 1 - \bar N_{\vec k_N + \vec q, \downarrow} \right) + \bar N_{\vec k_N + \vec q, \uparrow}\left( 1 - \bar N_{\vec k_N, \downarrow} \right) + b^\dagger_{\vec k_N, \uparrow} b^\dagger_{\vec k_N, \downarrow}b_{\vec k_N + \vec q, \uparrow} b_{\vec k_N + \vec q, \downarrow} + \text{h.c.}\right] \\
+\end{aligned}\end{equation}
+\end{widetext}
+Adding both contributions and setting \(S_d^z = 0\) owing to local SU(2) symmetry on the impurity site in the absence of fluctuations, we get
+\begin{equation}\begin{aligned}
+	\Delta \tilde H = \sum_{\vec q,\sigma}\left[\Delta(\vec q)\bar N_{\vec k_N + \vec q, \sigma} -2\Delta(\vec q)\bar N_{\vec k_N, \sigma}\bar N_{\vec k_N + \vec q, \sigma}\right.\\
+	\left. -\Delta(\vec q) \left(b^\dagger_{\vec k_N, \sigma} b^\dagger_{\vec k_N, \bar\sigma} b_{\vec k_N + \vec q, \bar\sigma}b_{\vec k_N + \vec q, \sigma} + \text{h.c.}\right) \right]~,
+\end{aligned}\end{equation}
+where \(\Delta(q) = -{J^*(\vec q)}^2/8W\) is a positive energy scale.
 
@@
 
-\begin{widetext}
+% \begin{widetext}
 
@@
 	G_W = 1/\left(\omega - |\varepsilon_j|/2 + W_{\bf q}/2)\right)
-\end{itemize}
+\end{aligned}\end{equation}
 

### 2025-01-17 numerics/SIAMTest.jl
obtained k-space spectral functions

@@ -1,0 +1,98 @@
+using Fermions, Plots, ProgressMeter
+
+
+function SpecFunc2(
+    eigVals::Vector{Float64},
+    eigVecs::Vector{Dict{BitVector,Float64}},
+    probes::Dict{String,Vector{Tuple{String,Vector{Int64},Float64}}},
+    freqValues::Vector{Float64},
+    basisStates::Vector{Dict{BitVector,Float64}},
+    standDev::Union{Vector{Float64}, Float64};
+    degenTol::Float64=0.,
+    normalise::Bool=true,
+    silent::Bool=false,
+    broadFuncType::String="lorentz",
+)
+    eigenStates = Vector{Float64}[] 
+    @time for vector in eigVecs
+        push!(eigenStates, ExpandIntoBasis(vector, basisStates))
+    end
+    probeMatrices = Dict{String,Matrix{Float64}}(name => zeros(length(basisStates), length(basisStates)) for name in keys(probes))
+    @time for (name,probe) in collect(probes)
+        probeMatrices[name] = OperatorMatrix(basisStates, probe)
+    end
+
+    return SpecFunc2(eigVals, eigenStates, probeMatrices, freqValues, standDev;
+                    normalise=normalise, degenTol=degenTol, silent=silent, broadFuncType=broadFuncType)
+end
+
+function SpecFunc2(
+    eigVals::Vector{Float64},
+    eigVecs::Vector{Vector{Float64}},
+    probes::Dict{String,Matrix{Float64}},
+    freqValues::Vector{Float64},
+    standDev::Union{Vector{Float64}, Float64};
+    degenTol::Float64=0.,
+    normalise::Bool=true,
+    silent::Bool=false,
+    broadFuncType::String="lorentz",
+    )
+
+    @assert length(eigVals) == length(eigVecs)
+    @assert broadFuncType ∈ ("lorentz", "gauss")
+    @assert issorted(freqValues)
+
+    broadeningFunc(x, standDev) = ifelse(broadFuncType=="lorentz", standDev ./ (x .^ 2 .+ standDev .^ 2), exp.(-0.5 .* ((x ./ standDev).^2)) ./ (standDev .* ((2π)^0.5)))
+
+    energyGs = minimum(eigVals)
+    specFunc = 0 .* freqValues
+
+    degenerateManifold = eigVals .≤ energyGs + degenTol
+    if !silent
[…]

### 2025-01-17 numerics/caller.jl

@@ -13,14 +13,15 @@ include("./source/plotting.jl")
 
 global J_val = 0.1
 @everywhere global orbitals = ("p", "p")
-maxSize = 1000
+maxSize = 600
 WmaxSize = 600
 
 colmap = reverse(ColorSchemes.cherry)
 numShells = 1
-bathIntLegs = 3
+bathIntLegs = 1
 NiceValues(size_BZ) = Dict{Int64, Vector{Float64}}(
                          13 => -1.0 .* [0., 1., 1.5, 1.55, 1.6, 1.61] ./ size_BZ,
+                         25 => -1.0 .* [0, 3.63, 3.7, 3.8, 3.88, 3.9] ./ size_BZ,
                          33 => -1.0 .* [0, 2.8, 5.6, 5.89, 5.92, 5.93] ./ size_BZ,
                          41 => -1.0 .* [0, 3.5, 7.13, 7.3, 7.5, 7.564, 7.6] ./ size_BZ,
                          49 => -1.0 .* [0, 4.1, 8.19, 8.55, 8.77, 8.8] ./ size_BZ,
@@ -255,7 +256,7 @@ function LocalSpecFunc(
     freqValuesZoom2 = 1.
     specFuncResults = Tuple{LaTeXString, Vector{Float64}}[]
     specFuncResultsTrunc = Tuple{LaTeXString, Vector{Float64}}[]
-    standDev = (0.1, 0.1 .+ exp.(abs.(freqValues) ./ maximum(freqValues)))
+    standDev = (0.3, 0.2 .+ exp.(abs.(freqValues) ./ maximum(freqValues)))
     resonanceHeight = 0.
     effective_Wval = 0.
 
@@ -269,8 +270,6 @@ function LocalSpecFunc(
         effectiveMaxSize = W_val ≠ 0 ? (maxSize > WmaxSize ? WmaxSize : maxSize) : maxSize
         savePath = joinpath(SAVEDIR, "imp-specfunc-$(W_val)-$(effective_Wval)-$(size_BZ)-$(effectiveNumShells)-$(effectiveMaxSize)-$(bathIntLegs)-$(maximum(freqValues))-$(length(freqValues))-$(GLOBALFIELD).jld2")
         if ispath(savePath) && loadData
-            #=specFunc = CSV.File(savePath) .|> first=#
-            #=specFunc = readdlm(savePath) |> vec=#
             specFunc = jldopen(savePath)["impSpecFunc"]
         else
             hamiltDetails = Dict(
[…]

### 2025-01-17 numerics/source/helpers.jl

@@ -238,7 +238,7 @@ end
 end
 
 
-function specFuncDictFunc(
+function impSpecFunc(
         numBathPoints::Int64,
     )
     siamSpecDict = Dict{String, Vector{Tuple{String,Vector{Int64}, Float64}}}("create" => [], "destroy" => [])
@@ -250,4 +250,39 @@ function specFuncDictFunc(
         append!(kondoSpecDict["destroy"], [("+--", [1, 2, 2 * index + 1], 1.), ("+--", [2, 1, 2 * index + 2], 1.),])
     end
     return siamSpecDict, kondoSpecDict
+end
+
+
+function kspaceSpecFunc(
+        numBathPoints::Int64,
+        kpointIndices::NTuple{2, Int64},
+    )
+    specDictSet = Dict{String, Dict{String, Vector{Tuple{String,Vector{Int64}, Float64}}}}()
+
+    # composite excitation where a bath k-state is created (|n_{k↑} = 0⟩ → |n_{k↑} = 1⟩) 
+    # along with the destruction of the impurity down state (|n_{d↓} = 0⟩ → |n_{d↓} = 1⟩).
+    # Overall spin is conserved, in line with the local Fermi liquid excitations
+    specDictSet["cd_down"] = Dict("create" => [("+-", [kpointIndices[1], 2], 1.)],
+                                "destroy" => [("+-", [2, kpointIndices[1]], 1.)],
+                               )
+    specDictSet["cd_up"] = Dict("create" => [("+-", [kpointIndices[2], 1], 1.)],
+                                "destroy" => [("+-", [1, kpointIndices[2]], 1.)],
+                               )
+    specDictSet["cdagd_down"] = Dict("create" => [("++", [kpointIndices[1], 2], 1.)],
+                                "destroy" => [("--", [2, kpointIndices[1]], 1.)],
+                               )
+    specDictSet["cdagd_up"] = Dict("create" => [("++", [kpointIndices[2], 1], 1.)],
+                                "destroy" => [("--", [1, kpointIndices[2]], 1.)],
+                               )
+
+    # composite excitation where a bath k-state is created (|n_{k↑} = 0⟩ → |n_{k↑} = 1⟩) 
+    # along with a down-flip of the impurity spin (|↑⟩ → |↓⟩).
+    # Overall spin is conserved, in line with the local Fermi liquid excitations
+    specDictSet["Sd-"] = Dict("create" => [("++-", [kpointIndices[1], 2, 1], 1.)],
[…]

### 2025-01-17 numerics/source/probes.jl

@@ -121,7 +121,7 @@ end
                              pointsSequence,
                              bathIntFunc;
                              bathIntLegs=bathIntLegs,
-                             globalField=1e-8,
+                             globalField=hamiltDetails["globalField"],
                              couplingTolerance=1e-10,
                             )
     indexPartitions = [2 + 2 * length(pivotPoints)]
@@ -183,11 +183,12 @@ function iterDiagSpecFunc(
         sortedPoints::Vector{Int64},
         specFuncDict::Dict,
         bathIntLegs::Int64,
-        addPerStep::Int64,
         freqValues::Vector{Float64},
-        standDev::Union{Float64, Vector{Float64}},
-        silent::Bool,
-        broadFuncType::String,
+        standDev::Union{Float64, Vector{Float64}};
+        addPerStep::Int64=2,
+        silent::Bool=false,
+        broadFuncType::String="gauss",
+        normEveryStep::Bool=true,
     )
 
     bathIntFunc = points -> hamiltDetails["bathIntForm"](hamiltDetails["W_val"], 
@@ -195,17 +196,25 @@ function iterDiagSpecFunc(
                                                          hamiltDetails["size_BZ"],
                                                          points)
                             
+    #=hybridisationArray = 0.0 .* [(sort(hamiltDetails["kondoJArray"][point, sortedPoints], by=abs, rev=true)[1] * impCorr) for point in sortedPoints]=#
+    #=localField = ifelse(hamiltDetails["kondoJArray"][sortedPoints, sortedPoints] .|> abs |> maximum == 0, -4., 0.)=#
     hamiltonian = KondoModel(
                              hamiltDetails["dispersion"][sortedPoints],
                              hamiltDetails["kondoJArray"][sortedPoints, sortedPoints],
-                             sortedPoints,
-                             bathIntFunc;
+                             sortedPoints, bathIntFunc;
                              bathIntLegs=bathIntLegs,
                              globalField=hamiltDetails["globalField"],
+                             #=impurityField=localField,=#
                              couplingTolerance=1e-10,
                             )
[…]

### 2025-01-23 numerics/caller.jl
implemented k-space DOS calculation

@@ -13,8 +13,8 @@ include("./source/plotting.jl")
 
 global J_val = 0.1
 @everywhere global orbitals = ("p", "p")
-maxSize = 1600
-WmaxSize = 1600
+maxSize = 1000
+WmaxSize = 1000
 
 colmap = reverse(ColorSchemes.cherry)
 numShells = 1
@@ -307,21 +307,25 @@ function KspaceLocalSpecFunc(
         size_BZ::Int64;
         loadData::Bool=false,
     )
-    W_val_arr = NiceValues(size_BZ)[1:1]
+    x_arr = get_x_arr(size_BZ)
+    W_val_arr = NiceValues(size_BZ)[[1, 3, 5]]
     @time kondoJArrays, dispersion = RGFlow(W_val_arr, size_BZ)
     freqValues = collect(-15:0.001:15)
     freqValuesZoom1 = 6.
     freqValuesZoom2 = 0.3
     specFuncResults = Tuple{LaTeXString, Vector{Float64}}[]
     specFuncResultsTrunc = Tuple{LaTeXString, Vector{Float64}}[]
-    standDev = (0.1, 0.01 .+ exp.(0.01 .* abs.(freqValues) ./ maximum(freqValues)))
+    standDev = (0.1, 0.0 .+ exp.(0.01 .* abs.(freqValues) ./ maximum(freqValues)))
     effective_Wval = 0.
+    targetHeight = 0.0
+    standDevGuess = 0.1
+    kspaceDOS = Dict{Float64, Vector{Float64}}(W_val => zeros(size_BZ^2) for W_val in W_val_arr)
+    saveNames = []
 
     for W_val in W_val_arr
 
         effectiveNumShells = W_val == 0 ? numShells : 1
         effectiveMaxSize = W_val ≠ 0 ? (maxSize > WmaxSize ? WmaxSize : maxSize) : maxSize
-        #=kstate = [-3π/4, -π/4]=#
         savePath = joinpath(SAVEDIR, "klocal-specfunc-$(W_val)-$(effective_Wval)-$(size_BZ)-$(map2DTo1D(kstate..., size_BZ))-$(effectiveNumShells)-$(effectiveMaxSize)-$(bathIntLegs)-$(maximum(freqValues))-$(length(freqValues))-$(GLOBALFIELD).jld2")
         if ispath(savePath) && loadData
             specFunc = jldopen(savePath)["specFuncKstate"]
@@ -335,28 +339,37 @@ function KspaceLocalSpecFunc(
[…]

### 2025-01-23 numerics/source/probes.jl

@@ -176,7 +176,7 @@ end
 end
 
 
-function iterDiagSpecFunc(
+@everywhere function iterDiagSpecFunc(
         hamiltDetails::Dict,
         maxSize::Int64,
         sortedPoints::Vector{Int64},
@@ -188,6 +188,7 @@ function iterDiagSpecFunc(
         silent::Bool=false,
         broadFuncType::Union{String, Dict{String, String}}="gauss",
         normEveryStep::Bool=true,
+        onlyCoeffs::Vector{String}=String[],
     )
     if typeof(broadFuncType) == String
         broadFuncType = Dict(name => broadFuncType for name in specFuncDict)
@@ -198,8 +199,6 @@ function iterDiagSpecFunc(
                                                          hamiltDetails["size_BZ"],
                                                          points)
                             
-    #=hybridisationArray = 0.0 .* [(sort(hamiltDetails["kondoJArray"][point, sortedPoints], by=abs, rev=true)[1] * impCorr) for point in sortedPoints]=#
-    #=localField = ifelse(hamiltDetails["kondoJArray"][sortedPoints, sortedPoints] .|> abs |> maximum == 0, -4., 0.)=#
     hamiltonian = KondoModel(
                              hamiltDetails["dispersion"][sortedPoints],
                              hamiltDetails["kondoJArray"][sortedPoints, sortedPoints],
@@ -211,11 +210,11 @@ function iterDiagSpecFunc(
                             )
 
     # impurity local terms
-    impCorr = 8
+    impCorr = 10
     push!(hamiltonian, ("n",  [1], -impCorr/2)) # Ed nup
     push!(hamiltonian, ("n",  [2], -impCorr/2)) # Ed ndown
     push!(hamiltonian, ("nn",  [1, 2], impCorr)) # U nup ndown
-    excludeRange = [0.5 * maximum(hamiltDetails["kondoJArray"][sortedPoints, sortedPoints]), impCorr/4]
+    excludeRange = [1 .* maximum(hamiltDetails["kondoJArray"][sortedPoints, sortedPoints]), impCorr/4]
 
     indexPartitions = [10]
     while indexPartitions[end] < 2 + 2 * length(sortedPoints)
@@ -233,18 +232,27 @@ function iterDiagSpecFunc(
                                                          maxMaxSize=maxSize,
                                                          specFuncDefDict=specFuncDict,
                                                         ) 
-    totalSpecFunc = freqValues |> length |> zeros
+
+    specFuncResults = Dict()
     for (name, operator) in specFuncOperators
[…]

### 2025-02-07 TilingProjectDraft/tilingProject.tex
implemented k-space DOS calculation
updated notes with latest Greens function, correlation and entanglement calculations, and added 2CK and Heisenberg model calculations

--- 2024-12-15 TilingProjectDraft/tilingProject.tex
@@
-\documentclass[reprint,hidelinks]{revtex4-2}
+\documentclass[reprint,hidelinks,onecolumn]{revtex4-2}
 \usepackage{braket,amsmath,color,graphicx,bookmark,bm}
@@
 Translating both the momenta leads to the reversal of the sign change.
-\begin{equation}\begin{aligned}
+\begin{equation}\begin{aligned}\label{hamiltonanSymms}
 	\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2} = \Delta J^{(j)}_{{\bf k}_1, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2}~.
@@
 
+\subsection{Emergence of a two-channel Kondo Model as the low-energy theory near the transition}
+As the bath interaction \(W\) is tuned through the L-PG phase, the four nodal points in the Brillouin zone are the last to decouple from the impurity.
+This allows us to write down a simpler Kondo model near the transition, focusing on scattering processes involving the nodal region.
+Specifically, for the Kondo term \(J_{{\bf k}_1, {\bf k}_2})\), we find that only the following classes of scattering processes survive close to the critical point:
+\begin{itemize}
+	\item Both momenta in a neighbourhood around \({\bf k}_N\), where \({\bf k}_N\) can be any of the four nodal points,
+	\item One momentum from the neighbourhood around \({\bf k}_N\), while the other from the neighbourhood around \({\bf k}_N + \left( \pi, \pi \right) \)~.
+\end{itemize}
+The second class is tied to the first through a symmetry of the Hamiltonian (eq.~\ref{hamiltonanSymms}).
+The crucial feature of these processes is that each node only interacts with the other node directly opposite to it across the origin.
+That is, \(\left(\pi/2, \pi/2\right) \) and \(\left(-\pi/2, -\pi/2\right) \) only interact between themselves, while \(\left(\pi/2, -\pi/2\right) \) and \(\left(-\pi/2, \pi/2\right) \) form their own pair of connected regions.
+
+Let \(S^\pm\) be the set of momentum states in a small window around nodes along \(k_x = \pm k_y\).
+As discussed immediately above, the Kondo spin-exchange term close to the transition does not lead to scattering of any \(k-\)state from \(S^+\) to \(S^-\).
+This is captured by the following simplified Hamiltonian:
+\begin{equation}\begin{aligned}\label{twoChannel}
+H_\text{eff} = H(S^+) + H(S^-);~H(S) = \sum_{{\bf q}\in S,\sigma}\varepsilon_{\bf q}c^\dagger_{{\bf q}\sigma}c_{{\bf q}\sigma} + \sum_{{\bf q}_1\in S,{\bf q}_2\in S}\sum_{\alpha,\beta}J^*({\bf q}_1,{\bf q}_2){\bf S}_d\cdot {\bf \sigma}_{\alpha\beta}c^\dagger_{{\bf q}_1\alpha}c_{{\bf q}_2\beta}~,
+\end{aligned}\end{equation}
+where \(H(S^\pm)\) represents the dynamics of momentum states residing in regions \(S^\pm\).
+The only source of information transfer between the two regions is the fact that they interact with the same impurity local moment.
+
+Eq.\ref{twoChannel} tells us that the low-energy dynamics of the embedded eSIAM close to the Kondo-breakdown transition is governed by an emergent {\bf two-channel Kondo model}, with the conduction bath states in the sets \(S^\pm\) making up the two channels.
+Given that this is a critical point in the impurity model phase diagram (separating the local Fermi liquid and local moment phases), it is not surprising that a quantum critical model emerges at that point.
+Signatures of the quantum critical nature include power-law divergence in various correlation functions as temperature \(T \to 0\), and non-Fermi liquid excitations replacing the local Fermi liquid.
+
 \section{The Tiling Algorithm}
 
-\subsection{Formal description of the tiling procedure}\label{formalDescription}
+\subsection{Formal description of the tiling procedure}
 We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian.
@@
 \begin{equation}\begin{aligned}\label{tilingPrescriptionFinal}
-	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}~,
-\end{aligned}\end{equation}
-using which the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}~,
+\end{aligned}\end{equation}
+where we replaced \(N-3\) with \(N\) assuming a large number of sites. Using this, the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.
 
@@
 \begin{equation}\begin{aligned}\label{eigenstateProposal}
-	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} \\
-				&= \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d, {\bf z}\right)}~,
+	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d, {\bf z}\right)}~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}\label{groundstateProposal}
-	\ket{\Psi_\text{gs}} \equiv \ket{\Psi_{s_0}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)} \\
-			     &= \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d, {\bf z}\right)}
-\end{aligned}\end{equation}
-
-\section{1-particle Greens Functions}
+	\ket{\Psi_\text{gs}} \equiv \ket{\Psi_{s_0}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d, {\bf z}\right)}
+\end{aligned}\end{equation}
+
+\section{One-Particle Greens Functions}
+\subsection{Momentum-space}
 In the previous part, we proposed a form for the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{gs}}\) of the auxiliary models.
@@
 We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
-We define the retarded time-domain Greens function between two quantum numbers \(\nu_1\) and \(\nu_2 \) at zero temperature as
-\begin{equation}\begin{aligned}
-	\tilde G(\nu_2, \nu_1; T) = -i\theta(T) \braket{\Psi_\text{gs} | \left\{ c(\nu_2, T), c^\dagger(\nu_1) \right\} | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(T\): 
-\begin{equation}\begin{aligned}
-	c(\nu,t) = e^{iT H_\text{tiled} }c(\nu)e^{-i T H_\text{tiled}}~.
-\end{aligned}\end{equation}
-The quantum number \(\nu\) typically refers to position or momentum: setting \(\nu_1={\bf r}_1, \nu_2={\bf r}_2\) will lead to a real-space Greens function between the two spatial points.
-By introducing the Fourier transform \(g(T) = \int d\omega~ e^{-i\omega T}f(\omega)\), the frequency-domain Greens function can be cast in its spectral representation
-\begin{equation}\begin{aligned}\label{spectralRepresentation}
-	&\tilde G(\nu_2, \nu_1; \tilde\omega) \\
-	&= \frac{1}{\mathcal{D}_\text{gs}}\sum_{s_0 \in \text{GS}}\sum_s \left[\frac{F_{c^\dagger}^*(s, \nu_2)F_{c^\dagger}(s, \nu_1)}{\tilde\omega - \left( \tilde E_s - \tilde E_\text{gs} \right) } + \frac{F_{c}(s, \nu_1)F_{c}^*(s, \nu_2)}{\tilde\omega + \left( \tilde E_s - \tilde E_\text{gs} \right) }\right] ~,
-\end{aligned}\end{equation}
-where \(s_0=\left({\bf k}_0, n_0\right)\) sums over the ground state(s) of the system (with energy \(\tilde E_\text{gs}\) and degeneracy \(\mathcal{D}_\text{gs}\)) and \(s=\left({\bf k}, n\right)\) sums over all eigenstates (with energies \(\tilde E_s\)).
-The coefficients
-\begin{equation}\begin{aligned}
-	F_{c^\dagger}(s, \nu) = \braket{\Psi_{s}|c^\dagger(\nu)|\Psi_{s_0}},\\
-	F_{c}(s, \nu) = \braket{\Psi_{s}|c(\nu)|\Psi_{s_0}}~,
-\end{aligned}\end{equation}
-represent spectral weights for particle and hole excitations from the ground state \(\ket{s_0}\) into the excited state \(\ket{s}\).
-
-In order to make contact with the auxiliary models, the first simplification  that we carry out is of the eigenenergies \(\tilde E_s\)in the denominators.
-The label \(s\) involves a total momentum \({\bf k}\) and a band index \(n\).
-Guided by the relation eq.~\ref{tilingPrescriptionFinal} between the Hamiltonians, we assume a separation of the total energy into an impurity model contribution \(E_n\) coming from \(\mathcal{H}_\text{aux}\) and a contribution \(\varepsilon({\bf k})\) coming from the non-interacting background Hamiltonian \(\mathcal{H}_\text{cbath-nint}\): \(E_s \simeq N E_n - (N-3) \varepsilon_{\bf k}\)~, where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\).
-Replacing \(N-3\) with \(N\) for a system of large number of particles, the spectral representation can be written as
-\begin{equation}\begin{aligned}
-	&\tilde G(\nu_2, \nu_1; \tilde\omega) \\
-	&= \frac{1}{\mathcal{D}_\text{gs}}\sum_{s_0 \in \text{GS}}\sum_s \left[\frac{F_{c^\dagger}^*(s, \nu_2)F_{c^\dagger}(s, \nu_1)}{\tilde\omega - N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) } \right.\\
-	&\left. + \frac{F_{c}(s, \nu_1)F_{c}^*(s, \nu_2)}{\tilde\omega + N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) }\right] ~,
-\end{aligned}\end{equation}
-where the absence of the tilde in the denominators indicates that those energies arise from the auxiliary model Hamiltonian.
-In order to rewrite this expression in terms of quantities that can be computed purely from the auxiliary models, we replace the eigenstates with the forms given in eq.~\ref{eigenstateProposal}:
-\begin{equation}\begin{aligned}\label{spectralWeightsAuxiliary}
-	&F_{c^\dagger}^*(s, \nu_2) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{i {\bf k}\cdot{\bf r}_d - {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_{n_0}({\bf r}_d^\prime)|c(\nu_2)|\psi_{n}({\bf r}_d)}\\
-	&F_{c^\dagger}(s, \nu_1) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{-i {\bf k}\cdot{\bf r}_d + {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_n({\bf r}_d)|c^\dagger(\nu_1)|\psi_{n_0}({\bf r}_d^\prime)}~,
-\end{aligned}\end{equation}
-where \({\bf k}_0\) is the crystal momentum value in the ground state.
-
-\subsection{Real-space Greens functions}
-We first consider one-particle Greens functions \(\tilde G({\bf r}; \tilde\omega)\) for the propagation of excitations between two spatial points \(\nu_1={\bf r}_c\) and \(\nu_2={\bf r}_c + {\bf r}\), where \({\bf r}_c\) is a fixed reference point in the lattice.
-Within the impurity model, the lattice site that most closely resembles the bulk lattice model is of course the impurity site; in order to ensure that all terms in eq.~\ref{spectralRepresentation} involve the impurity site, we approximate the states within \(F_{c^\dagger}(s,\nu_1) = F_{c^\dagger}(s,{\bf r}_c)\) of eq.~\ref{spectralWeightsAuxiliary} purely in terms of the auxiliary model at \({\bf r}_c\):
-\begin{equation}\begin{aligned}\label{eigenstateUniform}
-	\ket{\Psi_s} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} \left[e^{i {\bf k}\cdot{\bf r}_c} \ket{\psi_{n}\left({\bf r}_c\right)} + \ket{\psi_{n}}_\text{diff}\right]\\
-		     &\simeq \sqrt N e^{i {\bf k}\cdot{\bf r}_c} \ket{\psi_{n}\left({\bf r}_c\right)}.
-\end{aligned}\end{equation}
-This amounts to retaining the spatially uniform part of the wavefunction and dropping the modulating difference term \(\ket{\psi_{n}}_\text{diff} = e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} - e^{i {\bf k}\cdot{\bf r}_c} \ket{\psi_{n}\left({\bf r}_c\right)}\).
-Replacing the exact forms in \(F_{c^\dagger}(s, {\bf r}_c)\) with this approximation results in the expression
-\begin{equation}\begin{aligned}
-	F_{c^\dagger}(s, {\bf r}_c) \simeq N e^{-i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_c} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}~.
-\end{aligned}\end{equation}
-For the other term \(F_{c^\dagger}(s,\nu_2) = F_{c^\dagger}(s,{\bf r}_2)\), we make the less drastic approximation of retaining the matrix elements between the same auxiliary models \({\bf r}_d = {\bf r}_d^\prime\), leading to
-\begin{equation}\begin{aligned}
-	F_{c^\dagger}^*(s, {\bf r}_2) = \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_d)|c({\bf r}_2)|\psi_{n}({\bf r}_d)}~.
-\end{aligned}\end{equation}
-The summation can be transferred on to the annihilation operator by using translation operators:
-\begin{equation}\begin{aligned}
-	&\braket{\psi_{n_0}({\bf r}_d)|c({\bf r}_2)|\psi_{n}({\bf r}_d)} \\
-	&= \braket{\psi_{n_0}({\bf r}_c)|T\left({\bf r}_d - {\bf r}_c\right) c({\bf r}_2) T^\dagger\left({\bf r}_d - {\bf r}_c\right) |\psi_{n}({\bf r}_c)}\\
-	&= \braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_2 + {\bf r}_c - {\bf r}_d) |\psi_{n}({\bf r}_c)}~,
-\end{aligned}\end{equation}
-leading to the more useful form
-\begin{equation}\begin{aligned}
-	&F_{c^\dagger}^*(s, {\bf r}_2) \\
-	&= \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k}- {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_2 + {\bf r}_c - {\bf r}_d) |\psi_{n}({\bf r}_c)}\\
-	&= \frac{1}{N}\sum_{{\bf r}_x} e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r}_2 - {\bf r}_x\right)} \braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_c + {\bf r}_x) |\psi_{n}({\bf r}_c)}~.
-\end{aligned}\end{equation}
-In the second step, we introduced a new dummy variable \({\bf r}_x = {\bf r}_2 - {\bf r}_d\) that tracks the propagation of excitations into the auxiliary model.
-
-Having obtained the particle spectral coefficients, we can obtain the hole counterparts by mapping them onto each other.
-This can be done by noting that under our assumptions of \({\bf r}_d = {\bf r}_d^\prime\) in eq.~\ref{spectralWeightsAuxiliary}, we have the following relations:
-\begin{equation}\begin{aligned}
-	F_{c} &= F_{c^\dagger}^*\left({\bf k}\leftrightarrow{\bf k}_0, n \leftrightarrow n_0\right),\\
-	F_{c}^* &= F_{c^\dagger}\left({\bf k}\leftrightarrow{\bf k}_0, n \leftrightarrow n_0\right)~.
-\end{aligned}\end{equation}
-Using these, we get
-\begin{equation}\begin{aligned}\label{spectralParticleHoleRelation}
-	F_{c} &= \frac{1}{N}\sum_{{\bf r}_x} e^{i \left({\bf k}_0- {\bf k}\right)\cdot\left({\bf r}_2 - {\bf r}_x\right)} \braket{\psi_{n}({\bf r}_c)| c({\bf r}_x) |\psi_{n_0}({\bf r}_c)},\\
-	F_{c}^* &= N e^{-i \left({\bf k}_0 - {\bf k}\right)\cdot{\bf r}_c} \braket{\psi_{n_0}({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n}({\bf r}_c)}~.
-\end{aligned}\end{equation}
-
-The complete expression for \(\tilde G_\text{loc}(\tilde\omega)\) now looks like
-\begin{widetext}
-\begin{equation}\begin{aligned}
-	\tilde G({\bf r}; \tilde\omega) &= \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,{\bf k}_0}\sum_{{\bf k}, n}\sum_{{\bf r}_x}  \left[e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}\frac{\braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_x) |\psi_{n}({\bf r}_c)} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}}{\tilde\omega - N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) } \right.\\
-					  &\left.+ e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}\frac{\braket{\psi_{n_0}({\bf r}_c)| c^\dagger({\bf r}_c) |\psi_{n}({\bf r}_c)} \braket{\psi_n({\bf r}_c)|c({\bf r}_x)|\psi_{n_0}({\bf r}_c)}}{\tilde\omega + N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) }\right] ~,\\
-					  &= \frac{1}{N}\sum_{{\bf k}_0, {\bf k}}\sum_{{\bf r}_x}  \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,n}\left[e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}\frac{\braket{\psi_{n_0}({\bf r}_c)| c({\bf r}_x) |\psi_{n}({\bf r}_c)} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}}{\omega - \left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) } \right.\\
-					  &\left.+ e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}\frac{\braket{\psi_{n_0}({\bf r}_c)| c^\dagger({\bf r}_c) |\psi_{n}({\bf r}_c)} \braket{\psi_n({\bf r}_c)|c({\bf r}_x)|\psi_{n_0}({\bf r}_c)}}{\omega + \left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) }\right] ~,
-\end{aligned}\end{equation}
-\end{widetext}
-where \(\omega = \tilde\omega/N\) is the frequency scale for the auxiliary model.
-We can define an auxiliary model Greens functions \(G(d,{\bf r}_x; T) = -i\theta(T)\braket{\psi_\text{gs} | \left\{c^\dagger_{{\bf d}\sigma}, c_{{\bf d} + {\bf r}_x\sigma}\right\} | \psi_\text{gs}}\) for the propagation of excitations that start from the impurity site and extend up to a distance \({\bf r}_x\) into the auxiliary model; the subscripts \(p\) and \(h\) indicate that that Greens function involves only the positive and negative frequency poles respectively.
-In terms of these, the lattice model Greens function can be written in a more intuitive form.
-Assuming a unique momentum \({\bf k}_0\) for the ground state and adjusting the ground state non-interacting energy \(\varepsilon_{{\bf k}0}\) to zero, we get
-\begin{equation}\begin{aligned}
-	&\tilde G({\bf r}; \tilde\omega) \\
-	&= \frac{1}{N}\sum_{{\bf k}}\sum_{{\bf r}_x}  \left[e^{i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}G_p\left({\bf r}_x;\omega + \varepsilon_{\bf k}\right) \right.\\
-	&\left.+ e^{-i \left({\bf k}- {\bf k}_0\right)\cdot\left({\bf r} - {\bf r}_x\right)}G_h\left({\bf r}_x;\omega - \varepsilon_{\bf k}\right)\right]
-\end{aligned}\end{equation}
-
-\subsection{Momentum-space Greens functions}
-We now consider Greens functions at a particular momentum \({\bf K}\), obtained by setting \(\nu_1=\nu_2={\bf K}\). The spectral coefficients are of the form
-\begin{equation}\begin{aligned}
-	F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{i {\bf k}\cdot{\bf r}_d - {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_{n_0}({\bf r}_d^\prime)|c({\bf K})|\psi_{n}({\bf r}_d)}\\
-	F_{c^\dagger}(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d, {\bf r}_d^\prime} e^{-i {\bf k}\cdot{\bf r}_d + {\bf k}_0\cdot{\bf r}_d^\prime} \braket{\psi_n({\bf r}_d)|c^\dagger({\bf K})|\psi_{n_0}({\bf r}_d^\prime)}~.
-\end{aligned}\end{equation}
-Similar to the approach for the real-space Greens function, we simplify \(F^*_p(s, {\bf K})\) by retaining only the \({\bf r}_d = {\bf r}_d^\prime\) members, and then translating the arbitrary point \({\bf r}_d\) to a common reference point \({\bf r}_c\) in the lattice:
-\begin{equation}\begin{aligned}
-	&F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}\sum_{{\bf r}_d} e^{i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_d} \braket{\psi_{n_0}({\bf r}_d)|c({\bf K})|\psi_{n}({\bf r}_d)}~,\\
-	&\braket{\psi_{n_0}({\bf r}_d)|c({\bf K})|\psi_{n}({\bf r}_d)}\\
-	&= \braket{\psi_{n_0}({\bf r}_c)| T\left({\bf r}_d - {\bf r}_c\right) c({\bf K}) T^\dagger\left({\bf r}_d - {\bf r}_c\right) |\psi_{n}({\bf r}_c)}~.
-\end{aligned}\end{equation}
-The effect of the translation operators on the \(k-\)space annihilation operator can be easily deduced by transforming it to real-space, using the Fourier transform definition
+We define the retarded time-domain lattice \(k-\)space Greens function at zero temperature as
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c_{{\bf K}\sigma}(t), c^\dagger_{{\bf K}\sigma} \right\} | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(t\): 
+\begin{equation}\begin{aligned}\label{heisenberg}
+	c_{{\bf K}\sigma}(t) = e^{it H_\text{tiled} }c_{{\bf K}\sigma}e^{-i t H_\text{tiled}}~.
+\end{aligned}\end{equation}
+We now proceed to simplify one of the terms of the anticommutator (for simplicity of notation):
+\begin{equation}\begin{aligned}\label{greensFunction1}
+	&\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_{\vec r,\vec \Delta}e^{-i{\bf K}_0\cdot\vec\Delta}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+To make further progress, we insert the identity resolution \(1 = \sum_s\ket{\Psi_s}\bra{\Psi_s}\) in between the two operators, where \(s=\left({\bf k}, n\right)\) sums over all eigenstates (with energies \(\tilde E_s\)).
+The lattice eigenstates themselves can again be written in terms of those of the auxiliary model, using eq.~\ref{eigenstateProposal}:
+\begin{equation}\begin{aligned}
+	\ket{\Psi_s}\bra{\Psi_s} = \sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\vec k\cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}~.
+\end{aligned}\end{equation}
+With this, eq.~\ref{greensFunction1} becomes
+	\begin{equation}\begin{aligned}\label{greensfunction2}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\vec k_0\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+In order to bring this expression closer to the form of an auxiliary model Greens function, we would like to transform the initial and final states \(\ket{\psi(\vec r)}\) and \(\ket{\psi(\vec r + \vec \Delta)}\) to apply to the same auxiliary model.
+This is done by using the relation: \(\ket{\psi(\vec r + \Delta)} = T^\dagger(\vec \Delta)\ket{\psi(\vec r)}\), where \(T^\dagger(\vec \Delta)\) translates all lattice sites by the vector \(\vec\Delta\).
+\begin{equation}\begin{aligned}
+	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) T^\dagger(\vec \Delta) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
+\end{aligned}\end{equation}
+The effect of the translation operators on the \(k-\)space annihilation operator can be easily ascertained by transforming it to real-space, using the Fourier transform definition
 \begin{equation}\begin{aligned}\label{fourTransf}
-	c({\bf K}) = \frac{1}{\sqrt N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}c({\bf r})~.
+	c({\bf K}) = \frac{1}{\sqrt N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r})~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}\label{translationOnField}
-	&T\left({\bf r}_d - {\bf r}_c\right) c({\bf K}) T^\dagger\left({\bf r}_d - {\bf r}_c\right)\\
-	&= \frac{1}{N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}T\left({\bf r}_d - {\bf r}_c\right) c({\bf r}) T^\dagger\left({\bf r}_d - {\bf r}_c\right)\\
-	&= \frac{1}{N}\sum_{\bf r}e^{i{\bf K}\cdot{\bf r}}c({\bf r} - {\bf r}_d + {\bf r}_c)\\
-	&= e^{i{\bf K}\cdot\left({\bf r}_d - {\bf r}_c\right)}c({\bf K})~.
-\end{aligned}\end{equation}
-With this, the final form of \(F_{c^\dagger}^*(s, {\bf K})\) becomes
-\begin{equation}\begin{aligned}
-	F_{c^\dagger}^*(s, {\bf K}) = \frac{1}{N}e^{-i {\bf K}\cdot{\bf r}_c}\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}\\
-	\times\sum_{{\bf r}_d}e^{i \left({\bf K} + {\bf k} - {\bf k}_0\right)\cdot{\bf r}_d}
-\end{aligned}\end{equation}
-The sum over \({\bf r}_d\) evaluates to \(\sum_{{\bf r}_d}e^{i \left({\bf K} + {\bf k} - {\bf k}_0\right)\cdot{\bf r}_d} = N \delta_{{\bf K}, - {\bf k} + {\bf k}_0}\), leading to
-\begin{equation}\begin{aligned}
-	F_{c^\dagger}^*(s, {\bf K}) = e^{-i {\bf K}\cdot{\bf r}_c}\delta_{{\bf K}, - {\bf k} + {\bf k}_0}\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}
-\end{aligned}\end{equation}
-
-For the other coefficient \(F_{c^\dagger}(s, {\bf K})\), we again proceed similar to the previous subsection: we retain only the uniform part of the wavefunction, placing all the impurity models at the reference point \({\bf r}_c\):
-\begin{equation}\begin{aligned}
-	F_{c^\dagger}(s, {\bf K}) = Ne^{-i \left({\bf k} - {\bf k}_0\right)\cdot{\bf r}_c} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf K})|\psi_{n_0}({\bf r}_c)}~.
-\end{aligned}\end{equation}
-In order to introduce the impurity site operator in the expression, we Fourier transform \(c^\dagger({\bf K})\) (following eq.~\ref{fourTransf}), and keep only that real-space mode that lies on the impurity reference point \({\bf r}_c\):
-\begin{equation}\begin{aligned}
-	F_{c^\dagger}(s, {\bf K}) = e^{-i \left({\bf k} - {\bf k}_0 + {\bf K}\right)\cdot{\bf r}_c} \braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}~.
-\end{aligned}\end{equation}
-
-Using eq.~\ref{spectralParticleHoleRelation}, we obtain the hole transition coefficients:
-\begin{equation}\begin{aligned}
-	F_{c}(s, {\bf K}) &= e^{-i {\bf K}\cdot{\bf r}_c}\delta_{{\bf K}, {\bf k} - {\bf k}_0}\braket{\psi_{n}({\bf r}_c)|c({\bf K})|\psi_{n_0}({\bf r}_c)},\\
-	F_{c}^*(s, {\bf K}) &= e^{-i \left({\bf k}_0 - {\bf k} + {\bf K}\right)\cdot{\bf r}_c} \braket{\psi_{n_0}({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n}({\bf r}_c)}~.
-\end{aligned}\end{equation}
-
-The complete expression for the momentum space Greens function is therefore
-\begin{widetext}
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}; \tilde\omega) = \frac{1}{\mathcal{D}_\text{gs}}\sum_{n_0,{\bf k}_0 \in \text{GS}}\sum_{n,{\bf k}} e^{-i {\bf K}\cdot{\bf r}_c}\left[\delta_{{\bf K}, - {\bf k} + {\bf k}_0}\frac{\braket{\psi_{n_0}({\bf r}_c)|c({\bf K})|\psi_{n}({\bf r}_c)}\braket{\psi_n({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n_0}({\bf r}_c)}}{\tilde\omega - N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) } \right.
+	T\left(\vec a\right) c({\bf K}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}T\left(\vec a\right) c({\bf r}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r} - \vec a) = e^{-i{\bf K}\cdot\vec a}c({\bf K})~.
+\end{aligned}\end{equation}
+Using this identity on the above expression gives
+\begin{equation}\begin{aligned}
+	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = e^{-i{\bf K} \cdot \vec \Delta}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
+\end{aligned}\end{equation}
+Finally replacing this all the way back into eq.~\ref{greensfunction2} gives
+	\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K}\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime - \vec\Delta)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+To further unify the operators, we make the substitution \(\vec \Delta^\prime \to \vec \Delta^\prime + \vec \Delta\), leading to the expression
+	\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K} - \vec k\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+The sum over \(\vec\Delta\) can now be carried out, resulting in
+\begin{equation}\begin{aligned}\label{greensfunction3}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~,
+\end{aligned}\end{equation}
+where the sum over \(s=(\vec k, n)\) has been reduced to a sum over the auxiliary model eigenstate index \(n\) because of the Kronecker delta \(\delta\left(\vec k_0 + {\bf K} - \vec k\right)\).
+This can be further simplified by splitting the sum over \(\vec\Delta^\prime\) into positive and negative parts and then making the transformation \(\vec r^\prime \to \vec r^\prime + \vec \Delta^\prime\):
+\begin{equation}\begin{aligned}
+	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime-\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}\right] \\
+																																												   &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\right] \\
+\end{aligned}\end{equation}
+For each pair of \(\vec r^\prime\) and \(\vec\Delta^\prime\), the term within the box brackets has the form of a two-level Hamiltonian between the states \(\ket{\psi_n(\vec r^\prime)}\) and \(\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\), with a tunnelling amplitude \(e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\).
+The term can therefore be written in the eigenbasis of this Hamiltonian:
+\begin{equation}\begin{aligned}
+	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &=\frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right],
+\end{aligned}\end{equation}
+where \(\ket{\chi_n^\pm(\vec r^\prime,\vec\Delta^\prime)} = \frac{1}{\sqrt 2}\left[\ket{\psi_n(\vec r^\prime)} \pm e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime + \vec\Delta^\prime)}\right] \) are the eigenvectors of the tunnelling Hamiltonian with eigenvalues \(\pm 1\) respectively.
+With this basis transformation, we can rewrite eq.~\ref{greensfunction3} as
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+
+In order to make the expression more transparent, we consider the various components separately:
+\paragraph{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}:
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+These terms represent those contributions to the total Greens function that arise from excitations that start and end at a specific auxiliary model (at \(\vec r\)), and also evolve dynamically within the same auxiliary model.
+These terms are therefore exactly equal to the auxiliary model Greens function at position \(\vec r\), and are the most dominant contribution due to the localised nature of the impurity model.
+
+\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}:
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime \neq \vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+These are more non-local contributions; they involve excitations whose time evolution is governed by a different auxiliary model than the terminal one.
+These contributions are highly suppressed in the Kondo screened phase because of the strong entanglement of the singlet ground state.
+
+\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime \neq 0\)}:
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime \neq \vec r,\vec \Delta^\prime \neq 0} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+These are the most non-local contributions; they involve excitations whose time evolution is governed by three different auxiliary models. Accordingly, these contributions are further suppressed.
+
+We now consider each type of contribution in more detail.
+\subsection{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}
+Restricting ourselves to just the single auxiliary model contributions gives
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+We first consider more carefully the transition operator \(\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\) for the 1-particle excitation giving rise to the above Greens function.
+Within our auxiliary model approach, gapless excitations within the lattice model are represented by gapless excitations of the impurity site, specifically those that screen the impurity site and form the local Fermi liquid.
+As a result, the uncoordinated \(\mathcal{T}-\)matrix for the lattice model must be replaced by a combined \(\mathcal{T}-\)matrix within the impurity model that captures those gapless excitations that occur in connection with the impurity, and projects out the uncorrelated excitations that take place even when the impurity site is decoupled from the bath.
+
+In order to construct this auxiliary model \(\mathcal{T}-\)matrix, we note that the impurity site can have both spin and charge excitations.
+Considering both excitations, the modified \(\mathcal{T}-\)matrix that constructs \(k-\)space excitations in correlation with the impurity site are
+\begin{equation}\begin{aligned}\label{tmatrix}
+	\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\left(\sum_{\sigma^\prime}c^\dagger_{d\sigma} + \text{h.c.}\right) + c_{{\bf K}\sigma}\left(S_d^+ + \text{h.c.}\right)~,
+\end{aligned}\end{equation}
+leading to the updated expression for the complete Greens function:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+
+In order to convert this into a more useful form, we use eq.~\ref{heisenberg}:
+\begin{equation}\begin{aligned}
+		\braket{\psi_{0}(\vec r) | \mathcal{T}_{{\bf K}\sigma}(t) | \psi_n(\vec r)} = \braket{\psi_{0}(\vec r) | e^{it H_\text{tiled} }\mathcal{T}_{{\bf K}\sigma}e^{-i t H_\text{tiled}} | \psi_n(\vec r)}~.
+\end{aligned}\end{equation}
+Guided by the relation in eq.~\ref{tilingPrescriptionFinal} \(H_\text{tiled} = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}\) between the tiled Hamiltonian and the auxiliary model, we assume that the operator \(e^{-i t H_\text{tiled}}\) acting on the state \(\ket{\psi_n(\vec r)}\) involves the excitation energy \(E_n\) of only a single auxiliary model.
+Specifically, \(E_n\) is the energy of the eigenstate \(\ket{\psi_n(\vec r)}\).
+This is supported by the fact that this class of contributions to the Greens function is completed within a single auxiliary model.
+Accordingly, we replace \(H_\text{tiled}\) with \(E_n - \varepsilon_{\bf k} \), where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\) and \({\bf k}\) is the crystal momentum associated with the state \(\ket{\psi_n(\vec r)}\).
+This momentum was found to be constrained to \({\bf k}_0 + {\bf K}\) below eq.~\ref{greensfunction3}.
+In the same way, the action of \(H_\text{tiled}\) on the terminal state \(\ket{\psi_{0}(\vec r)}\) gives \(E_0 - \varepsilon_{\bf k_0}\), where \(E_0\) is the ground state energy of the auxiliary model at \({\bf r}\).
+Applying this to our expression gives
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[e^{-it\omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + e^{-it\omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~,
+\end{aligned}\end{equation}
+where \(\omega_p = (E_n - \varepsilon_{\bf k_0 + \bf K}) - (E_0 - \varepsilon_{\bf k_0})\) is the particle-excitation cost and \(\omega_h = -\omega_p\) is the hole-excitation cost.
+We now introduce the Fourier transform \(g(\omega) = \int~dt~ e^{i\omega T}f(t)\) to obtain the frequency-domain Greens function in its spectral representation:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; \omega) = \frac{1}{N}\sum_{\vec r}\sum_n \braket{\psi_{0}(\vec r) | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+For each value of \({\vec r}\), the term within that summation is simply the Greens function (for the excitation \(\mathcal{T}_{{\bf K}\sigma}\)) of the auxiliary model with the impurity site at \({\vec r}\).
+Since all these impurity models are physically equivalent (because of translation invariance), we can replace the average over \({\bf r}\) with the value obtained from any one auxiliary model.
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; \omega) = \sum_n \braket{\psi_{0} | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}} ~.
+\end{aligned}\end{equation}
+
+\subsection{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}
+Allowing for more non-local contributions, and updating the \(\mathcal{T}-\)matrix similar to the previous section gives the following Greens function:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+In order to allow computations within a single auxiliary model, we replace the translated state \(\ket{\psi_n(\vec r^\prime)}\) with \(T^\dagger(\vec r \to \vec r^\prime)\ket{\psi_n(\vec r)} \), where \(T^\dagger(\vec r - \vec r^\prime)\) translates all sites by the vector \(\vec r^\prime - \vec r\).
+This leads to a modified correlation function but within a single auxiliary model:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_{n,\vec r, \vec r^\prime} \bra{\psi_{0}(\vec r)} &\left[\mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.
 \\
-	+ \left.\delta_{{\bf K}, {\bf k} - {\bf k}_0}\frac{\braket{\psi_{n}({\bf r}_c)|c({\bf K})|\psi_{n_0}({\bf r}_c)}\braket{\psi_{n_0}({\bf r}_c)|c^\dagger({\bf r}_c)|\psi_{n}({\bf r}_c)}}{\tilde\omega + N\left( E_n - E_{n_0} - \varepsilon_{\bf k} + \varepsilon_{{\bf k}0}\right) }\right] ~.
-\end{aligned}\end{equation}
-\end{widetext}
-Once again assuming the uniqueness of \({\bf k}_0\), setting \(\varepsilon_{{\bf k}0}\) to zero and choosing the reference point \({\bf r}_c\) such that \({\bf K}\cdot{\bf r}_c = 0\), we have
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}; \tilde\omega) = G_p\left({\bf r}_c, {\bf K}; \omega + \varepsilon_{{\bf k}_0 - {\bf K}}\right) + G_h\left({\bf r}_c, {\bf K}; \omega - \varepsilon_{{\bf k}_0 + {\bf K}}\right),
-\end{aligned}\end{equation}
-where we have identified \({\bf r}_c\) as the impurity site and defined an auxiliary model Greens function \(G\left(d, {\bf K}; T\right) = -i\theta(T)\braket{\psi_\text{gs} | \left\{c^\dagger_{d\sigma}, c_{{\bf K},\sigma}\right\} | \psi_\text{gs}} \) for propagation of excitations from the \(d(f)-\)orbital impurity state \(\ket{d\sigma}\) into a momentum state of the conduction bath.
-
-\subsection{Spectral function and self-energies}
-Having obtained the one-particle Greens functions in both real and momentum-space, one can directly obtain the corresponding spectral functions \(\tilde A(\nu_2,\nu_1; \omega)\) and self-energies \(\tilde \Sigma(\nu_2,\nu_1; \omega)\), using standard relations.
-For eg., in momentum space, we have
-\begin{equation}\begin{aligned}
-	&\tilde A({\bf K}; \omega) \\
-	&= -\frac{1}{\pi}\text{Im}\left[\tilde G({\bf K}; \tilde\omega)\right]  \\
-	&= -\frac{1}{\pi}\text{Im}\left[G_p\left(d, {\bf K}; \omega + \varepsilon_{{\bf k}_0 - {\bf K}}\right) + G_h\left(d, {\bf K}; \omega - \varepsilon_{{\bf k}_0 + {\bf K}}\right)\right],\\
-\end{aligned}\end{equation}
-and
-\begin{equation}\begin{aligned}
-	\tilde \Sigma({\bf K}; \omega) = \left(\tilde G^{(0)}({\bf K}; \tilde\omega)\right)^{-1} - \left(\tilde G({\bf K}; \tilde\omega)\right)^{-1},
-\end{aligned}\end{equation}
-where \(\text{Im}[\cdot]\) is the imaginary part, and \(\tilde G^{(0)}\) is the non-interacting Greens function that is obtained by setting \(U = U_b = 0\) within the auxiliary model.
+								&\left.
+\mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+In fact, by the same arguments as in the previous section, we can obtain a frequency-resolved Greens function:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; \omega) = \sum_n \bra{\psi_{0}} &\left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.\\
+															&\left.
+\frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}} ~.
+\end{aligned}\end{equation}
+To obtain the above, we used the fact that \(H_\text{tiled}\) commutes with the translation operator.
 
@@
 
-\section{Two-particle static correlators}
-Properties of the ground state can be probed using static correlation functions that are expectation values of two-particle excitation operators.
-We will consider spin and charge correlations, in real and momentum space.
-
-We first consider spin-spin correlations in real space, defined as
-\begin{equation}\begin{aligned}
-	\tilde{S}_\text{flip}({\bf r}) = \frac{1}{2}\braket{S^+\left({\bf r}_c + {\bf r}\right)S^-\left({\bf r}_c\right) + \text{h.c.}}~,
-\end{aligned}\end{equation}
-where \(S^-(\nu) = c^\dagger(\nu,\downarrow)c(\nu, \uparrow)\) and \(S^+ = \left( S^- \right)^\dagger \) are the spin-flip operators, and the expectation value is in the ground state \(\ket{\Psi_\text{gs}}\).
-We replace the full ground state with the ground state of the auxiliary model at \({\bf r}_c\):
-\begin{equation}\begin{aligned}
-	\tilde{S}_\text{flip}({\bf r}) = \frac{1}{2}\braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf d} + {\bf r}\right)S^-\left({\bf d}\right) + \text{h.c.} | \psi_\text{gs}({\bf r}_c)}~,
-\end{aligned}\end{equation}
-where we have interpereted the site at \({\bf r}_c\) as the impurity site \({\bf d}\) for the auxiliary model in question.
-The final expression therefore involves the spin-flip correlation function between the impurity site and a site in the bath, within a single auxiliary model.
-
-Charge correlations involve flips of the charge isospin states (instead of the spin states), and are defined as
-\begin{equation}\begin{aligned}
-	\tilde{C}_\text{flip}({\bf r}) = \frac{1}{2}\braket{C^+\left({\bf r}_c + {\bf r}\right)C^-\left({\bf r}_c\right) + \text{h.c.}}~,
-\end{aligned}\end{equation}
-where \(C^-(\nu) = c(\nu,\downarrow)c(\nu, \uparrow)\) and \(C^+ = \left( C^- \right)^\dagger \). Making identical substitutions here gives
-\begin{equation}\begin{aligned}
-	\tilde{C}_\text{flip}({\bf r}) = \frac{1}{2}\braket{\psi_\text{gs}({\bf r}_c) | C^+\left({\bf d} + {\bf r}\right)C^-\left({\bf d}\right) + \text{h.c.} | \psi_\text{gs}({\bf r}_c)}~.
-\end{aligned}\end{equation}
-
-One can also look at \(k-\)space correlations, of the spin or charge kind:
-\begin{equation}\begin{aligned}
-	\tilde{S}_\text{flip}({\bf K}_1, {\bf K}_2) &= \frac{1}{2}\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right) + \text{h.c.}}~,\\
-	\tilde{C}_\text{flip}({\bf K}_1, {\bf K}_2) &= \frac{1}{2}\braket{C^+\left({\bf K}_1\right)C^-\left({\bf K}_2\right) + \text{h.c.}}~.
-\end{aligned}\end{equation}
-We again consider the spin-flip correlation first.
-In order to introduce the impurity site, we rewrite the expectation values sum of all coherent scattering processes involving the impurity site and the two \(k-\)states.
-Using eq.~\ref{eigenstateProposal}, we express the correlation in terms of a single auxiliary model:
-\begin{equation}\begin{aligned}
-	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} \\
-	&= \frac{1}{N}\sum_{{\bf r}_d}\braket{\psi_\text{gs}({\bf r}_d) | S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_d)}~,
-\end{aligned}\end{equation}
-where \({\bf r}_d\) is the location of the impurity site, and we average over the correlation values calculated over all possible auxiliary models.
-Assuming translation invariance, the static correlation values should be equal on every auxiliary model, allowing us to replace the average with the value at the reference origin \({\bf r}_c\):
-\begin{equation}\begin{aligned}\label{correlationAuxiliary}
-	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} = \braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}~.
-\end{aligned}\end{equation}
-Using the definition \(S^+(\nu) = c^\dagger_{\nu \uparrow} c_{nu \downarrow}\), one can Fourier transform the fermionic operators in eq.~\ref{correlationAuxiliary},
-\begin{equation}\begin{aligned}
-	c_{{\bf k}\sigma} = \sum_{\bf r} e^{i {\bf k}\cdot{\bf r}} c_{{\bf r}\sigma},
-\end{aligned}\end{equation}
-and retain the only impurity site contribution \({\bf r}={\bf r}_c\) in order to introduce the dynamics of the impurity site. Carrying this out for one and two fermionic operators gives
-\begin{equation}\begin{aligned}\label{correlationAuxiliaryProcess}
-	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} \\
-	&= \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf r}_c \uparrow} c_{{\bf K}_1 \downarrow} S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}\\
-	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf K}_1 \uparrow} c_{{\bf r}_c \downarrow} S^-\left({\bf K}_2\right) | \psi_\text{gs}({\bf r}_c)}\\
-	&+ \braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf K}_1\right) c^\dagger_{{\bf r}_c \downarrow} c_{{\bf K}_2 \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
-	&+ \braket{\psi_\text{gs}({\bf r}_c) | S^+\left({\bf K}_1\right) c^\dagger_{{\bf K}_2 \downarrow} c_{{\bf r}_c \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
-	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf r}_c \uparrow} c_{{\bf K}_1 \downarrow} c^\dagger_{{\bf r}_c \downarrow} c_{{\bf K}_2 \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
-	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf r}_c \uparrow} c_{{\bf K}_1 \downarrow} c^\dagger_{{\bf K}_2 \downarrow} c_{{\bf r}_c \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
-	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf K}_1 \uparrow} c_{{\bf r}_c \downarrow} c^\dagger_{{\bf r}_c \downarrow} c_{{\bf K}_2 \uparrow} | \psi_\text{gs}({\bf r}_c)}\\
-	&+ \braket{\psi_\text{gs}({\bf r}_c) | c^\dagger_{{\bf K}_1 \uparrow} c_{{\bf r}_c \downarrow} c^\dagger_{{\bf K}_2 \downarrow} c_{{\bf r}_c \uparrow} | \psi_\text{gs}({\bf r}_c)}~.
-\end{aligned}\end{equation}
-We haven't considered three-particle dynamics on the impurity site because those would involve only one momentum state and would hence be incoherent for the other momentum state; for the same reason, certain two-particle terms have also been ignored.
-Henceforth, we replace the index \({\bf r}_c\) with \(d\), indicating that it is the position of the impurity site.
-By introducing the off-site spin operator \(S^+_{\nu_1,\nu_2} = c^\dagger_{\nu_1 \uparrow} c_{\nu_2 \downarrow}\) that flips an effective spin across multiple orbitals, we can express eq.~\ref{correlationAuxiliaryProcess} in a more illuminating form:
-\begin{equation}\begin{aligned}
-	&\braket{S^+\left({\bf K}_1\right)S^-\left({\bf K}_2\right)} =\\
-	& \braket{(S^+_{d, {\bf K}_1} + S^+_{{\bf K}_1,d}) S^-({\bf K}_2) + S^+({\bf K}_1) (S^-_{d, {\bf K}_2} + S^-_{{\bf K}_2, d})} \\
-	&+ \braket{S^+_{d, {\bf K}_1} (S^-_{{\bf K}_2, d} + S^-_{d, {\bf K}_2}) + (S^+_{{\bf K}_1, d} + S^+_{{\bf K}_1, d}) S^-_{{\bf K}_2, d}}~.
-\end{aligned}\end{equation}
-This allows us to visualise the \(k-\)space correlation function through various scattering processes within the auxiliary model: the net correlation between \({\bf K}_1\) and \({\bf K}_2\) occur either through (i) simultaneous and opposite flips of the spin on one momentum state and the shared spin on the impurity site and another momentum state, or (ii) the simultaneous flips of spins shared between all three members.
-
-The charge correlations can be treated exactly the same way.
-We quote the final result here, in terms of the off-site charge operators \(C^+_{\nu_1, \nu_2} = c^\dagger_{\nu_1 \uparrow} c^\dagger_{\nu_2 \downarrow}\) :
-\begin{equation}\begin{aligned}
-	&\left<C^+({\bf K}_1) C^-({\bf K}_2)\right> = \\
-	& \braket{(C^+_{d, {\bf K}_1} + C^+_{{\bf K}_1,d}) C^-({\bf K}_2) + C^+({\bf K}_1) (C^-_{d, {\bf K}_2} + C^-_{{\bf K}_2, d})}\\
-	&+ \braket{C^+_{d, {\bf K}_1} (C^-_{{\bf K}_2, d} + C^-_{d, {\bf K}_2}) + (C^+_{{\bf K}_1, d} + C^+_{{\bf K}_1, d}) C^-_{{\bf K}_2, d}}~.
-\end{aligned}\end{equation}
+\section{Equal-Time Ground State Correlators}\label{staticCorr}
+Properties of the ground state can be probed using static correlation functions that are expectation values of operators that propagate excitations.
+We will consider general correlations, in real and momentum space.
+\subsection{Real-space correlation functions}
+We first consider a real-space operator \(\mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r})\) that quantifies the presence of correlations over a distance \({\bf \Delta}\).
+The correlation function itself is given by the expectation value of this operator in the ground state:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_1 + {\bf r}^\prime + {\bf r}_c + {\bf r}\right)  | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_1 + {\bf r}_c + {\bf r}\right)} e^{-i{\bf k}_0\cdot\left({\bf r}_1 - {\bf r}_2\right)}~,
+\end{aligned}\end{equation}
+where \({\bf r}_1\) and \({\bf r}_1 + {\bf r}^\prime\) are the positions of the incoming and outgoing auxiliary model states, relative to \({\bf r}_c + {\bf r}\), and \({\bf k}_0\) is the crystal momentum of the ground state (which we will immediately set to zero).
+In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
+Substituting this appropriately for both the auxiliary model states gives:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_1 + {\bf r}^\prime + {\bf r}\right) \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) T^\dagger\left({\bf r}_1 + {\bf r}\right) | \psi_\text{gs}\left({\bf r}_c\right)}\\
+								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}^\prime\right) \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
+								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+As a final cosmetic change, we transform \({\bf r}_1 \to -{\bf r}\):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r},{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+Like in the Greens function calculation, we now consider the various kinds of contributions separately.
+
+\subsubsection{Intra-auxiliary model contributions: \({\bf r}^\prime = 0\)}
+These terms describe excitations that start and propagate within the same auxiliary model, upto a distance \({\bf \Delta}\):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+For the excitations that exist purely in the conduction bath \(({\bf r} \neq {\bf r}_c)\), the excitation operators must be suitably modified (see the arguments around eq.~\ref{tmatrix}) in order to incorporate Kondo screening.
+The modified excitation operators are generally defined as
+\begin{equation}\begin{aligned}\label{operatorTmatrix}
+\mathcal{\tilde O} = \mathcal{O} \left[\sum_{\sigma}\left(c^\dagger_{d\sigma} + \text{h.c.}\right) + S_d^+ + \text{h.c.}\right] ~.
+\end{aligned}\end{equation}
+The operator multiplying the old correlation operator represents all possible excitations of the impurity site, and ensure that the bath and impurity excitation processes take place in correlation.
+With this modified operator, this class of correlation functions can be written as
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r} }\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r})\mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+
+\subsubsection{Inter-auxiliary model contributions: \({\bf r}^\prime \neq 0\)}
+These are the most non-local contributions, and involve excitations that connect different auxiliary models:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}^\prime \neq 0}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r})\mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+
+\subsection{Momentum-space correlation functions}
+We now consider momentum space correlations, through a general operator \(\mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1)\):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+Note that \(\mathcal{O}\) itself is a two-particle operator.
+To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_2\right)  | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_1\right)}~,
+\end{aligned}\end{equation}
+where \({\bf r}_1\) and \({\bf r}_2 \) are the positions of the incoming and outgoing auxiliary model states.
+In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
+Substituting this appropriately for both the auxiliary model states gives:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_c\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) T^\dagger\left({\bf r}_1 - {\bf r}_c\right) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+In order to simplify the translation operators, we can use eq.~\ref{translationOnField}.
+For that, we would need to know whether the operator \(\mathcal{O}\) involves the net transfer of momentum.
+If \(\mathcal{O}({\bf k})\) commutes with the total number operator \(n_{\bf k} = \sum_\sigma n_{{\bf k},\sigma}\), there is no momentum transfer.
+Examples of such operators are spin operators, \(S_{\alpha\beta}({\bf k}) \equiv c^\dagger_{{\bf k \alpha}}c_{{\bf k}\beta}\), and density operators \(n_{{\bf k}\alpha}\).
+If \(\mathcal{O}({\bf k})\) does not commute with \(n_{\bf k}\), there is a net transfer of momentum, and one such operator would be the charge isospin operator \(C^+({\bf k}) = c^\dagger_{{\bf k}\uparrow}c^\dagger_{{\bf k}\downarrow}\).
+For the first kind of operators, we have \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = \mathcal{O}({\bf k})\), while the for the latter, we get \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = e^{-{\bf a}\cdot{\bf 2k}}\mathcal{O}({\bf k})\), where \(2{\bf k}\) represents the momentum being transferred by the operator.
+We consider the two cases separately.
+
+\subsubsection{Momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] = 0\)}
+For these operators, the expression for the correlation gives
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
+										 &=\sum_{{\bf r},{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+To obtain the last form, we defined \({\bf \Delta}={\bf r}_2 - {\bf r}_1\) as the distance between the incoming and outgoing auxiliary model states, and preformed the sum over the free variable \({\bf r}_1\) to cancel out the factor of \(1/N\).
+Just like before, this expression can be decomposed into a term that involves a single auxiliary model and other terms that involve two distinct auxiliary models.
+
+\subsubsection{Non-momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] \neq 0\)}
+This class of operators incur an additional phase factor of \(e^{-{\bf a}\cdot{\bf 2k}}\) when the translation operators are translated across them:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}e^{2i\left( {\bf r}_1 - {\bf r}_c \right) \cdot \left( {\bf k}_1 - {\bf k}_2 \right)} \\
+										 &= \delta_{{\bf k}_1, {\bf k}_2}\sum_{{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+For this expression, we again defined \({\bf \Delta}\) similar to before, and carried out the sum of \({\bf r}_1\) involving the exponential to obtain a factor of \(N \delta_{{\bf k}_1, {\bf k}_2}\).
+The Kronecker delta factor is a manifestation of translational invariance and the associated total momentum conservation.
+
+As it stands, operators like \(\mathcal{O}({\bf k}_1)\) act purely on the conduction bath degrees of freedom.
+In order to incorporate impurity-bath correlation effects, we modify these operators using the appropriate \(T-\)matrices, by employing eq.~\ref{operatorTmatrix}.
+The final computations are carried out using these modified operators.
 
 \section{Entanglement measures}
-
-Given the \(T=0\) density matrix \(\tilde\rho_\text{gs} = \ket{\Psi}_\text{gs}\bra{{\Psi}_\text{gs}}\) of the lattice model and a fermionic two-level subspace \(\nu\), the reduced density matrix for the {\it complement} subspace of \(\nu\) can be obtained by tracing over the configurations of that subspace
-\begin{equation}\begin{aligned}
-	&\overline\rho_{\nu} \\
-	&= \sum_{n_{\nu}=0,1}\braket{n_{\nu}|\tilde\rho_\text{gs}|n_{\nu}}\\
-	&= \rho_{\nu}^{(0,0)} + \rho_{\nu}^{(1,1)}~,
-\end{aligned}\end{equation}
-where \(\ket{n_{\nu}}\) is a state in the Hilbert space of \(\nu\) with fixed occupancy that can be 0 or 1, such that \(c^\dagger_\nu\ket{0}=\ket{1}\) and \(c_\nu\ket{1}=\ket{0}\).
-The entanglement entropy of the subspace \(\nu\) is then obtained straightforwardly from the eigenvalues of \(\overline\rho_{\nu}\), also known as the entanglement spectrum for this subspace:
-\begin{equation}\begin{aligned}
-	\tilde S_\text{EE}(\nu) = -\text{Tr}\left[\overline\rho_{\nu}\ln \overline\rho_{\nu}\right]  ~.
-\end{aligned}\end{equation}
-
-In order to facilitate expressing this in terms of auxiliary model quantities, we rewrite the total density matrix in the following manner:
-\begin{equation}\begin{aligned}
-	\tilde\rho_\text{gs} = \sum_{n_\nu=0,1}\sum_{n_\nu^\prime=0,1}\ket{n_{\nu^\prime}}\bra{n_{\nu}}\otimes\rho_\nu^{(n_\nu, n_\nu^\prime)}~.
-\end{aligned}\end{equation}
-which then allows a convenient form for the reduced density matrix in a block-diagonal form:
-\begin{equation}\begin{aligned}
-	\overline\rho_{\nu} = c^\dagger_\nu \tilde\rho_\text{gs} c_\nu + n_\nu \tilde\rho_\text{gs} n_\nu = \begin{pmatrix} 0 & 0 \\ 0 & \rho_{\nu}^{(0,0)} + \rho_{\nu}^{(1,1)} \end{pmatrix} ~.
-\end{aligned}\end{equation}
-Even though the matrix on the right has an additional zero block that should technically not be present in \(\overline\rho_{\nu}\), it does not make any difference for our purposes since that block only contributes zero eigenvalues which do not alter the entanglement entropy.
-
-We first consider entanglement in real-space, setting the subspace \(\nu\) to \(\nu=({\bf r}_c,\sigma)\), where \({\bf r}_c\) is the previously chosen reference point on the lattice.
-The expression for the enlarged \(\overline\rho_{\nu}\) becomes
-\begin{equation}\begin{aligned}
-	\overline\rho_{{\bf r}_c,\sigma} = c^\dagger_{{\bf r}_c,\sigma} \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}} c_{{\bf r}_c,\sigma} + n_{{\bf r}_c,\sigma} \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}} n_{{\bf r}_c,\sigma}~.
-\end{aligned}\end{equation}
-As has been done before, we simplify \(\Psi_\text{gs}\) by retaining only the uniform part of the eigenstate at \({\bf r}_c\) (following eq.~\ref{eigenstateUniform}), leading to the expression
-\begin{equation}\begin{aligned}
-	\overline\rho_{{\bf r}_c,\sigma} = c^\dagger_{{\bf r}_c,\sigma} \rho_\text{gs}({\bf r}_c) c_{{\bf r}_c,\sigma} + n_{{\bf r}_c,\sigma} \rho_\text{gs}({\bf r}_c) n_{{\bf r}_c,\sigma}
-\end{aligned}\end{equation}
-where \(\rho_\text{gs}({\bf r}_c) = \ket{\psi_\text{gs}({\bf r}_c)}\bra{\psi_\text{gs}({\bf r}_c)}\) is the \(T=0\) density matrix for the auxiliary model at \({\bf r}_c\).
-This is simply the reduced density matrix of the impurity site for the auxiliary model at \({\bf r}_c\), leading to the following simple relation for the local entanglement entropy of the lattice model:
-\begin{equation}\begin{aligned}
-	\tilde S_\text{EE}({\bf r}_c;\sigma) = S_\text{EE}(d;\sigma)~,
-\end{aligned}\end{equation}
-where \(S_\text{EE}(d)\) is the entanglement entropy of the impurity site.
-
-We might also be interested in entanglement entropy of subsystems with multiple sites.
-The reduced density matrix for the composite subsystem of the sites \({\bf r}_c\) and \({\bf r}_c + {\bf r}\) is obtained by tracing out the site \({\bf r}_c + {\bf r}\) from \(\overline\rho_{{\bf r}_c,\sigma}\).
-That then gives
-\begin{equation}\begin{aligned}
-	\overline\rho_{({\bf r}_c, {\bf r}_c + {\bf r}),\sigma} = c^\dagger_{{\bf r}_c + {\bf r},\sigma} \overline\rho_{{\bf r}_c,\sigma} c_{{\bf r}_c + {\bf r},\sigma} + n_{{\bf r}_c + {\bf r},\sigma} \overline\rho_{{\bf r}_c,\sigma} n_{{\bf r}_c + {\bf r},\sigma}~,
-\end{aligned}\end{equation}
-leading to the expression
-\begin{equation}\begin{aligned}
-	\tilde S_\text{EE}\left({\bf r}_c, {\bf r}_c + {\bf r};\sigma\right) = S_\text{EE}(d, {\bf r};\sigma)~,
-\end{aligned}\end{equation}
-where \(S_\text{EE}(d, r)\) is the entanglement entropy of the impurity site and the conduction bath site at a distance \({\bf r}\) from it.
-
-We now come to the \(k-\)space entanglement entropy, defined by \(\nu = ({\bf K},\sigma)\) and the reduced density matrix
-\begin{equation}\begin{aligned}
-	\overline\rho_{{\bf K},\sigma} = c^\dagger_{{\bf K},\sigma} \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}} c_{{\bf K},\sigma} + n_{{\bf K},\sigma} \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}} n_{{\bf K},\sigma}~.
-\end{aligned}\end{equation}
-We again replace the states with the uniform part, while we expand the operators on one side of the density matrix in a Fourier series in order to extract an impurity site operator:
-\begin{equation}\begin{aligned}
-	\overline\rho_{{\bf K},\sigma} &= \frac{1}{2}\left[c^\dagger_{{\bf K},\sigma} \rho_\text{gs}({\bf r}_c) c_{{\bf r}_c,\sigma} + n_{{\bf K},\sigma} \rho_\text{gs}({\bf r}_c) n_{{\bf r}_c,\sigma} \right.\\
-	&+ \left. c^\dagger_{{\bf r}_c,\sigma} \rho_\text{gs}({\bf r}_c) c_{{\bf K},\sigma} + n_{{\bf r}_c,\sigma} \rho_\text{gs}({\bf r}_c) n_{{\bf K},\sigma}\right. ~.
-\end{aligned}\end{equation}
-The eigenvalues of this operator can be used to compute the entanglement entropy of the state \({\bf K}\sigma\). If we define an {\it off-site} entanglement entropy 
-\begin{equation}\begin{aligned}
-	S^\prime_{\text{EE}}(\nu_1,\nu_2) = -\text{Tr}\left[\rho_{\nu_1,\nu_2}\ln \rho_{\nu_1,\nu_2}\right]
-\end{aligned}\end{equation}
-with 
-\begin{equation}\begin{aligned}
-	\rho_{\nu_1,\nu_2} = (c^\dagger_{\nu_1} \tilde\rho_\text{gs} c_{\nu_2} + n_{\nu_1} \tilde\rho_\text{gs} n_{\nu_2}) + \text{h.c.}~,
-\end{aligned}\end{equation}
-we can frame the expression for the \(k-\)space entanglement entropy in terms of the auxiliary model off-site entanglement entropy:
-\begin{equation}\begin{aligned}
-	S_\text{EE}({\bf K};\sigma) = S^\prime_\text{EE}\left(d, {\bf K};\sigma\right) 
-\end{aligned}\end{equation}
-
-Using the same approach as that for the real space case, the reduced density matrix for two \(k-\)states is again obtained by tracing out the second \(k-\)state from this density matrix:
-\begin{equation}\begin{aligned}
-	\overline\rho_{({\bf K}_1, {\bf K}_2),\sigma} &= \frac{1}{2}\left[c^\dagger_{{\bf K}_2,\sigma} \overline\rho_{{\bf K}_1,\sigma} c_{{\bf r}_c,\sigma} + n_{{\bf K}_2,\sigma} \overline\rho_{{\bf K}_1,\sigma} n_{{\bf r}_c,\sigma} \right.\\
-	&+ \left. c^\dagger_{{\bf r}_c,\sigma} \overline\rho_{{\bf K}_1,\sigma} c_{{\bf K}_2,\sigma} + n_{{\bf r}_c,\sigma} \overline\rho_{{\bf K}_1,\sigma} n_{{\bf K}_2,\sigma}\right] ~.
-\end{aligned}\end{equation}
-This straightforwardly leads to the relation
-\begin{equation}\begin{aligned}
-	S_\text{EE}({\bf K}_1,{\bf K}_2;\sigma) = S^\prime_\text{EE}\left(d, {\bf K}_1;\sigma\right) + S^\prime_\text{EE}\left(d, {\bf K}_2;\sigma\right)
-\end{aligned}\end{equation}
+In order to relate bipartite measures of entanglement (such as the entanglement entropy and mutual information) across the tiling algorithm, we will express the matrix elements of an arbitrary reduced density matrix (RDM) in terms of generalised correlation functions.
+Since these correlation functions can always be computed using the algorithm provided in the previous section, this suffices to compute the RDM using auxiliary model calculations.
+If the RDM is known, other bipartite measures can be easily calculated.
+
+We consider the \(T=0\) density matrix, \(\tilde\rho_\text{gs} = \ket{\Psi}_\text{gs}\bra{{\Psi}_\text{gs}}\) of the lattice model, and a division of the total degrees of freedom (real or momentum space) into two sets \(A\) and \(B\).
+If basis set for the two subsystems are \(\left\{ \ket{A_i} \right\} \) and \(\left\{ B_j \right\} \), the ground state can be written as
+\begin{equation}\begin{aligned}
+	\ket{\Psi}_\text{gs} = \sum_{i,j}C_{i,j}\ket{A_i}\ket{B_j}~.
+\end{aligned}\end{equation}
+Tracing out the states of subsystem B leads to the RDM for subsystem A:
+\begin{equation}\begin{aligned}
+	\tilde \rho^{(A)} = \sum_k\braket{B_k | \rho | B_k} = \sum_{{i_1},{i_2}, k}C_{{i_1},k}C^*_{{i_2},k}\ket{A_{i_1}}\bra{A_{i_2}},~~\tilde \rho^{(A)}_{{i_1},{i_2}} = \sum_k C_{{i_1},k}C^*_{{i_2},k}~.
+\end{aligned}\end{equation}
+We will now show that the product of coefficients \(C_{i,k}C^*_{j,k}\) can also be obtained through expectation value calculations of product operators in the subspace of \(A\).
+Consider the following transition operator:
+\begin{equation}\begin{aligned}
+	P^{(A)}_{i_1,i_2} = \ket{A_{i_1}}\bra{A_{i_2}}~.
+\end{aligned}\end{equation}
+The RDM elements are expectation values of this operator in the ground state:
+\begin{equation}\begin{aligned}
+	\braket{P^{(A)}_{i_1,i_2}} = \sum_k C_{{i_1},k}C^*_{{i_2},k} = \tilde \rho^{(A)}_{{i_1},{i_2}}~.
+\end{aligned}\end{equation}
+
+We now argue that these expectation values are simply correlation functions corresponding to products of local operators.
+If the subsystem \(A\) is composed of \(N_A\) one-particle Hilbert spaces \(A^{(\nu)}\), any basis state \(\ket{A_{i}}\) can be written as the product of one-particle basis states:
+\begin{equation}\begin{aligned}
+	\ket{A_i} = \otimes_{\nu=1}^{N_A}\ket{s_\nu(A_i)}~,
+\end{aligned}\end{equation}
+where \(s_\nu(A_i)\) can be 0 or 1 and represents the configuration (occupied/unoccupied) of the local degree of freedom \(A^{(\nu)}\) in the basis state \(\ket{A_i}\), and \(\ket{s_\nu(A_i)}\) is the state of \(A^{(\nu)}\) in that configuration.
+The transition operator \(P^{(A)}_{i_1,i_2}\) can therefore be written as
+\begin{equation}\begin{aligned}
+	P^{(A)}_{i_1,i_2} = \ket{s_1(A_{i_1})}\otimes\ket{s_2(A_{i_1})} \ldots\otimes\ket{s_{N_A}(A_{i_1})}\bra{s_{N_A}(A_{i_2})}\otimes\ldots\bra{s_2(A_{i_2})}\otimes\bra{s_1(A_{i_2})}~.
+\end{aligned}\end{equation}
+This can be converted into a second-quantised operator, by making the substitution:
+\begin{equation}\begin{aligned}
+	\ket{s} \to 
+	\begin{cases}
+		c^\dagger,~\text{if }s=1,\\
+		1-n,~\text{if }s=0,	
+	\end{cases}~.
+\end{aligned}\end{equation}
+As an example, for a two-qubit subspace \(A\), the transition operator \(P^{(A)}_{00,01}\) between the states \(i_1=00\) (both unoccupied) and \(i_2=01\) (only one occupied) can be expressed as
+\begin{equation}\begin{aligned}
+	P^{(A)}_{00,01} = \ket{0}_1\ket{0}_2\bra{1}_2\bra{0}_1 = (1-n_1)(1-n_2)(1-n_2)c_1 = c_1(1-n_2)~.
+\end{aligned}\end{equation}
+This means the RDM element for this subspace, at the location \((00, 01)\), is equal to the ground state expectation value of the operator \(c_1(1-n_2)\).
+The process of calculating such expectation values, within the present algorithm, has already been explained in Sec.~\ref{staticCorr}.
+Note that this allows the computation of reduced density matrix for real-space as well as momentum-space partitioning.
 
@@
 
-\section{Momentum-space picture of the MIT}
+\section{Metal-insulator transition in the Lattice Model}
+\subsection{Momentum-space picture etc etc}
 In order to understand the nature of the transition in momentum space, we employ the expression obtained in the previous sections and compute the spectral function, self-energy and correlation functions in the top right quadrant of the first Brillouin zone.
@@
 
+\subsection{Heisenberg model as a low-energy description of the insulator}
+
+In the insulating phase, the ground state of each auxiliary model hosts a decoupled local moment.
+Upon applying the tiling procedure, the lattice model ground state becomes that of the Hubbard model in the atomic limit.
+In order to lift the extensive degeneracy of the state, we will now take into consideration inter-auxiliary model virtual scattering processes that were subdominant in the metallic phase and were hence ignored.
+These one-particle scattering processes lead to the emergence of a nearest-neighbour superexchange interaction.
+
+For simplicity, we consider two impurity sites labelled \(1\) and \(2\) associated with two nearest-neighbour auxiliary models. The ground state subspace is four-fold degenerate:
+\begin{equation}\begin{aligned}
+	\ket{\Psi_L} = \left\{\ket{\sigma_1,\sigma_2}\right\}~,\quad \sigma_i = \pm 1
+\end{aligned}\end{equation}
+where \(\sigma_i\) is the spin state of site \(i\).
+This ground state is derived from the following "zeroth order" Hamiltonian that emerges in the local moment phase of the auxiliary models when all scattering processes between the impurity and conduction bath are RG-irrelevant:
+\begin{equation}\begin{aligned}
+	H_0 = -\frac{U}{2}\sum_{i=1,2}\left(n_{i \uparrow} - n_{i \downarrow}\right)^2~;
+\end{aligned}\end{equation}
+the local correlation on the impurity site becomes the largest scale in the problem in this phase and pushes the \(\ket{n_i=2}\) and \(\ket{n_i=0}\) states to high energies.
+This then defines the high-energy subspace for our calculation:
+\begin{equation}\begin{aligned}
+	\ket{\Psi_H} = \ket{C_1,C_2}~,
+\end{aligned}\end{equation}
+where \(C_i\) can take values 0 or 2, indicating that the state \(i\) is either empty or full, respectively.
+Both the double and hole states exist at a charge gap of the order of \(U/2\) above the low-energy singly-occupied subspace defined by the states \(\ket{\Psi_L}\).
+
+In order to allow virtual fluctuations that can lift the large ground state degeneracy and lower the energy, we consider (perturbatively) the effects of an irrelevant single-particle hybridisation that connects the nearest-neighbour sites.
+This perturbation Hamiltonian is therefore of the form
+\begin{equation}\begin{aligned}
+	H_t = \sum_\omega V(\omega) \mathcal{P}(\omega)~\sum_\sigma\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) ~,
+\end{aligned}\end{equation}
+where \(V(\omega)\) only acts on states at the energy scale \(\omega\); the renormalisation of \(V\) is encoded in the fact that \(V(\omega)\) is largest for the excited states and vanishes at low-energies: \(V(\omega \to 0) = 0\).
+
+In order to obtain a low-energy effective Hamiltonian for the impurity sites arising from this hybridisation, we integrate out \(H_t\) via a Schrieffer-Wolff transformation.
+This leads to the following second-order Hamiltonian:
+\begin{equation}\begin{aligned}
+	H_\text{eff} = \mathcal{P}_L H_t G\mathcal H_t \mathcal{P}_L~.
+\end{aligned}\end{equation}
+The operator \(\mathcal{P}_L\) projects onto the low-energy subspace \(\ket{\Psi_L}\) - this ensures that we remain in the low-energy subspace at the beginning and at the end of the total process.
+The Greens function \(G = (E_L - H_0)^{-1}\) incorporates the excitation energy to go from the low-energy subspace \(\ket{\Psi}_L\) (of energy \(E_L\)) to the excited subspace \(\ket{\Psi}_H\) of energy \(E_L + U/2\).
+Substituting the form of the perturbation Hamiltonian and the excitation energy into the above expression gives
+\begin{equation}\begin{aligned}\label{effHam1}
+	H_\text{eff} = \frac{V(U/2)^2}{-U/2}\sum_{\sigma,\sigma^\prime} \left[c^\dagger_{1\sigma}c_{2\sigma}c^\dagger_{2\sigma^\prime}c_{1\sigma^\prime} + c^\dagger_{2\sigma}c_{1\sigma}c^\dagger_{1\sigma^\prime}c_{2\sigma^\prime}\right] ~.
+\end{aligned}\end{equation}
+where \(V(U/2)\) is the impurity-bath hybridisation at energy scales of the order of the Mott gap, in the sense of an RG flow.
+Terms with consecutive creation or annihilation operators on the same site are prohibited because each site is singly-occupied in the ground state.
+It is now easy to cast this Hamiltonian into a more recognizable form.
+For \(\sigma^\prime=\sigma\), we get
+\begin{equation}\begin{aligned}
+	\sum_{\sigma}\delta_{\sigma,\sigma^\prime}c^\dagger_{1\sigma}c_{2\sigma}c^\dagger_{2\sigma^\prime}c_{1\sigma^\prime} = \sum_\sigma \left(n_{1\sigma} - n_{1\sigma}n_{2\sigma}\right) ~,
+\end{aligned}\end{equation}
+while \(\sigma=-\sigma^\prime=\pm 1\) gives 
+\begin{equation}\begin{aligned}
+	\sum_{\sigma}\delta_{\sigma,-\sigma^\prime}c^\dagger_{1\sigma}c_{2\sigma}c^\dagger_{2\sigma^\prime}c_{1\sigma^\prime} = -\left(S_1^+ S_2^- + \text{h.c.}\right)~.
+\end{aligned}\end{equation}
+For the latter expression, we introduced the local spin-flip operators \(S_i^\pm\). The expression above it can also be cast into spin variables, using the equations
+\begin{equation}\begin{aligned}
+	\frac{1}{2}\sum_{\sigma}n_{i\sigma} = \frac{1}{2},\\
+    \frac{1}{2}\sum_{\sigma}\sigma n_{i\sigma} = S_i^z,
+\end{aligned}\end{equation}
+where the first equation is simply the condition of half-filling at each site, and the second equation is the definition of the local spin operator in \(z-\)direction.
+Adding and subtracting the equations gives \(n_{i\sigma} = \frac{1}{2} + \sigma S_i^z\)~.
+
+Substituting everything back into eq.~\ref{effHam1} and dropping constant terms gives
+\begin{equation}\begin{aligned}
+	H_\text{eff} = 2\frac{V(U/2)^2}{U/2}\left(2S_1^z S_2^z + S_1^+S_2^- + S_1^-S_2^+\right) = J_\text{eff} {\bf S}_1\cdot{\bf S}_2~,
+\end{aligned}\end{equation}
+where the effective antiferromagnetic Heisenberg coupling is \(J_\text{eff} = \frac{8V(U/2)^2}{U}\).
+
 \clearpage
-
-\begin{widetext}
 
@@
 
-\section{Momentum-space picture of the MIT}
-% In order to understand the nature of the transition in momentum space, we employ the expression obtained in the previous sections and compute the spectral function, self-energy and correlation functions in the top right quadrant of the first Brillouin zone.
-We first show the \(k-\)space spectral functions near zero frequency, in Fig.~\ref{kspace_specfunc}.
-% \begin{figure}[htpb]
-% 	\centering
-% 	\includegraphics[width=0.8\textwidth]{tiledSF.pdf}
-% 	\caption{tiledSF.pdf}
-% 	\label{fig:tiledSF-pdf}
-% \end{figure}
-%
-% \begin{figure}[!htb]
-% \centering
-% \includegraphics[width=\textwidth]{kspace-spectral-function-all.pdf}\hspace{\fill}
-% \caption{\(k-\)space dependence of single-particle spectral function, \(A_{\vec k}(\omega \sim 0)\), at four values of the tuning parameter \(r\).
-The \(\vec k\) values are taken from the top right quadrant of the first Brillouin zone.
-In the metallic phase (\(r < r_c\)), the spectral function shows a \(k-\)dependence, indicating the presence of gapless excitations.
-Close to the transition (and beyond it), the momentum dependence gets removed and there is no spectral weight left in the infrared regime.}
-% \label{kspace_specfunc}
-% \end{figure}
-%
-% In Fig.~\ref{kspace_selfenergy}, we plot the momentum dependence of the single-particle self-energy, similar to the spectral function.
-The self-energy is flat in \(k-\)space away from the transition, consistent with the fact that the correlations are small in that regime.
-Close to the transition, the correlations pick up, and lead to a momentum-dependence of the self-energy, renormalising the Fermi liquid in the process and ultimately destroying it.
-% \begin{figure}[!htb]
-% \centering
-% \includegraphics[width=\textwidth]{kspace-imagsigma-all.pdf}\hspace{\fill}
-% \caption{\(k-\)space dependence of imaginary part of the self-energy, \(\Sigma_{\vec k}(\omega \sim 0)\), at four values of the tuning parameter \(r\).
-In the metallic phase (\(r \ll r_c\)), the self-energy is quite small, indicating that the phase consists of an uncorrelated Fermi liquid.
-It increases close to the transition (and beyond it).}
-% \label{kspace_selfenergy}
-% \end{figure}
-%
-% In Figs.~\ref{spin_kspace},\ref{charge_kspace} and \ref{pair_kspace}, we show the momentum dependence of two-particle correlation functions.
-In every figure, each panel shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
-Moving from the left panel to the right is equivalent to moving upwards in the top right quadrant of the first Brillouin zone.
-In each panel, moving upwards amounts to tuning the system towards the transition.
-The spin-spin correlations (in Fig.~\ref{spin_kspace}) are large near the \(\vec k = \left( 0,0 \right) \) point, presumably because of the dominance of the Kondo cloud at long wavelengths.
-They vanish in the local moment phase (flat blue region near the top).
-The charge and pairing correlations (Figs.~\ref{charge_kspace} and \ref{pair_kspace}) disappear as the system moves into the Kondo regime, but reappear exactly at the transition.
-This is tied to the non-Fermi liquid theory at the QCP, as seen in the auxiliary model.
-% \begin{figure}[!htb]
-% \centering
-% \includegraphics[width=\textwidth]{spin_rspace_all.pdf}
-% \caption{Momentum dependence of spin-spin correlation \(\left<\vec{S}_{-\vec k}\cdot\vec{S}_{\vec k} \right>\).
-Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
-Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone.
-In each figure, moving upwards amounts to tuning the system towards the transition.
-The flat blue region at the top is the local moment phase, void of any non-local correlations.}
-% \label{spin_kspace}
-% \end{figure}
-%
-% \begin{figure}[!htb]
-% \centering
-% \includegraphics[width=\textwidth]{charge_rspace_all.pdf}
-% \caption{Momentum dependence of charge-charge correlation \(\left<\vec{C}_{-\vec k}\cdot\vec{C}_{\vec k} \right>\), where \(\vec C\) is the charge isospin associated with the doublet formed by the doublon and holon states.
-Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
-Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone.
-In each figure, moving upwards amounts to tuning the system towards the transition.
-The flat blue region at the top is the local moment phase, void of any non-local correlations.}
-% \label{charge_kspace}
-% \end{figure}
-%
-% \begin{figure}[!htb]
-% \includegraphics[width=\textwidth]{pair_rspace_all.pdf}
-% \caption{Momentum dependence of pairing correlation \(\left<c^\dagger_{-k\uparrow}c^\dagger_{-k\downarrow}c_{k\downarrow}c_{k\uparrow}\right>\).
-Each frame shows the variation along a specific horizontal cut \(k_y=\text{constant}\), as a function of \(r\).
-Moving from the left figure to the right figure is equivalent to moving upwards in the top right quadrant of the first Brillouin zone.
-In each figure, moving upwards amounts to tuning the system towards the transition.
-The flat blue region at the top is the local moment phase, void of any non-local correlations.}
-% \label{pair_kspace}
-% \end{figure}
-%
-% \begin{figure}[!htb]
-% \includegraphics[width=\textwidth]{vne_kspace_all.pdf}
-% \caption{Momentum dependence of \(k-\)space von Neumann entanglement entropy \(S_\text{EE}(\vec k)\).
-The four frames (from the left) show the variation in entanglement of a \(k-\)space in the \(k_x-k_y\) plane as the transition parameter \(r\) is tuned through the metal-insulator transition.
-\(r/r_c=0.5\) represents a very weakly correlated metal, \(r/r_c=0.8,0.9\) represents a highly correlated metal in the Kondo phase of the auxiliary model, and \(r/r_c \sim 1\) represents the non-Fermi liquid metal formed at the transition.}
-% \label{entanglement_kspace}
-% \end{figure}
-%
-% \begin{figure}[!htb]
-% \includegraphics[width=\textwidth]{mutinfo_kspace_all.pdf}
-% \caption{Momentum dependence of \(k-\)space mutual information \(I_2(\vec k: -\vec k)\).
-The four frames (from the left) show the variation in entanglement between the \(\vec k\) and \(-\vec k\) states in the \(k_x-k_y\) plane as the transition parameter \(r\) is tuned through the metal-insulator transition.
-\(r/r_c=0.5\) represents a very weakly correlated metal, \(r/r_c=0.8,0.9\) represents a highly correlated metal in the Kondo phase of the auxiliary model, and \(r/r_c \sim 1\) represents the non-Fermi liquid metal formed at the transition.}
-% \label{mutinfo_kspace}
-% \end{figure}
-%
-% {\color{blue} In order to provide a second way of visualising these correlations, we have provided some videos that show their variation in the \(k_x-k_y\) plane as a function of \(r/r_c\).
-The videos for the spin-spin correlation and the pairing correlations are named ``ss\_rspace.gif" and ``pairing\_rspace.gif", respectively.
-Each frame of the video shows a colourmap of the correlation in the top right quadrant of the first Brillouin zone, at a {\it specific value of \(r\)}.
-The movie then shows the {\it evolution of this \(k-\)space colourmap} as \(r\) is tuned towards and into the transition.}
-
 \section{Emergence of effectively pseudogapped Anderson model at the MIT}
@@
 
-\end{widetext}
 \bibliography{tilingProject}

### 2025-02-10 TilingProjectDraft/tilingProject.tex
fixed issue of specfunc operators becoming stale

@@
 \begin{equation}\begin{aligned}\label{effHam1}
-	H_\text{eff} = \frac{V(U/2)^2}{-U/2}\sum_{\sigma,\sigma^\prime} \left[c^\dagger_{1\sigma}c_{2\sigma}c^\dagger_{2\sigma^\prime}c_{1\sigma^\prime} + c^\dagger_{2\sigma}c_{1\sigma}c^\dagger_{1\sigma^\prime}c_{2\sigma^\prime}\right] ~.
-\end{aligned}\end{equation}
-where \(V(U/2)\) is the impurity-bath hybridisation at energy scales of the order of the Mott gap, in the sense of an RG flow.
+	H_\text{eff} = \frac{V_H^2}{-U/2}\sum_{\sigma,\sigma^\prime} \left[c^\dagger_{1\sigma}c_{2\sigma}c^\dagger_{2\sigma^\prime}c_{1\sigma^\prime} + c^\dagger_{2\sigma}c_{1\sigma}c^\dagger_{1\sigma^\prime}c_{2\sigma^\prime}\right] ~.
+\end{aligned}\end{equation}
+where \(V_H \equiv V(\omega \to U/2)\) is the impurity-bath hybridisation at energy scales of the order of the Mott gap, in the sense of an RG flow.
 Terms with consecutive creation or annihilation operators on the same site are prohibited because each site is singly-occupied in the ground state.
@@
 \begin{equation}\begin{aligned}
-	H_\text{eff} = 2\frac{V(U/2)^2}{U/2}\left(2S_1^z S_2^z + S_1^+S_2^- + S_1^-S_2^+\right) = J_\text{eff} {\bf S}_1\cdot{\bf S}_2~,
-\end{aligned}\end{equation}
-where the effective antiferromagnetic Heisenberg coupling is \(J_\text{eff} = \frac{8V(U/2)^2}{U}\).
+	H_\text{eff} = 2\frac{V_H^2}{U/2}\left(2S_1^z S_2^z + S_1^+S_2^- + S_1^-S_2^+\right) = J_\text{eff} {\bf S}_1\cdot{\bf S}_2~,
+\end{aligned}\end{equation}
+where the effective antiferromagnetic Heisenberg coupling is \(J_\text{eff} = \frac{8V_H^2}{U}\).
 

### 2025-02-10 numerics/caller.jl

@@ -1,7 +1,7 @@
 using Distributed, Random
 
 if length(Sys.cpu_info()) > 10 && nprocs() == 1
-    addprocs(10)
+    addprocs(8)
 end
 @everywhere using LinearAlgebra, CSV, JLD2, FileIO, CodecZlib
 
@@ -27,6 +27,7 @@ NiceValues(size_BZ) = Dict{Int64, Vector{Float64}}(
                          49 => -1.0 .* [0, 4.1, 8.19, 8.55, 8.77, 8.8] ./ size_BZ,
                          57 => -1.0 .* [0, 5., 10.2, 10.6, 10.852] ./ size_BZ,
                          69 => -1.0 .* [0, 6., 12.5, 13.1, 13.34, 13.4] ./ size_BZ,
+                         77 => -1.0 .* [0., 14.04, 14.5, 14.99] ./ size_BZ,
                         )[size_BZ]
 transitionValues(size_BZ) = Dict{Int64, Float64}(
                          13 => -1.0 * 1.6 / size_BZ,
@@ -36,6 +37,7 @@ transitionValues(size_BZ) = Dict{Int64, Float64}(
                          49 => -1.0 * 8.77 / size_BZ,
                          57 => -1.0 * 10.852 / size_BZ,
                          69 => -1.0 * 13.34 / size_BZ,
+                         77 => -1.0 * 14.99 / size_BZ,
                         )[size_BZ]
 
 get_x_arr(size_BZ) = collect(range(K_MIN, stop=K_MAX, length=size_BZ) ./ pi)
@@ -67,7 +69,7 @@ function ScattProb(
     )
     x_arr = get_x_arr(size_BZ)
     W_val_arr = NiceValues(size_BZ)
-    @time kondoJArrays, dispersion = RGFlow(W_val_arr, size_BZ; loadData=true)
+    @time kondoJArrays, dispersion = RGFlow(W_val_arr, size_BZ; loadData=loadData)
     saveNames = String[]
     results = [ScattProb(size_BZ, kondoJArrays[W_val], dispersion)[2] for W_val in W_val_arr]
     quadrantResults = [result[filter(p -> all(map1DTo2D(p, size_BZ) .≥ 0), 1:size_BZ^2)] 
@@ -99,7 +101,7 @@ function KondoCouplingMap(
         size_BZ::Int64;
     )
     x_arr = get_x_arr(size_BZ)
-    W_val_arr = NiceValues(size_BZ)[[1, 3, 5]]
[…]

### 2025-02-10 numerics/source/probes.jl

@@ -486,7 +486,6 @@ function LatticeKspaceDOS(
     fixedContrib = [freqValues |> length |> zeros for _ in calculatePoints]
 
     onlyCoeffs = ["Sd+", "Sd-"]
-    specDictSet = specFuncDictFunc(length(SWIndices), (3, 4))
 
     function SpectralCoeffsAtKpoint(
             kspacePoint::Int64,
@@ -498,6 +497,7 @@ function LatticeKspaceDOS(
                            ]
         sortedPoints = SWIndices[sortperm(distancesFromPivot)]
         
+        specDictSet = specFuncDictFunc(length(SWIndices), (3, 4))
         if hamiltDetails["kondoJArray"][sortedPoints[1], sortedPoints] .|> abs |> maximum == 0 
             delete!(specDictSet, "Sd+")
             delete!(specDictSet, "Sd-")
@@ -534,7 +534,7 @@ function LatticeKspaceDOS(
         end
     end
 
-    centerSpecFuncArr, localSpecFunc, standDev = SpecFuncVariational(specCoeffsBZone, freqValues, targetHeight, 1e-3; 
+    centerSpecFuncArr, localSpecFunc, standDevFinal = SpecFuncVariational(specCoeffsBZone, freqValues, targetHeight, 1e-3; 
                                    degenTol=1e-10, silent=false, 
                                    broadFuncType="lorentz", fixedContrib=fixedContrib,
                                    standDevGuess=standDevGuess,
@@ -558,7 +558,7 @@ function LatticeKspaceDOS(
     results = PropagateIndices(calculatePoints, results, size_BZ, 
                                  oppositePoints)
 
-    return specFuncKSpace, localSpecFunc, standDev, results
+    return specFuncKSpace, localSpecFunc, standDevFinal, results
 end
 
 

### 2025-02-21 TilingProjectDraft/tilingProject.tex
added new entanglement analytics

@@
 \end{aligned}\end{equation}
+With an eye towards introducing the impurity operators into the correlations, we insert a complete basis defined by the eigenstates \(\left\{\ket{\psi_n\left({\bf r}_c\right)}\right\} \) of the auxiliary model into the expression:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\sum_{n}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \ket{\psi_n\left({\bf r}_c\right)}\bra{\psi_n\left({\bf r}_c\right)} \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+
 For the excitations that exist purely in the conduction bath \(({\bf r} \neq {\bf r}_c)\), the excitation operators must be suitably modified (see the arguments around eq.~\ref{tmatrix}) in order to incorporate Kondo screening.
@@
 \begin{equation}\begin{aligned}\label{operatorTmatrix}
-\mathcal{\tilde O} = \mathcal{O} \left[\sum_{\sigma}\left(c^\dagger_{d\sigma} + \text{h.c.}\right) + S_d^+ + \text{h.c.}\right] ~.
-\end{aligned}\end{equation}
+	\mathcal{\tilde O}({\bf r}) = \mathcal{O}({\bf r})\mathcal{O}^\dagger(d) \mathcal{P}_\text{gs} ~,
+\end{aligned}\end{equation}
+where \(\mathcal{O}^\dagger(d)\) is the hermitian conjugate of the correlation operator \(\mathcal{O}\), but applied on the impurity sites.
+This therefore constitutes a time-reversed scattering process on the impurity site relative to the process in the bath.
+The operator \(\mathcal{P}_\text{gs}\) projects onto the ground state of the auxiliary model, since we are interested in ground state correlations.
 The operator multiplying the old correlation operator represents all possible excitations of the impurity site, and ensure that the bath and impurity excitation processes take place in correlation.
+The projector ensures that only tripartite correlations between the impurity site and the two momentum states are captured by the correlation, which is what's desired within the tiling method.
+
 With this modified operator, this class of correlation functions can be written as
 \begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r} }\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r})\mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r} }\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+This can be interpreted as the fact that within our auxiliary model formalism, the correlation between the sites \({\bf r}\) and \({\bf \Delta + r}\) can only occur through a transition process that connect one of the sites with the impurity site and then a return process that connects the impurity site with the other site.
 
@@
 \begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}^\prime \neq 0}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r})\mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}^\prime \neq 0}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
 \end{aligned}\end{equation}
@@
 
-\section{Entanglement measures}
+\section{Entanglement}
+We will now describe the prescription of calculating entanglement measures of the lattice model from within our auxiliary model treatment.
+In this section, we are interested mainly in two such measures, the entanglement entropy and the mutual information.
+Given a pure state \(\ket{\Psi}\) describing the complete system, the entanglement entropy \(S_\text{EE}(\nu)\) of a subsystem \(\nu\) quantifies the entanglement of \(\nu\) with the rest of the subsystem, and is defined as
+\begin{equation}\begin{aligned}
+	S_\text{EE}(\nu) = -\text{Tr}\left[\rho(\nu)\log \rho(\nu)\right],\quad \rho(\nu) = \text{Tr}_\nu\left[\ket{\Psi}\bra{\Psi}\right] 
+\end{aligned}\end{equation}
+where \(\text{Tr}\left[\cdot\right] \) is the trace operator, and \(\rho(\nu)\) is the reduced density matrix for the subsystem \(\nu\) obtained by taking the partial trace \(\text{Tr}_\nu\) (over the states of \(\nu\)) of the full density matrix \(\rho = \ket{\Psi}\bra{\Psi}\).
+If the subsystem \(\nu\) describes local regions in real space (or states in \(k-\)space), we might be interested in the entanglement between two such subsystems \(\nu_1\) and \(\nu_2\).
+The correct measure to quantify such entanglement is the mutual information:
+\begin{equation}\begin{aligned}
+	I_2(\nu_1,\nu_2) = S_\text{EE}(\nu_1) + S_\text{EE}(\nu_2) - S_\text{EE}(\nu_1 \cup \nu_2)~,
+\end{aligned}\end{equation}
+where \(\nu_1 \cup \nu_2\) is a larger subsystem formed by combining \(\nu_1\) and \(\nu_2\).
+
+In line with our auxiliary model strategy, entanglement measures in the auxiliary model must involve the impurity site - this means, for example, that entanglement measures must always be correlated with the impurity site, through mutual information and higher-party measures (\(I_3,~I_4\) and so on).
+This requires us to express the entanglement entropy as a function of these higher-party measures, and we will now derive such a relation.
+
+\subsection{Decomposition of entanglement entropy in terms of multipartite information \(I_n\)}
+We first define a partitioning of the entire system into \(N\) disjoint regions, \(\mathcal{S}_N = \left\{ \nu_1, \nu_2,\ldots\nu_N\right\} \).
+Going beyond bipartite mutual information, one can define the \(n-\)partite information \(I_n\) between the members of \(\mathcal{S}_n = \left\{\nu_1,\nu_2,\ldots,\nu_n\right\} \), which is itself a subset of the exhaustive set of regions \(\mathcal{S}_N\):
+\begin{equation}\begin{aligned}
+	I_n(\nu_1,\ldots,\nu_n) = \sum_{\sigma \in \mathcal{P}\left(\mathcal{S}_n\right)} (-1)^{1 + |\sigma|} S_\text{EE}(\sigma)~,
+\end{aligned}\end{equation}
+where \(\sigma\) is a subset drawn from the power set of \(\mathcal{S}_n\), and \(|\sigma|\) is the number of members in the subset \(\sigma\). The 4-partite information can be written as
+\begin{equation}\begin{aligned}
+	I_4 = & ~ S_\text{EE}(\nu_1) + S_\text{EE}(\nu_2) + S_\text{EE}(\nu_3) + S_\text{EE}(\nu_4) \\
+		  & - S_\text{EE}(\nu_1 \cup \nu_2) - S_\text{EE}(\nu_1 \cup \nu_3) - S_\text{EE}(\nu_1 \cup \nu_4) - S_\text{EE}(\nu_2 \cup \nu_3) - S_\text{EE}(\nu_2 \cup \nu_4) - S_\text{EE}(\nu_3 \cup \nu_4) \\
+		  & + S_\text{EE}(\nu_1 \cup \nu_2 \cup \nu_3) + S_\text{EE}(\nu_1 \cup \nu_2 \cup \nu_4) + S_\text{EE}(\nu_1 \cup \nu_3 \cup \nu_4) + S_\text{EE}(\nu_2 \cup \nu_3 \cup \nu_4)\\
+		  & + S_\text{EE}(\nu_1 \cup \nu_2 \cup \nu_3 \cup \nu_4)~.
+\end{aligned}\end{equation}
+One can also define the average \(n-\)partite information, \(\bar I_n\):
+\begin{equation}\begin{aligned}
+\bar I_n = \frac{1}{N^n}\sum_{\nu_1 \in \mathcal{S}_N} \sum_{\nu_2 \in \mathcal{S}_N}\ldots\sum_{\nu_n \in \mathcal{S}_N} I_n(\nu_1,\ldots,\nu_n) = \frac{1}{N^n}\sum_{\nu_1 \in \mathcal{S}_N} \sum_{\nu_2 \in \mathcal{S}_N}\ldots\sum_{\nu_n \in \mathcal{S}_N}\sum_{\sigma \in \mathcal{P}\left(\mathcal{S}_n\right)} (-1)^{1 + |\sigma|} S_\text{EE}(\sigma)~.
+\end{aligned}\end{equation}
+This can be simplified by bringing the summations over \(\nu_i\) inside the summation over \(\sigma\):
+\begin{equation}\begin{aligned}
+	\bar I_n = \frac{1}{N^n}\sum_{\sigma \in \mathcal{P}\left(\mathcal{S}_n\right)} (-1)^{1 + |\sigma|} \sum_{\nu_1 \in \mathcal{S}_N} \sum_{\nu_2 \in \mathcal{S}_N}\ldots\sum_{\nu_n \in \mathcal{S}_N}S_\text{EE}(\sigma) = \sum_{\sigma \in \mathcal{P}\left(\mathcal{S}_n\right)} (-1)^{1 + |\sigma|} S_\text{EE}^{(|\sigma|)} ~,
+\end{aligned}\end{equation}
+where we have define the average entanglement entropy for subsystem size \(|\sigma|\), 
+\begin{equation}\begin{aligned}
+	S_\text{EE}^{(|\sigma|)} = \frac{1}{N^n}\sum_{\nu_1 \in \mathcal{S}_N} \ldots\sum_{\nu_n \in \mathcal{S}_N}S_\text{EE}(\sigma)~.
+\end{aligned}\end{equation}
+The advantage of doing this is that \(S_\text{EE}^{(|\sigma|)}\) depends only on the length \(|\sigma|\), not on the elements themselves.
+This allows us to carry out the sum over \(\sigma\), for a fixed \(|\sigma|\):
+\begin{equation}\begin{aligned}
+	\bar I_n = \sum_{l=1}^n  (-1)^{1+l} S_\text{EE}^{(l)}\sum_{\sigma \in \mathcal{P}\left(\mathcal{S}_n\right),\atop{|\sigma|=l}} = \sum_{l=1}^n  (-1)^{1+l} \binom{n}{l} S_\text{EE}^{(l)} ~,
+\end{aligned}\end{equation}
+where \(\binom{n}{l} = \frac{n!}{l!~(n-l)!}\) is the number of subsets of \(\mathcal{S}_n\) that have length \(l\).
+With most of the machinery in place, we would now like to express the entanglement entropy \(S_\text{EE}\) purely in terms multipartite measures \(I_n\), for the reasons stated above.
+For a system that is invariant under real-space translation (as our lattice model is), the entanglement entropy of any real-space interval should only depend on the extent of the interval.
+It therefore suffices to calculate the entanglement entropy averaged over all such intervals, and the corresponding measure in our formulation is \(S_\text{EE}^{(1)}\).
+
+We will now express \(S_\text{EE}^{(1)}\) in terms of \(\bar I_n\), by eliminating \(S_\text{EE}^{(l)} (l > 1)\) from the equations. We adopt the ansatz
+\begin{equation}\begin{aligned}\label{expansion}
+	S_\text{EE}^{(1)} = \sum_{n=2}^N \lambda_n \bar I_n = S_\text{EE}^{(1)}\sum_{n=2}^N n \lambda_n - \sum_{l=2}^{N-1} S_\text{EE}^{(l)} (-1)^{l} \sum_{n=l}^N \binom{n}{l} \lambda_n~,
+\end{aligned}\end{equation}
+where the \(N-1\) coefficients \(\left\{ \lambda_n \right\} \) will be determined by requiring that the \(S_\text{EE}^{(l)} (l > 1)\) vanish on the right-hand side, as well as by matching the coefficients of \(S_\text{EE}^{(1)}\) on both sides.
+Note that \(l\) runs only upto \(N-1\) in the second term; this is because, \(S_\text{EE}^{(N)}\) is the entanglement entropy of the full system and hence automatically zero.
+The equations are
+\begin{gather}\label{equation1}
+	\sum_{n=2}^N n \lambda_n = 1,\\
+	\sum_{n=l}^N \binom{n}{l} \lambda_n = 0;~l=2,\ldots,N-1~.
+\end{gather}
+We focus on the second equation first, since it is very short for \(l\) close to \(N\). For \(l=N-1\) and \(l=N-2\), we get
+\begin{equation}\begin{aligned}
+	l=N-1:~&\lambda_{N-1} + N\lambda_{N} = 0 \implies &\lambda_{N-1} = -N \lambda_N\\
+	l=N-2:~&\lambda_{N-2} + \left(N-1\right) \lambda_{N-1} + \frac{N(N-1)}{2}\lambda_{N} = 0 \implies &\lambda_{N-2} = \frac{N(N-1)}{2}\lambda_N~.
+\end{aligned}\end{equation}
+We extrapolate this to the general solution,
+\begin{equation}\begin{aligned}\label{coeffSolution}
+	\lambda_{N-m} = (-1)^m \binom{N}{m} \lambda_N,~m>0,
+\end{aligned}\end{equation}
+and then prove that if this is true for \(\lambda_{N-m}\), it also solves the equation for \(\lambda_{N-m-1}\), thus amounting to a proof by mathematical induction.
+The general equation for \(\lambda_{N-m-1}\) is
+\begin{equation}\begin{aligned}
+	\sum_{n=N-m-1}^N \binom{n}{N-m-1} \lambda_n = 0 \implies \lambda_{N-m-1} + \sum_{m^\prime=0}^{m}\binom{N-m^\prime}{N-m-1} \lambda_{N-m^\prime} = 0~.
+\end{aligned}\end{equation}
+Substituting the extrapolated solution gives
+\begin{equation}\begin{aligned}
+	\lambda_{N-m-1} = -\sum_{m^\prime=0}^{m} (-1)^{m^\prime}\binom{N-m^\prime}{N-m-1} \binom{N}{m^\prime} \lambda_N = \binom{N}{m+1} \lambda_N\sum_{m^\prime=0}^{m} (-1)^{m^\prime + 1}\binom{m+1}{m^\prime} = (-1)^{m+1}\binom{N}{m+1} \lambda_N~,
+\end{aligned}\end{equation}
+which is consistent with the general solution eq.~\ref{coeffSolution}.
+This determines all coefficients \(\lambda_n\) for \(n < N\) in terms of \(\lambda_N\).
+To determine \(\lambda_N\) itself, we use eq.~\ref{equation1}.
+Substituting eq.~\ref{coeffSolution} into it gives
+\begin{equation}\begin{aligned}\label{finalCoeff}
+	\lambda_N \sum_{n=2}^N n (-1)^{N-n} \binom{N}{n} = 1 \implies \lambda_N =  \frac{(-1)^N}{N}~.
+\end{aligned}\end{equation}
+The decomposition of entanglement entropy into multipartite measures is now complete:
+\begin{equation}\begin{aligned}
+	S_\text{EE}^{(1)} &= \sum_{n=2}^N \lambda_n \bar I_n,\\
+	\bar I_n &= \frac{1}{N^n}\sum_{\nu_1 \in \mathcal{S}_N} \sum_{\nu_2 \in \mathcal{S}_N}\ldots\sum_{\nu_n \in \mathcal{S}_N} I_n(\nu_1,\ldots,\nu_n),\\
+	\lambda_{n} &= (-1)^{N-n} \binom{N}{m} \lambda_N (m>0),\quad \lambda_N = \frac{(-1)^N}{N}~.
+\end{aligned}\end{equation}
+
+\subsection{Real-space entanglement}
+The simplest measure to look at is the entanglement entropy of a local state, in real space.
+This suggests a partitioning of the system such that each \(\nu_i\) describes a lattice site.
+Since the local entanglement entropy will be uniform at each lattice site for a system with translation invariance, it suffices to calculate the real-space averaged entanglement entropy \(\frac{1}{N}\sum_{{\bf r}}S_\text{EE}\left( {\bf r} \right) \).
+But given our real-space partitioning, this is equivalent to calculating \(S_\text{EE}^{(1)}\).
+Within our auxiliary model formalism, all correlations must derive from the impurity site.
+This can be formally expressed as subtracting the contribution obtained in the absence of the impurity site.
+Accordingly, in every \(\bar I_n\), we retain only those terms that involve the impurity site:
+\begin{equation}\begin{aligned}\label{localEnt}
+	S_\text{EE}^{\text{loc}} = \lambda_1 \bar I_2(d,{\bf r}) + \lambda_2 \bar I_3(d,{\bf r},{\bf r}^\prime) + \ldots~,
+\end{aligned}\end{equation}
+where \(\bar I_2(d,{\bf r}_1)\) is the mutual information between the impurity site and any conduction bath site \({\bf r}\), averaged over all bath sites, while \(\bar I_3(d,{\bf r},{\bf r}^\prime)\) is the tripartite mutual information between the impurity site and two other bath sites, averaged over all pairs of bath sites \(\left({\bf r},{\bf r}^\prime\right) \), and so on.
+We emphasise that \({\bf r}_1\) and \({\bf r}_2\) are dummy indices that are ultimately averaged over, and they have been added simply to indicate how the averaging is carried out.
+
+This approach can be extended to calculate the entanglement entropy \(S_\text{EE}(L)\) of a region of space (containing, say, \(L\) sites).
+We now partition the system into disjoint continuous chunks \(\nu_i^{(L)}\), of size \(L\).
+For the impurity model, this leads to a chunk \(\nu^{(L)}_d\) that involves the impurity site, and other chunks \(\nu^{(L)}_{{\bf r}}\) without it.
+In terms of the \(n-\)partite information, we get
+\begin{equation}\begin{aligned}
+	S_\text{EE}(L) = \lambda_1 \bar I_2(\nu^{(L)}_d,\nu^{(L)}_{\bf r}) + \lambda_2 \bar I_3(\nu^{(L)}_d,\nu^{(L)}_{\bf r},\nu^{(L)}_{\bf r^\prime}) + \ldots~,
+\end{aligned}\end{equation}
+where the averaging is now over the chunks \(\nu^{(L)}_{\bf r}\) that do not involve the impurity site.
+
+\subsection{Momentum-space entanglement}
+In order to calculate entanglement entropy of \(k-\)states, some modifications are required. By partitioning the system in \(k-\)space, one again obtains an equation similar to eq.\ref{localEnt}:
+\begin{equation}\begin{aligned}
+	\bar S_\text{EE} = \lambda_1 \bar I_2(d,{\bf k}) + \lambda_2 \bar I_3(d,{\bf k},{\bf k}^\prime) + \ldots~,
+\end{aligned}\end{equation}
+but \(\bar S_\text{EE}\) is now an average over \(k-\)space entanglement, and the \(\bar I_n\) involve similar averages of the \(k-\)states of the conduction bath.
+Because of the average on the left-hand side, it is not possible to extract the entanglement entropy of a single \(k-\)mode (which we call \({\bf q}\)) from this expression.
+
+To proceed, we employ the following trick.
+We consider a slightly different scenario for eq.~\ref{expansion}: the averages are now carried out over all states except \({\bf q}\).
+For the sake of keeping the notation unchanged, we let \(N\) be the number of elements in this modified set.
+Eq.~\ref{expansion} will again hold true, apart from the inclusion of the term \(S_\text{EE}^{(N)}\) on the right-hand side; this term was zero in the original calculation (see discussion immediately below eq.~\ref{expansion}) because there it represented the entanglement entropy of the full state (which is always in a pure state and therefore not entangled).
+In this new scenario, \(S_\text{EE}^{(N)}\) refers to the entanglement entropy of all states apart from \({\bf q}\) (or equivalently of just \({\bf q}\)), and is not {\it a priori} zero.
+The equations for the \(\lambda_n\), however, remain unchanged, and one carry out the same derivation to obtain the same results.
+The only difference is that the decomposition of \(\bar S_\text{EE}\) in this "cavity" system will now involve the additional term \(S_\text{EE}^{(N)}\):
+\begin{equation}\begin{aligned}
+	\bar S_\text{EE, {\bf q}} &= \sum_{n=2}^N \lambda_n \bar I_{n, {\bf q}} + S_\text{EE}^{(N)}(-1)^N \lambda_N~.
+\end{aligned}\end{equation}
+The \({\bf q}\) in the subscripts refers to the fact that these quantities are calculated in the cavity representation (that is, in the absence of \({\bf q}\)).
+The final step is to note that since \(S_\text{EE}^{(N)}\) does not scale with the system size \(N\) whle \(\lambda_N\) scales as \(1/N\) (eq.~\ref{finalCoeff}), the last term drops out from the above equation in the limit of \(N \gg 1\).
+
+The reason for considering the cavity representation is the following: the entanglement entropy of just the \({\bf q}\) state can be obtained as the difference between the average in the full system and the average in the cavity:
+\begin{equation}\begin{aligned}
+	S_\text{EE}({\bf q}) \equiv N\left(\bar S_\text{EE} - \bar S_\text{EE, {\bf q}}\right) ~.
+\end{aligned}\end{equation}
+Comparing the decompositions in the presence and absence of \({\bf q}\), it is easy to see that the only terms that survive the difference are those that involve \({\bf q}\):
+\begin{equation}\begin{aligned}
+	S_\text{EE}({\bf q}) = \lambda_1 I_2(d,{\bf q}) + \lambda_2 \bar I_3(d,{\bf q},{\bf k}) + \ldots~,
+\end{aligned}\end{equation}
+where the first term is just the mutual information between the impurity site and the momentum state \({\bf q}\), while the second term is a tripartite information among the impurity site, \({\bf q}\) and \({\bf k}\), with \({\bf k}\) being averaged over the conduction bath states.
+
+The above arguments do not require \({\bf q}\) to be a single momentum state; the entanglement entropy of a patch of \(k-\)states \(q_1, q_2, \ldots, q_L\) can be obtained simply by replacing \({\bf q}\) with \(q_1\cup q_2\ldots q_L\).
+The average over \({\bf k}\) is then also replaced by an average similar collections of \(k-\)states.
+These two results together also allow us to calculate the mutual information between two \(k-\)states.
+
+\section{Entanglement - Older Version}
 In order to relate bipartite measures of entanglement (such as the entanglement entropy and mutual information) across the tiling algorithm, we will express the matrix elements of an arbitrary reduced density matrix (RDM) in terms of generalised correlation functions.
@@
 
-\section{Metal-insulator transition in the Lattice Model}
+\section{Insights on the Mott MIT on the lattice model}
 \subsection{Momentum-space picture etc etc}
@@
 	\centering
-	\includegraphics[width=0.23\textwidth]{tiledSF-1.pdf}
-	\includegraphics[width=0.23\textwidth]{tiledSF-2.pdf}
-	\caption{tiledSF.pdf}
+	\includegraphics[width=0.24\textwidth]{tiledSF-1.pdf}
+	\includegraphics[width=0.24\textwidth]{tiledSF-2.pdf}
+	\includegraphics[width=0.24\textwidth]{tiledSF-3.pdf}
+	\includegraphics[width=0.24\textwidth]{tiledSF-4.pdf}
+	\caption{Spin-flip correlations \(\left<S(k_N)^+, S({\bf k})^-\right>\) between the nodal point \(k_N = \left( -\pi/2, -\pi/2\right)\) and an arbitrary \(k-\)point on the Fermi surface.
+In the absence of bath interaction (first panel), the correlations are somewhat uniformly distributed along the Fermi surface.
+As we enter the pseudogap (second panel), the spin-correlations near the antinode vanish, indicating that they have been removed from the metallic excitations.
+Passing through the pseudogap involves in the extensions of the gapped region (third panel), until finally only the node remains (fourth panel).}
+	\label{tiledSF}
+\end{figure}
+
+\subsection{Fermi surface destablisation through the pseudogap}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.23\textwidth]{kspaceDOS-1.pdf}
+	\includegraphics[width=0.23\textwidth]{kspaceDOS-2.pdf}
+	\includegraphics[width=0.23\textwidth]{kspaceDOS-3.pdf}
+	\includegraphics[width=0.23\textwidth]{kspaceDOS-4.pdf}
+	\caption{One-particle \(k-\)space spectral function.
+In the absence of bath interactions, all points on Fermi surface are gapless (first panel).
+Proceeding through the pseudogap results in the gapping out of Fermi surface points starting from the antinode (second panel) and approaching the node (third panel), until finally only the node remains at the critical point (fourth panel).}
 	\label{fig:tiledSF-pdf}
 \end{figure}
-% \begin{figure*}[htpb]
-% 	\centering
-% 	\includegraphics[width=\textwidth]{charge-p-p_37_-2.0_-1.7297_-0.0_0.1.pdf}
-% \end{figure*}
-% \begin{figure*}[htpb]
-% 	\centering
-% 	\includegraphics[width=\textwidth]{vne-p-p_37_-2.0_-1.7297_-0.0_0.1.pdf}
-% \end{figure*}
 

### 2025-02-26 iterDiagAlgorithm/iterDiagAlgo.tex
added method of transforming states across Hamiltonians, via iterative diagonalisation

@@
 \title{Iterative Ground State Approach Algorithm}
+\author{Abhirup Mukherjee}
+\affiliation{EPQM}
 \begin{abstract}
@@
 The reduced basis for this rotated truncated subspace is constructed by stacking the column vectors \(X_n\) horizontally:
-		\begin{equation}\begin{aligned}
+		\begin{equation}\begin{aligned}\label{rotationMatrix}
 			R = [X_1 X_2 \ldots X_{M_s}]_{D_0\times M_s}~.
@@
 \end{widetext}
+
+\section{Transforming Across Reduced Bases}
+\subsection{The problem of mixing states across Hamiltonians}
+Consider the following problem: We have a quantum impurity problem that undergoes a transition from a Kondo-screened phase to a local moment phase through a critical point, and we wish to study the nature of the critical point.
+In order to take account of the enhanced fluctuations arising at the critical point because of the degeneracy between the Kondo-screened ground state \(\ket{\Psi_\text{KS}}\) and the local moment state \(\ket{\Psi_\text{LM}}\), it is helpful to use a superposition ground state, of the form
+\begin{equation}\begin{aligned}\label{superposition}
+	\ket{\Psi_c} = \frac{1}{\sqrt 2}\left(\ket{\Psi_\text{KS}} + \ket{\Psi_\text{LM}}\right) ~.
+\end{aligned}\end{equation}
+More explicitly, \(\ket{\Psi_\text{KS}}\) and \(\ket{\Psi_\text{LM}}\) are obtained as ground states of the low-energy Hamiltonians \(H_\text{KS}\) and \(H_\text{LM}\) in the Kondo-screened and local moment phases respectively.
+If we use the iterative diagonalisation algorithm described above to obtain these states, the state vectors will be represented in terms of inconsistent basis states.
+That is, \(\ket{\Psi_\text{KS}}\) will be represented in terms of the eigenstates of \(H_\text{KS}\), while \(\ket{\Psi_\text{LM}}\) will be available in terms of the eigenstates of \(H_\text{LM}\), making the addition operation in eq.~\ref{superposition} tricky (we can only add two column vectors if they are in the same basis).
+
+\subsection{Basis transformation of states}
+In order to remedy this, it is necessary to transform one of the states into the basis of the other.
+Suppose we are given two states \(\ket{\Psi^{(1)}}\) and \(\ket{\Psi^{(2)}}\) written in two basis sets \(\left\{ \ket{b^{(1)}_i}\right\} \) and \(\left\{ \ket{b^{(2)}_i}\right\} \),
+\begin{equation}\begin{aligned}
+	\ket{\Psi^{(1)}} = \begin{pmatrix} c_1^{(1)} ~ c_2^{(1)} ~ \ldots ~ c_N^{(1)} \end{pmatrix}^T = \sum_i c_i^{(1)} \ket{b_i^{(1)}},\\
+	\ket{\Psi^{(2)}} = \begin{pmatrix} c_1^{(2)} ~ c_2^{(2)} ~ \ldots ~ c_N^{(2)} \end{pmatrix}^T = \sum_i c_i^{(2)} \ket{b_i^{(2)}}.
+\end{aligned}\end{equation}
+We can transform \(\ket{\Psi^{(1)}}\) into the basis \(\left\{ \ket{b^{(2)}_i}\right\} \) by inserting an identity resolution:
+\begin{equation}\begin{aligned}
+	\ket{\Psi^{(1)}} &= \sum_{i, j} c_i^{(1)} \ket{b_j^{(2)}}\braket{b_j^{(2)}|b_i^{(1)}} \\
+					 &= \sum_{j} \left(\sum_i c_i^{(1)} M^{2, 1}_{ji} \right)\ket{b_j^{(2)}},
+\end{aligned}\end{equation}
+where \(M^{2, 1}_{ji} = \braket{b_j^{(2)}|b_i^{(1)}}\). This can also be represented as a matrix multiplication operation:
+\begin{equation}\begin{aligned}\label{stateTransform}
+	\Psi^{(1)}\vert_{1} \to \Psi^{(1)}\vert_{2} = \hat M^{2, 1}~\Psi^{(1)}\vert_{1}~,
+\end{aligned}\end{equation}
+where \(\Psi^{(1)}\vert_{1}\) and \(\Psi^{(1)}\vert_{2}\) are the column vector representations of the state \(\ket{\Psi^{(1)}}\) in the first basis and second basis respectively, and \(\hat M^{2, 1}\) is the matrix (obviously in the first basis, since it is multiplied with a state in that basis) defined by the matrix elements \(\hat M^{2, 1}_{ij} = \braket{b_i^{(2)} | b_j^{(1)}}\).
+In summary, eq.\ref{stateTransform} is the recipe for transforming the representation of a state from one basis to another.
+
+\subsection{The problem of incompatible basis sets}
+Formulating eq.~\ref{stateTransform} above for the problem laid out in the first part of this section, we interpret \(\ket{\Psi_\text{LM}}\) as \(\ket{\Psi^{(1)}}\) (the state whose representation needs to be modified), and we interpret the two basis sets \(\left\{ \ket{b^{(1)}_i}\right\}\) and \(\left\{ \ket{b^{(2)}_i}\right\}\) as the eigenbasis of \(H_\text{LM}\) and \(H_\text{KS}\) respectively:
+\begin{equation}\begin{aligned}
+	\left\{ \ket{b^{(1)}_i}\right\} &= \left\{ \ket{b^{\text{LM}}_i}\right\}\\
+	\left\{ \ket{b^{(2)}_i}\right\} &= \left\{ \ket{b^{\text{KS}}_i}\right\}~.
+\end{aligned}\end{equation}
+More specifically, the iterative diagonalisation of \(H_\text{LM}\) will lead to a sequence of Hamiltonians (with increasing number of one-particle states), and the eigenbasis of each such Hamiltonian acts as the basis for the next Hamiltonian in the sequence (the initial Hamiltonian is written in the local computational basis); \(\left\{ \ket{b^{\text{LM}}_i}\right\}\) is then the basis in which the final Hamiltonian and its ground state is expressed (before it is diagonalised).
+Same holds for the other Hamiltonian \(H_\text{KS}\) and the basis \(\left\{ \ket{b^{\text{KS}}_i}\right\}\).
+
+The creation of the matrix \(\hat M\) requires the calculation of inner products between basis vectors of two distinct basis sets.
+This can be carried out in practise only if the vectors of both sets are themselves represented in a common basis (the inner product is essentially the multiplication of a row matrix with a column matrix, and the two matrices must be written in the same basis).
+This reveals a problem in the application of eq.~\ref{stateTransform} directly to the problem at hand: a calculation of the kind
+\begin{equation}\begin{aligned}
+	\hat M^{\text{KS}, \text{LM}}_{i,j} = \braket{b^{\text{KS}}_i | b^{\text{LM}}_j}~,
+\end{aligned}\end{equation}
+followed by
+\begin{equation}\begin{aligned}
+	 \ket{\Psi_\text{LM}} \to \hat M^{\text{KS},\text{LM}}\ket{\Psi_\text{LM}}~,
+\end{aligned}\end{equation}
+is incorrect; this is because, the final basis sets in the iterative diagonalisation of the two Hamiltonians are written in the next to last basis set of the same Hamiltonian, which means that \(\left\{ \ket{b^{\text{LM}}_j}\right\}\) and \(\left\{ \ket{b^{\text{KS}}_i}\right\}\) are not available in the same basis.
+
+\subsection{Transforming both states to a common basis}
+As pointed out above, it is not possible to directly construct a basis transformation operator \(\hat M\) that places both \(\ket{\Psi_\text{LM}}\) and \(\ket{\Psi_\text{KS}}\)  in the same basis.
+We therefore adopt a different strategy: we will transform both the states, individually, to the completely local single-particle basis (CLSB).
+This CLSB is, in fact, the starting point of any iterative diagonalisation procedure - it is the basis in which the first Hamiltonian of the flow is constructed.
+
+For concreteness, let the basis set in which the \(j^\text{th}\) Hamiltonian \(H_j\) is written be \(B_j\).
+An important point is that the explicit basis vectors of the set \(B_j\) are available (during the actual computation) only in the earlier basis (even though \(H_j\) itself is written using the \(j^\text{th}\) basis).
+This continues all the way back to \(B_2\), where \(B_2\) is the second basis set and is represented in terms of the CLSB \(B_1\); \(B_1\) is written in its own basis.
+
+Let the final ground state (after the \(N^\text{th}\) diagonalisation) be \(\ket{\Psi_N^{(N)}}\).
+The superscript indicates that the state is computationally expressed in the basis \(B_N\).
+The first step is to express this state in the basis \(B_{N-1}\).
+Following our earlier discussion, this can be achieved through
+\begin{equation}\begin{aligned}
+	\ket{\Psi_N^{(N)}} \to \ket{\Psi_N^{(N - 1)}} = \hat M^{N-1, N}\ket{\Psi_N^{(N)}}~,
+\end{aligned}\end{equation}
+where the basis transformation matrix is expressed in the basis \(B_N\), and its elements are given by
+\begin{equation}\begin{aligned}\label{actualTransform}
+	\hat M^{N-1, N}_{i, j} = \braket{B_{N-1, i}^{(N-1)} | B_{N, j}^{(N-1)}}~;
+\end{aligned}\end{equation}
+the subscripts indicate that the state is the \(i^\text{th}\) (or the \(j^\text{th}\)) basis vector the \((N-1)^\text{th}\) (or the \(N^\text{th}\) basis set.
+The superscript indicates that both the basis vectors are computationally represented in the \((N-1)^\text{th}\) basis.
+This of course means that the basis vectors of \(B_{N-1}\) will be very simple.
+Assuming there as \(D\) states in \(B_{N-1}\), we have
+\begin{equation}\begin{aligned}\label{identity}
+	B_{N-1} = \left\{ \begin{pmatrix} 1 \\ 0 \\ \vdots \\ 0\end{pmatrix}, \begin{pmatrix} 0 \\ 1 \\ \vdots \\ 0\end{pmatrix} \ldots \begin{pmatrix} 0 \\ 0 \\ \vdots \\ 1\end{pmatrix}\right\} = \left\{ P^1_D, P^2_D, \ldots, P^D_D \right\} ~,
+\end{aligned}\end{equation}
+where \(P^i_D\) is the vector of size \(D\) with 1 at the \(i^\text{th}\) position and zeros elsewhere.
+
+More specifically, let's say that we are retaining \(M_s\) number of eigenstates at each step of the iterative diagonalisation process.
+By diagonalisating the Hamiltonian \(H_{N-1}\) (which is written in the basis \(B_{N-1}\)), we obtain \(M_s\) eigenstates \( \left\{ \ket{e^i_{N-1}}; i=1,2,\ldots,M_s\right\} \).
+If we insert, say, another qubit into the system for the next step, we can only retain at most \(M_s/2\) of these eigenstates (the qubit itself will increase the number of states by a factor of 2, leading to the required \(M_s\) number of basis states).
+The complete basis \(B_{N}\) is obtained by rotating and truncating the existing system into the basis \(\left\{\ket{e^i_{N-1}}; i=1,2,\ldots,M_s/2\right\}\) and then taking the direct product of these states with the CLSB of the newly added qubit, which is just identity \(\mathbb{I}(2)\):
+\begin{equation}\begin{aligned}\label{Nthstep}
+	B_{N} = \left\{\ket{e^i_{N-1}}; i=1 \to M_s/2\right\}  \otimes \mathbb{I}(2)~.
+\end{aligned}\end{equation}
+The representation of \(B_N\) is therefore sort of hybrid - it uses the basis \(B_{N-1}\) for the old qubits (\(M_s/2\) states)	but uses the CLSB for the newly added qubit (2 states).
+That's just because the newly added qubit wasn't available when \(B_{N-1}\) was constructed, so the old basis \(B_{N-1}\) cannot account for that.
+In order to use eq.~\ref{actualTransform}, \(B_{N-1}\) and \(B_N\) must be in the same representation and of the same dimensions.
+For the older qubits, we have \(B_{N-1} = \mathbb I(M_s/2)\) (via eq.~\ref{identity}).
+For the new qubits, we again use the CLSB, which leads to the full \(B_{N-1}\),
+\begin{equation}\begin{aligned}\label{brokenidentity}
+	B_{N-1} = \mathbb I(M_s/2) \otimes \mathbb I(2) = \left\{ P^i_{M_s}; i=1\to M_s \right\} ~,
+\end{aligned}\end{equation}
+which keeps eq.~\ref{identity} unchanged but gives us a clearer picture of what's going on.
+In fact, we can simplify eq.~\ref{actualTransform} by combining eqs.~\ref{Nthstep} and \ref{brokenidentity}.
+Since the new qubits are represented by identity matrices in both basis sets, it is only the old qubits whose states changes during the basis transformation.
+Therefore, the full transformation matrix \(\hat M^{N-1, N}\) can be split into two parts, one for the old qubits and one for the new qubits:
+\begin{equation}\begin{aligned}
+	\hat M^{N_1, N} \otimes \mathbb{I}(2),~\hat M^{N-1, N}_{i, j} = \braket{P^i_{M_s/2} | e^j_{N-1}}~.
+\end{aligned}\end{equation}
+The structure of the matrix element implies that the matrix \(\hat M^{N-1, N}\) has the eigenvectors \(\ket{e^j}\) as its columns.
+We conclude from this that the matrix \(\hat M^{N-1, N}\) is simply the diagonalising matrix \(R^{N-1}\) obtained after diagonalisation of the Hamiltonian \(H_{N-1}\) (see eq.~\ref{rotationMatrix}).
+
+None of the arguments was specific to the final step of the iterative diagonalisation procedure, so we can immediately write down the general expressions for transforming a state \(\ket{\Psi_N^n}\) from \(B_n\) to \(B_{n-1}\):
+\begin{equation}\begin{aligned}
+\ket{\Psi_N^{(n)}} \to \ket{\Psi_N^{(n - 1)}} = \left( R^{n-1} \otimes \mathbb{I}(\Delta) \right) \ket{\Psi_N^{(n)}},
+\end{aligned}\end{equation}
+where \(\Delta\) is the number of states that must be padded in order to make up the correct dimension of the transformation operator.
+
 \end{document}

### 2025-02-26 TilingProjectDraft/tilingProject.tex
updated tiled entanglement formulation and implemented corresponding numerics

--- 2025-02-10 TilingProjectDraft/tilingProject.tex
@@
 \documentclass[reprint,hidelinks,onecolumn]{revtex4-2}
-\usepackage{braket,amsmath,color,graphicx,bookmark,bm}
+\usepackage{braket,amsmath,color,graphicx,bookmark,bm,amssymb}
 \graphicspath{{./figures/}}
@@
 
+\section{The Tiling Algorithm}
+
+\subsection{Formal description of the tiling procedure}
+We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian.
+The first step is of course to identify an impurity model that can act as a good auxiliary model for out lattice model.
+The local behaviour of this impurity model should reflect the essential local physics of the lattice model.
+Typically, we will consider impurity model geometries where the real-space bath site connected directly to the impurity also harbours some kind of local interaction.
+We will henceforth refer to this site as the zeroth site.
+In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout.
+
+In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})\).
+The unit cell at the position \({\bf r}_d\) is then obtained by placing the zeroth site on all nearest-neighbours of \({\bf r}_d\) and averaging over these configurations:
+\begin{equation}\begin{aligned}\label{unitCellHamiltonian}
+	\mathcal{H}_\text{aux}({\bf r}_d) = \frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})~,
+\end{aligned}\end{equation}
+where \({\bf z}\) is summed over all nearest-neighbours of \({\bf r}_d\) and \(\mathcal{Z}\) is the number of such nearest-neighbours.
+
+In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice.
+For this, we define {\it many-particle global} translation operators \(T({\bf a})\) that translate all positions by a vector \({\bf a}\).
+In terms of manybody states and operators, their action is defined as
+\begin{equation}\begin{aligned}\label{translationDefinition}
+	&T^\dagger({\bf a}) \ket{{\bf r}_1, {\bf r}_2,\ldots} = \ket{{\bf r}_1 + {\bf a}}\otimes\ket{{\bf r}_2 + {\bf a}}\ldots\otimes\ket{{\bf r}_n + {\bf a}}\\
+	&T^\dagger({\bf a}) \mathcal{O}\left({\bf r}_1, {\bf r}_2,\ldots\right)T({\bf a}) = \mathcal{O}\left({\bf r}_1 + {\bf a}, {\bf r}_2 + {\bf a},\ldots\right)~,
+\end{aligned}\end{equation}
+where \(\ket{{\bf r}_1, {\bf r}_2,\ldots}\) is a state in the manyparticle Fock-space basis with the particles localised at the specified positions.
+For example, for a local fermionic creation operator \(c^\dagger({\bf r})\), we have
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a}) c^\dagger({\bf r}) T({\bf a}) = c^\dagger({\bf r} + {\bf a})~.
+\end{aligned}\end{equation}
+It acts similarly on the auxiliary model Hamiltonian:
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a})\mathcal{H}_\text{aux}({\bf r}_d)T({\bf a}) = \mathcal{H}_\text{aux}({\bf r}_d + {\bf a})~,
+\end{aligned}\end{equation}
+translating all sites by the vector \({\bf a}\). By introducing the Fourier transform to momentum space,
+\begin{equation}\begin{aligned}
+	\ket{{\bf r}_1, {\bf r}_2,\ldots} = \otimes_{j=1}^N \int d{\bf k}_j e^{-i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf k}_j}~,
+\end{aligned}\end{equation}
+it is easy to see that the total momentum states are eigenstates of the global translation operators:
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a})\ket{{\bf k}_1, {\bf k}_2,\ldots} &= \otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} T^\dagger({\bf a})\ket{{\bf r}_j}~,\\
+							    &=\otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf r}_j + {\bf a}}\\
+							    &=e^{-i {\bf a}_j\cdot{\bf k}_\text{tot}}\ket{{\bf k}_1, {\bf k}_2,\ldots},
+\end{aligned}\end{equation}
+where \({\bf k}_\text{tot} = \sum_j {\bf k}_j\) is the total momentum.
+
+The auxiliary model, being an impurity model, lacks translation symmetry.
+The lattice model does remain invariant under global translation operations.
+In order to reconstruct the full lattice model and restore its translation invariance, we translate the unit cell across all sites of the lattice:
+\begin{equation}\begin{aligned}
+	\label{tilingPrescription}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})\\
+				&= \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r} - {\bf r}_d)~ \\
+				&= \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d)~ \\
+\end{aligned}\end{equation}
+where \({\bf r}\) sums over all lattice sites.
+
+\subsection{Extending the Anderson impurity model: Identifying the correct auxiliary model}
+The standard Anderson model consists of a correlated impurity site coupled with a non-interacting conduction bath.
+The double occupancy cost on the impurity is \(U\), while the single-particle hopping strength between the impurity and the conduction bath is \(V\).
+Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes.
+We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model).
+The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
+\begin{equation}\begin{aligned}
+	\label{siam_attr}
+	\mathcal{H}_\text{E-S} = \mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} + \mathcal{H}_\text{imp-cbath}~,
+\end{aligned}\end{equation}
+where 
+\begin{itemize}
+	\item \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site,
+	\item \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and
+	\item \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 - V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath.
+\end{itemize}
+Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath.
+We have found that the e-SIAM has a stable local moment phase for \(U_b < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)).
+We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of an optical gap in the local spectral function beyond a certain value of interaction strength.
+Note that the impurity site and the conduction bath are both at half-filling.
+
+\subsection{Tiling towards a Hubbard-Heisenberg model with an embedded extended SIAM}
+In this subsection, we provide an explicit example of constructing a lattice model.
+We will consider a slightly more generalised version of the extended SIAM described in the previous section, where the impurity site coupled to the conduction bath purely through the s-wave channel.
+We will show that that model leads to a form of a Hubbard-Heisenberg model upon restoring translation invariance via repeated translation operations.
+The generalisation involve allowing an arbitrary filling on the impurity site and in the conduction bath, through two additional parameter: (i) a particle-hole asymmetry parameter \(\eta\) for the impurity site, (ii) a chemical potential for the conduction bath, and (iii) embedding the impurity into the lattice of the 2D conduction bath.
+This modified impurity model is shown in Fig.~\ref{embeddedEsiam}.
+The first term modifies the impurity Hamiltonian \(\mathcal{H}_\text{imp}\) into
+\begin{equation}\begin{aligned}\label{onsiteHamiltonian}
+	\mathcal{H}_\text{imp} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 - \eta\sum_\sigma \hat n_{{\bf r}_d\sigma}~.
+\end{aligned}\end{equation}
+where we have placed the impurity site at the position \({\bf r}_d\). The second term modifies the conduction bath Hamiltonian \(\mathcal{H}_\text{cbath}\):
+\begin{equation}\begin{aligned}\label{bathHamiltonian}
+	\mathcal{H}_\text{cbath} &= -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
+							 &- \frac{1}{2 \mathcal{Z}}U_b\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
+\end{aligned}\end{equation}
+where \(\left<{\bf r}_i, {\bf r}_j\right>\neq {\bf r}_d\) indicates that the sum is over all nearest-neighbour pairs of sites avoiding the impurity site \({\bf r}_d\).
+
+In this notation, the interaction Hamiltonian can be written as
+\begin{equation}\begin{aligned}\label{interactionHamiltonian}
+	\mathcal{H}_\text{imp-cbath} &= \frac{J}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}\sum_{{\bf z}\in\text{NN}({\bf r}_d)} {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \\
+								 & - \frac{V}{\sqrt{\mathcal{Z}}}\sum_{\sigma} \sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)
+\end{aligned}\end{equation}
+where \(\boldsymbol \tau = \left( \tau_x, \tau_y, \tau_z \right) \) is the vector of Pauli matrices. \(\sigma\) and \(\sigma^\prime\) can be \(\pm 1\) and represent up and down configurations.
+
+We now follow the prescription laid out in eq.~\ref{tilingPrescription}. The tiled Hamiltonian can be written as 
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{tiled} = \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} \right.\\
+\left.+ \mathcal{H}_\text{imp-cbath}\right]T({\bf r} - {\bf r}_d)~.
+\end{aligned}\end{equation}
+Note that in comparison to eq.~\ref{tilingPrescription}, we have dropped the sum over the zeroth sites, because our impurity model Hamiltonian (defined using eqs.~\ref{onsiteHamiltonian} through \ref{interactionHamiltonian}) already contains a sum over these zeroth sites.
+
+We consider the effect of the translation operations on each part of the Hamiltonian. We first have
+\begin{equation}\begin{aligned}
+	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d) \\
+	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \right.\\
+	 &\left.- \frac{U_b}{2\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}\right]T({\bf r} - {\bf r}_d) \\
+	=& -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
+	 &- \frac{U_b}{2\mathcal{Z}}\sum_{\bf r}\sum_{{\bf z}\in\text{NN}\left({\bf r}\right)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i}\sum_{{\bf r} \neq {\bf r}_i}\hat n_{{\bf r}_i,\sigma}\\
+	=& -\frac{1}{\sqrt\mathcal{Z}}(N-2)t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
+	 &- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+\end{aligned}\end{equation}
+In the first step, the factor of \(\mathcal{Z}\) is cancelled out by the trivial sum over \({\bf r}_0\) in the first and third terms.
+At the last step, the three terms simplified for the following reasons.
+The inequality \(\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}\) in the first term ensures that each nearest-neighbour pair appears in \(N-2\) instances of the auxiliary model, \(N\) being the total number of lattice sites; the two instances that do not contribute are the ones in which the impurity site itself is at \({\bf r}_i\) or \({\bf r}_j\).
+For the second term, the double sum \(\sum_{\bf r}\sum_{{\bf z} \in \text{NN}({\bf r})}\) evaluates to \(\mathcal{Z}\sum_{\bf r}\), because each point on the lattice appears \(\mathcal{W}\) times in the summation.
+This factor of \(\mathcal{W}\) cancels the one in the denominator.
+In the third term, the inner summation simply evaluates to \(N-1\), and we finally replace the dummy index \({\bf r}_i\) with \({\bf r}\).
+
+The next part is
+\begin{equation}\begin{aligned}
+	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp}T({\bf r} - {\bf r}_d) \\
+	=& -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}~.
+\end{aligned}\end{equation}
+This is obtained simply by replacing the impurity position \({\bf r}_d\) with the translated position \({\bf r}\), generating a translation-invariant Hubbard term (the first term) and a finite chemical potential (second term).
+
+We now consider the final term:
+\begin{equation}\begin{aligned}
+	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp-cbath}T({\bf r} - {\bf r}_d)\\
+	&=\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
+				     &-  \left. \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma} V \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]T({\bf r} - {\bf r}_d)\\
+	&=\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r})}\left[\frac{1}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
+				     &-  \frac{1}{\sqrt\mathcal{Z}}\left.\sum_{\sigma} V\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]\\
+					 &=\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]\\
+\end{aligned}\end{equation}
+At the last step, each nearest-neighbour pair of sites \({\bf r}_i, {\bf r}_j\) appear 2 times in the summation, because any site is a member of two distinct nearest-neighbour pairs.
+We have also defined \({\bf S}_{{\bf r}_j} =\sum_{\sigma,\sigma^\prime} {\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime}\) as the local spin operator.
+
+The total tiled Hamiltonian is therefore
+\begin{equation}\begin{aligned}
+	&\mathcal{H}_\text{tiled} \\
+	&= -\frac{N-2}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>,\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+	&- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}\\
+	& + \sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]
+\end{aligned}\end{equation}
+While constructing the tiled Hamiltonian, we have added extra copies of the non-interacting Hamiltonian \(\mathcal{H}_\text{cbath-nint} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\) for the conduction bath (this results in the factors of \(N-2\) and \(N-1\) in front of the first and third terms).
+Upon removing these repeated terms, the tiled Hamiltonian becomes
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}\\
+							 &= -\frac{1}{\sqrt\mathcal{Z}}(t + 2V)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
+							 &- \frac{1}{2}\left(U + U_b\right)\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \left(\eta + 2\mu\right) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} \\
+							 &+ \frac{2}{\mathcal{Z}}J\sum_{\left< {\bf r}_i, {\bf r}_j\right>} {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j}
+\end{aligned}\end{equation}
+
+The result of the tiling operations is a Hubbard-Heisenberg model, of the form
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{HH} &= -\frac{1}{\sqrt\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+						  &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
+\end{aligned}\end{equation}
+where the tilde symbol indicates that the parameters are for the lattice model (and not the auxiliary model).
+By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to each other:
+\begin{equation}\begin{aligned}\label{couplingsMappings}
+	\tilde t = t+2V,~~ \tilde U = U + U_b, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
+\end{aligned}\end{equation}
+In summary, the appropriate method for reconstructing the lattice model Hamiltonian is therefore
+\begin{equation}\begin{aligned}\label{tilingPrescriptionFinal}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}~,
+\end{aligned}\end{equation}
+where we replaced \(N-3\) with \(N\) assuming a large number of sites. Using this, the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.
+
+\subsection{Translation symmetry and a conserved total momentum}
+From the form in eq.~\ref{tilingPrescriptionFinal}, the tiled Hamiltonian is symmetric under global many-body translations of the kind defined in eq.~\ref{translationDefinition}, by arbitrary lattice spacings:
+\begin{equation}\begin{aligned}\label{translationSymmetry}
+	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})T({\bf a}) = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r + a}) = \sum_{{\bf r}^\prime}\mathcal{H}_\text{aux}({\bf r}^\prime)\\
+	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{cbath-nint}T({\bf a}) = \mathcal{H}_\text{cbath-nint}\\
+	&\implies T({\bf a})^\dagger\mathcal{H}_\text{tiled}T({\bf a}) = \mathcal{H}_\text{tiled}~.
+\end{aligned}\end{equation}
+In the first equation, we used the fact that the translation operator simply translates the auxiliary model at the position \({\bf r}\) into another one at the position \({\bf r} + {\bf a}\).
+Since both are part of the summation, the summation remains unchanged.
+The second equation uses the fact that the Hamiltonian \(\mathcal{H}_\text{cbath-nint}\) is that of a tight-binding model and is therefore translation-invariant.
+The fact that the Hamiltonian \(\mathcal{H}_\text{tiled}\) commutes with the many-body translation operator implies that the total crystal momentum \(\vec k\) is a conserved quantity.
+
+\section{Form of the eigenstates: Bloch's theorem}
+In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\bf k}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_i}\), where \({\bf r}_i\) sums over the positions of the local Hamiltonians.
+Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation by an arbitrary number of lattice spacings \({n\bf a}\):
+\begin{equation}\begin{aligned}
+	T^\dagger(n{\bf a})\ket{\Psi_{{\bf k}}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_{i + n}} = e^{-in{\bf k}\cdot{\bf a}}\ket{\Psi_{\bf k}}
+\end{aligned}\end{equation}
+The definition and some properties of these global translation operations were provided in subsection~\ref{formalDescription}.
+It was shown there that they share eigenstates with the total momentum operator.
+In a lattice model, this continuous symmetry gets lowered to its discrete form: the total {\it crystal} momentum is conserved by any scattering process.
+As a result, the eigenstates can be labelled using the combined index \(s = \left({\bf k}, n\right) \) where \({\bf k}\) is the total crystal momentum and \(n\) is a band index \(n\).
+
+The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using eq.~\ref{tilingPrescriptionFinal} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}).
+This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) defined in eq.~\ref{unitCellHamiltonian} can be used to construct eigenstates of the lattice Hamiltonian.
+The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
+
+The state \(\ket{\psi_n\left({\bf r}_d\right)}\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself has been averaged over \(\mathcal{Z}\) zeroth sites.
+Accordingly, we can express the averaged eigenstate \(\ket{\psi_n\left({\bf r}_d\right)}\) as
+\begin{equation}\begin{aligned}
+	\ket{\psi_n\left({\bf r}_d\right)} = \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z} \in \text{NN}({\bf r}_d)}\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}~,
+\end{aligned}\end{equation}
+where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\).
+With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:
+\begin{equation}\begin{aligned}\label{eigenstateProposal}
+	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d, {\bf z}\right)}~,
+\end{aligned}\end{equation}
+where \(N\) is the total number of lattice sites and \({\bf r}_d\) is summed over all lattice spacings.
+The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands.
+The ground state \(s = s_0\) is obtained by setting \({\bf k}\) and \(n\) to 0:
+\begin{equation}\begin{aligned}\label{groundstateProposal}
+	\ket{\Psi_\text{gs}} \equiv \ket{\Psi_{s_0}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d, {\bf z}\right)}
+\end{aligned}\end{equation}
+
+\section{One-Particle Greens Functions}
+\subsection{Momentum-space}
+In the previous part, we proposed a form for the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{gs}}\) of the auxiliary models.
+In this section, we will relate one-particle Greens functions of the bulk lattice to those of the auxiliary model.
+We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
+We define the retarded time-domain lattice \(k-\)space Greens function at zero temperature as
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c_{{\bf K}\sigma}(t), c^\dagger_{{\bf K}\sigma} \right\} | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(t\): 
+\begin{equation}\begin{aligned}\label{heisenberg}
+	c_{{\bf K}\sigma}(t) = e^{it H_\text{tiled} }c_{{\bf K}\sigma}e^{-i t H_\text{tiled}}~.
+\end{aligned}\end{equation}
+We now proceed to simplify one of the terms of the anticommutator (for simplicity of notation):
+\begin{equation}\begin{aligned}\label{greensFunction1}
+	&\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_{\vec r,\vec \Delta}e^{-i{\bf K}_0\cdot\vec\Delta}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+To make further progress, we insert the identity resolution \(1 = \sum_s\ket{\Psi_s}\bra{\Psi_s}\) in between the two operators, where \(s=\left({\bf k}, n\right)\) sums over all eigenstates (with energies \(\tilde E_s\)).
+The lattice eigenstates themselves can again be written in terms of those of the auxiliary model, using eq.~\ref{eigenstateProposal}:
+\begin{equation}\begin{aligned}
+	\ket{\Psi_s}\bra{\Psi_s} = \sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\vec k\cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}~.
+\end{aligned}\end{equation}
+With this, eq.~\ref{greensFunction1} becomes
+	\begin{equation}\begin{aligned}\label{greensfunction2}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\vec k_0\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+In order to bring this expression closer to the form of an auxiliary model Greens function, we would like to transform the initial and final states \(\ket{\psi(\vec r)}\) and \(\ket{\psi(\vec r + \vec \Delta)}\) to apply to the same auxiliary model.
+This is done by using the relation: \(\ket{\psi(\vec r + \Delta)} = T^\dagger(\vec \Delta)\ket{\psi(\vec r)}\), where \(T^\dagger(\vec \Delta)\) translates all lattice sites by the vector \(\vec\Delta\).
+\begin{equation}\begin{aligned}
+	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) T^\dagger(\vec \Delta) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
+\end{aligned}\end{equation}
+The effect of the translation operators on the \(k-\)space annihilation operator can be easily ascertained by transforming it to real-space, using the Fourier transform definition
+\begin{equation}\begin{aligned}\label{fourTransf}
+	c({\bf K}) = \frac{1}{\sqrt N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r})~.
+\end{aligned}\end{equation}
+Upon applying this, we get
+\begin{equation}\begin{aligned}\label{translationOnField}
+	T\left(\vec a\right) c({\bf K}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}T\left(\vec a\right) c({\bf r}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r} - \vec a) = e^{-i{\bf K}\cdot\vec a}c({\bf K})~.
+\end{aligned}\end{equation}
+Using this identity on the above expression gives
+\begin{equation}\begin{aligned}
+	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = e^{-i{\bf K} \cdot \vec \Delta}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
+\end{aligned}\end{equation}
+Finally replacing this all the way back into eq.~\ref{greensfunction2} gives
+	\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K}\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime - \vec\Delta)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+To further unify the operators, we make the substitution \(\vec \Delta^\prime \to \vec \Delta^\prime + \vec \Delta\), leading to the expression
+	\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K} - \vec k\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+The sum over \(\vec\Delta\) can now be carried out, resulting in
+\begin{equation}\begin{aligned}\label{greensfunction3}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~,
+\end{aligned}\end{equation}
+where the sum over \(s=(\vec k, n)\) has been reduced to a sum over the auxiliary model eigenstate index \(n\) because of the Kronecker delta \(\delta\left(\vec k_0 + {\bf K} - \vec k\right)\).
+This can be further simplified by splitting the sum over \(\vec\Delta^\prime\) into positive and negative parts and then making the transformation \(\vec r^\prime \to \vec r^\prime + \vec \Delta^\prime\):
+\begin{equation}\begin{aligned}
+	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime-\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}\right] \\
+																																												   &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\right] \\
+\end{aligned}\end{equation}
+For each pair of \(\vec r^\prime\) and \(\vec\Delta^\prime\), the term within the box brackets has the form of a two-level Hamiltonian between the states \(\ket{\psi_n(\vec r^\prime)}\) and \(\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\), with a tunnelling amplitude \(e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\).
+The term can therefore be written in the eigenbasis of this Hamiltonian:
+\begin{equation}\begin{aligned}
+	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &=\frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right],
+\end{aligned}\end{equation}
+where \(\ket{\chi_n^\pm(\vec r^\prime,\vec\Delta^\prime)} = \frac{1}{\sqrt 2}\left[\ket{\psi_n(\vec r^\prime)} \pm e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime + \vec\Delta^\prime)}\right] \) are the eigenvectors of the tunnelling Hamiltonian with eigenvalues \(\pm 1\) respectively.
+With this basis transformation, we can rewrite eq.~\ref{greensfunction3} as
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+
+In order to make the expression more transparent, we consider the various components separately:
+\paragraph{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}:
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+These terms represent those contributions to the total Greens function that arise from excitations that start and end at a specific auxiliary model (at \(\vec r\)), and also evolve dynamically within the same auxiliary model.
+These terms are therefore exactly equal to the auxiliary model Greens function at position \(\vec r\), and are the most dominant contribution due to the localised nature of the impurity model.
+
+\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}:
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime \neq \vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+These are more non-local contributions; they involve excitations whose time evolution is governed by a different auxiliary model than the terminal one.
+These contributions are highly suppressed in the Kondo screened phase because of the strong entanglement of the singlet ground state.
+
+\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime \neq 0\)}:
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime \neq \vec r,\vec \Delta^\prime \neq 0} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+These are the most non-local contributions; they involve excitations whose time evolution is governed by three different auxiliary models. Accordingly, these contributions are further suppressed.
+
+We now consider each type of contribution in more detail.
+\subsection{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}
+Restricting ourselves to just the single auxiliary model contributions gives
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+We first consider more carefully the transition operator \(\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\) for the 1-particle excitation giving rise to the above Greens function.
+Within our auxiliary model approach, gapless excitations within the lattice model are represented by gapless excitations of the impurity site, specifically those that screen the impurity site and form the local Fermi liquid.
+As a result, the uncoordinated \(\mathcal{T}-\)matrix for the lattice model must be replaced by a combined \(\mathcal{T}-\)matrix within the impurity model that captures those gapless excitations that occur in connection with the impurity, and projects out the uncorrelated excitations that take place even when the impurity site is decoupled from the bath.
+
+In order to construct this auxiliary model \(\mathcal{T}-\)matrix, we note that the impurity site can have both spin and charge excitations.
+Considering both excitations, the modified \(\mathcal{T}-\)matrix that constructs \(k-\)space excitations in correlation with the impurity site are
+\begin{equation}\begin{aligned}\label{tmatrix}
+	\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\left(\sum_{\sigma^\prime}c^\dagger_{d\sigma} + \text{h.c.}\right) + c_{{\bf K}\sigma}\left(S_d^+ + \text{h.c.}\right)~,
+\end{aligned}\end{equation}
+leading to the updated expression for the complete Greens function:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+
+In order to convert this into a more useful form, we use eq.~\ref{heisenberg}:
+\begin{equation}\begin{aligned}
+		\braket{\psi_{0}(\vec r) | \mathcal{T}_{{\bf K}\sigma}(t) | \psi_n(\vec r)} = \braket{\psi_{0}(\vec r) | e^{it H_\text{tiled} }\mathcal{T}_{{\bf K}\sigma}e^{-i t H_\text{tiled}} | \psi_n(\vec r)}~.
+\end{aligned}\end{equation}
+Guided by the relation in eq.~\ref{tilingPrescriptionFinal} \(H_\text{tiled} = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}\) between the tiled Hamiltonian and the auxiliary model, we assume that the operator \(e^{-i t H_\text{tiled}}\) acting on the state \(\ket{\psi_n(\vec r)}\) involves the excitation energy \(E_n\) of only a single auxiliary model.
+Specifically, \(E_n\) is the energy of the eigenstate \(\ket{\psi_n(\vec r)}\).
+This is supported by the fact that this class of contributions to the Greens function is completed within a single auxiliary model.
+Accordingly, we replace \(H_\text{tiled}\) with \(E_n - \varepsilon_{\bf k} \), where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\) and \({\bf k}\) is the crystal momentum associated with the state \(\ket{\psi_n(\vec r)}\).
+This momentum was found to be constrained to \({\bf k}_0 + {\bf K}\) below eq.~\ref{greensfunction3}.
+In the same way, the action of \(H_\text{tiled}\) on the terminal state \(\ket{\psi_{0}(\vec r)}\) gives \(E_0 - \varepsilon_{\bf k_0}\), where \(E_0\) is the ground state energy of the auxiliary model at \({\bf r}\).
+Applying this to our expression gives
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[e^{-it\omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + e^{-it\omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~,
+\end{aligned}\end{equation}
+where \(\omega_p = (E_n - \varepsilon_{\bf k_0 + \bf K}) - (E_0 - \varepsilon_{\bf k_0})\) is the particle-excitation cost and \(\omega_h = -\omega_p\) is the hole-excitation cost.
+We now introduce the Fourier transform \(g(\omega) = \int~dt~ e^{i\omega T}f(t)\) to obtain the frequency-domain Greens function in its spectral representation:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; \omega) = \frac{1}{N}\sum_{\vec r}\sum_n \braket{\psi_{0}(\vec r) | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+For each value of \({\vec r}\), the term within that summation is simply the Greens function (for the excitation \(\mathcal{T}_{{\bf K}\sigma}\)) of the auxiliary model with the impurity site at \({\vec r}\).
+Since all these impurity models are physically equivalent (because of translation invariance), we can replace the average over \({\bf r}\) with the value obtained from any one auxiliary model.
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; \omega) = \sum_n \braket{\psi_{0} | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}} ~.
+\end{aligned}\end{equation}
+
+\subsection{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}
+Allowing for more non-local contributions, and updating the \(\mathcal{T}-\)matrix similar to the previous section gives the following Greens function:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+In order to allow computations within a single auxiliary model, we replace the translated state \(\ket{\psi_n(\vec r^\prime)}\) with \(T^\dagger(\vec r \to \vec r^\prime)\ket{\psi_n(\vec r)} \), where \(T^\dagger(\vec r - \vec r^\prime)\) translates all sites by the vector \(\vec r^\prime - \vec r\).
+This leads to a modified correlation function but within a single auxiliary model:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_{n,\vec r, \vec r^\prime} \bra{\psi_{0}(\vec r)} &\left[\mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.
+\\
+								&\left.
+\mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+In fact, by the same arguments as in the previous section, we can obtain a frequency-resolved Greens function:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; \omega) = \sum_n \bra{\psi_{0}} &\left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.\\
+															&\left.
+\frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}} ~.
+\end{aligned}\end{equation}
+To obtain the above, we used the fact that \(H_\text{tiled}\) commutes with the translation operator.
+
+%TODO
+%By expanding in terms of the small parameter $\frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}}$, this expression for $\Sigma_{H-H}(\vec k,\omega)$ can be recast in the following form:
+%\begin{equation}\begin{aligned}
+%	\Sigma_{H-H}(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~\label{selfenergy2}
+%\end{aligned}\end{equation}
+%where $\Sigma_\text{loc}$ and $\Sigma_\text{near-n}$ correspond to the local and nearest-neighbour self-energies defined on the real-space lattice 
+%\begin{eqnarray}
+%\Sigma_\text{loc}(\omega) &=& \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^{(0)}} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}}~,\\ 
+%\tilde{\Sigma}(\vec k, \omega)&=&\xi_{\vec k}\Sigma_\text{near-n}~,~\Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}^2}~.
+%\end{eqnarray}
+%We note that the form of $\Sigma(\vec k, \omega)$ obtained by us is similar to the form proposed on phenomenological grounds in the generalised DMFT + $\Sigma$ approach~\cite{sadovskii2012}.
+
+\section{Equal-Time Ground State Correlators}\label{staticCorr}
+Properties of the ground state can be probed using static correlation functions that are expectation values of operators that propagate excitations.
+We will consider general correlations, in real and momentum space.
+\subsection{Real-space correlation functions}
+We first consider a real-space operator \(\mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r})\) that quantifies the presence of correlations over a distance \({\bf \Delta}\).
+The correlation function itself is given by the expectation value of this operator in the ground state:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_1 + {\bf r}^\prime + {\bf r}_c + {\bf r}\right)  | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_1 + {\bf r}_c + {\bf r}\right)} e^{-i{\bf k}_0\cdot\left({\bf r}_1 - {\bf r}_2\right)}~,
+\end{aligned}\end{equation}
+where \({\bf r}_1\) and \({\bf r}_1 + {\bf r}^\prime\) are the positions of the incoming and outgoing auxiliary model states, relative to \({\bf r}_c + {\bf r}\), and \({\bf k}_0\) is the crystal momentum of the ground state (which we will immediately set to zero).
+In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
+Substituting this appropriately for both the auxiliary model states gives:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_1 + {\bf r}^\prime + {\bf r}\right) \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) T^\dagger\left({\bf r}_1 + {\bf r}\right) | \psi_\text{gs}\left({\bf r}_c\right)}\\
+								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}^\prime\right) \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
+								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+As a final cosmetic change, we transform \({\bf r}_1 \to -{\bf r}\):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r},{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+Like in the Greens function calculation, we now consider the various kinds of contributions separately.
+
+\subsubsection{Intra-auxiliary model contributions: \({\bf r}^\prime = 0\)}
+These terms describe excitations that start and propagate within the same auxiliary model, upto a distance \({\bf \Delta}\):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+With an eye towards introducing the impurity operators into the correlations, we insert a complete basis defined by the eigenstates \(\left\{\ket{\psi_n\left({\bf r}_c\right)}\right\} \) of the auxiliary model into the expression:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\sum_{n}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \ket{\psi_n\left({\bf r}_c\right)}\bra{\psi_n\left({\bf r}_c\right)} \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+
+For the excitations that exist purely in the conduction bath \(({\bf r} \neq {\bf r}_c)\), the excitation operators must be suitably modified (see the arguments around eq.~\ref{tmatrix}) in order to incorporate Kondo screening.
+The modified excitation operators are generally defined as
+\begin{equation}\begin{aligned}\label{operatorTmatrix}
+	\mathcal{\tilde O}({\bf r}) = \mathcal{O}({\bf r})\mathcal{O}^\dagger(d) \mathcal{P}_\text{gs} ~,
+\end{aligned}\end{equation}
+where \(\mathcal{O}^\dagger(d)\) is the hermitian conjugate of the correlation operator \(\mathcal{O}\), but applied on the impurity sites.
+This therefore constitutes a time-reversed scattering process on the impurity site relative to the process in the bath.
+The operator \(\mathcal{P}_\text{gs}\) projects onto the ground state of the auxiliary model, since we are interested in ground state correlations.
+The operator multiplying the old correlation operator represents all possible excitations of the impurity site, and ensure that the bath and impurity excitation processes take place in correlation.
+The projector ensures that only tripartite correlations between the impurity site and the two momentum states are captured by the correlation, which is what's desired within the tiling method.
+
+With this modified operator, this class of correlation functions can be written as
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r} }\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+This can be interpreted as the fact that within our auxiliary model formalism, the correlation between the sites \({\bf r}\) and \({\bf \Delta + r}\) can only occur through a transition process that connect one of the sites with the impurity site and then a return process that connects the impurity site with the other site.
+
+\subsubsection{Inter-auxiliary model contributions: \({\bf r}^\prime \neq 0\)}
+These are the most non-local contributions, and involve excitations that connect different auxiliary models:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}^\prime \neq 0}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+
+\subsection{Momentum-space correlation functions}
+We now consider momentum space correlations, through a general operator \(\mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1)\):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+Note that \(\mathcal{O}\) itself is a two-particle operator.
+To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_2\right)  | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_1\right)}~,
+\end{aligned}\end{equation}
+where \({\bf r}_1\) and \({\bf r}_2 \) are the positions of the incoming and outgoing auxiliary model states.
+In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
+Substituting this appropriately for both the auxiliary model states gives:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_c\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) T^\dagger\left({\bf r}_1 - {\bf r}_c\right) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+In order to simplify the translation operators, we can use eq.~\ref{translationOnField}.
+For that, we would need to know whether the operator \(\mathcal{O}\) involves the net transfer of momentum.
+If \(\mathcal{O}({\bf k})\) commutes with the total number operator \(n_{\bf k} = \sum_\sigma n_{{\bf k},\sigma}\), there is no momentum transfer.
+Examples of such operators are spin operators, \(S_{\alpha\beta}({\bf k}) \equiv c^\dagger_{{\bf k \alpha}}c_{{\bf k}\beta}\), and density operators \(n_{{\bf k}\alpha}\).
+If \(\mathcal{O}({\bf k})\) does not commute with \(n_{\bf k}\), there is a net transfer of momentum, and one such operator would be the charge isospin operator \(C^+({\bf k}) = c^\dagger_{{\bf k}\uparrow}c^\dagger_{{\bf k}\downarrow}\).
+For the first kind of operators, we have \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = \mathcal{O}({\bf k})\), while the for the latter, we get \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = e^{-{\bf a}\cdot{\bf 2k}}\mathcal{O}({\bf k})\), where \(2{\bf k}\) represents the momentum being transferred by the operator.
+We consider the two cases separately.
+
+\subsubsection{Momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] = 0\)}
+For these operators, the expression for the correlation gives
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
+										 &=\sum_{{\bf r},{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+To obtain the last form, we defined \({\bf \Delta}={\bf r}_2 - {\bf r}_1\) as the distance between the incoming and outgoing auxiliary model states, and preformed the sum over the free variable \({\bf r}_1\) to cancel out the factor of \(1/N\).
+Just like before, this expression can be decomposed into a term that involves a single auxiliary model and other terms that involve two distinct auxiliary models.
+
+\subsubsection{Non-momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] \neq 0\)}
+This class of operators incur an additional phase factor of \(e^{-{\bf a}\cdot{\bf 2k}}\) when the translation operators are translated across them:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}e^{2i\left( {\bf r}_1 - {\bf r}_c \right) \cdot \left( {\bf k}_1 - {\bf k}_2 \right)} \\
+										 &= \delta_{{\bf k}_1, {\bf k}_2}\sum_{{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+For this expression, we again defined \({\bf \Delta}\) similar to before, and carried out the sum of \({\bf r}_1\) involving the exponential to obtain a factor of \(N \delta_{{\bf k}_1, {\bf k}_2}\).
+The Kronecker delta factor is a manifestation of translational invariance and the associated total momentum conservation.
+
+As it stands, operators like \(\mathcal{O}({\bf k}_1)\) act purely on the conduction bath degrees of freedom.
+In order to incorporate impurity-bath correlation effects, we modify these operators using the appropriate \(T-\)matrices, by employing eq.~\ref{operatorTmatrix}.
+The final computations are carried out using these modified operators.
+
+\section{Entanglement}
+We will now describe the prescription of calculating entanglement measures of the lattice model from within our auxiliary model treatment.
+In this section, we are interested mainly in two such measures, the entanglement entropy and the mutual information.
+Given a pure state \(\ket{\Psi}\) describing the complete system, the entanglement entropy \(S_\text{EE}(\nu)\) of a subsystem \(\nu\) quantifies the entanglement of \(\nu\) with the rest of the subsystem, and is defined as
+\begin{equation}\begin{aligned}
+	S_\text{EE}(\nu) = -\text{Tr}\left[\rho(\nu)\log \rho(\nu)\right],\quad \rho(\nu) = \text{Tr}_\nu\left[\ket{\Psi}\bra{\Psi}\right] 
+\end{aligned}\end{equation}
+where \(\text{Tr}\left[\cdot\right] \) is the trace operator, and \(\rho(\nu)\) is the reduced density matrix for the subsystem \(\nu\) obtained by taking the partial trace \(\text{Tr}_\nu\) (over the states of \(\nu\)) of the full density matrix \(\rho = \ket{\Psi}\bra{\Psi}\).
+If the subsystem \(\nu\) describes local regions in real space (or states in \(k-\)space), we might be interested in the entanglement between two such subsystems \(\nu_1\) and \(\nu_2\).
+The correct measure to quantify such entanglement is the mutual information:
+\begin{equation}\begin{aligned}
+	I_2(\nu_1,\nu_2) = S_\text{EE}(\nu_1) + S_\text{EE}(\nu_2) - S_\text{EE}(\nu_1 \cup \nu_2)~,
+\end{aligned}\end{equation}
+where \(\nu_1 \cup \nu_2\) is a larger subsystem formed by combining \(\nu_1\) and \(\nu_2\).
+
+\subsection{Real-space entanglement}
+Real-space entanglement measures can be used to probe delocalisation-localisation transitions.
+The simplest such measure is the entanglement of a local mode.
+Since the local entanglement entropy will be uniform at each lattice site for a system with translation invariance, it suffices to calculate the real-space averaged entanglement entropy \(S_\text{EE}^\text{loc} = \frac{1}{N}\sum_{{\bf r}}S_\text{EE}\left( {\bf r} \right) \).
+By visualising the lattice model as a superposition of auxiliary models placed at various sites (eq.~\ref{tilingPrescriptionFinal}), the real space average of the lattice model can be thought of as an average over sites of a particular impurity model, and then a second average over all the impurity models.
+But since all all impurity models are equivalent to each other, the second average is redundant.
+Secondly, all correlations must derive from the impurity site, which can be formally encoded by subtracting, from this average, the corresponding contribution obtained in the absence of the impurity site.
+In total, the lattice-auxiliary model relation for the local entanglement entropy can be written as
+\begin{equation}\begin{aligned}
+	S_\text{EE}^\text{loc} = \frac{1}{N}\sum_{{\bf r}}\left[S_\text{EE}({\bf r}_d + {\bf r}) - S_\text{EE}^{(0)}({\bf r}_d + {\bf r})\right] ~,
+\end{aligned}\end{equation}
+where \({\bf r}_d\) is the impurity site position, \({\bf r}\) is the distance of a conduction bath site from the impurity site (can be zero), and \(S_\text{EE}({\bf r}_d + {\bf r})\) is the entanglement entropy, calculated within the impurity model, at the locatiom \({\bf r}_d + {\bf r}\).
+\(S^{(0)}_\text{EE}({\bf r}_d + {\bf r})\) is the same entanglement entropy, but calculated for an impurity model but with vanishing impurity-bath hybridisation and bath interaction.
+
+\subsection{Momentum-space entanglement}
+Entanglement measures in \(k-\)space can provide valuable information regarding the Fermi surface structure and the nature of gapless excitations proximate to it.
+The most elementary measure is the entanglement entropy \(S_\text{EE}({\bf q})\) of a single excitation carrying momentum \({\bf q}\).
+Unlike \(S_\text{EE}^\text{loc}\), this does not involve an average, and involves a single computation:
+\begin{equation}\begin{aligned}
+	S_\text{EE}^\text{loc} = S_\text{EE}({\bf q}) - S_\text{EE}^{(0)}({\bf q})~.
+\end{aligned}\end{equation}
+It is possible to improve this by considering inter-auxiliary model contributions in the reduced density matrix \(\rho({\bf q})\). On the lattice model, \(\rho({\bf q})\) is defined as
+\begin{equation}\begin{aligned}\label{SEE-k}
+	\rho({\bf q}) = \text{Tr}_{\bf q}\left[\ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\right] ~,
+\end{aligned}\end{equation}
+where \(\text{Tr}_{\bf q}\left[\cdot\right]\) is the partial trace over the Hilbert space of \({\bf q}\), and \(\ket{\Psi_\text{gs}}\) is the tiled ground state.
+Using eq.~\ref{groundstateProposal}, we can write the ground state in terms of those of the auxiliary model.
+These leads to two classes of terms, one purely within a single auxiliary model ground state \(\ket{\psi_\text{gs}}\), and the other involving transitions across auxiliary models:
+\begin{equation}\begin{aligned}
+	\rho({\bf q}) = \text{Tr}_{\bf q}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d)}\right] + \frac{1}{N}\text{Tr}_{\bf q}\sum_{{\bf r}}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d + {\bf r})}\right]~,
+\end{aligned}\end{equation}
+where \(\ket{\psi_\text{gs}({\bf r}_d)}\) is a reference auxiliary model ground state, and \(\ket{\psi_\text{gs}({\bf r}_d + {\bf r})}\) sums over other auxiliary models at increasing distances from this reference model.
+The first term leads to the expression in eq.~\ref{SEE-k}, while the second term can be used to improve this estimate.
+Away from any quantum critical points, the localised nature of the impurity-bath hybridisation ensures that impurity correlations decay exponentially away from the transition.
+This ensures that the second term is very small away from a critical point.
+We therefore restrict ourselves to just the first term in the present work.
+
 \section{Low-energy description of the embedded eSIAM}
@@
 	\caption{Variation of \(\Gamma\) as \(W/J\) is increased from left to right and top to bottom.
-Each plot shows whether \(\Gamma({\bf k}\) is relevant (black) or irrelevant (white).
+Each plot shows whether \(\Gamma({\bf k})\) is relevant (white) or irrelevant (black).
 The antinodal points are the first state to be removed from the Kondo cloud, while the node is the last to be removed.}
@@
 
-\section{The Tiling Algorithm}
-
-\subsection{Formal description of the tiling procedure}
-We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian.
-The first step is of course to identify an impurity model that can act as a good auxiliary model for out lattice model.
-The local behaviour of this impurity model should reflect the essential local physics of the lattice model.
-Typically, we will consider impurity model geometries where the real-space bath site connected directly to the impurity also harbours some kind of local interaction.
-We will henceforth refer to this site as the zeroth site.
-In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout.
-
-In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})\).
-The unit cell at the position \({\bf r}_d\) is then obtained by placing the zeroth site on all nearest-neighbours of \({\bf r}_d\) and averaging over these configurations:
-\begin{equation}\begin{aligned}\label{unitCellHamiltonian}
-	\mathcal{H}_\text{aux}({\bf r}_d) = \frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})~,
-\end{aligned}\end{equation}
-where \({\bf z}\) is summed over all nearest-neighbours of \({\bf r}_d\) and \(\mathcal{Z}\) is the number of such nearest-neighbours.
-
-In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice.
-For this, we define {\it many-particle global} translation operators \(T({\bf a})\) that translate all positions by a vector \({\bf a}\).
-In terms of manybody states and operators, their action is defined as
-\begin{equation}\begin{aligned}\label{translationDefinition}
-	&T^\dagger({\bf a}) \ket{{\bf r}_1, {\bf r}_2,\ldots} = \ket{{\bf r}_1 + {\bf a}}\otimes\ket{{\bf r}_2 + {\bf a}}\ldots\otimes\ket{{\bf r}_n + {\bf a}}\\
-	&T^\dagger({\bf a}) \mathcal{O}\left({\bf r}_1, {\bf r}_2,\ldots\right)T({\bf a}) = \mathcal{O}\left({\bf r}_1 + {\bf a}, {\bf r}_2 + {\bf a},\ldots\right)~,
-\end{aligned}\end{equation}
-where \(\ket{{\bf r}_1, {\bf r}_2,\ldots}\) is a state in the manyparticle Fock-space basis with the particles localised at the specified positions.
-For example, for a local fermionic creation operator \(c^\dagger({\bf r})\), we have
-\begin{equation}\begin{aligned}
-	T^\dagger({\bf a}) c^\dagger({\bf r}) T({\bf a}) = c^\dagger({\bf r} + {\bf a})~.
-\end{aligned}\end{equation}
-It acts similarly on the auxiliary model Hamiltonian:
-\begin{equation}\begin{aligned}
-	T^\dagger({\bf a})\mathcal{H}_\text{aux}({\bf r}_d)T({\bf a}) = \mathcal{H}_\text{aux}({\bf r}_d + {\bf a})~,
-\end{aligned}\end{equation}
-translating all sites by the vector \({\bf a}\). By introducing the Fourier transform to momentum space,
-\begin{equation}\begin{aligned}
-	\ket{{\bf r}_1, {\bf r}_2,\ldots} = \otimes_{j=1}^N \int d{\bf k}_j e^{-i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf k}_j}~,
-\end{aligned}\end{equation}
-it is easy to see that the total momentum states are eigenstates of the global translation operators:
-\begin{equation}\begin{aligned}
-	T^\dagger({\bf a})\ket{{\bf k}_1, {\bf k}_2,\ldots} &= \otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} T^\dagger({\bf a})\ket{{\bf r}_j}~,\\
-							    &=\otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf r}_j + {\bf a}}\\
-							    &=e^{-i {\bf a}_j\cdot{\bf k}_\text{tot}}\ket{{\bf k}_1, {\bf k}_2,\ldots},
-\end{aligned}\end{equation}
-where \({\bf k}_\text{tot} = \sum_j {\bf k}_j\) is the total momentum.
-
-The auxiliary model, being an impurity model, lacks translation symmetry.
-The lattice model does remain invariant under global translation operations.
-In order to reconstruct the full lattice model and restore its translation invariance, we translate the unit cell across all sites of the lattice:
-\begin{equation}\begin{aligned}
-	\label{tilingPrescription}
-	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})\\
-				&= \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r} - {\bf r}_d)~ \\
-				&= \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d)~ \\
-\end{aligned}\end{equation}
-where \({\bf r}\) sums over all lattice sites.
-
-\subsection{Extending the Anderson impurity model: Identifying the correct auxiliary model}
-The standard Anderson model consists of a correlated impurity site coupled with a non-interacting conduction bath.
-The double occupancy cost on the impurity is \(U\), while the single-particle hopping strength between the impurity and the conduction bath is \(V\).
-Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes.
-We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model).
-The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
-\begin{equation}\begin{aligned}
-	\label{siam_attr}
-	\mathcal{H}_\text{E-S} = \mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} + \mathcal{H}_\text{imp-cbath}~,
-\end{aligned}\end{equation}
-where 
-\begin{itemize}
-	\item \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site,
-	\item \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and
-	\item \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 - V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath.
-\end{itemize}
-Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath.
-We have found that the e-SIAM has a stable local moment phase for \(U_b < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)).
-We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of an optical gap in the local spectral function beyond a certain value of interaction strength.
-Note that the impurity site and the conduction bath are both at half-filling.
-
-\subsection{Tiling towards a Hubbard-Heisenberg model with an embedded extended SIAM}
-In this subsection, we provide an explicit example of constructing a lattice model.
-We will consider a slightly more generalised version of the extended SIAM described in the previous section, where the impurity site coupled to the conduction bath purely through the s-wave channel.
-We will show that that model leads to a form of a Hubbard-Heisenberg model upon restoring translation invariance via repeated translation operations.
-The generalisation involve allowing an arbitrary filling on the impurity site and in the conduction bath, through two additional parameter: (i) a particle-hole asymmetry parameter \(\eta\) for the impurity site, (ii) a chemical potential for the conduction bath, and (iii) embedding the impurity into the lattice of the 2D conduction bath.
-This modified impurity model is shown in Fig.~\ref{embeddedEsiam}.
-The first term modifies the impurity Hamiltonian \(\mathcal{H}_\text{imp}\) into
-\begin{equation}\begin{aligned}\label{onsiteHamiltonian}
-	\mathcal{H}_\text{imp} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 - \eta\sum_\sigma \hat n_{{\bf r}_d\sigma}~.
-\end{aligned}\end{equation}
-where we have placed the impurity site at the position \({\bf r}_d\). The second term modifies the conduction bath Hamiltonian \(\mathcal{H}_\text{cbath}\):
-\begin{equation}\begin{aligned}\label{bathHamiltonian}
-	\mathcal{H}_\text{cbath} &= -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
-							 &- \frac{1}{2 \mathcal{Z}}U_b\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
-\end{aligned}\end{equation}
-where \(\left<{\bf r}_i, {\bf r}_j\right>\neq {\bf r}_d\) indicates that the sum is over all nearest-neighbour pairs of sites avoiding the impurity site \({\bf r}_d\).
-
-In this notation, the interaction Hamiltonian can be written as
-\begin{equation}\begin{aligned}\label{interactionHamiltonian}
-	\mathcal{H}_\text{imp-cbath} &= \frac{J}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}\sum_{{\bf z}\in\text{NN}({\bf r}_d)} {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \\
-								 & - \frac{V}{\sqrt{\mathcal{Z}}}\sum_{\sigma} \sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)
-\end{aligned}\end{equation}
-where \(\boldsymbol \tau = \left( \tau_x, \tau_y, \tau_z \right) \) is the vector of Pauli matrices. \(\sigma\) and \(\sigma^\prime\) can be \(\pm 1\) and represent up and down configurations.
-
-We now follow the prescription laid out in eq.~\ref{tilingPrescription}. The tiled Hamiltonian can be written as 
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{tiled} = \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} \right.\\
-\left.+ \mathcal{H}_\text{imp-cbath}\right]T({\bf r} - {\bf r}_d)~.
-\end{aligned}\end{equation}
-Note that in comparison to eq.~\ref{tilingPrescription}, we have dropped the sum over the zeroth sites, because our impurity model Hamiltonian (defined using eqs.~\ref{onsiteHamiltonian} through \ref{interactionHamiltonian}) already contains a sum over these zeroth sites.
-
-We consider the effect of the translation operations on each part of the Hamiltonian. We first have
-\begin{equation}\begin{aligned}
-	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d) \\
-	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \right.\\
-	 &\left.- \frac{U_b}{2\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}\right]T({\bf r} - {\bf r}_d) \\
-	=& -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
-	 &- \frac{U_b}{2\mathcal{Z}}\sum_{\bf r}\sum_{{\bf z}\in\text{NN}\left({\bf r}\right)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i}\sum_{{\bf r} \neq {\bf r}_i}\hat n_{{\bf r}_i,\sigma}\\
-	=& -\frac{1}{\sqrt\mathcal{Z}}(N-2)t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
-	 &- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
-\end{aligned}\end{equation}
-In the first step, the factor of \(\mathcal{Z}\) is cancelled out by the trivial sum over \({\bf r}_0\) in the first and third terms.
-At the last step, the three terms simplified for the following reasons.
-The inequality \(\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}\) in the first term ensures that each nearest-neighbour pair appears in \(N-2\) instances of the auxiliary model, \(N\) being the total number of lattice sites; the two instances that do not contribute are the ones in which the impurity site itself is at \({\bf r}_i\) or \({\bf r}_j\).
-For the second term, the double sum \(\sum_{\bf r}\sum_{{\bf z} \in \text{NN}({\bf r})}\) evaluates to \(\mathcal{Z}\sum_{\bf r}\), because each point on the lattice appears \(\mathcal{W}\) times in the summation.
-This factor of \(\mathcal{W}\) cancels the one in the denominator.
-In the third term, the inner summation simply evaluates to \(N-1\), and we finally replace the dummy index \({\bf r}_i\) with \({\bf r}\).
-
-The next part is
-\begin{equation}\begin{aligned}
-	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp}T({\bf r} - {\bf r}_d) \\
-	=& -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}~.
-\end{aligned}\end{equation}
-This is obtained simply by replacing the impurity position \({\bf r}_d\) with the translated position \({\bf r}\), generating a translation-invariant Hubbard term (the first term) and a finite chemical potential (second term).
-
-We now consider the final term:
-\begin{equation}\begin{aligned}
-	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp-cbath}T({\bf r} - {\bf r}_d)\\
-	&=\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
-				     &-  \left. \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma} V \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]T({\bf r} - {\bf r}_d)\\
-	&=\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r})}\left[\frac{1}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
-				     &-  \frac{1}{\sqrt\mathcal{Z}}\left.\sum_{\sigma} V\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]\\
-					 &=\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]\\
-\end{aligned}\end{equation}
-At the last step, each nearest-neighbour pair of sites \({\bf r}_i, {\bf r}_j\) appear 2 times in the summation, because any site is a member of two distinct nearest-neighbour pairs.
-We have also defined \({\bf S}_{{\bf r}_j} =\sum_{\sigma,\sigma^\prime} {\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime}\) as the local spin operator.
-
-The total tiled Hamiltonian is therefore
-\begin{equation}\begin{aligned}
-	&\mathcal{H}_\text{tiled} \\
-	&= -\frac{N-2}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>,\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
-	&- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}\\
-	& + \sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]
-\end{aligned}\end{equation}
-While constructing the tiled Hamiltonian, we have added extra copies of the non-interacting Hamiltonian \(\mathcal{H}_\text{cbath-nint} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\) for the conduction bath (this results in the factors of \(N-2\) and \(N-1\) in front of the first and third terms).
-Upon removing these repeated terms, the tiled Hamiltonian becomes
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}\\
-							 &= -\frac{1}{\sqrt\mathcal{Z}}(t + 2V)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
-							 &- \frac{1}{2}\left(U + U_b\right)\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \left(\eta + 2\mu\right) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} \\
-							 &+ \frac{2}{\mathcal{Z}}J\sum_{\left< {\bf r}_i, {\bf r}_j\right>} {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j}
-\end{aligned}\end{equation}
-
-The result of the tiling operations is a Hubbard-Heisenberg model, of the form
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{HH} &= -\frac{1}{\sqrt\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
-						  &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
-\end{aligned}\end{equation}
-where the tilde symbol indicates that the parameters are for the lattice model (and not the auxiliary model).
-By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to each other:
-\begin{equation}\begin{aligned}\label{couplingsMappings}
-	\tilde t = t+2V,~~ \tilde U = U + U_b, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
-\end{aligned}\end{equation}
-In summary, the appropriate method for reconstructing the lattice model Hamiltonian is therefore
-\begin{equation}\begin{aligned}\label{tilingPrescriptionFinal}
-	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}~,
-\end{aligned}\end{equation}
-where we replaced \(N-3\) with \(N\) assuming a large number of sites. Using this, the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.
-
-\subsection{Translation symmetry and a conserved total momentum}
-From the form in eq.~\ref{tilingPrescriptionFinal}, the tiled Hamiltonian is symmetric under global many-body translations of the kind defined in eq.~\ref{translationDefinition}, by arbitrary lattice spacings:
-\begin{equation}\begin{aligned}\label{translationSymmetry}
-	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})T({\bf a}) = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r + a}) = \sum_{{\bf r}^\prime}\mathcal{H}_\text{aux}({\bf r}^\prime)\\
-	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{cbath-nint}T({\bf a}) = \mathcal{H}_\text{cbath-nint}\\
-	&\implies T({\bf a})^\dagger\mathcal{H}_\text{tiled}T({\bf a}) = \mathcal{H}_\text{tiled}~.
-\end{aligned}\end{equation}
-In the first equation, we used the fact that the translation operator simply translates the auxiliary model at the position \({\bf r}\) into another one at the position \({\bf r} + {\bf a}\).
-Since both are part of the summation, the summation remains unchanged.
-The second equation uses the fact that the Hamiltonian \(\mathcal{H}_\text{cbath-nint}\) is that of a tight-binding model and is therefore translation-invariant.
-The fact that the Hamiltonian \(\mathcal{H}_\text{tiled}\) commutes with the many-body translation operator implies that the total crystal momentum \(\vec k\) is a conserved quantity.
-
-\section{Form of the eigenstates: Bloch's theorem}
-In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\bf k}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_i}\), where \({\bf r}_i\) sums over the positions of the local Hamiltonians.
-Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation by an arbitrary number of lattice spacings \({n\bf a}\):
-\begin{equation}\begin{aligned}
-	T^\dagger(n{\bf a})\ket{\Psi_{{\bf k}}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_{i + n}} = e^{-in{\bf k}\cdot{\bf a}}\ket{\Psi_{\bf k}}
-\end{aligned}\end{equation}
-The definition and some properties of these global translation operations were provided in subsection~\ref{formalDescription}.
-It was shown there that they share eigenstates with the total momentum operator.
-In a lattice model, this continuous symmetry gets lowered to its discrete form: the total {\it crystal} momentum is conserved by any scattering process.
-As a result, the eigenstates can be labelled using the combined index \(s = \left({\bf k}, n\right) \) where \({\bf k}\) is the total crystal momentum and \(n\) is a band index \(n\).
-
-The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using eq.~\ref{tilingPrescriptionFinal} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}).
-This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) defined in eq.~\ref{unitCellHamiltonian} can be used to construct eigenstates of the lattice Hamiltonian.
-The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
-
-The state \(\ket{\psi_n\left({\bf r}_d\right)}\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself has been averaged over \(\mathcal{Z}\) zeroth sites.
-Accordingly, we can express the averaged eigenstate \(\ket{\psi_n\left({\bf r}_d\right)}\) as
-\begin{equation}\begin{aligned}
-	\ket{\psi_n\left({\bf r}_d\right)} = \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z} \in \text{NN}({\bf r}_d)}\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}~,
-\end{aligned}\end{equation}
-where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\).
-With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:
-\begin{equation}\begin{aligned}\label{eigenstateProposal}
-	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d, {\bf z}\right)}~,
-\end{aligned}\end{equation}
-where \(N\) is the total number of lattice sites and \({\bf r}_d\) is summed over all lattice spacings.
-The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands.
-The ground state \(s = s_0\) is obtained by setting \({\bf k}\) and \(n\) to 0:
-\begin{equation}\begin{aligned}\label{groundstateProposal}
-	\ket{\Psi_\text{gs}} \equiv \ket{\Psi_{s_0}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d, {\bf z}\right)}
-\end{aligned}\end{equation}
-
-\section{One-Particle Greens Functions}
-\subsection{Momentum-space}
-In the previous part, we proposed a form for the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{gs}}\) of the auxiliary models.
-In this section, we will relate one-particle Greens functions of the bulk lattice to those of the auxiliary model.
-We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
-We define the retarded time-domain lattice \(k-\)space Greens function at zero temperature as
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c_{{\bf K}\sigma}(t), c^\dagger_{{\bf K}\sigma} \right\} | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(t\): 
-\begin{equation}\begin{aligned}\label{heisenberg}
-	c_{{\bf K}\sigma}(t) = e^{it H_\text{tiled} }c_{{\bf K}\sigma}e^{-i t H_\text{tiled}}~.
-\end{aligned}\end{equation}
-We now proceed to simplify one of the terms of the anticommutator (for simplicity of notation):
-\begin{equation}\begin{aligned}\label{greensFunction1}
-	&\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_{\vec r,\vec \Delta}e^{-i{\bf K}_0\cdot\vec\Delta}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-To make further progress, we insert the identity resolution \(1 = \sum_s\ket{\Psi_s}\bra{\Psi_s}\) in between the two operators, where \(s=\left({\bf k}, n\right)\) sums over all eigenstates (with energies \(\tilde E_s\)).
-The lattice eigenstates themselves can again be written in terms of those of the auxiliary model, using eq.~\ref{eigenstateProposal}:
-\begin{equation}\begin{aligned}
-	\ket{\Psi_s}\bra{\Psi_s} = \sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\vec k\cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}~.
-\end{aligned}\end{equation}
-With this, eq.~\ref{greensFunction1} becomes
-	\begin{equation}\begin{aligned}\label{greensfunction2}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\vec k_0\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-In order to bring this expression closer to the form of an auxiliary model Greens function, we would like to transform the initial and final states \(\ket{\psi(\vec r)}\) and \(\ket{\psi(\vec r + \vec \Delta)}\) to apply to the same auxiliary model.
-This is done by using the relation: \(\ket{\psi(\vec r + \Delta)} = T^\dagger(\vec \Delta)\ket{\psi(\vec r)}\), where \(T^\dagger(\vec \Delta)\) translates all lattice sites by the vector \(\vec\Delta\).
-\begin{equation}\begin{aligned}
-	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) T^\dagger(\vec \Delta) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
-\end{aligned}\end{equation}
-The effect of the translation operators on the \(k-\)space annihilation operator can be easily ascertained by transforming it to real-space, using the Fourier transform definition
-\begin{equation}\begin{aligned}\label{fourTransf}
-	c({\bf K}) = \frac{1}{\sqrt N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r})~.
-\end{aligned}\end{equation}
-Upon applying this, we get
-\begin{equation}\begin{aligned}\label{translationOnField}
-	T\left(\vec a\right) c({\bf K}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}T\left(\vec a\right) c({\bf r}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r} - \vec a) = e^{-i{\bf K}\cdot\vec a}c({\bf K})~.
-\end{aligned}\end{equation}
-Using this identity on the above expression gives
-\begin{equation}\begin{aligned}
-	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = e^{-i{\bf K} \cdot \vec \Delta}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
-\end{aligned}\end{equation}
-Finally replacing this all the way back into eq.~\ref{greensfunction2} gives
-	\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K}\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime - \vec\Delta)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-To further unify the operators, we make the substitution \(\vec \Delta^\prime \to \vec \Delta^\prime + \vec \Delta\), leading to the expression
-	\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K} - \vec k\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-The sum over \(\vec\Delta\) can now be carried out, resulting in
-\begin{equation}\begin{aligned}\label{greensfunction3}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~,
-\end{aligned}\end{equation}
-where the sum over \(s=(\vec k, n)\) has been reduced to a sum over the auxiliary model eigenstate index \(n\) because of the Kronecker delta \(\delta\left(\vec k_0 + {\bf K} - \vec k\right)\).
-This can be further simplified by splitting the sum over \(\vec\Delta^\prime\) into positive and negative parts and then making the transformation \(\vec r^\prime \to \vec r^\prime + \vec \Delta^\prime\):
-\begin{equation}\begin{aligned}
-	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime-\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}\right] \\
-																																												   &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\right] \\
-\end{aligned}\end{equation}
-For each pair of \(\vec r^\prime\) and \(\vec\Delta^\prime\), the term within the box brackets has the form of a two-level Hamiltonian between the states \(\ket{\psi_n(\vec r^\prime)}\) and \(\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\), with a tunnelling amplitude \(e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\).
-The term can therefore be written in the eigenbasis of this Hamiltonian:
-\begin{equation}\begin{aligned}
-	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &=\frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right],
-\end{aligned}\end{equation}
-where \(\ket{\chi_n^\pm(\vec r^\prime,\vec\Delta^\prime)} = \frac{1}{\sqrt 2}\left[\ket{\psi_n(\vec r^\prime)} \pm e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime + \vec\Delta^\prime)}\right] \) are the eigenvectors of the tunnelling Hamiltonian with eigenvalues \(\pm 1\) respectively.
-With this basis transformation, we can rewrite eq.~\ref{greensfunction3} as
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-
-In order to make the expression more transparent, we consider the various components separately:
-\paragraph{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}:
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-These terms represent those contributions to the total Greens function that arise from excitations that start and end at a specific auxiliary model (at \(\vec r\)), and also evolve dynamically within the same auxiliary model.
-These terms are therefore exactly equal to the auxiliary model Greens function at position \(\vec r\), and are the most dominant contribution due to the localised nature of the impurity model.
-
-\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}:
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime \neq \vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-These are more non-local contributions; they involve excitations whose time evolution is governed by a different auxiliary model than the terminal one.
-These contributions are highly suppressed in the Kondo screened phase because of the strong entanglement of the singlet ground state.
-
-\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime \neq 0\)}:
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime \neq \vec r,\vec \Delta^\prime \neq 0} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-These are the most non-local contributions; they involve excitations whose time evolution is governed by three different auxiliary models. Accordingly, these contributions are further suppressed.
-
-We now consider each type of contribution in more detail.
-\subsection{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}
-Restricting ourselves to just the single auxiliary model contributions gives
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-We first consider more carefully the transition operator \(\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\) for the 1-particle excitation giving rise to the above Greens function.
-Within our auxiliary model approach, gapless excitations within the lattice model are represented by gapless excitations of the impurity site, specifically those that screen the impurity site and form the local Fermi liquid.
-As a result, the uncoordinated \(\mathcal{T}-\)matrix for the lattice model must be replaced by a combined \(\mathcal{T}-\)matrix within the impurity model that captures those gapless excitations that occur in connection with the impurity, and projects out the uncorrelated excitations that take place even when the impurity site is decoupled from the bath.
-
-In order to construct this auxiliary model \(\mathcal{T}-\)matrix, we note that the impurity site can have both spin and charge excitations.
-Considering both excitations, the modified \(\mathcal{T}-\)matrix that constructs \(k-\)space excitations in correlation with the impurity site are
-\begin{equation}\begin{aligned}\label{tmatrix}
-	\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\left(\sum_{\sigma^\prime}c^\dagger_{d\sigma} + \text{h.c.}\right) + c_{{\bf K}\sigma}\left(S_d^+ + \text{h.c.}\right)~,
-\end{aligned}\end{equation}
-leading to the updated expression for the complete Greens function:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-
-In order to convert this into a more useful form, we use eq.~\ref{heisenberg}:
-\begin{equation}\begin{aligned}
-		\braket{\psi_{0}(\vec r) | \mathcal{T}_{{\bf K}\sigma}(t) | \psi_n(\vec r)} = \braket{\psi_{0}(\vec r) | e^{it H_\text{tiled} }\mathcal{T}_{{\bf K}\sigma}e^{-i t H_\text{tiled}} | \psi_n(\vec r)}~.
-\end{aligned}\end{equation}
-Guided by the relation in eq.~\ref{tilingPrescriptionFinal} \(H_\text{tiled} = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}\) between the tiled Hamiltonian and the auxiliary model, we assume that the operator \(e^{-i t H_\text{tiled}}\) acting on the state \(\ket{\psi_n(\vec r)}\) involves the excitation energy \(E_n\) of only a single auxiliary model.
-Specifically, \(E_n\) is the energy of the eigenstate \(\ket{\psi_n(\vec r)}\).
-This is supported by the fact that this class of contributions to the Greens function is completed within a single auxiliary model.
-Accordingly, we replace \(H_\text{tiled}\) with \(E_n - \varepsilon_{\bf k} \), where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\) and \({\bf k}\) is the crystal momentum associated with the state \(\ket{\psi_n(\vec r)}\).
-This momentum was found to be constrained to \({\bf k}_0 + {\bf K}\) below eq.~\ref{greensfunction3}.
-In the same way, the action of \(H_\text{tiled}\) on the terminal state \(\ket{\psi_{0}(\vec r)}\) gives \(E_0 - \varepsilon_{\bf k_0}\), where \(E_0\) is the ground state energy of the auxiliary model at \({\bf r}\).
-Applying this to our expression gives
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[e^{-it\omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + e^{-it\omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~,
-\end{aligned}\end{equation}
-where \(\omega_p = (E_n - \varepsilon_{\bf k_0 + \bf K}) - (E_0 - \varepsilon_{\bf k_0})\) is the particle-excitation cost and \(\omega_h = -\omega_p\) is the hole-excitation cost.
-We now introduce the Fourier transform \(g(\omega) = \int~dt~ e^{i\omega T}f(t)\) to obtain the frequency-domain Greens function in its spectral representation:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; \omega) = \frac{1}{N}\sum_{\vec r}\sum_n \braket{\psi_{0}(\vec r) | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-For each value of \({\vec r}\), the term within that summation is simply the Greens function (for the excitation \(\mathcal{T}_{{\bf K}\sigma}\)) of the auxiliary model with the impurity site at \({\vec r}\).
-Since all these impurity models are physically equivalent (because of translation invariance), we can replace the average over \({\bf r}\) with the value obtained from any one auxiliary model.
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; \omega) = \sum_n \braket{\psi_{0} | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}} ~.
-\end{aligned}\end{equation}
-
-\subsection{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}
-Allowing for more non-local contributions, and updating the \(\mathcal{T}-\)matrix similar to the previous section gives the following Greens function:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-In order to allow computations within a single auxiliary model, we replace the translated state \(\ket{\psi_n(\vec r^\prime)}\) with \(T^\dagger(\vec r \to \vec r^\prime)\ket{\psi_n(\vec r)} \), where \(T^\dagger(\vec r - \vec r^\prime)\) translates all sites by the vector \(\vec r^\prime - \vec r\).
-This leads to a modified correlation function but within a single auxiliary model:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_{n,\vec r, \vec r^\prime} \bra{\psi_{0}(\vec r)} &\left[\mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.
-\\
-								&\left.
-\mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-In fact, by the same arguments as in the previous section, we can obtain a frequency-resolved Greens function:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; \omega) = \sum_n \bra{\psi_{0}} &\left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.\\
-															&\left.
-\frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}} ~.
-\end{aligned}\end{equation}
-To obtain the above, we used the fact that \(H_\text{tiled}\) commutes with the translation operator.
-
-%TODO
-%By expanding in terms of the small parameter $\frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}}$, this expression for $\Sigma_{H-H}(\vec k,\omega)$ can be recast in the following form:
-%\begin{equation}\begin{aligned}
-%	\Sigma_{H-H}(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~\label{selfenergy2}
-%\end{aligned}\end{equation}
-%where $\Sigma_\text{loc}$ and $\Sigma_\text{near-n}$ correspond to the local and nearest-neighbour self-energies defined on the real-space lattice 
-%\begin{eqnarray}
-%\Sigma_\text{loc}(\omega) &=& \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^{(0)}} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}}~,\\ 
-%\tilde{\Sigma}(\vec k, \omega)&=&\xi_{\vec k}\Sigma_\text{near-n}~,~\Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}^2}~.
-%\end{eqnarray}
-%We note that the form of $\Sigma(\vec k, \omega)$ obtained by us is similar to the form proposed on phenomenological grounds in the generalised DMFT + $\Sigma$ approach~\cite{sadovskii2012}.
-
-\section{Equal-Time Ground State Correlators}\label{staticCorr}
-Properties of the ground state can be probed using static correlation functions that are expectation values of operators that propagate excitations.
-We will consider general correlations, in real and momentum space.
-\subsection{Real-space correlation functions}
-We first consider a real-space operator \(\mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r})\) that quantifies the presence of correlations over a distance \({\bf \Delta}\).
-The correlation function itself is given by the expectation value of this operator in the ground state:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_1 + {\bf r}^\prime + {\bf r}_c + {\bf r}\right)  | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_1 + {\bf r}_c + {\bf r}\right)} e^{-i{\bf k}_0\cdot\left({\bf r}_1 - {\bf r}_2\right)}~,
-\end{aligned}\end{equation}
-where \({\bf r}_1\) and \({\bf r}_1 + {\bf r}^\prime\) are the positions of the incoming and outgoing auxiliary model states, relative to \({\bf r}_c + {\bf r}\), and \({\bf k}_0\) is the crystal momentum of the ground state (which we will immediately set to zero).
-In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
-Substituting this appropriately for both the auxiliary model states gives:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_1 + {\bf r}^\prime + {\bf r}\right) \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) T^\dagger\left({\bf r}_1 + {\bf r}\right) | \psi_\text{gs}\left({\bf r}_c\right)}\\
-								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}^\prime\right) \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
-								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-As a final cosmetic change, we transform \({\bf r}_1 \to -{\bf r}\):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r},{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-Like in the Greens function calculation, we now consider the various kinds of contributions separately.
-
-\subsubsection{Intra-auxiliary model contributions: \({\bf r}^\prime = 0\)}
-These terms describe excitations that start and propagate within the same auxiliary model, upto a distance \({\bf \Delta}\):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-For the excitations that exist purely in the conduction bath \(({\bf r} \neq {\bf r}_c)\), the excitation operators must be suitably modified (see the arguments around eq.~\ref{tmatrix}) in order to incorporate Kondo screening.
-The modified excitation operators are generally defined as
-\begin{equation}\begin{aligned}\label{operatorTmatrix}
-\mathcal{\tilde O} = \mathcal{O} \left[\sum_{\sigma}\left(c^\dagger_{d\sigma} + \text{h.c.}\right) + S_d^+ + \text{h.c.}\right] ~.
-\end{aligned}\end{equation}
-The operator multiplying the old correlation operator represents all possible excitations of the impurity site, and ensure that the bath and impurity excitation processes take place in correlation.
-With this modified operator, this class of correlation functions can be written as
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r} }\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r})\mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-
-\subsubsection{Inter-auxiliary model contributions: \({\bf r}^\prime \neq 0\)}
-These are the most non-local contributions, and involve excitations that connect different auxiliary models:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}^\prime \neq 0}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r})\mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-
-\subsection{Momentum-space correlation functions}
-We now consider momentum space correlations, through a general operator \(\mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1)\):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-Note that \(\mathcal{O}\) itself is a two-particle operator.
-To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_2\right)  | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_1\right)}~,
-\end{aligned}\end{equation}
-where \({\bf r}_1\) and \({\bf r}_2 \) are the positions of the incoming and outgoing auxiliary model states.
-In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
-Substituting this appropriately for both the auxiliary model states gives:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_c\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) T^\dagger\left({\bf r}_1 - {\bf r}_c\right) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-In order to simplify the translation operators, we can use eq.~\ref{translationOnField}.
-For that, we would need to know whether the operator \(\mathcal{O}\) involves the net transfer of momentum.
-If \(\mathcal{O}({\bf k})\) commutes with the total number operator \(n_{\bf k} = \sum_\sigma n_{{\bf k},\sigma}\), there is no momentum transfer.
-Examples of such operators are spin operators, \(S_{\alpha\beta}({\bf k}) \equiv c^\dagger_{{\bf k \alpha}}c_{{\bf k}\beta}\), and density operators \(n_{{\bf k}\alpha}\).
-If \(\mathcal{O}({\bf k})\) does not commute with \(n_{\bf k}\), there is a net transfer of momentum, and one such operator would be the charge isospin operator \(C^+({\bf k}) = c^\dagger_{{\bf k}\uparrow}c^\dagger_{{\bf k}\downarrow}\).
-For the first kind of operators, we have \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = \mathcal{O}({\bf k})\), while the for the latter, we get \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = e^{-{\bf a}\cdot{\bf 2k}}\mathcal{O}({\bf k})\), where \(2{\bf k}\) represents the momentum being transferred by the operator.
-We consider the two cases separately.
-
-\subsubsection{Momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] = 0\)}
-For these operators, the expression for the correlation gives
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
-										 &=\sum_{{\bf r},{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-To obtain the last form, we defined \({\bf \Delta}={\bf r}_2 - {\bf r}_1\) as the distance between the incoming and outgoing auxiliary model states, and preformed the sum over the free variable \({\bf r}_1\) to cancel out the factor of \(1/N\).
-Just like before, this expression can be decomposed into a term that involves a single auxiliary model and other terms that involve two distinct auxiliary models.
-
-\subsubsection{Non-momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] \neq 0\)}
-This class of operators incur an additional phase factor of \(e^{-{\bf a}\cdot{\bf 2k}}\) when the translation operators are translated across them:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}e^{2i\left( {\bf r}_1 - {\bf r}_c \right) \cdot \left( {\bf k}_1 - {\bf k}_2 \right)} \\
-										 &= \delta_{{\bf k}_1, {\bf k}_2}\sum_{{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-For this expression, we again defined \({\bf \Delta}\) similar to before, and carried out the sum of \({\bf r}_1\) involving the exponential to obtain a factor of \(N \delta_{{\bf k}_1, {\bf k}_2}\).
-The Kronecker delta factor is a manifestation of translational invariance and the associated total momentum conservation.
-
-As it stands, operators like \(\mathcal{O}({\bf k}_1)\) act purely on the conduction bath degrees of freedom.
-In order to incorporate impurity-bath correlation effects, we modify these operators using the appropriate \(T-\)matrices, by employing eq.~\ref{operatorTmatrix}.
-The final computations are carried out using these modified operators.
-
-\section{Entanglement measures}
-In order to relate bipartite measures of entanglement (such as the entanglement entropy and mutual information) across the tiling algorithm, we will express the matrix elements of an arbitrary reduced density matrix (RDM) in terms of generalised correlation functions.
-Since these correlation functions can always be computed using the algorithm provided in the previous section, this suffices to compute the RDM using auxiliary model calculations.
-If the RDM is known, other bipartite measures can be easily calculated.
-
-We consider the \(T=0\) density matrix, \(\tilde\rho_\text{gs} = \ket{\Psi}_\text{gs}\bra{{\Psi}_\text{gs}}\) of the lattice model, and a division of the total degrees of freedom (real or momentum space) into two sets \(A\) and \(B\).
-If basis set for the two subsystems are \(\left\{ \ket{A_i} \right\} \) and \(\left\{ B_j \right\} \), the ground state can be written as
-\begin{equation}\begin{aligned}
-	\ket{\Psi}_\text{gs} = \sum_{i,j}C_{i,j}\ket{A_i}\ket{B_j}~.
-\end{aligned}\end{equation}
-Tracing out the states of subsystem B leads to the RDM for subsystem A:
-\begin{equation}\begin{aligned}
-	\tilde \rho^{(A)} = \sum_k\braket{B_k | \rho | B_k} = \sum_{{i_1},{i_2}, k}C_{{i_1},k}C^*_{{i_2},k}\ket{A_{i_1}}\bra{A_{i_2}},~~\tilde \rho^{(A)}_{{i_1},{i_2}} = \sum_k C_{{i_1},k}C^*_{{i_2},k}~.
-\end{aligned}\end{equation}
-We will now show that the product of coefficients \(C_{i,k}C^*_{j,k}\) can also be obtained through expectation value calculations of product operators in the subspace of \(A\).
-Consider the following transition operator:
-\begin{equation}\begin{aligned}
-	P^{(A)}_{i_1,i_2} = \ket{A_{i_1}}\bra{A_{i_2}}~.
-\end{aligned}\end{equation}
-The RDM elements are expectation values of this operator in the ground state:
-\begin{equation}\begin{aligned}
-	\braket{P^{(A)}_{i_1,i_2}} = \sum_k C_{{i_1},k}C^*_{{i_2},k} = \tilde \rho^{(A)}_{{i_1},{i_2}}~.
-\end{aligned}\end{equation}
-
-We now argue that these expectation values are simply correlation functions corresponding to products of local operators.
-If the subsystem \(A\) is composed of \(N_A\) one-particle Hilbert spaces \(A^{(\nu)}\), any basis state \(\ket{A_{i}}\) can be written as the product of one-particle basis states:
-\begin{equation}\begin{aligned}
-	\ket{A_i} = \otimes_{\nu=1}^{N_A}\ket{s_\nu(A_i)}~,
-\end{aligned}\end{equation}
-where \(s_\nu(A_i)\) can be 0 or 1 and represents the configuration (occupied/unoccupied) of the local degree of freedom \(A^{(\nu)}\) in the basis state \(\ket{A_i}\), and \(\ket{s_\nu(A_i)}\) is the state of \(A^{(\nu)}\) in that configuration.
-The transition operator \(P^{(A)}_{i_1,i_2}\) can therefore be written as
-\begin{equation}\begin{aligned}
-	P^{(A)}_{i_1,i_2} = \ket{s_1(A_{i_1})}\otimes\ket{s_2(A_{i_1})} \ldots\otimes\ket{s_{N_A}(A_{i_1})}\bra{s_{N_A}(A_{i_2})}\otimes\ldots\bra{s_2(A_{i_2})}\otimes\bra{s_1(A_{i_2})}~.
-\end{aligned}\end{equation}
-This can be converted into a second-quantised operator, by making the substitution:
-\begin{equation}\begin{aligned}
-	\ket{s} \to 
-	\begin{cases}
-		c^\dagger,~\text{if }s=1,\\
-		1-n,~\text{if }s=0,	
-	\end{cases}~.
-\end{aligned}\end{equation}
-As an example, for a two-qubit subspace \(A\), the transition operator \(P^{(A)}_{00,01}\) between the states \(i_1=00\) (both unoccupied) and \(i_2=01\) (only one occupied) can be expressed as
-\begin{equation}\begin{aligned}
-	P^{(A)}_{00,01} = \ket{0}_1\ket{0}_2\bra{1}_2\bra{0}_1 = (1-n_1)(1-n_2)(1-n_2)c_1 = c_1(1-n_2)~.
-\end{aligned}\end{equation}
-This means the RDM element for this subspace, at the location \((00, 01)\), is equal to the ground state expectation value of the operator \(c_1(1-n_2)\).
-The process of calculating such expectation values, within the present algorithm, has already been explained in Sec.~\ref{staticCorr}.
-Note that this allows the computation of reduced density matrix for real-space as well as momentum-space partitioning.
-
-Other measures like mutual information can be obtained by using these elementary measures.
-
-\section{Metal-insulator transition in the Lattice Model}
-\subsection{Momentum-space picture etc etc}
-In order to understand the nature of the transition in momentum space, we employ the expression obtained in the previous sections and compute the spectral function, self-energy and correlation functions in the top right quadrant of the first Brillouin zone.
-We first show the \(k-\)space spectral functions near zero frequency, in Fig.~\ref{kspace_specfunc}.
+\section{Journey Through the Pseudogap on The Lattice model}
+We have already seen from the lattice-embedded impurity model that the impurity phase transition is anisotropic in \(k-\)space.
+This has consequences for the metal-insulator transition of the lattice model.
+We now describe, in terms of correlations, how the Fermi surface of the lattice model is destabilised when the system is tuned through the pseudogap.
+For this, we employ the relations we derived between correlations on the impurity model and those on the lattice model.
+
+\subsection{One-particle \(k-\)space spectral function}
 \begin{figure}[htpb]
 	\centering
-	\includegraphics[width=0.23\textwidth]{tiledSF-1.pdf}
-	\includegraphics[width=0.23\textwidth]{tiledSF-2.pdf}
-	\caption{tiledSF.pdf}
+	\includegraphics[width=0.23\textwidth]{kspaceDOS-1.pdf}
+	\includegraphics[width=0.23\textwidth]{kspaceDOS-2.pdf}
+	\includegraphics[width=0.23\textwidth]{kspaceDOS-3.pdf}
+	\includegraphics[width=0.23\textwidth]{kspaceDOS-4.pdf}
+	\caption{One-particle \(k-\)space spectral function.
+In the absence of bath interactions, all points on Fermi surface are gapless (first panel).
+Proceeding through the pseudogap results in the gapping out of Fermi surface points starting from the antinode (second panel) and approaching the node (third panel), until finally only the node remains at the critical point (fourth panel).}
 	\label{fig:tiledSF-pdf}
 \end{figure}
-% \begin{figure*}[htpb]
-% 	\centering
-% 	\includegraphics[width=\textwidth]{charge-p-p_37_-2.0_-1.7297_-0.0_0.1.pdf}
-% \end{figure*}
-% \begin{figure*}[htpb]
-% 	\centering
-% 	\includegraphics[width=\textwidth]{vne-p-p_37_-2.0_-1.7297_-0.0_0.1.pdf}
-% \end{figure*}
+
+\subsection{Momentum-space spin-correlations}
+We first look at static spin correlations \(\chi_s(k_1, k_2) = \frac{1}{2}\left<S_{k_1}^+ S_{k_2}^- + \text{h.c.} \right>\).
+These processes correspond to the gapless excitations of the Fermi liquid phase.
+We find that
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.24\textwidth]{tiledSF-1.pdf}
+	\includegraphics[width=0.24\textwidth]{tiledSF-2.pdf}
+	\includegraphics[width=0.24\textwidth]{tiledSF-3.pdf}
+	\includegraphics[width=0.24\textwidth]{tiledSF-4.pdf}
+	\caption{Spin-flip correlations \(\left<S(k_N)^+, S({\bf k})^-\right>\) between the nodal point \(k_N = \left( -\pi/2, -\pi/2\right)\) and an arbitrary \(k-\)point on the Fermi surface.
+In the absence of bath interaction (first panel), the correlations are somewhat uniformly distributed along the Fermi surface.
+As we enter the pseudogap (second panel), the spin-correlations near the antinode vanish, indicating that they have been removed from the metallic excitations.
+Passing through the pseudogap involves in the extensions of the gapped region (third panel), until finally only the node remains (fourth panel).}
+	\label{tiledSF}
+\end{figure}
 
@@
 \label{appx-spectral-func}
-The impurity retarded Green's function (assuming the Hamiltonian to be time-independent, which it is) is defined as
-\begin{equation}\begin{aligned}
-	G_{dd}^\sigma(t) = -i\theta(t) \left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right>
-\end{aligned}\end{equation}
-where the average \(\left< \right>\) is over a canonical ensemble at temperature \(T\), and \(\mathcal{O}_\sigma = c_{d\sigma} + S_d^- c_{0\overline\sigma} + S_d^z c_{0\sigma}\) is the excitation whose spectral function we are interested in.
-The excitations defined in \(\mathcal{O}\) incorporates both single-particle excitations brought about by the hybridisation as well as two-particle spin excitations brought about by the spin-exchange term.
-What follows is a standard calculation where we write the Green's function in the Lehmann-Kallen representation.
-The ensemble average for an arbitrary operator \(\hat M\) can be written in terms of the exact eigenstates of the fixed point Hamiltonian:
-\begin{equation}\begin{aligned}
-	H^* \ket{n} &= E_n^* \ket{n}, ~ ~ ~\left<\hat M \right> &\equiv \frac{1}{Z}\sum_n \bra{n} \hat M \ket{n} e^{-\beta E_n^*}
-\end{aligned}\end{equation}
-where \(Z = \sum_n e^{-\beta E_n^*}\) is the fixed point partition function and \(\left\{ \ket{n} \right\} \) is the set of eigenfunctions of the fixed point Hamiltonian. We can therefore write
+
+\subsection{Spectral representation of Greens function}
+The impurity retarded Green's function is defined as
+\begin{equation}\begin{aligned}
+	G_{d\sigma}(t) = -i\theta(t) \left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right>
+\end{aligned}\end{equation}
+where the average \(\left< \right>\) is over a canonical ensemble at temperature \(T\), and \(\mathcal{O}_\sigma\) is the excitation whose spectral function we are interested in.
+What follows is a standard calculation where we write the Green's function in the spectral representation.
+The ensemble average for the operator \(\mathcal{O}_\sigma\) can be written in terms of the exact eigenstates of the Hamiltonian:
+\begin{equation}\begin{aligned}
+	H \ket{n} &= E_n \ket{n}, \quad\left<\mathcal{O}_\sigma\right> &\equiv \frac{1}{Z}\sum_n \braket{n | \mathcal{O}_\sigma | n} e^{-\beta E_n}
+\end{aligned}\end{equation}
+where \(Z = \sum_n e^{-\beta E_n}\) is the partition function and \(\left\{ \ket{n} \right\} \) is the set of eigenfunctions of the Hamiltonian. We can therefore write
 \begin{equation}\begin{aligned}
@@
 \begin{equation}\begin{aligned}
-	G_{dd}^\sigma = -i\theta(t)\frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
+	G_{d\sigma} = -i\theta(t)\frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega) &= \int_{-\infty}^\infty dt e^{i \omega t}G_{d d}^\sigma(t) \\
-			       &= \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t}
+	G_{d d}^\sigma(\omega) &= \int_{-\infty}^\infty dt e^{i \left(\omega \right)t}G_{d d}^\sigma(t) \\
+			       &= \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left(\omega + E_m - E_n \right)t}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\theta(t) = \frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty \frac{1}{x- i\eta}e^{ixt}dx
-\end{aligned}\end{equation}
-With this definition, the integral in \(G_{dd}^\sigma(\omega)\) becomes
-\begin{equation}\begin{aligned}
-	\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + E_m - E_n \right)t} &= \left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta}\int_{-\infty}^\infty dt e^{i\left( \omega + E_m - E_n + x\right)t} \\
-									     &=\left(-i\right)\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x- i\eta} 2\pi \delta\left( \omega + E_m - E_n + x\right) \\
-									     &=\left(-i\right)\frac{1}{i}\lim_{\eta \to 0^+} \frac{-1}{\omega + E_m - E_n- i\eta} \\
-									     &=\frac{1}{\omega + E_m - E_n} \\
+	\theta(t) = -\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty \frac{1}{x + i\eta}e^{-ixt}dx
+\end{aligned}\end{equation}
+With this definition, the integral in \(G_{d\sigma}(\omega)\) becomes
+\begin{equation}\begin{aligned}
+	\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + i0^+ + E_m - E_n \right)t} &= \left(-i\right)\frac{-1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x+ i\eta}\int_{-\infty}^\infty dt e^{i\left( \omega + i0^+ + E_m - E_n - x\right)t} \\
+									     &=\frac{1}{2\pi}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x+ i\eta} 2\pi \delta\left( \omega + i0^+ + E_m - E_n - x\right) \\
+									     &=\frac{1}{\omega + E_m - E_n + i0^+}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n}
-\end{aligned}\end{equation}
-The zero temperature Green's function is obtained by taking the limit of \(\beta \to \infty\).
-In both the partition function as well as inside the summation, the only term that will survive is the exponential of the ground state energy \(E_0\).
+	G_{d d}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n + i0^+}
+\end{aligned}\end{equation}
+The infinitesimally positive imaginary part in the denominator shifts the poles onto the lower half of the complex plane, leaving it analytic in the upper half: this is necessary to make the retarded Greens function causal.
+
+\subsection{Real and imaginary parts - The Sokhotski-Plemelj theorem}
+In order to write down the real and imaginary parts of the Greens function, we first prove the {\it Sokhotski-Plemelj} formula:
+\begin{equation}\begin{aligned}\label{SokhotskiPlemelj}
+	\lim_{\eta \to 0^+} \frac{1}{x + i \eta} = P\left(\frac{1}{x}\right) - i \pi \delta(x)~.
+\end{aligned}\end{equation}
+where \(P(f(x))\) is the Cauchy principal value, defined as 
+\begin{equation}\begin{aligned}
+	P\left[\int_{-\infty}^{\infty}\frac{dx}{x}\right] = \int_{-\infty}^{0^-}\frac{dx}{x} + \int_{0^+}^{\infty}\frac{dx}{x}~.
+\end{aligned}\end{equation}
+
+To prove the above identity, we integrate the left-hand side using a test function \(f(x)\):
+\begin{equation}\begin{aligned}\label{twoIntegrals}
+	\lim_{\eta \to 0^+}\int_{-\infty}^{\infty} \text{dx}~\frac{f(x)}{x + i \eta} &= \lim_{\eta \to 0^+}\int_{-\infty}^{\infty} \text{dx}~\frac{f(x)\left( x - i\eta \right) }{x^2 + \eta^2} \\
+																				 &= \lim_{\eta \to 0^+}\int_{-\infty}^{\infty} \text{dx}~f(x)\left[\frac{x}{x^2 + \eta^2} - i\eta\frac{1}{x^2 + \eta^2}\right]
+\end{aligned}\end{equation}
+The first integral can be split into three parts:
+\begin{equation}\begin{aligned}
+	\lim_{\eta \to 0^+}\int_{-\infty}^{\infty} \text{dx}~f(x)\frac{x}{x^2 + \eta^2} &= \lim_{\eta \to 0^+}\lim_{\varepsilon_\to 0^+}\left[\int_{-\infty}^{-\varepsilon} \text{dx}~\frac{f(x) x}{x^2 + \eta^2} + \int_{\varepsilon}^{\infty} \text{dx}~\frac{f(x)x}{x^2 + \eta^2} + \int_{-\varepsilon}^{\varepsilon} \text{dx}~\frac{f(x)x}{x^2 + \eta^2}\right]
+\end{aligned}\end{equation}
+For the first two parts, it is safe to take the limit of \(\eta\), because \(x\) is always non-vanishing there.
+For the third part, we can approximate \(f(x)\) as \(f(0)\) in the neighbourhood \(x \in \left[-\varepsilon, \varepsilon\right], \varepsilon \to 0 \).
+This leaves an odd function \(x/(x^2 + \eta^2)\) as the integrand, being integrated over a symmetric range.
+The third term therefore vanishes.
+In total, we get
+\begin{equation}\begin{aligned}\label{integral1}
+	\lim_{\eta \to 0^+}\int_{-\infty}^{\infty} \text{dx}~f(x)\frac{x}{x^2 + \eta^2} &= \int_{-\infty}^{-\varepsilon} \text{dx}~\frac{f(x)}{x} + \int_{\varepsilon}^{\infty} \text{dx}~\frac{f(x)}{x}  = P\left(\int_{-\infty}^{\infty} \text{dx}~\frac{f(x)}{x}\right) ~.
+\end{aligned}\end{equation}
+To evaluate the second integral of eq.~\ref{twoIntegrals}, we note that the only region in which the integrand is non-zero is when \(|x| \simeq 0\); there, we again approximate \(f(x)\) as \(f(0)\).
+The remaining integral can then be evaluated easily:
+\begin{equation}\begin{aligned}\label{integral2}
+	-i\lim_{\eta \to 0^+}\eta\int_{-\infty}^{\infty} \text{dx}~\frac{f(x)}{x^2 + \eta^2} = -i \lim_{\eta \to 0^+}\eta f(0)\int_{-\infty}^{\infty} \frac{\text{dx}}{x^2 + \eta^2} = -i \pi f(0),
+\end{aligned}\end{equation}
+where we used \(\int \frac{dx}{x^2 + \eta^2} = \frac{1}{\eta} \arctan\left( x/\eta \right) \). Combining eqs.~\ref{twoIntegrals},\ref{integral1} and \ref{integral2}, we get
+\begin{equation}\begin{aligned}
+	\lim_{\eta \to 0^+}\int_{-\infty}^{\infty} \text{dx}~\frac{f(x)}{x + i \eta} = P\left(\int_{-\infty}^{\infty} \text{dx}~\frac{f(x)}{x}\right) - i\pi \int_{-\infty}^{\infty} \text{dx}~f(x)\delta(x)~.
+\end{aligned}\end{equation}
+This proves eq.~\ref{SokhotskiPlemelj}.
+
+The Sokhotski-Plemelj formula allows us to split the spectral representation into a real and an imaginary part:
+\begin{equation}\begin{aligned}
+	G_{d\sigma}^\prime = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)P\left(\frac{1}{\omega + E_m - E_n}\right)\\
+	G_{d\sigma}^{\prime\prime} = -\pi\frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\delta\left(\omega + E_m - E_n\right)~.
+\end{aligned}\end{equation}
+The spectral function, specifically, is defined as follows:
+\begin{equation}\begin{aligned}
+	A_{d\sigma}(\omega) = -\frac{1}{\pi}G_{d\sigma}^\prime = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\delta\left(\omega + E_m - E_n\right)
+\end{aligned}\end{equation}
+
+\subsection{Zero temperature spectral function}
+We specialise to zero temperature by taking the limit of \(\beta \to \infty\).
+In both the partition function as well as inside the summation, the only term that will survive is the exponential of the ground state energy \(E_\text{GS}\).
 \begin{equation*}\begin{aligned}
-	Z \equiv \sum_m e^{-\beta E_m} \implies \lim_{\beta \to \infty}Z = d_0 e^{-\beta E_0}, && E_0 \equiv \text{min}\left\{ E_n \right\} 
+	Z \equiv \sum_m e^{-\beta E_m} \implies \lim_{\beta \to \infty}Z = d_\text{GS} e^{-\beta E_\text{GS}}, && E_\text{GS} \equiv \text{min}\left\{ E_n \right\} 
 \end{aligned}\end{equation*}
-where \(d_0\) is the degeneracy of the ground state. The Greens function then simplifies to
+where \(d_\text{GS}\) is the degeneracy of the ground state. The spectral function then simplifies to
 \begin{equation}\begin{aligned}
 	\label{Gf_lk}
-	G_{d d}^\sigma(\omega, \beta \to \infty) &= \frac{1}{d_0e^{-\beta E_0}}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left[e^{-\beta E_m}\delta_{E_m, E_0} + e^{-\beta E_n}\delta_{E_n, E_0}\right]\frac{1}{\omega + E_m - E_n}\\
-						 &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n}\right]\\
-\end{aligned}\end{equation}
-The label 0 sums over all states \(\ket{0}\) with energy \(E_0\).
-The spectral function is the imaginary part of this Green's function.
-To extract the imaginary part, we insert an infinitesimal imaginary part in the denominator:
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega, \eta) = \frac{1}{d_0}\lim_{\eta \to 0^-}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\frac{1}{\omega + E_0 - E_n + i\eta} + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\frac{1}{\omega - E_0 + E_n + i\eta}\right]\\
-\end{aligned}\end{equation}
-The spectral function at zero temperature can then be written as
-\begin{equation}\begin{aligned}
-	\mathcal{A(\omega)} &= -\frac{1}{\pi}\text{ Im }\left[G_{dd}^\sigma\left( \omega \right) \right] \\
-			    &= \frac{1}{d_0}\frac{1}{\pi}\text{ Im }\left[\lim_{\eta \to 0^-}\sum_{n,0}\left(\frac{-i\eta ||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2}{\left(\omega + E_0 - E_n\right)^2 + \eta^2} + \frac{-i\eta ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2}{\left(\omega - E_0 + E_n\right)^2 + \eta^2}\right)\right]\\
-			    &= \frac{1}{d_0}\frac{1}{\pi}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\pi\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\pi\delta\left(\omega - E_0 + E_n\right)\right]\\
-			    &= \frac{1}{d_0}\sum_{n,0}\left[||\bra{0}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_0 - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{0}||^2\delta\left(\omega - E_0 + E_n\right)\right]\\
-\end{aligned}\end{equation}
+	A_{d\sigma} &= \frac{1}{d_\text{GS}e^{-\beta E_\text{GS}}}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left[e^{-\beta E_m}\delta_{E_m, E_\text{GS}} + e^{-\beta E_n}\delta_{E_n, E_\text{GS}}\right]\delta\left(\omega + E_m - E_n\right)\\
+											 &= \frac{1}{d_\text{GS}}\sum_{n,n_\text{GS}}\left[||\bra{n_\text{GS}}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_\text{GS} - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{n_\text{GS}}||^2\delta\left(\omega - E_\text{GS} + E_n\right)\right]\\
+\end{aligned}\end{equation}
+The label \(n_\text{GS}\) sums over all states \(\ket{n_\text{GS}}\) with energy \(E_\text{GS}\).
+In practise, we evaluate this expression by replacing the formal Dirac delta functions with "nascent" ones, such as a Lorentzian function with a sufficiently sharp peak.
+
+\subsection{Reconstructing full Green function from spectral function: Kramers-Kronig relations}
+As mentioned earlier, the retarded Greens function \(G_R(\omega + i 0^+)\) has a complex pole in the lower half of the complex plane.
+In the following, the frequency \(\omega\) is assumed to be complex.
+Consider the integral
+\begin{equation}\begin{aligned}
+	I(\omega) = \oint_C d\omega^\prime \frac{G_R(\omega^\prime)}{\omega^\prime - \omega},~\omega \in \mathbb{R}~.
+\end{aligned}\end{equation}
+The contour \(C\) encloses the entirety of the upper half of the complex plane as well as almost all points of the real line but avoids the pole at \(\omega^\prime = \omega\) by forming a semicircle about that point that extends into the upper half of the plane.
+Since the integrand is completely analytic in the region enclosed by the contour (recall again that \(G_R\) is analytic in the upper half), the integral evaluates to zero (by Cauchy's theorem):
+\begin{equation}\begin{aligned}\label{zerointegral}
+	I(\omega) = 0~.
+\end{aligned}\end{equation}
+One can also evaluate the integral along each part of the contour.
+The semicircular part contributes zero: this is because while the length of the semicircular arc goes as \(|\omega^\prime|\), the integrand vanishes faster than \(1/|\omega^\prime|\) as \(|\omega^\prime| \to \infty\) (this assumes that the Green function vanishes in the limit of \(\omega \to \infty\)).
+The part of the contour along the real axis can now be evaluated.
+The two parts of the contour on either side of the pole contribute
+\begin{equation}\begin{aligned}
+	\int_{-\infty}^{\omega - 0^+}d\omega^\prime~\frac{G_R(\omega^\prime)}{\omega^\prime - \omega} + \int_{\omega + 0^+}^{\infty}d\omega^\prime~\frac{G_R(\omega^\prime)}{\omega^\prime - \omega} = P\int_{-\infty}^{\infty}d\omega^\prime~\frac{G_R(\omega^\prime)}{\omega^\prime - \omega}
+\end{aligned}\end{equation}
+To evaluate the part of the integral along the small semicircular around \(\omega^\prime = \omega\) (that extends into the upper half), we argue that this contribution should be equal to that obtained by taking the semicircle that goes instead into the lower half but circulates in the opposite direction.
+Each of these contributions should, in turn, be equal to that obtained from joining these two contours.
+But joining these contours leads to a closed integral about the pole at \(\omega^\prime = \omega\), which is equal to \(2\pi G_R(\omega)\).
+\begin{equation}\begin{aligned}
+	\int_\text{upper} d\omega^\prime~\frac{G_R(\omega^\prime)}{\omega^\prime - \omega} = \int_\text{lower} d\omega^\prime~\frac{G_R(\omega^\prime)}{\omega^\prime - \omega} = \frac{1}{2}\oint_{C(\omega)} d\omega^\prime~\frac{G_R(\omega^\prime)}{\omega^\prime - \omega} = i\pi G_R(\omega)~.
+\end{aligned}\end{equation}
+Combining the last two equations, we get
+\begin{equation}\begin{aligned}
+	I(\omega) = P\int_{-\infty}^{\infty}d\omega^\prime~\frac{G_R(\omega^\prime)}{\omega^\prime - \omega} + i\pi G_R(\omega)~.
+\end{aligned}\end{equation}
+Comparing with eq.~\ref{zerointegral} and separating into real part \(G_R^\prime\) and imaginary part \(G_R^{\prime\prime}\) gives
+\begin{equation}\begin{aligned}
+	P\int_{-\infty}^{\infty}d\omega^\prime~\frac{\left[G_R^\prime(\omega^\prime) + i G_R^{\prime\prime}(\omega^\prime)\right]}{\omega^\prime - \omega} + \pi\left[-G_R^{\prime\prime}(\omega) + i G_R^\prime(\omega) \right]= 0~.
+\end{aligned}\end{equation}
+Comparing the imaginary parts gives
+\begin{equation}\begin{aligned}
+	\pi G_R^\prime(\omega) = P\int_{-\infty}^{\infty}d\omega^\prime~\frac{G_R^{\prime\prime}(\omega^\prime)}{\omega^\prime - \omega}~.
+\end{aligned}\end{equation}
+The spectral function was defined above as \(-1/\pi\) times the imaginary part of the Greens function. Exchanging \(G_R^{\prime\prime}\) for \(A\) gives
+\begin{equation}\begin{aligned}
+	G_R^\prime(\omega) = -P\int_{-\infty}^{\infty}d\omega^\prime~\frac{A(\omega^\prime)}{\omega^\prime - \omega}~.
+\end{aligned}\end{equation}
+This provides a way of calculating the real part of the Greens function if the spectral function is already known.
 

### 2025-02-26 numerics/caller.jl

@@ -1,7 +1,7 @@
 using Distributed, Random
 
 if length(Sys.cpu_info()) > 10 && nprocs() == 1
-    addprocs(8)
+    addprocs(3)
 end
 @everywhere using LinearAlgebra, CSV, JLD2, FileIO, CodecZlib
 
@@ -13,10 +13,10 @@ include("./source/plotting.jl")
 
 global J_val = 0.1
 @everywhere global orbitals = ("p", "p")
-maxSize = 1000
+maxSize = 2000
 WmaxSize = 500
 
-colmap = ColorSchemes.viridis # ColorSchemes.thermal # reverse(ColorSchemes.cherry)
+colmap = ColorSchemes.thermal # ColorSchemes.thermal # reverse(ColorSchemes.cherry)
 numShells = 1
 bathIntLegs = 2
 NiceValues(size_BZ) = Dict{Int64, Vector{Float64}}(
@@ -169,7 +169,7 @@ function AuxiliaryCorrelations(
     x_arr = get_x_arr(size_BZ)
     W_val_arr = NiceValues(size_BZ)
     @time kondoJArrays, dispersion = RGFlow(W_val_arr, size_BZ; loadData=true)
-    spinCorrelation = Dict("SF" => [nothing, (i, j) -> [
+    spinCorrelation = Dict{String, Tuple{Union{Nothing, Int64}, Function}}("SF" => (nothing, (i, j) -> [
                                              ("nn", [1, 2, 2 * i + 1, 2 * i + 1], -0.25),
                                              ("nn", [1, 2, 2 * i + 2, 2 * i + 2], 0.25),
                                              ("nn", [2, 1, 2 * i + 1, 2 * i + 1], 0.25),
@@ -177,22 +177,22 @@ function AuxiliaryCorrelations(
                                              ("+-+-", [1, 2, 2 * i + 2, 2 * i + 1], -0.5),
                                              ("+-+-", [2, 1, 2 * i + 1, 2 * i + 2], -0.5),
                                             ]
-                                   ]
+                                   )
                           )
     node = map2DTo1D(-π/2, -π/2, size_BZ)
     antinode = map2DTo1D(-π, 0., size_BZ)
 
-    chargeCorrelation = Dict(
-                             "doubOcc" => [nothing, (i, j) -> [("nn", [2 * i + 1, 2 * i + 2], 1.), ("hh", [2 * i + 1, 2 * i + 2], 0.)]
[…]

### 2025-02-26 numerics/source/probes.jl

@@ -62,7 +62,7 @@ end
         maxSize::Int64,
         pivotPoints::Vector{Int64},
         sortedPoints::Vector{Int64},
-        correlationFuncDict::Dict,
+        correlationFuncDict::Dict{String, Tuple{Union{Nothing, Int64}, Function}},
         vneFuncDict::Dict,
         mutInfoFuncDict::Dict,
         bathIntLegs::Int64,
@@ -262,7 +262,7 @@ end
 @everywhere function AuxiliaryCorrelations(
         hamiltDetails::Dict,
         numShells::Int64,
-        correlationFuncDict::Dict,
+        correlationFuncDict::Dict{String, Tuple{Union{Nothing, Int64}, Function}},
         maxSize::Int64,
         savePath::String;
         vneFuncDict::Dict=Dict(),
@@ -351,16 +351,6 @@ end
         corrResultsBool[name] = [ifelse(isnan(r), r, abs(r) ≤ 1e-6 ? -1 : 1) for r in results]
     end
     return corrResults, corrResultsBool
-end
-
-
-function localSpecFuncAverage(
-        argsNode,
-        argsAntinode
-    )
-    specFuncOuter = IterDiagSpecFunc(argsNode...)
-    specFuncOuter .+= IterDiagSpecFunc(argsAntinode...)
-    return specFuncOuter
 end
 
 
@@ -560,6 +550,7 @@ function LatticeKspaceDOS(
 
     return specFuncKSpace, localSpecFunc, standDevFinal, results
 end
+
 
 
 @everywhere function PhaseIndex(

### 2025-02-27 TilingProjectDraft/tilingProject.tex
added entanglement plots

@@
 	\label{tiledSF}
+\end{figure}
+
+\subsection{Entanglement entropy and Mutual information}
+\begin{figure}[htpb]
+	\includegraphics[width=0.24\textwidth]{S_k-1.pdf}
+	\includegraphics[width=0.24\textwidth]{S_k-2.pdf}
+	\includegraphics[width=0.24\textwidth]{S_k-3.pdf}
+	\includegraphics[width=0.24\textwidth]{S_k-4.pdf}
+\end{figure}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.24\textwidth]{I2_k_N-1.pdf}
+	\includegraphics[width=0.24\textwidth]{I2_k_N-2.pdf}
+	\includegraphics[width=0.24\textwidth]{I2_k_N-3.pdf}
+	% \includegraphics[width=0.24\textwidth]{I2_k_N-4.pdf}
 \end{figure}
@@
 \begin{equation}\begin{aligned}
-	\pi G_R^\prime(\omega) = P\int_{-\infty}^{\infty}d\omega^\prime~\frac{G_R^{\prime\prime}(\omega^\prime)}{\omega^\prime - \omega}~.
-\end{aligned}\end{equation}
-The spectral function was defined above as \(-1/\pi\) times the imaginary part of the Greens function. Exchanging \(G_R^{\prime\prime}\) for \(A\) gives
-\begin{equation}\begin{aligned}
-	G_R^\prime(\omega) = -P\int_{-\infty}^{\infty}d\omega^\prime~\frac{A(\omega^\prime)}{\omega^\prime - \omega}~.
-\end{aligned}\end{equation}
-This provides a way of calculating the real part of the Greens function if the spectral function is already known.
+	G_R^\prime(\omega) = \frac{1}{\pi}P\int_{-\infty}^{\infty}d\omega^\prime~\frac{G_R^{\prime\prime}(\omega^\prime)}{\omega^\prime - \omega} = - \mathcal{H}\left[G_R^{\prime\prime}(\omega)\right] ~,
+\end{aligned}\end{equation}
+where \(\mathcal{H}\left[g(\omega)\right]=\frac{1}{\pi}P\int_{-\infty}^{\infty}d\omega^\prime~\frac{g(\omega^\prime)}{\omega - \omega^\prime}\) is the Hilbert transform of the function \(g(\omega)\).
+The spectral function was defined above as \(-1/\pi\) times the imaginary part of the Greens function.
+Exchanging \(G_R^{\prime\prime}\) for \(A\) gives
+\begin{equation}\begin{aligned}
+	G_R^\prime(\omega) = \pi \mathcal{H}\left[A(\omega)\right]~.
+\end{aligned}\end{equation}
+This provides a method for calculating the real part of a Greens function if the spectral function is already known.
 

### 2025-02-27 numerics/caller.jl
added self-energy numerics

@@ -13,7 +13,7 @@ include("./source/plotting.jl")
 
 global J_val = 0.1
 @everywhere global orbitals = ("p", "p")
-maxSize = 2000
+maxSize = 1500
 WmaxSize = 500
 
 colmap = ColorSchemes.thermal # ColorSchemes.thermal # reverse(ColorSchemes.cherry)
@@ -299,24 +299,26 @@ function AuxiliaryLocalSpecfunc(
         fixHeight::Bool=false,
         loadData::Bool=false,
     )
-    W_val_arr = NiceValues(size_BZ)[[1]]
+    W_val_arr = NiceValues(size_BZ)
     if fixHeight
         @assert 0 ∈ W_val_arr
     end
     kondoJArrays, dispersion = RGFlow(W_val_arr, size_BZ; loadData=true)
-    freqValues = collect(-15:0.005:15)
-    freqValuesZoom1 = 13.
+    freqValues = collect(-20:0.001:20)
+    freqValuesZoom1 = 5.
     freqValuesZoom2 = 1.
-    specFuncResults = Dict{LaTeXString, Vector{Float64}}()
-    specFuncResultsTrunc = Dict{LaTeXString, Vector{Float64}}()
-    imagSelfEnergyResults = Dict{LaTeXString, Vector{Float64}}()
-    realSelfEnergyResults = Dict{LaTeXString, Vector{Float64}}()
+    specFuncResults = Tuple{LaTeXString, Vector{Float64}}[]
+    specFuncResultsTrunc = Tuple{LaTeXString, Vector{Float64}}[]
+    imagSelfEnergyResults = Tuple{LaTeXString, Vector{Float64}}[]
+    realSelfEnergyResults = Tuple{LaTeXString, Vector{Float64}}[]
     standDev = (0.1, 0.0 .+ exp.(abs.(freqValues) ./ maximum(freqValues)))
     targetHeight = 0.
     effective_Wval = 0.
     standDevGuess = 0.1
 
     standDevInner = standDev[1]
+
+    nonIntSpecFunc = nothing
     for W_val in W_val_arr
 
         if abs(W_val) > abs(transitionValues(size_BZ))
@@ -348,15 +350,21 @@ function AuxiliaryLocalSpecfunc(
             roundDigits = trunc(Int, log(1/maximum(specFunc)) + 7)
             jldsave(savePath; impSpecFunc=round.(specFunc, digits=roundDigits))
         end
[…]

### 2025-02-27 numerics/source/plotting.jl

@@ -111,7 +111,7 @@ end
 
 
 function plotLines(
-        nameValuePairs::Dict{LaTeXString, Vector{Float64}},
+        nameValuePairs::Vector{Tuple{LaTeXString, Vector{Float64}}},
         xvalues::Vector{Float64},
         xlabel::LaTeXString,
         ylabel::LaTeXString,

### 2025-02-27 numerics/caller.jl
entanglement fixes

@@ -13,7 +13,7 @@ include("./source/plotting.jl")
 
 global J_val = 0.1
 @everywhere global orbitals = ("p", "p")
-maxSize = 1500
+maxSize = 2000
 WmaxSize = 500
 
 colmap = ColorSchemes.thermal # ColorSchemes.thermal # reverse(ColorSchemes.cherry)
@@ -630,7 +630,7 @@ function TiledEntanglement(
         loadData::Bool=false,
     )
     x_arr = get_x_arr(size_BZ)
-    W_val_arr = NiceValues(size_BZ)
+    W_val_arr = NiceValues(size_BZ)[[5, 6]]
     kondoJArrays, dispersion = RGFlow(W_val_arr, size_BZ; loadData=true)
 
     vnEntropyArr = Float64[]
@@ -703,10 +703,10 @@ size_BZ = 33
 #=@time ScattProb(size_BZ; loadData=true)=#
 #=@time KondoCouplingMap(size_BZ)=#
 #=@time AuxiliaryCorrelations(size_BZ; loadData=false)=#
-@time AuxiliaryLocalSpecfunc(size_BZ; loadData=true, fixHeight=true)
+#=@time AuxiliaryLocalSpecfunc(size_BZ; loadData=true, fixHeight=true)=#
 #=@time AuxiliaryMomentumSpecfunc(size_BZ, (-π/2, -π/2); loadData=false)=#
 #=@time AuxiliaryMomentumSpecfunc(size_BZ, (-3π/4, -π/4); loadData=false)=#
 #=@time LatticeKspaceDOS(size_BZ; loadData=true)=#
 #=@time TiledSpinCorr(size_BZ; loadData=true)=#
 #=@time PhaseDiagram(size_BZ, 1e-3; loadData=false)=#
-#=@time TiledEntanglement(size_BZ; loadData=false);=#
+@time TiledEntanglement(size_BZ; loadData=false);

### 2025-02-27 numerics/source/probes.jl

@@ -113,7 +113,9 @@ end
                                                          hamiltDetails["orbitals"][2],
                                                          hamiltDetails["size_BZ"],
                                                          points)
-                            
+    if "chemPot" in keys(hamiltDetails)
+        hamiltDetails["dispersion"][pointsSequence] .+= hamiltDetails["chemPot"]
+    end    
     hamiltonian = KondoModel(
                              hamiltDetails["dispersion"][pointsSequence],
                              hamiltDetails["kondoJArray"][pointsSequence, pointsSequence],
@@ -139,7 +141,7 @@ end
                           hamiltonianFamily, 
                           maxSize;
                           symmetries=Char['N', 'S'],
-                          magzReq=(m, N) -> -1 ≤ m ≤ 2,
+                          #=magzReq=(m, N) -> -1 ≤ m ≤ 2,=#
                           occReq=(x, N) -> div(N, 2) - 3 ≤ x ≤ div(N, 2) + 3,
                           correlationDefDict=correlationDefDict,
                           vneDefDict=vneDefDict,

### 2025-03-13 TilingProjectDraft/tilingProject.tex
added channel decoupling discussion

@@
 As discussed immediately above, the Kondo spin-exchange term close to the transition does not lead to scattering of any \(k-\)state from \(S^+\) to \(S^-\).
+This is verified by calculating the ratio \(\text{max}\left\{ J_{k^+_1, k^-_2} \right\} / \text{max}\left\{ J_{k^+_1, k^+_2} \right\}\), where the maximum in the numerator is calculated from all the low-energy (fixed point) Kondo scattering processes that connect the two sets \(S^\pm\), while the denominator maximum is from within the set \(S^+\).
+This ratio vanishes (Fig.~\ref{channelDecoupling}) within the local pseudogap regime, indicating that no direct Kondo scattering process persists between the two sectors \(S^\pm\) at low energies, deep within the pseudogap regime.
+
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.45\textwidth]{quadrantMaxKondo-49.pdf}
+	\caption{}
+	\label{channelDecoupling}
+\end{figure}
+
 This is captured by the following simplified Hamiltonian:
@@
 	\includegraphics[width=0.24\textwidth]{S_k-1.pdf}
-	\includegraphics[width=0.24\textwidth]{S_k-2.pdf}
 	\includegraphics[width=0.24\textwidth]{S_k-3.pdf}
 	\includegraphics[width=0.24\textwidth]{S_k-4.pdf}
+	\includegraphics[width=0.24\textwidth]{S_k-5.pdf}
 \end{figure}
@@
 	\includegraphics[width=0.24\textwidth]{I2_k_N-1.pdf}
-	\includegraphics[width=0.24\textwidth]{I2_k_N-2.pdf}
 	\includegraphics[width=0.24\textwidth]{I2_k_N-3.pdf}
-	% \includegraphics[width=0.24\textwidth]{I2_k_N-4.pdf}
+	\includegraphics[width=0.24\textwidth]{I2_k_N-4.pdf}
+	\includegraphics[width=0.24\textwidth]{I2_k_N-5.pdf}
+\end{figure}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.24\textwidth]{I2_k_edge-1.pdf}
+	\includegraphics[width=0.24\textwidth]{I2_k_edge-3.pdf}
+	\includegraphics[width=0.24\textwidth]{I2_k_edge-4.pdf}
+	\includegraphics[width=0.24\textwidth]{I2_k_edge-5.pdf}
 \end{figure}

### 2025-03-13 numerics/caller.jl
finalised self-energy calculations

@@ -13,7 +13,7 @@ include("./source/plotting.jl")
 
 global J_val = 0.1
 @everywhere global orbitals = ("p", "p")
-maxSize = 15
+maxSize = 500
 WmaxSize = 500
 
 colmap = ColorSchemes.thermal # ColorSchemes.thermal # reverse(ColorSchemes.cherry)
@@ -188,7 +188,6 @@ function ChannelDecoupling(
         scattProbEncoup = maximum(kondoJArrays[W_val][pivotPoint, encoupledPoints, end])
         push!(acrossQuadrantStrengthRatio, scattProbDecoup / scattProbEncoup)
     end
-    println(acrossQuadrantStrengthRatio)
     W_val_decouple = W_val_arr[abs.(acrossQuadrantStrengthRatio) .< 1e-2][1]
 
     plotLines(Tuple{LaTeXString, Vector{Float64}}[("", acrossQuadrantStrengthRatio[1:1:end])],
@@ -343,24 +342,23 @@ function AuxiliaryLocalSpecfunc(
         fixHeight::Bool=false,
         loadData::Bool=false,
     )
-    W_val_arr = NiceValues(size_BZ)[[1, 3, 4]]
+    W_val_arr = NiceValues(size_BZ)[[1, 3, 5]]
     if fixHeight
         @assert 0 ∈ W_val_arr
     end
     kondoJArrays, dispersion = RGFlow(W_val_arr, size_BZ; loadData=true)
-    freqValues = collect(-20:0.0005:20)
-    freqValuesZoom1 = 10.
-    freqValuesZoom2 = 0.4
+    freqValues = collect(-200:0.01:200)
     specFuncFull = Tuple{LaTeXString, Vector{Float64}}[]
-    specFuncTrunc = Tuple{LaTeXString, Vector{Float64}}[]
     imagSelfEnergy = Tuple{LaTeXString, Vector{Float64}}[]
-    imagSelfEnergyTrunc = Tuple{LaTeXString, Vector{Float64}}[]
     realSelfEnergy = Tuple{LaTeXString, Vector{Float64}}[]
     quasipResidueArr = Float64[]
-    standDev = (0.1, 0.0 .+ exp.(abs.(freqValues) ./ maximum(freqValues)))
+    standDev = (0.5, exp.(abs.(freqValues).^2 ./ maximum(freqValues)))
     targetHeight = 0.
     effective_Wval = 0.
     standDevGuess = 0.1
[…]

### 2025-03-13 numerics/source/plotting.jl

@@ -14,6 +14,8 @@ update_theme!(
                 spinewidth = 1.5,
                 xticklabelsize = 24,
                 yticklabelsize = 24,
+                xminorgridvisible=false,
+                xmajorgridvisible=false,
                      ),
               ScatterLines = (
                        linewidth = 6,
@@ -125,12 +127,14 @@ function plotLines(
         ylabel::LaTeXString,
         saveName::String;
         ylimits::Union{Nothing, NTuple{2, Float64}}=nothing,
+        xlimits::Union{Nothing, NTuple{2, Float64}}=nothing,
         scatter::Bool=false,
         vlines::Vector{Tuple{AbstractString, Float64}}=Tuple{AbstractString, Float64}[],
         hlines::Vector{Tuple{AbstractString, Float64}}=Tuple{AbstractString, Float64}[],
         figSize::NTuple{2, Int64}=(300, 250),
         figPad::Union{Number, NTuple{4, Number}}=0,
         legendPos::String="rt",
+        linewidth::Number=4,
     )
     @assert legendPos ∈ Iterators.product(["r", "l", "c"], ["t", "b", "c"]) .|> join |> vec
 
@@ -146,11 +150,11 @@ function plotLines(
     markers = [:circle, :rect, :diamond, :hexagon, :xcross]
     for (i, (name, yvalues)) in enumerate(nameValuePairs)
         if !scatter
-            if !isempty(name)
-                lines!(xvalues, yvalues; label=name, linestyle=linestyles[((i - 1) % 6) + 1])
-                needsLegend = true
+            if isempty(name)
+                lines!(xvalues, yvalues; linestyle=linestyles[((i - 1) % 6) + 1], linewidth=linewidth)
             else
-                lines!(xvalues, yvalues; linestyle=linestyles[((i - 1) % 6) + 1])
+                lines!(xvalues, yvalues; label=name, linestyle=linestyles[((i - 1) % 6) + 1], linewidth=linewidth)
+                needsLegend = true
             end
         else
             if !isempty(name)
@@ -179,6 +183,9 @@ function plotLines(
 
     if !isnothing(ylimits)
         ylims!(ax, ylimits...)
+    end
+    if !isnothing(xlimits)
+        xlims!(ax, xlimits...)
     end
     resize_to_layout!(f)
 

### 2025-03-13 numerics/source/probes.jl

@@ -197,7 +197,6 @@ end
         broadFuncType::Union{String, Dict{String, String}}="gauss",
         normEveryStep::Bool=true,
         onlyCoeffs::Vector{String}=String[],
-        kondoTemp::Float64=1.,
     )
     if typeof(broadFuncType) == String
         broadFuncType = Dict(name => broadFuncType for name in specFuncDict)
@@ -217,12 +216,13 @@ end
                              couplingTolerance=1e-10,
                             )
 
+    kondoTemp = 1.0 * (sum(hamiltDetails["kondoJArray"][sortedPoints[1], sortedPoints] .|> abs) / sum(hamiltDetails["kondoJArray_bare"][sortedPoints[1], sortedPoints] .|> abs))^0.5
+
     # impurity local terms
-    impCorr = 5 * (2 + 5 * abs(hamiltDetails["W_val"]))
-    push!(hamiltonian, ("n",  [1], -impCorr/2)) # Ed nup
-    push!(hamiltonian, ("n",  [2], -impCorr/2)) # Ed ndown
-    push!(hamiltonian, ("nn",  [1, 2], impCorr)) # U nup ndown
-    excludeRange = (hamiltDetails["J_val_bare"], impCorr/4)
+    push!(hamiltonian, ("n",  [1], -hamiltDetails["imp_corr"]/2)) # Ed nup
+    push!(hamiltonian, ("n",  [2], -hamiltDetails["imp_corr"]/2)) # Ed ndown
+    push!(hamiltonian, ("nn",  [1, 2], hamiltDetails["imp_corr"])) # U nup ndown
+    excludeRange = (1.0 * maximum(hamiltDetails["kondoJArray_bare"]), hamiltDetails["imp_corr"]/4)
 
     indexPartitions = [10]
     while indexPartitions[end] < 2 + 2 * length(sortedPoints)
@@ -378,7 +378,6 @@ function AuxiliaryLocalSpecfunc(
         addPerStep::Int64=1,
         maxIter::Int64=20,
         broadFuncType::String="gauss",
-        kondoTemp::Float64=1.,
     )
     if targetHeight < 0
         targetHeight = 0
@@ -392,7 +391,7 @@ function AuxiliaryLocalSpecfunc(
     SWIndices = [p for p in 1:size_BZ^2 if 
                  #=map1DTo2D(p, size_BZ)[1] ≤ 0 &&=#
[…]

### 2025-03-31 TilingProjectDraft/tilingProject.tex
added new figures to notes

@@
 \section{Low-energy description of the embedded eSIAM}
-\subsection{Zero temperature phase diagram}
+\subsection{Zero temperature phase diagram and impurity site dynamics}
+The ground state phase diagram of the impurity model is shown in the left panel of Fig.~\ref{phaseDiagram}.
+We find that upon tuning the ratio \(W/J\) of the bath interaction strength \(W\) and the Kondo coupling \(J\), the impurity site undergoes a transition from a screened paramagnetic phase (dark green) to an unscreened local moment phase (yellow), through an intermediate pseudogapped regime (pink).
+The nature of pseudogapped phase will be clarified in the upcoming sections.
+The phase transition is seen through the evolution of the local spectral function (middle panel of Fig.~\ref{phaseDiagram}); increasing the ratio \(W/J\) leads to the sharpening of the central Kondo resonance, indicating that the local Fermi liquid excitations are becoming poorer.
+At the transition, the extremely sharp peak disappears and we are left with a hard gap at zero frequency.
+A complimentary picture is painted by the imaginary part \(\Sigma^{\prime\prime}\) of the impurity self-energy.
+The poles in \(\Sigma^{\prime\prime}\) are the edges of the central Kondo resonance, and its sharpening leads to the coalescing of the poles.
+
 \begin{figure}[htpb]
 	\centering
-	\includegraphics[width=0.23\textwidth]{phaseDiagram.pdf}
-	\includegraphics[width=0.24\textwidth]{impSpecFuncTrunc_49.pdf}
+	\includegraphics[width=0.32\textwidth]{phaseDiagram.pdf}
+	\includegraphics[width=0.32\textwidth]{impSpecFunc_49-1000.pdf}
+	\includegraphics[width=0.32\textwidth]{sigmaImag_49-1000.pdf}
 	\caption{{\bf Left}: Zero temperature phase diagram of the embedded impurity model, obtained by tracking impurity-bath spin correlations.
@@
 The red phase is a local pseudogap (L-PG)  phase, where a part of the Fermi surface (starting from the antinodal regions) no longer participates in Kondo screening.
-This leads to "Fermi arc"-like behaviour in the spin-correlations.
+This leads to "Fermi arc"-like behaviour in the spin-correlations and the \(k-\)space density of states.
 The black phase is a local moment (LM) phase, where the impurity is completely decoupled from the conduction electrons.
-{\bf Right}: Local spectral function of the impurity site.
+{\bf Middle}: Local spectral function of the impurity site.
 The blue curve is the normal Kondo resonance in the absence of any bath interaction.
 The yellow and green curves show the sharpening the spectral function through the locally pseudogapped phase, as momentum states are expelled from the Kondo cloud.
-The final pink curve shows the charge gap in the local moment phase.}
+The final pink curve shows the charge gap in the local moment phase.
+{\bf Right:} Imaginary part of impurity self-energy.
+Poles represent the beginning of the optical gap between the central Kondo resonance and the Hubbard sidebands.
+Increasing the bath interaction leads to the coalescing of the poles (due to the sharpening of the Kondo resonance), ultimately leading to a zero frequency pole  in the local moment phase.}
 	\label{phaseDiagram}
@@
 \subsection{Presence of a local pseuodogapping transition with electronic differentiation in momentum space}
-We find that upon tuning the ratio \(W/J\) of the bath interaction strength \(W\) and the Kondo coupling  \(J\), the impurity site undergoes a transition from a screened paramagnetic phase to an unscreened local moment phase, similar to the extended-SIAM.
-The transition starts through the removal, from the Kondo cloud, of the antinodal points of the conduction bath Fermi surface.
+We now discuss the intervening pseudogapped regime (pink region) of the phase diagram.
+We find that the process of Kondo breakdown in our model occurs anisotropically in our model - the transition starts through the removal, from the Kondo cloud, of the antinodal points of the conduction bath Fermi surface.
 This is followed by the sequential removal of points away from the antinodes, with the nodal points being removed at the very end.
@@
 	\centering
+	\includegraphics[width=0.23\textwidth]{scattProb-1.pdf}
 	\includegraphics[width=0.23\textwidth]{scattProb-3.pdf}
+	\includegraphics[width=0.23\textwidth]{scattProb-4.pdf}
 	\includegraphics[width=0.23\textwidth]{scattProb-5.pdf}
-	\includegraphics[width=0.23\textwidth]{scattProb-6.pdf}
-	\includegraphics[width=0.23\textwidth]{scattProb-7.pdf}
 	\caption{Variation of \(\Gamma\) as \(W/J\) is increased from left to right and top to bottom.
@@
 
-\subsection{Emergence of a two-channel Kondo Model as the low-energy theory near the transition}
+\subsection{Emergence of a two-channel Kondo Model as the low-energy theory in the pseudogap phase}
 As the bath interaction \(W\) is tuned through the L-PG phase, the four nodal points in the Brillouin zone are the last to decouple from the impurity.
@@
 This is verified by calculating the ratio \(\text{max}\left\{ J_{k^+_1, k^-_2} \right\} / \text{max}\left\{ J_{k^+_1, k^+_2} \right\}\), where the maximum in the numerator is calculated from all the low-energy (fixed point) Kondo scattering processes that connect the two sets \(S^\pm\), while the denominator maximum is from within the set \(S^+\).
-This ratio vanishes (Fig.~\ref{channelDecoupling}) within the local pseudogap regime, indicating that no direct Kondo scattering process persists between the two sectors \(S^\pm\) at low energies, deep within the pseudogap regime.
+This ratio vanishes (left panel of Fig.~\ref{channelDecoupling}) within the local pseudogap regime, indicating that no direct Kondo scattering process persists between the two sectors \(S^\pm\) at low energies, deep within the pseudogap regime.
 
@@
 	\includegraphics[width=0.45\textwidth]{quadrantMaxKondo-49.pdf}
-	\caption{}
+	\includegraphics[width=0.45\textwidth]{localQPResidue.pdf}
+	\caption{Left: Ratio between the maximum values of the fixed point values of the Kondo couplings for scattering processes between and within the regions \(S^+\) and \(S^-\).
+The vanishing of the fixed point ratio indicates that the pseudogap regime features a singular low-energy effective theory, where the Fermi surface neighbourhood splits into two disconnected regions with no explicit term in the Hamiltonian connecting them directly.
+Right: The quasiparticle residue \(Z_\text{imp}\) of the local gapless excitations in various regions.
+The vanishingly small values of \(Z_\text{imp}\) lend more support to the two-channel (and hence the non-Fermi liquid) nature of the low-energy physics in the pseudogap regime.}
 	\label{channelDecoupling}
@@
 
-This is captured by the following simplified Hamiltonian:
+The decoupling of the \(k-\)space regions \(S^\pm\) is captured by the following simplified low-energy Hamiltonian:
 \begin{equation}\begin{aligned}\label{twoChannel}
@@
 Eq.\ref{twoChannel} tells us that the low-energy dynamics of the embedded eSIAM close to the Kondo-breakdown transition is governed by an emergent {\bf two-channel Kondo model}, with the conduction bath states in the sets \(S^\pm\) making up the two channels.
+It is well-known that the two-channel Kondo model hosts non-Fermi liquid excitations at low-energies; this is also corroborated by our calculations of the quasiparticle residue \(Z_\text{imp}\) for the local gapless excitations.
+For a single-particle Greens function of an interacting model, the quasiparticle residue \(Z\) is defined as
+\begin{equation}\begin{aligned}
+	G = Z G^{(0)} + G_\text{inc}~,
+\end{aligned}\end{equation}
+where \(G^{(0)}\) is the non-interacting Greens function and \(G_\text{inc}\) is contribution to the Greens function arising from incoherent short-lived excitations.
+Small values of \(Z\) indicate that the excitations cannot be described in terms of a Fermi liquid theory.
+Indeed, as shown in the right panel of Fig.~\ref{channelDecoupling}, the quasiparticle residue \(Z_\text{imp}\) of the impurity excitations becomes vanishingly small in the pseudogap region, signalling that the excitations are of a non-Fermi liquid nature.
+
 Given that this is a critical point in the impurity model phase diagram (separating the local Fermi liquid and local moment phases), it is not surprising that a quantum critical model emerges at that point.
@@
 
-\subsection{One-particle \(k-\)space spectral function}
+\subsection{\(k-\)space spectral function and self-energy}
+The primary indicator of the pseudogapping nature of the transition is of course the \(k-\)space density of states or the spectral function, shown in Fig.~\ref{tiledSpecFunc}.
+For \(W=0\), all points on the Fermi surface are gapless.
+As we enter the pseudogap, the region around the antinodes lose all spectral weight and become gapped.
+Increasing the value of \(W\) further leads to the enlargement of the gapped region; exactly at the transition, we end up with a singular Fermi surface composed of just the nodal points.
+
+This is also supported by our computations of the \(k-\)space self-energy.
+We show the zero frequency value of the \(k-\)space self-energy in Fig.~\ref{selfenergy}.
+This is computed from using Dyson's equation \(\Sigma_k = 1/G_k^{(0)} - 1/G_k\), where \(G_k\) is the interacting \(k-\)space Greens function while \(G_k^{(0)}\) is the non-interacting \(W=0\) Greens function.
+We find that the beginning of the pseudogap is marked by poles in the self-energy at the antinodal points; at the transition, only the nodes display vanishing self-energy at zero frequency.
 \begin{figure}[htpb]
@@
 Proceeding through the pseudogap results in the gapping out of Fermi surface points starting from the antinode (second panel) and approaching the node (third panel), until finally only the node remains at the critical point (fourth panel).}
-	\label{fig:tiledSF-pdf}
+	\label{tiledSpecFunc}
+\end{figure}
+\begin{figure}[htpb]
+	\centering
+	\includegraphics[width=0.23\textwidth]{selfEnergyKspace-1.pdf}
+	\includegraphics[width=0.23\textwidth]{selfEnergyKspace-2.pdf}
+	\includegraphics[width=0.23\textwidth]{selfEnergyKspace-3.pdf}
+	\includegraphics[width=0.23\textwidth]{selfEnergyKspace-4.pdf}
+	\caption{\(k-\)space self-energy.
+For \(W=0\), the self-energy is vanishingly small, leading to a Fermi liquid phase described by well-defined quasiparticles.
+Inside the pseudogap, the self-energy diverges near the antinodes, leading to their gapping.
+The coexistence of gapped and gapless points on the Fermi surface in the pseudogapped region leads to non-Fermi liquid behaviour of the gapless excitations, as captured by the emergent two-channel behaviour within the impurity model.
+The metal at the transition is supported only the four nodal points.}
+	\label{selfenergy}
 \end{figure}

### 2025-03-31 numerics/caller.jl

@@ -375,7 +375,7 @@ function AuxiliaryLocalSpecfunc(
     for W_val in W_val_arr
         effectiveNumShells = W_val == 0 ? numShells : 1
         savePath = joinpath(SAVEDIR, "imp-specfunc-$(W_val)-$(effective_Wval)-$(size_BZ)-$(effectiveNumShells)-$(maxSize)-$(bathIntLegs)-$(maximum(freqValues))-$(length(freqValues))-$(GLOBALFIELD).jld2")
-        if ispath(savePath) && loadData && W_val == W_val_arr[1]
+        if ispath(savePath) && loadData
             specFunc = jldopen(savePath)["impSpecFunc"]
             quasipResidue = jldopen(savePath)["quasipResidue"]
             centerSpec = jldopen(savePath)["centerSpec"]

### 2025-04-02 TilingProjectDraft/tilingProject.tex
filled in discussions wherever I could, added MFL derivation

@@
 
-\section{Extending the Anderson impurity model}
-We have shown in a previous work that by including a local attractive interacting on the conduction bath site coupled to the impurity site of the Anderson impurity model, one can obtain an impurity phase transition from a screened phase to an unscreened local moment phase at a certain critical value of the attractive interaction strength.
-We now consider a more realistic form of this model, by embedding the impurity site into the lattice of a 2D  conduction bath and accounting for the lowering of the \(s-\)wave symmetry of the interactions down to just the \(C_4\) symmetry of the 2D square lattice.
-A general structure of such a model is shown in fig.~\ref{embeddedEsiam}; one of the sites of the 2D square lattice is identified as the impurity, while the four nearest-neghbours interact directly with this impurity site.
+\section{Extending the Anderson Model To a Lattice-Embedded Impurity Model}
+Crucial to our method is the choice of an impurity auxiliary model that is able to capture important aspects of the lattice model in a local sense.
+Some of us have shown in a previous work~\cite{Mukherjee_2023} that almost all aspects of the Mott metal-insulator transition on the infinite dimensional Hubbard model on the Bethe lattice (as seen, for example, from dynamical mean-field theory~\cite{georges1996}) can be captured from a simple extension of the Anderson impurity model (eSIAM).
+The extension involves including a local attractive interacting \(U_b\) on the conduction bath site coupled to the impurity site; by tuning the ratio of \(|U_b|\) and the Kondo coupling \(J\), we obtained an impurity phase transition from a screened phase to an unscreened local moment phase.
+Since the impurity site of the auxiliary model is a representative of each correlated site on the lattice, the mapping to the lattice model then involves identifying the locally gapless impurity phase with the bulk gapless of the lattice model.
+In other words, the ability of the impurity site to participate in low-energy excitations corresponds to the ability of an electron, within the lattice model, to delocalise from one site into the rest of the lattice.
+In the same vein, a local moment phase of the impurity model maps to a gapped Mott insulating phase on the lattice model, where there's a charge gap to electron hopping processes.
+
+In the present work, the goal is to tackle interacting fermions on a 2D square lattice, which makes it important for us to incorporate the effects of the lattice within the impurity model.
+More specifically, while the impurity-bath interactions on the infinite dimensional Bethe lattice are \(s-\)wave symmetric, that is not a realistic form for a 2D lattice.
+To make a realistic impurity model, we embed the impurity site into the lattice of a 2D conduction bath, and lower the \(s-\)wave symmetry of the interactions down to the \(C_4\) symmetry of the 2D square lattice.
+A general structure of such a model is shown in fig.~\ref{embeddedEsiam}; one of the sites of the 2D square lattice is identified as the impurity (red), while the four nearest-neghbours (navy blue) interact directly with this impurity site through a \(C_4\)-symmetric interaction.
 \begin{figure}[htpb]
@@
 \end{aligned}\end{equation}
-The form of the impurity-bath interaction \(H_\text{imp-cbath}\) and the local interaction \(H_\text{cbath-int}\) in the bath can be of various forms, depending in the choice of the bath orbital which participates in the interaction.
-We now consider some interesting cases:
-\paragraph{\(d-\)wave interactions:} This is the case when a coherent \(d-\)wave combination of the bath sites closest to the impurity participates in the interaction:
-\begin{equation}\begin{aligned}
-	d_{\sigma} &= \frac{1}{2}\left(c^\dagger_{L,\sigma} + c^\dagger_{R,\sigma} - c^\dagger_{U\sigma} - c^\dagger_{D\sigma}\right)~,
-\end{aligned}\end{equation}
-leading to the interaction terms
-\begin{equation}\begin{aligned}
-	H^{(d)}_\text{imp-cbath} &= J\vec{S}_d\cdot\frac{1}{2}\sum_{\sigma_1,\sigma_2}\vec{\tau}_{\sigma_1,\sigma_2} d^\dagger_{\sigma_1}d_{\sigma_2}~,\\
-	H^{(d)}_\text{cbath-int} &= -\frac{W}{2}\left(d^\dagger_{\uparrow}d_{\uparrow} - d^\dagger_{\downarrow}d_{\downarrow}\right)^2~,
-\end{aligned}\end{equation}
-where \(\vec \tau\) is the vector of sigma matrices, \(\sigma_1,\sigma_2\) are spin indices, and \(L,R,U,D\) represent the four lattice sites ({\it L}eft, {\it R}ight, {\it U}p, {\it D}own) closest to the impurity.
-When Fourier-transformed to momentum space, it gives rise to the momentum-dependent couplings
-\begin{equation}\begin{aligned}\label{d-wave k-space}
-	J_{{\bf k}_1, {\bf k}_2} = J f_{\pi}\left({\bf k}_1\right) f_{\pi}\left({\bf k}_2\right) ~,\quad W_{\left\{ k_i \right\} } = W\prod_{i=1,2,3,4}f_{\pi}(k_i)~,
-\end{aligned}\end{equation}
-where \(f_{\pi}({\bf k}) = \cos\left( ak_x \right) - \cos\left( ak_y \right) \) is the \(d-\)wave symmetric functional form in \(k-\)space.
-\paragraph{\(p-\)wave interaction:} One can also consider the case when the \(p-\)wave orbital of the nearest sites participates in the interaction:
-\begin{equation}\begin{aligned}
-	p_{\sigma} &= \frac{1}{2}\left(c^\dagger_{L,\sigma} + c^\dagger_{R,\sigma} + c^\dagger_{U\sigma} + c^\dagger_{D\sigma}\right)~,\\
-	H^{(p)}_\text{imp-cbath} &= J\vec{S}_d\cdot\frac{1}{2}\sum_{\sigma_1,\sigma_2}\vec{\tau}_{\sigma_1,\sigma_2} p^\dagger_{\sigma_1}p_{\sigma_2}~,\\
-	H^{(p)}_\text{cbath-int} &= -\frac{W}{2}\left(p^\dagger_{\uparrow}p_{\uparrow} - p^\dagger_{\downarrow}p_{\downarrow}\right)^2~.
-\end{aligned}\end{equation}
-The momentum-dependent Kondo coupling in this case is 
-\begin{equation}\begin{aligned}\label{p-wave k-space}
-	J_{{\bf k}_1, {\bf k}_2} = J f_{{2\pi}}\left({\bf k}_1\right) f_{{2\pi}}\left({\bf k}_2\right) ~, \quad W_{\left\{ k_i \right\} } = W\prod_{i=1,2,3,4}f_{{2\pi}}(k_i)~,
-\end{aligned}\end{equation}
-where \(f_{2\pi}({\bf k}) = \cos\left( ak_x \right) + \cos\left( ak_y \right)\) is the form for the \(p-\)wave symmetric function.
-
-Note that both these interactions involve not only local terms as well as quasi-local terms in the form of off-site interactions that connect the impurity site with multiple bath sites.
-An example of such a term is \(\vec{S}_d\cdot\frac{1}{2}\sum_{\sigma_1,\sigma_2}\vec{\tau}_{\sigma_1,\sigma_2} c^\dagger_{R,\sigma_1}c_{U,\sigma_2}\), which couples the impurity site with both the right and up sites in the bath.
-One can consider simple modifications of these cases by retaining only the on-site terms in the interaction Hamiltonian.
-This gives us the modified \(d-\)wave and \(p-\)wave symmetries:
-\begin{equation}\begin{aligned}
-	H^{(\bar d(\bar p))}_\text{imp-cbath} &= J\vec{S}_d\cdot\frac{1}{2}\sum_{\sigma_1,\sigma_2}\vec{\tau}_{\sigma_1,\sigma_2} \sum_{i \in \left\{L,R,U,D\right\}} \lambda_i c^\dagger_{i,\sigma_1}c_{i,\sigma_2}~,\\
-	H^{(\bar d(\bar p))}_\text{cbath-int} &= -\frac{W}{2}\sum_{i \in \left\{L,R,U,D\right\}} \lambda_i \left(c^\dagger_{i, \uparrow}c_{i, \uparrow} - c^\dagger_{i, \downarrow}c_{i, \downarrow}\right) ~,
-\end{aligned}\end{equation}
-where \(\lambda_R = \lambda_L = \lambda_U = \lambda_D = 1\) for the \(\bar p\)-wave case, but \(\lambda_R = \lambda_L = -\lambda_U = -\lambda_D = 1\) for the \(\bar d\)-wave case.
-The \(k-\)dependent couplings have the form
-\begin{equation}\begin{aligned}
-	J_{{\bf k}_1, {\bf k}_2} &= J f_{\bar d(\bar p)}\left({\bf k}_1 -{\bf k}_2\right),\\
-	W_{\left\{ \bf k_i \right\} } &= Wf_{\bar d(\bar p)}\left({\bf k}_1 -{\bf k}_2 + {\bf k}_3 -{\bf k}_4\right) ,
-\end{aligned}\end{equation}
-where 
-\begin{equation}\begin{aligned}
-	&f_{\bar d(\bar p)}\left({\bf k}_1 -{\bf k}_2 + {\bf k}_3 -{\bf k}_4\right) \\
-	&= \frac{1}{2}\left[\lambda_R \cos\left(k_{1x} - k_{2x} + k_{3x} - k_{4x}\right) \right.\\
-	&\quad\left. + \lambda_U \cos\left(k_{1y} - k_{2y} + k_{3y} - k_{4y}\right)\right] ~.
-\end{aligned}\end{equation}
-
-\subsection{Unitary RG analysis of the model}
+For the impurity-bath interaction \(H_\text{imp-cbath}\) and the local interaction \(H_\text{cbath-int}\) in the bath, we take the simplest choices consistent with the 2D square lattice geometry:
+\begin{equation}\begin{aligned}
+	H_\text{imp-cbath} &=\frac{1}{2} J\sum_{\sigma_1,\sigma_2}\sum_{Z} {\bf S}_d\cdot c^\dagger_{Z\sigma_1}{\boldsymbol \tau}_{\sigma_1,\sigma_2} c_{Z\sigma_2}~,\\
+	H_\text{cbath-int} &= -\frac{W}{2}\sum_{Z} \left(n_{Z\uparrow} - n_{Z\downarrow}\right)^2 ~,
+\end{aligned}\end{equation}
+where \(Z\) sums over all nearest-neighbour sites of the impurity site (navy blue circles in Fig.~\ref{embeddedEsiam}, henceforth referred to as bath zeroth sites).
+The impurity interacts with the bath zeroth sites in \(H_\text{imp-cbath}\) through four local Kondo terms, of uniform strength.
+The other term \(H_\text{cbath-int}\) represents local Hubbard interactions on the four zeroth sites, again of uniform strength.
+
+The 2D structure of the impurity model and its distinction from the infinite-dimensional counterpart becomes apparent once we transform the Hamiltonian to momentum space:
+\begin{equation}\begin{aligned}
+	J_{{\bf k}, {\bf k}^\prime} &= \frac{J}{2}\left[\cos\left({\bf k}_x - {\bf k}^\prime_x\right) + \cos\left({\bf k}_y - {\bf k}^\prime_y\right)\right] ~,\\
+	W_{{\bf k}, {\bf k}^\prime,{\bf q}, {\bf q}^\prime} &= W\left[\cos\left({\bf k}_x - {\bf k}^\prime_x + {\bf q}_x - {\bf q}^\prime_x\right) + \cos\left({\bf k}_y - {\bf k}^\prime_y + {\bf q}_y - {\bf q}^\prime_y\right)\right] ~.
+\end{aligned}\end{equation}
+where the subscripts \(x\) and \(y\) represent components of the momenta vector.
+This form shows that the Kondo coupling is no longer independent of the exchange momentum, and encodes information of the lattice geometry in it.
+
+\subsection{The unitary renormalisation group method}
+In order to obtain the various low-energy phases of our impurity model, we perform a scaling analysis of the associated Hamiltonian using the recently developed unitary renormalisation group (URG) method \cite{anirbanurg1,anirbanurg2}.
+The method has been applied successfully on a wide variety of problems of correlated fermions~\cite{santanukagome,1dhubjhep,anirbanmott2,anirbanmott1,siddharthacpi,anirban_kondo,Patra_2023,anirbanurg1,anirbanurg2}.
+The method proceeds by resolving quantum fluctuations in high-energy degrees of freedom, leading to a low-energy Hamiltonian with renormalised couplings and new emergent degrees of freedom.
+Typically, for a system with Fermi energy \(\epsilon_F\) and bandwidth \(E_N\), the sequence of isoenergetic shells \(\left\{E_{(j)}\right\}, E_{j}\in \left[E_0, E_N\right] \) define the states whose quantum fluctuations we sequentially resolve.
+The momentum states lying on shells \(E_N\) that are far away from the Fermi surface comprise the UV states, while those on shells near the Fermi surface comprise the IR states.
+This scheme is shown in Fig.~\eqref{zeromode-bare}.
+
+\begin{figure}[!htb]
+	\includegraphics[width=0.3\textwidth]{urgScheme.pdf}
+	\caption{High energy - low energy scheme defined and used in the URG method.
+The states away from the Fermi surface (\(E_N\) in the figure) form the UV subspace and are decoupled first, leading to a Hamiltonian which is more block-diagonal and comprised of only the IR states near the Fermi surface (\(E_0\) in the figure).}
+	\label{zeromode-bare}
+\end{figure}
+
+As a result of the URG transformations, the Hamiltonian \(H_{(j)}\) at a given RG step \(j\) involves scattering processes between the \(k-\)states that have energies lower than \(D_{(j+1)}\).
+The unitary transformation \(U_{(j)}\) is then defined so as to remove the number fluctuations of the currently most energetic set of states \(D_{(j)}\)~\cite{anirbanurg1,anirbanurg2}:
+\begin{eqnarray}
+	H_{(j-1)} = U_{(j)} H_{(j)} U^\dagger_{(j)}~, \text{such that} ~\left[H_{(j-1)}, \hat n_{j}\right] =0~.
+\end{eqnarray}
+The eigenvalue of $\hat{n}_{j}$ has, thus, been rendered an integral of motion (IOM) under the RG transformation.
+
+The unitary transformations can be expressed in terms of a generator \(\eta_{(j)}\) that has fermionic algebra~\cite{anirbanurg1,anirbanurg2}:
+\begin{eqnarray}
+	\label{unitary}
+	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ \quad\left\{ \eta_{(j)},\eta_{(j)}^\dagger \right\} = 1~,
+\end{eqnarray}
+where \(\left\{\cdot\right\}\) is the anticommutator.
+The unitary operator \(U_{(j)}\) that appears in Eq.~\eqref{unitary} can be cast into the well-known general form \(U = e^\mathcal{S}, \mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger_{(j)} - \eta_{(j)} \right)\) that a unitary operator can take, defined by an anti-Hermitian operator \(\mathcal{S}\).
+The generator \(\eta_{(j)}\) is given by the expression~\cite{anirbanurg1,anirbanurg2}
+\begin{eqnarray}
+	\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} \text{Tr}\left(H_{(j)}c_{j}\right)~.
+\end{eqnarray}
+The operators \(\eta_{(j)},\eta^\dagger_{(j)}\) behave as the many-particle analogues of the single-particle field operators \(c_j,c^\dagger_j\) - they change the occupation number of the single-particle Fock space \(\ket{n_j}\).
+The important operator \(\hat \omega_{(j)}\) originates from the quantum fluctuations that exist in the problem because of the non-commutation of the kinetic energy terms and the interaction terms in the Hamiltonian:
+\begin{eqnarray}
+	\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)}~.
+	\label{omega}
+\end{eqnarray}
+\(H^i_{(j)}\) is the part of \(H_{(j)}\) that commutes with \(\hat n_j\) but does {\it not} commute with at least one \(\hat n_l\) for \(l < j\).
+The RG flow continues up to energy \(D^*\), where a fixed point is reached from the vanishing of the RG function.
+Detailed comparisons of the URG with other methods (e.g., the functional RG, spectrum bifurcation RG etc.) can be found in Refs.~\cite{anirbanmott1,anirbanurg1}.
+
+\subsection{Unitary RG analysis of the embedded eSIAM}
 We studied the low-energy physics of this model through a unitary renormalisation group calculation that decouples the high-energy modes of the conduction bath and incorporates their effects in the form of renormalised Hamiltonian couplings.
@@
 
-We now consider some specific cases of these results.
-\paragraph{Interactions with off-site terms:}
-The case with the complete \(d-\)wave and \(p-\)wave terms enjoy a factorisation of the momentum space couplings into functions of the participating momenta, as shown in eq.~\ref{d-wave k-space} and \ref{p-wave k-space}.
-This factorisation also translates into the RG equation, ensuring that the momentum space Kondo coupling retains its form, and renormalisation occurs only in the magnitude \(J\), through the equation
-\begin{equation}\begin{aligned}
-	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} &= f_{{2\pi}(\pi)}\left({\bf k}_1\right) f_{{2\pi}(\pi)}\left({\bf k}_2\right) \Delta J~,\\
-\Delta J &= \sum_{{\bf q} \in \text{PS}} \frac{-f_{2\pi(\pi)}({\bf q})^2\left[J^2 + 4JWf_{2\pi(\pi)}({\bf q})^2\right]}{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_{2\pi(\pi)}({\bf q})^2 + \frac{W}{2}f_{2\pi(\pi)}({\bf q})^4}~.
-\end{aligned}\end{equation}
-\paragraph{Interactions without off-site terms:}
-This choice does not lead to a factorisation of the momentum-space dependence, and the form of the Kondo coupling therefore morphs during the RG flow, allowing the emergence of new degrees of freedom that screen the impurity at low-energies.
+With our chosen momentum-space dependence of the Kondo coupling and bath interaction, the form of the Kondo coupling morphs during the RG flow, allowing the emergence of new degrees of freedom that screen the impurity at low-energies.
 At the first step, the RG equation can be written down explicitly as
 \begin{equation}\begin{aligned}
-	&\Delta J^{(0)}_{{\bf k}_1, {\bf k}_2} =\\
-	&-\sum_{{\bf q} \in \text{PS}} \frac{J^2 f_{\bar p(\bar d)}\left({\bf k}_2 - {\bf q}\right) f_{\bar p(\bar d)}\left({\bf q} - {\bf k}_1\right) - 4JW f_{\bar p(\bar d)}\left({\bf k}_2 - {\bf k}_1\right)}{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{4}}
-\end{aligned}\end{equation}
-The first term in the numerator does not depend only on the momentum difference \({\bf k}_2 - {\bf k}_1\), unlike the bare Kondo coupling.
-This leads to a new \(k-\)space dependence of the Kondo coupling at the second step, hence leading to a modified RG equation if one makes the \(k-\)dependence explicit.
-
-\section{The Tiling Algorithm}
-
-\subsection{Formal description of the tiling procedure}
-We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian.
-The first step is of course to identify an impurity model that can act as a good auxiliary model for out lattice model.
-The local behaviour of this impurity model should reflect the essential local physics of the lattice model.
-Typically, we will consider impurity model geometries where the real-space bath site connected directly to the impurity also harbours some kind of local interaction.
-We will henceforth refer to this site as the zeroth site.
-In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout.
-
-In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})\).
-The unit cell at the position \({\bf r}_d\) is then obtained by placing the zeroth site on all nearest-neighbours of \({\bf r}_d\) and averaging over these configurations:
-\begin{equation}\begin{aligned}\label{unitCellHamiltonian}
-	\mathcal{H}_\text{aux}({\bf r}_d) = \frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})~,
-\end{aligned}\end{equation}
-where \({\bf z}\) is summed over all nearest-neighbours of \({\bf r}_d\) and \(\mathcal{Z}\) is the number of such nearest-neighbours.
-
-In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice.
-For this, we define {\it many-particle global} translation operators \(T({\bf a})\) that translate all positions by a vector \({\bf a}\).
-In terms of manybody states and operators, their action is defined as
-\begin{equation}\begin{aligned}\label{translationDefinition}
-	&T^\dagger({\bf a}) \ket{{\bf r}_1, {\bf r}_2,\ldots} = \ket{{\bf r}_1 + {\bf a}}\otimes\ket{{\bf r}_2 + {\bf a}}\ldots\otimes\ket{{\bf r}_n + {\bf a}}\\
-	&T^\dagger({\bf a}) \mathcal{O}\left({\bf r}_1, {\bf r}_2,\ldots\right)T({\bf a}) = \mathcal{O}\left({\bf r}_1 + {\bf a}, {\bf r}_2 + {\bf a},\ldots\right)~,
-\end{aligned}\end{equation}
-where \(\ket{{\bf r}_1, {\bf r}_2,\ldots}\) is a state in the manyparticle Fock-space basis with the particles localised at the specified positions.
-For example, for a local fermionic creation operator \(c^\dagger({\bf r})\), we have
-\begin{equation}\begin{aligned}
-	T^\dagger({\bf a}) c^\dagger({\bf r}) T({\bf a}) = c^\dagger({\bf r} + {\bf a})~.
-\end{aligned}\end{equation}
-It acts similarly on the auxiliary model Hamiltonian:
-\begin{equation}\begin{aligned}
-	T^\dagger({\bf a})\mathcal{H}_\text{aux}({\bf r}_d)T({\bf a}) = \mathcal{H}_\text{aux}({\bf r}_d + {\bf a})~,
-\end{aligned}\end{equation}
-translating all sites by the vector \({\bf a}\). By introducing the Fourier transform to momentum space,
-\begin{equation}\begin{aligned}
-	\ket{{\bf r}_1, {\bf r}_2,\ldots} = \otimes_{j=1}^N \int d{\bf k}_j e^{-i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf k}_j}~,
-\end{aligned}\end{equation}
-it is easy to see that the total momentum states are eigenstates of the global translation operators:
-\begin{equation}\begin{aligned}
-	T^\dagger({\bf a})\ket{{\bf k}_1, {\bf k}_2,\ldots} &= \otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} T^\dagger({\bf a})\ket{{\bf r}_j}~,\\
-							    &=\otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf r}_j + {\bf a}}\\
-							    &=e^{-i {\bf a}_j\cdot{\bf k}_\text{tot}}\ket{{\bf k}_1, {\bf k}_2,\ldots},
-\end{aligned}\end{equation}
-where \({\bf k}_\text{tot} = \sum_j {\bf k}_j\) is the total momentum.
-
-The auxiliary model, being an impurity model, lacks translation symmetry.
-The lattice model does remain invariant under global translation operations.
-In order to reconstruct the full lattice model and restore its translation invariance, we translate the unit cell across all sites of the lattice:
-\begin{equation}\begin{aligned}
-	\label{tilingPrescription}
-	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})\\
-				&= \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r} - {\bf r}_d)~ \\
-				&= \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d)~ \\
-\end{aligned}\end{equation}
-where \({\bf r}\) sums over all lattice sites.
-
-\subsection{Extending the Anderson impurity model: Identifying the correct auxiliary model}
-The standard Anderson model consists of a correlated impurity site coupled with a non-interacting conduction bath.
-The double occupancy cost on the impurity is \(U\), while the single-particle hopping strength between the impurity and the conduction bath is \(V\).
-Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes.
-We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model).
-The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
-\begin{equation}\begin{aligned}
-	\label{siam_attr}
-	\mathcal{H}_\text{E-S} = \mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} + \mathcal{H}_\text{imp-cbath}~,
-\end{aligned}\end{equation}
-where 
-\begin{itemize}
-	\item \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site,
-	\item \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and
-	\item \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 - V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath.
-\end{itemize}
-Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath.
-We have found that the e-SIAM has a stable local moment phase for \(U_b < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)).
-We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of an optical gap in the local spectral function beyond a certain value of interaction strength.
-Note that the impurity site and the conduction bath are both at half-filling.
-
-\subsection{Tiling towards a Hubbard-Heisenberg model with an embedded extended SIAM}
-In this subsection, we provide an explicit example of constructing a lattice model.
-We will consider a slightly more generalised version of the extended SIAM described in the previous section, where the impurity site coupled to the conduction bath purely through the s-wave channel.
-We will show that that model leads to a form of a Hubbard-Heisenberg model upon restoring translation invariance via repeated translation operations.
-The generalisation involve allowing an arbitrary filling on the impurity site and in the conduction bath, through two additional parameter: (i) a particle-hole asymmetry parameter \(\eta\) for the impurity site, (ii) a chemical potential for the conduction bath, and (iii) embedding the impurity into the lattice of the 2D conduction bath.
-This modified impurity model is shown in Fig.~\ref{embeddedEsiam}.
-The first term modifies the impurity Hamiltonian \(\mathcal{H}_\text{imp}\) into
-\begin{equation}\begin{aligned}\label{onsiteHamiltonian}
-	\mathcal{H}_\text{imp} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 - \eta\sum_\sigma \hat n_{{\bf r}_d\sigma}~.
-\end{aligned}\end{equation}
-where we have placed the impurity site at the position \({\bf r}_d\). The second term modifies the conduction bath Hamiltonian \(\mathcal{H}_\text{cbath}\):
-\begin{equation}\begin{aligned}\label{bathHamiltonian}
-	\mathcal{H}_\text{cbath} &= -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
-							 &- \frac{1}{2 \mathcal{Z}}U_b\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
-\end{aligned}\end{equation}
-where \(\left<{\bf r}_i, {\bf r}_j\right>\neq {\bf r}_d\) indicates that the sum is over all nearest-neighbour pairs of sites avoiding the impurity site \({\bf r}_d\).
-
-In this notation, the interaction Hamiltonian can be written as
-\begin{equation}\begin{aligned}\label{interactionHamiltonian}
-	\mathcal{H}_\text{imp-cbath} &= \frac{J}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}\sum_{{\bf z}\in\text{NN}({\bf r}_d)} {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \\
-								 & - \frac{V}{\sqrt{\mathcal{Z}}}\sum_{\sigma} \sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)
-\end{aligned}\end{equation}
-where \(\boldsymbol \tau = \left( \tau_x, \tau_y, \tau_z \right) \) is the vector of Pauli matrices. \(\sigma\) and \(\sigma^\prime\) can be \(\pm 1\) and represent up and down configurations.
-
-We now follow the prescription laid out in eq.~\ref{tilingPrescription}. The tiled Hamiltonian can be written as 
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{tiled} = \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} \right.\\
-\left.+ \mathcal{H}_\text{imp-cbath}\right]T({\bf r} - {\bf r}_d)~.
-\end{aligned}\end{equation}
-Note that in comparison to eq.~\ref{tilingPrescription}, we have dropped the sum over the zeroth sites, because our impurity model Hamiltonian (defined using eqs.~\ref{onsiteHamiltonian} through \ref{interactionHamiltonian}) already contains a sum over these zeroth sites.
-
-We consider the effect of the translation operations on each part of the Hamiltonian. We first have
-\begin{equation}\begin{aligned}
-	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d) \\
-	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \right.\\
-	 &\left.- \frac{U_b}{2\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}\right]T({\bf r} - {\bf r}_d) \\
-	=& -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
-	 &- \frac{U_b}{2\mathcal{Z}}\sum_{\bf r}\sum_{{\bf z}\in\text{NN}\left({\bf r}\right)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i}\sum_{{\bf r} \neq {\bf r}_i}\hat n_{{\bf r}_i,\sigma}\\
-	=& -\frac{1}{\sqrt\mathcal{Z}}(N-2)t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
-	 &- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
-\end{aligned}\end{equation}
-In the first step, the factor of \(\mathcal{Z}\) is cancelled out by the trivial sum over \({\bf r}_0\) in the first and third terms.
-At the last step, the three terms simplified for the following reasons.
-The inequality \(\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}\) in the first term ensures that each nearest-neighbour pair appears in \(N-2\) instances of the auxiliary model, \(N\) being the total number of lattice sites; the two instances that do not contribute are the ones in which the impurity site itself is at \({\bf r}_i\) or \({\bf r}_j\).
-For the second term, the double sum \(\sum_{\bf r}\sum_{{\bf z} \in \text{NN}({\bf r})}\) evaluates to \(\mathcal{Z}\sum_{\bf r}\), because each point on the lattice appears \(\mathcal{W}\) times in the summation.
-This factor of \(\mathcal{W}\) cancels the one in the denominator.
-In the third term, the inner summation simply evaluates to \(N-1\), and we finally replace the dummy index \({\bf r}_i\) with \({\bf r}\).
-
-The next part is
-\begin{equation}\begin{aligned}
-	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp}T({\bf r} - {\bf r}_d) \\
-	=& -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}~.
-\end{aligned}\end{equation}
-This is obtained simply by replacing the impurity position \({\bf r}_d\) with the translated position \({\bf r}\), generating a translation-invariant Hubbard term (the first term) and a finite chemical potential (second term).
-
-We now consider the final term:
-\begin{equation}\begin{aligned}
-	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp-cbath}T({\bf r} - {\bf r}_d)\\
-	&=\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
-				     &-  \left. \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma} V \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]T({\bf r} - {\bf r}_d)\\
-	&=\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r})}\left[\frac{1}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
-				     &-  \frac{1}{\sqrt\mathcal{Z}}\left.\sum_{\sigma} V\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]\\
-					 &=\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]\\
-\end{aligned}\end{equation}
-At the last step, each nearest-neighbour pair of sites \({\bf r}_i, {\bf r}_j\) appear 2 times in the summation, because any site is a member of two distinct nearest-neighbour pairs.
-We have also defined \({\bf S}_{{\bf r}_j} =\sum_{\sigma,\sigma^\prime} {\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime}\) as the local spin operator.
-
-The total tiled Hamiltonian is therefore
-\begin{equation}\begin{aligned}
-	&\mathcal{H}_\text{tiled} \\
-	&= -\frac{N-2}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>,\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
-	&- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}\\
-	& + \sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]
-\end{aligned}\end{equation}
-While constructing the tiled Hamiltonian, we have added extra copies of the non-interacting Hamiltonian \(\mathcal{H}_\text{cbath-nint} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\) for the conduction bath (this results in the factors of \(N-2\) and \(N-1\) in front of the first and third terms).
-Upon removing these repeated terms, the tiled Hamiltonian becomes
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}\\
-							 &= -\frac{1}{\sqrt\mathcal{Z}}(t + 2V)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
-							 &- \frac{1}{2}\left(U + U_b\right)\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \left(\eta + 2\mu\right) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} \\
-							 &+ \frac{2}{\mathcal{Z}}J\sum_{\left< {\bf r}_i, {\bf r}_j\right>} {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j}
-\end{aligned}\end{equation}
-
-The result of the tiling operations is a Hubbard-Heisenberg model, of the form
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{HH} &= -\frac{1}{\sqrt\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
-						  &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
-\end{aligned}\end{equation}
-where the tilde symbol indicates that the parameters are for the lattice model (and not the auxiliary model).
-By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to each other:
-\begin{equation}\begin{aligned}\label{couplingsMappings}
-	\tilde t = t+2V,~~ \tilde U = U + U_b, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
-\end{aligned}\end{equation}
-In summary, the appropriate method for reconstructing the lattice model Hamiltonian is therefore
-\begin{equation}\begin{aligned}\label{tilingPrescriptionFinal}
-	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}~,
-\end{aligned}\end{equation}
-where we replaced \(N-3\) with \(N\) assuming a large number of sites. Using this, the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.
-
-\subsection{Translation symmetry and a conserved total momentum}
-From the form in eq.~\ref{tilingPrescriptionFinal}, the tiled Hamiltonian is symmetric under global many-body translations of the kind defined in eq.~\ref{translationDefinition}, by arbitrary lattice spacings:
-\begin{equation}\begin{aligned}\label{translationSymmetry}
-	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})T({\bf a}) = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r + a}) = \sum_{{\bf r}^\prime}\mathcal{H}_\text{aux}({\bf r}^\prime)\\
-	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{cbath-nint}T({\bf a}) = \mathcal{H}_\text{cbath-nint}\\
-	&\implies T({\bf a})^\dagger\mathcal{H}_\text{tiled}T({\bf a}) = \mathcal{H}_\text{tiled}~.
-\end{aligned}\end{equation}
-In the first equation, we used the fact that the translation operator simply translates the auxiliary model at the position \({\bf r}\) into another one at the position \({\bf r} + {\bf a}\).
-Since both are part of the summation, the summation remains unchanged.
-The second equation uses the fact that the Hamiltonian \(\mathcal{H}_\text{cbath-nint}\) is that of a tight-binding model and is therefore translation-invariant.
-The fact that the Hamiltonian \(\mathcal{H}_\text{tiled}\) commutes with the many-body translation operator implies that the total crystal momentum \(\vec k\) is a conserved quantity.
-
-\section{Form of the eigenstates: Bloch's theorem}
-In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\bf k}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_i}\), where \({\bf r}_i\) sums over the positions of the local Hamiltonians.
-Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation by an arbitrary number of lattice spacings \({n\bf a}\):
-\begin{equation}\begin{aligned}
-	T^\dagger(n{\bf a})\ket{\Psi_{{\bf k}}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_{i + n}} = e^{-in{\bf k}\cdot{\bf a}}\ket{\Psi_{\bf k}}
-\end{aligned}\end{equation}
-The definition and some properties of these global translation operations were provided in subsection~\ref{formalDescription}.
-It was shown there that they share eigenstates with the total momentum operator.
-In a lattice model, this continuous symmetry gets lowered to its discrete form: the total {\it crystal} momentum is conserved by any scattering process.
-As a result, the eigenstates can be labelled using the combined index \(s = \left({\bf k}, n\right) \) where \({\bf k}\) is the total crystal momentum and \(n\) is a band index \(n\).
-
-The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using eq.~\ref{tilingPrescriptionFinal} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}).
-This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) defined in eq.~\ref{unitCellHamiltonian} can be used to construct eigenstates of the lattice Hamiltonian.
-The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
-
-The state \(\ket{\psi_n\left({\bf r}_d\right)}\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself has been averaged over \(\mathcal{Z}\) zeroth sites.
-Accordingly, we can express the averaged eigenstate \(\ket{\psi_n\left({\bf r}_d\right)}\) as
-\begin{equation}\begin{aligned}
-	\ket{\psi_n\left({\bf r}_d\right)} = \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z} \in \text{NN}({\bf r}_d)}\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}~,
-\end{aligned}\end{equation}
-where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\).
-With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:
-\begin{equation}\begin{aligned}\label{eigenstateProposal}
-	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d, {\bf z}\right)}~,
-\end{aligned}\end{equation}
-where \(N\) is the total number of lattice sites and \({\bf r}_d\) is summed over all lattice spacings.
-The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands.
-The ground state \(s = s_0\) is obtained by setting \({\bf k}\) and \(n\) to 0:
-\begin{equation}\begin{aligned}\label{groundstateProposal}
-	\ket{\Psi_\text{gs}} \equiv \ket{\Psi_{s_0}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d, {\bf z}\right)}
-\end{aligned}\end{equation}
-
-\section{One-Particle Greens Functions}
-\subsection{Momentum-space}
-In the previous part, we proposed a form for the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{gs}}\) of the auxiliary models.
-In this section, we will relate one-particle Greens functions of the bulk lattice to those of the auxiliary model.
-We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
-We define the retarded time-domain lattice \(k-\)space Greens function at zero temperature as
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c_{{\bf K}\sigma}(t), c^\dagger_{{\bf K}\sigma} \right\} | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(t\): 
-\begin{equation}\begin{aligned}\label{heisenberg}
-	c_{{\bf K}\sigma}(t) = e^{it H_\text{tiled} }c_{{\bf K}\sigma}e^{-i t H_\text{tiled}}~.
-\end{aligned}\end{equation}
-We now proceed to simplify one of the terms of the anticommutator (for simplicity of notation):
-\begin{equation}\begin{aligned}\label{greensFunction1}
-	&\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_{\vec r,\vec \Delta}e^{-i{\bf K}_0\cdot\vec\Delta}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-To make further progress, we insert the identity resolution \(1 = \sum_s\ket{\Psi_s}\bra{\Psi_s}\) in between the two operators, where \(s=\left({\bf k}, n\right)\) sums over all eigenstates (with energies \(\tilde E_s\)).
-The lattice eigenstates themselves can again be written in terms of those of the auxiliary model, using eq.~\ref{eigenstateProposal}:
-\begin{equation}\begin{aligned}
-	\ket{\Psi_s}\bra{\Psi_s} = \sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\vec k\cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}~.
-\end{aligned}\end{equation}
-With this, eq.~\ref{greensFunction1} becomes
-	\begin{equation}\begin{aligned}\label{greensfunction2}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\vec k_0\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-In order to bring this expression closer to the form of an auxiliary model Greens function, we would like to transform the initial and final states \(\ket{\psi(\vec r)}\) and \(\ket{\psi(\vec r + \vec \Delta)}\) to apply to the same auxiliary model.
-This is done by using the relation: \(\ket{\psi(\vec r + \Delta)} = T^\dagger(\vec \Delta)\ket{\psi(\vec r)}\), where \(T^\dagger(\vec \Delta)\) translates all lattice sites by the vector \(\vec\Delta\).
-\begin{equation}\begin{aligned}
-	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) T^\dagger(\vec \Delta) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
-\end{aligned}\end{equation}
-The effect of the translation operators on the \(k-\)space annihilation operator can be easily ascertained by transforming it to real-space, using the Fourier transform definition
-\begin{equation}\begin{aligned}\label{fourTransf}
-	c({\bf K}) = \frac{1}{\sqrt N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r})~.
-\end{aligned}\end{equation}
-Upon applying this, we get
-\begin{equation}\begin{aligned}\label{translationOnField}
-	T\left(\vec a\right) c({\bf K}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}T\left(\vec a\right) c({\bf r}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r} - \vec a) = e^{-i{\bf K}\cdot\vec a}c({\bf K})~.
-\end{aligned}\end{equation}
-Using this identity on the above expression gives
-\begin{equation}\begin{aligned}
-	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = e^{-i{\bf K} \cdot \vec \Delta}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
-\end{aligned}\end{equation}
-Finally replacing this all the way back into eq.~\ref{greensfunction2} gives
-	\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K}\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime - \vec\Delta)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-To further unify the operators, we make the substitution \(\vec \Delta^\prime \to \vec \Delta^\prime + \vec \Delta\), leading to the expression
-	\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K} - \vec k\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-The sum over \(\vec\Delta\) can now be carried out, resulting in
-\begin{equation}\begin{aligned}\label{greensfunction3}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~,
-\end{aligned}\end{equation}
-where the sum over \(s=(\vec k, n)\) has been reduced to a sum over the auxiliary model eigenstate index \(n\) because of the Kronecker delta \(\delta\left(\vec k_0 + {\bf K} - \vec k\right)\).
-This can be further simplified by splitting the sum over \(\vec\Delta^\prime\) into positive and negative parts and then making the transformation \(\vec r^\prime \to \vec r^\prime + \vec \Delta^\prime\):
-\begin{equation}\begin{aligned}
-	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime-\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}\right] \\
-																																												   &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\right] \\
-\end{aligned}\end{equation}
-For each pair of \(\vec r^\prime\) and \(\vec\Delta^\prime\), the term within the box brackets has the form of a two-level Hamiltonian between the states \(\ket{\psi_n(\vec r^\prime)}\) and \(\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\), with a tunnelling amplitude \(e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\).
-The term can therefore be written in the eigenbasis of this Hamiltonian:
-\begin{equation}\begin{aligned}
-	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &=\frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right],
-\end{aligned}\end{equation}
-where \(\ket{\chi_n^\pm(\vec r^\prime,\vec\Delta^\prime)} = \frac{1}{\sqrt 2}\left[\ket{\psi_n(\vec r^\prime)} \pm e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime + \vec\Delta^\prime)}\right] \) are the eigenvectors of the tunnelling Hamiltonian with eigenvalues \(\pm 1\) respectively.
-With this basis transformation, we can rewrite eq.~\ref{greensfunction3} as
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-
-In order to make the expression more transparent, we consider the various components separately:
-\paragraph{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}:
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-These terms represent those contributions to the total Greens function that arise from excitations that start and end at a specific auxiliary model (at \(\vec r\)), and also evolve dynamically within the same auxiliary model.
-These terms are therefore exactly equal to the auxiliary model Greens function at position \(\vec r\), and are the most dominant contribution due to the localised nature of the impurity model.
-
-\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}:
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime \neq \vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-These are more non-local contributions; they involve excitations whose time evolution is governed by a different auxiliary model than the terminal one.
-These contributions are highly suppressed in the Kondo screened phase because of the strong entanglement of the singlet ground state.
-
-\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime \neq 0\)}:
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime \neq \vec r,\vec \Delta^\prime \neq 0} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-These are the most non-local contributions; they involve excitations whose time evolution is governed by three different auxiliary models. Accordingly, these contributions are further suppressed.
-
-We now consider each type of contribution in more detail.
-\subsection{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}
-Restricting ourselves to just the single auxiliary model contributions gives
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-We first consider more carefully the transition operator \(\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\) for the 1-particle excitation giving rise to the above Greens function.
-Within our auxiliary model approach, gapless excitations within the lattice model are represented by gapless excitations of the impurity site, specifically those that screen the impurity site and form the local Fermi liquid.
-As a result, the uncoordinated \(\mathcal{T}-\)matrix for the lattice model must be replaced by a combined \(\mathcal{T}-\)matrix within the impurity model that captures those gapless excitations that occur in connection with the impurity, and projects out the uncorrelated excitations that take place even when the impurity site is decoupled from the bath.
-
-In order to construct this auxiliary model \(\mathcal{T}-\)matrix, we note that the impurity site can have both spin and charge excitations.
-Considering both excitations, the modified \(\mathcal{T}-\)matrix that constructs \(k-\)space excitations in correlation with the impurity site are
-\begin{equation}\begin{aligned}\label{tmatrix}
-	\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\left(\sum_{\sigma^\prime}c^\dagger_{d\sigma} + \text{h.c.}\right) + c_{{\bf K}\sigma}\left(S_d^+ + \text{h.c.}\right)~,
-\end{aligned}\end{equation}
-leading to the updated expression for the complete Greens function:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-
-In order to convert this into a more useful form, we use eq.~\ref{heisenberg}:
-\begin{equation}\begin{aligned}
-		\braket{\psi_{0}(\vec r) | \mathcal{T}_{{\bf K}\sigma}(t) | \psi_n(\vec r)} = \braket{\psi_{0}(\vec r) | e^{it H_\text{tiled} }\mathcal{T}_{{\bf K}\sigma}e^{-i t H_\text{tiled}} | \psi_n(\vec r)}~.
-\end{aligned}\end{equation}
-Guided by the relation in eq.~\ref{tilingPrescriptionFinal} \(H_\text{tiled} = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}\) between the tiled Hamiltonian and the auxiliary model, we assume that the operator \(e^{-i t H_\text{tiled}}\) acting on the state \(\ket{\psi_n(\vec r)}\) involves the excitation energy \(E_n\) of only a single auxiliary model.
-Specifically, \(E_n\) is the energy of the eigenstate \(\ket{\psi_n(\vec r)}\).
-This is supported by the fact that this class of contributions to the Greens function is completed within a single auxiliary model.
-Accordingly, we replace \(H_\text{tiled}\) with \(E_n - \varepsilon_{\bf k} \), where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\) and \({\bf k}\) is the crystal momentum associated with the state \(\ket{\psi_n(\vec r)}\).
-This momentum was found to be constrained to \({\bf k}_0 + {\bf K}\) below eq.~\ref{greensfunction3}.
-In the same way, the action of \(H_\text{tiled}\) on the terminal state \(\ket{\psi_{0}(\vec r)}\) gives \(E_0 - \varepsilon_{\bf k_0}\), where \(E_0\) is the ground state energy of the auxiliary model at \({\bf r}\).
-Applying this to our expression gives
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[e^{-it\omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + e^{-it\omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~,
-\end{aligned}\end{equation}
-where \(\omega_p = (E_n - \varepsilon_{\bf k_0 + \bf K}) - (E_0 - \varepsilon_{\bf k_0})\) is the particle-excitation cost and \(\omega_h = -\omega_p\) is the hole-excitation cost.
-We now introduce the Fourier transform \(g(\omega) = \int~dt~ e^{i\omega T}f(t)\) to obtain the frequency-domain Greens function in its spectral representation:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; \omega) = \frac{1}{N}\sum_{\vec r}\sum_n \braket{\psi_{0}(\vec r) | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-For each value of \({\vec r}\), the term within that summation is simply the Greens function (for the excitation \(\mathcal{T}_{{\bf K}\sigma}\)) of the auxiliary model with the impurity site at \({\vec r}\).
-Since all these impurity models are physically equivalent (because of translation invariance), we can replace the average over \({\bf r}\) with the value obtained from any one auxiliary model.
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; \omega) = \sum_n \braket{\psi_{0} | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}} ~.
-\end{aligned}\end{equation}
-
-\subsection{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}
-Allowing for more non-local contributions, and updating the \(\mathcal{T}-\)matrix similar to the previous section gives the following Greens function:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-In order to allow computations within a single auxiliary model, we replace the translated state \(\ket{\psi_n(\vec r^\prime)}\) with \(T^\dagger(\vec r \to \vec r^\prime)\ket{\psi_n(\vec r)} \), where \(T^\dagger(\vec r - \vec r^\prime)\) translates all sites by the vector \(\vec r^\prime - \vec r\).
-This leads to a modified correlation function but within a single auxiliary model:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_{n,\vec r, \vec r^\prime} \bra{\psi_{0}(\vec r)} &\left[\mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.
-\\
-								&\left.
-\mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-In fact, by the same arguments as in the previous section, we can obtain a frequency-resolved Greens function:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; \omega) = \sum_n \bra{\psi_{0}} &\left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.\\
-															&\left.
-\frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}} ~.
-\end{aligned}\end{equation}
-To obtain the above, we used the fact that \(H_\text{tiled}\) commutes with the translation operator.
-
-%TODO
-%By expanding in terms of the small parameter $\frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}}$, this expression for $\Sigma_{H-H}(\vec k,\omega)$ can be recast in the following form:
-%\begin{equation}\begin{aligned}
-%	\Sigma_{H-H}(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~\label{selfenergy2}
-%\end{aligned}\end{equation}
-%where $\Sigma_\text{loc}$ and $\Sigma_\text{near-n}$ correspond to the local and nearest-neighbour self-energies defined on the real-space lattice 
-%\begin{eqnarray}
-%\Sigma_\text{loc}(\omega) &=& \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^{(0)}} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}}~,\\ 
-%\tilde{\Sigma}(\vec k, \omega)&=&\xi_{\vec k}\Sigma_\text{near-n}~,~\Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}^2}~.
-%\end{eqnarray}
-%We note that the form of $\Sigma(\vec k, \omega)$ obtained by us is similar to the form proposed on phenomenological grounds in the generalised DMFT + $\Sigma$ approach~\cite{sadovskii2012}.
-
-\section{Equal-Time Ground State Correlators}\label{staticCorr}
-Properties of the ground state can be probed using static correlation functions that are expectation values of operators that propagate excitations.
-We will consider general correlations, in real and momentum space.
-\subsection{Real-space correlation functions}
-We first consider a real-space operator \(\mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r})\) that quantifies the presence of correlations over a distance \({\bf \Delta}\).
-The correlation function itself is given by the expectation value of this operator in the ground state:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_1 + {\bf r}^\prime + {\bf r}_c + {\bf r}\right)  | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_1 + {\bf r}_c + {\bf r}\right)} e^{-i{\bf k}_0\cdot\left({\bf r}_1 - {\bf r}_2\right)}~,
-\end{aligned}\end{equation}
-where \({\bf r}_1\) and \({\bf r}_1 + {\bf r}^\prime\) are the positions of the incoming and outgoing auxiliary model states, relative to \({\bf r}_c + {\bf r}\), and \({\bf k}_0\) is the crystal momentum of the ground state (which we will immediately set to zero).
-In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
-Substituting this appropriately for both the auxiliary model states gives:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_1 + {\bf r}^\prime + {\bf r}\right) \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) T^\dagger\left({\bf r}_1 + {\bf r}\right) | \psi_\text{gs}\left({\bf r}_c\right)}\\
-								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}^\prime\right) \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
-								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-As a final cosmetic change, we transform \({\bf r}_1 \to -{\bf r}\):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r},{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-Like in the Greens function calculation, we now consider the various kinds of contributions separately.
-
-\subsubsection{Intra-auxiliary model contributions: \({\bf r}^\prime = 0\)}
-These terms describe excitations that start and propagate within the same auxiliary model, upto a distance \({\bf \Delta}\):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-With an eye towards introducing the impurity operators into the correlations, we insert a complete basis defined by the eigenstates \(\left\{\ket{\psi_n\left({\bf r}_c\right)}\right\} \) of the auxiliary model into the expression:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\sum_{n}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \ket{\psi_n\left({\bf r}_c\right)}\bra{\psi_n\left({\bf r}_c\right)} \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-
-For the excitations that exist purely in the conduction bath \(({\bf r} \neq {\bf r}_c)\), the excitation operators must be suitably modified (see the arguments around eq.~\ref{tmatrix}) in order to incorporate Kondo screening.
-The modified excitation operators are generally defined as
-\begin{equation}\begin{aligned}\label{operatorTmatrix}
-	\mathcal{\tilde O}({\bf r}) = \mathcal{O}({\bf r})\mathcal{O}^\dagger(d) \mathcal{P}_\text{gs} ~,
-\end{aligned}\end{equation}
-where \(\mathcal{O}^\dagger(d)\) is the hermitian conjugate of the correlation operator \(\mathcal{O}\), but applied on the impurity sites.
-This therefore constitutes a time-reversed scattering process on the impurity site relative to the process in the bath.
-The operator \(\mathcal{P}_\text{gs}\) projects onto the ground state of the auxiliary model, since we are interested in ground state correlations.
-The operator multiplying the old correlation operator represents all possible excitations of the impurity site, and ensure that the bath and impurity excitation processes take place in correlation.
-The projector ensures that only tripartite correlations between the impurity site and the two momentum states are captured by the correlation, which is what's desired within the tiling method.
-
-With this modified operator, this class of correlation functions can be written as
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r} }\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-This can be interpreted as the fact that within our auxiliary model formalism, the correlation between the sites \({\bf r}\) and \({\bf \Delta + r}\) can only occur through a transition process that connect one of the sites with the impurity site and then a return process that connects the impurity site with the other site.
-
-\subsubsection{Inter-auxiliary model contributions: \({\bf r}^\prime \neq 0\)}
-These are the most non-local contributions, and involve excitations that connect different auxiliary models:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}^\prime \neq 0}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-
-\subsection{Momentum-space correlation functions}
-We now consider momentum space correlations, through a general operator \(\mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1)\):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-Note that \(\mathcal{O}\) itself is a two-particle operator.
-To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_2\right)  | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_1\right)}~,
-\end{aligned}\end{equation}
-where \({\bf r}_1\) and \({\bf r}_2 \) are the positions of the incoming and outgoing auxiliary model states.
-In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
-Substituting this appropriately for both the auxiliary model states gives:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_c\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) T^\dagger\left({\bf r}_1 - {\bf r}_c\right) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-In order to simplify the translation operators, we can use eq.~\ref{translationOnField}.
-For that, we would need to know whether the operator \(\mathcal{O}\) involves the net transfer of momentum.
-If \(\mathcal{O}({\bf k})\) commutes with the total number operator \(n_{\bf k} = \sum_\sigma n_{{\bf k},\sigma}\), there is no momentum transfer.
-Examples of such operators are spin operators, \(S_{\alpha\beta}({\bf k}) \equiv c^\dagger_{{\bf k \alpha}}c_{{\bf k}\beta}\), and density operators \(n_{{\bf k}\alpha}\).
-If \(\mathcal{O}({\bf k})\) does not commute with \(n_{\bf k}\), there is a net transfer of momentum, and one such operator would be the charge isospin operator \(C^+({\bf k}) = c^\dagger_{{\bf k}\uparrow}c^\dagger_{{\bf k}\downarrow}\).
-For the first kind of operators, we have \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = \mathcal{O}({\bf k})\), while the for the latter, we get \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = e^{-{\bf a}\cdot{\bf 2k}}\mathcal{O}({\bf k})\), where \(2{\bf k}\) represents the momentum being transferred by the operator.
-We consider the two cases separately.
-
-\subsubsection{Momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] = 0\)}
-For these operators, the expression for the correlation gives
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
-										 &=\sum_{{\bf r},{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-To obtain the last form, we defined \({\bf \Delta}={\bf r}_2 - {\bf r}_1\) as the distance between the incoming and outgoing auxiliary model states, and preformed the sum over the free variable \({\bf r}_1\) to cancel out the factor of \(1/N\).
-Just like before, this expression can be decomposed into a term that involves a single auxiliary model and other terms that involve two distinct auxiliary models.
-
-\subsubsection{Non-momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] \neq 0\)}
-This class of operators incur an additional phase factor of \(e^{-{\bf a}\cdot{\bf 2k}}\) when the translation operators are translated across them:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}e^{2i\left( {\bf r}_1 - {\bf r}_c \right) \cdot \left( {\bf k}_1 - {\bf k}_2 \right)} \\
-										 &= \delta_{{\bf k}_1, {\bf k}_2}\sum_{{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-For this expression, we again defined \({\bf \Delta}\) similar to before, and carried out the sum of \({\bf r}_1\) involving the exponential to obtain a factor of \(N \delta_{{\bf k}_1, {\bf k}_2}\).
-The Kronecker delta factor is a manifestation of translational invariance and the associated total momentum conservation.
-
-As it stands, operators like \(\mathcal{O}({\bf k}_1)\) act purely on the conduction bath degrees of freedom.
-In order to incorporate impurity-bath correlation effects, we modify these operators using the appropriate \(T-\)matrices, by employing eq.~\ref{operatorTmatrix}.
-The final computations are carried out using these modified operators.
-
-\section{Entanglement}
-We will now describe the prescription of calculating entanglement measures of the lattice model from within our auxiliary model treatment.
-In this section, we are interested mainly in two such measures, the entanglement entropy and the mutual information.
-Given a pure state \(\ket{\Psi}\) describing the complete system, the entanglement entropy \(S_\text{EE}(\nu)\) of a subsystem \(\nu\) quantifies the entanglement of \(\nu\) with the rest of the subsystem, and is defined as
-\begin{equation}\begin{aligned}
-	S_\text{EE}(\nu) = -\text{Tr}\left[\rho(\nu)\log \rho(\nu)\right],\quad \rho(\nu) = \text{Tr}_\nu\left[\ket{\Psi}\bra{\Psi}\right] 
-\end{aligned}\end{equation}
-where \(\text{Tr}\left[\cdot\right] \) is the trace operator, and \(\rho(\nu)\) is the reduced density matrix for the subsystem \(\nu\) obtained by taking the partial trace \(\text{Tr}_\nu\) (over the states of \(\nu\)) of the full density matrix \(\rho = \ket{\Psi}\bra{\Psi}\).
-If the subsystem \(\nu\) describes local regions in real space (or states in \(k-\)space), we might be interested in the entanglement between two such subsystems \(\nu_1\) and \(\nu_2\).
-The correct measure to quantify such entanglement is the mutual information:
-\begin{equation}\begin{aligned}
-	I_2(\nu_1,\nu_2) = S_\text{EE}(\nu_1) + S_\text{EE}(\nu_2) - S_\text{EE}(\nu_1 \cup \nu_2)~,
-\end{aligned}\end{equation}
-where \(\nu_1 \cup \nu_2\) is a larger subsystem formed by combining \(\nu_1\) and \(\nu_2\).
-
-\subsection{Real-space entanglement}
-Real-space entanglement measures can be used to probe delocalisation-localisation transitions.
-The simplest such measure is the entanglement of a local mode.
-Since the local entanglement entropy will be uniform at each lattice site for a system with translation invariance, it suffices to calculate the real-space averaged entanglement entropy \(S_\text{EE}^\text{loc} = \frac{1}{N}\sum_{{\bf r}}S_\text{EE}\left( {\bf r} \right) \).
-By visualising the lattice model as a superposition of auxiliary models placed at various sites (eq.~\ref{tilingPrescriptionFinal}), the real space average of the lattice model can be thought of as an average over sites of a particular impurity model, and then a second average over all the impurity models.
-But since all all impurity models are equivalent to each other, the second average is redundant.
-Secondly, all correlations must derive from the impurity site, which can be formally encoded by subtracting, from this average, the corresponding contribution obtained in the absence of the impurity site.
-In total, the lattice-auxiliary model relation for the local entanglement entropy can be written as
-\begin{equation}\begin{aligned}
-	S_\text{EE}^\text{loc} = \frac{1}{N}\sum_{{\bf r}}\left[S_\text{EE}({\bf r}_d + {\bf r}) - S_\text{EE}^{(0)}({\bf r}_d + {\bf r})\right] ~,
-\end{aligned}\end{equation}
-where \({\bf r}_d\) is the impurity site position, \({\bf r}\) is the distance of a conduction bath site from the impurity site (can be zero), and \(S_\text{EE}({\bf r}_d + {\bf r})\) is the entanglement entropy, calculated within the impurity model, at the locatiom \({\bf r}_d + {\bf r}\).
-\(S^{(0)}_\text{EE}({\bf r}_d + {\bf r})\) is the same entanglement entropy, but calculated for an impurity model but with vanishing impurity-bath hybridisation and bath interaction.
-
-\subsection{Momentum-space entanglement}
-Entanglement measures in \(k-\)space can provide valuable information regarding the Fermi surface structure and the nature of gapless excitations proximate to it.
-The most elementary measure is the entanglement entropy \(S_\text{EE}({\bf q})\) of a single excitation carrying momentum \({\bf q}\).
-Unlike \(S_\text{EE}^\text{loc}\), this does not involve an average, and involves a single computation:
-\begin{equation}\begin{aligned}
-	S_\text{EE}^\text{loc} = S_\text{EE}({\bf q}) - S_\text{EE}^{(0)}({\bf q})~.
-\end{aligned}\end{equation}
-It is possible to improve this by considering inter-auxiliary model contributions in the reduced density matrix \(\rho({\bf q})\). On the lattice model, \(\rho({\bf q})\) is defined as
-\begin{equation}\begin{aligned}\label{SEE-k}
-	\rho({\bf q}) = \text{Tr}_{\bf q}\left[\ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\right] ~,
-\end{aligned}\end{equation}
-where \(\text{Tr}_{\bf q}\left[\cdot\right]\) is the partial trace over the Hilbert space of \({\bf q}\), and \(\ket{\Psi_\text{gs}}\) is the tiled ground state.
-Using eq.~\ref{groundstateProposal}, we can write the ground state in terms of those of the auxiliary model.
-These leads to two classes of terms, one purely within a single auxiliary model ground state \(\ket{\psi_\text{gs}}\), and the other involving transitions across auxiliary models:
-\begin{equation}\begin{aligned}
-	\rho({\bf q}) = \text{Tr}_{\bf q}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d)}\right] + \frac{1}{N}\text{Tr}_{\bf q}\sum_{{\bf r}}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d + {\bf r})}\right]~,
-\end{aligned}\end{equation}
-where \(\ket{\psi_\text{gs}({\bf r}_d)}\) is a reference auxiliary model ground state, and \(\ket{\psi_\text{gs}({\bf r}_d + {\bf r})}\) sums over other auxiliary models at increasing distances from this reference model.
-The first term leads to the expression in eq.~\ref{SEE-k}, while the second term can be used to improve this estimate.
-Away from any quantum critical points, the localised nature of the impurity-bath hybridisation ensures that impurity correlations decay exponentially away from the transition.
-This ensures that the second term is very small away from a critical point.
-We therefore restrict ourselves to just the first term in the present work.
+	&\Delta J^{(0)}_{{\bf k}, {\bf k}^\prime} = -\sum_{{\bf q} \in \text{PS}} \frac{J^2 \frac{1}{2}\sum_a\cos\left({\bf k}^\prime_a - {\bf q}_a\right)\frac{1}{2}\sum_a\cos\left({\bf q}_a - {\bf k}_a\right) - 2JW \sum_a\cos\left({\bf k}^\prime_a - {\bf k}_a\right)}{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{4}}~,
+\end{aligned}\end{equation}
+where \(a\) sums over the \(x\) and \(y\) components of the momenta.
+We see that unlike the bare Kondo coupling \(J_{{\bf k}, {\bf k}^\prime}\) that depends only on the momentum difference \({\bf k} - {\bf k}^\prime\), the renormalisation \(\Delta J^{(0)}\) depends on products of the momenta.
+This shows the form of the Kondo coupling continuously changes under renormalisation.
 
@@
 	\includegraphics[width=0.23\textwidth]{scattProb-5.pdf}
-	\caption{Variation of \(\Gamma\) as \(W/J\) is increased from left to right and top to bottom.
-Each plot shows whether \(\Gamma({\bf k})\) is relevant (white) or irrelevant (black).
-The antinodal points are the first state to be removed from the Kondo cloud, while the node is the last to be removed.}
+	\caption{Variation of the total scattering probability \(\Gamma({\bf k})\) (defined in the main text) as \(W/J\) is increased from left to right.
+Each plot shows whether \(\Gamma({\bf k})\) is RG-relevant (pink) or irrelevant (black).
+RG-relevant values of \(\Gamma({\bf k})\) indicate that the \(k-\)point participates in Kondo screening at low-energies, while an irrelevant value indicates that the \(k-\)point is decoupled from the impurity site.
+As \(W/J\) is made more negative, the antinodal points are the first state to be removed from the Kondo cloud, while the node is the last to be removed.}
 	\label{gamma_kxky}
@@
 \subsection{Spin-correlations across the pseudogap}
-In figure ~\ref{spinCorr}, we show the evolution of the spin-flip correlations \(\chi_s(d,\vec k) = \left<S_d^+ S_{\vec k}^- + \text{h.c.}\right>\) in \(k-\)space, as the system is tuned through the pseudogap.
+In figure ~\ref{spinCorr}, we show the evolution of the spin-spin correlation \(\chi_s(d,\vec k) = \left<{\bf S_d}\cdot{\bf S}_{\vec k}\right>\) in \(k-\)space, as the system is tuned through the pseudogap.
 At vanishing value of the interaction \(W\), the spin correlations are concentrated around the antinode, because of the \(p-\)wave nature of the Kondo interaction.
@@
 	\includegraphics[width=0.23\textwidth]{SF-1.pdf}
+	\includegraphics[width=0.23\textwidth]{SF-2.pdf}
 	\includegraphics[width=0.23\textwidth]{SF-3.pdf}
-	\includegraphics[width=0.23\textwidth]{SF-5.pdf}
-	\includegraphics[width=0.23\textwidth]{SF-6.pdf}
-	\caption{\(k-\)space distribution of spin-flip scattering correlation \(\chi_s(d,\vec k)\) (defined in the main text).
-The last three figures \((W/J=-1.74, -1.83, -1.84)\) show how \(k-\)points starting from the antinode progressively exit the Kondo cloud, the node being the last \(k-\)point to decouple from the impurity.}
+	\includegraphics[width=0.23\textwidth]{SF-4.pdf}
+	\caption{\(k-\)space distribution of spin-spin correlation \(\chi_s(d,\vec k)\) (defined in the main text).
+The last three figures show how \(k-\)points starting from the antinode progressively exit the Kondo cloud, the node being the last \(k-\)point to decouple from the impurity.}
 	\label{spinCorr}
 \end{figure}
-
-As a second probe of the pseudogapping phenomenon, we have also studied the entanglement entropy (EE) \(S_\text{EE}(\vec k)\), which is just the von Neumann entropy \(-\text{Tr}\left[\rho \ln \rho\right] \) of the reduced density matrix \(\rho_{\vec k}\) for each \(k-\)state.
-In accordance with the Kondo spin correlations \(\chi_s\), the EE shows the sequential decoupling, from the impurity, of the antinodes followed by the nodes.
-
-Studies of \(k-\)space mutual information, \(I_2(\vec k, k_\text{N})\) and \(I_2(\vec k, k_\text{AN})\), between any given \(k-\)state and the node and antinode respectively, have revealed that each point interacts most strongly with it's own neighbourhood (see Supplementary Materials).
-This feature is in contrast to the charge-transfer correlations in the bath, that show ``long-ranged" interactions between the node and the antinode.
-These correlations will be discussed immediately after this, and are primarily responsible for driving the impurity transition and destabilising the Kondo cloud.
 
@@
 
-\subsection{Emergence of a two-channel Kondo Model as the low-energy theory in the pseudogap phase}
+\section{Nature of Gapless Excitations in the Impurity Pseudogap}
+\subsection{Emergence of a two-channel Kondo Model}
 As the bath interaction \(W\) is tuned through the L-PG phase, the four nodal points in the Brillouin zone are the last to decouple from the impurity.
@@
 The only source of information transfer between the two regions is the fact that they interact with the same impurity local moment.
-
 Eq.\ref{twoChannel} tells us that the low-energy dynamics of the embedded eSIAM close to the Kondo-breakdown transition is governed by an emergent {\bf two-channel Kondo model}, with the conduction bath states in the sets \(S^\pm\) making up the two channels.
-It is well-known that the two-channel Kondo model hosts non-Fermi liquid excitations at low-energies; this is also corroborated by our calculations of the quasiparticle residue \(Z_\text{imp}\) for the local gapless excitations.
-For a single-particle Greens function of an interacting model, the quasiparticle residue \(Z\) is defined as
-\begin{equation}\begin{aligned}
-	G = Z G^{(0)} + G_\text{inc}~,
-\end{aligned}\end{equation}
-where \(G^{(0)}\) is the non-interacting Greens function and \(G_\text{inc}\) is contribution to the Greens function arising from incoherent short-lived excitations.
+
+\subsection{Marginal Fermi liquid behaviour in the pseudogap}
+It is well-known that the two-channel Kondo model hosts non-Fermi liquid excitations at low-energies~\cite{Tsvelick_weigmann_mchannel_1985,emery_kivelson}; that this also happens in the present model is corroborated by our calculations of the quasiparticle residue \(Z_\text{imp}\) for the local gapless excitations.
+For a single-particle Greens function of an interacting model, the quasiparticle residue \(Z\) is defined as the spectral weight of low-energy resonance within the spectral function:
+\begin{equation}\begin{aligned}
+	G_k = \frac{Z}{\omega - \varepsilon_k - i \Sigma^{\prime\prime}} + G_\text{incoh}~,\quad 1/Z = 1- \frac{d \Sigma^{\prime}}{d\omega}~,
+\end{aligned}\end{equation}
+where \(\Sigma^\prime\) and \(\Sigma^{\prime\prime}\) are the real and imaginary parts of the self-energy, and \(G_\text{incoh}\) is contribution to the Greens function arising from incoherent short-lived excitations as well as high-energy features that are decoupled from the low-energy excitations~\cite{varma-physrevlett.63.1996}.
 Small values of \(Z\) indicate that the excitations cannot be described in terms of a Fermi liquid theory.
 Indeed, as shown in the right panel of Fig.~\ref{channelDecoupling}, the quasiparticle residue \(Z_\text{imp}\) of the impurity excitations becomes vanishingly small in the pseudogap region, signalling that the excitations are of a non-Fermi liquid nature.
-
-Given that this is a critical point in the impurity model phase diagram (separating the local Fermi liquid and local moment phases), it is not surprising that a quantum critical model emerges at that point.
-Signatures of the quantum critical nature include power-law divergence in various correlation functions as temperature \(T \to 0\), and non-Fermi liquid excitations replacing the local Fermi liquid.
+Given that the pseudogap phase is close to a critical point in the impurity model phase diagram (separating the local Fermi liquid and local moment phases), it is not surprising that a quantum critical model emerges at that point.
+
+Coleman and Ioffe have shown that by mapping the two-channel Kondo problem to a "compactified" form where the impurity spin hybridises with the spin and isospin degrees of freedom of a single conduction channel, the impurity self-energy can be shown to display marginal Fermi liquid behaviour~\cite{Coleman_tsvelik,Schofield1997}:
+\begin{equation}\begin{aligned}
+	\Sigma \propto \omega \ln \omega~.
+\end{aligned}\end{equation}
+As some of us have shown in a previous work~\cite{Patra2023MCK}, this can also be obtained from a renormalisation group calculation of the low-energy excitations of the two-channel overscreened fixed point.
+For the sake of completeness, we have reproduced the calculation here.
+By considering minimal hopping into the conduction bath, the low-energy excitations above the 2CK ground state are described by the following Hamiltonian~\cite{Patra2023MCK}:
+\begin{eqnarray}
+	\label{nfl_terms}
+	H_\mathrm{eff} =& \frac{8t^2}{{J}}\left[\left(S^z_{0,1}\right)^2 S^+_{0,2} + \left(S^z_{0,2}\right)^2 S^+_{0,1}\right] \left(S^-_{1,1} + S^-_{1,2}\right) + \mathrm{h.c.};
+\end{eqnarray}
+where \({\boldsymbol S}_{i,l} = \frac{1}{2}\sum_{\sigma_1,\sigma_2}c^\dagger_{i,\sigma_1,l}{\boldsymbol \sigma}_{\sigma_1,\sigma_2}c_{i,\sigma_2,l}\) are spin operators for the \(i^\text{th}\) site on the \(l^\text{th}\) conduction channel (\(l\) can be 1 or 2 for a two-channel model).
+The labels \(\sigma_1\) and \(\sigma_2\) are spin indices that can be \(\pm 1\).
+The site index \(0\) represents the bath sites connected immediately to the impurity site.
+The operator \(c^\dagger_{i,\sigma,l}\) creates an electron with spin \(\sigma\) on the \(i^\text{th}\) site of the \(l^\text{th}\) conduction channel.
+
+We will Fourier transform this effective Hamiltonian into \(k-\)space:
+\begin{eqnarray}
+	\label{k_space_od}
+	\frac{2t^2}{J}\sum_{\left\{k_i,k_i^\prime\right\}}\sum_{\sigma, l} &\left(e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \mathrm{h.c.}\right) ~.\qquad
+\end{eqnarray}
+Such a three particle interaction term was also obtained for the NFL phase of the 2D Hubbard model from a URG treatment (see Appendix B of Ref.\cite{anirbanmott1}).
+The channel indices in Eq.~\ref{k_space_od} can be mapped to the normal directions in~\cite{anirbanmott1}.
+The 2 particle-1 hole interaction in Eq.~\ref{k_space_od} has a diagonal component which can be obtained by setting \(k=k^\prime, k_1 = k_2^\prime\) and \(k_2 = k_1^\prime\):
+\begin{eqnarray}
+	H_\mathrm{MFL} &= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{2t^2e^{i\left(k_1 - k_2\right)a}}{J} \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right) + \mathrm{h.c.}\nonumber\\
+	&= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{4t^2}{J} \cos a\left(k_1 - k_2\right)  \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right).\qquad 
+\end{eqnarray}
+The most dominant contribution comes from \(k_1 = k_2 = k^\prime\), revealing the non-Fermi liquid metal~\cite{cox_jarrell_two_channel_rev,Andrei1995}:
+\begin{eqnarray}
+	\label{mfl_large}
+	H^*_\mathrm{MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)~.
+\end{eqnarray}
+A non-local version of this effective Hamiltonian was found to describe the normal phase of the Mott insulator of the 2D Hubbard model, as seen from a URG analysis~\cite{anirbanmott1,anirbanmott2}.
+Following~\cite{anirbanmott1}, one can track the RG evolution of the dual coupling \(R_j = \frac{4t^2}{J_j}\) at the \(j^\mathrm{th}\) RG step, in the form of the URG equation
+\begin{eqnarray}
+	\Delta R_j =- \frac{R_j^2}{\omega - \epsilon_{j}/2 - R_j/8}~.
+\end{eqnarray}
+In the RG equation, \(\epsilon_{j}\) represents the energy of the \(j^\mathrm{th}\) isoenergetic shell. It is seen from 
+the RG equation that \(R\) is relevant in the range of \(\omega < \frac{1}{2}\epsilon_j\) that has been used throughout, leading to a fixed-point at \(R^*/8 = \omega - \frac{1}{2}\epsilon^*)\).
+The relevance of \(R\) is expected because the strong coupling \(J\) is irrelevant and \(R \sim 1/J\).
+
+The renormalisation in \(R\) leads to a renormalisation in the single-particle self-energy~\cite{anirbanmott1}. The \(k-\)space-averaged self-energy renormalisation is
+\begin{eqnarray}
+	\Delta \Sigma(\omega) = \rho {R^*}^2\int_0^{\epsilon^*} \frac{d\epsilon_j}{\omega - \epsilon_j/2 + R_j/8}~.
+\end{eqnarray}
+The density of states can be approximated to be \(N^*/R^*\), where \(N^*\) is the total number of states over the interval \(R^*\).
+As suggested by the fixed point value of \(R_j\), we can approximate its behaviour near the fixed point by a linear dependence on the dispersion \(\epsilon_j\).
+The two limits of the integration are the starting and ending points of the RG.
+We start the RG very close to the Fermi surface and move towards the fixed point \(\epsilon^*\).
+Near the starting point, we substitute \(\epsilon = 0\) and \(R = \omega\), following the fixed point condition.
+From the fixed point condition, we also substitute \(R^*/8 = \omega - \frac{1}{2}\epsilon^*\).
+On defining \(\bar \omega = N^* \left(\omega - \frac{1}{2}\epsilon^*\right)\), we can write
+\begin{eqnarray}
+	\label{self_energy}
+	\Delta \Sigma(\omega) \sim  \bar \omega \ln \frac{N^* \omega}{\bar \omega}~.
+\end{eqnarray}
+The self-energy also provides the quasiparticle residue for each channel\cite{anirbanmott1}:
+\begin{eqnarray}
+	Z(\bar\omega) = \left(2 - \ln \frac{2\bar\omega}{N^* \omega}\right) ^{-1}~.
+\end{eqnarray}
+As \(\omega \to 0\), the \(Z\) vanishes, implying that the ground state is {\it not adiabatically connected} to the Fermi gas in the presence of the NFL terms.
+This is the orthogonality catastrophe~\cite{varma2002singular,anderson_infraredcat,yamada_catastrophe,yamada1979orthogonality} in the two-channel Kondo problem, and it is brought about by the presence of the channel-non diagonal terms in Eq.~\ref{mfl_large}.
+
+\section{The Tiling Algorithm}
+
+\subsection{Formal description of the tiling procedure}
+We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian.
+The first step is of course to identify an impurity model that can act as a good auxiliary model for out lattice model.
+The local behaviour of this impurity model should reflect the essential local physics of the lattice model.
+Typically, we will consider impurity model geometries where the real-space bath site connected directly to the impurity also harbours some kind of local interaction.
+We will henceforth refer to this site as the zeroth site.
+In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout.
+
+In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})\).
+The unit cell at the position \({\bf r}_d\) is then obtained by placing the zeroth site on all nearest-neighbours of \({\bf r}_d\) and averaging over these configurations:
+\begin{equation}\begin{aligned}\label{unitCellHamiltonian}
+	\mathcal{H}_\text{aux}({\bf r}_d) = \frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})~,
+\end{aligned}\end{equation}
+where \({\bf z}\) is summed over all nearest-neighbours of \({\bf r}_d\) and \(\mathcal{Z}\) is the number of such nearest-neighbours.
+
+In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice.
+For this, we define {\it many-particle global} translation operators \(T({\bf a})\) that translate all positions by a vector \({\bf a}\).
+In terms of manybody states and operators, their action is defined as
+\begin{equation}\begin{aligned}\label{translationDefinition}
+	&T^\dagger({\bf a}) \ket{{\bf r}_1, {\bf r}_2,\ldots} = \ket{{\bf r}_1 + {\bf a}}\otimes\ket{{\bf r}_2 + {\bf a}}\ldots\otimes\ket{{\bf r}_n + {\bf a}}\\
+	&T^\dagger({\bf a}) \mathcal{O}\left({\bf r}_1, {\bf r}_2,\ldots\right)T({\bf a}) = \mathcal{O}\left({\bf r}_1 + {\bf a}, {\bf r}_2 + {\bf a},\ldots\right)~,
+\end{aligned}\end{equation}
+where \(\ket{{\bf r}_1, {\bf r}_2,\ldots}\) is a state in the manyparticle Fock-space basis with the particles localised at the specified positions.
+For example, for a local fermionic creation operator \(c^\dagger({\bf r})\), we have
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a}) c^\dagger({\bf r}) T({\bf a}) = c^\dagger({\bf r} + {\bf a})~.
+\end{aligned}\end{equation}
+It acts similarly on the auxiliary model Hamiltonian:
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a})\mathcal{H}_\text{aux}({\bf r}_d)T({\bf a}) = \mathcal{H}_\text{aux}({\bf r}_d + {\bf a})~,
+\end{aligned}\end{equation}
+translating all sites by the vector \({\bf a}\). By introducing the Fourier transform to momentum space,
+\begin{equation}\begin{aligned}
+	\ket{{\bf r}_1, {\bf r}_2,\ldots} = \otimes_{j=1}^N \int d{\bf k}_j e^{-i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf k}_j}~,
+\end{aligned}\end{equation}
+it is easy to see that the total momentum states are eigenstates of the global translation operators:
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a})\ket{{\bf k}_1, {\bf k}_2,\ldots} &= \otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} T^\dagger({\bf a})\ket{{\bf r}_j}~,\\
+							    &=\otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf r}_j + {\bf a}}\\
+							    &=e^{-i {\bf a}_j\cdot{\bf k}_\text{tot}}\ket{{\bf k}_1, {\bf k}_2,\ldots},
+\end{aligned}\end{equation}
+where \({\bf k}_\text{tot} = \sum_j {\bf k}_j\) is the total momentum.
+
+The auxiliary model, being an impurity model, lacks translation symmetry.
+The lattice model does remain invariant under global translation operations.
+In order to reconstruct the full lattice model and restore its translation invariance, we translate the unit cell across all sites of the lattice:
+\begin{equation}\begin{aligned}
+	\label{tilingPrescription}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})\\
+				&= \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r} - {\bf r}_d)~ \\
+				&= \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d)~ \\
+\end{aligned}\end{equation}
+where \({\bf r}\) sums over all lattice sites.
+
+\subsection{Extending the Anderson impurity model: Identifying the correct auxiliary model}
+The standard Anderson model consists of a correlated impurity site coupled with a non-interacting conduction bath.
+The double occupancy cost on the impurity is \(U\), while the single-particle hopping strength between the impurity and the conduction bath is \(V\).
+Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes.
+We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model).
+The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
+\begin{equation}\begin{aligned}
+	\label{siam_attr}
+	\mathcal{H}_\text{E-S} = \mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} + \mathcal{H}_\text{imp-cbath}~,
+\end{aligned}\end{equation}
+where 
+\begin{itemize}
+	\item \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site,
+	\item \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and
+	\item \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 - V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath.
+\end{itemize}
+Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath.
+We have found that the e-SIAM has a stable local moment phase for \(U_b < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)).
+We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of an optical gap in the local spectral function beyond a certain value of interaction strength.
+Note that the impurity site and the conduction bath are both at half-filling.
+
+\subsection{Tiling towards a Hubbard-Heisenberg model with an embedded extended SIAM}
+In this subsection, we provide an explicit example of constructing a lattice model.
+We will consider a slightly more generalised version of the extended SIAM described in the previous section, where the impurity site coupled to the conduction bath purely through the s-wave channel.
+We will show that that model leads to a form of a Hubbard-Heisenberg model upon restoring translation invariance via repeated translation operations.
+The generalisation involve allowing an arbitrary filling on the impurity site and in the conduction bath, through two additional parameter: (i) a particle-hole asymmetry parameter \(\eta\) for the impurity site, (ii) a chemical potential for the conduction bath, and (iii) embedding the impurity into the lattice of the 2D conduction bath.
+This modified impurity model is shown in Fig.~\ref{embeddedEsiam}.
+The first term modifies the impurity Hamiltonian \(\mathcal{H}_\text{imp}\) into
+\begin{equation}\begin{aligned}\label{onsiteHamiltonian}
+	\mathcal{H}_\text{imp} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 - \eta\sum_\sigma \hat n_{{\bf r}_d\sigma}~.
+\end{aligned}\end{equation}
+where we have placed the impurity site at the position \({\bf r}_d\). The second term modifies the conduction bath Hamiltonian \(\mathcal{H}_\text{cbath}\):
+\begin{equation}\begin{aligned}\label{bathHamiltonian}
+	\mathcal{H}_\text{cbath} &= -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
+							 &- \frac{1}{2 \mathcal{Z}}U_b\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
+\end{aligned}\end{equation}
+where \(\left<{\bf r}_i, {\bf r}_j\right>\neq {\bf r}_d\) indicates that the sum is over all nearest-neighbour pairs of sites avoiding the impurity site \({\bf r}_d\).
+
+In this notation, the interaction Hamiltonian can be written as
+\begin{equation}\begin{aligned}\label{interactionHamiltonian}
+	\mathcal{H}_\text{imp-cbath} &= \frac{J}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}\sum_{{\bf z}\in\text{NN}({\bf r}_d)} {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \\
+								 & - \frac{V}{\sqrt{\mathcal{Z}}}\sum_{\sigma} \sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)
+\end{aligned}\end{equation}
+where \(\boldsymbol \tau = \left( \tau_x, \tau_y, \tau_z \right) \) is the vector of Pauli matrices. \(\sigma\) and \(\sigma^\prime\) can be \(\pm 1\) and represent up and down configurations.
+
+We now follow the prescription laid out in eq.~\ref{tilingPrescription}. The tiled Hamiltonian can be written as 
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{tiled} = \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} \right.\\
+\left.+ \mathcal{H}_\text{imp-cbath}\right]T({\bf r} - {\bf r}_d)~.
+\end{aligned}\end{equation}
+Note that in comparison to eq.~\ref{tilingPrescription}, we have dropped the sum over the zeroth sites, because our impurity model Hamiltonian (defined using eqs.~\ref{onsiteHamiltonian} through \ref{interactionHamiltonian}) already contains a sum over these zeroth sites.
+
+We consider the effect of the translation operations on each part of the Hamiltonian. We first have
+\begin{equation}\begin{aligned}
+	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d) \\
+	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \right.\\
+	 &\left.- \frac{U_b}{2\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}\right]T({\bf r} - {\bf r}_d) \\
+	=& -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
+	 &- \frac{U_b}{2\mathcal{Z}}\sum_{\bf r}\sum_{{\bf z}\in\text{NN}\left({\bf r}\right)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i}\sum_{{\bf r} \neq {\bf r}_i}\hat n_{{\bf r}_i,\sigma}\\
+	=& -\frac{1}{\sqrt\mathcal{Z}}(N-2)t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
+	 &- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+\end{aligned}\end{equation}
+In the first step, the factor of \(\mathcal{Z}\) is cancelled out by the trivial sum over \({\bf r}_0\) in the first and third terms.
+At the last step, the three terms simplified for the following reasons.
+The inequality \(\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}\) in the first term ensures that each nearest-neighbour pair appears in \(N-2\) instances of the auxiliary model, \(N\) being the total number of lattice sites; the two instances that do not contribute are the ones in which the impurity site itself is at \({\bf r}_i\) or \({\bf r}_j\).
+For the second term, the double sum \(\sum_{\bf r}\sum_{{\bf z} \in \text{NN}({\bf r})}\) evaluates to \(\mathcal{Z}\sum_{\bf r}\), because each point on the lattice appears \(\mathcal{W}\) times in the summation.
+This factor of \(\mathcal{W}\) cancels the one in the denominator.
+In the third term, the inner summation simply evaluates to \(N-1\), and we finally replace the dummy index \({\bf r}_i\) with \({\bf r}\).
+
+The next part is
+\begin{equation}\begin{aligned}
+	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp}T({\bf r} - {\bf r}_d) \\
+	=& -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}~.
+\end{aligned}\end{equation}
+This is obtained simply by replacing the impurity position \({\bf r}_d\) with the translated position \({\bf r}\), generating a translation-invariant Hubbard term (the first term) and a finite chemical potential (second term).
+
+We now consider the final term:
+\begin{equation}\begin{aligned}
+	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp-cbath}T({\bf r} - {\bf r}_d)\\
+	&=\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
+				     &-  \left. \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma} V \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]T({\bf r} - {\bf r}_d)\\
+	&=\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r})}\left[\frac{1}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
+				     &-  \frac{1}{\sqrt\mathcal{Z}}\left.\sum_{\sigma} V\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]\\
+					 &=\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]\\
+\end{aligned}\end{equation}
+At the last step, each nearest-neighbour pair of sites \({\bf r}_i, {\bf r}_j\) appear 2 times in the summation, because any site is a member of two distinct nearest-neighbour pairs.
+We have also defined \({\bf S}_{{\bf r}_j} =\sum_{\sigma,\sigma^\prime} {\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime}\) as the local spin operator.
+
+The total tiled Hamiltonian is therefore
+\begin{equation}\begin{aligned}
+	&\mathcal{H}_\text{tiled} \\
+	&= -\frac{N-2}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>,\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+	&- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}\\
+	& + \sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]
+\end{aligned}\end{equation}
+While constructing the tiled Hamiltonian, we have added extra copies of the non-interacting Hamiltonian \(\mathcal{H}_\text{cbath-nint} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\) for the conduction bath (this results in the factors of \(N-2\) and \(N-1\) in front of the first and third terms).
+Upon removing these repeated terms, the tiled Hamiltonian becomes
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}\\
+							 &= -\frac{1}{\sqrt\mathcal{Z}}(t + 2V)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
+							 &- \frac{1}{2}\left(U + U_b\right)\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \left(\eta + 2\mu\right) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} \\
+							 &+ \frac{2}{\mathcal{Z}}J\sum_{\left< {\bf r}_i, {\bf r}_j\right>} {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j}
+\end{aligned}\end{equation}
+
+The result of the tiling operations is a Hubbard-Heisenberg model, of the form
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{HH} &= -\frac{1}{\sqrt\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+						  &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
+\end{aligned}\end{equation}
+where the tilde symbol indicates that the parameters are for the lattice model (and not the auxiliary model).
+By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to each other:
+\begin{equation}\begin{aligned}\label{couplingsMappings}
+	\tilde t = t+2V,~~ \tilde U = U + U_b, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
+\end{aligned}\end{equation}
+In summary, the appropriate method for reconstructing the lattice model Hamiltonian is therefore
+\begin{equation}\begin{aligned}\label{tilingPrescriptionFinal}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}~,
+\end{aligned}\end{equation}
+where we replaced \(N-3\) with \(N\) assuming a large number of sites. Using this, the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.
+
+\subsection{Translation symmetry and a conserved total momentum}
+From the form in eq.~\ref{tilingPrescriptionFinal}, the tiled Hamiltonian is symmetric under global many-body translations of the kind defined in eq.~\ref{translationDefinition}, by arbitrary lattice spacings:
+\begin{equation}\begin{aligned}\label{translationSymmetry}
+	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})T({\bf a}) = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r + a}) = \sum_{{\bf r}^\prime}\mathcal{H}_\text{aux}({\bf r}^\prime)\\
+	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{cbath-nint}T({\bf a}) = \mathcal{H}_\text{cbath-nint}\\
+	&\implies T({\bf a})^\dagger\mathcal{H}_\text{tiled}T({\bf a}) = \mathcal{H}_\text{tiled}~.
+\end{aligned}\end{equation}
+In the first equation, we used the fact that the translation operator simply translates the auxiliary model at the position \({\bf r}\) into another one at the position \({\bf r} + {\bf a}\).
+Since both are part of the summation, the summation remains unchanged.
+The second equation uses the fact that the Hamiltonian \(\mathcal{H}_\text{cbath-nint}\) is that of a tight-binding model and is therefore translation-invariant.
+The fact that the Hamiltonian \(\mathcal{H}_\text{tiled}\) commutes with the many-body translation operator implies that the total crystal momentum \(\vec k\) is a conserved quantity.
+
+\section{Form of the eigenstates: Bloch's theorem}
+In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\bf k}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_i}\), where \({\bf r}_i\) sums over the positions of the local Hamiltonians.
+Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation by an arbitrary number of lattice spacings \({n\bf a}\):
+\begin{equation}\begin{aligned}
+	T^\dagger(n{\bf a})\ket{\Psi_{{\bf k}}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_{i + n}} = e^{-in{\bf k}\cdot{\bf a}}\ket{\Psi_{\bf k}}
+\end{aligned}\end{equation}
+The definition and some properties of these global translation operations were provided in Appendix~\ref{BlochProperties}.
+It was shown there that they share eigenstates with the total momentum operator.
+In a lattice model, this continuous symmetry gets lowered to its discrete form: the total {\it crystal} momentum is conserved by any scattering process.
+As a result, the eigenstates can be labelled using the combined index \(s = \left({\bf k}, n\right) \) where \({\bf k}\) is the total crystal momentum and \(n\) is a band index \(n\).
+
+The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using eq.~\ref{tilingPrescriptionFinal} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}).
+This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) defined in eq.~\ref{unitCellHamiltonian} can be used to construct eigenstates of the lattice Hamiltonian.
+The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
+
+The state \(\ket{\psi_n\left({\bf r}_d\right)}\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself has been averaged over \(\mathcal{Z}\) zeroth sites.
+Accordingly, we can express the averaged eigenstate \(\ket{\psi_n\left({\bf r}_d\right)}\) as
+\begin{equation}\begin{aligned}
+	\ket{\psi_n\left({\bf r}_d\right)} = \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z} \in \text{NN}({\bf r}_d)}\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}~,
+\end{aligned}\end{equation}
+where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\).
+With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:
+\begin{equation}\begin{aligned}\label{eigenstateProposal}
+	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d, {\bf z}\right)}~,
+\end{aligned}\end{equation}
+where \(N\) is the total number of lattice sites and \({\bf r}_d\) is summed over all lattice spacings.
+The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands.
+The ground state \(s = s_0\) is obtained by setting \({\bf k}\) and \(n\) to 0:
+\begin{equation}\begin{aligned}\label{groundstateProposal}
+	\ket{\Psi_\text{gs}} \equiv \ket{\Psi_{s_0}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d, {\bf z}\right)}
+\end{aligned}\end{equation}
+
+\section{One-Particle Greens Functions}
+\subsection{Momentum-space}
+In the previous part, we proposed a form for the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{gs}}\) of the auxiliary models.
+In this section, we will relate one-particle Greens functions of the bulk lattice to those of the auxiliary model.
+We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
+We define the retarded time-domain lattice \(k-\)space Greens function at zero temperature as
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c_{{\bf K}\sigma}(t), c^\dagger_{{\bf K}\sigma} \right\} | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(t\): 
+\begin{equation}\begin{aligned}\label{heisenberg}
+	c_{{\bf K}\sigma}(t) = e^{it H_\text{tiled} }c_{{\bf K}\sigma}e^{-i t H_\text{tiled}}~.
+\end{aligned}\end{equation}
+We now proceed to simplify one of the terms of the anticommutator (for simplicity of notation):
+\begin{equation}\begin{aligned}\label{greensFunction1}
+	&\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_{\vec r,\vec \Delta}e^{-i{\bf K}_0\cdot\vec\Delta}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+To make further progress, we insert the identity resolution \(1 = \sum_s\ket{\Psi_s}\bra{\Psi_s}\) in between the two operators, where \(s=\left({\bf k}, n\right)\) sums over all eigenstates (with energies \(\tilde E_s\)).
+The lattice eigenstates themselves can again be written in terms of those of the auxiliary model, using eq.~\ref{eigenstateProposal}:
+\begin{equation}\begin{aligned}
+	\ket{\Psi_s}\bra{\Psi_s} = \sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\vec k\cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}~.
+\end{aligned}\end{equation}
+With this, eq.~\ref{greensFunction1} becomes
+	\begin{equation}\begin{aligned}\label{greensfunction2}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\vec k_0\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+In order to bring this expression closer to the form of an auxiliary model Greens function, we would like to transform the initial and final states \(\ket{\psi(\vec r)}\) and \(\ket{\psi(\vec r + \vec \Delta)}\) to apply to the same auxiliary model.
+This is done by using the relation: \(\ket{\psi(\vec r + \Delta)} = T^\dagger(\vec \Delta)\ket{\psi(\vec r)}\), where \(T^\dagger(\vec \Delta)\) translates all lattice sites by the vector \(\vec\Delta\).
+\begin{equation}\begin{aligned}
+	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) T^\dagger(\vec \Delta) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
+\end{aligned}\end{equation}
+The effect of the translation operators on the \(k-\)space annihilation operator can be easily ascertained by transforming it to real-space, using the Fourier transform definition
+\begin{equation}\begin{aligned}\label{fourTransf}
+	c({\bf K}) = \frac{1}{\sqrt N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r})~.
+\end{aligned}\end{equation}
+Upon applying this, we get
+\begin{equation}\begin{aligned}\label{translationOnField}
+	T\left(\vec a\right) c({\bf K}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}T\left(\vec a\right) c({\bf r}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r} - \vec a) = e^{-i{\bf K}\cdot\vec a}c({\bf K})~.
+\end{aligned}\end{equation}
+Using this identity on the above expression gives
+\begin{equation}\begin{aligned}
+	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = e^{-i{\bf K} \cdot \vec \Delta}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
+\end{aligned}\end{equation}
+Finally replacing this all the way back into eq.~\ref{greensfunction2} gives
+	\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K}\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime - \vec\Delta)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+To further unify the operators, we make the substitution \(\vec \Delta^\prime \to \vec \Delta^\prime + \vec \Delta\), leading to the expression
+	\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K} - \vec k\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+The sum over \(\vec\Delta\) can now be carried out, resulting in
+\begin{equation}\begin{aligned}\label{greensfunction3}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~,
+\end{aligned}\end{equation}
+where the sum over \(s=(\vec k, n)\) has been reduced to a sum over the auxiliary model eigenstate index \(n\) because of the Kronecker delta \(\delta\left(\vec k_0 + {\bf K} - \vec k\right)\).
+This can be further simplified by splitting the sum over \(\vec\Delta^\prime\) into positive and negative parts and then making the transformation \(\vec r^\prime \to \vec r^\prime + \vec \Delta^\prime\):
+\begin{equation}\begin{aligned}
+	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime-\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}\right] \\
+																																												   &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\right] \\
+\end{aligned}\end{equation}
+For each pair of \(\vec r^\prime\) and \(\vec\Delta^\prime\), the term within the box brackets has the form of a two-level Hamiltonian between the states \(\ket{\psi_n(\vec r^\prime)}\) and \(\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\), with a tunnelling amplitude \(e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\).
+The term can therefore be written in the eigenbasis of this Hamiltonian:
+\begin{equation}\begin{aligned}
+	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &=\frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right],
+\end{aligned}\end{equation}
+where \(\ket{\chi_n^\pm(\vec r^\prime,\vec\Delta^\prime)} = \frac{1}{\sqrt 2}\left[\ket{\psi_n(\vec r^\prime)} \pm e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime + \vec\Delta^\prime)}\right] \) are the eigenvectors of the tunnelling Hamiltonian with eigenvalues \(\pm 1\) respectively.
+With this basis transformation, we can rewrite eq.~\ref{greensfunction3} as
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+
+In order to make the expression more transparent, we consider the various components separately:
+\paragraph{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}:
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+These terms represent those contributions to the total Greens function that arise from excitations that start and end at a specific auxiliary model (at \(\vec r\)), and also evolve dynamically within the same auxiliary model.
+These terms are therefore exactly equal to the auxiliary model Greens function at position \(\vec r\), and are the most dominant contribution due to the localised nature of the impurity model.
+
+\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}:
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime \neq \vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+These are more non-local contributions; they involve excitations whose time evolution is governed by a different auxiliary model than the terminal one.
+These contributions are highly suppressed in the Kondo screened phase because of the strong entanglement of the singlet ground state.
+
+\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime \neq 0\)}:
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime \neq \vec r,\vec \Delta^\prime \neq 0} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+These are the most non-local contributions; they involve excitations whose time evolution is governed by three different auxiliary models. Accordingly, these contributions are further suppressed.
+
+We now consider each type of contribution in more detail.
+\subsection{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}
+Restricting ourselves to just the single auxiliary model contributions gives
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+We first consider more carefully the transition operator \(\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\) for the 1-particle excitation giving rise to the above Greens function.
+Within our auxiliary model approach, gapless excitations within the lattice model are represented by gapless excitations of the impurity site, specifically those that screen the impurity site and form the local Fermi liquid.
+As a result, the uncoordinated \(\mathcal{T}-\)matrix for the lattice model must be replaced by a combined \(\mathcal{T}-\)matrix within the impurity model that captures those gapless excitations that occur in connection with the impurity, and projects out the uncorrelated excitations that take place even when the impurity site is decoupled from the bath.
+
+In order to construct this auxiliary model \(\mathcal{T}-\)matrix, we note that the impurity site can have both spin and charge excitations.
+Considering both excitations, the modified \(\mathcal{T}-\)matrix that constructs \(k-\)space excitations in correlation with the impurity site are
+\begin{equation}\begin{aligned}\label{tmatrix}
+	\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\left(\sum_{\sigma^\prime}c^\dagger_{d\sigma} + \text{h.c.}\right) + c_{{\bf K}\sigma}\left(S_d^+ + \text{h.c.}\right)~,
+\end{aligned}\end{equation}
+leading to the updated expression for the complete Greens function:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+
+In order to convert this into a more useful form, we use eq.~\ref{heisenberg}:
+\begin{equation}\begin{aligned}
+		\braket{\psi_{0}(\vec r) | \mathcal{T}_{{\bf K}\sigma}(t) | \psi_n(\vec r)} = \braket{\psi_{0}(\vec r) | e^{it H_\text{tiled} }\mathcal{T}_{{\bf K}\sigma}e^{-i t H_\text{tiled}} | \psi_n(\vec r)}~.
+\end{aligned}\end{equation}
+Guided by the relation in eq.~\ref{tilingPrescriptionFinal} \(H_\text{tiled} = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}\) between the tiled Hamiltonian and the auxiliary model, we assume that the operator \(e^{-i t H_\text{tiled}}\) acting on the state \(\ket{\psi_n(\vec r)}\) involves the excitation energy \(E_n\) of only a single auxiliary model.
+Specifically, \(E_n\) is the energy of the eigenstate \(\ket{\psi_n(\vec r)}\).
+This is supported by the fact that this class of contributions to the Greens function is completed within a single auxiliary model.
+Accordingly, we replace \(H_\text{tiled}\) with \(E_n - \varepsilon_{\bf k} \), where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\) and \({\bf k}\) is the crystal momentum associated with the state \(\ket{\psi_n(\vec r)}\).
+This momentum was found to be constrained to \({\bf k}_0 + {\bf K}\) below eq.~\ref{greensfunction3}.
+In the same way, the action of \(H_\text{tiled}\) on the terminal state \(\ket{\psi_{0}(\vec r)}\) gives \(E_0 - \varepsilon_{\bf k_0}\), where \(E_0\) is the ground state energy of the auxiliary model at \({\bf r}\).
+Applying this to our expression gives
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[e^{-it\omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + e^{-it\omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~,
+\end{aligned}\end{equation}
+where \(\omega_p = (E_n - \varepsilon_{\bf k_0 + \bf K}) - (E_0 - \varepsilon_{\bf k_0})\) is the particle-excitation cost and \(\omega_h = -\omega_p\) is the hole-excitation cost.
+We now introduce the Fourier transform \(g(\omega) = \int~dt~ e^{i\omega T}f(t)\) to obtain the frequency-domain Greens function in its spectral representation:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; \omega) = \frac{1}{N}\sum_{\vec r}\sum_n \braket{\psi_{0}(\vec r) | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+For each value of \({\vec r}\), the term within that summation is simply the Greens function (for the excitation \(\mathcal{T}_{{\bf K}\sigma}\)) of the auxiliary model with the impurity site at \({\vec r}\).
+Since all these impurity models are physically equivalent (because of translation invariance), we can replace the average over \({\bf r}\) with the value obtained from any one auxiliary model.
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; \omega) = \sum_n \braket{\psi_{0} | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}} ~.
+\end{aligned}\end{equation}
+
+\subsection{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}
+Allowing for more non-local contributions, and updating the \(\mathcal{T}-\)matrix similar to the previous section gives the following Greens function:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+In order to allow computations within a single auxiliary model, we replace the translated state \(\ket{\psi_n(\vec r^\prime)}\) with \(T^\dagger(\vec r \to \vec r^\prime)\ket{\psi_n(\vec r)} \), where \(T^\dagger(\vec r - \vec r^\prime)\) translates all sites by the vector \(\vec r^\prime - \vec r\).
+This leads to a modified correlation function but within a single auxiliary model:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_{n,\vec r, \vec r^\prime} \bra{\psi_{0}(\vec r)} &\left[\mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.
+\\
+								&\left.
+\mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+In fact, by the same arguments as in the previous section, we can obtain a frequency-resolved Greens function:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; \omega) = \sum_n \bra{\psi_{0}} &\left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.\\
+															&\left.
+\frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}} ~.
+\end{aligned}\end{equation}
+To obtain the above, we used the fact that \(H_\text{tiled}\) commutes with the translation operator.
+
+%TODO
+%By expanding in terms of the small parameter $\frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}}$, this expression for $\Sigma_{H-H}(\vec k,\omega)$ can be recast in the following form:
+%\begin{equation}\begin{aligned}
+%	\Sigma_{H-H}(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~\label{selfenergy2}
+%\end{aligned}\end{equation}
+%where $\Sigma_\text{loc}$ and $\Sigma_\text{near-n}$ correspond to the local and nearest-neighbour self-energies defined on the real-space lattice 
+%\begin{eqnarray}
+%\Sigma_\text{loc}(\omega) &=& \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^{(0)}} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}}~,\\ 
+%\tilde{\Sigma}(\vec k, \omega)&=&\xi_{\vec k}\Sigma_\text{near-n}~,~\Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}^2}~.
+%\end{eqnarray}
+%We note that the form of $\Sigma(\vec k, \omega)$ obtained by us is similar to the form proposed on phenomenological grounds in the generalised DMFT + $\Sigma$ approach~\cite{sadovskii2012}.
+
+\section{Equal-Time Ground State Correlators}\label{staticCorr}
+Properties of the ground state can be probed using static correlation functions that are expectation values of operators that propagate excitations.
+We will consider general correlations, in real and momentum space.
+\subsection{Real-space correlation functions}
+We first consider a real-space operator \(\mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r})\) that quantifies the presence of correlations over a distance \({\bf \Delta}\).
+The correlation function itself is given by the expectation value of this operator in the ground state:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_1 + {\bf r}^\prime + {\bf r}_c + {\bf r}\right)  | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_1 + {\bf r}_c + {\bf r}\right)} e^{-i{\bf k}_0\cdot\left({\bf r}_1 - {\bf r}_2\right)}~,
+\end{aligned}\end{equation}
+where \({\bf r}_1\) and \({\bf r}_1 + {\bf r}^\prime\) are the positions of the incoming and outgoing auxiliary model states, relative to \({\bf r}_c + {\bf r}\), and \({\bf k}_0\) is the crystal momentum of the ground state (which we will immediately set to zero).
+In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
+Substituting this appropriately for both the auxiliary model states gives:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_1 + {\bf r}^\prime + {\bf r}\right) \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) T^\dagger\left({\bf r}_1 + {\bf r}\right) | \psi_\text{gs}\left({\bf r}_c\right)}\\
+								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}^\prime\right) \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
+								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+As a final cosmetic change, we transform \({\bf r}_1 \to -{\bf r}\):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r},{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+Like in the Greens function calculation, we now consider the various kinds of contributions separately.
+
+\subsubsection{Intra-auxiliary model contributions: \({\bf r}^\prime = 0\)}
+These terms describe excitations that start and propagate within the same auxiliary model, upto a distance \({\bf \Delta}\):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+With an eye towards introducing the impurity operators into the correlations, we insert a complete basis defined by the eigenstates \(\left\{\ket{\psi_n\left({\bf r}_c\right)}\right\} \) of the auxiliary model into the expression:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\sum_{n}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \ket{\psi_n\left({\bf r}_c\right)}\bra{\psi_n\left({\bf r}_c\right)} \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+
+For the excitations that exist purely in the conduction bath \(({\bf r} \neq {\bf r}_c)\), the excitation operators must be suitably modified (see the arguments around eq.~\ref{tmatrix}) in order to incorporate Kondo screening.
+The modified excitation operators are generally defined as
+\begin{equation}\begin{aligned}\label{operatorTmatrix}
+	\mathcal{\tilde O}({\bf r}) = \mathcal{O}({\bf r})\mathcal{O}^\dagger(d) \mathcal{P}_\text{gs} ~,
+\end{aligned}\end{equation}
+where \(\mathcal{O}^\dagger(d)\) is the hermitian conjugate of the correlation operator \(\mathcal{O}\), but applied on the impurity sites.
+This therefore constitutes a time-reversed scattering process on the impurity site relative to the process in the bath.
+The operator \(\mathcal{P}_\text{gs}\) projects onto the ground state of the auxiliary model, since we are interested in ground state correlations.
+The operator multiplying the old correlation operator represents all possible excitations of the impurity site, and ensure that the bath and impurity excitation processes take place in correlation.
+The projector ensures that only tripartite correlations between the impurity site and the two momentum states are captured by the correlation, which is what's desired within the tiling method.
+
+With this modified operator, this class of correlation functions can be written as
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r} }\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+This can be interpreted as the fact that within our auxiliary model formalism, the correlation between the sites \({\bf r}\) and \({\bf \Delta + r}\) can only occur through a transition process that connect one of the sites with the impurity site and then a return process that connects the impurity site with the other site.
+
+\subsubsection{Inter-auxiliary model contributions: \({\bf r}^\prime \neq 0\)}
+These are the most non-local contributions, and involve excitations that connect different auxiliary models:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}^\prime \neq 0}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+
+\subsection{Momentum-space correlation functions}
+We now consider momentum space correlations, through a general operator \(\mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1)\):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+Note that \(\mathcal{O}\) itself is a two-particle operator.
+To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_2\right)  | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_1\right)}~,
+\end{aligned}\end{equation}
+where \({\bf r}_1\) and \({\bf r}_2 \) are the positions of the incoming and outgoing auxiliary model states.
+In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
+Substituting this appropriately for both the auxiliary model states gives:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_c\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) T^\dagger\left({\bf r}_1 - {\bf r}_c\right) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+In order to simplify the translation operators, we can use eq.~\ref{translationOnField}.
+For that, we would need to know whether the operator \(\mathcal{O}\) involves the net transfer of momentum.
+If \(\mathcal{O}({\bf k})\) commutes with the total number operator \(n_{\bf k} = \sum_\sigma n_{{\bf k},\sigma}\), there is no momentum transfer.
+Examples of such operators are spin operators, \(S_{\alpha\beta}({\bf k}) \equiv c^\dagger_{{\bf k \alpha}}c_{{\bf k}\beta}\), and density operators \(n_{{\bf k}\alpha}\).
+If \(\mathcal{O}({\bf k})\) does not commute with \(n_{\bf k}\), there is a net transfer of momentum, and one such operator would be the charge isospin operator \(C^+({\bf k}) = c^\dagger_{{\bf k}\uparrow}c^\dagger_{{\bf k}\downarrow}\).
+For the first kind of operators, we have \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = \mathcal{O}({\bf k})\), while the for the latter, we get \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = e^{-{\bf a}\cdot{\bf 2k}}\mathcal{O}({\bf k})\), where \(2{\bf k}\) represents the momentum being transferred by the operator.
+We consider the two cases separately.
+
+\subsubsection{Momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] = 0\)}
+For these operators, the expression for the correlation gives
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
+										 &=\sum_{{\bf r},{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+To obtain the last form, we defined \({\bf \Delta}={\bf r}_2 - {\bf r}_1\) as the distance between the incoming and outgoing auxiliary model states, and preformed the sum over the free variable \({\bf r}_1\) to cancel out the factor of \(1/N\).
+Just like before, this expression can be decomposed into a term that involves a single auxiliary model and other terms that involve two distinct auxiliary models.
+
+\subsubsection{Non-momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] \neq 0\)}
+This class of operators incur an additional phase factor of \(e^{-{\bf a}\cdot{\bf 2k}}\) when the translation operators are translated across them:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}e^{2i\left( {\bf r}_1 - {\bf r}_c \right) \cdot \left( {\bf k}_1 - {\bf k}_2 \right)} \\
+										 &= \delta_{{\bf k}_1, {\bf k}_2}\sum_{{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+For this expression, we again defined \({\bf \Delta}\) similar to before, and carried out the sum of \({\bf r}_1\) involving the exponential to obtain a factor of \(N \delta_{{\bf k}_1, {\bf k}_2}\).
+The Kronecker delta factor is a manifestation of translational invariance and the associated total momentum conservation.
+
+As it stands, operators like \(\mathcal{O}({\bf k}_1)\) act purely on the conduction bath degrees of freedom.
+In order to incorporate impurity-bath correlation effects, we modify these operators using the appropriate \(T-\)matrices, by employing eq.~\ref{operatorTmatrix}.
+The final computations are carried out using these modified operators.
+
+\section{Entanglement}
+We will now describe the prescription of calculating entanglement measures of the lattice model from within our auxiliary model treatment.
+In this section, we are interested mainly in two such measures, the entanglement entropy and the mutual information.
+Given a pure state \(\ket{\Psi}\) describing the complete system, the entanglement entropy \(S_\text{EE}(\nu)\) of a subsystem \(\nu\) quantifies the entanglement of \(\nu\) with the rest of the subsystem, and is defined as
+\begin{equation}\begin{aligned}
+	S_\text{EE}(\nu) = -\text{Tr}\left[\rho(\nu)\log \rho(\nu)\right],\quad \rho(\nu) = \text{Tr}_\nu\left[\ket{\Psi}\bra{\Psi}\right] 
+\end{aligned}\end{equation}
+where \(\text{Tr}\left[\cdot\right] \) is the trace operator, and \(\rho(\nu)\) is the reduced density matrix for the subsystem \(\nu\) obtained by taking the partial trace \(\text{Tr}_\nu\) (over the states of \(\nu\)) of the full density matrix \(\rho = \ket{\Psi}\bra{\Psi}\).
+If the subsystem \(\nu\) describes local regions in real space (or states in \(k-\)space), we might be interested in the entanglement between two such subsystems \(\nu_1\) and \(\nu_2\).
+The correct measure to quantify such entanglement is the mutual information:
+\begin{equation}\begin{aligned}
+	I_2(\nu_1,\nu_2) = S_\text{EE}(\nu_1) + S_\text{EE}(\nu_2) - S_\text{EE}(\nu_1 \cup \nu_2)~,
+\end{aligned}\end{equation}
+where \(\nu_1 \cup \nu_2\) is a larger subsystem formed by combining \(\nu_1\) and \(\nu_2\).
+
+\subsection{Real-space entanglement}
+Real-space entanglement measures can be used to probe delocalisation-localisation transitions.
+The simplest such measure is the entanglement of a local mode.
+Since the local entanglement entropy will be uniform at each lattice site for a system with translation invariance, it suffices to calculate the real-space averaged entanglement entropy \(S_\text{EE}^\text{loc} = \frac{1}{N}\sum_{{\bf r}}S_\text{EE}\left( {\bf r} \right) \).
+By visualising the lattice model as a superposition of auxiliary models placed at various sites (eq.~\ref{tilingPrescriptionFinal}), the real space average of the lattice model can be thought of as an average over sites of a particular impurity model, and then a second average over all the impurity models.
+But since all all impurity models are equivalent to each other, the second average is redundant.
+Secondly, all correlations must derive from the impurity site, which can be formally encoded by subtracting, from this average, the corresponding contribution obtained in the absence of the impurity site.
+In total, the lattice-auxiliary model relation for the local entanglement entropy can be written as
+\begin{equation}\begin{aligned}
+	S_\text{EE}^\text{loc} = \frac{1}{N}\sum_{{\bf r}}\left[S_\text{EE}({\bf r}_d + {\bf r}) - S_\text{EE}^{(0)}({\bf r}_d + {\bf r})\right] ~,
+\end{aligned}\end{equation}
+where \({\bf r}_d\) is the impurity site position, \({\bf r}\) is the distance of a conduction bath site from the impurity site (can be zero), and \(S_\text{EE}({\bf r}_d + {\bf r})\) is the entanglement entropy, calculated within the impurity model, at the locatiom \({\bf r}_d + {\bf r}\).
+\(S^{(0)}_\text{EE}({\bf r}_d + {\bf r})\) is the same entanglement entropy, but calculated for an impurity model but with vanishing impurity-bath hybridisation and bath interaction.
+
+\subsection{Momentum-space entanglement}
+Entanglement measures in \(k-\)space can provide valuable information regarding the Fermi surface structure and the nature of gapless excitations proximate to it.
+The most elementary measure is the entanglement entropy \(S_\text{EE}({\bf q})\) of a single excitation carrying momentum \({\bf q}\).
+Unlike \(S_\text{EE}^\text{loc}\), this does not involve an average, and involves a single computation:
+\begin{equation}\begin{aligned}
+	S_\text{EE}^\text{loc} = S_\text{EE}({\bf q}) - S_\text{EE}^{(0)}({\bf q})~.
+\end{aligned}\end{equation}
+It is possible to improve this by considering inter-auxiliary model contributions in the reduced density matrix \(\rho({\bf q})\). On the lattice model, \(\rho({\bf q})\) is defined as
+\begin{equation}\begin{aligned}\label{SEE-k}
+	\rho({\bf q}) = \text{Tr}_{\bf q}\left[\ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\right] ~,
+\end{aligned}\end{equation}
+where \(\text{Tr}_{\bf q}\left[\cdot\right]\) is the partial trace over the Hilbert space of \({\bf q}\), and \(\ket{\Psi_\text{gs}}\) is the tiled ground state.
+Using eq.~\ref{groundstateProposal}, we can write the ground state in terms of those of the auxiliary model.
+These leads to two classes of terms, one purely within a single auxiliary model ground state \(\ket{\psi_\text{gs}}\), and the other involving transitions across auxiliary models:
+\begin{equation}\begin{aligned}
+	\rho({\bf q}) = \text{Tr}_{\bf q}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d)}\right] + \frac{1}{N}\text{Tr}_{\bf q}\sum_{{\bf r}}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d + {\bf r})}\right]~,
+\end{aligned}\end{equation}
+where \(\ket{\psi_\text{gs}({\bf r}_d)}\) is a reference auxiliary model ground state, and \(\ket{\psi_\text{gs}({\bf r}_d + {\bf r})}\) sums over other auxiliary models at increasing distances from this reference model.
+The first term leads to the expression in eq.~\ref{SEE-k}, while the second term can be used to improve this estimate.
+Away from any quantum critical points, the localised nature of the impurity-bath hybridisation ensures that impurity correlations decay exponentially away from the transition.
+This ensures that the second term is very small away from a critical point.
+We therefore restrict ourselves to just the first term in the present work.
 
@@
 \begin{figure}[htpb]
-	\includegraphics[width=0.24\textwidth]{S_k-1.pdf}
-	\includegraphics[width=0.24\textwidth]{S_k-3.pdf}
-	\includegraphics[width=0.24\textwidth]{S_k-4.pdf}
-	\includegraphics[width=0.24\textwidth]{S_k-5.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_SEE_k-1.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_SEE_k-2.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_SEE_k-3.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_SEE_k-4.pdf}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.24\textwidth]{I2_k_N-1.pdf}
-	\includegraphics[width=0.24\textwidth]{I2_k_N-3.pdf}
-	\includegraphics[width=0.24\textwidth]{I2_k_N-4.pdf}
-	\includegraphics[width=0.24\textwidth]{I2_k_N-5.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_I2_k_N-1.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_I2_k_N-2.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_I2_k_N-3.pdf}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.24\textwidth]{I2_k_edge-1.pdf}
-	\includegraphics[width=0.24\textwidth]{I2_k_edge-3.pdf}
-	\includegraphics[width=0.24\textwidth]{I2_k_edge-4.pdf}
-	\includegraphics[width=0.24\textwidth]{I2_k_edge-5.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_I2_k_edge-1.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_I2_k_edge-2.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_I2_k_edge-3.pdf}
 \end{figure}
@@
 where the effective antiferromagnetic Heisenberg coupling is \(J_\text{eff} = \frac{8V_H^2}{U}\).
-
-\clearpage
-
-\section{The Mott MIT: a local perspective}
-\subsection{Gapping of the local spectral function and vanishing of correlations}
-% At a critical value \(U_b = -J/4\) of the local correlation \(U_b\) on the bath zeroth site, the couplings \(J\) and \(V\) of the auxiliary model become irrelevant while \(U\) becomes remains non-zero, leading to a low-energy phase where the impurity is cut off from the conduction bath.
-This is the local moment phase, where low-energy excitations have been gapped out.
-% \begin{figure}[htpb]
-% 	\centering
-% 	\includegraphics[width=0.48\textwidth]{phase-map-MIT.pdf}
-% 	\includegraphics[width=0.48\textwidth]{spectral-function_dd.pdf}
-% 	\caption{{\it Left:} Phase diagram of the extended SIAM auxiliary model.
-As the parameter \(r\) is tuned through 0.25, the metallic blue phase changes into the insulating violet phase.
-{\it Right:} Local spectral function of the auxiliary model.
-It shows a hard gap for \(r/r_c > 1\).}
-% 	\label{spec_func_mit}
-% \end{figure}
-%
-% The impurity local spectral function \(\mathcal{A}_{dd}(\omega)\) and the impurity-bath real space off-diagonal spectral function \(\mathcal{A}_{dz}(\omega)\) reveal a gap in the spectrum at low \(\omega\) for \(U_b > J/4\).
-We show the former in fig.~\ref{spec_func_mit}.
-The gap in the former shows the absence of any gapless excitations that can allow the impurity configuration to fluctuate, while the vanishing of the off-diagonal spectral function shows that this is because the entanglement between the impurity and the bath has been quenched.
-%
-% In Fig.~\ref{spin-charge-correlations}, we show the behaviour of the spin-flip and charge isospin-flip correlations between two neighbouring real space sites, as well as the mutual real space entanglement and mutual information.
-Both show a sharp fall on crossing the transition, demonstrating the destruction of the Kondo cloud and the stabilisation of the local moment on the impurity.
-Importantly, they charge correlations show a rise very close to the transition (can be seen as a single elevated blue point near \(r = 0.25\) in the left panel of Fig.~\ref{spin-charge-correlations}); this indicates that the transition is precipitated by the growth of pairing correlations.
-%
-% \begin{figure}[!htb]
-% \centering
-% 	\includegraphics[width=0.48\textwidth]{spin-charge-corr-full.pdf}
-% 	\includegraphics[width=0.48\textwidth]{impEE-mutinfo-d0.pdf}
-% 	\caption{{\it Left}: Spin-flip correlations(red) and charge-flip correlations(blue) in real space.
-The former increases as the system moves into the Kondo regime, and then vanishes at the transition.
-The latter decreases as the charge content is removed from the ground state in the Kondo regime, but shows a sudden increase at the transition.
-{\it Right}: Real space Entanglement and mutual information.
-Both vanish in the local moment phase.}
-% 	\label{spin-charge-correlations}
-% \end{figure}
-
-\subsection{Value of the critical paramter for the bulk model}
-Using the mappings between the auxiliary model parameters and the bulk parameters (eq.~\ref{couplingsMappings}), one can define a critical value \(r^{*}\) of the ratio \(r = U_{H-H}/J_{H-H}\) at the critical points \(-U_b/J=1/4\) \textit{for a given and fixed value of \(U\)}.
-We will now argue that this critical point describes a metal-insulator transition.
-For \(r < r^{*}\), the well-defined low-\(\omega\) central peak in the impurity spectral function, as well as the large mutual and information correlations, in the ground state, among the members of the Kondo cloud or between the impurity and the zeroth site show that the impurity and the bath are very strongly entangled.
-This means that both the local and the nearest-neighbour Greens functions have poles at low\(-\omega\) and support the propagation of electrons through gapless excitations.
-Since the spectral function is also very simply related to that of the auxiliary model, the former also shows the same zero-energy resonance.
-
-On the other side \(r > r^{*}\) of the critical point, we know that the impurity gets decoupled from the bath, leading to the transformation of poles into zeros in the Greens functions.
-This is demonstrated through the gapping of the impurity spectral function in fig.~\ref{spec_func_mit}, and it describes an insulating phase where the electrons get "jammed" in the local states.
-By the same argument as above, the bulk spectral function also sees a gap in this phase when the impurity spectral function is gapped.
-
-Finally, using relations \eqref{couplingsMappings} between the auxiliary model couplings and the bulk parameters, we can offer a functional form for the critical value of the parameter $r^{*} = U_{H-H}^{*}/J_{H-H}^{*}$.
-Using \(U_{H-H}^{*} = U^* + U_b\) and \(J_{H-H}^{*} = 2J^*\) (following \eqref{couplingsMappings}), we get
-\begin{equation}\begin{aligned}
-	r^{*} &=& \frac{1}{2}\left(\frac{U^{*}}{J^{*}} + \frac{U_b}{J^*}\right)
-\end{aligned}\end{equation}
-where $U^{*}$ and $J^{*}$ are the values of the on-site and Kondo couplings of the auxiliary model at the auxiliary model (i.e., the extended SIAM with a correlated bath) at the transition between the Kondo screened and the local moment phases.
-By using the auxiliary model criticality condition \(-4U_b = J^*\), the bulk criticality parameter \(r^*\) takes the form
-\begin{equation}\begin{aligned}
-	r^{*} &=& \frac{1}{2}\left(\frac{U^{*}}{J^{*}} - \frac{1}{4}\right)
-\end{aligned}\end{equation}
-Parametrising the bath correlation coupling as $U_{b}=-\frac{U}{10}$, we obtain $U^{*}/J^{*}=5/2$, and $r^{*} = 9/8$ for the 2D square lattice Hubbard-Heisenberg model.
-The reduction in the value of \(r\) from \(2.5\) in the auxiliary model to \(~1.1\) in the bulk model can be attributed to (i) the reduction in the effective bulk repulsion \(U\) due to the competition coming from the attractive \(U_b\), and (ii) increased hybdridisation through \(J\) due to the presence of multiple auxiliary models that connect two lattice sites.
-
-\section{Emergence of effectively pseudogapped Anderson model at the MIT}
-%\begin{itemize}
-%\item 
-We begin by recalling that the RG equation (in the weak coupling limit) of the \(J-U_b\) model that emerges in the Kondo limit of the eSIAM is similar to that of the pseudogapped Anderson model~\cite{fritzvojta2004} that has a bath density of states of the form \(\rho\sim |\omega|^\alpha\).
-If we define the dimensionless Kondo coupling \(g = \rho J\) and the dimensionless bath coupling \(u = \rho U_b\), the RG equation for \(g\),
-\begin{equation}\begin{aligned}
-	\Delta g \simeq g^2 + 4gu~,
-\end{aligned}\end{equation}
-can be mapped to the corresponding RG equation for the pseudogapped Kondo model,
-\begin{equation}\begin{aligned}
-	\Delta g = g^2 - \alpha g~,
-\end{aligned}\end{equation}
-with the identification \(\alpha = -4u = -4\rho U_b\).
-Specifically, this corresponds to a Kondo model that is coupled to a conduction bath with a single-particle density of states that is vanishing (pseudogapped): $\rho\sim |\omega|^{\alpha}$~.
-\par
-Now, following the work by Si and Kotliar~\cite{kotliarsi_1993}, the impurity self-energy of the \(J-U_b\) model takes the form
-	\begin{equation}\begin{aligned}
-		\Sigma_{dd} \sim |\omega|^{\gamma_{dd}}~,
-	\end{aligned}\end{equation}
-	where the exponent \(\gamma_{dd}\) can be written in terms of the phase shifts (at the RG fixed point) \(\delta^*_\text{sp}\) and \(\delta^*_\text{ch}\) suffered by the conduction electrons due to the potentials \(J\) and \(U_b\) respectively in the Hamiltonian:
-	\begin{equation}\begin{aligned}
-		\gamma_{dd} = \frac{5}{4} - \left[ \frac{1}{\pi}\left( \delta^*_\text{sp} + \delta^*_\text{ch} \right) - \frac{1}{2}  \right]^2 - \left( \frac{\delta^*_\text{ch}}{\pi} \right)^2~.
-	\end{aligned}\end{equation}
-	The phase shifts are given by \(\delta^*_\text{sp}=\arctan\left( \pi g/2 \right) \) and \(\delta^*_\text{ch}=\arctan\left( \pi u/2 \right) \).
-In the small coupling limit, these can be approximated as \(\delta^*_\text{sp}=\pi g/2\) and \(\delta^*_\text{ch}=\pi u/2\).
-\par 
-We now focus on the quantum critical point \(g = -4u\) of our model.
-At this point, the phase shifts get related to each other: \(\delta^*_\text{sp} = -4\delta^*_\text{ch}\), so that the exponent of the self-energy takes the form
-	\begin{equation}\begin{aligned}
-		\gamma_{dd} \simeq 1 - \frac{3}{\pi}\delta^*_\text{ch} = 1 + \frac{3}{8}\alpha
-	\end{aligned}\end{equation}
-	where we have used the fact that for our model, the effective pseudogap parameter \(\alpha\) is set to \(-4u\). The local self-energy then vanishes as
-	\begin{equation}\begin{aligned}
-		\Sigma_{dd} \sim |\omega|^{\gamma_{dd}} = |\omega|^{1 + \frac{3}{8}\alpha}
-	\end{aligned}\end{equation}
-The power-law exponent $\gamma_{dd}=1 + \frac{3}{8}\alpha$ lies in the following range: $1\leq \gamma_{dd} \leq 2$.
-This can be compared with the expression \(\sim|\omega|^{2-3\alpha}\) of the impurity self-energy obtained in ref.~\cite{fritzvojta2004} where the power law exponent ranges between $1/2$ and $2$.
-In a similar manner, the self-energy \(\Sigma_{dz}\) for scattering processes that connect the impurity site and the bath zeroth site can also be obtained.
-The exponent \(\gamma_{dz}\) for this self-energy is given by \(\gamma_{dz} = 2 - 2\gamma_{dd}\), so that this non-local self-energy diverges as
-\begin{equation}\begin{aligned}\label{selfenergydivergence}
-	\Sigma_{dz} \sim |\omega|^{- \frac{3}{4}\alpha}~.
-\end{aligned}\end{equation}
-
-We will now relate the auxiliary model self-energies \(\Sigma_{dd}\) and \(\Sigma_{dz}\) with their bulk (or lattice) model counterparts using the lattice Dyson equation.
-We consider self-energy matrices \(\Sigma\) and \(\Sigma_\text{aux}\) constructed out of real-space self-energies:
-\begin{equation}\begin{aligned}
-	\Sigma(\omega) = \begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} ,\quad \Sigma_\text{aux}(\omega) = \begin{bmatrix} \Sigma_{dd}(\omega) && \Sigma_{dz}(\omega) \\ \Sigma_{dz}(\omega) && \Sigma_{dd}(\omega)\end{bmatrix}~,
-\end{aligned}\end{equation}
-where \(\Sigma_\text{loc}\) is the real-space local self-energy and \(\Sigma_\text{near-n}\) is the self-energy for nearest-neighbour scattering processes. Using Dyson's equation, we can write
-\begin{equation}\begin{aligned}
-	\begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} = \begin{bmatrix} G^{(0)}_\text{loc}(\omega) && G^{(0)}_\text{near-n}(\omega) \\ G^{(0)}_\text{near-n}(\omega) && G^{(0)}_\text{loc}(\omega)\end{bmatrix}^{-1} - \begin{bmatrix} G_\text{loc}(\omega) && G_\text{near-n}(\omega) \\ G_\text{near-n}(\omega) && G_\text{loc}(\omega)\end{bmatrix}^{-1}~,
-\end{aligned}\end{equation}
-and
-\begin{equation}\begin{aligned}
-	\begin{bmatrix} \Sigma_{dd}(\omega) && \Sigma_{dz}(\omega) \\ \Sigma_{dz}(\omega) && \Sigma_{dd}(\omega)\end{bmatrix} = \begin{bmatrix} \mathcal{G}^{(0)}_{dd}(\omega) && \mathcal{G}^{(0)}_{dz}(\omega) \\ \mathcal{G}^{(0)}_{dz}(\omega) && \mathcal{G}^{(0)}_{dd}(\omega)\end{bmatrix}^{-1} - \begin{bmatrix} \mathcal{G}_{dd}(\omega) && \mathcal{G}_{dz}(\omega) \\ \mathcal{G}_{dz}(\omega) && \mathcal{G}_{dd}(\omega)\end{bmatrix}^{-1}~,
-\end{aligned}\end{equation}
-where the superscript \((0)\) indicates that the corresponding quantity has to be calculated from the non-interacting model.
-We now evaluate the second inverse matrix in each of the two equations, and expression the lattice Greens functions in terms of the auxiliary mode Greens functions (using eqs.~\ref{greens_func_relation} and \ref{greens_func_relation_near}).
-We get
-\begin{equation}\begin{aligned}
-	\begin{bmatrix} \Sigma_{dd}(\omega) && \Sigma_{dz}(\omega) \\ \Sigma_{dz}(\omega) && \Sigma_{dd}(\omega)\end{bmatrix} &= 1/\mathcal{G}^{(0)} - \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2}\begin{bmatrix} \mathcal{G}_{dd} && -\mathcal{G}_{dz} \\ -\mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}~,\\
-	\begin{bmatrix} \Sigma_\text{loc}(\omega) && \Sigma_\text{near-n}(\omega) \\ \Sigma_\text{near-n}(\omega) && \Sigma_\text{loc}(\omega)\end{bmatrix} &= 1/G^{(0)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{Z}^2}\begin{bmatrix} \mathcal{G}_{dd} && -\frac{1}{\mathcal{Z}}\mathcal{G}_{dz} \\ -\frac{1}{\mathcal{Z}}\mathcal{G}_{dz} && \mathcal{G}_{dd}\end{bmatrix}~.
-\end{aligned}\end{equation}
-This allows us to write down expressions for the off-diagonal self-energies, in terms of Greens functions, without evaluating the non-singular contribution coming from the non-interacting matrix:
-\begin{equation}\begin{aligned}
-	\Sigma_{dz} = \left(1/\mathcal{G}^{(0)}\right)_{dz} + \frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2} \mathcal{G}_{dz},\quad \Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{1}{\mathcal{G}_{dd}^2 - \mathcal{G}_{dz}^2 / \mathcal{Z}^2} \mathcal{G}_{dz}
-\end{aligned}\end{equation}
-The divergence of \(\Sigma_{dz}\) shown in eq.~\ref{selfenergydivergence} as \(\omega \to 0\) has to arise from the second term in the expression for \(\Sigma_{dz}\) above as it contains the effects of inter-particle correlations.
-%, because the non-interacting Greens function has well-defined poles which kill the first term. 
-Importantly, we note that the second term in the expression for \(\Sigma_\text{near-n}\) is very similar to the diverging term in \(\Sigma_{dz}\), differing only through the presence of some finite (i.e., non-divergent) non-zero factors of \(\lambda_{\vec k_0}^2\) and \(\mathcal{Z}\).
-We therefore conclude that the non-local self-energy of the lattice model $\Sigma_\text{near-n}$ contains the same power-law divergence  as $\Sigma_{dz}$ upon taking the limit $\omega\to 0$:
-\begin{equation}\begin{aligned}
-	\Sigma_\text{near-n}\left( \omega \right) \sim \omega^{-3\alpha/4}~.
-\end{aligned}\end{equation}
-By a similar argument, the local self-energy is found to vanish as \(\omega \to 0\).
-We have seen above that we can approximate the \(k-\)space self-energy in terms of these two real-space self-energies (eq.\eqref{selfenergy1}):
-\begin{equation}\begin{aligned}
-	\Sigma(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~~\textrm{where}~\tilde{\Sigma}(\vec k, \omega)=\xi_{\vec k}\Sigma_\text{near-n}~,
-\end{aligned}\end{equation}
-and $\xi_{\vec{k}}$ is the electronic lattice dispersion (in units of the hopping amplitude $t$).
-It is clear from the expression that the divergent $\Sigma_\text{near-n}$ does not affect the single-particle self-energy $\Sigma(\vec k,\omega)$ at the Fermi surface, i.e., for $\xi_{\vec{k}}= 0$, but $\Sigma(\vec k,\omega)$ diverges everywhere else in the Brillouin zone.
-This corresponds to a gapless non-Fermi liquid metal present at the QCP, corresponding to a system with Landau quasiparticle poles precisely on the Fermi surface but which are destroyed everywhere else.
-
-Now, following the arguments laid out in Ref.\cite{sujan2023}, the single-particle spectral function $A(\omega,\vec{k})$ will vanish (i.e., be pseudogapped) for excitations away from a critical Fermi surface~(see Chapter 8 of Ref.\cite{carr2010})
-\begin{equation}
-A(\vec{k},\omega) \sim |\omega|^{\frac{3}{4}\alpha}~.
-\end{equation}	
-This corresponds to the vanishing of the residue of the Landau quasiparticle precisely at the metal-insulator transition, and the emergence of a gapless non-Fermi liquid ``local quantum critical" metal~\cite{Si2001}.
-Further, the fact that the single-particle self-energy $\Sigma(\vec k, \omega)$ vanishes precisely at the Fermi surface signals the fact that the Luttinger's count for states on the Fermi surface is preserved and identical to that in the Fermi liquid phase.
 
@@
 
-\section{Properties of the Bloch states}
+\section{Properties of the Bloch states}\label{BlochProperties}
 
@@
 \end{aligned}\end{equation}
-
-\section{Analytic consistency check - On the Bethe lattice}
-We now apply our approach to the case of infinite number of nearest-neighbours $\mathcal{Z}\to\infty$ (the coordination number, and effectively the dimension), where the correct scaling of the $t^{H}$ hopping parameter is $t^{H}\to t^{H}/\sqrt{\mathcal{Z}}$~\cite{metzner_volhardt_1989,georges_kotliar_1992,pruschke_cox_jarrel_1993}, such that DMFT obtains a metal-insulator transition in that limit~\cite{georges1996}.
-It is well known from the works of Müller-Hartmann as well as Metzner and Vollhardt that self-energy arising from the correlations loses all momentum-dependence and becomes purely local~\cite{Muller-Hartmann1989,metzner_volhardt_1989}.
-This simplification is what makes DMFT exact in the limit of infinite dimensions.
-This simplification is also explicit in our formalism, as can be seen in the expression of the Self-energy (eq.~\eqref{selfenergy1}).
-Upon taking the limit of \(\mathcal{Z}\to\infty\), the non-local terms drop out:
-\begin{equation}\begin{aligned}
-	\lim_{\mathcal{Z}\to\infty}\Sigma_{H-H}(\vec k,\omega) = \frac{\left(\lambda_{\vec k_0}^{(0)}\right)^2}{\mathcal{G}^{(0)}_{dd}(\omega)} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}(\omega)} = \Sigma_\text{loc}(\omega)~,
-\end{aligned}\end{equation}
-making the self-energy completely local.
 

### 2025-04-04 TilingProjectDraft/tilingProject.tex
polished the notes

@@
 
-\section{What is the minimal impurity model for a Mott metal-insulator transition?}
-The Hubbard model is one of the fundamental models for strong electronic correlation; in its simplest form, it features a single band of conduction electrons hopping on a lattice and interacting via local correlations that provide a cost \(U\) if any site is doubly occupied:
-\begin{equation}\begin{aligned}
-	H_\text{hubb} = -t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}+\text{h.c.}\right) + U\sum_i \hat n_{i \uparrow} \hat n_{i \downarrow} - \mu \sum_{i,\sigma}\hat n_{i\sigma}~.
-\end{aligned}\end{equation}
-The model can be made particle-hole symmetric by choosing \(\mu = U/2\):
-\[H_\text{hubb} = -t\sum_{\left<i,j \right>,\sigma}\left(c^\dagger_{i\sigma}c_{j\sigma}+\text{h.c.}\right) - \frac{U}{2}\sum_i \left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\]
-There are two trivial limits of the model.
-At \(U=0\), the bath consists of just a kinetic energy part, and the ground state is just a filled Fermi sea.
-At \(t=0\), each lattice site decouples from the rest and becomes a local moment, which under symmetry-breaking becomes a Néel antiferromagnet.
-This suggests that on increasing \(U/t\) beyond some critical value, the system might undergo a phase transition from a metallic state to an insulating state~\cite{Mott_1949}.
-This transition is reflected in the local spectral function - while it has a well-defined zero energy peak in the metallic phase, it is gapped in the insulating phase.
-
-One method of studying Hubbard models is through auxiliary models, described in the next section.
-Auxiliary models are simpler versions of the full Hamiltonian that are able to capture the essential physics.
-For example, a correlated impurity interacting with a conduction bath is a potential auxiliary model for the Hubbard Hamiltonian:
-\begin{equation}\begin{aligned}
-\label{clus_bath_siam}
-\mathcal{H}_\text{SIAM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow} - t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) \\
-+ V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) 
-\end{aligned}\end{equation}
-The impurity has onsite energy \(\epsilon_d\) and an onsite correlation \(U\). It hybridises into the bath through \(V\).
-
-If the impurity site hybridises with a {\it non-interacting} bath defined by a uniform density of states, the impurity spectral function is found to have a well-defined Kondo resonance at low temperatures.
-Increasing the impurity correlation \(U\) only serves to reduce the width of the central peak at the cost of the appearance of side bands at energy scales of the order of \(U\), but the resonance never dies.
-The situation is however different if the impurity is embedded in a correlated conduction bath with a non-trivial density of states.
-For the case of a conduction band with the DOS shown in the right of the figure below, the impurity hybridises into a reduced bandwidth because of the correlation on the lattice~\cite{held_2013}.
-
-This difference in the type of conduction baths is utilised in dynamical mean-field theory to describe various phases of the bulk system.
-This is done through the DMFT algorithm: one starts with a non-interacting bath, but depending on the value of \(U\), the conduction bath then gets modified and we ultimately end up with something that is different from what we started with.
-For small \(U\), the bath does not change much and we retain the central resonance of the impurity spectral function.
-This then describes a metal in the bulk.
-For larger values of \(U\), however, the bath changes significantly such that its density of states becomes non-constant.
-Above a critical \(U_c\), the impurity spectral function gets gapped out, and that then describes the insulating phase in the bulk.
-\textit{This leaves open the following question: What is the minimal correlation one can insert into the non-interacting bath (of a single-impurity Anderson model) that can capture both the metallic and insulating phases of the bulk model?}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=0.45\textwidth]{dos_diff.pdf}
-\caption{Various kinds of bath that an impurity can hybridise into.
-The left panel shows a non-interacting conduction band with a flat density of states.
-The right panel shows an interacting bath with an energy-dependent density of states.
-In the latter case, the impurity "feels" a reduced effective bandwidth defined by the width of the central peak.}
-\end{figure}
-
-\section{Philosophy of auxiliary model methods}
+\section{The philosophy of auxiliary model methods}
+
 The present method is a realisation of the general method of using simpler systems called auxiliary models to study bulk systems~\cite{martin_2016}.
@@
 This combination of the cluster and the simpler bath is then called the \textit{auxiliary system}.
-A typical auxiliary system for the Hubbard model would be the SIAM, where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{RS}\).
+A typical auxiliary system for the Hubbard model could, potentially, be the single-impurity Anderson model (SIAM), where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{RS}\):
+\begin{equation}\begin{aligned}\label{clus_bath_siam}
+	\mathcal{H}_\text{SIAM} = \underbrace{\epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow}}_{H_S} + \underbrace{- t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_{H_{R}} + \underbrace{V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)}_{H_{SR}}~.
+\end{aligned}\end{equation}
 Such a construction is shown in fig.~\ref{cluster-bath}.
@@
 
-\subsection*{Dynamical mean-field theory - an example of an auxiliary model approach}
-Dynamical mean-field theory is an approximation scheme that use impurity models to obtain Greens functions of bulk systems of strong correlation~\cite{kotliar1996,kotliar1992}.
-The essential idea is to find the most suitable impurity model that replicates the full Hamiltonian.
-This is done through the following algorithm.
-Given a bulk Hamiltonian with on=site correlation \(U\) and a non-interacting \(k-\)space Greens function \(G_{k,0}\) for the bath:
+\section{A ``bottoms-up" approach to using auxiliary models}
+
+The present work is aimed towards developing a new auxiliary model method to study correlated electronic systems.
+We first outline the main steps of the method, to make it more convenient for the reader to following the next sections:
 \begin{itemize}
-	\item[1.] We first create an impurity model with on-site correlation \(U\) and non-interacting impurity Greens function \(G_{i,0} = \sum_k G_{k,0}\).
-		\[\mathcal{H}_\text{aux} = H_\text{imp}(U) -t \sum_\sigma \left(c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) + H_\text{bath}\left(t,G_{i,0}\right)\]
-
-	\item[2.] This impurity model is solved using some method like numerical renormalisation group, and the self-energy \(\Sigma_\text{aux}\) of the impurity is obtained.
-
-	\item[3.] The impurity self-energy is now {\it equated} with the bath momentum-space self-energy:
-		\[\Sigma_{k}(\omega) = \Sigma_\text{aux}(\omega)\]
-		Since the impurity is purely local, this is an approximation that involves replacing a non-local quantity by its purely local component: \(\Sigma_{k}(\omega) = \sum_{{\bf r}}e^{i \vec{k}\cdot\vec{r}}\Sigma_{{\bf r}}(\omega) \simeq \Sigma_{{\bf r} = 0}(\omega)\).
-This approximation is a result of the single-site nature of the cluster of the chosen auxiliary model - larger clusters with more impurities can generate non-local components.
-This local approximation becomes exact in the limit of large system dimension \(w\), because it can be shown that the non-local components of the self-energy scale as \(w^{-3/2}\).
-
-	\item[4.] With this updated bath self-energy, we now create a new \(k-\)space Greens function for the bath:
-		\begin{equation}\begin{aligned}
-		G_{i}(\omega) &= \sum_k G_{k}(\omega) \\
-			      &= \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_k(\omega)} \\
-			      &= \sum_k \frac{1}{\omega - H_\text{bath}(k) - \Sigma_\text{aux}(\omega)}
-		\end{aligned}\end{equation}
-	This interacting Greens function is then used to obtain the updated non-interacting Greens function, using Dyson's equation:
-	\[G_{i,0} = \frac{1}{1/G_{i} + \Sigma_\text{aux}}\]
-	\item[5.] Repeat the algorithm from step 1 with the updated \(G_{i,0}\), until \(\Sigma_\text{aux}\) stops changing.
+	\item The first step is to identify the correct impurity model which can faithfully capture the physics of lattice model we are trying to solve (see Subsection \ref{identifyModel}).
+This model must be solved using an impurity solver.
+In the present work, we use the recently-developed unitary renormalisation group method~\cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome}.
+	\item The leap to the bulk model is then made by applying lattice translation operators on the impurity model.
+This process, referred to as tiling here, allows us to reconstruct the lattice model Hamiltonian from that of the auxiliary model (see Subsection~\ref{tilingsubsection}).
+	\item Once the Hamiltonians are linked, it is possible to relate the eigenstates and correlations functions between the auxiliary model and lattice model, using a manybody version of Bloch's theorem (see Section~\ref{tilingProcedure}).
 \end{itemize}
-The stopping condition is the consistency relation that makes the bath and impurity self-energies equal.
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.35\textwidth]{dmft_scheme.pdf}
-\end{figure}
-
-\section{A ``bottoms-up" approach to using auxiliary models}
-As mentioned in the previous section, the question we are posing is the following: what is the simplest auxiliary model of impurity in a bath that can capture the metal-insulator transition in a Hubbard-like model of correlated electrons.
-We approach this problem in a constructionist/bottoms-up way: we first identity an appropriate quantum impurity model (fig.~\ref{cluster-bath}) that shows an impurity phase transition, and then create a bulk model out of this auxiliary model.
-The bulk model hence created will then show a metal-insulator transition.
-
-The impurity models are studied using the recently-developed unitary renormalisation group method~\cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome}.
-The leap to the bulk model is then made by applying lattice translation operators on the auxiliary model.
-This process, referred to as tiling here, relates the auxiliary model Hamiltonian with that of the bulk, and hence allows connecting the Greens functions and other related quantities across dimensions.
-One nice outcome is that since the auxiliary model has multiple sites, there is a real-space off-diagonal component of the self-energy, and this leads to a \(k-\)dependence in the self-energy of the bulk, which is in contrast with the lack of \(k-\)dependence in single-site DMFT.
-
-In our approach, the auxiliary models can be chosen in various ways. The simplest choice is of course the single-impurity Anderson model of eq.~\ref{clus_bath_siam}:
-\begin{equation}\begin{aligned}
-\mathcal{H}_\text{SIAM} = \epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow} - t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) \\
-+ V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right) 
-\end{aligned}\end{equation}
-This model does not show any impurity phase transition - the impurity is always screened~\cite{hrk_wilson_1980,wilson1975,bullaNRGreview}.
-Correlation can be introduced into the auxiliary model in two ways:
+
+\subsection{Formal description of the ``tiling" procedure}\label{tilingsubsection}
+
+We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian.
+The first step is of course to identify an impurity model that can act as a good auxiliary model for out lattice model.
+The local behaviour of this impurity model should reflect the essential local physics of the lattice model.
+Typically, we will consider impurity model geometries where the real-space bath site connected directly to the impurity also harbours some kind of local interaction.
+We will henceforth refer to this site as the zeroth site.
+In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout.
+
+In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})\).
+The unit cell at the position \({\bf r}_d\) is then obtained by placing the zeroth site on all nearest-neighbours of \({\bf r}_d\) and averaging over these configurations:
+\begin{equation}\begin{aligned}\label{unitCellHamiltonian}
+	\mathcal{H}_\text{aux}({\bf r}_d) = \frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})~,
+\end{aligned}\end{equation}
+where \({\bf z}\) is summed over all nearest-neighbours of \({\bf r}_d\) and \(\mathcal{Z}\) is the number of such nearest-neighbours.
+
+In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice.
+For this, we define {\it many-particle global} translation operators \(T({\bf a})\) that translate all positions by a vector \({\bf a}\).
+In terms of manybody states and operators, their action is defined as
+\begin{equation}\begin{aligned}\label{translationDefinition}
+	&T^\dagger({\bf a}) \ket{{\bf r}_1, {\bf r}_2,\ldots} = \ket{{\bf r}_1 + {\bf a}}\otimes\ket{{\bf r}_2 + {\bf a}}\ldots\otimes\ket{{\bf r}_n + {\bf a}}\\
+	&T^\dagger({\bf a}) \mathcal{O}\left({\bf r}_1, {\bf r}_2,\ldots\right)T({\bf a}) = \mathcal{O}\left({\bf r}_1 + {\bf a}, {\bf r}_2 + {\bf a},\ldots\right)~,
+\end{aligned}\end{equation}
+where \(\ket{{\bf r}_1, {\bf r}_2,\ldots}\) is a state in the manyparticle Fock-space basis with the particles localised at the specified positions.
+For example, for a local fermionic creation operator \(c^\dagger({\bf r})\), we have
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a}) c^\dagger({\bf r}) T({\bf a}) = c^\dagger({\bf r} + {\bf a})~.
+\end{aligned}\end{equation}
+It acts similarly on the auxiliary model Hamiltonian:
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a})\mathcal{H}_\text{aux}({\bf r}_d)T({\bf a}) = \mathcal{H}_\text{aux}({\bf r}_d + {\bf a})~,
+\end{aligned}\end{equation}
+translating all sites by the vector \({\bf a}\). By introducing the Fourier transform to momentum space,
+\begin{equation}\begin{aligned}
+	\ket{{\bf r}_1, {\bf r}_2,\ldots} = \otimes_{j=1}^N \int d{\bf k}_j e^{-i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf k}_j}~,
+\end{aligned}\end{equation}
+it is easy to see that the total momentum states are eigenstates of the global translation operators:
+\begin{equation}\begin{aligned}
+	T^\dagger({\bf a})\ket{{\bf k}_1, {\bf k}_2,\ldots} &= \otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} T^\dagger({\bf a})\ket{{\bf r}_j}~,\\
+							    &=\otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf r}_j + {\bf a}}\\
+							    &=e^{-i {\bf a}_j\cdot{\bf k}_\text{tot}}\ket{{\bf k}_1, {\bf k}_2,\ldots},
+\end{aligned}\end{equation}
+where \({\bf k}_\text{tot} = \sum_j {\bf k}_j\) is the total momentum.
+
+The auxiliary model, being an impurity model, lacks translation symmetry.
+The lattice model does remain invariant under global translation operations.
+In order to reconstruct the full lattice model and restore its translation invariance, we translate the unit cell across all sites of the lattice:
+\begin{equation}\begin{aligned}
+	\label{tilingPrescription}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})\\
+				&= \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r} - {\bf r}_d)~ \\
+				&= \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d)~ \\
+\end{aligned}\end{equation}
+where \({\bf r}\) sums over all lattice sites.
+
+\subsection{Extending the Anderson impurity model: Identifying the correct auxiliary model}\label{identifyModel}
+The standard Anderson model consists of a correlated impurity site coupled with a non-interacting conduction bath.
+The double occupancy cost on the impurity is \(U\), while the single-particle hopping strength between the impurity and the conduction bath is \(V\).
+If the impurity site hybridises with a {\it non-interacting} bath defined by a uniform density of states, the impurity spectral function is found to have a well-defined Kondo resonance at low temperatures.
+Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes.
+Increasing the impurity correlation \(U\) only serves to reduce the width of the central peak at the cost of the appearance of side bands at energy scales of the order of \(U\), but the resonance never dies.
+The situation is however different if the impurity is embedded in a correlated conduction bath with a non-trivial density of states.
+For the case of a conduction band with the DOS shown in the right of the figure below, the impurity hybridises into a reduced bandwidth because of the correlation on the lattice~\cite{held_2013}.
+
+This difference in the type of conduction baths is utilised in dynamical mean-field theory to describe various phases of the bulk system.
+This is done through the DMFT algorithm: one starts with a non-interacting bath, but depending on the value of \(U\), the conduction bath then gets modified and we ultimately end up with something that is different from what we started with.
+For small \(U\), the bath does not change much and we retain the central resonance of the impurity spectral function.
+This then describes a metal in the bulk.
+For larger values of \(U\), however, the bath changes significantly such that its density of states becomes non-constant.
+Above a critical \(U_c\), the impurity spectral function gets gapped out, and that then describes the insulating phase in the bulk.
+\textit{This leaves open the following question: What is the minimal correlation one can insert into the non-interacting bath (of a single-impurity Anderson model) that can capture both the metallic and insulating phases of the bulk model?}
+
+We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model).
+The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
+\begin{equation}\begin{aligned}
+	\label{siam_attr}
+	\mathcal{H}_\text{E-S} = \mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} + \mathcal{H}_\text{imp-cbath}~,
+\end{aligned}\end{equation}
+where 
 \begin{itemize}
-	\item[1.] The impurity or the bath can be made to have additional interaction: 
-\begin{gather}
-\mathcal{H}_\text{aux} = H_\text{SIAM} + J \vec{S}_d\cdot\vec{s}_0 - \frac{1}{2}U_b \left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2
-\end{gather}
-The additional terms are (i) a spin-exchange interaction between the impurity site and the zeroth site, and (ii) a local correlation on the zeroth site.
-\item[2.] The second method is to make the cluster itself more complicated. That is, one can introduce multiple impurity sites that are connected via the hopping:
-	\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{aux} = -\frac{U}{2}\sum_{d_i}\left(\hat n_{d_i \uparrow} - \hat n_{d_i \downarrow}\right) ^2 + V\sum_{d_i}\sum_\sigma\left( c^\dagger_{d_i\sigma}c_{0\sigma} + \text{h.c.} \right) \\
-	+ \text{K.E.} - t\sum_{\sigma}\left(c^\dagger_{d_1\sigma}c_{d_2\sigma} + \text{h.c.}\right)
-	\end{aligned}\end{equation}
-
+	\item \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site,
+	\item \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and
+	\item \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 - V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath.
 \end{itemize}
-
-\begin{figure}[!htb]
- 	\centering
- 	\includegraphics[width=0.35\textwidth]{gen_siam.pdf}
- 	\caption{Cluster+bath construction of auxiliary model.
-It consists of a cluster (red square) hybridising with a bath (ring) by hopping into and out of the zeroth site (pink).
-The other sites (green) form the rest of the bath.
-Just the cluster and the zeroth site have onsite correlations.}
- \end{figure}
- The next step in the programme is to tile the real-space lattice with this cluster+bath Hamiltonian \(\tilde H\) to restore translational invariance (shown in a later section), and obtain a new bulk Hamiltonian for correlated electrons, $\tilde H = T\left[ \mathcal{H}_\text{aux} \right] T^{-1}$, where $T$ denotes the operator that performs the set of iterative real-space translations, and enables the cluster-bath (auxiliary model) Hamiltonian to span the target real-space lattice.
-Given a general auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}\), the result of tiling can be written very generally as
- \begin{equation}\begin{aligned}
-	 \tilde H = \sum_{\left\{i_1,i_2,...\right\}} \mathcal{H}_\text{aux}\left(\left\{i_1,i_2,...\right\}\right)
- \end{aligned}\end{equation}
-where \(\left\{i_1,i_2,...\right\}\) represents the indices for the members of the cluster.
-To reiterate, what that means is that we have placed the cluster+bath system at all lattice point sets \(\left\{i_1,i_2,...\right\}\) to reconstruct a new model of correlated electrons.
-The answer to how closely $\tilde H$ approximates a target model of correlated electrons lies in (i) the choice of the cluster-bath construction of the auxiliary model, and (ii) the accuracy of the URG procedure on the auxiliary model.
-
-The strategy, therefore, is to relate Hamiltonians, wavefunctions and hence correlation functions of the bulk model to those of the auxiliary model.
-One can then substitute the information obtained from solutions of the auxiliary model, and thereby calculate quantities on the bulk lattice model.
+Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath.
+We have found that the e-SIAM has a stable local moment phase for \(U_b < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)).
+We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of an optical gap in the local spectral function beyond a certain value of interaction strength.
+Note that the impurity site and the conduction bath are both at half-filling.
+
+\subsection{Tiling towards a Hubbard-Heisenberg model with an embedded extended SIAM}
+In this subsection, we provide an explicit example of constructing a lattice model.
+We will consider a slightly more generalised version of the extended SIAM described in the previous section, where the impurity site coupled to the conduction bath purely through the s-wave channel.
+We will show that that model leads to a form of a Hubbard-Heisenberg model upon restoring translation invariance via repeated translation operations.
+The generalisation involve allowing an arbitrary filling on the impurity site and in the conduction bath, through two additional parameter: (i) a particle-hole asymmetry parameter \(\eta\) for the impurity site, (ii) a chemical potential for the conduction bath, and (iii) embedding the impurity into the lattice of the 2D conduction bath.
+This modified impurity model is shown in Fig.~\ref{embeddedEsiam}.
+The first term modifies the impurity Hamiltonian \(\mathcal{H}_\text{imp}\) into
+\begin{equation}\begin{aligned}\label{onsiteHamiltonian}
+	\mathcal{H}_\text{imp} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 - \eta\sum_\sigma \hat n_{{\bf r}_d\sigma}~.
+\end{aligned}\end{equation}
+where we have placed the impurity site at the position \({\bf r}_d\). The second term modifies the conduction bath Hamiltonian \(\mathcal{H}_\text{cbath}\):
+\begin{equation}\begin{aligned}\label{bathHamiltonian}
+	\mathcal{H}_\text{cbath} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2 \mathcal{Z}}U_b\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
+\end{aligned}\end{equation}
+where \(\left<{\bf r}_i, {\bf r}_j\right>\neq {\bf r}_d\) indicates that the sum is over all nearest-neighbour pairs of sites avoiding the impurity site \({\bf r}_d\).
+
+In this notation, the interaction Hamiltonian can be written as
+\begin{equation}\begin{aligned}\label{interactionHamiltonian}
+	\mathcal{H}_\text{imp-cbath} = \frac{J}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}\sum_{{\bf z}\in\text{NN}({\bf r}_d)} {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} - \frac{V}{\sqrt{\mathcal{Z}}}\sum_{\sigma} \sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)
+\end{aligned}\end{equation}
+where \(\boldsymbol \tau = \left( \tau_x, \tau_y, \tau_z \right) \) is the vector of Pauli matrices. \(\sigma\) and \(\sigma^\prime\) can be \(\pm 1\) and represent up and down configurations.
+
+We now follow the prescription laid out in eq.~\ref{tilingPrescription}. The tiled Hamiltonian can be written as 
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{tiled} = \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} + \mathcal{H}_\text{imp-cbath}\right]T({\bf r} - {\bf r}_d)~.
+\end{aligned}\end{equation}
+Note that in comparison to eq.~\ref{tilingPrescription}, we have dropped the sum over the zeroth sites, because our impurity model Hamiltonian (defined using eqs.~\ref{onsiteHamiltonian} through \ref{interactionHamiltonian}) already contains a sum over these zeroth sites.
+
+We consider the effect of the translation operations on each part of the Hamiltonian. We first have
+\begin{equation}\begin{aligned}
+	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d) \\
+	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{U_b}{2\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}\right]T({\bf r} - {\bf r}_d) \\
+	=& -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{U_b}{2\mathcal{Z}}\sum_{\bf r}\sum_{{\bf z}\in\text{NN}\left({\bf r}\right)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i}\sum_{{\bf r} \neq {\bf r}_i}\hat n_{{\bf r}_i,\sigma}\\
+	=& -\frac{1}{\sqrt\mathcal{Z}}(N-2)t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+\end{aligned}\end{equation}
+In the first step, the factor of \(\mathcal{Z}\) is cancelled out by the trivial sum over \({\bf r}_0\) in the first and third terms.
+At the last step, the three terms simplified for the following reasons.
+The inequality \(\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}\) in the first term ensures that each nearest-neighbour pair appears in \(N-2\) instances of the auxiliary model, \(N\) being the total number of lattice sites; the two instances that do not contribute are the ones in which the impurity site itself is at \({\bf r}_i\) or \({\bf r}_j\).
+For the second term, the double sum \(\sum_{\bf r}\sum_{{\bf z} \in \text{NN}({\bf r})}\) evaluates to \(\mathcal{Z}\sum_{\bf r}\), because each point on the lattice appears \(\mathcal{W}\) times in the summation.
+This factor of \(\mathcal{W}\) cancels the one in the denominator.
+In the third term, the inner summation simply evaluates to \(N-1\), and we finally replace the dummy index \({\bf r}_i\) with \({\bf r}\).
+
+The next part is
+\begin{equation}\begin{aligned}
+	\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp}T({\bf r} - {\bf r}_d) = -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}~.
+\end{aligned}\end{equation}
+This is obtained simply by replacing the impurity position \({\bf r}_d\) with the translated position \({\bf r}\), generating a translation-invariant Hubbard term (the first term) and a finite chemical potential (second term).
+
+We now consider the final term:
+\begin{equation}\begin{aligned}
+	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp-cbath}T({\bf r} - {\bf r}_d)\\
+	&=\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} - \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma} V \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]T({\bf r} - {\bf r}_d)\\
+	&=\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r})}\left[\frac{1}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.
+-  \frac{1}{\sqrt\mathcal{Z}}\left.\sum_{\sigma} V\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]\\
+					 &=\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]\\
+\end{aligned}\end{equation}
+At the last step, each nearest-neighbour pair of sites \({\bf r}_i, {\bf r}_j\) appear 2 times in the summation, because any site is a member of two distinct nearest-neighbour pairs.
+We have also defined \({\bf S}_{{\bf r}_j} =\sum_{\sigma,\sigma^\prime} {\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime}\) as the local spin operator.
+
+The total tiled Hamiltonian is therefore
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{tiled} = -\frac{N-2}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>,\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} - \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}\\
+	+ \sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]
+\end{aligned}\end{equation}
+While constructing the tiled Hamiltonian, we have added extra copies of the non-interacting Hamiltonian \(\mathcal{H}_\text{cbath-nint} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\) for the conduction bath (this results in the factors of \(N-2\) and \(N-1\) in front of the first and third terms).
+Upon removing these repeated terms, the tiled Hamiltonian becomes
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}\\
+							 &= -\frac{1}{\sqrt\mathcal{Z}}(t + 2V)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2}\left(U + U_b\right)\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \left(\eta + 2\mu\right) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} + \frac{2}{\mathcal{Z}}J\sum_{\left< {\bf r}_i, {\bf r}_j\right>} {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j}
+\end{aligned}\end{equation}
+
+The result of the tiling operations is a Hubbard-Heisenberg model, of the form
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{HH} &= -\frac{1}{\sqrt\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma} + \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
+\end{aligned}\end{equation}
+where the tilde symbol indicates that the parameters are for the lattice model (and not the auxiliary model).
+By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to each other:
+\begin{equation}\begin{aligned}\label{couplingsMappings}
+	\tilde t = t+2V,~~ \tilde U = U + U_b, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
+\end{aligned}\end{equation}
+In summary, the appropriate method for reconstructing the lattice model Hamiltonian is therefore
+\begin{equation}\begin{aligned}\label{tilingPrescriptionFinal}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}~,
+\end{aligned}\end{equation}
+where we replaced \(N-3\) with \(N\) assuming a large number of sites. Using this, the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.
+
+\subsection{Translation symmetry and a conserved total momentum}
+From the form in eq.~\ref{tilingPrescriptionFinal}, the tiled Hamiltonian is symmetric under global many-body translations of the kind defined in eq.~\ref{translationDefinition}, by arbitrary lattice spacings:
+\begin{equation}\begin{aligned}\label{translationSymmetry}
+	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})T({\bf a}) = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r + a}) = \sum_{{\bf r}^\prime}\mathcal{H}_\text{aux}({\bf r}^\prime)\\
+	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{cbath-nint}T({\bf a}) = \mathcal{H}_\text{cbath-nint}\\
+	&\implies T({\bf a})^\dagger\mathcal{H}_\text{tiled}T({\bf a}) = \mathcal{H}_\text{tiled}~.
+\end{aligned}\end{equation}
+In the first equation, we used the fact that the translation operator simply translates the auxiliary model at the position \({\bf r}\) into another one at the position \({\bf r} + {\bf a}\).
+Since both are part of the summation, the summation remains unchanged.
+The second equation uses the fact that the Hamiltonian \(\mathcal{H}_\text{cbath-nint}\) is that of a tight-binding model and is therefore translation-invariant.
+The fact that the Hamiltonian \(\mathcal{H}_\text{tiled}\) commutes with the many-body translation operator implies that the total crystal momentum \(\vec k\) is a conserved quantity.
+
+\subsection{Form of the eigenstates: Bloch's theorem}
+In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\bf k}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_i}\), where \({\bf r}_i\) sums over the positions of the local Hamiltonians.
+Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation by an arbitrary number of lattice spacings \({n\bf a}\):
+\begin{equation}\begin{aligned}
+	T^\dagger(n{\bf a})\ket{\Psi_{{\bf k}}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_{i + n}} = e^{-in{\bf k}\cdot{\bf a}}\ket{\Psi_{\bf k}}
+\end{aligned}\end{equation}
+The definition and some properties of these global translation operations were provided in Appendix~\ref{BlochProperties}.
+It was shown there that they share eigenstates with the total momentum operator.
+In a lattice model, this continuous symmetry gets lowered to its discrete form: the total {\it crystal} momentum is conserved by any scattering process.
+As a result, the eigenstates can be labelled using the combined index \(s = \left({\bf k}, n\right) \) where \({\bf k}\) is the total crystal momentum and \(n\) is a band index \(n\).
+
+The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using eq.~\ref{tilingPrescriptionFinal} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}).
+This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) defined in eq.~\ref{unitCellHamiltonian} can be used to construct eigenstates of the lattice Hamiltonian.
+The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
+
+The state \(\ket{\psi_n\left({\bf r}_d\right)}\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself has been averaged over \(\mathcal{Z}\) zeroth sites.
+Accordingly, we can express the averaged eigenstate \(\ket{\psi_n\left({\bf r}_d\right)}\) as
+\begin{equation}\begin{aligned}
+	\ket{\psi_n\left({\bf r}_d\right)} = \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z} \in \text{NN}({\bf r}_d)}\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}~,
+\end{aligned}\end{equation}
+where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\).
+With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:
+\begin{equation}\begin{aligned}\label{eigenstateProposal}
+	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d, {\bf z}\right)}~,
+\end{aligned}\end{equation}
+where \(N\) is the total number of lattice sites and \({\bf r}_d\) is summed over all lattice spacings.
+The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands.
+The ground state \(s = s_0\) is obtained by setting \({\bf k}\) and \(n\) to 0:
+\begin{equation}\begin{aligned}\label{groundstateProposal}
+	\ket{\Psi_\text{gs}} \equiv \ket{\Psi_{s_0}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d, {\bf z}\right)}
+\end{aligned}\end{equation}
+
+\section{Mapping Static and Dynamic Correlations from the Auxiliary Model to the Lattice Model}\label{tilingProcedure}
+\subsection{One-Particle Greens Functions: Momentum-space}
+In the previous part, we proposed a form for the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{gs}}\) of the auxiliary models.
+In this section, we will relate one-particle Greens functions of the bulk lattice to those of the auxiliary model.
+We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
+We define the retarded time-domain lattice \(k-\)space Greens function at zero temperature as
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c_{{\bf K}\sigma}(t), c^\dagger_{{\bf K}\sigma} \right\} | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(t\): 
+\begin{equation}\begin{aligned}\label{heisenberg}
+	c_{{\bf K}\sigma}(t) = e^{it H_\text{tiled} }c_{{\bf K}\sigma}e^{-i t H_\text{tiled}}~.
+\end{aligned}\end{equation}
+We now proceed to simplify one of the terms of the anticommutator (for simplicity of notation):
+\begin{equation}\begin{aligned}\label{greensFunction1}
+	&\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_{\vec r,\vec \Delta}e^{-i{\bf K}_0\cdot\vec\Delta}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+To make further progress, we insert the identity resolution \(1 = \sum_s\ket{\Psi_s}\bra{\Psi_s}\) in between the two operators, where \(s=\left({\bf k}, n\right)\) sums over all eigenstates (with energies \(\tilde E_s\)).
+The lattice eigenstates themselves can again be written in terms of those of the auxiliary model, using eq.~\ref{eigenstateProposal}:
+\begin{equation}\begin{aligned}
+	\ket{\Psi_s}\bra{\Psi_s} = \sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\vec k\cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}~.
+\end{aligned}\end{equation}
+With this, eq.~\ref{greensFunction1} becomes
+	\begin{equation}\begin{aligned}\label{greensfunction2}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\vec k_0\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+In order to bring this expression closer to the form of an auxiliary model Greens function, we would like to transform the initial and final states \(\ket{\psi(\vec r)}\) and \(\ket{\psi(\vec r + \vec \Delta)}\) to apply to the same auxiliary model.
+This is done by using the relation: \(\ket{\psi(\vec r + \Delta)} = T^\dagger(\vec \Delta)\ket{\psi(\vec r)}\), where \(T^\dagger(\vec \Delta)\) translates all lattice sites by the vector \(\vec\Delta\).
+\begin{equation}\begin{aligned}
+	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) T^\dagger(\vec \Delta) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
+\end{aligned}\end{equation}
+The effect of the translation operators on the \(k-\)space annihilation operator can be easily ascertained by transforming it to real-space, using the Fourier transform definition
+\begin{equation}\begin{aligned}\label{fourTransf}
+	c({\bf K}) = \frac{1}{\sqrt N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r})~.
+\end{aligned}\end{equation}
+Upon applying this, we get
+\begin{equation}\begin{aligned}\label{translationOnField}
+	T\left(\vec a\right) c({\bf K}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}T\left(\vec a\right) c({\bf r}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r} - \vec a) = e^{-i{\bf K}\cdot\vec a}c({\bf K})~.
+\end{aligned}\end{equation}
+Using this identity on the above expression gives
+\begin{equation}\begin{aligned}
+	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = e^{-i{\bf K} \cdot \vec \Delta}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
+\end{aligned}\end{equation}
+Finally replacing this all the way back into eq.~\ref{greensfunction2} gives
+	\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K}\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime - \vec\Delta)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+To further unify the operators, we make the substitution \(\vec \Delta^\prime \to \vec \Delta^\prime + \vec \Delta\), leading to the expression
+	\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K} - \vec k\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+The sum over \(\vec\Delta\) can now be carried out, resulting in
+\begin{equation}\begin{aligned}\label{greensfunction3}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~,
+\end{aligned}\end{equation}
+where the sum over \(s=(\vec k, n)\) has been reduced to a sum over the auxiliary model eigenstate index \(n\) because of the Kronecker delta \(\delta\left(\vec k_0 + {\bf K} - \vec k\right)\).
+This can be further simplified by splitting the sum over \(\vec\Delta^\prime\) into positive and negative parts and then making the transformation \(\vec r^\prime \to \vec r^\prime + \vec \Delta^\prime\):
+\begin{equation}\begin{aligned}
+	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime-\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}\right] \\
+																																												   &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\right] \\
+\end{aligned}\end{equation}
+For each pair of \(\vec r^\prime\) and \(\vec\Delta^\prime\), the term within the box brackets has the form of a two-level Hamiltonian between the states \(\ket{\psi_n(\vec r^\prime)}\) and \(\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\), with a tunnelling amplitude \(e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\).
+The term can therefore be written in the eigenbasis of this Hamiltonian:
+\begin{equation}\begin{aligned}
+	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &=\frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right],
+\end{aligned}\end{equation}
+where \(\ket{\chi_n^\pm(\vec r^\prime,\vec\Delta^\prime)} = \frac{1}{\sqrt 2}\left[\ket{\psi_n(\vec r^\prime)} \pm e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime + \vec\Delta^\prime)}\right] \) are the eigenvectors of the tunnelling Hamiltonian with eigenvalues \(\pm 1\) respectively.
+With this basis transformation, we can rewrite eq.~\ref{greensfunction3} as
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+
+In order to make the expression more transparent, we consider the various components separately:
+\paragraph{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}:
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+These terms represent those contributions to the total Greens function that arise from excitations that start and end at a specific auxiliary model (at \(\vec r\)), and also evolve dynamically within the same auxiliary model.
+These terms are therefore exactly equal to the auxiliary model Greens function at position \(\vec r\), and are the most dominant contribution due to the localised nature of the impurity model.
+
+\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}:
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime \neq \vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+These are more non-local contributions; they involve excitations whose time evolution is governed by a different auxiliary model than the terminal one.
+These contributions are highly suppressed in the Kondo screened phase because of the strong entanglement of the singlet ground state.
+
+\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime \neq 0\)}:
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime \neq \vec r,\vec \Delta^\prime \neq 0} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+These are the most non-local contributions; they involve excitations whose time evolution is governed by three different auxiliary models. Accordingly, these contributions are further suppressed.
+
+We now consider each type of contribution in more detail.
+\subsection{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}
+Restricting ourselves to just the single auxiliary model contributions gives
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+We first consider more carefully the transition operator \(\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\) for the 1-particle excitation giving rise to the above Greens function.
+Within our auxiliary model approach, gapless excitations within the lattice model are represented by gapless excitations of the impurity site, specifically those that screen the impurity site and form the local Fermi liquid.
+As a result, the uncoordinated \(\mathcal{T}-\)matrix for the lattice model must be replaced by a combined \(\mathcal{T}-\)matrix within the impurity model that captures those gapless excitations that occur in connection with the impurity, and projects out the uncorrelated excitations that take place even when the impurity site is decoupled from the bath.
+
+In order to construct this auxiliary model \(\mathcal{T}-\)matrix, we note that the impurity site can have both spin and charge excitations.
+Considering both excitations, the modified \(\mathcal{T}-\)matrix that constructs \(k-\)space excitations in correlation with the impurity site are
+\begin{equation}\begin{aligned}\label{tmatrix}
+	\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\left(\sum_{\sigma^\prime}c^\dagger_{d\sigma} + \text{h.c.}\right) + c_{{\bf K}\sigma}\left(S_d^+ + \text{h.c.}\right)~,
+\end{aligned}\end{equation}
+leading to the updated expression for the complete Greens function:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+
+In order to convert this into a more useful form, we use eq.~\ref{heisenberg}:
+\begin{equation}\begin{aligned}
+		\braket{\psi_{0}(\vec r) | \mathcal{T}_{{\bf K}\sigma}(t) | \psi_n(\vec r)} = \braket{\psi_{0}(\vec r) | e^{it H_\text{tiled} }\mathcal{T}_{{\bf K}\sigma}e^{-i t H_\text{tiled}} | \psi_n(\vec r)}~.
+\end{aligned}\end{equation}
+Guided by the relation in eq.~\ref{tilingPrescriptionFinal} \(H_\text{tiled} = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}\) between the tiled Hamiltonian and the auxiliary model, we assume that the operator \(e^{-i t H_\text{tiled}}\) acting on the state \(\ket{\psi_n(\vec r)}\) involves the excitation energy \(E_n\) of only a single auxiliary model.
+Specifically, \(E_n\) is the energy of the eigenstate \(\ket{\psi_n(\vec r)}\).
+This is supported by the fact that this class of contributions to the Greens function is completed within a single auxiliary model.
+Accordingly, we replace \(H_\text{tiled}\) with \(E_n - \varepsilon_{\bf k} \), where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\) and \({\bf k}\) is the crystal momentum associated with the state \(\ket{\psi_n(\vec r)}\).
+This momentum was found to be constrained to \({\bf k}_0 + {\bf K}\) below eq.~\ref{greensfunction3}.
+In the same way, the action of \(H_\text{tiled}\) on the terminal state \(\ket{\psi_{0}(\vec r)}\) gives \(E_0 - \varepsilon_{\bf k_0}\), where \(E_0\) is the ground state energy of the auxiliary model at \({\bf r}\).
+Applying this to our expression gives
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[e^{-it\omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + e^{-it\omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~,
+\end{aligned}\end{equation}
+where \(\omega_p = (E_n - \varepsilon_{\bf k_0 + \bf K}) - (E_0 - \varepsilon_{\bf k_0})\) is the particle-excitation cost and \(\omega_h = -\omega_p\) is the hole-excitation cost.
+We now introduce the Fourier transform \(g(\omega) = \int~dt~ e^{i\omega T}f(t)\) to obtain the frequency-domain Greens function in its spectral representation:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; \omega) = \frac{1}{N}\sum_{\vec r}\sum_n \braket{\psi_{0}(\vec r) | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}\right] | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+For each value of \({\vec r}\), the term within that summation is simply the Greens function (for the excitation \(\mathcal{T}_{{\bf K}\sigma}\)) of the auxiliary model with the impurity site at \({\vec r}\).
+Since all these impurity models are physically equivalent (because of translation invariance), we can replace the average over \({\bf r}\) with the value obtained from any one auxiliary model.
+\begin{equation}\begin{aligned}\label{kspaceGreensFunction}
+	\tilde G({\bf K}\sigma; \omega) &= \sum_n \braket{\psi_{0} | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma} \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}\right] | \psi_{0}} \\
+									&= G^>(\mathcal{T}^\dagger_{{\bf K}\sigma}, \omega - \varepsilon_{{\bf k}_0 + {\bf K}}) + G^<(\mathcal{T}^\dagger_{{\bf K}\sigma}, \omega + \varepsilon_{{\bf k}_0 + {\bf K}})~,
+\end{aligned}\end{equation}
+where \(G^>(\mathcal{O}^\dagger, t) = -i\braket{\mathcal{O}(t)\mathcal{O}^\dagger}\) and \(G^<(\mathcal{O}^\dagger, t) = -i\braket{\mathcal{O}^\dagger\mathcal{O}(t)}\) are the greater and lesser Greens function for the auxiliary model.
+
+\subsection{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}
+Allowing for more non-local contributions, and updating the \(\mathcal{T}-\)matrix similar to the previous section gives the following Greens function:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+In order to allow computations within a single auxiliary model, we replace the translated state \(\ket{\psi_n(\vec r^\prime)}\) with \(T^\dagger(\vec r \to \vec r^\prime)\ket{\psi_n(\vec r)} \), where \(T^\dagger(\vec r - \vec r^\prime)\) translates all sites by the vector \(\vec r^\prime - \vec r\).
+This leads to a modified correlation function but within a single auxiliary model:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_{n,\vec r, \vec r^\prime} \bra{\psi_{0}(\vec r)} &\left[\mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.
+\\
+								&\left.
+\mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+In fact, by the same arguments as in the previous section, we can obtain a frequency-resolved Greens function:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; \omega) = \sum_n \bra{\psi_{0}} &\left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.\\
+															&\left.
+\frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}} ~.
+\end{aligned}\end{equation}
+To obtain the above, we used the fact that \(H_\text{tiled}\) commutes with the translation operator.
+
+%TODO
+%By expanding in terms of the small parameter $\frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}}$, this expression for $\Sigma_{H-H}(\vec k,\omega)$ can be recast in the following form:
+%\begin{equation}\begin{aligned}
+%	\Sigma_{H-H}(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~\label{selfenergy2}
+%\end{aligned}\end{equation}
+%where $\Sigma_\text{loc}$ and $\Sigma_\text{near-n}$ correspond to the local and nearest-neighbour self-energies defined on the real-space lattice 
+%\begin{eqnarray}
+%\Sigma_\text{loc}(\omega) &=& \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^{(0)}} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}}~,\\ 
+%\tilde{\Sigma}(\vec k, \omega)&=&\xi_{\vec k}\Sigma_\text{near-n}~,~\Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}^2}~.
+%\end{eqnarray}
+%We note that the form of $\Sigma(\vec k, \omega)$ obtained by us is similar to the form proposed on phenomenological grounds in the generalised DMFT + $\Sigma$ approach~\cite{sadovskii2012}.
+
+\subsection{Equal-Time Ground State Correlators: Real-space}\label{staticCorr}
+We first consider a real-space operator \(\mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r})\) that quantifies the presence of correlations over a distance \({\bf \Delta}\).
+The correlation function itself is given by the expectation value of this operator in the ground state:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_1 + {\bf r}^\prime + {\bf r}_c + {\bf r}\right)  | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_1 + {\bf r}_c + {\bf r}\right)} e^{-i{\bf k}_0\cdot\left({\bf r}_1 - {\bf r}_2\right)}~,
+\end{aligned}\end{equation}
+where \({\bf r}_1\) and \({\bf r}_1 + {\bf r}^\prime\) are the positions of the incoming and outgoing auxiliary model states, relative to \({\bf r}_c + {\bf r}\), and \({\bf k}_0\) is the crystal momentum of the ground state (which we will immediately set to zero).
+In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
+Substituting this appropriately for both the auxiliary model states gives:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_1 + {\bf r}^\prime + {\bf r}\right) \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) T^\dagger\left({\bf r}_1 + {\bf r}\right) | \psi_\text{gs}\left({\bf r}_c\right)}\\
+								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}^\prime\right) \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
+								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+As a final cosmetic change, we transform \({\bf r}_1 \to -{\bf r}\):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r},{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+Like in the Greens function calculation, we now consider the various kinds of contributions separately.
+
+\subsubsection{Intra-auxiliary model contributions: \({\bf r}^\prime = 0\)}
+These terms describe excitations that start and propagate within the same auxiliary model, upto a distance \({\bf \Delta}\):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+With an eye towards introducing the impurity operators into the correlations, we insert a complete basis defined by the eigenstates \(\left\{\ket{\psi_n\left({\bf r}_c\right)}\right\} \) of the auxiliary model into the expression:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\sum_{n}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \ket{\psi_n\left({\bf r}_c\right)}\bra{\psi_n\left({\bf r}_c\right)} \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+
+For the excitations that exist purely in the conduction bath \(({\bf r} \neq {\bf r}_c)\), the excitation operators must be suitably modified (see the arguments around eq.~\ref{tmatrix}) in order to incorporate Kondo screening.
+The modified excitation operators are generally defined as
+\begin{equation}\begin{aligned}\label{operatorTmatrix}
+	\mathcal{\tilde O}({\bf r}) = \mathcal{O}({\bf r})\mathcal{O}^\dagger(d) \mathcal{P}_\text{gs} ~,
+\end{aligned}\end{equation}
+where \(\mathcal{O}^\dagger(d)\) is the hermitian conjugate of the correlation operator \(\mathcal{O}\), but applied on the impurity sites.
+This therefore constitutes a time-reversed scattering process on the impurity site relative to the process in the bath.
+The operator \(\mathcal{P}_\text{gs}\) projects onto the ground state of the auxiliary model, since we are interested in ground state correlations.
+The operator multiplying the old correlation operator represents all possible excitations of the impurity site, and ensure that the bath and impurity excitation processes take place coherently.
+The projector ensures that only tripartite correlations between the impurity site and the two momentum states are captured by the correlation, which is what's desired within the tiling method.
+
+With this modified operator, this class of correlation functions can be written as
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r} }\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+This can be interpreted as the fact that within our auxiliary model formalism, the correlation between the sites \({\bf r}\) and \({\bf \Delta + r}\) can only occur through a transition process that connect one of the sites with the impurity site and then a return process that connects the impurity site with the other site.
+
+\subsubsection{Inter-auxiliary model contributions: \({\bf r}^\prime \neq 0\)}
+These are the most non-local contributions, and involve excitations that connect different auxiliary models:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}^\prime \neq 0}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+
+\subsection{Equal-Time Ground State Correlators: Momentum-space}
+We now consider momentum space correlations, through a general operator \(\mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1)\):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+Note that \(\mathcal{O}\) itself is a two-particle operator.
+To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_2\right)  | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_1\right)}~,
+\end{aligned}\end{equation}
+where \({\bf r}_1\) and \({\bf r}_2 \) are the positions of the incoming and outgoing auxiliary model states.
+In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
+Substituting this appropriately for both the auxiliary model states gives:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_c\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) T^\dagger\left({\bf r}_1 - {\bf r}_c\right) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+In order to simplify the translation operators, we can use eq.~\ref{translationOnField}.
+For that, we would need to know whether the operator \(\mathcal{O}\) involves a net transfer of momentum.
+If \(\mathcal{O}({\bf k})\) commutes with the total number operator \(n_{\bf k} = \sum_\sigma n_{{\bf k},\sigma}\), there is no momentum transfer.
+Examples of such operators are spin operators, \(S_{\alpha\beta}({\bf k}) \equiv c^\dagger_{{\bf k \alpha}}c_{{\bf k}\beta}\), and density operators \(n_{{\bf k}\alpha}\).
+If \(\mathcal{O}({\bf k})\) does not commute with \(n_{\bf k}\), there is a net transfer of momentum, and one such operator would be the charge isospin operator \(C^+({\bf k}) = c^\dagger_{{\bf k}\uparrow}c^\dagger_{{\bf k}\downarrow}\).
+For the first kind of operators, we have \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = \mathcal{O}({\bf k})\), while the for the latter, we get \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = e^{-{\bf a}\cdot{\bf 2k}}\mathcal{O}({\bf k})\), where \(2{\bf k}\) represents the momentum being transferred by the operator.
+We consider the two cases separately.
+
+\subsubsection{Momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] = 0\)}
+For these operators, the expression for the correlation gives
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
+										 &=\sum_{{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+To obtain the last form, we defined \({\bf \Delta}={\bf r}_2 - {\bf r}_1\) as the distance between the incoming and outgoing auxiliary model states, and preformed the sum over the free variable \({\bf r}_1\) to cancel out the factor of \(1/N\).
+Just like before, this expression can be decomposed into a term that involves a single auxiliary model and other terms that involve two distinct auxiliary models.
+By making the identification of the right transition operator \(\mathcal{\tilde O}({\bf k}) = \mathcal{O}({\bf k})\mathcal{O}^\dagger(d)\mathcal{P}_\text{gs}\), we get
+\begin{equation}\begin{aligned}\label{kspaceCorrelation}
+C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \sum_{{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{\tilde O}({\bf k}_2) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+
+\subsubsection{Non-momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] \neq 0\)}
+This class of operators incur an additional phase factor of \(e^{-{\bf a}\cdot{\bf 2k}}\) when the translation operators are translated across them:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}e^{2i\left( {\bf r}_1 - {\bf r}_c \right) \cdot \left( {\bf k}_1 - {\bf k}_2 \right)} \\
+										 &= \delta_{{\bf k}_1, {\bf k}_2}\sum_{{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+For this expression, we again defined \({\bf \Delta}\) similar to before, and carried out the sum of \({\bf r}_1\) involving the exponential to obtain a factor of \(N \delta_{{\bf k}_1, {\bf k}_2}\).
+The Kronecker delta factor is a manifestation of translational invariance and the associated total momentum conservation.
+
+As it stands, operators like \(\mathcal{O}({\bf k}_1)\) act purely on the conduction bath degrees of freedom.
+In order to incorporate impurity-bath correlation effects, we modify these operators using the appropriate \(T-\)matrices, by employing eq.~\ref{operatorTmatrix}.
+The final computations are carried out using these modified operators.
+
+\subsection{Entanglement Measures}
+We will now describe the prescription of calculating entanglement measures of the lattice model from within our auxiliary model treatment.
+In this section, we are interested mainly in two such measures, the entanglement entropy and the mutual information.
+Given a pure state \(\ket{\Psi}\) describing the complete system, the entanglement entropy \(S_\text{EE}(\nu)\) of a subsystem \(\nu\) quantifies the entanglement of \(\nu\) with the rest of the subsystem, and is defined as
+\begin{equation}\begin{aligned}
+	S_\text{EE}(\nu) = -\text{Tr}\left[\rho(\nu)\log \rho(\nu)\right],\quad \rho(\nu) = \text{Tr}_\nu\left[\ket{\Psi}\bra{\Psi}\right] 
+\end{aligned}\end{equation}
+where \(\text{Tr}\left[\cdot\right] \) is the trace operator, and \(\rho(\nu)\) is the reduced density matrix (RDM) for the subsystem \(\nu\) obtained by taking the partial trace \(\text{Tr}_\nu\) (over the states of \(\nu\)) of the full density matrix \(\rho = \ket{\Psi}\bra{\Psi}\).
+If the subsystem \(\nu\) describes local regions in real space (or states in \(k-\)space), we might be interested in the entanglement between two such subsystems \(\nu_1\) and \(\nu_2\).
+The correct measure to quantify such entanglement is the mutual information:
+\begin{equation}\begin{aligned}
+	I_2(\nu_1,\nu_2) = S_\text{EE}(\nu_1) + S_\text{EE}(\nu_2) - S_\text{EE}(\nu_1 \cup \nu_2)~,
+\end{aligned}\end{equation}
+where \(\nu_1 \cup \nu_2\) is a larger subsystem formed by combining \(\nu_1\) and \(\nu_2\).
+
+\subsubsection{Real-space entanglement}
+Real-space entanglement measures can be used to probe delocalisation-localisation transitions.
+The simplest such measure is the entanglement of a local mode.
+Since the local entanglement entropy will be uniform at each lattice site for a system with translation invariance, it suffices to calculate the real-space averaged entanglement entropy \(S_\text{EE}^\text{loc} = \frac{1}{N}\sum_{{\bf r}}S_\text{EE}\left( {\bf r} \right) \).
+By visualising the lattice model as a superposition of auxiliary models placed at various sites (eq.~\ref{tilingPrescriptionFinal}), the real space average of the lattice model can be thought of as an average over sites of a particular impurity model, and then a second average over all the impurity models.
+But since all all impurity models are equivalent to each other, the second average is redundant.
+Secondly, all correlations must derive from the impurity site, which can be formally encoded by subtracting, from this average, the corresponding contribution obtained in the absence of the impurity site.
+In total, the lattice-auxiliary model relation for the local entanglement entropy can be written as
+\begin{equation}\begin{aligned}
+	S_\text{EE}^\text{loc} = \frac{1}{N}\sum_{{\bf r}}\left[S_\text{EE}({\bf r}_d + {\bf r}) - S_\text{EE}^{(0)}({\bf r}_d + {\bf r})\right] ~,
+\end{aligned}\end{equation}
+where \({\bf r}_d\) is the impurity site position, \({\bf r}\) is the distance of a conduction bath site from the impurity site (can be zero), and \(S_\text{EE}({\bf r}_d + {\bf r})\) is the entanglement entropy, calculated within the impurity model, at the locatiom \({\bf r}_d + {\bf r}\).
+\(S^{(0)}_\text{EE}({\bf r}_d + {\bf r})\) is the same entanglement entropy, but calculated for an impurity model with vanishing impurity-bath hybridisation and bath interaction.
+
+\subsubsection{Momentum-space entanglement}
+Entanglement measures in \(k-\)space can provide valuable information regarding the Fermi surface structure and the nature of gapless excitations proximate to it.
+The most elementary measure is the entanglement entropy \(S_\text{EE}({\bf q})\) of a single excitation carrying momentum \({\bf q}\).
+Unlike \(S_\text{EE}^\text{loc}\), this does not involve an average, and involves a single computation:
+\begin{equation}\begin{aligned}
+	\tilde S_\text{EE}({\bf q}) = S_\text{EE}({\bf q}) - S_\text{EE}^{(0)}({\bf q})~.
+\end{aligned}\end{equation}
+It is possible to improve this by considering inter-auxiliary model contributions in the reduced density matrix \(\rho({\bf q})\). On the lattice model, \(\rho({\bf q})\) is defined as
+\begin{equation}\begin{aligned}\label{SEE-k}
+	\rho({\bf q}) = \text{Tr}_{\bf q}\left[\ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\right] ~,
+\end{aligned}\end{equation}
+where \(\text{Tr}_{\bf q}\left[\cdot\right]\) is the partial trace over the Hilbert space of \({\bf q}\), and \(\ket{\Psi_\text{gs}}\) is the tiled ground state.
+Using eq.~\ref{groundstateProposal}, we can write the ground state in terms of those of the auxiliary model.
+These leads to two classes of terms, one purely within a single auxiliary model ground state \(\ket{\psi_\text{gs}}\), and the other involving transitions across auxiliary models:
+\begin{equation}\begin{aligned}\label{RDMTiled}
+	\rho({\bf q}) \sim \text{Tr}_{\bf q}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d)}\right] + \frac{1}{N}\text{Tr}_{\bf q}\sum_{{\bf r}}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d + {\bf r})}\right]~,
+\end{aligned}\end{equation}
+where \(\ket{\psi_\text{gs}({\bf r}_d)}\) is a reference auxiliary model ground state, and \(\ket{\psi_\text{gs}({\bf r}_d + {\bf r})}\) sums over other auxiliary models at increasing distances from this reference model.
+The \(\sim\) indicates that the RDM needs to be normalised.
+The first term leads to the expression in eq.~\ref{SEE-k}, while the second term can be used to improve this estimate.
+Away from any quantum critical points, the localised nature of the impurity-bath hybridisation ensures that impurity correlations decay exponentially away from the transition.
+This ensures that the second term is very small away from a critical point.
+We therefore restrict ourselves to just the first term in the present work.
 
@@
 	\centering
-	\includegraphics[width=0.23\textwidth]{doubOcc-1.pdf}
-	\includegraphics[width=0.23\textwidth]{doubOcc-3.pdf}
-	\includegraphics[width=0.23\textwidth]{cfantinode-3.pdf}
-	\includegraphics[width=0.23\textwidth]{cfnode-3.pdf}
+	\includegraphics[width=0.23\textwidth]{cfnode-1.pdf}
+	\includegraphics[width=0.23\textwidth]{cfnode-2.pdf}
+	\includegraphics[width=0.23\textwidth]{cfantinode-1.pdf}
+	\includegraphics[width=0.23\textwidth]{cfantinode-2.pdf}
 	\caption{{\it Top panels}: Distribution of double occupancy at \(W=0\) and \(W=-1.74\) (entry into the pseudogap).
@@
 
-\section{Nature of Gapless Excitations in the Impurity Pseudogap}
+\section{Nature of Gapless Excitations in the Impurity Pseudogap}\label{2CKEmerge}
 \subsection{Emergence of a two-channel Kondo Model}
@@
 This ratio vanishes (left panel of Fig.~\ref{channelDecoupling}) within the local pseudogap regime, indicating that no direct Kondo scattering process persists between the two sectors \(S^\pm\) at low energies, deep within the pseudogap regime.
+We call the value of \(W\) at which this ratio vanishes \(W^*\).
 
@@
 
-\subsection{Marginal Fermi liquid behaviour in the pseudogap}
+\subsection{Marginal Fermi liquid behaviour in the pseudogap}\label{marginalFL}
 It is well-known that the two-channel Kondo model hosts non-Fermi liquid excitations at low-energies~\cite{Tsvelick_weigmann_mchannel_1985,emery_kivelson}; that this also happens in the present model is corroborated by our calculations of the quasiparticle residue \(Z_\text{imp}\) for the local gapless excitations.
@@
 
-\section{The Tiling Algorithm}
-
-\subsection{Formal description of the tiling procedure}
-We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian.
-The first step is of course to identify an impurity model that can act as a good auxiliary model for out lattice model.
-The local behaviour of this impurity model should reflect the essential local physics of the lattice model.
-Typically, we will consider impurity model geometries where the real-space bath site connected directly to the impurity also harbours some kind of local interaction.
-We will henceforth refer to this site as the zeroth site.
-In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout.
-
-In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})\).
-The unit cell at the position \({\bf r}_d\) is then obtained by placing the zeroth site on all nearest-neighbours of \({\bf r}_d\) and averaging over these configurations:
-\begin{equation}\begin{aligned}\label{unitCellHamiltonian}
-	\mathcal{H}_\text{aux}({\bf r}_d) = \frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})~,
-\end{aligned}\end{equation}
-where \({\bf z}\) is summed over all nearest-neighbours of \({\bf r}_d\) and \(\mathcal{Z}\) is the number of such nearest-neighbours.
-
-In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice.
-For this, we define {\it many-particle global} translation operators \(T({\bf a})\) that translate all positions by a vector \({\bf a}\).
-In terms of manybody states and operators, their action is defined as
-\begin{equation}\begin{aligned}\label{translationDefinition}
-	&T^\dagger({\bf a}) \ket{{\bf r}_1, {\bf r}_2,\ldots} = \ket{{\bf r}_1 + {\bf a}}\otimes\ket{{\bf r}_2 + {\bf a}}\ldots\otimes\ket{{\bf r}_n + {\bf a}}\\
-	&T^\dagger({\bf a}) \mathcal{O}\left({\bf r}_1, {\bf r}_2,\ldots\right)T({\bf a}) = \mathcal{O}\left({\bf r}_1 + {\bf a}, {\bf r}_2 + {\bf a},\ldots\right)~,
-\end{aligned}\end{equation}
-where \(\ket{{\bf r}_1, {\bf r}_2,\ldots}\) is a state in the manyparticle Fock-space basis with the particles localised at the specified positions.
-For example, for a local fermionic creation operator \(c^\dagger({\bf r})\), we have
-\begin{equation}\begin{aligned}
-	T^\dagger({\bf a}) c^\dagger({\bf r}) T({\bf a}) = c^\dagger({\bf r} + {\bf a})~.
-\end{aligned}\end{equation}
-It acts similarly on the auxiliary model Hamiltonian:
-\begin{equation}\begin{aligned}
-	T^\dagger({\bf a})\mathcal{H}_\text{aux}({\bf r}_d)T({\bf a}) = \mathcal{H}_\text{aux}({\bf r}_d + {\bf a})~,
-\end{aligned}\end{equation}
-translating all sites by the vector \({\bf a}\). By introducing the Fourier transform to momentum space,
-\begin{equation}\begin{aligned}
-	\ket{{\bf r}_1, {\bf r}_2,\ldots} = \otimes_{j=1}^N \int d{\bf k}_j e^{-i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf k}_j}~,
-\end{aligned}\end{equation}
-it is easy to see that the total momentum states are eigenstates of the global translation operators:
-\begin{equation}\begin{aligned}
-	T^\dagger({\bf a})\ket{{\bf k}_1, {\bf k}_2,\ldots} &= \otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} T^\dagger({\bf a})\ket{{\bf r}_j}~,\\
-							    &=\otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf r}_j + {\bf a}}\\
-							    &=e^{-i {\bf a}_j\cdot{\bf k}_\text{tot}}\ket{{\bf k}_1, {\bf k}_2,\ldots},
-\end{aligned}\end{equation}
-where \({\bf k}_\text{tot} = \sum_j {\bf k}_j\) is the total momentum.
-
-The auxiliary model, being an impurity model, lacks translation symmetry.
-The lattice model does remain invariant under global translation operations.
-In order to reconstruct the full lattice model and restore its translation invariance, we translate the unit cell across all sites of the lattice:
-\begin{equation}\begin{aligned}
-	\label{tilingPrescription}
-	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})\\
-				&= \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r} - {\bf r}_d)~ \\
-				&= \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d)~ \\
-\end{aligned}\end{equation}
-where \({\bf r}\) sums over all lattice sites.
-
-\subsection{Extending the Anderson impurity model: Identifying the correct auxiliary model}
-The standard Anderson model consists of a correlated impurity site coupled with a non-interacting conduction bath.
-The double occupancy cost on the impurity is \(U\), while the single-particle hopping strength between the impurity and the conduction bath is \(V\).
-Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes.
-We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model).
-The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
-\begin{equation}\begin{aligned}
-	\label{siam_attr}
-	\mathcal{H}_\text{E-S} = \mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} + \mathcal{H}_\text{imp-cbath}~,
-\end{aligned}\end{equation}
-where 
-\begin{itemize}
-	\item \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site,
-	\item \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and
-	\item \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 - V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath.
-\end{itemize}
-Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath.
-We have found that the e-SIAM has a stable local moment phase for \(U_b < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)).
-We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of an optical gap in the local spectral function beyond a certain value of interaction strength.
-Note that the impurity site and the conduction bath are both at half-filling.
-
-\subsection{Tiling towards a Hubbard-Heisenberg model with an embedded extended SIAM}
-In this subsection, we provide an explicit example of constructing a lattice model.
-We will consider a slightly more generalised version of the extended SIAM described in the previous section, where the impurity site coupled to the conduction bath purely through the s-wave channel.
-We will show that that model leads to a form of a Hubbard-Heisenberg model upon restoring translation invariance via repeated translation operations.
-The generalisation involve allowing an arbitrary filling on the impurity site and in the conduction bath, through two additional parameter: (i) a particle-hole asymmetry parameter \(\eta\) for the impurity site, (ii) a chemical potential for the conduction bath, and (iii) embedding the impurity into the lattice of the 2D conduction bath.
-This modified impurity model is shown in Fig.~\ref{embeddedEsiam}.
-The first term modifies the impurity Hamiltonian \(\mathcal{H}_\text{imp}\) into
-\begin{equation}\begin{aligned}\label{onsiteHamiltonian}
-	\mathcal{H}_\text{imp} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 - \eta\sum_\sigma \hat n_{{\bf r}_d\sigma}~.
-\end{aligned}\end{equation}
-where we have placed the impurity site at the position \({\bf r}_d\). The second term modifies the conduction bath Hamiltonian \(\mathcal{H}_\text{cbath}\):
-\begin{equation}\begin{aligned}\label{bathHamiltonian}
-	\mathcal{H}_\text{cbath} &= -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
-							 &- \frac{1}{2 \mathcal{Z}}U_b\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
-\end{aligned}\end{equation}
-where \(\left<{\bf r}_i, {\bf r}_j\right>\neq {\bf r}_d\) indicates that the sum is over all nearest-neighbour pairs of sites avoiding the impurity site \({\bf r}_d\).
-
-In this notation, the interaction Hamiltonian can be written as
-\begin{equation}\begin{aligned}\label{interactionHamiltonian}
-	\mathcal{H}_\text{imp-cbath} &= \frac{J}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}\sum_{{\bf z}\in\text{NN}({\bf r}_d)} {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \\
-								 & - \frac{V}{\sqrt{\mathcal{Z}}}\sum_{\sigma} \sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)
-\end{aligned}\end{equation}
-where \(\boldsymbol \tau = \left( \tau_x, \tau_y, \tau_z \right) \) is the vector of Pauli matrices. \(\sigma\) and \(\sigma^\prime\) can be \(\pm 1\) and represent up and down configurations.
-
-We now follow the prescription laid out in eq.~\ref{tilingPrescription}. The tiled Hamiltonian can be written as 
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{tiled} = \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} \right.\\
-\left.+ \mathcal{H}_\text{imp-cbath}\right]T({\bf r} - {\bf r}_d)~.
-\end{aligned}\end{equation}
-Note that in comparison to eq.~\ref{tilingPrescription}, we have dropped the sum over the zeroth sites, because our impurity model Hamiltonian (defined using eqs.~\ref{onsiteHamiltonian} through \ref{interactionHamiltonian}) already contains a sum over these zeroth sites.
-
-We consider the effect of the translation operations on each part of the Hamiltonian. We first have
-\begin{equation}\begin{aligned}
-	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d) \\
-	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \right.\\
-	 &\left.- \frac{U_b}{2\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}\right]T({\bf r} - {\bf r}_d) \\
-	=& -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
-	 &- \frac{U_b}{2\mathcal{Z}}\sum_{\bf r}\sum_{{\bf z}\in\text{NN}\left({\bf r}\right)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i}\sum_{{\bf r} \neq {\bf r}_i}\hat n_{{\bf r}_i,\sigma}\\
-	=& -\frac{1}{\sqrt\mathcal{Z}}(N-2)t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right)\\
-	 &- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
-\end{aligned}\end{equation}
-In the first step, the factor of \(\mathcal{Z}\) is cancelled out by the trivial sum over \({\bf r}_0\) in the first and third terms.
-At the last step, the three terms simplified for the following reasons.
-The inequality \(\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}\) in the first term ensures that each nearest-neighbour pair appears in \(N-2\) instances of the auxiliary model, \(N\) being the total number of lattice sites; the two instances that do not contribute are the ones in which the impurity site itself is at \({\bf r}_i\) or \({\bf r}_j\).
-For the second term, the double sum \(\sum_{\bf r}\sum_{{\bf z} \in \text{NN}({\bf r})}\) evaluates to \(\mathcal{Z}\sum_{\bf r}\), because each point on the lattice appears \(\mathcal{W}\) times in the summation.
-This factor of \(\mathcal{W}\) cancels the one in the denominator.
-In the third term, the inner summation simply evaluates to \(N-1\), and we finally replace the dummy index \({\bf r}_i\) with \({\bf r}\).
-
-The next part is
-\begin{equation}\begin{aligned}
-	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp}T({\bf r} - {\bf r}_d) \\
-	=& -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}~.
-\end{aligned}\end{equation}
-This is obtained simply by replacing the impurity position \({\bf r}_d\) with the translated position \({\bf r}\), generating a translation-invariant Hubbard term (the first term) and a finite chemical potential (second term).
-
-We now consider the final term:
-\begin{equation}\begin{aligned}
-	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp-cbath}T({\bf r} - {\bf r}_d)\\
-	&=\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
-				     &-  \left. \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma} V \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]T({\bf r} - {\bf r}_d)\\
-	&=\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r})}\left[\frac{1}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.\\
-				     &-  \frac{1}{\sqrt\mathcal{Z}}\left.\sum_{\sigma} V\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]\\
-					 &=\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]\\
-\end{aligned}\end{equation}
-At the last step, each nearest-neighbour pair of sites \({\bf r}_i, {\bf r}_j\) appear 2 times in the summation, because any site is a member of two distinct nearest-neighbour pairs.
-We have also defined \({\bf S}_{{\bf r}_j} =\sum_{\sigma,\sigma^\prime} {\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime}\) as the local spin operator.
-
-The total tiled Hamiltonian is therefore
-\begin{equation}\begin{aligned}
-	&\mathcal{H}_\text{tiled} \\
-	&= -\frac{N-2}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>,\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
-	&- \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}\\
-	& + \sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]
-\end{aligned}\end{equation}
-While constructing the tiled Hamiltonian, we have added extra copies of the non-interacting Hamiltonian \(\mathcal{H}_\text{cbath-nint} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\) for the conduction bath (this results in the factors of \(N-2\) and \(N-1\) in front of the first and third terms).
-Upon removing these repeated terms, the tiled Hamiltonian becomes
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}\\
-							 &= -\frac{1}{\sqrt\mathcal{Z}}(t + 2V)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
-							 &- \frac{1}{2}\left(U + U_b\right)\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \left(\eta + 2\mu\right) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} \\
-							 &+ \frac{2}{\mathcal{Z}}J\sum_{\left< {\bf r}_i, {\bf r}_j\right>} {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j}
-\end{aligned}\end{equation}
-
-The result of the tiling operations is a Hubbard-Heisenberg model, of the form
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{HH} &= -\frac{1}{\sqrt\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
-						  &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
-\end{aligned}\end{equation}
-where the tilde symbol indicates that the parameters are for the lattice model (and not the auxiliary model).
-By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to each other:
-\begin{equation}\begin{aligned}\label{couplingsMappings}
-	\tilde t = t+2V,~~ \tilde U = U + U_b, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
-\end{aligned}\end{equation}
-In summary, the appropriate method for reconstructing the lattice model Hamiltonian is therefore
-\begin{equation}\begin{aligned}\label{tilingPrescriptionFinal}
-	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}~,
-\end{aligned}\end{equation}
-where we replaced \(N-3\) with \(N\) assuming a large number of sites. Using this, the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.
-
-\subsection{Translation symmetry and a conserved total momentum}
-From the form in eq.~\ref{tilingPrescriptionFinal}, the tiled Hamiltonian is symmetric under global many-body translations of the kind defined in eq.~\ref{translationDefinition}, by arbitrary lattice spacings:
-\begin{equation}\begin{aligned}\label{translationSymmetry}
-	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})T({\bf a}) = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r + a}) = \sum_{{\bf r}^\prime}\mathcal{H}_\text{aux}({\bf r}^\prime)\\
-	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{cbath-nint}T({\bf a}) = \mathcal{H}_\text{cbath-nint}\\
-	&\implies T({\bf a})^\dagger\mathcal{H}_\text{tiled}T({\bf a}) = \mathcal{H}_\text{tiled}~.
-\end{aligned}\end{equation}
-In the first equation, we used the fact that the translation operator simply translates the auxiliary model at the position \({\bf r}\) into another one at the position \({\bf r} + {\bf a}\).
-Since both are part of the summation, the summation remains unchanged.
-The second equation uses the fact that the Hamiltonian \(\mathcal{H}_\text{cbath-nint}\) is that of a tight-binding model and is therefore translation-invariant.
-The fact that the Hamiltonian \(\mathcal{H}_\text{tiled}\) commutes with the many-body translation operator implies that the total crystal momentum \(\vec k\) is a conserved quantity.
-
-\section{Form of the eigenstates: Bloch's theorem}
-In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full eigenstate \(\ket{\Psi}\) is then obtained by constructing liner combinations of the eigenstates \(\ket{\psi_i}\) of the local Hamiltonians such that \(\ket{\Psi}\) satisfies Bloch's theorem: \(\ket{\Psi_{\bf k}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_i}\), where \({\bf r}_i\) sums over the positions of the local Hamiltonians.
-Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation by an arbitrary number of lattice spacings \({n\bf a}\):
-\begin{equation}\begin{aligned}
-	T^\dagger(n{\bf a})\ket{\Psi_{{\bf k}}} = \sum_{i} e^{i {\bf k}\cdot{\bf r}_i} \ket{\psi_{i + n}} = e^{-in{\bf k}\cdot{\bf a}}\ket{\Psi_{\bf k}}
-\end{aligned}\end{equation}
-The definition and some properties of these global translation operations were provided in Appendix~\ref{BlochProperties}.
-It was shown there that they share eigenstates with the total momentum operator.
-In a lattice model, this continuous symmetry gets lowered to its discrete form: the total {\it crystal} momentum is conserved by any scattering process.
-As a result, the eigenstates can be labelled using the combined index \(s = \left({\bf k}, n\right) \) where \({\bf k}\) is the total crystal momentum and \(n\) is a band index \(n\).
-
-The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using eq.~\ref{tilingPrescriptionFinal} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}).
-This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) defined in eq.~\ref{unitCellHamiltonian} can be used to construct eigenstates of the lattice Hamiltonian.
-The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
-
-The state \(\ket{\psi_n\left({\bf r}_d\right)}\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself has been averaged over \(\mathcal{Z}\) zeroth sites.
-Accordingly, we can express the averaged eigenstate \(\ket{\psi_n\left({\bf r}_d\right)}\) as
-\begin{equation}\begin{aligned}
-	\ket{\psi_n\left({\bf r}_d\right)} = \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z} \in \text{NN}({\bf r}_d)}\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}~,
-\end{aligned}\end{equation}
-where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\).
-With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:
-\begin{equation}\begin{aligned}\label{eigenstateProposal}
-	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d, {\bf z}\right)}~,
-\end{aligned}\end{equation}
-where \(N\) is the total number of lattice sites and \({\bf r}_d\) is summed over all lattice spacings.
-The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands.
-The ground state \(s = s_0\) is obtained by setting \({\bf k}\) and \(n\) to 0:
-\begin{equation}\begin{aligned}\label{groundstateProposal}
-	\ket{\Psi_\text{gs}} \equiv \ket{\Psi_{s_0}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d, {\bf z}\right)}
-\end{aligned}\end{equation}
-
-\section{One-Particle Greens Functions}
-\subsection{Momentum-space}
-In the previous part, we proposed a form for the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{gs}}\) of the auxiliary models.
-In this section, we will relate one-particle Greens functions of the bulk lattice to those of the auxiliary model.
-We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
-We define the retarded time-domain lattice \(k-\)space Greens function at zero temperature as
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c_{{\bf K}\sigma}(t), c^\dagger_{{\bf K}\sigma} \right\} | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(t\): 
-\begin{equation}\begin{aligned}\label{heisenberg}
-	c_{{\bf K}\sigma}(t) = e^{it H_\text{tiled} }c_{{\bf K}\sigma}e^{-i t H_\text{tiled}}~.
-\end{aligned}\end{equation}
-We now proceed to simplify one of the terms of the anticommutator (for simplicity of notation):
-\begin{equation}\begin{aligned}\label{greensFunction1}
-	&\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_{\vec r,\vec \Delta}e^{-i{\bf K}_0\cdot\vec\Delta}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-To make further progress, we insert the identity resolution \(1 = \sum_s\ket{\Psi_s}\bra{\Psi_s}\) in between the two operators, where \(s=\left({\bf k}, n\right)\) sums over all eigenstates (with energies \(\tilde E_s\)).
-The lattice eigenstates themselves can again be written in terms of those of the auxiliary model, using eq.~\ref{eigenstateProposal}:
-\begin{equation}\begin{aligned}
-	\ket{\Psi_s}\bra{\Psi_s} = \sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\vec k\cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}~.
-\end{aligned}\end{equation}
-With this, eq.~\ref{greensFunction1} becomes
-	\begin{equation}\begin{aligned}\label{greensfunction2}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\vec k_0\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-In order to bring this expression closer to the form of an auxiliary model Greens function, we would like to transform the initial and final states \(\ket{\psi(\vec r)}\) and \(\ket{\psi(\vec r + \vec \Delta)}\) to apply to the same auxiliary model.
-This is done by using the relation: \(\ket{\psi(\vec r + \Delta)} = T^\dagger(\vec \Delta)\ket{\psi(\vec r)}\), where \(T^\dagger(\vec \Delta)\) translates all lattice sites by the vector \(\vec\Delta\).
-\begin{equation}\begin{aligned}
-	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) T^\dagger(\vec \Delta) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
-\end{aligned}\end{equation}
-The effect of the translation operators on the \(k-\)space annihilation operator can be easily ascertained by transforming it to real-space, using the Fourier transform definition
-\begin{equation}\begin{aligned}\label{fourTransf}
-	c({\bf K}) = \frac{1}{\sqrt N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r})~.
-\end{aligned}\end{equation}
-Upon applying this, we get
-\begin{equation}\begin{aligned}\label{translationOnField}
-	T\left(\vec a\right) c({\bf K}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}T\left(\vec a\right) c({\bf r}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r} - \vec a) = e^{-i{\bf K}\cdot\vec a}c({\bf K})~.
-\end{aligned}\end{equation}
-Using this identity on the above expression gives
-\begin{equation}\begin{aligned}
-	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = e^{-i{\bf K} \cdot \vec \Delta}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
-\end{aligned}\end{equation}
-Finally replacing this all the way back into eq.~\ref{greensfunction2} gives
-	\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K}\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime - \vec\Delta)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-To further unify the operators, we make the substitution \(\vec \Delta^\prime \to \vec \Delta^\prime + \vec \Delta\), leading to the expression
-	\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K} - \vec k\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-The sum over \(\vec\Delta\) can now be carried out, resulting in
-\begin{equation}\begin{aligned}\label{greensfunction3}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~,
-\end{aligned}\end{equation}
-where the sum over \(s=(\vec k, n)\) has been reduced to a sum over the auxiliary model eigenstate index \(n\) because of the Kronecker delta \(\delta\left(\vec k_0 + {\bf K} - \vec k\right)\).
-This can be further simplified by splitting the sum over \(\vec\Delta^\prime\) into positive and negative parts and then making the transformation \(\vec r^\prime \to \vec r^\prime + \vec \Delta^\prime\):
-\begin{equation}\begin{aligned}
-	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime-\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}\right] \\
-																																												   &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\right] \\
-\end{aligned}\end{equation}
-For each pair of \(\vec r^\prime\) and \(\vec\Delta^\prime\), the term within the box brackets has the form of a two-level Hamiltonian between the states \(\ket{\psi_n(\vec r^\prime)}\) and \(\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\), with a tunnelling amplitude \(e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\).
-The term can therefore be written in the eigenbasis of this Hamiltonian:
-\begin{equation}\begin{aligned}
-	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &=\frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right],
-\end{aligned}\end{equation}
-where \(\ket{\chi_n^\pm(\vec r^\prime,\vec\Delta^\prime)} = \frac{1}{\sqrt 2}\left[\ket{\psi_n(\vec r^\prime)} \pm e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime + \vec\Delta^\prime)}\right] \) are the eigenvectors of the tunnelling Hamiltonian with eigenvalues \(\pm 1\) respectively.
-With this basis transformation, we can rewrite eq.~\ref{greensfunction3} as
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-
-In order to make the expression more transparent, we consider the various components separately:
-\paragraph{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}:
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-These terms represent those contributions to the total Greens function that arise from excitations that start and end at a specific auxiliary model (at \(\vec r\)), and also evolve dynamically within the same auxiliary model.
-These terms are therefore exactly equal to the auxiliary model Greens function at position \(\vec r\), and are the most dominant contribution due to the localised nature of the impurity model.
-
-\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}:
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime \neq \vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-These are more non-local contributions; they involve excitations whose time evolution is governed by a different auxiliary model than the terminal one.
-These contributions are highly suppressed in the Kondo screened phase because of the strong entanglement of the singlet ground state.
-
-\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime \neq 0\)}:
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime \neq \vec r,\vec \Delta^\prime \neq 0} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-These are the most non-local contributions; they involve excitations whose time evolution is governed by three different auxiliary models. Accordingly, these contributions are further suppressed.
-
-We now consider each type of contribution in more detail.
-\subsection{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}
-Restricting ourselves to just the single auxiliary model contributions gives
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-We first consider more carefully the transition operator \(\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\) for the 1-particle excitation giving rise to the above Greens function.
-Within our auxiliary model approach, gapless excitations within the lattice model are represented by gapless excitations of the impurity site, specifically those that screen the impurity site and form the local Fermi liquid.
-As a result, the uncoordinated \(\mathcal{T}-\)matrix for the lattice model must be replaced by a combined \(\mathcal{T}-\)matrix within the impurity model that captures those gapless excitations that occur in connection with the impurity, and projects out the uncorrelated excitations that take place even when the impurity site is decoupled from the bath.
-
-In order to construct this auxiliary model \(\mathcal{T}-\)matrix, we note that the impurity site can have both spin and charge excitations.
-Considering both excitations, the modified \(\mathcal{T}-\)matrix that constructs \(k-\)space excitations in correlation with the impurity site are
-\begin{equation}\begin{aligned}\label{tmatrix}
-	\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\left(\sum_{\sigma^\prime}c^\dagger_{d\sigma} + \text{h.c.}\right) + c_{{\bf K}\sigma}\left(S_d^+ + \text{h.c.}\right)~,
-\end{aligned}\end{equation}
-leading to the updated expression for the complete Greens function:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-
-In order to convert this into a more useful form, we use eq.~\ref{heisenberg}:
-\begin{equation}\begin{aligned}
-		\braket{\psi_{0}(\vec r) | \mathcal{T}_{{\bf K}\sigma}(t) | \psi_n(\vec r)} = \braket{\psi_{0}(\vec r) | e^{it H_\text{tiled} }\mathcal{T}_{{\bf K}\sigma}e^{-i t H_\text{tiled}} | \psi_n(\vec r)}~.
-\end{aligned}\end{equation}
-Guided by the relation in eq.~\ref{tilingPrescriptionFinal} \(H_\text{tiled} = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}\) between the tiled Hamiltonian and the auxiliary model, we assume that the operator \(e^{-i t H_\text{tiled}}\) acting on the state \(\ket{\psi_n(\vec r)}\) involves the excitation energy \(E_n\) of only a single auxiliary model.
-Specifically, \(E_n\) is the energy of the eigenstate \(\ket{\psi_n(\vec r)}\).
-This is supported by the fact that this class of contributions to the Greens function is completed within a single auxiliary model.
-Accordingly, we replace \(H_\text{tiled}\) with \(E_n - \varepsilon_{\bf k} \), where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\) and \({\bf k}\) is the crystal momentum associated with the state \(\ket{\psi_n(\vec r)}\).
-This momentum was found to be constrained to \({\bf k}_0 + {\bf K}\) below eq.~\ref{greensfunction3}.
-In the same way, the action of \(H_\text{tiled}\) on the terminal state \(\ket{\psi_{0}(\vec r)}\) gives \(E_0 - \varepsilon_{\bf k_0}\), where \(E_0\) is the ground state energy of the auxiliary model at \({\bf r}\).
-Applying this to our expression gives
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[e^{-it\omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + e^{-it\omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~,
-\end{aligned}\end{equation}
-where \(\omega_p = (E_n - \varepsilon_{\bf k_0 + \bf K}) - (E_0 - \varepsilon_{\bf k_0})\) is the particle-excitation cost and \(\omega_h = -\omega_p\) is the hole-excitation cost.
-We now introduce the Fourier transform \(g(\omega) = \int~dt~ e^{i\omega T}f(t)\) to obtain the frequency-domain Greens function in its spectral representation:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; \omega) = \frac{1}{N}\sum_{\vec r}\sum_n \braket{\psi_{0}(\vec r) | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-For each value of \({\vec r}\), the term within that summation is simply the Greens function (for the excitation \(\mathcal{T}_{{\bf K}\sigma}\)) of the auxiliary model with the impurity site at \({\vec r}\).
-Since all these impurity models are physically equivalent (because of translation invariance), we can replace the average over \({\bf r}\) with the value obtained from any one auxiliary model.
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; \omega) = \sum_n \braket{\psi_{0} | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}} ~.
-\end{aligned}\end{equation}
-
-\subsection{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}
-Allowing for more non-local contributions, and updating the \(\mathcal{T}-\)matrix similar to the previous section gives the following Greens function:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-In order to allow computations within a single auxiliary model, we replace the translated state \(\ket{\psi_n(\vec r^\prime)}\) with \(T^\dagger(\vec r \to \vec r^\prime)\ket{\psi_n(\vec r)} \), where \(T^\dagger(\vec r - \vec r^\prime)\) translates all sites by the vector \(\vec r^\prime - \vec r\).
-This leads to a modified correlation function but within a single auxiliary model:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_{n,\vec r, \vec r^\prime} \bra{\psi_{0}(\vec r)} &\left[\mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.
-\\
-								&\left.
-\mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-In fact, by the same arguments as in the previous section, we can obtain a frequency-resolved Greens function:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; \omega) = \sum_n \bra{\psi_{0}} &\left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.\\
-															&\left.
-\frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}} ~.
-\end{aligned}\end{equation}
-To obtain the above, we used the fact that \(H_\text{tiled}\) commutes with the translation operator.
-
-%TODO
-%By expanding in terms of the small parameter $\frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}}$, this expression for $\Sigma_{H-H}(\vec k,\omega)$ can be recast in the following form:
-%\begin{equation}\begin{aligned}
-%	\Sigma_{H-H}(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~\label{selfenergy2}
-%\end{aligned}\end{equation}
-%where $\Sigma_\text{loc}$ and $\Sigma_\text{near-n}$ correspond to the local and nearest-neighbour self-energies defined on the real-space lattice 
-%\begin{eqnarray}
-%\Sigma_\text{loc}(\omega) &=& \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^{(0)}} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}}~,\\ 
-%\tilde{\Sigma}(\vec k, \omega)&=&\xi_{\vec k}\Sigma_\text{near-n}~,~\Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}^2}~.
-%\end{eqnarray}
-%We note that the form of $\Sigma(\vec k, \omega)$ obtained by us is similar to the form proposed on phenomenological grounds in the generalised DMFT + $\Sigma$ approach~\cite{sadovskii2012}.
-
-\section{Equal-Time Ground State Correlators}\label{staticCorr}
-Properties of the ground state can be probed using static correlation functions that are expectation values of operators that propagate excitations.
-We will consider general correlations, in real and momentum space.
-\subsection{Real-space correlation functions}
-We first consider a real-space operator \(\mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r})\) that quantifies the presence of correlations over a distance \({\bf \Delta}\).
-The correlation function itself is given by the expectation value of this operator in the ground state:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_1 + {\bf r}^\prime + {\bf r}_c + {\bf r}\right)  | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_1 + {\bf r}_c + {\bf r}\right)} e^{-i{\bf k}_0\cdot\left({\bf r}_1 - {\bf r}_2\right)}~,
-\end{aligned}\end{equation}
-where \({\bf r}_1\) and \({\bf r}_1 + {\bf r}^\prime\) are the positions of the incoming and outgoing auxiliary model states, relative to \({\bf r}_c + {\bf r}\), and \({\bf k}_0\) is the crystal momentum of the ground state (which we will immediately set to zero).
-In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
-Substituting this appropriately for both the auxiliary model states gives:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_1 + {\bf r}^\prime + {\bf r}\right) \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) T^\dagger\left({\bf r}_1 + {\bf r}\right) | \psi_\text{gs}\left({\bf r}_c\right)}\\
-								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}^\prime\right) \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
-								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-As a final cosmetic change, we transform \({\bf r}_1 \to -{\bf r}\):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r},{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-Like in the Greens function calculation, we now consider the various kinds of contributions separately.
-
-\subsubsection{Intra-auxiliary model contributions: \({\bf r}^\prime = 0\)}
-These terms describe excitations that start and propagate within the same auxiliary model, upto a distance \({\bf \Delta}\):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-With an eye towards introducing the impurity operators into the correlations, we insert a complete basis defined by the eigenstates \(\left\{\ket{\psi_n\left({\bf r}_c\right)}\right\} \) of the auxiliary model into the expression:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\sum_{n}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \ket{\psi_n\left({\bf r}_c\right)}\bra{\psi_n\left({\bf r}_c\right)} \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-
-For the excitations that exist purely in the conduction bath \(({\bf r} \neq {\bf r}_c)\), the excitation operators must be suitably modified (see the arguments around eq.~\ref{tmatrix}) in order to incorporate Kondo screening.
-The modified excitation operators are generally defined as
-\begin{equation}\begin{aligned}\label{operatorTmatrix}
-	\mathcal{\tilde O}({\bf r}) = \mathcal{O}({\bf r})\mathcal{O}^\dagger(d) \mathcal{P}_\text{gs} ~,
-\end{aligned}\end{equation}
-where \(\mathcal{O}^\dagger(d)\) is the hermitian conjugate of the correlation operator \(\mathcal{O}\), but applied on the impurity sites.
-This therefore constitutes a time-reversed scattering process on the impurity site relative to the process in the bath.
-The operator \(\mathcal{P}_\text{gs}\) projects onto the ground state of the auxiliary model, since we are interested in ground state correlations.
-The operator multiplying the old correlation operator represents all possible excitations of the impurity site, and ensure that the bath and impurity excitation processes take place in correlation.
-The projector ensures that only tripartite correlations between the impurity site and the two momentum states are captured by the correlation, which is what's desired within the tiling method.
-
-With this modified operator, this class of correlation functions can be written as
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r} }\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-This can be interpreted as the fact that within our auxiliary model formalism, the correlation between the sites \({\bf r}\) and \({\bf \Delta + r}\) can only occur through a transition process that connect one of the sites with the impurity site and then a return process that connects the impurity site with the other site.
-
-\subsubsection{Inter-auxiliary model contributions: \({\bf r}^\prime \neq 0\)}
-These are the most non-local contributions, and involve excitations that connect different auxiliary models:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}^\prime \neq 0}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-
-\subsection{Momentum-space correlation functions}
-We now consider momentum space correlations, through a general operator \(\mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1)\):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-Note that \(\mathcal{O}\) itself is a two-particle operator.
-To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_2\right)  | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_1\right)}~,
-\end{aligned}\end{equation}
-where \({\bf r}_1\) and \({\bf r}_2 \) are the positions of the incoming and outgoing auxiliary model states.
-In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
-Substituting this appropriately for both the auxiliary model states gives:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_c\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) T^\dagger\left({\bf r}_1 - {\bf r}_c\right) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-In order to simplify the translation operators, we can use eq.~\ref{translationOnField}.
-For that, we would need to know whether the operator \(\mathcal{O}\) involves the net transfer of momentum.
-If \(\mathcal{O}({\bf k})\) commutes with the total number operator \(n_{\bf k} = \sum_\sigma n_{{\bf k},\sigma}\), there is no momentum transfer.
-Examples of such operators are spin operators, \(S_{\alpha\beta}({\bf k}) \equiv c^\dagger_{{\bf k \alpha}}c_{{\bf k}\beta}\), and density operators \(n_{{\bf k}\alpha}\).
-If \(\mathcal{O}({\bf k})\) does not commute with \(n_{\bf k}\), there is a net transfer of momentum, and one such operator would be the charge isospin operator \(C^+({\bf k}) = c^\dagger_{{\bf k}\uparrow}c^\dagger_{{\bf k}\downarrow}\).
-For the first kind of operators, we have \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = \mathcal{O}({\bf k})\), while the for the latter, we get \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = e^{-{\bf a}\cdot{\bf 2k}}\mathcal{O}({\bf k})\), where \(2{\bf k}\) represents the momentum being transferred by the operator.
-We consider the two cases separately.
-
-\subsubsection{Momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] = 0\)}
-For these operators, the expression for the correlation gives
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
-										 &=\sum_{{\bf r},{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-To obtain the last form, we defined \({\bf \Delta}={\bf r}_2 - {\bf r}_1\) as the distance between the incoming and outgoing auxiliary model states, and preformed the sum over the free variable \({\bf r}_1\) to cancel out the factor of \(1/N\).
-Just like before, this expression can be decomposed into a term that involves a single auxiliary model and other terms that involve two distinct auxiliary models.
-
-\subsubsection{Non-momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] \neq 0\)}
-This class of operators incur an additional phase factor of \(e^{-{\bf a}\cdot{\bf 2k}}\) when the translation operators are translated across them:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}e^{2i\left( {\bf r}_1 - {\bf r}_c \right) \cdot \left( {\bf k}_1 - {\bf k}_2 \right)} \\
-										 &= \delta_{{\bf k}_1, {\bf k}_2}\sum_{{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-For this expression, we again defined \({\bf \Delta}\) similar to before, and carried out the sum of \({\bf r}_1\) involving the exponential to obtain a factor of \(N \delta_{{\bf k}_1, {\bf k}_2}\).
-The Kronecker delta factor is a manifestation of translational invariance and the associated total momentum conservation.
-
-As it stands, operators like \(\mathcal{O}({\bf k}_1)\) act purely on the conduction bath degrees of freedom.
-In order to incorporate impurity-bath correlation effects, we modify these operators using the appropriate \(T-\)matrices, by employing eq.~\ref{operatorTmatrix}.
-The final computations are carried out using these modified operators.
-
-\section{Entanglement}
-We will now describe the prescription of calculating entanglement measures of the lattice model from within our auxiliary model treatment.
-In this section, we are interested mainly in two such measures, the entanglement entropy and the mutual information.
-Given a pure state \(\ket{\Psi}\) describing the complete system, the entanglement entropy \(S_\text{EE}(\nu)\) of a subsystem \(\nu\) quantifies the entanglement of \(\nu\) with the rest of the subsystem, and is defined as
-\begin{equation}\begin{aligned}
-	S_\text{EE}(\nu) = -\text{Tr}\left[\rho(\nu)\log \rho(\nu)\right],\quad \rho(\nu) = \text{Tr}_\nu\left[\ket{\Psi}\bra{\Psi}\right] 
-\end{aligned}\end{equation}
-where \(\text{Tr}\left[\cdot\right] \) is the trace operator, and \(\rho(\nu)\) is the reduced density matrix for the subsystem \(\nu\) obtained by taking the partial trace \(\text{Tr}_\nu\) (over the states of \(\nu\)) of the full density matrix \(\rho = \ket{\Psi}\bra{\Psi}\).
-If the subsystem \(\nu\) describes local regions in real space (or states in \(k-\)space), we might be interested in the entanglement between two such subsystems \(\nu_1\) and \(\nu_2\).
-The correct measure to quantify such entanglement is the mutual information:
-\begin{equation}\begin{aligned}
-	I_2(\nu_1,\nu_2) = S_\text{EE}(\nu_1) + S_\text{EE}(\nu_2) - S_\text{EE}(\nu_1 \cup \nu_2)~,
-\end{aligned}\end{equation}
-where \(\nu_1 \cup \nu_2\) is a larger subsystem formed by combining \(\nu_1\) and \(\nu_2\).
-
-\subsection{Real-space entanglement}
-Real-space entanglement measures can be used to probe delocalisation-localisation transitions.
-The simplest such measure is the entanglement of a local mode.
-Since the local entanglement entropy will be uniform at each lattice site for a system with translation invariance, it suffices to calculate the real-space averaged entanglement entropy \(S_\text{EE}^\text{loc} = \frac{1}{N}\sum_{{\bf r}}S_\text{EE}\left( {\bf r} \right) \).
-By visualising the lattice model as a superposition of auxiliary models placed at various sites (eq.~\ref{tilingPrescriptionFinal}), the real space average of the lattice model can be thought of as an average over sites of a particular impurity model, and then a second average over all the impurity models.
-But since all all impurity models are equivalent to each other, the second average is redundant.
-Secondly, all correlations must derive from the impurity site, which can be formally encoded by subtracting, from this average, the corresponding contribution obtained in the absence of the impurity site.
-In total, the lattice-auxiliary model relation for the local entanglement entropy can be written as
-\begin{equation}\begin{aligned}
-	S_\text{EE}^\text{loc} = \frac{1}{N}\sum_{{\bf r}}\left[S_\text{EE}({\bf r}_d + {\bf r}) - S_\text{EE}^{(0)}({\bf r}_d + {\bf r})\right] ~,
-\end{aligned}\end{equation}
-where \({\bf r}_d\) is the impurity site position, \({\bf r}\) is the distance of a conduction bath site from the impurity site (can be zero), and \(S_\text{EE}({\bf r}_d + {\bf r})\) is the entanglement entropy, calculated within the impurity model, at the locatiom \({\bf r}_d + {\bf r}\).
-\(S^{(0)}_\text{EE}({\bf r}_d + {\bf r})\) is the same entanglement entropy, but calculated for an impurity model but with vanishing impurity-bath hybridisation and bath interaction.
-
-\subsection{Momentum-space entanglement}
-Entanglement measures in \(k-\)space can provide valuable information regarding the Fermi surface structure and the nature of gapless excitations proximate to it.
-The most elementary measure is the entanglement entropy \(S_\text{EE}({\bf q})\) of a single excitation carrying momentum \({\bf q}\).
-Unlike \(S_\text{EE}^\text{loc}\), this does not involve an average, and involves a single computation:
-\begin{equation}\begin{aligned}
-	S_\text{EE}^\text{loc} = S_\text{EE}({\bf q}) - S_\text{EE}^{(0)}({\bf q})~.
-\end{aligned}\end{equation}
-It is possible to improve this by considering inter-auxiliary model contributions in the reduced density matrix \(\rho({\bf q})\). On the lattice model, \(\rho({\bf q})\) is defined as
-\begin{equation}\begin{aligned}\label{SEE-k}
-	\rho({\bf q}) = \text{Tr}_{\bf q}\left[\ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\right] ~,
-\end{aligned}\end{equation}
-where \(\text{Tr}_{\bf q}\left[\cdot\right]\) is the partial trace over the Hilbert space of \({\bf q}\), and \(\ket{\Psi_\text{gs}}\) is the tiled ground state.
-Using eq.~\ref{groundstateProposal}, we can write the ground state in terms of those of the auxiliary model.
-These leads to two classes of terms, one purely within a single auxiliary model ground state \(\ket{\psi_\text{gs}}\), and the other involving transitions across auxiliary models:
-\begin{equation}\begin{aligned}
-	\rho({\bf q}) = \text{Tr}_{\bf q}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d)}\right] + \frac{1}{N}\text{Tr}_{\bf q}\sum_{{\bf r}}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d + {\bf r})}\right]~,
-\end{aligned}\end{equation}
-where \(\ket{\psi_\text{gs}({\bf r}_d)}\) is a reference auxiliary model ground state, and \(\ket{\psi_\text{gs}({\bf r}_d + {\bf r})}\) sums over other auxiliary models at increasing distances from this reference model.
-The first term leads to the expression in eq.~\ref{SEE-k}, while the second term can be used to improve this estimate.
-Away from any quantum critical points, the localised nature of the impurity-bath hybridisation ensures that impurity correlations decay exponentially away from the transition.
-This ensures that the second term is very small away from a critical point.
-We therefore restrict ourselves to just the first term in the present work.
-
-\section{Journey Through the Pseudogap on The Lattice model}
-We have already seen from the lattice-embedded impurity model that the impurity phase transition is anisotropic in \(k-\)space.
-This has consequences for the metal-insulator transition of the lattice model.
-We now describe, in terms of correlations, how the Fermi surface of the lattice model is destabilised when the system is tuned through the pseudogap.
-For this, we employ the relations we derived between correlations on the impurity model and those on the lattice model.
+\section{Journey Through the Pseudogap on The Lattice model: Spectral Function, Spin Correlations and Entanglement}
+Having studied the phase diagram of the lattice-embdedded impurity model, we now proceed to translate our results into the translation-invariant lattice model.
+For this, we use the results that we obtained in Sec.~\ref{tilingProcedure}.
+In particular, we focus in this section on the implications of the impurity model pseudogap phase on the lattice model.
+We find that the anistropic decoupling, from the impurity dynamics, of the conduction bath low-energy states leads to the formation of a partially gapped Fermi surface in the correlated model.
+The partial gapping is signalled by the replacement of Greens function poles with zeroes in the antinodal region.
 
 \subsection{\(k-\)space spectral function and self-energy}
-The primary indicator of the pseudogapping nature of the transition is of course the \(k-\)space density of states or the spectral function, shown in Fig.~\ref{tiledSpecFunc}.
-For \(W=0\), all points on the Fermi surface are gapless.
-As we enter the pseudogap, the region around the antinodes lose all spectral weight and become gapped.
-Increasing the value of \(W\) further leads to the enlargement of the gapped region; exactly at the transition, we end up with a singular Fermi surface composed of just the nodal points.
-
-This is also supported by our computations of the \(k-\)space self-energy.
-We show the zero frequency value of the \(k-\)space self-energy in Fig.~\ref{selfenergy}.
-This is computed from using Dyson's equation \(\Sigma_k = 1/G_k^{(0)} - 1/G_k\), where \(G_k\) is the interacting \(k-\)space Greens function while \(G_k^{(0)}\) is the non-interacting \(W=0\) Greens function.
-We find that the beginning of the pseudogap is marked by poles in the self-energy at the antinodal points; at the transition, only the nodes display vanishing self-energy at zero frequency.
+The primary indicator of the pseudogapping nature of the transition is of course the \(k-\)space density of states or the spectral function \(\tilde A_{\bf k}(\omega)\).
+We calculate \(\tilde A_{\bf k}(\omega)\) from the impurity-bath spectral function computations carried out for the impurity model, using the following expression that was obtained previously (eq.~\ref{kspaceGreensFunction}):
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; \omega) = G^>(\mathcal{T}^\dagger_{{\bf K}\sigma}, \omega - \varepsilon_{{\bf K}}) + G^<(\mathcal{T}^\dagger_{{\bf K}\sigma}, \omega + \varepsilon_{{\bf K}})~,
+\end{aligned}\end{equation}
+where \(\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\left(\sum_{\sigma^\prime}c^\dagger_{d\sigma} + \text{h.c.}\right) + c_{{\bf K}\sigma}\left(S_d^+ + \text{h.c.}\right)\) was defined in eq.~\ref{tmatrix}, and \(G^>(\mathcal{O}^\dagger, t) = -i\braket{\mathcal{O}(t)\mathcal{O}^\dagger}\) and \(G^<(\mathcal{O}^\dagger, t) = -i\braket{\mathcal{O}^\dagger\mathcal{O}(t)}\) are the greater and lesser Greens function for the auxiliary model, and \(\varepsilon_{{\bf K}}\) is the excitation energy associated with the momentum state \({\bf K}\), as determined by the dispersion on the lattice.
+In order to determine the low-energy behaviour in \(k-\)space, the zero frequency value \(\tilde A_{\bf k}(\omega \simeq 0)\) of the spectral function on the Fermi surface points is shown in Fig.~\ref{tiledSpecFunc} for various values of \(W/J\).
+
+We find that the Fermi surface remains completely gapless (seen through large non-zero values at zero frequency) for small values of \(W\) (first plot).
+However, if \(W\) is made sufficiently large, a partial gap opens up on the Fermi surface, starting from the antinode.
+Increasing the value of \(W/J\) leads to enlargement of the gapped region; exactly at the transition, we end up with a singular Fermi surface composed of just the nodal points.
+
+In order to better understand the nature of the metal in the partially gapped region, we have also calculated the \(k-\)space self-energy \(\tilde \Sigma({\bf k}(\omega)\), using Dyson's equation:
+\begin{equation}\begin{aligned}
+	\tilde \Sigma({\bf k}(\omega) = 1/\tilde G^{(0)}_{\bf k}(\omega) - 1/\tilde G_{\bf k}(\omega)~,
+\end{aligned}\end{equation}
+where \(\tilde G_k\) is the interacting \(k-\)space Greens function (whose spectral function is shown in Fig.~\ref{tiledSpecFunc}) while \(\tilde G_k^{(0)}\) is the non-interacting \(W=0\) Greens function.
+We show the zero frequency value of the self-energy in Fig.~\ref{selfenergy}, and the partial gapping of the Fermi surface is seen to arise from the appearance of poles in the self-energy at the antinodal region.
+As the partial gap expands, more and more \(k-\)space points exhibit poles in their self-energy.
+This, along with the behaviour of the spectral function, indicates that in the pseudogap region, the disconnected Fermi surface coexists with a Luttinger surface.
 \begin{figure}[htpb]
@@
 \subsection{Momentum-space spin-correlations}
-We first look at static spin correlations \(\chi_s(k_1, k_2) = \frac{1}{2}\left<S_{k_1}^+ S_{k_2}^- + \text{h.c.} \right>\).
-These processes correspond to the gapless excitations of the Fermi liquid phase.
-We find that
+To gain more insight on the nature of the fluctuations in various phases, we study the spin-spin correlation, \(\tilde \chi_s({\bf k}_1, {\bf k}_2) = \frac{1}{2}\left<{\boldsymbol S}_{{\bf k}_1}\cdot {\boldsymbol S}_{{\bf k}_2}\right>\), where \({\bf S}({\bf k}) = \sum_{\alpha\beta}c^\dagger_{{\bf k}\alpha}{\boldsymbol \sigma}_{\alpha \beta}c_{{\bf k}\beta}\).
+These correlations are again obtained from computations within the auxiliary model, using the relation obtained in eq.~\ref{kspaceCorrelation}.
+While the full expression contains contributions from various combinations of auxiliary models, in the present work we focus on the intra-auxiliary model contribution which is the largest term:
+\begin{equation}\begin{aligned}
+	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}({\bf k}_2) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
+\end{aligned}\end{equation}
+The results for Fermi surface points are shown in Fig.~\ref{tiledSF}.
+We find that at small values of the bath interaction (first plot from left), the spin correlations are spread out uniformly on the Fermi surface, and are quite small in magnitude.
+This is likely because of the weakly correlated nature of the Fermi liquid.
+As we enter the pseudogap (second plot from left and beyond), the spin correlations of the antinodal region vanish.
+Along with the divergence of self-energy observed along the same points, this indicates that the antinodal region no longer participates in scattering processes that can renormalise the metal.
+The nodal region, however, sees an enhancement of spin correlations, particularly in it's neighbourhood.
+This is a sign that the metallic excitations are becoming highly correlated through the pseudogap.
+
 \begin{figure}[htpb]
@@
 	\includegraphics[width=0.24\textwidth]{tiledSF-4.pdf}
-	\caption{Spin-flip correlations \(\left<S(k_N)^+, S({\bf k})^-\right>\) between the nodal point \(k_N = \left( -\pi/2, -\pi/2\right)\) and an arbitrary \(k-\)point on the Fermi surface.
-In the absence of bath interaction (first panel), the correlations are somewhat uniformly distributed along the Fermi surface.
-As we enter the pseudogap (second panel), the spin-correlations near the antinode vanish, indicating that they have been removed from the metallic excitations.
-Passing through the pseudogap involves in the extensions of the gapped region (third panel), until finally only the node remains (fourth panel).}
+	\caption{Spin-spin correlations \(\chi_s\) (defined in main text) between the nodal point \(k_N = \left( -\pi/2, -\pi/2\right)\) and an arbitrary \(k-\)point on the Fermi surface.
+In the absence of bath interaction (first panel), the correlations are somewhat uniformly distributed along the Fermi surface, and quite small.
+This describes the Fermi liquid phase of the lattice model.
+As we enter the pseudogap (second panel and beyond), the spin-correlations near the antinode vanish, indicating that they have been removed from the metallic excitations, while the correlations near the nodal point become enhanced because of the increasingly correlated nature of the metal.}
 	\label{tiledSF}
@@
 \subsection{Entanglement entropy and Mutual information}
+We have also used our method to study the \(k-\)space entanglement entropy and mutual information within the lattice model, in order to probe the transition and the pseudogap.
+Given a pure state \(\ket{\Psi}\) describing the complete system, the entanglement entropy \(S_\text{EE}(\nu)\) of a subsystem \(\nu\) quantifies the entanglement of \(\nu\) with the rest of the subsystem, and is defined as
+\begin{equation}\begin{aligned}
+	S_\text{EE}(\nu) = -\text{Tr}\left[\rho(\nu)\log \rho(\nu)\right],\quad \rho(\nu) = \text{Tr}_\nu\left[\ket{\Psi}\bra{\Psi}\right] 
+\end{aligned}\end{equation}
+where \(\text{Tr}\left[\cdot\right] \) is the trace operator, and \(\rho(\nu)\) is the reduced density matrix (RDM) for the subsystem \(\nu\) obtained by taking the partial trace \(\text{Tr}_\nu\) (over the states of \(\nu\)) of the full density matrix \(\rho = \ket{\Psi}\bra{\Psi}\).
+If the subsystem \(\nu\) describes local regions in real space (or states in \(k-\)space), we might be interested in the entanglement between two such subsystems \(\nu_1\) and \(\nu_2\).
+The correct measure to quantify such entanglement is the mutual information:
+\begin{equation}\begin{aligned}
+	I_2(\nu_1,\nu_2) = S_\text{EE}(\nu_1) + S_\text{EE}(\nu_2) - S_\text{EE}(\nu_1 \cup \nu_2)~,
+\end{aligned}\end{equation}
+where \(\nu_1 \cup \nu_2\) is a larger subsystem formed by combining \(\nu_1\) and \(\nu_2\).
+
+We have already shown how to obtain the RDM for a \(k-\)state from our approach, in eq.~\ref{RDMTiled}:
+\begin{equation}\begin{aligned}
+	\tilde \rho({\bf k}) \sim \text{Tr}_{\bf k}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d)}\right] + \frac{1}{N}\text{Tr}_{\bf k}\sum_{{\bf r}}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d + {\bf r})}\right]~,
+\end{aligned}\end{equation}
+where \(\ket{\psi_\text{gs}({\bf r}_d)}\) is a reference auxiliary model ground state, and \(\ket{\psi_\text{gs}({\bf r}_d + {\bf r})}\) sums over other auxiliary models at increasing distances from this reference model.
+The \(\sim\) indicates that the RDM needs to be normalised.
+In the present work, we have restricted our results to the intra-auxiliary model contribution (first term).
+We show, in Fig.~\ref{tiledEntanglement}, the results of entanglement calculations on the Fermi surface.
+The entanglement entropy distribution (top panel) in \(k-\)space shows how the partial gapping leads to the elimination of the antinodal \(k-\)modes from the ground state and excitations and the consequent vanishing of their entanglement.
+We also plot, in the lower panel, the mutual information between (i) an arbitrary \(k-\)state and the nodal point, and (ii) an arbitrary \(k-\)state and the edge of the disconnected Fermi surface in the pseudogap.
+While the nodal point is seen to remain somewhat strongly entangled with the other Fermi surface points, the edge of the ``Fermi arc" has minimal entanglement until the system comes close to the critical point.
+
 \begin{figure}[htpb]
@@
 	\includegraphics[width=0.24\textwidth]{tiled_SEE_k-4.pdf}
-\end{figure}
-\begin{figure}[htpb]
-	\centering
+
 	\includegraphics[width=0.24\textwidth]{tiled_I2_k_N-1.pdf}
 	\includegraphics[width=0.24\textwidth]{tiled_I2_k_N-2.pdf}
-	\includegraphics[width=0.24\textwidth]{tiled_I2_k_N-3.pdf}
-\end{figure}
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.24\textwidth]{tiled_I2_k_edge-1.pdf}
 	\includegraphics[width=0.24\textwidth]{tiled_I2_k_edge-2.pdf}
 	\includegraphics[width=0.24\textwidth]{tiled_I2_k_edge-3.pdf}
+	\caption{Top panel: Entanglement entropy \(S_\text{EE}({\bf k})\) on the Fermi surface.
+Similar to the correlations, the entanglement in the \(W=0\) model remains uniformly spread out over the Fermi surface.
+As the Fermi surface progressively shrinks, the entanglement gets concentrated to the nodal points.
+Bottom panel: Mutual information \(I_2\) between (i) an arbitrary \(k-\)state and the nodal point (first and second plots), and (ii) an arbitrary \(k-\)state and the edge of the disconnected Fermi surface in the pseudogap (third and fourth plots).
+The ends of the partial Fermi surface appear to be weakly entangled to the rest of the Fermi surface, while the nodal points remain strongly entangled all the way through to the transition.}
+	\label{tiledEntanglement}
 \end{figure}
+
+\section{Nature of Low-Energy Excitations in Various Regimes}
+\subsection{Metallic Regime}
+\paragraph{Fermi liquid excitations, \(|W| < |W|^*\):}
+As discussed in Sec.~\ref{2CKEmerge}, the effective description of the impurity model for \(|W| > |W|^*\) becomes that of a 2CK.
+Prior to that (\(|W| < |W|^*\)), the entire Fermi surface continues to screen the impurity, and this leads to local Fermi liquid description of the impurity excitations.
+Using our translation operator prescription for mapping an impurity model to a lattice model (eq.~\ref{tilingPrescription}), these local Fermi liquid excitations arising from each auxiliary model coherently combine to create extended Fermi liquid excitations in the lattice model.
+This is therefore the nature of the metal for \(|W| < |W|^*\), and further support for this is found from the non-zero values of the quasiparticle residue in this regime (right panel of Fig.~\ref{channelDecoupling}).
+
+\paragraph{Marginal Fermi liquid, \(|W| > |W|^*\):}
+We have demonstrated in Subsection.~\ref{marginalFL} that the low-lying excitations of the pseudogap phase are described by a marginal Fermi liquid.
+This is linked to the fact that the excitations within the impurity model become many-particle in nature - they involve fluctuations on multiple sites.
+This should be contrasted with the local Fermi liquid excitations that involve only the conduction bath site next to the zeroth site.
+Upon tiling, we can immediately see that the resulting metal is not a Fermi liquid; the extended excitations will involve excitations of multiple \(k-\)states, and just not a simple superposition of \(1-\)particle excitations (that gave rise to the Fermi liquid).
+The build up of additional correlations within the marginal Fermi liquid (in comparison to the Fermi liquid) can also be ascertained from the fact that the local physics is determined by an impurity model which is highly local in \(k-\)space (due to the decoupling of the Fermi arms, see Sec.~\ref{2CKEmerge}).
+Such a local-in-\(k-\)space impurity model is highly non-local in real-space, consisting of long-ranged interactions between the impurity and the conduction bath.
+This is another signature of the non-Fermi liquid nature of the excitations obtained upon tiling.
+
+\paragraph{At the critical point}
 
@@
 \begin{equation}\begin{aligned}
-	\ket{\Psi_L} = \left\{\ket{\sigma_1,\sigma_2}\right\}~,\quad \sigma_i = \pm 1
+	\ket{\Psi_L} = \left\{\ket{\sigma_1,\sigma_2}\right\}~,\quad \sigma_i = \pm 1~,
 \end{aligned}\end{equation}
@@
 
-\section{Topological nature of the transition}
-Since the impurity charge hybridising with the bath contributes to the total Luttinger volume of the system~\cite{martin1982fermi}, decoupling of the impurity from the conduction bath leads to a difference in the value of the Luttinger volume between the local moment (LM) and the strong-coupling (SC) fixed points.
+% \section{Topological nature of the transition}
+% Since the impurity charge hybridising with the bath contributes to the total Luttinger volume of the system~\cite{martin1982fermi}, decoupling of the impurity from the conduction bath leads to a difference in the value of the Luttinger volume between the local moment (LM) and the strong-coupling (SC) fixed points.
 If we define \(\mathcal{N}_L\) as the Luttinger volume with the spin-degeneracy accounted for, we can write
-\begin{equation}\begin{aligned}
-	\label{lutt_change}
-	\mathcal{N}_L^\text{lm} - \mathcal{N}_L^\text{sc} = 1
-\end{aligned}\end{equation}
-where \(\mathcal{N}_L^\text{lm},\mathcal{N}_L^\text{sc}\) are the Luttinger volumes at the local moment and strong-coupling fixed points respectively.
+% \begin{equation}\begin{aligned}
+% 	\label{lutt_change}
+% 	\mathcal{N}_L^\text{lm} - \mathcal{N}_L^\text{sc} = 1
+% \end{aligned}\end{equation}
+% where \(\mathcal{N}_L^\text{lm},\mathcal{N}_L^\text{sc}\) are the Luttinger volumes at the local moment and strong-coupling fixed points respectively.
 This equation expresses the fact that the Luttinger volume of the bath increases by \(1\) when the system is tuned from LM to SC, and this happens because the single-particle impurity excitation in the lower-Hubbard at the atomic limit gets transferred to the bath Greens function in the process.
 The quantity which tracks this transfer is therefore \(\mathcal{N}_\text{imp}\), the number of poles minus the number of zeros in the impurity Greens function at and below the Fermi surface:
-\begin{equation}\begin{aligned}
-	\label{imp_count_def}
-	\mathcal{N}_\text{imp} = \begin{cases}
-		1 & \text{ at LM}\\
-		0 & \text{ at SC}
-	\end{cases}\implies \Delta \mathcal{N}_\text{imp} = 1
-\end{aligned}\end{equation}
-The Luttinger volume \(\mathcal{N}_L\) is related to this impurity count by the equation
-\begin{equation}\begin{aligned}
-	\mathcal{N}_L = \mathcal{N} - \mathcal{N}_\text{imp}
-\end{aligned}\end{equation}
-where \(\mathcal{N}\) is the total number of electrons in the system, accounting for the spin degeneracy.
+% \begin{equation}\begin{aligned}
+% 	\label{imp_count_def}
+% 	\mathcal{N}_\text{imp} = \begin{cases}
+% 		1 & \text{ at LM}\\
+% 		0 & \text{ at SC}
+% 	\end{cases}\implies \Delta \mathcal{N}_\text{imp} = 1
+% \end{aligned}\end{equation}
+% The Luttinger volume \(\mathcal{N}_L\) is related to this impurity count by the equation
+% \begin{equation}\begin{aligned}
+% 	\mathcal{N}_L = \mathcal{N} - \mathcal{N}_\text{imp}
+% \end{aligned}\end{equation}
+% where \(\mathcal{N}\) is the total number of electrons in the system, accounting for the spin degeneracy.
 If we keep this total number fixed (isolated system), the changes in the impurity count and Luttinger volume become constrained:
-\begin{equation}\begin{aligned}
-	\Delta \mathcal{N}_L = - \Delta \mathcal{N}_\text{imp}~.
-\end{aligned}\end{equation}
-Eq.~\ref{imp_count_def} then readily implies eq.~\ref{lutt_change}.
-
-In order to connect this impurity topological change with the bulk model, we write the total number of particles in the bulk system in the following manner:
-\begin{equation}\begin{aligned}
-	\mathcal{N} = \mathcal{N}_\text{loc} + \mathcal{N}_\text{deloc}
-\end{aligned}\end{equation}
-\(\mathcal{N}_\text{loc}\) is the number of real poles minus the number of zeros of the local Greens function.
+% \begin{equation}\begin{aligned}
+% 	\Delta \mathcal{N}_L = - \Delta \mathcal{N}_\text{imp}~.
+% \end{aligned}\end{equation}
+% Eq.~\ref{imp_count_def} then readily implies eq.~\ref{lutt_change}.
+%
+% In order to connect this impurity topological change with the bulk model, we write the total number of particles in the bulk system in the following manner:
+% \begin{equation}\begin{aligned}
+% 	\mathcal{N} = \mathcal{N}_\text{loc} + \mathcal{N}_\text{deloc}
+% \end{aligned}\end{equation}
+% \(\mathcal{N}_\text{loc}\) is the number of real poles minus the number of zeros of the local Greens function.
 \(\mathcal{N}_\text{deloc}\) is the number of real poles minus the number of zeros of the \(k-\)space Greens functions.
@@
 These two terms are defined as
-\begin{equation}\begin{aligned}
-	\mathcal{N}_\text{loc} = \sum_i \mathcal{N}_i = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_i(z)\right], ~ ~ ~\mathcal{N}_\text{deloc} = \sum_k \mathcal{N}_k = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_k(z)\right] = \mathcal{N}_L
-\end{aligned}\end{equation}
-\(G_i(z)\) is the local Greens function at site \(i\) of the bulk model, and \(G_k(z)\) is the \(k-\)space Greens function in the bulk model.
+% \begin{equation}\begin{aligned}
+% 	\mathcal{N}_\text{loc} = \sum_i \mathcal{N}_i = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_i(z)\right], ~ ~ ~\mathcal{N}_\text{deloc} = \sum_k \mathcal{N}_k = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_k(z)\right] = \mathcal{N}_L
+% \end{aligned}\end{equation}
+% \(G_i(z)\) is the local Greens function at site \(i\) of the bulk model, and \(G_k(z)\) is the \(k-\)space Greens function in the bulk model.
 \(N_\text{deloc}\) is just the Luttinger volume \(\mathcal{N}_L\) of the bulk system.
 With this, the total number of particles in the bulk can be expressed as
-\begin{equation}\begin{aligned}
-	\label{bulk_total}
-	\mathcal{N} = \sum_i \mathcal{N}_i + \mathcal{N}_\text{L}
-\end{aligned}\end{equation}
-From eq.~\ref{greens_func_relation}, we know that the bulk local Greens function is proportional to that of the auxiliary model, and that gives \(\sum_i \mathcal{N}_i = \mathcal{N}_\text{imp}\sum_i = \mathcal{N} \mathcal{N}_\text{imp}\).
+% \begin{equation}\begin{aligned}
+% 	\label{bulk_total}
+% 	\mathcal{N} = \sum_i \mathcal{N}_i + \mathcal{N}_\text{L}
+% \end{aligned}\end{equation}
+% From eq.~\ref{greens_func_relation}, we know that the bulk local Greens function is proportional to that of the auxiliary model, and that gives \(\sum_i \mathcal{N}_i = \mathcal{N}_\text{imp}\sum_i = \mathcal{N} \mathcal{N}_\text{imp}\).
 There we used the fact that for a half-filled system, the total number of sites is equal to the total number of particles in the system.
 Substituting this into eq.~\ref{bulk_total} and again using \(\Delta \mathcal{N} = 0\) gives
-\begin{equation}\begin{aligned}
-	\mathcal{N} = \mathcal{N} \mathcal{N}_\text{imp} + \mathcal{N}_\text{L} \implies \Delta \mathcal{N}_\text{L} = - \mathcal{N} \Delta \mathcal{N}_\text{imp}
-\end{aligned}\end{equation}
-We already know that \(\Delta \mathcal{N}_\text{imp}=1\) across the transition, so we get
-\begin{equation}\begin{aligned}
-	\mathcal{N}_L^\text{metal} - \mathcal{N}_L^\text{insulator} = \mathcal{N}\left(\mathcal{N}_\text{imp}^\text{sc} - \mathcal{N}_\text{imp}^\text{lm}\right) = \mathcal{N}
-\end{aligned}\end{equation}
-The metal-insulator transition is therefore characterised by a change in the topological quantity \(\mathcal{N}_L\).
+% \begin{equation}\begin{aligned}
+% 	\mathcal{N} = \mathcal{N} \mathcal{N}_\text{imp} + \mathcal{N}_\text{L} \implies \Delta \mathcal{N}_\text{L} = - \mathcal{N} \Delta \mathcal{N}_\text{imp}
+% \end{aligned}\end{equation}
+% We already know that \(\Delta \mathcal{N}_\text{imp}=1\) across the transition, so we get
+% \begin{equation}\begin{aligned}
+% 	\mathcal{N}_L^\text{metal} - \mathcal{N}_L^\text{insulator} = \mathcal{N}\left(\mathcal{N}_\text{imp}^\text{sc} - \mathcal{N}_\text{imp}^\text{lm}\right) = \mathcal{N}
+% \end{aligned}\end{equation}
+% The metal-insulator transition is therefore characterised by a change in the topological quantity \(\mathcal{N}_L\).
 The topological nature arises from the fact that it can be expressed in terms of winding numbers related to the corresponding Greens functions.
@@
 An example of such a winding number is shown in fig.~\ref{imp_winding}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.4\textwidth]{windingNumbers.pdf}
-	\caption{The green lines describe the winding number related to the impurity Greens function, while the blue lines do it for the bath.
+% \begin{figure}[!htb]
+% 	\centering
+% 	\includegraphics[width=0.4\textwidth]{windingNumbers.pdf}
+% 	\caption{The green lines describe the winding number related to the impurity Greens function, while the blue lines do it for the bath.
 At the local moment fixed point \(V=0\), the impurity has a winding number of 1 because the curve encircles the origin once.
@@
 The reduction in the winding number on the part of the impurity is directly linked to the increase in the winding number of the bath - it encircles the origin once at the local moment fixed point but twice at strong-coupling.}
-	\label{imp_winding}
-\end{figure}
+% 	\label{imp_winding}
+% \end{figure}
 

### 2025-04-04 numerics/caller.jl
finalised algorithm for charge correlations

@@ -1,8 +1,8 @@
-using Distributed, Random
+using Distributed, Random, ProgressMeter
 
-#=if length(Sys.cpu_info()) > 10 && nprocs() == 1=#
-#=    addprocs(2)=#
-#=end=#
+if length(Sys.cpu_info()) > 10 && nprocs() == 1
+    addprocs(1)
+end
 @everywhere using LinearAlgebra, CSV, JLD2, FileIO, CodecZlib
 
 @everywhere include("./source/constants.jl")
@@ -16,9 +16,10 @@ global J_val = 0.1
 maxSize = 500
 WmaxSize = 500
 
-colmap = ColorSchemes.thermal # ColorSchemes.thermal # reverse(ColorSchemes.cherry)
+colmap = [ColorSchemes.thermal, ColorSchemes.cherry[1:end-1]][2]
+phasesColmap = reverse(ColorSchemes.cherry)
 numShells = 1
-bathIntLegs = 2
+bathIntLegs = 3
 NiceValues(size_BZ) = Dict{Int64, Vector{Float64}}(
                          13 => -1.0 .* [0., 1., 1.5, 1.55, 1.6, 1.61] ./ size_BZ,
                          25 => -1.0 .* [0, 2., 3.63, 3.7, 3.8, 3.88, 3.9] ./ size_BZ,
@@ -27,7 +28,7 @@ NiceValues(size_BZ) = Dict{Int64, Vector{Float64}}(
                          49 => -1.0 .* [0, 4.1, 8.19, 8.4, 8.55, 8.77, 8.8] ./ size_BZ,
                          57 => -1.0 .* [0, 5., 10.2, 10.6, 10.852] ./ size_BZ,
                          69 => -1.0 .* [0, 6., 12.5, 13.1, 13.34, 13.4] ./ size_BZ,
-                         77 => -1.0 .* [0., 14.04, 14.5, 14.99] ./ size_BZ,
+                         77 => -1.0 .* [0., 14.04, 14.5, 14.99, 15.0] ./ size_BZ,
                         )[size_BZ]
 pseudogapEnd(size_BZ) = Dict{Int64, Float64}(
                          13 => -1.0 * 1.6 / size_BZ,
@@ -78,7 +79,7 @@ function ScattProb(
         loadData::Bool=false
     )
     x_arr = get_x_arr(size_BZ)
-    W_val_arr = NiceValues(size_BZ)[[6]]
+    W_val_arr = NiceValues(size_BZ)
[…]

### 2025-04-04 numerics/source/helpers.jl

@@ -272,3 +272,14 @@ function KspaceExcitationOperators(
     specDictSet["Sd+"] = [("++-", [kpointIndices[2], 1, 2], 1.)]
     return specDictSet
 end
+
+
+function MinimalDistance(
+        point1::Int64,
+        point2::Int64,
+    )
+    rotationMatrix(rotateAngle) = [cos(rotateAngle) -sin(rotateAngle); sin(rotateAngle) cos(rotateAngle)]
+    equivalentPoints1 = [rotationMatrix(rotateAngle) * map1DTo2D(point1, size_BZ) for rotateAngle in (0, π/2, π, 3π/2)]
+    equivalentPoints2 = [rotationMatrix(rotateAngle) * map1DTo2D(point2, size_BZ) for rotateAngle in (0, π/2, π, 3π/2)]
+    return minimum([(p1 .- p2) .^ 2 .|> sum for p1 in equivalentPoints1 for p2 in equivalentPoints2])
+end

### 2025-04-04 numerics/source/plotting.jl

@@ -112,13 +112,15 @@ function plotPhaseDiagram(
         savename::String,
         colmap,
     )
-    figure = Figure(size=(350, 300), figure_padding=(0, 8, 4, 8))
+    figure = Figure(figure_padding=(0, 30, 5, 10))
     ax = Axis(figure[1, 1],
               xlabel = axisLabels[1], 
               ylabel=axisLabels[2], 
               xticklabelsize=22,
               yticklabelsize=22,
               xscale=log10,
+              width=250,
+              height=200,
              )
 
     for v in unique(matrixData)
@@ -130,6 +132,7 @@ function plotPhaseDiagram(
              colormap=colmap,
             )
     figure[0, 1] = axislegend(ax, orientation=:horizontal, margin=(0., 0., -10., -10.), patchcolor=:transparent, patchlabelgap=-10, colgap=0)
+    resize_to_layout!(figure)
     save(savename, figure)
 end
 

### 2025-04-04 numerics/source/probes.jl

@@ -89,8 +89,9 @@ end
     allKeys = vcat(keys(correlationFuncDict)..., keys(vneFuncDict)..., keys(mutInfoFuncDict)...)
     corrResults = Dict{String, Vector{Float64}}(k => repeat([NaN], hamiltDetails["size_BZ"]^2) for k in allKeys)
 
-    nonPivotPoints = filter(∉(pivotPoints), sortedPoints)
-    pointsSequence = vcat(pivotPoints, nonPivotPoints)
+    #=nonPivotPoints = filter(∉(pivotPoints), sortedPoints)=#
+    #=pointsSequence = vcat(pivotPoints, nonPivotPoints)=#
+    pointsSequence = copy(sortedPoints)
 
     mapCorrNameToIndex = Dict()
     correlationDefDict = Dict{String, Vector{Tuple{String, Vector{Int64}, Float64}}}()
@@ -117,6 +118,9 @@ end
     mutInfoDefDict = Dict{String, NTuple{2, Vector{Int64}}}()
     for (name, (secondMomentum, func)) in mutInfoFuncDict
         secondIndex = isnothing(secondMomentum) ? nothing : findfirst(==(secondMomentum), pointsSequence)
+        if !isnothing(secondMomentum) && isnothing(secondIndex)
+            continue
+        end
         for pivotIndex in pivotIndices
             partyA, partyB = func(pivotIndex, secondIndex)
             if partyA ≠ partyB
@@ -151,6 +155,7 @@ end
     for hamiltonian in hamiltonianFamily
         @assert all(!isempty, hamiltonian)
     end
+
     iterDiagResults = nothing
     id = nothing
     while true
@@ -290,8 +295,9 @@ end
         bathIntLegs::Int64=2,
         noSelfCorr::Vector{String}=String[],
         addPerStep::Int64=1,
-        numProcs::Int64=1,
+        numProcs::Int64=nprocs(),
         loadData::Bool=false,
+        sortByDistance::Bool=false,
     )
 
     size_BZ = hamiltDetails["size_BZ"]
@@ -300,9 +306,11 @@ end
 
     # pick out k-states from the southwest quadrant that have positive energies 
     # (hole states can be reconstructed from them (p-h symmetry))
-    SWIndices = [p for p in 1:size_BZ^2 if map1DTo2D(p, size_BZ)[1] < 0
-                 && map1DTo2D(p, size_BZ)[2] ≤ 0 
-                 && abs(cutoffEnergy) ≥ abs(hamiltDetails["dispersion"][p])
[…]

### 2025-04-09 TilingProjectDraft/tilingProject.tex
reimplemented Hatsugai-Kohmoto Hamiltonian, almost completed

@@
 
-\section{Nature of Gapless Excitations in the Impurity Pseudogap}\label{2CKEmerge}
-\subsection{Emergence of a two-channel Kondo Model}
+\section{Nature of Gapless Excitations in the Impurity Pseudogap}
+\subsection{Emergence of a two-channel Kondo Model}\label{2CKEmerge}
 As the bath interaction \(W\) is tuned through the L-PG phase, the four nodal points in the Brillouin zone are the last to decouple from the impurity.
@@
 This is the orthogonality catastrophe~\cite{varma2002singular,anderson_infraredcat,yamada_catastrophe,yamada1979orthogonality} in the two-channel Kondo problem, and it is brought about by the presence of the channel-non diagonal terms in Eq.~\ref{mfl_large}.
+
+\subsection{Emergence of long-ranged interactions near the NFL-Mott insulator transition}
+As the bath interaction \(W\) is tuned through the L-PG phase, the nodal region is the last to decouple from the impurity.
+This allows us to write down a simpler Kondo model near the transition, where only the nodal region is hybridising with the impurity spin through Kondo interactions.
+This is done by retaining only those scattering processes \({\bf k}_1 \to {\bf k}_2\) that originate from and end at \(k-\)points within a small neighborhood of width \(|{\bf q}|\) around the four nodal points: \({\bf k}_1, {\bf k}_2 \in {\bf N} + {\bf q}, |{\bf q}| \ll \pi\), where \({\bf N}\) can be any one of the four nodal points \({\bf N}_{1} = \left(\pi/2, \pi/2\right), {\bf N}_{2} = \left(-\pi/2, \pi/2\right)\) and \({\bf N}_1 + {\bf Q}_1\) and \({\bf N}_{2} + {\bf Q}_2\), where \({\bf Q}_1 = \left(-\pi,-\pi \right)\) and \({\bf Q}_2 = \left( \pi, -\pi \right) \) are the two nesting vectors.
+We have already seen, in Subsection ~\ref{2CKEmerge}, that the pseudogap regime displays a decoupling of the Brillouin zone into sets of points that have no explicit connecting term in the Hamiltonian.
+Near the transition, the neighbourhoods of \({\bf N}_{1}\) and \({\bf N}_{1} + {\bf Q}_1\) form one such connected set, while the other two nodes \({\bf N}_{2}\) and \({\bf N}_{2} + {\bf Q}_2\) form another connected set, but these two sets are disconnected from each other, in the sense of a two-channel model.
+
+With these considerations, the simplified low-energy model near the transition describing the Kondo scattering processes can be written as
+\begin{equation}\begin{aligned}
+	\tilde H_\text{imp-cbath} = \frac{1}{2}\sum_{l=1,2}\sum_{{\bf q}_1, {\bf q}_2}\sum_{\alpha,\beta}J^*({\bf q}_1, {\bf q}_2){\bf S}_d\cdot{\boldsymbol \sigma}_{\alpha\beta}&\left(c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} + c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta} \right.
+\\
+&\left. - c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} - c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta}\right)~.
+\end{aligned}\end{equation}
+where \(J^*({\bf q}_1, {\bf q}_2)\) is the Kondo coupling for the scattering processes involving \({\bf q}_1\) and \({\bf q}_2\) and a common nodal point between them.
+For scattering processes that involve two opposite nodal points (that is, connected by one of the nesting vectors \({\bf Q}_l\), the Kondo coupling is \(-J^*({\bf q}_1, {\bf q}_2)\), which explains the negative signs in the third and fourth terms.
+An explanation of the various dummy indices is in order.
+The label \(l\) can take values 1 or 2, allowing us to consider both the decoupled sets (associated with \({\bf N}_1\) and \({\bf N}_2\)).
+It also labels the nesting vectors \({\bf Q}_l\) associated with the two sets.
+\(\alpha\) and \(\beta\) indicate spin indices, and \({\bf q}_1\) and \({\bf q}_2\) represent incoming and outgoing momenta in the scattering processes.
+
+Because of the decoupling of the channel \(l=1\) and \(l=2\), we consider only the \(l=1\) channel for the rest of the calculations in this section, and we comment at the end on what the presence of two channels means for the results.
+In order to simplify the Hamiltonian, we define new fermionic operators
+\begin{equation}\begin{aligned}
+	\psi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} + c_{{\bf N}_1 + {\bf Q}_1 + {\bf q}, \sigma}\right)~,
+	\phi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} - c_{{\bf N}_1 + {\bf Q}_1 + {\bf q}, \sigma}\right)~,
+\end{aligned}\end{equation}
+The operator satisfy fermionic anticommutation relations:
+\begin{equation}\begin{aligned}
+	\left\{ \psi_{{\bf q},\sigma}, {\psi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left[\delta_{{\bf q}, {\bf q}^\prime} + \frac{1}{2}\left(\delta_{{\bf q} + {\bf Q}_1, {\bf q}^\prime} + \delta_{{\bf q}, {\bf q}^\prime + {\bf Q}_1}\right)  \right] \delta_{\sigma,\sigma^\prime} \\
+																							   &= \delta_{{\bf q}, {\bf q}^\prime}\delta_{\sigma,\sigma^\prime}~,\\
+	\left\{ \phi_{{\bf q},\sigma}, {\phi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left[\delta_{{\bf q}, {\bf q}^\prime} - \frac{1}{2}\left(\delta_{{\bf q} + {\bf Q}_1, {\bf q}^\prime} + \delta_{{\bf q}, {\bf q}^\prime + {\bf Q}_1}\right)  \right] \delta_{\sigma,\sigma^\prime} \\
+																				  &= \delta_{{\bf q}, {\bf q}^\prime}\delta_{\sigma,\sigma^\prime}~,\\
+	\left\{ \psi_{{\bf q},\sigma}, {\phi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left\{ \phi_{{\bf q},\sigma}, {\psi}^\dagger_{{\bf q}^\prime,\sigma} \right\} = 0~,
+\end{aligned}\end{equation}
+where both \({\bf q}\) and \({\bf q}^\prime\) are chosen from a small window around the nodes, so their difference is also small and it is therefore guaranteed that \(|{\bf q} - {\bf q}^\prime| \neq |{\bf Q}_1|\), rendering both \(\delta_{{\bf q} + {\bf Q}_1, {\bf q}^\prime}\) and \(\delta_{{\bf q}, {\bf q}^\prime + {\bf Q}_1}\) zero.
+For convenience, we define new number operators for the sum and relative degrees of freedom:
+\begin{equation}\begin{aligned}
+	s_{{\bf q},\sigma} = {\psi}^\dagger_{{\bf q}} {\psi}_{{\bf q}},~ r_{{\bf q},\sigma} = {\phi}^\dagger_{{\bf q}} {\phi}_{{\bf q}}~.
+\end{aligned}\end{equation}
+We then have the following useful relation between the corresponding number operators \(n = c^\dagger c\):
+\begin{equation}\begin{aligned}\label{numberOperatorRelation}
+	n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf q} + {\bf Q}_1, \sigma} = s_{{\bf q}, \sigma} + r_{{\bf q},\sigma}~.
+\end{aligned}\end{equation}
+
+We find that the sum degrees of freedom \(s_{{\bf q},\sigma}\) do not enter the Kondo scattering Hamiltonian \(\tilde H_\text{imp-cbath}\) (for the single channel \(l=1\)), and it is expressed purely in terms of the relative degrees of freedom:
+\begin{equation}\begin{aligned}
+	\tilde H_\text{imp-cbath} = \sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}J^*({\bf q}_1,{\bf q}_2){\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta}~.
+\end{aligned}\end{equation}
+We now proceed to rewrite the other parts of the Hamiltonian in terms of these new degrees of freedom. The kinetic energy can be written as
+\begin{equation}\begin{aligned}\label{kineticEnergy}
+	\tilde H_\text{cbath} &= \sum_{{\bf q},\sigma}\varepsilon_{{\bf N}_1 + {\bf q}}\left(n_{{\bf N}_1 + {\bf q},\sigma} - n_{{\bf N}_1 + {\bf Q}_1 + {\bf q},\sigma}\right)\\
+						  &= \sum_{{\bf q},\sigma}\epsilon_{{\bf q}}\left({\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma} + {\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma}\right)~,
+\end{aligned}\end{equation}
+where \(\epsilon_{{\bf q}}\) is a shorthand for \(\varepsilon_{{\bf N}_1 + {\bf q}}\).
+We also consider a simplified form of the bath interaction (for the channel \(l=1\)), taking into account the density-density correlations in \(k-\)space:
+\begin{widetext}
+\begin{equation}\begin{aligned}
+	\tilde H_\text{cbath-int} =& -W\sum_{{\bf q},\sigma}\left(n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 + {\bf q},\sigma}\right) + W\sum_{{\bf q}_1,{\bf q}_2}\left(n_{{\bf N}_{1} + {\bf q}_1, \uparrow} + n_{{\bf N}_{1} + {\bf Q}_{1} + {\bf q}_1, \uparrow} \right) \left( n_{{\bf N}_{1} + {\bf q}_2, \downarrow} + n_{{\bf N}_{1} + {\bf Q}_{1} + {\bf q}_2, \downarrow} \right)~,\\
+	=& -W\sum_{{\bf q},\sigma}\left(s_{{\bf q},\sigma} + r_{{\bf q},\sigma}\right) + W\sum_{{\bf q}_1,{\bf q}_2}\left(s_{{\bf q}_1,\uparrow} + r_{{\bf q}_1,\uparrow}\right) \left(s_{{\bf q}_2,\downarrow} + r_{{\bf q}_2,\downarrow}\right)~.
+\end{aligned}\end{equation}
+\end{widetext}
+We used eq.~\ref{numberOperatorRelation} in order to obtain the final form.
+Since the Hamiltonian is defined in a small window around the nodal point, the kinetic energy is the smallest term in the Hamiltonian.
+We therefore ignore it for the time-being, and address the two other terms.
+Since both \(\tilde H_\text{imp-cbath}\) and \(\tilde H_\text{cbath-int}\) commute with \(s_{{\bf q}, \sigma}\), we replace the local objects \(\sum_{\bf q}s_{{\bf q},\sigma}\) in \(\tilde H_\text{cbath-int}\) with \(\frac{1}{2}\) since the bath is always at half-filling.
+This results in a simplified Hamiltonian for just the \(\phi_{{\bf q},\sigma}\) degrees of freedom:
+\begin{equation}\begin{aligned}
+	\tilde H =& -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow} + \sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}J^*({\bf q}_1,{\bf q}_2){\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta}
+\end{aligned}\end{equation}
+
+For bath interaction strength close to the critical value (\(W \lesssim W_c\)), the fixed point coupling value \(J^*\) is much smaller than \(W\).
+In order to obtain the gapless excitations of the system arising from the presence of the impurity site, we integrate out the impurity dynamics via a Schrieffer-Wolff transformation.
+The perturbation term \(\mathcal{V}\) then consists of Hamiltonian terms that modify the impurity configuration,
+\begin{equation}\begin{aligned}
+	\mathcal{V} = \sum_{{\bf q}_1, {\bf q}_2}J^*({\bf q}_1,{\bf q}_2){S}_d^+{\phi}^\dagger_{{\bf q}_1 \downarrow} \phi_{{\bf q}_2 \uparrow} + \text{h.c.}~,
+\end{aligned}\end{equation}
+while the ``non-interacting" Hamiltonian is
+\begin{equation}\begin{aligned}
+	H_D &= -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow}~.
+\end{aligned}\end{equation}
+The renormalisation in the dynamics of \(b^\dagger_{\vec k,\sigma}\) are given by
+\begin{equation}\begin{aligned}
+	\Delta \tilde H &= \mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L,
+\end{aligned}\end{equation}
+where \(E_L\) is the energy of the ground state of \(H_D\), \(-(E_L - H_D)\) is the excitation energy of the state generated upon applying the perturbation \(\mathcal{V}\), and \(\mathcal{P}_{L(H)}\) projects onto the low(high)-energy subspace.
+For the present Hamiltonian, the low-energy state (associated with \(E_L\)) is the one that minimises the bath interaction term \(\tilde H_\text{cbath-int}\); since the coupling \(W\) is negative, it projects out the spin sector of each \(k-\)state at low energies, leading to the following ground state:
+\begin{equation}\begin{aligned}
+	\ket{L} = \otimes_{\vec q}\frac{1}{\sqrt 2}\left(\phi^\dagger_{{\bf q}, \uparrow}\phi^\dagger_{{\bf q}, \downarrow} + 1\right) \ket{0}
+\end{aligned}\end{equation}
+where \(\ket{0}\) is the \(r_{{\bf q} \uparrow} = r_{{\bf q} \downarrow} = 0\) state.
+The state \(\ket{L}\) is at zero energy.
+High-energy states are obtained by applying, on the state \(\ket{L}\), the excitation operator \(\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2,\bar\sigma}\) or its hermitian conjugate.
+The operator converts a double and a hole to spin states, incurring a total excitation cost of \(-W = |W|\).
+
+We now calculate the various terms in \(\Delta \tilde H\):
+\begin{equation}\begin{aligned}
+	&\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L = \left(\frac{1}{2} + S_d^z\right) \sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*({\bf q}_1,{\bf q}_2})^2}{-4W}\phi^\dagger_{{\bf q}_1,\downarrow}\phi_{{\bf q}_2, \uparrow} \left(\phi^\dagger_{{\bf q}_2,\uparrow}\phi_{{\bf q}_1, \downarrow} + (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\uparrow}\phi_{{\bf q}_2, \downarrow}\right)\\
+	&= -\sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*({\bf q}_1,{\bf q}_2})^2}{4W}\left[r_{{\bf q}_1 \downarrow} \left(1 - r_{{\bf q}_2 \uparrow}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\uparrow}\phi^\dagger_{{\bf q}_1,\downarrow}\phi_{{\bf q}_2, \downarrow}\phi_{{\bf q}_2, \uparrow}\right]\\
+	&\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L = \sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*({\bf q}_1,{\bf q}_2})^2}{-4W}\left[r_{{\bf q}_1 \uparrow} \left(1 - r_{{\bf q}_2 \downarrow}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\downarrow}\phi^\dagger_{{\bf q}_1,\uparrow}\phi_{{\bf q}_2, \uparrow}\phi_{{\bf q}_2, \downarrow}\right] \\
+\end{aligned}\end{equation}
+In both terms, we set \(S_d^z = 0\) owing to local SU(2) symmetry on the impurity site. Finally, we can treat the dispersion part of the Hamiltonian (eq.~\ref{kineticEnergy}) in the same way:
+\begin{equation}\begin{aligned}
+\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L &= \sum_{{\bf q},\sigma}\frac{\epsilon_{{\bf q}}^2}{-W}\left[\phi^\dagger_{{\bf q},\sigma}\psi_{{\bf q},\sigma}\psi^\dagger_{{\bf q},\sigma}\phi_{{\bf q},\sigma} + \psi^\dagger_{{\bf q},\sigma}\phi_{{\bf q},\sigma}\phi^\dagger_{{\bf q},\sigma}\psi_{{\bf q},\sigma}\right] \\
+&= -\frac{1}{2W}\sum_{{\bf q},\sigma}\epsilon_{{\bf q}}^2\phi^\dagger_{{\bf q},\sigma}\phi_{{\bf q},\sigma}~,
+\end{aligned}\end{equation}
+where, at the last step, we set \(\psi_{{\bf q},\sigma}\psi^\dagger_{{\bf q},\sigma} = 1/2\) owing to half-filling.
+
+\begin{equation}\begin{aligned}
+	\Delta \tilde H = \sum_{\vec q,\sigma}\left[\Delta(\vec q)\bar N_{\vec k_N + \vec q, \sigma} -2\Delta(\vec q)\bar N_{\vec k_N, \sigma}\bar N_{\vec k_N + \vec q, \sigma}\right.\\
+	\left. -\Delta(\vec q) \left(b^\dagger_{\vec k_N, \sigma} b^\dagger_{\vec k_N, \bar\sigma} b_{\vec k_N + \vec q, \bar\sigma}b_{\vec k_N + \vec q, \sigma} + \text{h.c.}\right) \right]~,
+\end{aligned}\end{equation}
+where \(\Delta(q) = -{J^*(\vec q)}^2/8W\) is a positive energy scale.
 
@@
 
-\paragraph{At the critical point}
+\paragraph{At the critical point, \(|W| \lesssim |W|^*\):}
 

### 2025-04-10 TilingProjectDraft/tilingProject.tex
recalculated effective Hamiltonian with different modes

@@
 Near the transition, the neighbourhoods of \({\bf N}_{1}\) and \({\bf N}_{1} + {\bf Q}_1\) form one such connected set, while the other two nodes \({\bf N}_{2}\) and \({\bf N}_{2} + {\bf Q}_2\) form another connected set, but these two sets are disconnected from each other, in the sense of a two-channel model.
+We also assume that the window of \({\bf q}\) is small enough so that the fixed point Kondo coupling values \(J^*({\bf q}_1, {\bf q}_2)\) for the scattering processes involving \({\bf q}_1\) and \({\bf q}_2\) can be replaced by an average value \(J^*\).
 
@@
 \begin{equation}\begin{aligned}
-	\tilde H_\text{imp-cbath} = \frac{1}{2}\sum_{l=1,2}\sum_{{\bf q}_1, {\bf q}_2}\sum_{\alpha,\beta}J^*({\bf q}_1, {\bf q}_2){\bf S}_d\cdot{\boldsymbol \sigma}_{\alpha\beta}&\left(c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} + c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta} \right.
+	\tilde H_\text{imp-cbath} = J^*\frac{1}{2}\sum_{l=1,2}\sum_{{\bf q}_1, {\bf q}_2}\sum_{\alpha,\beta}{\bf S}_d\cdot{\boldsymbol \sigma}_{\alpha\beta}&\left(c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} + c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta} \right.
 \\
@@
 \end{aligned}\end{equation}
-where \(J^*({\bf q}_1, {\bf q}_2)\) is the Kondo coupling for the scattering processes involving \({\bf q}_1\) and \({\bf q}_2\) and a common nodal point between them.
-For scattering processes that involve two opposite nodal points (that is, connected by one of the nesting vectors \({\bf Q}_l\), the Kondo coupling is \(-J^*({\bf q}_1, {\bf q}_2)\), which explains the negative signs in the third and fourth terms.
+For scattering processes that involve two opposite nodal points (that is, connected by one of the nesting vectors \({\bf Q}_l\), the Kondo coupling is \(-J^*\), which explains the negative signs in the third and fourth terms.
 An explanation of the various dummy indices is in order.
@@
 \begin{equation}\begin{aligned}
-	\psi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} + c_{{\bf N}_1 + {\bf Q}_1 + {\bf q}, \sigma}\right)~,
-	\phi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} - c_{{\bf N}_1 + {\bf Q}_1 + {\bf q}, \sigma}\right)~,
+	\psi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} + c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~,
+	\phi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} - c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~,
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\left\{ \psi_{{\bf q},\sigma}, {\psi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left[\delta_{{\bf q}, {\bf q}^\prime} + \frac{1}{2}\left(\delta_{{\bf q} + {\bf Q}_1, {\bf q}^\prime} + \delta_{{\bf q}, {\bf q}^\prime + {\bf Q}_1}\right)  \right] \delta_{\sigma,\sigma^\prime} \\
+	\left\{ \psi_{{\bf q},\sigma}, {\psi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left[\delta_{{\bf q}, {\bf q}^\prime} + \frac{1}{2}\left(\delta_{{\bf Q}_1 - {\bf q}, {\bf q}^\prime} + \delta_{{\bf q}, {\bf Q}_1 - {\bf q}^\prime}\right)  \right] \delta_{\sigma,\sigma^\prime} \\
 																							   &= \delta_{{\bf q}, {\bf q}^\prime}\delta_{\sigma,\sigma^\prime}~,\\
-	\left\{ \phi_{{\bf q},\sigma}, {\phi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left[\delta_{{\bf q}, {\bf q}^\prime} - \frac{1}{2}\left(\delta_{{\bf q} + {\bf Q}_1, {\bf q}^\prime} + \delta_{{\bf q}, {\bf q}^\prime + {\bf Q}_1}\right)  \right] \delta_{\sigma,\sigma^\prime} \\
+	\left\{ \phi_{{\bf q},\sigma}, {\phi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left[\delta_{{\bf q}, {\bf q}^\prime} - \frac{1}{2}\left(\delta_{{\bf Q}_1 - {\bf q}, {\bf q}^\prime} + \delta_{{\bf q}, {\bf Q}_1 - {\bf q}^\prime}\right)  \right] \delta_{\sigma,\sigma^\prime} \\
 																				  &= \delta_{{\bf q}, {\bf q}^\prime}\delta_{\sigma,\sigma^\prime}~,\\
@@
 \end{aligned}\end{equation}
-where both \({\bf q}\) and \({\bf q}^\prime\) are chosen from a small window around the nodes, so their difference is also small and it is therefore guaranteed that \(|{\bf q} - {\bf q}^\prime| \neq |{\bf Q}_1|\), rendering both \(\delta_{{\bf q} + {\bf Q}_1, {\bf q}^\prime}\) and \(\delta_{{\bf q}, {\bf q}^\prime + {\bf Q}_1}\) zero.
+where both \({\bf q}\) and \({\bf q}^\prime\) are chosen from a small window around the nodes, so their difference is also small and it is therefore guaranteed that \(|{\bf q} + {\bf q}^\prime| \neq |{\bf Q}_1|\), rendering both \(\delta_{{\bf q}, {\bf Q}_1 - {\bf q}^\prime}\) and \(\delta_{{\bf Q}_1 - {\bf q}, {\bf q}^\prime}\) zero.
 For convenience, we define new number operators for the sum and relative degrees of freedom:
@@
 \begin{equation}\begin{aligned}\label{numberOperatorRelation}
-	n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf q} + {\bf Q}_1, \sigma} = s_{{\bf q}, \sigma} + r_{{\bf q},\sigma}~.
+	n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma} = s_{{\bf q}, \sigma} + r_{{\bf q},\sigma}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\tilde H_\text{imp-cbath} = \sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}J^*({\bf q}_1,{\bf q}_2){\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta}~.
+	\tilde H_\text{imp-cbath} = J^*\sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}{\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta}~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}\label{kineticEnergy}
-	\tilde H_\text{cbath} &= \sum_{{\bf q},\sigma}\varepsilon_{{\bf N}_1 + {\bf q}}\left(n_{{\bf N}_1 + {\bf q},\sigma} - n_{{\bf N}_1 + {\bf Q}_1 + {\bf q},\sigma}\right)\\
+	\tilde H_\text{cbath} &= \sum_{{\bf q},\sigma}\varepsilon_{{\bf N}_1 + {\bf q}}\left(n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q},\sigma}\right)\\
 						  &= \sum_{{\bf q},\sigma}\epsilon_{{\bf q}}\left({\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma} + {\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma}\right)~,
@@
 \begin{equation}\begin{aligned}
-	\tilde H_\text{cbath-int} =& -W\sum_{{\bf q},\sigma}\left(n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 + {\bf q},\sigma}\right) + W\sum_{{\bf q}_1,{\bf q}_2}\left(n_{{\bf N}_{1} + {\bf q}_1, \uparrow} + n_{{\bf N}_{1} + {\bf Q}_{1} + {\bf q}_1, \uparrow} \right) \left( n_{{\bf N}_{1} + {\bf q}_2, \downarrow} + n_{{\bf N}_{1} + {\bf Q}_{1} + {\bf q}_2, \downarrow} \right)~,\\
+	\tilde H_\text{cbath-int} =& -W\sum_{{\bf q},\sigma}\left(n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q},\sigma}\right) + W\sum_{{\bf q}_1,{\bf q}_2}\left(n_{{\bf N}_{1} + {\bf q}_1, \uparrow} + n_{{\bf N}_{1} + {\bf Q}_{1} - {\bf q}_1, \uparrow} \right) \left( n_{{\bf N}_{1} + {\bf q}_2, \downarrow} + n_{{\bf N}_{1} + {\bf Q}_{1} - {\bf q}_2, \downarrow} \right)~,\\
 	=& -W\sum_{{\bf q},\sigma}\left(s_{{\bf q},\sigma} + r_{{\bf q},\sigma}\right) + W\sum_{{\bf q}_1,{\bf q}_2}\left(s_{{\bf q}_1,\uparrow} + r_{{\bf q}_1,\uparrow}\right) \left(s_{{\bf q}_2,\downarrow} + r_{{\bf q}_2,\downarrow}\right)~.
@@
 We used eq.~\ref{numberOperatorRelation} in order to obtain the final form.
-Since the Hamiltonian is defined in a small window around the nodal point, the kinetic energy is the smallest term in the Hamiltonian.
-We therefore ignore it for the time-being, and address the two other terms.
+
 Since both \(\tilde H_\text{imp-cbath}\) and \(\tilde H_\text{cbath-int}\) commute with \(s_{{\bf q}, \sigma}\), we replace the local objects \(\sum_{\bf q}s_{{\bf q},\sigma}\) in \(\tilde H_\text{cbath-int}\) with \(\frac{1}{2}\) since the bath is always at half-filling.
@@
 \begin{equation}\begin{aligned}
-	\tilde H =& -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow} + \sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}J^*({\bf q}_1,{\bf q}_2){\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta}
+	\tilde H =& -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow} + \sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}J^*{\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\mathcal{V} = \sum_{{\bf q}_1, {\bf q}_2}J^*({\bf q}_1,{\bf q}_2){S}_d^+{\phi}^\dagger_{{\bf q}_1 \downarrow} \phi_{{\bf q}_2 \uparrow} + \text{h.c.}~,
+	\mathcal{V} = \sum_{{\bf q}_1, {\bf q}_2}J^*{S}_d^+{\phi}^\dagger_{{\bf q}_1 \downarrow} \phi_{{\bf q}_2 \uparrow} + \text{h.c.}~,
 \end{aligned}\end{equation}
@@
 where \(E_L\) is the energy of the ground state of \(H_D\), \(-(E_L - H_D)\) is the excitation energy of the state generated upon applying the perturbation \(\mathcal{V}\), and \(\mathcal{P}_{L(H)}\) projects onto the low(high)-energy subspace.
-For the present Hamiltonian, the low-energy state (associated with \(E_L\)) is the one that minimises the bath interaction term \(\tilde H_\text{cbath-int}\); since the coupling \(W\) is negative, it projects out the spin sector of each \(k-\)state at low energies, leading to the following ground state:
-\begin{equation}\begin{aligned}
-	\ket{L} = \otimes_{\vec q}\frac{1}{\sqrt 2}\left(\phi^\dagger_{{\bf q}, \uparrow}\phi^\dagger_{{\bf q}, \downarrow} + 1\right) \ket{0}
+For the present Hamiltonian, the low-energy state (associated with \(E_L\)) is the one that minimises the bath interaction term \(\tilde H_\text{cbath-int}\); since the coupling \(W\) is negative, the minimal configuration is one in which the local operators \(\sum_{{\bf q}}r_{{\bf q},\sigma}\) (for \(\sigma=\pm 1\)) are unity.
+This leads to the following low-energy state:
+\begin{equation}\begin{aligned}
+	\ket{L} = \frac{1}{N}\sum_{{\bf q}_1{\bf q}_2}\phi^\dagger_{{\bf q}_1, \uparrow}\phi^\dagger_{{\bf q}_2, \downarrow} \ket{0}
 \end{aligned}\end{equation}
@@
 We now calculate the various terms in \(\Delta \tilde H\):
-\begin{equation}\begin{aligned}
-	&\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L = \left(\frac{1}{2} + S_d^z\right) \sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*({\bf q}_1,{\bf q}_2})^2}{-4W}\phi^\dagger_{{\bf q}_1,\downarrow}\phi_{{\bf q}_2, \uparrow} \left(\phi^\dagger_{{\bf q}_2,\uparrow}\phi_{{\bf q}_1, \downarrow} + (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\uparrow}\phi_{{\bf q}_2, \downarrow}\right)\\
-	&= -\sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*({\bf q}_1,{\bf q}_2})^2}{4W}\left[r_{{\bf q}_1 \downarrow} \left(1 - r_{{\bf q}_2 \uparrow}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\uparrow}\phi^\dagger_{{\bf q}_1,\downarrow}\phi_{{\bf q}_2, \downarrow}\phi_{{\bf q}_2, \uparrow}\right]\\
-	&\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L = \sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*({\bf q}_1,{\bf q}_2})^2}{-4W}\left[r_{{\bf q}_1 \uparrow} \left(1 - r_{{\bf q}_2 \downarrow}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\downarrow}\phi^\dagger_{{\bf q}_1,\uparrow}\phi_{{\bf q}_2, \uparrow}\phi_{{\bf q}_2, \downarrow}\right] \\
-\end{aligned}\end{equation}
-In both terms, we set \(S_d^z = 0\) owing to local SU(2) symmetry on the impurity site. Finally, we can treat the dispersion part of the Hamiltonian (eq.~\ref{kineticEnergy}) in the same way:
-\begin{equation}\begin{aligned}
-\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L &= \sum_{{\bf q},\sigma}\frac{\epsilon_{{\bf q}}^2}{-W}\left[\phi^\dagger_{{\bf q},\sigma}\psi_{{\bf q},\sigma}\psi^\dagger_{{\bf q},\sigma}\phi_{{\bf q},\sigma} + \psi^\dagger_{{\bf q},\sigma}\phi_{{\bf q},\sigma}\phi^\dagger_{{\bf q},\sigma}\psi_{{\bf q},\sigma}\right] \\
-&= -\frac{1}{2W}\sum_{{\bf q},\sigma}\epsilon_{{\bf q}}^2\phi^\dagger_{{\bf q},\sigma}\phi_{{\bf q},\sigma}~,
-\end{aligned}\end{equation}
-where, at the last step, we set \(\psi_{{\bf q},\sigma}\psi^\dagger_{{\bf q},\sigma} = 1/2\) owing to half-filling.
-
-\begin{equation}\begin{aligned}
-	\Delta \tilde H = \sum_{\vec q,\sigma}\left[\Delta(\vec q)\bar N_{\vec k_N + \vec q, \sigma} -2\Delta(\vec q)\bar N_{\vec k_N, \sigma}\bar N_{\vec k_N + \vec q, \sigma}\right.\\
-	\left. -\Delta(\vec q) \left(b^\dagger_{\vec k_N, \sigma} b^\dagger_{\vec k_N, \bar\sigma} b_{\vec k_N + \vec q, \bar\sigma}b_{\vec k_N + \vec q, \sigma} + \text{h.c.}\right) \right]~,
+\begin{equation}\begin{aligned}\label{kondoPert}
+	&\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L = \left(\frac{1}{2} + S_d^z\right) \sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*}^2}{-4W}\phi^\dagger_{{\bf q}_1,\downarrow}\phi_{{\bf q}_2, \uparrow} \left(\phi^\dagger_{{\bf q}_2,\uparrow}\phi_{{\bf q}_1, \downarrow} + (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\uparrow}\phi_{{\bf q}_2, \downarrow}\right)\\
+	&= -\sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*}^2}{4W}\left[r_{{\bf q}_1 \downarrow} \left(1 - r_{{\bf q}_2 \uparrow}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\uparrow}\phi^\dagger_{{\bf q}_1,\downarrow}\phi_{{\bf q}_2, \downarrow}\phi_{{\bf q}_2, \uparrow}\right]\\
+	&\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L = \sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*}^2}{-4W}\left[r_{{\bf q}_1 \uparrow} \left(1 - r_{{\bf q}_2 \downarrow}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\downarrow}\phi^\dagger_{{\bf q}_1,\uparrow}\phi_{{\bf q}_2, \uparrow}\phi_{{\bf q}_2, \downarrow}\right] \\
+\end{aligned}\end{equation}
+In both terms, we set \(S_d^z = 0\) owing to local SU(2) symmetry on the impurity site.
+Finally, we add the disperson part (eq.~\ref{kineticEnergy}) back into the Hamiltonian (since it is also vanishingly small close to the Fermi surface and can therefore lead to gapless excitations).
+The complete Hamiltonian is
+\begin{equation}\begin{aligned}
+	\Delta \tilde H = \sum_{\vec q,\sigma}\left[\Delta(\vec q)\bar N_{\vec k_N + \vec q, \sigma} -2\Delta(\vec q)\bar N_{\vec k_N, \sigma}\bar N_{\vec k_N + \vec q, \sigma} -\Delta(\vec q) \left(b^\dagger_{\vec k_N, \sigma} b^\dagger_{\vec k_N, \bar\sigma} b_{\vec k_N + \vec q, \bar\sigma}b_{\vec k_N + \vec q, \sigma} + \text{h.c.}\right) \right]~,
 \end{aligned}\end{equation}

### 2025-04-11 TilingProjectDraft/tilingProject.tex
updated notes with complete HKM calculations

@@
+%! TEX program = latexmk
 \documentclass[reprint,hidelinks,onecolumn]{revtex4-2}
@@
 
-\subsection{Marginal Fermi liquid behaviour in the pseudogap}\label{marginalFL}
+\subsection{Non-Fermi liquid behaviour in the pseudogap}\label{marginalFL}
 It is well-known that the two-channel Kondo model hosts non-Fermi liquid excitations at low-energies~\cite{Tsvelick_weigmann_mchannel_1985,emery_kivelson}; that this also happens in the present model is corroborated by our calculations of the quasiparticle residue \(Z_\text{imp}\) for the local gapless excitations.
@@
 
-Coleman and Ioffe have shown that by mapping the two-channel Kondo problem to a "compactified" form where the impurity spin hybridises with the spin and isospin degrees of freedom of a single conduction channel, the impurity self-energy can be shown to display marginal Fermi liquid behaviour~\cite{Coleman_tsvelik,Schofield1997}:
+Coleman and Ioffe have shown that by mapping the two-channel Kondo problem to a ``compactified" form where the impurity spin hybridises with the spin and isospin degrees of freedom of a single conduction channel, the impurity self-energy can be shown to display marginal Fermi liquid behaviour~\cite{Coleman_tsvelik,Schofield1997}:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-As some of us have shown in a previous work~\cite{Patra2023MCK}, this can also be obtained from a renormalisation group calculation of the low-energy excitations of the two-channel overscreened fixed point.
-For the sake of completeness, we have reproduced the calculation here.
-By considering minimal hopping into the conduction bath, the low-energy excitations above the 2CK ground state are described by the following Hamiltonian~\cite{Patra2023MCK}:
-\begin{eqnarray}
-	\label{nfl_terms}
-	H_\mathrm{eff} =& \frac{8t^2}{{J}}\left[\left(S^z_{0,1}\right)^2 S^+_{0,2} + \left(S^z_{0,2}\right)^2 S^+_{0,1}\right] \left(S^-_{1,1} + S^-_{1,2}\right) + \mathrm{h.c.};
-\end{eqnarray}
-where \({\boldsymbol S}_{i,l} = \frac{1}{2}\sum_{\sigma_1,\sigma_2}c^\dagger_{i,\sigma_1,l}{\boldsymbol \sigma}_{\sigma_1,\sigma_2}c_{i,\sigma_2,l}\) are spin operators for the \(i^\text{th}\) site on the \(l^\text{th}\) conduction channel (\(l\) can be 1 or 2 for a two-channel model).
-The labels \(\sigma_1\) and \(\sigma_2\) are spin indices that can be \(\pm 1\).
-The site index \(0\) represents the bath sites connected immediately to the impurity site.
-The operator \(c^\dagger_{i,\sigma,l}\) creates an electron with spin \(\sigma\) on the \(i^\text{th}\) site of the \(l^\text{th}\) conduction channel.
-
-We will Fourier transform this effective Hamiltonian into \(k-\)space:
-\begin{eqnarray}
-	\label{k_space_od}
-	\frac{2t^2}{J}\sum_{\left\{k_i,k_i^\prime\right\}}\sum_{\sigma, l} &\left(e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \mathrm{h.c.}\right) ~.\qquad
-\end{eqnarray}
-Such a three particle interaction term was also obtained for the NFL phase of the 2D Hubbard model from a URG treatment (see Appendix B of Ref.\cite{anirbanmott1}).
-The channel indices in Eq.~\ref{k_space_od} can be mapped to the normal directions in~\cite{anirbanmott1}.
-The 2 particle-1 hole interaction in Eq.~\ref{k_space_od} has a diagonal component which can be obtained by setting \(k=k^\prime, k_1 = k_2^\prime\) and \(k_2 = k_1^\prime\):
-\begin{eqnarray}
-	H_\mathrm{MFL} &= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{2t^2e^{i\left(k_1 - k_2\right)a}}{J} \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right) + \mathrm{h.c.}\nonumber\\
-	&= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{4t^2}{J} \cos a\left(k_1 - k_2\right)  \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right).\qquad 
-\end{eqnarray}
-The most dominant contribution comes from \(k_1 = k_2 = k^\prime\), revealing the non-Fermi liquid metal~\cite{cox_jarrell_two_channel_rev,Andrei1995}:
-\begin{eqnarray}
-	\label{mfl_large}
-	H^*_\mathrm{MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)~.
-\end{eqnarray}
-A non-local version of this effective Hamiltonian was found to describe the normal phase of the Mott insulator of the 2D Hubbard model, as seen from a URG analysis~\cite{anirbanmott1,anirbanmott2}.
-Following~\cite{anirbanmott1}, one can track the RG evolution of the dual coupling \(R_j = \frac{4t^2}{J_j}\) at the \(j^\mathrm{th}\) RG step, in the form of the URG equation
-\begin{eqnarray}
-	\Delta R_j =- \frac{R_j^2}{\omega - \epsilon_{j}/2 - R_j/8}~.
-\end{eqnarray}
-In the RG equation, \(\epsilon_{j}\) represents the energy of the \(j^\mathrm{th}\) isoenergetic shell. It is seen from 
-the RG equation that \(R\) is relevant in the range of \(\omega < \frac{1}{2}\epsilon_j\) that has been used throughout, leading to a fixed-point at \(R^*/8 = \omega - \frac{1}{2}\epsilon^*)\).
-The relevance of \(R\) is expected because the strong coupling \(J\) is irrelevant and \(R \sim 1/J\).
-
-The renormalisation in \(R\) leads to a renormalisation in the single-particle self-energy~\cite{anirbanmott1}. The \(k-\)space-averaged self-energy renormalisation is
-\begin{eqnarray}
-	\Delta \Sigma(\omega) = \rho {R^*}^2\int_0^{\epsilon^*} \frac{d\epsilon_j}{\omega - \epsilon_j/2 + R_j/8}~.
-\end{eqnarray}
-The density of states can be approximated to be \(N^*/R^*\), where \(N^*\) is the total number of states over the interval \(R^*\).
-As suggested by the fixed point value of \(R_j\), we can approximate its behaviour near the fixed point by a linear dependence on the dispersion \(\epsilon_j\).
-The two limits of the integration are the starting and ending points of the RG.
-We start the RG very close to the Fermi surface and move towards the fixed point \(\epsilon^*\).
-Near the starting point, we substitute \(\epsilon = 0\) and \(R = \omega\), following the fixed point condition.
-From the fixed point condition, we also substitute \(R^*/8 = \omega - \frac{1}{2}\epsilon^*\).
-On defining \(\bar \omega = N^* \left(\omega - \frac{1}{2}\epsilon^*\right)\), we can write
-\begin{eqnarray}
-	\label{self_energy}
-	\Delta \Sigma(\omega) \sim  \bar \omega \ln \frac{N^* \omega}{\bar \omega}~.
-\end{eqnarray}
-The self-energy also provides the quasiparticle residue for each channel\cite{anirbanmott1}:
-\begin{eqnarray}
-	Z(\bar\omega) = \left(2 - \ln \frac{2\bar\omega}{N^* \omega}\right) ^{-1}~.
-\end{eqnarray}
-As \(\omega \to 0\), the \(Z\) vanishes, implying that the ground state is {\it not adiabatically connected} to the Fermi gas in the presence of the NFL terms.
-This is the orthogonality catastrophe~\cite{varma2002singular,anderson_infraredcat,yamada_catastrophe,yamada1979orthogonality} in the two-channel Kondo problem, and it is brought about by the presence of the channel-non diagonal terms in Eq.~\ref{mfl_large}.
-
-\subsection{Emergence of long-ranged interactions near the NFL-Mott insulator transition}
-As the bath interaction \(W\) is tuned through the L-PG phase, the nodal region is the last to decouple from the impurity.
-This allows us to write down a simpler Kondo model near the transition, where only the nodal region is hybridising with the impurity spin through Kondo interactions.
-This is done by retaining only those scattering processes \({\bf k}_1 \to {\bf k}_2\) that originate from and end at \(k-\)points within a small neighborhood of width \(|{\bf q}|\) around the four nodal points: \({\bf k}_1, {\bf k}_2 \in {\bf N} + {\bf q}, |{\bf q}| \ll \pi\), where \({\bf N}\) can be any one of the four nodal points \({\bf N}_{1} = \left(\pi/2, \pi/2\right), {\bf N}_{2} = \left(-\pi/2, \pi/2\right)\) and \({\bf N}_1 + {\bf Q}_1\) and \({\bf N}_{2} + {\bf Q}_2\), where \({\bf Q}_1 = \left(-\pi,-\pi \right)\) and \({\bf Q}_2 = \left( \pi, -\pi \right) \) are the two nesting vectors.
-We have already seen, in Subsection ~\ref{2CKEmerge}, that the pseudogap regime displays a decoupling of the Brillouin zone into sets of points that have no explicit connecting term in the Hamiltonian.
-Near the transition, the neighbourhoods of \({\bf N}_{1}\) and \({\bf N}_{1} + {\bf Q}_1\) form one such connected set, while the other two nodes \({\bf N}_{2}\) and \({\bf N}_{2} + {\bf Q}_2\) form another connected set, but these two sets are disconnected from each other, in the sense of a two-channel model.
-We also assume that the window of \({\bf q}\) is small enough so that the fixed point Kondo coupling values \(J^*({\bf q}_1, {\bf q}_2)\) for the scattering processes involving \({\bf q}_1\) and \({\bf q}_2\) can be replaced by an average value \(J^*\).
-
-With these considerations, the simplified low-energy model near the transition describing the Kondo scattering processes can be written as
-\begin{equation}\begin{aligned}
-	\tilde H_\text{imp-cbath} = J^*\frac{1}{2}\sum_{l=1,2}\sum_{{\bf q}_1, {\bf q}_2}\sum_{\alpha,\beta}{\bf S}_d\cdot{\boldsymbol \sigma}_{\alpha\beta}&\left(c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} + c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta} \right.
-\\
-&\left. - c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} - c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta}\right)~.
-\end{aligned}\end{equation}
-For scattering processes that involve two opposite nodal points (that is, connected by one of the nesting vectors \({\bf Q}_l\), the Kondo coupling is \(-J^*\), which explains the negative signs in the third and fourth terms.
-An explanation of the various dummy indices is in order.
-The label \(l\) can take values 1 or 2, allowing us to consider both the decoupled sets (associated with \({\bf N}_1\) and \({\bf N}_2\)).
-It also labels the nesting vectors \({\bf Q}_l\) associated with the two sets.
-\(\alpha\) and \(\beta\) indicate spin indices, and \({\bf q}_1\) and \({\bf q}_2\) represent incoming and outgoing momenta in the scattering processes.
-
-Because of the decoupling of the channel \(l=1\) and \(l=2\), we consider only the \(l=1\) channel for the rest of the calculations in this section, and we comment at the end on what the presence of two channels means for the results.
-In order to simplify the Hamiltonian, we define new fermionic operators
-\begin{equation}\begin{aligned}
-	\psi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} + c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~,
+Some of us have shown in a previous work~\cite{Patra2023MCK} that this can also be obtained from a renormalisation group calculation of the low-energy excitations of the two-channel overscreened fixed point.
+For the sake of completeness, we have reproduced the calculation in Appendix~\ref{mflDerivation}.
+
+\subsection{Emergence of long-ranged interactions near the NFL-Mott insulator transition}\label{hkmEmerge}
+We will now obtain a low-energy Hamiltonian for the excitations very close to the transition, where the Kondo coupling is about to turn irrelevant.
+In order to do this, we carry out a perturbation-theoretic treatment of the fixed point Hamiltonian in this region of the phase diagram, by considering the effects of a small fixed point Kondo scattering probability \(J^*\) in the backdrop of a larger bath interaction parameter \(W\).
+We note that this is in contrast to the state of affairs that gave rise to the marginal Fermi liquid excitations in Subsection ~\ref{marginalFL}, where the Kondo coupling fixed the ground state and the conduction bath hopping processes led to the low-energy excitations; it is this contrast that leads to the emergence of a new effective Hamiltonian close to the transition.
+
+The complete Hamiltonian (details described in Appendix~\ref{hkmDerivation}) is
+\begin{equation}\begin{aligned}
+	\Delta \tilde H = \sum_{{\bf q}, \sigma}\text{sign}\left(\varepsilon_{{\bf N}_1 + {\bf q}}\right)\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W} r_{{\bf q},\sigma} + \sum_{{\bf q}_1,{\bf q}_2, \sigma}\frac{{J^*}^2}{-4W}\left[r_{{\bf q}_1 \sigma} \left(1 - r_{{\bf q}_2 \bar\sigma}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\bar\sigma}\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2, \sigma}\phi_{{\bf q}_2, \bar\sigma}\right]~,
+\end{aligned}\end{equation}
+where the fermionic operator \(\phi_{{\bf q}, \sigma}\) defines emergent relative modes,
+\begin{equation}\begin{aligned}
 	\phi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} - c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~,
 \end{aligned}\end{equation}
-The operator satisfy fermionic anticommutation relations:
-\begin{equation}\begin{aligned}
-	\left\{ \psi_{{\bf q},\sigma}, {\psi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left[\delta_{{\bf q}, {\bf q}^\prime} + \frac{1}{2}\left(\delta_{{\bf Q}_1 - {\bf q}, {\bf q}^\prime} + \delta_{{\bf q}, {\bf Q}_1 - {\bf q}^\prime}\right)  \right] \delta_{\sigma,\sigma^\prime} \\
-																							   &= \delta_{{\bf q}, {\bf q}^\prime}\delta_{\sigma,\sigma^\prime}~,\\
-	\left\{ \phi_{{\bf q},\sigma}, {\phi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left[\delta_{{\bf q}, {\bf q}^\prime} - \frac{1}{2}\left(\delta_{{\bf Q}_1 - {\bf q}, {\bf q}^\prime} + \delta_{{\bf q}, {\bf Q}_1 - {\bf q}^\prime}\right)  \right] \delta_{\sigma,\sigma^\prime} \\
-																				  &= \delta_{{\bf q}, {\bf q}^\prime}\delta_{\sigma,\sigma^\prime}~,\\
-	\left\{ \psi_{{\bf q},\sigma}, {\phi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left\{ \phi_{{\bf q},\sigma}, {\psi}^\dagger_{{\bf q}^\prime,\sigma} \right\} = 0~,
-\end{aligned}\end{equation}
-where both \({\bf q}\) and \({\bf q}^\prime\) are chosen from a small window around the nodes, so their difference is also small and it is therefore guaranteed that \(|{\bf q} + {\bf q}^\prime| \neq |{\bf Q}_1|\), rendering both \(\delta_{{\bf q}, {\bf Q}_1 - {\bf q}^\prime}\) and \(\delta_{{\bf Q}_1 - {\bf q}, {\bf q}^\prime}\) zero.
-For convenience, we define new number operators for the sum and relative degrees of freedom:
-\begin{equation}\begin{aligned}
-	s_{{\bf q},\sigma} = {\psi}^\dagger_{{\bf q}} {\psi}_{{\bf q}},~ r_{{\bf q},\sigma} = {\phi}^\dagger_{{\bf q}} {\phi}_{{\bf q}}~.
-\end{aligned}\end{equation}
-We then have the following useful relation between the corresponding number operators \(n = c^\dagger c\):
-\begin{equation}\begin{aligned}\label{numberOperatorRelation}
-	n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma} = s_{{\bf q}, \sigma} + r_{{\bf q},\sigma}~.
-\end{aligned}\end{equation}
-
-We find that the sum degrees of freedom \(s_{{\bf q},\sigma}\) do not enter the Kondo scattering Hamiltonian \(\tilde H_\text{imp-cbath}\) (for the single channel \(l=1\)), and it is expressed purely in terms of the relative degrees of freedom:
-\begin{equation}\begin{aligned}
-	\tilde H_\text{imp-cbath} = J^*\sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}{\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta}~.
-\end{aligned}\end{equation}
-We now proceed to rewrite the other parts of the Hamiltonian in terms of these new degrees of freedom. The kinetic energy can be written as
-\begin{equation}\begin{aligned}\label{kineticEnergy}
-	\tilde H_\text{cbath} &= \sum_{{\bf q},\sigma}\varepsilon_{{\bf N}_1 + {\bf q}}\left(n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q},\sigma}\right)\\
-						  &= \sum_{{\bf q},\sigma}\epsilon_{{\bf q}}\left({\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma} + {\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma}\right)~,
-\end{aligned}\end{equation}
-where \(\epsilon_{{\bf q}}\) is a shorthand for \(\varepsilon_{{\bf N}_1 + {\bf q}}\).
-We also consider a simplified form of the bath interaction (for the channel \(l=1\)), taking into account the density-density correlations in \(k-\)space:
-\begin{widetext}
-\begin{equation}\begin{aligned}
-	\tilde H_\text{cbath-int} =& -W\sum_{{\bf q},\sigma}\left(n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q},\sigma}\right) + W\sum_{{\bf q}_1,{\bf q}_2}\left(n_{{\bf N}_{1} + {\bf q}_1, \uparrow} + n_{{\bf N}_{1} + {\bf Q}_{1} - {\bf q}_1, \uparrow} \right) \left( n_{{\bf N}_{1} + {\bf q}_2, \downarrow} + n_{{\bf N}_{1} + {\bf Q}_{1} - {\bf q}_2, \downarrow} \right)~,\\
-	=& -W\sum_{{\bf q},\sigma}\left(s_{{\bf q},\sigma} + r_{{\bf q},\sigma}\right) + W\sum_{{\bf q}_1,{\bf q}_2}\left(s_{{\bf q}_1,\uparrow} + r_{{\bf q}_1,\uparrow}\right) \left(s_{{\bf q}_2,\downarrow} + r_{{\bf q}_2,\downarrow}\right)~.
-\end{aligned}\end{equation}
-\end{widetext}
-We used eq.~\ref{numberOperatorRelation} in order to obtain the final form.
-
-Since both \(\tilde H_\text{imp-cbath}\) and \(\tilde H_\text{cbath-int}\) commute with \(s_{{\bf q}, \sigma}\), we replace the local objects \(\sum_{\bf q}s_{{\bf q},\sigma}\) in \(\tilde H_\text{cbath-int}\) with \(\frac{1}{2}\) since the bath is always at half-filling.
-This results in a simplified Hamiltonian for just the \(\phi_{{\bf q},\sigma}\) degrees of freedom:
-\begin{equation}\begin{aligned}
-	\tilde H =& -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow} + \sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}J^*{\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta}
-\end{aligned}\end{equation}
-
-For bath interaction strength close to the critical value (\(W \lesssim W_c\)), the fixed point coupling value \(J^*\) is much smaller than \(W\).
-In order to obtain the gapless excitations of the system arising from the presence of the impurity site, we integrate out the impurity dynamics via a Schrieffer-Wolff transformation.
-The perturbation term \(\mathcal{V}\) then consists of Hamiltonian terms that modify the impurity configuration,
-\begin{equation}\begin{aligned}
-	\mathcal{V} = \sum_{{\bf q}_1, {\bf q}_2}J^*{S}_d^+{\phi}^\dagger_{{\bf q}_1 \downarrow} \phi_{{\bf q}_2 \uparrow} + \text{h.c.}~,
-\end{aligned}\end{equation}
-while the ``non-interacting" Hamiltonian is
-\begin{equation}\begin{aligned}
-	H_D &= -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow}~.
-\end{aligned}\end{equation}
-The renormalisation in the dynamics of \(b^\dagger_{\vec k,\sigma}\) are given by
-\begin{equation}\begin{aligned}
-	\Delta \tilde H &= \mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L,
-\end{aligned}\end{equation}
-where \(E_L\) is the energy of the ground state of \(H_D\), \(-(E_L - H_D)\) is the excitation energy of the state generated upon applying the perturbation \(\mathcal{V}\), and \(\mathcal{P}_{L(H)}\) projects onto the low(high)-energy subspace.
-For the present Hamiltonian, the low-energy state (associated with \(E_L\)) is the one that minimises the bath interaction term \(\tilde H_\text{cbath-int}\); since the coupling \(W\) is negative, the minimal configuration is one in which the local operators \(\sum_{{\bf q}}r_{{\bf q},\sigma}\) (for \(\sigma=\pm 1\)) are unity.
-This leads to the following low-energy state:
-\begin{equation}\begin{aligned}
-	\ket{L} = \frac{1}{N}\sum_{{\bf q}_1{\bf q}_2}\phi^\dagger_{{\bf q}_1, \uparrow}\phi^\dagger_{{\bf q}_2, \downarrow} \ket{0}
-\end{aligned}\end{equation}
-where \(\ket{0}\) is the \(r_{{\bf q} \uparrow} = r_{{\bf q} \downarrow} = 0\) state.
-The state \(\ket{L}\) is at zero energy.
-High-energy states are obtained by applying, on the state \(\ket{L}\), the excitation operator \(\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2,\bar\sigma}\) or its hermitian conjugate.
-The operator converts a double and a hole to spin states, incurring a total excitation cost of \(-W = |W|\).
-
-We now calculate the various terms in \(\Delta \tilde H\):
-\begin{equation}\begin{aligned}\label{kondoPert}
-	&\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L = \left(\frac{1}{2} + S_d^z\right) \sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*}^2}{-4W}\phi^\dagger_{{\bf q}_1,\downarrow}\phi_{{\bf q}_2, \uparrow} \left(\phi^\dagger_{{\bf q}_2,\uparrow}\phi_{{\bf q}_1, \downarrow} + (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\uparrow}\phi_{{\bf q}_2, \downarrow}\right)\\
-	&= -\sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*}^2}{4W}\left[r_{{\bf q}_1 \downarrow} \left(1 - r_{{\bf q}_2 \uparrow}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\uparrow}\phi^\dagger_{{\bf q}_1,\downarrow}\phi_{{\bf q}_2, \downarrow}\phi_{{\bf q}_2, \uparrow}\right]\\
-	&\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L = \sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*}^2}{-4W}\left[r_{{\bf q}_1 \uparrow} \left(1 - r_{{\bf q}_2 \downarrow}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\downarrow}\phi^\dagger_{{\bf q}_1,\uparrow}\phi_{{\bf q}_2, \uparrow}\phi_{{\bf q}_2, \downarrow}\right] \\
-\end{aligned}\end{equation}
-In both terms, we set \(S_d^z = 0\) owing to local SU(2) symmetry on the impurity site.
-Finally, we add the disperson part (eq.~\ref{kineticEnergy}) back into the Hamiltonian (since it is also vanishingly small close to the Fermi surface and can therefore lead to gapless excitations).
-The complete Hamiltonian is
-\begin{equation}\begin{aligned}
-	\Delta \tilde H = \sum_{\vec q,\sigma}\left[\Delta(\vec q)\bar N_{\vec k_N + \vec q, \sigma} -2\Delta(\vec q)\bar N_{\vec k_N, \sigma}\bar N_{\vec k_N + \vec q, \sigma} -\Delta(\vec q) \left(b^\dagger_{\vec k_N, \sigma} b^\dagger_{\vec k_N, \bar\sigma} b_{\vec k_N + \vec q, \bar\sigma}b_{\vec k_N + \vec q, \sigma} + \text{h.c.}\right) \right]~,
-\end{aligned}\end{equation}
-where \(\Delta(q) = -{J^*(\vec q)}^2/8W\) is a positive energy scale.
+that are shifted by an excitation momentum \({\bf q}\) away from the nodal point \({\bf N}_1 = \left(\pi/2, \pi/2\right)\) and its nested partner \({\bf N}_1 + {\bf Q}_1 = \left(-\pi/2, -\pi/2\right)\).
+The number operator \(r_{{\bf q} \sigma}\) is defined as \(r_{{\bf q} \sigma} = \phi_{{\bf q}, \sigma}\dagger \phi_{{\bf q}, \sigma}\).
+\(\varepsilon_{{\bf N}_1 + {\bf q}}\) represents the non-interacting kinetic energy of the conduction bath.
+
+In order to extract the singular, critical part of the Hamiltonian, we focus on the \({\bf q}_1 = {\bf q}_2\) forward scattering processes:
+\begin{equation}\begin{aligned}\label{HKModel}
+	\Delta \tilde H_{{\bf q}_1 = {\bf q}_2} = \sum_{{\bf q},\sigma}\epsilon_{{\bf q}}{r}_{{\bf q},\sigma} + u\sum_{{\bf q}, \sigma}r_{{\bf q} \sigma} r_{{\bf q} \bar\sigma}
+\end{aligned}\end{equation}
+where \(\epsilon_{\bf q}\) and \(u\) are emergent energy scales:
+\begin{equation}\begin{aligned}
+	\epsilon_{\bf q} = \text{sign}\left(\varepsilon_{{\bf N}_1 + {\bf q}}\right)\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W} + \frac{{J^*}^2}{-4W},~u = \frac{{J^*}^2}{4W}~.
+\end{aligned}\end{equation}
+Eq.~\ref{HKModel} describes a Hatsugai-Kohmoto model~\cite{Baskaran1991,Hatsugai1992}, an exactly solvable model of correlated electrons; by tuning the ratio of the interaction strength \(u\) and the bandwidth \(w\), the model describes a transition between a non-Fermi liquid and a Mott insulator.
+The non-Fermi liquid nature of the gapless excitations in the metallic phase of the model manifests in the form of a divergent one-particle self-energy at the non-interacting Fermi surface~\cite{Phillips2020}:
+\begin{equation}\begin{aligned}
+	\Sigma_{{\bf q}}(\omega) = -\frac{u^2/4}{\omega - \epsilon_{\bf q}}, ~\Sigma_{\epsilon_{\bf q}=0}(\omega \to 0)  \to \infty~.
+\end{aligned}\end{equation}
+Beyond the transition and inside the Mott insulating phase, this zero frequency pole continues to exist and marks the hard gap in the spectral function for charge excitations.
 
@@
 \section{Nature of Low-Energy Excitations in Various Regimes}
-\subsection{Metallic Regime}
-\paragraph{Fermi liquid excitations, \(|W| < |W|^*\):}
-As discussed in Sec.~\ref{2CKEmerge}, the effective description of the impurity model for \(|W| > |W|^*\) becomes that of a 2CK.
+\subsection{Fermi liquid excitations, \(|W| < |W|^*\)}
+As discussed in Sec.~\ref{2CKEmerge}, the effective description of the impurity model for \(|W| > |W|^*\) becomes that of a two-channel Kondo (2CK) model.
 Prior to that (\(|W| < |W|^*\)), the entire Fermi surface continues to screen the impurity, and this leads to local Fermi liquid description of the impurity excitations.
@@
 
-\paragraph{Marginal Fermi liquid, \(|W| > |W|^*\):}
+\subsection{Marginal Fermi liquid, \(|W| > |W|^*\)}
 We have demonstrated in Subsection.~\ref{marginalFL} that the low-lying excitations of the pseudogap phase are described by a marginal Fermi liquid.
@@
 
-\paragraph{At the critical point, \(|W| \lesssim |W|^*\):}
-
-\subsection{Heisenberg model as a low-energy description of the insulator}
+\subsection{At the critical point, \(|W| \lesssim |W|^*\)}
+Crucially, we find that during the passage through the pseudogap phase, the nature of the non-Fermi liquid metal itself morphs; the marginal Fermi liquid description is found to break down at the transition, and is replaced by the non-Fermi liquid excitations of a Hatsugai-Kohmoto model.
+The singular nature of the excitations in this regime can be ascertained from the self-energy displaying divergent behaviour (see Subsection~\ref{hkmEmerge}).
+This can be attributed to the extremely non-local form of the impurity model (arising from the fact that it couples to only the nodal points in \(k-\)space).
+This divergent self-energy is consistent with our numerical calculations of the impurity self-energy which showed that the self-energy poles approach the \(\omega=0\) point as the system is tuned towards the transition.
+
+\subsection{Heisenberg model as a low-energy description of the Mott insulator}
 
@@
 These one-particle scattering processes lead to the emergence of a nearest-neighbour superexchange interaction.
-
+The calculation is a straightforward application of second order perturbation theory (Schrieffer-Wolff transformation).
+In order to allow virtual fluctuations that can lift the large ground state degeneracy and lower the energy, we consider (perturbatively) the effects of an irrelevant single-particle hybridisation that connects the nearest-neighbour sites.
+This perturbation Hamiltonian is therefore of the form
+\begin{equation}\begin{aligned}
+	H_t = \sum_\omega V(\omega) \mathcal{P}(\omega)~\sum_\sigma\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) ~,
+\end{aligned}\end{equation}
+where \(V(\omega)\) only acts on states at the energy scale \(\omega\); the renormalisation of \(V\) is encoded in the fact that \(V(\omega)\) is largest for the excited states and vanishes at low-energies: \(V(\omega \to 0) = 0\).
+
+We show the details in Appendix~\ref{heisenbergDerivation}.
+The final result is the emergence of the following effective Hamiltonian for the low-energy dynamics between any two nearst-neighbour sites \(i\) and \(j\):
+\begin{equation}\begin{aligned}
+	H_\text{eff} = 2\frac{V_H^2}{U/2}\left(2S_i^z S_j^z + S_i^+S_j^- + S_i^-S_j^+\right) = J_\text{eff} {\bf S}_i\cdot{\bf S}_j~,
+\end{aligned}\end{equation}
+where the effective antiferromagnetic Heisenberg coupling is \(J_\text{eff} = \frac{8V_H^2}{U}\) and \(V_H \equiv V(\omega \to U/2)\) is the impurity-bath hybridisation at energy scales of the order of the Mott gap, in the sense of an RG flow.
+
+\clearpage
+\section*{Appendices}
+\appendix
+\subsection{Marginal Fermi liquid excitations in a two-channel Kondo model}\label{mflDerivation}
+By considering minimal hopping into the conduction bath and treating the effects of this hopping perturbatively against the overscreened screened ground state (determined by an intermediate coupling \(J^*\)), the low-energy excitations above the ground state of the two-channel Kondo (2CK) model are described by the following Hamiltonian~\cite{Patra2023MCK}:
+\begin{eqnarray}
+	\label{nfl_terms}
+	H_\mathrm{eff} =& \frac{8t^2}{{J}}\left[\left(S^z_{0,1}\right)^2 S^+_{0,2} + \left(S^z_{0,2}\right)^2 S^+_{0,1}\right] \left(S^-_{1,1} + S^-_{1,2}\right) + \mathrm{h.c.};
+\end{eqnarray}
+where \({\boldsymbol S}_{i,l} = \frac{1}{2}\sum_{\sigma_1,\sigma_2}c^\dagger_{i,\sigma_1,l}{\boldsymbol \sigma}_{\sigma_1,\sigma_2}c_{i,\sigma_2,l}\) are spin operators for the \(i^\text{th}\) site on the \(l^\text{th}\) conduction channel (\(l\) can be 1 or 2 for a two-channel model).
+The labels \(\sigma_1\) and \(\sigma_2\) are spin indices that can be \(\pm 1\).
+The site index \(0\) represents the bath sites connected immediately to the impurity site.
+The operator \(c^\dagger_{i,\sigma,l}\) creates an electron with spin \(\sigma\) on the \(i^\text{th}\) site of the \(l^\text{th}\) conduction channel.
+
+We will Fourier transform this effective Hamiltonian into \(k-\)space:
+\begin{eqnarray}
+	\label{k_space_od}
+	\frac{2t^2}{J}\sum_{\left\{k_i,k_i^\prime\right\}}\sum_{\sigma, l} &\left(e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \mathrm{h.c.}\right) ~.\qquad
+\end{eqnarray}
+Such a three particle interaction term was also obtained for the NFL phase of the 2D Hubbard model from a URG treatment (see Appendix B of Ref.\cite{anirbanmott1}).
+The channel indices in Eq.~\ref{k_space_od} can be mapped to the normal directions in~\cite{anirbanmott1}.
+The 2 particle-1 hole interaction in Eq.~\ref{k_space_od} has a diagonal component which can be obtained by setting \(k=k^\prime, k_1 = k_2^\prime\) and \(k_2 = k_1^\prime\):
+\begin{eqnarray}
+	H_\mathrm{MFL} &= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{2t^2e^{i\left(k_1 - k_2\right)a}}{J} \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right) + \mathrm{h.c.}\nonumber\\
+	&= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{4t^2}{J} \cos a\left(k_1 - k_2\right)  \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right).\qquad 
+\end{eqnarray}
+The most dominant contribution comes from \(k_1 = k_2 = k^\prime\), revealing the non-Fermi liquid metal~\cite{cox_jarrell_two_channel_rev,Andrei1995}:
+\begin{eqnarray}
+	\label{mfl_large}
+	H^*_\mathrm{MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)~.
+\end{eqnarray}
+A non-local version of this effective Hamiltonian was found to describe the normal phase of the Mott insulator of the 2D Hubbard model, as seen from a URG analysis~\cite{anirbanmott1,anirbanmott2}.
+Following~\cite{anirbanmott1}, one can track the RG evolution of the dual coupling \(R_j = \frac{4t^2}{J_j}\) at the \(j^\mathrm{th}\) RG step, in the form of the URG equation
+\begin{eqnarray}
+	\Delta R_j =- \frac{R_j^2}{\omega - \epsilon_{j}/2 - R_j/8}~.
+\end{eqnarray}
+In the RG equation, \(\epsilon_{j}\) represents the energy of the \(j^\mathrm{th}\) isoenergetic shell. It is seen from 
+the RG equation that \(R\) is relevant in the range of \(\omega < \frac{1}{2}\epsilon_j\) that has been used throughout, leading to a fixed-point at \(R^*/8 = \omega - \frac{1}{2}\epsilon^*)\).
+The relevance of \(R\) is expected because the strong coupling \(J\) is irrelevant and \(R \sim 1/J\).
+
+The renormalisation in \(R\) leads to a renormalisation in the single-particle self-energy~\cite{anirbanmott1}. The \(k-\)space-averaged self-energy renormalisation is
+\begin{eqnarray}
+	\Delta \Sigma(\omega) = \rho {R^*}^2\int_0^{\epsilon^*} \frac{d\epsilon_j}{\omega - \epsilon_j/2 + R_j/8}~.
+\end{eqnarray}
+The density of states can be approximated to be \(N^*/R^*\), where \(N^*\) is the total number of states over the interval \(R^*\).
+As suggested by the fixed point value of \(R_j\), we can approximate its behaviour near the fixed point by a linear dependence on the dispersion \(\epsilon_j\).
+The two limits of the integration are the starting and ending points of the RG.
+We start the RG very close to the Fermi surface and move towards the fixed point \(\epsilon^*\).
+Near the starting point, we substitute \(\epsilon = 0\) and \(R = \omega\), following the fixed point condition.
+From the fixed point condition, we also substitute \(R^*/8 = \omega - \frac{1}{2}\epsilon^*\).
+On defining \(\bar \omega = N^* \left(\omega - \frac{1}{2}\epsilon^*\right)\), we can write
+\begin{eqnarray}
+	\label{self_energy}
+	\Delta \Sigma(\omega) \sim  \bar \omega \ln \frac{N^* \omega}{\bar \omega}~.
+\end{eqnarray}
+The self-energy also provides the quasiparticle residue for each channel\cite{anirbanmott1}:
+\begin{eqnarray}
+	Z(\bar\omega) = \left(2 - \ln \frac{2\bar\omega}{N^* \omega}\right) ^{-1}~.
+\end{eqnarray}
+As \(\omega \to 0\), the \(Z\) vanishes, implying that the ground state is {\it not adiabatically connected} to the Fermi gas in the presence of the NFL terms.
+This is the orthogonality catastrophe~\cite{varma2002singular,anderson_infraredcat,yamada_catastrophe,yamada1979orthogonality} in the two-channel Kondo problem, and it is brought about by the presence of the channel-non diagonal terms in Eq.~\ref{mfl_large}.
+
+\subsection{Emergence of Hatsugai-Kohmoto model near the NFL-Mott insulator transition}\label{hkmDerivation}
+As the bath interaction \(W\) is tuned through the L-PG phase, the nodal region is the last to decouple from the impurity.
+This allows us to write down a simpler Kondo model near the transition, where only the nodal region is hybridising with the impurity spin through Kondo interactions.
+This is done by retaining only those scattering processes \({\bf k}_1 \to {\bf k}_2\) that originate from and end at \(k-\)points within a small neighborhood of width \(|{\bf q}|\) around the four nodal points: \({\bf k}_1, {\bf k}_2 \in {\bf N} + {\bf q}, |{\bf q}| \ll \pi\), where \({\bf N}\) can be any one of the four nodal points \({\bf N}_{1} = \left(\pi/2, \pi/2\right), {\bf N}_{2} = \left(-\pi/2, \pi/2\right)\) and \({\bf N}_1 + {\bf Q}_1\) and \({\bf N}_{2} + {\bf Q}_2\), where \({\bf Q}_1 = \left(-\pi,-\pi \right)\) and \({\bf Q}_2 = \left( \pi, -\pi \right) \) are the two nesting vectors.
+We have already seen, in Subsection ~\ref{2CKEmerge}, that the pseudogap regime displays a decoupling of the Brillouin zone into sets of points that have no explicit connecting term in the Hamiltonian.
+Near the transition, the neighbourhoods of \({\bf N}_{1}\) and \({\bf N}_{1} + {\bf Q}_1\) form one such connected set, while the other two nodes \({\bf N}_{2}\) and \({\bf N}_{2} + {\bf Q}_2\) form another connected set, but these two sets are disconnected from each other, in the sense of a two-channel model.
+We also assume that the window of \({\bf q}\) is small enough so that the fixed point Kondo coupling values \(J^*({\bf q}_1, {\bf q}_2)\) for the scattering processes involving \({\bf q}_1\) and \({\bf q}_2\) can be replaced by an average value \(J^*\).
+
+With these considerations, the simplified low-energy model near the transition describing the Kondo scattering processes can be written as
+\begin{equation}\begin{aligned}
+	\tilde H_\text{imp-cbath} = J^*\frac{1}{2}\sum_{l=1,2}\sum_{{\bf q}_1, {\bf q}_2}\sum_{\alpha,\beta}{\bf S}_d\cdot{\boldsymbol \sigma}_{\alpha\beta}&\left(c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} + c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta} \right.
+\\
+&\left. - c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} - c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta}\right)~.
+\end{aligned}\end{equation}
+For scattering processes that involve two opposite nodal points (that is, connected by one of the nesting vectors \({\bf Q}_l\), the Kondo coupling is \(-J^*\), which explains the negative signs in the third and fourth terms.
+An explanation of the various dummy indices is in order.
+The label \(l\) can take values 1 or 2, allowing us to consider both the decoupled sets (associated with \({\bf N}_1\) and \({\bf N}_2\)).
+It also labels the nesting vectors \({\bf Q}_l\) associated with the two sets.
+\(\alpha\) and \(\beta\) indicate spin indices, and \({\bf q}_1\) and \({\bf q}_2\) represent incoming and outgoing momenta in the scattering processes.
+
+Because of the decoupling of the channel \(l=1\) and \(l=2\), we consider only the \(l=1\) channel for the rest of the calculations in this section, and we comment at the end on what the presence of two channels means for the results.
+In order to simplify the Hamiltonian, we define new fermionic operators
+\begin{equation}\begin{aligned}
+	\psi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} + c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~,
+	\phi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} - c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~,
+\end{aligned}\end{equation}
+The operator satisfy fermionic anticommutation relations:
+\begin{equation}\begin{aligned}
+	\left\{ \psi_{{\bf q},\sigma}, {\psi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left[\delta_{{\bf q}, {\bf q}^\prime} + \frac{1}{2}\left(\delta_{{\bf Q}_1 - {\bf q}, {\bf q}^\prime} + \delta_{{\bf q}, {\bf Q}_1 - {\bf q}^\prime}\right)  \right] \delta_{\sigma,\sigma^\prime} \\
+																							   &= \delta_{{\bf q}, {\bf q}^\prime}\delta_{\sigma,\sigma^\prime}~,\\
+	\left\{ \phi_{{\bf q},\sigma}, {\phi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left[\delta_{{\bf q}, {\bf q}^\prime} - \frac{1}{2}\left(\delta_{{\bf Q}_1 - {\bf q}, {\bf q}^\prime} + \delta_{{\bf q}, {\bf Q}_1 - {\bf q}^\prime}\right)  \right] \delta_{\sigma,\sigma^\prime} \\
+																				  &= \delta_{{\bf q}, {\bf q}^\prime}\delta_{\sigma,\sigma^\prime}~,\\
+	\left\{ \psi_{{\bf q},\sigma}, {\phi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left\{ \phi_{{\bf q},\sigma}, {\psi}^\dagger_{{\bf q}^\prime,\sigma} \right\} = 0~,
+\end{aligned}\end{equation}
+where both \({\bf q}\) and \({\bf q}^\prime\) are chosen from a small window around the nodes, so their difference is also small and it is therefore guaranteed that \(|{\bf q} + {\bf q}^\prime| \neq |{\bf Q}_1|\), rendering both \(\delta_{{\bf q}, {\bf Q}_1 - {\bf q}^\prime}\) and \(\delta_{{\bf Q}_1 - {\bf q}, {\bf q}^\prime}\) zero.
+For convenience, we define new number operators for the sum and relative degrees of freedom:
+\begin{equation}\begin{aligned}
+	s_{{\bf q},\sigma} = {\psi}^\dagger_{{\bf q}} {\psi}_{{\bf q}},~ r_{{\bf q},\sigma} = {\phi}^\dagger_{{\bf q}} {\phi}_{{\bf q}}~.
+\end{aligned}\end{equation}
+We then have the following useful relation between the corresponding number operators \(n = c^\dagger c\):
+\begin{equation}\begin{aligned}\label{numberOperatorRelation}
+	n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma} = s_{{\bf q}, \sigma} + r_{{\bf q},\sigma}~.
+\end{aligned}\end{equation}
+
+We find that the sum degrees of freedom \(s_{{\bf q},\sigma}\) do not enter the Kondo scattering Hamiltonian \(\tilde H_\text{imp-cbath}\) (for the single channel \(l=1\)), and it is expressed purely in terms of the relative degrees of freedom:
+\begin{equation}\begin{aligned}
+	\tilde H_\text{imp-cbath} = J^*\sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}{\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta}~.
+\end{aligned}\end{equation}
+We now proceed to rewrite the other parts of the Hamiltonian in terms of these new degrees of freedom. The kinetic energy can be written as
+\begin{equation}\begin{aligned}\label{kineticEnergy}
+	\tilde H_\text{cbath} &= \sum_{{\bf q},\sigma}\varepsilon_{{\bf N}_1 + {\bf q}}\left(n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q},\sigma}\right)\\
+						  &= \sum_{{\bf q},\sigma}\varepsilon_{{\bf N}_1 + {\bf q}}\left({\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma} + {\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma}\right)~,
+\end{aligned}\end{equation}
+We also consider a simplified form of the bath interaction (for the channel \(l=1\)), taking into account the density-density correlations in \(k-\)space:
+\begin{widetext}
+\begin{equation}\begin{aligned}
+	\tilde H_\text{cbath-int} =& -W\sum_{{\bf q},\sigma}\left(n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q},\sigma}\right) + W\sum_{{\bf q}_1,{\bf q}_2}\left(n_{{\bf N}_{1} + {\bf q}_1, \uparrow} + n_{{\bf N}_{1} + {\bf Q}_{1} - {\bf q}_1, \uparrow} \right) \left( n_{{\bf N}_{1} + {\bf q}_2, \downarrow} + n_{{\bf N}_{1} + {\bf Q}_{1} - {\bf q}_2, \downarrow} \right)~,\\
+	=& -W\sum_{{\bf q},\sigma}\left(s_{{\bf q},\sigma} + r_{{\bf q},\sigma}\right) + W\sum_{{\bf q}_1,{\bf q}_2}\left(s_{{\bf q}_1,\uparrow} + r_{{\bf q}_1,\uparrow}\right) \left(s_{{\bf q}_2,\downarrow} + r_{{\bf q}_2,\downarrow}\right)~.
+\end{aligned}\end{equation}
+\end{widetext}
+We used eq.~\ref{numberOperatorRelation} in order to obtain the final form.
+
+Since both \(\tilde H_\text{imp-cbath}\) and \(\tilde H_\text{cbath-int}\) commute with \(s_{{\bf q}, \sigma}\), we replace the local objects \(\sum_{\bf q}s_{{\bf q},\sigma}\) in \(\tilde H_\text{cbath-int}\) with \(\frac{1}{2}\) since the bath is always at half-filling.
+This results in a simplified Hamiltonian for just the \(\phi_{{\bf q},\sigma}\) degrees of freedom:
+\begin{equation}\begin{aligned}
+	\tilde H =& -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow} + \sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}J^*{\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta}
+\end{aligned}\end{equation}
+
+For bath interaction strength close to the critical value (\(W \lesssim W_c\)), the fixed point coupling value \(J^*\) is much smaller than \(W\).
+In order to obtain the gapless excitations of the system arising from the presence of the impurity site, we integrate out the impurity dynamics via a Schrieffer-Wolff transformation.
+The perturbation term \(\mathcal{V}\) then consists of Hamiltonian terms that modify the impurity configuration,
+\begin{equation}\begin{aligned}
+	\mathcal{V} = \sum_{{\bf q}_1, {\bf q}_2}J^*{S}_d^+{\phi}^\dagger_{{\bf q}_1 \downarrow} \phi_{{\bf q}_2 \uparrow} + \text{h.c.}~,
+\end{aligned}\end{equation}
+while the ``non-interacting" Hamiltonian is
+\begin{equation}\begin{aligned}
+	H_D &= -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow}~.
+\end{aligned}\end{equation}
+The renormalisation in the dynamics of \(b^\dagger_{\vec k,\sigma}\) are given by
+\begin{equation}\begin{aligned}
+	\Delta \tilde H &= \mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L,
+\end{aligned}\end{equation}
+where \(E_L\) is the energy of the ground state of \(H_D\), \(-(E_L - H_D)\) is the excitation energy of the state generated upon applying the perturbation \(\mathcal{V}\), and \(\mathcal{P}_{L(H)}\) projects onto the low(high)-energy subspace.
+For the present Hamiltonian, the low-energy state (associated with \(E_L\)) is the one that minimises the bath interaction term \(\tilde H_\text{cbath-int}\); since the coupling \(W\) is negative, the minimal configuration is one in which the local operators \(\sum_{{\bf q}}r_{{\bf q},\sigma}\) (for \(\sigma=\pm 1\)) are unity.
+This leads to the following low-energy state:
+\begin{equation}\begin{aligned}
+	\ket{L} = \frac{1}{N}\sum_{{\bf q}_1{\bf q}_2}\phi^\dagger_{{\bf q}_1, \uparrow}\phi^\dagger_{{\bf q}_2, \downarrow} \ket{0}
+\end{aligned}\end{equation}
+where \(\ket{0}\) is the \(r_{{\bf q} \uparrow} = r_{{\bf q} \downarrow} = 0\) state.
+The state \(\ket{L}\) is at zero energy.
+High-energy states are obtained by applying, on the state \(\ket{L}\), the excitation operator \(\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2,\bar\sigma}\) or its hermitian conjugate.
+The operator converts a double and a hole to spin states, incurring a total excitation cost of \(-W = |W|\).
+
+We now calculate the various terms in \(\Delta \tilde H\):
+\begin{equation}\begin{aligned}\label{kondoPert}
+	&\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L = \left(\frac{1}{2} + S_d^z\right) \sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*}^2}{-4W}\phi^\dagger_{{\bf q}_1,\downarrow}\phi_{{\bf q}_2, \uparrow} \left(\phi^\dagger_{{\bf q}_2,\uparrow}\phi_{{\bf q}_1, \downarrow} + (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\uparrow}\phi_{{\bf q}_2, \downarrow}\right)\\
+	&= -\sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*}^2}{4W}\left[r_{{\bf q}_1 \downarrow} \left(1 - r_{{\bf q}_2 \uparrow}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\uparrow}\phi^\dagger_{{\bf q}_1,\downarrow}\phi_{{\bf q}_2, \downarrow}\phi_{{\bf q}_2, \uparrow}\right]\\
+	&\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L = \sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*}^2}{-4W}\left[r_{{\bf q}_1 \uparrow} \left(1 - r_{{\bf q}_2 \downarrow}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\downarrow}\phi^\dagger_{{\bf q}_1,\uparrow}\phi_{{\bf q}_2, \uparrow}\phi_{{\bf q}_2, \downarrow}\right] \\
+\end{aligned}\end{equation}
+In both terms, we set \(S_d^z = 0\) owing to local SU(2) symmetry on the impurity site. In the same way, we treat the effects of the dispersion term (eq.~\ref{kineticEnergy}) to second order:
+\begin{equation}\begin{aligned}
+	\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L &= \sum_{{\bf q}, \sigma}\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W}\left[ {\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma}{\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma} + {\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma}{\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma}\right] \\
+																						 &= \sum_{{\bf q}, \sigma}\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W}\left[ s_{{\bf q},\sigma} \left(1 - r_{{\bf q},\sigma}\right) + r_{{\bf q},\sigma} \left(1 - s_{{\bf q},\sigma}\right)\right]~.
+\end{aligned}\end{equation}
+At the values of \({\bf q}\) for which \(\varepsilon_{{\bf N}_1 + {\bf q}} > 0\), we can set the number operator \(s_{{\bf q},\sigma} = 0\) (these positive energy modes are unoccupied in the ground state), while for \(\varepsilon_{{\bf N}_1 + {\bf q}} < 0\), we have \(s_{{\bf q},\sigma} = 1\):
+\begin{equation}\begin{aligned}\label{dispersionSecondOrder}
+	\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L = \sum_{{\bf q} \left(\varepsilon_{{\bf N}_1 + {\bf q}} > 0\right), \sigma}\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W} r_{{\bf q},\sigma} + \sum_{{\bf q} \left(\varepsilon_{{\bf N}_1 + {\bf q}} < 0\right), \sigma}\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W} \left(1 - r_{{\bf q},\sigma}\right)~.
+\end{aligned}\end{equation}
+
+The complete Hamiltonian (combining eqs.~\ref{dispersionSecondOrder} and \ref{kondoPert}) is
+\begin{equation}\begin{aligned}
+	\Delta \tilde H = \sum_{{\bf q}, \sigma}\text{sign}\left(\varepsilon_{{\bf N}_1 + {\bf q}}\right)\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W} r_{{\bf q},\sigma} + \sum_{{\bf q}_1,{\bf q}_2, \sigma}\frac{{J^*}^2}{-4W}\left[r_{{\bf q}_1 \sigma} \left(1 - r_{{\bf q}_2 \bar\sigma}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\bar\sigma}\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2, \sigma}\phi_{{\bf q}_2, \bar\sigma}\right]~.
+\end{aligned}\end{equation}
+
+\subsection{Heisenberg Model as a low-energy description of the tiled Mott insulator}\label{heisenbergDerivation}
 For simplicity, we consider two impurity sites labelled \(1\) and \(2\) associated with two nearest-neighbour auxiliary models. The ground state subspace is four-fold degenerate:
@@
 
-% \section{Topological nature of the transition}
-% Since the impurity charge hybridising with the bath contributes to the total Luttinger volume of the system~\cite{martin1982fermi}, decoupling of the impurity from the conduction bath leads to a difference in the value of the Luttinger volume between the local moment (LM) and the strong-coupling (SC) fixed points.
-If we define \(\mathcal{N}_L\) as the Luttinger volume with the spin-degeneracy accounted for, we can write
-% \begin{equation}\begin{aligned}
-% 	\label{lutt_change}
-% 	\mathcal{N}_L^\text{lm} - \mathcal{N}_L^\text{sc} = 1
-% \end{aligned}\end{equation}
-% where \(\mathcal{N}_L^\text{lm},\mathcal{N}_L^\text{sc}\) are the Luttinger volumes at the local moment and strong-coupling fixed points respectively.
-This equation expresses the fact that the Luttinger volume of the bath increases by \(1\) when the system is tuned from LM to SC, and this happens because the single-particle impurity excitation in the lower-Hubbard at the atomic limit gets transferred to the bath Greens function in the process.
-The quantity which tracks this transfer is therefore \(\mathcal{N}_\text{imp}\), the number of poles minus the number of zeros in the impurity Greens function at and below the Fermi surface:
-% \begin{equation}\begin{aligned}
-% 	\label{imp_count_def}
-% 	\mathcal{N}_\text{imp} = \begin{cases}
-% 		1 & \text{ at LM}\\
-% 		0 & \text{ at SC}
-% 	\end{cases}\implies \Delta \mathcal{N}_\text{imp} = 1
-% \end{aligned}\end{equation}
-% The Luttinger volume \(\mathcal{N}_L\) is related to this impurity count by the equation
-% \begin{equation}\begin{aligned}
-% 	\mathcal{N}_L = \mathcal{N} - \mathcal{N}_\text{imp}
-% \end{aligned}\end{equation}
-% where \(\mathcal{N}\) is the total number of electrons in the system, accounting for the spin degeneracy.
-If we keep this total number fixed (isolated system), the changes in the impurity count and Luttinger volume become constrained:
-% \begin{equation}\begin{aligned}
-% 	\Delta \mathcal{N}_L = - \Delta \mathcal{N}_\text{imp}~.
-% \end{aligned}\end{equation}
-% Eq.~\ref{imp_count_def} then readily implies eq.~\ref{lutt_change}.
-%
-% In order to connect this impurity topological change with the bulk model, we write the total number of particles in the bulk system in the following manner:
-% \begin{equation}\begin{aligned}
-% 	\mathcal{N} = \mathcal{N}_\text{loc} + \mathcal{N}_\text{deloc}
-% \end{aligned}\end{equation}
-% \(\mathcal{N}_\text{loc}\) is the number of real poles minus the number of zeros of the local Greens function.
-\(\mathcal{N}_\text{deloc}\) is the number of real poles minus the number of zeros of the \(k-\)space Greens functions.
-The former (latter) contributes only in the insulating (metallic) phase, because in the metallic (insulating) phase, the local (\(k-\)space) Greens function develop imaginary self-energy and the real poles in these Greens functions get replaced by imaginary poles.
-Together, these two terms accurately count the total number of particles in both these phases.
-These two terms are defined as
-% \begin{equation}\begin{aligned}
-% 	\mathcal{N}_\text{loc} = \sum_i \mathcal{N}_i = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_i(z)\right], ~ ~ ~\mathcal{N}_\text{deloc} = \sum_k \mathcal{N}_k = \oint \frac{dz}{2\pi i}n_F(z) \text{Tr}\left[G_k(z)\right] = \mathcal{N}_L
-% \end{aligned}\end{equation}
-% \(G_i(z)\) is the local Greens function at site \(i\) of the bulk model, and \(G_k(z)\) is the \(k-\)space Greens function in the bulk model.
-\(N_\text{deloc}\) is just the Luttinger volume \(\mathcal{N}_L\) of the bulk system.
-With this, the total number of particles in the bulk can be expressed as
-% \begin{equation}\begin{aligned}
-% 	\label{bulk_total}
-% 	\mathcal{N} = \sum_i \mathcal{N}_i + \mathcal{N}_\text{L}
-% \end{aligned}\end{equation}
-% From eq.~\ref{greens_func_relation}, we know that the bulk local Greens function is proportional to that of the auxiliary model, and that gives \(\sum_i \mathcal{N}_i = \mathcal{N}_\text{imp}\sum_i = \mathcal{N} \mathcal{N}_\text{imp}\).
-There we used the fact that for a half-filled system, the total number of sites is equal to the total number of particles in the system.
-Substituting this into eq.~\ref{bulk_total} and again using \(\Delta \mathcal{N} = 0\) gives
-% \begin{equation}\begin{aligned}
-% 	\mathcal{N} = \mathcal{N} \mathcal{N}_\text{imp} + \mathcal{N}_\text{L} \implies \Delta \mathcal{N}_\text{L} = - \mathcal{N} \Delta \mathcal{N}_\text{imp}
-% \end{aligned}\end{equation}
-% We already know that \(\Delta \mathcal{N}_\text{imp}=1\) across the transition, so we get
-% \begin{equation}\begin{aligned}
-% 	\mathcal{N}_L^\text{metal} - \mathcal{N}_L^\text{insulator} = \mathcal{N}\left(\mathcal{N}_\text{imp}^\text{sc} - \mathcal{N}_\text{imp}^\text{lm}\right) = \mathcal{N}
-% \end{aligned}\end{equation}
-% The metal-insulator transition is therefore characterised by a change in the topological quantity \(\mathcal{N}_L\).
-The topological nature arises from the fact that it can be expressed in terms of winding numbers related to the corresponding Greens functions.
-\(\mathcal{N}_\text{imp}\), which derives from the impurity Greens function \(G_d\), is related to the winding numbers of the curves \(\text{Det}[G_d^{-1}(\Gamma^<)]\) and \(\text{Det}[G_d^{-1}(\Gamma^0)]\).
-The winding number is simply the number of times this function encircles the origin when traced on the curves \(\Gamma^<\) and \(\Gamma^0\) that enclose all poles inside and on the Fermi surface respectively.
-An example of such a winding number is shown in fig.~\ref{imp_winding}.
-% \begin{figure}[!htb]
-% 	\centering
-% 	\includegraphics[width=0.4\textwidth]{windingNumbers.pdf}
-% 	\caption{The green lines describe the winding number related to the impurity Greens function, while the blue lines do it for the bath.
-At the local moment fixed point \(V=0\), the impurity has a winding number of 1 because the curve encircles the origin once.
-At the strong-coupling fixed point, this winding number becomes zero, indicated by the fact that the curve does not encircle the origin even once.
-The reduction in the winding number on the part of the impurity is directly linked to the increase in the winding number of the bath - it encircles the origin once at the local moment fixed point but twice at strong-coupling.}
-% 	\label{imp_winding}
-% \end{figure}
-
-\clearpage
-\section*{Appendices}
-\appendix
 \section{Effective action for the Hubbard-Heisenberg model and the eSIAM}

### 2025-04-17 TilingProjectDraft/tilingProject.tex
changed some figures

@@
 
-We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(U_b\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model).
+We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(W\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model).
 The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
@@
 \begin{itemize}
-	\item \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site,
+	\item \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}W\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site,
 	\item \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and
@@
 Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath.
-We have found that the e-SIAM has a stable local moment phase for \(U_b < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)).
+We have found that the e-SIAM has a stable local moment phase for \(W < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)).
 We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of an optical gap in the local spectral function beyond a certain value of interaction strength.
@@
 \begin{equation}\begin{aligned}\label{bathHamiltonian}
-	\mathcal{H}_\text{cbath} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2 \mathcal{Z}}U_b\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
+	\mathcal{H}_\text{cbath} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2 \mathcal{Z}}W\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
 \end{aligned}\end{equation}
@@
 	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d) \\
-	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{U_b}{2\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}\right]T({\bf r} - {\bf r}_d) \\
-	=& -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{U_b}{2\mathcal{Z}}\sum_{\bf r}\sum_{{\bf z}\in\text{NN}\left({\bf r}\right)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i}\sum_{{\bf r} \neq {\bf r}_i}\hat n_{{\bf r}_i,\sigma}\\
-	=& -\frac{1}{\sqrt\mathcal{Z}}(N-2)t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
+	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{W}{2\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}\right]T({\bf r} - {\bf r}_d) \\
+	=& -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{W}{2\mathcal{Z}}\sum_{\bf r}\sum_{{\bf z}\in\text{NN}\left({\bf r}\right)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i}\sum_{{\bf r} \neq {\bf r}_i}\hat n_{{\bf r}_i,\sigma}\\
+	=& -\frac{1}{\sqrt\mathcal{Z}}(N-2)t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2}W\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\mathcal{H}_\text{tiled} = -\frac{N-2}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>,\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} - \frac{1}{2}U_b\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}\\
+	\mathcal{H}_\text{tiled} = -\frac{N-2}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>,\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} - \frac{1}{2}W\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}\\
 	+ \sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]
@@
 	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}\\
-							 &= -\frac{1}{\sqrt\mathcal{Z}}(t + 2V)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2}\left(U + U_b\right)\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \left(\eta + 2\mu\right) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} + \frac{2}{\mathcal{Z}}J\sum_{\left< {\bf r}_i, {\bf r}_j\right>} {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j}
+							 &= -\frac{1}{\sqrt\mathcal{Z}}(t + 2V)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2}\left(U + W\right)\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \left(\eta + 2\mu\right) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} + \frac{2}{\mathcal{Z}}J\sum_{\left< {\bf r}_i, {\bf r}_j\right>} {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j}
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}\label{couplingsMappings}
-	\tilde t = t+2V,~~ \tilde U = U + U_b, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
+	\tilde t = t+2V,~~ \tilde U = U + W, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
 \end{aligned}\end{equation}
@@
 Some of us have shown in a previous work~\cite{Mukherjee_2023} that almost all aspects of the Mott metal-insulator transition on the infinite dimensional Hubbard model on the Bethe lattice (as seen, for example, from dynamical mean-field theory~\cite{georges1996}) can be captured from a simple extension of the Anderson impurity model (eSIAM).
-The extension involves including a local attractive interacting \(U_b\) on the conduction bath site coupled to the impurity site; by tuning the ratio of \(|U_b|\) and the Kondo coupling \(J\), we obtained an impurity phase transition from a screened phase to an unscreened local moment phase.
+The extension involves including a local attractive interacting \(W\) on the conduction bath site coupled to the impurity site; by tuning the ratio of \(|W|\) and the Kondo coupling \(J\), we obtained an impurity phase transition from a screened phase to an unscreened local moment phase.
 Since the impurity site of the auxiliary model is a representative of each correlated site on the lattice, the mapping to the lattice model then involves identifying the locally gapless impurity phase with the bulk gapless of the lattice model.
@@
 	S_\text{ES} = \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - t\sum_{\left<i,j \right> \in c,\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{i\sigma}(\tau)c_{j\sigma}(\tau) + \text{h.c.}\right] - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right]\\
-+ J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{U_b}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 ~,
++ J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{W}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 ~,
 \end{aligned}\end{equation}
@@
 	S^{d,z}_\text{eff} =& \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right] + J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) \\
-	&- \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{U_b}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 \\
+	&- \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{W}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 \\
 	&+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\sum_{\sigma}\Delta_{zz,\sigma}(\tau - \tau^\prime)c^\dagger_{z\sigma}(\tau)c_{z\sigma}(\tau^\prime)
@@
 One can go one step further and also remove the zeroth site in order to obtain a theory for the impurity site.
-With this choice, the cavity model now also includes the zeroth site, and hence contains the correlation term associated with \(U_b\).
+With this choice, the cavity model now also includes the zeroth site, and hence contains the correlation term associated with \(W\).
 The one-particle connection \(V\) will lead to a modified hybridisation \(\mathcal{F}\) for this effective theory; the Kondo terms will generate a susceptibility.
@@
 with the average computed in the interacting cavity model that has the impurity site removed.
-The interaction arises from the \(U_b-\)term.
+The interaction arises from the \(W-\)term.
 The susceptibility is also calculated in this interacting cavity model, and follows the same definition as in the bulk model:

### 2025-05-02 numerics/caller.jl
implemented Kondo coupling unravelling detection

@@ -26,7 +26,7 @@ NiceValues(size_BZ) = Dict{Int64, Vector{Float64}}(
                          33 => -1.0 .* [0, 2.8, 5.6, 5.7, 5.89, 5.92, 5.93] ./ size_BZ,
                          41 => -1.0 .* [0, 3.5, 7.13, 7.3, 7.5, 7.564, 7.6] ./ size_BZ,
                          49 => -1.0 .* [0, 4.1, 8.19, 8.4, 8.55, 8.77, 8.8] ./ size_BZ,
-                         57 => -1.0 .* [0, 5., 10.2, 10.6, 10.852] ./ size_BZ,
+                         57 => -1.0 .* [0, 4., 7., 10.2, 10.6, 10.852] ./ size_BZ,
                          69 => -1.0 .* [0, 6., 12.5, 13.1, 13.34, 13.4] ./ size_BZ,
                          77 => -1.0 .* [0., 14.04, 14.5, 14.99, 15.0] ./ size_BZ,
                         )[size_BZ]
@@ -105,6 +105,50 @@ function ScattProb(
     end
     println("\n Saved at $(saveNames).")
     run(`pdfunite $(saveNames) scattprob.pdf`)
+
+    node = map2DTo1D(π/2, π/2, size_BZ)
+    antinode = map2DTo1D(0., π/1, size_BZ)
+    mid = map2DTo1D(π/4, 3π/4, size_BZ)
+    saveNames = Dict(point => String[] for point in [node, antinode, mid])
+    for W_val in W_val_arr
+        for point in [node, antinode, mid]
+            matrix = kondoJArrays[W_val][point, :, end]
+            matrix[abs.(matrix) .< 1e-10] .= NaN
+            matrix[matrix .> 1e-10] .= 1
+            matrix[matrix .< -1e-10] .= -1
+            push!(saveNames[point], 
+                  plotHeatmap(matrix, 
+                              (x_arr, x_arr),
+                              (L"$ak_x/\pi$", L"$ak_y/\pi$"),
+                              L"$\Gamma/\Gamma_0$", 
+                              getlabelInt(W_val, size_BZ), 
+                              colmap[2:end];
+                              line=Tuple{Number, Number}[(kx, ky) for kx in -1:0.01:1 for ky in -1:0.01:1 if abs(kx + ky) == 1 || abs(kx - ky) == 1],
[…]

### 2025-05-02 numerics/source/plotting.jl

@@ -64,7 +64,9 @@ function plotHeatmap(
         figSize::NTuple{2, Int64}=(200, 200),
         figPad::Union{NTuple{4, Float64}, Float64}=0.,
         colorScale::Function=identity,
-        marker::Union{Nothing, Vector{Float64}}=nothing,
+        marker::Union{Nothing, NTuple{2, Float64}}=nothing,
+        line::Vector{NTuple{2, Number}}=NTuple{2, Number}[],
+        legendPos::NTuple{2, Symbol}=(:top, :right),
     )
 
     if isnothing(colorbarLimits)
@@ -86,14 +88,16 @@ function plotHeatmap(
              colorscale=colorScale,
              colorrange=colorbarLimits,
             )
-    if !isnothing(marker)
-        hlines!(ax, marker[2], color=:gray, linestyle=:dash)
-        vlines!(ax, marker[1], color=:gray, linestyle=:dash)
-    end
-
-    gl = GridLayout(figure[1, 1], tellwidth = false, tellheight = false, valign=:top, halign=:right)
+    gl = GridLayout(figure[1, 1], tellwidth = false, tellheight = false, valign=legendPos[1], halign=legendPos[2])
     Box(gl[1, 1], color = RGBAf(0, 0, 0, 0.4), strokewidth=0, strokecolor=RGBAf(0, 0, 0, 0.8))
     Label(gl[1, 1], annotation, padding = (5, 5, 5, 5), fontsize=div(FONTSIZE, 1.3), color=:white)
+
+    if !isempty(line)
+        scatter!(ax, line .|> first, line .|> last, color = :gray, markersize=4)
+    end
+    if !isnothing(marker)
+        scatter!(ax, marker..., color=:orange, markersize=20)
+    end
 
     Colorbar(figure[1, 2], hm)
     resize_to_layout!(figure)

### 2025-05-02 numerics/HKMSpectralFunction.jl
added real space correlations function

@@ -1,24 +1,0 @@
-using Plots
-
-function GreensFunction(
-        freqValues::Vector{Float64},
-        correlation::Number,
-        epsilonValues::Vector{Float64},
-        broadening::Number,
-    )
-    return [0.5 ./ (freqValues .- epsilon .+ correlation / 2 .+ 1im .* broadening) .+ 0.5 ./ (freqValues .- epsilon .- correlation / 2 .+ 1im .* broadening) for epsilon in epsilonValues]
-end
-
-
-W = 1
-epsilonValues = range(-W/2, W/2, length=1000) |> collect
-freqValues = collect(range(-2, 2, length=1000))
-freqPlot = 0.5
-xlims!(p, (-freqPlot, freqPlot))
-lstyles = [:solid, :dash, :dashdot]
-for (i, U_by_W) in enumerate([0.99, 1, 1.111])
-    greensFunctionArr = GreensFunction(freqValues, U_by_W * W, epsilonValues, 0.001)
-    specFunc = sum([-imag(g) for g in greensFunctionArr])
-    plot!(p, specFunc, label="U/W=$(U_by_W*W)", linestyle=lstyles[i])
-end
-display(p)

### 2025-05-02 numerics/caller.jl

@@ -407,12 +407,17 @@ function AuxiliaryRealSpaceEntanglement(
         loadData::Bool=false,
     )
     x_arr = get_x_arr(size_BZ)
-    W_val_arr = NiceValues(size_BZ)[[1, 5]]
+    W_val_arr = range(0.95 * pseudogapStart(size_BZ), pseudogapEnd(size_BZ), length=20) |> collect
+    #=W_val_arr = NiceValues(size_BZ)[[1,3,5]]=#
     @time kondoJArrays, dispersion = RGFlow(W_val_arr, size_BZ; loadData=true)
-    saveNames = Dict(name => [] for name in ["I2_real"])
-    plotTitles = Dict("I2_di" => L"$I_2(d, {\bf r})$",
-                     )
-    corrResults = Tuple{LaTeXString, Vector{Float64}}[]
+
+    SF_di = Tuple{LaTeXString, Vector{Float64}}[]
+    I2_di = Tuple{LaTeXString, Vector{Float64}}[]
+    ZZ_di = Tuple{LaTeXString, Vector{Float64}}[]
+    I2_d0 = Float64[]
+    Sdz = Float64[]
+    xvals1 = nothing
+    xvals2 = nothing
     for W_val in W_val_arr
         hamiltDetails = Dict(
                              "dispersion" => dispersion,
@@ -423,31 +428,94 @@ function AuxiliaryRealSpaceEntanglement(
                              "globalField" => GLOBALFIELD,
                             )
         effective_Wval = -0.0
-        effectiveNumShells = 1
+        effectiveNumShells = numShells
         effectiveMaxSize = maxSize
         savePath = joinpath(SAVEDIR, "$(W_val)-$(effective_Wval)-$(size_BZ)-$(effectiveNumShells)-$(maxSize)-$(bathIntLegs)-I2-di.jld2")
         hamiltDetails["W_val"] = effective_Wval
         println("\n W = $(W_val), eff_W=$(effective_Wval), $(effectiveNumShells) shells, maxSize = $(effectiveMaxSize)")
-        r, x_arr = AuxiliaryRealSpaceEntanglement(
+        corrResults, xvals1, xvals2 = AuxiliaryRealSpaceEntanglement(
                                                     hamiltDetails,
                                                     effectiveNumShells,
                                                     effectiveMaxSize; 
                                                     savePath=savePath,
                                                     addPerStep=1,
-                                                    loadData=loadData
[…]

### 2025-05-02 numerics/source/plotting.jl

@@ -1,8 +1,7 @@
 using CairoMakie, Random, Measures, LaTeXStrings, ColorSchemes
 
 const FONTSIZE = 28
-# set_theme!(theme_latexfonts())
-set_theme!(merge(theme_light(), theme_latexfonts()))
+set_theme!(theme_latexfonts())
 update_theme!(
               figure_padding = 0,
               fontsize=FONTSIZE,
@@ -14,8 +13,8 @@ update_theme!(
                 spinewidth = 1.5,
                 xticklabelsize = 24,
                 yticklabelsize = 24,
-                xminorgridvisible=false,
-                xmajorgridvisible=false,
+                xgridvisible=false,
+                ygridvisible=false,
                      ),
               ScatterLines = (
                        linewidth = 6,
@@ -28,6 +27,9 @@ update_theme!(
                         patchsize=(50,20),
                         halign = :right,
                         valign = :top,
+                        labelsize = 18,
+                        backgroundcolor=(:gray, 0.2),
+                        framecolor=:transparent,
                        ),
              )
 
@@ -64,7 +66,7 @@ function plotHeatmap(
         figSize::NTuple{2, Int64}=(200, 200),
         figPad::Union{NTuple{4, Float64}, Float64}=0.,
         colorScale::Function=identity,
-        marker::Union{Nothing, NTuple{2, Float64}}=nothing,
+        marker::Union{Nothing, Vector{Float64}}=nothing,
         line::Vector{NTuple{2, Number}}=NTuple{2, Number}[],
         legendPos::NTuple{2, Symbol}=(:top, :right),
     )
@@ -142,24 +144,24 @@ end
 
 
 function plotLines(
-        nameValuePairs::Vector{Tuple{LaTeXString, Vector{Float64}}},
-        xvalues::Vector{Float64},
+        nameValuePairs::Union{Vector{Tuple{LaTeXString, Vector{Float64}}}, Vector{Tuple{String, Vector{Float64}}}},
+        xvalues::Union{Vector{Int64}, Vector{Float64}},
         xlabel::LaTeXString,
         ylabel::LaTeXString,
         saveName::String;
         ylimits::Union{Nothing, NTuple{2, Float64}}=nothing,
         xlimits::Union{Nothing, NTuple{2, Float64}}=nothing,
         scatter::Bool=false,
[…]

### 2025-05-02 numerics/source/probes.jl

@@ -204,32 +204,51 @@ end
 
 @everywhere function IterDiagRealSpace(
         hamiltDetails::Dict,
-        realSpaceKondoArray::Array{Float64, 2},
+        realKondo1D::Vector{Dict{NTuple{2, Int64}, Float64}},
         maxSize::Int64,
-        sortedIndices::Vector{Int64},
-        calculateFor::Vector{Int64},
+        numBathSites::Int64,
         addPerStep::Int64,
     )
-    hamiltonian = KondoModel2D(realSpaceKondoArray, sortedIndices, HOP_T)
-    mutInfoDefDict = Dict("I2-d-$(i)" => ([1, 2], [2 * i + 1, 2 * i + 2]) for i in calculateFor)
-    indexPartitions = [4]
-    while indexPartitions[end] < 2 * length(sortedIndices)
-        push!(indexPartitions, indexPartitions[end] + 2 * addPerStep)
+    numChannels = length(realKondo1D)
+    #=for i in 1:2=#
+    #=    for (k, v) in realKondo1D[i]=#
+    #=        realKondo1D[i][k] = 10.=#
+    #=    end=#
+    #=end=#
+    hamiltonian = KondoModel(numBathSites, HOP_T, realKondo1D)
+
+    mutInfoSites = 1:2:numBathSites
+    mutInfoDefDict = Dict("I2-d-$(i)" => ([1, 2], [3 + 2 * numChannels * (i-1), 4 + 2 * numChannels * (i-1)]) for i in mutInfoSites)
+    spinFlipCorrDefDict = Dict("SF-d-$(i)" => [("+-+-", [1, 2, 4 + 2 * numChannels * (i-1), 3 + 2 * numChannels * (i-1)], 0.5), ("+-+-", [2, 1, 3 + 2 * numChannels * (i-1), 4 + 2 * numChannels * (i-1)], 0.5)] for i in 1:numBathSites)
+    isingCorrDefDict = Dict("ZZ-d-$(i)" => [("nn", [1, 3 + 2 * numChannels * (i-1)], 0.25), ("nn", [1, 4 + 2 * numChannels * (i-1)], -0.25), ("nn", [2, 3 + 2 * numChannels * (i-1)], -0.25), ("nn", [2, 4 + 2 * numChannels * (i-1)], 0.25)] for i in 1:numBathSites)
+    Sdz = Dict("Sdz" => [("n", [1], 0.5), ("n", [2], -0.5)])
+    corrDefDict = Sdz
[…]

### 2025-05-02 TilingProjectDraft/manuscript.tex
latest version of manuscript and notes, with most of the figures added

\documentclass[%
 reprint,
superscriptaddress,
groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
prl
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{braket}
\usepackage{color}
\graphicspath{{./figures/}}
\bibliographystyle{apsrev4-2}

\begin{document}

\title{Pseudogapped non-Fermi liquid phase arising from Kondo breakdown at the Mott transition}

%\title{What lies between a Fermi liquid and a Mott insulator in two dimensions? Insights from an impurity model}% Force line breaks with \\

\author{Abhirup Mukherjee}
\author{Siddhartha Lal}
\affiliation{%
 Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
}%

\date{\today}
\begin{abstract}
We present an auxiliary model approach that illuminates the centrality of the pseudogap phenomenon in the Mott transition of the Hubbard-Heisenberg model on the half-filled square lattice. Passage from Fermi liquid metal to Mott insulator involves two stages: the first involves a systematic unraveling of Kondo screening due to frustrating charge fluctuations in the conduction bath of the underlying lattice-embedded quantum impurity model. The unraveling destabilises the Fermi liquid, culminating in disconnection of the Fermi surface by gapping the antinodes. In the second stage, an emergent pseudogap phase arises from an effective two-channel Kondo problem in the underlying impurity model. The resulting momentum space Fermi arcs possess non-Fermi liquid excitations proximate to a critical Fermi surface. Upon approaching the transition, the nature of this exotic metal evolves with shrinking size of the arcs to a singular nodal non-Fermi liquid along with the onset of long-ranged real-space entanglement and spin-flip correlations. This reveals the Mott transition on the square lattice to be well beyond the paradigm of local quantum criticality.
\end{abstract}

\maketitle

\paragraph*{Introduction.}
The origin of the pseudogap and strange metal phases of the cuprates continue to be hotly debated topics in the context of high-temperature superconductivity~\cite{keimer2015quantum,ProustTaillefer2019}. The anomalous pseudogap (PG) phase, observed most prominently in the cuprates, exhibits nodal-antinodal dichotomy with spectral weight being concentrated on Fermi arcs around the node~\cite{loeserKapitulnik1996,Norman1998,Hashimoto2014}. While several methods have observed a PG in the Hubbard model ~\cite{KyungKotliar2006,MacridinAzevedo2006,WuFerrero2018,anirbanmott2,HilleAndergassen2020}, there is no general consensus yet regarding various aspects of the PG phase, such as its relation to the Mott insulating and superconducting phases proximate to it, how it evolves from weak-coupling to strong-coupling, and whether the nodal-antinodal dichotomy is intrinsic to the model.

In order to investigate the precise mechanism of transition/crossover connecting the metallic phases with the Mott insulating phase, we present a new auxiliary model method to study correlated electronic systems, and apply it to the particle-hole symmetric Hubbard-Heisenberg model to investigate the origin and nature of its pseudogap phase and the subsequent transition into a Mott insulator. The method requires identifying an appropriate impurity model which can faithfully capture the physics of lattice model we are trying to solve. Passage to the bulk model is accomplished by applying lattice translation operators on the impurity model, which makes it possible to relate various computables of the auxiliary model to those of the lattice model.

Our approach differs from dynamical mean-field approximation based methods (specifically the cellular and cluster-based avatars) in the fact there no self-consistency condition that needs to be imposed - the lattice model is explicitly constructed from a {\it lattice-embedded} impurity model. While this makes the impurity model trickier to solve, it makes more transparent the underlying local physics arising from correlations, and provides increased momentum-space resolution which is crucial for studying PG physics. Indeed, an important conclusion of our work that results from this is that the Mott transition on the square lattice appears to be well beyond the paradigm of local quantum criticality, due to the onset of long-ranged real-space entanglement and spin-flip correlations close to the transition.

\paragraph*{A lattice-embedded impurity model.}
%Crucial to our method is the choice of an impurity auxiliary model that is able 
In order to capture important local aspects of electronic correlations in the lattice model,  
%Some of us have shown in a previous work
%~\cite{Mukherjee_2023} that various aspects of the Mott metal-insulator transition on the infinite dimensional Hubbard model on the Bethe lattice (as seen, for example, from dynamical mean-field theory~\cite{georges1996}) can be captured from the breakdown of the strongly coupled Kondo phase of a simple extension of the Anderson impurity model (eSIAM). 
%Building on this insight, 
we embed an extended Anderson impurity 
%spin-$1/2$ moment ${\bf S}_d$ 
into the lattice of a half-filled 2D conduction bath (with nearest-neighbour hopping). This builds on insight 
%of an earlier work
\cite{Mukherjee_2023} that various aspects of the Mott %metal-insulator 
transition on the %infinite-dimensional 
Hubbard model on the Bethe lattice in infinite dimensions (as seen %, for example, 
from 
%dynamical mean-field theory
DMFT~\cite{georges1996}) can be captured from the breakdown of the strongly coupled Kondo phase of a simple extension of the Anderson impurity model (eSIAM). 
%This lowers the \(s-\)wave symmetry of Kondo interactions (on, say, an infinite-dimensional Bethe lattice) down to the \(C_4\) symmetry of the 2D square lattice.

In capturing the Mott transition, we focus on the %large-$U$ 
limit of large local correlations within the impurity model, where the impurity-bath hybridisation occurs through an antiferromagnetic Kondo coupling ($J>0$). The model is described by the Hamiltonian
\begin{equation}\begin{aligned}\label{impurityModel}
	\mathcal{H}_\text{aux} = H_\text{cbath} + H_\text{imp-cbath} + H_\text{cbath-int}~,
\end{aligned}\end{equation}
where $H_\text{cbath} = -2t\sum_{{\bf k}}\left[\cos(ak_x) + \cos(ak_y)\right] c^\dagger_{{\bf k},\sigma}c_{{\bf k},\sigma}$ is the kinetic energy for conduction bath tight-binding electrons ($c^\dagger_{{\bf k},\sigma}$) on a half-filled square lattice, and the impurity spin-1/2 moment (${\bf S}_d$) interacts with four nearest neighbour sites (henceforth labelled as \textit{zeroth} sites with index $Z$) 
%in \(H_\text{imp-cbath}\) 
through local Kondo terms of uniform strength \(H_\text{imp-cbath} =\frac{1}{2} J\sum_{\sigma_1,\sigma_2}\sum_{Z} {\bf S}_d\cdot c^\dagger_{Z\sigma_1}{\boldsymbol \tau}_{\sigma_1,\sigma_2} c_{Z\sigma_2}\).
%is the impurity-bath Kondo interaction. 
%and \(H_\text{cbath-int} = -\frac{W}{2}\sum_{Z} \left(n_{Z\uparrow} - n_{Z\downarrow}\right)^2\). 
%is a local intra-bath correlation that 
%models minimally the correlated nature of the conduction bath. 
%The index \(Z\) sums over all four nearest-neighbour sites of the impurity site, henceforth referred to as bath {\it zeroth} sites). 
A minimal model for correlations within the conduction bath that frustrate the Kondo screening is given by the third term:
%$H_\text{cbath-int}$ 
%represents local correlations on the four bath zeroth sites, 
\(H_\text{cbath-int} = -\frac{W}{2}\sum_{Z} \left(n_{Z\uparrow} - n_{Z\downarrow}\right)^2\). 
%, again of uniform strength. 
%In the above definitions, \(c^\dagger_{d\sigma}\) is the impurity site creation operator (for spin \(\sigma \)), while \(c^\dagger_{{\bf k}\sigma}\) is the conduction bath creation operator (for momentum \({\bf k}\) and spin \(\sigma\)).
The 2D structure of the impurity model, and its distinction from the infinite-dimensional counterpart, becomes apparent upon Fourier transforming the Kondo coupling to ${\bf k}$-space (with lattice spacing set to unity):
%once we transform the Hamiltonian to momentum space:
\begin{equation}\begin{aligned}
	J_{{\bf k}, {\bf k}^\prime} = \frac{J}{2}&\left[\cos\left({\bf k}_x - {\bf k}^\prime_x\right) + \cos\left({\bf k}_y - {\bf k}^\prime_y\right)\right]~,
\end{aligned}\end{equation}
with $J>0$.
%where the subscripts \(x\) and \(y\) represent components of the momenta vector, and the lattice spacing has been set to unity. This form shows that The Kondo coupling 
Clearly, $J_{{\bf k}, {\bf k}^\prime}$ is 
%no longer in
dependent on the exchange of momentum, and encodes the $C_{4}$ lattice symmetry. 
%geometry. Throughout the work
%In all that follows, we set the lattice spacing to unity.

\paragraph*{Reconstructing the Hubbard-Heisenberg model.} %from the auxiliary model: Formal prescription of our method.}
We will now define the {\it tiling} (or periodisation) procedure by which we recreate the lattice model 
%by using instances of 
from the 
%auxilliary
impurity model Hamiltonian. 
%In order to identify a 
For a {\it unit cell} 
%for 
of the tiling, 
%procedure, 
we consider an impurity model \(\mathcal{H}_\text{aux}({\bf r}_d)\) that has the impurity site at a reference site \({\bf r}_d\) of our lattice. In order to create the bulk model, we translate the unit cell across all sites of the lattice:
\begin{equation}\begin{aligned}
	\label{tilingPrescription}
	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}T^\dagger({\bf r})\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r}) - N\mathcal{H}_\text{cbath},
\end{aligned}\end{equation}
where \({\bf r}\) sums over all lattice sites, and $T({\bf r})$ is a many-body translation operator that translates all 
%electrons 
coordinates by a vector \({\bf r}\). Further details of the tiling procedure are provided in the Supplemental Material~\cite{suppmat}.
%We have removed extra copies of conduction bath kinetic energy \(\mathcal{H}_\text{cbath}\) that were added during the translation operations. 
Implementing this procedure for the impurity model defined above (eq.~\ref{impurityModel}) generates a {\it Hubbard-Heisenberg} lattice model in two spatial dimensions:
\begin{equation}\begin{aligned}
		\mathcal{H}_\text{tiled} &= -\frac{1}{\sqrt\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma} \\
        &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
\end{aligned}\end{equation}
%where the tilde symbol indicates that the 
with parameters for the lattice model that are related to those in $\mathcal{H}_\text{aux}$
%the auxiliary model
~\cite{suppmat}. 
%By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to one another. 
The form of the eigenstates of $H_{\text{tiled}}$
%the lattice Hamiltonians obtained using eq.~\ref{tilingPrescription} 
are dictated by a many-body version of Bloch's theorem~\cite{stoyanova}. Further, the relation between Hamiltonians and eigenstates of the auxiliary and tiled models can be exploited in obtaining equal-time correlation functions and
%from the auxiliary model to the lattice model, as well as equal-time correlations and 
entanglement measures of the latter from the former~\cite{suppmat}.
%such entanglement entropy and mutual information.
\begin{figure}
    \centering
    \includegraphics[width=0.49\linewidth]{SF-3.pdf}
    \includegraphics[width=0.49\linewidth]{kspaceDOS-3.pdf}
    \caption{Left: $k-$space resolved spin-spin correlation $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$, in the peudogap phase, confirmed from the fact that only a part of the Fermi surface screens the impurity, the antinodes being the first to decouple from the impurity. This leads, through our tiling relations, to a $k-$space resolved gap on the lattice model, as seen from the DOS (right panel). The region around the antinode of the lattice Fermi surface gets replaced by a Luttinger surface of zeros.}
    \label{spinCorr}
\end{figure}

\paragraph*{Pseudogapping transition from Kondo breakdown.} To obtain various low-energy phases of the impurity model, we perform a scaling analysis of the associated Hamiltonian using the recently developed 
unitary renormalisation group (URG) method \cite{anirbanurg1}. The URG
%method 
proceeds by resolving quantum fluctuations at $T=0$ involving high-energy degrees of freedom in systems of correlated fermions~\cite{santanukagome,1dhubjhep,anirbanmott2,anirbanmott1,siddharthacpi,anirban_kondo,Patra_2023,anirbanurg2}, leading to a low-energy Hamiltonian with renormalised couplings and emergent degrees of freedom. 
%The method has been applied successfully to a variety of problems involving correlated fermions~\cite{santanukagome,1dhubjhep,anirbanmott2,anirbanmott1,siddharthacpi,anirban_kondo,Patra_2023,anirbanurg1,anirbanurg2}; 
We present the results for the present impurity model here, and the details of the calculation are presented in \cite{suppmat}. 
%We find that 
The renormalisation in the %momentum
${\bf k}$-resolved Kondo coupling \(J^{(j)}_{{\bf k}_1, {\bf k}_2}\) at the \(j^\text{th}\) RG step is obtained as
\begin{equation}\begin{aligned}\label{KondoRGequation}
	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}~,
\end{aligned}\end{equation}
where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, the sum is over all momentum states \({\bf q}\) in the particle sector (PS) of the energy shell \(\varepsilon_j\) (i.e., all states 
%that are 
occupied at \(T=0\) and in the absence of any quantum fluctuations), and  \({\bf \bar q} = {\bf q} + {\boldsymbol \pi}\). The bath interaction coupling $W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}$ is found to be marginal under these transformations. While the complexity of the RG equation for $J_{{\bf k}_1, {\bf k}_2}$ (eq.\eqref{KondoRGequation}) is clarified through a detailed numerical evaluation, the structure of the equation is qualitatively similar to its counterpart in a study of the Mott MIT in infinite dimensions~\cite{Mukherjee_2023}. This permits the broad conclusion that for the case of attractive bath interactions $(W<0)$, the frustration of Kondo screening due to charge fluctuations (arising from $W$) lead to the Mott metal-insulator transition.

%As we 
Upon tuning the ratio of the bath and Kondo interactions ($W/J$) from zero to negative values, we observe that the following phases are emergent in the impurity model from the competition between the competing $J$ and $W$ couplings in eq.~\eqref{KondoRGequation}- (i) for $W/J<(W/J)_{\text{PG}}$, a local Fermi liquid phase (where the entirety of the Fermi surface participates in Kondo screening), (ii) for $\frac{W}{J} \in [(\frac{W}{J})_{\text{PG}}, (\frac{W}{J})_c]$, a local pseudogapped phase where disconnected parts of the Fermi surface around the node participate in Kondo screening, and (iii) a local moment phase for $\frac{W}{J} > (\frac{W}{J})_c$, where the impurity remains unscreened at low-energies. These can be visualised from $k-$space resolved spin correlations $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$; see Fig.~\ref{spinCorr} for $\chi_s(d,{\bf k})$ in the PG. The values $(W/J)_{\text{PG}}$ and $(W/J)_c$ are hence defined as the entry into and exit from
%boundaries of 
the pseudogap phase. %Using our 
Upon mapping to the lattice model via tiling, we %consequently 
observe that the $T=0$ Mott transition 
%in $k-$space for 
of the 2D Hubbard-Heisenberg model proceeds from Fermi liquid to Mott insulator through an intervening pseudogap phase
%. obtain an $k$-space pseudogapped phase 
with a partially gapped Fermi surface (i.e., a vanishing electronic density of states around the antinodal regions, Fig.~\ref{spinCorr}, right panel). 
%This constitutes one of the main results of our work, and 
We now lay out the mechanism leading to the formation of the pseudogap. 
%it shows that the breakdown of Kondo screening on the 
%a realistic 2D square lattice very naturally gives rise to a pseudogapped phase with Fermi arc-like behaviour. 
%The local Fermi liquid and local moment phases for the impurity model correspond, respectively, to Fermi liquid and Mott insulating phases on the lattice.

\paragraph*{Unraveling of Kondo screening.} 
% As shown in Fig.~\ref{rgProgression}, the $k-$space anisotropic nature of the Kondo breakdown process 
% %in this model 
% can be visualised in terms of zeros of $J_{{\bf k}_1, {\bf k}_2}$.
% %the Kondo coupling in $k-$space. 
% Consider processes $J_{{\bf k}_N, {\bf k}}$ that involve spin-flip scattering between the node ${\bf k}_N = (\pi/2, \pi/2)$  and a general wavevector ${\bf k}$. 
As shown in Fig.~\ref{rgProgression}, the $k-$space anisotropic nature of the Kondo breakdown process 
can be visualised in terms of zeros of $J_{{\bf k}_N, {\bf k}}$, involving spin-flip scattering between the node ${\bf k}_N = (\pi/2, \pi/2)$  and a general wavevector ${\bf k}$. 
At $W/J=0$, $J_{{\bf k}_N, {\bf k}}$ vanishes if ${\bf k}$ is either any of the antinodes or adjacent nodes. 
%As 
Tuning $W/J$ %is tuned 
towards $(W/J)_{\text{PG}}$ leads to an unraveling of Kondo screening:
%the beginning of the pseudogap, we find that 
$J_{{\bf k}_N, {\bf k}}$ for ${\bf k}$ close to the adjacent nodes turn RG irrelevant first, and a patch of zeros subsequently appears in $J_{{\bf k}_N, {\bf k}}$ around this point (Fig. \ref{rgProgression} (left) panel). %This is the first step towards the decoupling of $J_{{\bf k}_1, {\bf k}_2}$ connecting adjacent quadrants of the Brillouin zone quadrants. 
%that is described in more detail in a later section.
Tuning $W/J$ further extends the patch of zeros
%systematic decoupling of 
in $J_{{\bf k}_1, {\bf k}_2}$ for all ${\bf k}_{1}$ lying between a given node and the nearest antinodes (Fig. \ref{rgProgression} (center) and (right) panels), visualising a systematic decoupling of $J_{{\bf k}_1, {\bf k}_2}$ connecting adjacent quadrants of the Brillouin zone quadrants. 
%via an outwards progression of the patch of zeros 
%from the nodal towards 
%the single zeroes on the nearest antinodal regions . 
Precisely At $W/J=(W/J)_{\text{PG}}$, the antinode joins this connected region of zeros in $J_{{\bf k}_1, {\bf k}_2}$, %and this coincides 
marking (within our numerical precision) to the decoupling of the antinodes from all other points in the neighbourhood of the Fermi surface. This is an interaction-driven Lifshitz transition of the Fermi surface, and marks entry into a pseudogap phase possessing Fermi arcs~\cite{WuFerrero2018}. Importantly, it coincides with an emergent two-channel Kondo impurity model, where each channel corresponds to a pair of Fermi arcs on opposite faces of the conduction bath Fermi surface. 
%At this point, $J(k_N, k)$ is distributed through two disconnected non-zero patches, in the quadrant of $k_N$ and in the opposite quadrant. 
The pseudogap expands by shrinking these disconnected Fermi arcs towards the respective nodes, leading to nodal metals whose disappearance marks the Mott transition. 
%[TODO That the unraveling begins and ends at zeros of the Kondo coupling reveals the role of Fermi surface topology in obtaining the pseudogap~\cite{WuFerrero2018}.]

\begin{figure}[htpb]
    \centering
    \includegraphics[width=\linewidth]{zerosFlow.pdf}
    \caption{Progression of Kondo couplings into decoupling of adjacent quadrants and the beginning of pseudogap. This is shown by tracking how $J(k_N, k)$ (with $k_N$ pivotted at the top left node and $k$ (depicted as an orange circle) moving along the top right Fermi surface arm) vanishes at different values of $W$ for different values of $k$. The route towards decoupling begins as scattering processes starting from the node and ending at the adjacent node lose spectral weight. This can be seen in the growth of the white zero region at the top left node. As we get closer to the pseudogap, points $k$ in between the node and antinode also decouple from the adjacent node (middle panel). The adjacent quadrant decoupling and onset into the pseudogap is completed by the antinode, which decouples from all points in the neighborhood of the Fermi surface.}
    \label{rgProgression}
\end{figure}

\paragraph*{{\bf k}-resolved dynamical spectral weight transfer.} 
%In order to understand the mechanism driving 
Further insight into the pseudogapping 
%transition 
%in our model, we study 
is obtained from the strong fluctuations observed in charge correlations between the gapless nodal and gapped antinodal regions in this 
%pseudogapped 
regime
%, and find strong fluctuations
(Fig.~\ref{chargeCorr}, left panel). This suggests that the 
%creation of the 
pseudogap in the lattice model
%is brought about by 
emerges from the impurity model from the 
%development 
onset of charge fluctuations in the bath that prohibit correlated spin fluctuations with the impurity spin that
%. Since the latter 
%processes are the ones that give rise 
lead to the 
%central 
Kondo resonance at low-energies in the impurity spectral function. In this way, pseudogap formation 
%is a demonstration of 
results from the transfer of spectral weight from low to high energies. Accordingly, the pseudogap coincides 
%is also seen from 
with the appearance of poles of the lattice model self-energy $\Sigma ({\bf k},\omega=0)$
%in $k-$space  
near the antinodes; these poles approach the nodes 
%as the system is 
upon tuning towards the Mott transition
%through the pseudogap 
(Fig.~\ref{chargeCorr} right panel). The same is observed in the imaginary part of the impurity self-energy of the underlying impurity model~(Fig.\ref{channelDecoupling} (right panel)).

\begin{figure}
    \centering
    \includegraphics[width=0.49\linewidth]{cfnode-2.pdf}
    \includegraphics[width=0.49\linewidth]{selfEnergyKspace-3.pdf}
    \caption{Left: Charge isospin correlations $\chi_c({\bf k}_1, {\bf k}_2) = \braket{c^\dagger_{{\bf k}_1\uparrow}c^\dagger_{{\bf k}_1\downarrow}c_{{\bf k}_2\downarrow}c_{{\bf k}_2\uparrow} + \text{h.c.}}$ between the node and other $k-$points, in the pseudogap phase. The enhanced correlations between the node and the antinode suggests that these charge correlations lead to Kondo breakdown. The Kondo breakdown in turn leads to the gapping out of these regions in $k-$space on the lattice model, as seen from the appearance of poles in the imaginary self-enery (right panel).}
    \label{chargeCorr}
\end{figure}

\paragraph*{Non-Fermi liquid nature of the pseudogap.} In the pseudogap regime $|W/J|_{\text{PG}} < |W/J| < |W/J|_{c}$, the nature of the %metal 
gapless Fermi arcs is observed to change dramatically. 
%In this regime, we find that the Kondo couplings $J({\bf k}_1, {\bf k}_2)$ involving momenta from adjacent quadrants of the Brillouin zone are RG-irrelevant, disappearing from the low-energy fixed point Hamiltonian. 
First, we have already argued that the low-energy dynamics of these gapless Fermi arcs are governed by an underlying %simpler 
two-channel Kondo (2CK) impurity model~\cite{Tsvelick_weigmann_mchannel_1985,emery_kivelson}.
%, where the two pairs of opposite Brillouin zones form the two channels. 
Previous works 
%by Coleman and Ioffe
%, as well as one of our own previous works~\cite{Patra2023MCK}, 
show that the impurity self-energy of such a two-channel Kondo model displays marginal Fermi liquid (MFL) behaviour~\cite{Coleman_tsvelik,Schofield1997,Patra2023MCK}: $\Sigma \propto \omega \ln \omega$. The excitations of the 2CK also exhibit a separation of the spin, charge and channel quantum numbers~\cite{affleck1992}, i.e., with gapless excitations carrying only spin quantum number. The non-Fermi liquid nature
%at this also happens in the present model 
is further corroborated by the passage of the impurity quasiparticle residue $Z_\text{imp} = 1/(1 - \frac{\text{d}}{\text{d}\omega}\text{Re}(\Sigma))$ (Fig.~\ref{channelDecoupling} left panel) from finite values in the Fermi liquid phase to vanishingly small values in the pseudogap.
%, where $\Sigma^\prime(\omega)$ is the real part of the impurity self-energy. 
Upon tiling, 
%we can immediately see that 
the resulting MFL metal of the lattice model 
%is arising from such a is not a Fermi liquid; the 
possesses many-particle excitations that involve 
%of the MFL will involve excitations of 
multiple \(k-\)states.

Crucially, we find that passage through the pseudogap phase causes the nature of the non-Fermi liquid to evolve: very near the transition, the excitations of the marginal Fermi liquid %description is found to break down at the transition, and is 
are replaced by 
%those the non-Fermi liquid excitations 
of a Hatsugai-Kohmoto model~\cite{Baskaran1991,Hatsugai1992}. %In order to obtain this, we carry out a 
This insight is obtained from a perturbation-theoretic treatment of the RG fixed point Hamiltonian of the impurity model for $W/J\lesssim (W/J)_{\text{PG}}$,
%in this region of the phase diagram, 
by considering the effects of a small fixed point Kondo scattering probability \(J^*\) in the backdrop of a larger bath interaction parameter \(|W|\). 
%We focus here on 
This yields the HK model~\cite{Baskaran1991,Hatsugai1992} as the singular
%, critical 
part of the effective Hamiltonian arising from forward scattering processes 
%within the complete Hamiltonian 
(details 
%described 
in Appendix~\ref{hkmDerivation}):
\begin{equation}\begin{aligned}\label{HKModel}
	\Delta \tilde H_{{\bf q}_1 = {\bf q}_2} = \sum_{{\bf q},\sigma}\epsilon_{{\bf q}}{n}_{{\bf q},\sigma} + u\sum_{{\bf q}, \sigma}n_{{\bf q} \sigma} n_{{\bf q} \bar\sigma}~,
\end{aligned}\end{equation}
where the number operator \(n_{{\bf q} \sigma} = \phi^\dagger_{{\bf q}, \sigma} \phi_{{\bf q}, \sigma}\) pertains to emergent fermionic modes,
\begin{equation}\begin{aligned}
	\phi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} - c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~,
\end{aligned}\end{equation}
that are shifted by an excitation momentum \({\bf q}\) away from the nodal point \({\bf N}_1 = \left(\pi/2, \pi/2\right)\) and its nested partner \({\bf N}_1 + {\bf Q}_1 = \left(-\pi/2, -\pi/2\right)\). The kinetic energy (\(\epsilon_{\bf q}\)) and interaction \(u\) energy scales of the excitations are:
\begin{equation}\begin{aligned}
	\epsilon_{\bf q} = \text{sign}\left(\varepsilon_{{\bf N}_1 + {\bf q}}\right)\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W} + \frac{{J^*}^2}{-4W},~u = \frac{{J^*}^2}{4W}~.
\end{aligned}\end{equation}
%Eq.~\ref{HKModel} describes a Hatsugai-Kohmoto (HK) model~\cite{Baskaran1991,Hatsugai1992}, an exactly solvable model of correlated electrons. 
The non-Fermi liquid 
%nature of the gapless 
excitations in the %metallic 
gapless phase of the model 
manifests as
%in the form of 
a divergent one-particle self-energy at the non-interacting Fermi surface~\cite{Phillips2020}:
\begin{equation}\begin{aligned}
	\Sigma_{{\bf q}}(\omega) = -\frac{u^2/4}{\omega - \epsilon_{\bf q}}, ~\Sigma_{\epsilon_{\bf q}=0}(\omega \to 0)  \to \infty~.
\end{aligned}\end{equation}
The zero-frequency pole of this singular metal %continues to 
exists beyond the transition: in the Mott insulating phase, it marks a hard gap in the spectral function for charge excitations. The singular nature of the excitations in this regime can be attributed to the extremely non-local form of the impurity model (arising from the fact that it couples to only the nodal points in $k-$space). This divergent self-energy is consistent with our numerical calculations of the impurity self-energy which showed that the self-energy poles approach the $\omega=0$ point as the system is tuned towards the transition

\begin{figure}
    \centering
    \includegraphics[width=0.49\linewidth]{localQPResidue.pdf}
    \includegraphics[width=0.49\linewidth]{sigmaImag_49-1000.pdf}
    \caption{Left: Suppression of quasiparticle residue as the system is tuned through various phases. There is an initial abrupt fall at $|W| = |W^*|$, where the system enters the pseudogap and the excitations become non-Fermi liquid. There's a second abrupt fall at the transition due to the presence of a divergent self-energy. Right: Analogous progress of imaginary part of the local self-energy. The poles at the edge of the central Kondo resonance move progressively closer to zero frequency until the Mott pole emerges at zero frequency at the transition.}
    \label{channelDecoupling}
\end{figure}

\paragraph{Morphing of the non-Fermi liquid through the pseudogap}
In order to probe how the metal becomes increasingly correlated as it is tuned through the pseudogap, we compare the quasiparticle residue \(Z_\text{imp}\) and the scattering rate \(\Gamma\) of the quasiparticles, at the beginning and end of the pseudogap. For the regime \(|W| \gtrapprox |W|^*\), the low-energy excitations obey the marginal Fermi liquid theory: \(\Sigma^{\prime} \sim \omega\ln\omega, \Sigma^{\prime\prime}\sim-\omega\). This gives rise to a linear scattering rate \(\Gamma \sim \omega\) (arising from the imaginary part of the self-energy), and a logarithmically vanishing quasiparticle residue~\cite{varma2002singular}
\begin{equation}\begin{aligned}
Z_\text{imp}(\omega) = (1 - \frac{d\Sigma^\prime}{d\omega})^{-1} \sim (c - \ln \omega)^{-1}
\end{aligned}\end{equation}
where \(c\) is a constant. Close to the transition (\(|W| \lesssim |W_c|\)), the low-energy theory is described by a Hatsugai-Kohmoto model, with a diverging self-energy (obtained in eq.~\eqref{HKSelfenergy} above): 
\begin{equation}\begin{aligned}\label{HKSelfenergy}
	\Sigma({\bf k}) = u^2/\left(\omega - \epsilon_{\bf k}\right) = U^2 \left[\mathcal{P}(\frac{1}{\omega - \epsilon_{\bf k}}) - i\pi \delta(\omega - \epsilon_{\bf k})\right]~,
\end{aligned}\end{equation}
where \(\mathcal{P}\left(\cdot\right)\) represents the principal value, and we used the Sokhotski–Plemelj theorem to write down the final expression. For small but non-zero values of \(\omega - \epsilon_{\bf k}\), we get \(Z_\text{imp} \sim \omega^2/U^2 \). The metal near the transition therefore displays a much more rapid vanishing of the quasiparticle residue compared to the logarithmic vanishing for the marginal Fermi liquid. The scattering rate precisely at the surface \(\omega=\epsilon_{\bf k}\), in fact, diverges: \(\Gamma \sim U^2\delta(\omega - \epsilon_{\bf k})\), in contrast to the linearly vanishing scattering rate of the MFL.

The divergence of the self-energy at the transition also mark the onset of the Mott insulator (Fig.~\ref{channelDecoupling}, righ panel). In this way, we have shown that the Fermi liquid must first morph into a marginal Fermi liquid and then into a Hatsugai-Kohmoto non-Fermi liquid before the Mott insulator can emerge. Our calculations also show that beyond the HK terms, the effective Hamiltonian near the transition contains pairing fluctuations: while subdominant at $1/2$-filling, their presence suggests that upon doping away from the Mott insulating state, such a non-Fermi liquid can undergo a superconducting transition. Recent works on the HK model suggest that such a superconductor is likely to be of the non-BCS kind~\cite{Phillips2020}.

Real-space spin-correlations and entanglement within the impurity model (Fig.~\ref{realSpaceCorrelations}) reveal that the spin correlations undergo a crossover within the PG from short-ranged behaviour at the onset to long-ranged behaviour as the Mott transition is approached. [TODO This matches well with similar observations from diagrammatic Monte Carlo simulations of the Hubbard model at finite temperatures, suggesting that the behaviour observed here is generic~\cite{SimkovicFerrero2024}]. the This is further evidence of the breakdown of local Kondo screening and Landau quasiparticles inside the PG. Another implication of these results is that the paradigm governing such a transition is most likely not that of {\it local quantum criticality} - the critical behaviour close to the transition cannot be described by the dynamics of the local sites, and the excitations become truly long-ranged in this regime.

\begin{figure}
    \centering
    \includegraphics[width=0.49\linewidth]{SF-di_69-2000.pdf}
    \includegraphics[width=0.49\linewidth]{I2-di_69-2000.pdf}
    \caption{Emergence of long-ranged correlations near the critical point. Left panel: Spin correlations $\chi_s(d,{\bf k}) = \braket{{\bf S}_d^+\cdot{\bf S}_{\bf r}^-}$ between the impurity spin and conduction bath local spins at a distance {\bf r}, as a function of {\bf r}. Right: Mutual information between the same objects, again as a function of the distance. Both decay exponentially fast in the Fermi liquid phase (blue), but show long-ranged behaviour in the non-Fermi liquid phase (green, yellow) and particularly close to the transition (green), indicating that the description of the transition is beyond local quantum criticality.}
    \label{realSpaceCorrelations}
\end{figure}

\paragraph{Luttinger's theorem in the presence of Luttinger surfaces}
One can also ask whether Luttinger's theorem is satisfied in our model in the presence of Luttinger surfaces. It has been shown that particle-hole symmetric systems always satisfy a generalised Luttinger's theorem~\cite{seki2017topological}, where the Fermi volume $V_L$ is represented as the difference in the number of poles and zeros, of the single-particle Greens function, that are enclosed by the Fermi surface~\cite{seki2017topological}. This holds true even in the presence of a divergent self-energy~\cite{Phillips2013}. Since our model is always at half-filling, Luttinger's theorem is always satisfied.

The way it works out (despite the presence of Luttinger surfaces) is as follows. We need only show that the number of occupied states below the chemical potential remains unchanged across the first Lifshitz transition. Before the transition, the presence of gapless excitations ensures that the Fermi surface is singly-occupied on average. Inside the pseudogap, the gapless $k-$states continue to contribute one pole on average to the Luttinger count, while the gapping out of certain $k-$states leads to a rearrangement of their spectrum: doubly-occupied states on the Luttinger surfaces become more favourable compared to the singly-occupied states (due to the attractive $W$-interaction). Owing to particle-hole symmetry, these states are degenerate with the zero occupancy states, so that on average, a single state is again occupied. This ensures that the number of occupied states (and hence the number of occupied poles) remains unchanged across the transition. The same argument works for the Mott insulator, where the entire Fermi surface gets replaced by a Luttinger surface.

\paragraph*{Acknowledgements}
AM thanks IISER Kolkata for funding through a JRF and SRF. S Lal thanks the SERB, Govt. of India for funding through MATRICS Grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.

\appendix

\section{Appendixes}

\bibliography{tilingProject}% Produces the bibliography via BibTeX.

\end{document}

### 2025-05-02 TilingProjectDraft/tilingProject.tex
latest version of manuscript and notes, with most of the figures added

@@
 \end{aligned}\end{equation}
-These transformations involve translating one or both momenta through the center of the Brillouin zone.
+These transformations involve translating one or both momenta through the center of the Brillouin zone. \textcolor{red}{Is this a d-wave symmetry of the RG equation?}
 
@@
 
-Coleman and Ioffe have shown that by mapping the two-channel Kondo problem to a ``compactified" form where the impurity spin hybridises with the spin and isospin degrees of freedom of a single conduction channel, the impurity self-energy can be shown to display marginal Fermi liquid behaviour~\cite{Coleman_tsvelik,Schofield1997}:
-\begin{equation}\begin{aligned}
-	\Sigma \propto \omega \ln \omega~.
+Coleman and Ioffe have shown that by mapping the two-channel Kondo problem to a ``compactified" form where the impurity spin hybridises with the spin and isospin degrees of freedom of a single conduction channel, the impurity self-energy \(\Sigma = \Sigma^\prime + i\Sigma^{\prime\prime}\) can be shown to display marginal Fermi liquid behaviour~\cite{Coleman_tsvelik,Schofield1997}:
+\begin{equation}\begin{aligned}
+	\Sigma^\prime \propto \omega \ln \omega, ~\Sigma^{\prime\prime} \propto \omega~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	\Sigma_{{\bf q}}(\omega) = -\frac{u^2/4}{\omega - \epsilon_{\bf q}}, ~\Sigma_{\epsilon_{\bf q}=0}(\omega \to 0)  \to \infty~.
-\end{aligned}\end{equation}
+	\Sigma_{{\bf q}}(\omega) = -\frac{u^2/4}{\omega - \epsilon_{\bf q}}, ~\Sigma_{\epsilon_{\bf q}=0}(\omega \to 0)  \to \infty~,
+\end{aligned}\end{equation}
+while the spectral function $A(k,\omega=0)$ shows a sharp peak at each of the four nodal Fermi surface points.
+This will be observed to lead to a nodal non-Fermi liquid metal shown below in Fig.\ref{tiledSpecFunc} (fourth panel).
 Beyond the transition and inside the Mott insulating phase, this zero frequency pole continues to exist and marks the hard gap in the spectral function for charge excitations.
+We note that the ${\bf q}_{1}\neq {\bf q}_{2}$ scattering processes correspond to the forward and tangential scattering of the coherent superposition of \({\bf N}_1 = \left(\pi/2, \pi/2\right)\) and its nested partner \({\bf N}_1 + {\bf Q}_1 = \left(-\pi/2, -\pi/2\right)\) along the respective Fermi arcs.
+Such scattering processes add non-singular contributions to the self-energy, and do not open gaps at the Fermi surface.
+WE EXPECT SUCH A NODAL NON-FERMI LIQUID METAL TO EXHIBIT VOLUME LAW SCALING OF THE BIPARTITION ENTANGLEMENT ENTROPY.
 
@@
 This, along with the behaviour of the spectral function, indicates that in the pseudogap region, the disconnected Fermi surface coexists with a Luttinger surface.
+WE EXPECT THAT THE JOURNEY THROUGH THE PSEUDOGAP DOES NOT VIOLATE LUTTINGER'S THEOREM; THIS CAN BE SEEN BY COUNTING BOTH THE POLES AND THE ZEROS OF THE SINGLE PARTICLE GREENS FUNCTION.
+CHECK.
 \begin{figure}[htpb]
@@
 This divergent self-energy is consistent with our numerical calculations of the impurity self-energy which showed that the self-energy poles approach the \(\omega=0\) point as the system is tuned towards the transition.
+
+In order to probe how the metal becomes increasingly correlated as it is tuned through the pseudogap, we compare the quasiparticle residue \(Z_\text{imp}\) and the scattering rate \(\Gamma\) of the quasiparticles, at the beginning and end of the pseudogap.
+For the regime \(|W| \gtrapprox |W|^*\), the low-energy excitations obey the marginal Fermi liquid theory: \(\Sigma^{\prime} \sim \omega\ln\omega, \Sigma^{\prime\prime}\sim-\omega\).
+This gives rise to a linear scattering rate \(\Gamma \sim \omega\) (arising from the imaginary part of the self-energy), and a logarithmically vanishing quasiparticle residue~\cite{varma2002singular}
+\begin{equation}\begin{aligned}
+Z_\text{imp}(\omega) = (1 - \frac{d\Sigma^\prime}{d\omega})^{-1} \sim (c - \ln \omega)^{-1}
+\end{aligned}\end{equation}
+where \(c\) is a constant. Close to the transition (\(|W| \lesssim |W_c|\)), the low-energy theory is described by a Hatsugai-Kohmoto model, with a diverging self-energy: 
+\begin{equation}\begin{aligned}
+	\Sigma({\bf k}) = U^2/\left(\omega - \epsilon_{\bf k}\right) = U^2 \left[\mathcal{P}(\frac{1}{\omega - \epsilon_{\bf k}}) - i\pi \delta(\omega - \epsilon_{\bf k})\right]~,
+\end{aligned}\end{equation}
+where \(\mathcal{P}\left(\cdot\right)\) represents the principal value, and we used the Sokhotski–Plemelj theorem to write down the final expression.
+For small but non-zero values of \(\omega - \epsilon_{\bf k}\), we get \(Z_\text{imp} \sim \omega^2/U^2 \).
+The metal near the transition therefore displays a much more rapid vanishing of the quasiparticle residue compared to the logarithmic vanishing for the marginal Fermi liquid.
+The scattering rate precisely at the surface \(\omega=\epsilon_{\bf k}\), in fact, diverges: \(\Gamma \sim U^2\delta(\omega - \epsilon_{\bf k})\), in contrast to the linearly vanishing scattering rate of the MFL.
 
@@
 
-The renormalisation in \(R\) leads to a renormalisation in the single-particle self-energy~\cite{anirbanmott1}. The \(k-\)space-averaged self-energy renormalisation is
+The renormalisation in \(R\) leads to a renormalisation in the real part of the single-particle self-energy~\cite{anirbanmott1}. The \(k-\)space-averaged self-energy renormalisation is
 \begin{eqnarray}
-	\Delta \Sigma(\omega) = \rho {R^*}^2\int_0^{\epsilon^*} \frac{d\epsilon_j}{\omega - \epsilon_j/2 + R_j/8}~.
+	\Delta \Sigma^\prime(\omega) = \rho {R^*}^2\int_0^{\epsilon^*} \frac{d\epsilon_j}{\omega - \epsilon_j/2 + R_j/8}~.
 \end{eqnarray}
@@
 	\label{self_energy}
-	\Delta \Sigma(\omega) \sim  \bar \omega \ln \frac{N^* \omega}{\bar \omega}~.
+	\Delta \Sigma^\prime(\omega) \sim  \bar \omega \ln \frac{N^* \omega}{\bar \omega}~.
 \end{eqnarray}
+The imaginary part of the self-energy can be obtained using the Kramers-Kronig relations:
+\begin{equation}\begin{aligned}
+\Delta \Sigma^{\prime\prime}(\omega) = \frac{1}{\pi}\mathcal{P} \int_{-\infty}^\infty d\omega^\prime \frac{\Sigma^\prime(\omega^\prime)}{\omega - \omega^\prime} \sim -\bar\omega~.
+\end{aligned}\end{equation}
+
 The self-energy also provides the quasiparticle residue for each channel\cite{anirbanmott1}:

### 2025-05-02 numerics/caller.jl
actual version for the real-space entanglement

@@ -13,12 +13,12 @@ include("./source/plotting.jl")
 
 global J_val = 0.1
 @everywhere global orbitals = ("p", "p")
-maxSize = 500
+maxSize = 2000
 WmaxSize = 500
 
 colmap = [ColorSchemes.thermal, ColorSchemes.cherry[1:end-1]][2]
 phasesColmap = reverse(ColorSchemes.cherry)
-numShells = 1
+numShells = 3
 bathIntLegs = 3
 NiceValues(size_BZ) = Dict{Int64, Vector{Float64}}(
                          13 => -1.0 .* [0., 1., 1.5, 1.55, 1.6, 1.61] ./ size_BZ,

### 2025-05-09 numerics/caller.jl
minor improvements

@@ -27,7 +27,7 @@ NiceValues(size_BZ) = Dict{Int64, Vector{Float64}}(
                          41 => -1.0 .* [0, 3.5, 7.13, 7.3, 7.5, 7.564, 7.6] ./ size_BZ,
                          49 => -1.0 .* [0, 4.1, 8.19, 8.4, 8.55, 8.77, 8.8] ./ size_BZ,
                          57 => -1.0 .* [0, 4., 7., 10.2, 10.6, 10.852] ./ size_BZ,
-                         69 => -1.0 .* [0, 6., 12.5, 13.1, 13.34, 13.4] ./ size_BZ,
+                         69 => -1.0 .* [0, 3, 8, 12.5, 13.1, 13.34, 13.4] ./ size_BZ,
                          77 => -1.0 .* [0., 14.04, 14.5, 14.99, 15.0] ./ size_BZ,
                         )[size_BZ]
 pseudogapEnd(size_BZ) = Dict{Int64, Float64}(
@@ -79,7 +79,7 @@ function ScattProb(
         loadData::Bool=false
     )
     x_arr = get_x_arr(size_BZ)
-    W_val_arr = NiceValues(size_BZ)
+    W_val_arr = NiceValues(size_BZ)[2:4]
     @time kondoJArrays, dispersion = RGFlow(W_val_arr, size_BZ; loadData=loadData)
     saveNames = String[]
     results = [ScattProb(size_BZ, kondoJArrays[W_val], dispersion)[2] for W_val in W_val_arr]
@@ -113,7 +113,7 @@ function ScattProb(
     for W_val in W_val_arr
         for point in [node, antinode, mid]
             matrix = kondoJArrays[W_val][point, :, end]
-            matrix[abs.(matrix) .< 1e-10] .= NaN
+            matrix[abs.(matrix) .< 1e-10] .= 0
             matrix[matrix .> 1e-10] .= 1
             matrix[matrix .< -1e-10] .= -1
             push!(saveNames[point], 
@@ -122,30 +122,14 @@ function ScattProb(
                               (L"$ak_x/\pi$", L"$ak_y/\pi$"),
                               L"$\Gamma/\Gamma_0$", 
                               getlabelInt(W_val, size_BZ), 
-                              colmap[2:end];
+                              ColorSchemes.viridis;
[…]

### 2025-05-09 numerics/source/plotting.jl

@@ -95,10 +95,10 @@ function plotHeatmap(
     Label(gl[1, 1], annotation, padding = (5, 5, 5, 5), fontsize=div(FONTSIZE, 1.3), color=:white)
 
     if !isempty(line)
-        scatter!(ax, line .|> first, line .|> last, color = :gray, markersize=4)
+        scatter!(ax, line .|> first, line .|> last, color = :maroon, markersize=4)
     end
     if !isnothing(marker)
-        scatter!(ax, marker..., color=:orange, markersize=20)
+        scatter!(ax, marker..., color=:gray, markersize=20)
     end
 
     Colorbar(figure[1, 2], hm)

### 2025-05-09 TilingProjectDraft/manuscript.tex
polished manuscript and started adding endmatter

@@
  aps,
-prl
+prl,superscriptaddress
 %prb,
@@
 
-\title{Pseudogapped non-Fermi liquid phase arising from Kondo breakdown at the Mott transition}
+%\title{Pseudogapped non-Fermi liquid phase arising from Kondo breakdown at the Mott transition}
+
+%\title{Long range entangled Fermi arcs in a Pseudogapped Mott transition}
+
+\title{Pseudogapped Mott criticality: Stretching Kondo Screening to Breaking Point}
 
@@
 \author{Abhirup Mukherjee}
+\affiliation{%
+ Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
+}
+\author{S. R. Hassan}
+\affiliation{The Institute of Mathematical Sciences, C.I.T. Campus, Chennai 600 113, India}
+\author{Anamitra Mukherjee}
+\affiliation{1 School of Physical Sciences, National Institute of Science, Education and Research, HBNI, Jatni 752050, India}
+\author{N. S. Vidhyadhiraja}
+\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
+\author{A. Taraphder}
+\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
+%
 \author{Siddhartha Lal}
@@
  Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
-}%
+}
 
@@
 Passage from Fermi liquid metal to Mott insulator involves two stages: the first involves a systematic unraveling of Kondo screening due to frustrating charge fluctuations in the conduction bath of the underlying lattice-embedded quantum impurity model.
-The unraveling destabilises the Fermi liquid, culminating in disconnection of the Fermi surface by gapping the antinodes.
+The destabilises the bulk Fermi liquid, culminating in disconnection of the Fermi surface by gapping the antinodes.
 In the second stage, an emergent pseudogap phase arises from an effective two-channel Kondo problem in the underlying impurity model.
-The resulting momentum space Fermi arcs possess non-Fermi liquid excitations proximate to a critical Fermi surface.
-Upon approaching the transition, the nature of this exotic metal evolves with shrinking size of the arcs to a singular nodal non-Fermi liquid along with the onset of long-ranged real-space entanglement and spin-flip correlations.
-This reveals the Mott transition on the square lattice to be well beyond the paradigm of local quantum criticality.
+The resulting momentum-space Fermi arcs possess non-Fermi liquid excitations proximate to a critical Fermi surface.
+Upon approaching the transition, the nature of this exotic metal evolves with shrinking size of the arcs towards a singular nodal non-Fermi liquid.
+This accompanies the onset of long-ranged real-space entanglement and spin-flip correlations, and reveals the Mott transition on the square lattice to be well beyond the paradigm of local quantum criticality.
 \end{abstract}
@@
 
-\paragraph*{Introduction.}
-The origin of the pseudogap and strange metal phases of the cuprates continue to be hotly debated topics in the context of high-temperature superconductivity~\cite{keimer2015quantum,ProustTaillefer2019}.
-The anomalous pseudogap (PG) phase, observed most prominently in the cuprates, exhibits nodal-antinodal dichotomy with spectral weight being concentrated on Fermi arcs around the node~\cite{loeserKapitulnik1996,Norman1998,Hashimoto2014}.
-While several methods have observed a PG in the Hubbard model ~\cite{KyungKotliar2006,MacridinAzevedo2006,WuFerrero2018,anirbanmott2,HilleAndergassen2020}, there is no general consensus yet regarding various aspects of the PG phase, such as its relation to the Mott insulating and superconducting phases proximate to it, how it evolves from weak-coupling to strong-coupling, and whether the nodal-antinodal dichotomy is intrinsic to the model.
+\par\noindent\textit{Introduction.}
+The origin of the pseudogap and strange metal phases of the cuprates continue to be hotly debated topics in the context of high-temperature superconductivity~\cite{keimer2015quantum}.
+The anomalous pseudogap (PG) phase, observed most prominently in the cuprates, exhibits nodal-antinodal dichotomy with spectral weight
+concentrated on Fermi arcs around the nodal regions~\cite{loeserKapitulnik1996,Norman1998,Hashimoto2014}.
+While several methods have observed a PG in the two dimensional Hubbard model ~\cite{KyungKotliar2006,MacridinAzevedo2006,WuFerrero2018,anirbanmott2,HilleAndergassen2020}, there is no general consensus regarding various aspects of the PG phase, including its relation to proximate Mott insulating and superconducting phases~\cite{FradkinRevModPhys2015,anirbanmott2,Kitatani2023,Sorella2023}, its evolution from weak- to strong-coupling ~\cite{HuangDevereaux2018,Fedor2022,SimkovicFerrero2024}, and whether nodal-antinodal dichotomy is intrinsic to the model~\cite{Hashimoto2014,Schafer2021}.
+Importantly, the connection between finite-temperature crossovers and zero-temperature ground states observed in various analyses remains unclear~\cite{White1998,Ido2018,ProustTaillefer2019,Ponsioen2019,Shengtao2021,XuZhang2022}.
 
-In order to investigate the precise mechanism of transition/crossover connecting the metallic phases with the Mott insulating phase, we present a new auxiliary model method to study correlated electronic systems, and apply it to the particle-hole symmetric Hubbard-Heisenberg model to investigate the origin and nature of its pseudogap phase and the subsequent transition into a Mott insulator.
-The method requires identifying an appropriate impurity model which can faithfully capture the physics of lattice model we are trying to solve.
-Passage to the bulk model is accomplished by applying lattice translation operators on the impurity model, which makes it possible to relate various computables of the auxiliary model to those of the lattice model.
+We present here a new auxiliary model approach 
+to the strong coupling physics of the particle-hole symmetric 2D Hubbard-Heisenberg model at zero temperature, revealing the origin and nature of its PG phase and subsequent Mott transition.
+The first step
+requires identifying an appropriate lattice-embedded quantum impurity model, and conducting a scaling analysis of its low-energy phases.
+Subsequently, the lattice model is  constructed by applying many-body lattice translation operators~\cite{stoyanova} on the impurity model (referred to henceforth as \textit{tiling}), obtaining thereby various quantities
+of the former from the latter.
+Translation invariance is thus restored differently within our approach from the dynamical mean-field approximation~\cite{georges1996} and its cluster variants~\cite{Hettler2000DCA,Kotliar2001Cellular,Maier2005,Sakai2023}.
 
-Our approach differs from dynamical mean-field approximation based methods (specifically the cellular and cluster-based avatars) in the fact there no self-consistency condition that needs to be imposed - the lattice model is explicitly constructed from a {\it lattice-embedded} impurity model.
-While this makes the impurity model trickier to solve, it makes more transparent the underlying local physics arising from correlations, and provides increased momentum-space resolution which is crucial for studying PG physics.
-Indeed, an important conclusion of our work that results from this is that the Mott transition on the square lattice appears to be well beyond the paradigm of local quantum criticality, due to the onset of long-ranged real-space entanglement and spin-flip correlations close to the transition.
+Combining the scaling analysis of the impurity model with the tiling procedure provides the momentum-space resolution crucial to unveiling the PG phenomenon, and clarifies the role of the Kondo breakdown process at the heart of the Mott transition~\cite{fabrizio2017kondophysicsmotttransition,RADEMAKER2025}.
+Emerging from a systematic unraveling of Kondo screening, the PG phase is separated from Fermi liquid and Mott insulating phases by correlation-driven Lifshitz transitions of the Fermi surface~\cite{sakai2009evolution}.
+Passage through the PG involves dynamical transfer of spectral weight between gapped anti-nodal Luttinger surfaces (zeros of the single-particle Greens function) and gapless nodal arcs with non-Fermi liquid excitations.
+We also observe the onset of long-ranged real-space entanglement and spin-flip correlations close to the Mott transition, rendering it beyond the paradigm of local quantum criticality~\cite{Si2001}.
 
-\paragraph*{A lattice-embedded impurity model.}
-%Crucial to our method is the choice of an impurity auxiliary model that is able 
-In order to capture important local aspects of electronic correlations in the lattice model,  
-%Some of us have shown in a previous work
-%~\cite{Mukherjee_2023} that various aspects of the Mott metal-insulator transition on the infinite dimensional Hubbard model on the Bethe lattice (as seen, for example, from dynamical mean-field theory~\cite{georges1996}) can be captured from the breakdown of the strongly coupled Kondo phase of a simple extension of the Anderson impurity model (eSIAM).
-%Building on this insight, 
-we embed an extended Anderson impurity 
-%spin-$1/2$ moment ${\bf S}_d$ 
-into the lattice of a half-filled 2D conduction bath (with nearest-neighbour hopping). This builds on insight 
-%of an earlier work
-\cite{Mukherjee_2023} that various aspects of the Mott %metal-insulator 
-transition on the %infinite-dimensional 
-Hubbard model on the Bethe lattice in infinite dimensions (as seen %, for example, 
-from 
-%dynamical mean-field theory
-DMFT~\cite{georges1996}) can be captured from the breakdown of the strongly coupled Kondo phase of a simple extension of the Anderson impurity model (eSIAM). 
-%This lowers the \(s-\)wave symmetry of Kondo interactions (on, say, an infinite-dimensional Bethe lattice) down to the \(C_4\) symmetry of the 2D square lattice.
-
-In capturing the Mott transition, we focus on the %large-$U$ 
-limit of large local correlations within the impurity model, where the impurity-bath hybridisation occurs through an antiferromagnetic Kondo coupling ($J>0$). The model is described by the Hamiltonian
+\par\noindent\textit{A lattice-embedded impurity model.}
+Building on insight that Kondo breakdown in a simple extension of the Anderson impurity~\cite{Mukherjee_2023} captures the physics of the Mott transition in infinite dimensions~\cite{georges1996}), we study the Kondo physics of a similar Anderson impurity model embedded within a square lattice
 \begin{equation}\begin{aligned}\label{impurityModel}
-	\mathcal{H}_\text{aux} = H_\text{cbath} + H_\text{imp-cbath} + H_\text{cbath-int}~,
+	\mathcal{H}_\text{aux} = H_\text{imp} + H_\text{imp-cbath} + H_\text{cbath}~, 
 \end{aligned}\end{equation}
-where $H_\text{cbath} = -2t\sum_{{\bf k}}\left[\cos(ak_x) + \cos(ak_y)\right] c^\dagger_{{\bf k},\sigma}c_{{\bf k},\sigma}$ is the kinetic energy for conduction bath tight-binding electrons ($c^\dagger_{{\bf k},\sigma}$) on a half-filled square lattice, and the impurity spin-1/2 moment (${\bf S}_d$) interacts with four nearest neighbour sites (henceforth labelled as \textit{zeroth} sites with index $Z$)
-%in \(H_\text{imp-cbath}\) 
-through local Kondo terms of uniform strength \(H_\text{imp-cbath} =\frac{1}{2} J\sum_{\sigma_1,\sigma_2}\sum_{Z} {\bf S}_d\cdot c^\dagger_{Z\sigma_1}{\boldsymbol \tau}_{\sigma_1,\sigma_2} c_{Z\sigma_2}\).
-%is the impurity-bath Kondo interaction. 
-%and \(H_\text{cbath-int} = -\frac{W}{2}\sum_{Z} \left(n_{Z\uparrow} - n_{Z\downarrow}\right)^2\). 
-%is a local intra-bath correlation that 
-%models minimally the correlated nature of the conduction bath. 
-%The index \(Z\) sums over all four nearest-neighbour sites of the impurity site, henceforth referred to as bath {\it zeroth} sites). 
-A minimal model for correlations within the conduction bath that frustrate the Kondo screening is given by the third term:
-%$H_\text{cbath-int}$ 
-%represents local correlations on the four bath zeroth sites, 
-\(H_\text{cbath-int} = -\frac{W}{2}\sum_{Z} \left(n_{Z\uparrow} - n_{Z\downarrow}\right)^2\). 
-%, again of uniform strength. 
-%In the above definitions, \(c^\dagger_{d\sigma}\) is the impurity site creation operator (for spin \(\sigma \)), while \(c^\dagger_{{\bf k}\sigma}\) is the conduction bath creation operator (for momentum \({\bf k}\) and spin \(\sigma\)).
-The 2D structure of the impurity model, and its distinction from the infinite-dimensional counterpart, becomes apparent upon Fourier transforming the Kondo coupling to ${\bf k}$-space (with lattice spacing set to unity):
-%once we transform the Hamiltonian to momentum space:
-\begin{equation}\begin{aligned}
-	J_{{\bf k}, {\bf k}^\prime} = \frac{J}{2}&\left[\cos\left({\bf k}_x - {\bf k}^\prime_x\right) + \cos\left({\bf k}_y - {\bf k}^\prime_y\right)\right]~,
-\end{aligned}\end{equation}
-with $J>0$.
-%where the subscripts \(x\) and \(y\) represent components of the momenta vector, and the lattice spacing has been set to unity. This form shows that The Kondo coupling 
-Clearly, $J_{{\bf k}, {\bf k}^\prime}$ is 
-%no longer in
-dependent on the exchange of momentum, and encodes the $C_{4}$ lattice symmetry. 
-%geometry. Throughout the work
-%In all that follows, we set the lattice spacing to unity.
-
-\paragraph*{Reconstructing the Hubbard-Heisenberg model.} %from the auxiliary model: Formal prescription of our method.}
-We will now define the {\it tiling} (or periodisation) procedure by which we recreate the lattice model 
-%by using instances of 
-from the 
-%auxilliary
-impurity model Hamiltonian. 
-%In order to identify a 
-For a {\it unit cell} 
-%for 
-of the tiling, 
-%procedure, 
+where $H_{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2$ is the Hamiltonian for the localised impurity site, and the impurity ($c_{d\sigma}$, with spin-1/2 moment ${\bf S}_d$)
+interacts with four nearest neighbour sites ($c_{Z\sigma}$, labelled with index $Z$) 
+through local Kondo terms of uniform strength $J$ as well as single-particle hybridisation $V$, \(H_\text{imp-cbath} =\frac{1}{2} J\sum_{\sigma_1,\sigma_2}\sum_{Z} {\bf S}_d\cdot c^\dagger_{Z\sigma_1}{\boldsymbol \tau}_{\sigma_1,\sigma_2} c_{Z\sigma_2} - V \sum_{\sigma, Z} \left(c^\dagger_{Z\sigma} c_{d\sigma} + h.c.\right)\).
+Finally, the term
+$H_\text{cbath} = \sum_{{\bf k}}\epsilon_{\textbf{k}}
+c^\dagger_{{\bf k},\sigma}c_{{\bf k},\sigma} -\frac{W}{2}\sum_{Z} \left(n_{Z\uparrow} - n_{Z\downarrow}\right)^2$ includes the kinetic energy ($\epsilon_{\textbf{k}}=-2t\left(\cos k_x + \cos k_y\right)$) for conduction bath tight-binding electrons ($c^\dagger_{{\bf k},\sigma}$)
+on a half-filled square lattice (with lattice spacing set to unity), together with local correlations ($W$) that frustrate the Kondo screening.
+The 2D structure of the impurity model, and its distinction from the infinite-dimensional counterpart, becomes apparent upon Fourier transforming the Kondo coupling to ${\bf k}$-space:
+$J_{{\bf k}, {\bf k}^\prime} = \frac{J}{2}\left[\cos\left({\bf k}_x - {\bf k}^\prime_x\right) + \cos\left({\bf k}_y - {\bf k}^\prime_y\right)\right]$, with $J>0$.
+Clearly, $J_{{\bf k}, {\bf k}^\prime}$
+possesses the $C_{4}$ lattice symmetry. 
+\par\noindent\textit{Reconstructing the lattice model.}
+We now define the {\it tiling} procedure by which we recreate the lattice model from the impurity model Hamiltonian. For a {\it unit cell} of the tiling,  
 we consider an impurity model \(\mathcal{H}_\text{aux}({\bf r}_d)\) that has the impurity site at a reference site \({\bf r}_d\) of our lattice.
-In order to create the bulk model, we translate the unit cell across all sites of the lattice:
+In order to create the lattice model, we translate the unit cell across all sites of the lattice:
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-where \({\bf r}\) sums over all lattice sites, and $T({\bf r})$ is a many-body translation operator that translates all 
-%electrons 
-coordinates by a vector \({\bf r}\). Further details of the tiling procedure are provided in the Supplemental Material~\cite{suppmat}.
-%We have removed extra copies of conduction bath kinetic energy \(\mathcal{H}_\text{cbath}\) that were added during the translation operations. 
-Implementing this procedure for the impurity model defined above (eq.~\ref{impurityModel}) generates a {\it Hubbard-Heisenberg} lattice model in two spatial dimensions:
-\begin{equation}\begin{aligned}
-		\mathcal{H}_\text{tiled} &= -\frac{1}{\sqrt\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma} \\
-        &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
-\end{aligned}\end{equation}
-%where the tilde symbol indicates that the 
-with parameters for the lattice model that are related to those in $\mathcal{H}_\text{aux}$
-%the auxiliary model
-~\cite{suppmat}. 
-%By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to one another. 
-The form of the eigenstates of $H_{\text{tiled}}$
-%the lattice Hamiltonians obtained using eq.~\ref{tilingPrescription} 
-are dictated by a many-body version of Bloch's theorem~\cite{stoyanova}.
-Further, the relation between Hamiltonians and eigenstates of the auxiliary and tiled models can be exploited in obtaining equal-time correlation functions and
-%from the auxiliary model to the lattice model, as well as equal-time correlations and 
-entanglement measures of the latter from the former~\cite{suppmat}.
-%such entanglement entropy and mutual information.
+where \({\bf r}\) sums over all lattice sites, and $T({\bf r})$ is a many-body translation operator that translates all coordinates by a vector \({\bf r}\).
+Further details of the tiling procedure are provided in the Supplemental Material~\cite{suppmat}.
+Implementing this procedure for the extended Anderson impurity model defined above (eq.~\ref{impurityModel}) generates a {\it Hubbard-Heisenberg} lattice model in two spatial dimensions:
+    \begin{eqnarray}
+        &&\mathcal{H}_\text{tiled} = -\frac{\tilde t}{\sqrt\mathcal{Z}}\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\nonumber \\
+        &&+ \frac{\tilde J}{\mathcal{Z}}\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2~,
+        \end{eqnarray}
+with parameters $(\tilde{t},\tilde{\mu},\tilde{J},\tilde{U})$
+that are related simply to those in $\mathcal{H}_\text{aux}$~\cite{suppmat}.
+The form of the eigenstates of $H_{\text{tiled}}$ are dictated by a many-body version of Bloch's theorem~\cite{stoyanova}.
+Further, relations between the Hamiltonians and eigenstates of the impurity and lattice models are exploited in obtaining equal-time correlation functions and entanglement measures of the latter from the former~\cite{suppmat}.
 \begin{figure}
     \centering
-    \includegraphics[width=0.49\linewidth]{SF-3.pdf}
-    \includegraphics[width=0.49\linewidth]{kspaceDOS-3.pdf}
-    \caption{Left: $k-$space resolved spin-spin correlation $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$, in the peudogap phase, confirmed from the fact that only a part of the Fermi surface screens the impurity, the antinodes being the first to decouple from the impurity.
-This leads, through our tiling relations, to a $k-$space resolved gap on the lattice model, as seen from the DOS (right panel).
-The region around the antinode of the lattice Fermi surface gets replaced by a Luttinger surface of zeros.}
+    \includegraphics[width=0.31\linewidth, height=2.45cm]{phaseDiagram.pdf}
+    \includegraphics[width=0.67\linewidth]{SF-DOS.pdf}
+    \caption{Left: Phase diagram of impurity model at strong coupling in $U$ in terms of competing dimensionless Kondo ($J/t$) and bath correlation ($W/t$) couplings.
+A pseudogap phase (red, PG) is observed between the local Fermi liquid (pink, LFL) and local moment (black, LM) phases.
+Center: $k-$space resolved spin-spin correlation $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$ in the pseudogap phase of the impurity model.
+Antinodal regions are observed to decouple from Kondo screening of the impurity.
+Right: Upon tiling, this leads to a $k-$space resolved antinodal gap in the electronic density of states of the lattice model, corresponding to Luttinger surfaces of zeros.}
     \label{spinCorr}
 \end{figure}
-
-\paragraph*{Pseudogapping transition from Kondo breakdown.} To obtain various low-energy phases of the impurity model, we perform a scaling analysis of the associated Hamiltonian using the recently developed
-unitary renormalisation group (URG) method \cite{anirbanurg1}. The URG
-%method 
-proceeds by resolving quantum fluctuations at $T=0$ involving high-energy degrees of freedom in systems of correlated fermions~\cite{santanukagome,1dhubjhep,anirbanmott2,anirbanmott1,siddharthacpi,anirban_kondo,Patra_2023,anirbanurg2}, leading to a low-energy Hamiltonian with renormalised couplings and emergent degrees of freedom.
-%The method has been applied successfully to a variety of problems involving correlated fermions~\cite{santanukagome,1dhubjhep,anirbanmott2,anirbanmott1,siddharthacpi,anirban_kondo,Patra_2023,anirbanurg1,anirbanurg2};
-We present the results for the present impurity model here, and the details of the calculation are presented in \cite{suppmat}. 
-%We find that 
-The renormalisation in the %momentum
-${\bf k}$-resolved Kondo coupling \(J^{(j)}_{{\bf k}_1, {\bf k}_2}\) at the \(j^\text{th}\) RG step is obtained as
+\par\noindent\textit{Pseudogapping transition from Kondo breakdown.} A detailed picture of Kondo breakdown in the large $U$ phase of $H_\text{aux}$ is obtained from a scaling analysis of the ${\bf k}$-resolved Kondo coupling \(J^{(j)}_{{\bf k}_1, {\bf k}_2}\) using the
+unitary renormalisation group (URG) method \cite{anirbanurg1} (see \cite{suppmat} for details)
 \begin{equation}\begin{aligned}\label{KondoRGequation}
@@
 \end{aligned}\end{equation}
-where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, the sum is over all momentum states \({\bf q}\) in the particle sector (PS) of the energy shell \(\varepsilon_j\) (i.e., all states
-%that are 
-occupied at \(T=0\) and in the absence of any quantum fluctuations), and  \({\bf \bar q} = {\bf q} + {\boldsymbol \pi}\).
+where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, the sum is over all momentum states \({\bf q}\) in the particle sector (PS) of the energy shell \(\varepsilon_j\) (i.e., all states occupied at \(T=0\) and in the absence of any quantum fluctuations), and  \({\bf \bar q} = {\bf q} + {\boldsymbol \pi}\) is the particle-hole transformed state associated with ${\bf q}$.
 The bath interaction coupling $W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}$ is found to be marginal under these transformations.
-While the complexity of the RG equation for $J_{{\bf k}_1, {\bf k}_2}$ (eq.\eqref{KondoRGequation}) is clarified through a detailed numerical evaluation, the structure of the equation is qualitatively similar to its counterpart in a study of the Mott MIT in infinite dimensions~\cite{Mukherjee_2023}.
-This permits the broad conclusion that for the case of attractive bath interactions $(W<0)$, the frustration of Kondo screening due to charge fluctuations (arising from $W$) lead to the Mott metal-insulator transition.
+While the complexity of the RG equation for $J_{{\bf k}_1, {\bf k}_2}$ (eq.\eqref{KondoRGequation}) is clarified through a detailed numerical evaluation whose results are discussed below, its structure permits the broad conclusion that the frustration of Kondo screening due to charge fluctuations (arising for attractive bath interactions $W<0$) lead to the Mott metal-insulator transition~\cite{Mukherjee_2023}.
 
-%As we 
-Upon tuning the ratio of the bath and Kondo interactions ($W/J$) from zero to negative values, we observe that the following phases are emergent in the impurity model from the competition between the competing $J$ and $W$ couplings in eq.~\eqref{KondoRGequation}- (i) for $W/J<(W/J)_{\text{PG}}$, a local Fermi liquid phase (where the entirety of the Fermi surface participates in Kondo screening), (ii) for $\frac{W}{J} \in [(\frac{W}{J})_{\text{PG}}, (\frac{W}{J})_c]$, a local pseudogapped phase where disconnected parts of the Fermi surface around the node participate in Kondo screening, and (iii) a local moment phase for $\frac{W}{J} > (\frac{W}{J})_c$, where the impurity remains unscreened at low-energies.
-These can be visualised from $k-$space resolved spin correlations $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$; see Fig.~\ref{spinCorr} for $\chi_s(d,{\bf k})$ in the PG.
-The values $(W/J)_{\text{PG}}$ and $(W/J)_c$ are hence defined as the entry into and exit from
-%boundaries of 
-the pseudogap phase. %Using our 
-Upon mapping to the lattice model via tiling, we %consequently 
-observe that the $T=0$ Mott transition 
-%in $k-$space for 
-of the 2D Hubbard-Heisenberg model proceeds from Fermi liquid to Mott insulator through an intervening pseudogap phase
-%. obtain an $k$-space pseudogapped phase 
-with a partially gapped Fermi surface (i.e., a vanishing electronic density of states around the antinodal regions, Fig.~\ref{spinCorr}, right panel). 
-%This constitutes one of the main results of our work, and 
-We now lay out the mechanism leading to the formation of the pseudogap. 
-%it shows that the breakdown of Kondo screening on the 
-%a realistic 2D square lattice very naturally gives rise to a pseudogapped phase with Fermi arc-like behaviour. 
-%The local Fermi liquid and local moment phases for the impurity model correspond, respectively, to Fermi liquid and Mott insulating phases on the lattice.
-
-\paragraph*{Unraveling of Kondo screening.} 
-% As shown in Fig.~\ref{rgProgression}, the $k-$space anisotropic nature of the Kondo breakdown process 
-% %in this model 
-% can be visualised in terms of zeros of $J_{{\bf k}_1, {\bf k}_2}$.
-% %the Kondo coupling in $k-$space. 
-% Consider processes $J_{{\bf k}_N, {\bf k}}$ that involve spin-flip scattering between the node ${\bf k}_N = (\pi/2, \pi/2)$  and a general wavevector ${\bf k}$. 
-As shown in Fig.~\ref{rgProgression}, the $k-$space anisotropic nature of the Kondo breakdown process 
-can be visualised in terms of zeros of $J_{{\bf k}_N, {\bf k}}$, involving spin-flip scattering between the node ${\bf k}_N = (\pi/2, \pi/2)$  and a general wavevector ${\bf k}$. 
-At $W/J=0$, $J_{{\bf k}_N, {\bf k}}$ vanishes if ${\bf k}$ is either any of the antinodes or adjacent nodes. 
-%As 
-Tuning $W/J$ %is tuned 
-towards $(W/J)_{\text{PG}}$ leads to an unraveling of Kondo screening:
-%the beginning of the pseudogap, we find that 
-$J_{{\bf k}_N, {\bf k}}$ for ${\bf k}$ close to the adjacent nodes turn RG irrelevant first, and a patch of zeros subsequently appears in $J_{{\bf k}_N, {\bf k}}$ around this point (Fig.
-\ref{rgProgression} (left) panel).
-%This is the first step towards the decoupling of $J_{{\bf k}_1, {\bf k}_2}$ connecting adjacent quadrants of the Brillouin zone quadrants.
-%that is described in more detail in a later section.
-Tuning $W/J$ further extends the patch of zeros
-%systematic decoupling of 
-in $J_{{\bf k}_1, {\bf k}_2}$ for all ${\bf k}_{1}$ lying between a given node and the nearest antinodes (Fig.
-\ref{rgProgression} (center) and (right) panels), visualising a systematic decoupling of $J_{{\bf k}_1, {\bf k}_2}$ connecting adjacent quadrants of the Brillouin zone quadrants.
-%via an outwards progression of the patch of zeros 
-%from the nodal towards 
-%the single zeroes on the nearest antinodal regions . 
-Precisely At $W/J=(W/J)_{\text{PG}}$, the antinode joins this connected region of zeros in $J_{{\bf k}_1, {\bf k}_2}$, %and this coincides 
-marking (within our numerical precision) to the decoupling of the antinodes from all other points in the neighbourhood of the Fermi surface.
-This is an interaction-driven Lifshitz transition of the Fermi surface, and marks entry into a pseudogap phase possessing Fermi arcs~\cite{WuFerrero2018}.
-Importantly, it coincides with an emergent two-channel Kondo impurity model, where each channel corresponds to a pair of Fermi arcs on opposite faces of the conduction bath Fermi surface.
-%At this point, $J(k_N, k)$ is distributed through two disconnected non-zero patches, in the quadrant of $k_N$ and in the opposite quadrant. 
-The pseudogap expands by shrinking these disconnected Fermi arcs towards the respective nodes, leading to nodal metals whose disappearance marks the Mott transition. 
-%[TODO That the unraveling begins and ends at zeros of the Kondo coupling reveals the role of Fermi surface topology in obtaining the pseudogap~\cite{WuFerrero2018}.]
+Upon tuning the ratio of the bath and Kondo interactions ($W/J$) from zero to negative values (see phase diagram in Fig.\ref{spinCorr}(left)), we observe that the following phases are emergent in the impurity model from the competition between the competing $J$ and $W$ couplings in eq.~\eqref{KondoRGequation}- (i) for $W/J<(W/J)_{\text{PG}}$, a local Fermi liquid phase (where the entirety of the Fermi surface participates in Kondo screening), (ii) for $\frac{W}{J} \in [(\frac{W}{J})_{\text{PG}}, (\frac{W}{J})_c]$, a local PG phase where disconnected parts of the Fermi surface around the node participate in Kondo screening, and (iii) a local moment phase for $\frac{W}{J} > (\frac{W}{J})_c$, where the impurity remains unscreened at low-energies.
+These can be visualised from $k-$space resolved spin correlations $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$; see Fig.\ref{spinCorr}(center) for $\chi_s(d,{\bf k})$ in the PG.
+The values $(W/J)_{\text{PG}}$ and $(W/J)_c$ are hence defined as the entry into and exit from the PG phase.
+Upon mapping to the lattice model via tiling, we observe that the $T=0$ Mott transition of the 2D Hubbard-Heisenberg model proceeds from Fermi liquid to Mott insulator through an intervening PG phase with a partially gapped Fermi surface (i.e., a vanishing electronic density of states around the antinodal regions, Fig.\ref{spinCorr}(right)).
+We now lay out the mechanism for the formation of the PG.
 
@@
     \includegraphics[width=\linewidth]{zerosFlow.pdf}
-    \caption{Progression of Kondo couplings into decoupling of adjacent quadrants and the beginning of pseudogap.
-This is shown by tracking how $J(k_N, k)$ (with $k_N$ pivotted at the top left node and $k$ (depicted as an orange circle) moving along the top right Fermi surface arm) vanishes at different values of $W$ for different values of $k$.
-The route towards decoupling begins as scattering processes starting from the node and ending at the adjacent node lose spectral weight.
-This can be seen in the growth of the white zero region at the top left node.
-As we get closer to the pseudogap, points $k$ in between the node and antinode also decouple from the adjacent node (middle panel).
-The adjacent quadrant decoupling and onset into the pseudogap is completed by the antinode, which decouples from all points in the neighborhood of the Fermi surface.}
+    \caption{Left, Right and Center: Decoupling of $J_{{\bf k}, {\bf k'}}$ (positive, negative and zeros shown in yellow, purple and green respectively), with ${\bf k}$ (grey circle) corresponding to the node, antinode and a point mid-way between them on the top right arm of the Fermi surface respectively.
+This is seen via the appearance of zeros (green patches) of $J_{{\bf k}, {\bf k'}}$ for ${\bf k'}$ initially on the nodal regions of adjacent arms, and their subsequent progression towards the antinodes.
+The decoupling
+    ends with the onset of the pseudogap.
+    }
     \label{rgProgression}
@@
 
-\paragraph*{{\bf k}-resolved dynamical spectral weight transfer.} 
-%In order to understand the mechanism driving 
-Further insight into the pseudogapping 
-%transition 
-%in our model, we study 
-is obtained from the strong fluctuations observed in charge correlations between the gapless nodal and gapped antinodal regions in this 
-%pseudogapped 
-regime
-%, and find strong fluctuations
-(Fig.~\ref{chargeCorr}, left panel). This suggests that the 
-%creation of the 
-pseudogap in the lattice model
-%is brought about by 
-emerges from the impurity model from the 
-%development 
-onset of charge fluctuations in the bath that prohibit correlated spin fluctuations with the impurity spin that
-%. Since the latter 
-%processes are the ones that give rise 
-lead to the 
-%central 
-Kondo resonance at low-energies in the impurity spectral function. In this way, pseudogap formation 
-%is a demonstration of 
-results from the transfer of spectral weight from low to high energies. Accordingly, the pseudogap coincides 
-%is also seen from 
-with the appearance of poles of the lattice model self-energy $\Sigma ({\bf k},\omega=0)$
-%in $k-$space  
-near the antinodes; these poles approach the nodes 
-%as the system is 
-upon tuning towards the Mott transition
-%through the pseudogap 
-(Fig.~\ref{chargeCorr} right panel). The same is observed in the imaginary part of the impurity self-energy of the underlying impurity model~(Fig.\ref{channelDecoupling} (right panel)).
-
+\par\noindent\textit{Unraveling of Kondo screening.} 
+As shown in Fig.\ref{rgProgression}, the $k-$space anisotropic nature of the Kondo breakdown process 
+can be visualised in terms of zeros of $J_{{\bf k}_N, {\bf k}}$, involving spin-flip scattering between the node ${\bf k}_N = (\pi/2, \pi/2)$  and a general wavevector ${\bf k}$. 
+At $W/J=0$, $J_{{\bf k}_N, {\bf k}}$ vanishes if ${\bf k}$ is either any of the antinodes or adjacent nodes.
+Tuning $W/J$ towards $(W/J)_{\text{PG}}$ leads to an unraveling of Kondo screening: $J_{{\bf k}_N, {\bf k}}$ for ${\bf k}$ close to the adjacent nodes turn RG irrelevant first, and a patch of zeros subsequently appears in $J_{{\bf k}_N, {\bf k}}$ around this point (Fig.\ref{rgProgression}(left)).
+Tuning $W/J$ further extends the patch of zeros in $J_{{\bf k}_1, {\bf k}_2}$ for ${\bf k}_{1}$ lying between a given node and the nearest antinodes (Fig.\ref{rgProgression}(center) and (right)), visualising a systematic decoupling of $J_{{\bf k}_1, {\bf k}_2}$ connecting adjacent quadrants of the Brillouin zone quadrants.
+Precisely at $W/J=(W/J)_{\text{PG}}$, the antinode joins this connected region of zeros in $J_{{\bf k}_1, {\bf k}_2}$, marking (within our numerical precision) to the decoupling of the antinodes from all other points in the neighbourhood of the Fermi surface.
+This is an interaction-driven Lifshitz transition of the Fermi surface, and marks entry into a PG phase possessing Fermi arcs~\cite{WuFerrero2018}.
+Importantly, it coincides with an emergent two-channel Kondo (2CK) impurity model, where each channel corresponds to a pair of Fermi arcs on opposite faces of the conduction bath Fermi surface.
+The 2CK nature of the PG is guaranteed by the symmetry:
+$J_{{\bf k},{\bf k'}}= -J_{{\bf k}+{\bf Q},{\bf k'}}=-J_{{\bf k},{\bf k'}+{\bf Q}}$, where ${\bf Q} = (\pi,\pi)$.
+The PG expands by shrinking these disconnected Fermi arcs towards the respective nodes, leading to nodal metals whose disappearance marks the Mott transition.
+\par\noindent\textit{{\bf k}-resolved dynamical spectral weight transfer.}
+As shown in Fig.\ref{chargeCorr}(left), strong charge fluctuations develop between the nodal and antinodal regions of the Fermi surface in the PG regime, removing low-energy spectral weight from the antinodes to higher energies and leading to their selecting gapping.
+Accordingly, the PG coincides with the appearance of poles of the lattice model self-energy $\Sigma ({\bf k},\omega=0)$ near the antinodes; these poles approach the nodes upon tuning towards the Mott transition (Fig.\ref{chargeCorr}(right)).
+This mirrors the coalescing of self-energy poles at zero frequency in the underlying impurity model~\cite{suppmat}.
 \begin{figure}
@@
     \includegraphics[width=0.49\linewidth]{selfEnergyKspace-3.pdf}
-    \caption{Left: Charge isospin correlations $\chi_c({\bf k}_1, {\bf k}_2) = \braket{c^\dagger_{{\bf k}_1\uparrow}c^\dagger_{{\bf k}_1\downarrow}c_{{\bf k}_2\downarrow}c_{{\bf k}_2\uparrow} + \text{h.c.}}$ between the node and other $k-$points, in the pseudogap phase.
-The enhanced correlations between the node and the antinode suggests that these charge correlations lead to Kondo breakdown.
-The Kondo breakdown in turn leads to the gapping out of these regions in $k-$space on the lattice model, as seen from the appearance of poles in the imaginary self-enery (right panel).}
+    \caption{Left: Enhanced charge isospin correlations $\chi_c({\bf k}_1, {\bf k}_2) = \braket{c^\dagger_{{\bf k}_1\uparrow}c^\dagger_{{\bf k}_1\downarrow}c_{{\bf k}_2\downarrow}c_{{\bf k}_2\uparrow} + \text{h.c.}}$ between the nodal and antinodal regions, signalling Kondo breakdown in the pseudogap phase of the impurity model.
+Right: In turn, the breakdown leads to the gapping of the antinodal regions in the lattice model, seen from the appearance of poles in the imaginary part of the self-energy.}
     \label{chargeCorr}
@@
 
-\paragraph*{Non-Fermi liquid nature of the pseudogap.} In the pseudogap regime $|W/J|_{\text{PG}} < |W/J| < |W/J|_{c}$, the nature of the %metal 
-gapless Fermi arcs is observed to change dramatically. 
-%In this regime, we find that the Kondo couplings $J({\bf k}_1, {\bf k}_2)$ involving momenta from adjacent quadrants of the Brillouin zone are RG-irrelevant, disappearing from the low-energy fixed point Hamiltonian.
-First, we have already argued that the low-energy dynamics of these gapless Fermi arcs are governed by an underlying %simpler 
-two-channel Kondo (2CK) impurity model~\cite{Tsvelick_weigmann_mchannel_1985,emery_kivelson}.
-%, where the two pairs of opposite Brillouin zones form the two channels. 
-Previous works 
-%by Coleman and Ioffe
-%, as well as one of our own previous works~\cite{Patra2023MCK}, 
-show that the impurity self-energy of such a two-channel Kondo model displays marginal Fermi liquid (MFL) behaviour~\cite{Coleman_tsvelik,Schofield1997,Patra2023MCK}: $\Sigma \propto \omega \ln \omega$.
-The excitations of the 2CK also exhibit a separation of the spin, charge and channel quantum numbers~\cite{affleck1992}, i.e., with gapless excitations carrying only spin quantum number.
-The non-Fermi liquid nature
-%at this also happens in the present model 
-is further corroborated by the passage of the impurity quasiparticle residue $Z_\text{imp} = 1/(1 - \frac{\text{d}}{\text{d}\omega}\text{Re}(\Sigma))$ (Fig.~\ref{channelDecoupling} left panel) from finite values in the Fermi liquid phase to vanishingly small values in the pseudogap.
-%, where $\Sigma^\prime(\omega)$ is the real part of the impurity self-energy. 
-Upon tiling, 
-%we can immediately see that 
-the resulting MFL metal of the lattice model 
-%is arising from such a is not a Fermi liquid; the 
-possesses many-particle excitations that involve 
-%of the MFL will involve excitations of 
-multiple \(k-\)states.
-
-Crucially, we find that passage through the pseudogap phase causes the nature of the non-Fermi liquid to evolve: very near the transition, the excitations of the marginal Fermi liquid %description is found to break down at the transition, and is
-are replaced by 
-%those the non-Fermi liquid excitations 
-of a Hatsugai-Kohmoto model~\cite{Baskaran1991,Hatsugai1992}. %In order to obtain this, we carry out a 
-This insight is obtained from a perturbation-theoretic treatment of the RG fixed point Hamiltonian of the impurity model for $W/J\lesssim (W/J)_{\text{PG}}$,
-%in this region of the phase diagram, 
-by considering the effects of a small fixed point Kondo scattering probability \(J^*\) in the backdrop of a larger bath interaction parameter \(|W|\). 
-%We focus here on 
-This yields the HK model~\cite{Baskaran1991,Hatsugai1992} as the singular
-%, critical 
-part of the effective Hamiltonian arising from forward scattering processes 
-%within the complete Hamiltonian 
-(details 
-%described 
-in Appendix~\ref{hkmDerivation}):
-\begin{equation}\begin{aligned}\label{HKModel}
-	\Delta \tilde H_{{\bf q}_1 = {\bf q}_2} = \sum_{{\bf q},\sigma}\epsilon_{{\bf q}}{n}_{{\bf q},\sigma} + u\sum_{{\bf q}, \sigma}n_{{\bf q} \sigma} n_{{\bf q} \bar\sigma}~,
-\end{aligned}\end{equation}
-where the number operator \(n_{{\bf q} \sigma} = \phi^\dagger_{{\bf q}, \sigma} \phi_{{\bf q}, \sigma}\) pertains to emergent fermionic modes,
-\begin{equation}\begin{aligned}
-	\phi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} - c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~,
-\end{aligned}\end{equation}
-that are shifted by an excitation momentum \({\bf q}\) away from the nodal point \({\bf N}_1 = \left(\pi/2, \pi/2\right)\) and its nested partner \({\bf N}_1 + {\bf Q}_1 = \left(-\pi/2, -\pi/2\right)\).
-The kinetic energy (\(\epsilon_{\bf q}\)) and interaction \(u\) energy scales of the excitations are:
-\begin{equation}\begin{aligned}
-	\epsilon_{\bf q} = \text{sign}\left(\varepsilon_{{\bf N}_1 + {\bf q}}\right)\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W} + \frac{{J^*}^2}{-4W},~u = \frac{{J^*}^2}{4W}~.
-\end{aligned}\end{equation}
-%Eq.~\ref{HKModel} describes a Hatsugai-Kohmoto (HK) model~\cite{Baskaran1991,Hatsugai1992}, an exactly solvable model of correlated electrons. 
-The non-Fermi liquid 
-%nature of the gapless 
-excitations in the %metallic 
-gapless phase of the model 
-manifests as
-%in the form of 
-a divergent one-particle self-energy at the non-interacting Fermi surface~\cite{Phillips2020}:
-\begin{equation}\begin{aligned}
-	\Sigma_{{\bf q}}(\omega) = -\frac{u^2/4}{\omega - \epsilon_{\bf q}}, ~\Sigma_{\epsilon_{\bf q}=0}(\omega \to 0)  \to \infty~.
-\end{aligned}\end{equation}
-The zero-frequency pole of this singular metal %continues to 
-exists beyond the transition: in the Mott insulating phase, it marks a hard gap in the spectral function for charge excitations.
-The singular nature of the excitations in this regime can be attributed to the extremely non-local form of the impurity model (arising from the fact that it couples to only the nodal points in $k-$space).
-This divergent self-energy is consistent with our numerical calculations of the impurity self-energy which showed that the self-energy poles approach the $\omega=0$ point as the system is tuned towards the transition
+\par\noindent\textit{Non-Fermi liquid nature of the pseudogap.}
+In the PG regime $|W/J|_{\text{PG}} < |W/J| < |W/J|_{c}$, the nature of the gapless Fermi arcs is observed to change dramatically.
+We have already argued that the low-energy dynamics of these gapless Fermi arcs are governed by an underlying two-channel Kondo (2CK) impurity model~\cite{Tsvelick_weigmann_mchannel_1985,emery_kivelson}.
+The excitations of the 2CK exhibit a separation of spin, charge and channel quantum numbers~\cite{affleck1992}, with gapless excitations carrying only the spin quantum number.
+Previous works show that the impurity self-energy of such a two-channel Kondo model displays marginal Fermi liquid (MFL) behaviour~\cite{Coleman_tsvelik,Schofield1997,Patra2023MCK} with real and imaginary parts of the self-energy as $\Sigma^{\prime} \sim \omega\ln\omega, \Sigma^{\prime\prime}\sim-\omega$.
+This gives rise~\cite{varma2002singular} to a linear scattering rate \(\Gamma \sim \omega\), and a logarithmically vanishing quasiparticle residue $Z_\text{imp}(\omega)
+\sim (c - \ln \omega)^{-1}$ (where \(c\) is a constant). 
+This is consistent with the rapid fall of the impurity quasiparticle residue $Z_\text{imp}$ (Fig.\ref{channelDecoupling}(left)) from finite values in the Fermi liquid phase to vanishingly small values in the PG.
+The inset of Fig.\ref{channelDecoupling}(left) shows the emergence of increasingly uncompensated local magnetic moments upon traversing the PG phase.
 
@@
     \includegraphics[width=0.49\linewidth]{localQPResidue.pdf}
-    \includegraphics[width=0.49\linewidth]{sigmaImag_49-1000.pdf}
-    \caption{Left: Suppression of quasiparticle residue as the system is tuned through various phases.
-There is an initial abrupt fall at $|W| = |W^*|$, where the system enters the pseudogap and the excitations become non-Fermi liquid.
-There's a second abrupt fall at the transition due to the presence of a divergent self-energy.
-Right: Analogous progress of imaginary part of the local self-energy.
-The poles at the edge of the central Kondo resonance move progressively closer to zero frequency until the Mott pole emerges at zero frequency at the transition.}
+    \includegraphics[width=0.49\linewidth]{I2-di_69-2000.pdf}
+    \caption{Left: Suppression of quasiparticle residue as the impurity model is tuned towards the Mott transition.
+An initial drastic fall observed for $W/J \lesssim (W/J)_\text{PG}$, signalling the destruction of the Fermi liquid with unraveling of Kondo screening.
+A second drastic fall is observed close to the Mott transition due to a divergent self-energy.
+Inset shows the growth of unscreened impurity magnetic moment in the pseudogap phase.
+    Right: Mutual information $I_{2}(d,r)$ between the impurity spin and conduction bath local spins as a function of the distance {\bf r} between them.
+$I_{2}(d,r)$ decays exponentially in the Fermi liquid phase (blue), but show long-ranged behaviour in the non-Fermi liquid phase (green, yellow).
+The range of the entanglement is seen to grow yet larger particularly close to the transition (green).
+    }
     \label{channelDecoupling}
@@
 
-\paragraph{Morphing of the non-Fermi liquid through the pseudogap}
-In order to probe how the metal becomes increasingly correlated as it is tuned through the pseudogap, we compare the quasiparticle residue \(Z_\text{imp}\) and the scattering rate \(\Gamma\) of the quasiparticles, at the beginning and end of the pseudogap.
-For the regime \(|W| \gtrapprox |W|^*\), the low-energy excitations obey the marginal Fermi liquid theory: \(\Sigma^{\prime} \sim \omega\ln\omega, \Sigma^{\prime\prime}\sim-\omega\).
-This gives rise to a linear scattering rate \(\Gamma \sim \omega\) (arising from the imaginary part of the self-energy), and a logarithmically vanishing quasiparticle residue~\cite{varma2002singular}
-\begin{equation}\begin{aligned}
-Z_\text{imp}(\omega) = (1 - \frac{d\Sigma^\prime}{d\omega})^{-1} \sim (c - \ln \omega)^{-1}
+\par\noindent\textit{Evolution of the pseudogapped non-Fermi liquid.} Very close to the transition, the excitations of the marginal Fermi liquid are replaced by those of a Hatsugai-Kohmoto model~\cite{Baskaran1991,Hatsugai1992}.
+This insight is obtained from a perturbation-theoretic treatment of the RG fixed point Hamiltonian of the impurity model for $W/J\lesssim (W/J)_{\text{PG}}$, by considering the effects of a small fixed point Kondo scattering probability \(J^*\) in the backdrop of a larger bath interaction parameter \(|W|\).
+This yields the HK model~\cite{Baskaran1991,Hatsugai1992} as the singular part of the effective Hamiltonian arising from forward scattering processes (details in Appendix~\ref{hkmDerivation}):
+\begin{equation}\begin{aligned}\label{HKModel}
+	\Delta \tilde H_{{\bf q}_1 = {\bf q}_2} = \sum_{{\bf q},\sigma}\epsilon_{{\bf q}}{n}_{{\bf q},\sigma} + u\sum_{{\bf q}, \sigma}n_{{\bf q} \sigma} n_{{\bf q} \bar\sigma}~,
 \end{aligned}\end{equation}
-where \(c\) is a constant.
-Close to the transition (\(|W| \lesssim |W_c|\)), the low-energy theory is described by a Hatsugai-Kohmoto model, with a diverging self-energy (obtained in eq.~\eqref{HKSelfenergy} above):
-\begin{equation}\begin{aligned}\label{HKSelfenergy}
-	\Sigma({\bf k}) = u^2/\left(\omega - \epsilon_{\bf k}\right) = U^2 \left[\mathcal{P}(\frac{1}{\omega - \epsilon_{\bf k}}) - i\pi \delta(\omega - \epsilon_{\bf k})\right]~,
-\end{aligned}\end{equation}
-where \(\mathcal{P}\left(\cdot\right)\) represents the principal value, and we used the Sokhotski–Plemelj theorem to write down the final expression.
-For small but non-zero values of \(\omega - \epsilon_{\bf k}\), we get \(Z_\text{imp} \sim \omega^2/U^2 \).
-The metal near the transition therefore displays a much more rapid vanishing of the quasiparticle residue compared to the logarithmic vanishing for the marginal Fermi liquid.
-The scattering rate precisely at the surface \(\omega=\epsilon_{\bf k}\), in fact, diverges: \(\Gamma \sim U^2\delta(\omega - \epsilon_{\bf k})\), in contrast to the linearly vanishing scattering rate of the MFL.
+where the number operator \(n_{{\bf q} \sigma} = \phi^\dagger_{{\bf q}, \sigma} \phi_{{\bf q}, \sigma}\) pertains to emergent fermionic relative modes $\phi_{{\bf q}, \sigma}$ that are shifted by an excitation momentum \({\bf q}\) away from the nodal point \({\bf N}_1 = \left(\pi/2, \pi/2\right)\) and its
+partner \({\bf N}_1 + {\bf Q}_1 = \left(-\pi/2, -\pi/2\right)\).
+The kinetic energy \(\epsilon_{\bf q}\) and interaction energy \(u\sim J^{2}/W\) are dispersion and Kondo scales renormalised by conduction bath correlations~\cite{suppmat}.
 
-The divergence of the self-energy at the transition also mark the onset of the Mott insulator (Fig.~\ref{channelDecoupling}, righ panel).
-In this way, we have shown that the Fermi liquid must first morph into a marginal Fermi liquid and then into a Hatsugai-Kohmoto non-Fermi liquid before the Mott insulator can emerge.
-Our calculations also show that beyond the HK terms, the effective Hamiltonian near the transition contains pairing fluctuations: while subdominant at $1/2$-filling, their presence suggests that upon doping away from the Mott insulating state, such a non-Fermi liquid can undergo a superconducting transition.
-Recent works on the HK model suggest that such a superconductor is likely to be of the non-BCS kind~\cite{Phillips2020}.
+Consequently, the resulting non-Fermi liquid metal of the lattice model involves long-lived excitations of multiple \({\bf k}\)-states, and manifest in the form of 
+a divergent one-particle self-energy at the non-interacting Fermi surface~\cite{Phillips2020}:
+	$\Sigma_{{\bf q}}(\omega) = -\frac{u^2/4}{\omega - \epsilon_{\bf q}}$, such that $\Sigma_{\epsilon_{\bf q}=0}(\omega \to 0)  \to \infty$. This zero-frequency self-energy pole 
+presages the transition into a Mott insulating phase, where it marks a hard gap in the spectral function for charge excitations.
+This is consistent with our findings for the lattice (Fig.\ref{chargeCorr}(right)) and impurity self-energies~\cite{suppmat}.
+Further, for small but non-zero values of \(\omega - \epsilon_{\bf k}\), we obtain the quasiparticle residue \(Z_\text{imp} \sim \omega^2/U^2 \), i.e., a faster vanishing of $Z_{imp}$ compared to the MFL.
+This explains the sharp fall in $Z_\text{imp}$ observed precisely at the transition (Fig.\ref{channelDecoupling}(left)).
+The scattering rate precisely at the Fermi surface \(\omega=\epsilon_{\bf k}\) diverges, \(\Gamma \sim U^2\delta(\omega - \epsilon_{\bf k})\), in contrast to \(\Gamma \sim \omega\) observed for the MFL.
+\par\noindent\textit{Non-local nature of the pseudogap.}
+In Fig.\ref{channelDecoupling}(right), mutual information between the impurity spin and conduction bath sites are observed to undergo a crossover within the PG, from short-ranged behaviour at its onset to long-ranged behaviour as the Mott transition is approached.
+Similar long-ranged behaviour of spin-flip correlations is also observed between the impurity and bath sites~\cite{suppmat}.
+This is further evidence of the breakdown of local Kondo screening, and resulting Landau quasiparticle excitations.
+This implies that the observed Mott transition lies well beyond the paradigm of local quantum criticality~\cite{Si2001}: the non-Fermi liquid Fermi arcs of the PG phase display increasingly critical behaviour close to the transition, with dynamics that cannot be described by local quantum fluctuations, and excitations that become truly long-ranged.
+Additionally, we observe that the nodal metal possesses pairing fluctuations~\cite{suppmat} that can be rendered dominant upon doping~\cite{Phillips2020}.
+\par\noindent\textit{Conclusions.} We find compelling evidence that the Mott transition involves continuous passage through a PG phase possessing an increasingly singular, non-local nodal non-Fermi liquid metal, and the onset of long-ranged entanglement at criticality.
+The evolution of this singular PG phase with doping
+deserves attention.
+\par\noindent\textit{Acknowledgments.}
+AM thanks IISER Kolkata for funding through a JRF and SRF. S Lal thanks the SERB, Govt. of India for funding through MATRICS Grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
+\bibliography{tilingProject}% Produces the bibliography via BibTeX.
 
-Real-space spin-correlations and entanglement within the impurity model (Fig.~\ref{realSpaceCorrelations}) reveal that the spin correlations undergo a crossover within the PG from short-ranged behaviour at the onset to long-ranged behaviour as the Mott transition is approached.
-[TODO This matches well with similar observations from diagrammatic Monte Carlo simulations of the Hubbard model at finite temperatures, suggesting that the behaviour observed here is generic~\cite{SimkovicFerrero2024}].
-the This is further evidence of the breakdown of local Kondo screening and Landau quasiparticles inside the PG.
-Another implication of these results is that the paradigm governing such a transition is most likely not that of {\it local quantum criticality} - the critical behaviour close to the transition cannot be described by the dynamics of the local sites, and the excitations become truly long-ranged in this regime.
+\appendix
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.49\linewidth]{SF-di_69-2000.pdf}
-    \includegraphics[width=0.49\linewidth]{I2-di_69-2000.pdf}
-    \caption{Emergence of long-ranged correlations near the critical point.
-Left panel: Spin correlations $\chi_s(d,{\bf k}) = \braket{{\bf S}_d^+\cdot{\bf S}_{\bf r}^-}$ between the impurity spin and conduction bath local spins at a distance {\bf r}, as a function of {\bf r}.
-Right: Mutual information between the same objects, again as a function of the distance.
-Both decay exponentially fast in the Fermi liquid phase (blue), but show long-ranged behaviour in the non-Fermi liquid phase (green, yellow) and particularly close to the transition (green), indicating that the description of the transition is beyond local quantum criticality.}
-    \label{realSpaceCorrelations}
-\end{figure}
-
-\paragraph{Luttinger's theorem in the presence of Luttinger surfaces}
-One can also ask whether Luttinger's theorem is satisfied in our model in the presence of Luttinger surfaces.
+\section{Appendixes}
+\paragraph*{Luttinger's theorem in the presence of Luttinger surfaces.} One can also ask whether Luttinger's theorem is satisfied in our model in the presence of Luttinger surfaces.
 It has been shown that particle-hole symmetric systems always satisfy a generalised Luttinger's theorem~\cite{seki2017topological}, where the Fermi volume $V_L$ is represented as the difference in the number of poles and zeros, of the single-particle Greens function, that are enclosed by the Fermi surface~\cite{seki2017topological}.
@@
 
-\paragraph*{Acknowledgements}
-AM thanks IISER Kolkata for funding through a JRF and SRF. S Lal thanks the SERB, Govt. of India for funding through MATRICS Grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
+\paragraph*{Tiling towards a Hubbard-Heisenberg model with an embedded extended SIAM}
+We give more details here regarding the construction of the lattice model from the impurity model.
+As mentioned in the manuscript, the lattice-embedded impurity model is of the form $H({\bf r}_d) = H_\text{imp} + H_\text{cbath} + H_\text{imp-cbath}$, where $H_\text{imp}$ is the impurity part:
+\begin{equation}\begin{aligned}\label{onsiteHamiltonian}
+	H_\text{imp} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 - \eta\sum_\sigma \hat n_{{\bf r}_d\sigma}~,
+\end{aligned}\end{equation}
+\(\mathcal{H}_\text{cbath}\) is the conduction bath part:
+\begin{equation}\begin{aligned}\label{bathHamiltonian}
+	{H}_\text{cbath} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \\
+    \frac{1}{2 \mathcal{Z}}W\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
+\end{aligned}\end{equation}
+and ${H}_\text{imp-cbath}$ is the impurity-bath hybridisation:
+\begin{equation}\begin{aligned}\label{interactionHamiltonian}
+	{H}_\text{imp-cbath} = \frac{J}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}\sum_{{\bf z}\in\text{NN}({\bf r}_d)} {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \\
+    - \frac{V}{\sqrt{\mathcal{Z}}}\sum_{\sigma} \sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)~.
+\end{aligned}\end{equation}
+In this model, ${\bf r}_d$ is the position of the impurity site, and \(\left<{\bf r}_i, {\bf r}_j\right>\neq {\bf r}_d\) indicates that the sum is over all nearest-neighbour pairs of sites avoiding the impurity site \({\bf r}_d\).
+\(\boldsymbol \tau = \left( \tau_x, \tau_y, \tau_z \right) \) is the vector of Pauli matrices.
+\(\sigma\) and \(\sigma^\prime\) can be \(\pm 1\) and represent up and down configurations.
 
-\appendix
+The tiled Hamiltonian can be obtained as 
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{tiled} = \mathcal{T}[H({\bf r}_d)]
+    % \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)H({\bf r}_d)T({\bf r} - {\bf r}_d)~,
+\end{aligned}\end{equation}
+where the $\mathcal{T}[H] = \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)HT({\bf r} - {\bf r}_d)$ represents the symmetrisation/tiling procedure, and the action of the many-body translation operators $T^\dagger({\bf a})$ on a general operator are defined as
+\begin{equation}\begin{aligned}
+T^\dagger({\bf a}) \mathcal{O}\left({\bf r}_1, {\bf r}_2,\ldots\right)T({\bf a}) = \mathcal{O}\left({\bf r}_1 + {\bf a}, {\bf r}_2 + {\bf a},\ldots\right)~.
+\end{aligned}\end{equation}
 
-\section{Appendixes}
+We consider the effect of the translation operations on each part of the Hamiltonian:
+\begin{equation}\begin{aligned}
+	&\mathcal{T}\left[{H}_\text{cbath}({\bf r}_d, {\bf z})\right] = -\frac{(N-2)t}{\sqrt\mathcal{Z}}\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
+    &- \frac{1}{2}W\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}~,\\
+	&\mathcal{T}\left[{H}_\text{imp}\right] = -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}~,\\
+    &\mathcal{T}\left[{H}_\text{imp-cbath}\right]\\
+     &=\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]~.
+\end{aligned}\end{equation}
+We have defined \({\bf S}_{{\bf r}_j} =\sum_{\sigma,\sigma^\prime} {\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime}\) as the local spin operator.
+While constructing the tiled Hamiltonian, we have added extra copies of the non-interacting Hamiltonian \(\mathcal{H}_\text{cbath-nint} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\) for the conduction bath (this results in the factors of \(N-2\) and \(N-1\) in front of the first and third terms).
 
-\bibliography{tilingProject}% Produces the bibliography via BibTeX.
-
+Upon removing these repeated terms, the result of the tiling operations is a Hubbard-Heisenberg model, of the form
+\begin{equation}\begin{aligned}
+	\mathcal{H}_\text{HH} &= -\frac{1}{\sqrt\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma} \\
+    &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
+\end{aligned}\end{equation}
+where the tilde symbol indicates that the parameters are for the lattice model (and not the auxiliary model).
+By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to each other:
+\begin{equation}\begin{aligned}\label{couplingsMappings}
+	\tilde t = t+2V,~~ \tilde U = U + W, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
+\end{aligned}\end{equation}
+In summary, the appropriate method for reconstructing the lattice model Hamiltonian is therefore
+\begin{equation}\begin{aligned}\label{tilingPrescriptionFinal}
+	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}~,
+\end{aligned}\end{equation}
+where we replaced \(N-3\) with \(N\) assuming a large number of sites. Using this, the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.
 \end{document}

### 2025-12-10 submissions/TilingUploadNJPResponse/RefereeResponse.tex
started creating referee response

\documentclass[10pt]{revtex4-2}
\usepackage{amsmath,amssymb,braket,newtxtext}
\usepackage[hidelinks]{hyperref}
\usepackage{color}
\usepackage{xcolor}
% \usepackage[margin=1.5cm,bottom=1.5cm]{geometry}
\newcommand{\shat}{\hat{\mathbf{s}}}
\newcommand{\response}[1]{{\bf Response. }{\color{blue}{#1}}}

\begin{document}

\title{RESPONSE TO REFEREE COMMENTS FOR NJP-119431}
\author{Abhirup Mukherjee}
\author{S. R. Hassan}
\author{Anamitra Mukherjee}
\author{N. S. Vidhyadhiraja}
\author{A. Taraphder}
\author{Siddhartha Lal}
\maketitle
\vspace{-20pt}
\hrulefill
\vspace{10pt}

We thank the Editorial Board Member and all referees for their careful reading of our manuscript and for their constructive comments and questions. We are encouraged by the overall positive reception of our work, including the acknowledgement of its relevance, technical soundness, and suitability for publication in New Journal of Physics.

Below, we present our responses (in blue) to the points raised by the referees.

\section*{Response to Referee 1}
The authors proposed the possibility that the pseudogap phase is a distinct quantum phase characterized by the so-called Mott metal. I recommend sending the manuscript to reviewers.

\section*{Response to Referee 2}
The impurity-to-lattice tiling procedure and unitary renormalization group (URG) methods, while carefully implemented, appear to extend prior impurity-based constructions rather than introduce a fundamentally new paradigm. The claimed "controlled route to Mott criticality" should be more clearly distinguished from existing dynamical mean-field theory (DMFT) and functional renormalization group (fRG) approaches, particularly in terms of predictive power or access to uncharted regimes.

\response{}

The identification of the pseudogap as a "Mott metal" with deconfined holon-doublon excitations is intriguing but lacks direct experimental or numerical validation beyond the model itself. Comparisons with established benchmarks from quantum Monte Carlo, ARPES, or optical conductivity experiments on cuprates would help ground these claims and clarify the added value beyond prior theoretical proposals.

\response{hi}

The restriction to a single-band extended Hubbard model on a square lattice limits the generality of the conclusions. Demonstrating the framework's applicability to at least one additional model or geometry would strengthen its broad relevance to correlated systems.

\response{}

Critical experimental realities such as disorder, doping inhomogeneity, or phonon coupling are not addressed. A discussion of how such effects could be incorporated or might alter the conclusions is necessary to assess the experimental relevance of the proposed mechanism.

\response{hi}

The connection to the Hatsugai-Kohmoto model at criticality, while mathematically interesting, risks being viewed as a special case. The authors should clarify whether this connection holds for generic models or relies on fine-tuned symmetries or fillings.

\response{hi}

\section*{Response to Referee 3}
In the present manuscript the authors have studied the interplay between the spin exchange and local Coulomb interaction in a two-dimensional model by employing a unitary renormalization group (URG). This work can be considered as a continuation of the author's previous published works. While I found that the URG is acceptable for treating electron correlation problems, the principal model studied in this manuscript (Eq. (15)) looks like an artefact, because the spin exchange  (the second term in Eq. (15)) is actually can be generated by the hopping and local interaction terms. In general, the spin exchange is roughly proportional to $t^2/U$ (t, U here correspond to the ones with tilde symbol in Eq. (15)). Therefore, the studied model already double-counts the spin exchange. In addition, it is not clear what real materials or systems can be described by the studied model. The authors have to clarify these points before the manuscript can be acceptable for publication.

\section*{Response to Referee 4}
The manuscript addresses metal-to-insulator transition in strongly correlated lattice models applicable to materials such as layered copper oxides, with particular focus on intermediate pseudogap (PG) state. First, a lattice impurity model is formulated, and subsequently mapped to a lattice t-J-U model via tiling procedure. The Authors subsequently map the Green's functions from the auxiliary impurity model to the target t-J-U model, and analyze its dynamical phase diagram as a function of microscopic parameters. The employed methodology is based on solving normalization group equations for the auxiliary model and translating the results into the of target lattice model language via derived mapping. The Authors link the PG state to the to the breakdown of the Kondo screening within the underlying auxiliary model, and provide a comprehensive theoretical analysis of thereof.

I have looked through it with interest, and I have several comments and queries:

1. The Authors consider the model with nearest-neighbor hopping (t') integrals only, which is also reflected in the target lattice model. It is well known that t' is highly relevant to the physics of systems exhibiting pseudogap (such as high-Tc cuprates). Is it possible to incorporate those terms within the present method and is there any qualitative change expected?
2. The Hamiltonian term $H_coup$ [Eq. (3)] incorporates both hybridization and Kondo-type exchange. Within an impurity model, the former Kondo term is typically derived by canonical perturbation expansion from he model containing V-term, so (technically) including both may be regarded as double-counting. Can, for instance, either V or J term be neglected in the analysis? What would be the consequences for PG state?
3. Technical remarks: In Eq. (3), J should be probably a function of Z to reproduce k-dependen form of J in Eq. (5). Apparently in Eq. (A1) of the first Appendix this is the case. Also, it is not immediately clear to me why the impurity creation and annihilation operators disappear from the impurity model (1) following tiling procedure in Sec. III, resulting in single-band Hamiltonian (15). This could be explained in grater detail in the manuscript.
4. The lattice model of Eq. (15), referred to by the Authors as extended-Hubbard, has been extensively studied in literature in the context of high-Tc superconductors as the t-J-U model. See, e.g., https://doi.org/10.1103/PhysRevB.95.024506 or a review https://doi.org/10.1016/j.physrep.2022.02.003 and references therein. Comparison with previous work on t-J-U model would benefit the manuscript.
5. Whereas the Authors work is clearly relevant to specific materials, such and layered copper oxides, nickelates, and possibly several other systems, the discussion of specific experimental consequences is limited. The manuscript would benefit from more direct and detailed relation to specific materials in the introduction and/or summary section.

The manuscript is well written and organized. The methodology appears sound and the mapping of the auxiliary to physical model is of interest. I believe that the manuscript could be suitable for publication in NJP, following clarification of the above points.

\end{document}

### 2025-12-10 submissions/Earlier Versions of Manuscript/manuscript.tex
started creating referee response

% \documentclass[%
%  reprint,
% superscriptaddress,
% groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
% amsmath,amssymb,
% aps,
% prl,superscriptaddress
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
% pdflatex,
% sn-nature,
% ]{sn-jnl}
\documentclass[pdflatex,sn-mathphys-num]{sn-jnl}

\usepackage{amsmath,amssymb}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{braket}
\usepackage{color}

\graphicspath{{./figures/}}

\begin{document}

%\title{Pseudogapped non-Fermi liquid phase arising from Kondo breakdown at the Mott transition}

\title{Pseudogap Mott criticality via a long-range multipartite entangled strongly coupled non-Fermi liquid}

%\title{Pseudogap and Mott criticality: Stretching Kondo Screening to Breaking Point}

%\title{What lies between a Fermi liquid and a Mott insulator in two dimensions? Insights from an impurity model}% Force line breaks with \\

\author[1]{Abhirup Mukherjee}
\affil[1]{
 Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
}
\author[2]{S. R. Hassan}
\affil[2]{The Institute of Mathematical Sciences, C.I.T. Campus, Chennai 600 113, India}
\author[3]{Anamitra Mukherjee}
\affil[3]{School of Physical Sciences, National Institute of Science, Education and Research, HBNI, Jatni 752050, India}
\author[4]{N. S. Vidhyadhiraja}
\affil[4]{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
\author[5]{A. Taraphder}
\affil[5]{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
%
\author*[1]{Siddhartha Lal}

\date{\today}
\abstract{
We propose a new theoretical framework for strongly correlated electron systems 
%We present an auxiliary model approach 
that illustrates the centrality of the pseudogap phenomenon in the Mott transition of the extended Hubbard model on a half-filled square lattice. Our approach is based on %Vacancy--Kondo--Heisenberg (VKH) model and a Quantum Tiling Reconstruction (QTR) scheme. 
%a real-space Kondo-defect unit ---comprising a localized 
a spin-1/2 defect at a lattice vacancy that is Kondo exchange-coupled to neighbouring lattice sites, and which is tiled across a square lattice to yield a translationally invariant model. The pseudogap is emergent from a Fermi liquid via the systematic unravelling of Kondo screening frustrated by charge fluctuations in the conduction bath of the underlying lattice-embedded Kondo model. We demonstrate that the pseudogap is a strongly interacting phase of quantum matter intimately tied to the existence of a critical Fermi surface, with non-Fermi excitations that have long-ranged and multipartite entanglement. The Mott criticality of the non-Fermi liquid is signalled by the emergence of a singular self-energy at the Fermi energy. Our analysis points to this novel phase of gapless quantum matter being stabilised by changes in the topological properties of the Fermi surface that arise from encroaching surfaces of zeros of the single-particle Greens function.
%passage from a Fermi liquid to a Mott insulator involves two stages: the first involves a systematic unravelling of Kondo screening, frustrated by charge fluctuations in the conduction bath of the underlying lattice-embedded quantum impurity model. 
%This destabilises the Fermi liquid, culminating in the disconnection of the Fermi surface with the appearance of gaps at the antinodes. In the second stage, an emergent pseudogap phase arises from an effective two-channel Kondo problem in the underlying impurity model. The resulting Fermi arcs possess non-Fermi liquid excitations proximate to a critical Fermi surface. Upon approaching the Mott transition, the nature of this exotic metal evolves with shrinking of the Fermi arcs towards a singular nodal non-Fermi liquid. This accompanies the onset of long-range multipartite entanglement and spin-flip correlations in real-space, revealing the Mott transition on the square lattice to be beyond the paradigm of local quantum criticality.
}

\maketitle

\section{Introduction.}
The origin of the pseudogap and strange metal phases of the cuprates continues to be hotly debated in the context of high-temperature superconductivity~\cite{keimer2015quantum}. The anomalous pseudogap (PG) phase, observed in the cuprates, exhibits nodal-antinodal dichotomy with spectral weight concentrated on Fermi arcs around the nodal regions~\cite{loeserKapitulnik1996,Norman1998,Hashimoto2014}. While several calculations have observed a PG in the two dimensional Hubbard model ~\cite{KyungKotliar2006,MacridinAzevedo2006,WuFerrero2018,anirbanmott2,HilleAndergassen2020}, there is no general consensus regarding various aspects of the PG phase, including its relation to the proximate Mott insulating and superconducting phases~\cite{FradkinRevModPhys2015,anirbanmott2,Kitatani2023,Sorella2023}, its evolution from weak- to strong-coupling ~\cite{HuangDevereaux2018,Fedor2022,SimkovicFerrero2024}, and whether the nodal-antinodal dichotomy is intrinsic to the model~\cite{Hashimoto2014,Schafer2021}. Importantly, the connection between finite-temperature crossovers and zero-temperature ground states observed in various analyses remains unclear~\cite{White1998,Ido2018,ProustTaillefer2019,Ponsioen2019,Shengtao2021,XuZhang2022}.

Viewed as a quantum mechanical phenomenon, the PG involves the emergence of disconnected gapped regions of the Fermi surface (known as Luttinger surfaces of zeros of the single-particle Greens function ~\cite{dzyaloshinskii2003some,phillips2006mottness}) from a Fermi liquid with a connected Fermi surface. The growth and eventual connection of these Luttinger surfaces then leads to the transition into the Mott insulator. Which physical principles guide these events and what do they teach us about the criticality that obtains Mott insulation? Further, can the excitations of the gapless Fermi arcs be adiabatically connected to those of a non-interacting electron gas in the presence of the Luttinger surfaces? If not, what kind of scale-invariant quantum matter do they characterise? Which features of the PG elucidate the breakdown of screening in the Fermi liquid and lead instead to a singular self-energy in the Mott insulator?

We present a new auxiliary model approach 
to the strong coupling physics of particle-hole symmetric 2D Hubbard-Heisenberg model at zero temperature, revealing the origin and nature of its PG phase and the subsequent Mott transition. The first step 
requires identifying an appropriate lattice-embedded quantum impurity model, and a scaling analysis of its low-energy phases. Subsequently, a lattice model is  constructed by applying many-body lattice translation operators~\cite{stoyanova} on the impurity model (henceforth referred as \textit{tiling}), obtaining thereby various quantities of the former from the latter. Translation invariance is thus restored differently within our approach from the dynamical mean-field approximation~\cite{georges1996} and its cluster variants~\cite{Hettler2000DCA, Kotliar2001Cellular, Maier2005, Sakai2023}.

Combining the scaling analysis of the impurity model with tiling procedure provides momentum-space resolution crucial to unveiling the PG phenomenon, and clarifies the role of the Kondo breakdown process at the heart of Mott transition~\cite{fabrizio2017kondophysicsmotttransition,RADEMAKER2025}. 
Emerging from a systematic unraveling of Kondo screening, the PG phase is separated from the Fermi liquid (FL) and Mott insulating phases by correlation-driven Lifshitz transitions of the Fermi surface (FS)~\cite{sakai2009evolution}. Passage through the PG involves dynamical transfer of spectral weight between gapped anti-nodal Luttinger surfaces (zeros of the single-particle Green's function) and gapless nodal arcs with non-FL excitations. We also observe the concomitant onset of long-range real-space entanglement and spin-flip correlations close to the Mott transition, rendering it beyond local quantum criticality~\cite{Si2001}. Our findings serve as a demonstration of the PG as a strongly interacting long-range multipartite entangled phase of quantum matter linked to the Mott criticality of the 2D extended Hubbard model~\cite{Phillips2013Unparticles}. This follows a recent proposal~\cite{lanave2025} that the emergence of Luttinger surfaces lead to the spontaneous violation of a $\mathbb{Z}_{2}$ symmetry associated with the Fermi surface~\cite{Anderson2001,Huang2022}, and thence to the existence of non-local propagating degrees of freedom.

\textcolor{red}{ AM: Some comments expanding on for identifying a underlying principle: The encroaching of the Fermi surface by the creeping Luttinger surface increases with electronic interaction between the bath electrons (W), which frustrates the Kondo screening and is controlled by (W/J). This phenomenon leads to a transition to a non-Fermi liquid state, where the quasiparticle excitations lose coherence and are characterized by disconnected Fermi surfaces and a pseudo-gapped density of states. The eventual demise of the Fermi surface and its replacement by a connected Luttinger surface finally leads to the Mott phase. }

\textcolor{red}{We demonstrate that a nodal non-Fermi liquid (at the verge of the Mott transition, when the Fermi surface has shrunk to a point) is described by the exactly solvable Hatsugai-Kohmoto (HK) model. The (HK) model exhibits a specific type of symmetry breaking, which is crucial for stabilizing non-Fermi liquids and Mott physics. This involves breaking a local-in-momentum space $Z_2$ symmetry, which serves as an organizing principle for the Mott transition. This $Z_2$ symmetry [Ansderon, Haldane,  Phillips] is local-in-momentum space and non-local in real space (exhibiting long-range multi-partite entanglement (it would be nice if we could demonstrate this) ). When this symmetry is disrupted, the symmetry between particle addition and removal around the chemical potential is also lost. The resulting non-Fermi liquid is characterized by a self-energy scaling as $\omega^{-2}$ with energy in the HK model. We show that the same self-energy characterizes the entire pseudo-gapped regime of the extended Hubbard-Heisenberg model. We also demonstrate the $Z_2$ breaking for the URG-derived Hamiltonian in the pseudo-gapped phase, concretely linking the origin of the non-Fermi liquid behavior to the loss of particle-hole symmetry.  Our result reveals a new adiabatic continuity connecting the Mott insulator phase (described by the HK model by the emergence of a fully connected Luttinger surface) to a family of pseudo-gapped non-Fermi liquid states, in analogy to adiabatic continuity of the noninteracting fermions to the Fermi liquid phase.}

\section{A lattice-embedded impurity model.}
Building on the insight, that the Kondo breakdown in a simple extension of the Anderson impurity model~\cite{Mukherjee_2023} captures the physics of Mott transition in infinite dimensions~\cite{georges1996}), we study a similar Anderson impurity model embedded within a square lattice 
\begin{equation}\begin{aligned}\label{impurityModel}
	\mathcal{H}_\text{aux} = H_\text{imp} + H_\text{imp-cbath} + H_\text{cbath}~, 
\end{aligned}\end{equation}
where $H_{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2$ is the Hamiltonian for the localised impurity site, and the impurity (with creation operator $c^\dagger_{d\sigma}$, and spin-1/2 moment ${\bf S}_d$) interacts with four nearest neighbour sites ($c_{Z\sigma}$, labelled by index $Z$) 
through local Kondo terms of uniform strength $J$ as well as single-particle hybridisation $V$, \(H_\text{imp-cbath} =\frac{1}{2} J\sum_{\sigma_1,\sigma_2}\sum_{Z} {\bf S}_d\cdot c^\dagger_{Z\sigma_1}{\boldsymbol \tau}_{\sigma_1,\sigma_2} c_{Z\sigma_2} - V \sum_{\sigma, Z} \left(c^\dagger_{Z\sigma} c_{d\sigma} + h.c.\right)\). Finally, the term
$H_\text{cbath} = \sum_{{\bf k}}\epsilon_{\textbf{k}}
c^\dagger_{{\bf k},\sigma}c_{{\bf k},\sigma} -\frac{W}{2}\sum_{Z} \left(n_{Z\uparrow} - n_{Z\downarrow}\right)^2$ includes the kinetic energy ($\epsilon_{\textbf{k}}=-2t\left(\cos k_x + \cos k_y\right)$) for tight-binding conduction bath electrons ($c^\dagger_{{\bf k},\sigma}$) on a half-filled square lattice, together with local correlations ($W$) that frustrate Kondo screening. The 2D structure of the impurity model and its distinction from the infinite-dimensional counterpart becomes apparent on Fourier transforming the Kondo coupling to ${\bf k}$-space:
$J_{{\bf k}, {\bf k}^\prime} = \frac{J}{2}\left[\cos\left({\bf k}_x - {\bf k}^\prime_x\right) + \cos\left({\bf k}_y - {\bf k}^\prime_y\right)\right]$, with $J>0$. Clearly, $J_{{\bf k}, {\bf k}^\prime}$ possesses $C_{4}$ lattice symmetry. 
\section{Reconstructing the lattice model.}
We now define the {\it tiling} procedure, which recreates the lattice model from the impurity Hamiltonian. For a {\it unit cell} of the tiling,  
we consider \(\mathcal{H}_\text{aux}({\bf r}_d)\) to have the impurity at a reference site \({\bf r}_d\) of our lattice. To create the lattice model, we translate the unit cell across all sites of the lattice:
\begin{equation}\begin{aligned}
	\label{tilingPrescription}
	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}T^\dagger({\bf r})\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r}) - N\mathcal{H}_\text{cbath},
\end{aligned}\end{equation}
where \({\bf r}\) sums over all lattice sites, and $T({\bf r})$ is a many-body translation operator that translates all coordinates by a vector \({\bf r}\). Details of tiling procedure are provided in the Supplemental Information (SI)~\cite{suppmat}. Implementing this for the extended Anderson impurity model (eq.~\ref{impurityModel}) generates a {\it Hubbard-Heisenberg} lattice model in two spatial dimensions:
    \begin{eqnarray}
        &&\mathcal{H}_\text{tiled} = -\frac{\tilde t}{\sqrt\mathcal{Z}}\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\nonumber \\
        &&+ \frac{\tilde J}{\mathcal{Z}}\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2~,
        \end{eqnarray}
with parameters $(\tilde{t},\tilde{\mu},\tilde{J},\tilde{U})$ that are related simply to those in $\mathcal{H}_\text{aux}$~\cite{suppmat}. The eigenstates of $H_{\text{tiled}}$ are dictated by a many-body version of Bloch's theorem~\cite{stoyanova}. Relations between Hamiltonians and eigenstates of the impurity and lattice models are exploited to obtain equal-time correlation functions and entanglement measures of the latter from the former~\cite{suppmat}.
\begin{figure}
    \centering
    \includegraphics[width=0.325\linewidth]{phaseDiagram-77-0.001.pdf}
    \includegraphics[width=0.325\linewidth]{SF.pdf}
    \includegraphics[width=0.325\linewidth]{kspaceDOS-77.pdf}
    \caption{Left: Phase diagram of impurity model at strong coupling in $U$ in terms of competing dimensionless Kondo ($J/t$) and bath correlation ($W/t$) couplings. A pseudogap phase (red, PG) is observed between the local Fermi liquid (pink, LFL) and local moment (black, LM) phases. Center: $k$-space-resolved spin-spin correlation $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$ in the pseudogap phase of the impurity model. Antinodal regions are observed to decouple from Kondo screening of the impurity. Right: Upon tiling, this leads to a 
    $k$-space-resolved antinodal gap in the electronic density of states of the lattice model, corresponding to Luttinger surfaces of zeros.}
    \label{spinCorr}
\end{figure}
%\par\noindent\textit{Pseudogapping{\textcolor{red}``pseudogapping"  DOESN'T SOUND GOOD}} transition from Kondo breakdown.} 
\section{Pseudogap Formation via Kondo Breakdown.}
A detailed picture of Kondo breakdown in the large $U$ phase of $H_\text{aux}$ is obtained from a scaling analysis of the ${\bf k}$-resolved Kondo coupling \(J^{(j)}_{{\bf k}_1, {\bf k}_2}\) using the 
unitary renormalisation group (URG) method \cite{anirbanurg1} (see \cite{suppmat} for details)
\begin{equation}\begin{aligned}\label{KondoRGequation}
	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}~,
\end{aligned}\end{equation}
where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, the sum is over all occupied momentum states \({\bf q}\) 
%in the particle sector (PS {\textcolor{green}{are we using the abbreviation PS anywhere else?}}) 
of the energy shell \(\varepsilon_j\), 
%(i.e., all states occupied at \(T=0\) and in the absence of any quantum fluctuations), 
and  \({\bf \bar q} = {\bf q} + {\boldsymbol \pi}\) is the particle-hole transformed state associated with ${\bf q}$. The bath interaction coupling $W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}$ is found to be marginal under these transformations. While the complexity of the RG equation for $J_{{\bf k}_1, {\bf k}_2}$ (eq.\eqref{KondoRGequation}) is clarified through a detailed numerical evaluation whose results are discussed below, its structure permits the broad conclusion that the frustration of Kondo screening due to charge fluctuations (for attractive bath interactions $W<0$) lead to the Mott metal-insulator transition~\cite{Mukherjee_2023}.

Upon tuning the ratio of the bath and Kondo interactions ($W/J$) from zero to negative values (see phase diagram in Fig.~\ref{spinCorr}(left)), the following phases emerge in the impurity model from the competition between $J$ and $W$ in eq.~\eqref{KondoRGequation}: (i) for $W/J<(W/J)_{\text{PG}}$, an LFL phase (where the entire FS participates in Kondo screening), (ii) for $\frac{W}{J} \in [(\frac{W}{J})_{\text{PG}}, (\frac{W}{J})_c]$, a local PG phase where disconnected parts of the FS around the node participate in Kondo screening, and (iii) a local moment phase for $\frac{W}{J} > (\frac{W}{J})_c$, where the impurity remains unscreened at low-energies. These can be visualised from spin correlations $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$; see Fig.~\ref{spinCorr}(center) for $\chi_s(d,{\bf k})$ in the PG. The values $(W/J)_{\text{PG}}$ and $(W/J)_c$ are therefore the entry into and exit from the PG phase. Mapping on to the lattice model via tiling, we observe that the $T=0$ Mott transition of the 2D Hubbard-Heisenberg model proceeds from FL to Mott insulator through an intervening PG phase having a partially gapped FS (i.e., a vanishing electronic density of states around the antinodal regions, Fig.~\ref{spinCorr}(right)). We now outline the mechanism for the formation of the PG.

\begin{figure}[htpb]
    \centering
    \includegraphics[width=\linewidth]{kondoUnravelling.pdf}
    \caption{Left, Right and Center: Initiation of the decoupling of $J_{{\bf k}, {\bf k'}}$ (positive, negative and zeros shown in red, blue and white respectively), with ${\bf k}$ (black circle) at low-energies for ${\bf k}$ corresponding to the node, antinode and a point mid-way between them on the top right arm of the FS respectively with tuning $W/J$. As dictated by the symmetry of $J_{{\bf k}, {\bf k'}}$, the decoupling for a given ${\bf k}$ proceeds} via the appearance of zeros (white patches) of $J_{{\bf k}, {\bf k'}}$ for ${\bf k'}$ initially on the nodal regions of adjacent arms, and progresses gradually towards the antinodes. The decoupling ends with the onset of the pseudogap.
    \label{rgProgression}
\end{figure}
%\newline 
\section{Unraveling of Kondo screening.} 
As shown in Fig.~\ref{rgProgression}, the anisotropy in the ${\bf k}$-space of Kondo breakdown can be visualized in terms of zeros of $J_{{\bf k}_N, {\bf k}}$, involving spin-flip scattering between the node ${\bf k}_N = (\pi/2, \pi/2)$  and a general wavevector ${\bf k}$. 
For any $W/J$, the $\mathcal{C}_{4}$ lattice symmetry dictates that $J_{{\bf k}_N, {\bf k}}$ vanishes if ${\bf k}$ belongs to any of the antinodes or adjacent nodes. Tuning $W/J$ towards $(W/J)_{\text{PG}}$ leads to an unraveling of the Kondo screening: $J_{{\bf k}_N, {\bf k}}$ for ${\bf k}$ close to the adjacent nodes turns RG-irrelevant first, and a patch of zeros subsequently appears in $J_{{\bf k}_N, {\bf k}}$ around this point (Fig.~\ref{rgProgression} left). Tuning $W/J$ further extends the patch of zeros towards the antinodes (Fig.~\ref{rgProgression} center and right). Kondo screening thus unravels by a systematic decoupling of all $J_{{\bf k}_1, {\bf k}_2}$ that connect adjacent quadrants of the Brillouin zone.   
Precisely at $W/J=(W/J)_{\text{PG}}$, the antinode joins this connected region of zeros in $J_{{\bf k}_1, {\bf k}_2}$, marking the decoupling of the antinodes from all other points in the neighbourhood of the FS. This is an interaction-driven Lifshitz transition of the FS, and marks the entry into a PG phase possessing Fermi arcs~\cite{WuFerrero2018}. Importantly, it coincides with an emergent two-channel Kondo (2CK) impurity model, where each channel corresponds to a pair of Fermi arcs on opposite faces of the conduction bath FS. The 2CK nature of the PG is guaranteed by the symmetry of $J_{{\bf k},{\bf k'}}$ (see Fig.\ref{rgProgression}): 
$J_{{\bf k},{\bf k'}}= -J_{{\bf k}+{\bf Q},{\bf k'}}=-J_{{\bf k},{\bf k'}+{\bf Q}}$, where ${\bf Q} = (\pi,\pi)$. The PG expands by shrinking these disconnected Fermi arcs towards the respective nodes, leading to nodal metals whose disappearance heralds the Mott transition.

\section{{\bf k}-resolved dynamical spectral weight transfer.}
Strong charge fluctuations develop between the nodal and antinodal regions of the FS in the PG regime (Fig.~\ref{chargeCorr} (left)), removing low-energy spectral weight from the antinodes to higher energies and leading to selective gap formation. Accordingly, the PG coincides with the appearance of poles of the lattice model self-energy $\Sigma ({\bf k},\omega=0)$ near the antinodes; these poles approach the nodes on tuning towards the Mott transition (Fig.~\ref{chargeCorr} (right)). This mirrors the coalescing of self-energy poles at zero frequency in the underlying impurity model~\cite{suppmat}. This process corresponds to the formation of Luttinger surfaces of zeros of the single-particle Greens function~\cite{dzyaloshinskii2003some} whose growth characterises the PG, and connection to the Mott insulator.
\begin{figure}
    \centering
    \includegraphics[width=0.49\linewidth]{cfnode.pdf}
    \includegraphics[width=0.49\linewidth]{selfEnergyKspace.pdf}
    \caption{Left: Enhanced charge correlations $\chi_c({\bf k}_1, {\bf k}_2) = \braket{c^\dagger_{{\bf k}_1\uparrow}c^\dagger_{{\bf k}_1\downarrow}c_{{\bf k}_2\downarrow}c_{{\bf k}_2\uparrow} + \text{h.c.}}$ between the nodal and antinodal regions, signalling Kondo breakdown in the pseudogap phase of the impurity model. Right: In turn, the breakdown leads to the gapping of the antinodal regions in the lattice model, seen from the appearance of poles in the imaginary part of the self-energy.}
    \label{chargeCorr}
\end{figure}

\section{Non-FL excitations within the pseudogap.}
In the PG regime, the nature of gapless Fermi arcs changes dramatically. We have already argued that the low-energy dynamics of these gapless Fermi arcs are governed by an underlying two-channel Kondo (2CK) impurity model~\cite{Tsvelick_weigmann_mchannel_1985,emery_kivelson}. This is consistent with the rapid fall of the impurity quasiparticle residue $Z_\text{imp}$ (Fig.~\ref{channelDecoupling} (left)) from finite values in the FL phase to vanishingly small values just before the onset of the PG. Fig.~\ref{channelDecoupling} (left) shows the emergence of increasingly uncompensated local magnetic moments upon traversing the PG phase. The underlying impurity spectral function of the gapless arcs show a pseudogapped behaviour for $\omega\simeq 0$, with a rapid fall in the spectral weight at $\omega=0$ upon traversing the PG. The collapse of the Kondo resonance into a pseudogapped spectral function is another display of the dynamical spectral weight transfer ~\cite{dzyaloshinskii2003some}. Concomitant with this is the emergence of a zero-frequency peak in the imaginary part of the self-energy of the NFL in the PG phase, with $\Sigma''(\omega)\sim \omega^{\alpha}$. Remarkably, we find that the exponent $\alpha=-2$ characterises the NFL for the entire PG phase (see Fig.~\ref{selfEnergy}(Left)), including the critical end-point. This is in stark contrast with the vanishing $\Sigma''(\omega)\sim \omega^{2}$ for the Fermi liquid. The height of the zero-frequency peak rises by almost 4 orders of magnitude from the start of the PG till its end at the Mott transition point (Fig.\ref{selfEnergy}(Right)); the dramatic growth of the peak height very near the Mott critical point coincides with the coalescing of the finite-frequency poles of the self-energy into a single pole at zero-frequency, signalling the singular nodal non-Fermi liquid present at the Mott quantum critical point.

\begin{figure}
    \centering
    \includegraphics[width=0.45\linewidth]{figures/Ad_zoomout_77-1500.pdf}
    \includegraphics[width=0.45\linewidth]{figures/Ad_zoomin_77-1500.pdf}
    \includegraphics[width=0.45\linewidth]{figures/selfEnergy_d_zoomout_77-1500.pdf}
    \includegraphics[width=0.45\linewidth]{figures/selfEnergy_d_zoomin_77-1500.pdf}
    \caption{Top Left: , Top Right: , Bottom Left: , Bottom Right:}
    \label{specfunc}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.52\linewidth]{figures/selfEnergy_d_fit_77-1500.pdf}
    \includegraphics[width=0.4\linewidth]{figures/selfEnergy_d_height_77-1500.pdf}
    \caption{Left: Imaginary part of impurity self-energy for Fermi liquid (FL, $|W/J| < 1.79$) and pseudogapped phases (NFL, $|W/J| \geq 1.79$). The FL self-energy fits to $\Sigma^{\prime\prime} \sim \omega^{\alpha}$ with $\alpha\approx 2$, vanishing as $\omega\to 0$, while the NFL self-energy grows as $\Sigma^{\prime\prime} \approx a - b\omega^{\beta}$ for small $\omega$, with $\beta\approx -2$. Remarkably, the NFL exponent remains mostly unchanged through the entirety of the PG phase. Right:}
    \label{selfEnergy}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.49\linewidth]{QPR_77-1500.pdf}
    \includegraphics[width=0.49\linewidth]{Sdz_49-2000-fixed.pdf}
    \caption{Suppression of quasiparticle residue ($Z_{imp}$) as the impurity model is tuned towards the Mott transition. An initial drastic fall in $Z_{imp}$ is observed for $W/J \lesssim (W/J)_\text{PG}$ from $0.3$ to around $0.05$, signalling the destruction of the FL with unraveling of Kondo screening. A steady decrease in $Z_{imp}$ is observed in passage through the PG, and is vanishingly small close to the Mott transition due to a divergent self-energy. Inset shows the growth of unscreened impurity magnetic moment in the pseudogap phase.
    }
    \label{channelDecoupling}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.49\linewidth]{SF-di_77-700.pdf}
    \includegraphics[width=0.49\linewidth]{I2-di_77-700.pdf}
    \caption{Spin-flip correlation $\braket{S_d^+ S_{r}^- + \text{h.c.}}$ and mutual information $I_{2}(d,r)$ between the impurity spin and conduction bath local spins as a function of the distance {\bf r} between them, normalised against the value for the nearest-neighbour sites. Both decay very quickly in the FL phase (blue), but show long-ranged behaviour in the non-FL phase (yellow, green), extending to the edges of the system at the critical point (green).}
    \label{longranged}
\end{figure}

\section{Non-local nature of the pseudogap non-FL.}
In Fig.~\ref{longranged}, both the mutual information and spin-flip correlations between the impurity spin and conduction bath sites are observed to undergo a crossover within the PG, from a short-ranged behaviour at its onset, to a long-ranged behaviour as the Mott transition approaches~\cite{suppmat}. The entanglement is also observed to be multipartite in nature: in Fig.\ref{qfiplot}, the quantum Fisher information (QFI)~\cite{Hauke2016} computed for the ground state wavefunction using an operator corresponding to the sum of local spin-flip exchange processes shows a jump at the onset of the PG. Further, the Fermi liquid is observed to possess bi-partite entanglement while the NFL of the PG phase displays pentapartite entanglement.
%Similar long-ranged behaviour of spin-flip correlations is also observed \textcolor{blue}{in Fig.~\ref{channelDecoupling}(right)} between the impurity and bath sites~\cite{suppmat}. 
% \textcolor{blue}{
%This is further evidence of the breakdown of local Kondo screening, and the resulting Landau quasiparticle excitations. 
These striking results imply that the Mott transition observed by us lies beyond the local quantum criticality scenario~\cite{Si2001}. Instead,  we observe the PG phase to be a novel state of strongly interacting quantum matter emergent from the breakdown of local Kondo screening. This state is described by a quantum critical Fermi surface with non-FL Fermi arcs that display increasingly critical behaviour, i.e., dynamics described by non-local quantum fluctuations, and excitations that become truly long-ranged close to the transition.

\begin{figure}
    \centering
    \includegraphics[width=0.49\linewidth]{qfi_77-2000.pdf}
    \caption{Evolution of the Quantum Fisher Information $F_Q$ for a nearest-neighbour spin-flip operator $\mathcal{O} = \sum_{i \in \text{odd}}(S_i^+S_{i+1}^- + \text{h.c.})$ through the first Lifshitz transition and the pseudogap. The vertical dashed line marks the onset of the PG. To the left of it, the QFI in the Fermi liquid phase shows at most bipartite entanglement ($F_Q < 2$), while the PG shows the presence of multipartite entanglement upto 5 parties ($F_Q > 4$).}
    \label{qfiplot}
\end{figure}
\section{An exactly solvable singular nodal non-Fermi liquid at Mott criticality.}
%\section{Evolution of the pseudogapped non-FL.} 
Very close to the transition, the excitations of the nodal non-FL correspond to those of a Hatsugai-Kohmoto model~\cite{Baskaran1991,Hatsugai1992}. This insight is obtained from a perturbation-theoretic treatment of the RG fixed point Hamiltonian of the impurity model for $W/J\lesssim (W/J)_{\text{PG}}$, by considering the effects of a small fixed point Kondo scattering probability \(J^*\) in the backdrop of a larger bath interaction parameter \(|W|\). This yields the HK model~\cite{Baskaran1991,Hatsugai1992} as the singular part of the effective Hamiltonian arising from forward scattering processes (details in Appendix~\ref{hkmDerivation}):
\begin{equation}\begin{aligned}\label{HKModel}
	\Delta \tilde H_{{\bf q}_1 = {\bf q}_2} = \sum_{{\bf q},\sigma}\epsilon_{{\bf q}}{n}_{{\bf q},\sigma} + u\sum_{{\bf q}, \sigma}n_{{\bf q} \sigma} n_{{\bf q} \bar\sigma}~,
\end{aligned}\end{equation}
where the number operator \(n_{{\bf q} \sigma} = \phi^\dagger_{{\bf q}, \sigma} \phi_{{\bf q}, \sigma}\) pertains to emergent fermionic relative modes $\phi_{{\bf q}, \sigma}$ that are shifted by an excitation momentum \({\bf q}\) away from the nodal point \({\bf N}_1 = \left(\pi/2, \pi/2\right)\) and its 
partner \({\bf N}_1 + {\bf Q}_1 = \left(-\pi/2, -\pi/2\right)\). The kinetic energy \(\epsilon_{\bf q}\) and interaction energy \(u\sim J^{2}/W\) are dispersion and Kondo scales renormalised by conduction bath correlations~\cite{suppmat}.

Consequently, the resulting non-FL metal of the lattice model involves long-lived excitations of multiple \({\bf k}\)-states, and manifest in the form of a divergent one-particle self-energy at the non-interacting Fermi surface~\cite{Phillips2020}:
	$\Sigma_{{\bf q}}(\omega) = -\frac{u^2/4}{\omega - \epsilon_{\bf q}}$, such that $\Sigma_{\epsilon_{\bf q}=0}(\omega \to 0)  \to \infty$. This zero-frequency self-energy pole 
presages the transition into a Mott insulating phase, where it marks a hard gap in the spectral function for charge excitations. This is consistent with our findings for the lattice (Fig.~\ref{chargeCorr}(Right)) and impurity self-energies~(Fig.\ref{selfEnergy} (Right)). 
For small but non-zero values of \(\omega - \epsilon_{\bf k}\), we obtain a quasiparticle residue that vanishes with $\omega$, \(Z_\text{imp} \sim \omega^2/U^2 \). The scattering rate of this singular NFL possesses a sharp peak at the Fermi surface (\(\omega=\epsilon_{\bf k_{\mathrm{F}}}\)): \(\Gamma \sim U^2\delta(\omega - \epsilon_{\bf k})\), consistent with the sharply peaked Lorentzian $\Sigma''_{{\bf k}}(\omega)\sim \omega^{-2}$ captured in Fig.\ref{selfEnergy}(Left). This quantum critical non-Fermi liquid metal is an example of a strongly coupled scale-invariant form of quantum matter. The exact solution for eq.\eqref{HKModel} reveals the presence of low-energy excitations comprised of holons and doublons~\cite{Hatsugai1992}. These features point to the nodal NFL as a long-ranged and multipartite entangled, strongly interacting scale-invariant state of quantum matter with unparticle-like excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} that are completely disconnected from the quasiparticles of the Fermi liquid. Additionally, we observe that the nodal metal possesses pairing fluctuations~\cite{suppmat} that can become dominant upon doping~\cite{Phillips2020}.

\section{Pseudogap as a strongly coupled phase of quantum matter.}
We now unveil an organising principle that leads to the remarkable properties observed above for the strongly interacting NFL of the PG phase. The existence of a sharp connected FS at $T=0$ can be understood as the existence of a topologically protected manifold of gapless chiral excitations in ${\bf k}$-space at the Fermi surface~\cite{Heath_2020}. The FS is characterised by a topological index corresponding to an anomaly in the quantum many-body theory for electrons, and can be understood as a generalised symmetry of such a system~\cite{lanave2025,McGreevy2023}. A theorem by Luttinger and Ward~\cite{luttinger1960ground} shows that a count of the physical charge (known as Luttinger's volume) is identical to the topological index (a so-called homotopy charge known as Luttinger's count) even in the presence of electronic interactions that do not disturb the FS. We will now argue that the emergence of antinodal Luttinger surfaces involve a disconnection of the Fermi surface (into Fermi arcs) and that, by following La Nave et al.~\cite{lanave2025}, the accompanying change in its topological properties leads to the existence of gapless NFL excitations that are non-local in nature.

The antinodal Luttinger surfaces arise from the splitting of double poles of the single-particle Greens function on the FS into poles lying on opposite complex half-planes, together with zeros that are pinned at the FS. These changes in the analytic structure of the single-particle Greens function have several important consequences. First, the emergent zeros break a $\mathbb{Z}_{2}$ symmetry of the FS~\cite{Anderson2001,Huang2022,lanave2025}. Second, they signal a divergent electronic self-energy as a function of the wavevector ${\bf k}$, render ill-behaved the Luttinger-Ward functional of the interacting electronic problem, and violate the generalised symmetry encoded within it. The changes in the pole structure change the Luttinger count topological invariant, while the zeros give rise to an additional topological contribution (linked to the triangle Adler-Bell-Jackiw anomaly~\cite{adler1969axial,bell1969pcac,Altshuler_1998}). As a consequence of the half-filled particle-hole symmetric nature of the system at hand, Luttinger's volume is preserved upon taking into account topological contributions from both the Luttinger count {\it and} the zeros~\cite{seki2017topological}.

Importantly, 
% the additional anomaly arising from the Luttinger surfaces serves as a disconnection of the Luttinger's count from the physical charge. 
La Nave et al.~\cite{lanave2025} argue, following recent developments in understanding generalised symmetries~\cite{Casini2021Symmetries}, that the additional anomaly arising from the Luttinger surfaces 
% such a disconnection of the physical and topological (Luttinger's count) charges 
guarantees the existence of gapless NFL excitations that are non-local in nature.  
%and disconnection of the homotopy charge associated with the Luttinger count with the physical charge, i.e., the backflow contribution from the zeros at the FS must be taken into account (for the half-filled p-h symmetric system being studied here) to account for how Luttinger's volume is maintained. 
%Further, it has recently been shown (Cite Heath & Bedell, NJP 2020; La Nave et al., arXiv:2506.04342) that the existence of Luttinger surfaces indicates the existence of an anomaly; that the existence of this Adler-Bell-Jackiw triangle anomaly related to the PG FS leads naturally (via recent works of Casini et al., La Nave et al., Altshuler et al., von Neumann, Haag etc.) to the existence of non-local propagating degrees of freedom in the gapless NFL arcs. The appearance of zeros at the FS affects the Atiyah-Singer index associated with the FS (cite Heath and Bedell) that leads to the Luttinger volume. As the ABJ triangle anomaly is captured by Atiyah-Singer index theorem (cite Jackiw et al lectures), the appearance of this anomaly at the FS topology changing Lifshitz transition is linked to changes in topological properties of the FS, and hence invariant under renormalization. 
Thus, the drastic change in nature of the real-space excitations observed by us - from local Landau quasiparticles of the Fermi liquid to the increasingly nonlocal excitations of the NFL Fermi arcs in the PG phase - appears to be dictated by a topological principle and, therefore, robust under renormalisation. This signals the NFL Fermi arcs of the PG as an emergent phase of strongly interacting quantum matter that is the parent metal of the Mott insulator. The same topological principle connects the nonlocal unparticle-like gapless excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} of the scale-invariant nodal NFL observed precisely at the Mott critical point to those of the rest of PG phase, e.g., a universal power-law scaling of $\Sigma''_{{\bf k}}(\omega)\sim \omega^{-2}$ of the NFL throughout the PG phase (Fig.~\ref{selfEnergy} (Left)).

\section{Conclusions.} We find compelling evidence that the Mott transition in the 2D extended Hubbard model involves continuous passage through a PG phase whose gapless Fermi arcs host a long-ranged multipartite entangled non-FL metal. This non-FL turns increasingly singular with the onset of criticality into a Mott insulator. The evolution of this PG phase with doping 
deserves further attention.

\section{Acknowledgments.}
AM thanks IISER Kolkata for funding through a JRF and SRF. S Lal thanks the SERB, Govt. of India for funding through MATRICS Grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
\bibliography{tilingProject}% Produces the bibliography via BibTeX.

\appendix

\section{Appendixes}
\paragraph*{Luttinger's theorem in the presence of Luttinger surfaces.} One can also ask whether Luttinger's theorem is satisfied in our model in the presence of Luttinger surfaces. It has been shown that particle-hole symmetric systems always satisfy a generalised Luttinger's theorem~\cite{seki2017topological}, where the Fermi volume $V_L$ is represented as the difference in the number of poles and zeros, of the single-particle Greens function, that are enclosed by the FSface~\cite{seki2017topological}. This holds true even in the presence of a divergent self-energy~\cite{Phillips2013}. Since our model is always at half-filling, Luttinger's theorem is always satisfied.

The way it works out (despite the presence of Luttinger surfaces) is as follows. We need only show that the number of occupied states below the chemical potential remains unchanged across the first Lifshitz transition. Before the transition, the presence of gapless excitations ensures that the FSface is singly-occupied on average. Inside the pseudogap, the gapless $k-$states continue to contribute one pole on average to the Luttinger count, while the gapping out of certain $k-$states leads to a rearrangement of their spectrum: doubly-occupied states on the Luttinger surfaces become more favourable compared to the singly-occupied states (due to the attractive $W$-interaction). Owing to particle-hole symmetry, these states are degenerate with the zero occupancy states, so that on average, a single state is again occupied. This ensures that the number of occupied states (and hence the number of occupied poles) remains unchanged across the transition. The same argument works for the Mott insulator, where the entire FSface gets replaced by a Luttinger surface.

\paragraph*{Tiling towards a Hubbard-Heisenberg model with an embedded extended SIAM}
We give more details here regarding the construction of the lattice model from the impurity model. As mentioned in the manuscript, the lattice-embedded impurity model is of the form $H({\bf r}_d) = H_\text{imp} + H_\text{cbath} + H_\text{imp-cbath}$, where $H_\text{imp}$ is the impurity part:
\begin{equation}\begin{aligned}\label{onsiteHamiltonian}
	H_\text{imp} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 - \eta\sum_\sigma \hat n_{{\bf r}_d\sigma}~,
\end{aligned}\end{equation}
\(\mathcal{H}_\text{cbath}\) is the conduction bath part:
\begin{equation}\begin{aligned}\label{bathHamiltonian}
	{H}_\text{cbath} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \\
    \frac{1}{2 \mathcal{Z}}W\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
\end{aligned}\end{equation}
and ${H}_\text{imp-cbath}$ is the impurity-bath hybridisation:
\begin{equation}\begin{aligned}\label{interactionHamiltonian}
	{H}_\text{imp-cbath} = \frac{J}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}\sum_{{\bf z}\in\text{NN}({\bf r}_d)} {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \\
    - \frac{V}{\sqrt{\mathcal{Z}}}\sum_{\sigma} \sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)~.
\end{aligned}\end{equation}
In this model, ${\bf r}_d$ is the position of the impurity site, and \(\left<{\bf r}_i, {\bf r}_j\right>\neq {\bf r}_d\) indicates that the sum is over all nearest-neighbour pairs of sites avoiding the impurity site \({\bf r}_d\). \(\boldsymbol \tau = \left( \tau_x, \tau_y, \tau_z \right) \) is the vector of Pauli matrices. \(\sigma\) and \(\sigma^\prime\) can be \(\pm 1\) and represent up and down configurations.

The tiled Hamiltonian can be obtained as 
\begin{equation}\begin{aligned}
	\mathcal{H}_\text{tiled} = \mathcal{T}[H({\bf r}_d)]
    % \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)H({\bf r}_d)T({\bf r} - {\bf r}_d)~,
\end{aligned}\end{equation}
where the $\mathcal{T}[H] = \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)HT({\bf r} - {\bf r}_d)$ represents the symmetrisation/tiling procedure, and the action of the many-body translation operators $T^\dagger({\bf a})$ on a general operator are defined as
\begin{equation}\begin{aligned}
T^\dagger({\bf a}) \mathcal{O}\left({\bf r}_1, {\bf r}_2,\ldots\right)T({\bf a}) = \mathcal{O}\left({\bf r}_1 + {\bf a}, {\bf r}_2 + {\bf a},\ldots\right)~.
\end{aligned}\end{equation}

We consider the effect of the translation operations on each part of the Hamiltonian:
\begin{equation}\begin{aligned}
	&\mathcal{T}\left[{H}_\text{cbath}({\bf r}_d, {\bf z})\right] = -\frac{(N-2)t}{\sqrt\mathcal{Z}}\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) \\
    &- \frac{1}{2}W\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}~,\\
	&\mathcal{T}\left[{H}_\text{imp}\right] = -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}~,\\
    &\mathcal{T}\left[{H}_\text{imp-cbath}\right]\\
     &=\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]~.
\end{aligned}\end{equation}
We have defined \({\bf S}_{{\bf r}_j} =\sum_{\sigma,\sigma^\prime} {\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime}\) as the local spin operator. While constructing the tiled Hamiltonian, we have added extra copies of the non-interacting Hamiltonian \(\mathcal{H}_\text{cbath-nint} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\) for the conduction bath (this results in the factors of \(N-2\) and \(N-1\) in front of the first and third terms).

Upon removing these repeated terms, the result of the tiling operations is a Hubbard-Heisenberg model, of the form
\begin{equation}\begin{aligned}
	\mathcal{H}_\text{HH} &= -\frac{1}{\sqrt\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma} \\
    &+ \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
\end{aligned}\end{equation}
where the tilde symbol indicates that the parameters are for the lattice model (and not the auxiliary model). By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to each other:
\begin{equation}\begin{aligned}\label{couplingsMappings}
	\tilde t = t+2V,~~ \tilde U = U + W, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
\end{aligned}\end{equation}
In summary, the appropriate method for reconstructing the lattice model Hamiltonian is therefore
\begin{equation}\begin{aligned}\label{tilingPrescriptionFinal}
	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}~,
\end{aligned}\end{equation}
where we replaced \(N-3\) with \(N\) assuming a large number of sites. Using this, the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.

\section{Emergence of a Hatsugai-Kohmoto model at the quantum critical point}\label{hkmDerivation}

\end{document}

### 2025-12-10 submissions/Earlier Versions of Manuscript/manuscript2.tex
started creating referee response

--- 2025-12-10 submissions/Earlier Versions of Manuscript/manuscript.tex
@@
-% \documentclass[%
-%  reprint,
-% superscriptaddress,
-% groupedaddress,
+\documentclass[%
+ reprint,
+superscriptaddress,
+groupedaddress,
 %unsortedaddress,
@@
 %bibnotes,
-% amsmath,amssymb,
-% aps,
-% prl,superscriptaddress
+ amsmath,amssymb,
+ aps,
+prl,superscriptaddress
 %prb,
@@
 %floatfix,
-% pdflatex,
-% sn-nature,
-% ]{sn-jnl}
-\documentclass[pdflatex,sn-mathphys-num]{sn-jnl}
+]{revtex4-2}
 
-\usepackage{amsmath,amssymb}
 \usepackage{graphicx}% Include figure files
@@
 \usepackage{color}
-
 \graphicspath{{./figures/}}
+\bibliographystyle{apsrev4-2}
 
@@
 
-\title{Pseudogap Mott criticality via a long-range multipartite entangled strongly coupled non-Fermi liquid}
+%\title{Long range entangled Fermi arcs at a Pseudogapped Mott transition}
 
-%\title{Pseudogap and Mott criticality: Stretching Kondo Screening to Breaking Point}
+\title{Pseudogap and Mott criticality: Stretching Kondo Screening to Breaking Point}
 
@@
 
-\author[1]{Abhirup Mukherjee}
-\affil[1]{
+\author{Abhirup Mukherjee}
+\affiliation{%
  Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
 }
-\author[2]{S. R. Hassan}
-\affil[2]{The Institute of Mathematical Sciences, C.I.T. Campus, Chennai 600 113, India}
-\author[3]{Anamitra Mukherjee}
-\affil[3]{School of Physical Sciences, National Institute of Science, Education and Research, HBNI, Jatni 752050, India}
-\author[4]{N. S. Vidhyadhiraja}
-\affil[4]{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
-\author[5]{A. Taraphder}
-\affil[5]{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
+\author{S. R. Hassan}
+\affiliation{The Institute of Mathematical Sciences, C.I.T. Campus, Chennai 600 113, India}
+\author{Anamitra Mukherjee}
+\affiliation{School of Physical Sciences, National Institute of Science, Education and Research, HBNI, Jatni 752050, India}
+\author{N. S. Vidhyadhiraja}
+\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
+\author{A. Taraphder}
+\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
 %
-\author*[1]{Siddhartha Lal}
+\author{Siddhartha Lal}
+\affiliation{%
+ Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
+}
 
 \date{\today}
-\abstract{
-We propose a new theoretical framework for strongly correlated electron systems 
-%We present an auxiliary model approach 
-that illustrates the centrality of the pseudogap phenomenon in the Mott transition of the extended Hubbard model on a half-filled square lattice.
-Our approach is based on %Vacancy--Kondo--Heisenberg (VKH) model and a Quantum Tiling Reconstruction (QTR) scheme.
-%a real-space Kondo-defect unit ---comprising a localized 
-a spin-1/2 defect at a lattice vacancy that is Kondo exchange-coupled to neighbouring lattice sites, and which is tiled across a square lattice to yield a translationally invariant model.
-The pseudogap is emergent from a Fermi liquid via the systematic unravelling of Kondo screening frustrated by charge fluctuations in the conduction bath of the underlying lattice-embedded Kondo model.
-We demonstrate that the pseudogap is a strongly interacting phase of quantum matter intimately tied to the existence of a critical Fermi surface, with non-Fermi excitations that have long-ranged and multipartite entanglement.
-The Mott criticality of the non-Fermi liquid is signalled by the emergence of a singular self-energy at the Fermi energy.
-Our analysis points to this novel phase of gapless quantum matter being stabilised by changes in the topological properties of the Fermi surface that arise from encroaching surfaces of zeros of the single-particle Greens function.
-%passage from a Fermi liquid to a Mott insulator involves two stages: the first involves a systematic unravelling of Kondo screening, frustrated by charge fluctuations in the conduction bath of the underlying lattice-embedded quantum impurity model.
-%This destabilises the Fermi liquid, culminating in the disconnection of the Fermi surface with the appearance of gaps at the antinodes.
+\begin{abstract}
+We present an auxiliary model approach that illustrates the centrality of the pseudogap phenomenon in the Mott transition of the Hubbard-Heisenberg model on a half-filled square lattice.
+The passage from a Fermi liquid to a Mott insulator involves two stages: the first involves a systematic unravelling of Kondo screening, frustrated by charge fluctuations in the conduction bath of the underlying lattice-embedded quantum impurity model.
+This destabilises the Fermi liquid, culminating in the disconnection of the Fermi surface with the appearance of gaps at the antinodes.
 In the second stage, an emergent pseudogap phase arises from an effective two-channel Kondo problem in the underlying impurity model.
@@
 Upon approaching the Mott transition, the nature of this exotic metal evolves with shrinking of the Fermi arcs towards a singular nodal non-Fermi liquid.
-This accompanies the onset of long-range multipartite entanglement and spin-flip correlations in real-space, revealing the Mott transition on the square lattice to be beyond the paradigm of local quantum criticality.
-}
+This accompanies the onset of long-range real-space entanglement and spin-flip correlations, revealing the Mott transition on the square lattice to be beyond the paradigm of local quantum criticality.
+\end{abstract}
 
@@
 
-\section{Introduction.}
+\par\noindent\textit{Introduction.}
 The origin of the pseudogap and strange metal phases of the cuprates continues to be hotly debated in the context of high-temperature superconductivity~\cite{keimer2015quantum}.
@@
 
-Viewed as a quantum mechanical phenomenon, the PG involves the emergence of disconnected gapped regions of the Fermi surface (known as Luttinger surfaces of zeros of the single-particle Greens function ~\cite{dzyaloshinskii2003some,phillips2006mottness}) from a Fermi liquid with a connected Fermi surface.
+\textcolor{blue}{Viewed as a quantum mechanical phenomenon, the PG involves the emergence of disconnected gapped regions of the Fermi surface (known as Luttinger surfaces of zeros of the single-particle Greens function (CITE references)) from a Fermi liquid with a connected Fermi surface.
 The growth and eventual connection of these Luttinger surfaces then leads to the transition into the Mott insulator.
@@
 If not, what kind of scale-invariant quantum matter do they characterise?
-Which features of the PG elucidate the breakdown of screening in the Fermi liquid and lead instead to a singular self-energy in the Mott insulator?
+Which features of the PG elucidate the breakdown of screening in the Fermi liquid and lead instead to a singular self-energy in the Mott insulator?}
 
@@
 Subsequently, a lattice model is  constructed by applying many-body lattice translation operators~\cite{stoyanova} on the impurity model (henceforth referred as \textit{tiling}), obtaining thereby various quantities of the former from the latter.
-Translation invariance is thus restored differently within our approach from the dynamical mean-field approximation~\cite{georges1996} and its cluster variants~\cite{Hettler2000DCA, Kotliar2001Cellular, Maier2005, Sakai2023}.
+Translation invariance is thus restored differently within our approach from the dynamical mean-field approximation~\cite{georges1996} and its cluster variants~\cite{Hettler2000DCA,Kotliar2001Cellular,Maier2005,Sakai2023}.
 
@@
 Passage through the PG involves dynamical transfer of spectral weight between gapped anti-nodal Luttinger surfaces (zeros of the single-particle Green's function) and gapless nodal arcs with non-FL excitations.
-We also observe the concomitant onset of long-range real-space entanglement and spin-flip correlations close to the Mott transition, rendering it beyond local quantum criticality~\cite{Si2001}.
-Our findings serve as a demonstration of the PG as a strongly interacting long-range multipartite entangled phase of quantum matter linked to the Mott criticality of the 2D extended Hubbard model~\cite{Phillips2013Unparticles}.
-This follows a recent proposal~\cite{lanave2025} that the emergence of Luttinger surfaces lead to the spontaneous violation of a $\mathbb{Z}_{2}$ symmetry associated with the Fermi surface~\cite{Anderson2001,Huang2022}, and thence to the existence of non-local propagating degrees of freedom.
+We also observe the \textcolor{blue}{concomitant} onset of long-range real-space entanglement and spin-flip correlations close to the Mott transition, rendering it beyond local quantum criticality~\cite{Si2001}.
+\textcolor{blue}{Our findings serve as a demonstration of a recent proposal (CITE La Nave etal.
+arXiv:2506.04342) that disconnected Luttinger surfaces leads to the spontaneous violation of a $\mathbb{Z}_{2}$ symmetry associated with the Fermi surface (CITE HALDANE-ANDERSON, Recent work by Philips etal), and thence to the existence of non-local propagating degrees of freedom.}
 
-\textcolor{red}{ AM: Some comments expanding on for identifying a underlying principle: The encroaching of the Fermi surface by the creeping Luttinger surface increases with electronic interaction between the bath electrons (W), which frustrates the Kondo screening and is controlled by (W/J).
-This phenomenon leads to a transition to a non-Fermi liquid state, where the quasiparticle excitations lose coherence and are characterized by disconnected Fermi surfaces and a pseudo-gapped density of states.
-The eventual demise of the Fermi surface and its replacement by a connected Luttinger surface finally leads to the Mott phase.
-}
-
-\textcolor{red}{We demonstrate that a nodal non-Fermi liquid (at the verge of the Mott transition, when the Fermi surface has shrunk to a point) is described by the exactly solvable Hatsugai-Kohmoto (HK) model.
-The (HK) model exhibits a specific type of symmetry breaking, which is crucial for stabilizing non-Fermi liquids and Mott physics.
-This involves breaking a local-in-momentum space $Z_2$ symmetry, which serves as an organizing principle for the Mott transition.
-This $Z_2$ symmetry [Ansderon, Haldane,  Phillips] is local-in-momentum space and non-local in real space (exhibiting long-range multi-partite entanglement (it would be nice if we could demonstrate this) ).
-When this symmetry is disrupted, the symmetry between particle addition and removal around the chemical potential is also lost.
-The resulting non-Fermi liquid is characterized by a self-energy scaling as $\omega^{-2}$ with energy in the HK model.
-We show that the same self-energy characterizes the entire pseudo-gapped regime of the extended Hubbard-Heisenberg model.
-We also demonstrate the $Z_2$ breaking for the URG-derived Hamiltonian in the pseudo-gapped phase, concretely linking the origin of the non-Fermi liquid behavior to the loss of particle-hole symmetry.
-Our result reveals a new adiabatic continuity connecting the Mott insulator phase (described by the HK model by the emergence of a fully connected Luttinger surface) to a family of pseudo-gapped non-Fermi liquid states, in analogy to adiabatic continuity of the noninteracting fermions to the Fermi liquid phase.}
-
-\section{A lattice-embedded impurity model.}
+\par\noindent\textit{A lattice-embedded impurity model.}
 Building on the insight, that the Kondo breakdown in a simple extension of the Anderson impurity model~\cite{Mukherjee_2023} captures the physics of Mott transition in infinite dimensions~\cite{georges1996}), we study a similar Anderson impurity model embedded within a square lattice
@@
 Clearly, $J_{{\bf k}, {\bf k}^\prime}$ possesses $C_{4}$ lattice symmetry.
-\section{Reconstructing the lattice model.}
+\par\noindent\textit{Reconstructing the lattice model.}
 We now define the {\it tiling} procedure, which recreates the lattice model from the impurity Hamiltonian. For a {\it unit cell} of the tiling,  
@@
     \centering
-    \includegraphics[width=0.325\linewidth]{phaseDiagram-77-0.001.pdf}
-    \includegraphics[width=0.325\linewidth]{SF.pdf}
-    \includegraphics[width=0.325\linewidth]{kspaceDOS-77.pdf}
+    \includegraphics[width=0.31\linewidth, height=2.45cm]{phaseDiagram.pdf}
+    \includegraphics[width=0.67\linewidth]{SF-DOS.pdf}
     \caption{Left: Phase diagram of impurity model at strong coupling in $U$ in terms of competing dimensionless Kondo ($J/t$) and bath correlation ($W/t$) couplings.
@@
 %\par\noindent\textit{Pseudogapping{\textcolor{red}``pseudogapping"  DOESN'T SOUND GOOD}} transition from Kondo breakdown.}
-\section{Pseudogap Formation via Kondo Breakdown.}
+
+\par\noindent\textit{Pseudogap Formation via Kondo Breakdown.}
 A detailed picture of Kondo breakdown in the large $U$ phase of $H_\text{aux}$ is obtained from a scaling analysis of the ${\bf k}$-resolved Kondo coupling \(J^{(j)}_{{\bf k}_1, {\bf k}_2}\) using the
@@
 
-Upon tuning the ratio of the bath and Kondo interactions ($W/J$) from zero to negative values (see phase diagram in Fig.~\ref{spinCorr}(left)), the following phases emerge in the impurity model from the competition between $J$ and $W$ in eq.~\eqref{KondoRGequation}: (i) for $W/J<(W/J)_{\text{PG}}$, an LFL phase (where the entire FS participates in Kondo screening), (ii) for $\frac{W}{J} \in [(\frac{W}{J})_{\text{PG}}, (\frac{W}{J})_c]$, a local PG phase where disconnected parts of the FS around the node participate in Kondo screening, and (iii) a local moment phase for $\frac{W}{J} > (\frac{W}{J})_c$, where the impurity remains unscreened at low-energies.
-These can be visualised from spin correlations $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$; see Fig.~\ref{spinCorr}(center) for $\chi_s(d,{\bf k})$ in the PG.
+Upon tuning the ratio of the bath and Kondo interactions ($W/J$) from zero to negative values (see phase diagram in Fig.\ref{spinCorr}(left)), the following phases emerge in the impurity model from the competition between $J$ and $W$ in eq.~\eqref{KondoRGequation}: (i) for $W/J<(W/J)_{\text{PG}}$, an LFL phase (where the entire FS participates in Kondo screening), (ii) for $\frac{W}{J} \in [(\frac{W}{J})_{\text{PG}}, (\frac{W}{J})_c]$, a local PG phase where disconnected parts of the FS around the node participate in Kondo screening, and (iii) a local moment phase for $\frac{W}{J} > (\frac{W}{J})_c$, where the impurity remains unscreened at low-energies.
+These can be visualised from spin correlations $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$; see Fig.\ref{spinCorr}(center) for $\chi_s(d,{\bf k})$ in the PG.
 The values $(W/J)_{\text{PG}}$ and $(W/J)_c$ are therefore the entry into and exit from the PG phase.
-Mapping on to the lattice model via tiling, we observe that the $T=0$ Mott transition of the 2D Hubbard-Heisenberg model proceeds from FL to Mott insulator through an intervening PG phase having a partially gapped FS (i.e., a vanishing electronic density of states around the antinodal regions, Fig.~\ref{spinCorr}(right)).
+Mapping on to the lattice model via tiling, we observe that the $T=0$ Mott transition of the 2D Hubbard-Heisenberg model proceeds from FL to Mott insulator through an intervening PG phase having a partially gapped FS (i.e., a vanishing electronic density of states around the antinodal regions, Fig.\ref{spinCorr}(right)).
 We now outline the mechanism for the formation of the PG.
@@
     \centering
-    \includegraphics[width=\linewidth]{kondoUnravelling.pdf}
-    \caption{Left, Right and Center: Initiation of the decoupling of $J_{{\bf k}, {\bf k'}}$ (positive, negative and zeros shown in red, blue and white respectively), with ${\bf k}$ (black circle) at low-energies for ${\bf k}$ corresponding to the node, antinode and a point mid-way between them on the top right arm of the FS respectively with tuning $W/J$.
-As dictated by the symmetry of $J_{{\bf k}, {\bf k'}}$, the decoupling for a given ${\bf k}$ proceeds} via the appearance of zeros (white patches) of $J_{{\bf k}, {\bf k'}}$ for ${\bf k'}$ initially on the nodal regions of adjacent arms, and progresses gradually towards the antinodes.
-The decoupling ends with the onset of the pseudogap.
+    \includegraphics[width=\linewidth]{zerosFlow.pdf}
+    \caption{Left, Right and Center: Decoupling of $J_{{\bf k}, {\bf k'}}$ (positive, negative and zeros shown in yellow, purple and green respectively), with ${\bf k}$ (grey circle) corresponding to the node, antinode and a point mid-way between them on the top right arm of the FS respectively.
+This is seen via the appearance of zeros (green patches) of $J_{{\bf k}, {\bf k'}}$ for ${\bf k'}$ initially on the nodal regions of adjacent arms, and their subsequent progression towards the antinodes.
+The decoupling
+    ends with the onset of the pseudogap.
+    }
     \label{rgProgression}
@@
 %\newline 
-\section{Unraveling of Kondo screening.} 
-As shown in Fig.~\ref{rgProgression}, the anisotropy in the ${\bf k}$-space of Kondo breakdown can be visualized in terms of zeros of $J_{{\bf k}_N, {\bf k}}$, involving spin-flip scattering between the node ${\bf k}_N = (\pi/2, \pi/2)$  and a general wavevector ${\bf k}$.
+\par\noindent\textit{Unraveling of Kondo screening.} 
+As shown in Fig.\ref{rgProgression}, the anisotropy in the ${\bf k}$-space of Kondo breakdown can be visualized in terms of zeros of $J_{{\bf k}_N, {\bf k}}$, involving spin-flip scattering between the node ${\bf k}_N = (\pi/2, \pi/2)$  and a general wavevector ${\bf k}$.
 For any $W/J$, the $\mathcal{C}_{4}$ lattice symmetry dictates that $J_{{\bf k}_N, {\bf k}}$ vanishes if ${\bf k}$ belongs to any of the antinodes or adjacent nodes.
-Tuning $W/J$ towards $(W/J)_{\text{PG}}$ leads to an unraveling of the Kondo screening: $J_{{\bf k}_N, {\bf k}}$ for ${\bf k}$ close to the adjacent nodes turns RG-irrelevant first, and a patch of zeros subsequently appears in $J_{{\bf k}_N, {\bf k}}$ around this point (Fig.~\ref{rgProgression} left).
-Tuning $W/J$ further extends the patch of zeros towards the antinodes (Fig.~\ref{rgProgression} center and right).
+Tuning $W/J$ towards $(W/J)_{\text{PG}}$ leads to an unraveling of the Kondo screening: $J_{{\bf k}_N, {\bf k}}$ for ${\bf k}$ close to the adjacent nodes turns RG-irrelevant first, and a patch of zeros subsequently appears in $J_{{\bf k}_N, {\bf k}}$ around this point (Fig.\ref{rgProgression}(left)).
+Tuning $W/J$ further extends the patch of zeros towards the antinodes (Fig.\ref{rgProgression}(center) and (right)).
 Kondo screening thus unravels by a systematic decoupling of all $J_{{\bf k}_1, {\bf k}_2}$ that connect adjacent quadrants of the Brillouin zone.
+%{{\textcolor{cyan}{Tuning $W/J$ further extends the patch of zeros in $J_{{\bf k}_1, {\bf k}_2}$ for ${\bf k}_{1}$ lying between a given node and the nearest antinodes (Fig.\ref{rgProgression}(center) and (right)), visualising a systematic decoupling of $J_{{\bf k}_1, {\bf k}_2}$ connecting adjacent quadrants of the Brillouin zone quadrants -- (CHECK THIS SENTENCE, TOO LONG AND SOMEWHAT UNCLEAR)}}.
+
 Precisely at $W/J=(W/J)_{\text{PG}}$, the antinode joins this connected region of zeros in $J_{{\bf k}_1, {\bf k}_2}$, marking the decoupling of the antinodes from all other points in the neighbourhood of the FS.
@@
 Importantly, it coincides with an emergent two-channel Kondo (2CK) impurity model, where each channel corresponds to a pair of Fermi arcs on opposite faces of the conduction bath FS.
-The 2CK nature of the PG is guaranteed by the symmetry of $J_{{\bf k},{\bf k'}}$ (see Fig.\ref{rgProgression}):
+The 2CK nature of the PG is guaranteed by the symmetry:
 $J_{{\bf k},{\bf k'}}= -J_{{\bf k}+{\bf Q},{\bf k'}}=-J_{{\bf k},{\bf k'}+{\bf Q}}$, where ${\bf Q} = (\pi,\pi)$.
@@
 
-\section{{\bf k}-resolved dynamical spectral weight transfer.}
-Strong charge fluctuations develop between the nodal and antinodal regions of the FS in the PG regime (Fig.~\ref{chargeCorr} (left)), removing low-energy spectral weight from the antinodes to higher energies and leading to selective gap formation.
-Accordingly, the PG coincides with the appearance of poles of the lattice model self-energy $\Sigma ({\bf k},\omega=0)$ near the antinodes; these poles approach the nodes on tuning towards the Mott transition (Fig.~\ref{chargeCorr} (right)).
+\par\noindent\textit{{\bf k}-resolved dynamical spectral weight transfer.}
+ Strong charge fluctuations develop between the nodal and antinodal regions of the FS in the PG regime (Fig.\ref{chargeCorr}(left)), removing low-energy spectral weight from the antinodes to higher energies and leading to selective gap formation.
+Accordingly, the PG coincides with the appearance of poles of the lattice model self-energy $\Sigma ({\bf k},\omega=0)$ near the antinodes; these poles approach the nodes on tuning towards the Mott transition (Fig.\ref{chargeCorr}(right)).
 This mirrors the coalescing of self-energy poles at zero frequency in the underlying impurity model~\cite{suppmat}.
-This process corresponds to the formation of Luttinger surfaces of zeros of the single-particle Greens function~\cite{dzyaloshinskii2003some} whose growth characterises the PG, and connection to the Mott insulator.
+\textcolor{blue}{This process corresponds to the formation of Luttinger surfaces of zeros of the single-particle Greens function (CITE Dzyaloshinskii PRB  68, 085113 (2003)) whose growth characterises the PG, and connection to the Mott insulator.}
 \begin{figure}
     \centering
-    \includegraphics[width=0.49\linewidth]{cfnode.pdf}
-    \includegraphics[width=0.49\linewidth]{selfEnergyKspace.pdf}
-    \caption{Left: Enhanced charge correlations $\chi_c({\bf k}_1, {\bf k}_2) = \braket{c^\dagger_{{\bf k}_1\uparrow}c^\dagger_{{\bf k}_1\downarrow}c_{{\bf k}_2\downarrow}c_{{\bf k}_2\uparrow} + \text{h.c.}}$ between the nodal and antinodal regions, signalling Kondo breakdown in the pseudogap phase of the impurity model.
+    \includegraphics[width=0.49\linewidth]{cfnode-2.pdf}
+    \includegraphics[width=0.49\linewidth]{selfEnergyKspace-3.pdf}
+    \caption{Left: Enhanced charge isospin correlations $\chi_c({\bf k}_1, {\bf k}_2) = \braket{c^\dagger_{{\bf k}_1\uparrow}c^\dagger_{{\bf k}_1\downarrow}c_{{\bf k}_2\downarrow}c_{{\bf k}_2\uparrow} + \text{h.c.}}$ between the nodal and antinodal regions, signalling Kondo breakdown in the pseudogap phase of the impurity model.
 Right: In turn, the breakdown leads to the gapping of the antinodal regions in the lattice model, seen from the appearance of poles in the imaginary part of the self-energy.}
@@
 
-\section{Non-FL excitations within the pseudogap.}
-In the PG regime, the nature of gapless Fermi arcs changes dramatically.
+\par\noindent\textit{Non-FL excitations within the pseudogap.}
+In the PG regime, 
+%$|W/J|_{\text{PG}} < |W/J| < |W/J|_{c}$, 
+the nature of gapless Fermi arcs changes dramatically.
 We have already argued that the low-energy dynamics of these gapless Fermi arcs are governed by an underlying two-channel Kondo (2CK) impurity model~\cite{Tsvelick_weigmann_mchannel_1985,emery_kivelson}.
-This is consistent with the rapid fall of the impurity quasiparticle residue $Z_\text{imp}$ (Fig.~\ref{channelDecoupling} (left)) from finite values in the FL phase to vanishingly small values just before the onset of the PG.
-Fig.~\ref{channelDecoupling} (left) shows the emergence of increasingly uncompensated local magnetic moments upon traversing the PG phase.
-The underlying impurity spectral function of the gapless arcs show a pseudogapped behaviour for $\omega\simeq 0$, with a rapid fall in the spectral weight at $\omega=0$ upon traversing the PG.
-The collapse of the Kondo resonance into a pseudogapped spectral function is another display of the dynamical spectral weight transfer ~\cite{dzyaloshinskii2003some}.
+\textcolor{red}{The excitations of the 2CK exhibit a separation of spin, charge and channel quantum numbers~\cite{affleck1992}, with gapless excitations carrying only the spin quantum number.
+Previous works show that the impurity self-energy of such a two-channel Kondo model displays marginal Fermi liquid (MFL) behaviour~\cite{Coleman_tsvelik,Schofield1997,Patra2023MCK} with real and imaginary parts of the self-energy as $\Sigma^{\prime} \sim \omega\ln\omega, \Sigma^{\prime\prime}\sim-\omega$.
+This gives rise~\cite{varma2002singular} to a linear scattering rate \(\Gamma \sim \omega\), and a logarithmically vanishing quasiparticle residue $Z_\text{imp}(\omega) \sim (c - \ln \omega)^{-1}$ (where \(c\) is a constant).}
+This is consistent with the rapid fall of the impurity quasiparticle residue $Z_\text{imp}$ (Fig.\ref{channelDecoupling}(left)) from finite values in the FL phase to vanishingly small values in the PG.
+The inset of Fig.\ref{channelDecoupling}(left) shows the emergence of increasingly uncompensated local magnetic moments upon traversing the PG phase.
+\textcolor{blue}{The underlying impurity spectral function of the gapless arcs show a pseudogapped behaviour for $\omega\simeq 0$, with a rapid fall in the spectral weight at $\omega=0$ upon traversing the PG.
+The collapse of the Kondo resonance into a pseudogapped spectral function is another display of the dynamical spectral weight transfer (CITE Dzyaloshinskii PRB  68, 085113 (2003)).
 Concomitant with this is the emergence of a zero-frequency peak in the imaginary part of the self-energy of the NFL in the PG phase, with $\Sigma''(\omega)\sim \omega^{\alpha}$.
-Remarkably, we find that the exponent $\alpha=-2$ characterises the NFL for the entire PG phase (see Fig.~\ref{selfEnergy}(Left)), including the critical end-point.
-This is in stark contrast with the vanishing $\Sigma''(\omega)\sim \omega^{2}$ for the Fermi liquid.
-The height of the zero-frequency peak rises by almost 4 orders of magnitude from the start of the PG till its end at the Mott transition point (Fig.\ref{selfEnergy}(Right)); the dramatic growth of the peak height very near the Mott critical point coincides with the coalescing of the finite-frequency poles of the self-energy into a single pole at zero-frequency, signalling the singular nodal non-Fermi liquid present at the Mott quantum critical point.
+Remarkably, we find that the exponent $\alpha=-2$ characterises the NFL for the entire PG phase (CITE FIGURE); this is in stark contrast with the vanishing $\Sigma''(\omega)\sim \omega^{2}$ for the Fermi liquid).
+The height of the zero-frequency peak rises by almost 4 orders of magnitude from the start of the PG till its end at the Mott transition point (CITE FIGURE INSET?); this dramatic growth of the peak height coincides with the coalescing of the finite-frequency poles of the self-energy into a single pole at zero-frequency, signalling the singular nodal non-Fermi liquid present at the Mott quantum critical point.}
 
@@
     \centering
-    \includegraphics[width=0.45\linewidth]{figures/Ad_zoomout_77-1500.pdf}
-    \includegraphics[width=0.45\linewidth]{figures/Ad_zoomin_77-1500.pdf}
-    \includegraphics[width=0.45\linewidth]{figures/selfEnergy_d_zoomout_77-1500.pdf}
-    \includegraphics[width=0.45\linewidth]{figures/selfEnergy_d_zoomin_77-1500.pdf}
-    \caption{Top Left: , Top Right: , Bottom Left: , Bottom Right:}
-    \label{specfunc}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.52\linewidth]{figures/selfEnergy_d_fit_77-1500.pdf}
-    \includegraphics[width=0.4\linewidth]{figures/selfEnergy_d_height_77-1500.pdf}
-    \caption{Left: Imaginary part of impurity self-energy for Fermi liquid (FL, $|W/J| < 1.79$) and pseudogapped phases (NFL, $|W/J| \geq 1.79$).
-The FL self-energy fits to $\Sigma^{\prime\prime} \sim \omega^{\alpha}$ with $\alpha\approx 2$, vanishing as $\omega\to 0$, while the NFL self-energy grows as $\Sigma^{\prime\prime} \approx a - b\omega^{\beta}$ for small $\omega$, with $\beta\approx -2$.
-Remarkably, the NFL exponent remains mostly unchanged through the entirety of the PG phase.
-Right:}
-    \label{selfEnergy}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.49\linewidth]{QPR_77-1500.pdf}
-    \includegraphics[width=0.49\linewidth]{Sdz_49-2000-fixed.pdf}
-    \caption{Suppression of quasiparticle residue ($Z_{imp}$) as the impurity model is tuned towards the Mott transition.
-An initial drastic fall in $Z_{imp}$ is observed for $W/J \lesssim (W/J)_\text{PG}$ from $0.3$ to around $0.05$, signalling the destruction of the FL with unraveling of Kondo screening.
-A steady decrease in $Z_{imp}$ is observed in passage through the PG, and is vanishingly small close to the Mott transition due to a divergent self-energy.
+    \includegraphics[width=0.49\linewidth]{localQPResidue.pdf}
+    \includegraphics[width=0.49\linewidth]{I2-di_69-2000.pdf}
+    \caption{Left: Suppression of quasiparticle residue as the impurity model is tuned towards the Mott transition.
+An initial drastic fall observed for $W/J \lesssim (W/J)_\text{PG}$, signalling the destruction of the FL with unraveling of Kondo screening.
+A second drastic fall is observed close to the Mott transition due to a divergent self-energy.
 Inset shows the growth of unscreened impurity magnetic moment in the pseudogap phase.
+    Right: Mutual information $I_{2}(d,r)$ between the impurity spin and conduction bath local spins as a function of the distance {\bf r} between them.
+$I_{2}(d,r)$ decays exponentially in the FL phase (blue), but show long-ranged behaviour in the non-FL phase (green, yellow).
+The range of the entanglement is seen to grow yet larger particularly close to the transition (green).
     }
@@
 \end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.49\linewidth]{SF-di_77-700.pdf}
-    \includegraphics[width=0.49\linewidth]{I2-di_77-700.pdf}
-    \caption{Spin-flip correlation $\braket{S_d^+ S_{r}^- + \text{h.c.}}$ and mutual information $I_{2}(d,r)$ between the impurity spin and conduction bath local spins as a function of the distance {\bf r} between them, normalised against the value for the nearest-neighbour sites.
-Both decay very quickly in the FL phase (blue), but show long-ranged behaviour in the non-FL phase (yellow, green), extending to the edges of the system at the critical point (green).}
-    \label{longranged}
-\end{figure}
 
-\section{Non-local nature of the pseudogap non-FL.}
-In Fig.~\ref{longranged}, both the mutual information and spin-flip correlations between the impurity spin and conduction bath sites are observed to undergo a crossover within the PG, from a short-ranged behaviour at its onset, to a long-ranged behaviour as the Mott transition approaches~\cite{suppmat}.
-The entanglement is also observed to be multipartite in nature: in Fig.\ref{qfiplot}, the quantum Fisher information (QFI)~\cite{Hauke2016} computed for the ground state wavefunction using an operator corresponding to the sum of local spin-flip exchange processes shows a jump at the onset of the PG.
-Further, the Fermi liquid is observed to possess bi-partite entanglement while the NFL of the PG phase displays pentapartite entanglement.
-%Similar long-ranged behaviour of spin-flip correlations is also observed \textcolor{blue}{in Fig.~\ref{channelDecoupling}(right)} between the impurity and bath sites~\cite{suppmat}. 
-% \textcolor{blue}{
-%This is further evidence of the breakdown of local Kondo screening, and the resulting Landau quasiparticle excitations. 
-These striking results imply that the Mott transition observed by us lies beyond the local quantum criticality scenario~\cite{Si2001}.
-Instead,  we observe the PG phase to be a novel state of strongly interacting quantum matter emergent from the breakdown of local Kondo screening.
-This state is described by a quantum critical Fermi surface with non-FL Fermi arcs that display increasingly critical behaviour, i.e., dynamics described by non-local quantum fluctuations, and excitations that become truly long-ranged close to the transition.
+\par\noindent\textit{Non-local nature of the pseudogap.}
+In Fig.\ref{channelDecoupling}(right), both the mutual information and spin-flip correlations between the impurity spin and conduction bath sites are observed to undergo a crossover within the PG, from a short-ranged behaviour at its onset, to a long-ranged behaviour as the Mott transition approaches~\cite{suppmat}.
+%Similar long-ranged behaviour of spin-flip correlations is also observed \textcolor{blue}{in Fig.\ref{channelDecoupling}(right)} between the impurity and bath sites~\cite{suppmat}. 
+This is further evidence of the breakdown of local Kondo screening, and the resulting Landau quasiparticle excitations. 
+This implies that the observed Mott transition lies beyond local quantum criticality scenario~\cite{Si2001}: the non-FL Fermi arcs of the PG phase display increasingly critical behaviour close to the transition, with dynamics that cannot be described by local quantum fluctuations, and excitations that become truly long-ranged.
+\textcolor{blue}{Discuss that the pseudogapped Fermi arcs and gapped Luttinger surfaces (zeros of Greens function) arise from splitting of double poles on the Fermi surface into poles on either side together with zeros pinned at the FS; gapping and emergence of zeros breaks $\mathcal{Z}_{2}$ symmetry of the FS (cite Haldane-Anderson, recent works by Phillips et al.), and disconnection of the homotopy charge associated with the Luttinger count with the physical charge, i.e., the backflow contribution from the zeros at the FS must be taken into account (for the half-filled p-h symmetric system being studied here) to account for how Luttinger's volume is maintained.
+Further, that the existence of this Adler-Bell-Jackiw triangle anomaly related to the PG FS leads naturally (via recent works of Casini et al., La Nave et al., Altshuler et al., von Neumann, Haag etc.) to the existence of non-local propagating degrees of freedom in the gapless NFL arcs.
+The appearance of zeros at the FS affects the Atiyah-Singer index associated with the FS (cite Heath and Bedell) that leads to the Luttinger volume.
+As the ABJ triangle anomaly is captured by Atiyah-Singer index theorem (cite Jackiw et al lectures), the appearance of this anomaly at the FS topology changing Lifshitz transition is linked to changes in topological properties of the FS, and hence invariant under renormalization.
+Thus, the drastic change in nature of the real-space excitations (from local Landau qps to something increasingly non-local in the NFL Fermi arcs of the PG phase) is dictated by topological principles even as they are emergent under renormalisation.}
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.49\linewidth]{qfi_77-2000.pdf}
-    \caption{Evolution of the Quantum Fisher Information $F_Q$ for a nearest-neighbour spin-flip operator $\mathcal{O} = \sum_{i \in \text{odd}}(S_i^+S_{i+1}^- + \text{h.c.})$ through the first Lifshitz transition and the pseudogap.
-The vertical dashed line marks the onset of the PG.
-To the left of it, the QFI in the Fermi liquid phase shows at most bipartite entanglement ($F_Q < 2$), while the PG shows the presence of multipartite entanglement upto 5 parties ($F_Q > 4$).}
-    \label{qfiplot}
-\end{figure}
-\section{An exactly solvable singular nodal non-Fermi liquid at Mott criticality.}
-%\section{Evolution of the pseudogapped non-FL.} 
-Very close to the transition, the excitations of the nodal non-FL correspond to those of a Hatsugai-Kohmoto model~\cite{Baskaran1991,Hatsugai1992}.
+\par\noindent\textit{Evolution of the pseudogapped non-FL.} Very close to the transition, the excitations of the marginal FL are replaced by those of a Hatsugai-Kohmoto model~\cite{Baskaran1991,Hatsugai1992}.
 This insight is obtained from a perturbation-theoretic treatment of the RG fixed point Hamiltonian of the impurity model for $W/J\lesssim (W/J)_{\text{PG}}$, by considering the effects of a small fixed point Kondo scattering probability \(J^*\) in the backdrop of a larger bath interaction parameter \(|W|\).
@@
 
-Consequently, the resulting non-FL metal of the lattice model involves long-lived excitations of multiple \({\bf k}\)-states, and manifest in the form of a divergent one-particle self-energy at the non-interacting Fermi surface~\cite{Phillips2020}:
+Consequently, the resulting non-FL metal of the lattice model involves long-lived excitations of multiple \({\bf k}\)-states, and manifest in the form of 
+a divergent one-particle self-energy at the non-interacting FS face~\cite{Phillips2020}:
 	$\Sigma_{{\bf q}}(\omega) = -\frac{u^2/4}{\omega - \epsilon_{\bf q}}$, such that $\Sigma_{\epsilon_{\bf q}=0}(\omega \to 0)  \to \infty$. This zero-frequency self-energy pole 
 presages the transition into a Mott insulating phase, where it marks a hard gap in the spectral function for charge excitations.
-This is consistent with our findings for the lattice (Fig.~\ref{chargeCorr}(Right)) and impurity self-energies~(Fig.\ref{selfEnergy} (Right)).
-For small but non-zero values of \(\omega - \epsilon_{\bf k}\), we obtain a quasiparticle residue that vanishes with $\omega$, \(Z_\text{imp} \sim \omega^2/U^2 \).
-The scattering rate of this singular NFL possesses a sharp peak at the Fermi surface (\(\omega=\epsilon_{\bf k_{\mathrm{F}}}\)): \(\Gamma \sim U^2\delta(\omega - \epsilon_{\bf k})\), consistent with the sharply peaked Lorentzian $\Sigma''_{{\bf k}}(\omega)\sim \omega^{-2}$ captured in Fig.\ref{selfEnergy}(Left).
-This quantum critical non-Fermi liquid metal is an example of a strongly coupled scale-invariant form of quantum matter.
-The exact solution for eq.\eqref{HKModel} reveals the presence of low-energy excitations comprised of holons and doublons~\cite{Hatsugai1992}.
-These features point to the nodal NFL as a long-ranged and multipartite entangled, strongly interacting scale-invariant state of quantum matter with unparticle-like excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} that are completely disconnected from the quasiparticles of the Fermi liquid.
+This is consistent with our findings for the lattice (Fig.\ref{chargeCorr}(right)) and impurity self-energies~\cite{suppmat}.
+Further, for small but non-zero values of \(\omega - \epsilon_{\bf k}\), we obtain the quasiparticle residue \(Z_\text{imp} \sim \omega^2/U^2 \), i.e., $Z_{imp}$ vanishing faster compared to MFL.
+This explains the sharp fall in $Z_\text{imp}$ observed at the transition (Fig.\ref{channelDecoupling}(left)).
+The scattering rate at the FS \(\omega=\epsilon_{\bf k}\) diverges, \(\Gamma \sim U^2\delta(\omega - \epsilon_{\bf k})\), \textcolor{red}{in contrast to \(\Gamma \sim \omega\) observed in MFL}.
  Additionally, we observe that the nodal metal possesses pairing fluctuations~\cite{suppmat} that can become dominant upon doping~\cite{Phillips2020}.
-
-\section{Pseudogap as a strongly coupled phase of quantum matter.}
-We now unveil an organising principle that leads to the remarkable properties observed above for the strongly interacting NFL of the PG phase.
-The existence of a sharp connected FS at $T=0$ can be understood as the existence of a topologically protected manifold of gapless chiral excitations in ${\bf k}$-space at the Fermi surface~\cite{Heath_2020}.
-The FS is characterised by a topological index corresponding to an anomaly in the quantum many-body theory for electrons, and can be understood as a generalised symmetry of such a system~\cite{lanave2025,McGreevy2023}.
-A theorem by Luttinger and Ward~\cite{luttinger1960ground} shows that a count of the physical charge (known as Luttinger's volume) is identical to the topological index (a so-called homotopy charge known as Luttinger's count) even in the presence of electronic interactions that do not disturb the FS.
-We will now argue that the emergence of antinodal Luttinger surfaces involve a disconnection of the Fermi surface (into Fermi arcs) and that, by following La Nave et al.~\cite{lanave2025}, the accompanying change in its topological properties leads to the existence of gapless NFL excitations that are non-local in nature.
-
-The antinodal Luttinger surfaces arise from the splitting of double poles of the single-particle Greens function on the FS into poles lying on opposite complex half-planes, together with zeros that are pinned at the FS.
-These changes in the analytic structure of the single-particle Greens function have several important consequences.
-First, the emergent zeros break a $\mathbb{Z}_{2}$ symmetry of the FS~\cite{Anderson2001,Huang2022,lanave2025}.
-Second, they signal a divergent electronic self-energy as a function of the wavevector ${\bf k}$, render ill-behaved the Luttinger-Ward functional of the interacting electronic problem, and violate the generalised symmetry encoded within it.
-The changes in the pole structure change the Luttinger count topological invariant, while the zeros give rise to an additional topological contribution (linked to the triangle Adler-Bell-Jackiw anomaly~\cite{adler1969axial,bell1969pcac,Altshuler_1998}).
-As a consequence of the half-filled particle-hole symmetric nature of the system at hand, Luttinger's volume is preserved upon taking into account topological contributions from both the Luttinger count {\it and} the zeros~\cite{seki2017topological}.
-
-Importantly, 
-% the additional anomaly arising from the Luttinger surfaces serves as a disconnection of the Luttinger's count from the physical charge. 
-La Nave et al.~\cite{lanave2025} argue, following recent developments in understanding generalised symmetries~\cite{Casini2021Symmetries}, that the additional anomaly arising from the Luttinger surfaces
-% such a disconnection of the physical and topological (Luttinger's count) charges 
-guarantees the existence of gapless NFL excitations that are non-local in nature.  
-%and disconnection of the homotopy charge associated with the Luttinger count with the physical charge, i.e., the backflow contribution from the zeros at the FS must be taken into account (for the half-filled p-h symmetric system being studied here) to account for how Luttinger's volume is maintained.
-%Further, it has recently been shown (Cite Heath & Bedell, NJP 2020; La Nave et al., arXiv:2506.04342) that the existence of Luttinger surfaces indicates the existence of an anomaly; that the existence of this Adler-Bell-Jackiw triangle anomaly related to the PG FS leads naturally (via recent works of Casini et al., La Nave et al., Altshuler et al., von Neumann, Haag etc.) to the existence of non-local propagating degrees of freedom in the gapless NFL arcs.
-The appearance of zeros at the FS affects the Atiyah-Singer index associated with the FS (cite Heath and Bedell) that leads to the Luttinger volume.
-As the ABJ triangle anomaly is captured by Atiyah-Singer index theorem (cite Jackiw et al lectures), the appearance of this anomaly at the FS topology changing Lifshitz transition is linked to changes in topological properties of the FS, and hence invariant under renormalization.
-Thus, the drastic change in nature of the real-space excitations observed by us - from local Landau quasiparticles of the Fermi liquid to the increasingly nonlocal excitations of the NFL Fermi arcs in the PG phase - appears to be dictated by a topological principle and, therefore, robust under renormalisation.
-This signals the NFL Fermi arcs of the PG as an emergent phase of strongly interacting quantum matter that is the parent metal of the Mott insulator.
-The same topological principle connects the nonlocal unparticle-like gapless excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} of the scale-invariant nodal NFL observed precisely at the Mott critical point to those of the rest of PG phase, e.g., a universal power-law scaling of $\Sigma''_{{\bf k}}(\omega)\sim \omega^{-2}$ of the NFL throughout the PG phase (Fig.~\ref{selfEnergy} (Left)).
-
-\section{Conclusions.} We find compelling evidence that the Mott transition in the 2D extended Hubbard model involves continuous passage through a PG phase whose gapless Fermi arcs host a long-ranged multipartite entangled non-FL metal.
-This non-FL turns increasingly singular with the onset of criticality into a Mott insulator.
-The evolution of this PG phase with doping
+\par\noindent\textit{Conclusions.} We find compelling evidence that the Mott transition involves continuous passage through a PG phase possessing an increasingly singular, non-local nodal non-FL metal, and the onset of long-ranged entanglement at criticality.
+The evolution of this singular PG phase with doping
 deserves further attention.
-
-\section{Acknowledgments.}
+\par\noindent\textit{Acknowledgments.}
 AM thanks IISER Kolkata for funding through a JRF and SRF. S Lal thanks the SERB, Govt. of India for funding through MATRICS Grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
@@
 where we replaced \(N-3\) with \(N\) assuming a large number of sites. Using this, the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.
-
-\section{Emergence of a Hatsugai-Kohmoto model at the quantum critical point}\label{hkmDerivation}
-
 \end{document}

### 2025-12-10 submissions/Earlier Versions of Manuscript/tilingProject.tex
started creating referee response

--- 2025-05-02 TilingProjectDraft/tilingProject.tex
@@
 	\centering
+
     \includegraphics[width=0.48\textwidth]{clusterBath.pdf}
@@
 \subsection{Hamiltonian}
-We consider an impurity spin \(\vec S_d\) interacting with a two-dimensional tight-binding conduction bath through a highly localised interaction, described by the Hamiltonian
-\begin{equation}\begin{aligned}
-	\mathcal{H} = H_\text{cbath} + H_\text{imp-cbath} + H_\text{cbath-int}~,
-\end{aligned}\end{equation}
-where \(H_\text{cbath}\) is the kinetic energy arising out of nearest-neighbour hopping processes,
-\begin{equation}\begin{aligned}
-	H_\text{cbath} = -2t\sum_{{\bf k}}\left[\cos(ak_x) + \cos(ak_y)\right] c^\dagger_{{\bf k},\sigma}c_{{\bf k},\sigma}~.
+We consider an impurity site \(\vec S_d\) interacting with a two-dimensional tight-binding conduction bath through a highly localised interaction, described by the Hamiltonian
+\begin{equation}\begin{aligned}
+	\mathcal{H} = H_\text{cbath} + H_\text{imp} + H_\text{imp-cbath} + H_\text{cbath-int}~,
+\end{aligned}\end{equation}
+where \(H_\text{cbath}\) is the kinetic energy arising out of nearest-neighbour hopping processes and $H_\text{imp}$ is the particle-hole symmetric impurity-local term,
+\begin{equation}\begin{aligned}
+	H_\text{cbath} = -2t\sum_{{\bf k}}\left[\cos(ak_x) + \cos(ak_y)\right] c^\dagger_{{\bf k},\sigma}c_{{\bf k},\sigma}~,\quad H_\text{imp} = -\frac{U}{2}\left(n_{d\uparrow} - n_{d\downarrow}\right)^2~.
 \end{aligned}\end{equation}
@@
 \begin{equation}\begin{aligned}
-	H_\text{imp-cbath} &=\frac{1}{2} J\sum_{\sigma_1,\sigma_2}\sum_{Z} {\bf S}_d\cdot c^\dagger_{Z\sigma_1}{\boldsymbol \tau}_{\sigma_1,\sigma_2} c_{Z\sigma_2}~,\\
+	H_\text{imp-cbath} &=\frac{1}{2} J\sum_{\sigma_1,\sigma_2}\sum_{Z} {\bf S}_d\cdot c^\dagger_{Z\sigma_1}{\boldsymbol \tau}_{\sigma_1,\sigma_2} c_{Z\sigma_2} - V\sum_{\sigma,Z}\left(c^\dagger_{d\sigma}c_{Z\sigma} + \text{h.c.}\right)~,\\
 	H_\text{cbath-int} &= -\frac{W}{2}\sum_{Z} \left(n_{Z\uparrow} - n_{Z\downarrow}\right)^2 ~,
@@
 where \(Z\) sums over all nearest-neighbour sites of the impurity site (navy blue circles in Fig.~\ref{embeddedEsiam}, henceforth referred to as bath zeroth sites).
-The impurity interacts with the bath zeroth sites in \(H_\text{imp-cbath}\) through four local Kondo terms, of uniform strength.
+The impurity interacts with the bath zeroth sites in \(H_\text{imp-cbath}\) through four single-particle hybridisation terms of strength $V$ and spin-exchange terms of strength $J$.
 The other term \(H_\text{cbath-int}\) represents local Hubbard interactions on the four zeroth sites, again of uniform strength.
 
-The 2D structure of the impurity model and its distinction from the infinite-dimensional counterpart becomes apparent once we transform the Hamiltonian to momentum space:
+The 2D structure of the impurity model and its distinction from the infinite-dimensional counterpart becomes apparent once we transform the Hamiltonian to momentum space.The conduction bath operators transform as
+\begin{equation}\begin{aligned}
+	c^\dagger_{{\bf r}} = \sum_{\bf k}e^{-i{\bf k}\cdot{\bf r}}c^\dagger_{\bf k}~,
+\end{aligned}\end{equation}
+where the momentum states $\bf k$ are the plane wave solutions of the tight-binding model obtained in the non-interacting limit: $U=J=0,V=t$.
+Transforming all bath operators leads to the following form:
+\begin{equation}\begin{aligned}
+	H_\text{imp-cbath} &=\frac{1}{2} \sum_{\sigma_1,\sigma_2,{\bf k}, {\bf k}^\prime} J_{{\bf k}, {\bf k}^\prime}{\bf S}_d\cdot c^\dagger_{{\bf k}\sigma_1}{\boldsymbol \tau}_{\sigma_1,\sigma_2} c_{{\bf k}^\prime\sigma_2}~,\\
+	H_\text{cbath-int} &= -\frac{1}{2}\sum_{{\bf k}, {\bf k}^\prime, {\bf q}, {\bf q}^\prime} W_{{\bf k}, {\bf k}^\prime,{\bf q}, {\bf q}^\prime} c^\dagger_{\bf k}c_{{\bf k}^\prime}c^\dagger_{\bf q}c_{{\bf q}^\prime}~,
+\end{aligned}\end{equation}
+where the momentum-dependent couplings are defined as
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-These transformations involve translating one or both momenta through the center of the Brillouin zone. \textcolor{red}{Is this a d-wave symmetry of the RG equation?}
+These transformations involve translating one or both momenta through the center of the Brillouin zone.
 

### 2025-12-10 submissions/NPJ/Supplementary/supplementary.tex
started creating referee response

--- 2025-04-17 TilingProjectDraft/tilingProject.tex
@@
-%! TEX program = latexmk
-\documentclass[reprint,hidelinks,onecolumn]{revtex4-2}
-\usepackage{braket,amsmath,color,graphicx,bookmark,bm,amssymb}
-\graphicspath{{./figures/}}
+%\documentclass{article}
+%\documentclass[
+%%preprint,
+%reprint,onecolumn,
+%superscriptaddress,
+%groupedaddress,
+%%unsortedaddress,
+%%runinaddress,
+%%frontmatterverbose, 
+%%preprint,
+%%preprintnumbers,
+%%nofootinbib,
+%%nobibnotes,
+%%bibnotes,
+%%aps,superscriptaddress,
+%aps,pra,
+%%rmp,
+%%prstab,
+%%prstper,
+%%floatfix,
+%10pt
+%]{revtex4-2}
+\documentclass[%
+ reprint,onecolumn,
+superscriptaddress,
+groupedaddress,
+%unsortedaddress,
+%runinaddress,
+%frontmatterverbose, 
+%preprint,
+%preprintnumbers,
+%nofootinbib,
+%nobibnotes,
+%bibnotes,
+aps,superscriptaddress,
+pra,
+%rmp,
+%prstab,
+%prstper,
+%floatfix,
+]{revtex4-2}
+%\usepackage{amsmath,amssymb,bm,graphicx,braket}
+\usepackage[margin=1.5cm]{geometry}
+%\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue,urlcolor=blue]{hyperref}
+\usepackage{graphicx,braket,color,bm,amsmath,amssymb,braket,placeins}
+% \graphicspath{{./figures/}}
 \bibliographystyle{apsrev4-2}
+\usepackage{natbib}
+
+\usepackage{etoolbox}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\makeatletter
+\apptocmd{\thebibliography}{\global\c@NAT@ctr 89\relax}{}{}
+\makeatother
 \begin{document}
-
-\title{\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electrons}
-\author{Abhirup Mukherjee, Siddhartha Lal}
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research-Kolkata, Mohanpur Campus, West Bengal 741246, India}
+\title{Supplementary Materials for ``Mott Criticality as the Confinement Transition of a Pseudogap-Mott Metal"}
+
+\author{Abhirup Mukherjee}
+\email{am18ip014@iiserkol.ac.in}
+\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
+}
+\author{S. R. Hassan}
+\email{shassan@imsc.res.in}
+\affiliation{The Institute of Mathematical Sciences, HBNI, C.I.T. Campus, Chennai 600 113, India}
+\author{Anamitra Mukherjee}
+\email{anamitra@niser.ac.in}
+\affiliation{School of Physical Sciences, National Institute of Science, Education and Research, HBNI, Jatni 752050, India}
+\author{N. S. Vidhyadhiraja}
+\email{raja@jncasr.ac.in}
+\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
+\author{A. Taraphder}
+\email{arghya@phy.iitkgp.ac.in}
+\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
+\author{Siddhartha Lal}
+\email{slal@iiserkol.ac.in}
+\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
+}
+
 \date{\today}
@@
 
-\section{The philosophy of auxiliary model methods}
-
-The present method is a realisation of the general method of using simpler systems called auxiliary models to study bulk systems~\cite{martin_2016}.
-In general, a full Hamiltonian can be separated into the Hamiltonians for a particular subsystem \(S\), the rest of the system \(R\), and the interactions between \(S\) and \(R\).
-\begin{equation}\begin{aligned}
-	\mathcal{H} &= \mathcal{H}_S\ket{S}\bra{S} + \mathcal{H}_R \ket{R}\bra{R} + \mathcal{H}_{SR} \ket{S}\bra{R} \\
-				&+ \mathcal{H}_{RS}\ket{S}\bra{R} = \begin{bmatrix} & \mathcal{H}_{R} && \mathcal{H}_{RS} & \\ & \mathcal{H}_{RS}^* && \mathcal{H}_{S} & \end{bmatrix}
-\end{aligned}\end{equation}
-where \(\ket{S}\) and \(\ket{R}\) actually represents sums over all basis kets of \(S\) and \(R\) respectively.
-As an example, we can split the Hubbard model Hamiltonian between a particular site \(i = p\) and the rest of the lattice into three parts \(H_\text{hubb} = H_S + H_R + H_{SR} + H_{RS}\) (fig.~\ref{cluster-bath}), where
-\begin{equation}\begin{aligned}
-	H_S &= U^H\hat n_{p \uparrow} \hat n_{p \downarrow} - \mu^H \sum_\sigma \hat n_{p \sigma}\\
-	H_R &= U^H\sum_{i \neq p}\hat n_{i \uparrow} \hat n_{p \downarrow} - \mu^H \sum_{i \neq p, \sigma} \hat n_{i \sigma} \\
-		&-t^H\sum_{\sigma,\left<i,j \right>\atop{i \neq p \neq j}}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right) \\
-	H_{SR} + H_{Rs} &= - t^H\sum_{\sigma,\atop{i \in \text{N.N. of }p}}\left(c^\dagger_{i\sigma} c_{p\sigma} + \text{h.c.}\right)~.
-\end{aligned}\end{equation}
-The Greens function of the full Hamiltonian can also be split in a similar fashion:
-\begin{equation}\begin{aligned}
-	G(\omega) = \begin{bmatrix} G_S && G_{SR} \\ G_{RS} && G_R \end{bmatrix}
-\end{aligned}\end{equation}
-Each Greens function can be written in terms of the non-interacting counterpart and the self-energy through the Dyson equation: \(\Sigma_i = 1/G_{i,0} - 1/G_i\).
-
-The subsystem \(S\) is usually taken to be the "cluster", and consequently, \(R\) represents the "bath".
-The smaller system is typically chosen such that its eigenstates are known exactly.
-Progress is then made by choosing a simpler version of \(H_R\) and a simpler form also for its coupling \(H_{RS}\) with the smaller system.
-This combination of the cluster and the simpler bath is then called the \textit{auxiliary system}.
-A typical auxiliary system for the Hubbard model could, potentially, be the single-impurity Anderson model (SIAM), where the impurity represents an arbitrary site \(p\) of the lattice, the bath represents the rest of the lattice sites and the hybridisation term between the impurity and the bath represents the coupling term \(H_{RS}\):
-\begin{equation}\begin{aligned}\label{clus_bath_siam}
-	\mathcal{H}_\text{SIAM} = \underbrace{\epsilon_d \hat n_d + U \hat n_{d \uparrow} \hat n_{d \downarrow}}_{H_S} + \underbrace{- t\sum_{\left<i,j \right>, \sigma}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right)}_{H_{R}} + \underbrace{V\sum_\sigma \left( c^\dagger_{d\sigma}c_{0\sigma} + \text{h.c.}\right)}_{H_{SR}}~.
-\end{aligned}\end{equation}
-Such a construction is shown in fig.~\ref{cluster-bath}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.48\textwidth]{clusterBath.pdf}
-	\caption{\textit{Left}: Full Hubbard model lattice with onsite repulsion $U^H$ on all sites and hopping between nearest neighbour sites with strength $t^H$.
-\textit{Right}: Extraction of the auxiliary (cluster+bath) system from the full lattice.
-The central site on left becomes the impurity site (red) on the right (with an onsite repulsion $\epsilon_d$), while the rest of the $N-1$ sites on the left form a conduction bath (green circles) (with dispersion $\epsilon_k$ and correlation modelled by the self-energy $\Sigma_k(\omega)$) that hybridizes with the impurity through the coupling $V$.}
-	\label{cluster-bath}
-\end{figure}
-\textit{It should be noted that any reasonable choice of the cluster and bath would break the translational symmetry of the full model}.
-To allow computing quantities, one would need to make the bath (which is a much larger system) simpler than the cluster (which is a single site).
-This distinction breaks the translational symmetry of the Hubbard model.
-For eg., if one chooses eq.~\ref{clus_bath_siam} as the auxiliary system, then the fact that the impurity has an onsite correlation while the bath does not means we have broken the symmetry between the cluster and the bath.
-
-\section{A ``bottoms-up" approach to using auxiliary models}
-
-The present work is aimed towards developing a new auxiliary model method to study correlated electronic systems.
-We first outline the main steps of the method, to make it more convenient for the reader to following the next sections:
-\begin{itemize}
-	\item The first step is to identify the correct impurity model which can faithfully capture the physics of lattice model we are trying to solve (see Subsection \ref{identifyModel}).
-This model must be solved using an impurity solver.
-In the present work, we use the recently-developed unitary renormalisation group method~\cite{anirbanmott1,anirbanmott2,anirbanurg1,anirbanurg2,siddharthacpi,santanukagome}.
-	\item The leap to the bulk model is then made by applying lattice translation operators on the impurity model.
-This process, referred to as tiling here, allows us to reconstruct the lattice model Hamiltonian from that of the auxiliary model (see Subsection~\ref{tilingsubsection}).
-	\item Once the Hamiltonians are linked, it is possible to relate the eigenstates and correlations functions between the auxiliary model and lattice model, using a manybody version of Bloch's theorem (see Section~\ref{tilingProcedure}).
-\end{itemize}
-
-\subsection{Formal description of the ``tiling" procedure}\label{tilingsubsection}
-
-We will now define the {\it tiling} procedure by which we can recreate the complete lattice model by using instances of an auxiliary model Hamiltonian.
-The first step is of course to identify an impurity model that can act as a good auxiliary model for out lattice model.
-The local behaviour of this impurity model should reflect the essential local physics of the lattice model.
-Typically, we will consider impurity model geometries where the real-space bath site connected directly to the impurity also harbours some kind of local interaction.
-We will henceforth refer to this site as the zeroth site.
-In the case where multiple sites are connected directly to the impurity, we will choose one of these sites for reference and call that the {\it bath zeroth site} throughout.
-
-In order to identify a {\it unit cell} for our tiling procedure, we place the impurity site at a reference site \({\bf r}_d\) of our lattice, and the bath zeroth site at a nearest-neighbour site \({\bf z}\), and label the corresponding auxiliary model Hamiltonian as \(\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})\).
-The unit cell at the position \({\bf r}_d\) is then obtained by placing the zeroth site on all nearest-neighbours of \({\bf r}_d\) and averaging over these configurations:
-\begin{equation}\begin{aligned}\label{unitCellHamiltonian}
-	\mathcal{H}_\text{aux}({\bf r}_d) = \frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})~,
-\end{aligned}\end{equation}
-where \({\bf z}\) is summed over all nearest-neighbours of \({\bf r}_d\) and \(\mathcal{Z}\) is the number of such nearest-neighbours.
-
-In order to create the bulk model, we now need to translate this auxiliary model over the entire lattice.
-For this, we define {\it many-particle global} translation operators \(T({\bf a})\) that translate all positions by a vector \({\bf a}\).
-In terms of manybody states and operators, their action is defined as
-\begin{equation}\begin{aligned}\label{translationDefinition}
-	&T^\dagger({\bf a}) \ket{{\bf r}_1, {\bf r}_2,\ldots} = \ket{{\bf r}_1 + {\bf a}}\otimes\ket{{\bf r}_2 + {\bf a}}\ldots\otimes\ket{{\bf r}_n + {\bf a}}\\
-	&T^\dagger({\bf a}) \mathcal{O}\left({\bf r}_1, {\bf r}_2,\ldots\right)T({\bf a}) = \mathcal{O}\left({\bf r}_1 + {\bf a}, {\bf r}_2 + {\bf a},\ldots\right)~,
-\end{aligned}\end{equation}
-where \(\ket{{\bf r}_1, {\bf r}_2,\ldots}\) is a state in the manyparticle Fock-space basis with the particles localised at the specified positions.
-For example, for a local fermionic creation operator \(c^\dagger({\bf r})\), we have
-\begin{equation}\begin{aligned}
-	T^\dagger({\bf a}) c^\dagger({\bf r}) T({\bf a}) = c^\dagger({\bf r} + {\bf a})~.
-\end{aligned}\end{equation}
-It acts similarly on the auxiliary model Hamiltonian:
-\begin{equation}\begin{aligned}
-	T^\dagger({\bf a})\mathcal{H}_\text{aux}({\bf r}_d)T({\bf a}) = \mathcal{H}_\text{aux}({\bf r}_d + {\bf a})~,
-\end{aligned}\end{equation}
-translating all sites by the vector \({\bf a}\). By introducing the Fourier transform to momentum space,
-\begin{equation}\begin{aligned}
-	\ket{{\bf r}_1, {\bf r}_2,\ldots} = \otimes_{j=1}^N \int d{\bf k}_j e^{-i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf k}_j}~,
-\end{aligned}\end{equation}
-it is easy to see that the total momentum states are eigenstates of the global translation operators:
-\begin{equation}\begin{aligned}
-	T^\dagger({\bf a})\ket{{\bf k}_1, {\bf k}_2,\ldots} &= \otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} T^\dagger({\bf a})\ket{{\bf r}_j}~,\\
-							    &=\otimes_{j=1}^N \int d{\bf r}_j e^{i {\bf r}_j\cdot{\bf k}_j} \ket{{\bf r}_j + {\bf a}}\\
-							    &=e^{-i {\bf a}_j\cdot{\bf k}_\text{tot}}\ket{{\bf k}_1, {\bf k}_2,\ldots},
-\end{aligned}\end{equation}
-where \({\bf k}_\text{tot} = \sum_j {\bf k}_j\) is the total momentum.
-
-The auxiliary model, being an impurity model, lacks translation symmetry.
-The lattice model does remain invariant under global translation operations.
-In order to reconstruct the full lattice model and restore its translation invariance, we translate the unit cell across all sites of the lattice:
-\begin{equation}\begin{aligned}
-	\label{tilingPrescription}
-	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})\\
-				&= \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d)T({\bf r} - {\bf r}_d)~ \\
-				&= \frac{1}{\mathcal{Z}}\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{aux}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d)~ \\
-\end{aligned}\end{equation}
-where \({\bf r}\) sums over all lattice sites.
-
-\subsection{Extending the Anderson impurity model: Identifying the correct auxiliary model}\label{identifyModel}
-The standard Anderson model consists of a correlated impurity site coupled with a non-interacting conduction bath.
-The double occupancy cost on the impurity is \(U\), while the single-particle hopping strength between the impurity and the conduction bath is \(V\).
-If the impurity site hybridises with a {\it non-interacting} bath defined by a uniform density of states, the impurity spectral function is found to have a well-defined Kondo resonance at low temperatures.
-Such a model does not exhibit a phase transition; the low-energy phase is one of strong-coupling for all parameter regimes.
-Increasing the impurity correlation \(U\) only serves to reduce the width of the central peak at the cost of the appearance of side bands at energy scales of the order of \(U\), but the resonance never dies.
-The situation is however different if the impurity is embedded in a correlated conduction bath with a non-trivial density of states.
-For the case of a conduction band with the DOS shown in the right of the figure below, the impurity hybridises into a reduced bandwidth because of the correlation on the lattice~\cite{held_2013}.
-
-This difference in the type of conduction baths is utilised in dynamical mean-field theory to describe various phases of the bulk system.
-This is done through the DMFT algorithm: one starts with a non-interacting bath, but depending on the value of \(U\), the conduction bath then gets modified and we ultimately end up with something that is different from what we started with.
-For small \(U\), the bath does not change much and we retain the central resonance of the impurity spectral function.
-This then describes a metal in the bulk.
-For larger values of \(U\), however, the bath changes significantly such that its density of states becomes non-constant.
-Above a critical \(U_c\), the impurity spectral function gets gapped out, and that then describes the insulating phase in the bulk.
-\textit{This leaves open the following question: What is the minimal correlation one can insert into the non-interacting bath (of a single-impurity Anderson model) that can capture both the metallic and insulating phases of the bulk model?}
-
-We have recently studied an extended Anderson impurity model (e-SIAM) where we introduced an explicit Kondo coupling \(J\) and a local correlation \(W\) on the bath zeroth site, which is the site connected to the impurity (see \cite{gazizovaleblanc2023} for some recent findings of non-local effective attractive interactions within the Hubbard model).
-The Hamiltonian of the e-SIAM for a half-filled impurity site is of the form
-\begin{equation}\begin{aligned}
-	\label{siam_attr}
-	\mathcal{H}_\text{E-S} = \mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} + \mathcal{H}_\text{imp-cbath}~,
-\end{aligned}\end{equation}
-where 
-\begin{itemize}
-	\item \(\mathcal{H}_\text{cbath} = -\frac{1}{\mathcal{Z}}t\sum_{i=0,1,\ldots;\sigma}\left(c^\dagger_{i,\sigma}c_{i+1,\sigma} + \text{h.c.}\right) - \frac{1}{2}W\left(\hat n_{0 \uparrow} - \hat n_{0 \downarrow}\right)^2\) is the Hamiltonian of the conduction bath consisting of a kinetic energy term and some local interaction terms on the zeroth site,
-	\item \(\mathcal{H}_\text{imp} = - \frac{U}{2}\left(\hat n_{d \uparrow} - \hat n_{d \downarrow} \right) ^2\) is the Hamiltonian for the localised impurity site, and
-	\item \(\mathcal{H}_\text{imp-bath} = J {\bf S}_d\cdot{\bf S}_0 - V \sum_{\sigma} \left(c^\dagger_{0\sigma} c_{d\sigma} + h.c.\right)\) describes the interaction between the impurity orbitals and the conduction bath.
-\end{itemize}
-Here, \(c_{d\sigma}\) is the impurity electron operator, \(c_{i\sigma}\) is the conduction bath electron operator, \(c_{0,\sigma}\) is the bath zeroth site operator, \({\bf S}_d\) is the impurity spin operator and \({\bf S}_0 = \sum_{\alpha,\beta}{\bf \sigma}c^\dagger_{0,\alpha}c_{0,\beta}\) is the operator for the local spin in the conduction bath.
-We have found that the e-SIAM has a stable local moment phase for \(W < -J/4\) with an antiferromagnetic Kondo coupling (\(J > 0\)).
-We have also shown that this model captures much of the phenomenology of the infinite dimensional Hubbard model (as discovered via DMFT), such as a second-order phase transition at \(T=0\) and the presence of an optical gap in the local spectral function beyond a certain value of interaction strength.
-Note that the impurity site and the conduction bath are both at half-filling.
-
-\subsection{Tiling towards a Hubbard-Heisenberg model with an embedded extended SIAM}
-In this subsection, we provide an explicit example of constructing a lattice model.
-We will consider a slightly more generalised version of the extended SIAM described in the previous section, where the impurity site coupled to the conduction bath purely through the s-wave channel.
-We will show that that model leads to a form of a Hubbard-Heisenberg model upon restoring translation invariance via repeated translation operations.
-The generalisation involve allowing an arbitrary filling on the impurity site and in the conduction bath, through two additional parameter: (i) a particle-hole asymmetry parameter \(\eta\) for the impurity site, (ii) a chemical potential for the conduction bath, and (iii) embedding the impurity into the lattice of the 2D conduction bath.
-This modified impurity model is shown in Fig.~\ref{embeddedEsiam}.
-The first term modifies the impurity Hamiltonian \(\mathcal{H}_\text{imp}\) into
-\begin{equation}\begin{aligned}\label{onsiteHamiltonian}
-	\mathcal{H}_\text{imp} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 - \eta\sum_\sigma \hat n_{{\bf r}_d\sigma}~.
-\end{aligned}\end{equation}
-where we have placed the impurity site at the position \({\bf r}_d\). The second term modifies the conduction bath Hamiltonian \(\mathcal{H}_\text{cbath}\):
-\begin{equation}\begin{aligned}\label{bathHamiltonian}
-	\mathcal{H}_\text{cbath} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2 \mathcal{Z}}W\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}~,
-\end{aligned}\end{equation}
-where \(\left<{\bf r}_i, {\bf r}_j\right>\neq {\bf r}_d\) indicates that the sum is over all nearest-neighbour pairs of sites avoiding the impurity site \({\bf r}_d\).
-
-In this notation, the interaction Hamiltonian can be written as
-\begin{equation}\begin{aligned}\label{interactionHamiltonian}
-	\mathcal{H}_\text{imp-cbath} = \frac{J}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}\sum_{{\bf z}\in\text{NN}({\bf r}_d)} {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} - \frac{V}{\sqrt{\mathcal{Z}}}\sum_{\sigma} \sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)
-\end{aligned}\end{equation}
-where \(\boldsymbol \tau = \left( \tau_x, \tau_y, \tau_z \right) \) is the vector of Pauli matrices. \(\sigma\) and \(\sigma^\prime\) can be \(\pm 1\) and represent up and down configurations.
-
-We now follow the prescription laid out in eq.~\ref{tilingPrescription}. The tiled Hamiltonian can be written as 
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{tiled} = \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\mathcal{H}_\text{cbath} + \mathcal{H}_\text{imp} + \mathcal{H}_\text{imp-cbath}\right]T({\bf r} - {\bf r}_d)~.
-\end{aligned}\end{equation}
-Note that in comparison to eq.~\ref{tilingPrescription}, we have dropped the sum over the zeroth sites, because our impurity model Hamiltonian (defined using eqs.~\ref{onsiteHamiltonian} through \ref{interactionHamiltonian}) already contains a sum over these zeroth sites.
-
-We consider the effect of the translation operations on each part of the Hamiltonian. We first have
-\begin{equation}\begin{aligned}
-	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{cbath}({\bf r}_d, {\bf z})T({\bf r} - {\bf r}_d) \\
-	=& \sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[-\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}_d;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{W}{2\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d}\hat n_{{\bf r}_i,\sigma}\right]T({\bf r} - {\bf r}_d) \\
-	=& -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\sum_{{\bf r}\neq{\bf r}_i,{\bf r}_j}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{W}{2\mathcal{Z}}\sum_{\bf r}\sum_{{\bf z}\in\text{NN}\left({\bf r}\right)}\left(\hat n_{{\bf z}, \uparrow} - \hat n_{{\bf z}, \downarrow}\right)^2 - \mu \sum_{{\bf r}_i}\sum_{{\bf r} \neq {\bf r}_i}\hat n_{{\bf r}_i,\sigma}\\
-	=& -\frac{1}{\sqrt\mathcal{Z}}(N-2)t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2}W\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\\
-\end{aligned}\end{equation}
-In the first step, the factor of \(\mathcal{Z}\) is cancelled out by the trivial sum over \({\bf r}_0\) in the first and third terms.
-At the last step, the three terms simplified for the following reasons.
-The inequality \(\left<{\bf r}_i, {\bf r}_j\right>\neq{\bf r}\) in the first term ensures that each nearest-neighbour pair appears in \(N-2\) instances of the auxiliary model, \(N\) being the total number of lattice sites; the two instances that do not contribute are the ones in which the impurity site itself is at \({\bf r}_i\) or \({\bf r}_j\).
-For the second term, the double sum \(\sum_{\bf r}\sum_{{\bf z} \in \text{NN}({\bf r})}\) evaluates to \(\mathcal{Z}\sum_{\bf r}\), because each point on the lattice appears \(\mathcal{W}\) times in the summation.
-This factor of \(\mathcal{W}\) cancels the one in the denominator.
-In the third term, the inner summation simply evaluates to \(N-1\), and we finally replace the dummy index \({\bf r}_i\) with \({\bf r}\).
-
-The next part is
-\begin{equation}\begin{aligned}
-	\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp}T({\bf r} - {\bf r}_d) = -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}~.
-\end{aligned}\end{equation}
-This is obtained simply by replacing the impurity position \({\bf r}_d\) with the translated position \({\bf r}\), generating a translation-invariant Hubbard term (the first term) and a finite chemical potential (second term).
-
-We now consider the final term:
-\begin{equation}\begin{aligned}
-	&\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\mathcal{H}_\text{imp-cbath}T({\bf r} - {\bf r}_d)\\
-	&=\sum_{{\bf r}}T^\dagger({\bf r} - {\bf r}_d)\left[\frac{1}{\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}_d}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} - \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z}\in\text{NN}({\bf r}_d)}\sum_{\sigma} V \left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]T({\bf r} - {\bf r}_d)\\
-	&=\sum_{{\bf r}}\sum_{{\bf z}\in\text{NN}({\bf r})}\left[\frac{1}{\mathcal{Z}}\sum_{\sigma,\sigma^\prime}J {\bf S}_{{\bf r}}\cdot{\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime} \right.
--  \frac{1}{\sqrt\mathcal{Z}}\left.\sum_{\sigma} V\left(c^\dagger_{{\bf r}_d,\sigma} c_{{{\bf z}},\sigma} + h.c.\right)\right]\\
-					 &=\sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]\\
-\end{aligned}\end{equation}
-At the last step, each nearest-neighbour pair of sites \({\bf r}_i, {\bf r}_j\) appear 2 times in the summation, because any site is a member of two distinct nearest-neighbour pairs.
-We have also defined \({\bf S}_{{\bf r}_j} =\sum_{\sigma,\sigma^\prime} {\boldsymbol \tau}_{\sigma,\sigma^\prime}c^\dagger_{{\bf z},\sigma}c_{{\bf z},\sigma^\prime}\) as the local spin operator.
-
-The total tiled Hamiltonian is therefore
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{tiled} = -\frac{N-2}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>,\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu (N-1) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} - \frac{1}{2}W\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  -\frac{U}{2}\sum_{{\bf r}}\left(\hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta\sum_{{\bf r},\sigma} \hat n_{{\bf r}\sigma}\\
-	+ \sum_{\left< {\bf r}_i, {\bf r}_j\right>}\left[\frac{2}{\mathcal{Z}}J {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{2}{\sqrt\mathcal{Z}}V \sum_{\sigma}\left(c^\dagger_{{\bf r}_i,\sigma} c_{{{\bf r}_j},\sigma} + h.c.\right)\right]
-\end{aligned}\end{equation}
-While constructing the tiled Hamiltonian, we have added extra copies of the non-interacting Hamiltonian \(\mathcal{H}_\text{cbath-nint} = -\frac{1}{\sqrt\mathcal{Z}}t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma}\) for the conduction bath (this results in the factors of \(N-2\) and \(N-1\) in front of the first and third terms).
-Upon removing these repeated terms, the tiled Hamiltonian becomes
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - (N-3)\mathcal{H}_\text{cbath-nint}\\
-							 &= -\frac{1}{\sqrt\mathcal{Z}}(t + 2V)\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \frac{1}{2}\left(U + W\right)\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2 - \left(\eta + 2\mu\right) \sum_{{\bf r}}\hat n_{{\bf r},\sigma} + \frac{2}{\mathcal{Z}}J\sum_{\left< {\bf r}_i, {\bf r}_j\right>} {\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j}
-\end{aligned}\end{equation}
-
-The result of the tiling operations is a Hubbard-Heisenberg model, of the form
-\begin{equation}\begin{aligned}
-	\mathcal{H}_\text{HH} &= -\frac{1}{\sqrt\mathcal{Z}}\tilde t\sum_{\left<{\bf r}_i, {\bf r}_j\right>;\sigma}\left(c^\dagger_{{\bf r}_i,\sigma}c_{{\bf r}_j,\sigma} + \text{h.c.}\right) - \tilde \mu \sum_{{\bf r}}\hat n_{{\bf r},\sigma} + \frac{1}{\mathcal{Z}}\tilde J\sum_{\left< {\bf r}_i, {\bf r}_j\right>}{\bf S}_{{\bf r}_i}\cdot{\bf S}_{{\bf r}_j} - \frac{1}{2}\tilde U\sum_{\bf r}\left(\hat n_{{\bf r} , \uparrow} - \hat n_{{\bf r} , \downarrow}\right)^2  ~,
-\end{aligned}\end{equation}
-where the tilde symbol indicates that the parameters are for the lattice model (and not the auxiliary model).
-By comparing the tiled model and the general lattice model, the lattice model parameters and the auxiliary model parameters can be mapped to each other:
-\begin{equation}\begin{aligned}\label{couplingsMappings}
-	\tilde t = t+2V,~~ \tilde U = U + W, ~ ~ \tilde \mu = 2\mu + \eta,~ ~ \tilde J = 2J~.
-\end{aligned}\end{equation}
-In summary, the appropriate method for reconstructing the lattice model Hamiltonian is therefore
-\begin{equation}\begin{aligned}\label{tilingPrescriptionFinal}
-	\mathcal{H}_\text{tiled} &= \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}~,
-\end{aligned}\end{equation}
-where we replaced \(N-3\) with \(N\) assuming a large number of sites. Using this, the extended-SIAM gets ``expanded" into a Hubbard-Heisenberg model.
-
+\section{Tiling basics}
 \subsection{Translation symmetry and a conserved total momentum}
-From the form in eq.~\ref{tilingPrescriptionFinal}, the tiled Hamiltonian is symmetric under global many-body translations of the kind defined in eq.~\ref{translationDefinition}, by arbitrary lattice spacings:
+The tiled Hamiltonian is symmetric under global many-body translations 
+%of the kind defined in eq.~\ref{translationDefinition}, 
+by arbitrary lattice spacings:
 \begin{equation}\begin{aligned}\label{translationSymmetry}
-	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})T({\bf a}) = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r + a}) = \sum_{{\bf r}^\prime}\mathcal{H}_\text{aux}({\bf r}^\prime)\\
+	&T({\bf a})^\dagger \mathcal{H}_\text{tiled} T({\bf a}) = T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r})T({\bf a}) = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r + a}) = \sum_{{\bf r}^\prime}\mathcal{H}_\text{aux}({\bf r}^\prime)\\
 	&T({\bf a})^\dagger\sum_{{\bf r}}\mathcal{H}_\text{cbath-nint}T({\bf a}) = \mathcal{H}_\text{cbath-nint}\\
@@
 \end{aligned}\end{equation}
-The definition and some properties of these global translation operations were provided in Appendix~\ref{BlochProperties}.
+%The definition and some properties of these global translation operations were provided in Appendix~\ref{BlochProperties}.
 It was shown there that they share eigenstates with the total momentum operator.
-In a lattice model, this continuous symmetry gets lowered to its discrete form: the total {\it crystal} momentum is conserved by any scattering process.
+In a lattice model, the continuous translation symmetry is lowered to its discrete form: the total {\it crystal} momentum is conserved by any scattering process.
 As a result, the eigenstates can be labelled using the combined index \(s = \left({\bf k}, n\right) \) where \({\bf k}\) is the total crystal momentum and \(n\) is a band index \(n\).
 
-The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using eq.~\ref{tilingPrescriptionFinal} also enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}).
-This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) defined in eq.~\ref{unitCellHamiltonian} can be used to construct eigenstates of the lattice Hamiltonian.
-The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
+The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians 
+%obtained using eq.~\ref{tilingPrescriptionFinal} also 
+enjoy a {\it many-body} Bloch's theorem~[55]
+%\cite{stoyanova}, 
+because the tiling procedure restores the translation symmetry of the Hamiltonian (as shown in eq.~\ref{translationSymmetry}).
+This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) %defined in eq.~\ref{unitCellHamiltonian}
+can be used to construct eigenstates of the lattice Hamiltonian. The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
 
@@
 where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\).
-With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~\cite{stoyanova}:
+With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~[55]:
+%\cite{stoyanova}:
 \begin{equation}\begin{aligned}\label{eigenstateProposal}
@@
 
-\section{Mapping Static and Dynamic Correlations from the Auxiliary Model to the Lattice Model}\label{tilingProcedure}
-\subsection{One-Particle Greens Functions: Momentum-space}
-In the previous part, we proposed a form for the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{gs}}\) of the auxiliary models.
-In this section, we will relate one-particle Greens functions of the bulk lattice to those of the auxiliary model.
-We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
-We define the retarded time-domain lattice \(k-\)space Greens function at zero temperature as
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c_{{\bf K}\sigma}(t), c^\dagger_{{\bf K}\sigma} \right\} | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(t\): 
-\begin{equation}\begin{aligned}\label{heisenberg}
-	c_{{\bf K}\sigma}(t) = e^{it H_\text{tiled} }c_{{\bf K}\sigma}e^{-i t H_\text{tiled}}~.
-\end{aligned}\end{equation}
-We now proceed to simplify one of the terms of the anticommutator (for simplicity of notation):
-\begin{equation}\begin{aligned}\label{greensFunction1}
-	&\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_{\vec r,\vec \Delta}e^{-i{\bf K}_0\cdot\vec\Delta}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-To make further progress, we insert the identity resolution \(1 = \sum_s\ket{\Psi_s}\bra{\Psi_s}\) in between the two operators, where \(s=\left({\bf k}, n\right)\) sums over all eigenstates (with energies \(\tilde E_s\)).
-The lattice eigenstates themselves can again be written in terms of those of the auxiliary model, using eq.~\ref{eigenstateProposal}:
-\begin{equation}\begin{aligned}
-	\ket{\Psi_s}\bra{\Psi_s} = \sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\vec k\cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}~.
-\end{aligned}\end{equation}
-With this, eq.~\ref{greensFunction1} becomes
-	\begin{equation}\begin{aligned}\label{greensfunction2}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\vec k_0\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-In order to bring this expression closer to the form of an auxiliary model Greens function, we would like to transform the initial and final states \(\ket{\psi(\vec r)}\) and \(\ket{\psi(\vec r + \vec \Delta)}\) to apply to the same auxiliary model.
-This is done by using the relation: \(\ket{\psi(\vec r + \Delta)} = T^\dagger(\vec \Delta)\ket{\psi(\vec r)}\), where \(T^\dagger(\vec \Delta)\) translates all lattice sites by the vector \(\vec\Delta\).
-\begin{equation}\begin{aligned}
-	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = \braket{\psi_{0}(\vec r) | T(\vec \Delta) c_{{\bf K}\sigma}(t) T^\dagger(\vec \Delta) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
-\end{aligned}\end{equation}
-The effect of the translation operators on the \(k-\)space annihilation operator can be easily ascertained by transforming it to real-space, using the Fourier transform definition
-\begin{equation}\begin{aligned}\label{fourTransf}
-	c({\bf K}) = \frac{1}{\sqrt N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r})~.
-\end{aligned}\end{equation}
-Upon applying this, we get
-\begin{equation}\begin{aligned}\label{translationOnField}
-	T\left(\vec a\right) c({\bf K}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}T\left(\vec a\right) c({\bf r}) T^\dagger\left(\vec a\right) = \frac{1}{N}\sum_{\bf r}e^{-i{\bf K}\cdot{\bf r}}c({\bf r} - \vec a) = e^{-i{\bf K}\cdot\vec a}c({\bf K})~.
-\end{aligned}\end{equation}
-Using this identity on the above expression gives
-\begin{equation}\begin{aligned}
-	\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime)} = e^{-i{\bf K} \cdot \vec \Delta}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) | \psi_n(\vec r^\prime+\vec \Delta^\prime - \vec \Delta)}
-\end{aligned}\end{equation}
-Finally replacing this all the way back into eq.~\ref{greensfunction2} gives
-	\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K}\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime - \vec\Delta)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-To further unify the operators, we make the substitution \(\vec \Delta^\prime \to \vec \Delta^\prime + \vec \Delta\), leading to the expression
-	\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\left(\vec k_0 + {\bf K} - \vec k\right)\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-The sum over \(\vec\Delta\) can now be carried out, resulting in
-\begin{equation}\begin{aligned}\label{greensfunction3}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~,
-\end{aligned}\end{equation}
-where the sum over \(s=(\vec k, n)\) has been reduced to a sum over the auxiliary model eigenstate index \(n\) because of the Kronecker delta \(\delta\left(\vec k_0 + {\bf K} - \vec k\right)\).
-This can be further simplified by splitting the sum over \(\vec\Delta^\prime\) into positive and negative parts and then making the transformation \(\vec r^\prime \to \vec r^\prime + \vec \Delta^\prime\):
-\begin{equation}\begin{aligned}
-	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime-\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}\right] \\
-																																												   &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\right] \\
-\end{aligned}\end{equation}
-For each pair of \(\vec r^\prime\) and \(\vec\Delta^\prime\), the term within the box brackets has the form of a two-level Hamiltonian between the states \(\ket{\psi_n(\vec r^\prime)}\) and \(\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\), with a tunnelling amplitude \(e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\).
-The term can therefore be written in the eigenbasis of this Hamiltonian:
-\begin{equation}\begin{aligned}
-	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &=\frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right],
-\end{aligned}\end{equation}
-where \(\ket{\chi_n^\pm(\vec r^\prime,\vec\Delta^\prime)} = \frac{1}{\sqrt 2}\left[\ket{\psi_n(\vec r^\prime)} \pm e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime + \vec\Delta^\prime)}\right] \) are the eigenvectors of the tunnelling Hamiltonian with eigenvalues \(\pm 1\) respectively.
-With this basis transformation, we can rewrite eq.~\ref{greensfunction3} as
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-
-In order to make the expression more transparent, we consider the various components separately:
-\paragraph{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}:
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-These terms represent those contributions to the total Greens function that arise from excitations that start and end at a specific auxiliary model (at \(\vec r\)), and also evolve dynamically within the same auxiliary model.
-These terms are therefore exactly equal to the auxiliary model Greens function at position \(\vec r\), and are the most dominant contribution due to the localised nature of the impurity model.
-
-\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}:
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime \neq \vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-These are more non-local contributions; they involve excitations whose time evolution is governed by a different auxiliary model than the terminal one.
-These contributions are highly suppressed in the Kondo screened phase because of the strong entanglement of the singlet ground state.
-
-\paragraph{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime \neq 0\)}:
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \to \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime \neq \vec r,\vec \Delta^\prime \neq 0} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-These are the most non-local contributions; they involve excitations whose time evolution is governed by three different auxiliary models. Accordingly, these contributions are further suppressed.
-
-We now consider each type of contribution in more detail.
-\subsection{\(\vec r^\prime = \vec r,~\vec\Delta^\prime=0\)}
-Restricting ourselves to just the single auxiliary model contributions gives
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-We first consider more carefully the transition operator \(\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\) for the 1-particle excitation giving rise to the above Greens function.
-Within our auxiliary model approach, gapless excitations within the lattice model are represented by gapless excitations of the impurity site, specifically those that screen the impurity site and form the local Fermi liquid.
-As a result, the uncoordinated \(\mathcal{T}-\)matrix for the lattice model must be replaced by a combined \(\mathcal{T}-\)matrix within the impurity model that captures those gapless excitations that occur in connection with the impurity, and projects out the uncorrelated excitations that take place even when the impurity site is decoupled from the bath.
-
-In order to construct this auxiliary model \(\mathcal{T}-\)matrix, we note that the impurity site can have both spin and charge excitations.
-Considering both excitations, the modified \(\mathcal{T}-\)matrix that constructs \(k-\)space excitations in correlation with the impurity site are
-\begin{equation}\begin{aligned}\label{tmatrix}
-	\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\left(\sum_{\sigma^\prime}c^\dagger_{d\sigma} + \text{h.c.}\right) + c_{{\bf K}\sigma}\left(S_d^+ + \text{h.c.}\right)~,
-\end{aligned}\end{equation}
-leading to the updated expression for the complete Greens function:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-
-In order to convert this into a more useful form, we use eq.~\ref{heisenberg}:
-\begin{equation}\begin{aligned}
-		\braket{\psi_{0}(\vec r) | \mathcal{T}_{{\bf K}\sigma}(t) | \psi_n(\vec r)} = \braket{\psi_{0}(\vec r) | e^{it H_\text{tiled} }\mathcal{T}_{{\bf K}\sigma}e^{-i t H_\text{tiled}} | \psi_n(\vec r)}~.
-\end{aligned}\end{equation}
-Guided by the relation in eq.~\ref{tilingPrescriptionFinal} \(H_\text{tiled} = \sum_{{\bf r}}\mathcal{H}_\text{aux}({\bf r}) - N\mathcal{H}_\text{cbath-nint}\) between the tiled Hamiltonian and the auxiliary model, we assume that the operator \(e^{-i t H_\text{tiled}}\) acting on the state \(\ket{\psi_n(\vec r)}\) involves the excitation energy \(E_n\) of only a single auxiliary model.
-Specifically, \(E_n\) is the energy of the eigenstate \(\ket{\psi_n(\vec r)}\).
-This is supported by the fact that this class of contributions to the Greens function is completed within a single auxiliary model.
-Accordingly, we replace \(H_\text{tiled}\) with \(E_n - \varepsilon_{\bf k} \), where \(\varepsilon_{\bf k}\) are the eigenenergies of the non-interacting conduction bath \(\mathcal{H}_\text{cbath-nint}\) and \({\bf k}\) is the crystal momentum associated with the state \(\ket{\psi_n(\vec r)}\).
-This momentum was found to be constrained to \({\bf k}_0 + {\bf K}\) below eq.~\ref{greensfunction3}.
-In the same way, the action of \(H_\text{tiled}\) on the terminal state \(\ket{\psi_{0}(\vec r)}\) gives \(E_0 - \varepsilon_{\bf k_0}\), where \(E_0\) is the ground state energy of the auxiliary model at \({\bf r}\).
-Applying this to our expression gives
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[e^{-it\omega_p} \mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + e^{-it\omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~,
-\end{aligned}\end{equation}
-where \(\omega_p = (E_n - \varepsilon_{\bf k_0 + \bf K}) - (E_0 - \varepsilon_{\bf k_0})\) is the particle-excitation cost and \(\omega_h = -\omega_p\) is the hole-excitation cost.
-We now introduce the Fourier transform \(g(\omega) = \int~dt~ e^{i\omega T}f(t)\) to obtain the frequency-domain Greens function in its spectral representation:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; \omega) = \frac{1}{N}\sum_{\vec r}\sum_n \braket{\psi_{0}(\vec r) | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}\right] | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-For each value of \({\vec r}\), the term within that summation is simply the Greens function (for the excitation \(\mathcal{T}_{{\bf K}\sigma}\)) of the auxiliary model with the impurity site at \({\vec r}\).
-Since all these impurity models are physically equivalent (because of translation invariance), we can replace the average over \({\bf r}\) with the value obtained from any one auxiliary model.
-\begin{equation}\begin{aligned}\label{kspaceGreensFunction}
-	\tilde G({\bf K}\sigma; \omega) &= \sum_n \braket{\psi_{0} | \left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma} \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}^\dagger + \frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n}\bra{\psi_n} \mathcal{T}_{{\bf K}\sigma}\right] | \psi_{0}} \\
-									&= G^>(\mathcal{T}^\dagger_{{\bf K}\sigma}, \omega - \varepsilon_{{\bf k}_0 + {\bf K}}) + G^<(\mathcal{T}^\dagger_{{\bf K}\sigma}, \omega + \varepsilon_{{\bf k}_0 + {\bf K}})~,
-\end{aligned}\end{equation}
-where \(G^>(\mathcal{O}^\dagger, t) = -i\braket{\mathcal{O}(t)\mathcal{O}^\dagger}\) and \(G^<(\mathcal{O}^\dagger, t) = -i\braket{\mathcal{O}^\dagger\mathcal{O}(t)}\) are the greater and lesser Greens function for the auxiliary model.
-
-\subsection{\(\vec r^\prime \neq \vec r,~\vec\Delta^\prime=0\)}
-Allowing for more non-local contributions, and updating the \(\mathcal{T}-\)matrix similar to the previous section gives the following Greens function:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r, \vec r^\prime} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-In order to allow computations within a single auxiliary model, we replace the translated state \(\ket{\psi_n(\vec r^\prime)}\) with \(T^\dagger(\vec r \to \vec r^\prime)\ket{\psi_n(\vec r)} \), where \(T^\dagger(\vec r - \vec r^\prime)\) translates all sites by the vector \(\vec r^\prime - \vec r\).
-This leads to a modified correlation function but within a single auxiliary model:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_{n,\vec r, \vec r^\prime} \bra{\psi_{0}(\vec r)} &\left[\mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.
-\\
-								&\left.
-\mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-In fact, by the same arguments as in the previous section, we can obtain a frequency-resolved Greens function:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; \omega) = \sum_n \bra{\psi_{0}} &\left[\frac{1}{\omega - \omega_p} \mathcal{T}_{{\bf K}\sigma}(t)T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}^\dagger + \right.\\
-															&\left.
-\frac{1}{\omega - \omega_h} \mathcal{T}^\dagger_{{\bf K}\sigma}T^\dagger(\vec r - \vec r^\prime) \ket{\psi_n}\bra{\psi_n}T(\vec r - \vec r^\prime) \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}} ~.
-\end{aligned}\end{equation}
-To obtain the above, we used the fact that \(H_\text{tiled}\) commutes with the translation operator.
-
-%TODO
-%By expanding in terms of the small parameter $\frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}}$, this expression for $\Sigma_{H-H}(\vec k,\omega)$ can be recast in the following form:
-%\begin{equation}\begin{aligned}
-%	\Sigma_{H-H}(\vec k, \omega) \simeq \Sigma_\text{loc}(\omega) + \tilde{\Sigma}(\vec k, \omega)~,~\label{selfenergy2}
-%\end{aligned}\end{equation}
-%where $\Sigma_\text{loc}$ and $\Sigma_\text{near-n}$ correspond to the local and nearest-neighbour self-energies defined on the real-space lattice 
-%\begin{eqnarray}
-%\Sigma_\text{loc}(\omega) &=& \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}^{(0)}} - \frac{\lambda_{\vec k_0}^2}{\mathcal{G}_{dd}}~,\\ 
-%\tilde{\Sigma}(\vec k, \omega)&=&\xi_{\vec k}\Sigma_\text{near-n}~,~\Sigma_\text{near-n} = \left(1/G^{(0)}\right)_\text{near-n} + \frac{\lambda_{\vec k_0}^2}{\mathcal{Z}}\frac{\mathcal{G}_{dz}}{\mathcal{G}_{dd}^2}~.
-%\end{eqnarray}
-%We note that the form of $\Sigma(\vec k, \omega)$ obtained by us is similar to the form proposed on phenomenological grounds in the generalised DMFT + $\Sigma$ approach~\cite{sadovskii2012}.
-
-\subsection{Equal-Time Ground State Correlators: Real-space}\label{staticCorr}
-We first consider a real-space operator \(\mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r})\) that quantifies the presence of correlations over a distance \({\bf \Delta}\).
-The correlation function itself is given by the expectation value of this operator in the ground state:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_1 + {\bf r}^\prime + {\bf r}_c + {\bf r}\right)  | \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_1 + {\bf r}_c + {\bf r}\right)} e^{-i{\bf k}_0\cdot\left({\bf r}_1 - {\bf r}_2\right)}~,
-\end{aligned}\end{equation}
-where \({\bf r}_1\) and \({\bf r}_1 + {\bf r}^\prime\) are the positions of the incoming and outgoing auxiliary model states, relative to \({\bf r}_c + {\bf r}\), and \({\bf k}_0\) is the crystal momentum of the ground state (which we will immediately set to zero).
-In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
-Substituting this appropriately for both the auxiliary model states gives:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_1 + {\bf r}^\prime + {\bf r}\right) \mathcal{O}({\bf r} + {\bf \Delta})\mathcal{O}^\dagger({\bf r}) T^\dagger\left({\bf r}_1 + {\bf r}\right) | \psi_\text{gs}\left({\bf r}_c\right)}\\
-								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}^\prime\right) \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
-								  &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} - {\bf r}_1) \mathcal{O}^\dagger(- {\bf r}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-As a final cosmetic change, we transform \({\bf r}_1 \to -{\bf r}\):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) = \frac{1}{N}\sum_{{\bf r},{\bf r}^\prime}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-Like in the Greens function calculation, we now consider the various kinds of contributions separately.
-
-\subsubsection{Intra-auxiliary model contributions: \({\bf r}^\prime = 0\)}
-These terms describe excitations that start and propagate within the same auxiliary model, upto a distance \({\bf \Delta}\):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r})\mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-With an eye towards introducing the impurity operators into the correlations, we insert a complete basis defined by the eigenstates \(\left\{\ket{\psi_n\left({\bf r}_c\right)}\right\} \) of the auxiliary model into the expression:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}}\sum_{n}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{O}({\bf \Delta} + {\bf r}) \ket{\psi_n\left({\bf r}_c\right)}\bra{\psi_n\left({\bf r}_c\right)} \mathcal{O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-
-For the excitations that exist purely in the conduction bath \(({\bf r} \neq {\bf r}_c)\), the excitation operators must be suitably modified (see the arguments around eq.~\ref{tmatrix}) in order to incorporate Kondo screening.
-The modified excitation operators are generally defined as
-\begin{equation}\begin{aligned}\label{operatorTmatrix}
-	\mathcal{\tilde O}({\bf r}) = \mathcal{O}({\bf r})\mathcal{O}^\dagger(d) \mathcal{P}_\text{gs} ~,
-\end{aligned}\end{equation}
-where \(\mathcal{O}^\dagger(d)\) is the hermitian conjugate of the correlation operator \(\mathcal{O}\), but applied on the impurity sites.
-This therefore constitutes a time-reversed scattering process on the impurity site relative to the process in the bath.
-The operator \(\mathcal{P}_\text{gs}\) projects onto the ground state of the auxiliary model, since we are interested in ground state correlations.
-The operator multiplying the old correlation operator represents all possible excitations of the impurity site, and ensure that the bath and impurity excitation processes take place coherently.
-The projector ensures that only tripartite correlations between the impurity site and the two momentum states are captured by the correlation, which is what's desired within the tiling method.
-
-With this modified operator, this class of correlation functions can be written as
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r} }\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-This can be interpreted as the fact that within our auxiliary model formalism, the correlation between the sites \({\bf r}\) and \({\bf \Delta + r}\) can only occur through a transition process that connect one of the sites with the impurity site and then a return process that connects the impurity site with the other site.
-
-\subsubsection{Inter-auxiliary model contributions: \({\bf r}^\prime \neq 0\)}
-These are the most non-local contributions, and involve excitations that connect different auxiliary models:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf \Delta}) \to \frac{1}{N}\sum_{{\bf r}^\prime \neq 0}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf r}^\prime\right) | \mathcal{\tilde O}({\bf \Delta} + {\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf r}) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-
-\subsection{Equal-Time Ground State Correlators: Momentum-space}
-We now consider momentum space correlations, through a general operator \(\mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1)\):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \braket{\Psi_\text{gs} | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-Note that \(\mathcal{O}\) itself is a two-particle operator.
-To obtain a tractable expression for this, we first replace the full ground state with its expression in terms of the auxiliary model ground states (eq.~\ref{groundstateProposal}):
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) = \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_2\right)  | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_1\right)}~,
-\end{aligned}\end{equation}
-where \({\bf r}_1\) and \({\bf r}_2 \) are the positions of the incoming and outgoing auxiliary model states.
-In order to convert the incoming and outgoing states into the same auxiliary mode at a reference location \({\bf r}_c\) (which would then allow computations purely within a single auxiliary model), we use the relation: \(\ket{\psi_\text{gs}\left({\bf x}\right)} = T^\dagger\left({\bf x} - {\bf r}_c\right)\psi_\text{gs}\ket{\psi\left({\bf r}_c \right)}\).
-Substituting this appropriately for both the auxiliary model states gives:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_c\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) T^\dagger\left({\bf r}_1 - {\bf r}_c\right) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-In order to simplify the translation operators, we can use eq.~\ref{translationOnField}.
-For that, we would need to know whether the operator \(\mathcal{O}\) involves a net transfer of momentum.
-If \(\mathcal{O}({\bf k})\) commutes with the total number operator \(n_{\bf k} = \sum_\sigma n_{{\bf k},\sigma}\), there is no momentum transfer.
-Examples of such operators are spin operators, \(S_{\alpha\beta}({\bf k}) \equiv c^\dagger_{{\bf k \alpha}}c_{{\bf k}\beta}\), and density operators \(n_{{\bf k}\alpha}\).
-If \(\mathcal{O}({\bf k})\) does not commute with \(n_{\bf k}\), there is a net transfer of momentum, and one such operator would be the charge isospin operator \(C^+({\bf k}) = c^\dagger_{{\bf k}\uparrow}c^\dagger_{{\bf k}\downarrow}\).
-For the first kind of operators, we have \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = \mathcal{O}({\bf k})\), while the for the latter, we get \(T({\bf a})\mathcal{O}({\bf k})T^\dagger({\bf a}) = e^{-{\bf a}\cdot{\bf 2k}}\mathcal{O}({\bf k})\), where \(2{\bf k}\) represents the momentum being transferred by the operator.
-We consider the two cases separately.
-
-\subsubsection{Momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] = 0\)}
-For these operators, the expression for the correlation gives
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}\\
-										 &=\sum_{{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-To obtain the last form, we defined \({\bf \Delta}={\bf r}_2 - {\bf r}_1\) as the distance between the incoming and outgoing auxiliary model states, and preformed the sum over the free variable \({\bf r}_1\) to cancel out the factor of \(1/N\).
-Just like before, this expression can be decomposed into a term that involves a single auxiliary model and other terms that involve two distinct auxiliary models.
-By making the identification of the right transition operator \(\mathcal{\tilde O}({\bf k}) = \mathcal{O}({\bf k})\mathcal{O}^\dagger(d)\mathcal{P}_\text{gs}\), we get
-\begin{equation}\begin{aligned}\label{kspaceCorrelation}
-C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \sum_{{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{\tilde O}({\bf k}_2) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-
-\subsubsection{Non-momentum-conserving operators: \(\left[\mathcal{O}({\bf k}), n_{{\bf k}}\right] \neq 0\)}
-This class of operators incur an additional phase factor of \(e^{-{\bf a}\cdot{\bf 2k}}\) when the translation operators are translated across them:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \frac{1}{N}\sum_{{\bf r}_1,{\bf r}_2}\braket{\psi_\text{gs}\left({\bf r}_c\right) | T\left({\bf r}_2 - {\bf r}_1\right) \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}e^{2i\left( {\bf r}_1 - {\bf r}_c \right) \cdot \left( {\bf k}_1 - {\bf k}_2 \right)} \\
-										 &= \delta_{{\bf k}_1, {\bf k}_2}\sum_{{\bf \Delta}}\braket{\psi_\text{gs}\left({\bf r}_c + {\bf \Delta}\right) | \mathcal{O}({\bf k}_2)\mathcal{O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-For this expression, we again defined \({\bf \Delta}\) similar to before, and carried out the sum of \({\bf r}_1\) involving the exponential to obtain a factor of \(N \delta_{{\bf k}_1, {\bf k}_2}\).
-The Kronecker delta factor is a manifestation of translational invariance and the associated total momentum conservation.
-
-As it stands, operators like \(\mathcal{O}({\bf k}_1)\) act purely on the conduction bath degrees of freedom.
-In order to incorporate impurity-bath correlation effects, we modify these operators using the appropriate \(T-\)matrices, by employing eq.~\ref{operatorTmatrix}.
-The final computations are carried out using these modified operators.
-
-\subsection{Entanglement Measures}
-We will now describe the prescription of calculating entanglement measures of the lattice model from within our auxiliary model treatment.
-In this section, we are interested mainly in two such measures, the entanglement entropy and the mutual information.
-Given a pure state \(\ket{\Psi}\) describing the complete system, the entanglement entropy \(S_\text{EE}(\nu)\) of a subsystem \(\nu\) quantifies the entanglement of \(\nu\) with the rest of the subsystem, and is defined as
-\begin{equation}\begin{aligned}
-	S_\text{EE}(\nu) = -\text{Tr}\left[\rho(\nu)\log \rho(\nu)\right],\quad \rho(\nu) = \text{Tr}_\nu\left[\ket{\Psi}\bra{\Psi}\right] 
-\end{aligned}\end{equation}
-where \(\text{Tr}\left[\cdot\right] \) is the trace operator, and \(\rho(\nu)\) is the reduced density matrix (RDM) for the subsystem \(\nu\) obtained by taking the partial trace \(\text{Tr}_\nu\) (over the states of \(\nu\)) of the full density matrix \(\rho = \ket{\Psi}\bra{\Psi}\).
-If the subsystem \(\nu\) describes local regions in real space (or states in \(k-\)space), we might be interested in the entanglement between two such subsystems \(\nu_1\) and \(\nu_2\).
-The correct measure to quantify such entanglement is the mutual information:
-\begin{equation}\begin{aligned}
-	I_2(\nu_1,\nu_2) = S_\text{EE}(\nu_1) + S_\text{EE}(\nu_2) - S_\text{EE}(\nu_1 \cup \nu_2)~,
-\end{aligned}\end{equation}
-where \(\nu_1 \cup \nu_2\) is a larger subsystem formed by combining \(\nu_1\) and \(\nu_2\).
-
-\subsubsection{Real-space entanglement}
-Real-space entanglement measures can be used to probe delocalisation-localisation transitions.
-The simplest such measure is the entanglement of a local mode.
-Since the local entanglement entropy will be uniform at each lattice site for a system with translation invariance, it suffices to calculate the real-space averaged entanglement entropy \(S_\text{EE}^\text{loc} = \frac{1}{N}\sum_{{\bf r}}S_\text{EE}\left( {\bf r} \right) \).
-By visualising the lattice model as a superposition of auxiliary models placed at various sites (eq.~\ref{tilingPrescriptionFinal}), the real space average of the lattice model can be thought of as an average over sites of a particular impurity model, and then a second average over all the impurity models.
-But since all all impurity models are equivalent to each other, the second average is redundant.
-Secondly, all correlations must derive from the impurity site, which can be formally encoded by subtracting, from this average, the corresponding contribution obtained in the absence of the impurity site.
-In total, the lattice-auxiliary model relation for the local entanglement entropy can be written as
-\begin{equation}\begin{aligned}
-	S_\text{EE}^\text{loc} = \frac{1}{N}\sum_{{\bf r}}\left[S_\text{EE}({\bf r}_d + {\bf r}) - S_\text{EE}^{(0)}({\bf r}_d + {\bf r})\right] ~,
-\end{aligned}\end{equation}
-where \({\bf r}_d\) is the impurity site position, \({\bf r}\) is the distance of a conduction bath site from the impurity site (can be zero), and \(S_\text{EE}({\bf r}_d + {\bf r})\) is the entanglement entropy, calculated within the impurity model, at the locatiom \({\bf r}_d + {\bf r}\).
-\(S^{(0)}_\text{EE}({\bf r}_d + {\bf r})\) is the same entanglement entropy, but calculated for an impurity model with vanishing impurity-bath hybridisation and bath interaction.
-
-\subsubsection{Momentum-space entanglement}
-Entanglement measures in \(k-\)space can provide valuable information regarding the Fermi surface structure and the nature of gapless excitations proximate to it.
-The most elementary measure is the entanglement entropy \(S_\text{EE}({\bf q})\) of a single excitation carrying momentum \({\bf q}\).
-Unlike \(S_\text{EE}^\text{loc}\), this does not involve an average, and involves a single computation:
-\begin{equation}\begin{aligned}
-	\tilde S_\text{EE}({\bf q}) = S_\text{EE}({\bf q}) - S_\text{EE}^{(0)}({\bf q})~.
-\end{aligned}\end{equation}
-It is possible to improve this by considering inter-auxiliary model contributions in the reduced density matrix \(\rho({\bf q})\). On the lattice model, \(\rho({\bf q})\) is defined as
-\begin{equation}\begin{aligned}\label{SEE-k}
-	\rho({\bf q}) = \text{Tr}_{\bf q}\left[\ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\right] ~,
-\end{aligned}\end{equation}
-where \(\text{Tr}_{\bf q}\left[\cdot\right]\) is the partial trace over the Hilbert space of \({\bf q}\), and \(\ket{\Psi_\text{gs}}\) is the tiled ground state.
-Using eq.~\ref{groundstateProposal}, we can write the ground state in terms of those of the auxiliary model.
-These leads to two classes of terms, one purely within a single auxiliary model ground state \(\ket{\psi_\text{gs}}\), and the other involving transitions across auxiliary models:
-\begin{equation}\begin{aligned}\label{RDMTiled}
-	\rho({\bf q}) \sim \text{Tr}_{\bf q}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d)}\right] + \frac{1}{N}\text{Tr}_{\bf q}\sum_{{\bf r}}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d + {\bf r})}\right]~,
-\end{aligned}\end{equation}
-where \(\ket{\psi_\text{gs}({\bf r}_d)}\) is a reference auxiliary model ground state, and \(\ket{\psi_\text{gs}({\bf r}_d + {\bf r})}\) sums over other auxiliary models at increasing distances from this reference model.
-The \(\sim\) indicates that the RDM needs to be normalised.
-The first term leads to the expression in eq.~\ref{SEE-k}, while the second term can be used to improve this estimate.
-Away from any quantum critical points, the localised nature of the impurity-bath hybridisation ensures that impurity correlations decay exponentially away from the transition.
-This ensures that the second term is very small away from a critical point.
-We therefore restrict ourselves to just the first term in the present work.
-
-\section{Extending the Anderson Model To a Lattice-Embedded Impurity Model}
-Crucial to our method is the choice of an impurity auxiliary model that is able to capture important aspects of the lattice model in a local sense.
-Some of us have shown in a previous work~\cite{Mukherjee_2023} that almost all aspects of the Mott metal-insulator transition on the infinite dimensional Hubbard model on the Bethe lattice (as seen, for example, from dynamical mean-field theory~\cite{georges1996}) can be captured from a simple extension of the Anderson impurity model (eSIAM).
-The extension involves including a local attractive interacting \(W\) on the conduction bath site coupled to the impurity site; by tuning the ratio of \(|W|\) and the Kondo coupling \(J\), we obtained an impurity phase transition from a screened phase to an unscreened local moment phase.
-Since the impurity site of the auxiliary model is a representative of each correlated site on the lattice, the mapping to the lattice model then involves identifying the locally gapless impurity phase with the bulk gapless of the lattice model.
-In other words, the ability of the impurity site to participate in low-energy excitations corresponds to the ability of an electron, within the lattice model, to delocalise from one site into the rest of the lattice.
-In the same vein, a local moment phase of the impurity model maps to a gapped Mott insulating phase on the lattice model, where there's a charge gap to electron hopping processes.
-
-In the present work, the goal is to tackle interacting fermions on a 2D square lattice, which makes it important for us to incorporate the effects of the lattice within the impurity model.
-More specifically, while the impurity-bath interactions on the infinite dimensional Bethe lattice are \(s-\)wave symmetric, that is not a realistic form for a 2D lattice.
-To make a realistic impurity model, we embed the impurity site into the lattice of a 2D conduction bath, and lower the \(s-\)wave symmetry of the interactions down to the \(C_4\) symmetry of the 2D square lattice.
-A general structure of such a model is shown in fig.~\ref{embeddedEsiam}; one of the sites of the 2D square lattice is identified as the impurity (red), while the four nearest-neghbours (navy blue) interact directly with this impurity site through a \(C_4\)-symmetric interaction.
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.2\textwidth]{pWaveEsiam.pdf}
-	\caption{General structure of an embedded extended SIAM, where the impurity site is a part of the 2D square lattice.
-The four nearest-neghbour sites (dark blue) interact with the impurity site through one or more processes, and can host local interactions.
-The other lattice sites (light blue) are completely non-interacting.}
-	\label{embeddedEsiam}
-\end{figure}
-\subsection{Hamiltonian}
-We consider an impurity spin \(\vec S_d\) interacting with a two-dimensional tight-binding conduction bath through a highly localised interaction, described by the Hamiltonian
-\begin{equation}\begin{aligned}
-	\mathcal{H} = H_\text{cbath} + H_\text{imp-cbath} + H_\text{cbath-int}~,
-\end{aligned}\end{equation}
-where \(H_\text{cbath}\) is the kinetic energy arising out of nearest-neighbour hopping processes,
-\begin{equation}\begin{aligned}
-	H_\text{cbath} = -2t\sum_{{\bf k}}\left[\cos(ak_x) + \cos(ak_y)\right] c^\dagger_{{\bf k},\sigma}c_{{\bf k},\sigma}~.
-\end{aligned}\end{equation}
-For the impurity-bath interaction \(H_\text{imp-cbath}\) and the local interaction \(H_\text{cbath-int}\) in the bath, we take the simplest choices consistent with the 2D square lattice geometry:
-\begin{equation}\begin{aligned}
-	H_\text{imp-cbath} &=\frac{1}{2} J\sum_{\sigma_1,\sigma_2}\sum_{Z} {\bf S}_d\cdot c^\dagger_{Z\sigma_1}{\boldsymbol \tau}_{\sigma_1,\sigma_2} c_{Z\sigma_2}~,\\
-	H_\text{cbath-int} &= -\frac{W}{2}\sum_{Z} \left(n_{Z\uparrow} - n_{Z\downarrow}\right)^2 ~,
-\end{aligned}\end{equation}
-where \(Z\) sums over all nearest-neighbour sites of the impurity site (navy blue circles in Fig.~\ref{embeddedEsiam}, henceforth referred to as bath zeroth sites).
-The impurity interacts with the bath zeroth sites in \(H_\text{imp-cbath}\) through four local Kondo terms, of uniform strength.
-The other term \(H_\text{cbath-int}\) represents local Hubbard interactions on the four zeroth sites, again of uniform strength.
-
-The 2D structure of the impurity model and its distinction from the infinite-dimensional counterpart becomes apparent once we transform the Hamiltonian to momentum space:
-\begin{equation}\begin{aligned}
-	J_{{\bf k}, {\bf k}^\prime} &= \frac{J}{2}\left[\cos\left({\bf k}_x - {\bf k}^\prime_x\right) + \cos\left({\bf k}_y - {\bf k}^\prime_y\right)\right] ~,\\
-	W_{{\bf k}, {\bf k}^\prime,{\bf q}, {\bf q}^\prime} &= W\left[\cos\left({\bf k}_x - {\bf k}^\prime_x + {\bf q}_x - {\bf q}^\prime_x\right) + \cos\left({\bf k}_y - {\bf k}^\prime_y + {\bf q}_y - {\bf q}^\prime_y\right)\right] ~.
-\end{aligned}\end{equation}
-where the subscripts \(x\) and \(y\) represent components of the momenta vector.
-This form shows that the Kondo coupling is no longer independent of the exchange momentum, and encodes information of the lattice geometry in it.
+\section{Derivation of unitary RG equations for the lattice-embedded impurity model}
 
 \subsection{The unitary renormalisation group method}
-In order to obtain the various low-energy phases of our impurity model, we perform a scaling analysis of the associated Hamiltonian using the recently developed unitary renormalisation group (URG) method \cite{anirbanurg1,anirbanurg2}.
-The method has been applied successfully on a wide variety of problems of correlated fermions~\cite{santanukagome,1dhubjhep,anirbanmott2,anirbanmott1,siddharthacpi,anirban_kondo,Patra_2023,anirbanurg1,anirbanurg2}.
+In order to obtain the various low-energy phases of our impurity model, we perform a scaling analysis of the associated Hamiltonian using the recently developed unitary renormalisation group (URG) method ~[24,42,43].
+%\cite{anirbanurg1,anirbanurg2}. 
+The method has been applied successfully on a wide variety of problems of correlated fermions~\cite{santanukagome,1dhubjhep1,anirbanmott1,siddharthacpi,anirban_kondo,Patra_2023}.
 The method proceeds by resolving quantum fluctuations in high-energy degrees of freedom, leading to a low-energy Hamiltonian with renormalised couplings and new emergent degrees of freedom.
@@
 The momentum states lying on shells \(E_N\) that are far away from the Fermi surface comprise the UV states, while those on shells near the Fermi surface comprise the IR states.
-This scheme is shown in Fig.~\eqref{zeromode-bare}.
-
-\begin{figure}[!htb]
-	\includegraphics[width=0.3\textwidth]{urgScheme.pdf}
-	\caption{High energy - low energy scheme defined and used in the URG method.
-The states away from the Fermi surface (\(E_N\) in the figure) form the UV subspace and are decoupled first, leading to a Hamiltonian which is more block-diagonal and comprised of only the IR states near the Fermi surface (\(E_0\) in the figure).}
-	\label{zeromode-bare}
-\end{figure}
 
 As a result of the URG transformations, the Hamiltonian \(H_{(j)}\) at a given RG step \(j\) involves scattering processes between the \(k-\)states that have energies lower than \(D_{(j+1)}\).
-The unitary transformation \(U_{(j)}\) is then defined so as to remove the number fluctuations of the currently most energetic set of states \(D_{(j)}\)~\cite{anirbanurg1,anirbanurg2}:
+The unitary transformation \(U_{(j)}\) is then defined so as to remove the number fluctuations of the currently most energetic set of states \(D_{(j)}\)~[42,43]:
+%\cite{anirbanurg1,anirbanurg2}:
 \begin{eqnarray}
@@
 
-The unitary transformations can be expressed in terms of a generator \(\eta_{(j)}\) that has fermionic algebra~\cite{anirbanurg1,anirbanurg2}:
+The unitary transformations can be expressed in terms of a generator \(\eta_{(j)}\) that has fermionic algebra~[42,43]:
+%\cite{anirbanurg1,anirbanurg2}:
 \begin{eqnarray}
@@
 The unitary operator \(U_{(j)}\) that appears in Eq.~\eqref{unitary} can be cast into the well-known general form \(U = e^\mathcal{S}, \mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger_{(j)} - \eta_{(j)} \right)\) that a unitary operator can take, defined by an anti-Hermitian operator \(\mathcal{S}\).
-The generator \(\eta_{(j)}\) is given by the expression~\cite{anirbanurg1,anirbanurg2}
+The generator \(\eta_{(j)}\) is given by the expression~[42,43]:
+%\cite{anirbanurg1,anirbanurg2}
 \begin{eqnarray}
@@
 The RG flow continues up to energy \(D^*\), where a fixed point is reached from the vanishing of the RG function.
-Detailed comparisons of the URG with other methods (e.g., the functional RG, spectrum bifurcation RG etc.) can be found in Refs.~\cite{anirbanmott1,anirbanurg1}.
-
-\subsection{Unitary RG analysis of the embedded eSIAM}
-We studied the low-energy physics of this model through a unitary renormalisation group calculation that decouples the high-energy modes of the conduction bath and incorporates their effects in the form of renormalised Hamiltonian couplings.
-We find that the bath interaction \(W\) remains marginal (does not undergo any renormalisation), while the renormalisation in the momentum-resolved Kondo coupling \(J^{(j)}\) at the \(j^\text{th}\) step is of the form
-\begin{equation}\begin{aligned}\label{KondoRGequation}
-	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}~,
-\end{aligned}\end{equation}
-where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, and the sum is over all momentum states \({\bf q}\) in the particle sector (PS) of the shell \(\varepsilon_j\) (that is, all states that are occupied at \(T=0\) and in the absence of any quantum fluctuations).
-The Kondo coupling and the RG equation as well have certain symmetries under transformations in the Brillouin zone.
-If any one of the momenta \({\bf k}_1\) or \({\bf k}_2\) are translated by \(\pi\) (\(k_{1x} \to k_{1x} + \pi, k_{1y} \to k_{1y}+\pi\)), the coupling as well as the RG equation changes sign.
-Translating both the momenta leads to the reversal of the sign change.
-\begin{equation}\begin{aligned}\label{hamiltonanSymms}
-	\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2} = \Delta J^{(j)}_{{\bf k}_1, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2}~.
-\end{aligned}\end{equation}
-These transformations involve translating one or both momenta through the center of the Brillouin zone.
-
-With our chosen momentum-space dependence of the Kondo coupling and bath interaction, the form of the Kondo coupling morphs during the RG flow, allowing the emergence of new degrees of freedom that screen the impurity at low-energies.
-At the first step, the RG equation can be written down explicitly as
-\begin{equation}\begin{aligned}
-	&\Delta J^{(0)}_{{\bf k}, {\bf k}^\prime} = -\sum_{{\bf q} \in \text{PS}} \frac{J^2 \frac{1}{2}\sum_a\cos\left({\bf k}^\prime_a - {\bf q}_a\right)\frac{1}{2}\sum_a\cos\left({\bf q}_a - {\bf k}_a\right) - 2JW \sum_a\cos\left({\bf k}^\prime_a - {\bf k}_a\right)}{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{4}}~,
-\end{aligned}\end{equation}
-where \(a\) sums over the \(x\) and \(y\) components of the momenta.
-We see that unlike the bare Kondo coupling \(J_{{\bf k}, {\bf k}^\prime}\) that depends only on the momentum difference \({\bf k} - {\bf k}^\prime\), the renormalisation \(\Delta J^{(0)}\) depends on products of the momenta.
-This shows the form of the Kondo coupling continuously changes under renormalisation.
-
-\section{Low-energy description of the embedded eSIAM}
-\subsection{Zero temperature phase diagram and impurity site dynamics}
-The ground state phase diagram of the impurity model is shown in the left panel of Fig.~\ref{phaseDiagram}.
-We find that upon tuning the ratio \(W/J\) of the bath interaction strength \(W\) and the Kondo coupling \(J\), the impurity site undergoes a transition from a screened paramagnetic phase (dark green) to an unscreened local moment phase (yellow), through an intermediate pseudogapped regime (pink).
-The nature of pseudogapped phase will be clarified in the upcoming sections.
-The phase transition is seen through the evolution of the local spectral function (middle panel of Fig.~\ref{phaseDiagram}); increasing the ratio \(W/J\) leads to the sharpening of the central Kondo resonance, indicating that the local Fermi liquid excitations are becoming poorer.
-At the transition, the extremely sharp peak disappears and we are left with a hard gap at zero frequency.
-A complimentary picture is painted by the imaginary part \(\Sigma^{\prime\prime}\) of the impurity self-energy.
-The poles in \(\Sigma^{\prime\prime}\) are the edges of the central Kondo resonance, and its sharpening leads to the coalescing of the poles.
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.32\textwidth]{phaseDiagram.pdf}
-	\includegraphics[width=0.32\textwidth]{impSpecFunc_49-1000.pdf}
-	\includegraphics[width=0.32\textwidth]{sigmaImag_49-1000.pdf}
-	\caption{{\bf Left}: Zero temperature phase diagram of the embedded impurity model, obtained by tracking impurity-bath spin correlations.
-The pink phase is characterised by perfect Kondo screening and local Fermi liquid excitations (L-FL), leading to non-zero spin-correlations all over the Fermi surface of the conduction electrons.
-The red phase is a local pseudogap (L-PG)  phase, where a part of the Fermi surface (starting from the antinodal regions) no longer participates in Kondo screening.
-This leads to "Fermi arc"-like behaviour in the spin-correlations and the \(k-\)space density of states.
-The black phase is a local moment (LM) phase, where the impurity is completely decoupled from the conduction electrons.
-{\bf Middle}: Local spectral function of the impurity site.
-The blue curve is the normal Kondo resonance in the absence of any bath interaction.
-The yellow and green curves show the sharpening the spectral function through the locally pseudogapped phase, as momentum states are expelled from the Kondo cloud.
-The final pink curve shows the charge gap in the local moment phase.
-{\bf Right:} Imaginary part of impurity self-energy.
-Poles represent the beginning of the optical gap between the central Kondo resonance and the Hubbard sidebands.
-Increasing the bath interaction leads to the coalescing of the poles (due to the sharpening of the Kondo resonance), ultimately leading to a zero frequency pole  in the local moment phase.}
-	\label{phaseDiagram}
-\end{figure}
-
-\subsection{Presence of a local pseuodogapping transition with electronic differentiation in momentum space}
-We now discuss the intervening pseudogapped regime (pink region) of the phase diagram.
-We find that the process of Kondo breakdown in our model occurs anisotropically in our model - the transition starts through the removal, from the Kondo cloud, of the antinodal points of the conduction bath Fermi surface.
-This is followed by the sequential removal of points away from the antinodes, with the nodal points being removed at the very end.
-This electronic differentiation is a novel feature of this model that arises because of the more realistic embedding of the impurity site into the conduction bath lattice.
-
-We quantify the removal of these points by the vanishing (up to a tolerance) of the average renormalised scattering probability 
-\begin{equation}\begin{aligned}
-	\Gamma^*({\bf k}) = \sum_{{\bf q} < \Lambda^*} \left(J^*_{{\bf k}, {\bf q}}\right)^2~,
-\end{aligned}\end{equation}
-where the other momentum \({\bf q}\) is summed over all the momentum states that reside within the fixed point window.
-The quantity \(\Gamma({\bf k})\) therefore quantifies the degree to which the state \({\bf k}\) is participating in screening the impurity at low energies.
-The \(k-\)space forms of this quantity at various values of \(W/J\) is shown in fig.~\ref{gamma_kxky}, and the difference in the behaviour of the nodal and antinodel points is apparent.
-
-\begin{figure}[!htpb]
-	\centering
-	\includegraphics[width=0.23\textwidth]{scattProb-1.pdf}
-	\includegraphics[width=0.23\textwidth]{scattProb-3.pdf}
-	\includegraphics[width=0.23\textwidth]{scattProb-4.pdf}
-	\includegraphics[width=0.23\textwidth]{scattProb-5.pdf}
-	\caption{Variation of the total scattering probability \(\Gamma({\bf k})\) (defined in the main text) as \(W/J\) is increased from left to right.
-Each plot shows whether \(\Gamma({\bf k})\) is RG-relevant (pink) or irrelevant (black).
-RG-relevant values of \(\Gamma({\bf k})\) indicate that the \(k-\)point participates in Kondo screening at low-energies, while an irrelevant value indicates that the \(k-\)point is decoupled from the impurity site.
-As \(W/J\) is made more negative, the antinodal points are the first state to be removed from the Kondo cloud, while the node is the last to be removed.}
-	\label{gamma_kxky}
-\end{figure}
-
-\subsection{Spin-correlations across the pseudogap}
-In figure ~\ref{spinCorr}, we show the evolution of the spin-spin correlation \(\chi_s(d,\vec k) = \left<{\bf S_d}\cdot{\bf S}_{\vec k}\right>\) in \(k-\)space, as the system is tuned through the pseudogap.
-At vanishing value of the interaction \(W\), the spin correlations are concentrated around the antinode, because of the \(p-\)wave nature of the Kondo interaction.
-At the entry into the pseudogap, the correlations become more pronounced near the nodes and become suppressed near the antinodes, signalling that the latter parts will gap out first.
-The last three figures \((W/J=-1.74, -1.83, -1.84)\) show how \(k-\)points starting from the antinode progressively exit the Kondo cloud, the node being the last to decouple from the impurity.
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.23\textwidth]{SF-1.pdf}
-	\includegraphics[width=0.23\textwidth]{SF-2.pdf}
-	\includegraphics[width=0.23\textwidth]{SF-3.pdf}
-	\includegraphics[width=0.23\textwidth]{SF-4.pdf}
-	\caption{\(k-\)space distribution of spin-spin correlation \(\chi_s(d,\vec k)\) (defined in the main text).
-The last three figures show how \(k-\)points starting from the antinode progressively exit the Kondo cloud, the node being the last \(k-\)point to decouple from the impurity.}
-	\label{spinCorr}
-\end{figure}
-
-\subsection{Charge correlations}
-In order to study the mechanism behind the destabilisation of the Kondo cloud through the pseudogap, we calculate the \(k-\)space double occupancy \(\left<n_{\vec k \uparrow} n_{\vec k \downarrow}\right>\) and \(k-\)space charge-transfer correlation \(\chi_c(\vec k, \vec q) = \left<c^\dagger_{\vec k \uparrow} c^\dagger_{\vec k \downarrow} c_{\vec q \downarrow}c_{\vec q \uparrow}\right>\) (Fig.~\ref{cfnode}).
-We find that the entry into the pseudogap is marked by an increase of doubly-occupied states near the antinode in comparison to \(W=0\).
-These pairs likely lead to the concomitant vanishing of spin-correlations near the antinode at the same value of \(W\), as seen in Fig.~\ref{spinCorr}.
-More insight on the nature of these correlations are obtained from the fluctuations \(\chi_c(\vec k, \vec q)\) starting from the node \((\vec q = k_\text{N})\) and antinode \(\left( \vec q = k_\text{AN}\right) \).
-Interestingly, we find strong pair-transfer interactions between the node and antinode.
-Within the pseudogap, this leads to charge-isospin flip correlations between the decoupled antinodal region and the still-coupled nodal region.
-\begin{figure}[!htpb]
-	\centering
-	\includegraphics[width=0.23\textwidth]{cfnode-1.pdf}
-	\includegraphics[width=0.23\textwidth]{cfnode-2.pdf}
-	\includegraphics[width=0.23\textwidth]{cfantinode-1.pdf}
-	\includegraphics[width=0.23\textwidth]{cfantinode-2.pdf}
-	\caption{{\it Top panels}: Distribution of double occupancy at \(W=0\) and \(W=-1.74\) (entry into the pseudogap).
-While the double occupancy is concentrated near the nodes at \(W=0\), it rises near the antinodes at the start of the pseudogap, signalling its destabilisation.
-{\it Bottom panels}: Charge-transfer correlation \(\chi_c\) (defined in main text) starting from antinode (left) and node (right), at the beginning of the pseudogap phase.
-Strong node-antinode correlations are clearly visible.}
-	\label{cfnode}
-\end{figure}
-
-\section{Nature of Gapless Excitations in the Impurity Pseudogap}
-\subsection{Emergence of a two-channel Kondo Model}\label{2CKEmerge}
-As the bath interaction \(W\) is tuned through the L-PG phase, the four nodal points in the Brillouin zone are the last to decouple from the impurity.
-This allows us to write down a simpler Kondo model near the transition, focusing on scattering processes involving the nodal region.
-Specifically, for the Kondo term \(J_{{\bf k}_1, {\bf k}_2})\), we find that only the following classes of scattering processes survive close to the critical point:
-\begin{itemize}
-	\item Both momenta in a neighbourhood around \({\bf k}_N\), where \({\bf k}_N\) can be any of the four nodal points,
-	\item One momentum from the neighbourhood around \({\bf k}_N\), while the other from the neighbourhood around \({\bf k}_N + \left( \pi, \pi \right) \)~.
-\end{itemize}
-The second class is tied to the first through a symmetry of the Hamiltonian (eq.~\ref{hamiltonanSymms}).
-The crucial feature of these processes is that each node only interacts with the other node directly opposite to it across the origin.
-That is, \(\left(\pi/2, \pi/2\right) \) and \(\left(-\pi/2, -\pi/2\right) \) only interact between themselves, while \(\left(\pi/2, -\pi/2\right) \) and \(\left(-\pi/2, \pi/2\right) \) form their own pair of connected regions.
-
-Let \(S^\pm\) be the set of momentum states in a small window around nodes along \(k_x = \pm k_y\).
-As discussed immediately above, the Kondo spin-exchange term close to the transition does not lead to scattering of any \(k-\)state from \(S^+\) to \(S^-\).
-This is verified by calculating the ratio \(\text{max}\left\{ J_{k^+_1, k^-_2} \right\} / \text{max}\left\{ J_{k^+_1, k^+_2} \right\}\), where the maximum in the numerator is calculated from all the low-energy (fixed point) Kondo scattering processes that connect the two sets \(S^\pm\), while the denominator maximum is from within the set \(S^+\).
-This ratio vanishes (left panel of Fig.~\ref{channelDecoupling}) within the local pseudogap regime, indicating that no direct Kondo scattering process persists between the two sectors \(S^\pm\) at low energies, deep within the pseudogap regime.
-We call the value of \(W\) at which this ratio vanishes \(W^*\).
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.45\textwidth]{quadrantMaxKondo-49.pdf}
-	\includegraphics[width=0.45\textwidth]{localQPResidue.pdf}
-	\caption{Left: Ratio between the maximum values of the fixed point values of the Kondo couplings for scattering processes between and within the regions \(S^+\) and \(S^-\).
-The vanishing of the fixed point ratio indicates that the pseudogap regime features a singular low-energy effective theory, where the Fermi surface neighbourhood splits into two disconnected regions with no explicit term in the Hamiltonian connecting them directly.
-Right: The quasiparticle residue \(Z_\text{imp}\) of the local gapless excitations in various regions.
-The vanishingly small values of \(Z_\text{imp}\) lend more support to the two-channel (and hence the non-Fermi liquid) nature of the low-energy physics in the pseudogap regime.}
-	\label{channelDecoupling}
-\end{figure}
-
-The decoupling of the \(k-\)space regions \(S^\pm\) is captured by the following simplified low-energy Hamiltonian:
-\begin{equation}\begin{aligned}\label{twoChannel}
-H_\text{eff} = H(S^+) + H(S^-);~H(S) = \sum_{{\bf q}\in S,\sigma}\varepsilon_{\bf q}c^\dagger_{{\bf q}\sigma}c_{{\bf q}\sigma} + \sum_{{\bf q}_1\in S,{\bf q}_2\in S}\sum_{\alpha,\beta}J^*({\bf q}_1,{\bf q}_2){\bf S}_d\cdot {\bf \sigma}_{\alpha\beta}c^\dagger_{{\bf q}_1\alpha}c_{{\bf q}_2\beta}~,
-\end{aligned}\end{equation}
-where \(H(S^\pm)\) represents the dynamics of momentum states residing in regions \(S^\pm\).
-The only source of information transfer between the two regions is the fact that they interact with the same impurity local moment.
-Eq.\ref{twoChannel} tells us that the low-energy dynamics of the embedded eSIAM close to the Kondo-breakdown transition is governed by an emergent {\bf two-channel Kondo model}, with the conduction bath states in the sets \(S^\pm\) making up the two channels.
-
-\subsection{Non-Fermi liquid behaviour in the pseudogap}\label{marginalFL}
-It is well-known that the two-channel Kondo model hosts non-Fermi liquid excitations at low-energies~\cite{Tsvelick_weigmann_mchannel_1985,emery_kivelson}; that this also happens in the present model is corroborated by our calculations of the quasiparticle residue \(Z_\text{imp}\) for the local gapless excitations.
-For a single-particle Greens function of an interacting model, the quasiparticle residue \(Z\) is defined as the spectral weight of low-energy resonance within the spectral function:
-\begin{equation}\begin{aligned}
-	G_k = \frac{Z}{\omega - \varepsilon_k - i \Sigma^{\prime\prime}} + G_\text{incoh}~,\quad 1/Z = 1- \frac{d \Sigma^{\prime}}{d\omega}~,
-\end{aligned}\end{equation}
-where \(\Sigma^\prime\) and \(\Sigma^{\prime\prime}\) are the real and imaginary parts of the self-energy, and \(G_\text{incoh}\) is contribution to the Greens function arising from incoherent short-lived excitations as well as high-energy features that are decoupled from the low-energy excitations~\cite{varma-physrevlett.63.1996}.
-Small values of \(Z\) indicate that the excitations cannot be described in terms of a Fermi liquid theory.
-Indeed, as shown in the right panel of Fig.~\ref{channelDecoupling}, the quasiparticle residue \(Z_\text{imp}\) of the impurity excitations becomes vanishingly small in the pseudogap region, signalling that the excitations are of a non-Fermi liquid nature.
-Given that the pseudogap phase is close to a critical point in the impurity model phase diagram (separating the local Fermi liquid and local moment phases), it is not surprising that a quantum critical model emerges at that point.
-
-Coleman and Ioffe have shown that by mapping the two-channel Kondo problem to a ``compactified" form where the impurity spin hybridises with the spin and isospin degrees of freedom of a single conduction channel, the impurity self-energy can be shown to display marginal Fermi liquid behaviour~\cite{Coleman_tsvelik,Schofield1997}:
-\begin{equation}\begin{aligned}
-	\Sigma \propto \omega \ln \omega~.
-\end{aligned}\end{equation}
-Some of us have shown in a previous work~\cite{Patra2023MCK} that this can also be obtained from a renormalisation group calculation of the low-energy excitations of the two-channel overscreened fixed point.
-For the sake of completeness, we have reproduced the calculation in Appendix~\ref{mflDerivation}.
-
-\subsection{Emergence of long-ranged interactions near the NFL-Mott insulator transition}\label{hkmEmerge}
-We will now obtain a low-energy Hamiltonian for the excitations very close to the transition, where the Kondo coupling is about to turn irrelevant.
-In order to do this, we carry out a perturbation-theoretic treatment of the fixed point Hamiltonian in this region of the phase diagram, by considering the effects of a small fixed point Kondo scattering probability \(J^*\) in the backdrop of a larger bath interaction parameter \(W\).
-We note that this is in contrast to the state of affairs that gave rise to the marginal Fermi liquid excitations in Subsection ~\ref{marginalFL}, where the Kondo coupling fixed the ground state and the conduction bath hopping processes led to the low-energy excitations; it is this contrast that leads to the emergence of a new effective Hamiltonian close to the transition.
-
-The complete Hamiltonian (details described in Appendix~\ref{hkmDerivation}) is
-\begin{equation}\begin{aligned}
-	\Delta \tilde H = \sum_{{\bf q}, \sigma}\text{sign}\left(\varepsilon_{{\bf N}_1 + {\bf q}}\right)\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W} r_{{\bf q},\sigma} + \sum_{{\bf q}_1,{\bf q}_2, \sigma}\frac{{J^*}^2}{-4W}\left[r_{{\bf q}_1 \sigma} \left(1 - r_{{\bf q}_2 \bar\sigma}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\bar\sigma}\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2, \sigma}\phi_{{\bf q}_2, \bar\sigma}\right]~,
-\end{aligned}\end{equation}
-where the fermionic operator \(\phi_{{\bf q}, \sigma}\) defines emergent relative modes,
-\begin{equation}\begin{aligned}
-	\phi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} - c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~,
-\end{aligned}\end{equation}
-that are shifted by an excitation momentum \({\bf q}\) away from the nodal point \({\bf N}_1 = \left(\pi/2, \pi/2\right)\) and its nested partner \({\bf N}_1 + {\bf Q}_1 = \left(-\pi/2, -\pi/2\right)\).
-The number operator \(r_{{\bf q} \sigma}\) is defined as \(r_{{\bf q} \sigma} = \phi_{{\bf q}, \sigma}\dagger \phi_{{\bf q}, \sigma}\).
-\(\varepsilon_{{\bf N}_1 + {\bf q}}\) represents the non-interacting kinetic energy of the conduction bath.
-
-In order to extract the singular, critical part of the Hamiltonian, we focus on the \({\bf q}_1 = {\bf q}_2\) forward scattering processes:
-\begin{equation}\begin{aligned}\label{HKModel}
-	\Delta \tilde H_{{\bf q}_1 = {\bf q}_2} = \sum_{{\bf q},\sigma}\epsilon_{{\bf q}}{r}_{{\bf q},\sigma} + u\sum_{{\bf q}, \sigma}r_{{\bf q} \sigma} r_{{\bf q} \bar\sigma}
-\end{aligned}\end{equation}
-where \(\epsilon_{\bf q}\) and \(u\) are emergent energy scales:
-\begin{equation}\begin{aligned}
-	\epsilon_{\bf q} = \text{sign}\left(\varepsilon_{{\bf N}_1 + {\bf q}}\right)\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W} + \frac{{J^*}^2}{-4W},~u = \frac{{J^*}^2}{4W}~.
-\end{aligned}\end{equation}
-Eq.~\ref{HKModel} describes a Hatsugai-Kohmoto model~\cite{Baskaran1991,Hatsugai1992}, an exactly solvable model of correlated electrons; by tuning the ratio of the interaction strength \(u\) and the bandwidth \(w\), the model describes a transition between a non-Fermi liquid and a Mott insulator.
-The non-Fermi liquid nature of the gapless excitations in the metallic phase of the model manifests in the form of a divergent one-particle self-energy at the non-interacting Fermi surface~\cite{Phillips2020}:
-\begin{equation}\begin{aligned}
-	\Sigma_{{\bf q}}(\omega) = -\frac{u^2/4}{\omega - \epsilon_{\bf q}}, ~\Sigma_{\epsilon_{\bf q}=0}(\omega \to 0)  \to \infty~.
-\end{aligned}\end{equation}
-Beyond the transition and inside the Mott insulating phase, this zero frequency pole continues to exist and marks the hard gap in the spectral function for charge excitations.
-
-\section{Journey Through the Pseudogap on The Lattice model: Spectral Function, Spin Correlations and Entanglement}
-Having studied the phase diagram of the lattice-embdedded impurity model, we now proceed to translate our results into the translation-invariant lattice model.
-For this, we use the results that we obtained in Sec.~\ref{tilingProcedure}.
-In particular, we focus in this section on the implications of the impurity model pseudogap phase on the lattice model.
-We find that the anistropic decoupling, from the impurity dynamics, of the conduction bath low-energy states leads to the formation of a partially gapped Fermi surface in the correlated model.
-The partial gapping is signalled by the replacement of Greens function poles with zeroes in the antinodal region.
-
-\subsection{\(k-\)space spectral function and self-energy}
-The primary indicator of the pseudogapping nature of the transition is of course the \(k-\)space density of states or the spectral function \(\tilde A_{\bf k}(\omega)\).
-We calculate \(\tilde A_{\bf k}(\omega)\) from the impurity-bath spectral function computations carried out for the impurity model, using the following expression that was obtained previously (eq.~\ref{kspaceGreensFunction}):
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; \omega) = G^>(\mathcal{T}^\dagger_{{\bf K}\sigma}, \omega - \varepsilon_{{\bf K}}) + G^<(\mathcal{T}^\dagger_{{\bf K}\sigma}, \omega + \varepsilon_{{\bf K}})~,
-\end{aligned}\end{equation}
-where \(\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\left(\sum_{\sigma^\prime}c^\dagger_{d\sigma} + \text{h.c.}\right) + c_{{\bf K}\sigma}\left(S_d^+ + \text{h.c.}\right)\) was defined in eq.~\ref{tmatrix}, and \(G^>(\mathcal{O}^\dagger, t) = -i\braket{\mathcal{O}(t)\mathcal{O}^\dagger}\) and \(G^<(\mathcal{O}^\dagger, t) = -i\braket{\mathcal{O}^\dagger\mathcal{O}(t)}\) are the greater and lesser Greens function for the auxiliary model, and \(\varepsilon_{{\bf K}}\) is the excitation energy associated with the momentum state \({\bf K}\), as determined by the dispersion on the lattice.
-In order to determine the low-energy behaviour in \(k-\)space, the zero frequency value \(\tilde A_{\bf k}(\omega \simeq 0)\) of the spectral function on the Fermi surface points is shown in Fig.~\ref{tiledSpecFunc} for various values of \(W/J\).
-
-We find that the Fermi surface remains completely gapless (seen through large non-zero values at zero frequency) for small values of \(W\) (first plot).
-However, if \(W\) is made sufficiently large, a partial gap opens up on the Fermi surface, starting from the antinode.
-Increasing the value of \(W/J\) leads to enlargement of the gapped region; exactly at the transition, we end up with a singular Fermi surface composed of just the nodal points.
-
-In order to better understand the nature of the metal in the partially gapped region, we have also calculated the \(k-\)space self-energy \(\tilde \Sigma({\bf k}(\omega)\), using Dyson's equation:
-\begin{equation}\begin{aligned}
-	\tilde \Sigma({\bf k}(\omega) = 1/\tilde G^{(0)}_{\bf k}(\omega) - 1/\tilde G_{\bf k}(\omega)~,
-\end{aligned}\end{equation}
-where \(\tilde G_k\) is the interacting \(k-\)space Greens function (whose spectral function is shown in Fig.~\ref{tiledSpecFunc}) while \(\tilde G_k^{(0)}\) is the non-interacting \(W=0\) Greens function.
-We show the zero frequency value of the self-energy in Fig.~\ref{selfenergy}, and the partial gapping of the Fermi surface is seen to arise from the appearance of poles in the self-energy at the antinodal region.
-As the partial gap expands, more and more \(k-\)space points exhibit poles in their self-energy.
-This, along with the behaviour of the spectral function, indicates that in the pseudogap region, the disconnected Fermi surface coexists with a Luttinger surface.
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.23\textwidth]{kspaceDOS-1.pdf}
-	\includegraphics[width=0.23\textwidth]{kspaceDOS-2.pdf}
-	\includegraphics[width=0.23\textwidth]{kspaceDOS-3.pdf}
-	\includegraphics[width=0.23\textwidth]{kspaceDOS-4.pdf}
-	\caption{One-particle \(k-\)space spectral function.
-In the absence of bath interactions, all points on Fermi surface are gapless (first panel).
-Proceeding through the pseudogap results in the gapping out of Fermi surface points starting from the antinode (second panel) and approaching the node (third panel), until finally only the node remains at the critical point (fourth panel).}
-	\label{tiledSpecFunc}
-\end{figure}
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.23\textwidth]{selfEnergyKspace-1.pdf}
-	\includegraphics[width=0.23\textwidth]{selfEnergyKspace-2.pdf}
-	\includegraphics[width=0.23\textwidth]{selfEnergyKspace-3.pdf}
-	\includegraphics[width=0.23\textwidth]{selfEnergyKspace-4.pdf}
-	\caption{\(k-\)space self-energy.
-For \(W=0\), the self-energy is vanishingly small, leading to a Fermi liquid phase described by well-defined quasiparticles.
-Inside the pseudogap, the self-energy diverges near the antinodes, leading to their gapping.
-The coexistence of gapped and gapless points on the Fermi surface in the pseudogapped region leads to non-Fermi liquid behaviour of the gapless excitations, as captured by the emergent two-channel behaviour within the impurity model.
-The metal at the transition is supported only the four nodal points.}
-	\label{selfenergy}
-\end{figure}
-
-\subsection{Momentum-space spin-correlations}
-To gain more insight on the nature of the fluctuations in various phases, we study the spin-spin correlation, \(\tilde \chi_s({\bf k}_1, {\bf k}_2) = \frac{1}{2}\left<{\boldsymbol S}_{{\bf k}_1}\cdot {\boldsymbol S}_{{\bf k}_2}\right>\), where \({\bf S}({\bf k}) = \sum_{\alpha\beta}c^\dagger_{{\bf k}\alpha}{\boldsymbol \sigma}_{\alpha \beta}c_{{\bf k}\beta}\).
-These correlations are again obtained from computations within the auxiliary model, using the relation obtained in eq.~\ref{kspaceCorrelation}.
-While the full expression contains contributions from various combinations of auxiliary models, in the present work we focus on the intra-auxiliary model contribution which is the largest term:
-\begin{equation}\begin{aligned}
-	C_{\mathcal{O}}({\bf k}_1,{\bf k}_2) &= \braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}({\bf k}_2) | \psi_\text{gs}\left({\bf r}_c\right)}\braket{\psi_\text{gs}\left({\bf r}_c\right) | \mathcal{\tilde O}^\dagger({\bf k}_1) | \psi_\text{gs}\left({\bf r}_c\right)}~.
-\end{aligned}\end{equation}
-The results for Fermi surface points are shown in Fig.~\ref{tiledSF}.
-We find that at small values of the bath interaction (first plot from left), the spin correlations are spread out uniformly on the Fermi surface, and are quite small in magnitude.
-This is likely because of the weakly correlated nature of the Fermi liquid.
-As we enter the pseudogap (second plot from left and beyond), the spin correlations of the antinodal region vanish.
-Along with the divergence of self-energy observed along the same points, this indicates that the antinodal region no longer participates in scattering processes that can renormalise the metal.
-The nodal region, however, sees an enhancement of spin correlations, particularly in it's neighbourhood.
-This is a sign that the metallic excitations are becoming highly correlated through the pseudogap.
-
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.24\textwidth]{tiledSF-1.pdf}
-	\includegraphics[width=0.24\textwidth]{tiledSF-2.pdf}
-	\includegraphics[width=0.24\textwidth]{tiledSF-3.pdf}
-	\includegraphics[width=0.24\textwidth]{tiledSF-4.pdf}
-	\caption{Spin-spin correlations \(\chi_s\) (defined in main text) between the nodal point \(k_N = \left( -\pi/2, -\pi/2\right)\) and an arbitrary \(k-\)point on the Fermi surface.
-In the absence of bath interaction (first panel), the correlations are somewhat uniformly distributed along the Fermi surface, and quite small.
-This describes the Fermi liquid phase of the lattice model.
-As we enter the pseudogap (second panel and beyond), the spin-correlations near the antinode vanish, indicating that they have been removed from the metallic excitations, while the correlations near the nodal point become enhanced because of the increasingly correlated nature of the metal.}
-	\label{tiledSF}
-\end{figure}
-
-\subsection{Entanglement entropy and Mutual information}
-We have also used our method to study the \(k-\)space entanglement entropy and mutual information within the lattice model, in order to probe the transition and the pseudogap.
-Given a pure state \(\ket{\Psi}\) describing the complete system, the entanglement entropy \(S_\text{EE}(\nu)\) of a subsystem \(\nu\) quantifies the entanglement of \(\nu\) with the rest of the subsystem, and is defined as
-\begin{equation}\begin{aligned}
-	S_\text{EE}(\nu) = -\text{Tr}\left[\rho(\nu)\log \rho(\nu)\right],\quad \rho(\nu) = \text{Tr}_\nu\left[\ket{\Psi}\bra{\Psi}\right] 
-\end{aligned}\end{equation}
-where \(\text{Tr}\left[\cdot\right] \) is the trace operator, and \(\rho(\nu)\) is the reduced density matrix (RDM) for the subsystem \(\nu\) obtained by taking the partial trace \(\text{Tr}_\nu\) (over the states of \(\nu\)) of the full density matrix \(\rho = \ket{\Psi}\bra{\Psi}\).
-If the subsystem \(\nu\) describes local regions in real space (or states in \(k-\)space), we might be interested in the entanglement between two such subsystems \(\nu_1\) and \(\nu_2\).
-The correct measure to quantify such entanglement is the mutual information:
-\begin{equation}\begin{aligned}
-	I_2(\nu_1,\nu_2) = S_\text{EE}(\nu_1) + S_\text{EE}(\nu_2) - S_\text{EE}(\nu_1 \cup \nu_2)~,
-\end{aligned}\end{equation}
-where \(\nu_1 \cup \nu_2\) is a larger subsystem formed by combining \(\nu_1\) and \(\nu_2\).
-
-We have already shown how to obtain the RDM for a \(k-\)state from our approach, in eq.~\ref{RDMTiled}:
-\begin{equation}\begin{aligned}
-	\tilde \rho({\bf k}) \sim \text{Tr}_{\bf k}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d)}\right] + \frac{1}{N}\text{Tr}_{\bf k}\sum_{{\bf r}}\left[\ket{\psi_\text{gs}({\bf r}_d)}\bra{\psi_\text{gs}({\bf r}_d + {\bf r})}\right]~,
-\end{aligned}\end{equation}
-where \(\ket{\psi_\text{gs}({\bf r}_d)}\) is a reference auxiliary model ground state, and \(\ket{\psi_\text{gs}({\bf r}_d + {\bf r})}\) sums over other auxiliary models at increasing distances from this reference model.
-The \(\sim\) indicates that the RDM needs to be normalised.
-In the present work, we have restricted our results to the intra-auxiliary model contribution (first term).
-We show, in Fig.~\ref{tiledEntanglement}, the results of entanglement calculations on the Fermi surface.
-The entanglement entropy distribution (top panel) in \(k-\)space shows how the partial gapping leads to the elimination of the antinodal \(k-\)modes from the ground state and excitations and the consequent vanishing of their entanglement.
-We also plot, in the lower panel, the mutual information between (i) an arbitrary \(k-\)state and the nodal point, and (ii) an arbitrary \(k-\)state and the edge of the disconnected Fermi surface in the pseudogap.
-While the nodal point is seen to remain somewhat strongly entangled with the other Fermi surface points, the edge of the ``Fermi arc" has minimal entanglement until the system comes close to the critical point.
-
-\begin{figure}[htpb]
-	\includegraphics[width=0.24\textwidth]{tiled_SEE_k-1.pdf}
-	\includegraphics[width=0.24\textwidth]{tiled_SEE_k-2.pdf}
-	\includegraphics[width=0.24\textwidth]{tiled_SEE_k-3.pdf}
-	\includegraphics[width=0.24\textwidth]{tiled_SEE_k-4.pdf}
-
-	\includegraphics[width=0.24\textwidth]{tiled_I2_k_N-1.pdf}
-	\includegraphics[width=0.24\textwidth]{tiled_I2_k_N-2.pdf}
-	\includegraphics[width=0.24\textwidth]{tiled_I2_k_edge-2.pdf}
-	\includegraphics[width=0.24\textwidth]{tiled_I2_k_edge-3.pdf}
-	\caption{Top panel: Entanglement entropy \(S_\text{EE}({\bf k})\) on the Fermi surface.
-Similar to the correlations, the entanglement in the \(W=0\) model remains uniformly spread out over the Fermi surface.
-As the Fermi surface progressively shrinks, the entanglement gets concentrated to the nodal points.
-Bottom panel: Mutual information \(I_2\) between (i) an arbitrary \(k-\)state and the nodal point (first and second plots), and (ii) an arbitrary \(k-\)state and the edge of the disconnected Fermi surface in the pseudogap (third and fourth plots).
-The ends of the partial Fermi surface appear to be weakly entangled to the rest of the Fermi surface, while the nodal points remain strongly entangled all the way through to the transition.}
-	\label{tiledEntanglement}
-\end{figure}
-
-\section{Nature of Low-Energy Excitations in Various Regimes}
-\subsection{Fermi liquid excitations, \(|W| < |W|^*\)}
-As discussed in Sec.~\ref{2CKEmerge}, the effective description of the impurity model for \(|W| > |W|^*\) becomes that of a two-channel Kondo (2CK) model.
-Prior to that (\(|W| < |W|^*\)), the entire Fermi surface continues to screen the impurity, and this leads to local Fermi liquid description of the impurity excitations.
-Using our translation operator prescription for mapping an impurity model to a lattice model (eq.~\ref{tilingPrescription}), these local Fermi liquid excitations arising from each auxiliary model coherently combine to create extended Fermi liquid excitations in the lattice model.
-This is therefore the nature of the metal for \(|W| < |W|^*\), and further support for this is found from the non-zero values of the quasiparticle residue in this regime (right panel of Fig.~\ref{channelDecoupling}).
-
-\subsection{Marginal Fermi liquid, \(|W| > |W|^*\)}
-We have demonstrated in Subsection.~\ref{marginalFL} that the low-lying excitations of the pseudogap phase are described by a marginal Fermi liquid.
-This is linked to the fact that the excitations within the impurity model become many-particle in nature - they involve fluctuations on multiple sites.
-This should be contrasted with the local Fermi liquid excitations that involve only the conduction bath site next to the zeroth site.
-Upon tiling, we can immediately see that the resulting metal is not a Fermi liquid; the extended excitations will involve excitations of multiple \(k-\)states, and just not a simple superposition of \(1-\)particle excitations (that gave rise to the Fermi liquid).
-The build up of additional correlations within the marginal Fermi liquid (in comparison to the Fermi liquid) can also be ascertained from the fact that the local physics is determined by an impurity model which is highly local in \(k-\)space (due to the decoupling of the Fermi arms, see Sec.~\ref{2CKEmerge}).
-Such a local-in-\(k-\)space impurity model is highly non-local in real-space, consisting of long-ranged interactions between the impurity and the conduction bath.
-This is another signature of the non-Fermi liquid nature of the excitations obtained upon tiling.
-
-\subsection{At the critical point, \(|W| \lesssim |W|^*\)}
-Crucially, we find that during the passage through the pseudogap phase, the nature of the non-Fermi liquid metal itself morphs; the marginal Fermi liquid description is found to break down at the transition, and is replaced by the non-Fermi liquid excitations of a Hatsugai-Kohmoto model.
-The singular nature of the excitations in this regime can be ascertained from the self-energy displaying divergent behaviour (see Subsection~\ref{hkmEmerge}).
-This can be attributed to the extremely non-local form of the impurity model (arising from the fact that it couples to only the nodal points in \(k-\)space).
-This divergent self-energy is consistent with our numerical calculations of the impurity self-energy which showed that the self-energy poles approach the \(\omega=0\) point as the system is tuned towards the transition.
-
-\subsection{Heisenberg model as a low-energy description of the Mott insulator}
-
-In the insulating phase, the ground state of each auxiliary model hosts a decoupled local moment.
-Upon applying the tiling procedure, the lattice model ground state becomes that of the Hubbard model in the atomic limit.
-In order to lift the extensive degeneracy of the state, we will now take into consideration inter-auxiliary model virtual scattering processes that were subdominant in the metallic phase and were hence ignored.
-These one-particle scattering processes lead to the emergence of a nearest-neighbour superexchange interaction.
-The calculation is a straightforward application of second order perturbation theory (Schrieffer-Wolff transformation).
-In order to allow virtual fluctuations that can lift the large ground state degeneracy and lower the energy, we consider (perturbatively) the effects of an irrelevant single-particle hybridisation that connects the nearest-neighbour sites.
-This perturbation Hamiltonian is therefore of the form
-\begin{equation}\begin{aligned}
-	H_t = \sum_\omega V(\omega) \mathcal{P}(\omega)~\sum_\sigma\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) ~,
-\end{aligned}\end{equation}
-where \(V(\omega)\) only acts on states at the energy scale \(\omega\); the renormalisation of \(V\) is encoded in the fact that \(V(\omega)\) is largest for the excited states and vanishes at low-energies: \(V(\omega \to 0) = 0\).
-
-We show the details in Appendix~\ref{heisenbergDerivation}.
-The final result is the emergence of the following effective Hamiltonian for the low-energy dynamics between any two nearst-neighbour sites \(i\) and \(j\):
-\begin{equation}\begin{aligned}
-	H_\text{eff} = 2\frac{V_H^2}{U/2}\left(2S_i^z S_j^z + S_i^+S_j^- + S_i^-S_j^+\right) = J_\text{eff} {\bf S}_i\cdot{\bf S}_j~,
-\end{aligned}\end{equation}
-where the effective antiferromagnetic Heisenberg coupling is \(J_\text{eff} = \frac{8V_H^2}{U}\) and \(V_H \equiv V(\omega \to U/2)\) is the impurity-bath hybridisation at energy scales of the order of the Mott gap, in the sense of an RG flow.
-
-\clearpage
-\section*{Appendices}
-\appendix
-\subsection{Marginal Fermi liquid excitations in a two-channel Kondo model}\label{mflDerivation}
-By considering minimal hopping into the conduction bath and treating the effects of this hopping perturbatively against the overscreened screened ground state (determined by an intermediate coupling \(J^*\)), the low-energy excitations above the ground state of the two-channel Kondo (2CK) model are described by the following Hamiltonian~\cite{Patra2023MCK}:
-\begin{eqnarray}
-	\label{nfl_terms}
-	H_\mathrm{eff} =& \frac{8t^2}{{J}}\left[\left(S^z_{0,1}\right)^2 S^+_{0,2} + \left(S^z_{0,2}\right)^2 S^+_{0,1}\right] \left(S^-_{1,1} + S^-_{1,2}\right) + \mathrm{h.c.};
-\end{eqnarray}
-where \({\boldsymbol S}_{i,l} = \frac{1}{2}\sum_{\sigma_1,\sigma_2}c^\dagger_{i,\sigma_1,l}{\boldsymbol \sigma}_{\sigma_1,\sigma_2}c_{i,\sigma_2,l}\) are spin operators for the \(i^\text{th}\) site on the \(l^\text{th}\) conduction channel (\(l\) can be 1 or 2 for a two-channel model).
-The labels \(\sigma_1\) and \(\sigma_2\) are spin indices that can be \(\pm 1\).
-The site index \(0\) represents the bath sites connected immediately to the impurity site.
-The operator \(c^\dagger_{i,\sigma,l}\) creates an electron with spin \(\sigma\) on the \(i^\text{th}\) site of the \(l^\text{th}\) conduction channel.
-
-We will Fourier transform this effective Hamiltonian into \(k-\)space:
-\begin{eqnarray}
-	\label{k_space_od}
-	\frac{2t^2}{J}\sum_{\left\{k_i,k_i^\prime\right\}}\sum_{\sigma, l} &\left(e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \mathrm{h.c.}\right) ~.\qquad
-\end{eqnarray}
-Such a three particle interaction term was also obtained for the NFL phase of the 2D Hubbard model from a URG treatment (see Appendix B of Ref.\cite{anirbanmott1}).
-The channel indices in Eq.~\ref{k_space_od} can be mapped to the normal directions in~\cite{anirbanmott1}.
-The 2 particle-1 hole interaction in Eq.~\ref{k_space_od} has a diagonal component which can be obtained by setting \(k=k^\prime, k_1 = k_2^\prime\) and \(k_2 = k_1^\prime\):
-\begin{eqnarray}
-	H_\mathrm{MFL} &= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{2t^2e^{i\left(k_1 - k_2\right)a}}{J} \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right) + \mathrm{h.c.}\nonumber\\
-	&= \sum_{k, k_1, \atop{k_2,\sigma,  l}} \frac{4t^2}{J} \cos a\left(k_1 - k_2\right)  \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right).\qquad 
-\end{eqnarray}
-The most dominant contribution comes from \(k_1 = k_2 = k^\prime\), revealing the non-Fermi liquid metal~\cite{cox_jarrell_two_channel_rev,Andrei1995}:
-\begin{eqnarray}
-	\label{mfl_large}
-	H^*_\mathrm{MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)~.
-\end{eqnarray}
-A non-local version of this effective Hamiltonian was found to describe the normal phase of the Mott insulator of the 2D Hubbard model, as seen from a URG analysis~\cite{anirbanmott1,anirbanmott2}.
-Following~\cite{anirbanmott1}, one can track the RG evolution of the dual coupling \(R_j = \frac{4t^2}{J_j}\) at the \(j^\mathrm{th}\) RG step, in the form of the URG equation
-\begin{eqnarray}
-	\Delta R_j =- \frac{R_j^2}{\omega - \epsilon_{j}/2 - R_j/8}~.
-\end{eqnarray}
-In the RG equation, \(\epsilon_{j}\) represents the energy of the \(j^\mathrm{th}\) isoenergetic shell. It is seen from 
-the RG equation that \(R\) is relevant in the range of \(\omega < \frac{1}{2}\epsilon_j\) that has been used throughout, leading to a fixed-point at \(R^*/8 = \omega - \frac{1}{2}\epsilon^*)\).
-The relevance of \(R\) is expected because the strong coupling \(J\) is irrelevant and \(R \sim 1/J\).
-
-The renormalisation in \(R\) leads to a renormalisation in the single-particle self-energy~\cite{anirbanmott1}. The \(k-\)space-averaged self-energy renormalisation is
-\begin{eqnarray}
-	\Delta \Sigma(\omega) = \rho {R^*}^2\int_0^{\epsilon^*} \frac{d\epsilon_j}{\omega - \epsilon_j/2 + R_j/8}~.
-\end{eqnarray}
-The density of states can be approximated to be \(N^*/R^*\), where \(N^*\) is the total number of states over the interval \(R^*\).
-As suggested by the fixed point value of \(R_j\), we can approximate its behaviour near the fixed point by a linear dependence on the dispersion \(\epsilon_j\).
-The two limits of the integration are the starting and ending points of the RG.
-We start the RG very close to the Fermi surface and move towards the fixed point \(\epsilon^*\).
-Near the starting point, we substitute \(\epsilon = 0\) and \(R = \omega\), following the fixed point condition.
-From the fixed point condition, we also substitute \(R^*/8 = \omega - \frac{1}{2}\epsilon^*\).
-On defining \(\bar \omega = N^* \left(\omega - \frac{1}{2}\epsilon^*\right)\), we can write
-\begin{eqnarray}
-	\label{self_energy}
-	\Delta \Sigma(\omega) \sim  \bar \omega \ln \frac{N^* \omega}{\bar \omega}~.
-\end{eqnarray}
-The self-energy also provides the quasiparticle residue for each channel\cite{anirbanmott1}:
-\begin{eqnarray}
-	Z(\bar\omega) = \left(2 - \ln \frac{2\bar\omega}{N^* \omega}\right) ^{-1}~.
-\end{eqnarray}
-As \(\omega \to 0\), the \(Z\) vanishes, implying that the ground state is {\it not adiabatically connected} to the Fermi gas in the presence of the NFL terms.
-This is the orthogonality catastrophe~\cite{varma2002singular,anderson_infraredcat,yamada_catastrophe,yamada1979orthogonality} in the two-channel Kondo problem, and it is brought about by the presence of the channel-non diagonal terms in Eq.~\ref{mfl_large}.
-
-\subsection{Emergence of Hatsugai-Kohmoto model near the NFL-Mott insulator transition}\label{hkmDerivation}
-As the bath interaction \(W\) is tuned through the L-PG phase, the nodal region is the last to decouple from the impurity.
-This allows us to write down a simpler Kondo model near the transition, where only the nodal region is hybridising with the impurity spin through Kondo interactions.
-This is done by retaining only those scattering processes \({\bf k}_1 \to {\bf k}_2\) that originate from and end at \(k-\)points within a small neighborhood of width \(|{\bf q}|\) around the four nodal points: \({\bf k}_1, {\bf k}_2 \in {\bf N} + {\bf q}, |{\bf q}| \ll \pi\), where \({\bf N}\) can be any one of the four nodal points \({\bf N}_{1} = \left(\pi/2, \pi/2\right), {\bf N}_{2} = \left(-\pi/2, \pi/2\right)\) and \({\bf N}_1 + {\bf Q}_1\) and \({\bf N}_{2} + {\bf Q}_2\), where \({\bf Q}_1 = \left(-\pi,-\pi \right)\) and \({\bf Q}_2 = \left( \pi, -\pi \right) \) are the two nesting vectors.
-We have already seen, in Subsection ~\ref{2CKEmerge}, that the pseudogap regime displays a decoupling of the Brillouin zone into sets of points that have no explicit connecting term in the Hamiltonian.
-Near the transition, the neighbourhoods of \({\bf N}_{1}\) and \({\bf N}_{1} + {\bf Q}_1\) form one such connected set, while the other two nodes \({\bf N}_{2}\) and \({\bf N}_{2} + {\bf Q}_2\) form another connected set, but these two sets are disconnected from each other, in the sense of a two-channel model.
-We also assume that the window of \({\bf q}\) is small enough so that the fixed point Kondo coupling values \(J^*({\bf q}_1, {\bf q}_2)\) for the scattering processes involving \({\bf q}_1\) and \({\bf q}_2\) can be replaced by an average value \(J^*\).
-
-With these considerations, the simplified low-energy model near the transition describing the Kondo scattering processes can be written as
-\begin{equation}\begin{aligned}
-	\tilde H_\text{imp-cbath} = J^*\frac{1}{2}\sum_{l=1,2}\sum_{{\bf q}_1, {\bf q}_2}\sum_{\alpha,\beta}{\bf S}_d\cdot{\boldsymbol \sigma}_{\alpha\beta}&\left(c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} + c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta} \right.
-\\
-&\left. - c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} - c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta}\right)~.
-\end{aligned}\end{equation}
-For scattering processes that involve two opposite nodal points (that is, connected by one of the nesting vectors \({\bf Q}_l\), the Kondo coupling is \(-J^*\), which explains the negative signs in the third and fourth terms.
-An explanation of the various dummy indices is in order.
-The label \(l\) can take values 1 or 2, allowing us to consider both the decoupled sets (associated with \({\bf N}_1\) and \({\bf N}_2\)).
-It also labels the nesting vectors \({\bf Q}_l\) associated with the two sets.
-\(\alpha\) and \(\beta\) indicate spin indices, and \({\bf q}_1\) and \({\bf q}_2\) represent incoming and outgoing momenta in the scattering processes.
-
-Because of the decoupling of the channel \(l=1\) and \(l=2\), we consider only the \(l=1\) channel for the rest of the calculations in this section, and we comment at the end on what the presence of two channels means for the results.
-In order to simplify the Hamiltonian, we define new fermionic operators
-\begin{equation}\begin{aligned}
-	\psi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} + c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~,
-	\phi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} - c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~,
-\end{aligned}\end{equation}
-The operator satisfy fermionic anticommutation relations:
-\begin{equation}\begin{aligned}
-	\left\{ \psi_{{\bf q},\sigma}, {\psi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left[\delta_{{\bf q}, {\bf q}^\prime} + \frac{1}{2}\left(\delta_{{\bf Q}_1 - {\bf q}, {\bf q}^\prime} + \delta_{{\bf q}, {\bf Q}_1 - {\bf q}^\prime}\right)  \right] \delta_{\sigma,\sigma^\prime} \\
-																							   &= \delta_{{\bf q}, {\bf q}^\prime}\delta_{\sigma,\sigma^\prime}~,\\
-	\left\{ \phi_{{\bf q},\sigma}, {\phi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left[\delta_{{\bf q}, {\bf q}^\prime} - \frac{1}{2}\left(\delta_{{\bf Q}_1 - {\bf q}, {\bf q}^\prime} + \delta_{{\bf q}, {\bf Q}_1 - {\bf q}^\prime}\right)  \right] \delta_{\sigma,\sigma^\prime} \\
-																				  &= \delta_{{\bf q}, {\bf q}^\prime}\delta_{\sigma,\sigma^\prime}~,\\
-	\left\{ \psi_{{\bf q},\sigma}, {\phi}^\dagger_{{\bf q}^\prime,\sigma} \right\} &= \left\{ \phi_{{\bf q},\sigma}, {\psi}^\dagger_{{\bf q}^\prime,\sigma} \right\} = 0~,
-\end{aligned}\end{equation}
-where both \({\bf q}\) and \({\bf q}^\prime\) are chosen from a small window around the nodes, so their difference is also small and it is therefore guaranteed that \(|{\bf q} + {\bf q}^\prime| \neq |{\bf Q}_1|\), rendering both \(\delta_{{\bf q}, {\bf Q}_1 - {\bf q}^\prime}\) and \(\delta_{{\bf Q}_1 - {\bf q}, {\bf q}^\prime}\) zero.
-For convenience, we define new number operators for the sum and relative degrees of freedom:
-\begin{equation}\begin{aligned}
-	s_{{\bf q},\sigma} = {\psi}^\dagger_{{\bf q}} {\psi}_{{\bf q}},~ r_{{\bf q},\sigma} = {\phi}^\dagger_{{\bf q}} {\phi}_{{\bf q}}~.
-\end{aligned}\end{equation}
-We then have the following useful relation between the corresponding number operators \(n = c^\dagger c\):
-\begin{equation}\begin{aligned}\label{numberOperatorRelation}
-	n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma} = s_{{\bf q}, \sigma} + r_{{\bf q},\sigma}~.
-\end{aligned}\end{equation}
-
-We find that the sum degrees of freedom \(s_{{\bf q},\sigma}\) do not enter the Kondo scattering Hamiltonian \(\tilde H_\text{imp-cbath}\) (for the single channel \(l=1\)), and it is expressed purely in terms of the relative degrees of freedom:
-\begin{equation}\begin{aligned}
-	\tilde H_\text{imp-cbath} = J^*\sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}{\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta}~.
-\end{aligned}\end{equation}
-We now proceed to rewrite the other parts of the Hamiltonian in terms of these new degrees of freedom. The kinetic energy can be written as
-\begin{equation}\begin{aligned}\label{kineticEnergy}
-	\tilde H_\text{cbath} &= \sum_{{\bf q},\sigma}\varepsilon_{{\bf N}_1 + {\bf q}}\left(n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q},\sigma}\right)\\
-						  &= \sum_{{\bf q},\sigma}\varepsilon_{{\bf N}_1 + {\bf q}}\left({\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma} + {\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma}\right)~,
-\end{aligned}\end{equation}
-We also consider a simplified form of the bath interaction (for the channel \(l=1\)), taking into account the density-density correlations in \(k-\)space:
-\begin{widetext}
-\begin{equation}\begin{aligned}
-	\tilde H_\text{cbath-int} =& -W\sum_{{\bf q},\sigma}\left(n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q},\sigma}\right) + W\sum_{{\bf q}_1,{\bf q}_2}\left(n_{{\bf N}_{1} + {\bf q}_1, \uparrow} + n_{{\bf N}_{1} + {\bf Q}_{1} - {\bf q}_1, \uparrow} \right) \left( n_{{\bf N}_{1} + {\bf q}_2, \downarrow} + n_{{\bf N}_{1} + {\bf Q}_{1} - {\bf q}_2, \downarrow} \right)~,\\
-	=& -W\sum_{{\bf q},\sigma}\left(s_{{\bf q},\sigma} + r_{{\bf q},\sigma}\right) + W\sum_{{\bf q}_1,{\bf q}_2}\left(s_{{\bf q}_1,\uparrow} + r_{{\bf q}_1,\uparrow}\right) \left(s_{{\bf q}_2,\downarrow} + r_{{\bf q}_2,\downarrow}\right)~.
-\end{aligned}\end{equation}
-\end{widetext}
-We used eq.~\ref{numberOperatorRelation} in order to obtain the final form.
-
-Since both \(\tilde H_\text{imp-cbath}\) and \(\tilde H_\text{cbath-int}\) commute with \(s_{{\bf q}, \sigma}\), we replace the local objects \(\sum_{\bf q}s_{{\bf q},\sigma}\) in \(\tilde H_\text{cbath-int}\) with \(\frac{1}{2}\) since the bath is always at half-filling.
-This results in a simplified Hamiltonian for just the \(\phi_{{\bf q},\sigma}\) degrees of freedom:
-\begin{equation}\begin{aligned}
-	\tilde H =& -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow} + \sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}J^*{\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta}
-\end{aligned}\end{equation}
-
-For bath interaction strength close to the critical value (\(W \lesssim W_c\)), the fixed point coupling value \(J^*\) is much smaller than \(W\).
-In order to obtain the gapless excitations of the system arising from the presence of the impurity site, we integrate out the impurity dynamics via a Schrieffer-Wolff transformation.
-The perturbation term \(\mathcal{V}\) then consists of Hamiltonian terms that modify the impurity configuration,
-\begin{equation}\begin{aligned}
-	\mathcal{V} = \sum_{{\bf q}_1, {\bf q}_2}J^*{S}_d^+{\phi}^\dagger_{{\bf q}_1 \downarrow} \phi_{{\bf q}_2 \uparrow} + \text{h.c.}~,
-\end{aligned}\end{equation}
-while the ``non-interacting" Hamiltonian is
-\begin{equation}\begin{aligned}
-	H_D &= -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow}~.
-\end{aligned}\end{equation}
-The renormalisation in the dynamics of \(b^\dagger_{\vec k,\sigma}\) are given by
-\begin{equation}\begin{aligned}
-	\Delta \tilde H &= \mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L,
-\end{aligned}\end{equation}
-where \(E_L\) is the energy of the ground state of \(H_D\), \(-(E_L - H_D)\) is the excitation energy of the state generated upon applying the perturbation \(\mathcal{V}\), and \(\mathcal{P}_{L(H)}\) projects onto the low(high)-energy subspace.
-For the present Hamiltonian, the low-energy state (associated with \(E_L\)) is the one that minimises the bath interaction term \(\tilde H_\text{cbath-int}\); since the coupling \(W\) is negative, the minimal configuration is one in which the local operators \(\sum_{{\bf q}}r_{{\bf q},\sigma}\) (for \(\sigma=\pm 1\)) are unity.
-This leads to the following low-energy state:
-\begin{equation}\begin{aligned}
-	\ket{L} = \frac{1}{N}\sum_{{\bf q}_1{\bf q}_2}\phi^\dagger_{{\bf q}_1, \uparrow}\phi^\dagger_{{\bf q}_2, \downarrow} \ket{0}
-\end{aligned}\end{equation}
-where \(\ket{0}\) is the \(r_{{\bf q} \uparrow} = r_{{\bf q} \downarrow} = 0\) state.
-The state \(\ket{L}\) is at zero energy.
-High-energy states are obtained by applying, on the state \(\ket{L}\), the excitation operator \(\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2,\bar\sigma}\) or its hermitian conjugate.
-The operator converts a double and a hole to spin states, incurring a total excitation cost of \(-W = |W|\).
-
-We now calculate the various terms in \(\Delta \tilde H\):
-\begin{equation}\begin{aligned}\label{kondoPert}
-	&\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L = \left(\frac{1}{2} + S_d^z\right) \sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*}^2}{-4W}\phi^\dagger_{{\bf q}_1,\downarrow}\phi_{{\bf q}_2, \uparrow} \left(\phi^\dagger_{{\bf q}_2,\uparrow}\phi_{{\bf q}_1, \downarrow} + (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\uparrow}\phi_{{\bf q}_2, \downarrow}\right)\\
-	&= -\sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*}^2}{4W}\left[r_{{\bf q}_1 \downarrow} \left(1 - r_{{\bf q}_2 \uparrow}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\uparrow}\phi^\dagger_{{\bf q}_1,\downarrow}\phi_{{\bf q}_2, \downarrow}\phi_{{\bf q}_2, \uparrow}\right]\\
-	&\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L = \sum_{{\bf q}_1,{\bf q}_2}\frac{{J^*}^2}{-4W}\left[r_{{\bf q}_1 \uparrow} \left(1 - r_{{\bf q}_2 \downarrow}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\downarrow}\phi^\dagger_{{\bf q}_1,\uparrow}\phi_{{\bf q}_2, \uparrow}\phi_{{\bf q}_2, \downarrow}\right] \\
-\end{aligned}\end{equation}
-In both terms, we set \(S_d^z = 0\) owing to local SU(2) symmetry on the impurity site. In the same way, we treat the effects of the dispersion term (eq.~\ref{kineticEnergy}) to second order:
-\begin{equation}\begin{aligned}
-	\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L &= \sum_{{\bf q}, \sigma}\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W}\left[ {\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma}{\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma} + {\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma}{\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma}\right] \\
-																						 &= \sum_{{\bf q}, \sigma}\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W}\left[ s_{{\bf q},\sigma} \left(1 - r_{{\bf q},\sigma}\right) + r_{{\bf q},\sigma} \left(1 - s_{{\bf q},\sigma}\right)\right]~.
-\end{aligned}\end{equation}
-At the values of \({\bf q}\) for which \(\varepsilon_{{\bf N}_1 + {\bf q}} > 0\), we can set the number operator \(s_{{\bf q},\sigma} = 0\) (these positive energy modes are unoccupied in the ground state), while for \(\varepsilon_{{\bf N}_1 + {\bf q}} < 0\), we have \(s_{{\bf q},\sigma} = 1\):
-\begin{equation}\begin{aligned}\label{dispersionSecondOrder}
-	\mathcal{P}_L \mathcal{V} \mathcal{P}_H\frac{1}{E_L - H_D} \mathcal{V} \mathcal{P}_L = \sum_{{\bf q} \left(\varepsilon_{{\bf N}_1 + {\bf q}} > 0\right), \sigma}\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W} r_{{\bf q},\sigma} + \sum_{{\bf q} \left(\varepsilon_{{\bf N}_1 + {\bf q}} < 0\right), \sigma}\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W} \left(1 - r_{{\bf q},\sigma}\right)~.
-\end{aligned}\end{equation}
-
-The complete Hamiltonian (combining eqs.~\ref{dispersionSecondOrder} and \ref{kondoPert}) is
-\begin{equation}\begin{aligned}
-	\Delta \tilde H = \sum_{{\bf q}, \sigma}\text{sign}\left(\varepsilon_{{\bf N}_1 + {\bf q}}\right)\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W} r_{{\bf q},\sigma} + \sum_{{\bf q}_1,{\bf q}_2, \sigma}\frac{{J^*}^2}{-4W}\left[r_{{\bf q}_1 \sigma} \left(1 - r_{{\bf q}_2 \bar\sigma}\right) - (1 - \delta_{{\bf q}_1,{\bf q}_2})\phi^\dagger_{{\bf q}_1,\bar\sigma}\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2, \sigma}\phi_{{\bf q}_2, \bar\sigma}\right]~.
-\end{aligned}\end{equation}
-
-\subsection{Heisenberg Model as a low-energy description of the tiled Mott insulator}\label{heisenbergDerivation}
-For simplicity, we consider two impurity sites labelled \(1\) and \(2\) associated with two nearest-neighbour auxiliary models. The ground state subspace is four-fold degenerate:
-\begin{equation}\begin{aligned}
-	\ket{\Psi_L} = \left\{\ket{\sigma_1,\sigma_2}\right\}~,\quad \sigma_i = \pm 1~,
-\end{aligned}\end{equation}
-where \(\sigma_i\) is the spin state of site \(i\).
-This ground state is derived from the following "zeroth order" Hamiltonian that emerges in the local moment phase of the auxiliary models when all scattering processes between the impurity and conduction bath are RG-irrelevant:
-\begin{equation}\begin{aligned}
-	H_0 = -\frac{U}{2}\sum_{i=1,2}\left(n_{i \uparrow} - n_{i \downarrow}\right)^2~;
-\end{aligned}\end{equation}
-the local correlation on the impurity site becomes the largest scale in the problem in this phase and pushes the \(\ket{n_i=2}\) and \(\ket{n_i=0}\) states to high energies.
-This then defines the high-energy subspace for our calculation:
-\begin{equation}\begin{aligned}
-	\ket{\Psi_H} = \ket{C_1,C_2}~,
-\end{aligned}\end{equation}
-where \(C_i\) can take values 0 or 2, indicating that the state \(i\) is either empty or full, respectively.
-Both the double and hole states exist at a charge gap of the order of \(U/2\) above the low-energy singly-occupied subspace defined by the states \(\ket{\Psi_L}\).
-
-In order to allow virtual fluctuations that can lift the large ground state degeneracy and lower the energy, we consider (perturbatively) the effects of an irrelevant single-particle hybridisation that connects the nearest-neighbour sites.
-This perturbation Hamiltonian is therefore of the form
-\begin{equation}\begin{aligned}
-	H_t = \sum_\omega V(\omega) \mathcal{P}(\omega)~\sum_\sigma\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) ~,
-\end{aligned}\end{equation}
-where \(V(\omega)\) only acts on states at the energy scale \(\omega\); the renormalisation of \(V\) is encoded in the fact that \(V(\omega)\) is largest for the excited states and vanishes at low-energies: \(V(\omega \to 0) = 0\).
-
-In order to obtain a low-energy effective Hamiltonian for the impurity sites arising from this hybridisation, we integrate out \(H_t\) via a Schrieffer-Wolff transformation.
-This leads to the following second-order Hamiltonian:
-\begin{equation}\begin{aligned}
-	H_\text{eff} = \mathcal{P}_L H_t G\mathcal H_t \mathcal{P}_L~.
-\end{aligned}\end{equation}
-The operator \(\mathcal{P}_L\) projects onto the low-energy subspace \(\ket{\Psi_L}\) - this ensures that we remain in the low-energy subspace at the beginning and at the end of the total process.
-The Greens function \(G = (E_L - H_0)^{-1}\) incorporates the excitation energy to go from the low-energy subspace \(\ket{\Psi}_L\) (of energy \(E_L\)) to the excited subspace \(\ket{\Psi}_H\) of energy \(E_L + U/2\).
-Substituting the form of the perturbation Hamiltonian and the excitation energy into the above expression gives
-\begin{equation}\begin{aligned}\label{effHam1}
-	H_\text{eff} = \frac{V_H^2}{-U/2}\sum_{\sigma,\sigma^\prime} \left[c^\dagger_{1\sigma}c_{2\sigma}c^\dagger_{2\sigma^\prime}c_{1\sigma^\prime} + c^\dagger_{2\sigma}c_{1\sigma}c^\dagger_{1\sigma^\prime}c_{2\sigma^\prime}\right] ~.
-\end{aligned}\end{equation}
-where \(V_H \equiv V(\omega \to U/2)\) is the impurity-bath hybridisation at energy scales of the order of the Mott gap, in the sense of an RG flow.
-Terms with consecutive creation or annihilation operators on the same site are prohibited because each site is singly-occupied in the ground state.
-It is now easy to cast this Hamiltonian into a more recognizable form.
-For \(\sigma^\prime=\sigma\), we get
-\begin{equation}\begin{aligned}
-	\sum_{\sigma}\delta_{\sigma,\sigma^\prime}c^\dagger_{1\sigma}c_{2\sigma}c^\dagger_{2\sigma^\prime}c_{1\sigma^\prime} = \sum_\sigma \left(n_{1\sigma} - n_{1\sigma}n_{2\sigma}\right) ~,
-\end{aligned}\end{equation}
-while \(\sigma=-\sigma^\prime=\pm 1\) gives 
-\begin{equation}\begin{aligned}
-	\sum_{\sigma}\delta_{\sigma,-\sigma^\prime}c^\dagger_{1\sigma}c_{2\sigma}c^\dagger_{2\sigma^\prime}c_{1\sigma^\prime} = -\left(S_1^+ S_2^- + \text{h.c.}\right)~.
-\end{aligned}\end{equation}
-For the latter expression, we introduced the local spin-flip operators \(S_i^\pm\). The expression above it can also be cast into spin variables, using the equations
-\begin{equation}\begin{aligned}
-	\frac{1}{2}\sum_{\sigma}n_{i\sigma} = \frac{1}{2},\\
-    \frac{1}{2}\sum_{\sigma}\sigma n_{i\sigma} = S_i^z,
-\end{aligned}\end{equation}
-where the first equation is simply the condition of half-filling at each site, and the second equation is the definition of the local spin operator in \(z-\)direction.
-Adding and subtracting the equations gives \(n_{i\sigma} = \frac{1}{2} + \sigma S_i^z\)~.
-
-Substituting everything back into eq.~\ref{effHam1} and dropping constant terms gives
-\begin{equation}\begin{aligned}
-	H_\text{eff} = 2\frac{V_H^2}{U/2}\left(2S_1^z S_2^z + S_1^+S_2^- + S_1^-S_2^+\right) = J_\text{eff} {\bf S}_1\cdot{\bf S}_2~,
-\end{aligned}\end{equation}
-where the effective antiferromagnetic Heisenberg coupling is \(J_\text{eff} = \frac{8V_H^2}{U}\).
-
-\section{Effective action for the Hubbard-Heisenberg model and the eSIAM}
-In order to better understand the similarities and differences between the tiling approach outlined here and the approach adopted in dynamical mean-field approximations, we compute the effective action for the local impurity as well as the impurity-zeroth site system, in both the auxiliary and bulk models.
-This will be done in the limit of infinite coordination number, in order to create a tractable effective theory.
-
-\subsection{Local theory for the Hubbard-Heisenberg model}
-We will first work with the Hubbard-Heisenberg model.
-Let us recall that within the eSIAM, most of the dynamics is governed by the physics of the impurity site and the bath site coupled to the impurity.
-Accordingly, we will first obtain an effective action within the Hubbard-Heisenberg model for the small system consisting of a local site and all its nearest-neighbours.
-
-We choose a certain local site that we call \(0\), whose nearest-neighbours will be denoted as \(\left\{ {\bar 0} \right\} \).
-The action for the full Hubbard-Heisenberg model can be formally separated into three parts:
-\begin{equation}\begin{aligned}
-S_\text{H-H} = S_{0,{\bar 0}} + S^{(0,{\bar 0})} + S_\text{int}~,
-\end{aligned}\end{equation}
-where \(S_{0,{\bar 0}}\) represents the part of the action that involves only the sites \(0\) and $\left\{ {\bar 0} \right\}$, \(S^{(0,{\bar 0})}\) represents the part that has all the sites apart from \(0\) and \(\left\{ {\bar 0} \right\} \), while \(S_\text{int}\) contains all terms that connect these two parts.
-These three parts have the forms
-\begin{equation}\begin{aligned}
-S_{0,{\bar 0}} = \sum_{i=0,{\bar 0}}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau)  - t\sum_{{\bar 0},\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{0\sigma}(\tau)c_{{\bar 0}\sigma}(\tau) + \text{h.c.}\right] \\
-- \frac{U}{2}\sum_{i=0,{\bar 0}}\int_0^\beta\mathrm{d\tau}~\left(n_{i \uparrow}(\tau) - n_{i \downarrow}(\tau)\right)^2 + J\sum_{{\bar 0}}\int_0^\beta\mathrm{d\tau} \vec{S}_0(\tau)\cdot\vec{S}_{{\bar 0}}(\tau)~,
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-S^{(0,{\bar 0})} = \sum_{j\neq(0,{\bar 0})}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{j\sigma}(\tau)\partial_\tau c_{j\sigma}(\tau)  - t\sum_{\left<j,l\right>\neq (0,{\bar 0}),\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{j\sigma}(\tau)c_{l\sigma}(\tau) + \text{h.c.}\right] \\
-- \frac{U}{2}\sum_{j\neq(0,{\bar 0})}\int_0^\beta\mathrm{d\tau}~\left(n_{j\uparrow}(\tau) - n_{j\downarrow}(\tau)\right)^2 + J\sum_{\left<j,l\right>\neq(0,{\bar 0})}\int_0^\beta\mathrm{d\tau} \vec{S}_l(\tau)\cdot\vec{S}_j(\tau)~,
-\end{aligned}\end{equation}
-\begin{equation}\begin{aligned}
-S_\text{int} = -t\sum_{i \in {\bar 0}}\sum_{j \in \text{NN of}~i}\sum_\sigma \int_0^\beta\mathrm{d\tau}~\left(c^\dagger_{i\sigma}(\tau) c_{j\sigma}(\tau) + \text{h.c.}\right) + J\sum_{i \in {\bar 0}}\sum_{j \in \text{NN of}~i}\int_0^\beta\mathrm{d\tau}\vec{S}_i(\tau)\cdot\vec{S}_j(\tau) = S_\text{int}^\text{hop} + S_\text{int}^\text{spin}
-\end{aligned}\end{equation}
-
-In order to obtain an effective theory \(S^{0,{\bar 0}}_\text{eff}\) purely for the local system \((0,{\bar 0})\), we need to trace over all the other degrees of freedom.
-This partial trace will be carried out over the states of the so-called ``cavity" system \(S^{(0,{\bar 0})}\).
-The effective action can be constructed by tracing over scattering processes of all orders that leave the final action diagonal in the system \((0,{\bar 0})\).
-The formal expression can be written as
-\begin{equation}\begin{aligned}
-	S^{0,{\bar 0}}_\text{eff} = S_{0,{\bar 0}} + \sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} + \sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})}
-\end{aligned}\end{equation}
-where, as mentioned before, the average is carried out in the cavity system \(S^{(0,{\bar 0})}\). Each hopping term in the expansion is of the form
-\begin{equation}\begin{aligned}
-	\left(S_\text{int}^\text{hop}\right)^{2n} =& t^{2n}\sum_\sigma\sum_{(i_1, i_1^\prime)\ldots, (i_n, i_n^\prime)} ~\sum_{(j_1, j_1^\prime)\ldots, (j_n, j_n^\prime)} \int_0^\beta d\tau_{1}\ldots d\tau_{n}d\tau_{1}^\prime\ldots d\tau_{j_n}^\prime\\
-			   &c^\dagger_{i_1\sigma}(\tau_{i_1})c^\dagger_{i_2\sigma}(\tau_{2})\ldots c^\dagger_{i_n\sigma}(\tau_{n}) c_{i_1^\prime\sigma}(\tau_{1}^\prime)c_{i_2^\prime\sigma}(\tau_{2}^\prime)\ldots c_{i_n^\prime\sigma}(\tau_{n}^\prime)\left<c_{j_1\sigma}(\tau_{1})c_{j_2\sigma}(\tau_{2})\ldots c_{j_n\sigma} ~ c^\dagger_{j_1^\prime\sigma}(\tau_{1}^\prime)\ldots c^\dagger_{j_n^\prime\sigma}(\tau_{n}^\prime) \right>_{(0,{\bar 0})}\\
-	=& t^{2n}\sum_\sigma\sum_{(i_1, i_1^\prime)\ldots, (i_n, i_n^\prime)} ~\sum_{(j_1, j_1^\prime)\ldots, (j_n, j_n^\prime)} \int_0^\beta d\tau_{1}\ldots d\tau_{j_n}^\prime c^\dagger_{i_1\sigma}(\tau_{i_1})\ldots c^\dagger_{i_n\sigma}(\tau_{n})~c_{i_1^\prime\sigma}(\tau_{1}^\prime)\ldots c_{i_n^\prime\sigma}(\tau_{n}^\prime)\\
-	 &G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right)~,
-\end{aligned}\end{equation}
-where the indices \(i_1\) through \(i_n\) and their primed counterparts run through \(\bar 0\), while \(j_l\) (\(\in \left\{j_1,\ldots,j_n^\prime\right\}\)) runs through the nearest-neighbours of the corresponding \(i_l\) index.
-The \(n-\)particle Greens function \(G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right)\) for the cavity system is defined in the usual fashion
-\begin{equation}\begin{aligned}
-	G_n^{(0,\bar 0)}\left(\tau_1\ldots \tau_n; \tau_1^\prime\ldots \tau_n^\prime\right) = \left<c_{j_1\sigma}(\tau_{1})c_{j_2\sigma}(\tau_{2})\ldots c_{j_n\sigma} ~ c^\dagger_{j_1^\prime\sigma}(\tau_{1}^\prime)\ldots c^\dagger_{j_n^\prime\sigma}(\tau_{n}^\prime) \right>_{(0,{\bar 0})}
-\end{aligned}\end{equation}
-In the limit of infinite coordination number, only the \(n=1\) term survives:
-\begin{equation}\begin{aligned}
-	\lim_{\mathcal{Z}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{hop}\right)^{2n}}_{(0,{\bar 0})} = t^2\sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)\sum_{j,j^\prime}G_1^{(0,\bar 0)}\left(j\tau; j^\prime\tau^\prime\right) \\
-	= \sum_{\sigma}\sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime)~,
-\end{aligned}\end{equation}
-where we have defined the bath hybridisation function \(\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)\) as
-\begin{equation}\begin{aligned}
-	\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime) = t^2\sum_{j \in \text{NN of}~i}\sum_{j^\prime \in \text{NN of}~i^\prime}G_1^{(0,\bar 0)}\left(j\sigma\tau; j^\prime\sigma\tau^\prime\right)~.
-\end{aligned}\end{equation}
-
-Under similar approximations, the spin term in the action reduces to
-\begin{equation}\begin{aligned}
-	\lim_{\mathcal{Z}\to \infty}\sum_{n=1}^\infty \braket{\left(S_\text{int}^\text{spin}\right)^{2n}}_{(0,{\bar 0})} = \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\chi(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)~,
-\end{aligned}\end{equation}
-where the susceptibility \(\chi_{ii^\prime}(\tau - \tau^\prime)\) is defined as 
-\begin{equation}\begin{aligned}
-	\chi_{ii^\prime}(\tau - \tau^\prime) = J^2\sum_{j \in \text{NN of}~i}\sum_{j^\prime \in \text{NN of}~i^\prime}\vec{S}_{j}(\tau)\cdot\vec{S}_{j^\prime}(\tau^\prime)~.
-\end{aligned}\end{equation}
-The effective action for the \(0,\bar 0\) system, in the limit of large coordination number, simplifies to
-\begin{equation}\begin{aligned}
-	S^{0,{\bar 0}}_\text{eff} =& \sum_{i=0,{\bar 0}}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau)  - t\sum_{{\bar 0},\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{0\sigma}(\tau)c_{{\bar 0}\sigma}(\tau) + \text{h.c.}\right] - \frac{U}{2}\sum_{i=0,{\bar 0}}\int_0^\beta\mathrm{d\tau}~\left(n_{i \uparrow}(\tau) - n_{i \downarrow}(\tau)\right)^2 \\
-				   &+ J\sum_{{\bar 0}}\int_0^\beta\mathrm{d\tau} \vec{S}_0(\tau)\cdot\vec{S}_{{\bar 0}}(\tau) + \sum_{i,i^\prime}\int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\Delta_{ii^\prime,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{ii^\prime}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
-\end{aligned}\end{equation}
-
-One can also write down an effective action purely for the local site \(0\).
-The sites \(\bar 0\) will now be a part of the environment action \(S^{(0)}\) instead of the system action, but since the system is thermodynamically large, the cavity action can be assumed to remain the same, such the expectation values are calculated in the same system.
-As a result, the hybridisation and susceptibility functions remain unchanged.
-\(S_\text{int}\) is now made of terms that connect \(0\) and \(\bar 0\), so the transformation from \(S^{(0,\bar 0)}\) can be made by replacing the set \(\left\{ j \right\} \) with the set \(\bar 0\), and the set \(\bar 0\) itself will be replaced by the local site \(0\).
-We quote the final form of the local effective action:
-\begin{equation}\begin{aligned}
-	S^{0}_\text{eff} =& \sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{0\sigma}(\tau)\partial_\tau c_{0\sigma}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{0\uparrow}(\tau) - n_{0\downarrow}(\tau)\right)^2 \\
-			  &+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\Delta_{00,\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{00}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
-\end{aligned}\end{equation}
-
-\subsection{Local theory for the extended SIAM}
-The Hamiltonian for the extended SIAM model is shown in eq.~\ref{siam_attr}.
-We will denote the impurity with the label \(d\) and the bath sites with the label \(c\).
-Among the bath sites, we will represent the site coupled to the impurity with \(z\).
-The full action has the form
-\begin{equation}\begin{aligned}
-	S_\text{ES} = \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - t\sum_{\left<i,j \right> \in c,\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{i\sigma}(\tau)c_{j\sigma}(\tau) + \text{h.c.}\right] - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right]\\
-+ J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{W}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 ~,
-\end{aligned}\end{equation}
-As in the Hubbard-Heisenberg model, we first obtain an effective action for the pair of sites \((d,z)\).
-As in the previous calculation, this will again generate a hybridisation function \(\Delta_{zz,\sigma}\) for the bath site nearest to the zeroth site.
-No susceptibility will be generated however, because there is no spin-exchange coupling within the bath.
-The net result is
-\begin{equation}\begin{aligned}
-	S^{d,z}_\text{eff} =& \sum_{d,c}\sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{i\sigma}(\tau)\partial_\tau c_{i\sigma}(\tau) - V\sum_{\sigma}\int_0^\beta\mathrm{d\tau}~\left[c^\dagger_{d\sigma}(\tau)c_{z\sigma}(\tau) + \text{h.c.}\right] + J\int_0^\beta\mathrm{d\tau} \vec{S}_d(\tau)\cdot\vec{S}_{z}(\tau) \\
-	&- \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 - \frac{W}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{z\uparrow}(\tau) - n_{z\downarrow}(\tau)\right)^2 \\
-	&+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\sum_{\sigma}\Delta_{zz,\sigma}(\tau - \tau^\prime)c^\dagger_{z\sigma}(\tau)c_{z\sigma}(\tau^\prime)
-\end{aligned}\end{equation}
-This hybridisation \(\Delta_{zz,\sigma}\) is calculated in the cavity model of the eSIAM, obtained by removing the impurity and the zeroth site from the full model; it is a completely non-interacting system.
-
-One can go one step further and also remove the zeroth site in order to obtain a theory for the impurity site.
-With this choice, the cavity model now also includes the zeroth site, and hence contains the correlation term associated with \(W\).
-The one-particle connection \(V\) will lead to a modified hybridisation \(\mathcal{F}\) for this effective theory; the Kondo terms will generate a susceptibility.
-The resultant action is
-\begin{equation}\begin{aligned}
-	S^{d}_\text{eff} =& \sum_\sigma \int_0^\beta\mathrm{d\tau}~c^\dagger_{d\sigma}(\tau)\partial_\tau c_{d\sigma}(\tau) - \frac{U}{2}\int_0^\beta\mathrm{d\tau}~\left(n_{d\uparrow}(\tau) - n_{d\downarrow}(\tau)\right)^2 \\
-			  &+ \int_0^\beta\mathrm{d\tau}\mathrm{d\tau^\prime}~\left[\sum_{\sigma}\mathcal{F}_{\sigma}(\tau - \tau^\prime)c^\dagger_{i\sigma}(\tau)c_{i^\prime\sigma}(\tau^\prime) + \chi_{d}(\tau - \tau^\prime)\vec{S}_{i}(\tau)\cdot\vec{S}_{i^\prime}(\tau^\prime)\right]
-\end{aligned}\end{equation}
-where \(\mathcal{F}\) is defined in terms of the local correlator of the zeroth site
-\begin{equation}\begin{aligned}
-	\mathcal{F}_\sigma(\tau - \tau^\prime) = V^2 G_1^{(d)}\left(z\sigma\tau; z\sigma\tau^\prime\right) = V^2 \left<c_{z\sigma}(\tau)c^\dagger_{z\sigma}(\tau^\prime)\right>_{(d)}
-\end{aligned}\end{equation}
-with the average computed in the interacting cavity model that has the impurity site removed.
-The interaction arises from the \(W-\)term.
-The susceptibility is also calculated in this interacting cavity model, and follows the same definition as in the bulk model:
-\begin{equation}\begin{aligned}
-	\chi_{d}(\tau - \tau^\prime) = J^2\vec{S}_{z}(\tau)\cdot\vec{S}_{z}(\tau^\prime)~.
-\end{aligned}\end{equation}
-\section{Zero temperature Greens function in frequency domain}
-
-\label{appx-spectral-func}
-
-\subsection{Spectral representation of Greens function}
-The impurity retarded Green's function is defined as
-\begin{equation}\begin{aligned}
-	G_{d\sigma}(t) = -i\theta(t) \left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right>
-\end{aligned}\end{equation}
-where the average \(\left< \right>\) is over a canonical ensemble at temperature \(T\), and \(\mathcal{O}_\sigma\) is the excitation whose spectral function we are interested in.
-What follows is a standard calculation where we write the Green's function in the spectral representation.
-The ensemble average for the operator \(\mathcal{O}_\sigma\) can be written in terms of the exact eigenstates of the Hamiltonian:
-\begin{equation}\begin{aligned}
-	H \ket{n} &= E_n \ket{n}, \quad\left<\mathcal{O}_\sigma\right> &\equiv \frac{1}{Z}\sum_n \braket{n | \mathcal{O}_\sigma | n} e^{-\beta E_n}
-\end{aligned}\end{equation}
-where \(Z = \sum_n e^{-\beta E_n}\) is the partition function and \(\left\{ \ket{n} \right\} \) is the set of eigenfunctions of the Hamiltonian. We can therefore write
-\begin{equation}\begin{aligned}
-	&\left<\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\}  \right> \\
-	&= \frac{1}{Z}\sum_{m}e^{-\beta E_m}\bra{m}\left\{ \mathcal{O}_{\sigma}(t),\mathcal{O}^\dagger_{\sigma} \right\} \ket{m}\\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( \mathcal{O}_{\sigma}(t)\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma}(t)\right) \ket{m} && \left[\sum_n \ket{n}\bra{n} = 1\right]  \\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\bra{m}\left( e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} + \mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}e^{iH^* t}\mathcal{O}_{\sigma}e^{-iH^* t}\right) \ket{m}\\
-	&= \frac{1}{Z}\sum_{m,n}e^{-\beta E_m}\left( e^{i\left( E_m - E_n \right)  t}\bra{m}\mathcal{O}_{\sigma}\ket{n}\bra{n}\mathcal{O}^\dagger_{\sigma} \ket{m} + e^{i\left( E_n - E_m \right)  t}\bra{m}\mathcal{O}^\dagger_{\sigma}\ket{n}\bra{n}\mathcal{O}_{\sigma} \ket{m}\right)\\
-	&= \frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
-\end{aligned}\end{equation}
-The time-domain impurity Green's function can thus be written as (this is the so-called Lehmann-Kallen representation)
-\begin{equation}\begin{aligned}
-	G_{d\sigma} = -i\theta(t)\frac{1}{Z}\sum_{m,n}e^{i\left( E_m - E_n \right)  t}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\\
-\end{aligned}\end{equation}
-We are interested in the frequency domain form.
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega) &= \int_{-\infty}^\infty dt e^{i \left(\omega \right)t}G_{d d}^\sigma(t) \\
-			       &= \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left(\omega + E_m - E_n \right)t}
-\end{aligned}\end{equation}
-To evaluate the time-integral, we will use the integral representation of the Heaviside function:
-\begin{equation}\begin{aligned}
-	\theta(t) = -\frac{1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty \frac{1}{x + i\eta}e^{-ixt}dx
-\end{aligned}\end{equation}
-With this definition, the integral in \(G_{d\sigma}(\omega)\) becomes
-\begin{equation}\begin{aligned}
-	\left(-i\right)\int_{-\infty}^\infty dt \theta(t)e^{i\left( \omega + i0^+ + E_m - E_n \right)t} &= \left(-i\right)\frac{-1}{2\pi i}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x+ i\eta}\int_{-\infty}^\infty dt e^{i\left( \omega + i0^+ + E_m - E_n - x\right)t} \\
-									     &=\frac{1}{2\pi}\lim_{\eta \to 0^+} \int_{-\infty}^\infty dx\frac{1}{x+ i\eta} 2\pi \delta\left( \omega + i0^+ + E_m - E_n - x\right) \\
-									     &=\frac{1}{\omega + E_m - E_n + i0^+}~.
-\end{aligned}\end{equation}
-The frequency-domain Green's function is thus
-\begin{equation}\begin{aligned}
-	G_{d d}^\sigma(\omega) = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\frac{1}{\omega + E_m - E_n + i0^+}
-\end{aligned}\end{equation}
-The infinitesimally positive imaginary part in the denominator shifts the poles onto the lower half of the complex plane, leaving it analytic in the upper half: this is necessary to make the retarded Greens function causal.
-
-\subsection{Real and imaginary parts - The Sokhotski-Plemelj theorem}
-In order to write down the real and imaginary parts of the Greens function, we first prove the {\it Sokhotski-Plemelj} formula:
-\begin{equation}\begin{aligned}\label{SokhotskiPlemelj}
-	\lim_{\eta \to 0^+} \frac{1}{x + i \eta} = P\left(\frac{1}{x}\right) - i \pi \delta(x)~.
-\end{aligned}\end{equation}
-where \(P(f(x))\) is the Cauchy principal value, defined as 
-\begin{equation}\begin{aligned}
-	P\left[\int_{-\infty}^{\infty}\frac{dx}{x}\right] = \int_{-\infty}^{0^-}\frac{dx}{x} + \int_{0^+}^{\infty}\frac{dx}{x}~.
-\end{aligned}\end{equation}
-
-To prove the above identity, we integrate the left-hand side using a test function \(f(x)\):
-\begin{equation}\begin{aligned}\label{twoIntegrals}
-	\lim_{\eta \to 0^+}\int_{-\infty}^{\infty} \text{dx}~\frac{f(x)}{x + i \eta} &= \lim_{\eta \to 0^+}\int_{-\infty}^{\infty} \text{dx}~\frac{f(x)\left( x - i\eta \right) }{x^2 + \eta^2} \\
-																				 &= \lim_{\eta \to 0^+}\int_{-\infty}^{\infty} \text{dx}~f(x)\left[\frac{x}{x^2 + \eta^2} - i\eta\frac{1}{x^2 + \eta^2}\right]
-\end{aligned}\end{equation}
-The first integral can be split into three parts:
-\begin{equation}\begin{aligned}
-	\lim_{\eta \to 0^+}\int_{-\infty}^{\infty} \text{dx}~f(x)\frac{x}{x^2 + \eta^2} &= \lim_{\eta \to 0^+}\lim_{\varepsilon_\to 0^+}\left[\int_{-\infty}^{-\varepsilon} \text{dx}~\frac{f(x) x}{x^2 + \eta^2} + \int_{\varepsilon}^{\infty} \text{dx}~\frac{f(x)x}{x^2 + \eta^2} + \int_{-\varepsilon}^{\varepsilon} \text{dx}~\frac{f(x)x}{x^2 + \eta^2}\right]
-\end{aligned}\end{equation}
-For the first two parts, it is safe to take the limit of \(\eta\), because \(x\) is always non-vanishing there.
-For the third part, we can approximate \(f(x)\) as \(f(0)\) in the neighbourhood \(x \in \left[-\varepsilon, \varepsilon\right], \varepsilon \to 0 \).
-This leaves an odd function \(x/(x^2 + \eta^2)\) as the integrand, being integrated over a symmetric range.
-The third term therefore vanishes.
-In total, we get
-\begin{equation}\begin{aligned}\label{integral1}
-	\lim_{\eta \to 0^+}\int_{-\infty}^{\infty} \text{dx}~f(x)\frac{x}{x^2 + \eta^2} &= \int_{-\infty}^{-\varepsilon} \text{dx}~\frac{f(x)}{x} + \int_{\varepsilon}^{\infty} \text{dx}~\frac{f(x)}{x}  = P\left(\int_{-\infty}^{\infty} \text{dx}~\frac{f(x)}{x}\right) ~.
-\end{aligned}\end{equation}
-To evaluate the second integral of eq.~\ref{twoIntegrals}, we note that the only region in which the integrand is non-zero is when \(|x| \simeq 0\); there, we again approximate \(f(x)\) as \(f(0)\).
-The remaining integral can then be evaluated easily:
-\begin{equation}\begin{aligned}\label{integral2}
-	-i\lim_{\eta \to 0^+}\eta\int_{-\infty}^{\infty} \text{dx}~\frac{f(x)}{x^2 + \eta^2} = -i \lim_{\eta \to 0^+}\eta f(0)\int_{-\infty}^{\infty} \frac{\text{dx}}{x^2 + \eta^2} = -i \pi f(0),
-\end{aligned}\end{equation}
-where we used \(\int \frac{dx}{x^2 + \eta^2} = \frac{1}{\eta} \arctan\left( x/\eta \right) \). Combining eqs.~\ref{twoIntegrals},\ref{integral1} and \ref{integral2}, we get
-\begin{equation}\begin{aligned}
-	\lim_{\eta \to 0^+}\int_{-\infty}^{\infty} \text{dx}~\frac{f(x)}{x + i \eta} = P\left(\int_{-\infty}^{\infty} \text{dx}~\frac{f(x)}{x}\right) - i\pi \int_{-\infty}^{\infty} \text{dx}~f(x)\delta(x)~.
-\end{aligned}\end{equation}
-This proves eq.~\ref{SokhotskiPlemelj}.
-
-The Sokhotski-Plemelj formula allows us to split the spectral representation into a real and an imaginary part:
-\begin{equation}\begin{aligned}
-	G_{d\sigma}^\prime = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)P\left(\frac{1}{\omega + E_m - E_n}\right)\\
-	G_{d\sigma}^{\prime\prime} = -\pi\frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\delta\left(\omega + E_m - E_n\right)~.
-\end{aligned}\end{equation}
-The spectral function, specifically, is defined as follows:
-\begin{equation}\begin{aligned}
-	A_{d\sigma}(\omega) = -\frac{1}{\pi}G_{d\sigma}^\prime = \frac{1}{Z}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left( e^{-\beta E_m} + e^{-\beta E_n}\right)\delta\left(\omega + E_m - E_n\right)
-\end{aligned}\end{equation}
-
-\subsection{Zero temperature spectral function}
-We specialise to zero temperature by taking the limit of \(\beta \to \infty\).
-In both the partition function as well as inside the summation, the only term that will survive is the exponential of the ground state energy \(E_\text{GS}\).
-\begin{equation*}\begin{aligned}
-	Z \equiv \sum_m e^{-\beta E_m} \implies \lim_{\beta \to \infty}Z = d_\text{GS} e^{-\beta E_\text{GS}}, && E_\text{GS} \equiv \text{min}\left\{ E_n \right\} 
-\end{aligned}\end{equation*}
-where \(d_\text{GS}\) is the degeneracy of the ground state. The spectral function then simplifies to
-\begin{equation}\begin{aligned}
-	\label{Gf_lk}
-	A_{d\sigma} &= \frac{1}{d_\text{GS}e^{-\beta E_\text{GS}}}\sum_{m,n}||\bra{m}\mathcal{O}_{\sigma}\ket{n}||^2\left[e^{-\beta E_m}\delta_{E_m, E_\text{GS}} + e^{-\beta E_n}\delta_{E_n, E_\text{GS}}\right]\delta\left(\omega + E_m - E_n\right)\\
-											 &= \frac{1}{d_\text{GS}}\sum_{n,n_\text{GS}}\left[||\bra{n_\text{GS}}\mathcal{O}_{\sigma}\ket{n}||^2\delta\left(\omega + E_\text{GS} - E_n\right) + ||\bra{n}\mathcal{O}_{\sigma}\ket{n_\text{GS}}||^2\delta\left(\omega - E_\text{GS} + E_n\right)\right]\\
-\end{aligned}\end{equation}
-The label \(n_\text{GS}\) sums over all states \(\ket{n_\text{GS}}\) with energy \(E_\text{GS}\).
-In practise, we evaluate this expression by replacing the formal Dirac delta functions with "nascent" ones, such as a Lorentzian function with a sufficiently sharp peak.
-
-\subsection{Reconstructing full Green function from spectral function: Kramers-Kronig relations}
-As mentioned earlier, the retarded Greens function \(G_R(\omega + i 0^+)\) has a complex pole in the lower half of the complex plane.
-In the following, the frequency \(\omega\) is assumed to be complex.
-Consider the integral
-\begin{equation}\begin{aligned}
-	I(\omega) = \oint_C d\omega^\prime \frac{G_R(\omega^\prime)}{\omega^\prime - \omega},~\omega \in \mathbb{R}~.
-\end{aligned}\end{equation}
-The contour \(C\) encloses the entirety of the upper half of the complex plane as well as almost all points of the real line but avoids the pole at \(\omega^\prime = \omega\) by forming a semicircle about that point that extends into the upper half of the plane.
-Since the integrand is completely analytic in the region enclosed by the contour (recall again that \(G_R\) is analytic in the upper half), the integral evaluates to zero (by Cauchy's theorem):
-\begin{equation}\begin{aligned}\label{zerointegral}
-	I(\omega) = 0~.
-\end{aligned}\end{equation}
-One can also evaluate the integral along each part of the contour.
-The semicircular part contributes zero: this is because while the length of the semicircular arc goes as \(|\omega^\prime|\), the integrand vanishes faster than \(1/|\omega^\prime|\) as \(|\omega^\prime| \to \infty\) (this assumes that the Green function vanishes in the limit of \(\omega \to \infty\)).
-The part of the contour along the real axis can now be evaluated.
-The two parts of the contour on either side of the pole contribute
-\begin{equation}\begin{aligned}
-	\int_{-\infty}^{\omega - 0^+}d\omega^\prime~\frac{G_R(\omega^\prime)}{\omega^\prime - \omega} + \int_{\omega + 0^+}^{\infty}d\omega^\prime~\frac{G_R(\omega^\prime)}{\omega^\prime - \omega} = P\int_{-\infty}^{\infty}d\omega^\prime~\frac{G_R(\omega^\prime)}{\omega^\prime - \omega}
-\end{aligned}\end{equation}
-To evaluate the part of the integral along the small semicircular around \(\omega^\prime = \omega\) (that extends into the upper half), we argue that this contribution should be equal to that obtained by taking the semicircle that goes instead into the lower half but circulates in the opposite direction.
-Each of these contributions should, in turn, be equal to that obtained from joining these two contours.
-But joining these contours leads to a closed integral about the pole at \(\omega^\prime = \omega\), which is equal to \(2\pi G_R(\omega)\).
-\begin{equation}\begin{aligned}
-	\int_\text{upper} d\omega^\prime~\frac{G_R(\omega^\prime)}{\omega^\prime - \omega} = \int_\text{lower} d\omega^\prime~\frac{G_R(\omega^\prime)}{\omega^\prime - \omega} = \frac{1}{2}\oint_{C(\omega)} d\omega^\prime~\frac{G_R(\omega^\prime)}{\omega^\prime - \omega} = i\pi G_R(\omega)~.
-\end{aligned}\end{equation}
-Combining the last two equations, we get
-\begin{equation}\begin{aligned}
-	I(\omega) = P\int_{-\infty}^{\infty}d\omega^\prime~\frac{G_R(\omega^\prime)}{\omega^\prime - \omega} + i\pi G_R(\omega)~.
-\end{aligned}\end{equation}
-Comparing with eq.~\ref{zerointegral} and separating into real part \(G_R^\prime\) and imaginary part \(G_R^{\prime\prime}\) gives
-\begin{equation}\begin{aligned}
-	P\int_{-\infty}^{\infty}d\omega^\prime~\frac{\left[G_R^\prime(\omega^\prime) + i G_R^{\prime\prime}(\omega^\prime)\right]}{\omega^\prime - \omega} + \pi\left[-G_R^{\prime\prime}(\omega) + i G_R^\prime(\omega) \right]= 0~.
-\end{aligned}\end{equation}
-Comparing the imaginary parts gives
-\begin{equation}\begin{aligned}
-	G_R^\prime(\omega) = \frac{1}{\pi}P\int_{-\infty}^{\infty}d\omega^\prime~\frac{G_R^{\prime\prime}(\omega^\prime)}{\omega^\prime - \omega} = - \mathcal{H}\left[G_R^{\prime\prime}(\omega)\right] ~,
-\end{aligned}\end{equation}
-where \(\mathcal{H}\left[g(\omega)\right]=\frac{1}{\pi}P\int_{-\infty}^{\infty}d\omega^\prime~\frac{g(\omega^\prime)}{\omega - \omega^\prime}\) is the Hilbert transform of the function \(g(\omega)\).
-The spectral function was defined above as \(-1/\pi\) times the imaginary part of the Greens function.
-Exchanging \(G_R^{\prime\prime}\) for \(A\) gives
-\begin{equation}\begin{aligned}
-	G_R^\prime(\omega) = \pi \mathcal{H}\left[A(\omega)\right]~.
-\end{aligned}\end{equation}
-This provides a method for calculating the real part of a Greens function if the spectral function is already known.
-
-\section{Properties of the Bloch states}\label{BlochProperties}
-
-\subsection{Translation invariance}
-It is easy to verify that \(\Psi_{\vec k}\left(\left\{ {\bf r}_k \right\}  \right) \) transforms like Bloch functions under translation by a displacement \({\bf r}\):
-\begin{equation}\begin{aligned}
-	\Psi_{\vec k}\left(\left\{{\bf r}_k + {\bf r}\right\} \right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i,{\bf a}} e^{i \vec{k}\cdot\vec{R}_i} \psi_\text{aux}\left({\bf r}_i - {\bf r}, {\bf a}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_j, {\bf a}} e^{i \vec{k}\cdot\left(\vec{R}_j + {\bf r}\right)} \psi_\text{aux}\left({\bf r}_j, {\bf a}\right) = e^{i \vec{k}\cdot\vec{R}} \Psi_{\vec k}\left(\left\{ {\bf r}_k \right\} \right)
-\end{aligned}\end{equation}
-In the last equation, we transformed \({\bf r}_i \to {\bf r}_j = {\bf r}_i - {\bf r}\).
-Note that the argument \({\bf a}\) does not change under a translation of the system, because that vector always represents the difference between the impurity lattice position and its nearest neighbours, irrespective of the absolute position of the impurity.
-
-The wavefunction can be even brought into the familiar Bloch function form:
-\begin{equation}\begin{aligned}
-	\Psi^n_{\vec k}\left(\left\{{\bf r}_k\right\}\right) = \sum_{{\bf r}_i, {\bf a}} \frac{e^{i \vec{k}\cdot\vec{R}_i}}{\lambda_{\ket{\vec k}} \mathcal{Z} N} \psi_\text{aux}\left(\left\{ {\bf r}_d - {\bf r}_i, {\bf r_0} - {\bf r}_i - {\bf a} \right\} \right) = \frac{e^{i \vec{k}\cdot\frac{1}{N}\sum_k \vec{r}_k}}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i, {\bf a}} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k{\bf r}_k - \vec{R}_i\right)} \psi_\text{aux}\left(\left\{ {\bf r}_d - {\bf r}_i, {\bf r_0} - {\bf r}_i - {\bf a} \right\} \right) \\
-	= e^{i \vec{k}\cdot\vec{r}_\text{COM}} \eta_{\vec k}\left(\left\{{\bf r}_k\right\}\right)
-\end{aligned}\end{equation}
-where \({\bf r}_\text{COM} = \frac{1}{N}\sum_k {\bf r}_k\) is the center-of-mass coordinate and \(\eta_{\vec k}\left(\left\{{\bf r}_k\right\}\right) = \frac{1}{\lambda_{\ket{\vec k}} \mathcal{Z} N}\sum_{{\bf r}_i} e^{-i \vec{k}\cdot\left(\frac{1}{N}\sum_k{\bf r}_k - \vec{R}_i\right)} \psi^n_\text{aux}\left(\left\{{\bf r}_k - {\bf r}_i\right\}\right)\) is the translation symmetric function.
-This form of the eigenstate allows the interpretation that tuning the Bloch momentum \(\vec k\) corresponds to a translation of the center of mass of the system (or in this case, of the auxiliary models that comprise the system).
-
-\subsection{Orthonormality}
-It is straightforward to show that these states form an orthonormal basis. We start by writing down the inner product of two distinct such states:
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} 
-	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r}_j, {\bf a}^\prime \right) | \psi_\text{aux}\left( {\bf r}_i, {\bf a} \right)} \\
-	&= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) T^\dagger\left( {\bf r_0} - {\bf r}_j \right) T\left( {\bf r_0} - {\bf r}_i \right) | \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
-\end{aligned}\end{equation}
-At this point, we insert a complete basis of momentum eigenkets \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) to resolve the translation operators:
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) T\left( {\bf r}_j - {\bf r}_i \right) \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
-						      &= \frac{1}{\lambda_{\ket{\vec k^\prime}}^* \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf a}, {\bf a}^\prime, \vec q} e^{i \left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right) } \braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) e^{i \vec q \cdot \left( {\bf r}_j - {\bf r}_i \right)} \ket{\vec q}\bra{\vec q} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)} \\
-						      &= \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2} \delta_{\vec k, \vec k^\prime}\sum_{{\bf a}, {\bf a}^\prime}\braket{\psi_\text{aux}\left( {\bf r_0}, {\bf a}^\prime \right) \ket{\vec k}\bra{\vec k} \psi_\text{aux}\left( {\bf r_0}, {\bf a} \right)}\\
-\end{aligned}\end{equation}
-At the last step, we used the summation form of the Kronecker delta function: \(\sum_{{\bf r}_i}e^{i {\bf r}_i \left( \vec k - \vec q \right) }\sum_{{\bf r}_j}e^{i {\bf r}_j \left( \vec q - \vec k^\prime \right) } = N \delta_{\vec k,\vec q}N \delta_{\vec k^\prime,\vec q}\).
-The final remaining step is to identify that the inner products inside the summation are actually independent of the direction \({\bf a}, {\bf a}^\prime\) of the connecting vector, and both are equal to the normalisation factor \(\lambda_{\ket{\vec k}}\):
-\begin{equation}\begin{aligned}
-	\braket{\Psi_{\vec k^\prime} | \Psi_{\vec k}} = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2 } \delta_{\vec k, \vec k^\prime}\sum_{{\bf a},{\bf a}^\prime} |\lambda_{\ket{\vec k}}|^2 = \frac{1}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2 } \delta_{\vec k, \vec k^\prime}w^2 |\lambda_{\ket{\vec k}}|^2 = \delta_{\vec k, \vec k^\prime}
-\end{aligned}\end{equation}
-This concludes the proof of orthonormality.
-
-\subsection{Eigenstates}
-To demonstrate that these are indeed eigenstates of the bulk Hamiltonian, we will calculate the matrix elements of the full Hamiltonian between these states:
-\begin{equation}\begin{aligned}
-	&\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} = \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r}_j, {\bf a}^\prime\right)} H_\text{aux}\left({\bf r}_k\right) \ket{\psi_\text{aux}\left({\bf r}_i, {\bf a}\right)}\\
-	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)} T^\dagger_{{\bf r_0} - {\bf r}_j} T_{{\bf r_0} - {\bf r}_k} H_\text{aux}\left({\bf r_0}\right) T^\dagger_{{\bf r_0} - {\bf r}_k} T_{{\bf r_0} - {\bf r}_i} \ket{\psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
-	&= \frac{1}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2}\sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, {\bf a}, {\bf a}^\prime}e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)} \bra{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)} T^\dagger_{{\bf r}_k - {\bf r}_j} H_\text{aux}\left({\bf r_0}\right) T_{{\bf r}_k - {\bf r}_i} \ket{\psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}
-\end{aligned}\end{equation}
-To resolve the translation operators, we will now insert the momentum eigenstates \(\ket{\vec k}\) of the full model: \(1 = \sum_{\vec q}\ket{\vec q}\bra{\vec q}\) in between the operators.
-\begin{equation}\begin{aligned}
-	\bra{\Psi_{\vec k^\prime}}H_\text{H-H} \ket{\Psi_{\vec k}} &= \sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, \atop{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime}\bra{\vec q^\prime} T^\dagger_{{\bf r}_k - {\bf r}_j} H_\text{aux}\left({\bf r_0}\right) T_{{\bf r}_k - {\bf r}_i}  \ket{\vec q}\braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
-								   &= \sum_{{\bf r}_i, {\bf r}_j, {\bf r}_k, \atop{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime}}\frac{e^{i\left(\vec{k}\cdot\vec{R}_i - \vec{k}^\prime\cdot\vec{R}_j\right)}}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2 N^2} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime} e^{-i \vec q^\prime \cdot \left({\bf r}_k - {\bf r}_j\right) } e^{i \vec q \cdot \left({\bf r}_k - {\bf r}_i\right)} \braket{\vec q^\prime | H_\text{aux}\left({\bf r_0}\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
-								   &= \frac{N}{\lambda^*_{\ket{\vec k^\prime}} \lambda_{\ket{\vec k}} \mathcal{Z}^2}\sum_{{\bf a}, {\bf a}^\prime, \vec q, \vec q^\prime} \delta_{\vec k, \vec q} \delta_{\vec q,\vec q^\prime} \delta_{\vec q^\prime,\vec k} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec q^\prime} \braket{\vec q^\prime | H_\text{aux}\left({\bf r_0}\right) | \vec q}  \braket{\vec q | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
-								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2}\delta_{kk^\prime}\sum_{{\bf a}, {\bf a}^\prime} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec k} \braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k}  \braket{\vec k | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}\\
-								   &= \frac{N}{|\lambda_{\ket{\vec k}}|^2 \mathcal{Z}^2}\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k} \underbrace{\sum_{{\bf a}, {\bf a}^\prime} \braket{\psi_\text{aux}\left({\bf r_0}, {\bf a}^\prime\right)| \vec k} \braket{\vec k | \psi_\text{aux}\left({\bf r_0}, {\bf a}\right)}}_{w^2 |\lambda_{\ket{\vec k}}|^2}\\
-	&= N\delta_{kk^\prime}\braket{\vec k | H_\text{aux}\left({\bf r_0}\right) | \vec k}
-\end{aligned}\end{equation}
-The momentum eigenket \(\ket{\vec k}\) can be expressed as a sum over position eigenkets at varying distances from \({\bf r_0}\).
-This form allows a systematic method of improving the energy eigenvalue estimate, because the interacting in the impurity model is extremely localised, so the overlap between two auxiliary models decreases rapidly with distance.
-The majority of the contribution will come from the state at \({\bf r_0}\), and improvements are then made by considering auxiliary models at further distances.
-
-\section{Greens function in the insulating phase: the Hubbard bands and mottness}
-In the insulating state, the cluster becomes a local moment and the bulk system reduces to the atomic limit \(H = -\frac{U}{2}\sum_i\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2\).
-The Greens function in this limit is that of the atomic limit of the Hubbard model:
-\begin{equation}\begin{aligned}
-	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 + \left<\tau_{i }\right>}{\omega - \frac{U}{2}} + \frac{1 - \left<\tau_{i}\right>}{\omega + \frac{U}{2}}
-\end{aligned}\end{equation}
-where \(\tau_i = \sum_\sigma \hat n_{i,\sigma} - 1\).
-At half-filling \(\left<\tau_{i}\right>=0\), the low and high-energy poles have equal spectral weights.
-\textit{This is different from the situation in a band insulator, where the valence band has all the spectral weight in the ground state while the conduction band is empty.} On doping holes into the system such that \(\left<\tau_{i}\right> = -x < 0\), spectral weight is transferred from the upper Hubbard band at \(\omega = U/2\) to the lower one at \(\omega = -U/2\):
-
-\begin{equation}\begin{aligned}
-	G_{i}(\omega) = \sum_\sigma G_{i,\sigma}(\omega) = \frac{1 - x}{\omega - \frac{U}{2}} + \frac{1 + x}{\omega + \frac{U}{2}}
-\end{aligned}\end{equation}
-\textit{This transfer of spectral weight across energy scales of the order of \(U\), as well as the lack of poles at zero energies, is referred to as mottness}~\cite{phillips2006mottness}.
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.5\textwidth]{hubbard_bands.pdf}
-	\caption{Structure of the Greens function in the atomic limit.
-The two poles at \(\omega = \pm \frac{U}{2}\) form the two Hubbard bands.
-Doping the system leads to transfer of spectral weight between the bands.}
-\end{figure}
-
-\section{Nature of propagation: metal vs insulator}
-In the metallic state, the impurity in the auxiliary model hybridises with the bath through both 1-particle and 2-particle interactions.
-For any two auxiliary models differing by the locations \(i_1, i_2\) of the impurity, the baths will always overlap.
-This means that an electron that starts out from the impurity site at \(i_1\) can hop into the bath, and eventually reach \(i_2\) by hopping out of the other bath and into the other impurity.
-Such processes connect all sites of the lattice and \textit{allow spectral flow}.
-
-In the insulating state, each auxiliary model separates into an impurity and a bath that decoupled from each other.
-This means that the impurity cannot hybridise into the bath, and hence cannot tunnel into any other impurity.
-This leads to the atomic limit of the system, where each site develops a local moment configuration because of the repulsive local correlation, but these local moments cannot communicate with each other, either through spin-exchange processes or by breaking into holons and doublons.
-Any attempt at spectral flow fails because the boundaries of the system become disconnected from each other.
-
-A more accurate picture of the insulating and metallic phases can be obtained by working with a more complicated choice of the cluster.
-For instance, instead of a single impurity, one can take two correlated impurities interacting with each other through a single-particle hopping, and this cluster then interacts with the bath through the usual interactions.
-The ground state of such a cluster is actually a quantum liquid, consisting of the entangled spin and charge degrees of freedom.
-In the metallic state, various members of this liquid such as the holons, doublons and the spinons are free to propagate across the system through the baths.
-In the insulating state, it is this cluster that then gets decoupled from the other clusters.
-The composite degrees of freedom are then unable to propagate outside the cluster, and \textit{the holons and the doublons are bound to each other}~\cite{Mott_1949} within the confines of the cluster.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=0.55\textwidth]{metal_prop.pdf}
-	\caption{Propagation of electrons from one cluster to another through the bath, in the metallic state}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.75\textwidth]{ins_prop.pdf}
-	\caption{The clusters get isolated from each other in the insulator, because they get decoupled from their baths.}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.85\textwidth]{ins_prop_cluster.pdf}
-	\caption{Each cluster is a quantum liquid composed of spin \(\left(\uparrow,\downarrow\right) \) and charge \(\left(0,2\right) \) degrees of freedom.
-In the insulating state, these degrees of freedom get bound within the cluster and are unable to propagate outside.}
-\end{figure}
-
-\section{Presence of two self-energies under symmetry-breaking}
-The effective Hamiltonian that describes either the metallic or the insulating phase has $\mathrm{SU}(2)$ symmetry in both the spin and charge sectors.
-Since the repulsive correlation on the impurity picks out the spin sector, we focus on that for now.
-Applying a small magnetic field on the impurity breaks this spin-rotation symmetry and picks out either the up or the down state on the impurity, leading to two kinds of self-energies, one for each spin state~\cite{logan_2014,Logan_2015}.
-The Hamiltonian has the form \(H(h)_i = -\frac{U}{2}\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)^2 - h\left(\hat n_{i \uparrow} - \hat n_{i \downarrow}\right)\).
-The unique ground-state is \(\ket{\hat n_{i,\sigma = \text{sgn}(h)}=1,\hat n_{i,\sigma = -\text{sgn}(h)}=0}\), with an energy of \(E_\text{gs} = -\frac{U}{2} - h\).
-The Greens function is easiest to obtain from the Lehmann-Kallen representation (eq.~\ref{Gf_lk}):
-\begin{equation}\begin{aligned}
-	G_{i,\sigma} = \sum_{n}\left[||\bra{\text{GS}}c_{i\sigma}\ket{n}||^2\frac{1}{\omega + E_\text{GS} - E_n} + ||\bra{n}c_{i\sigma}\ket{\text{GS}}||^2\frac{1}{\omega - E_\text{GS} + E_n}\right]\\
-\end{aligned}\end{equation}
-We have \(c_{i,\sigma}\ket{\text{GS}} = \ket{\hat n_i = 0}\delta_{\sigma,\text{sgn}(h)}\) and \(c^\dagger_{i,\sigma}\ket{\text{GS}} = \ket{\hat n_i = 2}\delta_{\sigma,-\text{sgn}(h)}\), so that the only excited states that give non-zero inner product is \(\ket{n}=\ket{\hat n_i = 0}\) for the second term and \(\ket{n}=\ket{\hat n_i=2}\) for the first term, with energies \(E_n=0\).
-Substituting these, we get
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(h) = \frac{\delta_{\sigma,-\text{sgn}(h)}}{\omega - \frac{U}{2} - h} + \frac{\delta_{\sigma,\text{sgn}(h)}}{\omega + \frac{U}{2} + h} = \frac{1}{\omega + \left(\frac{U}{2}+h\right)\sigma \times \text{sgn}(h) }
-\end{aligned}\end{equation}
-Taking the limit of \(h \to 0^\pm\) then gives
-\begin{equation}\begin{aligned}
-	G_{i,\sigma}(h=0^\pm) = \frac{1}{\omega \pm \frac{U}{2}\sigma}
-\end{aligned}\end{equation}
-The self-energies arising from the correlation \(U\) can also be obtained using Dyson's equation \(\Sigma = G^{-1} - G_0^{-1}\), where \(G_0^{-1} = \omega\) is the Greens function at \(U=0\).
-Using Dyson's equation, we get
-\begin{equation}\begin{aligned}
-	\Sigma_{i,\sigma} = \pm\frac{U}{2}\sigma
-\end{aligned}\end{equation}
-
-\section{Derivation of RG equations for the embedded e-SIAM}
+Detailed comparisons of the URG with other methods (e.g., the functional RG, spectrum bifurcation RG etc.) can be found in Refs.~[42,43].
+%\cite{anirbanmott1,anirbanurg1}.
+
 \subsection{RG scheme}
@@
 
-\subsubsection*{Arising from the Kondo spin-exchange term}
+%\subsubsection*{Arising from the Kondo spin-exchange term}
+\vspace{0.25cm}
+\par\noindent\textbf{Arising from the Kondo spin-exchange term}\\
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-\subsubsection*{Arising from spin-preserving scattering within conduction bath}
+\vspace{0.25cm}
+\par\noindent\textbf{Arising from spin-preserving scattering within conduction bath}\\
+%\subsubsection*{Arising from spin-preserving scattering within conduction bath}
 \begin{equation}\begin{aligned}
@@
 \end{aligned}\end{equation}
-\subsubsection*{Arising from spin-flip scattering within conduction bath}
+\vspace{0.25cm}
+\par\noindent\textbf{Arising from spin-flip scattering within conduction bath}\\
+%\subsubsection*{Arising from spin-flip scattering within conduction bath}
 \begin{equation}\begin{aligned}
@@
 
-\begin{figure}[htpb]
-	\centering
-	\includegraphics[width=0.35\textwidth]{particleHoleRelation.pdf}
-	\caption{Particle and hole states.}
-	\label{fig:particleHoleRelation-pdf}
-\end{figure}
 \subsection{Renormalisation of the bath correlation term {\it W}}
@@
 The \(|\varepsilon_j|/2\) in \(H_D\) arises from the excited nature of the state after the initial scattering process.
-
-\subsubsection*{Scattering arising purely from spin-preserving processes}
+\vspace{0.25cm}
+\par\noindent\textbf{Scattering arising purely from spin-preserving processes}\\
+%\subsubsection*{Scattering arising purely from spin-preserving processes}
 In this subsection, we calculate the renormalisation to \(W\) arising from the terms \(T_{P1}\), \(T_{P2}\) and \(T_{P3}\). The first term is
@@
 Moreover, the remaining contributions \(T_{P3}^\dagger G_W T_{P1}\) and \(T_{P1}G_W T_{P2}^\dagger\) are effectively hermitian conjugates of the two contributions considered above, and therefore also cancel each other.
-
-\subsubsection*{Scattering arising from spin-flip processes}
+\vspace{0.25cm}
+\par\noindent\textbf{Scattering arising from spin-flip processes}\\
+%\subsubsection*{Scattering arising from spin-flip processes}
 We now come to the processes that involve spin-flips. Considering \(T_{F1}\) and \(T_{F4}\) first, we get
@@
 \end{aligned}\end{equation}
-
-\subsubsection*{Scattering involving both spin-flip and spin-preserving processes}
+\vspace{0.25cm}
+\par\noindent\textbf{Scattering involving both spin-flip and spin-preserving processes}\\
+%\subsubsection*{Scattering involving both spin-flip and spin-preserving processes}
 These processes involve the combination of terms like \(T_{P1}\) with \(T_{F4}\), and \(T_{P2}\) with \(T_{F1}\). These again cancel each other out for the same reasons as outline above.
-
-\subsubsection*{Net renormalisation for the bath correlation term}
+\vspace{0.25cm}
+\par\noindent\textbf{Net renormalisation for the bath correlation term}\\
+%\subsubsection*{Net renormalisation for the bath correlation term}
 Since all the contributions cancel out in pairs, the bath correlation term \(W\) is {\it marginal}.
@@
 For these processes, the intermediate many-body state always involves the impurity spin being anti-correlated with the conduction electron spin, such that the propagator for that state is \(G_J = 1/\left(\omega - |\varepsilon_j|/2 + J_{\bf q}/4 + W_{\bf q}/2)\right) \).
-\subsubsection*{Impurity-mediated spin-flip scattering purely through Kondo-like processes}
+\vspace{0.25cm}
+\par\noindent\textbf{Impurity-mediated spin-flip scattering purely through Kondo-like processes}\\
+%\subsubsection*{Impurity-mediated spin-flip scattering purely through Kondo-like processes}
 The following processes arising from the Kondo term renormalise the spin-flip interaction:
@@
 \end{aligned}\end{equation}
-
-\subsubsection*{Scattering processes involving interplay between the Kondo interaction and conduction bath interaction}
+\vspace{0.25cm}
+\par\noindent\textbf{Scattering processes involving interplay between the Kondo interaction and conduction bath interaction}\\
+%\subsubsection*{Scattering processes involving interplay between the Kondo interaction and conduction bath interaction}
 Looking at \(T_{KT1}^\dagger\) first, we have
@@
 \end{aligned}\end{equation}
-
-\subsubsection*{Net renormalisation to the Kondo interaction}
+\vspace{0.25cm}
+\par\noindent\textbf{Net renormalisation to the Kondo interaction}\\
+%\subsubsection*{Net renormalisation to the Kondo interaction}
 Combining the results from eqs.~\ref{kondoRenorm1}, \ref{kondoRenorm2}, \ref{kondoRenorm3} and \ref{kondoRenorm4}, as well as using the properties \(J_{{\bf \bar q}, {\bf k}_1} J_{{\bf k}_2,{\bf \bar q}} = J_{{\bf q}, {\bf k}_2} J_{{\bf k}_1,{\bf q}} = J_{{\bf k}_2, {\bf q}} J_{{\bf q},{\bf k}_1}\) and \(J_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} = J_{{\bf \bar q}, {\bf q}} W_{{\bf q}, {\bf k}_2, {\bf k}_1, {\bf \bar q}}\), the total renormalisation in the momentum-resolved Kondo coupling \(J^{(j)}\) at the \(j^\text{th}\) step amounts to
@@
 
-\bibliography{tilingProject}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\linewidth]{RGflows.pdf}
+    \caption{Renormalisation group (RG) flow diagram of the lattice model as obtained from a unitary RG analysis of the lattice-embedded impurity model.
+For $|W/J| < |W/J|_\text{PG}$, the flows lead to a Fermi liquid phase, while for $|W/J| < |W/J|_\text{c}$, they lead to a Mott insulator.
+For values in between, the system flows to a Mott metal phase that has a pseudogap in the density of states.}
+    \label{rgflows}
+\end{figure}
+
+\section{Tiling formalism: Mapping from the auxiliary model to the tiled lattice model}
+The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using  the tiling procedure outlined in the main text enjoy a {\it many-body} Bloch's theorem~[55],
+%\cite{stoyanova}, 
+because the tiling procedure restores the translation symmetry of the Hamiltonian.
+This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) can be used to construct eigenstates of the lattice Hamiltonian.
+The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
+
+The state \(\ket{\psi_n\left({\bf r}_d\right)}\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself has been averaged over \(\mathcal{Z}\) zeroth sites.
+Accordingly, we can express the averaged eigenstate \(\ket{\psi_n\left({\bf r}_d\right)}\) as
+\begin{equation}\begin{aligned}
+	\ket{\psi_n\left({\bf r}_d\right)} = \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z} \in \text{NN}({\bf r}_d)}\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}~,
+\end{aligned}\end{equation}
+where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\).
+With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~[55]:
+%\cite{stoyanova}:
+\begin{equation}\begin{aligned}\label{eigenstateProposal1}
+	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d, {\bf z}\right)}~,
+\end{aligned}\end{equation}
+where \(N\) is the total number of lattice sites and \({\bf r}_d\) is summed over all lattice spacings.
+The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands.
+The ground state \(s = s_0\) is obtained by setting \({\bf k}\) and \(n\) to 0:
+\begin{equation}\begin{aligned}\label{groundstateProposal1}
+	\ket{\Psi_\text{gs}} \equiv \ket{\Psi_{s_0}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d, {\bf z}\right)}
+\end{aligned}\end{equation}
+
+The retarded time-domain lattice \(k-\)space Greens function is defined as
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c_{{\bf K}\sigma}(t), c^\dagger_{{\bf K}\sigma} \right\} | \Psi_\text{gs}}~.
+\end{aligned}\end{equation}
+where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(t\): 
+\begin{equation}\begin{aligned}\label{heisenberg}
+	c_{{\bf K}\sigma}(t) = e^{it H_\text{tiled} }c_{{\bf K}\sigma}e^{-i t H_\text{tiled}}~.
+\end{aligned}\end{equation}
+We now proceed to simplify one of the terms of the anticommutator (for simplicity of notation):
+\begin{equation}\begin{aligned}\label{greensFunction1}
+	&\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_{\vec r,\vec \Delta}e^{-i{\bf K}_0\cdot\vec\Delta}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+Using eq.~\ref{eigenstateProposal1} and the identity resolution \(1 = \sum_s\ket{\Psi_s}\bra{\Psi_s}\), eq.~\ref{greensFunction1} becomes
+	\begin{equation}\begin{aligned}\label{greensfunction2}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\vec k_0\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+In order to bring this expression closer to the form of an auxiliary model Greens function, we
+\begin{itemize}
+    \item use the relation $\ket{\psi(\vec r + \Delta)} = T^\dagger(\vec \Delta)\ket{\psi(\vec r)}$, where \(T^\dagger(\vec \Delta)\) translates all lattice sites by the vector \(\vec\Delta\),
+    \item use the property $T\left(\vec a\right) c({\bf K}) T^\dagger\left(\vec a\right) = e^{-i{\bf K}\cdot\vec a}c({\bf K})$,
+    \item make the substitution \(\vec \Delta^\prime \to \vec \Delta^\prime + \vec \Delta\).
+\end{itemize}
+This leads to the expression
+\begin{equation}\begin{aligned}\label{greensfunction3}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~,
+\end{aligned}\end{equation}
+where the sum over \(s=(\vec k, n)\) has been reduced to a sum over the auxiliary model eigenstate index \(n\) because of the Kronecker delta \(\delta\left(\vec k_0 + {\bf K} - \vec k\right)\).
+This can be further simplified by splitting the sum over \(\vec\Delta^\prime\) into positive and negative parts and then making the transformation \(\vec r^\prime \to \vec r^\prime + \vec \Delta^\prime\):
+\begin{equation}\begin{aligned}
+	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime-\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}\right] \\
+																																												   &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\right] \\
+\end{aligned}\end{equation}
+For each pair of \(\vec r^\prime\) and \(\vec\Delta^\prime\), the term within the box brackets has the form of a two-level Hamiltonian between the states \(\ket{\psi_n(\vec r^\prime)}\) and \(\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\), with a tunnelling amplitude \(e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\).
+The term can therefore be written in the eigenbasis of this Hamiltonian:
+\begin{equation}\begin{aligned}
+	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &=\frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right],
+\end{aligned}\end{equation}
+where \(\ket{\chi_n^\pm(\vec r^\prime,\vec\Delta^\prime)} = \frac{1}{\sqrt 2}\left[\ket{\psi_n(\vec r^\prime)} \pm e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime + \vec\Delta^\prime)}\right] \) are the eigenvectors of the tunnelling Hamiltonian with eigenvalues \(\pm 1\) respectively.
+With this basis transformation, we can rewrite eq.~\ref{greensfunction3} as
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
+\end{aligned}\end{equation}
+
+In the present work, we consider only the $\vec r^\prime = \vec r,~\vec\Delta^\prime=0$ component.
+These terms represent those contributions to the total Greens function that arise from excitations that start and end at a specific auxiliary model (at \(\vec r\)), and also evolve dynamically within the same auxiliary model.
+These terms are therefore exactly equal to the auxiliary model Greens function at position \(\vec r\), and are the most dominant contribution due to the localised nature of the impurity model.
+
+Restricting ourselves to just the single auxiliary model contributions gives
+\begin{equation}\begin{aligned}
+		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+We first consider more carefully the transition operator \(\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\) for the 1-particle excitation giving rise to the above Greens function.
+Within our auxiliary model approach, gapless excitations within the lattice model are represented by gapless excitations of the impurity site, specifically those that screen the impurity site and form the local Fermi liquid.
+As a result, the uncoordinated \(\mathcal{T}-\)matrix for the lattice model must be replaced by a combined \(\mathcal{T}-\)matrix within the impurity model that captures those gapless excitations that occur in connection with the impurity, and projects out the uncorrelated excitations that take place even when the impurity site is decoupled from the bath.
+
+In order to construct this auxiliary model \(\mathcal{T}-\)matrix, we note that the impurity site can have both spin and charge excitations.
+Considering both excitations, the modified \(\mathcal{T}-\)matrix that constructs \(k-\)space excitations in correlation with the impurity site are
+\begin{equation}\begin{aligned}\label{tmatrix}
+	\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\left(\sum_{\sigma^\prime}c^\dagger_{d\sigma} + \text{h.c.}\right) + c_{{\bf K}\sigma}\left(S_d^+ + \text{h.c.}\right)~,
+\end{aligned}\end{equation}
+leading to the updated expression for the complete Greens function:
+\begin{equation}\begin{aligned}
+	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
+\end{aligned}\end{equation}
+
+\section{Theory for the nodal non-Fermi liquid: effective Hatsugai-Kohmoto model}
+As the bath interaction \(W\) is tuned through the L-PG phase, the nodal region is the last to decouple from the impurity.
+This allows us to write down a simpler Kondo model near the transition, where only the nodal region is hybridising with the impurity spin through Kondo interactions.
+This is done by retaining only those scattering processes \({\bf k}_1 \to {\bf k}_2\) that originate from and end at \(k-\)points within a small neighborhood of width \(|{\bf q}|\) around the four nodal points: \({\bf k}_1, {\bf k}_2 \in {\bf N} + {\bf q}, |{\bf q}| \ll \pi\), where \({\bf N}\) can be any one of the four nodal points \({\bf N}_{1} = \left(\pi/2, \pi/2\right), {\bf N}_{2} = \left(-\pi/2, \pi/2\right)\) and \({\bf N}_1 + {\bf Q}_1\) and \({\bf N}_{2} + {\bf Q}_2\), where \({\bf Q}_1 = \left(-\pi,-\pi \right)\) and \({\bf Q}_2 = \left( \pi, -\pi \right) \) are the two nesting vectors.
+We assume that the window of \({\bf q}\) is small enough so that the fixed point Kondo coupling values \(J^*({\bf q}_1, {\bf q}_2)\) for the scattering processes involving \({\bf q}_1\) and \({\bf q}_2\) can be replaced by an average value \(J^*\).
+
+With these considerations, the simplified low-energy model near the transition describing the Kondo scattering processes can be written as
+\begin{equation}\begin{aligned}
+	\tilde H_\text{imp-cbath} = J^*\frac{1}{2}\sum_{l=1,2}\sum_{{\bf q}_1, {\bf q}_2}\sum_{\alpha,\beta}{\bf S}_d\cdot{\boldsymbol \sigma}_{\alpha\beta}\left(c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} + c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta}  - c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} \right.\\
+    \left.- c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta}\right)~.
+\end{aligned}\end{equation}
+The label \(l\) can take values 1 or 2, allowing us to consider both the decoupled channels in the PG (associated with \({\bf N}_1\) and \({\bf N}_2\)).
+It also labels the nesting vectors \({\bf Q}_l\) associated with the two sets.
+\(\alpha\) and \(\beta\) indicate spin indices, and \({\bf q}_1\) and \({\bf q}_2\) represent incoming and outgoing momenta in the scattering processes.
+
+Because of the decoupling of the channel \(l=1\) and \(l=2\), we consider only the \(l=1\) channel for the rest of the calculations in this section.
+In order to simplify the Hamiltonian, we define new fermionic operators
+\begin{equation}\begin{aligned}
+	\psi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} + c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~, ~\phi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} - c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~,
+\end{aligned}\end{equation}
+The operator satisfy fermionic anticommutation relations. For convenience, we define new number operators for the sum and relative degrees of freedom:
+\begin{equation}\begin{aligned}
+	s_{{\bf q},\sigma} = {\psi}^\dagger_{{\bf q}} {\psi}_{{\bf q}},~ r_{{\bf q},\sigma} = {\phi}^\dagger_{{\bf q}} {\phi}_{{\bf q}}~.
+\end{aligned}\end{equation}
+We then have the following useful relation between the corresponding number operators \(n = c^\dagger c\):
+\begin{equation}\begin{aligned}\label{numberOperatorRelation}
+	n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma} = s_{{\bf q}, \sigma} + r_{{\bf q},\sigma}~.
+\end{aligned}\end{equation}
+
+In terms of these new degrees of freedom, the auxiliary model Hamiltonian takes the form
+\begin{equation}\begin{aligned}
+	\tilde H = -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow} + \sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}J^*{\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta} + \sum_{{\bf q},\sigma}\varepsilon_{{\bf N}_1 + {\bf q}}\left({\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma} + {\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma}\right),
+\end{aligned}\end{equation}
+where we have considered a simplified form of the bath interaction (for the channel \(l=1\)), taking into account the density-density correlations in \(k-\)space.
+
+For bath interaction strength close to the critical value (\(W \lesssim W_c\)), the fixed point coupling value \(J^*\) is much smaller than \(W\).
+In order to obtain the gapless excitations of the system arising from the presence of the impurity site, we integrate out the impurity dynamics via a Schrieffer-Wolff transformation.
+The perturbation term \(\mathcal{V}\) then consists of Hamiltonian terms that modify the impurity configuration,
+\begin{equation}\begin{aligned}
+	\mathcal{V} = \sum_{{\bf q},\sigma}\varepsilon_{{\bf N}_1 + {\bf q}}\left({\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma} + {\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma}\right) + \sum_{{\bf q}_1, {\bf q}_2}J^*{S}_d^+{\phi}^\dagger_{{\bf q}_1 \downarrow} \phi_{{\bf q}_2 \uparrow} + \text{h.c.}~,
+\end{aligned}\end{equation}
+while the ``non-interacting" Hamiltonian is
+\begin{equation}\begin{aligned}
+	H_D &= -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow}~.
+\end{aligned}\end{equation}
+For the present Hamiltonian, the low-energy state is the one that minimises the bath interaction term \(\tilde H_\text{cbath-int}\).
+High-energy states are obtained by applying, on the state \(\ket{L}\), the excitation operator \(\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2,\bar\sigma}\) or its hermitian conjugate.
+
+The complete second-order renormalised Hamiltonian is
+\begin{equation}\begin{aligned}
+    \Delta \tilde H =& \sum_{{\bf q}, \sigma}\epsilon_{\bf q} r_{{\bf q},\sigma} + \mathcal{U}\sum_{{\bf q}, \sigma}r_{{\bf q} \sigma}r_{{\bf q} \bar\sigma} + \mathcal{U}\sum_{{\bf q}_1 \neq {\bf q}_2, \sigma}\left[r_{{\bf q}_1 \sigma}r_{{\bf q}_2 \bar\sigma} + \phi^\dagger_{{\bf q}_1,\bar\sigma}\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2, \sigma}\phi_{{\bf q}_2, \bar\sigma}\right]~.
+\end{aligned}\end{equation}
+where $\epsilon_{\bf q} = \text{sign}\left(\varepsilon_{{\bf N}_1 + {\bf q}}\right)\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W}$ and $\mathcal{U} = \frac{{J^*}^2}{4W}$.
+
+The ${\bf q}_1={\bf q}_2$ component of the Hamiltonian shows the emergence of the exactly solvable Hatsugai-Kohmoto model~[45,46]
+%\cite{Baskaran1991,Hatsugai1992} 
+at the critical point.
+The correlation term $\mathcal{U}\sum_{{\bf q}, \sigma}r_{{\bf q} \sigma}r_{{\bf q} \bar\sigma}$ leads to a transfer of spectral weight across the Fermi surface and separates the available states into three classes:
+\begin{equation}\begin{aligned}
+\braket{n_{\bf q}} = \begin{cases}
+    2, \quad \epsilon_{\bf q} < -|\mathcal{U}/2|~,\\
+    1, \quad |\mathcal{U}/2| > \epsilon_{\bf q} > -|\mathcal{U}/2|~,\\
+    0, \quad |\mathcal{U}/2| < \epsilon_{\bf q}~.
+\end{cases}
+\end{aligned}\end{equation}
+Different from a Fermi liquid is the emergence of the highly degenerate single-occupied region in the middle, and this gives rise to non-Fermi liquid excitations.
+
+We now discuss the effects of the ${\bf q}_1 \neq {\bf q}_2$ component.
+The first term partially lifts the degeneracy of the central singly-occupied region and allows only zero magnetisation configurations.
+The second term creates gapped excitations involving the regions of zero and double occupancy; these represent subdominant pairing fluctuations of the nodal non-Fermi liquid.
+
+\section{Universal scaling of impurity spectral function}
+In the main manuscript, we demonstrate how the PG phase is characterised by a universal scaling exponent \(\beta\) for the self-energy: \(-1/\Sigma^{\prime\prime}(\omega)\sim 1/\Sigma^{\prime\prime}(0) + \omega^{\beta},~\beta=2\).
+We have verified that a similar behaviour holds for the low-frequency regime of the impurity spectral function (see Fig.~\ref{optical}, left panel).
+We observe that $A_{d}(\omega)$ scales as $A_d(0) + \omega^{2}$ for the pseudogap phase, while $1/A_{d}(\omega)\sim 1/A_{d}(0) + \omega^{2}$ for the Fermi liquid (inset of Fig.~\ref{optical}).
+
+\section{Finite-Frequency Optical Response Through the Pseudogap}
+\begin{figure}[!ht]
+    \includegraphics[width=0.45\linewidth]{Ad_fit.pdf}
+	\hfill
+	\includegraphics[width=0.45\textwidth]{sigma_in.pdf}
+    \caption{Left: Impurity spectral function $A_d(\omega)$ in the local Fermi liquid (inset) and pseudogap (main).
+The PG spectral function is fit to a power law (with the $\omega=0$ contribution subtracted, see figure in the main manuscript for the full spectral function).
+The exponent of the power law comes out to be $n\approx 2$ throughout the PG.
+The local FL spectral function (inset) is fit to a lorentzian (by fitting the inverse to a power law).\\ Right: Optical conductivity $\sigma(\omega)$ for excitations of the impurity model, approximated through the product of the carrier density (taken from the density of states $A(\omega)$) and the lifetime $\tau(\omega)$ (obtained from the inverse scattering rate $-1/\Sigma^{\prime\prime}(\omega)$, where $\Sigma^{\prime\prime}$ is the imaginary part of the self-energy).
+The Fermi liquid (blue) shows a sharp Drude peak at $\omega=0$ due to the presence of long-lived quasiparticles.
+The PG (green, red, orange) shows a shifted Drude peak at a non-zero frequency which is reminiscent of the mid-infrared (MIR) peak seen experimentally in the cuprates.
+Inset shows the robustness of the position of the MIR peak through the PG, indicating that it's a universal feature within the PG of our model.}
+	\label{optical}
+\end{figure}
+To further probe the breakdown of coherent transport in the pseudogap (PG) regime, we examine the product of the impurity spectral function $A(\omega)$ and the scattering lifetime $\tau(\omega)$, which approximates the optical conductivity $\sigma(\omega)$ via a Drude-type relation.
+As shown in the right panel panel of Fig.~\ref{optical}, this quantity exhibits a sharp Drude peak at $\omega = 0$ in the Fermi liquid (FL) regime (blue), consistent with long-lived quasiparticles.
+In stark contrast, the PG regime (green, red, orange) shows a pronounced suppression of low-frequency conductivity and the emergence of a finite-frequency peak centered near $\omega/D \sim 0.3{-}0.4$ (where $D$ is the kinetic energy bandwidth).
+
+Strikingly, this peak shifts very little across the PG regime (see inset of right panel), despite a deepening spectral gap and diverging self-energy.
+Its position lies well below the Mott gap ($\sim 2.5D$), suggesting that it represents an emergent mid-infrared (MIR) excitation intrinsic to the Mott metal characterising the PG.
+This feature closely mirrors the experimentally observed MIR peak in high-T$_\text{c}$ cuprates~\cite{Herr1987,Orenstein1987,Uchida1991}, which has been variously attributed to excitations of electrons bound to vacancies~\cite{Thomas1992Optical}, or the dressing of holes by spin excitations~\cite{Dagotto1994RMP}.
+Its robust energy scale and insensitivity to increasing incoherence imply a universality persisting through the PG, likely rooted in short-range entanglement between deconfined doublons and holons excitations of the Mott metal.
+This is further evidence that the PG metal is not simply a degraded Fermi liquid, but a distinct phase whose optical response is driven by emergent degrees of freedom.
+
+% To further probe the breakdown of coherent transport in the pseudogap (PG) regime, we examine the product of the impurity spectral function $A(\omega)$$ and the scattering lifetime $\tau(\omega)$$, which approximates the optical conductivity $\sigma(\omega)$ via a Drude-type relation.
+As shown in Fig.(REF)[X], this quantity exhibits a sharp Drude peak at $\omega = 0$ in the Fermi liquid (FL) regime, consistent with long-lived quasiparticles.
+In stark contrast, the PG regime (dashed curves) shows a pronounced suppression of low-frequency conductivity and the emergence of a finite-frequency peak centered near $\omega/D \sim 0.3{-}0.4$ (where $D$ is the kinetic energy bandwidth).
+Strikingly, this peak shifts very little across the PG regime, despite a deepening spectral gap and diverging self-energy.
+Its position lies well below the Mott gap ($\sim 2.5D$), suggesting that it represents an emergent mid-infrared excitation intrinsic to the PG–Mott crossover.
+This feature closely mirrors the experimentally observed mid-IR peak in high-T$_{\textrm{c}}$ cuprates (CITE), which has been variously attributed to preformed pairs (CITE), bound holon–doublon states (CITE), or emergent collective modes (CITE).
+Its robust energy scale and insensitivity to increasing incoherence imply a hidden order or resonance persisting across the PG regime, likely rooted in short-range entanglement between deconfined doublons and holons.
+Thus, the PG metal is not simply a degraded Fermi liquid, but a distinct dynamical phase whose optical response encodes the fingerprints of emergent quantum degrees of freedom.
+
+\section{Luttinger’s theorem in the presence of Luttinger surfaces.}
+A natural question is whether Luttinger’s theorem continues to hold in our model in the presence of Luttinger surfaces.
+It has been shown that particle-hole symmetric systems satisfy a generalized version of Luttinger’s theorem~[38],
+%\cite{seki2017topological}, 
+wherein the Luttinger volume $V_L$ is given by the difference between the number of poles and zeros of the single-particle Green’s function enclosed by the FS.
+This statement remains valid even when the self-energy $\Sigma(\mathbf{k}, \omega)$ diverges~[37].
+%\cite{Phillips2013}. 
+In our case, particle-hole symmetry is preserved and the system remains at half-filling, ensuring the total number of occupied states remains constant.
+Prior to the Lifshitz transition, gapless excitations on the FS contribute one pole per momentum state to the Luttinger count.
+Inside the PG phase, these gapless $k$-states persist, but the emergence of gapped regions redistributes spectral weight: doubly occupied states on Luttinger surfaces become energetically favorable due to the attractive $W$-interaction.
+These doubly occupied states are degenerate with the empty states by particle-hole symmetry, and thus, on average, one state remains occupied.
+The net result is that the number of occupied states - hence the Luttinger volume - remains unchanged.
+This argument extends to the MI, wherein the FS is entirely replaced by a Luttinger surface with zero quasiparticle weight.
+
+\section{Reconstructing Fermi liquid theory from local Fermi liquid excitations}
+For $|W| < |W_\text{PG}|$, the impurity spin gets screened by the conduction bath at low temperatures, and the low-energy physics of the impurity model is described by local Fermi liquid excitations at the conduction bath sites nearest neighbour to the impurity~\cite{nozieres1974fermi}:
+\begin{equation}\begin{aligned}
+    H_\text{LFL} = \epsilon \sum_{Z,\sigma} n_{Z\sigma} + U \sum_{Z}n_{Z \uparrow}n_{Z \downarrow},\quad U > 0~,
+\end{aligned}\end{equation}
+where $Z$ sums over the nearest-neighbour sites.
+Given the purely local nature of the effective Hamiltonian and the repulsive interaction $U$, excitations are generated through the local operators $c^\dagger_{Z\sigma}$.
+In order to obtain the excitations of the tiled model, we apply Bloch's theorem to the excitations of the auxiliary model.
+To find the form of the excitation at total crystal momentum ${\bf K}$, we have
+\begin{equation}\begin{aligned}
+    c^\dagger_{Z\sigma} \to \sum_{{\bf r}} e^{-i {\bf K}} c^\dagger_{{\bf r}\sigma} = c^\dagger_{{\bf K},\sigma}~,
+\end{aligned}\end{equation}
+where the specific lattice site ${\bf Z}$ has been replaced with the translated index ${\bf r}$.
+The tiled excitations are therefore one-particle in nature as well, with momentum as a quantum number.
+This shows that local Fermi liquid excitations in the auxiliary model very naturally lead to Fermi liquid excitations in the bulk lattice model.
+
+\section{Heisenberg Model as a low-energy description of the tiled Mott insulator}\label{heisenbergDerivation}
+In the insulating phase, the ground state of each auxiliary model hosts a decoupled local moment.
+Upon applying the tiling procedure, the lattice model ground state becomes that of the Hubbard model in the atomic limit.
+In order to lift the extensive degeneracy of the state, we will now take into consideration inter-auxiliary model virtual scattering processes that were subdominant in the metallic phase and were hence ignored.
+These one-particle scattering processes lead to the emergence of a nearest-neighbour superexchange interaction.
+The calculation is a straightforward application of second order perturbation theory (Schrieffer-Wolff transformation).
+In order to allow virtual fluctuations that can lift the large ground state degeneracy and lower the energy, we consider (perturbatively) the effects of an irrelevant single-particle hybridisation that connects the nearest-neighbour sites.
+
+For simplicity, we consider two impurity sites labelled \(1\) and \(2\) associated with two nearest-neighbour auxiliary models. The ground state subspace is four-fold degenerate:
+\begin{equation}\begin{aligned}
+	\ket{\Psi_L} = \left\{\ket{\sigma_1,\sigma_2}\right\}~,\quad \sigma_i = \pm 1~,
+\end{aligned}\end{equation}
+where \(\sigma_i\) is the spin state of site \(i\).
+This ground state is derived from the following "zeroth order" Hamiltonian that emerges in the local moment phase of the auxiliary models when all scattering processes between the impurity and conduction bath are RG-irrelevant:
+\begin{equation}\begin{aligned}
+	H_0 = -\frac{U}{2}\sum_{i=1,2}\left(n_{i \uparrow} - n_{i \downarrow}\right)^2~;
+\end{aligned}\end{equation}
+the local correlation on the impurity site becomes the largest scale in the problem in this phase and pushes the \(\ket{n_i=2}\) and \(\ket{n_i=0}\) states to high energies.
+This then defines the high-energy subspace for our calculation:
+\begin{equation}\begin{aligned}
+	\ket{\Psi_H} = \ket{C_1,C_2}~,
+\end{aligned}\end{equation}
+where \(C_i\) can take values 0 or 2, indicating that the state \(i\) is either empty or full, respectively.
+Both the double and hole states exist at a charge gap of the order of \(U/2\) above the low-energy singly-occupied subspace defined by the states \(\ket{\Psi_L}\).
+
+In order to allow virtual fluctuations that can lift the large ground state degeneracy and lower the energy, we consider (perturbatively) the effects of an irrelevant single-particle hybridisation that connects the nearest-neighbour sites.
+This perturbation Hamiltonian is therefore of the form
+\begin{equation}\begin{aligned}
+	H_t = \sum_\omega V(\omega) \mathcal{P}(\omega)~\sum_\sigma\left(c^\dagger_{1\sigma}c_{2\sigma} + \text{h.c.}\right) ~,
+\end{aligned}\end{equation}
+where \(V(\omega)\) only acts on states at the energy scale \(\omega\); the renormalisation of \(V\) is encoded in the fact that \(V(\omega)\) is largest for the excited states and vanishes at low-energies: \(V(\omega \to 0) = 0\).
+
+In order to obtain a low-energy effective Hamiltonian for the impurity sites arising from this hybridisation, we integrate out \(H_t\) via a Schrieffer-Wolff transformation.
+This leads to the following second-order Hamiltonian:
+\begin{equation}\begin{aligned}
+	H_\text{eff} = \mathcal{P}_L H_t G\mathcal H_t \mathcal{P}_L~.
+\end{aligned}\end{equation}
+The operator \(\mathcal{P}_L\) projects onto the low-energy subspace \(\ket{\Psi_L}\) - this ensures that we remain in the low-energy subspace at the beginning and at the end of the total process.
+The Greens function \(G = (E_L - H_0)^{-1}\) incorporates the excitation energy to go from the low-energy subspace \(\ket{\Psi}_L\) (of energy \(E_L\)) to the excited subspace \(\ket{\Psi}_H\) of energy \(E_L + U/2\).
+Substituting the form of the perturbation Hamiltonian and the excitation energy into the above expression gives
+\begin{equation}\begin{aligned}\label{effHam1}
+	H_\text{eff} = \frac{V_H^2}{-U/2}\sum_{\sigma,\sigma^\prime} \left[c^\dagger_{1\sigma}c_{2\sigma}c^\dagger_{2\sigma^\prime}c_{1\sigma^\prime} + c^\dagger_{2\sigma}c_{1\sigma}c^\dagger_{1\sigma^\prime}c_{2\sigma^\prime}\right] ~.
+\end{aligned}\end{equation}
+where \(V_H \equiv V(\omega \to U/2)\) is the impurity-bath hybridisation at energy scales of the order of the Mott gap, in the sense of an RG flow.
+Terms with consecutive creation or annihilation operators on the same site are prohibited because each site is singly-occupied in the ground state.
+It is now easy to cast this Hamiltonian into a more recognizable form.
+For \(\sigma^\prime=\sigma\), we get
+\begin{equation}\begin{aligned}
+	\sum_{\sigma}\delta_{\sigma,\sigma^\prime}c^\dagger_{1\sigma}c_{2\sigma}c^\dagger_{2\sigma^\prime}c_{1\sigma^\prime} = \sum_\sigma \left(n_{1\sigma} - n_{1\sigma}n_{2\sigma}\right) ~,
+\end{aligned}\end{equation}
+while \(\sigma=-\sigma^\prime=\pm 1\) gives 
+\begin{equation}\begin{aligned}
+	\sum_{\sigma}\delta_{\sigma,-\sigma^\prime}c^\dagger_{1\sigma}c_{2\sigma}c^\dagger_{2\sigma^\prime}c_{1\sigma^\prime} = -\left(S_1^+ S_2^- + \text{h.c.}\right)~.
+\end{aligned}\end{equation}
+For the latter expression, we introduced the local spin-flip operators \(S_i^\pm\). The expression above it can also be cast into spin variables, using the equations
+\begin{equation}\begin{aligned}
+	\frac{1}{2}\sum_{\sigma}n_{i\sigma} = \frac{1}{2},\\
+    \frac{1}{2}\sum_{\sigma}\sigma n_{i\sigma} = S_i^z,
+\end{aligned}\end{equation}
+where the first equation is simply the condition of half-filling at each site, and the second equation is the definition of the local spin operator in \(z-\)direction.
+Adding and subtracting the equations gives \(n_{i\sigma} = \frac{1}{2} + \sigma S_i^z\)~.
+
+Substituting everything back into eq.~\ref{effHam1} and dropping constant terms gives
+\begin{equation}\begin{aligned}
+	H_\text{eff} = 2\frac{V_H^2}{U/2}\left(2S_1^z S_2^z + S_1^+S_2^- + S_1^-S_2^+\right) = J_\text{eff} {\bf S}_1\cdot{\bf S}_2~,
+\end{aligned}\end{equation}
+where the effective antiferromagnetic Heisenberg coupling is \(J_\text{eff} = \frac{8V_H^2}{U}\).
+
+\section{Additional Results on the Fermi Liquid \& Pseudogap-Mott metal Phases}
+We present additional figures of the spin (Fig.\ref{spinCorr}) and charge (Fig.\ref{cfnode}) correlations in the impurity model, the impurity spectral function (Fig.\ref{specfunc}), the spin correlations (Fig.\ref{tiledSF}), entanglement entropy (Fig.\ref{tiledEntanglement} (upper panel)) and mutual function (Fig.\ref{tiledEntanglement} (lower panel)) of the tiled model in the pseudogap phase.
+All figures presented here are for a $77\times 77$ {\bf k}-space Brillouin zone grid.
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=0.32\textwidth]{SF-500-1.pdf}
+	\includegraphics[width=0.32\textwidth]{SF-500-3.pdf}
+	\includegraphics[width=0.32\textwidth]{SF-500-4.pdf}
+	\caption{\(k-\)space distribution of spin-spin correlation \(\chi_s(d,\vec k)\) between the impurity spin and momentum states in the conduction bath.
+The first shows a mostly uniform distribution of correlations on the Fermi surface for $W=0$.
+The second plot shows the same inside the PG: the antinodal region no longer participates in Kondo screening.
+The last plot represents the nodal metal emerging at the critical point, where the entirety of Kondo screening is carried out by a small neighbourhood about the nodes.}
+	\label{spinCorr}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=0.32\textwidth]{cfnode-700-1.pdf}
+	\includegraphics[width=0.32\textwidth]{cfnode-700-3.pdf}
+	\includegraphics[width=0.32\textwidth]{doubOcc-700-3.pdf}
+	\caption{The first two panels show charge correlation \(\chi_c\) between the node and an arbitrary $k-$point, in the Fermi liquid (first panel) and the PG (second panel).
+While the charge correlations between the node and antinode are very small in the FL, they grow in the PG.
+This is consistent with the growth in double occupancy at the node and antinode in the PG (third panel).}
+	\label{cfnode}
+\end{figure}
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=0.4\linewidth]{Ad_zoomout_77-1500.pdf}
+    \caption{Impurity Spectral function in the FL and PG phases.
+The evolution of the central peak from Kondo resonance to pseudogap is accompanied by dynamical spectral weight transfer to the Hubbard side bands at finite frequencies $\omega\simeq \pm 3$ (in units of the bandwidth).}
+    \label{specfunc}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=0.32\textwidth]{tiled-SF-1.pdf}
+	\includegraphics[width=0.32\textwidth]{tiled-SF-3.pdf}
+	\includegraphics[width=0.32\textwidth]{tiled-SF-4.pdf}
+	\caption{Spin-spin correlations \(\chi_s\) for the {\it tiled model}, between the nodal point \(k_N = \left( -\pi/2, -\pi/2\right)\) and an arbitrary \(k-\)point on the Fermi surface.
+In the absence of bath interaction (first panel), the correlations are somewhat uniformly distributed along the Fermi surface, and quite small.
+This describes the Fermi liquid phase of the lattice model.
+As we enter the pseudogap (second panel and beyond), the spin-correlations near the antinode vanish, indicating that they have been removed from the metallic excitations, while the correlations near the nodal point become enhanced because of the increasingly correlated nature of the metal.}
+	\label{tiledSF}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=0.32\textwidth]{tiled_SEE_k_2000-1.pdf}
+	\includegraphics[width=0.32\textwidth]{tiled_SEE_k_2000-2.pdf}
+	\includegraphics[width=0.32\textwidth]{tiled_SEE_k_2000-3.pdf}
+
+	\includegraphics[width=0.32\textwidth]{tiled_I2_k_N_2000-1.pdf}
+	\includegraphics[width=0.32\textwidth]{tiled_I2_k_N_2000-3.pdf}
+	\includegraphics[width=0.32\textwidth]{tiled_I2_k_edge_2000-3.pdf}
+	\caption{Top panel: Entanglement entropy \(S_\text{EE}({\bf k})\) on the Fermi surface of the tiled model.
+Similar to the correlations, the entanglement in the \(W=0\) model (first panel) remains uniformly spread out over the Fermi surface.
+As the Fermi surface progressively shrinks, the entanglement gets concentrated to the nodal points.
+Bottom panel: Mutual information \(I_2\) between (i) an arbitrary \(k-\)state and the nodal point (first and second plots), and (ii) an arbitrary \(k-\)state and the edge of the disconnected Fermi surface in the pseudogap (third plot).
+The ends of the partial Fermi surface appear to be weakly entangled to the rest of the Fermi surface, while the nodal points remain strongly entangled all the way through to the transition.}
+	\label{tiledEntanglement}
+\end{figure}
+
+%\bibliography{tilingProject}
+%\bibliographystyle{unsrt}
+
+\begin{thebibliography}{99}
+\bibliographystyle{unsrt}
+
+\bibitem{santanukagome}
+Santanu Pal, Anirban Mukherjee, and Siddhartha Lal.
+\newblock Correlated spin liquids in the quantum kagome antiferromagnet at
+  finite field: a renormalization group analysis.
+\newblock {\em New Journal of Physics}, 21(2):023019, feb 2019.
+
+\bibitem{1dhubjhep1}
+Anirban Mukherjee, Siddhartha Patra, and Siddhartha Lal.
+\newblock Fermionic criticality is shaped by fermi surface topology: a case
+  study of the tomonaga-luttinger liquid.
+\newblock {\em Journal of High Energy Physics}, 2021(4):148, Apr 2021.
+
+\bibitem{anirbanmott1}
+Anirban Mukherjee and Siddhartha Lal.
+\newblock Scaling theory for mott{\textendash}hubbard transitions: I. t = 0
+  phase diagram of the 1/2-filled hubbard model.
+\newblock {\em New Journal of Physics}, 22(6):063007, jun 2020.
+
+\bibitem{siddharthacpi}
+Siddhartha Patra and Siddhartha Lal.
+\newblock Origin of topological order in a cooper-pair insulator.
+\newblock {\em Phys. Rev. B}, 104:144514, Oct 2021.
+
+\bibitem{anirban_kondo}
+Anirban Mukherjee, Abhirup Mukherjee, N.~S. Vidhyadhiraja, A.~Taraphder, and
+  Siddhartha Lal.
+\newblock Unveiling the kondo cloud: Unitary renormalization-group study of the
+  kondo model.
+\newblock {\em Phys. Rev. B}, 105:085119, Feb 2022.
+
+\bibitem{Patra_2023}
+Siddhartha Patra, Anirban Mukherjee, and Siddhartha Lal.
+\newblock Universal entanglement signatures of quantum liquids as a guide to
+  fermionic criticality.
+\newblock {\em New Journal of Physics}, 25(6):063002, jun 2023.
+
+\bibitem{Herr1987}
+S.~L. Herr, K.~Kamar\'as, C.~D. Porter, M.~G. Doss, D.~B. Tanner, D.~A. Bonn,
+  J.~E. Greedan, C.~V. Stager, and T.~Timusk.
+\newblock Optical properties of
+  ${\mathrm{la}}_{1.85}$${\mathrm{sr}}_{0.15}$${\mathrm{cuo}}_{4}$: Evidence
+  for strong electron-phonon and electron-electron interactions.
+\newblock {\em Phys. Rev. B}, 36:733--735, Jul 1987.
+
+\bibitem{Orenstein1987}
+Joseph Orenstein, G.~A. Thomas, D.~H. Rapkine, C.~G. Bethea, B.~F. Levine,
+  R.~J. Cava, E.~A. Rietman, and D.~W. Johnson.
+\newblock Normal-state gap transition in cu-o superconductors.
+\newblock {\em Phys. Rev. B}, 36:729--732, Jul 1987.
+
+\bibitem{Uchida1991}
+S.~Uchida, T.~Ido, H.~Takagi, T.~Arima, Y.~Tokura, and S.~Tajima.
+\newblock Optical spectra of
+  ${\mathrm{la}}_{2\mathrm{\ensuremath{-}}\mathit{x}}$${\mathrm{sr}}_{\mathit{x}}$${\mathrm{cuo}}_{4}$:
+  Effect of carrier doping on the electronic structure of the
+  ${\mathrm{cuo}}_{2}$ plane.
+\newblock {\em Phys. Rev. B}, 43:7942--7954, Apr 1991.
+
+\bibitem{Thomas1992Optical}
+G.~A. Thomas, D.~H. Rapkine, S.~L. Cooper, S-W. Cheong, A.~S. Cooper, L.~F.
+  Schneemeyer, and J.~V. Waszczak.
+\newblock Optical excitations of a few charges in cuprates.
+\newblock {\em Phys. Rev. B}, 45:2474--2479, Feb 1992.
+
+\bibitem{Dagotto1994RMP}
+Elbio Dagotto.
+\newblock Correlated electrons in high-temperature superconductors.
+\newblock {\em Rev. Mod. Phys.}, 66:763--840, Jul 1994.
+
+\bibitem{nozieres1974fermi}
+P~Nozieres.
+\newblock A ``fermi-liquid" description of the kondo problem at low
+  temperatures.
+\newblock {\em Journal of Low Temperature Physics}, 17:31, 1974.
+
+\end{thebibliography}
+
 \end{document}

### 2025-12-10 submissions/NPJ/manuscript_Final.tex
started creating referee response

\documentclass[%
 reprint,
superscriptaddress,
groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
aps,superscriptaddress,
pra,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}
% ,bm,color,hyperref
\usepackage{graphicx,braket,color,bm,amsmath,amssymb,natbib}
% \graphicspath{{./figures/}}
%\bibliographystyle{apsrev4-2}

\begin{document}

\title{Mott Criticality as the Confinement Transition of a Pseudogap-Mott Metal}

\author{Abhirup Mukherjee}
\email{am18ip014@iiserkol.ac.in}
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
}
\author{S. R. Hassan}
\email{shassan@imsc.res.in}
\affiliation{The Institute of Mathematical Sciences, HBNI, C.I.T. Campus, Chennai 600 113, India}
\author{Anamitra Mukherjee}
\email{anamitra@niser.ac.in}
\affiliation{School of Physical Sciences, National Institute of Science, Education and Research, HBNI, Jatni 752050, India}
\author{N. S. Vidhyadhiraja}
\email{raja@jncasr.ac.in}
\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
\author{A. Taraphder}
\email{arghya@phy.iitkgp.ac.in}
\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
\author{Siddhartha Lal}
\email{Corresponding author: slal@iiserkol.ac.in}
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
}

\date{\today}

\begin{abstract}
\noindent
A key challenge in quantum matter involves understanding how strong electronic repulsion obtains the breakdown of quasiparticle excitations in a Fermi liquid and the transition into Mott insulation. The difficulty lies in assessing the role of Luttinger surfaces, zeros of the single-particle Greens function that replace the poles lying on the Fermi surface. Luttinger surfaces are observed to proliferate in the pseudogap regime of Mott systems, resulting in Fermi arcs whose gapless excitations remain unknown. Here, we develop a renormalization-based construction of strongly correlated lattice models that captures the emergence of the pseudogap phase and its transition to a Mott insulator. Applying a many-body tiling scheme to the fixed-point impurity model uncovers a lattice model with electron interactions and Kondo physics. At half-filling, the interplay between Kondo screening and bath charge fluctuations in the impurity model leads to Fermi liquid breakdown. 
This reveals a pseudogap phase characterized by a non-Fermi liquid (the Mott metal) residing on nodal arcs, gapped antinodal regions of the Fermi surface, and an anomalous scaling of the electronic scattering rate with frequency. The eventual confinement of holon–doublon excitations of this exotic metal obtains a continuous transition into the Mott insulator. Our results identify the pseudogap as a distinct long-range entangled quantum phase, and offer a new route to Mott criticality beyond the paradigm of local quantum criticality.

\end{abstract}

\maketitle
\par\noindent\textbf{\large Introduction}\\
\noindent
The Landau quasiparticle paradigm~\cite{landau1959theory} underpins our understanding of metallic behaviour, where the screening of long-ranged repulsive interactions between delocalised electrons leads to well-defined excitations that carry the same quantum numbers as free electrons. This remarkable phenomenon - known as adiabatic continuity -  is captured by excitations described by poles of the single-particle Greens function of the interacting system. But what defines metallicity when quasiparticles are no longer well-defined~\cite{Phillips2013Unparticles}? Can a surface of zeros of the Greens function~\cite{dzyaloshinskii2003some}, rather than poles forming a Fermi surface, define an entirely new kind of metal? Could such an exotic state serve as the precursor to Mott localisation driven purely by repulsion, and without invoking magnetic order~\cite{Mott_1949}? These questions necessitate a radical departure in understanding conduction in correlated electron systems beyond the quasiparticle paradigm~\cite{phillips2022}. \\

\noindent
The anomalous pseudogap (PG) phase, observed in the cuprates, exhibits nodal-antinodal dichotomy with spectral weight concentrated on Fermi arcs around the nodal regions~\cite{loeserKapitulnik1996, Norman1998, Hashimoto2014}. In the PG phase of such Mott systems
~\cite{taillefer2010,FradkinRevModPhys2015,Sato2017,DoironLeyraud2017,Mukhopadhyay2019,Naman2021,Masafumi2025,KyungKotliar2006,MacridinAzevedo2006,sakai2009evolution,werner2009momentum,sakai2010doped,lin2010,gull2010momentum,gull2012,Mirzaei2013,gull2013,anirbanmott2,HilleAndergassen2020,Jiang2022,Scheurer2018,Krien2022,Kitatani2023,Sorella2023,Schafer2021,White1998,Ido2018,ProustTaillefer2019,Ponsioen2019,XuZhang2022}, the single-particle Green’s function develops surfaces of zeros, also known as Luttinger surfaces~\cite{Phillips2013,dzyaloshinskii2003some}, that signals a fundamental obstruction to quasiparticle formation. As interaction strength increases, these zero surfaces proliferate, fragmenting the Fermi surface into nodal arcs~\cite{sakai2009evolution,Phillips2013}, violating the Luttinger sum rule by reconfiguring Fermi volume~\cite{seki2017topological}, and breaking an emergent $\mathbb{Z}_2$ symmetry associated with the conservation of spin currents in Fermi liquids~\cite{Anderson2001,Huang2022}. Unlike conventional instabilities driven by poles, this phenomenon marks a topological breakdown of Fermi liquid theory~\cite{Coleman_2001,Phillips2013Unparticles}. We show that this breakdown arises from a strongly entangled, scale-invariant state of quantum matter, one that serves as the parent metal to the Mott insulator in a half-filled lattice model of strongly correlated electrons. This offers a concrete, controlled framework to understand both the non-quasiparticle character of the pseudogap phase and its continuous evolution into a repulsion-driven insulator, in full alignment with Mott's original vision~\cite{Mott_1949}.\\

\begin{figure*}[tbh]
    \centering
    \includegraphics[width=\linewidth]{Figure1_Nature.pdf}
    \caption{Schematic representation of (a): flowchart of theoretical framework adopted by us (see main text for explanation of symbols), (b): phases obtained for the extended Hubbard model in two dimensions at $T=0$, and passage between them.}
    \label{schematic}
\end{figure*}

\noindent
Our approach involves developing a renormalization group (RG)-based impurity-to-lattice framework that reconstructs the low-energy physics of a strongly correlated system from the fixed-point structure of a quantum impurity model (Fig.~\ref{schematic}, left). Starting from a dynamical Anderson impurity embedded in a correlated bath, we solve the system using a unitary RG (URG) approach~\cite{anirbanurg1,anirbanurg2}. We then construct a translation-invariant lattice Hamiltonian through a many-body tiling procedure that preserves non-local correlations and inherits momentum-resolved self-energies and renormalized couplings from the impurity solution. The resulting model is an \textit{extended}-Hubbard Hamiltonian on a two-dimensional square lattice at half-filling, with both on-site repulsion and nearest-neighbour spin exchange interactions. These correlations, derived directly from the impurity dynamics, enable tracking the evolution from the FL to the Mott insulator (MI) via an intermediate PG phase.\\

\noindent
A central insight of our work is that the PG phase hosts a NFL state governed by Kondo frustration and doublon–holon deconfinement~\cite{keimer2015quantum} (Fig.~\ref{schematic}, right). A correlation scale ($W$) in the conduction bath suppresses Kondo screening (with coupling $J$) beyond a critical ratio of $W/J$, triggering the emergence of Luttinger surfaces in the lattice model. This breakdown of quasiparticles begins at the antinodes and progressively engulfs the nodal regions, driving a continuous transformation into the MI. The resulting NFL exhibits a pseudogapped density of states, multipartite long-range entanglement, and a universal scattering rate of the form $\sim (a + b\,\omega^2)^{-1}$ that grows as $\omega \to 0$. At the critical endpoint of this phase, the URG flow identifies a singular NFL described by the Hatsugai–Kohmoto (HK) model~\cite{Hatsugai1992,Baskaran1991,Huang2022}, with fully deconfined holon–doublon excitations.

\noindent
The emergence of Luttinger surfaces alters the anomaly structure associated with the generalized symmetry of the FS~\cite{Altshuler_1998,Heath_2020,lanave2025}. The corresponding topological charge is defined via the Luttinger–Ward functional. This charge is modified by Green’s function zeros, signalling a shift in the underlying anomaly. Within our framework, this reorganization grants topological protection to the RG flows terminating in the PG regime, ensuring the stability of its NFL excitations. These are adiabatically connected to the Hatsugai–Kohmoto model~\cite{Hatsugai1992,Baskaran1991}, reinforcing the interpretation of the PG as a distinct quantum phase. We thus identify the NFL state as a new gapless, long-range entangled phase of correlated matter - the \textit{Mott metal} - whose deconfined holon-doublon excitations are eventually confined across the Mott transition~\cite{Mott_1949}.

\noindent
While we demonstrate our approach for an extended Hubbard model, it applies broadly to correlated quantum systems. The impurity-plus-tiling construction accommodates multi-orbital degrees of freedom, frustrated geometries, and nontrivial band topology. By deriving lattice Hamiltonians directly from renormalized local dynamics - without relying on mean-field approximations - this method preserves nonlocal correlations and enhances momentum-space resolution. It thus provides a versatile and controlled route for engineering strongly correlated models, particularly in regimes where PG formation, NFL scaling, and Mott physics intersect.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth, height=10cm]{fig2.png}
    \caption{(a): Phase diagram of impurity model at strong coupling in $U$ in terms of competing dimensionless Kondo ($J/t$) and bath correlation ($W/t$) couplings. Colourbar represents the fraction of states on the Fermi surface replaced by zeros of the Greens function (Luttinger surface). A pseudogap phase (shaded region) is observed between the local Fermi liquid (red region) and local moment (blue region) phases (b): $k$-space-resolved spin correlation $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$ in the pseudogap phase of the impurity model. Antinodal regions are observed to decouple from Kondo screening of the impurity. (c): Upon tiling, this leads to a 
    $k$-space-resolved antinodal gap in the electronic density of states of the lattice model, corresponding to Luttinger surfaces of zeros. (d)-(f): Initiation of the decoupling of $J_{{\bf k}, {\bf k'}}$ (positive, negative and zeros shown in red, blue and white respectively), with ${\bf k}$ (black circle) at low-energies for ${\bf k}$ corresponding to the node, antinode and a point mid-way between them on the top right arm of the FS respectively with tuning $W/J$. As dictated by the symmetry of $J_{{\bf k}, {\bf k'}}$, the decoupling for a given ${\bf k}$ proceeds via the appearance of zeros (white patches) of $J_{{\bf k}, {\bf k'}}$ for ${\bf k'}$ initially on the nodal regions of adjacent arms, and progresses gradually towards the antinodes. The decoupling ends with the onset of the pseudogap.}
    \label{spinCorr}
\end{figure*}

\vspace{0.25cm}

\begin{figure*}[tbh]
    \centering
    \includegraphics[width=\textwidth]{fig3.pdf}
    \caption{(a): Enhanced charge correlations $\chi_c({\bf k}_1, {\bf k}_2) = \braket{c^\dagger_{{\bf k}_1\uparrow}c^\dagger_{{\bf k}_1\downarrow}c_{{\bf k}_2\downarrow}c_{{\bf k}_2\uparrow} + \text{h.c.}}$ between the nodal and antinodal regions, signalling Kondo breakdown in the pseudogap phase of the impurity model. (b): In turn, the breakdown leads to the gapping of the antinodal regions in the lattice model, seen from the appearance of poles in the imaginary part of the self-energy. (c): The imaginary part of the impurity self-energy $\Sigma^{\prime\prime}(\omega >0)$ possesses a pole at non-zero $\omega$ in the PG that moves towards $\omega=0$ as the Mott transition is approached.}
    \label{chargeCorr}
\end{figure*}

\vspace{0.25cm}
\par\noindent\textbf{\large Tiling Reconstruction of Lattice Model}\\ 
To capture the interplay between Kondo physics and Mott localization, our approach relies on a two-dimensional auxiliary model inspired by insights on the impurity model~\cite{Mukherjee_2023} at the heart of dynamical mean-field theory (DMFT) ~\cite{georges1996} and its extensions ~ \cite{hettler1998,kotliar2001,maier2005}. The model (see Methods for details) consists of a correlated impurity site (with a double occupancy cost $U$) embedded within a correlated conduction bath defined on a square lattice (see Fig.~\ref{schematic}(a)). The impurity site hybridises with the conduction bath sites adjacent to it through one-particle hybridisation $V$ as well as a spin-exchange interaction $J$ arising from fluctuations in local spin densities of the electrons. The conduction bath has minimal correlations in the form of a local correlation term $W$ on the sites that are adjacent to the impurity. Crucially, the Kondo coupling acquires a momentum structure upon Fourier transforming:
\begin{equation}
J_{{\bf k}, {\bf k}^\prime} = \frac{J}{2} \left[ \cos(k_x - k^\prime_x) + \cos(k_y - k^\prime_y) \right],
\end{equation}
which respects the $C_4$ symmetry of the square lattice.

\noindent
To reconstruct a translationally invariant lattice Hamiltonian from the impurity model (with Hamiltonian $\mathcal{H}_\text{aux}$), we define a many-body tiling prescription that embeds the auxiliary impurity system uniformly across the two-dimensional square lattice. Thus,  the tiling process systematically derives the full lattice dynamics from the renormalized fixed-point structure of the impurity. Let ${\bf r}_d$ denote the location of the impurity within a single unit cell. We define the full Hamiltonian by translating this unit cell across all sites of the lattice:
\begin{equation}
\mathcal{H}_\text{tiled} = \sum_{{\bf r}} T^\dagger({\bf r}) \, \mathcal{H}_\text{aux}({\bf r}_d) \, T({\bf r}) - N \mathcal{H}_\text{cbath},
\end{equation}
where $T({\bf r})$ denotes the operator that translates all degrees of freedom by vector ${\bf r}$, and $N$ is the number of lattice sites. Subtracting $N \mathcal{H}_\text{cbath}$ ensures proper normalization and avoids double-counting of bath terms.

\noindent
This procedure yields an effective \textit{extended}-Hubbard model that retains local and nonlocal correlation effects from the original impurity. The resulting Hamiltonian reads:
\begin{equation}
\label{eq:effectiveH}
\begin{aligned}
\hspace*{-0.3cm}\mathcal{H}_\text{tiled} =
&- \frac{\tilde{t}}{\sqrt{\mathcal{Z}}} \sum_{\langle {\bf r}_i, {\bf r}_j \rangle, \sigma} \left( c^\dagger_{{\bf r}_i,\sigma} c_{{\bf r}_j,\sigma} + \text{h.c.} \right) \\
%- \tilde{\mu} \sum_{{\bf r},\sigma} \hat{n}_{{\bf r},\sigma} \\
&+ \frac{\tilde{J}}{\mathcal{Z}} \sum_{\langle {\bf r}_i, {\bf r}_j \rangle} {\bf S}_{{\bf r}_i} \cdot {\bf S}_{{\bf r}_j}
- \frac{\tilde{U}}{2} \sum_{{\bf r}} \left( \hat{n}_{{\bf r}, \uparrow} - \hat{n}_{{\bf r}, \downarrow} \right)^2,
\end{aligned}
\end{equation}
where $\mathcal{Z} = 4$ is the coordination number of the square lattice. The parameters $(\tilde{t}, %\tilde{\mu}, 
\tilde{J}, \tilde{U})$ are renormalized couplings inherited from the impurity solution: $\tilde{t} = t + 2V,\quad \tilde{U} = U + W,
%\quad \tilde{\mu} = 2\mu + \eta,
\quad \tilde{J} = 2J$. A non-zero chemical potential in the bath and/or the impurity can be included to study the effects of doping. Crucially, the eigenstates of $\mathcal{H}_\text{tiled}$ obey a many-body generalization of Bloch’s theorem~\cite{stoyanova} (see Sec.1 of Supplementary Information~\cite{suppmat}), which allows for the exact computation of momentum-resolved observables (presented here for a $77\times 77$ {\bf k}-space Brillouin zone grid). This lattice embedding provides a controlled route to capture low-energy NFL behavior and Mott criticality directly from a quantum impurity model.

\vspace{0.25cm}
\par\noindent\textbf{\large  Pseudogap Formation via Kondo Breakdown}\\
A detailed picture of the PG in the impurity model is obtained from a momentum-resolved breakdown of Kondo screening in the strong-coupling regime $U \gg t$ phase of $H_\text{aux}$. A unitary renormalisation group (URG) scaling analysis~\cite{anirbanurg1} obtains a flow equation of the Kondo coupling \(J^{(j)}_{{\bf k}_1, {\bf k}_2}\) (see Sec.2 of~\cite{suppmat})
\begin{equation}\begin{aligned}\label{KondoRGequation}
	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}~,
\end{aligned}\end{equation}
where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, the sum is over all occupied momentum states \({\bf q}\) of the energy shell \(\varepsilon_j\), and  \({\bf \bar q} = {\bf q} + {\boldsymbol \pi}\) is the particle-hole transformed partner. The bath interaction coupling $W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}$ is found to be marginal under these transformations. While we present a detailed numerical evaluation of the RG equation for $J_{{\bf k}_1, {\bf k}_2}$ (eq.\eqref{KondoRGequation}) below, it is clear that the frustration of Kondo screening due to charge fluctuations (for attractive bath interactions $W<0$) leads to the Mott transition~\cite{Mukherjee_2023}.\\

\noindent
Upon tuning the ratio of the bath and Kondo interactions ($W/J$) from zero to negative values (see phase diagram in Fig.~\ref{spinCorr}(a)), the following phases emerge in the impurity model from the competition between $J$ and $W$ in eq.~\eqref{KondoRGequation}: (i) for $W/J<(W/J)_{\text{PG}}$, an LFL phase (red region), where the entire FS participates in Kondo screening, (ii) for $\frac{W}{J} \in [(\frac{W}{J})_{\text{PG}}, (\frac{W}{J})_c]$ (shaded region), a local PG phase where disconnected parts of the FS around the node participate in Kondo screening, and (iii) a local moment phase for $\frac{W}{J} > (\frac{W}{J})_c$ (blue region), where the impurity remains unscreened at low-energies. These can be visualised from spin correlations, $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$~, as shown in Fig.~\ref{spinCorr}(b) for the PG. The values $(W/J)_{\text{PG}}$ and $(W/J)_c$ are therefore the entry into and exit from the PG phase. Mapping onto the lattice model via tiling (see Sec.~3 of \cite{suppmat}), we observe that RG-induced nodal–antinodal dichotomy in $J_{{\bf k}, {\bf k}^\prime}$ in the impurity model is the microscopic origin of the PG in the lattice model: the extinction of Kondo coherence translates into spectral zeros in the lattice Green’s function (i.e., Luttinger surfaces) at antinodal momenta (Fig.~\ref{spinCorr}(c)). This establishes that the $T=0$ Mott transition of the 2D \textit{extended}-Hubbard model proceeds from FL to MI through an intervening PG phase. A schematic RG flow diagram can be found in the supplementary materials (Fig.~S1).

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig4.pdf}
    \caption{(a): Suppression of quasiparticle residue ($Z_\text{imp}$) as the impurity model is tuned towards the Mott transition. An initial drastic fall in $Z_\text{imp}$ is observed for $W/J \lesssim (W/J)_\text{PG}$ from $0.3$ to around $0.05$, signalling the destruction of the FL with unravelling of Kondo screening. A steady decrease in $Z_{imp}$ is observed in passage through the PG, and is vanishingly small close to the Mott transition due to a divergent self-energy. (b): Growth of unscreened impurity magnetic moment in the pseudogap phase, signalling the breakdown of Kondo screening. (c): The central (Kondo) resonance of the impurity spectral function in the Fermi liquid phase splits into a pseudogap in the PG phase, with its height diminishing rapidly as the Mott transition is approached.
    }
    \label{channelDecoupling}
\end{figure*}
\vspace{0.25cm}
\par\noindent\textbf{\large Unravelling of Kondo Screening}\\
The ${\bf k}$-space anisotropy of Kondo breakdown can be visualized in terms of zeros of $J_{{\bf k}_N, {\bf k}}$, involving spin-flip scattering between the node ${\bf k}_N = (\pi/2, \pi/2)$  and a general wavevector ${\bf k}$.
For any $W/J$, the $\mathcal{C}_{4}$ lattice symmetry dictates that $J_{{\bf k}_N, {\bf k}}$ vanishes if ${\bf k}$ belongs to any of the antinodes or adjacent nodes. Tuning $W/J$ towards $(W/J)_{\text{PG}}$ leads to an unravelling of the Kondo screening: $J_{{\bf k}_N, {\bf k}}$ for ${\bf k}$ close to the adjacent nodes turns RG-irrelevant first, and a patch of zeros subsequently appears in $J_{{\bf k}_N, {\bf k}}$ around this point (Fig.~\ref{spinCorr} (d)). Tuning $W/J$ further extends the patch of zeros towards the antinodes (Fig.~\ref{spinCorr} (e) and (f)). Kondo screening thus unravels by a systematic decoupling of all $J_{{\bf k}_1, {\bf k}_2}$ that connect adjacent quadrants of the Brillouin zone.   
Precisely at $W/J=(W/J)_{\text{PG}}$, the antinode joins this connected region of zeros in $J_{{\bf k}_1, {\bf k}_2}$, marking the decoupling of the antinodes from all other points in the neighbourhood of the FS. This is an interaction-driven Lifshitz transition of the FS, and marks the entry into a PG phase possessing Fermi arcs~\cite{WuFerrero2018}. Importantly, it coincides with an emergent two-channel Kondo (2CK) impurity model, where each channel corresponds to a pair of Fermi arcs on opposite faces of the conduction bath FS. The 2CK nature of the PG is guaranteed by the symmetry of $J_{{\bf k},{\bf k'}}$: $J_{{\bf k},{\bf k'}}= -J_{{\bf k}+{\bf Q},{\bf k'}}=-J_{{\bf k},{\bf k'}+{\bf Q}}$, where ${\bf Q} = (\pi,\pi)$. The PG expands by shrinking these disconnected Fermi arcs towards the respective nodes, leading to nodal metals whose disappearance heralds the Mott transition.

\vspace{0.25cm}
\par\noindent\textbf{\large Momentum-resolved Dynamical Spectral Weight Transfer}\\
Passage through the PG phase is accompanied by a highly structured transfer of spectral weight across the FS. Strong charge fluctuations develop between the nodal and antinodal regions of the FS in the PG regime of the impurity model (Fig.~\ref{chargeCorr} (a)), as captured by the correlator:
\begin{equation}
\chi_c({\bf k}_1, {\bf k}2) = \left\langle
c^{\dagger}_{{\bf k}1 \uparrow} c^{\dagger}_{{\bf k}1 \downarrow} c_{{\bf k}2 \downarrow} c_{{\bf k}_2 \uparrow} + \text{h.c.}\right\rangle~.
\end{equation}
These fluctuations dynamically redistribute low-energy spectral weight from the antinodes to higher energies, leading to selective gap formation. Accordingly, the Luttinger surfaces of the PG~\cite{dzyaloshinskii2003some} coincides with the appearance of poles of the lattice model self-energy $\Sigma ({\bf k},\omega=0)$ near the antinodes; these poles approach the nodes on tuning towards the Mott transition (Fig.~\ref{chargeCorr} (b)). This mirrors the coalescing of finite-frequency poles of the self-energy poles towards zero frequency in the underlying impurity model~(Fig.~\ref{chargeCorr} (c)). See ~\cite{suppmat} (Figs.~S3 and S4) for additional spin and charge correlation results.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig5.pdf}
    \caption{(a): Imaginary part of impurity self-energy $\Sigma^{\prime\prime}(\omega)$ as a function of frequency $\omega$ for Fermi liquid (FL, $|W/J| < 1.79$) and pseudogapped phases (NFL, $|W/J| \geq 1.79$). $\Sigma''(\omega)$ falls to zero as $\omega\to 0$ for the FL, while it attains a peak in the pseudogap. All $\Sigma''(\omega)$ for the NFL are observed to lie above the Mott-Ioffe-Regel (MIR) bound (dashed blue line), while those for the FL lie below. (b): Scaling of $\Sigma^{\prime\prime}(\omega)$ with frequency for Fermi liquid and pseudogapped phases. The FL self-energy fits to $\Sigma^{\prime\prime} \sim \omega^{\alpha}$ with $\alpha\approx 2$, vanishing as $\omega\to 0$, while the NFL self-energy grows as 
$-1/\Sigma^{\prime\prime}(\omega)\sim -1/\Sigma^{\prime\prime}(0) + \omega^{\beta}$,    
%$\Sigma^{\prime\prime} \approx a + b\omega^{\beta}$ for small $\omega$, 
with $\beta\approx 2$. Remarkably, the NFL exponent remains mostly unchanged through the entirety of the PG phase. (c): Variation of the zero-frequency imaginary self-energy $-\Sigma''(\omega=0)$ with $\omega$ in the FL and pseudogap phases (entry into the PG is marked by the vertical dashed line). The inset shows the same but in linear scale, in order to display the dramatic rise (by almost 30 times) on entering the PG.}
    \label{selfEnergy}
\end{figure*}

\vspace{0.25cm}
\par\noindent\textbf{\large Non-Fermi liquid excitations within the Pseudogap}\\
In the PG regime, the nature of gapless Fermi arcs changes dramatically. We have already argued that the low-energy dynamics of these gapless Fermi arcs are governed by an underlying two-channel Kondo (2CK) impurity model~\cite{Tsvelick_weigmann_mchannel_1985, emery_kivelson}. This is consistent with the rapid fall of the impurity quasiparticle residue $Z_\text{imp}$ (Fig.~\ref{channelDecoupling} (a)) from finite values in the FL phase to vanishingly small values just before the onset of the PG. Fig.~\ref{channelDecoupling} (b) shows the simultaneous emergence of increasingly uncompensated local magnetic moments upon traversing the PG phase. The accompanying impurity spectral function of the gapless arcs show a pseudogapped behaviour for $\omega\simeq 0$, with a rapid fall in the spectral weight at $\omega=0$ upon traversing the PG~(Fig.~\ref{channelDecoupling} (c)). The collapse of the Kondo resonance into a pseudogapped spectral function is accompanied by the redistribution of spectral weight~\cite{dzyaloshinskii2003some} in the impurity spectral function from $\omega\sim 0$ to the Hubbard sidebands at finite frequencies $\omega\simeq \pm 3$ (in units of the bandwidth) (Fig.~S5 of \cite{suppmat}). Concomitant with this is the emergence of a zero-frequency peak in the imaginary part of the self-energy of the NFL in the PG phase, $-1/\Sigma^{\prime\prime}(\omega)\sim -1/\Sigma^{\prime\prime}(0) + \omega^{\beta}$
%$-\Sigma''(\omega)\sim (a + \omega^{\beta})^{-1}$~, with $a$ being a constant
~(Fig.\ref{selfEnergy} (a)). Remarkably, we find that the exponent $\beta=2$ characterises the NFL for the entire PG phase (see Fig.~\ref{selfEnergy}(b)), including the critical end-point. This is in stark contrast with the $\Sigma''(\omega)\sim \omega^{2}$ for the FL (Fig.~\ref{selfEnergy}(b)). A similar analysis reveals the power-law scaling for the low-frequency behaviour of the impurity spectral function (see Fig.~S2 (left) and Sec.V of \cite{suppmat}): $A_{d}(\omega)\sim A_d(0) + \omega^{2}$ for the pseudogap phase, while $1/A_{d}(\omega)\sim 1/A_{d}(0) + \omega^{2}$ for the Fermi liquid.

\noindent
All $\Sigma''(\omega)$ for the NFL are observed to lie above the Mott-Ioffe-Regel (MIR) bound~\cite{GunnarssonRMP2003,Hussey2004} (dashed blue line in Fig.\ref{selfEnergy} (a)), while those for the FL lie below. The MIR bound is the maximum expected scattering rate in metals when the mean free path approaches the lattice spacing: 
$-2\Sigma^{\prime\prime}_\text{MIR} = 1/\tau_\text{MIR}~, ~\tau_\text{MIR} = l_\text{min}/v_{F}$~,where $l_\text{min}$ is the minimum mean free path in metals (equal to one lattice spacing) and $\tau_\text{MIR}$ is the associated lifetime of quasiparticles close to the FS (with Fermi velocity $v_F$). The transport lifetime $\tau (\omega)$ of the NFL thus undergoes a suppression as $\omega \to 0$, together with a shift of the Drude peak to finite $\omega$~\cite{Hussey2004,pustogow2021,qazilbash2008} (see Fig.~S2 (right) and Sec.VI in \cite{suppmat}). The height of the zero-frequency peak rises by almost 4 orders of magnitude from the start of the PG till its end at the Mott transition point (Fig.\ref{selfEnergy}(c)); the dramatic growth of the peak height very near the Mott critical point coincides with the coalescing of the finite-frequency poles of the self-energy into a single pole at zero-frequency, signalling the singular nodal NFL present at the Mott quantum critical point.

\vspace{0.25cm}
\par\noindent\textbf{\large Non-local nature of the Pseudogap}\\
In Fig.~\ref{longranged}(a) and (b), the spin-flip correlations and mutual information between the impurity spin and conduction bath sites respectively are observed to undergo a crossover within the PG, from a short-ranged behaviour at its onset, to a long-ranged behaviour near the Mott transition. The entanglement is observed to be multipartite in nature: in Fig.~\ref{longranged}(c), the quantum Fisher information (QFI)~\cite{Hauke2016} computed for the ground state wavefunction using an operator corresponding to the sum of local spin-flip exchange processes shows a jump at the onset of the PG. Further, the FL is observed to possess bi-partite entanglement while the NFL of the PG phase displays 5-partite entanglement~\cite{balut2025,mazza2024}. See ~\cite{suppmat} (Figs.~S6 and S7) for additional spin correlations and entanglement measures in momentum space for the tiled model.\\

\noindent
These striking results imply that the Mott transition observed by us lies beyond the local quantum criticality scenario~\cite{Si2001}. Instead,  we observe the PG phase to be a novel state of strongly interacting quantum matter emergent from the breakdown of local Kondo screening. This state is described by a quantum critical Fermi surface~\cite{senthil2008CriticalFermiSurface} with NFL Fermi arcs that display increasingly critical behaviour, i.e., dynamics described by non-local quantum fluctuations, and excitations that become truly long-ranged close to the transition. It is tempting to conjecture that the long-range entangled critical state captured in Fig.~\ref{longranged}(b) reflects the existence of a highly efficient fast scrambler~\cite{sekino2008,hayden2007,bentsen2019}, i.e., a state in which entanglement spreads among its constituents at the fastest rate permissible by quantum mechanics.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig6.pdf}
    \caption{Spin correlation $\braket{{\bf S}_d \cdot {\bf S}_r}$ (a) and mutual information $I_{2}(d,r)$ (b) between the impurity spin and conduction bath local spin density as a function of the distance {\bf r} between them, normalised against the value at $r=1$. Both decay very quickly in the FL phase (blue), but show long-ranged behaviour in the NFL phase (green and red), extending to the edges of the system at the critical point (red). (c): Evolution of the Quantum Fisher Information $F_Q$ for a nearest-neighbour spin-flip operator $\mathcal{O} = \sum_{i \in \text{odd}}(S_i^+S_{i+1}^- + \text{h.c.})$ through the first Lifshitz transition and the pseudogap. The vertical dashed line marks the onset of the PG. To the left of it, the QFI in the Fermi liquid phase shows at most bipartite entanglement ($F_Q < 2$ (below blue dashed line)), while the PG shows the presence of multipartite entanglement upto 5 parties ($F_Q > 4$ (above red dashed line)).}
    \label{longranged}
\end{figure*}

\vspace{0.25cm}
\par\noindent\textbf{\large Exactly solvable nodal Non-Fermi liquid at Mott Criticality}\\
Very close to the transition, the excitations of the nodal NFL correspond to those of a Hatsugai-Kohmoto model~\cite{Baskaran1991,Hatsugai1992}. This insight is obtained from a perturbation-theoretic treatment of the RG fixed point Hamiltonian of the impurity model for $W/J\lesssim (W/J)_{\text{PG}}$, by considering the effects of a small fixed point Kondo scattering probability \(J^*\) in the backdrop of a larger bath interaction parameter \(|W|\). This yields the HK model~\cite{Baskaran1991,Hatsugai1992} as the singular part of the effective Hamiltonian arising from forward scattering processes (see Sec.4 of \cite{suppmat}):
\begin{equation}\begin{aligned}\label{HKModel}
	\Delta \tilde H_{{\bf q}_1 = {\bf q}_2} = \sum_{{\bf q},\sigma}\epsilon_{{\bf q}}{n}_{{\bf q},\sigma} + \mathcal{U}\sum_{{\bf q}, \sigma}n_{{\bf q} \sigma} n_{{\bf q} \bar\sigma}~,
\end{aligned}\end{equation}
where the number operator \(n_{{\bf q} \sigma} = \phi^\dagger_{{\bf q}, \sigma} \phi_{{\bf q}, \sigma}\) pertains to emergent fermionic relative modes $\phi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} - c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)$ that are shifted by an excitation momentum \({\bf q}\) away from the nodal point \({\bf N}_1 = \left(\pi/2, \pi/2\right)\) and its 
partner \({\bf N}_1 + {\bf Q}_1 = \left(-\pi/2, -\pi/2\right)\). The kinetic energy \(\epsilon_{\bf q}\) and interaction energy \(\mathcal{U}\sim J^{2}/W\) are dispersion and Kondo scales renormalised by conduction bath correlations (see Sec.4 of \cite{suppmat}).\\

\noindent
Consequently, the resulting NFL metal of the lattice model involves long-lived excitations of multiple \({\bf k}\)-states, and manifest in the form of a divergent one-particle self-energy at the non-interacting FS~\cite{Phillips2020}:
$\Sigma_{{\bf q}}(\omega) = -\mathcal{U}^2/4(\omega - \epsilon_{\bf q})$~, such that $\Sigma_{\epsilon_{\bf q}=0}(\omega \to 0)  \to \infty$. This zero-frequency self-energy pole presages the transition into a Mott insulating phase, where it marks a hard gap in the spectral function for charge excitations. This is consistent with our findings for the lattice (Fig.~\ref{chargeCorr}(c)) and impurity self-energies~(Fig.\ref{selfEnergy} (c)). The nodal Mott metal thus comprises of a Greens function zero at the Fermi energy together with an anistropic massless Dirac dispersion, leading to a non-zero Chern number~\cite{vafekvishwanath2014,morimoto2016,calderon2025}. This topological index survives into the Mott insulator.\\

\noindent For small but non-zero values of \(\omega - \epsilon_{\bf k}\), we obtain a quasiparticle residue that vanishes with $\omega$, \(Z_\text{imp} \sim \omega^2/\mathcal{U}^2 \). The scattering rate of this singular NFL possesses a sharp peak at the FS (\(\omega=\epsilon_{\bf k_{\mathrm{F}}}\)): \(\Gamma \sim \mathcal{U}^2\delta(\omega - \epsilon_{\bf k})\), consistent with the sharply peaked Lorentzian $\Sigma''_{{\bf k}}(\omega)\sim \omega^{-2}$ captured in Fig.\ref{selfEnergy}(a). This quantum critical NFL metal is an example of a strongly coupled scale-invariant form of quantum matter. The exact solution for eq.\eqref{HKModel} reveals the presence of low-energy excitations comprised of holons and doublons~\cite{Hatsugai1992}. These features point to the nodal NFL as a long-ranged and multipartite entangled, strongly interacting scale-invariant state of quantum matter 
~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} that are completely disconnected from the quasiparticles of the FL. Following the arguments laid out in~\cite{phillips2022}, at finite temperatures, such a scale-invariant highly entangled non-Fermi liquid is likely associated with Planckian dissipation (i.e., $\Sigma'' (T)\sim k_{B}T$) and a resistivity that varies linearly with temperature ($\rho\sim T$)~\cite{zaanen2019,legros2019,hartnoll2022}. This sits well with the possibility that this state is also a highly efficient scrambler~\cite{sekino2008,hayden2007,bentsen2019}. Additionally, we observe that the nodal metal possesses pairing fluctuations (see Sec.4 of \cite{suppmat}) that can become dominant upon doping~\cite{Phillips2020}.
\vspace{0.25cm}
\par\noindent\textbf{\large Pseudogap as a strongly coupled phase of quantum matter}\\
We now unveil an organising principle that leads to the remarkable properties observed above for the strongly interacting NFL of the PG phase. The existence of a sharp connected FS at $T=0$ can be understood as the existence of a topologically protected manifold of gapless chiral excitations in ${\bf k}$-space at the FS~\cite{Heath_2020}. The FS is characterised by a topological index corresponding to an anomaly in the quantum many-body theory for electrons, and can be understood as a generalised symmetry of such a system~\cite{lanave2025,McGreevy2023}. A theorem by Luttinger and Ward~\cite{luttinger1960ground} shows that a count of the physical charge (known as Luttinger's volume) is identical to the topological index (a so-called homotopy charge known as Luttinger's count) even in the presence of electronic interactions that do not disturb the FS. We will now argue that the emergence of antinodal Luttinger surfaces involve a disconnection of the FS (into Fermi arcs) and that, by following La Nave et al.~\cite{lanave2025}, the accompanying change in its topological properties leads to the existence of gapless NFL excitations that are non-local in nature.\\

\noindent
The antinodal Luttinger surfaces arise from the splitting of double poles of the single-particle Greens function on the FS into poles lying on opposite complex half-planes, together with zeros that are pinned at the FS. These changes in the analytic structure of the single-particle Greens function have important consequences. First, the emergent zeros break a $\mathbb{Z}_{2}$ symmetry of the FS~\cite{Anderson2001,Huang2022,lanave2025}. This symmetry is guaranteed within FL theory because the presence of quasiparticles vanishingly close to the FS allows the interchange of spin and charge degrees of freedom, promoting the separate $SU(2)$ symmetries of spin and charge to the larger symmetry of $O(4) = SU(2) \times SU(2) \times \mathbb{Z}_2$~\cite{Anderson2001}. The insertion of zeros of the Greens function at the Fermi surface in the PG, and the associated splitting of the Greens function, breaks this $\mathbb{Z}_{2}$ symmetry by placing the pole for the spin excitation in one half of the complex plane while placing that for the charge excitation in the other half~\cite{su2025anomalies,Huang2022}.

\noindent
Second, they signal a divergent electronic self-energy as a function of the wavevector ${\bf k}$, render ill-behaved the Luttinger-Ward functional of the interacting electronic problem, and violate the generalised symmetry encoded within it. The changes in the pole structure change the Luttinger count topological invariant, while the zeros give rise to an additional topological contribution (linked to the Adler-Bell-Jackiw-type chiral anomaly)~\cite{adler1969axial,bell1969pcac,Altshuler_1998,calderon2025}. As a consequence of the half-filled particle-hole symmetric nature of the system at hand, Luttinger's volume is preserved upon taking into account topological contributions from both the Luttinger count {\it and} the zeros~\cite{seki2017topological}. Importantly, La Nave et al.~\cite{lanave2025} argue, following recent developments in understanding generalised symmetries~\cite{Casini2021Symmetries}, that the additional anomaly arising from the Luttinger surfaces guarantees the existence of gapless NFL excitations that are non-local in nature.

\noindent
Thus, the drastic change in nature of the real-space excitations - from locally well-defined Landau quasiparticles of the FL to the increasingly nonlocal excitations of the NFL Fermi arcs in the PG phase - appears to be dictated by a topological principle and, therefore, robust under renormalisation. This signals the NFL Fermi arcs of the PG as an emergent phase of strongly interacting quantum matter - which we dub the {\it Mott metal} - that is the parent metal of the MI. The same topological principle connects the nonlocal unparticle-like gapless excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} of the scale-invariant nodal NFL of the HK model observed precisely at the Mott critical point to those of the rest of the PG phase, e.g., a universal scaling of $-1/\Sigma^{\prime\prime}(\omega)\sim -1/\Sigma^{\prime\prime}(0) + \omega^{2}$ of the NFL throughout the PG phase (Fig.~\ref{selfEnergy} (a)) such that $\Sigma''(\omega=0)$ continues to grow upon violating the MIR bound, and a local density of states $A_{d}(\omega) \sim \omega^{2}$ (see Fig.~S2 (left) of \cite{suppmat}). 
\vspace{0.25cm}
\par\noindent\textbf{\large Conclusions}\\
Our analysis reveals that the Mott transition proceeds via a continuous evolution through a PG regime characterized by a singular NFL metal - the Mott metal - with deconfined holon–doublon excitations confined to nodal Fermi arcs, and a scaling of it's spectral features with universal power-law exponents. As the system approaches criticality, this metallic phase exhibits increasingly non-local correlations and a divergent self-energy, signalling the breakdown of Landau quasiparticles, formation of local moments and the onset of long-range quantum entanglement. Anchored in two-channel Kondo dynamics at intermediate scales and governed by Hatsugai–Kohmoto physics near the critical endpoint, the Mott metal provides a unified framework for understanding anomalous metallicity in strongly correlated systems. It's fate under finite doping presents a compelling direction for future investigation.

%\begin{thebibliography}{99}
%\makeatletter
%\providecommand \@ifxundefined [1]{%
% \@ifx{#1\undefined}
%}%
%\providecommand \@ifnum [1]{%
% \ifnum #1\expandafter \@firstoftwo
% \else \expandafter \@secondoftwo
% \fi
%}%
%\providecommand \@ifx [1]{%
% \ifx #1\expandafter \@firstoftwo
% \else \expandafter \@secondoftwo
% \fi
%}%
%\providecommand \natexlab [1]{#1}%
%\providecommand \enquote  [1]{``#1''}%
%\providecommand \bibnamefont  [1]{#1}%
%\providecommand \bibfnamefont [1]{#1}%
%\providecommand \citenamefont [1]{#1}%
%\providecommand \href@noop [0]{\@secondoftwo}%
%\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
%\providecommand \@href[1]{\@@startlink{#1}\@@href}%
%\providecommand \@@href[1]{\endgroup#1\@@endlink}%
%\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
%  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
%\providecommand \@@startlink[1]{}%
%\providecommand \@@endlink[0]{}%
%\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
%\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
%\providecommand \urlprefix  [0]{URL }%
%\providecommand \Eprint [0]{\href }%
%\providecommand \doibase [0]{https://doi.org/}%
%\providecommand \selectlanguage [0]{\@gobble}%
%\providecommand \bibinfo  [0]{\@secondoftwo}%
%\providecommand \bibfield  [0]{\@secondoftwo}%
%\providecommand \translation [1]{[#1]}%
%\providecommand \BibitemOpen [0]{}%
%\providecommand \bibitemStop [0]{}%
%\providecommand \bibitemNoStop [0]{.\EOS\space}%
%\providecommand \EOS [0]{\spacefactor3000\relax}%
%\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
%\let\auto@bib@innerbib\@empty
%%</preamble>
%
%\bibitem [{\citenamefont {Landau}(1957)}]{landau1959theory}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
%  {Landau}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Soviet
%  Physics Jetp-Ussr}\ }\textbf {\bibinfo {volume} {3}},\ \bibinfo {pages} {920}
%  (\bibinfo {year} {1957})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2013)\citenamefont
%  {Phillips}, \citenamefont {Langley},\ and\ \citenamefont
%  {Hutasoit}}]{Phillips2013Unparticles}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
%  {Phillips}}, \bibinfo {author} {\bibfnamefont {B.~W.}\ \bibnamefont
%  {Langley}},\ and\ \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont
%  {Hutasoit}},\ }\href {https://doi.org/10.1103/PhysRevB.88.115129} {\bibfield
%  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
%  {88}},\ \bibinfo {pages} {115129} (\bibinfo {year} {2013})}\BibitemShut
%  {NoStop}%
%\bibitem [{\citenamefont {Dzyaloshinskii}(2003)}]{dzyaloshinskii2003some}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
%  {Dzyaloshinskii}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
%  {Physical Review B}\ }\textbf {\bibinfo {volume} {68}},\ \bibinfo {pages}
%  {085113} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Mott}(1949)}]{Mott_1949}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~F.}\ \bibnamefont
%  {Mott}},\ }\href {https://doi.org/10.1088/0370-1298/62/7/303} {\bibfield
%  {journal} {\bibinfo  {journal} {Proceedings of the Physical Society. Section
%  A}\ }\textbf {\bibinfo {volume} {62}},\ \bibinfo {pages} {416} (\bibinfo
%  {year} {1949})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2022)\citenamefont
%  {Phillips}, \citenamefont {Hussey},\ and\ \citenamefont
%  {Abbamonte}}]{phillips2022}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
%  {Phillips}}, \bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
%  {Hussey}},\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
%  {Abbamonte}},\ }\href {https://doi.org/10.1126/science.abh4273} {\bibfield
%  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
%  {377}},\ \bibinfo {pages} {eabh4273} (\bibinfo {year} {2022})}\BibitemShut
%  {NoStop}%
%\bibitem [{\citenamefont {Loeser}\ \emph {et~al.}(1996)\citenamefont {Loeser},
%  \citenamefont {Shen}, \citenamefont {Dessau}, \citenamefont {Marshall},
%  \citenamefont {Park}, \citenamefont {Fournier},\ and\ \citenamefont
%  {Kapitulnik}}]{loeserKapitulnik1996}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~G.}\ \bibnamefont
%  {Loeser}}, \bibinfo {author} {\bibfnamefont {Z.-X.}\ \bibnamefont {Shen}},
%  \bibinfo {author} {\bibfnamefont {D.~S.}\ \bibnamefont {Dessau}}, \bibinfo
%  {author} {\bibfnamefont {D.~S.}\ \bibnamefont {Marshall}}, \bibinfo {author}
%  {\bibfnamefont {C.~H.}\ \bibnamefont {Park}}, \bibinfo {author}
%  {\bibfnamefont {P.}~\bibnamefont {Fournier}},\ and\ \bibinfo {author}
%  {\bibfnamefont {A.}~\bibnamefont {Kapitulnik}},\ }\href
%  {https://doi.org/10.1126/science.273.5273.325} {\bibfield  {journal}
%  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {273}},\ \bibinfo
%  {pages} {325} (\bibinfo {year} {1996})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Norman}\ \emph {et~al.}(1998)\citenamefont {Norman},
%  \citenamefont {Ding}, \citenamefont {Randeria}, \citenamefont {Campuzano},
%  \citenamefont {Yokoya}, \citenamefont {Takeuchi}, \citenamefont {Takahashi},
%  \citenamefont {Mochiku}, \citenamefont {Kadowaki}, \citenamefont
%  {Guptasarma},\ and\ \citenamefont {Hinks}}]{Norman1998}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
%  {Norman}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Ding}},
%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Randeria}}, \bibinfo
%  {author} {\bibfnamefont {J.~C.}\ \bibnamefont {Campuzano}}, \bibinfo {author}
%  {\bibfnamefont {T.}~\bibnamefont {Yokoya}}, \bibinfo {author} {\bibfnamefont
%  {T.}~\bibnamefont {Takeuchi}}, \bibinfo {author} {\bibfnamefont
%  {T.}~\bibnamefont {Takahashi}}, \bibinfo {author} {\bibfnamefont
%  {T.}~\bibnamefont {Mochiku}}, \bibinfo {author} {\bibfnamefont
%  {K.}~\bibnamefont {Kadowaki}}, \bibinfo {author} {\bibfnamefont
%  {P.}~\bibnamefont {Guptasarma}},\ and\ \bibinfo {author} {\bibfnamefont
%  {D.~G.}\ \bibnamefont {Hinks}},\ }\href {https://doi.org/10.1038/32366}
%  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
%  {volume} {392}},\ \bibinfo {pages} {157} (\bibinfo {year}
%  {1998})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Hashimoto}\ \emph {et~al.}(2014)\citenamefont
%  {Hashimoto}, \citenamefont {Vishik}, \citenamefont {He}, \citenamefont
%  {Devereaux},\ and\ \citenamefont {Shen}}]{Hashimoto2014}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
%  {Hashimoto}}, \bibinfo {author} {\bibfnamefont {I.~M.}\ \bibnamefont
%  {Vishik}}, \bibinfo {author} {\bibfnamefont {R.-H.}\ \bibnamefont {He}},
%  \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont {Devereaux}},\ and\
%  \bibinfo {author} {\bibfnamefont {Z.-X.}\ \bibnamefont {Shen}},\ }\href
%  {https://doi.org/10.1038/nphys3009} {\bibfield  {journal} {\bibinfo
%  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo
%  {pages} {483} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Taillefer}(2010)}]{taillefer2010}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
%  {Taillefer}},\ }\href
%  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-070909-104117}
%  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
%  Physics}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo {pages} {51} (\bibinfo
%  {year} {2010})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Fradkin}\ \emph {et~al.}(2015)\citenamefont
%  {Fradkin}, \citenamefont {Kivelson},\ and\ \citenamefont
%  {Tranquada}}]{FradkinRevModPhys2015}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
%  {Fradkin}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
%  {Kivelson}},\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
%  {Tranquada}},\ }\href {https://doi.org/10.1103/RevModPhys.87.457} {\bibfield
%  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume}
%  {87}},\ \bibinfo {pages} {457} (\bibinfo {year} {2015})}\BibitemShut
%  {NoStop}%
%\bibitem [{\citenamefont {Sato}\ \emph {et~al.}(2017)\citenamefont {Sato},
%  \citenamefont {Kasahara}, \citenamefont {Murayama}, \citenamefont {Kasahara},
%  \citenamefont {Moon}, \citenamefont {Nishizaki}, \citenamefont {Loew},
%  \citenamefont {Porras}, \citenamefont {Keimer}, \citenamefont {Shibauchi},\
%  and\ \citenamefont {Matsuda}}]{Sato2017}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
%  {Sato}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Kasahara}},
%  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Murayama}}, \bibinfo
%  {author} {\bibfnamefont {Y.}~\bibnamefont {Kasahara}}, \bibinfo {author}
%  {\bibfnamefont {E.-G.}\ \bibnamefont {Moon}}, \bibinfo {author}
%  {\bibfnamefont {T.}~\bibnamefont {Nishizaki}}, \bibinfo {author}
%  {\bibfnamefont {T.}~\bibnamefont {Loew}}, \bibinfo {author} {\bibfnamefont
%  {J.}~\bibnamefont {Porras}}, \bibinfo {author} {\bibfnamefont
%  {B.}~\bibnamefont {Keimer}}, \bibinfo {author} {\bibfnamefont
%  {T.}~\bibnamefont {Shibauchi}},\ and\ \bibinfo {author} {\bibfnamefont
%  {Y.}~\bibnamefont {Matsuda}},\ }\href {https://doi.org/10.1038/nphys4205}
%  {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf
%  {\bibinfo {volume} {13}},\ \bibinfo {pages} {1074} (\bibinfo {year}
%  {2017})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Doiron-Leyraud}\ \emph {et~al.}(2017)\citenamefont
%  {Doiron-Leyraud}, \citenamefont {Cyr-Choini{\`e}re}, \citenamefont {Badoux},
%  \citenamefont {Ataei}, \citenamefont {Collignon}, \citenamefont {Gourgout},
%  \citenamefont {Dufour-Beaus{\'e}jour}, \citenamefont {Tafti}, \citenamefont
%  {Lalibert{\'e}}, \citenamefont {Boulanger}, \citenamefont {Matusiak},
%  \citenamefont {Graf}, \citenamefont {Kim}, \citenamefont {Zhou},
%  \citenamefont {Momono}, \citenamefont {Kurosawa}, \citenamefont {Takagi},\
%  and\ \citenamefont {Taillefer}}]{DoironLeyraud2017}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
%  {Doiron-Leyraud}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
%  {Cyr-Choini{\`e}re}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
%  {Badoux}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Ataei}},
%  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Collignon}}, \bibinfo
%  {author} {\bibfnamefont {A.}~\bibnamefont {Gourgout}}, \bibinfo {author}
%  {\bibfnamefont {S.}~\bibnamefont {Dufour-Beaus{\'e}jour}}, \bibinfo {author}
%  {\bibfnamefont {F.~F.}\ \bibnamefont {Tafti}}, \bibinfo {author}
%  {\bibfnamefont {F.}~\bibnamefont {Lalibert{\'e}}}, \bibinfo {author}
%  {\bibfnamefont {M.-E.}\ \bibnamefont {Boulanger}}, \bibinfo {author}
%  {\bibfnamefont {M.}~\bibnamefont {Matusiak}}, \bibinfo {author}
%  {\bibfnamefont {D.}~\bibnamefont {Graf}}, \bibinfo {author} {\bibfnamefont
%  {M.}~\bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont {J.-S.}\
%  \bibnamefont {Zhou}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
%  {Momono}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Kurosawa}},
%  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\ and\ \bibinfo
%  {author} {\bibfnamefont {L.}~\bibnamefont {Taillefer}},\ }\href
%  {https://doi.org/10.1038/s41467-017-02122-x} {\bibfield  {journal} {\bibinfo
%  {journal} {Nature Communications}\ }\textbf {\bibinfo {volume} {8}},\
%  \bibinfo {pages} {2044} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Mukhopadhyay}\ \emph {et~al.}(2019)\citenamefont
%  {Mukhopadhyay}, \citenamefont {Sharma}, \citenamefont {Kim}, \citenamefont
%  {Edkins}, \citenamefont {Hamidian}, \citenamefont {Eisaki}, \citenamefont
%  {ichi Uchida}, \citenamefont {Kim}, \citenamefont {Lawler}, \citenamefont
%  {Mackenzie}, \citenamefont {Davis},\ and\ \citenamefont
%  {Fujita}}]{Mukhopadhyay2019}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
%  {Mukhopadhyay}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
%  {Sharma}}, \bibinfo {author} {\bibfnamefont {C.~K.}\ \bibnamefont {Kim}},
%  \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont {Edkins}}, \bibinfo
%  {author} {\bibfnamefont {M.~H.}\ \bibnamefont {Hamidian}}, \bibinfo {author}
%  {\bibfnamefont {H.}~\bibnamefont {Eisaki}}, \bibinfo {author} {\bibfnamefont
%  {S.}~\bibnamefont {ichi Uchida}}, \bibinfo {author} {\bibfnamefont {E.-A.}\
%  \bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
%  {Lawler}}, \bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont
%  {Mackenzie}}, \bibinfo {author} {\bibfnamefont {J.~C.~S.}\ \bibnamefont
%  {Davis}},\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
%  {Fujita}},\ }\href {https://doi.org/10.1073/pnas.1821454116} {\bibfield
%  {journal} {\bibinfo  {journal} {Proceedings of the National Academy of
%  Sciences}\ }\textbf {\bibinfo {volume} {116}},\ \bibinfo {pages} {13249}
%  (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Gupta}\ \emph {et~al.}(2021)\citenamefont {Gupta},
%  \citenamefont {McMahon}, \citenamefont {Sutarto}, \citenamefont {Shi},
%  \citenamefont {Gong}, \citenamefont {Wei}, \citenamefont {Shen},
%  \citenamefont {He}, \citenamefont {Ma}, \citenamefont {Dragomir},
%  \citenamefont {Gaulin},\ and\ \citenamefont {Hawthorn}}]{Naman2021}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~K.}\ \bibnamefont
%  {Gupta}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {McMahon}},
%  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Sutarto}}, \bibinfo
%  {author} {\bibfnamefont {T.}~\bibnamefont {Shi}}, \bibinfo {author}
%  {\bibfnamefont {R.}~\bibnamefont {Gong}}, \bibinfo {author} {\bibfnamefont
%  {H.~I.}\ \bibnamefont {Wei}}, \bibinfo {author} {\bibfnamefont {K.~M.}\
%  \bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
%  {He}}, \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Ma}}, \bibinfo
%  {author} {\bibfnamefont {M.}~\bibnamefont {Dragomir}}, \bibinfo {author}
%  {\bibfnamefont {B.~D.}\ \bibnamefont {Gaulin}},\ and\ \bibinfo {author}
%  {\bibfnamefont {D.~G.}\ \bibnamefont {Hawthorn}},\ }\href
%  {https://doi.org/10.1073/pnas.2106881118} {\bibfield  {journal} {\bibinfo
%  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
%  {\bibinfo {volume} {118}},\ \bibinfo {pages} {e2106881118} (\bibinfo {year}
%  {2021})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Horio}\ \emph {et~al.}(2025)\citenamefont {Horio},
%  \citenamefont {Sakai}, \citenamefont {Suzuki}, \citenamefont {Nonaka},
%  \citenamefont {Hashimoto}, \citenamefont {Lu}, \citenamefont {Shen},
%  \citenamefont {Ohgi}, \citenamefont {Konno}, \citenamefont {Adachi},
%  \citenamefont {Koike}, \citenamefont {Imada},\ and\ \citenamefont
%  {Fujimori}}]{Masafumi2025}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
%  {Horio}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Sakai}},
%  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Suzuki}}, \bibinfo
%  {author} {\bibfnamefont {Y.}~\bibnamefont {Nonaka}}, \bibinfo {author}
%  {\bibfnamefont {M.}~\bibnamefont {Hashimoto}}, \bibinfo {author}
%  {\bibfnamefont {D.}~\bibnamefont {Lu}}, \bibinfo {author} {\bibfnamefont
%  {Z.-X.}\ \bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont
%  {T.}~\bibnamefont {Ohgi}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
%  {Konno}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Adachi}},
%  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Koike}}, \bibinfo
%  {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ and\ \bibinfo {author}
%  {\bibfnamefont {A.}~\bibnamefont {Fujimori}},\ }\href
%  {https://doi.org/10.1073/pnas.2406624122} {\bibfield  {journal} {\bibinfo
%  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
%  {\bibinfo {volume} {122}},\ \bibinfo {pages} {e2406624122} (\bibinfo {year}
%  {2025})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Kyung}\ \emph {et~al.}(2006)\citenamefont {Kyung},
%  \citenamefont {Kancharla}, \citenamefont {S\'en\'echal}, \citenamefont
%  {Tremblay}, \citenamefont {Civelli},\ and\ \citenamefont
%  {Kotliar}}]{KyungKotliar2006}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
%  {Kyung}}, \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont
%  {Kancharla}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
%  {S\'en\'echal}}, \bibinfo {author} {\bibfnamefont {A.-M.~S.}\ \bibnamefont
%  {Tremblay}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Civelli}},\
%  and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Kotliar}},\ }\href
%  {https://doi.org/10.1103/PhysRevB.73.165114} {\bibfield  {journal} {\bibinfo
%  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo
%  {pages} {165114} (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Macridin}\ \emph {et~al.}(2006)\citenamefont
%  {Macridin}, \citenamefont {Jarrell}, \citenamefont {Maier}, \citenamefont
%  {Kent},\ and\ \citenamefont {D'Azevedo}}]{MacridinAzevedo2006}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
%  {Macridin}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Jarrell}},
%  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Maier}}, \bibinfo
%  {author} {\bibfnamefont {P.~R.~C.}\ \bibnamefont {Kent}},\ and\ \bibinfo
%  {author} {\bibfnamefont {E.}~\bibnamefont {D'Azevedo}},\ }\href
%  {https://doi.org/10.1103/PhysRevLett.97.036401} {\bibfield  {journal}
%  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {97}},\
%  \bibinfo {pages} {036401} (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2009)\citenamefont {Sakai},
%  \citenamefont {Motome},\ and\ \citenamefont {Imada}}]{sakai2009evolution}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
%  {Sakai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Motome}},\ and\
%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href@noop {}
%  {\bibfield  {journal} {\bibinfo  {journal} {Physical review letters}\
%  }\textbf {\bibinfo {volume} {102}},\ \bibinfo {pages} {056404} (\bibinfo
%  {year} {2009})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Werner}\ \emph {et~al.}(2009)\citenamefont {Werner},
%  \citenamefont {Gull}, \citenamefont {Parcollet},\ and\ \citenamefont
%  {Millis}}]{werner2009momentum}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
%  {Werner}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Gull}},
%  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}},\ and\
%  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
%  B}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages} {045120} (\bibinfo
%  {year} {2009})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2010)\citenamefont {Sakai},
%  \citenamefont {Motome},\ and\ \citenamefont {Imada}}]{sakai2010doped}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
%  {Sakai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Motome}},\ and\
%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href@noop {}
%  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review B}\ }\textbf
%  {\bibinfo {volume} {82}},\ \bibinfo {pages} {134505} (\bibinfo {year}
%  {2010})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Lin}\ \emph {et~al.}(2010)\citenamefont {Lin},
%  \citenamefont {Gull},\ and\ \citenamefont {Millis}}]{lin2010}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
%  {Lin}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Gull}},\ and\
%  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
%  }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {045104} (\bibinfo
%  {year} {2010})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Gull}\ \emph {et~al.}(2010)\citenamefont {Gull},
%  \citenamefont {Ferrero}, \citenamefont {Parcollet}, \citenamefont {Georges},\
%  and\ \citenamefont {Millis}}]{gull2010momentum}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
%  {Gull}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ferrero}},
%  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}}, \bibinfo
%  {author} {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
%  {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\ }\href@noop {} {\bibfield
%  {journal} {\bibinfo  {journal} {Physical Review B}\ }\textbf {\bibinfo
%  {volume} {82}},\ \bibinfo {pages} {155101} (\bibinfo {year}
%  {2010})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Gull}\ and\ \citenamefont {Millis}(2012)}]{gull2012}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
%  {Gull}}\ and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
%  {Millis}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
%  Rev. B}\ }\textbf {\bibinfo {volume} {86}},\ \bibinfo {pages} {241106}
%  (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Mirzaei}\ \emph {et~al.}(2013)\citenamefont
%  {Mirzaei}, \citenamefont {Stricker}, \citenamefont {Hancock}, \citenamefont
%  {Berthod}, \citenamefont {Georges}, \citenamefont {van Heumen}, \citenamefont
%  {Chan}, \citenamefont {Zhao}, \citenamefont {Li}, \citenamefont {Greven},
%  \citenamefont {Barišić},\ and\ \citenamefont {van~der
%  Marel}}]{Mirzaei2013}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~I.}\ \bibnamefont
%  {Mirzaei}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Stricker}},
%  \bibinfo {author} {\bibfnamefont {J.~N.}\ \bibnamefont {Hancock}}, \bibinfo
%  {author} {\bibfnamefont {C.}~\bibnamefont {Berthod}}, \bibinfo {author}
%  {\bibfnamefont {A.}~\bibnamefont {Georges}}, \bibinfo {author} {\bibfnamefont
%  {E.}~\bibnamefont {van Heumen}}, \bibinfo {author} {\bibfnamefont {M.~K.}\
%  \bibnamefont {Chan}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
%  {Zhao}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Li}}, \bibinfo
%  {author} {\bibfnamefont {M.}~\bibnamefont {Greven}}, \bibinfo {author}
%  {\bibfnamefont {N.}~\bibnamefont {Barišić}},\ and\ \bibinfo {author}
%  {\bibfnamefont {D.}~\bibnamefont {van~der Marel}},\ }\href
%  {https://doi.org/10.1073/pnas.1218846110} {\bibfield  {journal} {\bibinfo
%  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
%  {\bibinfo {volume} {110}},\ \bibinfo {pages} {5774} (\bibinfo {year}
%  {2013})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Gull}\ \emph {et~al.}(2013)\citenamefont {Gull},
%  \citenamefont {Parcollet},\ and\ \citenamefont {Millis}}]{gull2013}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
%  {Gull}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}},\
%  and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical review
%  letters}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo {pages} {216405}
%  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
%  {Lal}(2020{\natexlab{a}})}]{anirbanmott2}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
%  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
%  {Lal}},\ }\href {https://doi.org/10.1088/1367-2630/ab890c} {\bibfield
%  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
%  {volume} {22}},\ \bibinfo {pages} {063008} (\bibinfo {year}
%  {2020}{\natexlab{a}})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Hille}\ \emph {et~al.}(2020)\citenamefont {Hille},
%  \citenamefont {Rohe}, \citenamefont {Honerkamp},\ and\ \citenamefont
%  {Andergassen}}]{HilleAndergassen2020}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
%  {Hille}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Rohe}},
%  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Honerkamp}},\ and\
%  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Andergassen}},\ }\href
%  {https://doi.org/10.1103/PhysRevResearch.2.033068} {\bibfield  {journal}
%  {\bibinfo  {journal} {Phys. Rev. Res.}\ }\textbf {\bibinfo {volume} {2}},\
%  \bibinfo {pages} {033068} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Jiang}\ \emph {et~al.}(2022)\citenamefont {Jiang},
%  \citenamefont {Liu}, \citenamefont {Klein}, \citenamefont {Wang},
%  \citenamefont {Sun}, \citenamefont {Chubukov},\ and\ \citenamefont
%  {Meng}}]{Jiang2022}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
%  {Jiang}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Liu}}, \bibinfo
%  {author} {\bibfnamefont {A.}~\bibnamefont {Klein}}, \bibinfo {author}
%  {\bibfnamefont {Y.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont
%  {K.}~\bibnamefont {Sun}}, \bibinfo {author} {\bibfnamefont {A.~V.}\
%  \bibnamefont {Chubukov}},\ and\ \bibinfo {author} {\bibfnamefont {Z.~Y.}\
%  \bibnamefont {Meng}},\ }\href {https://doi.org/10.1038/s41467-022-30302-x}
%  {\bibfield  {journal} {\bibinfo  {journal} {Nature Communications}\ }\textbf
%  {\bibinfo {volume} {13}},\ \bibinfo {pages} {2655} (\bibinfo {year}
%  {2022})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Scheurer}\ \emph {et~al.}(2018)\citenamefont
%  {Scheurer}, \citenamefont {Chatterjee}, \citenamefont {Wu}, \citenamefont
%  {Ferrero}, \citenamefont {Georges},\ and\ \citenamefont
%  {Sachdev}}]{Scheurer2018}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont
%  {Scheurer}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
%  {Chatterjee}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Wu}},
%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ferrero}}, \bibinfo
%  {author} {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
%  {\bibfnamefont {S.}~\bibnamefont {Sachdev}},\ }\href
%  {https://doi.org/10.1073/pnas.1720580115} {\bibfield  {journal} {\bibinfo
%  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
%  {\bibinfo {volume} {115}},\ \bibinfo {pages} {E3665} (\bibinfo {year}
%  {2018})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Krien}\ \emph {et~al.}(2022)\citenamefont {Krien},
%  \citenamefont {Worm}, \citenamefont {Chalupa-Gantner}, \citenamefont
%  {Toschi},\ and\ \citenamefont {Held}}]{Krien2022}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
%  {Krien}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Worm}},
%  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Chalupa-Gantner}},
%  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Toschi}},\ and\ \bibinfo
%  {author} {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\href
%  {https://doi.org/10.1038/s42005-022-01117-5} {\bibfield  {journal} {\bibinfo
%  {journal} {Communications Physics}\ }\textbf {\bibinfo {volume} {5}},\
%  \bibinfo {pages} {336} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Kitatani}\ \emph {et~al.}(2023)\citenamefont
%  {Kitatani}, \citenamefont {Si}, \citenamefont {Worm}, \citenamefont
%  {Tomczak}, \citenamefont {Arita},\ and\ \citenamefont {Held}}]{Kitatani2023}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
%  {Kitatani}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Si}},
%  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Worm}}, \bibinfo {author}
%  {\bibfnamefont {J.~M.}\ \bibnamefont {Tomczak}}, \bibinfo {author}
%  {\bibfnamefont {R.}~\bibnamefont {Arita}},\ and\ \bibinfo {author}
%  {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\href
%  {https://doi.org/10.1103/PhysRevLett.130.166002} {\bibfield  {journal}
%  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {130}},\
%  \bibinfo {pages} {166002} (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Sorella}(2023)}]{Sorella2023}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
%  {Sorella}},\ }\href {https://doi.org/10.1103/PhysRevB.107.115133} {\bibfield
%  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
%  {107}},\ \bibinfo {pages} {115133} (\bibinfo {year} {2023})}\BibitemShut
%  {NoStop}%
%\bibitem [{\citenamefont {Schäfer}\ \emph {et~al.}(2021)\citenamefont
%  {Schäfer}, \citenamefont {Wentzell}, \citenamefont {Šimkovic},
%  \citenamefont {He}, \citenamefont {Hille}, \citenamefont {Klett},
%  \citenamefont {Eckhardt}, \citenamefont {Arzhang}, \citenamefont {Harkov},
%  \citenamefont {Le~R\'egent}, \citenamefont {Kirsch}, \citenamefont {Wang},
%  \citenamefont {Kim}, \citenamefont {Kozik}, \citenamefont {Stepanov},
%  \citenamefont {Kauch}, \citenamefont {Andergassen}, \citenamefont {Hansmann},
%  \citenamefont {Rohe}, \citenamefont {Vilk}, \citenamefont {LeBlanc},
%  \citenamefont {Zhang}, \citenamefont {Tremblay}, \citenamefont {Ferrero},
%  \citenamefont {Parcollet},\ and\ \citenamefont {Georges}}]{Schafer2021}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
%  {Schäfer}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Wentzell}},
%  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Šimkovic}}, \bibinfo
%  {author} {\bibfnamefont {Y.-Y.}\ \bibnamefont {He}}, \bibinfo {author}
%  {\bibfnamefont {C.}~\bibnamefont {Hille}}, \bibinfo {author} {\bibfnamefont
%  {M.}~\bibnamefont {Klett}}, \bibinfo {author} {\bibfnamefont {C.~J.}\
%  \bibnamefont {Eckhardt}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
%  {Arzhang}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Harkov}},
%  \bibinfo {author} {\bibfnamefont {F.~m. c.-M.}\ \bibnamefont {Le~R\'egent}},
%  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kirsch}}, \bibinfo
%  {author} {\bibfnamefont {Y.}~\bibnamefont {Wang}}, \bibinfo {author}
%  {\bibfnamefont {A.~J.}\ \bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont
%  {E.}~\bibnamefont {Kozik}}, \bibinfo {author} {\bibfnamefont {E.~A.}\
%  \bibnamefont {Stepanov}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
%  {Kauch}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Andergassen}},
%  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Hansmann}}, \bibinfo
%  {author} {\bibfnamefont {D.}~\bibnamefont {Rohe}}, \bibinfo {author}
%  {\bibfnamefont {Y.~M.}\ \bibnamefont {Vilk}}, \bibinfo {author}
%  {\bibfnamefont {J.~P.~F.}\ \bibnamefont {LeBlanc}}, \bibinfo {author}
%  {\bibfnamefont {S.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
%  {A.-M.~S.}\ \bibnamefont {Tremblay}}, \bibinfo {author} {\bibfnamefont
%  {M.}~\bibnamefont {Ferrero}}, \bibinfo {author} {\bibfnamefont
%  {O.}~\bibnamefont {Parcollet}},\ and\ \bibinfo {author} {\bibfnamefont
%  {A.}~\bibnamefont {Georges}},\ }\href
%  {https://doi.org/10.1103/PhysRevX.11.011058} {\bibfield  {journal} {\bibinfo
%  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
%  {pages} {011058} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {White}\ and\ \citenamefont
%  {Scalapino}(1998)}]{White1998}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~R.}\ \bibnamefont
%  {White}}\ and\ \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
%  {Scalapino}},\ }\href {https://doi.org/10.1103/PhysRevLett.80.1272}
%  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
%  {\bibinfo {volume} {80}},\ \bibinfo {pages} {1272} (\bibinfo {year}
%  {1998})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Ido}\ \emph {et~al.}(2018)\citenamefont {Ido},
%  \citenamefont {Ohgoe},\ and\ \citenamefont {Imada}}]{Ido2018}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
%  {Ido}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Ohgoe}},\ and\
%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href
%  {https://doi.org/10.1103/PhysRevB.97.045138} {\bibfield  {journal} {\bibinfo
%  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo
%  {pages} {045138} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Proust}\ and\ \citenamefont
%  {Taillefer}(2019)}]{ProustTaillefer2019}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
%  {Proust}}\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
%  {Taillefer}},\ }\href
%  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-031218-013210}
%  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
%  Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {409}
%  (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Ponsioen}\ \emph {et~al.}(2019)\citenamefont
%  {Ponsioen}, \citenamefont {Chung},\ and\ \citenamefont
%  {Corboz}}]{Ponsioen2019}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
%  {Ponsioen}}, \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont
%  {Chung}},\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
%  {Corboz}},\ }\href {https://doi.org/10.1103/PhysRevB.100.195141} {\bibfield
%  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
%  {100}},\ \bibinfo {pages} {195141} (\bibinfo {year} {2019})}\BibitemShut
%  {NoStop}%
%\bibitem [{\citenamefont {Xu}\ \emph {et~al.}(2022)\citenamefont {Xu},
%  \citenamefont {Shi}, \citenamefont {Vitali}, \citenamefont {Qin},\ and\
%  \citenamefont {Zhang}}]{XuZhang2022}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
%  {Xu}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Shi}}, \bibinfo
%  {author} {\bibfnamefont {E.}~\bibnamefont {Vitali}}, \bibinfo {author}
%  {\bibfnamefont {M.}~\bibnamefont {Qin}},\ and\ \bibinfo {author}
%  {\bibfnamefont {S.}~\bibnamefont {Zhang}},\ }\href
%  {https://doi.org/10.1103/PhysRevResearch.4.013239} {\bibfield  {journal}
%  {\bibinfo  {journal} {Phys. Rev. Res.}\ }\textbf {\bibinfo {volume} {4}},\
%  \bibinfo {pages} {013239} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Dave}\ \emph {et~al.}(2013)\citenamefont {Dave},
%  \citenamefont {Phillips},\ and\ \citenamefont {Kane}}]{Phillips2013}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~B.}\ \bibnamefont
%  {Dave}}, \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\
%  and\ \bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont {Kane}},\ }\href
%  {https://doi.org/10.1103/PhysRevLett.110.090403} {\bibfield  {journal}
%  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {110}},\
%  \bibinfo {pages} {090403} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Seki}\ and\ \citenamefont
%  {Yunoki}(2017)}]{seki2017topological}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
%  {Seki}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Yunoki}},\
%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
%  B}\ }\textbf {\bibinfo {volume} {96}},\ \bibinfo {pages} {085124} (\bibinfo
%  {year} {2017})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Anderson}\ and\ \citenamefont
%  {Haldane}(2001)}]{Anderson2001}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
%  {Anderson}}\ and\ \bibinfo {author} {\bibfnamefont {F.~D.~M.}\ \bibnamefont
%  {Haldane}},\ }\href {https://doi.org/10.1023/A:1010324912515} {\bibfield
%  {journal} {\bibinfo  {journal} {Journal of Statistical Physics}\ }\textbf
%  {\bibinfo {volume} {103}},\ \bibinfo {pages} {425} (\bibinfo {year}
%  {2001})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Huang}\ \emph {et~al.}(2022)\citenamefont {Huang},
%  \citenamefont {Nave},\ and\ \citenamefont {Phillips}}]{Huang2022}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont
%  {Huang}}, \bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont {Nave}},\
%  and\ \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\
%  }\href {https://doi.org/10.1038/s41567-022-01529-8} {\bibfield  {journal}
%  {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {18}},\
%  \bibinfo {pages} {511} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Coleman}\ \emph {et~al.}(2001)\citenamefont
%  {Coleman}, \citenamefont {Pépin}, \citenamefont {Si},\ and\ \citenamefont
%  {Ramazashvili}}]{Coleman_2001}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
%  {Coleman}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Pépin}},
%  \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Si}},\ and\ \bibinfo
%  {author} {\bibfnamefont {R.}~\bibnamefont {Ramazashvili}},\ }\href
%  {https://doi.org/10.1088/0953-8984/13/35/202} {\bibfield  {journal} {\bibinfo
%   {journal} {Journal of Physics: Condensed Matter}\ }\textbf {\bibinfo
%  {volume} {13}},\ \bibinfo {pages} {R723} (\bibinfo {year}
%  {2001})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
%  {Lal}(2020{\natexlab{b}})}]{anirbanurg1}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
%  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
%  {Lal}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nuclear
%  Physics B}\ }\textbf {\bibinfo {volume} {960}},\ \bibinfo {pages} {115170}
%  (\bibinfo {year} {2020}{\natexlab{b}})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
%  {Lal}(2020{\natexlab{c}})}]{anirbanurg2}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
%  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
%  {Lal}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nuclear
%  Physics B}\ }\textbf {\bibinfo {volume} {960}},\ \bibinfo {pages} {115163}
%  (\bibinfo {year} {2020}{\natexlab{c}})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Keimer}\ \emph {et~al.}(2015)\citenamefont {Keimer},
%  \citenamefont {Kivelson}, \citenamefont {Norman}, \citenamefont {Uchida},\
%  and\ \citenamefont {Zaanen}}]{keimer2015quantum}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
%  {Keimer}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
%  {Kivelson}}, \bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
%  {Norman}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Uchida}},\
%  and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zaanen}},\
%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf
%  {\bibinfo {volume} {518}},\ \bibinfo {pages} {179} (\bibinfo {year}
%  {2015})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Hatsugai}\ and\ \citenamefont
%  {Kohmoto}(1992)}]{Hatsugai1992}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
%  {Hatsugai}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
%  {Kohmoto}},\ }\href {https://doi.org/10.1143/JPSJ.61.2056} {\bibfield
%  {journal} {\bibinfo  {journal} {Journal of the Physical Society of Japan}\
%  }\textbf {\bibinfo {volume} {61}},\ \bibinfo {pages} {2056} (\bibinfo {year}
%  {1992})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Baskaran}(1991)}]{Baskaran1991}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
%  {Baskaran}},\ }\href {https://doi.org/10.1142/S0217984991000782} {\bibfield
%  {journal} {\bibinfo  {journal} {Modern Physics Letters B}\ }\textbf {\bibinfo
%  {volume} {05}},\ \bibinfo {pages} {643} (\bibinfo {year} {1991})}\BibitemShut
%  {NoStop}%
%\bibitem [{\citenamefont {Altshuler}\ \emph {et~al.}(1998)\citenamefont
%  {Altshuler}, \citenamefont {Chubukov}, \citenamefont {Dashevskii},
%  \citenamefont {Finkel'stein},\ and\ \citenamefont {Morr}}]{Altshuler_1998}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~L.}\ \bibnamefont
%  {Altshuler}}, \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
%  {Chubukov}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
%  {Dashevskii}}, \bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
%  {Finkel'stein}},\ and\ \bibinfo {author} {\bibfnamefont {D.~K.}\ \bibnamefont
%  {Morr}},\ }\href {https://doi.org/10.1209/epl/i1998-00164-y} {\bibfield
%  {journal} {\bibinfo  {journal} {Europhysics Letters}\ }\textbf {\bibinfo
%  {volume} {41}},\ \bibinfo {pages} {401} (\bibinfo {year} {1998})}\BibitemShut
%  {NoStop}%
%\bibitem [{\citenamefont {Heath}\ and\ \citenamefont
%  {Bedell}(2020)}]{Heath_2020}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont
%  {Heath}}\ and\ \bibinfo {author} {\bibfnamefont {K.~S.}\ \bibnamefont
%  {Bedell}},\ }\href {https://doi.org/10.1088/1367-2630/ab890e} {\bibfield
%  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
%  {volume} {22}},\ \bibinfo {pages} {063011} (\bibinfo {year}
%  {2020})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Nave}\ \emph {et~al.}(2025)\citenamefont {Nave},
%  \citenamefont {Zhao},\ and\ \citenamefont {Phillips}}]{lanave2025}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont
%  {Nave}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zhao}},\ and\
%  \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\ }\href
%  {https://arxiv.org/abs/2506.04342} {} (\bibinfo {year} {2025}),\ \Eprint
%  {https://arxiv.org/abs/2506.04342} {arXiv:2506.04342 [cond-mat.str-el]}
%  \BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Mukherjee}\ \emph {et~al.}(2023)\citenamefont
%  {Mukherjee}, \citenamefont {Vidhyadhiraja}, \citenamefont {Taraphder},\ and\
%  \citenamefont {Lal}}]{Mukherjee_2023}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
%  {Mukherjee}}, \bibinfo {author} {\bibfnamefont {N.~S.}\ \bibnamefont
%  {Vidhyadhiraja}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
%  {Taraphder}},\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
%  {Lal}},\ }\href {https://doi.org/10.1088/1367-2630/ad08f3} {\bibfield
%  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
%  {volume} {25}},\ \bibinfo {pages} {113011} (\bibinfo {year}
%  {2023})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Georges}\ \emph {et~al.}(1996)\citenamefont
%  {Georges}, \citenamefont {Kotliar}, \citenamefont {Krauth},\ and\
%  \citenamefont {Rozenberg}}]{georges1996}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
%  {Georges}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Kotliar}},
%  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Krauth}},\ and\ \bibinfo
%  {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Rozenberg}},\ }\href@noop {}
%  {\bibfield  {journal} {\bibinfo  {journal} {Reviews of Modern Physics}\
%  }\textbf {\bibinfo {volume} {68}},\ \bibinfo {pages} {13} (\bibinfo {year}
%  {1996})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Hettler}\ \emph {et~al.}(1998)\citenamefont
%  {Hettler}, \citenamefont {Tahvildar-Zadeh}, \citenamefont {Jarrell},
%  \citenamefont {Pruschke},\ and\ \citenamefont {Krishnamurthy}}]{hettler1998}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
%  {Hettler}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
%  {Tahvildar-Zadeh}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
%  {Jarrell}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Pruschke}},\
%  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Krishnamurthy}},\
%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
%  B}\ }\textbf {\bibinfo {volume} {58}},\ \bibinfo {pages} {R7475} (\bibinfo
%  {year} {1998})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Kotliar}\ \emph {et~al.}(2001)\citenamefont
%  {Kotliar}, \citenamefont {Savrasov}, \citenamefont {P{\'a}lsson},\ and\
%  \citenamefont {Biroli}}]{kotliar2001}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
%  {Kotliar}}, \bibinfo {author} {\bibfnamefont {S.~Y.}\ \bibnamefont
%  {Savrasov}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
%  {P{\'a}lsson}},\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
%  {Biroli}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
%  {Physical review letters}\ }\textbf {\bibinfo {volume} {87}},\ \bibinfo
%  {pages} {186401} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Maier}\ \emph {et~al.}(2005)\citenamefont {Maier},
%  \citenamefont {Jarrell}, \citenamefont {Schulthess}, \citenamefont {Kent},\
%  and\ \citenamefont {White}}]{maier2005}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont
%  {Maier}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Jarrell}},
%  \bibinfo {author} {\bibfnamefont {T.~C.}\ \bibnamefont {Schulthess}},
%  \bibinfo {author} {\bibfnamefont {P.~R.~C.}\ \bibnamefont {Kent}},\ and\
%  \bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont {White}},\ }\href@noop
%  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
%  {\bibinfo {volume} {95}},\ \bibinfo {pages} {237001} (\bibinfo {year}
%  {2005})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Stoyanova}(2006)}]{stoyanova}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
%  {Stoyanova}},\ }\emph {\bibinfo {title} {Delocalized and correlated wave
%  functions for excited states in extended systems}},\ \href@noop {} {Ph.D.
%  thesis},\ \bibinfo  {school} {University of Groningen} (\bibinfo {year}
%  {2006})\BibitemShut {NoStop}%
%\bibitem [{sup()}]{suppmat}%
%  \BibitemOpen
%  \href@noop {} {\bibinfo {title} {See supplemental material for additional
%  information.}}\BibitemShut {Stop}%
%\bibitem [{\citenamefont {Wu}\ \emph {et~al.}(2018)\citenamefont {Wu},
%  \citenamefont {Scheurer}, \citenamefont {Chatterjee}, \citenamefont
%  {Sachdev}, \citenamefont {Georges},\ and\ \citenamefont
%  {Ferrero}}]{WuFerrero2018}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
%  {Wu}}, \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Scheurer}},
%  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Chatterjee}}, \bibinfo
%  {author} {\bibfnamefont {S.}~\bibnamefont {Sachdev}}, \bibinfo {author}
%  {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
%  {\bibfnamefont {M.}~\bibnamefont {Ferrero}},\ }\href
%  {https://doi.org/10.1103/PhysRevX.8.021048} {\bibfield  {journal} {\bibinfo
%  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {8}},\ \bibinfo {pages}
%  {021048} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Tsvelick}\ and\ \citenamefont
%  {Wiegmann}(1985)}]{Tsvelick_weigmann_mchannel_1985}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
%  {Tsvelick}}\ and\ \bibinfo {author} {\bibfnamefont {P.~B.}\ \bibnamefont
%  {Wiegmann}},\ }\href {https://doi.org/10.1007/BF01017853} {\bibfield
%  {journal} {\bibinfo  {journal} {Journal of Statistical Physics}\ }\textbf
%  {\bibinfo {volume} {38}},\ \bibinfo {pages} {125} (\bibinfo {year}
%  {1985})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Emery}\ and\ \citenamefont
%  {Kivelson}(1992)}]{emery_kivelson}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~J.}\ \bibnamefont
%  {Emery}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
%  {Kivelson}},\ }\href {https://doi.org/10.1103/PhysRevB.46.10812} {\bibfield
%  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
%  {46}},\ \bibinfo {pages} {10812} (\bibinfo {year} {1992})}\BibitemShut
%  {NoStop}%
%\bibitem [{\citenamefont {Gunnarsson}\ \emph {et~al.}(2003)\citenamefont
%  {Gunnarsson}, \citenamefont {Calandra},\ and\ \citenamefont
%  {Han}}]{GunnarssonRMP2003}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
%  {Gunnarsson}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
%  {Calandra}},\ and\ \bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont
%  {Han}},\ }\href {https://doi.org/10.1103/RevModPhys.75.1085} {\bibfield
%  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume}
%  {75}},\ \bibinfo {pages} {1085} (\bibinfo {year} {2003})}\BibitemShut
%  {NoStop}%
%\bibitem [{\citenamefont {Hussey}\ \emph {et~al.}(2004)\citenamefont {Hussey},
%  \citenamefont {Takenaka},\ and\ \citenamefont {Takagi}}]{Hussey2004}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
%  {Hussey}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Takenaka}},\
%  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\ }\href
%  {https://doi.org/10.1080/14786430410001716944} {\bibfield  {journal}
%  {\bibinfo  {journal} {Philosophical Magazine}\ }\textbf {\bibinfo {volume}
%  {84}},\ \bibinfo {pages} {2847} (\bibinfo {year} {2004})}\BibitemShut
%  {NoStop}%
%\bibitem [{\citenamefont {Pustogow}\ \emph {et~al.}(2021)\citenamefont
%  {Pustogow}, \citenamefont {Saito}, \citenamefont {Anja~Löhle}, \citenamefont
%  {Alonso}, \citenamefont {Kawamoto}, \citenamefont {Dobrosavljevic},
%  \citenamefont {Dressel},\ and\ \citenamefont {Fratini}}]{pustogow2021}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
%  {Pustogow}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Saito}},
%  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Anja~Löhle}}, \bibinfo
%  {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Alonso}}, \bibinfo {author}
%  {\bibfnamefont {A.}~\bibnamefont {Kawamoto}}, \bibinfo {author}
%  {\bibfnamefont {V.}~\bibnamefont {Dobrosavljevic}}, \bibinfo {author}
%  {\bibfnamefont {M.}~\bibnamefont {Dressel}},\ and\ \bibinfo {author}
%  {\bibfnamefont {S.}~\bibnamefont {Fratini}},\ }\href@noop {} {\bibfield
%  {journal} {\bibinfo  {journal} {Nat. Comm.}\ }\textbf {\bibinfo {volume}
%  {12}},\ \bibinfo {pages} {1571} (\bibinfo {year} {2021})}\BibitemShut
%  {NoStop}%
%\bibitem [{\citenamefont {Qazilbash}\ \emph {et~al.}(2008)\citenamefont
%  {Qazilbash}, \citenamefont {Schafgans}, \citenamefont {Burch}, \citenamefont
%  {Yun}, \citenamefont {Chae}, \citenamefont {Kim}, \citenamefont {Kim},\ and\
%  \citenamefont {Basov}}]{qazilbash2008}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~M.}\ \bibnamefont
%  {Qazilbash}}, \bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont
%  {Schafgans}}, \bibinfo {author} {\bibfnamefont {K.~S.}\ \bibnamefont
%  {Burch}}, \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont {Yun}},
%  \bibinfo {author} {\bibfnamefont {B.~G.}\ \bibnamefont {Chae}}, \bibinfo
%  {author} {\bibfnamefont {B.~J.}\ \bibnamefont {Kim}}, \bibinfo {author}
%  {\bibfnamefont {H.~T.}\ \bibnamefont {Kim}},\ and\ \bibinfo {author}
%  {\bibfnamefont {D.~N.}\ \bibnamefont {Basov}},\ }\href
%  {https://doi.org/10.1103/PhysRevB.77.115121} {\bibfield  {journal} {\bibinfo
%  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo
%  {pages} {115121} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Hauke}\ \emph {et~al.}(2016)\citenamefont {Hauke},
%  \citenamefont {Heyl}, \citenamefont {Tagliacozzo},\ and\ \citenamefont
%  {Zoller}}]{Hauke2016}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
%  {Hauke}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Heyl}},
%  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Tagliacozzo}},\ and\
%  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Zoller}},\ }\href
%  {https://doi.org/10.1038/nphys3700} {\bibfield  {journal} {\bibinfo
%  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
%  {pages} {778} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Balut}\ \emph {et~al.}(2025)\citenamefont {Balut},
%  \citenamefont {Guo}, \citenamefont {de~Vriesa}, \citenamefont {Chaudhuri},
%  \citenamefont {Bradlyn}, \citenamefont {Abbamonte},\ and\ \citenamefont
%  {W.}}]{balut2025}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
%  {Balut}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Guo}}, \bibinfo
%  {author} {\bibfnamefont {N.}~\bibnamefont {de~Vriesa}}, \bibinfo {author}
%  {\bibfnamefont {D.}~\bibnamefont {Chaudhuri}}, \bibinfo {author}
%  {\bibfnamefont {B.}~\bibnamefont {Bradlyn}}, \bibinfo {author} {\bibfnamefont
%  {P.}~\bibnamefont {Abbamonte}},\ and\ \bibinfo {author} {\bibfnamefont
%  {P.~P.}\ \bibnamefont {W.}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
%  {journal} {Physica C}\ }\textbf {\bibinfo {volume} {635}},\ \bibinfo {pages}
%  {1354750} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Mazza}\ \emph {et~al.}(2024)\citenamefont {Mazza},
%  \citenamefont {Biswas}, \citenamefont {Yan}, \citenamefont {Prokofiev},
%  \citenamefont {Steffens}, \citenamefont {Si}, \citenamefont {Assaad},\ and\
%  \citenamefont {Paschen}}]{mazza2024}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
%  {Mazza}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Biswas}},
%  \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Yan}}, \bibinfo {author}
%  {\bibfnamefont {A.}~\bibnamefont {Prokofiev}}, \bibinfo {author}
%  {\bibfnamefont {P.}~\bibnamefont {Steffens}}, \bibinfo {author}
%  {\bibfnamefont {Q.}~\bibnamefont {Si}}, \bibinfo {author} {\bibfnamefont
%  {F.~F.}\ \bibnamefont {Assaad}},\ and\ \bibinfo {author} {\bibfnamefont
%  {S.}~\bibnamefont {Paschen}},\ }\href {https://arxiv.org/abs/2403.12779} {}
%  (\bibinfo {year} {2024}),\ \Eprint {https://arxiv.org/abs/2403.12779}
%  {arXiv:2403.12779 [cond-mat.str-el]} \BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Si}\ \emph {et~al.}(2001)\citenamefont {Si},
%  \citenamefont {Rabello}, \citenamefont {Ingersent},\ and\ \citenamefont
%  {Smith}}]{Si2001}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont
%  {Si}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Rabello}},
%  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Ingersent}},\ and\
%  \bibinfo {author} {\bibfnamefont {J.~L.}\ \bibnamefont {Smith}},\ }\href
%  {https://doi.org/10.1038/35101507} {\bibfield  {journal} {\bibinfo  {journal}
%  {Nature}\ }\textbf {\bibinfo {volume} {413}},\ \bibinfo {pages} {804}
%  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2020)\citenamefont
%  {Phillips}, \citenamefont {Yeo},\ and\ \citenamefont {Huang}}]{Phillips2020}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
%  {Phillips}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Yeo}},\ and\
%  \bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont {Huang}},\ }\href
%  {https://doi.org/10.1038/s41567-020-0988-4} {\bibfield  {journal} {\bibinfo
%  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo
%  {pages} {1175} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Vafek}\ and\ \citenamefont
%  {Vishwanath}(2014)}]{vafekvishwanath2014}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
%  {Vafek}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
%  {Vishwanath}},\ }\href
%  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-031113-133841}
%  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
%  Physics}\ }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {83} (\bibinfo
%  {year} {2014})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Morimoto}\ and\ \citenamefont
%  {Nagaosa}(2016)}]{morimoto2016}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
%  {Morimoto}}\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
%  {Nagaosa}},\ }\href {https://doi.org/10.1038/srep19853} {\bibfield  {journal}
%  {\bibinfo  {journal} {Sci. Rep.}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo
%  {pages} {19853} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Flores-Calder\'on}\ and\ \citenamefont
%  {Hooley}(2025)}]{calderon2025}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
%  {Flores-Calder\'on}}\ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
%  {Hooley}},\ }\href {https://doi.org/10.1103/k4st-77ph} {\bibfield  {journal}
%  {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {111}},\
%  \bibinfo {pages} {235139} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Georgi}(2007{\natexlab{a}})}]{Georgi2007PRL}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
%  {Georgi}},\ }\href {https://doi.org/10.1103/PhysRevLett.98.221601} {\bibfield
%   {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
%  {volume} {98}},\ \bibinfo {pages} {221601} (\bibinfo {year}
%  {2007}{\natexlab{a}})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Georgi}(2007{\natexlab{b}})}]{Georgi2007}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
%  {Georgi}},\ }\href
%  {https://doi.org/https://doi.org/10.1016/j.physletb.2007.05.037} {\bibfield
%  {journal} {\bibinfo  {journal} {Physics Letters B}\ }\textbf {\bibinfo
%  {volume} {650}},\ \bibinfo {pages} {275} (\bibinfo {year}
%  {2007}{\natexlab{b}})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Phillips}(2014)}]{PhillipsLectures2014}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
%  {Phillips}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {Quantum
%  Criticality in Condensed Matter}}},\ \bibinfo {editor} {edited by\ \bibinfo
%  {editor} {\bibfnamefont {J.}~\bibnamefont {Jedrzejewski}}}\ (\bibinfo
%  {publisher} {World Scientific, Singapore},\ \bibinfo {year} {2014})\ pp.\
%  \bibinfo {pages} {133--158}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Zaanen}(2019)}]{zaanen2019}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
%  {Zaanen}},\ }\href {https://doi.org/10.21468/SciPostPhys.6.5.061} {\bibfield
%  {journal} {\bibinfo  {journal} {SciPost Phys.}\ }\textbf {\bibinfo {volume}
%  {6}},\ \bibinfo {pages} {061} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Legros}\ \emph {et~al.}(2019)\citenamefont {Legros},
%  \citenamefont {Benhabib}, \citenamefont {Tabis}, \citenamefont
%  {Lalibert{\'e}}, \citenamefont {Dion}, \citenamefont {Lizaire}, \citenamefont
%  {Vignolle}, \citenamefont {Vignolles}, \citenamefont {Raffy}, \citenamefont
%  {Li} \emph {et~al.}}]{legros2019}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
%  {Legros}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Benhabib}},
%  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Tabis}}, \bibinfo
%  {author} {\bibfnamefont {F.}~\bibnamefont {Lalibert{\'e}}}, \bibinfo {author}
%  {\bibfnamefont {M.}~\bibnamefont {Dion}}, \bibinfo {author} {\bibfnamefont
%  {M.}~\bibnamefont {Lizaire}}, \bibinfo {author} {\bibfnamefont
%  {B.}~\bibnamefont {Vignolle}}, \bibinfo {author} {\bibfnamefont
%  {D.}~\bibnamefont {Vignolles}}, \bibinfo {author} {\bibfnamefont
%  {H.}~\bibnamefont {Raffy}}, \bibinfo {author} {\bibfnamefont
%  {Z.}~\bibnamefont {Li}}, \emph {et~al.},\ }\href@noop {} {\bibfield
%  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
%  {15}},\ \bibinfo {pages} {142} (\bibinfo {year} {2019})}\BibitemShut
%  {NoStop}%
%\bibitem [{\citenamefont {McGreevy}(2023)}]{McGreevy2023}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
%  {McGreevy}},\ }\href
%  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-040721-021029}
%  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
%  Physics}\ }\textbf {\bibinfo {volume} {14}},\ \bibinfo {pages} {57} (\bibinfo
%  {year} {2023})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Luttinger}\ and\ \citenamefont
%  {Ward}(1960)}]{luttinger1960ground}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
%  {Luttinger}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
%  {Ward}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical
%  Review}\ }\textbf {\bibinfo {volume} {118}},\ \bibinfo {pages} {1417}
%  (\bibinfo {year} {1960})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Su}\ and\ \citenamefont
%  {Martin}(2025)}]{su2025anomalies}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
%  {Su}}\ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Martin}},\
%  }\href {https://arxiv.org/abs/2405.08093} {} (\bibinfo {year} {2025}),\
%  \Eprint {https://arxiv.org/abs/2405.08093} {arXiv:2405.08093
%  [cond-mat.str-el]} \BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Adler}(1969)}]{adler1969axial}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont
%  {Adler}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
%  {Physical Review}\ }\textbf {\bibinfo {volume} {177}},\ \bibinfo {pages}
%  {2426} (\bibinfo {year} {1969})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Bell}\ and\ \citenamefont
%  {Jackiw}(1969)}]{bell1969pcac}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~S.}\ \bibnamefont
%  {Bell}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Jackiw}},\
%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Il Nuovo Cimento
%  A}\ }\textbf {\bibinfo {volume} {60}},\ \bibinfo {pages} {47} (\bibinfo
%  {year} {1969})}\BibitemShut {NoStop}%
%\bibitem [{\citenamefont {Casini}\ and\ \citenamefont
%  {Mag\'{a}n}(2021)}]{Casini2021Symmetries}%
%  \BibitemOpen
%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
%  {Casini}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
%  {Mag\'{a}n}},\ }\href {https://doi.org/10.1142/S0217732321300251} {\bibfield
%  {journal} {\bibinfo  {journal} {Modern Physics Letters A}\ }\textbf {\bibinfo
%  {volume} {36}},\ \bibinfo {pages} {2130025} (\bibinfo {year}
%  {2021})}\BibitemShut {NoStop}%
%\end{thebibliography}

%\bibliography{tilingProject}

\begin{thebibliography}{89}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{https://doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Landau}(1957)}]{landau1959theory}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Landau}},\ }\bibfield  {title} {\bibinfo {title} {The theory of a fermi
  liquid},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Soviet
  Physics Jetp-Ussr}\ }\textbf {\bibinfo {volume} {3}},\ \bibinfo {pages} {920}
  (\bibinfo {year} {1957})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2013)\citenamefont
  {Phillips}, \citenamefont {Langley},\ and\ \citenamefont
  {Hutasoit}}]{Phillips2013Unparticles}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
  {Phillips}}, \bibinfo {author} {\bibfnamefont {B.~W.}\ \bibnamefont
  {Langley}},\ and\ \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont
  {Hutasoit}},\ }\bibfield  {title} {\bibinfo {title} {Un-fermi liquids:
  Unparticles in strongly correlated electron matter},\ }\href
  {https://doi.org/10.1103/PhysRevB.88.115129} {\bibfield  {journal} {\bibinfo
  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {88}},\ \bibinfo
  {pages} {115129} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Dzyaloshinskii}(2003)}]{dzyaloshinskii2003some}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
  {Dzyaloshinskii}},\ }\bibfield  {title} {\bibinfo {title} {Some consequences
  of the luttinger theorem: The luttinger surfaces in non-fermi liquids and
  mott insulators},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
  {Physical Review B}\ }\textbf {\bibinfo {volume} {68}},\ \bibinfo {pages}
  {085113} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Mott}(1949)}]{Mott_1949}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~F.}\ \bibnamefont
  {Mott}},\ }\bibfield  {title} {\bibinfo {title} {The basis of the electron
  theory of metals, with special reference to the transition metals},\ }\href
  {https://doi.org/10.1088/0370-1298/62/7/303} {\bibfield  {journal} {\bibinfo
  {journal} {Proceedings of the Physical Society. Section A}\ }\textbf
  {\bibinfo {volume} {62}},\ \bibinfo {pages} {416} (\bibinfo {year}
  {1949})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2022)\citenamefont
  {Phillips}, \citenamefont {Hussey},\ and\ \citenamefont
  {Abbamonte}}]{phillips2022}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
  {Phillips}}, \bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
  {Hussey}},\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {Abbamonte}},\ }\bibfield  {title} {\bibinfo {title} {Stranger than metals},\
  }\href {https://doi.org/10.1126/science.abh4273} {\bibfield  {journal}
  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {377}},\ \bibinfo
  {pages} {eabh4273} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Loeser}\ \emph {et~al.}(1996)\citenamefont {Loeser},
  \citenamefont {Shen}, \citenamefont {Dessau}, \citenamefont {Marshall},
  \citenamefont {Park}, \citenamefont {Fournier},\ and\ \citenamefont
  {Kapitulnik}}]{loeserKapitulnik1996}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~G.}\ \bibnamefont
  {Loeser}}, \bibinfo {author} {\bibfnamefont {Z.-X.}\ \bibnamefont {Shen}},
  \bibinfo {author} {\bibfnamefont {D.~S.}\ \bibnamefont {Dessau}}, \bibinfo
  {author} {\bibfnamefont {D.~S.}\ \bibnamefont {Marshall}}, \bibinfo {author}
  {\bibfnamefont {C.~H.}\ \bibnamefont {Park}}, \bibinfo {author}
  {\bibfnamefont {P.}~\bibnamefont {Fournier}},\ and\ \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Kapitulnik}},\ }\bibfield  {title}
  {\bibinfo {title} {Excitation gap in the normal state of underdoped
  bi2sr2cacu2o8},\ }\href {https://doi.org/10.1126/science.273.5273.325}
  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
  {volume} {273}},\ \bibinfo {pages} {325} (\bibinfo {year}
  {1996})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Norman}\ \emph {et~al.}(1998)\citenamefont {Norman},
  \citenamefont {Ding}, \citenamefont {Randeria}, \citenamefont {Campuzano},
  \citenamefont {Yokoya}, \citenamefont {Takeuchi}, \citenamefont {Takahashi},
  \citenamefont {Mochiku}, \citenamefont {Kadowaki}, \citenamefont
  {Guptasarma},\ and\ \citenamefont {Hinks}}]{Norman1998}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
  {Norman}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Ding}},
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Randeria}}, \bibinfo
  {author} {\bibfnamefont {J.~C.}\ \bibnamefont {Campuzano}}, \bibinfo {author}
  {\bibfnamefont {T.}~\bibnamefont {Yokoya}}, \bibinfo {author} {\bibfnamefont
  {T.}~\bibnamefont {Takeuchi}}, \bibinfo {author} {\bibfnamefont
  {T.}~\bibnamefont {Takahashi}}, \bibinfo {author} {\bibfnamefont
  {T.}~\bibnamefont {Mochiku}}, \bibinfo {author} {\bibfnamefont
  {K.}~\bibnamefont {Kadowaki}}, \bibinfo {author} {\bibfnamefont
  {P.}~\bibnamefont {Guptasarma}},\ and\ \bibinfo {author} {\bibfnamefont
  {D.~G.}\ \bibnamefont {Hinks}},\ }\bibfield  {title} {\bibinfo {title}
  {Destruction of the fermi surface in underdoped high-tc superconductors},\
  }\href {https://doi.org/10.1038/32366} {\bibfield  {journal} {\bibinfo
  {journal} {Nature}\ }\textbf {\bibinfo {volume} {392}},\ \bibinfo {pages}
  {157} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Hashimoto}\ \emph {et~al.}(2014)\citenamefont
  {Hashimoto}, \citenamefont {Vishik}, \citenamefont {He}, \citenamefont
  {Devereaux},\ and\ \citenamefont {Shen}}]{Hashimoto2014}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Hashimoto}}, \bibinfo {author} {\bibfnamefont {I.~M.}\ \bibnamefont
  {Vishik}}, \bibinfo {author} {\bibfnamefont {R.-H.}\ \bibnamefont {He}},
  \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont {Devereaux}},\ and\
  \bibinfo {author} {\bibfnamefont {Z.-X.}\ \bibnamefont {Shen}},\ }\bibfield
  {title} {\bibinfo {title} {Energy gaps in high-transition-temperature cuprate
  superconductors},\ }\href {https://doi.org/10.1038/nphys3009} {\bibfield
  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
  {10}},\ \bibinfo {pages} {483} (\bibinfo {year} {2014})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Taillefer}(2010)}]{taillefer2010}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Taillefer}},\ }\bibfield  {title} {\bibinfo {title} {Scattering and pairing
  in cuprate superconductors},\ }\href
  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-070909-104117}
  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
  Physics}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo {pages} {51} (\bibinfo
  {year} {2010})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Fradkin}\ \emph {et~al.}(2015)\citenamefont
  {Fradkin}, \citenamefont {Kivelson},\ and\ \citenamefont
  {Tranquada}}]{FradkinRevModPhys2015}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
  {Fradkin}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
  {Kivelson}},\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
  {Tranquada}},\ }\bibfield  {title} {\bibinfo {title} {Colloquium: Theory of
  intertwined orders in high temperature superconductors},\ }\href
  {https://doi.org/10.1103/RevModPhys.87.457} {\bibfield  {journal} {\bibinfo
  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {87}},\ \bibinfo
  {pages} {457} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Sato}\ \emph {et~al.}(2017)\citenamefont {Sato},
  \citenamefont {Kasahara}, \citenamefont {Murayama}, \citenamefont {Kasahara},
  \citenamefont {Moon}, \citenamefont {Nishizaki}, \citenamefont {Loew},
  \citenamefont {Porras}, \citenamefont {Keimer}, \citenamefont {Shibauchi},\
  and\ \citenamefont {Matsuda}}]{Sato2017}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
  {Sato}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Kasahara}},
  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Murayama}}, \bibinfo
  {author} {\bibfnamefont {Y.}~\bibnamefont {Kasahara}}, \bibinfo {author}
  {\bibfnamefont {E.-G.}\ \bibnamefont {Moon}}, \bibinfo {author}
  {\bibfnamefont {T.}~\bibnamefont {Nishizaki}}, \bibinfo {author}
  {\bibfnamefont {T.}~\bibnamefont {Loew}}, \bibinfo {author} {\bibfnamefont
  {J.}~\bibnamefont {Porras}}, \bibinfo {author} {\bibfnamefont
  {B.}~\bibnamefont {Keimer}}, \bibinfo {author} {\bibfnamefont
  {T.}~\bibnamefont {Shibauchi}},\ and\ \bibinfo {author} {\bibfnamefont
  {Y.}~\bibnamefont {Matsuda}},\ }\bibfield  {title} {\bibinfo {title}
  {Thermodynamic evidence for a nematic phase transition at the onset of the
  pseudogap in yba2cu3oy},\ }\href {https://doi.org/10.1038/nphys4205}
  {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf
  {\bibinfo {volume} {13}},\ \bibinfo {pages} {1074} (\bibinfo {year}
  {2017})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Doiron-Leyraud}\ \emph {et~al.}(2017)\citenamefont
  {Doiron-Leyraud}, \citenamefont {Cyr-Choini{\`e}re}, \citenamefont {Badoux},
  \citenamefont {Ataei}, \citenamefont {Collignon}, \citenamefont {Gourgout},
  \citenamefont {Dufour-Beaus{\'e}jour}, \citenamefont {Tafti}, \citenamefont
  {Lalibert{\'e}}, \citenamefont {Boulanger}, \citenamefont {Matusiak},
  \citenamefont {Graf}, \citenamefont {Kim}, \citenamefont {Zhou},
  \citenamefont {Momono}, \citenamefont {Kurosawa}, \citenamefont {Takagi},\
  and\ \citenamefont {Taillefer}}]{DoironLeyraud2017}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
  {Doiron-Leyraud}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
  {Cyr-Choini{\`e}re}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Badoux}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Ataei}},
  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Collignon}}, \bibinfo
  {author} {\bibfnamefont {A.}~\bibnamefont {Gourgout}}, \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Dufour-Beaus{\'e}jour}}, \bibinfo {author}
  {\bibfnamefont {F.~F.}\ \bibnamefont {Tafti}}, \bibinfo {author}
  {\bibfnamefont {F.}~\bibnamefont {Lalibert{\'e}}}, \bibinfo {author}
  {\bibfnamefont {M.-E.}\ \bibnamefont {Boulanger}}, \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Matusiak}}, \bibinfo {author}
  {\bibfnamefont {D.}~\bibnamefont {Graf}}, \bibinfo {author} {\bibfnamefont
  {M.}~\bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont {J.-S.}\
  \bibnamefont {Zhou}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
  {Momono}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Kurosawa}},
  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\ and\ \bibinfo
  {author} {\bibfnamefont {L.}~\bibnamefont {Taillefer}},\ }\bibfield  {title}
  {\bibinfo {title} {Pseudogap phase of cuprate superconductors confined by
  fermi surface topology},\ }\href {https://doi.org/10.1038/s41467-017-02122-x}
  {\bibfield  {journal} {\bibinfo  {journal} {Nature Communications}\ }\textbf
  {\bibinfo {volume} {8}},\ \bibinfo {pages} {2044} (\bibinfo {year}
  {2017})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Mukhopadhyay}\ \emph {et~al.}(2019)\citenamefont
  {Mukhopadhyay}, \citenamefont {Sharma}, \citenamefont {Kim}, \citenamefont
  {Edkins}, \citenamefont {Hamidian}, \citenamefont {Eisaki}, \citenamefont
  {ichi Uchida}, \citenamefont {Kim}, \citenamefont {Lawler}, \citenamefont
  {Mackenzie}, \citenamefont {Davis},\ and\ \citenamefont
  {Fujita}}]{Mukhopadhyay2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Mukhopadhyay}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
  {Sharma}}, \bibinfo {author} {\bibfnamefont {C.~K.}\ \bibnamefont {Kim}},
  \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont {Edkins}}, \bibinfo
  {author} {\bibfnamefont {M.~H.}\ \bibnamefont {Hamidian}}, \bibinfo {author}
  {\bibfnamefont {H.}~\bibnamefont {Eisaki}}, \bibinfo {author} {\bibfnamefont
  {S.}~\bibnamefont {ichi Uchida}}, \bibinfo {author} {\bibfnamefont {E.-A.}\
  \bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
  {Lawler}}, \bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont
  {Mackenzie}}, \bibinfo {author} {\bibfnamefont {J.~C.~S.}\ \bibnamefont
  {Davis}},\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
  {Fujita}},\ }\bibfield  {title} {\bibinfo {title} {Evidence for a vestigial
  nematic state in the cuprate pseudogap phase},\ }\href
  {https://doi.org/10.1073/pnas.1821454116} {\bibfield  {journal} {\bibinfo
  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
  {\bibinfo {volume} {116}},\ \bibinfo {pages} {13249} (\bibinfo {year}
  {2019})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Gupta}\ \emph {et~al.}(2021)\citenamefont {Gupta},
  \citenamefont {McMahon}, \citenamefont {Sutarto}, \citenamefont {Shi},
  \citenamefont {Gong}, \citenamefont {Wei}, \citenamefont {Shen},
  \citenamefont {He}, \citenamefont {Ma}, \citenamefont {Dragomir},
  \citenamefont {Gaulin},\ and\ \citenamefont {Hawthorn}}]{Naman2021}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~K.}\ \bibnamefont
  {Gupta}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {McMahon}},
  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Sutarto}}, \bibinfo
  {author} {\bibfnamefont {T.}~\bibnamefont {Shi}}, \bibinfo {author}
  {\bibfnamefont {R.}~\bibnamefont {Gong}}, \bibinfo {author} {\bibfnamefont
  {H.~I.}\ \bibnamefont {Wei}}, \bibinfo {author} {\bibfnamefont {K.~M.}\
  \bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {He}}, \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Ma}}, \bibinfo
  {author} {\bibfnamefont {M.}~\bibnamefont {Dragomir}}, \bibinfo {author}
  {\bibfnamefont {B.~D.}\ \bibnamefont {Gaulin}},\ and\ \bibinfo {author}
  {\bibfnamefont {D.~G.}\ \bibnamefont {Hawthorn}},\ }\bibfield  {title}
  {\bibinfo {title} {Vanishing nematic order beyond the pseudogap phase in
  overdoped cuprate superconductors},\ }\href
  {https://doi.org/10.1073/pnas.2106881118} {\bibfield  {journal} {\bibinfo
  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
  {\bibinfo {volume} {118}},\ \bibinfo {pages} {e2106881118} (\bibinfo {year}
  {2021})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Horio}\ \emph {et~al.}(2025)\citenamefont {Horio},
  \citenamefont {Sakai}, \citenamefont {Suzuki}, \citenamefont {Nonaka},
  \citenamefont {Hashimoto}, \citenamefont {Lu}, \citenamefont {Shen},
  \citenamefont {Ohgi}, \citenamefont {Konno}, \citenamefont {Adachi},
  \citenamefont {Koike}, \citenamefont {Imada},\ and\ \citenamefont
  {Fujimori}}]{Masafumi2025}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Horio}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Sakai}},
  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Suzuki}}, \bibinfo
  {author} {\bibfnamefont {Y.}~\bibnamefont {Nonaka}}, \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Hashimoto}}, \bibinfo {author}
  {\bibfnamefont {D.}~\bibnamefont {Lu}}, \bibinfo {author} {\bibfnamefont
  {Z.-X.}\ \bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont
  {T.}~\bibnamefont {Ohgi}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
  {Konno}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Adachi}},
  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Koike}}, \bibinfo
  {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ and\ \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Fujimori}},\ }\bibfield  {title} {\bibinfo
  {title} {Pseudogap in electron-doped cuprates: Strong correlation leading to
  band splitting},\ }\href {https://doi.org/10.1073/pnas.2406624122} {\bibfield
   {journal} {\bibinfo  {journal} {Proceedings of the National Academy of
  Sciences}\ }\textbf {\bibinfo {volume} {122}},\ \bibinfo {pages}
  {e2406624122} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Kyung}\ \emph {et~al.}(2006)\citenamefont {Kyung},
  \citenamefont {Kancharla}, \citenamefont {S\'en\'echal}, \citenamefont
  {Tremblay}, \citenamefont {Civelli},\ and\ \citenamefont
  {Kotliar}}]{KyungKotliar2006}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
  {Kyung}}, \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont
  {Kancharla}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
  {S\'en\'echal}}, \bibinfo {author} {\bibfnamefont {A.-M.~S.}\ \bibnamefont
  {Tremblay}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Civelli}},\
  and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Kotliar}},\
  }\bibfield  {title} {\bibinfo {title} {Pseudogap induced by short-range spin
  correlations in a doped mott insulator},\ }\href
  {https://doi.org/10.1103/PhysRevB.73.165114} {\bibfield  {journal} {\bibinfo
  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo
  {pages} {165114} (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Macridin}\ \emph {et~al.}(2006)\citenamefont
  {Macridin}, \citenamefont {Jarrell}, \citenamefont {Maier}, \citenamefont
  {Kent},\ and\ \citenamefont {D'Azevedo}}]{MacridinAzevedo2006}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Macridin}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Jarrell}},
  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Maier}}, \bibinfo
  {author} {\bibfnamefont {P.~R.~C.}\ \bibnamefont {Kent}},\ and\ \bibinfo
  {author} {\bibfnamefont {E.}~\bibnamefont {D'Azevedo}},\ }\bibfield  {title}
  {\bibinfo {title} {Pseudogap and antiferromagnetic correlations in the
  hubbard model},\ }\href {https://doi.org/10.1103/PhysRevLett.97.036401}
  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
  {\bibinfo {volume} {97}},\ \bibinfo {pages} {036401} (\bibinfo {year}
  {2006})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2009)\citenamefont {Sakai},
  \citenamefont {Motome},\ and\ \citenamefont {Imada}}]{sakai2009evolution}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Sakai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Motome}},\ and\
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\bibfield
  {title} {\bibinfo {title} {Evolution of electronic structure of doped mott
  insulators: Reconstruction of poles and zeros of green’s function},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical review
  letters}\ }\textbf {\bibinfo {volume} {102}},\ \bibinfo {pages} {056404}
  (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Werner}\ \emph {et~al.}(2009)\citenamefont {Werner},
  \citenamefont {Gull}, \citenamefont {Parcollet},\ and\ \citenamefont
  {Millis}}]{werner2009momentum}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {Werner}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Gull}},
  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}},\ and\
  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\ }\bibfield
   {title} {\bibinfo {title} {Momentum-selective metal-insulator transition in
  the two-dimensional hubbard model: An 8-site dynamical cluster approximation
  study},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical
  Review B}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages} {045120}
  (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2010)\citenamefont {Sakai},
  \citenamefont {Motome},\ and\ \citenamefont {Imada}}]{sakai2010doped}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Sakai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Motome}},\ and\
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\bibfield
  {title} {\bibinfo {title} {Doped high-t c cuprate superconductors elucidated
  in the light of zeros and poles of the electronic green’s function},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
  B}\ }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {134505} (\bibinfo
  {year} {2010})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Lin}\ \emph {et~al.}(2010)\citenamefont {Lin},
  \citenamefont {Gull},\ and\ \citenamefont {Millis}}]{lin2010}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
  {Lin}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Gull}},\ and\
  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\ }\bibfield
   {title} {\bibinfo {title} {Physics of the pseudogap in eight-site cluster
  dynamical mean-field theory: Photoemission, raman scattering, and in-plane
  and c-axs=is conductivity},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {82}},\ \bibinfo
  {pages} {045104} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Gull}\ \emph {et~al.}(2010)\citenamefont {Gull},
  \citenamefont {Ferrero}, \citenamefont {Parcollet}, \citenamefont {Georges},\
  and\ \citenamefont {Millis}}]{gull2010momentum}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
  {Gull}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ferrero}},
  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}}, \bibinfo
  {author} {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
  {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\ }\bibfield  {title}
  {\bibinfo {title} {Momentum-space anisotropy and pseudogaps: A comparative
  cluster dynamical mean-field analysis of the doping-driven metal-insulator
  transition in the two-dimensional hubbard model},\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {Physical Review B}\ }\textbf {\bibinfo
  {volume} {82}},\ \bibinfo {pages} {155101} (\bibinfo {year}
  {2010})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Gull}\ and\ \citenamefont {Millis}(2012)}]{gull2012}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
  {Gull}}\ and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
  {Millis}},\ }\bibfield  {title} {\bibinfo {title} {Energetics of
  superconductivity in the two-dimensional hubbard model},\ }\href@noop {}
  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo
  {volume} {86}},\ \bibinfo {pages} {241106} (\bibinfo {year}
  {2012})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Mirzaei}\ \emph {et~al.}(2013)\citenamefont
  {Mirzaei}, \citenamefont {Stricker}, \citenamefont {Hancock}, \citenamefont
  {Berthod}, \citenamefont {Georges}, \citenamefont {van Heumen}, \citenamefont
  {Chan}, \citenamefont {Zhao}, \citenamefont {Li}, \citenamefont {Greven},
  \citenamefont {Barišić},\ and\ \citenamefont {van~der
  Marel}}]{Mirzaei2013}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~I.}\ \bibnamefont
  {Mirzaei}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Stricker}},
  \bibinfo {author} {\bibfnamefont {J.~N.}\ \bibnamefont {Hancock}}, \bibinfo
  {author} {\bibfnamefont {C.}~\bibnamefont {Berthod}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Georges}}, \bibinfo {author} {\bibfnamefont
  {E.}~\bibnamefont {van Heumen}}, \bibinfo {author} {\bibfnamefont {M.~K.}\
  \bibnamefont {Chan}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
  {Zhao}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Li}}, \bibinfo
  {author} {\bibfnamefont {M.}~\bibnamefont {Greven}}, \bibinfo {author}
  {\bibfnamefont {N.}~\bibnamefont {Barišić}},\ and\ \bibinfo {author}
  {\bibfnamefont {D.}~\bibnamefont {van~der Marel}},\ }\bibfield  {title}
  {\bibinfo {title} {Spectroscopic evidence for fermi liquid-like energy and
  temperature dependence of the relaxation rate in the pseudogap phase of the
  cuprates},\ }\href {https://doi.org/10.1073/pnas.1218846110} {\bibfield
  {journal} {\bibinfo  {journal} {Proceedings of the National Academy of
  Sciences}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo {pages} {5774}
  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Gull}\ \emph {et~al.}(2013)\citenamefont {Gull},
  \citenamefont {Parcollet},\ and\ \citenamefont {Millis}}]{gull2013}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
  {Gull}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}},\
  and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
  }\bibfield  {title} {\bibinfo {title} {Superconductivity and the pseudogap in
  the two-dimensional hubbard model},\ }\href@noop {} {\bibfield  {journal}
  {\bibinfo  {journal} {Physical review letters}\ }\textbf {\bibinfo {volume}
  {110}},\ \bibinfo {pages} {216405} (\bibinfo {year} {2013})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
  {Lal}(2020{\natexlab{a}})}]{anirbanmott2}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Lal}},\ }\bibfield  {title} {\bibinfo {title} {Scaling theory for
  mott{\textendash}hubbard transitions-{II}: quantum criticality of the doped
  mott insulator},\ }\href {https://doi.org/10.1088/1367-2630/ab890c}
  {\bibfield  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf
  {\bibinfo {volume} {22}},\ \bibinfo {pages} {063008} (\bibinfo {year}
  {2020}{\natexlab{a}})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Hille}\ \emph {et~al.}(2020)\citenamefont {Hille},
  \citenamefont {Rohe}, \citenamefont {Honerkamp},\ and\ \citenamefont
  {Andergassen}}]{HilleAndergassen2020}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
  {Hille}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Rohe}},
  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Honerkamp}},\ and\
  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Andergassen}},\
  }\bibfield  {title} {\bibinfo {title} {Pseudogap opening in the
  two-dimensional hubbard model: A functional renormalization group analysis},\
  }\href {https://doi.org/10.1103/PhysRevResearch.2.033068} {\bibfield
  {journal} {\bibinfo  {journal} {Phys. Rev. Res.}\ }\textbf {\bibinfo {volume}
  {2}},\ \bibinfo {pages} {033068} (\bibinfo {year} {2020})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Jiang}\ \emph {et~al.}(2022)\citenamefont {Jiang},
  \citenamefont {Liu}, \citenamefont {Klein}, \citenamefont {Wang},
  \citenamefont {Sun}, \citenamefont {Chubukov},\ and\ \citenamefont
  {Meng}}]{Jiang2022}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
  {Jiang}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Liu}}, \bibinfo
  {author} {\bibfnamefont {A.}~\bibnamefont {Klein}}, \bibinfo {author}
  {\bibfnamefont {Y.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont
  {K.}~\bibnamefont {Sun}}, \bibinfo {author} {\bibfnamefont {A.~V.}\
  \bibnamefont {Chubukov}},\ and\ \bibinfo {author} {\bibfnamefont {Z.~Y.}\
  \bibnamefont {Meng}},\ }\bibfield  {title} {\bibinfo {title} {Monte carlo
  study of the pseudogap and superconductivity emerging from quantum magnetic
  fluctuations},\ }\href {https://doi.org/10.1038/s41467-022-30302-x}
  {\bibfield  {journal} {\bibinfo  {journal} {Nature Communications}\ }\textbf
  {\bibinfo {volume} {13}},\ \bibinfo {pages} {2655} (\bibinfo {year}
  {2022})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Scheurer}\ \emph {et~al.}(2018)\citenamefont
  {Scheurer}, \citenamefont {Chatterjee}, \citenamefont {Wu}, \citenamefont
  {Ferrero}, \citenamefont {Georges},\ and\ \citenamefont
  {Sachdev}}]{Scheurer2018}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont
  {Scheurer}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Chatterjee}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Wu}},
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ferrero}}, \bibinfo
  {author} {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Sachdev}},\ }\bibfield  {title} {\bibinfo
  {title} {Topological order in the pseudogap metal},\ }\href
  {https://doi.org/10.1073/pnas.1720580115} {\bibfield  {journal} {\bibinfo
  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
  {\bibinfo {volume} {115}},\ \bibinfo {pages} {E3665} (\bibinfo {year}
  {2018})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Krien}\ \emph {et~al.}(2022)\citenamefont {Krien},
  \citenamefont {Worm}, \citenamefont {Chalupa-Gantner}, \citenamefont
  {Toschi},\ and\ \citenamefont {Held}}]{Krien2022}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {Krien}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Worm}},
  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Chalupa-Gantner}},
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Toschi}},\ and\ \bibinfo
  {author} {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\bibfield  {title}
  {\bibinfo {title} {Explaining the pseudogap through damping and antidamping
  on the fermi surface by imaginary spin scattering},\ }\href
  {https://doi.org/10.1038/s42005-022-01117-5} {\bibfield  {journal} {\bibinfo
  {journal} {Communications Physics}\ }\textbf {\bibinfo {volume} {5}},\
  \bibinfo {pages} {336} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Kitatani}\ \emph {et~al.}(2023)\citenamefont
  {Kitatani}, \citenamefont {Si}, \citenamefont {Worm}, \citenamefont
  {Tomczak}, \citenamefont {Arita},\ and\ \citenamefont {Held}}]{Kitatani2023}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Kitatani}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Si}},
  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Worm}}, \bibinfo {author}
  {\bibfnamefont {J.~M.}\ \bibnamefont {Tomczak}}, \bibinfo {author}
  {\bibfnamefont {R.}~\bibnamefont {Arita}},\ and\ \bibinfo {author}
  {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\bibfield  {title} {\bibinfo
  {title} {Optimizing superconductivity: From cuprates via nickelates to
  palladates},\ }\href {https://doi.org/10.1103/PhysRevLett.130.166002}
  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
  {\bibinfo {volume} {130}},\ \bibinfo {pages} {166002} (\bibinfo {year}
  {2023})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Sorella}(2023)}]{Sorella2023}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Sorella}},\ }\bibfield  {title} {\bibinfo {title} {Systematically improvable
  mean-field variational ansatz for strongly correlated systems: Application to
  the hubbard model},\ }\href {https://doi.org/10.1103/PhysRevB.107.115133}
  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo
  {volume} {107}},\ \bibinfo {pages} {115133} (\bibinfo {year}
  {2023})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Schäfer}\ \emph {et~al.}(2021)\citenamefont
  {Schäfer}, \citenamefont {Wentzell}, \citenamefont {Šimkovic},
  \citenamefont {He}, \citenamefont {Hille}, \citenamefont {Klett},
  \citenamefont {Eckhardt}, \citenamefont {Arzhang}, \citenamefont {Harkov},
  \citenamefont {Le~R\'egent}, \citenamefont {Kirsch}, \citenamefont {Wang},
  \citenamefont {Kim}, \citenamefont {Kozik}, \citenamefont {Stepanov},
  \citenamefont {Kauch}, \citenamefont {Andergassen}, \citenamefont {Hansmann},
  \citenamefont {Rohe}, \citenamefont {Vilk}, \citenamefont {LeBlanc},
  \citenamefont {Zhang}, \citenamefont {Tremblay}, \citenamefont {Ferrero},
  \citenamefont {Parcollet},\ and\ \citenamefont {Georges}}]{Schafer2021}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
  {Schäfer}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Wentzell}},
  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Šimkovic}}, \bibinfo
  {author} {\bibfnamefont {Y.-Y.}\ \bibnamefont {He}}, \bibinfo {author}
  {\bibfnamefont {C.}~\bibnamefont {Hille}}, \bibinfo {author} {\bibfnamefont
  {M.}~\bibnamefont {Klett}}, \bibinfo {author} {\bibfnamefont {C.~J.}\
  \bibnamefont {Eckhardt}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
  {Arzhang}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Harkov}},
  \bibinfo {author} {\bibfnamefont {F.~m. c.-M.}\ \bibnamefont {Le~R\'egent}},
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kirsch}}, \bibinfo
  {author} {\bibfnamefont {Y.}~\bibnamefont {Wang}}, \bibinfo {author}
  {\bibfnamefont {A.~J.}\ \bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont
  {E.}~\bibnamefont {Kozik}}, \bibinfo {author} {\bibfnamefont {E.~A.}\
  \bibnamefont {Stepanov}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Kauch}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Andergassen}},
  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Hansmann}}, \bibinfo
  {author} {\bibfnamefont {D.}~\bibnamefont {Rohe}}, \bibinfo {author}
  {\bibfnamefont {Y.~M.}\ \bibnamefont {Vilk}}, \bibinfo {author}
  {\bibfnamefont {J.~P.~F.}\ \bibnamefont {LeBlanc}}, \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
  {A.-M.~S.}\ \bibnamefont {Tremblay}}, \bibinfo {author} {\bibfnamefont
  {M.}~\bibnamefont {Ferrero}}, \bibinfo {author} {\bibfnamefont
  {O.}~\bibnamefont {Parcollet}},\ and\ \bibinfo {author} {\bibfnamefont
  {A.}~\bibnamefont {Georges}},\ }\bibfield  {title} {\bibinfo {title}
  {Tracking the footprints of spin fluctuations: A multimethod, multimessenger
  study of the two-dimensional hubbard model},\ }\href
  {https://doi.org/10.1103/PhysRevX.11.011058} {\bibfield  {journal} {\bibinfo
  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
  {pages} {011058} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {White}\ and\ \citenamefont
  {Scalapino}(1998)}]{White1998}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~R.}\ \bibnamefont
  {White}}\ and\ \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
  {Scalapino}},\ }\bibfield  {title} {\bibinfo {title} {Density matrix
  renormalization group study of the striped phase in the 2d
  $\mathit{t}\ensuremath{-}\mathit{J}$ model},\ }\href
  {https://doi.org/10.1103/PhysRevLett.80.1272} {\bibfield  {journal} {\bibinfo
   {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo
  {pages} {1272} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Ido}\ \emph {et~al.}(2018)\citenamefont {Ido},
  \citenamefont {Ohgoe},\ and\ \citenamefont {Imada}}]{Ido2018}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
  {Ido}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Ohgoe}},\ and\
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\bibfield
  {title} {\bibinfo {title} {Competition among various charge-inhomogeneous
  states and $d$-wave superconducting state in hubbard models on square
  lattices},\ }\href {https://doi.org/10.1103/PhysRevB.97.045138} {\bibfield
  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
  {97}},\ \bibinfo {pages} {045138} (\bibinfo {year} {2018})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Proust}\ and\ \citenamefont
  {Taillefer}(2019)}]{ProustTaillefer2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
  {Proust}}\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Taillefer}},\ }\bibfield  {title} {\bibinfo {title} {The remarkable
  underlying ground states of cuprate superconductors},\ }\href
  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-031218-013210}
  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
  Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {409}
  (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Ponsioen}\ \emph {et~al.}(2019)\citenamefont
  {Ponsioen}, \citenamefont {Chung},\ and\ \citenamefont
  {Corboz}}]{Ponsioen2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
  {Ponsioen}}, \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont
  {Chung}},\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {Corboz}},\ }\bibfield  {title} {\bibinfo {title} {Period 4 stripe in the
  extended two-dimensional hubbard model},\ }\href
  {https://doi.org/10.1103/PhysRevB.100.195141} {\bibfield  {journal} {\bibinfo
   {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {100}},\ \bibinfo
  {pages} {195141} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Xu}\ \emph {et~al.}(2022)\citenamefont {Xu},
  \citenamefont {Shi}, \citenamefont {Vitali}, \citenamefont {Qin},\ and\
  \citenamefont {Zhang}}]{XuZhang2022}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
  {Xu}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Shi}}, \bibinfo
  {author} {\bibfnamefont {E.}~\bibnamefont {Vitali}}, \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Qin}},\ and\ \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Zhang}},\ }\bibfield  {title} {\bibinfo
  {title} {Stripes and spin-density waves in the doped two-dimensional hubbard
  model: Ground state phase diagram},\ }\href
  {https://doi.org/10.1103/PhysRevResearch.4.013239} {\bibfield  {journal}
  {\bibinfo  {journal} {Phys. Rev. Res.}\ }\textbf {\bibinfo {volume} {4}},\
  \bibinfo {pages} {013239} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Dave}\ \emph {et~al.}(2013)\citenamefont {Dave},
  \citenamefont {Phillips},\ and\ \citenamefont {Kane}}]{Phillips2013}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~B.}\ \bibnamefont
  {Dave}}, \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\
  and\ \bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont {Kane}},\
  }\bibfield  {title} {\bibinfo {title} {Absence of luttinger's theorem due to
  zeros in the single-particle green function},\ }\href
  {https://doi.org/10.1103/PhysRevLett.110.090403} {\bibfield  {journal}
  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {110}},\
  \bibinfo {pages} {090403} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Seki}\ and\ \citenamefont
  {Yunoki}(2017)}]{seki2017topological}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
  {Seki}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Yunoki}},\
  }\bibfield  {title} {\bibinfo {title} {Topological interpretation of the
  luttinger theorem},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
  {journal} {Physical Review B}\ }\textbf {\bibinfo {volume} {96}},\ \bibinfo
  {pages} {085124} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Anderson}\ and\ \citenamefont
  {Haldane}(2001)}]{Anderson2001}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
  {Anderson}}\ and\ \bibinfo {author} {\bibfnamefont {F.~D.~M.}\ \bibnamefont
  {Haldane}},\ }\bibfield  {title} {\bibinfo {title} {The symmetries of fermion
  fluids at low dimensions},\ }\href {https://doi.org/10.1023/A:1010324912515}
  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Statistical Physics}\
  }\textbf {\bibinfo {volume} {103}},\ \bibinfo {pages} {425} (\bibinfo {year}
  {2001})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Huang}\ \emph {et~al.}(2022)\citenamefont {Huang},
  \citenamefont {Nave},\ and\ \citenamefont {Phillips}}]{Huang2022}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont
  {Huang}}, \bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont {Nave}},\
  and\ \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\
  }\bibfield  {title} {\bibinfo {title} {Discrete symmetry breaking defines the
  mott quartic fixed point},\ }\href
  {https://doi.org/10.1038/s41567-022-01529-8} {\bibfield  {journal} {\bibinfo
  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {18}},\ \bibinfo
  {pages} {511} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Coleman}\ \emph {et~al.}(2001)\citenamefont
  {Coleman}, \citenamefont {Pépin}, \citenamefont {Si},\ and\ \citenamefont
  {Ramazashvili}}]{Coleman_2001}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {Coleman}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Pépin}},
  \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Si}},\ and\ \bibinfo
  {author} {\bibfnamefont {R.}~\bibnamefont {Ramazashvili}},\ }\bibfield
  {title} {\bibinfo {title} {How do fermi liquids get heavy and die?},\ }\href
  {https://doi.org/10.1088/0953-8984/13/35/202} {\bibfield  {journal} {\bibinfo
   {journal} {Journal of Physics: Condensed Matter}\ }\textbf {\bibinfo
  {volume} {13}},\ \bibinfo {pages} {R723} (\bibinfo {year}
  {2001})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
  {Lal}(2020{\natexlab{b}})}]{anirbanurg1}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Lal}},\ }\bibfield  {title} {\bibinfo {title} {Unitary renormalisation group
  for correlated electrons-i: a tensor network approach},\ }\href@noop {}
  {\bibfield  {journal} {\bibinfo  {journal} {Nuclear Physics B}\ }\textbf
  {\bibinfo {volume} {960}},\ \bibinfo {pages} {115170} (\bibinfo {year}
  {2020}{\natexlab{b}})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
  {Lal}(2020{\natexlab{c}})}]{anirbanurg2}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Lal}},\ }\bibfield  {title} {\bibinfo {title} {Unitary renormalisation group
  for correlated electrons-ii: insights on fermionic criticality},\ }\href@noop
  {} {\bibfield  {journal} {\bibinfo  {journal} {Nuclear Physics B}\ }\textbf
  {\bibinfo {volume} {960}},\ \bibinfo {pages} {115163} (\bibinfo {year}
  {2020}{\natexlab{c}})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Keimer}\ \emph {et~al.}(2015)\citenamefont {Keimer},
  \citenamefont {Kivelson}, \citenamefont {Norman}, \citenamefont {Uchida},\
  and\ \citenamefont {Zaanen}}]{keimer2015quantum}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
  {Keimer}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
  {Kivelson}}, \bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
  {Norman}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Uchida}},\
  and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zaanen}},\
  }\bibfield  {title} {\bibinfo {title} {From quantum matter to
  high-temperature superconductivity in copper oxides},\ }\href@noop {}
  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
  {volume} {518}},\ \bibinfo {pages} {179} (\bibinfo {year}
  {2015})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Hatsugai}\ and\ \citenamefont
  {Kohmoto}(1992)}]{Hatsugai1992}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
  {Hatsugai}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Kohmoto}},\ }\bibfield  {title} {\bibinfo {title} {Exactly solvable model of
  correlated lattice electrons in any dimensions},\ }\href
  {https://doi.org/10.1143/JPSJ.61.2056} {\bibfield  {journal} {\bibinfo
  {journal} {Journal of the Physical Society of Japan}\ }\textbf {\bibinfo
  {volume} {61}},\ \bibinfo {pages} {2056} (\bibinfo {year}
  {1992})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Baskaran}(1991)}]{Baskaran1991}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Baskaran}},\ }\bibfield  {title} {\bibinfo {title} {An exactly solvable
  fermion model: spinons, holons and a non-fermi liquid phase},\ }\href
  {https://doi.org/10.1142/S0217984991000782} {\bibfield  {journal} {\bibinfo
  {journal} {Modern Physics Letters B}\ }\textbf {\bibinfo {volume} {05}},\
  \bibinfo {pages} {643} (\bibinfo {year} {1991})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Altshuler}\ \emph {et~al.}(1998)\citenamefont
  {Altshuler}, \citenamefont {Chubukov}, \citenamefont {Dashevskii},
  \citenamefont {Finkel'stein},\ and\ \citenamefont {Morr}}]{Altshuler_1998}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~L.}\ \bibnamefont
  {Altshuler}}, \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
  {Chubukov}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Dashevskii}}, \bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
  {Finkel'stein}},\ and\ \bibinfo {author} {\bibfnamefont {D.~K.}\ \bibnamefont
  {Morr}},\ }\bibfield  {title} {\bibinfo {title} {Luttinger theorem for a
  spin-density-wave state},\ }\href {https://doi.org/10.1209/epl/i1998-00164-y}
  {\bibfield  {journal} {\bibinfo  {journal} {Europhysics Letters}\ }\textbf
  {\bibinfo {volume} {41}},\ \bibinfo {pages} {401} (\bibinfo {year}
  {1998})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Heath}\ and\ \citenamefont
  {Bedell}(2020)}]{Heath_2020}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont
  {Heath}}\ and\ \bibinfo {author} {\bibfnamefont {K.~S.}\ \bibnamefont
  {Bedell}},\ }\bibfield  {title} {\bibinfo {title} {Necessary and sufficient
  conditions for the validity of luttinger’s theorem},\ }\href
  {https://doi.org/10.1088/1367-2630/ab890e} {\bibfield  {journal} {\bibinfo
  {journal} {New Journal of Physics}\ }\textbf {\bibinfo {volume} {22}},\
  \bibinfo {pages} {063011} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Nave}\ \emph {et~al.}(2025)\citenamefont {Nave},
  \citenamefont {Zhao},\ and\ \citenamefont {Phillips}}]{lanave2025}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont
  {Nave}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zhao}},\ and\
  \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\ }\href
  {https://arxiv.org/abs/2506.04342} {} (\bibinfo {year} {2025}),\ \Eprint
  {https://arxiv.org/abs/2506.04342} {arXiv:2506.04342 [cond-mat.str-el]}
  \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Mukherjee}\ \emph {et~al.}(2023)\citenamefont
  {Mukherjee}, \citenamefont {Vidhyadhiraja}, \citenamefont {Taraphder},\ and\
  \citenamefont {Lal}}]{Mukherjee_2023}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Mukherjee}}, \bibinfo {author} {\bibfnamefont {N.~S.}\ \bibnamefont
  {Vidhyadhiraja}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Taraphder}},\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Lal}},\ }\bibfield  {title} {\bibinfo {title} {Kondo frustration via charge
  fluctuations: a route to mott localisation},\ }\href
  {https://doi.org/10.1088/1367-2630/ad08f3} {\bibfield  {journal} {\bibinfo
  {journal} {New Journal of Physics}\ }\textbf {\bibinfo {volume} {25}},\
  \bibinfo {pages} {113011} (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Georges}\ \emph {et~al.}(1996)\citenamefont
  {Georges}, \citenamefont {Kotliar}, \citenamefont {Krauth},\ and\
  \citenamefont {Rozenberg}}]{georges1996}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Georges}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Kotliar}},
  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Krauth}},\ and\ \bibinfo
  {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Rozenberg}},\ }\bibfield
  {title} {\bibinfo {title} {Dynamical mean-field theory of strongly correlated
  fermion systems and the limit of infinite dimensions},\ }\href@noop {}
  {\bibfield  {journal} {\bibinfo  {journal} {Reviews of Modern Physics}\
  }\textbf {\bibinfo {volume} {68}},\ \bibinfo {pages} {13} (\bibinfo {year}
  {1996})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Hettler}\ \emph {et~al.}(1998)\citenamefont
  {Hettler}, \citenamefont {Tahvildar-Zadeh}, \citenamefont {Jarrell},
  \citenamefont {Pruschke},\ and\ \citenamefont {Krishnamurthy}}]{hettler1998}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Hettler}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Tahvildar-Zadeh}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Jarrell}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Pruschke}},\
  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Krishnamurthy}},\
  }\bibfield  {title} {\bibinfo {title} {Nonlocal dynamical correlations of
  strongly interacting electron systems},\ }\href@noop {} {\bibfield  {journal}
  {\bibinfo  {journal} {Physical Review B}\ }\textbf {\bibinfo {volume} {58}},\
  \bibinfo {pages} {R7475} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Kotliar}\ \emph {et~al.}(2001)\citenamefont
  {Kotliar}, \citenamefont {Savrasov}, \citenamefont {P{\'a}lsson},\ and\
  \citenamefont {Biroli}}]{kotliar2001}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Kotliar}}, \bibinfo {author} {\bibfnamefont {S.~Y.}\ \bibnamefont
  {Savrasov}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {P{\'a}lsson}},\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Biroli}},\ }\bibfield  {title} {\bibinfo {title} {Cellular dynamical mean
  field approach to strongly correlated systems},\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {Physical review letters}\ }\textbf {\bibinfo
  {volume} {87}},\ \bibinfo {pages} {186401} (\bibinfo {year}
  {2001})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Maier}\ \emph {et~al.}(2005)\citenamefont {Maier},
  \citenamefont {Jarrell}, \citenamefont {Schulthess}, \citenamefont {Kent},\
  and\ \citenamefont {White}}]{maier2005}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont
  {Maier}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Jarrell}},
  \bibinfo {author} {\bibfnamefont {T.~C.}\ \bibnamefont {Schulthess}},
  \bibinfo {author} {\bibfnamefont {P.~R.~C.}\ \bibnamefont {Kent}},\ and\
  \bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont {White}},\ }\bibfield
  {title} {\bibinfo {title} {Systematic study of d-wave superconductivity in
  the 2d repulsive hubbard model},\ }\href@noop {} {\bibfield  {journal}
  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {95}},\
  \bibinfo {pages} {237001} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Stoyanova}(2006)}]{stoyanova}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Stoyanova}},\ }\emph {\bibinfo {title} {Delocalized and correlated wave
  functions for excited states in extended systems}},\ \href@noop {} {Ph.D.
  thesis},\ \bibinfo  {school} {University of Groningen} (\bibinfo {year}
  {2006})\BibitemShut {NoStop}%
\bibitem [{sup()}]{suppmat}%
  \BibitemOpen
  \href@noop {} {\bibinfo {title} {See supplemental material for additional
  information.}}\BibitemShut {Stop}%
\bibitem [{\citenamefont {Wu}\ \emph {et~al.}(2018)\citenamefont {Wu},
  \citenamefont {Scheurer}, \citenamefont {Chatterjee}, \citenamefont
  {Sachdev}, \citenamefont {Georges},\ and\ \citenamefont
  {Ferrero}}]{WuFerrero2018}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
  {Wu}}, \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Scheurer}},
  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Chatterjee}}, \bibinfo
  {author} {\bibfnamefont {S.}~\bibnamefont {Sachdev}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Ferrero}},\ }\bibfield  {title} {\bibinfo
  {title} {Pseudogap and fermi-surface topology in the two-dimensional hubbard
  model},\ }\href {https://doi.org/10.1103/PhysRevX.8.021048} {\bibfield
  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume}
  {8}},\ \bibinfo {pages} {021048} (\bibinfo {year} {2018})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Tsvelick}\ and\ \citenamefont
  {Wiegmann}(1985)}]{Tsvelick_weigmann_mchannel_1985}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
  {Tsvelick}}\ and\ \bibinfo {author} {\bibfnamefont {P.~B.}\ \bibnamefont
  {Wiegmann}},\ }\bibfield  {title} {\bibinfo {title} {Exact solution of the
  multichannel kondo problem, scaling, and integrability},\ }\href
  {https://doi.org/10.1007/BF01017853} {\bibfield  {journal} {\bibinfo
  {journal} {Journal of Statistical Physics}\ }\textbf {\bibinfo {volume}
  {38}},\ \bibinfo {pages} {125} (\bibinfo {year} {1985})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Emery}\ and\ \citenamefont
  {Kivelson}(1992)}]{emery_kivelson}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~J.}\ \bibnamefont
  {Emery}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Kivelson}},\ }\bibfield  {title} {\bibinfo {title} {Mapping of the
  two-channel kondo problem to a resonant-level model},\ }\href
  {https://doi.org/10.1103/PhysRevB.46.10812} {\bibfield  {journal} {\bibinfo
  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {46}},\ \bibinfo
  {pages} {10812} (\bibinfo {year} {1992})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Gunnarsson}\ \emph {et~al.}(2003)\citenamefont
  {Gunnarsson}, \citenamefont {Calandra},\ and\ \citenamefont
  {Han}}]{GunnarssonRMP2003}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
  {Gunnarsson}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Calandra}},\ and\ \bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont
  {Han}},\ }\bibfield  {title} {\bibinfo {title} {Colloquium: Saturation of
  electrical resistivity},\ }\href {https://doi.org/10.1103/RevModPhys.75.1085}
  {\bibfield  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf
  {\bibinfo {volume} {75}},\ \bibinfo {pages} {1085} (\bibinfo {year}
  {2003})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Hussey}\ \emph {et~al.}(2004)\citenamefont {Hussey},
  \citenamefont {Takenaka},\ and\ \citenamefont {Takagi}}]{Hussey2004}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
  {Hussey}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Takenaka}},\
  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\
  }\bibfield  {title} {\bibinfo {title} {Universality of the
  mott–ioffe–regel limit in metals},\ }\href
  {https://doi.org/10.1080/14786430410001716944} {\bibfield  {journal}
  {\bibinfo  {journal} {Philosophical Magazine}\ }\textbf {\bibinfo {volume}
  {84}},\ \bibinfo {pages} {2847} (\bibinfo {year} {2004})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Pustogow}\ \emph {et~al.}(2021)\citenamefont
  {Pustogow}, \citenamefont {Saito}, \citenamefont {Anja~Löhle}, \citenamefont
  {Alonso}, \citenamefont {Kawamoto}, \citenamefont {Dobrosavljevic},
  \citenamefont {Dressel},\ and\ \citenamefont {Fratini}}]{pustogow2021}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Pustogow}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Saito}},
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Anja~Löhle}}, \bibinfo
  {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Alonso}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Kawamoto}}, \bibinfo {author}
  {\bibfnamefont {V.}~\bibnamefont {Dobrosavljevic}}, \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Dressel}},\ and\ \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Fratini}},\ }\bibfield  {title} {\bibinfo
  {title} {Rise and fall of landau’s quasiparticles while approaching the
  mott transition},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
  {Nat. Comm.}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {1571}
  (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Qazilbash}\ \emph {et~al.}(2008)\citenamefont
  {Qazilbash}, \citenamefont {Schafgans}, \citenamefont {Burch}, \citenamefont
  {Yun}, \citenamefont {Chae}, \citenamefont {Kim}, \citenamefont {Kim},\ and\
  \citenamefont {Basov}}]{qazilbash2008}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~M.}\ \bibnamefont
  {Qazilbash}}, \bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont
  {Schafgans}}, \bibinfo {author} {\bibfnamefont {K.~S.}\ \bibnamefont
  {Burch}}, \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont {Yun}},
  \bibinfo {author} {\bibfnamefont {B.~G.}\ \bibnamefont {Chae}}, \bibinfo
  {author} {\bibfnamefont {B.~J.}\ \bibnamefont {Kim}}, \bibinfo {author}
  {\bibfnamefont {H.~T.}\ \bibnamefont {Kim}},\ and\ \bibinfo {author}
  {\bibfnamefont {D.~N.}\ \bibnamefont {Basov}},\ }\bibfield  {title} {\bibinfo
  {title} {Electrodynamics of the vanadium oxides $\mathrm{V}{\mathrm{o}}_{2}$
  and ${\mathrm{v}}_{2}{\mathrm{o}}_{3}$},\ }\href
  {https://doi.org/10.1103/PhysRevB.77.115121} {\bibfield  {journal} {\bibinfo
  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo
  {pages} {115121} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Hauke}\ \emph {et~al.}(2016)\citenamefont {Hauke},
  \citenamefont {Heyl}, \citenamefont {Tagliacozzo},\ and\ \citenamefont
  {Zoller}}]{Hauke2016}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {Hauke}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Heyl}},
  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Tagliacozzo}},\ and\
  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Zoller}},\ }\bibfield
  {title} {\bibinfo {title} {Measuring multipartite entanglement through
  dynamic susceptibilities},\ }\href {https://doi.org/10.1038/nphys3700}
  {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf
  {\bibinfo {volume} {12}},\ \bibinfo {pages} {778} (\bibinfo {year}
  {2016})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Balut}\ \emph {et~al.}(2025)\citenamefont {Balut},
  \citenamefont {Guo}, \citenamefont {de~Vriesa}, \citenamefont {Chaudhuri},
  \citenamefont {Bradlyn}, \citenamefont {Abbamonte},\ and\ \citenamefont
  {W.}}]{balut2025}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
  {Balut}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Guo}}, \bibinfo
  {author} {\bibfnamefont {N.}~\bibnamefont {de~Vriesa}}, \bibinfo {author}
  {\bibfnamefont {D.}~\bibnamefont {Chaudhuri}}, \bibinfo {author}
  {\bibfnamefont {B.}~\bibnamefont {Bradlyn}}, \bibinfo {author} {\bibfnamefont
  {P.}~\bibnamefont {Abbamonte}},\ and\ \bibinfo {author} {\bibfnamefont
  {P.~P.}\ \bibnamefont {W.}},\ }\bibfield  {title} {\bibinfo {title} {Quantum
  fisher information reveals uv-ir mixing in the strange metal},\ }\href@noop
  {} {\bibfield  {journal} {\bibinfo  {journal} {Physica C}\ }\textbf {\bibinfo
  {volume} {635}},\ \bibinfo {pages} {1354750} (\bibinfo {year}
  {2025})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Mazza}\ \emph {et~al.}(2024)\citenamefont {Mazza},
  \citenamefont {Biswas}, \citenamefont {Yan}, \citenamefont {Prokofiev},
  \citenamefont {Steffens}, \citenamefont {Si}, \citenamefont {Assaad},\ and\
  \citenamefont {Paschen}}]{mazza2024}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {Mazza}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Biswas}},
  \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Yan}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Prokofiev}}, \bibinfo {author}
  {\bibfnamefont {P.}~\bibnamefont {Steffens}}, \bibinfo {author}
  {\bibfnamefont {Q.}~\bibnamefont {Si}}, \bibinfo {author} {\bibfnamefont
  {F.~F.}\ \bibnamefont {Assaad}},\ and\ \bibinfo {author} {\bibfnamefont
  {S.}~\bibnamefont {Paschen}},\ }\href {https://arxiv.org/abs/2403.12779} {}
  (\bibinfo {year} {2024}),\ \Eprint {https://arxiv.org/abs/2403.12779}
  {arXiv:2403.12779 [cond-mat.str-el]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Si}\ \emph {et~al.}(2001)\citenamefont {Si},
  \citenamefont {Rabello}, \citenamefont {Ingersent},\ and\ \citenamefont
  {Smith}}]{Si2001}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont
  {Si}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Rabello}},
  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Ingersent}},\ and\
  \bibinfo {author} {\bibfnamefont {J.~L.}\ \bibnamefont {Smith}},\ }\bibfield
  {title} {\bibinfo {title} {Locally critical quantum phase transitions in
  strongly correlated metals},\ }\href {https://doi.org/10.1038/35101507}
  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
  {volume} {413}},\ \bibinfo {pages} {804} (\bibinfo {year}
  {2001})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Senthil}(2008)}]{senthil2008CriticalFermiSurface}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
  {Senthil}},\ }\bibfield  {title} {\bibinfo {title} {Critical fermi surfaces
  and non-fermi liquid metals},\ }\href
  {https://doi.org/10.1103/PhysRevB.78.035103} {\bibfield  {journal} {\bibinfo
  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {78}},\ \bibinfo
  {pages} {035103} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Sekino}\ and\ \citenamefont
  {Susskind}(2008)}]{sekino2008}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
  {Sekino}}\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Susskind}},\ }\bibfield  {title} {\bibinfo {title} {Fast scramblers},\
  }\href {https://doi.org/10.1088/1126-6708/2008/10/065} {\bibfield  {journal}
  {\bibinfo  {journal} {Journal of High Energy Physics}\ }\textbf {\bibinfo
  {volume} {2008}},\ \bibinfo {pages} {065} (\bibinfo {year}
  {2008})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Hayden}\ and\ \citenamefont
  {Preskill}(2007)}]{hayden2007}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {Hayden}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Preskill}},\ }\bibfield  {title} {\bibinfo {title} {Black holes as mirrors:
  quantum information in random subsystems},\ }\href
  {https://doi.org/10.1088/1126-6708/2007/09/120} {\bibfield  {journal}
  {\bibinfo  {journal} {Journal of High Energy Physics}\ }\textbf {\bibinfo
  {volume} {2007}},\ \bibinfo {pages} {120} (\bibinfo {year}
  {2007})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Bentsen}\ \emph {et~al.}(2019)\citenamefont
  {Bentsen}, \citenamefont {Hashizume}, \citenamefont {Buyskikh}, \citenamefont
  {Davis}, \citenamefont {Daley}, \citenamefont {Gubser},\ and\ \citenamefont
  {Schleier-Smith}}]{bentsen2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Bentsen}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Hashizume}},
  \bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont {Buyskikh}}, \bibinfo
  {author} {\bibfnamefont {E.~J.}\ \bibnamefont {Davis}}, \bibinfo {author}
  {\bibfnamefont {A.~J.}\ \bibnamefont {Daley}}, \bibinfo {author}
  {\bibfnamefont {S.~S.}\ \bibnamefont {Gubser}},\ and\ \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Schleier-Smith}},\ }\bibfield  {title}
  {\bibinfo {title} {Treelike interactions and fast scrambling with cold
  atoms},\ }\href {https://doi.org/10.1103/PhysRevLett.123.130601} {\bibfield
  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
  {volume} {123}},\ \bibinfo {pages} {130601} (\bibinfo {year}
  {2019})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2020)\citenamefont
  {Phillips}, \citenamefont {Yeo},\ and\ \citenamefont {Huang}}]{Phillips2020}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
  {Phillips}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Yeo}},\ and\
  \bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont {Huang}},\ }\bibfield
  {title} {\bibinfo {title} {Exact theory for superconductivity in a doped mott
  insulator},\ }\href {https://doi.org/10.1038/s41567-020-0988-4} {\bibfield
  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
  {16}},\ \bibinfo {pages} {1175} (\bibinfo {year} {2020})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Vafek}\ and\ \citenamefont
  {Vishwanath}(2014)}]{vafekvishwanath2014}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
  {Vafek}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Vishwanath}},\ }\bibfield  {title} {\bibinfo {title} {Dirac fermions in
  solids: From high-tc cuprates and graphene to topological insulators and weyl
  semimetals},\ }\href
  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-031113-133841}
  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
  Physics}\ }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {83} (\bibinfo
  {year} {2014})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Morimoto}\ and\ \citenamefont
  {Nagaosa}(2016)}]{morimoto2016}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
  {Morimoto}}\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
  {Nagaosa}},\ }\bibfield  {title} {\bibinfo {title} {Weyl mott insulator},\
  }\href {https://doi.org/10.1038/srep19853} {\bibfield  {journal} {\bibinfo
  {journal} {Sci. Rep.}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages}
  {19853} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Flores-Calder\'on}\ and\ \citenamefont
  {Hooley}(2025)}]{calderon2025}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
  {Flores-Calder\'on}}\ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
  {Hooley}},\ }\bibfield  {title} {\bibinfo {title} {Weyl-mott point:
  Topological and non-fermi liquid behavior from an isolated green's function
  zero},\ }\href {https://doi.org/10.1103/k4st-77ph} {\bibfield  {journal}
  {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {111}},\
  \bibinfo {pages} {235139} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Georgi}(2007{\natexlab{a}})}]{Georgi2007PRL}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
  {Georgi}},\ }\bibfield  {title} {\bibinfo {title} {Unparticle physics},\
  }\href {https://doi.org/10.1103/PhysRevLett.98.221601} {\bibfield  {journal}
  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {98}},\
  \bibinfo {pages} {221601} (\bibinfo {year} {2007}{\natexlab{a}})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Georgi}(2007{\natexlab{b}})}]{Georgi2007}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
  {Georgi}},\ }\bibfield  {title} {\bibinfo {title} {Another odd thing about
  unparticle physics},\ }\href
  {https://doi.org/https://doi.org/10.1016/j.physletb.2007.05.037} {\bibfield
  {journal} {\bibinfo  {journal} {Physics Letters B}\ }\textbf {\bibinfo
  {volume} {650}},\ \bibinfo {pages} {275} (\bibinfo {year}
  {2007}{\natexlab{b}})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Phillips}(2014)}]{PhillipsLectures2014}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
  {Phillips}},\ }\bibfield  {title} {\bibinfo {title} {Beyond particles:
  Unparticles in strongly correlated electron matter},\ }in\ \href@noop {}
  {\emph {\bibinfo {booktitle} {Quantum Criticality in Condensed Matter}}},\
  \bibinfo {editor} {edited by\ \bibinfo {editor} {\bibfnamefont
  {J.}~\bibnamefont {Jedrzejewski}}}\ (\bibinfo  {publisher} {World Scientific,
  Singapore},\ \bibinfo {year} {2014})\ pp.\ \bibinfo {pages}
  {133--158}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Zaanen}(2019)}]{zaanen2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Zaanen}},\ }\bibfield  {title} {\bibinfo {title} {Planckian dissipation,
  minimal viscosity and the transport in cuprate strange metals},\ }\href
  {https://doi.org/10.21468/SciPostPhys.6.5.061} {\bibfield  {journal}
  {\bibinfo  {journal} {SciPost Phys.}\ }\textbf {\bibinfo {volume} {6}},\
  \bibinfo {pages} {061} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Legros}\ \emph {et~al.}(2019)\citenamefont {Legros},
  \citenamefont {Benhabib}, \citenamefont {Tabis}, \citenamefont
  {Lalibert{\'e}}, \citenamefont {Dion}, \citenamefont {Lizaire}, \citenamefont
  {Vignolle}, \citenamefont {Vignolles}, \citenamefont {Raffy}, \citenamefont
  {Li} \emph {et~al.}}]{legros2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Legros}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Benhabib}},
  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Tabis}}, \bibinfo
  {author} {\bibfnamefont {F.}~\bibnamefont {Lalibert{\'e}}}, \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Dion}}, \bibinfo {author} {\bibfnamefont
  {M.}~\bibnamefont {Lizaire}}, \bibinfo {author} {\bibfnamefont
  {B.}~\bibnamefont {Vignolle}}, \bibinfo {author} {\bibfnamefont
  {D.}~\bibnamefont {Vignolles}}, \bibinfo {author} {\bibfnamefont
  {H.}~\bibnamefont {Raffy}}, \bibinfo {author} {\bibfnamefont
  {Z.}~\bibnamefont {Li}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
  {title} {Universal $ t $-linear resistivity and planckian dissipation in
  overdoped cuprates},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {15}},\ \bibinfo
  {pages} {142} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Hartnoll}\ and\ \citenamefont
  {Mackenzie}(2022)}]{hartnoll2022}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
  {Hartnoll}}\ and\ \bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont
  {Mackenzie}},\ }\bibfield  {title} {\bibinfo {title} {Colloquium: Planckian
  dissipation in metals},\ }\href
  {https://doi.org/10.1103/RevModPhys.94.041002} {\bibfield  {journal}
  {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {94}},\
  \bibinfo {pages} {041002} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {McGreevy}(2023)}]{McGreevy2023}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {McGreevy}},\ }\bibfield  {title} {\bibinfo {title} {Generalized symmetries
  in condensed matter},\ }\href
  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-040721-021029}
  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
  Physics}\ }\textbf {\bibinfo {volume} {14}},\ \bibinfo {pages} {57} (\bibinfo
  {year} {2023})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Luttinger}\ and\ \citenamefont
  {Ward}(1960)}]{luttinger1960ground}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
  {Luttinger}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
  {Ward}},\ }\bibfield  {title} {\bibinfo {title} {Ground-state energy of a
  many-fermion system. ii},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
  {journal} {Physical Review}\ }\textbf {\bibinfo {volume} {118}},\ \bibinfo
  {pages} {1417} (\bibinfo {year} {1960})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Su}\ and\ \citenamefont
  {Martin}(2025)}]{su2025anomalies}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Su}}\ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Martin}},\
  }\href {https://arxiv.org/abs/2405.08093} {} (\bibinfo {year} {2025}),\
  \Eprint {https://arxiv.org/abs/2405.08093} {arXiv:2405.08093
  [cond-mat.str-el]} \BibitemShut {NoStop}%
\bibitem [{\citenamefont {Adler}(1969)}]{adler1969axial}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont
  {Adler}},\ }\bibfield  {title} {\bibinfo {title} {Axial-vector vertex in
  spinor electrodynamics},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
  {journal} {Physical Review}\ }\textbf {\bibinfo {volume} {177}},\ \bibinfo
  {pages} {2426} (\bibinfo {year} {1969})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Bell}\ and\ \citenamefont
  {Jackiw}(1969)}]{bell1969pcac}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~S.}\ \bibnamefont
  {Bell}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Jackiw}},\
  }\bibfield  {title} {\bibinfo {title} {A pcac puzzle: $\pi$0→
  $\gamma$$\gamma$ in the $\sigma$-model},\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {Il Nuovo Cimento A}\ }\textbf {\bibinfo
  {volume} {60}},\ \bibinfo {pages} {47} (\bibinfo {year} {1969})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Casini}\ and\ \citenamefont
  {Mag\'{a}n}(2021)}]{Casini2021Symmetries}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
  {Casini}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
  {Mag\'{a}n}},\ }\bibfield  {title} {\bibinfo {title} {On completeness and
  generalized symmetries in quantum field theory},\ }\href
  {https://doi.org/10.1142/S0217732321300251} {\bibfield  {journal} {\bibinfo
  {journal} {Modern Physics Letters A}\ }\textbf {\bibinfo {volume} {36}},\
  \bibinfo {pages} {2130025} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
\end{thebibliography}

\vspace{0.25cm}
\par\noindent\textbf{Acknowledgements.}
We acknowledge National Supercomputing Mission (NSM) for providing computing resources of ‘PARAM RUDRA’ at Aruna Asaf Ali Marg, near Vasant Kunj, New Delhi, Delhi 110067, which is implemented by C-DAC and supported by the Ministry of Electronics and Information Technology (MeitY) and Department of Science and Technology (DST), Government of India. SL thanks Mayank Shreshtha for designing Fig.1.

\vspace{0.25cm}
\par\noindent\textbf{Funding.}
SL thanks the SERB, Govt. of India for funding through MATRICS grant MTR/2021/000141 and Core Research Grant CRG/2021/000852. AM thanks IISER Kolkata for funding through a JRF and an SRF. AM would also like to acknowledge the SERB-MATRICS grant (Grant No. MTR/2022/000636) from the Science and Engineering Research Board (SERB) for funding.

\vspace{0.25cm}
\par\noindent\textbf{Author Contributions.}
AM, SRH and SL conceived and designed the research. AM performed the calculations and analysis with support from all authors. AM, SRH, AM, NSV, AT and SL wrote the manuscript. All work was supervised by SL.

\vspace{0.25cm}
\par\noindent\textbf{Code Availability.}
The underlying code for this study is not publicly available but may be made available to qualified researchers on reasonable request from the corresponding author.

\vspace{0.25cm}
\par\noindent\textbf{Competing Interest.}
The authors declare no competing interests.

\vspace*{0.5cm}
\par\noindent\textbf{\large Models and Methods}\\
\noindent\textbf{Lattice-embedded Impurity Model}\\
We state the detailed Hamiltonian of the auxiliary model here: $\mathcal{H}_\text{aux} = H_\text{imp} + H_\text{coup} + H_\text{cbath}$,
where the particle-hole symmetric impurity term is
\begin{equation}
H_\text{imp} = - \frac{U}{2} \left( \hat{n}_{d \uparrow} - \hat{n}_{d \downarrow} \right)^2,
\end{equation}
describing on-site Coulomb interactions at the impurity. Here, $c^\dagger_{d\sigma}$ creates an electron with spin $\sigma$ at the impurity site, and $\hat{n}_{d\sigma} = c^\dagger_{d\sigma} c_{d\sigma}$ denotes the corresponding number operator. The impurity couples to four nearest-neighbour bath sites $c_{Z\sigma}$ through both hybridization and Kondo exchange:
\begin{equation}\begin{aligned}
\hspace{-1cm} H_\text{coup} = \frac{J}{2} \hspace{-0.25cm}\sum_{\sigma_1,\sigma_2,Z} 
%\sum_{Z} 
{\bf S}_d \cdot c^\dagger_{Z\sigma_1} {\boldsymbol \tau}_{\sigma_1 \sigma_2} c_{Z\sigma_2} 
- V \sum_{\sigma,Z} \left( c^\dagger_{Z\sigma} c_{d\sigma} + \text{h.c.} \right),    
\end{aligned}\end{equation}
where ${\boldsymbol \tau}$ are the Pauli matrices, and $Z$ indexes the four neighbouring bath sites. The half-filled bath includes nearest neighbour hopping and on-site correlations on the site neighbouring the impurity:
\begin{equation}
H_\text{cbath} = \sum_{\bf k} \epsilon_{\bf k} c^\dagger_{{\bf k},\sigma} c_{{\bf k},\sigma} - \frac{W}{2} \sum_{Z} \left( \hat{n}_{Z\uparrow} - \hat{n}_{Z\downarrow} \right)^2,
\end{equation}
where $\epsilon_{\bf k} = -2t(\cos k_x + \cos k_y)$, and $W$ parametrizes local repulsion in the bath. This frustrates Kondo screening and drives the system towards local-moment formation. A crucial feature of this construction is that the Kondo coupling acquires a momentum structure upon Fourier transforming:
\begin{equation}
J_{{\bf k}, {\bf k}^\prime} = \frac{J}{2} \left[ \cos(k_x - k^\prime_x) + \cos(k_y - k^\prime_y) \right],
\end{equation}
which respects the $C_4$ symmetry of the square lattice.
\vspace{0.25cm}
\par\noindent\textbf{Tiling the impurity model}\\
\noindent
We now provide details on how the effective lattice Hamiltonian is constructed from the underlying impurity model. As described in the main text, the auxiliary model consists of a single impurity embedded in a correlated bath:

\begin{equation}
H(\mathbf{r}_d) = H_{\text{imp}} + H_{\text{cbath}} + H_{\text{imp-cbath}},
\end{equation}
where the impurity Hamiltonian is
\begin{equation}
H_{\text{imp}} = -\frac{U}{2} \left( \hat{n}_{\mathbf{r}_d\uparrow} - \hat{n}_{\mathbf{r}_d\downarrow} \right)^2,
\end{equation}
and the conduction bath is described by
\begin{equation}
\begin{aligned}
H_{\text{cbath}} = & -\frac{1}{\sqrt{\mathcal{Z}}} t \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle \ne \mathbf{r}_d; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
& - \frac{1}{2\mathcal{Z}} W \sum_{\mathbf{z} \in \text{NN}(\mathbf{r}_d)} \left( \hat{n}_{\mathbf{z}\uparrow} - \hat{n}_{\mathbf{z}\downarrow} \right)^2 ,
\end{aligned}
\end{equation}
and the impurity–bath hybridization term is
\begin{equation}
\begin{aligned}
H_{\text{imp-cbath}} = & \frac{J}{\mathcal{Z}} \sum_{\sigma, \sigma'} \sum_{\mathbf{z} \in \text{NN}(\mathbf{r}_d)} \mathbf{S}_{\mathbf{r}_d} \cdot \boldsymbol{\tau}_{\sigma \sigma'} c^\dagger_{\mathbf{z}\sigma} c_{\mathbf{z}\sigma'} \\
& - \frac{V}{\sqrt{\mathcal{Z}}} \sum_{\sigma} \sum_{\mathbf{z} \in \text{NN}(\mathbf{r}_d)} \left( c^\dagger_{\mathbf{r}_d\sigma} c_{\mathbf{z}\sigma} + \text{h.c.} \right),
\end{aligned}
\end{equation}
where $\boldsymbol{\tau} = (\tau_x, \tau_y, \tau_z)$ are Pauli matrices, and ${\bf r}_d$ denotes the impurity position.

\noindent
The tiled lattice Hamiltonian is generated by symmetrically translating this impurity model:
\begin{equation}
\mathcal{H}_{\text{tiled}} = \mathcal{T}[H(\mathbf{r}_d)] = \sum_{\mathbf{r}} T^\dagger(\mathbf{r} - \mathbf{r}_d) H(\mathbf{r}_d) T(\mathbf{r} - \mathbf{r}_d),
\end{equation}
where $T(\mathbf{a})$ are many-body translation operators, defined by $T^\dagger(\mathbf{a}) \mathcal{O}(\{\mathbf{r}_i\}) T(\mathbf{a}) = \mathcal{O}(\{\mathbf{r}_i + \mathbf{a}\})$.
Applying this to each term yields:
\begin{equation}\hspace{-0.5cm}\begin{aligned}
\mathcal{T}[H_{\text{cbath}}] &= -\frac{(N - 2)t}{\sqrt{\mathcal{Z}}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
&\quad - \frac{1}{2} W \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2, \\
\mathcal{T}[H_{\text{imp}}] &= -\frac{U}{2} \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2, \\
\mathcal{T}[H_{\text{imp-cbath}}] &= \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle} \left[ \frac{2J}{\mathcal{Z}} \mathbf{S}_{\mathbf{r}_i} \cdot \mathbf{S}_{\mathbf{r}_j} - \frac{2V}{\sqrt{\mathcal{Z}}} \sum_\sigma \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \right],
\end{aligned}\end{equation}
with local spin operators defined as $\mathbf{S}_{\mathbf{r}} = \sum_{\sigma, \sigma'} c^\dagger_{\mathbf{r}\sigma} \boldsymbol{\tau}_{\sigma \sigma'} c_{\mathbf{r}\sigma'}$.

\noindent
To avoid overcounting of the non-interacting bath terms, we subtract extra copies of of the kinetic energy term. The final reconstructed extended Hubbard model then reads:
\begin{equation}
\begin{aligned}
\mathcal{H}_{\text{tiled}} = & -\frac{1}{\sqrt{\mathcal{Z}}} \tilde{t} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
& + \frac{\tilde{J}}{\mathcal{Z}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle} \mathbf{S}_{\mathbf{r}_i} \cdot \mathbf{S}_{\mathbf{r}_j} - \frac{1}{2} \tilde{U} \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2,
\end{aligned}
\end{equation}
where the effective lattice couplings are given by:
\begin{equation}
\tilde{t} = t + 2V,\quad \tilde{U} = U + W,\quad \tilde{J} = 2J.
\end{equation}
\end{document}

### 2025-12-10 submissions/Supplementary/supplementary.tex
started creating referee response

--- 2025-12-10 submissions/NPJ/Supplementary/supplementary.tex
@@
 %\documentclass{article}
-%\documentclass[
-%%preprint,
-%reprint,onecolumn,
-%superscriptaddress,
-%groupedaddress,
-%%unsortedaddress,
-%%runinaddress,
-%%frontmatterverbose, 
-%%preprint,
-%%preprintnumbers,
-%%nofootinbib,
-%%nobibnotes,
-%%bibnotes,
-%%aps,superscriptaddress,
-%aps,pra,
-%%rmp,
-%%prstab,
-%%prstper,
-%%floatfix,
-%10pt
-%]{revtex4-2}
-\documentclass[%
- reprint,onecolumn,
+\documentclass[
+preprint,
 superscriptaddress,
@@
 %bibnotes,
-aps,superscriptaddress,
-pra,
+%aps,superscriptaddress,
+aps,pra,
 %rmp,
@@
 %floatfix,
+10pt
 ]{revtex4-2}
@@
 %\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue,urlcolor=blue]{hyperref}
-\usepackage{graphicx,braket,color,bm,amsmath,amssymb,braket,placeins}
+\usepackage{graphicx,braket,color,bm,amsmath,amssymb,braket}
 % \graphicspath{{./figures/}}
 \bibliographystyle{apsrev4-2}
-\usepackage{natbib}
+\usepackage[]{natbib}
 
 \usepackage{etoolbox}
-\renewcommand{\thefigure}{S\arabic{figure}}
+
 \makeatletter
-\apptocmd{\thebibliography}{\global\c@NAT@ctr 89\relax}{}{}
+\apptocmd{\thebibliography}{\global\c@NAT@ctr 80\relax}{}{}
 \makeatother
@@
 \author{Abhirup Mukherjee}
-\email{am18ip014@iiserkol.ac.in}
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
+\affiliation{
+ Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
 }
 \author{S. R. Hassan}
-\email{shassan@imsc.res.in}
-\affiliation{The Institute of Mathematical Sciences, HBNI, C.I.T. Campus, Chennai 600 113, India}
+\affiliation{The Institute of Mathematical Sciences, C.I.T. Campus, Chennai 600 113, India}
 \author{Anamitra Mukherjee}
-\email{anamitra@niser.ac.in}
 \affiliation{School of Physical Sciences, National Institute of Science, Education and Research, HBNI, Jatni 752050, India}
 \author{N. S. Vidhyadhiraja}
-\email{raja@jncasr.ac.in}
 \affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
 \author{A. Taraphder}
-\email{arghya@phy.iitkgp.ac.in}
 \affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
 \author{Siddhartha Lal}
-\email{slal@iiserkol.ac.in}
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
+\affiliation{
+ Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
 }
@@
 %obtained using eq.~\ref{tilingPrescriptionFinal} also 
-enjoy a {\it many-body} Bloch's theorem~[55]
+enjoy a {\it many-body} Bloch's theorem~[53]
 %\cite{stoyanova}, 
@@
 where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\).
-With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~[55]:
+With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~[53]:
 %\cite{stoyanova}:
@@
 \subsection{The unitary renormalisation group method}
-In order to obtain the various low-energy phases of our impurity model, we perform a scaling analysis of the associated Hamiltonian using the recently developed unitary renormalisation group (URG) method ~[24,42,43].
+In order to obtain the various low-energy phases of our impurity model, we perform a scaling analysis of the associated Hamiltonian using the recently developed unitary renormalisation group (URG) method ~[19,39,40].
 %\cite{anirbanurg1,anirbanurg2}. 
@@
 As a result of the URG transformations, the Hamiltonian \(H_{(j)}\) at a given RG step \(j\) involves scattering processes between the \(k-\)states that have energies lower than \(D_{(j+1)}\).
-The unitary transformation \(U_{(j)}\) is then defined so as to remove the number fluctuations of the currently most energetic set of states \(D_{(j)}\)~[42,43]:
+The unitary transformation \(U_{(j)}\) is then defined so as to remove the number fluctuations of the currently most energetic set of states \(D_{(j)}\)~[39,40]:
 %\cite{anirbanurg1,anirbanurg2}:
@@
 
-The unitary transformations can be expressed in terms of a generator \(\eta_{(j)}\) that has fermionic algebra~[42,43]:
+The unitary transformations can be expressed in terms of a generator \(\eta_{(j)}\) that has fermionic algebra~[39,40]:
 %\cite{anirbanurg1,anirbanurg2}:
@@
 The unitary operator \(U_{(j)}\) that appears in Eq.~\eqref{unitary} can be cast into the well-known general form \(U = e^\mathcal{S}, \mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger_{(j)} - \eta_{(j)} \right)\) that a unitary operator can take, defined by an anti-Hermitian operator \(\mathcal{S}\).
-The generator \(\eta_{(j)}\) is given by the expression~[42,43]:
+The generator \(\eta_{(j)}\) is given by the expression~[39,40]:
 %\cite{anirbanurg1,anirbanurg2}
@@
 The RG flow continues up to energy \(D^*\), where a fixed point is reached from the vanishing of the RG function.
-Detailed comparisons of the URG with other methods (e.g., the functional RG, spectrum bifurcation RG etc.) can be found in Refs.~[42,43].
+Detailed comparisons of the URG with other methods (e.g., the functional RG, spectrum bifurcation RG etc.) can be found in Refs.~[39,40].
 %\cite{anirbanmott1,anirbanurg1}.
@@
 \section{Tiling formalism: Mapping from the auxiliary model to the tiled lattice model}
-The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using  the tiling procedure outlined in the main text enjoy a {\it many-body} Bloch's theorem~[55],
+The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using  the tiling procedure outlined in the main text enjoy a {\it many-body} Bloch's theorem~[53],
 %\cite{stoyanova}, 
@@
 
-The ${\bf q}_1={\bf q}_2$ component of the Hamiltonian shows the emergence of the exactly solvable Hatsugai-Kohmoto model~[45,46]
+The ${\bf q}_1={\bf q}_2$ component of the Hamiltonian shows the emergence of the exactly solvable Hatsugai-Kohmoto model~[42,43]
 %\cite{Baskaran1991,Hatsugai1992} 
@@
     1, \quad |\mathcal{U}/2| > \epsilon_{\bf q} > -|\mathcal{U}/2|~,\\
-    0, \quad |\mathcal{U}/2| < \epsilon_{\bf q}~.
+    0, \quad |\mathcal{U}/2| > \epsilon_{\bf q}~.
 \end{cases}
@@
 
-\section{Universal scaling of impurity spectral function}
-In the main manuscript, we demonstrate how the PG phase is characterised by a universal scaling exponent \(\beta\) for the self-energy: \(-1/\Sigma^{\prime\prime}(\omega)\sim 1/\Sigma^{\prime\prime}(0) + \omega^{\beta},~\beta=2\).
-We have verified that a similar behaviour holds for the low-frequency regime of the impurity spectral function (see Fig.~\ref{optical}, left panel).
-We observe that $A_{d}(\omega)$ scales as $A_d(0) + \omega^{2}$ for the pseudogap phase, while $1/A_{d}(\omega)\sim 1/A_{d}(0) + \omega^{2}$ for the Fermi liquid (inset of Fig.~\ref{optical}).
-
-\section{Finite-Frequency Optical Response Through the Pseudogap}
-\begin{figure}[!ht]
-    \includegraphics[width=0.45\linewidth]{Ad_fit.pdf}
-	\hfill
-	\includegraphics[width=0.45\textwidth]{sigma_in.pdf}
-    \caption{Left: Impurity spectral function $A_d(\omega)$ in the local Fermi liquid (inset) and pseudogap (main).
-The PG spectral function is fit to a power law (with the $\omega=0$ contribution subtracted, see figure in the main manuscript for the full spectral function).
-The exponent of the power law comes out to be $n\approx 2$ throughout the PG.
-The local FL spectral function (inset) is fit to a lorentzian (by fitting the inverse to a power law).\\ Right: Optical conductivity $\sigma(\omega)$ for excitations of the impurity model, approximated through the product of the carrier density (taken from the density of states $A(\omega)$) and the lifetime $\tau(\omega)$ (obtained from the inverse scattering rate $-1/\Sigma^{\prime\prime}(\omega)$, where $\Sigma^{\prime\prime}$ is the imaginary part of the self-energy).
-The Fermi liquid (blue) shows a sharp Drude peak at $\omega=0$ due to the presence of long-lived quasiparticles.
-The PG (green, red, orange) shows a shifted Drude peak at a non-zero frequency which is reminiscent of the mid-infrared (MIR) peak seen experimentally in the cuprates.
-Inset shows the robustness of the position of the MIR peak through the PG, indicating that it's a universal feature within the PG of our model.}
-	\label{optical}
-\end{figure}
-To further probe the breakdown of coherent transport in the pseudogap (PG) regime, we examine the product of the impurity spectral function $A(\omega)$ and the scattering lifetime $\tau(\omega)$, which approximates the optical conductivity $\sigma(\omega)$ via a Drude-type relation.
-As shown in the right panel panel of Fig.~\ref{optical}, this quantity exhibits a sharp Drude peak at $\omega = 0$ in the Fermi liquid (FL) regime (blue), consistent with long-lived quasiparticles.
-In stark contrast, the PG regime (green, red, orange) shows a pronounced suppression of low-frequency conductivity and the emergence of a finite-frequency peak centered near $\omega/D \sim 0.3{-}0.4$ (where $D$ is the kinetic energy bandwidth).
-
-Strikingly, this peak shifts very little across the PG regime (see inset of right panel), despite a deepening spectral gap and diverging self-energy.
-Its position lies well below the Mott gap ($\sim 2.5D$), suggesting that it represents an emergent mid-infrared (MIR) excitation intrinsic to the Mott metal characterising the PG.
-This feature closely mirrors the experimentally observed MIR peak in high-T$_\text{c}$ cuprates~\cite{Herr1987,Orenstein1987,Uchida1991}, which has been variously attributed to excitations of electrons bound to vacancies~\cite{Thomas1992Optical}, or the dressing of holes by spin excitations~\cite{Dagotto1994RMP}.
-Its robust energy scale and insensitivity to increasing incoherence imply a universality persisting through the PG, likely rooted in short-range entanglement between deconfined doublons and holons excitations of the Mott metal.
-This is further evidence that the PG metal is not simply a degraded Fermi liquid, but a distinct phase whose optical response is driven by emergent degrees of freedom.
-
-% To further probe the breakdown of coherent transport in the pseudogap (PG) regime, we examine the product of the impurity spectral function $A(\omega)$$ and the scattering lifetime $\tau(\omega)$$, which approximates the optical conductivity $\sigma(\omega)$ via a Drude-type relation.
-As shown in Fig.(REF)[X], this quantity exhibits a sharp Drude peak at $\omega = 0$ in the Fermi liquid (FL) regime, consistent with long-lived quasiparticles.
-In stark contrast, the PG regime (dashed curves) shows a pronounced suppression of low-frequency conductivity and the emergence of a finite-frequency peak centered near $\omega/D \sim 0.3{-}0.4$ (where $D$ is the kinetic energy bandwidth).
-Strikingly, this peak shifts very little across the PG regime, despite a deepening spectral gap and diverging self-energy.
-Its position lies well below the Mott gap ($\sim 2.5D$), suggesting that it represents an emergent mid-infrared excitation intrinsic to the PG–Mott crossover.
-This feature closely mirrors the experimentally observed mid-IR peak in high-T$_{\textrm{c}}$ cuprates (CITE), which has been variously attributed to preformed pairs (CITE), bound holon–doublon states (CITE), or emergent collective modes (CITE).
-Its robust energy scale and insensitivity to increasing incoherence imply a hidden order or resonance persisting across the PG regime, likely rooted in short-range entanglement between deconfined doublons and holons.
-Thus, the PG metal is not simply a degraded Fermi liquid, but a distinct dynamical phase whose optical response encodes the fingerprints of emergent quantum degrees of freedom.
-
 \section{Luttinger’s theorem in the presence of Luttinger surfaces.}
 A natural question is whether Luttinger’s theorem continues to hold in our model in the presence of Luttinger surfaces.
-It has been shown that particle-hole symmetric systems satisfy a generalized version of Luttinger’s theorem~[38],
+It has been shown that particle-hole symmetric systems satisfy a generalized version of Luttinger’s theorem~[34],
 %\cite{seki2017topological}, 
 wherein the Luttinger volume $V_L$ is given by the difference between the number of poles and zeros of the single-particle Green’s function enclosed by the FS.
-This statement remains valid even when the self-energy $\Sigma(\mathbf{k}, \omega)$ diverges~[37].
+This statement remains valid even when the self-energy $\Sigma(\mathbf{k}, \omega)$ diverges~[32].
 %\cite{Phillips2013}. 
@@
 This argument extends to the MI, wherein the FS is entirely replaced by a Luttinger surface with zero quasiparticle weight.
+
+\section{Additional Results on the Fermi Liquid \& Pseudogap-Mott metal Phases}
+We present additional figures of the spin (Fig.\ref{spinCorr}) and charge (Fig.\ref{cfnode}) correlations in the impurity model, the impurity spectral function (Fig.\ref{specfunc}), the spin correlations (Fig.\ref{tiledSF}), entanglement entropy (Fig.\ref{tiledEntanglement} (upper panel)) and mutual function (Fig.\ref{tiledEntanglement} (lower panel)) of the tiled model in the pseudogap phase.
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.24\textwidth]{SF-1.pdf}
+	\includegraphics[width=0.24\textwidth]{SF-2.pdf}
+	\includegraphics[width=0.24\textwidth]{SF-3.pdf}
+	\includegraphics[width=0.24\textwidth]{SF-4.pdf}
+	\caption{\(k-\)space distribution of spin-spin correlation \(\chi_s(d,\vec k)\) between the impurity spin and momentum states in the conduction bath, calculated for a $69\times 69$ $k$-space grid.
+The last three figures show how \(k-\)points starting from the antinode progressively exit the Kondo cloud, the node being the last \(k-\)point to decouple from the impurity.}
+	\label{spinCorr}
+\end{figure}
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.24\textwidth]{cfnode-1.pdf}
+	\includegraphics[width=0.24\textwidth]{cfnode-2.pdf}
+	\includegraphics[width=0.24\textwidth]{cfantinode-1.pdf}
+	\includegraphics[width=0.24\textwidth]{cfantinode-2.pdf}
+	\caption{Charge correlation \(\chi_c\) starting from antinode (left) and node (right), at the beginning of the pseudogap phase, calculated for a $49\times 49$ $k$-space grid.
+Strong node-antinode correlations are clearly visible.}
+	\label{cfnode}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.4\linewidth]{Ad_zoomout_77-1500.pdf}
+    \caption{Impurity Spectral function in the FL and PG phases, calculated for a $77\times 77$ $k$-space grid.
+The evolution of the central peak from Kondo resonance to pseudogap is accompanied by dynamical spectral weight transfer to the Hubbard side bands at finite frequencies $\omega\simeq \pm 3$ (in units of the bandwidth).}
+    \label{specfunc}
+\end{figure}
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.24\textwidth]{tiledSF-1.pdf}
+	\includegraphics[width=0.24\textwidth]{tiledSF-2.pdf}
+	\includegraphics[width=0.24\textwidth]{tiledSF-3.pdf}
+	\includegraphics[width=0.24\textwidth]{tiledSF-4.pdf}
+	\caption{Spin-spin correlations \(\chi_s\) for the {\it tiled model}, between the nodal point \(k_N = \left( -\pi/2, -\pi/2\right)\) and an arbitrary \(k-\)point on the Fermi surface, calculated for a $69\times 69$ $k$-space grid.
+In the absence of bath interaction (first panel), the correlations are somewhat uniformly distributed along the Fermi surface, and quite small.
+This describes the Fermi liquid phase of the lattice model.
+As we enter the pseudogap (second panel and beyond), the spin-correlations near the antinode vanish, indicating that they have been removed from the metallic excitations, while the correlations near the nodal point become enhanced because of the increasingly correlated nature of the metal.}
+	\label{tiledSF}
+\end{figure}
+
+\begin{figure}[!h]
+	\includegraphics[width=0.24\textwidth]{tiled_SEE_k-1.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_SEE_k-2.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_SEE_k-3.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_SEE_k-4.pdf}
+
+	\includegraphics[width=0.24\textwidth]{tiled_I2_k_N-1.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_I2_k_N-2.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_I2_k_edge-2.pdf}
+	\includegraphics[width=0.24\textwidth]{tiled_I2_k_edge-3.pdf}
+	\caption{Top panel: Entanglement entropy \(S_\text{EE}({\bf k})\) on the Fermi surface of the tiled model, calculated for a $69\times 69$ $k$-space grid.
+Similar to the correlations, the entanglement in the \(W=0\) model remains uniformly spread out over the Fermi surface.
+As the Fermi surface progressively shrinks, the entanglement gets concentrated to the nodal points.
+Bottom panel: Mutual information \(I_2\) between (i) an arbitrary \(k-\)state and the nodal point (first and second plots), and (ii) an arbitrary \(k-\)state and the edge of the disconnected Fermi surface in the pseudogap (third and fourth plots).
+The ends of the partial Fermi surface appear to be weakly entangled to the rest of the Fermi surface, while the nodal points remain strongly entangled all the way through to the transition.}
+	\label{tiledEntanglement}
+\end{figure}
 
@@
 
-\section{Additional Results on the Fermi Liquid \& Pseudogap-Mott metal Phases}
-We present additional figures of the spin (Fig.\ref{spinCorr}) and charge (Fig.\ref{cfnode}) correlations in the impurity model, the impurity spectral function (Fig.\ref{specfunc}), the spin correlations (Fig.\ref{tiledSF}), entanglement entropy (Fig.\ref{tiledEntanglement} (upper panel)) and mutual function (Fig.\ref{tiledEntanglement} (lower panel)) of the tiled model in the pseudogap phase.
-All figures presented here are for a $77\times 77$ {\bf k}-space Brillouin zone grid.
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.32\textwidth]{SF-500-1.pdf}
-	\includegraphics[width=0.32\textwidth]{SF-500-3.pdf}
-	\includegraphics[width=0.32\textwidth]{SF-500-4.pdf}
-	\caption{\(k-\)space distribution of spin-spin correlation \(\chi_s(d,\vec k)\) between the impurity spin and momentum states in the conduction bath.
-The first shows a mostly uniform distribution of correlations on the Fermi surface for $W=0$.
-The second plot shows the same inside the PG: the antinodal region no longer participates in Kondo screening.
-The last plot represents the nodal metal emerging at the critical point, where the entirety of Kondo screening is carried out by a small neighbourhood about the nodes.}
-	\label{spinCorr}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.32\textwidth]{cfnode-700-1.pdf}
-	\includegraphics[width=0.32\textwidth]{cfnode-700-3.pdf}
-	\includegraphics[width=0.32\textwidth]{doubOcc-700-3.pdf}
-	\caption{The first two panels show charge correlation \(\chi_c\) between the node and an arbitrary $k-$point, in the Fermi liquid (first panel) and the PG (second panel).
-While the charge correlations between the node and antinode are very small in the FL, they grow in the PG.
-This is consistent with the growth in double occupancy at the node and antinode in the PG (third panel).}
-	\label{cfnode}
-\end{figure}
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=0.4\linewidth]{Ad_zoomout_77-1500.pdf}
-    \caption{Impurity Spectral function in the FL and PG phases.
-The evolution of the central peak from Kondo resonance to pseudogap is accompanied by dynamical spectral weight transfer to the Hubbard side bands at finite frequencies $\omega\simeq \pm 3$ (in units of the bandwidth).}
-    \label{specfunc}
-\end{figure}
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.32\textwidth]{tiled-SF-1.pdf}
-	\includegraphics[width=0.32\textwidth]{tiled-SF-3.pdf}
-	\includegraphics[width=0.32\textwidth]{tiled-SF-4.pdf}
-	\caption{Spin-spin correlations \(\chi_s\) for the {\it tiled model}, between the nodal point \(k_N = \left( -\pi/2, -\pi/2\right)\) and an arbitrary \(k-\)point on the Fermi surface.
-In the absence of bath interaction (first panel), the correlations are somewhat uniformly distributed along the Fermi surface, and quite small.
-This describes the Fermi liquid phase of the lattice model.
-As we enter the pseudogap (second panel and beyond), the spin-correlations near the antinode vanish, indicating that they have been removed from the metallic excitations, while the correlations near the nodal point become enhanced because of the increasingly correlated nature of the metal.}
-	\label{tiledSF}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=0.32\textwidth]{tiled_SEE_k_2000-1.pdf}
-	\includegraphics[width=0.32\textwidth]{tiled_SEE_k_2000-2.pdf}
-	\includegraphics[width=0.32\textwidth]{tiled_SEE_k_2000-3.pdf}
-
-	\includegraphics[width=0.32\textwidth]{tiled_I2_k_N_2000-1.pdf}
-	\includegraphics[width=0.32\textwidth]{tiled_I2_k_N_2000-3.pdf}
-	\includegraphics[width=0.32\textwidth]{tiled_I2_k_edge_2000-3.pdf}
-	\caption{Top panel: Entanglement entropy \(S_\text{EE}({\bf k})\) on the Fermi surface of the tiled model.
-Similar to the correlations, the entanglement in the \(W=0\) model (first panel) remains uniformly spread out over the Fermi surface.
-As the Fermi surface progressively shrinks, the entanglement gets concentrated to the nodal points.
-Bottom panel: Mutual information \(I_2\) between (i) an arbitrary \(k-\)state and the nodal point (first and second plots), and (ii) an arbitrary \(k-\)state and the edge of the disconnected Fermi surface in the pseudogap (third plot).
-The ends of the partial Fermi surface appear to be weakly entangled to the rest of the Fermi surface, while the nodal points remain strongly entangled all the way through to the transition.}
-	\label{tiledEntanglement}
-\end{figure}
-
-%\bibliography{tilingProject}
-%\bibliographystyle{unsrt}
-
-\begin{thebibliography}{99}
+\bibliography{tilingProject}
+%\addtocounter{NAT@ctr}{8}
 \bibliographystyle{unsrt}
 
-\bibitem{santanukagome}
-Santanu Pal, Anirban Mukherjee, and Siddhartha Lal.
-\newblock Correlated spin liquids in the quantum kagome antiferromagnet at
-  finite field: a renormalization group analysis.
-\newblock {\em New Journal of Physics}, 21(2):023019, feb 2019.
-
-\bibitem{1dhubjhep1}
-Anirban Mukherjee, Siddhartha Patra, and Siddhartha Lal.
-\newblock Fermionic criticality is shaped by fermi surface topology: a case
-  study of the tomonaga-luttinger liquid.
-\newblock {\em Journal of High Energy Physics}, 2021(4):148, Apr 2021.
-
-\bibitem{anirbanmott1}
-Anirban Mukherjee and Siddhartha Lal.
-\newblock Scaling theory for mott{\textendash}hubbard transitions: I. t = 0
-  phase diagram of the 1/2-filled hubbard model.
-\newblock {\em New Journal of Physics}, 22(6):063007, jun 2020.
-
-\bibitem{siddharthacpi}
-Siddhartha Patra and Siddhartha Lal.
-\newblock Origin of topological order in a cooper-pair insulator.
-\newblock {\em Phys. Rev. B}, 104:144514, Oct 2021.
-
-\bibitem{anirban_kondo}
-Anirban Mukherjee, Abhirup Mukherjee, N.~S. Vidhyadhiraja, A.~Taraphder, and
-  Siddhartha Lal.
-\newblock Unveiling the kondo cloud: Unitary renormalization-group study of the
-  kondo model.
-\newblock {\em Phys. Rev. B}, 105:085119, Feb 2022.
-
-\bibitem{Patra_2023}
-Siddhartha Patra, Anirban Mukherjee, and Siddhartha Lal.
-\newblock Universal entanglement signatures of quantum liquids as a guide to
-  fermionic criticality.
-\newblock {\em New Journal of Physics}, 25(6):063002, jun 2023.
-
-\bibitem{Herr1987}
-S.~L. Herr, K.~Kamar\'as, C.~D. Porter, M.~G. Doss, D.~B. Tanner, D.~A. Bonn,
-  J.~E. Greedan, C.~V. Stager, and T.~Timusk.
-\newblock Optical properties of
-  ${\mathrm{la}}_{1.85}$${\mathrm{sr}}_{0.15}$${\mathrm{cuo}}_{4}$: Evidence
-  for strong electron-phonon and electron-electron interactions.
-\newblock {\em Phys. Rev. B}, 36:733--735, Jul 1987.
-
-\bibitem{Orenstein1987}
-Joseph Orenstein, G.~A. Thomas, D.~H. Rapkine, C.~G. Bethea, B.~F. Levine,
-  R.~J. Cava, E.~A. Rietman, and D.~W. Johnson.
-\newblock Normal-state gap transition in cu-o superconductors.
-\newblock {\em Phys. Rev. B}, 36:729--732, Jul 1987.
-
-\bibitem{Uchida1991}
-S.~Uchida, T.~Ido, H.~Takagi, T.~Arima, Y.~Tokura, and S.~Tajima.
-\newblock Optical spectra of
-  ${\mathrm{la}}_{2\mathrm{\ensuremath{-}}\mathit{x}}$${\mathrm{sr}}_{\mathit{x}}$${\mathrm{cuo}}_{4}$:
-  Effect of carrier doping on the electronic structure of the
-  ${\mathrm{cuo}}_{2}$ plane.
-\newblock {\em Phys. Rev. B}, 43:7942--7954, Apr 1991.
-
-\bibitem{Thomas1992Optical}
-G.~A. Thomas, D.~H. Rapkine, S.~L. Cooper, S-W. Cheong, A.~S. Cooper, L.~F.
-  Schneemeyer, and J.~V. Waszczak.
-\newblock Optical excitations of a few charges in cuprates.
-\newblock {\em Phys. Rev. B}, 45:2474--2479, Feb 1992.
-
-\bibitem{Dagotto1994RMP}
-Elbio Dagotto.
-\newblock Correlated electrons in high-temperature superconductors.
-\newblock {\em Rev. Mod. Phys.}, 66:763--840, Jul 1994.
-
-\bibitem{nozieres1974fermi}
-P~Nozieres.
-\newblock A ``fermi-liquid" description of the kondo problem at low
-  temperatures.
-\newblock {\em Journal of Low Temperature Physics}, 17:31, 1974.
-
-\end{thebibliography}
-
 \end{document}

### 2025-12-10 submissions/TilingReUpload_NaturePhysics/Supplementary/supplementary.tex
started creating referee response

--- 2025-12-10 submissions/NPJ/Supplementary/supplementary.tex
@@
 \usepackage{etoolbox}
-\renewcommand{\thefigure}{S\arabic{figure}}
+
 \makeatletter
-\apptocmd{\thebibliography}{\global\c@NAT@ctr 89\relax}{}{}
+\apptocmd{\thebibliography}{\global\c@NAT@ctr 84\relax}{}{}
 \makeatother
@@
 
-\section{Universal scaling of impurity spectral function}
-In the main manuscript, we demonstrate how the PG phase is characterised by a universal scaling exponent \(\beta\) for the self-energy: \(-1/\Sigma^{\prime\prime}(\omega)\sim 1/\Sigma^{\prime\prime}(0) + \omega^{\beta},~\beta=2\).
-We have verified that a similar behaviour holds for the low-frequency regime of the impurity spectral function (see Fig.~\ref{optical}, left panel).
-We observe that $A_{d}(\omega)$ scales as $A_d(0) + \omega^{2}$ for the pseudogap phase, while $1/A_{d}(\omega)\sim 1/A_{d}(0) + \omega^{2}$ for the Fermi liquid (inset of Fig.~\ref{optical}).
-
 \section{Finite-Frequency Optical Response Through the Pseudogap}
 \begin{figure}[!ht]
-    \includegraphics[width=0.45\linewidth]{Ad_fit.pdf}
-	\hfill
-	\includegraphics[width=0.45\textwidth]{sigma_in.pdf}
-    \caption{Left: Impurity spectral function $A_d(\omega)$ in the local Fermi liquid (inset) and pseudogap (main).
-The PG spectral function is fit to a power law (with the $\omega=0$ contribution subtracted, see figure in the main manuscript for the full spectral function).
-The exponent of the power law comes out to be $n\approx 2$ throughout the PG.
-The local FL spectral function (inset) is fit to a lorentzian (by fitting the inverse to a power law).\\ Right: Optical conductivity $\sigma(\omega)$ for excitations of the impurity model, approximated through the product of the carrier density (taken from the density of states $A(\omega)$) and the lifetime $\tau(\omega)$ (obtained from the inverse scattering rate $-1/\Sigma^{\prime\prime}(\omega)$, where $\Sigma^{\prime\prime}$ is the imaginary part of the self-energy).
+	\includegraphics[width=0.5\textwidth]{sigma_in.pdf}
+	\caption{Optical conductivity $\sigma(\omega)$ for excitations of the impurity model, approximated through the product of the carrier density (taken from the density of states $A(\omega)$) and the lifetime $\tau(\omega)$ (obtained from the inverse scattering rate $-1/\Sigma^{\prime\prime}(\omega)$, where $\Sigma^{\prime\prime}$ is the imaginary part of the self-energy).
 The Fermi liquid (blue) shows a sharp Drude peak at $\omega=0$ due to the presence of long-lived quasiparticles.
@@
 To further probe the breakdown of coherent transport in the pseudogap (PG) regime, we examine the product of the impurity spectral function $A(\omega)$ and the scattering lifetime $\tau(\omega)$, which approximates the optical conductivity $\sigma(\omega)$ via a Drude-type relation.
-As shown in the right panel panel of Fig.~\ref{optical}, this quantity exhibits a sharp Drude peak at $\omega = 0$ in the Fermi liquid (FL) regime (blue), consistent with long-lived quasiparticles.
+As shown in the main panel of Fig.~\ref{optical}, this quantity exhibits a sharp Drude peak at $\omega = 0$ in the Fermi liquid (FL) regime (blue), consistent with long-lived quasiparticles.
 In stark contrast, the PG regime (green, red, orange) shows a pronounced suppression of low-frequency conductivity and the emergence of a finite-frequency peak centered near $\omega/D \sim 0.3{-}0.4$ (where $D$ is the kinetic energy bandwidth).
 
-Strikingly, this peak shifts very little across the PG regime (see inset of right panel), despite a deepening spectral gap and diverging self-energy.
+Strikingly, this peak shifts very little across the PG regime (see inset), despite a deepening spectral gap and diverging self-energy.
 Its position lies well below the Mott gap ($\sim 2.5D$), suggesting that it represents an emergent mid-infrared (MIR) excitation intrinsic to the Mott metal characterising the PG.

### 2025-12-10 submissions/TilingUploadNJP/manuscript_NJP.tex
started creating referee response

\documentclass[%
 reprint,
superscriptaddress,
groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
aps,superscriptaddress,
pra,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}
% ,bm,color,hyperref
\usepackage{graphicx,braket,color,bm,amsmath,amssymb,hyperref}
% \graphicspath{{./figures/}}
\bibliographystyle{apsrev4-2}

\begin{document}

\title{Mott Criticality as the Confinement Transition of a Pseudogap-Mott Metal}

\author{Abhirup Mukherjee}
\email{am18ip014@iiserkol.ac.in}
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
}
\author{S. R. Hassan}
\email{shassan@imsc.res.in}
\affiliation{The Institute of Mathematical Sciences, HBNI, C.I.T. Campus, Chennai 600 113, India}
\author{Anamitra Mukherjee}
\email{anamitra@niser.ac.in}
\affiliation{School of Physical Sciences, National Institute of Science, Education and Research, HBNI, Jatni 752050, India}
\author{N. S. Vidhyadhiraja}
\email{raja@jncasr.ac.in}
\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
\author{A. Taraphder}
\email{arghya@phy.iitkgp.ac.in}
\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
\author{Siddhartha Lal}
\email{slal@iiserkol.ac.in}
\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
}

\date{\today}

\begin{abstract}
The phenomenon of Mott insulation involves the localization of itinerant electrons due to strong local repulsion. Upon doping, a pseudogap (PG) phase emerges - marked by selective gapping of the Fermi surface without conventional symmetry breaking in spin or charge channels. A key challenge is understanding how quasiparticle breakdown in the Fermi liquid gives rise to this enigmatic state, and how it connects to both the Mott insulating and superconducting phases. Here, we develop a renormalization-based construction of strongly correlated lattice models that captures the emergence of the pseudogap phase and its transition to a Mott insulator. Applying a many-body tiling scheme to the fixed-point impurity model uncovers a lattice model with electron interactions and Kondo physics. At half-filling, the interplay between Kondo screening and bath charge fluctuations in the impurity model leads to Fermi liquid breakdown. This reveals a pseudogap phase characterized by a non-Fermi liquid (the Mott metal) residing on nodal arcs, gapped antinodal regions of the Fermi surface, and an anomalous scaling of the electronic scattering rate with frequency. The eventual confinement of holon–doublon excitations of this exotic metal obtains a continuous transition into the Mott insulator. Our results identify the pseudogap as a distinct long-range entangled quantum phase, and offer a new route to Mott criticality beyond the paradigm of local quantum criticality.

\end{abstract}

\maketitle
\section{Introduction}
The Landau quasiparticle paradigm~\cite{landau1959theory} underpins our understanding of metallic behaviour, where the screening of long-ranged repulsive interactions between delocalised electrons leads to well-defined excitations that carry the same quantum numbers as free electrons. This remarkable phenomenon - known as adiabatic continuity -  is captured by excitations described by poles of the single-particle Greens function of the interacting system. But what defines metallicity when quasiparticles are no longer well-defined~\cite{Phillips2013Unparticles}? Can a surface of zeros of the Greens function~\cite{dzyaloshinskii2003some}, rather than poles forming a Fermi surface, define an entirely new kind of metal? Could such an exotic state serve as the precursor to Mott localisation driven purely by repulsion, and without invoking magnetic order~\cite{Mott_1949}? These questions necessitate a radical departure in understanding conduction in correlated electron systems beyond the quasiparticle paradigm~\cite{phillips2022}. \\

\noindent
The anomalous pseudogap (PG) phase, observed in the cuprates, exhibits nodal-antinodal dichotomy with spectral weight concentrated on Fermi arcs around the nodal regions~\cite{loeserKapitulnik1996, Norman1998, Hashimoto2014}. In the PG phase of such Mott systems
~\cite{taillefer2010,FradkinRevModPhys2015,Sato2017,DoironLeyraud2017,Mukhopadhyay2019,Naman2021,Masafumi2025,KyungKotliar2006,MacridinAzevedo2006,sakai2009evolution,werner2009momentum,sakai2010doped,lin2010,gull2010momentum,gull2012,Mirzaei2013,gull2013,anirbanmott2,HilleAndergassen2020,Jiang2022,Scheurer2018,Krien2022,Kitatani2023,Sorella2023,Schafer2021,White1998,Ido2018,ProustTaillefer2019,Ponsioen2019,XuZhang2022}, the single-particle Green’s function develops surfaces of zeros, also known as Luttinger surfaces~\cite{Phillips2013,dzyaloshinskii2003some}, that signals a fundamental obstruction to quasiparticle formation. As interaction strength increases, these zero surfaces proliferate, fragmenting the Fermi surface into nodal arcs~\cite{sakai2009evolution,Phillips2013}, violating the Luttinger sum rule by reconfiguring Fermi volume~\cite{seki2017topological}, and breaking an emergent $\mathbb{Z}_2$ symmetry associated with the conservation of spin currents in Fermi liquids~\cite{Anderson2001,Huang2022}. Unlike conventional instabilities driven by poles, this phenomenon marks a topological breakdown of Fermi liquid theory~\cite{Coleman_2001,Phillips2013Unparticles}. We show that this breakdown arises from a strongly entangled, scale-invariant state of quantum matter, one that serves as the parent metal to the Mott insulator in a half-filled lattice model of strongly correlated electrons. This offers a concrete, controlled framework to understand both the non-quasiparticle character of the pseudogap phase and its continuous evolution into a repulsion-driven insulator, in full alignment with Mott's original vision~\cite{Mott_1949}.\\

\begin{figure*}[tbh]
    \centering
    \includegraphics[width=\linewidth]{Figure1_Nature.pdf}
    \caption{Schematic representation of (a) theoretical framework adopted by us (see main text for explanation of symbols), (b) phases obtained for the extended Hubbard model in two dimensions at $T=0$, and passage between them.}
    \label{schematic}
%    \label{schematic:b}
\end{figure*}

Our approach involves developing a renormalization group (RG)-based impurity-to-lattice framework that reconstructs the low-energy physics of a strongly correlated system from the fixed-point structure of a quantum impurity model (Fig.~\hyperref[schematic]{\ref*{schematic}(a)}). Starting from a dynamical Anderson impurity embedded in a correlated bath, we solve the system using a unitary RG (URG) approach~\cite{anirbanurg1,anirbanurg2}. We then construct a translation-invariant lattice Hamiltonian through a many-body tiling procedure that preserves non-local correlations and inherits momentum-resolved self-energies and renormalized couplings from the impurity solution. The resulting model is an \textit{extended}-Hubbard Hamiltonian on a two-dimensional square lattice at half-filling, with both on-site repulsion and nearest-neighbour spin exchange interactions. These correlations, derived directly from the impurity dynamics, enable tracking the evolution from the FL to the Mott insulator (MI) via an intermediate PG phase.

A central insight of our work is that the PG phase hosts a NFL state governed by Kondo frustration and doublon–holon deconfinement~\cite{keimer2015quantum} (Fig.~\hyperref[schematic]{\ref*{schematic}(b)}). A correlation scale ($W$) in the conduction bath suppresses Kondo screening (with coupling $J$) beyond a critical ratio of $W/J$, triggering the emergence of Luttinger surfaces in the lattice model. This breakdown of quasiparticles begins at the antinodes and progressively engulfs the nodal regions, driving a continuous transformation into the MI. The resulting NFL exhibits a pseudogapped density of states that vanishes as $\omega^{2}$ as $\omega \to 0$, multipartite long-range entanglement, and a universal scattering rate of the form $\sim (a + b\,\omega^2)^{-1}$ that grows as $\omega \to 0$. At the critical endpoint of this phase, the URG flow identifies a singular NFL described by the Hatsugai–Kohmoto (HK) model~\cite{Hatsugai1992,Baskaran1991,Huang2022}, with fully deconfined holon–doublon excitations.

The emergence of Luttinger surfaces alters the anomaly structure associated with the generalized symmetry of the FS~\cite{Altshuler_1998,Heath_2020,lanave2025}. The corresponding topological charge is defined via the Luttinger–Ward functional. This charge is modified by Green’s function zeros, signalling a shift in the underlying anomaly. Within our framework, this reorganization grants topological protection to the RG flows terminating in the PG regime, ensuring the stability of its NFL excitations. These are adiabatically connected to the Hatsugai–Kohmoto model~\cite{Hatsugai1992,Baskaran1991}, reinforcing the interpretation of the PG as a distinct quantum phase. We thus identify the NFL state as a new gapless, long-range entangled phase of correlated matter - the \textit{Mott metal} - whose deconfined holon-doublon excitations are eventually confined across the Mott transition~\cite{Mott_1949}.

While we demonstrate our approach for an extended Hubbard model, the underlying framework is broadly applicable to correlated quantum systems. The impurity-plus-tiling construction accommodates multi-orbital degrees of freedom, frustrated geometries, and nontrivial band topology. By deriving lattice Hamiltonians directly from renormalized local dynamics - without relying on mean-field approximations - this method preserves nonlocal correlations and enhances momentum-space resolution. It thus provides a versatile and controlled route for engineering strongly correlated models, particularly in regimes where PG formation, NFL scaling, and Mott physics intersect.

We now describe the layout of the work. In section \ref{auxurgsection}, we formulate the lattice-embedded auxiliary quantum impurity model and sketch the unitary renormalisation group (URG) method employed to analyse the impurity model. In section \ref{tilingsection}, we formulate the tiling procedure by which to map the impurity Hamiltonian, eigenstates and observables into a lattice model of strongly correlated electrons via the usage of many-body translation operators. Section \ref{kondobreakdownsection} displays the destruction of the Fermi liquid from the breakdown of Kondo screening, leading to a pseudogapped non-Fermi liquid phase of matter. The novel properties of this phase are rigorously established in section \ref{NFLproperties}. In section \ref{exactsolforMottCrit}, we demonstrate that the continuous transition between the pseudogap and Mott insulating phases is described by the exactly solvable Hatsugai-Kohmoto model. We demonstrate in section \ref{pseudogapasnovelphase} the universal organising principle that is responsible for the emergence of the pseudogap non-Fermi liquid phase. This also unveils the pseudogap as the strongly coupled long-range entangled parent metal of the Mott insulator. We conclude in section \ref{conclusions}. Finally, we present appendices containing the derivation of the URG analysis of the impurity model, and the exactly solvable model at the critical point.

\section{Auxiliary Model and URG analysis}\label{auxurgsection}
To capture the interplay between Kondo physics and Mott localization, our approach relies on a two-dimensional auxiliary model consisting of an Anderson impurity embedded in a minimally-correlated bath, which we solve the system using a unitary RG (URG) approach~\cite{anirbanurg1,anirbanurg2}. The impurity model and URG analysis are laid out in this section. In order to make contact with a lattice model, we construct a translation-invariant Hamiltonian from the impurity model through a many-body tiling procedure: this preserves non-local correlations, as well as allows for momentum-resolved self-energies and renormalized couplings generated from the impurity solution. For the impurity model chosen in this work, tiling results in an \textit{extended}-Hubbard Hamiltonian on a two-dimensional square lattice at particle-hole symmetry (half-filling). The interaction terms within the lattice model are a result of analogous correlations present in the auxiliary model. This is laid out next in Section~\ref{tilingsection}.

\subsection{Lattice-embedded Impurity Model}
The auxiliary model consists of a correlated impurity site (with a double occupancy cost $U$) embedded within a correlated conduction bath defined on a square lattice (see Fig.~\hyperref[schematic]{\ref*{schematic}(a)}). The impurity site hybridises with the conduction bath sites adjacent to it through one-particle hybridisation $V$ as well as a spin-exchange interaction $J$ arising from fluctuations in local spin densities of the electrons. The conduction bath has minimal correlations in the form of a local correlation term $W$ on the sites that are adjacent to the impurity.

The Hamiltonian of the auxiliary model studied here is
\begin{equation}
\label{impurityModel}
\mathcal{H}_\text{aux} = H_\text{imp} + H_\text{coup} + H_\text{cbath},
\end{equation}
where the particle-hole symmetric impurity term is
\begin{equation}
H_\text{imp} = - \frac{U}{2} \left( \hat{n}_{d \uparrow} - \hat{n}_{d \downarrow} \right)^2,
\label{localrepulsion}
\end{equation}
describing on-site Coulomb interactions at the impurity. Here, $c^\dagger_{d\sigma}$ creates an electron with spin $\sigma$ at the impurity site, and $\hat{n}_{d\sigma} = c^\dagger_{d\sigma} c_{d\sigma}$ denotes the corresponding number operator.

The impurity couples to four nearest-neighbour bath sites $c_{Z\sigma}$ through both hybridization and Kondo exchange:
\begin{equation}\begin{aligned}
H_\text{coup} = \frac{J}{2} \hspace{-0.25cm}\sum_{\sigma_1,\sigma_2,Z} 
%\sum_{Z} 
{\bf S}_d \cdot c^\dagger_{Z\sigma_1} {\boldsymbol \tau}_{\sigma_1 \sigma_2} c_{Z\sigma_2} 
- V \sum_{\sigma,Z} \left( c^\dagger_{Z\sigma} c_{d\sigma} + \text{h.c.} \right),    
\end{aligned}
\label{impbathcoup}\end{equation}
where ${\boldsymbol \tau}$ are the Pauli matrices, and $Z$ indexes the four neighbouring bath sites. The half-filled bath includes nearest neighbour hopping and on-site correlations on the site neighbouring the impurity:
\begin{equation}
H_\text{cbath} = \sum_{\bf k} \epsilon_{\bf k} c^\dagger_{{\bf k},\sigma} c_{{\bf k},\sigma} - \frac{W}{2} \sum_{Z} \left( \hat{n}_{Z\uparrow} - \hat{n}_{Z\downarrow} \right)^2,
\label{bathke}
\end{equation}
where $\epsilon_{\bf k} = -2t(\cos k_x + \cos k_y)$, and $W$ parametrizes local repulsion in the bath that frustrates Kondo screening and drives the system towards local-moment formation. A crucial feature of this construction is that the Kondo coupling acquires a momentum structure upon Fourier transforming:
\begin{equation}
J_{{\bf k}, {\bf k}^\prime} = \frac{J}{2} \left[ \cos(k_x - k^\prime_x) + \cos(k_y - k^\prime_y) \right],
\end{equation}
which respects the $C_4$ symmetry of the square lattice.

\subsection{The unitary renormalisation group method}
In order to obtain the various low-energy phases of our impurity model, we perform a scaling analysis of the associated Hamiltonian using the recently developed unitary renormalisation group (URG) method ~[19,39,40].
%\cite{anirbanurg1,anirbanurg2}. 
The method has been applied successfully on a wide variety of problems of correlated fermions~\cite{santanukagome,1dhubjhep1,anirbanmott1,siddharthacpi,anirban_kondo,Patra_2023}. The method proceeds by resolving quantum fluctuations in high-energy degrees of freedom, leading to a low-energy Hamiltonian with renormalised couplings and new emergent degrees of freedom. Typically, for a system with Fermi energy \(\epsilon_F\) and bandwidth \(E_N\), the sequence of isoenergetic shells \(\left\{E_{(j)}\right\}, E_{j}\in \left[E_0, E_N\right] \) define the states whose quantum fluctuations we sequentially resolve. The momentum states lying on shells \(E_N\) that are far away from the Fermi surface comprise the UV states, while those on shells near the Fermi surface comprise the IR states.

As a result of the URG transformations, the Hamiltonian \(H_{(j)}\) at a given RG step \(j\) involves scattering processes between the \(k-\)states that have energies lower than \(D_{(j+1)}\). The unitary transformation \(U_{(j)}\) is then defined so as to remove the number fluctuations of the currently most energetic set of states \(D_{(j)}\)~\cite{anirbanurg1,anirbanurg2}:
\begin{eqnarray}
	H_{(j-1)} = U_{(j)} H_{(j)} U^\dagger_{(j)}~, \text{such that} ~\left[H_{(j-1)}, \hat n_{j}\right] =0~.
\end{eqnarray}
The eigenvalue of $\hat{n}_{j}$ has, thus, been rendered an integral of motion (IOM) under the RG transformation.

The unitary transformations can be expressed in terms of a generator \(\eta_{(j)}\) that has fermionic algebra~\cite{anirbanurg1,anirbanurg2}:
\begin{eqnarray}
	\label{unitary}
	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ \quad\left\{ \eta_{(j)},\eta_{(j)}^\dagger \right\} = 1~,
\end{eqnarray}
where \(\left\{\cdot\right\}\) is the anticommutator. The unitary operator \(U_{(j)}\) that appears in Eq.~\eqref{unitary} can be cast into the well-known general form \(U = e^\mathcal{S}, \mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger_{(j)} - \eta_{(j)} \right)\) that a unitary operator can take, defined by an anti-Hermitian operator \(\mathcal{S}\). The generator \(\eta_{(j)}\) is given by the expression\cite{anirbanurg1,anirbanurg2}
\begin{eqnarray}
	\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} \text{Tr}\left(H_{(j)}c_{j}\right)~.
\end{eqnarray}
The operators \(\eta_{(j)},\eta^\dagger_{(j)}\) behave as the many-particle analogues of the single-particle field operators \(c_j,c^\dagger_j\) - they change the occupation number of the single-particle Fock space \(\ket{n_j}\).  The important operator \(\hat \omega_{(j)}\) originates from the quantum fluctuations that exist in the problem because of the non-commutation of the kinetic energy terms and the interaction terms in the Hamiltonian:
\begin{eqnarray}
	\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)}~.
	\label{omega}
\end{eqnarray}
\(H^i_{(j)}\) is the part of \(H_{(j)}\) that commutes with \(\hat n_j\) but does {\it not} commute with at least one \(\hat n_l\) for \(l < j\). The RG flow continues up to energy \(D^*\), where a fixed point is reached from the vanishing of the RG function. 
Detailed comparisons of the URG with other methods (e.g., the functional RG, spectrum bifurcation RG etc.) can be found in Refs.~\cite{anirbanmott1,anirbanurg1}, and implementation on the present problem in  Appendix A.

\section{Tiling formalism}\label{tilingsection}
\subsection{Reconstructing of lattice model from auxiliary model}
To reconstruct a translationally invariant lattice Hamiltonian from the impurity model (with Hamiltonian $\mathcal{H}_\text{aux}$), we define a many-body tiling prescription that embeds the auxiliary impurity system uniformly across the two-dimensional square lattice. Thus, the tiling process systematically derives the full lattice dynamics from the renormalized fixed-point structure of the impurity. As described in Section~\ref{auxurgsection}, the auxiliary model consists of a single impurity embedded in a correlated bath at the location $\mathbf{r}_d$: 
\begin{equation}
H(\mathbf{r}_d) = H_{\text{imp}} + H_{\text{cbath}} + H_{\text{imp-cbath}}~.
\label{auxmodel}
\end{equation}
The form of various terms in eq.\eqref{auxmodel}
have been defined in eqs.\eqref{localrepulsion}, \eqref{impbathcoup} and \eqref{bathke} in Section~\ref{auxurgsection}.
% where the impurity, conduction bath and impurity–bat Hamiltonians are defined as
% \begin{equation}
% \begin{aligned}
% H_{\text{imp}} &= -\frac{U}{2} \left( \hat{n}_{\mathbf{r}_d\uparrow} - \hat{n}_{\mathbf{r}_d\downarrow} \right)^2,\\
% H_{\text{cbath}} &= -\frac{1}{\sqrt{\mathcal{Z}}} t \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle \ne \mathbf{r}_d; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
% &- \frac{1}{2\mathcal{Z}} W \sum_{\mathbf{z} \in \text{NN}(\mathbf{r}_d)} \left( \hat{n}_{\mathbf{z}\uparrow} - \hat{n}_{\mathbf{z}\downarrow} \right)^2,\\
% H_{\text{imp-cbath}} &= \frac{J}{\mathcal{Z}} \sum_{\sigma, \sigma'} \sum_{\mathbf{z} \in \text{NN}(\mathbf{r}_d)} \mathbf{S}_{\mathbf{r}_d} \cdot \boldsymbol{\tau}_{\sigma \sigma'} c^\dagger_{\mathbf{z}\sigma} c_{\mathbf{z}\sigma'} \\
% &- \frac{V}{\sqrt{\mathcal{Z}}} \sum_{\sigma} \sum_{\mathbf{z} \in \text{NN}(\mathbf{r}_d)} \left( c^\dagger_{\mathbf{r}_d\sigma} c_{\mathbf{z}\sigma} + \text{h.c.} \right).
% \end{aligned}
% \end{equation}
% $\boldsymbol{\tau} = (\tau_x, \tau_y, \tau_z)$ are Pauli matrices, and ${\bf r}_d$ denotes the impurity position.

The tiled lattice Hamiltonian is generated by symmetrically translating this impurity model:
\begin{equation}
\mathcal{H}_{\text{tiled}} = \mathcal{T}[H(\mathbf{r}_d)] = \sum_{\mathbf{r}} T^\dagger(\mathbf{r} - \mathbf{r}_d) H(\mathbf{r}_d) T(\mathbf{r} - \mathbf{r}_d),
\end{equation}
where $T(\mathbf{a})$ are many-body translation operators~\cite{stoyanova}:
\begin{equation}
T^\dagger(\mathbf{a}) \mathcal{O}(\{\mathbf{r}_i\}) T(\mathbf{a}) = \mathcal{O}(\{\mathbf{r}_i + \mathbf{a}\}).
\end{equation}
Applying this to each term yields:
\begin{equation}\hspace{-0.5cm}\begin{aligned}
\mathcal{T}[H_{\text{cbath}}] &= -\frac{(N - 2)t}{\sqrt{\mathcal{Z}}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
&- \frac{1}{2} W \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2, \\
\mathcal{T}[H_{\text{imp}}] &= -\frac{U}{2} \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2, \\
\mathcal{T}[H_{\text{imp-cbath}}] &= \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle} \left[ \frac{2J}{\mathcal{Z}} \mathbf{S}_{\mathbf{r}_i} \cdot \mathbf{S}_{\mathbf{r}_j} - \frac{2V}{\sqrt{\mathcal{Z}}} \sum_\sigma \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \right],
\end{aligned}\end{equation}
with local spin operators defined as
\begin{equation}
\mathbf{S}_{\mathbf{r}} = \sum_{\sigma, \sigma'} c^\dagger_{\mathbf{r}\sigma} \boldsymbol{\tau}_{\sigma \sigma'} c_{\mathbf{r}\sigma'}.
\end{equation}

To avoid overcounting of the non-interacting bath terms, we subtract extra copies of the kinetic energy term. The reconstructed extended–Hubbard model then reads:
\begin{equation}
\begin{aligned}
\mathcal{H}_{\text{tiled}} = & -\frac{1}{\sqrt{\mathcal{Z}}} \tilde{t} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
&+ \frac{\tilde{J}}{\mathcal{Z}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle} \mathbf{S}_{\mathbf{r}_i} \cdot \mathbf{S}_{\mathbf{r}_j} - \frac{1}{2} \tilde{U} \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2,
\end{aligned}
\end{equation}
where the effective lattice couplings are given by:
\begin{equation}
\tilde{t} = t + 2V,\quad \tilde{U} = U + W,\quad \tilde{J} = 2J.
\end{equation}
% \end{widetext}

A non-zero chemical potential in the bath and/or the impurity can be included to study the effects of doping. Crucially, the eigenstates of $\mathcal{H}_\text{tiled}$ obey a many-body generalization of Bloch’s theorem~\cite{stoyanova}, which allows for the exact computation of momentum-resolved observables (presented here for a $77\times 77$ {\bf k}-space Brillouin zone grid). We shall demonstrate below that the lattice embedding and tiling procedures provide a controlled route to capture low-energy NFL behavior and Mott criticality directly from a quantum impurity model.

\subsection{Mapping eigenstates using a many-body Bloch's theorem}
As mentioned above, the eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using  the tiling procedure enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, as the tiling procedure restores the translation symmetry of the Hamiltonian. This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) can be used to construct eigenstates of the lattice Hamiltonian. The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.

The state \(\ket{\psi_n\left({\bf r}_d\right)}\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself has been averaged over \(\mathcal{Z}\) zeroth sites. Accordingly, we can express the averaged eigenstate \(\ket{\psi_n\left({\bf r}_d\right)}\) as
\begin{equation}\begin{aligned}
	\ket{\psi_n\left({\bf r}_d\right)} = \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z} \in \text{NN}({\bf r}_d)}\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}~,
\end{aligned}\end{equation}
where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\). With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~[53]:
%\cite{stoyanova}:
\begin{equation}\begin{aligned}\label{eigenstateProposal1}
	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} \\
\end{aligned}\end{equation}
where \(N\) is the total number of lattice sites and \({\bf r}_d\) is summed over all lattice spacings. The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands. The ground state \(s = s_0\) is obtained by setting \({\bf k}\) and \(n\) to 0:
\begin{equation}\begin{aligned}\label{groundstateProposal1}
	\ket{\Psi_\text{gs}} = \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)}
\end{aligned}\end{equation}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig2.pdf}
    \caption{(a) Phase diagram of impurity model at strong coupling in $U$ in terms of competing dimensionless Kondo ($J/t$) and bath correlation ($W/t$) couplings. Colourbar represents the fraction of states on the Fermi surface replaced by zeros of the Greens function (Luttinger surface). A pseudogap phase (shaded region) is observed between the local Fermi liquid (red region) and local moment (blue region) phases (b) $k$-space-resolved spin-spin correlation $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$ in the pseudogap phase of the impurity model. Antinodal regions are observed to decouple from Kondo screening of the impurity. (c) Upon tiling, this leads to a $k$-space-resolved antinodal gap in the electronic density of states of the lattice model, corresponding to Luttinger surfaces of zeros.}
    \label{spinCorr}
%    \label{spinCorr:b}
%    \label{spinCorr:c}
\end{figure*}

\subsection{Mapping the retarded Greens function from auxiliary model to lattice model}
We now show how to relate the one-particle retarded Greens functions of the bulk lattice to that of the auxiliary model. The retarded time-domain lattice \(k-\)space Greens function is defined as
\begin{equation}\begin{aligned}
	\tilde G({\bf K}\sigma; t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c_{{\bf K}\sigma}(t), c^\dagger_{{\bf K}\sigma} \right\} | \Psi_\text{gs}}~.
\end{aligned}\end{equation}
where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(t\): 
\begin{equation}\begin{aligned}\label{heisenberg}
	c_{{\bf K}\sigma}(t) = e^{it H_\text{tiled} }c_{{\bf K}\sigma}e^{-i t H_\text{tiled}}~.
\end{aligned}\end{equation}
We now proceed to simplify one of the terms of the anticommutator (for simplicity of notation):
\begin{equation}\begin{aligned}\label{greensFunction1}
	&\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \\
    &= \frac{1}{N^2}\sum_{\vec r,\vec \Delta}e^{-i{\bf K}_0\cdot\vec\Delta}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
\end{aligned}\end{equation}
Using eq.~\eqref{eigenstateProposal1}, eq.~\eqref{greensFunction1} becomes
\begin{widetext}
	\begin{equation}\begin{aligned}\label{greensfunction2}
		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\vec k_0\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
\end{aligned}\end{equation}
In order to bring this expression closer to the form of an auxiliary model Greens function, we
\begin{itemize}
    \item use the relation $\ket{\psi(\vec r + \Delta)} = T^\dagger(\vec \Delta)\ket{\psi(\vec r)}$, where \(T^\dagger(\vec \Delta)\) translates all lattice sites by the vector \(\vec\Delta\)~,
    \item use the property $T\left(\vec a\right) c({\bf K}) T^\dagger\left(\vec a\right) = e^{-i{\bf K}\cdot\vec a}c({\bf K})$~, and
    \item make the substitution \(\vec \Delta^\prime \to \vec \Delta^\prime + \vec \Delta\)~.
\end{itemize}
This leads to the expression
\begin{equation}\begin{aligned}\label{greensfunction3}
		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~,
\end{aligned}\end{equation}
where the sum over \(s=(\vec k, n)\) has been reduced to a sum over the auxiliary model eigenstate index \(n\) because of the Kronecker delta \(\delta\left(\vec k_0 + {\bf K} - \vec k\right)\). This can be further simplified by splitting the sum over \(\vec\Delta^\prime\) into positive and negative parts and then making the transformation \(\vec r^\prime \to \vec r^\prime + \vec \Delta^\prime\):
\begin{equation}\begin{aligned}
	&\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime-\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}\right]~, \\
																																												   &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\right]~. \\
\end{aligned}\end{equation}
For each pair of \(\vec r^\prime\) and \(\vec\Delta^\prime\), the term within the box brackets has the form of a two-level Hamiltonian between the states \(\ket{\psi_n(\vec r^\prime)}\) and \(\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\), with a tunnelling amplitude \(e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\). The term can therefore be written in the eigenbasis of this Hamiltonian:
\begin{equation}\begin{aligned}
	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &=\frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right],
\end{aligned}\end{equation}
where \(\ket{\chi_n^\pm(\vec r^\prime,\vec\Delta^\prime)} = \frac{1}{\sqrt 2}\left[\ket{\psi_n(\vec r^\prime)} \pm e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime + \vec\Delta^\prime)}\right] \) are the eigenvectors of the tunnelling Hamiltonian with eigenvalues \(\pm 1\) respectively. With this basis transformation, we can rewrite eq.~\eqref{greensfunction3} as
\begin{equation}\begin{aligned}
		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
\end{aligned}\end{equation}
\end{widetext}

In the present work, we consider only the $\vec r^\prime = \vec r,~\vec\Delta^\prime=0$ component. These terms represent those contributions to the total Greens function that arise from excitations that start and end at a specific auxiliary model (at \(\vec r\)), and also evolve dynamically within the same auxiliary model. These terms are therefore exactly equal to the auxiliary model Greens function at position \(\vec r\), and are the most dominant contribution due to the localised nature of the impurity model. Thus, restricting ourselves to just the single auxiliary model contributions gives
\begin{equation}\begin{aligned}
		&\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} =\\
        &\frac{1}{N}\sum_{n, {\vec r}} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
\end{aligned}\end{equation}

We now consider more carefully the transition operator \(\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\) for the 1-particle excitation giving rise to the above Greens function. Within our auxiliary model approach, gapless excitations within the lattice model are represented by gapless excitations of the impurity site, specifically those that screen the impurity site and form the local Fermi liquid. As a result, the uncoordinated \(\mathcal{T}-\)matrix for the lattice model must be replaced by a combined \(\mathcal{T}-\)matrix within the impurity model that captures those gapless excitations that occur in connection with the impurity, and projects out the uncorrelated excitations that take place even when the impurity site is decoupled from the bath.

In order to construct this auxiliary model \(\mathcal{T}-\)matrix, we note that the impurity site can have both spin and charge excitations. Considering both excitations, the modified \(\mathcal{T}-\)matrix that constructs \(k-\)space excitations in correlation with the impurity site are
\begin{equation}\begin{aligned}\label{tmatrix}
	\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\left(\sum_{\sigma^\prime}c^\dagger_{d\sigma} + \text{h.c.}\right) + c_{{\bf K}\sigma}\left(S_d^+ + \text{h.c.}\right)~,
\end{aligned}\end{equation}
leading to the updated expression for the complete Greens function:
\begin{equation}\begin{aligned}
	\tilde G&({\bf K}\sigma; t) \\
    =& \frac{-i\theta(t)}{N}\sum_{n, \vec{r}} \bra{\psi_{0}(\vec r)} \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger \right. \\
    &\left. + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}(\vec r)} ~.
\end{aligned}\end{equation}
\begin{figure}[!th]
    \centering
    \includegraphics[width=0.49\linewidth]{tiled-SF-3.pdf}
    \includegraphics[width=0.49\linewidth]{tiled_I2_k_N_2000-3.pdf}
    \caption{Left: Spin correlations \(\chi_s\) for the {\it tiled model}, between the nodal point \(k_N = \left( -\pi/2, -\pi/2\right)\) and an arbitrary \(k-\)point on the Fermi surface. In the PG, the spin-correlations near the antinode vanish, indicating that they have been removed from the metallic excitations, while the correlations near the nodal point become enhanced because of the increasingly correlated nature of the metal. Right: Mutual information \(I_2\) between an arbitrary \(k-\)state and the nodal point. The nodal points remain strongly entangled with each other all the way through the PG.}
    \label{tiledEntanglement}
\end{figure}

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{fig2.5.png}
    \caption{Initiation of the decoupling of $J_{{\bf k}, {\bf k'}}$ (positive, negative and zeros shown in red, blue and white respectively), with ${\bf k}$ (black circle) at low-energies for ${\bf k}$ corresponding to the node (a), antinode (b) and a point mid-way between them (c) on the top right arm of the FS respectively with tuning $W/J$. As dictated by the symmetry of $J_{{\bf k}, {\bf k'}}$, the decoupling for a given ${\bf k}$ proceeds via the appearance of zeros (white patches) of $J_{{\bf k}, {\bf k'}}$ for ${\bf k'}$ initially on the nodal regions of adjacent arms, and progresses gradually towards the antinodes. The decoupling ends with the onset of the pseudogap.}
    \label{unravelling}
%    \label{unravelling:b}
%    \label{unravelling:c}
\end{figure*}
\section{Pseudogap Formation via Kondo Breakdown}\label{kondobreakdownsection}

\subsection{RG Phase Diagram}
A detailed picture of the PG in the impurity model is obtained from a momentum-resolved breakdown of Kondo screening in the strong-coupling regime $U \gg t$ phase of $H_\text{aux}$. A unitary renormalisation group (URG) scaling analysis~\cite{anirbanurg1} obtains a flow equation of the Kondo coupling \(J^{(j)}_{{\bf k}_1, {\bf k}_2}\) (see Appendix A for details)
\begin{equation}\begin{aligned}\label{KondoRGequation}
	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}~,
\end{aligned}\end{equation}
where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, the sum is over all occupied momentum states \({\bf q}\) of the energy shell \(\varepsilon_j\), and  \({\bf \bar q} = {\bf q} + {\boldsymbol \pi}\) is the particle-hole transformed state associated with ${\bf q}$. The bath interaction coupling $W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}$ is found to be marginal under these transformations. While we present a detailed numerical evaluation of the RG equation for $J_{{\bf k}_1, {\bf k}_2}$ (eq.\eqref{KondoRGequation}) below, it is clear that the frustration of Kondo screening due to charge fluctuations (for attractive bath interactions $W<0$) leads to the Mott transition~\cite{Mukherjee_2023}.

A detailed numerical computation of the URG equation in eq.~\eqref{KondoRGequation} leads to the phase diagram shown in Fig.~\hyperref[spinCorr]{\ref*{spinCorr}(a)}. Upon tuning the ratio of the bath and Kondo interactions ($W/J$) from zero to negative values, the following phases emerge in the impurity model from the competition between $J$ and $W$ in eq.~\eqref{KondoRGequation}: (i) for $W/J<(W/J)_{\text{PG}}$, an LFL phase (red region), where the entire FS participates in Kondo screening, (ii) for $\frac{W}{J} \in [(\frac{W}{J})_{\text{PG}}, (\frac{W}{J})_c]$ (shaded region), a local PG phase where disconnected parts of the FS around the node participate in Kondo screening, and (iii) a local moment phase for $\frac{W}{J} > (\frac{W}{J})_c$ (blue region), where the impurity remains unscreened at low-energies. These can be visualised from spin correlations, $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$~, as shown in Fig.~\hyperref[spinCorr]{\ref*{spinCorr}(b)} for the PG. The values $(W/J)_{\text{PG}}$ and $(W/J)_c$ are therefore the entry into and exit from the PG phase.

Mapping onto the lattice model via tiling, we observe that RG-induced nodal–antinodal dichotomy in $J_{{\bf k}, {\bf k}^\prime}$ in the impurity model is the microscopic origin of the PG in the lattice model: the extinction of Kondo coherence translates into spectral zeros in the lattice Green’s function (i.e., Luttinger surfaces) at antinodal momenta (Fig.~\hyperref[spinCorr]{\ref*{spinCorr}(c)}). This establishes that the $T=0$ Mott transition of the 2D \textit{extended}-Hubbard model proceeds from FL to MI through an intervening PG phase. In Fig.~\ref{tiledEntanglement}, similar insights obtain from the spin-correlation $\chi_s({\bf k},k_N) = \braket{{\bf S}_{\bf k}\cdot{\bf S}_{k_N}}$ in $k-$space (where $k_N$ is the nodal momentum) and mutual information $I_2({\bf k}:k_N)$ between two momentum states: the PG displays Fermi arcs in the nodal regions along with vanishing correlation and entanglement in the antinodal regions.

\subsection{Unravelling of Kondo Screening}
The ${\bf k}$-space anisotropy of Kondo breakdown can be visualized in terms of zeros of $J_{{\bf k}_N, {\bf k}}$, involving spin-flip scattering between the node ${\bf k}_N = (\pi/2, \pi/2)$  and a general wavevector ${\bf k}$.
For any $W/J$, the $\mathcal{C}_{4}$ lattice symmetry dictates that $J_{{\bf k}_N, {\bf k}}$ vanishes if ${\bf k}$ belongs to any of the antinodes or adjacent nodes. Tuning $W/J$ towards $(W/J)_{\text{PG}}$ leads to an unravelling of the Kondo screening: $J_{{\bf k}_N, {\bf k}}$ for ${\bf k}$ close to the adjacent nodes turns RG-irrelevant first, and a patch of zeros subsequently appears in $J_{{\bf k}_N, {\bf k}}$ around this point (Fig.~\hyperref[unravelling]{\ref*{unravelling}(a)}). Tuning $W/J$ further extends the patch of zeros towards the antinodes (Fig.~\hyperref[unravelling]{\ref*{unravelling}(b)} and \hyperref[unravelling]{\ref*{unravelling}(c)}). Kondo screening thus unravels by a systematic decoupling of all $J_{{\bf k}_1, {\bf k}_2}$ that connect adjacent quadrants of the Brillouin zone.

Precisely at $W/J=(W/J)_{\text{PG}}$, the antinode joins this connected region of zeros in $J_{{\bf k}_1, {\bf k}_2}$, marking the decoupling of the antinodes from all other points in the neighbourhood of the FS. This is an interaction-driven Lifshitz transition of the FS, and marks the entry into a PG phase possessing Fermi arcs~\cite{WuFerrero2018}. Importantly, it coincides with an emergent two-channel Kondo (2CK) impurity model, where each channel corresponds to a pair of Fermi arcs on opposite faces of the conduction bath FS. The 2CK nature of the PG is guaranteed by the symmetry of $J_{{\bf k},{\bf k'}}$: 
\begin{equation}
\begin{aligned}
J_{{\bf k},{\bf k'}}= -J_{{\bf k}+{\bf Q},{\bf k'}}=-J_{{\bf k},{\bf k'}+{\bf Q}}, \quad {\bf Q} = (\pi,\pi).
\end{aligned}
\end{equation}
The PG expands by shrinking these disconnected Fermi arcs towards the respective nodes, leading to nodal metals whose disappearance heralds the Mott transition.

\subsection{Momentum-resolved Dynamical Spectral Weight Transfer}
Passage through the PG phase is accompanied by a highly structured transfer of spectral weight across the FS. Strong charge fluctuations develop between the nodal and antinodal regions of the FS in the PG regime of the impurity model (Fig.~\hyperref[chargeCorr]{\ref*{chargeCorr}(a)}), as captured by the correlator:
\begin{equation}
\chi_c({\bf k}_1, {\bf k}2) = \left\langle
c^{\dagger}_{{\bf k}1 \uparrow} c^{\dagger}_{{\bf k}1 \downarrow} c_{{\bf k}2 \downarrow} c_{{\bf k}_2 \uparrow} + \text{h.c.}\right\rangle~.
\end{equation}
These fluctuations dynamically redistribute low-energy spectral weight from the antinodes to higher energies, leading to selective gap formation. Accordingly, the Luttinger surfaces of the PG~\cite{dzyaloshinskii2003some} coincides with the appearance of poles of the lattice model self-energy $\Sigma ({\bf k},\omega=0)$ near the antinodes; these poles approach the nodes on tuning towards the Mott transition (Fig.~\hyperref[chargeCorr]{\ref*{chargeCorr}(b)}). This mirrors the coalescing of finite-frequency poles of the self-energy poles towards zero frequency in the underlying impurity model~(Fig.~\hyperref[chargeCorr]{\ref*{chargeCorr}(c)}). 
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig3.pdf}
    \caption{(a) Enhanced charge correlations $\chi_c({\bf k}_1, {\bf k}_2) = \braket{c^\dagger_{{\bf k}_1\uparrow}c^\dagger_{{\bf k}_1\downarrow}c_{{\bf k}_2\downarrow}c_{{\bf k}_2\uparrow} + \text{h.c.}}$ between the nodal and antinodal regions, signalling Kondo breakdown in the pseudogap phase of the impurity model. (b) In turn, the breakdown leads to the gapping of the antinodal regions in the lattice model, seen from the appearance of poles in the imaginary part of the self-energy. (c) The imaginary part of the impurity self-energy $\Sigma^{\prime\prime}(\omega >0)$ possesses a pole at non-zero $\omega$ in the PG that moves towards $\omega=0$ as the Mott transition is approached.}
    \label{chargeCorr}
\end{figure*}

\section{Non-Fermi liquid excitations within the Pseudogap}\label{NFLproperties}
\subsection{Pseudogapped spectral function and singular self-energy}
In the PG regime, the nature of gapless Fermi arcs changes dramatically. We have already argued that the low-energy dynamics of these gapless Fermi arcs are governed by an underlying two-channel Kondo (2CK) impurity model~\cite{Tsvelick_weigmann_mchannel_1985, emery_kivelson}. This is consistent with the rapid fall of the impurity quasiparticle residue $Z_\text{imp}$ (Fig.~\hyperref[channelDecoupling]{\ref*{channelDecoupling}(a)}) from finite values in the FL phase to vanishingly small values just before the onset of the PG. Inset  shows the simultaneous emergence of increasingly uncompensated local magnetic moments upon traversing the PG phase. The accompanying impurity spectral function of the gapless arcs show a pseudogapped behaviour for $\omega\simeq 0$, with a rapid fall in the spectral weight at $\omega=0$ upon traversing the PG~(Fig.~\hyperref[channelDecoupling]{\ref*{channelDecoupling}(c)}). The collapse of the Kondo resonance into a pseudogapped spectral function is accompanied by the redistribution of spectral weight~\cite{dzyaloshinskii2003some} in the impurity spectral function (Fig.~\hyperref[channelDecoupling]{\ref*{channelDecoupling}(b)}) from $\omega\sim 0$ to the Hubbard sidebands at finite frequencies $\omega\simeq \pm 3$ (in units of the bandwidth).

Concomitant with this is the emergence of a zero-frequency peak in the imaginary part of the self-energy of the NFL in the PG phase(Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(a)}),
\begin{equation}
\begin{aligned}
-1/\Sigma^{\prime\prime}(\omega)\sim 1/\Sigma^{\prime\prime}(0) + \omega^{\beta}~.
\end{aligned}
\end{equation}
Remarkably, we find that the exponent $\beta=2$ characterises the NFL for the entire PG phase (see Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(b)}), including the critical end-point. This is in stark contrast with the $\Sigma''(\omega)\sim \omega^{2}$ for the FL (Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(b)}). A similar analysis reveals the power-law scaling for the low-frequency behaviour of the impurity spectral function in Fig.\ref{ImpSpecFuncFits}. We observe that $A_{d}(\omega)\sim A_d(0) + \omega^{2}$ for the pseudogap phase, while $1/A_{d}(\omega)\sim 1/A_{d}(0) + \omega^{2}$
for the Fermi liquid (inset of Fig.~\ref{ImpSpecFuncFits}).
\subsection{Finite-Frequency Scattering Rate and Optical Response Through the Pseudogap}
All $\Sigma''(\omega)$ for the NFL are observed to lie above the Mott-Ioffe-Regel (MIR) bound~\cite{GunnarssonRMP2003,Hussey2004} (dashed blue line in Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(a)}), while those for the FL lie below. The MIR bound is the maximum expected scattering rate in metals when the mean free path approaches the lattice spacing: 
\begin{equation}
\begin{aligned}
-2\Sigma^{\prime\prime}_\text{MIR} = 1/\tau_\text{MIR}~, ~\tau_\text{MIR} = l_\text{min}/v_{F}~,
\end{aligned}
\end{equation}
where $l_\text{min}$ is the minimum mean free path in metals (equal to one lattice spacing) and $\tau_\text{MIR}$ is the associated lifetime of quasiparticles close to the FS (with Fermi velocity $v_F$). 
% The optical conductivity $\sigma (\omega)$ of the NFL thus undergoes a suppression as $\omega \to 0$, together with a shift of the Drude peak to finite $\omega$~\cite{Hussey2004,pustogow2021}. 
The height of the zero-frequency peak rises by almost 4 orders of magnitude from the start of the PG till its end at the Mott transition point (Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(c)}); the dramatic growth of the peak height very near the Mott critical point coincides with the coalescing of the finite-frequency poles of the self-energy into a single pole at zero-frequency, signalling the singular nodal NFL present at the Mott quantum critical point.

To further probe the breakdown of coherent transport in the pseudogap (PG) regime, we examine the product of the impurity spectral function $A(\omega)$ and the scattering lifetime $\tau(\omega)$, which approximates the optical conductivity $\sigma(\omega)$ via a Drude-type relation. As shown in the main panel of Fig.~\ref{optical}, this quantity exhibits a sharp Drude peak at $\omega = 0$ in the Fermi liquid (FL) regime (blue), consistent with long-lived quasiparticles. In stark contrast, the PG regime (green, red, orange) shows a pronounced suppression of low-frequency conductivity and the emergence of a finite-frequency peak centered near $\omega/D \sim 0.3{-}0.4$ (where $D$ is the kinetic energy bandwidth).

\begin{figure*}[!ht]
    \centering
    \includegraphics[width=\textwidth]{fig4.pdf}
    \caption{(a) Suppression of quasiparticle residue ($Z_\text{imp}$) as the impurity model is tuned towards the Mott transition. An initial drastic fall in $Z_\text{imp}$ is observed for $W/J \lesssim (W/J)_\text{PG}$ from $0.3$ to around $0.05$, signalling the destruction of the FL with unravelling of Kondo screening. A steady decrease in $Z_{imp}$ is observed in passage through the PG, and is vanishingly small close to the Mott transition due to a divergent self-energy. Inset shows the growth of unscreened impurity magnetic moment in the pseudogap phase, signalling the breakdown of Kondo screening. (b) Impurity Spectral function in the FL and PG phases. The evolution of the central peak from Kondo resonance to pseudogap is accompanied by dynamical spectral weight transfer to the Hubbard side bands at finite frequencies $\omega\simeq \pm 3$ (in units of the bandwidth). (c) Zoom-in of the central (Kondo) resonance of the impurity spectral function. While undisturbed in the Fermi liquid phase, it splits into a pseudogap in the PG phase, with its height diminishing rapidly as the Mott transition is approached.
    }
    \label{channelDecoupling}
\end{figure*}
Strikingly, this peak shifts very little across the PG regime (see inset), despite a deepening spectral gap and diverging self-energy. Its position lies well below the Mott gap ($\sim 2.5D$), suggesting that it represents an emergent mid-infrared (MIR) excitation intrinsic to the Mott metal characterising the PG. This feature closely mirrors the experimentally observed MIR peak in high-T$_\text{c}$ cuprates~\cite{Herr1987,Orenstein1987,Uchida1991}, which has been variously attributed to excitations of electrons bound to vacancies~\cite{Thomas1992Optical}, or the dressing of holes by spin excitations~\cite{Dagotto1994RMP}. Here, its robust energy scale and insensitivity to increasing incoherence imply a universality persisting through the PG, likely rooted in short-range entanglement between deconfined doublons and holons excitations of the Mott metal. This is further evidence that the PG metal is not simply a degraded Fermi liquid, but a distinct phase whose optical response is driven by emergent degrees of freedom.

\subsection{Non-local correlations in the pseudogap}
In Fig.~\hyperref[longranged]{\ref*{longranged}(a)} and \hyperref[longranged]{\ref*{longranged}(b)}, the spin-flip correlations and mutual information between the impurity spin and conduction bath sites respectively are observed to undergo a crossover within the PG, from a short-ranged behaviour at its onset, to a long-ranged behaviour as the Mott transition approaches. The entanglement is also observed to be multipartite in nature: in Fig.~\hyperref[longranged]{\ref*{longranged}(c)}, the quantum Fisher information (QFI)~\cite{Hauke2016} computed for the ground state wavefunction using an operator corresponding to the sum of local spin-flip exchange processes shows a jump at the onset of the PG. Further, the FL is observed to possess bi-partite entanglement while the NFL of the PG phase displays pentapartite entanglement~\cite{balut2025,mazza2024}.

These striking results imply that the Mott transition observed by us lies beyond the local quantum criticality scenario~\cite{Si2001}. Instead,  we observe the PG phase to be a novel state of strongly interacting quantum matter emergent from the breakdown of local Kondo screening. This state is described by a quantum critical Fermi surface~\cite{senthil2008CriticalFermiSurface} with NFL Fermi arcs that display increasingly critical behaviour, i.e., dynamics described by non-local quantum fluctuations, and excitations that become truly long-ranged close to the transition. It is tempting to conjecture that the long-range entangled critical state captured in Fig.~\hyperref[longranged]{\ref*{longranged}(b)} reflects the existence of a highly efficient scrambler~\cite{sekino2008,hayden2007,bentsen2019}, i.e., a state in which entanglement spreads among its constituents at the fastest rate permissible by quantum mechanics.

\section{Exactly solvable nodal Non-Fermi liquid at Mott Criticality}\label{exactsolforMottCrit}
Very close to the transition, the excitations of the nodal NFL correspond to those of a Hatsugai-Kohmoto model~\cite{Baskaran1991,Hatsugai1992}. This insight is obtained from a perturbation-theoretic treatment of the RG fixed point Hamiltonian of the impurity model for $W/J\lesssim (W/J)_{\text{PG}}$, by considering the effects of a small fixed point Kondo scattering probability \(J^*\) in the backdrop of a larger bath interaction parameter \(|W|\). This yields the HK model~\cite{Baskaran1991,Hatsugai1992} as the singular part of the effective Hamiltonian arising from forward scattering processes (see Appendix B for details of the derivation).

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig5.pdf}
    \caption{(a) Imaginary part of impurity self-energy $\Sigma^{\prime\prime}(\omega)$ as a function of frequency $\omega$ for Fermi liquid (FL, $|W/J| < 1.79$) and pseudogapped phases (NFL, $|W/J| \geq 1.79$). $\Sigma''(\omega)$ falls to zero as $\omega\to 0$ for the FL, while it attains a peak in the pseudogap. All $\Sigma''(\omega)$ for the NFL are observed to lie above the Mott-Ioffe-Regel (MIR) bound (dashed blue line), while those for the FL lie below. (b) Scaling of $\Sigma^{\prime\prime}(\omega)$ with frequency for Fermi liquid and pseudogapped phases. The FL self-energy fits to $\Sigma^{\prime\prime} \sim \omega^{\alpha}$ with $\alpha\approx 2$, vanishing as $\omega\to 0$, while the NFL self-energy grows as $\Sigma^{\prime\prime} \approx a - \omega^{\beta}$ for small $\omega$, with $\beta\approx 2$. Remarkably, the NFL exponent remains mostly unchanged through the entirety of the PG phase. (c) Variation of the zero-frequency imaginary self-energy $-\Sigma''(\omega=0)$ with $\omega$ in the FL and pseudogap phases (entry into the PG is marked by the vertical dashed line). The inset shows the same but in linear scale, in order to display the dramatic rise (by almost 30 times) on entering the PG.}
    \label{selfEnergy}
\end{figure*}

\begin{figure}[!hbtp]
    \centering
    \hspace*{-1cm}
    \includegraphics[width=0.9\linewidth]{Ad_fit.pdf}
    \caption{Impurity spectral function $A_d(\omega)$ in the local Fermi liquid (inset) and pseudogap (main). The PG spectral function is fit to a power law (with the $\omega=0$ contribution subtracted, see Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(c)} for the full spectral function). The exponent of the power law comes out to be $n\approx 2$ throughout the PG. The local FL spectral function (inset) is fit to a lorentzian (by fitting the inverse to a power law).
    }
    \label{ImpSpecFuncFits}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=0.48\textwidth]{sigma_in.pdf}
	\caption{Optical conductivity $\sigma(\omega)$ for excitations of the impurity model, approximated through the product of the carrier density (taken from the density of states $A(\omega)$) and the lifetime $\tau(\omega)$ (obtained from the inverse scattering rate $-1/\Sigma^{\prime\prime}(\omega)$, where $\Sigma^{\prime\prime}$ is the imaginary part of the self-energy). The Fermi liquid (blue) shows a sharp Drude peak at $\omega=0$ due to the presence of long-lived quasiparticles. The PG (green, red, orange) shows a shifted Drude peak at a non-zero frequency which is reminiscent of the mid-infrared (MIR) peak seen experimentally in the cuprates~\cite{Herr1987,Orenstein1987,Uchida1991}. Inset shows the robustness of the position of the MIR peak through the PG, indicating it as a universal feature of the Mott metal.}
	\label{optical}
\end{figure}
The second-order renormalised Hamiltonian is
\begin{equation}\begin{aligned}\label{HKModel}
    H_\text{eff} =& \sum_{{\bf q}, \sigma}\epsilon_{\bf q} r_{{\bf q},\sigma} + \mathcal{U}\sum_{{\bf q}, \sigma}r_{{\bf q} \sigma}r_{{\bf q} \bar\sigma} + \mathcal{U}\sum_{{\bf q}_1 \neq {\bf q}_2, \sigma}\left[r_{{\bf q}_1 \sigma}r_{{\bf q}_2 \bar\sigma} \right.\\
    &\left.+ \phi^\dagger_{{\bf q}_1,\bar\sigma}\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2, \sigma}\phi_{{\bf q}_2, \bar\sigma}\right]~.
\end{aligned}\end{equation}
where $\epsilon_{\bf q} = \text{sign}\left(\varepsilon_{{\bf N}_1 + {\bf q}}\right)\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W}$ and $\mathcal{U} = \frac{{J^*}^2}{4W}$. The number operator \(n_{{\bf q} \sigma} = \phi^\dagger_{{\bf q}, \sigma} \phi_{{\bf q}, \sigma}\) pertains to emergent fermionic relative modes $\phi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} - c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)$ that are shifted by an excitation momentum \({\bf q}\) away from the nodal point \({\bf N}_1 = \left(\pi/2, \pi/2\right)\) and its 
partner \({\bf N}_1 + {\bf Q}_1 = \left(-\pi/2, -\pi/2\right)\). 
The ${\bf q}_1={\bf q}_2$ component of the Hamiltonian shows the emergence of the exactly solvable Hatsugai-Kohmoto model~\cite{Baskaran1991,Hatsugai1992} 
at the critical point. The correlation term $\mathcal{U}\sum_{{\bf q}, \sigma}r_{{\bf q} \sigma}r_{{\bf q} \bar\sigma}$ leads to a transfer of spectral weight across the Fermi surface and separates the available states into three classes:
\begin{equation}\begin{aligned}
\braket{n_{\bf q}} = \begin{cases}
    2, \quad \epsilon_{\bf q} < -|\mathcal{U}/2|~,\\
    1, \quad |\mathcal{U}/2| > \epsilon_{\bf q} > -|\mathcal{U}/2|~,\\
    0, \quad |\mathcal{U}/2| < \epsilon_{\bf q}~.
\end{cases}
\end{aligned}\end{equation}
In constrast to a Fermi liquid, there is a highly degenerate single-occupied region in the middle, and this gives rise to non-Fermi liquid excitations.

We now discuss the effects of the ${\bf q}_1 \neq {\bf q}_2$ component. The first term partially lifts the degeneracy of the central singly-occupied region and allows only zero magnetisation configurations. The second term creates gapped excitations involving the regions of zero and double occupancy; these represent subdominant pairing fluctuations of the nodal non-Fermi liquid.

Consequently, the resulting NFL metal of the lattice model involves long-lived excitations of multiple \({\bf k}\)-states, and manifest in the form of a divergent one-particle self-energy at the non-interacting FS~\cite{Phillips2020}:
$\Sigma_{{\bf q}}(\omega) = -\mathcal{U}^2/4(\omega - \epsilon_{\bf q})$~, such that $\Sigma_{\epsilon_{\bf q}=0}(\omega \to 0)  \to \infty$. This zero-frequency self-energy pole presages the transition into a Mott insulating phase, where it marks a hard gap in the spectral function for charge excitations. This is consistent with our findings for the lattice (Fig.~\hyperref[chargeCorr]{\ref*{chargeCorr}(c)}) and impurity self-energies~(Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(c)}). The nodal Mott metal thus comprises of a Greens function zero at the Fermi energy together with an anistropic massless Dirac dispersion, leading to a non-zero Chern number~\cite{vafekvishwanath2014,morimoto2016,calderon2025}. This topological index survives into the Mott insulator.

For small but non-zero values of \(\omega - \epsilon_{\bf k}\), we obtain a quasiparticle residue that vanishes with $\omega$, \(Z_\text{imp} \sim \omega^2/\mathcal{U}^2 \). The scattering rate of this singular NFL possesses a sharp peak at the FS (\(\omega=\epsilon_{\bf k_{\mathrm{F}}}\)): 
\begin{equation}\begin{aligned}
\Gamma \sim \mathcal{U}^2\delta(\omega - \epsilon_{\bf k})~,
\end{aligned}\end{equation}
consistent with the sharply peaked Lorentzian $\Sigma''_{{\bf k}}(\omega)\sim \omega^{-2}$ captured in Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(a)}. This quantum critical NFL metal is an example of a strongly coupled scale-invariant form of quantum matter. The exact solution for eq.\eqref{HKModel} reveals the presence of low-energy excitations comprised of holons and doublons~\cite{Hatsugai1992}. These features point to the nodal NFL as a long-ranged and multipartite entangled, strongly interacting scale-invariant state of quantum matter 
~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} that are completely disconnected from the quasiparticles of the FL. Following the arguments laid out in~\cite{phillips2022}, at finite temperatures, such a scale-invariant highly entangled non-Fermi liquid is likely associated with Planckian dissipation (i.e., $\Sigma'' (T)\sim k_{B}T$) and a resistivity that varies linearly with temperature ($\rho\sim T$)~\cite{zaanen2019,legros2019,hartnoll2022}. This sits well with the possibility that this state is also a highly efficient scrambler~\cite{sekino2008,hayden2007,bentsen2019}. Additionally, as mentioned above, we observe that the nodal metal possesses pairing fluctuations that can become dominant upon doping~\cite{Phillips2020}.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig6.pdf}
    \caption{(a) Spin correlation $\braket{{\bf S}_d \cdot {\bf S}_r}$  and (b) mutual information $I_{2}(d,r)$  between the impurity spin and conduction bath local spin density as a function of the distance {\bf r} between them, normalised against the value at $r=1$. Both decay very quickly in the FL phase (blue), but show long-ranged behaviour in the NFL phase (green and red), extending to the edges of the system at the critical point (red). (c) Evolution of the Quantum Fisher Information $F_Q$ for a nearest-neighbour spin-flip operator $\mathcal{O} = \sum_{i \in \text{odd}}(S_i^+S_{i+1}^- + \text{h.c.})$ through the first Lifshitz transition and the pseudogap. The vertical dashed line marks the onset of the PG. To the left of it, the QFI in the Fermi liquid phase shows at most bipartite entanglement ($F_Q < 2$ (below blue dashed line)), while the PG shows the presence of multipartite entanglement upto 5 parties ($F_Q > 4$ (red dashed line)).}
    \label{longranged}
\end{figure*}

\section{Pseudogap as a strongly coupled phase of quantum matter}\label{pseudogapasnovelphase}
We now unveil an organising principle that leads to the remarkable properties observed above for the strongly interacting NFL of the PG phase. The existence of a sharp connected FS at $T=0$ can be understood as the existence of a topologically protected manifold of gapless chiral excitations in ${\bf k}$-space at the FS~\cite{Heath_2020}. The FS is characterised by a topological index corresponding to an anomaly in the quantum many-body theory for electrons, and can be understood as a generalised symmetry of such a system~\cite{lanave2025,McGreevy2023}. A theorem by Luttinger and Ward~\cite{luttinger1960ground} shows that a count of the physical charge (known as Luttinger's volume) is identical to the topological index (a so-called homotopy charge known as Luttinger's count) even in the presence of electronic interactions that do not disturb the FS. We will now argue that the emergence of antinodal Luttinger surfaces involve a disconnection of the FS (into Fermi arcs) and that, by following La Nave et al.~\cite{lanave2025}, the accompanying change in its topological properties leads to the existence of gapless NFL excitations that are non-local in nature.

The antinodal Luttinger surfaces arise from the splitting of double poles of the single-particle Greens function on the FS into poles lying on opposite complex half-planes, together with zeros that are pinned at the FS. These changes in the analytic structure of the single-particle Greens function have important consequences. First, the emergent zeros break a $\mathbb{Z}_{2}$ symmetry of the FS~\cite{Anderson2001,Huang2022,lanave2025}. This symmetry is guaranteed within FL theory because the presence of quasiparticles vanishingly close to the FS allows the interchange of spin and charge degrees of freedom, promoting the separate $SU(2)$ symmetries of spin and charge to the larger symmetry of $O(4) = SU(2) \times SU(2) \times \mathbb{Z}_2$~\cite{Anderson2001}. The insertion of zeros of the Greens function at the Fermi surface in the PG, and the associated splitting of the Greens function, breaks this $\mathbb{Z}_{2}$ symmetry by placing the pole for the spin excitation in one half of the complex plane while placing that for the charge excitation in the other half~\cite{su2025anomalies,Huang2022}.

Second, they signal a divergent electronic self-energy as a function of the wavevector ${\bf k}$, render ill-behaved the Luttinger-Ward functional of the interacting electronic problem, and violate the generalised symmetry encoded within it. The changes in the pole structure change the Luttinger count topological invariant, while the zeros give rise to an additional topological contribution (linked to the Adler-Bell-Jackiw-type chiral anomaly)~\cite{adler1969axial,bell1969pcac,Altshuler_1998,calderon2025}. As a consequence of the half-filled particle-hole symmetric nature of the system at hand, Luttinger's volume is preserved upon taking into account topological contributions from both the Luttinger count {\it and} the zeros~\cite{seki2017topological}. Importantly, La Nave et al.~\cite{lanave2025} argue, following recent developments in understanding generalised symmetries~\cite{Casini2021Symmetries}, that the additional anomaly arising from the Luttinger surfaces guarantees the existence of gapless NFL excitations that are non-local in nature.

Thus, the drastic change in nature of the real-space excitations - from locally well-defined Landau quasiparticles of the FL to the increasingly nonlocal excitations of the NFL Fermi arcs in the PG phase - appears to be dictated by a topological principle and, therefore, robust under renormalisation. This signals the NFL Fermi arcs of the PG as an emergent phase of strongly interacting quantum matter - which we dub the {\it Mott metal} - that is the parent metal of the MI. The same topological principle connects the nonlocal unparticle-like gapless excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} of the scale-invariant nodal NFL of the HK model observed precisely at the Mott critical point to those of the rest of the PG phase, e.g., a universal scaling of $\Sigma''_{{\bf k}}(\omega)\sim (a + \omega^{2})^{-1}$ (Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(b)}) and local density of states $A_{d}(\omega) \sim \omega^{2}$ (Fig.~\hyperref[ImpSpecFuncFits]{\ref*{ImpSpecFuncFits}}) of the NFL throughout the PG phase, such that the value of $\Sigma''_{{\bf k}}(\omega=0)$ value continues to grow upon violating the MIR bound (Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(c)}).

\section{Conclusions}\label{conclusions}
Our analysis reveals that the Mott transition proceeds via a continuous evolution through a PG regime characterized by a singular NFL metal - the Mott metal - with deconfined holon–doublon excitations confined to nodal Fermi arcs, and a scaling of it's spectral features with universal power-law exponents. As the system approaches criticality, this metallic phase exhibits increasingly non-local correlations and a divergent self-energy, signalling the breakdown of Landau quasiparticles, formation of local moments and the onset of long-range quantum entanglement. Anchored in two-channel Kondo dynamics at intermediate scales and governed by Hatsugai–Kohmoto physics near the critical endpoint, the Mott metal provides a unified framework for understanding anomalous metallicity in strongly correlated systems. It's fate under finite doping presents a compelling direction for future investigation.

\bibliography{tilingProject}

\section*{Acknowledgments}
We acknowledge National Supercomputing Mission (NSM) for providing computing resources of ‘PARAM RUDRA’ at Aruna Asaf Ali Marg, near Vasant Kunj, Vasant Kunj, New Delhi, Delhi 110067, which is implemented by C-DAC and supported by the Ministry of Electronics and Information Technology (MeitY) and Department of Science and Technology (DST), Government of India. SL thanks the SERB, Govt. of India for funding through MATRICS grant MTR/2021/000141 and Core Research Grant CRG/2021/000852. AM thanks IISER Kolkata for funding through a JRF and an SRF. A.M. would also like to acknowledge the SERB-MATRICS grant (Grant No. MTR/2022/000636) from the Science and Engineering Research Board (SERB) for funding. S.L. thanks Mayank Shreshtha for designing Fig.1, and Deepshikha Jaiswal-Nagar for comments on the manuscript.

\section{Code and Data availability}
The codes created during this research are available from the corresponding author upon reasonable request.

\clearpage
\begin{widetext}
\appendix

\section{Derivation of unitary RG equations for the lattice-embedded impurity model}
Following Refs.~\cite{anirbanmott1,anirbanurg1}, at any given step \(j\) of the RG procedure, we decouple the states \(\left\{ {\bf q} \right\} \) on the isoenergetic surface of energy \(\varepsilon_j\). The diagonal Hamiltonian \(H_D\) for this step consists of all terms that do not change the occupancy of the states \(\left\{{\bf q}\right\}\):
\begin{equation}\begin{aligned}
	H_D^{(j)} = \varepsilon_j\sum_{q,\sigma}\tau_{q,\sigma} + \frac{1}{2}\sum_{{\bf q}}J_{{\bf q}, {\bf q}}S_d^z\left(\hat n_{{\bf q}, \uparrow} - \hat n_{{\bf q}, \downarrow}\right) - \frac{1}{2}\sum_{{\bf q}}W_{\bf q}\left(\hat n_{{\bf q}, \uparrow} - \hat n_{{\bf q}, \downarrow}\right)^2~,
\end{aligned}\end{equation}
where \(\tau = \hat n - 1/2\) and \(W_{{\bf q}}\) is a shorthand for \(W_{{\bf q},{\bf q},{\bf q},{\bf q}}\). The three terms, respectively, are the kinetic energy of the momentum states on the isoenergetic shell that we are decoupling, the spin-correlation energy between the impurity spin and the spins formed by these momentum states and, finally, the local correlation energy associated with these states arising from the \(W\) term. The off-diagonal part of the Hamiltonian on the other hand leads to scattering in the states \(\left\{ {\bf q} \right\} \).

The renormalisation of the Hamiltonian is constructed from the general expression~~\cite{anirbanmott1,anirbanurg1}
\begin{equation}\begin{aligned}
	\Delta H^{(j)} = H_X \frac{1}{\omega- H_D} H_X~.
\end{aligned}\end{equation}

\subsection{Renormalisation of the bath correlation term {\it W}}
The bath correlation term \(W\) can undergo renormalisation only via scattering processes arising from itself. Irrespective of whether the state \({\bf q}\) being decoupled is in a particle or hole configuration in the initial many-body state, the propagator \(G = 1/(\omega - H_D)\) of the intermediate excited state is uniform, and equal to 
\begin{equation}\begin{aligned}\label{propagatorW}
	G_W = 1/\left(\omega - |\varepsilon_j|/2 + W_{\bf q}/2)\right)~,
\end{aligned}\end{equation}
where \(W_{\bf q}\) is the same whether \({\bf q}\) is above or below the Fermi surface. The \(|\varepsilon_j|/2\) in \(H_D\) arises from the excited nature of the state after the initial scattering process.

\subsubsection{Scattering arising purely from spin-preserving processes}
%\subsubsection*{Scattering arising purely from spin-preserving processes}
One possible set of processes gives
\begin{equation}\begin{aligned}
	T_{P1}^\dagger G_W T_{P3} = -\sum_\sigma\sum_{{\bf k}_1, {\bf k}_2, {\bf k}_3, {\bf k}_4} c^\dagger_{{\bf k}_1,\sigma} c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma}    \sum_{\bf q \in \text{PS}} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4} G_W W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}}~.
\end{aligned}\end{equation}

The second such contribution is obtained by flipping the sequence of scattering processes:
\begin{equation}\begin{aligned}
	T_{P3} G_W T_{P1}^\dagger = \sum_\sigma\sum_{{\bf k}_1, {\bf k}_2, {\bf k}_3, {\bf k}_4} c^\dagger_{{\bf k}_1,\sigma} c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} \sum_{\bf q \in \text{HS}} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4} G_W W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}}~.
\end{aligned}\end{equation}
The product of couplings \(W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4} G_W W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}}\) is the same irrespective of whether \({\bf q}\) belongs to the particle or hole sector. The two contributions therefore cancel each other.

\subsubsection{Scattering arising from spin-flip processes}
%\subsubsection*{Scattering arising from spin-flip processes}
We now come to the processes that involve spin-flips. The first class of processes is
\begin{equation}\begin{aligned}
	T_{F1}^\dagger G_W T_{F4} &= -\sum_{1,2,3,4}\sum_\sigma c^\dagger_{{\bf k}_1\sigma} c_{{\bf k}_2\sigma} c^\dagger_{{\bf k}_3\bar\sigma} c_{{\bf k}_4\bar \sigma} \sum_{\bf q \in \text{PS}} W_{{\bf q}, {\bf k}_2, {\bf k}_4, {\bf k}_4} G_W W_{{\bf k}_1, {\bf q}, {\bf q}, {\bf q}}~,\\
	T_{F4} G_W T_{F1}^\dagger &= \sum_{1,2,3,4}\sum_\sigma c^\dagger_{{\bf k}_1\sigma} c_{{\bf k}_2\sigma} c^\dagger_{{\bf k}_3\bar\sigma} c_{{\bf k}_4\bar \sigma} \sum_{\bf q \in \text{HS}} W_{{\bf q}, {\bf k}_2, {\bf k}_4, {\bf k}_4} G_W W_{{\bf k}_1, {\bf q}, {\bf q}, {\bf q}}~.
\end{aligned}\end{equation}
By the same arguments as in the previous subsection, these terms cancel each other out.

The other two terms also cancel out for the same reason:
\begin{equation}\begin{aligned}
	T_{F2} G_W T_{F2} &= \sum_{1,2,3,4}\sum_\sigma c^\dagger_{{\bf k}_1\sigma} c_{{\bf k}_2\sigma} c^\dagger_{{\bf k}_3\bar\sigma} c_{{\bf k}_4\bar \sigma} \sum_{\bf q \in \text{PS}} W_{{\bf q},{\bf \bar q},{\bf k}_3,{\bf k}_4} G_W W_{{\bf \bar q},{\bf q},{\bf k}_1,{\bf k}_2}~,\\
	T_{F3} G_W T_{F3} &= -\sum_{1,2,3,4}\sum_\sigma c^\dagger_{{\bf k}_1\sigma} c_{{\bf k}_2\sigma} c^\dagger_{{\bf k}_3\bar\sigma} c_{{\bf k}_4\bar \sigma} \sum_{\bf q \in \text{PS}} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf \bar q}} G_W W_{{\bf \bar q},{\bf k}_4,{\bf k}_1,{\bf q}}~,
\end{aligned}\end{equation}

\subsubsection{Scattering involving both spin-flip and spin-preserving processes}
%\subsubsection*{Scattering involving both spin-flip and spin-preserving processes}
These processes involve the combination of terms like \(T_{P1}\) with \(T_{F4}\), and \(T_{P2}\) with \(T_{F1}\). These again cancel each other out for the same reasons as outline above.

\subsubsection{Net renormalisation for the bath correlation term}
Since all the contributions cancel out in pairs, the bath correlation term \(W\) is {\it marginal}.

\subsection{Renormalisation of the Kondo scattering term {\it J}}
We focus on the renormalisation of the spin-flip part of the Kondo interaction. For these processes, the intermediate many-body state always involves the impurity spin being anti-correlated with the conduction electron spin, such that the propagator for that state is \(G_J = 1/\left(\omega - |\varepsilon_j|/2 + J_{\bf q}/4 + W_{\bf q}/2)\right) \).

\subsubsection{Impurity-mediated spin-flip scattering purely through Kondo-like processes}
%\subsubsection*{Impurity-mediated spin-flip scattering purely through Kondo-like processes}
The following processes arising from the Kondo term renormalise the spin-flip interaction:
\begin{equation}\begin{aligned}\label{kondoRenorm1}
	T^\dagger_{KT1} G_J \left(T_{KZ1} + T_{KZ1}^\dagger\right) &= -\frac{1}{8}\sum_{{\bf k}_1, {\bf k}_1}~ S_d^+ c^\dagger_{{\bf k}_1 \downarrow}c_{{\bf k}_2 \uparrow}\sum_{{\bf q} \in \text{PS}}\left[J_{{\bf q}, {\bf k}_2} J_{{\bf k}_1,{\bf q}} + J_{{\bf \bar q}, {\bf k}_1} J_{{\bf k}_2,{\bf \bar q}} \right]G_J~.
\end{aligned}\end{equation}
An identical contribution is obtained by switching the sequence of processes:
\begin{equation}\begin{aligned}\label{kondoRenorm2}
	 \left(T_{KZ1} + T_{KZ1}^\dagger\right) G_J T^\dagger_{KT1} &= -\frac{1}{8}\sum_{{\bf k}_1, {\bf k}_1}~ S_d^+ c^\dagger_{{\bf k}_1 \downarrow}c_{{\bf k}_2 \uparrow}\sum_{{\bf q} \in \text{PS}}\left[J_{{\bf \bar q}, {\bf k}_2} J_{{\bf k}_1,{\bf \bar q}} + J_{{\bf q}, {\bf k}_1} J_{{\bf k}_2,{\bf q}} \right]G_J~.
\end{aligned}\end{equation}

\subsubsection{Scattering processes involving interplay between the Kondo interaction and conduction bath interaction}
\begin{equation}\begin{aligned}\label{t7t6}
	T_{KT1}^\dagger G_J \left(T_{F4} + T_{F4}^\dagger\right) &= \frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2,{\bf q}} J_{{\bf k}_2, {\bf q}}S_d^+ \left(c^\dagger_{{\bf q}\downarrow}c_{{\bf k}_2\uparrow}  G_J W_{{\bf q}, {\bf q}, {\bf k}_1, {\bf q}} n_{q \uparrow} c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf q} \downarrow} + c^\dagger_{{\bf k}_2\downarrow}c_{{\bf q}\uparrow}  G_J W_{{\bf \bar q}, {\bf \bar q}, {\bf q}, {\bf k}_1} n_{\bar q \downarrow} c^\dagger_{{\bf q} \uparrow} c_{{\bf k}_1 \uparrow}\right) ~.
\end{aligned}\end{equation}
For either of the two choices of the functional form of \(W\), it is easy to show that \(W_{{\bf q}, {\bf q}, {\bf k}_1, {\bf q}} = W_{{\bf \bar q}, {\bf \bar q}, {\bf q}, {\bf k}_1}\).
\begin{equation}\begin{aligned}\label{KT1F4}
	T_{KT1}^\dagger G_J \left(T_{F4} + T_{F4}^\dagger\right) &= \frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2,{\bf q}} J_{{\bf k}_2, {\bf q}} W_{{\bf q}, {\bf q}, {\bf k}_1, {\bf q}} G_J S_d^+ \left[-c^\dagger_{{\bf k}_1 \downarrow}c_{{\bf k}_2\uparrow} n_{{\bf q}\downarrow} n_{q \uparrow} + c^\dagger_{{\bf k}_2\downarrow} c_{{\bf k}_1 \uparrow} (1 - n_{{\bf q}\uparrow}) n_{\bar q \downarrow}\right] ~.
\end{aligned}\end{equation}

Another contribution is obtained by switching the sequence of the scattering processes:
\begin{equation}\begin{aligned}\label{F4KT1}
	\left(T_{F4} + T_{F4}^\dagger\right) G_J T_{KT1}^\dagger &= \frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2,{\bf q}} \left(c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf k}_2\uparrow} n_{\bar q \uparrow} (1 - n_{{\bf q} \downarrow}) - c^\dagger_{{\bf k}_2\downarrow}c_{{\bf k}_1 \uparrow}n_{q \downarrow} n_{{\bf q} \uparrow}\right) W_{{\bf q}, {\bf q}, {\bf k}_1, {\bf q}} G_J J_{{\bf k}_2, {\bf q}}S_d^+
\end{aligned}\end{equation}
The two contributions (eqs.~\ref{KT1F4} and \ref{F4KT1}) arising from \(T_{KT1}\) cancel each other.

We now consider the other spin-exchange process \(T_{KT2}^\dagger\). One such contribution is
\begin{equation}\begin{aligned}\label{kondoRenorm3}
	T_{KT2}^\dagger G_J T_{F3} &= -\frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2} S_d^+ c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf k}_2 \uparrow}\sum_{{\bf q} \in \text{PS}}\left(J_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} + J_{{\bf \bar q}, {\bf q}} W_{{\bf q}, {\bf k}_2, {\bf k}_1, {\bf \bar q}}\right)G_J~.
\end{aligned}\end{equation}
An identical contribution is obtained from the reversed term:
\begin{equation}\begin{aligned}\label{kondoRenorm4}
	T_{F3}G_J T_{KT2}^\dagger  &= -\frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2} S_d^+ c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf k}_2 \uparrow}\sum_{{\bf q} \in \text{PS}}\left(J_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} + J_{{\bf \bar q}, {\bf q}} W_{{\bf q}, {\bf k}_2, {\bf k}_1, {\bf \bar q}}\right)G_J~.
\end{aligned}\end{equation}

\subsubsection{Net renormalisation to the Kondo interaction}
%\subsubsection*{Net renormalisation to the Kondo interaction}
Combining the results, the total renormalisation in the momentum-resolved Kondo coupling \(J^{(j)}\) at the \(j^\text{th}\) step amounts to
\begin{equation}\begin{aligned}
	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}
\end{aligned}
\label{rgeq2}\end{equation}
A representation of the RG phase diagram in the $-W/t$ vs. $J/t$ plane of couplings has been provided in Fig.\hyperref[spinCorr]{\ref*{spinCorr}(a)} from detailed numerical computations of eq.\eqref{rgeq2}. We also provide a schematic representation of RG flows to various fixed point theories in the $J$ vs. $W$ plane of couplings in Fig.\ref{rgflows}. This schematic figure shows the existence of three distinct phases (Fermi liquid metal, Mott Insulator, and Pseudogap-Mott metal) described by distinct fixed point theories of the RG flows. The Fermi liquid metal and Mott Insulator phases are distinguished from the Pseudogap-Mott metal by separatrices of the RG flows.
\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{RGflows.pdf}
    \caption{Renormalisation group (RG) flow diagram of the lattice model as obtained from a unitary RG analysis of the lattice-embedded impurity model. For $|W/J| < |W/J|_\text{PG}$, the flows lead to a Fermi liquid phase, while for $|W/J| < |W/J|_\text{c}$, they lead to a Mott insulator. For values in between, the system flows to a Mott metal phase that has a pseudogap in the density of states.}
    \label{rgflows}
\end{figure}

\section{Theory for the nodal non-Fermi liquid as an effective Hatsugai-Kohmoto model}
As the bath interaction \(W\) is tuned through the L-PG phase, the nodal region is the last to decouple from the impurity. This allows us to write down a simpler Kondo model near the transition, where only the nodal region is hybridising with the impurity spin through Kondo interactions. This is done by retaining only those scattering processes \({\bf k}_1 \to {\bf k}_2\) that originate from and end at \(k-\)points within a small neighborhood of width \(|{\bf q}|\) around the four nodal points: \({\bf k}_1, {\bf k}_2 \in {\bf N} + {\bf q}, |{\bf q}| \ll \pi\), where \({\bf N}\) can be any one of the four nodal points \({\bf N}_{1} = \left(\pi/2, \pi/2\right), {\bf N}_{2} = \left(-\pi/2, \pi/2\right)\) and \({\bf N}_1 + {\bf Q}_1\) and \({\bf N}_{2} + {\bf Q}_2\), where \({\bf Q}_1 = \left(-\pi,-\pi \right)\) and \({\bf Q}_2 = \left( \pi, -\pi \right) \) are the two nesting vectors. We assume that the window of \({\bf q}\) is small enough so that the fixed point Kondo coupling values \(J^*({\bf q}_1, {\bf q}_2)\) for the scattering processes involving \({\bf q}_1\) and \({\bf q}_2\) can be replaced by an average value \(J^*\).

With these considerations, the simplified low-energy model near the transition describing the Kondo scattering processes can be written as
\begin{equation}\begin{aligned}
	\tilde H_\text{imp-cbath} = J^*\frac{1}{2}\sum_{l=1,2}\sum_{{\bf q}_1, {\bf q}_2}\sum_{\alpha,\beta}{\bf S}_d\cdot{\boldsymbol \sigma}_{\alpha\beta}\left(c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} + c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta}  - c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} \right.\\
    \left.- c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta}\right)~.
\end{aligned}\end{equation}
The label \(l\) can take values 1 or 2, allowing us to consider both the decoupled channels in the PG (associated with \({\bf N}_1\) and \({\bf N}_2\)). It also labels the nesting vectors \({\bf Q}_l\) associated with the two sets. \(\alpha\) and \(\beta\) indicate spin indices, and \({\bf q}_1\) and \({\bf q}_2\) represent incoming and outgoing momenta in the scattering processes.

Because of the decoupling of the channel \(l=1\) and \(l=2\), we consider only the \(l=1\) channel for the rest of the calculations in this section. In order to simplify the Hamiltonian, we define new fermionic operators
\begin{equation}\begin{aligned}
	\psi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} + c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~, ~\phi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} - c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~,
\end{aligned}\end{equation}
The operator satisfy fermionic anticommutation relations. For convenience, we define new number operators for the sum and relative degrees of freedom:
\begin{equation}\begin{aligned}
	s_{{\bf q},\sigma} = {\psi}^\dagger_{{\bf q}} {\psi}_{{\bf q}},~ r_{{\bf q},\sigma} = {\phi}^\dagger_{{\bf q}} {\phi}_{{\bf q}}~.
\end{aligned}\end{equation}
We then have the following useful relation between the corresponding number operators \(n = c^\dagger c\):
\begin{equation}\begin{aligned}\label{numberOperatorRelation}
	n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma} = s_{{\bf q}, \sigma} + r_{{\bf q},\sigma}~.
\end{aligned}\end{equation}

In terms of these new degrees of freedom, the auxiliary model Hamiltonian takes the form
\begin{equation}\begin{aligned}
	\tilde H = -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow} + \sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}J^*{\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta} + \sum_{{\bf q},\sigma}\varepsilon_{{\bf N}_1 + {\bf q}}\left({\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma} + {\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma}\right),
\end{aligned}\end{equation}
where we have considered a simplified form of the bath interaction (for the channel \(l=1\)), taking into account the density-density correlations in \(k-\)space.

For bath interaction strength close to the critical value (\(W \lesssim W_c\)), the fixed point coupling value \(J^*\) is much smaller than \(W\). In order to obtain the gapless excitations of the system arising from the presence of the impurity site, we integrate out the impurity dynamics via a Schrieffer-Wolff transformation. The perturbation term \(\mathcal{V}\) then consists of Hamiltonian terms that modify the impurity configuration,
\begin{equation}\begin{aligned}
	\mathcal{V} = \sum_{{\bf q},\sigma}\varepsilon_{{\bf N}_1 + {\bf q}}\left({\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma} + {\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma}\right) + \sum_{{\bf q}_1, {\bf q}_2}J^*{S}_d^+{\phi}^\dagger_{{\bf q}_1 \downarrow} \phi_{{\bf q}_2 \uparrow} + \text{h.c.}~,
\end{aligned}\end{equation}
while the ``non-interacting" Hamiltonian is
\begin{equation}\begin{aligned}
	H_D &= -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow}~.
\end{aligned}\end{equation}
For the present Hamiltonian, the low-energy state is the one that minimises the bath interaction term \(\tilde H_\text{cbath-int}\). High-energy states are obtained by applying, on the state \(\ket{L}\), the excitation operator \(\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2,\bar\sigma}\) or its hermitian conjugate.

The complete second-order renormalised Hamiltonian is
\begin{equation}\begin{aligned}
    \Delta \tilde H =& \sum_{{\bf q}, \sigma}\epsilon_{\bf q} r_{{\bf q},\sigma} + \mathcal{U}\sum_{{\bf q}, \sigma}r_{{\bf q} \sigma}r_{{\bf q} \bar\sigma} + \mathcal{U}\sum_{{\bf q}_1 \neq {\bf q}_2, \sigma}\left[r_{{\bf q}_1 \sigma}r_{{\bf q}_2 \bar\sigma} + \phi^\dagger_{{\bf q}_1,\bar\sigma}\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2, \sigma}\phi_{{\bf q}_2, \bar\sigma}\right]~.
\end{aligned}\end{equation}
where $\epsilon_{\bf q} = \text{sign}\left(\varepsilon_{{\bf N}_1 + {\bf q}}\right)\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W}$ and $\mathcal{U} = \frac{{J^*}^2}{4W}$.
\end{widetext}

\end{document}

### 2025-12-10 submissions/TilingUploadROPP/Tiling_Project/QTR.tex
started creating referee response

\documentclass[%
 reprint,
superscriptaddress,
groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
prl,superscriptaddress
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{braket}
\usepackage{color}
\graphicspath{{./figures/}}
\bibliographystyle{apsrev4-2}

\begin{document}

%\title{Pseudogapped non-Fermi liquid phase arising from Kondo breakdown at the Mott transition}

%\title{Long range entangled Fermi arcs at a Pseudogapped Mott transition}

%\title{Long-range entangled Pseudogapped Mott Criticality: tracking Kondo breakdown via Quantum Tilling Reconstruction from cavity-Kondo defects}

\title{Quantum Tiling Reconstruction of long-range entangled Pseudogapped Mott Criticality from Cavity-Kondo defects}

%\title{What lies between a Fermi liquid and a Mott insulator in two dimensions? Insights from an impurity model}% Force line breaks with \\

\author{Abhirup Mukherjee}
\affiliation{%
 Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
}
\author{S. R. Hassan}
\affiliation{The Institute of Mathematical Sciences, C.I.T. Campus, Chennai 600 113, India}
\author{Anamitra Mukherjee}
\affiliation{School of Physical Sciences, National Institute of Science, Education and Research, HBNI, Jatni 752050, India}
\author{N. S. Vidhyadhiraja}
\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
\author{A. Taraphder}
\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
%
\author{Siddhartha Lal}
\affiliation{%
 Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
}

\date{\today}

\begin{abstract}
%We propose a new theoretical framework—centered on the Vacancy–Kondo (VK) model and implemented via a Quantum Tiling Reconstruction (QTR) protocol—to systematically investigate the Mott transition and pseudogap phenomena in strongly correlated lattice systems. This framework is built upon a lattice-compatible, defect-based formulation in which the fundamental unit is a local Kondo-defect: a vacancy-centered site hosting a spin-$\frac{1}{2}$ moment coupled to its neighboring conduction electrons via exchange and hybridization processes.The QTR procedure restores lattice translation symmetry by tiling these Kondo-defect units across the lattice, yielding a translationally invariant many-body Hamiltonian—termed the \textit{VK-Reconstructed Hubbard–Heisenberg Model}. This construction enables momentum-resolved access to spectral and transport observables, all derived from real-space correlation structures.Within this framework, the Mott transition at half-filling is reinterpreted as a two-stage breakdown of lattice coherence. In the first stage, Kondo screening is frustrated by local charge fluctuations, leading to decoherence and the formation of antinodal gaps that disrupt the connectivity of the Fermi surface. In the second stage, a pseudogap metal emerges, effectively described by an emergent two-channel Kondo (2CK) fixed point in the tiled lattice. The resulting Fermi arcs host non-Fermi liquid excitations and terminate on a critical Fermi surface.As the system nears the transition, these arcs shrink toward nodal points, signaling the onset of a singular nodal metallic state accompanied by enhanced spin-flip correlations and long-range entanglement in real space. This identifies the Mott transition as a fundamentally nonlocal and collective quantum phenomenon—well beyond the reach of traditional impurity-based approaches—and positions the VK+QTR framework as a powerful paradigm for capturing strong correlations, emergent momentum-space geometry, and unconventional quantum criticality in lattice systems.
We present a theoretical framework based on the Vacancy–Kondo (VK) model and a symmetry-restoring method called Quantum Tiling Reconstruction (QTR) to study the Mott transition and pseudogap behavior in correlated lattice systems. The starting point is a local Kondo-defect unit—a vacancy-centered spin-$\frac{1}{2}$ coupled to neighbouring sites through hybridization and exchange. By tiling such a unit across the lattice, QTR produces a translationally invariant many-body Hamiltonian, referred to as the VK-Reconstructed Hubbard–Heisenberg Model. This construction keeps the underlying lattice structure intact and allows momentum-resolved analysis using a real-space formulation. The QTR method is general: by changing the choice of defect unit, different lattice models with specific local interactions can be built. In the VK example, the Mott transition proceeds in two steps. First, Kondo screening is weakened by charge fluctuations, leading to antinodal gaps and partial loss of Fermi surface connectivity. Second, a pseudogap metal appears, described by an effective two-channel Kondo process, with low-energy excitations along Fermi arcs. As the system approaches the transition, these arcs narrow toward the nodal points, resulting in a nodal metal with enhanced long-range spin-slip correlations and entanglement. This framework offers a structured way to connect local interaction effects with the behavior of electrons in the full lattice.
\end{abstract}

\maketitle
\par\noindent\textit{Introduction.}
The pseudogap (PG) and strange metal phases observed in the cuprate high-$T_c$ superconductors remain among the most profound challenges in the physics of strongly correlated electrons~\cite{keimer2015quantum}. The PG phase, which displays a characteristic nodal–antinodal dichotomy and the emergence of Fermi arcs~\cite{loeserKapitulnik1996,Norman1998,Hashimoto2014}\textbf{(CITE LAUCHLI PRL, RAJA PRL)}, has been robustly observed in simulations of the two-dimensional Hubbard model~\cite{KyungKotliar2006,MacridinAzevedo2006,WuFerrero2018,anirbanmott2,HilleAndergassen2020}. Nevertheless, key questions remain unresolved: How is the pseudogap connected to the proximate Mott insulating and superconducting phases~\cite{FradkinRevModPhys2015,Kitatani2023,Sorella2023}? How does it evolve across coupling regimes~\cite{HuangDevereaux2018,Fedor2022,SimkovicFerrero2024}? And is the nodal–antinodal dichotomy intrinsic to the Hubbard model~\cite{Hashimoto2014,Schafer2021}? Most fundamentally, the relation between zero-temperature criticality and finite-temperature crossovers remains ambiguous~\cite{White1998,Ido2018,ProustTaillefer2019,Ponsioen2019,Shengtao2021,XuZhang2022}.

In this work, we introduce a new conceptual and computational framework to address these questions based on the \textbf{Vacancy–Kondo (VK)} model and a symmetry-restoring procedure we term \textbf{Quantum Tiling Reconstruction (QTR)}. At the heart of our construction is a localized \textit{Kondo-defect unit}—a spin-$\frac{1}{2}$ degree of freedom placed at a vacancy in the conduction lattice, coupled to neighbouring sites via hybridization and spin exchange. This defect unit serves as the fundamental building block for constructing the full lattice model. Unlike traditional impurity-based approaches, our formulation retains lattice geometry at every step, enabling a direct route from local many-body physics to global momentum-resolved observables.\\
To construct a translationally invariant correlated lattice system, we apply the Quantum Tiling Reconstruction (QTR) protocol to the local Kondo-defect unit, symmetrically placing it at every site of the lattice using a many-body translation operator. This procedure restores lattice symmetry in a controlled and non-perturbative manner, producing the \textit{VK-Reconstructed Hubbard–Heisenberg Model} (VK-RHH): a momentum-compatible, strongly correlated lattice Hamiltonian that encodes both spin and charge dynamics arising from real-space defect physics.

Importantly, this is a general scheme: the framework itself is adaptable to other vacancy-defect units, enabling systematic exploration of correlated phases in a diverse class of translationally invariant lattice Hamiltonians. In contrast to dynamical mean-field theory (DMFT) and its cluster extensions~\cite{georges1996,Hettler2000DCA,Kotliar2001Cellular,Maier2005,Sakai2023}—which approximate lattice self-energies via local or cluster embeddings—our approach derives the full lattice theory constructively from the local Kondo-defect unit. This preserves the geometric and correlation structure of the square lattice without resorting to self-consistent approximations or coarse graining.

The VK+QTR framework directly reveals the microscopic mechanism underlying pseudogap formation and its evolution into a Mott insulating phase in the half-filled VK-RHH model. As we increase the effective interaction strength and enhance local charge fluctuations, Kondo screening becomes increasingly frustrated and the system undergoes a two-stage coherence breakdown: (1) antinodal regions of the Fermi surface become gapped through a correlation-induced Lifshitz transition~\cite{sakai2009evolution}; and (2) a non-Fermi liquid pseudogap phase emerges, characterized by nodal Fermi arcs and critical spectral weight.

This pseudogap phase is not a mere thermal or numerical crossover, but rather arises from a bona fide quantum phase structure intrinsic to the Kondo-defect unit. Through QTR, these local features propagate coherently into the lattice, giving rise to long-range spin-flip correlations and entanglement patterns. The resulting criticality is inherently nonlocal—marking a sharp departure from the local quantum critical paradigm~\cite{Si2001}—and demonstrates the power of the VK+QTR framework in capturing the effects of lattice geometry and coherence loss in strongly correlated systems.

\par\noindent\textit{The Vacancy–Kondo (VK) Defect Unit.}
To explore pseudogap and Mott physics within a real-space framework that retains lattice geometry, we introduce a localized building block we call the \textbf{cavity-Kondo defect unit}, a composite object formed when a lattice site is removed and replaced by a localized orbital with internal interactions and dynamic coupling to surrounding conduction electrons. The defect orbital at the vacancy carries a local Hubbard interaction $U$, prohibiting double occupancy. It hybridizes with neighboring conduction electrons, 
as well as couples directly to the spins of nearby conduction electrons through an explicit exchange term. The VK defect thus serves as a natural building block for modeling both correlated charge dynamics of itinerant electrons and the dynamical screening of emergent local moments. The Hamiltonian describing the Kondo-defect unit is:
\begin{equation}
\label{eq:VK_defect}
\mathcal{H}_\text{VK} = H_{\text{defect}} + H_{\text{defect-coupling}} + H_{\text{bath}},
\end{equation}
where
\begin{equation}
H_{\text{defect}} = -\frac{U}{2} \left( \hat{n}_{d\uparrow} - \hat{n}_{d\downarrow} \right)^2
\end{equation}
describes the interaction at the vacancy-hosted spin center. This localized spin $\vec{S}_d$ couples to its four nearest neighbor conduction sites $c_{Z\sigma}$ through spin-exchange and one-particle hybridization:
\begin{equation}
H_{\text{defect-coupling}} = \frac{J}{2} \sum_{Z} \vec{S}_d \cdot c^\dagger_{Z\alpha} \boldsymbol{\tau}_{\alpha\beta} c_{Z\beta}
- V \sum_{Z,\sigma} \left( c^\dagger_{Z\sigma} c_{d\sigma} + \text{h.c.} \right).
\end{equation}
Here, $\vec{S}_d$ is the spin-$\frac{1}{2}$ operator at the vacancy, and $Z$ runs over the defect’s neighbors.

The surrounding conduction bath is described by:
\begin{equation}
H_{\text{bath}} = \sum_{\mathbf{k},\sigma} \epsilon_\mathbf{k} c^\dagger_{\mathbf{k}\sigma} c_{\mathbf{k}\sigma}
- \frac{W}{2} \sum_{Z} \left( n_{Z\uparrow} - n_{Z\downarrow} \right)^2,
\end{equation}
where $\epsilon_{\mathbf{k}} = -2t(\cos k_x + \cos k_y)$ defines the tight-binding dispersion at half-filling, and the $W$-term captures local spin-charge interactions that can frustrate the screening of the Kondo defect. A key feature of this VK unit is its spatially discrete embedding. Although the defect breaks translation symmetry locally, the Fourier-transformed Kondo coupling, 
\[
J_{\mathbf{k},\mathbf{k}'} = \frac{J}{2} \left[ \cos(k_x - k'_x) + \cos(k_y - k'_y) \right],
\]
captures how the defect scatters Bloch states of the surrounding lattice, encoding spatial anisotropy and enabling analysis of coherence loss and pseudogap formation. The $C_4$ symmetry of $J_{\mathbf{k},\mathbf{k}'}$ renders it suitable for momentum-resolved tiling.

\par\noindent\textit{Quantum Tiling Reconstruction (QTR).}
To extend the localized VK unit into a translationally invariant many-body system, we introduce the \textbf{Quantum Tiling Reconstruction (QTR)} scheme. In this approach, the local couplings—such as hybridization and spin exchange with neighboring sites—are repeated across the lattice following the symmetry and geometry of the underlying structure. This process builds a global lattice Hamiltonian that inherits its dynamics and geometry from the quantum behavior of the single defect unit. In this way, QTR reconstructs momentum-space features and coherence properties of the system from its local building blocks, providing a consistent framework for studying pseudogap formation, spectral weight redistribution, and other emergent many-body phenomena.

Let \( \mathcal{H}_\text{d}(\mathbf{r}_d) \) denote the local defect-unit Hamiltonian with a vacancy centered at position \( \mathbf{r}_d \). The full lattice Hamiltonian generated via Quantum Tiling Reconstruction (QTR) is defined as:
\begin{equation}
\label{eq:QTR_consistent}
\mathcal{H}_\text{QTR} = \sum_{\mathbf{r}} T^\dagger(\mathbf{r}) \mathcal{H}_\text{d}(\mathbf{r}_d) T(\mathbf{r}) - N H_\text{bath},
\end{equation}
where \( T(\mathbf{r}) \) is a many-body translation operator acting on both conduction electrons and localized defect degrees of freedom with $\mathcal{H}_\text{d}$, and \( N \) is the number of tiling units (introduced to avoid double-counting of the conduction bath).\\ When the cavity-Kondo Hamiltonian is used as the seed unit, $\mathcal{H}_\text{d}\equiv \mathcal{H}_\text{VK}$ the QTR construction yields a specific translationally invariant lattice model $\mathcal{H}_\text{QTR}$, the \textit{VK-Reconstructed Hubbard–Heisenberg Model} ($\mathcal{H}_\text{VK-RHH}$):
\begin{equation}
\begin{aligned}
\mathcal{H}_\text{VK-RHH} =\,
&- \frac{\tilde{t}}{\sqrt{\mathcal{Z}}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle, \sigma} \left( c^\dagger_{\mathbf{r}_i \sigma} c_{\mathbf{r}_j \sigma} + \text{h.c.} \right)
- \tilde{\mu} \sum_{\mathbf{r}, \sigma} n_{\mathbf{r} \sigma} \\
&+ \frac{\tilde{J}}{\mathcal{Z}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle} \vec{S}_{\mathbf{r}_i} \cdot \vec{S}_{\mathbf{r}_j}
- \frac{1}{2} \tilde{U} \sum_{\mathbf{r}} \left( n_{\mathbf{r} \uparrow} - n_{\mathbf{r} \downarrow} \right)^2.
\end{aligned}
\end{equation}

The renormalized lattice parameters $(\tilde{t}, \tilde{\mu}, \tilde{J}, \tilde{U})$ emerge directly from the local coupling constants of the Kondo-defect unit—such as the Kondo exchange $J$, hybridization $V$, charge fluctuation scale $W$, and onsite interaction $U$—as well as the tiling geometry. This construction encodes the interplay of spin and charge correlations within a fully symmetry-restored lattice framework.

Eigenstates of the QTR Hamiltonian obey a generalized many-body Bloch theorem~\cite{stoyanova}, and the construction enables momentum-resolved access to quantities like spectral functions and self-energies. Crucially, correlation functions and entanglement diagnostics computed within the Kondo-defect unit can be consistently mapped to the full lattice through the symmetry-preserving nature of QTR.
\begin{figure}
    \centering
    \includegraphics[width=0.31\linewidth, height=2.45cm]{phaseDiagram.pdf}
    \includegraphics[width=0.67\linewidth]{SF-DOS.pdf}
    \caption{Left: Phase diagram of impurity model at strong coupling in $U$ in terms of competing dimensionless Kondo ($J/t$) and bath correlation ($W/t$) couplings. A pseudogap phase (red, PG) is observed between the local Fermi liquid (pink, LFL) and local moment (black, LM) phases. Center: $k-$space resolved spin-spin correlation $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$ in the pseudogap phase of the impurity model. Antinodal regions are observed to decouple from Kondo screening of the impurity. Right: Upon tiling, this leads to a $k-$space resolved antinodal gap in the electronic density of states of the lattice model, corresponding to Luttinger surfaces of zeros.}
    \label{spinCorr}
\end{figure}

\par\noindent\textit{Pseudogap Formation via Kondo-Defect Breakdown.}
To understand how the pseudogap (PG) phase emerges within the Vacancy–Kondo (VK) model, we analyze the breakdown of Kondo screening in the large-$U$ regime of the Kondo-defect Hamiltonian. This analysis is carried out through a momentum-resolved scaling flow of the Kondo coupling \(J^{(j)}_{{\bf k}_1, {\bf k}_2}\), using the unitary renormalization group (URG) technique~\cite{anirbanurg1} (details in~\cite{suppmat}).

The RG flow equation takes the form:
\begin{equation}
\label{KondoRGequation}
\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2},
\end{equation}
where $\varepsilon_j$ denotes the energy of the shell being decoupled at the $j^\text{th}$ RG step, and the sum is over all momentum states ${\bf q}$ in the particle sector (PS) of the shell—i.e., all filled states at $T = 0$ in the absence of fluctuations. The notation ${\bf \bar q} = {\bf q} + {\boldsymbol \pi}$ refers to the particle-hole conjugate of ${\bf q}$. The interaction term $W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}$ is marginal under RG flow and encodes spin-charge interactions in the conduction background. While the full behavior of the flow equation is understood via numerical evaluation (discussed below), its analytic structure already shows that an \textit{attractive bath interaction} ($W < 0$) frustrates Kondo screening, ultimately driving a transition to a Mott insulating phase~\cite{Mukherjee_2023}.

By tuning the ratio $W/J$ from zero toward negative values (see Fig.~\ref{spinCorr}, left panel), we uncover a sequence of emergent phases arising from the competition between Kondo screening ($J$) and charge fluctuation suppression ($W$):
\begin{enumerate}
    \item For $|W|/J < (|W|/J)_{\text{PG}}$, the Kondo-defect unit exhibits a \textbf{local Fermi liquid} phase in which the entire Fermi surface participates in coherent Kondo screening.
    \item For $(|W|/J)_{\text{PG}} < |W|/J < (|W|/J)_c$, we observe a \textbf{local pseudogap} phase where only the nodal regions remain actively screened, and the antinodal regions become incoherent.
    \item For $|W|/J > (|W|/J)_c$, the system enters a \textbf{local moment phase} with complete breakdown of Kondo screening at the defect site.
\end{enumerate}

This progression is clearly reflected in the ${\bf k}$-resolved spin correlations between the defect and bath, defined as $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$. In the PG regime (Fig.~\ref{spinCorr}, center), $\chi_s(d,{\bf k})$ shows suppressed correlations in the antinodal regions, indicating momentum-selective screening failure.

We interpret $(W/J)_{\text{PG}}$ as the entry point into the pseudogap phase, and $(W/J)_c$ as its termination into the unscreened regime. Upon performing the Quantum Tiling Reconstruction (QTR), these local transitions propagate into the global lattice model. In particular, the $T=0$ Mott transition of the 2D Hubbard–Heisenberg model reconstructed from VK units now proceeds via a well-defined PG phase, characterized by partial gapping of the Fermi surface. The resulting momentum-resolved density of states exhibits spectral suppression in the antinodal zones, while nodal quasiparticles remain gapless (Fig.~\ref{spinCorr}, right panel).

We now present the microscopic mechanism for this pseudogap formation, as it emerges through the scaling flow of Kondo screening in the defect-centered VK unit.

\begin{figure}[htpb]
    \centering
    \includegraphics[width=\linewidth]{zerosFlow.pdf}
    \caption{Left, Right and Center: Decoupling of $J_{{\bf k}, {\bf k'}}$ (positive, negative and zeros shown in yellow, purple and green respectively), with ${\bf k}$ (grey circle) corresponding to the node, antinode and a point mid-way between them on the top right arm of the Fermi surface respectively. This is seen via the appearance of zeros (green patches) of $J_{{\bf k}, {\bf k'}}$ for ${\bf k'}$ initially on the nodal regions of adjacent arms, and their subsequent progression towards the antinodes. The decoupling 
    ends with the onset of the pseudogap.
    }
    \label{rgProgression}
\end{figure}
\par\noindent\textit{Unraveling of Kondo Screening in the Kondo-Defect Unit.}
As shown in Fig.~\ref{rgProgression}, the anisotropic breakdown of Kondo screening within the Kondo-defect unit can be tracked by analyzing the vanishing of the spin-flip scattering amplitude $J_{{\bf k}_N, {\bf k}}$, where ${\bf k}_N = (\pi/2, \pi/2)$ is a nodal point and ${\bf k}$ is a general wavevector on the Fermi surface.

At $W/J = 0$, the scattering amplitude $J_{{\bf k}_N, {\bf k}}$ vanishes for ${\bf k}$ located at antinodal points or nearby nodes. As $W/J$ is decreased towards the pseudogap onset value $(W/J)_{\text{PG}}$, the flow of the renormalized coupling under URG reveals an \textit{unraveling} of Kondo coherence: $J_{{\bf k}_N, {\bf k}}$ becomes RG-irrelevant for ${\bf k}$ near adjacent nodal directions, forming a patch of vanishing amplitude (Fig.~\ref{rgProgression}, left). With further decrease of $W/J$, this patch of zeros expands progressively toward the antinodal region, signaling a systematic decoupling of $J_{{\bf k}_1, {\bf k}_2}$ along connections between different Brillouin zone quadrants (Fig.~\ref{rgProgression}, center and right).

At the critical ratio $W/J = (W/J)_{\text{PG}}$, the antinodal wavevectors become fully disconnected from the rest of the Fermi surface in terms of spin-flip interactions, within numerical precision. This behavior constitutes an interaction-driven \textit{Lifshitz transition} in the effective scattering topology, demarcating the onset of the pseudogap (PG) phase characterized by Fermi arcs~\cite{WuFerrero2018}.

Notably, this phase coincides with the emergence of an effective two-channel Kondo (2CK) structure within the Kondo-defect unit. Each channel corresponds to a pair of symmetry-related Fermi arcs on opposite faces of the Fermi surface. This 2CK character is enforced by the symmetry of the Kondo coupling:
\[
J_{{\bf k},{\bf k'}}= -J_{{\bf k}+{\bf Q},{\bf k'}}=-J_{{\bf k},{\bf k'}+{\bf Q}},
\]
with ${\bf Q} = (\pi, \pi)$. As the PG phase develops further, the disconnected arcs shrink toward the nodal points. Their eventual collapse marks the transition to a fully gapped Mott insulating state, as reconstructed in the lattice model through QTR.

\par\noindent\textit{Momentum-Resolved Spectral Weight Redistribution.}
The dynamical process of spectral weight transfer associated with PG formation is illustrated in Fig.~\ref{chargeCorr}(left). In the PG regime, strong charge fluctuations emerge between nodal and antinodal sectors \textbf{(CITE LAUCHLI PRL)}, which selectively remove low-energy spectral weight from the antinodal regions, pushing it to higher energies and effectively gapping out these regions.

Correspondingly, the self-energy $\Sigma({\bf k}, \omega=0)$ of the QTR-reconstructed lattice model exhibits poles near the antinodal momenta, which migrate toward the nodes as the system is tuned further into the Mott insulating regime (Fig.~\ref{chargeCorr}, right). This behavior mirrors the coalescence of zero-frequency poles in the self-energy structure of the underlying Kondo-defect unit~\cite{suppmat}, indicating a consistent local-to-global mapping of spectral anomalies via Quantum Tiling Reconstruction.

Thus, the PG phase is not merely a phenomenological crossover but a well-defined emergent regime rooted in the breakdown of Kondo coherence within the defect-centered VK framework, and extended into the lattice via symmetry-preserving quantum reconstruction.

\begin{figure}
    \centering
    \includegraphics[width=0.49\linewidth]{cfnode-2.pdf}
    \includegraphics[width=0.49\linewidth]{selfEnergyKspace-3.pdf}
    \caption{Left: Enhanced charge correlations $\chi_c({\bf k}_1, {\bf k}_2) = \braket{c^\dagger_{{\bf k}_1\uparrow}c^\dagger_{{\bf k}_1\downarrow}c_{{\bf k}_2\downarrow}c_{{\bf k}_2\uparrow} + \text{h.c.}}$ are observed between the nodal and antinodal regions, signalling Kondo breakdown in the pseudogap phase of the impurity model. Right: In turn, the breakdown leads to the gapping of the antinodal regions in the lattice model, seen from the appearance of poles in the imaginary part of the self-energy.}
    \label{chargeCorr}
\end{figure}

\par\noindent\textit{Non-Fermi Liquid Behavior of the Pseudogap Phase.}
Within the pseudogap (PG) regime defined by $(|W|/J)_{\text{PG}} < |W|/J < (|W|/J)_c$, the nature of the residual gapless excitations on the Fermi arcs undergoes a qualitative transformation. As previously discussed, these Fermi arcs emerge from momentum-selective Kondo breakdown and are governed, at the level of the Kondo-defect unit, by an effective \textbf{two-channel Kondo (2CK)} model~\cite{Tsvelick_weigmann_mchannel_1985,emery_kivelson}.

The 2CK model exhibits non-Fermi liquid excitations characterized by the separation of spin, charge, and channel degrees of freedom~\cite{affleck1992}. Only the spin sector remains gapless, and its excitations dominate the low-energy physics. The self-energy associated with the Kondo-defect in this regime shows characteristic \textbf{marginal Fermi liquid} (MFL) behavior~\cite{Coleman_tsvelik,Schofield1997,Patra2023MCK}: the real and imaginary parts scale as
\[
\Sigma^{\prime}(\omega) \sim \omega \ln \omega, \qquad \Sigma^{\prime\prime}(\omega) \sim -\omega,
\]
yielding a linear scattering rate $\Gamma(\omega) \sim \omega$ and a logarithmically vanishing quasiparticle residue:
\[
Z_{\text{defect}}(\omega) \sim (c - \ln \omega)^{-1},
\]
where $c$ is a non-universal constant~\cite{varma2002singular}.

This behavior is evident in the numerical evolution of the Kondo-defect quasiparticle residue $Z_{\text{defect}}$, which drops sharply as the system moves from the Fermi liquid regime into the PG phase (Fig.~\ref{channelDecoupling}, left). The inset of the same figure illustrates the gradual emergence of uncompensated local moments—hallmarks of incomplete Kondo screening—across the PG region.

Upon applying Quantum Tiling Reconstruction (QTR), these local non-Fermi liquid features propagate into the reconstructed lattice model, imparting marginal Fermi liquid behavior to the nodal Fermi arcs and establishing a critical metallic state with suppressed quasiparticle coherence. Thus, the PG phase is not a crossover between metal and insulator, but rather a non-Fermi liquid metal born out of channel-symmetric Kondo-defect physics and extended into the lattice through symmetry-restoring reconstruction.

\begin{figure}
    \centering
    \includegraphics[width=0.49\linewidth]{localQPResidue.pdf}
    \includegraphics[width=0.49\linewidth]{I2-di_69-2000.pdf}
    \caption{Left: Suppression of quasiparticle residue as the impurity model is tuned towards the Mott transition. An initial drastic fall observed for $W/J \lesssim (W/J)_\text{PG}$, signalling the destruction of the Fermi liquid with unraveling of Kondo screening. A second drastic fall is observed close to the Mott transition due to a divergent self-energy. Inset shows the growth of unscreened impurity magnetic moment in the pseudogap phase. 
    Right: Mutual information $I_{2}(d,r)$ between the impurity spin and conduction bath local spins as a function of the distance {\bf r} between them. $I_{2}(d,r)$ decays exponentially in the Fermi liquid phase (blue), but show long-ranged behaviour in the non-Fermi liquid phase (green, yellow). The range of the entanglement is seen to grow yet larger particularly close to the transition (green).
    }
    \label{channelDecoupling}
\end{figure}

\par\noindent\textit{Evolution of the Pseudogapped Non-Fermi Liquid.}
As the system approaches the Mott transition from within the pseudogap (PG) regime, the marginal Fermi liquid (MFL) excitations characteristic of the two-channel Kondo (2CK) behavior give way to a distinct non-Fermi liquid phase described by the Hatsugai–Kohmoto (HK) model~\cite{Baskaran1991,Hatsugai1992}. This insight emerges from a perturbative analysis of the RG fixed-point Hamiltonian of the Kondo-defect unit in the regime $W/J \lesssim (W/J)_{\text{PG}}$, where the fixed-point Kondo scattering amplitude $J^*$ is small, but the background bath interaction $|W|$ is large.

Under these conditions, the dominant low-energy contribution to the effective Hamiltonian arises from forward scattering processes and assumes the form of an HK-like model (derived in Appendix~\ref{hkmDerivation}):
\begin{equation}
\label{HKModel}
\Delta \tilde H_{{\bf q}_1 = {\bf q}_2} = \sum_{{\bf q},\sigma} \epsilon_{{\bf q}}\, n_{{\bf q},\sigma} + u \sum_{{\bf q}, \sigma} n_{{\bf q} \sigma} n_{{\bf q} \bar\sigma},
\end{equation}
where $n_{{\bf q} \sigma} = \phi^\dagger_{{\bf q}, \sigma} \phi_{{\bf q}, \sigma}$ counts emergent fermionic relative modes $\phi_{{\bf q},\sigma}$ shifted by momentum ${\bf q}$ from the nodal points ${\bf N}_1 = (\pi/2, \pi/2)$ and its partner ${\bf N}_1 + {\bf Q}_1 = (-\pi/2, -\pi/2)$. The effective kinetic term $\epsilon_{\bf q}$ and interaction $u \sim J^2/W$ are renormalized by spin-charge correlations in the conduction background~\cite{suppmat}.

Within this effective theory, the low-energy metallic state is a singular non-Fermi liquid, characterized by excitations in the neighbourhood of the four nodal points in $k$-space, and a divergent one-particle self-energy at the Fermi surface~\cite{Phillips2020}:
\[
\Sigma_{{\bf q}}(\omega) = -\frac{u^2}{4(\omega - \epsilon_{\bf q})},
\]
such that $\Sigma_{\epsilon_{\bf q}=0}(\omega \to 0) \to \infty$. This divergence signals the collapse of quasiparticle coherence precisely at the non-interacting Fermi surface and anticipates the opening of a hard Mott gap in the charge excitation spectrum.

This behavior is consistently reflected in the QTR-reconstructed lattice model, where zero-frequency self-energy poles at the antinodes (Fig.~\ref{chargeCorr}, right) signal the breakdown of metallicity and the approach to Mott localization. Furthermore, near the critical point, the quasiparticle residue associated with the Kondo-defect unit scales as $Z_{\text{defect}} \sim \omega^2/U^2$, vanishing more rapidly than the logarithmic suppression found in the MFL regime. This explains the sharp drop in $Z_{\text{defect}}$ observed at the transition (Fig.~\ref{channelDecoupling}, left).

The scattering rate exhibits a corresponding change: while the MFL phase displays $\Gamma \sim \omega$, the HK criticality leads to a divergent rate at the Fermi surface,
\[
\Gamma(\omega = \epsilon_{\bf k}) \sim U^2 \delta(\omega - \epsilon_{\bf k}),
\]
signaling a complete loss of quasiparticle definition at the transition. This HK-driven mechanism thus provides a microscopic origin for the breakdown of metallicity and the emergence of Mott insulating behavior, arising naturally from the defect-centered VK model and extended to the lattice through the QTR framework.

\par\noindent\textit{Non-Local Nature of the Pseudogap Phase.}
As shown in Fig.~\ref{channelDecoupling}(right), the mutual information between the spin of the Kondo-defect unit and the surrounding conduction lattice sites exhibits a marked crossover within the pseudogap (PG) regime. Prior to the onset of the PG phase, this mutual information is short-ranged and localized near the defect site. However, as the Mott transition is approached, it becomes increasingly long-ranged—extending across distant parts of the conduction environment. A similar trend is observed in the spin-flip correlation functions between the Kondo-defect and conduction electrons~\cite{suppmat}, providing further evidence of the progressive breakdown of localized Kondo screening and the accompanying collapse of Landau quasiparticles.

This growing spatial range of correlations implies that the Mott transition lies well beyond the scope of \textit{local quantum criticality}~\cite{Si2001}. The non-Fermi liquid excitations residing on the Fermi arcs of the PG regime exhibit increasingly singular and non-local behavior as the transition is approached. Their dynamics cannot be attributed to purely local quantum fluctuations but instead reflect the emergence of collective, long-range entangled excitations.

Moreover, we observe the presence of pairing fluctuations centered around the nodal regions of the Fermi surface~\cite{suppmat} \textbf{(CITE LAUCHLI PRL, ANIRBAN NJP-II)}. These nodal metallic modes—partially protected from incoherence—serve as seeds for superconducting correlations that can become dominant upon doping~\cite{Phillips2020}.

\par\noindent\textit{Conclusions.}
This work introduces a general and flexible framework based on \textbf{Quantum Tiling Reconstruction (QTR)} for constructing momentum-resolved, symmetry-compatible lattice Hamiltonians from localized many-body building blocks. Using the Vacancy–Kondo (VK) unit as a prototype, we demonstrate how QTR reorganizes real-space impurity physics into an extended, translationally invariant correlated lattice model. The resulting VK-Reconstructed Hubbard–Heisenberg (VK-RHH) model preserves lattice geometry and enables direct access to global observables such as momentum-dependent spectral weight, pseudogap formation, and coherence suppression. Crucially, QTR is not limited to the VK unit; it provides a modular platform for systematically generating new classes of strongly correlated lattice models driven by local quantum structure.

For the VK defect unit, our findings reveal that the Mott transition proceeds through a pseudogap phase that is neither a simple crossover nor a local critical point, but a genuinely singular, non-Fermi liquid metal arising from a breakdown of Kondo coherence in the VK framework. This intermediate phase is characterized by non-locality and long-range entanglement, culminating with nodal criticality as the transition is approached. The Quantum Tiling Reconstruction (QTR) methodology allows us to faithfully extend these real-space features of the Kondo-defect unit to the full lattice, thereby capturing the true nonlocal structure of the transition. The doping evolution of this critical pseudogap phase—particularly its relation to nodal pairing—is an important direction for future exploration.

\par\noindent\textit{Acknowledgments.}
AM thanks IISER Kolkata for funding through a JRF and SRF. S Lal thanks the SERB, Govt. of India for funding through MATRICS Grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
\bibliography{tilingProject}% Produces the bibliography via BibTeX.

\appendix

\section{Appendixes}
\paragraph*{Luttinger's theorem in the presence of Luttinger surfaces.} One can also ask whether Luttinger's theorem is satisfied in our model in the presence of Luttinger surfaces. It has been shown that particle-hole symmetric systems always satisfy a generalised Luttinger's theorem~\cite{seki2017topological}, where the Fermi volume $V_L$ is represented as the difference in the number of poles and zeros, of the single-particle Green's function, that are enclosed by the Fermi surface~\cite{seki2017topological}. This holds true even in the presence of a divergent self-energy~\cite{Phillips2013}. Since our model is always at half-filling, Luttinger's theorem is always satisfied.

The way it works out (despite the presence of Luttinger surfaces) is as follows. We need only show that the number of occupied states below the chemical potential remains unchanged across the first Lifshitz transition. Before the transition, the presence of gapless excitations ensures that the Fermi surface is singly-occupied on average. Inside the pseudogap, the gapless $k-$states continue to contribute one pole on average to the Luttinger count, while the gapping out of certain $k-$states leads to a rearrangement of their spectrum: doubly-occupied states on the Luttinger surfaces become more favourable compared to the singly-occupied states (due to the attractive $W$-interaction). Owing to particle-hole symmetry, these states are degenerate with the zero occupancy states, so that on average, a single state is again occupied. This ensures that the number of occupied states (and hence the number of occupied poles) remains unchanged across the transition. The same argument works for the Mott insulator, where the entire Fermi surface gets replaced by a Luttinger surface.

\paragraph*{Quantum Tiling of a Kondo-Defect Unit into the VK-Reconstructed Hubbard–Heisenberg Model}

We now provide technical details on how the many-body lattice Hamiltonian arises from Quantum Tiling Reconstruction (QTR) of the Kondo-defect unit defined within the Vacancy–Kondo (VK) framework. As discussed in the main text, the local unit centered at position ${\bf r}_d$ is composed of three parts:
\[
H({\bf r}_d) = H_\text{defect} + H_\text{bath} + H_\text{defect-bath},
\]
where the local Kondo-defect Hamiltonian is
\begin{equation}
\label{onsiteHamiltonian}
H_\text{defect} = -\frac{U}{2}\left(\hat n_{{\bf r}_d \uparrow} - \hat n_{{\bf r}_d \downarrow} \right)^2 - \eta \sum_\sigma \hat n_{{\bf r}_d \sigma},
\end{equation}
and the surrounding conduction environment is described by:
\begin{equation}
\label{bathHamiltonian}
\begin{aligned}
H_\text{bath} &= -\frac{1}{\sqrt{\mathcal{Z}}} t \sum_{\langle {\bf r}_i, {\bf r}_j \rangle \neq {\bf r}_d;\, \sigma} \left( c^\dagger_{{\bf r}_i \sigma} c_{{\bf r}_j \sigma} + \text{h.c.} \right) \\
&\quad - \frac{1}{2\mathcal{Z}} W \sum_{{\bf z} \in \text{NN}({\bf r}_d)} \left( \hat n_{{\bf z} \uparrow} - \hat n_{{\bf z} \downarrow} \right)^2 - \mu \sum_{{\bf r}_i \neq {\bf r}_d} \hat n_{{\bf r}_i \sigma},
\end{aligned}
\end{equation}
with $\mathcal{Z}$ the coordination number, and $\text{NN}({\bf r}_d)$ the nearest neighbors of the defect. The defect–bath coupling includes both Kondo exchange and single-particle hybridization:
\begin{equation}
\label{interactionHamiltonian}
\begin{aligned}
H_\text{defect-bath} &= \frac{J}{\mathcal{Z}} \sum_{\sigma, \sigma'} \sum_{{\bf z} \in \text{NN}({\bf r}_d)} \vec{S}_{{\bf r}_d} \cdot \boldsymbol{\tau}_{\sigma \sigma'} c^\dagger_{{\bf z} \sigma} c_{{\bf z} \sigma'} \\
&\quad - \frac{V}{\sqrt{\mathcal{Z}}} \sum_\sigma \sum_{{\bf z} \in \text{NN}({\bf r}_d)} \left( c^\dagger_{{\bf r}_d \sigma} c_{{\bf z} \sigma} + \text{h.c.} \right).
\end{aligned}
\end{equation}

The QTR procedure symmetrizes this Kondo-defect unit over all lattice sites:
\begin{equation}
\mathcal{H}_\text{tiled} = \mathcal{T}[H({\bf r}_d)] = \sum_{{\bf r}} T^\dagger({\bf r} - {\bf r}_d)\, H({\bf r}_d)\, T({\bf r} - {\bf r}_d),
\end{equation}
where $T({\bf a})$ is the many-body translation operator acting on operator coordinates:
\[
T^\dagger({\bf a})\, \mathcal{O}({\bf r}_1, {\bf r}_2, \ldots)\, T({\bf a}) = \mathcal{O}({\bf r}_1 + {\bf a}, {\bf r}_2 + {\bf a}, \ldots).
\]

The components transform under QTR as:
\begin{equation}
\begin{aligned}
\mathcal{T}[H_\text{bath}] &= -\frac{(N-2)t}{\sqrt{\mathcal{Z}}} \sum_{\langle {\bf r}_i, {\bf r}_j \rangle;\, \sigma} \left( c^\dagger_{{\bf r}_i \sigma} c_{{\bf r}_j \sigma} + \text{h.c.} \right) \\
&\quad - \frac{1}{2} W \sum_{\bf r} \left( \hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - (N - 1) \mu \sum_{\bf r} \hat n_{{\bf r} \sigma}, \\
\mathcal{T}[H_\text{defect}] &= -\frac{U}{2} \sum_{\bf r} \left( \hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2 - \eta \sum_{\bf r, \sigma} \hat n_{{\bf r} \sigma}, \\
\mathcal{T}[H_\text{defect-bath}] &= \sum_{\langle {\bf r}_i, {\bf r}_j \rangle} \left[ \frac{2J}{\mathcal{Z}} \vec{S}_{{\bf r}_i} \cdot \vec{S}_{{\bf r}_j} - \frac{2V}{\sqrt{\mathcal{Z}}} \sum_\sigma \left( c^\dagger_{{\bf r}_i \sigma} c_{{\bf r}_j \sigma} + \text{h.c.} \right) \right].
\end{aligned}
\end{equation}

To avoid overcounting, we subtract repeated copies of the noninteracting bath:
\[
\mathcal{H}_\text{bath-nint} = -\frac{1}{\sqrt{\mathcal{Z}}} t \sum_{\langle {\bf r}_i, {\bf r}_j \rangle;\, \sigma} \left( c^\dagger_{{\bf r}_i \sigma} c_{{\bf r}_j \sigma} + \text{h.c.} \right) - \mu \sum_{\bf r} \hat n_{{\bf r} \sigma}.
\]

The final outcome of QTR is the VK-Reconstructed Hubbard–Heisenberg Model:
\begin{equation}
\begin{aligned}
\mathcal{H}_\text{VK-RHH} &= -\frac{1}{\sqrt{\mathcal{Z}}} \tilde{t} \sum_{\langle {\bf r}_i, {\bf r}_j \rangle;\, \sigma} \left( c^\dagger_{{\bf r}_i \sigma} c_{{\bf r}_j \sigma} + \text{h.c.} \right) - \tilde{\mu} \sum_{\bf r} \hat n_{{\bf r} \sigma} \\
&\quad + \frac{1}{\mathcal{Z}} \tilde{J} \sum_{\langle {\bf r}_i, {\bf r}_j \rangle} \vec{S}_{{\bf r}_i} \cdot \vec{S}_{{\bf r}_j} - \frac{1}{2} \tilde{U} \sum_{\bf r} \left( \hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2.
\end{aligned}
\end{equation}

With effective parameters:
\[
\tilde{t} = t + 2V, \quad \tilde{U} = U + W, \quad \tilde{\mu} = 2\mu + \eta, \quad \tilde{J} = 2J.
\]

Thus, QTR reconstructs a translationally invariant, spin–charge entangled lattice model—the VK-Reconstructed Hubbard–Heisenberg Model—from local Kondo-defect dynamics.

\end{document}

### 2025-12-10 submissions/TilingUploadROPP/Tiling_Project/QTR_PRL.tex
started creating referee response

--- 2025-12-10 submissions/TilingUploadROPP/Tiling_Project/QTR.tex
@@
 
-%\title{Long-range entangled Pseudogapped Mott Criticality: tracking Kondo breakdown via Quantum Tilling Reconstruction from cavity-Kondo defects}
-
-\title{Quantum Tiling Reconstruction of long-range entangled Pseudogapped Mott Criticality from Cavity-Kondo defects}
+\title{Pseudogapped Mott Criticality from Vacancy--Kondo Tiling: \protect\\ Quantum Tiling Reconstruction of Non-Fermi Liquid Phases}
 
@@
 \author{Anamitra Mukherjee}
-\affiliation{School of Physical Sciences, National Institute of Science, Education and Research, HBNI, Jatni 752050, India}
+\affiliation{1 School of Physical Sciences, National Institute of Science, Education and Research, HBNI, Jatni 752050, India}
 \author{N. S. Vidhyadhiraja}
@@
 \begin{abstract}
-%We propose a new theoretical framework—centered on the Vacancy–Kondo (VK) model and implemented via a Quantum Tiling Reconstruction (QTR) protocol—to systematically investigate the Mott transition and pseudogap phenomena in strongly correlated lattice systems.
-This framework is built upon a lattice-compatible, defect-based formulation in which the fundamental unit is a local Kondo-defect: a vacancy-centered site hosting a spin-$\frac{1}{2}$ moment coupled to its neighboring conduction electrons via exchange and hybridization processes.The QTR procedure restores lattice translation symmetry by tiling these Kondo-defect units across the lattice, yielding a translationally invariant many-body Hamiltonian—termed the \textit{VK-Reconstructed Hubbard–Heisenberg Model}.
-This construction enables momentum-resolved access to spectral and transport observables, all derived from real-space correlation structures.Within this framework, the Mott transition at half-filling is reinterpreted as a two-stage breakdown of lattice coherence.
-In the first stage, Kondo screening is frustrated by local charge fluctuations, leading to decoherence and the formation of antinodal gaps that disrupt the connectivity of the Fermi surface.
-In the second stage, a pseudogap metal emerges, effectively described by an emergent two-channel Kondo (2CK) fixed point in the tiled lattice.
-The resulting Fermi arcs host non-Fermi liquid excitations and terminate on a critical Fermi surface.As the system nears the transition, these arcs shrink toward nodal points, signaling the onset of a singular nodal metallic state accompanied by enhanced spin-flip correlations and long-range entanglement in real space.
-This identifies the Mott transition as a fundamentally nonlocal and collective quantum phenomenon—well beyond the reach of traditional impurity-based approaches—and positions the VK+QTR framework as a powerful paradigm for capturing strong correlations, emergent momentum-space geometry, and unconventional quantum criticality in lattice systems.
-We present a theoretical framework based on the Vacancy–Kondo (VK) model and a symmetry-restoring method called Quantum Tiling Reconstruction (QTR) to study the Mott transition and pseudogap behavior in correlated lattice systems.
-The starting point is a local Kondo-defect unit—a vacancy-centered spin-$\frac{1}{2}$ coupled to neighbouring sites through hybridization and exchange.
-By tiling such a unit across the lattice, QTR produces a translationally invariant many-body Hamiltonian, referred to as the VK-Reconstructed Hubbard–Heisenberg Model.
-This construction keeps the underlying lattice structure intact and allows momentum-resolved analysis using a real-space formulation.
-The QTR method is general: by changing the choice of defect unit, different lattice models with specific local interactions can be built.
-In the VK example, the Mott transition proceeds in two steps.
-First, Kondo screening is weakened by charge fluctuations, leading to antinodal gaps and partial loss of Fermi surface connectivity.
-Second, a pseudogap metal appears, described by an effective two-channel Kondo process, with low-energy excitations along Fermi arcs.
-As the system approaches the transition, these arcs narrow toward the nodal points, resulting in a nodal metal with enhanced long-range spin-slip correlations and entanglement.
-This framework offers a structured way to connect local interaction effects with the behavior of electrons in the full lattice.
+We propose a new theoretical framework to study pseudogap formation and the Mott transition in strongly correlated systems, based on the Vacancy--Kondo--Heisenberg (VKH) model and a Quantum Tiling Reconstruction (QTR) scheme.
+A real-space Kondo-defect unit---comprising a localized spin-1/2 at a lattice vacancy---is tiled across a square lattice to yield a translationally invariant Hubbard--Heisenberg-type model.
+This VKH-Reconstructed Hubbard--Heisenberg model displays a pseudogap phase characterized by Fermi arc non-Fermi liquid excitations and long-range entanglement.
+Our framework provides a momentum-resolved, lattice-consistent alternative to impurity-based methods for capturing nonlocal quantum criticality.
 \end{abstract}
@@
 \maketitle
-\par\noindent\textit{Introduction.}
-The pseudogap (PG) and strange metal phases observed in the cuprate high-$T_c$ superconductors remain among the most profound challenges in the physics of strongly correlated electrons~\cite{keimer2015quantum}.
-The PG phase, which displays a characteristic nodal–antinodal dichotomy and the emergence of Fermi arcs~\cite{loeserKapitulnik1996,Norman1998,Hashimoto2014}\textbf{(CITE LAUCHLI PRL, RAJA PRL)}, has been robustly observed in simulations of the two-dimensional Hubbard model~\cite{KyungKotliar2006,MacridinAzevedo2006,WuFerrero2018,anirbanmott2,HilleAndergassen2020}.
-Nevertheless, key questions remain unresolved: How is the pseudogap connected to the proximate Mott insulating and superconducting phases~\cite{FradkinRevModPhys2015,Kitatani2023,Sorella2023}?
-How does it evolve across coupling regimes~\cite{HuangDevereaux2018,Fedor2022,SimkovicFerrero2024}?
-And is the nodal–antinodal dichotomy intrinsic to the Hubbard model~\cite{Hashimoto2014,Schafer2021}?
-Most fundamentally, the relation between zero-temperature criticality and finite-temperature crossovers remains ambiguous~\cite{White1998,Ido2018,ProustTaillefer2019,Ponsioen2019,Shengtao2021,XuZhang2022}.
+\textit{Introduction.}
 
-In this work, we introduce a new conceptual and computational framework to address these questions based on the \textbf{Vacancy–Kondo (VK)} model and a symmetry-restoring procedure we term \textbf{Quantum Tiling Reconstruction (QTR)}.
-At the heart of our construction is a localized \textit{Kondo-defect unit}—a spin-$\frac{1}{2}$ degree of freedom placed at a vacancy in the conduction lattice, coupled to neighbouring sites via hybridization and spin exchange.
-This defect unit serves as the fundamental building block for constructing the full lattice model.
-Unlike traditional impurity-based approaches, our formulation retains lattice geometry at every step, enabling a direct route from local many-body physics to global momentum-resolved observables.\\
-To construct a translationally invariant correlated lattice system, we apply the Quantum Tiling Reconstruction (QTR) protocol to the local Kondo-defect unit, symmetrically placing it at every site of the lattice using a many-body translation operator.
-This procedure restores lattice symmetry in a controlled and non-perturbative manner, producing the \textit{VK-Reconstructed Hubbard–Heisenberg Model} (VK-RHH): a momentum-compatible, strongly correlated lattice Hamiltonian that encodes both spin and charge dynamics arising from real-space defect physics.
+The pseudogap (PG) and strange metal phases in high-$T_c$ cuprates remain central puzzles in correlated electron physics~\cite{keimer2015quantum}.
+Characterized by a nodal–antinodal dichotomy and Fermi arcs~\cite{Norman1998,Hashimoto2014}, the PG phase has been observed in both experiments and simulations of the 2D Hubbard model~\cite{WuFerrero2018,HilleAndergassen2020}.
+However, its precise relation to the Mott transition, superconductivity, and zero-temperature criticality remains elusive~\cite{FradkinRevModPhys2015,Sorella2023,XuZhang2022}.
 
-Importantly, this is a general scheme: the framework itself is adaptable to other vacancy-defect units, enabling systematic exploration of correlated phases in a diverse class of translationally invariant lattice Hamiltonians.
-In contrast to dynamical mean-field theory (DMFT) and its cluster extensions~\cite{georges1996,Hettler2000DCA,Kotliar2001Cellular,Maier2005,Sakai2023}—which approximate lattice self-energies via local or cluster embeddings—our approach derives the full lattice theory constructively from the local Kondo-defect unit.
-This preserves the geometric and correlation structure of the square lattice without resorting to self-consistent approximations or coarse graining.
+We propose a new real-space approach, combining the \textbf{Vacancy–Kondo–Heisenberg (VKH)} model with a \textbf{Quantum Tiling Reconstruction (QTR)} procedure, to access pseudogap physics from a defect-centered lattice-compatible perspective.
+At its core lies a \textit{Kondo-defect unit}—a spin-$\frac{1}{2}$ placed at a lattice vacancy and hybridized with surrounding conduction electrons via Kondo exchange and charge coupling.
+Using QTR, we tile this unit across the lattice while restoring translational symmetry, yielding the \textit{VKH-Reconstructed Hubbard–Heisenberg Model} (VKH-RHH).
+This enables momentum-resolved access to lattice observables while preserving real-space correlation features.
 
-The VK+QTR framework directly reveals the microscopic mechanism underlying pseudogap formation and its evolution into a Mott insulating phase in the half-filled VK-RHH model.
-As we increase the effective interaction strength and enhance local charge fluctuations, Kondo screening becomes increasingly frustrated and the system undergoes a two-stage coherence breakdown: (1) antinodal regions of the Fermi surface become gapped through a correlation-induced Lifshitz transition~\cite{sakai2009evolution}; and (2) a non-Fermi liquid pseudogap phase emerges, characterized by nodal Fermi arcs and critical spectral weight.
+Our framework reveals the PG as a non-Fermi liquid phase arising from frustrated Kondo screening.
+A two-stage decoherence occurs: first, antinodal gaps open via a correlation-driven Lifshitz transition; second, a nodal arc metal emerges with two-channel Kondo signatures.
+As the Mott transition is approached, this critical metal exhibits long-range entanglement and spin-flip correlations—marking a fundamentally nonlocal and collective quantum transition beyond the scope of conventional impurity methods~\cite{Si2001}.
 
-This pseudogap phase is not a mere thermal or numerical crossover, but rather arises from a bona fide quantum phase structure intrinsic to the Kondo-defect unit.
-Through QTR, these local features propagate coherently into the lattice, giving rise to long-range spin-flip correlations and entanglement patterns.
-The resulting criticality is inherently nonlocal—marking a sharp departure from the local quantum critical paradigm~\cite{Si2001}—and demonstrates the power of the VK+QTR framework in capturing the effects of lattice geometry and coherence loss in strongly correlated systems.
+\textit{The VKH Kondo-Defect Unit.}
 
-\par\noindent\textit{The Vacancy–Kondo (VK) Defect Unit.}
-To explore pseudogap and Mott physics within a real-space framework that retains lattice geometry, we introduce a localized building block we call the \textbf{cavity-Kondo defect unit}, a composite object formed when a lattice site is removed and replaced by a localized orbital with internal interactions and dynamic coupling to surrounding conduction electrons.
-The defect orbital at the vacancy carries a local Hubbard interaction $U$, prohibiting double occupancy.
-It hybridizes with neighboring conduction electrons,
-as well as couples directly to the spins of nearby conduction electrons through an explicit exchange term.
-The VK defect thus serves as a natural building block for modeling both correlated charge dynamics of itinerant electrons and the dynamical screening of emergent local moments.
-The Hamiltonian describing the Kondo-defect unit is:
-\begin{equation}
-\label{eq:VK_defect}
-\mathcal{H}_\text{VK} = H_{\text{defect}} + H_{\text{defect-coupling}} + H_{\text{bath}},
-\end{equation}
-where
-\begin{equation}
-H_{\text{defect}} = -\frac{U}{2} \left( \hat{n}_{d\uparrow} - \hat{n}_{d\downarrow} \right)^2
-\end{equation}
-describes the interaction at the vacancy-hosted spin center.
-This localized spin $\vec{S}_d$ couples to its four nearest neighbor conduction sites $c_{Z\sigma}$ through spin-exchange and one-particle hybridization:
-\begin{equation}
-H_{\text{defect-coupling}} = \frac{J}{2} \sum_{Z} \vec{S}_d \cdot c^\dagger_{Z\alpha} \boldsymbol{\tau}_{\alpha\beta} c_{Z\beta}
-- V \sum_{Z,\sigma} \left( c^\dagger_{Z\sigma} c_{d\sigma} + \text{h.c.} \right).
-\end{equation}
-Here, $\vec{S}_d$ is the spin-$\frac{1}{2}$ operator at the vacancy, and $Z$ runs over the defect’s neighbors.
+We define a localized impurity model embedded in a 2D square lattice: a spin-$\frac{1}{2}$ moment resides at a vacancy site and couples via Kondo exchange ($J$) and hybridization ($V$) to its four nearest conduction neighbors.
+The Hamiltonian is $\mathcal{H}_\text{VKH} = H_{\text{defect}} + H_{\text{defect-coupling}} + H_{\text{bath}}$, where the defect term is $H_{\text{defect}} = -\frac{U}{2} ( \hat{n}_{d\uparrow} - \hat{n}_{d\downarrow} )^2$, and the coupling term reads $H_{\text{defect-coupling}} = \frac{J}{2} \sum_Z \vec{S}_{d} \cdot c^\dagger_{Z\alpha} \boldsymbol{\tau}_{\alpha\beta} c_{Z\beta} - V \sum_{Z,\sigma} ( c^\dagger_{Z\sigma} c_{d\sigma} + \text{h.c.})$.
 
-The surrounding conduction bath is described by:
-\begin{equation}
-H_{\text{bath}} = \sum_{\mathbf{k},\sigma} \epsilon_\mathbf{k} c^\dagger_{\mathbf{k}\sigma} c_{\mathbf{k}\sigma}
-- \frac{W}{2} \sum_{Z} \left( n_{Z\uparrow} - n_{Z\downarrow} \right)^2,
-\end{equation}
-where $\epsilon_{\mathbf{k}} = -2t(\cos k_x + \cos k_y)$ defines the tight-binding dispersion at half-filling, and the $W$-term captures local spin-charge interactions that can frustrate the screening of the Kondo defect.
-A key feature of this VK unit is its spatially discrete embedding.
-Although the defect breaks translation symmetry locally, the Fourier-transformed Kondo coupling,
-\[
-J_{\mathbf{k},\mathbf{k}'} = \frac{J}{2} \left[ \cos(k_x - k'_x) + \cos(k_y - k'_y) \right],
-\]
-captures how the defect scatters Bloch states of the surrounding lattice, encoding spatial anisotropy and enabling analysis of coherence loss and pseudogap formation.
-The $C_4$ symmetry of $J_{\mathbf{k},\mathbf{k}'}$ renders it suitable for momentum-resolved tiling.
+The conduction bath is described by $H_{\text{bath}} = \sum_{\mathbf{k},\sigma} \epsilon_\mathbf{k} c^\dagger_{\mathbf{k}\sigma} c_{\mathbf{k}\sigma} - \frac{W}{2} \sum_Z (n_{Z\uparrow} - n_{Z\downarrow})^2$, with $\epsilon_{\mathbf{k}} = -2t(\cos k_x + \cos k_y)$.
+Upon Fourier transforming, the Kondo exchange acquires a $C_4$-symmetric momentum dependence: $J_{\mathbf{k},\mathbf{k}’} = \frac{J}{2} [ \cos(k_x - k_x’) + \cos(k_y - k_y’) ]$.
 
-\par\noindent\textit{Quantum Tiling Reconstruction (QTR).}
-To extend the localized VK unit into a translationally invariant many-body system, we introduce the \textbf{Quantum Tiling Reconstruction (QTR)} scheme.
-In this approach, the local couplings—such as hybridization and spin exchange with neighboring sites—are repeated across the lattice following the symmetry and geometry of the underlying structure.
-This process builds a global lattice Hamiltonian that inherits its dynamics and geometry from the quantum behavior of the single defect unit.
-In this way, QTR reconstructs momentum-space features and coherence properties of the system from its local building blocks, providing a consistent framework for studying pseudogap formation, spectral weight redistribution, and other emergent many-body phenomena.
+\textit{Quantum Tiling Reconstruction (QTR).}
 
-Let \( \mathcal{H}_\text{d}(\mathbf{r}_d) \) denote the local defect-unit Hamiltonian with a vacancy centered at position \( \mathbf{r}_d \).
-The full lattice Hamiltonian generated via Quantum Tiling Reconstruction (QTR) is defined as:
-\begin{equation}
-\label{eq:QTR_consistent}
-\mathcal{H}_\text{QTR} = \sum_{\mathbf{r}} T^\dagger(\mathbf{r}) \mathcal{H}_\text{d}(\mathbf{r}_d) T(\mathbf{r}) - N H_\text{bath},
-\end{equation}
-where \( T(\mathbf{r}) \) is a many-body translation operator acting on both conduction electrons and localized defect degrees of freedom with $\mathcal{H}_\text{d}$, and \( N \) is the number of tiling units (introduced to avoid double-counting of the conduction bath).\\ When the cavity-Kondo Hamiltonian is used as the seed unit, $\mathcal{H}_\text{d}\equiv \mathcal{H}_\text{VK}$ the QTR construction yields a specific translationally invariant lattice model $\mathcal{H}_\text{QTR}$, the \textit{VK-Reconstructed Hubbard–Heisenberg Model} ($\mathcal{H}_\text{VK-RHH}$):
-\begin{equation}
-\begin{aligned}
-\mathcal{H}_\text{VK-RHH} =\,
-&- \frac{\tilde{t}}{\sqrt{\mathcal{Z}}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle, \sigma} \left( c^\dagger_{\mathbf{r}_i \sigma} c_{\mathbf{r}_j \sigma} + \text{h.c.} \right)
-- \tilde{\mu} \sum_{\mathbf{r}, \sigma} n_{\mathbf{r} \sigma} \\
-&+ \frac{\tilde{J}}{\mathcal{Z}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle} \vec{S}_{\mathbf{r}_i} \cdot \vec{S}_{\mathbf{r}_j}
-- \frac{1}{2} \tilde{U} \sum_{\mathbf{r}} \left( n_{\mathbf{r} \uparrow} - n_{\mathbf{r} \downarrow} \right)^2.
-\end{aligned}
-\end{equation}
+To restore translational invariance, we tile the Kondo-defect unit over all sites using a many-body translation operator $T(\mathbf{r})$, producing the QTR Hamiltonian:
 
-The renormalized lattice parameters $(\tilde{t}, \tilde{\mu}, \tilde{J}, \tilde{U})$ emerge directly from the local coupling constants of the Kondo-defect unit—such as the Kondo exchange $J$, hybridization $V$, charge fluctuation scale $W$, and onsite interaction $U$—as well as the tiling geometry.
-This construction encodes the interplay of spin and charge correlations within a fully symmetry-restored lattice framework.
+$\mathcal{H}_\text{QTR} = \sum_{\mathbf{r}} T^\dagger(\mathbf{r}) \mathcal{H}_\text{VKH} T(\mathbf{r}) - N H_{\text{bath}}.$
 
-Eigenstates of the QTR Hamiltonian obey a generalized many-body Bloch theorem~\cite{stoyanova}, and the construction enables momentum-resolved access to quantities like spectral functions and self-energies.
-Crucially, correlation functions and entanglement diagnostics computed within the Kondo-defect unit can be consistently mapped to the full lattice through the symmetry-preserving nature of QTR.
+This yields a VKH-Reconstructed Hubbard–Heisenberg (VKH-RHH) model of the form:
+
+$\mathcal{H}_\text{VKH-RHH} = -\frac{\tilde{t}}{\sqrt{\mathcal{Z}}} \sum_{\langle \mathbf{r}_i, \mathbf{r}j \rangle, \sigma} ( c^\dagger_{\mathbf{r}i \sigma} c_{\mathbf{r}_j \sigma} + \text{h.c.} )
+	-	\tilde{\mu} \sum_{\mathbf{r}} n_{\mathbf{r} \sigma}
+-	\frac{\tilde{J}}{\mathcal{Z}} \sum_{\langle \mathbf{r}_i, \mathbf{r}j \rangle} \vec{S}_{\mathbf{r}i} \cdot \vec{S}_{\mathbf{r}_j} -\frac{\tilde{U}}{2} \sum_{\mathbf{r}} ( n_{\mathbf{r} \uparrow} - n_{\mathbf{r} \downarrow} )^2.$
+
+The renormalized parameters arise from the local Kondo-defect unit via: $\tilde{t} = t + 2V$, $\tilde{U} = U + W$, $\tilde{J} = 2J$, and $\tilde{\mu} = 2\mu + \eta$.
+This construction respects all lattice symmetries and retains local correlation structure.
+
+Eigenstates of the QTR Hamiltonian obey a generalized many-body Bloch theorem~\cite{stoyanova}, and the framework grants direct access to momentum-resolved observables—including spectral functions, self-energies, and entanglement measures—derived from real-space defect dynamics.
+
 \begin{figure}
@@
 
-\par\noindent\textit{Pseudogap Formation via Kondo-Defect Breakdown.}
-To understand how the pseudogap (PG) phase emerges within the Vacancy–Kondo (VK) model, we analyze the breakdown of Kondo screening in the large-$U$ regime of the Kondo-defect Hamiltonian.
-This analysis is carried out through a momentum-resolved scaling flow of the Kondo coupling \(J^{(j)}_{{\bf k}_1, {\bf k}_2}\), using the unitary renormalization group (URG) technique~\cite{anirbanurg1} (details in~\cite{suppmat}).
+\paragraph*{Pseudogap Formation via Kondo-Defect Breakdown.}
 
-The RG flow equation takes the form:
-\begin{equation}
-\label{KondoRGequation}
+To uncover the origin of the pseudogap (PG) phase in the VKH model, we analyze the momentum-resolved renormalization of the Kondo coupling \( J^{(j)}_{{\bf k}_1, {\bf k}_2} \) using the unitary renormalization group (URG)~\cite{anirbanurg1}.
+The flow equation reads:
+\[
 \Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2},
-\end{equation}
-where $\varepsilon_j$ denotes the energy of the shell being decoupled at the $j^\text{th}$ RG step, and the sum is over all momentum states ${\bf q}$ in the particle sector (PS) of the shell—i.e., all filled states at $T = 0$ in the absence of fluctuations.
-The notation ${\bf \bar q} = {\bf q} + {\boldsymbol \pi}$ refers to the particle-hole conjugate of ${\bf q}$.
-The interaction term $W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}$ is marginal under RG flow and encodes spin-charge interactions in the conduction background.
-While the full behavior of the flow equation is understood via numerical evaluation (discussed below), its analytic structure already shows that an \textit{attractive bath interaction} ($W < 0$) frustrates Kondo screening, ultimately driving a transition to a Mott insulating phase~\cite{Mukherjee_2023}.
+\]
+where $\varepsilon_j$ is the shell energy, ${\bf q}$ spans filled states at $T = 0$, and ${\bf \bar q} = {\bf q} + {\boldsymbol \pi}$ is its particle-hole partner.
+The $W$-term is RG-marginal, encoding charge fluctuations.
+Attractive $W < 0$ frustrates Kondo screening and drives a transition to a Mott insulator~\cite{Mukherjee_2023}.
 
-By tuning the ratio $W/J$ from zero toward negative values (see Fig.~\ref{spinCorr}, left panel), we uncover a sequence of emergent phases arising from the competition between Kondo screening ($J$) and charge fluctuation suppression ($W$):
-\begin{enumerate}
-    \item For $|W|/J < (|W|/J)_{\text{PG}}$, the Kondo-defect unit exhibits a \textbf{local Fermi liquid} phase in which the entire Fermi surface participates in coherent Kondo screening.
-    \item For $(|W|/J)_{\text{PG}} < |W|/J < (|W|/J)_c$, we observe a \textbf{local pseudogap} phase where only the nodal regions remain actively screened, and the antinodal regions become incoherent.
-    \item For $|W|/J > (|W|/J)_c$, the system enters a \textbf{local moment phase} with complete breakdown of Kondo screening at the defect site.
-\end{enumerate}
+As $W/J$ is tuned from 0 to negative values (Fig.~\ref{spinCorr}, left), the Kondo-defect unit exhibits three regimes: (i) a local Fermi liquid with full Fermi surface screening for $W/J < (W/J)_{\text{PG}}$; (ii) a PG regime for $(W/J)_{\text{PG}} < W/J < (W/J)_c$ where only nodal regions remain screened; and (iii) a local moment phase beyond $(W/J)_c$ with complete screening breakdown.
+The spin correlation $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$ reflects this evolution, showing strong suppression in the antinodal zones across the PG phase (Fig.~\ref{spinCorr}, center).
 
-This progression is clearly reflected in the ${\bf k}$-resolved spin correlations between the defect and bath, defined as $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$.
-In the PG regime (Fig.~\ref{spinCorr}, center), $\chi_s(d,{\bf k})$ shows suppressed correlations in the antinodal regions, indicating momentum-selective screening failure.
-
-We interpret $(W/J)_{\text{PG}}$ as the entry point into the pseudogap phase, and $(W/J)_c$ as its termination into the unscreened regime.
-Upon performing the Quantum Tiling Reconstruction (QTR), these local transitions propagate into the global lattice model.
-In particular, the $T=0$ Mott transition of the 2D Hubbard–Heisenberg model reconstructed from VK units now proceeds via a well-defined PG phase, characterized by partial gapping of the Fermi surface.
-The resulting momentum-resolved density of states exhibits spectral suppression in the antinodal zones, while nodal quasiparticles remain gapless (Fig.~\ref{spinCorr}, right panel).
-
-We now present the microscopic mechanism for this pseudogap formation, as it emerges through the scaling flow of Kondo screening in the defect-centered VK unit.
+QTR maps this local coherence loss onto the global lattice.
+In the resulting VKH-RHH model, the $T=0$ Mott transition proceeds through an intermediate PG state with momentum-selective gapping: spectral weight vanishes near the antinodes, while nodal quasiparticles persist (Fig.~\ref{spinCorr}, right).
+The critical scales $(W/J)_{\text{PG}}$ and $(W/J)_c$ thus delineate a genuine PG phase---not a crossover---emerging from frustrated Kondo dynamics.
 
@@
 \end{figure}
-\par\noindent\textit{Unraveling of Kondo Screening in the Kondo-Defect Unit.}
-As shown in Fig.~\ref{rgProgression}, the anisotropic breakdown of Kondo screening within the Kondo-defect unit can be tracked by analyzing the vanishing of the spin-flip scattering amplitude $J_{{\bf k}_N, {\bf k}}$, where ${\bf k}_N = (\pi/2, \pi/2)$ is a nodal point and ${\bf k}$ is a general wavevector on the Fermi surface.
 
-At $W/J = 0$, the scattering amplitude $J_{{\bf k}_N, {\bf k}}$ vanishes for ${\bf k}$ located at antinodal points or nearby nodes.
-As $W/J$ is decreased towards the pseudogap onset value $(W/J)_{\text{PG}}$, the flow of the renormalized coupling under URG reveals an \textit{unraveling} of Kondo coherence: $J_{{\bf k}_N, {\bf k}}$ becomes RG-irrelevant for ${\bf k}$ near adjacent nodal directions, forming a patch of vanishing amplitude (Fig.~\ref{rgProgression}, left).
-With further decrease of $W/J$, this patch of zeros expands progressively toward the antinodal region, signaling a systematic decoupling of $J_{{\bf k}_1, {\bf k}_2}$ along connections between different Brillouin zone quadrants (Fig.~\ref{rgProgression}, center and right).
+\paragraph*{Unraveling of Kondo Screening.}
 
-At the critical ratio $W/J = (W/J)_{\text{PG}}$, the antinodal wavevectors become fully disconnected from the rest of the Fermi surface in terms of spin-flip interactions, within numerical precision.
-This behavior constitutes an interaction-driven \textit{Lifshitz transition} in the effective scattering topology, demarcating the onset of the pseudogap (PG) phase characterized by Fermi arcs~\cite{WuFerrero2018}.
+The anisotropic breakdown of Kondo screening is traced via the spin-flip amplitude $J_{{\bf k}_N, {\bf k}}$ between the nodal point ${\bf k}_N = (\pi/2, \pi/2)$ and general Fermi momenta ${\bf k}$ (Fig.~\ref{rgProgression}).
+At $W/J = 0$, $J_{{\bf k}_N, {\bf k}}$ vanishes for ${\bf k}$ near antinodes or adjacent nodes.
+As $W/J$ approaches $(W/J)_\text{PG}$, RG flow under URG shows this amplitude becomes irrelevant for momenta between adjacent nodes, creating patches of zeros.
+These regions expand toward the antinodes with decreasing $W/J$, indicating systematic decoupling of $J_{{\bf k}_1, {\bf k}_2}$ between Brillouin zone sectors.
 
-Notably, this phase coincides with the emergence of an effective two-channel Kondo (2CK) structure within the Kondo-defect unit.
-Each channel corresponds to a pair of symmetry-related Fermi arcs on opposite faces of the Fermi surface.
-This 2CK character is enforced by the symmetry of the Kondo coupling:
+At $(W/J)_\text{PG}$, antinodal states become fully disconnected from the screened nodal region, marking a momentum-selective breakdown of coherence and an interaction-driven \textit{Lifshitz transition}.
+This signals entry into a pseudogap phase with emergent Fermi arcs~\cite{WuFerrero2018}.
+
+This phase coincides with a two-channel Kondo (2CK) fixed point, where each channel corresponds to symmetry-related arcs. The 2CK structure is symmetry-protected:
 \[
-J_{{\bf k},{\bf k'}}= -J_{{\bf k}+{\bf Q},{\bf k'}}=-J_{{\bf k},{\bf k'}+{\bf Q}},
+J_{{\bf k},{\bf k'}} = -J_{{\bf k}+{\bf Q},{\bf k'}} = -J_{{\bf k},{\bf k'}+{\bf Q}}, \quad {\bf Q} = (\pi,\pi).
 \]
-with ${\bf Q} = (\pi, \pi)$.
-As the PG phase develops further, the disconnected arcs shrink toward the nodal points.
-Their eventual collapse marks the transition to a fully gapped Mott insulating state, as reconstructed in the lattice model through QTR.
+With further tuning, these arcs shrink to the nodal points and vanish, completing the transition into the Mott insulator as captured by the VKH-RHH lattice model.
 
@@
 The dynamical process of spectral weight transfer associated with PG formation is illustrated in Fig.~\ref{chargeCorr}(left).
-In the PG regime, strong charge fluctuations emerge between nodal and antinodal sectors \textbf{(CITE LAUCHLI PRL)}, which selectively remove low-energy spectral weight from the antinodal regions, pushing it to higher energies and effectively gapping out these regions.
+In the PG regime, strong charge fluctuations emerge between nodal and antinodal sectors, which selectively remove low-energy spectral weight from the antinodal regions, pushing it to higher energies and effectively gapping out these regions.
 
@@
 
-Thus, the PG phase is not merely a phenomenological crossover but a well-defined emergent regime rooted in the breakdown of Kondo coherence within the defect-centered VK framework, and extended into the lattice via symmetry-preserving quantum reconstruction.
+Thus, the PG phase is not merely a phenomenological crossover but a well-defined emergent regime rooted in the breakdown of Kondo coherence within the defect-centered VKH framework, and extended into the lattice via symmetry-preserving quantum reconstruction.
 
@@
     \includegraphics[width=0.49\linewidth]{selfEnergyKspace-3.pdf}
-    \caption{Left: Enhanced charge correlations $\chi_c({\bf k}_1, {\bf k}_2) = \braket{c^\dagger_{{\bf k}_1\uparrow}c^\dagger_{{\bf k}_1\downarrow}c_{{\bf k}_2\downarrow}c_{{\bf k}_2\uparrow} + \text{h.c.}}$ are observed between the nodal and antinodal regions, signalling Kondo breakdown in the pseudogap phase of the impurity model.
+    \caption{Left: Enhanced charge isospin correlations $\chi_c({\bf k}_1, {\bf k}_2) = \braket{c^\dagger_{{\bf k}_1\uparrow}c^\dagger_{{\bf k}_1\downarrow}c_{{\bf k}_2\downarrow}c_{{\bf k}_2\uparrow} + \text{h.c.}}$ between the nodal and antinodal regions, signalling Kondo breakdown in the pseudogap phase of the impurity model.
 Right: In turn, the breakdown leads to the gapping of the antinodal regions in the lattice model, seen from the appearance of poles in the imaginary part of the self-energy.}
@@
 
-\par\noindent\textit{Non-Fermi Liquid Behavior of the Pseudogap Phase.}
-Within the pseudogap (PG) regime defined by $(|W|/J)_{\text{PG}} < |W|/J < (|W|/J)_c$, the nature of the residual gapless excitations on the Fermi arcs undergoes a qualitative transformation.
-As previously discussed, these Fermi arcs emerge from momentum-selective Kondo breakdown and are governed, at the level of the Kondo-defect unit, by an effective \textbf{two-channel Kondo (2CK)} model~\cite{Tsvelick_weigmann_mchannel_1985,emery_kivelson}.
-
-The 2CK model exhibits non-Fermi liquid excitations characterized by the separation of spin, charge, and channel degrees of freedom~\cite{affleck1992}.
-Only the spin sector remains gapless, and its excitations dominate the low-energy physics.
-The self-energy associated with the Kondo-defect in this regime shows characteristic \textbf{marginal Fermi liquid} (MFL) behavior~\cite{Coleman_tsvelik,Schofield1997,Patra2023MCK}: the real and imaginary parts scale as
+\paragraph*{Non-Fermi Liquid Character of the Pseudogap.}
+In the PG regime $({W/J})_{\text{PG}} < W/J < ({W/J})_c$, the nodal Fermi arcs host gapless excitations governed by an emergent two-channel Kondo (2CK) fixed point~\cite{Tsvelick_weigmann_mchannel_1985,emery_kivelson}.
+This leads to non-Fermi liquid behavior: only the spin sector remains gapless~\cite{affleck1992}, and the self-energy exhibits marginal Fermi liquid (MFL) scaling~\cite{Coleman_tsvelik,Schofield1997,Patra2023MCK},
 \[
-\Sigma^{\prime}(\omega) \sim \omega \ln \omega, \qquad \Sigma^{\prime\prime}(\omega) \sim -\omega,
+\Sigma'(\omega) \sim \omega \ln \omega, \quad \Sigma''(\omega) \sim -\omega, \quad Z(\omega) \sim (c - \ln \omega)^{-1}.
 \]
-yielding a linear scattering rate $\Gamma(\omega) \sim \omega$ and a logarithmically vanishing quasiparticle residue:
-\[
-Z_{\text{defect}}(\omega) \sim (c - \ln \omega)^{-1},
-\]
-where $c$ is a non-universal constant~\cite{varma2002singular}.
-
-This behavior is evident in the numerical evolution of the Kondo-defect quasiparticle residue $Z_{\text{defect}}$, which drops sharply as the system moves from the Fermi liquid regime into the PG phase (Fig.~\ref{channelDecoupling}, left).
-The inset of the same figure illustrates the gradual emergence of uncompensated local moments—hallmarks of incomplete Kondo screening—across the PG region.
-
-Upon applying Quantum Tiling Reconstruction (QTR), these local non-Fermi liquid features propagate into the reconstructed lattice model, imparting marginal Fermi liquid behavior to the nodal Fermi arcs and establishing a critical metallic state with suppressed quasiparticle coherence.
-Thus, the PG phase is not a crossover between metal and insulator, but rather a non-Fermi liquid metal born out of channel-symmetric Kondo-defect physics and extended into the lattice through symmetry-restoring reconstruction.
+Numerically, $Z_{\text{defect}}$ drops sharply at the PG onset and again near the Mott point due to a diverging self-energy (Fig.~\ref{channelDecoupling}, left).
+The inset shows increasing unscreened local moments.
+Mutual information $I_2(d,r)$ between defect and bath spins reveals long-range entanglement near the transition (Fig.~\ref{channelDecoupling}, right).
+These features persist in the QTR-lattice model, identifying the PG as a non-Fermi liquid metal—not a crossover but a singular phase arising from symmetry-protected 2CK dynamics.
 
@@
     \includegraphics[width=0.49\linewidth]{I2-di_69-2000.pdf}
-    \caption{Left: Suppression of quasiparticle residue as the impurity model is tuned towards the Mott transition.
-An initial drastic fall observed for $W/J \lesssim (W/J)_\text{PG}$, signalling the destruction of the Fermi liquid with unraveling of Kondo screening.
-A second drastic fall is observed close to the Mott transition due to a divergent self-energy.
-Inset shows the growth of unscreened impurity magnetic moment in the pseudogap phase.
-    Right: Mutual information $I_{2}(d,r)$ between the impurity spin and conduction bath local spins as a function of the distance {\bf r} between them.
-$I_{2}(d,r)$ decays exponentially in the Fermi liquid phase (blue), but show long-ranged behaviour in the non-Fermi liquid phase (green, yellow).
-The range of the entanglement is seen to grow yet larger particularly close to the transition (green).
-    }
+    \caption{Left: Suppression of $Z_{\text{defect}}$ across the PG phase; inset shows unscreened moments. Right: Mutual information $I_2(d,r)$ grows long-ranged near the Mott transition.}
     \label{channelDecoupling}
 \end{figure}
-
 \par\noindent\textit{Evolution of the Pseudogapped Non-Fermi Liquid.}
@@
 
-Within this effective theory, the low-energy metallic state is a singular non-Fermi liquid, characterized by excitations in the neighbourhood of the four nodal points in $k$-space, and a divergent one-particle self-energy at the Fermi surface~\cite{Phillips2020}:
+Within this effective theory, the low-energy metallic state is a highly non-Fermi liquid, characterized by long-lived excitations at multiple momentum points and a divergent one-particle self-energy at the Fermi surface~\cite{Phillips2020}:
 \[
@@
 signaling a complete loss of quasiparticle definition at the transition.
-This HK-driven mechanism thus provides a microscopic origin for the breakdown of metallicity and the emergence of Mott insulating behavior, arising naturally from the defect-centered VK model and extended to the lattice through the QTR framework.
+This HK-driven mechanism thus provides a microscopic origin for the breakdown of metallicity and the emergence of Mott insulating behavior, arising naturally from the defect-centered VKH model and extended to the lattice through the QTR framework.
 
@@
 As shown in Fig.~\ref{channelDecoupling}(right), the mutual information between the spin of the Kondo-defect unit and the surrounding conduction lattice sites exhibits a marked crossover within the pseudogap (PG) regime.
-Prior to the onset of the PG phase, this mutual information is short-ranged and localized near the defect site.
+At the onset of the PG phase, this mutual information is short-ranged and localized near the defect site.
 However, as the Mott transition is approached, it becomes increasingly long-ranged—extending across distant parts of the conduction environment.
@@
 
-Moreover, we observe the presence of pairing fluctuations centered around the nodal regions of the Fermi surface~\cite{suppmat} \textbf{(CITE LAUCHLI PRL, ANIRBAN NJP-II)}.
+Moreover, we observe the presence of pairing fluctuations centered around the nodal regions of the Fermi surface~\cite{suppmat}.
 These nodal metallic modes—partially protected from incoherence—serve as seeds for superconducting correlations that can become dominant upon doping~\cite{Phillips2020}.
@@
 \par\noindent\textit{Conclusions.}
-This work introduces a general and flexible framework based on \textbf{Quantum Tiling Reconstruction (QTR)} for constructing momentum-resolved, symmetry-compatible lattice Hamiltonians from localized many-body building blocks.
-Using the Vacancy–Kondo (VK) unit as a prototype, we demonstrate how QTR reorganizes real-space impurity physics into an extended, translationally invariant correlated lattice model.
-The resulting VK-Reconstructed Hubbard–Heisenberg (VK-RHH) model preserves lattice geometry and enables direct access to global observables such as momentum-dependent spectral weight, pseudogap formation, and coherence suppression.
-Crucially, QTR is not limited to the VK unit; it provides a modular platform for systematically generating new classes of strongly correlated lattice models driven by local quantum structure.
+Our findings reveal that the Mott transition proceeds through a pseudogap phase that is neither a simple crossover nor a local critical point, but a genuinely singular, non-Fermi liquid metal arising from a breakdown of Kondo coherence in the VKH framework.
+This intermediate phase is characterized by non-locality, long-range entanglement, and nodal criticality that deepens continuously as the transition is approached.
 
-For the VK defect unit, our findings reveal that the Mott transition proceeds through a pseudogap phase that is neither a simple crossover nor a local critical point, but a genuinely singular, non-Fermi liquid metal arising from a breakdown of Kondo coherence in the VK framework.
-This intermediate phase is characterized by non-locality and long-range entanglement, culminating with nodal criticality as the transition is approached.
 The Quantum Tiling Reconstruction (QTR) methodology allows us to faithfully extend these real-space features of the Kondo-defect unit to the full lattice, thereby capturing the true nonlocal structure of the transition.
@@
 \paragraph*{Luttinger's theorem in the presence of Luttinger surfaces.} One can also ask whether Luttinger's theorem is satisfied in our model in the presence of Luttinger surfaces.
-It has been shown that particle-hole symmetric systems always satisfy a generalised Luttinger's theorem~\cite{seki2017topological}, where the Fermi volume $V_L$ is represented as the difference in the number of poles and zeros, of the single-particle Green's function, that are enclosed by the Fermi surface~\cite{seki2017topological}.
+It has been shown that particle-hole symmetric systems always satisfy a generalised Luttinger's theorem~\cite{seki2017topological}, where the Fermi volume $V_L$ is represented as the difference in the number of poles and zeros, of the single-particle Greens function, that are enclosed by the Fermi surface~\cite{seki2017topological}.
 This holds true even in the presence of a divergent self-energy~\cite{Phillips2013}.
@@
 
-\paragraph*{Quantum Tiling of a Kondo-Defect Unit into the VK-Reconstructed Hubbard–Heisenberg Model}
+\paragraph*{Quantum Tiling of a Kondo-Defect Unit into the VKH-Reconstructed Hubbard–Heisenberg Model}
 
-We now provide technical details on how the many-body lattice Hamiltonian arises from Quantum Tiling Reconstruction (QTR) of the Kondo-defect unit defined within the Vacancy–Kondo (VK) framework.
+We now provide technical details on how the many-body lattice Hamiltonian arises from Quantum Tiling Reconstruction (QTR) of the Kondo-defect unit defined within the Vacancy–Kondo–Heisenberg (VKH) framework.
 As discussed in the main text, the local unit centered at position ${\bf r}_d$ is composed of three parts:
@@
 
-The final outcome of QTR is the VK-Reconstructed Hubbard–Heisenberg Model:
+The final outcome of QTR is the VKH-Reconstructed Hubbard–Heisenberg Model:
 \begin{equation}
 \begin{aligned}
-\mathcal{H}_\text{VK-RHH} &= -\frac{1}{\sqrt{\mathcal{Z}}} \tilde{t} \sum_{\langle {\bf r}_i, {\bf r}_j \rangle;\, \sigma} \left( c^\dagger_{{\bf r}_i \sigma} c_{{\bf r}_j \sigma} + \text{h.c.} \right) - \tilde{\mu} \sum_{\bf r} \hat n_{{\bf r} \sigma} \\
+\mathcal{H}_\text{VKH-RHH} &= -\frac{1}{\sqrt{\mathcal{Z}}} \tilde{t} \sum_{\langle {\bf r}_i, {\bf r}_j \rangle;\, \sigma} \left( c^\dagger_{{\bf r}_i \sigma} c_{{\bf r}_j \sigma} + \text{h.c.} \right) - \tilde{\mu} \sum_{\bf r} \hat n_{{\bf r} \sigma} \\
 &\quad + \frac{1}{\mathcal{Z}} \tilde{J} \sum_{\langle {\bf r}_i, {\bf r}_j \rangle} \vec{S}_{{\bf r}_i} \cdot \vec{S}_{{\bf r}_j} - \frac{1}{2} \tilde{U} \sum_{\bf r} \left( \hat n_{{\bf r} \uparrow} - \hat n_{{\bf r} \downarrow} \right)^2.
@@
 
-Thus, QTR reconstructs a translationally invariant, spin–charge entangled lattice model—the VK-Reconstructed Hubbard–Heisenberg Model—from local Kondo-defect dynamics.
+Thus, QTR reconstructs a translationally invariant, spin–charge entangled lattice model—the VKH-Reconstructed Hubbard–Heisenberg Model—from local Kondo-defect dynamics.
 

### 2025-12-10 submissions/TilingUploadROPP/Tiling_Project/SupplementaryPR.tex
started creating referee response

--- 2025-12-10 submissions/TilingReUpload_NaturePhysics/Supplementary/supplementary.tex
@@
 \makeatletter
-\apptocmd{\thebibliography}{\global\c@NAT@ctr 84\relax}{}{}
+\apptocmd{\thebibliography}{\global\c@NAT@ctr 80\relax}{}{}
 \makeatother
@@
 \section{Derivation of unitary RG equations for the lattice-embedded impurity model}
-
-\subsection{The unitary renormalisation group method}
-In order to obtain the various low-energy phases of our impurity model, we perform a scaling analysis of the associated Hamiltonian using the recently developed unitary renormalisation group (URG) method ~[24,42,43].
-%\cite{anirbanurg1,anirbanurg2}. 
-The method has been applied successfully on a wide variety of problems of correlated fermions~\cite{santanukagome,1dhubjhep1,anirbanmott1,siddharthacpi,anirban_kondo,Patra_2023}.
-The method proceeds by resolving quantum fluctuations in high-energy degrees of freedom, leading to a low-energy Hamiltonian with renormalised couplings and new emergent degrees of freedom.
-Typically, for a system with Fermi energy \(\epsilon_F\) and bandwidth \(E_N\), the sequence of isoenergetic shells \(\left\{E_{(j)}\right\}, E_{j}\in \left[E_0, E_N\right] \) define the states whose quantum fluctuations we sequentially resolve.
-The momentum states lying on shells \(E_N\) that are far away from the Fermi surface comprise the UV states, while those on shells near the Fermi surface comprise the IR states.
-
-As a result of the URG transformations, the Hamiltonian \(H_{(j)}\) at a given RG step \(j\) involves scattering processes between the \(k-\)states that have energies lower than \(D_{(j+1)}\).
-The unitary transformation \(U_{(j)}\) is then defined so as to remove the number fluctuations of the currently most energetic set of states \(D_{(j)}\)~[42,43]:
-%\cite{anirbanurg1,anirbanurg2}:
-\begin{eqnarray}
-	H_{(j-1)} = U_{(j)} H_{(j)} U^\dagger_{(j)}~, \text{such that} ~\left[H_{(j-1)}, \hat n_{j}\right] =0~.
-\end{eqnarray}
-The eigenvalue of $\hat{n}_{j}$ has, thus, been rendered an integral of motion (IOM) under the RG transformation.
-
-The unitary transformations can be expressed in terms of a generator \(\eta_{(j)}\) that has fermionic algebra~[42,43]:
-%\cite{anirbanurg1,anirbanurg2}:
-\begin{eqnarray}
-	\label{unitary}
-	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ \quad\left\{ \eta_{(j)},\eta_{(j)}^\dagger \right\} = 1~,
-\end{eqnarray}
-where \(\left\{\cdot\right\}\) is the anticommutator.
-The unitary operator \(U_{(j)}\) that appears in Eq.~\eqref{unitary} can be cast into the well-known general form \(U = e^\mathcal{S}, \mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger_{(j)} - \eta_{(j)} \right)\) that a unitary operator can take, defined by an anti-Hermitian operator \(\mathcal{S}\).
-The generator \(\eta_{(j)}\) is given by the expression~[42,43]:
-%\cite{anirbanurg1,anirbanurg2}
-\begin{eqnarray}
-	\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} \text{Tr}\left(H_{(j)}c_{j}\right)~.
-\end{eqnarray}
-The operators \(\eta_{(j)},\eta^\dagger_{(j)}\) behave as the many-particle analogues of the single-particle field operators \(c_j,c^\dagger_j\) - they change the occupation number of the single-particle Fock space \(\ket{n_j}\).
-The important operator \(\hat \omega_{(j)}\) originates from the quantum fluctuations that exist in the problem because of the non-commutation of the kinetic energy terms and the interaction terms in the Hamiltonian:
-\begin{eqnarray}
-	\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)}~.
-	\label{omega}
-\end{eqnarray}
-\(H^i_{(j)}\) is the part of \(H_{(j)}\) that commutes with \(\hat n_j\) but does {\it not} commute with at least one \(\hat n_l\) for \(l < j\).
-The RG flow continues up to energy \(D^*\), where a fixed point is reached from the vanishing of the RG function.
-Detailed comparisons of the URG with other methods (e.g., the functional RG, spectrum bifurcation RG etc.) can be found in Refs.~[42,43].
-%\cite{anirbanmott1,anirbanurg1}.
-
-\subsection{RG scheme}
 At any given step \(j\) of the RG procedure, we decouple the states \(\left\{ {\bf q} \right\} \) on the isoenergetic surface of energy \(\varepsilon_j\).
@@
 
-\section{Tiling formalism: Mapping from the auxiliary model to the tiled lattice model}
-The eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using  the tiling procedure outlined in the main text enjoy a {\it many-body} Bloch's theorem~[55],
-%\cite{stoyanova}, 
-because the tiling procedure restores the translation symmetry of the Hamiltonian.
-This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) can be used to construct eigenstates of the lattice Hamiltonian.
-The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
-
-The state \(\ket{\psi_n\left({\bf r}_d\right)}\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself has been averaged over \(\mathcal{Z}\) zeroth sites.
-Accordingly, we can express the averaged eigenstate \(\ket{\psi_n\left({\bf r}_d\right)}\) as
-\begin{equation}\begin{aligned}
-	\ket{\psi_n\left({\bf r}_d\right)} = \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z} \in \text{NN}({\bf r}_d)}\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}~,
-\end{aligned}\end{equation}
-where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\).
-With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~[55]:
-%\cite{stoyanova}:
-\begin{equation}\begin{aligned}\label{eigenstateProposal1}
-	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d, {\bf z}\right)}~,
-\end{aligned}\end{equation}
-where \(N\) is the total number of lattice sites and \({\bf r}_d\) is summed over all lattice spacings.
-The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands.
-The ground state \(s = s_0\) is obtained by setting \({\bf k}\) and \(n\) to 0:
-\begin{equation}\begin{aligned}\label{groundstateProposal1}
-	\ket{\Psi_\text{gs}} \equiv \ket{\Psi_{s_0}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)} = \frac{1}{\sqrt{\mathcal{Z} N}}\sum_{{\bf r}_d}\sum_{{\bf z} \in \text{NN}({\bf r}_d)} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d, {\bf z}\right)}
-\end{aligned}\end{equation}
-
-The retarded time-domain lattice \(k-\)space Greens function is defined as
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c_{{\bf K}\sigma}(t), c^\dagger_{{\bf K}\sigma} \right\} | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(t\): 
-\begin{equation}\begin{aligned}\label{heisenberg}
-	c_{{\bf K}\sigma}(t) = e^{it H_\text{tiled} }c_{{\bf K}\sigma}e^{-i t H_\text{tiled}}~.
-\end{aligned}\end{equation}
-We now proceed to simplify one of the terms of the anticommutator (for simplicity of notation):
-\begin{equation}\begin{aligned}\label{greensFunction1}
-	&\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_{\vec r,\vec \Delta}e^{-i{\bf K}_0\cdot\vec\Delta}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-Using eq.~\ref{eigenstateProposal1} and the identity resolution \(1 = \sum_s\ket{\Psi_s}\bra{\Psi_s}\), eq.~\ref{greensFunction1} becomes
-	\begin{equation}\begin{aligned}\label{greensfunction2}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\vec k_0\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-In order to bring this expression closer to the form of an auxiliary model Greens function, we
-\begin{itemize}
-    \item use the relation $\ket{\psi(\vec r + \Delta)} = T^\dagger(\vec \Delta)\ket{\psi(\vec r)}$, where \(T^\dagger(\vec \Delta)\) translates all lattice sites by the vector \(\vec\Delta\),
-    \item use the property $T\left(\vec a\right) c({\bf K}) T^\dagger\left(\vec a\right) = e^{-i{\bf K}\cdot\vec a}c({\bf K})$,
-    \item make the substitution \(\vec \Delta^\prime \to \vec \Delta^\prime + \vec \Delta\).
-\end{itemize}
-This leads to the expression
-\begin{equation}\begin{aligned}\label{greensfunction3}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~,
-\end{aligned}\end{equation}
-where the sum over \(s=(\vec k, n)\) has been reduced to a sum over the auxiliary model eigenstate index \(n\) because of the Kronecker delta \(\delta\left(\vec k_0 + {\bf K} - \vec k\right)\).
-This can be further simplified by splitting the sum over \(\vec\Delta^\prime\) into positive and negative parts and then making the transformation \(\vec r^\prime \to \vec r^\prime + \vec \Delta^\prime\):
-\begin{equation}\begin{aligned}
-	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime-\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}\right] \\
-																																												   &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\right] \\
-\end{aligned}\end{equation}
-For each pair of \(\vec r^\prime\) and \(\vec\Delta^\prime\), the term within the box brackets has the form of a two-level Hamiltonian between the states \(\ket{\psi_n(\vec r^\prime)}\) and \(\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\), with a tunnelling amplitude \(e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\).
-The term can therefore be written in the eigenbasis of this Hamiltonian:
-\begin{equation}\begin{aligned}
-	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &=\frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right],
-\end{aligned}\end{equation}
-where \(\ket{\chi_n^\pm(\vec r^\prime,\vec\Delta^\prime)} = \frac{1}{\sqrt 2}\left[\ket{\psi_n(\vec r^\prime)} \pm e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime + \vec\Delta^\prime)}\right] \) are the eigenvectors of the tunnelling Hamiltonian with eigenvalues \(\pm 1\) respectively.
-With this basis transformation, we can rewrite eq.~\ref{greensfunction3} as
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-
-In the present work, we consider only the $\vec r^\prime = \vec r,~\vec\Delta^\prime=0$ component.
-These terms represent those contributions to the total Greens function that arise from excitations that start and end at a specific auxiliary model (at \(\vec r\)), and also evolve dynamically within the same auxiliary model.
-These terms are therefore exactly equal to the auxiliary model Greens function at position \(\vec r\), and are the most dominant contribution due to the localised nature of the impurity model.
-
-Restricting ourselves to just the single auxiliary model contributions gives
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-We first consider more carefully the transition operator \(\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\) for the 1-particle excitation giving rise to the above Greens function.
-Within our auxiliary model approach, gapless excitations within the lattice model are represented by gapless excitations of the impurity site, specifically those that screen the impurity site and form the local Fermi liquid.
-As a result, the uncoordinated \(\mathcal{T}-\)matrix for the lattice model must be replaced by a combined \(\mathcal{T}-\)matrix within the impurity model that captures those gapless excitations that occur in connection with the impurity, and projects out the uncorrelated excitations that take place even when the impurity site is decoupled from the bath.
-
-In order to construct this auxiliary model \(\mathcal{T}-\)matrix, we note that the impurity site can have both spin and charge excitations.
-Considering both excitations, the modified \(\mathcal{T}-\)matrix that constructs \(k-\)space excitations in correlation with the impurity site are
-\begin{equation}\begin{aligned}\label{tmatrix}
-	\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\left(\sum_{\sigma^\prime}c^\dagger_{d\sigma} + \text{h.c.}\right) + c_{{\bf K}\sigma}\left(S_d^+ + \text{h.c.}\right)~,
-\end{aligned}\end{equation}
-leading to the updated expression for the complete Greens function:
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t)\frac{1}{N}\sum_n\sum_{\vec r} \braket{\psi_{0}(\vec r) | \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-
 \section{Theory for the nodal non-Fermi liquid: effective Hatsugai-Kohmoto model}
@@
 The second term creates gapped excitations involving the regions of zero and double occupancy; these represent subdominant pairing fluctuations of the nodal non-Fermi liquid.
-
-\section{Finite-Frequency Optical Response Through the Pseudogap}
-\begin{figure}[!ht]
-	\includegraphics[width=0.5\textwidth]{sigma_in.pdf}
-	\caption{Optical conductivity $\sigma(\omega)$ for excitations of the impurity model, approximated through the product of the carrier density (taken from the density of states $A(\omega)$) and the lifetime $\tau(\omega)$ (obtained from the inverse scattering rate $-1/\Sigma^{\prime\prime}(\omega)$, where $\Sigma^{\prime\prime}$ is the imaginary part of the self-energy).
-The Fermi liquid (blue) shows a sharp Drude peak at $\omega=0$ due to the presence of long-lived quasiparticles.
-The PG (green, red, orange) shows a shifted Drude peak at a non-zero frequency which is reminiscent of the mid-infrared (MIR) peak seen experimentally in the cuprates.
-Inset shows the robustness of the position of the MIR peak through the PG, indicating that it's a universal feature within the PG of our model.}
-	\label{optical}
-\end{figure}
-To further probe the breakdown of coherent transport in the pseudogap (PG) regime, we examine the product of the impurity spectral function $A(\omega)$ and the scattering lifetime $\tau(\omega)$, which approximates the optical conductivity $\sigma(\omega)$ via a Drude-type relation.
-As shown in the main panel of Fig.~\ref{optical}, this quantity exhibits a sharp Drude peak at $\omega = 0$ in the Fermi liquid (FL) regime (blue), consistent with long-lived quasiparticles.
-In stark contrast, the PG regime (green, red, orange) shows a pronounced suppression of low-frequency conductivity and the emergence of a finite-frequency peak centered near $\omega/D \sim 0.3{-}0.4$ (where $D$ is the kinetic energy bandwidth).
-
-Strikingly, this peak shifts very little across the PG regime (see inset), despite a deepening spectral gap and diverging self-energy.
-Its position lies well below the Mott gap ($\sim 2.5D$), suggesting that it represents an emergent mid-infrared (MIR) excitation intrinsic to the Mott metal characterising the PG.
-This feature closely mirrors the experimentally observed MIR peak in high-T$_\text{c}$ cuprates~\cite{Herr1987,Orenstein1987,Uchida1991}, which has been variously attributed to excitations of electrons bound to vacancies~\cite{Thomas1992Optical}, or the dressing of holes by spin excitations~\cite{Dagotto1994RMP}.
-Its robust energy scale and insensitivity to increasing incoherence imply a universality persisting through the PG, likely rooted in short-range entanglement between deconfined doublons and holons excitations of the Mott metal.
-This is further evidence that the PG metal is not simply a degraded Fermi liquid, but a distinct phase whose optical response is driven by emergent degrees of freedom.
-
-% To further probe the breakdown of coherent transport in the pseudogap (PG) regime, we examine the product of the impurity spectral function $A(\omega)$$ and the scattering lifetime $\tau(\omega)$$, which approximates the optical conductivity $\sigma(\omega)$ via a Drude-type relation.
-As shown in Fig.(REF)[X], this quantity exhibits a sharp Drude peak at $\omega = 0$ in the Fermi liquid (FL) regime, consistent with long-lived quasiparticles.
-In stark contrast, the PG regime (dashed curves) shows a pronounced suppression of low-frequency conductivity and the emergence of a finite-frequency peak centered near $\omega/D \sim 0.3{-}0.4$ (where $D$ is the kinetic energy bandwidth).
-Strikingly, this peak shifts very little across the PG regime, despite a deepening spectral gap and diverging self-energy.
-Its position lies well below the Mott gap ($\sim 2.5D$), suggesting that it represents an emergent mid-infrared excitation intrinsic to the PG–Mott crossover.
-This feature closely mirrors the experimentally observed mid-IR peak in high-T$_{\textrm{c}}$ cuprates (CITE), which has been variously attributed to preformed pairs (CITE), bound holon–doublon states (CITE), or emergent collective modes (CITE).
-Its robust energy scale and insensitivity to increasing incoherence imply a hidden order or resonance persisting across the PG regime, likely rooted in short-range entanglement between deconfined doublons and holons.
-Thus, the PG metal is not simply a degraded Fermi liquid, but a distinct dynamical phase whose optical response encodes the fingerprints of emergent quantum degrees of freedom.
 
@@
 We present additional figures of the spin (Fig.\ref{spinCorr}) and charge (Fig.\ref{cfnode}) correlations in the impurity model, the impurity spectral function (Fig.\ref{specfunc}), the spin correlations (Fig.\ref{tiledSF}), entanglement entropy (Fig.\ref{tiledEntanglement} (upper panel)) and mutual function (Fig.\ref{tiledEntanglement} (lower panel)) of the tiled model in the pseudogap phase.
-All figures presented here are for a $77\times 77$ {\bf k}-space Brillouin zone grid.
 \begin{figure}[!ht]
@@
     \centering
-    \includegraphics[width=0.4\linewidth]{Ad_zoomout_77-1500.pdf}
+    \includegraphics[width=0.4\linewidth]{figures/Ad_zoomout_77-1500.pdf}
     \caption{Impurity Spectral function in the FL and PG phases.
@@
 
-%\bibliography{tilingProject}
-%\bibliographystyle{unsrt}
-
-\begin{thebibliography}{99}
+\bibliography{tilingProject}
 \bibliographystyle{unsrt}
 
-\bibitem{santanukagome}
-Santanu Pal, Anirban Mukherjee, and Siddhartha Lal.
-\newblock Correlated spin liquids in the quantum kagome antiferromagnet at
-  finite field: a renormalization group analysis.
-\newblock {\em New Journal of Physics}, 21(2):023019, feb 2019.
-
-\bibitem{1dhubjhep1}
-Anirban Mukherjee, Siddhartha Patra, and Siddhartha Lal.
-\newblock Fermionic criticality is shaped by fermi surface topology: a case
-  study of the tomonaga-luttinger liquid.
-\newblock {\em Journal of High Energy Physics}, 2021(4):148, Apr 2021.
-
-\bibitem{anirbanmott1}
-Anirban Mukherjee and Siddhartha Lal.
-\newblock Scaling theory for mott{\textendash}hubbard transitions: I. t = 0
-  phase diagram of the 1/2-filled hubbard model.
-\newblock {\em New Journal of Physics}, 22(6):063007, jun 2020.
-
-\bibitem{siddharthacpi}
-Siddhartha Patra and Siddhartha Lal.
-\newblock Origin of topological order in a cooper-pair insulator.
-\newblock {\em Phys. Rev. B}, 104:144514, Oct 2021.
-
-\bibitem{anirban_kondo}
-Anirban Mukherjee, Abhirup Mukherjee, N.~S. Vidhyadhiraja, A.~Taraphder, and
-  Siddhartha Lal.
-\newblock Unveiling the kondo cloud: Unitary renormalization-group study of the
-  kondo model.
-\newblock {\em Phys. Rev. B}, 105:085119, Feb 2022.
-
-\bibitem{Patra_2023}
-Siddhartha Patra, Anirban Mukherjee, and Siddhartha Lal.
-\newblock Universal entanglement signatures of quantum liquids as a guide to
-  fermionic criticality.
-\newblock {\em New Journal of Physics}, 25(6):063002, jun 2023.
-
-\bibitem{Herr1987}
-S.~L. Herr, K.~Kamar\'as, C.~D. Porter, M.~G. Doss, D.~B. Tanner, D.~A. Bonn,
-  J.~E. Greedan, C.~V. Stager, and T.~Timusk.
-\newblock Optical properties of
-  ${\mathrm{la}}_{1.85}$${\mathrm{sr}}_{0.15}$${\mathrm{cuo}}_{4}$: Evidence
-  for strong electron-phonon and electron-electron interactions.
-\newblock {\em Phys. Rev. B}, 36:733--735, Jul 1987.
-
-\bibitem{Orenstein1987}
-Joseph Orenstein, G.~A. Thomas, D.~H. Rapkine, C.~G. Bethea, B.~F. Levine,
-  R.~J. Cava, E.~A. Rietman, and D.~W. Johnson.
-\newblock Normal-state gap transition in cu-o superconductors.
-\newblock {\em Phys. Rev. B}, 36:729--732, Jul 1987.
-
-\bibitem{Uchida1991}
-S.~Uchida, T.~Ido, H.~Takagi, T.~Arima, Y.~Tokura, and S.~Tajima.
-\newblock Optical spectra of
-  ${\mathrm{la}}_{2\mathrm{\ensuremath{-}}\mathit{x}}$${\mathrm{sr}}_{\mathit{x}}$${\mathrm{cuo}}_{4}$:
-  Effect of carrier doping on the electronic structure of the
-  ${\mathrm{cuo}}_{2}$ plane.
-\newblock {\em Phys. Rev. B}, 43:7942--7954, Apr 1991.
-
-\bibitem{Thomas1992Optical}
-G.~A. Thomas, D.~H. Rapkine, S.~L. Cooper, S-W. Cheong, A.~S. Cooper, L.~F.
-  Schneemeyer, and J.~V. Waszczak.
-\newblock Optical excitations of a few charges in cuprates.
-\newblock {\em Phys. Rev. B}, 45:2474--2479, Feb 1992.
-
-\bibitem{Dagotto1994RMP}
-Elbio Dagotto.
-\newblock Correlated electrons in high-temperature superconductors.
-\newblock {\em Rev. Mod. Phys.}, 66:763--840, Jul 1994.
-
-\bibitem{nozieres1974fermi}
-P~Nozieres.
-\newblock A ``fermi-liquid" description of the kondo problem at low
-  temperatures.
-\newblock {\em Journal of Low Temperature Physics}, 17:31, 1974.
-
-\end{thebibliography}
-
 \end{document}

### 2025-12-10 submissions/TilingUploadROPP/Tiling_Project/manuscript_Final.tex
started creating referee response

--- 2025-12-10 submissions/NPJ/manuscript_Final.tex
@@
 % ,bm,color,hyperref
-\usepackage{graphicx,braket,color,bm,amsmath,amssymb,natbib}
+\usepackage{graphicx,braket,color,bm,amsmath,amssymb}
 % \graphicspath{{./figures/}}
-%\bibliographystyle{apsrev4-2}
+\bibliographystyle{apsrev4-2}
 
@@
 \author{Abhirup Mukherjee}
-\email{am18ip014@iiserkol.ac.in}
 \affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
@@
 \author{S. R. Hassan}
-\email{shassan@imsc.res.in}
 \affiliation{The Institute of Mathematical Sciences, HBNI, C.I.T. Campus, Chennai 600 113, India}
 \author{Anamitra Mukherjee}
-\email{anamitra@niser.ac.in}
 \affiliation{School of Physical Sciences, National Institute of Science, Education and Research, HBNI, Jatni 752050, India}
 \author{N. S. Vidhyadhiraja}
-\email{raja@jncasr.ac.in}
 \affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
 \author{A. Taraphder}
-\email{arghya@phy.iitkgp.ac.in}
 \affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
+
 \author{Siddhartha Lal}
-\email{Corresponding author: slal@iiserkol.ac.in}
 \affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
@@
     \centering
-    \includegraphics[width=\textwidth, height=10cm]{fig2.png}
+    \includegraphics[width=\textwidth, height=10cm]{fig2.jpg}
     \caption{(a): Phase diagram of impurity model at strong coupling in $U$ in terms of competing dimensionless Kondo ($J/t$) and bath correlation ($W/t$) couplings.
 Colourbar represents the fraction of states on the Fermi surface replaced by zeros of the Greens function (Luttinger surface).
-A pseudogap phase (shaded region) is observed between the local Fermi liquid (red region) and local moment (blue region) phases (b): $k$-space-resolved spin correlation $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$ in the pseudogap phase of the impurity model.
+A pseudogap phase (shaded region) is observed between the local Fermi liquid (red region) and local moment (blue region) phases (b): $k$-space-resolved spin-spin correlation $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$ in the pseudogap phase of the impurity model.
 Antinodal regions are observed to decouple from Kondo screening of the impurity.
@@
 The values $(W/J)_{\text{PG}}$ and $(W/J)_c$ are therefore the entry into and exit from the PG phase.
-Mapping onto the lattice model via tiling (see Sec.~3 of \cite{suppmat}), we observe that RG-induced nodal–antinodal dichotomy in $J_{{\bf k}, {\bf k}^\prime}$ in the impurity model is the microscopic origin of the PG in the lattice model: the extinction of Kondo coherence translates into spectral zeros in the lattice Green’s function (i.e., Luttinger surfaces) at antinodal momenta (Fig.~\ref{spinCorr}(c)).
+Mapping onto the lattice model via tiling (see Sec.3 of \cite{suppmat}), we observe that RG-induced nodal–antinodal dichotomy in $J_{{\bf k}, {\bf k}^\prime}$ in the impurity model is the microscopic origin of the PG in the lattice model: the extinction of Kondo coherence translates into spectral zeros in the lattice Green’s function (i.e., Luttinger surfaces) at antinodal momenta (Fig.~\ref{spinCorr}(c)).
 This establishes that the $T=0$ Mott transition of the 2D \textit{extended}-Hubbard model proceeds from FL to MI through an intervening PG phase.
-A schematic RG flow diagram can be found in the supplementary materials (Fig.~S1).
 
@@
 This mirrors the coalescing of finite-frequency poles of the self-energy poles towards zero frequency in the underlying impurity model~(Fig.~\ref{chargeCorr} (c)).
-See ~\cite{suppmat} (Figs.~S3 and S4) for additional spin and charge correlation results.
 
@@
 (b): Scaling of $\Sigma^{\prime\prime}(\omega)$ with frequency for Fermi liquid and pseudogapped phases.
-The FL self-energy fits to $\Sigma^{\prime\prime} \sim \omega^{\alpha}$ with $\alpha\approx 2$, vanishing as $\omega\to 0$, while the NFL self-energy grows as
-$-1/\Sigma^{\prime\prime}(\omega)\sim -1/\Sigma^{\prime\prime}(0) + \omega^{\beta}$,    
-%$\Sigma^{\prime\prime} \approx a + b\omega^{\beta}$ for small $\omega$, 
-with $\beta\approx 2$.
+The FL self-energy fits to $\Sigma^{\prime\prime} \sim \omega^{\alpha}$ with $\alpha\approx 2$, vanishing as $\omega\to 0$, while the NFL self-energy grows as $\Sigma^{\prime\prime} \approx a + b\omega^{\beta}$ for small $\omega$, with $\beta\approx 2$.
 Remarkably, the NFL exponent remains mostly unchanged through the entirety of the PG phase.
@@
 The accompanying impurity spectral function of the gapless arcs show a pseudogapped behaviour for $\omega\simeq 0$, with a rapid fall in the spectral weight at $\omega=0$ upon traversing the PG~(Fig.~\ref{channelDecoupling} (c)).
-The collapse of the Kondo resonance into a pseudogapped spectral function is accompanied by the redistribution of spectral weight~\cite{dzyaloshinskii2003some} in the impurity spectral function from $\omega\sim 0$ to the Hubbard sidebands at finite frequencies $\omega\simeq \pm 3$ (in units of the bandwidth) (Fig.~S5 of \cite{suppmat}).
-Concomitant with this is the emergence of a zero-frequency peak in the imaginary part of the self-energy of the NFL in the PG phase, $-1/\Sigma^{\prime\prime}(\omega)\sim -1/\Sigma^{\prime\prime}(0) + \omega^{\beta}$
-%$-\Sigma''(\omega)\sim (a + \omega^{\beta})^{-1}$~, with $a$ being a constant
-~(Fig.\ref{selfEnergy} (a)).
+The collapse of the Kondo resonance into a pseudogapped spectral function is accompanied by the redistribution of spectral weight~\cite{dzyaloshinskii2003some} in the impurity spectral function from $\omega\sim 0$ to the Hubbard sidebands at finite frequencies $\omega\simeq \pm 3$ (in units of the bandwidth) (Fig.~5 of \cite{suppmat}).
+Concomitant with this is the emergence of a zero-frequency peak in the imaginary part of the self-energy of the NFL in the PG phase, $-\Sigma''(\omega)\sim (a + \omega^{\beta})^{-1}$~, with $a$ being a constant~(Fig.\ref{selfEnergy} (a)).
 Remarkably, we find that the exponent $\beta=2$ characterises the NFL for the entire PG phase (see Fig.~\ref{selfEnergy}(b)), including the critical end-point.
 This is in stark contrast with the $\Sigma''(\omega)\sim \omega^{2}$ for the FL (Fig.~\ref{selfEnergy}(b)).
-A similar analysis reveals the power-law scaling for the low-frequency behaviour of the impurity spectral function (see Fig.~S2 (left) and Sec.V of \cite{suppmat}): $A_{d}(\omega)\sim A_d(0) + \omega^{2}$ for the pseudogap phase, while $1/A_{d}(\omega)\sim 1/A_{d}(0) + \omega^{2}$ for the Fermi liquid.
 
@@
 $-2\Sigma^{\prime\prime}_\text{MIR} = 1/\tau_\text{MIR}~, ~\tau_\text{MIR} = l_\text{min}/v_{F}$~,where $l_\text{min}$ is the minimum mean free path in metals (equal to one lattice spacing) and $\tau_\text{MIR}$ is the associated lifetime of quasiparticles close to the FS (with Fermi velocity $v_F$).
-The transport lifetime $\tau (\omega)$ of the NFL thus undergoes a suppression as $\omega \to 0$, together with a shift of the Drude peak to finite $\omega$~\cite{Hussey2004,pustogow2021,qazilbash2008} (see Fig.~S2 (right) and Sec.VI in \cite{suppmat}).
+The transport lifetime $\tau (\omega)$ of the NFL thus undergoes a suppression as $\omega \to 0$, together with a shift of the Drude peak to finite $\omega$~\cite{Hussey2004,pustogow2021,qazilbash2008} (see Fig.~2 and Sec.V in \cite{suppmat}).
 The height of the zero-frequency peak rises by almost 4 orders of magnitude from the start of the PG till its end at the Mott transition point (Fig.\ref{selfEnergy}(c)); the dramatic growth of the peak height very near the Mott critical point coincides with the coalescing of the finite-frequency poles of the self-energy into a single pole at zero-frequency, signalling the singular nodal NFL present at the Mott quantum critical point.
@@
 The entanglement is observed to be multipartite in nature: in Fig.~\ref{longranged}(c), the quantum Fisher information (QFI)~\cite{Hauke2016} computed for the ground state wavefunction using an operator corresponding to the sum of local spin-flip exchange processes shows a jump at the onset of the PG.
-Further, the FL is observed to possess bi-partite entanglement while the NFL of the PG phase displays 5-partite entanglement~\cite{balut2025,mazza2024}.
-See ~\cite{suppmat} (Figs.~S6 and S7) for additional spin correlations and entanglement measures in momentum space for the tiled model.\\
+Further, the FL is observed to possess bi-partite entanglement while the NFL of the PG phase displays 5-partite entanglement~\cite{balut2025,mazza2024}.\\
 
@@
 This state is described by a quantum critical Fermi surface~\cite{senthil2008CriticalFermiSurface} with NFL Fermi arcs that display increasingly critical behaviour, i.e., dynamics described by non-local quantum fluctuations, and excitations that become truly long-ranged close to the transition.
-It is tempting to conjecture that the long-range entangled critical state captured in Fig.~\ref{longranged}(b) reflects the existence of a highly efficient fast scrambler~\cite{sekino2008,hayden2007,bentsen2019}, i.e., a state in which entanglement spreads among its constituents at the fastest rate permissible by quantum mechanics.
 
@@
     \includegraphics[width=\textwidth]{fig6.pdf}
-    \caption{Spin correlation $\braket{{\bf S}_d \cdot {\bf S}_r}$ (a) and mutual information $I_{2}(d,r)$ (b) between the impurity spin and conduction bath local spin density as a function of the distance {\bf r} between them, normalised against the value at $r=1$.
+    \caption{Spin-flip correlation $\braket{{\bf S}_d \cdot {\bf S}_r}$ (a) and mutual information $I_{2}(d,r)$ (b) between the impurity spin and conduction bath local spin density as a function of the distance {\bf r} between them, normalised against the value at $r=1$.
 Both decay very quickly in the FL phase (blue), but show long-ranged behaviour in the NFL phase (green and red), extending to the edges of the system at the critical point (red).
@@
 \begin{equation}\begin{aligned}\label{HKModel}
-	\Delta \tilde H_{{\bf q}_1 = {\bf q}_2} = \sum_{{\bf q},\sigma}\epsilon_{{\bf q}}{n}_{{\bf q},\sigma} + \mathcal{U}\sum_{{\bf q}, \sigma}n_{{\bf q} \sigma} n_{{\bf q} \bar\sigma}~,
+	\Delta \tilde H_{{\bf q}_1 = {\bf q}_2} = \sum_{{\bf q},\sigma}\epsilon_{{\bf q}}{n}_{{\bf q},\sigma} + u\sum_{{\bf q}, \sigma}n_{{\bf q} \sigma} n_{{\bf q} \bar\sigma}~,
 \end{aligned}\end{equation}
@@
 partner \({\bf N}_1 + {\bf Q}_1 = \left(-\pi/2, -\pi/2\right)\).
-The kinetic energy \(\epsilon_{\bf q}\) and interaction energy \(\mathcal{U}\sim J^{2}/W\) are dispersion and Kondo scales renormalised by conduction bath correlations (see Sec.4 of \cite{suppmat}).\\
+The kinetic energy \(\epsilon_{\bf q}\) and interaction energy \(u\sim J^{2}/W\) are dispersion and Kondo scales renormalised by conduction bath correlations (see Sec.4 of \cite{suppmat}).\\
 
@@
 Consequently, the resulting NFL metal of the lattice model involves long-lived excitations of multiple \({\bf k}\)-states, and manifest in the form of a divergent one-particle self-energy at the non-interacting FS~\cite{Phillips2020}:
-$\Sigma_{{\bf q}}(\omega) = -\mathcal{U}^2/4(\omega - \epsilon_{\bf q})$~, such that $\Sigma_{\epsilon_{\bf q}=0}(\omega \to 0)  \to \infty$.
+$\Sigma_{{\bf q}}(\omega) = -u^2/4(\omega - \epsilon_{\bf q})$~, such that $\Sigma_{\epsilon_{\bf q}=0}(\omega \to 0)  \to \infty$.
 This zero-frequency self-energy pole presages the transition into a Mott insulating phase, where it marks a hard gap in the spectral function for charge excitations.
@@
 
-\noindent For small but non-zero values of \(\omega - \epsilon_{\bf k}\), we obtain a quasiparticle residue that vanishes with $\omega$, \(Z_\text{imp} \sim \omega^2/\mathcal{U}^2 \).
-The scattering rate of this singular NFL possesses a sharp peak at the FS (\(\omega=\epsilon_{\bf k_{\mathrm{F}}}\)): \(\Gamma \sim \mathcal{U}^2\delta(\omega - \epsilon_{\bf k})\), consistent with the sharply peaked Lorentzian $\Sigma''_{{\bf k}}(\omega)\sim \omega^{-2}$ captured in Fig.\ref{selfEnergy}(a).
+\noindent For small but non-zero values of \(\omega - \epsilon_{\bf k}\), we obtain a quasiparticle residue that vanishes with $\omega$, \(Z_\text{imp} \sim \omega^2/U^2 \).
+The scattering rate of this singular NFL possesses a sharp peak at the FS (\(\omega=\epsilon_{\bf k_{\mathrm{F}}}\)): \(\Gamma \sim U^2\delta(\omega - \epsilon_{\bf k})\), consistent with the sharply peaked Lorentzian $\Sigma''_{{\bf k}}(\omega)\sim \omega^{-2}$ captured in Fig.\ref{selfEnergy}(a).
 This quantum critical NFL metal is an example of a strongly coupled scale-invariant form of quantum matter.
@@
 ~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} that are completely disconnected from the quasiparticles of the FL.
-Following the arguments laid out in~\cite{phillips2022}, at finite temperatures, such a scale-invariant highly entangled non-Fermi liquid is likely associated with Planckian dissipation (i.e., $\Sigma'' (T)\sim k_{B}T$) and a resistivity that varies linearly with temperature ($\rho\sim T$)~\cite{zaanen2019,legros2019,hartnoll2022}.
-This sits well with the possibility that this state is also a highly efficient scrambler~\cite{sekino2008,hayden2007,bentsen2019}.
+Following the arguments laid out in~\cite{phillips2022}, at finite temperatures, such a scale-invariant highly entangled non-Fermi liquid is likely associated with Planckian dissipation (i.e., $\Sigma'' (T)\sim k_{B}T$) and a resistivity that varies linearly with temperature ($\rho\sim T$)~\cite{zaanen2019,legros2019}.
 Additionally, we observe that the nodal metal possesses pairing fluctuations (see Sec.4 of \cite{suppmat}) that can become dominant upon doping~\cite{Phillips2020}.
@@
 This signals the NFL Fermi arcs of the PG as an emergent phase of strongly interacting quantum matter - which we dub the {\it Mott metal} - that is the parent metal of the MI.
-The same topological principle connects the nonlocal unparticle-like gapless excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} of the scale-invariant nodal NFL of the HK model observed precisely at the Mott critical point to those of the rest of the PG phase, e.g., a universal scaling of $-1/\Sigma^{\prime\prime}(\omega)\sim -1/\Sigma^{\prime\prime}(0) + \omega^{2}$ of the NFL throughout the PG phase (Fig.~\ref{selfEnergy} (a)) such that $\Sigma''(\omega=0)$ continues to grow upon violating the MIR bound, and a local density of states $A_{d}(\omega) \sim \omega^{2}$ (see Fig.~S2 (left) of \cite{suppmat}).
+The same topological principle connects the nonlocal unparticle-like gapless excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} of the scale-invariant nodal NFL of the HK model observed precisely at the Mott critical point to those of the rest of PG phase, e.g., a universal scaling of $\Sigma''_{{\bf k}}(\omega)\sim (a+b\omega^{2})^{-1}$ of the NFL throughout the PG phase (Fig.~\ref{selfEnergy} (a)) and whose $\omega=0$ value continues to grow upon violating the MIR bound.
 \vspace{0.25cm}
 \par\noindent\textbf{\large Conclusions}\\
-Our analysis reveals that the Mott transition proceeds via a continuous evolution through a PG regime characterized by a singular NFL metal - the Mott metal - with deconfined holon–doublon excitations confined to nodal Fermi arcs, and a scaling of it's spectral features with universal power-law exponents.
-As the system approaches criticality, this metallic phase exhibits increasingly non-local correlations and a divergent self-energy, signalling the breakdown of Landau quasiparticles, formation of local moments and the onset of long-range quantum entanglement.
+Our analysis reveals that the Mott transition proceeds via a continuous evolution through a PG regime characterized by a singular NFL metal - the Mott metal - with deconfined holon–doublon excitations confined to nodal Fermi arcs.
+As the system approaches criticality, this metallic phase exhibits increasingly non-local correlations and a divergent self-energy, signaling the breakdown of Landau quasiparticles and the onset of long-range quantum entanglement.
 Anchored in two-channel Kondo dynamics at intermediate scales and governed by Hatsugai–Kohmoto physics near the critical endpoint, the Mott metal provides a unified framework for understanding anomalous metallicity in strongly correlated systems.
-It's fate under finite doping presents a compelling direction for future investigation.
-
-%\begin{thebibliography}{99}
-%\makeatletter
-%\providecommand \@ifxundefined [1]{%
-% \@ifx{#1\undefined}
-%}%
-%\providecommand \@ifnum [1]{%
-% \ifnum #1\expandafter \@firstoftwo
-% \else \expandafter \@secondoftwo
-% \fi
-%}%
-%\providecommand \@ifx [1]{%
-% \ifx #1\expandafter \@firstoftwo
-% \else \expandafter \@secondoftwo
-% \fi
-%}%
-%\providecommand \natexlab [1]{#1}%
-%\providecommand \enquote  [1]{``#1''}%
-%\providecommand \bibnamefont  [1]{#1}%
-%\providecommand \bibfnamefont [1]{#1}%
-%\providecommand \citenamefont [1]{#1}%
-%\providecommand \href@noop [0]{\@secondoftwo}%
-%\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
-%\providecommand \@href[1]{\@@startlink{#1}\@@href}%
-%\providecommand \@@href[1]{\endgroup#1\@@endlink}%
-%\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
-%  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
-%\providecommand \@@startlink[1]{}%
-%\providecommand \@@endlink[0]{}%
-%\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
-%\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
-%\providecommand \urlprefix  [0]{URL }%
-%\providecommand \Eprint [0]{\href }%
-%\providecommand \doibase [0]{https://doi.org/}%
-%\providecommand \selectlanguage [0]{\@gobble}%
-%\providecommand \bibinfo  [0]{\@secondoftwo}%
-%\providecommand \bibfield  [0]{\@secondoftwo}%
-%\providecommand \translation [1]{[#1]}%
-%\providecommand \BibitemOpen [0]{}%
-%\providecommand \bibitemStop [0]{}%
-%\providecommand \bibitemNoStop [0]{.\EOS\space}%
-%\providecommand \EOS [0]{\spacefactor3000\relax}%
-%\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
-%\let\auto@bib@innerbib\@empty
-%%</preamble>
-%
-%\bibitem [{\citenamefont {Landau}(1957)}]{landau1959theory}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-%  {Landau}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Soviet
-%  Physics Jetp-Ussr}\ }\textbf {\bibinfo {volume} {3}},\ \bibinfo {pages} {920}
-%  (\bibinfo {year} {1957})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2013)\citenamefont
-%  {Phillips}, \citenamefont {Langley},\ and\ \citenamefont
-%  {Hutasoit}}]{Phillips2013Unparticles}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-%  {Phillips}}, \bibinfo {author} {\bibfnamefont {B.~W.}\ \bibnamefont
-%  {Langley}},\ and\ \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont
-%  {Hutasoit}},\ }\href {https://doi.org/10.1103/PhysRevB.88.115129} {\bibfield
-%  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-%  {88}},\ \bibinfo {pages} {115129} (\bibinfo {year} {2013})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Dzyaloshinskii}(2003)}]{dzyaloshinskii2003some}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
-%  {Dzyaloshinskii}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-%  {Physical Review B}\ }\textbf {\bibinfo {volume} {68}},\ \bibinfo {pages}
-%  {085113} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mott}(1949)}]{Mott_1949}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~F.}\ \bibnamefont
-%  {Mott}},\ }\href {https://doi.org/10.1088/0370-1298/62/7/303} {\bibfield
-%  {journal} {\bibinfo  {journal} {Proceedings of the Physical Society. Section
-%  A}\ }\textbf {\bibinfo {volume} {62}},\ \bibinfo {pages} {416} (\bibinfo
-%  {year} {1949})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2022)\citenamefont
-%  {Phillips}, \citenamefont {Hussey},\ and\ \citenamefont
-%  {Abbamonte}}]{phillips2022}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-%  {Phillips}}, \bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
-%  {Hussey}},\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-%  {Abbamonte}},\ }\href {https://doi.org/10.1126/science.abh4273} {\bibfield
-%  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
-%  {377}},\ \bibinfo {pages} {eabh4273} (\bibinfo {year} {2022})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Loeser}\ \emph {et~al.}(1996)\citenamefont {Loeser},
-%  \citenamefont {Shen}, \citenamefont {Dessau}, \citenamefont {Marshall},
-%  \citenamefont {Park}, \citenamefont {Fournier},\ and\ \citenamefont
-%  {Kapitulnik}}]{loeserKapitulnik1996}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~G.}\ \bibnamefont
-%  {Loeser}}, \bibinfo {author} {\bibfnamefont {Z.-X.}\ \bibnamefont {Shen}},
-%  \bibinfo {author} {\bibfnamefont {D.~S.}\ \bibnamefont {Dessau}}, \bibinfo
-%  {author} {\bibfnamefont {D.~S.}\ \bibnamefont {Marshall}}, \bibinfo {author}
-%  {\bibfnamefont {C.~H.}\ \bibnamefont {Park}}, \bibinfo {author}
-%  {\bibfnamefont {P.}~\bibnamefont {Fournier}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {A.}~\bibnamefont {Kapitulnik}},\ }\href
-%  {https://doi.org/10.1126/science.273.5273.325} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {273}},\ \bibinfo
-%  {pages} {325} (\bibinfo {year} {1996})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Norman}\ \emph {et~al.}(1998)\citenamefont {Norman},
-%  \citenamefont {Ding}, \citenamefont {Randeria}, \citenamefont {Campuzano},
-%  \citenamefont {Yokoya}, \citenamefont {Takeuchi}, \citenamefont {Takahashi},
-%  \citenamefont {Mochiku}, \citenamefont {Kadowaki}, \citenamefont
-%  {Guptasarma},\ and\ \citenamefont {Hinks}}]{Norman1998}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
-%  {Norman}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Ding}},
-%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Randeria}}, \bibinfo
-%  {author} {\bibfnamefont {J.~C.}\ \bibnamefont {Campuzano}}, \bibinfo {author}
-%  {\bibfnamefont {T.}~\bibnamefont {Yokoya}}, \bibinfo {author} {\bibfnamefont
-%  {T.}~\bibnamefont {Takeuchi}}, \bibinfo {author} {\bibfnamefont
-%  {T.}~\bibnamefont {Takahashi}}, \bibinfo {author} {\bibfnamefont
-%  {T.}~\bibnamefont {Mochiku}}, \bibinfo {author} {\bibfnamefont
-%  {K.}~\bibnamefont {Kadowaki}}, \bibinfo {author} {\bibfnamefont
-%  {P.}~\bibnamefont {Guptasarma}},\ and\ \bibinfo {author} {\bibfnamefont
-%  {D.~G.}\ \bibnamefont {Hinks}},\ }\href {https://doi.org/10.1038/32366}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
-%  {volume} {392}},\ \bibinfo {pages} {157} (\bibinfo {year}
-%  {1998})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Hashimoto}\ \emph {et~al.}(2014)\citenamefont
-%  {Hashimoto}, \citenamefont {Vishik}, \citenamefont {He}, \citenamefont
-%  {Devereaux},\ and\ \citenamefont {Shen}}]{Hashimoto2014}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-%  {Hashimoto}}, \bibinfo {author} {\bibfnamefont {I.~M.}\ \bibnamefont
-%  {Vishik}}, \bibinfo {author} {\bibfnamefont {R.-H.}\ \bibnamefont {He}},
-%  \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont {Devereaux}},\ and\
-%  \bibinfo {author} {\bibfnamefont {Z.-X.}\ \bibnamefont {Shen}},\ }\href
-%  {https://doi.org/10.1038/nphys3009} {\bibfield  {journal} {\bibinfo
-%  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo
-%  {pages} {483} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Taillefer}(2010)}]{taillefer2010}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-%  {Taillefer}},\ }\href
-%  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-070909-104117}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-%  Physics}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo {pages} {51} (\bibinfo
-%  {year} {2010})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Fradkin}\ \emph {et~al.}(2015)\citenamefont
-%  {Fradkin}, \citenamefont {Kivelson},\ and\ \citenamefont
-%  {Tranquada}}]{FradkinRevModPhys2015}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-%  {Fradkin}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
-%  {Kivelson}},\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-%  {Tranquada}},\ }\href {https://doi.org/10.1103/RevModPhys.87.457} {\bibfield
-%  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume}
-%  {87}},\ \bibinfo {pages} {457} (\bibinfo {year} {2015})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Sato}\ \emph {et~al.}(2017)\citenamefont {Sato},
-%  \citenamefont {Kasahara}, \citenamefont {Murayama}, \citenamefont {Kasahara},
-%  \citenamefont {Moon}, \citenamefont {Nishizaki}, \citenamefont {Loew},
-%  \citenamefont {Porras}, \citenamefont {Keimer}, \citenamefont {Shibauchi},\
-%  and\ \citenamefont {Matsuda}}]{Sato2017}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-%  {Sato}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Kasahara}},
-%  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Murayama}}, \bibinfo
-%  {author} {\bibfnamefont {Y.}~\bibnamefont {Kasahara}}, \bibinfo {author}
-%  {\bibfnamefont {E.-G.}\ \bibnamefont {Moon}}, \bibinfo {author}
-%  {\bibfnamefont {T.}~\bibnamefont {Nishizaki}}, \bibinfo {author}
-%  {\bibfnamefont {T.}~\bibnamefont {Loew}}, \bibinfo {author} {\bibfnamefont
-%  {J.}~\bibnamefont {Porras}}, \bibinfo {author} {\bibfnamefont
-%  {B.}~\bibnamefont {Keimer}}, \bibinfo {author} {\bibfnamefont
-%  {T.}~\bibnamefont {Shibauchi}},\ and\ \bibinfo {author} {\bibfnamefont
-%  {Y.}~\bibnamefont {Matsuda}},\ }\href {https://doi.org/10.1038/nphys4205}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf
-%  {\bibinfo {volume} {13}},\ \bibinfo {pages} {1074} (\bibinfo {year}
-%  {2017})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Doiron-Leyraud}\ \emph {et~al.}(2017)\citenamefont
-%  {Doiron-Leyraud}, \citenamefont {Cyr-Choini{\`e}re}, \citenamefont {Badoux},
-%  \citenamefont {Ataei}, \citenamefont {Collignon}, \citenamefont {Gourgout},
-%  \citenamefont {Dufour-Beaus{\'e}jour}, \citenamefont {Tafti}, \citenamefont
-%  {Lalibert{\'e}}, \citenamefont {Boulanger}, \citenamefont {Matusiak},
-%  \citenamefont {Graf}, \citenamefont {Kim}, \citenamefont {Zhou},
-%  \citenamefont {Momono}, \citenamefont {Kurosawa}, \citenamefont {Takagi},\
-%  and\ \citenamefont {Taillefer}}]{DoironLeyraud2017}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-%  {Doiron-Leyraud}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
-%  {Cyr-Choini{\`e}re}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Badoux}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Ataei}},
-%  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Collignon}}, \bibinfo
-%  {author} {\bibfnamefont {A.}~\bibnamefont {Gourgout}}, \bibinfo {author}
-%  {\bibfnamefont {S.}~\bibnamefont {Dufour-Beaus{\'e}jour}}, \bibinfo {author}
-%  {\bibfnamefont {F.~F.}\ \bibnamefont {Tafti}}, \bibinfo {author}
-%  {\bibfnamefont {F.}~\bibnamefont {Lalibert{\'e}}}, \bibinfo {author}
-%  {\bibfnamefont {M.-E.}\ \bibnamefont {Boulanger}}, \bibinfo {author}
-%  {\bibfnamefont {M.}~\bibnamefont {Matusiak}}, \bibinfo {author}
-%  {\bibfnamefont {D.}~\bibnamefont {Graf}}, \bibinfo {author} {\bibfnamefont
-%  {M.}~\bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont {J.-S.}\
-%  \bibnamefont {Zhou}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-%  {Momono}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Kurosawa}},
-%  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\ and\ \bibinfo
-%  {author} {\bibfnamefont {L.}~\bibnamefont {Taillefer}},\ }\href
-%  {https://doi.org/10.1038/s41467-017-02122-x} {\bibfield  {journal} {\bibinfo
-%  {journal} {Nature Communications}\ }\textbf {\bibinfo {volume} {8}},\
-%  \bibinfo {pages} {2044} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mukhopadhyay}\ \emph {et~al.}(2019)\citenamefont
-%  {Mukhopadhyay}, \citenamefont {Sharma}, \citenamefont {Kim}, \citenamefont
-%  {Edkins}, \citenamefont {Hamidian}, \citenamefont {Eisaki}, \citenamefont
-%  {ichi Uchida}, \citenamefont {Kim}, \citenamefont {Lawler}, \citenamefont
-%  {Mackenzie}, \citenamefont {Davis},\ and\ \citenamefont
-%  {Fujita}}]{Mukhopadhyay2019}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Mukhopadhyay}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-%  {Sharma}}, \bibinfo {author} {\bibfnamefont {C.~K.}\ \bibnamefont {Kim}},
-%  \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont {Edkins}}, \bibinfo
-%  {author} {\bibfnamefont {M.~H.}\ \bibnamefont {Hamidian}}, \bibinfo {author}
-%  {\bibfnamefont {H.}~\bibnamefont {Eisaki}}, \bibinfo {author} {\bibfnamefont
-%  {S.}~\bibnamefont {ichi Uchida}}, \bibinfo {author} {\bibfnamefont {E.-A.}\
-%  \bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
-%  {Lawler}}, \bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont
-%  {Mackenzie}}, \bibinfo {author} {\bibfnamefont {J.~C.~S.}\ \bibnamefont
-%  {Davis}},\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-%  {Fujita}},\ }\href {https://doi.org/10.1073/pnas.1821454116} {\bibfield
-%  {journal} {\bibinfo  {journal} {Proceedings of the National Academy of
-%  Sciences}\ }\textbf {\bibinfo {volume} {116}},\ \bibinfo {pages} {13249}
-%  (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Gupta}\ \emph {et~al.}(2021)\citenamefont {Gupta},
-%  \citenamefont {McMahon}, \citenamefont {Sutarto}, \citenamefont {Shi},
-%  \citenamefont {Gong}, \citenamefont {Wei}, \citenamefont {Shen},
-%  \citenamefont {He}, \citenamefont {Ma}, \citenamefont {Dragomir},
-%  \citenamefont {Gaulin},\ and\ \citenamefont {Hawthorn}}]{Naman2021}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~K.}\ \bibnamefont
-%  {Gupta}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {McMahon}},
-%  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Sutarto}}, \bibinfo
-%  {author} {\bibfnamefont {T.}~\bibnamefont {Shi}}, \bibinfo {author}
-%  {\bibfnamefont {R.}~\bibnamefont {Gong}}, \bibinfo {author} {\bibfnamefont
-%  {H.~I.}\ \bibnamefont {Wei}}, \bibinfo {author} {\bibfnamefont {K.~M.}\
-%  \bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-%  {He}}, \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Ma}}, \bibinfo
-%  {author} {\bibfnamefont {M.}~\bibnamefont {Dragomir}}, \bibinfo {author}
-%  {\bibfnamefont {B.~D.}\ \bibnamefont {Gaulin}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {D.~G.}\ \bibnamefont {Hawthorn}},\ }\href
-%  {https://doi.org/10.1073/pnas.2106881118} {\bibfield  {journal} {\bibinfo
-%  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-%  {\bibinfo {volume} {118}},\ \bibinfo {pages} {e2106881118} (\bibinfo {year}
-%  {2021})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Horio}\ \emph {et~al.}(2025)\citenamefont {Horio},
-%  \citenamefont {Sakai}, \citenamefont {Suzuki}, \citenamefont {Nonaka},
-%  \citenamefont {Hashimoto}, \citenamefont {Lu}, \citenamefont {Shen},
-%  \citenamefont {Ohgi}, \citenamefont {Konno}, \citenamefont {Adachi},
-%  \citenamefont {Koike}, \citenamefont {Imada},\ and\ \citenamefont
-%  {Fujimori}}]{Masafumi2025}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-%  {Horio}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Sakai}},
-%  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Suzuki}}, \bibinfo
-%  {author} {\bibfnamefont {Y.}~\bibnamefont {Nonaka}}, \bibinfo {author}
-%  {\bibfnamefont {M.}~\bibnamefont {Hashimoto}}, \bibinfo {author}
-%  {\bibfnamefont {D.}~\bibnamefont {Lu}}, \bibinfo {author} {\bibfnamefont
-%  {Z.-X.}\ \bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont
-%  {T.}~\bibnamefont {Ohgi}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-%  {Konno}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Adachi}},
-%  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Koike}}, \bibinfo
-%  {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {A.}~\bibnamefont {Fujimori}},\ }\href
-%  {https://doi.org/10.1073/pnas.2406624122} {\bibfield  {journal} {\bibinfo
-%  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-%  {\bibinfo {volume} {122}},\ \bibinfo {pages} {e2406624122} (\bibinfo {year}
-%  {2025})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Kyung}\ \emph {et~al.}(2006)\citenamefont {Kyung},
-%  \citenamefont {Kancharla}, \citenamefont {S\'en\'echal}, \citenamefont
-%  {Tremblay}, \citenamefont {Civelli},\ and\ \citenamefont
-%  {Kotliar}}]{KyungKotliar2006}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-%  {Kyung}}, \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont
-%  {Kancharla}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-%  {S\'en\'echal}}, \bibinfo {author} {\bibfnamefont {A.-M.~S.}\ \bibnamefont
-%  {Tremblay}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Civelli}},\
-%  and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Kotliar}},\ }\href
-%  {https://doi.org/10.1103/PhysRevB.73.165114} {\bibfield  {journal} {\bibinfo
-%  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo
-%  {pages} {165114} (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Macridin}\ \emph {et~al.}(2006)\citenamefont
-%  {Macridin}, \citenamefont {Jarrell}, \citenamefont {Maier}, \citenamefont
-%  {Kent},\ and\ \citenamefont {D'Azevedo}}]{MacridinAzevedo2006}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Macridin}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Jarrell}},
-%  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Maier}}, \bibinfo
-%  {author} {\bibfnamefont {P.~R.~C.}\ \bibnamefont {Kent}},\ and\ \bibinfo
-%  {author} {\bibfnamefont {E.}~\bibnamefont {D'Azevedo}},\ }\href
-%  {https://doi.org/10.1103/PhysRevLett.97.036401} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {97}},\
-%  \bibinfo {pages} {036401} (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2009)\citenamefont {Sakai},
-%  \citenamefont {Motome},\ and\ \citenamefont {Imada}}]{sakai2009evolution}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Sakai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Motome}},\ and\
-%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href@noop {}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Physical review letters}\
-%  }\textbf {\bibinfo {volume} {102}},\ \bibinfo {pages} {056404} (\bibinfo
-%  {year} {2009})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Werner}\ \emph {et~al.}(2009)\citenamefont {Werner},
-%  \citenamefont {Gull}, \citenamefont {Parcollet},\ and\ \citenamefont
-%  {Millis}}]{werner2009momentum}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-%  {Werner}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Gull}},
-%  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}},\ and\
-%  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
-%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
-%  B}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages} {045120} (\bibinfo
-%  {year} {2009})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2010)\citenamefont {Sakai},
-%  \citenamefont {Motome},\ and\ \citenamefont {Imada}}]{sakai2010doped}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Sakai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Motome}},\ and\
-%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href@noop {}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review B}\ }\textbf
-%  {\bibinfo {volume} {82}},\ \bibinfo {pages} {134505} (\bibinfo {year}
-%  {2010})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Lin}\ \emph {et~al.}(2010)\citenamefont {Lin},
-%  \citenamefont {Gull},\ and\ \citenamefont {Millis}}]{lin2010}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-%  {Lin}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Gull}},\ and\
-%  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
-%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-%  }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {045104} (\bibinfo
-%  {year} {2010})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Gull}\ \emph {et~al.}(2010)\citenamefont {Gull},
-%  \citenamefont {Ferrero}, \citenamefont {Parcollet}, \citenamefont {Georges},\
-%  and\ \citenamefont {Millis}}]{gull2010momentum}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-%  {Gull}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ferrero}},
-%  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}}, \bibinfo
-%  {author} {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\ }\href@noop {} {\bibfield
-%  {journal} {\bibinfo  {journal} {Physical Review B}\ }\textbf {\bibinfo
-%  {volume} {82}},\ \bibinfo {pages} {155101} (\bibinfo {year}
-%  {2010})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Gull}\ and\ \citenamefont {Millis}(2012)}]{gull2012}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-%  {Gull}}\ and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
-%  {Millis}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-%  Rev. B}\ }\textbf {\bibinfo {volume} {86}},\ \bibinfo {pages} {241106}
-%  (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mirzaei}\ \emph {et~al.}(2013)\citenamefont
-%  {Mirzaei}, \citenamefont {Stricker}, \citenamefont {Hancock}, \citenamefont
-%  {Berthod}, \citenamefont {Georges}, \citenamefont {van Heumen}, \citenamefont
-%  {Chan}, \citenamefont {Zhao}, \citenamefont {Li}, \citenamefont {Greven},
-%  \citenamefont {Barišić},\ and\ \citenamefont {van~der
-%  Marel}}]{Mirzaei2013}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~I.}\ \bibnamefont
-%  {Mirzaei}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Stricker}},
-%  \bibinfo {author} {\bibfnamefont {J.~N.}\ \bibnamefont {Hancock}}, \bibinfo
-%  {author} {\bibfnamefont {C.}~\bibnamefont {Berthod}}, \bibinfo {author}
-%  {\bibfnamefont {A.}~\bibnamefont {Georges}}, \bibinfo {author} {\bibfnamefont
-%  {E.}~\bibnamefont {van Heumen}}, \bibinfo {author} {\bibfnamefont {M.~K.}\
-%  \bibnamefont {Chan}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
-%  {Zhao}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Li}}, \bibinfo
-%  {author} {\bibfnamefont {M.}~\bibnamefont {Greven}}, \bibinfo {author}
-%  {\bibfnamefont {N.}~\bibnamefont {Barišić}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {D.}~\bibnamefont {van~der Marel}},\ }\href
-%  {https://doi.org/10.1073/pnas.1218846110} {\bibfield  {journal} {\bibinfo
-%  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-%  {\bibinfo {volume} {110}},\ \bibinfo {pages} {5774} (\bibinfo {year}
-%  {2013})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Gull}\ \emph {et~al.}(2013)\citenamefont {Gull},
-%  \citenamefont {Parcollet},\ and\ \citenamefont {Millis}}]{gull2013}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-%  {Gull}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}},\
-%  and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
-%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical review
-%  letters}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo {pages} {216405}
-%  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
-%  {Lal}(2020{\natexlab{a}})}]{anirbanmott2}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Lal}},\ }\href {https://doi.org/10.1088/1367-2630/ab890c} {\bibfield
-%  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
-%  {volume} {22}},\ \bibinfo {pages} {063008} (\bibinfo {year}
-%  {2020}{\natexlab{a}})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Hille}\ \emph {et~al.}(2020)\citenamefont {Hille},
-%  \citenamefont {Rohe}, \citenamefont {Honerkamp},\ and\ \citenamefont
-%  {Andergassen}}]{HilleAndergassen2020}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-%  {Hille}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Rohe}},
-%  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Honerkamp}},\ and\
-%  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Andergassen}},\ }\href
-%  {https://doi.org/10.1103/PhysRevResearch.2.033068} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Phys. Rev. Res.}\ }\textbf {\bibinfo {volume} {2}},\
-%  \bibinfo {pages} {033068} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Jiang}\ \emph {et~al.}(2022)\citenamefont {Jiang},
-%  \citenamefont {Liu}, \citenamefont {Klein}, \citenamefont {Wang},
-%  \citenamefont {Sun}, \citenamefont {Chubukov},\ and\ \citenamefont
-%  {Meng}}]{Jiang2022}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
-%  {Jiang}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Liu}}, \bibinfo
-%  {author} {\bibfnamefont {A.}~\bibnamefont {Klein}}, \bibinfo {author}
-%  {\bibfnamefont {Y.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont
-%  {K.}~\bibnamefont {Sun}}, \bibinfo {author} {\bibfnamefont {A.~V.}\
-%  \bibnamefont {Chubukov}},\ and\ \bibinfo {author} {\bibfnamefont {Z.~Y.}\
-%  \bibnamefont {Meng}},\ }\href {https://doi.org/10.1038/s41467-022-30302-x}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Nature Communications}\ }\textbf
-%  {\bibinfo {volume} {13}},\ \bibinfo {pages} {2655} (\bibinfo {year}
-%  {2022})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Scheurer}\ \emph {et~al.}(2018)\citenamefont
-%  {Scheurer}, \citenamefont {Chatterjee}, \citenamefont {Wu}, \citenamefont
-%  {Ferrero}, \citenamefont {Georges},\ and\ \citenamefont
-%  {Sachdev}}]{Scheurer2018}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont
-%  {Scheurer}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Chatterjee}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Wu}},
-%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ferrero}}, \bibinfo
-%  {author} {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {S.}~\bibnamefont {Sachdev}},\ }\href
-%  {https://doi.org/10.1073/pnas.1720580115} {\bibfield  {journal} {\bibinfo
-%  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-%  {\bibinfo {volume} {115}},\ \bibinfo {pages} {E3665} (\bibinfo {year}
-%  {2018})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Krien}\ \emph {et~al.}(2022)\citenamefont {Krien},
-%  \citenamefont {Worm}, \citenamefont {Chalupa-Gantner}, \citenamefont
-%  {Toschi},\ and\ \citenamefont {Held}}]{Krien2022}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-%  {Krien}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Worm}},
-%  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Chalupa-Gantner}},
-%  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Toschi}},\ and\ \bibinfo
-%  {author} {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\href
-%  {https://doi.org/10.1038/s42005-022-01117-5} {\bibfield  {journal} {\bibinfo
-%  {journal} {Communications Physics}\ }\textbf {\bibinfo {volume} {5}},\
-%  \bibinfo {pages} {336} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Kitatani}\ \emph {et~al.}(2023)\citenamefont
-%  {Kitatani}, \citenamefont {Si}, \citenamefont {Worm}, \citenamefont
-%  {Tomczak}, \citenamefont {Arita},\ and\ \citenamefont {Held}}]{Kitatani2023}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-%  {Kitatani}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Si}},
-%  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Worm}}, \bibinfo {author}
-%  {\bibfnamefont {J.~M.}\ \bibnamefont {Tomczak}}, \bibinfo {author}
-%  {\bibfnamefont {R.}~\bibnamefont {Arita}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\href
-%  {https://doi.org/10.1103/PhysRevLett.130.166002} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {130}},\
-%  \bibinfo {pages} {166002} (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Sorella}(2023)}]{Sorella2023}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Sorella}},\ }\href {https://doi.org/10.1103/PhysRevB.107.115133} {\bibfield
-%  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-%  {107}},\ \bibinfo {pages} {115133} (\bibinfo {year} {2023})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Schäfer}\ \emph {et~al.}(2021)\citenamefont
-%  {Schäfer}, \citenamefont {Wentzell}, \citenamefont {Šimkovic},
-%  \citenamefont {He}, \citenamefont {Hille}, \citenamefont {Klett},
-%  \citenamefont {Eckhardt}, \citenamefont {Arzhang}, \citenamefont {Harkov},
-%  \citenamefont {Le~R\'egent}, \citenamefont {Kirsch}, \citenamefont {Wang},
-%  \citenamefont {Kim}, \citenamefont {Kozik}, \citenamefont {Stepanov},
-%  \citenamefont {Kauch}, \citenamefont {Andergassen}, \citenamefont {Hansmann},
-%  \citenamefont {Rohe}, \citenamefont {Vilk}, \citenamefont {LeBlanc},
-%  \citenamefont {Zhang}, \citenamefont {Tremblay}, \citenamefont {Ferrero},
-%  \citenamefont {Parcollet},\ and\ \citenamefont {Georges}}]{Schafer2021}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-%  {Schäfer}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Wentzell}},
-%  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Šimkovic}}, \bibinfo
-%  {author} {\bibfnamefont {Y.-Y.}\ \bibnamefont {He}}, \bibinfo {author}
-%  {\bibfnamefont {C.}~\bibnamefont {Hille}}, \bibinfo {author} {\bibfnamefont
-%  {M.}~\bibnamefont {Klett}}, \bibinfo {author} {\bibfnamefont {C.~J.}\
-%  \bibnamefont {Eckhardt}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-%  {Arzhang}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Harkov}},
-%  \bibinfo {author} {\bibfnamefont {F.~m. c.-M.}\ \bibnamefont {Le~R\'egent}},
-%  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kirsch}}, \bibinfo
-%  {author} {\bibfnamefont {Y.}~\bibnamefont {Wang}}, \bibinfo {author}
-%  {\bibfnamefont {A.~J.}\ \bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont
-%  {E.}~\bibnamefont {Kozik}}, \bibinfo {author} {\bibfnamefont {E.~A.}\
-%  \bibnamefont {Stepanov}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Kauch}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Andergassen}},
-%  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Hansmann}}, \bibinfo
-%  {author} {\bibfnamefont {D.}~\bibnamefont {Rohe}}, \bibinfo {author}
-%  {\bibfnamefont {Y.~M.}\ \bibnamefont {Vilk}}, \bibinfo {author}
-%  {\bibfnamefont {J.~P.~F.}\ \bibnamefont {LeBlanc}}, \bibinfo {author}
-%  {\bibfnamefont {S.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
-%  {A.-M.~S.}\ \bibnamefont {Tremblay}}, \bibinfo {author} {\bibfnamefont
-%  {M.}~\bibnamefont {Ferrero}}, \bibinfo {author} {\bibfnamefont
-%  {O.}~\bibnamefont {Parcollet}},\ and\ \bibinfo {author} {\bibfnamefont
-%  {A.}~\bibnamefont {Georges}},\ }\href
-%  {https://doi.org/10.1103/PhysRevX.11.011058} {\bibfield  {journal} {\bibinfo
-%  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
-%  {pages} {011058} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {White}\ and\ \citenamefont
-%  {Scalapino}(1998)}]{White1998}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~R.}\ \bibnamefont
-%  {White}}\ and\ \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
-%  {Scalapino}},\ }\href {https://doi.org/10.1103/PhysRevLett.80.1272}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-%  {\bibinfo {volume} {80}},\ \bibinfo {pages} {1272} (\bibinfo {year}
-%  {1998})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Ido}\ \emph {et~al.}(2018)\citenamefont {Ido},
-%  \citenamefont {Ohgoe},\ and\ \citenamefont {Imada}}]{Ido2018}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-%  {Ido}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Ohgoe}},\ and\
-%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href
-%  {https://doi.org/10.1103/PhysRevB.97.045138} {\bibfield  {journal} {\bibinfo
-%  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo
-%  {pages} {045138} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Proust}\ and\ \citenamefont
-%  {Taillefer}(2019)}]{ProustTaillefer2019}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-%  {Proust}}\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-%  {Taillefer}},\ }\href
-%  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-031218-013210}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-%  Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {409}
-%  (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Ponsioen}\ \emph {et~al.}(2019)\citenamefont
-%  {Ponsioen}, \citenamefont {Chung},\ and\ \citenamefont
-%  {Corboz}}]{Ponsioen2019}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-%  {Ponsioen}}, \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont
-%  {Chung}},\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-%  {Corboz}},\ }\href {https://doi.org/10.1103/PhysRevB.100.195141} {\bibfield
-%  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-%  {100}},\ \bibinfo {pages} {195141} (\bibinfo {year} {2019})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Xu}\ \emph {et~al.}(2022)\citenamefont {Xu},
-%  \citenamefont {Shi}, \citenamefont {Vitali}, \citenamefont {Qin},\ and\
-%  \citenamefont {Zhang}}]{XuZhang2022}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-%  {Xu}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Shi}}, \bibinfo
-%  {author} {\bibfnamefont {E.}~\bibnamefont {Vitali}}, \bibinfo {author}
-%  {\bibfnamefont {M.}~\bibnamefont {Qin}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {S.}~\bibnamefont {Zhang}},\ }\href
-%  {https://doi.org/10.1103/PhysRevResearch.4.013239} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Phys. Rev. Res.}\ }\textbf {\bibinfo {volume} {4}},\
-%  \bibinfo {pages} {013239} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Dave}\ \emph {et~al.}(2013)\citenamefont {Dave},
-%  \citenamefont {Phillips},\ and\ \citenamefont {Kane}}]{Phillips2013}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~B.}\ \bibnamefont
-%  {Dave}}, \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\
-%  and\ \bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont {Kane}},\ }\href
-%  {https://doi.org/10.1103/PhysRevLett.110.090403} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {110}},\
-%  \bibinfo {pages} {090403} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Seki}\ and\ \citenamefont
-%  {Yunoki}(2017)}]{seki2017topological}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-%  {Seki}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Yunoki}},\
-%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
-%  B}\ }\textbf {\bibinfo {volume} {96}},\ \bibinfo {pages} {085124} (\bibinfo
-%  {year} {2017})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Anderson}\ and\ \citenamefont
-%  {Haldane}(2001)}]{Anderson2001}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-%  {Anderson}}\ and\ \bibinfo {author} {\bibfnamefont {F.~D.~M.}\ \bibnamefont
-%  {Haldane}},\ }\href {https://doi.org/10.1023/A:1010324912515} {\bibfield
-%  {journal} {\bibinfo  {journal} {Journal of Statistical Physics}\ }\textbf
-%  {\bibinfo {volume} {103}},\ \bibinfo {pages} {425} (\bibinfo {year}
-%  {2001})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Huang}\ \emph {et~al.}(2022)\citenamefont {Huang},
-%  \citenamefont {Nave},\ and\ \citenamefont {Phillips}}]{Huang2022}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont
-%  {Huang}}, \bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont {Nave}},\
-%  and\ \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\
-%  }\href {https://doi.org/10.1038/s41567-022-01529-8} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {18}},\
-%  \bibinfo {pages} {511} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Coleman}\ \emph {et~al.}(2001)\citenamefont
-%  {Coleman}, \citenamefont {Pépin}, \citenamefont {Si},\ and\ \citenamefont
-%  {Ramazashvili}}]{Coleman_2001}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-%  {Coleman}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Pépin}},
-%  \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Si}},\ and\ \bibinfo
-%  {author} {\bibfnamefont {R.}~\bibnamefont {Ramazashvili}},\ }\href
-%  {https://doi.org/10.1088/0953-8984/13/35/202} {\bibfield  {journal} {\bibinfo
-%   {journal} {Journal of Physics: Condensed Matter}\ }\textbf {\bibinfo
-%  {volume} {13}},\ \bibinfo {pages} {R723} (\bibinfo {year}
-%  {2001})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
-%  {Lal}(2020{\natexlab{b}})}]{anirbanurg1}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Lal}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nuclear
-%  Physics B}\ }\textbf {\bibinfo {volume} {960}},\ \bibinfo {pages} {115170}
-%  (\bibinfo {year} {2020}{\natexlab{b}})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
-%  {Lal}(2020{\natexlab{c}})}]{anirbanurg2}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Lal}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nuclear
-%  Physics B}\ }\textbf {\bibinfo {volume} {960}},\ \bibinfo {pages} {115163}
-%  (\bibinfo {year} {2020}{\natexlab{c}})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Keimer}\ \emph {et~al.}(2015)\citenamefont {Keimer},
-%  \citenamefont {Kivelson}, \citenamefont {Norman}, \citenamefont {Uchida},\
-%  and\ \citenamefont {Zaanen}}]{keimer2015quantum}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-%  {Keimer}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
-%  {Kivelson}}, \bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
-%  {Norman}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Uchida}},\
-%  and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zaanen}},\
-%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf
-%  {\bibinfo {volume} {518}},\ \bibinfo {pages} {179} (\bibinfo {year}
-%  {2015})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Hatsugai}\ and\ \citenamefont
-%  {Kohmoto}(1992)}]{Hatsugai1992}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-%  {Hatsugai}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-%  {Kohmoto}},\ }\href {https://doi.org/10.1143/JPSJ.61.2056} {\bibfield
-%  {journal} {\bibinfo  {journal} {Journal of the Physical Society of Japan}\
-%  }\textbf {\bibinfo {volume} {61}},\ \bibinfo {pages} {2056} (\bibinfo {year}
-%  {1992})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Baskaran}(1991)}]{Baskaran1991}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-%  {Baskaran}},\ }\href {https://doi.org/10.1142/S0217984991000782} {\bibfield
-%  {journal} {\bibinfo  {journal} {Modern Physics Letters B}\ }\textbf {\bibinfo
-%  {volume} {05}},\ \bibinfo {pages} {643} (\bibinfo {year} {1991})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Altshuler}\ \emph {et~al.}(1998)\citenamefont
-%  {Altshuler}, \citenamefont {Chubukov}, \citenamefont {Dashevskii},
-%  \citenamefont {Finkel'stein},\ and\ \citenamefont {Morr}}]{Altshuler_1998}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~L.}\ \bibnamefont
-%  {Altshuler}}, \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
-%  {Chubukov}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Dashevskii}}, \bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
-%  {Finkel'stein}},\ and\ \bibinfo {author} {\bibfnamefont {D.~K.}\ \bibnamefont
-%  {Morr}},\ }\href {https://doi.org/10.1209/epl/i1998-00164-y} {\bibfield
-%  {journal} {\bibinfo  {journal} {Europhysics Letters}\ }\textbf {\bibinfo
-%  {volume} {41}},\ \bibinfo {pages} {401} (\bibinfo {year} {1998})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Heath}\ and\ \citenamefont
-%  {Bedell}(2020)}]{Heath_2020}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont
-%  {Heath}}\ and\ \bibinfo {author} {\bibfnamefont {K.~S.}\ \bibnamefont
-%  {Bedell}},\ }\href {https://doi.org/10.1088/1367-2630/ab890e} {\bibfield
-%  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
-%  {volume} {22}},\ \bibinfo {pages} {063011} (\bibinfo {year}
-%  {2020})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Nave}\ \emph {et~al.}(2025)\citenamefont {Nave},
-%  \citenamefont {Zhao},\ and\ \citenamefont {Phillips}}]{lanave2025}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont
-%  {Nave}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zhao}},\ and\
-%  \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\ }\href
-%  {https://arxiv.org/abs/2506.04342} {} (\bibinfo {year} {2025}),\ \Eprint
-%  {https://arxiv.org/abs/2506.04342} {arXiv:2506.04342 [cond-mat.str-el]}
-%  \BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mukherjee}\ \emph {et~al.}(2023)\citenamefont
-%  {Mukherjee}, \citenamefont {Vidhyadhiraja}, \citenamefont {Taraphder},\ and\
-%  \citenamefont {Lal}}]{Mukherjee_2023}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Mukherjee}}, \bibinfo {author} {\bibfnamefont {N.~S.}\ \bibnamefont
-%  {Vidhyadhiraja}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Taraphder}},\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Lal}},\ }\href {https://doi.org/10.1088/1367-2630/ad08f3} {\bibfield
-%  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
-%  {volume} {25}},\ \bibinfo {pages} {113011} (\bibinfo {year}
-%  {2023})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Georges}\ \emph {et~al.}(1996)\citenamefont
-%  {Georges}, \citenamefont {Kotliar}, \citenamefont {Krauth},\ and\
-%  \citenamefont {Rozenberg}}]{georges1996}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Georges}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Kotliar}},
-%  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Krauth}},\ and\ \bibinfo
-%  {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Rozenberg}},\ }\href@noop {}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Reviews of Modern Physics}\
-%  }\textbf {\bibinfo {volume} {68}},\ \bibinfo {pages} {13} (\bibinfo {year}
-%  {1996})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Hettler}\ \emph {et~al.}(1998)\citenamefont
-%  {Hettler}, \citenamefont {Tahvildar-Zadeh}, \citenamefont {Jarrell},
-%  \citenamefont {Pruschke},\ and\ \citenamefont {Krishnamurthy}}]{hettler1998}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-%  {Hettler}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Tahvildar-Zadeh}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-%  {Jarrell}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Pruschke}},\
-%  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Krishnamurthy}},\
-%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
-%  B}\ }\textbf {\bibinfo {volume} {58}},\ \bibinfo {pages} {R7475} (\bibinfo
-%  {year} {1998})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Kotliar}\ \emph {et~al.}(2001)\citenamefont
-%  {Kotliar}, \citenamefont {Savrasov}, \citenamefont {P{\'a}lsson},\ and\
-%  \citenamefont {Biroli}}]{kotliar2001}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-%  {Kotliar}}, \bibinfo {author} {\bibfnamefont {S.~Y.}\ \bibnamefont
-%  {Savrasov}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-%  {P{\'a}lsson}},\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-%  {Biroli}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-%  {Physical review letters}\ }\textbf {\bibinfo {volume} {87}},\ \bibinfo
-%  {pages} {186401} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Maier}\ \emph {et~al.}(2005)\citenamefont {Maier},
-%  \citenamefont {Jarrell}, \citenamefont {Schulthess}, \citenamefont {Kent},\
-%  and\ \citenamefont {White}}]{maier2005}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont
-%  {Maier}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Jarrell}},
-%  \bibinfo {author} {\bibfnamefont {T.~C.}\ \bibnamefont {Schulthess}},
-%  \bibinfo {author} {\bibfnamefont {P.~R.~C.}\ \bibnamefont {Kent}},\ and\
-%  \bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont {White}},\ }\href@noop
-%  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-%  {\bibinfo {volume} {95}},\ \bibinfo {pages} {237001} (\bibinfo {year}
-%  {2005})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Stoyanova}(2006)}]{stoyanova}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Stoyanova}},\ }\emph {\bibinfo {title} {Delocalized and correlated wave
-%  functions for excited states in extended systems}},\ \href@noop {} {Ph.D.
-%  thesis},\ \bibinfo  {school} {University of Groningen} (\bibinfo {year}
-%  {2006})\BibitemShut {NoStop}%
-%\bibitem [{sup()}]{suppmat}%
-%  \BibitemOpen
-%  \href@noop {} {\bibinfo {title} {See supplemental material for additional
-%  information.}}\BibitemShut {Stop}%
-%\bibitem [{\citenamefont {Wu}\ \emph {et~al.}(2018)\citenamefont {Wu},
-%  \citenamefont {Scheurer}, \citenamefont {Chatterjee}, \citenamefont
-%  {Sachdev}, \citenamefont {Georges},\ and\ \citenamefont
-%  {Ferrero}}]{WuFerrero2018}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
-%  {Wu}}, \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Scheurer}},
-%  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Chatterjee}}, \bibinfo
-%  {author} {\bibfnamefont {S.}~\bibnamefont {Sachdev}}, \bibinfo {author}
-%  {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {M.}~\bibnamefont {Ferrero}},\ }\href
-%  {https://doi.org/10.1103/PhysRevX.8.021048} {\bibfield  {journal} {\bibinfo
-%  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {8}},\ \bibinfo {pages}
-%  {021048} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Tsvelick}\ and\ \citenamefont
-%  {Wiegmann}(1985)}]{Tsvelick_weigmann_mchannel_1985}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
-%  {Tsvelick}}\ and\ \bibinfo {author} {\bibfnamefont {P.~B.}\ \bibnamefont
-%  {Wiegmann}},\ }\href {https://doi.org/10.1007/BF01017853} {\bibfield
-%  {journal} {\bibinfo  {journal} {Journal of Statistical Physics}\ }\textbf
-%  {\bibinfo {volume} {38}},\ \bibinfo {pages} {125} (\bibinfo {year}
-%  {1985})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Emery}\ and\ \citenamefont
-%  {Kivelson}(1992)}]{emery_kivelson}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~J.}\ \bibnamefont
-%  {Emery}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Kivelson}},\ }\href {https://doi.org/10.1103/PhysRevB.46.10812} {\bibfield
-%  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-%  {46}},\ \bibinfo {pages} {10812} (\bibinfo {year} {1992})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Gunnarsson}\ \emph {et~al.}(2003)\citenamefont
-%  {Gunnarsson}, \citenamefont {Calandra},\ and\ \citenamefont
-%  {Han}}]{GunnarssonRMP2003}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
-%  {Gunnarsson}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-%  {Calandra}},\ and\ \bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont
-%  {Han}},\ }\href {https://doi.org/10.1103/RevModPhys.75.1085} {\bibfield
-%  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume}
-%  {75}},\ \bibinfo {pages} {1085} (\bibinfo {year} {2003})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Hussey}\ \emph {et~al.}(2004)\citenamefont {Hussey},
-%  \citenamefont {Takenaka},\ and\ \citenamefont {Takagi}}]{Hussey2004}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
-%  {Hussey}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Takenaka}},\
-%  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\ }\href
-%  {https://doi.org/10.1080/14786430410001716944} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Philosophical Magazine}\ }\textbf {\bibinfo {volume}
-%  {84}},\ \bibinfo {pages} {2847} (\bibinfo {year} {2004})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Pustogow}\ \emph {et~al.}(2021)\citenamefont
-%  {Pustogow}, \citenamefont {Saito}, \citenamefont {Anja~Löhle}, \citenamefont
-%  {Alonso}, \citenamefont {Kawamoto}, \citenamefont {Dobrosavljevic},
-%  \citenamefont {Dressel},\ and\ \citenamefont {Fratini}}]{pustogow2021}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Pustogow}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Saito}},
-%  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Anja~Löhle}}, \bibinfo
-%  {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Alonso}}, \bibinfo {author}
-%  {\bibfnamefont {A.}~\bibnamefont {Kawamoto}}, \bibinfo {author}
-%  {\bibfnamefont {V.}~\bibnamefont {Dobrosavljevic}}, \bibinfo {author}
-%  {\bibfnamefont {M.}~\bibnamefont {Dressel}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {S.}~\bibnamefont {Fratini}},\ }\href@noop {} {\bibfield
-%  {journal} {\bibinfo  {journal} {Nat. Comm.}\ }\textbf {\bibinfo {volume}
-%  {12}},\ \bibinfo {pages} {1571} (\bibinfo {year} {2021})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Qazilbash}\ \emph {et~al.}(2008)\citenamefont
-%  {Qazilbash}, \citenamefont {Schafgans}, \citenamefont {Burch}, \citenamefont
-%  {Yun}, \citenamefont {Chae}, \citenamefont {Kim}, \citenamefont {Kim},\ and\
-%  \citenamefont {Basov}}]{qazilbash2008}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~M.}\ \bibnamefont
-%  {Qazilbash}}, \bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont
-%  {Schafgans}}, \bibinfo {author} {\bibfnamefont {K.~S.}\ \bibnamefont
-%  {Burch}}, \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont {Yun}},
-%  \bibinfo {author} {\bibfnamefont {B.~G.}\ \bibnamefont {Chae}}, \bibinfo
-%  {author} {\bibfnamefont {B.~J.}\ \bibnamefont {Kim}}, \bibinfo {author}
-%  {\bibfnamefont {H.~T.}\ \bibnamefont {Kim}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {D.~N.}\ \bibnamefont {Basov}},\ }\href
-%  {https://doi.org/10.1103/PhysRevB.77.115121} {\bibfield  {journal} {\bibinfo
-%  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo
-%  {pages} {115121} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Hauke}\ \emph {et~al.}(2016)\citenamefont {Hauke},
-%  \citenamefont {Heyl}, \citenamefont {Tagliacozzo},\ and\ \citenamefont
-%  {Zoller}}]{Hauke2016}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-%  {Hauke}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Heyl}},
-%  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Tagliacozzo}},\ and\
-%  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Zoller}},\ }\href
-%  {https://doi.org/10.1038/nphys3700} {\bibfield  {journal} {\bibinfo
-%  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
-%  {pages} {778} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Balut}\ \emph {et~al.}(2025)\citenamefont {Balut},
-%  \citenamefont {Guo}, \citenamefont {de~Vriesa}, \citenamefont {Chaudhuri},
-%  \citenamefont {Bradlyn}, \citenamefont {Abbamonte},\ and\ \citenamefont
-%  {W.}}]{balut2025}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-%  {Balut}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Guo}}, \bibinfo
-%  {author} {\bibfnamefont {N.}~\bibnamefont {de~Vriesa}}, \bibinfo {author}
-%  {\bibfnamefont {D.}~\bibnamefont {Chaudhuri}}, \bibinfo {author}
-%  {\bibfnamefont {B.}~\bibnamefont {Bradlyn}}, \bibinfo {author} {\bibfnamefont
-%  {P.}~\bibnamefont {Abbamonte}},\ and\ \bibinfo {author} {\bibfnamefont
-%  {P.~P.}\ \bibnamefont {W.}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-%  {journal} {Physica C}\ }\textbf {\bibinfo {volume} {635}},\ \bibinfo {pages}
-%  {1354750} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mazza}\ \emph {et~al.}(2024)\citenamefont {Mazza},
-%  \citenamefont {Biswas}, \citenamefont {Yan}, \citenamefont {Prokofiev},
-%  \citenamefont {Steffens}, \citenamefont {Si}, \citenamefont {Assaad},\ and\
-%  \citenamefont {Paschen}}]{mazza2024}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-%  {Mazza}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Biswas}},
-%  \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Yan}}, \bibinfo {author}
-%  {\bibfnamefont {A.}~\bibnamefont {Prokofiev}}, \bibinfo {author}
-%  {\bibfnamefont {P.}~\bibnamefont {Steffens}}, \bibinfo {author}
-%  {\bibfnamefont {Q.}~\bibnamefont {Si}}, \bibinfo {author} {\bibfnamefont
-%  {F.~F.}\ \bibnamefont {Assaad}},\ and\ \bibinfo {author} {\bibfnamefont
-%  {S.}~\bibnamefont {Paschen}},\ }\href {https://arxiv.org/abs/2403.12779} {}
-%  (\bibinfo {year} {2024}),\ \Eprint {https://arxiv.org/abs/2403.12779}
-%  {arXiv:2403.12779 [cond-mat.str-el]} \BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Si}\ \emph {et~al.}(2001)\citenamefont {Si},
-%  \citenamefont {Rabello}, \citenamefont {Ingersent},\ and\ \citenamefont
-%  {Smith}}]{Si2001}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont
-%  {Si}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Rabello}},
-%  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Ingersent}},\ and\
-%  \bibinfo {author} {\bibfnamefont {J.~L.}\ \bibnamefont {Smith}},\ }\href
-%  {https://doi.org/10.1038/35101507} {\bibfield  {journal} {\bibinfo  {journal}
-%  {Nature}\ }\textbf {\bibinfo {volume} {413}},\ \bibinfo {pages} {804}
-%  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2020)\citenamefont
-%  {Phillips}, \citenamefont {Yeo},\ and\ \citenamefont {Huang}}]{Phillips2020}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-%  {Phillips}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Yeo}},\ and\
-%  \bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont {Huang}},\ }\href
-%  {https://doi.org/10.1038/s41567-020-0988-4} {\bibfield  {journal} {\bibinfo
-%  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo
-%  {pages} {1175} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Vafek}\ and\ \citenamefont
-%  {Vishwanath}(2014)}]{vafekvishwanath2014}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
-%  {Vafek}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Vishwanath}},\ }\href
-%  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-031113-133841}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-%  Physics}\ }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {83} (\bibinfo
-%  {year} {2014})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Morimoto}\ and\ \citenamefont
-%  {Nagaosa}(2016)}]{morimoto2016}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-%  {Morimoto}}\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-%  {Nagaosa}},\ }\href {https://doi.org/10.1038/srep19853} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Sci. Rep.}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo
-%  {pages} {19853} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Flores-Calder\'on}\ and\ \citenamefont
-%  {Hooley}(2025)}]{calderon2025}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-%  {Flores-Calder\'on}}\ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-%  {Hooley}},\ }\href {https://doi.org/10.1103/k4st-77ph} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {111}},\
-%  \bibinfo {pages} {235139} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Georgi}(2007{\natexlab{a}})}]{Georgi2007PRL}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-%  {Georgi}},\ }\href {https://doi.org/10.1103/PhysRevLett.98.221601} {\bibfield
-%   {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
-%  {volume} {98}},\ \bibinfo {pages} {221601} (\bibinfo {year}
-%  {2007}{\natexlab{a}})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Georgi}(2007{\natexlab{b}})}]{Georgi2007}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-%  {Georgi}},\ }\href
-%  {https://doi.org/https://doi.org/10.1016/j.physletb.2007.05.037} {\bibfield
-%  {journal} {\bibinfo  {journal} {Physics Letters B}\ }\textbf {\bibinfo
-%  {volume} {650}},\ \bibinfo {pages} {275} (\bibinfo {year}
-%  {2007}{\natexlab{b}})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Phillips}(2014)}]{PhillipsLectures2014}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-%  {Phillips}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {Quantum
-%  Criticality in Condensed Matter}}},\ \bibinfo {editor} {edited by\ \bibinfo
-%  {editor} {\bibfnamefont {J.}~\bibnamefont {Jedrzejewski}}}\ (\bibinfo
-%  {publisher} {World Scientific, Singapore},\ \bibinfo {year} {2014})\ pp.\
-%  \bibinfo {pages} {133--158}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Zaanen}(2019)}]{zaanen2019}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-%  {Zaanen}},\ }\href {https://doi.org/10.21468/SciPostPhys.6.5.061} {\bibfield
-%  {journal} {\bibinfo  {journal} {SciPost Phys.}\ }\textbf {\bibinfo {volume}
-%  {6}},\ \bibinfo {pages} {061} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Legros}\ \emph {et~al.}(2019)\citenamefont {Legros},
-%  \citenamefont {Benhabib}, \citenamefont {Tabis}, \citenamefont
-%  {Lalibert{\'e}}, \citenamefont {Dion}, \citenamefont {Lizaire}, \citenamefont
-%  {Vignolle}, \citenamefont {Vignolles}, \citenamefont {Raffy}, \citenamefont
-%  {Li} \emph {et~al.}}]{legros2019}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Legros}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Benhabib}},
-%  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Tabis}}, \bibinfo
-%  {author} {\bibfnamefont {F.}~\bibnamefont {Lalibert{\'e}}}, \bibinfo {author}
-%  {\bibfnamefont {M.}~\bibnamefont {Dion}}, \bibinfo {author} {\bibfnamefont
-%  {M.}~\bibnamefont {Lizaire}}, \bibinfo {author} {\bibfnamefont
-%  {B.}~\bibnamefont {Vignolle}}, \bibinfo {author} {\bibfnamefont
-%  {D.}~\bibnamefont {Vignolles}}, \bibinfo {author} {\bibfnamefont
-%  {H.}~\bibnamefont {Raffy}}, \bibinfo {author} {\bibfnamefont
-%  {Z.}~\bibnamefont {Li}}, \emph {et~al.},\ }\href@noop {} {\bibfield
-%  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
-%  {15}},\ \bibinfo {pages} {142} (\bibinfo {year} {2019})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {McGreevy}(2023)}]{McGreevy2023}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-%  {McGreevy}},\ }\href
-%  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-040721-021029}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-%  Physics}\ }\textbf {\bibinfo {volume} {14}},\ \bibinfo {pages} {57} (\bibinfo
-%  {year} {2023})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Luttinger}\ and\ \citenamefont
-%  {Ward}(1960)}]{luttinger1960ground}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-%  {Luttinger}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
-%  {Ward}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical
-%  Review}\ }\textbf {\bibinfo {volume} {118}},\ \bibinfo {pages} {1417}
-%  (\bibinfo {year} {1960})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Su}\ and\ \citenamefont
-%  {Martin}(2025)}]{su2025anomalies}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-%  {Su}}\ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Martin}},\
-%  }\href {https://arxiv.org/abs/2405.08093} {} (\bibinfo {year} {2025}),\
-%  \Eprint {https://arxiv.org/abs/2405.08093} {arXiv:2405.08093
-%  [cond-mat.str-el]} \BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Adler}(1969)}]{adler1969axial}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont
-%  {Adler}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-%  {Physical Review}\ }\textbf {\bibinfo {volume} {177}},\ \bibinfo {pages}
-%  {2426} (\bibinfo {year} {1969})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Bell}\ and\ \citenamefont
-%  {Jackiw}(1969)}]{bell1969pcac}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~S.}\ \bibnamefont
-%  {Bell}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Jackiw}},\
-%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Il Nuovo Cimento
-%  A}\ }\textbf {\bibinfo {volume} {60}},\ \bibinfo {pages} {47} (\bibinfo
-%  {year} {1969})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Casini}\ and\ \citenamefont
-%  {Mag\'{a}n}(2021)}]{Casini2021Symmetries}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-%  {Casini}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-%  {Mag\'{a}n}},\ }\href {https://doi.org/10.1142/S0217732321300251} {\bibfield
-%  {journal} {\bibinfo  {journal} {Modern Physics Letters A}\ }\textbf {\bibinfo
-%  {volume} {36}},\ \bibinfo {pages} {2130025} (\bibinfo {year}
-%  {2021})}\BibitemShut {NoStop}%
-%\end{thebibliography}
-
-%\bibliography{tilingProject}
-
-\begin{thebibliography}{89}%
-\makeatletter
-\providecommand \@ifxundefined [1]{%
- \@ifx{#1\undefined}
-}%
-\providecommand \@ifnum [1]{%
- \ifnum #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \@ifx [1]{%
- \ifx #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \natexlab [1]{#1}%
-\providecommand \enquote  [1]{``#1''}%
-\providecommand \bibnamefont  [1]{#1}%
-\providecommand \bibfnamefont [1]{#1}%
-\providecommand \citenamefont [1]{#1}%
-\providecommand \href@noop [0]{\@secondoftwo}%
-\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
-\providecommand \@href[1]{\@@startlink{#1}\@@href}%
-\providecommand \@@href[1]{\endgroup#1\@@endlink}%
-\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
-  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
-\providecommand \@@startlink[1]{}%
-\providecommand \@@endlink[0]{}%
-\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
-\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
-\providecommand \urlprefix  [0]{URL }%
-\providecommand \Eprint [0]{\href }%
-\providecommand \doibase [0]{https://doi.org/}%
-\providecommand \selectlanguage [0]{\@gobble}%
-\providecommand \bibinfo  [0]{\@secondoftwo}%
-\providecommand \bibfield  [0]{\@secondoftwo}%
-\providecommand \translation [1]{[#1]}%
-\providecommand \BibitemOpen [0]{}%
-\providecommand \bibitemStop [0]{}%
-\providecommand \bibitemNoStop [0]{.\EOS\space}%
-\providecommand \EOS [0]{\spacefactor3000\relax}%
-\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
-\let\auto@bib@innerbib\@empty
-%</preamble>
-\bibitem [{\citenamefont {Landau}(1957)}]{landau1959theory}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Landau}},\ }\bibfield  {title} {\bibinfo {title} {The theory of a fermi
-  liquid},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Soviet
-  Physics Jetp-Ussr}\ }\textbf {\bibinfo {volume} {3}},\ \bibinfo {pages} {920}
-  (\bibinfo {year} {1957})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2013)\citenamefont
-  {Phillips}, \citenamefont {Langley},\ and\ \citenamefont
-  {Hutasoit}}]{Phillips2013Unparticles}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-  {Phillips}}, \bibinfo {author} {\bibfnamefont {B.~W.}\ \bibnamefont
-  {Langley}},\ and\ \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont
-  {Hutasoit}},\ }\bibfield  {title} {\bibinfo {title} {Un-fermi liquids:
-  Unparticles in strongly correlated electron matter},\ }\href
-  {https://doi.org/10.1103/PhysRevB.88.115129} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {88}},\ \bibinfo
-  {pages} {115129} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Dzyaloshinskii}(2003)}]{dzyaloshinskii2003some}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
-  {Dzyaloshinskii}},\ }\bibfield  {title} {\bibinfo {title} {Some consequences
-  of the luttinger theorem: The luttinger surfaces in non-fermi liquids and
-  mott insulators},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Physical Review B}\ }\textbf {\bibinfo {volume} {68}},\ \bibinfo {pages}
-  {085113} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mott}(1949)}]{Mott_1949}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~F.}\ \bibnamefont
-  {Mott}},\ }\bibfield  {title} {\bibinfo {title} {The basis of the electron
-  theory of metals, with special reference to the transition metals},\ }\href
-  {https://doi.org/10.1088/0370-1298/62/7/303} {\bibfield  {journal} {\bibinfo
-  {journal} {Proceedings of the Physical Society. Section A}\ }\textbf
-  {\bibinfo {volume} {62}},\ \bibinfo {pages} {416} (\bibinfo {year}
-  {1949})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2022)\citenamefont
-  {Phillips}, \citenamefont {Hussey},\ and\ \citenamefont
-  {Abbamonte}}]{phillips2022}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-  {Phillips}}, \bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
-  {Hussey}},\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Abbamonte}},\ }\bibfield  {title} {\bibinfo {title} {Stranger than metals},\
-  }\href {https://doi.org/10.1126/science.abh4273} {\bibfield  {journal}
-  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {377}},\ \bibinfo
-  {pages} {eabh4273} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Loeser}\ \emph {et~al.}(1996)\citenamefont {Loeser},
-  \citenamefont {Shen}, \citenamefont {Dessau}, \citenamefont {Marshall},
-  \citenamefont {Park}, \citenamefont {Fournier},\ and\ \citenamefont
-  {Kapitulnik}}]{loeserKapitulnik1996}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~G.}\ \bibnamefont
-  {Loeser}}, \bibinfo {author} {\bibfnamefont {Z.-X.}\ \bibnamefont {Shen}},
-  \bibinfo {author} {\bibfnamefont {D.~S.}\ \bibnamefont {Dessau}}, \bibinfo
-  {author} {\bibfnamefont {D.~S.}\ \bibnamefont {Marshall}}, \bibinfo {author}
-  {\bibfnamefont {C.~H.}\ \bibnamefont {Park}}, \bibinfo {author}
-  {\bibfnamefont {P.}~\bibnamefont {Fournier}},\ and\ \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Kapitulnik}},\ }\bibfield  {title}
-  {\bibinfo {title} {Excitation gap in the normal state of underdoped
-  bi2sr2cacu2o8},\ }\href {https://doi.org/10.1126/science.273.5273.325}
-  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
-  {volume} {273}},\ \bibinfo {pages} {325} (\bibinfo {year}
-  {1996})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Norman}\ \emph {et~al.}(1998)\citenamefont {Norman},
-  \citenamefont {Ding}, \citenamefont {Randeria}, \citenamefont {Campuzano},
-  \citenamefont {Yokoya}, \citenamefont {Takeuchi}, \citenamefont {Takahashi},
-  \citenamefont {Mochiku}, \citenamefont {Kadowaki}, \citenamefont
-  {Guptasarma},\ and\ \citenamefont {Hinks}}]{Norman1998}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
-  {Norman}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Ding}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Randeria}}, \bibinfo
-  {author} {\bibfnamefont {J.~C.}\ \bibnamefont {Campuzano}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Yokoya}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Takeuchi}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Takahashi}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Mochiku}}, \bibinfo {author} {\bibfnamefont
-  {K.}~\bibnamefont {Kadowaki}}, \bibinfo {author} {\bibfnamefont
-  {P.}~\bibnamefont {Guptasarma}},\ and\ \bibinfo {author} {\bibfnamefont
-  {D.~G.}\ \bibnamefont {Hinks}},\ }\bibfield  {title} {\bibinfo {title}
-  {Destruction of the fermi surface in underdoped high-tc superconductors},\
-  }\href {https://doi.org/10.1038/32366} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature}\ }\textbf {\bibinfo {volume} {392}},\ \bibinfo {pages}
-  {157} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hashimoto}\ \emph {et~al.}(2014)\citenamefont
-  {Hashimoto}, \citenamefont {Vishik}, \citenamefont {He}, \citenamefont
-  {Devereaux},\ and\ \citenamefont {Shen}}]{Hashimoto2014}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Hashimoto}}, \bibinfo {author} {\bibfnamefont {I.~M.}\ \bibnamefont
-  {Vishik}}, \bibinfo {author} {\bibfnamefont {R.-H.}\ \bibnamefont {He}},
-  \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont {Devereaux}},\ and\
-  \bibinfo {author} {\bibfnamefont {Z.-X.}\ \bibnamefont {Shen}},\ }\bibfield
-  {title} {\bibinfo {title} {Energy gaps in high-transition-temperature cuprate
-  superconductors},\ }\href {https://doi.org/10.1038/nphys3009} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
-  {10}},\ \bibinfo {pages} {483} (\bibinfo {year} {2014})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Taillefer}(2010)}]{taillefer2010}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Taillefer}},\ }\bibfield  {title} {\bibinfo {title} {Scattering and pairing
-  in cuprate superconductors},\ }\href
-  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-070909-104117}
-  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-  Physics}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo {pages} {51} (\bibinfo
-  {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Fradkin}\ \emph {et~al.}(2015)\citenamefont
-  {Fradkin}, \citenamefont {Kivelson},\ and\ \citenamefont
-  {Tranquada}}]{FradkinRevModPhys2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Fradkin}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
-  {Kivelson}},\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-  {Tranquada}},\ }\bibfield  {title} {\bibinfo {title} {Colloquium: Theory of
-  intertwined orders in high temperature superconductors},\ }\href
-  {https://doi.org/10.1103/RevModPhys.87.457} {\bibfield  {journal} {\bibinfo
-  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {87}},\ \bibinfo
-  {pages} {457} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sato}\ \emph {et~al.}(2017)\citenamefont {Sato},
-  \citenamefont {Kasahara}, \citenamefont {Murayama}, \citenamefont {Kasahara},
-  \citenamefont {Moon}, \citenamefont {Nishizaki}, \citenamefont {Loew},
-  \citenamefont {Porras}, \citenamefont {Keimer}, \citenamefont {Shibauchi},\
-  and\ \citenamefont {Matsuda}}]{Sato2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Sato}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Kasahara}},
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Murayama}}, \bibinfo
-  {author} {\bibfnamefont {Y.}~\bibnamefont {Kasahara}}, \bibinfo {author}
-  {\bibfnamefont {E.-G.}\ \bibnamefont {Moon}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Nishizaki}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Loew}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Porras}}, \bibinfo {author} {\bibfnamefont
-  {B.}~\bibnamefont {Keimer}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Shibauchi}},\ and\ \bibinfo {author} {\bibfnamefont
-  {Y.}~\bibnamefont {Matsuda}},\ }\bibfield  {title} {\bibinfo {title}
-  {Thermodynamic evidence for a nematic phase transition at the onset of the
-  pseudogap in yba2cu3oy},\ }\href {https://doi.org/10.1038/nphys4205}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf
-  {\bibinfo {volume} {13}},\ \bibinfo {pages} {1074} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Doiron-Leyraud}\ \emph {et~al.}(2017)\citenamefont
-  {Doiron-Leyraud}, \citenamefont {Cyr-Choini{\`e}re}, \citenamefont {Badoux},
-  \citenamefont {Ataei}, \citenamefont {Collignon}, \citenamefont {Gourgout},
-  \citenamefont {Dufour-Beaus{\'e}jour}, \citenamefont {Tafti}, \citenamefont
-  {Lalibert{\'e}}, \citenamefont {Boulanger}, \citenamefont {Matusiak},
-  \citenamefont {Graf}, \citenamefont {Kim}, \citenamefont {Zhou},
-  \citenamefont {Momono}, \citenamefont {Kurosawa}, \citenamefont {Takagi},\
-  and\ \citenamefont {Taillefer}}]{DoironLeyraud2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Doiron-Leyraud}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
-  {Cyr-Choini{\`e}re}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Badoux}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Ataei}},
-  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Collignon}}, \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Gourgout}}, \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Dufour-Beaus{\'e}jour}}, \bibinfo {author}
-  {\bibfnamefont {F.~F.}\ \bibnamefont {Tafti}}, \bibinfo {author}
-  {\bibfnamefont {F.}~\bibnamefont {Lalibert{\'e}}}, \bibinfo {author}
-  {\bibfnamefont {M.-E.}\ \bibnamefont {Boulanger}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Matusiak}}, \bibinfo {author}
-  {\bibfnamefont {D.}~\bibnamefont {Graf}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont {J.-S.}\
-  \bibnamefont {Zhou}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Momono}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Kurosawa}},
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\ and\ \bibinfo
-  {author} {\bibfnamefont {L.}~\bibnamefont {Taillefer}},\ }\bibfield  {title}
-  {\bibinfo {title} {Pseudogap phase of cuprate superconductors confined by
-  fermi surface topology},\ }\href {https://doi.org/10.1038/s41467-017-02122-x}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature Communications}\ }\textbf
-  {\bibinfo {volume} {8}},\ \bibinfo {pages} {2044} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mukhopadhyay}\ \emph {et~al.}(2019)\citenamefont
-  {Mukhopadhyay}, \citenamefont {Sharma}, \citenamefont {Kim}, \citenamefont
-  {Edkins}, \citenamefont {Hamidian}, \citenamefont {Eisaki}, \citenamefont
-  {ichi Uchida}, \citenamefont {Kim}, \citenamefont {Lawler}, \citenamefont
-  {Mackenzie}, \citenamefont {Davis},\ and\ \citenamefont
-  {Fujita}}]{Mukhopadhyay2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Mukhopadhyay}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Sharma}}, \bibinfo {author} {\bibfnamefont {C.~K.}\ \bibnamefont {Kim}},
-  \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont {Edkins}}, \bibinfo
-  {author} {\bibfnamefont {M.~H.}\ \bibnamefont {Hamidian}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Eisaki}}, \bibinfo {author} {\bibfnamefont
-  {S.}~\bibnamefont {ichi Uchida}}, \bibinfo {author} {\bibfnamefont {E.-A.}\
-  \bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
-  {Lawler}}, \bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont
-  {Mackenzie}}, \bibinfo {author} {\bibfnamefont {J.~C.~S.}\ \bibnamefont
-  {Davis}},\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Fujita}},\ }\bibfield  {title} {\bibinfo {title} {Evidence for a vestigial
-  nematic state in the cuprate pseudogap phase},\ }\href
-  {https://doi.org/10.1073/pnas.1821454116} {\bibfield  {journal} {\bibinfo
-  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-  {\bibinfo {volume} {116}},\ \bibinfo {pages} {13249} (\bibinfo {year}
-  {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Gupta}\ \emph {et~al.}(2021)\citenamefont {Gupta},
-  \citenamefont {McMahon}, \citenamefont {Sutarto}, \citenamefont {Shi},
-  \citenamefont {Gong}, \citenamefont {Wei}, \citenamefont {Shen},
-  \citenamefont {He}, \citenamefont {Ma}, \citenamefont {Dragomir},
-  \citenamefont {Gaulin},\ and\ \citenamefont {Hawthorn}}]{Naman2021}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~K.}\ \bibnamefont
-  {Gupta}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {McMahon}},
-  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Sutarto}}, \bibinfo
-  {author} {\bibfnamefont {T.}~\bibnamefont {Shi}}, \bibinfo {author}
-  {\bibfnamefont {R.}~\bibnamefont {Gong}}, \bibinfo {author} {\bibfnamefont
-  {H.~I.}\ \bibnamefont {Wei}}, \bibinfo {author} {\bibfnamefont {K.~M.}\
-  \bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {He}}, \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Ma}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Dragomir}}, \bibinfo {author}
-  {\bibfnamefont {B.~D.}\ \bibnamefont {Gaulin}},\ and\ \bibinfo {author}
-  {\bibfnamefont {D.~G.}\ \bibnamefont {Hawthorn}},\ }\bibfield  {title}
-  {\bibinfo {title} {Vanishing nematic order beyond the pseudogap phase in
-  overdoped cuprate superconductors},\ }\href
-  {https://doi.org/10.1073/pnas.2106881118} {\bibfield  {journal} {\bibinfo
-  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-  {\bibinfo {volume} {118}},\ \bibinfo {pages} {e2106881118} (\bibinfo {year}
-  {2021})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Horio}\ \emph {et~al.}(2025)\citenamefont {Horio},
-  \citenamefont {Sakai}, \citenamefont {Suzuki}, \citenamefont {Nonaka},
-  \citenamefont {Hashimoto}, \citenamefont {Lu}, \citenamefont {Shen},
-  \citenamefont {Ohgi}, \citenamefont {Konno}, \citenamefont {Adachi},
-  \citenamefont {Koike}, \citenamefont {Imada},\ and\ \citenamefont
-  {Fujimori}}]{Masafumi2025}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Horio}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Sakai}},
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Suzuki}}, \bibinfo
-  {author} {\bibfnamefont {Y.}~\bibnamefont {Nonaka}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Hashimoto}}, \bibinfo {author}
-  {\bibfnamefont {D.}~\bibnamefont {Lu}}, \bibinfo {author} {\bibfnamefont
-  {Z.-X.}\ \bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Ohgi}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Konno}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Adachi}},
-  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Koike}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ and\ \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Fujimori}},\ }\bibfield  {title} {\bibinfo
-  {title} {Pseudogap in electron-doped cuprates: Strong correlation leading to
-  band splitting},\ }\href {https://doi.org/10.1073/pnas.2406624122} {\bibfield
-   {journal} {\bibinfo  {journal} {Proceedings of the National Academy of
-  Sciences}\ }\textbf {\bibinfo {volume} {122}},\ \bibinfo {pages}
-  {e2406624122} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kyung}\ \emph {et~al.}(2006)\citenamefont {Kyung},
-  \citenamefont {Kancharla}, \citenamefont {S\'en\'echal}, \citenamefont
-  {Tremblay}, \citenamefont {Civelli},\ and\ \citenamefont
-  {Kotliar}}]{KyungKotliar2006}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-  {Kyung}}, \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont
-  {Kancharla}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {S\'en\'echal}}, \bibinfo {author} {\bibfnamefont {A.-M.~S.}\ \bibnamefont
-  {Tremblay}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Civelli}},\
-  and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Kotliar}},\
-  }\bibfield  {title} {\bibinfo {title} {Pseudogap induced by short-range spin
-  correlations in a doped mott insulator},\ }\href
-  {https://doi.org/10.1103/PhysRevB.73.165114} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo
-  {pages} {165114} (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Macridin}\ \emph {et~al.}(2006)\citenamefont
-  {Macridin}, \citenamefont {Jarrell}, \citenamefont {Maier}, \citenamefont
-  {Kent},\ and\ \citenamefont {D'Azevedo}}]{MacridinAzevedo2006}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Macridin}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Jarrell}},
-  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Maier}}, \bibinfo
-  {author} {\bibfnamefont {P.~R.~C.}\ \bibnamefont {Kent}},\ and\ \bibinfo
-  {author} {\bibfnamefont {E.}~\bibnamefont {D'Azevedo}},\ }\bibfield  {title}
-  {\bibinfo {title} {Pseudogap and antiferromagnetic correlations in the
-  hubbard model},\ }\href {https://doi.org/10.1103/PhysRevLett.97.036401}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-  {\bibinfo {volume} {97}},\ \bibinfo {pages} {036401} (\bibinfo {year}
-  {2006})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2009)\citenamefont {Sakai},
-  \citenamefont {Motome},\ and\ \citenamefont {Imada}}]{sakai2009evolution}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Sakai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Motome}},\ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\bibfield
-  {title} {\bibinfo {title} {Evolution of electronic structure of doped mott
-  insulators: Reconstruction of poles and zeros of green’s function},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical review
-  letters}\ }\textbf {\bibinfo {volume} {102}},\ \bibinfo {pages} {056404}
-  (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Werner}\ \emph {et~al.}(2009)\citenamefont {Werner},
-  \citenamefont {Gull}, \citenamefont {Parcollet},\ and\ \citenamefont
-  {Millis}}]{werner2009momentum}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Werner}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Gull}},
-  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}},\ and\
-  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\ }\bibfield
-   {title} {\bibinfo {title} {Momentum-selective metal-insulator transition in
-  the two-dimensional hubbard model: An 8-site dynamical cluster approximation
-  study},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical
-  Review B}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages} {045120}
-  (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2010)\citenamefont {Sakai},
-  \citenamefont {Motome},\ and\ \citenamefont {Imada}}]{sakai2010doped}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Sakai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Motome}},\ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\bibfield
-  {title} {\bibinfo {title} {Doped high-t c cuprate superconductors elucidated
-  in the light of zeros and poles of the electronic green’s function},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
-  B}\ }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {134505} (\bibinfo
-  {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Lin}\ \emph {et~al.}(2010)\citenamefont {Lin},
-  \citenamefont {Gull},\ and\ \citenamefont {Millis}}]{lin2010}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Lin}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Gull}},\ and\
-  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\ }\bibfield
-   {title} {\bibinfo {title} {Physics of the pseudogap in eight-site cluster
-  dynamical mean-field theory: Photoemission, raman scattering, and in-plane
-  and c-axs=is conductivity},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {82}},\ \bibinfo
-  {pages} {045104} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Gull}\ \emph {et~al.}(2010)\citenamefont {Gull},
-  \citenamefont {Ferrero}, \citenamefont {Parcollet}, \citenamefont {Georges},\
-  and\ \citenamefont {Millis}}]{gull2010momentum}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Gull}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ferrero}},
-  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}}, \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-  {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\ }\bibfield  {title}
-  {\bibinfo {title} {Momentum-space anisotropy and pseudogaps: A comparative
-  cluster dynamical mean-field analysis of the doping-driven metal-insulator
-  transition in the two-dimensional hubbard model},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Physical Review B}\ }\textbf {\bibinfo
-  {volume} {82}},\ \bibinfo {pages} {155101} (\bibinfo {year}
-  {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Gull}\ and\ \citenamefont {Millis}(2012)}]{gull2012}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Gull}}\ and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
-  {Millis}},\ }\bibfield  {title} {\bibinfo {title} {Energetics of
-  superconductivity in the two-dimensional hubbard model},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo
-  {volume} {86}},\ \bibinfo {pages} {241106} (\bibinfo {year}
-  {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mirzaei}\ \emph {et~al.}(2013)\citenamefont
-  {Mirzaei}, \citenamefont {Stricker}, \citenamefont {Hancock}, \citenamefont
-  {Berthod}, \citenamefont {Georges}, \citenamefont {van Heumen}, \citenamefont
-  {Chan}, \citenamefont {Zhao}, \citenamefont {Li}, \citenamefont {Greven},
-  \citenamefont {Barišić},\ and\ \citenamefont {van~der
-  Marel}}]{Mirzaei2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~I.}\ \bibnamefont
-  {Mirzaei}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Stricker}},
-  \bibinfo {author} {\bibfnamefont {J.~N.}\ \bibnamefont {Hancock}}, \bibinfo
-  {author} {\bibfnamefont {C.}~\bibnamefont {Berthod}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Georges}}, \bibinfo {author} {\bibfnamefont
-  {E.}~\bibnamefont {van Heumen}}, \bibinfo {author} {\bibfnamefont {M.~K.}\
-  \bibnamefont {Chan}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
-  {Zhao}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Li}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Greven}}, \bibinfo {author}
-  {\bibfnamefont {N.}~\bibnamefont {Barišić}},\ and\ \bibinfo {author}
-  {\bibfnamefont {D.}~\bibnamefont {van~der Marel}},\ }\bibfield  {title}
-  {\bibinfo {title} {Spectroscopic evidence for fermi liquid-like energy and
-  temperature dependence of the relaxation rate in the pseudogap phase of the
-  cuprates},\ }\href {https://doi.org/10.1073/pnas.1218846110} {\bibfield
-  {journal} {\bibinfo  {journal} {Proceedings of the National Academy of
-  Sciences}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo {pages} {5774}
-  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Gull}\ \emph {et~al.}(2013)\citenamefont {Gull},
-  \citenamefont {Parcollet},\ and\ \citenamefont {Millis}}]{gull2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Gull}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}},\
-  and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
-  }\bibfield  {title} {\bibinfo {title} {Superconductivity and the pseudogap in
-  the two-dimensional hubbard model},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Physical review letters}\ }\textbf {\bibinfo {volume}
-  {110}},\ \bibinfo {pages} {216405} (\bibinfo {year} {2013})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
-  {Lal}(2020{\natexlab{a}})}]{anirbanmott2}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Lal}},\ }\bibfield  {title} {\bibinfo {title} {Scaling theory for
-  mott{\textendash}hubbard transitions-{II}: quantum criticality of the doped
-  mott insulator},\ }\href {https://doi.org/10.1088/1367-2630/ab890c}
-  {\bibfield  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf
-  {\bibinfo {volume} {22}},\ \bibinfo {pages} {063008} (\bibinfo {year}
-  {2020}{\natexlab{a}})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hille}\ \emph {et~al.}(2020)\citenamefont {Hille},
-  \citenamefont {Rohe}, \citenamefont {Honerkamp},\ and\ \citenamefont
-  {Andergassen}}]{HilleAndergassen2020}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Hille}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Rohe}},
-  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Honerkamp}},\ and\
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Andergassen}},\
-  }\bibfield  {title} {\bibinfo {title} {Pseudogap opening in the
-  two-dimensional hubbard model: A functional renormalization group analysis},\
-  }\href {https://doi.org/10.1103/PhysRevResearch.2.033068} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. Res.}\ }\textbf {\bibinfo {volume}
-  {2}},\ \bibinfo {pages} {033068} (\bibinfo {year} {2020})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Jiang}\ \emph {et~al.}(2022)\citenamefont {Jiang},
-  \citenamefont {Liu}, \citenamefont {Klein}, \citenamefont {Wang},
-  \citenamefont {Sun}, \citenamefont {Chubukov},\ and\ \citenamefont
-  {Meng}}]{Jiang2022}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
-  {Jiang}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Liu}}, \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Klein}}, \bibinfo {author}
-  {\bibfnamefont {Y.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont
-  {K.}~\bibnamefont {Sun}}, \bibinfo {author} {\bibfnamefont {A.~V.}\
-  \bibnamefont {Chubukov}},\ and\ \bibinfo {author} {\bibfnamefont {Z.~Y.}\
-  \bibnamefont {Meng}},\ }\bibfield  {title} {\bibinfo {title} {Monte carlo
-  study of the pseudogap and superconductivity emerging from quantum magnetic
-  fluctuations},\ }\href {https://doi.org/10.1038/s41467-022-30302-x}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature Communications}\ }\textbf
-  {\bibinfo {volume} {13}},\ \bibinfo {pages} {2655} (\bibinfo {year}
-  {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Scheurer}\ \emph {et~al.}(2018)\citenamefont
-  {Scheurer}, \citenamefont {Chatterjee}, \citenamefont {Wu}, \citenamefont
-  {Ferrero}, \citenamefont {Georges},\ and\ \citenamefont
-  {Sachdev}}]{Scheurer2018}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont
-  {Scheurer}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Chatterjee}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Wu}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ferrero}}, \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Sachdev}},\ }\bibfield  {title} {\bibinfo
-  {title} {Topological order in the pseudogap metal},\ }\href
-  {https://doi.org/10.1073/pnas.1720580115} {\bibfield  {journal} {\bibinfo
-  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-  {\bibinfo {volume} {115}},\ \bibinfo {pages} {E3665} (\bibinfo {year}
-  {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Krien}\ \emph {et~al.}(2022)\citenamefont {Krien},
-  \citenamefont {Worm}, \citenamefont {Chalupa-Gantner}, \citenamefont
-  {Toschi},\ and\ \citenamefont {Held}}]{Krien2022}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Krien}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Worm}},
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Chalupa-Gantner}},
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Toschi}},\ and\ \bibinfo
-  {author} {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\bibfield  {title}
-  {\bibinfo {title} {Explaining the pseudogap through damping and antidamping
-  on the fermi surface by imaginary spin scattering},\ }\href
-  {https://doi.org/10.1038/s42005-022-01117-5} {\bibfield  {journal} {\bibinfo
-  {journal} {Communications Physics}\ }\textbf {\bibinfo {volume} {5}},\
-  \bibinfo {pages} {336} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kitatani}\ \emph {et~al.}(2023)\citenamefont
-  {Kitatani}, \citenamefont {Si}, \citenamefont {Worm}, \citenamefont
-  {Tomczak}, \citenamefont {Arita},\ and\ \citenamefont {Held}}]{Kitatani2023}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Kitatani}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Si}},
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Worm}}, \bibinfo {author}
-  {\bibfnamefont {J.~M.}\ \bibnamefont {Tomczak}}, \bibinfo {author}
-  {\bibfnamefont {R.}~\bibnamefont {Arita}},\ and\ \bibinfo {author}
-  {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\bibfield  {title} {\bibinfo
-  {title} {Optimizing superconductivity: From cuprates via nickelates to
-  palladates},\ }\href {https://doi.org/10.1103/PhysRevLett.130.166002}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-  {\bibinfo {volume} {130}},\ \bibinfo {pages} {166002} (\bibinfo {year}
-  {2023})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sorella}(2023)}]{Sorella2023}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Sorella}},\ }\bibfield  {title} {\bibinfo {title} {Systematically improvable
-  mean-field variational ansatz for strongly correlated systems: Application to
-  the hubbard model},\ }\href {https://doi.org/10.1103/PhysRevB.107.115133}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo
-  {volume} {107}},\ \bibinfo {pages} {115133} (\bibinfo {year}
-  {2023})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Schäfer}\ \emph {et~al.}(2021)\citenamefont
-  {Schäfer}, \citenamefont {Wentzell}, \citenamefont {Šimkovic},
-  \citenamefont {He}, \citenamefont {Hille}, \citenamefont {Klett},
-  \citenamefont {Eckhardt}, \citenamefont {Arzhang}, \citenamefont {Harkov},
-  \citenamefont {Le~R\'egent}, \citenamefont {Kirsch}, \citenamefont {Wang},
-  \citenamefont {Kim}, \citenamefont {Kozik}, \citenamefont {Stepanov},
-  \citenamefont {Kauch}, \citenamefont {Andergassen}, \citenamefont {Hansmann},
-  \citenamefont {Rohe}, \citenamefont {Vilk}, \citenamefont {LeBlanc},
-  \citenamefont {Zhang}, \citenamefont {Tremblay}, \citenamefont {Ferrero},
-  \citenamefont {Parcollet},\ and\ \citenamefont {Georges}}]{Schafer2021}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Schäfer}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Wentzell}},
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Šimkovic}}, \bibinfo
-  {author} {\bibfnamefont {Y.-Y.}\ \bibnamefont {He}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {Hille}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Klett}}, \bibinfo {author} {\bibfnamefont {C.~J.}\
-  \bibnamefont {Eckhardt}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-  {Arzhang}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Harkov}},
-  \bibinfo {author} {\bibfnamefont {F.~m. c.-M.}\ \bibnamefont {Le~R\'egent}},
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kirsch}}, \bibinfo
-  {author} {\bibfnamefont {Y.}~\bibnamefont {Wang}}, \bibinfo {author}
-  {\bibfnamefont {A.~J.}\ \bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont
-  {E.}~\bibnamefont {Kozik}}, \bibinfo {author} {\bibfnamefont {E.~A.}\
-  \bibnamefont {Stepanov}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Kauch}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Andergassen}},
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Hansmann}}, \bibinfo
-  {author} {\bibfnamefont {D.}~\bibnamefont {Rohe}}, \bibinfo {author}
-  {\bibfnamefont {Y.~M.}\ \bibnamefont {Vilk}}, \bibinfo {author}
-  {\bibfnamefont {J.~P.~F.}\ \bibnamefont {LeBlanc}}, \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
-  {A.-M.~S.}\ \bibnamefont {Tremblay}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Ferrero}}, \bibinfo {author} {\bibfnamefont
-  {O.}~\bibnamefont {Parcollet}},\ and\ \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Georges}},\ }\bibfield  {title} {\bibinfo {title}
-  {Tracking the footprints of spin fluctuations: A multimethod, multimessenger
-  study of the two-dimensional hubbard model},\ }\href
-  {https://doi.org/10.1103/PhysRevX.11.011058} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
-  {pages} {011058} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {White}\ and\ \citenamefont
-  {Scalapino}(1998)}]{White1998}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~R.}\ \bibnamefont
-  {White}}\ and\ \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
-  {Scalapino}},\ }\bibfield  {title} {\bibinfo {title} {Density matrix
-  renormalization group study of the striped phase in the 2d
-  $\mathit{t}\ensuremath{-}\mathit{J}$ model},\ }\href
-  {https://doi.org/10.1103/PhysRevLett.80.1272} {\bibfield  {journal} {\bibinfo
-   {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo
-  {pages} {1272} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ido}\ \emph {et~al.}(2018)\citenamefont {Ido},
-  \citenamefont {Ohgoe},\ and\ \citenamefont {Imada}}]{Ido2018}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Ido}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Ohgoe}},\ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\bibfield
-  {title} {\bibinfo {title} {Competition among various charge-inhomogeneous
-  states and $d$-wave superconducting state in hubbard models on square
-  lattices},\ }\href {https://doi.org/10.1103/PhysRevB.97.045138} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-  {97}},\ \bibinfo {pages} {045138} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Proust}\ and\ \citenamefont
-  {Taillefer}(2019)}]{ProustTaillefer2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Proust}}\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Taillefer}},\ }\bibfield  {title} {\bibinfo {title} {The remarkable
-  underlying ground states of cuprate superconductors},\ }\href
-  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-031218-013210}
-  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-  Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {409}
-  (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ponsioen}\ \emph {et~al.}(2019)\citenamefont
-  {Ponsioen}, \citenamefont {Chung},\ and\ \citenamefont
-  {Corboz}}]{Ponsioen2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-  {Ponsioen}}, \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont
-  {Chung}},\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Corboz}},\ }\bibfield  {title} {\bibinfo {title} {Period 4 stripe in the
-  extended two-dimensional hubbard model},\ }\href
-  {https://doi.org/10.1103/PhysRevB.100.195141} {\bibfield  {journal} {\bibinfo
-   {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {100}},\ \bibinfo
-  {pages} {195141} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Xu}\ \emph {et~al.}(2022)\citenamefont {Xu},
-  \citenamefont {Shi}, \citenamefont {Vitali}, \citenamefont {Qin},\ and\
-  \citenamefont {Zhang}}]{XuZhang2022}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Xu}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Shi}}, \bibinfo
-  {author} {\bibfnamefont {E.}~\bibnamefont {Vitali}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Qin}},\ and\ \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Zhang}},\ }\bibfield  {title} {\bibinfo
-  {title} {Stripes and spin-density waves in the doped two-dimensional hubbard
-  model: Ground state phase diagram},\ }\href
-  {https://doi.org/10.1103/PhysRevResearch.4.013239} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Res.}\ }\textbf {\bibinfo {volume} {4}},\
-  \bibinfo {pages} {013239} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Dave}\ \emph {et~al.}(2013)\citenamefont {Dave},
-  \citenamefont {Phillips},\ and\ \citenamefont {Kane}}]{Phillips2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~B.}\ \bibnamefont
-  {Dave}}, \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\
-  and\ \bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont {Kane}},\
-  }\bibfield  {title} {\bibinfo {title} {Absence of luttinger's theorem due to
-  zeros in the single-particle green function},\ }\href
-  {https://doi.org/10.1103/PhysRevLett.110.090403} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {110}},\
-  \bibinfo {pages} {090403} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Seki}\ and\ \citenamefont
-  {Yunoki}(2017)}]{seki2017topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Seki}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Yunoki}},\
-  }\bibfield  {title} {\bibinfo {title} {Topological interpretation of the
-  luttinger theorem},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Physical Review B}\ }\textbf {\bibinfo {volume} {96}},\ \bibinfo
-  {pages} {085124} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Anderson}\ and\ \citenamefont
-  {Haldane}(2001)}]{Anderson2001}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-  {Anderson}}\ and\ \bibinfo {author} {\bibfnamefont {F.~D.~M.}\ \bibnamefont
-  {Haldane}},\ }\bibfield  {title} {\bibinfo {title} {The symmetries of fermion
-  fluids at low dimensions},\ }\href {https://doi.org/10.1023/A:1010324912515}
-  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Statistical Physics}\
-  }\textbf {\bibinfo {volume} {103}},\ \bibinfo {pages} {425} (\bibinfo {year}
-  {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Huang}\ \emph {et~al.}(2022)\citenamefont {Huang},
-  \citenamefont {Nave},\ and\ \citenamefont {Phillips}}]{Huang2022}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont
-  {Huang}}, \bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont {Nave}},\
-  and\ \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\
-  }\bibfield  {title} {\bibinfo {title} {Discrete symmetry breaking defines the
-  mott quartic fixed point},\ }\href
-  {https://doi.org/10.1038/s41567-022-01529-8} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {18}},\ \bibinfo
-  {pages} {511} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Coleman}\ \emph {et~al.}(2001)\citenamefont
-  {Coleman}, \citenamefont {Pépin}, \citenamefont {Si},\ and\ \citenamefont
-  {Ramazashvili}}]{Coleman_2001}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Coleman}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Pépin}},
-  \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Si}},\ and\ \bibinfo
-  {author} {\bibfnamefont {R.}~\bibnamefont {Ramazashvili}},\ }\bibfield
-  {title} {\bibinfo {title} {How do fermi liquids get heavy and die?},\ }\href
-  {https://doi.org/10.1088/0953-8984/13/35/202} {\bibfield  {journal} {\bibinfo
-   {journal} {Journal of Physics: Condensed Matter}\ }\textbf {\bibinfo
-  {volume} {13}},\ \bibinfo {pages} {R723} (\bibinfo {year}
-  {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
-  {Lal}(2020{\natexlab{b}})}]{anirbanurg1}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Lal}},\ }\bibfield  {title} {\bibinfo {title} {Unitary renormalisation group
-  for correlated electrons-i: a tensor network approach},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nuclear Physics B}\ }\textbf
-  {\bibinfo {volume} {960}},\ \bibinfo {pages} {115170} (\bibinfo {year}
-  {2020}{\natexlab{b}})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
-  {Lal}(2020{\natexlab{c}})}]{anirbanurg2}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Lal}},\ }\bibfield  {title} {\bibinfo {title} {Unitary renormalisation group
-  for correlated electrons-ii: insights on fermionic criticality},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Nuclear Physics B}\ }\textbf
-  {\bibinfo {volume} {960}},\ \bibinfo {pages} {115163} (\bibinfo {year}
-  {2020}{\natexlab{c}})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Keimer}\ \emph {et~al.}(2015)\citenamefont {Keimer},
-  \citenamefont {Kivelson}, \citenamefont {Norman}, \citenamefont {Uchida},\
-  and\ \citenamefont {Zaanen}}]{keimer2015quantum}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-  {Keimer}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
-  {Kivelson}}, \bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
-  {Norman}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Uchida}},\
-  and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zaanen}},\
-  }\bibfield  {title} {\bibinfo {title} {From quantum matter to
-  high-temperature superconductivity in copper oxides},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
-  {volume} {518}},\ \bibinfo {pages} {179} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hatsugai}\ and\ \citenamefont
-  {Kohmoto}(1992)}]{Hatsugai1992}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Hatsugai}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Kohmoto}},\ }\bibfield  {title} {\bibinfo {title} {Exactly solvable model of
-  correlated lattice electrons in any dimensions},\ }\href
-  {https://doi.org/10.1143/JPSJ.61.2056} {\bibfield  {journal} {\bibinfo
-  {journal} {Journal of the Physical Society of Japan}\ }\textbf {\bibinfo
-  {volume} {61}},\ \bibinfo {pages} {2056} (\bibinfo {year}
-  {1992})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Baskaran}(1991)}]{Baskaran1991}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Baskaran}},\ }\bibfield  {title} {\bibinfo {title} {An exactly solvable
-  fermion model: spinons, holons and a non-fermi liquid phase},\ }\href
-  {https://doi.org/10.1142/S0217984991000782} {\bibfield  {journal} {\bibinfo
-  {journal} {Modern Physics Letters B}\ }\textbf {\bibinfo {volume} {05}},\
-  \bibinfo {pages} {643} (\bibinfo {year} {1991})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Altshuler}\ \emph {et~al.}(1998)\citenamefont
-  {Altshuler}, \citenamefont {Chubukov}, \citenamefont {Dashevskii},
-  \citenamefont {Finkel'stein},\ and\ \citenamefont {Morr}}]{Altshuler_1998}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~L.}\ \bibnamefont
-  {Altshuler}}, \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
-  {Chubukov}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Dashevskii}}, \bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
-  {Finkel'stein}},\ and\ \bibinfo {author} {\bibfnamefont {D.~K.}\ \bibnamefont
-  {Morr}},\ }\bibfield  {title} {\bibinfo {title} {Luttinger theorem for a
-  spin-density-wave state},\ }\href {https://doi.org/10.1209/epl/i1998-00164-y}
-  {\bibfield  {journal} {\bibinfo  {journal} {Europhysics Letters}\ }\textbf
-  {\bibinfo {volume} {41}},\ \bibinfo {pages} {401} (\bibinfo {year}
-  {1998})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Heath}\ and\ \citenamefont
-  {Bedell}(2020)}]{Heath_2020}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont
-  {Heath}}\ and\ \bibinfo {author} {\bibfnamefont {K.~S.}\ \bibnamefont
-  {Bedell}},\ }\bibfield  {title} {\bibinfo {title} {Necessary and sufficient
-  conditions for the validity of luttinger’s theorem},\ }\href
-  {https://doi.org/10.1088/1367-2630/ab890e} {\bibfield  {journal} {\bibinfo
-  {journal} {New Journal of Physics}\ }\textbf {\bibinfo {volume} {22}},\
-  \bibinfo {pages} {063011} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Nave}\ \emph {et~al.}(2025)\citenamefont {Nave},
-  \citenamefont {Zhao},\ and\ \citenamefont {Phillips}}]{lanave2025}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont
-  {Nave}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zhao}},\ and\
-  \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\ }\href
-  {https://arxiv.org/abs/2506.04342} {} (\bibinfo {year} {2025}),\ \Eprint
-  {https://arxiv.org/abs/2506.04342} {arXiv:2506.04342 [cond-mat.str-el]}
-  \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mukherjee}\ \emph {et~al.}(2023)\citenamefont
-  {Mukherjee}, \citenamefont {Vidhyadhiraja}, \citenamefont {Taraphder},\ and\
-  \citenamefont {Lal}}]{Mukherjee_2023}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Mukherjee}}, \bibinfo {author} {\bibfnamefont {N.~S.}\ \bibnamefont
-  {Vidhyadhiraja}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Taraphder}},\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Lal}},\ }\bibfield  {title} {\bibinfo {title} {Kondo frustration via charge
-  fluctuations: a route to mott localisation},\ }\href
-  {https://doi.org/10.1088/1367-2630/ad08f3} {\bibfield  {journal} {\bibinfo
-  {journal} {New Journal of Physics}\ }\textbf {\bibinfo {volume} {25}},\
-  \bibinfo {pages} {113011} (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Georges}\ \emph {et~al.}(1996)\citenamefont
-  {Georges}, \citenamefont {Kotliar}, \citenamefont {Krauth},\ and\
-  \citenamefont {Rozenberg}}]{georges1996}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Georges}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Kotliar}},
-  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Krauth}},\ and\ \bibinfo
-  {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Rozenberg}},\ }\bibfield
-  {title} {\bibinfo {title} {Dynamical mean-field theory of strongly correlated
-  fermion systems and the limit of infinite dimensions},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Reviews of Modern Physics}\
-  }\textbf {\bibinfo {volume} {68}},\ \bibinfo {pages} {13} (\bibinfo {year}
-  {1996})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hettler}\ \emph {et~al.}(1998)\citenamefont
-  {Hettler}, \citenamefont {Tahvildar-Zadeh}, \citenamefont {Jarrell},
-  \citenamefont {Pruschke},\ and\ \citenamefont {Krishnamurthy}}]{hettler1998}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Hettler}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Tahvildar-Zadeh}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Jarrell}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Pruschke}},\
-  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Krishnamurthy}},\
-  }\bibfield  {title} {\bibinfo {title} {Nonlocal dynamical correlations of
-  strongly interacting electron systems},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Physical Review B}\ }\textbf {\bibinfo {volume} {58}},\
-  \bibinfo {pages} {R7475} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kotliar}\ \emph {et~al.}(2001)\citenamefont
-  {Kotliar}, \citenamefont {Savrasov}, \citenamefont {P{\'a}lsson},\ and\
-  \citenamefont {Biroli}}]{kotliar2001}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Kotliar}}, \bibinfo {author} {\bibfnamefont {S.~Y.}\ \bibnamefont
-  {Savrasov}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {P{\'a}lsson}},\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Biroli}},\ }\bibfield  {title} {\bibinfo {title} {Cellular dynamical mean
-  field approach to strongly correlated systems},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Physical review letters}\ }\textbf {\bibinfo
-  {volume} {87}},\ \bibinfo {pages} {186401} (\bibinfo {year}
-  {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Maier}\ \emph {et~al.}(2005)\citenamefont {Maier},
-  \citenamefont {Jarrell}, \citenamefont {Schulthess}, \citenamefont {Kent},\
-  and\ \citenamefont {White}}]{maier2005}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont
-  {Maier}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Jarrell}},
-  \bibinfo {author} {\bibfnamefont {T.~C.}\ \bibnamefont {Schulthess}},
-  \bibinfo {author} {\bibfnamefont {P.~R.~C.}\ \bibnamefont {Kent}},\ and\
-  \bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont {White}},\ }\bibfield
-  {title} {\bibinfo {title} {Systematic study of d-wave superconductivity in
-  the 2d repulsive hubbard model},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {95}},\
-  \bibinfo {pages} {237001} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Stoyanova}(2006)}]{stoyanova}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Stoyanova}},\ }\emph {\bibinfo {title} {Delocalized and correlated wave
-  functions for excited states in extended systems}},\ \href@noop {} {Ph.D.
-  thesis},\ \bibinfo  {school} {University of Groningen} (\bibinfo {year}
-  {2006})\BibitemShut {NoStop}%
-\bibitem [{sup()}]{suppmat}%
-  \BibitemOpen
-  \href@noop {} {\bibinfo {title} {See supplemental material for additional
-  information.}}\BibitemShut {Stop}%
-\bibitem [{\citenamefont {Wu}\ \emph {et~al.}(2018)\citenamefont {Wu},
-  \citenamefont {Scheurer}, \citenamefont {Chatterjee}, \citenamefont
-  {Sachdev}, \citenamefont {Georges},\ and\ \citenamefont
-  {Ferrero}}]{WuFerrero2018}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
-  {Wu}}, \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Scheurer}},
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Chatterjee}}, \bibinfo
-  {author} {\bibfnamefont {S.}~\bibnamefont {Sachdev}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Ferrero}},\ }\bibfield  {title} {\bibinfo
-  {title} {Pseudogap and fermi-surface topology in the two-dimensional hubbard
-  model},\ }\href {https://doi.org/10.1103/PhysRevX.8.021048} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume}
-  {8}},\ \bibinfo {pages} {021048} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Tsvelick}\ and\ \citenamefont
-  {Wiegmann}(1985)}]{Tsvelick_weigmann_mchannel_1985}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
-  {Tsvelick}}\ and\ \bibinfo {author} {\bibfnamefont {P.~B.}\ \bibnamefont
-  {Wiegmann}},\ }\bibfield  {title} {\bibinfo {title} {Exact solution of the
-  multichannel kondo problem, scaling, and integrability},\ }\href
-  {https://doi.org/10.1007/BF01017853} {\bibfield  {journal} {\bibinfo
-  {journal} {Journal of Statistical Physics}\ }\textbf {\bibinfo {volume}
-  {38}},\ \bibinfo {pages} {125} (\bibinfo {year} {1985})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Emery}\ and\ \citenamefont
-  {Kivelson}(1992)}]{emery_kivelson}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~J.}\ \bibnamefont
-  {Emery}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Kivelson}},\ }\bibfield  {title} {\bibinfo {title} {Mapping of the
-  two-channel kondo problem to a resonant-level model},\ }\href
-  {https://doi.org/10.1103/PhysRevB.46.10812} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {46}},\ \bibinfo
-  {pages} {10812} (\bibinfo {year} {1992})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Gunnarsson}\ \emph {et~al.}(2003)\citenamefont
-  {Gunnarsson}, \citenamefont {Calandra},\ and\ \citenamefont
-  {Han}}]{GunnarssonRMP2003}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
-  {Gunnarsson}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Calandra}},\ and\ \bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont
-  {Han}},\ }\bibfield  {title} {\bibinfo {title} {Colloquium: Saturation of
-  electrical resistivity},\ }\href {https://doi.org/10.1103/RevModPhys.75.1085}
-  {\bibfield  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf
-  {\bibinfo {volume} {75}},\ \bibinfo {pages} {1085} (\bibinfo {year}
-  {2003})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hussey}\ \emph {et~al.}(2004)\citenamefont {Hussey},
-  \citenamefont {Takenaka},\ and\ \citenamefont {Takagi}}]{Hussey2004}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
-  {Hussey}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Takenaka}},\
-  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\
-  }\bibfield  {title} {\bibinfo {title} {Universality of the
-  mott–ioffe–regel limit in metals},\ }\href
-  {https://doi.org/10.1080/14786430410001716944} {\bibfield  {journal}
-  {\bibinfo  {journal} {Philosophical Magazine}\ }\textbf {\bibinfo {volume}
-  {84}},\ \bibinfo {pages} {2847} (\bibinfo {year} {2004})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Pustogow}\ \emph {et~al.}(2021)\citenamefont
-  {Pustogow}, \citenamefont {Saito}, \citenamefont {Anja~Löhle}, \citenamefont
-  {Alonso}, \citenamefont {Kawamoto}, \citenamefont {Dobrosavljevic},
-  \citenamefont {Dressel},\ and\ \citenamefont {Fratini}}]{pustogow2021}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Pustogow}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Saito}},
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Anja~Löhle}}, \bibinfo
-  {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Alonso}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Kawamoto}}, \bibinfo {author}
-  {\bibfnamefont {V.}~\bibnamefont {Dobrosavljevic}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Dressel}},\ and\ \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Fratini}},\ }\bibfield  {title} {\bibinfo
-  {title} {Rise and fall of landau’s quasiparticles while approaching the
-  mott transition},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Nat. Comm.}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {1571}
-  (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Qazilbash}\ \emph {et~al.}(2008)\citenamefont
-  {Qazilbash}, \citenamefont {Schafgans}, \citenamefont {Burch}, \citenamefont
-  {Yun}, \citenamefont {Chae}, \citenamefont {Kim}, \citenamefont {Kim},\ and\
-  \citenamefont {Basov}}]{qazilbash2008}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~M.}\ \bibnamefont
-  {Qazilbash}}, \bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont
-  {Schafgans}}, \bibinfo {author} {\bibfnamefont {K.~S.}\ \bibnamefont
-  {Burch}}, \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont {Yun}},
-  \bibinfo {author} {\bibfnamefont {B.~G.}\ \bibnamefont {Chae}}, \bibinfo
-  {author} {\bibfnamefont {B.~J.}\ \bibnamefont {Kim}}, \bibinfo {author}
-  {\bibfnamefont {H.~T.}\ \bibnamefont {Kim}},\ and\ \bibinfo {author}
-  {\bibfnamefont {D.~N.}\ \bibnamefont {Basov}},\ }\bibfield  {title} {\bibinfo
-  {title} {Electrodynamics of the vanadium oxides $\mathrm{V}{\mathrm{o}}_{2}$
-  and ${\mathrm{v}}_{2}{\mathrm{o}}_{3}$},\ }\href
-  {https://doi.org/10.1103/PhysRevB.77.115121} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo
-  {pages} {115121} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hauke}\ \emph {et~al.}(2016)\citenamefont {Hauke},
-  \citenamefont {Heyl}, \citenamefont {Tagliacozzo},\ and\ \citenamefont
-  {Zoller}}]{Hauke2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Hauke}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Heyl}},
-  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Tagliacozzo}},\ and\
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Zoller}},\ }\bibfield
-  {title} {\bibinfo {title} {Measuring multipartite entanglement through
-  dynamic susceptibilities},\ }\href {https://doi.org/10.1038/nphys3700}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf
-  {\bibinfo {volume} {12}},\ \bibinfo {pages} {778} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Balut}\ \emph {et~al.}(2025)\citenamefont {Balut},
-  \citenamefont {Guo}, \citenamefont {de~Vriesa}, \citenamefont {Chaudhuri},
-  \citenamefont {Bradlyn}, \citenamefont {Abbamonte},\ and\ \citenamefont
-  {W.}}]{balut2025}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Balut}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Guo}}, \bibinfo
-  {author} {\bibfnamefont {N.}~\bibnamefont {de~Vriesa}}, \bibinfo {author}
-  {\bibfnamefont {D.}~\bibnamefont {Chaudhuri}}, \bibinfo {author}
-  {\bibfnamefont {B.}~\bibnamefont {Bradlyn}}, \bibinfo {author} {\bibfnamefont
-  {P.}~\bibnamefont {Abbamonte}},\ and\ \bibinfo {author} {\bibfnamefont
-  {P.~P.}\ \bibnamefont {W.}},\ }\bibfield  {title} {\bibinfo {title} {Quantum
-  fisher information reveals uv-ir mixing in the strange metal},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Physica C}\ }\textbf {\bibinfo
-  {volume} {635}},\ \bibinfo {pages} {1354750} (\bibinfo {year}
-  {2025})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mazza}\ \emph {et~al.}(2024)\citenamefont {Mazza},
-  \citenamefont {Biswas}, \citenamefont {Yan}, \citenamefont {Prokofiev},
-  \citenamefont {Steffens}, \citenamefont {Si}, \citenamefont {Assaad},\ and\
-  \citenamefont {Paschen}}]{mazza2024}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Mazza}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Biswas}},
-  \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Yan}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Prokofiev}}, \bibinfo {author}
-  {\bibfnamefont {P.}~\bibnamefont {Steffens}}, \bibinfo {author}
-  {\bibfnamefont {Q.}~\bibnamefont {Si}}, \bibinfo {author} {\bibfnamefont
-  {F.~F.}\ \bibnamefont {Assaad}},\ and\ \bibinfo {author} {\bibfnamefont
-  {S.}~\bibnamefont {Paschen}},\ }\href {https://arxiv.org/abs/2403.12779} {}
-  (\bibinfo {year} {2024}),\ \Eprint {https://arxiv.org/abs/2403.12779}
-  {arXiv:2403.12779 [cond-mat.str-el]} \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Si}\ \emph {et~al.}(2001)\citenamefont {Si},
-  \citenamefont {Rabello}, \citenamefont {Ingersent},\ and\ \citenamefont
-  {Smith}}]{Si2001}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont
-  {Si}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Rabello}},
-  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Ingersent}},\ and\
-  \bibinfo {author} {\bibfnamefont {J.~L.}\ \bibnamefont {Smith}},\ }\bibfield
-  {title} {\bibinfo {title} {Locally critical quantum phase transitions in
-  strongly correlated metals},\ }\href {https://doi.org/10.1038/35101507}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
-  {volume} {413}},\ \bibinfo {pages} {804} (\bibinfo {year}
-  {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Senthil}(2008)}]{senthil2008CriticalFermiSurface}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Senthil}},\ }\bibfield  {title} {\bibinfo {title} {Critical fermi surfaces
-  and non-fermi liquid metals},\ }\href
-  {https://doi.org/10.1103/PhysRevB.78.035103} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {78}},\ \bibinfo
-  {pages} {035103} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sekino}\ and\ \citenamefont
-  {Susskind}(2008)}]{sekino2008}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Sekino}}\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Susskind}},\ }\bibfield  {title} {\bibinfo {title} {Fast scramblers},\
-  }\href {https://doi.org/10.1088/1126-6708/2008/10/065} {\bibfield  {journal}
-  {\bibinfo  {journal} {Journal of High Energy Physics}\ }\textbf {\bibinfo
-  {volume} {2008}},\ \bibinfo {pages} {065} (\bibinfo {year}
-  {2008})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hayden}\ and\ \citenamefont
-  {Preskill}(2007)}]{hayden2007}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Hayden}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Preskill}},\ }\bibfield  {title} {\bibinfo {title} {Black holes as mirrors:
-  quantum information in random subsystems},\ }\href
-  {https://doi.org/10.1088/1126-6708/2007/09/120} {\bibfield  {journal}
-  {\bibinfo  {journal} {Journal of High Energy Physics}\ }\textbf {\bibinfo
-  {volume} {2007}},\ \bibinfo {pages} {120} (\bibinfo {year}
-  {2007})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bentsen}\ \emph {et~al.}(2019)\citenamefont
-  {Bentsen}, \citenamefont {Hashizume}, \citenamefont {Buyskikh}, \citenamefont
-  {Davis}, \citenamefont {Daley}, \citenamefont {Gubser},\ and\ \citenamefont
-  {Schleier-Smith}}]{bentsen2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Bentsen}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Hashizume}},
-  \bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont {Buyskikh}}, \bibinfo
-  {author} {\bibfnamefont {E.~J.}\ \bibnamefont {Davis}}, \bibinfo {author}
-  {\bibfnamefont {A.~J.}\ \bibnamefont {Daley}}, \bibinfo {author}
-  {\bibfnamefont {S.~S.}\ \bibnamefont {Gubser}},\ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Schleier-Smith}},\ }\bibfield  {title}
-  {\bibinfo {title} {Treelike interactions and fast scrambling with cold
-  atoms},\ }\href {https://doi.org/10.1103/PhysRevLett.123.130601} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
-  {volume} {123}},\ \bibinfo {pages} {130601} (\bibinfo {year}
-  {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2020)\citenamefont
-  {Phillips}, \citenamefont {Yeo},\ and\ \citenamefont {Huang}}]{Phillips2020}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-  {Phillips}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Yeo}},\ and\
-  \bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont {Huang}},\ }\bibfield
-  {title} {\bibinfo {title} {Exact theory for superconductivity in a doped mott
-  insulator},\ }\href {https://doi.org/10.1038/s41567-020-0988-4} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
-  {16}},\ \bibinfo {pages} {1175} (\bibinfo {year} {2020})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Vafek}\ and\ \citenamefont
-  {Vishwanath}(2014)}]{vafekvishwanath2014}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
-  {Vafek}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Vishwanath}},\ }\bibfield  {title} {\bibinfo {title} {Dirac fermions in
-  solids: From high-tc cuprates and graphene to topological insulators and weyl
-  semimetals},\ }\href
-  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-031113-133841}
-  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-  Physics}\ }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {83} (\bibinfo
-  {year} {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Morimoto}\ and\ \citenamefont
-  {Nagaosa}(2016)}]{morimoto2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Morimoto}}\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Nagaosa}},\ }\bibfield  {title} {\bibinfo {title} {Weyl mott insulator},\
-  }\href {https://doi.org/10.1038/srep19853} {\bibfield  {journal} {\bibinfo
-  {journal} {Sci. Rep.}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages}
-  {19853} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Flores-Calder\'on}\ and\ \citenamefont
-  {Hooley}(2025)}]{calderon2025}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Flores-Calder\'on}}\ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Hooley}},\ }\bibfield  {title} {\bibinfo {title} {Weyl-mott point:
-  Topological and non-fermi liquid behavior from an isolated green's function
-  zero},\ }\href {https://doi.org/10.1103/k4st-77ph} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {111}},\
-  \bibinfo {pages} {235139} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Georgi}(2007{\natexlab{a}})}]{Georgi2007PRL}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Georgi}},\ }\bibfield  {title} {\bibinfo {title} {Unparticle physics},\
-  }\href {https://doi.org/10.1103/PhysRevLett.98.221601} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {98}},\
-  \bibinfo {pages} {221601} (\bibinfo {year} {2007}{\natexlab{a}})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Georgi}(2007{\natexlab{b}})}]{Georgi2007}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Georgi}},\ }\bibfield  {title} {\bibinfo {title} {Another odd thing about
-  unparticle physics},\ }\href
-  {https://doi.org/https://doi.org/10.1016/j.physletb.2007.05.037} {\bibfield
-  {journal} {\bibinfo  {journal} {Physics Letters B}\ }\textbf {\bibinfo
-  {volume} {650}},\ \bibinfo {pages} {275} (\bibinfo {year}
-  {2007}{\natexlab{b}})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Phillips}(2014)}]{PhillipsLectures2014}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-  {Phillips}},\ }\bibfield  {title} {\bibinfo {title} {Beyond particles:
-  Unparticles in strongly correlated electron matter},\ }in\ \href@noop {}
-  {\emph {\bibinfo {booktitle} {Quantum Criticality in Condensed Matter}}},\
-  \bibinfo {editor} {edited by\ \bibinfo {editor} {\bibfnamefont
-  {J.}~\bibnamefont {Jedrzejewski}}}\ (\bibinfo  {publisher} {World Scientific,
-  Singapore},\ \bibinfo {year} {2014})\ pp.\ \bibinfo {pages}
-  {133--158}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zaanen}(2019)}]{zaanen2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Zaanen}},\ }\bibfield  {title} {\bibinfo {title} {Planckian dissipation,
-  minimal viscosity and the transport in cuprate strange metals},\ }\href
-  {https://doi.org/10.21468/SciPostPhys.6.5.061} {\bibfield  {journal}
-  {\bibinfo  {journal} {SciPost Phys.}\ }\textbf {\bibinfo {volume} {6}},\
-  \bibinfo {pages} {061} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Legros}\ \emph {et~al.}(2019)\citenamefont {Legros},
-  \citenamefont {Benhabib}, \citenamefont {Tabis}, \citenamefont
-  {Lalibert{\'e}}, \citenamefont {Dion}, \citenamefont {Lizaire}, \citenamefont
-  {Vignolle}, \citenamefont {Vignolles}, \citenamefont {Raffy}, \citenamefont
-  {Li} \emph {et~al.}}]{legros2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Legros}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Benhabib}},
-  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Tabis}}, \bibinfo
-  {author} {\bibfnamefont {F.}~\bibnamefont {Lalibert{\'e}}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Dion}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Lizaire}}, \bibinfo {author} {\bibfnamefont
-  {B.}~\bibnamefont {Vignolle}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Vignolles}}, \bibinfo {author} {\bibfnamefont
-  {H.}~\bibnamefont {Raffy}}, \bibinfo {author} {\bibfnamefont
-  {Z.}~\bibnamefont {Li}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
-  {title} {Universal $ t $-linear resistivity and planckian dissipation in
-  overdoped cuprates},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {15}},\ \bibinfo
-  {pages} {142} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hartnoll}\ and\ \citenamefont
-  {Mackenzie}(2022)}]{hartnoll2022}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
-  {Hartnoll}}\ and\ \bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont
-  {Mackenzie}},\ }\bibfield  {title} {\bibinfo {title} {Colloquium: Planckian
-  dissipation in metals},\ }\href
-  {https://doi.org/10.1103/RevModPhys.94.041002} {\bibfield  {journal}
-  {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {94}},\
-  \bibinfo {pages} {041002} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {McGreevy}(2023)}]{McGreevy2023}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {McGreevy}},\ }\bibfield  {title} {\bibinfo {title} {Generalized symmetries
-  in condensed matter},\ }\href
-  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-040721-021029}
-  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-  Physics}\ }\textbf {\bibinfo {volume} {14}},\ \bibinfo {pages} {57} (\bibinfo
-  {year} {2023})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Luttinger}\ and\ \citenamefont
-  {Ward}(1960)}]{luttinger1960ground}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-  {Luttinger}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
-  {Ward}},\ }\bibfield  {title} {\bibinfo {title} {Ground-state energy of a
-  many-fermion system. ii},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Physical Review}\ }\textbf {\bibinfo {volume} {118}},\ \bibinfo
-  {pages} {1417} (\bibinfo {year} {1960})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Su}\ and\ \citenamefont
-  {Martin}(2025)}]{su2025anomalies}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Su}}\ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Martin}},\
-  }\href {https://arxiv.org/abs/2405.08093} {} (\bibinfo {year} {2025}),\
-  \Eprint {https://arxiv.org/abs/2405.08093} {arXiv:2405.08093
-  [cond-mat.str-el]} \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Adler}(1969)}]{adler1969axial}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont
-  {Adler}},\ }\bibfield  {title} {\bibinfo {title} {Axial-vector vertex in
-  spinor electrodynamics},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Physical Review}\ }\textbf {\bibinfo {volume} {177}},\ \bibinfo
-  {pages} {2426} (\bibinfo {year} {1969})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bell}\ and\ \citenamefont
-  {Jackiw}(1969)}]{bell1969pcac}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~S.}\ \bibnamefont
-  {Bell}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Jackiw}},\
-  }\bibfield  {title} {\bibinfo {title} {A pcac puzzle: $\pi$0→
-  $\gamma$$\gamma$ in the $\sigma$-model},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Il Nuovo Cimento A}\ }\textbf {\bibinfo
-  {volume} {60}},\ \bibinfo {pages} {47} (\bibinfo {year} {1969})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Casini}\ and\ \citenamefont
-  {Mag\'{a}n}(2021)}]{Casini2021Symmetries}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Casini}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-  {Mag\'{a}n}},\ }\bibfield  {title} {\bibinfo {title} {On completeness and
-  generalized symmetries in quantum field theory},\ }\href
-  {https://doi.org/10.1142/S0217732321300251} {\bibfield  {journal} {\bibinfo
-  {journal} {Modern Physics Letters A}\ }\textbf {\bibinfo {volume} {36}},\
-  \bibinfo {pages} {2130025} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
-\end{thebibliography}
-
-\vspace{0.25cm}
-\par\noindent\textbf{Acknowledgements.}
+Its fate under finite doping presents a compelling direction for future investigation.
+
+\bibliography{tilingProject}
+
+\vspace{0.25cm}
+\par\noindent\textbf{Acknowledgments.}
 We acknowledge National Supercomputing Mission (NSM) for providing computing resources of ‘PARAM RUDRA’ at Aruna Asaf Ali Marg, near Vasant Kunj, New Delhi, Delhi 110067, which is implemented by C-DAC and supported by the Ministry of Electronics and Information Technology (MeitY) and Department of Science and Technology (DST), Government of India.
-SL thanks Mayank Shreshtha for designing Fig.1.
-
-\vspace{0.25cm}
-\par\noindent\textbf{Funding.}
 SL thanks the SERB, Govt.
@@
 AM thanks IISER Kolkata for funding through a JRF and an SRF.
-AM would also like to acknowledge the SERB-MATRICS grant (Grant No.
+A.M.
+would also like to acknowledge the SERB-MATRICS grant (Grant No.
 MTR/2022/000636) from the Science and Engineering Research Board (SERB) for funding.
+S.L.
+thanks Mayank Shreshtha for designing Fig.1.
 
@@
 \par\noindent\textbf{Author Contributions.}
-AM, SRH and SL conceived and designed the research.
-AM performed the calculations and analysis with support from all authors.
-AM, SRH, AM, NSV, AT and SL wrote the manuscript.
-All work was supervised by SL.
-
-\vspace{0.25cm}
-\par\noindent\textbf{Code Availability.}
-The underlying code for this study is not publicly available but may be made available to qualified researchers on reasonable request from the corresponding author.
-
-\vspace{0.25cm}
-\par\noindent\textbf{Competing Interest.}
-The authors declare no competing interests.
+A.M., S.R.H.
+and S.L.
+conceived and designed the research.
+A.M.
+performed the calculations and analysis with support from all authors.
+A.M., S.R.H., A.M.
+and S.L.
+wrote the manuscript with inputs from all authors.
+All work was supervised by S.L.
+
+\vspace{0.25cm}
+\par\noindent\textbf{Code Availability}
+The codes created and datasets generated during this research are available from the corresponding author upon reasonable request.
 
@@
 \noindent
-To avoid overcounting of the non-interacting bath terms, we subtract extra copies of of the kinetic energy term. The final reconstructed extended Hubbard model then reads:
+To avoid overcounting of the non-interacting bath terms, we subtract extra copies of $\mathcal{H}_{\text{cbath-nint}}$. The final reconstructed Hubbard–Heisenberg model then reads:
 \begin{equation}
 \begin{aligned}
-\mathcal{H}_{\text{tiled}} = & -\frac{1}{\sqrt{\mathcal{Z}}} \tilde{t} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
+\mathcal{H}_{\text{HH}} = & -\frac{1}{\sqrt{\mathcal{Z}}} \tilde{t} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
 & + \frac{\tilde{J}}{\mathcal{Z}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle} \mathbf{S}_{\mathbf{r}_i} \cdot \mathbf{S}_{\mathbf{r}_j} - \frac{1}{2} \tilde{U} \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2,

### 2025-12-10 submissions/TilingUploadROPP/Tiling_Project/manuscript_RP.tex
started creating referee response

--- 2025-12-10 submissions/TilingUploadNJP/manuscript_NJP.tex
@@
 It thus provides a versatile and controlled route for engineering strongly correlated models, particularly in regimes where PG formation, NFL scaling, and Mott physics intersect.
-
-We now describe the layout of the work.
-In section \ref{auxurgsection}, we formulate the lattice-embedded auxiliary quantum impurity model and sketch the unitary renormalisation group (URG) method employed to analyse the impurity model.
-In section \ref{tilingsection}, we formulate the tiling procedure by which to map the impurity Hamiltonian, eigenstates and observables into a lattice model of strongly correlated electrons via the usage of many-body translation operators.
-Section \ref{kondobreakdownsection} displays the destruction of the Fermi liquid from the breakdown of Kondo screening, leading to a pseudogapped non-Fermi liquid phase of matter.
-The novel properties of this phase are rigorously established in section \ref{NFLproperties}.
-In section \ref{exactsolforMottCrit}, we demonstrate that the continuous transition between the pseudogap and Mott insulating phases is described by the exactly solvable Hatsugai-Kohmoto model.
-We demonstrate in section \ref{pseudogapasnovelphase} the universal organising principle that is responsible for the emergence of the pseudogap non-Fermi liquid phase.
-This also unveils the pseudogap as the strongly coupled long-range entangled parent metal of the Mott insulator.
-We conclude in section \ref{conclusions}.
-Finally, we present appendices containing the derivation of the URG analysis of the impurity model, and the exactly solvable model at the critical point.
 
@@
 
-\subsection{Mapping eigenstates using a many-body Bloch's theorem}
+\subsection{Mapping eigenstates using a manybody Bloch's theorem}
 As mentioned above, the eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using  the tiling procedure enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, as the tiling procedure restores the translation symmetry of the Hamiltonian.
@@
 \end{aligned}\end{equation}
-Using eq.~\eqref{eigenstateProposal1}, eq.~\eqref{greensFunction1} becomes
+Using eq.~\ref{eigenstateProposal1}, eq.~\ref{greensFunction1} becomes
 \begin{widetext}
@@
 where \(\ket{\chi_n^\pm(\vec r^\prime,\vec\Delta^\prime)} = \frac{1}{\sqrt 2}\left[\ket{\psi_n(\vec r^\prime)} \pm e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime + \vec\Delta^\prime)}\right] \) are the eigenvectors of the tunnelling Hamiltonian with eigenvalues \(\pm 1\) respectively.
-With this basis transformation, we can rewrite eq.~\eqref{greensfunction3} as
+With this basis transformation, we can rewrite eq.~\ref{greensfunction3} as
 \begin{equation}\begin{aligned}
@@
     \includegraphics[width=0.49\linewidth]{tiled_I2_k_N_2000-3.pdf}
-    \caption{Left: Spin correlations \(\chi_s\) for the {\it tiled model}, between the nodal point \(k_N = \left( -\pi/2, -\pi/2\right)\) and an arbitrary \(k-\)point on the Fermi surface.
+    \caption{Left: Spin-spin correlations \(\chi_s\) for the {\it tiled model}, between the nodal point \(k_N = \left( -\pi/2, -\pi/2\right)\) and an arbitrary \(k-\)point on the Fermi surface.
 In the PG, the spin-correlations near the antinode vanish, indicating that they have been removed from the metallic excitations, while the correlations near the nodal point become enhanced because of the increasingly correlated nature of the metal.
@@
 \end{figure*}
-\section{Pseudogap Formation via Kondo Breakdown}\label{kondobreakdownsection}
+\section{Pseudogap Formation via Kondo Breakdown}
 
@@
 
-\section{Non-Fermi liquid excitations within the Pseudogap}\label{NFLproperties}
+\section{Non-Fermi liquid excitations within the Pseudogap}
 \subsection{Pseudogapped spectral function and singular self-energy}
@@
 
-\section{Exactly solvable nodal Non-Fermi liquid at Mott Criticality}\label{exactsolforMottCrit}
+\section{Exactly solvable nodal Non-Fermi liquid at Mott Criticality}
 Very close to the transition, the excitations of the nodal NFL correspond to those of a Hatsugai-Kohmoto model~\cite{Baskaran1991,Hatsugai1992}.
@@
     \centering
-    \hspace*{-1cm}
     \includegraphics[width=0.9\linewidth]{Ad_fit.pdf}
@@
     \includegraphics[width=\textwidth]{fig6.pdf}
-    \caption{(a) Spin correlation $\braket{{\bf S}_d \cdot {\bf S}_r}$  and (b) mutual information $I_{2}(d,r)$  between the impurity spin and conduction bath local spin density as a function of the distance {\bf r} between them, normalised against the value at $r=1$.
+    \caption{(a) Spin-flip correlation $\braket{{\bf S}_d \cdot {\bf S}_r}$  and (b) mutual information $I_{2}(d,r)$  between the impurity spin and conduction bath local spin density as a function of the distance {\bf r} between them, normalised against the value at $r=1$.
 Both decay very quickly in the FL phase (blue), but show long-ranged behaviour in the NFL phase (green and red), extending to the edges of the system at the critical point (red).
@@
 
-\section{Pseudogap as a strongly coupled phase of quantum matter}\label{pseudogapasnovelphase}
+\section{Pseudogap as a strongly coupled phase of quantum matter}
 We now unveil an organising principle that leads to the remarkable properties observed above for the strongly interacting NFL of the PG phase.
@@
 
-\section{Conclusions}\label{conclusions}
-Our analysis reveals that the Mott transition proceeds via a continuous evolution through a PG regime characterized by a singular NFL metal - the Mott metal - with deconfined holon–doublon excitations confined to nodal Fermi arcs, and a scaling of it's spectral features with universal power-law exponents.
-As the system approaches criticality, this metallic phase exhibits increasingly non-local correlations and a divergent self-energy, signalling the breakdown of Landau quasiparticles, formation of local moments and the onset of long-range quantum entanglement.
+\section{Conclusions}
+Our analysis reveals that the Mott transition proceeds via a continuous evolution through a PG regime characterized by a singular NFL metal - the Mott metal - with deconfined holon–doublon excitations confined to nodal Fermi arcs.
+As the system approaches criticality, this metallic phase exhibits increasingly non-local correlations and a divergent self-energy, signalling the breakdown of Landau quasiparticles and the onset of long-range quantum entanglement.
 Anchored in two-channel Kondo dynamics at intermediate scales and governed by Hatsugai–Kohmoto physics near the critical endpoint, the Mott metal provides a unified framework for understanding anomalous metallicity in strongly correlated systems.
-It's fate under finite doping presents a compelling direction for future investigation.
+Its fate under finite doping presents a compelling direction for future investigation.
 

### 2025-12-10 submissions/TilingUploadROPP/manuscript_RP.tex
started creating referee response

--- 2025-12-10 submissions/TilingUploadNJP/manuscript_NJP.tex
@@
 
-\section{Conclusions}\label{conclusions}
+\section{Conclusions}
 Our analysis reveals that the Mott transition proceeds via a continuous evolution through a PG regime characterized by a singular NFL metal - the Mott metal - with deconfined holon–doublon excitations confined to nodal Fermi arcs, and a scaling of it's spectral features with universal power-law exponents.

### 2025-12-10 submissions/TilingUpload_Nature/manuscript_Final.tex
started creating referee response

--- 2025-12-10 submissions/TilingUploadROPP/Tiling_Project/manuscript_Final.tex
@@
 \noindent
-A key challenge in quantum matter involves understanding how strong electronic repulsion obtains the breakdown of quasiparticle excitations in a Fermi liquid and the transition into Mott insulation.
-The difficulty lies in assessing the role of Luttinger surfaces, zeros of the single-particle Greens function that replace the poles lying on the Fermi surface.
-Luttinger surfaces are observed to proliferate in the pseudogap regime of Mott systems, resulting in Fermi arcs whose gapless excitations remain unknown.
+The phenomenon of Mott insulation involves the localization of itinerant electrons due to strong local repulsion.
+Upon doping, a pseudogap (PG) phase emerges - marked by selective gapping of the Fermi surface without conventional symmetry breaking in spin or charge channels.
+A key challenge is understanding how quasiparticle breakdown in the Fermi liquid gives rise to this enigmatic state, and how it connects to both the Mott insulating and superconducting phases.
 Here, we develop a renormalization-based construction of strongly correlated lattice models that captures the emergence of the pseudogap phase and its transition to a Mott insulator.
 Applying a many-body tiling scheme to the fixed-point impurity model uncovers a lattice model with electron interactions and Kondo physics.
-At half-filling, the interplay between Kondo screening and bath charge fluctuations in the impurity model leads to Fermi liquid breakdown.
-This reveals a pseudogap phase characterized by a non-Fermi liquid (the Mott metal) residing on nodal arcs, gapped antinodal regions of the Fermi surface, and an anomalous scaling of the electronic scattering rate with frequency.
+At half-filling,
+%the interplay between Kondo screening and bath charge fluctuations in the impurity model leads to Fermi liquid breakdown. 
+this reveals a pseudogap phase characterized by a non-Fermi liquid (the Mott metal) residing on nodal arcs, gapped antinodal regions of the Fermi surface, and an anomalous scaling of the electronic scattering rate with frequency.
 The eventual confinement of holon–doublon excitations of this exotic metal obtains a continuous transition into the Mott insulator.
@@
 \par\noindent\textbf{\large Introduction}\\
-\noindent
-The Landau quasiparticle paradigm~\cite{landau1959theory} underpins our understanding of metallic behaviour, where the screening of long-ranged repulsive interactions between delocalised electrons leads to well-defined excitations that carry the same quantum numbers as free electrons.
-This remarkable phenomenon - known as adiabatic continuity -  is captured by excitations described by poles of the single-particle Greens function of the interacting system.
-But what defines metallicity when quasiparticles are no longer well-defined~\cite{Phillips2013Unparticles}?
-Can a surface of zeros of the Greens function~\cite{dzyaloshinskii2003some}, rather than poles forming a Fermi surface, define an entirely new kind of metal?
-Could such an exotic state serve as the precursor to Mott localisation driven purely by repulsion, and without invoking magnetic order~\cite{Mott_1949}?
-These questions necessitate a radical departure in understanding conduction in correlated electron systems beyond the quasiparticle paradigm~\cite{phillips2022}.
-\\
+Understanding the breakdown of Fermi liquid (FL) \textcolor{blue}{metallic} behavior and the origin of the pseudogap (PG) in doped Mott systems remains a central challenge in correlated electron physics.
+The PG phase – characterised by a selective depletion of low-energy spectral weight on the Fermi surface – has been widely reported in experiments~\cite{taillefer2010,FradkinRevModPhys2015,Hashimoto2014,Sato2017,DoironLeyraud2017,Mukhopadhyay2019,Naman2021,Masafumi2025} and studied theoretically within the hole-doped two-dimensional Hubbard model~\cite{KyungKotliar2006,MacridinAzevedo2006,sakai2009evolution,werner2009momentum,sakai2010doped,lin2010,gull2010momentum,gull2012,Mirzaei2013,gull2013,anirbanmott2,HilleAndergassen2020,Jiang2022}.
+Yet its microscopic origin, connection to Mott and superconducting phases~\cite{Scheurer2018,Krien2022,Kitatani2023,Sorella2023}, and nature of the nodal–antinodal dichotomy~\cite{Schafer2021} remain unresolved.
+Furthermore, the origin of experimentally observed finite-temperature crossovers in $T=0$ quantum states is poorly understood~\cite{White1998,Ido2018,ProustTaillefer2019,Ponsioen2019,XuZhang2022}.
 
 \noindent
-The anomalous pseudogap (PG) phase, observed in the cuprates, exhibits nodal-antinodal dichotomy with spectral weight concentrated on Fermi arcs around the nodal regions~\cite{loeserKapitulnik1996, Norman1998, Hashimoto2014}.
-In the PG phase of such Mott systems
-~\cite{taillefer2010,FradkinRevModPhys2015,Sato2017,DoironLeyraud2017,Mukhopadhyay2019,Naman2021,Masafumi2025,KyungKotliar2006,MacridinAzevedo2006,sakai2009evolution,werner2009momentum,sakai2010doped,lin2010,gull2010momentum,gull2012,Mirzaei2013,gull2013,anirbanmott2,HilleAndergassen2020,Jiang2022,Scheurer2018,Krien2022,Kitatani2023,Sorella2023,Schafer2021,White1998,Ido2018,ProustTaillefer2019,Ponsioen2019,XuZhang2022}, the single-particle Green’s function develops surfaces of zeros, also known as Luttinger surfaces~\cite{Phillips2013,dzyaloshinskii2003some}, that signals a fundamental obstruction to quasiparticle formation.
-As interaction strength increases, these zero surfaces proliferate, fragmenting the Fermi surface into nodal arcs~\cite{sakai2009evolution,Phillips2013}, violating the Luttinger sum rule by reconfiguring Fermi volume~\cite{seki2017topological}, and breaking an emergent $\mathbb{Z}_2$ symmetry associated with the conservation of spin currents in Fermi liquids~\cite{Anderson2001,Huang2022}.
-Unlike conventional instabilities driven by poles, this phenomenon marks a topological breakdown of Fermi liquid theory~\cite{Coleman_2001,Phillips2013Unparticles}.
-We show that this breakdown arises from a strongly entangled, scale-invariant state of quantum matter, one that serves as the parent metal to the Mott insulator in a half-filled lattice model of strongly correlated electrons.
-This offers a concrete, controlled framework to understand both the non-quasiparticle character of the pseudogap phase and its continuous evolution into a repulsion-driven insulator, in full alignment with Mott's original vision~\cite{Mott_1949}.\\
+The breakdown of \textcolor{blue}{electronic} Landau quasiparticles in the PG regime is tied to the emergence of Luttinger surfaces - zero contours of the Green’s function that fragment the Fermi surface (FS) into nodal arcs~\cite{Phillips2013,dzyaloshinskii2003some}.
+These surfaces proliferate with increasing interaction strength, reconfiguring the Fermi volume~\cite{seki2017topological}, and breaking the emergent $\mathbb{Z}_2$ symmetry associated with separately conserved spin currents in the FL~\cite{Anderson2001,Huang2022}.
+Unlike conventional instabilities, these zeros signal a fundamental topological obstruction to quasiparticle formation~\cite{Coleman_2001,Phillips2013Unparticles}.
+\textcolor{blue}{The microscopic mechanism behind the formation of the Luttinger surfaces, the stability of the resulting non-Fermi liquid (NFL) metal, and the transition to the Mott insulating state likely have their origin in a strongly interacting, densely entangled scale-invariant state of matter~\cite{Phillips2013Unparticles}.
+Here, we demonstrate that such an exotic quantum phase acts as the parent metal of the interaction-tuned Mott insulator in a half-filled lattice model of strongly correlated electrons.}
+%Yet the microscopic mechanism behind their formation, the stability of the resulting non-Fermi liquid (NFL) metal, and the transition to the Mott insulating state remain poorly understood.
 
@@
 \noindent
-Our approach involves developing a renormalization group (RG)-based impurity-to-lattice framework that reconstructs the low-energy physics of a strongly correlated system from the fixed-point structure of a quantum impurity model (Fig.~\ref{schematic}, left).
+We address these questions by developing a renormalization group (RG)-based impurity-to-lattice framework that reconstructs the low-energy physics of a strongly correlated system from the fixed-point structure of a quantum impurity model (Fig.~\ref{schematic}, left).
 Starting from a dynamical Anderson impurity embedded in a correlated bath, we solve the system using a unitary RG (URG) approach~\cite{anirbanurg1,anirbanurg2}.
@@
 The resulting model is an \textit{extended}-Hubbard Hamiltonian on a two-dimensional square lattice at half-filling, with both on-site repulsion and nearest-neighbour spin exchange interactions.
-These correlations, derived directly from the impurity dynamics, enable tracking the evolution from the FL to the Mott insulator (MI) via an intermediate PG phase.\\
+These correlations, derived directly from the impurity dynamics, enable tracking the evolution from the FL to the Mott insulator (MI) via an intermediate PG phase.
 
@@
 \noindent
-While we demonstrate our approach for an extended Hubbard model, it applies broadly to correlated quantum systems.
+While we demonstrate our approach for an extended Hubbard model, the underlying framework is broadly applicable to correlated quantum systems.
 The impurity-plus-tiling construction accommodates multi-orbital degrees of freedom, frustrated geometries, and nontrivial band topology.
@@
     \centering
-    \includegraphics[width=\textwidth, height=10cm]{fig2.jpg}
+    \includegraphics[width=\textwidth, height=10cm]{fig2.png}
     \caption{(a): Phase diagram of impurity model at strong coupling in $U$ in terms of competing dimensionless Kondo ($J/t$) and bath correlation ($W/t$) couplings.
@@
 \end{aligned}\end{equation}
-where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, the sum is over all occupied momentum states \({\bf q}\) of the energy shell \(\varepsilon_j\), and  \({\bf \bar q} = {\bf q} + {\boldsymbol \pi}\) is the particle-hole transformed partner.
+where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, the sum is over all occupied momentum states \({\bf q}\) of the energy shell \(\varepsilon_j\), and  \({\bf \bar q} = {\bf q} + {\boldsymbol \pi}\) is the particle-hole transformed state associated with ${\bf q}$.
 The bath interaction coupling $W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}$ is found to be marginal under these transformations.
-While we present a detailed numerical evaluation of the RG equation for $J_{{\bf k}_1, {\bf k}_2}$ (eq.\eqref{KondoRGequation}) below, it is clear that the frustration of Kondo screening due to charge fluctuations (for attractive bath interactions $W<0$) leads to the Mott transition~\cite{Mukherjee_2023}.\\
+While we present a detailed numerical evaluation of the RG equation for $J_{{\bf k}_1, {\bf k}_2}$ (eq.\eqref{KondoRGequation}) below, it is clear that the frustration of Kondo screening due to charge fluctuations (for attractive bath interactions $W<0$) leads to the Mott transition~\cite{Mukherjee_2023}.
 
@@
 The accompanying impurity spectral function of the gapless arcs show a pseudogapped behaviour for $\omega\simeq 0$, with a rapid fall in the spectral weight at $\omega=0$ upon traversing the PG~(Fig.~\ref{channelDecoupling} (c)).
-The collapse of the Kondo resonance into a pseudogapped spectral function is accompanied by the redistribution of spectral weight~\cite{dzyaloshinskii2003some} in the impurity spectral function from $\omega\sim 0$ to the Hubbard sidebands at finite frequencies $\omega\simeq \pm 3$ (in units of the bandwidth) (Fig.~5 of \cite{suppmat}).
+The collapse of the Kondo resonance into a pseudogapped spectral function is accompanied by the redistribution of spectral weight~\cite{dzyaloshinskii2003some} in the impurity spectral function from $\omega\sim 0$ to the Hubbard sidebands at finite frequencies $\omega\simeq \pm 3$ (in units of the bandwidth) (Fig.4 of \cite{suppmat}).
 Concomitant with this is the emergence of a zero-frequency peak in the imaginary part of the self-energy of the NFL in the PG phase, $-\Sigma''(\omega)\sim (a + \omega^{\beta})^{-1}$~, with $a$ being a constant~(Fig.\ref{selfEnergy} (a)).
@@
 $-2\Sigma^{\prime\prime}_\text{MIR} = 1/\tau_\text{MIR}~, ~\tau_\text{MIR} = l_\text{min}/v_{F}$~,where $l_\text{min}$ is the minimum mean free path in metals (equal to one lattice spacing) and $\tau_\text{MIR}$ is the associated lifetime of quasiparticles close to the FS (with Fermi velocity $v_F$).
-The transport lifetime $\tau (\omega)$ of the NFL thus undergoes a suppression as $\omega \to 0$, together with a shift of the Drude peak to finite $\omega$~\cite{Hussey2004,pustogow2021,qazilbash2008} (see Fig.~2 and Sec.V in \cite{suppmat}).
+The optical conductivity $\sigma (\omega)$ of the NFL thus undergoes a suppression as $\omega \to 0$, together with a shift of the Drude peak to finite $\omega$~\cite{Hussey2004,pustogow2021}.
 The height of the zero-frequency peak rises by almost 4 orders of magnitude from the start of the PG till its end at the Mott transition point (Fig.\ref{selfEnergy}(c)); the dramatic growth of the peak height very near the Mott critical point coincides with the coalescing of the finite-frequency poles of the self-energy into a single pole at zero-frequency, signalling the singular nodal NFL present at the Mott quantum critical point.
@@
 \par\noindent\textbf{\large Non-local nature of the Pseudogap}\\
-In Fig.~\ref{longranged}(a) and (b), the spin-flip correlations and mutual information between the impurity spin and conduction bath sites respectively are observed to undergo a crossover within the PG, from a short-ranged behaviour at its onset, to a long-ranged behaviour near the Mott transition.
-The entanglement is observed to be multipartite in nature: in Fig.~\ref{longranged}(c), the quantum Fisher information (QFI)~\cite{Hauke2016} computed for the ground state wavefunction using an operator corresponding to the sum of local spin-flip exchange processes shows a jump at the onset of the PG.
-Further, the FL is observed to possess bi-partite entanglement while the NFL of the PG phase displays 5-partite entanglement~\cite{balut2025,mazza2024}.\\
+In Fig.~\ref{longranged}(a) and (b), the spin-flip correlations and mutual information between the impurity spin and conduction bath sites respectively are observed to undergo a crossover within the PG, from a short-ranged behaviour at its onset, to a long-ranged behaviour as the Mott transition approaches.
+The entanglement is also observed to be multipartite in nature: in Fig.~\ref{longranged}(c), the quantum Fisher information (QFI)~\cite{Hauke2016} computed for the ground state wavefunction using an operator corresponding to the sum of local spin-flip exchange processes shows a jump at the onset of the PG.
+Further, the FL is observed to possess bi-partite entanglement while the NFL of the PG phase displays pentapartite entanglement~\cite{balut2025,mazza2024}.
 
@@
 Instead,  we observe the PG phase to be a novel state of strongly interacting quantum matter emergent from the breakdown of local Kondo screening.
-This state is described by a quantum critical Fermi surface~\cite{senthil2008CriticalFermiSurface} with NFL Fermi arcs that display increasingly critical behaviour, i.e., dynamics described by non-local quantum fluctuations, and excitations that become truly long-ranged close to the transition.
+This state is described by a quantum critical Fermi surface with NFL Fermi arcs that display increasingly critical behaviour, i.e., dynamics described by non-local quantum fluctuations, and excitations that become truly long-ranged close to the transition.
 
@@
 partner \({\bf N}_1 + {\bf Q}_1 = \left(-\pi/2, -\pi/2\right)\).
-The kinetic energy \(\epsilon_{\bf q}\) and interaction energy \(u\sim J^{2}/W\) are dispersion and Kondo scales renormalised by conduction bath correlations (see Sec.4 of \cite{suppmat}).\\
+The kinetic energy \(\epsilon_{\bf q}\) and interaction energy \(u\sim J^{2}/W\) are dispersion and Kondo scales renormalised by conduction bath correlations (see Sec.4 of \cite{suppmat}).
 
@@
 The nodal Mott metal thus comprises of a Greens function zero at the Fermi energy together with an anistropic massless Dirac dispersion, leading to a non-zero Chern number~\cite{vafekvishwanath2014,morimoto2016,calderon2025}.
-This topological index survives into the Mott insulator.\\
+This topological index survives into the Mott insulator.
 
@@
 A theorem by Luttinger and Ward~\cite{luttinger1960ground} shows that a count of the physical charge (known as Luttinger's volume) is identical to the topological index (a so-called homotopy charge known as Luttinger's count) even in the presence of electronic interactions that do not disturb the FS.
-We will now argue that the emergence of antinodal Luttinger surfaces involve a disconnection of the FS (into Fermi arcs) and that, by following La Nave et al.~\cite{lanave2025}, the accompanying change in its topological properties leads to the existence of gapless NFL excitations that are non-local in nature.\\
+We will now argue that the emergence of antinodal Luttinger surfaces involve a disconnection of the FS (into Fermi arcs) and that, by following La Nave et al.~\cite{lanave2025}, the accompanying change in its topological properties leads to the existence of gapless NFL excitations that are non-local in nature.
 
@@
 \par\noindent\textbf{Acknowledgments.}
-We acknowledge National Supercomputing Mission (NSM) for providing computing resources of ‘PARAM RUDRA’ at Aruna Asaf Ali Marg, near Vasant Kunj, New Delhi, Delhi 110067, which is implemented by C-DAC and supported by the Ministry of Electronics and Information Technology (MeitY) and Department of Science and Technology (DST), Government of India.
+We acknowledge National Supercomputing Mission (NSM) for providing computing resources of ‘PARAM RUDRA’ at Aruna Asaf Ali Marg, near Vasant Kunj, Vasant Kunj, New Delhi, Delhi 110067, which is implemented by C-DAC and supported by the Ministry of Electronics and Information Technology (MeitY) and Department of Science and Technology (DST), Government of India.
 SL thanks the SERB, Govt.
@@
 A.M.
-performed the calculations and analysis with support from all authors.
+performed the calculations and analysis with support from all the authors.
 A.M., S.R.H., A.M.
@@
 wrote the manuscript with inputs from all authors.
-All work was supervised by S.L.
+All work was supervised by S.
+L.
 
 \vspace{0.25cm}
-\par\noindent\textbf{Code Availability}
+\par\noindent\textbf{Code and Data availability.}
 The codes created and datasets generated during this research are available from the corresponding author upon reasonable request.
@@
 \noindent\textbf{Lattice-embedded Impurity Model}\\
-We state the detailed Hamiltonian of the auxiliary model here: $\mathcal{H}_\text{aux} = H_\text{imp} + H_\text{coup} + H_\text{cbath}$,
+We state the detailed Hamiltonian of the auxiliary model here.
+\begin{equation}
+\label{impurityModel}
+\mathcal{H}_\text{aux} = H_\text{imp} + H_\text{coup} + H_\text{cbath},
+\end{equation}
 where the particle-hole symmetric impurity term is
@@
 Here, $c^\dagger_{d\sigma}$ creates an electron with spin $\sigma$ at the impurity site, and $\hat{n}_{d\sigma} = c^\dagger_{d\sigma} c_{d\sigma}$ denotes the corresponding number operator.
+
+\noindent
 The impurity couples to four nearest-neighbour bath sites $c_{Z\sigma}$ through both hybridization and Kondo exchange:
 \begin{equation}\begin{aligned}
-\hspace{-1cm} H_\text{coup} = \frac{J}{2} \hspace{-0.25cm}\sum_{\sigma_1,\sigma_2,Z} 
+H_\text{coup} = \frac{J}{2} \hspace{-0.25cm}\sum_{\sigma_1,\sigma_2,Z} 
 %\sum_{Z} 
@@
 \begin{equation}
-H_{\text{imp}} = -\frac{U}{2} \left( \hat{n}_{\mathbf{r}_d\uparrow} - \hat{n}_{\mathbf{r}_d\downarrow} \right)^2,
+H_{\text{imp}} = -\frac{U}{2} \left( \hat{n}_{\mathbf{r}_d\uparrow} - \hat{n}_{\mathbf{r}_d\downarrow} \right)^2 - \eta \sum_\sigma \hat{n}_{\mathbf{r}_d\sigma},
 \end{equation}
@@
 H_{\text{cbath}} = & -\frac{1}{\sqrt{\mathcal{Z}}} t \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle \ne \mathbf{r}_d; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
-& - \frac{1}{2\mathcal{Z}} W \sum_{\mathbf{z} \in \text{NN}(\mathbf{r}_d)} \left( \hat{n}_{\mathbf{z}\uparrow} - \hat{n}_{\mathbf{z}\downarrow} \right)^2 ,
+& - \frac{1}{2\mathcal{Z}} W \sum_{\mathbf{z} \in \text{NN}(\mathbf{r}_d)} \left( \hat{n}_{\mathbf{z}\uparrow} - \hat{n}_{\mathbf{z}\downarrow} \right)^2 - \mu \sum_{\mathbf{r}_i \ne \mathbf{r}_d, \sigma} \hat{n}_{\mathbf{r}_i\sigma},
 \end{aligned}
@@
 \end{equation}
-where $T(\mathbf{a})$ are many-body translation operators, defined by $T^\dagger(\mathbf{a}) \mathcal{O}(\{\mathbf{r}_i\}) T(\mathbf{a}) = \mathcal{O}(\{\mathbf{r}_i + \mathbf{a}\})$.
+where $T(\mathbf{a})$ are many-body translation operators, defined by
+\begin{equation}
+T^\dagger(\mathbf{a}) \mathcal{O}(\{\mathbf{r}_i\}) T(\mathbf{a}) = \mathcal{O}(\{\mathbf{r}_i + \mathbf{a}\}).
+\end{equation}
 Applying this to each term yields:
@@
 \mathcal{T}[H_{\text{cbath}}] &= -\frac{(N - 2)t}{\sqrt{\mathcal{Z}}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
-&\quad - \frac{1}{2} W \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2, \\
-\mathcal{T}[H_{\text{imp}}] &= -\frac{U}{2} \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2, \\
+&\quad - \frac{1}{2} W \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2 - \mu (N - 1) \sum_{\mathbf{r}, \sigma} \hat{n}_{\mathbf{r}\sigma}, \\
+\mathcal{T}[H_{\text{imp}}] &= -\frac{U}{2} \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2 - \eta \sum_{\mathbf{r}, \sigma} \hat{n}_{\mathbf{r}\sigma}, \\
 \mathcal{T}[H_{\text{imp-cbath}}] &= \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle} \left[ \frac{2J}{\mathcal{Z}} \mathbf{S}_{\mathbf{r}_i} \cdot \mathbf{S}_{\mathbf{r}_j} - \frac{2V}{\sqrt{\mathcal{Z}}} \sum_\sigma \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \right],
 \end{aligned}\end{equation}
-with local spin operators defined as $\mathbf{S}_{\mathbf{r}} = \sum_{\sigma, \sigma'} c^\dagger_{\mathbf{r}\sigma} \boldsymbol{\tau}_{\sigma \sigma'} c_{\mathbf{r}\sigma'}$.
+with local spin operators defined as
+\begin{equation}
+\mathbf{S}_{\mathbf{r}} = \sum_{\sigma, \sigma'} c^\dagger_{\mathbf{r}\sigma} \boldsymbol{\tau}_{\sigma \sigma'} c_{\mathbf{r}\sigma'}.
+\end{equation}
 
 \noindent
-To avoid overcounting of the non-interacting bath terms, we subtract extra copies of $\mathcal{H}_{\text{cbath-nint}}$. The final reconstructed Hubbard–Heisenberg model then reads:
+To avoid overcounting of the non-interacting bath terms, we subtract extra copies:
+\begin{equation}
+\mathcal{H}_{\text{cbath-nint}} = -\frac{1}{\sqrt{\mathcal{Z}}} t \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) - \mu \sum_{\mathbf{r}, \sigma} \hat{n}_{\mathbf{r}\sigma}.
+\end{equation}
+The final reconstructed Hubbard–Heisenberg model then reads:
 \begin{equation}
 \begin{aligned}
-\mathcal{H}_{\text{HH}} = & -\frac{1}{\sqrt{\mathcal{Z}}} \tilde{t} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
+\mathcal{H}_{\text{HH}} = & -\frac{1}{\sqrt{\mathcal{Z}}} \tilde{t} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) - \tilde{\mu} \sum_{\mathbf{r}, \sigma} \hat{n}_{\mathbf{r}\sigma} \\
 & + \frac{\tilde{J}}{\mathcal{Z}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle} \mathbf{S}_{\mathbf{r}_i} \cdot \mathbf{S}_{\mathbf{r}_j} - \frac{1}{2} \tilde{U} \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2,
@@
 \begin{equation}
-\tilde{t} = t + 2V,\quad \tilde{U} = U + W,\quad \tilde{J} = 2J.
+\tilde{t} = t + 2V,\quad \tilde{U} = U + W,\quad \tilde{\mu} = 2\mu + \eta,\quad \tilde{J} = 2J.
 \end{equation}
+In summary, the tiling prescription reconstructs the full Hamiltonian as
+\begin{equation}
+\mathcal{H}_{\text{tiled}} = \sum_{\mathbf{r}} H(\mathbf{r}) - N \mathcal{H}_{\text{cbath-nint}},
+\end{equation}
+effectively embedding the impurity physics into a global lattice model.
 \end{document}

### 2025-12-10 submissions/TilingUpload_NaturePhysics/manuscript_Final.tex
started creating referee response

--- 2025-12-10 submissions/NPJ/manuscript_Final.tex
@@
 \author{Siddhartha Lal}
-\email{Corresponding author: slal@iiserkol.ac.in}
+\email{slal@iiserkol.ac.in}
 \affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
@@
 Colourbar represents the fraction of states on the Fermi surface replaced by zeros of the Greens function (Luttinger surface).
-A pseudogap phase (shaded region) is observed between the local Fermi liquid (red region) and local moment (blue region) phases (b): $k$-space-resolved spin correlation $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$ in the pseudogap phase of the impurity model.
+A pseudogap phase (shaded region) is observed between the local Fermi liquid (red region) and local moment (blue region) phases (b): $k$-space-resolved spin-spin correlation $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$ in the pseudogap phase of the impurity model.
 Antinodal regions are observed to decouple from Kondo screening of the impurity.
@@
 Instead,  we observe the PG phase to be a novel state of strongly interacting quantum matter emergent from the breakdown of local Kondo screening.
-This state is described by a quantum critical Fermi surface~\cite{senthil2008CriticalFermiSurface} with NFL Fermi arcs that display increasingly critical behaviour, i.e., dynamics described by non-local quantum fluctuations, and excitations that become truly long-ranged close to the transition.
-It is tempting to conjecture that the long-range entangled critical state captured in Fig.~\ref{longranged}(b) reflects the existence of a highly efficient fast scrambler~\cite{sekino2008,hayden2007,bentsen2019}, i.e., a state in which entanglement spreads among its constituents at the fastest rate permissible by quantum mechanics.
+This state is described by a quantum critical Fermi surface with NFL Fermi arcs that display increasingly critical behaviour, i.e., dynamics described by non-local quantum fluctuations, and excitations that become truly long-ranged close to the transition.
 
@@
 This signals the NFL Fermi arcs of the PG as an emergent phase of strongly interacting quantum matter - which we dub the {\it Mott metal} - that is the parent metal of the MI.
-The same topological principle connects the nonlocal unparticle-like gapless excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} of the scale-invariant nodal NFL of the HK model observed precisely at the Mott critical point to those of the rest of the PG phase, e.g., a universal scaling of $-1/\Sigma^{\prime\prime}(\omega)\sim -1/\Sigma^{\prime\prime}(0) + \omega^{2}$ of the NFL throughout the PG phase (Fig.~\ref{selfEnergy} (a)) such that $\Sigma''(\omega=0)$ continues to grow upon violating the MIR bound, and a local density of states $A_{d}(\omega) \sim \omega^{2}$ (see Fig.~S2 (left) of \cite{suppmat}).
+The same topological principle connects the nonlocal unparticle-like gapless excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} of the scale-invariant nodal NFL of the HK model observed precisely at the Mott critical point to those of the rest of PG phase, e.g., a universal scaling of $\Sigma''_{{\bf k}}(\omega)\sim (a+b\omega^{2})^{-1}$ of the NFL throughout the PG phase (Fig.~\ref{selfEnergy} (a)) and whose $\omega=0$ value continues to grow upon violating the MIR bound.
 \vspace{0.25cm}
 \par\noindent\textbf{\large Conclusions}\\
-Our analysis reveals that the Mott transition proceeds via a continuous evolution through a PG regime characterized by a singular NFL metal - the Mott metal - with deconfined holon–doublon excitations confined to nodal Fermi arcs, and a scaling of it's spectral features with universal power-law exponents.
-As the system approaches criticality, this metallic phase exhibits increasingly non-local correlations and a divergent self-energy, signalling the breakdown of Landau quasiparticles, formation of local moments and the onset of long-range quantum entanglement.
+Our analysis reveals that the Mott transition proceeds via a continuous evolution through a PG regime characterized by a singular NFL metal - the Mott metal - with deconfined holon–doublon excitations confined to nodal Fermi arcs.
+As the system approaches criticality, this metallic phase exhibits increasingly non-local correlations and a divergent self-energy, signaling the breakdown of Landau quasiparticles and the onset of long-range quantum entanglement.
 Anchored in two-channel Kondo dynamics at intermediate scales and governed by Hatsugai–Kohmoto physics near the critical endpoint, the Mott metal provides a unified framework for understanding anomalous metallicity in strongly correlated systems.
-It's fate under finite doping presents a compelling direction for future investigation.
-
-%\begin{thebibliography}{99}
-%\makeatletter
-%\providecommand \@ifxundefined [1]{%
-% \@ifx{#1\undefined}
-%}%
-%\providecommand \@ifnum [1]{%
-% \ifnum #1\expandafter \@firstoftwo
-% \else \expandafter \@secondoftwo
-% \fi
-%}%
-%\providecommand \@ifx [1]{%
-% \ifx #1\expandafter \@firstoftwo
-% \else \expandafter \@secondoftwo
-% \fi
-%}%
-%\providecommand \natexlab [1]{#1}%
-%\providecommand \enquote  [1]{``#1''}%
-%\providecommand \bibnamefont  [1]{#1}%
-%\providecommand \bibfnamefont [1]{#1}%
-%\providecommand \citenamefont [1]{#1}%
-%\providecommand \href@noop [0]{\@secondoftwo}%
-%\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
-%\providecommand \@href[1]{\@@startlink{#1}\@@href}%
-%\providecommand \@@href[1]{\endgroup#1\@@endlink}%
-%\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
-%  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
-%\providecommand \@@startlink[1]{}%
-%\providecommand \@@endlink[0]{}%
-%\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
-%\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
-%\providecommand \urlprefix  [0]{URL }%
-%\providecommand \Eprint [0]{\href }%
-%\providecommand \doibase [0]{https://doi.org/}%
-%\providecommand \selectlanguage [0]{\@gobble}%
-%\providecommand \bibinfo  [0]{\@secondoftwo}%
-%\providecommand \bibfield  [0]{\@secondoftwo}%
-%\providecommand \translation [1]{[#1]}%
-%\providecommand \BibitemOpen [0]{}%
-%\providecommand \bibitemStop [0]{}%
-%\providecommand \bibitemNoStop [0]{.\EOS\space}%
-%\providecommand \EOS [0]{\spacefactor3000\relax}%
-%\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
-%\let\auto@bib@innerbib\@empty
-%%</preamble>
-%
-%\bibitem [{\citenamefont {Landau}(1957)}]{landau1959theory}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-%  {Landau}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Soviet
-%  Physics Jetp-Ussr}\ }\textbf {\bibinfo {volume} {3}},\ \bibinfo {pages} {920}
-%  (\bibinfo {year} {1957})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2013)\citenamefont
-%  {Phillips}, \citenamefont {Langley},\ and\ \citenamefont
-%  {Hutasoit}}]{Phillips2013Unparticles}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-%  {Phillips}}, \bibinfo {author} {\bibfnamefont {B.~W.}\ \bibnamefont
-%  {Langley}},\ and\ \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont
-%  {Hutasoit}},\ }\href {https://doi.org/10.1103/PhysRevB.88.115129} {\bibfield
-%  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-%  {88}},\ \bibinfo {pages} {115129} (\bibinfo {year} {2013})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Dzyaloshinskii}(2003)}]{dzyaloshinskii2003some}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
-%  {Dzyaloshinskii}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-%  {Physical Review B}\ }\textbf {\bibinfo {volume} {68}},\ \bibinfo {pages}
-%  {085113} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mott}(1949)}]{Mott_1949}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~F.}\ \bibnamefont
-%  {Mott}},\ }\href {https://doi.org/10.1088/0370-1298/62/7/303} {\bibfield
-%  {journal} {\bibinfo  {journal} {Proceedings of the Physical Society. Section
-%  A}\ }\textbf {\bibinfo {volume} {62}},\ \bibinfo {pages} {416} (\bibinfo
-%  {year} {1949})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2022)\citenamefont
-%  {Phillips}, \citenamefont {Hussey},\ and\ \citenamefont
-%  {Abbamonte}}]{phillips2022}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-%  {Phillips}}, \bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
-%  {Hussey}},\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-%  {Abbamonte}},\ }\href {https://doi.org/10.1126/science.abh4273} {\bibfield
-%  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
-%  {377}},\ \bibinfo {pages} {eabh4273} (\bibinfo {year} {2022})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Loeser}\ \emph {et~al.}(1996)\citenamefont {Loeser},
-%  \citenamefont {Shen}, \citenamefont {Dessau}, \citenamefont {Marshall},
-%  \citenamefont {Park}, \citenamefont {Fournier},\ and\ \citenamefont
-%  {Kapitulnik}}]{loeserKapitulnik1996}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~G.}\ \bibnamefont
-%  {Loeser}}, \bibinfo {author} {\bibfnamefont {Z.-X.}\ \bibnamefont {Shen}},
-%  \bibinfo {author} {\bibfnamefont {D.~S.}\ \bibnamefont {Dessau}}, \bibinfo
-%  {author} {\bibfnamefont {D.~S.}\ \bibnamefont {Marshall}}, \bibinfo {author}
-%  {\bibfnamefont {C.~H.}\ \bibnamefont {Park}}, \bibinfo {author}
-%  {\bibfnamefont {P.}~\bibnamefont {Fournier}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {A.}~\bibnamefont {Kapitulnik}},\ }\href
-%  {https://doi.org/10.1126/science.273.5273.325} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {273}},\ \bibinfo
-%  {pages} {325} (\bibinfo {year} {1996})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Norman}\ \emph {et~al.}(1998)\citenamefont {Norman},
-%  \citenamefont {Ding}, \citenamefont {Randeria}, \citenamefont {Campuzano},
-%  \citenamefont {Yokoya}, \citenamefont {Takeuchi}, \citenamefont {Takahashi},
-%  \citenamefont {Mochiku}, \citenamefont {Kadowaki}, \citenamefont
-%  {Guptasarma},\ and\ \citenamefont {Hinks}}]{Norman1998}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
-%  {Norman}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Ding}},
-%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Randeria}}, \bibinfo
-%  {author} {\bibfnamefont {J.~C.}\ \bibnamefont {Campuzano}}, \bibinfo {author}
-%  {\bibfnamefont {T.}~\bibnamefont {Yokoya}}, \bibinfo {author} {\bibfnamefont
-%  {T.}~\bibnamefont {Takeuchi}}, \bibinfo {author} {\bibfnamefont
-%  {T.}~\bibnamefont {Takahashi}}, \bibinfo {author} {\bibfnamefont
-%  {T.}~\bibnamefont {Mochiku}}, \bibinfo {author} {\bibfnamefont
-%  {K.}~\bibnamefont {Kadowaki}}, \bibinfo {author} {\bibfnamefont
-%  {P.}~\bibnamefont {Guptasarma}},\ and\ \bibinfo {author} {\bibfnamefont
-%  {D.~G.}\ \bibnamefont {Hinks}},\ }\href {https://doi.org/10.1038/32366}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
-%  {volume} {392}},\ \bibinfo {pages} {157} (\bibinfo {year}
-%  {1998})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Hashimoto}\ \emph {et~al.}(2014)\citenamefont
-%  {Hashimoto}, \citenamefont {Vishik}, \citenamefont {He}, \citenamefont
-%  {Devereaux},\ and\ \citenamefont {Shen}}]{Hashimoto2014}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-%  {Hashimoto}}, \bibinfo {author} {\bibfnamefont {I.~M.}\ \bibnamefont
-%  {Vishik}}, \bibinfo {author} {\bibfnamefont {R.-H.}\ \bibnamefont {He}},
-%  \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont {Devereaux}},\ and\
-%  \bibinfo {author} {\bibfnamefont {Z.-X.}\ \bibnamefont {Shen}},\ }\href
-%  {https://doi.org/10.1038/nphys3009} {\bibfield  {journal} {\bibinfo
-%  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo
-%  {pages} {483} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Taillefer}(2010)}]{taillefer2010}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-%  {Taillefer}},\ }\href
-%  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-070909-104117}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-%  Physics}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo {pages} {51} (\bibinfo
-%  {year} {2010})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Fradkin}\ \emph {et~al.}(2015)\citenamefont
-%  {Fradkin}, \citenamefont {Kivelson},\ and\ \citenamefont
-%  {Tranquada}}]{FradkinRevModPhys2015}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-%  {Fradkin}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
-%  {Kivelson}},\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-%  {Tranquada}},\ }\href {https://doi.org/10.1103/RevModPhys.87.457} {\bibfield
-%  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume}
-%  {87}},\ \bibinfo {pages} {457} (\bibinfo {year} {2015})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Sato}\ \emph {et~al.}(2017)\citenamefont {Sato},
-%  \citenamefont {Kasahara}, \citenamefont {Murayama}, \citenamefont {Kasahara},
-%  \citenamefont {Moon}, \citenamefont {Nishizaki}, \citenamefont {Loew},
-%  \citenamefont {Porras}, \citenamefont {Keimer}, \citenamefont {Shibauchi},\
-%  and\ \citenamefont {Matsuda}}]{Sato2017}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-%  {Sato}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Kasahara}},
-%  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Murayama}}, \bibinfo
-%  {author} {\bibfnamefont {Y.}~\bibnamefont {Kasahara}}, \bibinfo {author}
-%  {\bibfnamefont {E.-G.}\ \bibnamefont {Moon}}, \bibinfo {author}
-%  {\bibfnamefont {T.}~\bibnamefont {Nishizaki}}, \bibinfo {author}
-%  {\bibfnamefont {T.}~\bibnamefont {Loew}}, \bibinfo {author} {\bibfnamefont
-%  {J.}~\bibnamefont {Porras}}, \bibinfo {author} {\bibfnamefont
-%  {B.}~\bibnamefont {Keimer}}, \bibinfo {author} {\bibfnamefont
-%  {T.}~\bibnamefont {Shibauchi}},\ and\ \bibinfo {author} {\bibfnamefont
-%  {Y.}~\bibnamefont {Matsuda}},\ }\href {https://doi.org/10.1038/nphys4205}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf
-%  {\bibinfo {volume} {13}},\ \bibinfo {pages} {1074} (\bibinfo {year}
-%  {2017})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Doiron-Leyraud}\ \emph {et~al.}(2017)\citenamefont
-%  {Doiron-Leyraud}, \citenamefont {Cyr-Choini{\`e}re}, \citenamefont {Badoux},
-%  \citenamefont {Ataei}, \citenamefont {Collignon}, \citenamefont {Gourgout},
-%  \citenamefont {Dufour-Beaus{\'e}jour}, \citenamefont {Tafti}, \citenamefont
-%  {Lalibert{\'e}}, \citenamefont {Boulanger}, \citenamefont {Matusiak},
-%  \citenamefont {Graf}, \citenamefont {Kim}, \citenamefont {Zhou},
-%  \citenamefont {Momono}, \citenamefont {Kurosawa}, \citenamefont {Takagi},\
-%  and\ \citenamefont {Taillefer}}]{DoironLeyraud2017}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-%  {Doiron-Leyraud}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
-%  {Cyr-Choini{\`e}re}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Badoux}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Ataei}},
-%  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Collignon}}, \bibinfo
-%  {author} {\bibfnamefont {A.}~\bibnamefont {Gourgout}}, \bibinfo {author}
-%  {\bibfnamefont {S.}~\bibnamefont {Dufour-Beaus{\'e}jour}}, \bibinfo {author}
-%  {\bibfnamefont {F.~F.}\ \bibnamefont {Tafti}}, \bibinfo {author}
-%  {\bibfnamefont {F.}~\bibnamefont {Lalibert{\'e}}}, \bibinfo {author}
-%  {\bibfnamefont {M.-E.}\ \bibnamefont {Boulanger}}, \bibinfo {author}
-%  {\bibfnamefont {M.}~\bibnamefont {Matusiak}}, \bibinfo {author}
-%  {\bibfnamefont {D.}~\bibnamefont {Graf}}, \bibinfo {author} {\bibfnamefont
-%  {M.}~\bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont {J.-S.}\
-%  \bibnamefont {Zhou}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-%  {Momono}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Kurosawa}},
-%  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\ and\ \bibinfo
-%  {author} {\bibfnamefont {L.}~\bibnamefont {Taillefer}},\ }\href
-%  {https://doi.org/10.1038/s41467-017-02122-x} {\bibfield  {journal} {\bibinfo
-%  {journal} {Nature Communications}\ }\textbf {\bibinfo {volume} {8}},\
-%  \bibinfo {pages} {2044} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mukhopadhyay}\ \emph {et~al.}(2019)\citenamefont
-%  {Mukhopadhyay}, \citenamefont {Sharma}, \citenamefont {Kim}, \citenamefont
-%  {Edkins}, \citenamefont {Hamidian}, \citenamefont {Eisaki}, \citenamefont
-%  {ichi Uchida}, \citenamefont {Kim}, \citenamefont {Lawler}, \citenamefont
-%  {Mackenzie}, \citenamefont {Davis},\ and\ \citenamefont
-%  {Fujita}}]{Mukhopadhyay2019}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Mukhopadhyay}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-%  {Sharma}}, \bibinfo {author} {\bibfnamefont {C.~K.}\ \bibnamefont {Kim}},
-%  \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont {Edkins}}, \bibinfo
-%  {author} {\bibfnamefont {M.~H.}\ \bibnamefont {Hamidian}}, \bibinfo {author}
-%  {\bibfnamefont {H.}~\bibnamefont {Eisaki}}, \bibinfo {author} {\bibfnamefont
-%  {S.}~\bibnamefont {ichi Uchida}}, \bibinfo {author} {\bibfnamefont {E.-A.}\
-%  \bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
-%  {Lawler}}, \bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont
-%  {Mackenzie}}, \bibinfo {author} {\bibfnamefont {J.~C.~S.}\ \bibnamefont
-%  {Davis}},\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-%  {Fujita}},\ }\href {https://doi.org/10.1073/pnas.1821454116} {\bibfield
-%  {journal} {\bibinfo  {journal} {Proceedings of the National Academy of
-%  Sciences}\ }\textbf {\bibinfo {volume} {116}},\ \bibinfo {pages} {13249}
-%  (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Gupta}\ \emph {et~al.}(2021)\citenamefont {Gupta},
-%  \citenamefont {McMahon}, \citenamefont {Sutarto}, \citenamefont {Shi},
-%  \citenamefont {Gong}, \citenamefont {Wei}, \citenamefont {Shen},
-%  \citenamefont {He}, \citenamefont {Ma}, \citenamefont {Dragomir},
-%  \citenamefont {Gaulin},\ and\ \citenamefont {Hawthorn}}]{Naman2021}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~K.}\ \bibnamefont
-%  {Gupta}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {McMahon}},
-%  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Sutarto}}, \bibinfo
-%  {author} {\bibfnamefont {T.}~\bibnamefont {Shi}}, \bibinfo {author}
-%  {\bibfnamefont {R.}~\bibnamefont {Gong}}, \bibinfo {author} {\bibfnamefont
-%  {H.~I.}\ \bibnamefont {Wei}}, \bibinfo {author} {\bibfnamefont {K.~M.}\
-%  \bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-%  {He}}, \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Ma}}, \bibinfo
-%  {author} {\bibfnamefont {M.}~\bibnamefont {Dragomir}}, \bibinfo {author}
-%  {\bibfnamefont {B.~D.}\ \bibnamefont {Gaulin}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {D.~G.}\ \bibnamefont {Hawthorn}},\ }\href
-%  {https://doi.org/10.1073/pnas.2106881118} {\bibfield  {journal} {\bibinfo
-%  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-%  {\bibinfo {volume} {118}},\ \bibinfo {pages} {e2106881118} (\bibinfo {year}
-%  {2021})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Horio}\ \emph {et~al.}(2025)\citenamefont {Horio},
-%  \citenamefont {Sakai}, \citenamefont {Suzuki}, \citenamefont {Nonaka},
-%  \citenamefont {Hashimoto}, \citenamefont {Lu}, \citenamefont {Shen},
-%  \citenamefont {Ohgi}, \citenamefont {Konno}, \citenamefont {Adachi},
-%  \citenamefont {Koike}, \citenamefont {Imada},\ and\ \citenamefont
-%  {Fujimori}}]{Masafumi2025}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-%  {Horio}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Sakai}},
-%  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Suzuki}}, \bibinfo
-%  {author} {\bibfnamefont {Y.}~\bibnamefont {Nonaka}}, \bibinfo {author}
-%  {\bibfnamefont {M.}~\bibnamefont {Hashimoto}}, \bibinfo {author}
-%  {\bibfnamefont {D.}~\bibnamefont {Lu}}, \bibinfo {author} {\bibfnamefont
-%  {Z.-X.}\ \bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont
-%  {T.}~\bibnamefont {Ohgi}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-%  {Konno}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Adachi}},
-%  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Koike}}, \bibinfo
-%  {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {A.}~\bibnamefont {Fujimori}},\ }\href
-%  {https://doi.org/10.1073/pnas.2406624122} {\bibfield  {journal} {\bibinfo
-%  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-%  {\bibinfo {volume} {122}},\ \bibinfo {pages} {e2406624122} (\bibinfo {year}
-%  {2025})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Kyung}\ \emph {et~al.}(2006)\citenamefont {Kyung},
-%  \citenamefont {Kancharla}, \citenamefont {S\'en\'echal}, \citenamefont
-%  {Tremblay}, \citenamefont {Civelli},\ and\ \citenamefont
-%  {Kotliar}}]{KyungKotliar2006}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-%  {Kyung}}, \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont
-%  {Kancharla}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-%  {S\'en\'echal}}, \bibinfo {author} {\bibfnamefont {A.-M.~S.}\ \bibnamefont
-%  {Tremblay}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Civelli}},\
-%  and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Kotliar}},\ }\href
-%  {https://doi.org/10.1103/PhysRevB.73.165114} {\bibfield  {journal} {\bibinfo
-%  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo
-%  {pages} {165114} (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Macridin}\ \emph {et~al.}(2006)\citenamefont
-%  {Macridin}, \citenamefont {Jarrell}, \citenamefont {Maier}, \citenamefont
-%  {Kent},\ and\ \citenamefont {D'Azevedo}}]{MacridinAzevedo2006}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Macridin}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Jarrell}},
-%  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Maier}}, \bibinfo
-%  {author} {\bibfnamefont {P.~R.~C.}\ \bibnamefont {Kent}},\ and\ \bibinfo
-%  {author} {\bibfnamefont {E.}~\bibnamefont {D'Azevedo}},\ }\href
-%  {https://doi.org/10.1103/PhysRevLett.97.036401} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {97}},\
-%  \bibinfo {pages} {036401} (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2009)\citenamefont {Sakai},
-%  \citenamefont {Motome},\ and\ \citenamefont {Imada}}]{sakai2009evolution}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Sakai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Motome}},\ and\
-%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href@noop {}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Physical review letters}\
-%  }\textbf {\bibinfo {volume} {102}},\ \bibinfo {pages} {056404} (\bibinfo
-%  {year} {2009})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Werner}\ \emph {et~al.}(2009)\citenamefont {Werner},
-%  \citenamefont {Gull}, \citenamefont {Parcollet},\ and\ \citenamefont
-%  {Millis}}]{werner2009momentum}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-%  {Werner}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Gull}},
-%  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}},\ and\
-%  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
-%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
-%  B}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages} {045120} (\bibinfo
-%  {year} {2009})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2010)\citenamefont {Sakai},
-%  \citenamefont {Motome},\ and\ \citenamefont {Imada}}]{sakai2010doped}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Sakai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Motome}},\ and\
-%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href@noop {}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review B}\ }\textbf
-%  {\bibinfo {volume} {82}},\ \bibinfo {pages} {134505} (\bibinfo {year}
-%  {2010})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Lin}\ \emph {et~al.}(2010)\citenamefont {Lin},
-%  \citenamefont {Gull},\ and\ \citenamefont {Millis}}]{lin2010}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-%  {Lin}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Gull}},\ and\
-%  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
-%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-%  }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {045104} (\bibinfo
-%  {year} {2010})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Gull}\ \emph {et~al.}(2010)\citenamefont {Gull},
-%  \citenamefont {Ferrero}, \citenamefont {Parcollet}, \citenamefont {Georges},\
-%  and\ \citenamefont {Millis}}]{gull2010momentum}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-%  {Gull}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ferrero}},
-%  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}}, \bibinfo
-%  {author} {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\ }\href@noop {} {\bibfield
-%  {journal} {\bibinfo  {journal} {Physical Review B}\ }\textbf {\bibinfo
-%  {volume} {82}},\ \bibinfo {pages} {155101} (\bibinfo {year}
-%  {2010})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Gull}\ and\ \citenamefont {Millis}(2012)}]{gull2012}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-%  {Gull}}\ and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
-%  {Millis}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-%  Rev. B}\ }\textbf {\bibinfo {volume} {86}},\ \bibinfo {pages} {241106}
-%  (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mirzaei}\ \emph {et~al.}(2013)\citenamefont
-%  {Mirzaei}, \citenamefont {Stricker}, \citenamefont {Hancock}, \citenamefont
-%  {Berthod}, \citenamefont {Georges}, \citenamefont {van Heumen}, \citenamefont
-%  {Chan}, \citenamefont {Zhao}, \citenamefont {Li}, \citenamefont {Greven},
-%  \citenamefont {Barišić},\ and\ \citenamefont {van~der
-%  Marel}}]{Mirzaei2013}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~I.}\ \bibnamefont
-%  {Mirzaei}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Stricker}},
-%  \bibinfo {author} {\bibfnamefont {J.~N.}\ \bibnamefont {Hancock}}, \bibinfo
-%  {author} {\bibfnamefont {C.}~\bibnamefont {Berthod}}, \bibinfo {author}
-%  {\bibfnamefont {A.}~\bibnamefont {Georges}}, \bibinfo {author} {\bibfnamefont
-%  {E.}~\bibnamefont {van Heumen}}, \bibinfo {author} {\bibfnamefont {M.~K.}\
-%  \bibnamefont {Chan}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
-%  {Zhao}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Li}}, \bibinfo
-%  {author} {\bibfnamefont {M.}~\bibnamefont {Greven}}, \bibinfo {author}
-%  {\bibfnamefont {N.}~\bibnamefont {Barišić}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {D.}~\bibnamefont {van~der Marel}},\ }\href
-%  {https://doi.org/10.1073/pnas.1218846110} {\bibfield  {journal} {\bibinfo
-%  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-%  {\bibinfo {volume} {110}},\ \bibinfo {pages} {5774} (\bibinfo {year}
-%  {2013})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Gull}\ \emph {et~al.}(2013)\citenamefont {Gull},
-%  \citenamefont {Parcollet},\ and\ \citenamefont {Millis}}]{gull2013}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-%  {Gull}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}},\
-%  and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
-%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical review
-%  letters}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo {pages} {216405}
-%  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
-%  {Lal}(2020{\natexlab{a}})}]{anirbanmott2}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Lal}},\ }\href {https://doi.org/10.1088/1367-2630/ab890c} {\bibfield
-%  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
-%  {volume} {22}},\ \bibinfo {pages} {063008} (\bibinfo {year}
-%  {2020}{\natexlab{a}})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Hille}\ \emph {et~al.}(2020)\citenamefont {Hille},
-%  \citenamefont {Rohe}, \citenamefont {Honerkamp},\ and\ \citenamefont
-%  {Andergassen}}]{HilleAndergassen2020}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-%  {Hille}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Rohe}},
-%  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Honerkamp}},\ and\
-%  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Andergassen}},\ }\href
-%  {https://doi.org/10.1103/PhysRevResearch.2.033068} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Phys. Rev. Res.}\ }\textbf {\bibinfo {volume} {2}},\
-%  \bibinfo {pages} {033068} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Jiang}\ \emph {et~al.}(2022)\citenamefont {Jiang},
-%  \citenamefont {Liu}, \citenamefont {Klein}, \citenamefont {Wang},
-%  \citenamefont {Sun}, \citenamefont {Chubukov},\ and\ \citenamefont
-%  {Meng}}]{Jiang2022}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
-%  {Jiang}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Liu}}, \bibinfo
-%  {author} {\bibfnamefont {A.}~\bibnamefont {Klein}}, \bibinfo {author}
-%  {\bibfnamefont {Y.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont
-%  {K.}~\bibnamefont {Sun}}, \bibinfo {author} {\bibfnamefont {A.~V.}\
-%  \bibnamefont {Chubukov}},\ and\ \bibinfo {author} {\bibfnamefont {Z.~Y.}\
-%  \bibnamefont {Meng}},\ }\href {https://doi.org/10.1038/s41467-022-30302-x}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Nature Communications}\ }\textbf
-%  {\bibinfo {volume} {13}},\ \bibinfo {pages} {2655} (\bibinfo {year}
-%  {2022})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Scheurer}\ \emph {et~al.}(2018)\citenamefont
-%  {Scheurer}, \citenamefont {Chatterjee}, \citenamefont {Wu}, \citenamefont
-%  {Ferrero}, \citenamefont {Georges},\ and\ \citenamefont
-%  {Sachdev}}]{Scheurer2018}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont
-%  {Scheurer}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Chatterjee}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Wu}},
-%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ferrero}}, \bibinfo
-%  {author} {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {S.}~\bibnamefont {Sachdev}},\ }\href
-%  {https://doi.org/10.1073/pnas.1720580115} {\bibfield  {journal} {\bibinfo
-%  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-%  {\bibinfo {volume} {115}},\ \bibinfo {pages} {E3665} (\bibinfo {year}
-%  {2018})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Krien}\ \emph {et~al.}(2022)\citenamefont {Krien},
-%  \citenamefont {Worm}, \citenamefont {Chalupa-Gantner}, \citenamefont
-%  {Toschi},\ and\ \citenamefont {Held}}]{Krien2022}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-%  {Krien}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Worm}},
-%  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Chalupa-Gantner}},
-%  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Toschi}},\ and\ \bibinfo
-%  {author} {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\href
-%  {https://doi.org/10.1038/s42005-022-01117-5} {\bibfield  {journal} {\bibinfo
-%  {journal} {Communications Physics}\ }\textbf {\bibinfo {volume} {5}},\
-%  \bibinfo {pages} {336} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Kitatani}\ \emph {et~al.}(2023)\citenamefont
-%  {Kitatani}, \citenamefont {Si}, \citenamefont {Worm}, \citenamefont
-%  {Tomczak}, \citenamefont {Arita},\ and\ \citenamefont {Held}}]{Kitatani2023}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-%  {Kitatani}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Si}},
-%  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Worm}}, \bibinfo {author}
-%  {\bibfnamefont {J.~M.}\ \bibnamefont {Tomczak}}, \bibinfo {author}
-%  {\bibfnamefont {R.}~\bibnamefont {Arita}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\href
-%  {https://doi.org/10.1103/PhysRevLett.130.166002} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {130}},\
-%  \bibinfo {pages} {166002} (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Sorella}(2023)}]{Sorella2023}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Sorella}},\ }\href {https://doi.org/10.1103/PhysRevB.107.115133} {\bibfield
-%  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-%  {107}},\ \bibinfo {pages} {115133} (\bibinfo {year} {2023})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Schäfer}\ \emph {et~al.}(2021)\citenamefont
-%  {Schäfer}, \citenamefont {Wentzell}, \citenamefont {Šimkovic},
-%  \citenamefont {He}, \citenamefont {Hille}, \citenamefont {Klett},
-%  \citenamefont {Eckhardt}, \citenamefont {Arzhang}, \citenamefont {Harkov},
-%  \citenamefont {Le~R\'egent}, \citenamefont {Kirsch}, \citenamefont {Wang},
-%  \citenamefont {Kim}, \citenamefont {Kozik}, \citenamefont {Stepanov},
-%  \citenamefont {Kauch}, \citenamefont {Andergassen}, \citenamefont {Hansmann},
-%  \citenamefont {Rohe}, \citenamefont {Vilk}, \citenamefont {LeBlanc},
-%  \citenamefont {Zhang}, \citenamefont {Tremblay}, \citenamefont {Ferrero},
-%  \citenamefont {Parcollet},\ and\ \citenamefont {Georges}}]{Schafer2021}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-%  {Schäfer}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Wentzell}},
-%  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Šimkovic}}, \bibinfo
-%  {author} {\bibfnamefont {Y.-Y.}\ \bibnamefont {He}}, \bibinfo {author}
-%  {\bibfnamefont {C.}~\bibnamefont {Hille}}, \bibinfo {author} {\bibfnamefont
-%  {M.}~\bibnamefont {Klett}}, \bibinfo {author} {\bibfnamefont {C.~J.}\
-%  \bibnamefont {Eckhardt}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-%  {Arzhang}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Harkov}},
-%  \bibinfo {author} {\bibfnamefont {F.~m. c.-M.}\ \bibnamefont {Le~R\'egent}},
-%  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kirsch}}, \bibinfo
-%  {author} {\bibfnamefont {Y.}~\bibnamefont {Wang}}, \bibinfo {author}
-%  {\bibfnamefont {A.~J.}\ \bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont
-%  {E.}~\bibnamefont {Kozik}}, \bibinfo {author} {\bibfnamefont {E.~A.}\
-%  \bibnamefont {Stepanov}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Kauch}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Andergassen}},
-%  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Hansmann}}, \bibinfo
-%  {author} {\bibfnamefont {D.}~\bibnamefont {Rohe}}, \bibinfo {author}
-%  {\bibfnamefont {Y.~M.}\ \bibnamefont {Vilk}}, \bibinfo {author}
-%  {\bibfnamefont {J.~P.~F.}\ \bibnamefont {LeBlanc}}, \bibinfo {author}
-%  {\bibfnamefont {S.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
-%  {A.-M.~S.}\ \bibnamefont {Tremblay}}, \bibinfo {author} {\bibfnamefont
-%  {M.}~\bibnamefont {Ferrero}}, \bibinfo {author} {\bibfnamefont
-%  {O.}~\bibnamefont {Parcollet}},\ and\ \bibinfo {author} {\bibfnamefont
-%  {A.}~\bibnamefont {Georges}},\ }\href
-%  {https://doi.org/10.1103/PhysRevX.11.011058} {\bibfield  {journal} {\bibinfo
-%  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
-%  {pages} {011058} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {White}\ and\ \citenamefont
-%  {Scalapino}(1998)}]{White1998}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~R.}\ \bibnamefont
-%  {White}}\ and\ \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
-%  {Scalapino}},\ }\href {https://doi.org/10.1103/PhysRevLett.80.1272}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-%  {\bibinfo {volume} {80}},\ \bibinfo {pages} {1272} (\bibinfo {year}
-%  {1998})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Ido}\ \emph {et~al.}(2018)\citenamefont {Ido},
-%  \citenamefont {Ohgoe},\ and\ \citenamefont {Imada}}]{Ido2018}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-%  {Ido}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Ohgoe}},\ and\
-%  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href
-%  {https://doi.org/10.1103/PhysRevB.97.045138} {\bibfield  {journal} {\bibinfo
-%  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo
-%  {pages} {045138} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Proust}\ and\ \citenamefont
-%  {Taillefer}(2019)}]{ProustTaillefer2019}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-%  {Proust}}\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-%  {Taillefer}},\ }\href
-%  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-031218-013210}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-%  Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {409}
-%  (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Ponsioen}\ \emph {et~al.}(2019)\citenamefont
-%  {Ponsioen}, \citenamefont {Chung},\ and\ \citenamefont
-%  {Corboz}}]{Ponsioen2019}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-%  {Ponsioen}}, \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont
-%  {Chung}},\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-%  {Corboz}},\ }\href {https://doi.org/10.1103/PhysRevB.100.195141} {\bibfield
-%  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-%  {100}},\ \bibinfo {pages} {195141} (\bibinfo {year} {2019})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Xu}\ \emph {et~al.}(2022)\citenamefont {Xu},
-%  \citenamefont {Shi}, \citenamefont {Vitali}, \citenamefont {Qin},\ and\
-%  \citenamefont {Zhang}}]{XuZhang2022}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-%  {Xu}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Shi}}, \bibinfo
-%  {author} {\bibfnamefont {E.}~\bibnamefont {Vitali}}, \bibinfo {author}
-%  {\bibfnamefont {M.}~\bibnamefont {Qin}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {S.}~\bibnamefont {Zhang}},\ }\href
-%  {https://doi.org/10.1103/PhysRevResearch.4.013239} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Phys. Rev. Res.}\ }\textbf {\bibinfo {volume} {4}},\
-%  \bibinfo {pages} {013239} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Dave}\ \emph {et~al.}(2013)\citenamefont {Dave},
-%  \citenamefont {Phillips},\ and\ \citenamefont {Kane}}]{Phillips2013}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~B.}\ \bibnamefont
-%  {Dave}}, \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\
-%  and\ \bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont {Kane}},\ }\href
-%  {https://doi.org/10.1103/PhysRevLett.110.090403} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {110}},\
-%  \bibinfo {pages} {090403} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Seki}\ and\ \citenamefont
-%  {Yunoki}(2017)}]{seki2017topological}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-%  {Seki}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Yunoki}},\
-%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
-%  B}\ }\textbf {\bibinfo {volume} {96}},\ \bibinfo {pages} {085124} (\bibinfo
-%  {year} {2017})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Anderson}\ and\ \citenamefont
-%  {Haldane}(2001)}]{Anderson2001}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-%  {Anderson}}\ and\ \bibinfo {author} {\bibfnamefont {F.~D.~M.}\ \bibnamefont
-%  {Haldane}},\ }\href {https://doi.org/10.1023/A:1010324912515} {\bibfield
-%  {journal} {\bibinfo  {journal} {Journal of Statistical Physics}\ }\textbf
-%  {\bibinfo {volume} {103}},\ \bibinfo {pages} {425} (\bibinfo {year}
-%  {2001})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Huang}\ \emph {et~al.}(2022)\citenamefont {Huang},
-%  \citenamefont {Nave},\ and\ \citenamefont {Phillips}}]{Huang2022}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont
-%  {Huang}}, \bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont {Nave}},\
-%  and\ \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\
-%  }\href {https://doi.org/10.1038/s41567-022-01529-8} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {18}},\
-%  \bibinfo {pages} {511} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Coleman}\ \emph {et~al.}(2001)\citenamefont
-%  {Coleman}, \citenamefont {Pépin}, \citenamefont {Si},\ and\ \citenamefont
-%  {Ramazashvili}}]{Coleman_2001}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-%  {Coleman}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Pépin}},
-%  \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Si}},\ and\ \bibinfo
-%  {author} {\bibfnamefont {R.}~\bibnamefont {Ramazashvili}},\ }\href
-%  {https://doi.org/10.1088/0953-8984/13/35/202} {\bibfield  {journal} {\bibinfo
-%   {journal} {Journal of Physics: Condensed Matter}\ }\textbf {\bibinfo
-%  {volume} {13}},\ \bibinfo {pages} {R723} (\bibinfo {year}
-%  {2001})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
-%  {Lal}(2020{\natexlab{b}})}]{anirbanurg1}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Lal}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nuclear
-%  Physics B}\ }\textbf {\bibinfo {volume} {960}},\ \bibinfo {pages} {115170}
-%  (\bibinfo {year} {2020}{\natexlab{b}})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
-%  {Lal}(2020{\natexlab{c}})}]{anirbanurg2}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Lal}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nuclear
-%  Physics B}\ }\textbf {\bibinfo {volume} {960}},\ \bibinfo {pages} {115163}
-%  (\bibinfo {year} {2020}{\natexlab{c}})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Keimer}\ \emph {et~al.}(2015)\citenamefont {Keimer},
-%  \citenamefont {Kivelson}, \citenamefont {Norman}, \citenamefont {Uchida},\
-%  and\ \citenamefont {Zaanen}}]{keimer2015quantum}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-%  {Keimer}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
-%  {Kivelson}}, \bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
-%  {Norman}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Uchida}},\
-%  and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zaanen}},\
-%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf
-%  {\bibinfo {volume} {518}},\ \bibinfo {pages} {179} (\bibinfo {year}
-%  {2015})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Hatsugai}\ and\ \citenamefont
-%  {Kohmoto}(1992)}]{Hatsugai1992}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-%  {Hatsugai}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-%  {Kohmoto}},\ }\href {https://doi.org/10.1143/JPSJ.61.2056} {\bibfield
-%  {journal} {\bibinfo  {journal} {Journal of the Physical Society of Japan}\
-%  }\textbf {\bibinfo {volume} {61}},\ \bibinfo {pages} {2056} (\bibinfo {year}
-%  {1992})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Baskaran}(1991)}]{Baskaran1991}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-%  {Baskaran}},\ }\href {https://doi.org/10.1142/S0217984991000782} {\bibfield
-%  {journal} {\bibinfo  {journal} {Modern Physics Letters B}\ }\textbf {\bibinfo
-%  {volume} {05}},\ \bibinfo {pages} {643} (\bibinfo {year} {1991})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Altshuler}\ \emph {et~al.}(1998)\citenamefont
-%  {Altshuler}, \citenamefont {Chubukov}, \citenamefont {Dashevskii},
-%  \citenamefont {Finkel'stein},\ and\ \citenamefont {Morr}}]{Altshuler_1998}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~L.}\ \bibnamefont
-%  {Altshuler}}, \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
-%  {Chubukov}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Dashevskii}}, \bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
-%  {Finkel'stein}},\ and\ \bibinfo {author} {\bibfnamefont {D.~K.}\ \bibnamefont
-%  {Morr}},\ }\href {https://doi.org/10.1209/epl/i1998-00164-y} {\bibfield
-%  {journal} {\bibinfo  {journal} {Europhysics Letters}\ }\textbf {\bibinfo
-%  {volume} {41}},\ \bibinfo {pages} {401} (\bibinfo {year} {1998})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Heath}\ and\ \citenamefont
-%  {Bedell}(2020)}]{Heath_2020}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont
-%  {Heath}}\ and\ \bibinfo {author} {\bibfnamefont {K.~S.}\ \bibnamefont
-%  {Bedell}},\ }\href {https://doi.org/10.1088/1367-2630/ab890e} {\bibfield
-%  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
-%  {volume} {22}},\ \bibinfo {pages} {063011} (\bibinfo {year}
-%  {2020})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Nave}\ \emph {et~al.}(2025)\citenamefont {Nave},
-%  \citenamefont {Zhao},\ and\ \citenamefont {Phillips}}]{lanave2025}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont
-%  {Nave}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zhao}},\ and\
-%  \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\ }\href
-%  {https://arxiv.org/abs/2506.04342} {} (\bibinfo {year} {2025}),\ \Eprint
-%  {https://arxiv.org/abs/2506.04342} {arXiv:2506.04342 [cond-mat.str-el]}
-%  \BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mukherjee}\ \emph {et~al.}(2023)\citenamefont
-%  {Mukherjee}, \citenamefont {Vidhyadhiraja}, \citenamefont {Taraphder},\ and\
-%  \citenamefont {Lal}}]{Mukherjee_2023}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Mukherjee}}, \bibinfo {author} {\bibfnamefont {N.~S.}\ \bibnamefont
-%  {Vidhyadhiraja}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Taraphder}},\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Lal}},\ }\href {https://doi.org/10.1088/1367-2630/ad08f3} {\bibfield
-%  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
-%  {volume} {25}},\ \bibinfo {pages} {113011} (\bibinfo {year}
-%  {2023})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Georges}\ \emph {et~al.}(1996)\citenamefont
-%  {Georges}, \citenamefont {Kotliar}, \citenamefont {Krauth},\ and\
-%  \citenamefont {Rozenberg}}]{georges1996}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Georges}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Kotliar}},
-%  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Krauth}},\ and\ \bibinfo
-%  {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Rozenberg}},\ }\href@noop {}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Reviews of Modern Physics}\
-%  }\textbf {\bibinfo {volume} {68}},\ \bibinfo {pages} {13} (\bibinfo {year}
-%  {1996})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Hettler}\ \emph {et~al.}(1998)\citenamefont
-%  {Hettler}, \citenamefont {Tahvildar-Zadeh}, \citenamefont {Jarrell},
-%  \citenamefont {Pruschke},\ and\ \citenamefont {Krishnamurthy}}]{hettler1998}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-%  {Hettler}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Tahvildar-Zadeh}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-%  {Jarrell}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Pruschke}},\
-%  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Krishnamurthy}},\
-%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
-%  B}\ }\textbf {\bibinfo {volume} {58}},\ \bibinfo {pages} {R7475} (\bibinfo
-%  {year} {1998})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Kotliar}\ \emph {et~al.}(2001)\citenamefont
-%  {Kotliar}, \citenamefont {Savrasov}, \citenamefont {P{\'a}lsson},\ and\
-%  \citenamefont {Biroli}}]{kotliar2001}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-%  {Kotliar}}, \bibinfo {author} {\bibfnamefont {S.~Y.}\ \bibnamefont
-%  {Savrasov}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-%  {P{\'a}lsson}},\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-%  {Biroli}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-%  {Physical review letters}\ }\textbf {\bibinfo {volume} {87}},\ \bibinfo
-%  {pages} {186401} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Maier}\ \emph {et~al.}(2005)\citenamefont {Maier},
-%  \citenamefont {Jarrell}, \citenamefont {Schulthess}, \citenamefont {Kent},\
-%  and\ \citenamefont {White}}]{maier2005}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont
-%  {Maier}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Jarrell}},
-%  \bibinfo {author} {\bibfnamefont {T.~C.}\ \bibnamefont {Schulthess}},
-%  \bibinfo {author} {\bibfnamefont {P.~R.~C.}\ \bibnamefont {Kent}},\ and\
-%  \bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont {White}},\ }\href@noop
-%  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-%  {\bibinfo {volume} {95}},\ \bibinfo {pages} {237001} (\bibinfo {year}
-%  {2005})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Stoyanova}(2006)}]{stoyanova}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Stoyanova}},\ }\emph {\bibinfo {title} {Delocalized and correlated wave
-%  functions for excited states in extended systems}},\ \href@noop {} {Ph.D.
-%  thesis},\ \bibinfo  {school} {University of Groningen} (\bibinfo {year}
-%  {2006})\BibitemShut {NoStop}%
-%\bibitem [{sup()}]{suppmat}%
-%  \BibitemOpen
-%  \href@noop {} {\bibinfo {title} {See supplemental material for additional
-%  information.}}\BibitemShut {Stop}%
-%\bibitem [{\citenamefont {Wu}\ \emph {et~al.}(2018)\citenamefont {Wu},
-%  \citenamefont {Scheurer}, \citenamefont {Chatterjee}, \citenamefont
-%  {Sachdev}, \citenamefont {Georges},\ and\ \citenamefont
-%  {Ferrero}}]{WuFerrero2018}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
-%  {Wu}}, \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Scheurer}},
-%  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Chatterjee}}, \bibinfo
-%  {author} {\bibfnamefont {S.}~\bibnamefont {Sachdev}}, \bibinfo {author}
-%  {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {M.}~\bibnamefont {Ferrero}},\ }\href
-%  {https://doi.org/10.1103/PhysRevX.8.021048} {\bibfield  {journal} {\bibinfo
-%  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {8}},\ \bibinfo {pages}
-%  {021048} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Tsvelick}\ and\ \citenamefont
-%  {Wiegmann}(1985)}]{Tsvelick_weigmann_mchannel_1985}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
-%  {Tsvelick}}\ and\ \bibinfo {author} {\bibfnamefont {P.~B.}\ \bibnamefont
-%  {Wiegmann}},\ }\href {https://doi.org/10.1007/BF01017853} {\bibfield
-%  {journal} {\bibinfo  {journal} {Journal of Statistical Physics}\ }\textbf
-%  {\bibinfo {volume} {38}},\ \bibinfo {pages} {125} (\bibinfo {year}
-%  {1985})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Emery}\ and\ \citenamefont
-%  {Kivelson}(1992)}]{emery_kivelson}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~J.}\ \bibnamefont
-%  {Emery}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-%  {Kivelson}},\ }\href {https://doi.org/10.1103/PhysRevB.46.10812} {\bibfield
-%  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-%  {46}},\ \bibinfo {pages} {10812} (\bibinfo {year} {1992})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Gunnarsson}\ \emph {et~al.}(2003)\citenamefont
-%  {Gunnarsson}, \citenamefont {Calandra},\ and\ \citenamefont
-%  {Han}}]{GunnarssonRMP2003}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
-%  {Gunnarsson}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-%  {Calandra}},\ and\ \bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont
-%  {Han}},\ }\href {https://doi.org/10.1103/RevModPhys.75.1085} {\bibfield
-%  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume}
-%  {75}},\ \bibinfo {pages} {1085} (\bibinfo {year} {2003})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Hussey}\ \emph {et~al.}(2004)\citenamefont {Hussey},
-%  \citenamefont {Takenaka},\ and\ \citenamefont {Takagi}}]{Hussey2004}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
-%  {Hussey}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Takenaka}},\
-%  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\ }\href
-%  {https://doi.org/10.1080/14786430410001716944} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Philosophical Magazine}\ }\textbf {\bibinfo {volume}
-%  {84}},\ \bibinfo {pages} {2847} (\bibinfo {year} {2004})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Pustogow}\ \emph {et~al.}(2021)\citenamefont
-%  {Pustogow}, \citenamefont {Saito}, \citenamefont {Anja~Löhle}, \citenamefont
-%  {Alonso}, \citenamefont {Kawamoto}, \citenamefont {Dobrosavljevic},
-%  \citenamefont {Dressel},\ and\ \citenamefont {Fratini}}]{pustogow2021}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Pustogow}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Saito}},
-%  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Anja~Löhle}}, \bibinfo
-%  {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Alonso}}, \bibinfo {author}
-%  {\bibfnamefont {A.}~\bibnamefont {Kawamoto}}, \bibinfo {author}
-%  {\bibfnamefont {V.}~\bibnamefont {Dobrosavljevic}}, \bibinfo {author}
-%  {\bibfnamefont {M.}~\bibnamefont {Dressel}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {S.}~\bibnamefont {Fratini}},\ }\href@noop {} {\bibfield
-%  {journal} {\bibinfo  {journal} {Nat. Comm.}\ }\textbf {\bibinfo {volume}
-%  {12}},\ \bibinfo {pages} {1571} (\bibinfo {year} {2021})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {Qazilbash}\ \emph {et~al.}(2008)\citenamefont
-%  {Qazilbash}, \citenamefont {Schafgans}, \citenamefont {Burch}, \citenamefont
-%  {Yun}, \citenamefont {Chae}, \citenamefont {Kim}, \citenamefont {Kim},\ and\
-%  \citenamefont {Basov}}]{qazilbash2008}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~M.}\ \bibnamefont
-%  {Qazilbash}}, \bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont
-%  {Schafgans}}, \bibinfo {author} {\bibfnamefont {K.~S.}\ \bibnamefont
-%  {Burch}}, \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont {Yun}},
-%  \bibinfo {author} {\bibfnamefont {B.~G.}\ \bibnamefont {Chae}}, \bibinfo
-%  {author} {\bibfnamefont {B.~J.}\ \bibnamefont {Kim}}, \bibinfo {author}
-%  {\bibfnamefont {H.~T.}\ \bibnamefont {Kim}},\ and\ \bibinfo {author}
-%  {\bibfnamefont {D.~N.}\ \bibnamefont {Basov}},\ }\href
-%  {https://doi.org/10.1103/PhysRevB.77.115121} {\bibfield  {journal} {\bibinfo
-%  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo
-%  {pages} {115121} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Hauke}\ \emph {et~al.}(2016)\citenamefont {Hauke},
-%  \citenamefont {Heyl}, \citenamefont {Tagliacozzo},\ and\ \citenamefont
-%  {Zoller}}]{Hauke2016}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-%  {Hauke}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Heyl}},
-%  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Tagliacozzo}},\ and\
-%  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Zoller}},\ }\href
-%  {https://doi.org/10.1038/nphys3700} {\bibfield  {journal} {\bibinfo
-%  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
-%  {pages} {778} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Balut}\ \emph {et~al.}(2025)\citenamefont {Balut},
-%  \citenamefont {Guo}, \citenamefont {de~Vriesa}, \citenamefont {Chaudhuri},
-%  \citenamefont {Bradlyn}, \citenamefont {Abbamonte},\ and\ \citenamefont
-%  {W.}}]{balut2025}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-%  {Balut}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Guo}}, \bibinfo
-%  {author} {\bibfnamefont {N.}~\bibnamefont {de~Vriesa}}, \bibinfo {author}
-%  {\bibfnamefont {D.}~\bibnamefont {Chaudhuri}}, \bibinfo {author}
-%  {\bibfnamefont {B.}~\bibnamefont {Bradlyn}}, \bibinfo {author} {\bibfnamefont
-%  {P.}~\bibnamefont {Abbamonte}},\ and\ \bibinfo {author} {\bibfnamefont
-%  {P.~P.}\ \bibnamefont {W.}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-%  {journal} {Physica C}\ }\textbf {\bibinfo {volume} {635}},\ \bibinfo {pages}
-%  {1354750} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Mazza}\ \emph {et~al.}(2024)\citenamefont {Mazza},
-%  \citenamefont {Biswas}, \citenamefont {Yan}, \citenamefont {Prokofiev},
-%  \citenamefont {Steffens}, \citenamefont {Si}, \citenamefont {Assaad},\ and\
-%  \citenamefont {Paschen}}]{mazza2024}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-%  {Mazza}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Biswas}},
-%  \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Yan}}, \bibinfo {author}
-%  {\bibfnamefont {A.}~\bibnamefont {Prokofiev}}, \bibinfo {author}
-%  {\bibfnamefont {P.}~\bibnamefont {Steffens}}, \bibinfo {author}
-%  {\bibfnamefont {Q.}~\bibnamefont {Si}}, \bibinfo {author} {\bibfnamefont
-%  {F.~F.}\ \bibnamefont {Assaad}},\ and\ \bibinfo {author} {\bibfnamefont
-%  {S.}~\bibnamefont {Paschen}},\ }\href {https://arxiv.org/abs/2403.12779} {}
-%  (\bibinfo {year} {2024}),\ \Eprint {https://arxiv.org/abs/2403.12779}
-%  {arXiv:2403.12779 [cond-mat.str-el]} \BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Si}\ \emph {et~al.}(2001)\citenamefont {Si},
-%  \citenamefont {Rabello}, \citenamefont {Ingersent},\ and\ \citenamefont
-%  {Smith}}]{Si2001}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont
-%  {Si}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Rabello}},
-%  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Ingersent}},\ and\
-%  \bibinfo {author} {\bibfnamefont {J.~L.}\ \bibnamefont {Smith}},\ }\href
-%  {https://doi.org/10.1038/35101507} {\bibfield  {journal} {\bibinfo  {journal}
-%  {Nature}\ }\textbf {\bibinfo {volume} {413}},\ \bibinfo {pages} {804}
-%  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2020)\citenamefont
-%  {Phillips}, \citenamefont {Yeo},\ and\ \citenamefont {Huang}}]{Phillips2020}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-%  {Phillips}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Yeo}},\ and\
-%  \bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont {Huang}},\ }\href
-%  {https://doi.org/10.1038/s41567-020-0988-4} {\bibfield  {journal} {\bibinfo
-%  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo
-%  {pages} {1175} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Vafek}\ and\ \citenamefont
-%  {Vishwanath}(2014)}]{vafekvishwanath2014}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
-%  {Vafek}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Vishwanath}},\ }\href
-%  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-031113-133841}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-%  Physics}\ }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {83} (\bibinfo
-%  {year} {2014})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Morimoto}\ and\ \citenamefont
-%  {Nagaosa}(2016)}]{morimoto2016}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-%  {Morimoto}}\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-%  {Nagaosa}},\ }\href {https://doi.org/10.1038/srep19853} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Sci. Rep.}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo
-%  {pages} {19853} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Flores-Calder\'on}\ and\ \citenamefont
-%  {Hooley}(2025)}]{calderon2025}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-%  {Flores-Calder\'on}}\ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-%  {Hooley}},\ }\href {https://doi.org/10.1103/k4st-77ph} {\bibfield  {journal}
-%  {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {111}},\
-%  \bibinfo {pages} {235139} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Georgi}(2007{\natexlab{a}})}]{Georgi2007PRL}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-%  {Georgi}},\ }\href {https://doi.org/10.1103/PhysRevLett.98.221601} {\bibfield
-%   {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
-%  {volume} {98}},\ \bibinfo {pages} {221601} (\bibinfo {year}
-%  {2007}{\natexlab{a}})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Georgi}(2007{\natexlab{b}})}]{Georgi2007}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-%  {Georgi}},\ }\href
-%  {https://doi.org/https://doi.org/10.1016/j.physletb.2007.05.037} {\bibfield
-%  {journal} {\bibinfo  {journal} {Physics Letters B}\ }\textbf {\bibinfo
-%  {volume} {650}},\ \bibinfo {pages} {275} (\bibinfo {year}
-%  {2007}{\natexlab{b}})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Phillips}(2014)}]{PhillipsLectures2014}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-%  {Phillips}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {Quantum
-%  Criticality in Condensed Matter}}},\ \bibinfo {editor} {edited by\ \bibinfo
-%  {editor} {\bibfnamefont {J.}~\bibnamefont {Jedrzejewski}}}\ (\bibinfo
-%  {publisher} {World Scientific, Singapore},\ \bibinfo {year} {2014})\ pp.\
-%  \bibinfo {pages} {133--158}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Zaanen}(2019)}]{zaanen2019}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-%  {Zaanen}},\ }\href {https://doi.org/10.21468/SciPostPhys.6.5.061} {\bibfield
-%  {journal} {\bibinfo  {journal} {SciPost Phys.}\ }\textbf {\bibinfo {volume}
-%  {6}},\ \bibinfo {pages} {061} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Legros}\ \emph {et~al.}(2019)\citenamefont {Legros},
-%  \citenamefont {Benhabib}, \citenamefont {Tabis}, \citenamefont
-%  {Lalibert{\'e}}, \citenamefont {Dion}, \citenamefont {Lizaire}, \citenamefont
-%  {Vignolle}, \citenamefont {Vignolles}, \citenamefont {Raffy}, \citenamefont
-%  {Li} \emph {et~al.}}]{legros2019}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-%  {Legros}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Benhabib}},
-%  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Tabis}}, \bibinfo
-%  {author} {\bibfnamefont {F.}~\bibnamefont {Lalibert{\'e}}}, \bibinfo {author}
-%  {\bibfnamefont {M.}~\bibnamefont {Dion}}, \bibinfo {author} {\bibfnamefont
-%  {M.}~\bibnamefont {Lizaire}}, \bibinfo {author} {\bibfnamefont
-%  {B.}~\bibnamefont {Vignolle}}, \bibinfo {author} {\bibfnamefont
-%  {D.}~\bibnamefont {Vignolles}}, \bibinfo {author} {\bibfnamefont
-%  {H.}~\bibnamefont {Raffy}}, \bibinfo {author} {\bibfnamefont
-%  {Z.}~\bibnamefont {Li}}, \emph {et~al.},\ }\href@noop {} {\bibfield
-%  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
-%  {15}},\ \bibinfo {pages} {142} (\bibinfo {year} {2019})}\BibitemShut
-%  {NoStop}%
-%\bibitem [{\citenamefont {McGreevy}(2023)}]{McGreevy2023}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-%  {McGreevy}},\ }\href
-%  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-040721-021029}
-%  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-%  Physics}\ }\textbf {\bibinfo {volume} {14}},\ \bibinfo {pages} {57} (\bibinfo
-%  {year} {2023})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Luttinger}\ and\ \citenamefont
-%  {Ward}(1960)}]{luttinger1960ground}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-%  {Luttinger}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
-%  {Ward}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical
-%  Review}\ }\textbf {\bibinfo {volume} {118}},\ \bibinfo {pages} {1417}
-%  (\bibinfo {year} {1960})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Su}\ and\ \citenamefont
-%  {Martin}(2025)}]{su2025anomalies}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-%  {Su}}\ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Martin}},\
-%  }\href {https://arxiv.org/abs/2405.08093} {} (\bibinfo {year} {2025}),\
-%  \Eprint {https://arxiv.org/abs/2405.08093} {arXiv:2405.08093
-%  [cond-mat.str-el]} \BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Adler}(1969)}]{adler1969axial}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont
-%  {Adler}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-%  {Physical Review}\ }\textbf {\bibinfo {volume} {177}},\ \bibinfo {pages}
-%  {2426} (\bibinfo {year} {1969})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Bell}\ and\ \citenamefont
-%  {Jackiw}(1969)}]{bell1969pcac}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~S.}\ \bibnamefont
-%  {Bell}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Jackiw}},\
-%  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Il Nuovo Cimento
-%  A}\ }\textbf {\bibinfo {volume} {60}},\ \bibinfo {pages} {47} (\bibinfo
-%  {year} {1969})}\BibitemShut {NoStop}%
-%\bibitem [{\citenamefont {Casini}\ and\ \citenamefont
-%  {Mag\'{a}n}(2021)}]{Casini2021Symmetries}%
-%  \BibitemOpen
-%  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-%  {Casini}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-%  {Mag\'{a}n}},\ }\href {https://doi.org/10.1142/S0217732321300251} {\bibfield
-%  {journal} {\bibinfo  {journal} {Modern Physics Letters A}\ }\textbf {\bibinfo
-%  {volume} {36}},\ \bibinfo {pages} {2130025} (\bibinfo {year}
-%  {2021})}\BibitemShut {NoStop}%
-%\end{thebibliography}
-
-%\bibliography{tilingProject}
-
-\begin{thebibliography}{89}%
+Its fate under finite doping presents a compelling direction for future investigation.
+
+\begin{thebibliography}{99}
 \makeatletter
@@
 %</preamble>
+
 \bibitem [{\citenamefont {Landau}(1957)}]{landau1959theory}%
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Landau}},\ }\bibfield  {title} {\bibinfo {title} {The theory of a fermi
-  liquid},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Soviet
+  {Landau}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Soviet
   Physics Jetp-Ussr}\ }\textbf {\bibinfo {volume} {3}},\ \bibinfo {pages} {920}
@@
   {Langley}},\ and\ \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont
-  {Hutasoit}},\ }\bibfield  {title} {\bibinfo {title} {Un-fermi liquids:
-  Unparticles in strongly correlated electron matter},\ }\href
-  {https://doi.org/10.1103/PhysRevB.88.115129} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {88}},\ \bibinfo
-  {pages} {115129} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+  {Hutasoit}},\ }\href {https://doi.org/10.1103/PhysRevB.88.115129} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {88}},\ \bibinfo {pages} {115129} (\bibinfo {year} {2013})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Dzyaloshinskii}(2003)}]{dzyaloshinskii2003some}%
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
-  {Dzyaloshinskii}},\ }\bibfield  {title} {\bibinfo {title} {Some consequences
-  of the luttinger theorem: The luttinger surfaces in non-fermi liquids and
-  mott insulators},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Dzyaloshinskii}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
   {Physical Review B}\ }\textbf {\bibinfo {volume} {68}},\ \bibinfo {pages}
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~F.}\ \bibnamefont
-  {Mott}},\ }\bibfield  {title} {\bibinfo {title} {The basis of the electron
-  theory of metals, with special reference to the transition metals},\ }\href
-  {https://doi.org/10.1088/0370-1298/62/7/303} {\bibfield  {journal} {\bibinfo
-  {journal} {Proceedings of the Physical Society. Section A}\ }\textbf
-  {\bibinfo {volume} {62}},\ \bibinfo {pages} {416} (\bibinfo {year}
-  {1949})}\BibitemShut {NoStop}%
+  {Mott}},\ }\href {https://doi.org/10.1088/0370-1298/62/7/303} {\bibfield
+  {journal} {\bibinfo  {journal} {Proceedings of the Physical Society. Section
+  A}\ }\textbf {\bibinfo {volume} {62}},\ \bibinfo {pages} {416} (\bibinfo
+  {year} {1949})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2022)\citenamefont
@@
   {Hussey}},\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Abbamonte}},\ }\bibfield  {title} {\bibinfo {title} {Stranger than metals},\
-  }\href {https://doi.org/10.1126/science.abh4273} {\bibfield  {journal}
-  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {377}},\ \bibinfo
-  {pages} {eabh4273} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+  {Abbamonte}},\ }\href {https://doi.org/10.1126/science.abh4273} {\bibfield
+  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
+  {377}},\ \bibinfo {pages} {eabh4273} (\bibinfo {year} {2022})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Loeser}\ \emph {et~al.}(1996)\citenamefont {Loeser},
@@
   {\bibfnamefont {P.}~\bibnamefont {Fournier}},\ and\ \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Kapitulnik}},\ }\bibfield  {title}
-  {\bibinfo {title} {Excitation gap in the normal state of underdoped
-  bi2sr2cacu2o8},\ }\href {https://doi.org/10.1126/science.273.5273.325}
-  {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo
-  {volume} {273}},\ \bibinfo {pages} {325} (\bibinfo {year}
-  {1996})}\BibitemShut {NoStop}%
+  {\bibfnamefont {A.}~\bibnamefont {Kapitulnik}},\ }\href
+  {https://doi.org/10.1126/science.273.5273.325} {\bibfield  {journal}
+  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {273}},\ \bibinfo
+  {pages} {325} (\bibinfo {year} {1996})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Norman}\ \emph {et~al.}(1998)\citenamefont {Norman},
@@
   {P.}~\bibnamefont {Guptasarma}},\ and\ \bibinfo {author} {\bibfnamefont
-  {D.~G.}\ \bibnamefont {Hinks}},\ }\bibfield  {title} {\bibinfo {title}
-  {Destruction of the fermi surface in underdoped high-tc superconductors},\
-  }\href {https://doi.org/10.1038/32366} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature}\ }\textbf {\bibinfo {volume} {392}},\ \bibinfo {pages}
-  {157} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
+  {D.~G.}\ \bibnamefont {Hinks}},\ }\href {https://doi.org/10.1038/32366}
+  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
+  {volume} {392}},\ \bibinfo {pages} {157} (\bibinfo {year}
+  {1998})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Hashimoto}\ \emph {et~al.}(2014)\citenamefont
@@
   \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont {Devereaux}},\ and\
-  \bibinfo {author} {\bibfnamefont {Z.-X.}\ \bibnamefont {Shen}},\ }\bibfield
-  {title} {\bibinfo {title} {Energy gaps in high-transition-temperature cuprate
-  superconductors},\ }\href {https://doi.org/10.1038/nphys3009} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
-  {10}},\ \bibinfo {pages} {483} (\bibinfo {year} {2014})}\BibitemShut
-  {NoStop}%
+  \bibinfo {author} {\bibfnamefont {Z.-X.}\ \bibnamefont {Shen}},\ }\href
+  {https://doi.org/10.1038/nphys3009} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo
+  {pages} {483} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Taillefer}(2010)}]{taillefer2010}%
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Taillefer}},\ }\bibfield  {title} {\bibinfo {title} {Scattering and pairing
-  in cuprate superconductors},\ }\href
+  {Taillefer}},\ }\href
   {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-070909-104117}
@@
   {Kivelson}},\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-  {Tranquada}},\ }\bibfield  {title} {\bibinfo {title} {Colloquium: Theory of
-  intertwined orders in high temperature superconductors},\ }\href
-  {https://doi.org/10.1103/RevModPhys.87.457} {\bibfield  {journal} {\bibinfo
-  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {87}},\ \bibinfo
-  {pages} {457} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+  {Tranquada}},\ }\href {https://doi.org/10.1103/RevModPhys.87.457} {\bibfield
+  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume}
+  {87}},\ \bibinfo {pages} {457} (\bibinfo {year} {2015})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Sato}\ \emph {et~al.}(2017)\citenamefont {Sato},
@@
   {T.}~\bibnamefont {Shibauchi}},\ and\ \bibinfo {author} {\bibfnamefont
-  {Y.}~\bibnamefont {Matsuda}},\ }\bibfield  {title} {\bibinfo {title}
-  {Thermodynamic evidence for a nematic phase transition at the onset of the
-  pseudogap in yba2cu3oy},\ }\href {https://doi.org/10.1038/nphys4205}
+  {Y.}~\bibnamefont {Matsuda}},\ }\href {https://doi.org/10.1038/nphys4205}
   {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf
@@
   \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\ and\ \bibinfo
-  {author} {\bibfnamefont {L.}~\bibnamefont {Taillefer}},\ }\bibfield  {title}
-  {\bibinfo {title} {Pseudogap phase of cuprate superconductors confined by
-  fermi surface topology},\ }\href {https://doi.org/10.1038/s41467-017-02122-x}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature Communications}\ }\textbf
-  {\bibinfo {volume} {8}},\ \bibinfo {pages} {2044} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
+  {author} {\bibfnamefont {L.}~\bibnamefont {Taillefer}},\ }\href
+  {https://doi.org/10.1038/s41467-017-02122-x} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature Communications}\ }\textbf {\bibinfo {volume} {8}},\
+  \bibinfo {pages} {2044} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Mukhopadhyay}\ \emph {et~al.}(2019)\citenamefont
@@
   {Davis}},\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Fujita}},\ }\bibfield  {title} {\bibinfo {title} {Evidence for a vestigial
-  nematic state in the cuprate pseudogap phase},\ }\href
-  {https://doi.org/10.1073/pnas.1821454116} {\bibfield  {journal} {\bibinfo
-  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-  {\bibinfo {volume} {116}},\ \bibinfo {pages} {13249} (\bibinfo {year}
-  {2019})}\BibitemShut {NoStop}%
+  {Fujita}},\ }\href {https://doi.org/10.1073/pnas.1821454116} {\bibfield
+  {journal} {\bibinfo  {journal} {Proceedings of the National Academy of
+  Sciences}\ }\textbf {\bibinfo {volume} {116}},\ \bibinfo {pages} {13249}
+  (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Gupta}\ \emph {et~al.}(2021)\citenamefont {Gupta},
@@
   {\bibfnamefont {B.~D.}\ \bibnamefont {Gaulin}},\ and\ \bibinfo {author}
-  {\bibfnamefont {D.~G.}\ \bibnamefont {Hawthorn}},\ }\bibfield  {title}
-  {\bibinfo {title} {Vanishing nematic order beyond the pseudogap phase in
-  overdoped cuprate superconductors},\ }\href
+  {\bibfnamefont {D.~G.}\ \bibnamefont {Hawthorn}},\ }\href
   {https://doi.org/10.1073/pnas.2106881118} {\bibfield  {journal} {\bibinfo
@@
   {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ and\ \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Fujimori}},\ }\bibfield  {title} {\bibinfo
-  {title} {Pseudogap in electron-doped cuprates: Strong correlation leading to
-  band splitting},\ }\href {https://doi.org/10.1073/pnas.2406624122} {\bibfield
-   {journal} {\bibinfo  {journal} {Proceedings of the National Academy of
-  Sciences}\ }\textbf {\bibinfo {volume} {122}},\ \bibinfo {pages}
-  {e2406624122} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
+  {\bibfnamefont {A.}~\bibnamefont {Fujimori}},\ }\href
+  {https://doi.org/10.1073/pnas.2406624122} {\bibfield  {journal} {\bibinfo
+  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
+  {\bibinfo {volume} {122}},\ \bibinfo {pages} {e2406624122} (\bibinfo {year}
+  {2025})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Kyung}\ \emph {et~al.}(2006)\citenamefont {Kyung},
@@
   {Tremblay}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Civelli}},\
-  and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Kotliar}},\
-  }\bibfield  {title} {\bibinfo {title} {Pseudogap induced by short-range spin
-  correlations in a doped mott insulator},\ }\href
+  and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Kotliar}},\ }\href
   {https://doi.org/10.1103/PhysRevB.73.165114} {\bibfield  {journal} {\bibinfo
@@
   {author} {\bibfnamefont {P.~R.~C.}\ \bibnamefont {Kent}},\ and\ \bibinfo
-  {author} {\bibfnamefont {E.}~\bibnamefont {D'Azevedo}},\ }\bibfield  {title}
-  {\bibinfo {title} {Pseudogap and antiferromagnetic correlations in the
-  hubbard model},\ }\href {https://doi.org/10.1103/PhysRevLett.97.036401}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-  {\bibinfo {volume} {97}},\ \bibinfo {pages} {036401} (\bibinfo {year}
-  {2006})}\BibitemShut {NoStop}%
+  {author} {\bibfnamefont {E.}~\bibnamefont {D'Azevedo}},\ }\href
+  {https://doi.org/10.1103/PhysRevLett.97.036401} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {97}},\
+  \bibinfo {pages} {036401} (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2009)\citenamefont {Sakai},
@@
   {Sakai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Motome}},\ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\bibfield
-  {title} {\bibinfo {title} {Evolution of electronic structure of doped mott
-  insulators: Reconstruction of poles and zeros of green’s function},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical review
-  letters}\ }\textbf {\bibinfo {volume} {102}},\ \bibinfo {pages} {056404}
-  (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physical review letters}\
+  }\textbf {\bibinfo {volume} {102}},\ \bibinfo {pages} {056404} (\bibinfo
+  {year} {2009})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Werner}\ \emph {et~al.}(2009)\citenamefont {Werner},
@@
   \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}},\ and\
-  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\ }\bibfield
-   {title} {\bibinfo {title} {Momentum-selective metal-insulator transition in
-  the two-dimensional hubbard model: An 8-site dynamical cluster approximation
-  study},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical
-  Review B}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages} {045120}
-  (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  B}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages} {045120} (\bibinfo
+  {year} {2009})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2010)\citenamefont {Sakai},
@@
   {Sakai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Motome}},\ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\bibfield
-  {title} {\bibinfo {title} {Doped high-t c cuprate superconductors elucidated
-  in the light of zeros and poles of the electronic green’s function},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
-  B}\ }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {134505} (\bibinfo
-  {year} {2010})}\BibitemShut {NoStop}%
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review B}\ }\textbf
+  {\bibinfo {volume} {82}},\ \bibinfo {pages} {134505} (\bibinfo {year}
+  {2010})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Lin}\ \emph {et~al.}(2010)\citenamefont {Lin},
@@
   {Lin}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Gull}},\ and\
-  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\ }\bibfield
-   {title} {\bibinfo {title} {Physics of the pseudogap in eight-site cluster
-  dynamical mean-field theory: Photoemission, raman scattering, and in-plane
-  and c-axs=is conductivity},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {82}},\ \bibinfo
-  {pages} {045104} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
+  }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {045104} (\bibinfo
+  {year} {2010})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Gull}\ \emph {et~al.}(2010)\citenamefont {Gull},
@@
   {author} {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-  {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\ }\bibfield  {title}
-  {\bibinfo {title} {Momentum-space anisotropy and pseudogaps: A comparative
-  cluster dynamical mean-field analysis of the doping-driven metal-insulator
-  transition in the two-dimensional hubbard model},\ }\href@noop {} {\bibfield
+  {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\ }\href@noop {} {\bibfield
   {journal} {\bibinfo  {journal} {Physical Review B}\ }\textbf {\bibinfo
@@
   {Gull}}\ and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
-  {Millis}},\ }\bibfield  {title} {\bibinfo {title} {Energetics of
-  superconductivity in the two-dimensional hubbard model},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo
-  {volume} {86}},\ \bibinfo {pages} {241106} (\bibinfo {year}
-  {2012})}\BibitemShut {NoStop}%
+  {Millis}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. B}\ }\textbf {\bibinfo {volume} {86}},\ \bibinfo {pages} {241106}
+  (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Mirzaei}\ \emph {et~al.}(2013)\citenamefont
@@
   {\bibfnamefont {N.}~\bibnamefont {Barišić}},\ and\ \bibinfo {author}
-  {\bibfnamefont {D.}~\bibnamefont {van~der Marel}},\ }\bibfield  {title}
-  {\bibinfo {title} {Spectroscopic evidence for fermi liquid-like energy and
-  temperature dependence of the relaxation rate in the pseudogap phase of the
-  cuprates},\ }\href {https://doi.org/10.1073/pnas.1218846110} {\bibfield
-  {journal} {\bibinfo  {journal} {Proceedings of the National Academy of
-  Sciences}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo {pages} {5774}
-  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+  {\bibfnamefont {D.}~\bibnamefont {van~der Marel}},\ }\href
+  {https://doi.org/10.1073/pnas.1218846110} {\bibfield  {journal} {\bibinfo
+  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
+  {\bibinfo {volume} {110}},\ \bibinfo {pages} {5774} (\bibinfo {year}
+  {2013})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Gull}\ \emph {et~al.}(2013)\citenamefont {Gull},
@@
   and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
-  }\bibfield  {title} {\bibinfo {title} {Superconductivity and the pseudogap in
-  the two-dimensional hubbard model},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Physical review letters}\ }\textbf {\bibinfo {volume}
-  {110}},\ \bibinfo {pages} {216405} (\bibinfo {year} {2013})}\BibitemShut
-  {NoStop}%
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical review
+  letters}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo {pages} {216405}
+  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
@@
   {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Lal}},\ }\bibfield  {title} {\bibinfo {title} {Scaling theory for
-  mott{\textendash}hubbard transitions-{II}: quantum criticality of the doped
-  mott insulator},\ }\href {https://doi.org/10.1088/1367-2630/ab890c}
-  {\bibfield  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf
-  {\bibinfo {volume} {22}},\ \bibinfo {pages} {063008} (\bibinfo {year}
+  {Lal}},\ }\href {https://doi.org/10.1088/1367-2630/ab890c} {\bibfield
+  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
+  {volume} {22}},\ \bibinfo {pages} {063008} (\bibinfo {year}
   {2020}{\natexlab{a}})}\BibitemShut {NoStop}%
@@
   \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Honerkamp}},\ and\
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Andergassen}},\
-  }\bibfield  {title} {\bibinfo {title} {Pseudogap opening in the
-  two-dimensional hubbard model: A functional renormalization group analysis},\
-  }\href {https://doi.org/10.1103/PhysRevResearch.2.033068} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. Res.}\ }\textbf {\bibinfo {volume}
-  {2}},\ \bibinfo {pages} {033068} (\bibinfo {year} {2020})}\BibitemShut
-  {NoStop}%
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Andergassen}},\ }\href
+  {https://doi.org/10.1103/PhysRevResearch.2.033068} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Res.}\ }\textbf {\bibinfo {volume} {2}},\
+  \bibinfo {pages} {033068} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Jiang}\ \emph {et~al.}(2022)\citenamefont {Jiang},
@@
   \bibnamefont {Chubukov}},\ and\ \bibinfo {author} {\bibfnamefont {Z.~Y.}\
-  \bibnamefont {Meng}},\ }\bibfield  {title} {\bibinfo {title} {Monte carlo
-  study of the pseudogap and superconductivity emerging from quantum magnetic
-  fluctuations},\ }\href {https://doi.org/10.1038/s41467-022-30302-x}
+  \bibnamefont {Meng}},\ }\href {https://doi.org/10.1038/s41467-022-30302-x}
   {\bibfield  {journal} {\bibinfo  {journal} {Nature Communications}\ }\textbf
@@
   {author} {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Sachdev}},\ }\bibfield  {title} {\bibinfo
-  {title} {Topological order in the pseudogap metal},\ }\href
+  {\bibfnamefont {S.}~\bibnamefont {Sachdev}},\ }\href
   {https://doi.org/10.1073/pnas.1720580115} {\bibfield  {journal} {\bibinfo
@@
   \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Toschi}},\ and\ \bibinfo
-  {author} {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\bibfield  {title}
-  {\bibinfo {title} {Explaining the pseudogap through damping and antidamping
-  on the fermi surface by imaginary spin scattering},\ }\href
+  {author} {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\href
   {https://doi.org/10.1038/s42005-022-01117-5} {\bibfield  {journal} {\bibinfo
@@
   {\bibfnamefont {R.}~\bibnamefont {Arita}},\ and\ \bibinfo {author}
-  {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\bibfield  {title} {\bibinfo
-  {title} {Optimizing superconductivity: From cuprates via nickelates to
-  palladates},\ }\href {https://doi.org/10.1103/PhysRevLett.130.166002}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-  {\bibinfo {volume} {130}},\ \bibinfo {pages} {166002} (\bibinfo {year}
-  {2023})}\BibitemShut {NoStop}%
+  {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\href
+  {https://doi.org/10.1103/PhysRevLett.130.166002} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {130}},\
+  \bibinfo {pages} {166002} (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Sorella}(2023)}]{Sorella2023}%
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Sorella}},\ }\bibfield  {title} {\bibinfo {title} {Systematically improvable
-  mean-field variational ansatz for strongly correlated systems: Application to
-  the hubbard model},\ }\href {https://doi.org/10.1103/PhysRevB.107.115133}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo
-  {volume} {107}},\ \bibinfo {pages} {115133} (\bibinfo {year}
-  {2023})}\BibitemShut {NoStop}%
+  {Sorella}},\ }\href {https://doi.org/10.1103/PhysRevB.107.115133} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {107}},\ \bibinfo {pages} {115133} (\bibinfo {year} {2023})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Schäfer}\ \emph {et~al.}(2021)\citenamefont
@@
   {O.}~\bibnamefont {Parcollet}},\ and\ \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Georges}},\ }\bibfield  {title} {\bibinfo {title}
-  {Tracking the footprints of spin fluctuations: A multimethod, multimessenger
-  study of the two-dimensional hubbard model},\ }\href
+  {A.}~\bibnamefont {Georges}},\ }\href
   {https://doi.org/10.1103/PhysRevX.11.011058} {\bibfield  {journal} {\bibinfo
@@
   {White}}\ and\ \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
-  {Scalapino}},\ }\bibfield  {title} {\bibinfo {title} {Density matrix
-  renormalization group study of the striped phase in the 2d
-  $\mathit{t}\ensuremath{-}\mathit{J}$ model},\ }\href
-  {https://doi.org/10.1103/PhysRevLett.80.1272} {\bibfield  {journal} {\bibinfo
-   {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo
-  {pages} {1272} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
+  {Scalapino}},\ }\href {https://doi.org/10.1103/PhysRevLett.80.1272}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
+  {\bibinfo {volume} {80}},\ \bibinfo {pages} {1272} (\bibinfo {year}
+  {1998})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Ido}\ \emph {et~al.}(2018)\citenamefont {Ido},
@@
   {Ido}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Ohgoe}},\ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\bibfield
-  {title} {\bibinfo {title} {Competition among various charge-inhomogeneous
-  states and $d$-wave superconducting state in hubbard models on square
-  lattices},\ }\href {https://doi.org/10.1103/PhysRevB.97.045138} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-  {97}},\ \bibinfo {pages} {045138} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href
+  {https://doi.org/10.1103/PhysRevB.97.045138} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo
+  {pages} {045138} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Proust}\ and\ \citenamefont
@@
   {Proust}}\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Taillefer}},\ }\bibfield  {title} {\bibinfo {title} {The remarkable
-  underlying ground states of cuprate superconductors},\ }\href
+  {Taillefer}},\ }\href
   {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-031218-013210}
@@
   {Chung}},\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Corboz}},\ }\bibfield  {title} {\bibinfo {title} {Period 4 stripe in the
-  extended two-dimensional hubbard model},\ }\href
-  {https://doi.org/10.1103/PhysRevB.100.195141} {\bibfield  {journal} {\bibinfo
-   {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {100}},\ \bibinfo
-  {pages} {195141} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+  {Corboz}},\ }\href {https://doi.org/10.1103/PhysRevB.100.195141} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {100}},\ \bibinfo {pages} {195141} (\bibinfo {year} {2019})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Xu}\ \emph {et~al.}(2022)\citenamefont {Xu},
@@
   {\bibfnamefont {M.}~\bibnamefont {Qin}},\ and\ \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Zhang}},\ }\bibfield  {title} {\bibinfo
-  {title} {Stripes and spin-density waves in the doped two-dimensional hubbard
-  model: Ground state phase diagram},\ }\href
+  {\bibfnamefont {S.}~\bibnamefont {Zhang}},\ }\href
   {https://doi.org/10.1103/PhysRevResearch.4.013239} {\bibfield  {journal}
@@
   {Dave}}, \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\
-  and\ \bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont {Kane}},\
-  }\bibfield  {title} {\bibinfo {title} {Absence of luttinger's theorem due to
-  zeros in the single-particle green function},\ }\href
+  and\ \bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont {Kane}},\ }\href
   {https://doi.org/10.1103/PhysRevLett.110.090403} {\bibfield  {journal}
@@
   {Seki}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Yunoki}},\
-  }\bibfield  {title} {\bibinfo {title} {Topological interpretation of the
-  luttinger theorem},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Physical Review B}\ }\textbf {\bibinfo {volume} {96}},\ \bibinfo
-  {pages} {085124} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  B}\ }\textbf {\bibinfo {volume} {96}},\ \bibinfo {pages} {085124} (\bibinfo
+  {year} {2017})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Anderson}\ and\ \citenamefont
@@
   {Anderson}}\ and\ \bibinfo {author} {\bibfnamefont {F.~D.~M.}\ \bibnamefont
-  {Haldane}},\ }\bibfield  {title} {\bibinfo {title} {The symmetries of fermion
-  fluids at low dimensions},\ }\href {https://doi.org/10.1023/A:1010324912515}
-  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Statistical Physics}\
-  }\textbf {\bibinfo {volume} {103}},\ \bibinfo {pages} {425} (\bibinfo {year}
+  {Haldane}},\ }\href {https://doi.org/10.1023/A:1010324912515} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Statistical Physics}\ }\textbf
+  {\bibinfo {volume} {103}},\ \bibinfo {pages} {425} (\bibinfo {year}
   {2001})}\BibitemShut {NoStop}%
@@
   and\ \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\
-  }\bibfield  {title} {\bibinfo {title} {Discrete symmetry breaking defines the
-  mott quartic fixed point},\ }\href
-  {https://doi.org/10.1038/s41567-022-01529-8} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {18}},\ \bibinfo
-  {pages} {511} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+  }\href {https://doi.org/10.1038/s41567-022-01529-8} {\bibfield  {journal}
+  {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {18}},\
+  \bibinfo {pages} {511} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Coleman}\ \emph {et~al.}(2001)\citenamefont
@@
   \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Si}},\ and\ \bibinfo
-  {author} {\bibfnamefont {R.}~\bibnamefont {Ramazashvili}},\ }\bibfield
-  {title} {\bibinfo {title} {How do fermi liquids get heavy and die?},\ }\href
+  {author} {\bibfnamefont {R.}~\bibnamefont {Ramazashvili}},\ }\href
   {https://doi.org/10.1088/0953-8984/13/35/202} {\bibfield  {journal} {\bibinfo
@@
   {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Lal}},\ }\bibfield  {title} {\bibinfo {title} {Unitary renormalisation group
-  for correlated electrons-i: a tensor network approach},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nuclear Physics B}\ }\textbf
-  {\bibinfo {volume} {960}},\ \bibinfo {pages} {115170} (\bibinfo {year}
-  {2020}{\natexlab{b}})}\BibitemShut {NoStop}%
+  {Lal}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nuclear
+  Physics B}\ }\textbf {\bibinfo {volume} {960}},\ \bibinfo {pages} {115170}
+  (\bibinfo {year} {2020}{\natexlab{b}})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
@@
   {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Lal}},\ }\bibfield  {title} {\bibinfo {title} {Unitary renormalisation group
-  for correlated electrons-ii: insights on fermionic criticality},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Nuclear Physics B}\ }\textbf
-  {\bibinfo {volume} {960}},\ \bibinfo {pages} {115163} (\bibinfo {year}
-  {2020}{\natexlab{c}})}\BibitemShut {NoStop}%
+  {Lal}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nuclear
+  Physics B}\ }\textbf {\bibinfo {volume} {960}},\ \bibinfo {pages} {115163}
+  (\bibinfo {year} {2020}{\natexlab{c}})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Keimer}\ \emph {et~al.}(2015)\citenamefont {Keimer},
@@
   and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zaanen}},\
-  }\bibfield  {title} {\bibinfo {title} {From quantum matter to
-  high-temperature superconductivity in copper oxides},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
-  {volume} {518}},\ \bibinfo {pages} {179} (\bibinfo {year}
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf
+  {\bibinfo {volume} {518}},\ \bibinfo {pages} {179} (\bibinfo {year}
   {2015})}\BibitemShut {NoStop}%
@@
   {Hatsugai}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Kohmoto}},\ }\bibfield  {title} {\bibinfo {title} {Exactly solvable model of
-  correlated lattice electrons in any dimensions},\ }\href
-  {https://doi.org/10.1143/JPSJ.61.2056} {\bibfield  {journal} {\bibinfo
-  {journal} {Journal of the Physical Society of Japan}\ }\textbf {\bibinfo
-  {volume} {61}},\ \bibinfo {pages} {2056} (\bibinfo {year}
+  {Kohmoto}},\ }\href {https://doi.org/10.1143/JPSJ.61.2056} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of the Physical Society of Japan}\
+  }\textbf {\bibinfo {volume} {61}},\ \bibinfo {pages} {2056} (\bibinfo {year}
   {1992})}\BibitemShut {NoStop}%
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Baskaran}},\ }\bibfield  {title} {\bibinfo {title} {An exactly solvable
-  fermion model: spinons, holons and a non-fermi liquid phase},\ }\href
-  {https://doi.org/10.1142/S0217984991000782} {\bibfield  {journal} {\bibinfo
-  {journal} {Modern Physics Letters B}\ }\textbf {\bibinfo {volume} {05}},\
-  \bibinfo {pages} {643} (\bibinfo {year} {1991})}\BibitemShut {NoStop}%
+  {Baskaran}},\ }\href {https://doi.org/10.1142/S0217984991000782} {\bibfield
+  {journal} {\bibinfo  {journal} {Modern Physics Letters B}\ }\textbf {\bibinfo
+  {volume} {05}},\ \bibinfo {pages} {643} (\bibinfo {year} {1991})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Altshuler}\ \emph {et~al.}(1998)\citenamefont
@@
   {Finkel'stein}},\ and\ \bibinfo {author} {\bibfnamefont {D.~K.}\ \bibnamefont
-  {Morr}},\ }\bibfield  {title} {\bibinfo {title} {Luttinger theorem for a
-  spin-density-wave state},\ }\href {https://doi.org/10.1209/epl/i1998-00164-y}
-  {\bibfield  {journal} {\bibinfo  {journal} {Europhysics Letters}\ }\textbf
-  {\bibinfo {volume} {41}},\ \bibinfo {pages} {401} (\bibinfo {year}
-  {1998})}\BibitemShut {NoStop}%
+  {Morr}},\ }\href {https://doi.org/10.1209/epl/i1998-00164-y} {\bibfield
+  {journal} {\bibinfo  {journal} {Europhysics Letters}\ }\textbf {\bibinfo
+  {volume} {41}},\ \bibinfo {pages} {401} (\bibinfo {year} {1998})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Heath}\ and\ \citenamefont
@@
   {Heath}}\ and\ \bibinfo {author} {\bibfnamefont {K.~S.}\ \bibnamefont
-  {Bedell}},\ }\bibfield  {title} {\bibinfo {title} {Necessary and sufficient
-  conditions for the validity of luttinger’s theorem},\ }\href
-  {https://doi.org/10.1088/1367-2630/ab890e} {\bibfield  {journal} {\bibinfo
-  {journal} {New Journal of Physics}\ }\textbf {\bibinfo {volume} {22}},\
-  \bibinfo {pages} {063011} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+  {Bedell}},\ }\href {https://doi.org/10.1088/1367-2630/ab890e} {\bibfield
+  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
+  {volume} {22}},\ \bibinfo {pages} {063011} (\bibinfo {year}
+  {2020})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Nave}\ \emph {et~al.}(2025)\citenamefont {Nave},
@@
   {Taraphder}},\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Lal}},\ }\bibfield  {title} {\bibinfo {title} {Kondo frustration via charge
-  fluctuations: a route to mott localisation},\ }\href
-  {https://doi.org/10.1088/1367-2630/ad08f3} {\bibfield  {journal} {\bibinfo
-  {journal} {New Journal of Physics}\ }\textbf {\bibinfo {volume} {25}},\
-  \bibinfo {pages} {113011} (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
+  {Lal}},\ }\href {https://doi.org/10.1088/1367-2630/ad08f3} {\bibfield
+  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
+  {volume} {25}},\ \bibinfo {pages} {113011} (\bibinfo {year}
+  {2023})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Georges}\ \emph {et~al.}(1996)\citenamefont
@@
   \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Krauth}},\ and\ \bibinfo
-  {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Rozenberg}},\ }\bibfield
-  {title} {\bibinfo {title} {Dynamical mean-field theory of strongly correlated
-  fermion systems and the limit of infinite dimensions},\ }\href@noop {}
+  {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Rozenberg}},\ }\href@noop {}
   {\bibfield  {journal} {\bibinfo  {journal} {Reviews of Modern Physics}\
@@
   and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Krishnamurthy}},\
-  }\bibfield  {title} {\bibinfo {title} {Nonlocal dynamical correlations of
-  strongly interacting electron systems},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Physical Review B}\ }\textbf {\bibinfo {volume} {58}},\
-  \bibinfo {pages} {R7475} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
+  B}\ }\textbf {\bibinfo {volume} {58}},\ \bibinfo {pages} {R7475} (\bibinfo
+  {year} {1998})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Kotliar}\ \emph {et~al.}(2001)\citenamefont
@@
   {P{\'a}lsson}},\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Biroli}},\ }\bibfield  {title} {\bibinfo {title} {Cellular dynamical mean
-  field approach to strongly correlated systems},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Physical review letters}\ }\textbf {\bibinfo
-  {volume} {87}},\ \bibinfo {pages} {186401} (\bibinfo {year}
-  {2001})}\BibitemShut {NoStop}%
+  {Biroli}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical review letters}\ }\textbf {\bibinfo {volume} {87}},\ \bibinfo
+  {pages} {186401} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Maier}\ \emph {et~al.}(2005)\citenamefont {Maier},
@@
   \bibinfo {author} {\bibfnamefont {P.~R.~C.}\ \bibnamefont {Kent}},\ and\
-  \bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont {White}},\ }\bibfield
-  {title} {\bibinfo {title} {Systematic study of d-wave superconductivity in
-  the 2d repulsive hubbard model},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {95}},\
-  \bibinfo {pages} {237001} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+  \bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont {White}},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
+  {\bibinfo {volume} {95}},\ \bibinfo {pages} {237001} (\bibinfo {year}
+  {2005})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Stoyanova}(2006)}]{stoyanova}%
@@
   {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Ferrero}},\ }\bibfield  {title} {\bibinfo
-  {title} {Pseudogap and fermi-surface topology in the two-dimensional hubbard
-  model},\ }\href {https://doi.org/10.1103/PhysRevX.8.021048} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume}
-  {8}},\ \bibinfo {pages} {021048} (\bibinfo {year} {2018})}\BibitemShut
-  {NoStop}%
+  {\bibfnamefont {M.}~\bibnamefont {Ferrero}},\ }\href
+  {https://doi.org/10.1103/PhysRevX.8.021048} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {8}},\ \bibinfo {pages}
+  {021048} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Tsvelick}\ and\ \citenamefont
@@
   {Tsvelick}}\ and\ \bibinfo {author} {\bibfnamefont {P.~B.}\ \bibnamefont
-  {Wiegmann}},\ }\bibfield  {title} {\bibinfo {title} {Exact solution of the
-  multichannel kondo problem, scaling, and integrability},\ }\href
-  {https://doi.org/10.1007/BF01017853} {\bibfield  {journal} {\bibinfo
-  {journal} {Journal of Statistical Physics}\ }\textbf {\bibinfo {volume}
-  {38}},\ \bibinfo {pages} {125} (\bibinfo {year} {1985})}\BibitemShut
-  {NoStop}%
+  {Wiegmann}},\ }\href {https://doi.org/10.1007/BF01017853} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Statistical Physics}\ }\textbf
+  {\bibinfo {volume} {38}},\ \bibinfo {pages} {125} (\bibinfo {year}
+  {1985})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Emery}\ and\ \citenamefont
@@
   {Emery}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Kivelson}},\ }\bibfield  {title} {\bibinfo {title} {Mapping of the
-  two-channel kondo problem to a resonant-level model},\ }\href
-  {https://doi.org/10.1103/PhysRevB.46.10812} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {46}},\ \bibinfo
-  {pages} {10812} (\bibinfo {year} {1992})}\BibitemShut {NoStop}%
+  {Kivelson}},\ }\href {https://doi.org/10.1103/PhysRevB.46.10812} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {46}},\ \bibinfo {pages} {10812} (\bibinfo {year} {1992})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Gunnarsson}\ \emph {et~al.}(2003)\citenamefont
@@
   {Calandra}},\ and\ \bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont
-  {Han}},\ }\bibfield  {title} {\bibinfo {title} {Colloquium: Saturation of
-  electrical resistivity},\ }\href {https://doi.org/10.1103/RevModPhys.75.1085}
-  {\bibfield  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf
-  {\bibinfo {volume} {75}},\ \bibinfo {pages} {1085} (\bibinfo {year}
-  {2003})}\BibitemShut {NoStop}%
+  {Han}},\ }\href {https://doi.org/10.1103/RevModPhys.75.1085} {\bibfield
+  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume}
+  {75}},\ \bibinfo {pages} {1085} (\bibinfo {year} {2003})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Hussey}\ \emph {et~al.}(2004)\citenamefont {Hussey},
@@
   {Hussey}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Takenaka}},\
-  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\
-  }\bibfield  {title} {\bibinfo {title} {Universality of the
-  mott–ioffe–regel limit in metals},\ }\href
+  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\ }\href
   {https://doi.org/10.1080/14786430410001716944} {\bibfield  {journal}
@@
   {\bibfnamefont {M.}~\bibnamefont {Dressel}},\ and\ \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Fratini}},\ }\bibfield  {title} {\bibinfo
-  {title} {Rise and fall of landau’s quasiparticles while approaching the
-  mott transition},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Nat. Comm.}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {1571}
-  (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+  {\bibfnamefont {S.}~\bibnamefont {Fratini}},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Nat. Comm.}\ }\textbf {\bibinfo {volume}
+  {12}},\ \bibinfo {pages} {1571} (\bibinfo {year} {2021})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Qazilbash}\ \emph {et~al.}(2008)\citenamefont
@@
   {\bibfnamefont {H.~T.}\ \bibnamefont {Kim}},\ and\ \bibinfo {author}
-  {\bibfnamefont {D.~N.}\ \bibnamefont {Basov}},\ }\bibfield  {title} {\bibinfo
-  {title} {Electrodynamics of the vanadium oxides $\mathrm{V}{\mathrm{o}}_{2}$
-  and ${\mathrm{v}}_{2}{\mathrm{o}}_{3}$},\ }\href
+  {\bibfnamefont {D.~N.}\ \bibnamefont {Basov}},\ }\href
   {https://doi.org/10.1103/PhysRevB.77.115121} {\bibfield  {journal} {\bibinfo
@@
   \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Tagliacozzo}},\ and\
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Zoller}},\ }\bibfield
-  {title} {\bibinfo {title} {Measuring multipartite entanglement through
-  dynamic susceptibilities},\ }\href {https://doi.org/10.1038/nphys3700}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf
-  {\bibinfo {volume} {12}},\ \bibinfo {pages} {778} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
+  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Zoller}},\ }\href
+  {https://doi.org/10.1038/nphys3700} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
+  {pages} {778} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Balut}\ \emph {et~al.}(2025)\citenamefont {Balut},
@@
   {P.}~\bibnamefont {Abbamonte}},\ and\ \bibinfo {author} {\bibfnamefont
-  {P.~P.}\ \bibnamefont {W.}},\ }\bibfield  {title} {\bibinfo {title} {Quantum
-  fisher information reveals uv-ir mixing in the strange metal},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Physica C}\ }\textbf {\bibinfo
-  {volume} {635}},\ \bibinfo {pages} {1354750} (\bibinfo {year}
-  {2025})}\BibitemShut {NoStop}%
+  {P.~P.}\ \bibnamefont {W.}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Physica C}\ }\textbf {\bibinfo {volume} {635}},\ \bibinfo {pages}
+  {1354750} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Mazza}\ \emph {et~al.}(2024)\citenamefont {Mazza},
@@
   \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Ingersent}},\ and\
-  \bibinfo {author} {\bibfnamefont {J.~L.}\ \bibnamefont {Smith}},\ }\bibfield
-  {title} {\bibinfo {title} {Locally critical quantum phase transitions in
-  strongly correlated metals},\ }\href {https://doi.org/10.1038/35101507}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
-  {volume} {413}},\ \bibinfo {pages} {804} (\bibinfo {year}
-  {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Senthil}(2008)}]{senthil2008CriticalFermiSurface}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Senthil}},\ }\bibfield  {title} {\bibinfo {title} {Critical fermi surfaces
-  and non-fermi liquid metals},\ }\href
-  {https://doi.org/10.1103/PhysRevB.78.035103} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {78}},\ \bibinfo
-  {pages} {035103} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sekino}\ and\ \citenamefont
-  {Susskind}(2008)}]{sekino2008}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Sekino}}\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Susskind}},\ }\bibfield  {title} {\bibinfo {title} {Fast scramblers},\
-  }\href {https://doi.org/10.1088/1126-6708/2008/10/065} {\bibfield  {journal}
-  {\bibinfo  {journal} {Journal of High Energy Physics}\ }\textbf {\bibinfo
-  {volume} {2008}},\ \bibinfo {pages} {065} (\bibinfo {year}
-  {2008})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hayden}\ and\ \citenamefont
-  {Preskill}(2007)}]{hayden2007}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Hayden}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Preskill}},\ }\bibfield  {title} {\bibinfo {title} {Black holes as mirrors:
-  quantum information in random subsystems},\ }\href
-  {https://doi.org/10.1088/1126-6708/2007/09/120} {\bibfield  {journal}
-  {\bibinfo  {journal} {Journal of High Energy Physics}\ }\textbf {\bibinfo
-  {volume} {2007}},\ \bibinfo {pages} {120} (\bibinfo {year}
-  {2007})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bentsen}\ \emph {et~al.}(2019)\citenamefont
-  {Bentsen}, \citenamefont {Hashizume}, \citenamefont {Buyskikh}, \citenamefont
-  {Davis}, \citenamefont {Daley}, \citenamefont {Gubser},\ and\ \citenamefont
-  {Schleier-Smith}}]{bentsen2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Bentsen}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Hashizume}},
-  \bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont {Buyskikh}}, \bibinfo
-  {author} {\bibfnamefont {E.~J.}\ \bibnamefont {Davis}}, \bibinfo {author}
-  {\bibfnamefont {A.~J.}\ \bibnamefont {Daley}}, \bibinfo {author}
-  {\bibfnamefont {S.~S.}\ \bibnamefont {Gubser}},\ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Schleier-Smith}},\ }\bibfield  {title}
-  {\bibinfo {title} {Treelike interactions and fast scrambling with cold
-  atoms},\ }\href {https://doi.org/10.1103/PhysRevLett.123.130601} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
-  {volume} {123}},\ \bibinfo {pages} {130601} (\bibinfo {year}
-  {2019})}\BibitemShut {NoStop}%
+  \bibinfo {author} {\bibfnamefont {J.~L.}\ \bibnamefont {Smith}},\ }\href
+  {https://doi.org/10.1038/35101507} {\bibfield  {journal} {\bibinfo  {journal}
+  {Nature}\ }\textbf {\bibinfo {volume} {413}},\ \bibinfo {pages} {804}
+  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2020)\citenamefont
@@
   {Phillips}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Yeo}},\ and\
-  \bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont {Huang}},\ }\bibfield
-  {title} {\bibinfo {title} {Exact theory for superconductivity in a doped mott
-  insulator},\ }\href {https://doi.org/10.1038/s41567-020-0988-4} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
-  {16}},\ \bibinfo {pages} {1175} (\bibinfo {year} {2020})}\BibitemShut
-  {NoStop}%
+  \bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont {Huang}},\ }\href
+  {https://doi.org/10.1038/s41567-020-0988-4} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo
+  {pages} {1175} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Vafek}\ and\ \citenamefont
@@
   {Vafek}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Vishwanath}},\ }\bibfield  {title} {\bibinfo {title} {Dirac fermions in
-  solids: From high-tc cuprates and graphene to topological insulators and weyl
-  semimetals},\ }\href
+  {Vishwanath}},\ }\href
   {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-031113-133841}
@@
   {Morimoto}}\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Nagaosa}},\ }\bibfield  {title} {\bibinfo {title} {Weyl mott insulator},\
-  }\href {https://doi.org/10.1038/srep19853} {\bibfield  {journal} {\bibinfo
-  {journal} {Sci. Rep.}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages}
-  {19853} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+  {Nagaosa}},\ }\href {https://doi.org/10.1038/srep19853} {\bibfield  {journal}
+  {\bibinfo  {journal} {Sci. Rep.}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo
+  {pages} {19853} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Flores-Calder\'on}\ and\ \citenamefont
@@
   {Flores-Calder\'on}}\ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Hooley}},\ }\bibfield  {title} {\bibinfo {title} {Weyl-mott point:
-  Topological and non-fermi liquid behavior from an isolated green's function
-  zero},\ }\href {https://doi.org/10.1103/k4st-77ph} {\bibfield  {journal}
+  {Hooley}},\ }\href {https://doi.org/10.1103/k4st-77ph} {\bibfield  {journal}
   {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {111}},\
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Georgi}},\ }\bibfield  {title} {\bibinfo {title} {Unparticle physics},\
-  }\href {https://doi.org/10.1103/PhysRevLett.98.221601} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {98}},\
-  \bibinfo {pages} {221601} (\bibinfo {year} {2007}{\natexlab{a}})}\BibitemShut
-  {NoStop}%
+  {Georgi}},\ }\href {https://doi.org/10.1103/PhysRevLett.98.221601} {\bibfield
+   {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+  {volume} {98}},\ \bibinfo {pages} {221601} (\bibinfo {year}
+  {2007}{\natexlab{a}})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Georgi}(2007{\natexlab{b}})}]{Georgi2007}%
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Georgi}},\ }\bibfield  {title} {\bibinfo {title} {Another odd thing about
-  unparticle physics},\ }\href
+  {Georgi}},\ }\href
   {https://doi.org/https://doi.org/10.1016/j.physletb.2007.05.037} {\bibfield
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-  {Phillips}},\ }\bibfield  {title} {\bibinfo {title} {Beyond particles:
-  Unparticles in strongly correlated electron matter},\ }in\ \href@noop {}
-  {\emph {\bibinfo {booktitle} {Quantum Criticality in Condensed Matter}}},\
-  \bibinfo {editor} {edited by\ \bibinfo {editor} {\bibfnamefont
-  {J.}~\bibnamefont {Jedrzejewski}}}\ (\bibinfo  {publisher} {World Scientific,
-  Singapore},\ \bibinfo {year} {2014})\ pp.\ \bibinfo {pages}
-  {133--158}\BibitemShut {NoStop}%
+  {Phillips}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {Quantum
+  Criticality in Condensed Matter}}},\ \bibinfo {editor} {edited by\ \bibinfo
+  {editor} {\bibfnamefont {J.}~\bibnamefont {Jedrzejewski}}}\ (\bibinfo
+  {publisher} {World Scientific, Singapore},\ \bibinfo {year} {2014})\ pp.\
+  \bibinfo {pages} {133--158}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Zaanen}(2019)}]{zaanen2019}%
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Zaanen}},\ }\bibfield  {title} {\bibinfo {title} {Planckian dissipation,
-  minimal viscosity and the transport in cuprate strange metals},\ }\href
-  {https://doi.org/10.21468/SciPostPhys.6.5.061} {\bibfield  {journal}
-  {\bibinfo  {journal} {SciPost Phys.}\ }\textbf {\bibinfo {volume} {6}},\
-  \bibinfo {pages} {061} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+  {Zaanen}},\ }\href {https://doi.org/10.21468/SciPostPhys.6.5.061} {\bibfield
+  {journal} {\bibinfo  {journal} {SciPost Phys.}\ }\textbf {\bibinfo {volume}
+  {6}},\ \bibinfo {pages} {061} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Legros}\ \emph {et~al.}(2019)\citenamefont {Legros},
@@
   {H.}~\bibnamefont {Raffy}}, \bibinfo {author} {\bibfnamefont
-  {Z.}~\bibnamefont {Li}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
-  {title} {Universal $ t $-linear resistivity and planckian dissipation in
-  overdoped cuprates},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {15}},\ \bibinfo
-  {pages} {142} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hartnoll}\ and\ \citenamefont
-  {Mackenzie}(2022)}]{hartnoll2022}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
-  {Hartnoll}}\ and\ \bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont
-  {Mackenzie}},\ }\bibfield  {title} {\bibinfo {title} {Colloquium: Planckian
-  dissipation in metals},\ }\href
-  {https://doi.org/10.1103/RevModPhys.94.041002} {\bibfield  {journal}
-  {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {94}},\
-  \bibinfo {pages} {041002} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+  {Z.}~\bibnamefont {Li}}, \emph {et~al.},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
+  {15}},\ \bibinfo {pages} {142} (\bibinfo {year} {2019})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {McGreevy}(2023)}]{McGreevy2023}%
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {McGreevy}},\ }\bibfield  {title} {\bibinfo {title} {Generalized symmetries
-  in condensed matter},\ }\href
+  {McGreevy}},\ }\href
   {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-040721-021029}
@@
   {Luttinger}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
-  {Ward}},\ }\bibfield  {title} {\bibinfo {title} {Ground-state energy of a
-  many-fermion system. ii},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Physical Review}\ }\textbf {\bibinfo {volume} {118}},\ \bibinfo
-  {pages} {1417} (\bibinfo {year} {1960})}\BibitemShut {NoStop}%
+  {Ward}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical
+  Review}\ }\textbf {\bibinfo {volume} {118}},\ \bibinfo {pages} {1417}
+  (\bibinfo {year} {1960})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Su}\ and\ \citenamefont
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont
-  {Adler}},\ }\bibfield  {title} {\bibinfo {title} {Axial-vector vertex in
-  spinor electrodynamics},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Physical Review}\ }\textbf {\bibinfo {volume} {177}},\ \bibinfo
-  {pages} {2426} (\bibinfo {year} {1969})}\BibitemShut {NoStop}%
+  {Adler}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Physical Review}\ }\textbf {\bibinfo {volume} {177}},\ \bibinfo {pages}
+  {2426} (\bibinfo {year} {1969})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Bell}\ and\ \citenamefont
@@
   {Bell}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Jackiw}},\
-  }\bibfield  {title} {\bibinfo {title} {A pcac puzzle: $\pi$0→
-  $\gamma$$\gamma$ in the $\sigma$-model},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Il Nuovo Cimento A}\ }\textbf {\bibinfo
-  {volume} {60}},\ \bibinfo {pages} {47} (\bibinfo {year} {1969})}\BibitemShut
-  {NoStop}%
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Il Nuovo Cimento
+  A}\ }\textbf {\bibinfo {volume} {60}},\ \bibinfo {pages} {47} (\bibinfo
+  {year} {1969})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Casini}\ and\ \citenamefont
@@
   {Casini}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-  {Mag\'{a}n}},\ }\bibfield  {title} {\bibinfo {title} {On completeness and
-  generalized symmetries in quantum field theory},\ }\href
-  {https://doi.org/10.1142/S0217732321300251} {\bibfield  {journal} {\bibinfo
-  {journal} {Modern Physics Letters A}\ }\textbf {\bibinfo {volume} {36}},\
-  \bibinfo {pages} {2130025} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+  {Mag\'{a}n}},\ }\href {https://doi.org/10.1142/S0217732321300251} {\bibfield
+  {journal} {\bibinfo  {journal} {Modern Physics Letters A}\ }\textbf {\bibinfo
+  {volume} {36}},\ \bibinfo {pages} {2130025} (\bibinfo {year}
+  {2021})}\BibitemShut {NoStop}%
 \end{thebibliography}
 
+%\bibliography{tilingProject}
+
 \vspace{0.25cm}
-\par\noindent\textbf{Acknowledgements.}
+\par\noindent\textbf{Acknowledgments.}
 We acknowledge National Supercomputing Mission (NSM) for providing computing resources of ‘PARAM RUDRA’ at Aruna Asaf Ali Marg, near Vasant Kunj, New Delhi, Delhi 110067, which is implemented by C-DAC and supported by the Ministry of Electronics and Information Technology (MeitY) and Department of Science and Technology (DST), Government of India.
-SL thanks Mayank Shreshtha for designing Fig.1.
-
-\vspace{0.25cm}
-\par\noindent\textbf{Funding.}
 SL thanks the SERB, Govt.
@@
 \par\noindent\textbf{Author Contributions.}
-AM, SRH and SL conceived and designed the research.
-AM performed the calculations and analysis with support from all authors.
-AM, SRH, AM, NSV, AT and SL wrote the manuscript.
-All work was supervised by SL.
+A.M., S.R.H.
+and S.L.
+conceived and designed the research.
+A.M.
+performed the calculations and analysis with support from all authors.
+A.M., S.R.H., A.M.
+and S.L.
+wrote the manuscript with inputs from all authors.
+All work was supervised by S.L.
 
 \vspace{0.25cm}
-\par\noindent\textbf{Code Availability.}
-The underlying code for this study is not publicly available but may be made available to qualified researchers on reasonable request from the corresponding author.
-
-\vspace{0.25cm}
-\par\noindent\textbf{Competing Interest.}
-The authors declare no competing interests.
+\par\noindent\textbf{Code Availability}
+The codes created and datasets generated during this research are available from the corresponding author upon reasonable request.
 

### 2025-12-10 submissions/manuscript_Final.tex
started creating referee response

--- 2025-12-10 submissions/Upload_NatureComm/manuscript_Final.tex
@@
-\documentclass[%
- reprint,
-superscriptaddress,
-groupedaddress,
-%unsortedaddress,
-%runinaddress,
-%frontmatterverbose, 
-%preprint,
-%preprintnumbers,
-%nofootinbib,
-%nobibnotes,
-%bibnotes,
-aps,superscriptaddress,
-pra,
-%rmp,
-%prstab,
-%prstper,
-%floatfix,
-]{revtex4-2}
-% ,bm,color,hyperref
-\usepackage{graphicx,braket,color,bm,amsmath,amssymb,natbib}
-% \graphicspath{{./figures/}}
-%\bibliographystyle{apsrev4-2}
-
-\begin{document}
-
-\title{Mott Criticality as the Confinement Transition of a Pseudogap-Mott Metal}
-
-\author{Abhirup Mukherjee}
-\email{am18ip014@iiserkol.ac.in}
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
-}
-\author{S. R. Hassan}
-\email{shassan@imsc.res.in}
-\affiliation{The Institute of Mathematical Sciences, HBNI, C.I.T. Campus, Chennai 600 113, India}
-\author{Anamitra Mukherjee}
-\email{anamitra@niser.ac.in}
-\affiliation{School of Physical Sciences, National Institute of Science, Education and Research, HBNI, Jatni 752050, India}
-\author{N. S. Vidhyadhiraja}
-\email{raja@jncasr.ac.in}
-\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
-\author{A. Taraphder}
-\email{arghya@phy.iitkgp.ac.in}
-\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
-\author{Siddhartha Lal}
-\email{slal@iiserkol.ac.in}
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
-}
-
-\date{\today}
-
-\begin{abstract}
-\noindent
-A key challenge in quantum matter involves understanding how strong electronic repulsion obtains the breakdown of quasiparticle excitations in a Fermi liquid and the transition into Mott insulation.
-The difficulty lies in assessing the role of Luttinger surfaces, zeros of the single-particle Greens function that replace the poles lying on the Fermi surface.
-Luttinger surfaces are observed to proliferate in the pseudogap regime of Mott systems, resulting in Fermi arcs whose gapless excitations remain unknown.
-Here, we develop a renormalization-based construction of strongly correlated lattice models that captures the emergence of the pseudogap phase and its transition to a Mott insulator.
-Applying a many-body tiling scheme to the fixed-point impurity model uncovers a lattice model with electron interactions and Kondo physics.
-At half-filling, the interplay between Kondo screening and bath charge fluctuations in the impurity model leads to Fermi liquid breakdown.
-This reveals a pseudogap phase characterized by a non-Fermi liquid (the Mott metal) residing on nodal arcs, gapped antinodal regions of the Fermi surface, and an anomalous scaling of the electronic scattering rate with frequency.
-The eventual confinement of holon–doublon excitations of this exotic metal obtains a continuous transition into the Mott insulator.
-Our results identify the pseudogap as a distinct long-range entangled quantum phase, and offer a new route to Mott criticality beyond the paradigm of local quantum criticality.
-
-\end{abstract}
-
-\maketitle
-\par\noindent\textbf{\large Introduction}\\
-\noindent
-The Landau quasiparticle paradigm~\cite{landau1959theory} underpins our understanding of metallic behaviour, where the screening of long-ranged repulsive interactions between delocalised electrons leads to well-defined excitations that carry the same quantum numbers as free electrons.
-This remarkable phenomenon - known as adiabatic continuity -  is captured by excitations described by poles of the single-particle Greens function of the interacting system.
-But what defines metallicity when quasiparticles are no longer well-defined~\cite{Phillips2013Unparticles}?
-Can a surface of zeros of the Greens function~\cite{dzyaloshinskii2003some}, rather than poles forming a Fermi surface, define an entirely new kind of metal?
-Could such an exotic state serve as the precursor to Mott localisation driven purely by repulsion, and without invoking magnetic order~\cite{Mott_1949}?
-These questions necessitate a radical departure in understanding conduction in correlated electron systems beyond the quasiparticle paradigm~\cite{phillips2022}.
-\\
-
-\noindent
-The anomalous pseudogap (PG) phase, observed in the cuprates, exhibits nodal-antinodal dichotomy with spectral weight concentrated on Fermi arcs around the nodal regions~\cite{loeserKapitulnik1996, Norman1998, Hashimoto2014}.
-In the PG phase of such Mott systems
-~\cite{taillefer2010,FradkinRevModPhys2015,Sato2017,DoironLeyraud2017,Mukhopadhyay2019,Naman2021,Masafumi2025,KyungKotliar2006,MacridinAzevedo2006,sakai2009evolution,werner2009momentum,sakai2010doped,lin2010,gull2010momentum,gull2012,Mirzaei2013,gull2013,anirbanmott2,HilleAndergassen2020,Jiang2022,Scheurer2018,Krien2022,Kitatani2023,Sorella2023,Schafer2021,White1998,Ido2018,ProustTaillefer2019,Ponsioen2019,XuZhang2022}, the single-particle Green’s function develops surfaces of zeros, also known as Luttinger surfaces~\cite{Phillips2013,dzyaloshinskii2003some}, that signals a fundamental obstruction to quasiparticle formation.
-As interaction strength increases, these zero surfaces proliferate, fragmenting the Fermi surface into nodal arcs~\cite{sakai2009evolution,Phillips2013}, violating the Luttinger sum rule by reconfiguring Fermi volume~\cite{seki2017topological}, and breaking an emergent $\mathbb{Z}_2$ symmetry associated with the conservation of spin currents in Fermi liquids~\cite{Anderson2001,Huang2022}.
-Unlike conventional instabilities driven by poles, this phenomenon marks a topological breakdown of Fermi liquid theory~\cite{Coleman_2001,Phillips2013Unparticles}.
-We show that this breakdown arises from a strongly entangled, scale-invariant state of quantum matter, one that serves as the parent metal to the Mott insulator in a half-filled lattice model of strongly correlated electrons.
-This offers a concrete, controlled framework to understand both the non-quasiparticle character of the pseudogap phase and its continuous evolution into a repulsion-driven insulator, in full alignment with Mott's original vision~\cite{Mott_1949}.\\
-
-\begin{figure*}[tbh]
-    \centering
-    \includegraphics[width=\linewidth]{Figure1_Nature.pdf}
-    \caption{Schematic representation of (a): flowchart of theoretical framework adopted by us (see main text for explanation of symbols), (b): phases obtained for the extended Hubbard model in two dimensions at $T=0$, and passage between them.}
-    \label{schematic}
-\end{figure*}
-
-\noindent
-Our approach involves developing a renormalization group (RG)-based impurity-to-lattice framework that reconstructs the low-energy physics of a strongly correlated system from the fixed-point structure of a quantum impurity model (Fig.~\ref{schematic}, left).
-Starting from a dynamical Anderson impurity embedded in a correlated bath, we solve the system using a unitary RG (URG) approach~\cite{anirbanurg1,anirbanurg2}.
-We then construct a translation-invariant lattice Hamiltonian through a many-body tiling procedure that preserves non-local correlations and inherits momentum-resolved self-energies and renormalized couplings from the impurity solution.
-The resulting model is an \textit{extended}-Hubbard Hamiltonian on a two-dimensional square lattice at half-filling, with both on-site repulsion and nearest-neighbour spin exchange interactions.
-These correlations, derived directly from the impurity dynamics, enable tracking the evolution from the FL to the Mott insulator (MI) via an intermediate PG phase.\\
-
-\noindent
-A central insight of our work is that the PG phase hosts a NFL state governed by Kondo frustration and doublon–holon deconfinement~\cite{keimer2015quantum} (Fig.~\ref{schematic}, right).
-A correlation scale ($W$) in the conduction bath suppresses Kondo screening (with coupling $J$) beyond a critical ratio of $W/J$, triggering the emergence of Luttinger surfaces in the lattice model.
-This breakdown of quasiparticles begins at the antinodes and progressively engulfs the nodal regions, driving a continuous transformation into the MI.
-The resulting NFL exhibits a pseudogapped density of states, multipartite long-range entanglement, and a universal scattering rate of the form $\sim (a + b\,\omega^2)^{-1}$ that grows as $\omega \to 0$.
-At the critical endpoint of this phase, the URG flow identifies a singular NFL described by the Hatsugai–Kohmoto (HK) model~\cite{Hatsugai1992,Baskaran1991,Huang2022}, with fully deconfined holon–doublon excitations.
-
-\noindent
-The emergence of Luttinger surfaces alters the anomaly structure associated with the generalized symmetry of the FS~\cite{Altshuler_1998,Heath_2020,lanave2025}.
-The corresponding topological charge is defined via the Luttinger–Ward functional.
-This charge is modified by Green’s function zeros, signalling a shift in the underlying anomaly.
-Within our framework, this reorganization grants topological protection to the RG flows terminating in the PG regime, ensuring the stability of its NFL excitations.
-These are adiabatically connected to the Hatsugai–Kohmoto model~\cite{Hatsugai1992,Baskaran1991}, reinforcing the interpretation of the PG as a distinct quantum phase.
-We thus identify the NFL state as a new gapless, long-range entangled phase of correlated matter - the \textit{Mott metal} - whose deconfined holon-doublon excitations are eventually confined across the Mott transition~\cite{Mott_1949}.
-
-\noindent
-While we demonstrate our approach for an extended Hubbard model, it applies broadly to correlated quantum systems.
-The impurity-plus-tiling construction accommodates multi-orbital degrees of freedom, frustrated geometries, and nontrivial band topology.
-By deriving lattice Hamiltonians directly from renormalized local dynamics - without relying on mean-field approximations - this method preserves nonlocal correlations and enhances momentum-space resolution.
-It thus provides a versatile and controlled route for engineering strongly correlated models, particularly in regimes where PG formation, NFL scaling, and Mott physics intersect.
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth, height=10cm]{fig2.png}
-    \caption{(a): Phase diagram of impurity model at strong coupling in $U$ in terms of competing dimensionless Kondo ($J/t$) and bath correlation ($W/t$) couplings.
-Colourbar represents the fraction of states on the Fermi surface replaced by zeros of the Greens function (Luttinger surface).
-A pseudogap phase (shaded region) is observed between the local Fermi liquid (red region) and local moment (blue region) phases (b): $k$-space-resolved spin-spin correlation $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$ in the pseudogap phase of the impurity model.
-Antinodal regions are observed to decouple from Kondo screening of the impurity.
-(c): Upon tiling, this leads to a
-    $k$-space-resolved antinodal gap in the electronic density of states of the lattice model, corresponding to Luttinger surfaces of zeros.
-(d)-(f): Initiation of the decoupling of $J_{{\bf k}, {\bf k'}}$ (positive, negative and zeros shown in red, blue and white respectively), with ${\bf k}$ (black circle) at low-energies for ${\bf k}$ corresponding to the node, antinode and a point mid-way between them on the top right arm of the FS respectively with tuning $W/J$.
-As dictated by the symmetry of $J_{{\bf k}, {\bf k'}}$, the decoupling for a given ${\bf k}$ proceeds via the appearance of zeros (white patches) of $J_{{\bf k}, {\bf k'}}$ for ${\bf k'}$ initially on the nodal regions of adjacent arms, and progresses gradually towards the antinodes.
-The decoupling ends with the onset of the pseudogap.}
-    \label{spinCorr}
-\end{figure*}
-
-\vspace{0.25cm}
-
-\begin{figure*}[tbh]
-    \centering
-    \includegraphics[width=\textwidth]{fig3.pdf}
-    \caption{(a): Enhanced charge correlations $\chi_c({\bf k}_1, {\bf k}_2) = \braket{c^\dagger_{{\bf k}_1\uparrow}c^\dagger_{{\bf k}_1\downarrow}c_{{\bf k}_2\downarrow}c_{{\bf k}_2\uparrow} + \text{h.c.}}$ between the nodal and antinodal regions, signalling Kondo breakdown in the pseudogap phase of the impurity model.
-(b): In turn, the breakdown leads to the gapping of the antinodal regions in the lattice model, seen from the appearance of poles in the imaginary part of the self-energy.
-(c): The imaginary part of the impurity self-energy $\Sigma^{\prime\prime}(\omega >0)$ possesses a pole at non-zero $\omega$ in the PG that moves towards $\omega=0$ as the Mott transition is approached.}
-    \label{chargeCorr}
-\end{figure*}
-
-\vspace{0.25cm}
-\par\noindent\textbf{\large Tiling Reconstruction of Lattice Model}\\ 
-To capture the interplay between Kondo physics and Mott localization, our approach relies on a two-dimensional auxiliary model inspired by insights on the impurity model~\cite{Mukherjee_2023} at the heart of dynamical mean-field theory (DMFT) ~\cite{georges1996} and its extensions ~ \cite{hettler1998,kotliar2001,maier2005}.
-The model (see Methods for details) consists of a correlated impurity site (with a double occupancy cost $U$) embedded within a correlated conduction bath defined on a square lattice (see Fig.~\ref{schematic}(a)).
-The impurity site hybridises with the conduction bath sites adjacent to it through one-particle hybridisation $V$ as well as a spin-exchange interaction $J$ arising from fluctuations in local spin densities of the electrons.
-The conduction bath has minimal correlations in the form of a local correlation term $W$ on the sites that are adjacent to the impurity.
-Crucially, the Kondo coupling acquires a momentum structure upon Fourier transforming:
-\begin{equation}
-J_{{\bf k}, {\bf k}^\prime} = \frac{J}{2} \left[ \cos(k_x - k^\prime_x) + \cos(k_y - k^\prime_y) \right],
-\end{equation}
-which respects the $C_4$ symmetry of the square lattice.
-
-\noindent
-To reconstruct a translationally invariant lattice Hamiltonian from the impurity model (with Hamiltonian $\mathcal{H}_\text{aux}$), we define a many-body tiling prescription that embeds the auxiliary impurity system uniformly across the two-dimensional square lattice.
-Thus,  the tiling process systematically derives the full lattice dynamics from the renormalized fixed-point structure of the impurity.
-Let ${\bf r}_d$ denote the location of the impurity within a single unit cell.
-We define the full Hamiltonian by translating this unit cell across all sites of the lattice:
-\begin{equation}
-\mathcal{H}_\text{tiled} = \sum_{{\bf r}} T^\dagger({\bf r}) \, \mathcal{H}_\text{aux}({\bf r}_d) \, T({\bf r}) - N \mathcal{H}_\text{cbath},
-\end{equation}
-where $T({\bf r})$ denotes the operator that translates all degrees of freedom by vector ${\bf r}$, and $N$ is the number of lattice sites.
-Subtracting $N \mathcal{H}_\text{cbath}$ ensures proper normalization and avoids double-counting of bath terms.
-
-\noindent
-This procedure yields an effective \textit{extended}-Hubbard model that retains local and nonlocal correlation effects from the original impurity. The resulting Hamiltonian reads:
-\begin{equation}
-\label{eq:effectiveH}
-\begin{aligned}
-\hspace*{-0.3cm}\mathcal{H}_\text{tiled} =
-&- \frac{\tilde{t}}{\sqrt{\mathcal{Z}}} \sum_{\langle {\bf r}_i, {\bf r}_j \rangle, \sigma} \left( c^\dagger_{{\bf r}_i,\sigma} c_{{\bf r}_j,\sigma} + \text{h.c.} \right) \\
-%- \tilde{\mu} \sum_{{\bf r},\sigma} \hat{n}_{{\bf r},\sigma} \\
-&+ \frac{\tilde{J}}{\mathcal{Z}} \sum_{\langle {\bf r}_i, {\bf r}_j \rangle} {\bf S}_{{\bf r}_i} \cdot {\bf S}_{{\bf r}_j}
-- \frac{\tilde{U}}{2} \sum_{{\bf r}} \left( \hat{n}_{{\bf r}, \uparrow} - \hat{n}_{{\bf r}, \downarrow} \right)^2,
-\end{aligned}
-\end{equation}
-where $\mathcal{Z} = 4$ is the coordination number of the square lattice. The parameters $(\tilde{t}, %\tilde{\mu}, 
-\tilde{J}, \tilde{U})$ are renormalized couplings inherited from the impurity solution: $\tilde{t} = t + 2V,\quad \tilde{U} = U + W,
-%\quad \tilde{\mu} = 2\mu + \eta,
-\quad \tilde{J} = 2J$.
-A non-zero chemical potential in the bath and/or the impurity can be included to study the effects of doping.
-Crucially, the eigenstates of $\mathcal{H}_\text{tiled}$ obey a many-body generalization of Bloch’s theorem~\cite{stoyanova} (see Sec.1 of Supplementary Information~\cite{suppmat}), which allows for the exact computation of momentum-resolved observables (presented here for a $77\times 77$ {\bf k}-space Brillouin zone grid).
-This lattice embedding provides a controlled route to capture low-energy NFL behavior and Mott criticality directly from a quantum impurity model.
-
-\vspace{0.25cm}
-\par\noindent\textbf{\large  Pseudogap Formation via Kondo Breakdown}\\
-A detailed picture of the PG in the impurity model is obtained from a momentum-resolved breakdown of Kondo screening in the strong-coupling regime $U \gg t$ phase of $H_\text{aux}$.
-A unitary renormalisation group (URG) scaling analysis~\cite{anirbanurg1} obtains a flow equation of the Kondo coupling \(J^{(j)}_{{\bf k}_1, {\bf k}_2}\) (see Sec.2 of~\cite{suppmat})
-\begin{equation}\begin{aligned}\label{KondoRGequation}
-	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}~,
-\end{aligned}\end{equation}
-where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, the sum is over all occupied momentum states \({\bf q}\) of the energy shell \(\varepsilon_j\), and  \({\bf \bar q} = {\bf q} + {\boldsymbol \pi}\) is the particle-hole transformed partner.
-The bath interaction coupling $W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}$ is found to be marginal under these transformations.
-While we present a detailed numerical evaluation of the RG equation for $J_{{\bf k}_1, {\bf k}_2}$ (eq.\eqref{KondoRGequation}) below, it is clear that the frustration of Kondo screening due to charge fluctuations (for attractive bath interactions $W<0$) leads to the Mott transition~\cite{Mukherjee_2023}.\\
-
-\noindent
-Upon tuning the ratio of the bath and Kondo interactions ($W/J$) from zero to negative values (see phase diagram in Fig.~\ref{spinCorr}(a)), the following phases emerge in the impurity model from the competition between $J$ and $W$ in eq.~\eqref{KondoRGequation}: (i) for $W/J<(W/J)_{\text{PG}}$, an LFL phase (red region), where the entire FS participates in Kondo screening, (ii) for $\frac{W}{J} \in [(\frac{W}{J})_{\text{PG}}, (\frac{W}{J})_c]$ (shaded region), a local PG phase where disconnected parts of the FS around the node participate in Kondo screening, and (iii) a local moment phase for $\frac{W}{J} > (\frac{W}{J})_c$ (blue region), where the impurity remains unscreened at low-energies.
-These can be visualised from spin correlations, $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$~, as shown in Fig.~\ref{spinCorr}(b) for the PG.
-The values $(W/J)_{\text{PG}}$ and $(W/J)_c$ are therefore the entry into and exit from the PG phase.
-Mapping onto the lattice model via tiling (see Sec.3 of \cite{suppmat}), we observe that RG-induced nodal–antinodal dichotomy in $J_{{\bf k}, {\bf k}^\prime}$ in the impurity model is the microscopic origin of the PG in the lattice model: the extinction of Kondo coherence translates into spectral zeros in the lattice Green’s function (i.e., Luttinger surfaces) at antinodal momenta (Fig.~\ref{spinCorr}(c)).
-This establishes that the $T=0$ Mott transition of the 2D \textit{extended}-Hubbard model proceeds from FL to MI through an intervening PG phase.
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{fig4.pdf}
-    \caption{(a): Suppression of quasiparticle residue ($Z_\text{imp}$) as the impurity model is tuned towards the Mott transition.
-An initial drastic fall in $Z_\text{imp}$ is observed for $W/J \lesssim (W/J)_\text{PG}$ from $0.3$ to around $0.05$, signalling the destruction of the FL with unravelling of Kondo screening.
-A steady decrease in $Z_{imp}$ is observed in passage through the PG, and is vanishingly small close to the Mott transition due to a divergent self-energy.
-(b): Growth of unscreened impurity magnetic moment in the pseudogap phase, signalling the breakdown of Kondo screening.
-(c): The central (Kondo) resonance of the impurity spectral function in the Fermi liquid phase splits into a pseudogap in the PG phase, with its height diminishing rapidly as the Mott transition is approached.
-    }
-    \label{channelDecoupling}
-\end{figure*}
-\vspace{0.25cm}
-\par\noindent\textbf{\large Unravelling of Kondo Screening}\\
-The ${\bf k}$-space anisotropy of Kondo breakdown can be visualized in terms of zeros of $J_{{\bf k}_N, {\bf k}}$, involving spin-flip scattering between the node ${\bf k}_N = (\pi/2, \pi/2)$  and a general wavevector ${\bf k}$.
-For any $W/J$, the $\mathcal{C}_{4}$ lattice symmetry dictates that $J_{{\bf k}_N, {\bf k}}$ vanishes if ${\bf k}$ belongs to any of the antinodes or adjacent nodes.
-Tuning $W/J$ towards $(W/J)_{\text{PG}}$ leads to an unravelling of the Kondo screening: $J_{{\bf k}_N, {\bf k}}$ for ${\bf k}$ close to the adjacent nodes turns RG-irrelevant first, and a patch of zeros subsequently appears in $J_{{\bf k}_N, {\bf k}}$ around this point (Fig.~\ref{spinCorr} (d)).
-Tuning $W/J$ further extends the patch of zeros towards the antinodes (Fig.~\ref{spinCorr} (e) and (f)).
-Kondo screening thus unravels by a systematic decoupling of all $J_{{\bf k}_1, {\bf k}_2}$ that connect adjacent quadrants of the Brillouin zone.
 Precisely at $W/J=(W/J)_{\text{PG}}$, the antinode joins this connected region of zeros in $J_{{\bf k}_1, {\bf k}_2}$, marking the decoupling of the antinodes from all other points in the neighbourhood of the FS.
@@
 Importantly, it coincides with an emergent two-channel Kondo (2CK) impurity model, where each channel corresponds to a pair of Fermi arcs on opposite faces of the conduction bath FS.
-The 2CK nature of the PG is guaranteed by the symmetry of $J_{{\bf k},{\bf k'}}$: $J_{{\bf k},{\bf k'}}= -J_{{\bf k}+{\bf Q},{\bf k'}}=-J_{{\bf k},{\bf k'}+{\bf Q}}$, where ${\bf Q} = (\pi,\pi)$.
-The PG expands by shrinking these disconnected Fermi arcs towards the respective nodes, leading to nodal metals whose disappearance heralds the Mott transition.
+The 2CK nature of the PG is guaranteed by the symmetry of $J_{{\bf k},{\bf k'}}$:
 
@@
 
-\noindent
 Thus, the drastic change in nature of the real-space excitations - from locally well-defined Landau quasiparticles of the FL to the increasingly nonlocal excitations of the NFL Fermi arcs in the PG phase - appears to be dictated by a topological principle and, therefore, robust under renormalisation.
 This signals the NFL Fermi arcs of the PG as an emergent phase of strongly interacting quantum matter - which we dub the {\it Mott metal} - that is the parent metal of the MI.
-The same topological principle connects the nonlocal unparticle-like gapless excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} of the scale-invariant nodal NFL of the HK model observed precisely at the Mott critical point to those of the rest of PG phase, e.g., a universal scaling of $\Sigma''_{{\bf k}}(\omega)\sim (a+b\omega^{2})^{-1}$ of the NFL throughout the PG phase (Fig.~\ref{selfEnergy} (a)) and whose $\omega=0$ value continues to grow upon violating the MIR bound.
-\vspace{0.25cm}
-\par\noindent\textbf{\large Conclusions}\\
+The same topological principle connects the nonlocal unparticle-like gapless excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} of the scale-invariant nodal NFL of the HK model observed precisely at the Mott critical point to those of the rest of
+PG phase, e.g., a universal scaling of $\Sigma''_{{\bf k}}(\omega)\sim (a+b\omega^{2})^{-1}$ of the NFL throughout the PG phase (Fig.~\ref{selfEnergy} (a)) and whose $\omega=0$ value continues to grow upon violating the MIR bound.
+
+\section{Conclusions}
 Our analysis reveals that the Mott transition proceeds via a continuous evolution through a PG regime characterized by a singular NFL metal - the Mott metal - with deconfined holon–doublon excitations confined to nodal Fermi arcs.
@@
 Its fate under finite doping presents a compelling direction for future investigation.
-
-\begin{thebibliography}{99}
-\makeatletter
-\providecommand \@ifxundefined [1]{%
- \@ifx{#1\undefined}
-}%
-\providecommand \@ifnum [1]{%
- \ifnum #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \@ifx [1]{%
- \ifx #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \natexlab [1]{#1}%
-\providecommand \enquote  [1]{``#1''}%
-\providecommand \bibnamefont  [1]{#1}%
-\providecommand \bibfnamefont [1]{#1}%
-\providecommand \citenamefont [1]{#1}%
-\providecommand \href@noop [0]{\@secondoftwo}%
-\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
-\providecommand \@href[1]{\@@startlink{#1}\@@href}%
-\providecommand \@@href[1]{\endgroup#1\@@endlink}%
-\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
-  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
-\providecommand \@@startlink[1]{}%
-\providecommand \@@endlink[0]{}%
-\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
-\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
-\providecommand \urlprefix  [0]{URL }%
-\providecommand \Eprint [0]{\href }%
-\providecommand \doibase [0]{https://doi.org/}%
-\providecommand \selectlanguage [0]{\@gobble}%
-\providecommand \bibinfo  [0]{\@secondoftwo}%
-\providecommand \bibfield  [0]{\@secondoftwo}%
-\providecommand \translation [1]{[#1]}%
-\providecommand \BibitemOpen [0]{}%
-\providecommand \bibitemStop [0]{}%
-\providecommand \bibitemNoStop [0]{.\EOS\space}%
-\providecommand \EOS [0]{\spacefactor3000\relax}%
-\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
-\let\auto@bib@innerbib\@empty
-%</preamble>
-
-\bibitem [{\citenamefont {Landau}(1957)}]{landau1959theory}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Landau}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Soviet
-  Physics Jetp-Ussr}\ }\textbf {\bibinfo {volume} {3}},\ \bibinfo {pages} {920}
-  (\bibinfo {year} {1957})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2013)\citenamefont
-  {Phillips}, \citenamefont {Langley},\ and\ \citenamefont
-  {Hutasoit}}]{Phillips2013Unparticles}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-  {Phillips}}, \bibinfo {author} {\bibfnamefont {B.~W.}\ \bibnamefont
-  {Langley}},\ and\ \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont
-  {Hutasoit}},\ }\href {https://doi.org/10.1103/PhysRevB.88.115129} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-  {88}},\ \bibinfo {pages} {115129} (\bibinfo {year} {2013})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Dzyaloshinskii}(2003)}]{dzyaloshinskii2003some}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
-  {Dzyaloshinskii}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Physical Review B}\ }\textbf {\bibinfo {volume} {68}},\ \bibinfo {pages}
-  {085113} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mott}(1949)}]{Mott_1949}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~F.}\ \bibnamefont
-  {Mott}},\ }\href {https://doi.org/10.1088/0370-1298/62/7/303} {\bibfield
-  {journal} {\bibinfo  {journal} {Proceedings of the Physical Society. Section
-  A}\ }\textbf {\bibinfo {volume} {62}},\ \bibinfo {pages} {416} (\bibinfo
-  {year} {1949})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2022)\citenamefont
-  {Phillips}, \citenamefont {Hussey},\ and\ \citenamefont
-  {Abbamonte}}]{phillips2022}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-  {Phillips}}, \bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
-  {Hussey}},\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Abbamonte}},\ }\href {https://doi.org/10.1126/science.abh4273} {\bibfield
-  {journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
-  {377}},\ \bibinfo {pages} {eabh4273} (\bibinfo {year} {2022})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Loeser}\ \emph {et~al.}(1996)\citenamefont {Loeser},
-  \citenamefont {Shen}, \citenamefont {Dessau}, \citenamefont {Marshall},
-  \citenamefont {Park}, \citenamefont {Fournier},\ and\ \citenamefont
-  {Kapitulnik}}]{loeserKapitulnik1996}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~G.}\ \bibnamefont
-  {Loeser}}, \bibinfo {author} {\bibfnamefont {Z.-X.}\ \bibnamefont {Shen}},
-  \bibinfo {author} {\bibfnamefont {D.~S.}\ \bibnamefont {Dessau}}, \bibinfo
-  {author} {\bibfnamefont {D.~S.}\ \bibnamefont {Marshall}}, \bibinfo {author}
-  {\bibfnamefont {C.~H.}\ \bibnamefont {Park}}, \bibinfo {author}
-  {\bibfnamefont {P.}~\bibnamefont {Fournier}},\ and\ \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Kapitulnik}},\ }\href
-  {https://doi.org/10.1126/science.273.5273.325} {\bibfield  {journal}
-  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {273}},\ \bibinfo
-  {pages} {325} (\bibinfo {year} {1996})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Norman}\ \emph {et~al.}(1998)\citenamefont {Norman},
-  \citenamefont {Ding}, \citenamefont {Randeria}, \citenamefont {Campuzano},
-  \citenamefont {Yokoya}, \citenamefont {Takeuchi}, \citenamefont {Takahashi},
-  \citenamefont {Mochiku}, \citenamefont {Kadowaki}, \citenamefont
-  {Guptasarma},\ and\ \citenamefont {Hinks}}]{Norman1998}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
-  {Norman}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Ding}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Randeria}}, \bibinfo
-  {author} {\bibfnamefont {J.~C.}\ \bibnamefont {Campuzano}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Yokoya}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Takeuchi}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Takahashi}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Mochiku}}, \bibinfo {author} {\bibfnamefont
-  {K.}~\bibnamefont {Kadowaki}}, \bibinfo {author} {\bibfnamefont
-  {P.}~\bibnamefont {Guptasarma}},\ and\ \bibinfo {author} {\bibfnamefont
-  {D.~G.}\ \bibnamefont {Hinks}},\ }\href {https://doi.org/10.1038/32366}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
-  {volume} {392}},\ \bibinfo {pages} {157} (\bibinfo {year}
-  {1998})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hashimoto}\ \emph {et~al.}(2014)\citenamefont
-  {Hashimoto}, \citenamefont {Vishik}, \citenamefont {He}, \citenamefont
-  {Devereaux},\ and\ \citenamefont {Shen}}]{Hashimoto2014}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Hashimoto}}, \bibinfo {author} {\bibfnamefont {I.~M.}\ \bibnamefont
-  {Vishik}}, \bibinfo {author} {\bibfnamefont {R.-H.}\ \bibnamefont {He}},
-  \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont {Devereaux}},\ and\
-  \bibinfo {author} {\bibfnamefont {Z.-X.}\ \bibnamefont {Shen}},\ }\href
-  {https://doi.org/10.1038/nphys3009} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo
-  {pages} {483} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Taillefer}(2010)}]{taillefer2010}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Taillefer}},\ }\href
-  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-070909-104117}
-  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-  Physics}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo {pages} {51} (\bibinfo
-  {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Fradkin}\ \emph {et~al.}(2015)\citenamefont
-  {Fradkin}, \citenamefont {Kivelson},\ and\ \citenamefont
-  {Tranquada}}]{FradkinRevModPhys2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Fradkin}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
-  {Kivelson}},\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-  {Tranquada}},\ }\href {https://doi.org/10.1103/RevModPhys.87.457} {\bibfield
-  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume}
-  {87}},\ \bibinfo {pages} {457} (\bibinfo {year} {2015})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Sato}\ \emph {et~al.}(2017)\citenamefont {Sato},
-  \citenamefont {Kasahara}, \citenamefont {Murayama}, \citenamefont {Kasahara},
-  \citenamefont {Moon}, \citenamefont {Nishizaki}, \citenamefont {Loew},
-  \citenamefont {Porras}, \citenamefont {Keimer}, \citenamefont {Shibauchi},\
-  and\ \citenamefont {Matsuda}}]{Sato2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Sato}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Kasahara}},
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Murayama}}, \bibinfo
-  {author} {\bibfnamefont {Y.}~\bibnamefont {Kasahara}}, \bibinfo {author}
-  {\bibfnamefont {E.-G.}\ \bibnamefont {Moon}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Nishizaki}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Loew}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Porras}}, \bibinfo {author} {\bibfnamefont
-  {B.}~\bibnamefont {Keimer}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Shibauchi}},\ and\ \bibinfo {author} {\bibfnamefont
-  {Y.}~\bibnamefont {Matsuda}},\ }\href {https://doi.org/10.1038/nphys4205}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf
-  {\bibinfo {volume} {13}},\ \bibinfo {pages} {1074} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Doiron-Leyraud}\ \emph {et~al.}(2017)\citenamefont
-  {Doiron-Leyraud}, \citenamefont {Cyr-Choini{\`e}re}, \citenamefont {Badoux},
-  \citenamefont {Ataei}, \citenamefont {Collignon}, \citenamefont {Gourgout},
-  \citenamefont {Dufour-Beaus{\'e}jour}, \citenamefont {Tafti}, \citenamefont
-  {Lalibert{\'e}}, \citenamefont {Boulanger}, \citenamefont {Matusiak},
-  \citenamefont {Graf}, \citenamefont {Kim}, \citenamefont {Zhou},
-  \citenamefont {Momono}, \citenamefont {Kurosawa}, \citenamefont {Takagi},\
-  and\ \citenamefont {Taillefer}}]{DoironLeyraud2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Doiron-Leyraud}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
-  {Cyr-Choini{\`e}re}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Badoux}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Ataei}},
-  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Collignon}}, \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Gourgout}}, \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Dufour-Beaus{\'e}jour}}, \bibinfo {author}
-  {\bibfnamefont {F.~F.}\ \bibnamefont {Tafti}}, \bibinfo {author}
-  {\bibfnamefont {F.}~\bibnamefont {Lalibert{\'e}}}, \bibinfo {author}
-  {\bibfnamefont {M.-E.}\ \bibnamefont {Boulanger}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Matusiak}}, \bibinfo {author}
-  {\bibfnamefont {D.}~\bibnamefont {Graf}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont {J.-S.}\
-  \bibnamefont {Zhou}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Momono}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Kurosawa}},
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\ and\ \bibinfo
-  {author} {\bibfnamefont {L.}~\bibnamefont {Taillefer}},\ }\href
-  {https://doi.org/10.1038/s41467-017-02122-x} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Communications}\ }\textbf {\bibinfo {volume} {8}},\
-  \bibinfo {pages} {2044} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mukhopadhyay}\ \emph {et~al.}(2019)\citenamefont
-  {Mukhopadhyay}, \citenamefont {Sharma}, \citenamefont {Kim}, \citenamefont
-  {Edkins}, \citenamefont {Hamidian}, \citenamefont {Eisaki}, \citenamefont
-  {ichi Uchida}, \citenamefont {Kim}, \citenamefont {Lawler}, \citenamefont
-  {Mackenzie}, \citenamefont {Davis},\ and\ \citenamefont
-  {Fujita}}]{Mukhopadhyay2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Mukhopadhyay}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Sharma}}, \bibinfo {author} {\bibfnamefont {C.~K.}\ \bibnamefont {Kim}},
-  \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont {Edkins}}, \bibinfo
-  {author} {\bibfnamefont {M.~H.}\ \bibnamefont {Hamidian}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Eisaki}}, \bibinfo {author} {\bibfnamefont
-  {S.}~\bibnamefont {ichi Uchida}}, \bibinfo {author} {\bibfnamefont {E.-A.}\
-  \bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
-  {Lawler}}, \bibinfo {author} {\bibfnamefont {A.~P.}\ \bibnamefont
-  {Mackenzie}}, \bibinfo {author} {\bibfnamefont {J.~C.~S.}\ \bibnamefont
-  {Davis}},\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Fujita}},\ }\href {https://doi.org/10.1073/pnas.1821454116} {\bibfield
-  {journal} {\bibinfo  {journal} {Proceedings of the National Academy of
-  Sciences}\ }\textbf {\bibinfo {volume} {116}},\ \bibinfo {pages} {13249}
-  (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Gupta}\ \emph {et~al.}(2021)\citenamefont {Gupta},
-  \citenamefont {McMahon}, \citenamefont {Sutarto}, \citenamefont {Shi},
-  \citenamefont {Gong}, \citenamefont {Wei}, \citenamefont {Shen},
-  \citenamefont {He}, \citenamefont {Ma}, \citenamefont {Dragomir},
-  \citenamefont {Gaulin},\ and\ \citenamefont {Hawthorn}}]{Naman2021}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~K.}\ \bibnamefont
-  {Gupta}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {McMahon}},
-  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Sutarto}}, \bibinfo
-  {author} {\bibfnamefont {T.}~\bibnamefont {Shi}}, \bibinfo {author}
-  {\bibfnamefont {R.}~\bibnamefont {Gong}}, \bibinfo {author} {\bibfnamefont
-  {H.~I.}\ \bibnamefont {Wei}}, \bibinfo {author} {\bibfnamefont {K.~M.}\
-  \bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {He}}, \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Ma}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Dragomir}}, \bibinfo {author}
-  {\bibfnamefont {B.~D.}\ \bibnamefont {Gaulin}},\ and\ \bibinfo {author}
-  {\bibfnamefont {D.~G.}\ \bibnamefont {Hawthorn}},\ }\href
-  {https://doi.org/10.1073/pnas.2106881118} {\bibfield  {journal} {\bibinfo
-  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-  {\bibinfo {volume} {118}},\ \bibinfo {pages} {e2106881118} (\bibinfo {year}
-  {2021})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Horio}\ \emph {et~al.}(2025)\citenamefont {Horio},
-  \citenamefont {Sakai}, \citenamefont {Suzuki}, \citenamefont {Nonaka},
-  \citenamefont {Hashimoto}, \citenamefont {Lu}, \citenamefont {Shen},
-  \citenamefont {Ohgi}, \citenamefont {Konno}, \citenamefont {Adachi},
-  \citenamefont {Koike}, \citenamefont {Imada},\ and\ \citenamefont
-  {Fujimori}}]{Masafumi2025}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Horio}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Sakai}},
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Suzuki}}, \bibinfo
-  {author} {\bibfnamefont {Y.}~\bibnamefont {Nonaka}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Hashimoto}}, \bibinfo {author}
-  {\bibfnamefont {D.}~\bibnamefont {Lu}}, \bibinfo {author} {\bibfnamefont
-  {Z.-X.}\ \bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont
-  {T.}~\bibnamefont {Ohgi}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Konno}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Adachi}},
-  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Koike}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ and\ \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Fujimori}},\ }\href
-  {https://doi.org/10.1073/pnas.2406624122} {\bibfield  {journal} {\bibinfo
-  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-  {\bibinfo {volume} {122}},\ \bibinfo {pages} {e2406624122} (\bibinfo {year}
-  {2025})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kyung}\ \emph {et~al.}(2006)\citenamefont {Kyung},
-  \citenamefont {Kancharla}, \citenamefont {S\'en\'echal}, \citenamefont
-  {Tremblay}, \citenamefont {Civelli},\ and\ \citenamefont
-  {Kotliar}}]{KyungKotliar2006}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-  {Kyung}}, \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont
-  {Kancharla}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {S\'en\'echal}}, \bibinfo {author} {\bibfnamefont {A.-M.~S.}\ \bibnamefont
-  {Tremblay}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Civelli}},\
-  and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Kotliar}},\ }\href
-  {https://doi.org/10.1103/PhysRevB.73.165114} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo
-  {pages} {165114} (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Macridin}\ \emph {et~al.}(2006)\citenamefont
-  {Macridin}, \citenamefont {Jarrell}, \citenamefont {Maier}, \citenamefont
-  {Kent},\ and\ \citenamefont {D'Azevedo}}]{MacridinAzevedo2006}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Macridin}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Jarrell}},
-  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Maier}}, \bibinfo
-  {author} {\bibfnamefont {P.~R.~C.}\ \bibnamefont {Kent}},\ and\ \bibinfo
-  {author} {\bibfnamefont {E.}~\bibnamefont {D'Azevedo}},\ }\href
-  {https://doi.org/10.1103/PhysRevLett.97.036401} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {97}},\
-  \bibinfo {pages} {036401} (\bibinfo {year} {2006})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2009)\citenamefont {Sakai},
-  \citenamefont {Motome},\ and\ \citenamefont {Imada}}]{sakai2009evolution}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Sakai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Motome}},\ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Physical review letters}\
-  }\textbf {\bibinfo {volume} {102}},\ \bibinfo {pages} {056404} (\bibinfo
-  {year} {2009})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Werner}\ \emph {et~al.}(2009)\citenamefont {Werner},
-  \citenamefont {Gull}, \citenamefont {Parcollet},\ and\ \citenamefont
-  {Millis}}]{werner2009momentum}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Werner}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Gull}},
-  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}},\ and\
-  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
-  B}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo {pages} {045120} (\bibinfo
-  {year} {2009})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sakai}\ \emph {et~al.}(2010)\citenamefont {Sakai},
-  \citenamefont {Motome},\ and\ \citenamefont {Imada}}]{sakai2010doped}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Sakai}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Motome}},\ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Physical Review B}\ }\textbf
-  {\bibinfo {volume} {82}},\ \bibinfo {pages} {134505} (\bibinfo {year}
-  {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Lin}\ \emph {et~al.}(2010)\citenamefont {Lin},
-  \citenamefont {Gull},\ and\ \citenamefont {Millis}}]{lin2010}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Lin}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Gull}},\ and\
-  \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-  }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {045104} (\bibinfo
-  {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Gull}\ \emph {et~al.}(2010)\citenamefont {Gull},
-  \citenamefont {Ferrero}, \citenamefont {Parcollet}, \citenamefont {Georges},\
-  and\ \citenamefont {Millis}}]{gull2010momentum}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Gull}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ferrero}},
-  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}}, \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-  {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Physical Review B}\ }\textbf {\bibinfo
-  {volume} {82}},\ \bibinfo {pages} {155101} (\bibinfo {year}
-  {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Gull}\ and\ \citenamefont {Millis}(2012)}]{gull2012}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Gull}}\ and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
-  {Millis}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-  Rev. B}\ }\textbf {\bibinfo {volume} {86}},\ \bibinfo {pages} {241106}
-  (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mirzaei}\ \emph {et~al.}(2013)\citenamefont
-  {Mirzaei}, \citenamefont {Stricker}, \citenamefont {Hancock}, \citenamefont
-  {Berthod}, \citenamefont {Georges}, \citenamefont {van Heumen}, \citenamefont
-  {Chan}, \citenamefont {Zhao}, \citenamefont {Li}, \citenamefont {Greven},
-  \citenamefont {Barišić},\ and\ \citenamefont {van~der
-  Marel}}]{Mirzaei2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~I.}\ \bibnamefont
-  {Mirzaei}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Stricker}},
-  \bibinfo {author} {\bibfnamefont {J.~N.}\ \bibnamefont {Hancock}}, \bibinfo
-  {author} {\bibfnamefont {C.}~\bibnamefont {Berthod}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Georges}}, \bibinfo {author} {\bibfnamefont
-  {E.}~\bibnamefont {van Heumen}}, \bibinfo {author} {\bibfnamefont {M.~K.}\
-  \bibnamefont {Chan}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
-  {Zhao}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Li}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Greven}}, \bibinfo {author}
-  {\bibfnamefont {N.}~\bibnamefont {Barišić}},\ and\ \bibinfo {author}
-  {\bibfnamefont {D.}~\bibnamefont {van~der Marel}},\ }\href
-  {https://doi.org/10.1073/pnas.1218846110} {\bibfield  {journal} {\bibinfo
-  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-  {\bibinfo {volume} {110}},\ \bibinfo {pages} {5774} (\bibinfo {year}
-  {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Gull}\ \emph {et~al.}(2013)\citenamefont {Gull},
-  \citenamefont {Parcollet},\ and\ \citenamefont {Millis}}]{gull2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Gull}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Parcollet}},\
-  and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont {Millis}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical review
-  letters}\ }\textbf {\bibinfo {volume} {110}},\ \bibinfo {pages} {216405}
-  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
-  {Lal}(2020{\natexlab{a}})}]{anirbanmott2}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Lal}},\ }\href {https://doi.org/10.1088/1367-2630/ab890c} {\bibfield
-  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
-  {volume} {22}},\ \bibinfo {pages} {063008} (\bibinfo {year}
-  {2020}{\natexlab{a}})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hille}\ \emph {et~al.}(2020)\citenamefont {Hille},
-  \citenamefont {Rohe}, \citenamefont {Honerkamp},\ and\ \citenamefont
-  {Andergassen}}]{HilleAndergassen2020}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Hille}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Rohe}},
-  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Honerkamp}},\ and\
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Andergassen}},\ }\href
-  {https://doi.org/10.1103/PhysRevResearch.2.033068} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Res.}\ }\textbf {\bibinfo {volume} {2}},\
-  \bibinfo {pages} {033068} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Jiang}\ \emph {et~al.}(2022)\citenamefont {Jiang},
-  \citenamefont {Liu}, \citenamefont {Klein}, \citenamefont {Wang},
-  \citenamefont {Sun}, \citenamefont {Chubukov},\ and\ \citenamefont
-  {Meng}}]{Jiang2022}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
-  {Jiang}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Liu}}, \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Klein}}, \bibinfo {author}
-  {\bibfnamefont {Y.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont
-  {K.}~\bibnamefont {Sun}}, \bibinfo {author} {\bibfnamefont {A.~V.}\
-  \bibnamefont {Chubukov}},\ and\ \bibinfo {author} {\bibfnamefont {Z.~Y.}\
-  \bibnamefont {Meng}},\ }\href {https://doi.org/10.1038/s41467-022-30302-x}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nature Communications}\ }\textbf
-  {\bibinfo {volume} {13}},\ \bibinfo {pages} {2655} (\bibinfo {year}
-  {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Scheurer}\ \emph {et~al.}(2018)\citenamefont
-  {Scheurer}, \citenamefont {Chatterjee}, \citenamefont {Wu}, \citenamefont
-  {Ferrero}, \citenamefont {Georges},\ and\ \citenamefont
-  {Sachdev}}]{Scheurer2018}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont
-  {Scheurer}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Chatterjee}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Wu}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ferrero}}, \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Sachdev}},\ }\href
-  {https://doi.org/10.1073/pnas.1720580115} {\bibfield  {journal} {\bibinfo
-  {journal} {Proceedings of the National Academy of Sciences}\ }\textbf
-  {\bibinfo {volume} {115}},\ \bibinfo {pages} {E3665} (\bibinfo {year}
-  {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Krien}\ \emph {et~al.}(2022)\citenamefont {Krien},
-  \citenamefont {Worm}, \citenamefont {Chalupa-Gantner}, \citenamefont
-  {Toschi},\ and\ \citenamefont {Held}}]{Krien2022}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Krien}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Worm}},
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Chalupa-Gantner}},
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Toschi}},\ and\ \bibinfo
-  {author} {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\href
-  {https://doi.org/10.1038/s42005-022-01117-5} {\bibfield  {journal} {\bibinfo
-  {journal} {Communications Physics}\ }\textbf {\bibinfo {volume} {5}},\
-  \bibinfo {pages} {336} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kitatani}\ \emph {et~al.}(2023)\citenamefont
-  {Kitatani}, \citenamefont {Si}, \citenamefont {Worm}, \citenamefont
-  {Tomczak}, \citenamefont {Arita},\ and\ \citenamefont {Held}}]{Kitatani2023}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Kitatani}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Si}},
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Worm}}, \bibinfo {author}
-  {\bibfnamefont {J.~M.}\ \bibnamefont {Tomczak}}, \bibinfo {author}
-  {\bibfnamefont {R.}~\bibnamefont {Arita}},\ and\ \bibinfo {author}
-  {\bibfnamefont {K.}~\bibnamefont {Held}},\ }\href
-  {https://doi.org/10.1103/PhysRevLett.130.166002} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {130}},\
-  \bibinfo {pages} {166002} (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sorella}(2023)}]{Sorella2023}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Sorella}},\ }\href {https://doi.org/10.1103/PhysRevB.107.115133} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-  {107}},\ \bibinfo {pages} {115133} (\bibinfo {year} {2023})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Schäfer}\ \emph {et~al.}(2021)\citenamefont
-  {Schäfer}, \citenamefont {Wentzell}, \citenamefont {Šimkovic},
-  \citenamefont {He}, \citenamefont {Hille}, \citenamefont {Klett},
-  \citenamefont {Eckhardt}, \citenamefont {Arzhang}, \citenamefont {Harkov},
-  \citenamefont {Le~R\'egent}, \citenamefont {Kirsch}, \citenamefont {Wang},
-  \citenamefont {Kim}, \citenamefont {Kozik}, \citenamefont {Stepanov},
-  \citenamefont {Kauch}, \citenamefont {Andergassen}, \citenamefont {Hansmann},
-  \citenamefont {Rohe}, \citenamefont {Vilk}, \citenamefont {LeBlanc},
-  \citenamefont {Zhang}, \citenamefont {Tremblay}, \citenamefont {Ferrero},
-  \citenamefont {Parcollet},\ and\ \citenamefont {Georges}}]{Schafer2021}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Schäfer}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Wentzell}},
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Šimkovic}}, \bibinfo
-  {author} {\bibfnamefont {Y.-Y.}\ \bibnamefont {He}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {Hille}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Klett}}, \bibinfo {author} {\bibfnamefont {C.~J.}\
-  \bibnamefont {Eckhardt}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-  {Arzhang}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Harkov}},
-  \bibinfo {author} {\bibfnamefont {F.~m. c.-M.}\ \bibnamefont {Le~R\'egent}},
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Kirsch}}, \bibinfo
-  {author} {\bibfnamefont {Y.}~\bibnamefont {Wang}}, \bibinfo {author}
-  {\bibfnamefont {A.~J.}\ \bibnamefont {Kim}}, \bibinfo {author} {\bibfnamefont
-  {E.}~\bibnamefont {Kozik}}, \bibinfo {author} {\bibfnamefont {E.~A.}\
-  \bibnamefont {Stepanov}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Kauch}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Andergassen}},
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Hansmann}}, \bibinfo
-  {author} {\bibfnamefont {D.}~\bibnamefont {Rohe}}, \bibinfo {author}
-  {\bibfnamefont {Y.~M.}\ \bibnamefont {Vilk}}, \bibinfo {author}
-  {\bibfnamefont {J.~P.~F.}\ \bibnamefont {LeBlanc}}, \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
-  {A.-M.~S.}\ \bibnamefont {Tremblay}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Ferrero}}, \bibinfo {author} {\bibfnamefont
-  {O.}~\bibnamefont {Parcollet}},\ and\ \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Georges}},\ }\href
-  {https://doi.org/10.1103/PhysRevX.11.011058} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
-  {pages} {011058} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {White}\ and\ \citenamefont
-  {Scalapino}(1998)}]{White1998}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~R.}\ \bibnamefont
-  {White}}\ and\ \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
-  {Scalapino}},\ }\href {https://doi.org/10.1103/PhysRevLett.80.1272}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-  {\bibinfo {volume} {80}},\ \bibinfo {pages} {1272} (\bibinfo {year}
-  {1998})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ido}\ \emph {et~al.}(2018)\citenamefont {Ido},
-  \citenamefont {Ohgoe},\ and\ \citenamefont {Imada}}]{Ido2018}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Ido}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Ohgoe}},\ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Imada}},\ }\href
-  {https://doi.org/10.1103/PhysRevB.97.045138} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo
-  {pages} {045138} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Proust}\ and\ \citenamefont
-  {Taillefer}(2019)}]{ProustTaillefer2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Proust}}\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Taillefer}},\ }\href
-  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-031218-013210}
-  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-  Physics}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {409}
-  (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ponsioen}\ \emph {et~al.}(2019)\citenamefont
-  {Ponsioen}, \citenamefont {Chung},\ and\ \citenamefont
-  {Corboz}}]{Ponsioen2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-  {Ponsioen}}, \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont
-  {Chung}},\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Corboz}},\ }\href {https://doi.org/10.1103/PhysRevB.100.195141} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-  {100}},\ \bibinfo {pages} {195141} (\bibinfo {year} {2019})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Xu}\ \emph {et~al.}(2022)\citenamefont {Xu},
-  \citenamefont {Shi}, \citenamefont {Vitali}, \citenamefont {Qin},\ and\
-  \citenamefont {Zhang}}]{XuZhang2022}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Xu}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Shi}}, \bibinfo
-  {author} {\bibfnamefont {E.}~\bibnamefont {Vitali}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Qin}},\ and\ \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Zhang}},\ }\href
-  {https://doi.org/10.1103/PhysRevResearch.4.013239} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Res.}\ }\textbf {\bibinfo {volume} {4}},\
-  \bibinfo {pages} {013239} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Dave}\ \emph {et~al.}(2013)\citenamefont {Dave},
-  \citenamefont {Phillips},\ and\ \citenamefont {Kane}}]{Phillips2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~B.}\ \bibnamefont
-  {Dave}}, \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\
-  and\ \bibinfo {author} {\bibfnamefont {C.~L.}\ \bibnamefont {Kane}},\ }\href
-  {https://doi.org/10.1103/PhysRevLett.110.090403} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {110}},\
-  \bibinfo {pages} {090403} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Seki}\ and\ \citenamefont
-  {Yunoki}(2017)}]{seki2017topological}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Seki}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Yunoki}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
-  B}\ }\textbf {\bibinfo {volume} {96}},\ \bibinfo {pages} {085124} (\bibinfo
-  {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Anderson}\ and\ \citenamefont
-  {Haldane}(2001)}]{Anderson2001}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-  {Anderson}}\ and\ \bibinfo {author} {\bibfnamefont {F.~D.~M.}\ \bibnamefont
-  {Haldane}},\ }\href {https://doi.org/10.1023/A:1010324912515} {\bibfield
-  {journal} {\bibinfo  {journal} {Journal of Statistical Physics}\ }\textbf
-  {\bibinfo {volume} {103}},\ \bibinfo {pages} {425} (\bibinfo {year}
-  {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Huang}\ \emph {et~al.}(2022)\citenamefont {Huang},
-  \citenamefont {Nave},\ and\ \citenamefont {Phillips}}]{Huang2022}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont
-  {Huang}}, \bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont {Nave}},\
-  and\ \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\
-  }\href {https://doi.org/10.1038/s41567-022-01529-8} {\bibfield  {journal}
-  {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {18}},\
-  \bibinfo {pages} {511} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Coleman}\ \emph {et~al.}(2001)\citenamefont
-  {Coleman}, \citenamefont {Pépin}, \citenamefont {Si},\ and\ \citenamefont
-  {Ramazashvili}}]{Coleman_2001}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Coleman}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Pépin}},
-  \bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont {Si}},\ and\ \bibinfo
-  {author} {\bibfnamefont {R.}~\bibnamefont {Ramazashvili}},\ }\href
-  {https://doi.org/10.1088/0953-8984/13/35/202} {\bibfield  {journal} {\bibinfo
-   {journal} {Journal of Physics: Condensed Matter}\ }\textbf {\bibinfo
-  {volume} {13}},\ \bibinfo {pages} {R723} (\bibinfo {year}
-  {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
-  {Lal}(2020{\natexlab{b}})}]{anirbanurg1}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Lal}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nuclear
-  Physics B}\ }\textbf {\bibinfo {volume} {960}},\ \bibinfo {pages} {115170}
-  (\bibinfo {year} {2020}{\natexlab{b}})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mukherjee}\ and\ \citenamefont
-  {Lal}(2020{\natexlab{c}})}]{anirbanurg2}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Mukherjee}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Lal}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nuclear
-  Physics B}\ }\textbf {\bibinfo {volume} {960}},\ \bibinfo {pages} {115163}
-  (\bibinfo {year} {2020}{\natexlab{c}})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Keimer}\ \emph {et~al.}(2015)\citenamefont {Keimer},
-  \citenamefont {Kivelson}, \citenamefont {Norman}, \citenamefont {Uchida},\
-  and\ \citenamefont {Zaanen}}]{keimer2015quantum}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-  {Keimer}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
-  {Kivelson}}, \bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
-  {Norman}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Uchida}},\
-  and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zaanen}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf
-  {\bibinfo {volume} {518}},\ \bibinfo {pages} {179} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hatsugai}\ and\ \citenamefont
-  {Kohmoto}(1992)}]{Hatsugai1992}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Hatsugai}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Kohmoto}},\ }\href {https://doi.org/10.1143/JPSJ.61.2056} {\bibfield
-  {journal} {\bibinfo  {journal} {Journal of the Physical Society of Japan}\
-  }\textbf {\bibinfo {volume} {61}},\ \bibinfo {pages} {2056} (\bibinfo {year}
-  {1992})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Baskaran}(1991)}]{Baskaran1991}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Baskaran}},\ }\href {https://doi.org/10.1142/S0217984991000782} {\bibfield
-  {journal} {\bibinfo  {journal} {Modern Physics Letters B}\ }\textbf {\bibinfo
-  {volume} {05}},\ \bibinfo {pages} {643} (\bibinfo {year} {1991})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Altshuler}\ \emph {et~al.}(1998)\citenamefont
-  {Altshuler}, \citenamefont {Chubukov}, \citenamefont {Dashevskii},
-  \citenamefont {Finkel'stein},\ and\ \citenamefont {Morr}}]{Altshuler_1998}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~L.}\ \bibnamefont
-  {Altshuler}}, \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
-  {Chubukov}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Dashevskii}}, \bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
-  {Finkel'stein}},\ and\ \bibinfo {author} {\bibfnamefont {D.~K.}\ \bibnamefont
-  {Morr}},\ }\href {https://doi.org/10.1209/epl/i1998-00164-y} {\bibfield
-  {journal} {\bibinfo  {journal} {Europhysics Letters}\ }\textbf {\bibinfo
-  {volume} {41}},\ \bibinfo {pages} {401} (\bibinfo {year} {1998})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Heath}\ and\ \citenamefont
-  {Bedell}(2020)}]{Heath_2020}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont
-  {Heath}}\ and\ \bibinfo {author} {\bibfnamefont {K.~S.}\ \bibnamefont
-  {Bedell}},\ }\href {https://doi.org/10.1088/1367-2630/ab890e} {\bibfield
-  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
-  {volume} {22}},\ \bibinfo {pages} {063011} (\bibinfo {year}
-  {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Nave}\ \emph {et~al.}(2025)\citenamefont {Nave},
-  \citenamefont {Zhao},\ and\ \citenamefont {Phillips}}]{lanave2025}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont
-  {Nave}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zhao}},\ and\
-  \bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont {Phillips}},\ }\href
-  {https://arxiv.org/abs/2506.04342} {} (\bibinfo {year} {2025}),\ \Eprint
-  {https://arxiv.org/abs/2506.04342} {arXiv:2506.04342 [cond-mat.str-el]}
-  \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mukherjee}\ \emph {et~al.}(2023)\citenamefont
-  {Mukherjee}, \citenamefont {Vidhyadhiraja}, \citenamefont {Taraphder},\ and\
-  \citenamefont {Lal}}]{Mukherjee_2023}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Mukherjee}}, \bibinfo {author} {\bibfnamefont {N.~S.}\ \bibnamefont
-  {Vidhyadhiraja}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Taraphder}},\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Lal}},\ }\href {https://doi.org/10.1088/1367-2630/ad08f3} {\bibfield
-  {journal} {\bibinfo  {journal} {New Journal of Physics}\ }\textbf {\bibinfo
-  {volume} {25}},\ \bibinfo {pages} {113011} (\bibinfo {year}
-  {2023})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Georges}\ \emph {et~al.}(1996)\citenamefont
-  {Georges}, \citenamefont {Kotliar}, \citenamefont {Krauth},\ and\
-  \citenamefont {Rozenberg}}]{georges1996}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Georges}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Kotliar}},
-  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Krauth}},\ and\ \bibinfo
-  {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Rozenberg}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Reviews of Modern Physics}\
-  }\textbf {\bibinfo {volume} {68}},\ \bibinfo {pages} {13} (\bibinfo {year}
-  {1996})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hettler}\ \emph {et~al.}(1998)\citenamefont
-  {Hettler}, \citenamefont {Tahvildar-Zadeh}, \citenamefont {Jarrell},
-  \citenamefont {Pruschke},\ and\ \citenamefont {Krishnamurthy}}]{hettler1998}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Hettler}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Tahvildar-Zadeh}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Jarrell}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Pruschke}},\
-  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Krishnamurthy}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical Review
-  B}\ }\textbf {\bibinfo {volume} {58}},\ \bibinfo {pages} {R7475} (\bibinfo
-  {year} {1998})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kotliar}\ \emph {et~al.}(2001)\citenamefont
-  {Kotliar}, \citenamefont {Savrasov}, \citenamefont {P{\'a}lsson},\ and\
-  \citenamefont {Biroli}}]{kotliar2001}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Kotliar}}, \bibinfo {author} {\bibfnamefont {S.~Y.}\ \bibnamefont
-  {Savrasov}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {P{\'a}lsson}},\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Biroli}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Physical review letters}\ }\textbf {\bibinfo {volume} {87}},\ \bibinfo
-  {pages} {186401} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Maier}\ \emph {et~al.}(2005)\citenamefont {Maier},
-  \citenamefont {Jarrell}, \citenamefont {Schulthess}, \citenamefont {Kent},\
-  and\ \citenamefont {White}}]{maier2005}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont
-  {Maier}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Jarrell}},
-  \bibinfo {author} {\bibfnamefont {T.~C.}\ \bibnamefont {Schulthess}},
-  \bibinfo {author} {\bibfnamefont {P.~R.~C.}\ \bibnamefont {Kent}},\ and\
-  \bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont {White}},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-  {\bibinfo {volume} {95}},\ \bibinfo {pages} {237001} (\bibinfo {year}
-  {2005})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Stoyanova}(2006)}]{stoyanova}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Stoyanova}},\ }\emph {\bibinfo {title} {Delocalized and correlated wave
-  functions for excited states in extended systems}},\ \href@noop {} {Ph.D.
-  thesis},\ \bibinfo  {school} {University of Groningen} (\bibinfo {year}
-  {2006})\BibitemShut {NoStop}%
-\bibitem [{sup()}]{suppmat}%
-  \BibitemOpen
-  \href@noop {} {\bibinfo {title} {See supplemental material for additional
-  information.}}\BibitemShut {Stop}%
-\bibitem [{\citenamefont {Wu}\ \emph {et~al.}(2018)\citenamefont {Wu},
-  \citenamefont {Scheurer}, \citenamefont {Chatterjee}, \citenamefont
-  {Sachdev}, \citenamefont {Georges},\ and\ \citenamefont
-  {Ferrero}}]{WuFerrero2018}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
-  {Wu}}, \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Scheurer}},
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Chatterjee}}, \bibinfo
-  {author} {\bibfnamefont {S.}~\bibnamefont {Sachdev}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Georges}},\ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Ferrero}},\ }\href
-  {https://doi.org/10.1103/PhysRevX.8.021048} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {8}},\ \bibinfo {pages}
-  {021048} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Tsvelick}\ and\ \citenamefont
-  {Wiegmann}(1985)}]{Tsvelick_weigmann_mchannel_1985}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
-  {Tsvelick}}\ and\ \bibinfo {author} {\bibfnamefont {P.~B.}\ \bibnamefont
-  {Wiegmann}},\ }\href {https://doi.org/10.1007/BF01017853} {\bibfield
-  {journal} {\bibinfo  {journal} {Journal of Statistical Physics}\ }\textbf
-  {\bibinfo {volume} {38}},\ \bibinfo {pages} {125} (\bibinfo {year}
-  {1985})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Emery}\ and\ \citenamefont
-  {Kivelson}(1992)}]{emery_kivelson}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~J.}\ \bibnamefont
-  {Emery}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Kivelson}},\ }\href {https://doi.org/10.1103/PhysRevB.46.10812} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-  {46}},\ \bibinfo {pages} {10812} (\bibinfo {year} {1992})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Gunnarsson}\ \emph {et~al.}(2003)\citenamefont
-  {Gunnarsson}, \citenamefont {Calandra},\ and\ \citenamefont
-  {Han}}]{GunnarssonRMP2003}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
-  {Gunnarsson}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Calandra}},\ and\ \bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont
-  {Han}},\ }\href {https://doi.org/10.1103/RevModPhys.75.1085} {\bibfield
-  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume}
-  {75}},\ \bibinfo {pages} {1085} (\bibinfo {year} {2003})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Hussey}\ \emph {et~al.}(2004)\citenamefont {Hussey},
-  \citenamefont {Takenaka},\ and\ \citenamefont {Takagi}}]{Hussey2004}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~E.}\ \bibnamefont
-  {Hussey}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Takenaka}},\
-  and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Takagi}},\ }\href
-  {https://doi.org/10.1080/14786430410001716944} {\bibfield  {journal}
-  {\bibinfo  {journal} {Philosophical Magazine}\ }\textbf {\bibinfo {volume}
-  {84}},\ \bibinfo {pages} {2847} (\bibinfo {year} {2004})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Pustogow}\ \emph {et~al.}(2021)\citenamefont
-  {Pustogow}, \citenamefont {Saito}, \citenamefont {Anja~Löhle}, \citenamefont
-  {Alonso}, \citenamefont {Kawamoto}, \citenamefont {Dobrosavljevic},
-  \citenamefont {Dressel},\ and\ \citenamefont {Fratini}}]{pustogow2021}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Pustogow}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Saito}},
-  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Anja~Löhle}}, \bibinfo
-  {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Alonso}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Kawamoto}}, \bibinfo {author}
-  {\bibfnamefont {V.}~\bibnamefont {Dobrosavljevic}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Dressel}},\ and\ \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Fratini}},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nat. Comm.}\ }\textbf {\bibinfo {volume}
-  {12}},\ \bibinfo {pages} {1571} (\bibinfo {year} {2021})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Qazilbash}\ \emph {et~al.}(2008)\citenamefont
-  {Qazilbash}, \citenamefont {Schafgans}, \citenamefont {Burch}, \citenamefont
-  {Yun}, \citenamefont {Chae}, \citenamefont {Kim}, \citenamefont {Kim},\ and\
-  \citenamefont {Basov}}]{qazilbash2008}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~M.}\ \bibnamefont
-  {Qazilbash}}, \bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont
-  {Schafgans}}, \bibinfo {author} {\bibfnamefont {K.~S.}\ \bibnamefont
-  {Burch}}, \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont {Yun}},
-  \bibinfo {author} {\bibfnamefont {B.~G.}\ \bibnamefont {Chae}}, \bibinfo
-  {author} {\bibfnamefont {B.~J.}\ \bibnamefont {Kim}}, \bibinfo {author}
-  {\bibfnamefont {H.~T.}\ \bibnamefont {Kim}},\ and\ \bibinfo {author}
-  {\bibfnamefont {D.~N.}\ \bibnamefont {Basov}},\ }\href
-  {https://doi.org/10.1103/PhysRevB.77.115121} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo
-  {pages} {115121} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hauke}\ \emph {et~al.}(2016)\citenamefont {Hauke},
-  \citenamefont {Heyl}, \citenamefont {Tagliacozzo},\ and\ \citenamefont
-  {Zoller}}]{Hauke2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Hauke}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Heyl}},
-  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Tagliacozzo}},\ and\
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Zoller}},\ }\href
-  {https://doi.org/10.1038/nphys3700} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
-  {pages} {778} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Balut}\ \emph {et~al.}(2025)\citenamefont {Balut},
-  \citenamefont {Guo}, \citenamefont {de~Vriesa}, \citenamefont {Chaudhuri},
-  \citenamefont {Bradlyn}, \citenamefont {Abbamonte},\ and\ \citenamefont
-  {W.}}]{balut2025}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Balut}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Guo}}, \bibinfo
-  {author} {\bibfnamefont {N.}~\bibnamefont {de~Vriesa}}, \bibinfo {author}
-  {\bibfnamefont {D.}~\bibnamefont {Chaudhuri}}, \bibinfo {author}
-  {\bibfnamefont {B.}~\bibnamefont {Bradlyn}}, \bibinfo {author} {\bibfnamefont
-  {P.}~\bibnamefont {Abbamonte}},\ and\ \bibinfo {author} {\bibfnamefont
-  {P.~P.}\ \bibnamefont {W.}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Physica C}\ }\textbf {\bibinfo {volume} {635}},\ \bibinfo {pages}
-  {1354750} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mazza}\ \emph {et~al.}(2024)\citenamefont {Mazza},
-  \citenamefont {Biswas}, \citenamefont {Yan}, \citenamefont {Prokofiev},
-  \citenamefont {Steffens}, \citenamefont {Si}, \citenamefont {Assaad},\ and\
-  \citenamefont {Paschen}}]{mazza2024}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Mazza}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Biswas}},
-  \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Yan}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Prokofiev}}, \bibinfo {author}
-  {\bibfnamefont {P.}~\bibnamefont {Steffens}}, \bibinfo {author}
-  {\bibfnamefont {Q.}~\bibnamefont {Si}}, \bibinfo {author} {\bibfnamefont
-  {F.~F.}\ \bibnamefont {Assaad}},\ and\ \bibinfo {author} {\bibfnamefont
-  {S.}~\bibnamefont {Paschen}},\ }\href {https://arxiv.org/abs/2403.12779} {}
-  (\bibinfo {year} {2024}),\ \Eprint {https://arxiv.org/abs/2403.12779}
-  {arXiv:2403.12779 [cond-mat.str-el]} \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Si}\ \emph {et~al.}(2001)\citenamefont {Si},
-  \citenamefont {Rabello}, \citenamefont {Ingersent},\ and\ \citenamefont
-  {Smith}}]{Si2001}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont
-  {Si}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Rabello}},
-  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Ingersent}},\ and\
-  \bibinfo {author} {\bibfnamefont {J.~L.}\ \bibnamefont {Smith}},\ }\href
-  {https://doi.org/10.1038/35101507} {\bibfield  {journal} {\bibinfo  {journal}
-  {Nature}\ }\textbf {\bibinfo {volume} {413}},\ \bibinfo {pages} {804}
-  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Phillips}\ \emph {et~al.}(2020)\citenamefont
-  {Phillips}, \citenamefont {Yeo},\ and\ \citenamefont {Huang}}]{Phillips2020}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-  {Phillips}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Yeo}},\ and\
-  \bibinfo {author} {\bibfnamefont {E.~W.}\ \bibnamefont {Huang}},\ }\href
-  {https://doi.org/10.1038/s41567-020-0988-4} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo
-  {pages} {1175} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Vafek}\ and\ \citenamefont
-  {Vishwanath}(2014)}]{vafekvishwanath2014}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
-  {Vafek}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Vishwanath}},\ }\href
-  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-031113-133841}
-  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-  Physics}\ }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {83} (\bibinfo
-  {year} {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Morimoto}\ and\ \citenamefont
-  {Nagaosa}(2016)}]{morimoto2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Morimoto}}\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Nagaosa}},\ }\href {https://doi.org/10.1038/srep19853} {\bibfield  {journal}
-  {\bibinfo  {journal} {Sci. Rep.}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo
-  {pages} {19853} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Flores-Calder\'on}\ and\ \citenamefont
-  {Hooley}(2025)}]{calderon2025}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Flores-Calder\'on}}\ and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Hooley}},\ }\href {https://doi.org/10.1103/k4st-77ph} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {111}},\
-  \bibinfo {pages} {235139} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Georgi}(2007{\natexlab{a}})}]{Georgi2007PRL}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Georgi}},\ }\href {https://doi.org/10.1103/PhysRevLett.98.221601} {\bibfield
-   {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
-  {volume} {98}},\ \bibinfo {pages} {221601} (\bibinfo {year}
-  {2007}{\natexlab{a}})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Georgi}(2007{\natexlab{b}})}]{Georgi2007}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Georgi}},\ }\href
-  {https://doi.org/https://doi.org/10.1016/j.physletb.2007.05.037} {\bibfield
-  {journal} {\bibinfo  {journal} {Physics Letters B}\ }\textbf {\bibinfo
-  {volume} {650}},\ \bibinfo {pages} {275} (\bibinfo {year}
-  {2007}{\natexlab{b}})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Phillips}(2014)}]{PhillipsLectures2014}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~W.}\ \bibnamefont
-  {Phillips}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {Quantum
-  Criticality in Condensed Matter}}},\ \bibinfo {editor} {edited by\ \bibinfo
-  {editor} {\bibfnamefont {J.}~\bibnamefont {Jedrzejewski}}}\ (\bibinfo
-  {publisher} {World Scientific, Singapore},\ \bibinfo {year} {2014})\ pp.\
-  \bibinfo {pages} {133--158}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zaanen}(2019)}]{zaanen2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Zaanen}},\ }\href {https://doi.org/10.21468/SciPostPhys.6.5.061} {\bibfield
-  {journal} {\bibinfo  {journal} {SciPost Phys.}\ }\textbf {\bibinfo {volume}
-  {6}},\ \bibinfo {pages} {061} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Legros}\ \emph {et~al.}(2019)\citenamefont {Legros},
-  \citenamefont {Benhabib}, \citenamefont {Tabis}, \citenamefont
-  {Lalibert{\'e}}, \citenamefont {Dion}, \citenamefont {Lizaire}, \citenamefont
-  {Vignolle}, \citenamefont {Vignolles}, \citenamefont {Raffy}, \citenamefont
-  {Li} \emph {et~al.}}]{legros2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Legros}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Benhabib}},
-  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Tabis}}, \bibinfo
-  {author} {\bibfnamefont {F.}~\bibnamefont {Lalibert{\'e}}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Dion}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Lizaire}}, \bibinfo {author} {\bibfnamefont
-  {B.}~\bibnamefont {Vignolle}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Vignolles}}, \bibinfo {author} {\bibfnamefont
-  {H.}~\bibnamefont {Raffy}}, \bibinfo {author} {\bibfnamefont
-  {Z.}~\bibnamefont {Li}}, \emph {et~al.},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Nature Physics}\ }\textbf {\bibinfo {volume}
-  {15}},\ \bibinfo {pages} {142} (\bibinfo {year} {2019})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {McGreevy}(2023)}]{McGreevy2023}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {McGreevy}},\ }\href
-  {https://doi.org/https://doi.org/10.1146/annurev-conmatphys-040721-021029}
-  {\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Condensed Matter
-  Physics}\ }\textbf {\bibinfo {volume} {14}},\ \bibinfo {pages} {57} (\bibinfo
-  {year} {2023})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Luttinger}\ and\ \citenamefont
-  {Ward}(1960)}]{luttinger1960ground}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-  {Luttinger}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
-  {Ward}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Physical
-  Review}\ }\textbf {\bibinfo {volume} {118}},\ \bibinfo {pages} {1417}
-  (\bibinfo {year} {1960})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Su}\ and\ \citenamefont
-  {Martin}(2025)}]{su2025anomalies}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Su}}\ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Martin}},\
-  }\href {https://arxiv.org/abs/2405.08093} {} (\bibinfo {year} {2025}),\
-  \Eprint {https://arxiv.org/abs/2405.08093} {arXiv:2405.08093
-  [cond-mat.str-el]} \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Adler}(1969)}]{adler1969axial}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~L.}\ \bibnamefont
-  {Adler}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Physical Review}\ }\textbf {\bibinfo {volume} {177}},\ \bibinfo {pages}
-  {2426} (\bibinfo {year} {1969})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bell}\ and\ \citenamefont
-  {Jackiw}(1969)}]{bell1969pcac}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~S.}\ \bibnamefont
-  {Bell}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Jackiw}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Il Nuovo Cimento
-  A}\ }\textbf {\bibinfo {volume} {60}},\ \bibinfo {pages} {47} (\bibinfo
-  {year} {1969})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Casini}\ and\ \citenamefont
-  {Mag\'{a}n}(2021)}]{Casini2021Symmetries}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Casini}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-  {Mag\'{a}n}},\ }\href {https://doi.org/10.1142/S0217732321300251} {\bibfield
-  {journal} {\bibinfo  {journal} {Modern Physics Letters A}\ }\textbf {\bibinfo
-  {volume} {36}},\ \bibinfo {pages} {2130025} (\bibinfo {year}
-  {2021})}\BibitemShut {NoStop}%
-\end{thebibliography}
-
-%\bibliography{tilingProject}
-
-\vspace{0.25cm}
-\par\noindent\textbf{Acknowledgments.}
-We acknowledge National Supercomputing Mission (NSM) for providing computing resources of ‘PARAM RUDRA’ at Aruna Asaf Ali Marg, near Vasant Kunj, New Delhi, Delhi 110067, which is implemented by C-DAC and supported by the Ministry of Electronics and Information Technology (MeitY) and Department of Science and Technology (DST), Government of India.
-SL thanks the SERB, Govt.
-of India for funding through MATRICS grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
-AM thanks IISER Kolkata for funding through a JRF and an SRF.
-A.M.
-would also like to acknowledge the SERB-MATRICS grant (Grant No.
-MTR/2022/000636) from the Science and Engineering Research Board (SERB) for funding.
-S.L.
-thanks Mayank Shreshtha for designing Fig.1.
-
-\vspace{0.25cm}
-\par\noindent\textbf{Author Contributions.}
-A.M., S.R.H.
-and S.L.
-conceived and designed the research.
-A.M.
-performed the calculations and analysis with support from all authors.
-A.M., S.R.H., A.M.
-and S.L.
-wrote the manuscript with inputs from all authors.
-All work was supervised by S.L.
-
-\vspace{0.25cm}
-\par\noindent\textbf{Code Availability}
-The codes created and datasets generated during this research are available from the corresponding author upon reasonable request.
-
-\vspace*{0.5cm}
-\par\noindent\textbf{\large Models and Methods}\\
-\noindent\textbf{Lattice-embedded Impurity Model}\\
-We state the detailed Hamiltonian of the auxiliary model here: $\mathcal{H}_\text{aux} = H_\text{imp} + H_\text{coup} + H_\text{cbath}$,
-where the particle-hole symmetric impurity term is
-\begin{equation}
-H_\text{imp} = - \frac{U}{2} \left( \hat{n}_{d \uparrow} - \hat{n}_{d \downarrow} \right)^2,
-\end{equation}
-describing on-site Coulomb interactions at the impurity.
-Here, $c^\dagger_{d\sigma}$ creates an electron with spin $\sigma$ at the impurity site, and $\hat{n}_{d\sigma} = c^\dagger_{d\sigma} c_{d\sigma}$ denotes the corresponding number operator.
-The impurity couples to four nearest-neighbour bath sites $c_{Z\sigma}$ through both hybridization and Kondo exchange:
-\begin{equation}\begin{aligned}
-\hspace{-1cm} H_\text{coup} = \frac{J}{2} \hspace{-0.25cm}\sum_{\sigma_1,\sigma_2,Z} 
-%\sum_{Z} 
-{\bf S}_d \cdot c^\dagger_{Z\sigma_1} {\boldsymbol \tau}_{\sigma_1 \sigma_2} c_{Z\sigma_2} 
-- V \sum_{\sigma,Z} \left( c^\dagger_{Z\sigma} c_{d\sigma} + \text{h.c.} \right),    
-\end{aligned}\end{equation}
-where ${\boldsymbol \tau}$ are the Pauli matrices, and $Z$ indexes the four neighbouring bath sites.
-The half-filled bath includes nearest neighbour hopping and on-site correlations on the site neighbouring the impurity:
-\begin{equation}
-H_\text{cbath} = \sum_{\bf k} \epsilon_{\bf k} c^\dagger_{{\bf k},\sigma} c_{{\bf k},\sigma} - \frac{W}{2} \sum_{Z} \left( \hat{n}_{Z\uparrow} - \hat{n}_{Z\downarrow} \right)^2,
-\end{equation}
-where $\epsilon_{\bf k} = -2t(\cos k_x + \cos k_y)$, and $W$ parametrizes local repulsion in the bath.
-This frustrates Kondo screening and drives the system towards local-moment formation.
-A crucial feature of this construction is that the Kondo coupling acquires a momentum structure upon Fourier transforming:
-\begin{equation}
-J_{{\bf k}, {\bf k}^\prime} = \frac{J}{2} \left[ \cos(k_x - k^\prime_x) + \cos(k_y - k^\prime_y) \right],
-\end{equation}
-which respects the $C_4$ symmetry of the square lattice.
-\vspace{0.25cm}
-\par\noindent\textbf{Tiling the impurity model}\\
-\noindent
-We now provide details on how the effective lattice Hamiltonian is constructed from the underlying impurity model.
-As described in the main text, the auxiliary model consists of a single impurity embedded in a correlated bath:
-
-\begin{equation}
-H(\mathbf{r}_d) = H_{\text{imp}} + H_{\text{cbath}} + H_{\text{imp-cbath}},
-\end{equation}
-where the impurity Hamiltonian is
-\begin{equation}
-H_{\text{imp}} = -\frac{U}{2} \left( \hat{n}_{\mathbf{r}_d\uparrow} - \hat{n}_{\mathbf{r}_d\downarrow} \right)^2,
-\end{equation}
-and the conduction bath is described by
-\begin{equation}
-\begin{aligned}
-H_{\text{cbath}} = & -\frac{1}{\sqrt{\mathcal{Z}}} t \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle \ne \mathbf{r}_d; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
-& - \frac{1}{2\mathcal{Z}} W \sum_{\mathbf{z} \in \text{NN}(\mathbf{r}_d)} \left( \hat{n}_{\mathbf{z}\uparrow} - \hat{n}_{\mathbf{z}\downarrow} \right)^2 ,
-\end{aligned}
-\end{equation}
-and the impurity–bath hybridization term is
-\begin{equation}
-\begin{aligned}
-H_{\text{imp-cbath}} = & \frac{J}{\mathcal{Z}} \sum_{\sigma, \sigma'} \sum_{\mathbf{z} \in \text{NN}(\mathbf{r}_d)} \mathbf{S}_{\mathbf{r}_d} \cdot \boldsymbol{\tau}_{\sigma \sigma'} c^\dagger_{\mathbf{z}\sigma} c_{\mathbf{z}\sigma'} \\
-& - \frac{V}{\sqrt{\mathcal{Z}}} \sum_{\sigma} \sum_{\mathbf{z} \in \text{NN}(\mathbf{r}_d)} \left( c^\dagger_{\mathbf{r}_d\sigma} c_{\mathbf{z}\sigma} + \text{h.c.} \right),
-\end{aligned}
-\end{equation}
-where $\boldsymbol{\tau} = (\tau_x, \tau_y, \tau_z)$ are Pauli matrices, and ${\bf r}_d$ denotes the impurity position.
-
-\noindent
-The tiled lattice Hamiltonian is generated by symmetrically translating this impurity model:
-\begin{equation}
-\mathcal{H}_{\text{tiled}} = \mathcal{T}[H(\mathbf{r}_d)] = \sum_{\mathbf{r}} T^\dagger(\mathbf{r} - \mathbf{r}_d) H(\mathbf{r}_d) T(\mathbf{r} - \mathbf{r}_d),
-\end{equation}
-where $T(\mathbf{a})$ are many-body translation operators, defined by $T^\dagger(\mathbf{a}) \mathcal{O}(\{\mathbf{r}_i\}) T(\mathbf{a}) = \mathcal{O}(\{\mathbf{r}_i + \mathbf{a}\})$.
-Applying this to each term yields:
-\begin{equation}\hspace{-0.5cm}\begin{aligned}
-\mathcal{T}[H_{\text{cbath}}] &= -\frac{(N - 2)t}{\sqrt{\mathcal{Z}}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
-&\quad - \frac{1}{2} W \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2, \\
-\mathcal{T}[H_{\text{imp}}] &= -\frac{U}{2} \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2, \\
-\mathcal{T}[H_{\text{imp-cbath}}] &= \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle} \left[ \frac{2J}{\mathcal{Z}} \mathbf{S}_{\mathbf{r}_i} \cdot \mathbf{S}_{\mathbf{r}_j} - \frac{2V}{\sqrt{\mathcal{Z}}} \sum_\sigma \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \right],
-\end{aligned}\end{equation}
-with local spin operators defined as $\mathbf{S}_{\mathbf{r}} = \sum_{\sigma, \sigma'} c^\dagger_{\mathbf{r}\sigma} \boldsymbol{\tau}_{\sigma \sigma'} c_{\mathbf{r}\sigma'}$.
-
-\noindent
-To avoid overcounting of the non-interacting bath terms, we subtract extra copies of $\mathcal{H}_{\text{cbath-nint}}$. The final reconstructed Hubbard–Heisenberg model then reads:
-\begin{equation}
-\begin{aligned}
-\mathcal{H}_{\text{HH}} = & -\frac{1}{\sqrt{\mathcal{Z}}} \tilde{t} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
-& + \frac{\tilde{J}}{\mathcal{Z}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle} \mathbf{S}_{\mathbf{r}_i} \cdot \mathbf{S}_{\mathbf{r}_j} - \frac{1}{2} \tilde{U} \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2,
-\end{aligned}
-\end{equation}
-where the effective lattice couplings are given by:
-\begin{equation}
-\tilde{t} = t + 2V,\quad \tilde{U} = U + W,\quad \tilde{J} = 2J.
-\end{equation}
-\end{document}

### 2025-12-10 submissions/manuscript_RP.tex
started creating referee response

--- 2025-12-10 submissions/TilingUploadROPP/manuscript_RP.tex
@@
-\documentclass[%
- reprint,
-superscriptaddress,
-groupedaddress,
-%unsortedaddress,
-%runinaddress,
-%frontmatterverbose, 
-%preprint,
-%preprintnumbers,
-%nofootinbib,
-%nobibnotes,
-%bibnotes,
-aps,superscriptaddress,
-pra,
-%rmp,
-%prstab,
-%prstper,
-%floatfix,
-]{revtex4-2}
-% ,bm,color,hyperref
-\usepackage{graphicx,braket,color,bm,amsmath,amssymb,hyperref}
-% \graphicspath{{./figures/}}
-\bibliographystyle{apsrev4-2}
-
-\begin{document}
-
-\title{Mott Criticality as the Confinement Transition of a Pseudogap-Mott Metal}
-
-\author{Abhirup Mukherjee}
-\email{am18ip014@iiserkol.ac.in}
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
-}
-\author{S. R. Hassan}
-\email{shassan@imsc.res.in}
-\affiliation{The Institute of Mathematical Sciences, HBNI, C.I.T. Campus, Chennai 600 113, India}
-\author{Anamitra Mukherjee}
-\email{anamitra@niser.ac.in}
-\affiliation{School of Physical Sciences, National Institute of Science, Education and Research, HBNI, Jatni 752050, India}
-\author{N. S. Vidhyadhiraja}
-\email{raja@jncasr.ac.in}
-\affiliation{Theoretical Sciences Unit, Jawaharlal Nehru Center for Advanced Scientific Research, Jakkur, Bengaluru 560064, India}
-\author{A. Taraphder}
-\email{arghya@phy.iitkgp.ac.in}
-\affiliation{Department of Physics, Indian Institute of Technology Kharagpur, Kharagpur 721302, India}
-\author{Siddhartha Lal}
-\email{slal@iiserkol.ac.in}
-\affiliation{Department of Physical Sciences, Indian Institute of Science Education and Research Kolkata, Nadia - 741246, India
-}
-
-\date{\today}
-
-\begin{abstract}
-The phenomenon of Mott insulation involves the localization of itinerant electrons due to strong local repulsion.
-Upon doping, a pseudogap (PG) phase emerges - marked by selective gapping of the Fermi surface without conventional symmetry breaking in spin or charge channels.
-A key challenge is understanding how quasiparticle breakdown in the Fermi liquid gives rise to this enigmatic state, and how it connects to both the Mott insulating and superconducting phases.
-Here, we develop a renormalization-based construction of strongly correlated lattice models that captures the emergence of the pseudogap phase and its transition to a Mott insulator.
-Applying a many-body tiling scheme to the fixed-point impurity model uncovers a lattice model with electron interactions and Kondo physics.
-At half-filling, the interplay between Kondo screening and bath charge fluctuations in the impurity model leads to Fermi liquid breakdown.
-This reveals a pseudogap phase characterized by a non-Fermi liquid (the Mott metal) residing on nodal arcs, gapped antinodal regions of the Fermi surface, and an anomalous scaling of the electronic scattering rate with frequency.
-The eventual confinement of holon–doublon excitations of this exotic metal obtains a continuous transition into the Mott insulator.
-Our results identify the pseudogap as a distinct long-range entangled quantum phase, and offer a new route to Mott criticality beyond the paradigm of local quantum criticality.
-
-\end{abstract}
-
-\maketitle
-\section{Introduction}
-The Landau quasiparticle paradigm~\cite{landau1959theory} underpins our understanding of metallic behaviour, where the screening of long-ranged repulsive interactions between delocalised electrons leads to well-defined excitations that carry the same quantum numbers as free electrons.
-This remarkable phenomenon - known as adiabatic continuity -  is captured by excitations described by poles of the single-particle Greens function of the interacting system.
-But what defines metallicity when quasiparticles are no longer well-defined~\cite{Phillips2013Unparticles}?
-Can a surface of zeros of the Greens function~\cite{dzyaloshinskii2003some}, rather than poles forming a Fermi surface, define an entirely new kind of metal?
-Could such an exotic state serve as the precursor to Mott localisation driven purely by repulsion, and without invoking magnetic order~\cite{Mott_1949}?
-These questions necessitate a radical departure in understanding conduction in correlated electron systems beyond the quasiparticle paradigm~\cite{phillips2022}.
-\\
-
-\noindent
-The anomalous pseudogap (PG) phase, observed in the cuprates, exhibits nodal-antinodal dichotomy with spectral weight concentrated on Fermi arcs around the nodal regions~\cite{loeserKapitulnik1996, Norman1998, Hashimoto2014}.
-In the PG phase of such Mott systems
-~\cite{taillefer2010,FradkinRevModPhys2015,Sato2017,DoironLeyraud2017,Mukhopadhyay2019,Naman2021,Masafumi2025,KyungKotliar2006,MacridinAzevedo2006,sakai2009evolution,werner2009momentum,sakai2010doped,lin2010,gull2010momentum,gull2012,Mirzaei2013,gull2013,anirbanmott2,HilleAndergassen2020,Jiang2022,Scheurer2018,Krien2022,Kitatani2023,Sorella2023,Schafer2021,White1998,Ido2018,ProustTaillefer2019,Ponsioen2019,XuZhang2022}, the single-particle Green’s function develops surfaces of zeros, also known as Luttinger surfaces~\cite{Phillips2013,dzyaloshinskii2003some}, that signals a fundamental obstruction to quasiparticle formation.
-As interaction strength increases, these zero surfaces proliferate, fragmenting the Fermi surface into nodal arcs~\cite{sakai2009evolution,Phillips2013}, violating the Luttinger sum rule by reconfiguring Fermi volume~\cite{seki2017topological}, and breaking an emergent $\mathbb{Z}_2$ symmetry associated with the conservation of spin currents in Fermi liquids~\cite{Anderson2001,Huang2022}.
-Unlike conventional instabilities driven by poles, this phenomenon marks a topological breakdown of Fermi liquid theory~\cite{Coleman_2001,Phillips2013Unparticles}.
-We show that this breakdown arises from a strongly entangled, scale-invariant state of quantum matter, one that serves as the parent metal to the Mott insulator in a half-filled lattice model of strongly correlated electrons.
-This offers a concrete, controlled framework to understand both the non-quasiparticle character of the pseudogap phase and its continuous evolution into a repulsion-driven insulator, in full alignment with Mott's original vision~\cite{Mott_1949}.\\
-
-\begin{figure*}[tbh]
-    \centering
-    \includegraphics[width=\linewidth]{Figure1_Nature.pdf}
-    \caption{Schematic representation of (a) theoretical framework adopted by us (see main text for explanation of symbols), (b) phases obtained for the extended Hubbard model in two dimensions at $T=0$, and passage between them.}
-    \label{schematic}
-%    \label{schematic:b}
-\end{figure*}
-
-Our approach involves developing a renormalization group (RG)-based impurity-to-lattice framework that reconstructs the low-energy physics of a strongly correlated system from the fixed-point structure of a quantum impurity model (Fig.~\hyperref[schematic]{\ref*{schematic}(a)}).
-Starting from a dynamical Anderson impurity embedded in a correlated bath, we solve the system using a unitary RG (URG) approach~\cite{anirbanurg1,anirbanurg2}.
-We then construct a translation-invariant lattice Hamiltonian through a many-body tiling procedure that preserves non-local correlations and inherits momentum-resolved self-energies and renormalized couplings from the impurity solution.
-The resulting model is an \textit{extended}-Hubbard Hamiltonian on a two-dimensional square lattice at half-filling, with both on-site repulsion and nearest-neighbour spin exchange interactions.
-These correlations, derived directly from the impurity dynamics, enable tracking the evolution from the FL to the Mott insulator (MI) via an intermediate PG phase.
-
-A central insight of our work is that the PG phase hosts a NFL state governed by Kondo frustration and doublon–holon deconfinement~\cite{keimer2015quantum} (Fig.~\hyperref[schematic]{\ref*{schematic}(b)}).
-A correlation scale ($W$) in the conduction bath suppresses Kondo screening (with coupling $J$) beyond a critical ratio of $W/J$, triggering the emergence of Luttinger surfaces in the lattice model.
-This breakdown of quasiparticles begins at the antinodes and progressively engulfs the nodal regions, driving a continuous transformation into the MI.
-The resulting NFL exhibits a pseudogapped density of states that vanishes as $\omega^{2}$ as $\omega \to 0$, multipartite long-range entanglement, and a universal scattering rate of the form $\sim (a + b\,\omega^2)^{-1}$ that grows as $\omega \to 0$.
-At the critical endpoint of this phase, the URG flow identifies a singular NFL described by the Hatsugai–Kohmoto (HK) model~\cite{Hatsugai1992,Baskaran1991,Huang2022}, with fully deconfined holon–doublon excitations.
-
-The emergence of Luttinger surfaces alters the anomaly structure associated with the generalized symmetry of the FS~\cite{Altshuler_1998,Heath_2020,lanave2025}.
-The corresponding topological charge is defined via the Luttinger–Ward functional.
-This charge is modified by Green’s function zeros, signalling a shift in the underlying anomaly.
-Within our framework, this reorganization grants topological protection to the RG flows terminating in the PG regime, ensuring the stability of its NFL excitations.
-These are adiabatically connected to the Hatsugai–Kohmoto model~\cite{Hatsugai1992,Baskaran1991}, reinforcing the interpretation of the PG as a distinct quantum phase.
-We thus identify the NFL state as a new gapless, long-range entangled phase of correlated matter - the \textit{Mott metal} - whose deconfined holon-doublon excitations are eventually confined across the Mott transition~\cite{Mott_1949}.
-
-While we demonstrate our approach for an extended Hubbard model, the underlying framework is broadly applicable to correlated quantum systems.
-The impurity-plus-tiling construction accommodates multi-orbital degrees of freedom, frustrated geometries, and nontrivial band topology.
-By deriving lattice Hamiltonians directly from renormalized local dynamics - without relying on mean-field approximations - this method preserves nonlocal correlations and enhances momentum-space resolution.
-It thus provides a versatile and controlled route for engineering strongly correlated models, particularly in regimes where PG formation, NFL scaling, and Mott physics intersect.
-
-\section{Auxiliary Model and URG analysis}\label{auxurgsection}
-To capture the interplay between Kondo physics and Mott localization, our approach relies on a two-dimensional auxiliary model consisting of an Anderson impurity embedded in a minimally-correlated bath, which we solve the system using a unitary RG (URG) approach~\cite{anirbanurg1,anirbanurg2}.
-The impurity model and URG analysis are laid out in this section.
-In order to make contact with a lattice model, we construct a translation-invariant Hamiltonian from the impurity model through a many-body tiling procedure: this preserves non-local correlations, as well as allows for momentum-resolved self-energies and renormalized couplings generated from the impurity solution.
-For the impurity model chosen in this work, tiling results in an \textit{extended}-Hubbard Hamiltonian on a two-dimensional square lattice at particle-hole symmetry (half-filling).
-The interaction terms within the lattice model are a result of analogous correlations present in the auxiliary model.
-This is laid out next in Section~\ref{tilingsection}.
-
-\subsection{Lattice-embedded Impurity Model}
-The auxiliary model consists of a correlated impurity site (with a double occupancy cost $U$) embedded within a correlated conduction bath defined on a square lattice (see Fig.~\hyperref[schematic]{\ref*{schematic}(a)}).
-The impurity site hybridises with the conduction bath sites adjacent to it through one-particle hybridisation $V$ as well as a spin-exchange interaction $J$ arising from fluctuations in local spin densities of the electrons.
-The conduction bath has minimal correlations in the form of a local correlation term $W$ on the sites that are adjacent to the impurity.
-
-The Hamiltonian of the auxiliary model studied here is
-\begin{equation}
-\label{impurityModel}
-\mathcal{H}_\text{aux} = H_\text{imp} + H_\text{coup} + H_\text{cbath},
-\end{equation}
-where the particle-hole symmetric impurity term is
-\begin{equation}
-H_\text{imp} = - \frac{U}{2} \left( \hat{n}_{d \uparrow} - \hat{n}_{d \downarrow} \right)^2,
-\label{localrepulsion}
-\end{equation}
-describing on-site Coulomb interactions at the impurity.
-Here, $c^\dagger_{d\sigma}$ creates an electron with spin $\sigma$ at the impurity site, and $\hat{n}_{d\sigma} = c^\dagger_{d\sigma} c_{d\sigma}$ denotes the corresponding number operator.
-
-The impurity couples to four nearest-neighbour bath sites $c_{Z\sigma}$ through both hybridization and Kondo exchange:
-\begin{equation}\begin{aligned}
-H_\text{coup} = \frac{J}{2} \hspace{-0.25cm}\sum_{\sigma_1,\sigma_2,Z} 
-%\sum_{Z} 
-{\bf S}_d \cdot c^\dagger_{Z\sigma_1} {\boldsymbol \tau}_{\sigma_1 \sigma_2} c_{Z\sigma_2} 
-- V \sum_{\sigma,Z} \left( c^\dagger_{Z\sigma} c_{d\sigma} + \text{h.c.} \right),    
-\end{aligned}
-\label{impbathcoup}\end{equation}
-where ${\boldsymbol \tau}$ are the Pauli matrices, and $Z$ indexes the four neighbouring bath sites.
-The half-filled bath includes nearest neighbour hopping and on-site correlations on the site neighbouring the impurity:
-\begin{equation}
-H_\text{cbath} = \sum_{\bf k} \epsilon_{\bf k} c^\dagger_{{\bf k},\sigma} c_{{\bf k},\sigma} - \frac{W}{2} \sum_{Z} \left( \hat{n}_{Z\uparrow} - \hat{n}_{Z\downarrow} \right)^2,
-\label{bathke}
-\end{equation}
-where $\epsilon_{\bf k} = -2t(\cos k_x + \cos k_y)$, and $W$ parametrizes local repulsion in the bath that frustrates Kondo screening and drives the system towards local-moment formation.
-A crucial feature of this construction is that the Kondo coupling acquires a momentum structure upon Fourier transforming:
-\begin{equation}
-J_{{\bf k}, {\bf k}^\prime} = \frac{J}{2} \left[ \cos(k_x - k^\prime_x) + \cos(k_y - k^\prime_y) \right],
-\end{equation}
-which respects the $C_4$ symmetry of the square lattice.
-
-\subsection{The unitary renormalisation group method}
-In order to obtain the various low-energy phases of our impurity model, we perform a scaling analysis of the associated Hamiltonian using the recently developed unitary renormalisation group (URG) method ~[19,39,40].
-%\cite{anirbanurg1,anirbanurg2}. 
-The method has been applied successfully on a wide variety of problems of correlated fermions~\cite{santanukagome,1dhubjhep1,anirbanmott1,siddharthacpi,anirban_kondo,Patra_2023}.
-The method proceeds by resolving quantum fluctuations in high-energy degrees of freedom, leading to a low-energy Hamiltonian with renormalised couplings and new emergent degrees of freedom.
-Typically, for a system with Fermi energy \(\epsilon_F\) and bandwidth \(E_N\), the sequence of isoenergetic shells \(\left\{E_{(j)}\right\}, E_{j}\in \left[E_0, E_N\right] \) define the states whose quantum fluctuations we sequentially resolve.
-The momentum states lying on shells \(E_N\) that are far away from the Fermi surface comprise the UV states, while those on shells near the Fermi surface comprise the IR states.
-
-As a result of the URG transformations, the Hamiltonian \(H_{(j)}\) at a given RG step \(j\) involves scattering processes between the \(k-\)states that have energies lower than \(D_{(j+1)}\).
-The unitary transformation \(U_{(j)}\) is then defined so as to remove the number fluctuations of the currently most energetic set of states \(D_{(j)}\)~\cite{anirbanurg1,anirbanurg2}:
-\begin{eqnarray}
-	H_{(j-1)} = U_{(j)} H_{(j)} U^\dagger_{(j)}~, \text{such that} ~\left[H_{(j-1)}, \hat n_{j}\right] =0~.
-\end{eqnarray}
-The eigenvalue of $\hat{n}_{j}$ has, thus, been rendered an integral of motion (IOM) under the RG transformation.
-
-The unitary transformations can be expressed in terms of a generator \(\eta_{(j)}\) that has fermionic algebra~\cite{anirbanurg1,anirbanurg2}:
-\begin{eqnarray}
-	\label{unitary}
-	U_{(j)} = \frac{1}{\sqrt 2}\left(1 + \eta_{(j)} - \eta_{(j)}^\dagger\right)~,~ \quad\left\{ \eta_{(j)},\eta_{(j)}^\dagger \right\} = 1~,
-\end{eqnarray}
-where \(\left\{\cdot\right\}\) is the anticommutator.
-The unitary operator \(U_{(j)}\) that appears in Eq.~\eqref{unitary} can be cast into the well-known general form \(U = e^\mathcal{S}, \mathcal{S} = \frac{\pi}{4}\left( \eta^\dagger_{(j)} - \eta_{(j)} \right)\) that a unitary operator can take, defined by an anti-Hermitian operator \(\mathcal{S}\).
-The generator \(\eta_{(j)}\) is given by the expression\cite{anirbanurg1,anirbanurg2}
-\begin{eqnarray}
-	\eta^\dagger_{(j)} = \frac{1}{\hat \omega_{(j)} - \text{Tr}\left(H_{(j)} \hat n_{j}\right) } c^\dagger_{j} \text{Tr}\left(H_{(j)}c_{j}\right)~.
-\end{eqnarray}
-The operators \(\eta_{(j)},\eta^\dagger_{(j)}\) behave as the many-particle analogues of the single-particle field operators \(c_j,c^\dagger_j\) - they change the occupation number of the single-particle Fock space \(\ket{n_j}\).
-The important operator \(\hat \omega_{(j)}\) originates from the quantum fluctuations that exist in the problem because of the non-commutation of the kinetic energy terms and the interaction terms in the Hamiltonian:
-\begin{eqnarray}
-	\hat \omega_{(j)} = H_{(j-1)} - H^i_{(j)}~.
-	\label{omega}
-\end{eqnarray}
-\(H^i_{(j)}\) is the part of \(H_{(j)}\) that commutes with \(\hat n_j\) but does {\it not} commute with at least one \(\hat n_l\) for \(l < j\).
-The RG flow continues up to energy \(D^*\), where a fixed point is reached from the vanishing of the RG function.
-Detailed comparisons of the URG with other methods (e.g., the functional RG, spectrum bifurcation RG etc.) can be found in Refs.~\cite{anirbanmott1,anirbanurg1}, and implementation on the present problem in  Appendix A.
-
-\section{Tiling formalism}\label{tilingsection}
-\subsection{Reconstructing of lattice model from auxiliary model}
-To reconstruct a translationally invariant lattice Hamiltonian from the impurity model (with Hamiltonian $\mathcal{H}_\text{aux}$), we define a many-body tiling prescription that embeds the auxiliary impurity system uniformly across the two-dimensional square lattice.
-Thus, the tiling process systematically derives the full lattice dynamics from the renormalized fixed-point structure of the impurity.
-As described in Section~\ref{auxurgsection}, the auxiliary model consists of a single impurity embedded in a correlated bath at the location $\mathbf{r}_d$:
-\begin{equation}
-H(\mathbf{r}_d) = H_{\text{imp}} + H_{\text{cbath}} + H_{\text{imp-cbath}}~.
-\label{auxmodel}
-\end{equation}
-The form of various terms in eq.\eqref{auxmodel}
-have been defined in eqs.\eqref{localrepulsion}, \eqref{impbathcoup} and \eqref{bathke} in Section~\ref{auxurgsection}.
-% where the impurity, conduction bath and impurity–bat Hamiltonians are defined as
-% \begin{equation}
-% \begin{aligned}
-% H_{\text{imp}} &= -\frac{U}{2} \left( \hat{n}_{\mathbf{r}_d\uparrow} - \hat{n}_{\mathbf{r}_d\downarrow} \right)^2,\\
-% H_{\text{cbath}} &= -\frac{1}{\sqrt{\mathcal{Z}}} t \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle \ne \mathbf{r}_d; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
-% &- \frac{1}{2\mathcal{Z}} W \sum_{\mathbf{z} \in \text{NN}(\mathbf{r}_d)} \left( \hat{n}_{\mathbf{z}\uparrow} - \hat{n}_{\mathbf{z}\downarrow} \right)^2,\\
-% H_{\text{imp-cbath}} &= \frac{J}{\mathcal{Z}} \sum_{\sigma, \sigma'} \sum_{\mathbf{z} \in \text{NN}(\mathbf{r}_d)} \mathbf{S}_{\mathbf{r}_d} \cdot \boldsymbol{\tau}_{\sigma \sigma'} c^\dagger_{\mathbf{z}\sigma} c_{\mathbf{z}\sigma'} \\
-% &- \frac{V}{\sqrt{\mathcal{Z}}} \sum_{\sigma} \sum_{\mathbf{z} \in \text{NN}(\mathbf{r}_d)} \left( c^\dagger_{\mathbf{r}_d\sigma} c_{\mathbf{z}\sigma} + \text{h.c.} \right).
-% \end{aligned}
-% \end{equation}
-% $\boldsymbol{\tau} = (\tau_x, \tau_y, \tau_z)$ are Pauli matrices, and ${\bf r}_d$ denotes the impurity position.
-
-The tiled lattice Hamiltonian is generated by symmetrically translating this impurity model:
-\begin{equation}
-\mathcal{H}_{\text{tiled}} = \mathcal{T}[H(\mathbf{r}_d)] = \sum_{\mathbf{r}} T^\dagger(\mathbf{r} - \mathbf{r}_d) H(\mathbf{r}_d) T(\mathbf{r} - \mathbf{r}_d),
-\end{equation}
-where $T(\mathbf{a})$ are many-body translation operators~\cite{stoyanova}:
-\begin{equation}
-T^\dagger(\mathbf{a}) \mathcal{O}(\{\mathbf{r}_i\}) T(\mathbf{a}) = \mathcal{O}(\{\mathbf{r}_i + \mathbf{a}\}).
-\end{equation}
-Applying this to each term yields:
-\begin{equation}\hspace{-0.5cm}\begin{aligned}
-\mathcal{T}[H_{\text{cbath}}] &= -\frac{(N - 2)t}{\sqrt{\mathcal{Z}}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
-&- \frac{1}{2} W \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2, \\
-\mathcal{T}[H_{\text{imp}}] &= -\frac{U}{2} \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2, \\
-\mathcal{T}[H_{\text{imp-cbath}}] &= \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle} \left[ \frac{2J}{\mathcal{Z}} \mathbf{S}_{\mathbf{r}_i} \cdot \mathbf{S}_{\mathbf{r}_j} - \frac{2V}{\sqrt{\mathcal{Z}}} \sum_\sigma \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \right],
-\end{aligned}\end{equation}
-with local spin operators defined as
-\begin{equation}
-\mathbf{S}_{\mathbf{r}} = \sum_{\sigma, \sigma'} c^\dagger_{\mathbf{r}\sigma} \boldsymbol{\tau}_{\sigma \sigma'} c_{\mathbf{r}\sigma'}.
-\end{equation}
-
-To avoid overcounting of the non-interacting bath terms, we subtract extra copies of the kinetic energy term. The reconstructed extended–Hubbard model then reads:
-\begin{equation}
-\begin{aligned}
-\mathcal{H}_{\text{tiled}} = & -\frac{1}{\sqrt{\mathcal{Z}}} \tilde{t} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle; \sigma} \left( c^\dagger_{\mathbf{r}_i\sigma} c_{\mathbf{r}_j\sigma} + \text{h.c.} \right) \\
-&+ \frac{\tilde{J}}{\mathcal{Z}} \sum_{\langle \mathbf{r}_i, \mathbf{r}_j \rangle} \mathbf{S}_{\mathbf{r}_i} \cdot \mathbf{S}_{\mathbf{r}_j} - \frac{1}{2} \tilde{U} \sum_{\mathbf{r}} \left( \hat{n}_{\mathbf{r}\uparrow} - \hat{n}_{\mathbf{r}\downarrow} \right)^2,
-\end{aligned}
-\end{equation}
-where the effective lattice couplings are given by:
-\begin{equation}
-\tilde{t} = t + 2V,\quad \tilde{U} = U + W,\quad \tilde{J} = 2J.
-\end{equation}
-% \end{widetext}
-
-A non-zero chemical potential in the bath and/or the impurity can be included to study the effects of doping.
-Crucially, the eigenstates of $\mathcal{H}_\text{tiled}$ obey a many-body generalization of Bloch’s theorem~\cite{stoyanova}, which allows for the exact computation of momentum-resolved observables (presented here for a $77\times 77$ {\bf k}-space Brillouin zone grid).
-We shall demonstrate below that the lattice embedding and tiling procedures provide a controlled route to capture low-energy NFL behavior and Mott criticality directly from a quantum impurity model.
-
-\subsection{Mapping eigenstates using a manybody Bloch's theorem}
-As mentioned above, the eigenstates \(\ket{\Psi_{s}}\) (\(s = \left({\bf k}, n\right)\)) of the lattice Hamiltonians obtained using  the tiling procedure enjoy a {\it many-body} Bloch's theorem~\cite{stoyanova}, as the tiling procedure restores the translation symmetry of the Hamiltonian.
-This means that the {\it local} eigenstates \(\ket{\psi_n\left({\bf r}_d\right)}\) (with the impurity located at an arbitrary position \({\bf r}_d\)) of the unit cell auxiliary model Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) can be used to construct eigenstates of the lattice Hamiltonian.
-The index \(n(=0,1,\ldots)\) in the subscript indicates that it is the \(n^\text{th}\) eigenstate of the auxiliary model.
-
-The state \(\ket{\psi_n\left({\bf r}_d\right)}\) does not specify the position of the zeroth site, because the unit cell Hamiltonian \(\mathcal{H}_\text{aux}({\bf r}_d)\) itself has been averaged over \(\mathcal{Z}\) zeroth sites.
-Accordingly, we can express the averaged eigenstate \(\ket{\psi_n\left({\bf r}_d\right)}\) as
-\begin{equation}\begin{aligned}
-	\ket{\psi_n\left({\bf r}_d\right)} = \frac{1}{\sqrt\mathcal{Z}}\sum_{{\bf z} \in \text{NN}({\bf r}_d)}\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}~,
-\end{aligned}\end{equation}
-where \(\ket{\psi_n\left({\bf r}_d, {\bf z}\right)}\) is an auxiliary model eigenstate with the impurity and zeroth sites placed at \({\bf r}_d\) and \({\bf z}\).
-With this in mind, the following unnormalised combination of the auxiliary model eigenstates satisfies a many-particle equivalent of Bloch's theorem~[53]:
-%\cite{stoyanova}:
-\begin{equation}\begin{aligned}\label{eigenstateProposal1}
-	\ket{\Psi_{s}} \equiv \ket{\Psi_{{\bf k}, n}} &= \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_{n}\left({\bf r}_d\right)} \\
-\end{aligned}\end{equation}
-where \(N\) is the total number of lattice sites and \({\bf r}_d\) is summed over all lattice spacings.
-The set of \(n=0\) states form the lowest band in the spectrum of the lattice, while higher values of \(n\) produce the more energetic bands.
-The ground state \(s = s_0\) is obtained by setting \({\bf k}\) and \(n\) to 0:
-\begin{equation}\begin{aligned}\label{groundstateProposal1}
-	\ket{\Psi_\text{gs}} = \frac{1}{\sqrt N}\sum_{{\bf r}_d} e^{i {\bf k}\cdot{\bf r}_d} \ket{\psi_\text{gs}\left({\bf r}_d\right)}
-\end{aligned}\end{equation}
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{fig2.pdf}
-    \caption{(a) Phase diagram of impurity model at strong coupling in $U$ in terms of competing dimensionless Kondo ($J/t$) and bath correlation ($W/t$) couplings.
-Colourbar represents the fraction of states on the Fermi surface replaced by zeros of the Greens function (Luttinger surface).
-A pseudogap phase (shaded region) is observed between the local Fermi liquid (red region) and local moment (blue region) phases (b) $k$-space-resolved spin-spin correlation $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$ in the pseudogap phase of the impurity model.
-Antinodal regions are observed to decouple from Kondo screening of the impurity.
-(c) Upon tiling, this leads to a $k$-space-resolved antinodal gap in the electronic density of states of the lattice model, corresponding to Luttinger surfaces of zeros.}
-    \label{spinCorr}
-%    \label{spinCorr:b}
-%    \label{spinCorr:c}
-\end{figure*}
-
-\subsection{Mapping the retarded Greens function from auxiliary model to lattice model}
-We now show how to relate the one-particle retarded Greens functions of the bulk lattice to that of the auxiliary model. The retarded time-domain lattice \(k-\)space Greens function is defined as
-\begin{equation}\begin{aligned}
-	\tilde G({\bf K}\sigma; t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c_{{\bf K}\sigma}(t), c^\dagger_{{\bf K}\sigma} \right\} | \Psi_\text{gs}}~.
-\end{aligned}\end{equation}
-where the bulk Hamiltonian \(H_\text{tiled}\) leads to the dynamics of the annihilation operators at time \(t\): 
-\begin{equation}\begin{aligned}\label{heisenberg}
-	c_{{\bf K}\sigma}(t) = e^{it H_\text{tiled} }c_{{\bf K}\sigma}e^{-i t H_\text{tiled}}~.
-\end{aligned}\end{equation}
-We now proceed to simplify one of the terms of the anticommutator (for simplicity of notation):
-\begin{equation}\begin{aligned}\label{greensFunction1}
-	&\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} \\
-    &= \frac{1}{N^2}\sum_{\vec r,\vec \Delta}e^{-i{\bf K}_0\cdot\vec\Delta}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-Using eq.~\eqref{eigenstateProposal1}, eq.~\eqref{greensFunction1} becomes
-\begin{widetext}
-	\begin{equation}\begin{aligned}\label{greensfunction2}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N^2}\sum_s\sum_{\vec r,\vec \Delta}\sum_{\vec r^\prime,\vec \Delta^\prime}e^{-i\vec k_0\cdot\vec\Delta} e^{i\vec k\cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r+\vec \Delta) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-In order to bring this expression closer to the form of an auxiliary model Greens function, we
-\begin{itemize}
-    \item use the relation $\ket{\psi(\vec r + \Delta)} = T^\dagger(\vec \Delta)\ket{\psi(\vec r)}$, where \(T^\dagger(\vec \Delta)\) translates all lattice sites by the vector \(\vec\Delta\)~,
-    \item use the property $T\left(\vec a\right) c({\bf K}) T^\dagger\left(\vec a\right) = e^{-i{\bf K}\cdot\vec a}c({\bf K})$~, and
-    \item make the substitution \(\vec \Delta^\prime \to \vec \Delta^\prime + \vec \Delta\)~.
-\end{itemize}
-This leads to the expression
-\begin{equation}\begin{aligned}\label{greensfunction3}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~,
-\end{aligned}\end{equation}
-where the sum over \(s=(\vec k, n)\) has been reduced to a sum over the auxiliary model eigenstate index \(n\) because of the Kronecker delta \(\delta\left(\vec k_0 + {\bf K} - \vec k\right)\).
-This can be further simplified by splitting the sum over \(\vec\Delta^\prime\) into positive and negative parts and then making the transformation \(\vec r^\prime \to \vec r^\prime + \vec \Delta^\prime\):
-\begin{equation}\begin{aligned}
-	&\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime-\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)}\right]~, \\
-																																												   &= \frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} + e^{-i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime)}\bra{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\right]~.
-\\
-\end{aligned}\end{equation}
-For each pair of \(\vec r^\prime\) and \(\vec\Delta^\prime\), the term within the box brackets has the form of a two-level Hamiltonian between the states \(\ket{\psi_n(\vec r^\prime)}\) and \(\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\), with a tunnelling amplitude \(e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\).
-The term can therefore be written in the eigenbasis of this Hamiltonian:
-\begin{equation}\begin{aligned}
-	\sum_{\vec r^\prime,\vec \Delta^\prime} e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime+\vec \Delta^\prime)}\bra{\psi_n(\vec r^\prime)} &=\frac{1}{2}\sum_{\vec r^\prime,\vec \Delta^\prime}\left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right],
-\end{aligned}\end{equation}
-where \(\ket{\chi_n^\pm(\vec r^\prime,\vec\Delta^\prime)} = \frac{1}{\sqrt 2}\left[\ket{\psi_n(\vec r^\prime)} \pm e^{i\left( \vec k_0 + {\bf K} \right) \cdot\vec\Delta^\prime}\ket{\psi_n(\vec r^\prime + \vec\Delta^\prime)}\right] \) are the eigenvectors of the tunnelling Hamiltonian with eigenvalues \(\pm 1\) respectively.
-With this basis transformation, we can rewrite eq.~\eqref{greensfunction3} as
-\begin{equation}\begin{aligned}
-		\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} = \frac{1}{2N}\sum_n\sum_{\vec r,\vec r^\prime,\vec \Delta^\prime} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \left[ \ket{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^+(\vec r^\prime,\vec\Delta^\prime)} - \ket{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\bra{\chi_n^-(\vec r^\prime,\vec\Delta^\prime)}\right] c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)}~.
-\end{aligned}\end{equation}
-\end{widetext}
-
-In the present work, we consider only the $\vec r^\prime = \vec r,~\vec\Delta^\prime=0$ component.
-These terms represent those contributions to the total Greens function that arise from excitations that start and end at a specific auxiliary model (at \(\vec r\)), and also evolve dynamically within the same auxiliary model.
-These terms are therefore exactly equal to the auxiliary model Greens function at position \(\vec r\), and are the most dominant contribution due to the localised nature of the impurity model.
-Thus, restricting ourselves to just the single auxiliary model contributions gives
-\begin{equation}\begin{aligned}
-		&\braket{\Psi_\text{gs} | c_{{\bf K}\sigma}(t) c^\dagger_{{\bf K}\sigma} | \Psi_\text{gs}} =\\
-        &\frac{1}{N}\sum_{n, {\vec r}} \braket{\psi_{0}(\vec r) | c_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} c^\dagger_{{\bf K}\sigma} | \psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-
-We now consider more carefully the transition operator \(\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\) for the 1-particle excitation giving rise to the above Greens function.
-Within our auxiliary model approach, gapless excitations within the lattice model are represented by gapless excitations of the impurity site, specifically those that screen the impurity site and form the local Fermi liquid.
-As a result, the uncoordinated \(\mathcal{T}-\)matrix for the lattice model must be replaced by a combined \(\mathcal{T}-\)matrix within the impurity model that captures those gapless excitations that occur in connection with the impurity, and projects out the uncorrelated excitations that take place even when the impurity site is decoupled from the bath.
-
-In order to construct this auxiliary model \(\mathcal{T}-\)matrix, we note that the impurity site can have both spin and charge excitations.
-Considering both excitations, the modified \(\mathcal{T}-\)matrix that constructs \(k-\)space excitations in correlation with the impurity site are
-\begin{equation}\begin{aligned}\label{tmatrix}
-	\mathcal{T}_{{\bf K}\sigma} = c_{{\bf K}\sigma}\left(\sum_{\sigma^\prime}c^\dagger_{d\sigma} + \text{h.c.}\right) + c_{{\bf K}\sigma}\left(S_d^+ + \text{h.c.}\right)~,
-\end{aligned}\end{equation}
-leading to the updated expression for the complete Greens function:
-\begin{equation}\begin{aligned}
-	\tilde G&({\bf K}\sigma; t) \\
-    =& \frac{-i\theta(t)}{N}\sum_{n, \vec{r}} \bra{\psi_{0}(\vec r)} \left[\mathcal{T}_{{\bf K}\sigma}(t) \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}^\dagger \right. \\
-    &\left. + \mathcal{T}^\dagger_{{\bf K}\sigma} \ket{\psi_n(\vec r)}\bra{\psi_n(\vec r)} \mathcal{T}_{{\bf K}\sigma}(t)\right] \ket{\psi_{0}(\vec r)} ~.
-\end{aligned}\end{equation}
-\begin{figure}[!th]
-    \centering
-    \includegraphics[width=0.49\linewidth]{tiled-SF-3.pdf}
-    \includegraphics[width=0.49\linewidth]{tiled_I2_k_N_2000-3.pdf}
-    \caption{Left: Spin correlations \(\chi_s\) for the {\it tiled model}, between the nodal point \(k_N = \left( -\pi/2, -\pi/2\right)\) and an arbitrary \(k-\)point on the Fermi surface.
-In the PG, the spin-correlations near the antinode vanish, indicating that they have been removed from the metallic excitations, while the correlations near the nodal point become enhanced because of the increasingly correlated nature of the metal.
-Right: Mutual information \(I_2\) between an arbitrary \(k-\)state and the nodal point.
-The nodal points remain strongly entangled with each other all the way through the PG.}
-    \label{tiledEntanglement}
-\end{figure}
-
-\begin{figure*}[!th]
-    \centering
-    \includegraphics[width=\textwidth]{fig2.5.png}
-    \caption{Initiation of the decoupling of $J_{{\bf k}, {\bf k'}}$ (positive, negative and zeros shown in red, blue and white respectively), with ${\bf k}$ (black circle) at low-energies for ${\bf k}$ corresponding to the node (a), antinode (b) and a point mid-way between them (c) on the top right arm of the FS respectively with tuning $W/J$.
-As dictated by the symmetry of $J_{{\bf k}, {\bf k'}}$, the decoupling for a given ${\bf k}$ proceeds via the appearance of zeros (white patches) of $J_{{\bf k}, {\bf k'}}$ for ${\bf k'}$ initially on the nodal regions of adjacent arms, and progresses gradually towards the antinodes.
-The decoupling ends with the onset of the pseudogap.}
-    \label{unravelling}
-%    \label{unravelling:b}
-%    \label{unravelling:c}
-\end{figure*}
-\section{Pseudogap Formation via Kondo Breakdown}
-
-\subsection{RG Phase Diagram}
-A detailed picture of the PG in the impurity model is obtained from a momentum-resolved breakdown of Kondo screening in the strong-coupling regime $U \gg t$ phase of $H_\text{aux}$.
-A unitary renormalisation group (URG) scaling analysis~\cite{anirbanurg1} obtains a flow equation of the Kondo coupling \(J^{(j)}_{{\bf k}_1, {\bf k}_2}\) (see Appendix A for details)
-\begin{equation}\begin{aligned}\label{KondoRGequation}
-	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}~,
-\end{aligned}\end{equation}
-where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, the sum is over all occupied momentum states \({\bf q}\) of the energy shell \(\varepsilon_j\), and  \({\bf \bar q} = {\bf q} + {\boldsymbol \pi}\) is the particle-hole transformed state associated with ${\bf q}$.
-The bath interaction coupling $W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}$ is found to be marginal under these transformations.
-While we present a detailed numerical evaluation of the RG equation for $J_{{\bf k}_1, {\bf k}_2}$ (eq.\eqref{KondoRGequation}) below, it is clear that the frustration of Kondo screening due to charge fluctuations (for attractive bath interactions $W<0$) leads to the Mott transition~\cite{Mukherjee_2023}.
-
-A detailed numerical computation of the URG equation in eq.~\eqref{KondoRGequation} leads to the phase diagram shown in Fig.~\hyperref[spinCorr]{\ref*{spinCorr}(a)}.
-Upon tuning the ratio of the bath and Kondo interactions ($W/J$) from zero to negative values, the following phases emerge in the impurity model from the competition between $J$ and $W$ in eq.~\eqref{KondoRGequation}: (i) for $W/J<(W/J)_{\text{PG}}$, an LFL phase (red region), where the entire FS participates in Kondo screening, (ii) for $\frac{W}{J} \in [(\frac{W}{J})_{\text{PG}}, (\frac{W}{J})_c]$ (shaded region), a local PG phase where disconnected parts of the FS around the node participate in Kondo screening, and (iii) a local moment phase for $\frac{W}{J} > (\frac{W}{J})_c$ (blue region), where the impurity remains unscreened at low-energies.
-These can be visualised from spin correlations, $\chi_s(d,{\bf k}) = \braket{{\bf S}_d\cdot{\bf S}_{\bf k}}$~, as shown in Fig.~\hyperref[spinCorr]{\ref*{spinCorr}(b)} for the PG.
-The values $(W/J)_{\text{PG}}$ and $(W/J)_c$ are therefore the entry into and exit from the PG phase.
-
-Mapping onto the lattice model via tiling, we observe that RG-induced nodal–antinodal dichotomy in $J_{{\bf k}, {\bf k}^\prime}$ in the impurity model is the microscopic origin of the PG in the lattice model: the extinction of Kondo coherence translates into spectral zeros in the lattice Green’s function (i.e., Luttinger surfaces) at antinodal momenta (Fig.~\hyperref[spinCorr]{\ref*{spinCorr}(c)}).
-This establishes that the $T=0$ Mott transition of the 2D \textit{extended}-Hubbard model proceeds from FL to MI through an intervening PG phase.
-In Fig.~\ref{tiledEntanglement}, similar insights obtain from the spin-correlation $\chi_s({\bf k},k_N) = \braket{{\bf S}_{\bf k}\cdot{\bf S}_{k_N}}$ in $k-$space (where $k_N$ is the nodal momentum) and mutual information $I_2({\bf k}:k_N)$ between two momentum states: the PG displays Fermi arcs in the nodal regions along with vanishing correlation and entanglement in the antinodal regions.
-
-\subsection{Unravelling of Kondo Screening}
-The ${\bf k}$-space anisotropy of Kondo breakdown can be visualized in terms of zeros of $J_{{\bf k}_N, {\bf k}}$, involving spin-flip scattering between the node ${\bf k}_N = (\pi/2, \pi/2)$  and a general wavevector ${\bf k}$.
-For any $W/J$, the $\mathcal{C}_{4}$ lattice symmetry dictates that $J_{{\bf k}_N, {\bf k}}$ vanishes if ${\bf k}$ belongs to any of the antinodes or adjacent nodes.
-Tuning $W/J$ towards $(W/J)_{\text{PG}}$ leads to an unravelling of the Kondo screening: $J_{{\bf k}_N, {\bf k}}$ for ${\bf k}$ close to the adjacent nodes turns RG-irrelevant first, and a patch of zeros subsequently appears in $J_{{\bf k}_N, {\bf k}}$ around this point (Fig.~\hyperref[unravelling]{\ref*{unravelling}(a)}).
-Tuning $W/J$ further extends the patch of zeros towards the antinodes (Fig.~\hyperref[unravelling]{\ref*{unravelling}(b)} and \hyperref[unravelling]{\ref*{unravelling}(c)}).
-Kondo screening thus unravels by a systematic decoupling of all $J_{{\bf k}_1, {\bf k}_2}$ that connect adjacent quadrants of the Brillouin zone.
-
 Precisely at $W/J=(W/J)_{\text{PG}}$, the antinode joins this connected region of zeros in $J_{{\bf k}_1, {\bf k}_2}$, marking the decoupling of the antinodes from all other points in the neighbourhood of the FS.
@@
 The 2CK nature of the PG is guaranteed by the symmetry of $J_{{\bf k},{\bf k'}}$:
-\begin{equation}
-\begin{aligned}
-J_{{\bf k},{\bf k'}}= -J_{{\bf k}+{\bf Q},{\bf k'}}=-J_{{\bf k},{\bf k'}+{\bf Q}}, \quad {\bf Q} = (\pi,\pi).
-\end{aligned}
-\end{equation}
-The PG expands by shrinking these disconnected Fermi arcs towards the respective nodes, leading to nodal metals whose disappearance heralds the Mott transition.
 
@@
 This signals the NFL Fermi arcs of the PG as an emergent phase of strongly interacting quantum matter - which we dub the {\it Mott metal} - that is the parent metal of the MI.
-The same topological principle connects the nonlocal unparticle-like gapless excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} of the scale-invariant nodal NFL of the HK model observed precisely at the Mott critical point to those of the rest of the PG phase, e.g., a universal scaling of $\Sigma''_{{\bf k}}(\omega)\sim (a + \omega^{2})^{-1}$ (Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(b)}) and local density of states $A_{d}(\omega) \sim \omega^{2}$ (Fig.~\hyperref[ImpSpecFuncFits]{\ref*{ImpSpecFuncFits}}) of the NFL throughout the PG phase, such that the value of $\Sigma''_{{\bf k}}(\omega=0)$ value continues to grow upon violating the MIR bound (Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(c)}).
+The same topological principle connects the nonlocal unparticle-like gapless excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} of the scale-invariant nodal NFL of the HK model observed precisely at the Mott critical point to those of the rest of
+the PG phase, e.g., a universal scaling of $\Sigma''_{{\bf k}}(\omega)\sim (a + \omega^{2})^{-1}$ (Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(b)}) and local density of states $A_{d}(\omega) \sim \omega^{2}$ (Fig.~\hyperref[ImpSpecFuncFits]{\ref*{ImpSpecFuncFits}}) of the NFL throughout the PG phase, such that the value of $\Sigma''_{{\bf k}}(\omega=0)$ value continues to grow upon violating the MIR bound (Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(c)}).
 
 \section{Conclusions}
-Our analysis reveals that the Mott transition proceeds via a continuous evolution through a PG regime characterized by a singular NFL metal - the Mott metal - with deconfined holon–doublon excitations confined to nodal Fermi arcs, and a scaling of it's spectral features with universal power-law exponents.
-As the system approaches criticality, this metallic phase exhibits increasingly non-local correlations and a divergent self-energy, signalling the breakdown of Landau quasiparticles, formation of local moments and the onset of long-range quantum entanglement.
+Our analysis reveals that the Mott transition proceeds via a continuous evolution through a PG regime characterized by a singular NFL metal - the Mott metal - with deconfined holon–doublon excitations confined to nodal Fermi arcs.
+, and a scaling of it's spectral features with universal power-law exponents. 
+As the system approaches criticality, this metallic phase exhibits increasingly non-local correlations and a divergent self-energy, signaling the breakdown of Landau quasiparticles, formation of local moments and the onset of long-range quantum entanglement.
 Anchored in two-channel Kondo dynamics at intermediate scales and governed by Hatsugai–Kohmoto physics near the critical endpoint, the Mott metal provides a unified framework for understanding anomalous metallicity in strongly correlated systems.
 It's fate under finite doping presents a compelling direction for future investigation.
-
-\bibliography{tilingProject}
-
-\section*{Acknowledgments}
-We acknowledge National Supercomputing Mission (NSM) for providing computing resources of ‘PARAM RUDRA’ at Aruna Asaf Ali Marg, near Vasant Kunj, Vasant Kunj, New Delhi, Delhi 110067, which is implemented by C-DAC and supported by the Ministry of Electronics and Information Technology (MeitY) and Department of Science and Technology (DST), Government of India.
-SL thanks the SERB, Govt.
-of India for funding through MATRICS grant MTR/2021/000141 and Core Research Grant CRG/2021/000852.
-AM thanks IISER Kolkata for funding through a JRF and an SRF.
-A.M.
-would also like to acknowledge the SERB-MATRICS grant (Grant No.
-MTR/2022/000636) from the Science and Engineering Research Board (SERB) for funding.
-S.L.
-thanks Mayank Shreshtha for designing Fig.1, and Deepshikha Jaiswal-Nagar for comments on the manuscript.
-
-\section{Code and Data availability}
-The codes created during this research are available from the corresponding author upon reasonable request.
-
-\clearpage
-\begin{widetext}
-\appendix
-
-\section{Derivation of unitary RG equations for the lattice-embedded impurity model}
-Following Refs.~\cite{anirbanmott1,anirbanurg1}, at any given step \(j\) of the RG procedure, we decouple the states \(\left\{ {\bf q} \right\} \) on the isoenergetic surface of energy \(\varepsilon_j\).
-The diagonal Hamiltonian \(H_D\) for this step consists of all terms that do not change the occupancy of the states \(\left\{{\bf q}\right\}\):
-\begin{equation}\begin{aligned}
-	H_D^{(j)} = \varepsilon_j\sum_{q,\sigma}\tau_{q,\sigma} + \frac{1}{2}\sum_{{\bf q}}J_{{\bf q}, {\bf q}}S_d^z\left(\hat n_{{\bf q}, \uparrow} - \hat n_{{\bf q}, \downarrow}\right) - \frac{1}{2}\sum_{{\bf q}}W_{\bf q}\left(\hat n_{{\bf q}, \uparrow} - \hat n_{{\bf q}, \downarrow}\right)^2~,
-\end{aligned}\end{equation}
-where \(\tau = \hat n - 1/2\) and \(W_{{\bf q}}\) is a shorthand for \(W_{{\bf q},{\bf q},{\bf q},{\bf q}}\).
-The three terms, respectively, are the kinetic energy of the momentum states on the isoenergetic shell that we are decoupling, the spin-correlation energy between the impurity spin and the spins formed by these momentum states and, finally, the local correlation energy associated with these states arising from the \(W\) term.
-The off-diagonal part of the Hamiltonian on the other hand leads to scattering in the states \(\left\{ {\bf q} \right\} \).
-
-The renormalisation of the Hamiltonian is constructed from the general expression~~\cite{anirbanmott1,anirbanurg1}
-\begin{equation}\begin{aligned}
-	\Delta H^{(j)} = H_X \frac{1}{\omega- H_D} H_X~.
-\end{aligned}\end{equation}
-
-\subsection{Renormalisation of the bath correlation term {\it W}}
-The bath correlation term \(W\) can undergo renormalisation only via scattering processes arising from itself.
-Irrespective of whether the state \({\bf q}\) being decoupled is in a particle or hole configuration in the initial many-body state, the propagator \(G = 1/(\omega - H_D)\) of the intermediate excited state is uniform, and equal to
-\begin{equation}\begin{aligned}\label{propagatorW}
-	G_W = 1/\left(\omega - |\varepsilon_j|/2 + W_{\bf q}/2)\right)~,
-\end{aligned}\end{equation}
-where \(W_{\bf q}\) is the same whether \({\bf q}\) is above or below the Fermi surface.
-The \(|\varepsilon_j|/2\) in \(H_D\) arises from the excited nature of the state after the initial scattering process.
-
-\subsubsection{Scattering arising purely from spin-preserving processes}
-%\subsubsection*{Scattering arising purely from spin-preserving processes}
-One possible set of processes gives
-\begin{equation}\begin{aligned}
-	T_{P1}^\dagger G_W T_{P3} = -\sum_\sigma\sum_{{\bf k}_1, {\bf k}_2, {\bf k}_3, {\bf k}_4} c^\dagger_{{\bf k}_1,\sigma} c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma}    \sum_{\bf q \in \text{PS}} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4} G_W W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}}~.
-\end{aligned}\end{equation}
-
-The second such contribution is obtained by flipping the sequence of scattering processes:
-\begin{equation}\begin{aligned}
-	T_{P3} G_W T_{P1}^\dagger = \sum_\sigma\sum_{{\bf k}_1, {\bf k}_2, {\bf k}_3, {\bf k}_4} c^\dagger_{{\bf k}_1,\sigma} c_{{\bf k}_2,\sigma}c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} \sum_{\bf q \in \text{HS}} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4} G_W W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}}~.
-\end{aligned}\end{equation}
-The product of couplings \(W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf k}_4} G_W W_{{\bf k}_1,{\bf q},{\bf q},{\bf q}}\) is the same irrespective of whether \({\bf q}\) belongs to the particle or hole sector.
-The two contributions therefore cancel each other.
-
-\subsubsection{Scattering arising from spin-flip processes}
-%\subsubsection*{Scattering arising from spin-flip processes}
-We now come to the processes that involve spin-flips. The first class of processes is
-\begin{equation}\begin{aligned}
-	T_{F1}^\dagger G_W T_{F4} &= -\sum_{1,2,3,4}\sum_\sigma c^\dagger_{{\bf k}_1\sigma} c_{{\bf k}_2\sigma} c^\dagger_{{\bf k}_3\bar\sigma} c_{{\bf k}_4\bar \sigma} \sum_{\bf q \in \text{PS}} W_{{\bf q}, {\bf k}_2, {\bf k}_4, {\bf k}_4} G_W W_{{\bf k}_1, {\bf q}, {\bf q}, {\bf q}}~,\\
-	T_{F4} G_W T_{F1}^\dagger &= \sum_{1,2,3,4}\sum_\sigma c^\dagger_{{\bf k}_1\sigma} c_{{\bf k}_2\sigma} c^\dagger_{{\bf k}_3\bar\sigma} c_{{\bf k}_4\bar \sigma} \sum_{\bf q \in \text{HS}} W_{{\bf q}, {\bf k}_2, {\bf k}_4, {\bf k}_4} G_W W_{{\bf k}_1, {\bf q}, {\bf q}, {\bf q}}~.
-\end{aligned}\end{equation}
-By the same arguments as in the previous subsection, these terms cancel each other out.
-
-The other two terms also cancel out for the same reason:
-\begin{equation}\begin{aligned}
-	T_{F2} G_W T_{F2} &= \sum_{1,2,3,4}\sum_\sigma c^\dagger_{{\bf k}_1\sigma} c_{{\bf k}_2\sigma} c^\dagger_{{\bf k}_3\bar\sigma} c_{{\bf k}_4\bar \sigma} \sum_{\bf q \in \text{PS}} W_{{\bf q},{\bf \bar q},{\bf k}_3,{\bf k}_4} G_W W_{{\bf \bar q},{\bf q},{\bf k}_1,{\bf k}_2}~,\\
-	T_{F3} G_W T_{F3} &= -\sum_{1,2,3,4}\sum_\sigma c^\dagger_{{\bf k}_1\sigma} c_{{\bf k}_2\sigma} c^\dagger_{{\bf k}_3\bar\sigma} c_{{\bf k}_4\bar \sigma} \sum_{\bf q \in \text{PS}} W_{{\bf q},{\bf k}_2,{\bf k}_3,{\bf \bar q}} G_W W_{{\bf \bar q},{\bf k}_4,{\bf k}_1,{\bf q}}~,
-\end{aligned}\end{equation}
-
-\subsubsection{Scattering involving both spin-flip and spin-preserving processes}
-%\subsubsection*{Scattering involving both spin-flip and spin-preserving processes}
-These processes involve the combination of terms like \(T_{P1}\) with \(T_{F4}\), and \(T_{P2}\) with \(T_{F1}\). These again cancel each other out for the same reasons as outline above.
-
-\subsubsection{Net renormalisation for the bath correlation term}
-Since all the contributions cancel out in pairs, the bath correlation term \(W\) is {\it marginal}.
-
-\subsection{Renormalisation of the Kondo scattering term {\it J}}
-We focus on the renormalisation of the spin-flip part of the Kondo interaction.
-For these processes, the intermediate many-body state always involves the impurity spin being anti-correlated with the conduction electron spin, such that the propagator for that state is \(G_J = 1/\left(\omega - |\varepsilon_j|/2 + J_{\bf q}/4 + W_{\bf q}/2)\right) \).
-
-\subsubsection{Impurity-mediated spin-flip scattering purely through Kondo-like processes}
-%\subsubsection*{Impurity-mediated spin-flip scattering purely through Kondo-like processes}
-The following processes arising from the Kondo term renormalise the spin-flip interaction:
-\begin{equation}\begin{aligned}\label{kondoRenorm1}
-	T^\dagger_{KT1} G_J \left(T_{KZ1} + T_{KZ1}^\dagger\right) &= -\frac{1}{8}\sum_{{\bf k}_1, {\bf k}_1}~ S_d^+ c^\dagger_{{\bf k}_1 \downarrow}c_{{\bf k}_2 \uparrow}\sum_{{\bf q} \in \text{PS}}\left[J_{{\bf q}, {\bf k}_2} J_{{\bf k}_1,{\bf q}} + J_{{\bf \bar q}, {\bf k}_1} J_{{\bf k}_2,{\bf \bar q}} \right]G_J~.
-\end{aligned}\end{equation}
-An identical contribution is obtained by switching the sequence of processes:
-\begin{equation}\begin{aligned}\label{kondoRenorm2}
-	 \left(T_{KZ1} + T_{KZ1}^\dagger\right) G_J T^\dagger_{KT1} &= -\frac{1}{8}\sum_{{\bf k}_1, {\bf k}_1}~ S_d^+ c^\dagger_{{\bf k}_1 \downarrow}c_{{\bf k}_2 \uparrow}\sum_{{\bf q} \in \text{PS}}\left[J_{{\bf \bar q}, {\bf k}_2} J_{{\bf k}_1,{\bf \bar q}} + J_{{\bf q}, {\bf k}_1} J_{{\bf k}_2,{\bf q}} \right]G_J~.
-\end{aligned}\end{equation}
-
-\subsubsection{Scattering processes involving interplay between the Kondo interaction and conduction bath interaction}
-\begin{equation}\begin{aligned}\label{t7t6}
-	T_{KT1}^\dagger G_J \left(T_{F4} + T_{F4}^\dagger\right) &= \frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2,{\bf q}} J_{{\bf k}_2, {\bf q}}S_d^+ \left(c^\dagger_{{\bf q}\downarrow}c_{{\bf k}_2\uparrow}  G_J W_{{\bf q}, {\bf q}, {\bf k}_1, {\bf q}} n_{q \uparrow} c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf q} \downarrow} + c^\dagger_{{\bf k}_2\downarrow}c_{{\bf q}\uparrow}  G_J W_{{\bf \bar q}, {\bf \bar q}, {\bf q}, {\bf k}_1} n_{\bar q \downarrow} c^\dagger_{{\bf q} \uparrow} c_{{\bf k}_1 \uparrow}\right) ~.
-\end{aligned}\end{equation}
-For either of the two choices of the functional form of \(W\), it is easy to show that \(W_{{\bf q}, {\bf q}, {\bf k}_1, {\bf q}} = W_{{\bf \bar q}, {\bf \bar q}, {\bf q}, {\bf k}_1}\).
-\begin{equation}\begin{aligned}\label{KT1F4}
-	T_{KT1}^\dagger G_J \left(T_{F4} + T_{F4}^\dagger\right) &= \frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2,{\bf q}} J_{{\bf k}_2, {\bf q}} W_{{\bf q}, {\bf q}, {\bf k}_1, {\bf q}} G_J S_d^+ \left[-c^\dagger_{{\bf k}_1 \downarrow}c_{{\bf k}_2\uparrow} n_{{\bf q}\downarrow} n_{q \uparrow} + c^\dagger_{{\bf k}_2\downarrow} c_{{\bf k}_1 \uparrow} (1 - n_{{\bf q}\uparrow}) n_{\bar q \downarrow}\right] ~.
-\end{aligned}\end{equation}
-
-Another contribution is obtained by switching the sequence of the scattering processes:
-\begin{equation}\begin{aligned}\label{F4KT1}
-	\left(T_{F4} + T_{F4}^\dagger\right) G_J T_{KT1}^\dagger &= \frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2,{\bf q}} \left(c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf k}_2\uparrow} n_{\bar q \uparrow} (1 - n_{{\bf q} \downarrow}) - c^\dagger_{{\bf k}_2\downarrow}c_{{\bf k}_1 \uparrow}n_{q \downarrow} n_{{\bf q} \uparrow}\right) W_{{\bf q}, {\bf q}, {\bf k}_1, {\bf q}} G_J J_{{\bf k}_2, {\bf q}}S_d^+
-\end{aligned}\end{equation}
-The two contributions (eqs.~\ref{KT1F4} and \ref{F4KT1}) arising from \(T_{KT1}\) cancel each other.
-
-We now consider the other spin-exchange process \(T_{KT2}^\dagger\). One such contribution is
-\begin{equation}\begin{aligned}\label{kondoRenorm3}
-	T_{KT2}^\dagger G_J T_{F3} &= -\frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2} S_d^+ c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf k}_2 \uparrow}\sum_{{\bf q} \in \text{PS}}\left(J_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} + J_{{\bf \bar q}, {\bf q}} W_{{\bf q}, {\bf k}_2, {\bf k}_1, {\bf \bar q}}\right)G_J~.
-\end{aligned}\end{equation}
-An identical contribution is obtained from the reversed term:
-\begin{equation}\begin{aligned}\label{kondoRenorm4}
-	T_{F3}G_J T_{KT2}^\dagger  &= -\frac{1}{2}\sum_{{\bf k}_1,{\bf k}_2} S_d^+ c^\dagger_{{\bf k}_1 \downarrow} c_{{\bf k}_2 \uparrow}\sum_{{\bf q} \in \text{PS}}\left(J_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} + J_{{\bf \bar q}, {\bf q}} W_{{\bf q}, {\bf k}_2, {\bf k}_1, {\bf \bar q}}\right)G_J~.
-\end{aligned}\end{equation}
-
-\subsubsection{Net renormalisation to the Kondo interaction}
-%\subsubsection*{Net renormalisation to the Kondo interaction}
-Combining the results, the total renormalisation in the momentum-resolved Kondo coupling \(J^{(j)}\) at the \(j^\text{th}\) step amounts to
-\begin{equation}\begin{aligned}
-	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}
-\end{aligned}
-\label{rgeq2}\end{equation}
-A representation of the RG phase diagram in the $-W/t$ vs.
-$J/t$ plane of couplings has been provided in Fig.\hyperref[spinCorr]{\ref*{spinCorr}(a)} from detailed numerical computations of eq.\eqref{rgeq2}.
-We also provide a schematic representation of RG flows to various fixed point theories in the $J$ vs.
-$W$ plane of couplings in Fig.\ref{rgflows}.
-This schematic figure shows the existence of three distinct phases (Fermi liquid metal, Mott Insulator, and Pseudogap-Mott metal) described by distinct fixed point theories of the RG flows.
-The Fermi liquid metal and Mott Insulator phases are distinguished from the Pseudogap-Mott metal by separatrices of the RG flows.
-\begin{figure}
-    \centering
-    \includegraphics[width=0.5\linewidth]{RGflows.pdf}
-    \caption{Renormalisation group (RG) flow diagram of the lattice model as obtained from a unitary RG analysis of the lattice-embedded impurity model.
-For $|W/J| < |W/J|_\text{PG}$, the flows lead to a Fermi liquid phase, while for $|W/J| < |W/J|_\text{c}$, they lead to a Mott insulator.
-For values in between, the system flows to a Mott metal phase that has a pseudogap in the density of states.}
-    \label{rgflows}
-\end{figure}
-
-\section{Theory for the nodal non-Fermi liquid as an effective Hatsugai-Kohmoto model}
-As the bath interaction \(W\) is tuned through the L-PG phase, the nodal region is the last to decouple from the impurity.
-This allows us to write down a simpler Kondo model near the transition, where only the nodal region is hybridising with the impurity spin through Kondo interactions.
-This is done by retaining only those scattering processes \({\bf k}_1 \to {\bf k}_2\) that originate from and end at \(k-\)points within a small neighborhood of width \(|{\bf q}|\) around the four nodal points: \({\bf k}_1, {\bf k}_2 \in {\bf N} + {\bf q}, |{\bf q}| \ll \pi\), where \({\bf N}\) can be any one of the four nodal points \({\bf N}_{1} = \left(\pi/2, \pi/2\right), {\bf N}_{2} = \left(-\pi/2, \pi/2\right)\) and \({\bf N}_1 + {\bf Q}_1\) and \({\bf N}_{2} + {\bf Q}_2\), where \({\bf Q}_1 = \left(-\pi,-\pi \right)\) and \({\bf Q}_2 = \left( \pi, -\pi \right) \) are the two nesting vectors.
-We assume that the window of \({\bf q}\) is small enough so that the fixed point Kondo coupling values \(J^*({\bf q}_1, {\bf q}_2)\) for the scattering processes involving \({\bf q}_1\) and \({\bf q}_2\) can be replaced by an average value \(J^*\).
-
-With these considerations, the simplified low-energy model near the transition describing the Kondo scattering processes can be written as
-\begin{equation}\begin{aligned}
-	\tilde H_\text{imp-cbath} = J^*\frac{1}{2}\sum_{l=1,2}\sum_{{\bf q}_1, {\bf q}_2}\sum_{\alpha,\beta}{\bf S}_d\cdot{\boldsymbol \sigma}_{\alpha\beta}\left(c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} + c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta}  - c^\dagger_{{\bf N}_l + {\bf Q}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf q}_2,\beta} \right.\\
-    \left.- c^\dagger_{{\bf N}_l + {\bf q}_1,\alpha}c_{{\bf N}_l + {\bf Q}_l + {\bf q}_2,\beta}\right)~.
-\end{aligned}\end{equation}
-The label \(l\) can take values 1 or 2, allowing us to consider both the decoupled channels in the PG (associated with \({\bf N}_1\) and \({\bf N}_2\)).
-It also labels the nesting vectors \({\bf Q}_l\) associated with the two sets.
-\(\alpha\) and \(\beta\) indicate spin indices, and \({\bf q}_1\) and \({\bf q}_2\) represent incoming and outgoing momenta in the scattering processes.
-
-Because of the decoupling of the channel \(l=1\) and \(l=2\), we consider only the \(l=1\) channel for the rest of the calculations in this section.
-In order to simplify the Hamiltonian, we define new fermionic operators
-\begin{equation}\begin{aligned}
-	\psi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} + c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~, ~\phi_{{\bf q}, \sigma} = \frac{1}{\sqrt 2}\left(c_{{\bf N}_1 + {\bf q},\sigma} - c_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma}\right)~,
-\end{aligned}\end{equation}
-The operator satisfy fermionic anticommutation relations. For convenience, we define new number operators for the sum and relative degrees of freedom:
-\begin{equation}\begin{aligned}
-	s_{{\bf q},\sigma} = {\psi}^\dagger_{{\bf q}} {\psi}_{{\bf q}},~ r_{{\bf q},\sigma} = {\phi}^\dagger_{{\bf q}} {\phi}_{{\bf q}}~.
-\end{aligned}\end{equation}
-We then have the following useful relation between the corresponding number operators \(n = c^\dagger c\):
-\begin{equation}\begin{aligned}\label{numberOperatorRelation}
-	n_{{\bf N}_1 + {\bf q},\sigma} + n_{{\bf N}_1 + {\bf Q}_1 - {\bf q}, \sigma} = s_{{\bf q}, \sigma} + r_{{\bf q},\sigma}~.
-\end{aligned}\end{equation}
-
-In terms of these new degrees of freedom, the auxiliary model Hamiltonian takes the form
-\begin{equation}\begin{aligned}
-	\tilde H = -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow} + \sum_{{\bf q}_1, {\bf q}_2,\alpha,\beta}J^*{\bf S}_d\cdot{\boldsymbol\sigma}_{\alpha\beta} {\phi}^\dagger_{{\bf q}_1\alpha} \phi_{{\bf q}_2\beta} + \sum_{{\bf q},\sigma}\varepsilon_{{\bf N}_1 + {\bf q}}\left({\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma} + {\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma}\right),
-\end{aligned}\end{equation}
-where we have considered a simplified form of the bath interaction (for the channel \(l=1\)), taking into account the density-density correlations in \(k-\)space.
-
-For bath interaction strength close to the critical value (\(W \lesssim W_c\)), the fixed point coupling value \(J^*\) is much smaller than \(W\).
-In order to obtain the gapless excitations of the system arising from the presence of the impurity site, we integrate out the impurity dynamics via a Schrieffer-Wolff transformation.
-The perturbation term \(\mathcal{V}\) then consists of Hamiltonian terms that modify the impurity configuration,
-\begin{equation}\begin{aligned}
-	\mathcal{V} = \sum_{{\bf q},\sigma}\varepsilon_{{\bf N}_1 + {\bf q}}\left({\psi}^\dagger_{{\bf q},\sigma} {\phi}_{{\bf q},\sigma} + {\phi}^\dagger_{{\bf q},\sigma} \psi_{{\bf q},\sigma}\right) + \sum_{{\bf q}_1, {\bf q}_2}J^*{S}_d^+{\phi}^\dagger_{{\bf q}_1 \downarrow} \phi_{{\bf q}_2 \uparrow} + \text{h.c.}~,
-\end{aligned}\end{equation}
-while the ``non-interacting" Hamiltonian is
-\begin{equation}\begin{aligned}
-	H_D &= -\frac{1}{2}W\sum_{{\bf q},\sigma}r_{{\bf q},\sigma} + W\sum_{{\bf q}_1,{\bf q}_2}r_{{\bf q}_1,\uparrow} r_{{\bf q}_2,\downarrow}~.
-\end{aligned}\end{equation}
-For the present Hamiltonian, the low-energy state is the one that minimises the bath interaction term \(\tilde H_\text{cbath-int}\).
-High-energy states are obtained by applying, on the state \(\ket{L}\), the excitation operator \(\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2,\bar\sigma}\) or its hermitian conjugate.
-
-The complete second-order renormalised Hamiltonian is
-\begin{equation}\begin{aligned}
-    \Delta \tilde H =& \sum_{{\bf q}, \sigma}\epsilon_{\bf q} r_{{\bf q},\sigma} + \mathcal{U}\sum_{{\bf q}, \sigma}r_{{\bf q} \sigma}r_{{\bf q} \bar\sigma} + \mathcal{U}\sum_{{\bf q}_1 \neq {\bf q}_2, \sigma}\left[r_{{\bf q}_1 \sigma}r_{{\bf q}_2 \bar\sigma} + \phi^\dagger_{{\bf q}_1,\bar\sigma}\phi^\dagger_{{\bf q}_1,\sigma}\phi_{{\bf q}_2, \sigma}\phi_{{\bf q}_2, \bar\sigma}\right]~.
-\end{aligned}\end{equation}
-where $\epsilon_{\bf q} = \text{sign}\left(\varepsilon_{{\bf N}_1 + {\bf q}}\right)\frac{\varepsilon_{{\bf N}_1 + {\bf q}}^2}{-W}$ and $\mathcal{U} = \frac{{J^*}^2}{4W}$.
-\end{widetext}
-
-\end{document}

### 2025-12-13 submissions/TilingUploadNJPResponse/RefereeResponse.tex
finished response to referee 1

@@
 \newcommand{\shat}{\hat{\mathbf{s}}}
-\newcommand{\response}[1]{{\bf Response. }{\color{blue}{#1}}}
+\newcommand{\question}[1]{\par \noindent {\bf Question.\quad}{#1}\\}
+\newcommand{\response}[1]{\par \noindent {\bf Response.\quad}{\color{blue}{#1}}\\[1em]}
 
@@
 We are encouraged by the overall positive reception of our work, including the acknowledgement of its relevance, technical soundness, and suitability for publication in New Journal of Physics.
-
-Below, we present our responses (in blue) to the points raised by the referees.
+Below, we present our responses ({\color{blue}in blue}) to the points raised by the referees.
 
 \section*{Response to Referee 1}
-The authors proposed the possibility that the pseudogap phase is a distinct quantum phase characterized by the so-called Mott metal. I recommend sending the manuscript to reviewers.
+\question{The authors proposed the possibility that the pseudogap phase is a distinct quantum phase characterized by the so-called Mott metal. I recommend sending the manuscript to reviewers.}
 
 \section*{Response to Referee 2}
-The impurity-to-lattice tiling procedure and unitary renormalization group (URG) methods, while carefully implemented, appear to extend prior impurity-based constructions rather than introduce a fundamentally new paradigm.
-The claimed "controlled route to Mott criticality" should be more clearly distinguished from existing dynamical mean-field theory (DMFT) and functional renormalization group (fRG) approaches, particularly in terms of predictive power or access to uncharted regimes.
+\question{The impurity-to-lattice tiling procedure and unitary renormalization group (URG) methods, while carefully implemented, appear to extend prior impurity-based constructions rather than introduce a fundamentally new paradigm.
+The claimed "controlled route to Mott criticality" should be more clearly distinguished from existing dynamical mean-field theory (DMFT) and functional renormalization group (fRG) approaches, particularly in terms of predictive power or access to uncharted regimes.}
 
-\response{}
+\response{We thank the referee for their query about the novelty of the present method.
+The functional renormalisation group (FRG) approach is somewhat distict from the tiling method, since it works directly on a lattice model and is therefore not an impurity-based construction.
+For comparisons of the unitary renormalisation group approach to FRG, please see \cite{anirbanurg1,anirbanurg2}.
 
-The identification of the pseudogap as a "Mott metal" with deconfined holon-doublon excitations is intriguing but lacks direct experimental or numerical validation beyond the model itself.
-Comparisons with established benchmarks from quantum Monte Carlo, ARPES, or optical conductivity experiments on cuprates would help ground these claims and clarify the added value beyond prior theoretical proposals.
+	In comparison to DMFT and its cluster variants, our impurity-based tiling approach derives lattice Hamiltonians directly from renormalized local dynamics - without relying on mean-field approximations - this method preserves nonlocal correlations and enhances momentum-space resolution.
+It is also straightforward to incorporate multi-orbital degrees of freedom, frustrated geometries, and nontrivial band topology -- one simply needs to solve an impurity model with a suitable impurity-cluster or conduction bath.
+Moreover, coupled with the unitary renormalisation group (URG) method as the impurity solver, this approach provides access to one-particle as well as two-particle correlations, entanglement measures and several dynamical quantities, making the method very versatile.
+The URG does not suffer from the fermion sign problem, allowing it to access zero temperature, and it is computationally less intensive than other zero temperature methods such as the numerical renormalisation group.
 
-\response{hi}
+We hope that this is convincing evidence that the present approach is fundamentally different from existing auxiliary model approaches, and comes with several advantages over such methods.
+We have now improved the introduction to reflect this.}
 
-The restriction to a single-band extended Hubbard model on a square lattice limits the generality of the conclusions.
-Demonstrating the framework's applicability to at least one additional model or geometry would strengthen its broad relevance to correlated systems.
+\question{The identification of the pseudogap as a "Mott metal" with deconfined holon-doublon excitations is intriguing but lacks direct experimental or numerical validation beyond the model itself.
+Comparisons with established benchmarks from quantum Monte Carlo, ARPES, or optical conductivity experiments on cuprates would help ground these claims and clarify the added value beyond prior theoretical proposals.}
 
-\response{}
+\response{We appreciate the concern raised by the referee.
+We would like to point out that the manuscript already contains a comparison of our results to optical conductivity experiments on the cuprates (see the last two paragraphs of Sec V.B).
+As per the referee's suggestion, we have now also added a comparison of our results with quantum Monte Carlo calculations and ARPES experiments (see Secs.
+VI and VII), and they provide further support for our characterisation of the Mott metal.}
 
-Critical experimental realities such as disorder, doping inhomogeneity, or phonon coupling are not addressed.
-A discussion of how such effects could be incorporated or might alter the conclusions is necessary to assess the experimental relevance of the proposed mechanism.
+\question{The restriction to a single-band extended Hubbard model on a square lattice limits the generality of the conclusions.
+Demonstrating the framework's applicability to at least one additional model or geometry would strengthen its broad relevance to correlated systems.}
 
-\response{hi}
+\response{We thank the referee for pointing this out.
+Our goal with the present work has been to provide a concrete demonstration of a new auxiliary mode approach through a very comprehensive and detailed exploration of a paradigmatic model.
+We therefore humbly submit that the extension of our approach to other models be left for future works.
+Indeed, in an ongoing work, we have applied the tiling method to a bilayer extended Hubbard model and are studying its various properties in order to tackle the phenomenology of heavy fermion materials.}
 
-The connection to the Hatsugai-Kohmoto model at criticality, while mathematically interesting, risks being viewed as a special case.
-The authors should clarify whether this connection holds for generic models or relies on fine-tuned symmetries or fillings.
+\question{Critical experimental realities such as disorder, doping inhomogeneity, or phonon coupling are not addressed.
+A discussion of how such effects could be incorporated or might alter the conclusions is necessary to assess the experimental relevance of the proposed mechanism.}
 
-\response{hi}
+\response{We thank the referee for this question.
+We would like to humbly submit that introducing disorder, doping inhomogeneity, or phonon coupling into our model is beyond the scope of the present work, and so we defer such treatments to a later work.
+We have however updated the conclusions section with a discussion of how one might treat these aspects within our approach.}
+
+\question{The connection to the Hatsugai-Kohmoto model at criticality, while mathematically interesting, risks being viewed as a special case.
+The authors should clarify whether this connection holds for generic models or relies on fine-tuned symmetries or fillings.}
+
+\response{We appreciate this technical point raised by the referee.
+Indeed, the present work demonstrates that the Hatsugai-Kohmoto (HK) model arises at criticality for this particular model.
+Nevertheless, the (i) simplicity of our lattice model, and (ii) the universality of our Mott metal phase (in terms of various exponents) is strong evidence that the HK model is likely to be found whenever a "coexistence" phase of Luttinger and Fermi surfaces undergoes a transition into a Mott insulator.}
 
 \section*{Response to Referee 3}
-In the present manuscript the authors have studied the interplay between the spin exchange and local Coulomb interaction in a two-dimensional model by employing a unitary renormalization group (URG).
-This work can be considered as a continuation of the author's previous published works.
-While I found that the URG is acceptable for treating electron correlation problems, the principal model studied in this manuscript (Eq.
+\question{While I found that the URG is acceptable for treating electron correlation problems, the principal model studied in this manuscript (Eq.
 (15)) looks like an artefact, because the spin exchange  (the second term in Eq.
@@
 (15)).
-Therefore, the studied model already double-counts the spin exchange.
-In addition, it is not clear what real materials or systems can be described by the studied model.
-The authors have to clarify these points before the manuscript can be acceptable for publication.
+Therefore, the studied model already double-counts the spin exchange.}
+\response{We appreciate this technical point raised by the referee.
+Indeed, the present work demonstrates that the Hatsugai-Kohmoto (HK) model arises at criticality for this particular model.
+Nevertheless, the (i) simplicity of our lattice model, and (ii) the universality of our Mott metal phase (in terms of various exponents) is strong evidence that the HK model is likely to be found whenever a "coexistence" phase of Luttinger and Fermi surfaces undergoes a transition into a Mott insulator.}
+\question{In addition, it is not clear what real materials or systems can be described by the studied model.
+The authors have to clarify these points before the manuscript can be acceptable for publication.}
+\response{We appreciate this technical point raised by the referee.
+Indeed, the present work demonstrates that the Hatsugai-Kohmoto (HK) model arises at criticality for this particular model.
+Nevertheless, the (i) simplicity of our lattice model, and (ii) the universality of our Mott metal phase (in terms of various exponents) is strong evidence that the HK model is likely to be found whenever a "coexistence" phase of Luttinger and Fermi surfaces undergoes a transition into a Mott insulator.}
 
 \section*{Response to Referee 4}
-The manuscript addresses metal-to-insulator transition in strongly correlated lattice models applicable to materials such as layered copper oxides, with particular focus on intermediate pseudogap (PG) state.
-First, a lattice impurity model is formulated, and subsequently mapped to a lattice t-J-U model via tiling procedure.
-The Authors subsequently map the Green's functions from the auxiliary impurity model to the target t-J-U model, and analyze its dynamical phase diagram as a function of microscopic parameters.
-The employed methodology is based on solving normalization group equations for the auxiliary model and translating the results into the of target lattice model language via derived mapping.
-The Authors link the PG state to the to the breakdown of the Kondo screening within the underlying auxiliary model, and provide a comprehensive theoretical analysis of thereof.
 
-I have looked through it with interest, and I have several comments and queries:
+\question{The Authors consider the model with nearest-neighbor hopping (t') integrals only, which is also reflected in the target lattice model.
+It is well known that t' is highly relevant to the physics of systems exhibiting pseudogap (such as high-Tc cuprates).
+Is it possible to incorporate those terms within the present method and is there any qualitative change expected?}
 
-1.
-The Authors consider the model with nearest-neighbor hopping (t') integrals only, which is also reflected in the target lattice model.
-It is well known that t' is highly relevant to the physics of systems exhibiting pseudogap (such as high-Tc cuprates).
-Is it possible to incorporate those terms within the present method and is there any qualitative change expected?
-2.
-The Hamiltonian term $H_coup$ [Eq.
+\question{The Hamiltonian term $H_coup$ [Eq.
 (3)] incorporates both hybridization and Kondo-type exchange.
@@
 Can, for instance, either V or J term be neglected in the analysis?
-What would be the consequences for PG state?
-3.
-Technical remarks: In Eq.
-(3), J should be probably a function of Z to reproduce k-dependen form of J in Eq.
-(5).
-Apparently in Eq.
-(A1) of the first Appendix this is the case.
-Also, it is not immediately clear to me why the impurity creation and annihilation operators disappear from the impurity model (1) following tiling procedure in Sec.
+What would be the consequences for PG state?}
+\question{Technical remarks: In Eq. (3), J should be probably a function of Z to reproduce k-dependen form of J in Eq. (5). Apparently in Eq. (A1) of the first Appendix this is the case.}
+\question{Also, it is not immediately clear to me why the impurity creation and annihilation operators disappear from the impurity model (1) following tiling procedure in Sec.
 III, resulting in single-band Hamiltonian (15).
-This could be explained in grater detail in the manuscript.
-4.
-The lattice model of Eq.
+This could be explained in grater detail in the manuscript.}
+\question{The lattice model of Eq.
 (15), referred to by the Authors as extended-Hubbard, has been extensively studied in literature in the context of high-Tc superconductors as the t-J-U model.
 See, e.g., https://doi.org/10.1103/PhysRevB.95.024506 or a review https://doi.org/10.1016/j.physrep.2022.02.003 and references therein.
-Comparison with previous work on t-J-U model would benefit the manuscript.
-5.
-Whereas the Authors work is clearly relevant to specific materials, such and layered copper oxides, nickelates, and possibly several other systems, the discussion of specific experimental consequences is limited.
-The manuscript would benefit from more direct and detailed relation to specific materials in the introduction and/or summary section.
+Comparison with previous work on t-J-U model would benefit the manuscript.}
+\question{Whereas the Authors work is clearly relevant to specific materials, such and layered copper oxides, nickelates, and possibly several other systems, the discussion of specific experimental consequences is limited.
+The manuscript would benefit from more direct and detailed relation to specific materials in the introduction and/or summary section.}
 
-The manuscript is well written and organized.
-The methodology appears sound and the mapping of the auxiliary to physical model is of interest.
-I believe that the manuscript could be suitable for publication in NJP, following clarification of the above points.
-
+\bibliography{tilingProject.bib}
+\bibliographystyle{apsrev}
 \end{document}

### 2025-12-13 submissions/TilingUploadNJPResponse/manuscript_NJP.tex
finished response to referee 1

--- 2025-12-10 submissions/TilingUploadNJP/manuscript_NJP.tex
@@
 By deriving lattice Hamiltonians directly from renormalized local dynamics - without relying on mean-field approximations - this method preserves nonlocal correlations and enhances momentum-space resolution.
-It thus provides a versatile and controlled route for engineering strongly correlated models, particularly in regimes where PG formation, NFL scaling, and Mott physics intersect.
+{\color{blue} Coupled with the unitary renormalisation group method as the impurity solver, this approach provides access to one-particle as well as two-particle correlations, entanglement measures and several dynamical quantities, making the method very versatile.} It thus provides a versatile and controlled route for engineering strongly correlated models, particularly in regimes where PG formation, NFL scaling, and Mott physics intersect.
 
@@
 The second term creates gapped excitations involving the regions of zero and double occupancy; these represent subdominant pairing fluctuations of the nodal non-Fermi liquid.
+{\color{blue} We recall that similar fluctuations across the Fermi surface were observed in our calculations of charge correlations in Fig.~\ref{chargeCorr} (a), and are consistent with pairing fluctuations observed from quantum Monte Carlo simulations and found to give rise to quantum-critical behavior and PG physics~\cite{Jiang2022}.}
 
@@
 This signals the NFL Fermi arcs of the PG as an emergent phase of strongly interacting quantum matter - which we dub the {\it Mott metal} - that is the parent metal of the MI.
-The same topological principle connects the nonlocal unparticle-like gapless excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} of the scale-invariant nodal NFL of the HK model observed precisely at the Mott critical point to those of the rest of the PG phase, e.g., a universal scaling of $\Sigma''_{{\bf k}}(\omega)\sim (a + \omega^{2})^{-1}$ (Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(b)}) and local density of states $A_{d}(\omega) \sim \omega^{2}$ (Fig.~\hyperref[ImpSpecFuncFits]{\ref*{ImpSpecFuncFits}}) of the NFL throughout the PG phase, such that the value of $\Sigma''_{{\bf k}}(\omega=0)$ value continues to grow upon violating the MIR bound (Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(c)}).
+{\color{blue} Such an identification of the pseudogap as a distinct phase is backed up by angle-resolved photoemission spectroscopy (ARPES) experiments~\cite{Hashimoto2014}; the anomalous momentum, temperature and doping dependence of the gap function observed in the cuprates suggests that the pseudogap maybe described by an order parameter distinct from that of the superconductor~\cite{Hashimoto2012,Vishik2009}.} The same topological principle connects the nonlocal unparticle-like gapless excitations~\cite{Georgi2007PRL,Georgi2007,Phillips2013Unparticles,PhillipsLectures2014} of the scale-invariant nodal NFL of the HK model observed precisely at the Mott critical point to those of the rest of the PG phase, e.g., a universal scaling of $\Sigma''_{{\bf k}}(\omega)\sim (a + \omega^{2})^{-1}$ (Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(b)}) and local density of states $A_{d}(\omega) \sim \omega^{2}$ (Fig.~\hyperref[ImpSpecFuncFits]{\ref*{ImpSpecFuncFits}}) of the NFL throughout the PG phase, such that the value of $\Sigma''_{{\bf k}}(\omega=0)$ value continues to grow upon violating the MIR bound (Fig.~\hyperref[selfEnergy]{\ref*{selfEnergy}(c)}).
 
@@
 It's fate under finite doping presents a compelling direction for future investigation.
+{\color{blue} More complicated models can be studied by suitably extending the tiling approach and choosing an appropriate auxiliary model.
+Electron-phonon coupling can be taken into account by studying an Anderson-Holstein model that couples the impurity site to local lattice modes~\cite{ACHewson_2002}.
+The effects of disorder can be studied by averaging quantities over various disorder configurations of the conduction bath.
+The versatility of the unitary RG solver and the impurity model-based construction makes it convenient to explore a large variety of lattice models.}
 

### 2025-12-13 submissions/TilingUploadNJPResponse/RefereeResponse.tex
almost done with all responses

@@
 Therefore, the studied model already double-counts the spin exchange.}
-\response{We appreciate this technical point raised by the referee.
-Indeed, the present work demonstrates that the Hatsugai-Kohmoto (HK) model arises at criticality for this particular model.
-Nevertheless, the (i) simplicity of our lattice model, and (ii) the universality of our Mott metal phase (in terms of various exponents) is strong evidence that the HK model is likely to be found whenever a "coexistence" phase of Luttinger and Fermi surfaces undergoes a transition into a Mott insulator.}
+\response{We thank the referee for the question.
+The Hamiltonian in eq.~(15) of the original manuscript describes an extended Hubbard model, also known as the $t-J-U$ model elsewhere in the literature~\cite{spalek20221}.
+The nearest-neighbour spin-exchange coupling \(J\) in such a model can be regarded as arising from inter-band superexchange processes in a more complete multi-band model.
+Such processes are distinct from the ones that lead to a $t^2/U$ spin-exchange contribution arising from hopping processes within a single band.
+As a result, the coupling \(J\) is not an overcounting of processes, but represents a distinct physical mechanism.
+
+We have now clarified this point in the manuscript, below eq.~(15).}
+
 \question{In addition, it is not clear what real materials or systems can be described by the studied model.
 The authors have to clarify these points before the manuscript can be acceptable for publication.}
-\response{We appreciate this technical point raised by the referee.
-Indeed, the present work demonstrates that the Hatsugai-Kohmoto (HK) model arises at criticality for this particular model.
-Nevertheless, the (i) simplicity of our lattice model, and (ii) the universality of our Mott metal phase (in terms of various exponents) is strong evidence that the HK model is likely to be found whenever a "coexistence" phase of Luttinger and Fermi surfaces undergoes a transition into a Mott insulator.}
+\response{We are grateful to the referee for bringing this up.
+Given the minimal nature of the model studied here, we expect the conclusions derived here to apply to a large class of strongly correlated electronic systems on a 2D square lattice, prime example are the copper oxide materials.
+This is further supported by the similarity in the phenomenology of such materials and the various phases observed in the present work.
+Moreover, by considering multiple layers of the model studied here, it should be possible to describe heavy fermion materials as well.
+}
 
@@
 Is it possible to incorporate those terms within the present method and is there any qualitative change expected?}
+\response{We thank the referee for this question.
+It is certainly possible to incorporate a next-nearest nearest-neighbour hopping term within our approach, by suitably modifying the impurity model: the impurity-bath hybridisation will extend to beyond the nearest sites, and the conduction bath dispersion will have to be modified.
+Nevertheless, we would like to note that our extended Hubbard model is already able to capture much of the physics of the cuprate superconductor, such as the strange metal, pseudogap and Mott insulating phases.
+Incorporating the effects of longer ranged hopping would require a separate work, and we leave that for the future.
+}
 
-\question{The Hamiltonian term $H_coup$ [Eq.
+\question{The Hamiltonian term $H_\text{coup}$ [Eq.
 (3)] incorporates both hybridization and Kondo-type exchange.
@@
 What would be the consequences for PG state?}
+\response{We are grateful to the referee for bringing this up.
+The Hamiltonian in eq.~(15) of the manuscript describes an extended Hubbard model, also known as the $t-J-U$ model elsewhere in the literature~\cite{spalek20221} (we thank the referee for pointing out this reference).
+The nearest-neighbour spin-exchange coupling \(J\) in such a model can be regarded as arising from inter-band superexchange processes in a more complete multi-band model.
+In the corresponding impurity model, this corresponds to working with a multi layer impurity model, each layer with its own impurity site and then allowing for hopping processes that connect the impurity sites.
+Such processes are distinct from the ones that lead to a $t^2/U$ spin-exchange contribution arising from hopping processes within a single band.
+As a result, the coupling \(J\) is not an overcounting of processes, but represents a distinct physical mechanism.}
+
 \question{Technical remarks: In Eq. (3), J should be probably a function of Z to reproduce k-dependen form of J in Eq. (5). Apparently in Eq. (A1) of the first Appendix this is the case.}
+\response{We thank the referee for bringing this up.
+The symbol \(Z\) in eq.~(3) represents the four sites that surround the impurity site in the lattice-embedded impurity model.
+So, if the impurity site is located at \(r_d\), \(Z\) takes the values \(r_d \pm a_1\) and \(r_d \pm a_2\) where \(a_1=a\hat x\) and \(a_2=a \hat y\) are the primitive vectors on the square lattice.
+Since we have assumed that the impurity site hybridises with equal strength with all four nearest-neighbour sites, the Kondo coupling is in fact {\it independent} of \(Z\).
+
+In eq.~(A1), the Kondo coupling \(J\) is written in momentum space.
+Since the coupling is local in real-space, it does acquire a \(k-\)dependence, which is reflected through the subscript \(q\) in that equation.
+In summary, it appears that the equations are correct as they are.
+}
+
 \question{Also, it is not immediately clear to me why the impurity creation and annihilation operators disappear from the impurity model (1) following tiling procedure in Sec.
@@
 This could be explained in grater detail in the manuscript.}
+\response{
+	We thank the referee for this question.
+The disappearance of the impurity operators from the impurity model in eq.~(1) to the tiled model in eq.~(15) can be understood from the definition in eq.~(11).
+The tiled Hamiltonian of eq.~(15) is obtained by translating the impurity Hamiltonian of eq.~(1) over all sites of the lattice.
+This is equivalent to considering distinct representations of the impurity model where the impurity site is placed at a any arbitrary site \(\bf r\) and then summing over all such representations.
+This results in the single impurity index \(r_d\) in eq.~(1) getting replaced with the variable \(r\) which sums over all lattice sites, in eq.~(15).
+We have now explicitly clarified this in the manuscript.
+}
 \question{The lattice model of Eq.
@@
 Comparison with previous work on t-J-U model would benefit the manuscript.}
+
 \question{Whereas the Authors work is clearly relevant to specific materials, such and layered copper oxides, nickelates, and possibly several other systems, the discussion of specific experimental consequences is limited.
